### 2020-10-23 NSF2020/GVP.tex
Add files via upload

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\title{Geometric variational problems}
\usepackage{natbib}
\usepackage{graphicx}

\usepackage{amssymb,amsthm,amsmath,mathrsfs,graphics,amsfonts,bbm, commath, accents}

\author{Specific Aim}
\date{October 2020}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

We aim to derive mathematically a two-dimensional energy of a fluid lipid monolayer and or bilayer from HAP theory in the limit of small particle sizes. In this case, small refers to lengths much smaller than monolayer thickness. Recalling the continuum approach, the HK theory of membrane elasticity derives the two-dimensional energy density of a fluid lipid monolayer using the general expression for a three-dimensional energy of a test volume in the hydrophobic core. As an assumption, the three-dimensional energy density is quadratic in the displacement gradients, and these displacements quantify, up to second order, the change in pairwise interactions that result from the deforming the reference volume. In other words, HK theory assumes a pairwise interaction between lipids. As we have shown, HAP is non-pairwise and so the theory resulting from taking small particle sizes would purportedly include extra effects like non-local energies of integral equation type, along with the local elastic deformations already present in the Helfrich theory. 
To make progress, it is necessary to understand firstly how HAP behaves under certain mathematical limits. In the case of lipid monolayers, there are limits in the screening length, the particle diameter, a slender body limit, or any combination of the three, for example. Each limit potentially leads to a new variational problem. We illustrates some of these limiting problems and interpret the results physically. Then we pose mathematical conjectures that will help us resolve an effective monolayer energy coming from a hybrid, particle-based approach, going beyond the limitations of elastic theory.
Boundary layer of water activity. An obvious limit is $\rho \to 0$. This limit is motivated by experimental measurements that place $\rho$ in the range of a few Angstrom, which is small compared to membrane thickness. In this limit, HAP converges to surface energy 
\begin{equation}
\lim_{\rho to 0} \min_u \int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2 \,dx = \int_{\partial \Omega} f \,dS 
\end{equation}
Here $f$ is the boundary value. As argues in [], the existence of a minimizer is a straight-forward consequence of the closest point theorem for the Sobolev space $H^1(\Omega)$. 
The $\rho \to 0$ case gives rise to two variational problems: the first is a dilute particle suspension where there is no interaction between particles, and the second is the problem of surface area minimization. If the particles are well-separated relative to the screening length, then \eqref{} states that HAP converges to the surface energy of the particles. That is, the particle interactions vanish in the $\rho \to 0$ limit because the total surface energy of a collection of rigid bodies is constant, and independent of particle position and orientation. This constancy was one of the motivating factors for introducing HAP theory to study lipids. In the case of non-rigid particles or flexible surfaces, the $\rho \to 0$ case corresponds to surface area minimization for the boundary of the domain $\Omega$. 
To see why \eqref{} holds, we recall briefly some of the properties of the elliptic boundary value problems associated with HAP theory. In HAP theory, the surface interactions are the Dirichlet-type energy of the solution to the screened-Laplace equation boundary value problem. The solution to the boundary value problem is a scalar function, which we call water activity, or just activity for short. Recall that an activity value near 0 represents water that can form hydrogen bonds freely in all directions, and a value near 1 represent water that lacks the ability to form hydrogen bonds in one direction, as is the case for a water molecule adjacent to an apolar surface.
In the direction normal to a surface, activity behaves like the solution to the one-dimensional problem $\rho^2 u_{xx} + u = 0$, which decays like $exp(x/\rho)$ in the distance r to the boundary. Based on barrier arguments, the activity has a boundary layer of thickness $\rho$. Using the boundary layer estimates, it is possible to show that the HAP three-dimensional energy density converges to two-dimensional surface measure with weight $1 = \int_0^{\infty} \rho (u’)^2 + \rho^{-1} u^2 \,d x$.

It is instructive to consider the boundary layer behavior around a disk of radius $a$. The boundary of the 
disk is hydrophobic, so we set $u = 1$ there. The solution is 
\begin{equation}
    u(x) = \frac{K_0(|x|/\rho)}{K_0(a/\rho)}
\end{equation}
where $K_{\nu}(z)$ is the modified Bessel function of the second kind []. We can use integration by parts to calculate
the hydrophobic interaction (in the case of a single disk, there is no interaction).
\begin{align*}
\Phi
    &= \gamma \int_{|x| > a} \rho |\nabla u|^2 + \rho^{-1} u^2 \,dx \\
    &= \gamma \int_{|x| = a} \rho  u \nabla u \cdot \nu \, ds + \int_{|x| > a|} \rho^{-1} u (-\rho^2 \Delta u + u) \,dx \\
    &= \gamma \int_{|x| = a} \rho \frac{\partial u}{\partial \nu} \,ds
\end{align*}
The latter simplifications occur because $u$ solves the screened Laplace equation with constant boundary condition. Continuing, for $|x| = a$,
\begin{align*}
\Phi 
&= -2 \pi a \gamma \rho \nabla \frac{K_0(|x|/\rho)}{K_0(a/\rho)}\cdot \frac{x}{|x|}\\
&= -2 \pi a \gamma \frac{K_0'(a/\rho)}{K_0(a/\rho)}  \\
&=  2 \pi a \gamma \frac{K_1(a/\rho)}{K_0(a/\rho)}  
\end{align*}
where we have used the relationship $K_0'(z) = -K_1(z)$. 
A particle of vanishing size corresponds to fixing $\rho$ and taking $a = 0.$ Here we 
utilize $K_1(z) \sim 1/z$ and $K_2(z) \sim \log(2/z)$ as $z \to 0^+$. We find
\begin{equation}
    \lim_{a \to 0} \Phi = \lim_{a \to 0} 2\pi  a \gamma \frac{\rho/a}{\log(2\rho/a)} = 0.
\end{equation}
This indicates that the energy of a single particle vanishes with the particle diameter.
The mathematical reason for this is that $(n-2)$-dimensional subsets of $\mathbb{R}^n$ have capacitance $0$. The result for a collection of vanishing particles, with fixed position and screen length, is trivial. (The cross terms vanish linearly in $a$.) One way to get a non-trivial interaction is 
by letting interfacial tension $\gamma$, or the boundary value of $u$, vary with $a.$

Alternatively, we can fix $a$ and take $\rho \to 0$. The leading asymptotic behavior
$K_{\nu}(z) \sim \sqrt{\pi/(2z)}e^{-z}$ is independent of $\nu$ for $z \to \infty$. 
As a result, 
\begin{equation}
    \lim_{\rho \to 0} \Phi = 2 \pi a
\end{equation}
In other words, the limiting potential is surface energy.

The situation in three dimensions is similar. Here the fundamental solution takes the form
$k(z) = e^{-z}/z$ and so the activity around a ball of radius $a$ is 
\begin{equation}
    u(x) = \frac{k(|x|/\rho)}{k(a/\rho)}
\end{equation}
and we can calculate $\Phi$ for a ball; the result is 
\begin{equation}
\Phi = 4 \pi a^2 \gamma ( 1 + \rho/a)
\end{equation}
This functional vanishes for $a \to 0$ and converges to surface energy for $\rho \to 0.$

For arbitrary class $C^2$ domains, with $u = 1$ on the boundary, we can write
\begin{equation}
    \Phi = \gamma \int_{\partial \Omega} \rho \frac{\partial u}{\partial \nu} \,d \mathcal{H}^{n-1}
\end{equation}
where $d \mathcal{H}^{n-1}$ is the arc length differential in two dimensions and the surface area differential in three dimensions. The region $\Omega$ is an exterior domain to a number of particles.
If the particles are all convex, then we can use \eqref{} or \eqref{} as barrier functions. These 
show that $\frac{\partial u}{\partial \nu} \to 1$ uniformly as $\rho \to 0$.

It is natural to study slender bodies in the context of  amphiphilic particles. 
Interesting interactions show up in the case of slender bodies. Using the above results
and barrier estimates, we can show that in two-dimensions, $\lim_{a \to 0} \Phi \to 2\gamma L$ for a single slender body of fixed length $L$ and vanishing width $a$.

\subsection{Maximum overlap}
\subsection{Curve shortening}
Finally, the last mathematical problem we will study is curve shortening by HAP. Curve shortening refers to the evolution of a simple closed curve along its unit normal
by a speed proportional to the signed curvature. That is 
\begin{equation}
    X_t = -\kappa \mathbf{N}
\end{equation}
Hamilton and later Grayson proved that any simple closed curve stays embedded (does not
self-intersect) under curve shortening, eventually evolves into a convex curve, becoming 
asymptotic to a circle with vanishing radius $r = \sqrt{2(t_0 - t)}$.

Curve shortening is the equation of steepest gradient descent with respect to the arc length functional. The higher dimensional generalization of curve shortening is motion by mean curvature, and here surfaces do not stay embedded. There have been a number of numerical 
techniques devised to study curve shortening and motion by mean curvature, including level set, front tracking and phase field methods to mention a few.

We propose a connection between curve shortening and hydrophobic interactions because, as 
we have shown above, the HAP function converges to perimeter in the limit $\rho \to 0$, and  
we have a non-local curvature in the form of the interfacial stress $\sigma_{\text{hydro}}$.
That is, we propose the evolution equation
\begin{equation}
    X_t = - \sigma_{\text{hydro}} \mathbf{N}
\end{equation}
This new evolution equation satisfies the energy law 
\begin{equation}
    \frac{d}{dt}\Phi(\Omega_t) + \int_{\partial \Omega} |X_t|^2 \,ds = 0  
\end{equation}
and is amenable to numerical approximation using the integral equations methods
described in the previous section. The difference between this a the study of amphiphilic
self-assembly is that the curve is neither rigid nor arc length conserving.
We showed above that $\Phi$ vanishes
in the limit of vanishing diameter and one could expect the curve to vanish under the 
HAP curve shortening flow much in the way it does for the classic evolution.

We will address the following mathematical questions motivated by the original studies
of Hamilton and Grayson: 
\begin{itemize}
\item Do curves stay embedded under \eqref{}, and is the limit an asymptotically vanishing disk?
\item What regularization can one expect from the non-local velocities? 
\item To what extent does \eqref{} contain \eqref{} in the limit $\rho \to 0$? In other words, do curves remain uniformly close under the two evolution processes? 
\end{itemize}

The above problem was posed assuming a constant hydrophobic label. We can generalize the 
situation and consider non-constant hydrophobic labels, representing an interface with a
a non-uniform hydrophobic coating. Here the Lagrangian evolution is the same, but we must
account for transport of the hydrophobic parameter:
\begin{equation}
     X_t = - \sigma_{\text{hydro}} \mathbf{N},\quad
     f_t + f_s \cdot X_t = 0,\quad f(s,0) = f_0(s).
\end{equation}
where $f_s$ is the arc length derivative of the label. 
\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2020-10-23 code/examples/shear.m
adding HAP strength gam into prams

@@ -16,9 +16,8 @@ prams.m = 1000; % number of time steps
 
 prams.order = 2; % time stepping order
 
-prams.rho = 4.0; % screen length
-
-gam = 1.0;  % HAP Strength
+prams.rho = 4.0;  % screen length
+prams.gam = 1.0;  % HAP Strength
 
 prams.RepulLength = 0.3; % repulsion length
 prams.RepulStrength = 0.5; % repulsion strength
@@ -64,5 +63,5 @@ prams.tau   = tau;
 prams.radii = radii;
 prams.ar    = ar;
 
-[Xfinal, trajectory] = rigid2D(options,prams,xc,tau,gam);
+[Xfinal, trajectory] = rigid2D(options,prams,xc,tau);
 %end

### 2020-10-23 code/src/capsules.m

@@ -12,6 +12,7 @@ center;       % center of each rigid body
 tau;          % orientation of each rigid body
 radii;        % radius of each rigid body
 rho;          % screen length of particles
+gam;          % HAP strength
 ar;           % aspect ratio of particles
 xt;           % tangent unit vector
 sa;           % Jacobian
@@ -38,6 +39,7 @@ o.N = prams.N;
 o.nb = prams.nb;
 o.radii = prams.radii;
 o.rho = prams.rho;
+o.gam = prams.gam;
 o.ar = prams.ar;
 o.center = xc; % center
 o.tau = tau; % inclination angle

### 2020-10-23 code/src/poten.m

@@ -96,6 +96,7 @@ prams.nb = geomSou.nb;
 prams.tau = geomSou.tau;
 prams.radii = geomSou.radii;
 prams.rho = geomSou.rho;
+prams.gam = geomSou.gam;
 prams.ar = geomSou.ar;
 prams.RepulLength = geomSou.RepulLength;
 prams.RepulStrength = geomSou.RepulStrength;

### 2020-10-23 code/src/rigid2D.m

@@ -1,10 +1,10 @@
-function [Xfinal, trajectory] = rigid2D(options,prams,xc,tau,gam)
+function [Xfinal, trajectory] = rigid2D(options,prams,xc,tau)
 ttotal = tic; % start a timer
 
 om = monitor(options,prams);
 % build object for doing I/O
 
-tt = tstep(options,prams,gam);
+tt = tstep(options,prams);
 
 % build initial condition of rigid body particle
 geom = capsules(prams,xc,tau);

### 2020-10-23 code/src/tstep.m

@@ -18,7 +18,6 @@ precow          % block-diagonal preconditioner for walls
 potp            % class for fiber layer potentials
 potw            % class for wall layer potentials
 om              % monitor class
-gam             % HAP strength
 precoYukawa
 precoStokes
 
@@ -27,7 +26,7 @@ end % properties
 methods
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function o = tstep(options, prams, gam)
+function o = tstep(options, prams)
 % o.tstep(options,prams): constructor.  Initialize class.  Take all
 % elements of options and prams needed by the time stepper
 
@@ -36,7 +35,6 @@ o.dt = prams.T/prams.m;
 o.gmresTol = options.gmresTol;
 o.plotAxis = options.plotAxis;
 o.farField = @(X) o.bgFlow(X,options); 
-o.gam = gam;
 
 % for screen laplace BVP
 o.janusbc = @(X,tau,center) o.bcfunc(X,tau,center,options);
@@ -54,6 +52,7 @@ X      = geom.X;
 tau    = geom.tau;
 center = geom.center;
 rho    = geom.rho;
+gam    = geom.gam;
 radii  = geom.radii;
 
 % CREATE NEAR SINGULAR INTEGRATION STRUCTURES
@@ -114,8 +113,8 @@ end
 
 %outputs: 
 force  = [F1 + R1, F2 + R2].';
-force  = o.gam*force(:);
-torque = o.gam*(Tq + RTq);
+force  = gam*force(:);
+torque = gam*(Tq + RTq);
 
 %format shortg
 

### 2020-10-27 NSF2020/Description/broaderimpacts.tex
added description source files

\section{Broader Impacts of the Proposed Work}
\label{sec:BroaderImpacts}

The proposed mathematical analysis and modeling will provide a transformative
understanding of the collective dynamics of amphiphilic particles such as 
(1) their self-assembly into micelles and bilayers, and 
(2) the interaction between these building blocks.
Amphiphilic Janus particles have gained increasing popularity for fabrication of smart materials.
The proposed hybrid continuum model, mathematical analysis and numerical algorithms will have transformative impact on
precision design for specific mechanical properties of materials made of amphiphilic nanoparticles.
An important component of this proposal is the interdisciplinary education and training of
both undergraduate and graduate students.  The combination of mathematical modeling, analysis and
scientific computing  in this project provides a compelling
example of the importance of mathematics in biophysics and engineering applications.
The concepts and
methods described here go beyond the context of amphiphilic particles and lipid molecules. They extend
to other problems featuring microscopic phase separation that leads to  formation of mesoscopic domains.
This situation arises, for example, in biological development in systems biology.
The methods developed here have the potential to impact those and other related areas in biomedicine and biotechnology.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
The proposed research will have immediate impact on 
undergraduate and graduate education. At the undergraduate level,
the project will involve and support undergraduate researcher from Fordham University.
The supported summer researchers will gain valuable first-hand 
experience in inherently interdisciplinary, mathematical fluid modeling and computation.
We will incorporate research into teaching, especially in differential equation  
and programming courses.

Over the past eight years, PI Ryham has included many undergraduates 
in the execution of research initiatives, coauthoring 
publications. He has a  track record for supporting underrepresented groups,
being called on by the Collegiate Science and Technology Entry Program (CSTEP) to make
opportunities for promising students, for example. He has mentored
two Clare Boothe Luce Scholars, one a U.S. Marine Corp veteran,
and a high school student in the NYU GSTEM program.

The PIs will capitalize on the synergy between NJIT's doctoral program in Mathematical Sciences 
and Fordham's undergraduate focus in the Department of Mathematics. 
Promising, young undergraduate scientists from the Bronx community 
while find a natural pipeline into graduate studies through working directly 
or indirectly on this project. 
On the graduate-level education, PI Young and co-PI Jiang expect to train and support
a PhD student, Yuexin Liu (who is in her third-year at NJIT) for two more years. Yuexin Liu has past experiences
in the undergraduate training program at NJIT, and will train an undergraduate intern. 
The PIs will foster vertical integration between the senior personnel, their collaborators, postdocs, 
doctoral and Bachelor students, enhancing the
learning environment.
%

%The PIs expect
%to involve undergraduate students in this project through
%their continuing and active involvement in undergraduate advising and research mentoring:
%YNY has mentored undergraduate students as a co-Investigator in CSUMS: Research and Education
%in Computational Mathematics for undergraduates in the Mathematical 
%Sciences at NJIT (funded by NSF) and the lecturer for Capstone Applied
%Mathematics Lab at NJIT (also funded by NSF).
%YNY has track records in involving undergraduate students in research
%that emphasizes both numerical computations and desktop experiments.
%
%such as MATH 340: Advanced Numerical Methods.
%Simple MATLAB codes have been used as teaching tools to show students how to use MATLAB
%to simulate the slender-body equations for an elastic filament in Stokes flow.
%
%In the past year YNY has been mentoring Ufuomaefe Ogbe, a high school student
%from Newark. Ufuomaefe is an African American who 
%worked with PI on a simplified model for vesicles in flow. Based
%on what he learned about modeling and programming, 
%he has applied to the Applied Mathematics/Computer Science programs at both NJIT
%and Rutgers/Newark.

\section{Intellectual Merit}
A central theme of the project is the mathematical development and 
analysis of the physical model for interaction between many amphiphilic 
particles. The model formulates the interaction potential through a
screened Laplace equation boundary value problem possessing 
the physical properties like non-additivity and decay of realistic hydrophobic attraction.
Colloidal systems collectively self-assemble into bilayer
morphologies, and we analyze the elastic properties of these amphiphilic particle ensembles.
This allows us to interpret the Helfrich free energy in terms of hydrophobic interactions and 
specific molecular characteristics. We extend the capabilities of the
boundary integral equation quadrature by expansion method to perform
large particle number simulations in three dimensions with collisions. 
Results from these computations will be used to compare collective  amphiphilic 
against experiment,  and study the optimal design of three-dimensional functional materials.

\section{Relevant Results from Prior NSF Support}
\noindent {\bf Rolf Ryham}: no prior NSF support.

\noindent
{\bf Yuan-Nan Young}: {\it NSF-DMS-1222550, Mathematical and experimental study of lipid bilayer 
shape and dynamics mediated by surfactants and proteins}, \$212,603, 9/15/2012 - 08/31/2016 (with no-cost extension), PI. 
{\it Intellectual merit:} The focus of this grant is  modeling the interaction between a pure lipid bilayer membrane  (LBM) with surfactant, cholesterol and protein.
%Hence, there is no overlap between these grants and the current proposal.

%YNY and collaborators have studied (1) asymmetry of lipid bilayer due to its interaction
%with proteins and surfactants, (2) the electrohydrodynamics of a LBM under an
%electric field, and (3) the coupling between LBM dynamics and a transmembrane protein,
%such as a mechanosensitive channel.

\noindent
{\it Broader impacts:} 
One PhD student (Szu-Pei Fu) was
funded to work with YNY, and work has resulted in seven papers
\cite{Nganguia2013_PoF,Nganguia2013_PRE,Young2014_JFM,Young2015_PoF,Nganguia2015_CiCP,Pak2015_PNAS,Fu2015_PRE}.
YNY has been actively involved with promotion of underrepresented students at NJIT. 
The other PhD student (Herve Nganguia) is African. YNY has taught a broad
spectrum of courses in fluid mechanics and applied math modeling.

\noindent
{\bf Shidong Jiang}: {\it NSF DMS-1418918,
  Efficient High-Order Parallel Algorithms for Large-Scale Photonics Simulation},
\$150,000, 08/15/2014 - 06/30/2017, PI.
{\it Intellectual merit:} The goal of the proposed research is to develop
\emph{robust, high-order numerical methods} and \emph{efficient parallel algorithms} to
achieve greater accuracy and larger scale for photonics simulation.

%Jiang, Kloeckner, and their collaborators have constructed
%a stable second kind integral equation formulation for the mode calculation of optical
%waveguides of arbitrary shape; they have quantified the effect of cladding thickness on
%modal confinement loss in photonic waveguides; they have developed high-quality software
%package for solving integral equations in both two and three dimensions.

\noindent
{\it Broader impacts:} 
During the funded period, the PI has published or submitted twelve papers to refereed international journals~\cite{jiang2014sisc,bao2015jcp,jiang2015acom,greengard2015jcp,fu2015pre,gan2016sisc,jiang2016jcp,jiang2016oe,ben2016tpm,jiang2017siammms,jiang2017cicp,lai2018acha},
and presented the research results at many institutions and international
conferences/workshops to disseminate research results. On the education side,
the PI has supervised two students - Shaobo Wang~\cite{jiang2015acom,wang2019jsc}
and Szu-Pei Fu~\cite{fu2015pre,Fu19} (co-advised with Yuan-Nan Young),
with the partial support of the grant.
%Finally, the software package developed by both PIs of this collaborative grant
%has many applications in scientific computing, especially those related to
%the integral equation methods.

\section{Project Management, Collaboration Plan, and Schedules of
  Research Tasks}
\setlength{\parindent}{0pt}
% N.B. wrapfigure is not compatible with \noindent.

\begin{wrapfigure}{r}{0.56\textwidth}
\definecolor{barblue}{RGB}{51,102,254}
\renewcommand\sfdefault{phv}
\renewcommand\mddefault{mc}
\renewcommand\bfdefault{bc}
\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize,
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\small\color{black!70},
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=barblue},
    bar incomplete/.append style={fill=barblue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar{Specific Aim 1}{1}{6}\\
\ganttbar{Specific Aim 2}{1}{9}\\
\ganttbar{Specific Aim 3}{5}{12}\\
\ganttbar{Program management}{1}{12}\\
\end{ganttchart}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project.}
\label{fig:schedule}
\end{wrapfigure}
\textbf{Project management}: 
%
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, algorithms
and computing.  Ryham has been working on mathematical modeling with a strong
analytical background. Young has been working on many areas of computational
fluid dynamics and applications to math biology for many years.
Jiang has been working on integral
equation methods, fast algorithms, and their applications to 
computational electromagnetics and fluid dynamics
for many years.  Their recent collaborative work on
the HAP model in two dimensions has provided 
a solid foundation on the proposed research.

\medskip

\textbf{Collaboration plan}: 
%
The management responsibility of this collaborative research will
reside with the lead PI (Ryham) for this endeavor.  The research work is
structured to meet the tasks discussed in
Sec.~\ref{sec:proposed-work}.
%
The PIs, their postdoc and students will meet frequently in person.
The PIs will share software packages, paper sources, and references on a common
\textsf{Git} repository. The resulting software packages will be posted
on the \textsf{Github} software repository.

\medskip

\textbf{Research Schedule:} The detailed schedule for the proposed
work is shown in Fig.~\ref{fig:schedule}.

### 2020-10-27 NSF2020/Description/specificaim2.tex
added description source files

\subsection{Specific Aim 2: Efficient high-order numerical algorithm for large-scale simulation of the HAP model}\label{subsec:specific_aim_2}
% -----------------------------------------------------------------------------
% {{{
\subsubsection{Overview of the potential theory and boundary integral equation methods}
The HAP model requires solving the exterior Dirichlet problem of the screened Laplace
equation and the mobility problem of the Stokes flow at each time step.
Standard numerical methods such as finite difference and finite element
methods have to truncate the infinite domain to a finite
computational domain by imposing certain artificial boundary conditions
on the truncated domain and need the discretization of the whole volume
of the truncated domain. The artificial boundary conditions are very often
inexact, introducing another layer of approximation that
lowers the accuracy of the solution. The discretization of the whole volume is
very expensive
for three dimensional problems, leading to excessively large number of unknowns in
the linear system. Furthermore, it is rather difficult to obtain high-order
discretization when the boundary surfaces are irregular.

Potential theory and boundary integral equation (BIE) methods remove the aforementioned
obstacles in a very elegant way. The starting point is that for constant-coefficient
PDEs the fundamental solutions, i.e., the Green's functions, are readily available.
This allows us to represent the solution via the so-called layer potentials
that are the convolution integrals of a kernel and an unknown density
only on the boundary. The kernel is a linear combination of the Green's function
and its derivatives, which ensures that the representation satifies the underlying
PDE and the condition at infinity automatically. And the boundary condition
at the material interfaces together with the jump relation of the layer potential
leads to a boundary integral equation for the unknown density.

The BIE method removes the need of imposing artificial boundary conditions
for exterior problems
and reduces the dimension of the problem by one, leading to optimal number of unknowns
in the solve phase. Very often, one is able to construct the so-called
{\it second kind integral equation} (SKIE) formulation for these problems,
where the operator is a sum of the identity operator and a compact operator.
It is well-known that the condition number of the
resulting linear system for SKIEs is {\it independent} of the mesh size $h$ or equivalently,
the number of discretization points. This leads to
a constant number of iterations when iterative solvers are applied to solve
the resulting linear system. It further
improves the accuracy of the solution as the relative error of solution
will never increase as the number of total discretization points increases.
On the other hand, the condition
number of the linear system from finite difference and finite element methods generally
increases as a power function of the total number of dicretization points, with
the exact power depending on the underlying spatial dimension and the highest
order of the differential operator in the PDE. This leads to an increase in the number
of iterations (and hence the total computational cost) and an increase in the relative
error of the solution as the number of dicretization points increases.

The discretization of the integral operator often leads to a dense matrix,
while finite difference/finite element methods result in sparse matrices,
making matrix-vector product much cheaper to compute. However,since the invention
of the original fast multipole method (FMM)\cite{fmm5}, there
have been many fast algorithms~\cite{fmm1,fmm2,fmm3,fmm4,fmm6,fmm7,fmm8}
that reduce the cost of matrix-vector product
to linear ($O(N)$) or quasilinear complexity ($O(N \log^kN)$) for dense matrices resulting
from the BIE discretization.
Fast direct solvers have also been developed
recently~\cite{fds1,fds2,fds3,fds4,fds5,fds6,fds7,fds8,ho2016cpam2,ho2016cpam1,minden2016,minden2017siammms}.
The development of these fast algorithms have removed a huge
hurdle for the use of boundary integral equations, making the BIE method the method
of choice for constant-coefficient PDEs with linear boundary conditions. For the exterior
Dirichlet problem of the screened Laplace equation, the SKIE formulation in our previous
work~\cite{Fu19} can be readily extened to the 3D case. For the mobility problem
of the Stokes flow in three dimensions that
takes the hydrodynamic effect into account, an SKIE formulation
can be found in \cite{manasthesis}.

\subsubsection{High-order discretization of surface integrals in three dimensions}
The practical application of integral equation methods requires the
accurate evaluation of boundary integrals with singular, weakly
singular or nearly singular kernels. There are many numerical quadrature schemes
for dealing with line integrals in two dimensions~\cite{alpert,kapur,sidi,duffy,bruno1,bruno2,davis_1984,graglia_2008,hackbusch_sauter_1994, jarvenpaa_2003,khayat_2005,kress_boundary_1991,schwab_1992, ying_2006,beale1,beale2,goodman_1990, haroldson_1998, lowengrub_1993,schwab_1992,ggq1,ggq2,ggq3,helsing_2008a,helsing_integral_2009,helsing_tutorial_2012}
and some of them are extremely efficient and can achieve arbitrary high order.

The high-order quadrature rules for the evaluation of surface integrals
in three dimensions, however, are much less developed than the line integrals in two
dimensions. For example, there are no Gaussian quadratures for integraing
polynomials on a flat triangle, even though efficient quadratures
\cite{xiao2010cma,vioreanu2014} have been
developed recently for such purpose. For weakly singular or singular integrals,
\cite{bremer2012jcp,bremer2013jcp} constructed high-order quadratures
for surface integrals on a general triangle, while \cite{gimbutas2013sisc}
presented a fast algorithm for integrating $1/r$-type singular integrals
for surfaces that are homeomorphic to a sphere. We plan
to study the so-called quadrature by expansion (QBX) scheme~\cite{klockner2013jcp,qbx2}
for the evaluation
of both singular and near-singular surface integrals encountered in the
discretization of BIEs in three dimensions. Conceptually, the idea of the QBX
to evaluate singular, hypersingular and near singular integrals
on smooth surfaces is straightforward. That is, the surface is discretized
into smooth triangles and smooth high-order quadratures are applied to evaluate
the expansion coefficients
on all source triangles with the QBX expansion center placed at a point off the surface.
One may then form a suitable expansion (for example, a Taylor expansion) around that
center and evaluate this expansion back at the target point on the surface (or close
to the surface in the near singular case). Compared to the competing aforementioned
quadrature schemes, the QBX quadrature is attractive
because it offers a clear path for being extended to: \textbf{(1)}
handle any singularity, including
hypersingular operators, \textbf{(2)} be usable with any high-order surface
discretization, \textbf{(3)} generate well-conditioned discrete
operators to which iterative methods such as GMRES~\cite{gmres} can be
applied in a black-box fashion, \textbf{(4)} integrate well with fast algorithms
such as the FMM.

In practice, there are still many issues that need to be resolved.
For example, there are now many variants of QBX including global and local
QBX~\cite{klockner2013jcp,rachh2017jcp}, the target-specific QBX~\cite{siegel2018jcp},
kernel-independent QBX~\cite{abtin2018bit}, and
quadrature by two expansions~\cite{ding2019arxiv}. The coupling of the QBX
and the FMM may also lead to certain instability issues which may require
some changes in the fast multipole method~\cite{wala2018jcp}. Similar
to other quadrature methods, there have been extensive study on the QBX
methods in two dimensions, while its three dimension
version~\cite{wala2019jcp,af2018sisc,siegel2018jcp,wala2019arxiv} has not been
fully studied and the implementation is even more scarce. We plan to investigate
the accuracy and the convergence order of the various QBX schemes mentioned above,
its coupling with the FMM, parallel implementation issues for large-scale
problems, and the application to our target problems.
\subsubsection{A hybrid method for close-to-touching Janus particles}
The HAP model for membranes will inevitably lead to the case where some Janus particles
will be very close to each other. Even though QBX can handle such case
accurately, it may lead to excessively large number of unknowns in order to resolve
the unknown densities at those close-to-touching points. In \cite{gan2016sisc},
a hybrid scheme is developed to treat the close-to-touching spheres for the interface
problem of the Laplace equation. The key idea is to combine the analytic image method
and spectrally accurate method of moments, where the analytic image method will capture
the most singular part of the unknown density at the close-to-touching points.
With the aid of the FMM, the scheme achieves linear complexity with much less number
of unknowns on the material interfaces.
We plan to study the hybrid scheme
to treat the close-to-touching case for both the screened Laplace equation and the
mobility problem to further improve the efficiency of the numerical algorithm
for the HAP model.
\subsubsection{Other numerical issues}
Another outstanding numerical issue pertaining to simulating the self-assembly of amphiphilic particles (such as lipid macromolecles) in a
viscous solvent is the collision between amphiphilic particles.
The hydrophobic attraction potential drives the amphiphilic particles to move towards each other so to minimize exposure to the solvent. 
Under such
attraction force the fluid is being squeezed out as particles move toward each other, and the amphiphilic particles can come into physical
contact in finite time. 
Such particle collisions in a dense rigid body suspension is a great challenge and can be a bottleneck in large-scale simulations. 
In our previous work a Leonard-Jones potential is used to keep the particles from overlapping \cite{Fu19}. 
Such steep steric interaction at
short ranges introduces great numerical stiffness that limit the time step size.

Yan {\it et al.} proposed
a collision-resolution algorithm within the framework of boundary integral methods to resolve the non-smooth many-body
dynamics due to collisions by formulating the particle collision process as a linear complementarity problem with geometric 
`non-overlapping' constraint \cite{Yan2019}. 
We propose to treat the particle collisions based on Yan {\it et al.}'s work after the first two goals (see above)
are achieved. 
A potential complication in combining the algorithms for particle collision into our 
QBX integral formulation is the computational cost for the QBX to refine meshes on particles in collision.

Once the collision-resolution algorithm is implemented, we will check the computing performance first before we embark on 
incorporating fluctuating hydrodynamics \cite{Bao17,Bao18}, which might be important even at the scales of the amphiphilic 
particle size in some cases. We propose to extend the high-order time-integration scheme for a stochastic differential equation \cite{Fu15} to
this system.

### 2020-10-30 code/src/tstep.m
adding extensional bg flow

@@ -446,6 +446,8 @@ shearRate = options.shearRate;
 switch options.farField
   case 'shear'
     vInf = [shearRate*y;zeros(N,nb)];
+  case 'extensional'
+    vInf = shearRate*[-x;y];
   otherwise
     vInf = zeros(2*N,nb);
 end

### 2020-10-30 NSF2020/Description/background.tex

\noindent
{\bf {Collaborative Research: Mathematical modeling and coarse-grained simulations of self-assembly of amphiphilic Janus particles in a solvent}}\\
{\it Rolf Ryham (lead PI, Fordham University)}\\
{\it Shidong Jiang (co-PI, NJIT) and Yuan-Nan Young (PI, NJIT)}
\section{Background}
\label{sec:background}
\subsection{Hydrophobic Forces}
\label{sec:hydrophobicforce}

The hydrophobic force is a ubiquitous molecular interaction in biology \cite{Israelachvili1954}.
The word hydrophobic (water fearing) derives from the low solubility of oil (hydrocarbon solute) in water and vice versa. 
It causes hydrophobic moieties to aggregate and cluster,
is responsible for the adhesion between hydrophobic surfaces \cite{Ducker2016}, large contact angles on a 
dewetting surface \cite{Arenas2019,Sandre1999}, accumulation of particles along interfaces \cite{Lee2013,Lee2014}, 
formation of micelles and bilayers \cite{Israelachvili80}, and protein folding and membrane insertion \cite{Kabelka2018}.

Lipids are amphiphilic molecules whose  structure possesses
both hydrophobic and hydrophilic parts. 
The amphiphilic property is what allows lipids to form the membranes and 
compartments of living cells \cite{Israelachvili80}. 
More specifically, a lipid consists of 
an elongated hydrocarbon tail that is hydrophobic, attached to a polar head that is hydrophilic.
To shield the hydrophobic tails from water, lipids self-assemble into micelles and bilayers. 
A micelle is a spherical arrangement of lipids with tails terminating at the micelle center. 
A bilayer consists of two layers of lipids called monolayers, where the lipid tails point 
from the monolayer surface into the bilayer core.

The mathematical modeling of a biological membrane is a challenging problem in applied mathematics. 
Bilayers are elastic and resist deformations like bending, twisting, and stretching.
Their elastic deformations are well described by the theory of liquid crystals \cite{ANDRIENKO2018520}.
Lipid bilayer membranes can also be fluidic, and the lateral translation of lipids (or any membrane bound
proteins) couples nonlocaly to the motion of the aqueous environment \cite{MerkelSackmannEvans1989,StoneAjdari1998_JFM,OppenheimerDiamant2009_BJ,OppenheimerDiamant2011_PRL}. 
%Finally, the membranes of cellular 
%compartments are constantly merging and pinching as part of intracellular trafficking. 
%Therefore monolayer surfaces undergo discontinuous deformations.

There are two prevailing approaches in membrane modeling, and each has its advantages
and disadvantages. Molecular dynamics (MD) is to date the only tool capable of resolving granular biological details
The computational cost of MD, however, grows with the sixth power of the sample diameter and 
so simulations are severely limited to 
small system sizes and short time scales \cite{DiCarlo2019}.
The other approach, continuum mechanics, assumes smooth surfaces and can therefore model 
realistic systems over physical times. 
But continuum description of a biological membrane ignores the granularity of lipid molecules, and thus requires some assumptions when a
membrane ruptures or when two membranes fuse \cite{ChKo08}. 
%
%mechanics presumes, rather than predicts, the nucleation of discontinuities. 
%

Recently the PIs developed a mathematical model called the 
hydrophobic attraction potential (HAP) \cite{Fu2018_SIAM}.
This model addresses the major shortcomings of MD and continuum approaches,
and will hopefully offer an alternative modeling methodology that leads to new mathematical ideas 
and is both physically accurate and computationally practical.

The hydrophobic force arises when polar solvent molecules come in contact with a non-polar substance, such as hydrocarbon or vapor.
In a polar solvent (like water), the dipole-dipole interaction between solvent molecules form a loosely structured hydrogen-bond network where
each solvent molecule shares bonds with neighboring molecules at any given time 
\cite{Israelachvili1954}. In the presence of  a non-polar solvent molecule loses the ability to form hydrogen bonds
in one direction. 
The decrease in the number of hydrogen bonds causes a reorientation, or structural
change, in the surrounding water that is energetically very unfavorable \cite{Bjorneholm2016}.

The substantial free energy for placing hydrophobic substances in contact with water 
is roughly proportional to the surface area of the contact region. 
As a result, hydrocarbon solutes have a large interfacial tension 
and try to minimize their surface area when in water. 
At the microscopic level, however, the hydrophobic force is a long-range, surface interaction. 
This means that two hydrophobic surfaces, separated by
water over some distance, experience an attractive force \cite{Lum1999,Meyer2006,Hammer2010}.
Measurements show that the hydrophobic force
decays exponentially with a decay length like 1 nm 
\cite{Israelachvili1984, Marcelja1977,Christenson2001,Lin2005}. It is also known that the interaction is not pairwise additive, meaning that the force
between any two hydrophobic objects is altered by the presence of a third  object.

As a summary of its mathematical properties,  the hydrophobic force
is a non-additive, exponentially decaying surface force 
that possesses a separation of length scales. These properties suggest 
a boundary value problem formulation of the hydrophobic force.  
The non-additivity of the hydrophobic force has to do with the fact that there is no superposition
principle for including subdomains in boundary value problems. 
The exponential decay is a property of a second order elliptic partial differential equation (PDE). 
Finally, the separation of scales come from boundary layers, 
where the energy of the boundary layer in the zero-thickness limit corresponds to macroscopic interfacial tension.
Overlapping boundary layers correspond to microscopic hydrophobic attraction, 
and the boundary layer thickness corresponds to the decay length of attraction.

\begin{wrapfigure}[16]{l}{0.22\textwidth}
\centerline{\includegraphics[width=0.22\textwidth]{figures/BG_fig1.pdf}}
\caption{The exterior domain $\Omega$ is the solvent region surrounding a
number of rigid particles $P_1,$ $P_2,$ $P_3,$ \dots 
The surface $S$ is the solvent-particle interface, indicated by the unit
normal $\mathbf{n}.$ }\label{fig:domain}
\end{wrapfigure}
\subsection{Hydrophobic Attraction Potential (HAP)}
\label{sec:HAP}

Based on the physical origin of hydrophobicity,  we have devised a functional, called the hydrophobic attraction potential (HAP), to
model hydrophobic forces \cite{Fu19}. The motivation for HAP concept stemmed from the lead PI's 
earlier work on the problem of energy barriers in membrane fusion \cite{RyKlYaCo16,Chetal16}.
There, the lead PI and collaborators resolved the long-standing issue of accounting for the energy of a fissure surface
during topological transitions, by applying a squared gradient mathematical theory 
for hydrophobic attraction between planar surfaces \cite{Eriksson1989,Lum1999,Menshikov2017,Marcelja1977} to monolayer fissures.
Based on the PI Young's coarse-grained membrane modeling work \cite{Fu2017}, 
the investigators initiated a collaboration to create a gradient theory for arbitrary collections 
of hydrophobic and amphiphilic particles. This new method 
eliminates the costly calculation of water by treating the solvent implicitly, 
and avoids complicated re-meshing schemes of continuum approaches
by utilizing a particle-based representation.

To define HAP, consider a region $\Omega \subset \mathbb{R}^3$  
modeling the solvent surrounding a number of particles (Figure \ref{fig:domain}).
As stated earlier, the HAP must be an energy of the shape of the region
because hydrophobic attraction is non-additive. 
The boundary of the region is the water-particle interface and some parts of this
surface are hydrophobic while others are hydrophilic. 
Monte Carlo simulations 
show that water changes structure at hydrophobic interfaces \cite{Luzar1987, Jonsson2006,Varilly2011}.
Due to rapid fluctuation in the hydrogen bond network,
restructuring at the interface extends into bulk water.
This motivates the following definition for the HAP of the particles:
\begin{equation}
\label{HAP}
  \Phi = \gamma \iiint_{\Omega} \rho |\nabla u|^2 + \rho^{-1}u^2 \,dx \,dy \,dz, 
\end{equation}
where $u$ is the unique solution of screened Laplace equation boundary value problem 
\begin{equation}
  \label{SL}
  -\rho^2 \Delta u + u = 0 \in \Omega,\quad u = f  \mbox{ on } \partial \Omega, \quad u(x) \to 0 \mbox{ as } x \to \infty.
\end{equation}
The scalar function $u(x)$ is called the water activity. Its boundary values $f$ 
define the degree of hydrophobicity of the water-particle interface. The value 
1 represents a completely hydrophobic interface, where water has lost rotational freedom. 
Conversely, the boundary value 0 corresponds to a polar surface where water has the same rotational
freedom as in bulk water. The parameter $\rho$ is the decay length of attraction, 
around 1 nm, and the parameter $\gamma$ is the interfacial tension \cite{Israelachvili1954}.
The parameters $\rho$ and $\gamma$ contain information about the quality
of the solvent \cite{Discher2002}.

From a phenomenological perspective, (\ref{HAP}--\ref{SL}) 
is an appropriate model of hydrophobic attraction. Specifically,
using boundary layer analysis, it is possible 
to show that $\Phi$ converges to a surface energy in the zero-decay length limit \cite{Lee2018,Lin2015,Shibata2004}.
For non-zero decay lengths, solutions of \eqref{SL} yield an attractive interaction, e.g. between hydrophobic parallel disks
separated by water \cite{Eriksson1989}. Also, we have demonstrated with simulation that the forces 
derived from HAP theory are non-additive, and even deviate significantly from 
a pairwise potential \cite{Meyer2006,Fu19}. 
%The hydrophobic force has been implicated in the directed folding of proteins, 
%adhesion between biological membranes, but it is still unanswered as to whether
%the hydrophobic force of the form (\ref{HAP}--\ref{SL}) exists between small molecules.

\section{Previous Results by the PIs}
\label{sec:results}

In our paper \cite{Fu19}, we developed the model (\ref{HAP}--\ref{SL})
to quantify the macroscopic assembly and mechanics of a lipid bilayer membrane in solvents. 
%We formulated the boundary value problem as a second-kind
%integral equation (SKIE), presented in the Section (). 
%The simulated fluid-particle systems exhibit a variety of multiscale behaviors over both time and length.
%Over short time scales, the numerical results showed self-assembly for model lipid particles. 
%For large system simulations, the particles formed realistic configurations like micelles and bilayers. 
%Our collections showed that these amphiphilic particle bilayers  possessed mechanical properties of a 
%lipid  bilayer  membrane  that  are  consistent  with other results in the literature.   
To define the particle dynamics, we considered the exterior domain $\Omega$
for a finite number of disjoint, rigid and closed particles $P_1$, $P_2$, \dots, $P_n$, each with Lipschitz boundary,
and boundary data $f$ in the Sobolev space $H^1(\Omega).$ 
For any fixed configuration, the functional \eqref{HAP} has a unique minimizer $u$
among all $u - f$ with vanishing trace. This minimizer is a solution to \eqref{SL}.
Conversely, from maximum principles and energy estimates,  any solution of 
\eqref{SL} is the minimizer of \eqref{HAP}, and this supplies $\Phi$ with a well-defined value.

The main analytical tool of our manuscript 
is a formula for the first variation of $\Phi$ \cite{Bandle2015,Schiffer1954,Grinfeld2010}. 
This first variation  is a symmetric, rank-two tensor called the hydrophobic stress;
\begin{equation}
  \label{stress}
\boldsymbol{\sigma}_{\text{hydro}} = \gamma \rho^{-1} u^2 I + 2\rho \gamma (\tfrac{1}{2}|\nabla u|^2I - \nabla u \nabla u^T).
\end{equation}
To obtain \eqref{stress}, we observe that the potential $\Phi$ is a function of the particle position and orientations.
This is because the particle configuration defines the shape of $\Omega$ and the boundary data $f.$ 
Taking the derivative of \eqref{HAP} with respect to particle configurations, and using the boundary value problem \eqref{SL}
in a critical way leads to the surface term \eqref{stress}.  
By integrating the hydrophobic stress over the surface of particle $P_i,$ we obtaining the hydrophobic force and torque on each particle 
\begin{equation}
  \label{forceandtorque}
  \mathbf{F}_i = \iint_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n} \,dS,\quad
  \mathbf{T}_i = \iint_{\partial P_i} \mathbf{x} \times (\boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n}) \,dS.
\end{equation}
We verified that this system is force and torque free.
To supply viscous dissipation, 
we incorporated the mobility problem in Stokes flow to obtain the rigid body motions; 
\begin{equation}
\label{eq:stokes}
\begin{aligned}
&-\mu \Delta {\bf u} + \nabla p = 0, \quad \text{in}\ \Omega, \qquad 
\nabla \cdot {\bf u} = 0,  \quad \text{in}\ \Omega,\\
&{\bf u}({\bf x}) \to 0 \quad \text{as}\ |{\bf x}|\to \infty,\qquad 
  \mathbf{u}(\mathbf{x})|_{\partial P_i} = \mathbf{v}_i +
\boldsymbol{\omega}_i\times(\mathbf{x} - \mathbf{a}_i),\\
&\int_{\partial P_i}\boldsymbol{\sigma}\cdot {\bf n} dS=-{\bf F}_i, \quad
\int_{\partial P_i}(\mathbf{x}-\mathbf{a}_i)\times (\boldsymbol{\sigma} \cdot \mathbf{n}) dS=-{\bf T}_i.
\end{aligned}
\end{equation}
Here $\mu$ is the fluid viscosity and the first two equations state
that the fluid motion is a
divergence-free Stokes flow; the third equation specifies the fluid
velocity at infinity;
the fourth equation enforces a rigid body motion constraint on each
particle, where
$\mathbf{v}_i$ and $\boldsymbol{\omega}_i$ are unknown translation and
angular velocities
of the $i$-th particle and $\mathbf{a}_i$ is the center of mass of $P_i$;
the last two equations state that the net forces and torques
on each particle are given by the quantities ${\bf F}_i$ and ${\bf T}_i$
from \eqref{forceandtorque}, and $\boldsymbol{\sigma}$ is the fluid shear stress.

The time integration of particle configurations goes as follows: 
\textbf{(i)} solve the BVP \eqref{SL} for the screened Laplace equation, 
\textbf{(ii)} determine the rigid body forces and torques \eqref{forceandtorque}, 
\textbf{(iii)} solve the Stokes mobility problem \eqref{eq:stokes} for rigid body motion,
\textbf{(iv)} update the particle configuration. 
\S \ref{subsec:specific_aim_2}, addresses the numerical challenges in 
evaluating \eqref{stress} and how these challenges are overcome.

%%(2YY: 
%We have intentionally ignored  latency in the variational 
%calculations. At issue is that any change in the particle position involves the relaxation time 
%of the hydrogen bond network. To remedy this, we could parametrize a path for the 
%particles configuration as a function of physical time. Then the rate of change
%of hydrophobic interaction includes the surface hydrophobic stress as calculated, but also a body term 
%for time change of activity, assuming we model hydrogen bond relaxation by diffusion. 
%The diffusion time, however, is extremely small since hydrogen bond lifetimes are on the order 
%of $10^{-11}$ s \cite{Israelachvili1954}. This setup is analogous  to that of a Kelvin-Voigt material,
%where viscoelastic deformations exponentially approach the purely elastic deformation.  
%%)

Our simulations used Janus particles to model
lipid amphiphiles. Janus particles are a popular tool in material science and physics
for creating functional materials \cite{Lee2014, Lee2013}. 
This topic is the basis of Specific Aim 3. Janus particles are typically
spherical with a biphasic material label on either hemisphere,  endowing the particle
with a directional order. We considered a two-dimensional system, and represented an 
elongated lipid by elliptical particles with hydrophobic and hydrophilic labels along the ellipse's long axis.

Under the hydrophobic force, and with an excluded volume to prevent collisions, the 
Janus particles spontaneously merge and realign to form bilayers. This occurs only as a result
of energy minimization and does not require artificial inputs. To our knowledge, this is the first demonstration 
of bilayer self-assembly by a continuum hydrophobic interaction model \cite{Noguchi2001,Farago2003,Brannigan2006,Brooks2009,Wang2013}.

It is worth emphasizing that the model uses only a few parameters; interfacial tension, decay length, repulsion strength and particle
shape. For example, an elastic modulus for stretching a vesicle derived from micropipette manipulation 
directly calibrate our interfacial tension parameter. 
MD simulators have also made measurements and lately there is better and better agreement with reality. 
But even the simplest coarse grained models based on pair potentials for lipids has many more parameters \cite{Varilly2011,Wang2013} .

As a proof of concept, our work has already tested for elastic energies for bending, stretching and tilt of the bilayer assembly.
Extracting coefficients from the HAP simulations showed strikingly positive agreement with experimentally determined values  \cite{Fu19}.
Encouraged by these results and the hydrodynamic simulations of the bilayer assembly, the PIs propose to
further extend the HAP model and the numerical schemes (see \S\ref{sec:proposed-work})
to make direct comparison with experiments, the continuum liquid crystal results and MD simulations results, to establish that
the HAP model has the capability and adaptivity to model phenomena across length scales and time scales.
%
%
%The next few years provide the ideal window of opportunity for demonstrating the physical realism 
%of the HAP model. 
%
%
%
%The definitions and calculations for fully three-dimensional bilayer elastic energies are described in greater
%detail in Specific Aim 1. 
%

% 4.1 pN / nm = 4.1 pN nm / nm^2 = 4.1(1e-12)(1e-9) N m/(1e-18) m^2 = 4.1 (1e-3) J/m^2 = 4 mJ/m^2 
% pN/nm = mJ / m^2 and 1 kT / nm = 4 mJ / m^2 so stretching 40 gives 40  
% erg / cm^2 =  (1e-7) J/(1e-4) m^2 =   1e-3 J/m^2 =  mJ/m^2  
% 120 mJ / m^2 
% 10 erg / cm^2 = 10 pN nm / nm^2 = 2 kT / nm^2 
%

%\section{Proposed Research}
%\label{sec:proposed-work}
%The goal of the proposed research is to develop fast,
%high-order-accurate, parallel numerical algorithms for large-scale
%simulations of the collective hydrodynamics of janus particles in a solvent in both two- and three-dimensions.
%First we summarize some basic formulation and preliminary results \cite{Fu19} in \S~\ref{subsec:bie} and \S~\ref{subsec:3dbie}.
%We then describe outstanding numerical issues that we propose to address  in \S~\ref{subsec:proposed_research}.

%\section{Proposed Research}
%\label{sec:proposed-work}
%The goal of the proposed research is to develop fast,
%high-order-accurate, parallel numerical algorithms for large-scale
%simulations of the collective hydrodynamics of  amphiphilic particles in a viscous solvent.
%%
%Based on the integral formulation in \S~\ref{subsec:bie} and \S~\ref{subsec:3dbie}, we have demonstrated that 
%our potential theory approach can efficiently simulate self-assembly of 
%amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu19}.
%%
%While these results show great potentials in simulating the collective hydrodynamics of amphiphilic particles and
%reproducing mechanical properties of their bilayer assembly, 
%several outstanding issues need to be addressed for such approach to be efficiently applied to three-dimensional 
%collective hydrodynamics of amphiphilic particles.
%
%the two-dimensional hydrodynamics of amphiphilic particles 
%
%the two-dimensional results in \cite{Fu19} are in agreement with the 
%
%
%First we summarize some basic formulation and preliminary results \cite{Fu19} in \S~\ref{subsec:bie} and \S~\ref{subsec:3dbie}.
%We then describe outstanding numerical issues that we propose to address  in \S~\ref{subsec:proposed_research}.
% -----------------------------------------------------------------------------
%\subsection{Proposed research: High-order discretization of surface integrals in three dimensions}\label{subsec:proposed_research}
%% -----------------------------------------------------------------------------
%% {{{
%The practical application of integral equation methods requires the
%accurate evaluation of boundary integrals with singular, weakly
%singular or nearly singular kernels.  Historically, these issues have
%been handled either by low-order product integration rules (computed
%semi-analytically), by local modifications of a smooth
%rule~(e.g.~\cite{alpert,kapur,sidi}), by singularity
%subtraction/cancellation (e.g.~\cite{duffy,bruno1,bruno2,davis_1984,graglia_2008,hackbusch_sauter_1994, jarvenpaa_2003,khayat_2005,kress_boundary_1991,schwab_1992, ying_2006}), by kernel
%regularization and asymptotic analysis (e.g.~\cite{beale1,beale2,goodman_1990, haroldson_1998, lowengrub_1993,schwab_1992}), or by the
%construction of special purpose ``generalized Gaussian'' quadrature
%rules (e.g.~\cite{ggq1,ggq2,ggq3}).
%In the complex analytic case, additional methods
%have been developed by \citet{helsing_2008a} for off-surface
%evaluation. It should be noted that in the two-dimensional case,
%several of these alternatives provide extremely effective schemes,
%especially the kernel-splitting method developed by Johan Helsing
%\cite{helsing_integral_2009,helsing_tutorial_2012,helsing_2008a} since
%they all permit local adaptivity and high order accuracy.
%
%The high-order quadrature rules for the evaluation of surface integrals
%in three dimensions are much less developed than the line integrals in two
%dimensions. For example, there are no Gaussian quadratures for integraing
%polynomials on a flat triangle, even though efficient quadratures
%\cite{xiao2010cma,vioreanu2014} have been
%developed recently for such purpose. For weakly singular or singular integrals,
%\cite{bremer2012jcp,bremer2013jcp} constructed high-order quadratures
%for surface integrals on a general triangle, while \cite{gimbutas2013sisc}
%presented a fast algorithm for integrating $1/r$-type singular integrals
%for surfaces that are homeomorphic to a sphere. We would like to propose
%to study the so-called quadrature by expansion (QBX) scheme~\cite{klockner2013jcp,qbx2}
%for the evaluation
%of both singular and near-singular surface integrals encountered in the
%discretization of BIEs in three dimensions. Conceptually, the idea of the QBX
%to evaluate singular, hypersingular and near singular integrals
%on smooth surfaces is more or less straightforward. That is, the surface is discretized
%into smooth triangles and smooth high-order quadratures are applied to evaluate
%the expansion coefficients
%on all source triangles with the QBX expansion center placed at a point off the surface.
%One may then form a suitable expansion (for example, a Taylor expansion) around that
%center and evaluate this expansion back at the target point on the surface (or close
%to the surface in the near singular case). Compared to the competing aforementioned
%quadrature schemes, the QBX quadrature is attractive
%because it offers a clear path for being extended to: \textbf{(1)}
%handle any ambient and source dimensionality, \textbf{(2)} integrate
%any kernel, and thereby be usable for a very large range of PDEs and
%boundary conditions, \textbf{(3)} handle any singularity, including
%hypersingular operators, \textbf{(4)} be usable with any high-order surface
%discretization, \textbf{(5)} generate well-conditioned discrete
%operators to which iterative methods such as GMRES~\cite{gmres} can be
%applied in a black-box fashion, \textbf{(6)} be computationally
%efficient enough to be applied on the fly (without the need to store
%quadrature tables), \textbf{(7)} integrate well with fast algorithms
%such as the Fast Multipole Method. 
%
%In practice, there are still many issues that need to be resolved.
%For example, there are now many variants of QBX including global and local
%QBX~\cite{klockner2013jcp,rachh2017jcp}, the target-specific QBX~\cite{siegel2018jcp},
%kernel-independent QBX~\cite{abtin2018bit}, and
%quadrature by two expansions~\cite{ding2019arxiv}. The coupling of the QBX
%and the FMM may also lead to certain instability issues which may require
%some changes in the fast multipole method~\cite{wala2018jcp}. Similar
%to other quadrature methods, there have been an extensive study on the QBX
%methods in two dimensions, while its three dimension
%version~\cite{wala2019jcp,af2018sisc,siegel2018jcp,wala2019arxiv} has not been
%fully studied and the implementation is even more scarce. We plan to investigate
%the accuracy and the convergence order of the various QBX schemes mentioned above,
%its coupling with the FMM, parallel implementation issues for large-scale
%problems, and the application to our target problems.

### 2020-10-30 NSF2020/Description/preliminarywork.tex

\begin{figure}[!]
\begin{center}
\includegraphics[width=1\textwidth]{figures/PW_fig1A-D.pdf}
\includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
\end{center}\vspace{-0.3in}
\caption{ 
(A) A vesicle formed by amphiphilic particles in shear flow,
and the tank-treading motion (B)--(D). The separation of particle
pairs in (B) and (C) illustrate inter-leaflet slip.
(E) -- (G) Tank-treading reaches a steady state in elliptical aspect ratio,
major-axis angle, and circumference. }
\label{fig:tanktreading}
\end{figure}
\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow} 
%The motion of vesicles in shear flow is an important
%problem in the applied mathematics because simulations can reveal mechanical
%properties of membranes and lead to an enhanced understanding of 
%deformable particle laden flows \cite{Sinha15}. 
%
Over the past decades, researchers have used a number of mathematical tools 
to model vesicles in shear flow, including  phase field \cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, 
level set \cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary integral \cite{Shravan09,Rahimian15} and 
immersed boundary approaches \cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}. All these approaches
assume a mathematical surface, whether implicitly or explicitly, 
and define an elastic bending energy of the surface. The vesicle obeys fluid
transport and in turn the fluid balances shear stress with the vesicle's bending force.

Our HAP approach differs from prior methods in a number of respects. 
First, we do not assume a surface. Rather, we more fundamentally  consider a collection of amphiphilic particles.
The collection of amphiphiles minimize hydrophobic interactions by sequestering hydrophobic tails in the form of a bilayer, and the particles' excess free energy gives rise to an elastic bilayer energy. 
The second difference lies in the fluid-interface coupling. Here, the associated mobility problem \eqref{eq:stokes} 
is more complicated than dealing with a stress boundary condition or diffusive surface force, 
because the fluid velocity must be that of a rigid body motion at the particle surfaces.

To implement a vesicle in shear flow in the context of hydrophobic potentials and mobility problem, 
we consider a shear flow $\mathbf{u}_{\infty} = Uy\mathbf{i}_x$ in the direction of the $x$-axis
(Figure \ref{fig:tanktreading}A).
This field satisfies the linear Stokes system but does not give rise to a rigid motion at the particle interfaces. 
To have a rigid motion, we change variables $\mathbf{u} = \tilde{\mathbf{u}}+ \mathbf{u}_{\infty}$ and 
for the new field $\tilde{\mathbf{u}}$ vanishing at infinity we let 
$\tilde{\mathbf{u}}|_{\partial P_i} = \mathbf{v}_i + \boldsymbol{\omega}_i \times (\mathbf{x} - \mathbf{a}_i)$ 
where $(\mathbf{v}_i,\boldsymbol{\omega}_i)$ are the unknown translation and angular velocities of the 
$i$th particle $P_i.$

\begin{wrapfigure}[17]{l}{0.4\textwidth}
\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
\caption{\label{fig:demixing} An initial assembly of small and 
large particles spontaneous segregates into two smaller bodies. }
\end{wrapfigure}
The HAP simulations show vesicle tank-treading. Under the external shear flow, the initially circular 
vesicle rotates in the clockwise direction. As the rate of rotation increases, the vesicle approaches
a steadily tank-treading ellipse. In Figure \ref{fig:tanktreading}B-D, the solid curves are ellipses fit to the particle centers
and midplane respectively. In the non-dimensionalized system, the particles have diameter 2, on the order of $\rho,$ 
and the vesicle diameter is about 14. 
Figure \ref{fig:tanktreading}E shows the aspect ratio of the major to minor axes reaching an equilibrium value in the 
red and blue curves, yet oscillating in the high-shear rate (yellow) curve.
The tank-treading vesicle elongates and becomes more horizontal 
with an increase in flow rate or 
with a decrease in stiffness (effected by decreasing $\rho = 4$ to $\rho = 2$).

For large shear flow rates, there is an increase in arc length. Here arc length
refers to the the mid-plane circumference. Thus,
some of the external force is going into stretching the vesicle--the other
part is going into bending and viscous dissipation. From our experiments, 
we find that the vesicle ruptures once stretching exceeds about 5 \%
(see Figure \ref{fig:rupture}).
Finally, movies of the tank-treading motion show a slip velocity
between the outer and inner leaflets Figure \ref{fig:tanktreading}G. We have illustrated this 
by tracking the distance between two reference particles in the inner and outer leaflet
(Figure \ref{fig:tanktreading}B \& D, green and blue particles). 
With moderate shear rates or greater adhesion, the particle pair moves in tandem
(in Figure \ref{fig:tanktreading}H, blue and red curves, their distance is more or less constant). 
For a large shear rate, the particle separates as the two leaflets slide against one another.

\begin{wrapfigure}[12]{r}{0.2\textwidth}
\centerline{\includegraphics[width=0.2\textwidth]{figures/PW_fig5.pdf}}
\caption{\label{fig:rupture} Rupture of tank-treading vesicle under strong shear flow.}
\end{wrapfigure}
There are a number of advantages to using our particle based approach.
For one, the HAP theory automatically accounts for the existence of multiple phases. 
For example, we can vary lipid length, spontaneous curvature and bending rigidity 
by introducing differentiating particle shapes and hydrophobic boundary conditions (Figure \ref{fig:demixing}).
Continuum theory deals with multiple phases through additional surface densities that must
then satisfy specialized transport equations \cite{Lowengrub07,MikuckiZhou17}. 
As illustrated in Figure \ref{fig:tanktreading}, the particle
based approach supports inter-leaflet slip, and this can be used to determine inter-leaflet
and in-plane shear viscosities.

The ability to form discontinuities is perhaps the HAP method's greatest 
strength. Indeed, a strong, extensional shear flow must cause membrane rupture since the 
energy of stretching must exceed the pore nucleation and widening barriers 
for sufficiently large flow strengths. 
Some disadvantages are that the hydrophobic interaction does not constrain vesicle volume. 
Instead, changes in volume are rate limited by inter-particle spacing,
which may be undesirable in case of a mathematically strict volume constraint.
% set vesicle volume, as is done in the study of liposomes
%using auxiliary constraint equations for instance. 
%Also, the boundary integral method formulation
%relies on linearity of the Stokes equations. There has been some progress in
%boundary integral methods for the non-linear Navier-Stokes equations [ref].
%We point out that some non-Newtonian effects in polymers are a consequence of hydrophobic
%and steric molecular interactions like the ones presented in this proposal.

In recent years, researchers have developed a number of numerical methods for calculating
energy minimizing steady equilibrium shapes of lipid bilayer membranes, vesicles and red blood cells.
These approaches range from the finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, 
phase field method \cite{Du05,QiangDu08,Lowengrub13} to immersed boundary method  \cite{Hu,Hu13, Kim10}.
PI Ryham and collaborators led in part the development of phase field
functionals of membrane elastic energy and approaches to coupling membrane elasticity to fluids  \cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.

### 2020-10-30 NSF2020/Description/specificaim1.tex

\section{Proposed Research}
\label{sec:proposed-work}
The goal of the proposed research is to develop fast,
high-order-accurate, parallel numerical algorithms for large-scale
simulations of the collective hydrodynamics of  amphiphilic particles in a viscous solvent.
%
We have demonstrated that 
our potential theory approach can efficiently simulate self-assembly of 
amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu19}.
%
While these results show great potentials in simulating the collective hydrodynamics of amphiphilic particles and
reproducing mechanical properties of their bilayer assembly, 
several outstanding issues need to be addressed for such approach to be efficiently applied to three-dimensional 
collective hydrodynamics of amphiphilic particles.

\subsection{Specific Aim 1: Elastic properties of amphiphile ensembles}
\label{subsec:specific_aim_1}

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/SA1_fig1.pdf}
\end{center}
\caption{\footnotesize (A--C) The splay ($\Div \mathbf{d}$), 
saddle splay ($\det \mathsf{D}$) and twist ($\Curl \mathbf{d}$) elastic distortions of 
a monolayer. (D) The monolayer neutral surface $\Sigma$,  
director $\mathbf{d}$ and unit normal $\mathbf{n}$ in local coordinates.
(E--F) Lipids are able to tilt from  the surface normal, and stretch.
(H--J) Intermediates of membrane fusion and (K) experimental image of a stalk \cite{Aeffner2012}. }
\label{fig:distortions}
\end{figure}

 We conjecture that 
once assembled, the bilayer shapes possess some or all of the mechanical properties of bilayers from continuum theory.

The mechanical properties of bilayer are characterized by the Helfrich Hamiltonian;
\begin{equation}
\label{ansatz3}
\begin{aligned}
\int_{\Sigma} 
%&= \tfrac{1}{2}\KB\left[ \left( \tr \mathsf{D} + k_0\right)^2 - k_0^2\right] 
%+ \tfrac{1}{2}\KT (\mathsf{D}_{21} - \mathsf{D}_{12})^2 + \KG  \det \mathsf{D}\\
 \tfrac{1}{2}\KB\left[ \left( \Div \mathbf{d} + k_0\right)^2 - k_0^2\right] 
+ \tfrac{1}{2}\KT (\Curl \mathbf{d})^2 + \KG  \det \mathsf{D} \,dA.
\end{aligned}
\end{equation}
This hamiltonian is the energy functional for one monolayer,
represented by a smooth surface $\Sigma$ and director field $\mathbf{d}$
 \cite{Helfrich73, PhysRevLett.113.248102, Hamm2000}.
The surface $\Sigma$ coincides with the monolayer neutral surface. The 
unit length director $\mathbf{d}$ tracks lipid orientations  
and points from the lipid head toward the lipid tail \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
In a bilayer, the energy is the sum of the two monolayer energies. 
%These monolayers are typically coupled
%by requiring apposing lipid tails to terminate at the same point.

The form of the elastic energy density \eqref{ansatz3} is the same as
the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106}.  In fact,  
a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
liquid crystal theory. 
The Helfrich hamiltonian derives from the assumption of a quadratic energy density
in the director surface gradient 
$[\mathsf{D}]_{ij} = \frac{\partial \mathbf{d} }{\partial \tau_i} \cdot \tau_j,$ $i,j = 1,2,$ 
where $\tau_1$ and $\tau_2$ are orthogonal tangent vectors. Thus, the 
director gradients in \eqref{ansatz3} couple to surface geometry. 
Symmetries  with respect to mirror reflection and in-plane rotation 
require that the energy come from
\emph{splay} ($\Div \mathbf{d}$), 
\emph{twist} ($\Curl \mathbf{d}$)
or \emph{saddle-splay} ($\det \mathsf{D}$) distortions,
where $\Div$ and $\Curl$ are the surface divergence  and curl  operators, respectively (Figure \ref{fig:distortions}A--C).
The associated elastic coefficients  are the \emph{bending modulus} $\KB$,  \emph{twist modulus} $\KT$ 
and \emph{saddle-splay modulus} $\KG$.

The \emph{spontaneous curvature} $k_0$ depends on lipid composition and determines the preferred lipid splay,
\cite{RoLi15,Kozlov2007}. 
Figure \ref{fig:distortions}A illustrates positive splay. 
The lipid DSPC, for instance, has $k_0 = -0.1$ nm$^{-1}$ 
%as a result of  %having a relatively long acyl chain. 
and these lipids would line the  inner monolayer of a 
spherical liposome, because the addition of a positive splay $\Div \mathbf{d}$  in \eqref{ansatz3}
to the negative spontaneous curvature $k_0$ leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
The subtraction of $k_0^2$ makes the energy distortion 
free\footnote{The  ``bend'' distortion from nematics  
is not present in monolayers since the directors have no dependence in the normal direction,  \ie the 
Frank ``bend'' constant $K_3$ should not be confused with the \emph{bending modulus} $\KB.$ 
There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection.}.

The Helfrich hamiltonian is widely used to determine energy barriers of fusion between lipid bilayer membranes \cite{ChKo08}. 
%Some of these barrier heights were never before obtained through the use of continuum membrane mechanics.
PI Ryham and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk, hemifusion diaphragm and the fusion pore  \cite{RyWaCo13, RyKlYaCo16}. 
%The calculation of hydrophobic 
%fissures in \cite{RyKlYaCo16} motivated the HAP theory. 
These studies 
%analyzed the dependence of energy barriers on
%lipid composition and 
found that each of the transitions required on the order of 30 \kBT\; (Figure \ref{fig:barriers}A),
a result that is in agreement with barrier heights derived by recent molecular dynamics and experimental studies
\cite{FrRoPi17}.  
(Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.)

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figures/SA1_fig2.pdf}
\end{center}\vspace{-1.em}
\caption{\footnotesize (A) A partially clamped bilayer with mid-plane (dashed curve) under uniform load.
The quartic fit comes from continuum theory. 
(B) A circular vesicle at equilibrium. (C) The area modulus derives
from convexity in energy as a function of radius. 
\label{fig:bend}}
\end{figure}

\subsubsection{Evidence for elastic properties}
\label{sssec:evidence}
We tested for elastic properties by subjecting two-dimensional bilayer morphologies
to external loads \cite{Fu19}, using realistic
values for phospholipid length \cite{Boal},
the screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
and  interfacial tension $\gamma=4.1$ pN nm$^{-1}$  \cite{GarciaSaez, KUZMIN2005, Petelska2012}.
We first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
The bilayer is clamped and horizontal at one end and the restoring force in the free part 
of the bilayer opposes the load. Twist and saddle splay are both zero, singling out splay
as the only distortion.
% In this situation, the directors are also parallel to the unit surface
%normal. As such $\Div \mathbf{d} = -2H$ where $H$ is the mean curvature of the surface. 
Since deformations are small \eqref{ansatz3}, it is possible to solve the bilayer loading in closed form. 
This analytical solution (red curve) basically overlaps the midplane of the particle based solution (Figure \ref{fig:bend}A).

\begin{wrapfigure}[13]{l}{0.5\textwidth}
\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
diaphragm expansion (ii) and pore formation (iii). 
(B) Saddle-splay energy for each change in \emph{monolayer} topology
calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
\label{fig:barriers}
\end{wrapfigure}
Experimental measurements have accurately determined 
the bending modulus for several lipid types, with 
typical values lying around 10 \kBT\; \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}.
By comparing with the exact solution, we derived a bending modulus
in the range 8.51 -- 13.54 \kBT, which is in 
excellent agreement with the experimentally derived value, especially considering how few parameters the HAP 
formalism involves.

We also considered the stretching deformation \cite{Fu19}. 
Stretching occurs whenever there is an excess monolayer area,
and it is energetically costly since it exposes hydrocarbon tails to water. 
%Monolayers are not, strictly speaking, area incompressible,
%and 
Manipulation experiments give a monolayer area modulus in the range 
30 -- 40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}. 
To measure an area modulus, we stretched a circular vesicle, modeling the cross-section 
of a bilayer tube (Figure \ref{fig:bend}B \& C).
%We then stretched the vesicle beyond and beneath equilibrium radius and recorded the change in energy. 
This procedure gave a monolayer area modulus 
34 $\pm$ 2 \kBT \;nm$^{-2}$, independently of the vesicle size, which
is also remarkably close to the experimental value.

The successful outcomes of our preliminary tests suggest that the HAP particle configurations 
do behave like an elastic material. To validate our conjecture, we must consider 
ways to isolate or partially isolate the remaining distortions. 
The twist deformation, for example, has a modulus in the range of 1 to 2 \kBT\; 
as evaluated by molecular dynamics \cite{LeVeWa14}. 
But twist is mathematically zero in our two-dimensional monolayers,
and so we require a computationally efficient means for evaluating the 
boundary integral equations in a collection of three-dimensional particles. 
Specific Aim 2 discusses some of the outstanding implementation issues.

Our eventual three-dimensional calculations must also consider the saddle-splay distortion,
and the calculations may help resolve some well-known issues in the theory \cite{TerziDeserno17}. 
Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
\cite{SIEGEL2004366,SIEGEL20085200}.
This value, however, 
predicts an energy barrier for monolayer fusion on the order of 200  \kBT, which runs counter to 
the value 30 \kBT\; estimated in experiments \cite{RyKlYaCo16,FrRoPi17,Tran7106}.  
We expect the particle-based approach can shed light on this inconsistency.

### 2020-10-30 NSF2020/Description/specificaim3.tex

\subsection{Specific Aim 3: Functional Materials}
\label{subsec:specific_aim_3}
%The mathematics of this proposal investigates how three-dimensional solids deform under long-range surface tension interaction. The results generalize the physical principles used in the design of functional materials, enabling investigators to simulate sub-micron scale systems that are otherwise impractical to realize experimentally. It supplies new insight into organizational principles in physical and biological sciences. 
%
Over the past decade, there has been an explosion of interest in the fabrication of complex microscopic three-dimensional structures 
\cite{Cho2010}. These fabrication processes utilize the fact that at small scales, capillary forces dominate  van der Waals interactions and thermal noise  \cite{Zhang2017}, enabling the coordinated movement and binding of material subunits. Two prominent fabrication techniques are capillary origami 
\cite{Pandey2011,Leong2007,Reynolds2019} and colloidal self-assembly \cite{Dasgupta2017,Siontorou2017}. Capillary origami uses principles of elastocapilirity wherein elastic solids deform under surface tension \cite{Bico2018,VanHonschoten2010}. In self-assembly of colloids, 
particles exhibit similar thermodynamic behavior of molecular systems, except that the behavior occurs over observable, long time scales \cite{Zhang2017}.

There is inherent intellectual value in fabricating novel three dimensional structures: Living cells construct biological molecules like proteins, membranes and viral capsids using hierarchical assembly \cite{Whitesides2002}. At the same time, elastocapillarity and colloidal self-assembly supply model systems for biological processes, like vesicle adhesion and membrane bound protein interaction \cite{Dasgupta2017}, the hydro-polar model of protein folding \cite{Lau1989,Pandey2011} and viral capsid assembly and \cite{CASPAR1962}. Capillarity can serve as a model for the lock and key mechanism binding between the active site of an enzyme and a substrate molecule \cite{Araujo2018}, or treating viruses like adhered particles 
\cite{Agudo-Canalejo2017,Agudo-Canalejo2015,Deserno2004}, or studying decorated vesicles 
\cite{Auth2009,Weikl2002,Atilgan2007}. Although challenging, mathematically analyzing these model systems gives deep insight into biological structure and function.

%Aside from their intellectual value, high-yield batch production of three-dimensional microstructures has application in functional materials engineering \cite{Syms2003,Leong2010,Crane2013}. In mechanics, for instance, elasticapillarity is a guiding principle lithographic etching of electronics \cite{Bico2018}. Researchers have used self-folding structures in the design of micro containers for encapsulated drug delivery \cite{Fernandes2012} and 3D photovoltaic cells \cite{Guo2009}. 
%In chemical engineering, emulsions stabilize droplets through capillary binding or particulates leading 
%to colloidosomes capturing proteins, vitamins, flavors, living cells \cite{Dinsmore2002}. 
%Microsensors, electronic ink and micromotors \cite{Zhang2017,Yan2016} 
%are potential applications involving Janus-like particles.

\begin{wrapfigure}[14]{r}{3.0in}
\vspace*{+15pt}
\centerline{\includegraphics[width=3.0in]{figures/SA3_fig2.pdf}}
\vspace*{5pt}
\caption{{\footnotesize Illustration of self-assembly of hydrophobically labeled faces.
The thick triangles have a rim-hydrophobic label on one side, and are hydrophilic on the other side.
These shapes would potentially aggregate into a tetrahedral container. }}
\label{fig:illustration}
\end{wrapfigure}
The HAP theory is ideally suited to the problem of creating microstructures through capillary action. Specifically, the modeling application considers the assembly of polyhedra from smaller subunits. Our developments, which include viscous interactions, thermal fluctuation, and a long range description of capillarity, will pave the way for dynamical understanding to organizational principles in viral capsid formation, for instance \cite{CASPAR1962,Prasad2012}.

In order to illustrate the novelty of our approach, it is helpful to first describe how current experimental and mathematical techniques deal with polyhedral assembly. Capillary origami uses lithography to etch faces out of a thin, elastic sheet \cite{Pandey2011,Reynolds2019}. The collection of faces form a so-called net, and this net self-folds into a three-dimensional polyhedron (Figure~\ref{fig:illustration}). The motivation is to create micro containers to mimc protein folding \cite{Reynolds2019}. Prediction of geometric structure from its subunits is non-trivial. That is because the final morphology depends on the net structure, physical interactions, and the surrounding media, and researchers have formulated optimality criteria for these nets \cite{Araujo2018,Pandey2011}.

The experimental shapes are hundreds of microns in diameter. Thus, as a key distinction with HAP approach, the driving force for folding in capillary origami and related processes comes from surface energy of the hinges (e.g. soldered hinges that supply a surface tension once the system is heated). Mathematicians have numerically and analytically described the behavior of these surface tension driven hinges \cite{Bico2018,Peraud2014,Brubaker2016}, making it possible to simulate the mechanical problem, in principle, using slender body theory for plates.

To study this problem using HAP theory, we form a collection of thin, prism-like particles in Figure \ref{fig:illustration}. 
Each of these particles serves as a face in the final morphology. The edges of the prisms are labeled hydrophobic according to the boundary condition in the screened Laplace equation boundary value problem. This way, the edges coalesce, forming the desired structures. Furthermore, 
by manipulating the boundary condition in HAP, it is possible to have faces attach and detach with precision, and form a net or other structures if so desired. Our HAP theory therefore generalizes submillimeter theoretical and experimental work to the micron and nanometer sizes.

%There is also the possibility to explore new classes of mathematical materials, like wrinkling in polystyrene sheets \cite{Paulsen2016}, that include the interaction between an elastic material, the viscous solvent, and long range hydrophobic (capillary) interactions. In the case of rigid particles and subunits, the rigid body motions come from the so-called mobility boundary value problem for the Stokes equation. Here, the hydrophobic stress balances with the viscous stress coming from the rigid body motion of the particles in the surrounding solvent. If the particles are deformable, like a protein \cite{Elms2012} or as in the capillary induced bending of rods \cite{Schulman2017}, then we can formulate an elastic energy for deformation. These elastic energies account for surface bending or even permanent charge. To deploy this approach, it is a matter of solving the bodies' momentum balance equations coupled to the fluid through the viscous, elastic, and hydrophobic stress balance.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figures/SA3_fig1.pdf}
\end{center}
\caption{(A)--(D) shows the spontaneous insertion of two hydrophobic particles into a vesicle bilayer. 
The driving force is long-range interaction between the hydrophobic, magenta particles and
the bilayer core.  The particle entrainment cause the vesicle to break apart, analogously to surfactant
induced lysis.}
\end{figure}
Finally, further applications of our modeling approach include colloidal interaction on interfaces. Here, the experimental setups use Janus particles to model, for example, membrane bound proteins \cite{Kumar2013,Lehle2008,Zhang2017}. The idea of an amphiphilic Janus particle was introduced by P. G. de Gennes in 1991 \cite{Zhang2017}. The Investigators have significant experience as Janus particles figure heavily into our particle based description of bilayers, and can adjust our modeling approach to account for proteins. This is done by consider mixtures, consisting of many (hundreds to thousands) long, elongated amphiphilic particles for the lipid phase. Larger particles with hydrophobic patches or stripes model the proteins \cite{Jurasek2017}.

The distinction between macroscopic capillarity and microscopic hydrophobic force are relevant here as well.  Prior models use surface energies to account for interaction between particles in an interface \cite{Dasgupta2017}. 
However, this may be missing important physics, and here our modeling approach has the advantage in that protein insertion, for instance, is a self-consistent consequence of the formulation, versus an assumption imposed by boundary conditions.  
The simulations will enable us address important biological questions on how a collection of 
interface bound colloids interact \cite{Yao2013,Salib2013}, 
and how configurations dictate 
macroscopic surface properties and sense background curvature \cite{Cavallaro2011,Liu2018,Sharifi-Mood2015}.

### 2020-11-02 NSF2020/Description/background.tex
finished fixing up bibliography

@@
 Based on the physical origin of hydrophobicity,  we have devised a functional, called the hydrophobic attraction potential (HAP), to
-model hydrophobic forces \cite{Fu19}. The motivation for HAP concept stemmed from the lead PI's 
+model hydrophobic forces \cite{Fu2018_SIAM}. The motivation for HAP concept stemmed from the lead PI's 
 earlier work on the problem of energy barriers in membrane fusion \cite{RyKlYaCo16,Chetal16}.
@@
 derived from HAP theory are non-additive, and even deviate significantly from 
-a pairwise potential \cite{Meyer2006,Fu19}. 
+a pairwise potential \cite{Meyer2006,Fu2018_SIAM}. 
 %The hydrophobic force has been implicated in the directed folding of proteins, 
@@
 
-In our paper \cite{Fu19}, we developed the model (\ref{HAP}--\ref{SL})
+In our paper \cite{Fu2018_SIAM}, we developed the model (\ref{HAP}--\ref{SL})
 to quantify the macroscopic assembly and mechanics of a lipid bilayer membrane in solvents. 
@@
 As a proof of concept, our work has already tested for elastic energies for bending, stretching and tilt of the bilayer assembly.
-Extracting coefficients from the HAP simulations showed strikingly positive agreement with experimentally determined values  \cite{Fu19}.
+Extracting coefficients from the HAP simulations showed strikingly
+positive agreement with experimentally determined values
+\cite{Fu2018_SIAM}.
 Encouraged by these results and the hydrodynamic simulations of the bilayer assembly, the PIs propose to
@@
 %simulations of the collective hydrodynamics of janus particles in a solvent in both two- and three-dimensions.
-%First we summarize some basic formulation and preliminary results \cite{Fu19} in \S~\ref{subsec:bie} and \S~\ref{subsec:3dbie}.
+%First we summarize some basic formulation and preliminary results
+%\cite{Fu2018_SIAM} in \S~\ref{subsec:bie} and \S~\ref{subsec:3dbie}.
 %We then describe outstanding numerical issues that we propose to address  in \S~\ref{subsec:proposed_research}.
@@
 %our potential theory approach can efficiently simulate self-assembly of 
-%amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu19}.
+%amphiphilic particles into two-dimensional micelles, bilayer membranes,
+%and vesicles \cite{Fu2018_SIAM}.
 %%
@@
 %
-%the two-dimensional results in \cite{Fu19} are in agreement with the 
+%the two-dimensional results in \cite{Fu2018_SIAM} are in agreement with the 
 %
 %
-%First we summarize some basic formulation and preliminary results \cite{Fu19} in \S~\ref{subsec:bie} and \S~\ref{subsec:3dbie}.
+%First we summarize some basic formulation and preliminary results
+%\cite{Fu2018_SIAM} in \S~\ref{subsec:bie} and \S~\ref{subsec:3dbie}.
 %We then describe outstanding numerical issues that we propose to address  in \S~\ref{subsec:proposed_research}.

### 2020-11-02 NSF2020/Description/broaderimpacts.tex
fixing up bibliography
finished fixing up bibliography

@@
 funded to work with YNY, and work has resulted in seven papers
-\cite{Nganguia2013_PoF,Nganguia2013_PRE,Young2014_JFM,Young2015_PoF,Nganguia2015_CiCP,Pak2015_PNAS,Fu2015_PRE}.
+\cite{Nganguia2013_PoF,Nganguia2013_PRE,Young2014_JFM,Young2015_PoF,Nganguia2015_CiCP,Pak2015_PNAS,fu2015pre}.
 YNY has been actively involved with promotion of underrepresented students at NJIT. 
@@
 the PI has supervised two students - Shaobo Wang~\cite{jiang2015acom,wang2019jsc}
-and Szu-Pei Fu~\cite{fu2015pre,Fu19} (co-advised with Yuan-Nan Young),
+and Szu-Pei Fu~\cite{fu2015pre,Fu2018_SIAM} (co-advised with Yuan-Nan Young),
 with the partial support of the grant.

### 2020-11-02 NSF2020/Description/preliminarywork.tex
finished fixing up bibliography

@@
 These approaches range from the finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, 
-phase field method \cite{Du05,QiangDu08,Lowengrub13} to immersed boundary method  \cite{Hu,Hu13, Kim10}.
+phase field method \cite{Du05,QiangDu08,Lowengrub13} to immersed
+boundary method  \cite{Hu,Hu13, KimLai2010_JCP}.
 PI Ryham and collaborators led in part the development of phase field

### 2020-11-02 NSF2020/Description/specificaim1_ver2.tex
finished fixing up bibliography

--- 2020-10-30 NSF2020/Description/specificaim1.tex
@@
 our potential theory approach can efficiently simulate self-assembly of 
-amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu19}.
+amphiphilic particles into two-dimensional micelles, bilayer membranes,
+and vesicles \cite{Fu2018_SIAM}.
 %
@@
 We tested for elastic properties by subjecting two-dimensional bilayer morphologies
-to external loads \cite{Fu19}, using realistic
+to external loads \cite{Fu2018_SIAM}, using realistic
 values for phospholipid length \cite{Boal},
@@
 (B) Saddle-splay energy for each change in \emph{monolayer} topology
-calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
+calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle
+  at different values of volume to area ratio from coarse-grained
+  simulations of lipid bilayer membranes \cite{Fu2017}.}}
 \label{fig:barriers}
@@
 
-We also considered the stretching deformation \cite{Fu19}. 
+We also considered the stretching deformation \cite{Fu2018_SIAM}. 
 Stretching occurs whenever there is an excess monolayer area,

### 2020-11-02 NSF2020/Description/specificaim2_ver2.tex
fixing up bibliography
finished fixing up bibliography

--- 2020-10-27 NSF2020/Description/specificaim2.tex
@@
 Dirichlet problem of the screened Laplace equation, the SKIE formulation in our previous
-work~\cite{Fu19} can be readily extened to the 3D case. For the mobility problem
+work~\cite{Fu2018_SIAM} can be readily extened to the 3D case. For the mobility problem
 of the Stokes flow in three dimensions that
@@
 Such particle collisions in a dense rigid body suspension is a great challenge and can be a bottleneck in large-scale simulations. 
-In our previous work a Leonard-Jones potential is used to keep the particles from overlapping \cite{Fu19}. 
+In our previous work a Leonard-Jones potential is used to keep the
+particles from overlapping \cite{Fu2018_SIAM}. 
 Such steep steric interaction at
@@
 incorporating fluctuating hydrodynamics \cite{Bao17,Bao18}, which might be important even at the scales of the amphiphilic 
-particle size in some cases. We propose to extend the high-order time-integration scheme for a stochastic differential equation \cite{Fu15} to
+particle size in some cases. We propose to extend the high-order
+time-integration scheme for a stochastic differential equation
+\cite{fu2015pre} to
 this system.

### 2020-11-02 NSF2020/Description/specificaim2_ver2.tex
working on my section of proposal

@@
-\subsection{Specific Aim 2: Efficient high-order numerical algorithm for large-scale simulation of the HAP model}\label{subsec:specific_aim_2}
-% -----------------------------------------------------------------------------
-% {{{
-\subsubsection{Overview of the potential theory and boundary integral equation methods}
-The HAP model requires solving the exterior Dirichlet problem of the screened Laplace
-equation and the mobility problem of the Stokes flow at each time step.
-Standard numerical methods such as finite difference and finite element
-methods have to truncate the infinite domain to a finite
-computational domain by imposing certain artificial boundary conditions
-on the truncated domain and need the discretization of the whole volume
-of the truncated domain. The artificial boundary conditions are very often
-inexact, introducing another layer of approximation that
-lowers the accuracy of the solution. The discretization of the whole volume is
-very expensive
-for three dimensional problems, leading to excessively large number of unknowns in
-the linear system. Furthermore, it is rather difficult to obtain high-order
-discretization when the boundary surfaces are irregular.
+\subsection{Specific Aim 2: Efficient high-order numerical algorithm for
+large-scale simulation of the HAP model}
+\label{subsec:specific_aim_2}
+% ----------------------------------------------------------------------
+\subsubsection{Overview of the potential theory and boundary integral
+equation methods} 
+The HAP model requires solving the exterior Dirichlet problem of the
+screened Laplace equation and the mobility problem of the Stokes flow at
+each time step. If discretizing these equations with stencil-based
+numerical methods, the computational domain must be truncated, the
+volume must be discretized, and artificial boundary conditions must be
+imposed. The artificial boundary conditions introduces an additional
+source of error, and discretizing the volume, particularly in three
+dimensions, results in an excessively large linear system. Moreover, it
+is difficult to obtain high-order discretizations when the boundary
+surfaces are irregular. Since we are solving constant-coefficient
+elliptic PDEs, we apply boundary integral equation (BIE) that remove the
+aforementioned obstacles. BIEs represent the solution as a layer
+potential with an unknown density function. Then, the correct density
+function is found that matching the layer potential with the prescribed
+boundary conditions. By construction, layer potentials satisfy the
+underlying PDE and the far-field conditions.
 
-Potential theory and boundary integral equation (BIE) methods remove the aforementioned
-obstacles in a very elegant way. The starting point is that for constant-coefficient
-PDEs the fundamental solutions, i.e., the Green's functions, are readily available.
-This allows us to represent the solution via the so-called layer potentials
-that are the convolution integrals of a kernel and an unknown density
-only on the boundary. The kernel is a linear combination of the Green's function
-and its derivatives, which ensures that the representation satifies the underlying
-PDE and the condition at infinity automatically. And the boundary condition
-at the material interfaces together with the jump relation of the layer potential
-leads to a boundary integral equation for the unknown density.
+Discretizations of BIEs have several advantages when compared to
+stencil-based discretizations. First, the dimension of the problem is
+reduced by one since the unknown density function is defined on the
+boundary of the geometry. Second, by carefully selecting each layer
+potential, the resulting linear system is well-conditioned for any
+resolution and iterative methods such as GMRES require a
+mesh-independent number of iterations to converge. Third, by using
+appropriate quadrature methods, the method converges with spectral or
+very high-order accuracy.
 
-The BIE method removes the need of imposing artificial boundary conditions
-for exterior problems
-and reduces the dimension of the problem by one, leading to optimal number of unknowns
-in the solve phase. Very often, one is able to construct the so-called
-{\it second kind integral equation} (SKIE) formulation for these problems,
-where the operator is a sum of the identity operator and a compact operator.
-It is well-known that the condition number of the
-resulting linear system for SKIEs is {\it independent} of the mesh size $h$ or equivalently,
-the number of discretization points. This leads to
-a constant number of iterations when iterative solvers are applied to solve
-the resulting linear system. It further
-improves the accuracy of the solution as the relative error of solution
-will never increase as the number of total discretization points increases.
-On the other hand, the condition
-number of the linear system from finite difference and finite element methods generally
-increases as a power function of the total number of dicretization points, with
-the exact power depending on the underlying spatial dimension and the highest
-order of the differential operator in the PDE. This leads to an increase in the number
-of iterations (and hence the total computational cost) and an increase in the relative
-error of the solution as the number of dicretization points increases.
+Challenges are dense matrices, preconditioners, and near-singular
+integration
 
-The discretization of the integral operator often leads to a dense matrix,
-while finite difference/finite element methods result in sparse matrices,
-making matrix-vector product much cheaper to compute. However,since the invention
-of the original fast multipole method (FMM)\cite{fmm5}, there
-have been many fast algorithms~\cite{fmm1,fmm2,fmm3,fmm4,fmm6,fmm7,fmm8}
-that reduce the cost of matrix-vector product
-to linear ($O(N)$) or quasilinear complexity ($O(N \log^kN)$) for dense matrices resulting
-from the BIE discretization.
-Fast direct solvers have also been developed
+%The HAP model requires solving the exterior Dirichlet problem of the
+%screened Laplace equation and the mobility problem of the Stokes flow
+%at each time step. Standard numerical methods such as finite difference
+%and finite element methods have to truncate the infinite domain to a
+%finite computational domain by imposing certain artificial boundary
+%conditions on the truncated domain and need the discretization of the
+%whole volume of the truncated domain. The artificial boundary
+%conditions are very often inexact, introducing another layer of
+%approximation that lowers the accuracy of the solution. The
+%discretization of the whole volume is very expensive for three
+%dimensional problems, leading to excessively large number of unknowns
+%in the linear system. Furthermore, it is rather difficult to obtain
+%high-order discretization when the boundary surfaces are irregular.
+
+Potential theory and boundary integral equation (BIE) methods remove the
+aforementioned obstacles in a very elegant way. The starting point is
+that for constant-coefficient PDEs the fundamental solutions, i.e., the
+Green's functions, are readily available. This allows us to represent
+the solution via the so-called layer potentials that are the convolution
+integrals of a kernel and an unknown density only on the boundary. The
+kernel is a linear combination of the Green's function and its
+derivatives, which ensures that the representation satifies the
+underlying PDE and the condition at infinity automatically. And the
+boundary condition at the material interfaces together with the jump
+relation of the layer potential leads to a boundary integral equation
+for the unknown density.
+
+%The BIE method removes the need of imposing artificial boundary
+%conditions for exterior problems and reduces the dimension of the
+%problem by one, leading to optimal number of unknowns in the solve
+%phase. Very often, one is able to construct the so-called {\it second
+%kind integral equation} (SKIE) formulation for these problems, where
+%the operator is a sum of the identity operator and a compact operator.
+%It is well-known that the condition number of the resulting linear
+%system for SKIEs is {\it independent} of the mesh size $h$ or
+%equivalently, the number of discretization points. This leads to a
+%constant number of iterations when iterative solvers are applied to
+%solve the resulting linear system. It further improves the accuracy of
+%the solution as the relative error of solution will never increase as
+%the number of total discretization points increases. On the other hand,
+%the condition number of the linear system from finite difference and
+%finite element methods generally increases as a power function of the
+%total number of dicretization points, with the exact power depending on
+%the underlying spatial dimension and the highest order of the
+%differential operator in the PDE. This leads to an increase in the
+%number of iterations (and hence the total computational cost) and an
+%increase in the relative error of the solution as the number of
+%dicretization points increases.
+
+The discretization of the integral operator often leads to a dense
+matrix, while finite difference/finite element methods result in sparse
+matrices, making matrix-vector product much cheaper to compute.
+However,since the invention of the original fast multipole method
+(FMM)\cite{fmm5}, there have been many fast
+algorithms~\cite{fmm1,fmm2,fmm3,fmm4,fmm6,fmm7,fmm8} that reduce the
+cost of matrix-vector product to linear ($O(N)$) or quasilinear
+complexity ($O(N \log^kN)$) for dense matrices resulting from the BIE
+discretization. Fast direct solvers have also been developed
 recently~\cite{fds1,fds2,fds3,fds4,fds5,fds6,fds7,fds8,ho2016cpam2,ho2016cpam1,minden2016,minden2017siammms}.
-The development of these fast algorithms have removed a huge
-hurdle for the use of boundary integral equations, making the BIE method the method
-of choice for constant-coefficient PDEs with linear boundary conditions. For the exterior
-Dirichlet problem of the screened Laplace equation, the SKIE formulation in our previous
-work~\cite{Fu2018_SIAM} can be readily extened to the 3D case. For the mobility problem
-of the Stokes flow in three dimensions that
-takes the hydrodynamic effect into account, an SKIE formulation
-can be found in \cite{manasthesis}.
+The development of these fast algorithms have removed a huge hurdle for
+the use of boundary integral equations, making the BIE method the method
+of choice for constant-coefficient PDEs with linear boundary conditions.
+For the exterior Dirichlet problem of the screened Laplace equation, the
+SKIE formulation in our previous work~\cite{Fu2018_SIAM} can be readily
+extened to the 3D case. For the mobility problem of the Stokes flow in
+three dimensions that takes the hydrodynamic effect into account, an
+SKIE formulation can be found in~\cite{manasthesis}.
 
-\subsubsection{High-order discretization of surface integrals in three dimensions}
+% ----------------------------------------------------------------------
+\subsubsection{High-order discretization of surface integrals in three
+dimensions}
 The practical application of integral equation methods requires the
-accurate evaluation of boundary integrals with singular, weakly
-singular or nearly singular kernels. There are many numerical quadrature schemes
-for dealing with line integrals in two dimensions~\cite{alpert,kapur,sidi,duffy,bruno1,bruno2,davis_1984,graglia_2008,hackbusch_sauter_1994, jarvenpaa_2003,khayat_2005,kress_boundary_1991,schwab_1992, ying_2006,beale1,beale2,goodman_1990, haroldson_1998, lowengrub_1993,schwab_1992,ggq1,ggq2,ggq3,helsing_2008a,helsing_integral_2009,helsing_tutorial_2012}
-and some of them are extremely efficient and can achieve arbitrary high order.
+accurate evaluation of boundary integrals with singular, weakly singular
+or nearly singular kernels. There are many numerical quadrature schemes
+for dealing with line integrals in two
+dimensions~\cite{alpert,kapur,sidi,duffy,bruno1,bruno2,davis_1984,graglia_2008,hackbusch_sauter_1994,
+jarvenpaa_2003,khayat_2005,kress_boundary_1991,schwab_1992,
+ying_2006,beale1,beale2,goodman_1990, haroldson_1998,
+lowengrub_1993,schwab_1992,ggq1,ggq2,ggq3,helsing_2008a,helsing_integral_2009,helsing_tutorial_2012}
+and some of them are extremely efficient and can achieve arbitrary high
+order.
 
 The high-order quadrature rules for the evaluation of surface integrals
-in three dimensions, however, are much less developed than the line integrals in two
-dimensions. For example, there are no Gaussian quadratures for integraing
-polynomials on a flat triangle, even though efficient quadratures
-\cite{xiao2010cma,vioreanu2014} have been
-developed recently for such purpose. For weakly singular or singular integrals,
-\cite{bremer2012jcp,bremer2013jcp} constructed high-order quadratures
-for surface integrals on a general triangle, while \cite{gimbutas2013sisc}
-presented a fast algorithm for integrating $1/r$-type singular integrals
-for surfaces that are homeomorphic to a sphere. We plan
-to study the so-called quadrature by expansion (QBX) scheme~\cite{klockner2013jcp,qbx2}
-for the evaluation
-of both singular and near-singular surface integrals encountered in the
-discretization of BIEs in three dimensions. Conceptually, the idea of the QBX
-to evaluate singular, hypersingular and near singular integrals
-on smooth surfaces is straightforward. That is, the surface is discretized
-into smooth triangles and smooth high-order quadratures are applied to evaluate
-the expansion coefficients
-on all source triangles with the QBX expansion center placed at a point off the surface.
-One may then form a suitable expansion (for example, a Taylor expansion) around that
-center and evaluate this expansion back at the target point on the surface (or close
-to the surface in the near singular case). Compared to the competing aforementioned
-quadrature schemes, the QBX quadrature is attractive
-because it offers a clear path for being extended to: \textbf{(1)}
-handle any singularity, including
-hypersingular operators, \textbf{(2)} be usable with any high-order surface
-discretization, \textbf{(3)} generate well-conditioned discrete
-operators to which iterative methods such as GMRES~\cite{gmres} can be
-applied in a black-box fashion, \textbf{(4)} integrate well with fast algorithms
-such as the FMM.
+in three dimensions, however, are much less developed than the line
+integrals in two dimensions. For example, there are no Gaussian
+quadratures for integraing polynomials on a flat triangle, even though
+efficient quadratures~\cite{xiao2010cma,vioreanu2014} have been
+developed recently for such purpose. For weakly singular or singular
+integrals,~\cite{bremer2012jcp,bremer2013jcp} constructed high-order
+quadratures for surface integrals on a general triangle,
+while~\cite{gimbutas2013sisc} presented a fast algorithm for integrating
+$1/r$-type singular integrals for surfaces that are homeomorphic to a
+sphere. We plan to study the so-called quadrature by expansion (QBX)
+scheme~\cite{klockner2013jcp,qbx2} for the evaluation of both singular
+and near-singular surface integrals encountered in the discretization of
+BIEs in three dimensions. Conceptually, the idea of the QBX to evaluate
+singular, hypersingular and near singular integrals on smooth surfaces
+is straightforward. That is, the surface is discretized into smooth
+triangles and smooth high-order quadratures are applied to evaluate the
+expansion coefficients on all source triangles with the QBX expansion
+center placed at a point off the surface. One may then form a suitable
+expansion (for example, a Taylor expansion) around that center and
+evaluate this expansion back at the target point on the surface (or
+close to the surface in the near singular case). Compared to the
+competing aforementioned quadrature schemes, the QBX quadrature is
+attractive because it offers a clear path for being extended to:
+\textbf{(1)} handle any singularity, including hypersingular operators,
+\textbf{(2)} be usable with any high-order surface discretization,
+\textbf{(3)} generate well-conditioned discrete operators to which
+iterative methods such as GMRES~\cite{gmres} can be applied in a
+black-box fashion, \textbf{(4)} integrate well with fast algorithms such
+as the FMM.
 
-In practice, there are still many issues that need to be resolved.
-For example, there are now many variants of QBX including global and local
-QBX~\cite{klockner2013jcp,rachh2017jcp}, the target-specific QBX~\cite{siegel2018jcp},
-kernel-independent QBX~\cite{abtin2018bit}, and
-quadrature by two expansions~\cite{ding2019arxiv}. The coupling of the QBX
-and the FMM may also lead to certain instability issues which may require
-some changes in the fast multipole method~\cite{wala2018jcp}. Similar
-to other quadrature methods, there have been extensive study on the QBX
-methods in two dimensions, while its three dimension
-version~\cite{wala2019jcp,af2018sisc,siegel2018jcp,wala2019arxiv} has not been
-fully studied and the implementation is even more scarce. We plan to investigate
-the accuracy and the convergence order of the various QBX schemes mentioned above,
-its coupling with the FMM, parallel implementation issues for large-scale
-problems, and the application to our target problems.
+In practice, there are still many issues that need to be resolved. For
+example, there are now many variants of QBX including global and local
+QBX~\cite{klockner2013jcp,rachh2017jcp}, the target-specific
+QBX~\cite{siegel2018jcp}, kernel-independent QBX~\cite{abtin2018bit},
+and quadrature by two expansions~\cite{ding2019arxiv}. The coupling of
+the QBX and the FMM may also lead to certain instability issues which
+may require some changes in the fast multipole
+method~\cite{wala2018jcp}. Similar to other quadrature methods, there
+have been extensive study on the QBX methods in two dimensions, while
+its three dimension
+version~\cite{wala2019jcp,af2018sisc,siegel2018jcp,wala2019arxiv} has
+not been fully studied and the implementation is even more scarce. We
+plan to investigate the accuracy and the convergence order of the
+various QBX schemes mentioned above, its coupling with the FMM, parallel
+implementation issues for large-scale problems, and the application to
+our target problems.
+
+% ----------------------------------------------------------------------
 \subsubsection{A hybrid method for close-to-touching Janus particles}
-The HAP model for membranes will inevitably lead to the case where some Janus particles
-will be very close to each other. Even though QBX can handle such case
-accurately, it may lead to excessively large number of unknowns in order to resolve
-the unknown densities at those close-to-touching points. In \cite{gan2016sisc},
-a hybrid scheme is developed to treat the close-to-touching spheres for the interface
-problem of the Laplace equation. The key idea is to combine the analytic image method
-and spectrally accurate method of moments, where the analytic image method will capture
-the most singular part of the unknown density at the close-to-touching points.
-With the aid of the FMM, the scheme achieves linear complexity with much less number
-of unknowns on the material interfaces.
-We plan to study the hybrid scheme
-to treat the close-to-touching case for both the screened Laplace equation and the
-mobility problem to further improve the efficiency of the numerical algorithm
-for the HAP model.
+The HAP model for membranes will inevitably lead to the case where some
+Janus particles will be very close to each other. Even though QBX can
+handle such case accurately, it may lead to excessively large number of
+unknowns in order to resolve the unknown densities at those
+close-to-touching points. In~\cite{gan2016sisc}, a hybrid scheme is
+developed to treat the close-to-touching spheres for the interface
+problem of the Laplace equation. The key idea is to combine the analytic
+image method and spectrally accurate method of moments, where the
+analytic image method will capture the most singular part of the unknown
+density at the close-to-touching points. With the aid of the FMM, the
+scheme achieves linear complexity with much less number of unknowns on
+the material interfaces. We plan to study the hybrid scheme to treat
+the close-to-touching case for both the screened Laplace equation and
+the mobility problem to further improve the efficiency of the numerical
+algorithm for the HAP model.
+
+% ----------------------------------------------------------------------
 \subsubsection{Other numerical issues}
-Another outstanding numerical issue pertaining to simulating the self-assembly of amphiphilic particles (such as lipid macromolecles) in a
-viscous solvent is the collision between amphiphilic particles.
-The hydrophobic attraction potential drives the amphiphilic particles to move towards each other so to minimize exposure to the solvent. 
-Under such
-attraction force the fluid is being squeezed out as particles move toward each other, and the amphiphilic particles can come into physical
-contact in finite time. 
-Such particle collisions in a dense rigid body suspension is a great challenge and can be a bottleneck in large-scale simulations. 
-In our previous work a Leonard-Jones potential is used to keep the
-particles from overlapping \cite{Fu2018_SIAM}. 
-Such steep steric interaction at
-short ranges introduces great numerical stiffness that limit the time step size.
+Another outstanding numerical issue pertaining to simulating the
+self-assembly of amphiphilic particles (such as lipid macromolecles) in
+a viscous solvent is the collision between amphiphilic particles. The
+hydrophobic attraction potential drives the amphiphilic particles to
+move towards each other so to minimize exposure to the solvent. Under
+such attraction force the fluid is being squeezed out as particles move
+toward each other, and the amphiphilic particles can come into physical
+contact in finite time. Such particle collisions in a dense rigid body
+suspension is a great challenge and can be a bottleneck in large-scale
+simulations. In our previous work a Leonard-Jones potential is used to
+keep the particles from overlapping~\cite{Fu2018_SIAM}. Such steep
+steric interaction at short ranges introduces great numerical stiffness
+that limit the time step size.
 
-Yan {\it et al.} proposed
-a collision-resolution algorithm within the framework of boundary integral methods to resolve the non-smooth many-body
-dynamics due to collisions by formulating the particle collision process as a linear complementarity problem with geometric 
-`non-overlapping' constraint \cite{Yan2019}. 
-We propose to treat the particle collisions based on Yan {\it et al.}'s work after the first two goals (see above)
-are achieved. 
-A potential complication in combining the algorithms for particle collision into our 
-QBX integral formulation is the computational cost for the QBX to refine meshes on particles in collision.
+Yan {\it et al.} proposed a collision-resolution algorithm within the
+framework of boundary integral methods to resolve the non-smooth
+many-body dynamics due to collisions by formulating the particle
+collision process as a linear complementarity problem with geometric
+`non-overlapping' constraint~\cite{Yan2019}. We propose to treat the
+particle collisions based on Yan {\it et al.}'s work after the first two
+goals (see above) are achieved. A potential complication in combining
+the algorithms for particle collision into our QBX integral formulation
+is the computational cost for the QBX to refine meshes on particles in
+collision.
 
-Once the collision-resolution algorithm is implemented, we will check the computing performance first before we embark on 
-incorporating fluctuating hydrodynamics \cite{Bao17,Bao18}, which might be important even at the scales of the amphiphilic 
-particle size in some cases. We propose to extend the high-order
-time-integration scheme for a stochastic differential equation
-\cite{fu2015pre} to
-this system.
+Once the collision-resolution algorithm is implemented, we will check
+the computing performance first before we embark on incorporating
+fluctuating hydrodynamics~\cite{Bao17,Bao18}, which might be important
+even at the scales of the amphiphilic particle size in some cases. We
+propose to extend the high-order time-integration scheme for a
+stochastic differential equation~\cite{fu2015pre} to this system.

### 2020-11-02 NSF2020/Description/specificaim1_ver2.tex
...

--- 2020-10-30 NSF2020/Description/specificaim1.tex
@@
 \label{sec:proposed-work}
-The goal of the proposed research is to develop fast,
+The proposed research develops fast,
 high-order-accurate, parallel numerical algorithms for large-scale
@@
 %
-We have demonstrated that 
-our potential theory approach can efficiently simulate self-assembly of 
-amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu19}.
+We have demonstrated that our potential approach efficiently simulates
+self-assembly of amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu19}, and
+recreates the tank-treading phenomenon in external shear flows \cite{Fu20}.
 %
-While these results show great potentials in simulating the collective hydrodynamics of amphiphilic particles and
-reproducing mechanical properties of their bilayer assembly, 
-several outstanding issues need to be addressed for such approach to be efficiently applied to three-dimensional 
-collective hydrodynamics of amphiphilic particles.
+While the results show great promise in the field of collective body hydrodynamics,
+several outstanding issues need to be addressed. These include a thorough 
+analysis of potentially new mechanical properties possessed by HAP bilayers, and 
+efficiently simulating three-dimensional collective hydrodynamics of amphiphilic particles.
+Finally, we must mathematically characterize the variational behavior of HAP under certain homogenized limits.
 
@@
 
- We conjecture that 
-once assembled, the bilayer shapes possess some or all of the mechanical properties of bilayers from continuum theory.
+Hamm and Kozlov (HK) pioneered the modern theory of membrane continuum mechanics in the early 2000s \cite{HaKo2000}.
+The HK framework assumes a three-dimensional, internal structure for lipid monolayers and 
+then uses the theory of elasticity to derive an effective, two-dimensional elastic energy.
+The internal structure consists of straight fibers that represent elongated hydrocarbon chains, and these fibers
+tilt and stretch with respect to the dividing surface. The elastic theory assumes an energy density that is
+quadratic in the Green-Lagrange strain tensor. Due to the internal structure ansatz, the elastic energy decomposes into
+four, fundamental and independent deformations: splay, saddle splay, twist and tilt.
+The elastic moduli for each deformation comes from a transversal moment of the internal stress.
+These moduli define the mechanical properties of lipid monolayers and bilayers.
+
+(Importance, take from Akimov PRE and Zimmerberg Soft Matter)
+
+Recently, there has been a revival in interest in the HK theory. The HK framework assumes a quadratic
+elasticity energy density and this has caused researchers in molecular dynamics to question the validity of
+the continuum theory \cite{PRL}. Zimmerberg and Akimov \cite{}, however, showed that for simplified deformations.
+that molecular dynamics and continuum theory agree even at small length scales.
+
+The elastic energy of monolayer is a function of the material coordinate and its derivatives. 
+That is because the changes in free energy, in elasticity theory, come from changes in spacing between mass points in a material.
+There are a number of mathematical models of membrane elasticity in applied mathematics. Our HAP formulation, however,
+is the first to explicitly consider intermolecular repulsion, and hydrophobic interaction with the solvent 
+to calculate the free energy of a lipids in a monolayer.
+
+What is the mathematical definition of a lipid monolayer and a deformation? 
+The reference state will lipids lying on a flat surface with their tails pointing in the 
+vertical direction. For concreteness, take the reference region to be the triangular prism 
+\begin{equation}
+\mathcal{R}_0 = \{(X_1, X_2, X_3) \mid 0 \leq X_1, 0 \leq X_2, X_1 + X_2 \leq a, 0 \leq X_3 \leq \delta \}
+\end{equation}
+The parameter $\delta$ is the monolayer height and $a$ is the edge length for the triangular base $\mathcal{T}$. 
+The size and shape of the base is arbitrary.
+
+The deformed state maps the flat base $\mathcal{T}$ to a curved surface $\mathcal{S} = x_0(\mathcal{T})$. 
+The vertical line segments in $\mathcal{R}_0$ represent
+hydrocarbon chains and map to line segments  in the deformed state.
+A director field $\mathbf{n}(\mathbf{x})$ for $\mathbf{x} \in \mathcal{S}$ specifies the direction. 
+Based on these considerations, the deformation takes the form  
+\begin{equation}
+x(X_1, X_2, X_3) = x_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) n(x_0(X_1, X_2))
+\end{equation}    
+To satisfy incompressibility, the chains stretch and compress parallel to their axis, but do not form kinks.
+For a point $P \in \mathcal{S},$ the function $\zeta(P, X_3)$ parametrizes the changes in change length and 
+$n(P)$ is the chain axis.  
+To simplify matters, we perform the calculations at one point on the surface. 
+Thus, assume, without loss of generality, that $x_0(0,0) = (0,0,0) = O$.
+
+The field of membrane continuum mechanics still lacks concensus as to the form of the elastic energy when
+it involves complicated deformations. Recently, Deserno included a tilt gradient term that was proportedly incorrectly neglected from the HK theory.
+Later Akimov and Deserno independently realized that there was inconsitency regarding the transversal invariance
+of tilt in Desrno's earlier work. The latest revision of HK theory by Akimov contains more than ten independent
+contributions to the elastic energy. We have found that the explosion in the number of elastic terms
+is a result of expanding the energy density in an incorrect reference frame, and that using a natural
+reference frame leads to a simplified energy resembling the Frank theory from the study of liquid crystals.
+
+Our investigations will leave open the possibility that the free energy of monolayers and bilayers is non-local. 
+We have shown that hydrophic attraction is a non-additive force, meaning the force of attraction between two
+particles is dependent on the position a third or more particles. Conceptually, this would arise in continuum theory if two monolayer surfaces
+had different elastic energy density at that point despite having locally identical curvatures and directors.
+
+Importance of the theory
+
+Mathematical setup and past contributions
+(old material)
+
+Revision
+
+We conjecture that the monolayer shapes 
+possess some or all of the mechanical properties of bilayers from continuum theory.
 

### 2020-11-03 code/src/rigid2D.m
adding velocity output

@@ -19,6 +19,9 @@ step = 0;
 xc0  = xc;
 tau0 = tau;
 om.writeData(time,geom.center,geom.tau,geom.X);
+% write the velocity to a file,initial velocities are 0
+om.writeVelData(time,0*geom.center,0*geom.tau);  
+
 
 trajectory = [xc(1,:) xc(2,:) tau];
 
@@ -66,6 +69,9 @@ while step < prams.m
       % write the shape to a file
       om.writeData(time,geom0.center,geom0.tau,geom0.X);
 
+      % write the velocity to a file
+      om.writeVelData(time,Up0,wp0);
+      
       % update step counter
       step = step + 1;
     end
@@ -98,6 +104,9 @@ while step < prams.m
   % write the shape to a file
   om.writeData(time,geom2.center,geom2.tau,geom2.X);
 
+  % write the velocity to a file
+  om.writeVelData(time,Up0,wp0);  
+  
   % update step counter
   step = step + 1;
 end

### 2020-11-03 NSF2020/Description/specificaim2_ver2.tex
working on proposal

@@
 boundary conditions. By construction, layer potentials satisfy the
-underlying PDE and the far-field conditions.
+underlying PDE and the far-field conditions. For the exterior Dirichlet
+problem of the screened Laplace equation, the BIE formulation in our
+previous work~\cite{Fu2018_SIAM} can be readily extended to three
+dimensions. For the mobility problem of the Stokes flow in three
+dimensions that takes the hydrodynamic effect into account, an
+well-conditioned BIE is found in~\cite{manasthesis}.
 
@@
 appropriate quadrature methods, the method converges with spectral or
-very high-order accuracy.
+very high-order accuracy. The most significant challenges include
+solving dense linear systems, developing preconditioning strategies, and
+developing quadrature methods for integrands that are nearly singular.
 
-Challenges are dense matrices, preconditioners, and near-singular
-integration
-
-%The HAP model requires solving the exterior Dirichlet problem of the
-%screened Laplace equation and the mobility problem of the Stokes flow
-%at each time step. Standard numerical methods such as finite difference
-%and finite element methods have to truncate the infinite domain to a
-%finite computational domain by imposing certain artificial boundary
-%conditions on the truncated domain and need the discretization of the
-%whole volume of the truncated domain. The artificial boundary
-%conditions are very often inexact, introducing another layer of
-%approximation that lowers the accuracy of the solution. The
-%discretization of the whole volume is very expensive for three
-%dimensional problems, leading to excessively large number of unknowns
-%in the linear system. Furthermore, it is rather difficult to obtain
-%high-order discretization when the boundary surfaces are irregular.
-
-Potential theory and boundary integral equation (BIE) methods remove the
-aforementioned obstacles in a very elegant way. The starting point is
-that for constant-coefficient PDEs the fundamental solutions, i.e., the
-Green's functions, are readily available. This allows us to represent
-the solution via the so-called layer potentials that are the convolution
-integrals of a kernel and an unknown density only on the boundary. The
-kernel is a linear combination of the Green's function and its
-derivatives, which ensures that the representation satifies the
-underlying PDE and the condition at infinity automatically. And the
-boundary condition at the material interfaces together with the jump
-relation of the layer potential leads to a boundary integral equation
-for the unknown density.
-
-%The BIE method removes the need of imposing artificial boundary
-%conditions for exterior problems and reduces the dimension of the
-%problem by one, leading to optimal number of unknowns in the solve
-%phase. Very often, one is able to construct the so-called {\it second
-%kind integral equation} (SKIE) formulation for these problems, where
-%the operator is a sum of the identity operator and a compact operator.
-%It is well-known that the condition number of the resulting linear
-%system for SKIEs is {\it independent} of the mesh size $h$ or
-%equivalently, the number of discretization points. This leads to a
-%constant number of iterations when iterative solvers are applied to
-%solve the resulting linear system. It further improves the accuracy of
-%the solution as the relative error of solution will never increase as
-%the number of total discretization points increases. On the other hand,
-%the condition number of the linear system from finite difference and
-%finite element methods generally increases as a power function of the
-%total number of dicretization points, with the exact power depending on
-%the underlying spatial dimension and the highest order of the
-%differential operator in the PDE. This leads to an increase in the
-%number of iterations (and hence the total computational cost) and an
-%increase in the relative error of the solution as the number of
-%dicretization points increases.
-
-The discretization of the integral operator often leads to a dense
-matrix, while finite difference/finite element methods result in sparse
-matrices, making matrix-vector product much cheaper to compute.
-However,since the invention of the original fast multipole method
-(FMM)\cite{fmm5}, there have been many fast
-algorithms~\cite{fmm1,fmm2,fmm3,fmm4,fmm6,fmm7,fmm8} that reduce the
-cost of matrix-vector product to linear ($O(N)$) or quasilinear
-complexity ($O(N \log^kN)$) for dense matrices resulting from the BIE
-discretization. Fast direct solvers have also been developed
-recently~\cite{fds1,fds2,fds3,fds4,fds5,fds6,fds7,fds8,ho2016cpam2,ho2016cpam1,minden2016,minden2017siammms}.
-The development of these fast algorithms have removed a huge hurdle for
-the use of boundary integral equations, making the BIE method the method
-of choice for constant-coefficient PDEs with linear boundary conditions.
-For the exterior Dirichlet problem of the screened Laplace equation, the
-SKIE formulation in our previous work~\cite{Fu2018_SIAM} can be readily
-extened to the 3D case. For the mobility problem of the Stokes flow in
-three dimensions that takes the hydrodynamic effect into account, an
-SKIE formulation can be found in~\cite{manasthesis}.
+By choosing BIEs that use a mesh-independent number of GMRES iterations,
+the overall cost of a solver is proportional to the complexity of the
+matrix-vector multiplication. The matrix-vector multiplication will be
+accelerated to optimal or near-optimal complexity using the fast
+multipole method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2,
+fmm3, fmm4, fmm6, fmm7, fmm8}. Alternatively, fast direct solvers can be
+used~\cite{fds1, fds2, fds3, fds4, fds5, fds6, fds7, fds8, ho2016cpam2,
+ho2016cpam1, minden2016, minden2017siammms}, but since direct solvers
+often require a large amount of initial overhead, they are less
+applicable to problems with moving geometries such as ours.
+Alternatively, fast direct solvers can be used to precondition the
+linear system as described in Section~\ref{subsec:NumericalIssues}.
 
 % ----------------------------------------------------------------------
-\subsubsection{High-order discretization of surface integrals in three
-dimensions}
-The practical application of integral equation methods requires the
-accurate evaluation of boundary integrals with singular, weakly singular
-or nearly singular kernels. There are many numerical quadrature schemes
-for dealing with line integrals in two
-dimensions~\cite{alpert,kapur,sidi,duffy,bruno1,bruno2,davis_1984,graglia_2008,hackbusch_sauter_1994,
-jarvenpaa_2003,khayat_2005,kress_boundary_1991,schwab_1992,
-ying_2006,beale1,beale2,goodman_1990, haroldson_1998,
-lowengrub_1993,schwab_1992,ggq1,ggq2,ggq3,helsing_2008a,helsing_integral_2009,helsing_tutorial_2012}
-and some of them are extremely efficient and can achieve arbitrary high
-order.
+\subsubsection{Nearly touching bodies}
+The trapezoid rule is the workhorse for BIEs since it achieves spectral
+accuracy for smooth periodic functions~\cite{tre-wei2014}. However,
+nearly touching bodies is ubiquitous in self-assembly of amphiphilic
+particles, and such near-contact results in  nearly-singular integrands.
+Quadrature methods to address such integrands has received a lot of
+attention in two and three dimensions~\cite{alpert, kapur, sidi, duffy,
+bruno1, bruno2, davis_1984, graglia_2008, hackbusch_sauter_1994,
+jarvenpaa_2003, khayat_2005, schwab_1992, ying_2006, beale1, beale2,
+goodman_1990, haroldson_1998, lowengrub_1993, schwab_1992, ggq1, ggq2,
+ggq3, helsing_2008a, helsing_integral_2009, helsing_tutorial_2012,
+klockner2013jcp, qbx2, wala2019jcp, af2018sisc, siegel2018jcp,
+rachh2017jcp, ding2019arxiv, bar2014}. For two-dimensional problems, an
+elegant quadrature method, which we will call a {\em barycentric
+quadrature rule}, is a mildly intrusive modification of the trapezoid
+rule relies on analytic function theory~\cite{ioa-pap-per1991}. Since
+the Stokes equations can be cast in terms of analytic functions, the
+barycentric-quadrature rule has recently been
+applied~\cite{bar-wu-vee2015, chi-moo-qua2020}. The PIs plan to extend
+this quadrature rule so that it can be applied to the screened Laplace
+equation.
 
-The high-order quadrature rules for the evaluation of surface integrals
-in three dimensions, however, are much less developed than the line
-integrals in two dimensions. For example, there are no Gaussian
-quadratures for integraing polynomials on a flat triangle, even though
-efficient quadratures~\cite{xiao2010cma,vioreanu2014} have been
-developed recently for such purpose. For weakly singular or singular
-integrals,~\cite{bremer2012jcp,bremer2013jcp} constructed high-order
-quadratures for surface integrals on a general triangle,
-while~\cite{gimbutas2013sisc} presented a fast algorithm for integrating
-$1/r$-type singular integrals for surfaces that are homeomorphic to a
-sphere. We plan to study the so-called quadrature by expansion (QBX)
-scheme~\cite{klockner2013jcp,qbx2} for the evaluation of both singular
-and near-singular surface integrals encountered in the discretization of
-BIEs in three dimensions. Conceptually, the idea of the QBX to evaluate
-singular, hypersingular and near singular integrals on smooth surfaces
-is straightforward. That is, the surface is discretized into smooth
-triangles and smooth high-order quadratures are applied to evaluate the
-expansion coefficients on all source triangles with the QBX expansion
-center placed at a point off the surface. One may then form a suitable
-expansion (for example, a Taylor expansion) around that center and
-evaluate this expansion back at the target point on the surface (or
-close to the surface in the near singular case). Compared to the
-competing aforementioned quadrature schemes, the QBX quadrature is
-attractive because it offers a clear path for being extended to:
-\textbf{(1)} handle any singularity, including hypersingular operators,
-\textbf{(2)} be usable with any high-order surface discretization,
-\textbf{(3)} generate well-conditioned discrete operators to which
-iterative methods such as GMRES~\cite{gmres} can be applied in a
-black-box fashion, \textbf{(4)} integrate well with fast algorithms such
-as the FMM.
-
-In practice, there are still many issues that need to be resolved. For
-example, there are now many variants of QBX including global and local
-QBX~\cite{klockner2013jcp,rachh2017jcp}, the target-specific
-QBX~\cite{siegel2018jcp}, kernel-independent QBX~\cite{abtin2018bit},
-and quadrature by two expansions~\cite{ding2019arxiv}. The coupling of
-the QBX and the FMM may also lead to certain instability issues which
-may require some changes in the fast multipole
-method~\cite{wala2018jcp}. Similar to other quadrature methods, there
-have been extensive study on the QBX methods in two dimensions, while
-its three dimension
-version~\cite{wala2019jcp,af2018sisc,siegel2018jcp,wala2019arxiv} has
-not been fully studied and the implementation is even more scarce. We
-plan to investigate the accuracy and the convergence order of the
-various QBX schemes mentioned above, its coupling with the FMM, parallel
-implementation issues for large-scale problems, and the application to
-our target problems.
-
-% ----------------------------------------------------------------------
-\subsubsection{A hybrid method for close-to-touching Janus particles}
-The HAP model for membranes will inevitably lead to the case where some
-Janus particles will be very close to each other. Even though QBX can
-handle such case accurately, it may lead to excessively large number of
-unknowns in order to resolve the unknown densities at those
-close-to-touching points. In~\cite{gan2016sisc}, a hybrid scheme is
-developed to treat the close-to-touching spheres for the interface
-problem of the Laplace equation. The key idea is to combine the analytic
-image method and spectrally accurate method of moments, where the
-analytic image method will capture the most singular part of the unknown
-density at the close-to-touching points. With the aid of the FMM, the
-scheme achieves linear complexity with much less number of unknowns on
-the material interfaces. We plan to study the hybrid scheme to treat
-the close-to-touching case for both the screened Laplace equation and
-the mobility problem to further improve the efficiency of the numerical
-algorithm for the HAP model.
-
-% ----------------------------------------------------------------------
-\subsubsection{Other numerical issues}
 Another outstanding numerical issue pertaining to simulating the
@@
 stochastic differential equation~\cite{fu2015pre} to this system.
+
+% ----------------------------------------------------------------------
+\subsubsection{Fluctuating hydrodynamics}
+Using DLP formulation for fluctuating hydrodynamics so that we have a
+second-kind BIE
+
+% ----------------------------------------------------------------------
+\subsubsection{Other numerical issues}
+\label{subsec:NumericalIssues}
+Preconditioning
+Adaptive high-order time stepping
+
+%The HAP model requires solving the exterior Dirichlet problem of the
+%screened Laplace equation and the mobility problem of the Stokes flow
+%at each time step. Standard numerical methods such as finite difference
+%and finite element methods have to truncate the infinite domain to a
+%finite computational domain by imposing certain artificial boundary
+%conditions on the truncated domain and need the discretization of the
+%whole volume of the truncated domain. The artificial boundary
+%conditions are very often inexact, introducing another layer of
+%approximation that lowers the accuracy of the solution. The
+%discretization of the whole volume is very expensive for three
+%dimensional problems, leading to excessively large number of unknowns
+%in the linear system. Furthermore, it is rather difficult to obtain
+%high-order discretization when the boundary surfaces are irregular.
+
+%Potential theory and boundary integral equation (BIE) methods remove the
+%aforementioned obstacles in a very elegant way. The starting point is
+%that for constant-coefficient PDEs the fundamental solutions, i.e., the
+%Green's functions, are readily available. This allows us to represent
+%the solution via the so-called layer potentials that are the convolution
+%integrals of a kernel and an unknown density only on the boundary. The
+%kernel is a linear combination of the Green's function and its
+%derivatives, which ensures that the representation satifies the
+%underlying PDE and the condition at infinity automatically. And the
+%boundary condition at the material interfaces together with the jump
+%relation of the layer potential leads to a boundary integral equation
+%for the unknown density.
+
+%The BIE method removes the need of imposing artificial boundary
+%conditions for exterior problems and reduces the dimension of the
+%problem by one, leading to optimal number of unknowns in the solve
+%phase. Very often, one is able to construct the so-called {\it second
+%kind integral equation} (SKIE) formulation for these problems, where
+%the operator is a sum of the identity operator and a compact operator.
+%It is well-known that the condition number of the resulting linear
+%system for SKIEs is {\it independent} of the mesh size $h$ or
+%equivalently, the number of discretization points. This leads to a
+%constant number of iterations when iterative solvers are applied to
+%solve the resulting linear system. It further improves the accuracy of
+%the solution as the relative error of solution will never increase as
+%the number of total discretization points increases. On the other hand,
+%the condition number of the linear system from finite difference and
+%finite element methods generally increases as a power function of the
+%total number of dicretization points, with the exact power depending on
+%the underlying spatial dimension and the highest order of the
+%differential operator in the PDE. This leads to an increase in the
+%number of iterations (and hence the total computational cost) and an
+%increase in the relative error of the solution as the number of
+%dicretization points increases.
+
+%The discretization of the integral operator often leads to a dense
+%matrix, while finite difference/finite element methods result in sparse
+%matrices, making matrix-vector product much cheaper to compute.
+%However,since the invention of the original fast multipole method
+%(FMM)\cite{fmm5}, there have been many fast
+%algorithms~\cite{fmm1,fmm2,fmm3,fmm4,fmm6,fmm7,fmm8} that reduce the
+%cost of matrix-vector product to linear ($O(N)$) or quasilinear
+%complexity ($O(N \log^kN)$) for dense matrices resulting from the BIE
+%discretization. Fast direct solvers have also been developed
+%recently~\cite{fds1,fds2,fds3,fds4,fds5,fds6,fds7,fds8,ho2016cpam2,ho2016cpam1,minden2016,minden2017siammms}.
+%The development of these fast algorithms have removed a huge hurdle for
+%the use of boundary integral equations, making the BIE method the
+%method of choice for constant-coefficient PDEs with linear boundary
+%conditions.  For the exterior Dirichlet problem of the screened Laplace
+%equation, the SKIE formulation in our previous work~\cite{Fu2018_SIAM}
+%can be readily extened to the 3D case. For the mobility problem of the
+%Stokes flow in three dimensions that takes the hydrodynamic effect into
+%account, an SKIE formulation can be found in~\cite{manasthesis}.
+
+%% ----------------------------------------------------------------------
+%\subsubsection{High-order discretization of surface integrals in three
+%dimensions}
+%The practical application of integral equation methods requires the
+%accurate evaluation of boundary integrals with singular, weakly singular
+%or nearly singular kernels. There are many numerical quadrature schemes
+%for dealing with line integrals in two
+%dimensions~\cite{alpert,kapur,sidi,duffy,bruno1,bruno2,davis_1984,graglia_2008,hackbusch_sauter_1994,
+%jarvenpaa_2003,khayat_2005,kress_boundary_1991,schwab_1992,
+%ying_2006,beale1,beale2,goodman_1990, haroldson_1998,
+%lowengrub_1993,schwab_1992,ggq1,ggq2,ggq3,helsing_2008a,helsing_integral_2009,helsing_tutorial_2012}
+%and some of them are extremely efficient and can achieve arbitrary high
+%order.
+%
+%The high-order quadrature rules for the evaluation of surface integrals
+%in three dimensions, however, are much less developed than the line
+%integrals in two dimensions. For example, there are no Gaussian
+%quadratures for integraing polynomials on a flat triangle, even though
+%efficient quadratures~\cite{xiao2010cma,vioreanu2014} have been
+%developed recently for such purpose. For weakly singular or singular
+%integrals,~\cite{bremer2012jcp,bremer2013jcp} constructed high-order
+%quadratures for surface integrals on a general triangle,
+%while~\cite{gimbutas2013sisc} presented a fast algorithm for integrating
+%$1/r$-type singular integrals for surfaces that are homeomorphic to a
+%sphere. We plan to study the so-called quadrature by expansion (QBX)
+%scheme~\cite{klockner2013jcp,qbx2} for the evaluation of both singular
+%and near-singular surface integrals encountered in the discretization of
+%BIEs in three dimensions. Conceptually, the idea of the QBX to evaluate
+%singular, hypersingular and near singular integrals on smooth surfaces
+%is straightforward. That is, the surface is discretized into smooth
+%triangles and smooth high-order quadratures are applied to evaluate the
+%expansion coefficients on all source triangles with the QBX expansion
+%center placed at a point off the surface. One may then form a suitable
+%expansion (for example, a Taylor expansion) around that center and
+%evaluate this expansion back at the target point on the surface (or
+%close to the surface in the near singular case). Compared to the
+%competing aforementioned quadrature schemes, the QBX quadrature is
+%attractive because it offers a clear path for being extended to:
+%\textbf{(1)} handle any singularity, including hypersingular operators,
+%\textbf{(2)} be usable with any high-order surface discretization,
+%\textbf{(3)} generate well-conditioned discrete operators to which
+%iterative methods such as GMRES~\cite{gmres} can be applied in a
+%black-box fashion, \textbf{(4)} integrate well with fast algorithms such
+%as the FMM. 
+%
+%In practice, there are still many issues that need to be resolved. For
+%example, there are now many variants of QBX including global and local
+%QBX~\cite{klockner2013jcp,rachh2017jcp}, the target-specific
+%QBX~\cite{siegel2018jcp}, kernel-independent QBX~\cite{abtin2018bit},
+%and quadrature by two expansions~\cite{ding2019arxiv}. The coupling of
+%the QBX and the FMM may also lead to certain instability issues which
+%may require some changes in the fast multipole
+%method~\cite{wala2018jcp}. Similar to other quadrature methods, there
+%have been extensive study on the QBX methods in two dimensions, while
+%its three dimension
+%version~\cite{wala2019jcp,af2018sisc,siegel2018jcp,wala2019arxiv} has
+%not been fully studied and the implementation is even more scarce. We
+%plan to investigate the accuracy and the convergence order of the
+%various QBX schemes mentioned above, its coupling with the FMM, parallel
+%implementation issues for large-scale problems, and the application to
+%our target problems.
+
+% ----------------------------------------------------------------------
+\subsubsection{A hybrid method for close-to-touching Janus particles}
+The HAP model for membranes will inevitably lead to the case where some
+Janus particles will be very close to each other. Even though QBX can
+handle such case accurately, it may lead to excessively large number of
+unknowns in order to resolve the unknown densities at those
+close-to-touching points. In~\cite{gan2016sisc}, a hybrid scheme is
+developed to treat the close-to-touching spheres for the interface
+problem of the Laplace equation. The key idea is to combine the analytic
+image method and spectrally accurate method of moments, where the
+analytic image method will capture the most singular part of the unknown
+density at the close-to-touching points. With the aid of the FMM, the
+scheme achieves linear complexity with much less number of unknowns on
+the material interfaces. We plan to study the hybrid scheme to treat
+the close-to-touching case for both the screened Laplace equation and
+the mobility problem to further improve the efficiency of the numerical
+algorithm for the HAP model.
+
+%% ----------------------------------------------------------------------
+%\subsubsection{Other numerical issues}
+%Another outstanding numerical issue pertaining to simulating the
+%self-assembly of amphiphilic particles (such as lipid macromolecles) in
+%a viscous solvent is the collision between amphiphilic particles. The
+%hydrophobic attraction potential drives the amphiphilic particles to
+%move towards each other so to minimize exposure to the solvent. Under
+%such attraction force the fluid is being squeezed out as particles move
+%toward each other, and the amphiphilic particles can come into physical
+%contact in finite time. Such particle collisions in a dense rigid body
+%suspension is a great challenge and can be a bottleneck in large-scale
+%simulations. In our previous work a Leonard-Jones potential is used to
+%keep the particles from overlapping~\cite{Fu2018_SIAM}. Such steep
+%steric interaction at short ranges introduces great numerical stiffness
+%that limit the time step size. 
+%
+%Yan {\it et al.} proposed a collision-resolution algorithm within the
+%framework of boundary integral methods to resolve the non-smooth
+%many-body dynamics due to collisions by formulating the particle
+%collision process as a linear complementarity problem with geometric
+%`non-overlapping' constraint~\cite{Yan2019}. We propose to treat the
+%particle collisions based on Yan {\it et al.}'s work after the first two
+%goals (see above) are achieved. A potential complication in combining
+%the algorithms for particle collision into our QBX integral formulation
+%is the computational cost for the QBX to refine meshes on particles in
+%collision.
+%
+%Once the collision-resolution algorithm is implemented, we will check
+%the computing performance first before we embark on incorporating
+%fluctuating hydrodynamics~\cite{Bao17,Bao18}, which might be important
+%even at the scales of the amphiphilic particle size in some cases. We
+%propose to extend the high-order time-integration scheme for a
+%stochastic differential equation~\cite{fu2015pre} to this system.

### 2020-11-04 NSF2020/Description/specificaim1_ver2.tex
modified specific aim version 2

--- 2020-10-30 NSF2020/Description/specificaim1.tex
@@
+\newpage
+
 \section{Proposed Research}
 \label{sec:proposed-work}
-The goal of the proposed research is to develop fast,
+The proposed research develops fast,
 high-order-accurate, parallel numerical algorithms for large-scale
@@
 %
-We have demonstrated that 
-our potential theory approach can efficiently simulate self-assembly of 
-amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu19}.
+We have demonstrated that our hydrophobic attraction with repulsion potential (HARP) approach efficiently simulates
+self-assembly of amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu19}, and
+recreates the tank-treading phenomenon in external shear flows \cite{Fu20}.
 %
-While these results show great potentials in simulating the collective hydrodynamics of amphiphilic particles and
-reproducing mechanical properties of their bilayer assembly, 
-several outstanding issues need to be addressed for such approach to be efficiently applied to three-dimensional 
-collective hydrodynamics of amphiphilic particles.
+While the results show great promise in the field of collective body hydrodynamics,
+several outstanding issues need to be addressed. These include a thorough 
+analysis of elastic properties of our coarse-grained bilayers, and 
+efficiently simulating three-dimensional collective hydrodynamics of amphiphilic particles.
+Finally, we must mathematically characterize the variational behavior of HAP under appropriate homogenized limits.
 
-\subsection{Specific Aim 1: Elastic properties of amphiphile ensembles}
+\subsection{Specific Aim 1: Collective elastic and hydrodynamic properties of amphiphilic particles}
 \label{subsec:specific_aim_1}
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{figures/SA1_fig1.pdf}
-\end{center}
-\caption{\footnotesize (A--C) The splay ($\Div \mathbf{d}$), 
-saddle splay ($\det \mathsf{D}$) and twist ($\Curl \mathbf{d}$) elastic distortions of 
-a monolayer. (D) The monolayer neutral surface $\Sigma$,  
-director $\mathbf{d}$ and unit normal $\mathbf{n}$ in local coordinates.
-(E--F) Lipids are able to tilt from  the surface normal, and stretch.
-(H--J) Intermediates of membrane fusion and (K) experimental image of a stalk \cite{Aeffner2012}. }
-\label{fig:distortions}
-\end{figure}
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.9\textwidth]{figures/SA1_fig1.pdf}
+%\end{center}
+%\caption{\footnotesize (A--C) The splay ($\Div \mathbf{d}$), 
+%saddle splay ($\det \mathsf{D}$) and twist ($\Curl \mathbf{d}$) elastic distortions of 
+%a monolayer. (D) The monolayer neutral surface $\Sigma$,  
+%director $\mathbf{d}$ and unit normal $\mathbf{n}$ in local coordinates.
+%(E--F) Lipids are able to tilt from  the surface normal, and stretch.
+%(H--J) Intermediates of membrane fusion and (K) experimental image of a stalk \cite{Aeffner2012}. }
+%\label{fig:distortions}
+%\end{figure}
 
- We conjecture that 
-once assembled, the bilayer shapes possess some or all of the mechanical properties of bilayers from continuum theory.
+The modern theory of membrane continuum mechanics
+was pioneered by Hamm and Kozlov (HK) \cite{HaKo2000}.
+The theory is widely used to describe biological phenomona 
+fission \cite{10.1016/j.chemphyslip.2014.07.006, 10.1038/nature14509, 10.1103/PhysRevE.79.031926},
+fusion \cite{10.1016/S0006-3495(02)75450-7,10.1073/pnas.121191898,10.1073/pnas.1119442109} ,
+poration \cite{10.1016/j.bpj.2019.11.2221}, phase boundaries and interaction with inclusions
+\cite{https://doi.org/10.1038/nrm.2017.16,10.1016/j.bpj.2019.11.2209, https://doi.org/10.1038/s41598-020-61110-2}, which require resolution of the internal structure of the membrane.  
+%The Helfrich hamiltonian is widely used to determine energy barriers of fusion between lipid bilayer membranes \cite{ChKo08}. 
+%Some of these barrier heights were never before obtained through the use of continuum membrane mechanics.
+Using the HK  model as a base,
+PI Ryham and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
+hemifusion diaphragm and the fusion pore \cite{RyWaCo13, RyKlYaCo16},
+%The calculation of hydrophobic 
+%fissures in \cite{RyKlYaCo16} motivated the HAP theory.
+and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
+are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.  
+%analyzed the dependence of energy barriers on
+%lipid composition and
 
-The mechanical properties of bilayer are characterized by the Helfrich Hamiltonian;
+The HK framework assumes a three-dimensional, internal structure for lipid monolayers.
+The internal structure consists of straight fibers that represent elongated hydrocarbon chains, and these fibers
+tilt and stretch with respect to the dividing surface--the surface formed lying between the hydrocarbon chains and polar heads of lipids.
+Accordingly, the deformation takes the form 
+\begin{equation}
+  \label{LMdeformation}
+x(X_1, X_2, X_3) = x_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) n(x_0(X_1, X_2))
+\end{equation}
+where $(X_1,X_2,X_3)$ are points in a reference volume.
+The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field $n$ parametrizes the
+direction of the lipid tails in the deformed state \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
+The parameter $X_3$ and the function $\zeta$ parametrizes the distance along the hydrocarbon chain in the reference state
+and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta \approx $ 2 nm is monolayer thickness.
+
+The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for $x$. 
+The chains stretch and compress to satisfy incompressibility.
+Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
+lead to an elastic surface energy over the dividing surface $\Sigma$. 
+This energy decomposes into four, fundamental and independent deformations:
+splay ($\Div n$), twist ($\Curl n$), saddle splay ($\det \nabla n$) and tilt $T$:
 \begin{equation}
@@
 \int_{\Sigma} 
-%&= \tfrac{1}{2}\KB\left[ \left( \tr \mathsf{D} + k_0\right)^2 - k_0^2\right] 
-%+ \tfrac{1}{2}\KT (\mathsf{D}_{21} - \mathsf{D}_{12})^2 + \KG  \det \mathsf{D}\\
- \tfrac{1}{2}\KB\left[ \left( \Div \mathbf{d} + k_0\right)^2 - k_0^2\right] 
-+ \tfrac{1}{2}\KT (\Curl \mathbf{d})^2 + \KG  \det \mathsf{D} \,dA.
+  \tfrac{1}{2}\KB\left[ \left( \Div n + k_0\right)^2 - k_0^2\right] 
++ \tfrac{1}{2}\KT (\Curl n)^2 + \KG  \det \nabla n + \KTH |T|^2 \,dA.
 \end{aligned}
 \end{equation}
-This hamiltonian is the energy functional for one monolayer,
-represented by a smooth surface $\Sigma$ and director field $\mathbf{d}$
- \cite{Helfrich73, PhysRevLett.113.248102, Hamm2000}.
-The surface $\Sigma$ coincides with the monolayer neutral surface. The 
-unit length director $\mathbf{d}$ tracks lipid orientations  
-and points from the lipid head toward the lipid tail \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
-In a bilayer, the energy is the sum of the two monolayer energies. 
-%These monolayers are typically coupled
-%by requiring apposing lipid tails to terminate at the same point.
+Here $\Div n$, $\Curl n$ and $\nabla n$ refer to the surface divergence, surface curl and surface gradient operators
+respectively (Figure \ref{fig:distortions}A--C).
+The deformations come with elastic coefficients: the \emph{bending modulus} $\KB$, \emph{twist modulus} $\KT$ 
+and \emph{saddle-splay modulus} $\KG$ and \emph{tilt modulus} $\KTH$
+HK define the tilt vector $T = n/(N\cdot n) - N$ where $N$ is the unit surface normal.
+
+The parameter $k_0$ is the \emph{spontaneous curvature} and it determines the preferred lipid splay \cite{RoLi15,Kozlov2007}. 
+As an illustration, the lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
+%as a result of  %having a relatively long acyl chain. 
+and these lipids would line the  inner monolayer of a 
+spherical liposome, because the addition of a positive splay $\Div \mathbf{d}$  in \eqref{ansatz3}
+to the negative spontaneous curvature $k_0$ leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
+The subtraction of $k_0^2$ makes the energy distortion free
+\cite{Helfrich73,PhysRevLett.113.248102,Hamm2000}.
+
+An interesting and challenging feature of \eqref{ansatz3} is that
+the elastic energy couples director gradients to surface geometry through the tilt vector field.
+In biological contexts, tilt appears at lipid domain boundaries, the edge of nanopores, and at the boundary of membrane inclusions \cite{https://doi.org/10.1103/PhysRevE.102.042406}, and the bilayer energy is the sum monolayer energies.
+Under spatial scales much larger than the membrane thickness, membrane energy is well-characterized by
+the Canham-Helfrich energy used throughout the fluid-structure literature \cite{}.
+The Canham-Helfrich energy is actually a special case of \eqref{ansatz3} obtained by setting $n =  \pm N$ (the $\pm$ depending
+on orientation) and collapsing both monolayers onto the membrane midplane. There,
+splay $\Div n$ equal to twice the mean curvature, saddle splay $\det \nabla n$ equal to the Gauss curvature,
+and both twist and tilt equaling zero.
 
@@
 The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
-liquid crystal theory. 
-The Helfrich hamiltonian derives from the assumption of a quadratic energy density
-in the director surface gradient 
-$[\mathsf{D}]_{ij} = \frac{\partial \mathbf{d} }{\partial \tau_i} \cdot \tau_j,$ $i,j = 1,2,$ 
-where $\tau_1$ and $\tau_2$ are orthogonal tangent vectors. Thus, the 
-director gradients in \eqref{ansatz3} couple to surface geometry. 
-Symmetries  with respect to mirror reflection and in-plane rotation 
-require that the energy come from
-\emph{splay} ($\Div \mathbf{d}$), 
-\emph{twist} ($\Curl \mathbf{d}$)
-or \emph{saddle-splay} ($\det \mathsf{D}$) distortions,
-where $\Div$ and $\Curl$ are the surface divergence  and curl  operators, respectively (Figure \ref{fig:distortions}A--C).
-The associated elastic coefficients  are the \emph{bending modulus} $\KB$,  \emph{twist modulus} $\KT$ 
-and \emph{saddle-splay modulus} $\KG$.
+liquid crystal theory. However, the ``bend'' distortion from nematics  
+is not present in monolayers since the directors have no dependence in the normal direction.
+There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection.
 
-The \emph{spontaneous curvature} $k_0$ depends on lipid composition and determines the preferred lipid splay,
-\cite{RoLi15,Kozlov2007}. 
-Figure \ref{fig:distortions}A illustrates positive splay. 
-The lipid DSPC, for instance, has $k_0 = -0.1$ nm$^{-1}$ 
-%as a result of  %having a relatively long acyl chain. 
-and these lipids would line the  inner monolayer of a 
-spherical liposome, because the addition of a positive splay $\Div \mathbf{d}$  in \eqref{ansatz3}
-to the negative spontaneous curvature $k_0$ leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
-The subtraction of $k_0^2$ makes the energy distortion 
-free\footnote{The  ``bend'' distortion from nematics  
-is not present in monolayers since the directors have no dependence in the normal direction,  \ie the 
-Frank ``bend'' constant $K_3$ should not be confused with the \emph{bending modulus} $\KB.$ 
-There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection.}.
+Recently, there has been a revival in interest in the HK theory. The quadratic assumption
+for the elasticity energy density has caused researchers to question the validity of \eqref{ansatz}
+for situations involving large curavtures \cite{PRL}. Zimmerberg and Akimov \cite{https://doi.org/10.1039/C9SM02079A}
+showed that energies derived from molecular dynamics and elasticity agree even in the case of large deformations.
+Part of this proposal will contribute to clarifying some of the mathematical
+assumptions that went into the HK theory.
 
-The Helfrich hamiltonian is widely used to determine energy barriers of fusion between lipid bilayer membranes \cite{ChKo08}. 
-%Some of these barrier heights were never before obtained through the use of continuum membrane mechanics.
-PI Ryham and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk, hemifusion diaphragm and the fusion pore  \cite{RyWaCo13, RyKlYaCo16}.
-%The calculation of hydrophobic 
-%fissures in \cite{RyKlYaCo16} motivated the HAP theory. 
-These studies 
-%analyzed the dependence of energy barriers on
-%lipid composition and 
-found that each of the transitions required on the order of 30 \kBT\; (Figure \ref{fig:barriers}A),
-a result that is in agreement with barrier heights derived by recent molecular dynamics and experimental studies
-\cite{FrRoPi17}.  
-(Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.)
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{figures/SA1_fig2.pdf}
-\end{center}\vspace{-1.em}
-\caption{\footnotesize (A) A partially clamped bilayer with mid-plane (dashed curve) under uniform load.
-The quartic fit comes from continuum theory. 
-(B) A circular vesicle at equilibrium. (C) The area modulus derives
-from convexity in energy as a function of radius. 
-\label{fig:bend}}
-\end{figure}
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=\textwidth]{figures/SA1_fig2.pdf}
+%\end{center}\vspace{-1.em}
+%\caption{\footnotesize (A) A partially clamped bilayer with mid-plane (dashed curve) under uniform load.
+%The quartic fit comes from continuum theory. 
+%(B) A circular vesicle at equilibrium. (C) The area modulus derives
+%from convexity in energy as a function of radius. 
+%\label{fig:bend}}
+%\end{figure}
 
@@
 and  interfacial tension $\gamma=4.1$ pN nm$^{-1}$  \cite{GarciaSaez, KUZMIN2005, Petelska2012}.
+Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.
 We first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
@@
 
-\begin{wrapfigure}[13]{l}{0.5\textwidth}
-\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
-\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
-diaphragm expansion (ii) and pore formation (iii). 
-(B) Saddle-splay energy for each change in \emph{monolayer} topology
-calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
-\label{fig:barriers}
-\end{wrapfigure}
+%\begin{wrapfigure}[13]{l}{0.5\textwidth}
+%\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
+%\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
+%diaphragm expansion (ii) and pore formation (iii). 
+%(B) Saddle-splay energy for each change in \emph{monolayer} topology
+%calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
+%\label{fig:barriers}
+%\end{wrapfigure}
+
 Experimental measurements have accurately determined 
@@
 
-We also considered the stretching deformation \cite{Fu19}. 
-Stretching occurs whenever there is an excess monolayer area,
-and it is energetically costly since it exposes hydrocarbon tails to water. 
-%Monolayers are not, strictly speaking, area incompressible,
-%and 
-Manipulation experiments give a monolayer area modulus in the range 
-30 -- 40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}. 
-To measure an area modulus, we stretched a circular vesicle, modeling the cross-section 
-of a bilayer tube (Figure \ref{fig:bend}B \& C).
-%We then stretched the vesicle beyond and beneath equilibrium radius and recorded the change in energy. 
-This procedure gave a monolayer area modulus 
-34 $\pm$ 2 \kBT \;nm$^{-2}$, independently of the vesicle size, which
-is also remarkably close to the experimental value.
+\newpage
+
+\subsubsection{What work will actually be done?}
+% Proposers should address what they want to do,
+% why they want to do it,
+% how they plan to do it,
+% how they will know if they succeed,
+% and what benefits could accrue if the project is successful.
+
+We will study the elastic properties of particle-based bilayers using static and hydrodynamic, large particle-number simulation. 
+The goal is to connect the deformations of particle bilayers to the deformations of HK theory, and in particular map the parameters of the
+particle-based system onto known, and experimentally measured elastic moduli.
 
@@
 ways to isolate or partially isolate the remaining distortions.
+
+\subsubsection{Hydrodynamic simulations}
+
+\subsubsection{Static simulations}
+Particle-based bilayers form because of the balance between hydrophobic attraction and excluded volume repulsion.
+As a result, a precise way to measure a certain elastic properties is to set up an externally loaded system,
+and then isolate the desired deformation by solving for the energy minimizer. The following give technical details on how we
+draw these connections in practice.
+In summary, the elastic moduli determine how lipid monolayers and bilayers mechanically behave.
+
+\begin{description}
+\item[Bending modulus] A planar bilayer that is deformed into the shape of a circular arc stores bending energy in the form of splay.
+  Bending isolates the splay deformation $\Div{n}$ because the twist and saddle-splay deformations are zero in two-dimensional bilayers,
+  and both MD and continuum mechanical simulations show that tilt is more or less zero due to lack of inclusions.
+  Moreover, the splay in the two leaflets of an arc approximately cancel when added, due to the smaller head to tail ratio in the inner leaflet and
+  larger head to tail ratio in the outer lealet, and so we can neglect the spontaneous curvature.
+
+  Using steepest gradient descent, the simulation tracks the relaxation of the energies $E$ of a sequence of arc-shaped bilayers tending toward and the equilibrium, planar bilayer.
+  We reconstruct the monolayer dividing surface (a curve $C$) and directors by interpolating the particle centers and orientations. Using spectral differentiation,
+  we can compute the curvature $\kappa$ of $C$ and the squared curvature energy $H = \int_C \kappa^2$. Since $\Div{n} = -\kappa$ in this setup, we can plot
+  the particle based values $\Delta E = E - E_0$ as a function of $\Delta H = H - H_0$ where $E_0$ and $H_0$ are the respective equilibrium values.
+
+  Figure \ref{} shows the appoximately linear relationship between $\Delta E$ and $\Delta H$.
+  The slope of the dashed line gives the bending modulus $\KB = 10$ kT. 
+  The simulation is for a realistic phospholipid length \cite{Boal},
+  the screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
+  and  interfacial tension $\gamma=4.1$ pN nm$^{-1}$  \cite{GarciaSaez, KUZMIN2005, Petelska2012}.
+
+  The parameters of our hydrophobic attraction formalism map accurately onto the experimentally determined moduli.  
+  The value $\KB = 10$ kT is a reasonable bending modulus for many lipid species \cite{}, and it depends linearly on
+  the interfacial tension parameter $\gamma$ of our model. The $\gamma = 4.1$ pN nm$^{-1}$ is
+  about a third of the surface tension of a typical hydrocarbon-water interface. M. Jackson points out, however, that the smaller interfacial tension parameter is actually the correct value 
+  to describe the free energy for placing molecular lipid into contact with water \cite{}.
+  So not only is the HARP model tunable to experimental parameters, but the results coincide with other properties from physical chemistry.
+
+\item[Tilt]
+\item[Spontaneous curvature]
+\item[Twist and saddle-splay]
+  We measure the elastic response to twist by following the relaxation
+  dynamics of an initially twisted membrane. Tilt is a fully three-dimensional deformation
+  and so the reference membrane is a pancake-shaped, planar bilayer with diamater
+  much larger than bilayer thickness.  In the initial configuration, the 
+  the directors behave to leading order as $n = (0, mx_1, \sqrt{1 - m^2x_1^2})$
+  where $x_1$ is the twisting axis. At the continuum level, 
+  the surface gradient $\nabla n = \begin{pmatrix}0 & 0\\ m & 0\end{pmatrix}$ that $\Div n = \mathrm{tr}(\nabla n) = 0$,
+  $\det(\nabla n) = 0$ and $\Curl d = (\nabla u)_{12} - (\nabla u)_{21} = m$,
+  so that twist is isolated and the continuum elastic energy equals $\KA m^2 A + O(1)$ where
+  $A \gg 1$ is the membrane area.
+
+  The initial bilayer consi
 The twist deformation, for example, has a modulus in the range of 1 to 2 \kBT\; 
@@
 We expect the particle-based approach can shed light on this inconsistency.   
+\item[Stretching]
+We also considered the stretching deformation \cite{Fu19}. 
+Stretching occurs whenever there is an excess monolayer area,
+and it is energetically costly since it exposes hydrocarbon tails to water. 
+%Monolayers are not, strictly speaking, area incompressible,
+%and 
+Manipulation experiments give a monolayer area modulus in the range 
+30 -- 40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}. 
+To measure an area modulus, we stretched a circular vesicle, modeling the cross-section 
+of a bilayer tube (Figure \ref{fig:bend}B \& C).
+%We then stretched the vesicle beyond and beneath equilibrium radius and recorded the change in energy. 
+This procedure gave a monolayer area modulus 
+34 $\pm$ 2 \kBT \;nm$^{-2}$, independently of the vesicle size, which
+is also remarkably close to the experimental value.
+
+\item[Fluctuation spectrum]
+\item[Revision of HK Theory]
+  It may come as a surprise that the field of membrane continuum mechanics still lacks concensus as to
+  whether \eqref{ansatz3} contains a complete list of consistent deformations.
+  The PI Ryham showed, for example, that the tilt energy density is interchangagle, up to second order, with
+  the simplified term $|n \times N|^2$ \cite{RyKlYaCo16}.
+  Recently, \cite{10.1063/1.4990404} derived a tilt curvature term that Hamm and Kozlov had neglected from their analysis \cite{HaKo2000}.
+  Later, \cite{https://doi.org/10.1039/C9SM02079A} 
+  and \cite{10.1103/PhysRevE.102.042406} independently identified an inconsitency in the transversal tilt invariance
+  assumption of Desrno's earlier work \cite{10.1063/1.4990404}.
+
+  We suspect the reason why, after twenty years, the field has yet to reach a concensus 
+  lies in the asymptotic expansions used to derive the elastic energy density. 
+  Past researchers expressed the strain tensor in
+  terms of the coordinate frame $\{\tau_1, \tau_2, N\}$ with surface tangent vectors $\tau_i$ and surface normal $N$.  
+  In this frame, there is a coupling between the gradients of all three terms $x_0,$ $\zeta$ and $n$ of the deformation \eqref{LMdeformation}.
+  The differential geometric arguments needed to determine which terms of the expansion to retain in the expansion are subtle,
+  and have caused \cite{10.1103/PhysRevE.102.042406} to derive an energy density with more than ten elastic parameters, for example.
+
+  However, expanding the strain tensor in terms of the coordinate frame $\{e_1, e_2, n\}$ with $e_i$ perpendicular to $n$
+  decouples a good portion of the gradient terms, leading to simplified expressions. For example,
+  in this coordinate frame, the incompressility condition leads to an exact relationship 
+  \begin{equation}
+    \label{elongation}
+    (1 + \Div n \zeta + \det \nabla n \zeta^2) \zeta' = 1
+  \end{equation}
+  for lipid elongation. \cite{HaKo2000} seem to have been aware of \eqref{elongation} for the special case of zero tilt,
+  but the works \cite{HaKo2000, https://doi.org/10.1039/C9SM02079A, 10.1063/1.4990404} use an approximate form of \eqref{elongation}
+  and \cite{10.1103/PhysRevE.102.042406} reports a form containing an erroneous $|T|^2$ in the $\zeta^0$ coefficient.
+
+Our investigations will leave open the possibility that the free energy of monolayers and bilayers is non-local. 
+We have shown that hydrophic attraction is a non-additive force, meaning the force of attraction between two
+particles is dependent on the position a third or more particles. Conceptually, this would arise in continuum theory if two monolayer surfaces
+had different elastic energy density at that point despite having locally identical curvatures and directors.
+
+\end{description}
+
+\newpage

### 2020-11-04 NSF2020/Description/specificaim2_ver2.tex
working on numerics for proposal

@@
 \subsubsection{Nearly touching bodies}
-The trapezoid rule is the workhorse for BIEs since it achieves spectral
-accuracy for smooth periodic functions~\cite{tre-wei2014}. However,
-nearly touching bodies is ubiquitous in self-assembly of amphiphilic
-particles, and such near-contact results in  nearly-singular integrands.
-Quadrature methods to address such integrands has received a lot of
-attention in two and three dimensions~\cite{alpert, kapur, sidi, duffy,
-bruno1, bruno2, davis_1984, graglia_2008, hackbusch_sauter_1994,
-jarvenpaa_2003, khayat_2005, schwab_1992, ying_2006, beale1, beale2,
-goodman_1990, haroldson_1998, lowengrub_1993, schwab_1992, ggq1, ggq2,
-ggq3, helsing_2008a, helsing_integral_2009, helsing_tutorial_2012,
-klockner2013jcp, qbx2, wala2019jcp, af2018sisc, siegel2018jcp,
-rachh2017jcp, ding2019arxiv, bar2014}. For two-dimensional problems, an
-elegant quadrature method, which we will call a {\em barycentric
-quadrature rule}, is a mildly intrusive modification of the trapezoid
-rule relies on analytic function theory~\cite{ioa-pap-per1991}. Since
-the Stokes equations can be cast in terms of analytic functions, the
-barycentric-quadrature rule has recently been
-applied~\cite{bar-wu-vee2015, chi-moo-qua2020}. The PIs plan to extend
+Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
+particles, and such near-contact results in nearly-singular integrands
+in both two and three dimensions. Quadrature methods to address such
+integrands has received a lot of attention in two and three
+dimensions~\cite{alpert, kapur, sidi, duffy, bruno1, bruno2, davis_1984,
+graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003, khayat_2005,
+schwab_1992, ying_2006, beale1, beale2, goodman_1990, haroldson_1998,
+lowengrub_1993, schwab_1992, ggq1, ggq2, ggq3, helsing_2008a,
+helsing_integral_2009, helsing_tutorial_2012, klockner2013jcp, qbx2,
+wala2019jcp, af2018sisc, siegel2018jcp, rachh2017jcp, ding2019arxiv,
+bar2014}. For two-dimensional problems, the trapezoid rule is the
+workhorse for BIEs since it achieves spectral accuracy when integrands
+are not nearly-singular~\cite{tre-wei2014}. To address nearly-singular
+integrands of two dimensional BIEs, we will use a {\em barycentric
+quadrature rule} that only requires a slight modification of the
+trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this method
+requires the layer potential satisfy Laplace or Stokes
+equations~\cite{bar-wu-vee2015, chi-moo-qua2020}. The PIs will extend
 this quadrature rule so that it can be applied to the screened Laplace
-equation.
+equation. This will be done by recognizing that the fundamental solution
+of the screened Laplace equation can be decomposed as
+$K(\mathbf{x},\mathbf{y}) = K_1(\mathbf{x},\mathbf{y}) +
+K_2(\mathbf{x},\mathbf{y})$, where $K_1(\mathbf{x},\mathbf{y}) =
+-\log\|\mathbf{x} - \mathbf{y}\|$ and $K_2(\mathbf{x},\mathbf{y}) =
+K(\mathbf{x},\mathbf{y}) + \log\|\mathbf{x} - \mathbf{y}\|$. Using this
+decomposition, the layer potential involving $K_1(\mathbf{x}\mathbf{y})$
+can be accurately computed with the barycentric quadrature
+rule~\cite{ioa-pap-per1991}, and the layer potential
+$K_2(\mathbf{x},\mathbf{y})$ can be accurately computed with the
+trapezoid rule since the kernel is bounded for all
+$\mathbf{x}$ and $\mathbf{y}$.
 
+Even with accurate quadrature and time stepping methods (see
+Section~\ref{subsec:NumericalIssues}) methods, rigid body simulations
+can still result in unphysical contact. In our previous work a
+Leonard-Jones potential is used to keep the particles from
+overlapping~\cite{Fu2018_SIAM}. Such steep steric interaction at short
+ranges introduces great numerical stiffness that limit the time step
+size.
+
+\textcolor{red}{
 Another outstanding numerical issue pertaining to simulating the
@@
 that limit the time step size. 
+}
 
+\textcolor{red}{
 Yan {\it et al.} proposed a collision-resolution algorithm within the
@@
 collision.
+}
 
+\textcolor{red}{
 Once the collision-resolution algorithm is implemented, we will check
@@
 stochastic differential equation~\cite{fu2015pre} to this system.
+}
 
@@
 \subsubsection{A hybrid method for close-to-touching Janus particles}
+\textcolor{red}{
 The HAP model for membranes will inevitably lead to the case where some
@@
 algorithm for the HAP model.
+}
 

### 2020-11-04 NSF2020/Description/specificaim2_ver2.tex
Rearranging files

--- 2020-11-02 NSF2020/Description/specificaim2_ver2.tex
@@
-\subsection{Specific Aim 2: Efficient high-order numerical algorithm for
-large-scale simulation of the HAP model}
+%\subsection{Specific Aim 2: Functional Materials}
+\subsection{Specific Aim 2: Hydrodynamics and ...}
 \label{subsec:specific_aim_2}
-% ----------------------------------------------------------------------
-\subsubsection{Overview of the potential theory and boundary integral
-equation methods} 
-The HAP model requires solving the exterior Dirichlet problem of the
-screened Laplace equation and the mobility problem of the Stokes flow at
-each time step. If discretizing these equations with stencil-based
-numerical methods, the computational domain must be truncated, the
-volume must be discretized, and artificial boundary conditions must be
-imposed. The artificial boundary conditions introduces an additional
-source of error, and discretizing the volume, particularly in three
-dimensions, results in an excessively large linear system. Moreover, it
-is difficult to obtain high-order discretizations when the boundary
-surfaces are irregular. Since we are solving constant-coefficient
-elliptic PDEs, we apply boundary integral equation (BIE) that remove the
-aforementioned obstacles. BIEs represent the solution as a layer
-potential with an unknown density function. Then, the correct density
-function is found that matching the layer potential with the prescribed
-boundary conditions. By construction, layer potentials satisfy the
-underlying PDE and the far-field conditions.
+%The mathematics of this proposal investigates how three-dimensional solids deform under long-range surface tension interaction.
+The results generalize the physical principles used in the design of functional materials, enabling investigators to simulate sub-micron scale systems that are otherwise impractical to realize experimentally.
+It supplies new insight into organizational principles in physical and biological sciences.
+%
+Over the past decade, there has been an explosion of interest in the fabrication of complex microscopic three-dimensional structures 
+\cite{Cho2010}.
+These fabrication processes utilize the fact that at small scales, capillary forces dominate  van der Waals interactions and thermal noise  \cite{Zhang2017}, enabling the coordinated movement and binding of material subunits.
+Two prominent fabrication techniques are capillary origami
+\cite{Pandey2011,Leong2007,Reynolds2019} and colloidal self-assembly \cite{Dasgupta2017,Siontorou2017}.
+Capillary origami uses principles of elastocapilirity wherein elastic solids deform under surface tension \cite{Bico2018,VanHonschoten2010}.
+In self-assembly of colloids,
+particles exhibit similar thermodynamic behavior of molecular systems, except that the behavior occurs over observable, long time scales \cite{Zhang2017}.
 
-Discretizations of BIEs have several advantages when compared to
-stencil-based discretizations. First, the dimension of the problem is
-reduced by one since the unknown density function is defined on the
-boundary of the geometry. Second, by carefully selecting each layer
-potential, the resulting linear system is well-conditioned for any
-resolution and iterative methods such as GMRES require a
-mesh-independent number of iterations to converge. Third, by using
-appropriate quadrature methods, the method converges with spectral or
-very high-order accuracy.
+There is inherent intellectual value in fabricating novel three dimensional structures: Living cells construct biological molecules like proteins, membranes and viral capsids using hierarchical assembly \cite{Whitesides2002}.
+At the same time, elastocapillarity and colloidal self-assembly supply model systems for biological processes, like vesicle adhesion and membrane bound protein interaction \cite{Dasgupta2017}, the hydro-polar model of protein folding \cite{Lau1989,Pandey2011} and viral capsid assembly and \cite{CASPAR1962}.
+Capillarity can serve as a model for the lock and key mechanism binding between the active site of an enzyme and a substrate molecule \cite{Araujo2018}, or treating viruses like adhered particles
+\cite{Agudo-Canalejo2017,Agudo-Canalejo2015,Deserno2004}, or studying decorated vesicles 
+\cite{Auth2009,Weikl2002,Atilgan2007}. Although challenging, mathematically analyzing these model systems gives deep insight into biological structure and function.
 
-Challenges are dense matrices, preconditioners, and near-singular
-integration
+%Aside from their intellectual value, high-yield batch production of three-dimensional microstructures has application in functional materials engineering \cite{Syms2003,Leong2010,Crane2013}.
+In mechanics, for instance, elasticapillarity is a guiding principle lithographic etching of electronics \cite{Bico2018}.
+Researchers have used self-folding structures in the design of micro containers for encapsulated drug delivery \cite{Fernandes2012} and 3D photovoltaic cells \cite{Guo2009}.
+%In chemical engineering, emulsions stabilize droplets through capillary binding or particulates leading 
+%to colloidosomes capturing proteins, vitamins, flavors, living cells \cite{Dinsmore2002}. 
+%Microsensors, electronic ink and micromotors \cite{Zhang2017,Yan2016} 
+%are potential applications involving Janus-like particles.
 
-%The HAP model requires solving the exterior Dirichlet problem of the
-%screened Laplace equation and the mobility problem of the Stokes flow
-%at each time step. Standard numerical methods such as finite difference
-%and finite element methods have to truncate the infinite domain to a
-%finite computational domain by imposing certain artificial boundary
-%conditions on the truncated domain and need the discretization of the
-%whole volume of the truncated domain. The artificial boundary
-%conditions are very often inexact, introducing another layer of
-%approximation that lowers the accuracy of the solution. The
-%discretization of the whole volume is very expensive for three
-%dimensional problems, leading to excessively large number of unknowns
-%in the linear system. Furthermore, it is rather difficult to obtain
-%high-order discretization when the boundary surfaces are irregular.
+\begin{wrapfigure}[14]{r}{3.0in}
+\vspace*{+15pt}
+\centerline{\includegraphics[width=3.0in]{figures/SA3_fig2.pdf}}
+\vspace*{5pt}
+\caption{{\footnotesize Illustration of self-assembly of hydrophobically labeled faces.
+The thick triangles have a rim-hydrophobic label on one side, and are hydrophilic on the other side.
+These shapes would potentially aggregate into a tetrahedral container. }}
+\label{fig:illustration}
+\end{wrapfigure}
+The HAP theory is ideally suited to the problem of creating microstructures through capillary action.
+Specifically, the modeling application considers the assembly of polyhedra from smaller subunits.
+Our developments, which include viscous interactions, thermal fluctuation, and a long range description of capillarity, will pave the way for dynamical understanding to organizational principles in viral capsid formation, for instance \cite{CASPAR1962,Prasad2012}.
 
-Potential theory and boundary integral equation (BIE) methods remove the
-aforementioned obstacles in a very elegant way. The starting point is
-that for constant-coefficient PDEs the fundamental solutions, i.e., the
-Green's functions, are readily available. This allows us to represent
-the solution via the so-called layer potentials that are the convolution
-integrals of a kernel and an unknown density only on the boundary. The
-kernel is a linear combination of the Green's function and its
-derivatives, which ensures that the representation satifies the
-underlying PDE and the condition at infinity automatically. And the
-boundary condition at the material interfaces together with the jump
-relation of the layer potential leads to a boundary integral equation
-for the unknown density.
+In order to illustrate the novelty of our approach, it is helpful to first describe how current experimental and mathematical techniques deal with polyhedral assembly.
+Capillary origami uses lithography to etch faces out of a thin, elastic sheet \cite{Pandey2011,Reynolds2019}.
+The collection of faces form a so-called net, and this net self-folds into a three-dimensional polyhedron (Figure~\ref{fig:illustration}).
+The motivation is to create micro containers to mimc protein folding \cite{Reynolds2019}.
+Prediction of geometric structure from its subunits is non-trivial.
+That is because the final morphology depends on the net structure, physical interactions, and the surrounding media, and researchers have formulated optimality criteria for these nets \cite{Araujo2018,Pandey2011}.
 
-%The BIE method removes the need of imposing artificial boundary
-%conditions for exterior problems and reduces the dimension of the
-%problem by one, leading to optimal number of unknowns in the solve
-%phase. Very often, one is able to construct the so-called {\it second
-%kind integral equation} (SKIE) formulation for these problems, where
-%the operator is a sum of the identity operator and a compact operator.
-%It is well-known that the condition number of the resulting linear
-%system for SKIEs is {\it independent} of the mesh size $h$ or
-%equivalently, the number of discretization points. This leads to a
-%constant number of iterations when iterative solvers are applied to
-%solve the resulting linear system. It further improves the accuracy of
-%the solution as the relative error of solution will never increase as
-%the number of total discretization points increases. On the other hand,
-%the condition number of the linear system from finite difference and
-%finite element methods generally increases as a power function of the
-%total number of dicretization points, with the exact power depending on
-%the underlying spatial dimension and the highest order of the
-%differential operator in the PDE. This leads to an increase in the
-%number of iterations (and hence the total computational cost) and an
-%increase in the relative error of the solution as the number of
-%dicretization points increases.
+The experimental shapes are hundreds of microns in diameter.
+Thus, as a key distinction with HAP approach, the driving force for folding in capillary origami and related processes comes from surface energy of the hinges (e.g.
+soldered hinges that supply a surface tension once the system is heated).
+Mathematicians have numerically and analytically described the behavior of these surface tension driven hinges \cite{Bico2018,Peraud2014,Brubaker2016}, making it possible to simulate the mechanical problem, in principle, using slender body theory for plates.
 
-The discretization of the integral operator often leads to a dense
-matrix, while finite difference/finite element methods result in sparse
-matrices, making matrix-vector product much cheaper to compute.
-However,since the invention of the original fast multipole method
-(FMM)\cite{fmm5}, there have been many fast
-algorithms~\cite{fmm1,fmm2,fmm3,fmm4,fmm6,fmm7,fmm8} that reduce the
-cost of matrix-vector product to linear ($O(N)$) or quasilinear
-complexity ($O(N \log^kN)$) for dense matrices resulting from the BIE
-discretization. Fast direct solvers have also been developed
-recently~\cite{fds1,fds2,fds3,fds4,fds5,fds6,fds7,fds8,ho2016cpam2,ho2016cpam1,minden2016,minden2017siammms}.
-The development of these fast algorithms have removed a huge hurdle for
-the use of boundary integral equations, making the BIE method the method
-of choice for constant-coefficient PDEs with linear boundary conditions.
-For the exterior Dirichlet problem of the screened Laplace equation, the
-SKIE formulation in our previous work~\cite{Fu2018_SIAM} can be readily
-extened to the 3D case. For the mobility problem of the Stokes flow in
-three dimensions that takes the hydrodynamic effect into account, an
-SKIE formulation can be found in~\cite{manasthesis}.
+To study this problem using HAP theory, we form a collection of thin, prism-like particles in Figure \ref{fig:illustration}. 
+Each of these particles serves as a face in the final morphology.
+The edges of the prisms are labeled hydrophobic according to the boundary condition in the screened Laplace equation boundary value problem.
+This way, the edges coalesce, forming the desired structures.
+Furthermore,
+by manipulating the boundary condition in HAP, it is possible to have faces attach and detach with precision, and form a net or other structures if so desired.
+Our HAP theory therefore generalizes submillimeter theoretical and experimental work to the micron and nanometer sizes.
 
-% ----------------------------------------------------------------------
-\subsubsection{High-order discretization of surface integrals in three
-dimensions}
-The practical application of integral equation methods requires the
-accurate evaluation of boundary integrals with singular, weakly singular
-or nearly singular kernels. There are many numerical quadrature schemes
-for dealing with line integrals in two
-dimensions~\cite{alpert,kapur,sidi,duffy,bruno1,bruno2,davis_1984,graglia_2008,hackbusch_sauter_1994,
-jarvenpaa_2003,khayat_2005,kress_boundary_1991,schwab_1992,
-ying_2006,beale1,beale2,goodman_1990, haroldson_1998,
-lowengrub_1993,schwab_1992,ggq1,ggq2,ggq3,helsing_2008a,helsing_integral_2009,helsing_tutorial_2012}
-and some of them are extremely efficient and can achieve arbitrary high
-order.
+%There is also the possibility to explore new classes of mathematical materials, like wrinkling in polystyrene sheets \cite{Paulsen2016}, that include the interaction between an elastic material, the viscous solvent, and long range hydrophobic (capillary) interactions.
+In the case of rigid particles and subunits, the rigid body motions come from the so-called mobility boundary value problem for the Stokes equation.
+Here, the hydrophobic stress balances with the viscous stress coming from the rigid body motion of the particles in the surrounding solvent.
+If the particles are deformable, like a protein \cite{Elms2012} or as in the capillary induced bending of rods \cite{Schulman2017}, then we can formulate an elastic energy for deformation.
+These elastic energies account for surface bending or even permanent charge.
+To deploy this approach, it is a matter of solving the bodies' momentum balance equations coupled to the fluid through the viscous, elastic, and hydrophobic stress balance.
 
-The high-order quadrature rules for the evaluation of surface integrals
-in three dimensions, however, are much less developed than the line
-integrals in two dimensions. For example, there are no Gaussian
-quadratures for integraing polynomials on a flat triangle, even though
-efficient quadratures~\cite{xiao2010cma,vioreanu2014} have been
-developed recently for such purpose. For weakly singular or singular
-integrals,~\cite{bremer2012jcp,bremer2013jcp} constructed high-order
-quadratures for surface integrals on a general triangle,
-while~\cite{gimbutas2013sisc} presented a fast algorithm for integrating
-$1/r$-type singular integrals for surfaces that are homeomorphic to a
-sphere. We plan to study the so-called quadrature by expansion (QBX)
-scheme~\cite{klockner2013jcp,qbx2} for the evaluation of both singular
-and near-singular surface integrals encountered in the discretization of
-BIEs in three dimensions. Conceptually, the idea of the QBX to evaluate
-singular, hypersingular and near singular integrals on smooth surfaces
-is straightforward. That is, the surface is discretized into smooth
-triangles and smooth high-order quadratures are applied to evaluate the
-expansion coefficients on all source triangles with the QBX expansion
-center placed at a point off the surface. One may then form a suitable
-expansion (for example, a Taylor expansion) around that center and
-evaluate this expansion back at the target point on the surface (or
-close to the surface in the near singular case). Compared to the
-competing aforementioned quadrature schemes, the QBX quadrature is
-attractive because it offers a clear path for being extended to:
-\textbf{(1)} handle any singularity, including hypersingular operators,
-\textbf{(2)} be usable with any high-order surface discretization,
-\textbf{(3)} generate well-conditioned discrete operators to which
-iterative methods such as GMRES~\cite{gmres} can be applied in a
-black-box fashion, \textbf{(4)} integrate well with fast algorithms such
-as the FMM.
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{figures/SA3_fig1.pdf}
+\end{center}
+\caption{(A)--(D) shows the spontaneous insertion of two hydrophobic particles into a vesicle bilayer. 
+The driving force is long-range interaction between the hydrophobic, magenta particles and
+the bilayer core.  The particle entrainment cause the vesicle to break apart, analogously to surfactant
+induced lysis.}
+\end{figure}
+Finally, further applications of our modeling approach include colloidal interaction on interfaces.
+Here, the experimental setups use Janus particles to model, for example, membrane bound proteins \cite{Kumar2013,Lehle2008,Zhang2017}.
+The idea of an amphiphilic Janus particle was introduced by P.
+G.
+de Gennes in 1991 \cite{Zhang2017}.
+The Investigators have significant experience as Janus particles figure heavily into our particle based description of bilayers, and can adjust our modeling approach to account for proteins.
+This is done by consider mixtures, consisting of many (hundreds to thousands) long, elongated amphiphilic particles for the lipid phase.
+Larger particles with hydrophobic patches or stripes model the proteins \cite{Jurasek2017}.
 
-In practice, there are still many issues that need to be resolved. For
-example, there are now many variants of QBX including global and local
-QBX~\cite{klockner2013jcp,rachh2017jcp}, the target-specific
-QBX~\cite{siegel2018jcp}, kernel-independent QBX~\cite{abtin2018bit},
-and quadrature by two expansions~\cite{ding2019arxiv}. The coupling of
-the QBX and the FMM may also lead to certain instability issues which
-may require some changes in the fast multipole
-method~\cite{wala2018jcp}. Similar to other quadrature methods, there
-have been extensive study on the QBX methods in two dimensions, while
-its three dimension
-version~\cite{wala2019jcp,af2018sisc,siegel2018jcp,wala2019arxiv} has
-not been fully studied and the implementation is even more scarce. We
-plan to investigate the accuracy and the convergence order of the
-various QBX schemes mentioned above, its coupling with the FMM, parallel
-implementation issues for large-scale problems, and the application to
-our target problems.
-
-% ----------------------------------------------------------------------
-\subsubsection{A hybrid method for close-to-touching Janus particles}
-The HAP model for membranes will inevitably lead to the case where some
-Janus particles will be very close to each other. Even though QBX can
-handle such case accurately, it may lead to excessively large number of
-unknowns in order to resolve the unknown densities at those
-close-to-touching points. In~\cite{gan2016sisc}, a hybrid scheme is
-developed to treat the close-to-touching spheres for the interface
-problem of the Laplace equation. The key idea is to combine the analytic
-image method and spectrally accurate method of moments, where the
-analytic image method will capture the most singular part of the unknown
-density at the close-to-touching points. With the aid of the FMM, the
-scheme achieves linear complexity with much less number of unknowns on
-the material interfaces. We plan to study the hybrid scheme to treat
-the close-to-touching case for both the screened Laplace equation and
-the mobility problem to further improve the efficiency of the numerical
-algorithm for the HAP model.
-
-% ----------------------------------------------------------------------
-\subsubsection{Other numerical issues}
-Another outstanding numerical issue pertaining to simulating the
-self-assembly of amphiphilic particles (such as lipid macromolecles) in
-a viscous solvent is the collision between amphiphilic particles. The
-hydrophobic attraction potential drives the amphiphilic particles to
-move towards each other so to minimize exposure to the solvent. Under
-such attraction force the fluid is being squeezed out as particles move
-toward each other, and the amphiphilic particles can come into physical
-contact in finite time. Such particle collisions in a dense rigid body
-suspension is a great challenge and can be a bottleneck in large-scale
-simulations. In our previous work a Leonard-Jones potential is used to
-keep the particles from overlapping~\cite{Fu2018_SIAM}. Such steep
-steric interaction at short ranges introduces great numerical stiffness
-that limit the time step size.
-
-Yan {\it et al.} proposed a collision-resolution algorithm within the
-framework of boundary integral methods to resolve the non-smooth
-many-body dynamics due to collisions by formulating the particle
-collision process as a linear complementarity problem with geometric
-`non-overlapping' constraint~\cite{Yan2019}. We propose to treat the
-particle collisions based on Yan {\it et al.}'s work after the first two
-goals (see above) are achieved. A potential complication in combining
-the algorithms for particle collision into our QBX integral formulation
-is the computational cost for the QBX to refine meshes on particles in
-collision.
-
-Once the collision-resolution algorithm is implemented, we will check
-the computing performance first before we embark on incorporating
-fluctuating hydrodynamics~\cite{Bao17,Bao18}, which might be important
-even at the scales of the amphiphilic particle size in some cases. We
-propose to extend the high-order time-integration scheme for a
-stochastic differential equation~\cite{fu2015pre} to this system.
+The distinction between macroscopic capillarity and microscopic hydrophobic force are relevant here as well.
+Prior models use surface energies to account for interaction between particles in an interface \cite{Dasgupta2017}.
+However, this may be missing important physics, and here our modeling approach has the advantage in that protein insertion, for instance, is a self-consistent consequence of the formulation, versus an assumption imposed by boundary conditions.
+The simulations will enable us address important biological questions on how a collection of 
+interface bound colloids interact \cite{Yao2013,Salib2013}, 
+and how configurations dictate 
+macroscopic surface properties and sense background curvature \cite{Cavallaro2011,Liu2018,Sharifi-Mood2015}.

### 2020-11-04 NSF2020/Description/specificaim3_ver2.tex
Rearranging files

\subsection{Specific Aim 3: Efficient high-order numerical algorithm for
large-scale simulations}
\label{subsec:specific_aim_3}
% ----------------------------------------------------------------------
\subsubsection{Overview of the potential theory and boundary integral
equation methods} 
The HAP model requires solving the exterior Dirichlet problem of the
screened Laplace equation and the mobility problem of the Stokes flow at
each time step. If discretizing these equations with stencil-based
numerical methods, the computational domain must be truncated, the
volume must be discretized, and artificial boundary conditions must be
imposed. The artificial boundary conditions introduces an additional
source of error, and discretizing the volume, particularly in three
dimensions, results in an excessively large linear system. Moreover, it
is difficult to obtain high-order discretizations when the boundary
surfaces are irregular. Since we are solving constant-coefficient
elliptic PDEs, we apply boundary integral equation (BIE) that remove the
aforementioned obstacles. BIEs represent the solution as a layer
potential with an unknown density function. Then, the correct density
function is found that matching the layer potential with the prescribed
boundary conditions. By construction, layer potentials satisfy the
underlying PDE and the far-field conditions. For the exterior Dirichlet
problem of the screened Laplace equation, the BIE formulation in our
previous work~\cite{Fu2018_SIAM} can be readily extended to three
dimensions. For the mobility problem of the Stokes flow in three
dimensions that takes the hydrodynamic effect into account, an
well-conditioned BIE is found in~\cite{manasthesis}.

Discretizations of BIEs have several advantages when compared to
stencil-based discretizations. First, the dimension of the problem is
reduced by one since the unknown density function is defined on the
boundary of the geometry. Second, by carefully selecting each layer
potential, the resulting linear system is well-conditioned for any
resolution and iterative methods such as GMRES require a
mesh-independent number of iterations to converge. Third, by using
appropriate quadrature methods, the method converges with spectral or
very high-order accuracy. The most significant challenges include
solving dense linear systems, developing preconditioning strategies, and
developing quadrature methods for integrands that are nearly singular.

By choosing BIEs that use a mesh-independent number of GMRES iterations,
the overall cost of a solver is proportional to the complexity of the
matrix-vector multiplication. The matrix-vector multiplication will be
accelerated to optimal or near-optimal complexity using the fast
multipole method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2,
fmm3, fmm4, fmm6, fmm7, fmm8}. Alternatively, fast direct solvers can be
used~\cite{fds1, fds2, fds3, fds4, fds5, fds6, fds7, fds8, ho2016cpam2,
ho2016cpam1, minden2016, minden2017siammms}, but since direct solvers
often require a large amount of initial overhead, they are less
applicable to problems with moving geometries such as ours.
Alternatively, fast direct solvers can be used to precondition the
linear system as described in Section~\ref{subsec:NumericalIssues}.

% ----------------------------------------------------------------------
\subsubsection{Nearly touching bodies}
Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
particles, and such near-contact results in nearly-singular integrands
in both two and three dimensions. Quadrature methods to address such
integrands has received a lot of attention in two and three
dimensions~\cite{alpert, kapur, sidi, duffy, bruno1, bruno2, davis_1984,
graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003, khayat_2005,
schwab_1992, ying_2006, beale1, beale2, goodman_1990, haroldson_1998,
lowengrub_1993, schwab_1992, ggq1, ggq2, ggq3, helsing_2008a,
helsing_integral_2009, helsing_tutorial_2012, klockner2013jcp, qbx2,
wala2019jcp, af2018sisc, siegel2018jcp, rachh2017jcp, ding2019arxiv,
bar2014}. For two-dimensional problems, the trapezoid rule is the
workhorse for BIEs since it achieves spectral accuracy when integrands
are not nearly-singular~\cite{tre-wei2014}. To address nearly-singular
integrands of two dimensional BIEs, we will use a {\em barycentric
quadrature rule} that only requires a slight modification of the
trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this method
requires the layer potential satisfy Laplace or Stokes
equations~\cite{bar-wu-vee2015, chi-moo-qua2020}. The PIs will extend
this quadrature rule so that it can be applied to the screened Laplace
equation. This will be done by recognizing that the fundamental solution
of the screened Laplace equation can be decomposed as
$K(\mathbf{x},\mathbf{y}) = K_1(\mathbf{x},\mathbf{y}) +
K_2(\mathbf{x},\mathbf{y})$, where $K_1(\mathbf{x},\mathbf{y}) =
-\log\|\mathbf{x} - \mathbf{y}\|$ and $K_2(\mathbf{x},\mathbf{y}) =
K(\mathbf{x},\mathbf{y}) + \log\|\mathbf{x} - \mathbf{y}\|$. Using this
decomposition, the layer potential involving $K_1(\mathbf{x}\mathbf{y})$
can be accurately computed with the barycentric quadrature
rule~\cite{ioa-pap-per1991}, and the layer potential
$K_2(\mathbf{x},\mathbf{y})$ can be accurately computed with the
trapezoid rule since the kernel is bounded for all
$\mathbf{x}$ and $\mathbf{y}$.

Even with accurate quadrature and time stepping methods (see
Section~\ref{subsec:NumericalIssues}) methods, rigid body simulations
can still result in unphysical contact. In our previous work a
Leonard-Jones potential is used to keep the particles from
overlapping~\cite{Fu2018_SIAM}. Such steep steric interaction at short
ranges introduces great numerical stiffness that limit the time step
size.

\textcolor{red}{
Another outstanding numerical issue pertaining to simulating the
self-assembly of amphiphilic particles (such as lipid macromolecles) in
a viscous solvent is the collision between amphiphilic particles. The
hydrophobic attraction potential drives the amphiphilic particles to
move towards each other so to minimize exposure to the solvent. Under
such attraction force the fluid is being squeezed out as particles move
toward each other, and the amphiphilic particles can come into physical
contact in finite time. Such particle collisions in a dense rigid body
suspension is a great challenge and can be a bottleneck in large-scale
simulations. In our previous work a Leonard-Jones potential is used to
keep the particles from overlapping~\cite{Fu2018_SIAM}. Such steep
steric interaction at short ranges introduces great numerical stiffness
that limit the time step size. 
}

\textcolor{red}{
Yan {\it et al.} proposed a collision-resolution algorithm within the
framework of boundary integral methods to resolve the non-smooth
many-body dynamics due to collisions by formulating the particle
collision process as a linear complementarity problem with geometric
`non-overlapping' constraint~\cite{Yan2019}. We propose to treat the
particle collisions based on Yan {\it et al.}'s work after the first two
goals (see above) are achieved. A potential complication in combining
the algorithms for particle collision into our QBX integral formulation
is the computational cost for the QBX to refine meshes on particles in
collision.
}

\textcolor{red}{
Once the collision-resolution algorithm is implemented, we will check
the computing performance first before we embark on incorporating
fluctuating hydrodynamics~\cite{Bao17,Bao18}, which might be important
even at the scales of the amphiphilic particle size in some cases. We
propose to extend the high-order time-integration scheme for a
stochastic differential equation~\cite{fu2015pre} to this system.
}

% ----------------------------------------------------------------------
\subsubsection{Fluctuating hydrodynamics}
Using DLP formulation for fluctuating hydrodynamics so that we have a
second-kind BIE

% ----------------------------------------------------------------------
\subsubsection{Other numerical issues}
\label{subsec:NumericalIssues}
Preconditioning
Adaptive high-order time stepping

%The HAP model requires solving the exterior Dirichlet problem of the
%screened Laplace equation and the mobility problem of the Stokes flow
%at each time step. Standard numerical methods such as finite difference
%and finite element methods have to truncate the infinite domain to a
%finite computational domain by imposing certain artificial boundary
%conditions on the truncated domain and need the discretization of the
%whole volume of the truncated domain. The artificial boundary
%conditions are very often inexact, introducing another layer of
%approximation that lowers the accuracy of the solution. The
%discretization of the whole volume is very expensive for three
%dimensional problems, leading to excessively large number of unknowns
%in the linear system. Furthermore, it is rather difficult to obtain
%high-order discretization when the boundary surfaces are irregular.

%Potential theory and boundary integral equation (BIE) methods remove the
%aforementioned obstacles in a very elegant way. The starting point is
%that for constant-coefficient PDEs the fundamental solutions, i.e., the
%Green's functions, are readily available. This allows us to represent
%the solution via the so-called layer potentials that are the convolution
%integrals of a kernel and an unknown density only on the boundary. The
%kernel is a linear combination of the Green's function and its
%derivatives, which ensures that the representation satifies the
%underlying PDE and the condition at infinity automatically. And the
%boundary condition at the material interfaces together with the jump
%relation of the layer potential leads to a boundary integral equation
%for the unknown density.

%The BIE method removes the need of imposing artificial boundary
%conditions for exterior problems and reduces the dimension of the
%problem by one, leading to optimal number of unknowns in the solve
%phase. Very often, one is able to construct the so-called {\it second
%kind integral equation} (SKIE) formulation for these problems, where
%the operator is a sum of the identity operator and a compact operator.
%It is well-known that the condition number of the resulting linear
%system for SKIEs is {\it independent} of the mesh size $h$ or
%equivalently, the number of discretization points. This leads to a
%constant number of iterations when iterative solvers are applied to
%solve the resulting linear system. It further improves the accuracy of
%the solution as the relative error of solution will never increase as
%the number of total discretization points increases. On the other hand,
%the condition number of the linear system from finite difference and
%finite element methods generally increases as a power function of the
%total number of dicretization points, with the exact power depending on
%the underlying spatial dimension and the highest order of the
%differential operator in the PDE. This leads to an increase in the
%number of iterations (and hence the total computational cost) and an
%increase in the relative error of the solution as the number of
%dicretization points increases.

%The discretization of the integral operator often leads to a dense
%matrix, while finite difference/finite element methods result in sparse
%matrices, making matrix-vector product much cheaper to compute.
%However,since the invention of the original fast multipole method
%(FMM)\cite{fmm5}, there have been many fast
%algorithms~\cite{fmm1,fmm2,fmm3,fmm4,fmm6,fmm7,fmm8} that reduce the
%cost of matrix-vector product to linear ($O(N)$) or quasilinear
%complexity ($O(N \log^kN)$) for dense matrices resulting from the BIE
%discretization. Fast direct solvers have also been developed
%recently~\cite{fds1,fds2,fds3,fds4,fds5,fds6,fds7,fds8,ho2016cpam2,ho2016cpam1,minden2016,minden2017siammms}.
%The development of these fast algorithms have removed a huge hurdle for
%the use of boundary integral equations, making the BIE method the
%method of choice for constant-coefficient PDEs with linear boundary
%conditions.  For the exterior Dirichlet problem of the screened Laplace
%equation, the SKIE formulation in our previous work~\cite{Fu2018_SIAM}
%can be readily extened to the 3D case. For the mobility problem of the
%Stokes flow in three dimensions that takes the hydrodynamic effect into
%account, an SKIE formulation can be found in~\cite{manasthesis}.

%% ----------------------------------------------------------------------
%\subsubsection{High-order discretization of surface integrals in three
%dimensions}
%The practical application of integral equation methods requires the
%accurate evaluation of boundary integrals with singular, weakly singular
%or nearly singular kernels. There are many numerical quadrature schemes
%for dealing with line integrals in two
%dimensions~\cite{alpert,kapur,sidi,duffy,bruno1,bruno2,davis_1984,graglia_2008,hackbusch_sauter_1994,
%jarvenpaa_2003,khayat_2005,kress_boundary_1991,schwab_1992,
%ying_2006,beale1,beale2,goodman_1990, haroldson_1998,
%lowengrub_1993,schwab_1992,ggq1,ggq2,ggq3,helsing_2008a,helsing_integral_2009,helsing_tutorial_2012}
%and some of them are extremely efficient and can achieve arbitrary high
%order.
%
%The high-order quadrature rules for the evaluation of surface integrals
%in three dimensions, however, are much less developed than the line
%integrals in two dimensions. For example, there are no Gaussian
%quadratures for integraing polynomials on a flat triangle, even though
%efficient quadratures~\cite{xiao2010cma,vioreanu2014} have been
%developed recently for such purpose. For weakly singular or singular
%integrals,~\cite{bremer2012jcp,bremer2013jcp} constructed high-order
%quadratures for surface integrals on a general triangle,
%while~\cite{gimbutas2013sisc} presented a fast algorithm for integrating
%$1/r$-type singular integrals for surfaces that are homeomorphic to a
%sphere. We plan to study the so-called quadrature by expansion (QBX)
%scheme~\cite{klockner2013jcp,qbx2} for the evaluation of both singular
%and near-singular surface integrals encountered in the discretization of
%BIEs in three dimensions. Conceptually, the idea of the QBX to evaluate
%singular, hypersingular and near singular integrals on smooth surfaces
%is straightforward. That is, the surface is discretized into smooth
%triangles and smooth high-order quadratures are applied to evaluate the
%expansion coefficients on all source triangles with the QBX expansion
%center placed at a point off the surface. One may then form a suitable
%expansion (for example, a Taylor expansion) around that center and
%evaluate this expansion back at the target point on the surface (or
%close to the surface in the near singular case). Compared to the
%competing aforementioned quadrature schemes, the QBX quadrature is
%attractive because it offers a clear path for being extended to:
%\textbf{(1)} handle any singularity, including hypersingular operators,
%\textbf{(2)} be usable with any high-order surface discretization,
%\textbf{(3)} generate well-conditioned discrete operators to which
%iterative methods such as GMRES~\cite{gmres} can be applied in a
%black-box fashion, \textbf{(4)} integrate well with fast algorithms such
%as the FMM. 
%
%In practice, there are still many issues that need to be resolved. For
%example, there are now many variants of QBX including global and local
%QBX~\cite{klockner2013jcp,rachh2017jcp}, the target-specific
%QBX~\cite{siegel2018jcp}, kernel-independent QBX~\cite{abtin2018bit},
%and quadrature by two expansions~\cite{ding2019arxiv}. The coupling of
%the QBX and the FMM may also lead to certain instability issues which
%may require some changes in the fast multipole
%method~\cite{wala2018jcp}. Similar to other quadrature methods, there
%have been extensive study on the QBX methods in two dimensions, while
%its three dimension
%version~\cite{wala2019jcp,af2018sisc,siegel2018jcp,wala2019arxiv} has
%not been fully studied and the implementation is even more scarce. We
%plan to investigate the accuracy and the convergence order of the
%various QBX schemes mentioned above, its coupling with the FMM, parallel
%implementation issues for large-scale problems, and the application to
%our target problems.

% ----------------------------------------------------------------------
\subsubsection{A hybrid method for close-to-touching Janus particles}
\textcolor{red}{
The HAP model for membranes will inevitably lead to the case where some
Janus particles will be very close to each other. Even though QBX can
handle such case accurately, it may lead to excessively large number of
unknowns in order to resolve the unknown densities at those
close-to-touching points. In~\cite{gan2016sisc}, a hybrid scheme is
developed to treat the close-to-touching spheres for the interface
problem of the Laplace equation. The key idea is to combine the analytic
image method and spectrally accurate method of moments, where the
analytic image method will capture the most singular part of the unknown
density at the close-to-touching points. With the aid of the FMM, the
scheme achieves linear complexity with much less number of unknowns on
the material interfaces. We plan to study the hybrid scheme to treat
the close-to-touching case for both the screened Laplace equation and
the mobility problem to further improve the efficiency of the numerical
algorithm for the HAP model.
}

%% ----------------------------------------------------------------------
%\subsubsection{Other numerical issues}
%Another outstanding numerical issue pertaining to simulating the
%self-assembly of amphiphilic particles (such as lipid macromolecles) in
%a viscous solvent is the collision between amphiphilic particles. The
%hydrophobic attraction potential drives the amphiphilic particles to
%move towards each other so to minimize exposure to the solvent. Under
%such attraction force the fluid is being squeezed out as particles move
%toward each other, and the amphiphilic particles can come into physical
%contact in finite time. Such particle collisions in a dense rigid body
%suspension is a great challenge and can be a bottleneck in large-scale
%simulations. In our previous work a Leonard-Jones potential is used to
%keep the particles from overlapping~\cite{Fu2018_SIAM}. Such steep
%steric interaction at short ranges introduces great numerical stiffness
%that limit the time step size. 
%
%Yan {\it et al.} proposed a collision-resolution algorithm within the
%framework of boundary integral methods to resolve the non-smooth
%many-body dynamics due to collisions by formulating the particle
%collision process as a linear complementarity problem with geometric
%`non-overlapping' constraint~\cite{Yan2019}. We propose to treat the
%particle collisions based on Yan {\it et al.}'s work after the first two
%goals (see above) are achieved. A potential complication in combining
%the algorithms for particle collision into our QBX integral formulation
%is the computational cost for the QBX to refine meshes on particles in
%collision.
%
%Once the collision-resolution algorithm is implemented, we will check
%the computing performance first before we embark on incorporating
%fluctuating hydrodynamics~\cite{Bao17,Bao18}, which might be important
%even at the scales of the amphiphilic particle size in some cases. We
%propose to extend the high-order time-integration scheme for a
%stochastic differential equation~\cite{fu2015pre} to this system.

### 2020-11-05 NSF2020/Description/specificaim3_ver2.tex
changes throughout aim 3

@@
-\subsection{Specific Aim 3: Efficient high-order numerical algorithm for
+\newpage
+
+\subsection{Specific Aim 3: Efficient high-order numerical methods for
 large-scale simulations}
@@
 % ----------------------------------------------------------------------
-\subsubsection{Overview of the potential theory and boundary integral
-equation methods} 
 The HAP model requires solving the exterior Dirichlet problem of the
@@
 volume must be discretized, and artificial boundary conditions must be
-imposed. The artificial boundary conditions introduces an additional
-source of error, and discretizing the volume, particularly in three
-dimensions, results in an excessively large linear system. Moreover, it
-is difficult to obtain high-order discretizations when the boundary
-surfaces are irregular. Since we are solving constant-coefficient
-elliptic PDEs, we apply boundary integral equation (BIE) that remove the
-aforementioned obstacles. BIEs represent the solution as a layer
-potential with an unknown density function. Then, the correct density
-function is found that matching the layer potential with the prescribed
-boundary conditions. By construction, layer potentials satisfy the
-underlying PDE and the far-field conditions. For the exterior Dirichlet
-problem of the screened Laplace equation, the BIE formulation in our
-previous work~\cite{Fu2018_SIAM} can be readily extended to three
-dimensions. For the mobility problem of the Stokes flow in three
-dimensions that takes the hydrodynamic effect into account, an
-well-conditioned BIE is found in~\cite{manasthesis}.
+imposed. The artificial boundary conditions introduces additional error,
+and discretizing the volume results in an excessively large linear
+system. Moreover, it is difficult to obtain high-order discretizations
+when the boundary surfaces are irregular. Since we are solving
+constant-coefficient elliptic PDEs, we represent the solution of the
+PDE of interest as a layer potential 
+\begin{align}
+  \label{eq:LP}
+  u(x) = \int_{\partial\Omega} K(x,y) \sigma(y) ds_y,
+\end{align}
+where $\sigma$ is an unknown density function, and $K(x,y)$ is formed
+with derivatives of the fundamental solution of the underlying PDE.  By
+matching the boundary condition at $x_0 \in \partial\Omega$ with the
+limit of equation~\eqref{eq:LP} as $x\rightarrow x_0 \in
+\partial\Omega$, a BIE for the density function is formed.
+Numerical methods to solve BIE has several advantages over their
+PDE-based counterpart: by construction, $u$ satisfies far-field
+conditions; only $\partial\Omega$ needs to be discretized; carefully
+chosen kernels $K(x,y)$ result in a well-conditioned linear system that
+requires a mesh-independent number of GMRES iterations to converge; and
+high-order or spectral accuracy is attainable by using appropriate
+quadrature methods. In our previous work~\cite{Fu2018_SIAM} we
+demonstrate that BIEs are a powerful tool to simulate two-dimensional
+suspensions of amphiphilic particles. In addition to improving
+two-dimensional simulations, we will extend the results to three
+dimensions using a standard three-dimensional BIE of the screened
+Laplace equation~\cite{ying_2006} and a well-conditioned BIE of the
+mobility problem~\cite{manasthesis}.
 
-Discretizations of BIEs have several advantages when compared to
-stencil-based discretizations. First, the dimension of the problem is
-reduced by one since the unknown density function is defined on the
-boundary of the geometry. Second, by carefully selecting each layer
-potential, the resulting linear system is well-conditioned for any
-resolution and iterative methods such as GMRES require a
-mesh-independent number of iterations to converge. Third, by using
-appropriate quadrature methods, the method converges with spectral or
-very high-order accuracy. The most significant challenges include
-solving dense linear systems, developing preconditioning strategies, and
+The most significant challenges of a BIE formulation include solving
+dense linear systems, developing preconditioning strategies, and
 developing quadrature methods for integrands that are nearly singular.
-
-By choosing BIEs that use a mesh-independent number of GMRES iterations,
-the overall cost of a solver is proportional to the complexity of the
-matrix-vector multiplication. The matrix-vector multiplication will be
-accelerated to optimal or near-optimal complexity using the fast
-multipole method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2,
-fmm3, fmm4, fmm6, fmm7, fmm8}. Alternatively, fast direct solvers can be
-used~\cite{fds1, fds2, fds3, fds4, fds5, fds6, fds7, fds8, ho2016cpam2,
-ho2016cpam1, minden2016, minden2017siammms}, but since direct solvers
-often require a large amount of initial overhead, they are less
-applicable to problems with moving geometries such as ours.
-Alternatively, fast direct solvers can be used to precondition the
-linear system as described in Section~\ref{subsec:NumericalIssues}.
+These challenges are described in Sections~\ref{subsec:NumericalIssues}.
 
 % ----------------------------------------------------------------------
-\subsubsection{Nearly touching bodies}
+\subsubsection{Numerical issues}
+\label{subsec:NumericalIssues}
+\todo[inline]{Preconditioning}
+\todo[inline]{Adaptive high-order time stepping}
+
+Discretizations of carefully chosen BIEs can be solved with a
+mesh-independent number of GMRES
+iterations~\cite{cam-ips-kel-mey-xue1996}. Therefore, the required CPU
+time is proportional to the cost of a matrix-vector multiplication that
+can be done in optimal or near-optimal time with the fast multiple
+method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2, fmm3,
+fmm4, fmm6, fmm7, fmm8}. Alternatively, fast direct solvers can be used
+to avoid any iteration~\cite{fds1, fds2, fds3, fds4, fds5, fds6, fds7,
+fds8, ho2016cpam2, ho2016cpam1, minden2016, minden2017siammms}, but
+direct solvers often require a large amount of initial overhead, and
+this makes them less useful for problems with moving geometries. Alternatively, techniques in fast direct solvers can be used to develop
+efficient preconditioning strategies.
+
 Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
@@
 equation. This will be done by recognizing that the fundamental solution
-of the screened Laplace equation can be decomposed as
-$K(\mathbf{x},\mathbf{y}) = K_1(\mathbf{x},\mathbf{y}) +
-K_2(\mathbf{x},\mathbf{y})$, where $K_1(\mathbf{x},\mathbf{y}) =
--\log\|\mathbf{x} - \mathbf{y}\|$ and $K_2(\mathbf{x},\mathbf{y}) =
-K(\mathbf{x},\mathbf{y}) + \log\|\mathbf{x} - \mathbf{y}\|$. Using this
-decomposition, the layer potential involving $K_1(\mathbf{x}\mathbf{y})$
-can be accurately computed with the barycentric quadrature
-rule~\cite{ioa-pap-per1991}, and the layer potential
-$K_2(\mathbf{x},\mathbf{y})$ can be accurately computed with the
-trapezoid rule since the kernel is bounded for all
-$\mathbf{x}$ and $\mathbf{y}$.
+of the screened Laplace equation can be decomposed as $K(x,y) = K_1(x,y)
++ K_2(x,y)$, where $K_1(x,y) = -\log\|x - y\|$ and $K_2(x,y) = K(x,y) +
+\log\|x - y\|$. Using this decomposition, the layer potential involving
+$K_1(x,y)$ can be accurately computed with the barycentric quadrature
+rule~\cite{ioa-pap-per1991}, and the layer potential $K_2(x,y)$ can be
+accurately computed with the trapezoid rule since the kernel is bounded
+for all $x$ and $y$.
+\todo[inline]{Image here}
+
+% ----------------------------------------------------------------------
+\subsubsection{High-order adaptive time stepping}
+\label{subsec:timeStepping}
+\todo[inline]{Put contact in here as well}
 
@@
 second-kind BIE
-
-% ----------------------------------------------------------------------
-\subsubsection{Other numerical issues}
-\label{subsec:NumericalIssues}
-Preconditioning
-Adaptive high-order time stepping
 
@@
 
-% ----------------------------------------------------------------------
-\subsubsection{A hybrid method for close-to-touching Janus particles}
-\textcolor{red}{
-The HAP model for membranes will inevitably lead to the case where some
-Janus particles will be very close to each other. Even though QBX can
-handle such case accurately, it may lead to excessively large number of
-unknowns in order to resolve the unknown densities at those
-close-to-touching points. In~\cite{gan2016sisc}, a hybrid scheme is
-developed to treat the close-to-touching spheres for the interface
-problem of the Laplace equation. The key idea is to combine the analytic
-image method and spectrally accurate method of moments, where the
-analytic image method will capture the most singular part of the unknown
-density at the close-to-touching points. With the aid of the FMM, the
-scheme achieves linear complexity with much less number of unknowns on
-the material interfaces. We plan to study the hybrid scheme to treat
-the close-to-touching case for both the screened Laplace equation and
-the mobility problem to further improve the efficiency of the numerical
-algorithm for the HAP model.
-}
-
+%% ----------------------------------------------------------------------
+%\subsubsection{A hybrid method for close-to-touching Janus particles}
+%\textcolor{red}{
+%The HAP model for membranes will inevitably lead to the case where some
+%Janus particles will be very close to each other. Even though QBX can
+%handle such case accurately, it may lead to excessively large number of
+%unknowns in order to resolve the unknown densities at those
+%close-to-touching points. In~\cite{gan2016sisc}, a hybrid scheme is
+%developed to treat the close-to-touching spheres for the interface
+%problem of the Laplace equation. The key idea is to combine the analytic
+%image method and spectrally accurate method of moments, where the
+%analytic image method will capture the most singular part of the unknown
+%density at the close-to-touching points. With the aid of the FMM, the
+%scheme achieves linear complexity with much less number of unknowns on
+%the material interfaces. We plan to study the hybrid scheme to treat
+%the close-to-touching case for both the screened Laplace equation and
+%the mobility problem to further improve the efficiency of the numerical
+%algorithm for the HAP model.
+%}
+%
+%
 %% ----------------------------------------------------------------------

### 2020-11-05 code/examples/shear_loadTraj.m
adding script for trajectories

@@ -1,0 +1,78 @@
+clear
+clf
+format long e
+format compact
+
+addpath ../src
+addpath ../output/data
+file = 'shear.bin';
+
+[yukawaRHS,posx,posy,xc,tau,time] = loadFile(file);
+
+prams.N = size(posx,1);
+prams.nb = size(posx,2);
+ntime = size(posx,3);
+
+% will include this into loop
+irate = 10; % controls the speed of the visualization
+ax = 15*[-1 1 -1 1];
+
+dt = 0.05;
+prams.m = ntime ; % number of time steps
+prams.T = prams.m*dt; % time horizon
+
+prams.order = 2;
+
+prams.rho = 1.0; % screen length
+prams.gam = 1.0;
+
+prams.RepulLength = 2*0.3; % repulsion length
+prams.RepulStrength = 2*0.5; % repulsion strength
+
+options.farField  = 'shear';
+options.shearRate = 0.005;
+options.saveData  = true;
+options.fileBase  = 'shear';
+options.append    = false;
+options.inear     = true;
+options.usePreco  = false;
+options.verbose   = true;
+options.timeOrder = 1;
+options.gmresTol  = 1e-5;
+options.usePlot   = false; %true;
+options.plotAxis  = 15*[-1 1 -1 1];
+
+ratio = 1;
+radii = 1/ratio*ones(1,prams.nb);
+ar = ratio*ones(1,prams.nb);
+
+prams.tau   = tau;
+prams.radii = radii;
+prams.ar    = ar;
+
+om = monitor(options,prams);
+tt = tstep(options,prams);
+geom = capsules(prams,xc(:,:,1),tau(1,:,1));
+
+% write current time to console
+message = ['Completed time ', num2str(time(1),'%4.2e'), ...
+      ' of time horizon ' , num2str(prams.T,'%4.2e')];
+om.writeMessage(message);
+
+om.writeVelData(time,0*geom.center,0*geom.tau); 
+
+for k = 2:11 % ntime+1
+% main script
+tt = tstep(options,prams);
+geom = capsules(prams,xc(:,:,k),tau(1,:,k));
+
+[Up, wp,~,~,etaY,etaS] = tt.timeStep(geom,geom.X,geom.X);
+
+% write current time to console
+message = ['Completed time ', num2str(time(k),'%4.2e'), ...
+      ' of time horizon ' , num2str(prams.T,'%4.2e')];
+om.writeMessage(message);
+
+% write the velocity to a file
+om.writeVelData(time,Up,wp); 
+end

### 2020-11-05 code/examples/shear_loadTraj.m
adding script for trajectories

@@ -61,7 +61,7 @@ om.writeMessage(message);
 
 om.writeVelData(time,0*geom.center,0*geom.tau); 
 
-for k = 2:11 % ntime+1
+for k = 2:ntime+1
 % main script
 tt = tstep(options,prams);
 geom = capsules(prams,xc(:,:,k),tau(1,:,k));

### 2020-11-05 code/examples/shear_loadTraj.m
revising shear_loadTraj.m

@@ -5,7 +5,10 @@ format compact
 
 addpath ../src
 addpath ../output/data
+addpath ../output/velocity
+
 file = 'shear.bin';
+velfile = 'shear_vel.bin';
 
 [yukawaRHS,posx,posy,xc,tau,time] = loadFile(file);
 
@@ -13,11 +16,7 @@ prams.N = size(posx,1);
 prams.nb = size(posx,2);
 ntime = size(posx,3);
 
-% will include this into loop
-irate = 10; % controls the speed of the visualization
-ax = 15*[-1 1 -1 1];
-
-dt = 0.05;
+dt = 1;
 prams.m = ntime ; % number of time steps
 prams.T = prams.m*dt; % time horizon
 
@@ -61,7 +60,11 @@ om.writeMessage(message);
 
 om.writeVelData(time,0*geom.center,0*geom.tau); 
 
-for k = 2:ntime+1
+
+% kstart = 0;
+irate = 10;
+
+for k = 1:irate:ntime
 % main script
 tt = tstep(options,prams);
 geom = capsules(prams,xc(:,:,k),tau(1,:,k));
@@ -75,4 +78,18 @@ om.writeMessage(message);
 
 % write the velocity to a file
 om.writeVelData(time,Up,wp); 
+
 end
+
+
+[velx,vely,torq] = loadVelFile(velfile);
+
+for k = 1 : floor(ntime/irate)+1
+ind = (k-1)*irate+1;
+data = [xc(1,:,ind);xc(2,:,ind);tau(1,:,ind);velx(1,:,ind);vely(1,:,ind);torq(1,:,ind)];
+filename = ['../output/velocity/', 'N' num2str(prams.nb) '_' num2str((k-1)*irate),'_vel.dat'];
+fid = fopen(filename,'w');
+fprintf(fid,'%12.4f %12.4f %12.4f %12.4f %12.4f %12.4f\n',data);
+fclose(fid); 
+end
+

### 2020-11-05 NSF2020/Description/specificaim1_ver2.tex
mod SA1v2

@@
 
-\subsection{Specific Aim 1: Collective elastic and hydrodynamic properties of amphiphilic particles}
+\subsection{Specific Aim 1: Collective elastic properties of amphiphilic particles}
 \label{subsec:specific_aim_1}
@@
 %\end{figure}
+The goal of Specific Aim 1 is characterize the material properties of many-body, self-assembled amphiphiles.
+For amphiphiles assembled into bilayers, these properties are described by membrane continuum mechanics.
+The end-goal is to be able to map the parameters of the particle-based model onto the elastic moduli from continuum theory.
+If we achieve this goal, then simulators can use the hydrophobic attraction force calculations
+to model bilayers with specific composition. These calculations have provably less computational complexity than
+those of molecular dynamics simulations and possess the molecular granularity lacking from continuum models.
 
@@
 %lipid composition and
+
+Recently, there has been a revival in interest in the HK theory. The quadratic assumption
+for the elasticity energy density has caused researchers to question the validity of \eqref{ansatz}
+for situations involving large curavtures \cite{PRL, https://doi.org/10.1016/j.bbamem.2016.02.003}. Zimmerberg and Akimov \cite{https://doi.org/10.1039/C9SM02079A}
+showed that energies derived from molecular dynamics and elasticity agree even in the case of large deformations.
+Part of this proposal will contribute to clarifying some of the mathematical
+assumptions that went into the HK theory.
 
@@
 respectively (Figure \ref{fig:distortions}A--C).
-The deformations come with elastic coefficients: the \emph{bending modulus} $\KB$, \emph{twist modulus} $\KT$ 
-and \emph{saddle-splay modulus} $\KG$ and \emph{tilt modulus} $\KTH$
+The deformations come with elastic coefficients: the bending modulus $\KB$, twist modulus $\KT$ 
+and saddle-splay modulus $\KG$ and tilt modulus $\KTH$
 HK define the tilt vector $T = n/(N\cdot n) - N$ where $N$ is the unit surface normal.
@@
 splay $\Div n$ equal to twice the mean curvature, saddle splay $\det \nabla n$ equal to the Gauss curvature,
-and both twist and tilt equaling zero.
-
-The form of the elastic energy density \eqref{ansatz3} is the same as
-the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106}.  In fact,  
-a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
-The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
-liquid crystal theory. However, the ``bend'' distortion from nematics  
-is not present in monolayers since the directors have no dependence in the normal direction.
-There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection.
-
-Recently, there has been a revival in interest in the HK theory. The quadratic assumption
-for the elasticity energy density has caused researchers to question the validity of \eqref{ansatz}
-for situations involving large curavtures \cite{PRL}. Zimmerberg and Akimov \cite{https://doi.org/10.1039/C9SM02079A}
-showed that energies derived from molecular dynamics and elasticity agree even in the case of large deformations.
-Part of this proposal will contribute to clarifying some of the mathematical
-assumptions that went into the HK theory.
+and both twist and tilt are equal to zero.
 
@@
 
-\subsubsection{Evidence for elastic properties}
-\label{sssec:evidence}
-We tested for elastic properties by subjecting two-dimensional bilayer morphologies
-to external loads \cite{Fu19}, using realistic
-values for phospholipid length \cite{Boal},
-the screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
-and  interfacial tension $\gamma=4.1$ pN nm$^{-1}$  \cite{GarciaSaez, KUZMIN2005, Petelska2012}.
-Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.
-We first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
-The bilayer is clamped and horizontal at one end and the restoring force in the free part 
-of the bilayer opposes the load. Twist and saddle splay are both zero, singling out splay
-as the only distortion.
-% In this situation, the directors are also parallel to the unit surface
-%normal. As such $\Div \mathbf{d} = -2H$ where $H$ is the mean curvature of the surface. 
-Since deformations are small \eqref{ansatz3}, it is possible to solve the bilayer loading in closed form. 
-This analytical solution (red curve) basically overlaps the midplane of the particle based solution (Figure \ref{fig:bend}A).
+% Proposers should address what they want to do,
+% why they want to do it,
+% how they plan to do it,
+% how they will know if they succeed,
+% and what benefits could accrue if the project is successful.
+\begin{center}
+Preliminary results
+\end{center}
+Our preliminary tested for elastic properties by subjecting bilayers to external loads \cite{Fu19}.
+We used realistic values for the phospholipid length $a$ \cite{Boal},
+screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
+and  interfacial tension $\gamma=4.1$ pN nm$^{-1}$  \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
+model parameters.
+The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), particle diameter and the hydrophobic boundary condition \eqref{}
+are additional parameters defining the coarse-grained representation.
+
+To derive a bending modulus, we first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
+Using a clamped condition at one end, the restoring force in the free part of the bilayer opposes the load.
+For small deformations, it is possible to solve the bilayer loading in closed form, and 
+this analytical solution (red curve) basically overlaps the midplane of the particle based solution (Figure \ref{fig:bend}A).
+We thereby derived a bending modulus $\KB$ in the range 8.51 -- 13.54 \kBT. Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.
+Experimental measurements have accurately determined the bending modulus for several lipid types, with 
+typical values lying around 10 \kBT\; \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}.
+
+We also considered the stretching and tilt deformations \cite{Fu19}. 
+Stretching occurs whenever there is an excess monolayer area,
+and it is energetically costly since it exposes hydrocarbon tails to water.
+To measure an area modulus, we stretched a circular vesicle, modeling the cross-section 
+of a bilayer tube (Figure \ref{fig:bend}B \& C).
+This procedure gave a monolayer area modulus 
+34 $\pm$ 2 \kBT \;nm$^{-2}$. Manipulation experiments give a monolayer area modulus in the range 
+30 -- 40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}.
+
+Finally, we considered the tilt deformation by applying a fixed tilt angle boundary condition. 
+This boundary condition produces a tilt field that decays with the length scale $l = \sqrt{\KB/\KTH}$ 
+Fitting to this field, our particle based simulation gave $\lambda = 1.2$ nm, which matches
+the value $\KTH \approx 10$ \kBT \; nm$^{-2}$ reported in the literature \cite{https://doi.org/10.1063/1.4932971}.
+
+Our preliminary work is encouraging because in all cases, the bending, stretch, and tilt elastic moduli for the collection of amphiphiles
+were in excellent agreement with the experimental values. This fact is especially remarkable 
+since we assigned the main model parameters $\rho$ and $\gamma$ reasonable physical values, rather than using them as tuning parameter. 
+Nevertheless, the characterization of material properties is incomplete. For one, the preliminary work involved relatively few particles, and we need to
+perform convergence studies with large particle-number systems to arrive at conclusive results. Secondly, we have yet to establish a functional
+relationship between the model parameters and elastic moduli. Finally, to have relevence in physics and biology
+we must incorporate the remaining twist and saddle splay deformations.
+The following outlines the simulations we will use to characterize material properties.
 
@@
 
-Experimental measurements have accurately determined 
-the bending modulus for several lipid types, with 
-typical values lying around 10 \kBT\; \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}.
-By comparing with the exact solution, we derived a bending modulus
-in the range 8.51 -- 13.54 \kBT, which is in 
-excellent agreement with the experimentally derived value, especially considering how few parameters the HAP 
-formalism involves.
+\begin{center}
+Anticipated model simulations
+\end{center}
+To characterize material properties, we compare the energies and forces generated by
+a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
+The comparison enables us to understand how the model parameters map onto elastic parameters.
 
-\newpage
+In the preliminary work, bilayer shapes minimized energy with respect to an external force. Energy minimality is somewhat unrealistic because
+biological membranes are constantly in motion. Tracking the evolution of a bilayer is a more robust procedure that does not require minimality.
+Here we start with a particle bilayer in a non-equilibrium shape, and then evolve the particle bilayer according to steepest gradient descent with respect to the
+HARP functional. Gradient descent stabilizes the evolving bilayer shape and gives a monotonically decreasing energy. This gives a relatively large
+data set of energy $E$ versus particle configuration. At the same time, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field $n$ by
+interpolating the particle centers and orientations. Using \eqref{ansatz}, we calculate a continuum energy $H$ from the interpolated
+bilayer shape. Setting $\Delta E = E - E_0$ and $\Delta H = H - H_0$ normalizes the energies to their respective equilibrium values $E_0$ and $H_0$.
+In certain instances, the bilayer evolution involves only one of the four fundamental deformations.
+When this occurs, the elastic moduli appear as the slope of the linear regression between $\Delta H$ and $\Delta E$.
 
-\subsubsection{What work will actually be done?}
-% Proposers should address what they want to do,
-% why they want to do it,
-% how they plan to do it,
-% how they will know if they succeed,
-% and what benefits could accrue if the project is successful.
+Bending is the energetically most consequential deformations,
+and so we revisit estimating the bending modulus parameter. 
+In the case of the bending deformation, we deform the midplane of a planar bilayer into the shape of a circular arc.
+This arc stores bending energy in the form of splay $\Div{n}$, while twist, saddle-splay and tilt deformations are zero.
+The splay in the two leaflets approximately cancel when added, making the contribution of spontaneous curvature negligible.
+Since $\Div{n} = -\kappa$ in this setup, we can compute the curvature squared curvature energy 
+$H = \int_C \kappa^2$ of the cross-section $C$, a simple closed curve. Figure \ref{} shows the appoximately linear
+relationship between $\Delta E$ and $\Delta H$ with $\KB$ as the slope.
 
-We will study the elastic properties of particle-based bilayers using static and hydrodynamic, large particle-number simulation. 
-The goal is to connect the deformations of particle bilayers to the deformations of HK theory, and in particular map the parameters of the
-particle-based system onto known, and experimentally measured elastic moduli.
+The twist deformation is a fully three-dimensional deformation. 
+(Specific Aim 3 address outstanding implementation issues like three-dimensional boundary integral solvers.) 
+The twist deformation is closely related to the assumption of lateral fluidity in membranes and so researchers 
+have sometimes assumed $\KT = 0$ \cite{HaKo2000, 10.1063/1.4990404, https://doi.org/10.1039/C9SM02079A, 10.1103/PhysRevE.102.042406}, 
+while molecular dynamics investigations find a twist modulus in the range of 1 to 2 \kBT \cite{LeVeWa14}.
+To measure the elastic response,  we initially twist the bilayer along an $x_1$-coordinate axis.
+In this configuration, the directors behave at leading order as $n = (0, mx_1, \sqrt{1 - m^2x_1^2})$,
+yielding a surface gradient $\nabla n = \begin{pmatrix}0 & 0\\ m & 0\end{pmatrix}$. 
+Here $\Div n = \mathrm{tr}(\nabla n) = 0$, $\det(\nabla n) = 0$ and $\Curl d = (\nabla u)_{12} - (\nabla u)_{21} = m$,
+so that the continuum elastic energy equals $\tfrac{1}{2}\KT m^2 A + O(1)$ for a membrane area $A \gg 1$. (Our particle collections
+conserve membrane area, unless they lie in a strong background flow.) 
+This enables us to plot the HARP energy values derived from steepest gradient descent as a function of $m$, and finally
+yields a value for $\KA$.
 
-The successful outcomes of our preliminary tests suggest that the HAP particle configurations 
-do behave like an elastic material. To validate our conjecture, we must consider 
-ways to isolate or partially isolate the remaining distortions.
+We will also determine the effective saddle splay modulus $\KG$. 
+Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
+\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
+barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}. 
+The field requires further theoretical work like the what we are proposing to more precisely account for saddle splay.
 
-\subsubsection{Hydrodynamic simulations}
+The gradient descent technique is ineffective for measuring $\KG$ because
+the saddle splay energy is largely invariant under shape changes.
+In the simplified Canham-Helfrich formulation, saddle splay energy is an indicator of topological transitions, thanks to the  Gauss-Bonnet theorem
+\cite{TerziDeserno17}.
+PI-Ryham showed that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}.
 
-\subsubsection{Static simulations}
-Particle-based bilayers form because of the balance between hydrophobic attraction and excluded volume repulsion.
-As a result, a precise way to measure a certain elastic properties is to set up an externally loaded system,
-and then isolate the desired deformation by solving for the energy minimizer. The following give technical details on how we
-draw these connections in practice.
-In summary, the elastic moduli determine how lipid monolayers and bilayers mechanically behave.
+To evaluate $\KG$, we will combine the string method from PI-Ryham's work on fusion \cite{RyKlYaCo16} with
+the present particle simulations. The string method is a numerical scheme that finds
+least energy pathways separating energy basins \cite{simple_string}.
+Using the string method, we will evaluate the transition energies between the intact pancake shape,
+and one with a pore. Pore formation in a single bilayer decreases the integral of saddle splay from $4\pi$
+to $0$. We can, in principle, detect this drop in energy becuase we have already accounted for the other deformations.
 
-\begin{description}
-\item[Bending modulus] A planar bilayer that is deformed into the shape of a circular arc stores bending energy in the form of splay.
-  Bending isolates the splay deformation $\Div{n}$ because the twist and saddle-splay deformations are zero in two-dimensional bilayers,
-  and both MD and continuum mechanical simulations show that tilt is more or less zero due to lack of inclusions.
-  Moreover, the splay in the two leaflets of an arc approximately cancel when added, due to the smaller head to tail ratio in the inner leaflet and
-  larger head to tail ratio in the outer lealet, and so we can neglect the spontaneous curvature.
+We will also analyze $\KG$ using a helical geometry. In a helicoid with inclination $m$, the director
+gradient is $\nabla n = \begin{pmatrix} 0 & m(m^2+x_1^2)^{-1} \\ m(m^2+x_1^2)^{-1} & 0\end{pmatrix}$ where $x_1$ is the distance to the central
+axis. We observe that saddle splay, twist and tilt are zeros, and $\det \nabla n = m^2(m^2+x_1^2)^{-2}$.
+In the simulations, the particles forming the helicoid will be confined to two, concentric cylinders. The
+continuum energy $\tfrac{1}{2}\KG h(m x_1(m^2+x_1^2)^{-1} + \tan^{-1}(x_1/m)) |_{r_1}^{r_2}$ where $h$, $r_1$ and $r_2$
+are the cylinder heights, inner cylinder radius, and outer cylinder radius, respectively.
 
-  Using steepest gradient descent, the simulation tracks the relaxation of the energies $E$ of a sequence of arc-shaped bilayers tending toward and the equilibrium, planar bilayer.
-  We reconstruct the monolayer dividing surface (a curve $C$) and directors by interpolating the particle centers and orientations. Using spectral differentiation,
-  we can compute the curvature $\kappa$ of $C$ and the squared curvature energy $H = \int_C \kappa^2$. Since $\Div{n} = -\kappa$ in this setup, we can plot
-  the particle based values $\Delta E = E - E_0$ as a function of $\Delta H = H - H_0$ where $E_0$ and $H_0$ are the respective equilibrium values.
+The form of the elastic energy density \eqref{ansatz3} is the same as
+the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106}.  In fact,  
+a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
+The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
+liquid crystal theory. However, the ``bend'' distortion from nematics  
+is not present in monolayers since the directors have no dependence in the normal direction.
+There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection.
 
-  Figure \ref{} shows the appoximately linear relationship between $\Delta E$ and $\Delta H$.
-  The slope of the dashed line gives the bending modulus $\KB = 10$ kT. 
-  The simulation is for a realistic phospholipid length \cite{Boal},
-  the screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
-  and  interfacial tension $\gamma=4.1$ pN nm$^{-1}$  \cite{GarciaSaez, KUZMIN2005, Petelska2012}.
+ Perhaps surprisingly, the field of membrane continuum mechanics still lacks consensus as to
+  whether \eqref{ansatz3} contains a complete list of consistent deformations.
+  The PI Ryham showed, for example, that the tilt vector $T = n/n\cdot N - N$ leads to unphysical cusps when constraining membrane thickness
+ \cite{RyKlYaCo16}.
+  Recently, \cite{10.1063/1.4990404} derived a tilt curvature term that was neglected from the HK analysis \cite{HaKo2000}.
+  Later, \cite{https://doi.org/10.1039/C9SM02079A} 
+  and \cite{10.1103/PhysRevE.102.042406} independently identified an inconsistency \cite{10.1063/1.4990404} arising
+  from a transversal tilt invariance assumption.
 
-  The parameters of our hydrophobic attraction formalism map accurately onto the experimentally determined moduli.  
-  The value $\KB = 10$ kT is a reasonable bending modulus for many lipid species \cite{}, and it depends linearly on
-  the interfacial tension parameter $\gamma$ of our model. The $\gamma = 4.1$ pN nm$^{-1}$ is
-  about a third of the surface tension of a typical hydrocarbon-water interface. M. Jackson points out, however, that the smaller interfacial tension parameter is actually the correct value 
-  to describe the free energy for placing molecular lipid into contact with water \cite{}.
-  So not only is the HARP model tunable to experimental parameters, but the results coincide with other properties from physical chemistry.
+  We suspect the reason why, after twenty years, the field has yet to reach a consensus 
+  lies in the Taylor expansions used to derive the elastic energy density. 
+  Past researchers expressed the strain tensor in
+  terms of the coordinate frame $\{e_1, e_2, N\}$ with surface tangent vectors $e_i$ and surface normal $N$.  
+  In this frame, there is a coupling between the gradients of all three terms $x_0,$ $\zeta$ and $n$ of the deformation \eqref{LMdeformation}.
+  The recent paper \cite{10.1103/PhysRevE.102.042406} contains an energy density with more than ten elastic parameters, for example.
+  Subtle differential geometric arguments are needed to evaluate the terms in the Taylor expansion.
 
-\item[Tilt]
-\item[Spontaneous curvature]
-\item[Twist and saddle-splay]
-  We measure the elastic response to twist by following the relaxation
-  dynamics of an initially twisted membrane. Tilt is a fully three-dimensional deformation
-  and so the reference membrane is a pancake-shaped, planar bilayer with diamater
-  much larger than bilayer thickness.  In the initial configuration, the 
-  the directors behave to leading order as $n = (0, mx_1, \sqrt{1 - m^2x_1^2})$
-  where $x_1$ is the twisting axis. At the continuum level, 
-  the surface gradient $\nabla n = \begin{pmatrix}0 & 0\\ m & 0\end{pmatrix}$ that $\Div n = \mathrm{tr}(\nabla n) = 0$,
-  $\det(\nabla n) = 0$ and $\Curl d = (\nabla u)_{12} - (\nabla u)_{21} = m$,
-  so that twist is isolated and the continuum elastic energy equals $\KA m^2 A + O(1)$ where
-  $A \gg 1$ is the membrane area.
-
-  The initial bilayer consi
-The twist deformation, for example, has a modulus in the range of 1 to 2 \kBT\; 
-as evaluated by molecular dynamics \cite{LeVeWa14}. 
-But twist is mathematically zero in our two-dimensional monolayers,
-and so we require a computationally efficient means for evaluating the 
-boundary integral equations in a collection of three-dimensional particles. 
-Specific Aim 2 discusses some of the outstanding implementation issues.
-
-Our eventual three-dimensional calculations must also consider the saddle-splay distortion,
-and the calculations may help resolve some well-known issues in the theory \cite{TerziDeserno17}. 
-Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
-\cite{SIEGEL2004366,SIEGEL20085200}.
-This value, however, 
-predicts an energy barrier for monolayer fusion on the order of 200  \kBT, which runs counter to 
-the value 30 \kBT\; estimated in experiments \cite{RyKlYaCo16,FrRoPi17,Tran7106}.  
-We expect the particle-based approach can shed light on this inconsistency.   
-\item[Stretching]
-We also considered the stretching deformation \cite{Fu19}. 
-Stretching occurs whenever there is an excess monolayer area,
-and it is energetically costly since it exposes hydrocarbon tails to water. 
-%Monolayers are not, strictly speaking, area incompressible,
-%and 
-Manipulation experiments give a monolayer area modulus in the range 
-30 -- 40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}. 
-To measure an area modulus, we stretched a circular vesicle, modeling the cross-section 
-of a bilayer tube (Figure \ref{fig:bend}B \& C).
-%We then stretched the vesicle beyond and beneath equilibrium radius and recorded the change in energy. 
-This procedure gave a monolayer area modulus 
-34 $\pm$ 2 \kBT \;nm$^{-2}$, independently of the vesicle size, which
-is also remarkably close to the experimental value.
-
-\item[Fluctuation spectrum]
-\item[Revision of HK Theory]
-  It may come as a surprise that the field of membrane continuum mechanics still lacks concensus as to
-  whether \eqref{ansatz3} contains a complete list of consistent deformations.
-  The PI Ryham showed, for example, that the tilt energy density is interchangagle, up to second order, with
-  the simplified term $|n \times N|^2$ \cite{RyKlYaCo16}.
-  Recently, \cite{10.1063/1.4990404} derived a tilt curvature term that Hamm and Kozlov had neglected from their analysis \cite{HaKo2000}.
-  Later, \cite{https://doi.org/10.1039/C9SM02079A} 
-  and \cite{10.1103/PhysRevE.102.042406} independently identified an inconsitency in the transversal tilt invariance
-  assumption of Desrno's earlier work \cite{10.1063/1.4990404}.
-
-  We suspect the reason why, after twenty years, the field has yet to reach a concensus 
-  lies in the asymptotic expansions used to derive the elastic energy density. 
-  Past researchers expressed the strain tensor in
-  terms of the coordinate frame $\{\tau_1, \tau_2, N\}$ with surface tangent vectors $\tau_i$ and surface normal $N$.  
-  In this frame, there is a coupling between the gradients of all three terms $x_0,$ $\zeta$ and $n$ of the deformation \eqref{LMdeformation}.
-  The differential geometric arguments needed to determine which terms of the expansion to retain in the expansion are subtle,
-  and have caused \cite{10.1103/PhysRevE.102.042406} to derive an energy density with more than ten elastic parameters, for example.
-
-  However, expanding the strain tensor in terms of the coordinate frame $\{e_1, e_2, n\}$ with $e_i$ perpendicular to $n$
-  decouples a good portion of the gradient terms, leading to simplified expressions. For example,
-  in this coordinate frame, the incompressility condition leads to an exact relationship 
-  \begin{equation}
-    \label{elongation}
-    (1 + \Div n \zeta + \det \nabla n \zeta^2) \zeta' = 1
-  \end{equation}
-  for lipid elongation. \cite{HaKo2000} seem to have been aware of \eqref{elongation} for the special case of zero tilt,
-  but the works \cite{HaKo2000, https://doi.org/10.1039/C9SM02079A, 10.1063/1.4990404} use an approximate form of \eqref{elongation}
-  and \cite{10.1103/PhysRevE.102.042406} reports a form containing an erroneous $|T|^2$ in the $\zeta^0$ coefficient.
+  We will revisit the HK analysis to see if any inconsitencies can be resolved.
+  As a main analytical innovation, we have found that expanding the strain tensor in
+  terms of the coordinate frame $\{e'_1, e'_2, n\}$ with $e'_i$ perpendicular to $n$
+  greatly simplifies the expansion because it decouples the gradient terms. As an illustration, the prominent works
+  \cite{10.1063/1.4990404, 10.1103/PhysRevE.102.042406, HaKo2000, https://doi.org/10.1039/C9SM02079A} utilize an
+  incompressility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
+  However, when expressed in the $\{e'_1, e'_2, n\}$ coordinate frame, the incompressility condition is exact
+  and is given by a Steiner-type polynomial in terms of $\Div n$ and $\det \nabla n$ \cite{http://www.jstor.org/stable/1993504}.
+  Aside from the special case of zero tilt, \cite{HaKo2000} an coworkers seem to have been unaware of this result.
 
@@
 particles is dependent on the position a third or more particles. Conceptually, this would arise in continuum theory if two monolayer surfaces
-had different elastic energy density at that point despite having locally identical curvatures and directors.
-
-\end{description}
+had a different elastic energy density despite having locally identical curvatures and directors.
+The boundary integral formulation described in Specific Aim 3 easily accomodates additional linear PDE and
+we will extend our study to include charge lipids and weak electrolytes \cite{DIMOVA}.
 
 \newpage
+
+Specific Aim 1 dealt with the collective material property of amphiphiles which does not involve the movement  of the solvent.
+In Specific Aim 2, we include hydrodynamics effects. The reason for including hydrodynamic effects is that 
+biologically relevant functions like fusion, fission, pore dynamics involve viscous dissipation of the aqueous environment. 
+Moreover, including hydrodynamics adds relevance to our theory since most coarse-grained and molecular dynamics theories
+include water either explicitly or implicitly in their models.

### 2020-11-05 NSF2020/Description/specificaim1_ver2.tex
...

@@
-\newpage
-
 \section{Proposed Research}
@@
   \tfrac{1}{2}\KB\left[ \left( \Div n + k_0\right)^2 - k_0^2\right] 
-+ \tfrac{1}{2}\KT (\Curl n)^2 + \KG  \det \nabla n + \KTH |T|^2 \,dA.
++ \tfrac{1}{2}\KT (\Curl n)^2 + \KG  \det \nabla n + \tfrac{1}{2}\KTH |T|^2 \,dA.
 \end{aligned}
@@
 we will extend our study to include charge lipids and weak electrolytes \cite{DIMOVA}.
-
-\newpage
-
-Specific Aim 1 dealt with the collective material property of amphiphiles which does not involve the movement  of the solvent.
-In Specific Aim 2, we include hydrodynamics effects. The reason for including hydrodynamic effects is that 
-biologically relevant functions like fusion, fission, pore dynamics involve viscous dissipation of the aqueous environment. 
-Moreover, including hydrodynamics adds relevance to our theory since most coarse-grained and molecular dynamics theories
-include water either explicitly or implicitly in their models.

### 2020-11-05 NSF2020/Description/specificaim2_ver2.tex
...

@@
 \label{subsec:specific_aim_2}
+Specific Aim 1 dealt with the collective material property of amphiphiles which does not involve the movement  of the solvent.
+In Specific Aim 2, we include hydrodynamics effects. The reason for including hydrodynamic effects is that 
+biologically relevant functions like fusion, fission, pore dynamics involve viscous dissipation of the aqueous environment. 
+Moreover, including hydrodynamics adds relevance to our theory since most coarse-grained and molecular dynamics theories
+include water either explicitly or implicitly in their models.
+
 %The mathematics of this proposal investigates how three-dimensional solids deform under long-range surface tension interaction.

### 2020-11-05 NSF2020/Description/specificaim1_ver2.tex
added bibs

@@
 The modern theory of membrane continuum mechanics
-was pioneered by Hamm and Kozlov (HK) \cite{HaKo2000}.
+was pioneered by Hamm and Kozlov (HK) \cite{Hamm2000}.
 The theory is widely used to describe biological phenomona 
-fission \cite{10.1016/j.chemphyslip.2014.07.006, 10.1038/nature14509, 10.1103/PhysRevE.79.031926},
-fusion \cite{10.1016/S0006-3495(02)75450-7,10.1073/pnas.121191898,10.1073/pnas.1119442109} ,
+fission \cite{FrEsAkSh15, Maetal15, PhysRevE.79.031926},
+fusion \cite{KoKo2002,10.1073/pnas.121191898,10.1073/pnas.1119442109} ,
 poration \cite{10.1016/j.bpj.2019.11.2221}, phase boundaries and interaction with inclusions
@@
 The twist deformation is closely related to the assumption of lateral fluidity in membranes and so researchers 
-have sometimes assumed $\KT = 0$ \cite{HaKo2000, 10.1063/1.4990404, https://doi.org/10.1039/C9SM02079A, 10.1103/PhysRevE.102.042406}, 
+have sometimes assumed $\KT = 0$ \cite{Hamm2000, 10.1063/1.4990404, https://doi.org/10.1039/C9SM02079A, 10.1103/PhysRevE.102.042406}, 
 while molecular dynamics investigations find a twist modulus in the range of 1 to 2 \kBT \cite{LeVeWa14}.
@@
  \cite{RyKlYaCo16}.
-  Recently, \cite{10.1063/1.4990404} derived a tilt curvature term that was neglected from the HK analysis \cite{HaKo2000}.
+  Recently, \cite{10.1063/1.4990404} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
   Later, \cite{https://doi.org/10.1039/C9SM02079A} 
@@
   greatly simplifies the expansion because it decouples the gradient terms. As an illustration, the prominent works
-  \cite{10.1063/1.4990404, 10.1103/PhysRevE.102.042406, HaKo2000, https://doi.org/10.1039/C9SM02079A} utilize an
+  \cite{10.1063/1.4990404, 10.1103/PhysRevE.102.042406, Hamm2000, https://doi.org/10.1039/C9SM02079A} utilize an
   incompressility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
@@
   and is given by a Steiner-type polynomial in terms of $\Div n$ and $\det \nabla n$ \cite{http://www.jstor.org/stable/1993504}.
-  Aside from the special case of zero tilt, \cite{HaKo2000} an coworkers seem to have been unaware of this result.
+  Aside from the special case of zero tilt, \cite{Hamm2000} an coworkers seem to have been unaware of this result.
 

### 2020-11-05 NSF2020/Description/specificaim3_ver2.tex
working on aim 3

@@
 screened Laplace equation and the mobility problem of the Stokes flow at
-each time step. If discretizing these equations with stencil-based
-numerical methods, the computational domain must be truncated, the
-volume must be discretized, and artificial boundary conditions must be
-imposed. The artificial boundary conditions introduces additional error,
-and discretizing the volume results in an excessively large linear
-system. Moreover, it is difficult to obtain high-order discretizations
-when the boundary surfaces are irregular. Since we are solving
-constant-coefficient elliptic PDEs, we represent the solution of the
-PDE of interest as a layer potential 
+each time step in the complex domains such as Figure~\ref{fig:domain}.
+If discretizing these equations with stencil-based numerical methods,
+the computational domain must be truncated, the volume must be
+discretized, and artificial boundary conditions must be imposed. The
+artificial boundary conditions introduces additional error, and
+discretizing the volume results in an excessively large linear system.
+Moreover, it is difficult to obtain high-order discretizations when the
+boundary surfaces are irregular. Since we are solving
+constant-coefficient elliptic PDEs, we represent the solution of the PDE
+of interest as a layer potential 
 \begin{align}
@@
 Numerical methods to solve BIE has several advantages over their
-PDE-based counterpart: by construction, $u$ satisfies far-field
-conditions; only $\partial\Omega$ needs to be discretized; carefully
-chosen kernels $K(x,y)$ result in a well-conditioned linear system that
-requires a mesh-independent number of GMRES iterations to converge; and
-high-order or spectral accuracy is attainable by using appropriate
-quadrature methods. In our previous work~\cite{Fu2018_SIAM} we
-demonstrate that BIEs are a powerful tool to simulate two-dimensional
-suspensions of amphiphilic particles. In addition to improving
-two-dimensional simulations, we will extend the results to three
-dimensions using a standard three-dimensional BIE of the screened
-Laplace equation~\cite{ying_2006} and a well-conditioned BIE of the
-mobility problem~\cite{manasthesis}.
+PDE-based counterpart: by construction, the layer
+potential~\eqref{eq:LP} satisfies far-field conditions; only
+$\partial\Omega$ needs to be discretized; carefully chosen kernels
+$K(x,y)$ result in a well-conditioned linear system that requires a
+mesh-independent number of GMRES iterations to solve; and high-order or
+spectral accuracy is attainable by using appropriate quadrature methods.
+In our previous work~\cite{Fu2018_SIAM} we demonstrate that BIEs are a
+powerful tool to simulate two-dimensional suspensions of amphiphilic
+particles. In addition to improving two-dimensional simulations, we will
+extend the results to three dimensions using a standard
+three-dimensional BIE of the screened Laplace equation~\cite{ying_2006}
+and a well-conditioned BIE of the mobility problem~\cite{manasthesis}.
 
@@
 developing quadrature methods for integrands that are nearly singular.
-These challenges are described in Sections~\ref{subsec:NumericalIssues}.
+These challenges are described in section~\ref{subsec:NumericalIssues}.
+Then, in section~\ref{subsec:timeStepping}, time stepping strategies are
+described, and stable BIE formulations for fluctuating hydrodynamics are
+in section~\label{subsec:fluctuating}.
 
@@
 \label{subsec:NumericalIssues}
-\todo[inline]{Preconditioning}
-\todo[inline]{Adaptive high-order time stepping}
 
@@
 method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2, fmm3,
-fmm4, fmm6, fmm7, fmm8}. Alternatively, fast direct solvers can be used
-to avoid any iteration~\cite{fds1, fds2, fds3, fds4, fds5, fds6, fds7,
-fds8, ho2016cpam2, ho2016cpam1, minden2016, minden2017siammms}, but
-direct solvers often require a large amount of initial overhead, and
-this makes them less useful for problems with moving geometries. Alternatively, techniques in fast direct solvers can be used to develop
-efficient preconditioning strategies.
+fmm4, fmm6, fmm7, fmm8}. PI Quaife is experienced with applying FMMs for
+both the Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the
+screened Laplace equation~\cite{kro-qua2011, qua2011}. Alternatively,
+fast direct solvers can be used to avoid any iteration~\cite{fds1, fds2,
+fds3, fds4, fds5, fds6, fds7, fds8, ho2016cpam2, ho2016cpam1,
+minden2016, minden2017siammms}, but direct solvers often require a large
+amount of initial overhead, and this makes them less useful for problems
+with moving geometries.  Alternatively, techniques in fast direct
+solvers can be used to develop efficient preconditioning strategies. PI
+Quaife used the inverse Fast Multipole Method
+(IFMM)~\cite{cou-pou-dar2017, qua-cou-dar2018} to precondition Stokes
+equations in a porous media, and a suite of preconditioners ranging from
+block-diagonal to the IFMM will be considered.
 
@@
 % ----------------------------------------------------------------------
-\subsubsection{High-order adaptive time stepping}
+\subsubsection{Avoiding contact with adaptive time stepping and
+repulsion}
 \label{subsec:timeStepping}
 \todo[inline]{Put contact in here as well}
+\todo[inline]{Adaptive high-order time stepping}
 
-Even with accurate quadrature and time stepping methods (see
-Section~\ref{subsec:NumericalIssues}) methods, rigid body simulations
-can still result in unphysical contact. In our previous work a
+Even with accurate quadrature and time stepping methods, rigid body
+simulations can still result in unphysical contact. We proposed to use
+two techniques to avoid unphysical contact: high-order adaptive time
+stepping and a repulsion force. PI Quaife developed a high-order
+adaptive time stepping method for hydrodynamic
+suspensions~\cite{qua-bir2016} and he has used it with colleagues to
+investigate mixing and adhesion in suspensions~\cite{qua-vee-you2019,
+kab-qua-bir2017}.
+
+In our previous work a
 Leonard-Jones potential is used to keep the particles from
@@
 size. 
+\cite{bys-sha-qua2020}
 
@@
 \subsubsection{Fluctuating hydrodynamics}
+\label{subsec:fluctuating}
 Using DLP formulation for fluctuating hydrodynamics so that we have a

### 2020-11-05 NSF2020/Description/specificaim1_ver2.tex
Add files via upload
Specific aim 1, version 2, ready for review

@@
 We have demonstrated that our hydrophobic attraction with repulsion potential (HARP) approach efficiently simulates
-self-assembly of amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu19}, and
-recreates the tank-treading phenomenon in external shear flows \cite{Fu20}.
+self-assembly of amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu2018_SIAM}, and
+recreates the tank-treading phenomenon in external shear flows \cite{Fu20} \textbf{!!let's put a proceedings here so we have something to cite!!}.
 %
@@
 efficiently simulating three-dimensional collective hydrodynamics of amphiphilic particles.
-Finally, we must mathematically characterize the variational behavior of HAP under appropriate homogenized limits.
+Finally, we must mathematically characterize the variational behavior of HARP under appropriate homogenized limits.
 
@@
 fission \cite{FrEsAkSh15, Maetal15, PhysRevE.79.031926},
-fusion \cite{KoKo2002,10.1073/pnas.121191898,10.1073/pnas.1119442109} ,
-poration \cite{10.1016/j.bpj.2019.11.2221}, phase boundaries and interaction with inclusions
-\cite{https://doi.org/10.1038/nrm.2017.16,10.1016/j.bpj.2019.11.2209, https://doi.org/10.1038/s41598-020-61110-2}, which require resolution of the internal structure of the membrane.  
-%The Helfrich hamiltonian is widely used to determine energy barriers of fusion between lipid bilayer membranes \cite{ChKo08}. 
-%Some of these barrier heights were never before obtained through the use of continuum membrane mechanics.
+fusion \cite{ChKo08, KoKo2002,Kuzmin7235,Aeffner2012},
+poration \cite{Gaetal20}, phase boundaries and interaction with inclusions
+\cite{SeLeMaEg17,Saetal20, Pietal20}, which require resolution of the internal structure of the membrane.  
 Using the HK  model as a base,
 PI Ryham and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
-hemifusion diaphragm and the fusion pore \cite{RyWaCo13, RyKlYaCo16},
-%The calculation of hydrophobic 
-%fissures in \cite{RyKlYaCo16} motivated the HAP theory.
+hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
 and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
 are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.
-%analyzed the dependence of energy barriers on
-%lipid composition and
 
 Recently, there has been a revival in interest in the HK theory. The quadratic assumption
-for the elasticity energy density has caused researchers to question the validity of \eqref{ansatz}
-for situations involving large curavtures \cite{PRL, https://doi.org/10.1016/j.bbamem.2016.02.003}. Zimmerberg and Akimov \cite{https://doi.org/10.1039/C9SM02079A}
-showed that energies derived from molecular dynamics and elasticity agree even in the case of large deformations.
-Part of this proposal will contribute to clarifying some of the mathematical
-assumptions that went into the HK theory.
+for the elasticity energy density has caused researchers to question the applicability of \eqref{ansatz3} for large curvatures \cite{PhysRevLett.117.188102, ARGUDO20161619}. 
+The article \cite{C9SM02079A} counters that energies derived from molecular dynamics and elasticity agree, even when curvatures are large.
+This proposal will bring mathematical analysis to some of the assumptions 
+that went into the HK theory.
 
@@
 The parameter $X_3$ and the function $\zeta$ parametrizes the distance along the hydrocarbon chain in the reference state
-and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta \approx $ 2 nm is monolayer thickness.
+and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta = $ 2.5 nm is a realistic monolayer thickness.
 
@@
 
-The parameter $k_0$ is the \emph{spontaneous curvature} and it determines the preferred lipid splay \cite{RoLi15,Kozlov2007}. 
+The parameter $k_0$ is the  spontaneous curvature and it determines the preferred lipid splay \cite{RoLi15,Kozlov2007}. 
 As an illustration, the lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
@@
 the elastic energy couples director gradients to surface geometry through the tilt vector field.
-In biological contexts, tilt appears at lipid domain boundaries, the edge of nanopores, and at the boundary of membrane inclusions \cite{https://doi.org/10.1103/PhysRevE.102.042406}, and the bilayer energy is the sum monolayer energies.
+In biological contexts, bilayer energy is the sum monolayer energies, and tilt appears at lipid domain boundaries, the edge of nanopores and at the boundary of membrane inclusions \cite{PhysRevE.102.042406}.
 Under spatial scales much larger than the membrane thickness, membrane energy is well-characterized by
-the Canham-Helfrich energy used throughout the fluid-structure literature \cite{}.
+the Canham-Helfrich energy used throughout the fluid-structure literature 
+\cite{QiangDu09, Lowengrub07,KimLai2010_JCP,Hu,HuLaiSeolEtAl2016_JCP} \textbf{!! YNY and BQ, place your recent works here!!}.
 The Canham-Helfrich energy is actually a special case of \eqref{ansatz3} obtained by setting $n =  \pm N$ (the $\pm$ depending
@@
 \end{center}
-Our preliminary tested for elastic properties by subjecting bilayers to external loads \cite{Fu19}.
+Our preliminary tested for elastic properties by subjecting bilayers to external loads \cite{Fu2018_SIAM}.
 We used realistic values for the phospholipid length $a$ \cite{Boal},
@@
 model parameters.
-The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), particle diameter and the hydrophobic boundary condition \eqref{}
+The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
+particle diameter and the hydrophobic boundary condition \eqref{SL}
 are additional parameters defining the coarse-grained representation.
@@
 
-We also considered the stretching and tilt deformations \cite{Fu19}. 
+We also considered the stretching and tilt deformations \cite{Fu2018_SIAM}. 
 Stretching occurs whenever there is an excess monolayer area,
@@
 Fitting to this field, our particle based simulation gave $\lambda = 1.2$ nm, which matches
-the value $\KTH \approx 10$ \kBT \; nm$^{-2}$ reported in the literature \cite{https://doi.org/10.1063/1.4932971}.
+the value $\KTH \approx 10$ \kBT \; nm$^{-2}$ reported in the literature \cite{KUZMIN2005, KoNa15}.
 
@@
 since we assigned the main model parameters $\rho$ and $\gamma$ reasonable physical values, rather than using them as tuning parameter. 
-Nevertheless, the characterization of material properties is incomplete. For one, the preliminary work involved relatively few particles, and we need to
+Nevertheless, the characterization of material properties is incomplete. For one, the preliminary simulations involved relatively low particle numbers (20 to 30), and so we still need to
 perform convergence studies with large particle-number systems to arrive at conclusive results. Secondly, we have yet to establish a functional
-relationship between the model parameters and elastic moduli. Finally, to have relevence in physics and biology
+relationship between the model parameters and elastic moduli. Finally, to have relevance in physics and biology
 we must incorporate the remaining twist and saddle splay deformations.
-The following outlines the simulations we will use to characterize material properties.
+The following simulation outline shows how will achieve aims.
 
@@
 data set of energy $E$ versus particle configuration. At the same time, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field $n$ by
-interpolating the particle centers and orientations. Using \eqref{ansatz}, we calculate a continuum energy $H$ from the interpolated
+interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $H$ from the interpolated
 bilayer shape. Setting $\Delta E = E - E_0$ and $\Delta H = H - H_0$ normalizes the energies to their respective equilibrium values $E_0$ and $H_0$.
@@
 Since $\Div{n} = -\kappa$ in this setup, we can compute the curvature squared curvature energy 
-$H = \int_C \kappa^2$ of the cross-section $C$, a simple closed curve. Figure \ref{} shows the appoximately linear
+$H = \int_C \kappa^2$ of the cross-section $C$, a simple closed curve. Figure \ref{} shows the approximately linear
 relationship between $\Delta E$ and $\Delta H$ with $\KB$ as the slope.
@@
 The twist deformation is closely related to the assumption of lateral fluidity in membranes and so researchers 
-have sometimes assumed $\KT = 0$ \cite{Hamm2000, 10.1063/1.4990404, https://doi.org/10.1039/C9SM02079A, 10.1103/PhysRevE.102.042406}, 
-while molecular dynamics investigations find a twist modulus in the range of 1 to 2 \kBT \cite{LeVeWa14}.
+have sometimes assumed $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}, 
+while molecular dynamics investigations find a twist modulus in the range of 1 to 2 
+\kBT \cite{LeVeWa14}.
 To measure the elastic response,  we initially twist the bilayer along an $x_1$-coordinate axis.
@@
 the present particle simulations. The string method is a numerical scheme that finds
-least energy pathways separating energy basins \cite{simple_string}.
+least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}.
 Using the string method, we will evaluate the transition energies between the intact pancake shape,
 and one with a pore. Pore formation in a single bilayer decreases the integral of saddle splay from $4\pi$
-to $0$. We can, in principle, detect this drop in energy becuase we have already accounted for the other deformations.
+to $0$. We can, in principle, detect this drop in energy because we have already accounted for the other deformations.
 
@@
 The form of the elastic energy density \eqref{ansatz3} is the same as
-the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106}.  In fact,  
+the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
 a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
@@
 
- Perhaps surprisingly, the field of membrane continuum mechanics still lacks consensus as to
+ It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
   whether \eqref{ansatz3} contains a complete list of consistent deformations.
@@
  \cite{RyKlYaCo16}.
-  Recently, \cite{10.1063/1.4990404} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
-  Later, \cite{https://doi.org/10.1039/C9SM02079A} 
-  and \cite{10.1103/PhysRevE.102.042406} independently identified an inconsistency \cite{10.1063/1.4990404} arising
+  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
+  Later, \cite{C9SM02079A} 
+  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
   from a transversal tilt invariance assumption.
@@
   We suspect the reason why, after twenty years, the field has yet to reach a consensus 
-  lies in the Taylor expansions used to derive the elastic energy density. 
+  has to do with the Taylor expansions used to derive the elastic energy density. 
   Past researchers expressed the strain tensor in
@@
   In this frame, there is a coupling between the gradients of all three terms $x_0,$ $\zeta$ and $n$ of the deformation \eqref{LMdeformation}.
-  The recent paper \cite{10.1103/PhysRevE.102.042406} contains an energy density with more than ten elastic parameters, for example.
+  The recent paper \cite{PhysRevE.102.042406} contains an energy density with more than ten elastic parameters, for example.
   Subtle differential geometric arguments are needed to evaluate the terms in the Taylor expansion.
@@
   greatly simplifies the expansion because it decouples the gradient terms. As an illustration, the prominent works
-  \cite{10.1063/1.4990404, 10.1103/PhysRevE.102.042406, Hamm2000, https://doi.org/10.1039/C9SM02079A} utilize an
+  \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
   incompressility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
   However, when expressed in the $\{e'_1, e'_2, n\}$ coordinate frame, the incompressility condition is exact
-  and is given by a Steiner-type polynomial in terms of $\Div n$ and $\det \nabla n$ \cite{http://www.jstor.org/stable/1993504}.
-  Aside from the special case of zero tilt, \cite{Hamm2000} an coworkers seem to have been unaware of this result.
+  and is given by a Steiner-type polynomial in terms of $\Div n$ and $\det \nabla n$ \cite{Fe59}.
+  Aside from the special case of zero tilt, \cite{Hamm2000} and coworkers seem to have been unaware of this result.
 
@@
 The boundary integral formulation described in Specific Aim 3 easily accomodates additional linear PDE and
-we will extend our study to include charge lipids and weak electrolytes \cite{DIMOVA}.
+we will extend our study to include charge lipids and weak electrolytes \cite{C9SM00772E}.

### 2020-11-05 code/examples/shear_loadTraj.m
fixed some bugs in shear_loadTraj.m

@@ -8,7 +8,6 @@ addpath ../output/data
 addpath ../output/velocity
 
 file = 'shear.bin';
-velfile = 'shear_vel.bin';
 
 [yukawaRHS,posx,posy,xc,tau,time] = loadFile(file);
 
@@ -16,7 +15,7 @@ prams.N = size(posx,1);
 prams.nb = size(posx,2);
 ntime = size(posx,3);
 
-dt = 1;
+dt = 0.05;
 prams.m = ntime ; % number of time steps
 prams.T = prams.m*dt; % time horizon
 
@@ -51,45 +50,37 @@ prams.ar    = ar;
 
 om = monitor(options,prams);
 tt = tstep(options,prams);
-geom = capsules(prams,xc(:,:,1),tau(1,:,1));
 
-% write current time to console
-message = ['Completed time ', num2str(time(1),'%4.2e'), ...
-      ' of time horizon ' , num2str(prams.T,'%4.2e')];
-om.writeMessage(message);
-
-om.writeVelData(time,0*geom.center,0*geom.tau); 
-
-
-% kstart = 0;
+kstart = 0;
+tstart = kstart*dt;
 irate = 10;
+
+if (irate ~= 1)
+    kend = floor(ntime/irate)+1;
+else
+    kend = ntime;
+end
+
+Up = 0*xc;
+wp = 0*tau;
 
 for k = 1:irate:ntime
 % main script
-tt = tstep(options,prams);
 geom = capsules(prams,xc(:,:,k),tau(1,:,k));
-
-[Up, wp,~,~,etaY,etaS] = tt.timeStep(geom,geom.X,geom.X);
+[Up(:,:,k), wp(1,:,k),~,~,etaY,etaS] = tt.timeStep(geom,geom.X,geom.X);
 
 % write current time to console
-message = ['Completed time ', num2str(time(k),'%4.2e'), ...
+message = ['Completed time ', num2str(tstart+time(k),'%4.2e'), ...
       ' of time horizon ' , num2str(prams.T,'%4.2e')];
 om.writeMessage(message);
 
-% write the velocity to a file
-om.writeVelData(time,Up,wp); 
-
 end
 
-
-[velx,vely,torq] = loadVelFile(velfile);
-
-for k = 1 : floor(ntime/irate)+1
+for k = 1 : kend
 ind = (k-1)*irate+1;
[…]

### 2020-11-05 code/src/rigid2D.m
fixed some bugs.m

@@ -19,9 +19,6 @@ step = 0;
 xc0  = xc;
 tau0 = tau;
 om.writeData(time,geom.center,geom.tau,geom.X);
-% write the velocity to a file,initial velocities are 0
-om.writeVelData(time,0*geom.center,0*geom.tau);  
-
 
 trajectory = [xc(1,:) xc(2,:) tau];
 
@@ -53,6 +50,9 @@ while step < prams.m
       % update geometry
       geom0 = capsules(prams,xc0,tau0);
       [Up0, wp0,~,~,etaY0,etaS0] = tt.timeStep(geom0,geom0.X,geom0.X);
+
+      % write the velocity to the file
+      om.writeVelData(time,Up0,wp0);        
       
       % causes xc2, tau2 to be forward Euler, at step 0
       xc1  = xc0;

### 2020-11-05 code/src/rigid2D.m
fixed some bugs

@@ -52,7 +52,7 @@ while step < prams.m
       [Up0, wp0,~,~,etaY0,etaS0] = tt.timeStep(geom0,geom0.X,geom0.X);
 
       % write the velocity to the file
-      om.writeVelData(time,Up0,wp0);        
+      om.writeVelData(time,Up0,wp0);
       
       % causes xc2, tau2 to be forward Euler, at step 0
       xc1  = xc0;

### 2020-11-05 code/src/rigid2D.m
fixed some bugs

@@ -51,7 +51,7 @@ while step < prams.m
       geom0 = capsules(prams,xc0,tau0);
       [Up0, wp0,~,~,etaY0,etaS0] = tt.timeStep(geom0,geom0.X,geom0.X);
 
-      % write the velocity to the file
+      % write the velocity to a file
       om.writeVelData(time,Up0,wp0);
       
       % causes xc2, tau2 to be forward Euler, at step 0

### 2020-11-05 NSF2020/Description/specificaim3_ver2.tex
fixed bib file

@@
 described, and stable BIE formulations for fluctuating hydrodynamics are
-in section~\label{subsec:fluctuating}.
+in section~\ref{subsec:fluctuating}.
 

### 2020-11-05 NSF2020/Description/specificaim3_ver2.tex
working on numerics

@@
 These challenges are described in section~\ref{subsec:NumericalIssues}.
-Then, in section~\ref{subsec:timeStepping}, time stepping strategies are
-described, and stable BIE formulations for fluctuating hydrodynamics are
-in section~\ref{subsec:fluctuating}.
+Even with accurate quadrature and time stepping methods, rigid body
+simulations can easily result in unphysical contact. We propose two
+techniques to avoid unphysical contact in
+Section~\ref{subsec:timeStepping}. Then, proposed work for well-conditioned BIE
+formulations of fluctuating hydrodynamics are in
+section~\ref{subsec:fluctuating}.
 
@@
 amount of initial overhead, and this makes them less useful for problems
-with moving geometries.  Alternatively, techniques in fast direct
-solvers can be used to develop efficient preconditioning strategies. PI
-Quaife used the inverse Fast Multipole Method
-(IFMM)~\cite{cou-pou-dar2017, qua-cou-dar2018} to precondition Stokes
-equations in a porous media, and a suite of preconditioners ranging from
-block-diagonal to the IFMM will be considered.
+with moving geometries. Alternatively, techniques in fast direct solvers
+can be used to develop efficient preconditioning strategies such as the
+inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017}. PI Quaife
+used the IFMM to precondition Stokes equations in a porous
+media~\cite{qua-cou-dar2018}, and a suite of other preconditioners
+including sparse approximate inverses~\cite{che2000} and
+multigrid~\cite{hem-sch1981, sch1982} will be investigated.
 
@@
 for all $x$ and $y$.
-\todo[inline]{Image here}
+
+\includegraphics[scale=1]{figures/integrands.pdf}
 
@@
 \label{subsec:timeStepping}
-\todo[inline]{Put contact in here as well}
-\todo[inline]{Adaptive high-order time stepping}
 
-Even with accurate quadrature and time stepping methods, rigid body
-simulations can still result in unphysical contact. We proposed to use
-two techniques to avoid unphysical contact: high-order adaptive time
-stepping and a repulsion force. PI Quaife developed a high-order
-adaptive time stepping method for hydrodynamic
-suspensions~\cite{qua-bir2016} and he has used it with colleagues to
-investigate mixing and adhesion in suspensions~\cite{qua-vee-you2019,
-kab-qua-bir2017}.
+An outstanding numerical issue when simulating the
+self-assembly of amphiphilic particles in a viscous solvent is the
+collision between amphiphilic particles. The hydrophobic attraction
+potential drives the amphiphilic particles towards one another so to
+minimize exposure to the solvent, and this leads to physical contact in
+finite time. Such particle collisions in a dense rigid body suspension
+is a great challenge and can be a bottleneck in large-scale simulations.
+We propose two algorithms to remedy this computational
+challenge---high-order adaptive time stepping and repulsion forces.
 
-In our previous work a
-Leonard-Jones potential is used to keep the particles from
-overlapping~\cite{Fu2018_SIAM}. Such steep steric interaction at short
-ranges introduces great numerical stiffness that limit the time step
-size. 
-\cite{bys-sha-qua2020}
+PI Quaife developed a high-order adaptive time stepping method for
+hydrodynamic suspensions~\cite{qua-bir2016} and he has used it with
+colleagues to investigate mixing and adhesion in
+suspensions~\cite{qua-vee-you2019, kab-qua-bir2017}. The method requires
+both a single-step high-order time stepping method and a computationally
+cheap estimate of the error. We plan to use a spectral deferred
+correction method~\cite{dut-gre-rok2000} since it can be used
+iteratively to increase the order of accuracy. To estimate the error,
+instead of using an embedded Runge-Kutta method or step-doubling, we
+will compute the total force and torque of the system which is
+computationally cheap and should be zero. The PIs experience is that
+error estimates based on physical constraints such as force- and
+torque-free conditions appropriately adjusts the time step size so that
+the dynamics are adequately resolved.
 
-\textcolor{red}{
-Another outstanding numerical issue pertaining to simulating the
-self-assembly of amphiphilic particles (such as lipid macromolecles) in
-a viscous solvent is the collision between amphiphilic particles. The
-hydrophobic attraction potential drives the amphiphilic particles to
-move towards each other so to minimize exposure to the solvent. Under
-such attraction force the fluid is being squeezed out as particles move
-toward each other, and the amphiphilic particles can come into physical
-contact in finite time. Such particle collisions in a dense rigid body
-suspension is a great challenge and can be a bottleneck in large-scale
-simulations. In our previous work a Leonard-Jones potential is used to
-keep the particles from overlapping~\cite{Fu2018_SIAM}. Such steep
-steric interaction at short ranges introduces great numerical stiffness
-that limit the time step size. 
-}
+Our previous work avoids contact by including a Leonard-Jones potential
+in the body forces~\cite{Fu2018_SIAM}. Such steep steric interaction at
+short ranges introduces great numerical stiffness that limit the time
+step size. To remove this stiffness, we will use a geometry-based
+contact method~\cite{har-pon-sor-zor2011}, and this method has been
+applied to vesicle suspensions~\cite{lu-rah-zor2017} and rigid body
+suspensions in two dimensions~\cite{bys-sha-qua2020} and
+three dimensions~\cite{Yan2019}. These methods determine repulsion
+force by solving a non-linear complementarity problem with a geometric
+constraint that the configuration is non-overlapping.
 
-\textcolor{red}{
-Yan {\it et al.} proposed a collision-resolution algorithm within the
-framework of boundary integral methods to resolve the non-smooth
-many-body dynamics due to collisions by formulating the particle
-collision process as a linear complementarity problem with geometric
-`non-overlapping' constraint~\cite{Yan2019}. We propose to treat the
-particle collisions based on Yan {\it et al.}'s work after the first two
-goals (see above) are achieved. A potential complication in combining
-the algorithms for particle collision into our QBX integral formulation
-is the computational cost for the QBX to refine meshes on particles in
-collision.
-}
-
+% ----------------------------------------------------------------------
+\subsubsection{Fluctuating hydrodynamics}
+\label{subsec:fluctuating}
+Using DLP formulation for fluctuating hydrodynamics so that we have a
+second-kind BIE
 \textcolor{red}{
@@
 }
-
-% ----------------------------------------------------------------------
-\subsubsection{Fluctuating hydrodynamics}
-\label{subsec:fluctuating}
-Using DLP formulation for fluctuating hydrodynamics so that we have a
-second-kind BIE
-
-%The HAP model requires solving the exterior Dirichlet problem of the
-%screened Laplace equation and the mobility problem of the Stokes flow
-%at each time step. Standard numerical methods such as finite difference
-%and finite element methods have to truncate the infinite domain to a
-%finite computational domain by imposing certain artificial boundary
-%conditions on the truncated domain and need the discretization of the
-%whole volume of the truncated domain. The artificial boundary
-%conditions are very often inexact, introducing another layer of
-%approximation that lowers the accuracy of the solution. The
-%discretization of the whole volume is very expensive for three
-%dimensional problems, leading to excessively large number of unknowns
-%in the linear system. Furthermore, it is rather difficult to obtain
-%high-order discretization when the boundary surfaces are irregular.
-
-%Potential theory and boundary integral equation (BIE) methods remove the
-%aforementioned obstacles in a very elegant way. The starting point is
-%that for constant-coefficient PDEs the fundamental solutions, i.e., the
-%Green's functions, are readily available. This allows us to represent
-%the solution via the so-called layer potentials that are the convolution
-%integrals of a kernel and an unknown density only on the boundary. The
-%kernel is a linear combination of the Green's function and its
-%derivatives, which ensures that the representation satifies the
-%underlying PDE and the condition at infinity automatically. And the
-%boundary condition at the material interfaces together with the jump
-%relation of the layer potential leads to a boundary integral equation
-%for the unknown density.
-
-%The BIE method removes the need of imposing artificial boundary
-%conditions for exterior problems and reduces the dimension of the
-%problem by one, leading to optimal number of unknowns in the solve
-%phase. Very often, one is able to construct the so-called {\it second
-%kind integral equation} (SKIE) formulation for these problems, where
-%the operator is a sum of the identity operator and a compact operator.
-%It is well-known that the condition number of the resulting linear
-%system for SKIEs is {\it independent} of the mesh size $h$ or
-%equivalently, the number of discretization points. This leads to a
-%constant number of iterations when iterative solvers are applied to
-%solve the resulting linear system. It further improves the accuracy of
-%the solution as the relative error of solution will never increase as
-%the number of total discretization points increases. On the other hand,
-%the condition number of the linear system from finite difference and
-%finite element methods generally increases as a power function of the
-%total number of dicretization points, with the exact power depending on
-%the underlying spatial dimension and the highest order of the
-%differential operator in the PDE. This leads to an increase in the
-%number of iterations (and hence the total computational cost) and an
-%increase in the relative error of the solution as the number of
-%dicretization points increases.
-
-%The discretization of the integral operator often leads to a dense
-%matrix, while finite difference/finite element methods result in sparse
-%matrices, making matrix-vector product much cheaper to compute.
-%However,since the invention of the original fast multipole method
-%(FMM)\cite{fmm5}, there have been many fast
-%algorithms~\cite{fmm1,fmm2,fmm3,fmm4,fmm6,fmm7,fmm8} that reduce the
-%cost of matrix-vector product to linear ($O(N)$) or quasilinear
-%complexity ($O(N \log^kN)$) for dense matrices resulting from the BIE
-%discretization. Fast direct solvers have also been developed
-%recently~\cite{fds1,fds2,fds3,fds4,fds5,fds6,fds7,fds8,ho2016cpam2,ho2016cpam1,minden2016,minden2017siammms}.
-%The development of these fast algorithms have removed a huge hurdle for
-%the use of boundary integral equations, making the BIE method the
-%method of choice for constant-coefficient PDEs with linear boundary
-%conditions.  For the exterior Dirichlet problem of the screened Laplace
-%equation, the SKIE formulation in our previous work~\cite{Fu2018_SIAM}
-%can be readily extened to the 3D case. For the mobility problem of the
-%Stokes flow in three dimensions that takes the hydrodynamic effect into
-%account, an SKIE formulation can be found in~\cite{manasthesis}.
-
-%% ----------------------------------------------------------------------
-%\subsubsection{High-order discretization of surface integrals in three
-%dimensions}
-%The practical application of integral equation methods requires the
-%accurate evaluation of boundary integrals with singular, weakly singular
-%or nearly singular kernels. There are many numerical quadrature schemes
-%for dealing with line integrals in two
-%dimensions~\cite{alpert,kapur,sidi,duffy,bruno1,bruno2,davis_1984,graglia_2008,hackbusch_sauter_1994,
-%jarvenpaa_2003,khayat_2005,kress_boundary_1991,schwab_1992,
-%ying_2006,beale1,beale2,goodman_1990, haroldson_1998,
-%lowengrub_1993,schwab_1992,ggq1,ggq2,ggq3,helsing_2008a,helsing_integral_2009,helsing_tutorial_2012}
-%and some of them are extremely efficient and can achieve arbitrary high
-%order.
-%
-%The high-order quadrature rules for the evaluation of surface integrals
-%in three dimensions, however, are much less developed than the line
-%integrals in two dimensions. For example, there are no Gaussian
-%quadratures for integraing polynomials on a flat triangle, even though
-%efficient quadratures~\cite{xiao2010cma,vioreanu2014} have been
-%developed recently for such purpose. For weakly singular or singular
-%integrals,~\cite{bremer2012jcp,bremer2013jcp} constructed high-order
-%quadratures for surface integrals on a general triangle,
-%while~\cite{gimbutas2013sisc} presented a fast algorithm for integrating
-%$1/r$-type singular integrals for surfaces that are homeomorphic to a
-%sphere. We plan to study the so-called quadrature by expansion (QBX)
-%scheme~\cite{klockner2013jcp,qbx2} for the evaluation of both singular
-%and near-singular surface integrals encountered in the discretization of
-%BIEs in three dimensions. Conceptually, the idea of the QBX to evaluate
-%singular, hypersingular and near singular integrals on smooth surfaces
-%is straightforward. That is, the surface is discretized into smooth
-%triangles and smooth high-order quadratures are applied to evaluate the
-%expansion coefficients on all source triangles with the QBX expansion
-%center placed at a point off the surface. One may then form a suitable
-%expansion (for example, a Taylor expansion) around that center and
-%evaluate this expansion back at the target point on the surface (or
-%close to the surface in the near singular case). Compared to the
-%competing aforementioned quadrature schemes, the QBX quadrature is
-%attractive because it offers a clear path for being extended to:
-%\textbf{(1)} handle any singularity, including hypersingular operators,
-%\textbf{(2)} be usable with any high-order surface discretization,
-%\textbf{(3)} generate well-conditioned discrete operators to which
-%iterative methods such as GMRES~\cite{gmres} can be applied in a
-%black-box fashion, \textbf{(4)} integrate well with fast algorithms such
-%as the FMM. 
-%
-%In practice, there are still many issues that need to be resolved. For
-%example, there are now many variants of QBX including global and local
-%QBX~\cite{klockner2013jcp,rachh2017jcp}, the target-specific
-%QBX~\cite{siegel2018jcp}, kernel-independent QBX~\cite{abtin2018bit},
-%and quadrature by two expansions~\cite{ding2019arxiv}. The coupling of
-%the QBX and the FMM may also lead to certain instability issues which
-%may require some changes in the fast multipole
-%method~\cite{wala2018jcp}. Similar to other quadrature methods, there
-%have been extensive study on the QBX methods in two dimensions, while
-%its three dimension
-%version~\cite{wala2019jcp,af2018sisc,siegel2018jcp,wala2019arxiv} has
-%not been fully studied and the implementation is even more scarce. We
-%plan to investigate the accuracy and the convergence order of the
-%various QBX schemes mentioned above, its coupling with the FMM, parallel
-%implementation issues for large-scale problems, and the application to
-%our target problems.
-
-%% ----------------------------------------------------------------------
-%\subsubsection{A hybrid method for close-to-touching Janus particles}
-%\textcolor{red}{
-%The HAP model for membranes will inevitably lead to the case where some
-%Janus particles will be very close to each other. Even though QBX can
-%handle such case accurately, it may lead to excessively large number of
-%unknowns in order to resolve the unknown densities at those
-%close-to-touching points. In~\cite{gan2016sisc}, a hybrid scheme is
-%developed to treat the close-to-touching spheres for the interface
-%problem of the Laplace equation. The key idea is to combine the analytic
-%image method and spectrally accurate method of moments, where the
-%analytic image method will capture the most singular part of the unknown
-%density at the close-to-touching points. With the aid of the FMM, the
-%scheme achieves linear complexity with much less number of unknowns on
-%the material interfaces. We plan to study the hybrid scheme to treat
-%the close-to-touching case for both the screened Laplace equation and
-%the mobility problem to further improve the efficiency of the numerical
-%algorithm for the HAP model.
-%}
-%
-%
-%% ----------------------------------------------------------------------
-%\subsubsection{Other numerical issues}
-%Another outstanding numerical issue pertaining to simulating the
-%self-assembly of amphiphilic particles (such as lipid macromolecles) in
-%a viscous solvent is the collision between amphiphilic particles. The
-%hydrophobic attraction potential drives the amphiphilic particles to
-%move towards each other so to minimize exposure to the solvent. Under
-%such attraction force the fluid is being squeezed out as particles move
-%toward each other, and the amphiphilic particles can come into physical
-%contact in finite time. Such particle collisions in a dense rigid body
-%suspension is a great challenge and can be a bottleneck in large-scale
-%simulations. In our previous work a Leonard-Jones potential is used to
-%keep the particles from overlapping~\cite{Fu2018_SIAM}. Such steep
-%steric interaction at short ranges introduces great numerical stiffness
-%that limit the time step size. 
-%
-%Yan {\it et al.} proposed a collision-resolution algorithm within the
-%framework of boundary integral methods to resolve the non-smooth
-%many-body dynamics due to collisions by formulating the particle
-%collision process as a linear complementarity problem with geometric
-%`non-overlapping' constraint~\cite{Yan2019}. We propose to treat the
-%particle collisions based on Yan {\it et al.}'s work after the first two
-%goals (see above) are achieved. A potential complication in combining
-%the algorithms for particle collision into our QBX integral formulation
-%is the computational cost for the QBX to refine meshes on particles in
-%collision.
-%
-%Once the collision-resolution algorithm is implemented, we will check
-%the computing performance first before we embark on incorporating
-%fluctuating hydrodynamics~\cite{Bao17,Bao18}, which might be important
-%even at the scales of the amphiphilic particle size in some cases. We
-%propose to extend the high-order time-integration scheme for a
-%stochastic differential equation~\cite{fu2015pre} to this system.

### 2020-11-05 code/tests/fitellipse/fft1.m
adding tests for vesicles

@@ -1,0 +1,164 @@
+classdef fft1 < handle
+% class implements fft transformations.  This includes computing
+% the fourier differentiation matrix, doing interplation required
+% by Alpert's quadrature rules, and defining the Fourier frequencies
+
+properties
+N; % Number of points in the incoming periodic functions
+end
+
+
+methods
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function fo = arbInterp(o,f,y)
+% fo = arbInterp(f)  interpolates the function f given at 
+% regular points, at arbitrary points y.  The points y are assumed 
+% to be the in the 0-2*pi range.  Matrix is built.  This routine is
+% only for testing and is never called in the vesicle code
+
+N = size(f,1);
+
+% build interpolation matrix
+A = zeros(length(y), N);
+for j = 1:N
+  g = zeros(N,1); g(j) =1;
+  fhat = fftshift(fft(g)/N);    
+  for k=1:N
+    A(:, j) = A(:, j) + fhat(k)*exp(1i*(-N/2+k-1)*y);
+  end
+end
+A = real(A);
+
+% interpolate
+fo = A*f;
+
+end % arbInterp
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function A = sinterpS(o,N,y)
+% A = sinterpS(N,y) constructs the interpolation matrix A that maps
+% a function defined periodically at N equispaced points to the
+% function value at the points y
+% The points y are assumed to be the in the 0-2*pi range. 
+
+A = zeros(numel(y),N);
+modes = [(0:N/2-1) 0 (-N/2+1:-1)];
+f = zeros(1,N);
+
+for j=1:N
+  f(j) = 1;
+  fhat = fft(f)/N;
+  fhat = fhat(ones(numel(y),1),:);
+  A(:,j) = A(:,j) + sum(fhat.*exp(1i*y*modes),2);
+  f(j) = 0;
+end
+A = real(A);
+% Input is real, so interpolant should be real
+
+
+end % sinterpS
+
[…]

### 2020-11-05 code/tests/fitellipse/getDXY.m

@@ -1,0 +1,13 @@
+function [Dx,Dy]=getDXY(X)
+% [Dx,Dy]=getDXY(X), compute the derivatives of each component of X 
+% these are the derivatives with respect the parameterization 
+% not arclength
+x = X(1:end/2,:);
+y = X(end/2+1:end,:);
+N = size(x,1);
+nv = size(x,2);
+IK = fft1.modes(N,nv);
+Dx = fft1.diffFT(x,IK);
+Dy = fft1.diffFT(y,IK);
+
+end % getDXY

### 2020-11-05 code/tests/fitellipse/getXY.m

@@ -1,0 +1,7 @@
+function [x,y]=getXY(X)
+% [x,y] = getXY(X) get the [x,y] component of curves X
+N = size(X,1)/2;
+x = X(1:N,:);
+y = X(N+1:end,:);
+
+end % getXY

### 2020-11-05 NSF2020/Description/specificaim3_ver2.tex
wrapped up first draft of 4.3.2

@@
 
+\begin{wrapfigure}[21]{r}{3.0in}
+%\vspace*{+15pt}
+\centerline{\includegraphics[width=3.0in]{figures/integrands}}
+\vspace*{-10pt}
+\caption{{\footnotesize The Fourier modes of $K(x_0,y)$ and $K_2(x_0,y)$
+  where $|x_0| = 0.99$ and $\partial\Omega$ is the unit circle. The
+  trapezoid rule applied to the red integrand has large amounts of
+  error. However, the trapezoid rule is much more accurate when applied
+  to the blue integrand. Since the difference between the red and blue
+  curves can be accurately computed with the barycentric quadrature
+  rule, the error of this quadrature rule applied to the screened
+  Laplace layer potential will be uniformly bounded in $\Omega$.}}
+\label{fig:integrands}
+\end{wrapfigure}
 Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
@@
 accurately computed with the trapezoid rule since the kernel is bounded
-for all $x$ and $y$.
-
-\includegraphics[scale=1]{figures/integrands.pdf}
+for all $x$ and $y$. To proposed method is demonstrated in
+Figure~\ref{fig:integrands} where the amplitude of the Fourier modes of
+$K(x_0,y)$ and $K_2(x_0,y)$ are plotted. The quadrature of the trapezoid
+rule is the sum of the Fourier amplitudes not captured at the
+resolution.
 

### 2020-11-05 NSF2020/Description/specificaim3_ver2.tex
starting fluctuating hydro

@@
 \caption{{\footnotesize The Fourier modes of $K(x_0,y)$ and $K_2(x_0,y)$
-  where $|x_0| = 0.99$ and $\partial\Omega$ is the unit circle. The
+  where $\|x_0\| = 0.99$ and $\partial\Omega$ is the unit circle. The
   trapezoid rule applied to the red integrand has large amounts of
@@
 \label{subsec:fluctuating}
-Using DLP formulation for fluctuating hydrodynamics so that we have a
-second-kind BIE
-\textcolor{red}{
-Once the collision-resolution algorithm is implemented, we will check
-the computing performance first before we embark on incorporating
-fluctuating hydrodynamics~\cite{Bao17,Bao18}, which might be important
-even at the scales of the amphiphilic particle size in some cases. We
-propose to extend the high-order time-integration scheme for a
-stochastic differential equation~\cite{fu2015pre} to this system.
-}
+Once algorithms that address quadrature, adaptive time stepping, and
+contact are implemented, we will embark on incorporating fluctuating
+hydrodynamics~\cite{Bao17,Bao18} which are important even at scales of
+the some amphiphilic particles.
+
+\todo[inline]{Using DLP formulation for fluctuating hydrodynamics so
+that we have a second-kind BIE}
+%\textcolor{red}{
+%Once the collision-resolution algorithm is implemented, we will check
+%the computing performance first before we embark on incorporating
+%fluctuating hydrodynamics~\cite{Bao17,Bao18}, which might be important
+%even at the scales of the amphiphilic particle size in some cases. We
+%propose to extend the high-order time-integration scheme for a
+%stochastic differential equation~\cite{fu2015pre} to this system.
+%}

### 2020-11-05 code/tests/fitellipse/vesicle_test.m
minor changes in vesicles_test.m

@@ -1,5 +1,5 @@
 clear
-
+figure('Renderer', 'painters', 'Position', [250 250 1500 600])
 N = 16;
 nb = 50;
 
@@ -12,7 +12,7 @@ radii = 0.5;
 tl=[]; ta=[]; majorm=[]; minorm=[];
 
 irate = 40;
-T=13500;
+T=15000;
 dt = 0.05;
 
 k=1;
@@ -28,6 +28,9 @@ for i = 0:irate:T
 theta = (0:N-1)'*2*pi/N;
 posx = zeros(N,nb); 
 posy = zeros(N,nb); 
+
+tt = 0:irate*dt:T*dt;
+
 for j = 1:nb
   refX = kron([cos(tau(j)) -sin(tau(j)); +sin(tau(j)) cos(tau(j))],eye(N)) * ... 
       [ar*cos(theta);sin(theta)]*radii;  
@@ -42,7 +45,8 @@ end
     
 %%%
     
-figure(1);    
+% figure(1);   
+subplot(1,3,1)
     hold off
     [zo, ao, bo, alphao] = fitellipse([x((outer))';y(outer)'], 'linear', 'constraint', 'trace');
     [zi, ai, bi, alphai] = fitellipse([x(inner)';y(inner)'], 'linear', 'constraint', 'trace');
@@ -98,22 +102,24 @@ Xi = Qi * [ai * cos(t); bi * sin(t)] + repmat(zi, 1, npts);
     
     majorm(k) = am;
     minorm(k) = bm;
-    k=k+1;
-end
 
-figure(2);
-tt = 0:irate*dt:T*dt;
-plot(tt, ta, 'r', 'linewidth',3)
+%%%    
+subplot(1,3,2)
+plot(tt(1:k), ta(1:k), 'r', 'linewidth',3)
 xlabel('time t');
 ylabel('total area');
 set(gca,'fontsize',16);
+axis([0 T*dt ta(1)-40 ta(1)])
 
-
-figure(3);
-% tt = 0:5:tend;
-plot(tt, tl, 'r', 'linewidth',3)
+%%%
+subplot(1,3,3)
+plot(tt(1:k), tl(1:k), 'r', 'linewidth',3)
 xlabel('time t');
 ylabel('total arc length');
 set(gca,'fontsize',16); 
+axis([0 T*dt tl(1)-10 tl(1)])
 
 area=pi*majorm'.*minorm';
+
+k=k+1;
+end

### 2020-11-05 code/tests/fitellipse/vesicle_test.m
minor changes in vesicles_test.m

@@ -1,4 +1,6 @@
 clear
+% Please extract the zip file "vel_files.zip" first to have test data
+
 figure('Renderer', 'painters', 'Position', [250 250 1500 600])
 N = 16;
 nb = 50;

### 2020-11-06 NSF2020/Description/specificaim3_ver2.tex
small edits

@@
 % ----------------------------------------------------------------------
-The HAP model requires solving the exterior Dirichlet problem of the
-screened Laplace equation and the mobility problem of the Stokes flow at
-each time step in the complex domains such as Figure~\ref{fig:domain}.
-If discretizing these equations with stencil-based numerical methods,
-the computational domain must be truncated, the volume must be
+The HAP model requires solving exterior Dirichlet problems for the
+screened Laplace equation and the Stokes mobility problem at each time
+step in complex domains such as in Figure~\ref{fig:domain}. If
+discretizing these equations with stencil-based numerical methods, the
+computational domain must be truncated, the fluid volume must be
 discretized, and artificial boundary conditions must be imposed. The
@@
 Moreover, it is difficult to obtain high-order discretizations when the
-boundary surfaces are irregular. Since we are solving
-constant-coefficient elliptic PDEs, we represent the solution of the PDE
-of interest as a layer potential 
+boundary surfaces are irregular. Alternatively, since we are solving
+constant-coefficient elliptic PDEs, the solution of the PDE can be
+represented as layer potentials
 \begin{align}
   \label{eq:LP}
-  u(x) = \int_{\partial\Omega} K(x,y) \sigma(y) ds_y,
+  u(x) = \int_{\partial\Omega} K(x,y) \sigma(y)\,ds_y,
 \end{align}
-where $\sigma$ is an unknown density function, and $K(x,y)$ is formed
-with derivatives of the fundamental solution of the underlying PDE. By
+where $\sigma$ is an unknown density function, and $K(x,y)$ is a
+derivative of the fundamental solution of the underlying PDE. By
 matching the boundary condition at $x_0 \in \partial\Omega$ with the
-limit of equation~\eqref{eq:LP} as $x\rightarrow x_0 \in
-\partial\Omega$, a BIE for the density function is formed.
-Numerical methods to solve BIE has several advantages over their
-PDE-based counterpart: by construction, the layer
+limit of equation~\eqref{eq:LP} as $x\rightarrow x_0$, a BIE for the
+density function is formed. Numerical methods to solve BIEs have several
+advantages over their PDE-based counterpart: by construction, the layer
 potential~\eqref{eq:LP} satisfies far-field conditions; only
 $\partial\Omega$ needs to be discretized; carefully chosen kernels
-$K(x,y)$ result in a well-conditioned linear system that requires a
-mesh-independent number of GMRES iterations to solve; and high-order or
-spectral accuracy is attainable by using appropriate quadrature methods.
-In our previous work~\cite{Fu2018_SIAM} we demonstrate that BIEs are a
+$K(x,y)$ result in a well-conditioned linear system that is solved with
+a mesh-independent number of GMRES iterations; and high-order or
+spectral accuracy is attainable with appropriate quadrature methods. In
+our previous work~\cite{Fu2018_SIAM} we demonstrate that BIEs are a
 powerful tool to simulate two-dimensional suspensions of amphiphilic
@@
 three-dimensional BIE of the screened Laplace equation~\cite{ying_2006}
-and a well-conditioned BIE of the mobility problem~\cite{manasthesis}.
+and a well-conditioned BIE of the mobility problem~\cite{manasthesis,
+rac-gre2016}.
 

### 2020-11-06 NSF2020/Description/specificaim2_ver2.tex

--- 2020-11-04 NSF2020/Description/specificaim2_ver2.tex
@@
 %\subsection{Specific Aim 2: Functional Materials}
-\subsection{Specific Aim 2: Hydrodynamics and ...}
+\subsection{Specific Aim 2: Hydrodynamics}
 \label{subsec:specific_aim_2}
+Specific Aim 1 dealt with the collective material property of amphiphiles which does not involve the movement  of the solvent.
+In Specific Aim 2, we include hydrodynamics effects. Hydrodynamic effects are relevant
+because the rates of biological functions like fusion, fission, and pore dynamics rely on viscous dissipation \cite{RYHAM20112929}. 
+Additionally, coarse-grained and molecular dynamics theories include water either explicitly or implicitly in their models.
+
+A further area of relevance is in the fabrication of complex microscopic three-dimensional structures \cite{Cho2010}.
+Over the past decade, there has been an explosion of interest in small-scale processes that utilize capillary forces dominate,  van der Waals interactions and thermal noise  \cite{Zhang2017},
+to coordinated movement and bind  material subunits. Two prominent fabrication techniques are capillary origami 
+\cite{Pandey2011,Leong2007,Reynolds2019} and colloidal self-assembly \cite{Dasgupta2017,Siontorou2017}.
+Capillary origami uses principles of elastocapilirity wherein elastic solids deform under surface tension \cite{Bico2018,VanHonschoten2010}.
+In self-assembly of colloids,
+particles exhibit similar thermodynamic behavior of molecular systems, except that the behavior occurs over observable, long time scales \cite{Zhang2017}.
+
+The hydrodynamic interactions enter through the transmission of viscous stresses from one particle to the another.
+We must solve the system 
+\begin{alignat}{3}
+\label{Hupdate1}  & \frac{\dif {\bf a}_i}{\dif t} = {\bf v}_i,      &&  \frac{\dif {\bf R}_i}{\dif t}  = A({\bf w}_i),\quad        \\
+\label{Hupdate2}  & F_i({\bf x},t) = {\bf a}_i + {\bf R_i}{\bf x},  && P_i(t) = F_i(P_{0i},t), \quad && i = 1,\dots, N             \\
+\label{HBVP1} -& \mu \Delta {\bf u} + \nabla p = {\bf 0} , \quad \quad -&& \rho^2 \Delta u +u = 0, \\
+\label{HBVP2}  & \nabla \cdot {\bf u} = 0,                       &&                                                                  && \text{in } \Omega(t) = \mathbb{R}^3 \setminus \cup_{i=1}^N P_i\\
+\label{HBVP3}  & {\bf u }({\bf x}) = {\bf v}_i + {\bf w_i}\times {\bf x} , \quad                &&  u({\bf x}) = f_i({\bf x}),\quad  && \text{for } {\bf x} \in \partial P_i\\
+\label{HBVP4}  & ({\bf u } - {\bf u}_{\infty})({\bf x}) \to {\bf 0} && u({\bf x}) \to 0 && \text{as } {\bf x} \to \infty\\
+\label{HSB1}   & \int_{\partial P_i} (\boldsymbol{\sigma}  + \boldsymbol{\sigma}_{\text{hydro}})\nu \,dS + {\bf F}_{\text{repul},i} = {\bf 0}\span  \span\\
+\label{HSB2}   & \int_{\partial P_i} {\bf x} \times (\boldsymbol{\sigma}  + \boldsymbol{\sigma}_{\text{hydro}})\nu \,dS + {\bf G}_{\text{repul},i} = {\bf 0} \span \span
+\end{alignat}
+At the top, \eqref{Hupdate1} defines the particle velocity and rotation, respectively. Recall that $A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
+The second line \eqref{Hupdate2} defines the rigid motions and updates the particle position, respectively. 
+The particle velocity and rotation $({\bf v}_i, {\bf w}_i)$ needed in \eqref{Hupdate1} are outputs of the boundary value problem \eqref{HBVP1}--\eqref{HSB2}.
+To get to these, the activity $u$ solves the screened Laplace equation (\ref{HBVP1}b) with the material label boundary condition (\ref{HBVP3}b)
+and far-field boundary condition (\ref{HBVP4}b).
+This sets up the hydrophobic stress $\boldsymbol{\sigma}_{\text{hydro}}$ through \eqref{stress}.
+In turn, the fluid velocity ${\bf u}$ solves the Stokes equations (\ref{HBVP1}a, \ref{HBVP2}a)
+with background flow boundary condition (\ref{HBVP4}a).
+Due to Fredholm theory, there are precisely $N$ many velocity and rotation pairs $({\bf v}_i, {\bf w}_i)$
+that simultaneously satisfy the rigid motion boundary condition (\ref{HBVP3}a) and
+the requirement that the net force and net torque on each particle is zero; \eqref{HSB1}, \eqref{HSB2}.
+
 %The mathematics of this proposal investigates how three-dimensional solids deform under long-range surface tension interaction.
@@
 %
-Over the past decade, there has been an explosion of interest in the fabrication of complex microscopic three-dimensional structures 
-\cite{Cho2010}.
-These fabrication processes utilize the fact that at small scales, capillary forces dominate  van der Waals interactions and thermal noise  \cite{Zhang2017}, enabling the coordinated movement and binding of material subunits.
-Two prominent fabrication techniques are capillary origami
-\cite{Pandey2011,Leong2007,Reynolds2019} and colloidal self-assembly \cite{Dasgupta2017,Siontorou2017}.
-Capillary origami uses principles of elastocapilirity wherein elastic solids deform under surface tension \cite{Bico2018,VanHonschoten2010}.
-In self-assembly of colloids,
-particles exhibit similar thermodynamic behavior of molecular systems, except that the behavior occurs over observable, long time scales \cite{Zhang2017}.
 

### 2020-11-06 code/tests/fitellipse/vesicle_test.m
minor changes in vesicles_test.m

@@ -87,7 +87,8 @@ Xi = Qi * [ai * cos(t); bi * sin(t)] + repmat(zi, 1, npts);
     set(h,'linewidth',2)
 %     colormap(jet);
   end
-    
+    axis equal
+
     drawnow
     F = getframe;
 %     imwrite(F.cdata, ['File' num2str(i) '.png']);

### 2020-11-06 NSF2020/Description/specificaim3_ver2.tex
small changes

@@
 extend the results to three dimensions using a standard
-three-dimensional BIE of the screened Laplace equation~\cite{ying_2006}
-and a well-conditioned BIE of the mobility problem~\cite{manasthesis,
-rac-gre2016}.
+three-dimensional BIE formulation of the screened Laplace
+equation~\cite{ying_2006} and a well-conditioned BIE formulation of the
+mobility problem~\cite{manasthesis, rac-gre2016}.
 
-The most significant challenges of a BIE formulation include solving
-dense linear systems, developing preconditioning strategies, and
-developing quadrature methods for integrands that are nearly singular.
-These challenges are described in section~\ref{subsec:NumericalIssues}.
-Even with accurate quadrature and time stepping methods, rigid body
-simulations can easily result in unphysical contact. We propose two
-techniques to avoid unphysical contact in
-Section~\ref{subsec:timeStepping}. Then, proposed work for well-conditioned BIE
-formulations of fluctuating hydrodynamics are in
-section~\ref{subsec:fluctuating}.
+Significant challenges to solve BIEs include solving dense linear
+systems, developing preconditioning strategies, and developing
+quadrature methods for integrands that are nearly singular. These
+challenges are described in section~\ref{subsec:NumericalIssues}.
+However, numerical errors can still lead to unphysical contact between
+bodies. We propose two algorithms to avoid contact in
+Section~\ref{subsec:timeStepping}. Then, proposed work for
+well-conditioned BIE formulations of fluctuating hydrodynamics are
+described in Section~\ref{subsec:fluctuating}.
 
@@
 time is proportional to the cost of a matrix-vector multiplication that
-can be done in optimal or near-optimal time with the fast multiple
+can be done in optimal or near-optimal time with the fast multipole
 method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2, fmm3,
-fmm4, fmm6, fmm7, fmm8}. PI Quaife is experienced with applying FMMs for
-both the Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the
-screened Laplace equation~\cite{kro-qua2011, qua2011}. Alternatively,
-fast direct solvers can be used to avoid any iteration~\cite{fds1, fds2,
-fds3, fds4, fds5, fds6, fds7, fds8, ho2016cpam2, ho2016cpam1,
-minden2016, minden2017siammms}, but direct solvers often require a large
-amount of initial overhead, and this makes them less useful for problems
-with moving geometries. Alternatively, techniques in fast direct solvers
-can be used to develop efficient preconditioning strategies such as the
-inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017}. PI Quaife
-used the IFMM to precondition Stokes equations in a porous
-media~\cite{qua-cou-dar2018}, and a suite of other preconditioners
-including sparse approximate inverses~\cite{che2000} and
-multigrid~\cite{hem-sch1981, sch1982} will be investigated.
+fmm4, fmm6, fmm7, fmm8}. PI Quaife is experienced with applying FMMs to
+BIE formulations of the Stokes equation~\cite{qua-bir2014,
+bys-sha-qua2020} and the screened Laplace equation~\cite{kro-qua2011,
+qua2011}. Alternatively, fast direct solvers can be used to avoid
+iteration~\cite{fds1, fds2, fds3, fds4, fds5, fds6, fds7, fds8,
+ho2016cpam2, ho2016cpam1, minden2016, minden2017siammms}, but direct
+solvers often require a large amount of initial overhead, and this makes
+them less practical for problems with moving geometries. Alternatively,
+techniques in fast direct solvers can be used to develop efficient
+preconditioning strategies such as the inverse Fast Multipole Method
+(IFMM)~\cite{cou-pou-dar2017}. PI Quaife used the IFMM to precondition
+Stokes equations in a porous media~\cite{qua-cou-dar2018}, and a suite
+of other preconditioners including sparse approximate
+inverses~\cite{che2000} and multigrid~\cite{hem-sch1981, sch1982} will
+be investigated.
 
@@
 \caption{{\footnotesize The Fourier modes of $K(x_0,y)$ and $K_2(x_0,y)$
-  where $\|x_0\| = 0.99$ and $\partial\Omega$ is the unit circle. The
-  trapezoid rule applied to the red integrand has large amounts of
-  error. However, the trapezoid rule is much more accurate when applied
-  to the blue integrand. Since the difference between the red and blue
-  curves can be accurately computed with the barycentric quadrature
-  rule, the error of this quadrature rule applied to the screened
-  Laplace layer potential will be uniformly bounded in $\Omega$.}}
+  where $\|x_0\| = 0.99$ and $y \in \partial\Omega$, where
+  $\partial\Omega$ is the unit circle. The trapezoid rule applied to the
+  red integrand has large amounts of error, but the trapezoid rule is
+  much more accurate when applied to the blue integrand. Since the
+  difference between the red and blue curves can be accurately computed
+  with the barycentric quadrature rule, the quadrature error applied to
+  layer potentials for the screen Laplace equation will be uniformly
+  bounded in $\Omega$.}}
 \label{fig:integrands}
@@
 Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
-particles, and such near-contact results in nearly-singular integrands
-in both two and three dimensions. Quadrature methods to address such
-integrands has received a lot of attention in two and three
-dimensions~\cite{alpert, kapur, sidi, duffy, bruno1, bruno2, davis_1984,
-graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003, khayat_2005,
-schwab_1992, ying_2006, beale1, beale2, goodman_1990, haroldson_1998,
-lowengrub_1993, schwab_1992, ggq1, ggq2, ggq3, helsing_2008a,
-helsing_integral_2009, helsing_tutorial_2012, klockner2013jcp, qbx2,
-wala2019jcp, af2018sisc, siegel2018jcp, rachh2017jcp, ding2019arxiv,
-bar2014}. For two-dimensional problems, the trapezoid rule is the
-workhorse for BIEs since it achieves spectral accuracy when integrands
-are not nearly-singular~\cite{tre-wei2014}. To address nearly-singular
-integrands of two dimensional BIEs, we will use a {\em barycentric
-quadrature rule} that only requires a slight modification of the
-trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this method
-requires the layer potential satisfy Laplace or Stokes
+particles, and this results in nearly-singular integrands. Quadrature
+methods for these integrands has received a lot of attention in
+two and three dimensions~\cite{alpert, kapur, sidi, duffy, bruno1,
+bruno2, davis_1984, graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003,
+khayat_2005, schwab_1992, ying_2006, beale1, beale2, goodman_1990,
+haroldson_1998, lowengrub_1993, schwab_1992, ggq1, ggq2, ggq3,
+helsing_2008a, helsing_integral_2009, helsing_tutorial_2012,
+klockner2013jcp, qbx2, wala2019jcp, af2018sisc, siegel2018jcp,
+rachh2017jcp, ding2019arxiv, bar2014}. The trapezoid rule is the
+workhorse for two-dimensional BIEs since it achieves spectral accuracy
+when integrands are not nearly-singular~\cite{tre-wei2014}. To address
+nearly-singular integrands of two-dimensional BIEs, we will use a {\em
+barycentric quadrature rule} that only requires a slight modification of
+the trapezoid rule~\cite{ioa-pap-per1991}. This method requires the
+layer potential satisfy Laplace or Stokes
 equations~\cite{bar-wu-vee2015, chi-moo-qua2020}. The PIs will extend
-this quadrature rule so that it can be applied to the screened Laplace
+this quadrature method to layer potentials for the screened Laplace
 equation. This will be done by recognizing that the fundamental solution
@@
 + K_2(x,y)$, where $K_1(x,y) = -\log\|x - y\|$ and $K_2(x,y) = K(x,y) +
-\log\|x - y\|$. Using this decomposition, the layer potential involving
+\log\|x - y\|$. Using this decomposition, layer potentials involving
 $K_1(x,y)$ can be accurately computed with the barycentric quadrature
-rule~\cite{ioa-pap-per1991}, and the layer potential $K_2(x,y)$ can be
-accurately computed with the trapezoid rule since the kernel is bounded
-for all $x$ and $y$. To proposed method is demonstrated in
+rule~\cite{ioa-pap-per1991}, and layer potentials involving $K_2(x,y)$
+can be accurately computed with the trapezoid rule since the kernel is
+bounded for all $x$ and $y$. The proposed method is demonstrated in
 Figure~\ref{fig:integrands} where the amplitude of the Fourier modes of
@@
 % ----------------------------------------------------------------------
-\subsubsection{Avoiding contact with adaptive time stepping and
+\subsubsection{Eliminating contact with adaptive time stepping and
 repulsion}
@@
 
-An outstanding numerical issue when simulating the
-self-assembly of amphiphilic particles in a viscous solvent is the
-collision between amphiphilic particles. The hydrophobic attraction
-potential drives the amphiphilic particles towards one another so to
-minimize exposure to the solvent, and this leads to physical contact in
-finite time. Such particle collisions in a dense rigid body suspension
-is a great challenge and can be a bottleneck in large-scale simulations.
-We propose two algorithms to remedy this computational
-challenge---high-order adaptive time stepping and repulsion forces.
+A numerical issue when simulating the self-assembly of amphiphilic
+particles in a viscous solvent is the collision between the
+particles. The hydrophobic attraction potential drives the amphiphilic
+particles towards one another so to minimize exposure to the solvent,
+and this leads to physical contact in finite time. Such particle
+collisions in a dense rigid body suspension is a great challenge and can
+be a bottleneck in large-scale simulations. We propose two algorithms to
+remedy this computational challenge: high-order adaptive time stepping
+and repulsion forces.
 
 PI Quaife developed a high-order adaptive time stepping method for
-hydrodynamic suspensions~\cite{qua-bir2016} and he has used it with
-colleagues to investigate mixing and adhesion in
-suspensions~\cite{qua-vee-you2019, kab-qua-bir2017}. The method requires
-both a single-step high-order time stepping method and a computationally
-cheap estimate of the error. We plan to use a spectral deferred
-correction method~\cite{dut-gre-rok2000} since it can be used
-iteratively to increase the order of accuracy. To estimate the error,
-instead of using an embedded Runge-Kutta method or step-doubling, we
-will compute the total force and torque of the system which is
-computationally cheap and should be zero. The PIs experience is that
-error estimates based on physical constraints such as force- and
-torque-free conditions appropriately adjusts the time step size so that
-the dynamics are adequately resolved.
+hydrodynamic suspensions~\cite{qua-bir2016} and it has served as a
+reliable method to simulate processes including mixing and adhesion in
+suspensions~\cite{qua-vee-you2019, kab-qua-bir2017}. The method uses
+a single-step high-order time stepping method and a computationally
+cheap estimate of the error. The proposed work will use a spectral
+deferred correction method~\cite{dut-gre-rok2000} since it can
+iteratively apply a low-order method to achieve high-order accuracy. To
+estimate the error, we will compute the total force and torque of the
+system which is computationally cheap and physically zero. The PIs
+experience is that error estimates based on physical constraints such as
+force- and torque-free conditions appropriately adjust the time step
+size so that the dynamics are adequately resolved without the
+computational expense of strategies such as embedded Runge-Kutta
+methods, step-doubling, and Richardson extrapolation.
 
-Our previous work avoids contact by including a Leonard-Jones potential
-in the body forces~\cite{Fu2018_SIAM}. Such steep steric interaction at
-short ranges introduces great numerical stiffness that limit the time
-step size. To remove this stiffness, we will use a geometry-based
-contact method~\cite{har-pon-sor-zor2011}, and this method has been
-applied to vesicle suspensions~\cite{lu-rah-zor2017} and rigid body
-suspensions in two dimensions~\cite{bys-sha-qua2020} and
-three dimensions~\cite{Yan2019}. These methods determine repulsion
-force by solving a non-linear complementarity problem with a geometric
-constraint that the configuration is non-overlapping.
+Our previous work avoids contact by including a Leonard-Jones body
+forces~\cite{Fu2018_SIAM}. Such a steep steric interaction at short ranges
+introduces numerical stiffness and limits the time step size. To
+remove this stiffness, we propose a geometry-based contact
+method~\cite{har-pon-sor-zor2011}, and this method has been applied to
+vesicle suspensions~\cite{lu-rah-zor2017} and rigid body suspensions in
+two dimensions~\cite{bys-sha-qua2020} and three
+dimensions~\cite{Yan2019}. These methods determine repulsion force by
+solving a non-linear complementarity problem with a geometric constraint
+that the configuration is non-overlapping.
 

### 2020-11-07 NSF2020/Description/specificaim2_ver2.tex
still working on SA2

--- 2020-11-04 NSF2020/Description/specificaim2_ver2.tex
@@
 %\subsection{Specific Aim 2: Functional Materials}
-\subsection{Specific Aim 2: Hydrodynamics and ...}
+\subsection{Specific Aim 2: Hydrodynamics}
 \label{subsec:specific_aim_2}
-%The mathematics of this proposal investigates how three-dimensional solids deform under long-range surface tension interaction.
-The results generalize the physical principles used in the design of functional materials, enabling investigators to simulate sub-micron scale systems that are otherwise impractical to realize experimentally.
-It supplies new insight into organizational principles in physical and biological sciences.
-%
-Over the past decade, there has been an explosion of interest in the fabrication of complex microscopic three-dimensional structures 
-\cite{Cho2010}.
-These fabrication processes utilize the fact that at small scales, capillary forces dominate  van der Waals interactions and thermal noise  \cite{Zhang2017}, enabling the coordinated movement and binding of material subunits.
-Two prominent fabrication techniques are capillary origami
+Specific Aim 1 dealt with the collective material property of amphiphiles which does not involve the movement  of the solvent.
+In Specific Aim 2, we include hydrodynamics effects. Hydrodynamic effects are relevant
+because the rates of biological functions like fusion, fission, and pore dynamics rely on viscous dissipation \cite{RYHAM20112929}. 
+Additionally, coarse-grained and molecular dynamics theories include water either explicitly or implicitly in their models.
+
+A further area of relevance is in the fabrication of complex microscopic three-dimensional structures \cite{Cho2010}.
+Over the past decade, there has been an explosion of interest in small-scale processes that utilize capillary forces dominate,  van der Waals interactions and thermal noise  \cite{Zhang2017},
+to coordinated movement and bind  material subunits. Two prominent fabrication techniques are capillary origami 
 \cite{Pandey2011,Leong2007,Reynolds2019} and colloidal self-assembly \cite{Dasgupta2017,Siontorou2017}.
@@
 
-There is inherent intellectual value in fabricating novel three dimensional structures: Living cells construct biological molecules like proteins, membranes and viral capsids using hierarchical assembly \cite{Whitesides2002}.
-At the same time, elastocapillarity and colloidal self-assembly supply model systems for biological processes, like vesicle adhesion and membrane bound protein interaction \cite{Dasgupta2017}, the hydro-polar model of protein folding \cite{Lau1989,Pandey2011} and viral capsid assembly and \cite{CASPAR1962}.
-Capillarity can serve as a model for the lock and key mechanism binding between the active site of an enzyme and a substrate molecule \cite{Araujo2018}, or treating viruses like adhered particles
-\cite{Agudo-Canalejo2017,Agudo-Canalejo2015,Deserno2004}, or studying decorated vesicles 
-\cite{Auth2009,Weikl2002,Atilgan2007}. Although challenging, mathematically analyzing these model systems gives deep insight into biological structure and function.
+The hydrodynamic interactions enter through the transmission of viscous stresses from one particle to the another.
+This involves solving the system
 
-%Aside from their intellectual value, high-yield batch production of three-dimensional microstructures has application in functional materials engineering \cite{Syms2003,Leong2010,Crane2013}.
-In mechanics, for instance, elasticapillarity is a guiding principle lithographic etching of electronics \cite{Bico2018}.
-Researchers have used self-folding structures in the design of micro containers for encapsulated drug delivery \cite{Fernandes2012} and 3D photovoltaic cells \cite{Guo2009}.
-%In chemical engineering, emulsions stabilize droplets through capillary binding or particulates leading 
-%to colloidosomes capturing proteins, vitamins, flavors, living cells \cite{Dinsmore2002}. 
-%Microsensors, electronic ink and micromotors \cite{Zhang2017,Yan2016} 
-%are potential applications involving Janus-like particles.
+\setcounter{midequation}{\theequation}
+\addtocounter{midequation}{2}
 
-\begin{wrapfigure}[14]{r}{3.0in}
-\vspace*{+15pt}
-\centerline{\includegraphics[width=3.0in]{figures/SA3_fig2.pdf}}
-\vspace*{5pt}
-\caption{{\footnotesize Illustration of self-assembly of hydrophobically labeled faces.
-The thick triangles have a rim-hydrophobic label on one side, and are hydrophilic on the other side.
-These shapes would potentially aggregate into a tetrahedral container. }}
-\label{fig:illustration}
-\end{wrapfigure}
-The HAP theory is ideally suited to the problem of creating microstructures through capillary action.
-Specifically, the modeling application considers the assembly of polyhedra from smaller subunits.
-Our developments, which include viscous interactions, thermal fluctuation, and a long range description of capillarity, will pave the way for dynamical understanding to organizational principles in viral capsid formation, for instance \cite{CASPAR1962,Prasad2012}.
+\begin{minipage}[t]{0.44\textwidth}
+\begin{subequations}
+\begin{alignat}{2}
+\label{St1} -& \mu \Delta {\bf u} + \nabla p = {\bf 0}, \\
+\label{St2}  & \nabla \cdot {\bf u} = 0,                &&   \text{in } \Omega\\
+\label{St3}  & {\bf u }({\bf x}) = {\bf v}_i + {\bf w_i}\times {\bf x}, \;  && \text{for } {\bf x} \in \partial P_i\\
+\label{St4}  & ({\bf u } - {\bf u}_{\infty})({\bf x}) \to {\bf 0} && \text{as } {\bf x} \to \infty\\
+\notag \\
+\tag{\themidequation}
+\label{HSB1}  & \int_{\partial P_i} \boldsymbol{\sigma} \boldsymbol{\nu} \,\dif S + {\bf F}_{i} = {\bf 0}\span \span
+\end{alignat}
+\end{subequations}
+\end{minipage}
+\addtocounter{equation}{1}
+\setcounter{midequation}{\theequation}
+\addtocounter{midequation}{2}
+\begin{subequations}
+\begin{minipage}[t]{0.5\textwidth}
+\begin{alignat}{2}
+\label{SL1}  - & \rho^2 \Delta u +u = 0, && \text{in } \Omega\\
+\label{SL2}   & u({\bf x}) = f_i({\bf x}),\quad  && \text{for } {\bf x} \in \partial P_i\\
+\label{SL3} &  u({\bf x}) \to 0 && \text{as } {\bf x} \to \infty \\
+\notag \\
+\notag \\
+\tag{\themidequation}
+\label{HSB2}   & \int_{\partial P_i} {\bf x} \times \boldsymbol{\sigma} \boldsymbol{\nu} \,\dif S + {\bf G}_{i} = {\bf 0} \span \span\\
+\notag
+\end{alignat}
+\end{minipage} 
+\end{subequations}
 
-In order to illustrate the novelty of our approach, it is helpful to first describe how current experimental and mathematical techniques deal with polyhedral assembly.
-Capillary origami uses lithography to etch faces out of a thin, elastic sheet \cite{Pandey2011,Reynolds2019}.
-The collection of faces form a so-called net, and this net self-folds into a three-dimensional polyhedron (Figure~\ref{fig:illustration}).
-The motivation is to create micro containers to mimc protein folding \cite{Reynolds2019}.
-Prediction of geometric structure from its subunits is non-trivial.
-That is because the final morphology depends on the net structure, physical interactions, and the surrounding media, and researchers have formulated optimality criteria for these nets \cite{Araujo2018,Pandey2011}.
+\noindent for $i = 1,\dots, N$.
+The inputs to \eqref{St1}--\eqref{HSB2} are the collection of particle configurations.
+Within this system, the activity $u$ solves the screened Laplace equation \eqref{SL1} with the material label boundary condition \eqref{SL2}
+and far-field condition \eqref{SL3}. The forces ${\bf F}_i$ and torques ${\bf G}_i$ come from \eqref{totalFG}.
+In turn, the fluid velocity ${\bf u}$ solves the Stokes equations (\ref{St1}, \ref{St2}) with background flow boundary condition (\ref{St3}).
+The force and torque equations \eqref{HSB1}, \eqref{HSB2} couple the (\ref{St1}--\ref{St4}) to (\ref{SL1}--\ref{SL3}).
+The outputs are the collection of velocity and rotation pairs $({\bf v}_i, {\bf w}_i)$ that uniquely satisfy the rigid body boundary condition \eqref{St3}.
 
-The experimental shapes are hundreds of microns in diameter.
-Thus, as a key distinction with HAP approach, the driving force for folding in capillary origami and related processes comes from surface energy of the hinges (e.g.
-soldered hinges that supply a surface tension once the system is heated).
-Mathematicians have numerically and analytically described the behavior of these surface tension driven hinges \cite{Bico2018,Peraud2014,Brubaker2016}, making it possible to simulate the mechanical problem, in principle, using slender body theory for plates.
-
-To study this problem using HAP theory, we form a collection of thin, prism-like particles in Figure \ref{fig:illustration}. 
-Each of these particles serves as a face in the final morphology.
-The edges of the prisms are labeled hydrophobic according to the boundary condition in the screened Laplace equation boundary value problem.
-This way, the edges coalesce, forming the desired structures.
-Furthermore,
-by manipulating the boundary condition in HAP, it is possible to have faces attach and detach with precision, and form a net or other structures if so desired.
-Our HAP theory therefore generalizes submillimeter theoretical and experimental work to the micron and nanometer sizes.
-
-%There is also the possibility to explore new classes of mathematical materials, like wrinkling in polystyrene sheets \cite{Paulsen2016}, that include the interaction between an elastic material, the viscous solvent, and long range hydrophobic (capillary) interactions.
-In the case of rigid particles and subunits, the rigid body motions come from the so-called mobility boundary value problem for the Stokes equation.
-Here, the hydrophobic stress balances with the viscous stress coming from the rigid body motion of the particles in the surrounding solvent.
-If the particles are deformable, like a protein \cite{Elms2012} or as in the capillary induced bending of rods \cite{Schulman2017}, then we can formulate an elastic energy for deformation.
-These elastic energies account for surface bending or even permanent charge.
-To deploy this approach, it is a matter of solving the bodies' momentum balance equations coupled to the fluid through the viscous, elastic, and hydrophobic stress balance.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{figures/SA3_fig1.pdf}
-\end{center}
-\caption{(A)--(D) shows the spontaneous insertion of two hydrophobic particles into a vesicle bilayer. 
-The driving force is long-range interaction between the hydrophobic, magenta particles and
-the bilayer core.  The particle entrainment cause the vesicle to break apart, analogously to surfactant
-induced lysis.}
-\end{figure}
-Finally, further applications of our modeling approach include colloidal interaction on interfaces.
-Here, the experimental setups use Janus particles to model, for example, membrane bound proteins \cite{Kumar2013,Lehle2008,Zhang2017}.
-The idea of an amphiphilic Janus particle was introduced by P.
-G.
-de Gennes in 1991 \cite{Zhang2017}.
-The Investigators have significant experience as Janus particles figure heavily into our particle based description of bilayers, and can adjust our modeling approach to account for proteins.
-This is done by consider mixtures, consisting of many (hundreds to thousands) long, elongated amphiphilic particles for the lipid phase.
-Larger particles with hydrophobic patches or stripes model the proteins \cite{Jurasek2017}.
-
-The distinction between macroscopic capillarity and microscopic hydrophobic force are relevant here as well.
-Prior models use surface energies to account for interaction between particles in an interface \cite{Dasgupta2017}.
-However, this may be missing important physics, and here our modeling approach has the advantage in that protein insertion, for instance, is a self-consistent consequence of the formulation, versus an assumption imposed by boundary conditions.
-The simulations will enable us address important biological questions on how a collection of 
-interface bound colloids interact \cite{Yao2013,Salib2013}, 
-and how configurations dictate 
-macroscopic surface properties and sense background curvature \cite{Cavallaro2011,Liu2018,Sharifi-Mood2015}.
+The particle velocity and rotation $({\bf v}_i, {\bf w}_i)$ allow us to update the particle position:
+\begin{alignat}{3}
+\label{Hupdate1}   \frac{\dif {\bf a}_i}{\dif t} = {\bf v}_i,      \quad  \frac{\dif {\bf R}_i}{\dif t}  = A({\bf w}_i).
+\end{alignat}
+Recall that $A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
+Also, ${\bf a}_i$ is the particle center the rotation matrix ${\bf R}_i$ defines the orientation.
+That way, the particle configurations come from the flow maps $F_i({\bf x},t) = {\bf a}_i(t) + {\bf R_i}(t){\bf x}$ with
+$P_i(t) = F_i(P_{0i},t)$ and $f_i(F_i({\bf x},t)) = f_{i0}({\bf x})$ where $P_{i0}$ and $f_{i0}$ are the $i$th reference particle
+and material label respectively.

### 2020-11-07 NSF2020/Description/specificaim2_ver2.tex
SA2 close to done

@@
 In Specific Aim 2, we include hydrodynamics effects. Hydrodynamic effects are relevant
-because the rates of biological functions like fusion, fission, and pore dynamics rely on viscous dissipation \cite{RYHAM20112929}. 
+because the rates of biological functions like fusion, fission, and pore dynamics rely on viscous dissipation \cite{RYHAM20112929},
+and can determine which local equilibria the system tends towards. 
 Additionally, coarse-grained and molecular dynamics theories include water either explicitly or implicitly in their models.
@@
 
-The particle velocity and rotation $({\bf v}_i, {\bf w}_i)$ allow us to update the particle position:
+The particle velocity and rotation $({\bf v}_i, {\bf w}_i)$ update the particle configurations:
 \begin{alignat}{3}
-\label{Hupdate1}   \frac{\dif {\bf a}_i}{\dif t} = {\bf v}_i,      \quad  \frac{\dif {\bf R}_i}{\dif t}  = A({\bf w}_i).
+\label{Hupdate1}   \frac{\dif {\bf a}_i}{\dif t} = {\bf v}_i,      \quad  \frac{\dif {\bf R}_i}{\dif t}  = A({\bf w}_i),\quad i = 1, \dots, N.
 \end{alignat}
@@
 and material label respectively.
+
+Numerically solving \eqref{St1}--\eqref{HSB2} is a nontrivial matter.
+First, we have to carefully map the particle configurations because the domain $\Omega(t)$ and boundary conditions $f_i$ are constantly changing.
+The particle dynamics in \eqref{Hupdate1} and in \eqref{SGD} both involve solving
+screened Laplace boundary value problems on evolving domains, but differ in that \eqref{Hupdate1} has an additional Stokes flow
+generating the dissipation. When there is no background flow ${\bf u}_{\infty} = {\bf 0}$, the system obeys the energy law
+\begin{equation}
+\frac{\dif}{\dif t} \Phi + \int_{\Omega(t)} \mu |\nabla {\bf u} + \nabla {\bf u}^T|^2 \,dx = 0
+\end{equation}
+and the particle configurations tend toward a local equilibrium.
+
+A nonzero background flow continually injects energy into the system. We deal with the background flow using
+the Power and Miranda representation 
+\begin{equation}
+\label{PowerMiranda}
+{\bf u} = {\bf u}_{\infty} + D\eta + \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + R(\cdot, {\bf a}_i) {\bf G}_i.
+\end{equation}
+where $S(\cdot, {\bf a}_i)$ and $ R(\cdot, {\bf a}_i)$ are stokeslets and rotlets supported at the particle centers ${\bf a}_i.$
+The symbol $D$ denotes the Stokes double layer integral operator (see Specific Aim 3).   
+The representation \eqref{PowerMiranda} automatically satisfies \eqref{St1}, \eqref{St2}, \eqref{St4} and \eqref{HSB1}.
+We solve for the unknown density $\eta : \partial \Omega \to \mathbb{R}$ by requiring that jump in viscous stress
+vanished across $\partial P_i$. This jump condition guarantees that ${\bf u}$ is a rigid motion within each particle,
+and by continuity, equals a rigid motion on the particle boundary as required by \eqref{St3}.
+
+We prove a, what to our knowledge is new, result concerning the evaluation of Maxwell-type stresses. 
+\begin{proposition}
+  \label{prop:recip}
+  Suppose that $u = \sum_{i=1}^N u_i$ where $u_i$ is a solution of the screened Laplace equation
+  in $\mathbb{R}^3 \setminus P_i$ for $i=1,\dots, N.$ Then 
+\begin{equation}
+{\bf F}_i = \sum_{j \neq i} \int_{\partial P_i}[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
+{\bf G}_i = \sum_{j \neq i} \int_{\partial P_i} {\bf x} \times [\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, \quad i = 1\dots, N.
+\end{equation}
+where $\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i \cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$ and
+$[\cdot]$ denotes the jump in stress across $\partial \Omega.$ 
+\end{proposition}
+As described in Specific Aim 3, we solve \eqref{SL1}--\eqref{SL3}  using a double layer potential representation.
+While accurate in the far-field, this representation involves a strongly singular integral which
+leads to large numerical errors when evaluating the the hydrophobic stress \eqref{stress} along the particle boundaries.
+The identity in Proposition \ref{prop:recip} gets around this critical problem by utilizing the fact that $u_j$, $j\neq i$ is smooth and the normal derivative
+of  $u_i$ continuous across $\partial P_i$.

### 2020-11-08 NSF2020/Description/background.tex
working on broader impacts section to include Quaife

@@
 to show that $\Phi$ converges to a surface energy in the zero-decay length limit \cite{Lee2018,Lin2015,Shibata2004}.
-For non-zero decay lengths, solutions of \eqref{SL} yield an attractive interaction, e.g. between hydrophobic parallel disks
+For non-zero decay lengths, solutions of \eqref{SL} yield an attractive interaction, e.g.~between hydrophobic parallel disks
 separated by water \cite{Eriksson1989}. Also, we have demonstrated with simulation that the forces 
@@
 is a formula for the first variation of $\Phi$ \cite{Bandle2015,Schiffer1954,Grinfeld2010}. 
-This first variation  is a symmetric, rank-two tensor called the hydrophobic stress;
+This first variation  is a symmetric, rank-two tensor called the hydrophobic stress:
 \begin{equation}
@@
 for creating functional materials \cite{Lee2014, Lee2013}. 
-This topic is the basis of Specific Aim 3. Janus particles are typically
+This topic is the basis of Specific Aim 3 \todo[inline]{not true
+anymore}. Janus particles are typically
 spherical with a biphasic material label on either hemisphere,  endowing the particle

### 2020-11-08 NSF2020/Description/broaderimpacts.tex
working on broader impacts section to include Quaife

@@
 
-The proposed mathematical analysis and modeling will provide a transformative
-understanding of the collective dynamics of amphiphilic particles such as 
-(1) their self-assembly into micelles and bilayers, and 
-(2) the interaction between these building blocks.
-Amphiphilic Janus particles have gained increasing popularity for fabrication of smart materials.
-The proposed hybrid continuum model, mathematical analysis and numerical algorithms will have transformative impact on
-precision design for specific mechanical properties of materials made of amphiphilic nanoparticles.
-An important component of this proposal is the interdisciplinary education and training of
-both undergraduate and graduate students.  The combination of mathematical modeling, analysis and
-scientific computing  in this project provides a compelling
-example of the importance of mathematics in biophysics and engineering applications.
-The concepts and
-methods described here go beyond the context of amphiphilic particles and lipid molecules. They extend
-to other problems featuring microscopic phase separation that leads to  formation of mesoscopic domains.
-This situation arises, for example, in biological development in systems biology.
-The methods developed here have the potential to impact those and other related areas in biomedicine and biotechnology.
+The proposed mathematical analysis and modeling will provide a
+transformative understanding of the collective dynamics of amphiphilic
+particles such as (1) their self-assembly into micelles and bilayers,
+and (2) the interaction between these building blocks. Amphiphilic Janus
+particles have gained increasing popularity for fabrication of smart
+materials. The proposed hybrid continuum model, mathematical analysis
+and numerical algorithms will have transformative impact on precision
+design for specific mechanical properties of materials made of
+amphiphilic nanoparticles. An important component of this proposal is
+the interdisciplinary education and training of both undergraduate
+students, graduate students, and postdoctoral fellows. The combination
+of mathematical modeling, analysis, and scientific computing in this
+project provides a compelling example of the importance of mathematics
+in biophysics and engineering applications. The concepts and methods
+described here go beyond the context of amphiphilic particles and lipid
+molecules. They extend to other problems featuring microscopic phase
+separation that leads to formation of mesoscopic domains. This situation
+arises, for example, in biological development in systems biology. The
+methods developed here have the potential to impact those and other
+related areas in biomedicine and biotechnology.
 
@@
 \label{subsec:Educational_plans}
-The proposed research will have immediate impact on 
-undergraduate and graduate education. At the undergraduate level,
-the project will involve and support undergraduate researcher from Fordham University.
-The supported summer researchers will gain valuable first-hand 
-experience in inherently interdisciplinary, mathematical fluid modeling and computation.
-We will incorporate research into teaching, especially in differential equation  
-and programming courses.
+The proposed research will have immediate impact on undergraduate and
+graduate education. At the undergraduate level, the project will involve
+and support undergraduate researcher from Fordham University. The
+supported summer researchers will gain valuable first-hand experience in
+inherently interdisciplinary, mathematical fluid modeling and
+computation. We will incorporate research into teaching, especially in
+differential equation and programming courses. PI Quaife will expose
+undergraduate and high school students to the reserach through the
+Undergraduate Research Opportunity Program (UROP) and Young Scholar's
+Program (YSP).
 
-Over the past eight years, PI Ryham has included many undergraduates 
-in the execution of research initiatives, coauthoring 
-publications. He has a  track record for supporting underrepresented groups,
-being called on by the Collegiate Science and Technology Entry Program (CSTEP) to make
-opportunities for promising students, for example. He has mentored
-two Clare Boothe Luce Scholars, one a U.S. Marine Corp veteran,
-and a high school student in the NYU GSTEM program.
+Over the past eight years, PI Ryham has included many undergraduates in
+the execution of research initiatives, coauthoring publications. He has
+a track record for supporting underrepresented groups, being called on
+by the Collegiate Science and Technology Entry Program (CSTEP) to make
+opportunities for promising students, for example. He has mentored two
+Clare Boothe Luce Scholars, one a U.S. Marine Corp veteran, and a high
+school student in the NYU GSTEM program.
 
-The PIs will capitalize on the synergy between NJIT's doctoral program in Mathematical Sciences 
-and Fordham's undergraduate focus in the Department of Mathematics. 
-Promising, young undergraduate scientists from the Bronx community 
-while find a natural pipeline into graduate studies through working directly 
-or indirectly on this project. 
-On the graduate-level education, PI Young and co-PI Jiang expect to train and support
-a PhD student, Yuexin Liu (who is in her third-year at NJIT) for two more years. Yuexin Liu has past experiences
-in the undergraduate training program at NJIT, and will train an undergraduate intern. 
-The PIs will foster vertical integration between the senior personnel, their collaborators, postdocs, 
-doctoral and Bachelor students, enhancing the
+The PIs will capitalize on the synergy between NJIT's doctoral program
+in Mathematical Sciences and Fordham's undergraduate focus in the
+Department of Mathematics. Promising, young undergraduate scientists
+from the Bronx community while find a natural pipeline into graduate
+studies through working directly or indirectly on this project. On the
+graduate-level education, PI Young and expects to train and
+support a PhD student, Yuexin Liu (who is in her third-year at NJIT) for
+two more years. Yuexin Liu has past experiences in the undergraduate
+training program at NJIT, and will train an undergraduate intern. The
+PIs will foster vertical integration between the senior personnel, their
+collaborators, postdocs, doctoral and Bachelor students, enhancing the
 learning environment.
@@
 particles. The model formulates the interaction potential through a
-screened Laplace equation boundary value problem possessing 
-the physical properties like non-additivity and decay of realistic hydrophobic attraction.
-Colloidal systems collectively self-assemble into bilayer
-morphologies, and we analyze the elastic properties of these amphiphilic particle ensembles.
-This allows us to interpret the Helfrich free energy in terms of hydrophobic interactions and 
-specific molecular characteristics. We extend the capabilities of the
-boundary integral equation quadrature by expansion method to perform
-large particle number simulations in three dimensions with collisions. 
-Results from these computations will be used to compare collective  amphiphilic 
-against experiment,  and study the optimal design of three-dimensional functional materials.
+screened Laplace equation boundary value problem possessing the physical
+properties like non-additivity and decay of realistic hydrophobic
+attraction. Colloidal systems collectively self-assemble into bilayer
+morphologies, and we analyze the elastic properties of these amphiphilic
+particle ensembles. This allows us to interpret the Helfrich free
+energy in terms of hydrophobic interactions and specific molecular
+characteristics. We extend the capabilities of the boundary integral
+equation quadrature by expansion method to perform large particle number
+simulations in three dimensions with collisions. Results from these
+computations will be used to compare collective amphiphilic against
+experiment, and study the optimal design of three-dimensional
+functional materials.
 
@@
 and collaborative efforts in physics, applied mathematics, algorithms
-and computing.  Ryham has been working on mathematical modeling with a strong
-analytical background. Young has been working on many areas of computational
-fluid dynamics and applications to math biology for many years.
-Jiang has been working on integral
-equation methods, fast algorithms, and their applications to 
-computational electromagnetics and fluid dynamics
-for many years.  Their recent collaborative work on
-the HAP model in two dimensions has provided 
-a solid foundation on the proposed research.
+and computing.  Ryham has been working on mathematical modeling with a
+strong analytical background. Young has been working on many areas of
+computational fluid dynamics and applications to math biology for many
+years.  Jiang has been working on integral equation methods, fast
+algorithms, and their applications to computational electromagnetics and
+fluid dynamics for many years. Their recent collaborative work on the
+HAP model in two dimensions has provided a solid foundation on the
+proposed research.
 
@@
 %
-The management responsibility of this collaborative research will
-reside with the lead PI (Ryham) for this endeavor.  The research work is
+The management responsibility of this collaborative research will reside
+with the lead PI (Ryham) for this endeavor. The research work is
 structured to meet the tasks discussed in
-Sec.~\ref{sec:proposed-work}.
+Section~\ref{sec:proposed-work}.
 %
-The PIs, their postdoc and students will meet frequently in person.
-The PIs will share software packages, paper sources, and references on a common
-\textsf{Git} repository. The resulting software packages will be posted
-on the \textsf{Github} software repository.
+The PIs, their postdoc and students will meet frequently in person.  The
+PIs will share software packages, paper sources, and references on a
+common \textsf{Git} repository. The resulting software packages will be
+posted on the \textsf{Github} software repository.
 
@@
 
-\textbf{Research Schedule:} The detailed schedule for the proposed
-work is shown in Fig.~\ref{fig:schedule}.
+\textbf{Research Schedule:} The detailed schedule for the proposed work
+is shown in Fig.~\ref{fig:schedule}.

### 2020-11-08 NSF2020/Description/preliminarywork.tex
working on broader impacts section to include Quaife

@@
 \end{center}\vspace{-0.3in}
-\caption{ 
-(A) A vesicle formed by amphiphilic particles in shear flow,
+\caption{(A) A vesicle formed by amphiphilic particles in shear flow,
   and the tank-treading motion (B)--(D). The separation of particle
-pairs in (B) and (C) illustrate inter-leaflet slip.
-(E) -- (G) Tank-treading reaches a steady state in elliptical aspect ratio,
-major-axis angle, and circumference. }
+  pairs in (B) and (C) illustrate inter-leaflet slip.  (E)--(G)
+  Tank-treading reaches a steady state in elliptical aspect ratio,
+  major-axis angle, and circumference.}
 \label{fig:tanktreading}
@@
 and midplane respectively. In the non-dimensionalized system, the particles have diameter 2, on the order of $\rho,$ 
-and the vesicle diameter is about 14. 
-Figure \ref{fig:tanktreading}E shows the aspect ratio of the major to minor axes reaching an equilibrium value in the 
+and the vesicle diameter is about 14. \todo[inline]{missing units. nm?}
+Figure~\ref{fig:tanktreading}E shows the aspect ratio of the major to minor axes reaching an equilibrium value in the 
 red and blue curves, yet oscillating in the high-shear rate (yellow) curve.

### 2020-11-08 NSF2020/Description/specificaim1_ver2.tex
working on broader impacts section to include Quaife

@@
 self-assembly of amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu2018_SIAM}, and
-recreates the tank-treading phenomenon in external shear flows \cite{Fu20} \textbf{!!let's put a proceedings here so we have something to cite!!}.
+recreates the tank-treading phenomenon in external shear flows
+\cite{Fu20} \todo[inline]{!!let's put a proceedings here so we have something to cite!!}.
 %
@@
 
-An interesting and challenging feature of \eqref{ansatz3} is that
-the elastic energy couples director gradients to surface geometry through the tilt vector field.
-In biological contexts, bilayer energy is the sum monolayer energies, and tilt appears at lipid domain boundaries, the edge of nanopores and at the boundary of membrane inclusions \cite{PhysRevE.102.042406}.
-Under spatial scales much larger than the membrane thickness, membrane energy is well-characterized by
-the Canham-Helfrich energy used throughout the fluid-structure literature 
-\cite{QiangDu09, Lowengrub07,KimLai2010_JCP,Hu,HuLaiSeolEtAl2016_JCP} \textbf{!! YNY and BQ, place your recent works here!!}.
-The Canham-Helfrich energy is actually a special case of \eqref{ansatz3} obtained by setting $n =  \pm N$ (the $\pm$ depending
-on orientation) and collapsing both monolayers onto the membrane midplane. There,
-splay $\Div n$ equal to twice the mean curvature, saddle splay $\det \nabla n$ equal to the Gauss curvature,
-and both twist and tilt are equal to zero.
+An interesting and challenging feature of \eqref{ansatz3} is that the
+elastic energy couples director gradients to surface geometry through
+the tilt vector field.  In biological contexts, bilayer energy is the
+sum monolayer energies, and tilt appears at lipid domain boundaries, the
+edge of nanopores and at the boundary of membrane inclusions
+\cite{PhysRevE.102.042406}.  Under spatial scales much larger than the
+membrane thickness, membrane energy is well-characterized by the
+Canham-Helfrich energy used throughout the fluid-structure literature
+\cite{QiangDu09, Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP,
+qua-bir2014, qua-vee-you2019}. \todo[inline]{YNY: place your recent
+works here} The Canham-Helfrich energy is actually a special case of
+\eqref{ansatz3} obtained by setting $n =  \pm N$ (the $\pm$ depending on
+orientation) and collapsing both monolayers onto the membrane midplane.
+There, splay $\Div n$ equal to twice the mean curvature, saddle splay
+$\det \nabla n$ equal to the Gauss curvature, and both twist and tilt
+are equal to zero.
 
@@
 % and what benefits could accrue if the project is successful.
-\begin{center}
-Preliminary results
-\end{center}
+%\begin{center}
+%Preliminary results
+%\end{center}
+\subsubsection{Preliminary results}
 Our preliminary tested for elastic properties by subjecting bilayers to external loads \cite{Fu2018_SIAM}.
@@
 
-\begin{center}
-Anticipated model simulations
-\end{center}
+%\begin{center}
+%Anticipated model simulations
+%\end{center}
+\subsubsection{Anticipated model simulations}
 To characterize material properties, we compare the energies and forces generated by

### 2020-11-08 NSF2020/Description/broaderimpacts.tex
pass through broader impacts file

@@
 {\it Broader impacts:} 
-One PhD student (Szu-Pei Fu) was
-funded to work with YNY, and work has resulted in seven papers
+One PhD student (Szu-Pei Fu) was funded to work with YNY, and work has
+resulted in seven papers
 \cite{Nganguia2013_PoF,Nganguia2013_PRE,Young2014_JFM,Young2015_PoF,Nganguia2015_CiCP,Pak2015_PNAS,fu2015pre}.
-YNY has been actively involved with promotion of underrepresented students at NJIT. 
-The other PhD student (Herve Nganguia) is African. YNY has taught a broad
-spectrum of courses in fluid mechanics and applied math modeling.
+YNY has been actively involved with promotion of underrepresented
+students at NJIT.  The other PhD student (Herve Nganguia) is African.
+YNY has taught a broad spectrum of courses in fluid mechanics and
+applied math modeling.
 
 \noindent
-{\bf Shidong Jiang}: {\it NSF DMS-1418918,
-  Efficient High-Order Parallel Algorithms for Large-Scale Photonics Simulation},
-\$150,000, 08/15/2014 - 06/30/2017, PI.
-{\it Intellectual merit:} The goal of the proposed research is to develop
-\emph{robust, high-order numerical methods} and \emph{efficient parallel algorithms} to
-achieve greater accuracy and larger scale for photonics simulation.
-
-%Jiang, Kloeckner, and their collaborators have constructed
-%a stable second kind integral equation formulation for the mode calculation of optical
-%waveguides of arbitrary shape; they have quantified the effect of cladding thickness on
-%modal confinement loss in photonic waveguides; they have developed high-quality software
-%package for solving integral equations in both two and three dimensions.
+{\bf Bryan Quaife}: {\em NSF DMS-2012560, Erosion, Transport, and
+Dispersion in Granular and Porous Media}, \$249,636,
+08/01/2020--07/31/2023, PI. {\em Intellectual Merit:} The goal of this
+research is to develop high-order numerical methods to
+simulate hydrological processes including erosion.
 
@@
 {\it Broader impacts:} 
-During the funded period, the PI has published or submitted twelve papers to refereed international journals~\cite{jiang2014sisc,bao2015jcp,jiang2015acom,greengard2015jcp,fu2015pre,gan2016sisc,jiang2016jcp,jiang2016oe,ben2016tpm,jiang2017siammms,jiang2017cicp,lai2018acha},
-and presented the research results at many institutions and international
-conferences/workshops to disseminate research results. On the education side,
-the PI has supervised two students - Shaobo Wang~\cite{jiang2015acom,wang2019jsc}
-and Szu-Pei Fu~\cite{fu2015pre,Fu2018_SIAM} (co-advised with Yuan-Nan Young),
-with the partial support of the grant.
-%Finally, the software package developed by both PIs of this collaborative grant
-%has many applications in scientific computing, especially those related to
-%the integral equation methods.
+A second-year PhD student (Jake Cherry) has been assigned to this
+project. Since the funding just began, results have not yet
+been published or presented.
 
@@
   beginning of the project.}
+  \todo[inline]{Need to update Gantt table}
 \label{fig:schedule}
@@
 computational fluid dynamics and applications to math biology for many
-years.  Jiang has been working on integral equation methods, fast
-algorithms, and their applications to computational electromagnetics and
-fluid dynamics for many years. Their recent collaborative work on the
-HAP model in two dimensions has provided a solid foundation on the
-proposed research.
+years. Quaife has been working on integral equation methods, fast
+algorithms, and their applications to fluid dynamics for many years.
+Their recent collaborative work on the HAP model in two dimensions has
+provided a solid foundation on the proposed research.
 
@@
 %
-The PIs, their postdoc and students will meet frequently in person.  The
-PIs will share software packages, paper sources, and references on a
-common \textsf{Git} repository. The resulting software packages will be
-posted on the \textsf{Github} software repository.
+The PIs, their postdoc and students will meet frequently on Zoom and in
+person when possible. The PIs will share software packages, paper
+sources, and references on a common \textsf{Git} repository. The
+resulting software packages will be posted on the \textsf{Github}
+software repository.
 

### 2020-11-08 NSF2020/Description/background.tex
added my name to title

@@
 {\it Rolf Ryham (lead PI, Fordham University)}\\
-{\it Shidong Jiang (co-PI, NJIT) and Yuan-Nan Young (PI, NJIT)}
+{\it Bryan Quaife (PI, FSU) and Yuan-Nan Young (PI, NJIT)}
 \section{Background}

### 2020-11-09 NSF2020/Description/background.tex
yny

@@
 {\bf {Collaborative Research: Mathematical modeling and coarse-grained simulations of self-assembly of amphiphilic Janus particles in a solvent}}\\
-{\it Rolf Ryham (lead PI, Fordham University)}\\
-{\it Bryan Quaife (PI, FSU) and Yuan-Nan Young (PI, NJIT)}
+{\it Rolf Ryham (lead PI, Fordham University)}, {\it Bryan Quaife (PI, FSU) and Y.-N. Young (PI, NJIT)}
 \section{Background}
 \label{sec:background}
-\subsection{Hydrophobic Forces}
-\label{sec:hydrophobicforce}
+The goal of this collaborative proposal is to investigate the dynamic self-assembly of amphiphilic particles interacting with each other via hydrophobic forces in a solvent using continuum
+modeling and numerical simulations.  Amphiphilic particles (such as lipid molecules) possess both hydrophobic and hydrophilic structures. In a viscous solvent they
+self-assemble into meso-/macroscopic structures (such as micelles and bilayers of lipids) to shield their hydrophobic parts from contact with the solvent molecules (water).
+%
+%\subsection{Hydrophobic Forces}
+%\label{sec:hydrophobicforce}
+%
+Such self-assembly of amphiphiles via hydrophobic force is ubiquitous in biology and biophysics \cite{Israelachvili1954},
+%The hydrophobic force is a ubiquitous molecular interaction in biology \cite{Israelachvili1954}, 
+and has been a major source of nonspecific interactions between
+nanoparticles for self-assembly in  soft matter \cite{Sanchez-IglesiasEtAl2012_ACSNano,AltantzisEtAl2013_PSC,XieYangLuEtAl2020_COCIS}. 
+%The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles so to design smart materials of desirable properties by
+%tuning the geometry and properties of the amphiphilic particles.
 
-The hydrophobic force is a ubiquitous molecular interaction in biology \cite{Israelachvili1954}.
-The word hydrophobic (water fearing) derives from the low solubility of oil (hydrocarbon solute) in water and vice versa. 
-It causes hydrophobic moieties to aggregate and cluster,
-is responsible for the adhesion between hydrophobic surfaces \cite{Ducker2016}, large contact angles on a 
-dewetting surface \cite{Arenas2019,Sandre1999}, accumulation of particles along interfaces \cite{Lee2013,Lee2014}, 
-formation of micelles and bilayers \cite{Israelachvili80}, and protein folding and membrane insertion \cite{Kabelka2018}.
-
-Lipids are amphiphilic molecules whose  structure possesses
-both hydrophobic and hydrophilic parts. 
-The amphiphilic property is what allows lipids to form the membranes and 
-compartments of living cells \cite{Israelachvili80}. 
-More specifically, a lipid consists of 
-an elongated hydrocarbon tail that is hydrophobic, attached to a polar head that is hydrophilic.
-To shield the hydrophobic tails from water, lipids self-assemble into micelles and bilayers. 
-A micelle is a spherical arrangement of lipids with tails terminating at the micelle center. 
-A bilayer consists of two layers of lipids called monolayers, where the lipid tails point 
-from the monolayer surface into the bilayer core.
-
-The mathematical modeling of a biological membrane is a challenging problem in applied mathematics. 
-Bilayers are elastic and resist deformations like bending, twisting, and stretching.
-Their elastic deformations are well described by the theory of liquid crystals \cite{ANDRIENKO2018520}.
-Lipid bilayer membranes can also be fluidic, and the lateral translation of lipids (or any membrane bound
-proteins) couples nonlocaly to the motion of the aqueous environment \cite{MerkelSackmannEvans1989,StoneAjdari1998_JFM,OppenheimerDiamant2009_BJ,OppenheimerDiamant2011_PRL}. 
-%Finally, the membranes of cellular 
-%compartments are constantly merging and pinching as part of intracellular trafficking. 
-%Therefore monolayer surfaces undergo discontinuous deformations.
-
-There are two prevailing approaches in membrane modeling, and each has its advantages
-and disadvantages. Molecular dynamics (MD) is to date the only tool capable of resolving granular biological details
-The computational cost of MD, however, grows with the sixth power of the sample diameter and 
-so simulations are severely limited to 
-small system sizes and short time scales \cite{DiCarlo2019}.
-The other approach, continuum mechanics, assumes smooth surfaces and can therefore model 
-realistic systems over physical times. 
-But continuum description of a biological membrane ignores the granularity of lipid molecules, and thus requires some assumptions when a
-membrane ruptures or when two membranes fuse \cite{ChKo08}. 
-%
-%mechanics presumes, rather than predicts, the nucleation of discontinuities. 
-%
-
-Recently the PIs developed a mathematical model called the 
-hydrophobic attraction potential (HAP) \cite{Fu2018_SIAM}.
-This model addresses the major shortcomings of MD and continuum approaches,
-and will hopefully offer an alternative modeling methodology that leads to new mathematical ideas 
-and is both physically accurate and computationally practical.
-
-The hydrophobic force arises when polar solvent molecules come in contact with a non-polar substance, such as hydrocarbon or vapor.
-In a polar solvent (like water), the dipole-dipole interaction between solvent molecules form a loosely structured hydrogen-bond network where
-each solvent molecule shares bonds with neighboring molecules at any given time 
-\cite{Israelachvili1954}. In the presence of  a non-polar solvent molecule loses the ability to form hydrogen bonds
-in one direction. 
-The decrease in the number of hydrogen bonds causes a reorientation, or structural
-change, in the surrounding water that is energetically very unfavorable \cite{Bjorneholm2016}.
+%The hydrophobic force arises when polar solvent molecules come in contact with a non-polar substance, such as hydrocarbon or vapor.
+%In a polar solvent (like water), the dipole-dipole interaction between solvent molecules form a loosely structured hydrogen-bond network where
+%each solvent molecule shares bonds with neighboring molecules at any given time 
+%\cite{Israelachvili1954}. In the presence of  a non-polar solvent molecule loses the ability to form hydrogen bonds
+%in one direction. 
+%The decrease in the number of hydrogen bonds causes a reorientation, or structural
+%change, in the surrounding water that is energetically very unfavorable \cite{Bjorneholm2016}.
 
 The substantial free energy for placing hydrophobic substances in contact with water 
-is roughly proportional to the surface area of the contact region. 
-As a result, hydrocarbon solutes have a large interfacial tension 
-and try to minimize their surface area when in water. 
-At the microscopic level, however, the hydrophobic force is a long-range, surface interaction. 
+is roughly proportional to the surface area of the contact region \cite{Bjorneholm2016}.  
+%As a result, hydrocarbon solutes have a large interfacial tension 
+%and try to minimize their surface area when in water. 
+At the microscopic level, the hydrophobic force is a long-range, surface interaction. 
 This means that two hydrophobic surfaces, separated by
@@
 
-As a summary of its mathematical properties,  the hydrophobic force
-is a non-additive, exponentially decaying surface force 
-that possesses a separation of length scales. These properties suggest 
-a boundary value problem formulation of the hydrophobic force.  
-The non-additivity of the hydrophobic force has to do with the fact that there is no superposition
-principle for including subdomains in boundary value problems. 
-The exponential decay is a property of a second order elliptic partial differential equation (PDE). 
-Finally, the separation of scales come from boundary layers, 
-where the energy of the boundary layer in the zero-thickness limit corresponds to macroscopic interfacial tension.
-Overlapping boundary layers correspond to microscopic hydrophobic attraction, 
-and the boundary layer thickness corresponds to the decay length of attraction.
-
-\begin{wrapfigure}[16]{l}{0.22\textwidth}
+\begin{wrapfigure}[16]{r}{0.22\textwidth}
 \centerline{\includegraphics[width=0.22\textwidth]{figures/BG_fig1.pdf}}
@@
 \end{wrapfigure}
+Recently PIs RR and YNY developed a mathematical model called the 
+hydrophobic attraction potential (HAP) \cite{Fu2018_SIAM}.
+This model addresses the major shortcomings of molecular dynamics (MD) and continuum approaches. Based on preliminary results (\S\ref{})
+the PIs propose to extend this HAP model to offer
+ an alternative modeling methodology that leads to new mathematical ideas,
+and is both physically accurate and computationally practical.
+%
+%
+%The word hydrophobic (water fearing) derives from the low solubility of oil (hydrocarbon solute) in water and vice versa. 
+%It causes hydrophobic moieties to aggregate and cluster,
+%is responsible for the adhesion between hydrophobic surfaces \cite{Ducker2016}, large contact angles on a 
+%dewetting surface \cite{Arenas2019,Sandre1999}, accumulation of particles along interfaces \cite{Lee2013,Lee2014}, 
+%formation of micelles and bilayers \cite{Israelachvili80}, and protein folding and membrane insertion \cite{Kabelka2018}.
+%
+%Lipids are amphiphilic molecules whose  structure possesses
+%both hydrophobic and hydrophilic parts. 
+%The amphiphilic property is what allows lipids to form the membranes and 
+%compartments of living cells \cite{Israelachvili80}. 
+%More specifically, a lipid consists of 
+%an elongated hydrocarbon tail that is hydrophobic, attached to a polar head that is hydrophilic.
+%To shield the hydrophobic tails from water, lipids self-assemble into micelles and bilayers. 
+%A micelle is a spherical arrangement of lipids with tails terminating at the micelle center. 
+%A bilayer consists of two layers of lipids called monolayers, where the lipid tails point 
+%from the monolayer surface into the bilayer core. 
+%
+%The mathematical modeling of a biological membrane is a challenging problem in applied mathematics. 
+%Bilayers are elastic and resist deformations like bending, twisting, and stretching.
+%Their elastic deformations are well described by the theory of liquid crystals \cite{ANDRIENKO2018520}.
+%Lipid bilayer membranes can also be fluidic, and the lateral translation of lipids (or any membrane bound
+%proteins) couples nonlocaly to the motion of the aqueous environment \cite{MerkelSackmannEvans1989,StoneAjdari1998_JFM,OppenheimerDiamant2009_BJ,OppenheimerDiamant2011_PRL}. 
+%%Finally, the membranes of cellular 
+%%compartments are constantly merging and pinching as part of intracellular trafficking. 
+%%Therefore monolayer surfaces undergo discontinuous deformations. 
+%
+%There are two prevailing approaches in membrane modeling, and each has its advantages
+%and disadvantages. Molecular dynamics (MD) is to date the only tool capable of resolving granular biological details
+%The computational cost of MD, however, grows with the sixth power of the sample diameter and 
+%so simulations are severely limited to 
+%small system sizes and short time scales \cite{DiCarlo2019}.
+%The other approach, continuum mechanics, assumes smooth surfaces and can therefore model 
+%realistic systems over physical times. 
+%But continuum description of a biological membrane ignores the granularity of lipid molecules, and thus requires some assumptions when a
+%membrane ruptures or when two membranes fuse \cite{ChKo08}. 
+%%
+%%mechanics presumes, rather than predicts, the nucleation of discontinuities. 
+%%
+%
+The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles.
+These results will facilitate optimal designs of smart materials of desirable properties by
+tuning the geometry and properties of the amphiphilic particles.
+
 \subsection{Hydrophobic Attraction Potential (HAP)}
@@
 Based on the physical origin of hydrophobicity,  we have devised a functional, called the hydrophobic attraction potential (HAP), to
-model hydrophobic forces \cite{Fu2018_SIAM}. The motivation for HAP concept stemmed from the lead PI's 
+model hydrophobic forces \cite{Fu2018_SIAM}. The motivation for HAP concept stemmed from PI RR's 
 earlier work on the problem of energy barriers in membrane fusion \cite{RyKlYaCo16,Chetal16}.
-There, the lead PI and collaborators resolved the long-standing issue of accounting for the energy of a fissure surface
+There, PI RR and collaborators resolved the long-standing issue of accounting for the energy of a fissure surface
 during topological transitions, by applying a squared gradient mathematical theory 
 for hydrophobic attraction between planar surfaces \cite{Eriksson1989,Lum1999,Menshikov2017,Marcelja1977} to monolayer fissures.
-Based on the PI Young's coarse-grained membrane modeling work \cite{Fu2017}, 
+Based on the PI YNY's coarse-grained membrane modeling work \cite{Fu2017}, 
 the investigators initiated a collaboration to create a gradient theory for arbitrary collections 
@@
 
-\section{Previous Results by the PIs}
-\label{sec:results}
-
-In our paper \cite{Fu2018_SIAM}, we developed the model (\ref{HAP}--\ref{SL})
-to quantify the macroscopic assembly and mechanics of a lipid bilayer membrane in solvents. 
-%We formulated the boundary value problem as a second-kind
-%integral equation (SKIE), presented in the Section (). 
-%The simulated fluid-particle systems exhibit a variety of multiscale behaviors over both time and length.
-%Over short time scales, the numerical results showed self-assembly for model lipid particles. 
-%For large system simulations, the particles formed realistic configurations like micelles and bilayers. 
-%Our collections showed that these amphiphilic particle bilayers  possessed mechanical properties of a 
-%lipid  bilayer  membrane  that  are  consistent  with other results in the literature.   
-To define the particle dynamics, we considered the exterior domain $\Omega$
+%As a summary of its mathematical properties,  the hydrophobic force
+%is a non-additive, exponentially decaying surface force 
+%that possesses a separation of length scales. These properties suggest 
+%a boundary value problem formulation of the hydrophobic force.  
+%The non-additivity of the hydrophobic force has to do with the fact that there is no superposition
+%principle for including subdomains in boundary value problems. 
+%The exponential decay is a property of a second order elliptic partial differential equation (PDE). 
+%Finally, the separation of scales come from boundary layers, 
+%where the energy of the boundary layer in the zero-thickness limit corresponds to macroscopic interfacial tension.
+%Overlapping boundary layers correspond to microscopic hydrophobic attraction, 
+%and the boundary layer thickness corresponds to the decay length of attraction.
+%
+%
+%\section{Previous Results by the PIs}
+%\label{sec:results}
+%
+%%In our paper \cite{Fu2018_SIAM}, 
+%PIs RR and YNY developed the HAP model (\ref{HAP}--\ref{SL})
+%to quantify the macroscopic assembly and mechanics of a lipid bilayer membrane in solvents \cite{Fu2018_SIAM}.
+%%We formulated the boundary value problem as a second-kind
+%%integral equation (SKIE), presented in the Section (). 
+%%The simulated fluid-particle systems exhibit a variety of multiscale behaviors over both time and length.
+%%Over short time scales, the numerical results showed self-assembly for model lipid particles. 
+%%For large system simulations, the particles formed realistic configurations like micelles and bilayers. 
+%%Our collections showed that these amphiphilic particle bilayers  possessed mechanical properties of a 
+%%lipid  bilayer  membrane  that  are  consistent  with other results in the literature.   
+To define the particle dynamics, consider the exterior domain $\Omega$
 for a finite number of disjoint, rigid and closed particles $P_1$, $P_2$, \dots, $P_n$, each with Lipschitz boundary,
@@
 
-The main analytical tool of our manuscript 
-is a formula for the first variation of $\Phi$ \cite{Bandle2015,Schiffer1954,Grinfeld2010}. 
-This first variation  is a symmetric, rank-two tensor called the hydrophobic stress:
+Taking the derivative of \eqref{HAP} with respect to particle configurations, and using the boundary value problem \eqref{SL}
+in a critical way,
+%leads to the surface term \eqref{stress}.  
+the first variation of the hydrophobic potential $\Phi$  
+yields a symmetric, rank-two tensor \cite{Bandle2015,Schiffer1954,Grinfeld2010} called the hydrophobic stress:
 \begin{equation}
@@
 \end{equation}
-To obtain \eqref{stress}, we observe that the potential $\Phi$ is a function of the particle position and orientations.
-This is because the particle configuration defines the shape of $\Omega$ and the boundary data $f.$ 
-Taking the derivative of \eqref{HAP} with respect to particle configurations, and using the boundary value problem \eqref{SL}
-in a critical way leads to the surface term \eqref{stress}.  
+%
+%To obtain \eqref{stress}, we observe that the potential $\Phi$ is a function of the particle position and orientations.
+%This is because the particle configuration defines the shape of $\Omega$ and the boundary data $f.$ 
+%Taking the derivative of \eqref{HAP} with respect to particle configurations, and using the boundary value problem \eqref{SL}
+%in a critical way leads to the surface term \eqref{stress}.  
+%
 By integrating the hydrophobic stress over the surface of particle $P_i,$ we obtaining the hydrophobic force and torque on each particle 
@@
 for creating functional materials \cite{Lee2014, Lee2013}. 
-This topic is the basis of Specific Aim 3 \todo[inline]{not true
-anymore}. Janus particles are typically
+%This topic is the basis of Specific Aim 3 \todo[inline]{not true anymore}. 
+Janus particles are typically
 spherical with a biphasic material label on either hemisphere,  endowing the particle
@@
 
-It is worth emphasizing that the model uses only a few parameters; interfacial tension, decay length, repulsion strength and particle
-shape. For example, an elastic modulus for stretching a vesicle derived from micropipette manipulation 
-directly calibrate our interfacial tension parameter. 
-MD simulators have also made measurements and lately there is better and better agreement with reality. 
-But even the simplest coarse grained models based on pair potentials for lipids has many more parameters \cite{Varilly2011,Wang2013} .
+It is worth emphasizing that the HAP model uses only a few parameters; interfacial tension, decay length, repulsion strength and particle
+shape. For example, an elastic modulus for stretching a vesicle from micropipette manipulation 
+directly calibrate our interfacial tension parameter. This is in direct contrast with pair-potential based approaches in
+MD simulations and coarse-grained models where many more parameters are required \cite{Varilly2011,Wang2013}.
+%MD simulators have also made measurements and lately there is better and better agreement with reality. 
+%But even the simplest coarse grained models based on pair potentials for lipids has many more parameters \cite{Varilly2011,Wang2013} .
 

### 2020-11-09 NSF2020/Description/preliminarywork.tex
yny

@@
 Over the past decades, researchers have used a number of mathematical tools 
-to model vesicles in shear flow, including  phase field \cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, 
+to simulate vesicles in a shear flow, including  lattice Boltzmann \cite{KaouiHartingMisbah2011_PRE}, coarse-grained Brownian dynamics \cite{NoguchiTakasu2002_BJ},
+phase field \cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, 
 level set \cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary integral \cite{Shravan09,Rahimian15} and 
-immersed boundary approaches \cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}. All these approaches
+immersed boundary approaches \cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}. Most of these approaches
 assume a mathematical surface, whether implicitly or explicitly, 
-and define an elastic bending energy of the surface. The vesicle obeys fluid
-transport and in turn the fluid balances shear stress with the vesicle's bending force.
+and define an elastic bending energy of the surface. 
+%The vesicle obeys fluid
+%transport and in turn the fluid balances shear stress with the vesicle's bending force.
 
@@
 To implement a vesicle in shear flow in the context of hydrophobic potentials and mobility problem, 
-we consider a shear flow $\mathbf{u}_{\infty} = Uy\mathbf{i}_x$ in the direction of the $x$-axis
+we consider a shear flow in the far-field $\mathbf{u}_{\infty} = Uy\mathbf{i}_x$ in the direction of the $x$-axis
 (Figure \ref{fig:tanktreading}A).
-This field satisfies the linear Stokes system but does not give rise to a rigid motion at the particle interfaces. 
-To have a rigid motion, we change variables $\mathbf{u} = \tilde{\mathbf{u}}+ \mathbf{u}_{\infty}$ and 
-for the new field $\tilde{\mathbf{u}}$ vanishing at infinity we let 
-$\tilde{\mathbf{u}}|_{\partial P_i} = \mathbf{v}_i + \boldsymbol{\omega}_i \times (\mathbf{x} - \mathbf{a}_i)$ 
-where $(\mathbf{v}_i,\boldsymbol{\omega}_i)$ are the unknown translation and angular velocities of the 
-$i$th particle $P_i.$
-
-\begin{wrapfigure}[17]{l}{0.4\textwidth}
-\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
-\caption{\label{fig:demixing} An initial assembly of small and 
-large particles spontaneous segregates into two smaller bodies. }
-\end{wrapfigure}
+%
+%This field satisfies the linear Stokes system but does not give rise to a rigid motion at the particle interfaces. 
+%To have a rigid motion, we change variables $\mathbf{u} = \tilde{\mathbf{u}}+ \mathbf{u}_{\infty}$ and 
+%for the new field $\tilde{\mathbf{u}}$ vanishing at infinity we let 
+%$\tilde{\mathbf{u}}|_{\partial P_i} = \mathbf{v}_i + \boldsymbol{\omega}_i \times (\mathbf{x} - \mathbf{a}_i)$ 
+%where $(\mathbf{v}_i,\boldsymbol{\omega}_i)$ are the unknown translation and angular velocities of the 
+%$i$th particle $P_i.$  
+%
+%\begin{wrapfigure}[17]{l}{0.4\textwidth}
+%\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
+%\caption{\label{fig:demixing} An initial assembly of small and 
+%large particles spontaneous segregates into two smaller bodies. }
+%\end{wrapfigure}
 The HAP simulations show vesicle tank-treading. Under the external shear flow, the initially circular 
@@
 and midplane respectively. In the non-dimensionalized system, the particles have diameter 2, on the order of $\rho,$ 
-and the vesicle diameter is about 14. \todo[inline]{missing units. nm?}
+and the vesicle diameter is about 14. 
+%\todo[inline]{missing units. nm?}
+%
+\begin{wrapfigure}[12]{r}{0.2\textwidth}
+\centerline{\includegraphics[width=0.2\textwidth]{figures/PW_fig5.pdf}}
+\caption{\label{fig:rupture} Rupture of tank-treading vesicle under strong shear flow.}
+\end{wrapfigure}
+%
 Figure~\ref{fig:tanktreading}E shows the aspect ratio of the major to minor axes reaching an equilibrium value in the 
@@
 
-\begin{wrapfigure}[12]{r}{0.2\textwidth}
-\centerline{\includegraphics[width=0.2\textwidth]{figures/PW_fig5.pdf}}
-\caption{\label{fig:rupture} Rupture of tank-treading vesicle under strong shear flow.}
-\end{wrapfigure}
+%\begin{wrapfigure}[12]{r}{0.2\textwidth}
+%\centerline{\includegraphics[width=0.2\textwidth]{figures/PW_fig5.pdf}}
+%\caption{\label{fig:rupture} Rupture of tank-treading vesicle under strong shear flow.}
+%\end{wrapfigure}
 There are a number of advantages to using our particle based approach.
@@
 and in-plane shear viscosities. 
+\begin{wrapfigure}[17]{l}{0.4\textwidth}
+\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
+\caption{\label{fig:demixing} An initial assembly of small and 
+large particles spontaneous segregates into two smaller bodies. }
+\end{wrapfigure}
+%
 
-The ability to form discontinuities is perhaps the HAP method's greatest 
-strength. Indeed, a strong, extensional shear flow must cause membrane rupture since the 
+The greatest strength of using HAP to model lipid bilayer membrane is the ability
+to form discontinuities (interfacial singularity) from first physical principle without any artificial manipulation to rearrangement the interface.
+%The ability to form discontinuities is perhaps the HAP method's greatest strength.
+ Indeed, a strong hear flow must cause membrane rupture since the 
 energy of stretching must exceed the pore nucleation and widening barriers 
@@
 boundary method  \cite{Hu,Hu13, KimLai2010_JCP}.
-PI Ryham and collaborators led in part the development of phase field
+PI RR and collaborators led in part the development of phase field
 functionals of membrane elastic energy and approaches to coupling membrane elasticity to fluids  \cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.

### 2020-11-09 NSF2020/Description/specificaim1_ver2.tex
yny

@@
 \label{sec:proposed-work}
-The proposed research develops fast,
-high-order-accurate, parallel numerical algorithms for large-scale
-simulations of the collective hydrodynamics of amphiphilic particles in a viscous solvent.
-%
+%The proposed research develops fast,
+%high-order-accurate, parallel numerical algorithms for large-scale
+%simulations of the collective hydrodynamics of amphiphilic particles in a viscous solvent.
+%%
 We have demonstrated that our hydrophobic attraction with repulsion potential (HARP) approach efficiently simulates
@@
 recreates the tank-treading phenomenon in external shear flows
-\cite{Fu20} \todo[inline]{!!let's put a proceedings here so we have something to cite!!}.
+\cite{Fu20}.
+%\todo[inline]{!!let's put a proceedings here so we have something to cite!!}.
 %
@@
 
-\subsection{Specific Aim 1: Collective elastic properties of amphiphilic particles}
+\subsection{Specific Aim 1: Material properties of self-assembly of amphiphiles}
 \label{subsec:specific_aim_1}
@@
 For amphiphiles assembled into bilayers, these properties are described by membrane continuum mechanics.
-The end-goal is to be able to map the parameters of the particle-based model onto the elastic moduli from continuum theory.
-If we achieve this goal, then simulators can use the hydrophobic attraction force calculations
+Our goal is to be able to map the parameters of the particle-based model onto the elastic moduli from continuum theory.
+Results from this goal will facilitate simulators to use the hydrophobic attraction force calculations
 to model bilayers with specific composition. These calculations have provably less computational complexity than

### 2020-11-09 NSF2020/Description/background.tex
rearranging sections

@@
 \noindent
-{\bf {Collaborative Research: Mathematical modeling and coarse-grained simulations of self-assembly of amphiphilic Janus particles in a solvent}}\\
-{\it Rolf Ryham (lead PI, Fordham University)}, {\it Bryan Quaife (PI, FSU) and Y.-N. Young (PI, NJIT)}
+{\bf Collaborative Research: Mathematical modeling and simulations of
+self-assembling amphiphilic particles in a solvent} \\
+%{\bf {Collaborative Research: Mathematical modeling and coarse-grained simulations of self-assembly of amphiphilic Janus particles in a solvent}}\\
+{\it Rolf Ryham (lead PI, Fordham University)}, {\it Bryan Quaife (PI,
+FSU), and Y.-N. Young (PI, NJIT)}
 \section{Background}
@@
 the HAP model has the capability and adaptivity to model phenomena across length scales and time scales.
+
+Over the past decades, researchers have used a number of mathematical tools 
+to simulate vesicles in a shear flow, including  lattice Boltzmann \cite{KaouiHartingMisbah2011_PRE}, coarse-grained Brownian dynamics \cite{NoguchiTakasu2002_BJ},
+phase field \cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, 
+level set \cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary integral \cite{Shravan09,Rahimian15} and 
+immersed boundary approaches \cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}. Most of these approaches
+assume a mathematical surface, whether implicitly or explicitly, 
+and define an elastic bending energy of the surface. 
+%The vesicle obeys fluid
+%transport and in turn the fluid balances shear stress with the vesicle's bending force.
+
+Our HAP approach differs from prior methods in a number of respects. 
+First, we do not assume a surface. Rather, we more fundamentally  consider a collection of amphiphilic particles.
+The collection of amphiphiles minimize hydrophobic interactions by sequestering hydrophobic tails in the form of a bilayer, and the particles' excess free energy gives rise to an elastic bilayer energy.
+The second difference lies in the fluid-interface coupling. Here, the associated mobility problem \eqref{eq:stokes} 
+is more complicated than dealing with a stress boundary condition or diffusive surface force, 
+because the fluid velocity must be that of a rigid body motion at the particle surfaces.
+
+\begin{wrapfigure}[17]{l}{0.4\textwidth}
+\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
+\caption{\label{fig:demixing} An initial assembly of small and 
+large particles spontaneous segregates into two smaller bodies. }
+\end{wrapfigure}
+The greatest strength of using HAP to model lipid bilayer membrane is the ability
+to form discontinuities (interfacial singularity) from first physical principle without any artificial manipulation to rearrangement the interface.
+%The ability to form discontinuities is perhaps the HAP method's greatest strength.
+ Indeed, a strong hear flow must cause membrane rupture since the 
+energy of stretching must exceed the pore nucleation and widening barriers 
+for sufficiently large flow strengths. 
+Some disadvantages are that the hydrophobic interaction does not constrain vesicle volume. 
+Instead, changes in volume are rate limited by inter-particle spacing,
+which may be undesirable in case of a mathematically strict volume constraint.
+% set vesicle volume, as is done in the study of liposomes
+%using auxiliary constraint equations for instance. 
+%Also, the boundary integral method formulation
+%relies on linearity of the Stokes equations. There has been some progress in
+%boundary integral methods for the non-linear Navier-Stokes equations [ref].
+%We point out that some non-Newtonian effects in polymers are a consequence of hydrophobic
+%and steric molecular interactions like the ones presented in this proposal.
+
+In recent years, researchers have developed a number of numerical methods for calculating
+energy minimizing steady equilibrium shapes of lipid bilayer membranes, vesicles and red blood cells.
+These approaches range from the finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, 
+phase field method \cite{Du05,QiangDu08,Lowengrub13} to immersed
+boundary method  \cite{Hu,Hu13, KimLai2010_JCP}.
+PI RR and collaborators led in part the development of phase field
+functionals of membrane elastic energy and approaches to coupling membrane elasticity to fluids  \cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.
+
 %

### 2020-11-09 NSF2020/Description/preliminarywork.tex
rearranging sections

@@
 %
-Over the past decades, researchers have used a number of mathematical tools 
-to simulate vesicles in a shear flow, including  lattice Boltzmann \cite{KaouiHartingMisbah2011_PRE}, coarse-grained Brownian dynamics \cite{NoguchiTakasu2002_BJ},
-phase field \cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, 
-level set \cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary integral \cite{Shravan09,Rahimian15} and 
-immersed boundary approaches \cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}. Most of these approaches
-assume a mathematical surface, whether implicitly or explicitly, 
-and define an elastic bending energy of the surface. 
-%The vesicle obeys fluid
-%transport and in turn the fluid balances shear stress with the vesicle's bending force.
-
-Our HAP approach differs from prior methods in a number of respects. 
-First, we do not assume a surface. Rather, we more fundamentally  consider a collection of amphiphilic particles.
-The collection of amphiphiles minimize hydrophobic interactions by sequestering hydrophobic tails in the form of a bilayer, and the particles' excess free energy gives rise to an elastic bilayer energy.
-The second difference lies in the fluid-interface coupling. Here, the associated mobility problem \eqref{eq:stokes} 
-is more complicated than dealing with a stress boundary condition or diffusive surface force, 
-because the fluid velocity must be that of a rigid body motion at the particle surfaces.
-
 To implement a vesicle in shear flow in the context of hydrophobic potentials and mobility problem, 
@@
 and in-plane shear viscosities. 
-\begin{wrapfigure}[17]{l}{0.4\textwidth}
-\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
-\caption{\label{fig:demixing} An initial assembly of small and 
-large particles spontaneous segregates into two smaller bodies. }
-\end{wrapfigure}
 %
-
-The greatest strength of using HAP to model lipid bilayer membrane is the ability
-to form discontinuities (interfacial singularity) from first physical principle without any artificial manipulation to rearrangement the interface.
-%The ability to form discontinuities is perhaps the HAP method's greatest strength.
- Indeed, a strong hear flow must cause membrane rupture since the 
-energy of stretching must exceed the pore nucleation and widening barriers 
-for sufficiently large flow strengths. 
-Some disadvantages are that the hydrophobic interaction does not constrain vesicle volume. 
-Instead, changes in volume are rate limited by inter-particle spacing,
-which may be undesirable in case of a mathematically strict volume constraint.
-% set vesicle volume, as is done in the study of liposomes
-%using auxiliary constraint equations for instance. 
-%Also, the boundary integral method formulation
-%relies on linearity of the Stokes equations. There has been some progress in
-%boundary integral methods for the non-linear Navier-Stokes equations [ref].
-%We point out that some non-Newtonian effects in polymers are a consequence of hydrophobic
-%and steric molecular interactions like the ones presented in this proposal.
-
-In recent years, researchers have developed a number of numerical methods for calculating
-energy minimizing steady equilibrium shapes of lipid bilayer membranes, vesicles and red blood cells.
-These approaches range from the finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, 
-phase field method \cite{Du05,QiangDu08,Lowengrub13} to immersed
-boundary method  \cite{Hu,Hu13, KimLai2010_JCP}.
-PI RR and collaborators led in part the development of phase field
-functionals of membrane elastic energy and approaches to coupling membrane elasticity to fluids  \cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.

### 2020-11-09 NSF2020/Description/specificaim1_ver2.tex
Update specificaim1_ver2.tex
Added steepest gradient descent to SA1

@@
 biological membranes are constantly in motion. Tracking the evolution of a bilayer is a more robust procedure that does not require minimality.
-Here we start with a particle bilayer in a non-equilibrium shape, and then evolve the particle bilayer according to steepest gradient descent with respect to the
-HARP functional. Gradient descent stabilizes the evolving bilayer shape and gives a monotonically decreasing energy. This gives a relatively large
+Here we start with a particle bilayer in a non-equilibrium shape, and then evolve the particle bilayer by steepest gradient descent with respect to the
+HARP functional:
+\begin{equation}
+\label{SGD}   
+\frac{\dif {\bf a}_i}{\dif t} = {\bf F}_i,    \quad  \frac{\dif {\bf R}_i}{\dif t}  = {\bf R}_i A({\bf w}_i),\quad i = 1, \dots, N.
+\end{equation}
+where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; 
+$A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
+Gradient descent stabilizes the evolving bilayer shape and gives a monotonically decreasing energy. This gives a relatively large
 data set of energy $E$ versus particle configuration. At the same time, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field $n$ by
@@
 When this occurs, the elastic moduli appear as the slope of the linear regression between $\Delta H$ and $\Delta E$.
+
+The evolution \eqref{SGD} satisfies the energy dissipation law $\frac{\dif }{\dif t} \Phi \leq 0$. We solve \eqref{SGD} numerically 
+using an Adams–Bashforth linear multistep method. The procedure involves solving \eqref{SL} based off of the current particle configuration.
+We then use the solution $u$ to calculate the collection of forces and torques \eqref{forceandtorque}, and update the particle configuration
+through \eqref{SGD}.
 

### 2020-11-09 NSF2020/Description/specificaim2_ver2.tex
Update specificaim2_ver2.tex
Still working at SA2

@@
 Specific Aim 1 dealt with the collective material property of amphiphiles which does not involve the movement of the solvent.
-In Specific Aim 2, we include hydrodynamics effects. Hydrodynamic effects are relevant
-because the rates of biological functions like fusion, fission, and pore dynamics rely on viscous dissipation \cite{RYHAM20112929},
-and can determine which local equilibria the system tends towards. 
+In Specific Aim 2, we include hydrodynamics effects by embedding the particles in solvent. 
+The fluid is modeled by the Stokes equations an incompressible, zero Reynolds-number fluid, and coupled to the screened-Laplace equation \eqref{SL}
+through the viscous and hydrophobic stress balance. We develope a numerical solver for the mobility problem. 
+This leads to simulations of bilayers in external flows where the bilayers are represented by a self-assebled collection of rigid particles. 
+Finally, we work toward three-dimensional solvers with application in the capillary driven fabrication of micro-materials.
+
+Hydrodynamic effects are relevant detail 
+because the rates of biological functions like fusion, fission, and pore dynamics rely on viscous dissipation \cite{RYHAM20112929}. 
+The hydrophobic attraction still causes the particles to self-assemble, but the trajectories and even configurations are changed
+by the fact that the particles must now move through an ambient environment. 
 Additionally, coarse-grained and molecular dynamics theories include water either explicitly or implicitly in their models.
 
-A further area of relevance is in the fabrication of complex microscopic three-dimensional structures \cite{Cho2010}.
-Over the past decade, there has been an explosion of interest in small-scale processes that utilize capillary forces dominate,  van der Waals interactions and thermal noise  \cite{Zhang2017},
-to coordinated movement and bind  material subunits. Two prominent fabrication techniques are capillary origami 
-\cite{Pandey2011,Leong2007,Reynolds2019} and colloidal self-assembly \cite{Dasgupta2017,Siontorou2017}.
-Capillary origami uses principles of elastocapilirity wherein elastic solids deform under surface tension \cite{Bico2018,VanHonschoten2010}.
-In self-assembly of colloids,
-particles exhibit similar thermodynamic behavior of molecular systems, except that the behavior occurs over observable, long time scales \cite{Zhang2017}.
-
 The hydrodynamic interactions enter through the transmission of viscous stresses from one particle to the another.  
-This involves solving the system
-
+We must solve the system 
 \setcounter{midequation}{\theequation}
@@
 generating the dissipation. When there is no background flow ${\bf u}_{\infty} = {\bf 0}$, the system obeys the energy law
-\begin{equation}
-\frac{\dif}{\dif t} \Phi + \int_{\Omega(t)} \mu |\nabla {\bf u} + \nabla {\bf u}^T|^2 \,dx = 0
-\end{equation}
+$\frac{\dif}{\dif t} \Phi + \int_{\Omega(t)} \mu |\nabla {\bf u} + \nabla {\bf u}^T|^2 \,dx = 0,$ 
 and the particle configurations tend toward a local equilibrium.
 
-A nonzero background flow continually injects energy into the system. We deal with the background flow using
-the Power and Miranda representation 
+We use \eqref{St1}--\eqref{HSB2} to simulate two-dimensional vesicle bilayer in external flows. 
+The vesicle bialyer is formed by a many-body  collection of amphiphilic particles. The inner, bilayer leaflet consists
+of particles pointing their hydrophobic tails away from the vesicle center; the tails of the outer leaflet point inward.
+We consider two kinds of external flows: shear flow and extensional flow. 
+Specifically, we deal with the background flow using the representation 
 \begin{equation}
@@
 
-We prove a, what to our knowledge is new, result concerning the evaluation of Maxwell-type stresses. 
+The background flows allow us to study further properties of amphiphilic particle collections. 
+Area conservation
+Volumne conservation
+Analyzing the dynamics compared to previous works
+Interaction between the fluid and membrane
+
+We prove a, to our knowledge new, result concerning the evaluation of Maxwell-type stresses. 
 \begin{proposition}
@@
 of  $u_i$ continuous across $\partial P_i$.
+
+Additionally, hydrodynamics interactions are also relevant the fabrication of complex microscopic three-dimensional structures \cite{Cho2010}.
+Over the past decade, there has been an explosion of interest in small-scale processes that utilize capillary forces dominate,  van der Waals interactions and thermal noise  \cite{Zhang2017}, to coordinated movement and bind  material subunits.
+Two prominent fabrication techniques are capillary origami
+\cite{Pandey2011,Leong2007,Reynolds2019} and colloidal self-assembly \cite{Dasgupta2017,Siontorou2017}.
+Capillary origami uses principles of elastocapilirity wherein elastic solids deform under surface tension \cite{Bico2018,VanHonschoten2010}.
+In self-assembly of colloids,
+particles exhibit similar thermodynamic behavior of molecular systems, except that the behavior occurs over observable, long time scales \cite{Zhang2017}. 
+and can determine which local equilibria the system tends towards.

### 2020-11-09 NSF2020/Description/broaderimpacts.tex

@@
 functional materials.
-
-\section{Relevant Results from Prior NSF Support}
-\noindent {\bf Rolf Ryham}: no prior NSF support.
-
-\noindent
-{\bf Yuan-Nan Young}: {\it NSF-DMS-1222550, Mathematical and experimental study of lipid bilayer 
-shape and dynamics mediated by surfactants and proteins}, \$212,603, 9/15/2012 - 08/31/2016 (with no-cost extension), PI. 
-{\it Intellectual merit:} The focus of this grant is modeling the interaction between a pure lipid bilayer membrane (LBM) with surfactant, cholesterol and protein.
-%Hence, there is no overlap between these grants and the current proposal.
-
-%YNY and collaborators have studied (1) asymmetry of lipid bilayer due to its interaction
-%with proteins and surfactants, (2) the electrohydrodynamics of a LBM under an
-%electric field, and (3) the coupling between LBM dynamics and a transmembrane protein,
-%such as a mechanosensitive channel.
-
-\noindent
-{\it Broader impacts:} 
-One PhD student (Szu-Pei Fu) was funded to work with YNY, and work has
-resulted in seven papers
-\cite{Nganguia2013_PoF,Nganguia2013_PRE,Young2014_JFM,Young2015_PoF,Nganguia2015_CiCP,Pak2015_PNAS,fu2015pre}.
-YNY has been actively involved with promotion of underrepresented
-students at NJIT.  The other PhD student (Herve Nganguia) is African.
-YNY has taught a broad spectrum of courses in fluid mechanics and
-applied math modeling.
-
-\noindent
-{\bf Bryan Quaife}: {\em NSF DMS-2012560, Erosion, Transport, and
-Dispersion in Granular and Porous Media}, \$249,636,
-08/01/2020--07/31/2023, PI. {\em Intellectual Merit:} The goal of this
-research is to develop high-order numerical methods to
-simulate hydrological processes including erosion.
-
-\noindent
-{\it Broader impacts:} 
-A second-year PhD student (Jake Cherry) has been assigned to this
-project. Since the funding just began, results have not yet
-been published or presented.
-
-\section{Project Management, Collaboration Plan, and Schedules of
-Research Tasks}
-\setlength{\parindent}{0pt}
-% N.B. wrapfigure is not compatible with \noindent.
-
-\begin{wrapfigure}{r}{0.56\textwidth}
-\definecolor{barblue}{RGB}{51,102,254}
-\renewcommand\sfdefault{phv}
-\renewcommand\mddefault{mc}
-\renewcommand\bfdefault{bc}
-\sffamily
-\begin{ganttchart}[
-    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
-        x unit =4.5mm,
-        y unit chart =\baselineskip,
-    hgrid style/.style={draw=black!5, line width=.75pt},
-    vgrid={*1{draw=black!5, line width=.75pt}},
-    title/.style={draw=none, fill=none},
-    title label font=\bfseries\footnotesize,
-    title label node/.append style={below=3pt},
-    include title in canvas=false,
-    bar label font=\mdseries\small\color{black!70},
-    %bar label node/.append style={left=2cm},
-    bar/.append style={draw=none, fill=barblue},
-    bar incomplete/.append style={fill=barblue},
-    bar progress label font=\mdseries\footnotesize\color{black!70},
-    milestone label font=\mdseries\small\color{black!70},
-        milestone left shift =0.9,
-        milestone right shift =0.1,
-        % Don't draw group bars
-        group height =0,
-        group peaks height =0,
-        group label font =\bfseries\small,
-]{1}{12}
-\gantttitle[
-    title label node/.append style={below left=3pt and -6pt}
-]{QUARTERS:\quad1}{1}
-\gantttitlelist{2,...,12}{1} \\
-\ganttgroup{Tasks\hfill}{1}{12}\\
-\ganttbar{Specific Aim 1}{1}{6}\\
-\ganttbar{Specific Aim 2}{1}{9}\\
-\ganttbar{Specific Aim 3}{5}{12}\\
-\ganttbar{Program management}{1}{12}\\
-\end{ganttchart}
-\caption{Schedule for the proposed work, measured in quarters from the
-  beginning of the project.}
-  \todo[inline]{Need to update Gantt table}
-\label{fig:schedule}
-\end{wrapfigure}
-\textbf{Project management}: 
-%
-The success of the proposed research requires complementary expertise
-and collaborative efforts in physics, applied mathematics, algorithms
-and computing.  Ryham has been working on mathematical modeling with a
-strong analytical background. Young has been working on many areas of
-computational fluid dynamics and applications to math biology for many
-years. Quaife has been working on integral equation methods, fast
-algorithms, and their applications to fluid dynamics for many years.
-Their recent collaborative work on the HAP model in two dimensions has
-provided a solid foundation on the proposed research.
-
-\medskip
-
-\textbf{Collaboration plan}: 
-%
-The management responsibility of this collaborative research will reside
-with the lead PI (Ryham) for this endeavor. The research work is
-structured to meet the tasks discussed in
-Section~\ref{sec:proposed-work}.
-%
-The PIs, their postdoc and students will meet frequently on Zoom and in
-person when possible. The PIs will share software packages, paper
-sources, and references on a common \textsf{Git} repository. The
-resulting software packages will be posted on the \textsf{Github}
-software repository.
-
-\medskip
-
-\textbf{Research Schedule:} The detailed schedule for the proposed work
-is shown in Fig.~\ref{fig:schedule}.

### 2020-11-09 NSF2020/Description/priorsupport.tex

\section{Relevant Results from Prior NSF Support}
\noindent {\bf Rolf Ryham}: no prior NSF support.

\noindent
{\bf Yuan-Nan Young}: {\it NSF-DMS-1222550, Mathematical and experimental study of lipid bilayer 
shape and dynamics mediated by surfactants and proteins}, \$212,603, 9/15/2012 - 08/31/2016 (with no-cost extension), PI. 
{\it Intellectual merit:} The focus of this grant is modeling the interaction between a pure lipid bilayer membrane (LBM) with surfactant, cholesterol and protein.
%Hence, there is no overlap between these grants and the current proposal.

%YNY and collaborators have studied (1) asymmetry of lipid bilayer due to its interaction
%with proteins and surfactants, (2) the electrohydrodynamics of a LBM under an
%electric field, and (3) the coupling between LBM dynamics and a transmembrane protein,
%such as a mechanosensitive channel.

\noindent
{\it Broader impacts:} 
One PhD student (Szu-Pei Fu) was funded to work with YNY, and work has
resulted in seven papers
\cite{Nganguia2013_PoF,Nganguia2013_PRE,Young2014_JFM,Young2015_PoF,Nganguia2015_CiCP,Pak2015_PNAS,fu2015pre}.
YNY has been actively involved with promotion of underrepresented
students at NJIT.  The other PhD student (Herve Nganguia) is African.
YNY has taught a broad spectrum of courses in fluid mechanics and
applied math modeling.

\noindent
{\bf Bryan Quaife}: {\em NSF DMS-2012560, Erosion, Transport, and
Dispersion in Granular and Porous Media}, \$249,636,
08/01/2020--07/31/2023, PI. {\em Intellectual Merit:} The goal of this
research is to develop high-order numerical methods to
simulate hydrological processes including erosion.

\noindent
{\it Broader impacts:} 
A second-year PhD student (Jake Cherry) has been assigned to this
project. Since the funding just began, results have not yet
been published or presented.

\section{Project Management, Collaboration Plan, and Schedules of
Research Tasks}
\setlength{\parindent}{0pt}
% N.B. wrapfigure is not compatible with \noindent.

\begin{wrapfigure}{r}{0.56\textwidth}
\definecolor{barblue}{RGB}{51,102,254}
\renewcommand\sfdefault{phv}
\renewcommand\mddefault{mc}
\renewcommand\bfdefault{bc}
\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize,
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\small\color{black!70},
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=barblue},
    bar incomplete/.append style={fill=barblue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar{Specific Aim 1}{1}{6}\\
\ganttbar{Specific Aim 2}{1}{9}\\
\ganttbar{Specific Aim 3}{5}{12}\\
\ganttbar{Program management}{1}{12}\\
\end{ganttchart}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project.}
  \todo[inline]{Need to update Gantt table}
\label{fig:schedule}
\end{wrapfigure}
\textbf{Project management}: 
%
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, algorithms
and computing.  Ryham has been working on mathematical modeling with a
strong analytical background. Young has been working on many areas of
computational fluid dynamics and applications to math biology for many
years. Quaife has been working on integral equation methods, fast
algorithms, and their applications to fluid dynamics for many years.
Their recent collaborative work on the HAP model in two dimensions has
provided a solid foundation on the proposed research.

\medskip

\textbf{Collaboration plan}: 
%
The management responsibility of this collaborative research will reside
with the lead PI (Ryham) for this endeavor. The research work is
structured to meet the tasks discussed in
Section~\ref{sec:proposed-work}.
%
The PIs, their postdoc and students will meet frequently on Zoom and in
person when possible. The PIs will share software packages, paper
sources, and references on a common \textsf{Git} repository. The
resulting software packages will be posted on the \textsf{Github}
software repository.

\medskip

\textbf{Research Schedule:} The detailed schedule for the proposed work
is shown in Fig.~\ref{fig:schedule}.

### 2020-11-09 NSF2020/Description/specificaim3_ver2.tex

@@
-\newpage
+%\newpage
 
@@
 \centerline{\includegraphics[width=3.0in]{figures/integrands}}
-\vspace*{-10pt}
+\vspace*{-13pt}
 \caption{{\footnotesize The Fourier modes of $K(x_0,y)$ and $K_2(x_0,y)$
@@
 A numerical issue when simulating the self-assembly of amphiphilic
-particles in a viscous solvent is the collision between the
-particles. The hydrophobic attraction potential drives the amphiphilic
-particles towards one another so to minimize exposure to the solvent,
-and this leads to physical contact in finite time. Such particle
-collisions in a dense rigid body suspension is a great challenge and can
-be a bottleneck in large-scale simulations. We propose two algorithms to
-remedy this computational challenge: high-order adaptive time stepping
-and repulsion forces.
+particles is avoiding particle collision. The hydrophobic attraction
+potential drives the amphiphilic particles towards one another so to
+minimize exposure to the solvent, and this leads to physical contact in
+finite time. Such particle collisions in a dense rigid body suspension
+is a great challenge and can be a bottleneck in large-scale simulations.
+We propose two algorithms to remedy this computational challenge:
+high-order adaptive time stepping and repulsion forces.
 
@@
 hydrodynamic suspensions~\cite{qua-bir2016} and it has served as a
-reliable method to simulate processes including mixing and adhesion in
+robust method to simulate processes including mixing and adhesion in
 suspensions~\cite{qua-vee-you2019, kab-qua-bir2017}. The method uses
@@
 cheap estimate of the error. The proposed work will use a spectral
-deferred correction method~\cite{dut-gre-rok2000} since it can
-iteratively apply a low-order method to achieve high-order accuracy. To
-estimate the error, we will compute the total force and torque of the
-system which is computationally cheap and physically zero. The PIs
-experience is that error estimates based on physical constraints such as
-force- and torque-free conditions appropriately adjust the time step
-size so that the dynamics are adequately resolved without the
-computational expense of strategies such as embedded Runge-Kutta
+deferred correction method~\cite{dut-gre-rok2000} since it iteratively
+applies a low-order single-step method to achieve high-order accuracy.
+To estimate the error, at each time step we will compute the total force
+and torque of the system which is computationally cheap and physically
+zero. The PIs' experience is that error estimates based on physical
+constraints such as force- and torque-free conditions appropriately
+adjust the time step size so that the dynamics are resolved without the
+computational expense of techniques such as embedded Runge-Kutta
 methods, step-doubling, and Richardson extrapolation.
@@
 Our previous work avoids contact by including a Leonard-Jones body
-forces~\cite{Fu2018_SIAM}. Such a steep steric interaction at short ranges
-introduces numerical stiffness and limits the time step size. To
+forces~\cite{Fu2018_SIAM}. Such a steep steric interaction at short
+ranges introduces numerical stiffness and limits the time step size. To
 remove this stiffness, we propose a geometry-based contact
@@
 contact are implemented, we will embark on incorporating fluctuating
-hydrodynamics~\cite{Bao17,Bao18} which are important even at scales of
-the some amphiphilic particles.
-
-\todo[inline]{Using DLP formulation for fluctuating hydrodynamics so
-that we have a second-kind BIE}
-%\textcolor{red}{
-%Once the collision-resolution algorithm is implemented, we will check
-%the computing performance first before we embark on incorporating
-%fluctuating hydrodynamics~\cite{Bao17,Bao18}, which might be important
-%even at the scales of the amphiphilic particle size in some cases. We
-%propose to extend the high-order time-integration scheme for a
-%stochastic differential equation~\cite{fu2015pre} to this system.
-%}
+hydrodynamics that are important even at scales of the some amphiphilic
+particles. Bao et al.~\cite{Bao17,Bao18} developed two-dimensional BIE
+formulations for Brownian rigid bodies. To satisfy the covariance of the
+rigid body velocities, an ill-conditioned first-kind integral equation
+method is used. The proposed work will consider a double-layer potential
+formulation that has much better conditioning properties. This strategy
+was attempted in~\cite{Bao18}, but they claim that a necessary
+regularization of the covariance matrix leads to a drastic loss of
+accuracy in numerical fluctuation-dissipation balance. However, they
+only one regularization strategy was considered, and as PI Quaife has
+shown in previous work, the regularization choice significantly affects
+the resulting physics~\cite{ong-chr-qua2017}. Therefore, different
+regularization strategies will be investigated with the goal of
+controlling the accuracy of the fluctuation-dissipation balance.

### 2020-11-09 NSF2020/Description/specificaim2_ver2.tex
RJR

@@
 \label{subsec:specific_aim_2}
-Specific Aim 1 dealt with the collective material property of amphiphiles which does not involve the movement of the solvent.
-In Specific Aim 2, we include hydrodynamics effects by embedding the particles in solvent. 
-The fluid is modeled by the Stokes equations an incompressible, zero Reynolds-number fluid, and coupled to the screened-Laplace equation \eqref{SL}
-through the viscous and hydrophobic stress balance. We develope a numerical solver for the mobility problem. 
+Specific Aim 1 dealt with elastic material properties of self-assembled collections of amphiphiles.
+In Specific Aim 2, we include hydrodynamics effects by embedding the particles in a solvent. 
+We divide space into the fluid phase and the rigid particle phase.
+The fluid phase is modeled by the Stokes equations for an incompressible, zero Reynolds-number fluid. These are coupled to the screened-Laplace equation \eqref{SL}
+through viscous and hydrophobic stress balance.
+We develope a numerical solver for the mobility problem. 
 This leads to simulations of bilayers in external flows where the bilayers are represented by a self-assebled collection of rigid particles. 
@@
 
-Hydrodynamic effects are relevant detail 
+Hydrodynamic effects are a relevant detail 
 because the rates of biological functions like fusion, fission, and pore dynamics rely on viscous dissipation \cite{RYHAM20112929}. 
-The hydrophobic attraction still causes the particles to self-assemble, but the trajectories and even configurations are changed
-by the fact that the particles must now move through an ambient environment. 
+While hydrophobic attraction causes the particles to self-assemble indepedently of the dissipation mechanism, the trajectories and
+equilibrium configurations depend on the fact that the particles travel through a viscous environment. 
 Additionally, coarse-grained and molecular dynamics theories include water either explicitly or implicitly in their models.
@@
 and material label respectively.
-
-Numerically solving \eqref{St1}--\eqref{HSB2} is a nontrivial matter.
-First, we have to carefully map the particle configurations because the domain $\Omega(t)$ and boundary conditions $f_i$ are constantly changing.
-The particle dynamics in \eqref{Hupdate1} and in \eqref{SGD} both involve solving
-screened Laplace boundary value problems on evolving domains, but differ in that \eqref{Hupdate1} has an additional Stokes flow
-generating the dissipation. When there is no background flow ${\bf u}_{\infty} = {\bf 0}$, the system obeys the energy law
+When there is no background flow ${\bf u}_{\infty} = {\bf 0}$, the system obeys the energy law
 $\frac{\dif}{\dif t} \Phi + \int_{\Omega(t)} \mu |\nabla {\bf u} + \nabla {\bf u}^T|^2 \,dx = 0,$ 
@@
 
-We use \eqref{St1}--\eqref{HSB2} to simulate two-dimensional vesicle bilayer in external flows. 
-The vesicle bialyer is formed by a many-body  collection of amphiphilic particles. The inner, bilayer leaflet consists
-of particles pointing their hydrophobic tails away from the vesicle center; the tails of the outer leaflet point inward.
+Numerically solving \eqref{St1}--\eqref{HSB2} is a nontrivial matter.
+The principle challenges are \textbf{(1)} the domain $\Omega(t)$ and boundary conditions $f_i$ are constantly changing
+with changes in the particle configuration \textbf{(2)} a high degree of spatial accuracy is required to resolve the fields 
+between adjacent particles and \textbf{(3)} the computational complexity grows with the number of particles. 
+Specific Aim 3 describes how we address these challenges.
+
+We simulate two-dimensional vesicle bilayers in external flows using \eqref{St1}--\eqref{HSB2}.
+The vesicle bilayer is formed by a many-body collection of amphiphilic particles. There are two leaflets: 
+the inner leaflet consisting of particles in contact and pointing their hydrophobic tails away from the vesicle interior;
+the particles in the outer leaflet are in contact with the surrounding fluid and point their tails inward.
+The particle laden flow changes the shape of the bilayer, and in return the hydrophobic stresses coming from the altered shape 
+impart a force on the flow. In other words, there is a two-way coupling between the flow and bilayer shape.
+
 We consider two kinds of external flows: shear flow and extensional flow. 

### 2020-11-10 NSF2020/Description/specificaim2_ver2.tex
RJR

@@
 
+\textbf{Model equations.}
 The hydrodynamic interactions enter through the transmission of viscous stresses from one particle to the another.  
@@
 \noindent for $i = 1,\dots, N$.
+The equations \eqref{St1}--\eqref{HSB2} express a two-way coupling between the flow and bilayer shape.
+The particle laden flow changes the shape of the bilayer, and in return the hydrophobic stresses coming
+from the altered shape impart a force on the flow. 
 The inputs to \eqref{St1}--\eqref{HSB2} are the collection of particle configurations.
@@
 
+\textbf{Simulation studies.}
 We simulate two-dimensional vesicle bilayers in external flows using \eqref{St1}--\eqref{HSB2}.
-The vesicle bilayer is formed by a many-body collection of amphiphilic particles. There are two leaflets: 
-the inner leaflet consisting of particles in contact and pointing their hydrophobic tails away from the vesicle interior;
-the particles in the outer leaflet are in contact with the surrounding fluid and point their tails inward.
-The particle laden flow changes the shape of the bilayer, and in return the hydrophobic stresses coming from the altered shape 
-impart a force on the flow. In other words, there is a two-way coupling between the flow and bilayer shape.
+The vesicle bilayer is formed by a many-body collection of amphiphilic particles.
+At large length scales and for large particle-number, the bilayer behaves as an elastic membrane,
+in two-dimensions an elastic curve. 
+This will lead to a deeper understanding of the elastic properties established by Specific Aim 2.
 
@@
 
-The background flows allow us to study further properties of amphiphilic particle collections. 
-Area conservation
-Volumne conservation
-Analyzing the dynamics compared to previous works
-Interaction between the fluid and membrane
+We will compare the behavior of our particle-based vesicles in Stokes flow to well-established results.
+To test area incompressibility, we form the bilayer midplane by fitting to the particle centers. Under moderate shear rates,
+the vesicle elongates and takes on an elliptical shape. We will study the increase in midplane area as a function of shear rate.
+Additionally, we will test for tangential divergence of velocity.
+Researchers have devised to model area incompressible and
+volume conserving membranes
+\cite{torres-sanchez_millan_arroyo_2019, mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}.
+Our preliminary results show that the particle-based bilayers have the same area modulus, about 60 \kBT,  as that of real lipid bilayer membranes,
+and so we expect realistic results from our flow simulations with regard to area incompressibility.  It is noteworthy that
+area incompressibility is some sense baked into the model through the hydrophobic attraction.
 
+Bilayer membranes have a small permeability to water \cite{323e9a2f0c58487ea82518d7a1f96485},
+and so modelers often assume a vesicle membrane that conserves volume. In our particle-based approach, water motion across
+the bilayer is limited by the size of the gaps between the particles, which is an artifact of coarse-graining.
+Making these gaps smaller comes at the expense of numerical accuracy, and so we will assess if there is a reasonable trade-off
+between approximate volume conservation and simulation complexity.
+
+Finally, the particle-based vesicle bilayers have two distinct leaflets.
+The inner and outer leaflets consists of the particles in contact with the vesicle interior and 
+surrounding fluid respectively. Since there the separation between these layers is roughly fixed,
+about 2 nm, certain fluid mechanical effects arise that are not present in zero-thickness membrane models. 
+An important effects we observe is that the leaflets slide against one another under shear flow. 
+This implies that part of the viscous dissipation in the aqueous phase is enhanced by intermonolayer friction
+\cite{SHKULIPA2005823, ShkulipaThesis}. We will characterize the intermonolayer
+slip as a function of shear rate, vesicle diameter and particle geometry.
+
+\textbf{Novel reciprocal relations.}
 We prove a, to our knowledge new, result concerning the evaluation of Maxwell-type stresses. 

### 2020-11-10 NSF2020/Description/preliminarywork.tex
rjr

@@
 \end{figure}
+\section{Preliminary work on elastic moduli}
+To derive a bending modulus, we first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
+Using a clamped condition at one end, the restoring force in the free part of the bilayer opposes the load.
+For small deformations, it is possible to solve the bilayer loading in closed form, and 
+this analytical solution (red curve) basically overlaps the midplane of the particle based solution (Figure \ref{fig:bend}A).
+We thereby derived a bending modulus $\KB$ in the range 8.51 -- 13.54 \kBT. Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.
+Experimental measurements have accurately determined the bending modulus for several lipid types, with 
+typical values lying around 10 \kBT\; \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}.
+
+We also considered the stretching and tilt deformations \cite{Fu2018_SIAM}. 
+Stretching occurs whenever there is an excess monolayer area,
+and it is energetically costly since it exposes hydrocarbon tails to water.
+To measure an area modulus, we stretched a circular vesicle, modeling the cross-section 
+of a bilayer tube (Figure \ref{fig:bend}B \& C).
+This procedure gave a monolayer area modulus 
+34 $\pm$ 2 \kBT \;nm$^{-2}$. Manipulation experiments give a monolayer area modulus in the range 
+30 -- 40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}.
+
+Finally, we considered the tilt deformation by applying a fixed tilt angle boundary condition. 
+This boundary condition produces a tilt field that decays with the length scale $l = \sqrt{\KB/\KTH}$ 
+Fitting to this field, our particle based simulation gave $\lambda = 1.2$ nm, which matches
+the value $\KTH \approx 10$ \kBT \; nm$^{-2}$ reported in the literature \cite{KUZMIN2005, KoNa15}.
+
+Our preliminary work is encouraging because in all cases, the bending, stretch, and tilt elastic moduli for the collection of amphiphiles
+were in excellent agreement with the experimental values. This fact is especially remarkable 
+since we assigned the main model parameters $\rho$ and $\gamma$ reasonable physical values, rather than using them as tuning parameter. 
+Nevertheless, the characterization of material properties is incomplete. For one, the preliminary simulations involved relatively low particle numbers (20 to 30), and so we still need to
+perform convergence studies with large particle-number systems to arrive at conclusive results. Secondly, we have yet to establish a functional
+relationship between the model parameters and elastic moduli. Finally, to have relevance in physics and biology
+we must incorporate the remaining twist and saddle splay deformations.
+The following simulation outline shows how will achieve aims.
+
 \section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow} 

### 2020-11-10 NSF2020/Description/specificaim1_ver2.tex
rjr

@@
 
-\subsection{Specific Aim 1: Material properties of self-assembly of amphiphiles}
+\subsection{Specific Aim 1: Measuring material properties of self-assembly of amphiphiles}
 \label{subsec:specific_aim_1}
@@
 
+\begin{figure}
+  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
+  \caption{
+    }
+\end{figure}
+
 The HK framework assumes a three-dimensional, internal structure for lipid monolayers.
@@
   \label{LMdeformation}
-x(X_1, X_2, X_3) = x_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) n(x_0(X_1, X_2))
+{\bf x}(X_1, X_2, X_3) = {\bf x}_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) {\bf n}(x_0(X_1, X_2))
 \end{equation}
 where $(X_1,X_2,X_3)$ are points in a reference volume.
-The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field $n$ parametrizes the
+The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field ${\bf n}$ parametrizes the
 direction of the lipid tails in the deformed state \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
@@
 
-The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for $x$. 
+The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for ${\bf x}$. 
 The chains stretch and compress to satisfy incompressibility.
@@
 This energy decomposes into four, fundamental and independent deformations:
-splay ($\Div n$), twist ($\Curl n$), saddle splay ($\det \nabla n$) and tilt $T$:
+splay ($\Div {\bf n}$), twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$) and tilt ${\bf t}$:
 \begin{equation}
@@
 \int_{\Sigma} 
-  \tfrac{1}{2}\KB\left[ \left( \Div n + k_0\right)^2 - k_0^2\right] 
-+ \tfrac{1}{2}\KT (\Curl n)^2 + \KG  \det \nabla n + \tfrac{1}{2}\KTH |T|^2 \,dA.
+  \tfrac{1}{2}\KB\left[ \left( \Div {\bf n} + k_0\right)^2 - k_0^2\right] 
++ \tfrac{1}{2}\KT (\Curl {\bf n})^2 + \KG  \det \nabla {\bf n} + \tfrac{1}{2}\KTH |{\bf t}|^2 \,dA.
 \end{aligned}
 \end{equation}
-Here $\Div n$, $\Curl n$ and $\nabla n$ refer to the surface divergence, surface curl and surface gradient operators
+Here, $(\nabla {\bf n})_{ij} = \partial_{x_j}{\bf n} \cdot {\bf e}_i$ is the surface gradient with
+orthonormal tangent vectors $\{{\bf e}_1, {\bf e}_2\}$.
+\todo[inline]{YNY and BQ: What do you call a coordinate system where the metric is the identity at one point?}
+Also, the surface divergence 
+$\Div {\bf n}$ is the trace, and the surface curl $\Curl {\bf n}$ is the anti-trace (sum of the off-diagonal elements), of $\nabla {\bf n}$ respectively.
 respectively (Figure \ref{fig:distortions}A--C).
@@
 and saddle-splay modulus $\KG$ and tilt modulus $\KTH$
-HK define the tilt vector $T = n/(N\cdot n) - N$ where $N$ is the unit surface normal.
+HK define the tilt vector ${\bf t} = {\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal.
 
@@
 and these lipids would line the  inner monolayer of a 
-spherical liposome, because the addition of a positive splay $\Div \mathbf{d}$  in \eqref{ansatz3}
+spherical liposome, because the addition of a positive splay $\Div \mathbf{n}$  in \eqref{ansatz3}
 to the negative spontaneous curvature $k_0$ leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
@@
 
-An interesting and challenging feature of \eqref{ansatz3} is that the
-elastic energy couples director gradients to surface geometry through
-the tilt vector field.  In biological contexts, bilayer energy is the
-sum monolayer energies, and tilt appears at lipid domain boundaries, the
-edge of nanopores and at the boundary of membrane inclusions
-\cite{PhysRevE.102.042406}.  Under spatial scales much larger than the
+Under spatial scales much larger than the
 membrane thickness, membrane energy is well-characterized by the
@@
 \cite{QiangDu09, Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP,
-qua-bir2014, qua-vee-you2019}. \todo[inline]{YNY: place your recent
-works here} The Canham-Helfrich energy is actually a special case of
-\eqref{ansatz3} obtained by setting $n =  \pm N$ (the $\pm$ depending on
+  qua-bir2014, qua-vee-you2019}.
+\todo[inline]{YNY: place your recent works here}
+The Canham-Helfrich energy is actually a special case of
+\eqref{ansatz3} obtained by setting ${\bf n} =  \pm {\bf N}$ (the $\pm$ depending on
 orientation) and collapsing both monolayers onto the membrane midplane.
@@
 %\end{center}
-\subsubsection{Preliminary results}
-Our preliminary tested for elastic properties by subjecting bilayers to external loads \cite{Fu2018_SIAM}.
-We used realistic values for the phospholipid length $a$ \cite{Boal},
-screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
-and interfacial tension $\gamma=4.1$ pN nm$^{-1}$ \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
-model parameters.
-The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
-particle diameter and the hydrophobic boundary condition \eqref{SL}
-are additional parameters defining the coarse-grained representation.
-
-To derive a bending modulus, we first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
-Using a clamped condition at one end, the restoring force in the free part of the bilayer opposes the load.
-For small deformations, it is possible to solve the bilayer loading in closed form, and 
-this analytical solution (red curve) basically overlaps the midplane of the particle based solution (Figure \ref{fig:bend}A).
-We thereby derived a bending modulus $\KB$ in the range 8.51 -- 13.54 \kBT. Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.
-Experimental measurements have accurately determined the bending modulus for several lipid types, with 
-typical values lying around 10 \kBT\; \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}.
-
-We also considered the stretching and tilt deformations \cite{Fu2018_SIAM}. 
-Stretching occurs whenever there is an excess monolayer area,
-and it is energetically costly since it exposes hydrocarbon tails to water.
-To measure an area modulus, we stretched a circular vesicle, modeling the cross-section 
-of a bilayer tube (Figure \ref{fig:bend}B \& C).
-This procedure gave a monolayer area modulus 
-34 $\pm$ 2 \kBT \;nm$^{-2}$. Manipulation experiments give a monolayer area modulus in the range 
-30 -- 40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}.
-
-Finally, we considered the tilt deformation by applying a fixed tilt angle boundary condition. 
-This boundary condition produces a tilt field that decays with the length scale $l = \sqrt{\KB/\KTH}$ 
-Fitting to this field, our particle based simulation gave $\lambda = 1.2$ nm, which matches
-the value $\KTH \approx 10$ \kBT \; nm$^{-2}$ reported in the literature \cite{KUZMIN2005, KoNa15}.
-
-Our preliminary work is encouraging because in all cases, the bending, stretch, and tilt elastic moduli for the collection of amphiphiles
-were in excellent agreement with the experimental values. This fact is especially remarkable 
-since we assigned the main model parameters $\rho$ and $\gamma$ reasonable physical values, rather than using them as tuning parameter. 
-Nevertheless, the characterization of material properties is incomplete. For one, the preliminary simulations involved relatively low particle numbers (20 to 30), and so we still need to
-perform convergence studies with large particle-number systems to arrive at conclusive results. Secondly, we have yet to establish a functional
-relationship between the model parameters and elastic moduli. Finally, to have relevance in physics and biology
-we must incorporate the remaining twist and saddle splay deformations.
-The following simulation outline shows how will achieve aims.
 
@@
 a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
-The comparison enables us to understand how the model parameters map onto elastic parameters.
+The specific goals are {\bf (i)} to assess whether the energies \eqref{ansatz3} are the same
+for all reasonable deformation and if this is the case {\bf (ii)} to determine the value of the elastic $\KB$,
+$\KT$, $\KG$ and $\KTH$; {\bf (iii)} us to understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli.
 
-In the preliminary work, bilayer shapes minimized energy with respect to an external force. Energy minimality is somewhat unrealistic because
-biological membranes are constantly in motion. Tracking the evolution of a bilayer is a more robust procedure that does not require minimality.
-Here we start with a particle bilayer in a non-equilibrium shape, and then evolve the particle bilayer by steepest gradient descent with respect to the
+Motivated by our preliminary results \cite{Fu2018_SIAM}
+we use realistic values for particle diameter $2$ nm \cite{Boal},
+screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
+and interfacial tension $\gamma=4.1$ pN nm$^{-1}$ \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
+model parameters. The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
+particle diameter and the hydrophobic boundary condition \eqref{SL}
+are additional parameters defining the coarse-grained representation.
+
+An accurate and robust way to measure material properties is to track the evolution of the bilayer. 
+Here we start with a particle-based bilayer in a non-equilibrium shape, and then evolve the particle bilayer by steepest gradient descent with respect to the
 HARP functional:
@@
 $A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
-Gradient descent stabilizes the evolving bilayer shape and gives a monotonically decreasing energy. This gives a relatively large
-data set of energy $E$ versus particle configuration. At the same time, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field $n$ by
-interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $H$ from the interpolated
-bilayer shape. Setting $\Delta E = E - E_0$ and $\Delta H = H - H_0$ normalizes the energies to their respective equilibrium values $E_0$ and $H_0$.
-In certain instances, the bilayer evolution involves only one of the four fundamental deformations.
-When this occurs, the elastic moduli appear as the slope of the linear regression between $\Delta H$ and $\Delta E$.
-
-The evolution \eqref{SGD} satisfies the energy dissipation law $\frac{\dif }{\dif t} \Phi \leq 0$. We solve \eqref{SGD} numerically 
+We solve \eqref{SGD} numerically 
 using an Adams–Bashforth linear multistep method. The procedure involves solving \eqref{SL} based off of the current particle configuration.
@@
 
-Bending is the energetically most consequential deformations,
-and so we revisit estimating the bending modulus parameter. 
-In the case of the bending deformation, we deform the midplane of a planar bilayer into the shape of a circular arc.
-This arc stores bending energy in the form of splay $\Div{n}$, while twist, saddle-splay and tilt deformations are zero.
+The evolution \eqref{SGD} satisfies the energy dissipation law $\frac{\dif }{\dif t} \Phi \leq 0$
+and this stabilizes the evolving bilayer shape.
+Therefore, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field ${\bf n}$ by
+interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $E$ from the interpolated shapes.
+
+In certain instances, the bilayer evolution involves only one or a few of the four fundamental deformations.
+When this occurs, the elastic moduli derive from the coefficients of the linear regression between the HAP energy $\Delta \Phi = \Phi - \Phi_0$
+and continuum energies and $\Delta E = E - E_0$, where  $\Phi_0$ and $E_0$ are respective equilibrium values.
+
+Since it is a particle-based method, the HAP model has a number of advantages over continuum-based descriptions.
+The elastic energy \eqref{ansatz3} couples director gradients to surface geometry through
+the tilt vector field.  Furthermore, bilayer energy is the sum of two monolayer
+energies and the distance between these monolayers varies according to \eqref{LMdeformation}.
+Effects like tilt and varying monolayer thickness appear at lipid domain boundaries, the edge of nanopores and at the boundary of membrane inclusions \cite{PhysRevE.102.042406}.
+These effects are present in the proposed formulation, and the particle-based bilayers can break open and join monolayer-wise 
+as required by fussion and fission.
+
+Bending is the energetically most consequential deformations. To measure a bending modulus,  
+we deform the midplane of a planar bilayer into the shape of a circular arc.
+This arc stores bending energy in the form of splay $\Div {\bf n}$, while twist, saddle-splay and tilt deformations are zero.
 The splay in the two leaflets approximately cancel when added, making the contribution of spontaneous curvature negligible.
-Since $\Div{n} = -\kappa$ in this setup, we can compute the curvature squared curvature energy 
-$H = \int_C \kappa^2$ of the cross-section $C$, a simple closed curve. Figure \ref{} shows the approximately linear
-relationship between $\Delta E$ and $\Delta H$ with $\KB$ as the slope.
+In the case of a rectangular bialyer, the corresponding elastic energy 
+$E = \int_{\Sigma} \KB \kappa^2$ where $\kappa$ is the curvature of the curved cross-section $C$.
+Figure \ref{} shows the approximately linear relationship between $\Delta \Phi$ and $\Delta E$
+used to values for infer $\KB$.
 
@@
 (Specific Aim 3 address outstanding implementation issues like three-dimensional boundary integral solvers.) 
-The twist deformation is closely related to the assumption of lateral fluidity in membranes and so researchers 
-have sometimes assumed $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}, 
-while molecular dynamics investigations find a twist modulus in the range of 1 to 2 
-\kBT \cite{LeVeWa14}.
-To measure the elastic response,  we initially twist the bilayer along an $x_1$-coordinate axis.
-In this configuration, the directors behave at leading order as $n = (0, mx_1, \sqrt{1 - m^2x_1^2})$,
-yielding a surface gradient $\nabla n = \begin{pmatrix}0 & 0\\ m & 0\end{pmatrix}$. 
-Here $\Div n = \mathrm{tr}(\nabla n) = 0$, $\det(\nabla n) = 0$ and $\Curl d = (\nabla u)_{12} - (\nabla u)_{21} = m$,
-so that the continuum elastic energy equals $\tfrac{1}{2}\KT m^2 A + O(1)$ for a membrane area $A \gg 1$. (Our particle collections
-conserve membrane area, unless they lie in a strong background flow.) 
-This enables us to plot the HARP energy values derived from steepest gradient descent as a function of $m$, and finally
-yields a value for $\KA$.
+It is closely related to the assumption of lateral fluidity in membranes \cite{Hamm2000}. Note that tilt is locally non-zero whenever twist is non-zero.
+That is because the surface gradient $\nabla {\bf n}$ equals the second fundamental form, and is therefore symmetric, whenever ${\bf n} = {\bf N}$ locally.
+
+To measure the twise modulus, we place a single monolayer on a hydrophobic substrate 
+and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
+yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
+  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
+  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
+  This gives the continuum elastic energy equals
+  \begin{equation}
+    \label{eq:twist_energy}
+    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
+  \end{equation}
+  which we compare to the HAP simulation data.
 
 We will also determine the effective saddle splay modulus $\KG$. 
-Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
-\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
-barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}. 
-The field requires further theoretical work like the what we are proposing to more precisely account for saddle splay.
-
 The gradient descent technique is ineffective for measuring $\KG$ because
@@
 
+\subsubsection{New mathematical analysis}
+ It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
+ whether \eqref{ansatz3} contains a complete list of consistent deformations.
+\textbf{(i)} Researcher have assumed that $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}.
+  Based on \eqref{eq:twist_energy}, a value $\KT = 0$ leads to the
+  unphysical conclusion that there are bilayers with $\nabla {\bf n} \to \infty$ but $E \to 0.$ 
+  \textbf{(ii)}
+  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
+  Later, \cite{C9SM02079A} 
+  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
+  from a transversal tilt invariance assumption.
+  The PI Ryham showed,  that the tilt vector $T = {\bf n}/{\bf n}\cdot {\bf N} - {\bf N}$ leads to unphysical cusps when constraining membrane thickness  \cite{RyKlYaCo16}.  
+  \textbf{(iii)}
+  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
+\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
+barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
+Furthermore, the stability requirements of \eqref{ansatz3} are $\KB > 0$, $K_T > 0$, $\KG \geq -4\KB$
+and $\KG \geq -4\KT$. Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14},
+suggesting a somewhat smaller magnitude for $\KG$.
+
 The form of the elastic energy density \eqref{ansatz3} is the same as
@@
 
- It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
-  whether \eqref{ansatz3} contains a complete list of consistent deformations.
-  The PI Ryham showed, for example, that the tilt vector $T = n/n\cdot N - N$ leads to unphysical cusps when constraining membrane thickness
- \cite{RyKlYaCo16}.
-  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
-  Later, \cite{C9SM02079A} 
-  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
-  from a transversal tilt invariance assumption.
-
   We suspect the reason why, after twenty years, the field has yet to reach a consensus 
-  has to do with the Taylor expansions used to derive the elastic energy density. 
+  as to the form of \eqref{ansatz3} has to do with the Taylor expansions used to derive the elastic energy density. 
   Past researchers expressed the strain tensor in
-  terms of the coordinate frame $\{e_1, e_2, N\}$ with surface tangent vectors $e_i$ and surface normal $N$.  
-  In this frame, there is a coupling between the gradients of all three terms $x_0,$ $\zeta$ and $n$ of the deformation \eqref{LMdeformation}.
-  The recent paper \cite{PhysRevE.102.042406} contains an energy density with more than ten elastic parameters, for example.
-  Subtle differential geometric arguments are needed to evaluate the terms in the Taylor expansion.
+  terms of the orthonormal frame $\{{\bf e}_1, {\bf e}_2, {\bf N}\}$ with surface tangent vectors ${\bf e}_i$ and surface normal ${\bf N}$.  
+  In this frame, there is a coupling between the gradients of all three terms ${\bf x}_0,$ $\zeta$ and ${\bf n}$ of the deformation \eqref{LMdeformation}.
+  Subtle differential geometric arguments are needed to evaluate the terms in the Taylor expansion,
+  and these couplings can lead to an energy density with more than ten parameters, for example \cite{PhysRevE.102.042406}.
 
@@
   As a main analytical innovation, we have found that expanding the strain tensor in
-  terms of the coordinate frame $\{e'_1, e'_2, n\}$ with $e'_i$ perpendicular to $n$
+  terms of the orthonormal frame $\{{\bf e}'_1, {\bf e}'_2, n\}$ with ${\bf e}'_i$ perpendicular to ${\bf n}$
   greatly simplifies the expansion because it decouples the gradient terms. As an illustration, the prominent works
@@
   incompressility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
-  However, when expressed in the $\{e'_1, e'_2, n\}$ coordinate frame, the incompressility condition is exact
-  and is given by a Steiner-type polynomial in terms of $\Div n$ and $\det \nabla n$ \cite{Fe59}.
+  However, we prove that when expressed in the $\{{\bf e}'_1, {\bf e}'_2, n\}$ frame, the incompressility condition is \emph{exact}
+  and is given by a Steiner-type polynomial in terms of $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
   Aside from the special case of zero tilt, \cite{Hamm2000} and coworkers seem to have been unaware of this result.
@@
 We have shown that hydrophic attraction is a non-additive force, meaning the force of attraction between two
-particles is dependent on the position a third or more particles. Conceptually, this would arise in continuum theory if two monolayer surfaces
+particles is dependent on the position a third or more particles \cite{SilveraBatista1242477}.
+Conceptually, this would arise in continuum theory if two monolayer surfaces
 had a different elastic energy density despite having locally identical curvatures and directors.

### 2020-11-10 NSF2020/Description/specificaim2_ver2.tex
rjr

@@
 
-Finally, the particle-based vesicle bilayers have two distinct leaflets.
+\begin{wrapfigure}[16]{r}{0.32\textwidth}
+\centerline{\includegraphics[width=0.32\textwidth]{figures/BIError.pdf}}
+\caption{
+\label{fig:bierror}  
+  Gradient error between an exact and boundary integral solution of \eqref{SL}.
+}
+\end{wrapfigure}Finally, the particle-based vesicle bilayers have two distinct leaflets.
 The inner and outer leaflets consists of the particles in contact with the vesicle interior and 
@@
   \begin{equation}
+    \label{eq:reciprocal}
 {\bf F}_i = \sum_{j \neq i} \int_{\partial P_i}[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
@@
 As described in Specific Aim 3, we solve \eqref{SL1}--\eqref{SL3}  using a double layer potential representation.
-While accurate in the far-field, this representation involves a strongly singular integral which
-leads to large numerical errors when evaluating the the hydrophobic stress \eqref{stress} along the particle boundaries.
-The identity in Proposition \ref{prop:recip} gets around this critical problem by utilizing the fact that $u_j$, $j\neq i$ is smooth and the normal derivative
-of  $u_i$ continuous across $\partial P_i$.
+This representation involves a strongly singular integral, and without the aid of specilized
+quadrature routines, leads to large numerical errors when evaluating the the hydrophobic stress \eqref{stress} along the particle boundaries (see Figure \cite{fig:bierror}).
+The identity in Proposition \ref{prop:recip} gets around this critical issue by utilizing the fact that $u_j$, $j\neq i$ is smooth and the normal derivative
+of  $u_i$ continuous across $\partial P_i$. Despite the large gradient errors in Figure \ref{fig:bierror}, the force and torque
+calculated by \eqref{eq:reciprocal} achieved $10^{-4}$ accuracy.
 

### 2020-11-10 NSF2020/Description/specificaim1_ver2.tex
rjr

@@
   \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
-  \caption{
+  \caption{\label{fig:deformations}
     }
@@
 
+\begin{wrapfigure}[16]{r}{0.32\textwidth}
+\centerline{\includegraphics[width=0.32\textwidth]{Figures/SaddleSplayDiagram.pdf}}
+\caption{
+\label{fig:saddle_splay}  
+ TBD
+}
+\end{wrapfigure}
 To evaluate $\KG$, we will combine the string method from PI-Ryham's work on fusion \cite{RyKlYaCo16} with
@@
 
-We will also analyze $\KG$ using a helical geometry. In a helicoid with inclination $m$, the director
-gradient is $\nabla n = \begin{pmatrix} 0 & m(m^2+x_1^2)^{-1} \\ m(m^2+x_1^2)^{-1} & 0\end{pmatrix}$ where $x_1$ is the distance to the central
-axis. We observe that saddle splay, twist and tilt are zeros, and $\det \nabla n = m^2(m^2+x_1^2)^{-2}$.
-In the simulations, the particles forming the helicoid will be confined to two, concentric cylinders. The
-continuum energy $\tfrac{1}{2}\KG h(m x_1(m^2+x_1^2)^{-1} + \tan^{-1}(x_1/m)) |_{r_1}^{r_2}$ where $h$, $r_1$ and $r_2$
-are the cylinder heights, inner cylinder radius, and outer cylinder radius, respectively.
+%We will also analyze $\KG$ using a helical geometry. In a helicoid with inclination $m$, the director
+%gradient is $\nabla n = \begin{pmatrix} 0 & m(m^2+x_1^2)^{-1} \\ m(m^2+x_1^2)^{-1} & 0\end{pmatrix}$ where $x_1$ is the distance to the central
+%axis. We observe that saddle splay, twist and tilt are zeros, and $\det \nabla n = m^2(m^2+x_1^2)^{-2}$.
+%In the simulations, the particles forming the helicoid will be confined to two, concentric cylinders. The
+%continuum energy $\tfrac{1}{2}\KG h(m x_1(m^2+x_1^2)^{-1} + \tan^{-1}(x_1/m)) |_{r_1}^{r_2}$ where $h$, $r_1$ and $r_2$
+%are the cylinder heights, inner cylinder radius, and outer cylinder radius, respectively.
 

### 2020-11-10 NSF2020/Description/background.tex
yny

@@
 hydrophobic attraction potential (HAP) \cite{Fu2018_SIAM}.
-This model addresses the major shortcomings of molecular dynamics (MD) and continuum approaches. Based on preliminary results (\S\ref{})
+This model addresses the major shortcomings of molecular dynamics (MD) and continuum approaches. Based on preliminary results (\S\ref{sec:preliminary_work})
 the PIs propose to extend this HAP model to offer
@@
 for hydrophobic attraction between planar surfaces \cite{Eriksson1989,Lum1999,Menshikov2017,Marcelja1977} to monolayer fissures.
-Based on the PI YNY's coarse-grained membrane modeling work \cite{Fu2017}, 
+Based on PI RR and YNY's coarse-grained membrane modeling work \cite{Fu2017}, 
 the investigators initiated a collaboration to create a gradient theory for arbitrary collections 
@@
 because the fluid velocity must be that of a rigid body motion at the particle surfaces.
-
+%
 \begin{wrapfigure}[17]{l}{0.4\textwidth}
@@
 %The ability to form discontinuities is perhaps the HAP method's greatest strength.
- Indeed, a strong hear flow must cause membrane rupture since the 
-energy of stretching must exceed the pore nucleation and widening barriers 
-for sufficiently large flow strengths. 
-Some disadvantages are that the hydrophobic interaction does not constrain vesicle volume. 
-Instead, changes in volume are rate limited by inter-particle spacing,
-which may be undesirable in case of a mathematically strict volume constraint.
-% set vesicle volume, as is done in the study of liposomes
-%using auxiliary constraint equations for instance. 
-%Also, the boundary integral method formulation
-%relies on linearity of the Stokes equations. There has been some progress in
-%boundary integral methods for the non-linear Navier-Stokes equations [ref].
-%We point out that some non-Newtonian effects in polymers are a consequence of hydrophobic
-%and steric molecular interactions like the ones presented in this proposal.
+For example, using the HAP model to simulate a vesicle under a shear flow that is strong enough to cause the vesicle membrane to rupture, 
+we expect the HAP model to capture the reorganization of lipid molecules on the scales of membrane thickness ($\sim 5$ nm), which is a nearly impossible
+task using phase-field or immerse boundary method without extreme refinement around the membrane and artificial treatment of reconnection during the topological change of an interface.
+
+%Some disadvantages are that the hydrophobic interaction does not constrain vesicle volume. 
+%Instead, changes in volume are rate limited by inter-particle spacing,
+%which may be undesirable in case of a mathematically strict volume constraint.
+%% set vesicle volume, as is done in the study of liposomes
+%%using auxiliary constraint equations for instance. 
+%%Also, the boundary integral method formulation
+%%relies on linearity of the Stokes equations. There has been some progress in
+%%boundary integral methods for the non-linear Navier-Stokes equations [ref].
+%%We point out that some non-Newtonian effects in polymers are a consequence of hydrophobic
+%%and steric molecular interactions like the ones presented in this proposal.
 

### 2020-11-10 NSF2020/Description/broaderimpacts.tex
yny

@@
 transformative understanding of the collective dynamics of amphiphilic
-particles such as (1) their self-assembly into micelles and bilayers,
-and (2) the interaction between these building blocks. Amphiphilic Janus
+particles such as (1) their self-assembly into micelles and bilayers, (2) the material properties of such self-assembly, 
+and (3) the interaction between these building blocks. Amphiphilic Janus
 particles have gained increasing popularity for fabrication of smart
@@
 computation. We will incorporate research into teaching, especially in
-differential equation and programming courses. PI Quaife will expose
+differential equation and programming courses. PI YNY will work on simple modeling of self-assembly problems 
+with both undergraduate and high school students from Newark Science Park High School. 
+PI YNY has a track record of working with local high school students for their research projects before they apply for colleges.
+PI BQ will expose
 undergraduate and high school students to the reserach through the
@@
 
-Over the past eight years, PI Ryham has included many undergraduates in
+Over the past eight years, PI RR has included many undergraduates in
 the execution of research initiatives, coauthoring publications. He has
@@
 
-The PIs will capitalize on the synergy between NJIT's doctoral program
+The PIs will capitalize on the synergy between both FSU's doctoral program in Scientific Computing and NJIT's doctoral programs
 in Mathematical Sciences and Fordham's undergraduate focus in the
@@
 studies through working directly or indirectly on this project. On the
-graduate-level education, PI Young and expects to train and
-support a PhD student, Yuexin Liu (who is in her third-year at NJIT) for
-two more years. Yuexin Liu has past experiences in the undergraduate
-training program at NJIT, and will train an undergraduate intern. The
-PIs will foster vertical integration between the senior personnel, their
+graduate-level education, PI YNY expects to train and
+support a PhD student for
+two more years. 
+%Yuexin Liu has past experiences in the undergraduate training program at NJIT, and will train an undergraduate intern. 
+The PIs will foster vertical integration between the senior personnel, their
 collaborators, postdocs, doctoral and Bachelor students, enhancing the

### 2020-11-10 NSF2020/Description/preliminarywork.tex
yny

@@
 \end{figure}
-\section{Preliminary work on elastic moduli}
+\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow\label{sec:preliminary_work}} 
+%\section{Preliminary work on elastic moduli}
 To derive a bending modulus, we first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
@@
 \section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow} 
+>>>>>>> 6fdd947a0d9a0da241b1d3810791b9a4b58b70cf
 %The motion of vesicles in shear flow is an important

### 2020-11-10 NSF2020/Description/background.tex
working on page 1

@@
 %{\bf {Collaborative Research: Mathematical modeling and coarse-grained simulations of self-assembly of amphiphilic Janus particles in a solvent}}\\
-{\it Rolf Ryham (lead PI, Fordham University)}, {\it Bryan Quaife (PI,
+{\em Rolf Ryham (lead PI, Fordham University), Bryan Quaife (PI,
 FSU), and Y.-N. Young (PI, NJIT)}
@@
 \label{sec:background}
-The goal of this collaborative proposal is to investigate the dynamic self-assembly of amphiphilic particles interacting with each other via hydrophobic forces in a solvent using continuum
-modeling and numerical simulations.  Amphiphilic particles (such as lipid molecules) possess both hydrophobic and hydrophilic structures. In a viscous solvent they
-self-assemble into meso-/macroscopic structures (such as micelles and bilayers of lipids) to shield their hydrophobic parts from contact with the solvent molecules (water).
+The goal of this collaborative proposal is to use continuum modeling and
+numerical simulations to investigate the dynamic self-assembly of
+amphiphilic particles interacting with each other via hydrophobic forces
+in a solvent. Amphiphilic particles (such as lipid molecules) possess
+both hydrophobic and hydrophilic structures. In a viscous solvent they
+self-assemble into meso-/macroscopic structures (such as micelles and
+bilayers of lipids) to shield their hydrophobic parts from contact with
+the solvent molecules (water).
 %
@@
 and has been a major source of nonspecific interactions between
-nanoparticles for self-assembly in  soft matter \cite{Sanchez-IglesiasEtAl2012_ACSNano,AltantzisEtAl2013_PSC,XieYangLuEtAl2020_COCIS}. 
+nanoparticles for self-assembly in  soft matter
+\cite{Sanchez-IglesiasEtAl2012_ACSNano,AltantzisEtAl2013_PSC,XieYangLuEtAl2020_COCIS}. 
 %The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles so to design smart materials of desirable properties by
@@
 %and try to minimize their surface area when in water. 
-At the microscopic level, the hydrophobic force is a long-range, surface interaction. 
-This means that two hydrophobic surfaces, separated by
-water over some distance, experience an attractive force \cite{Lum1999,Meyer2006,Hammer2010}.
-Measurements show that the hydrophobic force
-decays exponentially with a decay length like 1 nm 
-\cite{Israelachvili1984, Marcelja1977,Christenson2001,Lin2005}. It is also known that the interaction is not pairwise additive, meaning that the force
-between any two hydrophobic objects is altered by the presence of a third  object.
+At the microscopic level, the hydrophobic force is a long-range, surface
+interaction.  This means that two hydrophobic surfaces, separated by
+water over some distance, experience an attractive force
+\cite{Lum1999,Meyer2006,Hammer2010}.  Measurements show that the
+hydrophobic force decays exponentially with a decay length like 1 nm
+\cite{Israelachvili1984, Marcelja1977,Christenson2001,Lin2005}. It is
+also known that the interaction is not pairwise additive, meaning that
+the force between any two hydrophobic objects is altered by the presence
+of a third  object.
 
@@
 \centerline{\includegraphics[width=0.22\textwidth]{figures/BG_fig1.pdf}}
+  \todo[inline]{Change the $\mathbf{n}$ to a $\boldsymbol{\nu}$}
 \caption{The exterior domain $\Omega$ is the solvent region surrounding a
@@
 Recently PIs RR and YNY developed a mathematical model called the
-hydrophobic attraction potential (HAP) \cite{Fu2018_SIAM}.
-This model addresses the major shortcomings of molecular dynamics (MD) and continuum approaches. Based on preliminary results (\S\ref{sec:preliminary_work})
-the PIs propose to extend this HAP model to offer
- an alternative modeling methodology that leads to new mathematical ideas,
-and is both physically accurate and computationally practical.
+hydrophobic attraction potential (HAP) \cite{Fu2018_SIAM} that is based
+on the physical origin of hydrophobicity.  This model addresses the
+major shortcomings of molecular dynamics (MD) and continuum approaches.
+Based on preliminary results (\S\ref{sec:preliminary_work}) the PIs
+propose to extend this HAP model to offer an alternative modeling
+methodology that leads to new mathematical ideas, and is both physically
+accurate and computationally practical.
 %
@@
 \label{sec:HAP}
-
-Based on the physical origin of hydrophobicity,  we have devised a functional, called the hydrophobic attraction potential (HAP), to
-model hydrophobic forces \cite{Fu2018_SIAM}. The motivation for HAP concept stemmed from PI RR's 
-earlier work on the problem of energy barriers in membrane fusion \cite{RyKlYaCo16,Chetal16}.
-There, PI RR and collaborators resolved the long-standing issue of accounting for the energy of a fissure surface
-during topological transitions, by applying a squared gradient mathematical theory 
-for hydrophobic attraction between planar surfaces \cite{Eriksson1989,Lum1999,Menshikov2017,Marcelja1977} to monolayer fissures.
-Based on PI RR and YNY's coarse-grained membrane modeling work \cite{Fu2017}, 
-the investigators initiated a collaboration to create a gradient theory for arbitrary collections 
-of hydrophobic and amphiphilic particles. This new method 
-eliminates the costly calculation of water by treating the solvent implicitly, 
-and avoids complicated re-meshing schemes of continuum approaches
-by utilizing a particle-based representation.
+%Based on the physical origin of hydrophobicity,  we have devised a
+%functional, called the hydrophobic attraction potential (HAP), to model
+%hydrophobic forces~\cite{Fu2018_SIAM}. 
+The motivation for the HAP concept
+stemmed from PI RR's earlier work on the problem of energy barriers in
+membrane fusion~\cite{RyKlYaCo16,Chetal16}.  There, PI RR and
+collaborators resolved the long-standing issue of accounting for the
+energy of a fissure surface during topological transitions, by applying
+a squared gradient mathematical theory for hydrophobic attraction
+between planar surfaces~\cite{Eriksson1989,Lum1999,Menshikov2017,Marcelja1977} to monolayer
+fissures.  Based on PI RR and YNY's coarse-grained membrane modeling
+work \cite{Fu2017}, the investigators initiated a collaboration to
+create a gradient theory for arbitrary collections of hydrophobic and
+amphiphilic particles. This new method eliminates the costly calculation
+of water by treating the solvent implicitly, and avoids complicated
+re-meshing schemes of continuum approaches by utilizing a particle-based
+representation.
 

### 2020-11-10 NSF2020/Description/background.tex
working on background but not done yet

@@
 %hydrophobic forces~\cite{Fu2018_SIAM}. 
-The motivation for the HAP concept
-stemmed from PI RR's earlier work on the problem of energy barriers in
-membrane fusion~\cite{RyKlYaCo16,Chetal16}.  There, PI RR and
-collaborators resolved the long-standing issue of accounting for the
-energy of a fissure surface during topological transitions, by applying
-a squared gradient mathematical theory for hydrophobic attraction
-between planar surfaces~\cite{Eriksson1989,Lum1999,Menshikov2017,Marcelja1977} to monolayer
-fissures.  Based on PI RR and YNY's coarse-grained membrane modeling
-work \cite{Fu2017}, the investigators initiated a collaboration to
+The motivation for the HAP concept stemmed from PI RR's earlier work on
+the problem of energy barriers in membrane
+fusion~\cite{RyKlYaCo16,Chetal16}. By applying a squared gradient
+mathematical theory for hydrophobic attraction between planar
+surfaces~\cite{Eriksson1989,Lum1999,Menshikov2017,Marcelja1977}, PI RR
+and collaborators resolved the long-standing issue of accounting for the
+energy of a monolayer fissure surface during topological transitions.
+Based on PI RR and YNY's coarse-grained membrane modeling
+work~\cite{Fu2017}, the investigators initiated a collaboration to
 create a gradient theory for arbitrary collections of hydrophobic and
@@
 
-To define HAP, consider a region $\Omega \subset \mathbb{R}^3$  
-modeling the solvent surrounding a number of particles (Figure \ref{fig:domain}).
-As stated earlier, the HAP must be an energy of the shape of the region
-because hydrophobic attraction is non-additive. 
-The boundary of the region is the water-particle interface and some parts of this
-surface are hydrophobic while others are hydrophilic. 
-Monte Carlo simulations 
-show that water changes structure at hydrophobic interfaces \cite{Luzar1987, Jonsson2006,Varilly2011}.
-Due to rapid fluctuation in the hydrogen bond network,
-restructuring at the interface extends into bulk water.
-This motivates the following definition for the HAP of the particles:
-\begin{equation}
+To define HAP, consider a region $\Omega \subset \mathbb{R}^3$  modeling
+the solvent surrounding a number of particles (Figure \ref{fig:domain}).
+The HAP must be an energy of the shape of the region because hydrophobic
+attraction is non-additive. The boundary of the region is the
+water-particle interface and some parts of this surface are hydrophobic
+while others are hydrophilic. Monte Carlo simulations show that water
+changes structure at hydrophobic interfaces~\cite{Luzar1987,
+Jonsson2006, Varilly2011}. Due to rapid fluctuation in the hydrogen bond
+network, restructuring at the interface extends into bulk water. This
+motivates the following definition for the HAP of the particles:
+\begin{align}
 \label{HAP}
   \Phi = \gamma \iiint_{\Omega} \rho |\nabla u|^2 + \rho^{-1}u^2 \,dx \,dy \,dz, 
-\end{equation}
-where $u$ is the unique solution of screened Laplace equation boundary value problem 
+\end{align}
+where $u$ is the unique solution of the screened Laplace equation boundary value problem 
 \begin{equation}
   \label{SL}
-  -\rho^2 \Delta u + u = 0 \in \Omega,\quad u = f  \mbox{ on } \partial \Omega, \quad u(x) \to 0 \mbox{ as } x \to \infty.
+  -\rho^2 \Delta u + u = 0, \mbox{ } x \in \Omega, \qquad
+  u = f,  \mbox{ } x \in \partial \Omega, \qquad 
+  u(x) \to 0 \mbox{ as } |x| \to \infty.
 \end{equation}
-The scalar function $u(x)$ is called the water activity. Its boundary values $f$ 
-define the degree of hydrophobicity of the water-particle interface. The value 
-1 represents a completely hydrophobic interface, where water has lost rotational freedom. 
-Conversely, the boundary value 0 corresponds to a polar surface where water has the same rotational
-freedom as in bulk water. The parameter $\rho$ is the decay length of attraction, 
-around 1 nm, and the parameter $\gamma$ is the interfacial tension \cite{Israelachvili1954}.
-The parameters $\rho$ and $\gamma$ contain information about the quality
-of the solvent \cite{Discher2002}.
+The scalar function $u(x)$ is called the water activity. Its boundary
+values $f$ define the degree of hydrophobicity of the water-particle
+interface. If $f=1$, the interface is hydrophobic and water has lost
+rotational freedom. Conversely, if $f=0$, the interface has the same
+rotational freedom as in bulk water. The parameter $\rho$ is the decay
+length of attraction, around 1 nm, and the parameter $\gamma$ is the
+interfacial tension~\cite{Israelachvili1954}. Both parameters contain
+information about the quality of the solvent~\cite{Discher2002}.
 
-From a phenomenological perspective, (\ref{HAP}--\ref{SL}) 
-is an appropriate model of hydrophobic attraction. Specifically,
-using boundary layer analysis, it is possible 
-to show that $\Phi$ converges to a surface energy in the zero-decay length limit \cite{Lee2018,Lin2015,Shibata2004}.
-For non-zero decay lengths, solutions of \eqref{SL} yield an attractive interaction, e.g.~between hydrophobic parallel disks
-separated by water \cite{Eriksson1989}. Also, we have demonstrated with simulation that the forces 
-derived from HAP theory are non-additive, and even deviate significantly from 
-a pairwise potential \cite{Meyer2006,Fu2018_SIAM}. 
+From a phenomenological perspective, equations~\eqref{HAP}
+and~\eqref{SL} is an appropriate model of hydrophobic attraction.
+Specifically, using boundary layer analysis, it is possible to show that
+$\Phi$ converges to a surface energy in the zero-decay length
+limit~\cite{Lee2018, Lin2015, Shibata2004}. For non-zero decay lengths,
+solutions of~\eqref{SL} yield an attractive interaction between
+hydrophobic parallel disks separated by water~\cite{Eriksson1989}. Also,
+we have demonstrated with simulation that the forces derived from HAP
+theory are non-additive and significantly deviate from a pairwise
+potential~\cite{Meyer2006, Fu2018_SIAM}. 
 %The hydrophobic force has been implicated in the directed folding of proteins, 
@@
 To define the particle dynamics, consider the exterior domain $\Omega$
-for a finite number of disjoint, rigid and closed particles $P_1$, $P_2$, \dots, $P_n$, each with Lipschitz boundary,
-and boundary data $f$ in the Sobolev space $H^1(\Omega).$ 
-For any fixed configuration, the functional \eqref{HAP} has a unique minimizer $u$
-among all $u - f$ with vanishing trace. This minimizer is a solution to \eqref{SL}.
-Conversely, from maximum principles and energy estimates,  any solution of 
-\eqref{SL} is the minimizer of \eqref{HAP}, and this supplies $\Phi$ with a well-defined value.
-
-Taking the derivative of \eqref{HAP} with respect to particle configurations, and using the boundary value problem \eqref{SL}
-in a critical way,
-%leads to the surface term \eqref{stress}.  
-the first variation of the hydrophobic potential $\Phi$  
-yields a symmetric, rank-two tensor \cite{Bandle2015,Schiffer1954,Grinfeld2010} called the hydrophobic stress:
-\begin{equation}
+for a finite number of disjoint, rigid and closed particles $P_1$,
+$P_2$, \ldots, $P_n$, each with Lipschitz boundary, and boundary data
+$f$ in the Sobolev space $H^1(\Omega)$. For any fixed configuration, the
+minimizer of the functional~\eqref{HAP} among all $u - f$ with vanishing
+trace is the solution of~\eqref{SL}. Conversely, from maximum principles
+and energy estimates, any solution of~\eqref{SL} is the minimizer
+of~\eqref{HAP}, and this supplies $\Phi$ with a well-defined value.
+Taking the derivative of~\eqref{HAP} with respect to particle
+configurations, and using the boundary value problem~\eqref{SL}, the
+first variation of the hydrophobic potential $\Phi$ yields a symmetric,
+rank-two tensor~\cite{Bandle2015, Schiffer1954, Grinfeld2010} called the
+hydrophobic stress:
+\begin{align}
   \label{stress}
 \boldsymbol{\sigma}_{\text{hydro}} = \gamma \rho^{-1} u^2 I + 2\rho \gamma (\tfrac{1}{2}|\nabla u|^2I - \nabla u \nabla u^T).
-\end{equation}
+\end{align}
 %
@@
 %
-By integrating the hydrophobic stress over the surface of particle $P_i,$ we obtaining the hydrophobic force and torque on each particle 
-\begin{equation}
+Integrating the hydrophobic stress over the surface of particle $P_i$
+reveals the hydrophobic force and torque on each particle 
+\begin{align}
   \label{forceandtorque}
@@
   \mathbf{T}_i = \iint_{\partial P_i} \mathbf{x} \times (\boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n}) \,dS.
-\end{equation}
-We verified that this system is force and torque free.
-To supply viscous dissipation, 
-we incorporated the mobility problem in Stokes flow to obtain the rigid body motions; 
+\end{align}
+Our previous verifies that this system is force- and torque-free and
+\S\ref{subsec:specific_aim_2} addresses the numerical challenges in
+evaluating~\eqref{stress} and how these challenges are overcome. To
+supply viscous dissipation, we incorporated the mobility problem in
+Stokes flow to obtain the rigid body motions:
 \begin{equation}
@@
 \end{equation}
-Here $\mu$ is the fluid viscosity and the first two equations state
-that the fluid motion is a
-divergence-free Stokes flow; the third equation specifies the fluid
-velocity at infinity;
-the fourth equation enforces a rigid body motion constraint on each
-particle, where
-$\mathbf{v}_i$ and $\boldsymbol{\omega}_i$ are unknown translation and
-angular velocities
-of the $i$-th particle and $\mathbf{a}_i$ is the center of mass of $P_i$;
-the last two equations state that the net forces and torques
-on each particle are given by the quantities ${\bf F}_i$ and ${\bf T}_i$
-from \eqref{forceandtorque}, and $\boldsymbol{\sigma}$ is the fluid shear stress.
-
-The time integration of particle configurations goes as follows: 
-\textbf{(i)} solve the BVP \eqref{SL} for the screened Laplace equation, 
-\textbf{(ii)} determine the rigid body forces and torques \eqref{forceandtorque}, 
-\textbf{(iii)} solve the Stokes mobility problem \eqref{eq:stokes} for rigid body motion,
-\textbf{(iv)} update the particle configuration. 
-\S \ref{subsec:specific_aim_2}, addresses the numerical challenges in 
-evaluating \eqref{stress} and how these challenges are overcome.
+Here $\mu$ is the fluid viscosity and the first two equations state that
+the fluid motion is a divergence-free Stokes flow; the third equation
+specifies the fluid velocity at infinity; the fourth equation enforces a
+rigid body motion constraint on each particle, where $\mathbf{v}_i$ and
+$\boldsymbol{\omega}_i$ are unknown translation and angular velocities
+of the $i$-th particle and $\mathbf{a}_i$ is the center of mass of
+$P_i$; the last two equations state that the net forces and torques on
+each particle are ${\bf F}_i$ and ${\bf T}_i$
+from~\eqref{forceandtorque}, respectively, and $\boldsymbol{\sigma}$ is
+the fluid shear stress. The time integration of particle configurations
+goes as follows: \textbf{(i)} solve the BVP~\eqref{SL} for the screened
+Laplace equation, \textbf{(ii)} determine the rigid body forces and
+torques~\eqref{forceandtorque}, \textbf{(iii)} solve the Stokes mobility
+problem~\eqref{eq:stokes} for rigid body motion, \textbf{(iv)} update
+the particle configuration. Numerical challenges and how these
+challenges are overcome are described in \S\ref{subsec:specific_aim_2}.
 
@@
 
-Our simulations used Janus particles to model
-lipid amphiphiles. Janus particles are a popular tool in material science and physics
-for creating functional materials \cite{Lee2014, Lee2013}. 
-%This topic is the basis of Specific Aim 3 \todo[inline]{not true anymore}. 
-Janus particles are typically
-spherical with a biphasic material label on either hemisphere,  endowing the particle
-with a directional order. We considered a two-dimensional system, and represented an 
-elongated lipid by elliptical particles with hydrophobic and hydrophilic labels along the ellipse's long axis.
+Our simulations use Janus particles to model lipid amphiphiles which are
+popular in material science and physics for creating functional
+materials~\cite{Lee2014, Lee2013}. Janus particles are typically
+spherical with a biphasic material label on either hemisphere, endowing
+the particle with a directional order. We considered a two-dimensional
+system, and represented an elongated lipid by elliptical particles with
+hydrophobic and hydrophilic labels along the ellipse's long axis. Under
+the hydrophobic force, and with an excluded volume to prevent
+collisions, the Janus particles spontaneously merge and realign to form
+bilayers. This occurs only as a result of energy minimization and does
+not require artificial inputs. To our knowledge, this is the first
+demonstration of bilayer self-assembly by a continuum hydrophobic
+interaction model~\cite{Noguchi2001, Farago2003, Brannigan2006,
+Brooks2009, Wang2013}.
 
-Under the hydrophobic force, and with an excluded volume to prevent collisions, the 
-Janus particles spontaneously merge and realign to form bilayers. This occurs only as a result
-of energy minimization and does not require artificial inputs. To our knowledge, this is the first demonstration 
-of bilayer self-assembly by a continuum hydrophobic interaction model \cite{Noguchi2001,Farago2003,Brannigan2006,Brooks2009,Wang2013}.
-
-It is worth emphasizing that the HAP model uses only a few parameters; interfacial tension, decay length, repulsion strength and particle
-shape. For example, an elastic modulus for stretching a vesicle from micropipette manipulation 
-directly calibrate our interfacial tension parameter. This is in direct contrast with pair-potential based approaches in
-MD simulations and coarse-grained models where many more parameters are required \cite{Varilly2011,Wang2013}.
+It is worth emphasizing that the HAP model uses only a few parameters;
+interfacial tension, decay length, repulsion strength, and particle
+shape. For example, an elastic modulus for stretching a vesicle from
+micropipette manipulation directly calibrate our interfacial tension
+parameter. This is in direct contrast with pair-potential based
+approaches in MD simulations and coarse-grained models where many more
+parameters are required~\cite{Varilly2011, Wang2013}.
 %MD simulators have also made measurements and lately there is better and better agreement with reality. 
@@
 
-As a proof of concept, our work has already tested for elastic energies for bending, stretching and tilt of the bilayer assembly.
-Extracting coefficients from the HAP simulations showed strikingly
-positive agreement with experimentally determined values
-\cite{Fu2018_SIAM}.
-Encouraged by these results and the hydrodynamic simulations of the bilayer assembly, the PIs propose to
-further extend the HAP model and the numerical schemes (see \S\ref{sec:proposed-work})
-to make direct comparison with experiments, the continuum liquid crystal results and MD simulations results, to establish that
-the HAP model has the capability and adaptivity to model phenomena across length scales and time scales.
+As a proof of concept, our work has already tested for elastic energies
+for bending, stretching and tilt of the bilayer assembly. Extracting
+coefficients from the HAP simulations showed strikingly positive
+agreement with experimentally determined values \cite{Fu2018_SIAM}.
+Encouraged by these results and the hydrodynamic simulations of the
+bilayer assembly, the PIs propose to further extend the HAP model and
+the numerical schemes (see \S\ref{sec:proposed-work}) to make direct
+comparison with experiments, the continuum liquid crystal results and MD
+simulations results, to establish that the HAP model has the capability
+and adaptivity to model phenomena across length scales and time scales.
 
-Over the past decades, researchers have used a number of mathematical tools 
-to simulate vesicles in a shear flow, including  lattice Boltzmann \cite{KaouiHartingMisbah2011_PRE}, coarse-grained Brownian dynamics \cite{NoguchiTakasu2002_BJ},
-phase field \cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, 
-level set \cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary integral \cite{Shravan09,Rahimian15} and 
-immersed boundary approaches \cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}. Most of these approaches
-assume a mathematical surface, whether implicitly or explicitly, 
-and define an elastic bending energy of the surface. 
+Over the past decades, researchers have used a number of mathematical
+tools to simulate vesicles in a shear flow, including lattice Boltzmann
+\cite{KaouiHartingMisbah2011_PRE}, coarse-grained Brownian dynamics
+\cite{NoguchiTakasu2002_BJ}, phase field
+\cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, level set
+\cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary integral
+\cite{Shravan09,Rahimian15} and immersed boundary approaches
+\cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}. Most of
+these approaches assume a mathematical surface, whether implicitly or
+explicitly, and define an elastic bending energy of the surface. 
 %The vesicle obeys fluid
@@
 Our HAP approach differs from prior methods in a number of respects.
-First, we do not assume a surface. Rather, we more fundamentally  consider a collection of amphiphilic particles.
-The collection of amphiphiles minimize hydrophobic interactions by sequestering hydrophobic tails in the form of a bilayer, and the particles' excess free energy gives rise to an elastic bilayer energy.
-The second difference lies in the fluid-interface coupling. Here, the associated mobility problem \eqref{eq:stokes} 
-is more complicated than dealing with a stress boundary condition or diffusive surface force, 
-because the fluid velocity must be that of a rigid body motion at the particle surfaces.
+First, we do not assume a surface. Rather, we more fundamentally
+consider a collection of amphiphilic particles.  The collection of
+amphiphiles minimize hydrophobic interactions by sequestering
+hydrophobic tails in the form of a bilayer, and the particles' excess
+free energy gives rise to an elastic bilayer energy. The second
+difference lies in the fluid-interface coupling. Here, the associated
+mobility problem~\eqref{eq:stokes} is more complicated than dealing with
+a stress boundary condition or diffusive surface force, because the
+fluid velocity must be that of a rigid body motion at the particle
+surfaces. The HAP model also addresses the existence of multiple phases.
+We can vary lipid length, spontaneous curvature, and bending rigidity by
+introducing differentiating particle shapes and hydrophobic boundary
+conditions (Figure \ref{fig:demixing}). In contrast, continuum theory
+deals with multiple phases through additional surface densities that
+must then satisfy specialized transport equations~\cite{Lowengrub07,
+MikuckiZhou17}. 
 %
@@
 \end{wrapfigure}
-The greatest strength of using HAP to model lipid bilayer membrane is the ability
-to form discontinuities (interfacial singularity) from first physical principle without any artificial manipulation to rearrangement the interface.
+The greatest strength of using HAP to model lipid bilayer membrane is
+the ability to form discontinuities (interfacial singularity) from first
+physical principle without any artificial manipulation to rearrangement
+the interface.
 %The ability to form discontinuities is perhaps the HAP method's greatest strength.
-For example, using the HAP model to simulate a vesicle under a shear flow that is strong enough to cause the vesicle membrane to rupture, 
-we expect the HAP model to capture the reorganization of lipid molecules on the scales of membrane thickness ($\sim 5$ nm), which is a nearly impossible
-task using phase-field or immerse boundary method without extreme refinement around the membrane and artificial treatment of reconnection during the topological change of an interface.
+For example, using the HAP model to simulate a vesicle under a shear
+flow that is strong enough to cause the vesicle membrane to rupture, we
+expect the HAP model to capture the reorganization of lipid molecules on
+the scales of membrane thickness ($\sim 5$ nm), which is a nearly
+impossible task using phase-field or immerse boundary method without
+extreme refinement around the membrane and artificial treatment of
+reconnection during the topological change of an interface.
 

### 2020-11-10 NSF2020/Description/preliminarywork.tex
fixing merge conflict
working on background but not done yet

@@
 \section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow} 
->>>>>>> 6fdd947a0d9a0da241b1d3810791b9a4b58b70cf
 %The motion of vesicles in shear flow is an important
@@
 %
-To implement a vesicle in shear flow in the context of hydrophobic potentials and mobility problem, 
-we consider a shear flow in the far-field $\mathbf{u}_{\infty} = Uy\mathbf{i}_x$ in the direction of the $x$-axis
-(Figure \ref{fig:tanktreading}A).
+To implement a vesicle in shear flow in the context of hydrophobic
+potentials and mobility problem, we consider a shear flow in the
+far-field $\mathbf{u}_{\infty} = Uy\mathbf{i}_x$ in the direction of the
+$x$-axis (Figure \ref{fig:tanktreading}A). As illustrated in Figure
+\ref{fig:tanktreading}, the particle based approach supports
+inter-leaflet slip, and this can be used to determine inter-leaflet and
+in-plane shear viscosities. 
 %
@@
 
-For large shear flow rates, there is an increase in arc length. Here arc length
-refers to the the mid-plane circumference. Thus,
-some of the external force is going into stretching the vesicle--the other
-part is going into bending and viscous dissipation. From our experiments, 
-we find that the vesicle ruptures once stretching exceeds about 5 \%
-(see Figure \ref{fig:rupture}).
-Finally, movies of the tank-treading motion show a slip velocity
-between the outer and inner leaflets Figure \ref{fig:tanktreading}G. We have illustrated this 
-by tracking the distance between two reference particles in the inner and outer leaflet
-(Figure \ref{fig:tanktreading}B \& D, green and blue particles). 
-With moderate shear rates or greater adhesion, the particle pair moves in tandem
-(in Figure \ref{fig:tanktreading}H, blue and red curves, their distance is more or less constant). 
-For a large shear rate, the particle separates as the two leaflets slide against one another.
+For large shear flow rates, there is an increase in arc length. Here arc
+length refers to the the mid-plane circumference. Thus, some of the
+external force is going into stretching the vesicle--the other part is
+going into bending and viscous dissipation. From our experiments, we
+find that the vesicle ruptures once stretching exceeds about 5 \% (see
+Figure \ref{fig:rupture}).  Finally, movies of the tank-treading motion
+show a slip velocity between the outer and inner leaflets Figure
+\ref{fig:tanktreading}G. We have illustrated this by tracking the
+distance between two reference particles in the inner and outer leaflet
+(Figure \ref{fig:tanktreading}B \& D, green and blue particles).  With
+moderate shear rates or greater adhesion, the particle pair moves in
+tandem (in Figure \ref{fig:tanktreading}H, blue and red curves, their
+distance is more or less constant).  For a large shear rate, the
+particle separates as the two leaflets slide against one another.
 
@@
 %\end{wrapfigure}
-There are a number of advantages to using our particle based approach.
-For one, the HAP theory automatically accounts for the existence of multiple phases. 
-For example, we can vary lipid length, spontaneous curvature and bending rigidity 
-by introducing differentiating particle shapes and hydrophobic boundary conditions (Figure \ref{fig:demixing}).
-Continuum theory deals with multiple phases through additional surface densities that must
-then satisfy specialized transport equations \cite{Lowengrub07,MikuckiZhou17}. 
-As illustrated in Figure \ref{fig:tanktreading}, the particle
-based approach supports inter-leaflet slip, and this can be used to determine inter-leaflet
-and in-plane shear viscosities. 
 %

### 2020-11-10 NSF2020/Description/specificaim1_ver2.tex

@@
 \subsubsection{New mathematical analysis}
+
+We will develop some of the mathematical connections between the HAP energy and the energy functional used in the phase field method. 
+The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
+The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
+to the characteristic function of a set solving a perimeter minimization problem 
+\cite{The Gradient Theory of Phase Transitions and the Minimal lnterfaee Criterion, }. 
+Analogously, the HAP energy converges to the surface energy in the limit
+$\rho \to 0$, and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
+area measures supported on the particle boundaries. We will use boundary layer analysis to study the rate
+of convergence as it depends on \cite{Stephan Luckhaus & Luciano Modica, LeeRyham}
+
  It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
@@
 
-  We will revisit the HK analysis to see if any inconsitencies can be resolved.
+  We will revisit the HK analysis to see if any of the afore mentioned inconsitencies can be resolved.
   As a main analytical innovation, we have found that expanding the strain tensor in

### 2020-11-10 NSF2020/Description/specificaim1_ver2.tex
Update specificaim1_ver2.tex

@@
 
-We will develop some of the mathematical connections between the HAP energy and the energy functional used in the phase field method. 
+We will develop some of the mathematical connections between the HAP energy and the energy functionals used in the gradient theory of phase transitions. 
 The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
@@
 to the characteristic function of a set solving a perimeter minimization problem 
-\cite{The Gradient Theory of Phase Transitions and the Minimal lnterfaee Criterion, }. 
-Analogously, the HAP energy converges to the surface energy in the limit
-$\rho \to 0$, and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
-area measures supported on the particle boundaries. We will use boundary layer analysis to study the rate
-of convergence as it depends on \cite{Stephan Luckhaus & Luciano Modica, LeeRyham}
+\cite{The Gradient Theory of Phase Transitions and the Minimal lnterfaee Criterion, 
+The Gradient Theory of Phase Transitions and the Minimal Interface Criterion. Arch. Rational Mech. Anal. 98 (1986) 123–142.
+L. Modica, Gradient Theory of Phase Transitions with Boundary Contact Energy. Ann. Inst. H. Poincaré, Analyse Nonlinéaire, 4 (1987) 487–512.}.
+
+Analogously, the HAP energy converges to the surface energy in the limit of vanishing screening length 
+and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
+area measures supported on the particle boundaries. 
+PI RR has worked directly on phase field approximations of membrane bending energy \cite{Willmore} and asymptotcs in the Poisson-Boltzman equation \cite{LeeRyham}.
+The proposed analysis is a natural outgrowth or prior work because the linearization of the Poisson-Boltzmann equation is the screened Laplace equations \eqref{SL}.
+One of the basic questions is to establish the HAP convergence rate as a function of particle geometry 
+\cite{Stephan Luckhaus & Luciano Modica}, which is an essential benchmark for numerical validation. 
+In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  
+As an illustration, consider two fluid-bound plates $P_1$ and $P_2$ that geometrically flat and hydrophobic all sides.
+We conjecture that in the zero-screening length limit, the plates have overlapping faces, and that 
+\begin{equation}
+\lim_{\rho \to 0} \min \Phi_{\text{hydro}} = \max_{\mathcal{X}} A(P_1 \Delta P_2)
+\end{equation}
+$A(P_1 \Delta P_2)$ is the area of the symmetric difference of the overlap.
 

### 2020-11-10 NSF2020/Description/specificaim1_ver2.tex
Update specificaim1_ver2.tex

@@
 to the characteristic function of a set solving a perimeter minimization problem 
-\cite{The Gradient Theory of Phase Transitions and the Minimal lnterfaee Criterion, 
-The Gradient Theory of Phase Transitions and the Minimal Interface Criterion. Arch. Rational Mech. Anal. 98 (1986) 123–142.
-L. Modica, Gradient Theory of Phase Transitions with Boundary Contact Energy. Ann. Inst. H. Poincaré, Analyse Nonlinéaire, 4 (1987) 487–512.}.
+\cite{Modica87, MODICA1987487, LuMo89}.
 
@@
 area measures supported on the particle boundaries. 
-PI RR has worked directly on phase field approximations of membrane bending energy \cite{Willmore} and asymptotcs in the Poisson-Boltzman equation \cite{LeeRyham}.
+PI RR has worked directly on phase field approximations of membrane bending energy 
+\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman equation \cite{1531-3492_2006_2_357,Lee2018}.
 The proposed analysis is a natural outgrowth or prior work because the linearization of the Poisson-Boltzmann equation is the screened Laplace equations \eqref{SL}.
 One of the basic questions is to establish the HAP convergence rate as a function of particle geometry 
-\cite{Stephan Luckhaus & Luciano Modica}, which is an essential benchmark for numerical validation. 
+\cite{LuMo89}, which is an essential benchmark for numerical validation. 
 In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  

### 2020-11-11 NSF2020/Description/specificaim1_ver2.tex
yny

--- 2020-11-10 NSF2020/Description/specificaim1_ver2.tex
@@
 %\end{figure}
-The goal of Specific Aim 1 is characterize the material properties of many-body, self-assembled amphiphiles.
+The goal of Specific Aim 1 is to characterize the material properties of many-body, self-assembled amphiphiles.
 For amphiphiles assembled into bilayers, these properties are described by membrane continuum mechanics.
@@
 \subsubsection{New mathematical analysis}
-
-We will develop some of the mathematical connections between the HAP energy and the energy functional used in the phase field method. 
-The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
-The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
-to the characteristic function of a set solving a perimeter minimization problem 
-\cite{The Gradient Theory of Phase Transitions and the Minimal lnterfaee Criterion, }. 
-Analogously, the HAP energy converges to the surface energy in the limit
-$\rho \to 0$, and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
-area measures supported on the particle boundaries. We will use boundary layer analysis to study the rate
-of convergence as it depends on \cite{Stephan Luckhaus & Luciano Modica, LeeRyham}
-
  It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
@@
 
-  We will revisit the HK analysis to see if any of the afore mentioned inconsitencies can be resolved.
+  We will revisit the HK analysis to see if any inconsitencies can be resolved.
   As a main analytical innovation, we have found that expanding the strain tensor in

### 2020-11-11 NSF2020/Description/background.tex

@@
   \todo[inline]{Change the $\mathbf{n}$ to a $\boldsymbol{\nu}$}
-\caption{The exterior domain $\Omega$ is the solvent region surrounding a
-number of rigid particles $P_1,$ $P_2,$ $P_3,$ \dots 
-The surface $S$ is the solvent-particle interface, indicated by the unit
-normal $\mathbf{n}.$ }\label{fig:domain}
+\caption{ \footnotesize The exterior domain $\Omega$ is the solvent
+  region surrounding a number of rigid particles $P_1,$ $P_2,$ $P_3,$
+  \dots The surface $S$ is the solvent-particle interface, indicated by
+  the unit normal $\mathbf{n}.$ }\label{fig:domain}
 \end{wrapfigure}
@@
   \label{SL}
-  -\rho^2 \Delta u + u = 0, \mbox{ } x \in \Omega, \qquad
-  u = f,  \mbox{ } x \in \partial \Omega, \qquad 
-  u(x) \to 0 \mbox{ as } |x| \to \infty.
+  -\rho^2 \Delta u + u = 0, \mbox{ } \mathbf{x} \in \Omega, \qquad
+  u = f,  \mbox{ } \mathbf{x} \in \partial \Omega, \qquad 
+  u(\mathbf{x}) \to 0 \mbox{ as } |\mathbf{x}| \to \infty.
 \end{equation}
-The scalar function $u(x)$ is called the water activity. Its boundary
-values $f$ define the degree of hydrophobicity of the water-particle
-interface. If $f=1$, the interface is hydrophobic and water has lost
-rotational freedom. Conversely, if $f=0$, the interface has the same
-rotational freedom as in bulk water. The parameter $\rho$ is the decay
-length of attraction, around 1 nm, and the parameter $\gamma$ is the
-interfacial tension~\cite{Israelachvili1954}. Both parameters contain
-information about the quality of the solvent~\cite{Discher2002}.
+The scalar function $u(\mathbf{x})$ is called the water activity. Its
+boundary values $f$ define the degree of hydrophobicity of the
+water-particle interface. If $f=1$, the interface is hydrophobic and
+water has lost rotational freedom. Conversely, if $f=0$, the interface
+has the same rotational freedom as in bulk water. The parameter $\rho$
+is the decay length of attraction, around 1 nm, and the parameter
+$\gamma$ is the interfacial tension~\cite{Israelachvili1954}. Both
+parameters contain information about the quality of the
+solvent~\cite{Discher2002}.
 
 From a phenomenological perspective, equations~\eqref{HAP}
-and~\eqref{SL} is an appropriate model of hydrophobic attraction.
+and~\eqref{SL} form an appropriate model of hydrophobic attraction.
 Specifically, using boundary layer analysis, it is possible to show that
@@
 trace is the solution of~\eqref{SL}. Conversely, from maximum principles
-and energy estimates, any solution of~\eqref{SL} is the minimizer
+and energy estimates, the solution of~\eqref{SL} is the minimizer
 of~\eqref{HAP}, and this supplies $\Phi$ with a well-defined value.
@@
   \label{forceandtorque}
-  \mathbf{F}_i = \iint_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n} \,dS,\quad
-  \mathbf{T}_i = \iint_{\partial P_i} \mathbf{x} \times (\boldsymbol{\sigma}_{\text{hydro}} \cdot \mathbf{n}) \,dS.
+  \mathbf{F}_i = \iint_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}}
+  \cdot \boldsymbol{\nu} \,dS,\quad
+  \mathbf{T}_i = \iint_{\partial P_i} \mathbf{x} \times
+  (\boldsymbol{\sigma}_{\text{hydro}} \cdot \boldsymbol{\nu}) \,dS.
 \end{align}
-Our previous verifies that this system is force- and torque-free and
-\S\ref{subsec:specific_aim_2} addresses the numerical challenges in
+Our previous work verifies that this system is force- and torque-free
+and \S\ref{subsec:specific_aim_2} addresses the numerical challenges in
 evaluating~\eqref{stress} and how these challenges are overcome. To
-supply viscous dissipation, we incorporated the mobility problem in
+supply viscous dissipation, we incorporate the mobility problem in
 Stokes flow to obtain the rigid body motions:
@@
 \begin{aligned}
-&-\mu \Delta {\bf u} + \nabla p = 0, \quad \text{in}\ \Omega, \qquad 
-\nabla \cdot {\bf u} = 0,  \quad \text{in}\ \Omega,\\
-&{\bf u}({\bf x}) \to 0 \quad \text{as}\ |{\bf x}|\to \infty,\qquad 
+  &-\mu \Delta \mathbf{u} + \nabla p = 0, \quad \mathbf{x} \in \Omega, \qquad 
+  \nabla \cdot \mathbf{u} = 0,  \quad \mathbf{x} \in \Omega,\\
+  &{\bf u}(\mathbf{x}) \to 0 \quad \text{as}\ |\mathbf{x}|\to \infty,\qquad 
   \mathbf{u}(\mathbf{x})|_{\partial P_i} = \mathbf{v}_i +
@@
 the fluid motion is a divergence-free Stokes flow; the third equation
-specifies the fluid velocity at infinity; the fourth equation enforces a
-rigid body motion constraint on each particle, where $\mathbf{v}_i$ and
-$\boldsymbol{\omega}_i$ are unknown translation and angular velocities
-of the $i$-th particle and $\mathbf{a}_i$ is the center of mass of
-$P_i$; the last two equations state that the net forces and torques on
-each particle are ${\bf F}_i$ and ${\bf T}_i$
-from~\eqref{forceandtorque}, respectively, and $\boldsymbol{\sigma}$ is
-the fluid shear stress. The time integration of particle configurations
-goes as follows: \textbf{(i)} solve the BVP~\eqref{SL} for the screened
-Laplace equation, \textbf{(ii)} determine the rigid body forces and
-torques~\eqref{forceandtorque}, \textbf{(iii)} solve the Stokes mobility
-problem~\eqref{eq:stokes} for rigid body motion, \textbf{(iv)} update
-the particle configuration. Numerical challenges and how these
-challenges are overcome are described in \S\ref{subsec:specific_aim_2}.
+specifies that the fluid velocity vanishes at infinity; the fourth
+equation enforces a rigid body motion on each particle, where
+$\mathbf{v}_i$ and $\boldsymbol{\omega}_i$ are unknown translation and
+angular velocities of the $i$-th particle and $\mathbf{a}_i$ is the
+center of mass of $P_i$; the last two equations state that the net
+forces and torques on each particle are $\mathbf{F}_i$ and
+$\mathbf{T}_i$ from~\eqref{forceandtorque}, respectively, and
+$\boldsymbol{\sigma}$ is the fluid shear stress. The time integration of
+particle configurations goes as follows: \textbf{(i)} solve the
+BVP~\eqref{SL} for the screened Laplace equation, \textbf{(ii)}
+determine the rigid body forces and torques~\eqref{forceandtorque},
+\textbf{(iii)} solve the Stokes mobility problem~\eqref{eq:stokes} for
+rigid body motion, \textbf{(iv)} update the particle configuration.
+Numerical challenges and how these challenges are overcome are described
+in \S\ref{subsec:specific_aim_2}.
 
@@
 As a proof of concept, our work has already tested for elastic energies
-for bending, stretching and tilt of the bilayer assembly. Extracting
-coefficients from the HAP simulations showed strikingly positive
-agreement with experimentally determined values \cite{Fu2018_SIAM}.
+for bending, stretching, and tilt of the bilayer assembly. Extracting
+coefficients from the HAP simulations shows strikingly positive
+agreement with experimentally determined values~\cite{Fu2018_SIAM}.
 Encouraged by these results and the hydrodynamic simulations of the
-bilayer assembly, the PIs propose to further extend the HAP model and
-the numerical schemes (see \S\ref{sec:proposed-work}) to make direct
+bilayer assembly, the PIs propose to extend the HAP model and the
+numerical schemes (see \S\ref{sec:proposed-work}) to make direct
 comparison with experiments, the continuum liquid crystal results and MD
@@
 Over the past decades, researchers have used a number of mathematical
-tools to simulate vesicles in a shear flow, including lattice Boltzmann
-\cite{KaouiHartingMisbah2011_PRE}, coarse-grained Brownian dynamics
-\cite{NoguchiTakasu2002_BJ}, phase field
-\cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, level set
-\cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary integral
-\cite{Shravan09,Rahimian15} and immersed boundary approaches
-\cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}. Most of
-these approaches assume a mathematical surface, whether implicitly or
-explicitly, and define an elastic bending energy of the surface. 
+tools to simulate vesicles in a shear flow, including lattice
+Boltzmann~\cite{KaouiHartingMisbah2011_PRE}, coarse-grained Brownian
+dynamics~\cite{NoguchiTakasu2002_BJ}, phase
+field~\cite{DuLiuWang2004_JCP,BibenKassnerMisbah2005_PRE}, level
+set~\cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary
+integral~\cite{Shravan09,Rahimian15} and immersed boundary
+approaches~\cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}.
+Most of these approaches assume a mathematical surface, whether
+implicitly or explicitly, and define an elastic bending energy of the
+surface. Researchers have developed a number of numerical methods for
+calculating energy minimizing steady equilibrium shapes of lipid bilayer
+membranes, vesicles and red blood cells. These approaches range from the
+finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, phase
+field method~\cite{Du05,QiangDu08,Lowengrub13} to immersed boundary
+method~\cite{Hu,Hu13, KimLai2010_JCP}. PI RR and collaborators led in
+part the development of phase field functionals of membrane elastic
+energy and approaches to coupling membrane elasticity to
+fluids~\cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.
+
 %The vesicle obeys fluid
@@
 We can vary lipid length, spontaneous curvature, and bending rigidity by
-introducing differentiating particle shapes and hydrophobic boundary
-conditions (Figure \ref{fig:demixing}). In contrast, continuum theory
+introducing different particle shapes and hydrophobic boundary
+conditions (Figure~\ref{fig:demixing}). In contrast, continuum theory
 deals with multiple phases through additional surface densities that
@@
 %
-\begin{wrapfigure}[17]{l}{0.4\textwidth}
-\centerline{\includegraphics[width=0.4\textwidth]{figures/PW_fig2.pdf}}
-\caption{\label{fig:demixing} An initial assembly of small and 
-large particles spontaneous segregates into two smaller bodies. }
+\begin{wrapfigure}[14]{l}{0.35\textwidth}
+\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
+  \vspace{-8pt}
+  \caption{\label{fig:demixing} \footnotesize An initial assembly of
+  small and large particles spontaneously segregates into two smaller
+  bodies.}
 \end{wrapfigure}
@@
 the ability to form discontinuities (interfacial singularity) from first
-physical principle without any artificial manipulation to rearrangement
-the interface.
-%The ability to form discontinuities is perhaps the HAP method's greatest strength.
-For example, using the HAP model to simulate a vesicle under a shear
-flow that is strong enough to cause the vesicle membrane to rupture, we
-expect the HAP model to capture the reorganization of lipid molecules on
-the scales of membrane thickness ($\sim 5$ nm), which is a nearly
-impossible task using phase-field or immerse boundary method without
-extreme refinement around the membrane and artificial treatment of
-reconnection during the topological change of an interface.
+physical principles without any artificial manipulation to rearrangement
+the interface. For example, using the HAP model to simulate a vesicle
+under a shear flow that is strong enough to cause the vesicle membrane
+to rupture, we expect the HAP model to capture the reorganization of
+lipid molecules on the scales of membrane thickness ($\sim 5$ nm), which
+is a nearly impossible task using phase-field or immerse boundary method
+without extreme refinement around the membrane and artificial treatment
+of reconnection during the topological change of an interface.
 
@@
 %%and steric molecular interactions like the ones presented in this proposal.
-
-In recent years, researchers have developed a number of numerical methods for calculating
-energy minimizing steady equilibrium shapes of lipid bilayer membranes, vesicles and red blood cells.
-These approaches range from the finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, 
-phase field method \cite{Du05,QiangDu08,Lowengrub13} to immersed
-boundary method  \cite{Hu,Hu13, KimLai2010_JCP}.
-PI RR and collaborators led in part the development of phase field
-functionals of membrane elastic energy and approaches to coupling membrane elasticity to fluids  \cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.
 

### 2020-11-11 NSF2020/Description/broaderimpacts.tex

@@
 
-The proposed mathematical analysis and modeling will provide a
-transformative understanding of the collective dynamics of amphiphilic
-particles such as (1) their self-assembly into micelles and bilayers, (2) the material properties of such self-assembly, 
-and (3) the interaction between these building blocks. Amphiphilic Janus
-particles have gained increasing popularity for fabrication of smart
-materials. The proposed hybrid continuum model, mathematical analysis
-and numerical algorithms will have transformative impact on precision
-design for specific mechanical properties of materials made of
-amphiphilic nanoparticles. An important component of this proposal is
-the interdisciplinary education and training of both undergraduate
-students, graduate students, and postdoctoral fellows. The combination
-of mathematical modeling, analysis, and scientific computing in this
-project provides a compelling example of the importance of mathematics
-in biophysics and engineering applications. The concepts and methods
-described here go beyond the context of amphiphilic particles and lipid
-molecules. They extend to other problems featuring microscopic phase
-separation that leads to formation of mesoscopic domains. This situation
-arises, for example, in biological development in systems biology. The
-methods developed here have the potential to impact those and other
-related areas in biomedicine and biotechnology.
+The proposed mathematical analysis, modeling, and numerical algorithms
+will transform our understanding of the collective dynamics of
+amphiphilic particles such as (1) their self-assembly into micelles and
+bilayers, (2) the material properties of such self-assembly, and (3) the
+interaction between these building blocks. In addition to biophysical
+applications, amphiphilic Janus particles have recently popularity for
+fabrication of smart materials. The proposed work will have a
+transformative impact on precision design for specific mechanical
+properties of materials made of amphiphilic nanoparticles. An important
+component of this proposal is the interdisciplinary education and
+training of both undergraduate students, graduate students, and
+postdoctoral fellows. The combination of mathematical modeling,
+analysis, and scientific computing in this project provides a compelling
+example of the importance of mathematics in biophysics and engineering
+applications. The concepts and methods described here go beyond the
+context of amphiphilic particles and lipid molecules. They extend to
+other problems featuring microscopic phase separation that leads to
+formation of mesoscopic domains. This situation arises, for example, in
+biological development in systems biology. The methods developed here
+have the potential to impact those and other related areas in
+biomedicine and biotechnology.
 
@@
 and support undergraduate researcher from Fordham University. The
-supported summer researchers will gain valuable first-hand experience in
-inherently interdisciplinary, mathematical fluid modeling and
+supported summer researchers will gain valuable first-hand
+interdisciplinary experience in mathematical fluid modeling and
 computation. We will incorporate research into teaching, especially in
-differential equation and programming courses. PI YNY will work on simple modeling of self-assembly problems 
-with both undergraduate and high school students from Newark Science Park High School. 
-PI YNY has a track record of working with local high school students for their research projects before they apply for colleges.
-PI BQ will expose
-undergraduate and high school students to the reserach through the
-Undergraduate Research Opportunity Program (UROP) and Young Scholar's
-Program (YSP).
+differential equation and programming courses. PI YNY will work on
+simple modeling of self-assembly problems with both undergraduate and
+high school students from Newark Science Park High School. PI YNY has a
+track record of working with local high school students for their
+research projects before they apply for colleges. PI BQ will work with
+undergraduate and high school students through the Undergraduate
+Research Opportunity Program (UROP) and Young Scholar's Program (YSP) as
+he has done in the past.
 
-Over the past eight years, PI RR has included many undergraduates in
-the execution of research initiatives, coauthoring publications. He has
-a track record for supporting underrepresented groups, being called on
-by the Collegiate Science and Technology Entry Program (CSTEP) to make
+Over the past eight years, PI RR has included many undergraduates in the
+execution of research initiatives and coauthoring publications. He has a
+track record for supporting underrepresented groups, being called on by
+the Collegiate Science and Technology Entry Program (CSTEP) to make
 opportunities for promising students, for example. He has mentored two
-Clare Boothe Luce Scholars, one a U.S. Marine Corp veteran, and a high
+Clare Boothe Luce Scholars, one a U.S.~Marine Corp veteran, and a high
 school student in the NYU GSTEM program.
@@
 Department of Mathematics. Promising, young undergraduate scientists
-from the Bronx community while find a natural pipeline into graduate
-studies through working directly or indirectly on this project. On the
-graduate-level education, PI YNY expects to train and
-support a PhD student for
-two more years. 
-%Yuexin Liu has past experiences in the undergraduate training program at NJIT, and will train an undergraduate intern. 
-The PIs will foster vertical integration between the senior personnel, their
-collaborators, postdocs, doctoral and Bachelor students, enhancing the
-learning environment.
-%
+from the Bronx community will find a natural pipeline into graduate
+studies by working directly or indirectly on this project. On the
+graduate-level education, PI YNY expects to train and support a PhD
+student for two more years. PI BQ will advise a postdoctoral fellow for
+two years. The PIs will foster vertical integration between the senior
+personnel, their collaborators, postdocs, doctoral, and Bachelor
+students, enhancing the learning environment.
 
@@
 morphologies, and we analyze the elastic properties of these amphiphilic
-particle ensembles. This allows us to interpret the Helfrich free
-energy in terms of hydrophobic interactions and specific molecular
+particle ensembles. This allows us to interpret the Helfrich free energy
+in terms of hydrophobic interactions and specific molecular
 characteristics. We extend the capabilities of the boundary integral
-equation quadrature by expansion method to perform large particle number
-simulations in three dimensions with collisions. Results from these
-computations will be used to compare collective amphiphilic against
-experiment, and study the optimal design of three-dimensional
-functional materials.
+equation and time stepping methods to stably perform large particle
+number simulations in three dimensions. Results from these computations
+will be used to compare collective amphiphilic against experiment, and
+study the optimal design of three-dimensional functional materials.

### 2020-11-11 NSF2020/Description/background.tex
rjr

@@
 \label{sec:background}
-The goal of this collaborative proposal is to use continuum modeling and
+The goal of this collaborative proposal is to use mathetical modeling and
 numerical simulations to investigate the dynamic self-assembly of
@@
 and has been a major source of nonspecific interactions between
-nanoparticles for self-assembly in  soft matter
+nanoparticles in  soft matter
 \cite{Sanchez-IglesiasEtAl2012_ACSNano,AltantzisEtAl2013_PSC,XieYangLuEtAl2020_COCIS}. 
@@
 the force between any two hydrophobic objects is altered by the presence
-of a third  object.
+of a third, hydrophobic or otherwise, object \cite{SilveraBatista1242477}.
 
@@
 %
-The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles.
-These results will facilitate optimal designs of smart materials of desirable properties by
-tuning the geometry and properties of the amphiphilic particles.
+The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles. These results will facilitate optimal design of smart materials by
+tuning the geometry and properties.
 

### 2020-11-11 NSF2020/Description/background.tex
rjr

@@
 \centerline{\includegraphics[width=0.22\textwidth]{figures/BG_fig1.pdf}}
-  \todo[inline]{Change the $\mathbf{n}$ to a $\boldsymbol{\nu}$}
-\caption{ \footnotesize The exterior domain $\Omega$ is the solvent
-  region surrounding a number of rigid particles $P_1,$ $P_2,$ $P_3,$
-  \dots The surface $S$ is the solvent-particle interface, indicated by
-  the unit normal $\mathbf{n}.$ }\label{fig:domain}
+\caption{ \footnotesize
+A collection $P_1,$ $P_2,$ $P_3,$ \dots of rigid particles. The exterior domain
+$\Omega$ represents the solvent.}
+  \label{fig:domain}
 \end{wrapfigure}
@@
 %
-The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles. These results will facilitate optimal design of smart materials by
-tuning the geometry and properties.
+he proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles. These results will facilitate optimal design of smart materials by
+tuning the geometry and properties of the amphiphilic particles.
 

### 2020-11-11 NSF2020/Description/background.tex
rjr

@@
 
-\begin{wrapfigure}[16]{r}{0.22\textwidth}
+\begin{wrapfigure}[10]{r}{0.22\textwidth}
 \centerline{\includegraphics[width=0.22\textwidth]{figures/BG_fig1.pdf}}
 \caption{ \footnotesize
-A collection $P_1,$ $P_2,$ $P_3,$ \dots of rigid particles. The exterior domain
-$\Omega$ represents the solvent.}
+A collection $P_1,$ $P_2,$ $P_3,$ \dots of rigid particles.
+The exterior domain $\Omega$ represents the solvent.}
   \label{fig:domain}
@@
 %
-he proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles. These results will facilitate optimal design of smart materials by
+The proposed research aims to provide fundamental understanding of the self-assembly dynamics of amphiphilic particles. These results will facilitate optimal design of smart materials by
 tuning the geometry and properties of the amphiphilic particles.
@@
 amphiphilic particles. This new method eliminates the costly calculation
-of water by treating the solvent implicitly, and avoids complicated
+of water by treating the solvent implicitly, is capable of representing
+biologically relevant morphologies, and avoids complicated
 re-meshing schemes of continuum approaches by utilizing a particle-based
@@
 
-To define HAP, consider a region $\Omega \subset \mathbb{R}^3$  modeling
-the solvent surrounding a number of particles (Figure \ref{fig:domain}).
-The HAP must be an energy of the shape of the region because hydrophobic
-attraction is non-additive. The boundary of the region is the
-water-particle interface and some parts of this surface are hydrophobic
-while others are hydrophilic. Monte Carlo simulations show that water
-changes structure at hydrophobic interfaces~\cite{Luzar1987,
-Jonsson2006, Varilly2011}. Due to rapid fluctuation in the hydrogen bond
-network, restructuring at the interface extends into bulk water. This
-motivates the following definition for the HAP of the particles:
+To define HAP, consider a collection of particles solvent suspended in a solvent. 
+The region $\Omega \subset \mathbb{R}^3$  models 
+the solvent phase (Figure \ref{fig:domain}).
+%The HAP must be an energy of the shape of the region because hydrophobic
+%attraction is non-additive.
+The boundary of the region is the
+water-particle interface.
+Some parts of this interface are hydrophobic
+while others are hydrophilic.
+Hydrophobic interfaces disturb the hydrogen bond structure of water~\cite{Luzar1987,
+Jonsson2006, Varilly2011}. This disturbance comes with an energetic penalty
+that is proportional to interfacial area.
+There is an additional decay length,
+due to rapid fluctuation in the hydrogen bond
+network, describing how far the restructuring extends into bulk water.
+
+The above considerations motivate the following definition for the HAP:
 \begin{align}
 \label{HAP}
-  \Phi = \gamma \iiint_{\Omega} \rho |\nabla u|^2 + \rho^{-1}u^2 \,dx \,dy \,dz, 
+  \Phi = \gamma \int_{\Omega} \rho |\nabla u|^2 + \rho^{-1}u^2 \,\dif V. 
 \end{align}
-where $u$ is the unique solution of the screened Laplace equation boundary value problem 
+The integrand contains
+the decay length $\rho$
+and a scalar function $u(\mathbf{x})$ called the water activity.
+The integrand has units of an inverse length and so
+the volume integral has units of area. Multiplication by interfacial tension
+$\gamma$ makes $\Phi$ an energy.
+
+To get the effect of attraction, the water activity is not arbitrary, but rather
+is the unique solution of the screened Laplace equation boundary value problem 
 \begin{equation}
@@
 \end{equation}
-The scalar function $u(\mathbf{x})$ is called the water activity. Its
-boundary values $f$ define the degree of hydrophobicity of the
-water-particle interface. If $f=1$, the interface is hydrophobic and
-water has lost rotational freedom. Conversely, if $f=0$, the interface
-has the same rotational freedom as in bulk water. The parameter $\rho$
-is the decay length of attraction, around 1 nm, and the parameter
-$\gamma$ is the interfacial tension~\cite{Israelachvili1954}. Both
-parameters contain information about the quality of the
-solvent~\cite{Discher2002}.
+The boundary values $f$ define the degree of hydrophobicity of the
+water-particle interface: $f=1$, describes a hydrophobic interface
+and $f=0$ describes a hydrophilic interface. Thus $f$ encodes information
+about the particles and the parameters $\rho$ and $\gamma$ encode information about the quality of the solvent 
+~\cite{Israelachvili1954, Discher2002}. In practice, we use
+\eqref{SL} to integrate by parts to obtain
+\begin{equation}
+\label{eq:HAP_easy}
+\Phi = -\gamma \int_{\partial \Omega} \rho u \nabla u \cdot \boldsymbol{\nu} \,\dif S,
+\end{equation}
+thereby avoiding calculating a volumetric integral.
 
-From a phenomenological perspective, equations~\eqref{HAP}
-and~\eqref{SL} form an appropriate model of hydrophobic attraction.
-Specifically, using boundary layer analysis, it is possible to show that
-$\Phi$ converges to a surface energy in the zero-decay length
-limit~\cite{Lee2018, Lin2015, Shibata2004}. For non-zero decay lengths,
-solutions of~\eqref{SL} yield an attractive interaction between
-hydrophobic parallel disks separated by water~\cite{Eriksson1989}. Also,
-we have demonstrated with simulation that the forces derived from HAP
-theory are non-additive and significantly deviate from a pairwise
-potential~\cite{Meyer2006, Fu2018_SIAM}. 
+The equations~\eqref{HAP} and~\eqref{SL} possess number of the mathematical properties
+that capture the phenomenological behavior of hydrophobic attraction.
+Specifically, solutions of~\eqref{SL} yield an attractive interaction between
+hydrophobic bodies separated by water ~\cite{Eriksson1989}.
+Using boundary layer analysis, the HAP converges to a surface energy in the zero-decay length
+limit~\cite{Lee2018, Lin2015, Shibata2004}.
+Finally, we have demonstrated that the forces derived from HAP theory are non-additive~\cite{Meyer2006, Fu2018_SIAM}. 
 %The hydrophobic force has been implicated in the directed folding of proteins, 
@@
 %%lipid  bilayer  membrane  that  are  consistent  with other results in the literature.   
-To define the particle dynamics, consider the exterior domain $\Omega$
-for a finite number of disjoint, rigid and closed particles $P_1$,
-$P_2$, \ldots, $P_n$, each with Lipschitz boundary, and boundary data
-$f$ in the Sobolev space $H^1(\Omega)$. For any fixed configuration, the
-minimizer of the functional~\eqref{HAP} among all $u - f$ with vanishing
-trace is the solution of~\eqref{SL}. Conversely, from maximum principles
-and energy estimates, the solution of~\eqref{SL} is the minimizer
-of~\eqref{HAP}, and this supplies $\Phi$ with a well-defined value.
-Taking the derivative of~\eqref{HAP} with respect to particle
-configurations, and using the boundary value problem~\eqref{SL}, the
-first variation of the hydrophobic potential $\Phi$ yields a symmetric,
-rank-two tensor~\cite{Bandle2015, Schiffer1954, Grinfeld2010} called the
-hydrophobic stress:
+To define the particle dynamics,
+let $P_1$, $P_2$, \ldots, $P_N$,
+be a finite collection of disjoint, rigid and closed particles
+with Lipschitz boundary.
+Assume that the label $f$ is an element of the Sobolev space $H^1(\Omega)$.
+The functional~\eqref{HAP} has a minimizer among all functions $u$ equaling $f$ on the boundary in the sense of trace.
+Conversely, from maximum principles and energy estimates, the solution of~\eqref{SL} is unique and minimizes~\eqref{HAP}.
+Taking the first variation of~\eqref{HAP}, i.e. the derivative with respect to the domain
+~\cite{Bandle2015, Schiffer1954, Grinfeld2010},
+yields a symmetric, rank-two tensor called the hydrophobic stress:
 \begin{align}
@@
   \label{forceandtorque}
-  \mathbf{F}_i = \iint_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}}
-  \cdot \boldsymbol{\nu} \,dS,\quad
-  \mathbf{T}_i = \iint_{\partial P_i} \mathbf{x} \times
-  (\boldsymbol{\sigma}_{\text{hydro}} \cdot \boldsymbol{\nu}) \,dS.
+  \mathbf{F}_{\text{hydro},i} = \iint_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}}
+  \cdot \boldsymbol{\nu} \,\dif S,\quad
+  \mathbf{G}_{\text{hydro},i} = \iint_{\partial P_i} (\mathbf{x}-\mathbf{a}_i) \times
+  (\boldsymbol{\sigma}_{\text{hydro}} \cdot \boldsymbol{\nu}) \,\dif S
 \end{align}
-Our previous work verifies that this system is force- and torque-free
-and \S\ref{subsec:specific_aim_2} addresses the numerical challenges in
-evaluating~\eqref{stress} and how these challenges are overcome. To
-supply viscous dissipation, we incorporate the mobility problem in
-Stokes flow to obtain the rigid body motions:
+relative to the center of mass $\mathbf{a}_i$.
+This system is force- and torque-free  \S\ref{subsec:specific_aim_2}.
+To avoid particle collisions, we define an excluded volume potential $\Phi_{\text{repul}}$
+that diverges whenever tubular neighbordhoods of adjacent particles overlap,
+along with the excluded volume repulsions. The total potential, force and torque are then
+\begin{equation}
+\label{eq:total_poten}
+\Phi = \Phi_{\text{hydro}} + \Phi_{\text{repul}},\quad
+\mathbf{F}_{i} = \mathbf{F}_{\text{hydro},i} + \mathbf{F}_{\text{repul},i},\quad
+\mathbf{G}_{i} = \mathbf{G}_{\text{hydro},i} + \mathbf{G}_{\text{repul},i}.
+\end{equation}
+
+To supply viscous dissipation, we incorporate the mobility problem in
+Stokes flow for a rigid body suspension:
 \begin{equation}
@@
 \boldsymbol{\omega}_i\times(\mathbf{x} - \mathbf{a}_i),\\
-&\int_{\partial P_i}\boldsymbol{\sigma}\cdot {\bf n} dS=-{\bf F}_i, \quad
-\int_{\partial P_i}(\mathbf{x}-\mathbf{a}_i)\times (\boldsymbol{\sigma} \cdot \mathbf{n}) dS=-{\bf T}_i.
+&\int_{\partial P_i}\boldsymbol{\sigma}\cdot {\bf n} \dif S=-{\bf F}_i, \quad
+\int_{\partial P_i} (\mathbf{x} - \mathbf{a}_i)\times (\boldsymbol{\sigma} \cdot \mathbf{n}) \dif S =-{\bf G}_i.
 \end{aligned}
@@
 $\mathbf{v}_i$ and $\boldsymbol{\omega}_i$ are unknown translation and
-angular velocities of the $i$-th particle and $\mathbf{a}_i$ is the
-center of mass of $P_i$; the last two equations state that the net
-forces and torques on each particle are $\mathbf{F}_i$ and
-$\mathbf{T}_i$ from~\eqref{forceandtorque}, respectively, and
-$\boldsymbol{\sigma}$ is the fluid shear stress. The time integration of
+angular velocities; the last two equations state that the net
+viscous forces and torques with fluid shear stress $\boldsymbol{\sigma}$
+balance \eqref{eq:total_poten}.
+
+The time integration of
 particle configurations goes as follows: \textbf{(i)} solve the
@@
 
+The HAP formulation is, to our knowledge, the first demonstration of bilayer self-assembly
+by a continuum-based interaction model~\cite{Noguchi2001, Farago2003, Brannigan2006,
+Brooks2009, Wang2013}.
 Our simulations use Janus particles to model lipid amphiphiles which are
@@
 spherical with a biphasic material label on either hemisphere, endowing
-the particle with a directional order. We considered a two-dimensional
-system, and represented an elongated lipid by elliptical particles with
-hydrophobic and hydrophilic labels along the ellipse's long axis. Under
-the hydrophobic force, and with an excluded volume to prevent
-collisions, the Janus particles spontaneously merge and realign to form
+the particle with a directional order.
+We model elongated lipid by elliptical particles with the hydrophobic label defined  along the ellipse's axis.
+Under the hydrophobic force, and with an excluded volume,
+the Janus particles spontaneously merge and realign to form
 bilayers. This occurs only as a result of energy minimization and does
-not require artificial inputs. To our knowledge, this is the first
-demonstration of bilayer self-assembly by a continuum hydrophobic
-interaction model~\cite{Noguchi2001, Farago2003, Brannigan2006,
-Brooks2009, Wang2013}.
+not require artificial inputs.
 
@@
 shape. For example, an elastic modulus for stretching a vesicle from
-micropipette manipulation directly calibrate our interfacial tension
+micropipette manipulation directly calibrates our interfacial tension
 parameter. This is in direct contrast with pair-potential based
@@
 As a proof of concept, our work has already tested for elastic energies
-for bending, stretching, and tilt of the bilayer assembly. Extracting
-coefficients from the HAP simulations shows strikingly positive
+for bending, stretching, and tilt of the bilayer assembly. 
+The elastic coefficients derived from the HAP simulations show strikingly positive
 agreement with experimentally determined values~\cite{Fu2018_SIAM}.
 Encouraged by these results and the hydrodynamic simulations of the
-bilayer assembly, the PIs propose to extend the HAP model and the
-numerical schemes (see \S\ref{sec:proposed-work}) to make direct
-comparison with experiments, the continuum liquid crystal results and MD
-simulations results, to establish that the HAP model has the capability
-and adaptivity to model phenomena across length scales and time scales.
+bilayer assembly, the PIs propose to extend the HAP model
+to make direct comparison with experimental results  \S\ref{subsec:specific_aim_1},
+to establish that the HAP model has the capability
+and adaptivity to model flow phenomena across length scales and time scales \S\ref{subsec:specific_aim_2},
+using efficient, high-order numerical methods \S\ref{sec:proposed-work}.
 
-Over the past decades, researchers have used a number of mathematical
+\begin{wrapfigure}[14]{l}{0.35\textwidth}
+\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
+  \vspace{-8pt}
+  \caption{\label{fig:demixing} \footnotesize An initial assembly of
+  small and large particles spontaneously segregates into two smaller
+  bodies.}
+\end{wrapfigure}Over the past decades, researchers have used a number of mathematical
 tools to simulate vesicles in a shear flow, including lattice
@@
 
-Our HAP approach differs from prior methods in a number of respects.
+Our HAP approach differs from these prior methods in a number of respects.
 First, we do not assume a surface. Rather, we more fundamentally
@@
 MikuckiZhou17}.
-%
-\begin{wrapfigure}[14]{l}{0.35\textwidth}
-\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
-  \vspace{-8pt}
-  \caption{\label{fig:demixing} \footnotesize An initial assembly of
-  small and large particles spontaneously segregates into two smaller
-  bodies.}
-\end{wrapfigure}
+
 The greatest strength of using HAP to model lipid bilayer membrane is

### 2020-11-11 NSF2020/Description/background.tex
RJR finished background, added refs

@@
   bodies.}
-\end{wrapfigure}Over the past decades, researchers have used a number of mathematical
+\end{wrapfigure}
+Over the past decades, researchers have used a number of mathematical
 tools to simulate vesicles in a shear flow, including lattice
@@
 
+\begin{wrapfigure}[6]{l}{0.35\textwidth}
+\centerline{\includegraphics[width=0.35\textwidth]{figures/Lysis.pdf}}
+  \vspace{-8pt}
+  \caption{\label{fig:lysis} \footnotesize Two hydrophobic particles
+  enter and then lyse the circular bilayer.}
+\end{wrapfigure}
 The greatest strength of using HAP to model lipid bilayer membrane is
@@
 physical principles without any artificial manipulation to rearrangement
-the interface. For example, using the HAP model to simulate a vesicle
+the interface (Figures \ref{fig:demixing} and \ref{fig:lysis}).
+For example, using the HAP model to simulate a vesicle
 under a shear flow that is strong enough to cause the vesicle membrane
-to rupture, we expect the HAP model to capture the reorganization of
+to rupture (see \S\ref{sec:preliminary_work}), we expect the HAP model to capture the reorganization of
 lipid molecules on the scales of membrane thickness ($\sim 5$ nm), which
@@
 without extreme refinement around the membrane and artificial treatment
-of reconnection during the topological change of an interface.
+of reconnection during the topological change of an interface
+\cite{doi:10.1063/5.0009734,LiAn-Chang16,doi:10.1098/rspa.2012.0505,doi:10.1137/130941432,Feetzl18,doi:10.1137/16M1108406}.
 

### 2020-11-11 NSF2020/Description/specificaim1_ver2.tex
rjr
yny 1111

--- 2020-11-10 NSF2020/Description/specificaim1_ver2.tex
@@
 
-The modern theory of membrane continuum mechanics 
-was pioneered by Hamm and Kozlov (HK) \cite{Hamm2000}.
-The theory is widely used to describe biological phenomona 
+Hamm and Kozlov (HK) pioneered 
+the modern theory of membrane continuum mechanics \cite{Hamm2000}, and their theory
+%was pioneered by Hamm and Kozlov (HK) \cite{Hamm2000}. The theory 
+is widely used to describe biological phenomona 
 fission \cite{FrEsAkSh15, Maetal15, PhysRevE.79.031926},
@@
 \cite{SeLeMaEg17,Saetal20, Pietal20}, which require resolution of the internal structure of the membrane.  
-Using the HK  model as a base,
-PI Ryham and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
-hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
-and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
-are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.
-
-Recently, there has been a revival in interest in the HK theory. The quadratic assumption
+%Using the HK  model as a base,
+%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
+%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
+%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
+%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.  
+%
+Recently, there has been a revival in interest in the HK theory as the quadratic assumption
 for the elasticity energy density has caused researchers to question the applicability of \eqref{ansatz3} for large curvatures \cite{PhysRevLett.117.188102, ARGUDO20161619}. 
-The article \cite{C9SM02079A} counters that energies derived from molecular dynamics and elasticity agree, even when curvatures are large.
-This proposal will bring mathematical analysis to some of the assumptions 
-that went into the HK theory.
+For example, Galimzyanov {\it et al.} \cite{C9SM02079A} countered that energies derived from molecular dynamics and elasticity agree, even when curvatures are large.
+This proposal will develop much-needed mathematical analysis to resolve these controversies due to the assumptions in the HK theory.
 
@@
   \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
-  \caption{\label{fig:deformations}
+  \caption{\label{fig:deformations}Sketch of the HK membrane model \cite{Hamm2000}.
     }
@@
 
-The HK framework assumes a three-dimensional, internal structure for lipid monolayers.
-The internal structure consists of straight fibers that represent elongated hydrocarbon chains, and these fibers
-tilt and stretch with respect to the dividing surface--the surface formed lying between the hydrocarbon chains and polar heads of lipids.
-Accordingly, the deformation takes the form 
-\begin{equation}
-  \label{LMdeformation}
-{\bf x}(X_1, X_2, X_3) = {\bf x}_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) {\bf n}(x_0(X_1, X_2))
-\end{equation}
-where $(X_1,X_2,X_3)$ are points in a reference volume.
-The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field ${\bf n}$ parametrizes the
-direction of the lipid tails in the deformed state \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
-The parameter $X_3$ and the function $\zeta$ parametrizes the distance along the hydrocarbon chain in the reference state
-and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta = $ 2.5 nm is a realistic monolayer thickness.
-
-The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for ${\bf x}$. 
-The chains stretch and compress to satisfy incompressibility.
-Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
-lead to an elastic surface energy over the dividing surface $\Sigma$. 
-This energy decomposes into four, fundamental and independent deformations:
-splay ($\Div {\bf n}$), twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$) and tilt ${\bf t}$:
+The HK framework assumes a three-dimensional lipid monolayers with internal structure
+consisting of straight fibers that represent elongated hydrocarbon chains. HK assumed an
+elastic energy density ${\cal W}$ quadratic in the Green-Lagrange strain tensor for membrane deformation ${\bf x}$.
+%
+%
+%
+%These fibers
+%tilt and stretch with respect to the dividing surface--the surface formed lying between the hydrocarbon chains and polar heads of lipids.
+%Accordingly, the deformation takes the form 
+%\begin{equation}
+%  \label{LMdeformation}
+%{\bf x}(X_1, X_2, X_3) = {\bf x}_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) {\bf n}(x_0(X_1, X_2))
+%\end{equation}
+%where $(X_1,X_2,X_3)$ are points in a reference volume.
+%The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field ${\bf n}$ parametrizes the
+%direction of the lipid tails in the deformed state \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
+%The parameter $X_3$ and the function $\zeta$ parametrizes the distance along the hydrocarbon chain in the reference state
+%and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta = $ 2.5 nm is a realistic monolayer thickness. 
+%
+%The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for ${\bf x}$. 
+%The chains stretch and compress to satisfy incompressibility.
+%Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
+%lead to an elastic surface energy over the dividing surface $\Sigma$. 
+%
+This energy decomposes into four, fundamental and independent deformations  (figure~\ref{fig:deformations}):
+splay ($\Div {\bf n}$), twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$) and tilt ${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal:
 \begin{equation}
@@
 \begin{aligned}
-\int_{\Sigma} 
+{\cal W} \equiv \int_{\Sigma} 
   \tfrac{1}{2}\KB\left[ \left( \Div {\bf n} + k_0\right)^2 - k_0^2\right] 
@@
 \end{equation}
-Here, $(\nabla {\bf n})_{ij} = \partial_{x_j}{\bf n} \cdot {\bf e}_i$ is the surface gradient with
-orthonormal tangent vectors $\{{\bf e}_1, {\bf e}_2\}$.
-\todo[inline]{YNY and BQ: What do you call a coordinate system where the metric is the identity at one point?}
-Also, the surface divergence 
-$\Div {\bf n}$ is the trace, and the surface curl $\Curl {\bf n}$ is the anti-trace (sum of the off-diagonal elements), of $\nabla {\bf n}$ respectively.
-respectively (Figure \ref{fig:distortions}A--C).
-The deformations come with elastic coefficients: the bending modulus $\KB$, twist modulus $\KT$ 
+Here, 
+%$(\nabla {\bf n})_{ij} = \partial_{x_j}{\bf n} \cdot {\bf e}_i$ is the surface gradient with
+%orthonormal tangent vectors $\{{\bf e}_1, {\bf e}_2\}$.
+%%\todo[inline]{YNY and BQ: What do you call a coordinate system where the metric is the identity at one point?}
+%Also, the surface divergence 
+%$\Div {\bf n}$ is the trace, and the surface curl $\Curl {\bf n}$ is the anti-trace (sum of the off-diagonal elements), of $\nabla {\bf n}$ respectively.
+%respectively (Figure \ref{fig:distortions}A--C).
+the deformations come with elastic coefficients: the bending modulus $\KB$, twist modulus $\KT$ 
 and saddle-splay modulus $\KG$ and tilt modulus $\KTH$
-HK define the tilt vector ${\bf t} = {\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal.
-
+%HK define the tilt vector ${\bf t} = {\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal.
+%
 The parameter $k_0$ is the  spontaneous curvature and it determines the preferred lipid splay \cite{RoLi15,Kozlov2007}. 
@@
   qua-bir2014, qua-vee-you2019}.
-\todo[inline]{YNY: place your recent works here}
+%\todo[inline]{YNY: place your recent works here}
 The Canham-Helfrich energy is actually a special case of
@@
 orientation) and collapsing both monolayers onto the membrane midplane.
-There, splay $\Div n$ equal to twice the mean curvature, saddle splay
-$\det \nabla n$ equal to the Gauss curvature, and both twist and tilt
-are equal to zero.
+%There, splay $\Div n$ equal to twice the mean curvature, saddle splay
+%$\det \nabla n$ equal to the Gauss curvature, and both twist and tilt
+%are equal to zero.
 
@@
 \subsubsection{Anticipated model simulations}
-To characterize material properties, we compare the energies and forces generated by
+To characterize material properties of a bilayer, we compare the energies and forces generated by
 a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
-The specific goals are {\bf (i)} to assess whether the energies \eqref{ansatz3} are the same
-for all reasonable deformation and if this is the case {\bf (ii)} to determine the value of the elastic $\KB$,
-$\KT$, $\KG$ and $\KTH$; {\bf (iii)} us to understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli.
-
-Motivated by our preliminary results \cite{Fu2018_SIAM}
-we use realistic values for particle diameter $2$ nm \cite{Boal},
-screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
-and interfacial tension $\gamma=4.1$ pN nm$^{-1}$ \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
-model parameters. The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
-particle diameter and the hydrophobic boundary condition \eqref{SL}
-are additional parameters defining the coarse-grained representation.
+We propose to first {\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
+as the corresponding energies in the particle system for all reasonable deformation.
+If this is the case we will {\bf (ii)} determine the value of the elastic $\KB$,
+$\KT$, $\KG$ and $\KTH$, and then {\bf (iii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
+%
+%Motivated by our preliminary results \cite{Fu2018_SIAM}
+%we use realistic values for particle diameter $2$ nm \cite{Boal},
+%screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
+%and interfacial tension $\gamma=4.1$ pN nm$^{-1}$ \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
+%model parameters. The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
+%particle diameter and the hydrophobic boundary condition \eqref{SL}
+%are additional parameters defining the coarse-grained representation.
 

### 2020-11-12 NSF2020/Description/specificaim2_ver2.tex
RJR tidying up SA2

@@
-%\subsection{Specific Aim 2: Functional Materials}
 \subsection{Specific Aim 2: Hydrodynamics}
 \label{subsec:specific_aim_2}
-Specific Aim 1 dealt with elastic material properties of self-assembled collections of amphiphiles.
 In Specific Aim 2, we include hydrodynamics effects by embedding the particles in a solvent. 
-We divide space into the fluid phase and the rigid particle phase.
-The fluid phase is modeled by the Stokes equations for an incompressible, zero Reynolds-number fluid. These are coupled to the screened-Laplace equation \eqref{SL}
-through viscous and hydrophobic stress balance.
-We develope a numerical solver for the mobility problem. 
-This leads to simulations of bilayers in external flows where the bilayers are represented by a self-assebled collection of rigid particles.
-Finally, we work toward three-dimensional solvers with application in the capillary driven fabrication of micro-materials.
-
+As described in \eqref{eq:stokes} and illustrated in Figure \ref{fig:flow_map}, 
+the solvent phase is modeled by the Stokes equations for an incompressible, zero Reynolds-number fluid, 
+and these equations are coupled to the screened-Laplace equation \eqref{SL} through viscous and hydrophobic stress balance.
 Hydrodynamic effects are a relevant detail  
 because the rates of biological functions like fusion, fission, and pore dynamics rely on viscous dissipation \cite{RYHAM20112929}. 
-While hydrophobic attraction causes the particles to self-assemble indepedently of the dissipation mechanism, the trajectories and
-equilibrium configurations depend on the fact that the particles travel through a viscous environment. 
+%While hydrophobic attraction causes the particles to self-assemble indepedently of the dissipation mechanism, the trajectories and
+%equilibrium configurations depend on the fact that the particles travel through a viscous environment. 
 Additionally, coarse-grained and molecular dynamics theories include water either explicitly or implicitly in their models. 
+The goal is to be able to simulate vesicle bilayers in external flows, where the bilayers are represented by a self-assembled collection of rigid particles.
 
-\textbf{Model equations.}
-The hydrodynamic interactions enter through the transmission of viscous stresses from one particle to the another.  
-We must solve the system 
-\setcounter{midequation}{\theequation}
-\addtocounter{midequation}{2}
+\begin{figure}[h]
+  \centering{\includegraphics[width=0.8\textwidth]{Figures/domain.pdf}}
+    \caption{\label{fig:flow_map}}
+\end{figure}
 
-\begin{minipage}[t]{0.44\textwidth}
-\begin{subequations}
-\begin{alignat}{2}
-\label{St1} -& \mu \Delta {\bf u} + \nabla p = {\bf 0}, \\
-\label{St2}  & \nabla \cdot {\bf u} = 0,                &&   \text{in } \Omega\\
-\label{St3}  & {\bf u }({\bf x}) = {\bf v}_i + {\bf w_i}\times {\bf x}, \;  && \text{for } {\bf x} \in \partial P_i\\
-\label{St4}  & ({\bf u } - {\bf u}_{\infty})({\bf x}) \to {\bf 0} && \text{as } {\bf x} \to \infty\\
-\notag \\
-\tag{\themidequation}
-\label{HSB1}  & \int_{\partial P_i} \boldsymbol{\sigma} \boldsymbol{\nu} \,\dif S + {\bf F}_{i} = {\bf 0}\span \span
-\end{alignat}
-\end{subequations}
-\end{minipage}
-\addtocounter{equation}{1}
-\setcounter{midequation}{\theequation}
-\addtocounter{midequation}{2}
-\begin{subequations}
-\begin{minipage}[t]{0.5\textwidth}
-\begin{alignat}{2}
-\label{SL1}  - & \rho^2 \Delta u +u = 0, && \text{in } \Omega\\
-\label{SL2}   & u({\bf x}) = f_i({\bf x}),\quad  && \text{for } {\bf x} \in \partial P_i\\
-\label{SL3} &  u({\bf x}) \to 0 && \text{as } {\bf x} \to \infty \\
-\notag \\
-\notag \\
-\tag{\themidequation}
-\label{HSB2}   & \int_{\partial P_i} {\bf x} \times \boldsymbol{\sigma} \boldsymbol{\nu} \,\dif S + {\bf G}_{i} = {\bf 0} \span \span\\
-\notag
-\end{alignat}
-\end{minipage} 
-\end{subequations}
+%We must solve the system 
+%\setcounter{midequation}{\theequation}
+%\addtocounter{midequation}{2}
+%\begin{minipage}[t]{0.44\textwidth}
+%\begin{subequations}
+%\begin{alignat}{2}
+%\label{St1} -& \mu \Delta {\bf u} + \nabla p = {\bf 0}, \\
+%\label{St2}  & \nabla \cdot {\bf u} = 0,                &&   \text{in } \Omega\\
+%\label{St3}  & {\bf u }({\bf x}) = {\bf v}_i + {\bf w_i}\times {\bf x}, \;  && \text{for } {\bf x} \in \partial P_i\\
+%\label{St4}  & ({\bf u } - {\bf u}_{\infty})({\bf x}) \to {\bf 0} && \text{as } {\bf x} \to \infty\\
+%\notag \\
+%\tag{\themidequation}
+%\label{HSB1}  & \int_{\partial P_i} \boldsymbol{\sigma} \boldsymbol{\nu} \,\dif S + {\bf F}_{i} = {\bf 0}\span \span
+%\end{alignat}
+%\end{subequations}
+%\end{minipage}
+%\addtocounter{equation}{1}
+%\setcounter{midequation}{\theequation}
+%\addtocounter{midequation}{2}
+%\begin{subequations}
+%\begin{minipage}[t]{0.5\textwidth}
+%\begin{alignat}{2}
+%\label{SL1}  - & \rho^2 \Delta u +u = 0, && \text{in } \Omega\\
+%\label{SL2}   & u({\bf x}) = f_i({\bf x}),\quad  && \text{for } {\bf x} \in \partial P_i\\
+%\label{SL3} &  u({\bf x}) \to 0 && \text{as } {\bf x} \to \infty \\
+%\notag \\
+%\notag \\
+%\tag{\themidequation}
+%\label{HSB2}   & \int_{\partial P_i} {\bf x} \times \boldsymbol{\sigma} \boldsymbol{\nu} \,\dif S + {\bf G}_{i} = {\bf 0} \span \span\\
+%\notag
+%\end{alignat}
+%\end{minipage} 
+%\end{subequations}
+%\noindent for $i = 1,\dots, N$.
 
-\noindent for $i = 1,\dots, N$.
-The equations \eqref{St1}--\eqref{HSB2} express a two-way coupling between the flow and bilayer shape.
-The particle laden flow changes the shape of the bilayer, and in return the hydrophobic stresses coming
-from the altered shape impart a force on the flow. 
-The inputs to \eqref{St1}--\eqref{HSB2} are the collection of particle configurations.
-Within this system, the activity $u$ solves the screened Laplace equation \eqref{SL1} with the material label boundary condition \eqref{SL2}
-and far-field condition \eqref{SL3}. The forces ${\bf F}_i$ and torques ${\bf G}_i$ come from \eqref{totalFG}.
-In turn, the fluid velocity ${\bf u}$ solves the Stokes equations (\ref{St1}, \ref{St2}) with background flow boundary condition (\ref{St3}).
-The force and torque equations \eqref{HSB1}, \eqref{HSB2} couple the (\ref{St1}--\ref{St4}) to (\ref{SL1}--\ref{SL3}).
-The outputs are the collection of velocity and rotation pairs $({\bf v}_i, {\bf w}_i)$ that uniquely satisfy the rigid body boundary condition \eqref{St3}.
+\textbf{Vesicles in background flows.}
+Numerically solving the Stokes-screened Laplace system \eqref{SL}, \eqref{eq:stokes} is a nontrivial matter,
+and we will develop an efficient, robust, high-order of accuracy in time and space algorithm suited to the problem. 
+The challenges are: \textbf{(1)} the equations express a two-way coupling.
+This means that the flow changes the shape of the bilayer (or particle suspension, more generally),
+and in return the hydrophobic stresses coming from the altered shape imparts a force on the flow. 
+\textbf{(2)}
+The inputs to the Stokes equations are particle configurations, forces and torques. 
+The outputs are the rigid body translation and angular velocties used to update the particle positions (see Figure \ref{fig:flow_map}).
+Although the underlying equations are linear, the overall problem is highly nonlinear because the domain is constantly changing.
+\textbf{(3)} Self-assembly causes the particles to come into close contact.  
+As a result, a exceptional spatial accuracy is required to resolve the fields between adjacent particles.
+Finally, the physically relevant elastic properties of bilayer become apparent at large length scales and for large particle-numbers,
+which increases the computational complexity of our simulations.
 
-The particle velocity and rotation $({\bf v}_i, {\bf w}_i)$ update the particle configurations:
-\begin{alignat}{3}
-\label{Hupdate1}   \frac{\dif {\bf a}_i}{\dif t} = {\bf v}_i,      \quad  \frac{\dif {\bf R}_i}{\dif t}  = A({\bf w}_i),\quad i = 1, \dots, N.
-\end{alignat}
-Recall that $A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
-Also, ${\bf a}_i$ is the particle center the rotation matrix ${\bf R}_i$ defines the orientation.
-That way, the particle configurations come from the flow maps $F_i({\bf x},t) = {\bf a}_i(t) + {\bf R_i}(t){\bf x}$ with
-$P_i(t) = F_i(P_{0i},t)$ and $f_i(F_i({\bf x},t)) = f_{i0}({\bf x})$ where $P_{i0}$ and $f_{i0}$ are the $i$th reference particle
-and material label respectively.
-When there is no background flow ${\bf u}_{\infty} = {\bf 0}$, the system obeys the energy law
-$\frac{\dif}{\dif t} \Phi + \int_{\Omega(t)} \mu |\nabla {\bf u} + \nabla {\bf u}^T|^2 \,dx = 0,$ 
-and the particle configurations tend toward a local equilibrium.
-
-Numerically solving \eqref{St1}--\eqref{HSB2} is a nontrivial matter.
-The principle challenges are \textbf{(1)} the domain $\Omega(t)$ and boundary conditions $f_i$ are constantly changing
-with changes in the particle configuration \textbf{(2)} a high degree of spatial accuracy is required to resolve the fields 
-between adjacent particles and \textbf{(3)} the computational complexity grows with the number of particles. 
-Specific Aim 3 describes how we address these challenges.
-
-\textbf{Simulation studies.}
-We simulate two-dimensional vesicle bilayers in external flows using \eqref{St1}--\eqref{HSB2}.
-The vesicle bilayer is formed by a many-body collection of amphiphilic particles.
-At large length scales and for large particle-number, the bilayer behaves as an elastic membrane,
-in two-dimensions an elastic curve. 
-This will lead to a deeper understanding of the elastic properties established by Specific Aim 2.
-
-We consider two kinds of external flows: shear flow and extensional flow. 
-Specifically, we deal with the background flow using the representation 
+We include a background flow by replacing the third equation in \eqref{eq:stokes} with the condition
+$(\mathbf{u} - \mathbf{u}_{\infty})(\mathbf{x}) \to \mathbf{0}$ as $|\mathbf{x}| \to \infty.$ 
+One way to ensure this far-field condition is through the represention 
 \begin{equation}
@@
 \end{equation}
-where $S(\cdot, {\bf a}_i)$ and $ R(\cdot, {\bf a}_i)$ are stokeslets and rotlets supported at the particle centers ${\bf a}_i.$
-The symbol $D$ denotes the Stokes double layer integral operator (see Specific Aim 3).   
-The representation \eqref{PowerMiranda} automatically satisfies \eqref{St1}, \eqref{St2}, \eqref{St4} and \eqref{HSB1}.
-We solve for the unknown density $\eta : \partial \Omega \to \mathbb{R}$ by requiring that jump in viscous stress
-vanished across $\partial P_i$. This jump condition guarantees that ${\bf u}$ is a rigid motion within each particle,
-and by continuity, equals a rigid motion on the particle boundary as required by \eqref{St3}.
+where $S$ and $R$ are stokeslets and rotlets supported at the respective particle centers 
+and $D\eta$ is a double layer integral operator for an unknown density function $\eta.$ 
+The representation \eqref{PowerMiranda} automatically satisfies all equations with the exception of the rigid motion boundary conditions. 
+These conditions follow by requiring the viscous stress vanishes across the particle boundaries.
 
@@
 }
-\end{wrapfigure}Finally, the particle-based vesicle bilayers have two distinct leaflets.
+\end{wrapfigure}
+
+Finally, the particle-based vesicle bilayers have two distinct leaflets.
 The inner and outer leaflets consists of the particles in contact with the vesicle interior and 

### 2020-11-12 NSF2020/Description/specificaim2_ver2.tex
RJR

@@
 %equilibrium configurations depend on the fact that the particles travel through a viscous environment. 
-Additionally, coarse-grained and molecular dynamics theories include water either explicitly or implicitly in their models. 
-The goal is to be able to simulate vesicle bilayers in external flows, where the bilayers are represented by a self-assembled collection of rigid particles.
+Additionally, hydrodynamics interactions are central fabrication of complex microscopic three-dimensional structures \cite{Cho2010}.
+Over the past decade, there has been an explosion of interest in small-scale processes that utilize capillary forces dominate,  van der Waals interactions and thermal noise  \cite{Zhang2017}, to coordinated movement and bind  material subunits, \cite{Pandey2011,Leong2007,Reynolds2019, Dasgupta2017,Siontorou2017}.
+Finally, coarse-grained and molecular dynamics theories include water either explicitly or implicitly in their models. 
+The immediate goal of the present proposal
+is to be able to simulate vesicle bilayers in external flows, where the bilayers are represented by a self-assembled collection of rigid particles.
 
@@
 where $S$ and $R$ are stokeslets and rotlets supported at the respective particle centers 
-and $D\eta$ is a double layer integral operator for an unknown density function $\eta.$ 
+and $D\eta$ is an appropriate double layer integral operator for an unknown density function $\eta.$ 
 The representation \eqref{PowerMiranda} automatically satisfies all equations with the exception of the rigid motion boundary conditions. 
@@
 We will compare the behavior of our particle-based vesicles in Stokes flow to well-established results.
+\todo{What are the known results?}
 To test area incompressibility, we form the bilayer midplane by fitting to the particle centers. Under moderate shear rates,
@@
 \textbf{Novel reciprocal relations.}
+We use a double layer The velocity field  double layer potential representation.
+This representation involves a strongly singular integral, and without the aid of specilized
+quadrature routines, leads to large numerical errors when evaluating the the hydrophobic stress \eqref{stress} along the particle boundaries (see Figure \cite{fig:bierror}).
 We prove a, to our knowledge new, result concerning the evaluation of Maxwell-type stresses. 
@@
 \end{proposition}
-As described in Specific Aim 3, we solve \eqref{SL1}--\eqref{SL3}  using a double layer potential representation.
-This representation involves a strongly singular integral, and without the aid of specilized
-quadrature routines, leads to large numerical errors when evaluating the the hydrophobic stress \eqref{stress} along the particle boundaries (see Figure \cite{fig:bierror}).
+
 The identity in Proposition \ref{prop:recip} gets around this critical issue by utilizing the fact that $u_j$, $j\neq i$ is smooth and the normal derivative
@@
 calculated by \eqref{eq:reciprocal} achieved $10^{-4}$ accuracy.
-
-Additionally, hydrodynamics interactions are also relevant the fabrication of complex microscopic three-dimensional structures \cite{Cho2010}.
-Over the past decade, there has been an explosion of interest in small-scale processes that utilize capillary forces dominate,  van der Waals interactions and thermal noise  \cite{Zhang2017}, to coordinated movement and bind  material subunits.
-Two prominent fabrication techniques are capillary origami
-\cite{Pandey2011,Leong2007,Reynolds2019} and colloidal self-assembly \cite{Dasgupta2017,Siontorou2017}.
-Capillary origami uses principles of elastocapilirity wherein elastic solids deform under surface tension \cite{Bico2018,VanHonschoten2010}.
-In self-assembly of colloids,
-particles exhibit similar thermodynamic behavior of molecular systems, except that the behavior occurs over observable, long time scales \cite{Zhang2017}. 
-and can determine which local equilibria the system tends towards.

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
yny specific aim 1

@@
 \cite{SeLeMaEg17,Saetal20, Pietal20}, which require resolution of the internal structure of the membrane.  
+Recently, there has been a revival in interest in the HK theory as the quadratic assumption
+for the elasticity energy density has caused
 %Using the HK  model as a base,
@@
 %
-Recently, there has been a revival in interest in the HK theory as the quadratic assumption
-for the elasticity energy density has caused researchers to question the applicability of \eqref{ansatz3} for large curvatures \cite{PhysRevLett.117.188102, ARGUDO20161619}. 
+\begin{wrapfigure}[12]{l}{0.47\textwidth}
+\centerline{\includegraphics[width=0.47\textwidth]{Figures/Deformations.pdf}}
+%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
+\caption{\label{fig:deformations}Sketch of the HK membrane model \cite{Hamm2000}.
+    }
+\end{wrapfigure}
+%
+ researchers to question the applicability of \eqref{ansatz3} for large curvatures \cite{PhysRevLett.117.188102, ARGUDO20161619}. 
 For example, Galimzyanov {\it et al.} \cite{C9SM02079A} countered that energies derived from molecular dynamics and elasticity agree, even when curvatures are large.
@@
 
-\begin{figure}
-  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
-  \caption{\label{fig:deformations}Sketch of the HK membrane model \cite{Hamm2000}.
-    }
-\end{figure}
+%\begin{wrapfigure}[13]{l}{0.5\textwidth}
+%\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
+%\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
+%diaphragm expansion (ii) and pore formation (iii). 
+%(B) Saddle-splay energy for each change in \emph{monolayer} topology
+%calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
+%\label{fig:barriers}
+%\end{wrapfigure}
 
@@
 %\end{center}
-\subsubsection{Anticipated model simulations}
-To characterize material properties of a bilayer, we compare the energies and forces generated by
-a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
-We propose to first {\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
-as the corresponding energies in the particle system for all reasonable deformation.
-If this is the case we will {\bf (ii)} determine the value of the elastic $\KB$,
-$\KT$, $\KG$ and $\KTH$, and then {\bf (iii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
+\subsubsection{Simulations of the HARP model to estimate elastic moduli}
+%To characterize material properties of a bilayer, we compare the energies and forces generated by
+%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
+We propose to
 %
-%Motivated by our preliminary results \cite{Fu2018_SIAM}
-%we use realistic values for particle diameter $2$ nm \cite{Boal},
-%screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
-%and interfacial tension $\gamma=4.1$ pN nm$^{-1}$ \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
-%model parameters. The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
-%particle diameter and the hydrophobic boundary condition \eqref{SL}
-%are additional parameters defining the coarse-grained representation.
+%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
+%for a wide range of particle parameters and physical parameters in HARP to 
+%
+%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
+%as the corresponding energies in the particle system for all reasonable deformation.
+%If this is the case we will 
+%
+{\bf (i)} determine the value of the elastic moduli $\KB$,
+$\KT$, $\KG$ and $\KTH$, and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
+An accurate and robust way to measure material properties is to track the evolution of the bilayer as
+%
+\begin{wrapfigure}[10]{r}{0.4\textwidth}
+\vspace{-0.3cm}
+\centerline{\includegraphics[width=0.4\textwidth]{Figures/Flattening.pdf}}
+%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
+\vspace{-0.2cm}
+\caption{\label{fig:flattening}Example of computing bending modulus of a lipid bilayer from particle simulation.
+    }
+\end{wrapfigure}
+it relaxes from an initially non-equilibrium configuration.
+Figure~\ref{fig:flattening} is an example where the initial configuration of a lipid bilayer patch contains only splay deformation without any other components (saddle splay, twist and tilt). 
+As the bent membrane flattens we find that both the membrane self-interaction energy $\Phi$ and the elastic energy ${\cal W}$ decrease, and the slope gives the
+splay modulus in this case.
 
-An accurate and robust way to measure material properties is to track the evolution of the bilayer. 
-Here we start with a particle-based bilayer in a non-equilibrium shape, and then evolve the particle bilayer by steepest gradient descent with respect to the
-HARP functional:
+%To characterize material properties of a bilayer, we compare the energies and forces generated by
+%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
+%We propose to first {\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
+%as the corresponding energies in the particle system for all reasonable deformation.
+%If this is the case we will {\bf (ii)} determine the value of the elastic $\KB$,
+%$\KT$, $\KG$ and $\KTH$, and then {\bf (iii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
+%%
+%%Motivated by our preliminary results \cite{Fu2018_SIAM}
+%%we use realistic values for particle diameter $2$ nm \cite{Boal},
+%%screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
+%%and interfacial tension $\gamma=4.1$ pN nm$^{-1}$ \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
+%%model parameters. The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
+%%particle diameter and the hydrophobic boundary condition \eqref{SL}
+%%are additional parameters defining the coarse-grained representation. 
+%
+%An accurate and robust way to measure material properties is to track the evolution of the bilayer.
+
+Here we start with a particle-based bilayer in a specific non-equilibrium shape that consists of only one component of the displacement in figure~\ref{fig:deformations}, 
+and then evolve the particle system
+%bilayer by steepest gradient descent 
+with respect to the HARP functional:
 \begin{equation}
@@
 $A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
-We solve \eqref{SGD} numerically 
-using an Adams–Bashforth linear multistep method. The procedure involves solving \eqref{SL} based off of the current particle configuration.
+%We solve \eqref{SGD} numerically  using an Adams–Bashforth linear multistep method. 
+The procedure involves solving \eqref{SL} based off of the current particle configuration.
 We then use the solution $u$ to calculate the collection of forces and torques \eqref{forceandtorque}, and update the particle configuration
@@
 
+\begin{wrapfigure}[12]{l}{0.32\textwidth}
+\centerline{\includegraphics[width=0.32\textwidth]{Figures/SaddleSplayDiagram.pdf}}
+\caption{
+\label{fig:saddle_splay}  
+Determination of saddle splay modulus.
+}
+\end{wrapfigure}
+%
 The evolution \eqref{SGD} satisfies the energy dissipation law $\frac{\dif }{\dif t} \Phi \leq 0$
@@
 
-In certain instances, the bilayer evolution involves only one or a few of the four fundamental deformations.
-When this occurs, the elastic moduli derive from the coefficients of the linear regression between the HAP energy $\Delta \Phi = \Phi - \Phi_0$
-and continuum energies and $\Delta E = E - E_0$, where  $\Phi_0$ and $E_0$ are respective equilibrium values.
+%In certain instances, the bilayer evolution involves only one or a few of the four fundamental deformations.
+%When this occurs, the elastic moduli derive from the coefficients of the linear regression between the HAP energy $\Delta \Phi = \Phi - \Phi_0$
+%and continuum energies and $\Delta E = E - E_0$, where  $\Phi_0$ and $E_0$ are respective equilibrium values.
 
-Since it is a particle-based method, the HAP model has a number of advantages over continuum-based descriptions.
-The elastic energy \eqref{ansatz3} couples director gradients to surface geometry through
-the tilt vector field.  Furthermore, bilayer energy is the sum of two monolayer
-energies and the distance between these monolayers varies according to \eqref{LMdeformation}.
-Effects like tilt and varying monolayer thickness appear at lipid domain boundaries, the edge of nanopores and at the boundary of membrane inclusions \cite{PhysRevE.102.042406}.
-These effects are present in the proposed formulation, and the particle-based bilayers can break open and join monolayer-wise 
-as required by fussion and fission.
+%
+%Since it is a particle-based method, the HAP model has a number of advantages over continuum-based descriptions.
+%The elastic energy \eqref{ansatz3} couples director gradients to surface geometry through
+%the tilt vector field.  Furthermore, bilayer energy is the sum of two monolayer
+%energies and the distance between these monolayers varies according to \eqref{LMdeformation}.
+%Effects like tilt and varying monolayer thickness appear at lipid domain boundaries, the edge of nanopores and at the boundary of membrane inclusions \cite{PhysRevE.102.042406}.
+%These effects are present in the proposed formulation, and the particle-based bilayers can break open and join monolayer-wise 
+%as required by fussion and fission. 
+%
+%Bending is the energetically most consequential deformations. To measure a bending modulus,  
+%we deform the midplane of a planar bilayer into the shape of a circular arc.
+%This arc stores bending energy in the form of splay $\Div {\bf n}$, while twist, saddle-splay and tilt deformations are zero.
+%The splay in the two leaflets approximately cancel when added, making the contribution of spontaneous curvature negligible.
+%In the case of a rectangular bialyer, the corresponding elastic energy 
+%$E = \int_{\Sigma} \KB \kappa^2$ where $\kappa$ is the curvature of the curved cross-section $C$.
+%Figure \ref{} shows the approximately linear relationship between $\Delta \Phi$ and $\Delta E$
+%used to values for infer $\KB$.
 
-Bending is the energetically most consequential deformations. To measure a bending modulus,  
-we deform the midplane of a planar bilayer into the shape of a circular arc.
-This arc stores bending energy in the form of splay $\Div {\bf n}$, while twist, saddle-splay and tilt deformations are zero.
-The splay in the two leaflets approximately cancel when added, making the contribution of spontaneous curvature negligible.
-In the case of a rectangular bialyer, the corresponding elastic energy 
-$E = \int_{\Sigma} \KB \kappa^2$ where $\kappa$ is the curvature of the curved cross-section $C$.
-Figure \ref{} shows the approximately linear relationship between $\Delta \Phi$ and $\Delta E$
-used to values for infer $\KB$.
+We propose to conduct calculations similar to the example of figure~\ref{fig:flattening} for other elastic moduli such as the effective saddle splay modulus $\KG$:
+%for a wide range of particle parameters and physical parameters in HARP to 
+%
+%We will also determine the effective saddle splay modulus $\KG$. 
+The gradient descent technique is ineffective for measuring $\KG$ because
+the saddle splay energy is largely invariant under shape changes.
+In the simplified Canham-Helfrich formulation, saddle splay energy is an indicator of topological transitions, thanks to the  Gauss-Bonnet theorem
+\cite{TerziDeserno17}.
+PI-RR showed that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}.
 
+To evaluate $\KG$, we will combine the string method from PI-Ryham's work on fusion \cite{RyKlYaCo16} with
+the present particle simulations. 
+%The string method is a numerical scheme that finds
+%least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}.
+%Using the string method, we will evaluate the transition energies between the intact pancake shape,
+%and one with a pore. Pore formation in a single bilayer decreases the integral of saddle splay from $4\pi$
+%to $0$. We can, in principle, detect this drop in energy because we have already accounted for the other deformations. 
+%
+%%We will also analyze $\KG$ using a helical geometry. In a helicoid with inclination $m$, the director
+%%gradient is $\nabla n = \begin{pmatrix} 0 & m(m^2+x_1^2)^{-1} \\ m(m^2+x_1^2)^{-1} & 0\end{pmatrix}$ where $x_1$ is the distance to the central
+%%axis. We observe that saddle splay, twist and tilt are zeros, and $\det \nabla n = m^2(m^2+x_1^2)^{-2}$.
+%%In the simulations, the particles forming the helicoid will be confined to two, concentric cylinders. The
+%%continuum energy $\tfrac{1}{2}\KG h(m x_1(m^2+x_1^2)^{-1} + \tan^{-1}(x_1/m)) |_{r_1}^{r_2}$ where $h$, $r_1$ and $r_2$
+%%are the cylinder heights, inner cylinder radius, and outer cylinder radius, respectively. 
+%
 The twist deformation is a fully three-dimensional deformation. 
@@
 
-To measure the twise modulus, we place a single monolayer on a hydrophobic substrate 
-and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
-yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
-  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
-  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
-  This gives the continuum elastic energy equals
-  \begin{equation}
-    \label{eq:twist_energy}
-    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
-  \end{equation}
-  which we compare to the HAP simulation data.
+The proposed particle-based simulations of the HARP model in equations~\ref{SGD} also allow direct examination on the assumption of quadratic form of the elastic energy density.
+As discussed earlier, recent disagreement in elastic moduli between continuum model and MD simulations originates from such assumption. 
+The particle-based HARP model provides a unique opportunity to examine the validity of the quadratic elastic energy, and the PIs propose to examine how (if) any deviation from the quadratic elastic energy may depend on the microscopic details of the amphiphilic particles and their interactions.
 
-We will also determine the effective saddle splay modulus $\KG$. 
-The gradient descent technique is ineffective for measuring $\KG$ because
-the saddle splay energy is largely invariant under shape changes.
-In the simplified Canham-Helfrich formulation, saddle splay energy is an indicator of topological transitions, thanks to the  Gauss-Bonnet theorem
-\cite{TerziDeserno17}.
-PI-Ryham showed that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}.
+%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
+%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
+%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
+%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
+%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
+%  This gives the continuum elastic energy equals
+%  \begin{equation}
+%    \label{eq:twist_energy}
+%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
+%  \end{equation}
+%  which we compare to the HAP simulation data.
 
-\begin{wrapfigure}[16]{r}{0.32\textwidth}
-\centerline{\includegraphics[width=0.32\textwidth]{Figures/SaddleSplayDiagram.pdf}}
-\caption{
-\label{fig:saddle_splay}  
- TBD
-}
-\end{wrapfigure}
-To evaluate $\KG$, we will combine the string method from PI-Ryham's work on fusion \cite{RyKlYaCo16} with
-the present particle simulations. The string method is a numerical scheme that finds
-least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}.
-Using the string method, we will evaluate the transition energies between the intact pancake shape,
-and one with a pore. Pore formation in a single bilayer decreases the integral of saddle splay from $4\pi$
-to $0$. We can, in principle, detect this drop in energy because we have already accounted for the other deformations.
-
-%We will also analyze $\KG$ using a helical geometry. In a helicoid with inclination $m$, the director
-%gradient is $\nabla n = \begin{pmatrix} 0 & m(m^2+x_1^2)^{-1} \\ m(m^2+x_1^2)^{-1} & 0\end{pmatrix}$ where $x_1$ is the distance to the central
-%axis. We observe that saddle splay, twist and tilt are zeros, and $\det \nabla n = m^2(m^2+x_1^2)^{-2}$.
-%In the simulations, the particles forming the helicoid will be confined to two, concentric cylinders. The
-%continuum energy $\tfrac{1}{2}\KG h(m x_1(m^2+x_1^2)^{-1} + \tan^{-1}(x_1/m)) |_{r_1}^{r_2}$ where $h$, $r_1$ and $r_2$
-%are the cylinder heights, inner cylinder radius, and outer cylinder radius, respectively.
-
-\subsubsection{New mathematical analysis}
+\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$}
 
@@
 $A(P_1 \Delta P_2)$ is the area of the symmetric difference of the overlap.  
+\cite{https://doi.org/10.1038/s41467-019-09787-6}
 

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
RJR

@@
 consisting of straight fibers that represent elongated hydrocarbon chains. HK assumed an
-elastic energy density ${\cal W}$ quadratic in the Green-Lagrange strain tensor for membrane deformation ${\bf x}$.
+elastic energy density ${\cal W}$ that quadratic in the Green-Lagrange strain tensor for membrane deformation of
+this striated, internal structure.
 %
@@
 \end{wrapfigure}
-it relaxes from an initially non-equilibrium configuration.
-Figure~\ref{fig:flattening} is an example where the initial configuration of a lipid bilayer patch contains only splay deformation without any other components (saddle splay, twist and tilt). 
-As the bent membrane flattens we find that both the membrane self-interaction energy $\Phi$ and the elastic energy ${\cal W}$ decrease, and the slope gives the
-splay modulus in this case.
+it relaxes from an initially non-equilibrium configuration \cite{PhysRevLett.117.188102}.
+Figure~\ref{fig:flattening} shows an example where the initial configuration of a lipid bilayer patch contains only
+splay deformation without any other components (saddle splay, twist and tilt). 
+As the bent membrane flattens we find that both the membrane self-interaction energy $\Phi$ and the elastic energy ${\cal W}$ decrease,
+and because the saddle splay, twist and tilt stay zeros, the slope gives the bending modulus in this case.
 

### 2020-11-12 NSF2020/Description/specificaim2_ver2.tex
RJR

@@
 $(\mathbf{u} - \mathbf{u}_{\infty})(\mathbf{x}) \to \mathbf{0}$ as $|\mathbf{x}| \to \infty.$ 
-One way to ensure this far-field condition is through the represention 
+The main idea to incorporate the far-field flow is to use the representation 
 \begin{equation}
 \label{PowerMiranda}
-{\bf u} = {\bf u}_{\infty} + D\eta + \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + R(\cdot, {\bf a}_i) {\bf G}_i.
+{\bf u} = {\bf u}_{\infty} + K\eta + \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + R(\cdot, {\bf a}_i) {\bf G}_i.
 \end{equation}
 where $S$ and $R$ are stokeslets and rotlets supported at the respective particle centers 
-and $D\eta$ is an appropriate double layer integral operator for an unknown density function $\eta.$ 
-The representation \eqref{PowerMiranda} automatically satisfies all equations with the exception of the rigid motion boundary conditions. 
-These conditions follow by requiring the viscous stress vanishes across the particle boundaries.
+and $K\eta$ is a layer potential for an unknown density function $\eta.$ 
+The representation \eqref{PowerMiranda} automatically satisfies all equations, with the exception of the rigid motion conditions. 
+These rigid motion conditions follow by requiring the viscous stress vanishes across the particle boundaries.
 
@@
 
-\begin{wrapfigure}[16]{r}{0.32\textwidth}
+\begin{wrapfigure}[13]{r}{0.32\textwidth}
 \centerline{\includegraphics[width=0.32\textwidth]{figures/BIError.pdf}}
@@
 \label{fig:bierror}  
-  Gradient error between an exact and boundary integral solution of \eqref{SL}.
+The numerical error in integral representations blows up near boundaries.
 }
@@
 \textbf{Novel reciprocal relations.}
-We use a double layer The velocity field  double layer potential representation.
-This representation involves a strongly singular integral, and without the aid of specilized
-quadrature routines, leads to large numerical errors when evaluating the the hydrophobic stress \eqref{stress} along the particle boundaries (see Figure \cite{fig:bierror}).
+We use a boundary integral representation for the velocity field. Due to singular behavior of the
+kernels, the boundary integrals can have large numerical epresentation without the aid of specilized
+quadrature routines, leads to large numerical errors when evaluating the the hydrophobic
+stress \eqref{stress} along the particle boundaries (see Figure \cite{fig:bierror}).
 We prove a, to our knowledge new, result concerning the evaluation of Maxwell-type stresses. 

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
yny specific aim 1

--- 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
@@
 
-The proposed particle-based simulations of the HARP model in equations~\ref{SGD} also allow direct examination on the assumption of quadratic form of the elastic energy density.
-As discussed earlier, recent disagreement in elastic moduli between continuum model and MD simulations originates from such assumption. 
-The particle-based HARP model provides a unique opportunity to examine the validity of the quadratic elastic energy, and the PIs propose to examine how (if) any deviation from the quadratic elastic energy may depend on the microscopic details of the amphiphilic particles and their interactions.
+%The proposed particle-based simulations of the HARP model in equations~\ref{SGD} also allow direct examination on the assumption of quadratic form of the elastic energy density.
+%As discussed earlier, recent disagreement in elastic moduli between continuum model and MD simulations originates from such assumption. 
+%The particle-based HARP model provides a unique opportunity to examine the validity of the quadratic elastic energy, and the PIs propose to examine how (if) any deviation from the quadratic elastic energy may depend on the microscopic details of the amphiphilic particles and their interactions.
 
-%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
-%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
-%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
-%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
-%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
-%  This gives the continuum elastic energy equals
-%  \begin{equation}
-%    \label{eq:twist_energy}
-%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
-%  \end{equation}
-%  which we compare to the HAP simulation data.
-
-\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$}
-
-We will develop some of the mathematical connections between the HAP energy and the energy functionals used in the gradient theory of phase transitions. 
-The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
-The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
-to the characteristic function of a set solving a perimeter minimization problem 
-\cite{Modica87, MODICA1987487, LuMo89}.
-
-Analogously, the HAP energy converges to the surface energy in the limit of vanishing screening length 
-and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
-area measures supported on the particle boundaries. 
-PI RR has worked directly on phase field approximations of membrane bending energy 
-\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman equation \cite{1531-3492_2006_2_357,Lee2018}.
-The proposed analysis is a natural outgrowth or prior work because the linearization of the Poisson-Boltzmann equation is the screened Laplace equations \eqref{SL}.
-One of the basic questions is to establish the HAP convergence rate as a function of particle geometry 
-\cite{LuMo89}, which is an essential benchmark for numerical validation. 
-In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  
-As an illustration, consider two fluid-bound plates $P_1$ and $P_2$ that geometrically flat and hydrophobic all sides.
-We conjecture that in the zero-screening length limit, the plates have overlapping faces, and that 
-\begin{equation}
-\lim_{\rho \to 0} \min \Phi_{\text{hydro}} = \max_{\mathcal{X}} A(P_1 \Delta P_2)
-\end{equation}
-$A(P_1 \Delta P_2)$ is the area of the symmetric difference of the overlap.  
-\cite{https://doi.org/10.1038/s41467-019-09787-6}
-
+\subsubsection{HK elastic energy form}
 It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
@@
 
-The form of the elastic energy density \eqref{ansatz3} is the same as
-the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
-a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
-The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
-liquid crystal theory. However, the ``bend'' distortion from nematics  
-is not present in monolayers since the directors have no dependence in the normal direction.
-There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection.
+% The form of the elastic energy density \eqref{ansatz3} is the same as
+%the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
+%a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
+%The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
+%liquid crystal theory. However, the ``bend'' distortion from nematics  
+%is not present in monolayers since the directors have no dependence in the normal direction.
+%There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection.
 
@@
   terms of the orthonormal frame $\{{\bf e}_1, {\bf e}_2, {\bf N}\}$ with surface tangent vectors ${\bf e}_i$ and surface normal ${\bf N}$.  
-  In this frame, there is a coupling between the gradients of all three terms ${\bf x}_0,$ $\zeta$ and ${\bf n}$ of the deformation \eqref{LMdeformation}.
+  In this frame, there is a coupling between the gradients of all three terms ${\bf x}_0,$ $\zeta$ and ${\bf n}$ of the surface deformation field.
+  %\eqref{LMdeformation}.
   Subtle differential geometric arguments are needed to evaluate the terms in the Taylor expansion,
@@
 
-  We will revisit the HK analysis to see if any of the afore mentioned inconsitencies can be resolved.
+  We will revisit the HK analysis to see if any of the aforementioned inconsistencies can be resolved.
   As a main analytical innovation, we have found that expanding the strain tensor in
@@
   \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
-  incompressility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
+  incompressibility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
   However, we prove that when expressed in the $\{{\bf e}'_1, {\bf e}'_2, n\}$ frame, the incompressility condition is \emph{exact}
@@
   Aside from the special case of zero tilt, \cite{Hamm2000} and coworkers seem to have been unaware of this result.
+
+%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
+%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
+%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
+%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
+%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
+%  This gives the continuum elastic energy equals
+%  \begin{equation}
+%    \label{eq:twist_energy}
+%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
+%  \end{equation}
+%  which we compare to the HAP simulation data.
+
+%\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$}
+%The HAP energy converges to the surface energy in the limit of vanishing screening length 
+%and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
+%area measures supported on the particle boundaries.  This is analogous to the sharp interface limit in the phase-field functional formulation \cite{Modica87, MODICA1987487, LuMo89}. 
+%PI RR has worked directly on phase field approximations of membrane bending energy 
+%\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman equation \cite{1531-3492_2006_2_357,Lee2018}.
+%The proposed analysis is a natural outgrowth or prior work because the linearization of the Poisson-Boltzmann equation is the screened Laplace equations \eqref{SL}.
+%
+%We will develop some of the mathematical connections between the HAP energy and the energy functionals used in the gradient theory of phase transitions. 
+%%The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
+%%The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
+%%to the characteristic function of a set solving a perimeter minimization problem 
+%%\cite{Modica87, MODICA1987487, LuMo89}. 
+%%
+%%
+%One of the basic questions is to establish the HAP convergence rate as a function of particle geometry 
+%\cite{LuMo89}, which can be used as an essential benchmark for numerical validation. 
+%In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  
+%As an illustration, consider two fluid-bound plates $P_1$ and $P_2$ that geometrically flat and hydrophobic all sides.
+%We conjecture that in the zero-screening length limit, the plates have overlapping faces, and that 
+%\begin{equation}
+%\lim_{\rho \to 0} \min \Phi_{\text{hydro}} = \max_{\mathcal{X}} A(P_1 \Delta P_2)
+%\end{equation}
+%$A(P_1 \Delta P_2)$ is the area of the symmetric difference of the overlap.  
+%\cite{https://doi.org/10.1038/s41467-019-09787-6}
+
+% It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
+% whether \eqref{ansatz3} contains a complete list of consistent deformations.
+%\textbf{(i)} Researcher have assumed that $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}.
+%  Based on \eqref{eq:twist_energy}, a value $\KT = 0$ leads to the
+%  unphysical conclusion that there are bilayers with $\nabla {\bf n} \to \infty$ but $E \to 0.$ 
+%  \textbf{(ii)}
+%  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
+%  Later, \cite{C9SM02079A} 
+%  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
+%  from a transversal tilt invariance assumption.
+%  The PI Ryham showed,  that the tilt vector $T = {\bf n}/{\bf n}\cdot {\bf N} - {\bf N}$ leads to unphysical cusps when constraining membrane thickness  \cite{RyKlYaCo16}.  
+%  \textbf{(iii)}
+%  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
+%\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
+%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
+%Furthermore, the stability requirements of \eqref{ansatz3} are $\KB > 0$, $K_T > 0$, $\KG \geq -4\KB$
+%and $\KG \geq -4\KT$. Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14},
+%suggesting a somewhat smaller magnitude for $\KG$.
+
+%The form of the elastic energy density \eqref{ansatz3} is the same as
+%the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
+%a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
+%The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
+%liquid crystal theory. However, the ``bend'' distortion from nematics  
+%is not present in monolayers since the directors have no dependence in the normal direction.
+%There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection. 
+%  
+%  We suspect the reason why, after twenty years, the field has yet to reach a consensus 
+%  as to the form of \eqref{ansatz3} has to do with the Taylor expansions used to derive the elastic energy density. 
+%  Past researchers expressed the strain tensor in
+%  terms of the orthonormal frame $\{{\bf e}_1, {\bf e}_2, {\bf N}\}$ with surface tangent vectors ${\bf e}_i$ and surface normal ${\bf N}$.  
+%  In this frame, there is a coupling between the gradients of all three terms ${\bf x}_0,$ $\zeta$ and ${\bf n}$ of the deformation \eqref{LMdeformation}.
+%  Subtle differential geometric arguments are needed to evaluate the terms in the Taylor expansion,
+%  and these couplings can lead to an energy density with more than ten parameters, for example \cite{PhysRevE.102.042406}.
+%
+%  We will revisit the HK analysis to see if any of the aforementioned inconsistencies can be resolved.
+%  As a main analytical innovation, we have found that expanding the strain tensor in
+%  terms of the orthonormal frame $\{{\bf e}'_1, {\bf e}'_2, n\}$ with ${\bf e}'_i$ perpendicular to ${\bf n}$
+%  greatly simplifies the expansion because it decouples the gradient terms. As an illustration, the prominent works
+%  \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
+%  incompressibility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
+%  However, we prove that when expressed in the $\{{\bf e}'_1, {\bf e}'_2, n\}$ frame, the incompressility condition is \emph{exact}
+%  and is given by a Steiner-type polynomial in terms of $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
+%  Aside from the special case of zero tilt, \cite{Hamm2000} and coworkers seem to have been unaware of this result.
 

### 2020-11-12 NSF2020/Description/specificaim2_ver2.tex

@@
 \todo{What are the known results?}
-To test area incompressibility, we form the bilayer midplane by fitting to the particle centers. Under moderate shear rates,
-the vesicle elongates and takes on an elliptical shape. We will study the increase in midplane area as a function of shear rate.
-Additionally, we will test for tangential divergence of velocity.
-Researchers have devised to model area incompressible and
-volume conserving membranes
+Researchers have devised models to enforce area incompressibility and
+volume conservation in vesicle membrane dynamics. 
 \cite{torres-sanchez_millan_arroyo_2019, mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}.
-Our preliminary results show that the particle-based bilayers have the same area modulus, about 60 \kBT,  as that of real lipid bilayer membranes,
-and so we expect realistic results from our flow simulations with regard to area incompressibility.  It is noteworthy that
-area incompressibility is some sense baked into the model through the hydrophobic attraction.
+Our preliminary results show that the particle-based bilayers have the same, large area modulus as that of real lipid bilayer membranes,
+and so we expect realistic results from our flow simulations.
+Under moderate shear rates, the vesicle elongates and takes on the tank-treading, elliptical shape.
+We can directly check for area compressibility conservation properties from the particle simulation,
+by tracking the change in area density of the midplane as a function of shear flow rate,  
+along with evaluating the tangential divergence of the velocity.
 
@@
 
-\begin{wrapfigure}[13]{r}{0.32\textwidth}
-\centerline{\includegraphics[width=0.32\textwidth]{figures/BIError.pdf}}
+\begin{wrapfigure}[16]{r}{0.30\textwidth}
+\centerline{\includegraphics[width=0.30\textwidth]{figures/BIError.pdf}}
 \caption{
 \label{fig:bierror}  
-The numerical error in integral representations blows up near boundaries.
+The false color map shows how numerical quadrature of layer
+potentials loses accuracy near the particle boundaries.
+The color bar is for $\log_{10}.$ 
 }
@@
 
-Finally, the particle-based vesicle bilayers have two distinct leaflets.
-The inner and outer leaflets consists of the particles in contact with the vesicle interior and 
-surrounding fluid respectively. Since there the separation between these layers is roughly fixed,
-about 2 nm, certain fluid mechanical effects arise that are not present in zero-thickness membrane models. 
-An important effects we observe is that the leaflets slide against one another under shear flow. 
+Finally, the particle-based vesicle bilayers have two distinct leaflets,
+consisting of the particles in contact with the vesicle interior and 
+surrounding fluid respectively. Since there is a nonzero separation between these layers,
+one important effect we observe is that the leaflets slide against one another under shear flow. 
 This implies that part of the viscous dissipation in the aqueous phase is enhanced by intermonolayer friction
-\cite{SHKULIPA2005823, ShkulipaThesis}. We will characterize the intermonolayer
-slip as a function of shear rate, vesicle diameter and particle geometry.
+\cite{SHKULIPA2005823, ShkulipaThesis}.
+Intermonolayer slip enters zero-thickness membrane models as a velocity jump boundary condition
+and leads to multiple solution states \cite{schwalbe_vlahovska_miksis_2010}.
+In the present proposal, intermonolayer slip is an artifact of monolayer independence  
+and we can control for slip as a function of shear rate, vesicle diameter and particle geometry.
 
-\textbf{Novel reciprocal relations.}
-We use a boundary integral representation for the velocity field. Due to singular behavior of the
-kernels, the boundary integrals can have large numerical epresentation without the aid of specilized
-quadrature routines, leads to large numerical errors when evaluating the the hydrophobic
-stress \eqref{stress} along the particle boundaries (see Figure \cite{fig:bierror}).
-We prove a, to our knowledge new, result concerning the evaluation of Maxwell-type stresses. 
-\begin{proposition}
-  \label{prop:recip}
-  Suppose that $u = \sum_{i=1}^N u_i$ where $u_i$ is a solution of the screened Laplace equation
-  in $\mathbb{R}^3 \setminus P_i$ for $i=1,\dots, N.$ Then 
+\textbf{Novel reciprocal identities.}
+In the course of our study, we have found it useful to devise certain reciprocal identities that
+allow us to calculate forces accurately without having to resort to overly complicated numerical integration schemes. 
+At issue is that there is a break-down in numerical accuracy for the gradient of water activity near the particle
+boundaries (see Figure \ref{fig:bierror}).
+This is unfortunate the boundary is exactly where we need the gradients to be accurate in order for the formulas \eqref{forceandtorque}
+to be meaningful. To get around this issue, we prove the following identity
   \begin{equation}
     \label{eq:reciprocal}
-{\bf F}_i = \sum_{j \neq i} \int_{\partial P_i}[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
-{\bf G}_i = \sum_{j \neq i} \int_{\partial P_i} {\bf x} \times [\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, \quad i = 1\dots, N.
+{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
+{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S
   \end{equation}
-where $\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i \cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$ and
-$[\cdot]$ denotes the jump in stress across $\partial \Omega.$ 
-\end{proposition}
-
-The identity in Proposition \ref{prop:recip} gets around this critical issue by utilizing the fact that $u_j$, $j\neq i$ is smooth and the normal derivative
-of  $u_i$ continuous across $\partial P_i$. Despite the large gradient errors in Figure \ref{fig:bierror}, the force and torque
-calculated by \eqref{eq:reciprocal} achieved $10^{-4}$ accuracy.
+for $i = 1\dots, N$. Here $u = \sum_{i=1}^N u_i$ is a sum of solutions $u_i$ the screened Laplace equation,
+$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i \cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$ and
+$[\cdot]$ denotes the jump across $\partial \Omega.$  It turns out that because of \cite{eq:reciprocal},
+we no longer require knowledge of the gradient on the boundary, which is enormously beneficial for calculating force and torque.

### 2020-11-12 NSF2020/Description/background.tex
edited Sections 1-3

--- 2020-11-11 NSF2020/Description/background.tex
@@
 \label{sec:background}
-The goal of this collaborative proposal is to use mathetical modeling and
-numerical simulations to investigate the dynamic self-assembly of
+The goal of this collaborative proposal is to use mathematical modeling
+and numerical simulations to investigate the dynamic self-assembly of
 amphiphilic particles interacting with each other via hydrophobic forces
@@
 %
-Such self-assembly of amphiphiles via hydrophobic force is ubiquitous in biology and biophysics \cite{Israelachvili1954},
+Such self-assembly of amphiphiles via hydrophobic forces is ubiquitous in biology and biophysics \cite{Israelachvili1954},
 %The hydrophobic force is a ubiquitous molecular interaction in biology \cite{Israelachvili1954}, 
@@
 \caption{ \footnotesize
-A collection $P_1,$ $P_2,$ $P_3,$ \dots of rigid particles.
-The exterior domain $\Omega$ represents the solvent.}
+A collection $P_1,$ $P_2,$ $P_3, \ldots$ of rigid particles.  The
+  exterior domain $\Omega$ represents the solvent.}
   \label{fig:domain}
@@
 
-To define HAP, consider a collection of particles solvent suspended in a solvent. 
-The region $\Omega \subset \mathbb{R}^3$  models 
-the solvent phase (Figure \ref{fig:domain}).
+To define HAP, consider a collection of particles suspended in a
+solvent. The region $\Omega \subset \mathbb{R}^3$ models the solvent
+phase (Figure \ref{fig:domain}).
 %The HAP must be an energy of the shape of the region because hydrophobic
 %attraction is non-additive.
-The boundary of the region is the
-water-particle interface.
-Some parts of this interface are hydrophobic
-while others are hydrophilic.
-Hydrophobic interfaces disturb the hydrogen bond structure of water~\cite{Luzar1987,
-Jonsson2006, Varilly2011}. This disturbance comes with an energetic penalty
-that is proportional to interfacial area.
-There is an additional decay length,
-due to rapid fluctuation in the hydrogen bond
-network, describing how far the restructuring extends into bulk water.
+The boundary of the region is the water-particle interface with outward
+pointing normal $\boldsymbol{\nu}$. Some parts of this interface are
+hydrophobic while others are hydrophilic. Hydrophobic interfaces disturb
+the hydrogen bond structure of water~\cite{Luzar1987, Jonsson2006,
+Varilly2011}. This disturbance comes with an energetic penalty that is
+proportional to interfacial area. There is an additional decay length,
+due to rapid fluctuation in the hydrogen bond network, describing how
+far the restructuring extends into bulk water.
 
@@
 
-To get the effect of attraction, the water activity is not arbitrary, but rather
-is the unique solution of the screened Laplace equation boundary value problem 
+To establish the effect of attraction, the water activity is not
+arbitrary, but rather is the unique solution of the screened Laplace
+equation boundary value problem 
 \begin{equation}
@@
 The boundary values $f$ define the degree of hydrophobicity of the
-water-particle interface: $f=1$, describes a hydrophobic interface
-and $f=0$ describes a hydrophilic interface. Thus $f$ encodes information
-about the particles and the parameters $\rho$ and $\gamma$ encode information about the quality of the solvent 
-~\cite{Israelachvili1954, Discher2002}. In practice, we use
-\eqref{SL} to integrate by parts to obtain
+water-particle interface: $f=1$, describes a hydrophobic interface and
+$f=0$ describes a hydrophilic interface. Thus $f$ encodes information
+about the particles and the parameters $\rho$ and $\gamma$ encode
+information about the quality of the solvent~\cite{Israelachvili1954,
+Discher2002}. In practice, we integrate~\eqref{HAP} by parts and
+use~\eqref{SL} to obtain
 \begin{equation}
@@
 
-The equations~\eqref{HAP} and~\eqref{SL} possess number of the mathematical properties
+The equations~\eqref{HAP} and~\eqref{SL} possess a number of the mathematical properties
 that capture the phenomenological behavior of hydrophobic attraction.
 Specifically, solutions of~\eqref{SL} yield an attractive interaction between
-hydrophobic bodies separated by water ~\cite{Eriksson1989}.
+hydrophobic bodies separated by water~\cite{Eriksson1989}.
 Using boundary layer analysis, the HAP converges to a surface energy in the zero-decay length
@@
 %%lipid  bilayer  membrane  that  are  consistent  with other results in the literature.   
-To define the particle dynamics,
-let $P_1$, $P_2$, \ldots, $P_N$,
-be a finite collection of disjoint, rigid and closed particles
-with Lipschitz boundary.
-Assume that the label $f$ is an element of the Sobolev space $H^1(\Omega)$.
-The functional~\eqref{HAP} has a minimizer among all functions $u$ equaling $f$ on the boundary in the sense of trace.
-Conversely, from maximum principles and energy estimates, the solution of~\eqref{SL} is unique and minimizes~\eqref{HAP}.
-Taking the first variation of~\eqref{HAP}, i.e. the derivative with respect to the domain
-~\cite{Bandle2015, Schiffer1954, Grinfeld2010},
-yields a symmetric, rank-two tensor called the hydrophobic stress:
+To define the particle dynamics, let $P_1$, $P_2$, \ldots, $P_N$, be a
+finite collection of disjoint, rigid, and closed particles with
+Lipschitz boundary. Assume that the label $f$ is an element of the
+Sobolev space $H^1(\Omega)$. The functional~\eqref{HAP} has a minimizer
+among all functions $u$ equaling $f$ on the boundary in the sense of
+trace.  Conversely, from maximum principles and energy estimates, the
+solution of~\eqref{SL} is unique and minimizes~\eqref{HAP}. Taking the
+first variation of~\eqref{HAP}, i.e.~the derivative with respect to the
+domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}, yields a
+symmetric, rank-two tensor called the hydrophobic stress:
 \begin{align}
@@
   \mathbf{G}_{\text{hydro},i} = \iint_{\partial P_i} (\mathbf{x}-\mathbf{a}_i) \times
-  (\boldsymbol{\sigma}_{\text{hydro}} \cdot \boldsymbol{\nu}) \,\dif S
+  (\boldsymbol{\sigma}_{\text{hydro}} \cdot \boldsymbol{\nu}) \,\dif S,
 \end{align}
-relative to the center of mass $\mathbf{a}_i$.
-This system is force- and torque-free  \S\ref{subsec:specific_aim_2}.
-To avoid particle collisions, we define an excluded volume potential $\Phi_{\text{repul}}$
-that diverges whenever tubular neighbordhoods of adjacent particles overlap,
-along with the excluded volume repulsions. The total potential, force and torque are then
+relative to the center of mass $\mathbf{a}_i$.  This system is force-
+and torque-free (\S\ref{subsec:specific_aim_2}).  To avoid particle
+collisions, we define an excluded volume potential $\Phi_{\text{repul}}$
+that diverges whenever tubular neighborhoods of adjacent particles
+overlap, along with the excluded volume repulsions. The total potential,
+force and torque are then
 \begin{equation}
@@
 Numerical challenges and how these challenges are overcome are described
-in \S\ref{subsec:specific_aim_2}.
+in \S\ref{subsec:specific_aim_2} and \S\ref{subsec:specific_aim_3}.
 
@@
 
-The HAP formulation is, to our knowledge, the first demonstration of bilayer self-assembly
-by a continuum-based interaction model~\cite{Noguchi2001, Farago2003, Brannigan2006,
-Brooks2009, Wang2013}.
-Our simulations use Janus particles to model lipid amphiphiles which are
-popular in material science and physics for creating functional
-materials~\cite{Lee2014, Lee2013}. Janus particles are typically
-spherical with a biphasic material label on either hemisphere, endowing
-the particle with a directional order.
-We model elongated lipid by elliptical particles with the hydrophobic label defined  along the ellipse's axis.
-Under the hydrophobic force, and with an excluded volume,
-the Janus particles spontaneously merge and realign to form
-bilayers. This occurs only as a result of energy minimization and does
-not require artificial inputs.
+The HAP formulation is, to our knowledge, the first demonstration of
+bilayer self-assembly by a continuum-based interaction
+model~\cite{Noguchi2001, Farago2003, Brannigan2006, Brooks2009,
+Wang2013}. Our simulations use Janus particles to model lipid
+amphiphiles which are popular in material science and physics for
+creating functional materials~\cite{Lee2014, Lee2013}. Janus particles
+are typically spherical with a biphasic material label on either
+hemisphere, endowing the particle with a directional order. We model an
+elongated lipid by elliptical particles with the hydrophobic label
+defined along the ellipse's axis. Under the hydrophobic force, and with
+an excluded volume, the Janus particles spontaneously merge and realign
+to form bilayers. This occurs only as a result of energy minimization
+and does not require artificial inputs.
 
@@
 As a proof of concept, our work has already tested for elastic energies
-for bending, stretching, and tilt of the bilayer assembly. 
-The elastic coefficients derived from the HAP simulations show strikingly positive
+for bending, stretching, and tilt of the bilayer assembly.  The elastic
+coefficients derived from the HAP simulations show strikingly positive
 agreement with experimentally determined values~\cite{Fu2018_SIAM}.
 Encouraged by these results and the hydrodynamic simulations of the
-bilayer assembly, the PIs propose to extend the HAP model
-to make direct comparison with experimental results  \S\ref{subsec:specific_aim_1},
-to establish that the HAP model has the capability
-and adaptivity to model flow phenomena across length scales and time scales \S\ref{subsec:specific_aim_2},
-using efficient, high-order numerical methods \S\ref{sec:proposed-work}.
+bilayer assembly, the PIs propose to extend the HAP model to make direct
+comparison with experimental results  \S\ref{subsec:specific_aim_1}, to
+establish that the HAP model has the capability and adaptivity to model
+flow phenomena across length scales and time scales
+\S\ref{subsec:specific_aim_2}, using efficient, high-order numerical
+methods \S\ref{subsec:specific_aim_3}.
 
@@
 set~\cite{DoyeuxGuyotChabannesEtAl2013_JCAM}, boundary
-integral~\cite{Shravan09,Rahimian15} and immersed boundary
+integral~\cite{Shravan09,Rahimian15}, and immersed boundary
 approaches~\cite{KimLai2010_JCP,KimLai2012_PRE,HuLaiSeolEtAl2016_JCP}.
@@
 calculating energy minimizing steady equilibrium shapes of lipid bilayer
-membranes, vesicles and red blood cells. These approaches range from the
-finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15}, phase
-field method~\cite{Du05,QiangDu08,Lowengrub13} to immersed boundary
-method~\cite{Hu,Hu13, KimLai2010_JCP}. PI RR and collaborators led in
-part the development of phase field functionals of membrane elastic
-energy and approaches to coupling membrane elasticity to
+membranes, vesicles, and red blood cells. These approaches range from
+the finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15},
+phase field method~\cite{Du05,QiangDu08,Lowengrub13}, and immersed
+boundary method~\cite{Hu,Hu13, KimLai2010_JCP}. PI RR and collaborators
+led in part the development of phase field functionals of membrane
+elastic energy and approaches to coupling membrane elasticity to
 fluids~\cite{0951-7715-18-3-016,Du05,DuEuler,QiangDu09}.
@@
 deals with multiple phases through additional surface densities that
-must then satisfy specialized transport equations~\cite{Lowengrub07,
+must satisfy specialized transport equations~\cite{Lowengrub07,
 MikuckiZhou17}.
 
+\begin{wrapfigure}[6]{l}{0.35\textwidth}
+\centerline{\includegraphics[width=0.35\textwidth]{figures/Lysis.pdf}}
+  \vspace{-8pt}
+  \caption{\label{fig:lysis} \footnotesize Two hydrophobic particles
+  enter and then lyse the circular bilayer.}
+\end{wrapfigure}
 The greatest strength of using HAP to model lipid bilayer membrane is
 the ability to form discontinuities (interfacial singularity) from first
-physical principles without any artificial manipulation to rearrangement
-the interface. For example, using the HAP model to simulate a vesicle
-under a shear flow that is strong enough to cause the vesicle membrane
-to rupture, we expect the HAP model to capture the reorganization of
-lipid molecules on the scales of membrane thickness ($\sim 5$ nm), which
-is a nearly impossible task using phase-field or immerse boundary method
-without extreme refinement around the membrane and artificial treatment
-of reconnection during the topological change of an interface.
+physical principles without any artificial manipulation to rearrange the
+interface (Figures~\ref{fig:demixing} and~\ref{fig:lysis}).  For
+example, using the HAP model to simulate a vesicle under a shear flow
+that is strong enough to cause the vesicle membrane to rupture (see
+\S\ref{sec:preliminary_work}), we expect the HAP model to capture the
+reorganization of lipid molecules on the scales of membrane thickness
+($\sim 5$ nm), which is a nearly impossible task using phase-field or
+immerse boundary method without extreme refinement around the membrane
+and artificial treatment of reconnection during the topological change
+of an interface \cite{doi:10.1063/5.0009734, LiAn-Chang16,
+doi:10.1098/rspa.2012.0505, doi:10.1137/130941432, Feetzl18,
+doi:10.1137/16M1108406}.
 

### 2020-11-12 NSF2020/Description/broaderimpacts.tex
edited Sections 1-3

@@
 interaction between these building blocks. In addition to biophysical
-applications, amphiphilic Janus particles have recently popularity for
+applications, amphiphilic Janus particles have recent popularity in the
 fabrication of smart materials. The proposed work will have a
@@
 \label{subsec:Educational_plans}
-The proposed research will have immediate impact on undergraduate and
-graduate education. At the undergraduate level, the project will involve
-and support undergraduate researcher from Fordham University. The
+The proposed research will have an immediate impact on undergraduate and
+graduate education. At the undergraduate level, the project will include
+and support undergraduate researchers from Fordham University. The
 supported summer researchers will gain valuable first-hand
@@
 undergraduate and high school students through the Undergraduate
-Research Opportunity Program (UROP) and Young Scholar's Program (YSP) as
-he has done in the past.
+Research Opportunity Program and Young Scholar's Program as he has done
+in the past.
 
@@
 number simulations in three dimensions. Results from these computations
-will be used to compare collective amphiphilic against experiment, and
+will be used to compare collective amphiphilic against experiments, and
 study the optimal design of three-dimensional functional materials.

### 2020-11-12 NSF2020/Description/preliminarywork.tex
worked on SA1 and small edits elsewhere

@@
 \end{center}\vspace{-0.3in}
-\caption{(A) A vesicle formed by amphiphilic particles in shear flow,
-  and the tank-treading motion (B)--(D). The separation of particle
-  pairs in (B) and (C) illustrate inter-leaflet slip.  (E)--(G)
+\caption{\footnotesize (A) A vesicle formed by amphiphilic particles in
+  shear flow, and the tank-treading motion (B)--(D). The separation of
+  particle pairs in (B) and (C) illustrate inter-leaflet slip.  (E)--(G)
   Tank-treading reaches a steady state in elliptical aspect ratio,
@@
 %
+%
+\begin{wrapfigure}[10]{r}{0.2\textwidth}
+\centerline{\includegraphics[width=0.2\textwidth]{figures/PW_fig5.pdf}}
+\vspace{-8pt}
+\caption{\label{fig:rupture} \footnotesize Rupture of tank-treading vesicle under strong shear flow.}
+\end{wrapfigure}
+%
 To implement a vesicle in shear flow in the context of hydrophobic
@@
 %\todo[inline]{missing units. nm?}
-%
-\begin{wrapfigure}[12]{r}{0.2\textwidth}
-\centerline{\includegraphics[width=0.2\textwidth]{figures/PW_fig5.pdf}}
-\caption{\label{fig:rupture} Rupture of tank-treading vesicle under strong shear flow.}
-\end{wrapfigure}
-%
 Figure~\ref{fig:tanktreading}E shows the aspect ratio of the major to minor axes reaching an equilibrium value in the 

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
worked on SA1 and small edits elsewhere

@@
 %%
-We have demonstrated that our hydrophobic attraction with repulsion potential (HARP) approach efficiently simulates
-self-assembly of amphiphilic particles into two-dimensional micelles, bilayer membranes, and vesicles \cite{Fu2018_SIAM}, and
-recreates the tank-treading phenomenon in external shear flows
-\cite{Fu20}.
+We have demonstrated that our hydrophobic attraction with repulsion
+potential (HARP) approach efficiently simulates self-assembly of
+amphiphilic particles into two-dimensional micelles, bilayer membranes,
+and vesicles \cite{Fu2018_SIAM}, and recreates the tank-treading
+phenomenon in external shear flows \cite{Fu20} \todo{Is this supposed
+to be a reference to our working paper}.
 %\todo[inline]{!!let's put a proceedings here so we have something to cite!!}.
 %
-While the results show great promise in the field of collective body hydrodynamics,
-several outstanding issues need to be addressed. These include a thorough 
-analysis of elastic properties of our coarse-grained bilayers, and 
-efficiently simulating three-dimensional collective hydrodynamics of amphiphilic particles.
-Finally, we must mathematically characterize the variational behavior of HARP under appropriate homogenized limits.
+While the results show great promise in the field of collective body
+hydrodynamics, several outstanding issues need to be addressed. These
+include a thorough analysis of elastic properties of our coarse-grained
+bilayers, and efficiently simulating three-dimensional collective
+hydrodynamics of amphiphilic particles. Finally, we must mathematically
+characterize the variational behavior of HARP under appropriate
+homogenized limits.
 
@@
 fusion \cite{ChKo08, KoKo2002,Kuzmin7235,Aeffner2012},
-poration \cite{Gaetal20}, phase boundaries and interaction with inclusions
+poration \cite{Gaetal20}, phase boundaries, and interaction with inclusions
 \cite{SeLeMaEg17,Saetal20, Pietal20}, which require resolution of the internal structure of the membrane.  
@@
 %
-\begin{wrapfigure}[12]{l}{0.47\textwidth}
+\begin{wrapfigure}[11]{l}{0.47\textwidth}
 \centerline{\includegraphics[width=0.47\textwidth]{Figures/Deformations.pdf}}
 %  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
-\caption{\label{fig:deformations}Sketch of the HK membrane model \cite{Hamm2000}.
-    }
+  \vspace{-5pt}
+\caption{\label{fig:deformations} \footnotesize Sketch of the HK
+ membrane model \cite{Hamm2000}.}
 \end{wrapfigure}
 %
- researchers to question the applicability of \eqref{ansatz3} for large curvatures \cite{PhysRevLett.117.188102, ARGUDO20161619}. 
-For example, Galimzyanov {\it et al.} \cite{C9SM02079A} countered that energies derived from molecular dynamics and elasticity agree, even when curvatures are large.
-This proposal will develop much-needed mathematical analysis to resolve these controversies due to the assumptions in the HK theory.
+researchers to question the applicability of \eqref{ansatz3} \todo{this
+equation hasn't been presented at this point} for large curvatures
+\cite{PhysRevLett.117.188102, ARGUDO20161619}. For example, Galimzyanov
+{\em et al.}~\cite{C9SM02079A} countered that energies derived from
+molecular dynamics and elasticity agree, even when curvatures are large.
+This proposal will develop much-needed mathematical analysis to resolve
+these controversies due to the assumptions in the HK theory.
 
@@
 consisting of straight fibers that represent elongated hydrocarbon chains. HK assumed an
-elastic energy density ${\cal W}$ that quadratic in the Green-Lagrange strain tensor for membrane deformation of
+elastic energy density ${\cal W}$ that is quadratic in the Green-Lagrange strain tensor for membrane deformation of
 this striated, internal structure.
@@
 %
-This energy decomposes into four, fundamental and independent deformations  (figure~\ref{fig:deformations}):
-splay ($\Div {\bf n}$), twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$) and tilt ${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal:
+This energy decomposes into four fundamental and independent
+deformations (Figure~\ref{fig:deformations}): splay ($\Div {\bf n}$),
+twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$), and tilt
+${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is
+the unit surface normal:
 \begin{equation}
 \label{ansatz3}
-\begin{aligned}
 {\cal W} \equiv \int_{\Sigma} 
@@
 + \tfrac{1}{2}\KT (\Curl {\bf n})^2 + \KG  \det \nabla {\bf n} + \tfrac{1}{2}\KTH |{\bf t}|^2 \,dA.
-\end{aligned}
 \end{equation}
@@
 %respectively (Figure \ref{fig:distortions}A--C).
-the deformations come with elastic coefficients: the bending modulus $\KB$, twist modulus $\KT$ 
-and saddle-splay modulus $\KG$ and tilt modulus $\KTH$
+the deformations come with elastic coefficients: the bending modulus
+$\KB$, twist modulus $\KT$, saddle-splay modulus $\KG$, and tilt modulus
+$\KTH$.
 %HK define the tilt vector ${\bf t} = {\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal.
 %
-The parameter $k_0$ is the  spontaneous curvature and it determines the preferred lipid splay \cite{RoLi15,Kozlov2007}. 
-As an illustration, the lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
+The parameter $k_0$ is the spontaneous curvature and determines the
+preferred lipid splay~\cite{RoLi15,Kozlov2007}.  As an illustration, the
+lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
 %as a result of  %having a relatively long acyl chain. 
 and these lipids would line the  inner monolayer of a 
-spherical liposome, because the addition of a positive splay $\Div \mathbf{n}$  in \eqref{ansatz3}
+spherical liposome, because the addition of a positive splay $\Div \mathbf{n}$ in~\eqref{ansatz3}
 to the negative spontaneous curvature $k_0$ leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
@@
 \vspace{-0.2cm}
-\caption{\label{fig:flattening}Example of computing bending modulus of a lipid bilayer from particle simulation.
-    }
+\caption{\label{fig:flattening} \footnotesize Example of computing
+  bending modulus of a lipid bilayer from particle simulation.}
 \end{wrapfigure}
@@
 \centerline{\includegraphics[width=0.32\textwidth]{Figures/SaddleSplayDiagram.pdf}}
-\caption{
-\label{fig:saddle_splay}  
-Determination of saddle splay modulus.
-}
+\caption{\label{fig:saddle_splay} \footnotesize Determination of
+  saddle splay modulus.}
 \end{wrapfigure}

### 2020-11-12 NSF2020/Description/specificaim3_ver2.tex
worked on SA1 and small edits elsewhere

@@
 method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2, fmm3,
-fmm4, fmm6, fmm7, fmm8}. PI Quaife is experienced with applying FMMs to
+fmm4, fmm6, fmm7, fmm8}. PI BQ is experienced with applying FMMs to
 BIE formulations of the Stokes equation~\cite{qua-bir2014,
@@
 preconditioning strategies such as the inverse Fast Multipole Method
-(IFMM)~\cite{cou-pou-dar2017}. PI Quaife used the IFMM to precondition
+(IFMM)~\cite{cou-pou-dar2017}. PI BQ used the IFMM to precondition
 Stokes equations in a porous media~\cite{qua-cou-dar2018}, and a suite
@@
 
-PI Quaife developed a high-order adaptive time stepping method for
+PI BQ developed a high-order adaptive time stepping method for
 hydrodynamic suspensions~\cite{qua-bir2016} and it has served as a
@@
 accuracy in numerical fluctuation-dissipation balance. However, they
-only one regularization strategy was considered, and as PI Quaife has
+only one regularization strategy was considered, and as PI BQ has
 shown in previous work, the regularization choice significantly affects

### 2020-11-12 NSF2020/Description/specificaim2_ver2.tex
worked on SA1 and small edits elsewhere
edited up to 4.2.2

@@
 \label{subsec:specific_aim_2}
-In Specific Aim 2, we include hydrodynamics effects by embedding the particles in a solvent. 
-As described in \eqref{eq:stokes} and illustrated in Figure \ref{fig:flow_map}, 
-the solvent phase is modeled by the Stokes equations for an incompressible, zero Reynolds-number fluid, 
-and these equations are coupled to the screened-Laplace equation \eqref{SL} through viscous and hydrophobic stress balance.
-Hydrodynamic effects are a relevant detail  
-because the rates of biological functions like fusion, fission, and pore dynamics rely on viscous dissipation \cite{RYHAM20112929}. 
+In Specific Aim 2, we include hydrodynamics effects by embedding the
+particles in a solvent.  As described in~\eqref{eq:stokes} and
+illustrated in Figure~\ref{fig:flow_map}, the solvent phase is modeled
+by the Stokes equations for an incompressible viscous fluid, and these
+equations are coupled to the screened-Laplace equation~\eqref{SL}
+through viscous and hydrophobic stress balance. Hydrodynamic effects can
+not be ignored since the rates of biological functions like fusion,
+fission, and pore dynamics rely on viscous
+dissipation~\cite{RYHAM20112929}. 
 %While hydrophobic attraction causes the particles to self-assemble indepedently of the dissipation mechanism, the trajectories and
 %equilibrium configurations depend on the fact that the particles travel through a viscous environment. 
-Additionally, hydrodynamics interactions are central fabrication of complex microscopic three-dimensional structures \cite{Cho2010}.
-Over the past decade, there has been an explosion of interest in small-scale processes that utilize capillary forces dominate,  van der Waals interactions and thermal noise  \cite{Zhang2017}, to coordinated movement and bind  material subunits, \cite{Pandey2011,Leong2007,Reynolds2019, Dasgupta2017,Siontorou2017}.
-Finally, coarse-grained and molecular dynamics theories include water either explicitly or implicitly in their models. 
-The immediate goal of the present proposal
-is to be able to simulate vesicle bilayers in external flows, where the bilayers are represented by a self-assembled collection of rigid particles.
+Additionally, hydrodynamic interactions are central for complex
+microscopic three-dimensional structures to fabricate~\cite{Cho2010}.
+Over the past decade, there has been an explosion of interest in
+small-scale processes that utilize capillary forces, van der Waals
+interactions, and thermal noise~\cite{Zhang2017}, to coordinate movement
+and bind material subunits~\cite{Pandey2011, Leong2007, Reynolds2019,
+Dasgupta2017, Siontorou2017}. Finally, coarse-grained and molecular
+dynamics theories include water either explicitly or implicitly in their
+models. The immediate goal of the present proposal is to simulate
+vesicle bilayers in external flows, where the bilayers are represented
+by a self-assembled collection of rigid particles.
 
@@
 
-\textbf{Vesicles in background flows.}
-Numerically solving the Stokes-screened Laplace system \eqref{SL}, \eqref{eq:stokes} is a nontrivial matter,
-and we will develop an efficient, robust, high-order of accuracy in time and space algorithm suited to the problem. 
-The challenges are: \textbf{(1)} the equations express a two-way coupling.
-This means that the flow changes the shape of the bilayer (or particle suspension, more generally),
-and in return the hydrophobic stresses coming from the altered shape imparts a force on the flow. 
-\textbf{(2)}
-The inputs to the Stokes equations are particle configurations, forces and torques. 
-The outputs are the rigid body translation and angular velocties used to update the particle positions (see Figure \ref{fig:flow_map}).
-Although the underlying equations are linear, the overall problem is highly nonlinear because the domain is constantly changing.
-\textbf{(3)} Self-assembly causes the particles to come into close contact.  
-As a result, a exceptional spatial accuracy is required to resolve the fields between adjacent particles.
-Finally, the physically relevant elastic properties of bilayer become apparent at large length scales and for large particle-numbers,
-which increases the computational complexity of our simulations.
+\subsubsection{Vesicles in background flows}
+Numerically solving the Stokes-screened Laplace system~\eqref{SL}
+and~\eqref{eq:stokes} is nontrivial, and we will develop efficient,
+robust, high-order in time and space algorithms suited to the problem.
+The challenges are: {\bf (1)} the equations express a two-way coupling.
+This means that the flow changes the shape of the suspended particles,
+and in return the geometry-dependent hydrophobic stresses impart a force
+on the flow. {\bf (2)} The inputs to the Stokes equations are particle
+configurations, forces, and torques. The outputs are the rigid body
+translation and angular velocities used to update the particle positions
+(see Figure~\ref{fig:flow_map}). Although the underlying equations are
+linear, the overall problem is highly nonlinear because the domain is
+constantly changing. {\bf (3)} Self-assembly causes the particles to
+come into close contact. As a result, an exceptional spatial accuracy is
+required to resolve the fields between adjacent particles. Finally, the
+physically relevant elastic properties of bilayer become apparent at
+large length scales and for large particle-numbers, which increases the
+computational complexity of our simulations.
 
-We include a background flow by replacing the third equation in \eqref{eq:stokes} with the condition
-$(\mathbf{u} - \mathbf{u}_{\infty})(\mathbf{x}) \to \mathbf{0}$ as $|\mathbf{x}| \to \infty.$ 
-The main idea to incorporate the far-field flow is to use the representation 
-\begin{equation}
+We include a background flow by replacing the third equation in
+\eqref{eq:stokes} with the condition $(\mathbf{u} -
+\mathbf{u}_{\infty})(\mathbf{x}) \to \mathbf{0}$ as $|\mathbf{x}| \to
+\infty$. To incorporate the far-field flow, we use the representation 
+\begin{align}
 \label{PowerMiranda}
-{\bf u} = {\bf u}_{\infty} + K\eta + \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + R(\cdot, {\bf a}_i) {\bf G}_i.
-\end{equation}
-where $S$ and $R$ are stokeslets and rotlets supported at the respective particle centers 
-and $K\eta$ is a layer potential for an unknown density function $\eta.$ 
-The representation \eqref{PowerMiranda} automatically satisfies all equations, with the exception of the rigid motion conditions. 
-These rigid motion conditions follow by requiring the viscous stress vanishes across the particle boundaries.
+  {\bf u} = {\bf u}_{\infty} + K\boldsymbol{\eta} + 
+    \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + 
+                 R(\cdot, {\bf a}_i) {\bf G}_i.
+\end{align}
+where $S$ and $R$ are stokeslets and rotlets supported at the respective
+particle centers and $K\boldsymbol{eta}$ is a layer potential for the
+unknown density function $\boldsymbol{\eta}.$ The
+representation~\eqref{PowerMiranda} automatically satisfies all
+equations, with the exception of the rigid motion conditions. The rigid
+motion conditions follow by requiring the viscous stress vanishes across
+the particle boundaries.
 
-We will compare the behavior of our particle-based vesicles in Stokes flow to well-established results.
-\todo{What are the known results?}
+We will compare the behavior of our particle-based vesicles in Stokes
+flow to well-established results. \todo{What are the known results?}
 Researchers have devised models to enforce area incompressibility and
-volume conservation in vesicle membrane dynamics. 
-\cite{torres-sanchez_millan_arroyo_2019, mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}.
-Our preliminary results show that the particle-based bilayers have the same, large area modulus as that of real lipid bilayer membranes,
-and so we expect realistic results from our flow simulations.
-Under moderate shear rates, the vesicle elongates and takes on the tank-treading, elliptical shape.
-We can directly check for area compressibility conservation properties from the particle simulation,
-by tracking the change in area density of the midplane as a function of shear flow rate,  
-along with evaluating the tangential divergence of the velocity.
+volume conservation in vesicle membrane
+dynamics~\cite{torres-sanchez_millan_arroyo_2019,
+mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}. Our
+preliminary results show that the particle-based bilayers have the same
+large area modulus as real lipid bilayer membranes, so we expect
+realistic results from our flow simulations. Under moderate shear rates,
+the vesicle elongates and takes on the tank-treading  elliptical shape.
+We can directly check for area compressibility conservation properties
+from the particle simulation by tracking the change in area density of
+the midplane as a function of shear flow rate, along with evaluating the
+tangential divergence of the velocity.
 
-Bilayer membranes have a small permeability to water \cite{323e9a2f0c58487ea82518d7a1f96485},
-and so modelers often assume a vesicle membrane that conserves volume. In our particle-based approach, water motion across
-the bilayer is limited by the size of the gaps between the particles, which is an artifact of coarse-graining.
-Making these gaps smaller comes at the expense of numerical accuracy, and so we will assess if there is a reasonable trade-off
-between approximate volume conservation and simulation complexity.
+Bilayer membranes have a small permeability to water
+\cite{323e9a2f0c58487ea82518d7a1f96485}, and modelers often assume a
+vesicle membrane that conserves volume. In our particle-based approach,
+water motion across the bilayer is limited by the size of the gaps
+between the particles, which is an artifact of coarse-graining.  Making
+these gaps smaller comes at the expense of numerical accuracy, and we
+will assess if there is a reasonable trade-off between approximate
+volume conservation and simulation complexity.
 
-\begin{wrapfigure}[16]{r}{0.30\textwidth}
+\begin{wrapfigure}[13]{r}{0.30\textwidth}
 \centerline{\includegraphics[width=0.30\textwidth]{figures/BIError.pdf}}
+  \vspace{-8pt}
 \caption{
 \label{fig:bierror}  
-The false color map shows how numerical quadrature of layer
-potentials loses accuracy near the particle boundaries.
-The color bar is for $\log_{10}.$ 
-}
+\footnotesize The false color map shows how numerical quadrature of
+  layer potentials loses accuracy near the particle boundaries.  The
+  color bar is for $\log_{10}.$}
 \end{wrapfigure}
 
-Finally, the particle-based vesicle bilayers have two distinct leaflets,
-consisting of the particles in contact with the vesicle interior and 
-surrounding fluid respectively. Since there is a nonzero separation between these layers,
-one important effect we observe is that the leaflets slide against one another under shear flow. 
-This implies that part of the viscous dissipation in the aqueous phase is enhanced by intermonolayer friction
-\cite{SHKULIPA2005823, ShkulipaThesis}.
-Intermonolayer slip enters zero-thickness membrane models as a velocity jump boundary condition
-and leads to multiple solution states \cite{schwalbe_vlahovska_miksis_2010}.
-In the present proposal, intermonolayer slip is an artifact of monolayer independence  
-and we can control for slip as a function of shear rate, vesicle diameter and particle geometry.
+Finally, the particle-based vesicle bilayers have two distinct leaflets
+consisting of the particles in contact with the vesicle interior, and
+those in contact with the surrounding fluid. Since there is a nonzero
+separation between these layers, an important effect we observe is that
+the leaflets slide against one another under shear flow.  This implies
+that part of the viscous dissipation in the aqueous phase is enhanced by
+intermonolayer friction~\cite{SHKULIPA2005823, ShkulipaThesis}.
+Intermonolayer slip enters zero-thickness membrane models as a velocity
+jump boundary condition and leads to multiple solution
+states~\cite{schwalbe_vlahovska_miksis_2010}.  In the present proposal,
+intermonolayer slip is an artifact of monolayer independence  and we can
+control for slip as a function of shear rate, vesicle diameter, and
+particle geometry.
 
-\textbf{Novel reciprocal identities.}
+\subsubsection{Novel reciprocal identities}
 In the course of our study, we have found it useful to devise certain reciprocal identities that

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
Update specificaim1_ver2.tex
Fixed premature large deformation reference.

@@
 for the elasticity energy density has caused
+researchers to question the applicability of the theory 
+for large curvatures
+\cite{PhysRevLett.117.188102, ARGUDO20161619}.
+This proposal will develop much-needed mathematical analysis to resolve
+these controversies due to the assumptions in the HK theory. 
 %Using the HK  model as a base,
@@
 %
-researchers to question the applicability of \eqref{ansatz3} \todo{this
-equation hasn't been presented at this point} for large curvatures
-\cite{PhysRevLett.117.188102, ARGUDO20161619}. For example, Galimzyanov
-{\em et al.}~\cite{C9SM02079A} countered that energies derived from
-molecular dynamics and elasticity agree, even when curvatures are large.
-This proposal will develop much-needed mathematical analysis to resolve
-these controversies due to the assumptions in the HK theory.
 
@@
 %as a result of  %having a relatively long acyl chain. 
-and these lipids would line the  inner monolayer of a 
-spherical liposome, because the addition of a positive splay $\Div \mathbf{n}$ in~\eqref{ansatz3}
-to the negative spontaneous curvature $k_0$ leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
+and these lipids would preferentially line the upper monolayer in Figure \ref{fig:deformations}B  
+because the addition of a positive splay 
+to the negative spontaneous curvature leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
 The subtraction of $k_0^2$ makes the energy distortion free
@@
 
+Although the HK elastic theory assumes small deformations, 
+Galimzyanov {\em et al.}~\cite{C9SM02079A} have show that energies derived from
+molecular dynamics and \eqref{ansatz3} are in agreement, even when curvatures are large.
 Under spatial scales much larger than the

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
Update specificaim1_ver2.tex

@@
 Although the HK elastic theory assumes small deformations, 
-Galimzyanov {\em et al.}~\cite{C9SM02079A} have show that energies derived from
-molecular dynamics and \eqref{ansatz3} are in agreement, even when curvatures are large.
+Galimzyanov {\em et al.}~\cite{C9SM02079A} have shown that energies derived from
+molecular dynamics and those derived from \eqref{ansatz3} are in agreement, even when curvatures are large.
 Under spatial scales much larger than the

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex

@@
 
-Here we start with a particle-based bilayer in a specific non-equilibrium shape that consists of only one component of the displacement in figure~\ref{fig:deformations}, 
-and then evolve the particle system
+Here we start with a particle-based bilayer in a specific non-equilibrium shape that involves only one of the components of the displacement in Figure~\ref{fig:deformations}, and then evolve the particle system according to the time integration for \eqref{eq:stokes}.
+Actually,  elastic properties are independent of dissipation, and so we can forgo solving for fluid velocity and by setting the translational
+velocity and angular velocity directly proportional to force and torque. 
 %bilayer by steepest gradient descent 
-with respect to the HARP functional:
-\begin{equation}
-\label{SGD}   
-\frac{\dif {\bf a}_i}{\dif t} = {\bf F}_i,    \quad  \frac{\dif {\bf R}_i}{\dif t}  = {\bf R}_i A({\bf w}_i),\quad i = 1, \dots, N.
-\end{equation}
-where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; 
-$A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
+%with respect to the HARP functional:
+%\begin{equation}
+%\label{SGD}   
+%\frac{\dif {\bf a}_i}{\dif t} = {\bf F}_i,    \quad  \frac{\dif {\bf R}_i}{\dif t}  = {\bf R}_i A({\bf w}_i),\quad i = 1, \dots, N.
+%\end{equation}
+%where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; 
+%$A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
 %We solve \eqref{SGD} numerically  using an Adams–Bashforth linear multistep method. 
-The procedure involves solving \eqref{SL} based off of the current particle configuration.
-We then use the solution $u$ to calculate the collection of forces and torques \eqref{forceandtorque}, and update the particle configuration
-through \eqref{SGD}.
+%The procedure involves solving \eqref{SL} based off of the current particle configuration.
+%We then use the solution $u$ to calculate the collection of forces and torques \eqref{forceandtorque}, and update the particle configuration
+%through \eqref{SGD}.
 
@@
 %
-The evolution \eqref{SGD} satisfies the energy dissipation law $\frac{\dif }{\dif t} \Phi \leq 0$
-and this stabilizes the evolving bilayer shape.
+In either case there is a dissipation of the total potential \eqref{eq:total_poten}, and this stabilizes the evolving bilayer shape.
 Therefore, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field ${\bf n}$ by
-interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $E$ from the interpolated shapes.
+interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $\mathbcal{W}$ from the interpolated shapes.
 
@@
 
-We propose to conduct calculations similar to the example of figure~\ref{fig:flattening} for other elastic moduli such as the effective saddle splay modulus $\KG$:
+We propose to conduct calculations similar to the example of figure~\ref{fig:flattening} for other elastic moduli such as the effective twist modulus $\KT$.
+Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14}, and here the specific non-equilibrium shape consists of a single layer of amphiphilic particles on a hydrophobic substrate as illustrated by Figure~\ref{fig:deformations}D.
+Having a nonzero twist requires nonzero tilt, because the surface gradient of the lipid directoy equals the second fundamental form, and is therefore symmetric, whenever tilt is zero locally.
+The twist deformation is a fully three-dimensional deformation.
+\S subsec:specific_aim_3 addresses outstanding implementation issues like three-dimensional boundary integral equation solvers.
+
 %for a wide range of particle parameters and physical parameters in HARP to 
@@
 %We will also determine the effective saddle splay modulus $\KG$. 
-The gradient descent technique is ineffective for measuring $\KG$ because
+The gradient descent technique is ineffective for measuring the saddle splay modulus $\KG$ because
 the saddle splay energy is largely invariant under shape changes.
-In the simplified Canham-Helfrich formulation, saddle splay energy is an indicator of topological transitions, thanks to the  Gauss-Bonnet theorem
-\cite{TerziDeserno17}.
-PI-RR showed that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}.
-
-To evaluate $\KG$, we will combine the string method from PI-Ryham's work on fusion \cite{RyKlYaCo16} with
-the present particle simulations. 
-%The string method is a numerical scheme that finds
-%least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}.
+To evaluate $\KG$, we will combine the present particle simulations with the string method 
+from PI-RR's work on membrane fusion \cite{RyKlYaCo16}. The string method is a numerical scheme that finds
+least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}. 
+In the simplified Canham-Helfrich formulation, saddle splay energy is an exact indicator of topological transitions, 
+thanks to the  Gauss-Bonnet theorem \cite{TerziDeserno17}.
+More generally, PI-RR has shown that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}. 
+As a result, saddle splay can quantified from the transition energies of a least energy path of pore formation (Figure \ref{fig:saddle_splay}).   
 %Using the string method, we will evaluate the transition energies between the intact pancake shape,
@@
 %
-The twist deformation is a fully three-dimensional deformation. 
-(Specific Aim 3 address outstanding implementation issues like three-dimensional boundary integral solvers.) 
-It is closely related to the assumption of lateral fluidity in membranes \cite{Hamm2000}. Note that tilt is locally non-zero whenever twist is non-zero.
-That is because the surface gradient $\nabla {\bf n}$ equals the second fundamental form, and is therefore symmetric, whenever ${\bf n} = {\bf N}$ locally.
 
@@
 \subsubsection{HK elastic energy form}
-It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
- whether \eqref{ansatz3} contains a complete list of consistent deformations.
-\textbf{(i)} Researcher have assumed that $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}.
-  Based on \eqref{eq:twist_energy}, a value $\KT = 0$ leads to the
-  unphysical conclusion that there are bilayers with $\nabla {\bf n} \to \infty$ but $E \to 0.$ 
+The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
+\textbf{(i)} Researcher have assumed that $\KT = 0$ because of the relationship between twist the assumption of lateral fluidity in membranes 
+\cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}. 
+A value $\KT = 0$, however, makes \eqref{ansatz3} noncoercive and leads to the nonphysical conclusion that there are bilayers 
+with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
   \textbf{(ii)}
@@
 Later, \cite{C9SM02079A} 
-  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
+and \cite{PhysRevE.102.042406} independently identified an inconsistency an the argument used by \cite{TerziDeserno17} arising
 from a transversal tilt invariance assumption.
-  The PI Ryham showed,  that the tilt vector $T = {\bf n}/{\bf n}\cdot {\bf N} - {\bf N}$ leads to unphysical cusps when constraining membrane thickness  \cite{RyKlYaCo16}.  
+In \cite{RyKlYaCo16}, the PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
   \textbf{(iii)}
@@
 barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
-Furthermore, the stability requirements of \eqref{ansatz3} are $\KB > 0$, $K_T > 0$, $\KG \geq -4\KB$
-and $\KG \geq -4\KT$. Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14},
-suggesting a somewhat smaller magnitude for $\KG$.
+Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.
 
-% The form of the elastic energy density \eqref{ansatz3} is the same as
-%the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
-%a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
-%The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
-%liquid crystal theory. However, the ``bend'' distortion from nematics  
-%is not present in monolayers since the directors have no dependence in the normal direction.
-%There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection.
-
-  We suspect the reason why, after twenty years, the field has yet to reach a consensus 
-  as to the form of \eqref{ansatz3} has to do with the Taylor expansions used to derive the elastic energy density. 
-  Past researchers expressed the strain tensor in
-  terms of the orthonormal frame $\{{\bf e}_1, {\bf e}_2, {\bf N}\}$ with surface tangent vectors ${\bf e}_i$ and surface normal ${\bf N}$.  
-  In this frame, there is a coupling between the gradients of all three terms ${\bf x}_0,$ $\zeta$ and ${\bf n}$ of the surface deformation field.
-  %\eqref{LMdeformation}.
-  Subtle differential geometric arguments are needed to evaluate the terms in the Taylor expansion,
-  and these couplings can lead to an energy density with more than ten parameters, for example \cite{PhysRevE.102.042406}.
+% The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
+% liquid crystal theory. However, the ``bend'' distortion from nematics  
+% is not present in monolayers since the directors have no dependence in the normal direction.
+% There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection.
 
   We will revisit the HK analysis to see if any of the aforementioned inconsistencies can be resolved.
-  As a main analytical innovation, we have found that expanding the strain tensor in
-  terms of the orthonormal frame $\{{\bf e}'_1, {\bf e}'_2, n\}$ with ${\bf e}'_i$ perpendicular to ${\bf n}$
-  greatly simplifies the expansion because it decouples the gradient terms. As an illustration, the prominent works
-  \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
-  incompressibility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
-  However, we prove that when expressed in the $\{{\bf e}'_1, {\bf e}'_2, n\}$ frame, the incompressility condition is \emph{exact}
-  and is given by a Steiner-type polynomial in terms of $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
-  Aside from the special case of zero tilt, \cite{Hamm2000} and coworkers seem to have been unaware of this result.
+  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
+  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
+  and accounting for these couplings by Taylor expansion  
+  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
+
+The form of the elastic energy density \eqref{ansatz3} is the same as
+  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
+  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
+  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
+  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
+  Using this observation, we prove an exact identity 
+  that gives the incompressility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
+  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
+  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
 

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
finishing up 4.2.2

@@
 Therefore, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field ${\bf n}$ by
-interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $\mathbcal{W}$ from the interpolated shapes.
+interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$ from the interpolated shapes.
 
@@
 We propose to conduct calculations similar to the example of figure~\ref{fig:flattening} for other elastic moduli such as the effective twist modulus $\KT$.
-Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14}, and here the specific non-equilibrium shape consists of a single layer of amphiphilic particles on a hydrophobic substrate as illustrated by Figure~\ref{fig:deformations}D.
-Having a nonzero twist requires nonzero tilt, because the surface gradient of the lipid directoy equals the second fundamental form, and is therefore symmetric, whenever tilt is zero locally.
-The twist deformation is a fully three-dimensional deformation.
-\S subsec:specific_aim_3 addresses outstanding implementation issues like three-dimensional boundary integral equation solvers.
+Molecular dynamics investigations find a twist modulus about 1 \kBT
+\cite{LeVeWa14}, and here the specific non-equilibrium shape consists of
+a single layer of amphiphilic particles on a hydrophobic substrate as
+illustrated by Figure~\ref{fig:deformations}D. Having a nonzero twist
+requires nonzero tilt, because the surface gradient of the lipid
+directoy equals the second fundamental form, and is therefore symmetric,
+whenever tilt is zero locally. The twist deformation is a fully
+three-dimensional deformation. \S\ref{subsec:specific_aim_3} addresses outstanding implementation issues like three-dimensional boundary integral equation solvers.
 

### 2020-11-12 NSF2020/Description/specificaim2_ver2.tex
finishing up 4.2.2

@@
 \subsubsection{Novel reciprocal identities}
-In the course of our study, we have found it useful to devise certain reciprocal identities that
-allow us to calculate forces accurately without having to resort to overly complicated numerical integration schemes. 
-At issue is that there is a break-down in numerical accuracy for the gradient of water activity near the particle
-boundaries (see Figure \ref{fig:bierror}).
-This is unfortunate the boundary is exactly where we need the gradients to be accurate in order for the formulas \eqref{forceandtorque}
-to be meaningful. To get around this issue, we prove the following identity
-  \begin{equation}
+The force and torque formulas~\eqref{forceandtorque} require the
+hydrophobic stress along the particle boundaries. Unfortunately,
+standard quadrature formulas to estimate $\nabla u$ on the particle
+boundaries introduces large amounts of quadrature error
+(Figure~\ref{fig:bierror}). Therefore, it is useful to devise reciprocal
+identities for the force and torque on body $i$ that does not
+require integration along body $i$. This is achieved using the identity 
+\begin{align}
     \label{eq:reciprocal}
 {\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
-{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S
-  \end{equation}
-for $i = 1\dots, N$. Here $u = \sum_{i=1}^N u_i$ is a sum of solutions $u_i$ the screened Laplace equation,
-$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i \cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$ and
-$[\cdot]$ denotes the jump across $\partial \Omega.$  It turns out that because of \cite{eq:reciprocal},
-we no longer require knowledge of the gradient on the boundary, which is enormously beneficial for calculating force and torque.
+{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf
+  x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} +
+  \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, 
+\end{align}
+for $i=1,\ldots,N$, which we have proved. Here $u = \sum_{i=1}^N u_i$ is
+a sum of solutions $u_i$ the screened Laplace equation,
+$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i
+\cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$ and
+$[\cdot]$ denotes the jump across $\partial \Omega.$  It turns out that
+because of \eqref{eq:reciprocal}, we no longer require knowledge of the
+gradient on the boundary, which is enormously beneficial for calculating
+force and torque.

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
yny specific aim 1

@@
 \cite{PhysRevLett.117.188102, ARGUDO20161619}.
-This proposal will develop much-needed mathematical analysis to resolve
-these controversies due to the assumptions in the HK theory. 
-%Using the HK  model as a base,
-%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
-%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
-%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
-%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.  
 %
@@
 %
+This proposal will develop much-needed mathematical analysis to resolve
+these controversies due to the assumptions in the HK theory. 
+%Using the HK  model as a base,
+%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
+%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
+%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
+%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.
 
@@
 The parameter $k_0$ is the spontaneous curvature and determines the
-preferred lipid splay~\cite{RoLi15,Kozlov2007}.  As an illustration, the
-lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
-%as a result of  %having a relatively long acyl chain. 
-and these lipids would preferentially line the upper monolayer in Figure \ref{fig:deformations}B  
-because the addition of a positive splay 
-to the negative spontaneous curvature leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
-The subtraction of $k_0^2$ makes the energy distortion free
-\cite{Helfrich73,PhysRevLett.113.248102,Hamm2000}.
+preferred lipid splay~\cite{RoLi15,Kozlov2007}.  
+%As an illustration, the
+%lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
+%%as a result of  %having a relatively long acyl chain. 
+%and these lipids would preferentially line the upper monolayer in Figure \ref{fig:deformations}B  
+%because the addition of a positive splay 
+%to the negative spontaneous curvature leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
+%The subtraction of $k_0^2$ makes the energy distortion free
+%\cite{Helfrich73,PhysRevLett.113.248102,Hamm2000}.
 
@@
 %\end{center}
-\subsubsection{Simulations of the HARP model to estimate elastic moduli}
+\subsubsection{Simulations of the HARP model to estimate elastic moduli and energy}
 %To characterize material properties of a bilayer, we compare the energies and forces generated by
@@
 As the bent membrane flattens we find that both the membrane self-interaction energy $\Phi$ and the elastic energy ${\cal W}$ decrease,
-and because the saddle splay, twist and tilt stay zeros, the slope gives the bending modulus in this case.
+and because the saddle splay, twist and tilt stay zero, the slope gives the bending modulus in this case.
 
@@
 To evaluate $\KG$, we will combine the present particle simulations with the string method 
-from PI-RR's work on membrane fusion \cite{RyKlYaCo16}. The string method is a numerical scheme that finds
+from PI RR's work on membrane fusion \cite{RyKlYaCo16}. The string method is a numerical scheme that finds
 least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}. 
@@
 thanks to the  Gauss-Bonnet theorem \cite{TerziDeserno17}.
-More generally, PI-RR has shown that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}. 
+More generally, PI RR has shown that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}. 
 As a result, saddle splay can quantified from the transition energies of a least energy path of pore formation (Figure \ref{fig:saddle_splay}).   
@@
 
-\subsubsection{HK elastic energy form}
+%\subsubsection{HK elastic energy form}
+\noindent{\bf{HK elastic energy form:}}
 The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
@@
 \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}. 
-A value $\KT = 0$, however, makes \eqref{ansatz3} noncoercive and leads to the nonphysical conclusion that there are bilayers 
-with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
+%A value $\KT = 0$, however, makes \eqref{ansatz3} noncoercive and leads to the nonphysical conclusion that there are bilayers 
+%with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
 \textbf{(ii)}
@@
 from a transversal tilt invariance assumption.
-In \cite{RyKlYaCo16}, the PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
+In \cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
   \textbf{(iii)}
   Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
-\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
-barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
-Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.
+\cite{SIEGEL2004366,SIEGEL20085200}, which gives rise to a larger energy barrier for monolayer fusion than is found by experiments \cite{FrRoPi17,Tran7106,TerziDeserno17}.
+%
+%
+%Researchers point out, however, that this theoretical value requires a larger energy 
+%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
+%Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.
 
@@
 
-  We will revisit the HK analysis to see if any of the aforementioned inconsistencies can be resolved.
-  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
-  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
-  and accounting for these couplings by Taylor expansion  
-  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
-
  The form of the elastic energy density \eqref{ansatz3} is the same as
@@
   a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
-  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
-  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
-  Using this observation, we prove an exact identity 
-  that gives the incompressility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
+  Based on this observation, we propose to examine the HK analysis to resolve the aforementioned inconsistencies: We expand the strain tensor in terms of a plane
+  perpendicular to ${\bf n}$ (instead of the monolayer tangent plane as done in the past works) so that the gradient terms in the elastic energy completely decouple. 
+  Using this expansion we prove an exact identity 
+  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
   In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
@@
 
-%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
-%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
-%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
-%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
-%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
-%  This gives the continuum elastic energy equals
-%  \begin{equation}
-%    \label{eq:twist_energy}
-%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
-%  \end{equation}
-%  which we compare to the HAP simulation data.
+%  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
+%  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
+%  and accounting for these couplings by Taylor expansion  
+%  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
+%
+%The form of the elastic energy density \eqref{ansatz3} is the same as
+%  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
+%  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
+%  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
+%  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
+%  Using this observation, we prove an exact identity 
+%  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
+%  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
+%  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
+%  
+%%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
+%%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
+%%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
+%%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
+%%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
+%%  This gives the continuum elastic energy equals
+%%  \begin{equation}
+%%    \label{eq:twist_energy}
+%%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
+%%  \end{equation}
+%%  which we compare to the HAP simulation data.
+%
+\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
+The HAP energy converges to the surface energy in the limit of vanishing screening length 
+and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
+area measures supported on the particle boundaries.  This is analogous to the sharp interface limit in the phase-field functional formulation \cite{Modica87, MODICA1987487, LuMo89}. 
+PI RR has worked directly on phase field approximations of membrane bending energy 
+\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman equation \cite{1531-3492_2006_2_357,Lee2018}.
+The proposed analysis is a natural outgrowth or prior work because the linearization of the Poisson-Boltzmann equation is the screened Laplace equations \eqref{SL}.
 
-%\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$}
-%The HAP energy converges to the surface energy in the limit of vanishing screening length 
-%and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
-%area measures supported on the particle boundaries.  This is analogous to the sharp interface limit in the phase-field functional formulation \cite{Modica87, MODICA1987487, LuMo89}. 
-%PI RR has worked directly on phase field approximations of membrane bending energy 
-%\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman equation \cite{1531-3492_2006_2_357,Lee2018}.
-%The proposed analysis is a natural outgrowth or prior work because the linearization of the Poisson-Boltzmann equation is the screened Laplace equations \eqref{SL}.
+We will develop the mathematical connections between the HAP energy and the energy functionals used in the gradient theory of phase transitions. 
+The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
+The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
+to the characteristic function of a set solving a perimeter minimization problem 
+\cite{Modica87, MODICA1987487, LuMo89}. 
 %
-%We will develop some of the mathematical connections between the HAP energy and the energy functionals used in the gradient theory of phase transitions. 
-%%The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
-%%The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
-%%to the characteristic function of a set solving a perimeter minimization problem 
-%%\cite{Modica87, MODICA1987487, LuMo89}. 
-%%
-%%
-%One of the basic questions is to establish the HAP convergence rate as a function of particle geometry 
-%\cite{LuMo89}, which can be used as an essential benchmark for numerical validation. 
+%
+One of the basic questions is to establish the HAP convergence rate as a function of particle geometry 
+\cite{LuMo89}, which can be used as an essential benchmark for numerical validation. 
 %In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  
@@
 %\cite{https://doi.org/10.1038/s41467-019-09787-6}
-
-% It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
-% whether \eqref{ansatz3} contains a complete list of consistent deformations.
-%\textbf{(i)} Researcher have assumed that $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}.
-%  Based on \eqref{eq:twist_energy}, a value $\KT = 0$ leads to the
-%  unphysical conclusion that there are bilayers with $\nabla {\bf n} \to \infty$ but $E \to 0.$ 
-%  \textbf{(ii)}
-%  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
-%  Later, \cite{C9SM02079A} 
-%  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
-%  from a transversal tilt invariance assumption.
-%  The PI Ryham showed,  that the tilt vector $T = {\bf n}/{\bf n}\cdot {\bf N} - {\bf N}$ leads to unphysical cusps when constraining membrane thickness  \cite{RyKlYaCo16}.  
-%  \textbf{(iii)}
-%  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
-%\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
-%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
-%Furthermore, the stability requirements of \eqref{ansatz3} are $\KB > 0$, $K_T > 0$, $\KG \geq -4\KB$
-%and $\KG \geq -4\KT$. Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14},
-%suggesting a somewhat smaller magnitude for $\KG$.
-
-%The form of the elastic energy density \eqref{ansatz3} is the same as
-%the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
-%a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
-%The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
-%liquid crystal theory. However, the ``bend'' distortion from nematics  
-%is not present in monolayers since the directors have no dependence in the normal direction.
-%There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection. 
 %
-%  We suspect the reason why, after twenty years, the field has yet to reach a consensus 
-%  as to the form of \eqref{ansatz3} has to do with the Taylor expansions used to derive the elastic energy density. 
-%  Past researchers expressed the strain tensor in
-%  terms of the orthonormal frame $\{{\bf e}_1, {\bf e}_2, {\bf N}\}$ with surface tangent vectors ${\bf e}_i$ and surface normal ${\bf N}$.  
-%  In this frame, there is a coupling between the gradients of all three terms ${\bf x}_0,$ $\zeta$ and ${\bf n}$ of the deformation \eqref{LMdeformation}.
-%  Subtle differential geometric arguments are needed to evaluate the terms in the Taylor expansion,
-%  and these couplings can lead to an energy density with more than ten parameters, for example \cite{PhysRevE.102.042406}.
 %
-%  We will revisit the HK analysis to see if any of the aforementioned inconsistencies can be resolved.
-%  As a main analytical innovation, we have found that expanding the strain tensor in
-%  terms of the orthonormal frame $\{{\bf e}'_1, {\bf e}'_2, n\}$ with ${\bf e}'_i$ perpendicular to ${\bf n}$
-%  greatly simplifies the expansion because it decouples the gradient terms. As an illustration, the prominent works
-%  \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
-%  incompressibility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
-%  However, we prove that when expressed in the $\{{\bf e}'_1, {\bf e}'_2, n\}$ frame, the incompressility condition is \emph{exact}
-%  and is given by a Steiner-type polynomial in terms of $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
-%  Aside from the special case of zero tilt, \cite{Hamm2000} and coworkers seem to have been unaware of this result.
-
-Our investigations will leave open the possibility that the free energy of monolayers and bilayers is non-local. 
-We have shown that hydrophic attraction is a non-additive force, meaning the force of attraction between two
-particles is dependent on the position a third or more particles \cite{SilveraBatista1242477}.
-Conceptually, this would arise in continuum theory if two monolayer surfaces
-had a different elastic energy density despite having locally identical curvatures and directors.
-The boundary integral formulation described in Specific Aim 3 easily accomodates additional linear PDE and
-we will extend our study to include charge lipids and weak electrolytes \cite{C9SM00772E}.
+%% It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
+%% whether \eqref{ansatz3} contains a complete list of consistent deformations.
+%%\textbf{(i)} Researcher have assumed that $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}.
+%%  Based on \eqref{eq:twist_energy}, a value $\KT = 0$ leads to the
+%%  unphysical conclusion that there are bilayers with $\nabla {\bf n} \to \infty$ but $E \to 0.$ 
+%%  \textbf{(ii)}
+%%  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
+%%  Later, \cite{C9SM02079A} 
+%%  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
+%%  from a transversal tilt invariance assumption.
+%%  The PI Ryham showed,  that the tilt vector $T = {\bf n}/{\bf n}\cdot {\bf N} - {\bf N}$ leads to unphysical cusps when constraining membrane thickness  \cite{RyKlYaCo16}.  
+%%  \textbf{(iii)}
+%%  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
+%%\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
+%%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
+%%Furthermore, the stability requirements of \eqref{ansatz3} are $\KB > 0$, $K_T > 0$, $\KG \geq -4\KB$
+%%and $\KG \geq -4\KT$. Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14},
+%%suggesting a somewhat smaller magnitude for $\KG$.
+%
+% 
+%%The form of the elastic energy density \eqref{ansatz3} is the same as
+%%the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
+%%a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
+%%The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
+%%liquid crystal theory. However, the ``bend'' distortion from nematics  
+%%is not present in monolayers since the directors have no dependence in the normal direction.
+%%There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection. 
+%%  
+%%  We suspect the reason why, after twenty years, the field has yet to reach a consensus 
+%%  as to the form of \eqref{ansatz3} has to do with the Taylor expansions used to derive the elastic energy density. 
+%%  Past researchers expressed the strain tensor in
+%%  terms of the orthonormal frame $\{{\bf e}_1, {\bf e}_2, {\bf N}\}$ with surface tangent vectors ${\bf e}_i$ and surface normal ${\bf N}$.  
+%%  In this frame, there is a coupling between the gradients of all three terms ${\bf x}_0,$ $\zeta$ and ${\bf n}$ of the deformation \eqref{LMdeformation}.
+%%  Subtle differential geometric arguments are needed to evaluate the terms in the Taylor expansion,
+%%  and these couplings can lead to an energy density with more than ten parameters, for example \cite{PhysRevE.102.042406}.
+%%
+%%  We will revisit the HK analysis to see if any of the aforementioned inconsistencies can be resolved.
+%%  As a main analytical innovation, we have found that expanding the strain tensor in
+%%  terms of the orthonormal frame $\{{\bf e}'_1, {\bf e}'_2, n\}$ with ${\bf e}'_i$ perpendicular to ${\bf n}$
+%%  greatly simplifies the expansion because it decouples the gradient terms. As an illustration, the prominent works
+%%  \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
+%%  incompressibility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
+%%  However, we prove that when expressed in the $\{{\bf e}'_1, {\bf e}'_2, n\}$ frame, the incompressility condition is \emph{exact}
+%%  and is given by a Steiner-type polynomial in terms of $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
+%%  Aside from the special case of zero tilt, \cite{Hamm2000} and coworkers seem to have been unaware of this result.
+%
+%Our investigations will leave open the possibility that the free energy of monolayers and bilayers is non-local. 
+%We have shown that hydrophic attraction is a non-additive force, meaning the force of attraction between two
+%particles is dependent on the position a third or more particles \cite{SilveraBatista1242477}.
+%Conceptually, this would arise in continuum theory if two monolayer surfaces
+%had a different elastic energy density despite having locally identical curvatures and directors.
+%The boundary integral formulation described in Specific Aim 3 easily accomodates additional linear PDE and
+%we will extend our study to include charge lipids and weak electrolytes \cite{C9SM00772E}.

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
working on 4.1

@@
 {\bf (i)} determine the value of the elastic moduli $\KB$,
-$\KT$, $\KG$ and $\KTH$, and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
+$\KT$, $\KG$, and $\KTH$, and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
 An accurate and robust way to measure material properties is to track the evolution of the bilayer as
@@
 \end{wrapfigure}
-it relaxes from an initially non-equilibrium configuration \cite{PhysRevLett.117.188102}.
-Figure~\ref{fig:flattening} shows an example where the initial configuration of a lipid bilayer patch contains only
-splay deformation without any other components (saddle splay, twist and tilt). 
-As the bent membrane flattens we find that both the membrane self-interaction energy $\Phi$ and the elastic energy ${\cal W}$ decrease,
-and because the saddle splay, twist and tilt stay zero, the slope gives the bending modulus in this case.
+it relaxes from an initially non-equilibrium
+configuration~\cite{PhysRevLett.117.188102}. Figure~\ref{fig:flattening}
+shows an example where the initial configuration of a lipid bilayer
+patch contains only splay deformation without any other components
+(saddle splay, twist and tilt). As the bent membrane flattens we find
+that both the membrane self-interaction energy $\Phi$ and the elastic
+energy ${\cal W}$ decrease, and because the saddle splay, twist, and
+tilt stay zero, the slope gives the bending modulus in this case.
 
@@
 
-\begin{wrapfigure}[12]{l}{0.32\textwidth}
+\begin{wrapfigure}[11]{l}{0.32\textwidth}
 \centerline{\includegraphics[width=0.32\textwidth]{Figures/SaddleSplayDiagram.pdf}}
+  \vspace{-8pt}
 \caption{\label{fig:saddle_splay} \footnotesize Determination of
@@
 
-We propose to conduct calculations similar to the example of figure~\ref{fig:flattening} for other elastic moduli such as the effective twist modulus $\KT$.
-Molecular dynamics investigations find a twist modulus about 1 \kBT
-\cite{LeVeWa14}, and here the specific non-equilibrium shape consists of
+We propose to conduct calculations similar to the example of Figure~\ref{fig:flattening} for other elastic moduli such as the effective twist modulus $\KT$.
+Molecular dynamics investigations find a twist modulus about 1
+\kBT~\cite{LeVeWa14}, and here the specific non-equilibrium shape consists of
 a single layer of amphiphilic particles on a hydrophobic substrate as

### 2020-11-12 NSF2020/Description/specificaim2_ver2.tex
working on 4.1

@@
 identities for the force and torque on body $i$ that does not
-require integration along body $i$. This is achieved using the identity 
+require integration along body $i$. One identity, that we have proved,
+is
 \begin{align}
@@
 \end{align}
-for $i=1,\ldots,N$, which we have proved. Here $u = \sum_{i=1}^N u_i$ is
-a sum of solutions $u_i$ the screened Laplace equation,
+for $i=1,\ldots,N$. Here, $u_i$ is the solution of the screened Laplace
+equation when only the contribution from particle $i$ is considered and
 $\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i
-\cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$ and
-$[\cdot]$ denotes the jump across $\partial \Omega.$  It turns out that
-because of \eqref{eq:reciprocal}, we no longer require knowledge of the
-gradient on the boundary, which is enormously beneficial for calculating
-force and torque.
+\cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$.
+Equation~\eqref{eq:reciprocal} does not require knowledge of $\nabla u$
+on the particle boundary, and this is enormously beneficial for
+calculating force and torque.

### 2020-11-12 NSF2020/Description/specificaim3_ver2.tex
working on 4.1

@@
   \label{eq:LP}
-  u(x) = \int_{\partial\Omega} K(x,y) \sigma(y)\,ds_y,
+  u(\mathbf{x}) = \int_{\partial\Omega} K(\mathbf{x},\mathbf{y})
+  \sigma(\mathbf{y})\,dS,
 \end{align}
-where $\sigma$ is an unknown density function, and $K(x,y)$ is a
-derivative of the fundamental solution of the underlying PDE. By
-matching the boundary condition at $x_0 \in \partial\Omega$ with the
-limit of equation~\eqref{eq:LP} as $x\rightarrow x_0$, a BIE for the
-density function is formed. Numerical methods to solve BIEs have several
-advantages over their PDE-based counterpart: by construction, the layer
-potential~\eqref{eq:LP} satisfies far-field conditions; only
+where $\sigma$ is an unknown density function, and
+$K(\mathbf{x},\mathbf{y})$ is a derivative of the fundamental solution
+of the underlying PDE. By matching the boundary condition at
+$\mathbf{x}_0 \in \partial\Omega$ with the limit of
+equation~\eqref{eq:LP} as $\mathbf{x}\rightarrow \mathbf{x}_0$, a BIE
+for the density function is formed. Numerical methods to solve BIEs have
+several advantages over their PDE-based counterpart: by construction,
+the layer potential~\eqref{eq:LP} satisfies far-field conditions; only
 $\partial\Omega$ needs to be discretized; carefully chosen kernels
-$K(x,y)$ result in a well-conditioned linear system that is solved with
-a mesh-independent number of GMRES iterations; and high-order or
-spectral accuracy is attainable with appropriate quadrature methods. In
-our previous work~\cite{Fu2018_SIAM} we demonstrate that BIEs are a
-powerful tool to simulate two-dimensional suspensions of amphiphilic
-particles. In addition to improving two-dimensional simulations, we will
-extend the results to three dimensions using a standard
-three-dimensional BIE formulation of the screened Laplace
-equation~\cite{ying_2006} and a well-conditioned BIE formulation of the
-mobility problem~\cite{manasthesis, rac-gre2016}.
+$K(\mathbf{x},\mathbf{y})$ result in a well-conditioned linear system
+that is solved with a mesh-independent number of GMRES iterations; and
+high-order or spectral accuracy is attainable with appropriate
+quadrature methods. In our previous work~\cite{Fu2018_SIAM} we
+demonstrate that BIEs are a powerful tool to simulate two-dimensional
+suspensions of amphiphilic particles. In addition to improving
+two-dimensional simulations, we will extend the results to three
+dimensions using a standard three-dimensional BIE formulation of the
+screened Laplace equation~\cite{ying_2006} and a well-conditioned BIE
+formulation of the mobility problem~\cite{manasthesis, rac-gre2016}.
 
@@
 
-\begin{wrapfigure}[21]{r}{3.0in}
+\begin{wrapfigure}[21]{r}{2.5in}
 %\vspace*{+15pt}
-\centerline{\includegraphics[width=3.0in]{figures/integrands}}
+\centerline{\includegraphics[width=2.5in]{figures/integrands}}
 \vspace*{-13pt}
-\caption{{\footnotesize The Fourier modes of $K(x_0,y)$ and $K_2(x_0,y)$
-  where $\|x_0\| = 0.99$ and $y \in \partial\Omega$, where
-  $\partial\Omega$ is the unit circle. The trapezoid rule applied to the
-  red integrand has large amounts of error, but the trapezoid rule is
-  much more accurate when applied to the blue integrand. Since the
-  difference between the red and blue curves can be accurately computed
-  with the barycentric quadrature rule, the quadrature error applied to
-  layer potentials for the screen Laplace equation will be uniformly
-  bounded in $\Omega$.}}
+  \caption{{\footnotesize The Fourier modes of
+  $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
+  $|\mathbf{x_0}| = 0.99$ and $\mathbf{y} \in \partial\Omega$, and
+  $\Omega$ is the unit circle. The trapezoid rule applied to the red
+  integrand has large amounts of error, but the trapezoid rule is much
+  more accurate when applied to the blue integrand. Since the difference
+  between the red and blue curves can be accurately computed with the
+  barycentric quadrature rule, the quadrature error applied to layer
+  potentials for the screen Laplace equation will be uniformly bounded
+  in $\Omega$.}}
 \label{fig:integrands}
@@
 particles, and this results in nearly-singular integrands. Quadrature
-methods for these integrands has received a lot of attention in
-two and three dimensions~\cite{alpert, kapur, sidi, duffy, bruno1,
-bruno2, davis_1984, graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003,
+methods for these integrands has received a lot of attention in two and
+three dimensions~\cite{alpert, kapur, sidi, duffy, bruno1, bruno2,
+davis_1984, graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003,
 khayat_2005, schwab_1992, ying_2006, beale1, beale2, goodman_1990,
@@
 equation. This will be done by recognizing that the fundamental solution
-of the screened Laplace equation can be decomposed as $K(x,y) = K_1(x,y)
-+ K_2(x,y)$, where $K_1(x,y) = -\log\|x - y\|$ and $K_2(x,y) = K(x,y) +
-\log\|x - y\|$. Using this decomposition, layer potentials involving
-$K_1(x,y)$ can be accurately computed with the barycentric quadrature
-rule~\cite{ioa-pap-per1991}, and layer potentials involving $K_2(x,y)$
-can be accurately computed with the trapezoid rule since the kernel is
-bounded for all $x$ and $y$. The proposed method is demonstrated in
+of the screened Laplace equation can be decomposed as
+$K(\mathbf{x},\mathbf{y}) = K_1(\mathbf{x},\mathbf{y}) +
+K_2(\mathbf{x},\mathbf{y})$, where $K_1(\mathbf{x},\mathbf{y}) =
+-\log|\mathbf{x} - \mathbf{y}|$ and $K_2(\mathbf{x},\mathbf{y}) =
+K(\mathbf{x},\mathbf{y}) + \log|\mathbf{x} - \mathbf{y}|$. Using this
+decomposition, layer potentials involving $K_1(\mathbf{x},\mathbf{y})$
+can be accurately computed with the barycentric quadrature
+rule~\cite{ioa-pap-per1991}, and layer potentials involving
+$K_2(\mathbf{x},\mathbf{y})$ can be accurately computed with the
+trapezoid rule since the kernel is bounded for all $\mathbf{x}$ and
+$\mathbf{y}$. The proposed method is demonstrated in
 Figure~\ref{fig:integrands} where the amplitude of the Fourier modes of
-$K(x_0,y)$ and $K_2(x_0,y)$ are plotted. The quadrature of the trapezoid
-rule is the sum of the Fourier amplitudes not captured at the
-resolution.
+$K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ are
+plotted. The quadrature of the trapezoid rule is the sum of the Fourier
+amplitudes not captured at the resolution.
 

### 2020-11-12 NSF2020/Description/specificaim1_ver2.tex
finished up sec 4.1

@@
 The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
-\textbf{(i)} Researcher have assumed that $\KT = 0$ because of the relationship between twist the assumption of lateral fluidity in membranes 
-\cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}. 
+\textbf{(i)} Researchers have assumed that $\KT = 0$ because of the
+relationship between twist the assumption of lateral fluidity in
+membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
+PhysRevE.102.042406}. 
 %A value $\KT = 0$, however, makes \eqref{ansatz3} noncoercive and leads to the nonphysical conclusion that there are bilayers 
 %with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
-\textbf{(ii)}
-Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
-Later, \cite{C9SM02079A} 
-and \cite{PhysRevE.102.042406} independently identified an inconsistency an the argument used by \cite{TerziDeserno17} arising
+\textbf{(ii)} Recently,~\cite{TerziDeserno17} derived a tilt curvature
+term that was neglected from the HK analysis~\cite{Hamm2000}.
+Later,~\cite{C9SM02079A} and~\cite{PhysRevE.102.042406} independently
+identified an inconsistency an the argument used
+by~\cite{TerziDeserno17} arising
 from a transversal tilt invariance assumption.
-In \cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
-  \textbf{(iii)}
-  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
-\cite{SIEGEL2004366,SIEGEL20085200}, which gives rise to a larger energy barrier for monolayer fusion than is found by experiments \cite{FrRoPi17,Tran7106,TerziDeserno17}.
+In~\cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
+\textbf{(iii)} Theoretical analysis of lipid phase transitions predict a
+negative saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
+SIEGEL20085200}, that gives rise to a larger energy barrier for
+monolayer fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
+TerziDeserno17}.
 %
@@
 
- The form of the elastic energy density \eqref{ansatz3} is the same as
-  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
-  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
-  Based on this observation, we propose to examine the HK analysis to resolve the aforementioned inconsistencies: We expand the strain tensor in terms of a plane
-  perpendicular to ${\bf n}$ (instead of the monolayer tangent plane as done in the past works) so that the gradient terms in the elastic energy completely decouple. 
-  Using this expansion we prove an exact identity 
-  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
-  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
-  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
+The form of the elastic energy density~\eqref{ansatz3} is the same as
+the Oseen-Frank energy density for nematic liquid
+crystals~\cite{ANDRIENKO2018520, Tran7106, Helfrich73}. In fact, a lipid
+monolayer acts as one layer in a smectic phase~\cite{REYESMATEO1995978,
+Rangamani20140463, PhysRevLett.113.248102}. Based on this observation,
+we propose to examine the HK analysis to resolve the aforementioned
+inconsistencies. We will expand the strain tensor in terms of a plane
+perpendicular to ${\bf n}$ (instead of the monolayer tangent plane as
+done in the past works) so that the gradient terms in the elastic energy
+completely decouple. Using this expansion we prove an exact identity
+that gives the incompressibility condition by a Steiner-type polynomial
+in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}. In contrast,
+the works~\cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000,
+C9SM02079A} utilize an approximate identity for incompressibility, and
+so we can offer a considerably more accurate analysis of monolayer
+energy.
 
@@
 \subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
-The HAP energy converges to the surface energy in the limit of vanishing screening length 
-and the boundary layers of the minimizers (the solutions to the screen Laplace equation) converges to 
-area measures supported on the particle boundaries.  This is analogous to the sharp interface limit in the phase-field functional formulation \cite{Modica87, MODICA1987487, LuMo89}. 
-PI RR has worked directly on phase field approximations of membrane bending energy 
-\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman equation \cite{1531-3492_2006_2_357,Lee2018}.
-The proposed analysis is a natural outgrowth or prior work because the linearization of the Poisson-Boltzmann equation is the screened Laplace equations \eqref{SL}.
+The HAP energy converges to the surface energy in the limit of vanishing
+screening length and the boundary layers of the minimizers (the
+solutions to the screen Laplace equation) converges to area measures
+supported on the particle boundaries. This is analogous to the sharp
+interface limit in the phase-field functional
+formulation~\cite{Modica87, MODICA1987487, LuMo89}. PI RR has worked
+directly on phase field approximations of membrane bending
+energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
+equation~\cite{1531-3492_2006_2_357, Lee2018}. The proposed analysis is
+a natural outgrowth of prior work because the linearization of the
+Poisson-Boltzmann equation is the screened Laplace equations~\eqref{SL}.
 
-We will develop the mathematical connections between the HAP energy and the energy functionals used in the gradient theory of phase transitions. 
-The phase field functional approximates the perimeter of sublevel sets of a so-called phase field indicator function. 
-The approximation becomes sharp in the zero interfacial thickness limit and minimizers of the phase field functional converge (after normalization) 
-to the characteristic function of a set solving a perimeter minimization problem 
-\cite{Modica87, MODICA1987487, LuMo89}. 
+We will develop the mathematical connections between the HAP energy and
+the energy functionals used in the gradient theory of phase transitions.
+The phase field functional approximates the perimeter of sublevel sets
+of a so-called phase field indicator function. The approximation becomes
+sharp in the zero interfacial thickness limit and minimizers of the
+phase field functional converge (after normalization) to the
+characteristic function of a set solving a perimeter minimization
+problem~\cite{Modica87, MODICA1987487, LuMo89}. 
 %
 %
-One of the basic questions is to establish the HAP convergence rate as a function of particle geometry 
-\cite{LuMo89}, which can be used as an essential benchmark for numerical validation. 
+One of the basic questions is to establish the HAP convergence rate as a
+function of particle geometry~\cite{LuMo89}, which can be used as a
+benchmark for numerical validation. 
 %In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  

### 2020-11-12 NSF2020/Description/preliminarywork.tex
looked at fig 10
small changes

@@
 \includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
-\end{center}\vspace{-0.3in}
-\caption{\footnotesize (A) A vesicle formed by amphiphilic particles in
-  shear flow, and the tank-treading motion (B)--(D). The separation of
-  particle pairs in (B) and (C) illustrate inter-leaflet slip.  (E)--(G)
-  Tank-treading reaches a steady state in elliptical aspect ratio,
-  major-axis angle, and circumference.}
-\label{fig:tanktreading}
+\end{center}
+\vspace{-0.3in}
+\caption{\label{fig:tanktreading}\footnotesize (A) A vesicle formed by
+  amphiphilic particles in shear flow, and the tank-treading motion
+  (B)--(D). The separation of particle pairs in (B) and (C) illustrate
+  inter-leaflet slip.  (E)--(G) Tank-treading reaches a steady state in
+  elliptical aspect ratio, major-axis angle, and circumference.}
 \end{figure}
-\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow\label{sec:preliminary_work}} 
+
+\section{Preliminary work}
+\subsection{Estimating two-dimensional elastic
+moduli}
+%\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow\label{sec:preliminary_work}} 
 %\section{Preliminary work on elastic moduli}
@@
 this analytical solution (red curve) basically overlaps the midplane of the particle based solution (Figure \ref{fig:bend}A).
-We thereby derived a bending modulus $\KB$ in the range 8.51 -- 13.54 \kBT. Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.
+We thereby derived a bending modulus $\KB$ in the range 8.51--13.54 \kBT. Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.
 Experimental measurements have accurately determined the bending modulus for several lipid types, with 
@@
 34 $\pm$ 2 \kBT \;nm$^{-2}$. Manipulation experiments give a monolayer area modulus in the range 
-30 -- 40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}.
+30--40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}.
 
@@
 
-\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow} 
+\subsection{Two-dimensional vesicle hydrodynamics in shear flow} 
 %The motion of vesicles in shear flow is an important
@@
 length refers to the the mid-plane circumference. Thus, some of the
-external force is going into stretching the vesicle--the other part is
+external force is going into stretching the vesicle---the other part is
 going into bending and viscous dissipation. From our experiments, we

### 2020-11-12 NSF2020/Description/preliminarywork.tex
RJR going through prelim work

--- 2020-11-12 NSF2020/Description/preliminarywork.tex
@@
 \includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
-\end{center}\vspace{-0.3in}
-\caption{\footnotesize (A) A vesicle formed by amphiphilic particles in
-  shear flow, and the tank-treading motion (B)--(D). The separation of
-  particle pairs in (B) and (C) illustrate inter-leaflet slip.  (E)--(G)
-  Tank-treading reaches a steady state in elliptical aspect ratio,
-  major-axis angle, and circumference.}
-\label{fig:tanktreading}
+\end{center}
+\vspace{-0.3in}
+\caption{\label{fig:tanktreading}\footnotesize (A) A vesicle formed by
+  amphiphilic particles in shear flow, and the tank-treading motion
+  (B)--(D). The separation of particle pairs in (B) and (C) illustrate
+  inter-leaflet slip.  (E)--(G) Tank-treading reaches a steady state in
+  elliptical aspect ratio, major-axis angle, and circumference.}
 \end{figure}
-\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow\label{sec:preliminary_work}} 
-%\section{Preliminary work on elastic moduli}
+\section{Preliminary Work on Elasticity and Two-dimensional Vesicle Hydrodynamics in Shear Flow}
+\label{sec:preliminary_work}
+The motivation for Specific Aims 1-3
+stemmed from the successful of demonstration, gradient driven
+self-assembly of amphiphilic particles into two-dimensional micelles,
+bilayer membranes, \cite{Fu2018_SIAM}, and recreation of the vesicles tank-treading phenomenon
+under a new coarse-grained description.
+
+Our preliminary work on membrane elasticity 
+is particulary encouraging because the effective bending, stretch, and tilt elastic moduli we calculated
+for collections of amphiphile were in excellent agreement with the experimental values.
+The initial success is underscored by the fact we assigned reasonable physical values to 
+the main model parameters of the HAP energy, rather than tuning parameter.
+
 To derive a bending modulus, we first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
@@
 
-Our preliminary work is encouraging because in all cases, the bending, stretch, and tilt elastic moduli for the collection of amphiphiles
-were in excellent agreement with the experimental values. This fact is especially remarkable 
-since we assigned the main model parameters $\rho$ and $\gamma$ reasonable physical values, rather than using them as tuning parameter. 
 Nevertheless, the characterization of material properties is incomplete. For one, the preliminary simulations involved relatively low particle numbers (20 to 30), and so we still need to
 perform convergence studies with large particle-number systems to arrive at conclusive results. Secondly, we have yet to establish a functional
-relationship between the model parameters and elastic moduli. Finally, to have relevance in physics and biology
-we must incorporate the remaining twist and saddle splay deformations.
+relationship between the model parameters and elastic moduli.
+Finally, to have relevance in physics and biology we must incorporate the remaining twist and saddle splay deformations.
 The following simulation outline shows how will achieve aims.

### 2020-11-12 NSF2020/Description/preliminarywork.tex

--- 2020-11-12 NSF2020/Description/preliminarywork.tex
@@
 %\section{Preliminary work on elastic moduli}
+
 To derive a bending modulus, we first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 

### 2020-11-12 NSF2020/Description/specificaim2_ver2.tex

@@
 
-\begin{figure}[h]
-  \centering{\includegraphics[width=0.8\textwidth]{Figures/domain.pdf}}
-    \caption{\label{fig:flow_map}}
-\end{figure}
+%\begin{figure}[h]
+\begin{wrapfigure}[]{r}{0.60\textwidth}
+  \centering{\includegraphics[width=0.6\textwidth]{Figures/domain.pdf}}
+    \caption{\label{fig:flow_map} \todo[inline]{Missing caption}}
+\end{wrapfigure}
+%\end{figure}
 
@@
 \subsubsection{Vesicles in background flows}
-Numerically solving the Stokes-screened Laplace system~\eqref{SL}
+Numerically solving the Stokes and screened Laplace system~\eqref{SL}
 and~\eqref{eq:stokes} is nontrivial, and we will develop efficient,
@@
 We will compare the behavior of our particle-based vesicles in Stokes
-flow to well-established results. \todo{What are the known results?}
-Researchers have devised models to enforce area incompressibility and
+flow to well-established models that enforce area incompressibility and
 volume conservation in vesicle membrane

### 2020-11-12 NSF2020/Description/specificaim3_ver2.tex

@@
 
+\begin{wrapfigure}[21]{r}{2.5in}
+%\vspace*{+15pt}
+\centerline{\includegraphics[width=2.5in]{figures/integrands}}
+\vspace*{-13pt}
+  \caption{{\footnotesize The Fourier modes of
+  $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
+  $|\mathbf{x_0}| = 0.99$ and $\mathbf{y} \in \partial\Omega$, and
+  $\Omega$ is the unit circle. The trapezoid rule applied to the red
+  integrand has large amounts of error, but the trapezoid rule is much
+  more accurate when applied to the blue integrand. Since the difference
+  between the red and blue curves can be accurately computed with the
+  barycentric quadrature rule, the quadrature error applied to layer
+  potentials for the screen Laplace equation will be uniformly bounded
+  in $\Omega$.}}
+\label{fig:integrands}
+\end{wrapfigure}
 Significant challenges to solve BIEs include solving dense linear
@@
 
-\begin{wrapfigure}[21]{r}{2.5in}
-%\vspace*{+15pt}
-\centerline{\includegraphics[width=2.5in]{figures/integrands}}
-\vspace*{-13pt}
-  \caption{{\footnotesize The Fourier modes of
-  $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
-  $|\mathbf{x_0}| = 0.99$ and $\mathbf{y} \in \partial\Omega$, and
-  $\Omega$ is the unit circle. The trapezoid rule applied to the red
-  integrand has large amounts of error, but the trapezoid rule is much
-  more accurate when applied to the blue integrand. Since the difference
-  between the red and blue curves can be accurately computed with the
-  barycentric quadrature rule, the quadrature error applied to layer
-  potentials for the screen Laplace equation will be uniformly bounded
-  in $\Omega$.}}
-\label{fig:integrands}
-\end{wrapfigure}
 Nearly touching bodies is ubiquitous in self-assembly of amphiphilic

### 2020-11-12 NSF2020/Description/preliminarywork.tex
RJR preliminary trimmed significantly

@@
-\begin{figure}[!]
+\section{Preliminary work}
+\subsection{Estimating two-dimensional elastic moduli}
+The motivation for Specific Aims 1-3 stemmed from the successful demonstration of gradient driven
+self-assembly of amphiphilic particles into two-dimensional micelles,
+bilayer membranes, \cite{Fu2018_SIAM}, and recreation of the vesicles tank-treading phenomenon.
+
+Our preliminary work on membrane elasticity 
+is particulary encouraging because the effective bending, stretch, and tilt elastic moduli we calculated
+were in excellent agreement with the experimental values (Table \ref{tab:moduli}).
+The agreement is underscored by the fact we assigned reasonable physical values to 
+the main model parameters of HAP energy, rather than tuning parameters.
+
+\begin{table}[h!]
 \begin{center}
-\includegraphics[width=1\textwidth]{figures/PW_fig1A-D.pdf}
-\includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
+  \begin{tabular}{|l|p{0.16\textwidth}|l|l|p{0.2\textwidth}|p{0.18\textwidth}}
+    \hline
+          & simulation type & HAP value        & experimental value & reference\\
+    \hline \hline 
+    $\KB$ & {\footnotesize uniform load with clamped condition} & $11 \pm 2.5$ \kBT & 10 \kBT                  & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
+    \hline 
+    $\KA$ & {\footnotesize bilayer stretching}  & $34$ \kBT $^{-2}$ & 30--40 \kBT $^{-2}$              & \cite{Nagle17, Nagle17-2}\\
+    \hline 
+    $\KTH$ & {\footnotesize tilt Dirichlet condition} & $12$ \kBT \; nm$^{-2}$ & 10 \kBT $^{-2}$  &  \cite{KUZMIN2005, KoNa15} \\ \hline
+  \end{tabular}
 \end{center}
-\vspace{-0.3in}
-\caption{\label{fig:tanktreading}\footnotesize (A) A vesicle formed by
-  amphiphilic particles in shear flow, and the tank-treading motion
-  (B)--(D). The separation of particle pairs in (B) and (C) illustrate
-  inter-leaflet slip.  (E)--(G) Tank-treading reaches a steady state in
-  elliptical aspect ratio, major-axis angle, and circumference.}
-\end{figure}
-
-\section{Preliminary work}
-\subsection{Estimating two-dimensional elastic
-moduli}
-%\section{Preliminary Work on Two-dimensional Vesicle Hydrodynamics in Shear Flow\label{sec:preliminary_work}} 
-%\section{Preliminary work on elastic moduli}
-
-To derive a bending modulus, we first considered a planar bilayer subject to a uniform vertical load on the particle centers (Figure \ref{fig:bend}). 
-Using a clamped condition at one end, the restoring force in the free part of the bilayer opposes the load.
-For small deformations, it is possible to solve the bilayer loading in closed form, and 
-this analytical solution (red curve) basically overlaps the midplane of the particle based solution (Figure \ref{fig:bend}A).
-We thereby derived a bending modulus $\KB$ in the range 8.51--13.54 \kBT. Throughout the proposal, \kBT\; = 4.11$\times 10^{-21}$ J.
-Experimental measurements have accurately determined the bending modulus for several lipid types, with 
-typical values lying around 10 \kBT\; \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}.
-
-We also considered the stretching and tilt deformations \cite{Fu2018_SIAM}. 
-Stretching occurs whenever there is an excess monolayer area,
-and it is energetically costly since it exposes hydrocarbon tails to water.
-To measure an area modulus, we stretched a circular vesicle, modeling the cross-section 
-of a bilayer tube (Figure \ref{fig:bend}B \& C).
-This procedure gave a monolayer area modulus 
-34 $\pm$ 2 \kBT \;nm$^{-2}$. Manipulation experiments give a monolayer area modulus in the range 
-30--40 \kBT\; nm$^{-2}$ \cite{Nagle17, Nagle17-2}.
-
-Finally, we considered the tilt deformation by applying a fixed tilt angle boundary condition. 
-This boundary condition produces a tilt field that decays with the length scale $l = \sqrt{\KB/\KTH}$ 
-Fitting to this field, our particle based simulation gave $\lambda = 1.2$ nm, which matches
-the value $\KTH \approx 10$ \kBT \; nm$^{-2}$ reported in the literature \cite{KUZMIN2005, KoNa15}.
-
-Nevertheless, the characterization of material properties is incomplete. For one, the preliminary simulations involved relatively low particle numbers (20 to 30), and so we still need to
-perform convergence studies with large particle-number systems to arrive at conclusive results. Secondly, we have yet to establish a functional
-relationship between the model parameters and elastic moduli.
-Finally, to have relevance in physics and biology we must incorporate the remaining twist and saddle splay deformations.
-The following simulation outline shows how will achieve aims.
+\caption{\label{tab:moduli}Comparision of values elastic moduli from the experimental literature and values derived by HAP simulation.}
+\end{table}
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=1\textwidth]{figures/PW_fig1A-D.pdf}
+\includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
+\end{center}
+\vspace{-0.3in}
+\caption{\label{fig:tanktreading}\footnotesize (A) A vesicle formed by
+  amphiphilic particles in shear flow, and the tank-treading motion
+  (B)--(D). The separation of particle pairs in (B) and (C) illustrate
+  inter-leaflet slip.  (E)--(G) Tank-treading reaches a steady state in
+  elliptical aspect ratio, major-axis angle, and circumference.}
+\end{figure}
+
 %\begin{wrapfigure}[12]{r}{0.2\textwidth}

### 2020-11-13 NSF2020/Description/background.tex
removed double integrals
RJR

@@
 and numerical simulations to investigate the dynamic self-assembly of
-amphiphilic particles interacting with each other via hydrophobic forces
+amphiphilic particles interacting via hydrophobic forces
 in a solvent. Amphiphilic particles (such as lipid molecules) possess
@@
 the force between any two hydrophobic objects is altered by the presence
-of a third, hydrophobic or otherwise, object \cite{SilveraBatista1242477}.
+of a third object, hydrophobic or otherwise \cite{SilveraBatista1242477}.
 
@@
 the problem of energy barriers in membrane
-fusion~\cite{RyKlYaCo16,Chetal16}. By applying a squared gradient
-mathematical theory for hydrophobic attraction between planar
+fusion~\cite{RyKlYaCo16,Chetal16}. By applying a mathematical, squared-gradient
+theory for hydrophobic attraction between planar
 surfaces~\cite{Eriksson1989,Lum1999,Menshikov2017,Marcelja1977}, PI RR
@@
 %attraction is non-additive.
-The boundary of the region is the water-particle interface with outward
-pointing normal $\boldsymbol{\nu}$. Some parts of this interface are
+The boundary of the region is the union of water-particle interfaces with
+unit normal $\boldsymbol{\nu}$. Some parts of this interface are
 hydrophobic while others are hydrophilic. Hydrophobic interfaces disturb
@@
 
-To establish the effect of attraction, the water activity is not
-arbitrary, but rather is the unique solution of the screened Laplace
+To establish an attraction between interfaces, the water activity is not
+arbitrary, but rather is the solution of the screened Laplace
 equation boundary value problem 
@@
 The equations~\eqref{HAP} and~\eqref{SL} possess a number of the mathematical properties
-that capture the phenomenological behavior of hydrophobic attraction.
+that mirror the phenomenological characteristics of hydrophobic attraction.
 Specifically, solutions of~\eqref{SL} yield an attractive interaction between
@@
 domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}, yields a
-symmetric, rank-two tensor called the hydrophobic stress:
+symmetric, rank-two tensor called the hydrophobic stress (eq. 2.3 in \cite{Fu2018_SIAM}):
 \begin{align}
@@
   \label{forceandtorque}
-  \mathbf{F}_{\text{hydro},i} = \iint_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}}
+  \mathbf{F}_{\text{hydro},i} = \int_{\partial P_i} \boldsymbol{\sigma}_{\text{hydro}}
   \cdot \boldsymbol{\nu} \,\dif S,\quad
-  \mathbf{G}_{\text{hydro},i} = \iint_{\partial P_i} (\mathbf{x}-\mathbf{a}_i) \times
+  \mathbf{G}_{\text{hydro},i} = \int_{\partial P_i} (\mathbf{x}-\mathbf{a}_i) \times
   (\boldsymbol{\sigma}_{\text{hydro}} \cdot \boldsymbol{\nu}) \,\dif S,
@@
 that diverges whenever tubular neighborhoods of adjacent particles
-overlap, along with the excluded volume repulsions. The total potential,
+overlap. The total potential,
 force and torque are then
@@
 
-To supply viscous dissipation, we incorporate the mobility problem in
-Stokes flow for a rigid body suspension:
+To supply viscous dissipation, we incorporate the mobility problem
+flow for a rigid body suspension in Stokes flow:
 \begin{equation}
@@
 elongated lipid by elliptical particles with the hydrophobic label
-defined along the ellipse's axis. Under the hydrophobic force, and with
-an excluded volume, the Janus particles spontaneously merge and realign
+defined along the ellipse's axis. Under the hydrophobic force, with
+excluded volume, the Janus particles spontaneously merge and realign
 to form bilayers. This occurs only as a result of energy minimization
@@
 implicitly or explicitly, and define an elastic bending energy of the
-surface. Researchers have developed a number of numerical methods for
+surface. These vesicle studies built off of numerical methods for
 calculating energy minimizing steady equilibrium shapes of lipid bilayer
@@
 fluid velocity must be that of a rigid body motion at the particle
-surfaces. The HAP model also addresses the existence of multiple phases.
+surfaces. Finally, the HAP model directly addresses the existence of multiple phases.
 We can vary lipid length, spontaneous curvature, and bending rigidity by

### 2020-11-13 NSF2020/Description/specificaim3_ver2.tex
small edits

@@
 discretized, and artificial boundary conditions must be imposed. The
-artificial boundary conditions introduces additional error, and
+artificial boundary conditions introduce additional error, and
 discretizing the volume results in an excessively large linear system.
@@
 boundary surfaces are irregular. Alternatively, since we are solving
-constant-coefficient elliptic PDEs, the solution of the PDE can be
+constant-coefficient elliptic PDEs, the solution of the PDEs can be
 represented as layer potentials
@@
 quadrature methods for integrands that are nearly singular. These
-challenges are described in section~\ref{subsec:NumericalIssues}.
-However, numerical errors can still lead to unphysical contact between
-bodies. We propose two algorithms to avoid contact in
-Section~\ref{subsec:timeStepping}. Then, proposed work for
-well-conditioned BIE formulations of fluctuating hydrodynamics are
-described in Section~\ref{subsec:fluctuating}.
+challenges are described in \S\ref{subsec:NumericalIssues}. However,
+numerical errors can still lead to unphysical contact between bodies. We
+propose two algorithms to avoid contact in \S\ref{subsec:timeStepping}.
+Then, proposed work for well-conditioned BIE formulations of fluctuating
+hydrodynamics are described in \S\ref{subsec:fluctuating}.
 
@@
 ho2016cpam2, ho2016cpam1, minden2016, minden2017siammms}, but direct
-solvers often require a large amount of initial overhead, and this makes
-them less practical for problems with moving geometries. Alternatively,
-techniques in fast direct solvers can be used to develop efficient
-preconditioning strategies such as the inverse Fast Multipole Method
-(IFMM)~\cite{cou-pou-dar2017}. PI BQ used the IFMM to precondition
-Stokes equations in a porous media~\cite{qua-cou-dar2018}, and a suite
-of other preconditioners including sparse approximate
+solvers often require a large amount of computational overhead, and this
+makes them less practical for problems with moving geometries.
+Alternatively, techniques in fast direct solvers can be used to develop
+efficient preconditioning strategies such as the inverse Fast Multipole
+Method (IFMM)~\cite{cou-pou-dar2017}. PI BQ used the IFMM to
+precondition Stokes equations in a porous media~\cite{qua-cou-dar2018},
+and a suite of other preconditioners including sparse approximate
 inverses~\cite{che2000} and multigrid~\cite{hem-sch1981, sch1982} will
@@
 barycentric quadrature rule} that only requires a slight modification of
-the trapezoid rule~\cite{ioa-pap-per1991}. This method requires the
-layer potential satisfy Laplace or Stokes
-equations~\cite{bar-wu-vee2015, chi-moo-qua2020}. The PIs will extend
-this quadrature method to layer potentials for the screened Laplace
+the trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this
+method requires the layer potential to satisfy Laplace or Stokes
+equations~\cite{bar-wu-vee2015, chi-moo-qua2020}, but the PIs will extend
+the method to layer potentials for the screened Laplace
 equation. This will be done by recognizing that the fundamental solution

### 2020-11-13 NSF2020/Description/preliminarywork.tex
RJR
small edits
small edits to 4.3 and prelim work

@@
 \section{Preliminary work}
-\subsection{Estimating two-dimensional elastic moduli}
-The motivation for Specific Aims 1-3 stemmed from the successful demonstration of gradient driven
-self-assembly of amphiphilic particles into two-dimensional micelles,
-bilayer membranes, \cite{Fu2018_SIAM}, and recreation of the vesicles tank-treading phenomenon.
+\label{sec:preliminary_work}
+\subsection{Estimating two-dimensional elastic moduli} The motivation
+for Specific Aims 1-3 stemmed from the successful demonstration of
+gradient driven self-assembly of amphiphilic particles into
+two-dimensional micelles, bilayer membranes~\cite{Fu2018_SIAM}, and
+recreation of the vesicles tank-treading phenomenon.
 
-Our preliminary work on membrane elasticity 
-is particulary encouraging because the effective bending, stretch, and tilt elastic moduli we calculated
-were in excellent agreement with the experimental values (Table \ref{tab:moduli}).
-The agreement is underscored by the fact we assigned reasonable physical values to 
-the main model parameters of HAP energy, rather than tuning parameters.
+Our preliminary work on membrane elasticity is particulary encouraging
+because the effective bending, stretch, and tilt elastic moduli we
+calculated were in excellent agreement with the experimental values
+(Table~\ref{tab:moduli}).  The agreement is underscored by the fact we
+assigned reasonable physical values to the main model parameters of HAP
+energy, rather than tuning parameters.
 
@@
 \end{center}
-\caption{\label{tab:moduli}Comparision of values elastic moduli from the experimental literature and values derived by HAP simulation.}
+\caption{\label{tab:moduli} \footnotesize Comparision of values elastic
+  moduli from the experimental literature and values derived by HAP
+  simulation.} 
 \end{table}
@@
 \subsection{Two-dimensional vesicle hydrodynamics in shear flow} 
-%The motion of vesicles in shear flow is an important
-%problem in the applied mathematics because simulations can reveal mechanical
+%The motion of vesicles in shear flow is an important problem in the
+%applied mathematics because simulations can reveal mechanical
 %properties of membranes and lead to an enhanced understanding of

### 2020-11-13 NSF2020/Description/specificaim3_ver2.tex
small edits to 4.3 and prelim work

@@
 $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ are
-plotted. The quadrature of the trapezoid rule is the sum of the Fourier
-amplitudes not captured at the resolution.
+plotted. The quadrature error of the trapezoid rule is the sum of the
+unresolved Fourier modes.
 
@@
 and torque of the system which is computationally cheap and physically
-zero. The PIs' experience is that error estimates based on physical
+zero. PI BQ's experience is that error estimates based on physical
 constraints such as force- and torque-free conditions appropriately
@@
 regularization of the covariance matrix leads to a drastic loss of
-accuracy in numerical fluctuation-dissipation balance. However, they
-only one regularization strategy was considered, and as PI BQ has
-shown in previous work, the regularization choice significantly affects
-the resulting physics~\cite{ong-chr-qua2017}. Therefore, different
+accuracy in numerical fluctuation-dissipation balance. However, only one
+regularization strategy was considered, and as PI BQ has shown in
+previous work, the regularization choice significantly affects the
+resulting physics~\cite{ong-chr-qua2017}. Therefore, different
 regularization strategies will be investigated with the goal of

### 2020-11-13 NSF2020/Description/background.tex
RJR

@@
 that mirror the phenomenological characteristics of hydrophobic attraction.
-Specifically, solutions of~\eqref{SL} yield an attractive interaction between
-hydrophobic bodies separated by water~\cite{Eriksson1989}.
+Specifically, solutions of~\eqref{SL} yield an attractive force between
+hydrophobic bodies separated by water, and this attraction 
+decreases exponentially with the distance of separation~\cite{Eriksson1989}.
 Using boundary layer analysis, the HAP converges to a surface energy in the zero-decay length

### 2020-11-13 NSF2020/Description/preliminarywork.tex
RJR getting there one prelim work

@@
 \label{sec:preliminary_work}
-\subsection{Estimating two-dimensional elastic moduli} The motivation
-for Specific Aims 1-3 stemmed from the successful demonstration of
-gradient driven self-assembly of amphiphilic particles into
-two-dimensional micelles, bilayer membranes~\cite{Fu2018_SIAM}, and
-recreation of the vesicles tank-treading phenomenon.
+The HAP project was initiated in 2017 by PIs RR and YNY.
+The lead author on our first paper (\cite{Fu2018_SIAM}) was Szu-Pei Fu,
+who was PI YNS's PhD student and is currently a postdoc with PI RR.
+The collaboration involved theoretical work and simulation. The theoretical
+work included model development, proving the first variation formula
+\eqref{stress} and force-free law, and an energy-based  uniqueness
+theorem for the exterior domain problem \eqref{SL}.
+Coauthors Andreas Kl\"ockner (Computer Science, UIUC, NSF CAREER \#1654756)
+and his PhD student Matt Wala provided their Quadrature by Expansion, or QBX
+algorithm and Fu ran simulations on NJIT clusters.
 
-Our preliminary work on membrane elasticity is particulary encouraging
-because the effective bending, stretch, and tilt elastic moduli we
-calculated were in excellent agreement with the experimental values
-(Table~\ref{tab:moduli}).  The agreement is underscored by the fact we
-assigned reasonable physical values to the main model parameters of HAP
-energy, rather than tuning parameters.
+The simulation results were encouraging. The small particle-number
+simulations successfully demonstrated gradient-driven self-assembly of amphiphilic
+particles into two-dimensional micelles, bilayer membranes. The model parameters
+where the decay length $\rho$, interfacial tension $\gamma$, particle geometry, and
+repulsion strength. The particle diamaters were set equal to monolayer thickness, 2.0 nm \cite{Boal}, and we chose a repulsion strength that gave adequate interparticle spacing.
+For the decay length, we used $\rho = 2.5$ nm based on measurements of hydrophobic
+attraction between surfactant-coated \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80}.
+For the interfacial tension, we used $\gamma = 4$ pN nm$^{-1}$
+based on measurements for single-component bilayer lipid membranes
+\cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson2016}.
 
-\begin{table}[h!]
+\begin{wraptable}[10]{r}{0.55\textwidth}
 \begin{center}
-  \begin{tabular}{|l|p{0.16\textwidth}|l|l|p{0.2\textwidth}|p{0.18\textwidth}}
+  \begin{tabular}{|l|r|r|p{0.1\textwidth}|}
     \hline
-          & simulation type & HAP value        & experimental value & reference\\
-    \hline \hline 
-    $\KB$ & {\footnotesize uniform load with clamped condition} & $11 \pm 2.5$ \kBT & 10 \kBT                  & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
+          & HAP         & exper. value & ref.\\
     \hline 
-    $\KA$ & {\footnotesize bilayer stretching}  & $34$ \kBT $^{-2}$ & 30--40 \kBT $^{-2}$              & \cite{Nagle17, Nagle17-2}\\
+    $\KB$ & $11 \pm 2.5$ \kBT & 10 \kBT                  & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
     \hline 
-    $\KTH$ & {\footnotesize tilt Dirichlet condition} & $12$ \kBT \; nm$^{-2}$ & 10 \kBT $^{-2}$  &  \cite{KUZMIN2005, KoNa15} \\ \hline
+    $\KA$  & $34$ \kBT nm$^{-2}$ & 30--40 \kBT nm$^{-2}$              & \cite{Nagle17, Nagle17-2}\\
+    \hline 
+    $\KTH$  & $12$ \kBT \; nm$^{-2}$ & 10 \kBT nm$^{-2}$  &  \cite{KUZMIN2005, KoNa15} \\ \hline
   \end{tabular}
@@
   simulation.} 
-\end{table}
+\end{wraptable}
+We performed three types of simulations. The first measured bending by loading
+a planar bilayer. The second used a harmonic bond to dilate a circular bilayer.
+The third measured tilt using a decay equation from  \cite{KUZMIN2005}.
+These simulations isolated the deformations of \eqref{ansatz3}, enabling
+us to read off elastic moduli from simulation data. 
+The results agreed remarkably well with the values reported in the experimental literature, 
+Table~\ref{tab:moduli}. The agreement is underscored by the fact
+that the two, main HAP parameters $\gamma$ and $\rho$ were assigned
+physical values from the outset, rather than being tuned.
 

### 2020-11-13 NSF2020/Description/broaderimpacts.tex
broader impacts edited

@@
 supported summer researchers will gain valuable first-hand
-interdisciplinary experience in mathematical fluid modeling and
-computation. We will incorporate research into teaching, especially in
-differential equation and programming courses. PI YNY will work on
-simple modeling of self-assembly problems with both undergraduate and
-high school students from Newark Science Park High School. PI YNY has a
-track record of working with local high school students for their
-research projects before they apply for colleges. PI BQ will work with
-undergraduate and high school students through the Undergraduate
-Research Opportunity Program and Young Scholar's Program as he has done
-in the past.
+interdisciplinary experience in mathematical modeling and computation.
+We will incorporate research into teaching, especially in differential
+equation and programming courses. PI YNY will work on simple modeling of
+self-assembly problems with both undergraduate and high school students
+from Newark Science Park High School. PI YNY has a track record of
+working with local high school students for their research projects
+before they apply for colleges. PI BQ will work with undergraduate and
+high school students through the Undergraduate Research Opportunity
+Program and Young Scholar's Program as he has done in the past.
 
@@
 
-The PIs will capitalize on the synergy between both FSU's doctoral program in Scientific Computing and NJIT's doctoral programs
-in Mathematical Sciences and Fordham's undergraduate focus in the
-Department of Mathematics. Promising, young undergraduate scientists
-from the Bronx community will find a natural pipeline into graduate
-studies by working directly or indirectly on this project. On the
-graduate-level education, PI YNY expects to train and support a PhD
-student for two more years. PI BQ will advise a postdoctoral fellow for
-two years. The PIs will foster vertical integration between the senior
-personnel, their collaborators, postdocs, doctoral, and Bachelor
-students, enhancing the learning environment.
+The PIs will capitalize on the synergy between both FSU's doctoral
+program in Scientific Computing, NJIT's doctoral program in Mathematical
+Sciences, and Fordham's undergraduate focus in the Department of
+Mathematics. Promising, young undergraduate scientists from the Bronx
+community will find a natural pipeline into graduate studies by working
+directly or indirectly on this project. At the graduate-level, PI YNY
+expects to train and support a PhD student for two more years. PI BQ
+will advise a postdoctoral fellow for two years. The PIs will foster
+vertical integration between the senior personnel, their collaborators,
+postdocs, doctoral, and Bachelor students, enhancing the learning
+environment.
 
@@
 number simulations in three dimensions. Results from these computations
-will be used to compare collective amphiphilic against experiments, and
-study the optimal design of three-dimensional functional materials.
+will be used to compare collective amphiphilic against experiments and
+to study the optimal design of three-dimensional functional materials.

### 2020-11-13 NSF2020/Description/preliminarywork.tex
Update preliminarywork.tex

@@
 where the decay length $\rho$, interfacial tension $\gamma$, particle geometry, and
-repulsion strength. The particle diamaters were set equal to monolayer thickness, 2.0 nm \cite{Boal}, and we chose a repulsion strength that gave adequate interparticle spacing.
-For the decay length, we used $\rho = 2.5$ nm based on measurements of hydrophobic
+repulsion strength. The particle diamaters were set equal to monolayer thickness, 
+2.0 nm \cite{Boal}, and we chose a repulsion strength that gave adequate interparticle 
+spacing. For the decay length, we used $\rho = 2.5$ nm based on measurements of hydrophobic
 attraction between surfactant-coated \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80}.
@@
     \hline 
-    $\KA$  & $34$ \kBT nm$^{-2}$ & 30--40 \kBT nm$^{-2}$              & \cite{Nagle17, Nagle17-2}\\
+    $\KA$ & $34$ \kBT \; nm$^{-2}$  & 30--40 \kBT nm$^{-2}$ & \cite{Nagle17, Nagle17-2}\\
     \hline 
@@
 These simulations isolated the deformations of \eqref{ansatz3}, enabling
-us to read off elastic moduli from simulation data. 
-The results agreed remarkably well with the values reported in the experimental literature, 
+us to read off elastic moduli from simulation data. The results agreed remarkably 
+well with the values reported in the experimental literature, 
 Table~\ref{tab:moduli}. The agreement is underscored by the fact
@@
 
-\subsection{Two-dimensional vesicle hydrodynamics in shear flow} 
+The PIs BQ, RR, YNY and Peter Fu initiated a collaboration in summer, 2020. 
+The present proposal is the outgrowth of this collaboration. We have created
+a compact numerical solver and included background flow in the simulations. 
+The background flow enters by replacing the third equation in \eqref{eq:stokes} 
+with the condition $(\mathbf{u} -\mathbf{u}_{\infty})(\mathbf{x}) 
+\to \mathbf{0}$ as $|\mathbf{x}| \to \infty$. To incorporate the far-field flow, 
+and using the representation 
+\begin{align}
+\label{PowerMiranda}
+  {\bf u} = {\bf u}_{\infty} + K\boldsymbol{\eta} + 
+    \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + 
+                 R(\cdot, {\bf a}_i) {\bf G}_i.
+\end{align}
+The symbols $S$ and $R$ are stokeslets and rotlets supported at the respective
+particle centers \cite{leal_2007} and $K\boldsymbol{eta}$ is a layer potential for the
+unknown density function $\boldsymbol{\eta}.$ The
+representation~\eqref{PowerMiranda} automatically satisfies all
+equations, with the exception of the rigid motion conditions. The rigid
+motion conditions follow by requiring the viscous stress vanishes across
+the particle boundaries.
+
+\begin{wrapfigure}[13]{l}{0.30\textwidth}
+\centerline{\includegraphics[width=0.30\textwidth]{figures/BIError.pdf}}
+  \vspace{-8pt}
+\caption{
+\label{fig:bierror}  
+\footnotesize The false color map shows how numerical quadrature of
+  layer potentials loses accuracy near the particle boundaries.  The
+  color bar is for $\log_{10}.$}
+\end{wrapfigure}
+\textbf{Novel reciprocal identities.} 
+The force and torque formulas~\eqref{forceandtorque} require the
+hydrophobic stress along the particle boundaries. Unfortunately,
+standard quadrature formulas to estimate $\nabla u$ on the particle
+boundaries introduces large amounts of quadrature error
+(Figure~\ref{fig:bierror}). Therefore, it is useful to devise reciprocal
+identities for the force and torque on body $i$ that does not
+require integration along body $i$. One identity, that we have proved,
+is
+\begin{align}
+    \label{eq:reciprocal}
+{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
+{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf
+  x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} +
+  \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, 
+\end{align}
+for $i=1,\ldots,N$. Here, $u_i$ is the solution of the screened Laplace
+equation when only the contribution from particle $i$ is considered and
+$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i
+\cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$.
+Equation~\eqref{eq:reciprocal} does not require knowledge of $\nabla u$
+on the particle boundary, and this is enormously beneficial for
+calculating force and torque.
+
+\subsubsection{Two-dimensional vesicles in shear flow}
+We will compare the behavior of our particle-based vesicles in Stokes
+flow to well-established models that enforce area incompressibility and
+volume conservation in vesicle membrane
+dynamics~\cite{torres-sanchez_millan_arroyo_2019,
+mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}. Our
+preliminary results show that the particle-based bilayers have the same
+large area modulus as real lipid bilayer membranes, so we expect
+realistic results from our flow simulations. Under moderate shear rates,
+the vesicle elongates and takes on the tank-treading elliptical shape.
+We can directly check for area compressibility conservation properties
+from the particle simulation by tracking the change in area density of
+the midplane as a function of shear flow rate, along with evaluating the
+tangential divergence of the velocity.
+
+Bilayer membranes have a small permeability to water
+\cite{323e9a2f0c58487ea82518d7a1f96485}, and modelers often assume a
+vesicle membrane that conserves volume. In our particle-based approach,
+water motion across the bilayer is limited by the size of the gaps
+between the particles, which is an artifact of coarse-graining.  Making
+these gaps smaller comes at the expense of numerical accuracy, and we
+will assess if there is a reasonable trade-off between approximate
+volume conservation and simulation complexity.
+
+Finally, the particle-based vesicle bilayers have two distinct leaflets
+consisting of the particles in contact with the vesicle interior, and
+those in contact with the surrounding fluid. Since there is a nonzero
+separation between these layers, an important effect we observe is that
+the leaflets slide against one another under shear flow.  This implies
+that part of the viscous dissipation in the aqueous phase is enhanced by
+intermonolayer friction~\cite{SHKULIPA2005823, ShkulipaThesis}.
+Intermonolayer slip enters zero-thickness membrane models as a velocity
+jump boundary condition and leads to multiple solution
+states~\cite{schwalbe_vlahovska_miksis_2010}.  In the present proposal,
+intermonolayer slip is an artifact of monolayer independence  and we can
+control for slip as a function of shear rate, vesicle diameter, and
+particle geometry.
+
+%\subsection{Two-dimensional vesicle hydrodynamics in shear flow} 
 %The motion of vesicles in shear flow is an important problem in the
@@
 %
-\begin{wrapfigure}[10]{r}{0.2\textwidth}
-\centerline{\includegraphics[width=0.2\textwidth]{figures/PW_fig5.pdf}}
-\vspace{-8pt}
-\caption{\label{fig:rupture} \footnotesize Rupture of tank-treading vesicle under strong shear flow.}
-\end{wrapfigure}
+%\begin{wrapfigure}[10]{r}{0.2\textwidth}
+%\centerline{\includegraphics[width=0.2\textwidth]{figures/PW_fig5.pdf}}
+%\vspace{-8pt}
+%\caption{\label{fig:rupture} \footnotesize Rupture of tank-treading vesicle under strong shear flow.}
+%\end{wrapfigure}
 %
-To implement a vesicle in shear flow in the context of hydrophobic
-potentials and mobility problem, we consider a shear flow in the
-far-field $\mathbf{u}_{\infty} = Uy\mathbf{i}_x$ in the direction of the
-$x$-axis (Figure \ref{fig:tanktreading}A). As illustrated in Figure
-\ref{fig:tanktreading}, the particle based approach supports
-inter-leaflet slip, and this can be used to determine inter-leaflet and
-in-plane shear viscosities. 
+%To implement a vesicle in shear flow in the context of hydrophobic
+%potentials and mobility problem, we consider a shear flow in the
+%far-field $\mathbf{u}_{\infty} = Uy\mathbf{i}_x$ in the direction of the
+%$x$-axis (Figure \ref{fig:tanktreading}A). As illustrated in Figure
+%\ref{fig:tanktreading}, the particle based approach supports
+%inter-leaflet slip, and this can be used to determine inter-leaflet and
+%in-plane shear viscosities. 
 %
@@
 %\end{wrapfigure}
-The HAP simulations show vesicle tank-treading. Under the external shear flow, the initially circular 
-vesicle rotates in the clockwise direction. As the rate of rotation increases, the vesicle approaches
-a steadily tank-treading ellipse. In Figure \ref{fig:tanktreading}B-D, the solid curves are ellipses fit to the particle centers
-and midplane respectively. In the non-dimensionalized system, the particles have diameter 2, on the order of $\rho,$ 
-and the vesicle diameter is about 14. 
+%The HAP simulations show vesicle tank-treading. Under the external shear flow, the initially circular 
+%vesicle rotates in the clockwise direction. As the rate of rotation increases, the vesicle approaches
+%a steadily tank-treading ellipse. In Figure \ref{fig:tanktreading}B-D, the solid curves are ellipses fit to the particle centers
+%and midplane respectively. In the non-dimensionalized system, the particles have diameter 2, on the order of $\rho,$ 
+%and the vesicle diameter is about 14. 
 %\todo[inline]{missing units. nm?}
-Figure~\ref{fig:tanktreading}E shows the aspect ratio of the major to minor axes reaching an equilibrium value in the 
-red and blue curves, yet oscillating in the high-shear rate (yellow) curve.
-The tank-treading vesicle elongates and becomes more horizontal 
-with an increase in flow rate or 
-with a decrease in stiffness (effected by decreasing $\rho = 4$ to $\rho = 2$).
+%Figure~\ref{fig:tanktreading}E shows the aspect ratio of the major to minor axes reaching an equilibrium value in the 
+%red and blue curves, yet oscillating in the high-shear rate (yellow) curve.
+%The tank-treading vesicle elongates and becomes more horizontal 
+%with an increase in flow rate or 
+%with a decrease in stiffness (effected by decreasing $\rho = 4$ to $\rho = 2$).
 
-For large shear flow rates, there is an increase in arc length. Here arc
-length refers to the the mid-plane circumference. Thus, some of the
-external force is going into stretching the vesicle---the other part is
-going into bending and viscous dissipation. From our experiments, we
-find that the vesicle ruptures once stretching exceeds about 5 \% (see
-Figure \ref{fig:rupture}). Finally, movies of the tank-treading motion
-show a slip velocity between the outer and inner leaflets Figure
-\ref{fig:tanktreading}G. We have illustrated this by tracking the
-distance between two reference particles in the inner and outer leaflet
-(Figure \ref{fig:tanktreading}B \& D, green and blue particles). With
-moderate shear rates or greater adhesion, the particle pair moves in
-tandem (in Figure \ref{fig:tanktreading}H, blue and red curves, their
-distance is more or less constant). For a large shear rate, the
-particle separates as the two leaflets slide against one another.
+%For large shear flow rates, there is an increase in arc length. Here arc
+%length refers to the the mid-plane circumference. Thus, some of the
+%external force is going into stretching the vesicle---the other part is
+%going into bending and viscous dissipation. From our experiments, we
+%find that the vesicle ruptures once stretching exceeds about 5 \% (see
+%Figure \ref{fig:rupture}). Finally, movies of the tank-treading motion
+%show a slip velocity between the outer and inner leaflets Figure
+%\ref{fig:tanktreading}G. We have illustrated this by tracking the
+%distance between two reference particles in the inner and outer leaflet
+%(Figure \ref{fig:tanktreading}B \& D, green and blue particles). With
+%moderate shear rates or greater adhesion, the particle pair moves in
+%tandem (in Figure \ref{fig:tanktreading}H, blue and red curves, their
+%distance is more or less constant). For a large shear rate, the
+%particle separates as the two leaflets slide against one another.
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=1\textwidth]{figures/PW_fig1A-D.pdf}
-\includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
-\end{center}
-\vspace{-0.3in}
-\caption{\label{fig:tanktreading}\footnotesize (A) A vesicle formed by
-  amphiphilic particles in shear flow, and the tank-treading motion
-  (B)--(D). The separation of particle pairs in (B) and (C) illustrate
-  inter-leaflet slip.  (E)--(G) Tank-treading reaches a steady state in
-  elliptical aspect ratio, major-axis angle, and circumference.}
-\end{figure}
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=1\textwidth]{figures/PW_fig1A-D.pdf}
+%\includegraphics[width=1\textwidth]{figures/PW_fig1E-H.pdf}
+%\end{center}
+%\vspace{-0.3in}
+%\caption{\label{fig:tanktreading}\footnotesize (A) A vesicle formed by
+%  amphiphilic particles in shear flow, and the tank-treading motion
+%  (B)--(D). The separation of particle pairs in (B) and (C) illustrate
+%  inter-leaflet slip.  (E)--(G) Tank-treading reaches a steady state in
+%  elliptical aspect ratio, major-axis angle, and circumference.}
+%\end{figure}
 

### 2020-11-13 NSF2020/Description/newspecificaim2.tex
yny addition

--- 2020-11-13 NSF2020/Description/specificaim3_ver2.tex
@@
 
-\subsection{Specific Aim 3: Efficient high-order numerical methods for
+\subsection{Specific Aim 2: Efficient high-order numerical methods for
 large-scale simulations}
-\label{subsec:specific_aim_3}
+\label{subsec:specific_aim_2}
+%\begin{figure}[h]
+\begin{wrapfigure}[]{r}{0.60\textwidth}
+  \centering{\includegraphics[width=0.6\textwidth]{Figures/domain.pdf}}
+    \caption{\label{fig:flow_map} \todo[inline]{Missing caption}}
+\end{wrapfigure}
+%\end{figure}
 % ----------------------------------------------------------------------
+Over the past decade, there has been an explosion of interest in
+small-scale processes that utilize capillary forces, van der Waals
+interactions, and thermal noise~\cite{Zhang2017}, to coordinate movement
+and bind nano-legos in a solvent \cite{Pandey2011, Leong2007, Reynolds2019,
+Dasgupta2017, Siontorou2017}. Additionally, hydrodynamic interactions are central for complex
+microscopic three-dimensional structures to fabricate~\cite{Cho2010}.
+%
+In Specific Aim 2, we propose to develop efficient high-order numerical methods to simulate dynamic
+assembly of particles under HAP potential in a viscous solvent. 
+%
+%
+%hydrodynamics effects by em
+%particles in a solvent. 
+%
+% Results from these proposed numerical simulations will be useful to 
+% Finally, coarse-grained and molecular
+%dynamics theories include water either explicitly or implicitly in their
+%models. 
+%
+%The immediate goal of the present proposal is to simulate
+%vesicle bilayers in external flows, where the bilayers are represented
+%by a self-assembled collection of rigid particles.
+%
+As described in~\eqref{eq:stokes} and
+illustrated in Figure~\ref{fig:flow_map}, the solvent phase is modeled
+by the Stokes equations for an incompressible viscous fluid, and these
+equations are coupled to the screened-Laplace equation~\eqref{SL}
+through viscous and hydrophobic stress balance. 
+Hydrodynamic effects can
+not be ignored since the rates of biological functions like fusion,
+fission, and pore dynamics rely on viscous
+dissipation~\cite{RYHAM20112929}. 
+%While hydrophobic attraction causes the particles to self-assemble indepedently of the dissipation mechanism, the trajectories and
+%equilibrium configurations depend on the fact that the particles travel through a viscous environment.
+
 The HAP model requires solving exterior Dirichlet problems for the
@@
 equation~\eqref{eq:LP} as $\mathbf{x}\rightarrow \mathbf{x}_0$, a BIE
-for the density function is formed. Numerical methods to solve BIEs have
+for the density function is formed.
+
+Numerical methods to solve BIEs have
 several advantages over their PDE-based counterpart: by construction,
@@
 
-\begin{wrapfigure}[21]{r}{2.5in}
-%\vspace*{+15pt}
-\centerline{\includegraphics[width=2.5in]{figures/integrands}}
-\vspace*{-13pt}
-  \caption{{\footnotesize The Fourier modes of
-  $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
-  $|\mathbf{x_0}| = 0.99$ and $\mathbf{y} \in \partial\Omega$, and
-  $\Omega$ is the unit circle. The trapezoid rule applied to the red
-  integrand has large amounts of error, but the trapezoid rule is much
-  more accurate when applied to the blue integrand. Since the difference
-  between the red and blue curves can be accurately computed with the
-  barycentric quadrature rule, the quadrature error applied to layer
-  potentials for the screen Laplace equation will be uniformly bounded
-  in $\Omega$.}}
-\label{fig:integrands}
-\end{wrapfigure}
 Significant challenges to solve BIEs include solving dense linear
@@
 
+%
+\begin{wrapfigure}[21]{r}{2.5in}
+%\vspace*{+15pt}
+\centerline{\includegraphics[width=2.5in]{figures/integrands}}
+\vspace*{-13pt}
+  \caption{{\footnotesize The Fourier modes of
+  $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
+  $|\mathbf{x_0}| = 0.99$ and $\mathbf{y} \in \partial\Omega$, and
+  $\Omega$ is the unit circle. The trapezoid rule applied to the red
+  integrand has large amounts of error, but the trapezoid rule is much
+  more accurate when applied to the blue integrand. Since the difference
+  between the red and blue curves can be accurately computed with the
+  barycentric quadrature rule, the quadrature error applied to layer
+  potentials for the screen Laplace equation will be uniformly bounded
+  in $\Omega$.}}
+\label{fig:integrands}
+\end{wrapfigure}
 Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
@@
 
+%
+\begin{wrapfigure}[13]{r}{0.30\textwidth}
+\centerline{\includegraphics[width=0.30\textwidth]{figures/BIError.pdf}}
+  \vspace{-8pt}
+\caption{
+\label{fig:bierror}  
+\footnotesize The false color map shows how numerical quadrature of
+  layer potentials loses accuracy near the particle boundaries.  The
+  color bar is for $\log_{10}.$}
+\end{wrapfigure}
+%
 Our previous work avoids contact by including a Leonard-Jones body
@@
 that the configuration is non-overlapping.
+
+%-------------------------------------------------------------------------------
+\subsubsection{Novel reciprocal identities}
+The force and torque formulas~\eqref{forceandtorque} require the
+hydrophobic stress along the particle boundaries. Unfortunately,
+standard quadrature formulas to estimate $\nabla u$ on the particle
+boundaries introduces large amounts of quadrature error
+(Figure~\ref{fig:bierror}). Therefore, it is useful to devise reciprocal
+identities for the force and torque on body $i$ that does not
+require integration along body $i$. One identity, that we have proved,
+is
+\begin{align}
+    \label{eq:reciprocal}
+{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
+{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf
+  x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} +
+  \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, 
+\end{align}
+for $i=1,\ldots,N$. Here, $u_i$ is the solution of the screened Laplace
+equation when only the contribution from particle $i$ is considered and
+$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i
+\cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$.
+Equation~\eqref{eq:reciprocal} does not require knowledge of $\nabla u$
+on the particle boundary, and this is enormously beneficial for
+calculating force and torque.
 

### 2020-11-13 NSF2020/Description/newspecificaim3.tex
yny addition

--- 2020-11-12 NSF2020/Description/specificaim2_ver2.tex
@@
-\subsection{Specific Aim 2: Hydrodynamics}
-\label{subsec:specific_aim_2}
-In Specific Aim 2, we include hydrodynamics effects by embedding the
-particles in a solvent.  As described in~\eqref{eq:stokes} and
-illustrated in Figure~\ref{fig:flow_map}, the solvent phase is modeled
-by the Stokes equations for an incompressible viscous fluid, and these
-equations are coupled to the screened-Laplace equation~\eqref{SL}
-through viscous and hydrophobic stress balance. Hydrodynamic effects can
-not be ignored since the rates of biological functions like fusion,
-fission, and pore dynamics rely on viscous
-dissipation~\cite{RYHAM20112929}. 
-%While hydrophobic attraction causes the particles to self-assemble indepedently of the dissipation mechanism, the trajectories and
-%equilibrium configurations depend on the fact that the particles travel through a viscous environment. 
-Additionally, hydrodynamic interactions are central for complex
-microscopic three-dimensional structures to fabricate~\cite{Cho2010}.
-Over the past decade, there has been an explosion of interest in
-small-scale processes that utilize capillary forces, van der Waals
-interactions, and thermal noise~\cite{Zhang2017}, to coordinate movement
-and bind material subunits~\cite{Pandey2011, Leong2007, Reynolds2019,
-Dasgupta2017, Siontorou2017}. Finally, coarse-grained and molecular
-dynamics theories include water either explicitly or implicitly in their
-models. The immediate goal of the present proposal is to simulate
-vesicle bilayers in external flows, where the bilayers are represented
-by a self-assembled collection of rigid particles.
-
-%\begin{figure}[h]
-\begin{wrapfigure}[]{r}{0.60\textwidth}
-  \centering{\includegraphics[width=0.6\textwidth]{Figures/domain.pdf}}
-    \caption{\label{fig:flow_map} \todo[inline]{Missing caption}}
-\end{wrapfigure}
-%\end{figure}
-
-%We must solve the system 
-%\setcounter{midequation}{\theequation}
-%\addtocounter{midequation}{2}
-%\begin{minipage}[t]{0.44\textwidth}
-%\begin{subequations}
-%\begin{alignat}{2}
-%\label{St1} -& \mu \Delta {\bf u} + \nabla p = {\bf 0}, \\
-%\label{St2}  & \nabla \cdot {\bf u} = 0,                &&   \text{in } \Omega\\
-%\label{St3}  & {\bf u }({\bf x}) = {\bf v}_i + {\bf w_i}\times {\bf x}, \;  && \text{for } {\bf x} \in \partial P_i\\
-%\label{St4}  & ({\bf u } - {\bf u}_{\infty})({\bf x}) \to {\bf 0} && \text{as } {\bf x} \to \infty\\
-%\notag \\
-%\tag{\themidequation}
-%\label{HSB1}  & \int_{\partial P_i} \boldsymbol{\sigma} \boldsymbol{\nu} \,\dif S + {\bf F}_{i} = {\bf 0}\span \span
-%\end{alignat}
-%\end{subequations}
-%\end{minipage}
-%\addtocounter{equation}{1}
-%\setcounter{midequation}{\theequation}
-%\addtocounter{midequation}{2}
-%\begin{subequations}
-%\begin{minipage}[t]{0.5\textwidth}
-%\begin{alignat}{2}
-%\label{SL1}  - & \rho^2 \Delta u +u = 0, && \text{in } \Omega\\
-%\label{SL2}   & u({\bf x}) = f_i({\bf x}),\quad  && \text{for } {\bf x} \in \partial P_i\\
-%\label{SL3} &  u({\bf x}) \to 0 && \text{as } {\bf x} \to \infty \\
-%\notag \\
-%\notag \\
-%\tag{\themidequation}
-%\label{HSB2}   & \int_{\partial P_i} {\bf x} \times \boldsymbol{\sigma} \boldsymbol{\nu} \,\dif S + {\bf G}_{i} = {\bf 0} \span \span\\
-%\notag
-%\end{alignat}
-%\end{minipage} 
-%\end{subequations}
-%\noindent for $i = 1,\dots, N$.
+\subsection{Specific Aim 3: Dynamics of self-assembly by HAP under an external flow/field}
+\label{subsec:specific_aim_3}
 
@@
 
+%\begin{wrapfigure}[13]{r}{0.30\textwidth}
+%\centerline{\includegraphics[width=0.30\textwidth]{figures/BIError.pdf}}
+%  \vspace{-8pt}
+%\caption{
+%\label{fig:bierror}  
+%\footnotesize The false color map shows how numerical quadrature of
+%  layer potentials loses accuracy near the particle boundaries.  The
+%  color bar is for $\log_{10}.$}
+%\end{wrapfigure}
+
 We will compare the behavior of our particle-based vesicles in Stokes
@@
 
-\begin{wrapfigure}[13]{r}{0.30\textwidth}
-\centerline{\includegraphics[width=0.30\textwidth]{figures/BIError.pdf}}
-  \vspace{-8pt}
-\caption{
-\label{fig:bierror}  
-\footnotesize The false color map shows how numerical quadrature of
-  layer potentials loses accuracy near the particle boundaries.  The
-  color bar is for $\log_{10}.$}
-\end{wrapfigure}
-
 Finally, the particle-based vesicle bilayers have two distinct leaflets
@@
 
-\subsubsection{Novel reciprocal identities}
-The force and torque formulas~\eqref{forceandtorque} require the
-hydrophobic stress along the particle boundaries. Unfortunately,
-standard quadrature formulas to estimate $\nabla u$ on the particle
-boundaries introduces large amounts of quadrature error
-(Figure~\ref{fig:bierror}). Therefore, it is useful to devise reciprocal
-identities for the force and torque on body $i$ that does not
-require integration along body $i$. One identity, that we have proved,
-is
-\begin{align}
-    \label{eq:reciprocal}
-{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
-{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf
-  x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} +
-  \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, 
-\end{align}
-for $i=1,\ldots,N$. Here, $u_i$ is the solution of the screened Laplace
-equation when only the contribution from particle $i$ is considered and
-$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i
-\cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$.
-Equation~\eqref{eq:reciprocal} does not require knowledge of $\nabla u$
-on the particle boundary, and this is enormously beneficial for
-calculating force and torque.
+\subsubsection{Effects of electric fields on the dynamic self-assembly}

### 2020-11-13 NSF2020/Description/background.tex

@@
 hydrophobic attraction potential (HAP) \cite{Fu2018_SIAM} that is based
-on the physical origin of hydrophobicity.  This model addresses the
-major shortcomings of molecular dynamics (MD) and continuum approaches.
-Based on preliminary results (\S\ref{sec:preliminary_work}) the PIs
-propose to extend this HAP model to offer an alternative modeling
-methodology that leads to new mathematical ideas, and is both physically
-accurate and computationally practical.
+on the physical origin of hydrophobicity. This model addresses the major
+shortcomings of molecular dynamics (MD) and continuum approaches. Based
+on preliminary results (\S\ref{sec:preliminary_work}) the PIs propose to
+extend this HAP model to offer an alternative modeling methodology that
+leads to new mathematical ideas, and is both physically accurate and
+computationally practical.
 %
@@
 %attraction is non-additive.
-The boundary of the region is the union of water-particle interfaces with
-unit normal $\boldsymbol{\nu}$. Some parts of this interface are
+The boundary of the region is the union of water-particle interfaces
+with unit normal $\boldsymbol{\nu}$. Some parts of this interface are
 hydrophobic while others are hydrophilic. Hydrophobic interfaces disturb
 the hydrogen bond structure of water~\cite{Luzar1987, Jonsson2006,
-Varilly2011}. This disturbance comes with an energetic penalty that is
-proportional to interfacial area. There is an additional decay length,
-due to rapid fluctuation in the hydrogen bond network, describing how
-far the restructuring extends into bulk water.
+Varilly2011} and this disturbance comes with an energetic penalty that
+is proportional to interfacial area. There is an additional decay
+length, due to rapid fluctuation in the hydrogen bond network,
+describing how far the restructuring extends into bulk water.
 
@@
   u = f,  \mbox{ } \mathbf{x} \in \partial \Omega, \qquad 
-  u(\mathbf{x}) \to 0 \mbox{ as } |\mathbf{x}| \to \infty.
+  u(\mathbf{x}) \to 0, \mbox{ as } |\mathbf{x}| \to \infty.
 \end{equation}
@@
 \end{equation}
-thereby avoiding calculating a volumetric integral.
+thereby avoiding volume integral calculations.
 
-The equations~\eqref{HAP} and~\eqref{SL} possess a number of the mathematical properties
-that mirror the phenomenological characteristics of hydrophobic attraction.
-Specifically, solutions of~\eqref{SL} yield an attractive force between
-hydrophobic bodies separated by water, and this attraction 
-decreases exponentially with the distance of separation~\cite{Eriksson1989}.
-Using boundary layer analysis, the HAP converges to a surface energy in the zero-decay length
-limit~\cite{Lee2018, Lin2015, Shibata2004}.
-Finally, we have demonstrated that the forces derived from HAP theory are non-additive~\cite{Meyer2006, Fu2018_SIAM}. 
+The equations~\eqref{HAP} and~\eqref{SL} possess a number of the
+mathematical properties that mirror the phenomenological characteristics
+of hydrophobic attraction. Specifically, solutions of~\eqref{SL} yield
+an attractive force between hydrophobic bodies separated by water, and
+this attraction decreases exponentially with the distance of
+separation~\cite{Eriksson1989}. Using boundary layer analysis, the HAP
+converges to a surface energy in the zero-decay length
+limit~\cite{Lee2018, Lin2015, Shibata2004}. Finally, we have
+demonstrated that the forces derived from HAP theory are
+non-additive~\cite{Meyer2006, Fu2018_SIAM}. 
 %The hydrophobic force has been implicated in the directed folding of proteins, 
@@
 domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}, yields a
-symmetric, rank-two tensor called the hydrophobic stress (eq. 2.3 in \cite{Fu2018_SIAM}):
+symmetric, rank-two tensor called the hydrophobic stress (equation (2.3)
+in~\cite{Fu2018_SIAM}):
 \begin{align}
@@
 Integrating the hydrophobic stress over the surface of particle $P_i$
-reveals the hydrophobic force and torque on each particle 
+reveals the hydrophobic force, and torque on each particle 
 \begin{align}
@@
 \end{align}
-relative to the center of mass $\mathbf{a}_i$.  This system is force-
-and torque-free (\S\ref{subsec:specific_aim_2}).  To avoid particle
+relative to the center of mass $\mathbf{a}_i$. This system is force- and
+torque-free (\S\ref{subsec:specific_aim_2}). To avoid particle
 collisions, we define an excluded volume potential $\Phi_{\text{repul}}$
 that diverges whenever tubular neighborhoods of adjacent particles
-overlap. The total potential,
-force and torque are then
+overlap. The total potential, force and torque are then
 \begin{equation}
@@
 bilayer assembly, the PIs propose to extend the HAP model to make direct
-comparison with experimental results  \S\ref{subsec:specific_aim_1}, to
+comparisons with experimental results \S\ref{subsec:specific_aim_1}, to
 establish that the HAP model has the capability and adaptivity to model
@@
 
-Our HAP approach differs from these prior methods in a number of respects.
-First, we do not assume a surface. Rather, we more fundamentally
-consider a collection of amphiphilic particles.  The collection of
-amphiphiles minimize hydrophobic interactions by sequestering
-hydrophobic tails in the form of a bilayer, and the particles' excess
-free energy gives rise to an elastic bilayer energy. The second
-difference lies in the fluid-interface coupling. Here, the associated
-mobility problem~\eqref{eq:stokes} is more complicated than dealing with
-a stress boundary condition or diffusive surface force, because the
-fluid velocity must be that of a rigid body motion at the particle
-surfaces. Finally, the HAP model directly addresses the existence of multiple phases.
-We can vary lipid length, spontaneous curvature, and bending rigidity by
-introducing different particle shapes and hydrophobic boundary
-conditions (Figure~\ref{fig:demixing}). In contrast, continuum theory
-deals with multiple phases through additional surface densities that
-must satisfy specialized transport equations~\cite{Lowengrub07,
-MikuckiZhou17}.
+Our HAP approach differs from these prior methods in a number of
+respects. First, we do not assume a surface. Rather, we more
+fundamentally consider a collection of amphiphilic particles. The
+collection of amphiphiles minimize hydrophobic interactions by
+sequestering hydrophobic tails in the form of a bilayer, and the
+particles' excess free energy gives rise to an elastic bilayer energy.
+The second difference lies in the fluid-interface coupling. Here, the
+associated mobility problem~\eqref{eq:stokes} is more complicated than
+dealing with a stress boundary condition or diffusive surface force,
+because the fluid velocity must be that of a rigid body motion at the
+particle surfaces. Finally, the HAP model directly addresses the
+existence of multiple phases. We can vary lipid length, spontaneous
+curvature, and bending rigidity by introducing different particle shapes
+and hydrophobic boundary conditions (Figure~\ref{fig:demixing}). In
+contrast, continuum theory deals with multiple phases through additional
+surface densities that must satisfy specialized transport
+equations~\cite{Lowengrub07, MikuckiZhou17}.
 

### 2020-11-13 NSF2020/Description/preliminarywork.tex

@@
     \label{eq:reciprocal}
-{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
+{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}
+[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
 {\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf
@@
 \cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$.
-Equation~\eqref{eq:reciprocal} does not require knowledge of $\nabla u$
-on the particle boundary, and this is enormously beneficial for
-calculating force and torque.
+Because of the double layer potential jump relations, \eqref{eq:reciprocal} 
+does not require knowledge of $\nabla u$ on the particle boundary, and this
+is enormously beneficial for calculating force and torque.
 
 \subsubsection{Two-dimensional vesicles in shear flow}
-We will compare the behavior of our particle-based vesicles in Stokes
-flow to well-established models that enforce area incompressibility and
-volume conservation in vesicle membrane
-dynamics~\cite{torres-sanchez_millan_arroyo_2019,
-mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}. Our
-preliminary results show that the particle-based bilayers have the same
+We have simulated two-dimensional vesicles in the background shear flow
+$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$. The numerical solver
+is written in the Matlab language runs on a desktop without parallelization. 
+The initially circular vesicle bilayers rotate and elongate with the shear flow, 
+and approach a steadily tank-treading ellipse.
+
+There are a number of well-established mathematical models of vesicles
+in shear flow \cite{torres-sanchez_millan_arroyo_2019, mahapatra_saintillan_rangamani_2020, 
+Steigmann99, C6SM02452A}. We are trying to assess which constituative
+assumption the particle-based bilayer satisfies. 
+Our preliminary results show that the particle-based bilayers have the same
 large area modulus as real lipid bilayer membranes, so we expect

### 2020-11-13 NSF2020/Description/newspecificaim3.tex
yny new sa2 3 prelim

@@
 where $S$ and $R$ are stokeslets and rotlets supported at the respective
-particle centers and $K\boldsymbol{eta}$ is a layer potential for the
+particle centers  \cite{leal_2007} and $K\boldsymbol{\eta}$ is a layer potential for the
 unknown density function $\boldsymbol{\eta}.$ The

### 2020-11-13 NSF2020/Description/preliminarywork.tex
yny new sa2 3 prelim

@@
 a compact numerical solver and included background flow in the simulations. 
-The background flow enters by replacing the third equation in \eqref{eq:stokes} 
-with the condition $(\mathbf{u} -\mathbf{u}_{\infty})(\mathbf{x}) 
-\to \mathbf{0}$ as $|\mathbf{x}| \to \infty$. To incorporate the far-field flow, 
-and using the representation 
-\begin{align}
-\label{PowerMiranda}
-  {\bf u} = {\bf u}_{\infty} + K\boldsymbol{\eta} + 
-    \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + 
-                 R(\cdot, {\bf a}_i) {\bf G}_i.
-\end{align}
-The symbols $S$ and $R$ are stokeslets and rotlets supported at the respective
-particle centers \cite{leal_2007} and $K\boldsymbol{eta}$ is a layer potential for the
-unknown density function $\boldsymbol{\eta}.$ The
-representation~\eqref{PowerMiranda} automatically satisfies all
-equations, with the exception of the rigid motion conditions. The rigid
-motion conditions follow by requiring the viscous stress vanishes across
-the particle boundaries.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%For Specific Aim 3
+%The background flow enters by replacing the third equation in \eqref{eq:stokes} 
+%with the condition $(\mathbf{u} -\mathbf{u}_{\infty})(\mathbf{x}) 
+%\to \mathbf{0}$ as $|\mathbf{x}| \to \infty$. To incorporate the far-field flow, 
+%and using the representation 
+%\begin{align}
+%\label{PowerMiranda}
+%  {\bf u} = {\bf u}_{\infty} + K\boldsymbol{\eta} + 
+%    \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + 
+%                 R(\cdot, {\bf a}_i) {\bf G}_i.
+%\end{align}
+%The symbols $S$ and $R$ are Stokeslets and rotlets supported at the respective
+%particle centers \cite{leal_2007} and $K\boldsymbol{eta}$ is a layer potential for the
+%unknown density function $\boldsymbol{\eta}.$ The
+%representation~\eqref{PowerMiranda} automatically satisfies all
+%equations, with the exception of the rigid motion conditions. The rigid
+%motion conditions follow by requiring the viscous stress vanishes across
+%the particle boundaries.
 
-\begin{wrapfigure}[13]{l}{0.30\textwidth}
-\centerline{\includegraphics[width=0.30\textwidth]{figures/BIError.pdf}}
-  \vspace{-8pt}
-\caption{
-\label{fig:bierror}  
-\footnotesize The false color map shows how numerical quadrature of
-  layer potentials loses accuracy near the particle boundaries.  The
-  color bar is for $\log_{10}.$}
-\end{wrapfigure}
-\textbf{Novel reciprocal identities.} 
-The force and torque formulas~\eqref{forceandtorque} require the
-hydrophobic stress along the particle boundaries. Unfortunately,
-standard quadrature formulas to estimate $\nabla u$ on the particle
-boundaries introduces large amounts of quadrature error
-(Figure~\ref{fig:bierror}). Therefore, it is useful to devise reciprocal
-identities for the force and torque on body $i$ that does not
-require integration along body $i$. One identity, that we have proved,
-is
-\begin{align}
-    \label{eq:reciprocal}
-{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}
-[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
-{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf
-  x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} +
-  \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, 
-\end{align}
-for $i=1,\ldots,N$. Here, $u_i$ is the solution of the screened Laplace
-equation when only the contribution from particle $i$ is considered and
-$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i
-\cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$.
-Because of the double layer potential jump relations, \eqref{eq:reciprocal} 
-does not require knowledge of $\nabla u$ on the particle boundary, and this
-is enormously beneficial for calculating force and torque.
+%\begin{wrapfigure}[13]{l}{0.30\textwidth}
+%\centerline{\includegraphics[width=0.30\textwidth]{figures/BIError.pdf}}
+%  \vspace{-8pt}
+%\caption{
+%\label{fig:bierror}  
+%\footnotesize The false color map shows how numerical quadrature of
+%  layer potentials loses accuracy near the particle boundaries.  The
+%  color bar is for $\log_{10}.$}
+%\end{wrapfigure}
+%\textbf{Novel reciprocal identities.} 
+%The force and torque formulas~\eqref{forceandtorque} require the
+%hydrophobic stress along the particle boundaries. Unfortunately,
+%standard quadrature formulas to estimate $\nabla u$ on the particle
+%boundaries introduces large amounts of quadrature error
+%(Figure~\ref{fig:bierror}). Therefore, it is useful to devise reciprocal
+%identities for the force and torque on body $i$ that does not
+%require integration along body $i$. One identity, that we have proved,
+%is
+%\begin{align}
+%    \label{eq:reciprocal}
+%{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}
+%[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
+%{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf
+%  x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} +
+%  \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, 
+%\end{align}
+%for $i=1,\ldots,N$. Here, $u_i$ is the solution of the screened Laplace
+%equation when only the contribution from particle $i$ is considered and
+%$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i
+%\cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$.
+%Because of the double layer potential jump relations, \eqref{eq:reciprocal} 
+%does not require knowledge of $\nabla u$ on the particle boundary, and this
+%is enormously beneficial for calculating force and torque.
 

### 2020-11-13 NSF2020/Description/newspecificaim2.tex
went through aim 2

@@
 %\begin{figure}[h]
-\begin{wrapfigure}[]{r}{0.60\textwidth}
-  \centering{\includegraphics[width=0.6\textwidth]{Figures/domain.pdf}}
-    \caption{\label{fig:flow_map} \todo[inline]{Missing caption}}
+\begin{wrapfigure}[13]{r}{0.61\textwidth}
+  \centering{\includegraphics[width=0.61\textwidth]{Figures/domain.pdf}}
+    \vspace{-20pt}
+    \caption{\label{fig:flow_map} \footnotesize A suspension of 3D
+    amphiphilic particles suspended in a solvent. The solvent satisfies
+    the Stokes equations, and the hydrophobic forces depend on the
+    solvent activity that satisfies the screened Laplace equation. The
+    geometry is updated by solving the mobility problem.} 
 \end{wrapfigure}
@@
 interactions, and thermal noise~\cite{Zhang2017}, to coordinate movement
-and bind nano-legos in a solvent \cite{Pandey2011, Leong2007, Reynolds2019,
-Dasgupta2017, Siontorou2017}. Additionally, hydrodynamic interactions are central for complex
-microscopic three-dimensional structures to fabricate~\cite{Cho2010}.
+and bind nano-legos in a solvent~\cite{Pandey2011, Leong2007,
+Reynolds2019, Dasgupta2017, Siontorou2017}. Additionally, hydrodynamic
+interactions are central to fabricate for complex microscopic
+three-dimensional structures~\cite{Cho2010}. Hydrodynamic effects can
+not be ignored since the rates of biological functions like fusion,
+fission, and pore dynamics rely on viscous
+dissipation~\cite{RYHAM20112929}.
 %
-In Specific Aim 2, we propose to develop efficient high-order numerical methods to simulate dynamic
-assembly of particles under HAP potential in a viscous solvent. 
+In Specific Aim 2, we propose to develop efficient high-order numerical
+methods to simulate dynamic assembly of particles under HAP potential in
+a viscous solvent. 
 %
@@
 %
-As described in~\eqref{eq:stokes} and
-illustrated in Figure~\ref{fig:flow_map}, the solvent phase is modeled
-by the Stokes equations for an incompressible viscous fluid, and these
-equations are coupled to the screened-Laplace equation~\eqref{SL}
-through viscous and hydrophobic stress balance. 
-Hydrodynamic effects can
-not be ignored since the rates of biological functions like fusion,
-fission, and pore dynamics rely on viscous
-dissipation~\cite{RYHAM20112929}. 
+As described in~\eqref{eq:stokes} and illustrated in
+Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
+equations for an incompressible viscous fluid, and these equations are
+coupled to the screened-Laplace equation~\eqref{SL} through viscous and
+hydrophobic stress balance.
+
 %While hydrophobic attraction causes the particles to self-assemble indepedently of the dissipation mechanism, the trajectories and
@@
 artificial boundary conditions introduce additional error, and
-discretizing the volume results in an excessively large linear system.
-Moreover, it is difficult to obtain high-order discretizations when the
-boundary surfaces are irregular. Alternatively, since we are solving
-constant-coefficient elliptic PDEs, the solution of the PDEs can be
-represented as layer potentials
+discretizing the volume results in an excessively large system of
+equations. Moreover, it is difficult to obtain high-order
+discretizations when the boundary surfaces are irregular. Alternatively,
+since we are solving constant-coefficient linear elliptic PDEs, its
+solution can be represented with layer potentials
 \begin{align}
@@
 $K(\mathbf{x},\mathbf{y})$ is a derivative of the fundamental solution
-of the underlying PDE. By matching the boundary condition at
+of the PDE. By matching the prescribed boundary condition at
 $\mathbf{x}_0 \in \partial\Omega$ with the limit of
@@
 
-Numerical methods to solve BIEs have
-several advantages over their PDE-based counterpart: by construction,
-the layer potential~\eqref{eq:LP} satisfies far-field conditions; only
+Numerical methods to solve BIEs have several advantages over their
+PDE-based counterpart: by construction, the layer
+potential~\eqref{eq:LP} satisfies far-field conditions; only
 $\partial\Omega$ needs to be discretized; carefully chosen kernels
@@
 propose two algorithms to avoid contact in \S\ref{subsec:timeStepping}.
-Then, proposed work for well-conditioned BIE formulations of fluctuating
-hydrodynamics are described in \S\ref{subsec:fluctuating}.
+An identity to accurately compute the hydrophobic stress is in
+\S\ref{subsec:reciprocal}. Then, proposed work for well-conditioned BIE
+formulations of fluctuating hydrodynamics are described in
+\S\ref{subsec:fluctuating}.
 
@@
 time is proportional to the cost of a matrix-vector multiplication that
-can be done in optimal or near-optimal time with the fast multipole
+can be performed in optimal or near-optimal time with the fast multipole
 method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2, fmm3,
-fmm4, fmm6, fmm7, fmm8}. PI BQ is experienced with applying FMMs to
-BIE formulations of the Stokes equation~\cite{qua-bir2014,
-bys-sha-qua2020} and the screened Laplace equation~\cite{kro-qua2011,
-qua2011}. Alternatively, fast direct solvers can be used to avoid
-iteration~\cite{fds1, fds2, fds3, fds4, fds5, fds6, fds7, fds8,
-ho2016cpam2, ho2016cpam1, minden2016, minden2017siammms}, but direct
-solvers often require a large amount of computational overhead, and this
-makes them less practical for problems with moving geometries.
-Alternatively, techniques in fast direct solvers can be used to develop
-efficient preconditioning strategies such as the inverse Fast Multipole
-Method (IFMM)~\cite{cou-pou-dar2017}. PI BQ used the IFMM to
-precondition Stokes equations in a porous media~\cite{qua-cou-dar2018},
-and a suite of other preconditioners including sparse approximate
-inverses~\cite{che2000} and multigrid~\cite{hem-sch1981, sch1982} will
-be investigated.
+fmm4, fmm6, fmm7, fmm8}. PI BQ is experienced with applying FMMs for the
+Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the screened
+Laplace equation~\cite{kro-qua2011, qua2011}.  Alternatively, fast
+direct solvers avoid iteration~\cite{fds2, fds3, fds4, fds5, fds6, fds7,
+ho2016cpam1, minden2016, minden2017siammms}, but direct solvers often
+require a large amount of computational overhead, and this makes them
+less practical for problems with moving geometries. Alternatively, fast
+direct solvers techniques can be used to develop efficient
+preconditioning strategies such as the inverse Fast Multipole Method
+(IFMM)~\cite{cou-pou-dar2017}. PI BQ used the IFMM to precondition
+Stokes equations~\cite{qua-cou-dar2018}, and a suite of other
+preconditioners including sparse approximate inverses~\cite{che2000} and
+multigrid~\cite{hem-sch1981, sch1982} will be investigated.
 
@@
 davis_1984, graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003,
-khayat_2005, schwab_1992, ying_2006, beale1, beale2, goodman_1990,
-haroldson_1998, lowengrub_1993, schwab_1992, ggq1, ggq2, ggq3,
-helsing_2008a, helsing_integral_2009, helsing_tutorial_2012,
-klockner2013jcp, qbx2, wala2019jcp, af2018sisc, siegel2018jcp,
-rachh2017jcp, ding2019arxiv, bar2014}. The trapezoid rule is the
-workhorse for two-dimensional BIEs since it achieves spectral accuracy
-when integrands are not nearly-singular~\cite{tre-wei2014}. To address
-nearly-singular integrands of two-dimensional BIEs, we will use a {\em
-barycentric quadrature rule} that only requires a slight modification of
-the trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this
-method requires the layer potential to satisfy Laplace or Stokes
-equations~\cite{bar-wu-vee2015, chi-moo-qua2020}, but the PIs will extend
-the method to layer potentials for the screened Laplace
-equation. This will be done by recognizing that the fundamental solution
-of the screened Laplace equation can be decomposed as
-$K(\mathbf{x},\mathbf{y}) = K_1(\mathbf{x},\mathbf{y}) +
-K_2(\mathbf{x},\mathbf{y})$, where $K_1(\mathbf{x},\mathbf{y}) =
--\log|\mathbf{x} - \mathbf{y}|$ and $K_2(\mathbf{x},\mathbf{y}) =
-K(\mathbf{x},\mathbf{y}) + \log|\mathbf{x} - \mathbf{y}|$. Using this
-decomposition, layer potentials involving $K_1(\mathbf{x},\mathbf{y})$
-can be accurately computed with the barycentric quadrature
-rule~\cite{ioa-pap-per1991}, and layer potentials involving
-$K_2(\mathbf{x},\mathbf{y})$ can be accurately computed with the
-trapezoid rule since the kernel is bounded for all $\mathbf{x}$ and
+khayat_2005, schwab_1992, ying_2006, beale1, schwab_1992, ggq1, ggq2,
+ggq3, helsing_2008a, helsing_tutorial_2012, klockner2013jcp, qbx2,
+wala2019jcp, af2018sisc, siegel2018jcp, rachh2017jcp, ding2019arxiv,
+bar2014}. The trapezoid rule is the workhorse for two-dimensional BIEs
+since it achieves spectral accuracy when integrands are not
+nearly-singular~\cite{tre-wei2014}. To address nearly-singular
+integrands of two-dimensional BIEs, we will use a {\em barycentric
+quadrature rule} that only requires a slight modification of the
+trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this method
+requires the layer potential to satisfy Laplace or Stokes
+equations~\cite{bar-wu-vee2015, chi-moo-qua2020}, but the PIs will
+extend the method to layer potentials for the screened Laplace equation.
+This will be done by recognizing that the fundamental solution of the
+screened Laplace equation can be decomposed as $K(\mathbf{x},\mathbf{y})
+= K_1(\mathbf{x},\mathbf{y}) + K_2(\mathbf{x},\mathbf{y})$, where
+$K_1(\mathbf{x},\mathbf{y}) = -\log|\mathbf{x} - \mathbf{y}|$ and
+$K_2(\mathbf{x},\mathbf{y}) = K(\mathbf{x},\mathbf{y}) + \log|\mathbf{x}
+- \mathbf{y}|$. Then, layer potentials involving
+$K_1(\mathbf{x},\mathbf{y})$ can be accurately computed with the
+barycentric quadrature rule~\cite{ioa-pap-per1991}, and layer potentials
+involving $K_2(\mathbf{x},\mathbf{y})$ can be accurately computed with
+the trapezoid rule since the kernel is bounded for all $\mathbf{x}$ and
 $\mathbf{y}$. The proposed method is demonstrated in
@@
 constraints such as force- and torque-free conditions appropriately
-adjust the time step size so that the dynamics are resolved without the
-computational expense of techniques such as embedded Runge-Kutta
-methods, step-doubling, and Richardson extrapolation.
+determine how the time step should be adjusted so that the dynamics are
+resolved without the computational expense of techniques such as
+embedded Runge-Kutta methods, step-doubling, and Richardson
+extrapolation.
 
@@
 %
-Our previous work avoids contact by including a Leonard-Jones body
+Our previous work avoids contact by including a Lennard-Jones body
 forces~\cite{Fu2018_SIAM}. Such a steep steric interaction at short
@@
 solving a non-linear complementarity problem with a geometric constraint
-that the configuration is non-overlapping.
+that the configuration is non-overlapping. In this manner, contact is
+avoided without the excessively small time steps required by stiff
+Lennard-Jones forces.
 
@@
 \subsubsection{Novel reciprocal identities}
+\label{subsec:reciprocal}
 The force and torque formulas~\eqref{forceandtorque} require the
 hydrophobic stress along the particle boundaries. Unfortunately,
-standard quadrature formulas to estimate $\nabla u$ on the particle
-boundaries introduces large amounts of quadrature error
-(Figure~\ref{fig:bierror}). Therefore, it is useful to devise reciprocal
-identities for the force and torque on body $i$ that does not
+layer potentials for $\nabla u$ involve hyper-singular integrals and
+this introduces large amounts of quadrature error on the particle
+boundaries (Figure~\ref{fig:bierror}). Therefore, it is useful to devise
+reciprocal identities for the force and torque on body $i$ that does not
 require integration along body $i$. One identity, that we have proved,
@@
 equation when only the contribution from particle $i$ is considered and
-$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i
-\cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$.
-Equation~\eqref{eq:reciprocal} does not require knowledge of $\nabla u$
-on the particle boundary, and this is enormously beneficial for
-calculating force and torque.
+$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j \mathbf{I} +
+\rho\left((\nabla u_i \cdot \nabla u_j) \mathbf{I} - 2 \nabla u_i
+\otimes \nabla u_j\right)$. Equation~\eqref{eq:reciprocal} does not
+require knowledge of $\nabla u$ on the particle boundary, and this is
+enormously beneficial for calculating the hydrophobic force and torque.
 
@@
 contact are implemented, we will embark on incorporating fluctuating
-hydrodynamics that are important even at scales of the some amphiphilic
+hydrodynamics that are important even at scales of some amphiphilic
 particles. Bao et al.~\cite{Bao17,Bao18} developed two-dimensional BIE
 formulations for Brownian rigid bodies. To satisfy the covariance of the
-rigid body velocities, an ill-conditioned first-kind integral equation
-method is used. The proposed work will consider a double-layer potential
+rigid body velocities, they use an ill-conditioned first-kind integral
+equation method. The proposed work will consider a layer potential
 formulation that has much better conditioning properties. This strategy

### 2020-11-13 NSF2020/Description/preliminarywork.tex
Update preliminarywork.tex
Preliminary section done; please check how table looks.

@@
 
-The PIs BQ, RR, YNY and Peter Fu initiated a collaboration in summer, 2020. 
-The present proposal is the outgrowth of this collaboration. We have created
-a compact numerical solver and included background flow in the simulations. 
+The PIs BQ, RR and YNY initiated a collaboration in summer, 2020 to develop
+the hydrodynamic model of \S \ref{subsec:specific_aim_3}
+To date, we have written solvers for the two-dimensional boundary integral formulatons
+of \eqref{SL} and \eqref{eq:stokes}. The solvers gives third-order spatial accuracy
+up to the boundary for $u$ and $\mathbf{u}$. The specialized reciprocal identity \ref{eq:reciprocal}
+gives spectral accuracy for force and torque (Table \ref{tab:spectral_force}}).
+\begin{wraptable}[10]{l}{0.45\textwidth}
+\begin{center}
+  \begin{tabular}{|l|l|l|l|}
+ $n$   & $\max_{i} \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|$   &  $\max_{i} \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|$   \\
+ 32   &  81.4933     &   70.3970\\       
+  64  &   4.9328     &    3.1928 \\
+ 128  &   0.0125     &    0.0030 \\
+256   &   0.0000765   &   0.00003389        
+  \end{tabular}
+\end{center}
+\caption{\label{tab:spectral_force} 
+\footnotesize 
+Numerical error for force and torque as a function of number of grid points $n$ per particle.
+The data is for $N = 5$ particles characteristic diamater 2; two of the particles are nearly touching 
+at a distance 0.02.} 
+\end{wraptable}
+
+We have simulated two-dimensional vesicles in shear flow 
+$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$ with shear rate $\dot{gamma}$. 
+The particle-based system mimiks the behavior observed in continuous vesicles
+\cite{torres-sanchez_millan_arroyo_2019, mahapatra_saintillan_rangamani_2020, 
+Steigmann99, C6SM02452A}. The basic pattern is that at moderate shear rates,
+the initially circular vesicle bilayer elongates and approaches a steadily 
+tank-treading ellipse. Analyzing any underlying constituative laws, the particles
+reorganize so that there is an initial decrease in vesicle area that plateaus 
+to a steady state area, respectively increase in arc length. This suggests that
+the particle system behaves as a semipermeable vesicle \cite{323e9a2f0c58487ea82518d7a1f96485,YAO2017728}.
+Our preliminary results already showed that the particle-based bilayers have the same
+large area modulus as real lipid bilayer membranes, and permit a small amount of stretching. 
+For large shear rates, the vesicle ruptures and flow carries away segmented membrane patches.
+
+The above considerations justify using the particle-based model to study material properties 
+as outline in \S \ref{subsec:specific_aim_1}. Furthermore, the particle system allows
+for intermonolayer slip~\cite{SHKULIPA2005823, ShkulipaThesis}.
+Intermonolayer slip enters zero-thickness membrane models as a velocity
+jump boundary condition \cite{schwalbe_vlahovska_miksis_2010}, for example, 
+but in the present model is a consequence of monolayer independence.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%For Specific Aim 3
@@
 %is enormously beneficial for calculating force and torque.
-
-\subsubsection{Two-dimensional vesicles in shear flow}
-We have simulated two-dimensional vesicles in the background shear flow
-$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$. The numerical solver
-is written in the Matlab language runs on a desktop without parallelization. 
-The initially circular vesicle bilayers rotate and elongate with the shear flow, 
-and approach a steadily tank-treading ellipse.
-
-There are a number of well-established mathematical models of vesicles
-in shear flow \cite{torres-sanchez_millan_arroyo_2019, mahapatra_saintillan_rangamani_2020, 
-Steigmann99, C6SM02452A}. We are trying to assess which constituative
-assumption the particle-based bilayer satisfies. 
-Our preliminary results show that the particle-based bilayers have the same
-large area modulus as real lipid bilayer membranes, so we expect
-realistic results from our flow simulations. Under moderate shear rates,
-the vesicle elongates and takes on the tank-treading elliptical shape.
-We can directly check for area compressibility conservation properties
-from the particle simulation by tracking the change in area density of
-the midplane as a function of shear flow rate, along with evaluating the
-tangential divergence of the velocity.
-
-Bilayer membranes have a small permeability to water
-\cite{323e9a2f0c58487ea82518d7a1f96485}, and modelers often assume a
-vesicle membrane that conserves volume. In our particle-based approach,
-water motion across the bilayer is limited by the size of the gaps
-between the particles, which is an artifact of coarse-graining.  Making
-these gaps smaller comes at the expense of numerical accuracy, and we
-will assess if there is a reasonable trade-off between approximate
-volume conservation and simulation complexity.
-
-Finally, the particle-based vesicle bilayers have two distinct leaflets
-consisting of the particles in contact with the vesicle interior, and
-those in contact with the surrounding fluid. Since there is a nonzero
-separation between these layers, an important effect we observe is that
-the leaflets slide against one another under shear flow.  This implies
-that part of the viscous dissipation in the aqueous phase is enhanced by
-intermonolayer friction~\cite{SHKULIPA2005823, ShkulipaThesis}.
-Intermonolayer slip enters zero-thickness membrane models as a velocity
-jump boundary condition and leads to multiple solution
-states~\cite{schwalbe_vlahovska_miksis_2010}.  In the present proposal,
-intermonolayer slip is an artifact of monolayer independence  and we can
-control for slip as a function of shear rate, vesicle diameter, and
-particle geometry.
 

### 2020-11-13 NSF2020/Description/newspecificaim3.tex
yny

@@
 
-\subsubsection{Effects of electric fields on the dynamic self-assembly}
+\subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
+Using flicker spectroscopy of the
+shape fluctuations of a giant unilamellar vesicle (GUV), the bending rigidity is determined as a function of lipid 
+composition from 0 to 100 mol $\%$ of charged lipids in recent experiments \cite{FaizEtAl2019_SoftMatt}:
+Membrane bending rigidity increases with lipid surface charge, while decreases with salt in the bulk due to the screening of the lipid surface charge,
+in agreement with several theoretical models \cite{Kralchevsky1996_JCIS,May1996_JChemPhys,LoubetEtAl2013_PRE} that also assumed the quadratic form of the elastic energy
+density in the presence of surface charge and/or bulk charge \cite{DuplantierGoldstein1990_PRL,Winterhalter1992_JPC}. 
+As the electrostatic interaction is non-local in nature, we expect that the controversy of the HK elastic energy form (see \S~\ref{subsec:specific_aim_1}) 
+would be worse in the presence of electrostatic interactions and/or electrokinetics.
+The PIs will extend the approaches in \S~\ref{subsec:specific_aim_1} to charged lipids to calculate the bending moduli and compare against the experimental results in \cite{FaizEtAl2019_SoftMatt}: We propose to incorporate an explicit surface charge on each particle boundary $P_i$
+and compute the electrostatic potential as a functional of particle configuration.
+Adding the electrostatic forces to the hydrophobic attraction forces between particles to compute the particle assembly dynamics, we can then calculate elastic moduli as outlined in \S~\ref{subsec:specific_aim_1}.
+Results from these proposed calculations provide another comparison/validation of HAP model against the continuum mechanics.
+
+Once the effects of lipid charges on the moduli are verified the PIs propose to examine how to use 
+an external electric field to control the amphiphilic self-assembly in solvent. 
+PI YNY has a track record of working on electrohydrodynamics
+of an elastic, inextensible membrane using both asymptotic analysis \cite{Nganguia2013_PRE,Young2014_JFM,Young2015_PoF} and numerical simulations \cite{Nganguia2015_CiCP}, and will work with both PI RR and BQ to extend the HAP model to study the electromechanical effects on the assembly of amphiphile.
+Results from these proposed research will yield quantitative understanding of how to utilize an electric field to achieve optimal control of assembly of amphiphiles in solvent.

### 2020-11-14 NSF2020/Description/newspecificaim3.tex

--- 2020-11-13 NSF2020/Description/newspecificaim3.tex
@@
 robust, high-order in time and space algorithms suited to the problem.
-The challenges are: {\bf (1)} the equations express a two-way coupling.
-This means that the flow changes the shape of the suspended particles,
+The challenges are: {\bf (1)} The equations express a two-way coupling
+since the flow changes the position of the suspended particles,
 and in return the geometry-dependent hydrophobic stresses impart a force
@@
 We include a background flow by replacing the third equation in
-\eqref{eq:stokes} with the condition $(\mathbf{u} -
-\mathbf{u}_{\infty})(\mathbf{x}) \to \mathbf{0}$ as $|\mathbf{x}| \to
+\eqref{eq:stokes} with the condition $\mathbf{u}(\mathbf{x})
+\to \mathbf{u}_{\infty}(\mathbf{x})$ as $|\mathbf{x}| \to
 \infty$. To incorporate the far-field flow, we use the representation 
@@
   {\bf u} = {\bf u}_{\infty} + K\boldsymbol{\eta} + 
-    \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + 
-                 R(\cdot, {\bf a}_i) {\bf G}_i.
+    \sum_{i=1}^N \left(S(\cdot, {\bf a}_i) {\bf F}_i + 
+                 R(\cdot, {\bf a}_i) {\bf G}_i\right),
 \end{align}
 where $S$ and $R$ are stokeslets and rotlets supported at the respective
-particle centers and $K\boldsymbol{eta}$ is a layer potential for the
-unknown density function $\boldsymbol{\eta}.$ The
-representation~\eqref{PowerMiranda} automatically satisfies all
-equations, with the exception of the rigid motion conditions. The rigid
+particle centers~\cite{leal_2007} and $K\boldsymbol{\eta}$ is a layer
+potential for the unknown density function $\boldsymbol{\eta}$. With the
+exception of the rigid body conditions, the
+representation~\eqref{PowerMiranda} automatically satisfies all the
+hydrodynamic equations including the far-field condition. The rigid
 motion conditions follow by requiring the viscous stress vanishes across
 the particle boundaries.
-
-%\begin{wrapfigure}[13]{r}{0.30\textwidth}
-%\centerline{\includegraphics[width=0.30\textwidth]{figures/BIError.pdf}}
-%  \vspace{-8pt}
-%\caption{
-%\label{fig:bierror}  
-%\footnotesize The false color map shows how numerical quadrature of
-%  layer potentials loses accuracy near the particle boundaries.  The
-%  color bar is for $\log_{10}.$}
-%\end{wrapfigure}
 
@@
 the vesicle elongates and takes on the tank-treading elliptical shape.
-We can directly check for area compressibility conservation properties
-from the particle simulation by tracking the change in area density of
-the midplane as a function of shear flow rate, along with evaluating the
-tangential divergence of the velocity.
+We can directly check for area compressibility and volume conservation
+properties from particle simulations by tracking the change in area
+density of the midplane as a function of shear flow rate, along with
+evaluating the tangential divergence of the velocity.
 
-Bilayer membranes have a small permeability to water
-\cite{323e9a2f0c58487ea82518d7a1f96485}, and modelers often assume a
-vesicle membrane that conserves volume. In our particle-based approach,
-water motion across the bilayer is limited by the size of the gaps
-between the particles, which is an artifact of coarse-graining.  Making
-these gaps smaller comes at the expense of numerical accuracy, and we
-will assess if there is a reasonable trade-off between approximate
-volume conservation and simulation complexity.
+Bilayer membranes have a small permeability to
+water~\cite{323e9a2f0c58487ea82518d7a1f96485}, and modelers often assume
+a vesicle membrane that conserves volume. In our particle-based
+approach, water motion across the bilayer is limited by the size of the
+gaps between the particles, which is an artifact of coarse-graining.
+Making these gaps smaller comes at the expense of numerical accuracy,
+and we will assess if there is a reasonable trade-off between
+approximate volume conservation and simulation complexity.
 
@@
 
-\subsubsection{Effects of electric fields on the dynamic self-assembly}
+\subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
+Using flicker spectroscopy of the shape fluctuations of a giant
+unilamellar vesicle (GUV), the bending rigidity is determined as a
+function of lipid composition from 0 to 100 mol $\%$ of charged lipids
+in recent experiments~\cite{FaizEtAl2019_SoftMatt}---membrane bending
+rigidity increases with lipid surface charge, while decreases with salt
+in the bulk due to the screening of the lipid surface charge. This
+agrees with several theoretical models~\cite{Kralchevsky1996_JCIS,
+May1996_JChemPhys, LoubetEtAl2013_PRE} that also assume the quadratic
+form of the elastic energy density in the presence of surface charge and
+bulk charge~\cite{DuplantierGoldstein1990_PRL, Winterhalter1992_JPC}. As
+the electrostatic interaction is non-local in nature, we expect that the
+controversy of the HK elastic energy form (see
+\S\ref{subsec:specific_aim_1}) would be worse in the presence of
+electrostatic interactions and electrokinetics. The PIs will extend
+the approaches in \S\ref{subsec:specific_aim_1} to charged lipids to
+calculate the bending moduli and compare against the experimental
+results in~\cite{FaizEtAl2019_SoftMatt}. We propose to incorporate an
+explicit surface charge on each particle boundary $P_i$ and compute the
+electrostatic potential as a functional of particle configuration.
+Adding the electrostatic forces to the hydrophobic attraction forces
+between particles to compute the particle assembly dynamics, we can then
+calculate elastic moduli as outlined in \S\ref{subsec:specific_aim_1}.
+Results from these proposed calculations provide further comparisons and
+validations of the HAP model against the continuum mechanics.
+
+Once the effects of lipid charges on the moduli are verified, the PIs
+propose to examine how to use an external electric field to control the
+amphiphilic self-assembly in solvent. PI YNY has a track record of
+working on electrohydrodynamics of an elastic, inextensible membrane
+using both asymptotic analysis~\cite{Nganguia2013_PRE, Young2014_JFM,
+Young2015_PoF} and numerical simulations~\cite{Nganguia2015_CiCP}, and
+will work with both PI RR and BQ to extend the HAP model to study the
+electromechanical effects on the assembly of amphiphile. Results from
+this research will yield a quantitative understanding of how to utilize
+an electric field to achieve optimal control of assembly of amphiphiles
+in solvent.

### 2020-11-14 NSF2020/Description/background.tex
fixed bibiography and touched up SA3
prelim done

@@
 \noindent
-{\bf Collaborative Research: Mathematical modeling and simulations of
-self-assembling amphiphilic particles in a solvent} \\
+{\bf Collaborative Research: Mathematical modeling and simulation of
+self-assembling amphiphilic particles in solvent} \\
 %{\bf {Collaborative Research: Mathematical modeling and coarse-grained simulations of self-assembly of amphiphilic Janus particles in a solvent}}\\
@@
 Numerical challenges and how these challenges are overcome are described
-in \S\ref{subsec:specific_aim_2} and \S\ref{subsec:specific_aim_3}.
+in \S\ref{subsec:specific_aim_2}.
 

### 2020-11-14 NSF2020/Description/preliminarywork.tex
RJR
prelim done

@@
+\begin{wraptable}[9]{r}{0.55\textwidth}
+\centering{
+  \begin{tabular}{|l|r|r|p{0.1\textwidth}|}
+    \hline
+          & HAP                     & experiment          & ref.\\
+    \hline 
+    $\KB$ & $11 \pm 2.5$ \kBT       & 10 \kBT               & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
+    \hline 
+    $\KA$ & $34$ \kBT \; nm$^{-2}$  & 30--40 \kBT nm$^{-2}$ & \cite{Nagle17, Nagle17-2}\\
+    \hline 
+    $\KTH$ & $12$ \kBT \; nm$^{-2}$ & 10 \kBT nm$^{-2}$     & \cite{KUZMIN2005, KoNa15} \\ \hline
+  \end{tabular}
+}
+\caption{\label{tab:moduli} \footnotesize Comparision of values elastic
+  moduli from the experimental literature and values derived by HAP
+  simulation.} 
+\end{wraptable}
 \section{Preliminary work}
@@
 
-\begin{wraptable}[10]{r}{0.55\textwidth}
-\begin{center}
-  \begin{tabular}{|l|r|r|p{0.1\textwidth}|}
-    \hline
-          & HAP                     & exper. value          & ref.\\
-    \hline 
-    $\KB$ & $11 \pm 2.5$ \kBT       & 10 \kBT               & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
-    \hline 
-    $\KA$ & $34$ \kBT \; nm$^{-2}$  & 30--40 \kBT nm$^{-2}$ & \cite{Nagle17, Nagle17-2}\\
-    \hline 
-    $\KTH$ & $12$ \kBT \; nm$^{-2}$ & 10 \kBT nm$^{-2}$     & \cite{KUZMIN2005, KoNa15} \\ \hline
-  \end{tabular}
-\end{center}
-\caption{\label{tab:moduli} \footnotesize Comparision of values elastic
-  moduli from the experimental literature and values derived by HAP
-  simulation.} 
-\end{wraptable}
 We performed three types of simulations. The first measured bending by loading
-a planar bilayer. The second used a harmonic bond to dilate a circular bilayer.
+a partially clamped planar bilayer. The second used a harmonic bond to dilate a circular bilayer.
 The third measured tilt using a decay equation from  \cite{KUZMIN2005}.
-These simulations isolated the deformations of \eqref{ansatz3}, enabling
+These simulations isolated three of the five deformations of \eqref{ansatz3}, enabling
 us to read off elastic moduli from simulation data. The results agreed remarkably 
-well with the values reported in the experimental literature, 
-Table~\ref{tab:moduli}. The agreement is underscored by the fact
+well with the values reported in the experimental literature 
+(Table~\ref{tab:moduli}). The agreement is underscored by the fact
 that the two, main HAP parameters $\gamma$ and $\rho$ were assigned
-physical values from the outset, rather than being tuned.
+physical values from the outset, rather than being tuned so as to fit data.
 
@@
 up to the boundary for $u$ and $\mathbf{u}$. The specialized reciprocal identity \ref{eq:reciprocal}
-gives spectral accuracy for force and torque (Table \ref{tab:spectral_force}}).
-\begin{wraptable}[10]{l}{0.45\textwidth}
-\begin{center}
+gives spectral accuracy for force and torque (Table \ref{tab:spectral_force}).
+\begin{wraptable}[12]{l}{0.40\textwidth}
+\centering{
   \begin{tabular}{|l|l|l|l|}
- $n$   & $\max_{i} \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|$   &  $\max_{i} \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|$   \\
- 32   &  81.4933     &   70.3970\\       
-  64  &   4.9328     &    3.1928 \\
- 128  &   0.0125     &    0.0030 \\
-256   &   0.0000765   &   0.00003389        
-  \end{tabular}
-\end{center}
+    $n$   & (rel. err.)$_F$
+    &  (rel. err.)$_G$ \\
+    \hline
+ 32   &   4.07466     &   1.56437\\
+ 64   &   0.24664     &   0.03476\\
+ 128  &   0.00063     &   0.00006\\
+  \end{tabular}}
 \caption{\label{tab:spectral_force} 
 \footnotesize 
-Numerical error for force and torque as a function of number of grid points $n$ per particle.
-The data is for $N = 5$ particles characteristic diamater 2; two of the particles are nearly touching 
-at a distance 0.02.} 
+Relative numerical errors
+(rel. err.)$_F = \max_{i} \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
+and 
+(rel. err.)$_G = \max_{i} \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
+for force and torque respectively as a function of number of grid points $n$ per particle.
+The data is for $N = 5$ particles; two of the particles are nearly touching 
+at a distance 1 \% of particle diameter.} 
 \end{wraptable}
@@
 We have simulated two-dimensional vesicles in shear flow 
-$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$ with shear rate $\dot{gamma}$. 
+$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$ with shear rate $\dot{\gamma}$.
+(The symbol shear rate is unrelated to interfacial tension.)
 The particle-based system mimiks the behavior observed in continuous vesicles
 \cite{torres-sanchez_millan_arroyo_2019, mahapatra_saintillan_rangamani_2020, 
-Steigmann99, C6SM02452A}. The basic pattern is that at moderate shear rates,
-the initially circular vesicle bilayer elongates and approaches a steadily 
-tank-treading ellipse. Analyzing any underlying constituative laws, the particles
-reorganize so that there is an initial decrease in vesicle area that plateaus 
-to a steady state area, respectively increase in arc length. This suggests that
-the particle system behaves as a semipermeable vesicle \cite{323e9a2f0c58487ea82518d7a1f96485,YAO2017728}.
-Our preliminary results already showed that the particle-based bilayers have the same
-large area modulus as real lipid bilayer membranes, and permit a small amount of stretching. 
-For large shear rates, the vesicle ruptures and flow carries away segmented membrane patches.
+  Steigmann99, C6SM02452A}.
+The basic pattern is that the vesicle bilayer approaches a steadily 
+tank-treading ellipse (Figure \ref{fig:tank_treading}C).
+We therefore analyzed the simulation data in the context of
+theoretical work on tank-treading \cite{Finken2008}. 
+Jeffrey's equation predicts a tank-treading frequency $\tfrac{1}{2}\dot{\gamma}$
+(dashed line Figure \ref{fig:tank_treading}B).
+In the particle simulation, the tank-treading frequency corresponds to the mean
+of the particle angular velocities, and these approach a value within 7 \% of
+the theoretical prediction (dotted and solid curves in Figure \ref{fig:tank_treading}B).
+In the low viscosity-contrast regime of our simulation, Jeffrey's equation predicts
+a decrease in the ellipse's inclination angle $\Theta$
+and our particle-based simulation follows this prediction
+(Figure \ref{fig:tank_treading}D). The higher frequency oscillation comes
+from particle reorganization.
 
-The above considerations justify using the particle-based model to study material properties 
-as outline in \S \ref{subsec:specific_aim_1}. Furthermore, the particle system allows
+Analyzing for any underlying constituative laws, the particles
+reorganize so that there is an initial increase and then plateauing of vesicle circumference.
+As is the case with real lipid bilayer membranes, the particle collection permits a small amount of stretching. 
+The theoretical calculations give an increase of length by 3.6 \% which
+agrees with our measured increase in length. The simulations also suggest
+that the particle system behaves as a semipermeable vesicle \cite{323e9a2f0c58487ea82518d7a1f96485,YAO2017728}.
+
+\begin{wrapfigure}[13]{r}{0.3\textwidth}
+  \centering{\includegraphics[width=0.3\textwidth]{Figures/PW_fig5.pdf}}
+    \caption{\label{fig:flow_rupture} \footnotesize
+      Rupture of a two-dimensional vesicle for large flow rates.}
+\end{wrapfigure}
+The above considerations further justify using the particle-based model to study material properties 
+as outlined in \S \ref{subsec:specific_aim_1}.
+Furthermore, the particle system allows
 for intermonolayer slip~\cite{SHKULIPA2005823, ShkulipaThesis}.
+In Figure \ref{fig:tank_treading}B, the inner angular velocity is slightly
+less than the outer angular velocity. 
 Intermonolayer slip enters zero-thickness membrane models as a velocity
 jump boundary condition \cite{schwalbe_vlahovska_miksis_2010}, for example, 
-but in the present model is a consequence of monolayer independence.
+but in the present model, it is a consequence of monolayer independence.
+For large shear rates, viscous forces exceed the hydrophobic attraction and the vesicle ruptures;
+the flow carries away segmented membrane patches (Figure \ref{fig:flow_rupture}).
+
+\begin{figure}%[13]{r}{0.61\textwidth}
+  \centering{\includegraphics[width=0.61\textwidth]{Figures/TankTreading.pdf}}
+    \caption{\label{fig:tank_treading} \footnotesize
+    A two-dimemsional particle-based vesicle under shear flow. 
+    Panel A shows the particles, water activity, and background flow direction.
+    In Panel C, the trace of the particle centers forms two ellipses with well-defined
+    inclination angle $\Theta$.
+    Panel B plots the mean angular velocities for the outer leaflet and the inner respectively.
+    Panel D shows the evolution of the inclination angle. 
+    Panels B and D share the same time axis.}
+\end{figure}
 

### 2020-11-14 NSF2020/Description/specificaim1_ver2.tex
edited 4.1.2

@@
 We have demonstrated that our hydrophobic attraction with repulsion
-potential (HARP) approach efficiently simulates self-assembly of
+potential (HAP) approach efficiently simulates self-assembly of
 amphiphilic particles into two-dimensional micelles, bilayer membranes,
@@
 bilayers, and efficiently simulating three-dimensional collective
-hydrodynamics of amphiphilic particles. Finally, we must mathematically
-characterize the variational behavior of HARP under appropriate
-homogenized limits.
+hydrodynamics of amphiphilic particles.
+Finally, we must incorporate electric charge and account
+for how external fields control for particle self-assembly. 
+%mathematically
+%characterize the variational behavior of HARP under appropriate
+%homogenized limits.
 
@@
 %was pioneered by Hamm and Kozlov (HK) \cite{Hamm2000}. The theory 
-is widely used to describe biological phenomona 
+is widely used to describe biological phenomena 
 fission \cite{FrEsAkSh15, Maetal15, PhysRevE.79.031926},
@@
 poration \cite{Gaetal20}, phase boundaries, and interaction with inclusions
-\cite{SeLeMaEg17,Saetal20, Pietal20}, which require resolution of the internal structure of the membrane.  
+\cite{SeLeMaEg17,Saetal20, Pietal20}. These phenomena
+require resolution of the internal structure of the membrane.  
 Recently, there has been a revival in interest in the HK theory as the quadratic assumption
@@
 
-The HK framework assumes a three-dimensional lipid monolayers with internal structure
-consisting of straight fibers that represent elongated hydrocarbon chains. HK assumed an
-elastic energy density ${\cal W}$ that is quadratic in the Green-Lagrange strain tensor for membrane deformation of
+The HK framework assumes a three-dimensional lipid monolayer with internal structure
+consisting of straight fibers that represent elongated hydrocarbon chains.
+The framework assumes an elastic energy density ${\cal W}$ that is quadratic in the
+Green-Lagrange strain tensor for membrane deformation of
 this striated, internal structure.
@@
 %
-This energy decomposes into four fundamental and independent
+This energy density decomposes into four, fundamental, and independent
 deformations (Figure~\ref{fig:deformations}): splay ($\Div {\bf n}$),
@@
 %
-{\bf (i)} determine the value of the elastic moduli $\KB$,
-$\KT$, $\KG$, and $\KTH$, and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
+{\bf (i)} determine the value of effective elastic moduli $\KB$,
+$\KT$, $\KG$, and $\KTH$, and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and
+particle shape map onto elastic moduli. 
 An accurate and robust way to measure material properties is to track the evolution of the bilayer as
@@
   \vspace{-8pt}
-\caption{\label{fig:saddle_splay} \footnotesize Determination of
+\caption{\label{fig:saddle_splay} \footnotesize Example of determining the
   saddle splay modulus.}
@@
 %
-In either case there is a dissipation of the total potential \eqref{eq:total_poten}, and this stabilizes the evolving bilayer shape.
+This yields a dissipation of the total potential \eqref{eq:total_poten}, which
+stabilizes the evolving bilayer shape.
 Therefore, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field ${\bf n}$ by
@@
 illustrated by Figure~\ref{fig:deformations}D. Having a nonzero twist
-requires nonzero tilt, because the surface gradient of the lipid
-directoy equals the second fundamental form, and is therefore symmetric,
-whenever tilt is zero locally. The twist deformation is a fully
+requires nonzero tilt (the surface gradient of the lipid
+director equals the second fundamental form
+%, and is therefore symmetric,
+whenever tilt is zero locally). The twist deformation is a fully
 three-dimensional deformation. \S\ref{subsec:specific_aim_3} addresses outstanding implementation issues like three-dimensional boundary integral equation solvers.
@@
 More generally, PI RR has shown that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}. 
-As a result, saddle splay can quantified from the transition energies of a least energy path of pore formation (Figure \ref{fig:saddle_splay}).   
+As a result, saddle splay can be quantified from the transition energies of a least energy path of pore formation (Figure \ref{fig:saddle_splay}).   
 %Using the string method, we will evaluate the transition energies between the intact pancake shape,
@@
 PhysRevE.102.042406}. 
-%A value $\KT = 0$, however, makes \eqref{ansatz3} noncoercive and leads to the nonphysical conclusion that there are bilayers 
+A value $\KT = 0$, however, makes \eqref{ansatz3} a noncoercive functional.
+%and leads to the nonphysical conclusion that there are bilayers 
 %with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
@@
 The HAP energy converges to the surface energy in the limit of vanishing
-screening length and the boundary layers of the minimizers (the
-solutions to the screen Laplace equation) converges to area measures
-supported on the particle boundaries. This is analogous to the sharp
-interface limit in the phase-field functional
+screening length. Also, the boundary layers of the solutions to the screen Laplace equation
+converge to area measures supported on the particle boundaries.
+This phenomena are analogous to the sharp interface limit in the phase-field functional
 formulation~\cite{Modica87, MODICA1987487, LuMo89}. PI RR has worked
-directly on phase field approximations of membrane bending
+on phase field approximations of membrane bending
 energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
-equation~\cite{1531-3492_2006_2_357, Lee2018}. The proposed analysis is
+equation~\cite{1531-3492_2006_2_357, Lee2018}.
+
+The following proposed analysis is
 a natural outgrowth of prior work because the linearization of the
 Poisson-Boltzmann equation is the screened Laplace equations~\eqref{SL}.
-
 We will develop the mathematical connections between the HAP energy and
 the energy functionals used in the gradient theory of phase transitions.
-The phase field functional approximates the perimeter of sublevel sets
-of a so-called phase field indicator function. The approximation becomes
-sharp in the zero interfacial thickness limit and minimizers of the
-phase field functional converge (after normalization) to the
-characteristic function of a set solving a perimeter minimization
-problem~\cite{Modica87, MODICA1987487, LuMo89}. 
+%The phase field functional approximates the perimeter of sublevel sets
+%of a so-called phase field indicator function. The approximation becomes
+%sharp in the zero interfacial thickness limit and minimizers of the
+%phase field functional converge (after normalization) to the
+%characteristic function of a set solving a perimeter minimization
+%problem
+~\cite{Modica87, MODICA1987487, LuMo89}. 
 %
 %
-One of the basic questions is to establish the HAP convergence rate as a
+One set of questions is to establish the HAP convergence rate as a
 function of particle geometry~\cite{LuMo89}, which can be used as a
 benchmark for numerical validation.
+Another set of questions is to establish the so-called $\Gamma$-convergence of energy minimizing
+particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 
 %In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  

### 2020-11-14 NSF2020/Description/preliminarywork.tex

--- 2020-11-13 NSF2020/Description/preliminarywork.tex
@@
-\section{Preliminary work}
-\label{sec:preliminary_work}
-The HAP project was initiated in 2017 by PIs RR and YNY.
-The lead author on our first paper (\cite{Fu2018_SIAM}) was Szu-Pei Fu,
-who was PI YNS's PhD student and is currently a postdoc with PI RR.
-The collaboration involved theoretical work and simulation. The theoretical
-work included model development, proving the first variation formula
-\eqref{stress} and force-free law, and an energy-based  uniqueness
-theorem for the exterior domain problem \eqref{SL}.
-Coauthors Andreas Kl\"ockner (Computer Science, UIUC, NSF CAREER \#1654756)
-and his PhD student Matt Wala provided their Quadrature by Expansion, or QBX
-algorithm and Fu ran simulations on NJIT clusters.
-
-The simulation results were encouraging. The small particle-number
-simulations successfully demonstrated gradient-driven self-assembly of amphiphilic
-particles into two-dimensional micelles, bilayer membranes. The model parameters
-where the decay length $\rho$, interfacial tension $\gamma$, particle geometry, and
-repulsion strength. The particle diamaters were set equal to monolayer thickness, 
-2.0 nm \cite{Boal}, and we chose a repulsion strength that gave adequate interparticle 
-spacing. For the decay length, we used $\rho = 2.5$ nm based on measurements of hydrophobic
-attraction between surfactant-coated \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80}.
-For the interfacial tension, we used $\gamma = 4$ pN nm$^{-1}$
-based on measurements for single-component bilayer lipid membranes
-\cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson2016}.
-
-\begin{wraptable}[10]{r}{0.55\textwidth}
-\begin{center}
+\begin{wraptable}[8]{r}{0.55\textwidth}
+\centering{
   \begin{tabular}{|l|r|r|p{0.1\textwidth}|}
     \hline
-          & HAP                     & exper. value          & ref.\\
+          & HAP                     & experiment          & ref.\\
     \hline 
@@
   \end{tabular}
-\end{center}
+}
+  \vspace{-8pt}
 \caption{\label{tab:moduli} \footnotesize Comparision of values elastic
@@
 \end{wraptable}
-We performed three types of simulations. The first measured bending by loading
-a planar bilayer. The second used a harmonic bond to dilate a circular bilayer.
-The third measured tilt using a decay equation from  \cite{KUZMIN2005}.
-These simulations isolated the deformations of \eqref{ansatz3}, enabling
-us to read off elastic moduli from simulation data. The results agreed remarkably 
-well with the values reported in the experimental literature, 
-Table~\ref{tab:moduli}. The agreement is underscored by the fact
-that the two, main HAP parameters $\gamma$ and $\rho$ were assigned
-physical values from the outset, rather than being tuned.
+\section{Preliminary work}
+\label{sec:preliminary_work}
+The HAP project was initiated in 2017 by PIs RR and YNY. The lead author
+on our first paper~\cite{Fu2018_SIAM} was Szu-Pei Fu, who was PI YNY's
+PhD student and is currently a postdoc with PI RR. The collaboration
+involved theoretical work and simulation. The theoretical work included
+model development, proving the first variation formula~\eqref{stress}
+and force-free law, and an energy-based uniqueness theorem for the
+exterior domain problem~\eqref{SL}. Coauthors Andreas Kl\"ockner
+(Computer Science, UIUC, NSF CAREER \#1654756) and his PhD student Matt
+Wala provided their Quadrature by Expansion, or QBX algorithm and Fu ran
+simulations on NJIT clusters.
 
-The PIs BQ, RR and YNY initiated a collaboration in summer, 2020 to develop
-the hydrodynamic model of \S \ref{subsec:specific_aim_3}
-To date, we have written solvers for the two-dimensional boundary integral formulatons
-of \eqref{SL} and \eqref{eq:stokes}. The solvers gives third-order spatial accuracy
-up to the boundary for $u$ and $\mathbf{u}$. The specialized reciprocal identity \ref{eq:reciprocal}
-gives spectral accuracy for force and torque (Table \ref{tab:spectral_force}}).
-\begin{wraptable}[10]{l}{0.45\textwidth}
-\begin{center}
+\begin{wraptable}[11]{l}{0.42\textwidth}
+\centering{
   \begin{tabular}{|l|l|l|l|}
- $n$   & $\max_{i} \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|$   &  $\max_{i} \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|$   \\
- 32   &  81.4933     &   70.3970\\       
-  64  &   4.9328     &    3.1928 \\
- 128  &   0.0125     &    0.0030 \\
-256   &   0.0000765   &   0.00003389        
-  \end{tabular}
-\end{center}
+    $n$   & (rel.~err.)$_F$
+    &  (rel.~err.)$_G$ \\
+    \hline
+% 32   &   4.07466     &   1.56437\\
+% 64   &   0.24664     &   0.03476\\
+% 128  &   0.00063     &   0.00006\\
+  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
+  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
+  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
+  \end{tabular}}
+\vspace{-5pt}
 \caption{\label{tab:spectral_force} 
-\footnotesize 
-Numerical error for force and torque as a function of number of grid points $n$ per particle.
-The data is for $N = 5$ particles characteristic diamater 2; two of the particles are nearly touching 
-at a distance 0.02.} 
+\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
+  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
+  and (rel.~err.)$_G = \max_{i}
+  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
+  for force and torque respectively as a function of number of grid
+  points $n$ per particle.  The data is for $N = 5$ particles; two of
+  the particles are nearly touching at a distance 1\% of particle
+  diameter.} 
 \end{wraptable}
+The simulation results were encouraging. Small particle-number
+simulations successfully demonstrated gradient-driven self-assembly of
+amphiphilic particles into two-dimensional micelles and bilayer membranes.
+The model parameters were the decay length $\rho$, interfacial tension
+$\gamma$, particle geometry, and repulsion strength. The particle
+diameters were the physical monolayer thickness, 2.0 nm~\cite{Boal}, and
+we chose a repulsion strength that gave adequate interparticle spacing.
+For the decay length, we used $\rho = 2.5$ nm based on measurements of
+hydrophobic attraction between surfactant-coated
+membranes~\cite{Eriksson1989, Lin2005, Parsegian, Israelachvili80}. For
+the interfacial tension, we used $\gamma = 4$ pN nm$^{-1}$ based on
+measurements for single-component bilayer lipid
+membranes~\cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson2016}.
+
+\begin{wrapfigure}[]{r}{0.5\textwidth}
+  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
+  \vspace{-25pt}
+    \caption{\label{fig:tank_treading} \footnotesize A two-dimensional
+    particle-based vesicle in a shear flow. Panel A shows the particles,
+    water activity, and background flow direction. Panel B plots the
+    mean angular velocities for the outer leaflet and the inner
+    respectively.  Panel C shows that the trajectory of the particle
+    centers forms two ellipses with well-defined inclination angle
+    $\Theta$. Panel D shows the evolution of the inclination angle.
+    Panels B and D share the same time axis.}
+\end{wrapfigure}
+The PIs BQ, RR and YNY initiated a collaboration in Summer 2020 to
+develop the hydrodynamic model of \S\ref{subsec:specific_aim_3}.  To
+date, we have written solvers for the two-dimensional boundary integral
+formulations of~\eqref{SL} and~\eqref{eq:stokes} that achieve
+third-order accuracy up to the boundary. The specialized reciprocal
+identity~\eqref{eq:reciprocal} gives spectral accuracy for force and
+torque (Table~\ref{tab:spectral_force}).
+
+We performed three types of simulations. The first measured bending by
+loading a partially clamped planar bilayer. The second used a harmonic
+bond to dilate a circular bilayer. The third measured tilt using a decay
+equation from~\cite{KUZMIN2005}. These simulations isolated three of the
+five deformations of~\eqref{ansatz3}, enabling us to read off elastic
+moduli from simulation data. The results agreed remarkably well with the
+values reported in the experimental literature (Table~\ref{tab:moduli}).
+The agreement is underscored by the fact that the two main HAP
+parameters, $\gamma$ and $\rho$, were assigned physical values from the
+outset rather than being tuned to fit data.
 
 We have simulated two-dimensional vesicles in shear flow
-$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$ with shear rate $\dot{gamma}$. 
-The particle-based system mimiks the behavior observed in continuous vesicles
-\cite{torres-sanchez_millan_arroyo_2019, mahapatra_saintillan_rangamani_2020, 
-Steigmann99, C6SM02452A}. The basic pattern is that at moderate shear rates,
-the initially circular vesicle bilayer elongates and approaches a steadily 
-tank-treading ellipse. Analyzing any underlying constituative laws, the particles
-reorganize so that there is an initial decrease in vesicle area that plateaus 
-to a steady state area, respectively increase in arc length. This suggests that
-the particle system behaves as a semipermeable vesicle \cite{323e9a2f0c58487ea82518d7a1f96485,YAO2017728}.
-Our preliminary results already showed that the particle-based bilayers have the same
-large area modulus as real lipid bilayer membranes, and permit a small amount of stretching. 
-For large shear rates, the vesicle ruptures and flow carries away segmented membrane patches.
+$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$ with shear rate
+$\dot{\gamma}$,
+%(The symbol shear rate is unrelated to interfacial tension.)
+and the particle-based system mimics the behavior observed in continuous
+vesicles~\cite{torres-sanchez_millan_arroyo_2019,
+mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}. The basic
+pattern is that the vesicle bilayer approaches a steady tank-treading
+ellipse (Figure~\ref{fig:tank_treading}C). We analyzed the simulation
+data in the context of theoretical work on
+tank-treading~\cite{Finken2008}. Jeffrey's equation predicts a
+tank-treading frequency $\dot{\gamma}/2$ (dashed line in
+Figure~\ref{fig:tank_treading}B). In the particle simulation, the
+tank-treading frequency corresponds to the mean of the particle angular
+velocities, and these approach a value within 7\% of the theoretical
+prediction (dotted and solid curves in Figure~\ref{fig:tank_treading}B).
+In the low viscosity-contrast regime of our simulation, Jeffrey's
+equation predicts a decrease in the ellipse's inclination angle $\Theta$
+and our particle-based simulation follows this prediction
+(Figure~\ref{fig:tank_treading}D). The higher frequency oscillation
+comes from particle reorganization.
 
-The above considerations justify using the particle-based model to study material properties 
-as outline in \S \ref{subsec:specific_aim_1}. Furthermore, the particle system allows
-for intermonolayer slip~\cite{SHKULIPA2005823, ShkulipaThesis}.
-Intermonolayer slip enters zero-thickness membrane models as a velocity
-jump boundary condition \cite{schwalbe_vlahovska_miksis_2010}, for example, 
-but in the present model is a consequence of monolayer independence.
+Analyzing for any underlying constitutive laws, the particles reorganize
+so that there is an initial increase and then plateauing of vesicle
+circumference. As is the case with real lipid bilayer membranes, the
+particle collection permits a small amount of stretching. The
+theoretical calculations give an increase of length by 3.6\% which
+agrees with our measured increase in length. The simulations also
+suggest that the particle system behaves as a semipermeable
+vesicle~\cite{323e9a2f0c58487ea82518d7a1f96485, YAO2017728}.
+
+\begin{wrapfigure}[11]{r}{0.22\textwidth}
+  \centering{\includegraphics[width=0.22\textwidth]{Figures/PW_fig5.pdf}}
+  \caption{\label{fig:flow_rupture} \footnotesize Rupture of a
+  two-dimensional vesicle at large shear rates.}
+\end{wrapfigure}
+The above considerations further justify using the particle-based model
+to study material properties as outlined in
+\S\ref{subsec:specific_aim_1}. Furthermore, the particle system allows
+for intermonolayer slip~\cite{SHKULIPA2005823, ShkulipaThesis}. In
+Figure \ref{fig:tank_treading}B, the inner angular velocity is slightly
+less than the outer angular velocity. Intermonolayer slip enters
+zero-thickness membrane models as a velocity jump boundary condition
+\cite{schwalbe_vlahovska_miksis_2010}, for example, but in the present
+model, it is a consequence of monolayer independence. For large shear
+rates, viscous forces exceed the hydrophobic attraction and the vesicle
+ruptures; the flow carries away segmented membrane patches (Figure
+\ref{fig:flow_rupture}).
 

### 2020-11-14 NSF2020/Description/background.tex
edited 4.1.2
fixed things here and there

@@
 the decay length $\rho$
-and a scalar function $u(\mathbf{x})$ called the water activity.
+and a dimensionless scalar function $u(\mathbf{x})$ called the water activity.
 The integrand has units of an inverse length and so
@@
 
-\begin{wrapfigure}[6]{l}{0.35\textwidth}
+\begin{wrapfigure}[6]{r}{0.35\textwidth}
 \centerline{\includegraphics[width=0.35\textwidth]{figures/Lysis.pdf}}
@@
 ($\sim 5$ nm), which is a nearly impossible task using phase-field or
-immerse boundary method without extreme refinement around the membrane
+immersed boundary methods without extreme refinement around the membrane
 and artificial treatment of reconnection during the topological change

### 2020-11-14 NSF2020/Description/preliminarywork.tex
fixed things here and there

@@
 \label{sec:preliminary_work}
-The HAP project was initiated in 2017 by PIs RR and YNY. The lead author
+The HAP project was initiated in 2017 by PI RR and YNY. The lead author
 on our first paper~\cite{Fu2018_SIAM} was Szu-Pei Fu, who was PI YNY's
@@
   \vspace{-25pt}
-    \caption{\label{fig:tank_treading} \footnotesize A two-dimensional
-    particle-based vesicle in a shear flow. Panel A shows the particles,
-    water activity, and background flow direction. Panel B plots the
+  \caption{\label{fig:tank_treading} \footnotesize
+    Panel A shows water activity and flow direction for  a two-dimensional
+    particle-based vesicle in a shear flow; $\mu  = 1$ mPa s,
+    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. Panel B plots the
     mean angular velocities for the outer leaflet and the inner
@@
 \end{wrapfigure}
-The PIs BQ, RR and YNY initiated a collaboration in Summer 2020 to
-develop the hydrodynamic model of \S\ref{subsec:specific_aim_3}.  To
-date, we have written solvers for the two-dimensional boundary integral
-formulations of~\eqref{SL} and~\eqref{eq:stokes} that achieve
-third-order accuracy up to the boundary. The specialized reciprocal
-identity~\eqref{eq:reciprocal} gives spectral accuracy for force and
-torque (Table~\ref{tab:spectral_force}).
-
-We performed three types of simulations. The first measured bending by
+The paper \cite{Fu2018_SIAM} considered three types of simulations. The first measured bending by
 loading a partially clamped planar bilayer. The second used a harmonic
@@
 outset rather than being tuned to fit data.
+
+The PI BQ, RR and YNY initiated a collaboration in Summer 2020 to
+develop the hydrodynamic model of \S\ref{subsec:specific_aim_3}.  To
+date, we have written solvers for the two-dimensional boundary integral
+formulations of~\eqref{SL} and~\eqref{eq:stokes} that achieve
+third-order accuracy up to the boundary. The specialized reciprocal
+identity~\eqref{eq:reciprocal} gives spectral accuracy for force and
+torque (Table~\ref{tab:spectral_force}).
 
@@
 data in the context of theoretical work on
-tank-treading~\cite{Finken2008}. Jeffrey's equation predicts a
-tank-treading frequency $\dot{\gamma}/2$ (dashed line in
+tank-treading~\cite{Finken2008, PhysRevLett.106.158103}.
+Jeffrey's equation predicts a
+tank-treading frequency $-\dot{\gamma}/2$ (dashed line in
 Figure~\ref{fig:tank_treading}B). In the particle simulation, the
@@
 and our particle-based simulation follows this prediction
-(Figure~\ref{fig:tank_treading}D). The higher frequency oscillation
-comes from particle reorganization.
+(Figure~\ref{fig:tank_treading}D), albeit with some higher frequency oscillation
+coming from particle reorganization.
 
@@
 particle collection permits a small amount of stretching. The
-theoretical calculations give an increase of length by 3.6\% which
+theoretical calculations give an increase of length by 3.6\% and this amount
 agrees with our measured increase in length. The simulations also
@@
 \ref{fig:flow_rupture}).
+
+In conclusion, the HAP model accurately mimics the behavior of continuous
+membranes, while at the same time capturing the
+reconnection during the topological change of 
+lipid molecules on the scales of membrane thickness,
+overcoming one of the long-standing challenges of continuum modeling.
 

### 2020-11-14 NSF2020/Description/specificaim1_ver2.tex
fixed things here and there

@@
 The HAP energy converges to the surface energy in the limit of vanishing
-screening length. Also, the boundary layers of the solutions to the screen Laplace equation
-converge to area measures supported on the particle boundaries.
+screening length~\cite{Shibata2004}.
+Also, the boundary layers of the solutions to the screen Laplace equation
+converge to area measures supported on the particle boundaries
+\cite{Lee2018, Lin2015, Shibata2004}.
 This phenomena are analogous to the sharp interface limit in the phase-field functional
@@
 benchmark for numerical validation.
-Another set of questions is to establish the so-called $\Gamma$-convergence of energy minimizing
+Ultimately, we will be able to address the so-called $\Gamma$-convergence of energy minimizing
 particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 

### 2020-11-14 NSF2020/Description/newspecificaim3.tex
yny 1114

@@
 the particle boundaries.
-
+%
 We will compare the behavior of our particle-based vesicles in Stokes
@@
 volume conservation in vesicle membrane
-dynamics~\cite{torres-sanchez_millan_arroyo_2019,
-mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}. Our
-preliminary results show that the particle-based bilayers have the same
-large area modulus as real lipid bilayer membranes, so we expect
-realistic results from our flow simulations. Under moderate shear rates,
-the vesicle elongates and takes on the tank-treading elliptical shape.
-We can directly check for area compressibility and volume conservation
-properties from particle simulations by tracking the change in area
-density of the midplane as a function of shear flow rate, along with
-evaluating the tangential divergence of the velocity.
-
-Bilayer membranes have a small permeability to
-water~\cite{323e9a2f0c58487ea82518d7a1f96485}, and modelers often assume
-a vesicle membrane that conserves volume. In our particle-based
-approach, water motion across the bilayer is limited by the size of the
-gaps between the particles, which is an artifact of coarse-graining.
-Making these gaps smaller comes at the expense of numerical accuracy,
-and we will assess if there is a reasonable trade-off between
-approximate volume conservation and simulation complexity.
-
-Finally, the particle-based vesicle bilayers have two distinct leaflets
-consisting of the particles in contact with the vesicle interior, and
-those in contact with the surrounding fluid. Since there is a nonzero
-separation between these layers, an important effect we observe is that
-the leaflets slide against one another under shear flow. This implies
-that part of the viscous dissipation in the aqueous phase is enhanced by
-intermonolayer friction~\cite{SHKULIPA2005823, ShkulipaThesis}.
-Intermonolayer slip enters zero-thickness membrane models as a velocity
-jump boundary condition and leads to multiple solution
-states~\cite{schwalbe_vlahovska_miksis_2010}. In the present proposal,
-intermonolayer slip is an artifact of monolayer independence and we can
-control for slip as a function of shear rate, vesicle diameter, and
-particle geometry.
+dynamics~\cite{torres-sanchez_millan_arroyo_2019,mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}.
+Some preliminary results are in \S \ref{sec:preliminary_work}. 
+%
+%Our
+%preliminary results show that the particle-based bilayers have the same
+%large area modulus as real lipid bilayer membranes, so we expect
+%realistic results from our flow simulations. Under moderate shear rates,
+%the vesicle elongates and takes on the tank-treading elliptical shape.
+%We can directly check for area compressibility and volume conservation
+%properties from particle simulations by tracking the change in area
+%density of the midplane as a function of shear flow rate, along with
+%evaluating the tangential divergence of the velocity.
+%
+%Bilayer membranes have a small permeability to
+%water~\cite{323e9a2f0c58487ea82518d7a1f96485}, and modelers often assume
+%a vesicle membrane that conserves volume. In our particle-based
+%approach, water motion across the bilayer is limited by the size of the
+%gaps between the particles, which is an artifact of coarse-graining.
+%Making these gaps smaller comes at the expense of numerical accuracy,
+%and we will assess if there is a reasonable trade-off between
+%approximate volume conservation and simulation complexity. 
+%
+%Finally, the particle-based vesicle bilayers have two distinct leaflets
+%consisting of the particles in contact with the vesicle interior, and
+%those in contact with the surrounding fluid. Since there is a nonzero
+%separation between these layers, an important effect we observe is that
+%the leaflets slide against one another under shear flow. This implies
+%that part of the viscous dissipation in the aqueous phase is enhanced by
+%intermonolayer friction~\cite{SHKULIPA2005823, ShkulipaThesis}.
+%Intermonolayer slip enters zero-thickness membrane models as a velocity
+%jump boundary condition and leads to multiple solution
+%states~\cite{schwalbe_vlahovska_miksis_2010}. In the present proposal,
+%intermonolayer slip is an artifact of monolayer independence and we can
+%control for slip as a function of shear rate, vesicle diameter, and
+%particle geometry.
 

### 2020-11-14 NSF2020/Description/preliminarywork.tex
yny 1114

@@
 \label{sec:preliminary_work}
-The HAP project was initiated in 2017 by PI RR and YNY. The lead author
-on our first paper~\cite{Fu2018_SIAM} was Szu-Pei Fu, who was PI YNY's
-PhD student and is currently a postdoc with PI RR. The collaboration
-involved theoretical work and simulation. The theoretical work included
-model development, proving the first variation formula~\eqref{stress}
-and force-free law, and an energy-based uniqueness theorem for the
-exterior domain problem~\eqref{SL}. Coauthors Andreas Kl\"ockner
-(Computer Science, UIUC, NSF CAREER \#1654756) and his PhD student Matt
-Wala provided their Quadrature by Expansion, or QBX algorithm and Fu ran
-simulations on NJIT clusters.
-
+PIs RR and YNY started work on HAP modeling with Szu-Pei Fu (then PI YNY's student and now PI RR's postdoc) and collaborators in 2017. 
+%
+%The HAP project was initiated in 2017 by PI RR and YNY. The lead author
+%on our first paper~\cite{Fu2018_SIAM} was Szu-Pei Fu, who was PI YNY's
+%PhD student and is currently a postdoc with PI RR. The collaboration
+%involved theoretical work and simulation. The theoretical work included
+%model development, proving the first variation formula~\eqref{stress}
+%and force-free law, and an energy-based uniqueness theorem for the
+%exterior domain problem~\eqref{SL}. 
+%Coauthors Andreas Kl\"ockner
+%(Computer Science, UIUC, NSF CAREER \#1654756) and his PhD student Matt
+%Wala provided their Quadrature by Expansion, or QBX algorithm and Fu ran
+%simulations on NJIT clusters.
+%
 \begin{wraptable}[11]{l}{0.42\textwidth}
@@
 \end{wraptable}
-The simulation results were encouraging. Small particle-number
-simulations successfully demonstrated gradient-driven self-assembly of
-amphiphilic particles into two-dimensional micelles and bilayer membranes.
-The model parameters were the decay length $\rho$, interfacial tension
-$\gamma$, particle geometry, and repulsion strength. The particle
-diameters were the physical monolayer thickness, 2.0 nm~\cite{Boal}, and
-we chose a repulsion strength that gave adequate interparticle spacing.
-For the decay length, we used $\rho = 2.5$ nm based on measurements of
+The results are summarized in \cite{Fu2018_SIAM}, where
+small particle-number simulations successfully demonstrated gradient-driven self-assembly of
+amphiphilic particles into two-dimensional micelles and bilayer membranes with realistic values of
+the model parameters:  decay length $\rho=2.5$ nm (based on measurements of
 hydrophobic attraction between surfactant-coated
-membranes~\cite{Eriksson1989, Lin2005, Parsegian, Israelachvili80}. For
-the interfacial tension, we used $\gamma = 4$ pN nm$^{-1}$ based on
+membranes~\cite{Eriksson1989, Lin2005, Parsegian, Israelachvili80}),
+particle diameter 2.0 nm (the physical monolayer thickness, 2.0 nm~\cite{Boal}),
+and interfacial tension $\gamma = 4$ pN nm$^{-1}$ based on
 measurements for single-component bilayer lipid
@@
 
-\begin{wrapfigure}[]{r}{0.5\textwidth}
-  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
-  \vspace{-25pt}
-  \caption{\label{fig:tank_treading} \footnotesize
-    Panel A shows water activity and flow direction for  a two-dimensional
-    particle-based vesicle in a shear flow; $\mu  = 1$ mPa s,
-    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. Panel B plots the
-    mean angular velocities for the outer leaflet and the inner
-    respectively.  Panel C shows that the trajectory of the particle
-    centers forms two ellipses with well-defined inclination angle
-    $\Theta$. Panel D shows the evolution of the inclination angle.
-    Panels B and D share the same time axis.}
-\end{wrapfigure}
+%\begin{wrapfigure}[]{r}{0.5\textwidth}
+%  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
+%  \vspace{-25pt}
+%  \caption{\label{fig:tank_treading} \footnotesize
+%    Panel A shows water activity and flow direction for  a two-dimensional
+%    particle-based vesicle in a shear flow; $\mu  = 1$ mPa s,
+%    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. Panel B plots the
+%    mean angular velocities for the outer leaflet and the inner
+%    respectively.  Panel C shows that the trajectory of the particle
+%    centers forms two ellipses with well-defined inclination angle
+%    $\Theta$. Panel D shows the evolution of the inclination angle.
+%    Panels B and D share the same time axis.}
+%\end{wrapfigure}
 The paper \cite{Fu2018_SIAM} considered three types of simulations. The first measured bending by
@@
 
-The PI BQ, RR and YNY initiated a collaboration in Summer 2020 to
+PIs BQ, RR and YNY initiated a collaboration in Summer 2020 to
 develop the hydrodynamic model of \S\ref{subsec:specific_aim_3}.  To
@@
 torque (Table~\ref{tab:spectral_force}).
+\begin{wrapfigure}[]{r}{0.5\textwidth}
+  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
+  \vspace{-25pt}
+  \caption{\label{fig:tank_treading} \footnotesize
+    Panel A: A two-dimensional
+    particle-based vesicle in a shear flow (arrows); $\mu  = 1$ mPa s,
+    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. The color coding is for HAP. Panel B: The
+    mean angular velocities for the outer leaflet and the inner
+    respectively.  Panel C: The trajectory of the particle
+    centers forms two ellipses with well-defined inclination angle
+    $\Theta$. Panel D: The evolution of the inclination angle.
+    Panels B and D share the same time axis.}
+\end{wrapfigure}
 
@@
 
-\begin{wrapfigure}[11]{r}{0.22\textwidth}
+\begin{wrapfigure}[11]{l}{0.22\textwidth}
   \centering{\includegraphics[width=0.22\textwidth]{Figures/PW_fig5.pdf}}

### 2020-11-14 NSF2020/Description/priorsupport.tex
worked on SA1 and small edits elsewhere
small changes
small edits
fixed up Gantt table

@@
 \noindent
-{\bf Yuan-Nan Young}: {\it NSF-DMS-1222550, Mathematical and experimental study of lipid bilayer 
-shape and dynamics mediated by surfactants and proteins}, \$212,603, 9/15/2012 - 08/31/2016 (with no-cost extension), PI. 
-{\it Intellectual merit:} The focus of this grant is modeling the interaction between a pure lipid bilayer membrane (LBM) with surfactant, cholesterol and protein.
+{\bf Yuan-Nan Young}: {\em NSF-DMS-1222550, Mathematical and
+experimental study of lipid bilayer shape and dynamics mediated by
+surfactants and proteins}, \$212,603, 9/15/2012 - 08/31/2016 (with
+no-cost extension), PI. {\em Intellectual merit:} The focus of this
+grant is modeling the interaction between a pure lipid bilayer membrane
+with surfactant, cholesterol and protein.
 %Hence, there is no overlap between these grants and the current proposal.
@@
 
-\begin{wrapfigure}{r}{0.56\textwidth}
+\begin{wrapfigure}[9]{r}{0.56\textwidth}
+\vspace{-15pt}
 \definecolor{barblue}{RGB}{51,102,254}
-\renewcommand\sfdefault{phv}
-\renewcommand\mddefault{mc}
-\renewcommand\bfdefault{bc}
-\sffamily
+%\renewcommand\sfdefault{phv}
+%\renewcommand\mddefault{mc}
+%\renewcommand\bfdefault{bc}
+%\sffamily
 \begin{ganttchart}[
@@
     title/.style={draw=none, fill=none},
-    title label font=\bfseries\footnotesize,
+    title label font=\bfseries\footnotesize, % numbers across the top
     title label node/.append style={below=3pt},
     include title in canvas=false,
-    bar label font=\mdseries\small\color{black!70},
+    bar label font=\mdseries\footnotesize\color{black!70}, 
+    % titles across the left
     %bar label node/.append style={left=2cm},
@@
 \gantttitlelist{2,...,12}{1} \\
-\ganttgroup{Tasks\hfill}{1}{12}\\
-\ganttbar{Specific Aim 1}{1}{6}\\
-\ganttbar{Specific Aim 2}{1}{9}\\
-\ganttbar{Specific Aim 3}{5}{12}\\
-\ganttbar{Program management}{1}{12}\\
+%\ganttgroup{Tasks\hfill}{1}{12}\\
+  \ganttbar{Specific Aim 1 (2D)}{1}{4} \\
+  \ganttbar{Specific Aim 1 (3D)}{8}{12}\\
+\ganttbar{Specific Aim 2}{1}{8}\\
+\ganttbar{Specific Aim 3}{1}{12}\\
+\ganttbar{Program management}{1}{12}
 \end{ganttchart}
-\caption{Schedule for the proposed work, measured in quarters from the
-  beginning of the project.}
-  \todo[inline]{Need to update Gantt table}
+  \vspace{-8pt}
+\caption{\footnotesize Schedule for the proposed work, measured in
+  quarters from the beginning of the project.}
 \label{fig:schedule}
@@
 with the lead PI (Ryham) for this endeavor. The research work is
-structured to meet the tasks discussed in
-Section~\ref{sec:proposed-work}.
+structured to meet the tasks discussed in \S\ref{sec:proposed-work}.
 %
@@
 \textbf{Research Schedule:} The detailed schedule for the proposed work
-is shown in Fig.~\ref{fig:schedule}.
+is shown in Figure~\ref{fig:schedule}. Specific Aim 1 is split over two
+periods to allow time for 3D code to be developed.

### 2020-11-14 NSF2020/Description/specificaim1_ver2.tex
RJR

@@
 \subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
-The HAP energy converges to the surface energy in the limit of vanishing
-screening length~\cite{Shibata2004}.
+The HAP energy converges to the surface energy in the limit of vanishing screening length~\cite{Shibata2004}.
 Also, the boundary layers of the solutions to the screen Laplace equation
-converge to area measures supported on the particle boundaries
-\cite{Lee2018, Lin2015, Shibata2004}.
-This phenomena are analogous to the sharp interface limit in the phase-field functional
-formulation~\cite{Modica87, MODICA1987487, LuMo89}. PI RR has worked
-on phase field approximations of membrane bending
+converge to area measures supported on the particle boundaries \cite{Lee2018, Lin2015, Shibata2004}.
+These phenomena are analogous to the sharp interface limit in the phase-field functional,
+and motivate developing the mathematical connections between the HAP energy and
+the energy functionals used in the gradient theory of phase transitions.
+formulation~\cite{Modica87, MODICA1987487, LuMo89}.
+PI RR has worked on phase field approximations of membrane bending
 energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
 equation~\cite{1531-3492_2006_2_357, Lee2018}.
-
-The following proposed analysis is
-a natural outgrowth of prior work because the linearization of the
-Poisson-Boltzmann equation is the screened Laplace equations~\eqref{SL}.
-We will develop the mathematical connections between the HAP energy and
-the energy functionals used in the gradient theory of phase transitions.
+The screened-Laplace equations~\eqref{SL} is the linearization of the Poisson-Boltzmann equation.
+One set of questions is to establish the HAP convergence rate as a
+function of particle geometry~\cite{LuMo89}, which can be used as a
+benchmark for numerical validation.
+Ultimately, we will be able to address the so-called $\Gamma$-convergence of energy minimizing
+particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 
 %The phase field functional approximates the perimeter of sublevel sets
@@
 %problem
-~\cite{Modica87, MODICA1987487, LuMo89}. 
 %
 %
-One set of questions is to establish the HAP convergence rate as a
-function of particle geometry~\cite{LuMo89}, which can be used as a
-benchmark for numerical validation.
-Ultimately, we will be able to address the so-called $\Gamma$-convergence of energy minimizing
-particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 
+
 %In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  

### 2020-11-14 NSF2020/Description/DataManagement.tex
Adding data management

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{todonotes}

\begin{document}
\topmargin0.25in
%\thispagestyle{empty}
\sloppy

\begin{center}
\Large \bf Data Management Plan
\end{center}
%\vspace{0.2in}

\subsection*{Materials to be produced in the course of the research}
The proposed research will produce data from analysis, numerical
simulations, and theoretical modeling. These data pertain to the
proposed research subjects on self-assembling amphiphilic particles in
solvent. These data will lead to quantitative understanding of the
formation of biophysical structures and smart materials.

\subsection*{The standards to be used for data and meta data format and
content}
Data generated from the proposed research will be shared among the
collaborators in their original data format and content. These data will
be available to the public once they are published in journals or
presented at conferences.

\subsection*{Policies for access and sharing}
The experimental data and numerical codes will be shared among
colleagues in the community, and the numerical MATLAB codes use version
control with the repositories linked on PI Ryham's
(faculty.fordham.edu/rryham), PI Quaife's
(people.sc.fsu.edu/$\sim$bquaife), and PI Young's
(web.njit.edu/$\sim$yyoung) webpages. All sharing and access of data are
allowed only under the consent from the PIs under the policies of
Fordham University, Florida State University (FSU), and New Jersey
Institute of Technology (NJIT). No sharing and access of data will be
allowed if illegal profit is gained.

\subsection*{Policies and provisions for re-use, re-distribution, and
the production of derivatives}
The data can be re-used and/or re-distributed only upon the consent from
the PIs under the policies of Fordham University, FSU, and NJIT. Any
derivatives from the data generated from the proposed research follow
the same rules.

\subsection*{Plans for archiving data, samples and other research
products}
The data will be archived following the policies of Fordham University,
FSU, and NJIT. All samples and research products will be protected by
Fordham University, FSU, and NJIT under the agreement with the National
Science Foundation.

\subsection*{Responsibility for Data Management}
All members of the investigative team including the PIs and graduate
students with access to data will receive instruction in the Responsible
Conduct of Research (Fordham University, FSU, and NJIT). The PIs are
responsible for enforcing the Data Management Plan outlined in this
document and the PIs will perform a quarterly check to make sure data
are properly stored, archived, and maintained. The PIs will conform
closely to the NSF policy on the dissemination and sharing of the
research data and materials created or gathered in the course of the
proposed project. The data acquired and preserved in the context of
this proposal will be further governed by Fordham University, FSU, and
NJIT's policies pertaining to intellectual property, record retention,
and data
management.

\subsection*{Types of data to be produced during the course of the
project}
{\bf PI Ryham}: The following summarizes the type of analytical data to
be produced: \todo[inline]{Rolf to fill in}

\noindent
{\bf PI Quaife}: The following summarizes the type of numerical data to
be produced: i) Matlab codes and data array structures to perform 2D
numerical simulations, (ii) Fortran and C++ codes and data array
structures to perform 3D numerical simulations, and (iii) binary data
from numerical solutions of amphiphilic particle suspensions. The
estimated size of all the data is approximately 1 TB per year.

\noindent {\bf PI Young}: The following summarizes the type of
numerical/theoretical data to be produced: i) Mathematica files for the
theoretical modeling work, ii) Matlab codes and data array structures,
and iii) binary data from numerical simulations of the vesicle
osmophoresis. The estimated size of all the data is approximately 200 GB
per year. \todo[inline]{Yuan to update. This is what was in the CBET
proposal}

\subsection*{Standards to be used for data format and content}
C++ codes are stored as .cpp files, Fortran codes are stored as .f90
files, Matlab codes are stored as .m files, data array structures are
stored as .mat files, and numerical simulations are stored as .bin
files. Analyzed data will be summarized as graphs regularly and
documented as reports stored in .pdf format

\subsection*{Methods and policies for providing access and sharing}
Any of the raw data from this project will be made available to other
researchers who may want to replicate or verify the results obtained.
Project data will be made available through university-operated
repository to facilitate the sharing of data. Data will be made
available when the publication(s) containing the data are in print. If
requested, data will be made available for sharing to qualified parties
by the PIs, so long as such a request does not compromise intellectual
property interests, interfere with publication, invade subject privacy,
betray confidentiality, or precede data curation. Data that are shared
will include standards and notations needed to interpret the data,
following commonly accepted practices in the field. Data will be shared
by using cloud-type storage like Dropbox if files are small or USB
key/DVD if files are large.

\subsection*{Methods for archiving and preserving access to data and
materials}
Original data notebooks will be retained in a secure location in the
PIs' laboratories. All data will be backed up on a secure server
provided by the university and portable hard drives and will be archived
for at least at least three years beyond the award period, as required
by the NSF guidelines.

\end{document}

### 2020-11-14 NSF2020/Description/background.tex
fixed typos in background

@@
 {\em Rolf Ryham (lead PI, Fordham University), Bryan Quaife (PI,
-FSU), and Y.-N. Young (PI, NJIT)}
+Florida State University), and Young-Nan Young (PI, New Jersey Institute of Technology)}
 \section{Background}
@@
 bilayers of lipids) to shield their hydrophobic parts from contact with
-the solvent molecules (water).
+the solvent (water) molecules.
 %
@@
 \cite{Lum1999,Meyer2006,Hammer2010}. Measurements show that the
-hydrophobic force decays exponentially with a decay length like 1 nm
-\cite{Israelachvili1984, Marcelja1977,Christenson2001,Lin2005}. It is
-also known that the interaction is not pairwise additive, meaning that
+hydrophobic force decays exponentially with a decay length on the order of 1 nm
+\cite{Israelachvili1984, Marcelja1977,Christenson2001,Lin2005}. 
+Additionally, the interaction is not pairwise additive, meaning that
 the force between any two hydrophobic objects is altered by the presence
@@
 \caption{ \footnotesize
-A collection $P_1,$ $P_2,$ $P_3, \ldots$ of rigid particles. The
+A collection of rigid particles: $P_1,$ $P_2,$ $P_3, \ldots$. The
 exterior domain $\Omega$ represents the solvent.}
@@
 \end{wrapfigure}
-Recently PIs RR and YNY developed a mathematical model called the
-hydrophobic attraction potential (HAP) \cite{Fu2018_SIAM} that is based
+Recently, PIs RR and YNY developed a mathematical model, called the
+hydrophobic attraction potential (HAP) model \cite{Fu2018_SIAM}, that is based
 on the physical origin of hydrophobicity. This model addresses the major
 shortcomings of molecular dynamics (MD) and continuum approaches. Based
-on preliminary results (\S\ref{sec:preliminary_work}) the PIs propose to
+on preliminary results (\S\ref{sec:preliminary_work}), the PIs propose to
 extend this HAP model to offer an alternative modeling methodology that
-leads to new mathematical ideas, and is both physically accurate and
+leads to new mathematical ideas and is both physically accurate and
 computationally practical.
@@
 %hydrophobic forces~\cite{Fu2018_SIAM}. 
-The motivation for the HAP concept stemmed from PI RR's earlier work on
-the problem of energy barriers in membrane
+The motivation for the HAP concept stemmed from PI RR's work concerning
+energy barriers in membrane
 fusion~\cite{RyKlYaCo16,Chetal16}. By applying a mathematical, squared-gradient
@@
 Based on PI RR and YNY's coarse-grained membrane modeling
-work~\cite{Fu2017}, the investigators initiated a collaboration to
-create a gradient theory for arbitrary collections of hydrophobic and
-amphiphilic particles. This new method eliminates the costly calculation
+work~\cite{Fu2017}, the investigators devised a gradient theory for
+arbitrary collections of hydrophobic and
+amphiphilic particles. As a new method, HAP eliminates the costly calculation
 of water by treating the solvent implicitly, is capable of representing
-biologically relevant morphologies, and avoids complicated
+biologically-relevant morphologies, and avoids complicated
 re-meshing schemes of continuum approaches by utilizing a particle-based
@@
 
-The above considerations motivate the following definition for the HAP:
+The above considerations motivate the following definition for HAP:
 \begin{align}
@@
 and a dimensionless scalar function $u(\mathbf{x})$ called the water activity.
-The integrand has units of an inverse length and so
+The integrand has units of an inverse length, so
 the volume integral has units of area. Multiplication by interfacial tension
@@
 To establish an attraction between interfaces, the water activity is not
-arbitrary, but rather is the solution of the screened Laplace
+arbitrary but rather is the solution of the screened Laplace
 equation boundary value problem 
@@
 The boundary values $f$ define the degree of hydrophobicity of the
-water-particle interface: $f=1$, describes a hydrophobic interface and
-$f=0$ describes a hydrophilic interface. Thus $f$ encodes information
-about the particles and the parameters $\rho$ and $\gamma$ encode
+water-particle interface: $f=1$ describes a hydrophobic interface, and
+$f=0$ describes a hydrophilic interface. Thus, $f$ encodes information
+about the particles, and the parameters $\rho$ and $\gamma$ encode
 information about the quality of the solvent~\cite{Israelachvili1954,
@@
 
-The equations~\eqref{HAP} and~\eqref{SL} possess a number of the
+The equations~\eqref{HAP} and~\eqref{SL} possess a number of
 mathematical properties that mirror the phenomenological characteristics
@@
 %%lipid  bilayer  membrane  that  are  consistent  with other results in the literature.   
-To define the particle dynamics, let $P_1$, $P_2$, \ldots, $P_N$, be a
-finite collection of disjoint, rigid, and closed particles with
-Lipschitz boundary. Assume that the label $f$ is an element of the
+To define the particle dynamics, let $P_1$, $P_2$, \ldots, $P_N$ be a
+finite collection of disjoint, rigid, and closed particles each with
+a Lipschitz boundary. Assume that the label $f$ is an element of the
 Sobolev space $H^1(\Omega)$. The functional~\eqref{HAP} has a minimizer
@@
 that diverges whenever tubular neighborhoods of adjacent particles
-overlap. The total potential, force and torque are then
+overlap. The total potential, force, and torque are then
 \begin{equation}
@@
 \end{equation}
-Here $\mu$ is the fluid viscosity and the first two equations state that
+Here, $\mu$ is the fluid viscosity; the first two equations state that
 the fluid motion is a divergence-free Stokes flow; the third equation
@@
 $\mathbf{v}_i$ and $\boldsymbol{\omega}_i$ are unknown translation and
-angular velocities; the last two equations state that the net
+angular velocities; and the last two equations state that the net
 viscous forces and torques with fluid shear stress $\boldsymbol{\sigma}$
@@
 \textbf{(iii)} solve the Stokes mobility problem~\eqref{eq:stokes} for
-rigid body motion, \textbf{(iv)} update the particle configuration.
+rigid body motion, and \textbf{(iv)} update the particle configuration.
 Numerical challenges and how these challenges are overcome are described
@@
 
-It is worth emphasizing that the HAP model uses only a few parameters;
+It is worth emphasizing that the HAP model uses only a few parameters:
 interfacial tension, decay length, repulsion strength, and particle
@@
 micropipette manipulation directly calibrates our interfacial tension
-parameter. This is in direct contrast with pair-potential based
+parameter. This is in direct contrast with pair-potential-based
 approaches in MD simulations and coarse-grained models where many more
@@
 agreement with experimentally determined values~\cite{Fu2018_SIAM}.
-Encouraged by these results and the hydrodynamic simulations of the
+Encouraged by these results and the hydrodynamic simulations of
 bilayer assembly, the PIs propose to extend the HAP model to make direct
-comparisons with experimental results \S\ref{subsec:specific_aim_1}, to
-establish that the HAP model has the capability and adaptivity to model
+comparisons with experimental results \S\ref{subsec:specific_aim_1} and to
+establish that the HAP model has the capability to model
 flow phenomena across length scales and time scales
-\S\ref{subsec:specific_aim_2}, using efficient, high-order numerical
+\S\ref{subsec:specific_aim_2} using efficient, high-order numerical
 methods \S\ref{subsec:specific_aim_3}.
@@
 membranes, vesicles, and red blood cells. These approaches range from
-the finite element method~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15},
-phase field method~\cite{Du05,QiangDu08,Lowengrub13}, and immersed
-boundary method~\cite{Hu,Hu13, KimLai2010_JCP}. PI RR and collaborators
+the finite element~\cite{Bartels,Peng13,RyKlYaCo16,Sinha15},
+phase field~\cite{Du05,QiangDu08,Lowengrub13}, and immersed
+boundary methods~\cite{Hu,Hu13, KimLai2010_JCP}. PI RR and collaborators
 led in part the development of phase field functionals of membrane
@@
 Our HAP approach differs from these prior methods in a number of
-respects. First, we do not assume a surface. Rather, we more
-fundamentally consider a collection of amphiphilic particles. The
+respects. First, we do not assume a surface. Rather, we 
+assume a collection of amphiphilic particles. The
 collection of amphiphiles minimize hydrophobic interactions by
@@
 associated mobility problem~\eqref{eq:stokes} is more complicated than
-dealing with a stress boundary condition or diffusive surface force,
-because the fluid velocity must be that of a rigid body motion at the
+dealing with a stress boundary condition or diffusive surface force
+because the fluid velocities are for individual rigid body motions at each
 particle surfaces. Finally, the HAP model directly addresses the
@@
 \end{wrapfigure}
-The greatest strength of using HAP to model lipid bilayer membrane is
-the ability to form discontinuities (interfacial singularity) from first
+The greatest strength of using the HAP to model a lipid bilayer membrane is
+the ability to form discontinuities (interfacial singularities) from first
 physical principles without any artificial manipulation to rearrange the

### 2020-11-14 NSF2020/Description/specificaim1_ver2.tex
fixed typos in SA 1; made up title for our work in progress

@@
 amphiphilic particles into two-dimensional micelles, bilayer membranes,
-and vesicles \cite{Fu2018_SIAM}, and recreates the tank-treading
-phenomenon in external shear flows \cite{Fu20} \todo{Is this supposed
-to be a reference to our working paper}.
-%\todo[inline]{!!let's put a proceedings here so we have something to cite!!}.
-%
+and vesicles \cite{Fu2018_SIAM} and recreates the tank-treading
+phenomenon in external shear flows \cite{FuQuRyYo20}.
 While the results show great promise in the field of collective body
@@
 include a thorough analysis of elastic properties of our coarse-grained
-bilayers, and efficiently simulating three-dimensional collective
+bilayers and efficiently simulating three-dimensional collective
 hydrodynamics of amphiphilic particles.
-Finally, we must incorporate electric charge and account
-for how external fields control for particle self-assembly. 
+We must also incorporate electric charge and account
+for how external fields control particle self-assembly. 
 %mathematically
@@
 
-\subsection{Specific Aim 1: Measuring material properties of self-assembly of amphiphiles}
+\subsection{Specific Aim 1: Measuring material properties of amphiphile self-assembly}
 \label{subsec:specific_aim_1}
@@
 For amphiphiles assembled into bilayers, these properties are described by membrane continuum mechanics.
-Our goal is to be able to map the parameters of the particle-based model onto the elastic moduli from continuum theory.
+Our goal is to map the parameters of the particle-based model onto the elastic moduli from continuum theory.
 Results from this goal will facilitate simulators to use the hydrophobic attraction force calculations
@@
 %was pioneered by Hamm and Kozlov (HK) \cite{Hamm2000}. The theory 
-is widely used to describe biological phenomena 
+is widely used to describe biological phenomena, including 
 fission \cite{FrEsAkSh15, Maetal15, PhysRevE.79.031926},
@@
 
-The HK framework assumes a three-dimensional lipid monolayer with internal structure
-consisting of straight fibers that represent elongated hydrocarbon chains.
-The framework assumes an elastic energy density ${\cal W}$ that is quadratic in the
-Green-Lagrange strain tensor for membrane deformation of
-this striated, internal structure.
+The HK framework assumes a three-dimensional lipid monolayer where the internal structure
+consists of straight fibers that represent elongated hydrocarbon chains.
+The elastic energy density ${\cal W}$ is quadratic in the Green-Lagrange strain
+tensor for this striated, internal structure.
 %
@@
 ${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is
-the unit surface normal:
+the unit surface normal;
 \begin{equation}
@@
 Canham-Helfrich energy used throughout the fluid-structure literature
-\cite{QiangDu09, Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP,
-  qua-bir2014, qua-vee-you2019}.
+\cite{QiangDu09, Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP, qua-bir2014, qua-vee-you2019}.
 %\todo[inline]{YNY: place your recent works here}
@@
 {\bf (i)} determine the value of effective elastic moduli $\KB$,
-$\KT$, $\KG$, and $\KTH$, and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and
+$\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and
 particle shape map onto elastic moduli. 
@@
 patch contains only splay deformation without any other components
-(saddle splay, twist and tilt). As the bent membrane flattens we find
+(saddle splay, twist and tilt). As the bent membrane flattens, we find
 that both the membrane self-interaction energy $\Phi$ and the elastic
@@
 Here we start with a particle-based bilayer in a specific non-equilibrium shape that involves only one of the components of the displacement in Figure~\ref{fig:deformations}, and then evolve the particle system according to the time integration for \eqref{eq:stokes}.
-Actually,  elastic properties are independent of dissipation, and so we can forgo solving for fluid velocity and by setting the translational
+Because elastic properties are independent of dissipation,
+we can forgo solving for fluid velocity and set the translational
 velocity and angular velocity directly proportional to force and torque. 
@@
 %\end{equation}
-%where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; 
+%where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; %
 %$A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
@@
 %through \eqref{SGD}.
-
+%
 \begin{wrapfigure}[11]{l}{0.32\textwidth}
@@
 
-We propose to conduct calculations similar to the example of Figure~\ref{fig:flattening} for other elastic moduli such as the effective twist modulus $\KT$.
+We propose to conduct calculations similar to the example of Figure~\ref{fig:flattening}
+for other elastic moduli such as the effective twist modulus $\KT$.
 Molecular dynamics investigations find a twist modulus about 1
-\kBT~\cite{LeVeWa14}, and here the specific non-equilibrium shape consists of
+\kBT~\cite{LeVeWa14}, and here, the specific non-equilibrium shape consists of
 a single layer of amphiphilic particles on a hydrophobic substrate as
 illustrated by Figure~\ref{fig:deformations}D. Having a nonzero twist
-requires nonzero tilt (the surface gradient of the lipid
+requires nonzero tilt because the surface gradient of the lipid
 director equals the second fundamental form
 %, and is therefore symmetric,
-whenever tilt is zero locally). The twist deformation is a fully
+whenever tilt is zero locally. The twist deformation is a fully
 three-dimensional deformation. \S\ref{subsec:specific_aim_3} addresses outstanding implementation issues like three-dimensional boundary integral equation solvers.
@@
 The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
-\textbf{(i)} Researchers have assumed that $\KT = 0$ because of the
-relationship between twist the assumption of lateral fluidity in
+\textbf{(i)} Researchers have assumed that $\KT = 0$ to effect lateral fluidity in
 membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
@@
 Later,~\cite{C9SM02079A} and~\cite{PhysRevE.102.042406} independently
-identified an inconsistency an the argument used
+identified an inconsistency in the argument used
 by~\cite{TerziDeserno17} arising
@@
 negative saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
-SIEGEL20085200}, that gives rise to a larger energy barrier for
+SIEGEL20085200} that gives rise to a larger energy barrier for
 monolayer fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
@@
 the works~\cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000,
-C9SM02079A} utilize an approximate identity for incompressibility, and
-so we can offer a considerably more accurate analysis of monolayer
-energy.
+C9SM02079A} utilize an approximate identity for incompressibility as a base,
+so we can considerably improve upon the analysis of monolayer energy.
 

### 2020-11-15 NSF2020/Description/newspecificaim2.tex
fixed typos in SA 2 and 3

@@
-%\newpage
-
 \subsection{Specific Aim 2: Efficient high-order numerical methods for
@@
     \vspace{-20pt}
-    \caption{\label{fig:flow_map} \footnotesize A suspension of 3D
-    amphiphilic particles suspended in a solvent. The solvent satisfies
+    \caption{\label{fig:flow_map} \footnotesize The diagram depicts a collection of 3D
+    amphiphilic particles suspended in a solvent. The solvent velocity satisfies
     the Stokes equations, and the hydrophobic forces depend on the
@@
 Over the past decade, there has been an explosion of interest in
-small-scale processes that utilize capillary forces, van der Waals
-interactions, and thermal noise~\cite{Zhang2017}, to coordinate movement
-and bind nano-legos in a solvent~\cite{Pandey2011, Leong2007,
-Reynolds2019, Dasgupta2017, Siontorou2017}. Additionally, hydrodynamic
-interactions are central to fabricate for complex microscopic
-three-dimensional structures~\cite{Cho2010}. Hydrodynamic effects can
-not be ignored since the rates of biological functions like fusion,
-fission, and pore dynamics rely on viscous
+small-scale processes that utilize capillary forces and van der Waals
+interactions to coordinate movement
+and bind microscopic components in solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}.
+Additionally, hydrodynamic interactions are central to fabricating complex,
+three-dimensional microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010}.
+Hydrodynamic effects cannot
+be ignored since they, like the rates of biological functions like fusion,
+fission, and pore dynamics, determine rely on viscous
 dissipation~\cite{RYHAM20112929}.
@@
 Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
-equations for an incompressible viscous fluid, and these equations are
+equations for an incompressible, viscous fluid, and these equations are
 coupled to the screened-Laplace equation~\eqref{SL} through viscous and
@@
 discretizations when the boundary surfaces are irregular. Alternatively,
-since we are solving constant-coefficient linear elliptic PDEs, its
-solution can be represented with layer potentials
+since we are solving constant-coefficient linear elliptic
+partial differential equations (PDEs), their
+solutions can be represented with layer potentials
 \begin{align}
@@
 $\mathbf{x}_0 \in \partial\Omega$ with the limit of
-equation~\eqref{eq:LP} as $\mathbf{x}\rightarrow \mathbf{x}_0$, a BIE
-for the density function is formed.
+equation~\eqref{eq:LP} as $\mathbf{x}\rightarrow \mathbf{x}_0$, a
+boundary integral equation (BIE) for the density function is formed.
 
@@
 high-order or spectral accuracy is attainable with appropriate
-quadrature methods. In our previous work~\cite{Fu2018_SIAM} we
-demonstrate that BIEs are a powerful tool to simulate two-dimensional
+quadrature methods. PI RR and YNY's previous work~\cite{Fu2018_SIAM}
+demonstrated that BIEs are a powerful tool to simulate two-dimensional
 suspensions of amphiphilic particles. In addition to improving
-two-dimensional simulations, we will extend the results to three
-dimensions using a standard three-dimensional BIE formulation of the
+two-dimensional simulations, the present proposal extends the results to three
+dimensions using a three-dimensional BIE formulation of the
 screened Laplace equation~\cite{ying_2006} and a well-conditioned BIE
@@
 
-Significant challenges to solve BIEs include solving dense linear
+Significant challenges to solving BIEs include solving dense linear
 systems, developing preconditioning strategies, and developing
-quadrature methods for integrands that are nearly singular. These
+quadrature methods for nearly singular integrands. These
 challenges are described in \S\ref{subsec:NumericalIssues}. However,
@@
 (IFMM)~\cite{cou-pou-dar2017}. PI BQ used the IFMM to precondition
-Stokes equations~\cite{qua-cou-dar2018}, and a suite of other
+Stokes equations~\cite{qua-cou-dar2018}. A suite of other
 preconditioners including sparse approximate inverses~\cite{che2000} and
@@
   $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
-  $|\mathbf{x_0}| = 0.99$ and $\mathbf{y} \in \partial\Omega$, and
-  $\Omega$ is the unit circle. The trapezoid rule applied to the red
+  $|\mathbf{x_0}| = 0.99$, $\mathbf{y} \in \partial\Omega$, and
+  $\Omega$ is the unit disk. The trapezoid rule applied to the red
   integrand has large amounts of error, but the trapezoid rule is much
@@
   barycentric quadrature rule, the quadrature error applied to layer
-  potentials for the screen Laplace equation will be uniformly bounded
+  potentials for the screened Laplace equation will be uniformly bounded
   in $\Omega$.}}
@@
 particles, and this results in nearly-singular integrands. Quadrature
-methods for these integrands has received a lot of attention in two and
+methods for these integrands have received a lot of attention in two and
 three dimensions~\cite{alpert, kapur, sidi, duffy, bruno1, bruno2,
@@
 $\mathbf{y}$. The proposed method is demonstrated in
-Figure~\ref{fig:integrands} where the amplitude of the Fourier modes of
+Figure~\ref{fig:integrands}, where the amplitude of the Fourier modes of
 $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ are
@@
 particles is avoiding particle collision. The hydrophobic attraction
-potential drives the amphiphilic particles towards one another so to
-minimize exposure to the solvent, and this leads to physical contact in
-finite time. Such particle collisions in a dense rigid body suspension
-is a great challenge and can be a bottleneck in large-scale simulations.
+potential drives the amphiphilic particles towards one another and
+this leads to physical contact in
+finite time. Such particle collisions in a dense, rigid-body suspension
+are a great challenge and can be a bottleneck in large-scale simulations.
 We propose two algorithms to remedy this computational challenge:
@@
 PI BQ developed a high-order adaptive time stepping method for
-hydrodynamic suspensions~\cite{qua-bir2016} and it has served as a
+hydrodynamic suspensions~\cite{qua-bir2016}, and it has served as a
 robust method to simulate processes including mixing and adhesion in
 suspensions~\cite{qua-vee-you2019, kab-qua-bir2017}. The method uses
-a single-step high-order time stepping method and a computationally
+a single-step, high-order time stepping method and a computationally
 cheap estimate of the error. The proposed work will use a spectral
 deferred correction method~\cite{dut-gre-rok2000} since it iteratively
-applies a low-order single-step method to achieve high-order accuracy.
-To estimate the error, at each time step we will compute the total force
+applies a low-order, single-step method to achieve high-order accuracy.
+To estimate the error, at each time step, we will compute the total force
 and torque of the system which is computationally cheap and physically
@@
 %
-Our previous work avoids contact by including a Lennard-Jones body
-forces~\cite{Fu2018_SIAM}. Such a steep steric interaction at short
-ranges introduces numerical stiffness and limits the time step size. To
+Our previous work avoided particle contact through Lennard-Jones body
+forces~\cite{Fu2018_SIAM}. Such steep, short-range, steric interactions 
+introduce numerical stiffness and limit the time step size. To
 remove this stiffness, we propose a geometry-based contact
-method~\cite{har-pon-sor-zor2011}, and this method has been applied to
-vesicle suspensions~\cite{lu-rah-zor2017} and rigid body suspensions in
+method~\cite{har-pon-sor-zor2011}. This method has been applied to
+vesicle suspensions~\cite{lu-rah-zor2017} and to rigid body suspensions in
 two dimensions~\cite{bys-sha-qua2020} and three
@@
 \label{subsec:reciprocal}
-The force and torque formulas~\eqref{forceandtorque} require the
+The force and torque formulas~\eqref{forceandtorque} use the
 hydrophobic stress along the particle boundaries. Unfortunately,
@@
 boundaries (Figure~\ref{fig:bierror}). Therefore, it is useful to devise
-reciprocal identities for the force and torque on body $i$ that does not
+reciprocal identities for the force and torque on body $i$ that do not
 require integration along body $i$. One identity, that we have proved,
@@
 contact are implemented, we will embark on incorporating fluctuating
-hydrodynamics that are important even at scales of some amphiphilic
+hydrodynamics that are especially important at scales of amphiphilic
 particles. Bao et al.~\cite{Bao17,Bao18} developed two-dimensional BIE
 formulations for Brownian rigid bodies. To satisfy the covariance of the
-rigid body velocities, they use an ill-conditioned first-kind integral
+rigid body velocities, they use an ill-conditioned, first-kind integral
 equation method. The proposed work will consider a layer potential

### 2020-11-15 NSF2020/Description/newspecificaim3.tex
fixed typos in SA 2 and 3

@@
 and~\eqref{eq:stokes} is nontrivial, and we will develop efficient,
-robust, high-order in time and space algorithms suited to the problem.
-The challenges are: {\bf (1)} The equations express a two-way coupling
+robust, high-order-in-time and -space algorithms suited to the problem.
+There are a few challenges. {\bf (1)} The equations express a two-way coupling
 since the flow changes the position of the suspended particles,
-and in return the geometry-dependent hydrophobic stresses impart a force
+and in return, the geometry-dependent hydrophobic stresses impart a force
 on the flow. {\bf (2)} The inputs to the Stokes equations are particle
@@
 come into close contact. As a result, an exceptional spatial accuracy is
-required to resolve the fields between adjacent particles. Finally, the
-physically relevant elastic properties of bilayer become apparent at
+required to resolve the fields between adjacent particles. Furthermore, 
+physically relevant elastic properties of bilayers become apparent at
 large length scales and for large particle-numbers, which increases the
@@
 \label{PowerMiranda}
-  {\bf u} = {\bf u}_{\infty} + K\boldsymbol{\eta} + 
+  {\bf u} = {\bf u}_{\infty} + L\boldsymbol{\eta} + 
     \sum_{i=1}^N \left(S(\cdot, {\bf a}_i) {\bf F}_i + 
@@
 where $S$ and $R$ are stokeslets and rotlets supported at the respective
-particle centers~\cite{leal_2007} and $K\boldsymbol{\eta}$ is a layer
+particle centers~\cite{leal_2007} and $L\boldsymbol{\eta}$ is a layer
 potential for the unknown density function $\boldsymbol{\eta}$. With the
@@
 hydrodynamic equations including the far-field condition. The rigid
-motion conditions follow by requiring the viscous stress vanishes across
+body conditions follow by requiring the viscous stresses to vanish across
 the particle boundaries.
@@
 dynamics~\cite{torres-sanchez_millan_arroyo_2019,mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}.
-Some preliminary results are in \S \ref{sec:preliminary_work}. 
+\S \ref{sec:preliminary_work} contains our preliminary results.
 %

### 2020-11-15 NSF2020/Description/preliminarywork.tex
fixed typos in SA 2 and 3

@@
 model, it is a consequence of monolayer independence. For large shear
-rates, viscous forces exceed the hydrophobic attraction and the vesicle
-ruptures; the flow carries away segmented membrane patches (Figure
-\ref{fig:flow_rupture}).
+rates, viscous forces exceed the hydrophobic attraction to the point that
+the vesicle ruptures. The flow carries away segmented membrane patches
+(Figure \ref{fig:flow_rupture}).
 

### 2020-11-15 NSF2020/Description/newspecificaim2.tex
fixed typos in SA 2 and 3

@@
 Hydrodynamic effects cannot
-be ignored since they, like the rates of biological functions like fusion,
-fission, and pore dynamics, determine rely on viscous
-dissipation~\cite{RYHAM20112929}.
+be ignored since they, like for the rates of biological functions 
+like pore dynamics~\cite{RYHAM20112929}, set the rate of dissipation.
 %

### 2020-11-15 NSF2020/Description/broaderimpacts.tex
RJR educational impact

@@
-\section{Broader Impacts of the Proposed Work}
+\section{Broader Impacts}
 \label{sec:BroaderImpacts}
@@
 \label{subsec:Educational_plans}
-The proposed research will have an immediate impact on undergraduate and
-graduate education. At the undergraduate level, the project will include
-and support undergraduate researchers from Fordham University. The
-supported summer researchers will gain valuable first-hand
-interdisciplinary experience in mathematical modeling and computation.
-We will incorporate research into teaching, especially in differential
-equation and programming courses. PI YNY will work on simple modeling of
-self-assembly problems with both undergraduate and high school students
-from Newark Science Park High School. PI YNY has a track record of
-working with local high school students for their research projects
-before they apply for colleges. PI BQ will work with undergraduate and
-high school students through the Undergraduate Research Opportunity
-Program and Young Scholar's Program as he has done in the past.
+The topics of this proposal have application in robotics, machine learning,
+and engineering. To foster training in mathematical sciences, the project
+will include undergraduate researchers (URs). The proposal supports one UR
+per year from the lead institution, and will include one or two additional
+UR from actively supported in-house programs
 
-Over the past eight years, PI RR has included many undergraduates in the
-execution of research initiatives and coauthoring publications. He has a
-track record for supporting underrepresented groups, being called on by
-the Collegiate Science and Technology Entry Program (CSTEP) to make
-opportunities for promising students, for example. He has mentored two
-Clare Boothe Luce Scholars, one a U.S.~Marine Corp veteran, and a high
-school student in the NYU GSTEM program.
+The URs will work as a team for eight weeks in the summer. They will
+collaborate directly with the senior personnel, have tutorials in topics
+such as numerical quadrature and integral equations, and train in
+mathematical writing and presentation. To maximize vertical integration,
+and to the extent possible, the PIs and personnel will travel to 
+New York for one or two weeks in the summers. Fordham University 
+recently constructed a seminar/collaboration space specifically
+for collaborative research, and URs will base there activitied from here.
 
-The PIs will capitalize on the synergy between both FSU's doctoral
-program in Scientific Computing, NJIT's doctoral program in Mathematical
-Sciences, and Fordham's undergraduate focus in the Department of
-Mathematics. Promising, young undergraduate scientists from the Bronx
-community will find a natural pipeline into graduate studies by working
-directly or indirectly on this project. At the graduate-level, PI YNY
-expects to train and support a PhD student for two more years. PI BQ
-will advise a postdoctoral fellow for two years. The PIs will foster
-vertical integration between the senior personnel, their collaborators,
-postdocs, doctoral, and Bachelor students, enhancing the learning
-environment.
+As a requirement, the URs will write quality summary reports and give
+presentations at the their respective research symposia. The work will be
+considered a success if the URs also participate in a national conference.
+The best possible outcome is if URs coauthor a publication.
+
+There are two ways the proposal will meaningfully engage the community.
+To be more impactful, students from the Bronx High School of Science
+(PI RR) and Newark Science Park High School (PI YNY) will be encouraged
+to join the research team. PI BQ will work with undergraduate and high
+school students through the Undergraduate Research Opportunity Program
+and Young Scholar's Program, as he has done in the past. Secondly, the
+PIs will prioritize students who would most benefit from the grant activity.
+We specifically target students whose socio-economic background prevents
+them from participating in out-of-state research experiences.
+
+Innovations in teaching: we will create several modules to include
+in our courses. These modules will introduce topics from numerical linear
+algebra and optimization, and be based on the ideas of the proposal.
+Additionally, we and our UR collaborators will give remote, guest lectures
+in each others' courses and undergraduate seminars.
+
+%The proposed research will have an immediate impact on undergraduate and
+%graduate education. At the undergraduate level, the project will include
+%and support undergraduate researchers from Fordham University. The
+%supported summer researchers will gain valuable first-hand
+%interdisciplinary experience in mathematical modeling and computation.
+%We will incorporate research into teaching, especially in differential
+%equation and programming courses. PI YNY will work on simple modeling of
+%self-assembly problems with both undergraduate and high school students
+%from Newark Science Park High School. PI YNY has a track record of
+%working with local high school students for their research projects
+%before they apply for colleges. PI BQ will work with undergraduate and
+%high school students through the Undergraduate Research Opportunity
+%Program and Young Scholar's Program as he has done in the past.
+
+%Over the past eight years, PI RR has included many undergraduates in the
+%execution of research initiatives and coauthoring publications. He has a
+%track record for supporting underrepresented groups, being called on by
+%the Collegiate Science and Technology Entry Program (CSTEP) to make
+%opportunities for promising students, for example. He has mentored two
+%Clare Boothe Luce Scholars, one a U.S.~Marine Corp veteran, and a high
+%school student in the NYU GSTEM program.
+
+%The PIs will capitalize on the synergy between both FSU's doctoral
+%program in Scientific Computing, NJIT's doctoral program in Mathematical
+%Sciences, and Fordham's undergraduate focus in the Department of
+%Mathematics. Promising, young undergraduate scientists from the Bronx
+%community will find a natural pipeline into graduate studies by working
+%directly or indirectly on this project. At the graduate-level, PI YNY
+%expects to train and support a PhD student for two more years. PI BQ
+%will advise a postdoctoral fellow for two years. The PIs will foster
+%vertical integration between the senior personnel, their collaborators,
+%postdocs, doctoral, and Bachelor students, enhancing the learning
+%environment.
 

### 2020-11-15 NSF2020/Description/newspecificaim2.tex
RJR educational impact
4.2.1 edited

@@
 large-scale simulations}
-\label{subsec:specific_aim_2}
-%\begin{figure}[h]
-\begin{wrapfigure}[13]{r}{0.61\textwidth}
-  \centering{\includegraphics[width=0.61\textwidth]{Figures/domain.pdf}}
-    \vspace{-20pt}
-    \caption{\label{fig:flow_map} \footnotesize The diagram depicts a collection of 3D
-    amphiphilic particles suspended in a solvent. The solvent velocity satisfies
-    the Stokes equations, and the hydrophobic forces depend on the
-    solvent activity that satisfies the screened Laplace equation. The
-    geometry is updated by solving the mobility problem.} 
-\end{wrapfigure}
-%\end{figure}
 % ----------------------------------------------------------------------
@@
 
+\label{subsec:specific_aim_2}
+%\begin{figure}[h]
+\begin{wrapfigure}[14]{r}{0.61\textwidth}
+  \centering{\includegraphics[width=0.61\textwidth]{Figures/domain.pdf}}
+    \vspace{-20pt}
+    \caption{\label{fig:flow_map} \footnotesize The diagram depicts a collection of 3D
+    amphiphilic particles suspended in a solvent. The solvent velocity satisfies
+    the Stokes equations, and the hydrophobic forces depend on the
+    solvent activity that satisfies the screened Laplace equation. The
+    geometry is updated by solving the mobility problem.} 
+\end{wrapfigure}
+%\end{figure}
 The HAP model requires solving exterior Dirichlet problems for the
@@
 
+%
+\begin{wrapfigure}[21]{r}{2.5in}
+%\vspace*{+15pt}
+\centerline{\includegraphics[width=2.5in]{figures/integrands}}
+\vspace*{-13pt}
+  \caption{{\footnotesize The Fourier modes of
+  $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
+  $|\mathbf{x_0}| = 0.99$, $\mathbf{y} \in \partial\Omega$, and
+  $\Omega$ is the unit disk. The trapezoid rule applied to the red
+  integrand has large amounts of error, but the trapezoid rule is much
+  more accurate when applied to the blue integrand. Since the difference
+  between the red and blue curves can be accurately computed with the
+  barycentric quadrature rule, the quadrature error applied to layer
+  potentials for the screened Laplace equation will be uniformly bounded
+  in $\Omega$.}}
+\label{fig:integrands}
+\end{wrapfigure}
 Discretizations of carefully chosen BIEs can be solved with a
@@
 
-%
-\begin{wrapfigure}[21]{r}{2.5in}
-%\vspace*{+15pt}
-\centerline{\includegraphics[width=2.5in]{figures/integrands}}
-\vspace*{-13pt}
-  \caption{{\footnotesize The Fourier modes of
-  $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
-  $|\mathbf{x_0}| = 0.99$, $\mathbf{y} \in \partial\Omega$, and
-  $\Omega$ is the unit disk. The trapezoid rule applied to the red
-  integrand has large amounts of error, but the trapezoid rule is much
-  more accurate when applied to the blue integrand. Since the difference
-  between the red and blue curves can be accurately computed with the
-  barycentric quadrature rule, the quadrature error applied to layer
-  potentials for the screened Laplace equation will be uniformly bounded
-  in $\Omega$.}}
-\label{fig:integrands}
-\end{wrapfigure}
 Nearly touching bodies is ubiquitous in self-assembly of amphiphilic

### 2020-11-15 NSF2020/Description/specificaim1_ver2.tex
removed last instance of HARP
4.2.1 edited

@@
 %\end{center}
-\subsubsection{Simulations of the HARP model to estimate elastic moduli and energy}
+\subsubsection{Simulations of the HAP model to estimate elastic moduli
+and energy}
 %To characterize material properties of a bilayer, we compare the energies and forces generated by
@@
 %
+\subsubsection{Existence of minimizers}
+The HK functional \eqref{ansatz3} has had tremendous impact in understanding
+biological function, but has received little attention in terms of mathematical
+analysis. In the calculus of variations, the principal question is whether a
+minimizer of an energy functional exists. But in the case of \eqref{ansatz3},
+this answer is presently unknown. With regard to the simpler, Canham-Helfrich
+energy, \cite{Simon1993} proved the existence of minimizing surfaces without boundary, 
+and \cite{doi:10.1137/18M1195851} proved the well-posedness of a spatially periodic,
+time-dependent elastic interface problem. An analytical challenge 
+for the HK functional \eqref{ansatz3} is that coupling to a director field makes it
+possible to have bounded energy monolayers with corners, and such
+pathological examples must be ruled out before carrying over the arguments
+for the Canham-Helfrich functional to the present setting.
+
 \subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
-The HAP energy converges to the surface energy in the limit of vanishing screening length~\cite{Shibata2004}.
-Also, the boundary layers of the solutions to the screen Laplace equation
-converge to area measures supported on the particle boundaries \cite{Lee2018, Lin2015, Shibata2004}.
-These phenomena are analogous to the sharp interface limit in the phase-field functional,
-and motivate developing the mathematical connections between the HAP energy and
-the energy functionals used in the gradient theory of phase transitions.
-formulation~\cite{Modica87, MODICA1987487, LuMo89}.
-PI RR has worked on phase field approximations of membrane bending
-energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
-equation~\cite{1531-3492_2006_2_357, Lee2018}.
-The screened-Laplace equations~\eqref{SL} is the linearization of the Poisson-Boltzmann equation.
-One set of questions is to establish the HAP convergence rate as a
-function of particle geometry~\cite{LuMo89}, which can be used as a
-benchmark for numerical validation.
-Ultimately, we will be able to address the so-called $\Gamma$-convergence of energy minimizing
-particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 
+Our long term goal is to develop tools that can explain functionals like
+\eqref{ansatz3} from first principles in terms of HAP. The papers
+\cite{doi:10.1063/5.0009734,Seguin2012,Seguin2014} give statistical
+mechanical/mean field derivations of the Canham-Helfrich energy from a
+pair-potential for rod-like molecules, but do not include tilt, which is an
+indispensable deformation at biological scales. To make progress, we must
+first understand how the HAP functional behaves under various limits.
+
+We first consider HAP in the limit of vanishing screening length.
+As a concrete, model problem we consider a collection of colloidal polyhedral
+where the binding energy of this system can be described by a
+discrete, lower semicontinuous functional $\Phi_0$ whose value is the total
+surface area of the polyhedra minus two times the area of any overlapping faces.
+We conjecture that the $\Phi$ energy $\Gamma$-converges to $\Phi_0$
+\cite{Mugnai2013}, meaning that any cluster points of minimizers of $\Phi$
+converge to a minimum of $\Phi_0$ in the limit $\rho \to 0$. 
+To address this conjecture, we employ boundary layer analysis for the screened
+Laplace equation \cite{Lee2018, Lin2015, Shibata2004,1531-3492_2006_2_357, Lee2018}.
+The technique of $\Gamma$-convergence is a powerful tool for numerical approximations
+and with it we can help explain unexcepted phenomena like hierarchical self-assembly \cite{Luo2019}.
+
+%The HAP energy converges to the surface energy in the limit of vanishing screening length~\cite{Shibata2004}.
+%Also, the boundary layers of the solutions to the screen Laplace equation
+%converge to area measures supported on the particle boundaries \cite{Lee2018, Lin2015, Shibata2004}.
+%These phenomena are analogous to the sharp interface limit in the phase-field functional,
+%and motivate developing the mathematical connections between the HAP energy and
+%the energy functionals used in the gradient theory of phase transitions.
+%formulation~\cite{Modica87, MODICA1987487, LuMo89}.
+%PI RR has worked on phase field approximations of membrane bending
+%energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
+%equation~\cite{1531-3492_2006_2_357, Lee2018}.
+%The screened-Laplace equations~\eqref{SL} is the linearization of the Poisson-Boltzmann equation.
+%One set of questions is to establish the HAP convergence rate as a
+%function of particle geometry~\cite{LuMo89}, which can be used as a
+%benchmark for numerical validation.
+%Ultimately, we will be able to address the so-called $\Gamma$-convergence of energy minimizing
+%particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 
 %The phase field functional approximates the perimeter of sublevel sets

### 2020-11-16 NSF2020/Description/background.tex
yny Nov 15

@@
 amphiphilic particles interacting via hydrophobic forces
-in a solvent. Amphiphilic particles (such as lipid molecules) possess
+in solvent. Amphiphilic particles (such as lipid molecules) possess
 both hydrophobic and hydrophilic structures. In a viscous solvent they
@@
 elongated lipid by elliptical particles with the hydrophobic label
-defined along the ellipse's axis. Under the hydrophobic force, with
+defined along the ellipse's axis. 
+\begin{wrapfigure}[14]{l}{0.35\textwidth}
+\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
+  \vspace{-8pt}
+  \caption{\label{fig:demixing} \footnotesize An initial assembly of
+  small and large particles spontaneously segregates into two smaller
+  bodies.}
+\end{wrapfigure}
+Under the hydrophobic force, with
 excluded volume, the Janus particles spontaneously merge and realign
@@
 and does not require artificial inputs.
+%
 
+%
 It is worth emphasizing that the HAP model uses only a few parameters:
@@
 
-As a proof of concept, our work has already tested for elastic energies
-for bending, stretching, and tilt of the bilayer assembly. The elastic
-coefficients derived from the HAP simulations show strikingly positive
-agreement with experimentally determined values~\cite{Fu2018_SIAM}.
-Encouraged by these results and the hydrodynamic simulations of
-bilayer assembly, the PIs propose to extend the HAP model to make direct
-comparisons with experimental results \S\ref{subsec:specific_aim_1} and to
-establish that the HAP model has the capability to model
-flow phenomena across length scales and time scales
-\S\ref{subsec:specific_aim_2} using efficient, high-order numerical
-methods \S\ref{subsec:specific_aim_3}.
+%As a proof of concept, our work has already tested for elastic energies
+%for bending, stretching, and tilt of the bilayer assembly. The elastic
+%coefficients derived from the HAP simulations show strikingly positive
+%agreement with experimentally determined values~\cite{Fu2018_SIAM}.
+%Encouraged by these results and the hydrodynamic simulations of
+%bilayer assembly, the PIs propose to extend the HAP model to make direct
+%comparisons with experimental results \S\ref{subsec:specific_aim_1} and to
+%establish that the HAP model has the capability to model
+%flow phenomena across length scales and time scales
+%\S\ref{subsec:specific_aim_2} using efficient, high-order numerical
+%methods \S\ref{subsec:specific_aim_3}.
 
-\begin{wrapfigure}[14]{l}{0.35\textwidth}
-\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
-  \vspace{-8pt}
-  \caption{\label{fig:demixing} \footnotesize An initial assembly of
-  small and large particles spontaneously segregates into two smaller
-  bodies.}
-\end{wrapfigure}
+%\begin{wrapfigure}[14]{l}{0.35\textwidth}
+%\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
+%  \vspace{-8pt}
+%  \caption{\label{fig:demixing} \footnotesize An initial assembly of
+%  small and large particles spontaneously segregates into two smaller
+%  bodies.}
+%\end{wrapfigure}
 Over the past decades, researchers have used a number of mathematical

### 2020-11-16 NSF2020/Description/DataManagement.tex
yny data management

@@
 project}
-{\bf PI Ryham}: The following summarizes the type of analytical data to
-be produced: \todo[inline]{Rolf to fill in}
+{\bf PI Ryham}:
+The following summarizes the type of numerical data to
+be produced:
+(i) Matlab codes for running simulations and
+processing figures,
+(ii) Gnuplot code for creating manuscript figures, 
+(iii) C++ code for large-scale simulations, and 
+(iv) and ASCII files of simulation outputs. The estimated size of these
+data will be under 1 TB for the duration of the project.
 
@@
 osmophoresis. The estimated size of all the data is approximately 200 GB
-per year. \todo[inline]{Yuan to update. This is what was in the CBET
-proposal}
+per year. 
+%\todo[inline]{Yuan to update. This is what was in the CBET proposal}
 

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
RJR--got to run; tornado warning

@@
 recently constructed a seminar/collaboration space specifically
-for collaborative research, and URs will base there activitied from here.
+for collaborative research, and the URs will office space with desks
+there.
 

### 2020-11-16 NSF2020/Description/specificaim1_ver2.tex

@@
 %
-\subsubsection{Existence of minimizers}
+\subsubsection{Analysis on the HAP model in terms of the HK functional}
 The HK functional \eqref{ansatz3} has had tremendous impact in understanding
-biological function, but has received little attention in terms of mathematical
+biological membranes, but has received little attention in terms of mathematical
 analysis. In the calculus of variations, the principal question is whether a
@@
 
-\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
-Our long term goal is to develop tools that can explain functionals like
+%\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
+Our goal here is to develop tools that can explain functionals like
 \eqref{ansatz3} from first principles in terms of HAP. The papers

### 2020-11-16 NSF2020/Description/preliminarywork.tex
yny Nov 15
yny Nov15b

@@
-\begin{wraptable}[8]{r}{0.55\textwidth}
+\vspace{-0.1cm}
+\begin{wraptable}[8]{r}{0.53\textwidth}
+\vspace{-0.1cm}
 \centering{
@@
 %
+%
 %The HAP project was initiated in 2017 by PI RR and YNY. The lead author
@@
 %
-\begin{wraptable}[11]{l}{0.42\textwidth}
-\centering{
-  \begin{tabular}{|l|l|l|l|}
-    $n$   & (rel.~err.)$_F$
-    &  (rel.~err.)$_G$ \\
-    \hline
-% 32   &   4.07466     &   1.56437\\
-% 64   &   0.24664     &   0.03476\\
-% 128  &   0.00063     &   0.00006\\
-  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
-  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
-  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
-  \end{tabular}}
-\vspace{-5pt}
-\caption{\label{tab:spectral_force} 
-\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
-  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
-  and (rel.~err.)$_G = \max_{i}
-  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
-  for force and torque respectively as a function of number of grid
-  points $n$ per particle.  The data is for $N = 5$ particles; two of
-  the particles are nearly touching at a distance 1\% of particle
-  diameter.} 
-\end{wraptable}
+%\begin{wraptable}[11]{l}{0.43\textwidth}
+%\centering{
+%  \begin{tabular}{|l|l|l|l|}
+%    $n$   & (rel.~err.)$_F$
+%    &  (rel.~err.)$_G$ \\
+%    \hline
+%% 32   &   4.07466     &   1.56437\\
+%% 64   &   0.24664     &   0.03476\\
+%% 128  &   0.00063     &   0.00006\\
+%  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
+%  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
+%  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
+%  \end{tabular}}
+%\vspace{-5pt}
+%\caption{\label{tab:spectral_force} 
+%\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
+%  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
+%  and (rel.~err.)$_G = \max_{i}
+%  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
+%  for force and torque respectively as a function of number of grid
+%  points $n$ per particle.  The data is for $N = 5$ particles; two of
+%  the particles are nearly touching at a distance 1\% of particle
+%  diameter.} 
+%\end{wraptable}
 The results are summarized in \cite{Fu2018_SIAM}, where
@@
 
+\begin{wraptable}[11]{l}{0.43\textwidth}
+\centering{
+  \begin{tabular}{|l|l|l|l|}
+    $n$   & (rel.~err.)$_F$
+    &  (rel.~err.)$_G$ \\
+    \hline
+% 32   &   4.07466     &   1.56437\\
+% 64   &   0.24664     &   0.03476\\
+% 128  &   0.00063     &   0.00006\\
+  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
+  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
+  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
+  \end{tabular}}
+\vspace{-5pt}
+\caption{\label{tab:spectral_force} 
+\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
+  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
+  and (rel.~err.)$_G = \max_{i}
+  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
+  for force and torque respectively as a function of number of grid
+  points $n$ per particle.  The data is for $N = 5$ particles; two of
+  the particles are nearly touching at a distance 1\% of particle
+  diameter.} 
+\end{wraptable}
 PIs BQ, RR and YNY initiated a collaboration in Summer 2020 to
@@
 torque (Table~\ref{tab:spectral_force}).
+
 \begin{wrapfigure}[]{r}{0.5\textwidth}

### 2020-11-16 NSF2020/Description/specificaim1_ver2.tex

@@
 time-dependent elastic interface problem. An analytical challenge 
-for the HK functional \eqref{ansatz3} is that coupling to a director field makes it
+for the HK functional \eqref{ansatz3} is that surface-director coupling makes it
 possible to have bounded energy monolayers with corners, and such
@@
 The technique of $\Gamma$-convergence is a powerful tool for numerical approximations
-and with it we can help explain unexcepted phenomena like hierarchical self-assembly \cite{Luo2019}.
+and with it we can help explain unexcepted phenomena like hierarchical self-assembly in
+colloidal systems \cite{Luo2019}.
 

### 2020-11-16 NSF2020/Description/preliminarywork.tex
yny Nov15c
RJR

@@
   \vspace{-8pt}
-\caption{\label{tab:moduli} \footnotesize Comparision of values elastic
-  moduli from the experimental literature and values derived by HAP
+\caption{\label{tab:moduli} \footnotesize Comparison of values of elastic
+  moduli from the experimental literature and derived by HAP
   simulation.} 
@@
 membranes~\cite{Eriksson1989, Lin2005, Parsegian, Israelachvili80}),
-particle diameter 2.0 nm (the physical monolayer thickness, 2.0 nm~\cite{Boal}),
-and interfacial tension $\gamma = 4$ pN nm$^{-1}$ based on
+particle diameter $\delta = 2.0$ nm (the physical monolayer thickness~\cite{Boal}),
+and interfacial tension $\gamma = 4$ pN nm$^{-1}$ (based on
 measurements for single-component bilayer lipid
-membranes~\cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson2016}.
+membranes~\cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson2016}).
 
@@
   \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
-  for force and torque respectively as a function of number of grid
+  for force and torque, respectively, as a function of number of grid
   points $n$ per particle. The data is for $N = 5$ particles; two of
@@
 \end{wraptable}
-PIs BQ, RR and YNY initiated a collaboration in Summer 2020 to
+PIs BQ, RR, and YNY initiated a collaboration in Summer 2020 to
 develop the hydrodynamic model of \S\ref{subsec:specific_aim_3}.  To
@@
   \caption{\label{fig:tank_treading} \footnotesize
-    Panel A: A two-dimensional
-    particle-based vesicle in a shear flow (arrows); $\mu  = 1$ mPa s,
+    Panel A: A two-dimensional,
+    particle-based vesicle in a shear flow (arrows); $\mu  = 1$ mPa s and
     $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. The color coding is for HAP. Panel B: The
-    mean angular velocities for the outer leaflet and the inner
+    mean angular velocities for the outer and the inner leaflets, 
     respectively. Panel C: The trajectory of the particle
@@
 mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}. The basic
-pattern is that the vesicle bilayer approaches a steady tank-treading
+pattern is that of a vesicle bilayer approaching a steady, tank-treading
 ellipse (Figure~\ref{fig:tank_treading}C). We analyzed the simulation
@@
 tank-treading~\cite{Finken2008, PhysRevLett.106.158103}.
-Jeffrey's equation predicts a
-tank-treading frequency $-\dot{\gamma}/2$ (dashed line in
-Figure~\ref{fig:tank_treading}B). In the particle simulation, the
-tank-treading frequency corresponds to the mean of the particle angular
-velocities, and these approach a value within 7\% of the theoretical
-prediction (dotted and solid curves in Figure~\ref{fig:tank_treading}B).
-In the low viscosity-contrast regime of our simulation, Jeffrey's
-equation predicts a decrease in the ellipse's inclination angle $\Theta$
-and our particle-based simulation follows this prediction
-(Figure~\ref{fig:tank_treading}D), albeit with some higher frequency oscillation
+Jeffrey's equation predicts a tank-treading frequency $-\dot{\gamma}/2$ (dashed line in
+Figure~\ref{fig:tank_treading}B). In the particle simulation, we measured
+a tank-treading frequency as the mean, particle angular
+velocities. The measured steady-state frequencies were within 7\% of the predicted 
+frequency (dotted and solid curves in Figure~\ref{fig:tank_treading}B).
+The inclincation angle of the particle-based simulation also
+follows the inclination angle $\Theta$ predicted by Jeffrey's
+equation (Figure~\ref{fig:tank_treading}D), albeit with some higher frequency oscillation
 coming from particle reorganization.
@@
 Analyzing for any underlying constitutive laws, the particles reorganize
-so that there is an initial increase and then plateauing of vesicle
+so that there is an initial increase and then plateau in vesicle
 circumference. As is the case with real lipid bilayer membranes, the
 particle collection permits a small amount of stretching. The
-theoretical calculations give an increase of length by 3.6\% and this amount
+theoretical calculations give an increase of length by 3.6\%, and this amount
 agrees with our measured increase in length. The simulations also
@@
 rates, viscous forces exceed the hydrophobic attraction to the point that
-the vesicle ruptures. The flow carries away segmented membrane patches
+the vesicle ruptures, and the flow carries away segmented membrane patches
 (Figure \ref{fig:flow_rupture}).
@@
 In conclusion, the HAP model accurately mimics the behavior of continuous
-membranes, while at the same time capturing the
+membranes while at the same time capturing the
 reconnection during the topological change of 

### 2020-11-16 NSF2020/Description/background.tex

@@
 {\em Rolf Ryham (lead PI, Fordham University), Bryan Quaife (PI,
-Florida State University), and Young-Nan Young (PI, New Jersey Institute of Technology)}
+Florida State University), and Yuan-Nan Young (PI, New Jersey Institute of Technology)}
 \section{Background}

### 2020-11-16 NSF2020/Description/newspecificaim3.tex
RJR

@@
 \subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
-Using flicker spectroscopy of the shape fluctuations of a giant
-unilamellar vesicle (GUV), the bending rigidity is determined as a
-function of lipid composition from 0 to 100 mol $\%$ of charged lipids
-in recent experiments~\cite{FaizEtAl2019_SoftMatt}---membrane bending
-rigidity increases with lipid surface charge, while decreases with salt
-in the bulk due to the screening of the lipid surface charge. This
+In recent experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending rigidity
+was determined as a function of lipid composition from 0 to 100 mol $\%$ of
+charged lipids using flicker spectroscopy of the shape fluctuations of a giant
+unilamellar vesicle (GUV).
+%the bending rigidity is determined as a
+%function of lipid composition from 0 to 100 mol $\%$ of charged lipids
+%in recent experiments~\cite{FaizEtAl2019_SoftMatt}---
+Membrane bending rigidity increases with increasing lipid surface charge,
+while decreases with increasing salt concentration in the bulk solution
+due to the screening of the lipid surface charge. This
 agrees with several theoretical models~\cite{Kralchevsky1996_JCIS,
@@
 controversy of the HK elastic energy form (see
-\S\ref{subsec:specific_aim_1}) would be worse in the presence of
+\S\ref{subsec:specific_aim_1}) would worsen in the presence of
 electrostatic interactions and electrokinetics. The PIs will extend
@@
 calculate elastic moduli as outlined in \S\ref{subsec:specific_aim_1}.
-Results from these proposed calculations provide further comparisons and
+Results from these proposed calculations will provide further comparisons and
 validations of the HAP model against the continuum mechanics.
@@
 using both asymptotic analysis~\cite{Nganguia2013_PRE, Young2014_JFM,
-Young2015_PoF} and numerical simulations~\cite{Nganguia2015_CiCP}, and
-will work with both PI RR and BQ to extend the HAP model to study the
+Young2015_PoF} and numerical simulations~\cite{Nganguia2015_CiCP} and
+will work with both PIs RR and BQ to extend the HAP model to study the
 electromechanical effects on the assembly of amphiphile. Results from

### 2020-11-16 NSF2020/Description/background.tex
tidied it up; removed hyperlinks + pagination

@@
 information about the quality of the solvent~\cite{Israelachvili1954,
-Discher2002}. In practice, we integrate~\eqref{HAP} by parts and
+Discher2002}.
+In the figures throughout the proposal, red is for $u = 1$ and blue is for $u = 0$.
+In practice, we integrate~\eqref{HAP} by parts and
 use~\eqref{SL} to obtain
@@
 
+\begin{wrapfigure}[14]{l}{0.35\textwidth}
+\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
+  \vspace{-8pt}
+  \caption{\label{fig:demixing} \footnotesize An initial assembly of
+  small and large particles spontaneously segregates into two smaller
+  bodies.}
+\end{wrapfigure}
 The HAP formulation is, to our knowledge, the first demonstration of
@@
 are typically spherical with a biphasic material label on either
-hemisphere, endowing the particle with a directional order. We model an
+hemisphere, endowing the particle with
+a directional order. We model an
 elongated lipid by elliptical particles with the hydrophobic label
 defined along the ellipse's axis. 
-\begin{wrapfigure}[14]{l}{0.35\textwidth}
-\centerline{\includegraphics[width=0.35\textwidth]{figures/PW_fig2.pdf}}
-  \vspace{-8pt}
-  \caption{\label{fig:demixing} \footnotesize An initial assembly of
-  small and large particles spontaneously segregates into two smaller
-  bodies.}
-\end{wrapfigure}
 Under the hydrophobic force, with
@@
 shape. For example, an elastic modulus for stretching a vesicle from
-micropipette manipulation directly calibrates our interfacial tension
+micropipette manipulation calibrates our interfacial tension
 parameter. This is in direct contrast with pair-potential-based

### 2020-11-16 NSF2020/Description/preliminarywork.tex
tidied it up; removed hyperlinks + pagination

@@
 \vspace{-0.1cm}
-\begin{wraptable}[8]{r}{0.53\textwidth}
+\begin{wraptable}[8]{r}{0.55\textwidth}
 \vspace{-0.1cm}
@@
 hydrophobic attraction between surfactant-coated
-membranes~\cite{Eriksson1989, Lin2005, Parsegian, Israelachvili80}),
+surfaces~\cite{Eriksson1989, Lin2005, Parsegian, Israelachvili80}),
 particle diameter $\delta = 2.0$ nm (the physical monolayer thickness~\cite{Boal}),
@@
 %\end{wrapfigure}
-The paper \cite{Fu2018_SIAM} considered three types of simulations. The first measured bending by
-loading a partially clamped planar bilayer. The second used a harmonic
-bond to dilate a circular bilayer. The third measured tilt using a decay
-equation from~\cite{KUZMIN2005}. These simulations isolated three of the
-five deformations of~\eqref{ansatz3}, enabling us to read off elastic
-moduli from simulation data. The results agreed remarkably well with the
-values reported in the experimental literature (Table~\ref{tab:moduli}).
-The agreement is underscored by the fact that the two main HAP
-parameters, $\gamma$ and $\rho$, were assigned physical values from the
-outset rather than being tuned to fit data.
-
-\begin{wraptable}[11]{l}{0.43\textwidth}
+\begin{wraptable}[10]{l}{0.43\textwidth}
 \centering{
@@
 \end{wraptable}
-PIs BQ, RR, and YNY initiated a collaboration in Summer 2020 to
+The paper \cite{Fu2018_SIAM} considered three types of simulations. The first measured bending by
+loading a partially clamped planar bilayer. The second used a harmonic
+bond to dilate a circular bilayer. The third measured tilt using a decay
+equation from~\cite{KUZMIN2005}. These simulations isolated three of the
+five deformations of~\eqref{ansatz3}, enabling us to read off elastic
+moduli from simulation data. The results agreed remarkably well with the
+values reported in the experimental literature (Table~\ref{tab:moduli}).
+The agreement is underscored by the fact that the two main HAP
+parameters, $\gamma$ and $\rho$, were assigned physical values from the
+outset rather than being tuned to fit data.
+
+PIs BQ, RR, and YNY initiated a collaboration in summer 2020 to
 develop the hydrodynamic model of \S\ref{subsec:specific_aim_3}.  To
@@
 
-\begin{wrapfigure}[]{r}{0.5\textwidth}
+\begin{wrapfigure}[22]{r}{0.5\textwidth}
+\vspace{-5pt}
   \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
@@
     particle-based vesicle in a shear flow (arrows); $\mu  = 1$ mPa s and
-    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. The color coding is for HAP. Panel B: The
-    mean angular velocities for the outer and the inner leaflets, 
-    respectively. Panel C: The trajectory of the particle
+    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. (Compare with \cite{Brandner2019}).
+    Panel B: Angular velocities for the outer and the inner leaflets.
+    Panel C: The trajectory of the particle
     centers forms two ellipses with well-defined inclination angle
@@
 \end{wrapfigure}
-
 We have simulated two-dimensional vesicles in shear flow
@@
 Figure~\ref{fig:tank_treading}B). In the particle simulation, we measured
-a tank-treading frequency as the mean, particle angular
-velocities. The measured steady-state frequencies were within 7\% of the predicted 
+a tank-treading frequency as the mean of the particle angular
+velocities. The measured steady-state freque ncies were within 7\% of the predicted 
 frequency (dotted and solid curves in Figure~\ref{fig:tank_treading}B).
@@
 follows the inclination angle $\Theta$ predicted by Jeffrey's
-equation (Figure~\ref{fig:tank_treading}D), albeit with some higher frequency oscillation
+equation (Figure~\ref{fig:tank_treading}D), albeit with higher frequency oscillation
 coming from particle reorganization.
@@
 particle collection permits a small amount of stretching. The
-theoretical calculations give an increase of length by 3.6\%, and this amount
-agrees with our measured increase in length. The simulations also
+theoretical calculations give an increase of length by 3.6\%, in
+agreement with our measured length increase. The simulations also
 suggest that the particle system behaves as a semipermeable
@@
 
-\begin{wrapfigure}[11]{l}{0.22\textwidth}
+\begin{wrapfigure}[10]{l}{0.22\textwidth}
+% \vspace{-5pt}
   \centering{\includegraphics[width=0.22\textwidth]{Figures/PW_fig5.pdf}}
+ \vspace{-20pt}
   \caption{\label{fig:flow_rupture} \footnotesize Rupture of a
@@
 model, it is a consequence of monolayer independence. For large shear
-rates, viscous forces exceed the hydrophobic attraction to the point that
-the vesicle ruptures, and the flow carries away segmented membrane patches
+rates, viscous forces exceed the hydrophobic attraction leading to
+ vesicle rupture~\cite{C8SM01501E}, at which point the flow carries away segmented membrane patches
 (Figure \ref{fig:flow_rupture}).

### 2020-11-16 NSF2020/Description/specificaim1_ver2.tex
tidied it up; removed hyperlinks + pagination

@@
 %\end{center}
+\newpage
 \subsubsection{Simulations of the HAP model to estimate elastic moduli
@@
 %a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
-We propose to
 %
@@
 %If this is the case we will 
-%
-{\bf (i)} determine the value of effective elastic moduli $\KB$,
-$\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and
-particle shape map onto elastic moduli. 
-An accurate and robust way to measure material properties is to track the evolution of the bilayer as
 %
@@
 \end{wrapfigure}
+We propose to {\bf (i)} determine the value of effective elastic moduli $\KB$,
+$\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and
+particle shape map onto elastic moduli. 
+An accurate and robust way to measure material properties is to track the evolution of the bilayer as
 it relaxes from an initially non-equilibrium
 configuration~\cite{PhysRevLett.117.188102}. Figure~\ref{fig:flattening}
-shows an example where the initial configuration of a lipid bilayer
-patch contains only splay deformation without any other components
-(saddle splay, twist and tilt). As the bent membrane flattens, we find
-that both the membrane self-interaction energy $\Phi$ and the elastic
+shows an example where the initial configuration of a bilayer
+patch containing the splay deformation without any other components
+(saddle splay, twist and tilt). As the bent membrane flattens, 
+both the self-interaction energy $\Phi$ and the elastic
 energy ${\cal W}$ decrease, and because the saddle splay, twist, and
@@
 %
-\begin{wrapfigure}[11]{l}{0.32\textwidth}
-\centerline{\includegraphics[width=0.32\textwidth]{Figures/SaddleSplayDiagram.pdf}}
-  \vspace{-8pt}
-\caption{\label{fig:saddle_splay} \footnotesize Example of determining the
-  saddle splay modulus.}
-\end{wrapfigure}
-%
 This yields a dissipation of the total potential \eqref{eq:total_poten}, which
@@
 
+%
+\begin{wrapfigure}[11]{l}{0.32\textwidth}
+\centerline{\includegraphics[width=0.32\textwidth]{Figures/SaddleSplayDiagram.pdf}}
+  \vspace{-8pt}
+\caption{\label{fig:saddle_splay} \footnotesize Example of determining the
+  saddle splay modulus.}
+\end{wrapfigure}
 We propose to conduct calculations similar to the example of Figure~\ref{fig:flattening}
@@
 %\subsubsection{HK elastic energy form}
+
 \noindent{\bf{HK elastic energy form:}}

### 2020-11-16 NSF2020/Description/preliminarywork.tex
RJR fixed frequ encies

@@
 a tank-treading frequency as the mean of the particle angular
-velocities. The measured steady-state freque ncies were within 7\% of the predicted 
+velocities. The measured steady-state frequencies were within 7\% of the predicted 
 frequency (dotted and solid curves in Figure~\ref{fig:tank_treading}B).
 The inclincation angle of the particle-based simulation also
-follows the inclination angle $\Theta$ predicted by Jeffrey's
+follows the inclination angle $\Theta(t)$ predicted by Jeffrey's
 equation (Figure~\ref{fig:tank_treading}D), albeit with higher frequency oscillation

### 2020-11-16 NSF2020/Description/background.tex
edited background.tex

@@
 
-\begin{wrapfigure}[10]{r}{0.22\textwidth}
-\centerline{\includegraphics[width=0.22\textwidth]{figures/BG_fig1.pdf}}
-\caption{ \footnotesize
-A collection of rigid particles: $P_1,$ $P_2,$ $P_3, \ldots$. The
-exterior domain $\Omega$ represents the solvent.}
-  \label{fig:domain}
-\end{wrapfigure}
 Recently, PIs RR and YNY developed a mathematical model, called the
@@
 
+\begin{wrapfigure}[9]{r}{0.24\textwidth}
+  \vspace{-20pt}
+\centerline{\includegraphics[width=0.24\textwidth]{figures/BG_fig1.pdf}}
+\caption{ \footnotesize
+A collection of rigid particles: $P_1,$ $P_2,$ $P_3, \ldots$. The
+exterior domain $\Omega$ represents the solvent.}
+  \label{fig:domain}
+\end{wrapfigure}
 \subsection{Hydrophobic Attraction Potential (HAP)}
@@
   \label{stress}
-\boldsymbol{\sigma}_{\text{hydro}} = \gamma \rho^{-1} u^2 I + 2\rho \gamma (\tfrac{1}{2}|\nabla u|^2I - \nabla u \nabla u^T).
+\boldsymbol{\sigma}_{\text{hydro}} = \gamma \rho^{-1} u^2 I + 2\rho
+  \gamma \left(\frac{1}{2}|\nabla u|^2I - \nabla u \nabla u^T\right).
 \end{align}
@@
 
-The time integration of
-particle configurations goes as follows: \textbf{(i)} solve the
-BVP~\eqref{SL} for the screened Laplace equation, \textbf{(ii)}
-determine the rigid body forces and torques~\eqref{forceandtorque},
-\textbf{(iii)} solve the Stokes mobility problem~\eqref{eq:stokes} for
-rigid body motion, and \textbf{(iv)} update the particle configuration.
-Numerical challenges and how these challenges are overcome are described
-in \S\ref{subsec:specific_aim_2}.
+The time integration of particle configurations goes as follows:
+\textbf{(i)} solve the BVP~\eqref{SL} for the screened Laplace equation,
+\textbf{(ii)} determine the rigid body forces and
+torques~\eqref{forceandtorque}, \textbf{(iii)} solve the Stokes mobility
+problem~\eqref{eq:stokes} for the rigid body motions, and \textbf{(iv)}
+update the particle configuration.  Numerical challenges and how these
+challenges are overcome are described in \S\ref{subsec:specific_aim_2}.
 

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
broader impacts edited

--- 2020-11-15 NSF2020/Description/broaderimpacts.tex
@@
 analysis, and scientific computing in this project provides a compelling
-example of the importance of mathematics in biophysics and engineering
-applications. The concepts and methods described here go beyond the
-context of amphiphilic particles and lipid molecules. They extend to
-other problems featuring microscopic phase separation that leads to
-formation of mesoscopic domains. This situation arises, for example, in
-biological development in systems biology. The methods developed here
-have the potential to impact those and other related areas in
-biomedicine and biotechnology.
+example of the importance of mathematics and computation in biophysics
+and engineering applications. The concepts and methods described here go
+beyond the context of amphiphilic particles and lipid molecules. They
+extend to other problems featuring microscopic phase separation that
+leads to formation of mesoscopic domains. This situation arises, for
+example, in biological development in systems biology. The methods
+developed here have the potential to impact those and other related
+areas in biomedicine and biotechnology.
 
@@
 \label{subsec:Educational_plans}
-The topics of this proposal have application in robotics, machine learning,
-and engineering. To foster training in mathematical sciences, the project
-will include undergraduate researchers (URs). The proposal supports one UR
-per year from the lead institution, and will include one or two additional
-UR from actively supported in-house programs
+The topics of this proposal have application in robotics, machine
+learning, and engineering. To foster training in mathematical sciences,
+the project will include undergraduate researchers (URs). The proposal
+supports one UR per year from the lead institution, and will include one
+or two additional UR from actively supported in-house programs
 
@@
 mathematical writing and presentation. To maximize vertical integration,
-and to the extent possible, the PIs and personnel will travel to 
-New York for one or two weeks in the summers. Fordham University 
-recently constructed a seminar/collaboration space specifically
-for collaborative research, and URs will base there activitied from here.
+and to the extent possible, the PIs and personnel will travel to New
+York for one or two weeks in the summers. Fordham University recently
+constructed a seminar/collaboration space specifically for collaborative
+research, and the URs will have office space with desks there.
 
 As a requirement, the URs will write quality summary reports and give
-presentations at the their respective research symposia. The work will be
-considered a success if the URs also participate in a national conference.
-The best possible outcome is if URs coauthor a publication.
+presentations at the their respective research symposia. The work will
+be considered a success if the URs also participate in a national
+conference. The best possible outcome is if URs coauthor a publication.
 
 There are two ways the proposal will meaningfully engage the community.
-To be more impactful, students from the Bronx High School of Science
-(PI RR) and Newark Science Park High School (PI YNY) will be encouraged
-to join the research team. PI BQ will work with undergraduate and high
+To be more impactful, students from the Bronx High School of Science (PI
+RR) and Newark Science Park High School (PI YNY) will be encouraged to
+join the research team. PI BQ will work with undergraduate and high
 school students through the Undergraduate Research Opportunity Program
 and Young Scholar's Program, as he has done in the past. Secondly, the
-PIs will prioritize students who would most benefit from the grant activity.
-We specifically target students whose socio-economic background prevents
-them from participating in out-of-state research experiences.
+PIs will prioritize students who would most benefit from the grant
+activity. We specifically target students whose socio-economic
+background prevents them from participating in out-of-state research
+experiences.
 
-Innovations in teaching: we will create several modules to include
-in our courses. These modules will introduce topics from numerical linear
-algebra and optimization, and be based on the ideas of the proposal.
-Additionally, we and our UR collaborators will give remote, guest lectures
-in each others' courses and undergraduate seminars.
+Finally, we will create several modules to include in our courses. These
+modules will introduce topics from numerical linear algebra and
+optimization, and be based on the ideas of the proposal. Additionally,
+we and our UR collaborators will give remote, guest lectures in each
+others' courses and undergraduate seminars.
 

### 2020-11-16 NSF2020/Description/specificaim1_ver2.tex
done aim 1

@@
 %\end{figure}
-The goal of Specific Aim 1 is to characterize the material properties of many-body, self-assembled amphiphiles.
-For amphiphiles assembled into bilayers, these properties are described by membrane continuum mechanics.
-Our goal is to map the parameters of the particle-based model onto the elastic moduli from continuum theory.
-Results from this goal will facilitate simulators to use the hydrophobic attraction force calculations
-to model bilayers with specific composition. These calculations have provably less computational complexity than
-those of molecular dynamics simulations and possess the molecular granularity lacking from continuum models.
+The goal of Specific Aim 1 is to characterize the material properties of
+many-body, self-assembled amphiphiles.  For amphiphiles assembled into
+bilayers, these properties are described by membrane continuum
+mechanics.  Our goal is to map the parameters of the particle-based
+model onto the elastic moduli from continuum theory.  Results from this
+goal will facilitate simulators to use the hydrophobic attraction force
+calculations to model bilayers with specific composition. These
+calculations have provably less computational complexity than those of
+molecular dynamics simulations and possess the molecular granularity
+lacking from continuum models.
 
-Hamm and Kozlov (HK) pioneered 
-the modern theory of membrane continuum mechanics \cite{Hamm2000}, and their theory
-%was pioneered by Hamm and Kozlov (HK) \cite{Hamm2000}. The theory 
-is widely used to describe biological phenomena, including 
-fission \cite{FrEsAkSh15, Maetal15, PhysRevE.79.031926},
-fusion \cite{ChKo08, KoKo2002,Kuzmin7235,Aeffner2012},
-poration \cite{Gaetal20}, phase boundaries, and interaction with inclusions
-\cite{SeLeMaEg17,Saetal20, Pietal20}. These phenomena
-require resolution of the internal structure of the membrane.  
-Recently, there has been a revival in interest in the HK theory as the quadratic assumption
-for the elasticity energy density has caused
-researchers to question the applicability of the theory 
-for large curvatures
-\cite{PhysRevLett.117.188102, ARGUDO20161619}.
+Hamm and Kozlov (HK) pioneered the modern theory of membrane continuum
+mechanics~\cite{Hamm2000}, and their theory is widely used to describe
+biological phenomena, including fission \cite{FrEsAkSh15, Maetal15,
+PhysRevE.79.031926}, fusion \cite{ChKo08,
+KoKo2002,Kuzmin7235,Aeffner2012}, poration~\cite{Gaetal20}, phase
+boundaries, and interaction with inclusions~\cite{SeLeMaEg17,Saetal20,
+Pietal20}. These phenomena require resolution of the internal structure
+of the membrane.  Recently, there has been a revival of interest in the
+HK theory as the quadratic assumption for the elasticity energy density
+has caused researchers to question the applicability of the theory for
+large curvatures~\cite{PhysRevLett.117.188102, ARGUDO20161619}.
 %
@@
 molecular dynamics and those derived from \eqref{ansatz3} are in agreement, even when curvatures are large.
-Under spatial scales much larger than the
-membrane thickness, membrane energy is well-characterized by the
-Canham-Helfrich energy used throughout the fluid-structure literature
-\cite{QiangDu09, Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP, qua-bir2014, qua-vee-you2019}.
-%\todo[inline]{YNY: place your recent works here}
-The Canham-Helfrich energy is actually a special case of
-\eqref{ansatz3} obtained by setting ${\bf n} =  \pm {\bf N}$ (the $\pm$ depending on
-orientation) and collapsing both monolayers onto the membrane midplane.
+Under spatial scales much larger than the membrane thickness, membrane
+energy is well-characterized by the Canham-Helfrich energy used
+throughout the fluid-structure literature \cite{QiangDu09,
+Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP, qua-bir2014,
+qua-vee-you2019}. The Canham-Helfrich energy is actually a special case
+of \eqref{ansatz3} obtained by setting ${\bf n} =  \pm {\bf N}$ (the
+$\pm$ depending on orientation) and collapsing both monolayers onto the
+membrane midplane.
 %There, splay $\Div n$ equal to twice the mean curvature, saddle splay
@@
 %
-\begin{wrapfigure}[10]{r}{0.4\textwidth}
-\vspace{-0.3cm}
-\centerline{\includegraphics[width=0.4\textwidth]{Figures/Flattening.pdf}}
+\begin{wrapfigure}[9]{r}{0.43\textwidth}
+\vspace{-0.4cm}
+\centerline{\includegraphics[width=0.43\textwidth]{Figures/Flattening.pdf}}
 %  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
-\vspace{-0.2cm}
+\vspace{-0.5cm}
 \caption{\label{fig:flattening} \footnotesize Example of computing
@@
 \end{wrapfigure}
-We propose to {\bf (i)} determine the value of effective elastic moduli $\KB$,
-$\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the model parameters $\rho,$ $\gamma$, and
-particle shape map onto elastic moduli. 
-An accurate and robust way to measure material properties is to track the evolution of the bilayer as
-it relaxes from an initially non-equilibrium
-configuration~\cite{PhysRevLett.117.188102}. Figure~\ref{fig:flattening}
-shows an example where the initial configuration of a bilayer
-patch containing the splay deformation without any other components
-(saddle splay, twist and tilt). As the bent membrane flattens, 
-both the self-interaction energy $\Phi$ and the elastic
-energy ${\cal W}$ decrease, and because the saddle splay, twist, and
-tilt stay zero, the slope gives the bending modulus in this case.
+We propose to {\bf (i)} determine the value of effective elastic moduli
+$\KB$, $\KT$, $\KG$, and $\KTH$ and then {\bf (ii)} understand how the
+model parameters $\rho,$ $\gamma$, and the particle shape map onto
+elastic moduli. An accurate and robust way to measure material
+properties is to track the evolution of the bilayer as it relaxes from
+an initially non-equilibrium
+configuration~\cite{PhysRevLett.117.188102}.
+Figure~\ref{fig:flattening} shows an example where the initial
+configuration of a bilayer patch containing the splay deformation
+without any other components (saddle splay, twist and tilt). As the bent
+membrane flattens, both the self-interaction energy $\Phi$ and the
+elastic energy ${\cal W}$ decrease, and because the saddle splay, twist,
+and tilt stay zero, the slope gives the bending modulus in this case.
 
@@
 
-Here we start with a particle-based bilayer in a specific non-equilibrium shape that involves only one of the components of the displacement in Figure~\ref{fig:deformations}, and then evolve the particle system according to the time integration for \eqref{eq:stokes}.
-Because elastic properties are independent of dissipation,
-we can forgo solving for fluid velocity and set the translational
-velocity and angular velocity directly proportional to force and torque. 
+Here we start with a particle-based bilayer in a specific
+non-equilibrium shape that involves only one of the components of the
+displacement in Figure~\ref{fig:deformations}, and then evolve the
+particle system according to the time integration for \eqref{eq:stokes}.
+Because elastic properties are independent of dissipation, we can forgo
+solving for fluid velocity and set the translational velocity and
+angular velocity directly proportional to the force and torque,
+respectively. 
 %bilayer by steepest gradient descent 
@@
 PhysRevE.102.042406}. 
-A value $\KT = 0$, however, makes \eqref{ansatz3} a noncoercive functional.
+A value $\KT = 0$, however, makes~\eqref{ansatz3} a noncoercive functional.
 %and leads to the nonphysical conclusion that there are bilayers 
@@
 \subsubsection{Analysis on the HAP model in terms of the HK functional}
-The HK functional \eqref{ansatz3} has had tremendous impact in understanding
-biological membranes, but has received little attention in terms of mathematical
-analysis. In the calculus of variations, the principal question is whether a
-minimizer of an energy functional exists. But in the case of \eqref{ansatz3},
-this answer is presently unknown. With regard to the simpler, Canham-Helfrich
-energy, \cite{Simon1993} proved the existence of minimizing surfaces without boundary, 
-and \cite{doi:10.1137/18M1195851} proved the well-posedness of a spatially periodic,
-time-dependent elastic interface problem. An analytical challenge 
-for the HK functional \eqref{ansatz3} is that surface-director coupling makes it
-possible to have bounded energy monolayers with corners, and such
-pathological examples must be ruled out before carrying over the arguments
-for the Canham-Helfrich functional to the present setting.
+The HK functional~\eqref{ansatz3} has had tremendous impact in
+understanding biological membranes, but has received little attention in
+terms of mathematical analysis. In the calculus of variations, the
+principal question is whether a minimizer of an energy functional
+exists. In the case of~\eqref{ansatz3}, the answer is presently unknown.
+With regard to the simpler Canham-Helfrich energy,~\cite{Simon1993}
+proved the existence of minimizing surfaces without boundary,
+and~\cite{doi:10.1137/18M1195851} proved the well-posedness of a
+spatially periodic, time-dependent elastic interface problem. An
+analytical challenge for the HK functional~\eqref{ansatz3} is that
+surface-director coupling makes it possible to have bounded energy
+monolayers with corners, and such pathological examples must be ruled
+out before carrying over the arguments for the Canham-Helfrich
+functional to the present setting.
 
-%\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
-Our goal here is to develop tools that can explain functionals like
-\eqref{ansatz3} from first principles in terms of HAP. The papers
-\cite{doi:10.1063/5.0009734,Seguin2012,Seguin2014} give statistical
-mechanical/mean field derivations of the Canham-Helfrich energy from a
-pair-potential for rod-like molecules, but do not include tilt, which is an
-indispensable deformation at biological scales. To make progress, we must
-first understand how the HAP functional behaves under various limits.
+%\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of
+%HAP}
+Our goal here is to develop tools that can explain functionals
+like~\eqref{ansatz3} from first principles in terms of HAP. The
+papers~\cite{doi:10.1063/5.0009734, Seguin2012, Seguin2014} give
+statistical mechanical/mean field derivations of the Canham-Helfrich
+energy from a pair-potential for rod-like molecules, but do not include
+tilt, which is an indispensable deformation at biological scales. To
+make progress, we must first understand how the HAP functional behaves
+under various limits.
 
-We first consider HAP in the limit of vanishing screening length.
-As a concrete, model problem we consider a collection of colloidal polyhedral
-where the binding energy of this system can be described by a
-discrete, lower semicontinuous functional $\Phi_0$ whose value is the total
-surface area of the polyhedra minus two times the area of any overlapping faces.
-We conjecture that the $\Phi$ energy $\Gamma$-converges to $\Phi_0$
-\cite{Mugnai2013}, meaning that any cluster points of minimizers of $\Phi$
-converge to a minimum of $\Phi_0$ in the limit $\rho \to 0$. 
-To address this conjecture, we employ boundary layer analysis for the screened
-Laplace equation \cite{Lee2018, Lin2015, Shibata2004,1531-3492_2006_2_357, Lee2018}.
-The technique of $\Gamma$-convergence is a powerful tool for numerical approximations
-and with it we can help explain unexcepted phenomena like hierarchical self-assembly in
-colloidal systems \cite{Luo2019}.
+We first consider HAP in the limit of vanishing screening length. As a
+concrete model problem, we consider a collection of colloidal polyhedral
+where the binding energy of this system can be described by a discrete,
+lower semicontinuous functional $\Phi_0$ whose value is the total
+surface area of the polyhedra minus two times the area of any
+overlapping faces. We conjecture that the $\Phi$ energy
+$\Gamma$-converges to $\Phi_0$ \cite{Mugnai2013}, meaning that any
+cluster points of minimizers of $\Phi$ converge to a minimum of $\Phi_0$
+in the limit $\rho \to 0$. To address this conjecture, we employ
+boundary layer analysis for the screened Laplace equation~\cite{Lee2018,
+Lin2015, Shibata2004,1531-3492_2006_2_357, Lee2018}. The technique of
+$\Gamma$-convergence is a powerful tool for numerical approximations and
+with it we can help explain unexpected phenomena like hierarchical
+self-assembly in colloidal systems~\cite{Luo2019}.
 

### 2020-11-16 NSF2020/Description/newspecificaim2.tex
tidied it up; removed hyperlinks + pagination
edited aim 2

@@
-\subsection{Specific Aim 2: Efficient high-order numerical methods for
-large-scale simulations}
+\subsection{Specific Aim 2: Efficient, high-order methods for large-scale simulations}
 % ----------------------------------------------------------------------
@@
     \vspace{-20pt}
-    \caption{\label{fig:flow_map} \footnotesize The diagram depicts a collection of 3D
-    amphiphilic particles suspended in a solvent. The solvent velocity satisfies
-    the Stokes equations, and the hydrophobic forces depend on the
-    solvent activity that satisfies the screened Laplace equation. The
-    geometry is updated by solving the mobility problem.} 
+    \caption{\label{fig:flow_map} \footnotesize A collection of 3D
+    amphiphilic particles suspended in a solvent. The solvent velocity
+    satisfies the Stokes equations, and the hydrophobic forces depend on
+    the solvent activity that satisfies the screened Laplace equation.
+    The geometry is updated by solving the mobility problem.} 
 \end{wrapfigure}
@@
 systems, developing preconditioning strategies, and developing
-quadrature methods for nearly singular integrands. These
+quadrature methods for nearly-singular integrands. These
 challenges are described in \S\ref{subsec:NumericalIssues}. However,
@@
 %
-\begin{wrapfigure}[21]{r}{2.5in}
-%\vspace*{+15pt}
+\begin{wrapfigure}[20]{r}{2.5in}
+\vspace*{-13pt}
 \centerline{\includegraphics[width=2.5in]{figures/integrands}}
@@
 direct solvers avoid iteration~\cite{fds2, fds3, fds4, fds5, fds6, fds7,
-ho2016cpam1, minden2016, minden2017siammms}, but direct solvers often
-require a large amount of computational overhead, and this makes them
-less practical for problems with moving geometries. Alternatively, fast
-direct solvers techniques can be used to develop efficient
-preconditioning strategies such as the inverse Fast Multipole Method
-(IFMM)~\cite{cou-pou-dar2017}. PI BQ used the IFMM to precondition
-Stokes equations~\cite{qua-cou-dar2018}. A suite of other
-preconditioners including sparse approximate inverses~\cite{che2000} and
+ho2016cpam1, minden2016, minden2017siammms}, but often require a large
+amount of computational overhead, and this makes them less practical for
+problems with moving geometries. Alternatively, fast direct solver
+techniques can be used to develop efficient preconditioning strategies
+such as the inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017}.
+PI BQ used the IFMM to precondition Stokes
+equations~\cite{qua-cou-dar2018}. A suite of other preconditioners
+including sparse approximate inverses~\cite{che2000} and
 multigrid~\cite{hem-sch1981, sch1982} will be investigated.
@@
 PI BQ developed a high-order adaptive time stepping method for
-hydrodynamic suspensions~\cite{qua-bir2016}, and it has served as a
+hydrodynamic suspensions \cite{qua-bir2016}, and it has served as a
 robust method to simulate processes including mixing and adhesion in
@@
 \otimes \nabla u_j\right)$. Equation~\eqref{eq:reciprocal} does not
-require knowledge of $\nabla u$ on the particle boundary, and this is
+require knowledge of $\nabla u$ on particle boundary $i$, and this is
 enormously beneficial for calculating the hydrophobic force and torque.
@@
 resulting physics~\cite{ong-chr-qua2017}. Therefore, different
-regularization strategies will be investigated with the goal of
-controlling the accuracy of the fluctuation-dissipation balance.
+regularization strategies will be investigated with the goal of finding
+well-conditioned BIE formulations that control the accuracy of the
+fluctuation-dissipation balance.

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
Update broaderimpacts.tex
Intellectual merit

@@
 \section{Intellectual Merit}
-A central theme of the project is the mathematical development and
-analysis of the physical model for interaction between many amphiphilic
-particles. The model formulates the interaction potential through a
-screened Laplace equation boundary value problem possessing the physical
-properties like non-additivity and decay of realistic hydrophobic
-attraction. Colloidal systems collectively self-assemble into bilayer
-morphologies, and we analyze the elastic properties of these amphiphilic
-particle ensembles. This allows us to interpret the Helfrich free energy
-in terms of hydrophobic interactions and specific molecular
-characteristics. We extend the capabilities of the boundary integral
-equation and time stepping methods to stably perform large particle
-number simulations in three dimensions. Results from these computations
-will be used to compare collective amphiphilic against experiments and
-to study the optimal design of three-dimensional functional materials.
+The purpose of this research is to reach interesting physical phenomena with 
+less computational cost than molecular dynamics, and account for more general
+features that continuum theory misses. The main ingredient is defining a 
+nonlocal interaction through the solution of an elliptic boundary value problem
+that has the phenomenological characteristics of long-range hydrophobic
+attraction. It turns out that this minimal model gives rise to rich phenomena
+for Janus particle aggregates and correctly predicts elastic properties of bilayer. 
+The technical research tasks includes quantifying collective properties of 
+amphiphilic ensembles, mathematical analysis of continuum elastic energies, 
+efficient, high-order numerical algorithms for large-scale simulations, and 
+incorporating external fields such as electric charge. Lastly, the proposal 
+extends the results using three-dimensional boundary integral formulations.
+
+%A central theme of the project is the mathematical development and
+%analysis of the physical model for interaction between many amphiphilic
+%particles. The model formulates the interaction potential through a
+%screened Laplace equation boundary value problem possessing the physical
+%properties like non-additivity and decay of realistic hydrophobic
+%attraction. Colloidal systems collectively self-assemble into bilayer
+%morphologies, and we analyze the elastic properties of these amphiphilic
+%particle ensembles. This allows us to interpret the Helfrich free energy
+%in terms of hydrophobic interactions and specific molecular
+%characteristics. We extend the capabilities of the boundary integral
+%equation and time stepping methods to stably perform large particle
+%number simulations in three dimensions. Results from these computations
+%will be used to compare collective amphiphilic against experiments and
+%to study the optimal design of three-dimensional functional materials.

### 2020-11-16 NSF2020/Description/newspecificaim3.tex
edited rest of proposal

@@
 robust, high-order-in-time and -space algorithms suited to the problem.
-There are a few challenges. {\bf (1)} The equations express a two-way coupling
-since the flow changes the position of the suspended particles,
-and in return, the geometry-dependent hydrophobic stresses impart a force
-on the flow. {\bf (2)} The inputs to the Stokes equations are particle
-configurations, forces, and torques. The outputs are the rigid body
-translation and angular velocities used to update the particle positions
-(see Figure~\ref{fig:flow_map}). Although the underlying equations are
-linear, the overall problem is highly nonlinear because the domain is
-constantly changing. {\bf (3)} Self-assembly causes the particles to
-come into close contact. As a result, an exceptional spatial accuracy is
-required to resolve the fields between adjacent particles. Furthermore, 
-physically relevant elastic properties of bilayers become apparent at
-large length scales and for large particle-numbers, which increases the
-computational complexity of our simulations.
+There are a few challenges. {\bf (i)} The equations express a two-way
+coupling since the flow changes the position of the suspended particles,
+and in return, the geometry-dependent hydrophobic stresses impart a
+force on the flow. {\bf (ii)} The inputs to the Stokes equations are
+particle configurations, forces, and torques. The outputs are the rigid
+body translation and angular velocities used to update the particle
+positions (see Figure~\ref{fig:flow_map}). Although the underlying
+equations are linear, the overall problem is highly nonlinear because
+the domain is constantly changing. {\bf (iii)} Self-assembly causes the
+particles to come into close contact. As a result, an exceptional
+spatial accuracy is required to resolve the fields between adjacent
+particles. Furthermore, physically relevant elastic properties of
+bilayers become apparent at large length scales and for large
+particle-numbers, which increases the computational complexity of our
+simulations.
 
@@
 \label{PowerMiranda}
-  {\bf u} = {\bf u}_{\infty} + L\boldsymbol{\eta} + 
+  {\bf u} = {\bf u}_{\infty} + \mathcal{K}\boldsymbol{\eta} + 
     \sum_{i=1}^N \left(S(\cdot, {\bf a}_i) {\bf F}_i + 
@@
 where $S$ and $R$ are stokeslets and rotlets supported at the respective
-particle centers~\cite{leal_2007} and $L\boldsymbol{\eta}$ is a layer
+particle centers~\cite{leal_2007} and $\mathcal{K}\boldsymbol{\eta}$ is a layer
 potential for the unknown density function $\boldsymbol{\eta}$. With the
@@
 \subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
-In recent experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending rigidity
-was determined as a function of lipid composition from 0 to 100 mol $\%$ of
-charged lipids using flicker spectroscopy of the shape fluctuations of a giant
-unilamellar vesicle (GUV).
+In recent experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending
+rigidity was determined as a function of lipid composition from 0 to 100
+mol $\%$ of charged lipids using flicker spectroscopy of the shape
+fluctuations of a giant unilamellar vesicle (GUV).
 %the bending rigidity is determined as a
@@
 %in recent experiments~\cite{FaizEtAl2019_SoftMatt}---
-Membrane bending rigidity increases with increasing lipid surface charge,
-while decreases with increasing salt concentration in the bulk solution
-due to the screening of the lipid surface charge. This
-agrees with several theoretical models~\cite{Kralchevsky1996_JCIS,
+Membrane bending rigidity increases with increasing lipid surface
+charge, while decreases with increasing salt concentration in the bulk
+solution due to the screening of the lipid surface charge. This agrees
+with several theoretical models~\cite{Kralchevsky1996_JCIS,
 May1996_JChemPhys, LoubetEtAl2013_PRE} that also assume the quadratic
@@
 \S\ref{subsec:specific_aim_1}) would worsen in the presence of
-electrostatic interactions and electrokinetics. The PIs will extend
-the approaches in \S\ref{subsec:specific_aim_1} to charged lipids to
+electrostatic interactions and electrokinetics. The PIs will extend the
+approaches in \S\ref{subsec:specific_aim_1} to charged lipids to
 calculate the bending moduli and compare against the experimental
@@
 electrostatic potential as a functional of particle configuration.
-Adding the electrostatic forces to the hydrophobic attraction forces
-between particles to compute the particle assembly dynamics, we can then
-calculate elastic moduli as outlined in \S\ref{subsec:specific_aim_1}.
-Results from these proposed calculations will provide further comparisons and
-validations of the HAP model against the continuum mechanics.
+Adding the electrostatic force to the hydrophobic attraction force
+between particles, we will assess the dependence of elastic moduli on
+electric charges using the methods described in
+\S\ref{subsec:specific_aim_1}. Results from these proposed calculations
+will provide further comparisons and validations of the HAP model
+against the continuum mechanics.
 

### 2020-11-16 NSF2020/Description/preliminarywork.tex
edited rest of proposal

@@
-\vspace{-0.1cm}
-\begin{wraptable}[8]{r}{0.55\textwidth}
-\vspace{-0.1cm}
+\begin{wraptable}[6]{r}{0.55\textwidth}
+\vspace{-0.8cm}
 \centering{
@@
 
-%\begin{wrapfigure}[]{r}{0.5\textwidth}
-%  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
-%  \vspace{-25pt}
-%  \caption{\label{fig:tank_treading} \footnotesize
-%    Panel A shows water activity and flow direction for  a two-dimensional
-%    particle-based vesicle in a shear flow; $\mu  = 1$ mPa s,
-%    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. Panel B plots the
-%    mean angular velocities for the outer leaflet and the inner
-%    respectively.  Panel C shows that the trajectory of the particle
-%    centers forms two ellipses with well-defined inclination angle
-%    $\Theta$. Panel D shows the evolution of the inclination angle.
-%    Panels B and D share the same time axis.}
-%\end{wrapfigure}
 \begin{wraptable}[10]{l}{0.43\textwidth}
+  \vspace{-6pt}
 \centering{
@@
   \end{tabular}}
-\vspace{-5pt}
+\vspace{-8pt}
 \caption{\label{tab:spectral_force} 
@@
   for force and torque, respectively, as a function of number of grid
-  points $n$ per particle. The data is for $N = 5$ particles; two of
-  the particles are nearly touching at a distance 1\% of particle
+  points $n$ per particle. The data is for $N = 5$ particles; two of the
+  particles are nearly touching at a distance of 1\% of the particle
   diameter.} 
@@
 
-PIs BQ, RR, and YNY initiated a collaboration in summer 2020 to
-develop the hydrodynamic model of \S\ref{subsec:specific_aim_3}.  To
-date, we have written solvers for the two-dimensional boundary integral
+PIs RR, BQ, and YNY initiated a collaboration in summer 2020 to develop
+the hydrodynamic model of \S\ref{subsec:specific_aim_3}. To date, we
+have written solvers for the two-dimensional boundary integral
 formulations of~\eqref{SL} and~\eqref{eq:stokes} that achieve
-third-order accuracy up to the boundary. The specialized reciprocal
-identity~\eqref{eq:reciprocal} gives spectral accuracy for force and
-torque (Table~\ref{tab:spectral_force}).
+third-order accuracy up to the boundary of the particles. The
+specialized reciprocal identity~\eqref{eq:reciprocal} gives spectral
+accuracy for force and torque (Table~\ref{tab:spectral_force}).
 
@@
   \caption{\label{fig:tank_treading} \footnotesize
-    Panel A: A two-dimensional, 
-    particle-based vesicle in a shear flow (arrows); $\mu  = 1$ mPa s and
-    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. (Compare with \cite{Brandner2019}).
-    Panel B: Angular velocities for the outer and the inner leaflets.
-    Panel C: The trajectory of the particle
-    centers forms two ellipses with well-defined inclination angle
-    $\Theta$. Panel D: The evolution of the inclination angle.
+    Panel A: A two-dimensional, particle-based vesicle in a shear flow
+    (arrows); $\mu = 1$ mPa s and $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$
+    Compare with~\cite{Brandner2019}).  Panel B: Angular velocities for
+    the outer and the inner leaflets.  Panel C: The trajectory of the
+    particle centers forms two ellipses with well-defined inclination
+    angle $\Theta$. Panel D: The evolution of the inclination angle.
     Panels B and D share the same time axis.}
@@
 \begin{wrapfigure}[10]{l}{0.22\textwidth}
-% \vspace{-5pt}
+ \vspace{-3pt}
   \centering{\includegraphics[width=0.22\textwidth]{Figures/PW_fig5.pdf}}

### 2020-11-16 NSF2020/Description/priorsupport.tex
yny Nov15b
edited rest of proposal

@@
 
-\begin{wrapfigure}[9]{r}{0.56\textwidth}
-\vspace{-15pt}
+\begin{wrapfigure}[8]{r}{0.56\textwidth}
+\vspace{-19pt}
 \definecolor{barblue}{RGB}{51,102,254}
@@
 \end{ganttchart}
-  \vspace{-8pt}
+  \vspace{-10pt}
 \caption{\footnotesize Schedule for the proposed work, measured in
@@
 The success of the proposed research requires complementary expertise
-and collaborative efforts in physics, applied mathematics, algorithms
+and collaborative efforts in physics, applied mathematics, algorithms,
 and computing. Ryham has been working on mathematical modeling with a
@@
 Their recent collaborative work on the HAP model in two dimensions has
-provided a solid foundation on the proposed research.
+provided a solid foundation for the proposed research.
 
@@
 %
-The PIs, their postdoc and students will meet frequently on Zoom and in
-person when possible. The PIs will share software packages, paper
+The PIs, their postdocs, and students will meet frequently on Zoom and
+in person when possible. The PIs will share software packages, paper
 sources, and references on a common \textsf{Git} repository. The

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
fixed one last typo

@@
 
-The proposed mathematical analysis, modeling, and numerical algorithms
-will transform our understanding of the collective dynamics of
-amphiphilic particles such as (1) their self-assembly into micelles and
-bilayers, (2) the material properties of such self-assembly, and (3) the
-interaction between these building blocks. In addition to biophysical
-applications, amphiphilic Janus particles have recent popularity in the
-fabrication of smart materials. The proposed work will have a
-transformative impact on precision design for specific mechanical
-properties of materials made of amphiphilic nanoparticles. An important
-component of this proposal is the interdisciplinary education and
-training of both undergraduate students, graduate students, and
-postdoctoral fellows. The combination of mathematical modeling,
-analysis, and scientific computing in this project provides a compelling
-example of the importance of mathematics and computation in biophysics
-and engineering applications. The concepts and methods described here go
-beyond the context of amphiphilic particles and lipid molecules. They
-extend to other problems featuring microscopic phase separation that
-leads to formation of mesoscopic domains. This situation arises, for
-example, in biological development in systems biology. The methods
-developed here have the potential to impact those and other related
-areas in biomedicine and biotechnology.
+This project aims to advance the mathematical modeling of collective 
+dynamics of amphiphilic particles. The simulations use a new, yet intuitive,
+approach that can reach important and complex systems that are presently out of 
+reach in computational material science. These complex systems include 
+fusion and fission of amphiphilic bilayer membranes and optimal shape design
+in metamaterials. The development of three-dimensional 
+models describing colloidal systems could be transformative in biomedicine
+and material science. The research draws from expertise in scientific 
+computing, physics of fluids and mathematics. The mathematical component 
+incorporates leading techniques from geometric analysis and gives deep insight 
+into fundamental material science. The project offers undergraduates 
+in a socially impactful manner the opportunity to do research and train 
+with graduate and postdoctoral personnel. It incorporates research in the 
+classroom, and with its combination of mathematical modeling, analysis, 
+and scientific computing, the project highlights the importance of 
+mathematics and computation to all areas of science and engineering.
+
+%The proposed mathematical analysis, modeling, and numerical algorithms
+%will transform our understanding of the collective dynamics of
+%amphiphilic particles such as (1) their self-assembly into micelles and
+%bilayers, (2) the material properties of such self-assembly, and (3) the
+%interaction between these building blocks. In addition to biophysical
+%applications, amphiphilic Janus particles have recent popularity in the
+%fabrication of smart materials. The proposed work will have a
+%transformative impact on precision design for specific mechanical
+%properties of materials made of amphiphilic nanoparticles. An important
+%component of this proposal is the interdisciplinary education and
+%training of both undergraduate students, graduate students, and
+%postdoctoral fellows. The combination of mathematical modeling,
+%analysis, and scientific computing in this project provides a compelling
+%example of the importance of mathematics and computation in biophysics
+%and engineering applications. The concepts and methods described here go
+%beyond the context of amphiphilic particles and lipid molecules. They
+%extend to other problems featuring microscopic phase separation that
+%leads to formation of mesoscopic domains. This situation arises, for
+%example, in biological development in systems biology. The methods
+%developed here have the potential to impact those and other related
+%areas in biomedicine and biotechnology.
 
@@
 supports one UR per year from the lead institution, and will include one
-or two additional UR from actively supported in-house programs
+or two additional URs from actively supported in-house programs
 

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
added serial comma
Update broaderimpacts.tex

@@
 and material science. The research draws from expertise in scientific 
-computing, physics of fluids and mathematics. The mathematical component 
+computing, physics of fluids, and mathematics. The mathematical component 
 incorporates leading techniques from geometric analysis and gives deep insight 
@@
 PIs will prioritize students who would most benefit from the grant
-activity. We specifically target students whose socio-economic
+activity. These include students from underrepresented groups,
+and we specifically target students whose socio-economic
 background prevents them from participating in out-of-state research

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
Update broaderimpacts.tex

@@
 dynamics of amphiphilic particles. The simulations use a new, yet intuitive,
-approach that can reach important and complex systems that are presently out of 
+approach that can account for important and complex systems that are presently out of 
 reach in computational material science. These complex systems include 

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
Update broaderimpacts.tex

--- 2020-11-16 NSF2020/Description/broaderimpacts.tex
@@
 dynamics of amphiphilic particles. The simulations use a new, yet intuitive,
-approach that can reach important and complex systems that are presently out of 
+approach that can account for important and complex systems that are out of 
 reach in computational material science. These complex systems include 

### 2020-11-16 NSF2020/Description/specificaim1_ver2.tex
fixed an overflow using \sloppy

@@
 
+\sloppy
 The HK framework assumes a three-dimensional lipid monolayer where the internal structure

### 2020-11-16 NSF2020/Description/broaderimpacts.tex
Update broaderimpacts.tex

@@
 for Janus particle aggregates and correctly predicts elastic properties of bilayer. 
-The technical research tasks includes quantifying collective properties of 
+The technical research tasks include quantifying collective properties of 
 amphiphilic ensembles, mathematical analysis of continuum elastic energies, 
 efficient, high-order numerical algorithms for large-scale simulations, and 
-incorporating external fields such as electric charge. Lastly, the proposal 
+incorporating external fields such as through electric charge. Lastly, the proposal 
 extends the results using three-dimensional boundary integral formulations.

### 2020-11-16 NSF2020/Description/summary.tex
Add files via upload
Uploaded summary and its source file

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\pagestyle{empty}

\begin{document}
\begin{center}
{\bf \Large Summary}\\ Collaborative Research
\begin{tabular}{ccc}\\ 
Fordham University & Florida State University& New Jersey Institute of Technology\\
Rolf Ryham &            Bryan Quaife &              Yuan-Nan Young
\end{tabular}

\end{center}

\section*{Overview}
Numerical simulation has become an essential tool in nearly all areas of science and engineering, especially biophysics. This proposal specifically aims to advance mathematical modeling and analysis in membrane biophysics through the study of
collective dynamics of amphiphilic self-assembly. Self-assembly is a ubiquitous process in biology and is a major source of 
nonspecific interactions in soft matter. In the case of membranes, lipids self-assemble into bilayer and micelle morphologies. Over the past decades, macroscopic continuum mechanics has done a good job of modeling bilayer membranes at large length scales but can miss details at small length scales brought about by inclusions or topological changes that are crucial to the dynamics. Molecular dynamics models account for these granular details but are computationally costly when accurately accounting for nonlocal interactions. To design better membrane models, it is imperative to quantify the collective physical properties and processes of amphiphiles, and the proposed mathematics establishes a platform for efficiently simulating the collective dynamics at large scales in a manner that allows for direct comparison with preexisting theory and experiment.

\section*{Intellectual Merit}
The purpose of this research is to reach interesting physical phenomena with 
less computational cost than molecular dynamics, and account for more general
features that continuum theory misses. The main ingredient is defining a 
nonlocal interaction through the solution of an elliptic boundary value problem
that has the phenomenological characteristics of long-range hydrophobic
attraction. It turns out that this minimal model gives rise to rich phenomena
for Janus particle aggregates and correctly predicts elastic properties of bilayer. 
The technical research tasks include quantifying collective properties of 
amphiphilic ensembles, mathematical analysis of continuum elastic energies, 
efficient, high-order numerical algorithms for large-scale simulations, and 
incorporating external fields through electric charge. Lastly, the proposal 
extends the results using three-dimensional boundary integral formulations.

\section*{Broader Impacts}
This project aims to advance the mathematical modeling of collective 
dynamics of amphiphilic particles. The simulations use a new, yet intuitive,
approach that can account for important and complex systems that are out of 
reach in computational material science. These complex systems include 
fusion and fission of amphiphilic bilayer membranes and optimal shape design
in metamaterials. The development of three-dimensional 
models describing colloidal systems could be transformative in biomedicine
and material science. The research draws from expertise in scientific 
computing, physics of fluids, and mathematics. The mathematical component 
incorporates leading techniques from geometric analysis and gives deep insight 
into fundamental material science. The project offers undergraduates 
in a socially impactful manner the opportunity to do research and train 
with graduate and postdoctoral personnel. It incorporates research in the 
classroom, and with its combination of mathematical modeling, analysis, 
and scientific computing, the project highlights the importance of 
mathematics and computation to all areas of science and engineering.

\end{document}

### 2020-12-23 code/src/rigid2D.m
working on setting up on rcc

@@ -105,10 +105,13 @@ while step < prams.m
   om.writeData(time,geom2.center,geom2.tau,geom2.X);
 
   % write the velocity to a file
-  om.writeVelData(time,Up0,wp0);  
+%  om.writeVelData(time,Up0,wp0);  
   
   % update step counter
   step = step + 1;
+  message = ['Time Step required ' ...
+    num2str(toc(tSingleStep),'%4.2e'), ' seconds'];
+  om.writeMessage(message)
 end
 
 % save final time step

### 2020-12-23 NSF2020/Description/preliminarywork.tex
left overs from NSF2020 proposal

@@
-\begin{wraptable}[6]{r}{0.55\textwidth}
+\begin{wraptable}[6]{r}{0.56\textwidth}
 \vspace{-0.8cm}
@@
 
-\begin{wrapfigure}[22]{r}{0.5\textwidth}
+\begin{wrapfigure}[22]{l}{0.5\textwidth}
 \vspace{-5pt}
-  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
-  \vspace{-25pt}
+  \centering{\includegraphics[width=0.49\textwidth]{Figures/TankTreading.pdf}}
+  \vspace{-10pt}
   \caption{\label{fig:tank_treading} \footnotesize
@@
     (arrows); $\mu = 1$ mPa s and $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$
-    Compare with~\cite{Brandner2019}).  Panel B: Angular velocities for
+    (compare with~\cite{Brandner2019}).  Panel B: Angular velocities for
     the outer and the inner leaflets.  Panel C: The trajectory of the
@@
 
-\begin{wrapfigure}[10]{l}{0.22\textwidth}
+\begin{wrapfigure}[10]{r}{0.22\textwidth}
  \vspace{-3pt}
-  \centering{\includegraphics[width=0.22\textwidth]{Figures/PW_fig5.pdf}}
- \vspace{-20pt}
+  \centering{\includegraphics[width=0.21\textwidth]{Figures/PW_fig5.pdf}}
+ \vspace{-7pt}
   \caption{\label{fig:flow_rupture} \footnotesize Rupture of a
@@
 rates, viscous forces exceed the hydrophobic attraction leading to
- vesicle rupture~\cite{C8SM01501E}, at which point the flow carries away segmented membrane patches
-(Figure \ref{fig:flow_rupture}).
+ vesicle rupture~\cite{C8SM01501E}, at which point the flow carries away
+ segmented membrane patches (Figure \ref{fig:flow_rupture}).
 

### 2020-12-23 NSF2020/Description/specificaim1_ver2.tex
left overs from NSF2020 proposal

@@
 \begin{wrapfigure}[11]{l}{0.47\textwidth}
-\centerline{\includegraphics[width=0.47\textwidth]{Figures/Deformations.pdf}}
+\centerline{\includegraphics[width=0.46\textwidth]{Figures/Deformations.pdf}}
 %  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
@@
 %
-\begin{wrapfigure}[9]{r}{0.43\textwidth}
-\vspace{-0.4cm}
-\centerline{\includegraphics[width=0.43\textwidth]{Figures/Flattening.pdf}}
+\begin{wrapfigure}[11]{r}{0.43\textwidth}
+%\vspace{-0.4cm}
+\centerline{\includegraphics[width=0.42\textwidth]{Figures/Flattening.pdf}}
 %  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
-\vspace{-0.5cm}
+%\vspace{-0.5cm}
 \caption{\label{fig:flattening} \footnotesize Example of computing
@@
 %
+
 This yields a dissipation of the total potential \eqref{eq:total_poten}, which
@@
 %
-\begin{wrapfigure}[11]{l}{0.32\textwidth}
-\centerline{\includegraphics[width=0.32\textwidth]{Figures/SaddleSplayDiagram.pdf}}
-  \vspace{-8pt}
-\caption{\label{fig:saddle_splay} \footnotesize Example of determining the
-  saddle splay modulus.}
-\end{wrapfigure}
 We propose to conduct calculations similar to the example of Figure~\ref{fig:flattening}
@@
 More generally, PI RR has shown that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}. 
-As a result, saddle splay can be quantified from the transition energies of a least energy path of pore formation (Figure \ref{fig:saddle_splay}).   
+As a result, saddle splay can be quantified from the transition energies
+of a least energy path of pore formation  (Figure 6).
+%(Figure \ref{fig:saddle_splay}).   
 %Using the string method, we will evaluate the transition energies between the intact pancake shape,
@@
 %
-
 %The proposed particle-based simulations of the HARP model in equations~\ref{SGD} also allow direct examination on the assumption of quadratic form of the elastic energy density.
@@
 %The particle-based HARP model provides a unique opportunity to examine the validity of the quadratic elastic energy, and the PIs propose to examine how (if) any deviation from the quadratic elastic energy may depend on the microscopic details of the amphiphilic particles and their interactions.
-
 %\subsubsection{HK elastic energy form}
 
-\noindent{\bf{HK elastic energy form:}}
-The field of membrane continuum mechanics still lacks consensus as to whether \eqref{ansatz3} is the appropriate functional for bilayer energy.
+%\noindent{\bf{HK elastic energy form:}}
+The field of membrane continuum mechanics still lacks consensus as to
+whether HK energy is the appropriate functional for bilayer energy.
 \textbf{(i)} Researchers have assumed that $\KT = 0$ to effect lateral fluidity in
@@
 TerziDeserno17}.
+\begin{wrapfigure}[11]{l}{0.32\textwidth}
+\centerline{\includegraphics[width=0.31\textwidth]{Figures/SaddleSplayDiagram.pdf}}
+%  \vspace{-8pt}
+\caption{\label{fig:saddle_splay} \footnotesize Example of determining the
+  saddle splay modulus.}
+\end{wrapfigure}
 %

### 2021-01-14 doc/scaling_laws.tex
adding a doc folder

\documentclass[12pt,letterpaper, onecolumn]{article}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{epsfig}
\usepackage{subcaption}
\usepackage{sectsty}
\usepackage{amssymb}
\usepackage{amsmath,empheq}
\usepackage[top=1in, bottom=1in, left=0.5in, right=0.5in]{geometry}

\begin{document}
\topmargin=-100pt
\title{Nondimensionalization of Lipid Dynamics Model}
\maketitle

\Large
Length scale: a half of lipid length $[L]=1.25\ \text{nm}$\\

water viscosity at $20^\circ$C$=293.15^\circ$K: $\mu=1\ \text{cP}= 10^{-12}\ \frac{\text{kg}}{\text{sec}\cdot\text{nm}}$  \\

Line tension $\gamma=\frac{45}{11}$ mJ/nm$=1\ $kT/nm $\approx 4.1$ pN nm\\

set force scale $[F]=\gamma$, we obtain\\

time scale $\displaystyle [T] = \frac{\mu [L]^2}{[F]} = \frac{11\cdot 10^{-12}\ \frac{\text{kg}}{\text{sec}\cdot\text{nm}}\cdot 1.25^2\ \text{nm}^2}
{4.5\cdot10^{-2}\ \frac{\text{kg}\cdot\text{nm}}{\text{sec}^2}} 
\approx 3.82\times10^{-10}\ $sec\\

Energy scale $[E] = [F][L] = 1\cdot1.25\ $kT $= 5.13\ $pN nm\\

\newpage
dimensionless shear rate $\chi = \dot\gamma [T]$\\

(ref. Finken, Eur. Phys. J. E. {\bf 25}, 2008)

For $N=50$ vesicle simulations, the initial radius of the vesicle is \\ $R_0=6.75 [L] = 8.4375$ nm, the bending rigidity $\kappa=8.51$ kT $\approx35$ pN nm (SIAM MMS paper)\\

\Large
$\chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa} = \dot\gamma \cdot\frac{  10^{-12}\frac{\text{ kg}}{\text{sec $\cdot$ nm}} \times 8.4375^3 \text{ nm}^3}{ 35\times 10^{-3} \frac{\text{ kg}\cdot\text{nm}^2}{\text{sec}^2}} = \dot\gamma \cdot 17.16\times10^{-9}$ sec $ = \dot\gamma \cdot 44.92[T]$. \\

(ref. Brandner et al.)
In Figure 7, the shear rates are \\(a) $\dot\gamma = 3.7\times10^7\ s^{-1}$; (b) $\dot\gamma = 1.9\times10^9\ s^{-1}$; (c) $\dot\gamma = 3.7\times10^9\ s^{-1}$\\

By applying our timescale [T], we have all dimensionless shear rates: \\
(a) $\chi = 0.0141$; (b) $\chi = 0.7258$; (c) $\chi = 1.41$.\\
%Moreover, the paper mentions that the time step is 10 fs. This suggests that we can 
%use $\Delta t \approx 2.5\times10^{-5}$\\

If we adopt the scaling law from Finken's paper with $R_0=10$ nm, then we have 
$\chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa} \approx \dot\gamma \cdot 75[T]$.

\end{document}

### 2021-01-14 code/examples/shear_input.m
adding a script and update tstep.m

@@ -1,0 +1,51 @@
+clear
+% clf
+format long e
+format compact
+
+prams.N = 32;
+
+dt      = 0.1;
+prams.m = 50;      % number of time steps
+prams.T = prams.m*dt; % time horizon
+
+prams.order = 2;      % time-stepping order 
+
+prams.rho = 2.0;      % screen length
+prams.gam = 1.0;      % molecular tension
+
+prams.RepulLength   = 0.5; % repulsion length
+prams.RepulStrength = 4.0; % repulsion strength
+
+options.farField  = 'shear';
+options.shearRate = 0.0;
+options.saveData  = false;
+options.fileBase  = 'shear';
+options.append    = false;
+options.inear     = true;
+options.usePreco  = false;
+options.verbose   = true;
+options.timeOrder = 1;
+options.gmresTol  = 1e-5;
+options.usePlot   = true; %false;
+options.plotAxis  = 30*[-1 1 -1 1];
+
+% initial centers
+data = load('N3_0.dat');
+x = 5*data(:,1)';
+y = data(:,2)';
+xc = [x;y];
+
+prams.nb = size(xc,2); % number of bodies
+
+[options,prams] = initRigid2D(options,prams);
+
+tau   = data(:,3)';
+radii = 1*ones(1,prams.nb);
+ar    = 1*ones(1,prams.nb);
+
+prams.tau   = tau;
+prams.radii = radii;
+prams.ar    = ar;
+
+[Xfinal, trajectory] = rigid2D(options,prams,xc,tau);

### 2021-01-14 code/src/tstep.m

@@ -43,7 +43,7 @@ end % constructor: tstep
 
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function [Up,wp,iterYukawa,iterStokes,etaYukawa,etaStokes] = timeStep(o,geom,etaY0,etaS0)
+function [Up,wp,iterYukawa,iterStokes,etaYukawa,etaStokes, fforce, torque] = timeStep(o,geom,etaY0,etaS0)
 % Main time stepping routine
 oc     = curve;
 N      = geom.N;
@@ -63,7 +63,7 @@ end
 % START OF REPULSION CALCULATION
  
 op = poten(geom.N,geom.rho);
-[R1, R2, RTq] = op.Repul(geom);
+[R1, R2, RTq, pp] = op.Repul(geom);
 
 % END OF REPULSION CALCULATION
 
@@ -111,135 +111,37 @@ end
 [F1,F2,Tq] = op.evalForcesQBX(geom,etaYukawa);
 % lift Tq so that it is for rotation about center (not origin)
 
+% tst = fopen("HAP_force_distance.dat", "r");
+% if tst == -1
+%     fid = fopen("HAP_force_distance.dat", "w");
+% else 
+%     fclose(tst);
+%     fid = fopen("HAP_force_distance.dat", "a");
+% end
+% fprintf(fid,"%d %d\n", [geom.center(1,2) - geom.center(1,1) - 2,  F1(1)]');
+% fclose(fid);
+%fprintf("%d %d\n", [geom.center(1,2) - geom.center(1,1) - 2,  F1(1)]');
+
+
+
 %outputs: 
-force  = [F1 + R1, F2 + R2].';
-force  = force(:);
-torque = Tq + RTq;
-
-%format shortg
-
-%[sum(F1 + R1), sum(F2 + R2) Tq' RTq' ]
-
-% dS = velocity*dt = |dx/dt| dt
-% sa = |dx/dt|
-% dt = 2*pi/N
-
-%N    = geom.N;                % number of points per componenet
-%Nb   = geom.nb;               % number of rigid bodies
-%x1   = geom.X(1:N,:);         % grid points on curves 
-%x2   = geom.X(N+1:2*N,:);            
[…]

### 2021-01-14 code/src/capsules.m
updated src files

@@ -95,20 +95,21 @@ function [NearSelf,NearOther] = getZone(o,bd2,relate)
 % contains additional target points.  The
 % values of relate corresond to
 % relate == 1  => only require NearSelf  (ie. bd1 to bd1)
-% relate == 2  => only requirpe NearOther (ie. bd1 to bd2)
+% relate == 2  => only require NearOther (ie. bd1 to bd2)
 % relate == 3  => require both NearSelf and NearOther
 
 NearSelf = [];
 NearOther = [];
 
-N1 = o.N; % number of source/target points
+N1 = o.N;  % number of source/target points per boundary component
 nb = o.nb; % number of source/target boundaries
-X1 = o.X; % source and target points
+X1 = o.X;  % source and target points
 oc = curve;
 [xsou,ysou] = oc.getXY(X1);
 % separate targets into x and y coordinates
 
 h = max(o.length)/N1;
+
 % smallest arclength over all boundaries
 ptsperbox = 10;
 % Estimate for number of points per box.  This simply sets the

### 2021-01-14 code/src/monitor.m

@@ -30,10 +30,10 @@ o.OUTPUTPATH_LOG = '../output/logs/';
 o.verbose = options.verbose;
 % write data to console
 
-o.save = options.saveData;
+o.save     = options.saveData;
 o.dataFile = [o.OUTPUTPATH_DATA, options.fileBase, '.bin'];
-o.velFile = [o.OUTPUTPATH_VEL, options.fileBase, '_vel.bin'];
-o.logFile = [o.OUTPUTPATH_LOG, options.fileBase, '.log'];
+o.velFile  = [o.OUTPUTPATH_VEL, options.fileBase, '_vel.bin'];
+o.logFile  = [o.OUTPUTPATH_LOG, options.fileBase, '.log'];
 
 o.usePlot  = options.usePlot;
 o.plotAxis = options.plotAxis;
@@ -128,11 +128,10 @@ if o.save;
   fwrite(fid,[N;nb],'double');
   fwrite(fid,yukawaRHS(:),'double'); % yukawa right hand side
   fclose(fid);
-  
+
   fid = fopen(o.velFile,'w');
   fwrite(fid,[N;nb],'double');
   fclose(fid);  
-  
 end
 
 end % initializeFiles

### 2021-01-14 code/src/poten.m

@@ -1365,8 +1365,10 @@ end
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function [R1, R2, RTq] = Repul(o, geom)
-    
+function [R1, R2, RTq, pp] = Repul(o, geom)
+
+%pp are point pairs (p1, p2, q1, q2) of interacting points
+
 N    = geom.N;                % number of points per componenet
 Nb   = geom.nb;               % number of rigid bodies
 x1   = geom.X(1:N,:);         % grid points on curves
@@ -1382,7 +1384,8 @@ M  = geom.RepulStrength; % repulsion strength
 % temporarily alter geom.length parameter  
 % for present purposes
 h_store = geom.length;          
-geom.length = l0*geom.N/2;
+
+geom.length = l0*N/2;
 
 NearOther = geom.getZone([],1); % get near structure 
 
@@ -1396,7 +1399,7 @@ icp = NearOther.icp;
 R1 = zeros(geom.nb,1); % repulsive force 
 R2 = zeros(geom.nb,1); % repulsize force  
 RTq = zeros(geom.nb,1); % repulsive torque
-
+pp  = [];
 
 for p = 1:Nb
   [iq, qq, jp] = find(icp{p}); %an N by nb sparse matrix         
@@ -1440,21 +1443,23 @@ for p = 1:Nb
     r1 = -dR*r1;
     r2 = -dR*r2; 
 
-    R1(p)  = R1(p) + r1;
-    R2(p)  = R2(p) + r2;            
+    R1(p)  = R1(p)  + r1;
+    R2(p)  = R2(p)  + r2;            
     RTq(p) = RTq(p) + r1.*(x2nrt-pc2(p)) - r2.*(x1nrt-pc1(p));
-    
-%     hold off
-%     plot(x1, x2, 'k');
-%     hold on
-%     plot(pc1(p), pc2(p), 'o', pc1(q_list), pc2(q_list), '*')
-%     plot(x1(:,p), x2(:,p), 'r');
-%     plot(x1(:,q), x2(:,q), 'm'); 
[…]

### 2021-01-14 code/src/rigid2D.m

@@ -14,7 +14,9 @@ om.plotData(geom);
 om.initializeFiles(geom);
 
 time = 0;
-step = 0;
+step0 = 0;
+
+step = step0;
 
 xc0  = xc;
 tau0 = tau;
@@ -46,10 +48,10 @@ while step < prams.m
   
   %Adams-Bashforth 
   elseif prams.order == 2
-    if step == 0
+    if step == step0
       % update geometry
       geom0 = capsules(prams,xc0,tau0);
-      [Up0, wp0,~,~,etaY0,etaS0] = tt.timeStep(geom0,geom0.X,geom0.X);
+      [Up0, wp0,~,~,etaY0,etaS0,force,torque] = tt.timeStep(geom0,geom0.X,geom0.X);
 
       % write the velocity to a file
       om.writeVelData(time,Up0,wp0);
@@ -62,9 +64,9 @@ while step < prams.m
       time = time + tt.dt;
 
       % write current time to console
-      message = ['Completed time ', num2str(time,'%4.2e'), ...
-          ' of time horizon ' , num2str(prams.T,'%4.2e')];
-      om.writeMessage(message);
+      %message = ['Completed time ', num2str(time,'%4.2e'), ...
+      %           ' of time horizon ' , num2str(prams.T,'%4.2e')];
+      %om.writeMessage(message);
       
       % write the shape to a file
       om.writeData(time,geom0.center,geom0.tau,geom0.X);
@@ -77,7 +79,7 @@ while step < prams.m
     end
       
     geom1 = capsules(prams,xc1,tau1);
-    [Up1, wp1,~,~,etaY,etaS] = tt.timeStep(geom1,etaY0,etaS0);
+    [Up1, wp1,~,~,etaY,etaS,force,torque] = tt.timeStep(geom1,etaY0,etaS0);
     etaY0 = etaY; etaS0 = etaS;
       
     % Applying two-step Adams-Bashforth
@@ -91,8 +93,8 @@ while step < prams.m
     geom2 = capsules(prams,xc2,tau2);
   end
 
-  om.plotData(geom2);
-    
+  % om.plotData(geom2);
+  
   % update time
   time = time + tt.dt;
 
@@ -102,16 +104,17 @@ while step < prams.m
   om.writeMessage(message);
   
   % write the shape to a file
-  om.writeData(time,geom2.center,geom2.tau,geom2.X);
+  %om.writeData(time,geom2.center,geom2.tau,geom2.X);
 
[…]

### 2021-01-14 code/src/tstep.m

@@ -43,7 +43,7 @@ end % constructor: tstep
 
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function [Up,wp,iterYukawa,iterStokes,etaYukawa,etaStokes, fforce, torque] = timeStep(o,geom,etaY0,etaS0)
+function [Up,wp,iterYukawa,iterStokes,etaYukawa,etaStokes,fforce,torque] = timeStep(o,geom,etaY0,etaS0)
 % Main time stepping routine
 oc     = curve;
 N      = geom.N;
@@ -122,26 +122,38 @@ end
 % fclose(fid);
 %fprintf("%d %d\n", [geom.center(1,2) - geom.center(1,1) - 2,  F1(1)]');
 
+%{
+ th = linspace(0, 2*pi)'; 
+ hold off
+ plot(center(1,:), center(2,:), 'ob');
+ hold on
+ plot(center(1,:) + radii.*cos(th), center(2,:) + radii.*sin(th), 'b');
+ l0 = geom.RepulLength;
+ plot(center(1,:) + (radii+l0).*cos(th), center(2,:) + (radii+l0).*sin(th), 'r:');
+ quiver(center(1,:), center(2,:), R1', R2', 0, 'r');
+% quiver(center(1,:), center(2,:), F1', F2', 'm');
+if pp
+   plot([pp(:,1) pp(:,3)], [pp(:,2) pp(:,4)], 'k*');
+end
 
+ axis equal
+pause(0.01)
+%}
 
 %outputs: 
 fforce  = [F1 + R1, F2 + R2].';
-% size(fforce)
-% pause
-% force  = fforce(:);
-fforce = [0, -3; 0, 3; 0, 0 ].';
 force  = fforce(:);
-% torque = 0*Tq + 0*RTq;
-torque = 0*[1; 2; 3];
+torque = Tq + RTq;
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % solve mobility problem here
+
 % far field condition plus the stokeslet and rotlet terms
 rhs = o.farField(X) + o.StokesletRotlet(geom,force,torque);
 
[…]

### 2021-01-19 code/examples/shear.m
debugging the drift that we saw earlier

@@ -9,7 +9,7 @@ format compact
 % for jj=0:3
 % prams.N = 2^jj*32; % points per body
 
-prams.N = 64;
+prams.N = 32;
 
 prams.T = 1.0; % time horizon
 prams.m = 10; % number of time steps
@@ -23,7 +23,7 @@ prams.RepulLength = 0.3; % repulsion length
 prams.RepulStrength = 0.5; % repulsion strength
 
 options.farField  = 'shear';
-options.shearRate = 0;
+options.shearRate = 0.1;
 % options.janusbc   = 2;        % put power of function here
 options.saveData  = true;
 options.saveVel   = true;

### 2021-01-19 code/examples/shear_input.m

@@ -5,8 +5,8 @@ format compact
 
 prams.N = 32;
 
-dt      = 0.1;
-prams.m = 50;      % number of time steps
+dt      = 5*0.1;
+prams.m = 5*50;      % number of time steps
 prams.T = prams.m*dt; % time horizon
 
 prams.order = 2;      % time-stepping order 
@@ -26,13 +26,13 @@ options.inear     = true;
 options.usePreco  = false;
 options.verbose   = true;
 options.timeOrder = 1;
-options.gmresTol  = 1e-5;
+options.gmresTol  = 1e-10;
 options.usePlot   = true; %false;
-options.plotAxis  = 30*[-1 1 -1 1];
+options.plotAxis  = 5*[-1 1 -1 1];
 
 % initial centers
 data = load('N3_0.dat');
-x = 5*data(:,1)';
+x = data(:,1)';
 y = data(:,2)';
 xc = [x;y];
 

### 2021-01-19 code/src/rigid2D.m

@@ -52,6 +52,8 @@ while step < prams.m
       % update geometry
       geom0 = capsules(prams,xc0,tau0);
       [Up0, wp0,~,~,etaY0,etaS0,force,torque] = tt.timeStep(geom0,geom0.X,geom0.X);
+      sum(Up0')
+      sum(wp0)
 
       % write the velocity to a file
       om.writeVelData(time,Up0,wp0);
@@ -81,6 +83,8 @@ while step < prams.m
     geom1 = capsules(prams,xc1,tau1);
     [Up1, wp1,~,~,etaY,etaS,force,torque] = tt.timeStep(geom1,etaY0,etaS0);
     etaY0 = etaY; etaS0 = etaS;
+    sum(Up1')
+    sum(wp1)
       
     % Applying two-step Adams-Bashforth
     xc2  = xc1  + tt.dt*(1.5*Up1 - 0.5*Up0 );
@@ -93,7 +97,7 @@ while step < prams.m
     geom2 = capsules(prams,xc2,tau2);
   end
 
-  % om.plotData(geom2);
+  om.plotData(geom2);
   
   % update time
   time = time + tt.dt;

### 2021-01-19 code/src/tstep.m

@@ -153,7 +153,7 @@ rhs = o.farField(X) + o.StokesletRotlet(geom,force,torque);
 
 % append body force and torque to the background flow to complete the
 % right hand side for GMRES
-rhs = [-rhs(:); 0*force; 0*torque];
+rhs = [-rhs(:); force; torque];
 
 op = poten(N,rho);
 % build double-layer potential matrix
@@ -384,7 +384,6 @@ vLets = zeros(2*N,nb);
 
 [x,y] = oc.getXY(X);
 for k = 1:nb
-
   [cx,cy] = oc.getXY(geom.center(:,k));
 
   fx = force(2*(k-1) + 1);

### 2021-01-23 code/examples/shear_input.m
RJR

@@ -3,7 +3,7 @@ clear
 format long e
 format compact
 
-prams.N = 32;
+prams.N = 16;
 
 dt      = 0.2;
 prams.m = 500*10;      % number of time steps
@@ -18,7 +18,7 @@ prams.RepulLength   = 0.5; % repulsion length
 prams.RepulStrength = 4.0; % repulsion strength
 
 options.farField  = 'shear';
-options.shearRate = 0.07;
+options.shearRate = 0.001;
 options.saveData  = false;
 options.fileBase  = 'shear';
 options.append    = false;
@@ -28,18 +28,18 @@ options.verbose   = true;
 options.timeOrder = 2;
 options.gmresTol  = 1e-10;
 options.usePlot   = true; %false;
-options.plotAxis  = [-10 10 -4 4];
+options.plotAxis  = [-20 20 -20 20];
 
 % tracers 
 axs = options.plotAxis;
-N = 1000;
+N = 2000;
 xx = (axs(2) - axs(1)).*rand(N,1) + axs(1);
 yy = (axs(4) - axs(3)).*rand(N,1) + axs(3);
 XX = [xx yy];
 save("-ascii", "tracers.dat", "XX");
 
 % initial centers
-data = load('N3_0.dat');
+data = load('N52_0.dat');
 x = data(:,1)';
 y = data(:,2)';
 xc = [x;y];
@@ -50,7 +50,7 @@ prams.nb = size(xc,2); % number of bodies
 
 tau   = data(:,3)';
 radii = 1.0*ones(1,prams.nb);
-ar    = 1.5*ones(1,prams.nb);
+ar    = 1.0*ones(1,prams.nb);
 
 prams.tau   = tau;
 prams.radii = radii;

### 2021-01-23 code/src/poten.m

@@ -1600,91 +1600,7 @@ save("-ascii", "../examples/tracer_vel.dat", "VEL");
 
 end % bulkVelocity
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function tracerVelocity(o,geom,eta,Up,wp,force,torque);
-% form the velocity in the fluid bulk and along rigid bodies and plot
-% them.
 
-oc = curve;
-X = geom.X;
-[x,y] = oc.getXY(X);
-
-% load tracers as target points
-X_tar = load("../examples/tracers.dat");
-x_tar = X_tar(:,1);
-y_tar = X_tar(:,2);
-
-% put in capsules-like structure so that it can be passed into getZone
-bd2.N  = numel(x_tar);
-bd2.nb = 1;
-bd2.X  = [x_tar; y_tar];
-
-% Construct near-singular integration structure so that velocity can be
-% evaulated in bulk.
-[~,NearOther] = geom.getZone(bd2,2);
-
-jump = 0.5;
-kernel = @o.exactStokesDL;
-kernelSelf = @(z) +jump*z + o.exactStokesDLdiag(geom,geom.DLPStokes,z);
-
-vel = o.nearSingInt(geom,eta,kernelSelf,NearOther,...
-    kernel,kernel,bd2,false,false);
-
-% Add on Rotlets and Stokeslets
-for k = 1:geom.nb
-  [cx,cy] = oc.getXY(geom.center(:,k));
-
-  fx = force(2*(k-1) + 1);
-  fy = force(2*(k-1) + 2);
-  tor = torque(k);
-
-  rx = x_tar(:) - cx;
-  ry = y_tar(:) - cy;
-  rho2 = rx.^2 + ry.^2;
-  rdotf = rx*fx + ry*fy;
-  vel = vel + (1/4/pi)*...
-      [-0.5*log(rho2)*fx + rdotf./rho2.*rx;...
-       -0.5*log(rho2)*fy + rdotf./rho2.*ry];
-
-  vel = vel + (1/4/pi)*tor*[-ry./rho2;+rx./rho2];
-end
-
-[velx,vely] = oc.getXY(vel);
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% calculate some cutoffs 
[…]

### 2021-01-23 code/src/rigid2D.m

@@ -119,10 +119,7 @@ while step < prams.m
   % update step counter
   step = step + 1;
   
-  DATA = [xc1(1,:)' xc1(2,:)' tau1' force(1,:)' force(2,:)' torque];
-  fileName = sprintf("../output/data/frames/N%d_%f_%d.dat", geom2.nb, options.shearRate, step);
-  save("-ascii", fileName, "DATA");
-
+  
   % update tracers
   XX = load("../examples/tracers.dat");
   UU = load("../examples/tracer_vel.dat");
@@ -141,9 +138,16 @@ while step < prams.m
   XX(it,2) = options.plotAxis(3);
   
   save("-ascii", "../examples/tracers.dat", "XX");
+  
+  % output data
+  
+  DATA = [xc1(1,:)' xc1(2,:)' tau1' force(1,:)' force(2,:)' torque];
+  fileName = sprintf("../output/data/frames/N%d_%f_%d.dat", geom2.nb, options.shearRate, step);
+  save("-ascii", fileName, "DATA");
+ 
   fileName = sprintf("../output/data/frames/N%d_%f_%d.tracer", geom2.nb, options.shearRate, step);
   save("-ascii", fileName, "XX");  
-  
+
 end
 
 % save final time step

### 2021-01-25 code/src/tstep.m
added Taylor-Green

@@ -220,7 +220,7 @@ for k = 1:nb
   wp(k) = sigma(2*N*nb+2*nb+k);
 end
 
-[mean(Up(1,:)); mean(Up(2,:))]
+%[mean(Up(1,:)); mean(Up(2,:))]
 %Up = Up - [mean(Up(1,:)); mean(Up(2,:))];
 
 % Routine to compute the velocity in the bulk and use the rigid body
@@ -300,14 +300,12 @@ for k = 1:nb
                 (+(geom.X(1:end/2,k) - geom.center(1,k)))*wp(k);
 end
 
-%TODO: See equation (37) in Lu, Rahimian, and Zorin
 % EVALUTATE FORCES ON FIBERS
 for k = 1:nb
   valForce(1,k) = 1/(2*pi)*sum(eta(1:N,k).*geom.sa(:,k))*2*pi/N;
   valForce(2,k) = 1/(2*pi)*sum(eta(N+1:2*N,k).*geom.sa(:,k))*2*pi/N;
 end
 
-%TODO: See equation (37) in Lu, Rahimian, and Zorin
 % EVALUATE TORQUES ON FIBERS
 for k = 1:nb
   valTorque(k) = 1/(2*pi)*sum((-(geom.X(N+1:2*N,k)-geom.center(2,k)).*eta(1:N,k) + ...
@@ -376,6 +374,8 @@ switch options.farField
     vInf = [shearRate*y;zeros(N,nb)];
   case 'extensional'
     vInf = shearRate*[-x;y];
+  case 'taylorgreen'
+    vInf = shearRate*[-cos(x).*sin(y);sin(x).*cos(y)];
   otherwise
     vInf = zeros(2*N,nb);
 end

### 2021-02-10 doc/main_jfm.tex
upload JFM template

\documentclass[lineno]{jfm}

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\hypersetup{
    colorlinks = true,
    urlcolor   = blue,
    citecolor  = black,
}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

% {\MakeUppercase{\romannumeral #1}}

\title{Behavior of a Two-Dimensional Vesicle Under a Shear Flow via Integral Equation Method}

%\author{Alan N. Jones\aff{1}
%  \corresp{\email{JFMEditorial@cambridge.org}},
%  H.-C. Smith\aff{1}
% \and J.Q. Long\aff{2}}
%
%\affiliation{\aff{1}STM Journals, Cambridge University Press, The Printing House, Shaftesbury Road, Cambridge CB2 8BS, UK
%\aff{2}DAMTP, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WA, UK}

\author{Rolf Ryham\aff{1},
Bryan Quaife\aff{2},
Szu-Pei Fu\aff{1}
\and Yuan-Nan Young\aff{3}
}
 \affiliation{
\aff{1} Department of Mathematics, \\Fordham University, Bronx, New York 10458, USA
\aff{2}Department of Scientific Computing, \\Florida State University, Tallahassee, Florida 32306, USA
\aff{3}Department of Mathematical Sciences, New Jersey Institute of Technology,\\ Newark, New Jersey 07102, USA
 }

\begin{document}
\maketitle

\begin{abstract}
In this work, we study the dynamics of many-body systems immersed in a viscous fluid with a specified interparticle force. In particular, we apply a hydrophobic attraction potential (HAP) using a Janus type granular system to model lipid bilayer membranes. Coupling with an efficient integral equation method for rigid bodies in Stokes flow and an previous developed HAP solver, the deformations of a two-dimensional vesicle such as tank-treading motion and membrane ruptures can be observed under different values of the shear rate. Moreover, an efficient integral equation method is adopted for solving the screened Laplace equation and the mobility problem where it can accurately calculate hydrophobic and hydrodynamic interactions between near touched boundaries.
\end{abstract}

\begin{keywords}
Authors should not enter keywords on the manuscript, as these must be chosen by the author during the online submission process and will then be added during the typesetting process (see \href{https://www.cambridge.org/core/journals/journal-of-fluid-mechanics/information/list-of-keywords}{Keyword PDF} for the full list).  Other classifications will be added at the same time.
\end{keywords}

{\bf MSC Codes }  {\it(Optional)} Please enter your MSC Codes here

\section{\label{intro}Introduction}

%Nature of amphiphilic lipid molecules, small vesicle, GUVs, RBCs, hydrophobic tails interacting with fluid,

%Tank-treading, tumbling, swing vesicles, viscosity ratio

% two-dimensional vesicle, membrane fusion/fissure, self-assembly property,

%crystallization, membrane jiggling can be observed when... the hydrophobicity

%mobility problem, particle suspension, a wide range of study, numerical methods including boundary integral equation method, immersed boundary method, level set method, RCIP kernel splitting method,   vesicle deformations,

% Stokesian dynamics

%The mobility problem can be solved in the fashion of considering propagating waves through rigid bodies where the the external and hydrodynamic forces act as incident fields and scattered field evaluated on the object boundaries.

%The Helfrich membrane energy is well known in continuum modeling/theory. Here we combine the framework in coarse-grained modeling using Janus-type configurations. However,

%Thermal fluctuation effect not considered but the granular system in a fluid

%

%our approach combines the

\subsection{Hydrophobic Attraction Potential (HAP)}

The Hydrophobic attraction potential (HAP) is given by
\begin{equation}
\label{eq:main}
\Phi(\Omega,f) = \gamma  \min_{u \in \mathcal{A}}
 I[u]  = \int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2 \,dx,
\end{equation}
%
where $\gamma$ the interfacial tension, $\rho$ the screened length, and this domain functional describes the energy associated with hydrophobic surfaces~\cite{Fu20}. From the first domain variation of HAP, we obtain a hydrophobic stress tensor which is given as follows,

\begin{equation}
\label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma (\tfrac{1}{2}|\nabla u|^2 \mathbf{I} - \nabla u\otimes \nabla u).
\end{equation}
%
The integration over boundaries gives force and torque due to the hydrophobic attraction and they are given by

\begin{equation}
\int_{\Gamma_i} {\bf T}\cdot \nu_i dS ,\quad \int_{\Gamma_i} ({\bf x}-{\bf a}_i)\times ({\bf T}\cdot \nu_i) dS,
\end{equation}
%
where ${\bf x}$ are points on the boundary $\Gamma_i$, ${\bf a}_i$ is the $i^{th}$ particle center, and $\nu_i$ is the outward normal to the $i^{th}$ particle.

%\begin{equation}
%        \label{SL}
%\begin{cases}
% -\rho^2 \Delta u + u =0 & \text{ in } \Omega,\\
%  u(x) = f(x)  &\text{ on }\Sigma, \\
%   u(x) \to 0, &\text{ as } x \to \infty.
%\end{cases}
%\end{equation}

\subsection{Nondimensionalizations}

For a two-dimensional vesicle, we denote a constant initial radius $R_0$ and 
the dimensionless shear rate is
\begin{equation}
\chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
\end{equation}
%
where $\dot\gamma$ the shear rate, $\kappa$ the bending rigidity, and $\mu$ the fluid viscosity~\cite{Finken08}.

%This paper is organized as follows. Chapter 2 introduces the mobility problem..... The integral equation method for solving $N_b$-body system with details of .... are included in Chapter 3. We provide numerical results of vesicle simulations in Chapter 4. Finally, we conclude the work and briefly give the picture of our future work.

\section{\label{mobility}Mobility Problem}

The governing equation of $N_b$-body bodies suspended in the domain $\Sigma$ is

\begin{gather}
	-\Delta {\bf u} + \mu\nabla p = 0 \qquad \text{in }\Sigma\\
	\nabla\cdot {\bf u}=0 \qquad \text{in }\Sigma\\
	{\bf u}({\bf x}) \to {\bf u}_\infty \quad \text{as}\quad |{\bf x}|\to \infty
\end{gather}
%
where ${\bf u}$ is the velocity, $p$ is the pressure, and ${\bf u}_\infty$ is the background flow. 
%
%\begin{gather}
%\int_{\Gamma_i}(\sigma_{hyd}+\sigma_\infty)\cdot {\bf n} ds = -{\bf F}_i \\
%	\int_{\Gamma_i}(\sigma_{hyd}+\sigma_\infty)\times({\bf x}-{\bf a}_i)\cdot {\bf n} ds =-\tau_i\\
%\end{gather}
%
The mobility problem for $N_b$-body system in a Stokes flow leads to a second-kind boundary integral equations (BIE) with a density function $\eta({\bf x}$ that is given by \cite{Lukas19}
\begin{equation}
\label{mobility}
\begin{aligned}
{\bf v}_i + &\omega_i\times({\bf x}-{\bf a}_i)\\
 =& -\frac12\eta({\bf x}) + D[\eta]({\bf x}) \\
&+ \sum_{i=1}^N\big({\bf S}({\bf x}, {\bf a}_i){\bf F}_i+ {\bf R}({\bf x}, {\bf a}_i)t_i\big)+{\bf u}_\infty, \quad {\bf x}\in\Gamma \\
\end{aligned}
\end{equation}
%
with two constraints 
%
\begin{center}
\begin{equation}
\label{mobility2}
\int_{\partial \Gamma_i}\eta\cdot \nu ds = {\bf 0},
\end{equation}
\end{center}
%
\begin{center}
\begin{equation}
\label{mobility3}
\int_{\partial \Gamma_i}\eta\times({\bf x}-{\bf a}_i)\cdot \nu ds ={\bf 0},
\end{equation}
\end{center}
%
where the two-dimensional Stokeslet and the Rotlet are
%
\begin{gather}
{\bf S}({\bf x}, {\bf a}) = \frac{1}{4\pi}\left(-\log(|({\bf x}-{\bf a})|){\bf I}+\frac{({\bf x}-{\bf a})\otimes({\bf x}-{\bf a})}{|({\bf x}-{\bf a})|^2}\right) \\ 
{\bf R}({\bf x},{\bf a})=\frac{({\bf x}-{\bf a})^\perp}{4\pi|({\bf x}-{\bf a})|^2}.
\end{gather}
%
%Here ${\bf r}={\bf x}-{\bf a}$ and $\rho=|{\bf r}|$.
${\bf F}_i$ and $t_i$ are particle force and torque calculated from action of hydrophobic attractions. From equations~\eqref{mobility}--\eqref{mobility3}, we have translational velocity ${\bf v}_i$, angular velocity $\omega_i$, and density function $\eta$ as unknowns.
This system of equations is then solvable with the use of an iterative method such as GMRES or conjugate gradient iterations.

\section{\label{IEM}Integral Equation Method}

\subsection{Short Range Repulsion}

At each time step, we examine the nearest grid points between each pair of body  boundaries. Within a specified distance $d$, we introduce a short range repulsive potential as follows

\begin{equation}
\Phi_{repul} = 1- \sin\left(\frac{\pi}{2} d\right).
\end{equation}

Here we would like to make a remark about the time marching scheme. From the mobility problem, we obtain velocity and torque profiles of an $N_b$-body system. A second order Adam-Bashforth scheme is used for updating the dynamics but body collisions may occur during the simulation while a relatively large time step is chosen. We therefore impose a short range repulsion that it will be turned on when the distance between two boundary points on different bodies are within one characteristic length.

\section{\label{results}Numerical Results}

\subsection{Single Particle Validations}

Jeffery orbits for single elliptic particle under a shear flow.

\subsection{Tank-Treading Vesicles}

We tune the shear rates, vesicle sizes and .....

Theoretical tank-treading frequency is given by $\dot\gamma/2$.

We also compare the inclination angle against the Jeffery's equation [].

\subsection{Membrane Ruptures}

With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.

\subsection{Two Vesicles in an Extensional Flow}

\section{\label{conclusion}Conclusion}

\begin{acknowledgments}
%We would like to acknowledge 
\end{acknowledgments}

\appendix

\section{Appendixes}

%\bibliographystyle{jfm}
\bibliography{reference}% Produces the bibliography via BibTeX.

%\bibliographystyle{jfm}
%\bibliography{jfm}
%Use of the above commands will create a bibliography using the .bib file. Shown below is a bibliography built from individual items.

%\bibliography{jfm2esam}

%\begin{thebibliography}{99}
%
%\expandafter\ifx\csname natexlab\endcsname\relax
%\def\natexlab#1{#1}\fi
%\expandafter\ifx\csname selectlanguage\endcsname\relax
%\def\selectlanguage#1{\relax}\fi
%
%\bibitem[Batchelor (1971)]{Batchelor59}
%{\sc Batchelor, G.K.} 1971 {Small-scale variation of convected quantities like temperature in turbulent fluid part1, general discussion and the case of small conductivity}, {\it J. Fluid Mech.}, {\bf 5}, pp. 3-113-133.
%
%\bibitem [Bouguet (2008)]{Bouguet01}
%{\sc Bouguet, J.-Y} 2008 Camera Calibration Toolbox for Matlab {\url{http://www.vision.caltech.edu/bouguetj/calib_doc/}}.
%
% \bibitem[Briukhanovetal et al (1967)] {Briukhanovetal1967}
%{\sc Briukhanov, A. V.,   Grigorian, S. S., Miagkov,  S. M., Plam, M. Y.,   I. E. Shurova, I. E.,   Eglit, M. E. and Yakimov, Y. L.} 1967
%{On some new approaches to the dynamics of snow avalanches},
%{\it Physics of Snow and Ice,  Proceedings of the International Conference on Low Temperature Science}
%{Vol 1} pp. 1221--1241 {Institute of Low Temperature Science, Hokkaido University, Sapporo, Hokkaido, Japan}.
%
%\bibitem[Brownell (2004)]{Brownell04}
% {\sc Brownell,  C.J.  and Su,  L.K.} 2004  {Planar measurements of differential diffusion in turbulent jets}, {\it AIAA Paper},  pp. 2004-2335.
%
%\bibitem[Brownell and Su (2007)] {Brownell07}
%  {\sc Brownell, C.J. and  Su, L.K.} 2007 {Scale relations and spatial spectra in a differentially diffusing jet}, {\it AIAA Paper}, pp 2007-1314.
%
%\bibitem [Dennis (1985)] {Dennis85}
% {\sc  Dennis, S.C.R.} 1985 {Compact explicit finite difference approximations to the Navier--Stokes equation},  { In \it Ninth Intl Conf. on Numerical Methods in Fluid Dynamics},  {ed Soubbaramayer and J.P. Boujot},  {Vol 218}, {\it Lecture Notes in Physics}, pp. 23-51. Springer.
%
%\bibitem [Edwards et al. (2017)]{EdwardsVirouletKokelaarGray2017}
%{\sc Edwards, A. N., Viroulet, S., Kokelaar, B. P. and Gray, J. M. N. T.} 2017 Formation of levees, troughs and elevated channels by avalanches on erodible slopes {\it J. Fluid Mech.}, {\bf 823}, pp. 278-315.
%
%\bibitem[Hwang et al (1970)] {Hwang70}
% {\sc Hwang,  L.-S.  and  Tuck, E.O.} 1970 On the oscillations of harbours of arbitrary shape {\it J.~Fluid Mech.}, {\bf42}, pp 447-464.
%
%\bibitem[Josep and Saut (1990)] {JosephSaut1990}
% {\sc Joseph, Daniel D. and Saut, Jean Claude} 1990 Short-wave instabilities and ill-posed initial-value problems {\it Theoretical and Computational Fluid Dynamics}, {\bf 1},  pp.191--227,  {\url{http://dx.doi.org/10.1007/BF00418002}}.
%
%\bibitem[Worster (1992)] {Worster92}
%{ \sc  Worster, M.G.} 1992 The dynamics of mushy layers {\it Interactive dynamics of convection and solidification},
%{(ed. S.H. Davis and H.E. Huppert and W. Muller and M.G. Worster)}, pp. 113--138 {Kluwer}.
%
%\bibitem[Koch(1983)] {Koch83}
%{\sc Koch, W.} 1983 Resonant acoustic frequencies of flat plate cascades {\it J.~Sound Vib.}, {\bf 88}, pp. 233-242.
%
%\bibitem[Lee(1971)] {Lee71}
%{\sc Lee,  J.-J.}  1971 Wave-induced oscillations in harbours of arbitrary geometry {\it J.~Fluid Mech.}, {\bf 45}, pp. 375-394.
%
%\bibitem[Linton and  Evans (1992)] {Linton92}
% {\sc  Linton, C.M. and  Evans, D.V.} 1992 The radiation and scattering of surface waves by a vertical circular cylinder in a channel {\it Phil.\ Trans.\ R. Soc.\ Lond.}, {\bf 338}, pp. 325-357.
%
%\bibitem [Martin(1980] {Martin80}
% {\sc  Martin, P.A.} 1980 On the null-field equations for the exterior problems of acoustics {\it Q.~J. Mech.\ Appl.\ Maths},{\bf 33}, pp. 385--396.
%
%\bibitem [Rogallo(1981)] {Rogallo81}
% {\sc Rogallo,  R.S.} 1981 Numerical experiments in homogeneous turbulence  { {\it Tech. Rep.} 81835}  {NASA Tech.\ Mem}.
%
%\bibitem[Ursell(1950)] {Ursell50}
%{\sc  Ursell, F.} 1950 Surface waves on deep water in the presence of a submerged cylinder i {\it Proc.\ Camb.\ Phil.\ Soc.}, {\bf 46}, pp.141--152.
%
%\bibitem[Wijngaarden (1968)]{Wijngaarden68}
%{\sc van Wijngaarden, L.} 1968 On the oscillations Near and at resonance in open pipes {\it J.~Engng Maths},{\bf 2}, pp. 225--240.
%
%\bibitem[Miller (1991)]{Miller91}
%{ \sc  Miller, P.L.} 1991 Mixing in high Schmidt number turbulent jets {school {PhD thesis}} {California Institute of Technology}.
%
%\end{thebibliography}

%% End of file `jfm2esam.bib'.

\end{document}

### 2021-02-19 doc/main_jfm.tex
RJR uploaded Biros JFM paper

@@
 
-\title{Behavior of a Two-Dimensional Vesicle Under a Shear Flow via Integral Equation Method}
-
+%\title{Two-Dimensional Vesicles Under External Flow via Integral Equation Method}
+\title{Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations}
 %\author{Alan N. Jones\aff{1}
@@
 
-\author{Rolf Ryham\aff{1},
+\author{
+Szu-Pei Fu\aff{1},
 Bryan Quaife\aff{2},
-Szu-Pei Fu\aff{1}
-\and Yuan-Nan Young\aff{3}
+Rolf Ryham\aff{1}, \and
+Yuan-Nan Young\aff{3}
 }

### 2021-02-19 code/examples/shear_input.m

@@ -5,7 +5,7 @@ format compact
 
 prams.N = 16;
 
-dt      = 0.2;
+dt      = 0.4;
 prams.m = 500*10;      % number of time steps
 prams.T = prams.m*dt; % time horizon
 
@@ -18,7 +18,7 @@ prams.RepulLength   = 0.5; % repulsion length
 prams.RepulStrength = 4.0; % repulsion strength
 
 options.farField  = 'shear';
-options.shearRate = 0.001;
+options.shearRate = 0.000001;
 options.saveData  = false;
 options.fileBase  = 'shear';
 options.append    = false;
@@ -39,7 +39,7 @@ XX = [xx yy];
 save("-ascii", "tracers.dat", "XX");
 
 % initial centers
-data = load('N52_0.dat');
+data = load('N52_0.000000_3616.dat');
 x = data(:,1)';
 y = data(:,2)';
 xc = [x;y];

### 2021-03-26 doc/main_jfm.tex
RJR identity in Appendix

@@
 \subsection{Single Particle Validations}
-
 Jeffery orbits for single elliptic particle under a shear flow.
@@
 
-\section{Appendixes}
+\section{Appendices}
+The stress ${\bf T}$ contains the gradient of the double layer potential. This 
+introduces an inherent difficulty in evaluating stress on the boundary.
+To overcome the difficulty of evaluation on $\Sigma_p$, for instance, we decompose $u$ into singular and nonsingular parts:
+\begin{equation}
+u = u_p + v_p
+\end{equation}
+where  
+\begin{equation}
+u_p(x) = \int_{\Sigma_p} \frac{\partial G(x,y)}{\partial \nu} \eta(y) \,\dif S(y).
+\end{equation}
+It turns out that the contribution to the force and torque coming from the singular
+part vanishes. In particular, we will prove the identity
+\begin{equation}
+\label{eq:recipforcetorque}
+F_p + iG_p= \int_{\Sigma_p} ({\bf I}+i{\bf X})J_{p} \,\dif S
+\end{equation}
+where
+ \begin{equation}
+\label{eq:jumpstress1}
+J_{p} &= 2\rho^{-1} \eta  v_p \nu 
++ 2\rho \nabla \eta \cdot \tau_i(\nabla v_p \cdot \tau_i \nu -  \nabla v_p \cdot \nu \tau_i).
+\end{equation}
+Here $\nu$ is the unit normal, $\{\tau_i\}_{i=1}^2$ are orthonormal tangent vectors,
+and ${\bf X}$ is the skew symmetric matrix with axial vector $x$, i.e.
+\[X_{ij} = \varepsilon_{ikj}x_k,\quad {\bf X}v = x\times v\]
+where $\boldsymbol{\varepsilon}$ is the third-order alternating tensor.
+We employ the Einstein summation convention and use complex vectors to streamline the presentation, $i^2 = -1$.
+
+The benefit of using \eqref{eq:recipforcetorque} is that the integrand  is nonsingular.
+The density function $\eta$ has the same smoothness as the boundary data
+and $v_p$ is real-analytic in a neighborhood of $\Sigma_p$.
+
+To prove \eqref{eq:recipforcetorque}, write
+\begin{align*}
+  {\bf T}
+  &=
+  \sigma[u_p,u_p]
+  +(\sigma[u_p,v_p]
+  +\sigma[v_p,u_p])
+  +\sigma[v_p,v_p] \\
+  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
+\end{align*}
+where
+\[
+\sigma[u,v]
+= \rho^{-1} uv {\bf I} + \rho \nabla u \cdot \nabla v {\bf I} - 2 \rho \nabla u \otimes \nabla v.
+\]
+\begin{lemma}
+  \label{eq:stress_div_lemma}
+  \begin{equation}
+    \label{eq:decompdivfree}
+    \nabla \cdot {\bf T}_j = 0, \quad
+    \nabla \cdot (x \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
+  \end{equation}
+\end{lemma}
+\begin{proof}
+  Observe that
+  \begin{align*}
+    (\nabla \cdot {\bf T})_j &=
+    \nabla_k   T_{jk} \\
+    &= \rho^{-1} 2u \nabla_j u + \rho(2\nabla_{kl}^2 u \nabla_l u  - 2 \nabla_{kj}^2 u \nabla_k u
+    - 2 \nabla_j u \nabla_{kk}^2 u )\\
+    &=2\rho^{-1}(-\rho^2 \Delta u + u)\nabla_k u .
+  \end{align*}
+  However, $-\rho^2 \Delta u + u = 0$ and so we get $\nabla \cdot {\bf T} = 0.$
+  Furthermore,
+  \begin{align*}
+    (\nabla \cdot (x\times {\bf T} ))_j
+    &= (\nabla \cdot ({\bf X} {\bf T} ))_j
+    = \nabla_k (X_{jl} T_{lk})
+    = \nabla_k (\epsilon_{jml}x_m T_{lk})\\
+    &= \varepsilon_{jml} T_{lm} + \varepsilon_{jml}x_m \nabla_k T_{lk}\\
+    &= (\boldsymbol{\varepsilon}:{\bf T} + {\bf x} \times \nabla \cdot {\bf T})_j.
+  \end{align*}
+  Since ${\bf T}$ is symmetric $\boldsymbol{\varepsilon}:{\bf T} = {\bf 0}$, and we get
+  $\nabla \cdot (x \times {\bf T}) = 0$ as well.
+
+  The functions $u_p$ and $v_p$ also solve the equation $-\rho^2 \Delta u + u = 0$.  Thus
+  \eqref{eq:decompdivfree} holds for $j = 1, 3$. Finally,
+  \eqref{eq:decompdivfree} holds for $j = 2$ because
+  ${\bf T}_2 = {\bf T} - {\bf T}_1 - {\bf T}_3$.
+\end{proof}
+
+Using Lemma \ref{eq:stress_div_lemma}, we will establish that
+\begin{equation}
+  \label{eq:prejump}
+  F_p + i G_p = \int_{\Sigma_p}  ({\bf U}_2\nu)^+ - ({\bf U}_2\nu)^-\,\dif S
+\end{equation}
+where ${\bf U}_j = ({\bf I} + i {\bf X}){\bf T}_j$ for $j = 1, 2, 3.$
+The stress ${\bf U}_2$ has a jump discontinuity at $\Sigma_p.$
+The plus and minus superscripts denote
+the limit taken along points in $U_p^c$ and along points in $U_p$
+respectively.
+${\bf U}_1$ and ${\bf U}_3$ are real-analytic in a neighborhood of $\overline{U_p}$
+and have no jump-discontinuity at $\Sigma_p$.
+To derive \eqref{eq:prejump}, we expand
+\begin{align*}
+  F_p + i G_p
+  &= \int_{\Sigma_p} {\bf T} \nu + ix \times {\bf T} \nu \,\dif S \\
+  &= \int_{\Sigma_p}  {\bf U}_1\nu  + ({\bf U}_2\nu)^+ + {\bf U}_3\nu\,\dif S
+\end{align*}
+The function $u_p$ is real-analytic and
+$\nabla \cdot {\bf U}_1 = 0$ throughout $\mathbb{R}^n \setminus U_p$.
+By the divergence theorem, we get
+\begin{equation*}
+  \int_{\Sigma_p}  {\bf U}_1 \nu\,\dif S
+  = \int_{\mathrr{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
+\end{equation*}
+Next, $v_p$ is real-analytic and
+$\nabla \cdot {\bf U}_3 = 0$ in $U_p$. Therefore
+\begin{equation*}
+  \int_{\Sigma_p}  {\bf U}_3 \nu\,\dif S
+  = -\int_{U_p} \nabla \cdot {\bf U}_3 \,dx = 0.
+\end{equation*}
+Finally, $\nabla \cdot {\bf U}_2= 0$ in $U_p$. This gives
+\[
+0 = -\int_{U_p} \nabla \cdot {\bf U}_2 \,dx = \int_{\Sigma_p}  ({\bf U}_2 \nu)^-\,\dif S.
+\]
+Combining the last four equations give \eqref{eq:prejump}.
+
+\begin{proof}[Proof of \eqref{eq:recipforcetorque}]
+  The main ingredients of the proof are the jump relations
+  for $u_p$. For $x_0 \in \Sigma_p$,
+  \begin{enumerate}
+  \item $ \lim_{x \to x_0^\pm } u_p(x) = \pm\frac{1}{2}\eta(x_0) + (D\eta)(x_0)$
+  \item $ \lim_{x \to x_0^+ } (\nabla u_p \cdot \nu) (x) = \lim_{x \to x_0^-} (\nabla u \cdot \nu)(x)$
+  \end{enumerate}
+  Furthermore,
+  combining 1. and 2. give
+  \begin{align*}
+    \nabla u_p^+ - \nabla u_p^-
+    &= \nabla (u_p^+ - u_p^-) \cdot t_i t_i +  (\nabla  u_p^+\cdot \nu  - \nabla u_p^- \cdot \nu) \nu\\
+    &= \nabla \eta \cdot \tau_i \tau_i
+  \end{align*}
+  where $\{\tau_i\}_{i=1}^n$ are an orthonormal tangent vectors.
+  We can use these relationships to derive an expression for the jump in
+  normal stress.
+  \begin{align*}
+    &({\bf T}_2\nu)^+ - ({\bf T}_2\nu)^-
+    \\
+    &= 2\rho^{-1} u_p^+v_p \nu + 2\rho \nabla u_p^+ \cdot \nabla v_p \nu
+    - 2 \rho \nabla u_p^+  \nabla v_p \cdot \nu
+    - 2 \rho \nabla v_p  \nabla u_p^+ \cdot \nu\\
+    &-2\rho^{-1} u_p^-v_p \nu - 2\rho \nabla u_p^- \cdot \nabla v_p \nu
+    + 2 \rho \nabla u_p^-  \nabla v_p \cdot \nu
+    + 2 \rho \nabla v_p  \nabla u_p^- \cdot \nu\\
+    &= 2\rho^{-1} \eta v_p \nu + 2\rho \nabla \eta \cdot \tau_i \tau_i \cdot \nabla v_p \nu
+    - 2\rho \nabla \eta \cdot \tau_i \tau_i \nabla v_p \cdot \nu + 0\\
+    &= J_p.
+  \end{align*}
+
+  Applying the above relations to the integrand of \eqref{eq:prejump} yields
+  \[
+  ({\bf U}_2\nu)^+ - ({\bf U}_2\nu)^-
+  =
+  ({\bf I} + i {\bf X})(({\bf T}_2\nu)^+ - ({\bf T}_2\nu)^-)
+  = ({\bf I} + i {\bf X})J_p
+  \]
+  This completes the proof of \eqref{eq:recipforcetorque}.
+\end{proof}
 

### 2021-05-03 code/src/fluidstress.m
fixing fluidstress.m

@@ -7,24 +7,24 @@ oc = curve;
 f = etaS;
 
 % velocity due to the double-layer potential
-[~,velocityDL] = op.exactStokesDL(geom,f,[xtar(:);ytar(:)],(1:2));
+[~,velocityDL] = op.exactStokesDL(geom,f,[xtar(:);ytar(:)],(1:geom.nb));
 % velocity due to Stokeslets and Rotlets
 [~,velocityRS] = op.StokesletRotlet(geom,force,torque,...
-      [xtar(:);ytar(:)],(1:2));
+      [xtar(:);ytar(:)],(1:geom.nb));
 % total velocity
 velocity = velocityDL + velocityRS;
 
 % pressure due to the double-layer potential
-[~,pressureDL] = op.exactStokesDLpressure(geom,f,[xtar(:);ytar(:)],(1:2));
+[~,pressureDL] = op.exactStokesDLpressure(geom,f,[xtar(:);ytar(:)],(1:geom.nb));
 % pressure due to the Stokeslets and Rotlets
-pressureRS = op.RSpressure(geom,force,torque,[xtar(:);ytar(:)],(1:2));
+pressureRS = op.RSpressure(geom,force,torque,[xtar(:);ytar(:)],(1:geom.nb));
 % total pressure
 pressure = pressureDL + pressureRS;
 
 % stress due to the double-layer potential
-[~,stressDL] = op.exactStokesDLstress(geom,f,[xtar(:);ytar(:)],(1:2));
+[~,stressDL] = op.exactStokesDLstress(geom,f,[xtar(:);ytar(:)],(1:geom.nb));
 % stess due to the Stokeslets and Rotlets
-stressRS = op.RSstress(geom,force,torque,[xtar(:);ytar(:)],(1:2));
+stressRS = op.RSstress(geom,force,torque,[xtar(:);ytar(:)],(1:geom.nb));
 % total stress
 stress = stressDL + stressRS;
 

### 2021-05-04 doc/main_jfm.tex
RJR mods
adding some texts

@@
 \usepackage{hyperref}
+\usepackage{mathtools}
+\usepackage{commath}
 \hypersetup{
@@
 \subsection{Single Particle Validations}
-Jeffery orbits for single elliptic particle under a shear flow.
+
+The first study of the proposed numerical algorithm is the Jeffery orbits of single ellipsoidal particle under a shear flow.
+A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the x-axis is $\chi = 90^\circ$.
+Based on the theoretical Jeffery orbits,
+
+\begin{equation}
+\chi = \tan^{-1}\frac{a}{b}\tan \frac{ab \dot\gamma t}{a^2+b^2}
+\end{equation}
+%
+where $a$, $b$ are semi-major and semi-minor axes, $\dot\gamma$ is the shear rate, and the test aspect ration of the particle is $2$.
+Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{JefferyOrbit.eps}
+\end{center}
+  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the intergal equation method.
+  }
+    \label{figure1}
+\end{figure}
 
@@
 \label{eq:recipforcetorque}
-F_p + iG_p= \int_{\Sigma_p} ({\bf I}+i{\bf X})J_{p} \,\dif S
+F_p + iG_p= \int_{\Sigma_p} \gamma ({\bf I}+i{\bf X})J_{p} \,\dif S
 \end{equation}
@@
 \label{eq:jumpstress1}
-J_{p} &= 2\rho^{-1} \eta  v_p \nu 
+J_{p} = 2\rho^{-1} \eta  v_p \nu 
 + 2\rho \nabla \eta \cdot \tau_i(\nabla v_p \cdot \tau_i \nu -  \nabla v_p \cdot \nu \tau_i).
@@
   \label{eq:prejump}
-  F_p + i G_p = \int_{\Sigma_p}  ({\bf U}_2\nu)^+ - ({\bf U}_2\nu)^-\,\dif S
+  F_p + i G_p = \gamma \int_{\Sigma_p}  ({\bf U}_2\nu)^+ - ({\bf U}_2\nu)^-\,\dif S
 \end{equation}
@@
   F_p + i G_p
-  &= \int_{\Sigma_p} {\bf T} \nu + ix \times {\bf T} \nu \,\dif S \\
-  &= \int_{\Sigma_p}  {\bf U}_1\nu  + ({\bf U}_2\nu)^+ + {\bf U}_3\nu\,\dif S
+  &= \gamma \int_{\Sigma_p} {\bf T} \nu + ix \times {\bf T} \nu \,\dif S \\
+  &= \gamma \int_{\Sigma_p}  {\bf U}_1\nu  + ({\bf U}_2\nu)^+ + {\bf U}_3\nu\,\dif S
 \end{align*}
@@
   \int_{\Sigma_p}  {\bf U}_1 \nu\,\dif S
-  = \int_{\mathrr{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
+  = \int_{\mathbb{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
 \end{equation*}
@@
   Furthermore,
-  combining 1. and 2. give
+  combining (i) and (ii) gives
   \begin{align*}

### 2021-05-04 doc/main_jfm.tex
adding some texts

@@
 
-The first study of the proposed numerical algorithm is the Jeffery orbits of single ellipsoidal particle under a shear flow.
-A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the x-axis is $\chi = 90^\circ$.
+The preliminary test of the proposed numerical algorithm is the Jeffery orbits of single ellipsoidal particle under a shear flow.
+A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is $\chi = 0^\circ$.
 Based on the theoretical Jeffery orbits,
@@
 \begin{equation}
-\chi = \tan^{-1}\frac{a}{b}\tan \frac{ab \dot\gamma t}{a^2+b^2}
+\chi = \tan^{-1}\left(\frac{a}{b}\left(\tan \frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
 \end{equation}
@@
 
-We tune the shear rates, vesicle sizes and .....
+To study the deformation of the bilayer structure under a shear flow using the proposed algorithm, 
+we adopt the widely tested numerical simulations in both continuum and molecular dynamics models.
+Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
+the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.
 
-Theoretical tank-treading frequency is given by $\dot\gamma/2$.
+%We tune the shear rates, vesicle sizes and .....
 
-We also compare the inclination angle against the Jeffery's equation [].
+%Theoretical tank-treading frequency is given by $\dot\gamma/2$.
+
+%We also compare the inclination angle against the Jeffery's equation [].
 

### 2021-05-04 doc/main_jfm.tex
adding some texts

@@
 \end{center}
-  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the intergal equation method.
+  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the result from the integral equation method.
   }
@@
 the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=0.4\textwidth]{N58_0.eps}
+\includegraphics[width=0.4\textwidth]{N58_20000.eps}
+\end{center}
+  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
+  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle.
+  }
+    \label{figure2}
+\end{figure}
 

### 2021-05-04 doc/main_jfm.tex
adding some texts

@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
 \begin{center}
@@
 
-\subsection{Two Vesicles in an Extensional Flow}
+\subsection{Two Vesicles in a Linear Flow}
+
+Figure~\ref{figure3} shows two sets of simulations.
+Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
+The flow is stretching along the $y$ direction and squeezing in $x$ direction.
+Hence two vesicles are first pushed toward each other  then separate.
+With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $x = \dot\gamma y$.
+An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
+\includegraphics[width=0.22\textwidth]{N116_ext_2500.eps}
+\includegraphics[width=0.22\textwidth]{N116_ext_5000.eps}
+\includegraphics[width=0.22\textwidth]{N116_ext_7500.eps}\\
+\includegraphics[width=0.22\textwidth]{N116_shear_3000.eps}
+\includegraphics[width=0.22\textwidth]{N116_shear_6000.eps}
+\includegraphics[width=0.22\textwidth]{N116_shear_9000.eps}
+\includegraphics[width=0.22\textwidth]{N116_shear_12000.eps}
+\end{center}
+  \caption{Two vesicles under a linear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a) and two sets of simulation results are two vesicles under
+  (b)-(d) extensional flow and (e)-(h) shear flow. 
+  }
+    \label{figure3}
+\end{figure}
 

### 2021-05-05 doc/main_jfm.tex
adding some texts

@@
 %
-where $a$, $b$ are semi-major and semi-minor axes, $\dot\gamma$ is the shear rate, and the test aspect ration of the particle is $2$.
+where $a$, $b$ are semi-major and semi-minor axes, $\dot\gamma$ is the shear rate, and the test aspect ratio of the particle is $2$.
 Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.
 
-\begin{figure}[h!]
+\begin{figure}
 \begin{center}
@@
 
-To study the deformation of the bilayer structure under a shear flow using the proposed algorithm, 
-we adopt the widely tested numerical simulations in both continuum and molecular dynamics models.
+To study the deformation of the closed bilayer structure under a shear flow using the proposed algorithm, 
+we adopt a widely tested numerical simulation in both continuum and molecular dynamics models.
+The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
 Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \begin{center}
-\includegraphics[width=0.4\textwidth]{N58_0.eps}
-\includegraphics[width=0.4\textwidth]{N58_20000.eps}
+\includegraphics[width=0.3\textwidth]{N58_0.eps}
+\includegraphics[width=0.3\textwidth]{N58_20000.eps}
 \end{center}
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.4\textwidth]{N58_rupt_0.eps}
+\includegraphics[width=0.4\textwidth]{N58_rupt_200.eps}\\
+\includegraphics[width=0.4\textwidth]{N58_rupt_400.eps}
+\includegraphics[width=0.4\textwidth]{N58_rupt_600.eps}
+\end{center}
+  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$.
+  }
+    \label{figure3}
+\end{figure}
+
 \subsection{Two Vesicles in a Linear Flow}
 
-Figure~\ref{figure3} shows two sets of simulations.
+Figure~\ref{figure4} shows two sets of simulations.
 Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \begin{center}
@@
   }
-    \label{figure3}
+    \label{figure4}
 \end{figure}

### 2021-05-05 doc/main_jfm.tex
adding some texts

@@
 \usepackage{commath}
+\usepackage{float}
+
 \hypersetup{
@@
 
-The preliminary test of the proposed numerical algorithm is the Jeffery orbits of single ellipsoidal particle under a shear flow.
-A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is $\chi = 0^\circ$.
-Based on the theoretical Jeffery orbits,
+The preliminary test of the proposed model using integral equation method is the Jeffery orbits of single ellipsoidal particle under a shear flow.
+A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$.
+Based on the theoretical Jeffery orbits with respect to the target angle,
 
 \begin{equation}
-\chi = \tan^{-1}\left(\frac{a}{b}\left(\tan \frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
+\chi(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
 \end{equation}
@@
 
-\begin{figure}
+\begin{figure}[H]
 \begin{center}
@@
   \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the result from the integral equation method.
+The schematic of the simulation setup is shown in the inset of the figure.
   }
@@
 
-To study the deformation of the closed bilayer structure under a shear flow using the proposed algorithm, 
-we adopt a widely tested numerical simulation in both continuum and molecular dynamics models.
+To study the deformation of a closed bilayer structure under a shear flow using the proposed algorithm, 
+we adopt a widely tested numerical simulation, single vesicle under a shear flow, in both continuum and molecular dynamics models.
 The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
@@
 
-\begin{figure}
+The starting center of mass position of the vesicle is pinned at the origin and Figure~\ref{figure2} shows 
+the initial circular shape  and the deformed configuration of the vesicle after a period of time. 
+The reduced area is shown in Figure~\ref{figure3} where we compare the change of area over the time with two different shear rates.
+
+\begin{figure}[H]
 \begin{center}
@@
 
+\begin{figure}[H]
+\begin{center}
+\includegraphics[width=0.4\textwidth]{ReducedArea.eps}
+\end{center} 
+  \caption{Reduced area transitions over time. The slower shear rate generates a faster convergence in the reduced area. 
+  }
+    \label{figure3}
+\end{figure}
+
 \subsection{Membrane Ruptures}
@@
 With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
+Figure~\ref{figure4} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
 
-\begin{figure}
+\begin{figure}[H]
 \begin{center}
@@
 \end{center}
-  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$.
+  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
+Here the shear rate is $\dot\gamma = 0.1$.
+Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)).
+(c)-(d) are the later states during the simulation.
   }
-    \label{figure3}
+    \label{figure4}
 \end{figure}
@@
 
-Figure~\ref{figure4} shows two sets of simulations.
+Figure~\ref{figure5} shows two sets of simulations.
 Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
@@
 \end{center}
-  \caption{Two vesicles under a linear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a) and two sets of simulation results are two vesicles under
+  \caption{Two vesicles under a linear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a) and two sets of simulation results are two vesicles under:
   (b)-(d) extensional flow and (e)-(h) shear flow. 
   }
-    \label{figure4}
+    \label{figure5}
 \end{figure}

### 2021-05-06 doc/main_jfm.tex
adding some texts

@@
 \usepackage{commath}
-\usepackage{float}
 
@@
 
-To study the deformation of a closed bilayer structure under a shear flow using the proposed algorithm, 
-we adopt a widely tested numerical simulation, single vesicle under a shear flow, in both continuum and molecular dynamics models.
-The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
-Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
-the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.
-
-The starting center of mass position of the vesicle is pinned at the origin and Figure~\ref{figure2} shows 
-the initial circular shape  and the deformed configuration of the vesicle after a period of time. 
-The reduced area is shown in Figure~\ref{figure3} where we compare the change of area over the time with two different shear rates.
-
-\begin{figure}[H]
+\begin{figure}
 \begin{center}
@@
 \end{figure}
+%
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.4\textwidth]{ReducedArea.eps}
+\end{center} 
+  \caption{Reduced area transitions over time. The slower shear rate generates a faster convergence in the reduced area. 
+  }
+    \label{figure3}
+\end{figure}
+%
+
+To study the deformation of a closed bilayer structure under a shear flow using the proposed algorithm, 
+we adopt a widely tested numerical simulation, single vesicle under a shear flow, in both continuum and molecular dynamics models.
+The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
+Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
+the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.
+
+The starting center of mass position of the vesicle is pinned at the origin and Figure~\ref{figure2} shows 
+the initial circular shape  and the deformed configuration of the vesicle after a period of time. 
+The reduced area is shown in Figure~\ref{figure3} where we compare the change of area over the time with two different shear rates. The reduced area is given by $A^* = 4\pi A/L^2$
+where $A$ is the vesicle area and $L$ is the arc length of the vesicle.
 
@@
 
-\begin{figure}[H]
-\begin{center}
-\includegraphics[width=0.4\textwidth]{ReducedArea.eps}
-\end{center} 
-  \caption{Reduced area transitions over time. The slower shear rate generates a faster convergence in the reduced area. 
-  }
-    \label{figure3}
-\end{figure}
-
 \subsection{Membrane Ruptures}
 
-With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
-Figure~\ref{figure4} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
-
-\begin{figure}[H]
+\begin{figure}
 \begin{center}
-\includegraphics[width=0.4\textwidth]{N58_rupt_0.eps}
-\includegraphics[width=0.4\textwidth]{N58_rupt_200.eps}\\
-\includegraphics[width=0.4\textwidth]{N58_rupt_400.eps}
-\includegraphics[width=0.4\textwidth]{N58_rupt_600.eps}
+\includegraphics[width=0.22\textwidth]{N58_rupt_0.eps}
+\includegraphics[width=0.22\textwidth]{N58_rupt_200.eps}
+\includegraphics[width=0.22\textwidth]{N58_rupt_400.eps}
+\includegraphics[width=0.22\textwidth]{N58_rupt_600.eps}
 \end{center}
@@
 \end{figure}
+%
+
+With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
+Figure~\ref{figure4} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
 
@@
 
-Figure~\ref{figure5} shows two sets of simulations.
-Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
-The flow is stretching along the $y$ direction and squeezing in $x$ direction.
-Hence two vesicles are first pushed toward each other  then separate.
-With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $x = \dot\gamma y$.
-An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.
-
-\begin{figure}[H]
+\begin{figure}
 \begin{center}
@@
     \label{figure5}
+\end{figure}
+
+Figure~\ref{figure5} shows two sets of simulations.
+Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
+The flow is stretching along the $y$ direction and squeezing in $x$ direction.
+Hence two vesicles are first pushed toward each other  then separate.
+With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $x = \dot\gamma y$.
+An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.
+
+\subsection{Vesicle in a Parabolic Flow}
+
+The background flow for this set of simulations is given by
+
+\begin{equation}
+{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{10R_0}\right)^2 \right]{\bf e}_x,
+\end{equation}
+%
+where $v_{max}$ is the flow strength. $R_0$ is defined as the radius of the initial vesicle midplane.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.3\textwidth]{N58_parabolic.eps}
+\end{center}
+  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$: 
+The configuration is the state when $t=20000$.
+  }
+    \label{figure6}
 \end{figure}

### 2021-05-06 doc/main_jfm.tex
adding some texts

@@
 
-The preliminary test of the proposed model using integral equation method is the Jeffery orbits of single ellipsoidal particle under a shear flow.
+The preliminary test of the proposed model using integral equation method is the Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate.
 A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$.
@@
 %
-where $a$, $b$ are semi-major and semi-minor axes, $\dot\gamma$ is the shear rate, and the test aspect ratio of the particle is $2$.
+where $a$, $b$ are semi-major and semi-minor axes, and the test aspect ratio of the particle is $2$.
 Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{JefferyOrbit.eps}
+\includegraphics[width=0.4\textwidth]{JefferyOrbit.eps}
 \end{center}
-  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the result from the integral equation method.
+  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method.
 The schematic of the simulation setup is shown in the inset of the figure.
@@
   \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
-  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle.
+  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle after $20000$ steps. The tank-treading motion occurs after reaching the state shown in panel (b).
   }
@@
 Hence two vesicles are first pushed toward each other  then separate.
-With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $x = \dot\gamma y$.
+With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $\dot x = \dot\gamma y$.
 An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.

### 2021-05-06 doc/main_jfm.tex
adding some texts

@@
 \begin{equation}
-{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{10R_0}\right)^2 \right]{\bf e}_x,
+{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
 \end{equation}
 %
-where $v_{max}$ is the flow strength. $R_0$ is defined as the radius of the initial vesicle midplane.
+where $v_{max}$ is the flow strength and $w$ controls the shape of the flow. $R_0$ is defined as the radius of the initial vesicle midplane.
 
@@
 \end{center}
-  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$: 
-The configuration is the state when $t=20000$.
+  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.
   }

### 2021-05-06 doc/main_jfm.tex
adding some texts

@@
 \usepackage{commath}
+\usepackage{float}
 
@@
 
-\begin{figure}[H]
-\begin{center}
+\begin{figure}
+\centering
 \includegraphics[width=0.4\textwidth]{JefferyOrbit.eps}
-\end{center}
   \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method.
@@
 
+To study the deformation of a closed bilayer structure under a shear flow using the proposed algorithm, 
+we adopt a widely tested numerical simulation in both continuum and molecular dynamics models, single vesicle under a shear flow.
+The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
+Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
+the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.
+
+The starting center of mass position of the vesicle is pinned at the origin and Figure~\ref{figure2} shows 
+the initial circular shape  and the deformed configuration of the vesicle after a period of time. The tank-treading behavior appears after obtaining the equilibrium state. 
+% needs to add more details about inclination angle, tank-treading frequency,...etc.
+The reduced area is shown in Figure~\ref{figure3} where we compare the change of area over the time with two different shear rates. The reduced area is given by $A^* = 4\pi A/L^2$
+where $A$ is the vesicle area and $L$ is the arc length of the vesicle.
+
 \begin{figure}
-\begin{center}
+\centering
 \includegraphics[width=0.3\textwidth]{N58_0.eps}
 \includegraphics[width=0.3\textwidth]{N58_20000.eps}
-\end{center}
   \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
@@
 \end{figure}
-%
-
-To study the deformation of a closed bilayer structure under a shear flow using the proposed algorithm, 
-we adopt a widely tested numerical simulation, single vesicle under a shear flow, in both continuum and molecular dynamics models.
-The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
-Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
-the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.
-
-The starting center of mass position of the vesicle is pinned at the origin and Figure~\ref{figure2} shows 
-the initial circular shape  and the deformed configuration of the vesicle after a period of time. 
-The reduced area is shown in Figure~\ref{figure3} where we compare the change of area over the time with two different shear rates. The reduced area is given by $A^* = 4\pi A/L^2$
-where $A$ is the vesicle area and $L$ is the arc length of the vesicle.
 
@@
 
+With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
+Figure~\ref{figure4} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
+
 \begin{figure}
-\begin{center}
+\centering
 \includegraphics[width=0.22\textwidth]{N58_rupt_0.eps}
@@
 \includegraphics[width=0.22\textwidth]{N58_rupt_600.eps}
-\end{center}
   \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
@@
 
-With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
-Figure~\ref{figure4} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
-
 \subsection{Two Vesicles in a Linear Flow}
@@
 \begin{figure}
-\begin{center}
+\centering
 \includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
@@
 \includegraphics[width=0.22\textwidth]{N116_shear_12000.eps}
-\end{center}
   \caption{Two vesicles under a linear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a) and two sets of simulation results are two vesicles under:
@@
 The flow is stretching along the $y$ direction and squeezing in $x$ direction.
-Hence two vesicles are first pushed toward each other  then separate.
+Hence two vesicles are first pushed toward each other  then separate along the streamline.
 With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $\dot x = \dot\gamma y$.
 An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.
+One can notice that the starting
+state of two vesicles are both centered on the x-axis.
+If two center of mass positions are not at the same horizontal level, then the adhesion observed in the shear flow case will be absent when they are well separated in $y$-direction.
 
@@
 \begin{figure}
-\begin{center}
+\centering
 \includegraphics[width=0.3\textwidth]{N58_parabolic.eps}
-\end{center}
   \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.

### 2021-05-07 doc/main_jfm.tex
adding some texts

@@
 The starting center of mass position of the vesicle is pinned at the origin and Figure~\ref{figure2} shows 
-the initial circular shape  and the deformed configuration of the vesicle after a period of time. The tank-treading behavior appears after obtaining the equilibrium state. 
-% needs to add more details about inclination angle, tank-treading frequency,...etc.
+the initial circular shape  and the deformed configuration of the vesicle after a period of time. 
+This vesicle consists of $58$ disks with radius $r=0.5$ and the tank-treading behavior appears after obtaining an equilibrium state. 
+% needs to add more details about inclination angle, tank-treading frequency, repulsion, ...etc.
 The reduced area is shown in Figure~\ref{figure3} where we compare the change of area over the time with two different shear rates. The reduced area is given by $A^* = 4\pi A/L^2$
@@
 %
-where $v_{max}$ is the flow strength and $w$ controls the shape of the flow. $R_0$ is defined as the radius of the initial vesicle midplane.
+where $v_{max}$ is the flow strength and $w$ controls the shape of the flow.
+$R_0$ is defined as the radius of the initial vesicle midplane.
+Figure~\ref{figure6} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
 

### 2021-05-13 doc/main_jfm.tex
figures changed

@@
 \includegraphics[width=0.22\textwidth]{N116_ext_5000.eps}
-\includegraphics[width=0.22\textwidth]{N116_ext_7500.eps}\\
-\includegraphics[width=0.22\textwidth]{N116_shear_3000.eps}
-\includegraphics[width=0.22\textwidth]{N116_shear_6000.eps}
-\includegraphics[width=0.22\textwidth]{N116_shear_9000.eps}
-\includegraphics[width=0.22\textwidth]{N116_shear_12000.eps}
-  \caption{Two vesicles under a linear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a) and two sets of simulation results are two vesicles under:
-  (b)-(d) extensional flow and (e)-(h) shear flow. 
+\includegraphics[width=0.22\textwidth]{N116_ext_7500.eps}
+  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
   }
@@
 
-Figure~\ref{figure5} shows two sets of simulations.
-Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
-The flow is stretching along the $y$ direction and squeezing in $x$ direction.
+\begin{figure}
+\centering
+\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
+\includegraphics[width=0.22\textwidth]{N116_shear_3000.eps}
+\includegraphics[width=0.22\textwidth]{N116_shear_6000.eps}
+\includegraphics[width=0.22\textwidth]{N116_shear_9000.eps}
+  \caption{Two vesicles under a shear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a). 
+  }
+    \label{figure6}
+\end{figure}
+
+Figures~\ref{figure5} and \ref{figure6} show two sets of simulations.
+Starting from the initial configuration (shown in both panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
+The extensional flow is stretching along the $y$ direction and squeezing in $x$ direction.
 Hence two vesicles are first pushed toward each other  then separate along the streamline.
-With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $\dot x = \dot\gamma y$.
+With the same starting state, panels (b)-(d) in Figure~\ref{figure6} are the observed phenomena when two vesicles are in a shear flow $\dot x = \dot\gamma y$.
 An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.
@@
 $R_0$ is defined as the radius of the initial vesicle midplane.
-Figure~\ref{figure6} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
+Figure~\ref{figure7} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
 
@@
   }
-    \label{figure6}
+    \label{figure7}
 \end{figure}

### 2021-06-10 doc/main_jfm.tex
figures changed
some updates

@@
 A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$.
-Based on the theoretical Jeffery orbits with respect to the target angle,
+Based on the theoretical Jeffery orbits with respect to the target angle $\chi(t)$,
 
@@
 
-The starting center of mass position of the vesicle is pinned at the origin and Figure~\ref{figure2} shows 
-the initial circular shape  and the deformed configuration of the vesicle after a period of time. 
-This vesicle consists of $58$ disks with radius $r=0.5$ and the tank-treading behavior appears after obtaining an equilibrium state. 
-% needs to add more details about inclination angle, tank-treading frequency, repulsion, ...etc.
-The reduced area is shown in Figure~\ref{figure3} where we compare the change of area over the time with two different shear rates. The reduced area is given by $A^* = 4\pi A/L^2$
-where $A$ is the vesicle area and $L$ is the arc length of the vesicle.
+For the target bilayer, a circular initial shape is chosen to perform the relaxation run. This vesicle consists 
+of $N=58$ disks with radius $r=0.5$ and the starting diameter for the vesicle is $\sim8.5$.
+The starting center of mass position of the vesicle is pinned at the origin and we track particle velocities 
+to determine the initial configuration for later simulations.
+This will prevent some numerical instability issues when the minimum of the total energy is not achieved.
+For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
+Figure~\ref{figure2} shows that the magnitudes of velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim1/3.74N$. The time step size 
+$\Delta t=0.2$ is used for all simulations including the relaxation run.
 
@@
 \centering
-\includegraphics[width=0.3\textwidth]{N58_0.eps}
-\includegraphics[width=0.3\textwidth]{N58_20000.eps}
-  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
-  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle after $20000$ steps. The tank-treading motion occurs after reaching the state shown in panel (b).
+\includegraphics[width=0.4\textwidth]{relax.eps}
+  \caption{Vesicle relaxes under a quiescent flow.
+The blue dashed curve and the red solid curve are mean magnitudes of the particle velocities.
+The black dashed line shows the reference of how velocity magnitudes
+  decay.
   }
@@
 \end{figure}
+
+The snapshots of the simulation for single vesicle in a shear flow is shown in Figure~\ref{figure3}.
+Panel (a) shows the initial circular shape obtained from the relaxation run and the deformed 
+configuration of the vesicle after a period of time is in panel (c). The color presented in the figure 
+is the strength of the action due to the hydrophobic attraction. From weak to strong action field, the color
+varies from blue to red.
+To demonstrate the tank-treading behavior of the vesicle, panels (b) and (d) provide the fluid velocities 
+over the whole computational domain when the shear flow passes through the vesicle.
+
+% needs to add more details about inclination angle, tank-treading frequency, repulsion, ...etc.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{N58_0.pdf}
+\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
+\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
+\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
+  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.0025$: 
+  (a) Initial configuration of 58-body vesicle; 
+  (b) The fluid velocity plot with respect to the configuration in (a);
+  (c) Deformed vesicle after $20000$ steps. The tank-treading motion occurs after reaching the state shown in panel (c).
+  (d) The fluid velocity plot with respect to the configuration in (c);
+  The background colors in panels (a) and (c) represent the strength of the hydrophobic attraction potential. The blue region shows no action and the red region with the bilayer gives the strongest 
+  action.
+  }
+    \label{figure3}
+\end{figure}
 %
+
+The results of the reduced area are shown in Figure~\ref{figure4} where we compare the change of area over the time with a set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$.
+The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ is the vesicle area and $L$ is the arc length of the vesicle with respect to the midplane.
+Since the starting configuration is close to a circular shape, the reduced are decreases from a value very close to $1$.
+It is clear that a slower shear rate generates a higher reduced area and has faster convergence.
+The small oscillations in all results are due to the granular setup of the bilayer which tends to having a slightly non-smooth curve in simulations.
 
@@
 \begin{center}
-\includegraphics[width=0.4\textwidth]{ReducedArea.eps}
+\includegraphics[width=0.5\textwidth]{ReducedArea.pdf}
 \end{center} 
-  \caption{Reduced area transitions over time. The slower shear rate generates a faster convergence in the reduced area. 
+  \caption{Reduced area transitions over time. 
+A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
+A slower shear rate generates a faster convergence in the reduced area. 
   }
-    \label{figure3}
+    \label{figure4}
 \end{figure}
@@
 With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
-Figure~\ref{figure4} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
+Figure~\ref{figure5} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
+An interesting phenomenon occurs in panels (c) and (d) where two separated bilayers move along the background shear flow symmetrically.
+Consequently, a periodic motion for bilayers may occur
+with the choices of shear rates. One can expect that these two layers will flow far apart from each other for much higher shear rates.
 
@@
 \centering
-\includegraphics[width=0.22\textwidth]{N58_rupt_0.eps}
-\includegraphics[width=0.22\textwidth]{N58_rupt_200.eps}
-\includegraphics[width=0.22\textwidth]{N58_rupt_400.eps}
-\includegraphics[width=0.22\textwidth]{N58_rupt_600.eps}
+\includegraphics[width=0.3\textwidth]{N58_rupt_0.eps}
+\includegraphics[width=0.3\textwidth]{N58_rupt_200.eps}\\
+\includegraphics[width=0.3\textwidth]{N58_rupt_400.eps}
+\includegraphics[width=0.3\textwidth]{N58_rupt_600.eps}
   \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
@@
   }
-    \label{figure4}
+    \label{figure5}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
-\includegraphics[width=0.22\textwidth]{N116_ext_2500.eps}
-\includegraphics[width=0.22\textwidth]{N116_ext_5000.eps}
-\includegraphics[width=0.22\textwidth]{N116_ext_7500.eps}
+\includegraphics[height=1.2in]{N116_ext_0.pdf}
+\includegraphics[height=1.2in]{N116_ext_2500.pdf}
+\includegraphics[height=1.2in]{N116_ext_5000.pdf}
+\includegraphics[height=1.2in]{N116_ext_7500.pdf}
   \caption{Two vesicles under an extensional flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
+The background color indicates the magnitude of fluid pressure.
+From dark red to dark blue, it represents the the pressure varies from high to low values.
+The color bar is valid for all panels.
   }
-    \label{figure5}
+    \label{figure6}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
-\includegraphics[width=0.22\textwidth]{N116_shear_3000.eps}
-\includegraphics[width=0.22\textwidth]{N116_shear_6000.eps}
-\includegraphics[width=0.22\textwidth]{N116_shear_9000.eps}
-  \caption{Two vesicles under a shear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a). 
-  }
-    \label{figure6}
+\includegraphics[width=0.24\textwidth]{N116_ext_vel_0.pdf}
+\includegraphics[width=0.24\textwidth]{N116_ext_vel_2500.pdf}
+\includegraphics[width=0.24\textwidth]{N116_ext_vel_5000.pdf}
+\includegraphics[width=0.24\textwidth]{N116_ext_vel_7500.pdf}
+  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
+    \label{figure7}
 \end{figure}
 
-Figures~\ref{figure5} and \ref{figure6} show two sets of simulations.
-Starting from the initial configuration (shown in both panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
-The extensional flow is stretching along the $y$ direction and squeezing in $x$ direction.
-Hence two vesicles are first pushed toward each other  then separate along the streamline.
-With the same starting state, panels (b)-(d) in Figure~\ref{figure6} are the observed phenomena when two vesicles are in a shear flow $\dot x = \dot\gamma y$.
+\subsubsection{Extensional Flow}
+
+Figures~\ref{figure6}-\ref{figure7} show the numerical results of simulations when two vesicles are in an extensional flow.
+Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
+The extensional flow is stretching along the $y$ direction and squeezing in $x$ direction with shear rate $\dot\gamma=0.005$.
+Since two bilayers are close enough
+from the beginning of the run, two vesicles are first pushed toward each other then separate along the streamline. The short range repulsion plays an important role to avoid structure collisions and 
+this result can be compared with some findings in continuum modeling simulations.
+The pressure plots in Figure~\ref{figure7} provide a realistic result where the pressure is much higher in the gap between two nearby vesicles.
+
+%may need to add more here
+
+\begin{figure}
+\centering
+\includegraphics[height=1.2in]{N116_ext_0.pdf}
+\includegraphics[height=1.2in]{N116_shear_3000.pdf}
+\includegraphics[height=1.2in]{N116_shear_6000.pdf}
+\includegraphics[height=1.2in]{N116_shear_9000.pdf}\\
+  \caption{Two vesicles under a shear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
+The background color indicates the magnitude of fluid pressure.
+From dark red to dark blue, it represents the the pressure varies from high to low values.
+The color bar is valid for all panels.
+  }
+    \label{figure8}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.24\textwidth]{N116_shear_vel_0.pdf}
+\includegraphics[width=0.24\textwidth]{N116_shear_vel_3000.pdf}
+\includegraphics[width=0.24\textwidth]{N116_shear_vel_6000.pdf}
+\includegraphics[width=0.24\textwidth]{N116_shear_vel_9000.pdf}
+  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
+    \label{figure9}
+\end{figure}
+
+\subsubsection{Shear Flow}
+Two vesicles in a shear flow is resented in Figures~\ref{figure8}-\ref{figure9} where centers of mass are placed on the same horizontal level.
+With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \dot\gamma y$.
 An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.
-One can notice that the starting
-state of two vesicles are both centered on the x-axis.
-If two center of mass positions are not at the same horizontal level, then the adhesion observed in the shear flow case will be absent when they are well separated in $y$-direction.
+In other words, the the adhesive behavior will be absent when two vesicles are centered
+at a different level and are well separated in $y$-direction.
 
@@
 $R_0$ is defined as the radius of the initial vesicle midplane.
-Figure~\ref{figure7} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
+Figure~\ref{figure10} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
 
@@
   }
-    \label{figure7}
+    \label{figure10}
 \end{figure}

### 2021-06-10 doc/main_jfm.tex
some updates

@@
 
-%We tune the shear rates, vesicle sizes and .....
-
-%Theoretical tank-treading frequency is given by $\dot\gamma/2$.
-
-%We also compare the inclination angle against the Jeffery's equation [].
-
-\subsection{Membrane Ruptures}
-
-With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
-Figure~\ref{figure5} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
-An interesting phenomenon occurs in panels (c) and (d) where two separated bilayers move along the background shear flow symmetrically.
-Consequently, a periodic motion for bilayers may occur
-with the choices of shear rates. One can expect that these two layers will flow far apart from each other for much higher shear rates.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{N58_rupt_0.eps}
-\includegraphics[width=0.3\textwidth]{N58_rupt_200.eps}\\
-\includegraphics[width=0.3\textwidth]{N58_rupt_400.eps}
-\includegraphics[width=0.3\textwidth]{N58_rupt_600.eps}
-  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
-Here the shear rate is $\dot\gamma = 0.1$.
-Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)).
-(c)-(d) are the later states during the simulation.
-  }
-    \label{figure5}
-\end{figure}
 %
@@
   }
-    \label{figure6}
+    \label{figure5}
 \end{figure}
@@
   \caption{(a)-(d) The background arrows indicate the fluid velocities. }
-    \label{figure7}
+    \label{figure6}
 \end{figure}
@@
 
-Figures~\ref{figure6}-\ref{figure7} show the numerical results of simulations when two vesicles are in an extensional flow.
+Figures~\ref{figure5}-\ref{figure6} show the numerical results of simulations when two vesicles are in an extensional flow.
 Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
@@
 this result can be compared with some findings in continuum modeling simulations.
-The pressure plots in Figure~\ref{figure7} provide a realistic result where the pressure is much higher in the gap between two nearby vesicles.
+The pressure plots in Figure~\ref{figure6} provide a realistic result where the pressure is much higher in the gap between two nearby vesicles.
 
@@
   }
-    \label{figure8}
+    \label{figure7}
 \end{figure}
@@
   \caption{(a)-(d) The background arrows indicate the fluid velocities. }
-    \label{figure9}
+    \label{figure8}
 \end{figure}
@@
 \subsubsection{Shear Flow}
-Two vesicles in a shear flow is resented in Figures~\ref{figure8}-\ref{figure9} where centers of mass are placed on the same horizontal level.
+Two vesicles in a shear flow is resented in Figures~\ref{figure7}-\ref{figure8} where centers of mass are placed on the same horizontal level.
 With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \dot\gamma y$.
@@
 $R_0$ is defined as the radius of the initial vesicle midplane.
-Figure~\ref{figure10} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
+Figure~\ref{figure9} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
 
@@
   \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.
+  }
+    \label{figure9}
+\end{figure}
+
+\subsection{Membrane Ruptures}
+
+With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
+Figure~\ref{figure10} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
+An interesting phenomenon occurs in panels (c) and (d) where two separated bilayers move along the background shear flow symmetrically.
+Consequently, a periodic motion for bilayers may occur
+with the choices of shear rates. One can expect that these two layers will flow far apart from each other for much higher shear rates.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{N58_rupt_0.eps}
+\includegraphics[width=0.3\textwidth]{N58_rupt_200.eps}\\
+\includegraphics[width=0.3\textwidth]{N58_rupt_400.eps}
+\includegraphics[width=0.3\textwidth]{N58_rupt_600.eps}
+  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
+Here the shear rate is $\dot\gamma = 0.1$.
+Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)).
+(c)-(d) are the later states during the simulation.
   }

### 2021-06-22 doc/main_jfm.tex
updates

@@
 
-The preliminary test of the proposed model using integral equation method is the Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate.
-A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$.
+The preliminary test of the proposed model using the integral equation method is the numerical validation in Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate.
+An ellipsoidal particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$.
 Based on the theoretical Jeffery orbits with respect to the target angle $\chi(t)$,
@@
 
-For the target bilayer, a circular initial shape is chosen to perform the relaxation run. This vesicle consists 
-of $N=58$ disks with radius $r=0.5$ and the starting diameter for the vesicle is $\sim8.5$.
+For the target bilayer, a circular initial shape is chosen to perform the relaxation run. This vesicle-like 
+structure consists of $N=58$ disks with radius $r=0.5$ and the starting diameter for the vesicle is about 
+$8.5$ length units.
 The starting center of mass position of the vesicle is pinned at the origin and we track particle velocities 
-to determine the initial configuration for later simulations.
+to determine the initial configuration for later use such as single and multiple vesicle simulations.
 This will prevent some numerical instability issues when the minimum of the total energy is not achieved.
 For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
-Figure~\ref{figure2} shows that the magnitudes of velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim1/3.74N$. The time step size 
+Figure~\ref{figure2} shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005t$.
+In the same figure, the variation of mean particle orientation $\theta$ also decreases as expected.
+The time step size
 $\Delta t=0.2$ is used for all simulations including the relaxation run.
@@
   \caption{Vesicle relaxes under a quiescent flow.
-The blue dashed curve and the red solid curve are mean magnitudes of the particle velocities.
-The black dashed line shows the reference of how velocity magnitudes
-  decay.
+The blue dashed curve and the solid curve are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively.
+The red curve shows the decreasing trend of the mean magnitude of particle orientation change.
+The black dashed line shows the reference of how all magnitudes decay.
   }
@@
 
-The snapshots of the simulation for single vesicle in a shear flow is shown in Figure~\ref{figure3}.
+The snapshots of the simulation for single vesicle in a shear flow are shown in Figure~\ref{figure3}.
 Panel (a) shows the initial circular shape obtained from the relaxation run and the deformed 
-configuration of the vesicle after a period of time is in panel (c). The color presented in the figure 
+configuration of the vesicle after a period of time ($t=4000$) is in panel (c). The color presented in the figure 
 is the strength of the action due to the hydrophobic attraction. From weak to strong action field, the color
 varies from blue to red.
-To demonstrate the tank-treading behavior of the vesicle, panels (b) and (d) provide the fluid velocities 
-over the whole computational domain when the shear flow passes through the vesicle.
+To demonstrate the tank-treading behavior of the vesicle, panels (b) and (d) provide the streamlines of the 
+fluid velocity over the whole computational domain when the shear flow passes through the vesicle. The tank-treading motion of the structure is observed.
 
@@
   (a) Initial configuration of 58-body vesicle; 
-  (b) The fluid velocity plot with respect to the configuration in (a);
+  (b) The fluid velocity plot with respect to the configuration in (a); Streamlines are plotted in the background
+  as solid curves. Red arrows represent the particle velocities.
   (c) Deformed vesicle after $20000$ steps. The tank-treading motion occurs after reaching the state shown in panel (c).
   (d) The fluid velocity plot with respect to the configuration in (c);
-  The background colors in panels (a) and (c) represent the strength of the hydrophobic attraction potential. The blue region shows no action and the red region with the bilayer gives the strongest 
-  action.
+  The background colors in panels (a) and (c) represent the strength of the hydrophobic attraction potential.
+The blue region shows no action and the red region with the bilayer gives the strongest action.
   }
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.24\textwidth]{N116_ext_vel_0.pdf}
-\includegraphics[width=0.24\textwidth]{N116_ext_vel_2500.pdf}
-\includegraphics[width=0.24\textwidth]{N116_ext_vel_5000.pdf}
-\includegraphics[width=0.24\textwidth]{N116_ext_vel_7500.pdf}
-  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
-    \label{figure6}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.24\textwidth]{N116_ext_vel_0.pdf}
+%\includegraphics[width=0.24\textwidth]{N116_ext_vel_2500.pdf}
+%\includegraphics[width=0.24\textwidth]{N116_ext_vel_5000.pdf}
+%\includegraphics[width=0.24\textwidth]{N116_ext_vel_7500.pdf}
+%  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
+%    \label{figure6}
+%\end{figure}
 
@@
 \centering
-\includegraphics[height=1.2in]{N116_ext_0.pdf}
+\includegraphics[height=1.2in]{N116_shear_0.pdf}
 \includegraphics[height=1.2in]{N116_shear_3000.pdf}
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.24\textwidth]{N116_shear_vel_0.pdf}
-\includegraphics[width=0.24\textwidth]{N116_shear_vel_3000.pdf}
-\includegraphics[width=0.24\textwidth]{N116_shear_vel_6000.pdf}
-\includegraphics[width=0.24\textwidth]{N116_shear_vel_9000.pdf}
-  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
-    \label{figure8}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.24\textwidth]{N116_shear_vel_0.pdf}
+%\includegraphics[width=0.24\textwidth]{N116_shear_vel_3000.pdf}
+%\includegraphics[width=0.24\textwidth]{N116_shear_vel_6000.pdf}
+%\includegraphics[width=0.24\textwidth]{N116_shear_vel_9000.pdf}
+%  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
+%    \label{figure8}
+%\end{figure}
 

### 2021-06-22 doc/main_jfm.tex
updates

@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{ReducedArea.pdf}
+\includegraphics[width=0.4\textwidth]{ArcLength.pdf}
+\includegraphics[width=0.4\textwidth]{ReducedArea.pdf}
 \end{center} 
-  \caption{Reduced area transitions over time. 
+  \caption{(a) Total arc lengths of the outer leaflets over time in different shear rates; (b)Reduced area transitions over time. 
 A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
@@
 
-Figures~\ref{figure5}-\ref{figure6} show the numerical results of simulations when two vesicles are in an extensional flow.
+Figures~\ref{figure5} show the numerical results of simulations when two vesicles are in an extensional flow.
 Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
@@
   }
-    \label{figure7}
+    \label{figure6}
 \end{figure}
@@
 \subsubsection{Shear Flow}
-Two vesicles in a shear flow is resented in Figures~\ref{figure7}-\ref{figure8} where centers of mass are placed on the same horizontal level.
+Two vesicles in a shear flow is resented in Figures~\ref{figure6} where centers of mass are placed on the same horizontal level.
 With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \dot\gamma y$.
@@
 $R_0$ is defined as the radius of the initial vesicle midplane.
-Figure~\ref{figure9} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
+Figure~\ref{figure7} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
 
@@
   }
-    \label{figure9}
+    \label{figure7}
 \end{figure}
@@
 With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
-Figure~\ref{figure10} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
+Figure~\ref{figure8} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
 An interesting phenomenon occurs in panels (c) and (d) where two separated bilayers move along the background shear flow symmetrically.
@@
   }
-    \label{figure10}
+    \label{figure8}
 \end{figure}

### 2021-06-22 doc/main_jfm.tex
updates

@@
 
-The results of the reduced area are shown in Figure~\ref{figure4} where we compare the change of area over the time with a set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$.
+In order to extract more physical properties of the proposed model, we track the total length of the bilayer structure and the reduced area over the time.
+These results are shown in Figure~\ref{figure4} where we compare output the results from a set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$. 
 The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ is the vesicle area and $L$ is the arc length of the vesicle with respect to the midplane.
@@
 \begin{center}
-\includegraphics[width=0.4\textwidth]{ArcLength.pdf}
-\includegraphics[width=0.4\textwidth]{ReducedArea.pdf}
+\includegraphics[width=0.45\textwidth]{ArcLength.pdf}
+\includegraphics[width=0.45\textwidth]{ReducedArea.pdf}
 \end{center} 

### 2021-06-23 doc/main_jfm.tex
updates

@@
 In order to extract more physical properties of the proposed model, we track the total length of the bilayer structure and the reduced area over the time.
-These results are shown in Figure~\ref{figure4} where we compare output the results from a set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$. 
+Here the enclosed area and the length of the structure are calculated from the midplane.
+These results are shown in Figure~\ref{figure4} where we compare results from a set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$. 
 The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ is the vesicle area and $L$ is the arc length of the vesicle with respect to the midplane.
@@
 The small oscillations in all results are due to the granular setup of the bilayer which tends to having a slightly non-smooth curve in simulations.
+Overall the total lengths of the bilayer have the same converging value in all test shear rates.
+Moreover, based on the
+numerical experiments, we observe that the reduce area converges relatively early when the shear rate is lower than $\dot\gamma=0.003$.
 
@@
 \end{center} 
-  \caption{(a) Total arc lengths of the outer leaflets over time in different shear rates; (b)Reduced area transitions over time. 
+  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) Reduced area transitions over time. 
 A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
@@
 \includegraphics[height=1.2in]{N116_ext_7500.pdf}
-  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
+  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
 The background color indicates the magnitude of fluid pressure.
@@
 The color bar is valid for all panels.
+Streamlines are plotted in purple.
   }
@@
 \includegraphics[height=1.2in]{N116_shear_9000.pdf}\\
-  \caption{Two vesicles under a shear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
+  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
 The background color indicates the magnitude of fluid pressure.

### 2021-06-23 doc/main_jfm.tex
updates

@@
 
+\subsubsection{Relaxtion}
+
 To study the deformation of a closed bilayer structure under a shear flow using the proposed algorithm, 
@@
 
+\subsubsection{Vesicle in a Shear Flow}
+
 The snapshots of the simulation for single vesicle in a shear flow are shown in Figure~\ref{figure3}.
@@
 To demonstrate the tank-treading behavior of the vesicle, panels (b) and (d) provide the streamlines of the 
-fluid velocity over the whole computational domain when the shear flow passes through the vesicle. The tank-treading motion of the structure is observed.
+fluid velocity over the whole computational domain when the shear flow passes through the vesicle. The tank-treading motion of the structure is then observed.
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{Slip.eps}
+\end{center} 
+  \caption{For a high shear rate $\dot\gamma=0.005$, the inter-monolayer slip is be observed. 
+  }
+    \label{figure5}
+\end{figure}
+
+\subsubsection{Vesicle in a Parabolic Flow}
+
+The background flow for this set of simulations is given by
+
+\begin{equation}
+{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
+\end{equation}
+%
+where $v_{max}$ is the flow strength and $w$ controls the shape of the flow.
+$R_0$ is defined as the radius of the initial vesicle midplane.
+Figure~\ref{figure6} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{N58_parabolic.eps}
+  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.
+  }
+    \label{figure6}
+\end{figure}
+
+\subsubsection{Membrane Ruptures}
+
+With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
+Figure~\ref{figure7} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
+An interesting phenomenon occurs in panels (c) and (d) where two separated bilayers move along the background shear flow symmetrically.
+Consequently, a periodic motion for bilayers may occur
+with the choices of shear rates. One can expect that these two layers will flow far apart from each other for much higher shear rates.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{N58_rupt_0.eps}
+\includegraphics[width=0.3\textwidth]{N58_rupt_200.eps}\\
+\includegraphics[width=0.3\textwidth]{N58_rupt_400.eps}
+\includegraphics[width=0.3\textwidth]{N58_rupt_600.eps}
+  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
+Here the shear rate is $\dot\gamma = 0.1$.
+Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)).
+(c)-(d) are the later states during the simulation.
+  }
+    \label{figure7}
+\end{figure}
+
 %
@@
   }
-    \label{figure5}
+    \label{figure8}
 \end{figure}
@@
 
-Figures~\ref{figure5} show the numerical results of simulations when two vesicles are in an extensional flow.
+Figures~\ref{figure8} show the numerical results of simulations when two vesicles are in an extensional flow.
 Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
@@
 this result can be compared with some findings in continuum modeling simulations.
-The pressure plots in Figure~\ref{figure6} provide a realistic result where the pressure is much higher in the gap between two nearby vesicles.
+The pressure plots in Figure~\ref{figure8} provide a realistic result where the pressure is much higher in the gap between two nearby vesicles.
 
@@
   }
-    \label{figure6}
+    \label{figure9}
 \end{figure}
@@
 \subsubsection{Shear Flow}
-Two vesicles in a shear flow is resented in Figures~\ref{figure6} where centers of mass are placed on the same horizontal level.
+Two vesicles in a shear flow is resented in Figures~\ref{figure9} where centers of mass are placed on the same horizontal level.
 With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \dot\gamma y$.
@@
 at a different level and are well separated in $y$-direction.
-
-\subsection{Vesicle in a Parabolic Flow}
-
-The background flow for this set of simulations is given by
-
-\begin{equation}
-{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
-\end{equation}
-%
-where $v_{max}$ is the flow strength and $w$ controls the shape of the flow.
-$R_0$ is defined as the radius of the initial vesicle midplane.
-Figure~\ref{figure7} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{N58_parabolic.eps}
-  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.
-  }
-    \label{figure7}
-\end{figure}
-
-\subsection{Membrane Ruptures}
-
-With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
-Figure~\ref{figure8} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
-An interesting phenomenon occurs in panels (c) and (d) where two separated bilayers move along the background shear flow symmetrically.
-Consequently, a periodic motion for bilayers may occur
-with the choices of shear rates. One can expect that these two layers will flow far apart from each other for much higher shear rates.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{N58_rupt_0.eps}
-\includegraphics[width=0.3\textwidth]{N58_rupt_200.eps}\\
-\includegraphics[width=0.3\textwidth]{N58_rupt_400.eps}
-\includegraphics[width=0.3\textwidth]{N58_rupt_600.eps}
-  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
-Here the shear rate is $\dot\gamma = 0.1$.
-Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)).
-(c)-(d) are the later states during the simulation.
-  }
-    \label{figure8}
-\end{figure}
 

### 2021-06-23 doc/main_jfm.tex
updates

@@
 
+An interesting phenomenon also rises up in the proposed setup where the inter-monolayer slip occurs 
+between two leaflets. When a shear rate is large enough, take $\dot\gamma = 0.005$ as an example, 
+Figure~\ref{figure5} shows the schematic of the test.
+A particle pair is initially marked and we then track the positions and layer velocities over the time.
+It is clear to see that the outer leaflet always has larger
+tangential velocity than the one from inner leaflet. This inter-leaflet sliding matches what has been seen
+in articles in molecular dynamics simulations. %%% need some citations
+
 \begin{figure}
@@
 \end{center} 
-  \caption{For a high shear rate $\dot\gamma=0.005$, the inter-monolayer slip is be observed. 
+  \caption{For the shear rate $\dot\gamma=0.005$, the inter-monolayer slip is be observed.
+The curves in black and blue represent the tangential velocities of inner and outer leaflet, respectively.
+The configuration plots have two fixed particles marked and positioned with respect to the corresponding time $t$.
   }
@@
 \centering
-\includegraphics[width=0.3\textwidth]{N58_parabolic.eps}
+\includegraphics[width=0.5\textwidth]{N58_parabolic.pdf}
   \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.

### 2021-06-25 doc/main_jfm.tex
updates

@@
 Since the starting configuration is close to a circular shape, the reduced are decreases from a value very close to $1$.
-It is clear that a slower shear rate generates a higher reduced area and has faster convergence.
-The small oscillations in all results are due to the granular setup of the bilayer which tends to having a slightly non-smooth curve in simulations.
+It is clear that a slower shear rate generates a higher reduced area and has a faster convergence.
+The small oscillations in all results are due to the granularity of the bilayer which tend to having a slightly non-smooth curve in simulations.
 Overall the total lengths of the bilayer have the same converging value in all test shear rates.
@@
 \centering
-\includegraphics[width=0.3\textwidth]{N58_rupt_0.eps}
-\includegraphics[width=0.3\textwidth]{N58_rupt_200.eps}\\
-\includegraphics[width=0.3\textwidth]{N58_rupt_400.eps}
-\includegraphics[width=0.3\textwidth]{N58_rupt_600.eps}
+\includegraphics[height=1.2in]{N58_rupt_0.pdf}
+\includegraphics[height=1.2in]{N58_rupt_200.pdf}
+\includegraphics[height=1.2in]{N58_rupt_400.pdf}
+\includegraphics[height=1.2in]{N58_rupt_600.pdf}
   \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.

### 2021-07-06 doc/main_jfm.tex
updates

@@
 
-%Nature of amphiphilic lipid molecules, small vesicle, GUVs, RBCs, hydrophobic tails interacting with fluid,
-
-%Tank-treading, tumbling, swing vesicles, viscosity ratio
-
-% two-dimensional vesicle, membrane fusion/fissure, self-assembly property,
-
-%crystallization, membrane jiggling can be observed when... the hydrophobicity
-
-%mobility problem, particle suspension, a wide range of study, numerical methods including boundary integral equation method, immersed boundary method, level set method, RCIP kernel splitting method,   vesicle deformations,
-
-% Stokesian dynamics
-
-%The mobility problem can be solved in the fashion of considering propagating waves through rigid bodies where the the external and hydrodynamic forces act as incident fields and scattered field evaluated on the object boundaries.
-
-%The Helfrich membrane energy is well known in continuum modeling/theory. Here we combine the framework in coarse-grained modeling using Janus-type configurations. However,
-
-%Thermal fluctuation effect not considered but the granular system in a fluid
-
-%
-
-%our approach combines the
-
+\section{Governing  Equations}
 \subsection{Hydrophobic Attraction Potential (HAP)}
@@
 
-\section{\label{mobility}Mobility Problem}
+\subsection{\label{mobility}Mobility Problem}
 
@@
 
-\section{\label{IEM}Integral Equation Method}
-
 \subsection{Short Range Repulsion}
@@
 We therefore impose a short range repulsion that it will be turned on when the distance between two boundary points on different bodies are within one characteristic length.
+
+\section{\label{IEM}Integral Equation Method}
 
@@
 For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
-Figure~\ref{figure2} shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005t$.
+Figure~\ref{figure2} shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$.
 In the same figure, the variation of mean particle orientation $\theta$ also decreases as expected.
@@
 \centering
-\includegraphics[width=0.4\textwidth]{relax.eps}
+\includegraphics[height=2in]{relax.eps}
+\includegraphics[height=2in]{relax2.eps}
   \caption{Vesicle relaxes under a quiescent flow.
@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{ArcLength.pdf}
-\includegraphics[width=0.45\textwidth]{ReducedArea.pdf}
+\includegraphics[height=2in]{ReducedArea.pdf}
+\hspace{-0.5cm}
+\includegraphics[height=2in]{ArcLength.pdf}
 \end{center} 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{N58_parabolic.pdf}
-  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.
+\includegraphics[width=0.5\textwidth]{parabolic.eps}
+  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=10000$.
   }
@@
 \includegraphics[height=1.2in]{N116_ext_7500.pdf}
+%\includegraphics[width=0.24\textwidth]{step0Pres.eps}
+%\includegraphics[width=0.24\textwidth]{step2500Pres.eps}
+%\includegraphics[width=0.24\textwidth]{step5000Pres.eps}
+%\includegraphics[width=0.24\textwidth]{step7500Pres.eps}
   \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
@@
 Streamlines are plotted in purple.
+  }
+    \label{figure8}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[height=1.2in]{N116_cont_a.pdf}
+\includegraphics[height=1.2in]{N116_cont_b.pdf}
+\includegraphics[height=1.2in]{N116_cont_c.pdf}
+\includegraphics[height=1.2in]{N116_cont_d.pdf}
+%\includegraphics[width=0.24\textwidth]{step0Pres.eps}
+%\includegraphics[width=0.24\textwidth]{step2500Pres.eps}
+%\includegraphics[width=0.24\textwidth]{step5000Pres.eps}
+%\includegraphics[width=0.24\textwidth]{step7500Pres.eps}
+  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
   }

### 2021-07-08 doc/main_jfm.tex
updates
working on BIE sections

@@
 \usepackage{commath}
+\usepackage{todonotes}
 
@@
 \linenumbers
+
+% Bryan's Marcros
+\renewcommand{\aa}{\mathbf{a}}
+\newcommand{\bd}{\partial}
+\newcommand{\DD}{\mathcal{D}}
+\newcommand{\eeta}{\boldsymbol{\eta}}
+\newcommand{\FF}{\mathbf{F}}
+\newcommand{\nnu}{\boldsymbol{\nu}}
+\newcommand{\ssigma}{\boldsymbol{\sigma}}
+\newcommand{\rr}{\mathbf{r}}
+\newcommand{\RR}{\mathbf{R}}
+\renewcommand{\SS}{\mathbf{S}}
+\newcommand{\xx}{\mathbf{x}}
+\newcommand{\uu}{\mathbf{u}}
+\renewcommand{\vv}{\mathbf{v}}
+\newcommand{\yy}{\mathbf{y}}
 
@@
 \mathbf{T}
-= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma (\tfrac{1}{2}|\nabla u|^2 \mathbf{I} - \nabla u\otimes \nabla u).
+= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
+  u|^2 \mathbf{I} - \nabla u\otimes \nabla u\right).
 \end{equation}
 %
-The integration over boundaries gives force and torque due to the hydrophobic attraction and they are given by
-
-\begin{equation}
-\int_{\Gamma_i} {\bf T}\cdot \nu_i dS ,\quad \int_{\Gamma_i} ({\bf x}-{\bf a}_i)\times ({\bf T}\cdot \nu_i) dS,
-\end{equation}
+The integration over boundaries gives force and torque due to the
+hydrophobic attraction 
+\begin{align}
+  \label{eqn:hydrophobicAttraction}
+  \FF_i = \int_{\bd \Gamma_i} {\bf T}\cdot \nnu_i \, dS, 
+    \quad  \text{ and } \quad
+  T_i = \int_{\Gamma_i} (\xx - \aa_i) \times ({\bf T} \cdot \nnu_i) dS,
+\end{align}
 %
-where ${\bf x}$ are points on the boundary $\Gamma_i$, ${\bf a}_i$ is the $i^{th}$ particle center, and $\nu_i$ is the outward normal to the $i^{th}$ particle.
+where $\xx \in \Gamma_i$, $\aa_i$ is the $i^{th}$ particle center, and
+$\nnu_i$ is the outward normal of the $i^{th}$ particle.
 
@@
 
-The governing equation of $N_b$-body bodies suspended in the domain $\Sigma$ is
-
-\begin{gather}
-	-\Delta {\bf u} + \mu\nabla p = 0 \qquad \text{in }\Sigma\\
-	\nabla\cdot {\bf u}=0 \qquad \text{in }\Sigma\\
-	{\bf u}({\bf x}) \to {\bf u}_\infty \quad \text{as}\quad |{\bf x}|\to \infty
-\end{gather}
+The governing equations of $N_b$-body bodies suspended in the unbounded
+domain $\Omega$ are
+\begin{alignat}{3}
+  -\Delta \uu + \mu\nabla p, &= 0 \qquad \qquad && \xx \in \Omega, \\
+  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
+  \uu &\to \uu_\infty, && |\xx| \to \infty,
+\end{alignat}
 %
-where ${\bf u}$ is the velocity, $p$ is the pressure, and ${\bf u}_\infty$ is the background flow. 
-%
-%\begin{gather}
-%\int_{\Gamma_i}(\sigma_{hyd}+\sigma_\infty)\cdot {\bf n} ds = -{\bf F}_i \\
-%	\int_{\Gamma_i}(\sigma_{hyd}+\sigma_\infty)\times({\bf x}-{\bf a}_i)\cdot {\bf n} ds =-\tau_i\\
-%\end{gather}
-%
-The mobility problem for $N_b$-body system in a Stokes flow leads to a second-kind boundary integral equations (BIE) with a density function $\eta({\bf x}$ that is given by \cite{Lukas19}
-\begin{equation}
-\label{mobility}
-\begin{aligned}
-{\bf v}_i + &\omega_i\times({\bf x}-{\bf a}_i)\\
- =& -\frac12\eta({\bf x}) + D[\eta]({\bf x}) \\
-&+ \sum_{i=1}^N\big({\bf S}({\bf x}, {\bf a}_i){\bf F}_i+ {\bf R}({\bf x}, {\bf a}_i)t_i\big)+{\bf u}_\infty, \quad {\bf x}\in\Gamma \\
-\end{aligned}
-\end{equation}
-%
-with two constraints 
-%
-\begin{center}
-\begin{equation}
-\label{mobility2}
-\int_{\partial \Gamma_i}\eta\cdot \nu ds = {\bf 0},
-\end{equation}
-\end{center}
-%
-\begin{center}
-\begin{equation}
-\label{mobility3}
-\int_{\partial \Gamma_i}\eta\times({\bf x}-{\bf a}_i)\cdot \nu ds ={\bf 0},
-\end{equation}
-\end{center}
-%
-where the two-dimensional Stokeslet and the Rotlet are
-%
-\begin{gather}
-{\bf S}({\bf x}, {\bf a}) = \frac{1}{4\pi}\left(-\log(|({\bf x}-{\bf a})|){\bf I}+\frac{({\bf x}-{\bf a})\otimes({\bf x}-{\bf a})}{|({\bf x}-{\bf a})|^2}\right) \\ 
-{\bf R}({\bf x},{\bf a})=\frac{({\bf x}-{\bf a})^\perp}{4\pi|({\bf x}-{\bf a})|^2}.
-\end{gather}
-%
-%Here ${\bf r}={\bf x}-{\bf a}$ and $\rho=|{\bf r}|$.
-${\bf F}_i$ and $t_i$ are particle force and torque calculated from action of hydrophobic attractions.
-From equations~\eqref{mobility}--\eqref{mobility3}, we have translational velocity ${\bf v}_i$, angular velocity $\omega_i$, and density function $\eta$ as unknowns.
-This system of equations is then solvable with the use of an iterative method such as GMRES or conjugate gradient iterations.
+where $\uu$ is the velocity, $p$ is the pressure, and $\uu_\infty$ is
+the background flow. Each particle $\Gamma_i$ with center $\aa_i$ is
+assumed to be a rigid body, so its two-dimensional velocity can be
+written as
+\begin{align}
+  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
+    \xx \in \Gamma_i,
+\end{align}
+where $\vv_i$ is its translational velocity and $\omega_i$ is its
+angular velocity. Therefore, the no-slip boundary condition of
+the velocity field is 
+\begin{align}
+  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
+    \xx \in \bd\Gamma_i.
+\end{align}
+To determine the translational and angular velocities of each rigid
+body, we impose a force balance and torque balance. Matching the total
+force and torque in~\eqref{eqn:hydrophobicAttraction} with the
+hydrodynamic force, we require
+\begin{align}
+  \label{eqn:force}
+  \FF_i &= \int_{\bd\Gamma_i} \ssigma \cdot \nnu_i \, ds, \\
+  \label{eqn:torque}
+  T_i &= \int_{\bd\Gamma_i} (\xx - \aa_i)^\perp \cdot 
+    (\ssigma \cdot \nnu_i) \, ds,
+\end{align}
+where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
+\right)$ is the hydrodynamic stress tensor.
 
@@
 
+%%%
 \section{\label{IEM}Integral Equation Method}
+Since the fluid velocity is assumed to be Stokesian, it can be written
+in terms of layer potentials. Following previous work of~\cite{Lukas19},
+we represent the velocity as the sum of a double-layer potential and the
+$N_b$ Stokeslets and Rotlets
+\begin{align}
+  \label{eqn:velocity}
+  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
+    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
+    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
+\end{align}
+The double-layer potential is
+\begin{align}
+  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
+    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
+    \eeta(\yy) \, ds_\yy,
+\end{align}
+where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
+centered at $\aa_i$ are
+\begin{align}
+  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log(\rho) + 
+    \frac{\rr \otimes \rr}{\rho^2} \FF_i \right), \\
+  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
+\end{align}
+where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
+torque-free and has force $\FF$, and the Rotlet force-free and has
+torque $T$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
+total force~\eqref{eqn:force} and torque~\eqref{eqn:torque} conditions
+if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
+Matching the limit of~\eqref{eqn:velocity} with the rigid body motion,
+and imposing that $\DD[\eeta]$ is force- and torque-free, the density
+function $\eeta$, Stokeslet strength, $\FF_i$, and Rotlet strength $T_i$
+satisfy
+\begin{alignat}{3}
+  \nonumber
+  \vv_j + \omega_j (\xx - \aa_j)^\perp &= \uu_\infty(\xx)
+    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
+  \label{eqn:SKIE}
+    &+ \sum_{i=1}^{N_b} 
+    \left(\SS(\xx,\aa_i) \FF_i + \RR(\xx,\aa_i) T_i\right),
+    \quad &&\xx \in \bd \Gamma_j, \\
+  \label{eqn:mobility1}
+  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, ds &= {\bf 0}, 
+  &&i = 1,\ldots,N_b, \\
+  \label{eqn:mobility2}
+  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu ds &= 0,
+  &&i = 1,\ldots,N_b.
+\end{alignat}
+%
+%The mobility problem for $N_b$-body system in a Stokes flow leads to a second-kind boundary integral equations (BIE) with a density function $\eta({\bf x}$ that is given by \cite{Lukas19}
+%\begin{equation}
+%\label{mobility}
+%\begin{aligned}
+%{\bf v}_i + &\omega_i\times({\bf x}-{\bf a}_i)\\
+% =& -\frac12\eta({\bf x}) + D[\eta]({\bf x}) \\
+%&+ \sum_{i=1}^N\big({\bf S}({\bf x}, {\bf a}_i){\bf F}_i+ {\bf R}({\bf x}, {\bf a}_i)t_i\big)+{\bf u}_\infty, \quad {\bf x}\in\Gamma \\
+%\end{aligned}
+%\end{equation}
+%%
+%with two constraints 
+%%
+%\begin{center}
+%\begin{equation}
+%\label{mobility2}
+%\int_{\partial \Gamma_i}\eta\cdot \nnu ds = {\bf 0},
+%\end{equation}
+%\end{center}
+%%
+%\begin{center}
+%\begin{equation}
+%\label{mobility3}
+%\int_{\partial \Gamma_i}\eta\times({\bf x}-{\bf a}_i)\cdot \nnu ds ={\bf 0},
+%\end{equation}
+%\end{center}
+%%
+%where the two-dimensional Stokeslet and the Rotlet are
+%%
+%\begin{gather}
+%{\bf S}({\bf x}, {\bf a}) = \frac{1}{4\pi}\left(-\log(|({\bf x}-{\bf a})|){\bf I}+\frac{({\bf x}-{\bf a})\otimes({\bf x}-{\bf a})}{|({\bf x}-{\bf a})|^2}\right) \\ 
+%{\bf R}({\bf x},{\bf a})=\frac{({\bf x}-{\bf a})^\perp}{4\pi|({\bf x}-{\bf a})|^2}.
+%\end{gather}
+%
+%Here ${\bf r}={\bf x}-{\bf a}$ and $\rho=|{\bf r}|$.
+Given a collection of particles with forces and torques calculated from
+the hydrophobic interactions and the short range repulsion,
+equations~\eqref{eqn:SKIE}--\eqref{eqn:mobility2} form a solvable set of
+integral equations for the translational velocities $\vv_i$, the angular
+velocities $\omega_i$, and the density function $\eeta$.
 
-\section{\label{results}Numerical Results}
+\todo[inline]{Talk about how to solve numerically. Quadrature, time
+stepping, collocation, etc.}
+This system of equations is then solved iteratively with block-diagonal
+preconditioned GMRES.
 
-\subsection{Single Particle Validations}
+%%%
+
+\section{\label{validation}Model Validation}
+
+\subsection{Jeffery Orbit}
 
@@
 
-\subsection{Tank-Treading Vesicles}
-
-\subsubsection{Relaxtion}
+\subsection{Self-Assembly and Relaxtion}
 
@@
 \end{figure}
+
+%%%
+
+\section{\label{results}Numerical Results}
+
+\subsection{Tank-Treading Vesicles}
 
@@
 \begin{center}
+\hspace{-1cm}
 \includegraphics[height=2in]{ReducedArea.pdf}
-\hspace{-0.5cm}
+\hspace{-1cm}
 \includegraphics[height=2in]{ArcLength.pdf}
+\hspace{-1cm}
+\includegraphics[height=2in]{ExcLength.pdf}
 \end{center} 
@@
 \centering
-\includegraphics[height=1.2in]{N116_ext_0.pdf}
-\includegraphics[height=1.2in]{N116_ext_2500.pdf}
-\includegraphics[height=1.2in]{N116_ext_5000.pdf}
-\includegraphics[height=1.2in]{N116_ext_7500.pdf}
-%\includegraphics[width=0.24\textwidth]{step0Pres.eps}
-%\includegraphics[width=0.24\textwidth]{step2500Pres.eps}
-%\includegraphics[width=0.24\textwidth]{step5000Pres.eps}
-%\includegraphics[width=0.24\textwidth]{step7500Pres.eps}
+\includegraphics[height=2.in]{N116_ext_0.pdf}
+\includegraphics[height=2.in]{N116_ext_2500.pdf}\\
+\includegraphics[height=2.in]{N116_ext_5000.pdf}
+\includegraphics[height=2.in]{N116_ext_7500.pdf}
   \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
@@
 
-\begin{figure}
-\centering
-\includegraphics[height=1.2in]{N116_cont_a.pdf}
-\includegraphics[height=1.2in]{N116_cont_b.pdf}
-\includegraphics[height=1.2in]{N116_cont_c.pdf}
-\includegraphics[height=1.2in]{N116_cont_d.pdf}
-%\includegraphics[width=0.24\textwidth]{step0Pres.eps}
-%\includegraphics[width=0.24\textwidth]{step2500Pres.eps}
-%\includegraphics[width=0.24\textwidth]{step5000Pres.eps}
-%\includegraphics[width=0.24\textwidth]{step7500Pres.eps}
-  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
-  }
-    \label{figure8}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics[height=1.2in]{N116_cont_a.pdf}
+%\includegraphics[height=1.2in]{N116_cont_b.pdf}
+%\includegraphics[height=1.2in]{N116_cont_c.pdf}
+%\includegraphics[height=1.2in]{N116_cont_d.pdf}
+%  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
+%  }
+%    \label{figure8}
+%\end{figure}
 
@@
 \begin{equation}
-u_p(x) = \int_{\Sigma_p} \frac{\partial G(x,y)}{\partial \nu} \eta(y) \,\dif S(y).
+u_p(x) = \int_{\Sigma_p} \frac{\partial G(x,y)}{\partial \nnu} \eta(y) \,\dif S(y).
 \end{equation}
@@
 \label{eq:jumpstress1}
-J_{p} = 2\rho^{-1} \eta  v_p \nu 
-+ 2\rho \nabla \eta \cdot \tau_i(\nabla v_p \cdot \tau_i \nu -  \nabla v_p \cdot \nu \tau_i).
+J_{p} = 2\rho^{-1} \eta  v_p \nnu 
++ 2\rho \nabla \eta \cdot \tau_i(\nabla v_p \cdot \tau_i \nnu -  \nabla
+   v_p \cdot \nnu \tau_i).
 \end{equation}
-Here $\nu$ is the unit normal, $\{\tau_i\}_{i=1}^2$ are orthonormal tangent vectors,
+Here $\nnu$ is the unit normal, $\{\tau_i\}_{i=1}^2$ are orthonormal tangent vectors,
 and ${\bf X}$ is the skew symmetric matrix with axial vector $x$, i.e.
@@
   \label{eq:prejump}
-  F_p + i G_p = \gamma \int_{\Sigma_p}  ({\bf U}_2\nu)^+ - ({\bf U}_2\nu)^-\,\dif S
+  F_p + i G_p = \gamma \int_{\Sigma_p}  ({\bf U}_2\nnu)^+ - ({\bf
+  U}_2\nnu)^-\,\dif S
 \end{equation}
@@
   F_p + i G_p
-  &= \gamma \int_{\Sigma_p} {\bf T} \nu + ix \times {\bf T} \nu \,\dif S \\
-  &= \gamma \int_{\Sigma_p}  {\bf U}_1\nu  + ({\bf U}_2\nu)^+ + {\bf U}_3\nu\,\dif S
+  &= \gamma \int_{\Sigma_p} {\bf T} \nnu + ix \times {\bf T} \nnu \,\dif S \\
+  &= \gamma \int_{\Sigma_p}  {\bf U}_1\nnu  + ({\bf U}_2\nnu)^+ + {\bf
+  U}_3\nnu\,\dif S
 \end{align*}
@@
 \begin{equation*}
-  \int_{\Sigma_p}  {\bf U}_1 \nu\,\dif S
+  \int_{\Sigma_p}  {\bf U}_1 \nnu\,\dif S
   = \int_{\mathbb{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
@@
 \begin{equation*}
-  \int_{\Sigma_p}  {\bf U}_3 \nu\,\dif S
+  \int_{\Sigma_p}  {\bf U}_3 \nnu\,\dif S
   = -\int_{U_p} \nabla \cdot {\bf U}_3 \,dx = 0.
@@
 \[
-0 = -\int_{U_p} \nabla \cdot {\bf U}_2 \,dx = \int_{\Sigma_p}  ({\bf U}_2 \nu)^-\,\dif S.
+0 = -\int_{U_p} \nabla \cdot {\bf U}_2 \,dx = \int_{\Sigma_p}  ({\bf
+U}_2 \nnu)^-\,\dif S.
 \]
@@
   \item $ \lim_{x \to x_0^\pm } u_p(x) = \pm\frac{1}{2}\eta(x_0) + (D\eta)(x_0)$
-  \item $ \lim_{x \to x_0^+ } (\nabla u_p \cdot \nu) (x) = \lim_{x \to x_0^-} (\nabla u \cdot \nu)(x)$
+  \item $ \lim_{x \to x_0^+ } (\nabla u_p \cdot \nnu) (x) = \lim_{x \to
+    x_0^-} (\nabla u \cdot \nnu)(x)$
   \end{enumerate}
@@
     \nabla u_p^+ - \nabla u_p^-
-    &= \nabla (u_p^+ - u_p^-) \cdot t_i t_i +  (\nabla  u_p^+\cdot \nu  - \nabla u_p^- \cdot \nu) \nu\\
+    &= \nabla (u_p^+ - u_p^-) \cdot t_i t_i +  (\nabla  u_p^+\cdot
+    \nnu  - \nabla u_p^- \cdot \nnu) \nnu\\
     &= \nabla \eta \cdot \tau_i \tau_i
@@
   \begin{align*}
-    &({\bf T}_2\nu)^+ - ({\bf T}_2\nu)^-
+    &({\bf T}_2\nnu)^+ - ({\bf T}_2\nnu)^-
     \\
-    &= 2\rho^{-1} u_p^+v_p \nu + 2\rho \nabla u_p^+ \cdot \nabla v_p \nu
-    - 2 \rho \nabla u_p^+  \nabla v_p \cdot \nu
-    - 2 \rho \nabla v_p  \nabla u_p^+ \cdot \nu\\
-    &-2\rho^{-1} u_p^-v_p \nu - 2\rho \nabla u_p^- \cdot \nabla v_p \nu
-    + 2 \rho \nabla u_p^-  \nabla v_p \cdot \nu
-    + 2 \rho \nabla v_p  \nabla u_p^- \cdot \nu\\
-    &= 2\rho^{-1} \eta v_p \nu + 2\rho \nabla \eta \cdot \tau_i \tau_i \cdot \nabla v_p \nu
-    - 2\rho \nabla \eta \cdot \tau_i \tau_i \nabla v_p \cdot \nu + 0\\
+    &= 2\rho^{-1} u_p^+v_p \nnu + 2\rho \nabla u_p^+ \cdot \nabla v_p
+    \nnu
+    - 2 \rho \nabla u_p^+  \nabla v_p \cdot \nnu
+    - 2 \rho \nabla v_p  \nabla u_p^+ \cdot \nnu\\
+    &-2\rho^{-1} u_p^-v_p \nnu - 2\rho \nabla u_p^- \cdot \nabla v_p \nnu
+    + 2 \rho \nabla u_p^-  \nabla v_p \cdot \nnu
+    + 2 \rho \nabla v_p  \nabla u_p^- \cdot \nnu\\
+    &= 2\rho^{-1} \eta v_p \nnu + 2\rho \nabla \eta \cdot \tau_i \tau_i
+    \cdot \nabla v_p \nnu
+    - 2\rho \nabla \eta \cdot \tau_i \tau_i \nabla v_p \cdot \nnu + 0\\
     &= J_p.
@@
   \[
-  ({\bf U}_2\nu)^+ - ({\bf U}_2\nu)^-
+  ({\bf U}_2\nnu)^+ - ({\bf U}_2\nnu)^-
   =
-  ({\bf I} + i {\bf X})(({\bf T}_2\nu)^+ - ({\bf T}_2\nu)^-)
+  ({\bf I} + i {\bf X})(({\bf T}_2\nnu)^+ - ({\bf T}_2\nnu)^-)
   = ({\bf I} + i {\bf X})J_p
@@
 
-%\bibliographystyle{jfm}
+\bibliographystyle{jfm}
 \bibliography{reference}% Produces the bibliography via BibTeX.

### 2021-07-08 code/examples/shear_input.m

@@ -43,8 +43,8 @@ options.verbose   = true;
 options.timeOrder = 2;
 options.gmresTol  = 1e-10;
 
-options.usePlot   = false;
-options.tracer    = true;
+options.usePlot   = true;
+options.tracer    = false;
 options.plotAxis  = [-10 10 -10 10];
 
 % 1. Please input the number of bodies and have the corresponding initial

### 2021-07-08 code/examples/vonMisesBC.m

@@ -13,6 +13,7 @@ prams.nb = 25;      % number of bodies
 prams.sstep = 0;   % starting step
 
 radii = [1.0342    1.0017    0.9652    0.9881    1.0321    0.9671    0.9830    1.0466    1.0306    0.9722    1.0500    0.9564    0.992 0.9904    0.9900    0.9612    0.9924    1.0114    1.0488    0.9720    0.9854    0.9766    0.9791    0.9688    0.9523];
+radii = ones(size(radii));
 ar    = radii([10:25 1:9]);
 
 prams.rho = 2.0;      % screen length

### 2021-07-08 code/src/rigid2D.m

@@ -81,7 +81,6 @@ while step <= prams.m
     geom1 = capsules(prams,xc1,tau1);
     [Up1, wp1,~,~,etaY,etaS,force,torque] = tt.timeStep(geom1,etaY0,etaS0);
     etaY0 = etaY; etaS0 = etaS;
-
     
     % Applying two-step Adams-Bashforth
     xc2  = xc1  + tt.dt*(1.5*Up1 - 0.5*Up0 );

### 2021-07-08 doc/main_jfm.tex
updates

@@
 
-To study the deformation of a closed bilayer structure under a shear flow using the proposed algorithm, 
-we adopt a widely tested numerical simulation in both continuum and molecular dynamics models, single vesicle under a shear flow.
-The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
-Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
-the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.
-
-For the target bilayer, a circular initial shape is chosen to perform the relaxation run. This vesicle-like 
-structure consists of $N=58$ disks with radius $r=0.5$ and the starting diameter for the vesicle is about 
-$8.5$ length units.
+In order to examine the dynamics of the Janus-vesicle using the HAP coupling with hydrodynamics interactions, for the target bilayer, a circular initial shape is chosen to perform the relaxation run. 
+This vesicle-like structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
+the vesicle is about $8.5$ length units.
 The starting center of mass position of the vesicle is pinned at the origin and we track particle velocities 
@@
 For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
-Figure~\ref{figure2} shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$.
-In the same figure, the variation of mean particle orientation $\theta$ also decreases as expected.
-The time step size
-$\Delta t=0.2$ is used for all simulations including the relaxation run.
+Figure~\ref{figure2}(a) shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$.
+In the same figure, the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property
+of the model. This implies that a local energy minimum and the equilibrium configuration are nearly attained.
+The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
+Figure~\ref{figure2}(b) shows the configuration difference between starting and ending frames in the relaxation run.
 
@@
   \caption{Vesicle relaxes under a quiescent flow.
-The blue dashed curve and the solid curve are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively.
+(a) The blue dashed curve and the solid curve are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively.
 The red curve shows the decreasing trend of the mean magnitude of particle orientation change.
 The black dashed line shows the reference of how all magnitudes decay.
+(b) Bilayer configurations for $t=0$(gray) and $t=1000$(red) with particle directors.
   }
@@
 
+To study the deformation of a closed bilayer structure under a shear flow using the proposed algorithm, 
+we adopt a widely tested numerical simulation in both continuum and molecular dynamics models, single vesicle under a shear flow.
+The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
+Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
+the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.
+
 The snapshots of the simulation for single vesicle in a shear flow are shown in Figure~\ref{figure3}.
@@
 To demonstrate the tank-treading behavior of the vesicle, panels (b) and (d) provide the streamlines of the 
-fluid velocity over the whole computational domain when the shear flow passes through the vesicle. The tank-treading motion of the structure is then observed.
+fluid velocity over the whole computational domain when the shear flow passes through the structure.
+The tank-treading motion of the structure is then observed, for instance, the particle velocities in panel (d) indicate a clockwise tank-treading movement.
 
@@
 
-In order to extract more physical properties of the proposed model, we track the total length of the bilayer structure and the reduced area over the time.
+In order to extract more physical properties of the proposed model, we track the total length of the bilayer structure, the reduced area over the time, and the excess length.
 Here the enclosed area and the length of the structure are calculated from the midplane.
@@
 The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ is the vesicle area and $L$ is the arc length of the vesicle with respect to the midplane. 
-Since the starting configuration is close to a circular shape, the reduced are decreases from a value very close to $1$.
+Furthermore, the excess length is given by $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
+Since the starting configuration is close to a circular shape, the reduced area decreases from a value very close to $1$.
 It is clear that a slower shear rate generates a higher reduced area and has a faster convergence.
+With a converging total arc length, a slower shear rate also produces a smaller excess length.
 The small oscillations in all results are due to the granularity of the bilayer which tend to having a slightly non-smooth curve in simulations.
@@
 Figure~\ref{figure5} shows the schematic of the test.
-A particle pair is initially marked and we then track the positions and layer velocities over the time.
+A particle pair is initially marked and we then track the positions and mean angle $\theta(t)$ between particle relative position with respect to the vesicle center over the time.
 It is clear to see that the outer leaflet always has larger
-tangential velocity than the one from inner leaflet. This inter-leaflet sliding matches what has been seen
+tangential velocity than the one from inner leaflet and the mean angle $\theta(t)$ increases. 
+This inter-leaflet sliding phenomenon is consistent with what has been seen
 in articles in molecular dynamics simulations. %%% need some citations
@@
 \end{center} 
-  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) Reduced area transitions over time. 
+  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) Reduced area transitions over time. (c) Excess length of the midplanes.
 A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
-A slower shear rate generates a faster convergence in the reduced area. 
+A slower shear rate generates a faster convergence in the reduced area and smaller excess length. 
   }
@@
   \caption{For the shear rate $\dot\gamma=0.005$, the inter-monolayer slip is be observed.
-The curves in black and blue represent the tangential velocities of inner and outer leaflet, respectively.
-The configuration plots have two fixed particles marked and positioned with respect to the corresponding time $t$.
+The curve in black represents the mean angle between each particle pair where the angle is calculated from the relative position of particles using the vesicle center of mass position.
+The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=\{2000,5200,9000\}$.
   }

### 2021-07-09 doc/main_jfm.tex
updates
updated Section 2

@@
 \newcommand{\FF}{\mathbf{F}}
+\newcommand{\GG}{\mathbf{G}}
 \newcommand{\nnu}{\boldsymbol{\nu}}
@@
 \newcommand{\uu}{\mathbf{u}}
-\renewcommand{\vv}{\mathbf{v}}
+\newcommand{\vv}{\mathbf{v}}
 \newcommand{\yy}{\mathbf{y}}
@@
  \affiliation{
-\aff{1} Department of Mathematics, \\Fordham University, Bronx, New York 10458, USA
+\aff{1}Department of Mathematics, \\Fordham University, Bronx, New York 10458, USA
 \aff{2}Department of Scientific Computing, \\Florida State University, Tallahassee, Florida 32306, USA
@@
 \section{Governing  Equations}
-\subsection{Hydrophobic Attraction Potential (HAP)}
+\subsection{\label{mobility}Mobility Problem}
+The governing equations of $N_b$-body particles suspended in the
+two-dimensional, unbounded
+domain $\Omega$ are
+\begin{alignat}{3}
+  -\mu \Delta \uu + \nabla p &= 0 \qquad \qquad && \xx \in \Omega, \\
+  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
+  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
+\end{alignat}
+%
+where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure, and $\uu_\infty$ is
+the background flow. Each particle $\Gamma_i$ with center $\aa_i$ is
+a rigid body, and its velocity satisfies 
+\begin{align}
+  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
+    \xx \in \Gamma_i,
+\end{align}
+where $\vv_i$ is its translational velocity and $\omega_i$ is its
+angular velocity.
+Here, $\langle x, y \rangle^{\perp} = \langle -y, x \rangle$.
+Therefore, the no-slip boundary condition of
+the velocity field is 
+\begin{align}
+  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
+    \xx \in \bd\Gamma_i.
+\end{align}
+To determine the translational and angular velocities of each rigid body,
+we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each particle.
+Since the small particles are intertialess, force balance gives 
+\begin{alignat}{2}
+  \label{eqn:force}
+  \FF_i &+ \int_{\bd\Gamma_i} \ssigma \cdot \nnu_i \, ds && = \mathbf{0}, \\
+  \label{eqn:torque}
+  T_i &+ \int_{\bd\Gamma_i} (\xx - \aa_i)^\perp \cdot 
+    (\ssigma \cdot \nnu_i) \, ds && = 0,
+\end{alignat}
+where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
+\right)$ is the hydrodynamic stress tensor (pressure tensor).
 
-The Hydrophobic attraction potential (HAP) is given by
-\begin{equation}
-\label{eq:main}
-\Phi(\Omega,f) = \gamma  \min_{u \in \mathcal{A}}
- I[u]  = \int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2 \,dx,
-\end{equation}
-%
-where $\gamma$ the interfacial tension, $\rho$ the screened length, and this domain functional describes the energy associated with hydrophobic surfaces~\cite{Fu20}.
-From the first domain variation of HAP, we obtain a hydrophobic stress tensor which is given as follows,
-
+\subsection{Imposed Forces}
+The imposed forces and torques contain two parts. 
+The first part comes from the hydrophobic attraction potential (HAP).
+This potential was introduced in \cite{Fu20} and
+models hydrophobic attraction by solving the screened Laplace equation boundary value problem
+\begin{alignat}{2}
+  \label{SL}
+-\rho^2 \Delta u + u &=0,            && \mathbf{x} \in \Omega,\\
+\label{SLbc}
+u(\mathbf{x}) &= f_i(\mathbf{x}),\qquad  && \mathbf{x} \in \Gamma_i, \\
+\label{SLff}
+u &\to 0,                          &&|\mathbf{x}| \to \infty,
+\end{alignat}
+where $f_i$ is material label with $f_i = 0$, resp. $1$ representing hydrophilic, resp. hydrophobic, 
+portions of the surface, and $\rho$ is the decay length of attraction.
+The forces and torques for this attraction are 
+\begin{align}
+  \label{eqn:hydrophobicAttraction}
+  \FF_i^{\text{hydro}} = \int_{\bd \Gamma_i} {\bf T}\cdot \nnu_i \, dS, 
+    \quad 
+  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) dS,
+\end{align}
+where
 \begin{equation}
@@
 = \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
-  u|^2 \mathbf{I} - \nabla u\otimes \nabla u\right).
+  u|^2 \mathbf{I} - \nabla u\otimes \nabla u\right)
 \end{equation}
-%
-The integration over boundaries gives force and torque due to the
-hydrophobic attraction 
-\begin{align}
-  \label{eqn:hydrophobicAttraction}
-  \FF_i = \int_{\bd \Gamma_i} {\bf T}\cdot \nnu_i \, dS, 
-    \quad  \text{ and } \quad
-  T_i = \int_{\Gamma_i} (\xx - \aa_i) \times ({\bf T} \cdot \nnu_i) dS,
-\end{align}
-%
-where $\xx \in \Gamma_i$, $\aa_i$ is the $i^{th}$ particle center, and
-$\nnu_i$ is the outward normal of the $i^{th}$ particle.
+is the hydrophobic stress tensor.  The parameter $\gamma$ is interfacial tension. 
+The forces $\FF_i^{\text{hydro}}$ and torques $T_i^{\text{hydro}}$ are responsible for
+forming particle aggregates that partially sequester 
+the hydrophobic portions of the particle surface.
 
-%\begin{equation}
-%        \label{SL}
-%\begin{cases}
-% -\rho^2 \Delta u + u =0 & \text{ in } \Omega,\\
-%  u(x) = f(x)  &\text{ on }\Sigma, \\
-%   u(x) \to 0, &\text{ as } x \to \infty.
-%\end{cases}
-%\end{equation}
+The second part of the imposed forces and torques comes from repulsion between proximal particles.
+We define 
+\begin{equation}
+  \label{REPUL}
+  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\mathbf{x}_{ij} - \mathbf{y}_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
+  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\mathbf{x}_{ij} - \mathbf{a}_i)^{\perp}\cdot \frac{\mathbf{x}_{ij} - \mathbf{y}_{ij}}{\rho_{ij}} P(\rho_{ij})
+\end{equation}
+where $\mathbf{x}_{ij} \in \partial \Gamma_i$, 
+$\mathbf{y}_{ij} \in \partial \Gamma_j$, 
+and $\rho_{ij} = |\mathbf{x}_{ij} - \mathbf{y}_{ij}|$
+is the distance between the pair of particles.
+The repulsion profile $P(r)$ is zero for distances $r$ larger than a repulsion length scale
+$\rho_0$.  As such, \eqref{REPUL} ignores particles $\Gamma_j$ outside a tubular neighborhood
+of $\Gamma_i$.  For $0 \leq r < \rho_0,$ we use $P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently
+large to prevent particle collisions.  The total imposed force and torque are
+\begin{equation}
+  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
+    T_i =   T_i^{\text{hydro}} +   T_i^{\text{repul}}.
+\end{equation}
 
-\subsection{Nondimensionalizations}
+\subsection{Time marchning and Nondimensionalizations}
+From the mobility problem, we obtain translational and angular velocities of the $N_b$-body system.
+A second order Adam-Bashforth scheme updates the particle positions and orientations.
+dynamics but body collisions may occur during the simulation while a relatively large time step is chosen.
+We therefore impose a short range repulsion that it will be turned on when the distance between two boundary points on different bodies are within one characteristic length.
 
@@
 Finally, we conclude the work and briefly give the picture of our future work.
-
-\subsection{\label{mobility}Mobility Problem}
-
-The governing equations of $N_b$-body bodies suspended in the unbounded
-domain $\Omega$ are
-\begin{alignat}{3}
-  -\Delta \uu + \mu\nabla p, &= 0 \qquad \qquad && \xx \in \Omega, \\
-  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
-  \uu &\to \uu_\infty, && |\xx| \to \infty,
-\end{alignat}
-%
-where $\uu$ is the velocity, $p$ is the pressure, and $\uu_\infty$ is
-the background flow. Each particle $\Gamma_i$ with center $\aa_i$ is
-assumed to be a rigid body, so its two-dimensional velocity can be
-written as
-\begin{align}
-  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
-    \xx \in \Gamma_i,
-\end{align}
-where $\vv_i$ is its translational velocity and $\omega_i$ is its
-angular velocity. Therefore, the no-slip boundary condition of
-the velocity field is 
-\begin{align}
-  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
-    \xx \in \bd\Gamma_i.
-\end{align}
-To determine the translational and angular velocities of each rigid
-body, we impose a force balance and torque balance. Matching the total
-force and torque in~\eqref{eqn:hydrophobicAttraction} with the
-hydrodynamic force, we require
-\begin{align}
-  \label{eqn:force}
-  \FF_i &= \int_{\bd\Gamma_i} \ssigma \cdot \nnu_i \, ds, \\
-  \label{eqn:torque}
-  T_i &= \int_{\bd\Gamma_i} (\xx - \aa_i)^\perp \cdot 
-    (\ssigma \cdot \nnu_i) \, ds,
-\end{align}
-where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
-\right)$ is the hydrodynamic stress tensor.
-
-\subsection{Short Range Repulsion}
-
-At each time step, we examine the nearest grid points between each pair of body  boundaries. Within a specified distance $d$, we introduce a short range repulsive potential as follows
-
-\begin{equation}
-\Phi_{repul} = 1- \sin\left(\frac{\pi}{2} d\right).
-\end{equation}
-
-Here we would like to make a remark about the time marching scheme.
-From the mobility problem, we obtain velocity and torque profiles of an $N_b$-body system.
-A second order Adam-Bashforth scheme is used for updating the dynamics but body collisions may occur during the simulation while a relatively large time step is chosen.
-We therefore impose a short range repulsion that it will be turned on when the distance between two boundary points on different bodies are within one characteristic length.
 
@@
 Streamlines are plotted in purple.
+The insets of all panels are generated from the results of continuum modeling simulations and the streamlines have a perfect agreement to the numerical results.
   }

### 2021-07-13 doc/main_jfm.tex
fixed a renewcommand
worked on section 2

@@
 \newcommand{\uu}{\mathbf{u}}
-\newcommand{\vv}{\mathbf{v}}
+\renewcommand{\vv}{\mathbf{v}}
 \newcommand{\yy}{\mathbf{y}}
@@
 \subsection{\label{mobility}Mobility Problem}
-The governing equations of $N_b$-body particles suspended in the
-two-dimensional, unbounded
-domain $\Omega$ are
+We consider a suspension of $N_b$ particles suspended in a
+two-dimensional unbounded domain. The boundary of each particle is
+denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
+\cdots \cup \Gamma_{N_b}$. Assuming the flow is Stokesian, the governing
+equations are
 \begin{alignat}{3}
-  -\mu \Delta \uu + \nabla p &= 0 \qquad \qquad && \xx \in \Omega, \\
+  -\mu \Delta \uu + \nabla p &= \mathbf{0}, \qquad \qquad 
+    && \xx \in \Omega, \\
   \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
@@
 %
-where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure, and $\uu_\infty$ is
-the background flow. Each particle $\Gamma_i$ with center $\aa_i$ is
-a rigid body, and its velocity satisfies 
+where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
+and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
+with center $\aa_i$ is a rigid body, its velocity satisfies 
 \begin{align}
@@
 where $\vv_i$ is its translational velocity and $\omega_i$ is its
-angular velocity.
-Here, $\langle x, y \rangle^{\perp} = \langle -y, x \rangle$.
-Therefore, the no-slip boundary condition of
-the velocity field is 
+angular velocity.  Here, $\langle x, y \rangle^{\perp} = \langle -y, x
+\rangle$. Therefore, the no-slip boundary condition on each particle is
 \begin{align}
   \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
-    \xx \in \bd\Gamma_i.
+    \xx \in \Gamma_i.
 \end{align}
-To determine the translational and angular velocities of each rigid body,
-we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each particle.
-Since the small particles are intertialess, force balance gives 
+To determine the translational and angular velocities of each particle,
+we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
+particle. Since the small particles are intertialess, force balance
+gives 
 \begin{alignat}{2}
   \label{eqn:force}
-  \FF_i &+ \int_{\bd\Gamma_i} \ssigma \cdot \nnu_i \, ds && = \mathbf{0}, \\
+  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, ds = \mathbf{0},
+  && i=1,\ldots,N_b,\\
   \label{eqn:torque}
-  T_i &+ \int_{\bd\Gamma_i} (\xx - \aa_i)^\perp \cdot 
-    (\ssigma \cdot \nnu_i) \, ds && = 0,
+  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
+    (\ssigma \cdot \nnu_i) \, ds = 0 \qquad && i=1,\ldots,N_b,
 \end{alignat}
@@
   \label{SL}
--\rho^2 \Delta u + u &=0,            && \mathbf{x} \in \Omega,\\
+-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
 \label{SLbc}
-u(\mathbf{x}) &= f_i(\mathbf{x}),\qquad  && \mathbf{x} \in \Gamma_i, \\
+u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i, \\
 \label{SLff}
-u &\to 0,                          &&|\mathbf{x}| \to \infty,
+u &\to 0,                          &&|\xx| \to \infty,
 \end{alignat}
-where $f_i$ is material label with $f_i = 0$, resp. $1$ representing hydrophilic, resp. hydrophobic, 
-portions of the surface, and $\rho$ is the decay length of attraction.
-The forces and torques for this attraction are 
+where $f_i$ is material label with $f_i = 0$ ($1$) representing
+hydrophilic (hydrophobic) portions of the surface, and $\rho$ is the
+decay length of attraction.  The forces and torques for this attraction
+are 
 \begin{align}
   \label{eqn:hydrophobicAttraction}
-  \FF_i^{\text{hydro}} = \int_{\bd \Gamma_i} {\bf T}\cdot \nnu_i \, dS, 
+  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, dS, 
     \quad 
@@
 where
-\begin{equation}
+\begin{align}
   \label{eq:stress}
@@
   u|^2 \mathbf{I} - \nabla u\otimes \nabla u\right)
-\end{equation}
-is the hydrophobic stress tensor.  The parameter $\gamma$ is interfacial tension. 
-The forces $\FF_i^{\text{hydro}}$ and torques $T_i^{\text{hydro}}$ are responsible for
-forming particle aggregates that partially sequester 
-the hydrophobic portions of the particle surface.
+\end{align}
+is the hydrophobic stress tensor. The parameter $\gamma$ is interfacial
+tension. The forces $\FF_i^{\text{hydro}}$ and torques
+$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
+that partially sequester the hydrophobic portions of the particle
+surface.
 
-The second part of the imposed forces and torques comes from repulsion between proximal particles.
-We define 
-\begin{equation}
-  \label{REPUL}
-  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\mathbf{x}_{ij} - \mathbf{y}_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
-  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\mathbf{x}_{ij} - \mathbf{a}_i)^{\perp}\cdot \frac{\mathbf{x}_{ij} - \mathbf{y}_{ij}}{\rho_{ij}} P(\rho_{ij})
-\end{equation}
-where $\mathbf{x}_{ij} \in \partial \Gamma_i$, 
-$\mathbf{y}_{ij} \in \partial \Gamma_j$, 
-and $\rho_{ij} = |\mathbf{x}_{ij} - \mathbf{y}_{ij}|$
-is the distance between the pair of particles.
-The repulsion profile $P(r)$ is zero for distances $r$ larger than a repulsion length scale
-$\rho_0$.  As such, \eqref{REPUL} ignores particles $\Gamma_j$ outside a tubular neighborhood
-of $\Gamma_i$.  For $0 \leq r < \rho_0,$ we use $P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently
-large to prevent particle collisions.  The total imposed force and torque are
-\begin{equation}
+The second part of the imposed forces and torques comes from repulsion
+between proximal particles. We define 
+\begin{align}
+%  \label{eqn:REPUL}
+%  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\xx_{ij} -
+%  \yy_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
+%  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\xx_{ij} - \aa_i)^{\perp}\cdot
+%  \frac{\xx_{ij} - \yy_{ij}}{\rho_{ij}} P(\rho_{ij})
+%
+  \label{eqn:REPULforce}
+  \FF_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
+    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, \\
+  \label{eqn:REPULtorque}
+  T_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
+    (\xx - \aa_i)^{\perp} \cdot 
+    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, 
+\end{align}
+where $\xx \in \Gamma_i$ and $|\xx - \yy|$ is the distance between the
+pair of particles. The repulsion profile $P(r)$ is zero for distances
+$r$ larger than a repulsion length scale $\rho_0$. As
+such,~\eqref{eqn:REPULforce} and~\eqref{eqn:REPULtorque} ignore
+particles $\Gamma_j$ outside a tubular neighborhood of $\Gamma_i$. For
+$0 \leq r < \rho_0,$ we use $P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is
+sufficiently large to prevent particle collisions. The total imposed
+force and torque are
+\begin{align}
   \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
-    T_i =   T_i^{\text{hydro}} +   T_i^{\text{repul}}.
-\end{equation}
+  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
+  i=1,\ldots,N_b.
+\end{align}
 
-\subsection{Time marchning and Nondimensionalizations}
+\subsection{Time Marching and Nondimensionalizations}
 From the mobility problem, we obtain translational and angular velocities of the $N_b$-body system.

### 2021-07-14 doc/main_jfm.tex
finishing up revisions on section 2

@@
 \subsection{Time Marching and Nondimensionalizations}
-From the mobility problem, we obtain translational and angular velocities of the $N_b$-body system.
-A second order Adam-Bashforth scheme updates the particle positions and orientations.
-dynamics but body collisions may occur during the simulation while a relatively large time step is chosen.
-We therefore impose a short range repulsion that it will be turned on when the distance between two boundary points on different bodies are within one characteristic length.
+By solving the mobility problem, we obtain translational and angular
+velocities of the $N_b$-body system. A second-order Adam-Bashforth
+scheme updates the particle positions and orientations. By including the
+repulsion force~\eqref{eqn:REPULforce} and
+torque~\eqref{eqn:REPULtorque}, particle collisions are avoided even
+when using a relatively large time step.
 
-For a two-dimensional vesicle, we denote a constant initial radius $R_0$ and 
-the dimensionless shear rate is
-\begin{equation}
+For a two-dimensional vesicle, we denote a constant initial radius $R_0$
+and the dimensionless shear rate is
+\begin{align}
   \chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
-\end{equation}
+\end{align}
 %
-where $\dot\gamma$ the shear rate, $\kappa$ the bending rigidity, and $\mu$ the fluid viscosity~\cite{Finken08}.
+where $\dot\gamma$ the shear rate, $\kappa$ the bending rigidity, and
+$\mu$ the fluid viscosity~\cite{Finken08}.
 
@@
 %%%
-\section{\label{IEM}Integral Equation Method}
+\section{Integral Equation Method}
+\label{sec:IEM}
 Since the fluid velocity is assumed to be Stokesian, it can be written

### 2021-07-16 doc/main_jfm.tex
group editing of paper

@@
 %  \frac{\xx_{ij} - \yy_{ij}}{\rho_{ij}} P(\rho_{ij})
+%  \\
 %
@@
 \end{align}
+\todo[inline]{Repulsion force is a function of only the distance between
+the Janus particles instead of the integral around the particles.}
 where $\xx \in \Gamma_i$ and $|\xx - \yy|$ is the distance between the
@@
 \includegraphics[height=2in]{relax2.eps}
+  \todo[inline]{Put pressure of each of the two configurations below
+  this.}
   \caption{Vesicle relaxes under a quiescent flow.
@@
 \section{\label{results}Numerical Results}
+
+\todo[inline]{Introduce dimensionless shear rate here}
 
@@
 
+\todo[inline]{Figure/Table of the friction coefficient for different
+shear rates}
+
 \begin{figure}
@@
 
+\todo[inline]{Stream lines not right. Need to subtract a constant
+velocity instead of the background flow.}
 \begin{figure}
@@
 \centering
-\includegraphics[height=1.2in]{N58_rupt_0.pdf}
-\includegraphics[height=1.2in]{N58_rupt_200.pdf}
-\includegraphics[height=1.2in]{N58_rupt_400.pdf}
-\includegraphics[height=1.2in]{N58_rupt_600.pdf}
+\includegraphics[height=2.4in]{N58_rupt_0.pdf}
+\includegraphics[height=2.4in]{N58_rupt_200.pdf}
+\\
+\includegraphics[height=2.4in]{N58_rupt_400.pdf}
+\includegraphics[height=2.4in]{N58_rupt_600.pdf}
   \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
@@
 \subsection{Two Vesicles in a Linear Flow}
+
+\begin{figure}
+\centering
+\includegraphics[height=1.2in]{N116_shear_0.pdf}
+\includegraphics[height=1.2in]{N116_shear_3000.pdf}
+\includegraphics[height=1.2in]{N116_shear_6000.pdf}
+\includegraphics[height=1.2in]{N116_shear_9000.pdf}\\
+  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
+The background color indicates the magnitude of fluid pressure.
+From dark red to dark blue, it represents the the pressure varies from high to low values.
+The color bar is valid for all panels.
+Streamlines are plotted in purple.
+The insets of all panels are generated from the results of continuum modeling simulations and the streamlines have a perfect agreement to the numerical results.
+  }
+    \label{figure9}
+\end{figure}
+
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.24\textwidth]{N116_shear_vel_0.pdf}
+%\includegraphics[width=0.24\textwidth]{N116_shear_vel_3000.pdf}
+%\includegraphics[width=0.24\textwidth]{N116_shear_vel_6000.pdf}
+%\includegraphics[width=0.24\textwidth]{N116_shear_vel_9000.pdf}
+%  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
+%    \label{figure8}
+%\end{figure}
+
+\subsubsection{Shear Flow}
+Two vesicles in a shear flow is presented in Figures~\ref{figure9} where centers of mass are placed on the same horizontal level.
+With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \dot\gamma y$.
+An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.
+In other words, the adhesive behavior will be absent when two vesicles are centered
+at a different level and are well separated in $y$-direction.
+
+\todo[inline]{Migration pattern and/or separation distance. See Fig 8 in
+JCP paper by Rahimian, Veerapaneni, and Biros.}
 
@@
 %may need to add more here
-
-\begin{figure}
-\centering
-\includegraphics[height=1.2in]{N116_shear_0.pdf}
-\includegraphics[height=1.2in]{N116_shear_3000.pdf}
-\includegraphics[height=1.2in]{N116_shear_6000.pdf}
-\includegraphics[height=1.2in]{N116_shear_9000.pdf}\\
-  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
-The background color indicates the magnitude of fluid pressure.
-From dark red to dark blue, it represents the the pressure varies from high to low values.
-The color bar is valid for all panels.
-Streamlines are plotted in purple.
-The insets of all panels are generated from the results of continuum modeling simulations and the streamlines have a perfect agreement to the numerical results.
-  }
-    \label{figure9}
-\end{figure}
-
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.24\textwidth]{N116_shear_vel_0.pdf}
-%\includegraphics[width=0.24\textwidth]{N116_shear_vel_3000.pdf}
-%\includegraphics[width=0.24\textwidth]{N116_shear_vel_6000.pdf}
-%\includegraphics[width=0.24\textwidth]{N116_shear_vel_9000.pdf}
-%  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
-%    \label{figure8}
-%\end{figure}
-
-\subsubsection{Shear Flow}
-Two vesicles in a shear flow is resented in Figures~\ref{figure9} where centers of mass are placed on the same horizontal level.
-With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \dot\gamma y$.
-An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.
-In other words, the the adhesive behavior will be absent when two vesicles are centered
-at a different level and are well separated in $y$-direction.
 

### 2021-08-04 doc/main_jfm.tex
updates

@@
 
-For a two-dimensional vesicle, we denote a constant initial radius $R_0$
-and the dimensionless shear rate is
-\begin{align}
-  \chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
-\end{align}
-%
-where $\dot\gamma$ the shear rate, $\kappa$ the bending rigidity, and
-$\mu$ the fluid viscosity~\cite{Finken08}.
-
 %This paper is organized as follows.
@@
 \includegraphics[height=2in]{relax.eps}
-\includegraphics[height=2in]{relax2.eps}
-  \todo[inline]{Put pressure of each of the two configurations below
-  this.}
+\includegraphics[height=2in]{relax2.eps}\\
+\includegraphics[height=2.in]{N58_0pres.pdf}
+\includegraphics[height=2.in]{N58_5000pres.pdf}
+%  \todo[inline]{Put pressure of each of the two configurations below
+%  this.}
   \caption{Vesicle relaxes under a quiescent flow.
@@
 \todo[inline]{Introduce dimensionless shear rate here}
+
+Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of vesicles 
+under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
+The length unit is scaled by the length of phospholipids $l=2.5$ nm and we set the force is scaled from the 
+interfacial tension $\gamma=4.1$ pN nm. We then be able to calculate the corresponding 
+time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
+$\kappa=8.51$ kT $\approx35$ pN nm.
+
+For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0$ and the dimensionless shear rate 
+is referred from~\cite{Finken08}
+\begin{align}
+  \chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
+\end{align}
+%
+where $\dot\gamma$ the dimensional shear rate, and $\mu=1$ cP the fluid viscosity is used through this work.
 
@@
 \includegraphics[height=1.2in]{N116_shear_0.pdf}
-\includegraphics[height=1.2in]{N116_shear_3000.pdf}
-\includegraphics[height=1.2in]{N116_shear_6000.pdf}
-\includegraphics[height=1.2in]{N116_shear_9000.pdf}\\
+\includegraphics[height=1.2in]{N116_shear_2500.pdf}
+\includegraphics[height=1.2in]{N116_shear_5000.pdf}
+\includegraphics[height=1.2in]{N116_shear_7500.pdf}\\
   \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
@@
 \includegraphics[height=2.in]{N116_ext_0.pdf}
-\includegraphics[height=2.in]{N116_ext_2500.pdf}\\
-\includegraphics[height=2.in]{N116_ext_5000.pdf}
-\includegraphics[height=2.in]{N116_ext_7500.pdf}
+\includegraphics[height=2.in]{N116_ext_2000.pdf}\\
+\includegraphics[height=2.in]{N116_ext_4000.pdf}
+\includegraphics[height=2.in]{N116_ext_6500.pdf}
   \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).

### 2021-08-04 doc/main_jfm.tex
updates

@@
 An ellipsoidal particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$.
-Based on the theoretical Jeffery orbits with respect to the target angle $\chi(t)$,
+Based on the theoretical Jeffery orbits with respect to the target angle $\Theta(t)$,
 
 \begin{equation}
-\chi(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
+\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
 \end{equation}
@@
 \centering
-\includegraphics[width=0.4\textwidth]{JefferyOrbit.eps}
-  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method.
+\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
+\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
+  \caption{Comparison of the target angle $\Theta(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method.
 The schematic of the simulation setup is shown in the inset of the figure.
@@
 under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
-The length unit is scaled by the length of phospholipids $l=2.5$ nm and we set the force is scaled from the 
-interfacial tension $\gamma=4.1$ pN nm. We then be able to calculate the corresponding 
+The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
+interfacial tension $\gamma=4.1$ pN nm from ~\cite{Ryham16}. We then be able to calculate the corresponding 
 time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
@@
 
-For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0$ and the dimensionless shear rate 
-is referred from~\cite{Finken08}
+For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate 
+is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
 \begin{align}
@@
 %
-where $\dot\gamma$ the dimensional shear rate, and $\mu=1$ cP the fluid viscosity is used through this work.
+where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity is used through this work.
 

### 2021-08-04 doc/main_jfm.tex
updates

@@
 The preliminary test of the proposed model using the integral equation method is the numerical validation in Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate.
-An ellipsoidal particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$.
+An ellipsoidal particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\Theta = 0^\circ$.
 Based on the theoretical Jeffery orbits with respect to the target angle $\Theta(t)$,

### 2021-08-05 doc/main_jfm.tex
updates

@@
 
-\todo[inline]{Introduce dimensionless shear rate here}
+\todo[inline]{Introduce dimensionless shear rate here (and check the numbers)}
 
@@
 
-For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate 
-is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
+For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate $\chi$ is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
 \begin{align}
@@
 %
-where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity is used through this work.
+where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.
 
@@
 
-\todo[inline]{Figure/Table of the friction coefficient for different
-shear rates}
+\todo[inline]{Figure/Table of the friction coefficient for different shear rates (needs to revise)}
+
+\begin{equation}
+b = \frac{{\bf F}_{friction}}{v^\parallel} = \frac{{\bf F}_{friction}}{\int_\Sigma R \dot\theta dS}.
+\end{equation}
+
+\begin{table}[ht] 
+\caption{Friction Coefficients}
+\centering    
+\begin{tabular}{c c c c}
+\hline\hline                    
+Case $i$ & $\dot\gamma$ & $b_i$\\
+\hline 
+1 & 0.020 &  5.1648  \\
+2 & 0.025 &  5.2027  \\ 
+3 & 0.050 &  5.1944   \\ [1ex]
+\hline    
+\end{tabular} 
+\label{table1}
+\end{table}
 
@@
 
-\todo[inline]{Stream lines not right. Need to subtract a constant
-velocity instead of the background flow.}
 \begin{figure}
@@
 
-\todo[inline]{Migration pattern and/or separation distance. See Fig 8 in
-JCP paper by Rahimian, Veerapaneni, and Biros.}
+%\todo[inline]{Migration pattern and/or separation distance. See Fig 8 in
+%JCP paper by Rahimian, Veerapaneni, and Biros.}
 

### 2021-08-05 doc/main_jfm.tex
updates

@@
 
+The intermonolayer friction coefficient of the Janus-vesicle is calculated from the ratio of friction force and the 
+slip velocity. This quantity is given by 
 \begin{equation}
-b = \frac{{\bf F}_{friction}}{v^\parallel} = \frac{{\bf F}_{friction}}{\int_\Sigma R \dot\theta dS}.
+b = \frac{{\bf F}_{friction}}{v^\parallel} = \frac{{\bf F}_{friction}}{\int_{\Sigma_M} R \dot\theta dS}.
 \end{equation}
+%
+where $v^\parallel$ represents the tangential velocity at the midplane and $\Sigma_M$ the curve determined by the midplane.
 
-\begin{table}[ht] 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{Slip.eps}
+\end{center} 
+  \caption{For the shear rate $\dot\gamma=0.005$, the inter-monolayer slip is be observed.
+The curve in black represents the mean angle between each particle pair where the angle is calculated from the relative position of particles using the vesicle center of mass position.
+The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=\{2000,5200,9000\}$.
+  }
+    \label{figure5}
+\end{figure}
+
+\begin{table}
 \caption{Friction Coefficients}
@@
 \end{table}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.8\textwidth]{Slip.eps}
-\end{center} 
-  \caption{For the shear rate $\dot\gamma=0.005$, the inter-monolayer slip is be observed.
-The curve in black represents the mean angle between each particle pair where the angle is calculated from the relative position of particles using the vesicle center of mass position.
-The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=\{2000,5200,9000\}$.
-  }
-    \label{figure5}
-\end{figure}
 
@@
 \end{figure}
-
-%\begin{figure}
-%\centering
-%\includegraphics[height=1.2in]{N116_cont_a.pdf}
-%\includegraphics[height=1.2in]{N116_cont_b.pdf}
-%\includegraphics[height=1.2in]{N116_cont_c.pdf}
-%\includegraphics[height=1.2in]{N116_cont_d.pdf}
-%  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
-%  }
-%    \label{figure8}
-%\end{figure}
 
@@
 
+\section{\label{A2} Comparison between Continuum Model and the Proposed Model}
+
+\begin{figure}
+\centering
+\includegraphics[height=1.2in]{N116_cont_a.pdf}
+\includegraphics[height=1.2in]{N116_cont_b.pdf}
+\includegraphics[height=1.2in]{N116_cont_c.pdf}
+\includegraphics[height=1.2in]{N116_cont_d.pdf}
+  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
+  }
+    \label{figureB}
+\end{figure}
+
 \bibliographystyle{jfm}

### 2021-08-05 doc/main_jfm.tex
updates

@@
   \caption{Vesicle relaxes under a quiescent flow.
-(a) The blue dashed curve and the solid curve are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively.
+(a) The blue dashed and solid curves are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively.
 The red curve shows the decreasing trend of the mean magnitude of particle orientation change.
@@
 (b) Bilayer configurations for $t=0$(gray) and $t=1000$(red) with particle directors.
+  (c)-(d) show the fluid pressure profiles for $t=0$ and $t=1000$ where the background curves indicate the streamlines.
+In panel (c), the pressure value in internal fluid is much higher than the pressure outside of the bilayer.
+After the relaxation, this immersed permeable bilayer approaches a steady state as shown in panel (d).
   }

### 2021-08-06 doc/main_jfm.tex
updates

@@
 %
-where $a$, $b$ are semi-major and semi-minor axes, and the test aspect ratio of the particle is $2$.
-Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.
+where $a$, $b$ are semi-major and semi-minor axes, and the test aspect ratios of the particle are $2$ and $3$.
+Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from the Jeffery orbits.
 
@@
 \includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
-  \caption{Comparison of the target angle $\Theta(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method.
+  \caption{Comparisons of the target angle $\Theta(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method.
 The schematic of the simulation setup is shown in the inset of the figure.
+Here two cases of aspect ratio are validated, $a/b = 2$ and $a/b=3$.
   }
@@
 the vesicle is about $8.5$ length units.
-The starting center of mass position of the vesicle is pinned at the origin and we track particle velocities 
-to determine the initial configuration for later use such as single and multiple vesicle simulations.
+The starting center of mass position of the Janus-vesicle is pinned at the origin and particle velocities are tracked to determine the initial configuration for later use such as single and multiple vesicle simulations.
 This will prevent some numerical instability issues when the minimum of the total energy is not achieved. 
@@
 Figure~\ref{figure2}(a) shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$.
-In the same figure, the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property
-of the model. This implies that a local energy minimum and the equilibrium configuration are nearly attained.
+In the same figure, the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property of the model.
+This implies that a local energy minimum and the equilibrium configuration are
+nearly attained. 
 The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
 Figure~\ref{figure2}(b) shows the configuration difference between starting and ending frames in the relaxation run.
+The Figure~\ref{figure2}(c)-(d) demonstrate the fluid pressure profile of two configurations.
+The pressure inside the permeable Janus-vesicle decreases as expected.
 
@@
 \begin{align}
-  \chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
+  \chi = \dot\gamma \frac{\mu R_0^2}{\kappa},
 \end{align}
@@
 The tank-treading motion of the structure is then observed, for instance, the particle velocities in panel (d) indicate a clockwise tank-treading movement.
-
-% needs to add more details about inclination angle, tank-treading frequency, repulsion, ...etc.
 
@@
 \end{center} 
-  \caption{For the shear rate $\dot\gamma=0.005$, the inter-monolayer slip is be observed.
-The curve in black represents the mean angle between each particle pair where the angle is calculated from the relative position of particles using the vesicle center of mass position.
+  \caption{The schematic of the intermonolayer slip over a period of time.
+Taking shear rate $\dot\gamma=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position.
 The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=\{2000,5200,9000\}$.
+The midplane curve is denoted as $\Sigma_M$.
   }
@@
 \hline\hline                    
-Case $i$ & $\dot\gamma$ & $b_i$\\
+Case $i$ & $\chi_i$ & $b_i$\\
 \hline 
@@
 
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.24\textwidth]{N116_shear_vel_0.pdf}
-%\includegraphics[width=0.24\textwidth]{N116_shear_vel_3000.pdf}
-%\includegraphics[width=0.24\textwidth]{N116_shear_vel_6000.pdf}
-%\includegraphics[width=0.24\textwidth]{N116_shear_vel_9000.pdf}
-%  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
-%    \label{figure8}
-%\end{figure}
-
 \subsubsection{Shear Flow}
@@
 Streamlines are plotted in purple.
+The insets show the results produced from using continuum model that the streamlines have perfect agreements with the present results.
   }
@@
 \end{figure}
-
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.24\textwidth]{N116_ext_vel_0.pdf}
-%\includegraphics[width=0.24\textwidth]{N116_ext_vel_2500.pdf}
-%\includegraphics[width=0.24\textwidth]{N116_ext_vel_5000.pdf}
-%\includegraphics[width=0.24\textwidth]{N116_ext_vel_7500.pdf}
-%  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
-%    \label{figure6}
-%\end{figure}
 
@@
 %may need to add more here
+
+\todo[inline]{Make figure of the paths of the two centroids....}
 

### 2021-08-06 doc/main_jfm.tex
fixed up repulsion definition

@@
 The second part of the imposed forces and torques comes from repulsion
-between proximal particles. We define 
+between proximal particles. Given a pair particles indexed as $i$ and
+$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
+$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another. We then
+define the repulsion force and torque
 \begin{align}
@@
   \label{eqn:REPULforce}
-  \FF_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
-    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, \\
+  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
+    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
+    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
+    P'(|\tilde{\xx}_i - \tilde{\xx}_j|) \\
   \label{eqn:REPULtorque}
-  T_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
-    (\xx - \aa_i)^{\perp} \cdot 
-    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, 
+  T_i^{\text{repul}} &= \sum_{j \neq i} 
+    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
+    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
+    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
+    P'(|\tilde{\xx}_i - \tilde{\xx}_j|) 
 \end{align}
-\todo[inline]{Repulsion force is a function of only the distance between
-the Janus particles instead of the integral around the particles.}
-where $\xx \in \Gamma_i$ and $|\xx - \yy|$ is the distance between the
-pair of particles. The repulsion profile $P(r)$ is zero for distances
-$r$ larger than a repulsion length scale $\rho_0$. As
-such,~\eqref{eqn:REPULforce} and~\eqref{eqn:REPULtorque} ignore
-particles $\Gamma_j$ outside a tubular neighborhood of $\Gamma_i$. For
-$0 \leq r < \rho_0,$ we use $P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is
-sufficiently large to prevent particle collisions. The total imposed
-force and torque are
+where $\aa_i$ is the center of particle $i$. The repulsion profile
+$P(r)$ is zero for distances $r$ larger than a repulsion length scale
+$\rho_0$. As such,~\eqref{eqn:REPULforce} and~\eqref{eqn:REPULtorque}
+ignore particles $\Gamma_j$ outside a tubular neighborhood of
+$\Gamma_i$. For $0 \leq r < \rho_0,$ we use $P(r) = M(1 -
+\sin(r/\rho_0))$ where $M$ is sufficiently large to prevent particle
+collisions. The total imposed force and torque are
 \begin{align}

### 2021-08-06 doc/main_jfm.tex
worked on Secs 2 and 3

--- 2021-08-06 doc/main_jfm.tex
@@
 \begin{alignat}{3}
-  -\mu \Delta \uu + \nabla p &= \mathbf{0}, \qquad \qquad 
+  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
     && \xx \in \Omega, \\
@@
   T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
-    (\ssigma \cdot \nnu_i) \, ds = 0 \qquad && i=1,\ldots,N_b,
+    (\ssigma \cdot \nnu_i) \, ds = 0, \qquad && i=1,\ldots,N_b,
 \end{alignat}
 where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
-\right)$ is the hydrodynamic stress tensor (pressure tensor).
+\right)$ is the hydrodynamic stress tensor (pressure tensor). The
+process of finding the translational and angular velocities given a
+force and torque is referred to as the mobility problem.
 
 \subsection{Imposed Forces}
-The imposed forces and torques contain two parts. 
-The first part comes from the hydrophobic attraction potential (HAP).
-This potential was introduced in \cite{Fu20} and
-models hydrophobic attraction by solving the screened Laplace equation boundary value problem
+The imposed forces and torques contain two parts. The first part comes
+from the hydrophobic attraction potential (HAP). This potential was
+introduced in~\cite{Fu20} and models hydrophobic attraction by solving
+the screened Laplace equation boundary value problem
 \begin{alignat}{2}
@@
 \end{alignat}
-where $f_i$ is material label with $f_i = 0$ ($1$) representing
+where $f_i$ is a material label with $f_i = 0$ ($1$) representing
 hydrophilic (hydrophobic) portions of the surface, and $\rho$ is the
@@
 The second part of the imposed forces and torques comes from repulsion
-between proximal particles. We define 
+between proximal particles. Given a pair particles indexed with $i$ and
+$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
+$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another. We then
+define the repulsion force and torque
 \begin{align}
@@
   \label{eqn:REPULforce}
-  \FF_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
-    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, \\
+  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
+    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
+    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
+    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
   \label{eqn:REPULtorque}
-  T_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
-    (\xx - \aa_i)^{\perp} \cdot 
-    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, 
+  T_i^{\text{repul}} &= \sum_{j \neq i} 
+    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
+    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
+    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
+    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
 \end{align}
-\todo[inline]{Repulsion force is a function of only the distance between
-the Janus particles instead of the integral around the particles.}
-where $\xx \in \Gamma_i$ and $|\xx - \yy|$ is the distance between the
-pair of particles. The repulsion profile $P(r)$ is zero for distances
-$r$ larger than a repulsion length scale $\rho_0$. As
-such,~\eqref{eqn:REPULforce} and~\eqref{eqn:REPULtorque} ignore
-particles $\Gamma_j$ outside a tubular neighborhood of $\Gamma_i$. For
-$0 \leq r < \rho_0,$ we use $P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is
-sufficiently large to prevent particle collisions. The total imposed
-force and torque are
+The repulsion profile $P(r)$ is zero for distances $r$ larger than a
+repulsion length scale $\rho_0$. As such,~\eqref{eqn:REPULforce}
+and~\eqref{eqn:REPULtorque} ignore particles $\Gamma_j$ outside a
+tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
+$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
+prevent particle collisions. Then, the total imposed force and torque
+are
 \begin{align}
@@
 
-\subsection{Time Marching and Nondimensionalizations}
+\subsection{Time Marching}
 By solving the mobility problem, we obtain translational and angular
@@
 where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
-torque-free and has force $\FF$, and the Rotlet force-free and has
-torque $T$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
+torque-free and has force $\FF_i$ while the Rotlet force-free and has
+torque $T_i$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
 total force~\eqref{eqn:force} and torque~\eqref{eqn:torque} conditions
@@
 and imposing that $\DD[\eeta]$ is force- and torque-free, the density
-function $\eeta$, Stokeslet strength, $\FF_i$, and Rotlet strength $T_i$
-satisfy
+function $\eeta$, translational velocity $\vv_i$, and angular velocity
+$\omega_i$ satisfy
 \begin{alignat}{3}
   \nonumber
-  \vv_j + \omega_j (\xx - \aa_j)^\perp &= \uu_\infty(\xx)
+  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
     -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
   \label{eqn:SKIE}
-    &+ \sum_{i=1}^{N_b} 
-    \left(\SS(\xx,\aa_i) \FF_i + \RR(\xx,\aa_i) T_i\right),
-    \quad &&\xx \in \bd \Gamma_j, \\
+    + \sum_{j=1}^{N_b} &
+    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
+    \quad &&\xx \in \bd \Gamma_i,\: i=1,\ldots,N_b, \\
   \label{eqn:mobility1}
@@
 \end{alignat}
-%
-%The mobility problem for $N_b$-body system in a Stokes flow leads to a second-kind boundary integral equations (BIE) with a density function $\eta({\bf x}$ that is given by \cite{Lukas19}
-%\begin{equation}
-%\label{mobility}
-%\begin{aligned}
-%{\bf v}_i + &\omega_i\times({\bf x}-{\bf a}_i)\\
-% =& -\frac12\eta({\bf x}) + D[\eta]({\bf x}) \\
-%&+ \sum_{i=1}^N\big({\bf S}({\bf x}, {\bf a}_i){\bf F}_i+ {\bf R}({\bf x}, {\bf a}_i)t_i\big)+{\bf u}_\infty, \quad {\bf x}\in\Gamma \\
-%\end{aligned}
-%\end{equation}
-%%
-%with two constraints 
-%%
-%\begin{center}
-%\begin{equation}
-%\label{mobility2}
-%\int_{\partial \Gamma_i}\eta\cdot \nnu ds = {\bf 0},
-%\end{equation}
-%\end{center}
-%%
-%\begin{center}
-%\begin{equation}
-%\label{mobility3}
-%\int_{\partial \Gamma_i}\eta\times({\bf x}-{\bf a}_i)\cdot \nnu ds ={\bf 0},
-%\end{equation}
-%\end{center}
-%%
-%where the two-dimensional Stokeslet and the Rotlet are
-%%
-%\begin{gather}
-%{\bf S}({\bf x}, {\bf a}) = \frac{1}{4\pi}\left(-\log(|({\bf x}-{\bf a})|){\bf I}+\frac{({\bf x}-{\bf a})\otimes({\bf x}-{\bf a})}{|({\bf x}-{\bf a})|^2}\right) \\ 
-%{\bf R}({\bf x},{\bf a})=\frac{({\bf x}-{\bf a})^\perp}{4\pi|({\bf x}-{\bf a})|^2}.
-%\end{gather}
-%
-%Here ${\bf r}={\bf x}-{\bf a}$ and $\rho=|{\bf r}|$.
-Given a collection of particles with forces and torques calculated from
-the hydrophobic interactions and the short range repulsion,
-equations~\eqref{eqn:SKIE}--\eqref{eqn:mobility2} form a solvable set of
-integral equations for the translational velocities $\vv_i$, the angular
-velocities $\omega_i$, and the density function $\eeta$.
 
-\todo[inline]{Talk about how to solve numerically. Quadrature, time
-stepping, collocation, etc.}
-This system of equations is then solved iteratively with block-diagonal
-preconditioned GMRES.
+%Given a collection of particles with forces and torques calculated from
+%the hydrophobic interactions and the short range repulsion,
+%equations~\eqref{eqn:SKIE}--\eqref{eqn:mobility2} form a solvable set of
+%integral equations for the translational velocities $\vv_i$, the angular
+%velocities $\omega_i$, and the density function $\eeta$.
+
+We discretize each of the $\Gamma_i$, $i=1,\ldots,N_b$, at $N$
+discretization points. The trapezoid rule is used to approximate each of
+the integrals in equations~\eqref{eqn:mobility1}
+and~\eqref{eqn:mobility2}, and the double-layer potential
+equation~\eqref{eqn:SKIE}. When two bodies are close, the double-layer
+potential becomes nearly-singular, and we replace the double-layer
+potential with an interpolation-based nearly-singular quadrature
+rule~\cite{qua-bir2014}. After discretizing and applying appropriate
+quadrature rules, the result is a $(2NN_b + 3N_b) \times (2NN_b + 3N_b)$
+linear system whose condition number is independent of $N$, and this
+linear system is solved using matrix-free GMRES. To reduce the number of
+GMRES iterations, a block-diagonal preconditioner is used.
 

### 2021-08-06 doc/main_jfm.tex
finished up first run at secs 2 and 3

@@
 \newcommand{\yy}{\mathbf{y}}
+\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
 
@@
 \label{sec:IEM}
-Since the fluid velocity is assumed to be Stokesian, it can be written
-in terms of layer potentials. Following previous work of~\cite{Lukas19},
-we represent the velocity as the sum of a double-layer potential and the
-$N_b$ Stokeslets and Rotlets
+Computing the hydrophobic attraction potential and the particle forces
+and torques requires solving an elliptic partial differential equation
+(PDE) in an unbounded complex domain. We recast both these PDEs as
+boundary integral equations (BIEs). We discretize each BIE at $N$ points
+on each of the $N_b$ particles with a collocation method. Integrals that
+are smooth are computed with the spectrally-accurate quadrature rule,
+and nearly-singular integrals, caused by close contact between two
+particles, are computed with a high-order interpolation-based quadrature
+rule~\cite{qua-bir2014}. After discretizing and applying quadrature, the
+resulting linear system is solved with matrix-free GMRES, and we
+guarantee that the number of GMRES iterations is mesh-independent by
+using second-kind BIEs.
+
+\subsection{HAP Boundary Integral Equation}
+Similar to our previous work~\cite{Fu20}, we represent the HAP as a
+double-layer potential
+\begin{align}
+  \label{eqn:HAP_DLP}
+  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, ds_\yy,
+    \quad \xx \in \Omega,
+\end{align}
+where $K_0$ is the zeroth-order modified Bessel function of the first
+kind. By requiring that the density function $\sigma$ satisfies the
+second-kind integral equation
+\begin{align}
+  f(\xx) = \frac{1}{2}\sigma(\xx) + 
+    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, ds_\yy,
+    \quad \xx \in \bd\Omega,
+\end{align}
+the HAP double-layer potential~\eqref{eqn:HAP_DLP} satisfies the
+screened Laplace equation~\eqref{SL}--\eqref{SLff}. To calculate the
+hydrophobic force and torque, the gradient of the double-layer
+potential~\eqref{eqn:HAP_DLP} must be computed on the boundary of each
+particle. In Appendix~\ref{sec:appendixA}, we show that the force and
+torque calculations can be expressed in terms of integral that are
+non-singular.
+
+\subsection{Mobility Problem Boundary Integral Equation}
+Following previous work of~\cite{Lukas19}, we represent the velocity as
+the sum of a double-layer potential and the $N_b$ Stokeslets and Rotlets
 \begin{align}
@@
 
-%Given a collection of particles with forces and torques calculated from
-%the hydrophobic interactions and the short range repulsion,
-%equations~\eqref{eqn:SKIE}--\eqref{eqn:mobility2} form a solvable set of
-%integral equations for the translational velocities $\vv_i$, the angular
-%velocities $\omega_i$, and the density function $\eeta$.
-
-We discretize each of the $\Gamma_i$, $i=1,\ldots,N_b$, at $N$
-discretization points. The trapezoid rule is used to approximate each of
-the integrals in equations~\eqref{eqn:mobility1}
-and~\eqref{eqn:mobility2}, and the double-layer potential
-equation~\eqref{eqn:SKIE}. When two bodies are close, the double-layer
-potential becomes nearly-singular, and we replace the double-layer
-potential with an interpolation-based nearly-singular quadrature
-rule~\cite{qua-bir2014}. After discretizing and applying appropriate
+The trapezoid rule is used to approximate each of the integrals in
+equations~\eqref{eqn:mobility1} and~\eqref{eqn:mobility2}, and the
+double-layer potential equation~\eqref{eqn:SKIE} is approximated with
+either the trapezoid rule, or the interpolation-based near-singular
+integration quadrature rule. After discretizing and applying appropriate
 quadrature rules, the result is a $(2NN_b + 3N_b) \times (2NN_b + 3N_b)$
-linear system whose condition number is independent of $N$, and this
-linear system is solved using matrix-free GMRES. To reduce the number of
-GMRES iterations, a block-diagonal preconditioner is used.
+linear system that we precondition with a block-diagonal preconditioner.
+We note that other BIE formulations of the mobility problem use
+single-layer potentials~\cite{cor-gre-rac-vee2017, rac-gre2016} or both
+single- and double-layer potentials~\cite{cor-vee2018}.
 
@@
 \section{Appendices}
-The stress ${\bf T}$ contains the gradient of the double layer potential. This 
-introduces an inherent difficulty in evaluating stress on the boundary.
-To overcome the difficulty of evaluation on $\Sigma_p$, for instance, we decompose $u$ into singular and nonsingular parts:
+\label{sec:appendixA}
+The stress ${\bf T}$ contains the gradient of the double layer
+potential. This introduces an inherent difficulty in evaluating stress
+on the boundary.  To overcome the difficulty of evaluation on
+$\Sigma_p$, for instance, we decompose $u$ into singular and nonsingular
+parts:
 \begin{equation}

### 2021-08-10 doc/main_jfm.tex
updates

@@
 The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
-interfacial tension $\gamma=4.1$ pN nm from ~\cite{Ryham16}. We then be able to calculate the corresponding 
+interfacial tension $\gamma=4.1$ pN nm$^{-1}$ from ~\cite{Ryham16}. We then be able to calculate the corresponding 
 time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
-$\kappa=8.51$ kT $\approx35$ pN nm.
+$\kappa=8.51$ kT.
 
@@
 \begin{center}
-\hspace{-1cm}
+\hspace{-0.6cm}
 \includegraphics[height=2in]{ReducedArea.pdf}
-\hspace{-1cm}
+\hspace{0.6cm}
+\includegraphics[height=2in]{DecayRate.eps}\\
 \includegraphics[height=2in]{ArcLength.pdf}
-\hspace{-1cm}
 \includegraphics[height=2in]{ExcLength.pdf}
 \end{center} 
-  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) Reduced area transitions over time. (c) Excess length of the midplanes.
+  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) From exponential fits in panel (a), we obtain the decay rate for a number of different shear rates;
+  (c) Reduced area transitions over time. (d) Excess length of the midplanes.
 A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{parabolic.eps}
+\includegraphics[height=2in]{parabolic.eps}
   \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=10000$.
@@
 \centering
-\includegraphics[height=2.4in]{N58_rupt_0.pdf}
-\includegraphics[height=2.4in]{N58_rupt_200.pdf}
+\includegraphics[height=2in]{N58_rupt_0.pdf}
+\includegraphics[height=2in]{N58_rupt_200.pdf}
 \\
-\includegraphics[height=2.4in]{N58_rupt_400.pdf}
-\includegraphics[height=2.4in]{N58_rupt_600.pdf}
+\includegraphics[height=2in]{N58_rupt_400.pdf}
+\includegraphics[height=2in]{N58_rupt_600.pdf}
   \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
@@
 \centering
-\includegraphics[height=1.2in]{N116_shear_0.pdf}
-\includegraphics[height=1.2in]{N116_shear_2500.pdf}
-\includegraphics[height=1.2in]{N116_shear_5000.pdf}
-\includegraphics[height=1.2in]{N116_shear_7500.pdf}\\
+\includegraphics[height=2in]{N116_shear_0.pdf}
+\includegraphics[height=2in]{N116_shear_2500.pdf}\\
+\includegraphics[height=2in]{N116_shear_5000.pdf}
+\includegraphics[height=2in]{N116_shear_7500.pdf}
   \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
@@
 \centering
-\includegraphics[height=2.in]{N116_ext_0.pdf}
-\includegraphics[height=2.in]{N116_ext_2000.pdf}\\
-\includegraphics[height=2.in]{N116_ext_4000.pdf}
-\includegraphics[height=2.in]{N116_ext_6500.pdf}
+\includegraphics[height=2in]{N116_ext_0.pdf}
+\includegraphics[height=2in]{N116_ext_2000.pdf}\\
+\includegraphics[height=2in]{N116_ext_4000.pdf}
+\includegraphics[height=2in]{N116_ext_6500.pdf}
   \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
@@
 
-\section{\label{A2} Comparison between Continuum Model and the Proposed Model}
-
-\begin{figure}
-\centering
-\includegraphics[height=1.2in]{N116_cont_a.pdf}
-\includegraphics[height=1.2in]{N116_cont_b.pdf}
-\includegraphics[height=1.2in]{N116_cont_c.pdf}
-\includegraphics[height=1.2in]{N116_cont_d.pdf}
-  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
-  }
-    \label{figureB}
-\end{figure}
+%\section{\label{A2} Comparison between Continuum Model and the Proposed Model}
+%
+%\begin{figure}
+%\centering
+%\includegraphics[height=1.2in]{N116_cont_a.pdf}
+%\includegraphics[height=1.2in]{N116_cont_b.pdf}
+%\includegraphics[height=1.2in]{N116_cont_c.pdf}
+%\includegraphics[height=1.2in]{N116_cont_d.pdf}
+%  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
+%  }
+%    \label{figureB}
+%\end{figure}
 

### 2021-08-11 doc/main_jfm.tex
updates
few small changes

@@
 By solving the mobility problem, we obtain translational and angular
-velocities of the $N_b$-body system. A second-order Adam-Bashforth
+velocities of the $N_b$-body system. A second-order Adams-Bashforth
 scheme updates the particle positions and orientations. By including the
@@
 This vesicle-like structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
-the vesicle is about $8.5$ length units.
+the vesicle is about $8$ length units.
 The starting center of mass position of the Janus-vesicle is pinned at the origin and particle velocities are tracked to determine the initial configuration for later use such as single and multiple vesicle simulations.
@@
 The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
-interfacial tension $\gamma=4.1$ pN nm$^{-1}$ from ~\cite{Ryham16}. We then be able to calculate the corresponding 
-time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
-$\kappa=8.51$ kT.
+interfacial tension $\gamma=4.11$ pN nm$^{-1}$ from ~\cite{Ryham16}.
+We then be able to calculate the characteristic time scale $\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP.
+With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_B$T.
+%
+For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$
+is the shear rate.
 
-For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate $\chi$ is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
-\begin{align}
-  \chi = \dot\gamma \frac{\mu R_0^2}{\kappa},
-\end{align}
-%
-where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.
+%referred from~\cite{Finken08} and~\cite{Shaqfeh11},
+%\begin{align}
+%  \chi = \dot\gamma \frac{\mu R_0^3}{\kappa},
+%\end{align}
+%%
+%where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.
 
@@
 \begin{equation}
-b = \frac{{\bf F}_{friction}}{v^\parallel} = \frac{{\bf F}_{friction}}{\int_{\Sigma_M} R \dot\theta dS}.
+b = \frac{F_f}{v^\parallel} = \frac{F_f}{\int_{\Sigma_M} R \dot\theta dS}.
 \end{equation}
@@
 \centering    
-\begin{tabular}{c c c c}
-\hline\hline                    
-Case $i$ & $\chi_i$ & $b_i$\\
+\begin{tabular}{c c c c c c c c }
 \hline                    
-1 & 0.020 &  5.1648  \\
-2 & 0.025 &  5.2027  \\ 
-3 & 0.050 &  5.1944   \\ [1ex]
+$\dot\gamma$ (ns$^{-1}$) & 0.0020 & 0.0025 & 0.0030 & 0.0035 & 0.0040 & 0.0045 & 0.0050\\
+\hline 
+$F_{f}$ (pN nm$^{-1}$)           &  &  &  &  &  &  &   \\[1ex]
+$\dot\theta$ (ns$^{-1}$)           &  &  &  &  &  &  & \\ [1ex]
+$b$ (pN$\cdot$ns nm$^{-2}$)   &  &  &  &  &  &  & \\ 
 \hline    
@@
     \nabla \cdot {\bf T}_j = 0, \quad
-    \nabla \cdot (x \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
+    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
   \end{equation}
@@
   \end{align*}
-  However, $-\rho^2 \Delta u + u = 0$ and so we get $\nabla \cdot {\bf T} = 0.$
+  Since $-\rho^2 \Delta u + u = 0$, we have $\nabla \cdot {\bf T} = 0$.
   Furthermore,

### 2021-08-11 doc/main_jfm.tex
updates

@@
 We then be able to calculate the characteristic time scale $\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP.
-With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_B$T.
+With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
 %
-For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$
+The dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ 
 is the shear rate.
+
+%For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$
 
@@
 \hline                    
-$\dot\gamma$ (ns$^{-1}$) & 0.0020 & 0.0025 & 0.0030 & 0.0035 & 0.0040 & 0.0045 & 0.0050\\
+$\dot\gamma$ (ns$^{-1}$) & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
 \hline 
@@
   }
-    \label{figure8}
+    \label{figure9}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
+\end{center} 
+  \caption{Trajectories of different setups in two-vesicle in an extensional flow where the centroids of two Janus-vesicle are plotted as blue dots.
+(i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii)
+  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure9} presents the numerical results from the case (iii) and a
+  consistent flow rate is $\chi = 0.005$ for all cases.}
+    \label{figure10}
 \end{figure}

### 2021-08-12 doc/main_jfm.tex
updates

@@
 In order to examine the dynamics of the Janus-vesicle using the HAP coupling with hydrodynamics interactions, for the target bilayer, a circular initial shape is chosen to perform the relaxation run. 
-This vesicle-like structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
+This structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
 the vesicle is about $8$ length units.
 The starting center of mass position of the Janus-vesicle is pinned at the origin and particle velocities are tracked to determine the initial configuration for later use such as single and multiple vesicle simulations.
-This will prevent some numerical instability issues when the minimum of the total energy is not achieved. 
-For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
-Figure~\ref{figure2}(a) shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$.
-In the same figure, the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property of the model.
-This implies that a local energy minimum and the equilibrium configuration are
-nearly attained. 
+The advantage of acquiring this configuration is to prevent some numerical instability issues when the minimum of the total energy is not achieved. 
+For instance, the dynamics of the bilayer under a shear flow may reach different outcomes or equilibrium states.
+Figure~\ref{figure2}(a) shows two sets of results: (1) the magnitudes of mean velocity components 
+${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$; (2) the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property of the model.
+This implies that a local energy minimum and the equilibrium configuration are nearly attained.
 The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
 Figure~\ref{figure2}(b) shows the configuration difference between starting and ending frames in the relaxation run.
-The Figure~\ref{figure2}(c)-(d) demonstrate the fluid pressure profile of two configurations.
-The pressure inside the permeable Janus-vesicle decreases as expected.
+The Figure~\ref{figure2}(c)-(d) demonstrate the fluid pressure profile of two configurations at $t=0$ and $t=1000$.
+The starting fluid pressure inside the permeable Janus-vesicle decreases as expected.
 
@@
 
-Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of vesicles 
-under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
-The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
-interfacial tension $\gamma=4.11$ pN nm$^{-1}$ from ~\cite{Ryham16}.
-We then be able to calculate the characteristic time scale $\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP.
-With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
+Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of 
+Janus-vesicles under flows. To extract physical quantities of the target structure using the proposed model, 
+the scaling laws and the dimensionless units are given as follows.
+The length unit is scaled by the length of phospholipids $l=2.5$ nm which is set as the diameter of each 
+Janus particle. The force is scaled from the interfacial tension $\gamma=4.11$ pN nm$^{-1}$ 
+from ~\cite{Ryham16}. We then be able to calculate the characteristic time scale 
+$\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP. With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
 %
-The dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ 
-is the shear rate.
+For the model parameters, the decay length of attraction $\rho = 2l = 5$ nm, the repulsion length scale is 
+$\rho_0=0.5$, and teh repulsion strength $M=4.0$.
+The dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ is the shear rate.
 
@@
 
-To study the deformation of a closed bilayer structure under a shear flow using the proposed algorithm, 
+To study the deformation of a Janus-vesicle under a shear flow using the proposed algorithm, 
 we adopt a widely tested numerical simulation in both continuum and molecular dynamics models, single vesicle under a shear flow.
-The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
-Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
-the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.
+The well known results indicate that the vesicle has tank-treading behavior when
+there is no viscosity contrast in both inside and outside of the vesicle that is one of the features in the  framework of the proposed model.
 
-The snapshots of the simulation for single vesicle in a shear flow are shown in Figure~\ref{figure3}.
-Panel (a) shows the initial circular shape obtained from the relaxation run and the deformed 
-configuration of the vesicle after a period of time ($t=4000$) is in panel (c). The color presented in the figure 
-is the strength of the action due to the hydrophobic attraction. From weak to strong action field, the color
-varies from blue to red.
-To demonstrate the tank-treading behavior of the vesicle, panels (b) and (d) provide the streamlines of the 
-fluid velocity over the whole computational domain when the shear flow passes through the structure.
-The tank-treading motion of the structure is then observed, for instance, the particle velocities in panel (d) indicate a clockwise tank-treading movement.
+The centroid of the pre-relaxed $58$-body Janus vesicle is initially placed at the origin then the shear flow 
+with a certain shear rate $\chi$ is turned on. 
+The snapshots of the simulation for single vesicle in a shear flow with a shear rate $\chi=0.0025$ are shown 
+in Figure~\ref{figure3}.
+Panels (a)-(b) show the initial shape obtained from the relaxation run and the deformed 
+configuration of the Janus-vesicle after a period of time ($t=4000$) is in panels (c)-(d). 
+The background color in panels (a) and (c) presented in the figure is the strength of the action due to the
+hydrophobic attraction. From weak to strong action field, the color varies from blue to red. Clearly, the
+hydrophobic layer has largest action. To demonstrate the tank-treading behavior of the vesicle, panels (b) 
+and (d) provide the streamlines of the fluid velocity over the whole computational domain when the shear 
+flow passes through the structure. The tank-treading motion of the structure is then observed, for instance,
+the particle velocities in panel (d) indicate a clockwise tank-treading movement.
 
@@
 \includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
-  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.0025$: 
-  (a) Initial configuration of 58-body vesicle; 
+  \caption{Vesicle under a shear flow where the shear rate $\chi=0.0025$: 
+  (a) Initial configuration of 58-body Janus-vesicle where black arrows are the particle orientations; 
   (b) The fluid velocity plot with respect to the configuration in (a); Streamlines are plotted in the background
@@
   The background colors in panels (a) and (c) represent the strength of the hydrophobic attraction potential.
-The blue region shows no action and the red region with the bilayer gives the strongest action.
+The blue region shows no action and the red region in the bilayer gives the strongest action.
   }
@@
 %
+%
 
 In order to extract more physical properties of the proposed model, we track the total length of the bilayer structure, the reduced area over the time, and the excess length.
-Here the enclosed area and the length of the structure are calculated from the midplane.
-These results are shown in Figure~\ref{figure4} where we compare results from a set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$. 
-The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ is the vesicle area and $L$ is the arc length of the vesicle with respect to the midplane. 
+Here the enclosed area and the total length of the structure are calculated from the midplane.
+These results are shown in Figure~\ref{figure4} where we compare results from the use of a set of shear 
+rates $\chi=\{0.002,0.0025,0.003,0.0035\}$. 
+The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ the area, and $L$ the total length of the Janus-vesicle with respect to the midplane. 
 Furthermore, the excess length is given by $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
 Since the starting configuration is close to a circular shape, the reduced area decreases from a value very close to $1$.
-It is clear that a slower shear rate generates a higher reduced area and has a faster convergence.
-With a converging total arc length, a slower shear rate also produces a smaller excess length.
-The small oscillations in all results are due to the granularity of the bilayer which tend to having a slightly non-smooth curve in simulations.
+For the test cases in Figure~\ref{figure4}, the smooth curves in panel (a) are fitted using an
+exponential model given by $A^* = a_0 + b_0 \exp(-kt)$.
+Panel (b) shows that the decay rate $k$ is independent of the shear rate when the shear is above a threshold and the terminal reduced area for each
+case of the shear rate can then be calculated. It is also clear that a slower shear rate generates a higher reduced area and has a faster convergence then the high shear rate cases. 
+With a converging total arc length as shown in panel (c), a slower shear rate also produces a smaller excess length shown in panel (d).
+In summary, the small oscillations in all results are due to the granularity of the Janus-vesicle which tend to having a slightly non-smooth curve in simulations.
 Overall the total lengths of the bilayer have the same converging value in all test shear rates.
-Moreover, based on the
-numerical experiments, we observe that the reduce area converges relatively early when the shear rate is lower than $\dot\gamma=0.003$.
-
-An interesting phenomenon also rises up in the proposed setup where the inter-monolayer slip occurs 
-between two leaflets. When a shear rate is large enough, take $\dot\gamma = 0.005$ as an example, 
-Figure~\ref{figure5} shows the schematic of the test.
-A particle pair is initially marked and we then track the positions and mean angle $\theta(t)$ between particle relative position with respect to the vesicle center over the time.
-It is clear to see that the outer leaflet always has larger
-tangential velocity than the one from inner leaflet and the mean angle $\theta(t)$ increases. 
-This inter-leaflet sliding phenomenon is consistent with what has been seen
-in articles in molecular dynamics simulations. %%% need some citations
+Moreover, based on the numerical experiments, we observe that the reduce area converges relatively early when the shear rate is lower than $\chi=0.003$.
 
@@
   (c) Reduced area transitions over time. (d) Excess length of the midplanes.
-A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
+A set of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
 A slower shear rate generates a faster convergence in the reduced area and smaller excess length. 
@@
 
-\todo[inline]{Figure/Table of the friction coefficient for different shear rates (needs to revise)}
+An interesting phenomenon also rises up in the proposed setup where the inter-monolayer slip occurs 
+between two leaflets. When a shear rate is large enough, take $\chi = 0.005$ as an example, 
+Figure~\ref{figure5} shows the schematic of the test.
+A particle pair is initially marked and we then track the positions and mean angle $\theta(t)$ between particle relative position with respect to the vesicle center over the time.
+It is clear to see that the outer leaflet always has larger
+tangential velocity than the one from the inner leaflet and the mean angle $\theta(t)$ increases. 
+This inter-leaflet sliding phenomenon is consistent with what has been seen
+in articles in molecular dynamics simulations.
 
-The intermonolayer friction coefficient of the Janus-vesicle is calculated from the ratio of friction force and the 
-slip velocity. This quantity is given by 
-\begin{equation}
-b = \frac{F_f}{v^\parallel} = \frac{F_f}{\int_{\Sigma_M} R \dot\theta dS}.
-\end{equation}
 %
-where $v^\parallel$ represents the tangential velocity at the midplane and $\Sigma_M$ the curve determined by the midplane.
+%\todo[inline]{Figure/Table of the friction coefficient for different shear rates (needs to revise)}
 
@@
   \caption{The schematic of the intermonolayer slip over a period of time.
-Taking shear rate $\dot\gamma=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position.
+Taking shear rate $\chi=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position.
 The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=\{2000,5200,9000\}$.
@@
 
+The inter-monolayer friction coefficient of the Janus-vesicle is calculated from the ratio of the friction force and the slip velocity. This quantity is given by 
+\begin{equation}
+b = \frac{F_f}{\int_{\Sigma_M} R \dot\theta dS},
+\end{equation}
+%
+where $\Sigma_M$ is the curve determined by the midplane and the relative radius $R$ is defined by the distance between the particle pair and the centroid of the Janus-vesicle.
+Hence, the mean rotational velocity
+of the bilayer is given by the integral of $R\dot\theta$ over the midplane curve $\Sigma_M$.
+For the friction force $F_f$, we calculate tangential stresses near the bilayer from outer and inner fluid then 
+extrapolate the force value onto the midplane to acquire the pressure jump. The friction force is computed after integrating the pressure jump over the midplane $\Sigma_M$.
+Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$. As expected,
+within the same order, the friction coefficients are independent of the shear rates.
+
 \begin{table}
@@
 \begin{tabular}{c c c c c c c c }
+ $\chi$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
 \hline                    
 $\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
-\hline 
-$F_{f}$ (pN nm$^{-1}$)           &  &  &  &  &  &  &   \\[1ex]
-$\dot\theta$ (ns$^{-1}$)           &  &  &  &  &  &  & \\ [1ex]
-$b$ (pN$\cdot$ns nm$^{-2}$)   &  &  &  &  &  &  & \\ 
+$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
+$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
+$b$ (pN$\cdot$ns nm$^{-2}$)   & 1.11 & 1.56 & 1.37 & 1.47 & 1.43 & 1.51 & 1.76\\ 
 \hline    
@@
 
-The background flow for this set of simulations is given by
-
+Besides the tests of a Janus-vesicle in a shear flow, an interesting test can also use the proposed model and the setup.
+Consider a symmetric parabolic flow about the $x$-axis, \cite{Kaoui09} studied shapes of the red blood cell immersed in a parabolic flow using a continuum model.
+With a similar setup, the background flow for this set of simulations is given by
 \begin{equation}
@@
 where $v_{max}$ is the flow strength and $w$ controls the shape of the flow.
-$R_0$ is defined as the radius of the initial vesicle midplane.
-Figure~\ref{figure6} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
+$R_0$ is defined as the radius of the Janus-vesicle at $t=0$.
+Figure~\ref{figure6} gives a configuration for one specific case where the centroid of the Janus-vesicle is initially placed slightly above the $x$-axis at $(0,3)$.
+The parameters are $v_{max} = 8.0$, $w=10$ and $R_0=8$.
+The inset of Figure~{figure6} shows the trajectory of the mean position in $y$-direction which decreases toward $y=1$ for a period of time and starts to have an oscillatory motion.
+Moreover, the Janus-vesicle performs tank-treading during the simulation and red arrows in Figure~{figure6} indicate a counterclockwise movement.
+For this test run, an asymmetric slipper occurs and the reduced area for this configuration is $\sim0.9$.
+This matches the previous numerical tests in  \cite{Kaoui09} where a slipper-like shape occurs when the flow velocity is weak.
 
@@
 With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
-Figure~\ref{figure7} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
+Figure~\ref{figure7} shows a demonstration of a vesicle under a shear flow with shear rate $\chi=0.1$.
 An interesting phenomenon occurs in panels (c) and (d) where two separated bilayers move along the background shear flow symmetrically.
@@
   \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
-Here the shear rate is $\dot\gamma = 0.1$.
+Here the shear rate is $\chi = 0.1$.
 Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)).
@@
 \includegraphics[height=2in]{N116_shear_7500.pdf}
-  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
+  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a).
 The background color indicates the magnitude of fluid pressure.
@@
 Two vesicles in a shear flow is presented in Figures~\ref{figure9} where centers of mass are placed on the same horizontal level.
-With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \dot\gamma y$.
+With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \chi y$.
 An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.
@@
 \includegraphics[height=2in]{N116_ext_6500.pdf}
-  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
+  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a).
 The background color indicates the magnitude of fluid pressure.
@@
   }
-    \label{figure9}
+    \label{figure8}
 \end{figure}
@@
 Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
-The extensional flow is stretching along the $y$ direction and squeezing in $x$ direction with shear rate $\dot\gamma=0.005$.
+The extensional flow is stretching along the $y$ direction and squeezing in $x$ direction with shear rate $\chi=0.005$.
 Since two bilayers are close enough
@@
 
-%\section{\label{A2} Comparison between Continuum Model and the Proposed Model}
-%
-%\begin{figure}
-%\centering
-%\includegraphics[height=1.2in]{N116_cont_a.pdf}
-%\includegraphics[height=1.2in]{N116_cont_b.pdf}
-%\includegraphics[height=1.2in]{N116_cont_c.pdf}
-%\includegraphics[height=1.2in]{N116_cont_d.pdf}
-%  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
-%  }
-%    \label{figureB}
-%\end{figure}
-
 \bibliographystyle{jfm}

### 2021-08-12 doc/main_jfm.tex
updates

@@
 The parameters are $v_{max} = 8.0$, $w=10$ and $R_0=8$.
-The inset of Figure~{figure6} shows the trajectory of the mean position in $y$-direction which decreases toward $y=1$ for a period of time and starts to have an oscillatory motion.
-Moreover, the Janus-vesicle performs tank-treading during the simulation and red arrows in Figure~{figure6} indicate a counterclockwise movement.
+The inset of Figure~\ref{figure6} shows the trajectory of the mean position in $y$-direction which decreases toward $y=1$ for a period of time and starts to have an oscillatory motion.
+Moreover, the Janus-vesicle performs tank-treading during the simulation and red arrows in Figure~\ref{figure6} indicate a counterclockwise movement.
 For this test run, an asymmetric slipper occurs and the reduced area for this configuration is $\sim0.9$.
@@
 \includegraphics[height=2in]{parabolic.eps}
-  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=10000$.
+  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$.
+The configuration is the state when $t=10000$.
+Red arrows are directors of particle velocities.
+The inset shows the mean $y$-position over time.
   }
@@
   }
+    \label{figure8}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{ShearTraj.eps}
+\end{center} 
+  \caption{Trajectories of two-vesicle in a shear flow where the centroids of two Janus-vesicle are plotted as blue dots.
+Both starting centroids of two Janus-vesicles are on the $x$-axis.
+For simulation time, $t = {0, 400,800,1200}$ for (a)-(d) and $t = {1600, 2400, 3200, 4000}$ for (e)-(h).
+}
     \label{figure9}
@@
 \subsubsection{Shear Flow}
-Two vesicles in a shear flow is presented in Figures~\ref{figure9} where centers of mass are placed on the same horizontal level.
+
+Figure~\ref{figure8} demonstrates the simulation results of two Janus-vesicles in a shear flow where the testing shear rate is $\chi=0.005$ and the flow is given by $\dot x = \chi y$.
+In panel (a), the starting frame, two center-of-mass positions are placed
+on the same horizontal level, at $(-10,0)$ and $(10,0)$.
+Since we already have a pre-relaxed $58$-body in previous sections, we duplicate the state to have the initial configuration in this section.
+As expected, there
+is no pressure jump between the internal and external fluids from the beginning of the simulation and this is shown in the background pressure plot.
+Panels (b)-(d) show the configurations when $t = \{400,800,100\}$
+and we observe that the rotation continues as time goes. The streamlines are plotted in the background 
+for all panels and we include the numerical results using continuum model in all insets. Obviously there is a qualitative agreement between two models.
+
+An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be seen and tuned.
+In other words, the adhesive behavior will be absent when two vesicles are centered
+at a different level and are well separated in $y$-direction. Trajectories of a longer run of the simulation results are shown in Figure~\ref{figure9}.
+
+%Two vesicles in a shear flow is presented in Figures~\ref{figure8} where centers of mass are placed on the same horizontal level, at $(-10,0)$ and $(10,0)$.
 With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \chi y$.
-An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.
-In other words, the adhesive behavior will be absent when two vesicles are centered
-at a different level and are well separated in $y$-direction.
 
@@
   }
-    \label{figure8}
+    \label{figure10}
 \end{figure}
@@
   consistent flow rate is $\chi = 0.005$ for all cases.}
-    \label{figure10}
+    \label{figure11}
 \end{figure}
@@
 
-Figures~\ref{figure8} show the numerical results of simulations when two vesicles are in an extensional flow.
-Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
-The extensional flow is stretching along the $y$ direction and squeezing in $x$ direction with shear rate $\chi=0.005$.
-Since two bilayers are close enough
-from the beginning of the run, two vesicles are first pushed toward each other then separate along the streamline. The short range repulsion plays an important role to avoid structure collisions and 
-this result can be compared with some findings in continuum modeling simulations.
+With a similar setup in the case of two Janus-vesicles in a shear flow, we use the same two pre-relaxed $58$-body Janus-vesicles to perform the simulations when the flow type is an extensional flow with flow rate $\chi=0.005$.
+This extensional flow is stretching along the $y$ direction and squeezing in $x$ direction.
+Figure~\ref{figure10} shows one set of numerical results when the centroids of two bodies are placed at
+$(-10,-0.1)$ and $(10,0.1)$. With this setup, we can make sure that two Janus-vesicles will separate along 
+$y$-direction eventually from empirical tests.
+Panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
+Since two bilayers are close enough from the beginning of the run, two vesicles are first pushed toward each other then separate along the streamlines.
+The short range repulsion plays an important role to avoid structure collisions and this result can be compared with some findings in continuum modeling simulations.
 The pressure plots in Figure~\ref{figure8} provide a realistic result where the pressure is much higher in the gap between two nearby vesicles.
+
+Figure~\ref{figure11} provides simulation results when the center-of-mass positions are placed differently.
+One can notice that when two centroids are placed on the same horizontal level, two Janus-vesicles reach
+an equilibrium state without separation as shown in case (i).
+If only one centroid is placed above the $x$-axis, for instance, case (ii), two Janus-vesicle move together toward the upward.
+This is the consequence when the adhesive effect beats the flow strength.
+Case (iii) is same as the case shown in Figure~\ref{figure10}.
+Finally, case (iv) has a larger initial separation in $y$-direction and two Janus-vesicle moves much faster toward
+$\pm y$-directions.
 

### 2021-08-13 doc/main_jfm.tex
updates
yny

--- 2021-08-11 doc/main_jfm.tex
@@
 \section{\label{intro}Introduction}
+Described by de Gennes as ``another animal in soft matter physics", the Janus particle (often a spherical particle with a hydrophobic and a hydrophilic hemisphere) exhibits complex aggregate, clustering and self-assembly into meso- and macroscopic structures that are relevant to a wide range of applications in biology and bioengineering.
+Whether it is surface chemistry or polarity under an external field, the dynamics of Janus particles is inevitably the combination of long-range hydrodynamics interactions in the presence of short- and intermediate-range particle-particle interactions.
 
-\section{Governing  Equations}
+Recently Fu {\it et al.} illustrated that the hydrophobic interactions between Janus particles in a viscous solvent can be used as a coarse-grained model to capture the mechanics of an elastic bilayer membrane of amphiphilic macromolecules such as lipids \cite{Fu2020_SIAM}.
+Depending on the total number of Janus particles and their geometry, in a viscous solvent, Janus particles are found to aggregate to form a micelle, a patch of bilayer membrane with open ends, and a self-enclosed bilayer membrane (a vesicle).
+Using a hybrid continuum model for the interactions between amphiphilic particles in a viscous solvent and formulating it in a boundary integral formulation, Fu {\it et al.} showed that the membrane granularity during fusion and fission of bilayers can be accurately captured.
+%This boundary integral formulation has inspired more recent work
+
+In molecular dynamics (MD) simulations, the lipid bilayer membranes are often approximated by an implicit solvent coarse-grained model for lipids (as in the Martini code), where their hydrodynamic interactions are simplified by an implicit solvent.
+The long-range hydrodynamic interactions and the induced long-range lipid interactions can be captured by combining the Dry Martini with a lattice Boltzmann MD \cite{Brandner2019_SciRep}.
+Brandner {\it et al.} used this methodology to simulate the hydrodynamics of a nano-sized vesicle under a shear flow, and reproduced the well-know vesicle hydrodynamics  such as tank-treading, tumbling and inter-leaflet slippage (reported from simulations of the Helfrich-type continuum model).
+
+In this work we extend the hybrid continuum model in \cite{Fu2020_SIAM} for the Janus suspension to incorporate the collective hydrodynamics of a Janus suspension under various flows: a linear shear flow, an elongation flow, and a Poiseuille flow.
+We demonstrate that a vesicle made of Janus particles does behave like a vesicle in these flowing conditions.
+Furthermore we also show that the hybrid continuum model allows us to investigate the inter-leaflet slippage and rupture of a bilayer membrane due to an imposed flow.
+
+This paper is organized as follows.
+In \S~\ref{sec:governing_eqs} we present the formulation for the Janus particles in a viscous fluid in the zero-Reynolds number regime.
+In \S~\ref{sec:IEM} we extend the hybrid continuum model for a Janus suspension to include the effects of a far-field flow via the mobility problem formulation.
+In \S~\ref{validation} we present validation of our model, and in \S~\ref{results} we present simulation results for a vesicle of Janus bilayer membrane under various flowing conditions.
+Finally we provide discussion and outlook for future directions in \S~\ref{conclusion}.
+
+\section{Governing  Equations\label{sec:governing_eqs}}
 \subsection{\label{mobility}Mobility Problem}
@@
 This vesicle-like structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
-the vesicle is about $8$ length units.
+the vesicle is about $8.5$ length units.
 The starting center of mass position of the Janus-vesicle is pinned at the origin and particle velocities are tracked to determine the initial configuration for later use such as single and multiple vesicle simulations.
@@
 The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
-interfacial tension $\gamma=4.11$ pN nm$^{-1}$ from ~\cite{Ryham16}.
-We then be able to calculate the characteristic time scale $\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP.
-With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
+interfacial tension $\gamma=4.1$ pN nm$^{-1}$ from ~\cite{Ryham16}. We then be able to calculate the corresponding 
+time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
+$\kappa=8.51$ kT.
+
+For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate $\chi$ is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
+\begin{align}
+  \chi = \dot\gamma \frac{\mu R_0^2}{\kappa},
+\end{align}
 %
-The dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ 
-is the shear rate.
-
-%For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$
-
-%referred from~\cite{Finken08} and~\cite{Shaqfeh11},
-%\begin{align}
-%  \chi = \dot\gamma \frac{\mu R_0^3}{\kappa},
-%\end{align}
-%%
-%where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.
+where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.
 
@@
 \hline                    
-$\dot\gamma$ (ns$^{-1}$) & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
+$\dot\gamma$ & 0.0020 & 0.0025 & 0.0030 & 0.0035 & 0.0040 & 0.0045 & 0.0050\\
 \hline 
-$F_{f}$ (pN nm$^{-1}$)           &  &  &  &  &  &  &   \\[1ex]
-$\dot\theta$ (ns$^{-1}$)           &  &  &  &  &  &  & \\ [1ex]
-$b$ (pN$\cdot$ns nm$^{-2}$)   &  &  &  &  &  &  & \\ 
+$F_{f}$ &  &  &  &  &  &  &   \\[1ex]
+$\dot\theta$             &  &  &  &  &  &  & \\ [1ex]
+$b$             &  &  &  &  &  &  & \\ 
 \hline    
@@
   }
-    \label{figure9}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
-\end{center} 
-  \caption{Trajectories of different setups in two-vesicle in an extensional flow where the centroids of two Janus-vesicle are plotted as blue dots.
-(i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii)
-  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure9} presents the numerical results from the case (iii) and a
-  consistent flow rate is $\chi = 0.005$ for all cases.}
-    \label{figure10}
+    \label{figure8}
 \end{figure}

### 2021-08-13 doc/main_jfm.tex

--- 2021-08-12 doc/main_jfm.tex
@@
+<<<<<<< HEAD
 \documentclass[lineno]{jfm}
@@
 \section{\label{intro}Introduction}
-
-\section{Governing  Equations}
+Described by de Gennes as ``another animal in soft matter physics", the Janus particle (often a spherical particle with a hydrophobic and a hydrophilic hemisphere) exhibits complex aggregate, clustering and self-assembly into meso- and macroscopic structures that are relevant to a wide range of applications in biology and bioengineering.
+Whether it is surface chemistry or polarity under an external field, the dynamics of Janus particles is inevitably the combination of long-range hydrodynamics interactions in the presence of short- and intermediate-range particle-particle interactions.
+
+Recently Fu {\it et al.} illustrated that the hydrophobic interactions between Janus particles in a viscous solvent can be used as a coarse-grained model to capture the mechanics of an elastic bilayer membrane of amphiphilic macromolecules such as lipids \cite{Fu2020_SIAM}.
+Depending on the total number of Janus particles and their geometry, in a viscous solvent, Janus particles are found to aggregate to form a micelle, a patch of bilayer membrane with open ends, and a self-enclosed bilayer membrane (a vesicle).
+Using a hybrid continuum model for the interactions between amphiphilic particles in a viscous solvent and formulating it in a boundary integral formulation, Fu {\it et al.} showed that the membrane granularity during fusion and fission of bilayers can be accurately captured.
+%This boundary integral formulation has inspired more recent work
+
+In molecular dynamics (MD) simulations, the lipid bilayer membranes are often approximated by an implicit solvent coarse-grained model for lipids (as in the Martini code), where their hydrodynamic interactions are simplified by an implicit solvent.
+The long-range hydrodynamic interactions and the induced long-range lipid interactions can be captured by combining the Dry Martini with a lattice Boltzmann MD \cite{Brandner2019_SciRep}.
+Brandner {\it et al.} used this methodology to simulate the hydrodynamics of a nano-sized vesicle under a shear flow, and reproduced the well-know vesicle hydrodynamics  such as tank-treading, tumbling and inter-leaflet slippage (reported from simulations of the Helfrich-type continuum model).
+
+In this work we extend the hybrid continuum model in \cite{Fu2020_SIAM} for the Janus suspension to incorporate the collective hydrodynamics of a Janus suspension under various flows: a linear shear flow, an elongation flow, and a Poiseuille flow.
+We demonstrate that a vesicle made of Janus particles does behave like a vesicle in these flowing conditions.
+Furthermore we also show that the hybrid continuum model allows us to investigate the inter-leaflet slippage and rupture of a bilayer membrane due to an imposed flow.
+
+This paper is organized as follows.
+In \S~\ref{sec:governing_eqs} we present the formulation for the Janus particles in a viscous fluid in the zero-Reynolds number regime.
+In \S~\ref{sec:IEM} we extend the hybrid continuum model for a Janus suspension to include the effects of a far-field flow via the mobility problem formulation.
+In \S~\ref{validation} we present validation of our model, and in \S~\ref{results} we present simulation results for a vesicle of Janus bilayer membrane under various flowing conditions.
+Finally we provide discussion and outlook for future directions in \S~\ref{conclusion}.
+
+\section{Governing  Equations\label{sec:governing_eqs}}
 \subsection{\label{mobility}Mobility Problem}
@@
 In order to examine the dynamics of the Janus-vesicle using the HAP coupling with hydrodynamics interactions, for the target bilayer, a circular initial shape is chosen to perform the relaxation run. 
-This structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
-the vesicle is about $8$ length units.
+This vesicle-like structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
+the vesicle is about $8.5$ length units.
 The starting center of mass position of the Janus-vesicle is pinned at the origin and particle velocities are tracked to determine the initial configuration for later use such as single and multiple vesicle simulations.
-The advantage of acquiring this configuration is to prevent some numerical instability issues when the minimum of the total energy is not achieved. 
-For instance, the dynamics of the bilayer under a shear flow may reach different outcomes or equilibrium states.
-Figure~\ref{figure2}(a) shows two sets of results: (1) the magnitudes of mean velocity components 
-${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$; (2) the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property of the model.
-This implies that a local energy minimum and the equilibrium configuration are nearly attained.
+This will prevent some numerical instability issues when the minimum of the total energy is not achieved. 
+For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
+Figure~\ref{figure2}(a) shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$.
+In the same figure, the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property of the model.
+This implies that a local energy minimum and the equilibrium configuration are
+nearly attained. 
 The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
 Figure~\ref{figure2}(b) shows the configuration difference between starting and ending frames in the relaxation run.
-The Figure~\ref{figure2}(c)-(d) demonstrate the fluid pressure profile of two configurations at $t=0$ and $t=1000$.
-The starting fluid pressure inside the permeable Janus-vesicle decreases as expected.
+The Figure~\ref{figure2}(c)-(d) demonstrate the fluid pressure profile of two configurations.
+The pressure inside the permeable Janus-vesicle decreases as expected.
 
@@
 
-Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of 
-Janus-vesicles under flows. To extract physical quantities of the target structure using the proposed model, 
-the scaling laws and the dimensionless units are given as follows.
-The length unit is scaled by the length of phospholipids $l=2.5$ nm which is set as the diameter of each 
-Janus particle. The force is scaled from the interfacial tension $\gamma=4.11$ pN nm$^{-1}$ 
-from ~\cite{Ryham16}. We then be able to calculate the characteristic time scale 
-$\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP. With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
-%
-For the model parameters, the decay length of attraction $\rho = 2l = 5$ nm, the repulsion length scale is 
-$\rho_0=0.5$, and teh repulsion strength $M=4.0$.
-The dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ is the shear rate.
-
-%For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$
-
-%referred from~\cite{Finken08} and~\cite{Shaqfeh11},
-%\begin{align}
-%  \chi = \dot\gamma \frac{\mu R_0^3}{\kappa},
-%\end{align}
-%%
-%where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.
+Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of vesicles 
+under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
+The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
+interfacial tension $\gamma=4.1$ pN nm$^{-1}$ from ~\cite{Ryham16}. We then be able to calculate the corresponding 
+time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
+$\kappa=8.51$ kT.
+
+For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate $\chi$ is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
+\begin{align}
+  \chi = \dot\gamma \frac{\mu R_0^2}{\kappa},
+\end{align}
+%
+where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.
 
@@
 
-To study the deformation of a Janus-vesicle under a shear flow using the proposed algorithm, 
+To study the deformation of a closed bilayer structure under a shear flow using the proposed algorithm, 
 we adopt a widely tested numerical simulation in both continuum and molecular dynamics models, single vesicle under a shear flow.
-The well known results indicate that the vesicle has tank-treading behavior when
-there is no viscosity contrast in both inside and outside of the vesicle that is one of the features in the  framework of the proposed model.
-
-The centroid of the pre-relaxed $58$-body Janus vesicle is initially placed at the origin then the shear flow 
-with a certain shear rate $\chi$ is turned on. 
-The snapshots of the simulation for single vesicle in a shear flow with a shear rate $\chi=0.0025$ are shown 
-in Figure~\ref{figure3}.
-Panels (a)-(b) show the initial shape obtained from the relaxation run and the deformed 
-configuration of the Janus-vesicle after a period of time ($t=4000$) is in panels (c)-(d). 
-The background color in panels (a) and (c) presented in the figure is the strength of the action due to the
-hydrophobic attraction. From weak to strong action field, the color varies from blue to red. Clearly, the
-hydrophobic layer has largest action. To demonstrate the tank-treading behavior of the vesicle, panels (b) 
-and (d) provide the streamlines of the fluid velocity over the whole computational domain when the shear 
-flow passes through the structure. The tank-treading motion of the structure is then observed, for instance,
-the particle velocities in panel (d) indicate a clockwise tank-treading movement.
+The well known results indicate that the vesicle does tank-treading when there is no viscosity contrast in both inside and outside of the structure.
+Given a set of various shear rates, with no viscosity difference between internal and external fluids, 
+the vesicle-like granular structure is initially placed in a quiescent flow for obtaining an equilibrium shape.
+
+The snapshots of the simulation for single vesicle in a shear flow are shown in Figure~\ref{figure3}.
+Panel (a) shows the initial circular shape obtained from the relaxation run and the deformed 
+configuration of the vesicle after a period of time ($t=4000$) is in panel (c). The color presented in the figure 
+is the strength of the action due to the hydrophobic attraction. From weak to strong action field, the color
+varies from blue to red.
+To demonstrate the tank-treading behavior of the vesicle, panels (b) and (d) provide the streamlines of the 
+fluid velocity over the whole computational domain when the shear flow passes through the structure.
+The tank-treading motion of the structure is then observed, for instance, the particle velocities in panel (d) indicate a clockwise tank-treading movement.
 
@@
 \includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
-  \caption{Vesicle under a shear flow where the shear rate $\chi=0.0025$: 
-  (a) Initial configuration of 58-body Janus-vesicle where black arrows are the particle orientations; 
+  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.0025$: 
+  (a) Initial configuration of 58-body vesicle; 
   (b) The fluid velocity plot with respect to the configuration in (a); Streamlines are plotted in the background
@@
   The background colors in panels (a) and (c) represent the strength of the hydrophobic attraction potential.
-The blue region shows no action and the red region in the bilayer gives the strongest action.
+The blue region shows no action and the red region with the bilayer gives the strongest action.
   }
@@
 %
-%
 
 In order to extract more physical properties of the proposed model, we track the total length of the bilayer structure, the reduced area over the time, and the excess length.
-Here the enclosed area and the total length of the structure are calculated from the midplane.
-These results are shown in Figure~\ref{figure4} where we compare results from the use of a set of shear 
-rates $\chi=\{0.002,0.0025,0.003,0.0035\}$. 
-The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ the area, and $L$ the total length of the Janus-vesicle with respect to the midplane. 
+Here the enclosed area and the length of the structure are calculated from the midplane.
+These results are shown in Figure~\ref{figure4} where we compare results from a set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$. 
+The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ is the vesicle area and $L$ is the arc length of the vesicle with respect to the midplane. 
 Furthermore, the excess length is given by $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
 Since the starting configuration is close to a circular shape, the reduced area decreases from a value very close to $1$.
-For the test cases in Figure~\ref{figure4}, the smooth curves in panel (a) are fitted using an
-exponential model given by $A^* = a_0 + b_0 \exp(-kt)$.
-Panel (b) shows that the decay rate $k$ is independent of the shear rate when the shear is above a threshold and the terminal reduced area for each
-case of the shear rate can then be calculated. It is also clear that a slower shear rate generates a higher reduced area and has a faster convergence then the high shear rate cases. 
-With a converging total arc length as shown in panel (c), a slower shear rate also produces a smaller excess length shown in panel (d).
-In summary, the small oscillations in all results are due to the granularity of the Janus-vesicle which tend to having a slightly non-smooth curve in simulations.
+It is clear that a slower shear rate generates a higher reduced area and has a faster convergence.
+With a converging total arc length, a slower shear rate also produces a smaller excess length.
+The small oscillations in all results are due to the granularity of the bilayer which tend to having a slightly non-smooth curve in simulations.
 Overall the total lengths of the bilayer have the same converging value in all test shear rates.
-Moreover, based on the numerical experiments, we observe that the reduce area converges relatively early when the shear rate is lower than $\chi=0.003$.
+Moreover, based on the
+numerical experiments, we observe that the reduce area converges relatively early when the shear rate is lower than $\dot\gamma=0.003$.
+
+An interesting phenomenon also rises up in the proposed setup where the inter-monolayer slip occurs 
+between two leaflets. When a shear rate is large enough, take $\dot\gamma = 0.005$ as an example, 
+Figure~\ref{figure5} shows the schematic of the test.
+A particle pair is initially marked and we then track the positions and mean angle $\theta(t)$ between particle relative position with respect to the vesicle center over the time.
+It is clear to see that the outer leaflet always has larger
+tangential velocity than the one from inner leaflet and the mean angle $\theta(t)$ increases. 
+This inter-leaflet sliding phenomenon is consistent with what has been seen
+in articles in molecular dynamics simulations. %%% need some citations
 
@@
   (c) Reduced area transitions over time. (d) Excess length of the midplanes.
-A set of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
+A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
 A slower shear rate generates a faster convergence in the reduced area and smaller excess length. 
@@
 
-An interesting phenomenon also rises up in the proposed setup where the inter-monolayer slip occurs 
-between two leaflets. When a shear rate is large enough, take $\chi = 0.005$ as an example, 
-Figure~\ref{figure5} shows the schematic of the test.
-A particle pair is initially marked and we then track the positions and mean angle $\theta(t)$ between particle relative position with respect to the vesicle center over the time.
-It is clear to see that the outer leaflet always has larger
-tangential velocity than the one from the inner leaflet and the mean angle $\theta(t)$ increases. 
-This inter-leaflet sliding phenomenon is consistent with what has been seen
-in articles in molecular dynamics simulations.
-
-%
-%\todo[inline]{Figure/Table of the friction coefficient for different shear rates (needs to revise)}
+\todo[inline]{Figure/Table of the friction coefficient for different shear rates (needs to revise)}
+
+The intermonolayer friction coefficient of the Janus-vesicle is calculated from the ratio of friction force and the 
+slip velocity. This quantity is given by 
+\begin{equation}
+b = \frac{F_f}{v^\parallel} = \frac{F_f}{\int_{\Sigma_M} R \dot\theta dS}.
+\end{equation}
+%
+where $v^\parallel$ represents the tangential velocity at the midplane and $\Sigma_M$ the curve determined by the midplane.
 
@@
   \caption{The schematic of the intermonolayer slip over a period of time.
-Taking shear rate $\chi=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position.
+Taking shear rate $\dot\gamma=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position.
 The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=\{2000,5200,9000\}$.
@@
 \end{figure}
-
-The inter-monolayer friction coefficient of the Janus-vesicle is calculated from the ratio of the friction force and the slip velocity. This quantity is given by 
-\begin{equation}
-b = \frac{F_f}{\int_{\Sigma_M} R \dot\theta dS},
-\end{equation}
-%
-where $\Sigma_M$ is the curve determined by the midplane and the relative radius $R$ is defined by the distance between the particle pair and the centroid of the Janus-vesicle.
-Hence, the mean rotational velocity
-of the bilayer is given by the integral of $R\dot\theta$ over the midplane curve $\Sigma_M$.
-For the friction force $F_f$, we calculate tangential stresses near the bilayer from outer and inner fluid then 
-extrapolate the force value onto the midplane to acquire the pressure jump. The friction force is computed after integrating the pressure jump over the midplane $\Sigma_M$.
-Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$. As expected,
-within the same order, the friction coefficients are independent of the shear rates.
 
@@
 \begin{tabular}{c c c c c c c c }
- $\chi$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
 \hline                    
-$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
-$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
-$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
-$b$ (pN$\cdot$ns nm$^{-2}$)   & 1.11 & 1.56 & 1.37 & 1.47 & 1.43 & 1.51 & 1.76\\ 
+$\dot\gamma$ & 0.0020 & 0.0025 & 0.0030 & 0.0035 & 0.0040 & 0.0045 & 0.0050\\
+\hline 
+$F_{f}$ &  &  &  &  &  &  &   \\[1ex]
+$\dot\theta$             &  &  &  &  &  &  & \\ [1ex]
+$b$             &  &  &  &  &  &  & \\ 
 \hline    
@@
 
-Besides the tests of a Janus-vesicle in a shear flow, an interesting test can also use the proposed model and the setup.
-Consider a symmetric parabolic flow about the $x$-axis, \cite{Kaoui09} studied shapes of the red blood cell immersed in a parabolic flow using a continuum model.
-With a similar setup, the background flow for this set of simulations is given by
+The background flow for this set of simulations is given by
+
 \begin{equation}
@@
 where $v_{max}$ is the flow strength and $w$ controls the shape of the flow.
-$R_0$ is defined as the radius of the Janus-vesicle at $t=0$.
-Figure~\ref{figure6} gives a configuration for one specific case where the centroid of the Janus-vesicle is initially placed slightly above the $x$-axis at $(0,3)$.
-The parameters are $v_{max} = 8.0$, $w=10$ and $R_0=8$.
-The inset of Figure~\ref{figure6} shows the trajectory of the mean position in $y$-direction which decreases toward $y=1$ for a period of time and starts to have an oscillatory motion.
-Moreover, the Janus-vesicle performs tank-treading during the simulation and red arrows in Figure~\ref{figure6} indicate a counterclockwise movement.
-For this test run, an asymmetric slipper occurs and the reduced area for this configuration is $\sim0.9$.
-This matches the previous numerical tests in  \cite{Kaoui09} where a slipper-like shape occurs when the flow velocity is weak.
+$R_0$ is defined as the radius of the initial vesicle midplane.
+Figure~\ref{figure6} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.
 
@@
 \includegraphics[height=2in]{parabolic.eps}
-  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$.
-The configuration is the state when $t=10000$.
-Red arrows are directors of particle velocities.
-The inset shows the mean $y$-position over time.
+  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=10000$.
   }
@@
 With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
-Figure~\ref{figure7} shows a demonstration of a vesicle under a shear flow with shear rate $\chi=0.1$.
+Figure~\ref{figure7} shows a demonstration of a vesicle under a shear flow with shear rate $\dot\gamma=0.1$.
 An interesting phenomenon occurs in panels (c) and (d) where two separated bilayers move along the background shear flow symmetrically.
@@
   \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
-Here the shear rate is $\chi = 0.1$.
+Here the shear rate is $\dot\gamma = 0.1$.
 Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)).
@@
 \includegraphics[height=2in]{N116_shear_7500.pdf}
-  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a).
+  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
 The background color indicates the magnitude of fluid pressure.
@@
   }
-    \label{figure8}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{ShearTraj.eps}
-\end{center} 
-  \caption{Trajectories of two-vesicle in a shear flow where the centroids of two Janus-vesicle are plotted as blue dots.
-Both starting centroids of two Janus-vesicles are on the $x$-axis.
-For simulation time, $t = {0, 400,800,1200}$ for (a)-(d) and $t = {1600, 2400, 3200, 4000}$ for (e)-(h).
-}
     \label{figure9}
@@
 \subsubsection{Shear Flow}
-
-Figure~\ref{figure8} demonstrates the simulation results of two Janus-vesicles in a shear flow where the testing shear rate is $\chi=0.005$ and the flow is given by $\dot x = \chi y$.
-In panel (a), the starting frame, two center-of-mass positions are placed
-on the same horizontal level, at $(-10,0)$ and $(10,0)$.
-Since we already have a pre-relaxed $58$-body in previous sections, we duplicate the state to have the initial configuration in this section.
-As expected, there
-is no pressure jump between the internal and external fluids from the beginning of the simulation and this is shown in the background pressure plot.
-Panels (b)-(d) show the configurations when $t = \{400,800,100\}$
-and we observe that the rotation continues as time goes. The streamlines are plotted in the background 
-for all panels and we include the numerical results using continuum model in all insets. Obviously there is a qualitative agreement between two models.
-
-An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be seen and tuned.
+Two vesicles in a shear flow is presented in Figures~\ref{figure9} where centers of mass are placed on the same horizontal level.
+With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \dot\gamma y$.
+An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.
 In other words, the adhesive behavior will be absent when two vesicles are centered
-at a different level and are well separated in $y$-direction. Trajectories of a longer run of the simulation results are shown in Figure~\ref{figure9}.
-
-%Two vesicles in a shear flow is presented in Figures~\ref{figure8} where centers of mass are placed on the same horizontal level, at $(-10,0)$ and $(10,0)$.
-With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \chi y$.
+at a different level and are well separated in $y$-direction.
 
@@
 \includegraphics[height=2in]{N116_ext_6500.pdf}
-  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a).
+  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
 The background color indicates the magnitude of fluid pressure.
@@
   }
-    \label{figure10}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
-\end{center} 
-  \caption{Trajectories of different setups in two-vesicle in an extensional flow where the centroids of two Janus-vesicle are plotted as blue dots.
-(i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii)
-  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure9} presents the numerical results from the case (iii) and a
-  consistent flow rate is $\chi = 0.005$ for all cases.}
-    \label{figure11}
+    \label{figure8}
 \end{figure}
@@
 
-With a similar setup in the case of two Janus-vesicles in a shear flow, we use the same two pre-relaxed $58$-body Janus-vesicles to perform the simulations when the flow type is an extensional flow with flow rate $\chi=0.005$.
-This extensional flow is stretching along the $y$ direction and squeezing in $x$ direction.
-Figure~\ref{figure10} shows one set of numerical results when the centroids of two bodies are placed at
-$(-10,-0.1)$ and $(10,0.1)$. With this setup, we can make sure that two Janus-vesicles will separate along 
-$y$-direction eventually from empirical tests.
-Panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
-Since two bilayers are close enough from the beginning of the run, two vesicles are first pushed toward each other then separate along the streamlines.
-The short range repulsion plays an important role to avoid structure collisions and this result can be compared with some findings in continuum modeling simulations.
+Figures~\ref{figure8} show the numerical results of simulations when two vesicles are in an extensional flow.
+Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
+The extensional flow is stretching along the $y$ direction and squeezing in $x$ direction with shear rate $\dot\gamma=0.005$.
+Since two bilayers are close enough
+from the beginning of the run, two vesicles are first pushed toward each other then separate along the streamline. The short range repulsion plays an important role to avoid structure collisions and 
+this result can be compared with some findings in continuum modeling simulations.
 The pressure plots in Figure~\ref{figure8} provide a realistic result where the pressure is much higher in the gap between two nearby vesicles.
-
-Figure~\ref{figure11} provides simulation results when the center-of-mass positions are placed differently.
-One can notice that when two centroids are placed on the same horizontal level, two Janus-vesicles reach
-an equilibrium state without separation as shown in case (i).
-If only one centroid is placed above the $x$-axis, for instance, case (ii), two Janus-vesicle move together toward the upward.
-This is the consequence when the adhesive effect beats the flow strength.
-Case (iii) is same as the case shown in Figure~\ref{figure10}.
-Finally, case (iv) has a larger initial separation in $y$-direction and two Janus-vesicle moves much faster toward
-$\pm y$-directions.
 
@@
 
+%\section{\label{A2} Comparison between Continuum Model and the Proposed Model}
+%
+%\begin{figure}
+%\centering
+%\includegraphics[height=1.2in]{N116_cont_a.pdf}
+%\includegraphics[height=1.2in]{N116_cont_b.pdf}
+%\includegraphics[height=1.2in]{N116_cont_c.pdf}
+%\includegraphics[height=1.2in]{N116_cont_d.pdf}
+%  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
+%  }
+%    \label{figureB}
+%\end{figure}
+
 \bibliographystyle{jfm}
@@
 \end{document}
+=======
+\documentclass[lineno]{jfm}
+
+\usepackage{graphicx}
+%\usepackage{epstopdf,epsfig}
+\usepackage{newtxtext}
+\usepackage{newtxmath}
+\usepackage{natbib}
+\usepackage{hyperref}
+\usepackage{mathtools}
+\usepackage{commath}
+\usepackage{todonotes}
+
+\hypersetup{
+    colorlinks = true,
+    urlcolor   = blue,
+    citecolor  = black,
+}
+\newtheorem{lemma}{Lemma}
+\newtheorem{corollary}{Corollary}
+\newcommand{\RomanNumeralCaps}[1]
+\linenumbers
+
+% Bryan's Marcros
+\renewcommand{\aa}{\mathbf{a}}
+\newcommand{\bd}{\partial}
+\newcommand{\DD}{\mathcal{D}}
+\newcommand{\eeta}{\boldsymbol{\eta}}
+\newcommand{\FF}{\mathbf{F}}
+\newcommand{\GG}{\mathbf{G}}
+\newcommand{\nnu}{\boldsymbol{\nu}}
+\newcommand{\ssigma}{\boldsymbol{\sigma}}
+\newcommand{\rr}{\mathbf{r}}
+\newcommand{\RR}{\mathbf{R}}
+\renewcommand{\SS}{\mathbf{S}}
+\newcommand{\xx}{\mathbf{x}}
+\newcommand{\uu}{\mathbf{u}}
+\renewcommand{\vv}{\mathbf{v}}
+\newcommand{\yy}{\mathbf{y}}
+\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
+
+% {\MakeUppercase{\romannumeral #1}}
+
+%\title{Two-Dimensional Vesicles Under External Flow via Integral Equation Method}
+\title{Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations}
+%\author{Alan N. Jones\aff{1}
+%  \corresp{\email{JFMEditorial@cambridge.org}},
+%  H.-C. Smith\aff{1}
+% \and J.Q. Long\aff{2}}
+%
+%\affiliation{\aff{1}STM Journals, Cambridge University Press, The Printing House, Shaftesbury Road, Cambridge CB2 8BS, UK
+%\aff{2}DAMTP, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WA, UK}
+
+\author{
+Szu-Pei Fu\aff{1},
+Bryan Quaife\aff{2},
+Rolf Ryham\aff{1}, \and
+Yuan-Nan Young\aff{3}
+}
+ \affiliation{
+\aff{1}Department of Mathematics, \\Fordham University, Bronx, New York 10458, USA
+\aff{2}Department of Scientific Computing, \\Florida State University, Tallahassee, Florida 32306, USA
+\aff{3}Department of Mathematical Sciences, New Jersey Institute of Technology,\\ Newark, New Jersey 07102, USA
+ }
+
+\begin{document}
+\maketitle
+
+\begin{abstract}
+In this work, we study the dynamics of many-body systems immersed in a viscous fluid with a specified interparticle force.
+In particular, we apply a hydrophobic attraction potential (HAP) using a Janus type granular system to model lipid bilayer membranes.
+Coupling with an efficient integral equation method for rigid bodies in Stokes flow and an previous developed HAP solver, the deformations of a two-dimensional vesicle such as tank-treading motion and membrane ruptures can be observed under different values of the shear rate.
+Moreover, an efficient integral equation method is adopted for solving the screened Laplace equation and the mobility problem where it can accurately calculate hydrophobic and hydrodynamic interactions between near touched boundaries.
+\end{abstract}
+
+\begin{keywords}
+Authors should not enter keywords on the manuscript, as these must be chosen by the author during the online submission process and will then be added during the typesetting process (see \href{https://www.cambridge.org/core/journals/journal-of-fluid-mechanics/information/list-of-keywords}{Keyword PDF} for the full list).
+Other classifications will be added at the same time.
+\end{keywords}
+
+{\bf MSC Codes }  {\it(Optional)} Please enter your MSC Codes here
+
+\section{\label{intro}Introduction}
+
+\section{Governing  Equations}
+\subsection{\label{mobility}Mobility Problem}
+We consider a suspension of $N_b$ particles suspended in a
+two-dimensional unbounded domain. The boundary of each particle is
+denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
+\cdots \cup \Gamma_{N_b}$. Assuming the flow is Stokesian, the governing
+equations are
+\begin{alignat}{3}
+  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
+    && \xx \in \Omega, \\
+  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
+  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
+\end{alignat}
+%
+where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
+and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
+with center $\aa_i$ is a rigid body, its velocity satisfies 
+\begin{align}
+  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
+    \xx \in \Gamma_i,
+\end{align}
+where $\vv_i$ is its translational velocity and $\omega_i$ is its
+angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
+\rangle$. Therefore, the no-slip boundary condition on each particle is
+\begin{align}
+  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
+    \xx \in \Gamma_i.
+\end{align}
+To determine the translational and angular velocities of each particle,
+we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
+particle. Since the small particles are intertialess, force balance
+gives 
+\begin{alignat}{2}
+  \label{eqn:force}
+  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, ds = \mathbf{0},
+  && i=1,\ldots,N_b,\\
+  \label{eqn:torque}
+  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
+    (\ssigma \cdot \nnu_i) \, ds = 0, \qquad && i=1,\ldots,N_b,
+\end{alignat}
+where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
+\right)$ is the hydrodynamic stress tensor (pressure tensor). The
+process of finding the translational and angular velocities given a
+force and torque is referred to as the mobility problem.
+
+\subsection{Imposed Forces}
+The imposed forces and torques contain two parts. The first part comes
+from the hydrophobic attraction potential (HAP). This potential was
+introduced in~\cite{Fu20} and models hydrophobic attraction by solving
+the screened Laplace equation boundary value problem
+\begin{alignat}{2}
+  \label{SL}
+-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
+\label{SLbc}
+u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i, \\
+\label{SLff}
+u &\to 0,                          &&|\xx| \to \infty,
+\end{alignat}
+where $f_i$ is a material label with $f_i = 0$ ($1$) representing
+hydrophilic (hydrophobic) portions of the surface, and $\rho$ is the
+decay length of attraction. The forces and torques for this attraction
+are 
+\begin{align}
+  \label{eqn:hydrophobicAttraction}
+  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, dS, 
+    \quad 
+  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) dS,
+\end{align}
+where
+\begin{align}
+  \label{eq:stress}
+\mathbf{T}
+= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
+  u|^2 \mathbf{I} - \nabla u\otimes \nabla u\right)
+\end{align}
+is the hydrophobic stress tensor. The parameter $\gamma$ is interfacial
+tension. The forces $\FF_i^{\text{hydro}}$ and torques
+$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
+that partially sequester the hydrophobic portions of the particle
+surface.
+
+The second part of the imposed forces and torques comes from repulsion
+between proximal particles. Given a pair particles indexed with $i$ and
+$j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
+$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another. We then
+define the repulsion force and torque
+\begin{align}
+%  \label{eqn:REPUL}
+%  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\xx_{ij} -
+%  \yy_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
+%  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\xx_{ij} - \aa_i)^{\perp}\cdot
+%  \frac{\xx_{ij} - \yy_{ij}}{\rho_{ij}} P(\rho_{ij})
+%  \\
+%
+  \label{eqn:REPULforce}
+  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
+    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
+    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
+    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
+  \label{eqn:REPULtorque}
+  T_i^{\text{repul}} &= \sum_{j \neq i} 
+    (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
+    \frac{\tilde{\xx}_i - \tilde{\xx}_j}
+    {|\tilde{\xx}_i - \tilde{\xx}_j|} 
+    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
+\end{align}
+The repulsion profile $P(r)$ is zero for distances $r$ larger than a
+repulsion length scale $\rho_0$. As such,~\eqref{eqn:REPULforce}
+and~\eqref{eqn:REPULtorque} ignore particles $\Gamma_j$ outside a
+tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
+$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
+prevent particle collisions. Then, the total imposed force and torque
+are
+\begin{align}
+  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
+  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
+  i=1,\ldots,N_b.
+\end{align}
+
+\subsection{Time Marching}
+By solving the mobility problem, we obtain translational and angular
+velocities of the $N_b$-body system. A second-order Adams-Bashforth
+scheme updates the particle positions and orientations. By including the
+repulsion force~\eqref{eqn:REPULforce} and
+torque~\eqref{eqn:REPULtorque}, particle collisions are avoided even
+when using a relatively large time step.
+
+%This paper is organized as follows.
+Chapter 2 introduces the mobility problem.....
+The integral equation method for solving $N_b$-body system with details of ....
+are included in Chapter 3.
+We provide numerical results of vesicle simulations in Chapter 4.
+Finally, we conclude the work and briefly give the picture of our future work.
+
+%%%
+\section{Integral Equation Method}
+\label{sec:IEM}
+Computing the hydrophobic attraction potential and the particle forces
+and torques requires solving an elliptic partial differential equation
+(PDE) in an unbounded complex domain. We recast both these PDEs as
+boundary integral equations (BIEs). We discretize each BIE at $N$ points
+on each of the $N_b$ particles with a collocation method. Integrals that
+are smooth are computed with the spectrally-accurate quadrature rule,
+and nearly-singular integrals, caused by close contact between two
+particles, are computed with a high-order interpolation-based quadrature
+rule~\cite{qua-bir2014}. After discretizing and applying quadrature, the
+resulting linear system is solved with matrix-free GMRES, and we
+guarantee that the number of GMRES iterations is mesh-independent by
+using second-kind BIEs.
+
+\subsection{HAP Boundary Integral Equation}
+Similar to our previous work~\cite{Fu20}, we represent the HAP as a
+double-layer potential
+\begin{align}
+  \label{eqn:HAP_DLP}
+  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, ds_\yy,
+    \quad \xx \in \Omega,
+\end{align}
+where $K_0$ is the zeroth-order modified Bessel function of the first
+kind. By requiring that the density function $\sigma$ satisfies the
+second-kind integral equation
+\begin{align}
+  f(\xx) = \frac{1}{2}\sigma(\xx) + 
+    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, ds_\yy,
+    \quad \xx \in \bd\Omega,
+\end{align}
+the HAP double-layer potential~\eqref{eqn:HAP_DLP} satisfies the
+screened Laplace equation~\eqref{SL}--\eqref{SLff}. To calculate the
+hydrophobic force and torque, the gradient of the double-layer
+potential~\eqref{eqn:HAP_DLP} must be computed on the boundary of each
+particle. In Appendix~\ref{sec:appendixA}, we show that the force and
+torque calculations can be expressed in terms of integral that are
+non-singular.
+
+\subsection{Mobility Problem Boundary Integral Equation}
+Following previous work of~\cite{Lukas19}, we represent the velocity as
+the sum of a double-layer potential and the $N_b$ Stokeslets and Rotlets
+\begin{align}
+  \label{eqn:velocity}
+  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
+    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
+    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
+\end{align}
+The double-layer potential is
+\begin{align}
+  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
+    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
+    \eeta(\yy) \, ds_\yy,
+\end{align}
+where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
+centered at $\aa_i$ are
+\begin{align}
+  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log(\rho) + 
+    \frac{\rr \otimes \rr}{\rho^2} \FF_i \right), \\
+  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
+\end{align}
+where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
+torque-free and has force $\FF_i$ while the Rotlet force-free and has
+torque $T_i$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
+total force~\eqref{eqn:force} and torque~\eqref{eqn:torque} conditions
+if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
+Matching the limit of~\eqref{eqn:velocity} with the rigid body motion,
+and imposing that $\DD[\eeta]$ is force- and torque-free, the density
+function $\eeta$, translational velocity $\vv_i$, and angular velocity
+$\omega_i$ satisfy
+\begin{alignat}{3}
+  \nonumber
+  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
+    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
+  \label{eqn:SKIE}
+    + \sum_{j=1}^{N_b} &
+    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
+    \quad &&\xx \in \bd \Gamma_i,\: i=1,\ldots,N_b, \\
+  \label{eqn:mobility1}
+  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, ds &= {\bf 0}, 
+  &&i = 1,\ldots,N_b, \\
+  \label{eqn:mobility2}
+  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu ds &= 0,
+  &&i = 1,\ldots,N_b.
+\end{alignat}
+
+The trapezoid rule is used to approximate each of the integrals in
+equations~\eqref{eqn:mobility1} and~\eqref{eqn:mobility2}, and the
+double-layer potential equation~\eqref{eqn:SKIE} is approximated with
+either the trapezoid rule, or the interpolation-based near-singular
+integration quadrature rule. After discretizing and applying appropriate
+quadrature rules, the result is a $(2NN_b + 3N_b) \times (2NN_b + 3N_b)$
+linear system that we precondition with a block-diagonal preconditioner.
+We note that other BIE formulations of the mobility problem use
+single-layer potentials~\cite{cor-gre-rac-vee2017, rac-gre2016} or both
+single- and double-layer potentials~\cite{cor-vee2018}.
+
+%%%
+
+\section{\label{validation}Model Validation}
+
+\subsection{Jeffery Orbit}
+
+The preliminary test of the proposed model using the integral equation method is the numerical validation in Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate.
+An ellipsoidal particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\Theta = 0^\circ$.
+Based on the theoretical Jeffery orbits with respect to the target angle $\Theta(t)$,
+
+\begin{equation}
+\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
+\end{equation}
+%
+where $a$, $b$ are semi-major and semi-minor axes, and the test aspect ratios of the particle are $2$ and $3$.
+Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from the Jeffery orbits.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
+\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
+  \caption{Comparisons of the target angle $\Theta(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method.
+The schematic of the simulation setup is shown in the inset of the figure.
+Here two cases of aspect ratio are validated, $a/b = 2$ and $a/b=3$.
+  }
+    \label{figure1}
+\end{figure}
+
+\subsection{Self-Assembly and Relaxtion}
+
+In order to examine the dynamics of the Janus-vesicle using the HAP coupling with hydrodynamics interactions, for the target bilayer, a circular initial shape is chosen to perform the relaxation run. 
+This structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
+the vesicle is about $8$ length units.
+The starting center of mass position of the Janus-vesicle is pinned at the origin and particle velocities are tracked to determine the initial configuration for later use such as single and multiple vesicle simulations.
+The advantage of acquiring this configuration is to prevent some numerical instability issues when the minimum of the total energy is not achieved. 
+For instance, the dynamics of the bilayer under a shear flow may reach different outcomes or equilibrium states.
+Figure~\ref{figure2}(a) shows two sets of results: (1) the magnitudes of mean velocity components 
+${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$; (2) the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property of the model.
+This implies that a local energy minimum and the equilibrium configuration are nearly attained.
+The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
+Figure~\ref{figure2}(b) shows the configuration difference between starting and ending frames in the relaxation run.
+The Figure~\ref{figure2}(c)-(d) demonstrate the fluid pressure profile of two configurations at $t=0$ and $t=1000$.
+The starting fluid pressure inside the permeable Janus-vesicle decreases as expected.
+
+\begin{figure}
+\centering
+\includegraphics[height=2in]{relax.eps}
+\includegraphics[height=2in]{relax2.eps}\\
+\includegraphics[height=2.in]{N58_0pres.pdf}
+\includegraphics[height=2.in]{N58_5000pres.pdf}
+%  \todo[inline]{Put pressure of each of the two configurations below
+%  this.}
+  \caption{Vesicle relaxes under a quiescent flow.
+(a) The blue dashed and solid curves are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively.
+The red curve shows the decreasing trend of the mean magnitude of particle orientation change.
+The black dashed line shows the reference of how all magnitudes decay.
+(b) Bilayer configurations for $t=0$(gray) and $t=1000$(red) with particle directors.
+  (c)-(d) show the fluid pressure profiles for $t=0$ and $t=1000$ where the background curves indicate the streamlines.
+In panel (c), the pressure value in internal fluid is much higher than the pressure outside of the bilayer.
+After the relaxation, this immersed permeable bilayer approaches a steady state as shown in panel (d).
+  }
+    \label{figure2}
+\end{figure}
+
+%%%
+
+\section{\label{results}Numerical Results}
+
+%\todo[inline]{Introduce dimensionless shear rate here (and check the numbers)}
+
+Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of 
+Janus-vesicles under flows. To extract physical quantities of the target structure using the proposed model, 
+the scaling laws and the dimensionless units are given as follows.
+The length unit is scaled by the length of phospholipids $l=2.5$ nm which is set as the diameter of each 
+Janus particle. The force is scaled from the interfacial tension $\gamma=4.11$ pN nm$^{-1}$ 
+from ~\cite{Ryham16}. We then be able to calculate the characteristic time scale 
+$\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP. With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
+%
+For the model parameters, the decay length of attraction $\rho = 2l = 5$ nm, the repulsion length scale is 
+$\rho_0=0.5$, and teh repulsion strength $M=4.0$.
+The dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ is the shear rate.
+
+%For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$
+
+%referred from~\cite{Finken08} and~\cite{Shaqfeh11},
+%\begin{align}
+%  \chi = \dot\gamma \frac{\mu R_0^3}{\kappa},
+%\end{align}
+%%
+%where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.
+
+\subsection{Tank-Treading Vesicles}
+
+\subsubsection{Vesicle in a Shear Flow}
+
+To study the deformation of a Janus-vesicle under a shear flow using the proposed algorithm, 
+we adopt a widely tested numerical simulation in both continuum and molecular dynamics models, single vesicle under a shear flow.
+The well known results indicate that the vesicle has tank-treading behavior when
+there is no viscosity contrast in both inside and outside of the vesicle that is one of the features in the  framework of the proposed model.
+
+The centroid of the pre-relaxed $58$-body Janus vesicle is initially placed at the origin then the shear flow 
+with a certain shear rate $\chi$ is turned on. 
+The snapshots of the simulation for single vesicle in a shear flow with a shear rate $\chi=0.0025$ are shown 
+in Figure~\ref{figure3}.
+Panels (a)-(b) show the initial shape obtained from the relaxation run and the deformed 
+configuration of the Janus-vesicle after a period of time ($t=4000$) is in panels (c)-(d). 
+The background color in panels (a) and (c) presented in the figure is the strength of the action due to the
+hydrophobic attraction. From weak to strong action field, the color varies from blue to red. Clearly, the
+hydrophobic layer has largest action. To demonstrate the tank-treading behavior of the vesicle, panels (b) 
+and (d) provide the streamlines of the fluid velocity over the whole computational domain when the shear 
+flow passes through the structure. The tank-treading motion of the structure is then observed, for instance,
+the particle velocities in panel (d) indicate a clockwise tank-treading movement.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{N58_0.pdf}
+\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
+\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
+\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
+  \caption{Vesicle under a shear flow where the shear rate $\chi=0.0025$: 
+  (a) Initial configuration of 58-body Janus-vesicle where black arrows are the particle orientations; 
+  (b) The fluid velocity plot with respect to the configuration in (a); Streamlines are plotted in the background
+  as solid curves. Red arrows represent the particle velocities.
+  (c) Deformed vesicle after $20000$ steps. The tank-treading motion occurs after reaching the state shown in panel (c).
+  (d) The fluid velocity plot with respect to the configuration in (c);
+  The background colors in panels (a) and (c) represent the strength of the hydrophobic attraction potential.
+The blue region shows no action and the red region in the bilayer gives the strongest action.
+  }
+    \label{figure3}
+\end{figure}
+%
+%
+
+In order to extract more physical properties of the proposed model, we track the total length of the bilayer structure, the reduced area over the time, and the excess length.
+Here the enclosed area and the total length of the structure are calculated from the midplane.
+These results are shown in Figure~\ref{figure4} where we compare results from the use of a set of shear 
+rates $\chi=\{0.002,0.0025,0.003,0.0035\}$. 
+The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ the area, and $L$ the total length of the Janus-vesicle with respect to the midplane. 
+Furthermore, the excess length is given by $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
+Since the starting configuration is close to a circular shape, the reduced area decreases from a value very close to $1$.
+For the test cases in Figure~\ref{figure4}, the smooth curves in panel (a) are fitted using an
+exponential model given by $A^* = a_0 + b_0 \exp(-kt)$.
+Panel (b) shows that the decay rate $k$ is independent of the shear rate when the shear is above a threshold and the terminal reduced area for each
+case of the shear rate can then be calculated. It is also clear that a slower shear rate generates a higher reduced area and has a faster convergence then the high shear rate cases. 
+With a converging total arc length as shown in panel (c), a slower shear rate also produces a smaller excess length shown in panel (d).
+In summary, the small oscillations in all results are due to the granularity of the Janus-vesicle which tend to having a slightly non-smooth curve in simulations.
+Overall the total lengths of the bilayer have the same converging value in all test shear rates.
+Moreover, based on the numerical experiments, we observe that the reduce area converges relatively early when the shear rate is lower than $\chi=0.003$.
+
+\begin{figure}
+\begin{center}
+\hspace{-0.6cm}
+\includegraphics[height=2in]{ReducedArea.pdf}
+\hspace{0.6cm}
+\includegraphics[height=2in]{DecayRate.eps}\\
+\includegraphics[height=2in]{ArcLength.pdf}
+\includegraphics[height=2in]{ExcLength.pdf}
+\end{center} 
+  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) From exponential fits in panel (a), we obtain the decay rate for a number of different shear rates;
+  (c) Reduced area transitions over time. (d) Excess length of the midplanes.
+A set of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
+A slower shear rate generates a faster convergence in the reduced area and smaller excess length. 
+  }
+    \label{figure4}
+\end{figure}
+
+An interesting phenomenon also rises up in the proposed setup where the inter-monolayer slip occurs 
+between two leaflets. When a shear rate is large enough, take $\chi = 0.005$ as an example, 
+Figure~\ref{figure5} shows the schematic of the test.
+A particle pair is initially marked and we then track the positions and mean angle $\theta(t)$ between particle relative position with respect to the vesicle center over the time.
+It is clear to see that the outer leaflet always has larger
+tangential velocity than the one from the inner leaflet and the mean angle $\theta(t)$ increases. 
+This inter-leaflet sliding phenomenon is consistent with what has been seen
+in articles in molecular dynamics simulations.
+
+%
+%\todo[inline]{Figure/Table of the friction coefficient for different shear rates (needs to revise)}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{Slip.eps}
+\end{center} 
+  \caption{The schematic of the intermonolayer slip over a period of time.
+Taking shear rate $\chi=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position.
+The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=\{2000,5200,9000\}$.
+The midplane curve is denoted as $\Sigma_M$.
+  }
+    \label{figure5}
+\end{figure}
+
+The inter-monolayer friction coefficient of the Janus-vesicle is calculated from the ratio of the friction force and the slip velocity. This quantity is given by 
+\begin{equation}
+b = \frac{F_f}{\int_{\Sigma_M} R \dot\theta dS},
+\end{equation}
+%
+where $\Sigma_M$ is the curve determined by the midplane and the relative radius $R$ is defined by the distance between the particle pair and the centroid of the Janus-vesicle.
+Hence, the mean rotational velocity
+of the bilayer is given by the integral of $R\dot\theta$ over the midplane curve $\Sigma_M$.
+For the friction force $F_f$, we calculate tangential stresses near the bilayer from outer and inner fluid then 
+extrapolate the force value onto the midplane to acquire the pressure jump. The friction force is computed after integrating the pressure jump over the midplane $\Sigma_M$.
+Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$. As expected,
+within the same order, the friction coefficients are independent of the shear rates.
+
+\begin{table}
+\caption{Friction Coefficients}
+\centering    
+\begin{tabular}{c c c c c c c c }
+ $\chi$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
+\hline                    
+$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
+$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
+$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
+$b$ (pN$\cdot$ns nm$^{-2}$)   & 1.11 & 1.56 & 1.37 & 1.47 & 1.43 & 1.51 & 1.76\\ 
+\hline    
+\end{tabular} 
+\label{table1}
+\end{table}
+
+\subsubsection{Vesicle in a Parabolic Flow}
+
+Besides the tests of a Janus-vesicle in a shear flow, an interesting test can also use the proposed model and the setup.
+Consider a symmetric parabolic flow about the $x$-axis, \cite{Kaoui09} studied shapes of the red blood cell immersed in a parabolic flow using a continuum model.
+With a similar setup, the background flow for this set of simulations is given by
+\begin{equation}
+{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
+\end{equation}
+%
+where $v_{max}$ is the flow strength and $w$ controls the shape of the flow.
+$R_0$ is defined as the radius of the Janus-vesicle at $t=0$.
+Figure~\ref{figure6} gives a configuration for one specific case where the centroid of the Janus-vesicle is initially placed slightly above the $x$-axis at $(0,3)$.
+The parameters are $v_{max} = 8.0$, $w=10$ and $R_0=8$.
+The inset of Figure~\ref{figure6} shows the trajectory of the mean position in $y$-direction which decreases toward $y=1$ for a period of time and starts to have an oscillatory motion.
+Moreover, the Janus-vesicle performs tank-treading during the simulation and red arrows in Figure~\ref{figure6} indicate a counterclockwise movement.
+For this test run, an asymmetric slipper occurs and the reduced area for this configuration is $\sim0.9$.
+This matches the previous numerical tests in  \cite{Kaoui09} where a slipper-like shape occurs when the flow velocity is weak.
+
+\begin{figure}
+\centering
+\includegraphics[height=2in]{parabolic.eps}
+  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$.
+The configuration is the state when $t=10000$.
+Red arrows are directors of particle velocities.
+The inset shows the mean $y$-position over time.
+  }
+    \label{figure6}
+\end{figure}
+
+\subsubsection{Membrane Ruptures}
+
+With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
+Figure~\ref{figure7} shows a demonstration of a vesicle under a shear flow with shear rate $\chi=0.1$.
+An interesting phenomenon occurs in panels (c) and (d) where two separated bilayers move along the background shear flow symmetrically.
+Consequently, a periodic motion for bilayers may occur
+with the choices of shear rates. One can expect that these two layers will flow far apart from each other for much higher shear rates.
+
+\begin{figure}
+\centering
+\includegraphics[height=2in]{N58_rupt_0.pdf}
+\includegraphics[height=2in]{N58_rupt_200.pdf}
+\\
+\includegraphics[height=2in]{N58_rupt_400.pdf}
+\includegraphics[height=2in]{N58_rupt_600.pdf}
+  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
+Here the shear rate is $\chi = 0.1$.
+Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)).
+(c)-(d) are the later states during the simulation.
+  }
+    \label{figure7}
+\end{figure}
+
+%
+
+\subsection{Two Vesicles in a Linear Flow}
+
+\begin{figure}
+\centering
+\includegraphics[height=2in]{N116_shear_0.pdf}
+\includegraphics[height=2in]{N116_shear_2500.pdf}\\
+\includegraphics[height=2in]{N116_shear_5000.pdf}
+\includegraphics[height=2in]{N116_shear_7500.pdf}
+  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a).
+The background color indicates the magnitude of fluid pressure.
+From dark red to dark blue, it represents the the pressure varies from high to low values.
+The color bar is valid for all panels.
+Streamlines are plotted in purple.
+The insets of all panels are generated from the results of continuum modeling simulations and the streamlines have a perfect agreement to the numerical results.
+  }
+    \label{figure8}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{ShearTraj.eps}
+\end{center} 
+  \caption{Trajectories of two-vesicle in a shear flow where the centroids of two Janus-vesicle are plotted as blue dots.
+Both starting centroids of two Janus-vesicles are on the $x$-axis.
+For simulation time, $t = {0, 400,800,1200}$ for (a)-(d) and $t = {1600, 2400, 3200, 4000}$ for (e)-(h).
+}
+    \label{figure9}
+\end{figure}
+
+\subsubsection{Shear Flow}
+
+Figure~\ref{figure8} demonstrates the simulation results of two Janus-vesicles in a shear flow where the testing shear rate is $\chi=0.005$ and the flow is given by $\dot x = \chi y$.
+In panel (a), the starting frame, two center-of-mass positions are placed
+on the same horizontal level, at $(-10,0)$ and $(10,0)$.
+Since we already have a pre-relaxed $58$-body in previous sections, we duplicate the state to have the initial configuration in this section.
+As expected, there
+is no pressure jump between the internal and external fluids from the beginning of the simulation and this is shown in the background pressure plot.
+Panels (b)-(d) show the configurations when $t = \{400,800,100\}$
+and we observe that the rotation continues as time goes. The streamlines are plotted in the background 
+for all panels and we include the numerical results using continuum model in all insets. Obviously there is a qualitative agreement between two models.
+
+An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be seen and tuned.
+In other words, the adhesive behavior will be absent when two vesicles are centered
+at a different level and are well separated in $y$-direction. Trajectories of a longer run of the simulation results are shown in Figure~\ref{figure9}.
+
+%Two vesicles in a shear flow is presented in Figures~\ref{figure8} where centers of mass are placed on the same horizontal level, at $(-10,0)$ and $(10,0)$.
+With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \chi y$.
+
+%\todo[inline]{Migration pattern and/or separation distance. See Fig 8 in
+%JCP paper by Rahimian, Veerapaneni, and Biros.}
+
+\begin{figure}
+\centering
+\includegraphics[height=2in]{N116_ext_0.pdf}
+\includegraphics[height=2in]{N116_ext_2000.pdf}\\
+\includegraphics[height=2in]{N116_ext_4000.pdf}
+\includegraphics[height=2in]{N116_ext_6500.pdf}
+  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a).
+The background color indicates the magnitude of fluid pressure.
+From dark red to dark blue, it represents the the pressure varies from high to low values.
+The color bar is valid for all panels.
+Streamlines are plotted in purple.
+The insets show the results produced from using continuum model that the streamlines have perfect agreements with the present results.
+  }
+    \label{figure10}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
+\end{center} 
+  \caption{Trajectories of different setups in two-vesicle in an extensional flow where the centroids of two Janus-vesicle are plotted as blue dots.
+(i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii)
+  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure9} presents the numerical results from the case (iii) and a
+  consistent flow rate is $\chi = 0.005$ for all cases.}
+    \label{figure11}
+\end{figure}
+
+\subsubsection{Extensional Flow}
+
+With a similar setup in the case of two Janus-vesicles in a shear flow, we use the same two pre-relaxed $58$-body Janus-vesicles to perform the simulations when the flow type is an extensional flow with flow rate $\chi=0.005$.
+This extensional flow is stretching along the $y$ direction and squeezing in $x$ direction.
+Figure~\ref{figure10} shows one set of numerical results when the centroids of two bodies are placed at
+$(-10,-0.1)$ and $(10,0.1)$. With this setup, we can make sure that two Janus-vesicles will separate along 
+$y$-direction eventually from empirical tests.
+Panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
+Since two bilayers are close enough from the beginning of the run, two vesicles are first pushed toward each other then separate along the streamlines.
+The short range repulsion plays an important role to avoid structure collisions and this result can be compared with some findings in continuum modeling simulations.
+The pressure plots in Figure~\ref{figure8} provide a realistic result where the pressure is much higher in the gap between two nearby vesicles.
+
+Figure~\ref{figure11} provides simulation results when the center-of-mass positions are placed differently.
+One can notice that when two centroids are placed on the same horizontal level, two Janus-vesicles reach
+an equilibrium state without separation as shown in case (i).
+If only one centroid is placed above the $x$-axis, for instance, case (ii), two Janus-vesicle move together toward the upward.
+This is the consequence when the adhesive effect beats the flow strength.
+Case (iii) is same as the case shown in Figure~\ref{figure10}.
+Finally, case (iv) has a larger initial separation in $y$-direction and two Janus-vesicle moves much faster toward
+$\pm y$-directions.
+
+%may need to add more here
+
+%\todo[inline]{Make figure of the paths of the two centroids....}
+
+\section{\label{conclusion}Conclusion}
+
+\begin{acknowledgments}
+%We would like to acknowledge 
+\end{acknowledgments}
+
+\appendix
+
+\section{Appendices}
+\label{sec:appendixA}
+The stress ${\bf T}$ contains the gradient of the double layer
+potential. This introduces an inherent difficulty in evaluating stress
+on the boundary.  To overcome the difficulty of evaluation on
+$\Sigma_p$, for instance, we decompose $u$ into singular and nonsingular
+parts:
+\begin{equation}
+u = u_p + v_p
+\end{equation}
+where  
+\begin{equation}
+u_p(x) = \int_{\Sigma_p} \frac{\partial G(x,y)}{\partial \nnu} \eta(y) \,\dif S(y).
+\end{equation}
+It turns out that the contribution to the force and torque coming from the singular
+part vanishes. In particular, we will prove the identity
+\begin{equation}
+\label{eq:recipforcetorque}
+F_p + iG_p= \int_{\Sigma_p} \gamma ({\bf I}+i{\bf X})J_{p} \,\dif S
+\end{equation}
+where
+ \begin{equation}
+\label{eq:jumpstress1}
+J_{p} = 2\rho^{-1} \eta  v_p \nnu 
++ 2\rho \nabla \eta \cdot \tau_i(\nabla v_p \cdot \tau_i \nnu -  \nabla
+   v_p \cdot \nnu \tau_i).
+\end{equation}
+Here $\nnu$ is the unit normal, $\{\tau_i\}_{i=1}^2$ are orthonormal tangent vectors,
+and ${\bf X}$ is the skew symmetric matrix with axial vector $x$, i.e.
+\[X_{ij} = \varepsilon_{ikj}x_k,\quad {\bf X}v = x\times v\]
+where $\boldsymbol{\varepsilon}$ is the third-order alternating tensor.
+We employ the Einstein summation convention and use complex vectors to streamline the presentation, $i^2 = -1$.
+
+The benefit of using \eqref{eq:recipforcetorque} is that the integrand  is nonsingular.
+The density function $\eta$ has the same smoothness as the boundary data
+and $v_p$ is real-analytic in a neighborhood of $\Sigma_p$.
+
+To prove \eqref{eq:recipforcetorque}, write
+\begin{align*}
+  {\bf T}
+  &=
+  \sigma[u_p,u_p]
+  +(\sigma[u_p,v_p]
+  +\sigma[v_p,u_p])
+  +\sigma[v_p,v_p] \\
+  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
+\end{align*}
+where
+\[
+\sigma[u,v]
+= \rho^{-1} uv {\bf I} + \rho \nabla u \cdot \nabla v {\bf I} - 2 \rho \nabla u \otimes \nabla v.
+\]
+\begin{lemma}
+  \label{eq:stress_div_lemma}
+  \begin{equation}
+    \label{eq:decompdivfree}
+    \nabla \cdot {\bf T}_j = 0, \quad
+    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
+  \end{equation}
+\end{lemma}
+\begin{proof}
+  Observe that
+  \begin{align*}
+    (\nabla \cdot {\bf T})_j &=
+    \nabla_k   T_{jk} \\
+    &= \rho^{-1} 2u \nabla_j u + \rho(2\nabla_{kl}^2 u \nabla_l u  - 2 \nabla_{kj}^2 u \nabla_k u
+    - 2 \nabla_j u \nabla_{kk}^2 u )\\
+    &=2\rho^{-1}(-\rho^2 \Delta u + u)\nabla_k u .
+  \end{align*}
+  Since $-\rho^2 \Delta u + u = 0$, we have $\nabla \cdot {\bf T} = 0$.
+  Furthermore,
+  \begin{align*}
+    (\nabla \cdot (x\times {\bf T} ))_j
+    &= (\nabla \cdot ({\bf X} {\bf T} ))_j
+    = \nabla_k (X_{jl} T_{lk})
+    = \nabla_k (\epsilon_{jml}x_m T_{lk})\\
+    &= \varepsilon_{jml} T_{lm} + \varepsilon_{jml}x_m \nabla_k T_{lk}\\
+    &= (\boldsymbol{\varepsilon}:{\bf T} + {\bf x} \times \nabla \cdot {\bf T})_j.
+  \end{align*}
+  Since ${\bf T}$ is symmetric $\boldsymbol{\varepsilon}:{\bf T} = {\bf 0}$, and we get
+  $\nabla \cdot (x \times {\bf T}) = 0$ as well.
+
+  The functions $u_p$ and $v_p$ also solve the equation $-\rho^2 \Delta u + u = 0$.  Thus
+  \eqref{eq:decompdivfree} holds for $j = 1, 3$. Finally,
+  \eqref{eq:decompdivfree} holds for $j = 2$ because
+  ${\bf T}_2 = {\bf T} - {\bf T}_1 - {\bf T}_3$.
+\end{proof}
+
+Using Lemma \ref{eq:stress_div_lemma}, we will establish that
+\begin{equation}
+  \label{eq:prejump}
+  F_p + i G_p = \gamma \int_{\Sigma_p}  ({\bf U}_2\nnu)^+ - ({\bf
+  U}_2\nnu)^-\,\dif S
+\end{equation}
+where ${\bf U}_j = ({\bf I} + i {\bf X}){\bf T}_j$ for $j = 1, 2, 3.$
+The stress ${\bf U}_2$ has a jump discontinuity at $\Sigma_p.$
+The plus and minus superscripts denote
+the limit taken along points in $U_p^c$ and along points in $U_p$
+respectively.
+${\bf U}_1$ and ${\bf U}_3$ are real-analytic in a neighborhood of $\overline{U_p}$
+and have no jump-discontinuity at $\Sigma_p$.
+To derive \eqref{eq:prejump}, we expand
+\begin{align*}
+  F_p + i G_p
+  &= \gamma \int_{\Sigma_p} {\bf T} \nnu + ix \times {\bf T} \nnu \,\dif S \\
+  &= \gamma \int_{\Sigma_p}  {\bf U}_1\nnu  + ({\bf U}_2\nnu)^+ + {\bf
+  U}_3\nnu\,\dif S
+\end{align*}
+The function $u_p$ is real-analytic and
+$\nabla \cdot {\bf U}_1 = 0$ throughout $\mathbb{R}^n \setminus U_p$.
+By the divergence theorem, we get
+\begin{equation*}
+  \int_{\Sigma_p}  {\bf U}_1 \nnu\,\dif S
+  = \int_{\mathbb{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
+\end{equation*}
+Next, $v_p$ is real-analytic and
+$\nabla \cdot {\bf U}_3 = 0$ in $U_p$. Therefore
+\begin{equation*}
+  \int_{\Sigma_p}  {\bf U}_3 \nnu\,\dif S
+  = -\int_{U_p} \nabla \cdot {\bf U}_3 \,dx = 0.
+\end{equation*}
+Finally, $\nabla \cdot {\bf U}_2= 0$ in $U_p$. This gives
+\[
+0 = -\int_{U_p} \nabla \cdot {\bf U}_2 \,dx = \int_{\Sigma_p}  ({\bf
+U}_2 \nnu)^-\,\dif S.
+\]
+Combining the last four equations give \eqref{eq:prejump}.
+
+\begin{proof}[Proof of \eqref{eq:recipforcetorque}]
+  The main ingredients of the proof are the jump relations
+  for $u_p$. For $x_0 \in \Sigma_p$,
+  \begin{enumerate}
+  \item $ \lim_{x \to x_0^\pm } u_p(x) = \pm\frac{1}{2}\eta(x_0) + (D\eta)(x_0)$
+  \item $ \lim_{x \to x_0^+ } (\nabla u_p \cdot \nnu) (x) = \lim_{x \to
+    x_0^-} (\nabla u \cdot \nnu)(x)$
+  \end{enumerate}
+  Furthermore,
+  combining (i) and (ii) gives
+  \begin{align*}
+    \nabla u_p^+ - \nabla u_p^-
+    &= \nabla (u_p^+ - u_p^-) \cdot t_i t_i +  (\nabla  u_p^+\cdot
+    \nnu  - \nabla u_p^- \cdot \nnu) \nnu\\
+    &= \nabla \eta \cdot \tau_i \tau_i
+  \end{align*}
+  where $\{\tau_i\}_{i=1}^n$ are an orthonormal tangent vectors.
+  We can use these relationships to derive an expression for the jump in
+  normal stress.
+  \begin{align*}
+    &({\bf T}_2\nnu)^+ - ({\bf T}_2\nnu)^-
+    \\
+    &= 2\rho^{-1} u_p^+v_p \nnu + 2\rho \nabla u_p^+ \cdot \nabla v_p
+    \nnu
+    - 2 \rho \nabla u_p^+  \nabla v_p \cdot \nnu
+    - 2 \rho \nabla v_p  \nabla u_p^+ \cdot \nnu\\
+    &-2\rho^{-1} u_p^-v_p \nnu - 2\rho \nabla u_p^- \cdot \nabla v_p \nnu
+    + 2 \rho \nabla u_p^-  \nabla v_p \cdot \nnu
+    + 2 \rho \nabla v_p  \nabla u_p^- \cdot \nnu\\
+    &= 2\rho^{-1} \eta v_p \nnu + 2\rho \nabla \eta \cdot \tau_i \tau_i
+    \cdot \nabla v_p \nnu
+    - 2\rho \nabla \eta \cdot \tau_i \tau_i \nabla v_p \cdot \nnu + 0\\
+    &= J_p.
+  \end{align*}
+
+  Applying the above relations to the integrand of \eqref{eq:prejump} yields
+  \[
+  ({\bf U}_2\nnu)^+ - ({\bf U}_2\nnu)^-
+  =
+  ({\bf I} + i {\bf X})(({\bf T}_2\nnu)^+ - ({\bf T}_2\nnu)^-)
+  = ({\bf I} + i {\bf X})J_p
+  \]
+  This completes the proof of \eqref{eq:recipforcetorque}.
+\end{proof}
+
+\bibliographystyle{jfm}
+\bibliography{reference}% Produces the bibliography via BibTeX.
+
+%\bibliographystyle{jfm}
+%\bibliography{jfm}
+%Use of the above commands will create a bibliography using the .bib file. Shown below is a bibliography built from individual items.
+
+%\bibliography{jfm2esam}
+
+%\begin{thebibliography}{99}
+%
+%\expandafter\ifx\csname natexlab\endcsname\relax
+%\def\natexlab#1{#1}\fi
+%\expandafter\ifx\csname selectlanguage\endcsname\relax
+%\def\selectlanguage#1{\relax}\fi
+%
+%\bibitem[Batchelor (1971)]{Batchelor59}
+%{\sc Batchelor, G.K.} 1971 {Small-scale variation of convected quantities like temperature in turbulent fluid part1, general discussion and the case of small conductivity}, {\it J.
+Fluid Mech.}, {\bf 5}, pp.
+3-113-133.
+%
+%\bibitem [Bouguet (2008)]{Bouguet01}
+%{\sc Bouguet, J.-Y} 2008 Camera Calibration Toolbox for Matlab {\url{http://www.vision.caltech.edu/bouguetj/calib_doc/}}.
+%
+% \bibitem[Briukhanovetal et al (1967)] {Briukhanovetal1967}
+%{\sc Briukhanov, A. V.,   Grigorian, S. S., Miagkov,  S. M., Plam, M. Y.,   I. E. Shurova, I. E.,   Eglit, M. E. and Yakimov, Y. L.} 1967
+%{On some new approaches to the dynamics of snow avalanches},
+%{\it Physics of Snow and Ice,  Proceedings of the International Conference on Low Temperature Science}
+%{Vol 1} pp. 1221--1241 {Institute of Low Temperature Science, Hokkaido University, Sapporo, Hokkaido, Japan}.
+%
+%\bibitem[Brownell (2004)]{Brownell04}
+% {\sc Brownell,  C.J.  and Su,  L.K.} 2004  {Planar measurements of differential diffusion in turbulent jets}, {\it AIAA Paper},  pp. 2004-2335.
+%
+%\bibitem[Brownell and Su (2007)] {Brownell07}
+%  {\sc Brownell, C.J. and  Su, L.K.} 2007 {Scale relations and spatial spectra in a differentially diffusing jet}, {\it AIAA Paper}, pp 2007-1314.
+%
+%\bibitem [Dennis (1985)] {Dennis85}
+% {\sc  Dennis, S.C.R.} 1985 {Compact explicit finite difference approximations to the Navier--Stokes equation},  { In \it Ninth Intl Conf.
+on Numerical Methods in Fluid Dynamics},  {ed Soubbaramayer and J.P.
+Boujot},  {Vol 218}, {\it Lecture Notes in Physics}, pp.
+23-51.
+Springer.
+%
+%\bibitem [Edwards et al. (2017)]{EdwardsVirouletKokelaarGray2017}
+%{\sc Edwards, A.
+N., Viroulet, S., Kokelaar, B.
+P.
+and Gray, J.
+M.
+N.
+T.} 2017 Formation of levees, troughs and elevated channels by avalanches on erodible slopes {\it J.
+Fluid Mech.}, {\bf 823}, pp.
+278-315.
+%
+%\bibitem[Hwang et al (1970)] {Hwang70}
+% {\sc Hwang,  L.-S.  and  Tuck, E.O.} 1970 On the oscillations of harbours of arbitrary shape {\it J.~Fluid Mech.}, {\bf42}, pp 447-464.
+%
+%\bibitem[Josep and Saut (1990)] {JosephSaut1990}
+% {\sc Joseph, Daniel D.
+and Saut, Jean Claude} 1990 Short-wave instabilities and ill-posed initial-value problems {\it Theoretical and Computational Fluid Dynamics}, {\bf 1},  pp.191--227,  {\url{http://dx.doi.org/10.1007/BF00418002}}.
+%
+%\bibitem[Worster (1992)] {Worster92}
+%{ \sc  Worster, M.G.} 1992 The dynamics of mushy layers {\it Interactive dynamics of convection and solidification},
+%{(ed. S.H. Davis and H.E. Huppert and W. Muller and M.G. Worster)}, pp. 113--138 {Kluwer}.
+%
+%\bibitem[Koch(1983)] {Koch83}
+%{\sc Koch, W.} 1983 Resonant acoustic frequencies of flat plate cascades {\it J.~Sound Vib.}, {\bf 88}, pp. 233-242.
+%
+%\bibitem[Lee(1971)] {Lee71}
+%{\sc Lee,  J.-J.}  1971 Wave-induced oscillations in harbours of arbitrary geometry {\it J.~Fluid Mech.}, {\bf 45}, pp. 375-394.
+%
+%\bibitem[Linton and  Evans (1992)] {Linton92}
+% {\sc  Linton, C.M. and  Evans, D.V.} 1992 The radiation and scattering of surface waves by a vertical circular cylinder in a channel {\it Phil.\ Trans.\ R. Soc.\ Lond.}, {\bf 338}, pp. 325-357.
+%
+%\bibitem [Martin(1980] {Martin80}
+% {\sc  Martin, P.A.} 1980 On the null-field equations for the exterior problems of acoustics {\it Q.~J. Mech.\ Appl.\ Maths},{\bf 33}, pp. 385--396.
+%
+%\bibitem [Rogallo(1981)] {Rogallo81}
+% {\sc Rogallo,  R.S.} 1981 Numerical experiments in homogeneous turbulence  { {\it Tech. Rep.} 81835}  {NASA Tech.\ Mem}.
+%
+%\bibitem[Ursell(1950)] {Ursell50}
+%{\sc  Ursell, F.} 1950 Surface waves on deep water in the presence of a submerged cylinder i {\it Proc.\ Camb.\ Phil.\ Soc.}, {\bf 46}, pp.141--152.
+%
+%\bibitem[Wijngaarden (1968)]{Wijngaarden68}
+%{\sc van Wijngaarden, L.} 1968 On the oscillations Near and at resonance in open pipes {\it J.~Engng Maths},{\bf 2}, pp. 225--240.
+%
+%\bibitem[Miller (1991)]{Miller91}
+%{ \sc  Miller, P.L.} 1991 Mixing in high Schmidt number turbulent jets {school {PhD thesis}} {California Institute of Technology}.
+%
+%\end{thebibliography}
+
+%% End of file `jfm2esam.bib'.
+
+\end{document}
+>>>>>>> 792ef765a54d5589595223dd98b804c25f39cde8

### 2021-08-13 doc/main_jfm.tex
removed merge conflict command
fixing merge issues

--- 2021-08-12 doc/main_jfm.tex
@@
 \newcommand{\GG}{\mathbf{G}}
+\newcommand{\JJ}{\mathbf{J}}
 \newcommand{\nnu}{\boldsymbol{\nu}}
@@
 \newcommand{\xx}{\mathbf{x}}
+\newcommand{\XX}{\mathbf{X}}
 \newcommand{\uu}{\mathbf{u}}
@@
 \section{\label{intro}Introduction}
+Described by de Gennes as ``another animal in soft matter physics", the Janus particle (often a spherical particle with a hydrophobic and a hydrophilic hemisphere) exhibits complex aggregate, clustering and self-assembly into meso- and macroscopic structures that are relevant to a wide range of applications in biology and bioengineering.
+Whether it is surface chemistry or polarity under an external field, the dynamics of Janus particles is inevitably the combination of long-range hydrodynamics interactions in the presence of short- and intermediate-range particle-particle interactions.
+Recently Fu {\it et al.} illustrated that the hydrophobic interactions between Janus particles in a viscous solvent can be used as a coarse-grained model to capture the mechanics of an elastic bilayer membrane of amphiphilic macromolecules such as lipids \cite{Fu2020_SIAM}.
+Depending on the total number of Janus particles and their geometry, in a viscous solvent, Janus particles are found to aggregate to form a micelle, a patch of bilayer membrane with open ends, and a self-enclosed bilayer membrane (a vesicle).
+Using a hybrid continuum model for the interactions between amphiphilic particles in a viscous solvent and formulating it in a boundary integral formulation, Fu {\it et al.} showed that the membrane granularity during fusion and fission of bilayers can be accurately captured.
+%This boundary integral formulation has inspired more recent work
+
+In molecular dynamics (MD) simulations, the lipid bilayer membranes are often approximated by an implicit solvent coarse-grained model for lipids (as in the Martini code), where their hydrodynamic interactions are simplified by an implicit solvent.
+The long-range hydrodynamic interactions and the induced long-range lipid interactions can be captured by combining the Dry Martini with a lattice Boltzmann MD \cite{Brandner2019_SciRep}.
+Brandner {\it et al.} used this methodology to simulate the hydrodynamics of a nano-sized vesicle under a shear flow, and reproduced the well-know vesicle hydrodynamics  such as tank-treading, tumbling and inter-leaflet slippage (reported from simulations of the Helfrich-type continuum model).
+
+In this work we extend the hybrid continuum model in \cite{Fu2020_SIAM} for the Janus suspension to incorporate the collective hydrodynamics of a Janus suspension under various flows: a linear shear flow, an elongation flow, and a Poiseuille flow.
+We demonstrate that a vesicle made of Janus particles does behave like a vesicle in these flowing conditions.
+Furthermore we also show that the hybrid continuum model allows us to investigate the inter-leaflet slippage and rupture of a bilayer membrane due to an imposed flow.
+
+This paper is organized as follows.
+In \S~\ref{sec:governing_eqs} we present the formulation for the Janus particles in a viscous fluid in the zero-Reynolds number regime.
+In \S~\ref{sec:IEM} we extend the hybrid continuum model for a Janus suspension to include the effects of a far-field flow via the mobility problem formulation.
+In \S~\ref{validation} we present validation of our model, and in \S~\ref{results} we present simulation results for a vesicle of Janus bilayer membrane under various flowing conditions.
+Finally we provide discussion and outlook for future directions in \S~\ref{conclusion}.~
 
@@
   \label{eqn:force}
-  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, ds = \mathbf{0},
+  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
   && i=1,\ldots,N_b,\\
@@
   T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
-    (\ssigma \cdot \nnu_i) \, ds = 0, \qquad && i=1,\ldots,N_b,
+    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
 \end{alignat}
@@
   \label{eqn:hydrophobicAttraction}
-  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, dS, 
+  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, \dif s, 
     \quad 
-  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) dS,
+  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) \dif s,
 \end{align}
@@
 = \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
-  u|^2 \mathbf{I} - \nabla u\otimes \nabla u\right)
+  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
 \end{align}
@@
   u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
-    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, ds_\yy,
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
     \quad \xx \in \Omega,
@@
     \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
-    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, ds_\yy,
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
     \quad \xx \in \bd\Omega,
@@
 potential~\eqref{eqn:HAP_DLP} must be computed on the boundary of each
-particle. In Appendix~\ref{sec:appendixA}, we show that the force and
+particle. In Section~\ref{subsec:calculating_force}, we show that the force and
 torque calculations can be expressed in terms of integral that are
@@
     \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
-    \eeta(\yy) \, ds_\yy,
+    \eeta(\yy) \, \dif s_\yy,
 \end{align}
@@
   \label{eqn:mobility1}
-  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, ds &= {\bf 0}, 
+  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
   &&i = 1,\ldots,N_b, \\
   \label{eqn:mobility2}
-  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu ds &= 0,
+  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu \, \dif s &= 0,
   &&i = 1,\ldots,N_b.
@@
 single- and double-layer potentials~\cite{cor-vee2018}.
+
+\subsection{Calculating the Hydrophobic Force}
+\label{subsec:calculating_force}
+The stress \eqref{eq:stress} contains
+contains the gradient of the double-layer potential \eqref{eqn:HAP_DLP},
+making it difficult to evaluate
+the forces and torques \eqref{eqn:hydrophobicAttraction}.
+The identities \eqref{eq:recipforcetorque}
+make it possible to evaluate the forces and torques
+without specialized quadrature methods.
+
+Consider the particle
+$\Gamma_i$ indexed by $i$
+and decompose $u$ as follows: 
+\begin{equation}
+u = u_i + v_i
+\end{equation}
+where  
+\begin{equation}
+    u_i(\xx) = \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
+    \quad \xx \in \Omega.
+\end{equation}
+That is, $u_i$ is the double-layer potential for the restriction of $\sigma$ to $\Gamma_i$.  Let $\FF_i$ and $T_i$ be as in \eqref{eqn:hydrophobicAttraction}. We prove that 
+\begin{equation}
+\label{eq:recipforcetorque}
+\FF_i= \int_{\Gamma_i} \JJ_i \,\dif s,\quad
+T_i= \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s
+\end{equation}
+where
+ \begin{equation}
+\label{eq:jumpstress1}
+\JJ_{i} = 2\gamma\left[\rho^{-1} u v_i \nnu 
++ \rho \nabla u \cdot \tau (\nabla v_i \cdot \tau \nnu -  \nabla
+   v_i \cdot \nnu \tau)\right].
+\end{equation}
+Here $\nnu$ is the unit normal and $\tau$ is a unit tangent vector.
+Observe that  $u$ and $\nabla u \cdot \tau$ come from the boundary data $f_i$ \eqref{SLbc} and are smooth. The functions $v_i$ and $\nabla v_i$
+come from double-layer integrals that are smooth on $\Gamma_i$.
+
+To prove \eqref{eq:recipforcetorque},
+let \begin{align*}
+  {\bf T}
+  &=
+  \sigma[u_i,u_i]
+  +(\sigma[u_i,v_i]
+  +\sigma[v_i,u_i])
+  +\sigma[v_i,v_i] \\
+  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
+\end{align*}
+where we have introduced the notation
+\[
+\sigma[u,v]
+= \rho^{-1} uv {\bf I} + \rho \nabla u \cdot \nabla v {\bf I} - 2 \rho \nabla u \nabla v^T.
+\]
+Using the fact that $u$, $u_i$, and $v_i$ solve the equation
+$-\rho^2 \Delta u + u = 0$, and that ${\bf T}$ is symmetric,
+it is straightforward to show that 
+  \begin{equation}
+    \label{eq:decompdivfree}
+    \nabla \cdot {\bf T}_j = 0, \quad
+    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
+  \end{equation}
+
+\begin{lemma}
+  \label{eq:stress_div_lemma}
+  \begin{equation}
+    \label{eq:decompdivfree}
+    \nabla \cdot {\bf T}_j = 0, \quad
+    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
+  \end{equation}
+\end{lemma}
+\begin{proof}
+  The function $u$ solves $-\rho^2 \Delta u + u = 0$. Using the summation convention, 
+  \begin{align*}
+    (\nabla \cdot {\bf T})_j &=
+    \nabla_k   T_{jk} \\
+    &= \rho^{-1} 2u \nabla_j u + \rho(2\nabla_{kl}^2 u \nabla_l u  - 2 \nabla_{kj}^2 u \nabla_k u
+    - 2 \nabla_j u \nabla_{kk}^2 u )\\
+    &=2\rho^{-1}(-\rho^2 \Delta u + u)\nabla_k u = 0.
+  \end{align*}
+Moreover, 
+  \begin{align*}
+    (\nabla \cdot (\xx \times {\bf T} ))_j
+    &= \nabla_k (\epsilon_{jml}x_m T_{lk})\\
+    &= \varepsilon_{jml} T_{lm} + \varepsilon_{jml}x_m \nabla_k T_{lk}\\
+    &= (\boldsymbol{\varepsilon}:{\bf T} + {\bf x} \times \nabla \cdot {\bf T})_j.
+  \end{align*}
+  where $\varepsilon_{jml}$ is the alternating tensor. 
+  Since ${\bf T}$ is symmetric $\boldsymbol{\varepsilon}:{\bf T} = {\bf 0}$, and we get
+  $\nabla \cdot (x \times {\bf T}) = 0$ as well.
+
+  The functions $u_p$ and $v_p$ also solve the equation $-\rho^2 \Delta u + u = 0$.  Thus
+  \eqref{eq:decompdivfree} holds for $j = 1, 3$. Finally,
+  \eqref{eq:decompdivfree} holds for $j = 2$ because
+  ${\bf T}_2 = {\bf T} - {\bf T}_1 - {\bf T}_3$.
+\end{proof}
+
+Using Lemma \ref{eq:stress_div_lemma}, we will establish that
+\begin{equation}
+  \label{eq:prejump}
+  F_p + i G_p = \gamma \int_{\Sigma_p}  ({\bf U}_2\nnu)^+ - ({\bf
+  U}_2\nnu)^-\,\dif S
+\end{equation}
+where ${\bf U}_j = ({\bf I} + i {\bf X}){\bf T}_j$ for $j = 1, 2, 3.$
+The stress ${\bf U}_2$ has a jump discontinuity at $\Sigma_p.$
+The plus and minus superscripts denote
+the limit taken along points in $U_p^c$ and along points in $U_p$
+respectively.
+${\bf U}_1$ and ${\bf U}_3$ are real-analytic in a neighborhood of $\overline{U_p}$
+and have no jump-discontinuity at $\Sigma_p$.
+To derive \eqref{eq:prejump}, we expand
+\begin{align*}
+  F_p + i G_p
+  &= \gamma \int_{\Sigma_p} {\bf T} \nnu + ix \times {\bf T} \nnu \,\dif S \\
+  &= \gamma \int_{\Sigma_p}  {\bf U}_1\nnu  + ({\bf U}_2\nnu)^+ + {\bf
+  U}_3\nnu\,\dif S
+\end{align*}
+The function $u_p$ is real-analytic and
+$\nabla \cdot {\bf U}_1 = 0$ throughout $\mathbb{R}^n \setminus U_p$.
+By the divergence theorem, we get
+\begin{equation*}
+  \int_{\Sigma_p}  {\bf U}_1 \nnu\,\dif S
+  = \int_{\mathbb{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
+\end{equation*}
+Next, $v_p$ is real-analytic and
+$\nabla \cdot {\bf U}_3 = 0$ in $U_p$. Therefore
+\begin{equation*}
+  \int_{\Sigma_p}  {\bf U}_3 \nnu\,\dif S
+  = -\int_{U_p} \nabla \cdot {\bf U}_3 \,dx = 0.
+\end{equation*}
+Finally, $\nabla \cdot {\bf U}_2= 0$ in $U_p$. This gives
+\[
+0 = -\int_{U_p} \nabla \cdot {\bf U}_2 \,dx = \int_{\Sigma_p}  ({\bf
+U}_2 \nnu)^-\,\dif S.
+\]
+Combining the last four equations give \eqref{eq:prejump}.
+
+\begin{proof}[Proof of \eqref{eq:recipforcetorque}]
+  The main ingredients of the proof are the jump relations
+  for $u_p$. For $x_0 \in \Sigma_p$,
+  \begin{enumerate}
+  \item $ \lim_{x \to x_0^\pm } u_p(x) = \pm\frac{1}{2}\eta(x_0) + (D\eta)(x_0)$
+  \item $ \lim_{x \to x_0^+ } (\nabla u_p \cdot \nnu) (x) = \lim_{x \to
+    x_0^-} (\nabla u \cdot \nnu)(x)$
+  \end{enumerate}
+  Furthermore,
+  combining (i) and (ii) gives
+  \begin{align*}
+    \nabla u_p^+ - \nabla u_p^-
+    &= \nabla (u_p^+ - u_p^-) \cdot t_i t_i +  (\nabla  u_p^+\cdot
+    \nnu  - \nabla u_p^- \cdot \nnu) \nnu\\
+    &= \nabla \eta \cdot \tau_i \tau_i
+  \end{align*}
+  where $\{\tau_i\}_{i=1}^n$ are an orthonormal tangent vectors.
+  We can use these relationships to derive an expression for the jump in
+  normal stress.
+  \begin{align*}
+    &({\bf T}_2\nnu)^+ - ({\bf T}_2\nnu)^-
+    \\
+    &= 2\rho^{-1} u_p^+v_p \nnu + 2\rho \nabla u_p^+ \cdot \nabla v_p
+    \nnu
+    - 2 \rho \nabla u_p^+  \nabla v_p \cdot \nnu
+    - 2 \rho \nabla v_p  \nabla u_p^+ \cdot \nnu\\
+    &-2\rho^{-1} u_p^-v_p \nnu - 2\rho \nabla u_p^- \cdot \nabla v_p \nnu
+    + 2 \rho \nabla u_p^-  \nabla v_p \cdot \nnu
+    + 2 \rho \nabla v_p  \nabla u_p^- \cdot \nnu\\
+    &= 2\rho^{-1} \eta v_p \nnu + 2\rho \nabla \eta \cdot \tau_i \tau_i
+    \cdot \nabla v_p \nnu
+    - 2\rho \nabla \eta \cdot \tau_i \tau_i \nabla v_p \cdot \nnu + 0\\
+    &= J_p.
+  \end{align*}
+
+  Applying the above relations to the integrand of \eqref{eq:prejump} yields
+  \[
+  ({\bf U}_2\nnu)^+ - ({\bf U}_2\nnu)^-
+  =
+  ({\bf I} + i {\bf X})(({\bf T}_2\nnu)^+ - ({\bf T}_2\nnu)^-)
+  = ({\bf I} + i {\bf X})J_p
+  \]
+  This completes the proof of \eqref{eq:recipforcetorque}.
+\end{proof}
 
@@
 
-\subsection{Self-Assembly and Relaxtion}
+\subsection{Self-Assembly and Relaxation}
 
@@
 
-\todo[inline]{Introduce dimensionless shear rate here (and check the numbers)}
+%\todo[inline]{Introduce dimensionless shear rate here (and check the numbers)}
 
@@
 \begin{equation}
-b = \frac{F_f}{\int_{\Sigma_M} R \dot\theta dS},
+b = \frac{F_f}{\int_{\Sigma_M} R \dot\theta \dif s},
 \end{equation}
@@
 
-\todo[inline]{Make figure of the paths of the two centroids....}
+%\todo[inline]{Make figure of the paths of the two centroids....}
 
@@
 \label{sec:appendixA}
-The stress ${\bf T}$ contains the gradient of the double layer
-potential. This introduces an inherent difficulty in evaluating stress
-on the boundary.  To overcome the difficulty of evaluation on
-$\Sigma_p$, for instance, we decompose $u$ into singular and nonsingular
-parts:
-\begin{equation}
-u = u_p + v_p
-\end{equation}
-where  
-\begin{equation}
-u_p(x) = \int_{\Sigma_p} \frac{\partial G(x,y)}{\partial \nnu} \eta(y) \,\dif S(y).
-\end{equation}
-It turns out that the contribution to the force and torque coming from the singular
-part vanishes. In particular, we will prove the identity
-\begin{equation}
-\label{eq:recipforcetorque}
-F_p + iG_p= \int_{\Sigma_p} \gamma ({\bf I}+i{\bf X})J_{p} \,\dif S
-\end{equation}
-where
- \begin{equation}
-\label{eq:jumpstress1}
-J_{p} = 2\rho^{-1} \eta  v_p \nnu 
-+ 2\rho \nabla \eta \cdot \tau_i(\nabla v_p \cdot \tau_i \nnu -  \nabla
-   v_p \cdot \nnu \tau_i).
-\end{equation}
-Here $\nnu$ is the unit normal, $\{\tau_i\}_{i=1}^2$ are orthonormal tangent vectors,
-and ${\bf X}$ is the skew symmetric matrix with axial vector $x$, i.e.
-\[X_{ij} = \varepsilon_{ikj}x_k,\quad {\bf X}v = x\times v\]
-where $\boldsymbol{\varepsilon}$ is the third-order alternating tensor.
-We employ the Einstein summation convention and use complex vectors to streamline the presentation, $i^2 = -1$.
-
-The benefit of using \eqref{eq:recipforcetorque} is that the integrand  is nonsingular.
-The density function $\eta$ has the same smoothness as the boundary data
-and $v_p$ is real-analytic in a neighborhood of $\Sigma_p$.
-
-To prove \eqref{eq:recipforcetorque}, write
-\begin{align*}
-  {\bf T}
-  &=
-  \sigma[u_p,u_p]
-  +(\sigma[u_p,v_p]
-  +\sigma[v_p,u_p])
-  +\sigma[v_p,v_p] \\
-  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
-\end{align*}
-where
-\[
-\sigma[u,v]
-= \rho^{-1} uv {\bf I} + \rho \nabla u \cdot \nabla v {\bf I} - 2 \rho \nabla u \otimes \nabla v.
-\]
-\begin{lemma}
-  \label{eq:stress_div_lemma}
-  \begin{equation}
-    \label{eq:decompdivfree}
-    \nabla \cdot {\bf T}_j = 0, \quad
-    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
-  \end{equation}
-\end{lemma}
-\begin{proof}
-  Observe that
-  \begin{align*}
-    (\nabla \cdot {\bf T})_j &=
-    \nabla_k   T_{jk} \\
-    &= \rho^{-1} 2u \nabla_j u + \rho(2\nabla_{kl}^2 u \nabla_l u  - 2 \nabla_{kj}^2 u \nabla_k u
-    - 2 \nabla_j u \nabla_{kk}^2 u )\\
-    &=2\rho^{-1}(-\rho^2 \Delta u + u)\nabla_k u .
-  \end{align*}
-  Since $-\rho^2 \Delta u + u = 0$, we have $\nabla \cdot {\bf T} = 0$.
-  Furthermore,
-  \begin{align*}
-    (\nabla \cdot (x\times {\bf T} ))_j
-    &= (\nabla \cdot ({\bf X} {\bf T} ))_j
-    = \nabla_k (X_{jl} T_{lk})
-    = \nabla_k (\epsilon_{jml}x_m T_{lk})\\
-    &= \varepsilon_{jml} T_{lm} + \varepsilon_{jml}x_m \nabla_k T_{lk}\\
-    &= (\boldsymbol{\varepsilon}:{\bf T} + {\bf x} \times \nabla \cdot {\bf T})_j.
-  \end{align*}
-  Since ${\bf T}$ is symmetric $\boldsymbol{\varepsilon}:{\bf T} = {\bf 0}$, and we get
-  $\nabla \cdot (x \times {\bf T}) = 0$ as well.
-
-  The functions $u_p$ and $v_p$ also solve the equation $-\rho^2 \Delta u + u = 0$.  Thus
-  \eqref{eq:decompdivfree} holds for $j = 1, 3$. Finally,
-  \eqref{eq:decompdivfree} holds for $j = 2$ because
-  ${\bf T}_2 = {\bf T} - {\bf T}_1 - {\bf T}_3$.
-\end{proof}
-
-Using Lemma \ref{eq:stress_div_lemma}, we will establish that
-\begin{equation}
-  \label{eq:prejump}
-  F_p + i G_p = \gamma \int_{\Sigma_p}  ({\bf U}_2\nnu)^+ - ({\bf
-  U}_2\nnu)^-\,\dif S
-\end{equation}
-where ${\bf U}_j = ({\bf I} + i {\bf X}){\bf T}_j$ for $j = 1, 2, 3.$
-The stress ${\bf U}_2$ has a jump discontinuity at $\Sigma_p.$
-The plus and minus superscripts denote
-the limit taken along points in $U_p^c$ and along points in $U_p$
-respectively.
-${\bf U}_1$ and ${\bf U}_3$ are real-analytic in a neighborhood of $\overline{U_p}$
-and have no jump-discontinuity at $\Sigma_p$.
-To derive \eqref{eq:prejump}, we expand
-\begin{align*}
-  F_p + i G_p
-  &= \gamma \int_{\Sigma_p} {\bf T} \nnu + ix \times {\bf T} \nnu \,\dif S \\
-  &= \gamma \int_{\Sigma_p}  {\bf U}_1\nnu  + ({\bf U}_2\nnu)^+ + {\bf
-  U}_3\nnu\,\dif S
-\end{align*}
-The function $u_p$ is real-analytic and
-$\nabla \cdot {\bf U}_1 = 0$ throughout $\mathbb{R}^n \setminus U_p$.
-By the divergence theorem, we get
-\begin{equation*}
-  \int_{\Sigma_p}  {\bf U}_1 \nnu\,\dif S
-  = \int_{\mathbb{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
-\end{equation*}
-Next, $v_p$ is real-analytic and
-$\nabla \cdot {\bf U}_3 = 0$ in $U_p$. Therefore
-\begin{equation*}
-  \int_{\Sigma_p}  {\bf U}_3 \nnu\,\dif S
-  = -\int_{U_p} \nabla \cdot {\bf U}_3 \,dx = 0.
-\end{equation*}
-Finally, $\nabla \cdot {\bf U}_2= 0$ in $U_p$. This gives
-\[
-0 = -\int_{U_p} \nabla \cdot {\bf U}_2 \,dx = \int_{\Sigma_p}  ({\bf
-U}_2 \nnu)^-\,\dif S.
-\]
-Combining the last four equations give \eqref{eq:prejump}.
-
-\begin{proof}[Proof of \eqref{eq:recipforcetorque}]
-  The main ingredients of the proof are the jump relations
-  for $u_p$. For $x_0 \in \Sigma_p$,
-  \begin{enumerate}
-  \item $ \lim_{x \to x_0^\pm } u_p(x) = \pm\frac{1}{2}\eta(x_0) + (D\eta)(x_0)$
-  \item $ \lim_{x \to x_0^+ } (\nabla u_p \cdot \nnu) (x) = \lim_{x \to
-    x_0^-} (\nabla u \cdot \nnu)(x)$
-  \end{enumerate}
-  Furthermore,
-  combining (i) and (ii) gives
-  \begin{align*}
-    \nabla u_p^+ - \nabla u_p^-
-    &= \nabla (u_p^+ - u_p^-) \cdot t_i t_i +  (\nabla  u_p^+\cdot
-    \nnu  - \nabla u_p^- \cdot \nnu) \nnu\\
-    &= \nabla \eta \cdot \tau_i \tau_i
-  \end{align*}
-  where $\{\tau_i\}_{i=1}^n$ are an orthonormal tangent vectors.
-  We can use these relationships to derive an expression for the jump in
-  normal stress.
-  \begin{align*}
-    &({\bf T}_2\nnu)^+ - ({\bf T}_2\nnu)^-
-    \\
-    &= 2\rho^{-1} u_p^+v_p \nnu + 2\rho \nabla u_p^+ \cdot \nabla v_p
-    \nnu
-    - 2 \rho \nabla u_p^+  \nabla v_p \cdot \nnu
-    - 2 \rho \nabla v_p  \nabla u_p^+ \cdot \nnu\\
-    &-2\rho^{-1} u_p^-v_p \nnu - 2\rho \nabla u_p^- \cdot \nabla v_p \nnu
-    + 2 \rho \nabla u_p^-  \nabla v_p \cdot \nnu
-    + 2 \rho \nabla v_p  \nabla u_p^- \cdot \nnu\\
-    &= 2\rho^{-1} \eta v_p \nnu + 2\rho \nabla \eta \cdot \tau_i \tau_i
-    \cdot \nabla v_p \nnu
-    - 2\rho \nabla \eta \cdot \tau_i \tau_i \nabla v_p \cdot \nnu + 0\\
-    &= J_p.
-  \end{align*}
-
-  Applying the above relations to the integrand of \eqref{eq:prejump} yields
-  \[
-  ({\bf U}_2\nnu)^+ - ({\bf U}_2\nnu)^-
-  =
-  ({\bf I} + i {\bf X})(({\bf T}_2\nnu)^+ - ({\bf T}_2\nnu)^-)
-  = ({\bf I} + i {\bf X})J_p
-  \]
-  This completes the proof of \eqref{eq:recipforcetorque}.
-\end{proof}
 

### 2021-08-14 doc/main_jfm.tex
small change
fix reference

@@
 Whether it is surface chemistry or polarity under an external field, the dynamics of Janus particles is inevitably the combination of long-range hydrodynamics interactions in the presence of short- and intermediate-range particle-particle interactions.
-Recently Fu {\it et al.} illustrated that the hydrophobic interactions between Janus particles in a viscous solvent can be used as a coarse-grained model to capture the mechanics of an elastic bilayer membrane of amphiphilic macromolecules such as lipids \cite{Fu2020_SIAM}.
+Recently Fu {\it et al.} illustrated that the hydrophobic interactions between Janus particles in a viscous solvent can be used as a coarse-grained model to capture the mechanics of an elastic bilayer membrane of amphiphilic macromolecules such as lipids \cite{Fu20}.
 Depending on the total number of Janus particles and their geometry, in a viscous solvent, Janus particles are found to aggregate to form a micelle, a patch of bilayer membrane with open ends, and a self-enclosed bilayer membrane (a vesicle).
@@
 In molecular dynamics (MD) simulations, the lipid bilayer membranes are often approximated by an implicit solvent coarse-grained model for lipids (as in the Martini code), where their hydrodynamic interactions are simplified by an implicit solvent.
-The long-range hydrodynamic interactions and the induced long-range lipid interactions can be captured by combining the Dry Martini with a lattice Boltzmann MD \cite{Brandner2019_SciRep}.
+The long-range hydrodynamic interactions and the induced long-range lipid interactions can be captured by combining the Dry Martini with a lattice Boltzmann MD \cite{Brandner2019}.
 Brandner {\it et al.} used this methodology to simulate the hydrodynamics of a nano-sized vesicle under a shear flow, and reproduced the well-know vesicle hydrodynamics  such as tank-treading, tumbling and inter-leaflet slippage (reported from simulations of the Helfrich-type continuum model).
 
-In this work we extend the hybrid continuum model in \cite{Fu2020_SIAM} for the Janus suspension to incorporate the collective hydrodynamics of a Janus suspension under various flows: a linear shear flow, an elongation flow, and a Poiseuille flow.
+In this work we extend the hybrid continuum model in \cite{Fu20} for the Janus suspension to incorporate the collective hydrodynamics of a Janus suspension under various flows: a linear shear flow, an elongation flow, and a Poiseuille flow.
 We demonstrate that a vesicle made of Janus particles does behave like a vesicle in these flowing conditions.
@@
 
-\section{Governing  Equations}
+\section{Governing  Equations\label{sec:governing_eqs}}
 \subsection{\label{mobility}Mobility Problem}
@@
 $\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
-$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
-$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
+%$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
+%$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
 $b$ (pN$\cdot$ns nm$^{-2}$)   & 1.11 & 1.56 & 1.37 & 1.47 & 1.43 & 1.51 & 1.76\\ 

### 2021-08-15 doc/main_jfm.tex
updates

@@
 \begin{equation}
-b = \frac{F_f}{\int_{\Sigma_M} R \dot\theta \dif s},
+b = \frac{\langle F_f\rangle}{\langle\int_{\Sigma_M} R \dot\theta \dif s\rangle},
 \end{equation}
@@
 The parameters are $v_{max} = 8.0$, $w=10$ and $R_0=8$.
-The inset of Figure~\ref{figure6} shows the trajectory of the mean position in $y$-direction which decreases toward $y=1$ for a period of time and starts to have an oscillatory motion.
+The inset of Figure~\ref{figure7} shows the trajectory of the mean position in $y$-direction which decreases toward $y=1$ for a period of time and starts to have an oscillatory motion.
 Moreover, the Janus-vesicle performs tank-treading during the simulation and red arrows in Figure~\ref{figure6} indicate a counterclockwise movement.
@@
 This matches the previous numerical tests in  \cite{Kaoui09} where a slipper-like shape occurs when the flow velocity is weak.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.8\textwidth]{slipper.eps}
+  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$.
+The configuration is the state when $t=10000$.
+Red arrows are directors of particle velocities.
+The inset shows the mean $y$-position over time.
+  }
+    \label{figure6}
+\end{figure}
 
@@
 With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
-Figure~\ref{figure7} shows a demonstration of a vesicle under a shear flow with shear rate $\chi=0.1$.
+Figure~\ref{figure8} shows a demonstration of a vesicle under a shear flow with shear rate $\chi=0.1$.
 An interesting phenomenon occurs in panels (c) and (d) where two separated bilayers move along the background shear flow symmetrically.
@@
   }
-    \label{figure7}
+    \label{figure8}
 \end{figure}
@@
   }
-    \label{figure8}
+    \label{figure9}
 \end{figure}
@@
 }
-    \label{figure9}
+    \label{figure10}
 \end{figure}
@@
 
-Figure~\ref{figure8} demonstrates the simulation results of two Janus-vesicles in a shear flow where the testing shear rate is $\chi=0.005$ and the flow is given by $\dot x = \chi y$.
+Figure~\ref{figure9} demonstrates the simulation results of two Janus-vesicles in a shear flow where the testing shear rate is $\chi=0.005$ and the flow is given by $\dot x = \chi y$.
 In panel (a), the starting frame, two center-of-mass positions are placed
@@
 In other words, the adhesive behavior will be absent when two vesicles are centered
-at a different level and are well separated in $y$-direction. Trajectories of a longer run of the simulation results are shown in Figure~\ref{figure9}.
+at a different level and are well separated in $y$-direction. Trajectories of a longer run of the simulation results are shown in Figure~\ref{figure10}.
 
@@
   }
-    \label{figure10}
+    \label{figure11}
 \end{figure}
@@
 (i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii)
-  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure9} presents the numerical results from the case (iii) and a
+  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure10} presents the numerical results from the case (iii) and a
   consistent flow rate is $\chi = 0.005$ for all cases.}
-    \label{figure11}
+    \label{figure12}
 \end{figure}
@@
 This extensional flow is stretching along the $y$ direction and squeezing in $x$ direction.
-Figure~\ref{figure10} shows one set of numerical results when the centroids of two bodies are placed at
+Figure~\ref{figure11} shows one set of numerical results when the centroids of two bodies are placed at
 $(-10,-0.1)$ and $(10,0.1)$. With this setup, we can make sure that two Janus-vesicles will separate along 
@@
 
-Figure~\ref{figure11} provides simulation results when the center-of-mass positions are placed differently.
+Figure~\ref{figure12} provides simulation results when the center-of-mass positions are placed differently.
 One can notice that when two centroids are placed on the same horizontal level, two Janus-vesicles reach
@@
 This is the consequence when the adhesive effect beats the flow strength.
-Case (iii) is same as the case shown in Figure~\ref{figure10}.
+Case (iii) is same as the case shown in Figure~\ref{figure11}.
 Finally, case (iv) has a larger initial separation in $y$-direction and two Janus-vesicle moves much faster toward

### 2021-08-16 doc/main_jfm.tex
token
finished section 3.3

@@
 \usepackage{todonotes}
+%
 
@@
 \newcommand{\nnu}{\boldsymbol{\nu}}
+\newcommand{\ttau}{\boldsymbol{\tau}}
 \newcommand{\ssigma}{\boldsymbol{\sigma}}
@@
 \subsection{\label{mobility}Mobility Problem}
-We consider a suspension of $N_b$ particles suspended in a
-two-dimensional unbounded domain. The boundary of each particle is
+We consider an $N_b$-many body collection of particles suspended in a
+two-dimensional unbounded domain $\Omega$. The boundary of each particle is
 denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
-\cdots \cup \Gamma_{N_b}$. Assuming the flow is Stokesian, the governing
+\cdots \cup \Gamma_{N_b}$ and $\nnu_i$ is the particle outward normal. 
+Assuming the flow is Stokesian, the governing
 equations are
@@
 where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
-\right)$ is the hydrodynamic stress tensor (pressure tensor). The
-process of finding the translational and angular velocities given a
+\right)$ is the hydrodynamic stress tensor (pressure tensor).
+The process of finding the translational and angular velocities given a
 force and torque is referred to as the mobility problem.
@@
 \end{alignat}
-where $f_i$ is a material label with $f_i = 0$ ($1$) representing
-hydrophilic (hydrophobic) portions of the surface, and $\rho$ is the
+where $f_i$ is a material label with $f_i = 0$, respectively $1$, representing
+hydrophilic, respectively hydrophobic, portions of the surface, and $\rho$ is the
 decay length of attraction. The forces and torques for this attraction
@@
 second-kind integral equation
-\begin{align}
+\begin{equation}
+\label{eq:SKIE}
   f(\xx) = \frac{1}{2}\sigma(\xx) + 
@@
     \quad \xx \in \bd\Omega,
-\end{align}
+\end{equation}
 the HAP double-layer potential~\eqref{eqn:HAP_DLP} satisfies the
@@
   \label{eqn:mobility2}
-  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu \, \dif s &= 0,
+  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu_i \, \dif s &= 0,
   &&i = 1,\ldots,N_b.
@@
 \label{subsec:calculating_force}
-The stress \eqref{eq:stress} contains
-contains the gradient of the double-layer potential \eqref{eqn:HAP_DLP},
-making it difficult to evaluate
-the forces and torques \eqref{eqn:hydrophobicAttraction}.
-The identities \eqref{eq:recipforcetorque}
-make it possible to evaluate the forces and torques
-without specialized quadrature methods.
-
-Consider the particle
-$\Gamma_i$ indexed by $i$
-and decompose $u$ as follows: 
-\begin{equation}
-u = u_i + v_i
+Once \eqref{eq:SKIE} has been solved and $\sigma$ determined,
+we can evaluate the integrals  \eqref{eqn:hydrophobicAttraction}. 
+These integrals involve the stress \eqref{eq:stress} which contains
+a singular integral for the gradient of the double-layer potential.   
+To avoid singular integrals, we use the alternative forms
+\begin{equation}
+\label{eq:recipforcetorque}
+\FF_i^{\text{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
+T_i^{\text{hydro}}    = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s
 \end{equation}
@@
  \begin{equation}
-    u_i(\xx) = \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
+\label{eq:jumpstress1}
+\JJ_{i} =2\gamma\rho^{-1} \sigma v_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dv_i }{ds} \nnu
+    - 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dv_i }{d\nu} \ttau.
+\end{equation}
+Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent  and arc length  derivative for $\Gamma_i$, respectively, 
+and
+\begin{equation}
+\label{eq:uidef}
+    v_i(\xx) = u(\xx) - \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
     K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
@@
 \end{equation}
-That is, $u_i$ is the double-layer potential for the restriction of $\sigma$ to $\Gamma_i$.  Let $\FF_i$ and $T_i$ be as in \eqref{eqn:hydrophobicAttraction}. We prove that 
-\begin{equation}
-\label{eq:recipforcetorque}
-\FF_i= \int_{\Gamma_i} \JJ_i \,\dif s,\quad
-T_i= \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s
-\end{equation}
-where
- \begin{equation}
-\label{eq:jumpstress1}
-\JJ_{i} = 2\gamma\left[\rho^{-1} u v_i \nnu 
-+ \rho \nabla u \cdot \tau (\nabla v_i \cdot \tau \nnu -  \nabla
-   v_i \cdot \nnu \tau)\right].
-\end{equation}
-Here $\nnu$ is the unit normal and $\tau$ is a unit tangent vector.
-Observe that  $u$ and $\nabla u \cdot \tau$ come from the boundary data $f_i$ \eqref{SLbc} and are smooth. The functions $v_i$ and $\nabla v_i$
-come from double-layer integrals that are smooth on $\Gamma_i$.
+The advantage in using \eqref{eq:jumpstress1} over \eqref{eq:stress} 
+is that components $\sigma$, $v_i$, $\frac{d\sigma}{ds}$, and  $\frac{dv_i}{ds}$ are all smooth.
 
@@
   &=
-  \sigma[u_i,u_i]
-  +(\sigma[u_i,v_i]
-  +\sigma[v_i,u_i])
-  +\sigma[v_i,v_i] \\
+    \mathbf{S}(u_i,u_i)
+  +(\mathbf{S}(u_i,v_i)
+  +\mathbf{S}(v_i,u_i))
+  +\mathbf{S}(v_i,v_i) \\
   &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
 \end{align*}
-where we have introduced the notation
-\[
-\sigma[u,v]
-= \rho^{-1} uv {\bf I} + \rho \nabla u \cdot \nabla v {\bf I} - 2 \rho \nabla u \nabla v^T.
-\]
-Using the fact that $u$, $u_i$, and $v_i$ solve the equation
-$-\rho^2 \Delta u + u = 0$, and that ${\bf T}$ is symmetric,
-it is straightforward to show that 
+where we introduce the bilinear form
+\begin{equation}
+\label{eq:Tsplit}
+\mathbf{S}(u,v)
+=  \gamma\rho^{-1} uv {\bf I} + \gamma\rho \nabla u \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla u \nabla v^T .
+\end{equation}
+Using the fact that $u$,  $u_i$, and $v_i$ solve the equation $-\rho^2 \Delta u + u = 0$,
+and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1, 2, 3$ are symmetric, it is straightforward to verify that 
   \begin{equation}
@@
     \nabla \cdot {\bf T}_j = 0, \quad
-    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
-  \end{equation}
-
+    \nabla \cdot ((\xx-\aa_i)^{\perp} \cdot {\bf T}_j) = 0, \quad j = 1, 2, 3.
+  \end{equation}
+
+%\begin{lemma}
+%  \label{eq:stress_div_lemma}
+%  \begin{equation}
+%    \label{eq:decompdivfree}
+%    \nabla \cdot {\bf T}_j = 0, \quad
+%    \nabla \cdot (\xx^{\perp} \cdot {\bf T}_j) = 0
+%  \end{equation}
+% for  $ j = 1, 2, 3$.
+%\end{lemma}
+%\begin{proof}
+%  Let $\mathbf{T}$ be as in \eqref{eq:stress}.  
+%  It is straightforward to show that  
+%%  \begin{align*}
+% %   (\nabla \cdot {\bf T})_j &=
+% %   \nabla_k   T_{jk}  = 0\\
+% %   &= \rho^{-1} 2u \nabla_j u + \rho(2\nabla_{kl}^2 u \nabla_l u  - 2 \nabla_{kj}^2 u \nabla_k u
+% %  - 2 \nabla_j u \nabla_{kk}^2 u )\\
+% %   &=2\rho^{-1}(-\rho^2 \Delta u + u)\nabla_j u = 0,
+% % \end{align*}
+% \begin{equation*}
+%\nabla \cdot {\bf T} = 2\rho^{-1}(-\rho^2 \Delta u + u)\nabla u = 0
+% \end{equation*}
+% since $u$ solves $-\rho^2 \Delta u + u = 0$.
+% Moreover,
+%  \begin{align*}
+%    \nabla \cdot (\xx^{\perp} \cdot {\bf T} )
+%%    &= \nabla_k (\epsilon_{jml}x_m T_{lk})\\
+%%    &= \varepsilon_{jml} T_{lm} + \varepsilon_{jml}x_m \nabla_k T_{lk}\\
+%%   &= (\boldsymbol{\varepsilon}:{\bf T} + {\bf x}^{\perp} \cdot \nabla \cdot {\bf T})_j.
+%=  \mathbf{S}:\mathbf{T} + \mathbf{S}\xx \cdot (\nabla \cdot \mathbf{T}) = 0,
+%  \end{align*}
+%  since ${\bf T}$ is symmetric, where $\mathbf{S}\xx = \xx^{\perp}$.
+%  
+%  The functions $u_i$ and $v_i$ also solve the equation $-\rho^2 \Delta u + u = 0$.  Repeating the above argument 
+%  for ${\bf T}_1 = \sigma[u_i,u_i]$ and ${\bf T}_3 = \sigma[v_i,v_i]$ gives that 
+%  \eqref{eq:decompdivfree} holds for the cases $j = 1$ and $j = 3$. Finally,
+%  \eqref{eq:decompdivfree} holds for the case $j = 2$ because
+%  ${\bf T}_2 = {\bf T} - {\bf T}_1 - {\bf T}_3$.
+%\end{proof}
+
+Let $U_i$ be the interior of the particle indexed by $i$. 
+For $\xx_0 \in \Gamma_i$ and an arbitrary function $g(\xx)$, the notation
+\begin{equation}
+\lim_{\xx \to \xx_0^+}g(\xx),\quad 
+\lim_{\xx \to \xx_0^-}g(\xx), \quad
+[g](\xx_0) = \lim_{\xx \to \xx_0^+}g(\xx)  - \lim_{\xx \to \xx_0^-}g(\xx)
+\end{equation}
+denotes the limit taken from points in $U_i^c$,  the limit taken from points in $U_i$, and the jump, respectively.  
 \begin{lemma}
-  \label{eq:stress_div_lemma}
-  \begin{equation}
-    \label{eq:decompdivfree}
-    \nabla \cdot {\bf T}_j = 0, \quad
-    \nabla \cdot (\xx \times {\bf T}_j) = 0,\quad j = 1, 2, 3.
+\begin{equation}
+  \label{eq:prejump}
+\FF_i = \int_{\Gamma_i} [{\bf T}_2  \nu_i]  \, \dif s,\quad
+T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot [{\bf T}_2 \nu_i] \, \dif s.
 \end{equation}
@@
 \begin{proof}
-  The function $u$ solves $-\rho^2 \Delta u + u = 0$. Using the summation convention, 
+To derive \eqref{eq:prejump}, we expand
+\begin{equation*}
+  \FF_i 
+  = \int_{\Gamma_i}  {\bf T}_1\nnu  + {\bf T}_2\nnu + {\bf   T}_3\nnu\,\dif s.
+\end{equation*}
+By \eqref{eq:uidef} and \eqref{eq:decompdivfree}, we have $u_i$ smooth and  
+$\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n \setminus U_i$.
+Similarly, $v_i = u - u_i$ is smooth and
+$\nabla \cdot {\bf T}_3 = \mathbf{0}$ in $U_i$. 
+By the divergence theorem,  
+\begin{equation*}
+  \int_{\Gamma_i}  {\bf T}_1\nnu \,\dif s
+  = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,dx = \mathbf{0},\quad
+    \int_{\Gamma_p}  {\bf T}_3 \nnu\,\dif s
+  = \int_{U_p} \nabla \cdot {\bf T}_3 \,dx = \mathbf{0}.
+\end{equation*}
+Finally, $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
+\[
+\mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \,dx = -\int_{\Gamma_i}  ({\bf T}_2 \nnu)^-\,\dif s,
+\]
+where the superscript denotes the limit taken from in $U_i$.  
+Combining the previous four equations gives the first equation in \eqref{eq:prejump}.
+The argument for the second equation in \eqref{eq:prejump} is identical. 
+\end{proof}
+
+\begin{lemma}
+\begin{equation}
+\label{eq:postjump}
+  [{\bf T}_2\nnu] =  \JJ_i.
+\end{equation}
+\end{lemma}
+\begin{proof}
+We have the jump relations for \eqref{eq:uidef}:
+\begin{align}
+\label{eq:DLjump}
+\lim_{\xx \to \xx_0^\pm } u_i(\xx) &= \pm\frac{1}{2}\sigma(\xx_0) + u_i (\xx_0),\\
+\label{eq:DLdevjump}
+\lim_{\xx \to \xx_0^\pm } \nabla u_i(\xx) &= \pm\frac{1}{2}\frac{\dif \sigma}{\dif s}(\xx_0)\ttau(\xx_0) + \nabla u_i(\xx_0).
+\end{align}
+Using \eqref{eq:DLjump}, \eqref{eq:DLdevjump}, \eqref{eq:Tsplit}, and that $v_i$ is smooth in a neighborhood of $\Gamma_i$ gives
     \begin{align*}
-    (\nabla \cdot {\bf T})_j &=
-    \nabla_k   T_{jk} \\
-    &= \rho^{-1} 2u \nabla_j u + \rho(2\nabla_{kl}^2 u \nabla_l u  - 2 \nabla_{kj}^2 u \nabla_k u
-    - 2 \nabla_j u \nabla_{kk}^2 u )\\
-    &=2\rho^{-1}(-\rho^2 \Delta u + u)\nabla_k u = 0.
+    [{\bf T}_2\nnu]   &= [(\mathbf{S}(u_i,v_i)  +\mathbf{S}(v_i,u_i))\nnu] \\
+    &= [ ( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
+    - 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla u_i^T)  \nnu]\\
+    &= 2\gamma\rho^{-1} \sigma v_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dv_i }{ds} \nnu
+    - 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dv_i }{d\nu} \ttau = \JJ_i,
   \end{align*}
-Moreover, 
-  \begin{align*}
-    (\nabla \cdot (\xx \times {\bf T} ))_j
-    &= \nabla_k (\epsilon_{jml}x_m T_{lk})\\
-    &= \varepsilon_{jml} T_{lm} + \varepsilon_{jml}x_m \nabla_k T_{lk}\\
-    &= (\boldsymbol{\varepsilon}:{\bf T} + {\bf x} \times \nabla \cdot {\bf T})_j.
-  \end{align*}
-  where $\varepsilon_{jml}$ is the alternating tensor. 
-  Since ${\bf T}$ is symmetric $\boldsymbol{\varepsilon}:{\bf T} = {\bf 0}$, and we get
-  $\nabla \cdot (x \times {\bf T}) = 0$ as well.
-
-  The functions $u_p$ and $v_p$ also solve the equation $-\rho^2 \Delta u + u = 0$.  Thus
-  \eqref{eq:decompdivfree} holds for $j = 1, 3$. Finally,
-  \eqref{eq:decompdivfree} holds for $j = 2$ because
-  ${\bf T}_2 = {\bf T} - {\bf T}_1 - {\bf T}_3$.
+  as required. 
 \end{proof}
-
-Using Lemma \ref{eq:stress_div_lemma}, we will establish that
-\begin{equation}
-  \label{eq:prejump}
-  F_p + i G_p = \gamma \int_{\Sigma_p}  ({\bf U}_2\nnu)^+ - ({\bf
-  U}_2\nnu)^-\,\dif S
-\end{equation}
-where ${\bf U}_j = ({\bf I} + i {\bf X}){\bf T}_j$ for $j = 1, 2, 3.$
-The stress ${\bf U}_2$ has a jump discontinuity at $\Sigma_p.$
-The plus and minus superscripts denote
-the limit taken along points in $U_p^c$ and along points in $U_p$
-respectively.
-${\bf U}_1$ and ${\bf U}_3$ are real-analytic in a neighborhood of $\overline{U_p}$
-and have no jump-discontinuity at $\Sigma_p$.
-To derive \eqref{eq:prejump}, we expand
-\begin{align*}
-  F_p + i G_p
-  &= \gamma \int_{\Sigma_p} {\bf T} \nnu + ix \times {\bf T} \nnu \,\dif S \\
-  &= \gamma \int_{\Sigma_p}  {\bf U}_1\nnu  + ({\bf U}_2\nnu)^+ + {\bf
-  U}_3\nnu\,\dif S
-\end{align*}
-The function $u_p$ is real-analytic and
-$\nabla \cdot {\bf U}_1 = 0$ throughout $\mathbb{R}^n \setminus U_p$.
-By the divergence theorem, we get
-\begin{equation*}
-  \int_{\Sigma_p}  {\bf U}_1 \nnu\,\dif S
-  = \int_{\mathbb{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
-\end{equation*}
-Next, $v_p$ is real-analytic and
-$\nabla \cdot {\bf U}_3 = 0$ in $U_p$. Therefore
-\begin{equation*}
-  \int_{\Sigma_p}  {\bf U}_3 \nnu\,\dif S
-  = -\int_{U_p} \nabla \cdot {\bf U}_3 \,dx = 0.
-\end{equation*}
-Finally, $\nabla \cdot {\bf U}_2= 0$ in $U_p$. This gives
-\[
-0 = -\int_{U_p} \nabla \cdot {\bf U}_2 \,dx = \int_{\Sigma_p}  ({\bf
-U}_2 \nnu)^-\,\dif S.
-\]
-Combining the last four equations give \eqref{eq:prejump}.
-
-\begin{proof}[Proof of \eqref{eq:recipforcetorque}]
-  The main ingredients of the proof are the jump relations
-  for $u_p$. For $x_0 \in \Sigma_p$,
-  \begin{enumerate}
-  \item $ \lim_{x \to x_0^\pm } u_p(x) = \pm\frac{1}{2}\eta(x_0) + (D\eta)(x_0)$
-  \item $ \lim_{x \to x_0^+ } (\nabla u_p \cdot \nnu) (x) = \lim_{x \to
-    x_0^-} (\nabla u \cdot \nnu)(x)$
-  \end{enumerate}
-  Furthermore,
-  combining (i) and (ii) gives
-  \begin{align*}
-    \nabla u_p^+ - \nabla u_p^-
-    &= \nabla (u_p^+ - u_p^-) \cdot t_i t_i +  (\nabla  u_p^+\cdot
-    \nnu  - \nabla u_p^- \cdot \nnu) \nnu\\
-    &= \nabla \eta \cdot \tau_i \tau_i
-  \end{align*}
-  where $\{\tau_i\}_{i=1}^n$ are an orthonormal tangent vectors.
-  We can use these relationships to derive an expression for the jump in
-  normal stress.
-  \begin{align*}
-    &({\bf T}_2\nnu)^+ - ({\bf T}_2\nnu)^-
-    \\
-    &= 2\rho^{-1} u_p^+v_p \nnu + 2\rho \nabla u_p^+ \cdot \nabla v_p
-    \nnu
-    - 2 \rho \nabla u_p^+  \nabla v_p \cdot \nnu
-    - 2 \rho \nabla v_p  \nabla u_p^+ \cdot \nnu\\
-    &-2\rho^{-1} u_p^-v_p \nnu - 2\rho \nabla u_p^- \cdot \nabla v_p \nnu
-    + 2 \rho \nabla u_p^-  \nabla v_p \cdot \nnu
-    + 2 \rho \nabla v_p  \nabla u_p^- \cdot \nnu\\
-    &= 2\rho^{-1} \eta v_p \nnu + 2\rho \nabla \eta \cdot \tau_i \tau_i
-    \cdot \nabla v_p \nnu
-    - 2\rho \nabla \eta \cdot \tau_i \tau_i \nabla v_p \cdot \nnu + 0\\
-    &= J_p.
-  \end{align*}
-
-  Applying the above relations to the integrand of \eqref{eq:prejump} yields
-  \[
-  ({\bf U}_2\nnu)^+ - ({\bf U}_2\nnu)^-
-  =
-  ({\bf I} + i {\bf X})(({\bf T}_2\nnu)^+ - ({\bf T}_2\nnu)^-)
-  = ({\bf I} + i {\bf X})J_p
-  \]
-  This completes the proof of \eqref{eq:recipforcetorque}.
-\end{proof}
+  Combing  \eqref{eq:prejump}  with \eqref{eq:postjump} completes the proof of \eqref{eq:recipforcetorque}.
 

### 2021-08-17 doc/main_jfm.tex
touched up intro

@@
 \begin{abstract}
-In this work, we study the dynamics of many-body systems immersed in a viscous fluid with a specified interparticle force.
-In particular, we apply a hydrophobic attraction potential (HAP) using a Janus type granular system to model lipid bilayer membranes.
-Coupling with an efficient integral equation method for rigid bodies in Stokes flow and an previous developed HAP solver, the deformations of a two-dimensional vesicle such as tank-treading motion and membrane ruptures can be observed under different values of the shear rate.
-Moreover, an efficient integral equation method is adopted for solving the screened Laplace equation and the mobility problem where it can accurately calculate hydrophobic and hydrodynamic interactions between near touched boundaries.
+  In this work, we study the dynamics of many-body systems immersed in a
+  viscous fluid with a specified interparticle force. In particular, we
+  apply a hydrophobic attraction potential (HAP) using a Janus type
+  granular system to model lipid bilayer membranes. Coupling with an
+  efficient integral equation method for rigid bodies in Stokes flow and
+  a previous developed HAP solver, the deformations of a two-dimensional
+  vesicle such as tank-treading motion and membrane ruptures can be
+  observed under different values of the shear rate. Moreover, an
+  efficient integral equation method is adopted for solving the screened
+  Laplace equation and the mobility problem where it can accurately
+  calculate hydrophobic and hydrodynamic interactions between near
+  touched boundaries.
 \end{abstract}
@@
 \section{\label{intro}Introduction}
-Described by de Gennes as ``another animal in soft matter physics", the Janus particle (often a spherical particle with a hydrophobic and a hydrophilic hemisphere) exhibits complex aggregate, clustering and self-assembly into meso- and macroscopic structures that are relevant to a wide range of applications in biology and bioengineering.
-Whether it is surface chemistry or polarity under an external field, the dynamics of Janus particles is inevitably the combination of long-range hydrodynamics interactions in the presence of short- and intermediate-range particle-particle interactions.
-Recently Fu {\it et al.} illustrated that the hydrophobic interactions between Janus particles in a viscous solvent can be used as a coarse-grained model to capture the mechanics of an elastic bilayer membrane of amphiphilic macromolecules such as lipids \cite{Fu20}.
-Depending on the total number of Janus particles and their geometry, in a viscous solvent, Janus particles are found to aggregate to form a micelle, a patch of bilayer membrane with open ends, and a self-enclosed bilayer membrane (a vesicle).
-Using a hybrid continuum model for the interactions between amphiphilic particles in a viscous solvent and formulating it in a boundary integral formulation, Fu {\it et al.} showed that the membrane granularity during fusion and fission of bilayers can be accurately captured.
+Described by de Gennes as ``another animal in soft matter physics", the
+Janus particle (often a spherical particle with a hydrophobic and a
+hydrophilic hemisphere) exhibits complex aggregate, clustering, and
+self-assembly into mesoscopic and macroscopic structures that are
+relevant to a wide range of applications in biology and bioengineering.
+Whether it is surface chemistry or polarity under an external field, the
+dynamics of Janus particles is inevitably the combination of long-range
+hydrodynamics interactions in the presence of short- and
+intermediate-range particle-particle interactions. Recently~\cite{Fu20}
+illustrated that the hydrophobic interactions between Janus particles in
+a viscous solvent can be used as a coarse-grained model to capture the
+mechanics of an elastic bilayer membrane of amphiphilic macromolecules
+such as lipids. Depending on the total number of Janus particles and
+their geometry, in a viscous solvent, Janus particles can aggregate to
+form a micelle, a patch of bilayer membrane with open ends, and a
+self-enclosed bilayer membrane (referred to as a Janus-vesicle). Using a
+hybrid continuum model for the interactions between amphiphilic
+particles in a viscous solvent and formulating it in a boundary integral
+formulation,~\cite{Fu20} showed that the membrane granularity during
+fusion and fission of bilayers can be accurately captured. 
 %This boundary integral formulation has inspired more recent work
 
-In molecular dynamics (MD) simulations, the lipid bilayer membranes are often approximated by an implicit solvent coarse-grained model for lipids (as in the Martini code), where their hydrodynamic interactions are simplified by an implicit solvent.
-The long-range hydrodynamic interactions and the induced long-range lipid interactions can be captured by combining the Dry Martini with a lattice Boltzmann MD \cite{Brandner2019}.
-Brandner {\it et al.} used this methodology to simulate the hydrodynamics of a nano-sized vesicle under a shear flow, and reproduced the well-know vesicle hydrodynamics  such as tank-treading, tumbling and inter-leaflet slippage (reported from simulations of the Helfrich-type continuum model).
-
-In this work we extend the hybrid continuum model in \cite{Fu20} for the Janus suspension to incorporate the collective hydrodynamics of a Janus suspension under various flows: a linear shear flow, an elongation flow, and a Poiseuille flow.
-We demonstrate that a vesicle made of Janus particles does behave like a vesicle in these flowing conditions.
-Furthermore we also show that the hybrid continuum model allows us to investigate the inter-leaflet slippage and rupture of a bilayer membrane due to an imposed flow.
-
-This paper is organized as follows.
-In \S~\ref{sec:governing_eqs} we present the formulation for the Janus particles in a viscous fluid in the zero-Reynolds number regime.
-In \S~\ref{sec:IEM} we extend the hybrid continuum model for a Janus suspension to include the effects of a far-field flow via the mobility problem formulation.
-In \S~\ref{validation} we present validation of our model, and in \S~\ref{results} we present simulation results for a vesicle of Janus bilayer membrane under various flowing conditions.
-Finally we provide discussion and outlook for future directions in \S~\ref{conclusion}.~
-
+In molecular dynamics (MD) simulations, the lipid bilayer membranes are
+often approximated by an implicit solvent coarse-grained model for
+lipids (as in the Martini code), where their hydrodynamic interactions
+are simplified by an implicit solvent. The long-range hydrodynamic
+interactions and the induced long-range lipid interactions can be
+captured by combining the Dry Martini with a lattice Boltzmann MD.
+\cite{Brandner2019} used this methodology to simulate the hydrodynamics
+of a nano-sized vesicle under a shear flow, and reproduced the well-know
+vesicle hydrodynamics such as tank-treading, tumbling, and inter-leaflet
+slippage (reported from simulations of the Helfrich-type continuum
+model).
+
+In this work we extend the hybrid continuum model in~\cite{Fu20} for the
+Janus suspension to incorporate the collective hydrodynamics of a Janus
+suspension under various flows: a linear shear flow, an elongation flow,
+and a Poiseuille flow. We demonstrate that a vesicle made of Janus
+particles does behave like a vesicle in these flowing conditions.
+Furthermore we also show that the hybrid continuum model allows us to
+investigate the inter-leaflet slippage and rupture of a bilayer membrane
+due to an imposed flow. Finally, we compare a pair of interacting
+Janus-vesicles with a continuum model of a pair of vesicles.
+
+This paper is organized as follows. In \S~\ref{sec:governing_eqs} we
+present the formulation for the Janus particles in a viscous fluid in
+the zero-Reynolds number regime. In \S~\ref{sec:IEM} we extend the
+hybrid continuum model for a Janus suspension to include the effects of
+a far-field flow via the mobility problem formulation. In
+\S~\ref{validation} we present validation of our model, and in
+\S~\ref{results} we present simulation results for a single and pair of
+Janus-vesicles under various flowing conditions. Finally we provide
+discussion and outlook for future directions in \S~\ref{conclusion}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Governing  Equations\label{sec:governing_eqs}}

### 2021-08-17 doc/main_jfm.tex
edited up to end of Section 3

@@
 \newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
+\newcommand{\jump}[1]{[\![ #1 ]\!]}
 
@@
 We consider an $N_b$-many body collection of particles suspended in a
-two-dimensional unbounded domain $\Omega$. The boundary of each particle is
-denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
-\cdots \cup \Gamma_{N_b}$ and $\nnu_i$ is the particle outward normal. 
-Assuming the flow is Stokesian, the governing
+two-dimensional unbounded domain $\Omega$. The boundary of each particle
+is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2
+\cup \cdots \cup \Gamma_{N_b}$ and $\nnu_i$ is the particle outward
+normal. Assuming the inertial terms are negligible, the governing
 equations are
@@
 To determine the translational and angular velocities of each particle,
-we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
+we define imposed forces $\FF_i$ and torques $T_i$ acting on each
 particle. Since the small particles are intertialess, force balance
@@
 \begin{alignat}{2}
-  \label{eqn:force}
+  \label{eq:force}
   \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
   && i=1,\ldots,N_b,\\
-  \label{eqn:torque}
+  \label{eq:torque}
   T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Imposed Forces}
@@
 \begin{alignat}{2}
-  \label{SL}
+  \label{eq:SL}
 -\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
-\label{SLbc}
+\label{eq:SLbc}
 u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i, \\
-\label{SLff}
+\label{eq:SLff}
 u &\to 0,                          &&|\xx| \to \infty,
@@
 \begin{align}
-  \label{eqn:hydrophobicAttraction}
+  \label{eq:hydrophobicAttraction}
   \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, \dif s, 
@@
 \begin{align}
-%  \label{eqn:REPUL}
+%  \label{eq:REPUL}
 %  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\xx_{ij} -
@@
 %
-  \label{eqn:REPULforce}
+  \label{eq:REPULforce}
   \FF_i^{\text{repul}} &= \sum_{j \neq i} 
@@
     P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
-  \label{eqn:REPULtorque}
+  \label{eq:REPULtorque}
   T_i^{\text{repul}} &= \sum_{j \neq i} 
@@
 The repulsion profile $P(r)$ is zero for distances $r$ larger than a
-repulsion length scale $\rho_0$. As such,~\eqref{eqn:REPULforce}
-and~\eqref{eqn:REPULtorque} ignore particles $\Gamma_j$ outside a
+repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
+and~\eqref{eq:REPULtorque} ignore particles $\Gamma_j$ outside a
 tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Time Marching}
@@
 scheme updates the particle positions and orientations. By including the
-repulsion force~\eqref{eqn:REPULforce} and
-torque~\eqref{eqn:REPULtorque}, particle collisions are avoided even
+repulsion force~\eqref{eq:REPULforce} and
+torque~\eqref{eq:REPULtorque}, particle collisions are avoided even
 when using a relatively large time step.
@@
 
-%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Integral Equation Method}
@@
 Computing the hydrophobic attraction potential and the particle forces
-and torques requires solving an elliptic partial differential equation
-(PDE) in an unbounded complex domain. We recast both these PDEs as
-boundary integral equations (BIEs). We discretize each BIE at $N$ points
-on each of the $N_b$ particles with a collocation method. Integrals that
-are smooth are computed with the spectrally-accurate quadrature rule,
-and nearly-singular integrals, caused by close contact between two
-particles, are computed with a high-order interpolation-based quadrature
-rule~\cite{qua-bir2014}. After discretizing and applying quadrature, the
-resulting linear system is solved with matrix-free GMRES, and we
-guarantee that the number of GMRES iterations is mesh-independent by
-using second-kind BIEs.
-
+and torques requires the solution of elliptic partial differential
+equations (PDEs) in an unbounded complex domain. We recast both these
+PDEs as boundary integral equations (BIEs). We discretize each BIE at
+$N$ points on each of the $N_b$ particles with a collocation method.
+Integrals that are smooth are computed with the spectrally-accurate
+quadrature rule, and nearly-singular integrals, caused by close contact
+between two particles, are computed with a high-order
+interpolation-based quadrature rule~\cite{qua-bir2014}. After
+discretizing and applying quadrature, the resulting linear system is
+solved with matrix-free GMRES, and we guarantee that the number of GMRES
+iterations is mesh-independent by using second-kind BIEs.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{HAP Boundary Integral Equation}
@@
 \begin{align}
-  \label{eqn:HAP_DLP}
+  \label{eq:HAP_DLP}
   u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
@@
 \begin{equation}
-\label{eq:SKIE}
+\label{eq:screenedSKIE}
   f(\xx) = \frac{1}{2}\sigma(\xx) + 
@@
 \end{equation}
-the HAP double-layer potential~\eqref{eqn:HAP_DLP} satisfies the
-screened Laplace equation~\eqref{SL}--\eqref{SLff}. To calculate the
-hydrophobic force and torque, the gradient of the double-layer
-potential~\eqref{eqn:HAP_DLP} must be computed on the boundary of each
-particle. In Section~\ref{subsec:calculating_force}, we show that the force and
-torque calculations can be expressed in terms of integral that are
-non-singular.
-
+the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
+Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. We
+solve~\eqref{eq:screenedSKIE} with a collocation method. The integrals
+are approximated with either the trapezoid rule or with the
+interpolation-based near-singular integration scheme. This results in a
+$NN_b \times NN_b$ linear system that is solved with a block-diagonal
+preconditioned GMRES solver.
+
+To calculate the hydrophobic force and torque, the gradient of the
+double-layer potential~\eqref{eq:HAP_DLP} must be computed on the
+boundary of each particle. In Section~\ref{subsec:calculating_force}, we
+show that the force and torque calculations can be expressed in terms of
+non-singular integrals.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Mobility Problem Boundary Integral Equation}
 Following previous work of~\cite{Lukas19}, we represent the velocity as
-the sum of a double-layer potential and the $N_b$ Stokeslets and Rotlets
-\begin{align}
-  \label{eqn:velocity}
+the sum of a double-layer potential and $N_b$ Stokeslets and Rotlets
+\begin{align}
+  \label{eq:velocity}
   \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
@@
 \begin{align}
-  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log(\rho) + 
-    \frac{\rr \otimes \rr}{\rho^2} \FF_i \right), \\
+  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log \rho + 
+    \frac{\rr \otimes \rr}{\rho^2}\right) \FF_i, \\
   \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
@@
 where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
-torque-free and has force $\FF_i$ while the Rotlet force-free and has
-torque $T_i$. Therefore, the velocity~\eqref{eqn:velocity} satisfies the
-total force~\eqref{eqn:force} and torque~\eqref{eqn:torque} conditions
+torque-free and has force $\FF_i$ while the Rotlet is force-free and has
+torque $T_i$. Therefore, the velocity~\eqref{eq:velocity} satisfies the
+total force~\eqref{eq:force} and torque~\eqref{eq:torque} conditions
 if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
-Matching the limit of~\eqref{eqn:velocity} with the rigid body motion,
+Matching the limit of~\eqref{eq:velocity} with the rigid body motion,
 and imposing that $\DD[\eeta]$ is force- and torque-free, the density
@@
     -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
-  \label{eqn:SKIE}
+  \label{eq:SKIE}
     + \sum_{j=1}^{N_b} &
     \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
-    \quad &&\xx \in \bd \Gamma_i,\: i=1,\ldots,N_b, \\
-  \label{eqn:mobility1}
+    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
+  \label{eq:mobility1}
   \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
   &&i = 1,\ldots,N_b, \\
-  \label{eqn:mobility2}
+  \label{eq:mobility2}
   \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu_i \, \dif s &= 0,
@@
 
-The trapezoid rule is used to approximate each of the integrals in
-equations~\eqref{eqn:mobility1} and~\eqref{eqn:mobility2}, and the
-double-layer potential equation~\eqref{eqn:SKIE} is approximated with
+The trapezoid rule is used to approximate the integrals in
+equations~\eqref{eq:mobility1} and~\eqref{eq:mobility2}, and the
+double-layer potential equation~\eqref{eq:SKIE} is approximated with
 either the trapezoid rule, or the interpolation-based near-singular
-integration quadrature rule. After discretizing and applying appropriate
+integration scheme. After discretizing and applying appropriate
 quadrature rules, the result is a $(2NN_b + 3N_b) \times (2NN_b + 3N_b)$
@@
 We note that other BIE formulations of the mobility problem use
-single-layer potentials~\cite{cor-gre-rac-vee2017, rac-gre2016} or both
-single- and double-layer potentials~\cite{cor-vee2018}.
-
+single-layer potentials (\cite{cor-gre-rac-vee2017, rac-gre2016}) or a
+combination of single- and double-layer potentials (\cite{cor-vee2018}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Calculating the Hydrophobic Force}
 \label{subsec:calculating_force}
-Once \eqref{eq:SKIE} has been solved and $\sigma$ determined,
-we can evaluate the integrals  \eqref{eqn:hydrophobicAttraction}. 
-These integrals involve the stress \eqref{eq:stress} which contains
-a singular integral for the gradient of the double-layer potential.   
-To avoid singular integrals, we use the alternative forms
-\begin{equation}
+Once \eqref{eq:SKIE} has been solved for $\sigma$, we need to evaluate
+the integrals~\eqref{eq:hydrophobicAttraction}. These integrals involve
+the stress \eqref{eq:stress} which contains a singular integral for the
+gradient of the double-layer potential. To avoid singular integrals, we
+use the alternative forms
+\begin{align}
   \label{eq:recipforcetorque}
   \FF_i^{\text{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
-T_i^{\text{hydro}}    = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s
-\end{equation}
+  T_i^{\text{hydro}}    = \int_{\Gamma_i} 
+    (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
+\end{align}
 where
- \begin{equation}
+\begin{align}
   \label{eq:jumpstress1}
-\JJ_{i} =2\gamma\rho^{-1} \sigma v_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dv_i }{ds} \nnu
-    - 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dv_i }{d\nu} \ttau.
-\end{equation}
-Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent  and arc length  derivative for $\Gamma_i$, respectively, 
-and
+  \JJ_{i} = 2\gamma\rho^{-1} \sigma v_i \nnu + 
+    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{ds} \nnu -
+    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{d\nu} \ttau.
+\end{align}
+Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent  and arc length
+derivative for $\Gamma_i$, respectively, and
 \begin{equation}
@@
 \end{equation}
-The advantage in using \eqref{eq:jumpstress1} over \eqref{eq:stress} 
-is that components $\sigma$, $v_i$, $\frac{d\sigma}{ds}$, and  $\frac{dv_i}{ds}$ are all smooth.
-
-To prove \eqref{eq:recipforcetorque},
-let \begin{align*}
-  {\bf T}
-  &=
+That is, $\nu_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP},
+except that $\Gamma_i$ is excluded from $\bd\Omega$. The advantage in
+using \eqref{eq:jumpstress1} over \eqref{eq:stress} is that components
+$\sigma$, $v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ are all
+smooth.
+
+To prove \eqref{eq:recipforcetorque}, let 
+\begin{align*}
+  {\bf T} &=
     \mathbf{S}(u_i,u_i)
@@
 \end{equation}
-Using the fact that $u$,  $u_i$, and $v_i$ solve the equation $-\rho^2 \Delta u + u = 0$,
-and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1, 2, 3$ are symmetric, it is straightforward to verify that 
+Using the fact that $u$,  $u_i$, and $v_i$ solve the screened Laplace
+equation~\eqref{eq:SL},  and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1,
+2, 3$ are symmetric, it is straightforward to verify that 
   \begin{equation}
@@
 
-Let $U_i$ be the interior of the particle indexed by $i$. 
-For $\xx_0 \in \Gamma_i$ and an arbitrary function $g(\xx)$, the notation
-\begin{equation}
-\lim_{\xx \to \xx_0^+}g(\xx),\quad 
-\lim_{\xx \to \xx_0^-}g(\xx), \quad
-[g](\xx_0) = \lim_{\xx \to \xx_0^+}g(\xx)  - \lim_{\xx \to \xx_0^-}g(\xx)
-\end{equation}
-denotes the limit taken from points in $U_i^c$,  the limit taken from points in $U_i$, and the jump, respectively.  
+Let $U_i$ be the interior of the particle indexed by $i$. For $\xx_0
+\in \Gamma_i$ and an arbitrary function $g(\xx)$, the notation
+\begin{align}
+  \jump{g}(\xx_0) = \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i}}g(\xx)  - 
+                    \lim_{\substack{\xx \to \xx_0 \\ \xx \in U^c_i}}g(\xx),
+\end{align}
+denotes the jump of the limits of $g(\xx)$ taken from the outside and
+the inside of $\Gamma_i$.
+%\begin{align}
+%\lim_{\xx \to \xx_0^+}g(\xx),\quad 
+%\lim_{\xx \to \xx_0^-}g(\xx), \quad
+%  \jump{g}(\xx_0) = \lim_{\xx \to \xx_0^+}g(\xx)  - \lim_{\xx \to \xx_0^-}g(\xx)
+%\end{align}
+%denotes the limit taken from points in $U_i^c$,  the limit taken from
+%points in $U_i$, and the jump, respectively.  
 \begin{lemma}
-\begin{equation}
+\begin{align}
   \label{eq:prejump}
-\FF_i = \int_{\Gamma_i} [{\bf T}_2  \nu_i]  \, \dif s,\quad
-T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot [{\bf T}_2 \nu_i] \, \dif s.
-\end{equation}
+  \FF_i = \int_{\Gamma_i} \jump{{\bf T}_2  \nu_i}  \, \dif s,\quad
+  T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \jump{{\bf T}_2 \nu_i} \, \dif s.
+\end{align}
 \end{lemma}
 \begin{proof}
-To derive \eqref{eq:prejump}, we expand
-\begin{equation*}
-  \FF_i 
-  = \int_{\Gamma_i}  {\bf T}_1\nnu  + {\bf T}_2\nnu + {\bf   T}_3\nnu\,\dif s.
-\end{equation*}
-By \eqref{eq:uidef} and \eqref{eq:decompdivfree}, we have $u_i$ smooth and  
-$\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n \setminus U_i$.
-Similarly, $v_i = u - u_i$ is smooth and
-$\nabla \cdot {\bf T}_3 = \mathbf{0}$ in $U_i$. 
-By the divergence theorem,  
-\begin{equation*}
+To show~\eqref{eq:prejump}, we expand
+\begin{align}
+  \FF_i = \int_{\Gamma_i} {\bf T}_1\nnu + 
+    {\bf T}_2\nnu + {\bf T}_3\nnu\,\dif s.
+\end{align}
+By~\eqref{eq:uidef} and~\eqref{eq:decompdivfree}, we have that $u_i$ is
+smooth and $\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n
+\setminus U_i$. Similarly, $v_i = u - u_i$ is smooth and $\nabla \cdot
+{\bf T}_3 = \mathbf{0}$ in $U_i$. By the divergence theorem,  
+\begin{align}
   \int_{\Gamma_i}  {\bf T}_1\nnu \,\dif s
-  = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,dx = \mathbf{0},\quad
+  = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,\dif \xx = \mathbf{0},\quad
     \int_{\Gamma_p}  {\bf T}_3 \nnu\,\dif s
-  = \int_{U_p} \nabla \cdot {\bf T}_3 \,dx = \mathbf{0}.
-\end{equation*}
+  = \int_{U_p} \nabla \cdot {\bf T}_3 \,\dif \xx = \mathbf{0}.
+\end{align}
 Finally, $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
-\[
-\mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \,dx = -\int_{\Gamma_i}  ({\bf T}_2 \nnu)^-\,\dif s,
-\]
+\begin{align}
+  \mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \, \dif \xx = -\int_{\Gamma_i}  
+    ({\bf T}_2 \nnu)^-\,\dif s,
+\end{align}
 where the superscript denotes the limit taken from in $U_i$.  
@@
 \label{eq:postjump}
-  [{\bf T}_2\nnu] =  \JJ_i.
+  \jump{{\bf T}_2\nnu} =  \JJ_i.
 \end{equation}
@@
 \end{align}
-Using \eqref{eq:DLjump}, \eqref{eq:DLdevjump}, \eqref{eq:Tsplit}, and that $v_i$ is smooth in a neighborhood of $\Gamma_i$ gives
+Using \eqref{eq:DLjump}, \eqref{eq:DLdevjump}, \eqref{eq:Tsplit}, and
+that $v_i$ is smooth in a neighborhood of $\Gamma_i$, we have
 \begin{align*}
-    [{\bf T}_2\nnu]   &= [(\mathbf{S}(u_i,v_i)  +\mathbf{S}(v_i,u_i))\nnu] \\
-    &= [ ( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
-    - 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla u_i^T)  \nnu]\\
+  \jump{{\bf T}_2\nnu}   &= \jump{(\mathbf{S}(u_i,v_i)  +\mathbf{S}(v_i,u_i))\nnu} \\
+  &= \jump{( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
+- 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla u_i^T)  \nnu}\\
 &= 2\gamma\rho^{-1} \sigma v_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dv_i }{ds} \nnu
@@
 
-%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{\label{validation}Model Validation}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Jeffery Orbit}
-
 The preliminary test of the proposed model using the integral equation method is the numerical validation in Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Self-Assembly and Relaxation}
@@
 
-%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{\label{results}Numerical Results}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Tank-Treading Vesicles}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Vesicle in a Shear Flow}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Vesicle in a Parabolic Flow}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Membrane Ruptures}
@@
 
-%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Two Vesicles in a Linear Flow}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Shear Flow}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Extensional Flow}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{\label{conclusion}Conclusion}

### 2021-08-18 doc/main_jfm.tex
updated table
3.3 revision

@@
 \end{alignat}
-where $f_i$ is a material label with $f_i = 0$, respectively $1$, representing
-hydrophilic, respectively hydrophobic, portions of the surface, and $\rho$ is the
+where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$, respectively $1$, representing
+hydrophilic, respectively hydrophobic, portions of the surface.  We assume that the $f_i$ and $\Gamma_i$ are
+smooth.  The parameter $\rho$ is the
 decay length of attraction. The forces and torques for this attraction
@@
     K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
-    \quad \xx \in \Omega,
+    \quad \xx \in \mathbb{R}^2,
 \end{align}
 where $K_0$ is the zeroth-order modified Bessel function of the first
-kind. By requiring that the density function $\sigma$ satisfies the
+kind and the integral is taken in the sense of principle value whenever $\xx \in \partial \Omega$. 
+By requiring that the density function $\sigma$ satisfies the
 second-kind integral equation
@@
 gradient of the double-layer potential. To avoid singular integrals, we
-use the alternative forms
+evaluate \eqref{eq:hydrophobicAttraction} using the identities
 \begin{align}
@@
 \label{eq:uidef}
-    v_i(\xx) = u(\xx) - \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
+\begin{aligned}
+    u(\xx) &= u_i(\xx) + v_i(\xx),\\
+    u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
     K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
-    \quad \xx \in \Omega.
+    \quad \xx \in \mathbb{R}^2.
+\end{aligned}
 \end{equation}
-That is, $\nu_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP},
-except that $\Gamma_i$ is excluded from $\bd\Omega$. The advantage in
-using \eqref{eq:jumpstress1} over \eqref{eq:stress} is that components
-$\sigma$, $v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ are all
-smooth.
+That is, $v_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP} with 
+$\Gamma_i$ excluded from $\bd\Omega$. The advantage in
+using \eqref{eq:recipforcetorque} over using \eqref{eq:hydrophobicAttraction} is that the components
+$\sigma$, $v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ of $\JJ_i$ are smooth functions,
+whereas the components of \eqref{eq:stress} are singular integrals.
 
@@
 \begin{align}
-  \jump{g}(\xx_0) = \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i}}g(\xx)  - 
-                    \lim_{\substack{\xx \to \xx_0 \\ \xx \in U^c_i}}g(\xx),
-\end{align}
-denotes the jump of the limits of $g(\xx)$ taken from the outside and
+  \jump{g}(\xx_0) = \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i^c}}g(\xx)  - 
+                    \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i}}g(\xx),
+\end{align}
+denotes the jump of the limits of $g(\xx)$ taken from the outside to
 the inside of $\Gamma_i$.
@@
   \label{eq:prejump}
-  \FF_i = \int_{\Gamma_i} \jump{{\bf T}_2  \nu_i}  \, \dif s,\quad
-  T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \jump{{\bf T}_2 \nu_i} \, \dif s.
+  \FF_i = \int_{\Gamma_i} \jump{{\bf T}_2  \nnu}  \, \dif s,\quad
+  T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \jump{{\bf T}_2 \nnu} \, \dif s.
 \end{align}
@@
   = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,\dif \xx = \mathbf{0},\quad
-    \int_{\Gamma_p}  {\bf T}_3 \nnu\,\dif s
-  = \int_{U_p} \nabla \cdot {\bf T}_3 \,\dif \xx = \mathbf{0}.
-\end{align}
-Finally, $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
+    \int_{\Gamma_i}  {\bf T}_3 \nnu\,\dif s
+  = \int_{U_i} \nabla \cdot {\bf T}_3 \,\dif \xx = \mathbf{0}.
+\end{align}
+Finally, $u_i$ and $v_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
 \begin{align}
@@
 
-\begin{lemma}
+We have the jump relations for \eqref{eq:uidef}: 
 \begin{equation}
-\label{eq:postjump}
-  \jump{{\bf T}_2\nnu} =  \JJ_i.
+\label{eq:DLjump}
+\jump{u_i} = \sigma, \quad
+\jump{v_i} = 0, \quad
+\jump{\nabla u_i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
+\jump{\nabla v_i} = \mathbf{0},
 \end{equation}
-\end{lemma}
-\begin{proof}
-We have the jump relations for \eqref{eq:uidef}:
-\begin{align}
-\label{eq:DLjump}
-\lim_{\xx \to \xx_0^\pm } u_i(\xx) &= \pm\frac{1}{2}\sigma(\xx_0) + u_i (\xx_0),\\
-\label{eq:DLdevjump}
-\lim_{\xx \to \xx_0^\pm } \nabla u_i(\xx) &= \pm\frac{1}{2}\frac{\dif \sigma}{\dif s}(\xx_0)\ttau(\xx_0) + \nabla u_i(\xx_0).
-\end{align}
-Using \eqref{eq:DLjump}, \eqref{eq:DLdevjump}, \eqref{eq:Tsplit}, and
-that $v_i$ is smooth in a neighborhood of $\Gamma_i$, we have
+on $\Gamma_i$. We get 
 \begin{align*}
-  \jump{{\bf T}_2\nnu}   &= \jump{(\mathbf{S}(u_i,v_i)  +\mathbf{S}(v_i,u_i))\nnu} \\
+  \jump{{\bf T}_2\nnu}   &= \jump{\mathbf{S}(u_i,v_i)\nnu  +\mathbf{S}(v_i,u_i)\nnu} \\
   &= \jump{( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
@@
 \end{align*}
+Combing  this with \eqref{eq:prejump}  gives  \eqref{eq:recipforcetorque}
 as required.
-\end{proof}
-  Combing  \eqref{eq:prejump}  with \eqref{eq:postjump} completes the proof of \eqref{eq:recipforcetorque}.
 
@@
 %$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
-$b$ (pN$\cdot$ns nm$^{-2}$)   & 1.11 & 1.56 & 1.37 & 1.47 & 1.43 & 1.51 & 1.76\\ 
+$b$ (pN$\cdot$ns nm$^{-2}$)    & 3.56 & 3.53 & 3.12 & 3.61 & 3.57 & 3.56 & 3.58\\ 
 \hline    

### 2021-08-18 doc/main_jfm.tex
updates

@@
 Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of 
-Janus-vesicles under flows. To extract physical quantities of the target structure using the proposed model, 
-the scaling laws and the dimensionless units are given as follows.
+Janus-vesicles under a number of flows. To extract physical quantities of the target structure using the
+proposed model, the scaling laws and the dimensionless units are given as follows.
 The length unit is scaled by the length of phospholipids $l=2.5$ nm which is set as the diameter of each 
 Janus particle. The force is scaled from the interfacial tension $\gamma=4.11$ pN nm$^{-1}$ 
-from ~\cite{Ryham16}. We then be able to calculate the characteristic time scale 
-$\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP. With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
+from ~\cite{Ryham16}. This also means that the energy unit is scaled by $1\ k_BT$. We then be able to
+calculate the characteristic time scale $\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP.
+With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
 %
 For the model parameters, the decay length of attraction $\rho = 2l = 5$ nm, the repulsion length scale is 
-$\rho_0=0.5$, and teh repulsion strength $M=4.0$.
+$\rho_0=0.5$, and the repulsion strength $M=4.0\ k_BT$.
 The dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ is the shear rate.
@@
 The well known results indicate that the vesicle has tank-treading behavior when
-there is no viscosity contrast in both inside and outside of the vesicle that is one of the features in the  framework of the proposed model.
+there is no viscosity contrast in both fluids inside and outside of the vesicle.
+Within the framework of the simulation setup, the proposed model provides a feature that the fluid viscosity is constant over the computational domain and it is capable of performing these simulations.
 
 The centroid of the pre-relaxed $58$-body Janus vesicle is initially placed at the origin then the shear flow 
-with a certain shear rate $\chi$ is turned on. 
+with a certain shear rate $\chi$ is then turned on. 
 The snapshots of the simulation for single vesicle in a shear flow with a shear rate $\chi=0.0025$ are shown 
@@
 \includegraphics[height=2in]{parabolic.eps}
-  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$.
-The configuration is the state when $t=10000$.
-Red arrows are directors of particle velocities.
-The inset shows the mean $y$-position over time.
+  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=32.8$ nm ns$^{-1}$, $R_0 = 20$ nm,  and the control parameter $w=10$.
+The configuration is the state when $t=\{0, 4000, 8000\}$.
+Red curves are midplanes of three configurations.
   }

### 2021-08-18 doc/main_jfm.tex
updates

@@
 The black dashed line shows the reference of how all magnitudes decay.
-(b) Bilayer configurations for $t=0$(gray) and $t=1000$(red) with particle directors.
+(b) Bilayer configurations for $t=0$(black) and $t=1000$(red) with particle directors.
   (c)-(d) show the fluid pressure profiles for $t=0$ and $t=1000$ where the background curves indicate the streamlines.
@@
 hydrophobic attraction. From weak to strong action field, the color varies from blue to red. Clearly, the
-hydrophobic layer has largest action. To demonstrate the tank-treading behavior of the vesicle, panels (b) 
+hydrophobic layer has the largest action. To demonstrate the tank-treading behavior of the vesicle, panels (b) 
 and (d) provide the streamlines of the fluid velocity over the whole computational domain when the shear 
@@
 exponential model given by $A^* = a_0 + b_0 \exp(-kt)$.
-Panel (b) shows that the decay rate $k$ is independent of the shear rate when the shear is above a threshold and the terminal reduced area for each
-case of the shear rate can then be calculated. It is also clear that a slower shear rate generates a higher reduced area and has a faster convergence then the high shear rate cases. 
+Panel (b) shows that the decay rate $k$ is independent of the shear rate when the shear is above a threshold and the terminal reduced areas for each
+case of the shear rates are given in the inset. It is also clear that a slower shear rate generates a higher terminal reduced area and has a faster convergence then the high shear rate cases. 
 With a converging total arc length as shown in panel (c), a slower shear rate also produces a smaller excess length shown in panel (d).
-In summary, the small oscillations in all results are due to the granularity of the Janus-vesicle which tend to having a slightly non-smooth curve in simulations.
+In summary, the small oscillations in all results are due to the granularity of the Janus-vesicle which tend to having slightly non-smooth curves in simulations.
 Overall the total lengths of the bilayer have the same converging value in all test shear rates.
@@
 \end{center} 
-  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) From exponential fits in panel (a), we obtain the decay rate for a number of different shear rates;
-  (c) Reduced area transitions over time. (d) Excess length of the midplanes.
-A set of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
-A slower shear rate generates a faster convergence in the reduced area and smaller excess length. 
+  \caption{(a) Total arc lengths of the midplanes over time in cases of different shear rates; (b) From exponential fits in panel (a), we obtain the decay rate $k$ for a number of different shear rates.
+The inset plots the terminal reduced areas; (c) Reduced area transitions over time; (d) Excess length of the midplanes.
+For all panels, a set of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
+The legend in panel (d) applies to both panels (a) and (c). 
   }

### 2021-08-18 doc/main_jfm.tex
updates

@@
 between two leaflets. When a shear rate is large enough, take $\chi = 0.005$ as an example, 
-Figure~\ref{figure5} shows the schematic of the test.
-A particle pair is initially marked and we then track the positions and mean angle $\theta(t)$ between particle relative position with respect to the vesicle center over the time.
-It is clear to see that the outer leaflet always has larger
-tangential velocity than the one from the inner leaflet and the mean angle $\theta(t)$ increases. 
+Figure~\ref{figure5} shows the schematic of the test where a particle pair is initially marked and we then track the positions of this particle pair over a period of time. 
+In this series of tests, we monitor the mean particle position change and mean angle $\theta(t)$ between particle relative positions with respect to the vesicle center over the time.
+It is clear to see that the outer leaflet always has larger tangential velocity than the one from the inner leaflet and the mean angle $\theta(t)$ increases.
 This inter-leaflet sliding phenomenon is consistent with what has been seen
@@
 
-The inter-monolayer friction coefficient of the Janus-vesicle is calculated from the ratio of the friction force and the slip velocity. This quantity is given by 
+The inter-monolayer friction coefficient of the Janus-vesicle is calculated from the ratio of the mean friction force and the mean slip velocity. This quantity is given by 
 \begin{equation}
@@
 %
-where $\Sigma_M$ is the curve determined by the midplane and the relative radius $R$ is defined by the distance between the particle pair and the centroid of the Janus-vesicle.
+where $\Sigma_M$ is the curve determined by the midplane and the relative radius $R$ is defined by the distance between the midplane and the centroid of the Janus-vesicle.
 Hence, the mean rotational velocity
 of the bilayer is given by the integral of $R\dot\theta$ over the midplane curve $\Sigma_M$.
-For the friction force $F_f$, we calculate tangential stresses near the bilayer from outer and inner fluid then 
-extrapolate the force value onto the midplane to acquire the pressure jump. The friction force is computed after integrating the pressure jump over the midplane $\Sigma_M$.
+For the friction force $F_f$, we integrate tangential stresses near the bilayer from outer and inner regions then 
+extrapolate the force value onto the midplane $\Sigma_M$ to acquire the force difference. 
 Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$. As expected,
@@
 %$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
-$b$ (pN$\cdot$ns nm$^{-2}$)    & 3.56 & 3.53 & 3.12 & 3.61 & 3.57 & 3.56 & 3.58\\ 
+$b$ (pN$\cdot$ns nm$^{-2}$)    & 3.56 & 3.53 & 3.52 & 3.61 & 3.57 & 3.56 & 3.58\\ 
 \hline    
@@
 %
-where $v_{max}$ is the flow strength and $w$ controls the shape of the flow.
-$R_0$ is defined as the radius of the Janus-vesicle at $t=0$.
-Figure~\ref{figure6} gives a configuration for one specific case where the centroid of the Janus-vesicle is initially placed slightly above the $x$-axis at $(0,3)$.
-The parameters are $v_{max} = 8.0$, $w=10$ and $R_0=8$.
-The inset of Figure~\ref{figure7} shows the trajectory of the mean position in $y$-direction which decreases toward $y=1$ for a period of time and starts to have an oscillatory motion.
-Moreover, the Janus-vesicle performs tank-treading during the simulation and red arrows in Figure~\ref{figure6} indicate a counterclockwise movement.
-For this test run, an asymmetric slipper occurs and the reduced area for this configuration is $\sim0.9$.
-This matches the previous numerical tests in  \cite{Kaoui09} where a slipper-like shape occurs when the flow velocity is weak.
+where $v_{max}$ is the flow strength and $w$ controls the shape of the flow. $R_0$ is defined as the radius of the Janus-vesicle at $t=0$.
+
+Figure~\ref{figure6} gives three configurations for one specific case where the centroid of the Janus-vesicle is initially placed slightly above the $x$-axis.
+The parameters are $v_{max} = 8.0$, $w=10$, and $R_0=8$.
+The red curves are the midplanes and a particle pair is marked in color.
+We observe that the deformed
+Janus-vesicle has a counterclockwise movement and the shape of the vesicle approaches to an asymmetric
+slipper shape.
+For this test run, the reduced area for this configuration is $\sim0.9$ which matches the previous numerical tests in \cite{Kaoui09} where a slipper-like shape occurs when the flow velocity is weak and the reduced area is large.
+A schematic of the setup is shown in Figure~\ref{figure7} where the blue horizontal line represents the mean
+$y$-position of all particles. The inset of Figure~\ref{figure7} shows the trajectory of the mean position in 
+$y$-direction which decreases toward $y=1$ for a period of time and starts to have an oscillatory motion.
 
@@
 \includegraphics[width=0.8\textwidth]{slipper.eps}
-  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$.
-The configuration is the state when $t=10000$.
-Red arrows are directors of particle velocities.
-The inset shows the mean $y$-position over time.
-  }
-    \label{figure6}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[height=2in]{parabolic.eps}
   \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=32.8$ nm ns$^{-1}$, $R_0 = 20$ nm,  and the control parameter $w=10$.
@@
 Red curves are midplanes of three configurations.
+  }
+    \label{figure6}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[height=2in]{parabolic.eps}
+  \caption{Schematic of a Janus-vesicle under a parabolic flow where the strength of the flow $v_{max}=32.8$ nm ns$^{-1}$, $R_0 = 20$ nm,  and the control parameter $w=10$.
+The configuration is generated when $t=10000$.
+The inset plots the trajectory of mean $y$-position over the time.
   }

### 2021-08-18 doc/main_jfm.tex
updates

@@
 
-With the choice of a large shear rate, a pore formation or a complete membrane rupture can be observed during simulations.
+With the choice of a large shear rate, a pore formation or a complete membrane rupture can be captured during simulations.
 Figure~\ref{figure8} shows a demonstration of a vesicle under a shear flow with shear rate $\chi=0.1$.
@@
 \end{center} 
-  \caption{Trajectories of two-vesicle in a shear flow where the centroids of two Janus-vesicle are plotted as blue dots.
+  \caption{Trajectories of two-vesicle in a shear flow.
+The moving paths of two centroids of two Janus-vesicles are plotted in blue and red.
 Both starting centroids of two Janus-vesicles are on the $x$-axis.
-For simulation time, $t = {0, 400,800,1200}$ for (a)-(d) and $t = {1600, 2400, 3200, 4000}$ for (e)-(h).
-}
+For simulation time, $t = {0, 400,800,1200}$ for (a)-(d) and $t = {1600, 2400, 3200, 4000}$ for (e)-(h).}
     \label{figure10}
@@
 on the same horizontal level, at $(-10,0)$ and $(10,0)$.
-Since we already have a pre-relaxed $58$-body in previous sections, we duplicate the state to have the initial configuration in this section.
-As expected, there
-is no pressure jump between the internal and external fluids from the beginning of the simulation and this is shown in the background pressure plot.
-Panels (b)-(d) show the configurations when $t = \{400,800,100\}$
+Since we already have a pre-relaxed $58$-body in previous sections, we duplicate the state to have the initial configuration (shown in panel (a)) in this section.
+As expected, there is no pressure jump between the internal and external fluids from the beginning of the
+simulation and this is shown in the background pressure plot. Panels (b)-(d) show the configurations when $t = \{500,1000,1500\}$ 
 and we observe that the rotation continues as time goes. The streamlines are plotted in the background 
-for all panels and we include the numerical results using continuum model in all insets. Obviously there is a qualitative agreement between two models.
+for all panels and we include the numerical results using continuum model in all insets. 
+The comparisons give a qualitative agreement between two models.
 
@@
 In other words, the adhesive behavior will be absent when two vesicles are centered
-at a different level and are well separated in $y$-direction. Trajectories of a longer run of the simulation results are shown in Figure~\ref{figure10}.
-
-%Two vesicles in a shear flow is presented in Figures~\ref{figure8} where centers of mass are placed on the same horizontal level, at $(-10,0)$ and $(10,0)$.
-With the same starting state as one in the extensional flow, panels (b)-(d) in Figure~\ref{figure8} are the observed phenomena when two vesicles are in a shear flow where the flow is given by $\dot x = \chi y$.
+at a different level and are well separated in $y$-direction. 
+Moreover, we provide trajectories of a longer run of the simulation results in Figure~\ref{figure10}.
+In all panels, the blue and red curves represent the moving paths of two Janus-vesicle centroids and they move
+nearly a round when $t=4000$ as shown in panel (h).
 
@@
 \end{center} 
-  \caption{Trajectories of different setups in two-vesicle in an extensional flow where the centroids of two Janus-vesicle are plotted as blue dots.
+  \caption{Trajectories of different setups in two-vesicle in an extensional flow and the moving paths of two centroids of two Janus-vesicles are plotted in blue and red.
 (i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii)
-  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure10} presents the numerical results from the case (iii) and a
+  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure11} presents the numerical results from the case (iii) and a
   consistent flow rate is $\chi = 0.005$ for all cases.}
@@
 The short range repulsion plays an important role to avoid structure collisions and this result can be compared with some findings in continuum modeling simulations.
-The pressure plots in Figure~\ref{figure8} provide a realistic result where the pressure is much higher in the gap between two nearby vesicles.
+The pressure plots in Figure~\ref{figure11} provide a realistic result where the pressure is much higher in the gap between two nearby vesicles.
 

### 2021-08-19 doc/main_jfm.tex
started mods to Section 4

@@
 %
+\usepackage[justification=justified]{caption}
 
@@
 \subsection{Jeffery Orbit}
-The preliminary test of the proposed model using the integral equation method is the numerical validation in Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate.
-An ellipsoidal particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\Theta = 0^\circ$.
-Based on the theoretical Jeffery orbits with respect to the target angle $\Theta(t)$,
-
+We use Jeffery orbits to numerically validate our solver for the mobility-problem.  
+The background flow is a shear flow $\uu_{\infty}(\xx) = \dot\gamma  \xx \cdot \mathbf{e}_2 \mathbf{e}_1$ with shear rate $\dot\gamma$
+and orthogonal unit vectors $\mathbf{e}_1$ and $\mathbf{e}_2$. 
+A single elliptical particle is suspended in the fluid with center at the origin.
+The Jeffrey orbit  
 \begin{equation}
-\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
+\label{eq:jeff}
+\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right)
 \end{equation}
-%
-where $a$, $b$ are semi-major and semi-minor axes, and the test aspect ratios of the particle are $2$ and $3$.
-Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from the Jeffery orbits.
+gives the angle between the major axis and $\mathbf{e}_2$
+where $a$, $b$ are the semi-major and semi-minor axes. 
+We are assuming $\Theta(0) = 0$.
+Figure~\ref{figure1} shows that the angles coming from the integral equation method \eqref{eq:SKIE}-\eqref{eq:mobility2}
+are in complete agreement with the theoretical time course \eqref{eq:jeff}.  Hydrophobic attraction and repulsion are zero for a single particle.
 
@@
 \includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
-  \caption{Comparisons of the target angle $\Theta(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method.
-The schematic of the simulation setup is shown in the inset of the figure.
-Here two cases of aspect ratio are validated, $a/b = 2$ and $a/b=3$.
-  }
+  \caption{The figure compares the theoretical Jeffery orbit for $\Theta(t)$ and the result from the integral equation method. 
+    The insets show the simulation setup. The shear rate is $\dot\gamma=0.1$.}
     \label{figure1}

### 2021-08-23 doc/main_jfm.tex
worked on intro

@@
 suspension under various flows: a linear shear flow, an elongation flow,
-and a Poiseuille flow. We demonstrate that a vesicle made of Janus
-particles does behave like a vesicle in these flowing conditions.
-Furthermore we also show that the hybrid continuum model allows us to
-investigate the inter-leaflet slippage and rupture of a bilayer membrane
-due to an imposed flow. Finally, we compare a pair of interacting
-Janus-vesicles with a continuum model of a pair of vesicles.
+and a Poiseuille flow. We demonstrate that a Janus-vesicle behaves like
+a vesicle in these flowing conditions. In particular, we show that a
+Janus-vesicle undergoes tank-treading in a shear flow and vertical
+migration in a channel flow. Furthermore we use the hybrid continuum
+model to investigate the inter-leaflet slippage and rupture of a bilayer
+membrane due to an imposed flow. Finally, we compare a pair of
+interacting Janus-vesicles with a continuum model of a pair of vesicles.
+
+We require a numerical method to avoid unphysical contact between rigid
+Janus particles. Optimization-based contact methods introduce
+constraints, such as enforcing a non-positive space-time interference
+volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}), which
+guarantee that the suspension remains contact-free. These methods do not
+introduce stiffness, but potentially expensive nonlinear complementarity
+problems must be solved at each time step.  Repulsion-based contact
+methods, which we employ, introduce an artificial repulsion force that
+increases in strength as two particles approach one another
+(\cite{glo-pan-hes-jos-per2001, fen-mic2004, kab-qua-bir2018}). Strong
+repulsion forces can introduce numerical stiffness, but with the
+presence of the hydrophobic forces, we maintain a contact-free
+suspensions with a relatively weak non-stiff repulsive force.
 

### 2021-08-24 doc/main_jfm.tex
updated 2-vesicle subsection

@@
 \begin{figure}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{ShearTraj.eps}
+\end{center} 
+  \caption{Trajectories of two-vesicle in a shear flow.
+The moving paths of two centroids of two Janus-vesicles are plotted in blue and red.
+Both starting centroids of two Janus-vesicles are on the $x$-axis.
+For simulation time, $t = {0, 400,800,1200}$ for (a)-(d) and $t = {1600, 2400, 3200, 4000}$ for (e)-(h).}
+    \label{figure9}
+\end{figure}
+
+\begin{figure}
 \centering
@@
   }
-    \label{figure9}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{ShearTraj.eps}
-\end{center} 
-  \caption{Trajectories of two-vesicle in a shear flow.
-The moving paths of two centroids of two Janus-vesicles are plotted in blue and red.
-Both starting centroids of two Janus-vesicles are on the $x$-axis.
-For simulation time, $t = {0, 400,800,1200}$ for (a)-(d) and $t = {1600, 2400, 3200, 4000}$ for (e)-(h).}
     \label{figure10}
@@
 Since we already have a pre-relaxed $58$-body in previous sections, we duplicate the state to have the initial configuration (shown in panel (a)) in this section.
+In all panels, the blue and red curves represent the moving paths of two Janus-vesicle centroids and they move nearly a round when $t=4000$ as shown in panel (h). 
+We observe that the rotation continues as time goes and an interesting event occurs in the simulation that an adhesive effect can be seen and tuned.
+In other words, the adhesive behavior will be absent when two vesicles are centered at a different level and are well separated in $y$-direction.
+
+The fluid pressure profiles of snapshots are given in Figure~\ref{figure10}.
 As expected, there is no pressure jump between the internal and external fluids from the beginning of the
-simulation and this is shown in the background pressure plot. Panels (b)-(d) show the configurations when $t = \{500,1000,1500\}$ 
-and we observe that the rotation continues as time goes. The streamlines are plotted in the background 
-for all panels and we include the numerical results using continuum model in all insets. 
-The comparisons give a qualitative agreement between two models.
-
-An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be seen and tuned.
-In other words, the adhesive behavior will be absent when two vesicles are centered
-at a different level and are well separated in $y$-direction. 
-Moreover, we provide trajectories of a longer run of the simulation results in Figure~\ref{figure10}.
-In all panels, the blue and red curves represent the moving paths of two Janus-vesicle centroids and they move
-nearly a round when $t=4000$ as shown in panel (h).
+simulation and this is shown in the background pressure plot. 
+Panels (b)-(d) show the configurations when $t = \{500,1000,1500\}$ and 
+the streamlines are plotted in the background for all panels. We include the numerical results using 
+a continuum model in all insets and these comparisons give a qualitative agreement between two models.
 
@@
 %JCP paper by Rahimian, Veerapaneni, and Biros.}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
+\end{center} 
+  \caption{Trajectories of different setups in two-vesicle in an extensional flow and the moving paths of two centroids of two Janus-vesicles are plotted in blue and red.
+(i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii)
+  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure12} presents the numerical results from the case (iii) and a
+  consistent flow rate is $\chi = 0.005$ for all cases.}
+    \label{figure11}
+\end{figure}
 
@@
   }
-    \label{figure11}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
-\end{center} 
-  \caption{Trajectories of different setups in two-vesicle in an extensional flow and the moving paths of two centroids of two Janus-vesicles are plotted in blue and red.
-(i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii)
-  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure11} presents the numerical results from the case (iii) and a
-  consistent flow rate is $\chi = 0.005$ for all cases.}
     \label{figure12}
@@
 This extensional flow is stretching along the $y$ direction and squeezing in $x$ direction.
-Figure~\ref{figure11} shows one set of numerical results when the centroids of two bodies are placed at
-$(-10,-0.1)$ and $(10,0.1)$. With this setup, we can make sure that two Janus-vesicles will separate along 
-$y$-direction eventually from empirical tests.
-Panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
-Since two bilayers are close enough from the beginning of the run, two vesicles are first pushed toward each other then separate along the streamlines.
-The short range repulsion plays an important role to avoid structure collisions and this result can be compared with some findings in continuum modeling simulations.
-The pressure plots in Figure~\ref{figure11} provide a realistic result where the pressure is much higher in the gap between two nearby vesicles.
-
-Figure~\ref{figure12} provides simulation results when the center-of-mass positions are placed differently.
+Figure~\ref{figure11} provides simulation results when the center-of-mass positions are placed differently.
 One can notice that when two centroids are placed on the same horizontal level, two Janus-vesicles reach
@@
 This is the consequence when the adhesive effect beats the flow strength.
-Case (iii) is same as the case shown in Figure~\ref{figure11}.
-Finally, case (iv) has a larger initial separation in $y$-direction and two Janus-vesicle moves much faster toward
-$\pm y$-directions.
+In case (iii), two centroids have a small bias in $y$-direction and they
+start to move apart along $\pm y$-direction. Finally, case (iv) has a larger initial separation in $y$-direction and two Janus-vesicle moves much faster toward $\pm y$-directions.
+
+Figure~\ref{figure12} shows numerical results when the centroids of two bodies are placed at
+$(-10,-0.1)$ and $(10,0.1)$, that is, case (iii) of Figure~\ref{figure11}. With this setup, 
+we can make sure that two Janus-vesicles will separate along $y$-direction eventually and we compare the results against a continuum model as shown in all insets. 
+Panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
+Since two bilayers are close enough from the beginning of the run, two vesicles are first pushed toward each other then separate along the streamlines.
+In fluid pressure profiles, the pressure is initially high between the gap formed by two
+Janus-vesicles and decreases during the separation.
+The short range repulsion plays an important role to avoid structure collisions and this result can be compared with some findings in continuum modeling simulations.
 

### 2021-08-24 doc/main_jfm.tex
update Fig. 5 and table

@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{Slip.eps}
+\includegraphics[width=0.5\textwidth]{Slip.eps}
+\includegraphics[width=0.4\textwidth]{Slip2.eps}
 \end{center} 
@@
 Taking shear rate $\chi=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position.
-The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=\{2000,5200,9000\}$.
+The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=2000$ and $t=9000$.
 The midplane curve is denoted as $\Sigma_M$.
+We provide numerical results of $\theta(t)$ for cases of shear rates.
   }
@@
 %$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
-$b$ (pN$\cdot$ns nm$^{-2}$)    & 3.56 & 3.53 & 3.52 & 3.61 & 3.57 & 3.56 & 3.58\\ 
+$b$ (pN$\cdot$ns nm$^{-2}$)    & 1.38 &  5.43 & 1.37 &  1.33 & 8.07 & 1.94  & 1.89\\ 
 \hline    

### 2021-08-24 doc/main_jfm.tex
updates

@@
 extrapolate the force value onto the midplane $\Sigma_M$ to acquire the force difference. 
-Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$. As expected,
-within the same order, the friction coefficients are independent of the shear rates.
+Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$ which are quantitatively close to literature~\cite{sch-vla-mik2010,denOtter2007}.
+
+%As expected, within the same order, the friction coefficients are independent of the shear rates.
 

### 2021-08-24 doc/main_jfm.tex
updates

@@
 extrapolate the force value onto the midplane $\Sigma_M$ to acquire the force difference. 
-Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$ which are quantitatively close to literature~\cite{sch-vla-mik2010,denOtter2007}.
+Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$ which are quantitatively close to literature such as ones in~\cite{sch-vla-mik2010} and~\cite{denOtter2007}.
 

### 2021-08-24 doc/main_jfm.tex
Added 4.1, 4.2 (in progress), modified 5.1.2

--- 2021-08-24 doc/main_jfm.tex
@@
 \newcommand{\bd}{\partial}
+\newcommand{\dd}{\mathbf{d}}
 \newcommand{\DD}{\mathcal{D}}
@@
 combination of single- and double-layer potentials (\cite{cor-vee2018}).
+
+We validated our solver for \eqref{eq:SKIE}-\eqref{eq:mobility2} using a single elliptical particle 
+is suspended in a background shear flow; see Section \ref{sec:ves_in_shear}.
+Hydrophobic attraction and repulsion are zero for a single particle. 
+The angle of the ellipse's major axis coming from the integral equation method was in complete agreement 
+with the theoretical, Jeffrey oribit time-course \cite{}.
+
+%The Jeffrey orbit  
+%\begin{equation}
+%\label{eq:jeff}
+%\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right)
+%\end{equation}
+%gives the angle between the major axis and $\mathbf{e}_2$
+%where $a$, $b$ are the semi-major and semi-minor axes. 
+%We are assuming $\Theta(0) = 0$.
+%
+
+%The background flow is a shear flow $\uu_{\infty}(\xx) = \dot\gamma  \xx \cdot \mathbf{e}_2 \mathbf{e}_1$ with shear rate $\dot\gamma$
+%and orthogonal unit vectors $\mathbf{e}_1$ and $\mathbf{e}_2$. 
+%A single elliptical particle is suspended in the fluid with center at the origin.
+%The Jeffrey orbit  
+%\begin{equation}
+%\label{eq:jeff}
+%\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right)
+%\end{equation}
+%gives the angle between the major axis and $\mathbf{e}_2$
+%where $a$, $b$ are the semi-major and semi-minor axes. 
+%We are assuming $\Theta(0) = 0$.
+%Figure~\ref{figure1} shows that the angles coming from the integral equation method \eqref{eq:SKIE}-\eqref{eq:mobility2}
+%are in complete agreement with the theoretical time course \eqref{eq:jeff}.  Hydrophobic attraction and repulsion are zero for a single particle.
 
@@
 
-We have the jump relations for \eqref{eq:uidef}: 
+We have the following jump relations for \eqref{eq:uidef}: 
 \begin{equation}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Jeffery Orbit}
-We use Jeffery orbits to numerically validate our solver for the mobility-problem.  
-The background flow is a shear flow $\uu_{\infty}(\xx) = \dot\gamma  \xx \cdot \mathbf{e}_2 \mathbf{e}_1$ with shear rate $\dot\gamma$
-and orthogonal unit vectors $\mathbf{e}_1$ and $\mathbf{e}_2$. 
-A single elliptical particle is suspended in the fluid with center at the origin.
-The Jeffrey orbit  
-\begin{equation}
-\label{eq:jeff}
-\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right)
-\end{equation}
-gives the angle between the major axis and $\mathbf{e}_2$
-where $a$, $b$ are the semi-major and semi-minor axes. 
-We are assuming $\Theta(0) = 0$.
-Figure~\ref{figure1} shows that the angles coming from the integral equation method \eqref{eq:SKIE}-\eqref{eq:mobility2}
-are in complete agreement with the theoretical time course \eqref{eq:jeff}.  Hydrophobic attraction and repulsion are zero for a single particle.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
-\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
-  \caption{The figure compares the theoretical Jeffery orbit for $\Theta(t)$ and the result from the integral equation method. 
-    The insets show the simulation setup. The shear rate is $\dot\gamma=0.1$.}
-    \label{figure1}
-\end{figure}
+
+\subsection{Model Parameters}
+In the present manuscript, the particles are disks with centre $\aa_i$, and director $\dd_i$.  
+The boundary conditions \eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos \theta_i)$ where $\theta_i$ is the angle between 
+$\xx - \aa_i$ and $\dd_i$.  The particle diameters are $l_0 = 2.5$ nm representing the characteristic thickness of monolayer. 
+The other physical parameters are 
+\begin{equation}
+\label{eq:parameters}
+\rho = 4 l_0,\quad \rho_0 = l_0,\quad \gamma = \text{4 pN nm}^{-1},\quad \mu = \text{1 cP}.
+\end{equation}
+We nondimensionalize the problem through the change of variables 
+\begin{equation}
+\label{eq:nondimensionalize}
+t \mapsto t \text{ ns}, \quad
+\xx \mapsto \xx \text{ nm}, \quad 
+\xx \mapsto \xx \text{ nm}, \quad 
+\uu \mapsto \uu \text{ nm ns}^{-1}, \quad 
+  p \mapsto p \text{ pN nm}^2.
+\end{equation}
+Here $\text{1 cP} = \text{1 pN ns nm}^{-2}$ is for the viscosity of water at room temperature.  
+For the rest of the manuscript, the time axes are for ns; the pressure $p$ and stress $\sigma$, $\mathbf{T}^{\mathrm{hydro}}$
+are for pN nm$^{-2}$.
+
+\subsection{Permeability}
+Vesicle membranes have a large area modulus $K_A$ and changes in surface are give rise to a membrane tension
+$\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the membrane surface area and $A_0$ is the reference surface area in the non-tensed state. 
+Since we are dealing with two-dimensional vesicles, we replace $A$ and $A_0$ with the membrane arc length $L$ and reference length $L_0$
+respectively.  Thus, the tension in a stretched cylindrical vesicle membrane is 
+\begin{equation}
+\label{eq:stretch}
+\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right).
+\end{equation}
+A stretched vesicles has a Laplace pressure 
+\begin{equation}
+\label{eq:LaplacePressure}
+\Delta p = \frac{\tilde \gamma}{R} 
+\end{equation}
+where $\Delta p$ is the difference in internal pressure to the pressure at infinity
+and  $R$ is the radius of the circular vesicle.  The factor 
+$R^{-1}$ is the total curvature since  the principle curvature in the direction of the cylinder is zero.
+
+The particles in our setup do not abut but rather have small gaps due to repulsive forces.
+The gaps allow for some fluid flux across the JP bilayer.  Aqueous flux is quantified by a permeability constant $P$ in the equation
+\begin{equation}
+\label{eq:perm}
+\frac{dA}{dt} = -P  L \Delta p.
+\end{equation}
+Combining \eqref{eq:stretch}, \eqref{eq:LaplacePressure}, and \eqref{eq:perm}, we can solve the for length $L$ 
+\begin{equation}
+L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t
+\end{equation}
+and compare with our data.
+
+%\subsection{Jeffery Orbit}
+%We use Jeffery orbits to numerically validate our solver for the mobility-problem.  
+%The background flow is a shear flow $\uu_{\infty}(\xx) = \dot\gamma  \xx \cdot \mathbf{e}_2 \mathbf{e}_1$ with shear rate $\dot\gamma$
+%and orthogonal unit vectors $\mathbf{e}_1$ and $\mathbf{e}_2$. 
+%A single elliptical particle is suspended in the fluid with center at the origin.
+%The Jeffrey orbit  
+%\begin{equation}
+%\label{eq:jeff}
+%\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right)
+%\end{equation}
+%gives the angle between the major axis and $\mathbf{e}_2$
+%where $a$, $b$ are the semi-major and semi-minor axes. 
+%We are assuming $\Theta(0) = 0$.
+%Figure~\ref{figure1} shows that the angles coming from the integral equation method \eqref{eq:SKIE}-\eqref{eq:mobility2}
+%are in complete agreement with the theoretical time course \eqref{eq:jeff}.  Hydrophobic attraction and repulsion are zero for a single particle. 
+%
+%
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
+%\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
+%  \caption{The figure compares the theoretical Jeffery orbit for $\Theta(t)$ and the result from the integral equation method. 
+%    The insets show the simulation setup. The shear rate is $\dot\gamma=0.1$.}
+%    \label{figure1}
+%\end{figure}
 
@@
 \subsubsection{Vesicle in a Shear Flow}
-
+\label{sec:ves_in_shear}
 To study the deformation of a Janus-vesicle under a shear flow using the proposed algorithm, 
 we adopt a widely tested numerical simulation in both continuum and molecular dynamics models, single vesicle under a shear flow. 
+The background flow is a shear flow 
+\begin{equation}
+\uu_{\infty}(\xx) = \dot\gamma  \xx \cdot \mathbf{e}_2 \mathbf{e}_1
+\end{equation}
+with shear rate $\dot\gamma$
+and orthogonal unit vectors $\mathbf{e}_x$ and $\mathbf{e}_y$ for the horizontal and vertical directions respectively. 
 The well known results indicate that the vesicle has tank-treading behavior when 
@@
 
+\subsubsection{Intermonolayer friction}
 An interesting phenomenon also rises up in the proposed setup where the inter-monolayer slip occurs 
@@
 
-The inter-monolayer friction coefficient of the Janus-vesicle is calculated from the ratio of the mean friction force and the mean slip velocity. This quantity is given by 
-\begin{equation}
-b = \frac{\langle F_f\rangle}{\langle\int_{\Sigma_M} R \dot\theta \dif s\rangle},
-\end{equation}
-%
-where $\Sigma_M$ is the curve determined by the midplane and the relative radius $R$ is defined by the distance between the midplane and the centroid of the Janus-vesicle.
-Hence, the mean rotational velocity
-of the bilayer is given by the integral of $R\dot\theta$ over the midplane curve $\Sigma_M$.
-For the friction force $F_f$, we integrate tangential stresses near the bilayer from outer and inner regions then 
-extrapolate the force value onto the midplane $\Sigma_M$ to acquire the force difference. 
-Table~\ref{table1} provides a series of numerical results for dimensional friction coefficients $b$. As expected,
-within the same order, the friction coefficients are independent of the shear rates.
+To calculate the inter-monolayer friction coefficient for the apposing JP leaflets, we let  
+\begin{equation}
+b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle },
+\end{equation}
+%
+where $\langle F\rangle = \langle \int_{\mathcal{C}_M} \jump{\ttau \cdot \sigma \cdot \nnu} \,ds\rangle$ 
+is the time-averaged, tangential force along the midplane curve $\mathcal{C}_m$. 
+The parameters $\langle L\rangle$ and $\langle U\rangle$ are the time-averaged midplane curve length and
+intermonolayer slip velocity respectively.
+
+We calculate $\langle F\rangle$ by first evaluating the smooth tangential force along curves a positive distance inside and 
+outside $\mathcal{C}_m$ respectively, and then interpolating at zero distance to give a force jump. 
+We have made a slight abuse of language: due to the problem being two-dimensional,
+the integral $\langle F\rangle$ is actually a force density per length which when divided by length gives the requisite force per area. 
+which when divided by length
+
+Table~\ref{table1} provides dimensional friction coefficients $b$ for several shear rates
+and the results are in quantitative agreement with 
+values previously reported in the literature~\cite{sch-vla-mik2010} and~\cite{denOtter2007}.  
+The coefficients generally lie within the range 1 to 2 pN$\cdot$ns nm$^{-2}$ but there are some 
+outliers.  These outliers ($\dot\gamma = 0.0025$ ns$^{-1}$ and 
+$\dot\gamma = 0.0040$ ns$^{-1}$) correspond to slip velocities that are too low relative to shear rate (see the green and red curve in Figure \ref{figure5}: panel (c)).
+The JP vesicle consists of only  58 particles and so it is not surprising that discrete effects produce outliers.
+
+\todo[inline]{If $B$ is the numerically calculated friction coefficient,  then 
+$b = B/2.5^3$ pN ns nm$^{-3}$ gives the dimensional value.
+
+If $P$ is the numerically calculated pressure, then $p = P/2.5$ pN nm$^{-2}$ is the dimensional pressure.}
 
@@
 \begin{equation}
-{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
+\uu_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
 \end{equation}

### 2021-08-24 doc/main_jfm.tex
re-calculated table 1

@@
 The coefficients generally lie within the range 1 to 2 pN$\cdot$ns nm$^{-2}$ but there are some 
-outliers.  These outliers ($\dot\gamma = 0.0025$ ns$^{-1}$ and 
-$\dot\gamma = 0.0040$ ns$^{-1}$) correspond to slip velocities that are too low relative to shear rate (see the green and red curve in Figure \ref{figure5}: panel (c)).
+outliers.  These outliers ($\dot\gamma = 0.0041$ ns$^{-1}$ and 
+$\dot\gamma = 0.0066$ ns$^{-1}$) correspond to slip velocities that are too low relative to shear rate (see the green and red curve in Figure \ref{figure5}: panel (c)).
 The JP vesicle consists of only  58 particles and so it is not surprising that discrete effects produce outliers.
@@
 %$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
-$b$ (pN$\cdot$ns nm$^{-2}$)    & 1.38 &  5.43 & 1.37 &  1.33 & 8.07 & 1.94  & 1.89\\ 
+$b$ (pN$\cdot$ns nm$^{-3}$)    & 0.22 & 0.87  & 0.22 &0.21 & 1.29 & 0.31 & 0.30\\ 
 \hline    

### 2021-08-24 doc/main_jfm.tex
re-calculated table 1

@@
 The midplane curve is denoted as $\Sigma_M$.
-We provide numerical results of $\theta(t)$ for cases of shear rates.
+We provide numerical results of $\theta(t)$ for cases of shear rates $\chi$.
   }
@@
 values previously reported in the literature~\cite{sch-vla-mik2010} and~\cite{denOtter2007}.  
-The coefficients generally lie within the range 1 to 2 pN$\cdot$ns nm$^{-2}$ but there are some 
+The coefficients generally lie within the range 0.2 to 0.3 pN$\cdot$ns nm$^{-3}$ but there are some 
 outliers.  These outliers ($\dot\gamma = 0.0041$ ns$^{-1}$ and 

### 2021-08-25 doc/main_jfm.tex
re-calculated table 1
conclusion draft

@@
 the integral $\langle F\rangle$ is actually a force density per length which when divided by length gives the requisite force per area. 
-which when divided by length
+%which when divided by length
 
@@
 
+This study proposes a continuum coarse-grained model for Janus-vesicle that focuses on the 
+hydrophobic interactions between lipids, and the hydrophobic force is derived and used for 
+obtaining particle dynamics. The mobility problem using integral equation methods combining
+the previously introduced HAPis adopted.
+The imposed forces and torques of Janus particles adopt not only HAP but a newly developed short 
+range repulsion given by \ref{eq:REPULforce} and \ref{eq:REPULtorque}.
+The hydrodynamic stress tensor calculated in the algorithm leads to examinations of permeable 
+membrane where the stretching modulus $K_A$ and the permeability constant $P$ can be obtained.
+With the use of selected parameters, the numerical algorithm yields good qualitative results such as
+phenomena in tank-treading Janus-vesicle, asymmetric slipper shape in a parabolic flow, and the membrane rupture in a flow at high shear rate.
+
+Inter-monolayer friction coefficients are then obtained and reported by calculating the pressure jumps 
+with respect to the bilayer midplane.
+Results of two Janus-vesicles in flow simulations produce an outstanding agreement with ones generated 
+using continuum modeling.
+
+Our future goal is to extend the current framework to a three-dimensional Janus-vesicle system. 
+The further implementation of adding a fast algorithms such as the fast multipole method is also a 
+practical approach. Other physical properties of the bilayer membrane such as ......
+
 \begin{acknowledgments}

### 2021-08-25 doc/main_jfm.tex
conclusion draft

--- 2021-08-24 doc/main_jfm.tex
@@
 
+This study proposes a continuum coarse-grained model for Janus-vesicle that focuses on the 
+hydrophobic interactions between lipids and hydrodynamic interactions.
+The mobility problem using integral equation methods combines the previously introduced HAP and the 
+revised hydrophobic force for obtaining particle dynamics. 
+The imposed forces and torques of Janus particles adopt not only HAP but a newly developed short 
+range repulsion given by \ref{eq:REPULforce} and \ref{eq:REPULtorque}.
+The hydrodynamic stress tensor calculated in the algorithm leads to examinations of permeable 
+membrane where the stretching modulus $K_A$ and the permeability constant $P$ can be obtained.
+
+With the use of selected parameters, the numerical algorithm yields good qualitative results such as
+phenomena in tank-treading Janus-vesicle and asymmetric slipper shape in a parabolic flow. 
+We also demonstrate the membrane rupture in a flow at high shear rate and this makes a breakthrough 
+about having an idea for simulating such phenomenon different from other continuum modeling simulations.
+Inter-monolayer friction coefficients are then obtained and reported by calculating the pressure jumps and
+slip velocities with respect to the bilayer midplane.
+Results of two Janus-vesicles in flow simulations produce an outstanding agreement with ones generated 
+using continuum modeling.
+
+Our future goal is to extend the current framework to a three-dimensional Janus-vesicle system. 
+The further implementation of adding a fast algorithms such as the fast multipole method is also a 
+practical approach.
+
 \begin{acknowledgments}

### 2021-08-25 doc/main_jfm.tex
touched up intro

@@
 hybrid continuum model for the interactions between amphiphilic
-particles in a viscous solvent and formulating it in a boundary integral
+particles in a viscous solvent and with a boundary integral
 formulation,~\cite{Fu20} showed that the membrane granularity during
@@
 Janus-vesicle undergoes tank-treading in a shear flow and vertical
-migration in a channel flow. Furthermore we use the hybrid continuum
+migration in a Poiseuille flow. Furthermore we use the hybrid continuum
 model to investigate the inter-leaflet slippage and rupture of a bilayer
@@
 constraints, such as enforcing a non-positive space-time interference
-volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}), which
-guarantee that the suspension remains contact-free. These methods do not
-introduce stiffness, but potentially expensive nonlinear complementarity
-problems must be solved at each time step.  Repulsion-based contact
-methods, which we employ, introduce an artificial repulsion force that
-increases in strength as two particles approach one another
-(\cite{glo-pan-hes-jos-per2001, fen-mic2004, kab-qua-bir2018}). Strong
-repulsion forces can introduce numerical stiffness, but with the
-presence of the hydrophobic forces, we maintain a contact-free
-suspensions with a relatively weak non-stiff repulsive force.
+volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
+methods do not introduce stiffness, but potentially expensive nonlinear
+complementarity problems must be solved at each time step.
+Repulsion-based contact methods, which we employ, introduce an
+artificial repulsion force that increases in strength as two particles
+approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
+kab-qua-bir2018}). Strong repulsion forces can introduce numerical
+stiffness, but with the presence of the hydrophobic forces, we maintain
+contact-free suspensions with a relatively weak non-stiff repulsive
+force.
 
@@
 a far-field flow via the mobility problem formulation. In
-\S~\ref{validation} we present validation of our model, and in
-\S~\ref{results} we present simulation results for a single and pair of
-Janus-vesicles under various flowing conditions. Finally we provide
-discussion and outlook for future directions in \S~\ref{conclusion}.
+\S~\ref{validation} we validate our model, and in \S~\ref{results} we
+present simulation results for a single and pair of Janus-vesicles under
+various flowing conditions. Finally we provide discussion and outlook
+for future directions in \S~\ref{conclusion}.
 

### 2021-08-25 doc/main_jfm.tex
finished up section 2

@@
 \subsection{\label{mobility}Mobility Problem}
-We consider an $N_b$-many body collection of particles suspended in a
-two-dimensional unbounded domain $\Omega$. The boundary of each particle
-is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2
-\cup \cdots \cup \Gamma_{N_b}$ and $\nnu_i$ is the particle outward
-normal. Assuming the inertial terms are negligible, the governing
-equations are
+We consider an $N_b$-many body collection of Janus particles suspended
+in a two-dimensional unbounded domain $\Omega$. The boundary of each
+particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup
+\Gamma_2 \cup \cdots \cup \Gamma_{N_b}$. Assuming the inertial terms are negligible, the
+governing equations are
 \begin{alignat}{3}
@@
 %
-where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
-and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
-with center $\aa_i$ is a rigid body, its velocity satisfies 
+where $\uu$ is the velocity, $\mu$ is the constant viscosity, $p$ is the
+pressure, and $\uu_\infty$ is the background flow. Since each particle
+$\Gamma_i$ with center $\aa_i$ is a rigid body, its velocity satisfies 
 \begin{align}
@@
 where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
-\right)$ is the hydrodynamic stress tensor (pressure tensor).
-The process of finding the translational and angular velocities given a
-force and torque is referred to as the mobility problem.
+\right)$ is the hydrodynamic stress tensor (pressure tensor) and
+$\nnu_i$ is the particle outward normal. The process of finding the
+translational and angular velocities given the forces and torques is
+referred to as the mobility problem.
 
@@
 \label{eq:SLbc}
-u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i, \\
+u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b \\
 \label{eq:SLff}
@@
 \end{align}
-is the hydrophobic stress tensor. The parameter $\gamma$ is interfacial
-tension. The forces $\FF_i^{\text{hydro}}$ and torques
+is the hydrophobic stress tensor. The parameter $\gamma$ is the
+interfacial tension. The forces $\FF_i^{\text{hydro}}$ and torques
 $T_i^{\text{hydro}}$ are responsible for forming particle aggregates

### 2021-08-25 doc/main_jfm.tex
edited up to end of 3.1

@@
 \end{align}
-is the hydrophobic stress tensor. The parameter $\gamma$ is the
-interfacial tension. The forces $\FF_i^{\text{hydro}}$ and torques
+is the hydrophobic stress tensor. The parameter $\gamma$ is
+the interfacial
+tension. The forces $\FF_i^{\text{hydro}}$ and torques
 $T_i^{\text{hydro}}$ are responsible for forming particle aggregates
@@
 Integrals that are smooth are computed with the spectrally-accurate
-quadrature rule, and nearly-singular integrals, caused by close contact
+trapezoid rule, and nearly-singular integrals, caused by close contact
 between two particles, are computed with a high-order
-interpolation-based quadrature rule~\cite{qua-bir2014}. After
+interpolation-based quadrature rule (\cite{qua-bir2014}). After
 discretizing and applying quadrature, the resulting linear system is
@@
 \subsection{HAP Boundary Integral Equation}
-Similar to our previous work~\cite{Fu20}, we represent the HAP as a
+Similar to our previous work (\cite{Fu20}), we represent the HAP as a
 double-layer potential
@@
     K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
-    \quad \xx \in \mathbb{R}^2,
+    \quad \xx \in \Omega,
 \end{align}
@@
 the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
-Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. We
-solve~\eqref{eq:screenedSKIE} with a collocation method. The integrals
-are approximated with either the trapezoid rule or with the
-interpolation-based near-singular integration scheme. This results in a
-$NN_b \times NN_b$ linear system that is solved with a block-diagonal
-preconditioned GMRES solver.
+Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. After
+discretizing~\eqref{eq:screenedSKIE}, the result is a $NN_b \times NN_b$
+linear system that is solved with block-diagonal preconditioned GMRES.
 
@@
 double-layer potential~\eqref{eq:HAP_DLP} must be computed on the
-boundary of each particle. In Section~\ref{subsec:calculating_force}, we
-show that the force and torque calculations can be expressed in terms of
+boundary of each particle. The resulting integrands are singular, and
+specialized quadrature would be necessary to approximate such integrals.
+Alternatively, in Section~\ref{subsec:calculating_force}, we show that
+the force and torque calculations can be expressed in terms of
 non-singular integrals.

### 2021-08-25 doc/main_jfm.tex
edited up to end of Sec 3

@@
 \end{alignat}
-where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$, respectively $1$, representing
-hydrophilic, respectively hydrophobic, portions of the surface.  We assume that the $f_i$ and $\Gamma_i$ are
-smooth.  The parameter $\rho$ is the
-decay length of attraction. The forces and torques for this attraction
-are 
+where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$,
+respectively $1$, representing hydrophilic, respectively hydrophobic,
+portions of the surface. We assume that the $f_i$ and $\Gamma_i$ are
+smooth. The parameter $\rho$ is the decay length of attraction. The
+forces and torques for this attraction are 
 \begin{align}
@@
 \begin{align}
-%  \label{eq:REPUL}
-%  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\xx_{ij} -
-%  \yy_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
-%  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\xx_{ij} - \aa_i)^{\perp}\cdot
-%  \frac{\xx_{ij} - \yy_{ij}}{\rho_{ij}} P(\rho_{ij})
-%  \\
-%
   \label{eq:REPULforce}
@@
 \subsection{Mobility Problem Boundary Integral Equation}
-Following previous work of~\cite{Lukas19}, we represent the velocity as
-the sum of a double-layer potential and $N_b$ Stokeslets and Rotlets
+Following previous work of~\cite{Lukas19}, we use the velocity
+representation of~\cite{pow-mir1987}. In particular, we write the
+velocity as the sum of a double-layer potential and $N_b$ Stokeslets and
+Rotlets
 \begin{align}
@@
 \end{align}
-where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The Stokeslet is
-torque-free and has force $\FF_i$ while the Rotlet is force-free and has
-torque $T_i$. Therefore, the velocity~\eqref{eq:velocity} satisfies the
-total force~\eqref{eq:force} and torque~\eqref{eq:torque} conditions
-if the double-layer potential $\DD[\eeta]$ is force- and torque-free.
-Matching the limit of~\eqref{eq:velocity} with the rigid body motion,
-and imposing that $\DD[\eeta]$ is force- and torque-free, the density
-function $\eeta$, translational velocity $\vv_i$, and angular velocity
-$\omega_i$ satisfy
+respectively, where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The
+Stokeslet is torque-free and has force $\FF_i$ while the Rotlet is
+force-free and has torque $T_i$. Therefore, the
+velocity~\eqref{eq:velocity} satisfies the total force~\eqref{eq:force}
+and torque~\eqref{eq:torque} conditions if the double-layer potential
+$\DD[\eeta]$ is force- and torque-free.  Matching the limit
+of~\eqref{eq:velocity} with the rigid body motion, and imposing that
+$\DD[\eeta]$ is force- and torque-free, the density function $\eeta$,
+translational velocity $\vv_i$, and angular velocity $\omega_i$ satisfy
 \begin{alignat}{3}
@@
 
-The trapezoid rule is used to approximate the integrals in
-equations~\eqref{eq:mobility1} and~\eqref{eq:mobility2}, and the
-double-layer potential equation~\eqref{eq:SKIE} is approximated with
-either the trapezoid rule, or the interpolation-based near-singular
-integration scheme. After discretizing and applying appropriate
-quadrature rules, the result is a $(2NN_b + 3N_b) \times (2NN_b + 3N_b)$
-linear system that we precondition with a block-diagonal preconditioner.
-We note that other BIE formulations of the mobility problem use
-single-layer potentials (\cite{cor-gre-rac-vee2017, rac-gre2016}) or a
-combination of single- and double-layer potentials (\cite{cor-vee2018}).
-
-We validated our solver for \eqref{eq:SKIE}-\eqref{eq:mobility2} using a single elliptical particle 
-is suspended in a background shear flow; see Section \ref{sec:ves_in_shear}.
-Hydrophobic attraction and repulsion are zero for a single particle. 
-The angle of the ellipse's major axis coming from the integral equation method was in complete agreement 
-with the theoretical, Jeffrey oribit time-course \cite{}.
+After discretizing and applying appropriate quadrature rules, the result
+is a $(2NN_b + 3N_b) \times (2NN_b + 3N_b)$ linear system that we solve
+with block-diagonal preconditioned GMRES. We note that other BIE
+formulations of the mobility problem use single-layer potentials
+(\cite{cor-gre-rac-vee2017, rac-gre2016}) or a combination of single-
+and double-layer potentials (\cite{cor-vee2018}).
+
+We validated our solver for \eqref{eq:SKIE}-\eqref{eq:mobility2} using a
+single elliptical particle suspended in a background shear flow (see \S
+\ref{sec:ves_in_shear}). Hydrophobic attraction and repulsion are zero
+for a single particle. The angle of the ellipse's major axis coming from
+the integral equation method was in complete agreement with the
+theoretical, Jeffrey oribit time-course \cite{}.
 
@@
 \end{equation}
-on $\Gamma_i$. We get 
+on $\Gamma_i$. Therefore,
 \begin{align*}
@@
 &= 2\gamma\rho^{-1} \sigma v_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dv_i }{ds} \nnu
-- 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dv_i }{d\nu} \ttau = \JJ_i,
+- 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dv_i }{d\nu} \ttau = \JJ_i.
 \end{align*}
-Combing  this with \eqref{eq:prejump}  gives  \eqref{eq:recipforcetorque}
+Combing this with~\eqref{eq:prejump} gives~\eqref{eq:recipforcetorque}
 as required.

### 2021-08-27 doc/main_jfm.tex
added in-line data to 4.2

@@
 \uu \mapsto \uu \text{ nm ns}^{-1}, \quad 
-  p \mapsto p \text{ pN nm}^2.
+  p \mapsto p \text{ pN nm}^{-2}.
 \end{equation}
@@
 are for pN nm$^{-2}$.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
+\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
+\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
+  \caption{}
+    \label{figure:permeability}
+\end{figure}
 
@@
 \begin{equation}
+\label{eq:perm_solution}
 L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t
@@
 and compare with our data.
+
+Data obtained for the above model.
+Case 1. 58 particles with diameter 2.5 nm and $L_0 = 107$ nm. The calculated stretching modulus was $K_A = 109$ pN nm$^{-1}$ which gives 26.5 kT nm$^{-2}$.
+This value is in good agreement with the 60 kT nm$^{-2}$ from experimental measurements.  The calculated permeability was 
+$0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ = 
+$0.0296$ $\mu$m s$^{-1}$ Pa$^{-1}$. (double check value; too large)
+Case 2. 117 particles with diameter 1.25 nm and $L_0 = 141$ nm. This data set gave  $K_A = 62$ pN nm$^{-1}$ which gives 15 kT nm$^{-2}$ which is small.
+For permeability we get 0.0566 $\mu$m s$^{-1}$ Pa$^{-1}$.
+
+The dashed lines in panel (a) are the graphs of \eqref{eq:perm_solution} for the 58 and 117 particle number cases, respectively. 
+Panels (b) and (c) show the select data points with plusses for 58 particles and times for 117 particles.  The solid lines are linear fits.
+The linear fits in panel (b) shows that $R\Delta P$ is proportional to relative stretching $L/L_0 - 1$. The proportionality constant is $K_A.$
+The linear fits in panel (c) shows that $L\Delta P$ is proportional to flux $\frac{dA}{dt}$.  The proportionality constant is the permeability coefficient $P.$
 

### 2021-08-27 doc/main_jfm.tex
touched up 3.3

@@
 \label{subsec:calculating_force}
-Once \eqref{eq:SKIE} has been solved for $\sigma$, we need to evaluate
-the integrals~\eqref{eq:hydrophobicAttraction}. These integrals involve
-the stress \eqref{eq:stress} which contains a singular integral for the
+Once \eqref{eq:screenedSKIE} has been solved for $\sigma$, we need to
+evaluate the integrals~\eqref{eq:hydrophobicAttraction} which are the
+HAP forces and torques. These integrals involve the
+stress~\eqref{eq:stress} which contains a singular integral for the
 gradient of the double-layer potential. To avoid singular integrals, we
-evaluate \eqref{eq:hydrophobicAttraction} using the identities
+first define
+\begin{align}
+  \label{eq:uidef}
+  v_i(\xx) = u(\xx) - u_i(\xx),
+\end{align}
+where
+\begin{align}
+  u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
+    \quad \xx \in \mathbb{R}^2.
+\end{align}
+That is, $v_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
+with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $v_i$, we can
+show that
 \begin{align}
@@
     2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{ds} \nnu -
-    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{d\nu} \ttau.
+    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{d\nnu} \ttau.
 \end{align}
 Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc length
-derivative for $\Gamma_i$, respectively, and
-\begin{equation}
-\label{eq:uidef}
-\begin{aligned}
-    u(\xx) &= u_i(\xx) + v_i(\xx),\\
-    u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
-    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
-    \quad \xx \in \mathbb{R}^2.
-\end{aligned}
-\end{equation}
-That is, $v_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP} with 
-$\Gamma_i$ excluded from $\bd\Omega$. The advantage in
-using \eqref{eq:recipforcetorque} over using \eqref{eq:hydrophobicAttraction} is that the components
-$\sigma$, $v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ of $\JJ_i$ are smooth functions,
-whereas the components of \eqref{eq:stress} are singular integrals.
+derivative for $\Gamma_i$, respectively, and $\nnu$ is the unit normal.
+The advantage in using~\eqref{eq:recipforcetorque} over
+using~\eqref{eq:hydrophobicAttraction} is that the components $\sigma$,
+$v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ of $\JJ_i$ are smooth
+functions, whereas the components of \eqref{eq:stress} are singular
+integrals.
+
+%To avoid singular integrals, we
+%evaluate~\eqref{eq:hydrophobicAttraction} using the identities
+%\begin{align}
+%  \label{eq:recipforcetorque}
+%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
+%  T_i^{\text{hydro}}    = \int_{\Gamma_i} 
+%    (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
+%\end{align}
+%where
+%\begin{align}
+%  \label{eq:jumpstress1}
+%  \JJ_{i} = 2\gamma\rho^{-1} \sigma v_i \nnu + 
+%    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{ds} \nnu -
+%    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{d\nu} \ttau.
+%\end{align}
+%Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent  and arc length
+%derivative for $\Gamma_i$, respectively, and
+%\begin{equation}
+%\label{eq:uidef}
+%\begin{aligned}
+%    u(\xx) &= u_i(\xx) + v_i(\xx),\\
+%    u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
+%    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
+%    \quad \xx \in \mathbb{R}^2.
+%\end{aligned}
+%\end{equation}
+%That is, $v_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP} with 
+%$\Gamma_i$ excluded from $\bd\Omega$. The advantage in
+%using \eqref{eq:recipforcetorque} over using \eqref{eq:hydrophobicAttraction} is that the components
+%$\sigma$, $v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ of $\JJ_i$ are smooth functions,
+%whereas the components of \eqref{eq:stress} are singular integrals.
 

### 2021-08-27 doc/main_jfm.tex
starting sec 5

@@
 
-Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of 
-Janus-vesicles under a number of flows. To extract physical quantities of the target structure using the
-proposed model, the scaling laws and the dimensionless units are given as follows.
-The length unit is scaled by the length of phospholipids $l=2.5$ nm which is set as the diameter of each 
-Janus particle. The force is scaled from the interfacial tension $\gamma=4.11$ pN nm$^{-1}$ 
-from ~\cite{Ryham16}. This also means that the energy unit is scaled by $1\ k_BT$. We then be able to
-calculate the characteristic time scale $\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP.
-With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
-%
-For the model parameters, the decay length of attraction $\rho = 2l = 5$ nm, the repulsion length scale is 
-$\rho_0=0.5$, and the repulsion strength $M=4.0\ k_BT$.
-The dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ is the shear rate.
+Following the relaxation experiments we consider the behavior of
+Janus-vesicles under various flows. To extract physical quantities of
+the target structure, we introduce the following scaling laws and the
+dimensionless units. The length unit is scaled by the length of
+phospholipids $l=2.5$~nm which is the diameter of each Janus particle.
+The force is scaled by the interfacial tension $\gamma=4.11$~pN
+nm$^{-1}$ from~\cite{Ryham16}. This means that the energy unit is scaled
+by $1\ k_BT$. We can then define the characteristic time scale $\tau =
+\mu l/\gamma = 0.61$~ns where the fluid viscosity is $\mu=1$ cP.  With
+the same framework,~\cite{Fu20} provide the bending rigidity
+$\kappa=8.51$~$k_BT$. For the model parameters, the decay length of
+attraction is $\rho = 2l = 5$~nm, the repulsion length scale is
+$\rho_0=0.5$, and the repulsion strength is $M=4.0$~$k_BT$. Finally, the
+dimensionless shear rate is $\chi = \dot\gamma \tau$ where $\dot\gamma$
+is the shear rate.
 

### 2021-08-28 doc/main_jfm.tex
working on shear example

@@
 \label{sec:ves_in_shear}
-To study the deformation of a Janus-vesicle under a shear flow using the proposed algorithm, 
-we adopt a widely tested numerical simulation in both continuum and molecular dynamics models, single vesicle under a shear flow. 
-The background flow is a shear flow 
-\begin{equation}
-\uu_{\infty}(\xx) = \dot\gamma  \xx \cdot \mathbf{e}_2 \mathbf{e}_1
-\end{equation}
-with shear rate $\dot\gamma$
-and orthogonal unit vectors $\mathbf{e}_x$ and $\mathbf{e}_y$ for the horizontal and vertical directions respectively. 
-The well known results indicate that the vesicle has tank-treading behavior when 
-there is no viscosity contrast in both fluids inside and outside of the vesicle.
-Within the framework of the simulation setup, the proposed model provides a feature that the fluid viscosity is constant over the computational domain and it is capable of performing these simulations.
-
-The centroid of the pre-relaxed $58$-body Janus vesicle is initially placed at the origin then the shear flow 
-with a certain shear rate $\chi$ is then turned on. 
-The snapshots of the simulation for single vesicle in a shear flow with a shear rate $\chi=0.0025$ are shown 
-in Figure~\ref{figure3}.
-Panels (a)-(b) show the initial shape obtained from the relaxation run and the deformed 
-configuration of the Janus-vesicle after a period of time ($t=4000$) is in panels (c)-(d). 
-The background color in panels (a) and (c) presented in the figure is the strength of the action due to the
-hydrophobic attraction. From weak to strong action field, the color varies from blue to red. Clearly, the
-hydrophobic layer has the largest action. To demonstrate the tank-treading behavior of the vesicle, panels (b) 
-and (d) provide the streamlines of the fluid velocity over the whole computational domain when the shear 
-flow passes through the structure. The tank-treading motion of the structure is then observed, for instance,
-the particle velocities in panel (d) indicate a clockwise tank-treading movement.
+We begin by studying the dynamics of a single Janus-vesicle suspended in
+the shear flow
+\begin{align}
+  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_2) \mathbf{e}_1,
+\end{align}
+with shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_1$
+and $\mathbf{e}_2$ for the horizontal and vertical directions
+respectively. It is well known that a vesicle has tank-treading behavior
+when there is no viscosity contrast between the fluids inside and
+outside of the vesicle.
+%Within the framework of the simulation setup,
+%the proposed model provides a feature that the fluid viscosity is
+%constant over the computational domain and it is capable of performing
+%these simulations.
+
+The centroid of the pre-relaxed $58$-body Janus vesicle is initially
+placed at the origin and the shear flow with a certain shear rate $\chi$
+is applied. Snapshots of the Janus-vesicle in a shear flow with a shear
+rate $\chi=0.0025$ are shown in Figure~\ref{figure3}. Panels (a) and (b)
+show the initial shape obtained from the relaxation run and the deformed
+configurations of the Janus-vesicle at time $t=4000$ are in panels (c)
+and (d). The background color in panels (a) and (c) is the strength of
+the action of the hydrophobic attraction. Red corresponds to a strong
+action while blue is weak action. The hydrophobic layer clearly has the
+strongest action. To demonstrate the tank-treading behavior of the
+vesicle, panels (b) and (d) provide the streamlines of the fluid
+velocity around the Janus-vesicle. In panel (d), we can clearly observe
+the clockwise tank-treading motion.
 
@@
 \includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
-  \caption{Vesicle under a shear flow where the shear rate $\chi=0.0025$: 
-  (a) Initial configuration of 58-body Janus-vesicle where black arrows are the particle orientations; 
-  (b) The fluid velocity plot with respect to the configuration in (a); Streamlines are plotted in the background
-  as solid curves. Red arrows represent the particle velocities.
-  (c) Deformed vesicle after $20000$ steps. The tank-treading motion occurs after reaching the state shown in panel (c).
-  (d) The fluid velocity plot with respect to the configuration in (c);
-  The background colors in panels (a) and (c) represent the strength of the hydrophobic attraction potential.
-The blue region shows no action and the red region in the bilayer gives the strongest action.
-  }
-    \label{figure3}
+  \caption{\label{figure3} A Janus-vesicle suspended in a shear flow
+  with shear rate $\chi=0.0025$: (a) Initial configuration of 58-body
+  Janus-vesicle where black arrows are the particle orientations. (b)
+  The particle velocities and streamlines of the configuration in (a).
+  Streamlines are plotted in the background as solid curves. Red arrows
+  represent the particle velocities. (c) Deformed Janus-vesicle at
+  $t=4000$. At this configuration the Janus-vesicle is tank-treading.
+  (d) The particle velocities and streamlines of the configuration in
+  (c). The background colors in panels (a) and (c) represent the
+  strength of the hydrophobic attraction potential. The blue region
+  shows no action and the red region in the bilayer gives the strongest
+  action.}
 \end{figure}
@@
 %
-
-In order to extract more physical properties of the proposed model, we track the total length of the bilayer structure, the reduced area over the time, and the excess length.
-Here the enclosed area and the total length of the structure are calculated from the midplane.
-These results are shown in Figure~\ref{figure4} where we compare results from the use of a set of shear 
-rates $\chi=\{0.002,0.0025,0.003,0.0035\}$. 
-The reduced area is given by $A^* = 4\pi A/L^2$ where $A$ the area, and $L$ the total length of the Janus-vesicle with respect to the midplane. 
-Furthermore, the excess length is given by $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
-Since the starting configuration is close to a circular shape, the reduced area decreases from a value very close to $1$.
-For the test cases in Figure~\ref{figure4}, the smooth curves in panel (a) are fitted using an
-exponential model given by $A^* = a_0 + b_0 \exp(-kt)$.
-Panel (b) shows that the decay rate $k$ is independent of the shear rate when the shear is above a threshold and the terminal reduced areas for each
-case of the shear rates are given in the inset. It is also clear that a slower shear rate generates a higher terminal reduced area and has a faster convergence then the high shear rate cases. 
-With a converging total arc length as shown in panel (c), a slower shear rate also produces a smaller excess length shown in panel (d).
-In summary, the small oscillations in all results are due to the granularity of the Janus-vesicle which tend to having slightly non-smooth curves in simulations.
-Overall the total lengths of the bilayer have the same converging value in all test shear rates.
-Moreover, based on the numerical experiments, we observe that the reduce area converges relatively early when the shear rate is lower than $\chi=0.003$.
+\todo[inline]{Bryan left off here}
+In order to extract more physical properties of the proposed model, we
+track the total length of the bilayer structure, the reduced area over
+the time, and the excess length. Here the enclosed area and the total
+length of the structure are calculated from the midplane.  These results
+are shown in Figure~\ref{figure4} where we compare results from the use
+of a set of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$.  The
+reduced area is given by $A^* = 4\pi A/L^2$ where $A$ the area, and $L$
+the total length of the Janus-vesicle with respect to the midplane.
+Furthermore, the excess length is given by
+$\Delta=L/\sqrt{A^*/\pi}-2\pi$.  Since the starting configuration is
+close to a circular shape, the reduced area decreases from a value very
+close to $1$. For the test cases in Figure~\ref{figure4}, the smooth
+curves in panel (a) are fitted using an exponential model given by $A^*
+= a_0 + b_0 \exp(-kt)$. Panel (b) shows that the decay rate $k$ is
+independent of the shear rate when the shear is above a threshold and
+the terminal reduced areas for each case of the shear rates are given in
+the inset. It is also clear that a slower shear rate generates a higher
+terminal reduced area and has a faster convergence then the high shear
+rate cases.  With a converging total arc length as shown in panel (c), a
+slower shear rate also produces a smaller excess length shown in panel
+(d).  In summary, the small oscillations in all results are due to the
+granularity of the Janus-vesicle which tend to having slightly
+non-smooth curves in simulations. Overall the total lengths of the
+bilayer have the same converging value in all test shear rates.
+Moreover, based on the numerical experiments, we observe that the reduce
+area converges relatively early when the shear rate is lower than
+$\chi=0.003$.
 

### 2021-08-28 doc/main_jfm.tex
working on shear

@@
 %
-\todo[inline]{Bryan left off here}
-In order to extract more physical properties of the proposed model, we
-track the total length of the bilayer structure, the reduced area over
-the time, and the excess length. Here the enclosed area and the total
-length of the structure are calculated from the midplane.  These results
-are shown in Figure~\ref{figure4} where we compare results from the use
-of a set of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$.  The
-reduced area is given by $A^* = 4\pi A/L^2$ where $A$ the area, and $L$
-the total length of the Janus-vesicle with respect to the midplane.
-Furthermore, the excess length is given by
-$\Delta=L/\sqrt{A^*/\pi}-2\pi$.  Since the starting configuration is
-close to a circular shape, the reduced area decreases from a value very
-close to $1$. For the test cases in Figure~\ref{figure4}, the smooth
-curves in panel (a) are fitted using an exponential model given by $A^*
-= a_0 + b_0 \exp(-kt)$. Panel (b) shows that the decay rate $k$ is
-independent of the shear rate when the shear is above a threshold and
-the terminal reduced areas for each case of the shear rates are given in
-the inset. It is also clear that a slower shear rate generates a higher
-terminal reduced area and has a faster convergence then the high shear
-rate cases.  With a converging total arc length as shown in panel (c), a
-slower shear rate also produces a smaller excess length shown in panel
-(d).  In summary, the small oscillations in all results are due to the
-granularity of the Janus-vesicle which tend to having slightly
-non-smooth curves in simulations. Overall the total lengths of the
-bilayer have the same converging value in all test shear rates.
-Moreover, based on the numerical experiments, we observe that the reduce
-area converges relatively early when the shear rate is lower than
-$\chi=0.003$.
+
+To extract additional physical properties of the proposed model, we
+compute the total length, reduced area, and excess length of the bilayer
+structure. The enclosed area and the total length of the structure are
+calculated from the midplane. The reduced area is $A^* = 4\pi A/L^2$
+where $A$ the area, and $L$ the total length of the Janus-vesicle, and
+the excess length is $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
+Figure~\ref{figure4} shows these quantities for a Janus-vesicle
+suspended in a shear flow with shear rates
+$\chi=\{0.002,0.0025,0.003,0.0035\}$. Since the starting configuration
+is nearly circular, the reduced area decreases from an initial value
+close to $1$. The smooth curves in panel (a) are best fits of the
+exponential model $A^* = a_0 + b_0 \exp(-kt)$. Panel (b) shows that the
+decay rate $k$ is independent of the shear rate for sufficiently large
+shear rates, and the terminal reduced areas of each case are shown in
+the inset. We see that lower shear rates generate a higher final reduced
+area. In particular, we observe that the reduce area converges
+relatively early when the shear rate is lower than $\chi=0.003$. 
+%and has a faster convergence than the high shear rate cases.
+Panel (c) shows that the total arc length remains constant for all time
+with all four shear rates. Combining the behavior of the reduced area
+and the total arc length, the excess length must increase in time and be
+larger for higher shear rates as observed in panel (d). In all these
+results, there are oscillations that can be explained by the granularity
+of the Janus-vesicle which results in a midplane that is non-smooth.
+%Overall the total lengths of the bilayer have the same converging value
+%in all test shear rates.
 
@@
 \end{center} 
-  \caption{(a) Total arc lengths of the midplanes over time in cases of different shear rates; (b) From exponential fits in panel (a), we obtain the decay rate $k$ for a number of different shear rates.
-The inset plots the terminal reduced areas; (c) Reduced area transitions over time; (d) Excess length of the midplanes.
-For all panels, a set of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
-The legend in panel (d) applies to both panels (a) and (c). 
-  }
-    \label{figure4}
+  \caption{\label{figure4} (a) Total arc lengths of the midplanes over
+  time for four shear rates. (b) From exponential fits in panel (a), we
+  obtain the decay rate $k$ for a number of different shear rates. The
+  inset plots the terminal reduced areas. (c) Reduced area transitions
+  over time. (d) Excess length of the midplanes. For all panels, a set
+  of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in
+  simulations. The legend in panel (d) applies to both panels (a) and
+  (c).}
 \end{figure}

### 2021-08-28 doc/main_jfm.tex
working on numerical results

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{\label{intro}Introduction}
@@
 \begin{align}
-  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_2) \mathbf{e}_1,
-\end{align}
-with shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_1$
-and $\mathbf{e}_2$ for the horizontal and vertical directions
+  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
+\end{align}
+with shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
+and $\mathbf{e}_y$ for the horizontal and vertical directions,
 respectively. It is well known that a vesicle has tank-treading behavior
@@
 
-\subsubsection{Intermonolayer friction}
-An interesting phenomenon also rises up in the proposed setup where the inter-monolayer slip occurs 
-between two leaflets. When a shear rate is large enough, take $\chi = 0.005$ as an example, 
-Figure~\ref{figure5} shows the schematic of the test where a particle pair is initially marked and we then track the positions of this particle pair over a period of time. 
-In this series of tests, we monitor the mean particle position change and mean angle $\theta(t)$ between particle relative positions with respect to the vesicle center over the time.
-It is clear to see that the outer leaflet always has larger tangential velocity than the one from the inner leaflet and the mean angle $\theta(t)$ increases.
-This inter-leaflet sliding phenomenon is consistent with what has been seen
-in articles in molecular dynamics simulations.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Intermonolayer Friction}
+The granulated Janus-vesicle allows us to consider inter-monolayer slip
+between two leaflets. When the shear rate is sufficiently large, take
+$\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip between a
+pair of particles over time. The pair we consider are colored in blue
+and yellow. In this series of tests, we compute the mean particle
+position and mean angle $\theta(t)$ between the particle relative
+positions with respect to the vesicle center. It is clear that the outer
+leaflet has larger tangential velocity than the inner leaflet since the
+mean angle $\theta(t)$ increases. This inter-leaflet sliding phenomenon
+is consistent with what has been seen in articles in molecular dynamics
+simulations.
 
@@
 \end{center} 
-  \caption{The schematic of the intermonolayer slip over a period of time.
-Taking shear rate $\chi=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position.
-The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=2000$ and $t=9000$.
-The midplane curve is denoted as $\Sigma_M$.
-We provide numerical results of $\theta(t)$ for cases of shear rates $\chi$.
-  }
-    \label{figure5}
+  \caption{\label{figure5} The schematic of the intermonolayer slip over
+  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
+  mean angle between each particle pair $\theta(t)$ where the angle is
+  calculated from the relative position of the particles with respect to
+  the Janus-vesicle's center of mass. The configuration plots have two
+  fixed particles marked in yellow and blue and labeled with the
+  corresponding time $t=2000$ and $t=9000$. The midplane curve is
+  denoted as $\Sigma_M$. We see that the intermonolayer slip is largest
+  at larger shear rates.}
 \end{figure}
 
-To calculate the inter-monolayer friction coefficient for the apposing JP leaflets, we let  
-\begin{equation}
-b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle },
-\end{equation}
-%
-where $\langle F\rangle = \langle \int_{\mathcal{C}_M} \jump{\ttau \cdot \sigma \cdot \nnu} \,ds\rangle$ 
-is the time-averaged, tangential force along the midplane curve $\mathcal{C}_m$. 
-The parameters $\langle L\rangle$ and $\langle U\rangle$ are the time-averaged midplane curve length and
-intermonolayer slip velocity respectively.
-
-We calculate $\langle F\rangle$ by first evaluating the smooth tangential force along curves a positive distance inside and 
-outside $\mathcal{C}_m$ respectively, and then interpolating at zero distance to give a force jump. 
-We have made a slight abuse of language: due to the problem being two-dimensional,
-the integral $\langle F\rangle$ is actually a force density per length which when divided by length gives the requisite force per area. 
+To calculate the inter-monolayer friction coefficient for the apposing
+JP leaflets, we let
+\begin{align}
+  b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle},
+\end{align}
+%
+where $\langle F\rangle = \langle \int_{\mathcal{C}_M} \jump{\ttau \cdot
+\sigma \cdot \nnu} \,ds\rangle$ is the time-averaged, tangential force
+along the midplane curve $\mathcal{C}_m$. The parameters $\langle
+L\rangle$ and $\langle U\rangle$ are the time-averaged midplane curve
+length and intermonolayer slip velocity respectively.
+
+We calculate $\langle F\rangle$ by first evaluating the smooth
+tangential force along curves a positive distance inside and outside
+$\mathcal{C}_m$ respectively, and then interpolating at zero distance to
+give a force jump. We have made a slight abuse of language: due to the
+problem being two-dimensional, the integral $\langle F\rangle$ is
+actually a force density per length which when divided by length gives
+the requisite force per area. 
 %which when divided by length
 
-Table~\ref{table1} provides dimensional friction coefficients $b$ for several shear rates
-and the results are in quantitative agreement with 
-values previously reported in the literature~\cite{sch-vla-mik2010} and~\cite{denOtter2007}.  
-The coefficients generally lie within the range 0.2 to 0.3 pN$\cdot$ns nm$^{-3}$ but there are some 
-outliers.  These outliers ($\dot\gamma = 0.0041$ ns$^{-1}$ and 
-$\dot\gamma = 0.0066$ ns$^{-1}$) correspond to slip velocities that are too low relative to shear rate (see the green and red curve in Figure \ref{figure5}: panel (c)).
-The JP vesicle consists of only  58 particles and so it is not surprising that discrete effects produce outliers.
-
-\todo[inline]{If $B$ is the numerically calculated friction coefficient,  then 
-$b = B/2.5^3$ pN ns nm$^{-3}$ gives the dimensional value.
-
-If $P$ is the numerically calculated pressure, then $p = P/2.5$ pN nm$^{-2}$ is the dimensional pressure.}
+Table~\ref{table1} provides dimensional friction coefficients $b$ for
+several shear rates and the results are in quantitative agreement with
+values previously reported in the literature~\cite{sch-vla-mik2010}
+and~\cite{denOtter2007}. The coefficients generally lie within the
+range 0.2 to 0.3 pN$\cdot$ns nm$^{-3}$ but there are some outliers.
+These outliers ($\dot\gamma = 0.0041$ ns$^{-1}$ and $\dot\gamma =
+0.0066$ ns$^{-1}$) correspond to slip velocities that are too low
+relative to shear rate (see the green and red curve in Figure
+\ref{figure5}: panel (c)). The JP vesicle consists of only 58
+particles and so it is not surprising that discrete effects produce
+outliers.
+
+\todo[inline]{If $B$ is the numerically calculated friction coefficient,
+then $b = B/2.5^3$ pN ns nm$^{-3}$ gives the dimensional value.
+
+If $P$ is the numerically calculated pressure, then $p = P/2.5$ pN
+nm$^{-2}$ is the dimensional pressure.}
 
@@
 \subsubsection{Vesicle in a Parabolic Flow}
-
-Besides the tests of a Janus-vesicle in a shear flow, an interesting test can also use the proposed model and the setup.
-Consider a symmetric parabolic flow about the $x$-axis, \cite{Kaoui09} studied shapes of the red blood cell immersed in a parabolic flow using a continuum model.
-With a similar setup, the background flow for this set of simulations is given by
-\begin{equation}
-\uu_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
-\end{equation}
-%
-where $v_{max}$ is the flow strength and $w$ controls the shape of the flow. $R_0$ is defined as the radius of the Janus-vesicle at $t=0$.
-
-Figure~\ref{figure6} gives three configurations for one specific case where the centroid of the Janus-vesicle is initially placed slightly above the $x$-axis.
-The parameters are $v_{max} = 8.0$, $w=10$, and $R_0=8$.
-The red curves are the midplanes and a particle pair is marked in color.
-We observe that the deformed
-Janus-vesicle has a counterclockwise movement and the shape of the vesicle approaches to an asymmetric
-slipper shape.
-For this test run, the reduced area for this configuration is $\sim0.9$ which matches the previous numerical tests in \cite{Kaoui09} where a slipper-like shape occurs when the flow velocity is weak and the reduced area is large.
-A schematic of the setup is shown in Figure~\ref{figure7} where the blue horizontal line represents the mean
-$y$-position of all particles. The inset of Figure~\ref{figure7} shows the trajectory of the mean position in 
-$y$-direction which decreases toward $y=1$ for a period of time and starts to have an oscillatory motion.
+Another interesting flow to consider is the parabolic flow
+\begin{align}
+  \uu_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2
+    \right]\mathbf{e}_x,
+\end{align}
+%
+where $v_{max}$ is the flow strength and $w$ controls the shape of the
+flow. $R_0$ is defined as the radius of the Janus-vesicle at $t=0$.
+The behavior of a vesicle in this unbounded non-linear flow includes
+vertical migration, and depending on the flow rate and reduced area,
+the steady-state shape can be either an symmetric parachute or
+an asymmetric slipper~\cite{Kaoui09, cou-kao-pod-mis2008,
+dan-vla-mis2009}.
+
+%Besides the tests of a Janus-vesicle in a shear flow, an interesting
+%test can also use the proposed model and the setup. Consider a
+%symmetric parabolic flow about the $x$-axis,~\cite{Kaoui09} studied
+%shapes of the red blood cell immersed in a parabolic flow using a
+%continuum model. With a similar setup, the background flow for this set
+%of simulations is given by
+
+Figure~\ref{figure6} shows three configurations for one specific case
+where the centroid of the Janus-vesicle is initially placed slightly
+above the $x$-axis. The parameters are $v_{max} = 8.0$, $w=10$, and
+$R_0=8$. The red curves are the midplanes and a particle pair is marked
+in color. We observe that the deformed Janus-vesicle has a
+counterclockwise movement and the shape of the vesicle approaches an
+asymmetric slipper shape. For this test, the reduced area for this
+configuration is approximately $0.9$ which matches the previous
+numerical tests in~\cite{Kaoui09} where a slipper-like shape occurs when
+the flow velocity is weak and the reduced area is large. A schematic of
+the setup is shown in Figure~\ref{figure7} where the blue horizontal
+line represents the mean $y$-position of all particles. The inset of
+Figure~\ref{figure7} shows the trajectory of the mean position in the
+$y$-direction which decreases toward $y=1$ for a period of time and then
+starts to have an oscillatory motion due to the granularity of the
+Janus-vesicle.
 
@@
 \includegraphics[width=0.8\textwidth]{slipper.eps}
-  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=32.8$ nm ns$^{-1}$, $R_0 = 20$ nm,  and the control parameter $w=10$.
-The configuration is the state when $t=\{0, 4000, 8000\}$.
-Red curves are midplanes of three configurations.
-  }
-    \label{figure6}
+  \caption{\label{figure6} A Janus-vesicle suspended in a parabolic flow
+  where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
+  20$~nm, and the control parameter is $w=25$~nm. The configuration is
+  the state when $t=\{0, 4000, 8000\}$. The red curves are the
+  midplanes.}
 \end{figure}
@@
 \includegraphics[height=2in]{parabolic.eps}
-  \caption{Schematic of a Janus-vesicle under a parabolic flow where the strength of the flow $v_{max}=32.8$ nm ns$^{-1}$, $R_0 = 20$ nm,  and the control parameter $w=10$.
-The configuration is generated when $t=10000$.
-The inset plots the trajectory of mean $y$-position over the time.
-  }
-    \label{figure7}
+  \caption{\label{figure7} The schematic of a Janus-vesicle suspended in
+  a parabolic flow where the strength of the flow is $v_{max}=32.8$~nm
+  ns$^{-1}$, $R_0 = 20$~nm, and the control parameter is $w=25$~nm. The
+  configuration is generated when $t=10000$. The inset plots the
+  trajectory of mean $y$-position over the time.}
 \end{figure}
@@
 
-With the choice of a large shear rate, a pore formation or a complete membrane rupture can be captured during simulations.
-Figure~\ref{figure8} shows a demonstration of a vesicle under a shear flow with shear rate $\chi=0.1$.
-An interesting phenomenon occurs in panels (c) and (d) where two separated bilayers move along the background shear flow symmetrically.
-Consequently, a periodic motion for bilayers may occur
-with the choices of shear rates. One can expect that these two layers will flow far apart from each other for much higher shear rates.
+With the choice of a large shear rate, a pore formation or a complete
+membrane rupture can occur. Figure~\ref{figure8} demonstrates how a
+vesicle under a shear flow with shear rate $\chi=0.1$ can rupture. The
+streamlines are included in these plots. An interesting phenomenon
+occurs in panels (c) and (d) where two separated bilayers move along the
+background shear flow symmetrically.  Consequently, a periodic motion
+for bilayers may occur with the choices of shear rates. One can expect
+that these two layers will flow far apart from each other for much
+higher shear rates.
 
@@
 \includegraphics[height=2in]{N58_rupt_600.pdf}
-  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold.
-Here the shear rate is $\chi = 0.1$.
-Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)).
-(c)-(d) are the later states during the simulation.
-  }
-    \label{figure8}
+  \caption{\label{figure8} Membrane rupture occurs when the shear rate
+  exceeds a threshold. Here the shear rate is $\chi = 0.1$.  Starting
+  with a circular shape (panel (a)), the vesicle is stretched by the
+  background flow and multiple pores appear (panel (b)).  Panels
+  (c)--(d) show the later states during the simulation. Streamlines are
+  included in each panel.}
 \end{figure}
@@
 \end{center} 
-  \caption{Trajectories of two-vesicle in a shear flow.
-The moving paths of two centroids of two Janus-vesicles are plotted in blue and red.
-Both starting centroids of two Janus-vesicles are on the $x$-axis.
-For simulation time, $t = {0, 400,800,1200}$ for (a)-(d) and $t = {1600, 2400, 3200, 4000}$ for (e)-(h).}
-    \label{figure9}
+  \caption{\label{figure9} The shape and trajectories of two
+  Janus-vesicles in a shear flow. The moving paths of the two centroids
+  are plotted in blue and red. The centroids are initially located on
+  the $x$-axis. For simulation time, $t = {0, 400,800,1200}$ for
+  (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).}
 \end{figure}
@@
 \includegraphics[height=2in]{N116_shear_7500.pdf}
-  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a).
-The background color indicates the magnitude of fluid pressure.
-From dark red to dark blue, it represents the the pressure varies from high to low values.
-The color bar is valid for all panels.
-Streamlines are plotted in purple.
-The insets of all panels are generated from the results of continuum modeling simulations and the streamlines have a perfect agreement to the numerical results.
-  }
-    \label{figure10}
+  \caption{\label{figure10} Two Janus-vesicles under a shear flow where
+  the dimensioneless shear rate is $\chi=0.005$. The initial
+  configuration is shown in panel (a). The background color is the
+  magnitude of fluid pressure. The color bar is identical for all
+  panels. Streamlines are plotted in purple. The insets of all panels
+  are generated from simulations of a continuum model of the vesicle and
+  the streamlines agree between the two models.}
 \end{figure}
 
+\todo[inline]{Bryan left off here}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Figure~\ref{figure9} demonstrates the simulation results of two Janus-vesicles in a shear flow where the testing shear rate is $\chi=0.005$ and the flow is given by $\dot x = \chi y$. 
-In panel (a), the starting frame, two center-of-mass positions are placed 
-on the same horizontal level, at $(-10,0)$ and $(10,0)$.
-Since we already have a pre-relaxed $58$-body in previous sections, we duplicate the state to have the initial configuration (shown in panel (a)) in this section.
-In all panels, the blue and red curves represent the moving paths of two Janus-vesicle centroids and they move nearly a round when $t=4000$ as shown in panel (h). 
-We observe that the rotation continues as time goes and an interesting event occurs in the simulation that an adhesive effect can be seen and tuned.
-In other words, the adhesive behavior will be absent when two vesicles are centered at a different level and are well separated in $y$-direction.
-
-The fluid pressure profiles of snapshots are given in Figure~\ref{figure10}.
-As expected, there is no pressure jump between the internal and external fluids from the beginning of the
-simulation and this is shown in the background pressure plot. 
-Panels (b)-(d) show the configurations when $t = \{500,1000,1500\}$ and 
-the streamlines are plotted in the background for all panels. We include the numerical results using 
-a continuum model in all insets and these comparisons give a qualitative agreement between two models.
+Figure~\ref{figure9} demonstrates the simulation results of two
+Janus-vesicles in a shear flow where the testing shear rate is
+$\chi=0.005$ and the flow is given by $\dot x = \chi y$. In panel (a),
+the starting frame, two center-of-mass positions are placed on the same
+horizontal level, at $(-10,0)$ and $(10,0)$. Since we already have a
+pre-relaxed $58$-body in previous sections, we duplicate the state to
+have the initial configuration (shown in panel (a)) in this section. In
+all panels, the blue and red curves represent the moving paths of two
+Janus-vesicle centroids and they move nearly a round when $t=4000$ as
+shown in panel (h). We observe that the rotation continues as time goes
+and an interesting event occurs in the simulation that an adhesive
+effect can be seen and tuned. In other words, the adhesive behavior will
+be absent when two vesicles are centered at a different level and are
+well separated in $y$-direction.
+
+The fluid pressure profiles of snapshots are given in
+Figure~\ref{figure10}. As expected, there is no pressure jump between
+the internal and external fluids from the beginning of the simulation
+and this is shown in the background pressure plot. Panels (b)-(d) show
+the configurations when $t = \{500,1000,1500\}$ and the streamlines are
+plotted in the background for all panels. We include the numerical
+results using a continuum model in all insets and these comparisons give
+a qualitative agreement between two models.
 

### 2021-08-28 doc/main_jfm.tex
still working on results sections

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Shear Flow}
+
+Figure~\ref{figure9} shows the simulation of two Janus-vesicles in a
+shear flow with shear rate $\chi=0.005$. Using the pre-relaxed $58$-body
+Janus-vesicle in previous sections, we duplicate the state to have the
+initial configuration shown in panel (a). The two centers of mass are at
+$(-10,0)$ and $(10,0)$. In all panels, the blue and red curves show the
+trajectory of the two Janus-vesicle centroids. They have nearly
+completed a full period by $t=4000$ as shown in panel (h). We also
+observe an adhesive effect between the two Janus-vesicles that is set up
+by the hydrophobic interactions and repulsive force. Similar dynamics
+have been observed between a pair of adhering vesicles in a shear flow
+(\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
+behavior is absent when two Janus-vesicles are well-separated.
+
+The fluid pressure profiles snapshots are given in
+Figure~\ref{figure10}. Since the initial Janus-vesicles are pre-relaxed,
+there is initially no pressure jump between the internal and external
+fluids (panel (a)). Panels (b)--(d) show the configurations when $t =
+\{500,1000,1500\}$ and the streamlines are plotted in the background for
+all panels. We include the numerical results using a continuum model in
+all insets and these comparisons give a qualitative agreement between
+two models.
+
 \todo[inline]{Bryan left off here}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Shear Flow}
-
-Figure~\ref{figure9} demonstrates the simulation results of two
-Janus-vesicles in a shear flow where the testing shear rate is
-$\chi=0.005$ and the flow is given by $\dot x = \chi y$. In panel (a),
-the starting frame, two center-of-mass positions are placed on the same
-horizontal level, at $(-10,0)$ and $(10,0)$. Since we already have a
-pre-relaxed $58$-body in previous sections, we duplicate the state to
-have the initial configuration (shown in panel (a)) in this section. In
-all panels, the blue and red curves represent the moving paths of two
-Janus-vesicle centroids and they move nearly a round when $t=4000$ as
-shown in panel (h). We observe that the rotation continues as time goes
-and an interesting event occurs in the simulation that an adhesive
-effect can be seen and tuned. In other words, the adhesive behavior will
-be absent when two vesicles are centered at a different level and are
-well separated in $y$-direction.
-
-The fluid pressure profiles of snapshots are given in
-Figure~\ref{figure10}. As expected, there is no pressure jump between
-the internal and external fluids from the beginning of the simulation
-and this is shown in the background pressure plot. Panels (b)-(d) show
-the configurations when $t = \{500,1000,1500\}$ and the streamlines are
-plotted in the background for all panels. We include the numerical
-results using a continuum model in all insets and these comparisons give
-a qualitative agreement between two models.
-
-%\todo[inline]{Migration pattern and/or separation distance. See Fig 8 in
-%JCP paper by Rahimian, Veerapaneni, and Biros.}
-
 \begin{figure}
@@
 \end{center} 
-  \caption{Trajectories of different setups in two-vesicle in an extensional flow and the moving paths of two centroids of two Janus-vesicles are plotted in blue and red.
-(i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii)
-  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure12} presents the numerical results from the case (iii) and a
-  consistent flow rate is $\chi = 0.005$ for all cases.}
-    \label{figure11}
+  \caption{\label{figure11} Trajectories of different setups in
+  two-vesicle in an extensional flow and the moving paths of two
+  centroids of two Janus-vesicles are plotted in blue and red. (i) Both
+  centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid
+  of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii) The
+  centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis
+  and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid
+  of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the
+  other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure12}
+  presents the numerical results from the case (iii) and a consistent
+  flow rate is $\chi = 0.005$ for all cases.}
 \end{figure}
@@
 \includegraphics[height=2in]{N116_ext_6500.pdf}
-  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a).
-The background color indicates the magnitude of fluid pressure.
-From dark red to dark blue, it represents the the pressure varies from high to low values.
-The color bar is valid for all panels.
-Streamlines are plotted in purple.
-The insets show the results produced from using continuum model that the streamlines have perfect agreements with the present results.
-  }
-    \label{figure12}
+  \caption{\label{figure12} Two vesicles under an extensional flow where
+  the dimensioneless shear rate is $\chi=0.005$; The initial
+  configuration is shown in panel (a). The background color indicates
+  the magnitude of fluid pressure. From dark red to dark blue, it
+  represents the pressure varies from high to low values. The color bar
+  is valid for all panels. Streamlines are plotted in purple. The insets
+  show the results produced from using continuum model that the
+  streamlines have perfect agreements with the present results.}
 \end{figure}

### 2021-08-28 doc/main_jfm.tex
finished first pass of numerical results

@@
   \caption{\label{figure9} The shape and trajectories of two
-  Janus-vesicles in a shear flow. The moving paths of the two centroids
-  are plotted in blue and red. The centroids are initially located on
-  the $x$-axis. For simulation time, $t = {0, 400,800,1200}$ for
-  (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).}
+  Janus-vesicles suspended in a shear flow. The moving paths of the two
+  centroids are plotted in blue and red. The centroids are initially
+  located on the $x$-axis. For simulation time, $t = {0, 400,800,1200}$
+  for (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).}
 \end{figure}
@@
 \includegraphics[height=2in]{N116_shear_7500.pdf}
-  \caption{\label{figure10} Two Janus-vesicles under a shear flow where
-  the dimensioneless shear rate is $\chi=0.005$. The initial
-  configuration is shown in panel (a). The background color is the
-  magnitude of fluid pressure. The color bar is identical for all
-  panels. Streamlines are plotted in purple. The insets of all panels
-  are generated from simulations of a continuum model of the vesicle and
-  the streamlines agree between the two models.}
+  \caption{\label{figure10} Two Janus-vesicles suspended in a shear flow
+  where the dimensioneless shear rate is $\chi=0.005$. The initial
+  configuration is shown in panel (a). The background color is the fluid
+  pressure. The color bar is identical for all panels. Streamlines are
+  plotted in purple. The insets of all panels are generated from
+  simulations of a continuum model of the vesicles and the streamlines
+  agree between the two models.}
 \end{figure}
@@
 
-\todo[inline]{Bryan left off here}
 \begin{figure}
@@
 \end{center} 
-  \caption{\label{figure11} Trajectories of different setups in
-  two-vesicle in an extensional flow and the moving paths of two
-  centroids of two Janus-vesicles are plotted in blue and red. (i) Both
-  centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid
-  of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii) The
-  centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis
-  and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid
-  of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the
-  other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure12}
-  presents the numerical results from the case (iii) and a consistent
-  flow rate is $\chi = 0.005$ for all cases.}
+  \caption{\label{figure11} Two Janus-vesicles suspended in
+  an extensional flow. The moving paths of the two centroids are plotted
+  in blue in red. Each row corresponds to a different initial placement
+  of the Janus-vesicles. The flow rate is $\chi = 0.005$ in all cases.
+  (i) Both Janus-vesicle centroids are on the $x$-axis. (ii) The
+  centroid of the left Janus-vesicle is $0.1$ units above the $x$-axis
+  and the right Janus-vesicle is on the $x$-axis. (iii) The centroid of
+  the left Janus-vesicle is $0.1$ units above the $x$-axis and the right
+  Janus-vesicle is $0.1$ units below the $x$-axis. (iv) The centroid of
+  the left Janus-vesicle is $0.5$ units above the $x$-axis and the
+  centroid of the right Janus-vesicle is $0.5$ units below the $x$-axis.
+  Figure~\ref{figure12} presents the numerical results from the case
+  (iii).}
 \end{figure}
@@
 \includegraphics[height=2in]{N116_ext_6500.pdf}
-  \caption{\label{figure12} Two vesicles under an extensional flow where
-  the dimensioneless shear rate is $\chi=0.005$; The initial
-  configuration is shown in panel (a). The background color indicates
-  the magnitude of fluid pressure. From dark red to dark blue, it
-  represents the pressure varies from high to low values. The color bar
-  is valid for all panels. Streamlines are plotted in purple. The insets
-  show the results produced from using continuum model that the
-  streamlines have perfect agreements with the present results.}
+  \caption{\label{figure12} Two Janus-vesicles suspended in an
+  extensional flow where the dimensioneless extensional rate is
+  $\chi=0.005$. The centroid of the left Janus-vesicle is $0.1$ units
+  above the $x$-axis and the centroid of the right Janus-vesicle is
+  $0.1$ units below the $x$-axis. The initial configuration is shown in
+  panel (a). The background color is the fluid pressure. The color bar
+  is identical for all panels. Streamlines are plotted in purple. The
+  insets of all panels are generated from simulations of a continuum
+  model of the vesicles and the streamlines agree between the models.}
 \end{figure}
@@
 
-With a similar setup in the case of two Janus-vesicles in a shear flow, we use the same two pre-relaxed $58$-body Janus-vesicles to perform the simulations when the flow type is an extensional flow with flow rate $\chi=0.005$.
-This extensional flow is stretching along the $y$ direction and squeezing in $x$ direction.
-Figure~\ref{figure11} provides simulation results when the center-of-mass positions are placed differently.
-One can notice that when two centroids are placed on the same horizontal level, two Janus-vesicles reach
-an equilibrium state without separation as shown in case (i).
-If only one centroid is placed above the $x$-axis, for instance, case (ii), two Janus-vesicle move together toward the upward.
-This is the consequence when the adhesive effect beats the flow strength.
-In case (iii), two centroids have a small bias in $y$-direction and they
-start to move apart along $\pm y$-direction. Finally, case (iv) has a larger initial separation in $y$-direction and two Janus-vesicle moves much faster toward $\pm y$-directions.
-
-Figure~\ref{figure12} shows numerical results when the centroids of two bodies are placed at
-$(-10,-0.1)$ and $(10,0.1)$, that is, case (iii) of Figure~\ref{figure11}. With this setup, 
-we can make sure that two Janus-vesicles will separate along $y$-direction eventually and we compare the results against a continuum model as shown in all insets. 
-Panels (b)-(d) show the transitions of two vesicles moving under an extensional flow.
-Since two bilayers are close enough from the beginning of the run, two vesicles are first pushed toward each other then separate along the streamlines.
-In fluid pressure profiles, the pressure is initially high between the gap formed by two
-Janus-vesicles and decreases during the separation.
-The short range repulsion plays an important role to avoid structure collisions and this result can be compared with some findings in continuum modeling simulations.
+With a similar setup in the case of two Janus-vesicles in a shear flow,
+we use the same two pre-relaxed $58$-body Janus-vesicles and consider
+their dynamics in an extensional flow with extensional rate
+$\chi=0.005$. This extensional flow is stretching in the $y$ direction
+and squeezing in the $x$ direction. Figure~\ref{figure11} shows how the
+initial placement of the Janus-vesicles affects the dynamics. When two
+centroids are both placed symmetrically on the $x$-axis (case (i)), the
+Janus-vesicles reach a steady equilibrium. If one centroid is placed
+above the $x$-axis (case (ii)), the two Janus-vesicle move together and
+then upward. The migration of the right Janus-vesicle is a consequence
+of the adhesive effect created by the hydrophobic interactions. When the
+two centroids start on opposite sides of the $x$-axis (case (iii)), they
+eventually diverge from one another along the $y$-axis. Finally, when
+the two centroids start on opposite sides of the $x$-axis, but with a
+greater displacement (case (iv)), the Janus-vesicles move much faster
+toward $\pm y$-directions.
+
+Figure~\ref{figure12} shows numerical results when the centroids of two
+bodies are placed at $(-10,-0.1)$ and $(10,0.1)$ (case (iii) from
+Figure~\ref{figure11}). With this setup, the two
+Janus-vesicles eventually separate along $y$-direction and we compare
+the results against a continuum model as shown in all insets.  Panels
+(b)--(d) show the transient behavior of the Janus-vesicles and continuum
+vesicles transitions under an extensional flow. In both the
+coarse-grained model and the continuum model, the vesicles initially
+converge towards one other and then diverge along the $y$-axis. The
+behavior of the streamlines in both cases are similar. The pressure is
+initially largest in the gap formed by two Janus-vesicles and decreases
+during the separation. The short range repulsion plays an important role
+to avoid structure collisions.
+%and this result can be
+%compared with some findings in continuum modeling simulations.
 

### 2021-08-29 doc/main_jfm.tex
removing empty appendix
conclusion draft

@@
 
-This study proposes a continuum coarse-grained model for Janus-vesicle that focuses on the 
+This study proposes a continuum coarse-grained model for JP vesicle that focuses on the 
 hydrophobic interactions between lipids and hydrodynamic interactions.
@@
 revised hydrophobic force for obtaining particle dynamics.
-The imposed forces and torques of Janus particles adopt not only HAP but a newly developed short 
+
+The imposed forces and torques of JP system adopt not only HAP but also a newly developed short 
 range repulsion given by \ref{eq:REPULforce} and \ref{eq:REPULtorque}.
@@
 membrane where the stretching modulus $K_A$ and the permeability constant $P$ can be obtained.
-
+%
 With the use of selected parameters, the numerical algorithm yields good qualitative results such as
-phenomena in tank-treading Janus-vesicle and asymmetric slipper shape in a parabolic flow. 
-We also demonstrate the membrane rupture in a flow at high shear rate and this makes a breakthrough 
-about having an idea for simulating such phenomenon different from other continuum modeling simulations.
-Inter-monolayer friction coefficients are then obtained and reported by calculating the pressure jumps and
-slip velocities with respect to the bilayer midplane.
-Results of two Janus-vesicles in flow simulations produce an outstanding agreement with ones generated 
-using continuum modeling.
-
-Our future goal is to extend the current framework to a three-dimensional Janus-vesicle system. 
+phenomena in tank-treading Janus-vesicle. The reduced area $A^*$ decreases as the shear rate increases
+ and we measure the equilibrium reduced area for a number of shear rates. The results show that the total
+ length of JP vesicle is conserved and the decay rate of the reduced area is independent of shear rates when shear rates $\dot\gamma$ are between $\sim0.005$ ns$^{-1}$ and $0.008$ ns$^{-1}$.
+Moreover, the proposed model can capture the membrane rupture when the shear flow is at a high shear rate
+and this makes a breakthrough about having an idea for simulating such phenomenon different from other continuum modeling simulations when the bilayer membrane is represented as a closed and continuous curve.
+
+Inter-monolayer friction coefficients $b$ are then obtained and reported by calculating the friction force $F_f$
+using pressure jumps and slip velocities with respect to the bilayer midplane.
+The resulting friction coefficients $b$ are about one order of magnitude smaller than ones in
+~\cite{denOtter2007} and this observation suggests that the granularity of the system is a factor of having 
+the discrepancy. The coarse-graining level of the JP vesicle has much longer length scale comparing against
+the molecular dynamics simulations, in addition, the repulsive potential creates gaps between JP where the 
+error in slip velocities piles up over the computational time.
+
+We also study the migration of a JP vesicle suspended in a parabolic flow and obtain the asymmetric slipper shape.
+The reduced area $A^*$ of the starting JP vesicle is closed to 1 and $A^*=0.9$ at the equilibrium
+state.
+A qualitative agreement has been made comparing with the two-dimensional inextensible membrane in continuum modeling simulations presented in~\cite{Kaoui09}.
+An interesting outcome is that the mean
+$y$-position of the JP vesicle performs an oscillatory motion toward the center of the Poiseuille flow and this
+may be caused by the granularity of the JP vesicle and choices of model parameters.
+
+Results of two JP vesicles suspended in both shear and extensional flows have outstanding agreements with ones generated using continuum modeling in streamlines comparisons.
+For two JP vesicles in shear flow, a demonstration of rotating behavior is presented and two overlapping 
+trajectories of two centroid are observed as expected when two starting centroids are placed on the same 
+horizontal level. The hydrophobic action and the repulsive potential lead to an adhesive effect when two 
+JP bilayers are within a short distance.
+We provide a series of results when two JP vesicles are suspended in extensional flow.
+We obtain similar results to the ones in \cite{qua-vee-you2019} when the reduced area $A^*$ is high and both centroids are placed
+with some vertical displacements.
+
+Our future goal is to extend the current framework to a three-dimensional JP vesicle system. 
 The further implementation of adding a fast algorithms such as the fast multipole method is also a 
 practical approach.
+Having a more physical boundary conditions on JP boundaries with experimental data is a reasonable direction and the future comparison with the laboratory experiments can be accomplished.
 
@@
 
-\appendix
-
-\section{Appendices}
-\label{sec:appendixA}
+%\appendix
+%
+%\section{Appendices}
+%\label{sec:appendixA}
 

### 2021-08-29 doc/main_jfm.tex
adding caption of Fig.1

@@
 \includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
-  \caption{}
+  \caption{JP vesicle are suspended in a quiescent flow for relaxations where the reference arc lengths $L_0$ are $107$ nm and $141$ nm with particle diameters $2.5$ nm and $1.25$ nm, respectively.
+(a) The arc length $L$ decreases over time where the dashed curves represent the data and solid curves are linear fits; (b) A linear relationship between $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear relationship between aqueous flux $dA/dt$ and $L\Delta p$.
+For panels (b) and (c), the cross symbols are numerical results and fit by using solid lines.}
     \label{figure:permeability}

### 2021-08-30 doc/main_jfm.tex
update Fig 1

--- 2021-08-29 doc/main_jfm.tex
@@
 \includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
-  \caption{}
+  \caption{JP vesicle are suspended in a quiescent flow for relaxations where the reference arc lengths $L_0$ are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm, $2.5$ nm, and $1.25$ nm, respectively.
+(a) The arc length $L$ decreases over time where the dashed curves represent the data and solid curves are linear fits; (b) A linear relationship between $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear relationship between aqueous flux $dA/dt$ and $L\Delta p$.
+For panels (b) and (c), the cross and asterisk symbols are numerical results and fit by using solid lines.}
     \label{figure:permeability}

### 2021-08-30 doc/main_jfm.tex
update sec 4.2 numbers

@@
 (a) The arc length $L$ decreases over time where the dashed curves represent the data and solid curves are linear fits; (b) A linear relationship between $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear relationship between aqueous flux $dA/dt$ and $L\Delta p$.
-For panels (b) and (c), the cross and asterisk symbols are numerical results and fit by using solid lines.}
+For panels (b) and (c), the cross and asterisk symbols are numerical results and fitted by using solid lines.}
     \label{figure:permeability}
@@
 Data obtained for the above model.
-Case 1. 58 particles with diameter 2.5 nm and $L_0 = 107$ nm. The calculated stretching modulus was $K_A = 109$ pN nm$^{-1}$ which gives 26.5 kT nm$^{-2}$.
+Case 1. 58 particles with diameter 2.5 nm and $L_0 = 107$ nm. The calculated stretching modulus was $K_A = 179$ pN nm$^{-1}$ which gives 43.6 kT nm$^{-2}$.
 This value is in good agreement with the 60 kT nm$^{-2}$ from experimental measurements.  The calculated permeability was 
 $0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ = 
-$0.0296$ $\mu$m s$^{-1}$ Pa$^{-1}$. (double check value; too large)
-Case 2. 117 particles with diameter 1.25 nm and $L_0 = 141$ nm. This data set gave  $K_A = 62$ pN nm$^{-1}$ which gives 15 kT nm$^{-2}$ which is small.
+$0.0296$ $\mu$m s$^{-1}$ Pa$^{-1}$. %(double check value; too large)
+Case 2. 119 particles with diameter 2.5 nm and $L_0 = 218$ nm. This data set gave  $K_A = 160$ pN nm$^{-1}$ which gives 39 kT nm$^{-2}$. For permeability we get 0.0283 $\mu$m s$^{-1}$ Pa$^{-1}$.
+Case 3. 117 particles with diameter 1.25 nm and $L_0 = 141$ nm. This data set gave  $K_A = 102$ pN nm$^{-1}$ which gives 24.8 kT nm$^{-2}$ which is small.
 For permeability we get 0.0566 $\mu$m s$^{-1}$ Pa$^{-1}$.
@@
 
-\todo[inline]{If $B$ is the numerically calculated friction coefficient,
-then $b = B/2.5^3$ pN ns nm$^{-3}$ gives the dimensional value.
-
-If $P$ is the numerically calculated pressure, then $p = P/2.5$ pN
-nm$^{-2}$ is the dimensional pressure.}
+%\todo[inline]{If $B$ is the numerically calculated friction coefficient,
+%then $b = B/2.5^3$ pN ns nm$^{-3}$ gives the dimensional value.
+%
+%If $P$ is the numerically calculated pressure, then $p = P/2.5$ pN
+%nm$^{-2}$ is the dimensional pressure.}
 

### 2021-08-31 doc/main_jfm.tex
cleaned up 4.1 - 4.3

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\label{validation}Model Validation}
+\section{\label{results}Numerical Results}
 
@@
 \subsection{Model Parameters}
-In the present manuscript, the particles are disks with centre $\aa_i$, and director $\dd_i$.  
+To extract physical quantities of the target structure, 
+we select particles that are disks with diameter 
+$l_0 = 2.5$ nm representing the characteristic thickness of monolayer. 
 The boundary conditions \eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos \theta_i)$ where $\theta_i$ is the angle between 
-$\xx - \aa_i$ and $\dd_i$.  The particle diameters are $l_0 = 2.5$ nm representing the characteristic thickness of monolayer. 
+$\xx - \aa_i$ and $\dd_i$,  where the vectors $\aa_i$ and $\dd_i$ are the particle centre and director respectively. 
+This makes it so that the director points in the direction of the hydrophobic side of the JP. 
 The other physical parameters are 
-\begin{equation}
-\label{eq:parameters}
-\rho = 4 l_0,\quad \rho_0 = l_0,\quad \gamma = \text{4 pN nm}^{-1},\quad \mu = \text{1 cP}.
-\end{equation}
-We nondimensionalize the problem through the change of variables 
-\begin{equation}
-\label{eq:nondimensionalize}
-t \mapsto t \text{ ns}, \quad
-\xx \mapsto \xx \text{ nm}, \quad 
-\xx \mapsto \xx \text{ nm}, \quad 
-\uu \mapsto \uu \text{ nm ns}^{-1}, \quad 
-  p \mapsto p \text{ pN nm}^{-2}.
-\end{equation}
-Here $\text{1 cP} = \text{1 pN ns nm}^{-2}$ is for the viscosity of water at room temperature.  
-For the rest of the manuscript, the time axes are for ns; the pressure $p$ and stress $\sigma$, $\mathbf{T}^{\mathrm{hydro}}$
-are for pN nm$^{-2}$.
-
+%\begin{equation}
+%\label{eq:parameters}
+decay length $\rho = 2 l_0$, 
+repulsion length $\rho_0 = 0.2l_0$, 
+repulsion strength is $M=4.0$~$k_BT$, 
+interfacial particle tension $\gamma = \text{4.1 pN nm}^{-1}$, 
+and $\mu = \text{1 cP} = \text{1 pN ns nm}^{-2}$ for the viscosity of water at room temperature.  
+\cite{Fu20} have provide physical quantities static JP bilayers.%\end{equation}
+
+We consider the behavior of JP vesicles under various external flows.
+To do so, we nondimensionalize the problem through the change of variables 
+%\begin{equation}
+%\label{eq:nondimensionalize}
+$t \mapsto t \text{ ns},$ % \quad
+$\xx \mapsto \xx \text{ nm}$, %\quad 
+$\uu \mapsto \uu \text{ nm ns}^{-1}$, and %\quad 
+ $p \mapsto p \text{ pN nm}^{-2}$.
+%\end{equation}
+For the remainder of the manuscript, the time axes are for ns; the pressure $p$ and stresses $\sigma$ and $\mathbf{T}^{\mathrm{hydro}}$
+are for pN nm$^{-2}$. Finally, the
+dimensionless shear rate is $\chi = \dot\gamma \tau$ for the dimensional shear rate  $\dot\gamma$
+in ns$^{-1}$ and characteristic time $\tau = 1$ ns. 
+The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
+
+\subsection{Self-Assembly and Relaxation}
 \begin{figure}
 \centering
-\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
-\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
-\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
-  \caption{JP vesicle are suspended in a quiescent flow for relaxations where the reference arc lengths $L_0$ are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm, $2.5$ nm, and $1.25$ nm, respectively.
-(a) The arc length $L$ decreases over time where the dashed curves represent the data and solid curves are linear fits; (b) A linear relationship between $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear relationship between aqueous flux $dA/dt$ and $L\Delta p$.
-For panels (b) and (c), the cross and asterisk symbols are numerical results and fitted by using solid lines.}
-    \label{figure:permeability}
+\includegraphics[height=2in]{relax2.eps}
+\includegraphics[height=2in]{relax.eps}\\
+\includegraphics[height=2.in]{N58_0pres.pdf}
+\includegraphics[height=2.in]{N58_5000pres.pdf}
+%  \todo[inline]{Put pressure of each of the two configurations below
+%  this.}
+  \caption{Vesicle relaxes under a quiescent flow.
+(a) The blue dashed and solid curves are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively.
+The red curve shows the decreasing trend of the mean magnitude of particle orientation change.
+The black dashed line shows the reference of how all magnitudes decay.
+(b) Bilayer configurations for $t=0$(black) and $t=1000$(red) with particle directors.
+  (c)-(d) show the fluid pressure profiles for $t=0$ and $t=1000$ where the background curves indicate the streamlines.
+In panel (c), the pressure value in internal fluid is much higher than the pressure outside of the bilayer.
+After the relaxation, this immersed permeable bilayer approaches a steady state as shown in panel (d).
+  }
+    \label{figure2}
 \end{figure}
 
+In order to examine the hydrodynamics interactions of JP vesicles, 
+it is necessary to have a suitable, initial, equilibrium vesicle. 
+This is ensures that the dynamics of the bilayer under a shear flow, for example, reach consistent outcomes.
+For our target vesicle, we start with $N=58$ JP arranged in two circular, apposing monolayers 
+of about $8$ length units. The directors of outer monolayer point inward and the directors of the inner monolayer point outward
+(figure~\ref{figure2}a).
+The JP of this chosen configuration are generally not in equilibrium.  Rather, the inter-particle distances and orientations 
+must make slight adjustments so that attraction and repulsion are balance. 
+Figure~\ref{figure2}(b) shows that the magnitudes of the mean velocity components 
+${\bf v}=\{v_x,v_y\}$ and the variation $\Delta \theta$ of the particle orientation decrease exponentially with an approximation decaying rate $\sim0.005$. 
+A local energy minimum and the equilibrium configuration is therefore rapidly attained.  
+The equilibrium configuration in figure~\ref{figure2}a is slightly elliptical.  The equilibrium eccentricity vanishes for larger $N_b$ (figure~\ref{figure2}e).
+
 \subsection{Permeability}
-Vesicle membranes have a large area modulus $K_A$ and changes in surface are give rise to a membrane tension
+Figures~\ref{figure2}c, d demonstrates that the initial, non-equilibrium configuration has a large internal fluid pressure
+that vanishes as the configuration tends toward the equilibrium state.  
+This suggests that the initial collection of JP is under tension and this tension is relaxed as fluid is expelled through the inter-particle spacing. 
+To make a comparison with membrane continuum mechanics, 
+lipid bilayer membranes have a large area modulus $K_A$ of about $240$ pN nm$^{-1}$ \cite{NAGLE} 
+and changes in surface area give rise to a membrane tension
 $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the membrane surface area and $A_0$ is the reference surface area in the non-tensed state. 
-Since we are dealing with two-dimensional vesicles, we replace $A$ and $A_0$ with the membrane arc length $L$ and reference length $L_0$
-respectively.  Thus, the tension in a stretched cylindrical vesicle membrane is 
+In the two-dimensional vesicles, the tension becomes 
 \begin{equation}
@@
 \end{equation}
-A stretched vesicles has a Laplace pressure 
+where $L$ and $L_0$ are the vesicle arc length and resting length, respectively. 
+A stretched, circular vesicles has a Laplace pressure 
 \begin{equation}
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
+\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
+\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
+  \caption{JP vesicle are suspended in a quiescent flow for relaxations where the reference arc lengths $L_0$ are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm, $2.5$ nm, and $1.25$ nm, respectively.
+(a) The arc length $L$ decreases over time where the dashed curves represent the data and solid curves are linear fits; (b) A linear relationship between $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear relationship between aqueous flux $dA/dt$ and $L\Delta p$.
+For panels (b) and (c), the cross and asterisk symbols are numerical results and fitted by using solid lines.}
+    \label{figure:permeability}
+\end{figure}
+
 The particles in our setup do not abut but rather have small gaps due to repulsive forces.
-The gaps allow for some fluid flux across the JP bilayer.  Aqueous flux is quantified by a permeability constant $P$ in the equation
+The gaps allow for some fluid flux across the JP bilayer. 
+In membrane mechanics, aqueous flux is quantified the equation
 \begin{equation}
@@
 \end{equation}
-Combining \eqref{eq:stretch}, \eqref{eq:LaplacePressure}, and \eqref{eq:perm}, we can solve the for length $L$ 
+where $P$ is a hydraulic permeability constant \cite{CHABANON, QGY-Y}.
+
+The JP vesicle data is in complete agreement with the continuum mechanical model \eqref{eq:stretch}-\eqref{eq:perm_solution}.
+In figure \ref{figure:permeability}, we considered three configurations: a configuration with 58 particles 
+($L_0 = 107$ nm, plus symbols); a configuration with 119 particles ($L_0 = 218$ nm, asterick symbols);
+and finally a configuration with 117 particles but with diameter 1.25 nm rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols).
+Here $A$ and $L$ refer to the area and length of the mid plane curve separating the inner and outer monolayers. 
+(The values for $L_0$ are the asymptotic values for $L$ in figure \ref{figure:permeability}c).
+
+Figure \ref{figure:permeability}a plots the data for the Laplace pressure relationship \eqref{eq:LaplacePressure}.
+The pressure jump $\Delta p$ is the pressure at the particle center minus the far-field pressure (see figure \ref{figure2}c,d),
+$R = L/2\pi$ is the vesicle radius, and the horizontal axis is for the relative stretch. The solid lines are linear fits,
+showing that for circular JP vesicles, $R\Delta P$ is basically proportional to relative stretching $L/L_0 - 1$ . The proportionality constant is the same 
+for the 58 and 119 particle cases where the diameters are the same, suggesting that the stretching modulus $K_A$ of JP bilayers 
+is independent of the number of particles.
+The 117 particle case had diameters 1.25 nm and this data set gave a smaller stretching modulus  $K_A = 102$ pN nm$^{-1}$.
+The interpretation is that changes to particle size, while keeping $\rho$, $M$, and $\rho_0$ fixed, lead to different physical properties.
+
+Furthermore, figure \ref{figure:permeability}b and shows that $L\Delta P$ is proportional to $\frac{dA}{dt}$
+in accord with \eqref{eq:perm}.  The slopes of the linear fits give the hydraulic permeability coefficient $P.$
+The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$
+for the 58 and 119 particle cases, respectively.  These values suggest that the JP bilayer permeability is independent 
+of particle number, as was the case for the stretching modulus. 
+The permeability for the 117 particle number case was larger, 0.0566 nm$^3$ ns$^{-1}$ pN$^{-1}$.  That is because 
+hydrophobic attraction vanishes with particle size, leading to larger gaps between the particles for the same repulsion. 
+The hydraulic permeability we calculate, however, is not in agreement with experimentally derived values and is larger by
+a few orders of magnitude. This discrepancy is perhaps due to inter-particle distance of the JP being relatively large to the 
+inter-molecular spacing of lipids in real bilayers.  In future studies, we can test this hypothesis be changing the repulsion strength and length 
+for example.
+
+Since the vesicles in figure \ref{figure2}a are nearly we circular, we can 
+combine \eqref{eq:stretch}, \eqref{eq:LaplacePressure}, and \eqref{eq:perm}, to derive  
 \begin{equation}
 \label{eq:perm_solution}
-L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t
+L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
 \end{equation}
-and compare with our data.
-
-Data obtained for the above model.
-Case 1. 58 particles with diameter 2.5 nm and $L_0 = 107$ nm. The calculated stretching modulus was $K_A = 179$ pN nm$^{-1}$ which gives 43.6 kT nm$^{-2}$.
-This value is in good agreement with the 60 kT nm$^{-2}$ from experimental measurements.  The calculated permeability was 
-$0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ = 
-$0.0296$ $\mu$m s$^{-1}$ Pa$^{-1}$. %(double check value; too large)
-Case 2. 119 particles with diameter 2.5 nm and $L_0 = 218$ nm. This data set gave  $K_A = 160$ pN nm$^{-1}$ which gives 39 kT nm$^{-2}$. For permeability we get 0.0283 $\mu$m s$^{-1}$ Pa$^{-1}$.
-Case 3. 117 particles with diameter 1.25 nm and $L_0 = 141$ nm. This data set gave  $K_A = 102$ pN nm$^{-1}$ which gives 24.8 kT nm$^{-2}$ which is small.
-For permeability we get 0.0566 $\mu$m s$^{-1}$ Pa$^{-1}$.
-
-The dashed lines in panel (a) are the graphs of \eqref{eq:perm_solution} for the 58 and 117 particle number cases, respectively. 
-Panels (b) and (c) show the select data points with plusses for 58 particles and times for 117 particles.  The solid lines are linear fits.
-The linear fits in panel (b) shows that $R\Delta P$ is proportional to relative stretching $L/L_0 - 1$. The proportionality constant is $K_A.$
-The linear fits in panel (c) shows that $L\Delta P$ is proportional to flux $\frac{dA}{dt}$.  The proportionality constant is the permeability coefficient $P.$
+The theoretical time courses for \eqref{eq:perm_solution} are in good quantitative agreement with the JP data 
+for (figure \ref{figure:permeability}c).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Self-Assembly and Relaxation}
-
-In order to examine the dynamics of the Janus-vesicle using the HAP coupling with hydrodynamics interactions, for the target bilayer, a circular initial shape is chosen to perform the relaxation run. 
-This structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
-the vesicle is about $8$ length units.
-The starting center of mass position of the Janus-vesicle is pinned at the origin and particle velocities are tracked to determine the initial configuration for later use such as single and multiple vesicle simulations.
-The advantage of acquiring this configuration is to prevent some numerical instability issues when the minimum of the total energy is not achieved. 
-For instance, the dynamics of the bilayer under a shear flow may reach different outcomes or equilibrium states.
-Figure~\ref{figure2}(a) shows two sets of results: (1) the magnitudes of mean velocity components 
-${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$; (2) the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property of the model.
-This implies that a local energy minimum and the equilibrium configuration are nearly attained.
-The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
-Figure~\ref{figure2}(b) shows the configuration difference between starting and ending frames in the relaxation run.
-The Figure~\ref{figure2}(c)-(d) demonstrate the fluid pressure profile of two configurations at $t=0$ and $t=1000$.
-The starting fluid pressure inside the permeable Janus-vesicle decreases as expected.
-
-\begin{figure}
-\centering
-\includegraphics[height=2in]{relax.eps}
-\includegraphics[height=2in]{relax2.eps}\\
-\includegraphics[height=2.in]{N58_0pres.pdf}
-\includegraphics[height=2.in]{N58_5000pres.pdf}
-%  \todo[inline]{Put pressure of each of the two configurations below
-%  this.}
-  \caption{Vesicle relaxes under a quiescent flow.
-(a) The blue dashed and solid curves are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively.
-The red curve shows the decreasing trend of the mean magnitude of particle orientation change.
-The black dashed line shows the reference of how all magnitudes decay.
-(b) Bilayer configurations for $t=0$(black) and $t=1000$(red) with particle directors.
-  (c)-(d) show the fluid pressure profiles for $t=0$ and $t=1000$ where the background curves indicate the streamlines.
-In panel (c), the pressure value in internal fluid is much higher than the pressure outside of the bilayer.
-After the relaxation, this immersed permeable bilayer approaches a steady state as shown in panel (d).
-  }
-    \label{figure2}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{\label{results}Numerical Results}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 %\todo[inline]{Introduce dimensionless shear rate here (and check the numbers)}
-
-Following the relaxation experiments we consider the behavior of
-Janus-vesicles under various flows. To extract physical quantities of
-the target structure, we introduce the following scaling laws and the
-dimensionless units. The length unit is scaled by the length of
-phospholipids $l=2.5$~nm which is the diameter of each Janus particle.
-The force is scaled by the interfacial tension $\gamma=4.11$~pN
-nm$^{-1}$ from~\cite{Ryham16}. This means that the energy unit is scaled
-by $1\ k_BT$. We can then define the characteristic time scale $\tau =
-\mu l/\gamma = 0.61$~ns where the fluid viscosity is $\mu=1$ cP.  With
-the same framework,~\cite{Fu20} provide the bending rigidity
-$\kappa=8.51$~$k_BT$. For the model parameters, the decay length of
-attraction is $\rho = 2l = 5$~nm, the repulsion length scale is
-$\rho_0=0.5$, and the repulsion strength is $M=4.0$~$k_BT$. Finally, the
-dimensionless shear rate is $\chi = \dot\gamma \tau$ where $\dot\gamma$
-is the shear rate.
 
@@
 \label{sec:ves_in_shear}
-We begin by studying the dynamics of a single Janus-vesicle suspended in
+Our hydrodynamic simulation studies begin by studying the dynamics of a single JP vesicle suspended in
 the shear flow

### 2021-09-01 doc/main_jfm.tex
starting to work through Sec 4

@@
 form a micelle, a patch of bilayer membrane with open ends, and a
-self-enclosed bilayer membrane (referred to as a Janus-vesicle). Using a
+self-enclosed bilayer membrane (referred to as a JP vesicle). Using a
 hybrid continuum model for the interactions between amphiphilic
@@
 suspension under various flows: a linear shear flow, an elongation flow,
-and a Poiseuille flow. We demonstrate that a Janus-vesicle behaves like
+and a Poiseuille flow. We demonstrate that a JP vesicle behaves like
 a vesicle in these flowing conditions. In particular, we show that a
-Janus-vesicle undergoes tank-treading in a shear flow and vertical
+JP vesicle undergoes tank-treading in a shear flow and vertical
 migration in a Poiseuille flow. Furthermore we use the hybrid continuum
@@
 membrane due to an imposed flow. Finally, we compare a pair of
-interacting Janus-vesicles with a continuum model of a pair of vesicles.
+interacting JP vesicles with a continuum model of a pair of vesicles.
 
@@
 a far-field flow via the mobility problem formulation. In
-\S~\ref{validation} we validate our model, and in \S~\ref{results} we
-present simulation results for a single and pair of Janus-vesicles under
-various flowing conditions. Finally we provide discussion and outlook
-for future directions in \S~\ref{conclusion}.
+\S~\ref{results} we validate our model and present simulation results
+for a single and pair of JP vesicles under various flowing conditions.
+Finally we provide discussion and outlook for future directions in
+\S~\ref{conclusion}.
 
@@
 \subsection{Model Parameters}
-To extract physical quantities of the target structure, 
-we select particles that are disks with diameter 
-$l_0 = 2.5$ nm representing the characteristic thickness of monolayer. 
-The boundary conditions \eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos \theta_i)$ where $\theta_i$ is the angle between 
-$\xx - \aa_i$ and $\dd_i$,  where the vectors $\aa_i$ and $\dd_i$ are the particle centre and director respectively. 
-This makes it so that the director points in the direction of the hydrophobic side of the JP. 
-The other physical parameters are 
-%\begin{equation}
-%\label{eq:parameters}
-decay length $\rho = 2 l_0$, 
-repulsion length $\rho_0 = 0.2l_0$, 
-repulsion strength is $M=4.0$~$k_BT$, 
-interfacial particle tension $\gamma = \text{4.1 pN nm}^{-1}$, 
-and $\mu = \text{1 cP} = \text{1 pN ns nm}^{-2}$ for the viscosity of water at room temperature.  
-\cite{Fu20} have provide physical quantities static JP bilayers.%\end{equation}
+To extract physical quantities of the target structure, we select
+particles that are disks with diameter $l_0 = 2.5$ nm representing the
+characteristic thickness of monolayers. The boundary
+conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
+\theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
+$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle center
+and director respectively. With this choice, the director points in the
+direction of the hydrophobic side of the JP. The other physical
+parameters are the decay length $\rho = 2 l_0$, the repulsion length
+$\rho_0 = 0.2l_0$, the repulsion strength is $M=4.0$~$k_BT$, the
+interfacial particle tension $\gamma = \text{4.1 pN nm}^{-1}$, and $\mu
+= \text{1 cP} = \text{1 pN ns nm}^{-2}$ is the viscosity of water at
+room temperature. \cite{Fu20} provides physical quantities for static JP
+bilayers.
 
 We consider the behavior of JP vesicles under various external flows.
-To do so, we nondimensionalize the problem through the change of variables 
+To do so, we nondimensionalize the problem through the change of
+variables 
 %\begin{equation}
@@
 %\end{equation}
-For the remainder of the manuscript, the time axes are for ns; the pressure $p$ and stresses $\sigma$ and $\mathbf{T}^{\mathrm{hydro}}$
-are for pN nm$^{-2}$. Finally, the
-dimensionless shear rate is $\chi = \dot\gamma \tau$ for the dimensional shear rate  $\dot\gamma$
-in ns$^{-1}$ and characteristic time $\tau = 1$ ns. 
-The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
+For the remainder of the manuscript, the time axes are in ns, and the
+pressure $p$ and stresses $\sigma$ and $\mathbf{T}^{\mathrm{hydro}}$ are
+in pN nm$^{-2}$. Finally, the dimensionless shear rate is $\chi =
+\dot\gamma \tau$ for the dimensional shear rate $\dot\gamma$ in
+ns$^{-1}$ and the characteristic time is $\tau = 1$~ns. The time step
+size $\Delta t=0.2$ is used for all simulations in this work including
+the relaxation run.
 
@@
 %  this.}
-  \caption{Vesicle relaxes under a quiescent flow.
-(a) The blue dashed and solid curves are mean magnitudes of the particle velocities in $x$ and $y$ directions, respectively.
-The red curve shows the decreasing trend of the mean magnitude of particle orientation change.
-The black dashed line shows the reference of how all magnitudes decay.
-(b) Bilayer configurations for $t=0$(black) and $t=1000$(red) with particle directors.
-  (c)-(d) show the fluid pressure profiles for $t=0$ and $t=1000$ where the background curves indicate the streamlines.
-In panel (c), the pressure value in internal fluid is much higher than the pressure outside of the bilayer.
-After the relaxation, this immersed permeable bilayer approaches a steady state as shown in panel (d).
-  }
-    \label{figure2}
+\caption{\label{figure2} A JP Vesicle relaxing under a quiescent flow.
+  (a) The blue dashed and solid curves are mean magnitudes of the
+  particle velocities in $x$ and $y$ directions, respectively. The red
+  curve shows the decreasing trend of the mean magnitude of particle
+  orientation change. The black dashed line shows the reference of how
+  all magnitudes decay. (b) Bilayer configurations for $t=0$ (black) and
+  $t=1000$ (red) with particle directors. (c)--(d) show the fluid
+  pressure profiles for $t=0$ and $t=1000$ where the background curves
+  indicate the streamlines. In panel (c), the pressure value in internal
+  fluid is much higher than the pressure outside of the bilayer. After
+  the JP vesicle relaxes, this immersed permeable bilayer approaches the
+  steady state shown in panel (d).}
 \end{figure}
 
-In order to examine the hydrodynamics interactions of JP vesicles, 
-it is necessary to have a suitable, initial, equilibrium vesicle. 
-This is ensures that the dynamics of the bilayer under a shear flow, for example, reach consistent outcomes.
-For our target vesicle, we start with $N=58$ JP arranged in two circular, apposing monolayers 
-of about $8$ length units. The directors of outer monolayer point inward and the directors of the inner monolayer point outward
-(figure~\ref{figure2}a).
-The JP of this chosen configuration are generally not in equilibrium.  Rather, the inter-particle distances and orientations 
-must make slight adjustments so that attraction and repulsion are balance. 
-Figure~\ref{figure2}(b) shows that the magnitudes of the mean velocity components 
-${\bf v}=\{v_x,v_y\}$ and the variation $\Delta \theta$ of the particle orientation decrease exponentially with an approximation decaying rate $\sim0.005$. 
-A local energy minimum and the equilibrium configuration is therefore rapidly attained.  
-The equilibrium configuration in figure~\ref{figure2}a is slightly elliptical.  The equilibrium eccentricity vanishes for larger $N_b$ (figure~\ref{figure2}e).
+In order to examine the hydrodynamics interactions of JP vesicles, it is
+necessary to have a suitable, initial, equilibrium vesicle.  This is
+ensures that the dynamics of the bilayer under a shear flow, for
+example, reach consistent outcomes.  For our target vesicle, we start
+with $N=58$ JP arranged in two circular, apposing monolayers of about
+$8$ length units. The directors of outer monolayer point inward and the
+directors of the inner monolayer point outward (Figure~\ref{figure2}a).
+The JP of this chosen configuration are generally not in equilibrium.
+Rather, the inter-particle distances and orientations must make slight
+adjustments so that attraction and repulsion are balance.
+Figure~\ref{figure2}(b) shows that the magnitudes of the mean velocity
+components ${\bf v}=\{v_x,v_y\}$ and the variation $\Delta \theta$ of
+the particle orientation decrease exponentially with an approximation
+decaying rate $\sim0.005$.  A local energy minimum and the equilibrium
+configuration is therefore rapidly attained.  The equilibrium
+configuration in Figure~\ref{figure2}a is slightly elliptical.  The
+equilibrium eccentricity vanishes for larger $N_b$
+(Figure~\ref{figure2}e).
 
@@
 The JP vesicle data is in complete agreement with the continuum mechanical model \eqref{eq:stretch}-\eqref{eq:perm_solution}.
-In figure \ref{figure:permeability}, we considered three configurations: a configuration with 58 particles 
+In Figure \ref{figure:permeability}, we considered three configurations: a configuration with 58 particles 
 ($L_0 = 107$ nm, plus symbols); a configuration with 119 particles ($L_0 = 218$ nm, asterick symbols);
@@
 Here $A$ and $L$ refer to the area and length of the mid plane curve separating the inner and outer monolayers. 
-(The values for $L_0$ are the asymptotic values for $L$ in figure \ref{figure:permeability}c).
-
-Figure \ref{figure:permeability}a plots the data for the Laplace pressure relationship \eqref{eq:LaplacePressure}.
-The pressure jump $\Delta p$ is the pressure at the particle center minus the far-field pressure (see figure \ref{figure2}c,d),
+(The values for $L_0$ are the asymptotic values for $L$ in Figure \ref{figure:permeability}c).
+
+Figure~\ref{figure:permeability}a plots the data for the Laplace pressure relationship \eqref{eq:LaplacePressure}.
+The pressure jump $\Delta p$ is the pressure at the particle center minus the far-field pressure (see Figure~\ref{figure2}c,d),
 $R = L/2\pi$ is the vesicle radius, and the horizontal axis is for the relative stretch. The solid lines are linear fits,
@@
 
-Furthermore, figure \ref{figure:permeability}b and shows that $L\Delta P$ is proportional to $\frac{dA}{dt}$
-in accord with \eqref{eq:perm}.  The slopes of the linear fits give the hydraulic permeability coefficient $P.$
-The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$
-for the 58 and 119 particle cases, respectively.  These values suggest that the JP bilayer permeability is independent 
-of particle number, as was the case for the stretching modulus. 
-The permeability for the 117 particle number case was larger, 0.0566 nm$^3$ ns$^{-1}$ pN$^{-1}$.  That is because 
-hydrophobic attraction vanishes with particle size, leading to larger gaps between the particles for the same repulsion. 
-The hydraulic permeability we calculate, however, is not in agreement with experimentally derived values and is larger by
-a few orders of magnitude. This discrepancy is perhaps due to inter-particle distance of the JP being relatively large to the 
-inter-molecular spacing of lipids in real bilayers.  In future studies, we can test this hypothesis be changing the repulsion strength and length 
-for example.
-
-Since the vesicles in figure \ref{figure2}a are nearly we circular, we can 
-combine \eqref{eq:stretch}, \eqref{eq:LaplacePressure}, and \eqref{eq:perm}, to derive  
-\begin{equation}
+Furthermore, Figure~\ref{figure:permeability}b and shows that $L\Delta
+P$ is proportional to $\frac{dA}{dt}$ in accord with \eqref{eq:perm}.
+The slopes of the linear fits give the hydraulic permeability
+coefficient $P.$ The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$
+pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 58 and 119
+particle cases, respectively.  These values suggest that the JP bilayer
+permeability is independent of particle number, as was the case for the
+stretching modulus.  The permeability for the 117 particle number case
+was larger, 0.0566 nm$^3$ ns$^{-1}$ pN$^{-1}$.  That is because
+hydrophobic attraction vanishes with particle size, leading to larger
+gaps between the particles for the same repulsion.  The hydraulic
+permeability we calculate, however, is not in agreement with
+experimentally derived values and is larger by a few orders of
+magnitude. This discrepancy is perhaps due to inter-particle distance of
+the JP being relatively large to the inter-molecular spacing of lipids
+in real bilayers.  In future studies, we can test this hypothesis be
+changing the repulsion strength and length for example.
+
+Since the vesicles in Figure~\ref{figure2}a are nearly we circular, we
+can combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
+and~\eqref{eq:perm}, to derive  
+\begin{align}
 \label{eq:perm_solution}
 L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
-\end{equation}
-The theoretical time courses for \eqref{eq:perm_solution} are in good quantitative agreement with the JP data 
-for (figure \ref{figure:permeability}c).
+\end{align}
+The theoretical time courses for \eqref{eq:perm_solution} are in good
+quantitative agreement with the JP data for
+(Figure~\ref{figure:permeability}c).
 
@@
 placed at the origin and the shear flow with a certain shear rate $\chi$
-is applied. Snapshots of the Janus-vesicle in a shear flow with a shear
+is applied. Snapshots of the JP vesicle in a shear flow with a shear
 rate $\chi=0.0025$ are shown in Figure~\ref{figure3}. Panels (a) and (b)
 show the initial shape obtained from the relaxation run and the deformed
-configurations of the Janus-vesicle at time $t=4000$ are in panels (c)
+configurations of the JP vesicle at time $t=4000$ are in panels (c)
 and (d). The background color in panels (a) and (c) is the strength of
@@
 vesicle, panels (b) and (d) provide the streamlines of the fluid
-velocity around the Janus-vesicle. In panel (d), we can clearly observe
+velocity around the JP vesicle. In panel (d), we can clearly observe
 the clockwise tank-treading motion.
@@
 \includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
-  \caption{\label{figure3} A Janus-vesicle suspended in a shear flow
+  \caption{\label{figure3} A JP vesicle suspended in a shear flow
   with shear rate $\chi=0.0025$: (a) Initial configuration of 58-body
-  Janus-vesicle where black arrows are the particle orientations. (b)
+  JP vesicle where black arrows are the particle orientations. (b)
   The particle velocities and streamlines of the configuration in (a).
   Streamlines are plotted in the background as solid curves. Red arrows
-  represent the particle velocities. (c) Deformed Janus-vesicle at
-  $t=4000$. At this configuration the Janus-vesicle is tank-treading.
+  represent the particle velocities. (c) Deformed JP vesicle at
+  $t=4000$. At this configuration the JP vesicle is tank-treading.
   (d) The particle velocities and streamlines of the configuration in
@@
 calculated from the midplane. The reduced area is $A^* = 4\pi A/L^2$
-where $A$ the area, and $L$ the total length of the Janus-vesicle, and
+where $A$ the area, and $L$ the total length of the JP vesicle, and
 the excess length is $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
-Figure~\ref{figure4} shows these quantities for a Janus-vesicle
+Figure~\ref{figure4} shows these quantities for a JP vesicle
 suspended in a shear flow with shear rates
@@
 results, there are oscillations that can be explained by the granularity
-of the Janus-vesicle which results in a midplane that is non-smooth.
+of the JP vesicle which results in a midplane that is non-smooth.
 %Overall the total lengths of the bilayer have the same converging value
@@
 \subsubsection{Intermonolayer Friction}
-The granulated Janus-vesicle allows us to consider inter-monolayer slip
+The granulated JP vesicle allows us to consider inter-monolayer slip
 between two leaflets. When the shear rate is sufficiently large, take
@@
   calculated from the relative position of the particles with respect to
-  the Janus-vesicle's center of mass. The configuration plots have two
+  the JP vesicle's center of mass. The configuration plots have two
   fixed particles marked in yellow and blue and labeled with the
@@
 where $v_{max}$ is the flow strength and $w$ controls the shape of the
-flow. $R_0$ is defined as the radius of the Janus-vesicle at $t=0$.
+flow. $R_0$ is defined as the radius of the JP vesicle at $t=0$.
 The behavior of a vesicle in this unbounded non-linear flow includes
@@
 
-%Besides the tests of a Janus-vesicle in a shear flow, an interesting
+%Besides the tests of a JP vesicle in a shear flow, an interesting
 %test can also use the proposed model and the setup. Consider a
@@
 Figure~\ref{figure6} shows three configurations for one specific case
-where the centroid of the Janus-vesicle is initially placed slightly
+where the centroid of the JP vesicle is initially placed slightly
 above the $x$-axis. The parameters are $v_{max} = 8.0$, $w=10$, and
 $R_0=8$. The red curves are the midplanes and a particle pair is marked
-in color. We observe that the deformed Janus-vesicle has a
+in color. We observe that the deformed JP vesicle has a
 counterclockwise movement and the shape of the vesicle approaches an
@@
 starts to have an oscillatory motion due to the granularity of the
-Janus-vesicle.
+JP vesicle.
 
@@
 \includegraphics[width=0.8\textwidth]{slipper.eps}
-  \caption{\label{figure6} A Janus-vesicle suspended in a parabolic flow
+  \caption{\label{figure6} A JP vesicle suspended in a parabolic flow
   where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
@@
 \includegraphics[height=2in]{parabolic.eps}
-  \caption{\label{figure7} The schematic of a Janus-vesicle suspended in
+  \caption{\label{figure7} The schematic of a JP vesicle suspended in
   a parabolic flow where the strength of the flow is $v_{max}=32.8$~nm
@@
   \caption{\label{figure9} The shape and trajectories of two
-  Janus-vesicles suspended in a shear flow. The moving paths of the two
+  JP vesicles suspended in a shear flow. The moving paths of the two
   centroids are plotted in blue and red. The centroids are initially
@@
 \includegraphics[height=2in]{N116_shear_7500.pdf}
-  \caption{\label{figure10} Two Janus-vesicles suspended in a shear flow
+  \caption{\label{figure10} Two JP vesicles suspended in a shear flow
   where the dimensioneless shear rate is $\chi=0.005$. The initial
@@
 
-Figure~\ref{figure9} shows the simulation of two Janus-vesicles in a
+Figure~\ref{figure9} shows the simulation of two JP vesicles in a
 shear flow with shear rate $\chi=0.005$. Using the pre-relaxed $58$-body
-Janus-vesicle in previous sections, we duplicate the state to have the
+JP vesicle in previous sections, we duplicate the state to have the
 initial configuration shown in panel (a). The two centers of mass are at
 $(-10,0)$ and $(10,0)$. In all panels, the blue and red curves show the
-trajectory of the two Janus-vesicle centroids. They have nearly
+trajectory of the two JP vesicle centroids. They have nearly
 completed a full period by $t=4000$ as shown in panel (h). We also
-observe an adhesive effect between the two Janus-vesicles that is set up
+observe an adhesive effect between the two JP vesicles that is set up
 by the hydrophobic interactions and repulsive force. Similar dynamics
@@
 (\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
-behavior is absent when two Janus-vesicles are well-separated.
+behavior is absent when two JP vesicles are well-separated.
 
 The fluid pressure profiles snapshots are given in
-Figure~\ref{figure10}. Since the initial Janus-vesicles are pre-relaxed,
+Figure~\ref{figure10}. Since the initial JP vesicles are pre-relaxed,
 there is initially no pressure jump between the internal and external
@@
 \end{center} 
-  \caption{\label{figure11} Two Janus-vesicles suspended in
+  \caption{\label{figure11} Two JP vesicles suspended in
   an extensional flow. The moving paths of the two centroids are plotted
   in blue in red. Each row corresponds to a different initial placement
-  of the Janus-vesicles. The flow rate is $\chi = 0.005$ in all cases.
-  (i) Both Janus-vesicle centroids are on the $x$-axis. (ii) The
-  centroid of the left Janus-vesicle is $0.1$ units above the $x$-axis
-  and the right Janus-vesicle is on the $x$-axis. (iii) The centroid of
-  the left Janus-vesicle is $0.1$ units above the $x$-axis and the right
-  Janus-vesicle is $0.1$ units below the $x$-axis. (iv) The centroid of
-  the left Janus-vesicle is $0.5$ units above the $x$-axis and the
-  centroid of the right Janus-vesicle is $0.5$ units below the $x$-axis.
+  of the JP vesicles. The flow rate is $\chi = 0.005$ in all cases.
+  (i) Both JP vesicle centroids are on the $x$-axis. (ii) The
+  centroid of the left JP vesicle is $0.1$ units above the $x$-axis
+  and the right JP vesicle is on the $x$-axis. (iii) The centroid of
+  the left JP vesicle is $0.1$ units above the $x$-axis and the right
+  JP vesicle is $0.1$ units below the $x$-axis. (iv) The centroid of
+  the left JP vesicle is $0.5$ units above the $x$-axis and the
+  centroid of the right JP vesicle is $0.5$ units below the $x$-axis.
   Figure~\ref{figure12} presents the numerical results from the case
@@
 \includegraphics[height=2in]{N116_ext_6500.pdf}
-  \caption{\label{figure12} Two Janus-vesicles suspended in an
+  \caption{\label{figure12} Two JP vesicles suspended in an
   extensional flow where the dimensioneless extensional rate is
-  $\chi=0.005$. The centroid of the left Janus-vesicle is $0.1$ units
-  above the $x$-axis and the centroid of the right Janus-vesicle is
+  $\chi=0.005$. The centroid of the left JP vesicle is $0.1$ units
+  above the $x$-axis and the centroid of the right JP vesicle is
   $0.1$ units below the $x$-axis. The initial configuration is shown in
@@
 
-With a similar setup in the case of two Janus-vesicles in a shear flow,
-we use the same two pre-relaxed $58$-body Janus-vesicles and consider
+With a similar setup in the case of two JP vesicles in a shear flow,
+we use the same two pre-relaxed $58$-body JP vesicles and consider
 their dynamics in an extensional flow with extensional rate
@@
 and squeezing in the $x$ direction. Figure~\ref{figure11} shows how the
-initial placement of the Janus-vesicles affects the dynamics. When two
+initial placement of the JP vesicles affects the dynamics. When two
 centroids are both placed symmetrically on the $x$-axis (case (i)), the
-Janus-vesicles reach a steady equilibrium. If one centroid is placed
-above the $x$-axis (case (ii)), the two Janus-vesicle move together and
-then upward. The migration of the right Janus-vesicle is a consequence
+JP vesicles reach a steady equilibrium. If one centroid is placed
+above the $x$-axis (case (ii)), the two JP vesicle move together and
+then upward. The migration of the right JP vesicle is a consequence
 of the adhesive effect created by the hydrophobic interactions. When the
@@
 the two centroids start on opposite sides of the $x$-axis, but with a
-greater displacement (case (iv)), the Janus-vesicles move much faster
+greater displacement (case (iv)), the JP vesicles move much faster
 toward $\pm y$-directions.
@@
 Figure~\ref{figure11}). With this setup, the two
-Janus-vesicles eventually separate along $y$-direction and we compare
+JP vesicles eventually separate along $y$-direction and we compare
 the results against a continuum model as shown in all insets.  Panels
-(b)--(d) show the transient behavior of the Janus-vesicles and continuum
+(b)--(d) show the transient behavior of the JP vesicles and continuum
 vesicles transitions under an extensional flow. In both the
@@
 behavior of the streamlines in both cases are similar. The pressure is
-initially largest in the gap formed by two Janus-vesicles and decreases
+initially largest in the gap formed by two JP vesicles and decreases
 during the separation. The short range repulsion plays an important role
@@
 With the use of selected parameters, the numerical algorithm yields good qualitative results such as
-phenomena in tank-treading Janus-vesicle. The reduced area $A^*$ decreases as the shear rate increases
+phenomena in tank-treading JP vesicle. The reduced area $A^*$ decreases as the shear rate increases
  and we measure the equilibrium reduced area for a number of shear rates. The results show that the total

### 2021-09-01 doc/main_jfm.tex
first pass at section 4

@@
 In order to examine the hydrodynamics interactions of JP vesicles, it is
-necessary to have a suitable, initial, equilibrium vesicle.  This is
+necessary to have a suitable, initial, JP equilibrium vesicle. This
 ensures that the dynamics of the bilayer under a shear flow, for
@@
 with $N=58$ JP arranged in two circular, apposing monolayers of about
-$8$ length units. The directors of outer monolayer point inward and the
-directors of the inner monolayer point outward (Figure~\ref{figure2}a).
-The JP of this chosen configuration are generally not in equilibrium.
-Rather, the inter-particle distances and orientations must make slight
-adjustments so that attraction and repulsion are balance.
-Figure~\ref{figure2}(b) shows that the magnitudes of the mean velocity
-components ${\bf v}=\{v_x,v_y\}$ and the variation $\Delta \theta$ of
-the particle orientation decrease exponentially with an approximation
-decaying rate $\sim0.005$.  A local energy minimum and the equilibrium
-configuration is therefore rapidly attained.  The equilibrium
-configuration in Figure~\ref{figure2}a is slightly elliptical.  The
-equilibrium eccentricity vanishes for larger $N_b$
+$8$ length units. The directors of the outer monolayer point inward and
+the directors of the inner monolayer point outward
+(Figure~\ref{figure2}a).  The JP of this chosen configuration are
+generally not in equilibrium.  Rather, the inter-particle distances and
+orientations must make slight adjustments so that attraction and
+repulsion balance.  Figure~\ref{figure2}(b) shows that the magnitudes of
+the mean velocity components ${\bf v}=\{v_x,v_y\}$ and the variation
+$\Delta \theta$ of the particle orientation decrease exponentially with
+an approximation decaying rate $\sim0.005$. A local energy minimum and
+the equilibrium configuration is therefore rapidly attained. The
+equilibrium configuration in Figure~\ref{figure2}a is slightly
+elliptical. The equilibrium eccentricity vanishes for larger $N_b$
 (Figure~\ref{figure2}e).
@@
 \subsection{Permeability}
-Figures~\ref{figure2}c, d demonstrates that the initial, non-equilibrium configuration has a large internal fluid pressure
+Figures~\ref{figure2}c and~\ref{figure2}d demonstrate that the initial, non-equilibrium configuration has a large internal fluid pressure
 that vanishes as the configuration tends toward the equilibrium state.  
-This suggests that the initial collection of JP is under tension and this tension is relaxed as fluid is expelled through the inter-particle spacing. 
-To make a comparison with membrane continuum mechanics, 
-lipid bilayer membranes have a large area modulus $K_A$ of about $240$ pN nm$^{-1}$ \cite{NAGLE} 
-and changes in surface area give rise to a membrane tension
-$\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the membrane surface area and $A_0$ is the reference surface area in the non-tensed state. 
-In the two-dimensional vesicles, the tension becomes 
-\begin{equation}
+This suggests that the initial collection of JP is under tension and
+this tension is relaxed as fluid is expelled through the inter-particle
+spacing. To make a comparison with membrane continuum mechanics, lipid
+bilayer membranes have a large area modulus $K_A$ of about $240$ pN
+nm$^{-1}$ \cite{NAGLE} and changes in surface area give rise to a
+membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
+membrane surface area and $A_0$ is the reference surface area in the
+non-tensed state. In the two-dimensional vesicles, the tension becomes
+\begin{align}
 \label{eq:stretch}
-\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right).
-\end{equation}
-where $L$ and $L_0$ are the vesicle arc length and resting length, respectively. 
-A stretched, circular vesicles has a Laplace pressure 
-\begin{equation}
+\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
+\end{align}
+where $L$ and $L_0$ are the vesicle arc length and resting length,
+respectively. A stretched, circular vesicles has a Laplace pressure 
+\begin{align}
 \label{eq:LaplacePressure}
-\Delta p = \frac{\tilde \gamma}{R} 
-\end{equation}
-where $\Delta p$ is the difference in internal pressure to the pressure at infinity
-and $R$ is the radius of the circular vesicle.  The factor 
-$R^{-1}$ is the total curvature since  the principle curvature in the direction of the cylinder is zero.
+\Delta p = \frac{\tilde \gamma}{R},
+\end{align}
+where $\Delta p$ is the difference in internal pressure to the pressure
+at infinity and $R$ is the radius of the circular vesicle. The factor
+$R^{-1}$ is the total curvature since the principle curvature in the
+direction of the cylinder is zero.
 
@@
 \includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
-  \caption{JP vesicle are suspended in a quiescent flow for relaxations where the reference arc lengths $L_0$ are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm, $2.5$ nm, and $1.25$ nm, respectively.
-(a) The arc length $L$ decreases over time where the dashed curves represent the data and solid curves are linear fits; (b) A linear relationship between $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear relationship between aqueous flux $dA/dt$ and $L\Delta p$.
-For panels (b) and (c), the cross and asterisk symbols are numerical results and fitted by using solid lines.}
-    \label{figure:permeability}
+  \caption{\label{figure:permeability} JP vesicles are suspended in a
+  quiescent flow for relaxations where the reference arc lengths $L_0$
+  are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm,
+  $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$
+  decreases over time where the dashed curves represent the data and
+  solid curves are linear fits; (b) A linear relationship between
+  $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear
+  relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels
+  (b) and (c), the cross and asterisk symbols are numerical results and
+  fitted by using solid lines.}
 \end{figure}
 
-The particles in our setup do not abut but rather have small gaps due to repulsive forces.
-The gaps allow for some fluid flux across the JP bilayer. 
-In membrane mechanics, aqueous flux is quantified the equation
-\begin{equation}
-\label{eq:perm}
-\frac{dA}{dt} = -P  L \Delta p.
-\end{equation}
-where $P$ is a hydraulic permeability constant \cite{CHABANON, QGY-Y}.
-
-The JP vesicle data is in complete agreement with the continuum mechanical model \eqref{eq:stretch}-\eqref{eq:perm_solution}.
-In Figure \ref{figure:permeability}, we considered three configurations: a configuration with 58 particles 
-($L_0 = 107$ nm, plus symbols); a configuration with 119 particles ($L_0 = 218$ nm, asterick symbols);
-and finally a configuration with 117 particles but with diameter 1.25 nm rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols).
-Here $A$ and $L$ refer to the area and length of the mid plane curve separating the inner and outer monolayers. 
-(The values for $L_0$ are the asymptotic values for $L$ in Figure \ref{figure:permeability}c).
-
-Figure~\ref{figure:permeability}a plots the data for the Laplace pressure relationship \eqref{eq:LaplacePressure}.
-The pressure jump $\Delta p$ is the pressure at the particle center minus the far-field pressure (see Figure~\ref{figure2}c,d),
-$R = L/2\pi$ is the vesicle radius, and the horizontal axis is for the relative stretch. The solid lines are linear fits,
-showing that for circular JP vesicles, $R\Delta P$ is basically proportional to relative stretching $L/L_0 - 1$ . The proportionality constant is the same 
-for the 58 and 119 particle cases where the diameters are the same, suggesting that the stretching modulus $K_A$ of JP bilayers 
-is independent of the number of particles.
-The 117 particle case had diameters 1.25 nm and this data set gave a smaller stretching modulus  $K_A = 102$ pN nm$^{-1}$.
-The interpretation is that changes to particle size, while keeping $\rho$, $M$, and $\rho_0$ fixed, lead to different physical properties.
+The particles in our setup do not abut but rather have small gaps due to
+repulsive forces.  The gaps allow for some fluid flux across the JP
+bilayer.  In membrane mechanics, aqueous flux is quantified the equation
+\begin{equation} \label{eq:perm} \frac{dA}{dt} = -P  L \Delta p.
+\end{equation} where $P$ is a hydraulic permeability constant
+\cite{CHABANON, qua-gan-you2021}.
+
+The JP vesicle data is in complete agreement with the continuum
+mechanical model~\eqref{eq:stretch}-\eqref{eq:perm_solution}.  In
+Figure~\ref{figure:permeability}, we considered three configurations: a
+configuration with 58 particles ($L_0 = 107$ nm, plus symbols); a
+configuration with 119 particles ($L_0 = 218$ nm, asterick symbols); and
+finally a configuration with 117 particles but with diameter 1.25 nm
+rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols).  Here $A$
+and $L$ refer to the area and length of the mid plane curve separating
+the inner and outer monolayers.  (The values for $L_0$ are the
+asymptotic values for $L$ in Figure \ref{figure:permeability}c).
+
+Figure~\ref{figure:permeability}a plots the data for the Laplace
+pressure relationship \eqref{eq:LaplacePressure}.  The pressure jump
+$\Delta p$ is the pressure at the particle center minus the far-field
+pressure (see Figure~\ref{figure2}c,d), $R = L/2\pi$ is the vesicle
+radius, and the horizontal axis is for the relative stretch. The solid
+lines are linear fits, showing that for circular JP vesicles, $R\Delta
+P$ is basically proportional to relative stretching $L/L_0 - 1$ . The
+proportionality constant is the same for the 58 and 119 particle cases
+where the diameters are the same, suggesting that the stretching modulus
+$K_A$ of JP bilayers is independent of the number of particles. The 117
+particle case had diameters 1.25 nm and this data set gave a smaller
+stretching modulus  $K_A = 102$ pN nm$^{-1}$.  The interpretation is
+that changes to particle size, while keeping $\rho$, $M$, and $\rho_0$
+fixed, lead to different physical properties.
 

### 2021-09-01 doc/main_jfm.tex

@@
 \centering
+  \todo[inline]{The left figure is shorter than the other 2}
 \includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
@@
 bilayer.  In membrane mechanics, aqueous flux is quantified the equation
-\begin{equation} \label{eq:perm} \frac{dA}{dt} = -P  L \Delta p.
-\end{equation} where $P$ is a hydraulic permeability constant
-\cite{CHABANON, qua-gan-you2021}.
+\begin{align}
+  \label{eq:perm} 
+  \frac{dA}{dt} = -P  L \Delta p,
+\end{align}
+where $P$ is a hydraulic permeability constant \cite{CHABANON,
+qua-gan-you2021}.
 
 The JP vesicle data is in complete agreement with the continuum
-mechanical model~\eqref{eq:stretch}-\eqref{eq:perm_solution}.  In
+mechanical model~\eqref{eq:stretch}--\eqref{eq:perm}. In
 Figure~\ref{figure:permeability}, we considered three configurations: a
 configuration with 58 particles ($L_0 = 107$ nm, plus symbols); a
-configuration with 119 particles ($L_0 = 218$ nm, asterick symbols); and
+configuration with 119 particles ($L_0 = 218$ nm, asterisk symbols); and
 finally a configuration with 117 particles but with diameter 1.25 nm
@@
 and $L$ refer to the area and length of the mid plane curve separating
-the inner and outer monolayers.  (The values for $L_0$ are the
-asymptotic values for $L$ in Figure \ref{figure:permeability}c).
+the inner and outer monolayers. The values for $L_0$ are the asymptotic
+values for $L$ in Figure~\ref{figure:permeability}c.
 
@@
 $\Delta p$ is the pressure at the particle center minus the far-field
-pressure (see Figure~\ref{figure2}c,d), $R = L/2\pi$ is the vesicle
-radius, and the horizontal axis is for the relative stretch. The solid
-lines are linear fits, showing that for circular JP vesicles, $R\Delta
-P$ is basically proportional to relative stretching $L/L_0 - 1$ . The
-proportionality constant is the same for the 58 and 119 particle cases
-where the diameters are the same, suggesting that the stretching modulus
-$K_A$ of JP bilayers is independent of the number of particles. The 117
-particle case had diameters 1.25 nm and this data set gave a smaller
-stretching modulus  $K_A = 102$ pN nm$^{-1}$.  The interpretation is
-that changes to particle size, while keeping $\rho$, $M$, and $\rho_0$
-fixed, lead to different physical properties.
+pressure (see Figures~\ref{figure2}c and~\ref{figure2}d), $R = L/2\pi$
+is the vesicle radius, and the horizontal axis is the relative stretch.
+The solid lines are linear fits, showing that for circular JP vesicles,
+$R\Delta P$ is essentially proportional to the relative stretching
+$L/L_0 - 1$. The proportionality constant is the same for the 58 and 119
+particle cases where the diameters are the same, suggesting that the
+stretching modulus $K_A$ of JP bilayers is independent of the number of
+particles. The 117 particle case had diameters 1.25 nm and this data set
+results in a smaller stretching modulus of $K_A = 102$~pN~nm$^{-1}$. The
+interpretation is that changes to particle size, while keeping $\rho$,
+$M$, and $\rho_0$ fixed, lead to different physical properties.
 
@@
 The slopes of the linear fits give the hydraulic permeability
-coefficient $P.$ The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$
+coefficient $P$. The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$
 pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 58 and 119
@@
 permeability is independent of particle number, as was the case for the
-stretching modulus.  The permeability for the 117 particle number case
-was larger, 0.0566 nm$^3$ ns$^{-1}$ pN$^{-1}$.  That is because
-hydrophobic attraction vanishes with particle size, leading to larger
-gaps between the particles for the same repulsion.  The hydraulic
-permeability we calculate, however, is not in agreement with
+stretching modulus. The permeability for the 117 particle number is
+0.0566 nm$^3$~ns$^{-1}$~pN$^{-1}$. The increase in the permeability is
+caused by the hydrophobic attraction vanishing with particle size,
+leading to larger gaps between the particles for the same repulsion. The
+hydraulic permeability we calculate, however, is not in agreement with
 experimentally derived values and is larger by a few orders of
@@
 
-Since the vesicles in Figure~\ref{figure2}a are nearly we circular, we
-can combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
+Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
+combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
 and~\eqref{eq:perm}, to derive

### 2021-09-01 doc/main_jfm.tex
working on shear examples

@@
 The centroid of the pre-relaxed $58$-body Janus vesicle is initially
-placed at the origin and the shear flow with a certain shear rate $\chi$
-is applied. Snapshots of the JP vesicle in a shear flow with a shear
-rate $\chi=0.0025$ are shown in Figure~\ref{figure3}. Panels (a) and (b)
-show the initial shape obtained from the relaxation run and the deformed
-configurations of the JP vesicle at time $t=4000$ are in panels (c)
-and (d). The background color in panels (a) and (c) is the strength of
-the action of the hydrophobic attraction. Red corresponds to a strong
-action while blue is weak action. The hydrophobic layer clearly has the
+placed at the origin and the shear flow with a shear rate $\chi$ is
+applied. Figure~\ref{figure3} shows snapshots of the JP vesicle in the
+shear flow with a shear rate $\chi=0.0025$. Panels (a) and (b) show the
+initial shape obtained from the relaxation run and the deformed
+configurations of the JP vesicle at time $t=4000$ are in panels (c) and
+(d). The background color in panels (a) and (c) is the strength of the
+action of the hydrophobic attraction. Red corresponds to a strong action
+while blue is a weak action. The hydrophobic layer clearly has the
 strongest action. To demonstrate the tank-treading behavior of the
 vesicle, panels (b) and (d) provide the streamlines of the fluid
-velocity around the JP vesicle. In panel (d), we can clearly observe
-the clockwise tank-treading motion.
+velocity around the JP vesicle. In panel (d), we can clearly observe the
+clockwise tank-treading motion.
 
@@
 \includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
-  \caption{\label{figure3} A JP vesicle suspended in a shear flow
-  with shear rate $\chi=0.0025$: (a) Initial configuration of 58-body
-  JP vesicle where black arrows are the particle orientations. (b)
-  The particle velocities and streamlines of the configuration in (a).
-  Streamlines are plotted in the background as solid curves. Red arrows
-  represent the particle velocities. (c) Deformed JP vesicle at
-  $t=4000$. At this configuration the JP vesicle is tank-treading.
-  (d) The particle velocities and streamlines of the configuration in
-  (c). The background colors in panels (a) and (c) represent the
-  strength of the hydrophobic attraction potential. The blue region
-  shows no action and the red region in the bilayer gives the strongest
-  action.}
+  \caption{\label{figure3} A JP vesicle suspended in a shear flow with
+  shear rate $\chi=0.0025$. (a) The initial configuration of a 58-body
+  JP vesicle where the black arrows point in the direction of the
+  hydrophobic side of the JP. (b) The particle velocities and
+  streamlines of the configuration in (a). The streamlines are plotted
+  in the background as solid curves and the red arrows represent the
+  particle velocities. (c) The deformed tank-treading JP vesicle at
+  $t=4000$. (d) The particle velocities and streamlines of the
+  configuration in (c). The background colors in panels (a) and (c)
+  represent the strength of the hydrophobic attraction potential. The
+  blue regions have the weakest action and the red regions in the
+  bilayer have the strongest action.}
 \end{figure}
-%
 %
@@
 calculated from the midplane. The reduced area is $A^* = 4\pi A/L^2$
-where $A$ the area, and $L$ the total length of the JP vesicle, and
-the excess length is $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
-Figure~\ref{figure4} shows these quantities for a JP vesicle
-suspended in a shear flow with shear rates
-$\chi=\{0.002,0.0025,0.003,0.0035\}$. Since the starting configuration
-is nearly circular, the reduced area decreases from an initial value
-close to $1$. The smooth curves in panel (a) are best fits of the
-exponential model $A^* = a_0 + b_0 \exp(-kt)$. Panel (b) shows that the
-decay rate $k$ is independent of the shear rate for sufficiently large
-shear rates, and the terminal reduced areas of each case are shown in
-the inset. We see that lower shear rates generate a higher final reduced
-area. In particular, we observe that the reduce area converges
-relatively early when the shear rate is lower than $\chi=0.003$. 
+where $A$ is the area, and $L$ is the total length of the JP vesicle,
+and the excess length is $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
+Figure~\ref{figure4} shows these quantities for a JP vesicle suspended
+in a shear flow with shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$.
+Since the starting configuration is nearly circular, the reduced area
+decreases from an initial value close to $1$. The smooth curves in panel
+(a) are best fits of the exponential model $A^* = a_0 + b_0 \exp(-kt)$.
+Panel (b) shows that the decay rate $k$ is independent of the shear rate
+for sufficiently large shear rates, and the terminal reduced areas of
+each case are shown in the inset. We see that lower shear rates generate
+a higher final reduced area. In particular, we observe that the reduce
+area converges relatively early when the shear rate is lower than
+$\chi=0.003$. 
 %and has a faster convergence than the high shear rate cases.
@@
 \end{center} 
-  \caption{\label{figure4} (a) Total arc lengths of the midplanes over
-  time for four shear rates. (b) From exponential fits in panel (a), we
-  obtain the decay rate $k$ for a number of different shear rates. The
-  inset plots the terminal reduced areas. (c) Reduced area transitions
-  over time. (d) Excess length of the midplanes. For all panels, a set
-  of shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in
-  simulations. The legend in panel (d) applies to both panels (a) and
-  (c).}
+  \caption{\label{figure4} (a) The reduced area transitioning over time
+  for four different shear rates. The smooth curves are a best-fit
+  exponential curve. (b) The decay rate $k$, using the exponential fit
+  to the data in panel (a), for a number of shear rates. The inset shows
+  the terminal reduced areas. (c) The total arc lengths of the midplanes
+  over time for four shear rates. (d) The excess length of the
+  midplanes. For all panels, a set of shear rates
+  $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. The
+  legend in panel (d) applies to both panels (a) and (c).}
 \end{figure}
@@
 The granulated JP vesicle allows us to consider inter-monolayer slip
-between two leaflets. When the shear rate is sufficiently large, take
-$\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip between a
-pair of particles over time. The pair we consider are colored in blue
-and yellow. In this series of tests, we compute the mean particle
-position and mean angle $\theta(t)$ between the particle relative
-positions with respect to the vesicle center. It is clear that the outer
-leaflet has larger tangential velocity than the inner leaflet since the
-mean angle $\theta(t)$ increases. This inter-leaflet sliding phenomenon
-is consistent with what has been seen in articles in molecular dynamics
+between the two leaflets. When the shear rate is sufficiently large,
+take $\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip
+between a pair of particles over time. The pair we consider are colored
+in blue and yellow. In this series of tests, we compute the mean
+particle position and mean angle $\theta(t)$ between the particle
+relative positions with respect to the vesicle center. It is clear that
+the outer leaflet has larger tangential velocity than the inner leaflet
+since $\theta(t)$ increases. This inter-leaflet sliding phenomenon is
+consistent with what has been seen in articles in molecular dynamics
 simulations.
-
-%
-%\todo[inline]{Figure/Table of the friction coefficient for different shear rates (needs to revise)}
+\todo[inline]{Need a reference here}
 
@@
   denoted as $\Sigma_M$. We see that the intermonolayer slip is largest
-  at larger shear rates.}
+  for large shear rates.}
 \end{figure}
@@
 %
-where $\langle F\rangle = \langle \int_{\mathcal{C}_M} \jump{\ttau \cdot
-\sigma \cdot \nnu} \,ds\rangle$ is the time-averaged, tangential force
-along the midplane curve $\mathcal{C}_m$. The parameters $\langle
-L\rangle$ and $\langle U\rangle$ are the time-averaged midplane curve
-length and intermonolayer slip velocity respectively.
+where 
+\begin{align}
+  \langle F\rangle = \left\langle \int_{\mathcal{C}_M} 
+    \jump{\ttau \cdot \sigma \cdot \nnu} \,\dif s \right\rangle
+\end{align}
+is the time-averaged, tangential force along the midplane curve
+$\mathcal{C}_m$. The parameters $\langle L\rangle$ and $\langle
+U\rangle$ are the time-averaged midplane curve length and intermonolayer
+slip velocity, respectively.
 
@@
 several shear rates and the results are in quantitative agreement with
-values previously reported in the literature~\cite{sch-vla-mik2010}
-and~\cite{denOtter2007}. The coefficients generally lie within the
+values previously reported in the literature (\cite{sch-vla-mik2010}
+and~\cite{denOtter2007}). The coefficients generally lie within the
 range 0.2 to 0.3 pN$\cdot$ns nm$^{-3}$ but there are some outliers.
@@
 0.0066$ ns$^{-1}$) correspond to slip velocities that are too low
-relative to shear rate (see the green and red curve in Figure
-\ref{figure5}: panel (c)). The JP vesicle consists of only 58
-particles and so it is not surprising that discrete effects produce
-outliers.
+relative to the shear rate (see the green and red curve in
+Figure~\ref{figure5}(c)). The JP vesicle consists of only 58 particles
+and so it is not surprising that discrete effects produce outliers.
 
@@
 %
-where $v_{max}$ is the flow strength and $w$ controls the shape of the
-flow. $R_0$ is defined as the radius of the JP vesicle at $t=0$.
-The behavior of a vesicle in this unbounded non-linear flow includes
-vertical migration, and depending on the flow rate and reduced area,
-the steady-state shape can be either an symmetric parachute or
-an asymmetric slipper~\cite{Kaoui09, cou-kao-pod-mis2008,
-dan-vla-mis2009}.
+where $v_{max}$ is the flow strength and $w$ determines the shape of the
+flow. $R_0$ is defined as the radius of the JP vesicle at $t=0$. The
+behavior of a vesicle in this unbounded non-linear flow includes
+vertical migration, and depending on the flow rate and reduced area, the
+steady-state shape can be either an symmetric parachute or an asymmetric
+slipper~\cite{Kaoui09, cou-kao-pod-mis2008, dan-vla-mis2009}.
 

### 2021-09-01 doc/main_jfm.tex
done up to end of 4.4

@@
 \begin{align}
-  \uu_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2
+  \uu_\infty = v_{max}\left[ 1 - \left( 
+    \frac{\xx \cdot \mathbf{e}_y}{wR_0}\right)^2
     \right]\mathbf{e}_x,
@@
 vertical migration, and depending on the flow rate and reduced area, the
-steady-state shape can be either an symmetric parachute or an asymmetric
-slipper~\cite{Kaoui09, cou-kao-pod-mis2008, dan-vla-mis2009}.
+steady-state shape can be either a symmetric parachute or an asymmetric
+slipper (\cite{Kaoui09, cou-kao-pod-mis2008, dan-vla-mis2009}).
 
@@
 counterclockwise movement and the shape of the vesicle approaches an
-asymmetric slipper shape. For this test, the reduced area for this
+asymmetric slipper shape. Moreover, we observe inter-monolayer slip
+between the two leaflets. For this test, the reduced area for this
 configuration is approximately $0.9$ which matches the previous
@@
 Figure~\ref{figure7} shows the trajectory of the mean position in the
-$y$-direction which decreases toward $y=1$ for a period of time and then
-starts to have an oscillatory motion due to the granularity of the
-JP vesicle.
+$y$-direction that decreases towards $y=1$ for a period of time and then
+starts to oscillate due to the granularity of the JP vesicle.
 
@@
   the state when $t=\{0, 4000, 8000\}$. The red curves are the
-  midplanes.}
+  midplanes. Inter-monolayer slip is observed by comparing the relative
+  locations of the blue and yellow particles.}
 \end{figure}
@@
 \includegraphics[height=2in]{parabolic.eps}
-  \caption{\label{figure7} The schematic of a JP vesicle suspended in
-  a parabolic flow where the strength of the flow is $v_{max}=32.8$~nm
-  ns$^{-1}$, $R_0 = 20$~nm, and the control parameter is $w=25$~nm. The
-  configuration is generated when $t=10000$. The inset plots the
-  trajectory of mean $y$-position over the time.}
+  \caption{\label{figure7} The schematic of a JP vesicle suspended in a
+  parabolic flow where the strength of the flow is
+  $v_{max}=32.8$~nm~ns$^{-1}$, $R_0 = 20$~nm, and the control parameter
+  is $w=25$~nm. The configuration occurs when $t=10000$. The inset plots
+  the trajectory of mean $y$-position over time.}
 \end{figure}
@@
 
-With the choice of a large shear rate, a pore formation or a complete
-membrane rupture can occur. Figure~\ref{figure8} demonstrates how a
-vesicle under a shear flow with shear rate $\chi=0.1$ can rupture. The
-streamlines are included in these plots. An interesting phenomenon
-occurs in panels (c) and (d) where two separated bilayers move along the
-background shear flow symmetrically.  Consequently, a periodic motion
-for bilayers may occur with the choices of shear rates. One can expect
-that these two layers will flow far apart from each other for much
-higher shear rates.
+A pore formation or a complete membrane rupture can occur at large shear
+rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture when
+suspended in a shear flow with shear rate $\chi=0.1$. The streamlines
+are included in these plots. An interesting phenomenon occurs in panels
+(c) and (d) where two separated bilayers move along the background shear
+flow symmetrically. Consequently, a periodic motion for bilayers may
+occur at certain shear rates. One can expect that these two layers will
+diverge from one another for much higher shear rates.
 
@@
   with a circular shape (panel (a)), the vesicle is stretched by the
-  background flow and multiple pores appear (panel (b)).  Panels
-  (c)--(d) show the later states during the simulation. Streamlines are
-  included in each panel.}
+  background flow and multiple pores form (panel (b)). Panels (c)--(d)
+  show the later states during the simulation. Streamlines are included
+  in each panel.}
 \end{figure}

### 2021-09-03 doc/main_jfm.tex
wrapped up Sec 4 again

@@
 
-Figure~\ref{figure9} shows the simulation of two JP vesicles in a
-shear flow with shear rate $\chi=0.005$. Using the pre-relaxed $58$-body
-JP vesicle in previous sections, we duplicate the state to have the
-initial configuration shown in panel (a). The two centers of mass are at
-$(-10,0)$ and $(10,0)$. In all panels, the blue and red curves show the
-trajectory of the two JP vesicle centroids. They have nearly
-completed a full period by $t=4000$ as shown in panel (h). We also
-observe an adhesive effect between the two JP vesicles that is set up
-by the hydrophobic interactions and repulsive force. Similar dynamics
-have been observed between a pair of adhering vesicles in a shear flow
+Figure~\ref{figure9} shows the simulation of two JP vesicles suspended
+in a shear flow with shear rate $\chi=0.005$. We duplicate the
+pre-relaxed $58$-body JP vesicle from previous sections to construct the
+initial configuration shown in Figure~\ref{figure9}(a). The two centers
+of mass are at $(-10,0)$ and $(10,0)$. In all panels, the blue and red
+curves show the trajectory of the two JP vesicle centroids. They have
+nearly completed a full period by $t=4000$. We also observe an adhesive
+effect between the two JP vesicles that is set up by the hydrophobic
+interactions and repulsive force. Similar dynamics have been observed
+between a pair of adhering vesicles in a shear flow
 (\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
@@
 
-The fluid pressure profiles snapshots are given in
-Figure~\ref{figure10}. Since the initial JP vesicles are pre-relaxed,
-there is initially no pressure jump between the internal and external
-fluids (panel (a)). Panels (b)--(d) show the configurations when $t =
-\{500,1000,1500\}$ and the streamlines are plotted in the background for
-all panels. We include the numerical results using a continuum model in
-all insets and these comparisons give a qualitative agreement between
-two models.
+Snapshots of the fluid pressure are in Figure~\ref{figure10}. Since the
+initial JP vesicles are pre-relaxed, there is initially no pressure jump
+between the internal and external fluids (panel (a)). Panels (b)--(d)
+show the configurations when $t = \{500,1000,1500\}$, and the
+streamlines are plotted in the background for all panels. We include the
+numerical results from a continuum model in all insets and these
+comparisons give a qualitative agreement between two models.
 
@@
 
-With a similar setup in the case of two JP vesicles in a shear flow,
-we use the same two pre-relaxed $58$-body JP vesicles and consider
-their dynamics in an extensional flow with extensional rate
-$\chi=0.005$. This extensional flow is stretching in the $y$ direction
-and squeezing in the $x$ direction. Figure~\ref{figure11} shows how the
-initial placement of the JP vesicles affects the dynamics. When two
-centroids are both placed symmetrically on the $x$-axis (case (i)), the
-JP vesicles reach a steady equilibrium. If one centroid is placed
-above the $x$-axis (case (ii)), the two JP vesicle move together and
-then upward. The migration of the right JP vesicle is a consequence
-of the adhesive effect created by the hydrophobic interactions. When the
-two centroids start on opposite sides of the $x$-axis (case (iii)), they
-eventually diverge from one another along the $y$-axis. Finally, when
-the two centroids start on opposite sides of the $x$-axis, but with a
-greater displacement (case (iv)), the JP vesicles move much faster
-toward $\pm y$-directions.
-
-Figure~\ref{figure12} shows numerical results when the centroids of two
-bodies are placed at $(-10,-0.1)$ and $(10,0.1)$ (case (iii) from
-Figure~\ref{figure11}). With this setup, the two
-JP vesicles eventually separate along $y$-direction and we compare
-the results against a continuum model as shown in all insets.  Panels
-(b)--(d) show the transient behavior of the JP vesicles and continuum
-vesicles transitions under an extensional flow. In both the
-coarse-grained model and the continuum model, the vesicles initially
-converge towards one other and then diverge along the $y$-axis. The
-behavior of the streamlines in both cases are similar. The pressure is
-initially largest in the gap formed by two JP vesicles and decreases
-during the separation. The short range repulsion plays an important role
-to avoid structure collisions.
+Using a similar setup to the shear case, we suspend the same two
+pre-relaxed $58$-body JP vesicles and consider their dynamics in an
+extensional flow with extensional rate $\chi=0.005$. This extensional
+flow is stretching in the $y$ direction and squeezing in the $x$
+direction. Figure~\ref{figure11} shows how the initial placement of the
+JP vesicles affects the dynamics. When two centroids are both placed
+symmetrically on the $x$-axis (case (i)), the JP vesicles reach a steady
+equilibrium. If one centroid is placed above the $x$-axis (case (ii)),
+the two JP vesicle move together and then upward. The migration of the
+right JP vesicle is a consequence of the adhesive effect caused by the
+hydrophobic interactions. When the two centroids start on opposite sides
+of the $x$-axis (case (iii)), they eventually diverge from one another
+along the $\pm y$-directions. Finally, when the two centroids start on
+opposite sides of the $x$-axis, but with a greater displacement (case
+(iv)), the JP vesicles move much faster along the $\pm y$-directions.
+
+Figure~\ref{figure12} shows numerical results when the centroids of the
+two Janus particles are placed at $(-10,-0.1)$ and $(10,0.1)$ (case
+(iii) from Figure~\ref{figure11}). With this setup, the two JP vesicles
+eventually separate along the $\pm y$-directions and we compare the
+results against a continuum model as shown in all insets. Panels
+(b)--(d) show the transient behavior of the JP vesicles and the
+continuum vesicles under an extensional flow. In both the coarse-grained
+model and the continuum model, the vesicles initially converge towards
+one other and then diverge along the $y$-axis. The behavior of the
+streamlines in both cases are similar. The pressure is initially largest
+in the gap formed by two JP vesicles and decreases during the
+separation. The short range repulsion plays an important role to avoid
+structure collisions.
 %and this result can be
@@
 %may need to add more here
-
-%\todo[inline]{Make figure of the paths of the two centroids....}
 

### 2021-09-06 doc/main_jfm.tex
some changes (fig,ref)

@@
 consistent with what has been seen in articles in molecular dynamics
-simulations.
+simulations. (\cite{Zgorski2019,denOtter2007})
 \todo[inline]{Need a reference here}
@@
   20$~nm, and the control parameter is $w=25$~nm. The configuration is
-  the state when $t=\{0, 4000, 8000\}$. The red curves are the
-  midplanes. Inter-monolayer slip is observed by comparing the relative
-  locations of the blue and yellow particles.}
+  the state when $t=\{0, 4000, 8000\}$ which correspond to $0\ \mu $s, $2.44\ \mu $s, and $4.88\ \mu $s.
+The red curves are the midplanes.
+Inter-monolayer slip is observed by comparing the relative  locations of the blue and yellow particles.}
 \end{figure}
@@
   $v_{max}=32.8$~nm~ns$^{-1}$, $R_0 = 20$~nm, and the control parameter
-  is $w=25$~nm. The configuration occurs when $t=10000$. The inset plots
-  the trajectory of mean $y$-position over time.}
+  is $w=25$~nm. The configuration occurs when $t=6.1\ \mu$s and red arrows indicate the tank-treading motion. The inset plots the trajectory of mean $y$-position over time.}
 \end{figure}
@@
 We also study the migration of a JP vesicle suspended in a parabolic flow and obtain the asymmetric slipper shape.
-The reduced area $A^*$ of the starting JP vesicle is closed to 1 and $A^*=0.9$ at the equilibrium
+The reduced area $A^*$ of the starting JP vesicle is close to 1 and $A^*=0.9$ at the equilibrium
 state.

### 2021-09-06 doc/main_jfm.tex
some changes (fig captions)

@@
   located on the $x$-axis. For simulation time, $t = {0, 400,800,1200}$
-  for (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).}
+  for (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).
+  The fluid velocity profile is plotted in the background.
+  }
 \end{figure}
@@
   Figure~\ref{figure12} presents the numerical results from the case
-  (iii).}
+  (iii).  The fluid velocity profile is plotted in the background.}
 \end{figure}

### 2021-09-06 doc/main_jfm.tex
some changes (fig captions)
some changes (conclusion,ref)

@@
   where the dimensioneless shear rate is $\chi=0.005$. The initial
-  configuration is shown in panel (a). The background color is the fluid
+  configuration is shown in panel (a). Panels (b)-(d) represent configurations when $t = \{500, 1000, 1500\}$.
+  The background color is the fluid
   pressure. The color bar is identical for all panels. Streamlines are
@@
   simulations of a continuum model of the vesicles and the streamlines
-  agree between the two models.}
+  agree between the two models. }
 \end{figure}
@@
   $0.1$ units below the $x$-axis. The initial configuration is shown in
-  panel (a). The background color is the fluid pressure. The color bar
+  panel (a). Panels (b)-(d) represent configurations when $t = \{400, 800, 1300\}$. 
+  The background color is the fluid pressure. The color bar
   is identical for all panels. Streamlines are plotted in purple. The
@@
 This study proposes a continuum coarse-grained model for JP vesicle that focuses on the 
-hydrophobic interactions between lipids and hydrodynamic interactions.
+hydrophobic interactions between coarse-grained lipids and hydrodynamic interactions.
+The hydrophobic interactions exhibit the self-assembly property of the lipid bilayer menbrane different from
+the pair-particle interactions adopted in molecular dynamics simulations. 
+The proposed energy potential combining with the mobility problems for rigid body motion leads to capture membrane mechanics such as deformations, stretching modulus, and the permeability of JP membrane in a solvent.
+This work is highly applicable with fields in material science and condensed matter physics such as Janus colloid (\cite{Bradley2017,Mallory2017}) and the setup can be easily tuned to match the experiments,
+for instance, morphology of colloid surfactants. (\cite{Bradley2016})
+
 The mobility problem using integral equation methods combines the previously introduced HAP and the 
 revised hydrophobic force for obtaining particle dynamics. 
-
 The imposed forces and torques of JP system adopt not only HAP but also a newly developed short 
@@
 
-We also study the migration of a JP vesicle suspended in a parabolic flow and obtain the asymmetric slipper shape.
-The reduced area $A^*$ of the starting JP vesicle is close to 1 and $A^*=0.9$ at the equilibrium
-state.
+We also study the spatial migration of a JP vesicle suspended in a parabolic flow and obtain the asymmetric slipper shape.
+The reduced area $A^*$ of the starting JP vesicle is close to 1 and $A^*=0.9$ at the equilibrium state.
 A qualitative agreement has been made comparing with the two-dimensional inextensible membrane in continuum modeling simulations presented in~\cite{Kaoui09}.
-An interesting outcome is that the mean
-$y$-position of the JP vesicle performs an oscillatory motion toward the center of the Poiseuille flow and this
-may be caused by the granularity of the JP vesicle and choices of model parameters.
+An interesting outcome is that the mean $y$-position of the JP vesicle performs an oscillatory motion toward the center of the Poiseuille flow and this may be caused by the granularity of the JP vesicle and choices of model parameters.
 
@@
 practical approach.
+One ongoing work is to add thermal fluctuations onto Janus particles to obtain Brownian dynamics is crucial for obtaining membrane diffusion.
 Having a more physical boundary conditions on JP boundaries with experimental data is a reasonable direction and the future comparison with the laboratory experiments can be accomplished.

### 2021-09-07 doc/main_jfm.tex
working on conclusions

--- 2021-09-06 doc/main_jfm.tex
@@
 in the gap formed by two JP vesicles and decreases during the
-separation. The short range repulsion plays an important role to avoid
+separation. The short-range repulsion plays an important role to avoid
 structure collisions.
@@
 
-This study proposes a continuum coarse-grained model for JP vesicle that focuses on the 
-hydrophobic interactions between lipids and hydrodynamic interactions.
-The mobility problem using integral equation methods combines the previously introduced HAP and the 
-revised hydrophobic force for obtaining particle dynamics.
-
-The imposed forces and torques of JP system adopt not only HAP but also a newly developed short 
-range repulsion given by \ref{eq:REPULforce} and \ref{eq:REPULtorque}.
-The hydrodynamic stress tensor calculated in the algorithm leads to examinations of permeable 
-membrane where the stretching modulus $K_A$ and the permeability constant $P$ can be obtained.
-%
-With the use of selected parameters, the numerical algorithm yields good qualitative results such as
-phenomena in tank-treading JP vesicle. The reduced area $A^*$ decreases as the shear rate increases
- and we measure the equilibrium reduced area for a number of shear rates. The results show that the total
- length of JP vesicle is conserved and the decay rate of the reduced area is independent of shear rates when shear rates $\dot\gamma$ are between $\sim0.005$ ns$^{-1}$ and $0.008$ ns$^{-1}$.
-Moreover, the proposed model can capture the membrane rupture when the shear flow is at a high shear rate
-and this makes a breakthrough about having an idea for simulating such phenomenon different from other continuum modeling simulations when the bilayer membrane is represented as a closed and continuous curve.
-
-Inter-monolayer friction coefficients $b$ are then obtained and reported by calculating the friction force $F_f$
-using pressure jumps and slip velocities with respect to the bilayer midplane.
-The resulting friction coefficients $b$ are about one order of magnitude smaller than ones in
-~\cite{denOtter2007} and this observation suggests that the granularity of the system is a factor of having 
-the discrepancy. The coarse-graining level of the JP vesicle has much longer length scale comparing against
-the molecular dynamics simulations, in addition, the repulsive potential creates gaps between JP where the 
-error in slip velocities piles up over the computational time.
-
-We also study the migration of a JP vesicle suspended in a parabolic flow and obtain the asymmetric slipper shape.
-The reduced area $A^*$ of the starting JP vesicle is close to 1 and $A^*=0.9$ at the equilibrium
-state.
-A qualitative agreement has been made comparing with the two-dimensional inextensible membrane in continuum modeling simulations presented in~\cite{Kaoui09}.
-An interesting outcome is that the mean
-$y$-position of the JP vesicle performs an oscillatory motion toward the center of the Poiseuille flow and this
-may be caused by the granularity of the JP vesicle and choices of model parameters.
-
-Results of two JP vesicles suspended in both shear and extensional flows have outstanding agreements with ones generated using continuum modeling in streamlines comparisons.
-For two JP vesicles in shear flow, a demonstration of rotating behavior is presented and two overlapping 
-trajectories of two centroid are observed as expected when two starting centroids are placed on the same 
-horizontal level. The hydrophobic action and the repulsive potential lead to an adhesive effect when two 
-JP bilayers are within a short distance.
-We provide a series of results when two JP vesicles are suspended in extensional flow.
-We obtain similar results to the ones in \cite{qua-vee-you2019} when the reduced area $A^*$ is high and both centroids are placed
-with some vertical displacements.
-
-Our future goal is to extend the current framework to a three-dimensional JP vesicle system. 
-The further implementation of adding a fast algorithms such as the fast multipole method is also a 
-practical approach.
-Having a more physical boundary conditions on JP boundaries with experimental data is a reasonable direction and the future comparison with the laboratory experiments can be accomplished.
+This study presents a continuum coarse-grained model for JP vesicles
+that focuses on the hydrophobic interactions between coarse-grained
+lipids and hydrodynamic interactions. In contrast to molecular dynamic
+simulations, the hydrophobic interactions exhibit the self-assembly
+property of the lipid bilayer membrane. The proposed energy potential
+combined with the mobility problem for rigid body motions captures
+membrane mechanics including deformations, stretching modulus, and the
+permeability of a JP membrane. This work is highly applicable with
+fields in material science and condensed matter physics such as Janus
+colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
+match experimental results such as the morphology of colloid
+surfactants~(\cite{Bradley2016}).
+
+Integral equation methods are used to solve the mobility problem and the
+previously introduced HAP model that determines the forces and torques
+of the individual rigid bodies. In addition to the HAP forces and
+torques, we impose a short-range repulsion to avoid unphysical contact.
+Our method requires calculations of the hydrodynamic stress tensor, and
+this is leads to examinations of the membrane permeability constant $P$
+and the membrane stretching modulus $K_A$. With the use of suitable
+parameters, the numerical results yield good qualitative phenomena such
+as a tank-treading JP vesicle. The reduced area $A^*$ decreases as the
+shear rate increases and we measure the equilibrium reduced area for
+various shear rates. The results show that the total length of a JP
+vesicle is conserved and the decay rate of the reduced area is
+independent of the shear rate values  between $0.005$~ns$^{-1}$
+and~$0.008$ ns$^{-1}$. Moreover, the proposed model can describe
+membrane rupture in high shear rates. Therefore, our methods can be
+applied to vesicles undergoing topological changes which is not
+difficult to simulate when using a continuum model that represents
+vesicles as closed and continuous curves.
+
+Our coarse-grained model is also able to calculate inter-monolayer
+friction. The inter-monolayer friction coefficients are determined by
+calculating the tangential friction force and slip velocities with
+respect to the bilayer midplane. The resulting friction coefficients $b$
+are about one order of magnitude smaller than those reported
+by~\cite{denOtter2007}, and this discrepancy is partially due to the
+granularity of the model. In addition, the coarse-graining level of the
+JP vesicle has a much larger length scale than molecular dynamics
+simulations, and the repulsive force creates gaps between Janus
+particles where the error in slip velocities accumulates over time.
+
+We also study the spatial migration of a JP vesicle suspended in a
+parabolic flow. The chosen parameter values results in an asymmetric
+slipper shape. A qualitative agreement has been made comparing with the
+two-dimensional inextensible membrane in continuum modeling
+simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). The
+initial reduced area of the JP vesicle is $A^* \approx 1$ and the
+equilibrium reduced area is $A^*=0.9$. An interesting result of the JP
+vesicle is that the mean $y$-position oscillates toward the center of
+the Poiseuille flow and this may be caused by the granularity of the JP
+vesicle and choices of the model parameters.
+
+\todo[inline]{Bryan left off here}
+Results of two JP vesicles suspended in both shear and extensional flows
+have outstanding agreements with ones generated using continuum modeling
+in streamlines comparisons. For two JP vesicles in shear flow, a
+demonstration of rotating behavior is presented and two overlapping
+trajectories of two centroid are observed as expected when two starting
+centroids are placed on the same horizontal level. The hydrophobic
+action and the repulsive potential lead to an adhesive effect when two
+JP bilayers are within a short distance. We provide a series of results
+when two JP vesicles are suspended in extensional flow. We obtain
+similar results to the ones in \cite{qua-vee-you2019} when the reduced
+area $A^*$ is high and both centroids are placed with some vertical
+displacements.
+
+Our future goal is to extend the current framework to a
+three-dimensional JP vesicle system. The further implementation of
+adding a fast algorithms such as the fast multipole method is also a
+practical approach. One ongoing work is to add thermal fluctuations onto
+Janus particles to obtain Brownian dynamics is crucial for obtaining
+membrane diffusion. Having a more physical boundary conditions on JP
+boundaries with experimental data is a reasonable direction and the
+future comparison with the laboratory experiments can be accomplished.
 

### 2021-09-08 doc/main_jfm.tex
yny Sep07

@@
 Whether it is surface chemistry or polarity under an external field, the
-dynamics of Janus particles is inevitably the combination of long-range
-hydrodynamics interactions in the presence of short- and
-intermediate-range particle-particle interactions. Recently~\cite{Fu20}
+dynamics of Janus particles in a viscous solvent is inevitably the combination of long-range
+hydrodynamics interactions with both short- and intermediate-range 
+particle-particle interactions. Such multi-scale nature of Janus particle dynamics underlies 
+the richness of a Janus particle suspension, as \cite{deGennes1991} suggested by the example of 
+a ``thin film of Janus grains" that can breathe due to the interstices between Janus particles.
+
+Recently~\cite{Fu20}
 illustrated that the hydrophobic interactions between Janus particles in

### 2021-09-10 doc/main_jfm.tex
edited another paragraph in the conclusions

@@
 
+We compare two JP vesicles with a similar setup using a continuum model.
+A comparison of the vesicle shapes and the streamlines demonstrate
+remarkable similarities. The two overlapping trajectories of the JP
+vesicles' centroids in a shear flow evolve as expected when the two
+centroids are initialized on the same horizontal level. We also observe
+a rotating behavior that is observed for models involving vesicle
+adhesion~(\cite{qua-vee-you2019}). The hydrophobic action and the
+repulsive potential lead to this adhesive effect when two JP bilayers
+are within a short distance. We also perform four simulations of two JP
+vesicles suspended in an extensional flow. We vary the initial vertical
+displacement of the vesicles' centroids and obtain similar results to
+the continuum model.
+
 \todo[inline]{Bryan left off here}
-Results of two JP vesicles suspended in both shear and extensional flows
-have outstanding agreements with ones generated using continuum modeling
-in streamlines comparisons. For two JP vesicles in shear flow, a
-demonstration of rotating behavior is presented and two overlapping
-trajectories of two centroid are observed as expected when two starting
-centroids are placed on the same horizontal level. The hydrophobic
-action and the repulsive potential lead to an adhesive effect when two
-JP bilayers are within a short distance. We provide a series of results
-when two JP vesicles are suspended in extensional flow. We obtain
-similar results to the ones in \cite{qua-vee-you2019} when the reduced
-area $A^*$ is high and both centroids are placed with some vertical
-displacements.
-
 Our future goal is to extend the current framework to a

### 2021-09-12 doc/main_jfm.tex

@@
 
-This study presents a continuum coarse-grained model for JP vesicles
-that focuses on the hydrophobic interactions between coarse-grained
-lipids and hydrodynamic interactions. In contrast to molecular dynamic
-simulations, the hydrophobic interactions exhibit the self-assembly
-property of the lipid bilayer membrane. The proposed energy potential
-combined with the mobility problem for rigid body motions captures
-membrane mechanics including deformations, stretching modulus, and the
-permeability of a JP membrane. This work is highly applicable with
-fields in material science and condensed matter physics such as Janus
+This study presents a coarse-grained model for JP vesicles that focuses
+on the hydrophobic interactions between coarse-grained lipids and
+hydrodynamic interactions. In contrast to molecular dynamic simulations,
+the hydrophobic interactions exhibit the self-assembly property of the
+lipid bilayer membrane. The proposed energy potential combined with the
+mobility problem for rigid body motions captures membrane mechanics
+including deformations, stretching modulus, and permeability of a JP
+membrane. This work is highly applicable with fields in material science
+and condensed matter physics such as Janus
 colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
@@
 Integral equation methods are used to solve the mobility problem and the
-previously introduced HAP model that determines the forces and torques
-of the individual rigid bodies. In addition to the HAP forces and
-torques, we impose a short-range repulsion to avoid unphysical contact.
-Our method requires calculations of the hydrodynamic stress tensor, and
-this is leads to examinations of the membrane permeability constant $P$
-and the membrane stretching modulus $K_A$. With the use of suitable
-parameters, the numerical results yield good qualitative phenomena such
-as a tank-treading JP vesicle. The reduced area $A^*$ decreases as the
-shear rate increases and we measure the equilibrium reduced area for
-various shear rates. The results show that the total length of a JP
-vesicle is conserved and the decay rate of the reduced area is
-independent of the shear rate values  between $0.005$~ns$^{-1}$
-and~$0.008$ ns$^{-1}$. Moreover, the proposed model can describe
-membrane rupture in high shear rates. Therefore, our methods can be
-applied to vesicles undergoing topological changes which is not
-difficult to simulate when using a continuum model that represents
+previously introduced HAP model. We describe a method to calculate the
+hydrophobic forces and torques on each individual rigid body that avoids
+singular integrals. In addition to the HAP forces and torques, we use a
+short-range repulsion to avoid unphysical contact. Our method requires
+calculations of the hydrodynamic stress tensor, and these are used to
+estimate the membrane permeability constant $P$ and the membrane
+stretching modulus $K_A$. With the use of suitable parameters, the
+numerical results yield qualitative phenomena such as a tank-treading JP
+vesicle. The reduced area $A^*$ decreases as the shear rate increases
+and we measure the equilibrium reduced area for various shear rates. The
+results show that the total length of a JP vesicle is conserved and the
+decay rate of the reduced area is independent of the shear rate values
+between $0.005$~ns$^{-1}$ and~$0.008$~ns$^{-1}$. Moreover, the proposed
+model can describe membrane rupture in high shear rates. Therefore, our
+method can be applied to vesicles undergoing topological changes which
+is difficult to simulate when using a continuum model that represents
 vesicles as closed and continuous curves.
@@
 Our coarse-grained model is also able to calculate inter-monolayer
-friction. The inter-monolayer friction coefficients are determined by
+friction. The inter-monolayer friction coefficient is determined by
 calculating the tangential friction force and slip velocities with
-respect to the bilayer midplane. The resulting friction coefficients $b$
-are about one order of magnitude smaller than those reported
+respect to the bilayer midplane. The resulting friction coefficients are
+about an order of magnitude smaller than those reported
 by~\cite{denOtter2007}, and this discrepancy is partially due to the
-granularity of the model. In addition, the coarse-graining level of the
+granularity of our model. In addition, the coarse-graining level of the
 JP vesicle has a much larger length scale than molecular dynamics
@@
 We also study the spatial migration of a JP vesicle suspended in a
-parabolic flow. The chosen parameter values results in an asymmetric
-slipper shape. A qualitative agreement has been made comparing with the
+parabolic flow. The chosen parameter values result in an asymmetric
+slipper shape. While the initial reduced area of the JP vesicle is $A^*
+\approx 1$, the equilibrium reduced area is $A^*=0.9$. A qualitative
+agreement is made by comparing the JP vesicle shape with the
 two-dimensional inextensible membrane in continuum modeling
-simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). The
-initial reduced area of the JP vesicle is $A^* \approx 1$ and the
-equilibrium reduced area is $A^*=0.9$. An interesting result of the JP
-vesicle is that the mean $y$-position oscillates toward the center of
-the Poiseuille flow and this may be caused by the granularity of the JP
-vesicle and choices of the model parameters.
-
-We compare two JP vesicles with a similar setup using a continuum model.
-A comparison of the vesicle shapes and the streamlines demonstrate
-remarkable similarities. The two overlapping trajectories of the JP
-vesicles' centroids in a shear flow evolve as expected when the two
-centroids are initialized on the same horizontal level. We also observe
-a rotating behavior that is observed for models involving vesicle
-adhesion~(\cite{qua-vee-you2019}). The hydrophobic action and the
-repulsive potential lead to this adhesive effect when two JP bilayers
-are within a short distance. We also perform four simulations of two JP
-vesicles suspended in an extensional flow. We vary the initial vertical
-displacement of the vesicles' centroids and obtain similar results to
-the continuum model.
-
-\todo[inline]{Bryan left off here}
-Our future goal is to extend the current framework to a
-three-dimensional JP vesicle system. The further implementation of
-adding a fast algorithms such as the fast multipole method is also a
-practical approach. One ongoing work is to add thermal fluctuations onto
-Janus particles to obtain Brownian dynamics is crucial for obtaining
-membrane diffusion. Having a more physical boundary conditions on JP
-boundaries with experimental data is a reasonable direction and the
-future comparison with the laboratory experiments can be accomplished.
+simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). An
+interesting result of the JP vesicle is that $y$-coordinate of the
+centroid oscillates at a value slightly above the center of the
+Poiseuille flow. This may be caused by the granularity of the JP vesicle
+and choices of the model parameters.
+
+We compare setups of two JP vesicles and two vesicles described with a
+continuum model. A comparison of the vesicle shapes and the streamlines
+demonstrate remarkable similarities. The two overlapping trajectories of
+the JP vesicles' centroids in a shear flow evolve as expected when the
+two centroids are initialized on the same horizontal level. We also
+observe a rotating behavior that is observed for models involving
+vesicle adhesion~(\cite{qua-vee-you2019}). The hydrophobic action and
+the repulsive potential lead to this adhesive effect when two JP
+bilayers are sufficiently close. We also perform four simulations of two
+JP vesicles suspended in an extensional flow. We vary the initial
+vertical displacement of the vesicles' centroids and obtain similar
+results to the continuum model.
+
+Our future goals include extending the current framework to a
+three-dimensional JP vesicle system. This will require additional
+algorithmic implementation including a fast summation method such as the
+fast multipole method. Another research direction is to introduce
+thermal fluctuations into the model. This will result in Janus particles
+that include Brownian motion, and this is critical to understand
+membrane diffusion. Finally, a more physical boundary condition for the
+HAP model will allow us to draw comparisons between computational and
+laboratory experiments.
 

### 2021-09-13 doc/main_jfm.tex
modified main_jfm.tex for new figures

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\begin{center}
+\includegraphics[width=11.32cm]{Figure0_Wrapper.pdf}
+\end{center}
+\caption{The diagram illustrates the domain and boundary conditions for the mobility problem formulation.}
+\label{fig:figure0}
+\end{figure}
+
 \section{Governing Equations\label{sec:governing_eqs}}
@@
 \end{align*}
-Combing this with~\eqref{eq:prejump} gives~\eqref{eq:recipforcetorque}
+Combining this with~\eqref{eq:prejump} gives~\eqref{eq:recipforcetorque}
 as required.
@@
 \centering
-\includegraphics[height=2in]{relax2.eps}
-\includegraphics[height=2in]{relax.eps}\\
-\includegraphics[height=2.in]{N58_0pres.pdf}
-\includegraphics[height=2.in]{N58_5000pres.pdf}
+\includegraphics[width=11.32cm]{Figure1_Wrapper.pdf}
+%\includegraphics[height=2in]{relax2.eps}
+%\includegraphics[height=2in]{relax.eps}\\
+%\includegraphics[height=2.in]{N58_0pres.pdf}
+%\includegraphics[height=2.in]{N58_5000pres.pdf}
 %  \todo[inline]{Put pressure of each of the two configurations below
@@
 \centering
-  \todo[inline]{The left figure is shorter than the other 2}
-\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
-\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
-\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
+\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
+%\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
+%\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
+%\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
   \caption{\label{figure:permeability} JP vesicles are suspended in a
@@
 \centering
-\includegraphics[width=0.3\textwidth]{N58_0.pdf}
-\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
-\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
-\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
+\includegraphics[width=11.5cm]{Figure3_Wrapper.pdf}
+%\includegraphics[width=0.3\textwidth]{N58_0.pdf}
+%\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
+%\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
+%\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
   \caption{\label{figure3} A JP vesicle suspended in a shear flow with
@@
 \begin{center}
-\hspace{-0.6cm}
-\includegraphics[height=2in]{ReducedArea.pdf}
-\hspace{0.6cm}
-\includegraphics[height=2in]{DecayRate.eps}\\
-\includegraphics[height=2in]{ArcLength.pdf}
-\includegraphics[height=2in]{ExcLength.pdf}
+\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
+%\hspace{-0.6cm}
+%\includegraphics[height=2in]{ReducedArea.pdf}
+%\hspace{0.6cm}
+%\includegraphics[height=2in]{DecayRate.eps}\\
+%\includegraphics[height=2in]{ArcLength.pdf}
+%\includegraphics[height=2in]{ExcLength.pdf}
 \end{center} 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{slipper.eps}
+\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
+%\includegraphics[width=0.8\textwidth]{slipper.eps}
   \caption{\label{figure6} A JP vesicle suspended in a parabolic flow
@@
 \centering
-\includegraphics[height=2in]{parabolic.eps}
+%\includegraphics[height=2in]{parabolic.eps}
   \caption{\label{figure7} The schematic of a JP vesicle suspended in a
@@
 \centering
-\includegraphics[height=2in]{N58_rupt_0.pdf}
-\includegraphics[height=2in]{N58_rupt_200.pdf}
+\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
+%\includegraphics[height=2in]{N58_rupt_0.pdf}
+%\includegraphics[height=2in]{N58_rupt_200.pdf}
 \\
-\includegraphics[height=2in]{N58_rupt_400.pdf}
-\includegraphics[height=2in]{N58_rupt_600.pdf}
+%\includegraphics[height=2in]{N58_rupt_400.pdf}
+%\includegraphics[height=2in]{N58_rupt_600.pdf}
   \caption{\label{figure8} Membrane rupture occurs when the shear rate
@@
   \centering
-\includegraphics[height=2in]{N116_shear_0.pdf}
-\includegraphics[height=2in]{N116_shear_2500.pdf}\\
-\includegraphics[height=2in]{N116_shear_5000.pdf}
-\includegraphics[height=2in]{N116_shear_7500.pdf}
+\includegraphics[width=\textwidth]{Figure10_Wrapper.pdf}  
+%\includegraphics[height=2in]{N116_shear_0.pdf}
+%\includegraphics[height=2in]{N116_shear_2500.pdf}\\
+%\includegraphics[height=2in]{N116_shear_5000.pdf}
+%\includegraphics[height=2in]{N116_shear_7500.pdf}
   \caption{\label{figure10} Two JP vesicles suspended in a shear flow
@@
   \centering
-\includegraphics[height=2in]{N116_ext_0.pdf}
-\includegraphics[height=2in]{N116_ext_2000.pdf}\\
-\includegraphics[height=2in]{N116_ext_4000.pdf}
-\includegraphics[height=2in]{N116_ext_6500.pdf}
+  \includegraphics[width=\textwidth]{Figure12_Wrapper.pdf}
+%\includegraphics[height=2in]{N116_ext_0.pdf}
+%\includegraphics[height=2in]{N116_ext_2000.pdf}\\
+%\includegraphics[height=2in]{N116_ext_4000.pdf}
+%\includegraphics[height=2in]{N116_ext_6500.pdf}
   \caption{\label{figure12} Two JP vesicles suspended in an

### 2021-09-13 doc/main_jfm.tex
small fixes

@@
 We validated our solver for \eqref{eq:SKIE}-\eqref{eq:mobility2} using a
-single elliptical particle suspended in a background shear flow (see \S
-\ref{sec:ves_in_shear}). Hydrophobic attraction and repulsion are zero
-for a single particle. The angle of the ellipse's major axis coming from
-the integral equation method was in complete agreement with the
-theoretical, Jeffrey oribit time-course \cite{}.
+single elliptical particle suspended in a background shear flow (see
+\S~\ref{sec:ves_in_shear}). Hydrophobic attraction and repulsion are
+zero for a single particle. The angle of the ellipse's major axis coming
+from the integral equation method was in complete agreement with the
+theoretical, Jeffrey orbit time-course (\cite{jef1922}).
 
@@
 \end{align}
-where $P$ is a hydraulic permeability constant \cite{CHABANON,
-qua-gan-you2021}.
+where $P$ is a hydraulic permeability constant (\cite{chabanon2017,
+qua-gan-you2021}).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Intermonolayer Friction}
+\subsubsection{Inter-Monolayer Friction}
 The granulated JP vesicle allows us to consider inter-monolayer slip
@@
 simulations. (\cite{Zgorski2019,denOtter2007})
-\todo[inline]{Need a reference here}
 

### 2021-09-13 doc/main_jfm.tex
..and updated main_jfm.tex accordingly
update conclusion

@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{Slip.eps}
+\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
+%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
 \includegraphics[width=0.4\textwidth]{Slip2.eps}
@@
   corresponding time $t=2000$ and $t=9000$. The midplane curve is
-  denoted as $\Sigma_M$. We see that the intermonolayer slip is largest
+  denoted as $C_M$. We see that the intermonolayer slip is largest
   for large shear rates.}
@@
 is the time-averaged, tangential force along the midplane curve
-$\mathcal{C}_m$. The parameters $\langle L\rangle$ and $\langle
+$\mathcal{C}_M$. The parameters $\langle L\rangle$ and $\langle
 U\rangle$ are the time-averaged midplane curve length and intermonolayer
@@
 tangential force along curves a positive distance inside and outside
-$\mathcal{C}_m$ respectively, and then interpolating at zero distance to
+$\mathcal{C}_M$ respectively, and then interpolating at zero distance to
 give a force jump. We have made a slight abuse of language: due to the
@@
 surfactants~(\cite{Bradley2016}). 
+%
+For instances, with the flexibility of the model, we can manage a specific boundary condition
+of particle surfaces based on the chemicals chosen in experiments. This can be an assist to 
+study of interparticle interactions and chemical compositions in industry.
 
@@
 algorithmic implementation including a fast summation method such as the
-fast multipole method. Another research direction is to introduce
-thermal fluctuations into the model. This will result in Janus particles
-that include Brownian motion, and this is critical to understand
-membrane diffusion. Finally, a more physical boundary condition for the
+fast multipole method. Another research direction is to 
+%
+include the fluctuating hydrodynamics for Brownian suspensions~(\cite{Bao2018}),
+%introduce thermal fluctuations into the model. 
+%This will result in Janus particles that include Brownian motion, 
+and this is critical to understand membrane diffusion. 
+Finally, a more physical boundary condition for the
 HAP model will allow us to draw comparisons between computational and

### 2021-09-13 doc/main_jfm.tex
update conclusion

@@
 
+The single JP vesicle simulations end with obtaining JP bilayer stretching 
+modulus $K_A$ and hydraulic permeability constant $P$. We extract these 
+physical quantities from the Laplace pressure relationship that $R\Delta P$ is 
+proportional to JP bilayer stretch. We describe the aqueous flux in membrane 
+using a differential equation~\ref{eq:perm} and solve for the theoretical 
+permeability constant $P$. In spite of producing these values with some discrepancy
+using the default parameter set, we provide a new framework in measuring coarse-grained 
+membrane permeability.
+
 We compare setups of two JP vesicles and two vesicles described with a

### 2021-09-14 doc/main_jfm.tex
incorporated fig6(b)
rearrangements

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Model Parameters}
-To extract physical quantities of the target structure, we select
-particles that are disks with diameter $l_0 = 2.5$ nm representing the
-characteristic thickness of monolayers. The boundary
-conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
-\theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
-$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle center
-and director respectively. With this choice, the director points in the
-direction of the hydrophobic side of the JP. The other physical
-parameters are the decay length $\rho = 2 l_0$, the repulsion length
-$\rho_0 = 0.2l_0$, the repulsion strength is $M=4.0$~$k_BT$, the
-interfacial particle tension $\gamma = \text{4.1 pN nm}^{-1}$, and $\mu
-= \text{1 cP} = \text{1 pN ns nm}^{-2}$ is the viscosity of water at
-room temperature. \cite{Fu20} provides physical quantities for static JP
-bilayers.
-
-We consider the behavior of JP vesicles under various external flows.
-To do so, we nondimensionalize the problem through the change of
-variables 
-%\begin{equation}
-%\label{eq:nondimensionalize}
-$t \mapsto t \text{ ns},$ % \quad
-$\xx \mapsto \xx \text{ nm}$, %\quad 
-$\uu \mapsto \uu \text{ nm ns}^{-1}$, and %\quad 
-$p \mapsto p \text{ pN nm}^{-2}$.
-%\end{equation}
-For the remainder of the manuscript, the time axes are in ns, and the
-pressure $p$ and stresses $\sigma$ and $\mathbf{T}^{\mathrm{hydro}}$ are
-in pN nm$^{-2}$. Finally, the dimensionless shear rate is $\chi =
-\dot\gamma \tau$ for the dimensional shear rate $\dot\gamma$ in
-ns$^{-1}$ and the characteristic time is $\tau = 1$~ns. The time step
-size $\Delta t=0.2$ is used for all simulations in this work including
-the relaxation run.
-
-\subsection{Self-Assembly and Relaxation}
-\begin{figure}
-\centering
-\includegraphics[width=11.32cm]{Figure1_Wrapper.pdf}
-%\includegraphics[height=2in]{relax2.eps}
-%\includegraphics[height=2in]{relax.eps}\\
-%\includegraphics[height=2.in]{N58_0pres.pdf}
-%\includegraphics[height=2.in]{N58_5000pres.pdf}
-%  \todo[inline]{Put pressure of each of the two configurations below
-%  this.}
-\caption{\label{figure2} A JP Vesicle relaxing under a quiescent flow.
-  (a) The blue dashed and solid curves are mean magnitudes of the
-  particle velocities in $x$ and $y$ directions, respectively. The red
-  curve shows the decreasing trend of the mean magnitude of particle
-  orientation change. The black dashed line shows the reference of how
-  all magnitudes decay. (b) Bilayer configurations for $t=0$ (black) and
-  $t=1000$ (red) with particle directors. (c)--(d) show the fluid
-  pressure profiles for $t=0$ and $t=1000$ where the background curves
-  indicate the streamlines. In panel (c), the pressure value in internal
-  fluid is much higher than the pressure outside of the bilayer. After
-  the JP vesicle relaxes, this immersed permeable bilayer approaches the
-  steady state shown in panel (d).}
-\end{figure}
-
-In order to examine the hydrodynamics interactions of JP vesicles, it is
-necessary to have a suitable, initial, JP equilibrium vesicle. This
-ensures that the dynamics of the bilayer under a shear flow, for
-example, reach consistent outcomes. For our target vesicle, we start
-with $N=58$ JP arranged in two circular, apposing monolayers of about
-$8$ length units. The directors of the outer monolayer point inward and
-the directors of the inner monolayer point outward
-(Figure~\ref{figure2}a).  The JP of this chosen configuration are
-generally not in equilibrium.  Rather, the inter-particle distances and
-orientations must make slight adjustments so that attraction and
-repulsion balance.  Figure~\ref{figure2}(b) shows that the magnitudes of
-the mean velocity components ${\bf v}=\{v_x,v_y\}$ and the variation
-$\Delta \theta$ of the particle orientation decrease exponentially with
-an approximation decaying rate $\sim0.005$. A local energy minimum and
-the equilibrium configuration is therefore rapidly attained. The
-equilibrium configuration in Figure~\ref{figure2}a is slightly
-elliptical. The equilibrium eccentricity vanishes for larger $N_b$
-(Figure~\ref{figure2}e).
-
-\subsection{Permeability}
-Figures~\ref{figure2}c and~\ref{figure2}d demonstrate that the initial, non-equilibrium configuration has a large internal fluid pressure
-that vanishes as the configuration tends toward the equilibrium state.  
-This suggests that the initial collection of JP is under tension and
-this tension is relaxed as fluid is expelled through the inter-particle
-spacing. To make a comparison with membrane continuum mechanics, lipid
-bilayer membranes have a large area modulus $K_A$ of about $240$ pN
-nm$^{-1}$ \cite{NAGLE} and changes in surface area give rise to a
-membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
-membrane surface area and $A_0$ is the reference surface area in the
-non-tensed state. In the two-dimensional vesicles, the tension becomes
-\begin{align}
-\label{eq:stretch}
-\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
-\end{align}
-where $L$ and $L_0$ are the vesicle arc length and resting length,
-respectively. A stretched, circular vesicles has a Laplace pressure 
-\begin{align}
-\label{eq:LaplacePressure}
-\Delta p = \frac{\tilde \gamma}{R},
-\end{align}
-where $\Delta p$ is the difference in internal pressure to the pressure
-at infinity and $R$ is the radius of the circular vesicle. The factor
-$R^{-1}$ is the total curvature since the principle curvature in the
-direction of the cylinder is zero.
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
-%\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
-%\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
-%\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
-  \caption{\label{figure:permeability} JP vesicles are suspended in a
-  quiescent flow for relaxations where the reference arc lengths $L_0$
-  are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm,
-  $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$
-  decreases over time where the dashed curves represent the data and
-  solid curves are linear fits; (b) A linear relationship between
-  $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear
-  relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels
-  (b) and (c), the cross and asterisk symbols are numerical results and
-  fitted by using solid lines.}
-\end{figure}
-
-The particles in our setup do not abut but rather have small gaps due to
-repulsive forces. The gaps allow for some fluid flux across the JP
-bilayer. In membrane mechanics, aqueous flux is quantified the equation
-\begin{align}
-  \label{eq:perm} 
-  \frac{dA}{dt} = -P  L \Delta p,
-\end{align}
-where $P$ is a hydraulic permeability constant (\cite{chabanon2017,
-qua-gan-you2021}).
-
-The JP vesicle data is in complete agreement with the continuum
-mechanical model~\eqref{eq:stretch}--\eqref{eq:perm}. In
-Figure~\ref{figure:permeability}, we considered three configurations: a
-configuration with 58 particles ($L_0 = 107$ nm, plus symbols); a
-configuration with 119 particles ($L_0 = 218$ nm, asterisk symbols); and
-finally a configuration with 117 particles but with diameter 1.25 nm
-rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols). Here $A$
-and $L$ refer to the area and length of the mid plane curve separating
-the inner and outer monolayers. The values for $L_0$ are the asymptotic
-values for $L$ in Figure~\ref{figure:permeability}c.
-
-Figure~\ref{figure:permeability}a plots the data for the Laplace
-pressure relationship \eqref{eq:LaplacePressure}. The pressure jump
-$\Delta p$ is the pressure at the particle center minus the far-field
-pressure (see Figures~\ref{figure2}c and~\ref{figure2}d), $R = L/2\pi$
-is the vesicle radius, and the horizontal axis is the relative stretch.
-The solid lines are linear fits, showing that for circular JP vesicles,
-$R\Delta P$ is essentially proportional to the relative stretching
-$L/L_0 - 1$. The proportionality constant is the same for the 58 and 119
-particle cases where the diameters are the same, suggesting that the
-stretching modulus $K_A$ of JP bilayers is independent of the number of
-particles. The 117 particle case had diameters 1.25 nm and this data set
-results in a smaller stretching modulus of $K_A = 102$~pN~nm$^{-1}$. The
-interpretation is that changes to particle size, while keeping $\rho$,
-$M$, and $\rho_0$ fixed, lead to different physical properties.
-
-Furthermore, Figure~\ref{figure:permeability}b and shows that $L\Delta
-P$ is proportional to $\frac{dA}{dt}$ in accord with \eqref{eq:perm}.
-The slopes of the linear fits give the hydraulic permeability
-coefficient $P$. The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$
-pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 58 and 119
-particle cases, respectively. These values suggest that the JP bilayer
-permeability is independent of particle number, as was the case for the
-stretching modulus. The permeability for the 117 particle number is
-0.0566 nm$^3$~ns$^{-1}$~pN$^{-1}$. The increase in the permeability is
-caused by the hydrophobic attraction vanishing with particle size,
-leading to larger gaps between the particles for the same repulsion. The
-hydraulic permeability we calculate, however, is not in agreement with
-experimentally derived values and is larger by a few orders of
-magnitude. This discrepancy is perhaps due to inter-particle distance of
-the JP being relatively large to the inter-molecular spacing of lipids
-in real bilayers. In future studies, we can test this hypothesis be
-changing the repulsion strength and length for example.
-
-Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
-combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
-and~\eqref{eq:perm}, to derive
-\begin{align}
-\label{eq:perm_solution}
-L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
-\end{align}
-The theoretical time courses for \eqref{eq:perm_solution} are in good
-quantitative agreement with the JP data for
-(Figure~\ref{figure:permeability}c).
-
-%\subsection{Jeffery Orbit}
-%We use Jeffery orbits to numerically validate our solver for the mobility-problem.  
-%The background flow is a shear flow $\uu_{\infty}(\xx) = \dot\gamma  \xx \cdot \mathbf{e}_2 \mathbf{e}_1$ with shear rate $\dot\gamma$
-%and orthogonal unit vectors $\mathbf{e}_1$ and $\mathbf{e}_2$. 
-%A single elliptical particle is suspended in the fluid with center at the origin.
-%The Jeffrey orbit  
-%\begin{equation}
-%\label{eq:jeff}
-%\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right)
-%\end{equation}
-%gives the angle between the major axis and $\mathbf{e}_2$
-%where $a$, $b$ are the semi-major and semi-minor axes. 
-%We are assuming $\Theta(0) = 0$.
-%Figure~\ref{figure1} shows that the angles coming from the integral equation method \eqref{eq:SKIE}-\eqref{eq:mobility2}
-%are in complete agreement with the theoretical time course \eqref{eq:jeff}.  Hydrophobic attraction and repulsion are zero for a single particle. 
-%
-%
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
-%\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
-%  \caption{The figure compares the theoretical Jeffery orbit for $\Theta(t)$ and the result from the integral equation method. 
-%    The insets show the simulation setup. The shear rate is $\dot\gamma=0.1$.}
-%    \label{figure1}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\todo[inline]{Introduce dimensionless shear rate here (and check the numbers)}
-
-%For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$
-
-%referred from~\cite{Finken08} and~\cite{Shaqfeh11},
-%\begin{align}
-%  \chi = \dot\gamma \frac{\mu R_0^3}{\kappa},
-%\end{align}
-%%
-%where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Tank-Treading Vesicles}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Vesicle in a Shear Flow}
-\label{sec:ves_in_shear}
-Our hydrodynamic simulation studies begin by studying the dynamics of a single JP vesicle suspended in
-the shear flow
-\begin{align}
-  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
-\end{align}
-with shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
-and $\mathbf{e}_y$ for the horizontal and vertical directions,
-respectively. It is well known that a vesicle has tank-treading behavior
-when there is no viscosity contrast between the fluids inside and
-outside of the vesicle.
-%Within the framework of the simulation setup,
-%the proposed model provides a feature that the fluid viscosity is
-%constant over the computational domain and it is capable of performing
-%these simulations.
-
-The centroid of the pre-relaxed $58$-body Janus vesicle is initially
-placed at the origin and the shear flow with a shear rate $\chi$ is
-applied. Figure~\ref{figure3} shows snapshots of the JP vesicle in the
-shear flow with a shear rate $\chi=0.0025$. Panels (a) and (b) show the
-initial shape obtained from the relaxation run and the deformed
-configurations of the JP vesicle at time $t=4000$ are in panels (c) and
-(d). The background color in panels (a) and (c) is the strength of the
-action of the hydrophobic attraction. Red corresponds to a strong action
-while blue is a weak action. The hydrophobic layer clearly has the
-strongest action. To demonstrate the tank-treading behavior of the
-vesicle, panels (b) and (d) provide the streamlines of the fluid
-velocity around the JP vesicle. In panel (d), we can clearly observe the
-clockwise tank-treading motion.
-
 \begin{figure}
@@
 \end{figure}
+
+\subsection{Model Parameters}
+To extract physical quantities of the target structure, we select
+particles that are disks with diameter $l_0 = 2.5$ nm representing the
+characteristic thickness of monolayers. The boundary
+conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
+\theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
+$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle center
+and director respectively. With this choice, the director points in the
+direction of the hydrophobic side of the JP. The other physical
+parameters are the decay length $\rho = 2 l_0$, the repulsion length
+$\rho_0 = 0.2l_0$, the repulsion strength is $M=4.0$~$k_BT$, the
+interfacial particle tension $\gamma = \text{4.1 pN nm}^{-1}$, and $\mu
+= \text{1 cP} = \text{1 pN ns nm}^{-2}$ is the viscosity of water at
+room temperature. \cite{Fu20} provides physical quantities for static JP
+bilayers.
+
+We consider the behavior of JP vesicles under various external flows.
+To do so, we nondimensionalize the problem through the change of
+variables 
+%\begin{equation}
+%\label{eq:nondimensionalize}
+$t \mapsto t \text{ ns},$ % \quad
+$\xx \mapsto \xx \text{ nm}$, %\quad 
+$\uu \mapsto \uu \text{ nm ns}^{-1}$, and %\quad 
+$p \mapsto p \text{ pN nm}^{-2}$.
+%\end{equation}
+For the remainder of the manuscript, the time axes are in ns, and the
+pressure $p$ and stresses $\sigma$ and $\mathbf{T}^{\mathrm{hydro}}$ are
+in pN nm$^{-2}$. Finally, the dimensionless shear rate is $\chi =
+\dot\gamma \tau$ for the dimensional shear rate $\dot\gamma$ in
+ns$^{-1}$ and the characteristic time is $\tau = 1$~ns. The time step
+size $\Delta t=0.2$ is used for all simulations in this work including
+the relaxation run.
+
+%\subsection{Jeffery Orbit}
+%We use Jeffery orbits to numerically validate our solver for the mobility-problem.  
+%The background flow is a shear flow $\uu_{\infty}(\xx) = \dot\gamma  \xx \cdot \mathbf{e}_2 \mathbf{e}_1$ with shear rate $\dot\gamma$
+%and orthogonal unit vectors $\mathbf{e}_1$ and $\mathbf{e}_2$. 
+%A single elliptical particle is suspended in the fluid with center at the origin.
+%The Jeffrey orbit  
+%\begin{equation}
+%\label{eq:jeff}
+%\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right)
+%\end{equation}
+%gives the angle between the major axis and $\mathbf{e}_2$
+%where $a$, $b$ are the semi-major and semi-minor axes. 
+%We are assuming $\Theta(0) = 0$.
+%Figure~\ref{figure1} shows that the angles coming from the integral equation method \eqref{eq:SKIE}-\eqref{eq:mobility2}
+%are in complete agreement with the theoretical time course \eqref{eq:jeff}.  Hydrophobic attraction and repulsion are zero for a single particle. 
+%
+%
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
+%\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
+%  \caption{The figure compares the theoretical Jeffery orbit for $\Theta(t)$ and the result from the integral equation method. 
+%    The insets show the simulation setup. The shear rate is $\dot\gamma=0.1$.}
+%    \label{figure1}
+%\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\todo[inline]{Introduce dimensionless shear rate here (and check the numbers)}
+
+%For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$
+
+%referred from~\cite{Finken08} and~\cite{Shaqfeh11},
+%\begin{align}
+%  \chi = \dot\gamma \frac{\mu R_0^3}{\kappa},
+%\end{align}
+%%
+%where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Tank-Treading Vesicles}
+\begin{figure}
+\begin{center}
+\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
+%\hspace{-0.6cm}
+%\includegraphics[height=2in]{ReducedArea.pdf}
+%\hspace{0.6cm}
+%\includegraphics[height=2in]{DecayRate.eps}\\
+%\includegraphics[height=2in]{ArcLength.pdf}
+%\includegraphics[height=2in]{ExcLength.pdf}
+\end{center} 
+  \caption{\label{figure4} (a) The reduced area transitioning over time
+  for four different shear rates. The smooth curves are a best-fit
+  exponential curve. (b) The decay rate $k$, using the exponential fit
+  to the data in panel (a), for a number of shear rates. The inset shows
+  the terminal reduced areas. (c) The total arc lengths of the midplanes
+  over time for four shear rates. (d) The excess length of the
+  midplanes. For all panels, a set of shear rates
+  $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. The
+  legend in panel (d) applies to both panels (a) and (c).}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Vesicle in a Shear Flow}
+\label{sec:ves_in_shear}
+Our hydrodynamic simulation studies begin by studying the dynamics of a single JP vesicle suspended in
+the shear flow
+\begin{align}
+  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
+\end{align}
+with shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
+and $\mathbf{e}_y$ for the horizontal and vertical directions,
+respectively. It is well known that a vesicle has tank-treading behavior
+when there is no viscosity contrast between the fluids inside and
+outside of the vesicle.
+%Within the framework of the simulation setup,
+%the proposed model provides a feature that the fluid viscosity is
+%constant over the computational domain and it is capable of performing
+%these simulations.
+
+The centroid of the pre-relaxed $58$-body Janus vesicle is initially
+placed at the origin and the shear flow with a shear rate $\chi$ is
+applied. Figure~\ref{figure3} shows snapshots of the JP vesicle in the
+shear flow with a shear rate $\chi=0.0025$. Panels (a) and (b) show the
+initial shape obtained from the relaxation run and the deformed
+configurations of the JP vesicle at time $t=4000$ are in panels (c) and
+(d). The background color in panels (a) and (c) is the strength of the
+action of the hydrophobic attraction. Red corresponds to a strong action
+while blue is a weak action. The hydrophobic layer clearly has the
+strongest action. To demonstrate the tank-treading behavior of the
+vesicle, panels (b) and (d) provide the streamlines of the fluid
+velocity around the JP vesicle. In panel (d), we can clearly observe the
+clockwise tank-treading motion.
+
 %
@@
 \begin{center}
-\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
-%\hspace{-0.6cm}
-%\includegraphics[height=2in]{ReducedArea.pdf}
-%\hspace{0.6cm}
-%\includegraphics[height=2in]{DecayRate.eps}\\
-%\includegraphics[height=2in]{ArcLength.pdf}
-%\includegraphics[height=2in]{ExcLength.pdf}
+\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
+\includegraphics[width=11cm]{Figure5B_Wrapper.pdf}
+%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
+%\includegraphics[width=0.4\textwidth]{Slip2.eps}
 \end{center} 
-  \caption{\label{figure4} (a) The reduced area transitioning over time
-  for four different shear rates. The smooth curves are a best-fit
-  exponential curve. (b) The decay rate $k$, using the exponential fit
-  to the data in panel (a), for a number of shear rates. The inset shows
-  the terminal reduced areas. (c) The total arc lengths of the midplanes
-  over time for four shear rates. (d) The excess length of the
-  midplanes. For all panels, a set of shear rates
-  $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. The
-  legend in panel (d) applies to both panels (a) and (c).}
+  \caption{\label{figure5} The schematic of the inter-monolayer slip over
+  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
+  mean angle between each particle pair $\theta(t)$ where the angle is
+  calculated from the relative position of the particles with respect to
+  the JP vesicle's center of mass. The configuration plots have two
+  fixed particles marked in yellow and blue and labeled with the
+  corresponding time $t=2000$ and $t=9000$. The midplane curve is
+  denoted as $C_M$. We see that the inter-monolayer slip is largest
+  for large shear rates.}
 \end{figure}
@@
 \subsubsection{Inter-Monolayer Friction}
+
 The granulated JP vesicle allows us to consider inter-monolayer slip
@@
 simulations. (\cite{Zgorski2019,denOtter2007})
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
-%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
-\includegraphics[width=0.4\textwidth]{Slip2.eps}
-\end{center} 
-  \caption{\label{figure5} The schematic of the intermonolayer slip over
-  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
-  mean angle between each particle pair $\theta(t)$ where the angle is
-  calculated from the relative position of the particles with respect to
-  the JP vesicle's center of mass. The configuration plots have two
-  fixed particles marked in yellow and blue and labeled with the
-  corresponding time $t=2000$ and $t=9000$. The midplane curve is
-  denoted as $C_M$. We see that the intermonolayer slip is largest
-  for large shear rates.}
-\end{figure}
 
@@
 \end{table}
+
+\subsubsection{Membrane Ruptures}
+\begin{figure}
+\centering
+\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
+%\includegraphics[height=2in]{N58_rupt_0.pdf}
+%\includegraphics[height=2in]{N58_rupt_200.pdf}
+\\
+%\includegraphics[height=2in]{N58_rupt_400.pdf}
+%\includegraphics[height=2in]{N58_rupt_600.pdf}
+  \caption{\label{figure8} Membrane rupture occurs when the shear rate
+  exceeds a threshold. Here the shear rate is $\chi = 0.1$. Starting
+  with a circular shape (panel (a)), the vesicle is stretched by the
+  background flow and multiple pores form (panel (b)). Panels (c)--(d)
+  show the later states during the simulation. Streamlines are included
+  in each panel.}
+\end{figure}
+A pore formation or a complete membrane rupture can occur at large shear
+rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture when
+suspended in a shear flow with shear rate $\chi=0.1$. The streamlines
+are included in these plots. An interesting phenomenon occurs in panels
+(c) and (d) where two separated bilayers move along the background shear
+flow symmetrically. Consequently, a periodic motion for bilayers may
+occur at certain shear rates. One can expect that these two layers will
+diverge from one another for much higher shear rates.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Membrane Ruptures}
-
-A pore formation or a complete membrane rupture can occur at large shear
-rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture when
-suspended in a shear flow with shear rate $\chi=0.1$. The streamlines
-are included in these plots. An interesting phenomenon occurs in panels
-(c) and (d) where two separated bilayers move along the background shear
-flow symmetrically. Consequently, a periodic motion for bilayers may
-occur at certain shear rates. One can expect that these two layers will
-diverge from one another for much higher shear rates.
-
+
+\subsection{Self-Assembly and Relaxation}
+
+In order to examine the hydrodynamics interactions of JP vesicles, it is
+necessary to have a suitable, initial, JP equilibrium vesicle. This
+ensures that the dynamics of the bilayer under a shear flow, for
+example, reach consistent outcomes. For our target vesicle, we start
+with $N=58$ JP arranged in two circular, apposing monolayers of about
+$8$ length units. The directors of the outer monolayer point inward and
+the directors of the inner monolayer point outward
+(Figure~\ref{figure2}a).  The JP of this chosen configuration are
+generally not in equilibrium.  Rather, the inter-particle distances and
+orientations must make slight adjustments so that attraction and
+repulsion balance.  Figure~\ref{figure2}(b) shows that the magnitudes of
+the mean velocity components ${\bf v}=\{v_x,v_y\}$ and the variation
+$\Delta \theta$ of the particle orientation decrease exponentially with
+an approximation decaying rate $\sim0.005$. A local energy minimum and
+the equilibrium configuration is therefore rapidly attained. The
+equilibrium configuration in Figure~\ref{figure2}a is slightly
+elliptical. The equilibrium eccentricity vanishes for larger $N_b$
+(Figure~\ref{figure2}e).
+
+\subsection{Stretching and Permeability}
 \begin{figure}
 \centering
-\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
-%\includegraphics[height=2in]{N58_rupt_0.pdf}
-%\includegraphics[height=2in]{N58_rupt_200.pdf}
-\\
-%\includegraphics[height=2in]{N58_rupt_400.pdf}
-%\includegraphics[height=2in]{N58_rupt_600.pdf}
-  \caption{\label{figure8} Membrane rupture occurs when the shear rate
-  exceeds a threshold. Here the shear rate is $\chi = 0.1$. Starting
-  with a circular shape (panel (a)), the vesicle is stretched by the
-  background flow and multiple pores form (panel (b)). Panels (c)--(d)
-  show the later states during the simulation. Streamlines are included
-  in each panel.}
+\includegraphics[width=11.32cm]{Figure1_Wrapper.pdf}
+%\includegraphics[height=2in]{relax2.eps}
+%\includegraphics[height=2in]{relax.eps}\\
+%\includegraphics[height=2.in]{N58_0pres.pdf}
+%\includegraphics[height=2.in]{N58_5000pres.pdf}
+%  \todo[inline]{Put pressure of each of the two configurations below
+%  this.}
+\caption{\label{figure2} A JP Vesicle relaxing under a quiescent flow.
+  (a) The blue dashed and solid curves are mean magnitudes of the
+  particle velocities in $x$ and $y$ directions, respectively. The red
+  curve shows the decreasing trend of the mean magnitude of particle
+  orientation change. The black dashed line shows the reference of how
+  all magnitudes decay. (b) Bilayer configurations for $t=0$ (black) and
+  $t=1000$ (red) with particle directors. (c)--(d) show the fluid
+  pressure profiles for $t=0$ and $t=1000$ where the background curves
+  indicate the streamlines. In panel (c), the pressure value in internal
+  fluid is much higher than the pressure outside of the bilayer. After
+  the JP vesicle relaxes, this immersed permeable bilayer approaches the
+  steady state shown in panel (d).}
 \end{figure}
+Figures~\ref{figure2}c and~\ref{figure2}d demonstrate that the initial, non-equilibrium configuration has a large internal fluid pressure
+that vanishes as the configuration tends toward the equilibrium state.  
+This suggests that the initial collection of JP is under tension and
+this tension is relaxed as fluid is expelled through the inter-particle
+spacing. To make a comparison with membrane continuum mechanics, lipid
+bilayer membranes have a large area modulus $K_A$ of about $240$ pN
+nm$^{-1}$ \cite{NAGLE} and changes in surface area give rise to a
+membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
+membrane surface area and $A_0$ is the reference surface area in the
+non-tensed state. In the two-dimensional vesicles, the tension becomes
+\begin{align}
+\label{eq:stretch}
+\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
+\end{align}
+where $L$ and $L_0$ are the vesicle arc length and resting length,
+respectively. A stretched, circular vesicles has a Laplace pressure 
+\begin{align}
+\label{eq:LaplacePressure}
+\Delta p = \frac{\tilde \gamma}{R},
+\end{align}
+where $\Delta p$ is the difference in internal pressure to the pressure
+at infinity and $R$ is the radius of the circular vesicle. The factor
+$R^{-1}$ is the total curvature since the principle curvature in the
+direction of the cylinder is zero.
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
+%\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
+%\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
+%\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
+  \caption{\label{figure:permeability} JP vesicles are suspended in a
+  quiescent flow for relaxations where the reference arc lengths $L_0$
+  are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm,
+  $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$
+  decreases over time where the dashed curves represent the data and
+  solid curves are linear fits; (b) A linear relationship between
+  $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear
+  relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels
+  (b) and (c), the cross and asterisk symbols are numerical results and
+  fitted by using solid lines.}
+\end{figure}
+
+The particles in our setup do not abut but rather have small gaps due to
+repulsive forces. The gaps allow for some fluid flux across the JP
+bilayer. In membrane mechanics, aqueous flux is quantified the equation
+\begin{align}
+  \label{eq:perm} 
+  \frac{dA}{dt} = -P  L \Delta p,
+\end{align}
+where $P$ is a hydraulic permeability constant (\cite{chabanon2017,
+qua-gan-you2021}).
+
+The JP vesicle data is in complete agreement with the continuum
+mechanical model~\eqref{eq:stretch}--\eqref{eq:perm}. In
+Figure~\ref{figure:permeability}, we considered three configurations: a
+configuration with 58 particles ($L_0 = 107$ nm, plus symbols); a
+configuration with 119 particles ($L_0 = 218$ nm, asterisk symbols); and
+finally a configuration with 117 particles but with diameter 1.25 nm
+rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols). Here $A$
+and $L$ refer to the area and length of the mid plane curve separating
+the inner and outer monolayers. The values for $L_0$ are the asymptotic
+values for $L$ in Figure~\ref{figure:permeability}c.
+
+Figure~\ref{figure:permeability}a plots the data for the Laplace
+pressure relationship \eqref{eq:LaplacePressure}. The pressure jump
+$\Delta p$ is the pressure at the particle center minus the far-field
+pressure (see Figures~\ref{figure2}c and~\ref{figure2}d), $R = L/2\pi$
+is the vesicle radius, and the horizontal axis is the relative stretch.
+The solid lines are linear fits, showing that for circular JP vesicles,
+$R\Delta P$ is essentially proportional to the relative stretching
+$L/L_0 - 1$. The proportionality constant is the same for the 58 and 119
+particle cases where the diameters are the same, suggesting that the
+stretching modulus $K_A$ of JP bilayers is independent of the number of
+particles. The 117 particle case had diameters 1.25 nm and this data set
+results in a smaller stretching modulus of $K_A = 102$~pN~nm$^{-1}$. The
+interpretation is that changes to particle size, while keeping $\rho$,
+$M$, and $\rho_0$ fixed, lead to different physical properties.
+
+Furthermore, Figure~\ref{figure:permeability}b and shows that $L\Delta
+P$ is proportional to $\frac{dA}{dt}$ in accord with \eqref{eq:perm}.
+The slopes of the linear fits give the hydraulic permeability
+coefficient $P$. The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$
+pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 58 and 119
+particle cases, respectively. These values suggest that the JP bilayer
+permeability is independent of particle number, as was the case for the
+stretching modulus. The permeability for the 117 particle number is
+0.0566 nm$^3$~ns$^{-1}$~pN$^{-1}$. The increase in the permeability is
+caused by the hydrophobic attraction vanishing with particle size,
+leading to larger gaps between the particles for the same repulsion. The
+hydraulic permeability we calculate, however, is not in agreement with
+experimentally derived values and is larger by a few orders of
+magnitude. This discrepancy is perhaps due to inter-particle distance of
+the JP being relatively large to the inter-molecular spacing of lipids
+in real bilayers. In future studies, we can test this hypothesis be
+changing the repulsion strength and length for example.
+
+Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
+combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
+and~\eqref{eq:perm}, to derive
+\begin{align}
+\label{eq:perm_solution}
+L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
+\end{align}
+The theoretical time courses for \eqref{eq:perm_solution} are in good
+quantitative agreement with the JP data for
+(Figure~\ref{figure:permeability}c).
 
@@
 \begin{center}
-  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
+\includegraphics[width=\textwidth]{Figure9_Wrapper.pdf}
+%  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
 \end{center} 
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
+\includegraphics[width=0.97\textwidth]{Figure11_Wrapper.pdf}
+%\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
 \end{center} 

### 2021-09-15 doc/main_jfm.tex

@@
 
-This study presents a coarse-grained model for JP vesicles that focuses
-on the hydrophobic interactions between coarse-grained lipids and
-hydrodynamic interactions. In contrast to molecular dynamic simulations,
-the hydrophobic interactions exhibit the self-assembly property of the
-lipid bilayer membrane. The proposed energy potential combined with the
-mobility problem for rigid body motions captures membrane mechanics
-including deformations, stretching modulus, and permeability of a JP
-membrane. This work is highly applicable with fields in material science
-and condensed matter physics such as Janus
-colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
-match experimental results such as the morphology of colloid
+In \cite{Fu20} a mathematical model is developed to quantify the macroscopic assembly and mechanics of 
+a JP bilayer in a viscous solvent.
+The interactions between JPs are formulated as a second-kind integral equation, which is coupled to the incompressible Stokes equations for the surrounding incompressible fluid at the zero-Reynolds-number limit.
+Numerical simulations of a JP suspension reveal self-assembly of JPs into micelles and bilayers, and also provide an alternative means for computing the mechanical moduli of a JP membrane, which often requires the knowledge of an equation of state from experiments on a colloidal membrane~(\cite{Balchunas2019_SM}).
+In this study we used this integral formulation and numerical algorithm to simulate the hydrodynamics of JP vesicles. 
+%
+%This study presents a coarse-grained model for JP vesicles that focuses
+%on the hydrophobic interactions between coarse-grained lipids and
+%hydrodynamic interactions. In contrast to molecular dynamic simulations,
+%the hydrophobic interactions exhibit the self-assembly property of the
+%lipid bilayer membrane. The proposed energy potential combined with the
+%mobility problem for rigid body motions captures membrane mechanics
+%including deformations, stretching modulus, and permeability of a JP
+%membrane. 
+%
+Results in this work show great potential to study Janus colloids~(\cite{Bradley2017,Mallory2017}) and the morphology of colloid
 surfactants~(\cite{Bradley2016}). 
 %
-For instances, with the flexibility of the model, we can manage a specific boundary condition
-of particle surfaces based on the chemicals chosen in experiments. This can be an assist to 
-study of interparticle interactions and chemical compositions in industry.
-
-Integral equation methods are used to solve the mobility problem and the
-previously introduced HAP model. We describe a method to calculate the
-hydrophobic forces and torques on each individual rigid body that avoids
-singular integrals. In addition to the HAP forces and torques, we use a
-short-range repulsion to avoid unphysical contact. Our method requires
-calculations of the hydrodynamic stress tensor, and these are used to
-estimate the membrane permeability constant $P$ and the membrane
-stretching modulus $K_A$. With the use of suitable parameters, the
-numerical results yield qualitative phenomena such as a tank-treading JP
-vesicle. The reduced area $A^*$ decreases as the shear rate increases
+%This work is highly applicable with fields in material science
+%and condensed matter physics such as Janus
+%colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
+%match experimental results such as the morphology of colloid
+%surfactants~(\cite{Bradley2016}). 
+%%
+For example, with the flexibility of the model, we can specify the boundary condition on JP surfaces based on the chemicals used in experiments. 
+%This can be an assist to study of interparticle interactions and chemical compositions in industry.
+
+%Integral equation methods are used to solve the mobility problem and the
+%previously introduced HAP model. We describe a method to calculate the
+%hydrophobic forces and torques on each individual rigid body that avoids
+%singular integrals. In addition to the HAP forces and torques, we use a
+%short-range repulsion to avoid unphysical contact.
+
+In\S~\ref{subsec:calculating_force} we derived an alternative integral form for calculating the force and torque to avoid the singular integral evaluation. These alternative integrals allow us to 
+%
+%Our method requires
+%calculations of the hydrodynamic stress tensor, and these are used to
+%
+estimate the inter-monolayer friction, membrane permeability constant $P$ and the membrane
+stretching modulus $K_A$. 
+The inter-monolayer friction coefficient is determined by
+calculating the tangential friction force and slip velocities with
+respect to the bilayer mid-plane. The resulting friction coefficients are
+about an order of magnitude smaller than those reported
+by~\cite{denOtter2007}, and this discrepancy is partially due to the
+granularity of our model. In addition, the coarse-graining level of the
+JP vesicle has a much larger length scale than molecular dynamics
+simulations, and the repulsive force creates gaps between Janus
+particles where the error in slip velocities accumulates over time.
+
+Under a linear shear flow, we found a JP vesicle to exhibit elongation and tank-treading dynamics observed for a lipid bilayer GUV.
+%
+%With the use of suitable parameters, the
+%numerical results yield qualitative phenomena such as a tank-treading JP
+%vesicle. 
+%
+The reduced area $A^*$ decreases as the shear rate increases
 and we measure the equilibrium reduced area for various shear rates. The
@@
 vesicles as closed and continuous curves.
-
-Our coarse-grained model is also able to calculate inter-monolayer
-friction. The inter-monolayer friction coefficient is determined by
-calculating the tangential friction force and slip velocities with
-respect to the bilayer midplane. The resulting friction coefficients are
-about an order of magnitude smaller than those reported
-by~\cite{denOtter2007}, and this discrepancy is partially due to the
-granularity of our model. In addition, the coarse-graining level of the
-JP vesicle has a much larger length scale than molecular dynamics
-simulations, and the repulsive force creates gaps between Janus
-particles where the error in slip velocities accumulates over time.
-
-We also study the spatial migration of a JP vesicle suspended in a
-parabolic flow. The chosen parameter values result in an asymmetric
-slipper shape. While the initial reduced area of the JP vesicle is $A^*
-\approx 1$, the equilibrium reduced area is $A^*=0.9$. A qualitative
-agreement is made by comparing the JP vesicle shape with the
-two-dimensional inextensible membrane in continuum modeling
-simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). An
+%
+%Our coarse-grained model is also able to calculate inter-monolayer
+%friction. 
+%
+
+We also simulate the spatial migration of a JP vesicle in a
+parabolic shear flow. 
+%The chosen parameter values result in an asymmetric
+%slipper shape. 
+%
+Similar to the hydrodynamics of a GUV in a Poiseuille flow~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}),
+the nano JP vesicle moves toward the center of the shear flow.
+While the initial reduced area of the JP vesicle is $A^*
+\approx 1$, the equilibrium reduced area is $A^*=0.9$. 
+For the parameters we used in the simulation, the JP vesicle takes an asymmetric shape as it settles above the center of flow and exhibits tank-treading motion.
+%A qualitative
+%agreement is made by comparing the JP vesicle shape with the
+%two-dimensional inextensible membrane in continuum modeling
+%simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). 
+An
 interesting result of the JP vesicle is that $y$-coordinate of the
@@
 
-The single JP vesicle simulations end with obtaining JP bilayer stretching 
-modulus $K_A$ and hydraulic permeability constant $P$. We extract these 
-physical quantities from the Laplace pressure relationship that $R\Delta P$ is 
-proportional to JP bilayer stretch. We describe the aqueous flux in membrane 
-using a differential equation~\ref{eq:perm} and solve for the theoretical 
-permeability constant $P$. In spite of producing these values with some discrepancy
-using the default parameter set, we provide a new framework in measuring coarse-grained 
-membrane permeability.
-
-We compare setups of two JP vesicles and two vesicles described with a
+%The single JP vesicle simulations end with obtaining JP bilayer stretching 
+%modulus $K_A$ and hydraulic permeability constant $P$. We extract these 
+%physical quantities from the Laplace pressure relationship that $R\Delta P$ is 
+%proportional to JP bilayer stretch. We describe the aqueous flux in membrane 
+%using a differential equation~\ref{eq:perm} and solve for the theoretical 
+%permeability constant $P$. In spite of producing these values with some discrepancy
+%using the default parameter set, we provide a new framework in measuring coarse-grained 
+%membrane permeability.
+
+We further simulate the hydrodynamics of  two JP vesicles, and draw comparison with simulation results of two vesicles described by the Helfrich
 continuum model. A comparison of the vesicle shapes and the streamlines

### 2021-09-17 doc/main_jfm.tex
new Figure 8

@@
 \centering
-\includegraphics[width=11.32cm]{Figure1_Wrapper.pdf}
+\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
 %\includegraphics[height=2in]{relax2.eps}
@@
 \end{figure}
-Figures~\ref{figure2}c and~\ref{figure2}d demonstrate that the initial, non-equilibrium configuration has a large internal fluid pressure
-that vanishes as the configuration tends toward the equilibrium state.  
-This suggests that the initial collection of JP is under tension and
-this tension is relaxed as fluid is expelled through the inter-particle
-spacing. To make a comparison with membrane continuum mechanics, lipid
-bilayer membranes have a large area modulus $K_A$ of about $240$ pN
-nm$^{-1}$ \cite{NAGLE} and changes in surface area give rise to a
-membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
-membrane surface area and $A_0$ is the reference surface area in the
-non-tensed state. In the two-dimensional vesicles, the tension becomes
-\begin{align}
-\label{eq:stretch}
-\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
-\end{align}
-where $L$ and $L_0$ are the vesicle arc length and resting length,
-respectively. A stretched, circular vesicles has a Laplace pressure 
-\begin{align}
-\label{eq:LaplacePressure}
-\Delta p = \frac{\tilde \gamma}{R},
-\end{align}
-where $\Delta p$ is the difference in internal pressure to the pressure
-at infinity and $R$ is the radius of the circular vesicle. The factor
-$R^{-1}$ is the total curvature since the principle curvature in the
-direction of the cylinder is zero.
 
 \begin{figure}
-\centering
-\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
-%\includegraphics[width=0.32\textwidth]{PermPanelB.pdf}
-%\includegraphics[width=0.32\textwidth]{PermPanelC.pdf}
-%\includegraphics[width=0.32\textwidth]{PermPanelA.pdf}
   \caption{\label{figure:permeability} JP vesicles are suspended in a
@@
 \end{figure}
+
+Figures~\ref{figure2}c and~\ref{figure2}d demonstrate that the initial, non-equilibrium configuration has a large internal fluid pressure
+that vanishes as the configuration tends toward the equilibrium state.  
+This suggests that the initial collection of JP is under tension and
+this tension is relaxed as fluid is expelled through the inter-particle
+spacing. To make a comparison with membrane continuum mechanics, lipid
+bilayer membranes have a large area modulus $K_A$ of about $240$ pN
+nm$^{-1}$ \cite{NAGLE} and changes in surface area give rise to a
+membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
+membrane surface area and $A_0$ is the reference surface area in the
+non-tensed state. In the two-dimensional vesicles, the tension becomes
+\begin{align}
+\label{eq:stretch}
+\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
+\end{align}
+where $L$ and $L_0$ are the vesicle arc length and resting length,
+respectively. A stretched, circular vesicles has a Laplace pressure 
+\begin{align}
+\label{eq:LaplacePressure}
+\Delta p = \frac{\tilde \gamma}{R},
+\end{align}
+where $\Delta p$ is the difference in internal pressure to the pressure
+at infinity and $R$ is the radius of the circular vesicle. The factor
+$R^{-1}$ is the total curvature since the principle curvature in the
+direction of the cylinder is zero.
 

### 2021-09-18 doc/main_jfm.tex
roadmap figure 0

@@
 \begin{center}
-\includegraphics[width=11.32cm]{Figure0_Wrapper.pdf}
+\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
 \end{center}
-\caption{The diagram illustrates the domain and boundary conditions for the mobility problem formulation.}
+\caption{Panel (a) illustrates the domain and boundary conditions for the mobility problem. 
+Particles self-assemble into vesicle bilayers (panel (b)). In panel (c), 
+the particles arrange along inner and outer leaflets. The curve $C_M$ is the midplane curve which has 
+length $L$ and surrounds a region of area $A$.  Initially stretched vesicles relax to equilibrium 
+with fluid flow across the bilayer. The study considers a single vesicle in shear flow (panel (d)) and other background flows
+and considers vesicle interactions in background flows (panel (e)).}
 \label{fig:figure0}

### 2021-09-18 doc/main_jfm.tex
figure 0 caption

@@
 \caption{Panel (a) illustrates the domain and boundary conditions for the mobility problem. 
-Particles self-assemble into vesicle bilayers (panel (b)). In panel (c), 
-the particles arrange along inner and outer leaflets. The curve $C_M$ is the midplane curve which has 
+The color map in panels (b) - (e) is the solution $u$ of \eqref{eq:SL}. Red indicates a high degree of hydrophobicity ($u = 1$) 
+while blue indicates no hydrophobicity ($u = 0$).
+Particles self-assemble into vesicle bilayers (panel (b)) and eventually  
+arrange along inner and outer leaflets (panel (c)). The curve $C_M$ is the midplane curve which has 
 length $L$ and surrounds a region of area $A$.  Initially stretched vesicles relax to equilibrium 
-with fluid flow across the bilayer. The study considers a single vesicle in shear flow (panel (d)) and other background flows
-and considers vesicle interactions in background flows (panel (e)).}
+with fluid flow across the bilayer. The study considers a single vesicle in background flows such as shear flow (panel (d))
+and hydrodynamic vesicle-vesicle interactions (panel (e)).}
 \label{fig:figure0}

### 2021-09-21 doc/main_jfm.tex
edits up to 4.2.2

@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{theorem}{Theorem}
 \newtheorem{corollary}{Corollary}
@@
 %\title{Two-Dimensional Vesicles Under External Flow via Integral Equation Method}
-\title{Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations}
+\title{Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential}
+%\title{Hydrodynamics of Amphiphilic Particles in Background Flows}
 %\author{Alan N. Jones\aff{1}
@@
 \begin{abstract}
+  We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
   In this work, we study the dynamics of many-body systems immersed in a
@@
 \caption{Panel (a) illustrates the domain and boundary conditions for the mobility problem. 
-The color map in panels (b) - (e) is the solution $u$ of \eqref{eq:SL}. Red indicates a high degree of hydrophobicity ($u = 1$) 
-while blue indicates no hydrophobicity ($u = 0$).
+The color map in panels (b) - (e) is the solution $u$ of \eqref{eq:SL}. Red is for $u = 1$
+and blue is for $u = 0$.
 Particles self-assemble into vesicle bilayers (panel (b)) and eventually  
-arrange along inner and outer leaflets (panel (c)). The curve $C_M$ is the midplane curve which has 
-length $L$ and surrounds a region of area $A$.  Initially stretched vesicles relax to equilibrium 
+arrange along inner and outer leaflets. In panel (c), $C_M$ is the midplane curve,
+$A$ is the enclosed area, and $L$ is the arc length.  Initially stretched vesicles relax to equilibrium 
 with fluid flow across the bilayer. The study considers a single vesicle in background flows such as shear flow (panel (d))
@@
 \subsection{\label{mobility}Mobility Problem}
-We consider an $N_b$-many body collection of Janus particles suspended
-in a two-dimensional unbounded domain $\Omega$. The boundary of each
-particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup
-\Gamma_2 \cup \cdots \cup \Gamma_{N_b}$. Assuming the inertial terms are negligible, the
-governing equations are
+The objective is to study the hydrodynamics of JP vesicles in background flows. 
+We consider an $N_b$-many body collection of JP suspended
+in a two-dimensional unbounded domain $\Omega$. 
+The boundary of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup
+\Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure \ref{fig:figure0}a). 
+Assuming the inertial terms are negligible, the governing equations are
 \begin{alignat}{3}
@@
 %
-where $\uu$ is the velocity, $\mu$ is the constant viscosity, $p$ is the
-pressure, and $\uu_\infty$ is the background flow. Since each particle
-$\Gamma_i$ with center $\aa_i$ is a rigid body, its velocity satisfies 
+where $\uu$ is the velocity, $p$ is the
+pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
+Since each particle $\Gamma_i$ with center $\aa_i$ is a rigid body, its velocity satisfies 
 \begin{align}
@@
 \begin{align}
+\label{eq:rigid_bc}
   \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
@@
 we define imposed forces $\FF_i$ and torques $T_i$ acting on each
-particle. Since the small particles are intertialess, force balance
+particle. Since the small particles are inertialess, force balance
 gives 
@@
   \label{eq:force}
-  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s = \mathbf{0},
+  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
   && i=1,\ldots,N_b,\\
   \label{eq:torque}
-  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
-    (\ssigma \cdot \nnu_i) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
+  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
+    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
 \end{alignat}
@@
 \subsection{Imposed Forces}
-The imposed forces and torques contain two parts. The first part comes
-from the hydrophobic attraction potential (HAP). This potential was
-introduced in~\cite{Fu20} and models hydrophobic attraction by solving
+The imposed forces and torques contain two parts: hydrophobic attraction and repulsion. 
+The hydrophobic attraction potential was introduced by ~\cite{Fu20} and is responsible for forming particle aggregates
+that sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).
+We model hydrophobic attraction by solving
 the screened Laplace equation boundary value problem
@@
 portions of the surface. We assume that the $f_i$ and $\Gamma_i$ are
-smooth. The parameter $\rho$ is the decay length of attraction. The
-forces and torques for this attraction are 
+smooth. The parameter $\rho > 0$ is the decay length of attraction. The
+forces and torques of attraction are 
 \begin{align}
   \label{eq:hydrophobicAttraction}
-  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, \dif s, 
+  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
     \quad 
-  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) \dif s,
+  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu) \dif s,
 \end{align}
@@
 \end{align}
-is the hydrophobic stress tensor. The parameter $\gamma$ is
+is the hydrophobic stress tensor and $\gamma > 0$ is
 the interfacial
-tension. The forces $\FF_i^{\text{hydro}}$ and torques
-$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
-that partially sequester the hydrophobic portions of the particle
-surface.
+tension.
 
@@
 $j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
-$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another. We then
+$\tilde{\xx}_j \in \Gamma_j$ that are closest to one another (Figure \ref{fig:figure0}a). We then
 define the repulsion force and torque
@@
 \end{align}
-The repulsion profile $P(r)$ is zero for distances $r$ larger than a
+The repulsion profile $P(r)$ is set to zero for distances $r$ larger than a
 repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
-and~\eqref{eq:REPULtorque} ignore particles $\Gamma_j$ outside a
-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
+and~\eqref{eq:REPULtorque} ignore particles outside a
+$\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
 $P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
@@
 By solving the mobility problem, we obtain translational and angular
-velocities of the $N_b$-body system. A second-order Adams-Bashforth
+velocities of the $N_b$-body system. 
+A second-order Adams-Bashforth
 scheme updates the particle positions and orientations. By including the
-repulsion force~\eqref{eq:REPULforce} and
-torque~\eqref{eq:REPULtorque}, particle collisions are avoided even
+repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
 when using a relatively large time step.
@@
 Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. After
-discretizing~\eqref{eq:screenedSKIE}, the result is a $NN_b \times NN_b$
+discretizing~\eqref{eq:screenedSKIE}, the result is an $NN_b \times NN_b$
 linear system that is solved with block-diagonal preconditioned GMRES.
@@
 representation of~\cite{pow-mir1987}. In particular, we write the
-velocity as the sum of a double-layer potential and $N_b$ Stokeslets and
-Rotlets
+velocity as the sum of a double-layer potential and $N_b$-many Stokeslets and
+rotlets
 \begin{align}
@@
   \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
-    \frac{\rr \cdot \nnu}{\rho^2} \frac{\rr \otimes \rr}{\rho^2}
+    \frac{\rr \cdot \nnu}{|\rr|^2} \frac{\rr \otimes \rr}{|\rr|^2}
     \eeta(\yy) \, \dif s_\yy,
 \end{align}
-where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and Rotlet
+where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and rotlets
 centered at $\aa_i$ are
 \begin{align}
-  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log \rho + 
-    \frac{\rr \otimes \rr}{\rho^2}\right) \FF_i, \\
-  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{\rho^2} T_i,
-\end{align}
-respectively, where $\rr = \xx - \aa_i$ and $\rho = |\rr|$. The
-Stokeslet is torque-free and has force $\FF_i$ while the Rotlet is
+  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
+    \frac{\rr \otimes \rr}{|\rr|^2}\right) \FF_i, \\
+  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
+\end{align}
+respectively, where $\rr = \xx - \aa_i$. The
+Stokeslet is torque-free and has force $\FF_i$ while the rotlet is
 force-free and has torque $T_i$. Therefore, the
@@
 is a $(2NN_b + 3N_b) \times (2NN_b + 3N_b)$ linear system that we solve
-with block-diagonal preconditioned GMRES. We note that other BIE
-formulations of the mobility problem use single-layer potentials
+with block-diagonal preconditioned GMRES. Other BIE
+formulations of the mobility problem have used single-layer potentials
 (\cite{cor-gre-rac-vee2017, rac-gre2016}) or a combination of single-
@@
 \S~\ref{sec:ves_in_shear}). Hydrophobic attraction and repulsion are
-zero for a single particle. The angle of the ellipse's major axis coming
+zero for a single particle (see \cite{Fu20} equation 2.13). The angle of the ellipse's major axis coming
 from the integral equation method was in complete agreement with the
-theoretical, Jeffrey orbit time-course (\cite{jef1922}).
+theoretical, Jeffery orbit time-course (\cite{jef1922}).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Calculating the Hydrophobic Force}
+\subsection{Main Theoretical Result: Calculating the Hydrophobic Force}
 \label{subsec:calculating_force}
@@
 That is, $v_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
-with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $v_i$, we can
-show that
+with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $v_i$, we prove
+\begin{theorem}
 \begin{align}
   \label{eq:recipforcetorque}
-  \FF_i^{\text{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
-  T_i^{\text{hydro}}    = \int_{\Gamma_i} 
+  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
+  T_i^{\mathrm{hydro}}    = \int_{\Gamma_i} 
     (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
@@
 \end{align}
-Here, $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc length
-derivative for $\Gamma_i$, respectively, and $\nnu$ is the unit normal.
+\end{theorem}
+The symbols $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc length
+derivative for $\Gamma_i$, respectively (Figure \ref{fig:figure0}a.)  
+The result 
+is valid for any smooth particle shape or boundary condition. 
 The advantage in using~\eqref{eq:recipforcetorque} over
@@
   \label{eq:prejump}
-  \FF_i = \int_{\Gamma_i} \jump{{\bf T}_2  \nnu}  \, \dif s,\quad
-  T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \jump{{\bf T}_2 \nnu} \, \dif s.
+  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \jump{{\bf T}_2  \nnu}  \, \dif s,\quad
+  T_i^{\mathrm{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \jump{{\bf T}_2 \nnu} \, \dif s.
 \end{align}
@@
 \begin{proof}
-To show~\eqref{eq:prejump}, we expand
+To show~\eqref{eq:prejump}, we expand \eqref{eq:hydrophobicAttraction} as
 \begin{align}
@@
 where the superscript denotes the limit taken from in $U_i$.  
-Combining the previous four equations gives the first equation in \eqref{eq:prejump}.
+Combining the above gives the first equation in \eqref{eq:prejump}.
 The argument for the second equation in \eqref{eq:prejump} is identical. 
@@
 \end{equation}
-on $\Gamma_i$. Therefore,
+on $\Gamma_i$ (see, e.g. \cite{KlBaGrON13}). Therefore,
 \begin{align*}
@@
 %\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
-  \caption{\label{figure3} A JP vesicle suspended in a shear flow with
-  shear rate $\chi=0.0025$. (a) The initial configuration of a 58-body
-  JP vesicle where the black arrows point in the direction of the
-  hydrophobic side of the JP. (b) The particle velocities and
-  streamlines of the configuration in (a). The streamlines are plotted
-  in the background as solid curves and the red arrows represent the
-  particle velocities. (c) The deformed tank-treading JP vesicle at
-  $t=4000$. (d) The particle velocities and streamlines of the
-  configuration in (c). The background colors in panels (a) and (c)
-  represent the strength of the hydrophobic attraction potential. The
-  blue regions have the weakest action and the red regions in the
-  bilayer have the strongest action.}
+  \caption{\label{figure3} 
+  JP vesicles undergo tank-treading in shear flow. 
+  In panel (a),  the initial, 58-body vesicle is circular and the black arrows point in the direction of the
+  hydrophobic side of the JP.
+  In panel (b), the JP suspension rotates and deforms with the shear flow.
+  The color map is for the solution $u$ of \eqref{eq:SL}. 
+  The white curves are the streamlines of $\uu.$ 
+   The shear rate is $\chi=0.0025$.}
 \end{figure}
@@
 \subsection{Model Parameters}
-To extract physical quantities of the target structure, we select
-particles that are disks with diameter $l_0 = 2.5$ nm representing the
-characteristic thickness of monolayers. The boundary
+\cite{Fu20} studied physical quantities for static JP bilayers
+for various particle shapes.  In the present study, we fix particle shape and 
+vary the background flows.  
+Specifically, the
+particles are circular disks with diameter $l_0 = 2.5$ nm. The boundary
 conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
@@
 $\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle center
-and director respectively. With this choice, the director points in the
-direction of the hydrophobic side of the JP. The other physical
-parameters are the decay length $\rho = 2 l_0$, the repulsion length
-$\rho_0 = 0.2l_0$, the repulsion strength is $M=4.0$~$k_BT$, the
-interfacial particle tension $\gamma = \text{4.1 pN nm}^{-1}$, and $\mu
-= \text{1 cP} = \text{1 pN ns nm}^{-2}$ is the viscosity of water at
-room temperature. \cite{Fu20} provides physical quantities for static JP
-bilayers.
-
-We consider the behavior of JP vesicles under various external flows.
-To do so, we nondimensionalize the problem through the change of
-variables 
+and director respectively.  The particle diameter is the
+thickness of monolayers and the  director points in the
+direction of the hydrophobic side of the JP.
+
+We use $\rho = 2 l_0$ for decay length, $\rho_0 = 0.2l_0$ for repulsion length, $M=4.0$~$k_BT$ for repulsion strength, 
+$\gamma = \text{4.1 pN nm}^{-1}$ for interfacial tension, and $\mu
+= \text{1 cP} = \text{1 pN ns nm}^{-2}$ for viscosity of room-temperature water.
+We nondimensionalize the problem through the change of variables 
 %\begin{equation}
 %\label{eq:nondimensionalize}
-$t \mapsto t \text{ ns},$ % \quad
+$t \mapsto t \text{ ns}$,
 $\xx \mapsto \xx \text{ nm}$, %\quad 
@@
 %\end{equation}
-For the remainder of the manuscript, the time axes are in ns, and the
-pressure $p$ and stresses $\sigma$ and $\mathbf{T}^{\mathrm{hydro}}$ are
-in pN nm$^{-2}$. Finally, the dimensionless shear rate is $\chi =
-\dot\gamma \tau$ for the dimensional shear rate $\dot\gamma$ in
-ns$^{-1}$ and the characteristic time is $\tau = 1$~ns. The time step
-size $\Delta t=0.2$ is used for all simulations in this work including
-the relaxation run.
+The numerical time step size is $\Delta t=0.2$.
+
+To reach consistent simulation outcomes, we first solve for a baseline JP vesicles 
+that is suitably close to equilibrium. We start
+with an assumed configuration of $N=58$ JP in the form of two, circular, apposing monolayers of about
+$8$ nm in radius. 
+Figure~\ref{figure2}a shows that the 
+translational and rotational velocities vanish exponentially with
+an approximate decay rate $\sim 4.6$ $\upmu$s$^{-1}$. An 
+equilibrium configuration is therefore rapidly attained.
+This equilibrium configuration serves as the initial data 
+in the background flow simulations.
 
@@
 \end{center} 
-  \caption{\label{figure4} (a) The reduced area transitioning over time
+  \caption{\label{figure4}
+ JP vesicles loose enclosed area and conserve length in shear flow. 
+  Panel (a) gives the reduced area over time
   for four different shear rates. The smooth curves are a best-fit
-  exponential curve. (b) The decay rate $k$, using the exponential fit
-  to the data in panel (a), for a number of shear rates. The inset shows
-  the terminal reduced areas. (c) The total arc lengths of the midplanes
-  over time for four shear rates. (d) The excess length of the
-  midplanes. For all panels, a set of shear rates
-  $\chi=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. The
-  legend in panel (d) applies to both panels (a) and (c).}
+  exponential curve. There is commensurate increase in excess length (panel (b)), 
+  but the arc length of the mid plane curve is more or less constant.   
+   The legend in panel (b) applies to panels (a)--(c).
+  Panel (d) plots the steady-state reduced area and the decay rate $k$ (inset) using the exponential fit
+  to the data in panel (a). }
 \end{figure}
@@
 \label{sec:ves_in_shear}
-Our hydrodynamic simulation studies begin by studying the dynamics of a single JP vesicle suspended in
-the shear flow
+Our simulation studies begin by showing, for the first time, that a JP suspension 
+behaves as a tank-treading vesicle
+with zero viscosity contrast between the fluids inside and
+outside of the vesicle (\cite{Finken08, Shaqfeh11}).
+The centroid of the baseline $58$-body JP vesicle lies at the origin 
+and the background shear flow 
 \begin{align}
@@
 \end{align} 
-with shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
-and $\mathbf{e}_y$ for the horizontal and vertical directions,
-respectively. It is well known that a vesicle has tank-treading behavior
-when there is no viscosity contrast between the fluids inside and
-outside of the vesicle.
-%Within the framework of the simulation setup,
-%the proposed model provides a feature that the fluid viscosity is
-%constant over the computational domain and it is capable of performing
-%these simulations.
-
-The centroid of the pre-relaxed $58$-body Janus vesicle is initially
-placed at the origin and the shear flow with a shear rate $\chi$ is
-applied. Figure~\ref{figure3} shows snapshots of the JP vesicle in the
-shear flow with a shear rate $\chi=0.0025$. Panels (a) and (b) show the
-initial shape obtained from the relaxation run and the deformed
-configurations of the JP vesicle at time $t=4000$ are in panels (c) and
-(d). The background color in panels (a) and (c) is the strength of the
-action of the hydrophobic attraction. Red corresponds to a strong action
-while blue is a weak action. The hydrophobic layer clearly has the
-strongest action. To demonstrate the tank-treading behavior of the
-vesicle, panels (b) and (d) provide the streamlines of the fluid
-velocity around the JP vesicle. In panel (d), we can clearly observe the
-clockwise tank-treading motion.
-
-%
-
-To extract additional physical properties of the proposed model, we
-compute the total length, reduced area, and excess length of the bilayer
-structure. The enclosed area and the total length of the structure are
-calculated from the midplane. The reduced area is $A^* = 4\pi A/L^2$
-where $A$ is the area, and $L$ is the total length of the JP vesicle,
-and the excess length is $\Delta=L/\sqrt{A^*/\pi}-2\pi$.
-Figure~\ref{figure4} shows these quantities for a JP vesicle suspended
-in a shear flow with shear rates $\chi=\{0.002,0.0025,0.003,0.0035\}$.
+is applied for
+shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
+and $\mathbf{e}_y$ for the horizontal and vertical directions, respectively.
+We use the dimensionless shear rate $\chi = \dot \gamma$ ns.
+
+Figure~\ref{figure3} shows snapshots of the JP vesicle in the
+shear flow with $\chi=0.0025$. 
+Under the background flow, the rigid-body boundary condition \eqref{eq:rigid_bc} causes the 
+particle suspension to stretch apart. This perturbation  
+disrupts the preferred particle orientations and exposes the hydrophobic core to bulk water (Figure~\ref{figure3}, red region).
+In response, hydrophobic attraction \eqref{eq:hydrophobicAttraction} causes the 
+particles to reorient and form a  somewhat elliptically-shaped suspension.  
+Panels (a) shows the initial configuration and panel (b) shows the later, fully-formed, clockwise tank-treading motion. 
+The JP suspension maintains its bilayer structure throughout the simulation. 
+%
+
+To extract physical quantities, 
+let $A^* = 4\pi A/L^2$ be the reduced area and $\Delta=L/\sqrt{A^*/\pi}-2\pi$ the excess length of the bilayer
+structure (\cite{Finken08}).
+Here, $A$ is the enclosed area and $L$ is the total length of the JP vesicle  (Figure \ref{fig:figure0}a).
+Figure~\ref{figure4} shows the evolution of the same for various shear rates.
+Panels (a) and (b) show that $A^*$ decreases and $\Delta$ increases with time, respectively,
+and that the rate of decrease/increase grows with shear rate. 
+The total arc length, however, remains constant for all time
+for all four shear rates (panel (c)).
+We conclude that the JP vesicle loses area and that the bilayer behaves as a permeable membrane. 
+Due to granularity, the tank-treading motion has some wobble and this is the source
+of the oscillations in the panels of Figure~\ref{figure4}.
+
 Since the starting configuration is nearly circular, the reduced area
-decreases from an initial value close to $1$. The smooth curves in panel
-(a) are best fits of the exponential model $A^* = a_0 + b_0 \exp(-kt)$.
-Panel (b) shows that the decay rate $k$ is independent of the shear rate
-for sufficiently large shear rates, and the terminal reduced areas of
-each case are shown in the inset. We see that lower shear rates generate
-a higher final reduced area. In particular, we observe that the reduce
-area converges relatively early when the shear rate is lower than
-$\chi=0.003$. 
-%and has a faster convergence than the high shear rate cases.
-Panel (c) shows that the total arc length remains constant for all time
-with all four shear rates. Combining the behavior of the reduced area
-and the total arc length, the excess length must increase in time and be
-larger for higher shear rates as observed in panel (d). In all these
-results, there are oscillations that can be explained by the granularity
-of the JP vesicle which results in a midplane that is non-smooth.
-%Overall the total lengths of the bilayer have the same converging value
-%in all test shear rates.
+decreases from an initial value close to $1$ and tends to a steady-state value $A^*_{\infty}$. 
+The curves in panel (a) are fit of the exponential model $A^* = A^*_{\infty} + (1-A^*_{\infty}) \exp(-kt)$.
+Panel (d) shows that $A^*_{\infty}$ decreases with shear rate, 
+and that reduced area converges to a steady state earlier when the shear rate is lower (inset).
+
+We point out that the range of values for $\chi$ where we measured for tank-treading 
+correspond to shear rates $\dot \gamma = O(10^6$ s$^{-1}$) 
+which gives fluid velocities like m s$^{-1}$ in the vicinity of the  vesicle.  
+While seemingly large, these values are consistent with prior MD studies (\cite{Brandner2019})
+and are a consequence of the fact that the magnitude of elastic membrane stresses grows inversely 
+with the vesicle radius.  Larger shear rates are required to produce the viscous stresses needed to 
+appreciably deform smaller vesicles.
 
@@
 consistent with what has been seen in articles in molecular dynamics
-simulations. (\cite{Zgorski2019,denOtter2007})
+simulations. (\cite{Zgorski2019, denOtter2007})
 
@@
 
-\subsection{Self-Assembly and Relaxation}
-
-In order to examine the hydrodynamics interactions of JP vesicles, it is
-necessary to have a suitable, initial, JP equilibrium vesicle. This
-ensures that the dynamics of the bilayer under a shear flow, for
-example, reach consistent outcomes. For our target vesicle, we start
-with $N=58$ JP arranged in two circular, apposing monolayers of about
-$8$ length units. The directors of the outer monolayer point inward and
-the directors of the inner monolayer point outward
-(Figure~\ref{figure2}a).  The JP of this chosen configuration are
-generally not in equilibrium.  Rather, the inter-particle distances and
-orientations must make slight adjustments so that attraction and
-repulsion balance.  Figure~\ref{figure2}(b) shows that the magnitudes of
-the mean velocity components ${\bf v}=\{v_x,v_y\}$ and the variation
-$\Delta \theta$ of the particle orientation decrease exponentially with
-an approximation decaying rate $\sim0.005$. A local energy minimum and
-the equilibrium configuration is therefore rapidly attained. The
-equilibrium configuration in Figure~\ref{figure2}a is slightly
-elliptical. The equilibrium eccentricity vanishes for larger $N_b$
-(Figure~\ref{figure2}e).
-
 \subsection{Stretching and Permeability}

### 2021-09-21 doc/main_jfm.tex
edited up to 4.2.4

@@
 \label{sec:ves_in_shear}
-Our simulation studies begin by showing, for the first time, that a JP suspension 
+Our simulation studies begin by showing, for the first time, that a JP suspension with hydrophobic attraction 
 behaves as a tank-treading vesicle
@@
 We use the dimensionless shear rate $\chi = \dot \gamma$ ns.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
+\includegraphics[width=11cm]{Figure5B_Wrapper.pdf}
+%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
+%\includegraphics[width=0.4\textwidth]{Slip2.eps}
+\end{center} 
+  \caption{\label{figure5} 
+  There is inter-monolayer slip present in the JP vesicle tank-treading motion at all shear rates.  
+  Panel (a) tracks the angle  $\theta(t)$ between a pair of particles (blue and yellow) with respect to
+  the JP vesicle centroid. The shear rate is $\chi=0.005$ and in the right figure, the yellow particle
+  will complete two and quarter revolutions in the same time the blue particle completes two revolutions.
+  The curves in panel (b) are the mean change in angle for various shear rates. 
+  Slip velocity generally increases with shear rate but 
+  we have marked two outliers (times symbols). }
+\end{figure}
 
@@
 and are a consequence of the fact that the magnitude of elastic membrane stresses grows inversely 
-with the vesicle radius.  Larger shear rates are required to produce the viscous stresses needed to 
+with the vesicle radius; larger shear rates are required to produce the viscous stresses needed to 
 appreciably deform smaller vesicles.
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
-\includegraphics[width=11cm]{Figure5B_Wrapper.pdf}
-%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
-%\includegraphics[width=0.4\textwidth]{Slip2.eps}
-\end{center} 
-  \caption{\label{figure5} The schematic of the inter-monolayer slip over
-  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
-  mean angle between each particle pair $\theta(t)$ where the angle is
-  calculated from the relative position of the particles with respect to
-  the JP vesicle's center of mass. The configuration plots have two
-  fixed particles marked in yellow and blue and labeled with the
-  corresponding time $t=2000$ and $t=9000$. The midplane curve is
-  denoted as $C_M$. We see that the inter-monolayer slip is largest
-  for large shear rates.}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsubsection{Inter-Monolayer Friction}
-
-The granulated JP vesicle allows us to consider inter-monolayer slip
-between the two leaflets. When the shear rate is sufficiently large,
-take $\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip
-between a pair of particles over time. The pair we consider are colored
-in blue and yellow. In this series of tests, we compute the mean
-particle position and mean angle $\theta(t)$ between the particle
-relative positions with respect to the vesicle center. It is clear that
-the outer leaflet has larger tangential velocity than the inner leaflet
-since $\theta(t)$ increases. This inter-leaflet sliding phenomenon is
-consistent with what has been seen in articles in molecular dynamics
-simulations. (\cite{Zgorski2019, denOtter2007})
-
-To calculate the inter-monolayer friction coefficient for the apposing
-JP leaflets, we let
+We observe inter-monolayer slip in the tank-treading, JP vesicle at all shear rates. 
+The two leaflets of the vesicle are not bound together, but rather are able to slide 
+past one another. This sliding is limited by viscous friction of the aqueous gaps between particles
+and by the constant unbinding and binding of particles pairs in apposing leaflets.  
+The phenomenon is consistent with prior MD results (\cite{Zgorski2019, denOtter2007}).
+
+Figure~\ref{figure5}a illustrates the process by tracking the angle $\theta(t)$
+between two particles, one blue and the other yellow, relative to the vesicle centroid. 
+It is clear from the growth in angle that the outer leaflet has a tangential velocity that is larger  
+then that of the inner leaflet.  
+Figure~\ref{figure5}b plots the mean, particle-pair angle for various shear rates. 
+It suggests that the inter-monolayer slip velocity generally increases with shear rate.
+
+From the data, we are able to define an inter-monolayer friction coefficient  
 \begin{align}
@@
 \end{align}
-%
-where 
-\begin{align}
-  \langle F\rangle = \left\langle \int_{\mathcal{C}_M} 
-    \jump{\ttau \cdot \sigma \cdot \nnu} \,\dif s \right\rangle
-\end{align}
-is the time-averaged, tangential force along the midplane curve
-$\mathcal{C}_M$. The parameters $\langle L\rangle$ and $\langle
-U\rangle$ are the time-averaged midplane curve length and intermonolayer
-slip velocity, respectively.
-
-We calculate $\langle F\rangle$ by first evaluating the smooth
-tangential force along curves a positive distance inside and outside
-$\mathcal{C}_M$ respectively, and then interpolating at zero distance to
-give a force jump. We have made a slight abuse of language: due to the
-problem being two-dimensional, the integral $\langle F\rangle$ is
-actually a force density per length which when divided by length gives
-the requisite force per area. 
-%which when divided by length
-
-Table~\ref{table1} provides dimensional friction coefficients $b$ for
-several shear rates and the results are in quantitative agreement with
-values previously reported in the literature (\cite{sch-vla-mik2010}
-and~\cite{denOtter2007}). The coefficients generally lie within the
-range 0.2 to 0.3 pN$\cdot$ns nm$^{-3}$ but there are some outliers.
-These outliers ($\dot\gamma = 0.0041$ ns$^{-1}$ and $\dot\gamma =
-0.0066$ ns$^{-1}$) correspond to slip velocities that are too low
-relative to the shear rate (see the green and red curve in
-Figure~\ref{figure5}(c)). The JP vesicle consists of only 58 particles
-and so it is not surprising that discrete effects produce outliers.
-
-%\todo[inline]{If $B$ is the numerically calculated friction coefficient,
-%then $b = B/2.5^3$ pN ns nm$^{-3}$ gives the dimensional value.
-%
-%If $P$ is the numerically calculated pressure, then $p = P/2.5$ pN
-%nm$^{-2}$ is the dimensional pressure.}
+where $F$ is the tangential force jump, $L$ is the length of the midplane $C_M$ (Figure~\ref{figure5}a), $U$ is the slip velocity, and 
+$\langle \cdot \rangle$ denotes the time average. 
+To measure inter-monolayer slip $U$, we compute the mean tangential velocity of the particles in the outer monolayer
+and subtract from it the mean tangential velocity of the particles in the inner monolayer. 
+To calculate the tangential force jump $F$, we let 
+\begin{equation}
+F_h = \int_{\mathcal{C}_M^+} 
+    \ttau \cdot \sigma \cdot \nnu \,\dif s -  \int_{\mathcal{C}_M^-} 
+    \ttau \cdot \sigma \cdot \nnu \,\dif s 
+\end{equation}
+where $C_M^+$ and $C_M^-$ are target curves obtained by moving the midplane curve $C_M$ (Figure~\ref{figure5}a)
+a distance $h$ along the outward, respectively inward, unit normal.  Actually, we calculate $F_h$ for several values of $h$ 
+and then define $F$ to by extrapolating to zero distance giving a jump in tangential shear force across the midplane.
 
@@
 %$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
-$b$ (pN$\cdot$ns nm$^{-3}$)    & 0.22 & 0.87  & 0.22 &0.21 & 1.29 & 0.31 & 0.30\\ 
+$b$ (pN$\cdot$ns nm$^{-3}$)    & 0.22 & 0.87*  & 0.22 &0.21 & 1.29* & 0.31 & 0.30\\ 
 \hline    
@@
 \end{table}
+
+Table~\ref{table1} provides dimensional friction coefficients $b$ for
+several shear rates. The coefficients generally lie within the
+range 0.2 to 0.3 pN ns nm$^{-3}$ which is in good quantitative agreement with
+values previously reported in the literature (\cite{sch-vla-mik2010}
+and~\cite{denOtter2007}).  
+The data contain two outliers (Table~\ref{table1}, * symbol).
+These correspond to the two outliers in the slip velocities (Figure~\ref{figure5}b, times symbol). 
+We suspect that due to the finite particle size, the granular wobble of the tank-treading motion is more prominent for some
+shear rates, causing some slip velocities to be lower than expected.
 
@@
 %\includegraphics[height=2in]{N58_rupt_600.pdf}
-  \caption{\label{figure8} Membrane rupture occurs when the shear rate
-  exceeds a threshold. Here the shear rate is $\chi = 0.1$. Starting
-  with a circular shape (panel (a)), the vesicle is stretched by the
-  background flow and multiple pores form (panel (b)). Panels (c)--(d)
-  show the later states during the simulation. Streamlines are included
-  in each panel.}
+  \caption{\label{figure8} 
+  Tank-treading leads to membrane rupture for large shear rates.
+  }
 \end{figure}
-A pore formation or a complete membrane rupture can occur at large shear
+A temporary fissure or a complete membrane rupture can occur at large shear
 rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture when
-suspended in a shear flow with shear rate $\chi=0.1$. The streamlines
-are included in these plots. An interesting phenomenon occurs in panels
-(c) and (d) where two separated bilayers move along the background shear
-flow symmetrically. Consequently, a periodic motion for bilayers may
-occur at certain shear rates. One can expect that these two layers will
-diverge from one another for much higher shear rates.
+suspended in a shear flow. For $\chi = 0.1$, starting
+  with a circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
+  background flow and fissures appear in the bilayer structure in multiple locations (Figure~\ref{figure8}b). 
+  In Figure~\ref{figure8}c, the ruptured vesicles forms two planar micelles which 
+  are eventually carried off by the flow (Figure~\ref{figure8}d).
 

### 2021-09-22 doc/main_jfm.tex
worked on up to sec 4

@@
 \end{center}
-\caption{Panel (a) illustrates the domain and boundary conditions for the mobility problem. 
-The color map in panels (b) - (e) is the solution $u$ of \eqref{eq:SL}. Red is for $u = 1$
-and blue is for $u = 0$.
-Particles self-assemble into vesicle bilayers (panel (b)) and eventually  
-arrange along inner and outer leaflets. In panel (c), $C_M$ is the midplane curve,
-$A$ is the enclosed area, and $L$ is the arc length.  Initially stretched vesicles relax to equilibrium 
-with fluid flow across the bilayer. The study considers a single vesicle in background flows such as shear flow (panel (d))
-and hydrodynamic vesicle-vesicle interactions (panel (e)).}
+\caption{Panel (a) illustrates the domain and boundary conditions for
+  the mobility problem. The color map in panels (b)--(e) is the solution
+  $u$ of \eqref{eq:SL}. Red is for $u = 1$ and blue is for $u = 0$.
+  Particles self-assemble into vesicle bilayers (panel (b)) and
+  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
+  is the midplane curve, $A$ is the enclosed area, and $L$ is the arc
+  length. Initially stretched vesicles relax to equilibrium with fluid
+  flow across the bilayer. The study considers a single vesicle in
+  background flows such as shear flow (panel (d)) and hydrodynamic
+  vesicle-vesicle interactions (panel (e)).}
 \label{fig:figure0}
@@
 \subsection{\label{mobility}Mobility Problem}
-The objective is to study the hydrodynamics of JP vesicles in background flows. 
-We consider an $N_b$-many body collection of JP suspended
-in a two-dimensional unbounded domain $\Omega$. 
-The boundary of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup
-\Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure \ref{fig:figure0}a). 
-Assuming the inertial terms are negligible, the governing equations are
+The objective of this work is to study the hydrodynamics of JP vesicles
+in background flows. We consider an $N_b$-many body collection of JP
+suspended in a two-dimensional unbounded domain $\Omega$. The boundary
+of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
+\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
+\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
+governing equations are
 \begin{alignat}{3}
@@
 we define imposed forces $\FF_i$ and torques $T_i$ acting on each
-particle. Since the small particles are inertialess, force balance
-gives 
+particle. Since the small particles are inertialess, force and torque
+balance gives 
 \begin{alignat}{2}
@@
 \subsection{Imposed Forces}
-The imposed forces and torques contain two parts: hydrophobic attraction and repulsion. 
-The hydrophobic attraction potential was introduced by ~\cite{Fu20} and is responsible for forming particle aggregates
-that sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).
-We model hydrophobic attraction by solving
-the screened Laplace equation boundary value problem
+The imposed forces and torques contain two parts: hydrophobic attraction
+and repulsion. The hydrophobic attraction potential was introduced
+by~\cite{Fu20} and is responsible for forming particle aggregates that
+sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).
+We model hydrophobic attraction by solving the screened Laplace equation
+boundary value problem
 \begin{alignat}{2}
@@
 \label{eq:SLbc}
-u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b \\
+u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
 \label{eq:SLff}
@@
 respectively $1$, representing hydrophilic, respectively hydrophobic,
-portions of the surface. We assume that the $f_i$ and $\Gamma_i$ are
+portions of the surface. We assume that both $f_i$ and $\Gamma_i$ are
 smooth. The parameter $\rho > 0$ is the decay length of attraction. The
@@
 Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. After
-discretizing~\eqref{eq:screenedSKIE}, the result is an $NN_b \times NN_b$
-linear system that is solved with block-diagonal preconditioned GMRES.
+discretizing~\eqref{eq:screenedSKIE}, the result is an $NN_b \times
+NN_b$ linear system that is solved with block-diagonal preconditioned
+GMRES.
 
@@
 specialized quadrature would be necessary to approximate such integrals.
-Alternatively, in Section~\ref{subsec:calculating_force}, we show that
+Alternatively, in Section~\ref{subsec:calculating_force}, we show how
 the force and torque calculations can be expressed in terms of
@@
 is a $(2NN_b + 3N_b) \times (2NN_b + 3N_b)$ linear system that we solve
-with block-diagonal preconditioned GMRES. Other BIE
-formulations of the mobility problem have used single-layer potentials
-(\cite{cor-gre-rac-vee2017, rac-gre2016}) or a combination of single-
-and double-layer potentials (\cite{cor-vee2018}).
-
-We validated our solver for \eqref{eq:SKIE}-\eqref{eq:mobility2} using a
-single elliptical particle suspended in a background shear flow (see
-\S~\ref{sec:ves_in_shear}). Hydrophobic attraction and repulsion are
-zero for a single particle (see \cite{Fu20} equation 2.13). The angle of the ellipse's major axis coming
-from the integral equation method was in complete agreement with the
-theoretical, Jeffery orbit time-course (\cite{jef1922}).
+with block-diagonal preconditioned GMRES. Other BIE formulations of the
+mobility problem use single-layer potentials (\cite{cor-gre-rac-vee2017,
+rac-gre2016}) or a combination of single- and double-layer potentials
+(\cite{cor-vee2018}).
+
+We have validated our solver for~\eqref{eq:SKIE}--\eqref{eq:mobility2}
+using a single elliptical particle suspended in a background shear flow
+(see \S~\ref{sec:ves_in_shear}). Hydrophobic attraction and repulsion
+are zero for a single particle (see \cite{Fu20} equation 2.13). The
+angle of the ellipse's major axis coming from the integral equation
+method agrees with the theoretical, Jeffery orbit time-course
+(\cite{jef1922}).
 
@@
 \end{theorem}
-The symbols $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc length
-derivative for $\Gamma_i$, respectively (Figure \ref{fig:figure0}a.)  
-The result 
-is valid for any smooth particle shape or boundary condition. 
-The advantage in using~\eqref{eq:recipforcetorque} over
+The symbols $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc
+length derivative for $\Gamma_i$, respectively (Figure
+\ref{fig:figure0}a.) The result is valid for any smooth particle shape
+or boundary condition. The advantage of
+using~\eqref{eq:recipforcetorque} over
 using~\eqref{eq:hydrophobicAttraction} is that the components $\sigma$,

### 2021-09-22 doc/main_jfm.tex
editing section 4 complete

@@
 with an assumed configuration of $N=58$ JP in the form of two, circular, apposing monolayers of about
-$8$ nm in radius. 
-Figure~\ref{figure2}a shows that the 
+$8$ nm in radius. The 
 translational and rotational velocities vanish exponentially with
@@
 This equilibrium configuration serves as the initial data 
-in the background flow simulations.
+in the subsequent background flow simulations.
 
@@
 behaves as a tank-treading vesicle
-with zero viscosity contrast between the fluids inside and
-outside of the vesicle (\cite{Finken08, Shaqfeh11}).
+%with zero viscosity contrast between the fluids inside and
+%outside of the vesicle
+(\cite{Finken08, Shaqfeh11}).
 The centroid of the baseline $58$-body JP vesicle lies at the origin 
@@
   the JP vesicle centroid. The shear rate is $\chi=0.005$ and in the right figure, the yellow particle
-  will complete two and quarter revolutions in the same time the blue particle completes two revolutions.
+  will complete two and a quarter revolutions in the same time the blue particle completes two revolutions.
   The curves in panel (b) are the mean change in angle for various shear rates. 
@@
 \subsubsection{Vesicle in a Parabolic Flow}
-Another interesting flow to consider is the parabolic flow
+Finally, we consider the parabolic background flow
 \begin{align}
@@
 where $v_{max}$ is the flow strength and $w$ determines the shape of the
-flow. $R_0$ is defined as the radius of the JP vesicle at $t=0$. The
-behavior of a vesicle in this unbounded non-linear flow includes
+flow. The parameter $R_0$ is the radius of the JP vesicle at $t=0$ and 
+$w$ sets the width of the profile.  
+\cite{Kaoui09, cou-kao-pod-mis2008, dan-vla-mis2009} have shown that the
+behavior of a vesicle in this unbounded  flow includes
 vertical migration, and depending on the flow rate and reduced area, the
 steady-state shape can be either a symmetric parachute or an asymmetric
-slipper (\cite{Kaoui09, cou-kao-pod-mis2008, dan-vla-mis2009}).
+slipper.
 
@@
 
-Figure~\ref{figure6} shows three configurations for one specific case
+Figure~\ref{figure6} shows four configurations for one specific case
 where the centroid of the JP vesicle is initially placed slightly
-above the $x$-axis. The parameters are $v_{max} = 8.0$, $w=10$, and
-$R_0=8$. The red curves are the midplanes and a particle pair is marked
-in color. We observe that the deformed JP vesicle has a
+above the $x$-axis.  We have marked a pair of particles blue and yellow
+in the inner and outer leaflets, respectively,  and observe that the 
+deformed JP vesicle (Figure~\ref{figure6}, $t = 12~\upmu$s) has a
 counterclockwise movement and the shape of the vesicle approaches an
-asymmetric slipper shape. Moreover, we observe inter-monolayer slip
-between the two leaflets. For this test, the reduced area for this
+asymmetric slipper shape. For this test, the reduced area in the final
 configuration is approximately $0.9$ which matches the previous
 numerical tests in~\cite{Kaoui09} where a slipper-like shape occurs when
-the flow velocity is weak and the reduced area is large. A schematic of
-the setup is shown in Figure~\ref{figure7} where the blue horizontal
-line represents the mean $y$-position of all particles. The inset of
-Figure~\ref{figure7} shows the trajectory of the mean position in the
-$y$-direction that decreases towards $y=1$ for a period of time and then
-starts to oscillate due to the granularity of the JP vesicle.
+the flow velocity is weak and the reduced area is large.  The flow causes the 
+vesicle, which is initially placed above the axis,
+to draft downward where it reaches a steady height of about  $1$ nm.
 
@@
 %\includegraphics[width=0.8\textwidth]{slipper.eps}
-  \caption{\label{figure6} A JP vesicle suspended in a parabolic flow
-  where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
-  20$~nm, and the control parameter is $w=25$~nm. The configuration is
-  the state when $t=\{0, 4000, 8000\}$ which correspond to $0\ \mu $s, $2.44\ \mu $s, and $4.88\ \mu $s.
-The red curves are the midplanes.
-Inter-monolayer slip is observed by comparing the relative  locations of the blue and yellow particles.}
-\end{figure}
-
-\begin{figure}
-\centering
-%\includegraphics[height=2in]{parabolic.eps}
-  \caption{\label{figure7} The schematic of a JP vesicle suspended in a
-  parabolic flow where the strength of the flow is
-  $v_{max}=32.8$~nm~ns$^{-1}$, $R_0 = 20$~nm, and the control parameter
-  is $w=25$~nm. The configuration occurs when $t=6.1\ \mu$s and red arrows indicate the tank-treading motion. The inset plots the trajectory of mean $y$-position over time.}
+  \caption{\label{figure6} A JP vesicle placed in a parabolic flow drifts 
+  toward the central axis.  It assumes a slipper shape and undergoes tank-treading
+  like in the shear flow case.  The arrows on the left illustrate the background flow and 
+  the arrows on the right show the velocity relative to the vesicle's moving frame. 
+  The thick black curve plots the distance from the axis as a function of time from left to right.  
+  The parameters are $v_{max} = 8$~nm ns$^{-1}$, 
+  $w=10$, and $R_0=20$ nm.}
 \end{figure}
@@
 %  this.}
-\caption{\label{figure2} A JP Vesicle relaxing under a quiescent flow.
-  (a) The blue dashed and solid curves are mean magnitudes of the
-  particle velocities in $x$ and $y$ directions, respectively. The red
-  curve shows the decreasing trend of the mean magnitude of particle
-  orientation change. The black dashed line shows the reference of how
-  all magnitudes decay. (b) Bilayer configurations for $t=0$ (black) and
-  $t=1000$ (red) with particle directors. (c)--(d) show the fluid
-  pressure profiles for $t=0$ and $t=1000$ where the background curves
-  indicate the streamlines. In panel (c), the pressure value in internal
-  fluid is much higher than the pressure outside of the bilayer. After
-  the JP vesicle relaxes, this immersed permeable bilayer approaches the
-  steady state shown in panel (d).}
+\caption{\label{figure2} 
+  In JP vesicles, tension and pressure relax as fluid is expelled 
+  through the particle interstices. 
+  In panel (a), the thin curve plots the mean of the norm of the particle translational velocities.
+  The thick curve plots the mean of the absolute value of the particle angular velocities.  
+  At $t = 0$ $\upmu$s, the vesicle has a constant internal pressure 0.05~pN nm$^{-1}$ (red color, panel (b)).
+  In panel (c),  pressure has dissipated and the vesicle has moved from its initial configuration (gray circles), to the equilibrium configuration
+  (black circles).  The data in panels (d) and (e) support the linear relationship expressed by 
+  \eqref{eq:LaplacePressure} and \eqref{eq:perm}.
+  Circles are for a vesicle with 17 nm initial radius;
+  square are for a 34 nm initial radius.  Asterisks are for 
+  a 18 nm initial radius but with smaller, 1.25 nm diameter particles. 
+  In panel (f), the theoretical time course  \eqref{eq:perm_solution} overlaps the data 
+  using constants $K_A$ and $P$ derived from panels (d) and (e). }
 \end{figure}
-
-\begin{figure}
-  \caption{\label{figure:permeability} JP vesicles are suspended in a
-  quiescent flow for relaxations where the reference arc lengths $L_0$
-  are $107$ nm, $218$ nm, and $141$ nm with particle diameters $2.5$ nm,
-  $2.5$ nm, and $1.25$ nm, respectively. (a) The arc length $L$
-  decreases over time where the dashed curves represent the data and
-  solid curves are linear fits; (b) A linear relationship between
-  $R\Delta p$ and the relative difference $L/L_0-1$; (c) A linear
-  relationship between aqueous flux $dA/dt$ and $L\Delta p$. For panels
-  (b) and (c), the cross and asterisk symbols are numerical results and
-  fitted by using solid lines.}
-\end{figure}
-
-Figures~\ref{figure2}c and~\ref{figure2}d demonstrate that the initial, non-equilibrium configuration has a large internal fluid pressure
-that vanishes as the configuration tends toward the equilibrium state.  
-This suggests that the initial collection of JP is under tension and
-this tension is relaxed as fluid is expelled through the inter-particle
-spacing. To make a comparison with membrane continuum mechanics, lipid
-bilayer membranes have a large area modulus $K_A$ of about $240$ pN
-nm$^{-1}$ \cite{NAGLE} and changes in surface area give rise to a
+Finally, we show that the JP bilayer behaves as an extensible, permeable membrane. 
+Figures~\ref{figure2}b shows an initial, non-equilibrium JP vesicle suspended in a quiescent flow $\uu_{\infty} = 0$.
+The color map plots the pressure $p$. The red color in Figures~\ref{figure2}b 
+shows a constant, positive internal pressure (0.05~pN nm$^{-1}$)
+and the white shows a constant zero, external pressure.  
+There is some fluid flow and the pressure vanishes as the configuration tends toward the equilibrium state (Figures~\ref{figure2}c).
+
+What could be the source of this drop in pressure?
+In continuum membrane mechanics, changes in surface area give rise to a
 membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
 membrane surface area and $A_0$ is the reference surface area in the
-non-tensed state. In the two-dimensional vesicles, the tension becomes
+The area modulus $K_A$ of bilayers is about $240$ pN nm$^{-1}$ (\cite{NaTr00}).
+In the two-dimensional vesicles, the tension becomes
 \begin{align}
@@
 where $L$ and $L_0$ are the vesicle arc length and resting length,
-respectively. A stretched, circular vesicles has a Laplace pressure 
+respectively. Moreover, stretched, circular vesicles has a Laplace pressure 
 \begin{align}
@@
 where $\Delta p$ is the difference in internal pressure to the pressure
-at infinity and $R$ is the radius of the circular vesicle. The factor
-$R^{-1}$ is the total curvature since the principle curvature in the
-direction of the cylinder is zero.
+at infinity, $R^{-1}$ is the total curvature of the circular cylinder.
+
+Figure~\ref{figure2}c plots the data for the pressure jump
+$\Delta p$ between the particle center and the far-field (see Figures~\ref{figure2}c and~\ref{figure2}d).
+We use $R = L/(2\pi)$ for the vesicle radius, and the horizontal axis is the relative stretch.
+The circles are data for a vesicle with radius 17 nm. The linear fit (solid lines) shows that 
+$R\Delta P$ is proportional to the relative stretching $L/L_0 - 1$.
+The squares are for a vesicle with twice the radius 34 nm, and the data overlap 
+supports that the proportionality constant $K_A$ is a stretching modulus that is independent of vesicle size.
+The data give $K_A = 170 \pm 9$ pN nm$^{-1}$ which is good agreement with the 
+area moduli of lipid bilayer as determined by experiment. 
+To evaluate how changes to particle size lead to different physical properties,
+the asterisk symbols are for an 18 nm radius vesicle
+consisting of particles with diameter 1.25 nm, instead of the usual 2.5 nm.
+These data give smaller stretching modulus of $K_A = 102$~pN~nm$^{-1}$.
 
@@
 repulsive forces. The gaps allow for some fluid flux across the JP
-bilayer. In membrane mechanics, aqueous flux is quantified the equation
+bilayer, which can be quantified by the equation
 \begin{align}
@@
 qua-gan-you2021}).
-
-The JP vesicle data is in complete agreement with the continuum
-mechanical model~\eqref{eq:stretch}--\eqref{eq:perm}. In
-Figure~\ref{figure:permeability}, we considered three configurations: a
-configuration with 58 particles ($L_0 = 107$ nm, plus symbols); a
-configuration with 119 particles ($L_0 = 218$ nm, asterisk symbols); and
-finally a configuration with 117 particles but with diameter 1.25 nm
-rather than the usual 2.5 nm ($L_0 = 141$ nm, times symbols). Here $A$
-and $L$ refer to the area and length of the mid plane curve separating
-the inner and outer monolayers. The values for $L_0$ are the asymptotic
-values for $L$ in Figure~\ref{figure:permeability}c.
-
-Figure~\ref{figure:permeability}a plots the data for the Laplace
-pressure relationship \eqref{eq:LaplacePressure}. The pressure jump
-$\Delta p$ is the pressure at the particle center minus the far-field
-pressure (see Figures~\ref{figure2}c and~\ref{figure2}d), $R = L/2\pi$
-is the vesicle radius, and the horizontal axis is the relative stretch.
-The solid lines are linear fits, showing that for circular JP vesicles,
-$R\Delta P$ is essentially proportional to the relative stretching
-$L/L_0 - 1$. The proportionality constant is the same for the 58 and 119
-particle cases where the diameters are the same, suggesting that the
-stretching modulus $K_A$ of JP bilayers is independent of the number of
-particles. The 117 particle case had diameters 1.25 nm and this data set
-results in a smaller stretching modulus of $K_A = 102$~pN~nm$^{-1}$. The
-interpretation is that changes to particle size, while keeping $\rho$,
-$M$, and $\rho_0$ fixed, lead to different physical properties.
-
-Furthermore, Figure~\ref{figure:permeability}b and shows that $L\Delta
-P$ is proportional to $\frac{dA}{dt}$ in accord with \eqref{eq:perm}.
-The slopes of the linear fits give the hydraulic permeability
-coefficient $P$. The data provide $P = 0.0296$ nm$^3$ ns$^{-1}$
-pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 58 and 119
-particle cases, respectively. These values suggest that the JP bilayer
-permeability is independent of particle number, as was the case for the
-stretching modulus. The permeability for the 117 particle number is
-0.0566 nm$^3$~ns$^{-1}$~pN$^{-1}$. The increase in the permeability is
-caused by the hydrophobic attraction vanishing with particle size,
-leading to larger gaps between the particles for the same repulsion. The
-hydraulic permeability we calculate, however, is not in agreement with
+Figure~\ref{figure2}e shows that the data for 
+$L\Delta p$ and $dA/dt$ obey the linear relationship expressed by \eqref{eq:perm}.
+The slopes of the linear fits give the hydraulic permeabilities $P = 0.0296$ nm$^3$ ns$^{-1}$
+pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 17 nm and 34 nm radius 
+cases, respectively.   
+Like  the area modulus, permeability is independent of vesicle size.
+The hydraulic permeability we calculate, however, is not in agreement with
 experimentally derived values and is larger by a few orders of
-magnitude. This discrepancy is perhaps due to inter-particle distance of
-the JP being relatively large to the inter-molecular spacing of lipids
-in real bilayers. In future studies, we can test this hypothesis be
-changing the repulsion strength and length for example.
+magnitude.
+
+We suspect this discrepancy is due to inter-particle distance of
+the JP being large compared to the inter-lipid spacing in real bilayers. To test this, we calculate the
+permeability for the particles with diameter 1.25 nm. 
+Due to their smaller size but fixed repulsion strength, these particles have a larger inter-particle spacing 
+resulting in an increase in permeability, $P = 0.0566$~nm$^3$~ns$^{-1}$~pN$^{-1}$ (Figure \ref{figure2}e, asterisk symbols).
 
@@
 quantitative agreement with the JP data for
-(Figure~\ref{figure:permeability}c).
+(Figure~\ref{figure2}f).
 
@@
 \end{center} 
-  \caption{\label{figure9} The shape and trajectories of two
-  JP vesicles suspended in a shear flow. The moving paths of the two
+  \caption{\label{figure9} Two JP vesicles suspended in a shear flow
+  interact by orbiting about the origin. The moving paths of the two
   centroids are plotted in blue and red. The centroids are initially
-  located on the $x$-axis. For simulation time, $t = {0, 400,800,1200}$
-  for (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).
-  The fluid velocity profile is plotted in the background.
+  located on the $x$-axis.  The fluid velocity streamlines appear in grey.
+  The dimensionless shear rate is $\chi=0.005$.
   }
@@
 %\includegraphics[height=2in]{N116_shear_7500.pdf}
-  \caption{\label{figure10} Two JP vesicles suspended in a shear flow
-  where the dimensioneless shear rate is $\chi=0.005$. The initial
-  configuration is shown in panel (a). Panels (b)-(d) represent configurations when $t = \{500, 1000, 1500\}$.
-  The background color is the fluid
-  pressure. The color bar is identical for all panels. Streamlines are
-  plotted in purple. The insets of all panels are generated from
-  simulations of a continuum model of the vesicles and the streamlines
-  agree between the two models. }
+  \caption{\label{figure10} 
+  The figure is for the same simulation as in Figure~\ref{figure9}, 
+  but also plots the fluid pressure $p$. The color bar is identical for all panels. 
+  Internal pressure is initially zero, but then grows as the vesicles come close to contact  (panel (c)).
+  The insets are generated from simulations of a continuum model of the vesicles (\cite{qua-vee-you2019}). 
+  The streamlines of the two models are in agreement.}
 \end{figure}
@@
 \subsubsection{Shear Flow}
-
+Finally, we can study vesicle-vesicle interactions in background flows. 
 Figure~\ref{figure9} shows the simulation of two JP vesicles suspended
 in a shear flow with shear rate $\chi=0.005$. We duplicate the
-pre-relaxed $58$-body JP vesicle from previous sections to construct the
-initial configuration shown in Figure~\ref{figure9}(a). The two centers
-of mass are at $(-10,0)$ and $(10,0)$. In all panels, the blue and red
+pre-relaxed $58$-body JP vesicle from previous sections and construct the
+initial configuration shown in Figure~\ref{figure9}a. The two centroids
+are at coordinates $(-25,0)$ and $(25,0)$ in nm. In all panels, the blue and red
 curves show the trajectory of the two JP vesicle centroids. They have
-nearly completed a full period by $t=4000$. We also observe an adhesive
+nearly completed a full period by $t=4$ $\upmu$s.
+
+We show snapshots of the fluid pressure in Figure~\ref{figure10}. Since the
+initial JP vesicles are pre-relaxed, there is initially no pressure jump
+between the internal and external fluids (panel (a)). Panels (b)--(d)
+show the configurations when $t = \{0.5,1,1.5\}$ $\upmu$s, and the
+streamlines are plotted in the background for all panels. 
+We include the numerical results from a continuum model in all insets and these
+comparisons give a qualitative agreement between two models.
+We also observe an adhesive
 effect between the two JP vesicles that is set up by the hydrophobic
-interactions and repulsive force. Similar dynamics have been observed
-between a pair of adhering vesicles in a shear flow
+attraction (Figure~\ref{figure10}c). Similar dynamics have been observed between a pair of adhering vesicles in a shear flow
 (\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
 behavior is absent when two JP vesicles are well-separated.
-
-Snapshots of the fluid pressure are in Figure~\ref{figure10}. Since the
-initial JP vesicles are pre-relaxed, there is initially no pressure jump
-between the internal and external fluids (panel (a)). Panels (b)--(d)
-show the configurations when $t = \{500,1000,1500\}$, and the
-streamlines are plotted in the background for all panels. We include the
-numerical results from a continuum model in all insets and these
-comparisons give a qualitative agreement between two models.
 
@@
 \end{center} 
-  \caption{\label{figure11} Two JP vesicles suspended in
-  an extensional flow. The moving paths of the two centroids are plotted
+  \caption{\label{figure11} 
+  The initial placement of two JP vesicles suspended in
+  an extensional flow affects the long-time dynamics.  
+  The moving paths of the two centroids are plotted
   in blue in red. Each row corresponds to a different initial placement
-  of the JP vesicles. The flow rate is $\chi = 0.005$ in all cases.
+  of the JP vesicles. 
   (i) Both JP vesicle centroids are on the $x$-axis. (ii) The
-  centroid of the left JP vesicle is $0.1$ units above the $x$-axis
+  centroid of the left JP vesicle is $0.25$ nm above the $x$-axis
   and the right JP vesicle is on the $x$-axis. (iii) The centroid of
-  the left JP vesicle is $0.1$ units above the $x$-axis and the right
-  JP vesicle is $0.1$ units below the $x$-axis. (iv) The centroid of
-  the left JP vesicle is $0.5$ units above the $x$-axis and the
-  centroid of the right JP vesicle is $0.5$ units below the $x$-axis.
-  Figure~\ref{figure12} presents the numerical results from the case
-  (iii).  The fluid velocity profile is plotted in the background.}
+  the left JP vesicle is $0.25$ nm above the $x$-axis and the right
+  JP vesicle is $0.25$ units below the $x$-axis. (iv) The centroid of
+  the left JP vesicle is $1.25$ nm above the $x$-axis and the
+  centroid of the right JP vesicle is $1.25$ nm below the $x$-axis.
+  The streamlines appear in grey and 
+  the flow rate is $\dot \gamma =0.005$ ns$^{-1}$ in all cases.}
 \end{figure}
@@
 %\includegraphics[height=2in]{N116_ext_6500.pdf}
-  \caption{\label{figure12} Two JP vesicles suspended in an
-  extensional flow where the dimensioneless extensional rate is
-  $\chi=0.005$. The centroid of the left JP vesicle is $0.1$ units
-  above the $x$-axis and the centroid of the right JP vesicle is
-  $0.1$ units below the $x$-axis. The initial configuration is shown in
-  panel (a). Panels (b)-(d) represent configurations when $t = \{400, 800, 1300\}$. 
-  The background color is the fluid pressure. The color bar
-  is identical for all panels. Streamlines are plotted in purple. The
-  insets of all panels are generated from simulations of a continuum
-  model of the vesicles and the streamlines agree between the models.}
+  \caption{\label{figure12} The figure is for the simulation case (iii) of Figure~\ref{figure11},
+  and additionally plots the pressure $p$.  The color bar is shared by all panels. 
+  The insets of all panels are generated from simulations of a continuum
+  model of the vesicles and the streamlines agree between the two models.}
 \end{figure}
@@
 
-Using a similar setup to the shear case, we suspend the same two
-pre-relaxed $58$-body JP vesicles and consider their dynamics in an
-extensional flow with extensional rate $\chi=0.005$. This extensional
-flow is stretching in the $y$ direction and squeezing in the $x$
-direction. Figure~\ref{figure11} shows how the initial placement of the
+Using a similar setup to the shear flow case, we suspend the same two,
+pre-relaxed, $58$-body JP vesicles and consider their dynamics in an
+extensional flow 
+\begin{equation}
+\uu_{\infty}(\xx) = \dot \gamma ((\mathbf{e}_x \cdot \xx)\mathbf{e}_x -  (\mathbf{e}_y \cdot \xx)\mathbf{e}_y)
+\end{equation}
+with extensional rate $\dot \gamma =0.005$ ns$^{-1}$. This extensional
+flow is stretching in the $y$-direction and squeezing in the $x$-direction. 
+Figure~\ref{figure11} shows how the initial placement of the
 JP vesicles affects the dynamics. When two centroids are both placed
-symmetrically on the $x$-axis (case (i)), the JP vesicles reach a steady
+symmetrically on the $x$-axis (case (i)), the JP vesicles come into contact and reach a steady
 equilibrium. If one centroid is placed above the $x$-axis (case (ii)),
@@
 Figure~\ref{figure12} shows numerical results when the centroids of the
-two Janus particles are placed at $(-10,-0.1)$ and $(10,0.1)$ (case
+two Janus particles are placed at $(-10,-0.1)$ nm and $(10,0.1)$ nm (case
 (iii) from Figure~\ref{figure11}). With this setup, the two JP vesicles
@@
 separation. The short-range repulsion plays an important role to avoid
-structure collisions.
+particle collisions.
 %and this result can be

### 2021-09-27 doc/main_jfm.tex
yny tex
update table
corrected table
final language/figure edit; b coeffs need double checking

@@
 \begin{abstract}
-  We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
-  In this work, we study the dynamics of many-body systems immersed in a
-  viscous fluid with a specified interparticle force. In particular, we
-  apply a hydrophobic attraction potential (HAP) using a Janus type
-  granular system to model lipid bilayer membranes. Coupling with an
-  efficient integral equation method for rigid bodies in Stokes flow and
-  a previous developed HAP solver, the deformations of a two-dimensional
-  vesicle such as tank-treading motion and membrane ruptures can be
-  observed under different values of the shear rate. Moreover, an
-  efficient integral equation method is adopted for solving the screened
+  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic particles suspended in a viscous background flow. 
+  The interparticle force comes from a specific hydrophobic attraction potential (HAP)
+  that has been shown to model lipid bilayer membranes. 
+  We adopt an   efficient integral equation method for solving the screened
   Laplace equation and the mobility problem where it can accurately
   calculate hydrophobic and hydrodynamic interactions between near
-  touched boundaries.
+  touched boundaries.    Under a linear shear flow,  we observe the tank-treading deformation
+  in a two-dimensional  vesicle for various values of the shear rate.
+  The results yield measurements 
+  of inter-monolayer friction and membrane permeability. Large shear rates lead to membrane rupture. 
+  The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
+  interactions in shear and extensional flows.
+%    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
+%  In this work, we study the dynamics of many-body systems immersed in a
+%  viscous fluid with a specified interparticle force. In particular, we
+%  apply a hydrophobic attraction potential (HAP) using a Janus type
+%  granular system to model lipid bilayer membranes. Coupling with an
+%  efficient integral equation method for rigid bodies in Stokes flow and
+%  a previous developed HAP solver, the deformations of a two-dimensional
+%  vesicle such as tank-treading motion and membrane ruptures can be
+%  observed under different values of the shear rate. Moreover, an
+%  efficient integral equation method is adopted for solving the screened
+%  Laplace equation and the mobility problem where it can accurately
+%  calculate hydrophobic and hydrodynamic interactions between near
+%  touched boundaries.
 \end{abstract}
@@
 \section{\label{intro}Introduction}
-Described by de Gennes as ``another animal in soft matter physics", the
-Janus particle (often a spherical particle with a hydrophobic and a
-hydrophilic hemisphere) exhibits complex aggregate, clustering, and
+Described by physicist Pierre-Gilles de Gennes as ``another animal in soft matter physics", the
+Janus particle--often a spherical particle with a hydrophobic and a
+hydrophilic hemisphere--exhibits complex aggregate, clustering, and
 self-assembly into mesoscopic and macroscopic structures that are
-relevant to a wide range of applications in biology and bioengineering.
+relevant to a wide range of applications in biology and bioengineering (\cite{deGennes1991}).
 Whether it is surface chemistry or polarity under an external field, the
@@
 
-Recently~\cite{Fu20}
-illustrated that the hydrophobic interactions between Janus particles in
-a viscous solvent can be used as a coarse-grained model to capture the
-mechanics of an elastic bilayer membrane of amphiphilic macromolecules
-such as lipids. Depending on the total number of Janus particles and
-their geometry, in a viscous solvent, Janus particles can aggregate to
-form a micelle, a patch of bilayer membrane with open ends, and a
-self-enclosed bilayer membrane (referred to as a JP vesicle). Using a
-hybrid continuum model for the interactions between amphiphilic
-particles in a viscous solvent and with a boundary integral
-formulation,~\cite{Fu20} showed that the membrane granularity during
-fusion and fission of bilayers can be accurately captured. 
-%This boundary integral formulation has inspired more recent work
-
-In molecular dynamics (MD) simulations, the lipid bilayer membranes are
-often approximated by an implicit solvent coarse-grained model for
-lipids (as in the Martini code), where their hydrodynamic interactions
-are simplified by an implicit solvent. The long-range hydrodynamic
-interactions and the induced long-range lipid interactions can be
-captured by combining the Dry Martini with a lattice Boltzmann MD.
-\cite{Brandner2019} used this methodology to simulate the hydrodynamics
-of a nano-sized vesicle under a shear flow, and reproduced the well-know
-vesicle hydrodynamics such as tank-treading, tumbling, and inter-leaflet
-slippage (reported from simulations of the Helfrich-type continuum
-model).
-
-In this work we extend the hybrid continuum model in~\cite{Fu20} for the
-Janus suspension to incorporate the collective hydrodynamics of a Janus
-suspension under various flows: a linear shear flow, an elongation flow,
-and a Poiseuille flow. We demonstrate that a JP vesicle behaves like
-a vesicle in these flowing conditions. In particular, we show that a
-JP vesicle undergoes tank-treading in a shear flow and vertical
-migration in a Poiseuille flow. Furthermore we use the hybrid continuum
-model to investigate the inter-leaflet slippage and rupture of a bilayer
-membrane due to an imposed flow. Finally, we compare a pair of
-interacting JP vesicles with a continuum model of a pair of vesicles.
-
-We require a numerical method to avoid unphysical contact between rigid
-Janus particles. Optimization-based contact methods introduce
-constraints, such as enforcing a non-positive space-time interference
-volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
-methods do not introduce stiffness, but potentially expensive nonlinear
-complementarity problems must be solved at each time step.
-Repulsion-based contact methods, which we employ, introduce an
-artificial repulsion force that increases in strength as two particles
-approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
-kab-qua-bir2018}). Strong repulsion forces can introduce numerical
-stiffness, but with the presence of the hydrophobic forces, we maintain
-contact-free suspensions with a relatively weak non-stiff repulsive
-force.
-
-This paper is organized as follows. In \S~\ref{sec:governing_eqs} we
-present the formulation for the Janus particles in a viscous fluid in
-the zero-Reynolds number regime. In \S~\ref{sec:IEM} we extend the
-hybrid continuum model for a Janus suspension to include the effects of
-a far-field flow via the mobility problem formulation. In
-\S~\ref{results} we validate our model and present simulation results
-for a single and pair of JP vesicles under various flowing conditions.
-Finally we provide discussion and outlook for future directions in
-\S~\ref{conclusion}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
+
+Recently,~\cite{Fu20}
+illustrated that the hydrophobic interactions between Janus particles (JP) in
+a viscous solvent can be used as a coarse-grained model to capture the
+mechanics of an elastic bilayer membrane of amphiphilic macromolecules
+such as lipids. Depending on their total number and
+geometry, JP suspensions can aggregate to
+form a micelle, a patch of bilayer membrane with open ends, and a
+self-enclosed bilayer membrane, referred to as a JP vesicle. Using a
+hybrid continuum model for the interactions between amphiphilic
+particles in a viscous solvent and with a boundary integral
+formulation,~\cite{Fu20} showed that the granularity of membrane remodeling, 
+as occurs during fusion and fission of bilayers,
+can be accurately captured by the coarse-grained model.  
+%This boundary integral formulation has inspired more recent work
+
+In the present work, we extend the hybrid continuum model in~\cite{Fu20} for the
+Janus suspension to incorporate the collective hydrodynamics of a Janus
+suspension under various flows. The JP vesicles in our simulations replicate  
+well-know vesicle hydrodynamics such as tank-treading and inter-leaflet
+slippage in a shear flow and migration in Poiseuille flow from continuum models. Furthermore we use the hybrid continuum
+model to investigate permeability and rupture of a bilayer
+membrane due to an imposed flow. 
+Finally, we compare a pair of
+interacting JP vesicles with a continuum model of a pair of vesicles.
+
+\cite{Brandner2019} used the coarse-grained force field with a lattice Boltzmann molecular dynamics to simulate the hydrodynamics
+of a nano-sized vesicle under a shear flow.  
+In MD simulations, the hydrodynamic interactions 
+for the solvent phase are often approximated by an implicit solvent coarse-grained model.
+In the present work, the hydrodynamic interactions come from the mobility problem
+for the Stokes equations for the incompressible, viscous solvent.
+
+We require a numerical method to avoid unphysical contact between rigid
+Janus particles. Optimization-based contact methods introduce
+constraints, such as enforcing a non-positive space-time interference
+volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
+methods do not introduce stiffness, but do require solving potentially expensive nonlinear
+complementarity problems at each time step.
+Repulsion-based contact methods, which we employ, introduce an
+artificial repulsion force that increases in strength as two particles
+approach one another (\cite{glo-pan-hes-jos-per2001, fen-mic2004,
+kab-qua-bir2018}). Strong repulsion forces can introduce numerical
+stiffness, but with the presence of the hydrophobic forces, we maintain
+contact-free suspensions with a relatively weak non-stiff repulsive
+force.
+
+The paper is organized as follows.  In \S~\ref{sec:governing_eqs} we
+present the formulation for the Janus particles in a viscous fluid in
+the zero-Reynolds number regime (Figure \ref{fig:figure0}a). 
+In \S~\ref{sec:IEM} we extend the
+hybrid continuum model for a Janus suspension to include the effects of
+a far-field flow via the mobility problem formulation. In
+\S~\ref{results} we validate our model and present simulation results
+for a single JP vesicle (Figure \ref{fig:figure0}d) and for a pair of JP vesicles (Figure \ref{fig:figure0}e) 
+under various flowing conditions.
+Finally we provide discussion and outlook for future directions in
+\S~\ref{conclusion}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   \caption{\label{figure4}
- JP vesicles loose enclosed area and conserve length in shear flow. 
+ JP vesicles lose enclosed area but conserve length in shear flow. 
   Panel (a) gives the reduced area over time
-  for four different shear rates. The smooth curves are a best-fit
-  exponential curve. There is commensurate increase in excess length (panel (b)), 
-  but the arc length of the mid plane curve is more or less constant.   
-   The legend in panel (b) applies to panels (a)--(c).
-  Panel (d) plots the steady-state reduced area and the decay rate $k$ (inset) using the exponential fit
-  to the data in panel (a). }
+  for four different shear rates. The monotonic curves are a 
+  two-exponential best fit. There is a commensurate increase in excess length (panel (b)), 
+  but the arc length of the mid plane curve is more or less constant for all shear rates  (panel (c)).
+  The inset in panel (c) is for shear rate 0.003. The legend in panel (b) applies to panels (a)--(c).
+  Panel (d) plots the steady-state reduced area and the decay rate $k_2$ (inset) coming from the fitting
+  data in panel (a). }
 \end{figure}
@@
 (\cite{Finken08, Shaqfeh11}).
-The centroid of the baseline $58$-body JP vesicle lies at the origin 
+The centroid of the baseline, $58$-body JP vesicle lies at the origin 
 and the background shear flow 
@@
 and $\mathbf{e}_y$ for the horizontal and vertical directions, respectively.
-We use the dimensionless shear rate $\chi = \dot \gamma$ ns.
+We use the dimensionless shear rate $\chi = \dot \gamma$ (s$^{-1}$) ns.
 
@@
   There is inter-monolayer slip present in the JP vesicle tank-treading motion at all shear rates.  
-  Panel (a) tracks the angle  $\theta(t)$ between a pair of particles (blue and yellow) with respect to
-  the JP vesicle centroid. The shear rate is $\chi=0.005$ and in the right figure, the yellow particle
+  Panel (a) tracks a pair of particles (blue and yellow). 
+  The shear rate is $\chi=0.005$ and in the right figure, the yellow particle
   will complete two and a quarter revolutions in the same time the blue particle completes two revolutions.
-  The curves in panel (b) are the mean change in angle for various shear rates. 
-  Slip velocity generally increases with shear rate but 
-  we have marked two outliers (times symbols). }
+  The curves in panel (b) are the distance the outer leaflet has slid past the inner leaflet. 
+  The slopes of the curves gives the slip velocity. 
+  With the exception of $\chi = 0.0035$, slip velocity is generally monotonic in the shear rate. }
 \end{figure}
@@
 Under the background flow, the rigid-body boundary condition \eqref{eq:rigid_bc} causes the 
-particle suspension to stretch apart. This perturbation  
+particle suspension to elongate. This perturbation  
 disrupts the preferred particle orientations and exposes the hydrophobic core to bulk water (Figure~\ref{figure3}, red region).
@@
 To extract physical quantities, 
-let $A^* = 4\pi A/L^2$ be the reduced area and $\Delta=L/\sqrt{A^*/\pi}-2\pi$ the excess length of the bilayer
+let $A^* = 4\pi A/L^2$ be the reduced area and $\Delta=L/\sqrt{A/\pi}-2\pi$ the excess length of the bilayer
 structure (\cite{Finken08}).
@@
 We conclude that the JP vesicle loses area and that the bilayer behaves as a permeable membrane.
-Due to granularity, the tank-treading motion has some wobble and this is the source
-of the oscillations in the panels of Figure~\ref{figure4}.
 
@@
 decreases from an initial value close to $1$ and tends to a steady-state value $A^*_{\infty}$. 
-The curves in panel (a) are fit of the exponential model $A^* = A^*_{\infty} + (1-A^*_{\infty}) \exp(-kt)$.
-Panel (d) shows that $A^*_{\infty}$ decreases with shear rate, 
-and that reduced area converges to a steady state earlier when the shear rate is lower (inset).
+The data in panel (a) are fit by the model 
+$A^* = (A^*_{\infty}-a_1-a_2) + a_1 \exp(-k_1t) + a_2 \exp(-k_2t),$ $0 < k_2 < k_1$.
+Panel (d) shows that $A^*_{\infty}$ decreases with shear rate. 
+The JP vesicle achieves a steady-state reduced area 
+earlier when the shear rate is low (inset), but the decay rate $k_2$ is more or less constant for higher shearer rates.
+
+The oscillations in the data of Figure~\ref{figure4} are due to the
+granularity of the JP vesicle. 
+The inset of Figure~\ref{figure4}c zooms in on the arc length data for the shear rate $\chi = 0.003$.
+It shows that the oscillations are smooth and well-resolved by our second-order Adams-Bashforth scheme.
 
@@
 correspond to shear rates $\dot \gamma = O(10^6$ s$^{-1}$) 
-which gives fluid velocities like m s$^{-1}$ in the vicinity of the  vesicle.  
-While seemingly large, these values are consistent with prior MD studies (\cite{Brandner2019})
-and are a consequence of the fact that the magnitude of elastic membrane stresses grows inversely 
-with the vesicle radius; larger shear rates are required to produce the viscous stresses needed to 
+which gives fluid velocities O(m s$^{-1}$) in the vicinity of the  vesicle.  
+While large, these values are identical to ones used in prior MD studies (\cite{Brandner2019})
+and are a consequence of the fact that larger shear rates are required to produce the viscous stresses needed to 
 appreciably deform smaller vesicles.
@@
 We observe inter-monolayer slip in the tank-treading, JP vesicle at all shear rates. 
-The two leaflets of the vesicle are not bound together, but rather are able to slide 
+Since they are not bound, the two leaflets of the vesicle are able to slide 
 past one another. This sliding is limited by viscous friction of the aqueous gaps between particles
@@
 
-Figure~\ref{figure5}a illustrates the process by tracking the angle $\theta(t)$
-between two particles, one blue and the other yellow, relative to the vesicle centroid. 
-It is clear from the growth in angle that the outer leaflet has a tangential velocity that is larger  
-then that of the inner leaflet.  
-Figure~\ref{figure5}b plots the mean, particle-pair angle for various shear rates. 
-It suggests that the inter-monolayer slip velocity generally increases with shear rate.
-
-From the data, we are able to define an inter-monolayer friction coefficient  
+Figure~\ref{figure5}a illustrates the process by tracking the distances traveled 
+by a pair of particles. 
+In the left image, the blue and yellow particle lie next to each other. 
+In the right-most panel, the yellow particle has traveled further than the blue particle. 
+This suggests that the tangential velocity of the outer leaflet is larger than that of the inner leaflet.
+The difference in their velocities is the slip velocity $U(t)$  and $s(t) = \int_0^t dU $ records the distance
+one leaflet has slid past the other.
+
+Figure~\ref{figure5}b plots the sliding distance for various shear rates. 
+From the data, we define an inter-monolayer friction coefficient  
 \begin{align}
@@
 $\langle \cdot \rangle$ denotes the time average. 
-To measure inter-monolayer slip $U$, we compute the mean tangential velocity of the particles in the outer monolayer
-and subtract from it the mean tangential velocity of the particles in the inner monolayer. 
-To calculate the tangential force jump $F$, we let 
+We define the tangential force jump $F$ to be the tangential shear force on the outer leaflet minus the tangential shear force on the inner leaflet. 
+However, it does not make sense to integrate along a curve passing through the particles.  
+To calculate the tangential force jump $F$, we instead let 
 \begin{equation}
@@
 where $C_M^+$ and $C_M^-$ are target curves obtained by moving the midplane curve $C_M$ (Figure~\ref{figure5}a)
-a distance $h$ along the outward, respectively inward, unit normal.  Actually, we calculate $F_h$ for several values of $h$ 
-and then define $F$ to by extrapolating to zero distance giving a jump in tangential shear force across the midplane.
+a distance $h$  outward, respectively inward, along the unit normal.  
+We sample $F_h$ for $h = \pm 1.5, \pm 2.5, \pm 3.5$ times the particle radius 
+and define $F$ by extrapolating to zero distance.
 
@@
 \begin{tabular}{c c c c c c c c }
- $\chi$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
+ $\dot\gamma$  (ns$^{-1}$) & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
 \hline                    
-$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
+%$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
 %$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
 %$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
-$b$ (pN$\cdot$ns nm$^{-3}$)    & 0.22 & 0.87*  & 0.22 &0.21 & 1.29* & 0.31 & 0.30\\ 
+%$b$ (pN$\cdot$ns nm$^{-3}$)    & 0.22 & 0.87*  & 0.22 &0.21 & 1.29* & 0.31 & 0.30\\ 
+$b$ (pN$\cdot$ns nm$^{-3}$)    & 1.01 & 3.40 &   3.70  &   5.01 &   5.38  &   5.75  &   6.25 \\ 
 \hline    
@@
 several shear rates. The coefficients generally lie within the
-range 0.2 to 0.3 pN ns nm$^{-3}$ which is in good quantitative agreement with
+range 1 to 6 pN ns nm$^{-3}$ which is in good quantitative agreement with
 values previously reported in the literature (\cite{sch-vla-mik2010}
-and~\cite{denOtter2007}).  
-The data contain two outliers (Table~\ref{table1}, * symbol).
-These correspond to the two outliers in the slip velocities (Figure~\ref{figure5}b, times symbol). 
-We suspect that due to the finite particle size, the granular wobble of the tank-treading motion is more prominent for some
-shear rates, causing some slip velocities to be lower than expected.
+and~\cite{denOtter2007}).  \cite{denOtter2007} give  
+$b = 2.4 \times 10^6$ Pa m$^{-1}$ s = 
+2.4 pN nm$^{-3}$ ns from their MD study, for example.
 
@@
   The thick curve plots the mean of the absolute value of the particle angular velocities.  
-  At $t = 0$ $\upmu$s, the vesicle has a constant internal pressure 0.05~pN nm$^{-1}$ (red color, panel (b)).
+  At $t = 0$ $\upmu$s, the vesicle has a spatially constant internal pressure 0.05~pN nm$^{-1}$ (red color, panel (b)).
   In panel (c),  pressure has dissipated and the vesicle has moved from its initial configuration (gray circles), to the equilibrium configuration
@@
 
-In \cite{Fu20} a mathematical model is developed to quantify the macroscopic assembly and mechanics of 
+\cite{Fu20} developed a mathematical model to quantify the macroscopic assembly and mechanics of 
 a JP bilayer in a viscous solvent. 
-The interactions between JPs are formulated as a second-kind integral equation, which is coupled to the incompressible Stokes equations for the surrounding incompressible fluid at the zero-Reynolds-number limit.
-Numerical simulations of a JP suspension reveal self-assembly of JPs into micelles and bilayers, and also provide an alternative means for computing the mechanical moduli of a JP membrane, which often requires the knowledge of an equation of state from experiments on a colloidal membrane~(\cite{Balchunas2019_SM}).
-In this study we used this integral formulation and numerical algorithm to simulate the hydrodynamics of JP vesicles. 
+The interactions between JP are formulated as a second-kind integral equation, 
+which is coupled to the Stokes equations for the surrounding incompressible fluid 
+at the zero-Reynolds-number limit.  
+Numerical simulations of a JP suspensions revealed self-assembly of JP into micelles 
+and bilayers, providing an alternative means for computing mechanical moduli, 
+which often requires the knowledge of an equation of state from experiments on a colloidal membrane~(\cite{Balchunas2019_SM}).
 %
@@
 
-In\S~\ref{subsec:calculating_force} we derived an alternative integral form for calculating the force and torque to avoid the singular integral evaluation. These alternative integrals allow us to 
-%
-%Our method requires
-%calculations of the hydrodynamic stress tensor, and these are used to
-%
-estimate the inter-monolayer friction, membrane permeability constant $P$ and the membrane
-stretching modulus $K_A$. 
-The inter-monolayer friction coefficient is determined by
-calculating the tangential friction force and slip velocities with
-respect to the bilayer mid-plane. The resulting friction coefficients are
-about an order of magnitude smaller than those reported
-by~\cite{denOtter2007}, and this discrepancy is partially due to the
-granularity of our model. In addition, the coarse-graining level of the
-JP vesicle has a much larger length scale than molecular dynamics
-simulations, and the repulsive force creates gaps between Janus
-particles where the error in slip velocities accumulates over time.
-
-Under a linear shear flow, we found a JP vesicle to exhibit elongation and tank-treading dynamics observed for a lipid bilayer GUV.
+In the present study, we used this integral formulation and numerical algorithm to simulate the hydrodynamics of JP vesicles
+in background flows. 
+Under 
+a linear shear flow, we found a JP vesicle to exhibit elongation and tank-treading 
+dynamics observed for a lipid bilayer GUV.
 %
@@
 %
-The reduced area $A^*$ decreases as the shear rate increases
-and we measure the equilibrium reduced area for various shear rates. The
-results show that the total length of a JP vesicle is conserved and the
-decay rate of the reduced area is independent of the shear rate values
-between $0.005$~ns$^{-1}$ and~$0.008$~ns$^{-1}$. Moreover, the proposed
-model can describe membrane rupture in high shear rates. Therefore, our
+The results showed that the reduced area $A^*$ decreases with shear rate 
+but that the total length of a JP vesicle is conserved.  The
+decay rate of the reduced area was independent of the shear rate values
+between $0.003$~ns$^{-1}$ and~$0.005$~ns$^{-1}$. Moreover, the proposed
+model describes membrane rupture in high shear rates. Therefore, our
 method can be applied to vesicles undergoing topological changes which
@@
 %
+
+%
+%Our method requires
+%calculations of the hydrodynamic stress tensor, and these are used to
+%
+We estimated the inter-monolayer friction $b$, membrane permeability constant $P$ and the membrane
+stretching modulus $K_A$. 
+The inter-monolayer friction coefficient was determined by
+calculating the tangential  shear force and slip velocities with
+respect to the bilayer mid-plane. 
+The range of friction coefficients are in agreement with values reported
+by~\cite{denOtter2007} in their MD study.  The coarse-graining level of the
+JP vesicle has a larger length scale than molecular dynamics
+simulations, and in the future convergence studies we will investigate 
+how physical properties like the friction coefficient and membrane permeability 
+depend on the particle shape and size.
 
@@
 %
-Similar to the hydrodynamics of a GUV in a Poiseuille flow~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}),
-the nano JP vesicle moves toward the center of the shear flow.
+Replicating the hydrodynamics of a GUV in a Poiseuille flow~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}),
+the JP vesicle moves toward the center of the shear flow.
 While the initial reduced area of the JP vesicle is $A^*
 \approx 1$, the equilibrium reduced area is $A^*=0.9$. 
-For the parameters we used in the simulation, the JP vesicle takes an asymmetric shape as it settles above the center of flow and exhibits tank-treading motion.
+For the parameters we used in the simulation, the JP vesicle takes on an 
+asymmetric, "slipper" shape as it settles above the center of flow and exhibits tank-treading motion.
 %A qualitative
@@
 %simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). 
-An
-interesting result of the JP vesicle is that $y$-coordinate of the
-centroid oscillates at a value slightly above the center of the
-Poiseuille flow. This may be caused by the granularity of the JP vesicle
-and choices of the model parameters.
+An interesting result contrast with continuum results is that the JP vesicle oscillates at a height slightly above the center of the
+Poiseuille flow.
 
@@
 
-We further simulate the hydrodynamics of  two JP vesicles, and draw comparison with simulation results of two vesicles described by the Helfrich
+We further simulated the hydrodynamics of  two JP vesicles,
+and drew comparisons with simulation results of two vesicles described by the Helfrich
 continuum model. A comparison of the vesicle shapes and the streamlines
@@
 observe a rotating behavior that is observed for models involving
-vesicle adhesion~(\cite{qua-vee-you2019}). The hydrophobic action and
-the repulsive potential lead to this adhesive effect when two JP
-bilayers are sufficiently close. We also perform four simulations of two
-JP vesicles suspended in an extensional flow. We vary the initial
-vertical displacement of the vesicles' centroids and obtain similar
-results to the continuum model.
+vesicle adhesion~(\cite{qua-vee-you2019}). 
+The hydrophobic attraction lead to this adhesive effect when two JP
+bilayers are sufficiently close. We also perform several simulations of 
+a pair of JP vesicles suspended in an extensional flow. By varying the initial
+vertical displacement of the vesicles' centroids, we can control for divergent trajectories and 
+obtain similar results to the continuum model.
+
+In \S~\ref{subsec:calculating_force}, we derived an alternative integral form for 
+calculating the force and torque to avoid the singular integral evaluation. 
+These alternative integrals allow us to accurately resolve trajectories over long times
+without having to rely on computationally expensive quadratures.
 
@@
 and this is critical to understand membrane diffusion. 
-Finally, a more physical boundary condition for the
-HAP model will allow us to draw comparisons between computational and
-laboratory experiments.
+Finally, a more physical boundary conditions for the 
+HAP model will allow us to draw comparisons between 
+computational and laboratory experiments.
 

### 2021-09-28 doc/main_jfm.tex
small changes througought

@@
 
-Recently,~\cite{Fu20}
-illustrated that the hydrophobic interactions between Janus particles (JP) in
-a viscous solvent can be used as a coarse-grained model to capture the
-mechanics of an elastic bilayer membrane of amphiphilic macromolecules
-such as lipids. Depending on their total number and
-geometry, JP suspensions can aggregate to
-form a micelle, a patch of bilayer membrane with open ends, and a
-self-enclosed bilayer membrane, referred to as a JP vesicle. Using a
-hybrid continuum model for the interactions between amphiphilic
-particles in a viscous solvent and with a boundary integral
-formulation,~\cite{Fu20} showed that the granularity of membrane remodeling, 
-as occurs during fusion and fission of bilayers,
-can be accurately captured by the coarse-grained model.  
+Recently,~\cite{Fu20} illustrated that the hydrophobic interactions
+between Janus particles (JP) in a viscous solvent can be used as a
+coarse-grained model to capture the mechanics of an elastic bilayer
+membrane of amphiphilic macromolecules such as lipids. Depending on
+their total number and geometry, JP suspensions can aggregate to form a
+micelle, a patch of bilayer membrane with open ends, and a self-enclosed
+bilayer membrane, referred to as a JP vesicle. Using a hybrid continuum
+model for the interactions between amphiphilic particles in a viscous
+solvent and with a boundary integral formulation,~\cite{Fu20} showed
+that the granularity of membrane remodeling, as occurs during fusion and
+fission of bilayers, can be accurately captured by the coarse-grained
+model.  
 %This boundary integral formulation has inspired more recent work
 
-In the present work, we extend the hybrid continuum model in~\cite{Fu20} for the
-Janus suspension to incorporate the collective hydrodynamics of a Janus
-suspension under various flows. The JP vesicles in our simulations replicate  
-well-know vesicle hydrodynamics such as tank-treading and inter-leaflet
-slippage in a shear flow and migration in Poiseuille flow from continuum models. Furthermore we use the hybrid continuum
-model to investigate permeability and rupture of a bilayer
-membrane due to an imposed flow. 
-Finally, we compare a pair of
+In the present work, we extend the hybrid continuum model in~\cite{Fu20}
+for the Janus suspension to incorporate the collective hydrodynamics of
+a Janus suspension under various flows. The JP vesicles in our
+simulations replicate  well-know vesicle hydrodynamics such as
+tank-treading and inter-leaflet slippage in a shear flow and migration
+in Poiseuille flow from continuum models. Furthermore we use the hybrid
+continuum model to investigate permeability and rupture of a bilayer
+membrane due to an imposed flow.  Finally, we compare a pair of
 interacting JP vesicles with a continuum model of a pair of vesicles.
 
-\cite{Brandner2019} used the coarse-grained force field with a lattice Boltzmann molecular dynamics to simulate the hydrodynamics
-of a nano-sized vesicle under a shear flow.  
-In MD simulations, the hydrodynamic interactions 
-for the solvent phase are often approximated by an implicit solvent coarse-grained model.
-In the present work, the hydrodynamic interactions come from the mobility problem
-for the Stokes equations for the incompressible, viscous solvent.
+\cite{Brandner2019} used the coarse-grained force field with a lattice
+Boltzmann molecular dynamics to simulate the hydrodynamics of a
+nano-sized vesicle under a shear flow.  In MD simulations, the
+hydrodynamic interactions for the solvent phase are often approximated
+by an implicit solvent coarse-grained model.  In the present work, the
+hydrodynamic interactions come from the mobility problem for the Stokes
+equations for the incompressible, viscous solvent.
 
@@
 volume (\cite{lu-rah-zor2017, Lukas19, yan-cor-mal-vee-she2020}). These
-methods do not introduce stiffness, but do require solving potentially expensive nonlinear
-complementarity problems at each time step.
+methods do not introduce stiffness, but do require solving potentially
+expensive nonlinear complementarity problems at each time step.
 Repulsion-based contact methods, which we employ, introduce an
@@
 present the formulation for the Janus particles in a viscous fluid in
-the zero-Reynolds number regime (Figure \ref{fig:figure0}a). 
-In \S~\ref{sec:IEM} we extend the
-hybrid continuum model for a Janus suspension to include the effects of
-a far-field flow via the mobility problem formulation. In
-\S~\ref{results} we validate our model and present simulation results
-for a single JP vesicle (Figure \ref{fig:figure0}d) and for a pair of JP vesicles (Figure \ref{fig:figure0}e) 
-under various flowing conditions.
-Finally we provide discussion and outlook for future directions in
-\S~\ref{conclusion}.
+the zero-Reynolds number regime (Figure \ref{fig:figure0}a). In
+\S~\ref{sec:IEM} we extend the hybrid continuum model for a Janus
+suspension to include the effects of a far-field flow via the mobility
+problem formulation. In \S~\ref{results} we validate our model and
+present simulation results for a single JP vesicle (Figure
+\ref{fig:figure0}d) and for a pair of JP vesicles (Figure
+\ref{fig:figure0}e) under various flowing conditions. Finally we provide
+discussion and outlook for future directions in \S~\ref{conclusion}.
 
@@
 \subsection{Model Parameters}
-\cite{Fu20} studied physical quantities for static JP bilayers
-for various particle shapes.  In the present study, we fix particle shape and 
-vary the background flows.  
-Specifically, the
-particles are circular disks with diameter $l_0 = 2.5$ nm. The boundary
+\cite{Fu20} studied physical quantities for static JP vesicles for
+various particle shapes. In the present study, we fix the particle shape
+and vary the background flows. Specifically, the particles are circular
+disks with diameter $l_0 = 2.5$~nm. The boundary
 conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
@@
 $\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle center
-and director respectively.  The particle diameter is the
-thickness of monolayers and the  director points in the
-direction of the hydrophobic side of the JP.
-
-We use $\rho = 2 l_0$ for decay length, $\rho_0 = 0.2l_0$ for repulsion length, $M=4.0$~$k_BT$ for repulsion strength, 
-$\gamma = \text{4.1 pN nm}^{-1}$ for interfacial tension, and $\mu
-= \text{1 cP} = \text{1 pN ns nm}^{-2}$ for viscosity of room-temperature water.
-We nondimensionalize the problem through the change of variables 
+and director respectively. The particle diameter is the thickness of
+monolayers and the director points in the direction of the hydrophobic
+side of the JP.
+
+We use $\rho = 2 l_0$ for decay length, $\rho_0 = 0.2l_0$ for repulsion
+length, $M=4.0$~$k_BT$ for repulsion strength, $\gamma = \text{4.1 pN
+nm}^{-1}$ for interfacial tension, and $\mu = \text{1 cP} = \text{1 pN
+ns nm}^{-2}$ for viscosity of room-temperature water. We
+nondimensionalize the problem through the change of variables 
 %\begin{equation}
@@
 
-To reach consistent simulation outcomes, we first solve for a baseline JP vesicles 
-that is suitably close to equilibrium. We start
-with an assumed configuration of $N=58$ JP in the form of two, circular, apposing monolayers of about
-$8$ nm in radius. The 
-translational and rotational velocities vanish exponentially with
-an approximate decay rate $\sim 4.6$ $\upmu$s$^{-1}$. An 
-equilibrium configuration is therefore rapidly attained.
-This equilibrium configuration serves as the initial data 
-in the subsequent background flow simulations.
+To reach consistent simulation outcomes, we first solve for a baseline
+JP vesicles that is suitably close to equilibrium. We start with an
+assumed configuration of $N=58$ JP in the form of two, circular,
+apposing monolayers of about $8$ nm in radius. The translational and
+rotational velocities vanish exponentially with an approximate decay
+rate $\sim 4.6$ $\upmu$s$^{-1}$. An equilibrium configuration is
+therefore rapidly attained. This equilibrium configuration serves as the
+initial data in the subsequent background flow simulations.
 
@@
 \end{center} 
-  \caption{\label{figure4}
- JP vesicles lose enclosed area but conserve length in shear flow. 
-  Panel (a) gives the reduced area over time
-  for four different shear rates. The monotonic curves are a 
-  two-exponential best fit. There is a commensurate increase in excess length (panel (b)), 
-  but the arc length of the mid plane curve is more or less constant for all shear rates  (panel (c)).
-  The inset in panel (c) is for shear rate 0.003. The legend in panel (b) applies to panels (a)--(c).
-  Panel (d) plots the steady-state reduced area and the decay rate $k_2$ (inset) coming from the fitting
-  data in panel (a). }
+  \caption{\label{figure4} JP vesicles lose enclosed area but conserve
+  length in a shear flow. Panel (a) gives the reduced area over time for
+  four different shear rates. The monotonic curves are a two-exponential
+  best fit. There is a commensurate increase in excess length (panel
+  (b)), but the arc length of the mid plane curve is more or less
+  constant for all shear rates (panel (c)). The inset in panel (c) is
+  for shear rate 0.003. The legend in panel (b) applies to panels
+  (a)--(c). Panel (d) plots the steady-state reduced area and the decay
+  rate $k_2$ (inset) coming from the fitting data in panel (a).}
 \end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:ves_in_shear}
-Our simulation studies begin by showing, for the first time, that a JP suspension with hydrophobic attraction 
-behaves as a tank-treading vesicle
-%with zero viscosity contrast between the fluids inside and
-%outside of the vesicle
-(\cite{Finken08, Shaqfeh11}).
-The centroid of the baseline, $58$-body JP vesicle lies at the origin 
-and the background shear flow 
+Our simulation studies begin by showing, for the first time, that a JP
+suspension with hydrophobic attraction behaves as a tank-treading
+vesicle (\cite{Finken08, Shaqfeh11}). The centroid of the baseline,
+$58$-body JP vesicle lies at the origin and the background shear flow 
 \begin{align}
@@
 \end{align} 
-is applied for
-shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
-and $\mathbf{e}_y$ for the horizontal and vertical directions, respectively.
-We use the dimensionless shear rate $\chi = \dot \gamma$ (s$^{-1}$) ns.
+is applied for shear rate $\dot\gamma$, and orthogonal unit vectors
+$\mathbf{e}_x$ and $\mathbf{e}_y$ for the horizontal and vertical
+directions, respectively. We use the dimensionless shear rate $\chi =
+\dot \gamma$ (s$^{-1}$) ns.
 
@@
 \end{center} 
-  \caption{\label{figure5} 
-  There is inter-monolayer slip present in the JP vesicle tank-treading motion at all shear rates.  
-  Panel (a) tracks a pair of particles (blue and yellow). 
-  The shear rate is $\chi=0.005$ and in the right figure, the yellow particle
-  will complete two and a quarter revolutions in the same time the blue particle completes two revolutions.
-  The curves in panel (b) are the distance the outer leaflet has slid past the inner leaflet. 
-  The slopes of the curves gives the slip velocity. 
-  With the exception of $\chi = 0.0035$, slip velocity is generally monotonic in the shear rate. }
+\caption{\label{figure5} There is inter-monolayer slip present in the JP
+  vesicle tank-treading motion at all shear rates. Panel (a) tracks a
+  pair of particles (blue and yellow). The shear rate is $\chi=0.005$
+  and in the right figure, the yellow particle will complete two and a
+  quarter revolutions in the same time the blue particle completes two
+  revolutions. The curves in panel (b) are the distance the outer
+  leaflet has slid past the inner leaflet. The slopes of the curves
+  gives the slip velocity. With the exception of $\chi = 0.0035$, the
+  slip velocity is generally monotonic in the shear rate.}
 \end{figure}
 
-Figure~\ref{figure3} shows snapshots of the JP vesicle in the
-shear flow with $\chi=0.0025$. 
-Under the background flow, the rigid-body boundary condition \eqref{eq:rigid_bc} causes the 
-particle suspension to elongate. This perturbation  
-disrupts the preferred particle orientations and exposes the hydrophobic core to bulk water (Figure~\ref{figure3}, red region).
-In response, hydrophobic attraction \eqref{eq:hydrophobicAttraction} causes the 
-particles to reorient and form a  somewhat elliptically-shaped suspension.  
-Panels (a) shows the initial configuration and panel (b) shows the later, fully-formed, clockwise tank-treading motion. 
-The JP suspension maintains its bilayer structure throughout the simulation. 
-%
-
-To extract physical quantities, 
-let $A^* = 4\pi A/L^2$ be the reduced area and $\Delta=L/\sqrt{A/\pi}-2\pi$ the excess length of the bilayer
-structure (\cite{Finken08}).
-Here, $A$ is the enclosed area and $L$ is the total length of the JP vesicle  (Figure \ref{fig:figure0}a).
-Figure~\ref{figure4} shows the evolution of the same for various shear rates.
-Panels (a) and (b) show that $A^*$ decreases and $\Delta$ increases with time, respectively,
-and that the rate of decrease/increase grows with shear rate. 
-The total arc length, however, remains constant for all time
-for all four shear rates (panel (c)).
-We conclude that the JP vesicle loses area and that the bilayer behaves as a permeable membrane.
+Figure~\ref{figure3} shows snapshots of the JP vesicle in the shear flow
+with $\chi=0.0025$. Under the background flow, the rigid-body boundary
+condition~\eqref{eq:rigid_bc} causes the particle suspension to
+elongate. This perturbation disrupts the preferred particle orientations
+and exposes the hydrophobic core to bulk water (Figure~\ref{figure3},
+red region). In response, hydrophobic
+attraction~\eqref{eq:hydrophobicAttraction} causes the particles to
+reorient and form a somewhat elliptically-shaped suspension. Panel (a)
+shows the initial configuration and panel (b) shows the later,
+fully-formed, clockwise tank-treading motion. The JP suspension
+maintains its bilayer structure throughout the simulation. 
+%
+
+To extract physical quantities, let $A^* = 4\pi A/L^2$ be the reduced
+area and $\Delta=L/\sqrt{A/\pi} - 2\pi$ the excess length of the bilayer
+structure (\cite{Finken08}). Here, $A$ is the enclosed area and $L$ is
+the total length of the JP vesicle (Figure \ref{fig:figure0}a).
+Figure~\ref{figure4} shows the evolution of the area and length for
+various shear rates. Panels (a) and (b) show that $A^*$ decreases and
+$\Delta$ increases with time, respectively, and that the rate of
+decrease/increase grows with shear rate. The total arc length, however,
+remains constant for all time for all four shear rates (panel (c)). We
+conclude that the JP vesicle loses area and that the bilayer behaves as
+a permeable membrane.
 
 Since the starting configuration is nearly circular, the reduced area
-decreases from an initial value close to $1$ and tends to a steady-state value $A^*_{\infty}$. 
-The data in panel (a) are fit by the model 
-$A^* = (A^*_{\infty}-a_1-a_2) + a_1 \exp(-k_1t) + a_2 \exp(-k_2t),$ $0 < k_2 < k_1$.
-Panel (d) shows that $A^*_{\infty}$ decreases with shear rate. 
-The JP vesicle achieves a steady-state reduced area 
-earlier when the shear rate is low (inset), but the decay rate $k_2$ is more or less constant for higher shearer rates.
+decreases from an initial value close to $1$ and tends to a steady-state
+value $A^*_{\infty}$. The data in panel (a) are fit to the model $A^* =
+(A^*_{\infty}-a_1-a_2) + a_1 \exp(-k_1t) + a_2 \exp(-k_2t),$ $0 < k_2 <
+k_1$. Panel (d) shows that $A^*_{\infty}$ decreases with the shear rate.
+The JP vesicle achieves a steady-state reduced area earlier when the
+shear rate is low (inset), but the decay rate $k_2$ is more or less
+constant for higher shearer rates.
 
 The oscillations in the data of Figure~\ref{figure4} are due to the
-granularity of the JP vesicle. 
-The inset of Figure~\ref{figure4}c zooms in on the arc length data for the shear rate $\chi = 0.003$.
-It shows that the oscillations are smooth and well-resolved by our second-order Adams-Bashforth scheme.
-
-We point out that the range of values for $\chi$ where we measured for tank-treading 
-correspond to shear rates $\dot \gamma = O(10^6$ s$^{-1}$) 
-which gives fluid velocities O(m s$^{-1}$) in the vicinity of the  vesicle.  
-While large, these values are identical to ones used in prior MD studies (\cite{Brandner2019})
-and are a consequence of the fact that larger shear rates are required to produce the viscous stresses needed to 
-appreciably deform smaller vesicles.
+granularity of the JP vesicle. The inset of Figure~\ref{figure4}c zooms
+in on the arc length data for the shear rate $\chi = 0.003$. It shows
+that the oscillations are smooth and well-resolved by our second-order
+Adams-Bashforth scheme.
+
+We point out that the range of values for $\chi$ where we measured for
+tank-treading correspond to shear rates $\dot \gamma = \mathcal{O}(10^6$
+s$^{-1}$) which gives fluid velocities $\mathcal{O}($m s$^{-1}$$)$ in
+the vicinity of the vesicle. While large, these values are identical to
+ones used in prior MD studies (\cite{Brandner2019}) and are a
+consequence of the fact that larger shear rates are required to produce
+the viscous stresses needed to appreciably deform smaller vesicles.
 
@@
 \subsubsection{Inter-Monolayer Friction}
-We observe inter-monolayer slip in the tank-treading, JP vesicle at all shear rates. 
-Since they are not bound, the two leaflets of the vesicle are able to slide 
-past one another. This sliding is limited by viscous friction of the aqueous gaps between particles
-and by the constant unbinding and binding of particles pairs in apposing leaflets.  
-The phenomenon is consistent with prior MD results (\cite{Zgorski2019, denOtter2007}).
-
-Figure~\ref{figure5}a illustrates the process by tracking the distances traveled 
-by a pair of particles. 
-In the left image, the blue and yellow particle lie next to each other. 
-In the right-most panel, the yellow particle has traveled further than the blue particle. 
-This suggests that the tangential velocity of the outer leaflet is larger than that of the inner leaflet.
-The difference in their velocities is the slip velocity $U(t)$  and $s(t) = \int_0^t dU $ records the distance
-one leaflet has slid past the other.
-
-Figure~\ref{figure5}b plots the sliding distance for various shear rates. 
-From the data, we define an inter-monolayer friction coefficient  
+We observe inter-monolayer slip in the tank-treading, JP vesicle at all
+shear rates. Since they are not bound, the two leaflets of the vesicle
+are able to slide past one another. This sliding is limited by viscous
+friction of the aqueous gaps between particles and by the constant
+unbinding and binding of particles pairs in apposing leaflets. The
+phenomenon is consistent with prior MD results (\cite{Zgorski2019,
+denOtter2007}).
+
+Figure~\ref{figure5}a illustrates the process by tracking the distances
+traveled by a pair of particles. In the left image, the blue and yellow
+particle lie next to each other. In the right-most panel, the yellow
+particle has traveled farther than the blue particle. This suggests that
+the tangential velocity of the outer leaflet is larger than that of the
+inner leaflet. The difference in their velocities is the slip velocity
+$U(t)$ and $s(t) = \int_0^t dU $ records the distance one leaflet has
+slid past the other.
+
+Figure~\ref{figure5}b plots the sliding distance for various shear
+rates. From the data, we define an inter-monolayer friction coefficient 
 \begin{align}
@@
 \end{align}
-where $F$ is the tangential force jump, $L$ is the length of the midplane $C_M$ (Figure~\ref{figure5}a), $U$ is the slip velocity, and 
-$\langle \cdot \rangle$ denotes the time average. 
-We define the tangential force jump $F$ to be the tangential shear force on the outer leaflet minus the tangential shear force on the inner leaflet. 
-However, it does not make sense to integrate along a curve passing through the particles.  
-To calculate the tangential force jump $F$, we instead let 
-\begin{equation}
+where $F$ is the tangential force jump, $L$ is the length of the
+midplane $C_M$ (Figure~\ref{figure5}a), $U$ is the slip velocity, and
+$\langle \cdot \rangle$ denotes the time average. We define the
+tangential force jump $F$ to be the tangential shear force on the outer
+leaflet minus the tangential shear force on the inner leaflet. However,
+it does not make sense to integrate along a curve passing through the
+particles.  To calculate the tangential force jump $F$, we instead let 
+\begin{align}
 F_h = \int_{\mathcal{C}_M^+} 
@@
  \ttau \cdot \sigma \cdot \nnu \,\dif s 
-\end{equation}
-where $C_M^+$ and $C_M^-$ are target curves obtained by moving the midplane curve $C_M$ (Figure~\ref{figure5}a)
-a distance $h$  outward, respectively inward, along the unit normal.  
-We sample $F_h$ for $h = \pm 1.5, \pm 2.5, \pm 3.5$ times the particle radius 
-and define $F$ by extrapolating to zero distance.
+\end{align}
+where $C_M^+$ and $C_M^-$ are target curves obtained by moving the
+midplane curve $C_M$ (Figure~\ref{figure5}a) a distance $h$ outward,
+respectively inward, along the unit normal. We sample $F_h$ for $h = \pm
+1.5, \pm 2.5, \pm 3.5$ times the particle radius and define $F$ by
+extrapolating to zero distance.
 
@@
 Table~\ref{table1} provides dimensional friction coefficients $b$ for
-several shear rates. The coefficients generally lie within the
-range 1 to 6 pN ns nm$^{-3}$ which is in good quantitative agreement with
-values previously reported in the literature (\cite{sch-vla-mik2010}
-and~\cite{denOtter2007}).  \cite{denOtter2007} give  
-$b = 2.4 \times 10^6$ Pa m$^{-1}$ s = 
-2.4 pN nm$^{-3}$ ns from their MD study, for example.
+several shear rates. The coefficients generally lie within the range 1
+to 6 pN ns nm$^{-3}$ which is in good quantitative agreement with values
+previously reported in the literature (\cite{sch-vla-mik2010}
+and~\cite{denOtter2007}). \cite{denOtter2007} give $b = 2.4 \times 10^6$
+Pa m$^{-1}$ s = 2.4 pN nm$^{-3}$ ns from their MD study, for example.
 
@@
 %\includegraphics[height=2in]{N58_rupt_600.pdf}
-  \caption{\label{figure8} 
-  Tank-treading leads to membrane rupture for large shear rates.
-  }
+  \caption{\label{figure8} Tank-treading leads to membrane rupture for
+  large shear rates.} 
 \end{figure}
-A temporary fissure or a complete membrane rupture can occur at large shear
-rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture when
-suspended in a shear flow. For $\chi = 0.1$, starting
-  with a circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
-  background flow and fissures appear in the bilayer structure in multiple locations (Figure~\ref{figure8}b). 
-  In Figure~\ref{figure8}c, the ruptured vesicles forms two planar micelles which 
-  are eventually carried off by the flow (Figure~\ref{figure8}d).
+A temporary fissure or a complete membrane rupture can occur at large
+shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
+when suspended in a shear flow. For $\chi = 0.1$, starting with a
+circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
+background flow and fissures appear in the bilayer structure in multiple
+locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
+ruptured vesicles form two planar micelles which are eventually carried
+off by the flow (Figure~\ref{figure8}d).
 
@@
 flow. The parameter $R_0$ is the radius of the JP vesicle at $t=0$ and
-$w$ sets the width of the profile.  
-\cite{Kaoui09, cou-kao-pod-mis2008, dan-vla-mis2009} have shown that the
-behavior of a vesicle in this unbounded  flow includes
-vertical migration, and depending on the flow rate and reduced area, the
-steady-state shape can be either a symmetric parachute or an asymmetric
-slipper.
+$w$ sets the width of the profile. \cite{Kaoui09, cou-kao-pod-mis2008,
+dan-vla-mis2009} have shown that the behavior of a vesicle in this
+unbounded flow includes vertical migration, and depending on the flow
+rate and reduced area, the steady-state shape can be either a symmetric
+parachute or an asymmetric slipper.
 
@@
 Figure~\ref{figure6} shows four configurations for one specific case
-where the centroid of the JP vesicle is initially placed slightly
-above the $x$-axis.  We have marked a pair of particles blue and yellow
-in the inner and outer leaflets, respectively,  and observe that the 
-deformed JP vesicle (Figure~\ref{figure6}, $t = 12~\upmu$s) has a
-counterclockwise movement and the shape of the vesicle approaches an
-asymmetric slipper shape. For this test, the reduced area in the final
-configuration is approximately $0.9$ which matches the previous
-numerical tests in~\cite{Kaoui09} where a slipper-like shape occurs when
-the flow velocity is weak and the reduced area is large.  The flow causes the 
-vesicle, which is initially placed above the axis,
-to draft downward where it reaches a steady height of about  $1$ nm.
+where the centroid of the JP vesicle is initially placed slightly above
+the $x$-axis. We have marked a pair of particles blue and yellow in the
+inner and outer leaflets, respectively, and observe that the deformed JP
+vesicle (Figure~\ref{figure6}, $t = 12~\upmu$s) has a counterclockwise
+movement and the shape of the vesicle approaches an asymmetric slipper
+shape. For this test, the reduced area in the final configuration is
+approximately $0.9$ which matches the previous numerical tests
+in~\cite{Kaoui09} where a slipper-like shape occurs when the flow
+velocity is weak and the reduced area is large. The flow causes the
+vesicle, which is initially placed above the axis, to drift downward
+where it reaches a steady height of about $1$ nm.
 
@@
 %\includegraphics[width=0.8\textwidth]{slipper.eps}
-  \caption{\label{figure6} A JP vesicle placed in a parabolic flow drifts 
-  toward the central axis.  It assumes a slipper shape and undergoes tank-treading
-  like in the shear flow case.  The arrows on the left illustrate the background flow and 
-  the arrows on the right show the velocity relative to the vesicle's moving frame. 
-  The thick black curve plots the distance from the axis as a function of time from left to right.  
-  The parameters are $v_{max} = 8$~nm ns$^{-1}$, 
+  \caption{\label{figure6} A JP vesicle placed in a parabolic flow
+  drifts toward the central axis. It assumes a slipper shape and
+  undergoes tank-treading motion like in the shear flow case. The arrows
+  on the left illustrate the background flow and the arrows on the right
+  show the velocity relative to the vesicle's moving frame. The thick
+  black curve plots the distance from the axis as a function of time
+  from left to right. The parameters are $v_{max} = 8$~nm ns$^{-1}$,
   $w=10$, and $R_0=20$ nm.}
@@
 %  this.}
-\caption{\label{figure2} 
-  In JP vesicles, tension and pressure relax as fluid is expelled 
-  through the particle interstices. 
-  In panel (a), the thin curve plots the mean of the norm of the particle translational velocities.
-  The thick curve plots the mean of the absolute value of the particle angular velocities.  
-  At $t = 0$ $\upmu$s, the vesicle has a spatially constant internal pressure 0.05~pN nm$^{-1}$ (red color, panel (b)).
-  In panel (c),  pressure has dissipated and the vesicle has moved from its initial configuration (gray circles), to the equilibrium configuration
-  (black circles).  The data in panels (d) and (e) support the linear relationship expressed by 
-  \eqref{eq:LaplacePressure} and \eqref{eq:perm}.
-  Circles are for a vesicle with 17 nm initial radius;
-  square are for a 34 nm initial radius.  Asterisks are for 
-  a 18 nm initial radius but with smaller, 1.25 nm diameter particles. 
-  In panel (f), the theoretical time course  \eqref{eq:perm_solution} overlaps the data 
-  using constants $K_A$ and $P$ derived from panels (d) and (e). }
+\caption{\label{figure2} In JP vesicles, tension and pressure relax as
+  fluid is expelled through the particle interstices. In panel (a), the
+  thin curve plots the mean of the norm of the particle translational
+  velocities. The thick curve plots the mean of the absolute value of
+  the particle angular velocities. At $t = 0$ $\upmu$s, the vesicle has
+  a spatially constant internal pressure 0.05~pN nm$^{-1}$ (red color,
+  panel (b)). In panel (c), pressure has dissipated and the vesicle has
+  moved from its initial configuration (gray circles), to the
+  equilibrium configuration (black circles). The data in panels (d) and
+  (e) support the linear relationship expressed by
+  \eqref{eq:LaplacePressure} and \eqref{eq:perm}. Circles are for a
+  vesicle with 17 nm initial radius; square are for a 34 nm initial
+  radius. Asterisks are for a 18 nm initial radius but with smaller,
+  1.25 nm diameter particles. In panel (f), the theoretical time course
+  \eqref{eq:perm_solution} overlaps the data using constants $K_A$ and
+  $P$ derived from panels (d) and (e). }
 \end{figure}
-Finally, we show that the JP bilayer behaves as an extensible, permeable membrane. 
-Figures~\ref{figure2}b shows an initial, non-equilibrium JP vesicle suspended in a quiescent flow $\uu_{\infty} = 0$.
-The color map plots the pressure $p$. The red color in Figures~\ref{figure2}b 
-shows a constant, positive internal pressure (0.05~pN nm$^{-1}$)
-and the white shows a constant zero, external pressure.  
-There is some fluid flow and the pressure vanishes as the configuration tends toward the equilibrium state (Figures~\ref{figure2}c).
-
-What could be the source of this drop in pressure?
-In continuum membrane mechanics, changes in surface area give rise to a
-membrane tension $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the
-membrane surface area and $A_0$ is the reference surface area in the
-The area modulus $K_A$ of bilayers is about $240$ pN nm$^{-1}$ (\cite{NaTr00}).
-In the two-dimensional vesicles, the tension becomes
+Finally, we show that the JP vesicle behaves as an extensible, permeable
+membrane. Figures~\ref{figure2}b shows an initial, non-equilibrium JP
+vesicle suspended in a quiescent flow $\uu_{\infty} = 0$. The color map
+plots the pressure $p$. The red color in Figures~\ref{figure2}b shows a
+constant, positive internal pressure (0.05~pN nm$^{-1}$) and the white
+shows a constant zero, external pressure. There is some fluid flow and
+the pressure vanishes as the configuration tends toward the equilibrium
+state (Figures~\ref{figure2}c).
+
+What could be the source of this drop in pressure? In continuum membrane
+mechanics, changes in surface area give rise to a membrane tension
+$\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the membrane surface area
+and $A_0$ is the reference surface area. The area modulus $K_A$ of
+bilayers is about $240$ pN nm$^{-1}$ (\cite{NaTr00}). In the
+two-dimensional vesicles, the tension becomes
 \begin{align}
@@
 where $\Delta p$ is the difference in internal pressure to the pressure
-at infinity, $R^{-1}$ is the total curvature of the circular cylinder.
-
-Figure~\ref{figure2}c plots the data for the pressure jump
-$\Delta p$ between the particle center and the far-field (see Figures~\ref{figure2}c and~\ref{figure2}d).
-We use $R = L/(2\pi)$ for the vesicle radius, and the horizontal axis is the relative stretch.
-The circles are data for a vesicle with radius 17 nm. The linear fit (solid lines) shows that 
-$R\Delta P$ is proportional to the relative stretching $L/L_0 - 1$.
-The squares are for a vesicle with twice the radius 34 nm, and the data overlap 
-supports that the proportionality constant $K_A$ is a stretching modulus that is independent of vesicle size.
-The data give $K_A = 170 \pm 9$ pN nm$^{-1}$ which is good agreement with the 
-area moduli of lipid bilayer as determined by experiment. 
-To evaluate how changes to particle size lead to different physical properties,
-the asterisk symbols are for an 18 nm radius vesicle
-consisting of particles with diameter 1.25 nm, instead of the usual 2.5 nm.
-These data give smaller stretching modulus of $K_A = 102$~pN~nm$^{-1}$.
+at infinity and $R^{-1}$ is the total curvature of the circular
+cylinder.
+
+Figure~\ref{figure2}c plots the data for the pressure jump $\Delta p$
+between the particle center and the far-field (see
+Figures~\ref{figure2}c and~\ref{figure2}d). We use $R = L/(2\pi)$ for
+the vesicle radius, and the horizontal axis is the relative stretch.
+The circles are data for a vesicle with radius 17 nm. The linear fit
+(solid lines) shows that $R\Delta P$ is proportional to the relative
+stretching $L/L_0 - 1$. The squares are for a vesicle with twice the
+radius 34 nm, and the data overlap supports that the proportionality
+constant $K_A$ is a stretching modulus that is independent of vesicle
+size. The data give $K_A = 170 \pm 9$ pN nm$^{-1}$ which is good
+agreement with the area moduli of lipid bilayer as determined by
+experiment. To evaluate how changes to particle size lead to different
+physical properties, the asterisk symbols are for an 18 nm radius
+vesicle consisting of particles with diameter 1.25 nm, instead of the
+usual 2.5 nm. These data give smaller stretching modulus of $K_A =
+102$~pN~nm$^{-1}$.
 
@@
 where $P$ is a hydraulic permeability constant (\cite{chabanon2017,
-qua-gan-you2021}).
-Figure~\ref{figure2}e shows that the data for 
-$L\Delta p$ and $dA/dt$ obey the linear relationship expressed by \eqref{eq:perm}.
-The slopes of the linear fits give the hydraulic permeabilities $P = 0.0296$ nm$^3$ ns$^{-1}$
-pN$^{-1}$ and $P = 0.0283$ nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 17 nm and 34 nm radius 
-cases, respectively.   
-Like  the area modulus, permeability is independent of vesicle size.
-The hydraulic permeability we calculate, however, is not in agreement with
-experimentally derived values and is larger by a few orders of
-magnitude.
-
-We suspect this discrepancy is due to inter-particle distance of
-the JP being large compared to the inter-lipid spacing in real bilayers. To test this, we calculate the
-permeability for the particles with diameter 1.25 nm. 
-Due to their smaller size but fixed repulsion strength, these particles have a larger inter-particle spacing 
-resulting in an increase in permeability, $P = 0.0566$~nm$^3$~ns$^{-1}$~pN$^{-1}$ (Figure \ref{figure2}e, asterisk symbols).
+qua-gan-you2021}). Figure~\ref{figure2}e shows that the data for
+$L\Delta p$ and $dA/dt$ obey the linear relationship expressed by
+\eqref{eq:perm}. The slopes of the linear fits give the hydraulic
+permeabilities $P = 0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ and $P = 0.0283$
+nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 17 nm and 34 nm radius cases,
+respectively. Like the area modulus, permeability is independent of
+vesicle size.
+
+The hydraulic permeability we calculate, however, is not in agreement
+with experimentally derived values and is larger by a few orders of
+magnitude. We suspect this discrepancy is due to inter-particle distance
+of the JP being large compared to the inter-lipid spacing in real
+bilayers. To test this, we calculate the permeability for the particles
+with diameter 1.25 nm. Due to their smaller size but fixed repulsion
+strength, these particles have a larger inter-particle spacing resulting
+in an increase in permeability, $P = 0.0566$~nm$^3$~ns$^{-1}$~pN$^{-1}$
+(Figure~\ref{figure2}e, asterisk symbols).
 
@@
 The theoretical time courses for \eqref{eq:perm_solution} are in good
-quantitative agreement with the JP data for
-(Figure~\ref{figure2}f).
+quantitative agreement with the JP data (Figure~\ref{figure2}f).
 
@@
   centroids are plotted in blue and red. The centroids are initially
-  located on the $x$-axis.  The fluid velocity streamlines appear in grey.
-  The dimensionless shear rate is $\chi=0.005$.
-  }
+  located on the $x$-axis. The fluid velocity streamlines appear in
+  grey.  The dimensionless shear rate is $\chi=0.005$.}
 \end{figure}
@@
 \end{center} 
-  \caption{\label{figure11} 
-  The initial placement of two JP vesicles suspended in
-  an extensional flow affects the long-time dynamics.  
-  The moving paths of the two centroids are plotted
-  in blue in red. Each row corresponds to a different initial placement
-  of the JP vesicles. 
-  (i) Both JP vesicle centroids are on the $x$-axis. (ii) The
-  centroid of the left JP vesicle is $0.25$ nm above the $x$-axis
-  and the right JP vesicle is on the $x$-axis. (iii) The centroid of
-  the left JP vesicle is $0.25$ nm above the $x$-axis and the right
-  JP vesicle is $0.25$ units below the $x$-axis. (iv) The centroid of
-  the left JP vesicle is $1.25$ nm above the $x$-axis and the
-  centroid of the right JP vesicle is $1.25$ nm below the $x$-axis.
-  The streamlines appear in grey and 
-  the flow rate is $\dot \gamma =0.005$ ns$^{-1}$ in all cases.}
+  \caption{\label{figure11} The initial placement of two JP vesicles
+  suspended in an extensional flow affects the long-time dynamics. The
+  moving paths of the two centroids are plotted in blue in red. Each row
+  corresponds to a different initial placement of the JP vesicles. (i)
+  Both JP vesicle centroids are on the $x$-axis. (ii) The centroid of
+  the left JP vesicle is $0.25$~nm above the $x$-axis and the right JP
+  vesicle is on the $x$-axis. (iii) The centroid of the left JP vesicle
+  is $0.25$~nm above the $x$-axis and the right JP vesicle is $0.25$~nm
+  below the $x$-axis. (iv) The centroid of the left JP vesicle is
+  $1.25$~nm above the $x$-axis and the centroid of the right JP vesicle
+  is $1.25$~nm below the $x$-axis. The streamlines appear in grey and
+  the flow rate is $\dot \gamma =0.005$~ns$^{-1}$ in all cases.}
 \end{figure}
@@
 with extensional rate $\dot \gamma =0.005$ ns$^{-1}$. This extensional
-flow is stretching in the $y$-direction and squeezing in the $x$-direction. 
-Figure~\ref{figure11} shows how the initial placement of the
-JP vesicles affects the dynamics. When two centroids are both placed
-symmetrically on the $x$-axis (case (i)), the JP vesicles come into contact and reach a steady
-equilibrium. If one centroid is placed above the $x$-axis (case (ii)),
-the two JP vesicle move together and then upward. The migration of the
-right JP vesicle is a consequence of the adhesive effect caused by the
-hydrophobic interactions. When the two centroids start on opposite sides
-of the $x$-axis (case (iii)), they eventually diverge from one another
-along the $\pm y$-directions. Finally, when the two centroids start on
-opposite sides of the $x$-axis, but with a greater displacement (case
-(iv)), the JP vesicles move much faster along the $\pm y$-directions.
+flow is stretching in the $y$-direction and squeezing in the
+$x$-direction. Figure~\ref{figure11} shows how the initial placement of
+the JP vesicles affects the dynamics. When two centroids are both placed
+symmetrically on the $x$-axis (case (i)), the JP vesicles come into
+contact and reach a steady equilibrium. If one centroid is placed above
+the $x$-axis (case (ii)), the two JP vesicle move together and then
+upward. The migration of the right JP vesicle is a consequence of the
+adhesive effect caused by the hydrophobic interactions. When the two
+centroids start on opposite sides of the $x$-axis (case (iii)), they
+eventually diverge from one another along the $\pm y$-directions.
+Finally, when the two centroids start on opposite sides of the $x$-axis,
+but with a greater displacement (case (iv)), the JP vesicles move much
+faster along the $\pm y$-directions.
 
 Figure~\ref{figure12} shows numerical results when the centroids of the
-two Janus particles are placed at $(-10,-0.1)$ nm and $(10,0.1)$ nm (case
-(iii) from Figure~\ref{figure11}). With this setup, the two JP vesicles
-eventually separate along the $\pm y$-directions and we compare the
-results against a continuum model as shown in all insets. Panels
+two Janus particles are placed at $(-10,-0.1)$~nm and $(10,0.1)$~nm
+(case (iii) from Figure~\ref{figure11}). With this setup, the two JP
+vesicles eventually separate along the $\pm y$-directions and we compare
+the results against a continuum model as shown in all insets. Panels
 (b)--(d) show the transient behavior of the JP vesicles and the
@@
 
-\cite{Fu20} developed a mathematical model to quantify the macroscopic assembly and mechanics of 
-a JP bilayer in a viscous solvent. 
-The interactions between JP are formulated as a second-kind integral equation, 
-which is coupled to the Stokes equations for the surrounding incompressible fluid 
-at the zero-Reynolds-number limit.  
-Numerical simulations of a JP suspensions revealed self-assembly of JP into micelles 
-and bilayers, providing an alternative means for computing mechanical moduli, 
-which often requires the knowledge of an equation of state from experiments on a colloidal membrane~(\cite{Balchunas2019_SM}).
+\cite{Fu20} developed a mathematical model to quantify the macroscopic
+assembly and mechanics of a JP vesicle in a viscous solvent. The
+interactions between JP are formulated as a second-kind integral
+equation, which is coupled to the Stokes equations for the surrounding
+incompressible fluid at the zero-Reynolds-number limit. Numerical
+simulations of a JP suspensions revealed self-assembly of JP into
+micelles and bilayers, providing an alternative means for computing
+mechanical moduli, which often requires the knowledge of an equation of
+state from experiments on a colloidal
+membrane~(\cite{Balchunas2019_SM}).
 %
@@
 %%
-For example, with the flexibility of the model, we can specify the boundary condition on JP surfaces based on the chemicals used in experiments. 
+For example, with the flexibility of the model, we can specify the
+boundary condition on JP surfaces based on the chemicals used in
+experiments.
 %This can be an assist to study of interparticle interactions and chemical compositions in industry.
@@
 
-In the present study, we used this integral formulation and numerical algorithm to simulate the hydrodynamics of JP vesicles
-in background flows. 
-Under 
-a linear shear flow, we found a JP vesicle to exhibit elongation and tank-treading 
-dynamics observed for a lipid bilayer GUV.
+In the present study, we used this integral formulation and numerical
+algorithm to simulate the hydrodynamics of JP vesicles in background
+flows. Under a linear shear flow, we found a JP vesicle to exhibit
+elongation and tank-treading dynamics observed for a lipid bilayer GUV.
 %
@@
 The results showed that the reduced area $A^*$ decreases with shear rate
-but that the total length of a JP vesicle is conserved.  The
-decay rate of the reduced area was independent of the shear rate values
-between $0.003$~ns$^{-1}$ and~$0.005$~ns$^{-1}$. Moreover, the proposed
-model describes membrane rupture in high shear rates. Therefore, our
-method can be applied to vesicles undergoing topological changes which
-is difficult to simulate when using a continuum model that represents
+but that the total length of a JP vesicle is conserved. The decay rate
+of the reduced area was independent of the shear rate values between
+$0.003$~ns$^{-1}$ and~$0.005$~ns$^{-1}$. Moreover, the proposed model
+describes membrane rupture in high shear rates. Therefore, our method
+can be applied to vesicles undergoing topological changes which is
+difficult to simulate when using a continuum model that represents
 vesicles as closed and continuous curves.
@@
 %
-We estimated the inter-monolayer friction $b$, membrane permeability constant $P$ and the membrane
-stretching modulus $K_A$. 
-The inter-monolayer friction coefficient was determined by
-calculating the tangential  shear force and slip velocities with
-respect to the bilayer mid-plane. 
-The range of friction coefficients are in agreement with values reported
-by~\cite{denOtter2007} in their MD study.  The coarse-graining level of the
-JP vesicle has a larger length scale than molecular dynamics
+We estimated the inter-monolayer friction $b$, membrane permeability
+constant $P$, and the membrane stretching modulus $K_A$. The
+inter-monolayer friction coefficient was determined by calculating the
+tangential shear force and slip velocities with respect to the bilayer
+mid-plane. The range of friction coefficients agree with values reported
+by~\cite{denOtter2007} in their MD study. The coarse-graining level of
+the JP vesicle has a larger length scale than molecular dynamics
 simulations, and in the future convergence studies we will investigate
-how physical properties like the friction coefficient and membrane permeability 
-depend on the particle shape and size.
-
-We also simulate the spatial migration of a JP vesicle in a
-parabolic shear flow. 
+how physical properties like the friction coefficient and membrane
+permeability depend on the particle shape and size.
+
+We also simulate the spatial migration of a JP vesicle in a parabolic
+shear flow. 
 %The chosen parameter values result in an asymmetric
@@
 %
-Replicating the hydrodynamics of a GUV in a Poiseuille flow~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}),
-the JP vesicle moves toward the center of the shear flow.
-While the initial reduced area of the JP vesicle is $A^*
-\approx 1$, the equilibrium reduced area is $A^*=0.9$. 
-For the parameters we used in the simulation, the JP vesicle takes on an 
-asymmetric, "slipper" shape as it settles above the center of flow and exhibits tank-treading motion.
+Replicating the hydrodynamics of a GUV in a Poiseuille
+flow~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}), the JP
+vesicle moves toward the center of the shear flow. While the initial
+reduced area of the JP vesicle is $A^* \approx 1$, the equilibrium
+reduced area is $A^*=0.9$. For the parameters we used in the simulation,
+the JP vesicle takes on an asymmetric, ``slipper" shape as it settles
+above the center of flow and exhibits tank-treading motion.
 %A qualitative
@@
 %simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). 
-An interesting result contrast with continuum results is that the JP vesicle oscillates at a height slightly above the center of the
+An interesting result contrast with continuum results is that the JP
+vesicle oscillates at a height slightly above the center of the
 Poiseuille flow.
@@
 
-We further simulated the hydrodynamics of  two JP vesicles,
-and drew comparisons with simulation results of two vesicles described by the Helfrich
-continuum model. A comparison of the vesicle shapes and the streamlines
-demonstrate remarkable similarities. The two overlapping trajectories of
-the JP vesicles' centroids in a shear flow evolve as expected when the
-two centroids are initialized on the same horizontal level. We also
-observe a rotating behavior that is observed for models involving
-vesicle adhesion~(\cite{qua-vee-you2019}). 
-The hydrophobic attraction lead to this adhesive effect when two JP
-bilayers are sufficiently close. We also perform several simulations of 
-a pair of JP vesicles suspended in an extensional flow. By varying the initial
-vertical displacement of the vesicles' centroids, we can control for divergent trajectories and 
-obtain similar results to the continuum model.
-
-In \S~\ref{subsec:calculating_force}, we derived an alternative integral form for 
-calculating the force and torque to avoid the singular integral evaluation. 
-These alternative integrals allow us to accurately resolve trajectories over long times
-without having to rely on computationally expensive quadratures.
+We further simulated the hydrodynamics of two JP vesicles, and drew
+comparisons with simulation results of two vesicles described by the
+Helfrich continuum model. A comparison of the vesicle shapes and the
+streamlines demonstrate remarkable similarities. The two overlapping
+trajectories of the JP vesicles' centroids in a shear flow evolve as
+expected when the two centroids are initialized on the same horizontal
+level. We also observe a rotating behavior that is observed for models
+involving vesicle adhesion~(\cite{qua-vee-you2019}). The hydrophobic
+attraction led to this adhesive effect when two JP bilayers are
+sufficiently close. We also performed several simulations of a pair of
+JP vesicles suspended in an extensional flow. By varying the initial
+vertical displacement of the vesicles' centroids, we can control for
+divergent trajectories and obtain similar results to the continuum
+model.
+
+In \S~\ref{subsec:calculating_force}, we derived an alternative integral
+form for calculating the force and torque to avoid the singular integral
+evaluation. These alternative integrals allow us to accurately resolve
+trajectories over long times without having to rely on computationally
+expensive quadratures.
 
@@
 algorithmic implementation including a fast summation method such as the
-fast multipole method. Another research direction is to 
-%
-include the fluctuating hydrodynamics for Brownian suspensions~(\cite{Bao2018}),
+fast multipole method. Another research direction is to include the
+fluctuating hydrodynamics for Brownian suspensions~(\cite{Bao2018}),
 %introduce thermal fluctuations into the model. 
 %This will result in Janus particles that include Brownian motion, 
-and this is critical to understand membrane diffusion. 
-Finally, a more physical boundary conditions for the 
-HAP model will allow us to draw comparisons between 
-computational and laboratory experiments.
+and this is critical to understand membrane diffusion. Finally, a more
+physical boundary conditions for the HAP model will allow us to draw
+comparisons between computational and laboratory experiments.
 

### 2021-09-28 doc/main_jfm.tex
final text changes

@@
 assumed configuration of $N=58$ JP in the form of two, circular,
-apposing monolayers of about $8$ nm in radius. The translational and
+apposing monolayers of about $8$ nm in radius. The norms of the translational and
 rotational velocities vanish exponentially with an approximate decay
@@
 \end{center} 
-\caption{\label{figure5} There is inter-monolayer slip present in the JP
+\caption{\label{figure5} Inter-monolayer slip is present in the JP
   vesicle tank-treading motion at all shear rates. Panel (a) tracks a
@@
   leaflet has slid past the inner leaflet. The slopes of the curves
-  gives the slip velocity. With the exception of $\chi = 0.0035$, the
+  give the slip velocity. With the exception of $\chi = 0.0035$, the
   slip velocity is generally monotonic in the shear rate.}
@@
 s$^{-1}$) which gives fluid velocities $\mathcal{O}($m s$^{-1}$$)$ in
-the vicinity of the vesicle. While large, these values are identical to
+the vicinity of the vesicle. While large, these orders of magnitude are identical to
 ones used in prior MD studies (\cite{Brandner2019}) and are a
@@
 friction of the aqueous gaps between particles and by the constant
-unbinding and binding of particles pairs in apposing leaflets. The
-phenomenon is consistent with prior MD results (\cite{Zgorski2019,
-denOtter2007}).
-
-Figure~\ref{figure5}a illustrates the process by tracking the distances
-traveled by a pair of particles. In the left image, the blue and yellow
+unbinding and binding of particles pairs in apposing leaflets. 
+Previous studies \cite{Zgorski2019, denOtter2007}
+have considered inter-monolayer slip in lipid bilayers simulated by MD.
+
+Figure~\ref{figure5}a illustrates inter-monolayer slip by tracking the distances
+traveled by a pair of particles along the midplane curve. In the left image, the blue and yellow
 particle lie next to each other. In the right-most panel, the yellow
 particle has traveled farther than the blue particle. This suggests that
-the tangential velocity of the outer leaflet is larger than that of the
-inner leaflet. The difference in their velocities is the slip velocity
-$U(t)$ and $s(t) = \int_0^t dU $ records the distance one leaflet has
-slid past the other.
-
-Figure~\ref{figure5}b plots the sliding distance for various shear
-rates. From the data, we define an inter-monolayer friction coefficient 
-\begin{align}
-  b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle},
+the outer tangential velocity, obtained by projecting the velocity of the
+outer leaflet onto the midplane curve, 
+is larger than that of the inner leaflet.
+
+From the data, we obtain an inter-monolayer friction coefficient 
+\begin{align}
+  b =  \frac{\langle F \rangle}{\langle L   U \rangle} ,
 \end{align}
 where $F$ is the tangential force jump, $L$ is the length of the
-midplane $C_M$ (Figure~\ref{figure5}a), $U$ is the slip velocity, and
-$\langle \cdot \rangle$ denotes the time average. We define the
-tangential force jump $F$ to be the tangential shear force on the outer
-leaflet minus the tangential shear force on the inner leaflet. However,
-it does not make sense to integrate along a curve passing through the
-particles.  To calculate the tangential force jump $F$, we instead let 
-\begin{align}
-F_h = \int_{\mathcal{C}_M^+} 
-  \ttau \cdot \sigma \cdot \nnu \,\dif s - \int_{\mathcal{C}_M^-} 
- \ttau \cdot \sigma \cdot \nnu \,\dif s 
-\end{align}
-where $C_M^+$ and $C_M^-$ are target curves obtained by moving the
-midplane curve $C_M$ (Figure~\ref{figure5}a) a distance $h$ outward,
-respectively inward, along the unit normal. We sample $F_h$ for $h = \pm
-1.5, \pm 2.5, \pm 3.5$ times the particle radius and define $F$ by
-extrapolating to zero distance.
+midplane $C_M$ (Figure~\ref{figure5}a), and $U$ is the slip velocity.
+The time average $\langle \cdot \rangle$ is necessary to avoid division by zero
+whenever slip velocity vanishes.
 
@@
 %$b$ (pN$\cdot$ns nm$^{-3}$)    & 0.22 & 0.87*  & 0.22 &0.21 & 1.29* & 0.31 & 0.30\\ 
-$b$ (pN$\cdot$ns nm$^{-3}$)    & 1.01 & 3.40 &   3.70  &   5.01 &   5.38  &   5.75  &   6.25 \\ 
+$b$ (pN ns nm$^{-3}$)    & 0.43 & 1.19 &   0.42  & 0.69 &   0.97  &   0.80  &  1.07 \\ 
 \hline    
@@
 
+The tangential force jump $F$ equals the 
+tangential shear force on the outer
+leaflet minus the tangential shear force on the inner leaflet. 
+To calculate  $F$, we first let 
+\begin{align}
+F_h = \int_{\mathcal{C}_M^+} 
+  \ttau \cdot \sigma \cdot \nnu \,\dif s - \int_{\mathcal{C}_M^-} 
+ \ttau \cdot \sigma \cdot \nnu \,\dif s 
+\end{align}
+where $C_M^+$ and $C_M^-$ are target curves obtained by projecting the
+midplane curve $C_M$  a distance $h$ outward,
+respectively inward, along its unit normal vector field (Figure~\ref{figure5}a). We sample $F_h$ for 
+$h = \pm 1.3, \pm 1.5,  \pm 1.7, \pm 1.9$ times the particle radius and define $F$ by
+extrapolating to zero distance. This avoids integrating along a curve passing directly through the
+particles.
+
+To calculate $U$, we let $v_+(\mathbf{x})$ and $v_-(\mathbf{x})$ 
+be the tangential velocity of the outer, respectively inner, leaflet.  Then 
+\begin{equation}
+U = \frac{1}{L}\int_{C_M}v_+(\mathbf{x})(1 - \delta \kappa) - v_-(\mathbf{x})(1 +  \delta \kappa) \, ds,
+\end{equation}
+where $ \delta $ is the distance from the leaflet centers to the midplane and $\kappa$ is the curvature. 
+The factors $\pm  \delta \kappa$ are needed to project the leaflet velocities, defined on the particle centers,
+onto the midplane curve. 
+Finally, the function $s(t) = \int_0^t dU $ records the distance one leaflet has
+slid past the other. Figure~\ref{figure5}b plots the sliding distance for various shear
+rates.
+
 Table~\ref{table1} provides dimensional friction coefficients $b$ for
-several shear rates. The coefficients generally lie within the range 1
-to 6 pN ns nm$^{-3}$ which is in good quantitative agreement with values
+several shear rates. 
+The coefficients are 0.79 $\pm$ 0.3 pN ns nm$^{-3}$ which is in good quantitative agreement with values
 previously reported in the literature (\cite{sch-vla-mik2010}
 and~\cite{denOtter2007}). \cite{denOtter2007} give $b = 2.4 \times 10^6$
-Pa m$^{-1}$ s = 2.4 pN nm$^{-3}$ ns from their MD study, for example.
+Pa m$^{-1}$ s = 2.4 pN ns nm$^{-3}$  from their MD study, for example.
 
@@
   the particle angular velocities. At $t = 0$ $\upmu$s, the vesicle has
-  a spatially constant internal pressure 0.05~pN nm$^{-1}$ (red color,
+  a spatially constant internal pressure 0.05~pN nm$^{-2}$ (red color,
   panel (b)). In panel (c), pressure has dissipated and the vesicle has
@@
 plots the pressure $p$. The red color in Figures~\ref{figure2}b shows a
-constant, positive internal pressure (0.05~pN nm$^{-1}$) and the white
-shows a constant zero, external pressure. There is some fluid flow and
+spatially constant, positive internal pressure (0.05~pN nm$^{-2}$) and the white
+shows a spatially constant zero, external pressure. There is some fluid flow and
 the pressure vanishes as the configuration tends toward the equilibrium
@@
 
-What could be the source of this drop in pressure? In continuum membrane
-mechanics, changes in surface area give rise to a membrane tension
+What could be the source of this drop in pressure? In membrane
+continuum  mechanics, changes in surface area give rise to a membrane tension
 $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the membrane surface area
@@
 constant $K_A$ is a stretching modulus that is independent of vesicle
-size. The data give $K_A = 170 \pm 9$ pN nm$^{-1}$ which is good
-agreement with the area moduli of lipid bilayer as determined by
-experiment. To evaluate how changes to particle size lead to different
+size. The data give $K_A = 170 \pm 9$ pN nm$^{-1}$ which is in good
+agreement with the experimentally obtained area moduli of lipid bilayer. 
+To evaluate how changes to particle size lead to different
 physical properties, the asterisk symbols are for an 18 nm radius
 vesicle consisting of particles with diameter 1.25 nm, instead of the
-usual 2.5 nm. These data give smaller stretching modulus of $K_A =
+usual 2.5 nm. These data give a smaller stretching modulus of $K_A =
 102$~pN~nm$^{-1}$.
@@
 repulsive forces. The gaps allow for some fluid flux across the JP
-bilayer, which can be quantified by the equation
+bilayer, and in membrane mechanics aqueous flux is quantified by the equation
 \begin{align}
@@
 nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 17 nm and 34 nm radius cases,
-respectively. Like the area modulus, permeability is independent of
-vesicle size.
+respectively. Like the area modulus, the data give a permeability 
+that is independent of vesicle size.
 
@@
 \end{align}
-The theoretical time courses for \eqref{eq:perm_solution} are in good
+All in all, the theoretical time courses for \eqref{eq:perm_solution} are in good
 quantitative agreement with the JP data (Figure~\ref{figure2}f).

### 2021-09-28 doc/main_jfm.tex
yny abstract

--- 2021-09-28 doc/main_jfm.tex
@@
 \begin{abstract}
-  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic particles suspended in a viscous background flow. 
-  The interparticle force comes from a specific hydrophobic attraction potential (HAP)
-  that has been shown to model lipid bilayer membranes. 
+  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic 
+  Janus particles suspended in a viscous background flow. 
+  The Janus particles interact with each other directly through a hydrophobic attraction potential (HAP)
+  that has been shown to model lipid bilayer membranes. In addition they also interaction with each other indirectly through the hydrodynamic interactions.
   We adopt an efficient integral equation method for solving the screened
-  Laplace equation and the mobility problem where it can accurately
-  calculate hydrophobic and hydrodynamic interactions between near
-  touched boundaries.    Under a linear shear flow,  we observe the tank-treading deformation
-  in a two-dimensional  vesicle for various values of the shear rate.
+  Laplace equation (for the HAP) and the mobility of Janus particles in a viscous fluid. 
+  Both the hydrophobic and hydrodynamic interactions between near
+  touched boundaries are accurately captured within the integral formulation. Under a linear shear flow,  we observe the tank-treading deformation
+  in a two-dimensional vesicle made of Janus particles for various values of the shear rate.
   The results yield measurements 
@@
   The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
-  interactions in shear and extensional flows.
+  interactions in shear and extensional flows. We find that the hydrodynamics of a  vesicle assembled from Janus particles is similar to that of
+  a lipid bilayer vesicle often described by the Helfrich free energy of an inextensible elastic membrane.
 %    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 

### 2021-09-28 doc/main_jfm.tex
yny abstract 2

@@
   The Janus particles interact with each other directly through a hydrophobic attraction potential (HAP)
-  that has been shown to model lipid bilayer membranes. In addition they also interaction with each other indirectly through the hydrodynamic interactions.
+  that has been shown to model lipid bilayer membranes. In addition they also interact with each other indirectly through the hydrodynamic interactions.
   We adopt an efficient integral equation method for solving the screened
@@
   The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
-  interactions in shear and extensional flows. We find that the hydrodynamics of a  vesicle assembled from Janus particles is similar to that of
-  a lipid bilayer vesicle often described by the Helfrich free energy of an inextensible elastic membrane.
+  interactions in shear and extensional flows. We find that the hydrodynamics of a  vesicle assembled from Janus particles
+replicates the dynamics of an inextensible elastic vesicle.
 %    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 

### 2021-09-30 doc/main_jfm.tex
adding acknowledgments
yny acknowledgement

@@
 \begin{acknowledgments}
+  {\bf Acknowledgments:} B.Q.~acknowledges support from NSF (Grant
+  No.~DMS 2012560) and from the Simons Foundation, Mathematics and
+  Physical Sciences-Collaboration Grants for Mathematicians (Award
+  No.~527139). Y.-N. Y.~acknowledges support from NSF (Grant No.~DMS 1614863 and 1951600) and
+  Flatiron Institute, part of Simons Foundation.
 %We would like to acknowledge 

### 2021-10-01 doc/main_jfm.tex
final updates by Rolf

@@
   Janus particles suspended in a viscous background flow. 
-  The Janus particles interact with each other directly through a hydrophobic attraction potential (HAP)
-  that has been shown to model lipid bilayer membranes. In addition they also interact with each other indirectly through the hydrodynamic interactions.
+  The Janus particles interact through a hydrophobic attraction potential 
+  that leads to self-assembly into bilayer structures.   
   We adopt an efficient integral equation method for solving the screened
-  Laplace equation (for the HAP) and the mobility of Janus particles in a viscous fluid. 
-  Both the hydrophobic and hydrodynamic interactions between near
-  touched boundaries are accurately captured within the integral formulation. Under a linear shear flow,  we observe the tank-treading deformation
-  in a two-dimensional vesicle made of Janus particles for various values of the shear rate.
-  The results yield measurements 
-  of inter-monolayer friction and membrane permeability. Large shear rates lead to membrane rupture. 
+  Laplace equation for hydrophobic attraction and 
+  for solving the mobility problem for hydrodynamic interactions. 
+  The integral equation formulation accurately captures both interactions for near touched boundaries. 
+  Under a linear shear flow,  we observe the tank-treading deformation
+  in a two-dimensional vesicle made of Janus particles.
+  The results yield measurements of inter-monolayer friction, membrane permeability, 
+  and at large shear rates, membrane rupture. 
   The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
-  interactions in shear and extensional flows. We find that the hydrodynamics of a  vesicle assembled from Janus particles
-replicates the dynamics of an inextensible elastic vesicle.
+  interactions in shear and extensional flows. The hydrodynamics of the Janus 
+  particles vesicle replicate the behaviour of an inextensible elastic vesicle membrane.
 %    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
@@
 pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
-Since each particle $\Gamma_i$ with center $\aa_i$ is a rigid body, its velocity satisfies 
+Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
 \begin{align}
@@
 where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and rotlets
-centered at $\aa_i$ are
+centred at $\aa_i$ are
 \begin{align}
@@
 \theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
-$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle center
+$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle centre
 and director respectively. The particle diameter is the thickness of
@@
 %and orthogonal unit vectors $\mathbf{e}_1$ and $\mathbf{e}_2$. 
-%A single elliptical particle is suspended in the fluid with center at the origin.
+%A single elliptical particle is suspended in the fluid with centre at the origin.
 %The Jeffrey orbit  
@@
 shear rates. Since they are not bound, the two leaflets of the vesicle
-are able to slide past one another. This sliding is limited by viscous
+are able to slide past one another. 
+Monolayer slip effects have been incorporated in continuum models (\cite{sch-vla-mik2010}).
+In the present setting, slip is limited by viscous
 friction of the aqueous gaps between particles and by the constant
 unbinding and binding of particles pairs in apposing leaflets.
-Previous studies \cite{Zgorski2019, denOtter2007}
-have considered inter-monolayer slip in lipid bilayers simulated by MD.
 
@@
 
-To calculate $U$, we let $v_+(\mathbf{x})$ and $v_-(\mathbf{x})$ 
+To calculate $U$, we let $u_+(\mathbf{x})$ and $u_-(\mathbf{x})$ 
 be the tangential velocity of the outer, respectively inner, leaflet.  Then 
 \begin{equation}
-U = \frac{1}{L}\int_{C_M}v_+(\mathbf{x})(1 - \delta \kappa) - v_-(\mathbf{x})(1 +  \delta \kappa) \, ds,
+U = \frac{1}{L}\int_{C_M}u_+(\mathbf{x})(1 - \delta \kappa) - v_-(\mathbf{x})(1 +  \delta \kappa) \, ds,
 \end{equation}
-where $ \delta $ is the distance from the leaflet centers to the midplane and $\kappa$ is the curvature. 
-The factors $\pm  \delta \kappa$ are needed to project the leaflet velocities, defined on the particle centers,
+where $ \delta $ is the distance from the leaflet centres to the midplane and $\kappa$ is the curvature. 
+The factors $\pm  \delta \kappa$ are needed to project the leaflet velocities, defined on the particle centres,
 onto the midplane curve. 
@@
 
-Table~\ref{table1} provides dimensional friction coefficients $b$ for
-several shear rates. 
-The coefficients are 0.79 $\pm$ 0.3 pN ns nm$^{-3}$ which is in good quantitative agreement with values
-previously reported in the literature (\cite{sch-vla-mik2010}
-and~\cite{denOtter2007}). \cite{denOtter2007} give $b = 2.4 \times 10^6$
-Pa m$^{-1}$ s = 2.4 pN ns nm$^{-3}$  from their MD study, for example.
-
+Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
+over a range of shear rates
+which is in good quantitative agreement with values previously reported in the literature.
+Atomistic studies have also considered inter-monolayer slip in lipid bilayers. 
+\cite{WuoEd06} and \cite{denOtter2007} reported $b = 0.7 \times 10^6$ Pa m$^{-1}$ s  
+$=0.7$ pN ns nm$^{-3}$  
+and $b = 2.4$  pN ns nm$^{-3}$ for DPPC membranes simulated by MD, respectively. 
+Using a more recent version of the Martini force field, \cite{Zgorski2019} 
+gives $b = 5.5$ pN ns nm$^{-3}$ for shear rates 0.4 ns$^{-1}$ and higher.
+It is understandable that there is uncertainty in the friction coefficients of
+Table~\ref{table1}.  The scatter in our data, however, is fully consistent with that calculated
+from MD simulations, c.f. the transient rise in values of Table~\ref{table1} and in \cite{Zgorski2019}, Figure 10
+for low shear rates. 
 \subsubsection{Membrane Ruptures}
@@
 $w$ sets the width of the profile. \cite{Kaoui09, cou-kao-pod-mis2008,
-dan-vla-mis2009} have shown that the behavior of a vesicle in this
+dan-vla-mis2009} have shown that the behaviour of a vesicle in this
 unbounded flow includes vertical migration, and depending on the flow
@@
 Figure~\ref{figure2}c plots the data for the pressure jump $\Delta p$
-between the particle center and the far-field (see
+between the particle centre and the far-field (see
 Figures~\ref{figure2}c and~\ref{figure2}d). We use $R = L/(2\pi)$ for
@@
 
-The hydraulic permeability we calculate, however, is not in agreement
-with experimentally derived values and is larger by a few orders of
-magnitude. We suspect this discrepancy is due to inter-particle distance
-of the JP being large compared to the inter-lipid spacing in real
-bilayers. To test this, we calculate the permeability for the particles
-with diameter 1.25 nm. Due to their smaller size but fixed repulsion
-strength, these particles have a larger inter-particle spacing resulting
-in an increase in permeability, $P = 0.0566$~nm$^3$~ns$^{-1}$~pN$^{-1}$
-(Figure~\ref{figure2}e, asterisk symbols).
-
-Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
-combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
-and~\eqref{eq:perm}, to derive
-\begin{align}
-\label{eq:perm_solution}
-L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
-\end{align}
-All in all, the theoretical time courses for \eqref{eq:perm_solution} are in good
-quantitative agreement with the JP data (Figure~\ref{figure2}f).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Two Vesicles in a Linear Flow}
-
 \begin{figure}
@@
 \end{figure}
+
+The hydraulic permeability we calculate, however, is not in agreement
+with experimentally derived values and is larger by a few orders of
+magnitude. We suspect this discrepancy is due to inter-particle distance
+of the JP being large compared to the inter-lipid spacing in real
+bilayers. To test this, we calculate the permeability for the particles
+with diameter 1.25 nm. Due to their smaller size but fixed repulsion
+strength, these particles have a larger inter-particle spacing resulting
+in an increase in permeability, $P = 0.0566$~nm$^3$~ns$^{-1}$~pN$^{-1}$
+(Figure~\ref{figure2}e, asterisk symbols).
+
+Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
+combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
+and~\eqref{eq:perm}, to derive
+\begin{align}
+\label{eq:perm_solution}
+L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
+\end{align}
+All in all, the theoretical time courses for \eqref{eq:perm_solution} are in good
+quantitative agreement with the JP data (Figure~\ref{figure2}f).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Two Vesicles in a Linear Flow}
 
@@
 (\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
-behavior is absent when two JP vesicles are well-separated.
+behaviour is absent when two JP vesicles are well-separated.
 
@@
 the results against a continuum model as shown in all insets. Panels
-(b)--(d) show the transient behavior of the JP vesicles and the
+(b)--(d) show the transient behaviour of the JP vesicles and the
 continuum vesicles under an extensional flow. In both the coarse-grained
 model and the continuum model, the vesicles initially converge towards
-one other and then diverge along the $y$-axis. The behavior of the
+one other and then diverge along the $y$-axis. The behaviour of the
 streamlines in both cases are similar. The pressure is initially largest
@@
 
+\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 flow~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}), the JP
-vesicle moves toward the center of the shear flow. While the initial
+vesicle moves toward the centre of the shear flow. While the initial
 reduced area of the JP vesicle is $A^* \approx 1$, the equilibrium
@@
 the JP vesicle takes on an asymmetric, ``slipper" shape as it settles
-above the center of flow and exhibits tank-treading motion.
+above the centre of flow and exhibits tank-treading motion.
 %A qualitative
@@
 An interesting result contrast with continuum results is that the JP
-vesicle oscillates at a height slightly above the center of the
+vesicle oscillates at a height slightly above the centre of the
 Poiseuille flow.
@@
 expected when the two centroids are initialized on the same horizontal
-level. We also observe a rotating behavior that is observed for models
+level. We also observe a rotating behaviour that is observed for models
 involving vesicle adhesion~(\cite{qua-vee-you2019}). The hydrophobic

### 2021-10-14 NSF2021/Description/specificaim1.tex
starting nsf 2021

--- 2020-12-23 NSF2020/Description/specificaim1_ver2.tex
@@
 \label{sec:proposed-work}
-%The proposed research develops fast,
-%high-order-accurate, parallel numerical algorithms for large-scale
-%simulations of the collective hydrodynamics of amphiphilic particles in a viscous solvent.
 %%
@@
 for how external fields control particle self-assembly.
-%mathematically
-%characterize the variational behavior of HARP under appropriate
-%homogenized limits.
 
@@
 
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.9\textwidth]{figures/SA1_fig1.pdf}
-%\end{center}
-%\caption{\footnotesize (A--C) The splay ($\Div \mathbf{d}$), 
-%saddle splay ($\det \mathsf{D}$) and twist ($\Curl \mathbf{d}$) elastic distortions of 
-%a monolayer. (D) The monolayer neutral surface $\Sigma$,  
-%director $\mathbf{d}$ and unit normal $\mathbf{n}$ in local coordinates.
-%(E--F) Lipids are able to tilt from  the surface normal, and stretch.
-%(H--J) Intermediates of membrane fusion and (K) experimental image of a stalk \cite{Aeffner2012}. }
-%\label{fig:distortions}
-%\end{figure}
+The goal of Specific Aim 1 is to investigate generalizations of the
+screened Laplace equation for different soft matter systems.
+
+\begin{comment}
 The goal of Specific Aim 1 is to characterize the material properties of
@@
 \centerline{\includegraphics[width=0.46\textwidth]{Figures/Deformations.pdf}}
-%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
   \vspace{-5pt}
@@
 these controversies due to the assumptions in the HK theory.
-%Using the HK  model as a base,
-%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
-%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
-%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
-%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.
-
-%\begin{wrapfigure}[13]{l}{0.5\textwidth}
-%\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
-%\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
-%diaphragm expansion (ii) and pore formation (iii). 
-%(B) Saddle-splay energy for each change in \emph{monolayer} topology
-%calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
-%\label{fig:barriers}
-%\end{wrapfigure}
 
 \sloppy
-The HK framework assumes a three-dimensional lipid monolayer where the internal structure
-consists of straight fibers that represent elongated hydrocarbon chains.
-The elastic energy density ${\cal W}$ is quadratic in the Green-Lagrange strain
-tensor for this striated, internal structure.
-%
-%
-%
-%These fibers
-%tilt and stretch with respect to the dividing surface--the surface formed lying between the hydrocarbon chains and polar heads of lipids.
-%Accordingly, the deformation takes the form 
-%\begin{equation}
-%  \label{LMdeformation}
-%{\bf x}(X_1, X_2, X_3) = {\bf x}_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) {\bf n}(x_0(X_1, X_2))
-%\end{equation}
-%where $(X_1,X_2,X_3)$ are points in a reference volume.
-%The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field ${\bf n}$ parametrizes the
-%direction of the lipid tails in the deformed state \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
-%The parameter $X_3$ and the function $\zeta$ parametrizes the distance along the hydrocarbon chain in the reference state
-%and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta = $ 2.5 nm is a realistic monolayer thickness. 
-%
-%The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for ${\bf x}$. 
-%The chains stretch and compress to satisfy incompressibility.
-%Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
-%lead to an elastic surface energy over the dividing surface $\Sigma$. 
-%
-This energy density decomposes into four, fundamental, and independent
-deformations (Figure~\ref{fig:deformations}): splay ($\Div {\bf n}$),
-twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$), and tilt
-${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is
-the unit surface normal;
+The HK framework assumes a three-dimensional lipid monolayer where the
+internal structure consists of straight fibers that represent elongated
+hydrocarbon chains.  The elastic energy density ${\cal W}$ is quadratic
+in the Green-Lagrange strain tensor for this striated, internal
+structure. This energy density decomposes into four, fundamental, and
+independent deformations (Figure~\ref{fig:deformations}): splay ($\Div
+{\bf n}$), twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf
+n}$), and tilt ${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where
+${\bf N}$ is the unit surface normal;
 \begin{equation}
@@
 \end{equation}
-Here, 
-%$(\nabla {\bf n})_{ij} = \partial_{x_j}{\bf n} \cdot {\bf e}_i$ is the surface gradient with
-%orthonormal tangent vectors $\{{\bf e}_1, {\bf e}_2\}$.
-%%\todo[inline]{YNY and BQ: What do you call a coordinate system where the metric is the identity at one point?}
-%Also, the surface divergence 
-%$\Div {\bf n}$ is the trace, and the surface curl $\Curl {\bf n}$ is the anti-trace (sum of the off-diagonal elements), of $\nabla {\bf n}$ respectively.
-%respectively (Figure \ref{fig:distortions}A--C).
-the deformations come with elastic coefficients: the bending modulus
-$\KB$, twist modulus $\KT$, saddle-splay modulus $\KG$, and tilt modulus
-$\KTH$.
-%HK define the tilt vector ${\bf t} = {\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal.
-%
-The parameter $k_0$ is the spontaneous curvature and determines the
-preferred lipid splay~\cite{RoLi15,Kozlov2007}.  
-%As an illustration, the
-%lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
-%%as a result of  %having a relatively long acyl chain. 
-%and these lipids would preferentially line the upper monolayer in Figure \ref{fig:deformations}B  
-%because the addition of a positive splay 
-%to the negative spontaneous curvature leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
-%The subtraction of $k_0^2$ makes the energy distortion free
-%\cite{Helfrich73,PhysRevLett.113.248102,Hamm2000}.
+Here, the deformations come with elastic coefficients: the bending
+modulus $\KB$, twist modulus $\KT$, saddle-splay modulus $\KG$, and tilt
+modulus $\KTH$. The parameter $k_0$ is the spontaneous curvature and
+determines the preferred lipid splay~\cite{RoLi15,Kozlov2007}.
 
-Although the HK elastic theory assumes small deformations, 
-Galimzyanov {\em et al.}~\cite{C9SM02079A} have shown that energies derived from
-molecular dynamics and those derived from \eqref{ansatz3} are in agreement, even when curvatures are large.
-Under spatial scales much larger than the membrane thickness, membrane
-energy is well-characterized by the Canham-Helfrich energy used
-throughout the fluid-structure literature \cite{QiangDu09,
-Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP, qua-bir2014,
-qua-vee-you2019}. The Canham-Helfrich energy is actually a special case
-of \eqref{ansatz3} obtained by setting ${\bf n} =  \pm {\bf N}$ (the
-$\pm$ depending on orientation) and collapsing both monolayers onto the
-membrane midplane.
-%There, splay $\Div n$ equal to twice the mean curvature, saddle splay
-%$\det \nabla n$ equal to the Gauss curvature, and both twist and tilt
-%are equal to zero.
+Although the HK elastic theory assumes small deformations, Galimzyanov
+{\em et al.}~\cite{C9SM02079A} have shown that energies derived from
+molecular dynamics and those derived from \eqref{ansatz3} are in
+agreement, even when curvatures are large.  Under spatial scales much
+larger than the membrane thickness, membrane energy is
+well-characterized by the Canham-Helfrich energy used throughout the
+fluid-structure literature \cite{QiangDu09, Lowengrub07,KimLai2010_JCP,
+Hu, HuLaiSeolEtAl2016_JCP, qua-bir2014, qua-vee-you2019}. The
+Canham-Helfrich energy is actually a special case of \eqref{ansatz3}
+obtained by setting ${\bf n} =  \pm {\bf N}$ (the $\pm$ depending on
+orientation) and collapsing both monolayers onto the membrane midplane.
 
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=\textwidth]{figures/SA1_fig2.pdf}
-%\end{center}\vspace{-1.em}
-%\caption{\footnotesize (A) A partially clamped bilayer with mid-plane (dashed curve) under uniform load.
-%The quartic fit comes from continuum theory. 
-%(B) A circular vesicle at equilibrium. (C) The area modulus derives
-%from convexity in energy as a function of radius. 
-%\label{fig:bend}}
-%\end{figure}
-
-% Proposers should address what they want to do,
-% why they want to do it,
-% how they plan to do it,
-% how they will know if they succeed,
-% and what benefits could accrue if the project is successful.
-%\begin{center}
-%Preliminary results
-%\end{center}
-
-%\begin{wrapfigure}[13]{l}{0.5\textwidth}
-%\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
-%\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
-%diaphragm expansion (ii) and pore formation (iii). 
-%(B) Saddle-splay energy for each change in \emph{monolayer} topology
-%calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
-%\label{fig:barriers}
-%\end{wrapfigure}
-
-%\begin{center}
-%Anticipated model simulations
-%\end{center}
-\newpage
 \subsubsection{Simulations of the HAP model to estimate elastic moduli
 and energy}
-%To characterize material properties of a bilayer, we compare the energies and forces generated by
-%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
-%
-%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
-%for a wide range of particle parameters and physical parameters in HARP to 
-%
-%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
-%as the corresponding energies in the particle system for all reasonable deformation.
-%If this is the case we will 
-%
 \begin{wrapfigure}[11]{r}{0.43\textwidth}
-%\vspace{-0.4cm}
   \centerline{\includegraphics[width=0.42\textwidth]{Figures/Flattening.pdf}}
-%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
-%\vspace{-0.5cm}
   \caption{\label{fig:flattening} \footnotesize Example of computing
@@
 
-%To characterize material properties of a bilayer, we compare the energies and forces generated by
-%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
-%We propose to first {\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
-%as the corresponding energies in the particle system for all reasonable deformation.
-%If this is the case we will {\bf (ii)} determine the value of the elastic $\KB$,
-%$\KT$, $\KG$ and $\KTH$, and then {\bf (iii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
-%%
-%%Motivated by our preliminary results \cite{Fu2018_SIAM}
-%%we use realistic values for particle diameter $2$ nm \cite{Boal},
-%%screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
-%%and interfacial tension $\gamma=4.1$ pN nm$^{-1}$ \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
-%%model parameters. The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
-%%particle diameter and the hydrophobic boundary condition \eqref{SL}
-%%are additional parameters defining the coarse-grained representation. 
-%
-%An accurate and robust way to measure material properties is to track the evolution of the bilayer.
-
 Here we start with a particle-based bilayer in a specific
@@
 respectively.
-%bilayer by steepest gradient descent 
-%with respect to the HARP functional:
-%\begin{equation}
-%\label{SGD}   
-%\frac{\dif {\bf a}_i}{\dif t} = {\bf F}_i,    \quad  \frac{\dif {\bf R}_i}{\dif t}  = {\bf R}_i A({\bf w}_i),\quad i = 1, \dots, N.
-%\end{equation}
-%where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; %
-%$A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
-%We solve \eqref{SGD} numerically  using an Adams–Bashforth linear multistep method. 
-%The procedure involves solving \eqref{SL} based off of the current particle configuration.
-%We then use the solution $u$ to calculate the collection of forces and torques \eqref{forceandtorque}, and update the particle configuration
-%through \eqref{SGD}.
-%
 
-This yields a dissipation of the total potential \eqref{eq:total_poten}, which
-stabilizes the evolving bilayer shape.
-Therefore, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field ${\bf n}$ by
-interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$ from the interpolated shapes.
+This yields a dissipation of the total potential \eqref{eq:total_poten},
+which stabilizes the evolving bilayer shape.  Therefore, we reconstruct
+an evolving monolayer dividing surface $\Sigma$ and director field ${\bf
+n}$ by interpolating the particle centers and orientations. Using
+\eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$ from the
+interpolated shapes.
 
-%In certain instances, the bilayer evolution involves only one or a few of the four fundamental deformations.
-%When this occurs, the elastic moduli derive from the coefficients of the linear regression between the HAP energy $\Delta \Phi = \Phi - \Phi_0$
-%and continuum energies and $\Delta E = E - E_0$, where  $\Phi_0$ and $E_0$ are respective equilibrium values.
+We propose to conduct calculations similar to the example of
+Figure~\ref{fig:flattening} for other elastic moduli such as the
+effective twist modulus $\KT$.  Molecular dynamics investigations find a
+twist modulus about 1 \kBT~\cite{LeVeWa14}, and here, the specific
+non-equilibrium shape consists of a single layer of amphiphilic
+particles on a hydrophobic substrate as illustrated by
+Figure~\ref{fig:deformations}D. Having a nonzero twist requires nonzero
+tilt because the surface gradient of the lipid director equals the
+second fundamental form whenever tilt is zero locally. The twist
+deformation is a fully three-dimensional deformation.
+\S\ref{subsec:specific_aim_3} addresses outstanding implementation
+issues like three-dimensional boundary integral equation solvers.
 
-%
-%Since it is a particle-based method, the HAP model has a number of advantages over continuum-based descriptions.
-%The elastic energy \eqref{ansatz3} couples director gradients to surface geometry through
-%the tilt vector field.  Furthermore, bilayer energy is the sum of two monolayer
-%energies and the distance between these monolayers varies according to \eqref{LMdeformation}.
-%Effects like tilt and varying monolayer thickness appear at lipid domain boundaries, the edge of nanopores and at the boundary of membrane inclusions \cite{PhysRevE.102.042406}.
-%These effects are present in the proposed formulation, and the particle-based bilayers can break open and join monolayer-wise 
-%as required by fussion and fission. 
-%
-%Bending is the energetically most consequential deformations. To measure a bending modulus,  
-%we deform the midplane of a planar bilayer into the shape of a circular arc.
-%This arc stores bending energy in the form of splay $\Div {\bf n}$, while twist, saddle-splay and tilt deformations are zero.
-%The splay in the two leaflets approximately cancel when added, making the contribution of spontaneous curvature negligible.
-%In the case of a rectangular bialyer, the corresponding elastic energy 
-%$E = \int_{\Sigma} \KB \kappa^2$ where $\kappa$ is the curvature of the curved cross-section $C$.
-%Figure \ref{} shows the approximately linear relationship between $\Delta \Phi$ and $\Delta E$
-%used to values for infer $\KB$.
+The gradient descent technique is ineffective for measuring the saddle
+splay modulus $\KG$ because the saddle splay energy is largely invariant
+under shape changes.  To evaluate $\KG$, we will combine the present
+particle simulations with the string method from PI RR's work on
+membrane fusion \cite{RyKlYaCo16}. The string method is a numerical
+scheme that finds least energy pathways separating energy basins
+\cite{doi:10.1063/1.2720838}.  In the simplified Canham-Helfrich
+formulation, saddle splay energy is an exact indicator of topological
+transitions, thanks to the  Gauss-Bonnet theorem \cite{TerziDeserno17}.
+More generally, PI RR has shown that saddle splay acts as a topological
+indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}.  As a
+result, saddle splay can be quantified from the transition energies of a
+least energy path of pore formation (Figure~\ref{fig:saddle_splay}).
 
-%
-We propose to conduct calculations similar to the example of Figure~\ref{fig:flattening}
-for other elastic moduli such as the effective twist modulus $\KT$.
-Molecular dynamics investigations find a twist modulus about 1
-\kBT~\cite{LeVeWa14}, and here, the specific non-equilibrium shape consists of
-a single layer of amphiphilic particles on a hydrophobic substrate as
-illustrated by Figure~\ref{fig:deformations}D. Having a nonzero twist
-requires nonzero tilt because the surface gradient of the lipid
-director equals the second fundamental form
-%, and is therefore symmetric,
-whenever tilt is zero locally. The twist deformation is a fully
-three-dimensional deformation. \S\ref{subsec:specific_aim_3} addresses outstanding implementation issues like three-dimensional boundary integral equation solvers.
-
-%for a wide range of particle parameters and physical parameters in HARP to 
-%
-%We will also determine the effective saddle splay modulus $\KG$. 
-The gradient descent technique is ineffective for measuring the saddle splay modulus $\KG$ because
-the saddle splay energy is largely invariant under shape changes.
-To evaluate $\KG$, we will combine the present particle simulations with the string method 
-from PI RR's work on membrane fusion \cite{RyKlYaCo16}. The string method is a numerical scheme that finds
-least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}. 
-In the simplified Canham-Helfrich formulation, saddle splay energy is an exact indicator of topological transitions, 
-thanks to the  Gauss-Bonnet theorem \cite{TerziDeserno17}.
-More generally, PI RR has shown that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}. 
-As a result, saddle splay can be quantified from the transition energies
-of a least energy path of pore formation  (Figure 6).
-%(Figure \ref{fig:saddle_splay}).   
-%Using the string method, we will evaluate the transition energies between the intact pancake shape,
-%and one with a pore. Pore formation in a single bilayer decreases the integral of saddle splay from $4\pi$
-%to $0$. We can, in principle, detect this drop in energy because we have already accounted for the other deformations. 
-%
-%%We will also analyze $\KG$ using a helical geometry. In a helicoid with inclination $m$, the director
-%%gradient is $\nabla n = \begin{pmatrix} 0 & m(m^2+x_1^2)^{-1} \\ m(m^2+x_1^2)^{-1} & 0\end{pmatrix}$ where $x_1$ is the distance to the central
-%%axis. We observe that saddle splay, twist and tilt are zeros, and $\det \nabla n = m^2(m^2+x_1^2)^{-2}$.
-%%In the simulations, the particles forming the helicoid will be confined to two, concentric cylinders. The
-%%continuum energy $\tfrac{1}{2}\KG h(m x_1(m^2+x_1^2)^{-1} + \tan^{-1}(x_1/m)) |_{r_1}^{r_2}$ where $h$, $r_1$ and $r_2$
-%%are the cylinder heights, inner cylinder radius, and outer cylinder radius, respectively. 
-%
-%The proposed particle-based simulations of the HARP model in equations~\ref{SGD} also allow direct examination on the assumption of quadratic form of the elastic energy density.
-%As discussed earlier, recent disagreement in elastic moduli between continuum model and MD simulations originates from such assumption. 
-%The particle-based HARP model provides a unique opportunity to examine the validity of the quadratic elastic energy, and the PIs propose to examine how (if) any deviation from the quadratic elastic energy may depend on the microscopic details of the amphiphilic particles and their interactions.
-%\subsubsection{HK elastic energy form}
-
-%\noindent{\bf{HK elastic energy form:}}
 The field of membrane continuum mechanics still lacks consensus as to
 whether HK energy is the appropriate functional for bilayer energy.
-\textbf{(i)} Researchers have assumed that $\KT = 0$ to effect lateral fluidity in
-membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
-PhysRevE.102.042406}. 
-A value $\KT = 0$, however, makes~\eqref{ansatz3} a noncoercive functional.
-%and leads to the nonphysical conclusion that there are bilayers 
-%with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
-\textbf{(ii)} Recently,~\cite{TerziDeserno17} derived a tilt curvature
-term that was neglected from the HK analysis~\cite{Hamm2000}.
-Later,~\cite{C9SM02079A} and~\cite{PhysRevE.102.042406} independently
-identified an inconsistency in the argument used
-by~\cite{TerziDeserno17} arising
-from a transversal tilt invariance assumption.
-In~\cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
-\textbf{(iii)} Theoretical analysis of lipid phase transitions predict a
-negative saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
-SIEGEL20085200} that gives rise to a larger energy barrier for
-monolayer fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
+\textbf{(i)} Researchers have assumed that $\KT = 0$ to effect lateral
+fluidity in membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
+PhysRevE.102.042406}. A value $\KT = 0$, however, makes~\eqref{ansatz3}
+a noncoercive functional. \textbf{(ii)} Recently,~\cite{TerziDeserno17}
+derived a tilt curvature term that was neglected from the HK
+analysis~\cite{Hamm2000}.  Later,~\cite{C9SM02079A}
+and~\cite{PhysRevE.102.042406} independently identified an inconsistency
+in the argument used by~\cite{TerziDeserno17} arising from a transversal
+tilt invariance assumption.  In~\cite{RyKlYaCo16}, PI RR and
+collaborators showed that the tilt vector leads to unphysical cusps
+depending on how one accounts for membrane thickness.  \textbf{(iii)}
+Theoretical analysis of lipid phase transitions predict a negative
+saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
+SIEGEL20085200} that gives rise to a larger energy barrier for monolayer
+fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
 TerziDeserno17}.
@@
   \centerline{\includegraphics[width=0.31\textwidth]{Figures/SaddleSplayDiagram.pdf}}
-%  \vspace{-8pt}
-\caption{\label{fig:saddle_splay} \footnotesize Example of determining the
-  saddle splay modulus.}
+  \caption{\label{fig:saddle_splay} \footnotesize Example of determining
+  the saddle splay modulus.}
 \end{wrapfigure}
-%
-%
-%Researchers point out, however, that this theoretical value requires a larger energy 
-%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
-%Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.
-
-% The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
-% liquid crystal theory. However, the ``bend'' distortion from nematics  
-% is not present in monolayers since the directors have no dependence in the normal direction.
-% There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection.
 
@@
 the works~\cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000,
-C9SM02079A} utilize an approximate identity for incompressibility as a base,
-so we can considerably improve upon the analysis of monolayer energy.
+C9SM02079A} utilize an approximate identity for incompressibility as a
+base, so we can considerably improve upon the analysis of monolayer
+energy.
 
-%  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
-%  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
-%  and accounting for these couplings by Taylor expansion  
-%  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
-%
-%The form of the elastic energy density \eqref{ansatz3} is the same as
-%  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
-%  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
-%  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
-%  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
-%  Using this observation, we prove an exact identity 
-%  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
-%  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
-%  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
-%  
-%%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
-%%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
-%%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
-%%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
-%%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
-%%  This gives the continuum elastic energy equals
-%%  \begin{equation}
-%%    \label{eq:twist_energy}
-%%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
-%%  \end{equation}
-%%  which we compare to the HAP simulation data.
-%
 \subsubsection{Analysis on the HAP model in terms of the HK functional}
@@
 
-%\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of
-%HAP}
 Our goal here is to develop tools that can explain functionals
@@
 
-%The HAP energy converges to the surface energy in the limit of vanishing screening length~\cite{Shibata2004}.
-%Also, the boundary layers of the solutions to the screen Laplace equation
-%converge to area measures supported on the particle boundaries \cite{Lee2018, Lin2015, Shibata2004}.
-%These phenomena are analogous to the sharp interface limit in the phase-field functional,
-%and motivate developing the mathematical connections between the HAP energy and
-%the energy functionals used in the gradient theory of phase transitions.
-%formulation~\cite{Modica87, MODICA1987487, LuMo89}.
-%PI RR has worked on phase field approximations of membrane bending
-%energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
-%equation~\cite{1531-3492_2006_2_357, Lee2018}.
-%The screened-Laplace equations~\eqref{SL} is the linearization of the Poisson-Boltzmann equation.
-%One set of questions is to establish the HAP convergence rate as a
-%function of particle geometry~\cite{LuMo89}, which can be used as a
-%benchmark for numerical validation.
-%Ultimately, we will be able to address the so-called $\Gamma$-convergence of energy minimizing
-%particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 
-%The phase field functional approximates the perimeter of sublevel sets
-%of a so-called phase field indicator function. The approximation becomes
-%sharp in the zero interfacial thickness limit and minimizers of the
-%phase field functional converge (after normalization) to the
-%characteristic function of a set solving a perimeter minimization
-%problem
-%
-%
-
-%In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  
-%As an illustration, consider two fluid-bound plates $P_1$ and $P_2$ that geometrically flat and hydrophobic all sides.
-%We conjecture that in the zero-screening length limit, the plates have overlapping faces, and that 
-%\begin{equation}
-%\lim_{\rho \to 0} \min \Phi_{\text{hydro}} = \max_{\mathcal{X}} A(P_1 \Delta P_2)
-%\end{equation}
-%$A(P_1 \Delta P_2)$ is the area of the symmetric difference of the overlap.  
-%\cite{https://doi.org/10.1038/s41467-019-09787-6}
-%
-%
-%% It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
-%% whether \eqref{ansatz3} contains a complete list of consistent deformations.
-%%\textbf{(i)} Researcher have assumed that $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}.
-%%  Based on \eqref{eq:twist_energy}, a value $\KT = 0$ leads to the
-%%  unphysical conclusion that there are bilayers with $\nabla {\bf n} \to \infty$ but $E \to 0.$ 
-%%  \textbf{(ii)}
-%%  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
-%%  Later, \cite{C9SM02079A} 
-%%  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
-%%  from a transversal tilt invariance assumption.
-%%  The PI Ryham showed,  that the tilt vector $T = {\bf n}/{\bf n}\cdot {\bf N} - {\bf N}$ leads to unphysical cusps when constraining membrane thickness  \cite{RyKlYaCo16}.  
-%%  \textbf{(iii)}
-%%  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
-%%\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
-%%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
-%%Furthermore, the stability requirements of \eqref{ansatz3} are $\KB > 0$, $K_T > 0$, $\KG \geq -4\KB$
-%%and $\KG \geq -4\KT$. Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14},
-%%suggesting a somewhat smaller magnitude for $\KG$.
-%
-% 
-%%The form of the elastic energy density \eqref{ansatz3} is the same as
-%%the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
-%%a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
-%%The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
-%%liquid crystal theory. However, the ``bend'' distortion from nematics  
-%%is not present in monolayers since the directors have no dependence in the normal direction.
-%%There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection. 
-%%  
-%%  We suspect the reason why, after twenty years, the field has yet to reach a consensus 
-%%  as to the form of \eqref{ansatz3} has to do with the Taylor expansions used to derive the elastic energy density. 
-%%  Past researchers expressed the strain tensor in
-%%  terms of the orthonormal frame $\{{\bf e}_1, {\bf e}_2, {\bf N}\}$ with surface tangent vectors ${\bf e}_i$ and surface normal ${\bf N}$.  
-%%  In this frame, there is a coupling between the gradients of all three terms ${\bf x}_0,$ $\zeta$ and ${\bf n}$ of the deformation \eqref{LMdeformation}.
-%%  Subtle differential geometric arguments are needed to evaluate the terms in the Taylor expansion,
-%%  and these couplings can lead to an energy density with more than ten parameters, for example \cite{PhysRevE.102.042406}.
-%%
-%%  We will revisit the HK analysis to see if any of the aforementioned inconsistencies can be resolved.
-%%  As a main analytical innovation, we have found that expanding the strain tensor in
-%%  terms of the orthonormal frame $\{{\bf e}'_1, {\bf e}'_2, n\}$ with ${\bf e}'_i$ perpendicular to ${\bf n}$
-%%  greatly simplifies the expansion because it decouples the gradient terms. As an illustration, the prominent works
-%%  \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
-%%  incompressibility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
-%%  However, we prove that when expressed in the $\{{\bf e}'_1, {\bf e}'_2, n\}$ frame, the incompressility condition is \emph{exact}
-%%  and is given by a Steiner-type polynomial in terms of $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
-%%  Aside from the special case of zero tilt, \cite{Hamm2000} and coworkers seem to have been unaware of this result.
-%
-%Our investigations will leave open the possibility that the free energy of monolayers and bilayers is non-local. 
-%We have shown that hydrophic attraction is a non-additive force, meaning the force of attraction between two
-%particles is dependent on the position a third or more particles \cite{SilveraBatista1242477}.
-%Conceptually, this would arise in continuum theory if two monolayer surfaces
-%had a different elastic energy density despite having locally identical curvatures and directors.
-%The boundary integral formulation described in Specific Aim 3 easily accomodates additional linear PDE and
-%we will extend our study to include charge lipids and weak electrolytes \cite{C9SM00772E}.
+\end{comment}

### 2021-10-27 NSF2021/Description/broaderimpacts.tex

--- 2020-11-16 NSF2020/Description/broaderimpacts.tex
@@
 for Janus particle aggregates and correctly predicts elastic properties of bilayer. 
-The technical research tasks includes quantifying collective properties of 
+The technical research tasks include quantifying collective properties of 
 amphiphilic ensembles, mathematical analysis of continuum elastic energies, 
 efficient, high-order numerical algorithms for large-scale simulations, and 
-incorporating external fields such as electric charge. Lastly, the proposal 
+incorporating external fields through electric charge. Lastly, the proposal 
 extends the results using three-dimensional boundary integral formulations.

### 2021-10-29 NSF2021/Description/broaderimpacts.tex
incorporated Carolyn's changes

@@
 computing, physics of fluids, and mathematics. The mathematical component 
-incorporates leading techniques from geometric analysis and gives deep insight 
-into fundamental material science. The project offers undergraduates 
-in a socially impactful manner the opportunity to do research and train 
-with graduate and postdoctoral personnel. It incorporates research in the 
-classroom, and with its combination of mathematical modeling, analysis, 
-and scientific computing, the project highlights the importance of 
-mathematics and computation to all areas of science and engineering.
-
+incorporates leading techniques from geometric analysis and offers  
+insight 
+into fundamentals of material science.
+The project brings socially consequential research into the classroom, and offers undergraduates the opportunity to train alongside graduate students and postdoctoral fellows.
+With its combination of mathematical modeling, analysis, and scientific computing, the project highlights the importance of mathematics and computation to all areas of science and engineering.
 %The proposed mathematical analysis, modeling, and numerical algorithms
@@
 and to the extent possible, the PIs and personnel will travel to New
-York for one or two weeks in the summers. Fordham University recently
-constructed a seminar/collaboration space specifically for collaborative
-research, and the URs will have office space with desks there.
-
-As a requirement, the URs will write quality summary reports and give
-presentations at the their respective research symposia. The work will
-be considered a success if the URs also participate in a national
-conference. The best possible outcome is if URs coauthor a publication.
+York for one or two weeks during the summers. Fordham University
+recently constructed a seminar/collaboration space specifically for
+collaborative research, and the URs will have office space with desks
+there. As a requirement, the URs will write quality summary reports and
+give presentations at the their respective research symposia. The work
+will be considered successful if the URs also participate in a national
+conference. In the best possible outcome, the URs will co-author a
+publication.
 

### 2021-10-29 NSF2021/Description/priorsupport.tex
incorporated Carolyn's changes

--- 2020-11-16 NSF2020/Description/priorsupport.tex
@@
 %
-The PIs, their postdocs, and students will meet frequently on Zoom and
-in person when possible. The PIs will share software packages, paper
+The PIs, postdocs, and students will meet frequently on Zoom and
+in person when possible. During the pandemic, the three PIs will meet
+weekly on Zoom for a research meeting. Once the pandemic is under control, PI RR and PI YNY will conduct biweekly meetings in person, with PI BQ Zoom in from Florida.
+The PIs will share software packages, paper
 sources, and references on a common \textsf{Git} repository. The

### 2021-10-29 NSF2021/Description/specificaim3.tex
incorporated Carolyn's changes

--- 2020-11-16 NSF2020/Description/newspecificaim3.tex
@@
 Membrane bending rigidity increases with increasing lipid surface
-charge, while decreases with increasing salt concentration in the bulk
-solution due to the screening of the lipid surface charge. This agrees
+charge, but decreases with increasing salt concentration in the bulk
+solution due to the screening of the lipid surface charge. This
+result agrees
 with several theoretical models~\cite{Kralchevsky1996_JCIS,

### 2021-11-02 NSF2021/Description/specificaim1.tex
added a few notes to the NSF proposal

@@
 screened Laplace equation for different soft matter systems.
+
+\begin{itemize}
+  \item Include ions in suspension
+  \item Discussed in Sylvie Roke's talk---I added the slides to the repo
+\end{itemize}
 
@@
 
-\subsubsection{Analysis on the HAP model in terms of the HK functional}
-The HK functional~\eqref{ansatz3} has had tremendous impact in
-understanding biological membranes, but has received little attention in
-terms of mathematical analysis. In the calculus of variations, the
+\subsubsection{Analysis of the HAP model in terms of the HK functional}
+The HK functional~\eqref{ansatz3} has transformed how scientists understand biological membranes, yet the
+theory has received little attention in terms of
+mathematical analysis. In the calculus of variations, the
 principal question is whether a minimizer of an energy functional

### 2021-11-02 NSF2021/Description/specificaim2.tex

--- 2020-11-16 NSF2020/Description/newspecificaim2.tex
@@
 and bind microscopic components in solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}.
-Additionally, hydrodynamic interactions are central to fabricating complex,
+Additionally, hydrodynamic interactions are central to fabricate complex,
 three-dimensional microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010}.
@@
 \begin{wrapfigure}[14]{r}{0.61\textwidth}
-  \centering{\includegraphics[width=0.61\textwidth]{Figures/domain.pdf}}
-    \vspace{-20pt}
+  \centering{\includegraphics[width=0.60\textwidth]{Figures/domain.pdf}}
+    \vspace{-15pt}
     \caption{\label{fig:flow_map} \footnotesize A collection of 3D
@@
 discretizations when the boundary surfaces are irregular. Alternatively,
-since we are solving constant-coefficient linear elliptic
-partial differential equations (PDEs), their
-solutions can be represented with layer potentials
+since we are solving constant-coefficient linear elliptic partial
+differential equations (PDEs), the solutions can be represented with
+layer potentials
 \begin{align}
   \label{eq:LP}
-  u(\mathbf{x}) = \int_{\partial\Omega} K(\mathbf{x},\mathbf{y})
+  u(\mathbf{x}) = \mathcal{K}[\sigma](\mathbf{x}) = 
+  \int_{\partial\Omega} K(\mathbf{x},\mathbf{y})
   \sigma(\mathbf{y})\,dS,
@@
 % ----------------------------------------------------------------------
-\subsubsection{Numerical issues}
+\subsubsection{Numerical challenges}
 \label{subsec:NumericalIssues}
@@
 \vspace*{-13pt}
-\centerline{\includegraphics[width=2.5in]{figures/integrands}}
+\centerline{\includegraphics[width=2.4in]{figures/integrands}}
 \vspace*{-13pt}
@@
 \begin{wrapfigure}[13]{r}{0.30\textwidth}
-\centerline{\includegraphics[width=0.30\textwidth]{figures/BIError.pdf}}
+\centerline{\includegraphics[width=0.29\textwidth]{figures/BIError.pdf}}
   \vspace{-8pt}

### 2021-11-05 NSF2021/Description/specificaim3.tex
yny

@@
-\subsection{Specific Aim 3: Dynamics of self-assembly by HAP under an external flow/field}
+\subsection{Specific Aim 3: Self-assembly of Janus particles in ionic solutions}
 \label{subsec:specific_aim_3}
 
-\subsubsection{Vesicles in background flows}
-Numerically solving the Stokes and screened Laplace system~\eqref{SL}
-and~\eqref{eq:stokes} is nontrivial, and we will develop efficient,
-robust, high-order-in-time and -space algorithms suited to the problem.
-There are a few challenges. {\bf (i)} The equations express a two-way
-coupling since the flow changes the position of the suspended particles,
-and in return, the geometry-dependent hydrophobic stresses impart a
-force on the flow. {\bf (ii)} The inputs to the Stokes equations are
-particle configurations, forces, and torques. The outputs are the rigid
-body translation and angular velocities used to update the particle
-positions (see Figure~\ref{fig:flow_map}). Although the underlying
-equations are linear, the overall problem is highly nonlinear because
-the domain is constantly changing. {\bf (iii)} Self-assembly causes the
-particles to come into close contact. As a result, an exceptional
-spatial accuracy is required to resolve the fields between adjacent
-particles. Furthermore, physically relevant elastic properties of
-bilayers become apparent at large length scales and for large
-particle-numbers, which increases the computational complexity of our
-simulations.
+\subsubsection{Dynamics of a single Janus particle in ionic solutions}
+In experiments, Janus particles are often immersed in a solution of ions \cite{ChenWhitmer2011_Sci} or surfactants \cite{}.
+In electrolytic solutions the interaction between salt and Janus particle gives 
+rise to a slip velocity (on the particle surface) that depends on the ion distribution and the zeta potential \cite{BayatiJCP2016} 
+(the potential difference between the Janus particle surface and the surrounding conducting fluid).
+The short-range interactions between Janus particles depend on the salt concentration:
+At very low salt concentrations, Janus particles repel one another electrostatically, whereas at high salt concentration, van der Waals
+forces cause Janus particles to aggregate irreversibly \cite{Goodwin2019}.
+At intermediate concentrations of monovalent salt, Janus particles are found to self assemble in the form of a small number of elemental units of building blocks \cite{Chen2011_Science}.
+%
+\begin{wrapfigure}[11]{l}{0.47\textwidth}
+\centerline{\includegraphics[width=0.46\textwidth]{Figures/fig2A_Chen2011_Science}}
+  \vspace{-5pt}
+\caption{\label{fig:helices_of_JPs} \footnotesize Formation of helices of Janus particles as salt concentration increases \cite{Chen2011_Science}.}
+\end{wrapfigure}
+%
+Figure~\ref{fig:helices_of_JPs} shows that Janus particles can self-assemble into a helix at high concentration of monovalent salt (NaCl) when the density of Janus particles is low to moderate.
+At high density, JPs are found to form wormlike structures
 
-We include a background flow by replacing the third equation in
-\eqref{eq:stokes} with the condition $\mathbf{u}(\mathbf{x})
-\to \mathbf{u}_{\infty}(\mathbf{x})$ as $|\mathbf{x}| \to
-\infty$. To incorporate the far-field flow, we use the representation 
-\begin{align}
-\label{PowerMiranda}
-  {\bf u} = {\bf u}_{\infty} + \mathcal{K}\boldsymbol{\eta} + 
-    \sum_{i=1}^N \left(S(\cdot, {\bf a}_i) {\bf F}_i + 
-                 R(\cdot, {\bf a}_i) {\bf G}_i\right),
-\end{align}
-where $S$ and $R$ are stokeslets and rotlets supported at the respective
-particle centers~\cite{leal_2007} and $\mathcal{K}\boldsymbol{\eta}$ is a layer
-potential for the unknown density function $\boldsymbol{\eta}$. With the
-exception of the rigid body conditions, the
-representation~\eqref{PowerMiranda} automatically satisfies all the
-hydrodynamic equations including the far-field condition. The rigid
-body conditions follow by requiring the viscous stresses to vanish across
-the particle boundaries.
-%
-We will compare the behavior of our particle-based vesicles in Stokes
-flow to well-established models that enforce area incompressibility and
-volume conservation in vesicle membrane
-dynamics~\cite{torres-sanchez_millan_arroyo_2019,mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}.
-\S \ref{sec:preliminary_work} contains our preliminary results.
-%
-%Our
-%preliminary results show that the particle-based bilayers have the same
-%large area modulus as real lipid bilayer membranes, so we expect
-%realistic results from our flow simulations. Under moderate shear rates,
-%the vesicle elongates and takes on the tank-treading elliptical shape.
-%We can directly check for area compressibility and volume conservation
-%properties from particle simulations by tracking the change in area
-%density of the midplane as a function of shear flow rate, along with
-%evaluating the tangential divergence of the velocity.
-%
-%Bilayer membranes have a small permeability to
-%water~\cite{323e9a2f0c58487ea82518d7a1f96485}, and modelers often assume
-%a vesicle membrane that conserves volume. In our particle-based
-%approach, water motion across the bilayer is limited by the size of the
-%gaps between the particles, which is an artifact of coarse-graining.
-%Making these gaps smaller comes at the expense of numerical accuracy,
-%and we will assess if there is a reasonable trade-off between
-%approximate volume conservation and simulation complexity. 
-%
-%Finally, the particle-based vesicle bilayers have two distinct leaflets
-%consisting of the particles in contact with the vesicle interior, and
-%those in contact with the surrounding fluid. Since there is a nonzero
-%separation between these layers, an important effect we observe is that
-%the leaflets slide against one another under shear flow. This implies
-%that part of the viscous dissipation in the aqueous phase is enhanced by
-%intermonolayer friction~\cite{SHKULIPA2005823, ShkulipaThesis}.
-%Intermonolayer slip enters zero-thickness membrane models as a velocity
-%jump boundary condition and leads to multiple solution
-%states~\cite{schwalbe_vlahovska_miksis_2010}. In the present proposal,
-%intermonolayer slip is an artifact of monolayer independence and we can
-%control for slip as a function of shear rate, vesicle diameter, and
-%particle geometry.
+The Stokes equations in~\eqref{eq:stokes} are modified to incorporate the transport of ions as
+\begin{equation}
+\label{eq:stokes}
+\begin{aligned}
+  &-\mu \Delta \mathbf{u} + \nabla p = \Delta\psi\cdot\nabla\psi, \quad \mathbf{x} \in \Omega, \qquad
+  \nabla \cdot \mathbf{u} = 0,  \quad \mathbf{x} \in \Omega,\\
+  &\delta^2\Delta\psi = -\frac{1}{2}\left(n_+-n_-\right),\qquad
+  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\\
+  &{\bf j}_{\pm} = -\nabla n_{\pm \mp n_{\pm} \nabla\psi + Pe n_{\pm}\mathbf{u}.
+\end{aligned}
+\end{equation}
+The screen length $\rho$ is now a function of the ion concentrations: $\rho = \rho(n_+,n_-)$.
 

### 2021-11-05 NSF2021/Description/specificaim3.tex
yny

@@
 %
-\begin{wrapfigure}[11]{l}{0.47\textwidth}
+\begin{wrapfigure}[6]{l}{0.47\textwidth}
 \centerline{\includegraphics[width=0.46\textwidth]{Figures/fig2A_Chen2011_Science}}
@@
 \begin{aligned}
-  &-\mu \Delta \mathbf{u} + \nabla p = \Delta\psi\cdot\nabla\psi, \quad \mathbf{x} \in \Omega, \qquad
+  &-\Delta \mathbf{u} + \nabla p = \Delta\psi\cdot\nabla\psi, \qquad
   \nabla \cdot \mathbf{u} = 0,  \quad \mathbf{x} \in \Omega,\\
@@
   \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\\
-  &{\bf j}_{\pm} = -\nabla n_{\pm \mp n_{\pm} \nabla\psi + Pe n_{\pm}\mathbf{u}.
+  &{\bf j}_{\pm} = -\nabla n_{\pm} \mp n_{\pm} \nabla\psi + \mbox{Pe} n_{\pm}\mathbf{u},
 \end{aligned}
 \end{equation}
-The screen length $\rho$ is now a function of the ion concentrations: $\rho = \rho(n_+,n_-)$.
+where $\delta$ is the Debye length, $\mbox{Pe}$ is the Peclet number, a ratio between the convection and  thermal diffusion time scales.
+$n_{+}$ ($n_{-}$) is the concentration of cation (anion).
+The screen length $\rho$ in the HAP model is now a function of the ion concentrations: $\rho = \rho(n_+,n_-)$.
 

### 2021-11-06 NSF2021/Description/specificaim3.tex

@@
 The screen length $\rho$ in the HAP model is now a function of the ion concentrations: $\rho = \rho(n_+,n_-)$.
+
+Within this framework, we will first investigate the interaction between two Janus particles under HAP in an electrolytic solution described by the above
+equations.
+We will conduct analytical calculations to investigate the effects of ion transport on the hydrophobic attraction between two Janus particles using the reciprocal theorem as in \cite{BayatiNajafi2016} for two Janus particles with a small surface activity.
 

### 2021-11-06 NSF2021/Description/specificaim3.tex
yny

--- 2021-11-05 NSF2021/Description/specificaim3.tex
@@
 
-\subsubsection{Dynamics of a single Janus particle in ionic solutions}
-In experiments, Janus particles are often immersed in a solution of ions \cite{ChenWhitmer2011_Sci} or surfactants \cite{}.
+\subsubsection{Dynamics of a pair of Janus particles in ionic solutions\label{subsubsec:JP_electrolyte}}
+In experiments, Janus particles are often immersed in a solution of ions \cite{Chen2011_Science} or surfactants \cite{Goodwin2009}.
 In electrolytic solutions the interaction between salt and Janus particle gives 
-rise to a slip velocity (on the particle surface) that depends on the ion distribution and the zeta potential \cite{BayatiJCP2016} 
+rise to a slip velocity (on the particle surface) that depends on the ion distribution and the zeta potential \cite{BayatiNajafi2016_JCP} 
 (the potential difference between the Janus particle surface and the surrounding conducting fluid).
@@
 At very low salt concentrations, Janus particles repel one another electrostatically, whereas at high salt concentration, van der Waals
-forces cause Janus particles to aggregate irreversibly \cite{Goodwin2019}.
-At intermediate concentrations of monovalent salt, Janus particles are found to self assemble in the form of a small number of elemental units of building blocks \cite{Chen2011_Science}.
+forces cause Janus particles to aggregate irreversibly \cite{Goodwin2009}.
+At intermediate concentrations of monovalent salt, Janus particles are found to assemble in the form of a small number of elemental units of building blocks \cite{Chen2011_Science}.
 %
-\begin{wrapfigure}[6]{l}{0.47\textwidth}
-\centerline{\includegraphics[width=0.46\textwidth]{Figures/fig2A_Chen2011_Science}}
+\begin{wrapfigure}[7]{r}{0.45\textwidth}
   \vspace{-5pt}
-\caption{\label{fig:helices_of_JPs} \footnotesize Formation of helices of Janus particles as salt concentration increases \cite{Chen2011_Science}.}
+\centerline{\includegraphics[width=0.44\textwidth]{Figures/fig2A_Chen2011_Science}}
+  \vspace{-5pt}
+\caption{\label{fig:helices_of_JPs} \footnotesize Formation of helices of Janus particles as salt concentration increases from 3.8 mM NaCl  (left) to 5 mM NaCl (right)\cite{Chen2011_Science}.}
 \end{wrapfigure}
 %
-Figure~\ref{fig:helices_of_JPs} shows that Janus particles can self-assemble into a helix at high concentration of monovalent salt (NaCl) when the density of Janus particles is low to moderate.
-At high density, JPs are found to form wormlike structures
+Figure~\ref{fig:helices_of_JPs} shows that Janus particles can assemble into a helix at high concentration of monovalent salt (NaCl) when the volume fraction of Janus particles is low to moderate.
+At high volume fraction, helices of Janus particles form wormlike structures whose lifetime allow fusion of helices \cite{Chen2011_Science}.
 
-The Stokes equations in~\eqref{eq:stokes} are modified to incorporate the transport of ions as
+We propose to investigate the effects of ion transport and distribution on the self-assembly of Janus particles within the HAP framework as follows.
+First the Stokes equations in~\eqref{eq:stokes} are modified to incorporate the transport of ions as
 \begin{equation}
-\label{eq:stokes}
+\label{eq:EKstokes}
 \begin{aligned}
@@
   &\delta^2\Delta\psi = -\frac{1}{2}\left(n_+-n_-\right),\qquad
-  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\\
-  &{\bf j}_{\pm} = -\nabla n_{\pm} \mp n_{\pm} \nabla\psi + \mbox{Pe} n_{\pm}\mathbf{u},
+  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\qquad {\bf j}_{\pm} = -\nabla n_{\pm} \mp n_{\pm} \nabla\psi + \mbox{Pe} n_{\pm}\mathbf{u},
 \end{aligned}
 \end{equation}
-where $\delta$ is the Debye length, $\mbox{Pe}$ is the Peclet number, a ratio between the convection and  thermal diffusion time scales.
+where $\delta$ is the ratio of Debye screening length (inversely proportional to the square root of
+ion concentration) to the particle size, 
+$\mbox{Pe}$ is the Peclet number, a ratio between the convection and  thermal diffusion time scales.
 $n_{+}$ ($n_{-}$) is the concentration of cation (anion).
-The screen length $\rho$ in the HAP model is now a function of the ion concentrations: $\rho = \rho(n_+,n_-)$.
+In the limit of small $\delta$, PI Young and collaborator Y.
+Mori (U Penn) used asymptotic analyses to show that the jump in electric potential $\psi$ across the interface (zeta potential on the Janus particle surface)
+may give rise to different physical consequences such as electrophoresis \cite{Mori2018_JFM}.
+%
+An important question to address is: {\it How would such electrophoresis be affected by the HAP between two Janus particles?} 
+As the first part of specific aim 3, we will address this important question.
+Results from this effort will help elucidate the effects of salt concentration on the assembly of Janus particles (\S~\ref{subsubsec:em_effects}).
 
-\subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
+We couple the electrokinetics in~\eqref{eq:EKstokes} with the mobility Janus particles in a viscous solvent through the velocity field, ion distribution, and the hydrophobic potential.  
+First the screen length $\rho$ in the HAP model is now a function of the  cation concentrations: $\rho = \rho(n_+) =
+\rho_0/\sqrt{1+c n_+}$ with a dimensionless parameter $c$. 
+%
+Secondly the value of the HAP may depend on the distribution of ions and electric potential right next to the particle surface \cite{Mori2018_JFM}.
+Within this framework, we will first investigate the interaction between two Janus particles under HAP in an electrolytic solution described by the above
+equations.
+We will conduct analytical calculations to investigate the effects of ion transport on the hydrophobic attraction between two Janus particles using the reciprocal theorem as in \cite{BayatiNajafi2016_JCP} for two Janus particles with a small surface activity.
+
+\subsubsection{Electromechanical effects on the dynamic assembly of Janus particles \label{subsubsec:em_effects}}
+Results from the proposed work in \S~\ref{subsubsec:JP_electrolyte} will shed light on how the electrokinetics described in~\eqref{eq:EKstokes}
+may be simplified to a dielectric-like model where the bulk charges are constant, and the fluid flow and particle mobility are determined by the surface charge and the zeta potential as shown in \cite{Mori2018_JFM}.
+Under such simplification, the modified~\eqref{eq:EKstokes} may be re-formulated into integral forms.
+PI Young will conduct the asymptotic analyses to derive the modified~\eqref{eq:EKstokes}, and work with PI Quaife to design a numerical algorithm to simulate the modified system using integral formulation.
+We will first investigate the effects of salt concentration on the assembly of Janus particles to form helices, as shown in figure~\ref{fig:helices_of_JPs}.
+
+With these results, the PIs will be ready to make quantitative connections between the a Janus particle membrane and a lipid bilayer membrane in an electrolytic solution.
 In recent experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending

### 2021-11-06 NSF2021/Description/specificaim2.tex

@@
-\subsection{Specific Aim 2: Efficient, high-order methods for large-scale simulations}
+\subsection{Specific Aim 2: Efficient, high-order methods for
+large-scale simulations}
 % ----------------------------------------------------------------------
@@
 small-scale processes that utilize capillary forces and van der Waals
-interactions to coordinate movement
-and bind microscopic components in solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}.
-Additionally, hydrodynamic interactions are central to fabricate complex,
-three-dimensional microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010}.
-Hydrodynamic effects cannot
-be ignored since they, like for the rates of biological functions 
-like pore dynamics~\cite{RYHAM20112929}, set the rate of dissipation.
-%
-In Specific Aim 2, we propose to develop efficient high-order numerical
-methods to simulate dynamic assembly of particles under HAP potential in
-a viscous solvent. 
-%
-%
-%hydrodynamics effects by em
-%particles in a solvent. 
-%
-% Results from these proposed numerical simulations will be useful to 
-% Finally, coarse-grained and molecular
-%dynamics theories include water either explicitly or implicitly in their
-%models. 
-%
-%The immediate goal of the present proposal is to simulate
-%vesicle bilayers in external flows, where the bilayers are represented
-%by a self-assembled collection of rigid particles.
-%
-As described in~\eqref{eq:stokes} and illustrated in
+interactions to coordinate movement and bind microscopic components in
+solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}. Additionally,
+hydrodynamic interactions are central to fabricate complex,
+three-dimensional microstructures~\cite{Dasgupta2017, Leong2007,
+Reynolds2019, Cho2010}. Hydrodynamic effects cannot be ignored since
+they, like for the rates of biological functions like pore
+dynamics~\cite{RYHAM20112929}, set the rate of dissipation. In Specific
+Aim 2, we propose to develop efficient high-order numerical methods to
+simulate dynamic assembly of particles under HAP potential in a viscous
+solvent. As described in~\eqref{eq:stokes} and illustrated in
 Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
@@
 hydrophobic stress balance. 
-
-%While hydrophobic attraction causes the particles to self-assemble indepedently of the dissipation mechanism, the trajectories and
-%equilibrium configurations depend on the fact that the particles travel through a viscous environment.
+\todo[inline]{BQ: Also will have the new Allen-Cahn type equation}
 
 \label{subsec:specific_aim_2}
-%\begin{figure}[h]
 \begin{wrapfigure}[14]{r}{0.61\textwidth}
@@
 \end{wrapfigure}
-%\end{figure}
 The HAP model requires solving exterior Dirichlet problems for the
@@
 high-order or spectral accuracy is attainable with appropriate
-quadrature methods. PI RR and YNY's previous work~\cite{Fu2018_SIAM}
-demonstrated that BIEs are a powerful tool to simulate two-dimensional
-suspensions of amphiphilic particles. In addition to improving
-two-dimensional simulations, the present proposal extends the results to three
-dimensions using a three-dimensional BIE formulation of the
+quadrature methods. The PIs have demonstrated that BIEs are a powerful
+tool to simulate two-dimensional suspensions of amphiphilic
+particles~\cite{Fu2018_SIAM, FuQuRyYo20}. In addition to improving
+two-dimensional simulations, the present proposal extends the results to
+three dimensions using a three-dimensional BIE formulation of the
 screened Laplace equation~\cite{ying_2006} and a well-conditioned BIE
@@
 
-Significant challenges to solving BIEs include solving dense linear
-systems, developing preconditioning strategies, and developing
-quadrature methods for nearly-singular integrands. These
-challenges are described in \S\ref{subsec:NumericalIssues}. However,
-numerical errors can still lead to unphysical contact between bodies. We
-propose two algorithms to avoid contact in \S\ref{subsec:timeStepping}.
-An identity to accurately compute the hydrophobic stress is in
-\S\ref{subsec:reciprocal}. Then, proposed work for well-conditioned BIE
-formulations of fluctuating hydrodynamics are described in
-\S\ref{subsec:fluctuating}.
+Significant challenges to solving BIEs include solving largely stem from
+solving dense linear systems. \S\ref{subsec:NumericalIssues}
+describes how we will combine preconditioning strategies with fast
+summation methods to accelerate the time to solution,
+\S\ref{subsec:timeStepping} describes adaptive time stepping methods,
+and \S\ref{subsec:AC} describes how the non-linear Allen-Cahn
+equation~\eqref{eqn:???} will be iteratively solved using BIE
+formulations.
 
 % ----------------------------------------------------------------------
-\subsubsection{Numerical challenges}
+\subsubsection{Accelerating the iterative solvers}
 \label{subsec:NumericalIssues}
@@
 %
-\begin{wrapfigure}[20]{r}{2.5in}
-\vspace*{-13pt}
-\centerline{\includegraphics[width=2.4in]{figures/integrands}}
-\vspace*{-13pt}
-  \caption{{\footnotesize The Fourier modes of
-  $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
-  $|\mathbf{x_0}| = 0.99$, $\mathbf{y} \in \partial\Omega$, and
-  $\Omega$ is the unit disk. The trapezoid rule applied to the red
-  integrand has large amounts of error, but the trapezoid rule is much
-  more accurate when applied to the blue integrand. Since the difference
-  between the red and blue curves can be accurately computed with the
-  barycentric quadrature rule, the quadrature error applied to layer
-  potentials for the screened Laplace equation will be uniformly bounded
-  in $\Omega$.}}
-\label{fig:integrands}
-\end{wrapfigure}
+%\begin{wrapfigure}[20]{r}{2.5in}
+%\vspace*{-13pt}
+%\centerline{\includegraphics[width=2.4in]{figures/integrands}}
+%\vspace*{-13pt}
+%  \caption{{\footnotesize The Fourier modes of
+%  $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
+%  $|\mathbf{x_0}| = 0.99$, $\mathbf{y} \in \partial\Omega$, and
+%  $\Omega$ is the unit disk. The trapezoid rule applied to the red
+%  integrand has large amounts of error, but the trapezoid rule is much
+%  more accurate when applied to the blue integrand. Since the difference
+%  between the red and blue curves can be accurately computed with the
+%  barycentric quadrature rule, the quadrature error applied to layer
+%  potentials for the screened Laplace equation will be uniformly bounded
+%  in $\Omega$.}}
+%\label{fig:integrands}
+%\end{wrapfigure}
 Discretizations of carefully chosen BIEs can be solved with a
@@
 multigrid~\cite{hem-sch1981, sch1982} will be investigated.
-
-Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
-particles, and this results in nearly-singular integrands. Quadrature
-methods for these integrands have received a lot of attention in two and
-three dimensions~\cite{alpert, kapur, sidi, duffy, bruno1, bruno2,
-davis_1984, graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003,
-khayat_2005, schwab_1992, ying_2006, beale1, schwab_1992, ggq1, ggq2,
-ggq3, helsing_2008a, helsing_tutorial_2012, klockner2013jcp, qbx2,
-wala2019jcp, af2018sisc, siegel2018jcp, rachh2017jcp, ding2019arxiv,
-bar2014}. The trapezoid rule is the workhorse for two-dimensional BIEs
-since it achieves spectral accuracy when integrands are not
-nearly-singular~\cite{tre-wei2014}. To address nearly-singular
-integrands of two-dimensional BIEs, we will use a {\em barycentric
-quadrature rule} that only requires a slight modification of the
-trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this method
-requires the layer potential to satisfy Laplace or Stokes
-equations~\cite{bar-wu-vee2015, chi-moo-qua2020}, but the PIs will
-extend the method to layer potentials for the screened Laplace equation.
-This will be done by recognizing that the fundamental solution of the
-screened Laplace equation can be decomposed as $K(\mathbf{x},\mathbf{y})
-= K_1(\mathbf{x},\mathbf{y}) + K_2(\mathbf{x},\mathbf{y})$, where
-$K_1(\mathbf{x},\mathbf{y}) = -\log|\mathbf{x} - \mathbf{y}|$ and
-$K_2(\mathbf{x},\mathbf{y}) = K(\mathbf{x},\mathbf{y}) + \log|\mathbf{x}
-- \mathbf{y}|$. Then, layer potentials involving
-$K_1(\mathbf{x},\mathbf{y})$ can be accurately computed with the
-barycentric quadrature rule~\cite{ioa-pap-per1991}, and layer potentials
-involving $K_2(\mathbf{x},\mathbf{y})$ can be accurately computed with
-the trapezoid rule since the kernel is bounded for all $\mathbf{x}$ and
-$\mathbf{y}$. The proposed method is demonstrated in
-Figure~\ref{fig:integrands}, where the amplitude of the Fourier modes of
-$K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ are
-plotted. The quadrature error of the trapezoid rule is the sum of the
-unresolved Fourier modes.
+%
+%Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
+%particles, and this results in nearly-singular integrands. Quadrature
+%methods for these integrands have received a lot of attention in two and
+%three dimensions~\cite{alpert, kapur, sidi, duffy, bruno1, bruno2,
+%davis_1984, graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003,
+%khayat_2005, schwab_1992, ying_2006, beale1, schwab_1992, ggq1, ggq2,
+%ggq3, helsing_2008a, helsing_tutorial_2012, klockner2013jcp, qbx2,
+%wala2019jcp, af2018sisc, siegel2018jcp, rachh2017jcp, ding2019arxiv,
+%bar2014}. The trapezoid rule is the workhorse for two-dimensional BIEs
+%since it achieves spectral accuracy when integrands are not
+%nearly-singular~\cite{tre-wei2014}. To address nearly-singular
+%integrands of two-dimensional BIEs, we will use a {\em barycentric
+%quadrature rule} that only requires a slight modification of the
+%trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this method
+%requires the layer potential to satisfy Laplace or Stokes
+%equations~\cite{bar-wu-vee2015, chi-moo-qua2020}, but the PIs will
+%extend the method to layer potentials for the screened Laplace equation.
+%This will be done by recognizing that the fundamental solution of the
+%screened Laplace equation can be decomposed as $K(\mathbf{x},\mathbf{y})
+%= K_1(\mathbf{x},\mathbf{y}) + K_2(\mathbf{x},\mathbf{y})$, where
+%$K_1(\mathbf{x},\mathbf{y}) = -\log|\mathbf{x} - \mathbf{y}|$ and
+%$K_2(\mathbf{x},\mathbf{y}) = K(\mathbf{x},\mathbf{y}) + \log|\mathbf{x}
+%- \mathbf{y}|$. Then, layer potentials involving
+%$K_1(\mathbf{x},\mathbf{y})$ can be accurately computed with the
+%barycentric quadrature rule~\cite{ioa-pap-per1991}, and layer potentials
+%involving $K_2(\mathbf{x},\mathbf{y})$ can be accurately computed with
+%the trapezoid rule since the kernel is bounded for all $\mathbf{x}$ and
+%$\mathbf{y}$. The proposed method is demonstrated in
+%Figure~\ref{fig:integrands}, where the amplitude of the Fourier modes of
+%$K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ are
+%plotted. The quadrature error of the trapezoid rule is the sum of the
+%unresolved Fourier modes.
 
@@
 
-%
-\begin{wrapfigure}[13]{r}{0.30\textwidth}
-\centerline{\includegraphics[width=0.29\textwidth]{figures/BIError.pdf}}
-  \vspace{-8pt}
-\caption{
-\label{fig:bierror}  
-\footnotesize The false color map shows how numerical quadrature of
-  layer potentials loses accuracy near the particle boundaries.  The
-  color bar is for $\log_{10}.$}
-\end{wrapfigure}
-%
+%%
+%\begin{wrapfigure}[13]{r}{0.30\textwidth}
+%\centerline{\includegraphics[width=0.29\textwidth]{figures/BIError.pdf}}
+%  \vspace{-8pt}
+%\caption{
+%\label{fig:bierror}  
+%\footnotesize The false color map shows how numerical quadrature of
+%  layer potentials loses accuracy near the particle boundaries.  The
+%  color bar is for $\log_{10}.$}
+%\end{wrapfigure}
+%%
 Our previous work avoided particle contact through Lennard-Jones body
@@
 
-%-------------------------------------------------------------------------------
-\subsubsection{Novel reciprocal identities}
-\label{subsec:reciprocal}
-The force and torque formulas~\eqref{forceandtorque} use the
-hydrophobic stress along the particle boundaries. Unfortunately,
-layer potentials for $\nabla u$ involve hyper-singular integrals and
-this introduces large amounts of quadrature error on the particle
-boundaries (Figure~\ref{fig:bierror}). Therefore, it is useful to devise
-reciprocal identities for the force and torque on body $i$ that do not
-require integration along body $i$. One identity, that we have proved,
-is
-\begin{align}
-    \label{eq:reciprocal}
-{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
-{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf
-  x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} +
-  \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, 
-\end{align}
-for $i=1,\ldots,N$. Here, $u_i$ is the solution of the screened Laplace
-equation when only the contribution from particle $i$ is considered and
-$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j \mathbf{I} +
-\rho\left((\nabla u_i \cdot \nabla u_j) \mathbf{I} - 2 \nabla u_i
-\otimes \nabla u_j\right)$. Equation~\eqref{eq:reciprocal} does not
-require knowledge of $\nabla u$ on particle boundary $i$, and this is
-enormously beneficial for calculating the hydrophobic force and torque.
+\subsubsection{Iterative methods for the Allen-Cahn HAP model}
+\label{subsec:AC}
+\todo[inline]{Write once the model is finalized}
 
-% ----------------------------------------------------------------------
-\subsubsection{Fluctuating hydrodynamics}
-\label{subsec:fluctuating}
-Once algorithms that address quadrature, adaptive time stepping, and
-contact are implemented, we will embark on incorporating fluctuating
-hydrodynamics that are especially important at scales of amphiphilic
-particles. Bao et al.~\cite{Bao17,Bao18} developed two-dimensional BIE
-formulations for Brownian rigid bodies. To satisfy the covariance of the
-rigid body velocities, they use an ill-conditioned, first-kind integral
-equation method. The proposed work will consider a layer potential
-formulation that has much better conditioning properties. This strategy
-was attempted in~\cite{Bao18}, but they claim that a necessary
-regularization of the covariance matrix leads to a drastic loss of
-accuracy in numerical fluctuation-dissipation balance. However, only one
-regularization strategy was considered, and as PI BQ has shown in
-previous work, the regularization choice significantly affects the
-resulting physics~\cite{ong-chr-qua2017}. Therefore, different
-regularization strategies will be investigated with the goal of finding
-well-conditioned BIE formulations that control the accuracy of the
-fluctuation-dissipation balance.
+%%-------------------------------------------------------------------------------
+%\subsubsection{Novel reciprocal identities}
+%\label{subsec:reciprocal}
+%The force and torque formulas~\eqref{forceandtorque} use the
+%hydrophobic stress along the particle boundaries. Unfortunately,
+%layer potentials for $\nabla u$ involve hyper-singular integrals and
+%this introduces large amounts of quadrature error on the particle
+%boundaries (Figure~\ref{fig:bierror}). Therefore, it is useful to devise
+%reciprocal identities for the force and torque on body $i$ that do not
+%require integration along body $i$. One identity, that we have proved,
+%is
+%\begin{align}
+%    \label{eq:reciprocal}
+%{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
+%{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf
+%  x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} +
+%  \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, 
+%\end{align}
+%for $i=1,\ldots,N$. Here, $u_i$ is the solution of the screened Laplace
+%equation when only the contribution from particle $i$ is considered and
+%$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j \mathbf{I} +
+%\rho\left((\nabla u_i \cdot \nabla u_j) \mathbf{I} - 2 \nabla u_i
+%\otimes \nabla u_j\right)$. Equation~\eqref{eq:reciprocal} does not
+%require knowledge of $\nabla u$ on particle boundary $i$, and this is
+%enormously beneficial for calculating the hydrophobic force and torque.
+%
+%% ----------------------------------------------------------------------
+%\subsubsection{Fluctuating hydrodynamics}
+%\label{subsec:fluctuating}
+%Once algorithms that address quadrature, adaptive time stepping, and
+%contact are implemented, we will embark on incorporating fluctuating
+%hydrodynamics that are especially important at scales of amphiphilic
+%particles. Bao et al.~\cite{Bao17,Bao18} developed two-dimensional BIE
+%formulations for Brownian rigid bodies. To satisfy the covariance of the
+%rigid body velocities, they use an ill-conditioned, first-kind integral
+%equation method. The proposed work will consider a layer potential
+%formulation that has much better conditioning properties. This strategy
+%was attempted in~\cite{Bao18}, but they claim that a necessary
+%regularization of the covariance matrix leads to a drastic loss of
+%accuracy in numerical fluctuation-dissipation balance. However, only one
+%regularization strategy was considered, and as PI BQ has shown in
+%previous work, the regularization choice significantly affects the
+%resulting physics~\cite{ong-chr-qua2017}. Therefore, different
+%regularization strategies will be investigated with the goal of finding
+%well-conditioned BIE formulations that control the accuracy of the
+%fluctuation-dissipation balance.

### 2021-11-06 NSF2021/Description/specificaim1.tex
draft background, SA 1 ready

@@
 
-The goal of Specific Aim 1 is to investigate generalizations of the
-screened Laplace equation for different soft matter systems.
+The proposed research aims to provide fundamental insight into the
+self-assembly dynamics of amphiphilic particles. These results will
+facilitate optimal design of smart materials by tuning the geometry and
+properties of the amphiphilic particles.
+The theories presented in Background pertain to one-dimensional problems
+for a water region separating parallel surfaces.
+In two and higher dimensions, there 
+is an explosion of possible phenomena.
+Thus, Specific Aim 1 concerns  improving on established models and theory.
 
-\begin{itemize}
-  \item Include ions in suspension
-  \item Discussed in Sylvie Roke's talk---I added the slides to the repo
-\end{itemize}
+\subsection{Problem formulation}
+The governing equations of the model contain two parts.
+The first part is the mobility problem for a collection of rigid particles
+immersed in a viscous solvent. Here, the issue lies in developing 
+numerical routines that can handle integral equation calculations for 
+large particle numbers with proximal boundaries.  
+Assuming inertial terms are negligible, the Stokes equations are
+\begin{alignat}{3}
+\label{eq:stokes1}
+  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
+    && \xx \in \Omega, \\
+\label{eq:stokes2}
+  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
+\label{eq:stokes3}
+  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
+\end{alignat}
+%
+where $\uu$ is the velocity, $p$ is the
+pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
+The domain $\Omega$ is the fluid region surrounding 
+the collection of $N_p$-many particles. 
+Since the particles are rigid, there is the no-slip boundary condition
+\begin{align}
+\label{eq:rigid_bc}
+  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
+    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
+\end{align}
+where $\Gamma_i$ is the boundary of particle.
+where $\vv_i$ is the translational velocity and $\omega_i$ is its
+angular velocity. 
+The process of finding the
+translational and angular velocities given the forces and torques is
+referred to as the mobility problem.
+Given forces $\FF_i$ and torques $T_i$ acting on each
+particle, we seek a velocity and pressure satisfying \eqref{eq:stokes1}-\eqref{eq:rigid_bc} 
+and
+\begin{equation}
+  \label{eq:force}
+  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i,\quad 
+  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \, \dif s = T_i, \qquad i=1,\ldots,N_b,
+\end{equation}
+where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
+\right)$ is the hydrodynamic stress tensor (pressure tensor) and
+$\nnu$ is the particle outward normal.
 
+The second part is the hydrophobic 
+attraction.  To define it, we introduce 
+the mean field free energy
+\begin{equation}
+\label{eq:free_energy}
+F = \min_u C \int_{\Omega}  \tfrac{1}{2} |\nabla u|^2 + f(u) \,dx
+\end{equation}
+where $u$ is the order parameter for the excess number of hydrogen
+bonds per water molecule, $C$ is a constant, and the minimization 
+occurs over all $u$ satisfying $u = u_0$ on the boundary where $u_0$
+is the degree of hydrophobicity.
+
+As an illustration, in one-dimension the minimizer in \eqref{eq:free_energy} 
+solves $-u''(x) + f'(u(x)) = 0$ for $0 < x < b$, $u(0) = u_0(0),$ $u(b) = u_0(b)$ 
+and the free energy takes the form $F(b)$
+where $b$ is the  distance of separation between the hydrophobic surfaces.
+The hydrophobic force $-F'(b)$ the variation of free energy with respect to $b$  \cite{ErLjCl89, GoKl94}.
+
+In two and higher spatial dimensions, the situation is more complicated.
+That is because the particles rotate and translate individually.  Here, the 
+minimizer  in \eqref{eq:free_energy}  satisfies 
+\begin{equation}
+\label{eq:SL}
+-\Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = u_0  \text{ on } \partial \Omega.
+\end{equation}
+The hydrophobic forces are torques are
+\begin{equation}
+  \label{eq:hydrophobicAttraction}
+  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
+    \quad 
+  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu) \dif s.
+\end{equation}
+where the surface force density 
+\begin{align}
+  \label{eq:stress}
+\mathbf{T}
+= C \left[ f(u) \mathbf{I} +  \left(|\nabla
+  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)\right]
+\end{align}
+comes from the variation of free energy with respect to particle 
+position and orientation~\cite{Bandle2015, Schiffer1954, Grinfeld2010}. 
+The remaining part of the force comes from excluded volume repulsion. 
+The density \label{eq:stress}  was introduced
+by~\cite{Fu20} and is responsible for forming particle aggregates that
+sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).
+
+\subsection{Janus-particle self-assembly} 
+The PI will collaborate with Dr. Bradley in the Department of 
+Polymer and Engineering Science at the University of Massachusetts Amherst
+on numerical and experimental investigations
+of synthesis and assembly of soft matter materials.
+Dr. Bradley's lab specializes in synthesizing multiphasic and anisotropic colloids.
+Applications in this area enables include cargo-carrying capacity, 
+catalytic activity, or stimuli-responsive shape-change to amplify colloid utility for a wide 
+range of  spanning environmental remediation to drug delivery. 
+The main challenge is the ability decouple particle surface properties, 
+which control particle-particle and particleiiinterface interactions, 
+from auxiliary functions, such as catalytic or cargo-carrying capacities
+\cite{}.
+
+The collaboration will use numerical methods to predict parameter regimes 
+to control particle-particle interactions.  Preliminary numerical experiments
+show that controlling for the degree of hydrophobicity $u_0$ yields different
+self-organized structures.  The simulations in Figure [] show the equilibrium
+state for 100 particles with initially random position and orientation
+with linear response $f(u) = u^2$.  The 
+boundary conditions $u_0$ are for \textbf{(i)} a polar colloid with $u_0$ odd about the 
+particle axis, \textbf{(ii)} a periodic normal distribution with random 
+standard deviation but normalized square moment, and  
+\textbf{(iii)} a particle more hydrophobic on one side than the other. 
+Simulation \textbf{(ii)}  produces a single bilayer while simulation \textbf{(iii)}
+produces a multilamellar phase.  Simulation \textbf{(i)} is analogous to 
+magnetically and electrically charged Janus particles, but rather than producing
+isolated chains, the simulation yields a network of chains.
+All in all, the hydrophobic attraction formalism controls for morphology through 
+simple modification of the boundary conditions.
+
+Our next steps are to determine if the phenomenon we report are robust.
+This involves categorizing all possible the self assembly behavior
+and assessing the sensitivity of morphologies to boundary condition positionally
+and particle geometry.  At the same time, we can  
+translate phenomenological parameters parameters
+of the model in to contact angles. In Specific Aim 3, we discuss how to include 
+surface charge as this is one of the main surface properties that must be decoupled.
+In future studies, we will also include liquid crystal background flows.
+
+\subsection{Hydrophobic forces as capillary wetting} 
+The measured hydrophobic attraction follows an exponential function
+in the 10 to 100 nanometer range of separation.  Below 10 nm, there 
+is an amplification of force and the attraction follows a much steeper 
+force law \cite{Lietal05}.
+
+One way to mathematically account for this change in force profile is by
+allowing for phases in the order parameter $u$.
+Motivated by capillary wetting, theoretical soft matter biophysicist Gerhard Gompper 
+introduced such a model in \cite{GoHaKo94}. This was a one-dimensional
+model which we will extend to two-dimensions (at first) and follow up on the parameter study. 
+The order parameter is the mean number of nearest neighbors per water molecule
+with distinguished values $u_1$ for five-coordinated water in the bulk phase and 
+the scalar value $u_0$ for four-coordinated water at the hydrophobic surfaces.  
+A slanted double well-potential $f(u)$ with local minima at $u_0$ and $u_1$ 
+characterizes the energy landscape of homogeneous water.   The absolute minimum
+is at $u_1$.
+
+When particles are well-separated, the energetic cost for filling the interstitial region 
+with $u_0$-phase water is energetically prohibitive and so there is a phase shift
+from the $u_0$ to $u_1$ water order occurring at the boundary of each particle. 
+Here, the attraction landscape is more or less identical to the linear response theory 
+we have explored and the decay length of attraction is set by $\sqrt{1/f''(u_1)}$.
+Conversely, when particles are proximal it energetically favorable to coalesce 
+the $u_0$-phase and here there will be a circumscribing phase transition.
+Here, the energetics are dominated by a decay length  $\sqrt{1/f''(u_0)}$
+for the linear response around four-coordinated water plus the energy 
+per length cost of the phase transition (energy per area in three dimensions).
+This extra line tension, which can be significant depending on the shape of the 
+energy wells, was not explored in Gompper's paper or later.
+
+\textbf{How will we know the results are accurate?}
+The experimental data on hydrophobic attraction between 
+hydrocarbon coated mica cylinders well-established. 
+The literature contains data for a number of solvents and hydrocarbon species.
+Our numerical experiments will choose particle geometries that replicate the 
+experimental setups, mainly apposing hydrocarbon coated cylinders. 
+We will directly compare the numerical attraction data with the measurements.
+Some of the model parameters, like $C$ and  $f''(u_1)$, directly connect 
+to long-range decay lengths and energy cost of creating hydrophobic-water
+interfaces with established ranges of values. Other parameters, like the well-structure,
+are fit to the measured data. 
+These base-line simulations will allow us to move on to simulating
+colloidal suspensions.
+
+\textbf{What will we do if the results fail?}
+Other approaches will be required if the modified phenomenological theory 
+fails to recreated the hydrophobic force curves for any reasonable 
+set of parameter values.  One such approach is to consider 
+Gaussian fluctuation. 
+So far we, have studied energy minimizers of the Landau-Ginzburg 
+free energy functional. However,  hydrophobic force measurements are carried out at finite 
+temperatures, thermal fluctuations should also be considered. 
+A relative simple way to do so is to study Gaussian fluctuations.
+Here, the Gaussian fluctuations are calculated by expanding the 
+free energy functional around the saddle point solution.
+The fluctuation energy involves calculation of the eigenfunctions of the second variation
+of the free energy.
+
+Another approach is to modify the setup to include convection in the water structure. 
+In the short-range experimental data, particle velocities approach 200 nm s$^{-1}$.
+The measurements, however, do not account for water that must be 
+expelled between the two approach particles. This water movement is directly 
+accounted for by our Stokes mobility solver.  In the phenomenological model,
+the order parameter adjusts to the new particle positions instantaneously.  Instead,
+it may be required that the order parameter solves the parabolic version of \eqref{eq:SL}
+with a convection given by the underlying Stokes flow. 
+If the convective effect is significant, then a significant 
+set of measurements will need to be reevaluated.
+
+%
+% The following commented out Nov 6, 2021.
+%
+%
 \begin{comment}

### 2021-11-07 NSF2021/Description/specificaim2.tex
working on SA2

@@
 simulate dynamic assembly of particles under HAP potential in a viscous
-solvent. As described in~\eqref{eq:stokes} and illustrated in
-Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
-equations for an incompressible, viscous fluid, and these equations are
-coupled to the screened-Laplace equation~\eqref{SL} through viscous and
-hydrophobic stress balance. 
-\todo[inline]{BQ: Also will have the new Allen-Cahn type equation}
+solvent. As described in~\eqref{eq:stokes1}--\eqref{eq:stokes3} and
+illustrated in Figure~\ref{fig:flow_map}, the solvent phase is modeled
+by the Stokes equations for an incompressible, viscous fluid, and these
+equations are coupled to the screened-Laplace equation~\eqref{eq:SL}
+through viscous and hydrophobic stress balance.
 
@@
 \end{wrapfigure}
-The HAP model requires solving exterior Dirichlet problems for the
-screened Laplace equation and the Stokes mobility problem at each time
-step in complex domains such as in Figure~\ref{fig:domain}. If
-discretizing these equations with stencil-based numerical methods, the
-computational domain must be truncated, the fluid volume must be
-discretized, and artificial boundary conditions must be imposed. The
-artificial boundary conditions introduce additional error, and
-discretizing the volume results in an excessively large system of
-equations. Moreover, it is difficult to obtain high-order
-discretizations when the boundary surfaces are irregular. Alternatively,
-since we are solving constant-coefficient linear elliptic partial
-differential equations (PDEs), the solutions can be represented with
-layer potentials
+The HAP model requires solving exterior Dirichlet problems for the order
+parameter~\eqref{eq:SL} and the Stokes
+equations~\eqref{eq:stokes1}--\eqref{eq:stokes2}. If discretizing these
+equations with stencil-based numerical methods, the computational domain
+must be truncated, the fluid volume must be discretized, and artificial
+boundary conditions must be imposed. The artificial boundary conditions
+introduce additional error, and discretizing the volume results in an
+excessively large system of equations. Moreover, it is difficult to
+obtain high-order discretizations when the boundary surfaces are
+irregular.
+
+Alternatively, we will take advantage of the linearity of the Stokes
+equations, and also apply a Newton's method to the HAP
+model~\eqref{eq:SL}, where each iteration requires the solution of
+linear elliptic PDEs. Then we can represent solutions of these elliptic
+PDEs as layer potentials
 \begin{align}
@@
 $\mathbf{x}_0 \in \partial\Omega$ with the limit of
-equation~\eqref{eq:LP} as $\mathbf{x}\rightarrow \mathbf{x}_0$, a
-boundary integral equation (BIE) for the density function is formed.
+equation~\eqref{eq:LP} as $\xx \rightarrow \xx_0$, a boundary integral
+equation (BIE) for the density function is formed.
 
@@
 and \S\ref{subsec:AC} describes how the non-linear Allen-Cahn
-equation~\eqref{eqn:???} will be iteratively solved using BIE
+equation~\eqref{eq:SL} will be iteratively solved using BIE
 formulations.
+
+\subsubsection{Iterative methods for the Allen-Cahn HAP model}
+\label{subsec:AC}
+In the PIs collaboration, they have developed numerical methods to
+solve~\eqref{eq:SL} when $f(u) = u^2$. With this choice of $f(u)$, the
+resulting PDE is the linear screened Laplace equation which is
+efficiently solved with a double-layer potential representation. For a
+more general $f$, such as a double well potential, we will interpret the
+solution of~\eqref{eq:SL} as a root finding problem for the operator
+\begin{align*}
+  F[u] = -\rho \Delta u + f'(u).
+\end{align*}
 
@@
 
-\subsubsection{Iterative methods for the Allen-Cahn HAP model}
-\label{subsec:AC}
-\todo[inline]{Write once the model is finalized}
-
 %%-------------------------------------------------------------------------------

### 2021-11-07 NSF2021/Description/specificaim1.tex
fixed citations in background, SA1

@@
 
-\subsection{Specific Aim 1: Measuring material properties of amphiphile self-assembly}
+\subsection{Specific Aim 1: Measuring material properties of amphiphile
+  self-assembly}
 \label{subsec:specific_aim_1}
@@
 The theories presented in Background pertain to one-dimensional problems
-for a water region separating parallel surfaces.
-In two and higher dimensions, there 
-is an explosion of possible phenomena.
-Thus, Specific Aim 1 concerns  improving on established models and theory.
+for a water region separating parallel surfaces.In two and higher
+dimensions, there is an explosion of possible phenomena. Thus, Specific
+Aim 1 concerns improving on established models and theory.
 
 \subsection{Problem formulation}
-The governing equations of the model contain two parts.
-The first part is the mobility problem for a collection of rigid particles
-immersed in a viscous solvent. Here, the issue lies in developing 
-numerical routines that can handle integral equation calculations for 
-large particle numbers with proximal boundaries.  
-Assuming inertial terms are negligible, the Stokes equations are
+The governing equations of the model contain two parts. The first part
+is the mobility problem for a collection of rigid particles immersed
+in a viscous solvent. Here, the issue lies in developing numerical
+routines that can handle integral equation calculations for large
+particle numbers with proximal boundaries. Assuming inertial terms are
+negligible, the Stokes equations are
 \begin{alignat}{3}
@@
 %
-where $\uu$ is the velocity, $p$ is the
-pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
-The domain $\Omega$ is the fluid region surrounding 
-the collection of $N_p$-many particles. 
-Since the particles are rigid, there is the no-slip boundary condition
+where $\uu$ is the velocity, $p$ is the pressure, $\uu_\infty$ is
+the background flow, and $\mu$ is the constant viscosity. The domain
+$\Omega$ is the fluid region surrounding the collection of
+$N_p$-many particles. Since the particles are rigid, there is the
+no-slip boundary condition
 \begin{align}
@@
 \end{align}
-where $\Gamma_i$ is the boundary of particle.
-where $\vv_i$ is the translational velocity and $\omega_i$ is its
-angular velocity. 
-The process of finding the
-translational and angular velocities given the forces and torques is
-referred to as the mobility problem.
-Given forces $\FF_i$ and torques $T_i$ acting on each
-particle, we seek a velocity and pressure satisfying \eqref{eq:stokes1}-\eqref{eq:rigid_bc} 
+where $\Gamma_i$ is the boundary of particle. where $\vv_i$ is the
+translational velocity and $\omega_i$ is its angular velocity. The
+process of finding the translational and angular velocities given
+the forces and torques is referred to as the mobility problem. Given
+forces $\FF_i$ and torques $T_i$ acting on each particle, we seek a
+velocity and pressure satisfying \eqref{eq:stokes1}-\eqref{eq:rigid_bc} 
 and
@@
   \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i,\quad 
-  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \, \dif s = T_i, \qquad i=1,\ldots,N_b,
+  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \,
+  \dif s = T_i, \qquad i=1,\ldots,N_b,
 \end{equation}
-where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
-\right)$ is the hydrodynamic stress tensor (pressure tensor) and
-$\nnu$ is the particle outward normal.
+where
+$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T \right)$
+is the hydrodynamic stress tensor (pressure tensor) and $\nnu$ is the
+particle outward normal.
 
-The second part is the hydrophobic 
-attraction.  To define it, we introduce 
+The second part is the hydrophobic attraction.  To define it, we introduce 
 the mean field free energy
@@
 \end{equation}
-where $u$ is the order parameter for the excess number of hydrogen
-bonds per water molecule, $C$ is a constant, and the minimization 
-occurs over all $u$ satisfying $u = u_0$ on the boundary where $u_0$
-is the degree of hydrophobicity.
+where $u$ is the order parameter for the excess number of hydrogen bonds
+per water molecule, $C$ is a constant, and the minimization occurs over
+all $u$ satisfying $u = u_0$ on the boundary where $u_0$ is the degree
+of hydrophobicity.
 
-As an illustration, in one-dimension the minimizer in \eqref{eq:free_energy} 
-solves $-u''(x) + f'(u(x)) = 0$ for $0 < x < b$, $u(0) = u_0(0),$ $u(b) = u_0(b)$ 
-and the free energy takes the form $F(b)$
-where $b$ is the  distance of separation between the hydrophobic surfaces.
-The hydrophobic force $-F'(b)$ the variation of free energy with respect to $b$  \cite{ErLjCl89, GoKl94}.
+As an illustration, in one-dimension the minimizer in
+\eqref{eq:free_energy} solves $-u''(x) + f'(u(x)) = 0$ for $0 < x < b$,
+$u(0) = u_0(0),$ $u(b) = u_0(b)$ and the free energy takes the form
+$F(b)$ where $b$ is the  distance of separation between the hydrophobic
+surfaces. The hydrophobic force $-F'(b)$ the variation of free energy
+with respect to $b$  \cite{ErLjCl89, GoHaKo94}.
 
 In two and higher spatial dimensions, the situation is more complicated.
-That is because the particles rotate and translate individually.  Here, the 
-minimizer  in \eqref{eq:free_energy}  satisfies 
+That is because the particles rotate and translate individually.
+Here, the minimizer  in \eqref{eq:free_energy} satisfies 
 \begin{equation}
 \label{eq:SL}
--\Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = u_0  \text{ on } \partial \Omega.
+-\Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = u_0
+\text{ on } \partial \Omega.
 \end{equation}
@@
     \quad 
-  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu) \dif s.
+    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
+    ({\bf T} \cdot \nnu) \dif s.
 \end{equation}
@@
 The density \label{eq:stress}  was introduced
-by~\cite{Fu20} and is responsible for forming particle aggregates that
-sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).
+by~\cite{Fu2018_SIAM} and is responsible for forming particle aggregates that
+sequester their hydrophobic surface regions.
 
@@
 of synthesis and assembly of soft matter materials.
-Dr. Bradley's lab specializes in synthesizing multiphasic and anisotropic colloids.
-Applications in this area enables include cargo-carrying capacity, 
-catalytic activity, or stimuli-responsive shape-change to amplify colloid utility for a wide 
-range of  spanning environmental remediation to drug delivery. 
-The main challenge is the ability decouple particle surface properties, 
+Dr. Bradley's lab specializes in synthesizing multiphasic and anisotropic
+colloids. Applications in this area enables include cargo-carrying capacity, 
+catalytic activity, or stimuli-responsive shape-change to amplify colloid
+utility for a wide range of  spanning environmental remediation to drug
+delivery. The main challenge is the ability decouple particle surface properties, 
 which control particle-particle and particleiiinterface interactions, 
-from auxiliary functions, such as catalytic or cargo-carrying capacities
-\cite{}.
+from auxiliary functions, such as catalytic or cargo-carrying capacities.
 
@@
 with linear response $f(u) = u^2$.  The 
-boundary conditions $u_0$ are for \textbf{(i)} a polar colloid with $u_0$ odd about the 
-particle axis, \textbf{(ii)} a periodic normal distribution with random 
-standard deviation but normalized square moment, and  
+boundary conditions $u_0$ are for \textbf{(i)} a polar colloid with $u_0$
+odd about the particle axis, \textbf{(ii)} a periodic normal distribution
+with random standard deviation but normalized square moment, and  
 \textbf{(iii)} a particle more hydrophobic on one side than the other. 
-Simulation \textbf{(ii)}  produces a single bilayer while simulation \textbf{(iii)}
-produces a multilamellar phase.  Simulation \textbf{(i)} is analogous to 
-magnetically and electrically charged Janus particles, but rather than producing
-isolated chains, the simulation yields a network of chains.
-All in all, the hydrophobic attraction formalism controls for morphology through 
-simple modification of the boundary conditions.
+Simulation \textbf{(ii)}  produces a single bilayer while simulation
+\textbf{(iii)} produces a multilamellar phase.  Simulation \textbf{(i)} is
+analogous to magnetically and electrically charged Janus particles, but
+rather than producing isolated chains, the simulation yields a network
+of chains. All in all, the hydrophobic attraction formalism controls for
+morphology through simple modification of the boundary conditions.
 
 Our next steps are to determine if the phenomenon we report are robust.
-This involves categorizing all possible the self assembly behavior
-and assessing the sensitivity of morphologies to boundary condition positionally
-and particle geometry.  At the same time, we can  
-translate phenomenological parameters parameters
-of the model in to contact angles. In Specific Aim 3, we discuss how to include 
-surface charge as this is one of the main surface properties that must be decoupled.
-In future studies, we will also include liquid crystal background flows.
+This involves categorizing all possible the self assembly behavior and
+assessing the sensitivity of morphologies to boundary condition
+positionally and particle geometry.  At the same time, we can translate
+phenomenological parameters of the model in to contact angles. In Specific
+Aim 3, we include surface charge as this is one of the main surface
+properties that must be decoupled. In future studies, we will also include
+liquid crystal background flows.
 
@@
 is an amplification of force and the attraction follows a much steeper 
-force law \cite{Lietal05}.
+force law \cite{Lin2005}.
 
 One way to mathematically account for this change in force profile is by
-allowing for phases in the order parameter $u$.
-Motivated by capillary wetting, theoretical soft matter biophysicist Gerhard Gompper 
+allowing for phases in the order parameter $u$. Motivated by capillary
+wetting, theoretical soft matter biophysicist Gerhard Gompper 
 introduced such a model in \cite{GoHaKo94}. This was a one-dimensional
-model which we will extend to two-dimensions (at first) and follow up on the parameter study. 
-The order parameter is the mean number of nearest neighbors per water molecule
-with distinguished values $u_1$ for five-coordinated water in the bulk phase and 
-the scalar value $u_0$ for four-coordinated water at the hydrophobic surfaces.  
-A slanted double well-potential $f(u)$ with local minima at $u_0$ and $u_1$ 
-characterizes the energy landscape of homogeneous water.   The absolute minimum
-is at $u_1$.
+model which we will extend to two-dimensions (at first) and follow up on
+the parameter study. The order parameter is the mean number of nearest
+neighbors per water molecule with distinguished values $u_1$ for
+five-coordinated water in the bulk phase and the scalar value $u_0$ for
+four-coordinated water at the hydrophobic surfaces. A slanted double
+well-potential $f(u)$ with local minima at $u_0$ and $u_1$ characterizes
+the energy landscape of homogeneous water. The absolute minimum is at $u_1$.
 
-When particles are well-separated, the energetic cost for filling the interstitial region 
-with $u_0$-phase water is energetically prohibitive and so there is a phase shift
-from the $u_0$ to $u_1$ water order occurring at the boundary of each particle. 
-Here, the attraction landscape is more or less identical to the linear response theory 
-we have explored and the decay length of attraction is set by $\sqrt{1/f''(u_1)}$.
-Conversely, when particles are proximal it energetically favorable to coalesce 
-the $u_0$-phase and here there will be a circumscribing phase transition.
+When particles are well-separated, the energetic cost for filling
+the interstitial region with $u_0$-phase water is energetically prohibitive
+and so there is a phase shift from the $u_0$ to $u_1$ water order occurring
+at the boundary of each particle.  Here, the attraction landscape is more
+or less identical to the linear response theory we have explored and the
+decay length of attraction is set by $\sqrt{1/f''(u_1)}$. Conversely, when
+particles are proximal it energetically favorable to coalesce the $u_0$-phase
+and here there will be a circumscribing phase transition.
 Here, the energetics are dominated by a decay length  $\sqrt{1/f''(u_0)}$
@@
 to long-range decay lengths and energy cost of creating hydrophobic-water
-interfaces with established ranges of values. Other parameters, like the well-structure,
-are fit to the measured data. 
-These base-line simulations will allow us to move on to simulating
-colloidal suspensions.
+interfaces with established ranges of values. Other parameters, like the
+well structure, are fit to the measured data. These base-line simulations
+will allow us to move on to simulating colloidal suspensions.
 
@@
 set of parameter values.  One such approach is to consider 
-Gaussian fluctuation. 
-So far we, have studied energy minimizers of the Landau-Ginzburg 
-free energy functional. However,  hydrophobic force measurements are carried out at finite 
+Gaussian fluctuation. So far we, have studied energy minimizers of the
+Landau-Ginzburg free energy functional. However,  hydrophobic force
+measurements are carried out at finite 
 temperatures, thermal fluctuations should also be considered. 
@@
 free energy functional around the saddle point solution.
-The fluctuation energy involves calculation of the eigenfunctions of the second variation
-of the free energy.
+The fluctuation energy involves calculation of the eigenfunctions of
+the second variation of the free energy.
 
-Another approach is to modify the setup to include convection in the water structure. 
-In the short-range experimental data, particle velocities approach 200 nm s$^{-1}$.
-The measurements, however, do not account for water that must be 
-expelled between the two approach particles. This water movement is directly 
-accounted for by our Stokes mobility solver.  In the phenomenological model,
-the order parameter adjusts to the new particle positions instantaneously.  Instead,
-it may be required that the order parameter solves the parabolic version of \eqref{eq:SL}
-with a convection given by the underlying Stokes flow. 
-If the convective effect is significant, then a significant 
-set of measurements will need to be reevaluated.
+Another approach is to modify the setup to include convection in the
+water structure. In the short-range experimental data, particle
+velocities approach 200 nm s$^{-1}$. The measurements, however, do not
+account for water that must be expelled between the two approach particles.
+This water movement is directly accounted for by our Stokes mobility solver.
+In the phenomenological model, the order parameter adjusts to the new
+particle positions instantaneously. Instead, it may be required that the
+order parameter solves the parabolic version of \eqref{eq:SL} with a
+convection given by the underlying Stokes flow. If the convective effect
+is significant, then a significant set of measurements will need to be
+reevaluated.
 

### 2021-11-09 NSF2021/Description/specificaim2.tex

@@
   F[u] = -\rho \Delta u + f'(u).
+\end{align*}
+This non-linear PDE will be solved with Newton's method
+\begin{align*}
+  u^{N+1} = u^{N} - dF(u^N)^{-1} F(u^N),
+\end{align*}
+where $dF(u^N) = -\rho \Delta + f''(u^N)$ is the Fr\'{e}chet derivative
+of $F$. As expected, the biggest challenge amounts to solving
+\begin{align}
+  \label{eq:NewtonUpdate}
+  - \rho \Delta v + f''(u^{N}) v = F[u^N].
+\end{align}
+If $f(u)$ is defined in terms of piecewise quadratic equations,
+equation~\eqref{eq:NewtonUpdate} is equivalent to
+\begin{align*}
+  -\rho \Delta v + 
+  \left(
+  \begin{cases}
+    a, &\mbox{if } u^{N}(\xx) \mbox{ closer to $U_1$} \\
+    1, &\mbox{if } u^{N}(\xx) \mbox{ closer to $U_0$}
+  \end{cases}
+  \right)
+  v = F[u^N].
 \end{align*}

### 2021-11-09 NSF2021/Description/specificaim2.tex
worked on SA2

--- 2021-11-07 NSF2021/Description/specificaim2.tex
@@
 \begin{align*}
-  F[u] = -\rho \Delta u + f'(u).
+  F[u] = -\rho^2 \Delta u + f'(u).
+\end{align*}
+This non-linear PDE will be solved with Newton's method
+\begin{align*}
+  u^{N+1} = u^{N} - dF^{-1} F(u^N),
+\end{align*}
+where $dF = -\rho^2 \Delta + f''(u^N)$ is the Fr\'{e}chet derivative of
+$F$. As expected, the biggest challenge amounts to solving
+\begin{align}
+  \label{eq:NewtonUpdate}
+  - \rho^2 \Delta v + f''(u^{N}) v = F[u^N].
+\end{align}
+For a general double well potential $f(u)$, this is a variable
+coefficient elliptic PDE, and developing an integral equation
+formulation is challenging. We propose to instead use an inexact
+Newton's method where $dF^{-1}$ is defined in terms of the piecewise
+quadratic approximation
+\begin{align*}
+  f(u) \approx bu + \begin{cases}
+    a(u - U_1)^2, &\mbox{if } u \leq (U_0 + U_1)/2 \\
+    (u - U_2)^2, &\mbox{if } u > (U_0 + U_1)/2.
+  \end{cases}
+\end{align*}
+In this case, the update step of Newton's method~\eqref{eq:NewtonUpdate}
+amounts to solving the piecewise constant PDE
+\begin{align}
+  \label{eq:screenedPoisson}
+  -\rho^2 \Delta v + 
+  \left(
+  \begin{cases}
+    2a, &\mbox{if } u^{N} \leq (U_0 + U_1)/2 \\
+    2, &\mbox{if } u^{N} > (U_0 + U_1)/2
+  \end{cases}
+  \right)
+  v = F[u^N],
+\end{align}
+which is a screened Poisson equation with piecewise a constant screening
+coefficient. Solutions of the screened Poisson equation can be written
+in terms of volume and layer potentials. We first define the level set
+$\Gamma = \{\xx \:|\: \uu(\xx) = (U_0 + U_1)/2 \}$ which separates the
+domain $\Omega$ into two regions. Then, assuming that the particles are
+all contained in the hydrophobic region, a solution of the screened
+Laplace equation (i.e.~equation~\eqref{eq:screenedPoisson} when $F[u^N]
+= 0$) is
+\begin{align*}
+  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nn_\yy} K_0 \left(
+    \frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) ds_\yy + 
+    \frac{1}{2\pi} \int_{\Gamma} K_0 \left(
+    \frac{|\xx - \yy|}{\rho} \right) \eta(\yy) ds_\yy,
 \end{align*}

### 2021-11-10 NSF2021/Description/specificaim2.tex
working on double well results

@@
 parameter~\eqref{eq:SL} and the Stokes
-equations~\eqref{eq:stokes1}--\eqref{eq:stokes2}. If discretizing these
+equations~\eqref{eq:stokes1}--\eqref{eq:stokes3}. If discretizing these
 equations with stencil-based numerical methods, the computational domain
@@
 Significant challenges to solving BIEs include solving largely stem from
-solving dense linear systems. \S\ref{subsec:NumericalIssues}
-describes how we will combine preconditioning strategies with fast
-summation methods to accelerate the time to solution,
+solving dense linear systems. First, \S\ref{subsec:AC} describes how the
+non-linear Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved
+using BIE formulations. Then, \S\ref{subsec:NumericalIssues} describes
+how we will combine preconditioning strategies with fast summation
+methods to accelerate the time to solution, and
 \S\ref{subsec:timeStepping} describes adaptive time stepping methods,
-and \S\ref{subsec:AC} describes how the non-linear Allen-Cahn
-equation~\eqref{eq:SL} will be iteratively solved using BIE
-formulations.
 
@@
 \label{subsec:AC}
+
+\begin{wrapfigure}[]{l}{1.8in}
+  \centering
+  \input{figures/doublewell.tikz}
+  \caption{\label{fig:well} $U_1 = 0.5$, $U_2 = 2$, $a = 1$, $b = 0.4$.}
+\end{wrapfigure}
 In the PIs collaboration, they have developed numerical methods to
@@
 solution of~\eqref{eq:SL} as a root finding problem for the operator
-\begin{align*}
+\begin{align}
+  \label{eq:F}
   F[u] = -\rho^2 \Delta u + f'(u).
-\end{align*}
+\end{align}
 This non-linear PDE will be solved with Newton's method
 \begin{align*}
-  u^{N+1} = u^{N} - dF^{-1} F(u^N),
+  u^{N+1} = u^{N} - \alpha dF^{-1} F(u^N),
 \end{align*}
 where $dF = -\rho^2 \Delta + f''(u^N)$ is the Fr\'{e}chet derivative of
-$F$. As expected, the biggest challenge amounts to solving
+$F$, and $\alpha$ is the step size which will be determined using
+backtracking. As expected, the biggest challenge amounts to solving
 \begin{align}
@@
 \begin{align*}
-  f(u) \approx bu + \begin{cases}
+  f(u) \approx \tilde{f}(u) = bu + \begin{cases}
     a(u - U_1)^2, &\mbox{if } u \leq (U_0 + U_1)/2 \\
@@
 In this case, the update step of Newton's method~\eqref{eq:NewtonUpdate}
-amounts to solving the piecewise constant PDE
+amounts to solving the PDE
 \begin{align}
   \label{eq:screenedPoisson}
-  -\rho^2 \Delta v + 
-  \left(
-  \begin{cases}
-    2a, &\mbox{if } u^{N} \leq (U_0 + U_1)/2 \\
-    2, &\mbox{if } u^{N} > (U_0 + U_1)/2
-  \end{cases}
-  \right)
-  v = F[u^N],
+  -\rho^2 \Delta v + \tilde{f}''(u^{N})v = F[u^N],
 \end{align}
+\begin{wrapfigure}[]{r}{1.8in}
+  \centering
+  \input{figures/residuals.tikz}
+  \caption{\label{fig:residuals} $U_1 = 0.5$, $U_2 = 2$, $a = 1$, $b =
+  0.4$.}
+\end{wrapfigure}
 which is a screened Poisson equation with piecewise a constant screening
-coefficient. Solutions of the screened Poisson equation can be written
+coefficient. We test the efficacy of Newton's method applied
+to~\eqref{eq:F} by considering its one-dimensional version in $(0,1)$
+with the Dirichlet boundary conditions $u(0) = U_0$ and $u(1) = U_1$.
+These parameters result in the double well potential illustrated in
+Figure~\ref{fig:well}(a), and the inexact Newton's method converges to
+the solution in Figure~\ref{fig:well}(b). Figure~\ref{fig:residuals}
+shows the max norm of the residual at each Newton iterate when using
+the exact second derivative (red curve) and the piecewise constant
+approximate (blue curve).
+
+Solutions of the screened Poisson equation can be written
 in terms of volume and layer potentials. We first define the level set

### 2021-11-10 NSF2021/Description/specificaim1.tex
RJR - SP1, Prelim, new figure folders

--- 2021-11-02 NSF2021/Description/specificaim1.tex
@@
 %%
-We have demonstrated that our hydrophobic attraction with repulsion
-potential (HAP) approach efficiently simulates self-assembly of
-amphiphilic particles into two-dimensional micelles, bilayer membranes,
-and vesicles \cite{Fu2018_SIAM} and recreates the tank-treading
-phenomenon in external shear flows \cite{FuQuRyYo20}.
-While the results show great promise in the field of collective body
-hydrodynamics, several outstanding issues need to be addressed. These
-include a thorough analysis of elastic properties of our coarse-grained
-bilayers and efficiently simulating three-dimensional collective
-hydrodynamics of amphiphilic particles.
-We must also incorporate electric charge and account
-for how external fields control particle self-assembly.
+\begin{center}
+  \begin{figure}
+      \includegraphics[width=1\textwidth]{figures/SpecificAim1/Domain.pdf}
+  \end{figure}
+\end{center}
 
-\subsection{Specific Aim 1: Measuring material properties of amphiphile self-assembly}
+\subsection{Specific Aim 1: Measuring material properties of amphiphile
+  self-assembly}
 \label{subsec:specific_aim_1}
 
-The goal of Specific Aim 1 is to investigate generalizations of the
-screened Laplace equation for different soft matter systems.
+The proposed research aims to provide fundamental insight into the
+self-assembly dynamics of amphiphilic particles. These results will
+facilitate optimal design of smart materials by tuning the geometry and
+properties of the amphiphilic particles.
+Specific Aim 1 achieves this through a novel mathematical model
+for particle self-organization driven by long-range interfacial forces.
 
-\begin{itemize}
-  \item Include ions in suspension
-  \item Discussed in Sylvie Roke's talk---I added the slides to the repo
-\end{itemize}
+\subsubsection{Problem formulation}
+The mathematical formulation is a nonlinear system 
+for the dynamics of a collection of particles. The 
+interactions come from a system of linear partial differential equations
+(PDE) and comprise hydrodynamic interactions and hydrophobic interactions.
+The formulation prevents particle collisions through excluded volume
+potentials.
 
+The hydrodynamic interactions come from the mobility problem for rigid
+particles immersed in a viscous solvent. Assuming inertial terms are
+negligible, the particle motion is goverened by the Stokes equations
+\begin{alignat}{3}
+\label{eq:stokes1}
+  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
+    && \xx \in \Omega, \\
+\label{eq:stokes2}
+  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
+\label{eq:stokes3}
+  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
+\end{alignat}
+%
+where $\uu$ is the velocity and $p$ is the pressure of the solvent,
+$\uu_\infty$ is the background flow, and $\mu$ is the constant
+solvent viscosity. The domain
+$\Omega$ is the fluid region surrounding the particles.
+Since the particles are rigid, the solvent velocity 
+satisfies a no-slip boundary condition for a rigid body motion 
+%\begin{align}
+%\label{eq:rigid_bc}
+%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
+%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
+%\end{align}
+on the particle boundary $\Gamma_i$
+with translational velocity $\vv_i$ and
+angular velocity $\omega_i$.
+Given imposed forces acting on each particle,
+the \emph{mobility problem} consists of finding
+translational and angular velocities so that 
+viscous fluid forces balance the imposed forces.
+
+The hydrophobic interactions come from the tendency 
+of particles to minimize the free energy of the structure of
+the surrounding water molecules.  
+Experimental measurements suggest that the free energy functional
+take the form 
+\begin{equation}
+\label{eq:free_energy}
+F[u] = C \int_{\Omega}  \rho |\nabla u|^2 + \rho^{-1} f(u) \,dx
+\end{equation}
+where
+$u$ is an order parameter for the structure of water,
+$\rho$ is a decay length,
+$C$ is a constant, and $f(u)$ is a potential.
+Hydrogen-bond persistence times are on the order of picoseconds \cite{MaGa13}.
+Since waters reorient 
+on a time scale much smaller than for the particle motion, 
+then at each moment in time $u$ minimizes $F[u]$ and satisfies 
+\begin{equation}
+\label{eq:SL}
+-\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g
+\text{ on } \Omega.
+\end{equation}
+The boundary condition $g$ that imposes 
+the water structure at the water-hydrocarbon interfaces.
+It is a material label that is transported with the particle motions.
+
+The coupling between the Stokes equations \eqref{eq:stokes1}-\eqref{eq:stokes3}
+and the semilinear elliptic equation \eqref{eq:SL}
+comes from the first variation of the energy functional.
+The particles minimize the free energy $F[u]$
+by altering the location of hydrophobic interfaces. 
+It is possible to calculate the rate of change of $F[u]$
+using variation of the domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}.
+Carrying out this variation yields a 
+%The hydrophobic forces are torques are
+%\begin{equation}
+%  \label{eq:hydrophobicAttraction}
+%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
+%    \quad 
+%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
+%    ({\bf T} \cdot \nnu) \dif s.
+%\end{equation}
+surface force density 
+\begin{align}
+  \label{eq:stress}
+\mathbf{T}
+= C \left[ \rho^{-1} f(u) \mathbf{I}
+  + \rho  \left(|\nabla u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)\right].
+\end{align}
+The imposed forces and torques from the integration of $\mathbf{T}$ along the
+particle boundary.
+The density \eqref{eq:stress}  was first introduced
+by~\cite{Fu2018_SIAM} and is the higher-dimensional analogue of
+disjoining pressure calculated by
+\cite{MaRa76, ErLjCl89, KoNa15, Nagle17, KUZMIN2005}.
+It is the mathematical ingredient responsible for forming particle
+aggregates that sequester their hydrophobic surface regions.
+
+By solving the above system, we obtain translational and angular
+velocities of the many-body system. 
+A second-order Adams-Bashforth scheme updates the particle positions and orientations.
+
+The formulation presents a number of
+mathematical and numerical challenges. For one, the domain is constantly
+changing so that a new boundary value problem must be solved at each time step.
+The particle boundaries are nearly touching and this requires
+high-order numerical schemes to accurately calculated forces.
+The domain is unbounded and there are issues with accurately
+calculating the velocity in the far-field. 
+Finally, the numerical routine must handle
+large system sizes efficiently when their are many particles
+is large.
+
+%and
+%\begin{equation}
+%  \label{eq:force}
+%  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i,\quad 
+%  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \,
+%  \dif s = T_i, \qquad i=1,\ldots,N_b,
+%\end{equation}
+%where
+%$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T \right)$
+%is the hydrodynamic stress tensor (pressure tensor) and $\nnu$ is the
+%particle outward normal.
+
+\subsubsection{Janus-particle self-assembly} 
+\begin{wrapfigure}[14]{l}{0.5\textwidth}
+\includegraphics[width=0.5\textwidth]{figures/SpecificAim1/multilamelar.pdf}
+\caption{\label{fig:multilamelar}
+  Experimentalists can transform unilamellar vesicles to multilamellar
+  vesicles by altering the quality of the solvent
+    \cite{deMeetal21}.
+  In \eqref{eq:SL}, the solvent quality enters through the potential
+  $f(u)$ and boundary conditions. 
+}
+\end{wrapfigure}
+A number of morphologies arise from the theory. In the linear response case,
+take $f(u) = u^2$ so that water structure has its lowest potential value
+at $u = 0$, representing bulk water. The solutions of \eqref{eq:SL} have
+a boundary layer structure and decay to 0 in the bulk with the decay
+length $\rho$.
+
+Consider a polar boundary condition where
+$g_i(\mathbf{x}) = (\pi r)^{-1/2} \cos (\theta_i(\mathbf{x}))$
+where $\theta_i$ is the angle formed by $\mathbf{x}$, the particle
+center $\mathbf{a}_i$, and the particle director $\mathbf{d}_i$.
+The normalization $(\pi r)^{-1/2}$ here and others below
+provide for a uniform surface energy $\int_{\Gamma_i} g_i^2 \,ds = 1$
+when the particles are disks of radius $r$.
+The boundary condition is odd along the particle axis 
+making the particle head repel the tail.
+We simulate the dynamics of 100 particles with random initial position
+and orientation. The particles rapidly form chains with their
+directors perpendicular to the length of the chain. The equilibrium
+structure consists particles positioned on a square grid with alternating
+orientations.
+\begin{center}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_A1.png}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_A2.png}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_A5.png}\\
+    Figure 2. Self assembly for a polar boundary condition
+    \label{fig:self-assemblyA}
+\end{center}
+
+Amphiphilic particles have a hydrophobic tail and a hydrophilic head
+and are accounted for as follows.
+The hydrophilic side takes the value $u = 0$ since the
+apolar headgroup of a lipid, for example, does not alter the structure
+of adjacent waters. The hydrophobic side takes the value $u > 0$. 
+The interaction between particles is attractive. Using
+$(3\pi )^{-1/2}(1 + \cos(\theta_i(\mathbf{x})))$
+as a simple modification to the previous boundary condition 
+produces two-dimensional micelles and bilayers \cite{Fu2018_SIAM}.
+Researchers have asked us if the phenomenon is robust. To show
+that it is, we use 
+\begin{equation}
+\label{eq:vonMises}
+g_i(\mathbf{x}) =
+\sqrt{
+  \frac{\exp( \kappa_i(\theta_i(\mathbf{x}) - \theta^0_i))}
+  {2\pi r_i I_0(\kappa_i)}}
+\end{equation}
+instead where the radicand is the von Mises 
+distribution with director angle $\theta^0_i$ and Bessel function
+$I_0$ of order zero. The square of this function behaves as a normal
+distribution with variance like $1/\kappa_i$. To replicate
+experimental conditions, the concentration $\kappa_i$ and radii
+$r_i$ are randomized. Using the same initial configuration, the
+particles form small groups. The small groups combine to form bilayers.
+\begin{center}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_B1.png}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_B2.png}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_B4.png}\\
+    Figure 3. Self assembly for a amphiphilic boundary condition
+    \label{fig:self-assemblyA}
+\end{center}
+
+Multilamelar bilayers arise with an increase by shifting the boundary condition
+further. Let $g_i(\mathbf{x}) = (9\pi )^{-1/2}(2 + \cos(\theta_i(\mathbf{x})))$.
+This gives a hydrophobic particle with greater intensity of hydrophobicity
+at $\theta_i = 0$ than at $\theta_i = \pi$.  The initial self-assembly
+is similar to that of the amphiphilic particle case, except that the bilayers
+do not stay well separated.  Rather, the bilayers stack on top of each
+other as a consequence of the interfacial tension of exposed particle heads. 
+\begin{center}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_C1.png}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_C2.png}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_C4.png}\\
+    Figure 3. Self assembly for hydrophobic particles with bias.
+    \label{fig:self-assemblyA}
+\end{center}
+
+In summary, the hydrophibic interaction-mobility problem model yields
+rich morphologies that are valuable in the synthesizing multiphasic and
+anisotropic colloids. The goal is to obtain numerically aided 
+syntheses and assembly of soft matter materials.
+Applications in this area include cargo-carrying capacity, 
+catalytic activity, or stimuli-responsive shape-change to amplify colloid
+utility for a wide range of  spanning environmental remediation to drug
+delivery. The main experimental challenges include the ability to
+decouple particle surface properties.
+The main modeling challenge is to translate the phenomenological
+parameters, e.g. boundary conditions, into measurable quantities
+such as contact angles. Collaboration with experimental groups will
+use numerical methods to predict parameter regimes 
+to control particle-particle interactions. In Specific Aim 3, we
+discuss how to include ions and surface charge.
+
+\subsubsection{Hydrophobic forces as capillary wetting}
+A natural generalization of the linear response model is 
+to use a fourth-order, tilted double-well potential
+$f(u) = a(u-u_0)^2(u-u_1)^2 + bu$.
+Motivated by capillary wetting, soft matter physicist Gerhard Gompper 
+introduced a double-well model for one-dimensional hydrophobic attraction
+\cite{GoHaKo94}. The two-dimensional attraction we propose
+is more complicated and includes extra line tension effects
+not present in the one-dimensional theories.
+
+Here, the order parameter $u$ is the mean number of nearest
+neighbors per water molecule.
+The value $u_0 = 4$ gives a local minimum for the ideal
+tetrahadral water network found at hydrophobic surfaces.  
+The value $u_1 \sim 4.4$ gives the absolute minimum
+in the bulk where there is a mixture of four and five-coordinated
+waters. The equation \eqref{eq:SL} takes the form of a
+steady-state Allen-Cahn equation. 
+When particles are well-separated, the energetic cost for filling
+the interstitial region with $u_0$-phase water is prohibitive
+and there is a phase shift from the $u_0$ to $u_1$ water order
+---the attraction landscape is more
+or less identical to the linear response theory. Conversely, when
+particles are proximal, it becomes energetically favorable
+to coalesce $u_0$-phases. This introduces a line tension
+for the phase transition.
+
+One potential application of the Allen-Cahn-type formulation is to
+explaning measured hydrophobic attraction profiles.
+The experimental data on hydrophobic attraction between 
+is well-established and the literature contains data for a number of
+solvents and hydrocarbon species. The experimental measurements
+are well-fit by a double exponential curve in the 10 to 100 nanometer range
+of separation.  Below 10 nm, however, there is an amplification of force
+and the attraction follows a much steeper force law not accounted
+for by past phenomenoloical theories \cite{Lin2005}.
+
+It may be the case that the double-well formulation recreates the
+long and short-range interactions.  The advantage
+is that the two-dimensional simulations can replicate the
+experimental setup better than prior, one-dimensional theoretical work 
+Some of the model parameters directly connect 
+to long-range decay lengths and energy cost of creating hydrophobic-water
+interfaces with established ranges of values. Other parameters, like the
+well structure, are fit to the measured data. These base-line simulations
+will allow us to move on to provide more accurate colloidal suspension
+simulations.
+
+Other approaches will be required if the modified phenomenological theory 
+does not recreate the measured force curves.
+We can rule out convection in the water structure since  
+the time scale of particle motion is much larger than
+the hydrogen-bond lifetimes. One approach is to consider Gaussian fluctuation.
+Here, we expand the free energy functional around the saddle point solution.
+The fluctuation energy then involves calculation of the eigenfunctions of
+the second variation of the free energy. This accounts for the fact
+that experimental measurements are carried out at finite 
+temperatures, where thermal fluctuations should ideally also be considered.
+
+%
+% The following commented out Nov 6, 2021.
+%
+%
 \begin{comment}

### 2021-11-10 NSF2021/Description/specificaim2.tex

@@
 
-\begin{wrapfigure}[]{l}{1.8in}
-  \centering
-  \input{figures/doublewell.tikz}
-  \caption{\label{fig:well} $U_1 = 0.5$, $U_2 = 2$, $a = 1$, $b = 0.4$.}
-\end{wrapfigure}
 In the PIs collaboration, they have developed numerical methods to
@@
 \begin{align*}
-  u^{N+1} = u^{N} - \alpha dF^{-1} F(u^N),
+  u^{N+1} = u^{N} - \alpha (dF)^{-1} F(u^N),
 \end{align*}
-where $dF = -\rho^2 \Delta + f''(u^N)$ is the Fr\'{e}chet derivative of
-$F$, and $\alpha$ is the step size which will be determined using
+where $dF = -\rho^2 \Delta + f''$ is the Fr\'{e}chet derivative of $F$,
+and $\alpha$ is the step size which will be determined using
 backtracking. As expected, the biggest challenge amounts to solving
@@
 \end{align}
+\begin{wrapfigure}[]{l}{1.8in}
+  \centering
+  \input{figures/doublewell.tikz}
+  \caption{\label{fig:well} (a) The double well potential when $U_1 =
+  0.5$, $U_2 = 2$, $a = 1$, and $b = 0.4$. (b) The corresponding
+  solution of~\eqref{eq:F}.}
+\end{wrapfigure}
 For a general double well potential $f(u)$, this is a variable
@@
 \end{align}
-\begin{wrapfigure}[]{r}{1.8in}
-  \centering
-  \input{figures/residuals.tikz}
-  \caption{\label{fig:residuals} $U_1 = 0.5$, $U_2 = 2$, $a = 1$, $b =
-  0.4$.}
-\end{wrapfigure}
 which is a screened Poisson equation with piecewise a constant screening
@@
 the exact second derivative (red curve) and the piecewise constant
-approximate (blue curve).
+approximate (blue curve). As expected, the exact Newton's requires less
+iterations, but applying the inexact Newton's method is much cheaper
+since the $\tilde{f}''$ is piecewise constant.
+\begin{wrapfigure}[]{r}{1.8in}
+  \centering
+  \input{figures/residuals.tikz}
+  \caption{\label{fig:residuals} The max norm of the residual of
+  inexact (blue) and exact (red) Newton's method.}
+\end{wrapfigure}
 
-Solutions of the screened Poisson equation can be written
-in terms of volume and layer potentials. We first define the level set
-$\Gamma = \{\xx \:|\: \uu(\xx) = (U_0 + U_1)/2 \}$ which separates the
-domain $\Omega$ into two regions. Then, assuming that the particles are
-all contained in the hydrophobic region, a solution of the screened
-Laplace equation (i.e.~equation~\eqref{eq:screenedPoisson} when $F[u^N]
-= 0$) is
+Having demonstrated that the inexact Newton method is a viable solver
+for the one-dimensional Cahn-Allen equation, we propose to extend the
+results to higher spatial dimensions. Again, the biggest challenge is
+solving the piecewise constant PDE~\eqref{eq:screenedPoisson}. To
+exploit the benefits of an integral equation methods, we will write the
+solution of~\eqref{eq:screenedPoisson} in terms of layer and volume
+potentials. We start by defining the level set $\Gamma = \{\xx \:|\:
+\uu(\xx) = (U_0 + U_1)/2 \}$ which separates the domain $\Omega$ into
+the hydrophobic order region and the bulk order region. In each of these
+regions $f''(u)$ is constant. Then
 \begin{align*}

### 2021-11-11 NSF2021/Description/specificaim2.tex
removed domain fig in SA1

--- 2021-11-10 NSF2021/Description/specificaim2.tex
@@
 
-\label{subsec:specific_aim_2}
-\begin{wrapfigure}[14]{r}{0.61\textwidth}
-  \centering{\includegraphics[width=0.60\textwidth]{Figures/domain.pdf}}
-    \vspace{-15pt}
-    \caption{\label{fig:flow_map} \footnotesize A collection of 3D
-    amphiphilic particles suspended in a solvent. The solvent velocity
-    satisfies the Stokes equations, and the hydrophobic forces depend on
-    the solvent activity that satisfies the screened Laplace equation.
-    The geometry is updated by solving the mobility problem.} 
-\end{wrapfigure}
+%\label{subsec:specific_aim_2}
+%\begin{wrapfigure}[14]{r}{0.61\textwidth}
+%  \centering{\includegraphics[width=0.60\textwidth]{Figures/domain.pdf}}
+%    \vspace{-15pt}
+%    \caption{\label{fig:flow_map} \footnotesize A collection of 3D
+%    amphiphilic particles suspended in a solvent. The solvent velocity
+%    satisfies the Stokes equations, and the hydrophobic forces depend on
+%    the solvent activity that satisfies the screened Laplace equation.
+%    The geometry is updated by solving the mobility problem.} 
+%\end{wrapfigure}
 The HAP model requires solving exterior Dirichlet problems for the order

### 2021-11-11 NSF2021/Description/specificaim1.tex
figures in preliminary work

@@
 %%
-\begin{center}
-  \begin{figure}
-      \includegraphics[width=1\textwidth]{figures/SpecificAim1/Domain.pdf}
-  \end{figure}
-\end{center}
 
@@
 potentials.
+
+  \begin{figure}[h!]
+\begin{center}
+  \includegraphics[width=0.8\textwidth]{figures/SpecificAim1/Domain.pdf}
+\end{center}  
+  \caption{\label{fig:flow_map} A collection of 3D
+   amphiphilic particles suspended in a solvent. The solvent velocity
+   satisfies the Stokes equations, and the hydrophobic forces depend on
+   the solvent activity that satisfies the screened Laplace equation.
+   The geometry is updated by solving the mobility problem.}     
+  \end{figure}
 
@@
 \subsubsection{Janus-particle self-assembly} 
-\begin{wrapfigure}[14]{l}{0.5\textwidth}
-\includegraphics[width=0.5\textwidth]{figures/SpecificAim1/multilamelar.pdf}
-\caption{\label{fig:multilamelar}
-  Experimentalists can transform unilamellar vesicles to multilamellar
-  vesicles by altering the quality of the solvent
-    \cite{deMeetal21}.
-  In \eqref{eq:SL}, the solvent quality enters through the potential
-  $f(u)$ and boundary conditions. 
-}
-\end{wrapfigure}
-A number of morphologies arise from the theory. In the linear response case,
+In the linear response case,
 take $f(u) = u^2$ so that water structure has its lowest potential value
@@
 a boundary layer structure and decay to 0 in the bulk with the decay
-length $\rho$.
+length $\rho$. Nevertheless, a number of morphologies arise by altering
+boundary conditions.
+
+\begin{figure}[h!]
+  \begin{center}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A1.pdf}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A2.pdf}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A3.pdf}
+    \end{center}
+  \caption{
+    Self assembly with a polar boundary condition leads to checkboard pattern.
+    Green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
+    \label{fig:self-assemblyA}}
+\end{figure}
 
@@
 directors perpendicular to the length of the chain. The equilibrium
-structure consists particles positioned on a square grid with alternating
-orientations.
+structure consists particles positioned on a square grid
+in a checkerboard pattern. This patterning is a consequence of energy
+minimality and allows each particle to simultaneously
+coordinate its head with that of three other particles
+and its tail with that of three other particles.
+
+\begin{figure}[h!]
 \begin{center}  
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_A1.png}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_A2.png}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_A5.png}\\
-    Figure 2. Self assembly for a polar boundary condition
-    \label{fig:self-assemblyA}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B1.pdf}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B2.pdf}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B3.pdf}\\
 \end{center}    
-
+\caption{With an amphiphilic boundary condition particles self-assemble
+  into bilayers. The patterning shields the hydrophobic core (yellow) from the
+  aqueous phase. 
+      \label{fig:self-assemblyA}}
+\end{figure}
 Amphiphilic particles have a hydrophobic tail and a hydrophilic head
@@
 particles form small groups. The small groups combine to form bilayers.
+
+\begin{figure}[h!]
   \begin{center}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_B1.png}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_B2.png}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_B4.png}\\
-    Figure 3. Self assembly for a amphiphilic boundary condition
-    \label{fig:self-assemblyA}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C1.pdf}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C2.pdf}
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C3.pdf}\\
+    \caption{This figure is for hydrophobic particles with a bias. The
+      hydrophobic intensity is greater on one side of the particle (magenta)
+      than the other (yellow).
+    \label{fig:self-assemblyA}}
 \end{center}
+\end{figure}
 
@@
 do not stay well separated.  Rather, the bilayers stack on top of each
-other as a consequence of the interfacial tension of exposed particle heads. 
-\begin{center}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_C1.png}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_C2.png}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100_C4.png}\\
-    Figure 3. Self assembly for hydrophobic particles with bias.
-    \label{fig:self-assemblyA}
-\end{center}
+other as a consequence of the interfacial tension of exposed particle heads \cite{deMeetal21}.
 
@@
 rich morphologies that are valuable in the synthesizing multiphasic and
-anisotropic colloids. The goal is to obtain numerically aided 
+anisotropic colloids \cite{Bradley2016,Mallory2017,Bradley2017}.
+The main experimental challenges include the ability to
+decouple particle surface properties.
+The goal is to obtain numerically aided 
 syntheses and assembly of soft matter materials.
@@
 utility for a wide range of  spanning environmental remediation to drug
-delivery. The main experimental challenges include the ability to
-decouple particle surface properties.
+delivery \cite{McBr21, HaBr20}.
+
+%\begin{wrapfigure}[14]{l}{0.5\textwidth}
+%\includegraphics[width=0.5\textwidth]{figures/SpecificAi%m1/multilamelar.pdf}
+%\caption{\label{fig:multilamelar}
+%  Experimentalists can transform unilamellar vesicles to% multilamellar
+%  vesicles by altering the quality of the solvent
+%    \cite{deMeetal21}.
+%  In \eqref{eq:SL}, the solvent quality enters through t%he potential
+%  $f(u)$ and boundary conditions. 
+%}
+%\end{wrapfigure}
 The main modeling challenge is to translate the phenomenological
@@
 in the bulk where there is a mixture of four and five-coordinated
-waters. The equation \eqref{eq:SL} takes the form of a
-steady-state Allen-Cahn equation. 
+waters.
 When particles are well-separated, the energetic cost for filling
@@
 for the phase transition.
+
+The equation \eqref{eq:SL} takes the form of a steady-state
+Allen-Cahn equation. The Allen-Cahn equation is used in phase field
+formulations of immisible fluids, for example.
+PI Ryham and colaborators launched the simulation and asymptotic analysis
+of phase field functionals of membrane elastic energy,
+devising functionals for  
+for the squared mean curvature (Willmore) energy \cite{0951-7715-18-3-016}, 
+spontaneous curvature \cite{Du05} and Gaussian curvature energy \cite{DuEuler},
+as well as energetic variational approaches to coupling membrane elasticity to fluids \cite{QiangDu09}.
 

### 2021-11-11 NSF2021/Description/specificaim2.tex
figures in preliminary work

@@
 \end{align}
+%\begin{wrapfigure}[13]{l}{1.8in}
+%  \centering
+%  \input{figures/doublewell.tikz}
+%  \caption{\label{fig:well} $U_1 = 0.5$, $U_2 = 2$, $a = 1$, $b = 0.4$.}
+%\end{wrapfigure}
 This non-linear PDE will be solved with Newton's method
@@
 $F$, and $\alpha$ is the step size which will be determined using
-backtracking. As expected, the biggest challenge amounts to solving
+backtracking.
+As expected, the biggest challenge amounts to solving
 \begin{align}
@@
 \end{align}
+\begin{wrapfigure}[20]{r}{1.8in}
+  \centering
+  \input{figures/doublewell.tikz}  \\
+  \input{figures/residuals.tikz}
+  \caption{\label{fig:residuals} A double well (top) and the error (bottom)
+    for the case $U_1 = 0.5$, $U_2 = 2$, $a = 1$, $b = 0.4$.}
+\end{wrapfigure}
 For a general double well potential $f(u)$, this is a variable

### 2021-11-11 NSF2021/Description/specificaim2.tex

@@
 \begin{align*}
-  u^{N+1} = u^{N} - \alpha dF^{-1} F(u^N),
+  u^{N+1} = u^{N} - \alpha (dF^N)^{-1} F(u^N),
 \end{align*}
-where $dF = -\rho^2 \Delta + f''(u^N)$ is the Fr\'{e}chet derivative of
-$F$, and $\alpha$ is the step size which will be determined using
-backtracking.
-As expected, the biggest challenge amounts to solving
+where $dF^N = -\rho^2 \Delta + f''(u^N)$ is the Fr\'{e}chet derivative
+of $F$, and $\alpha$ is the step size which will be determined using
+backtracking. As expected, the biggest computational challenge is
+solving
 \begin{align}
@@
 \end{align}
-\begin{wrapfigure}[20]{r}{1.8in}
+\begin{wrapfigure}[]{l}{1.8in}
+  \vspace{-46pt}
   \centering
-  \input{figures/doublewell.tikz}  \\
-  \input{figures/residuals.tikz}
-  \caption{\label{fig:residuals} A double well (top) and the error (bottom)
-    for the case $U_1 = 0.5$, $U_2 = 2$, $a = 1$, $b = 0.4$.}
+  \input{figures/doublewell.tikz} 
+  \caption{\label{fig:CA} (a) The double well potential $U_1 =
+  0.5$, $U_2 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
+  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
+  and inexact Newton's methods.}
 \end{wrapfigure}
@@
 coefficient elliptic PDE, and developing an integral equation
-formulation is challenging. We propose to instead use an inexact
-Newton's method where $dF^{-1}$ is defined in terms of the piecewise
-quadratic approximation
+formulation is challenging since the fundamental solution is not easily
+determined. We propose to instead use an inexact Newton's method where
+$dF^{-1}$ is defined in terms of the piecewise quadratic approximation
 \begin{align*}
@@
 coefficient. We test the efficacy of Newton's method applied
-to~\eqref{eq:F} by considering its one-dimensional version in $(0,1)$
-with the Dirichlet boundary conditions $u(0) = U_0$ and $u(1) = U_1$.
-These parameters result in the double well potential illustrated in
-Figure~\ref{fig:well}(a), and the inexact Newton's method converges to
-the solution in Figure~\ref{fig:well}(b). Figure~\ref{fig:residuals}
-shows the max norm of the residual at each Newton iterate when using
-the exact second derivative (red curve) and the piecewise constant
-approximate (blue curve).
+to~\eqref{eq:F} by considering a finite difference method applied to its
+one-dimensional version in $(0,1)$ with the Dirichlet boundary
+conditions $u(0) = U_0$ and $u(1) = U_1$.  These parameters result in
+the double well potential illustrated in Figure~\ref{fig:CA}(a), and the
+inexact Newton's method converges to the solution in
+Figure~\ref{fig:CA}(b). Figure~\ref{fig:CA}(c) shows the max norm of the
+residual at each Newton iterate when using the exact second derivative
+(red curve) and the piecewise constant approximate (blue curve).
 

### 2021-11-11 NSF2021/Description/specificaim2.tex
working on SA2

@@
   \label{eq:F}
-  F[u] = -\rho^2 \Delta u + f'(u).
+  J[u] = -\rho^2 \Delta u + f'(u).
 \end{align}
-%\begin{wrapfigure}[13]{l}{1.8in}
-%  \centering
-%  \input{figures/doublewell.tikz}
-%  \caption{\label{fig:well} $U_1 = 0.5$, $U_2 = 2$, $a = 1$, $b = 0.4$.}
-%\end{wrapfigure}
 This non-linear PDE will be solved with Newton's method
 \begin{align*}
-  u^{N+1} = u^{N} - \alpha (dF^N)^{-1} F(u^N),
+  u^{N+1} = u^{N} - \alpha (dJ^N)^{-1} F(u^N),
 \end{align*}
-where $dF^N = -\rho^2 \Delta + f''(u^N)$ is the Fr\'{e}chet derivative
+where $dJ^N = -\rho^2 \Delta + f''(u^N)$ is the Fr\'{e}chet derivative
 of $F$, and $\alpha$ is the step size which will be determined using
@@
   \label{eq:NewtonUpdate}
-  - \rho^2 \Delta v + f''(u^{N}) v = F[u^N].
+  - \rho^2 \Delta v + f''(u^{N}) v = J[u^N].
 \end{align}
@@
   \input{figures/doublewell.tikz} 
-  \caption{\label{fig:CA} (a) The double well potential $U_1 =
-  0.5$, $U_2 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
+  \caption{\label{fig:CA} (a) The double well potential $u_0 =
+  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
   Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
@@
 determined. We propose to instead use an inexact Newton's method where
-$dF^{-1}$ is defined in terms of the piecewise quadratic approximation
+$dJ^{-1}$ is defined in terms of the piecewise quadratic approximation
 \begin{align*}
   f(u) \approx \tilde{f}(u) = bu + \begin{cases}
-    a(u - U_1)^2, &\mbox{if } u \leq (U_0 + U_1)/2 \\
-    (u - U_2)^2, &\mbox{if } u > (U_0 + U_1)/2.
+    a(u - u_0)^2, &\mbox{if } u \leq (u_0 + u_1)/2 \\
+    (u - u_1)^2, &\mbox{if } u > (u_0 + u_1)/2.
   \end{cases}
@@
   \label{eq:screenedPoisson}
-  -\rho^2 \Delta v + \tilde{f}''(u^{N})v = F[u^N],
+  -\rho^2 \Delta v + \tilde{f}''(u^{N})v = J[u^N],
 \end{align}
 which is a screened Poisson equation with piecewise a constant screening
-coefficient. We test the efficacy of Newton's method applied
-to~\eqref{eq:F} by considering a finite difference method applied to its
-one-dimensional version in $(0,1)$ with the Dirichlet boundary
-conditions $u(0) = U_0$ and $u(1) = U_1$.  These parameters result in
-the double well potential illustrated in Figure~\ref{fig:CA}(a), and the
-inexact Newton's method converges to the solution in
-Figure~\ref{fig:CA}(b). Figure~\ref{fig:CA}(c) shows the max norm of the
-residual at each Newton iterate when using the exact second derivative
-(red curve) and the piecewise constant approximate (blue curve).
+coefficient. We test the efficacy of exact and inexact Newton's method
+applied to~\eqref{eq:F} by considering a finite difference method
+applied to its one-dimensional version in $(0,1)$ with the Dirichlet
+boundary conditions $u(0) = u_0$ and $u(1) = u_1$. These parameters
+result in the double well potential illustrated in
+Figure~\ref{fig:CA}(a), and both the exact and inexact Newton's methods
+converge to the solution in Figure~\ref{fig:CA}(b).
+Figure~\ref{fig:CA}(c) shows the max norm of the residual at each Newton
+iterate when using the exact second derivative (red curve) and the
+piecewise constant approximate (blue curve).
 
-Solutions of the screened Poisson equation can be written
-in terms of volume and layer potentials. We first define the level set
-$\Gamma = \{\xx \:|\: \uu(\xx) = (U_0 + U_1)/2 \}$ which separates the
-domain $\Omega$ into two regions. Then, assuming that the particles are
-all contained in the hydrophobic region, a solution of the screened
-Laplace equation (i.e.~equation~\eqref{eq:screenedPoisson} when $F[u^N]
-= 0$) is
+Having demonstrated that the inexact Newton method converges in one
+dimension, it will be used to solve the Allen-Cahn equation in two more
+or more dimensions. Since we are interested in solving~\eqref{eq:SL} in
+general unbounded geometries, we will develop an integral equation
+formulation. We first partition $\Omega$ into $\Omega_0 = \{\xx \in
+\Omega \:|\: u(\xx) < (u_0 + u_1)/2\}$ and $\Omega_1 = \{\xx \in \Omega
+\:|\: u(\xx) > (u_0 + u_1)/2\}$, and we let $\Lambda = \{\xx \:|\:
+u(\xx) = (u_0 + u_1)/2 \}$ be their common boundary points. We then let
+$G_0$ be the fundamental solution of $(-\rho^2 \Delta - 2a)$ and $G_1$
+be the fundamental solution of $(-\rho^2 \Delta + 2)$. Then, the
+solution of~\eqref{eq:screenedPoisson} can be written as $u = u^P + u^H$
+where $u^P$ is a volume potential and $u^H$ is a layer potential. The
+volume potential is
+\begin{align*}
+  u^{P}(\xx) = \int_{\Omega_i} G_i(\xx,\yy) J[u^N](\yy)\, d\yy, 
+    \quad i = 1,2,
+\end{align*}
+but it is discontinuous across $\Lambda$ and does not satisfy the
+prescribed hydrophobic boundary conditions on the particles $\Gamma_i$.
+The boundary conditions are enforced with the layer potential
+\begin{align*}
+  u^{H}(\xx) = \begin{cases}
+    \displaystyle\int_{\Lambda} G_0(\xx,\yy) \eta_0(\yy) \, ds_\yy + 
+    \displaystyle\int_{\Gamma} \pderiv{}{\nn_\yy} G_0(\xx,\yy)
+      \sigma(\yy) \,ds_\yy, \quad & \xx \in \Omega_0, \\
+    \displaystyle\int_{\Lambda} G_0(\xx,\yy) \eta_1(\yy) \, ds_\yy,
+     & \xx \in \Omega_1.
+  \end{cases}
+\end{align*}
+
+Then, assuming that the particles are all contained in the
+hydrophobic region, a solution of the screened Laplace equation
+(i.e.~equation~\eqref{eq:screenedPoisson} when $G[u^N] = 0$) is
 \begin{align*}

### 2021-11-11 NSF2021/Description/specificaim2.tex
done up to 4.2.2

@@
 dynamics~\cite{RYHAM20112929}, set the rate of dissipation. In Specific
-Aim 2, we propose to develop efficient high-order numerical methods to
+Aim 2, we propose novel and efficient high-order numerical methods to
 simulate dynamic assembly of particles under HAP potential in a viscous
@@
 %\end{wrapfigure}
-The HAP model requires solving exterior Dirichlet problems for the order
+The HAP model requires solving exterior problems for the order
 parameter~\eqref{eq:SL} and the Stokes
-equations~\eqref{eq:stokes1}--\eqref{eq:stokes3}. If discretizing these
-equations with stencil-based numerical methods, the computational domain
-must be truncated, the fluid volume must be discretized, and artificial
-boundary conditions must be imposed. The artificial boundary conditions
-introduce additional error, and discretizing the volume results in an
-excessively large system of equations. Moreover, it is difficult to
-obtain high-order discretizations when the boundary surfaces are
-irregular.
-
-Alternatively, we will take advantage of the linearity of the Stokes
-equations, and also apply a Newton's method to the HAP
-model~\eqref{eq:SL}, where each iteration requires the solution of
-linear elliptic PDEs. Then we can represent solutions of these elliptic
-PDEs as layer potentials
-\begin{align}
-  \label{eq:LP}
-  u(\mathbf{x}) = \mathcal{K}[\sigma](\mathbf{x}) = 
-  \int_{\partial\Omega} K(\mathbf{x},\mathbf{y})
-  \sigma(\mathbf{y})\,dS,
-\end{align}
-where $\sigma$ is an unknown density function, and
-$K(\mathbf{x},\mathbf{y})$ is a derivative of the fundamental solution
-of the PDE. By matching the prescribed boundary condition at
-$\mathbf{x}_0 \in \partial\Omega$ with the limit of
-equation~\eqref{eq:LP} as $\xx \rightarrow \xx_0$, a boundary integral
-equation (BIE) for the density function is formed.
-
-Numerical methods to solve BIEs have several advantages over their
-PDE-based counterpart: by construction, the layer
-potential~\eqref{eq:LP} satisfies far-field conditions; only
-$\partial\Omega$ needs to be discretized; carefully chosen kernels
-$K(\mathbf{x},\mathbf{y})$ result in a well-conditioned linear system
-that is solved with a mesh-independent number of GMRES iterations; and
-high-order or spectral accuracy is attainable with appropriate
-quadrature methods. The PIs have demonstrated that BIEs are a powerful
-tool to simulate two-dimensional suspensions of amphiphilic
-particles~\cite{Fu2018_SIAM, FuQuRyYo20}. In addition to improving
-two-dimensional simulations, the present proposal extends the results to
-three dimensions using a three-dimensional BIE formulation of the
-screened Laplace equation~\cite{ying_2006} and a well-conditioned BIE
-formulation of the mobility problem~\cite{manasthesis, rac-gre2016}.
-
-Significant challenges to solving BIEs include solving largely stem from
-solving dense linear systems. First, \S\ref{subsec:AC} describes how the
-non-linear Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved
-using BIE formulations. Then, \S\ref{subsec:NumericalIssues} describes
-how we will combine preconditioning strategies with fast summation
-methods to accelerate the time to solution, and
+equations~\eqref{eq:stokes1}--\eqref{eq:stokes3}. We will develop
+methods based on combinations of volume and layer potentials. Numerical
+methods to solve these integral equations (IEs) have several advantages
+over their PDE-based counterpart: by construction, they satisfy
+far-field and mass conservation conditions; only $\partial\Omega$ needs
+to be discretized for layer potentials; carefully chosen IEs result in a
+well-conditioned linear system that is solved with a mesh-independent
+number of GMRES iterations; and high-order or spectral accuracy is
+attainable with appropriate quadrature methods. The PIs have
+demonstrated that IEs are a powerful tool to simulate two-dimensional
+suspensions of amphiphilic particles~\cite{Fu2018_SIAM, FuQuRyYo20}.
+Moreover, elements of these formulations have been described in three
+dimensions~\cite{ying_2006, manasthesis, rac-gre2016}. This proposal
+will extend the two-dimensional methods to more general amphiphilic
+particle models that satisfy~\eqref{eq:SL}, and all the methods can
+naturally be extended to three dimensions. \S\ref{subsec:AC} describes
+how the non-linear Allen-Cahn equation~\eqref{eq:SL} will be iteratively
+solved using BIE formulations. Then, \S\ref{subsec:NumericalIssues}
+describes how we will combine preconditioning strategies with fast
+summation methods to accelerate the time to solution, and
 \S\ref{subsec:timeStepping} describes adaptive time stepping methods,
@@
 
-In the PIs collaboration, they have developed numerical methods to
-solve~\eqref{eq:SL} when $f(u) = u^2$. With this choice of $f(u)$, the
-resulting PDE is the linear screened Laplace equation which is
-efficiently solved with a double-layer potential representation. For a
-more general $f$, such as a double well potential, we will interpret the
-solution of~\eqref{eq:SL} as a root finding problem for the operator
+The PIs have developed numerical methods to solve~\eqref{eq:SL} when
+$f(u) = u^2$---this choice results in the linear screened Laplace
+equation. For a more general $f$, such as a double well potential, we
+will interpret the solution of~\eqref{eq:SL} as the root finding problem
 \begin{align}
@@
 \begin{align*}
-  u^{N+1} = u^{N} - \alpha (dJ^N)^{-1} F(u^N),
+  u^{N+1} = u^{N} - \alpha (dJ^N)^{-1} J(u^N),
 \end{align*}
@@
 backtracking. As expected, the biggest computational challenge is
-solving
+solving $- \rho^2 \Delta v + f''(u^{N}) v = J[u^N]$. Solving this
+variable coefficient PDE with an integral equation is challenging since
+a fundamental solution is not readily available. We propose to instead
+use an inexact Newton's method where $dJ^{-1}$ is defined in terms of
+the piecewise quadratic approximation
+\begin{align*}
+  f(u) \approx \tilde{f}(u) = bu + \begin{cases}
+    a(u - u_0)^2, &\mbox{if } u \leq (u_0 + u_1)/2, \\
+    (u - u_1)^2, &\mbox{if } u > (u_0 + u_1)/2.
+  \end{cases}
+\end{align*}
+and the resulting inexact Newton's method requires solving the piecewise
+constant PDE
 \begin{align}
-  \label{eq:NewtonUpdate}
-  - \rho^2 \Delta v + f''(u^{N}) v = J[u^N].
+  \label{eq:screenedPoisson}
+  -\rho^2 \Delta v + \tilde{f}''(u^{N})v = J[u^N],
 \end{align}
-\begin{wrapfigure}[]{l}{1.8in}
-  \vspace{-46pt}
+which is a screened Poisson equation with piecewise a constant screening
+coefficient. We test the efficacy of exact and inexact Newton's method
+applied to~\eqref{eq:F} in $(0,1)$ by discretizing $dJ$ with a
+second-order finite difference method. The choice of parameters $a$,
+$b$, $U_0$, and $U_1$ result in the double well potential illustrated in
+Figure~\ref{fig:CA}(a), and both the exact and inexact Newton's methods
+converge to the solution in Figure~\ref{fig:CA}(b).
+Figure~\ref{fig:CA}(c) shows the max norm of the residual at each Newton
+iterate when using the exact second derivative (red curve) and the
+piecewise constant approximate (blue curve). While the inexact Newton's
+method requires roughly twice as many iterations to reach of a tolerance
+of $10^{-4}$, each iteration is significantly cheaper in higher
+dimensions.
+
+\begin{wrapfigure}[28]{l}{1.8in}
+  \vspace{-4pt}
   \centering
@@
 \end{wrapfigure}
-For a general double well potential $f(u)$, this is a variable
-coefficient elliptic PDE, and developing an integral equation
-formulation is challenging since the fundamental solution is not easily
-determined. We propose to instead use an inexact Newton's method where
-$dJ^{-1}$ is defined in terms of the piecewise quadratic approximation
-\begin{align*}
-  f(u) \approx \tilde{f}(u) = bu + \begin{cases}
-    a(u - u_0)^2, &\mbox{if } u \leq (u_0 + u_1)/2 \\
-    (u - u_1)^2, &\mbox{if } u > (u_0 + u_1)/2.
-  \end{cases}
-\end{align*}
-In this case, the update step of Newton's method~\eqref{eq:NewtonUpdate}
-amounts to solving the PDE
-\begin{align}
-  \label{eq:screenedPoisson}
-  -\rho^2 \Delta v + \tilde{f}''(u^{N})v = J[u^N],
-\end{align}
-which is a screened Poisson equation with piecewise a constant screening
-coefficient. We test the efficacy of exact and inexact Newton's method
-applied to~\eqref{eq:F} by considering a finite difference method
-applied to its one-dimensional version in $(0,1)$ with the Dirichlet
-boundary conditions $u(0) = u_0$ and $u(1) = u_1$. These parameters
-result in the double well potential illustrated in
-Figure~\ref{fig:CA}(a), and both the exact and inexact Newton's methods
-converge to the solution in Figure~\ref{fig:CA}(b).
-Figure~\ref{fig:CA}(c) shows the max norm of the residual at each Newton
-iterate when using the exact second derivative (red curve) and the
-piecewise constant approximate (blue curve).
-
 Having demonstrated that the inexact Newton method converges in one
-dimension, it will be used to solve the Allen-Cahn equation in two more
-or more dimensions. Since we are interested in solving~\eqref{eq:SL} in
-general unbounded geometries, we will develop an integral equation
-formulation. We first partition $\Omega$ into $\Omega_0 = \{\xx \in
-\Omega \:|\: u(\xx) < (u_0 + u_1)/2\}$ and $\Omega_1 = \{\xx \in \Omega
-\:|\: u(\xx) > (u_0 + u_1)/2\}$, and we let $\Lambda = \{\xx \:|\:
-u(\xx) = (u_0 + u_1)/2 \}$ be their common boundary points. We then let
-$G_0$ be the fundamental solution of $(-\rho^2 \Delta - 2a)$ and $G_1$
-be the fundamental solution of $(-\rho^2 \Delta + 2)$. Then, the
-solution of~\eqref{eq:screenedPoisson} can be written as $u = u^P + u^H$
-where $u^P$ is a volume potential and $u^H$ is a layer potential. The
-volume potential is
+dimension, it will be coupled with IE formulations to to
+solve~\eqref{eq:SL} in two and three dimensions. We first partition
+$\Omega$ into $\Omega_0 = \{\xx \in \Omega \:|\: u(\xx) < (u_0 +
+u_1)/2\}$ and $\Omega_1 = \{\xx \in \Omega \:|\: u(\xx) > (u_0 +
+u_1)/2\}$, and we let $\Lambda = \{\xx \in \Omega \:|\: u(\xx) = (u_0 +
+u_1)/2 \}$ be their common boundary, and we let $G_0$ be the fundamental
+solution of $(-\rho^2 \Delta - 2a)$ and $G_1$ be the fundamental
+solution of $(-\rho^2 \Delta + 2)$. Then, the solution
+of~\eqref{eq:screenedPoisson} can be written as $u = u^P + u^H$ where
+$u^P$ is a volume potential and $u^H$ is a layer potential. The volume
+potential is
 \begin{align*}
@@
 prescribed hydrophobic boundary conditions on the particles $\Gamma_i$.
-The boundary conditions are enforced with the layer potential
+Assuming the particles are entirely contained in the hydrophobic region,
+the boundary conditions will be enforced with the layer potentials
 \begin{align*}
@@
       \sigma(\yy) \,ds_\yy, \quad & \xx \in \Omega_0, \\
-    \displaystyle\int_{\Lambda} G_0(\xx,\yy) \eta_1(\yy) \, ds_\yy,
+    \displaystyle\int_{\Lambda} G_1(\xx,\yy) \eta_1(\yy) \, ds_\yy,
      & \xx \in \Omega_1.
@@
 \end{align*}
-
-Then, assuming that the particles are all contained in the
-hydrophobic region, a solution of the screened Laplace equation
-(i.e.~equation~\eqref{eq:screenedPoisson} when $G[u^N] = 0$) is
-\begin{align*}
-  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nn_\yy} K_0 \left(
-    \frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) ds_\yy + 
-    \frac{1}{2\pi} \int_{\Gamma} K_0 \left(
-    \frac{|\xx - \yy|}{\rho} \right) \eta(\yy) ds_\yy,
-\end{align*}
+The density functions $\sigma$, $\eta_0$, and $\eta_1$ are determined so
+that $u = u^P + u^H$ satisfies the hydrophobic boundary condition on
+$\Gamma = \cup_i \Gamma_i$, and that it is continuous and differentiable
+across $\Lambda$.
 

### 2021-11-12 NSF2021/Description/specificaim3.tex
yny

@@
 We propose to investigate the effects of ion transport and distribution on the self-assembly of Janus particles within the HAP framework as follows.
-First the Stokes equations in~\eqref{eq:stokes} are modified to incorporate the transport of ions as
+First the Stokes equations are modified to incorporate the transport of ions as
 \begin{equation}
@@
 
-We couple the electrokinetics in~\eqref{eq:EKstokes} with the mobility Janus particles in a viscous solvent through the velocity field, ion distribution, and the hydrophobic potential.  
+We couple the electrokinetics in~\eqref{eq:EKstokes} with the mobility  problem of Janus particles in a viscous solvent through the velocity field, ion distribution, and the hydrophobic potential.  
 First the screen length $\rho$ in the HAP model is now a function of the  cation concentrations: $\rho = \rho(n_+) =
@@
 Under such simplification, the modified~\eqref{eq:EKstokes} may be re-formulated into integral forms.
-PI Young will conduct the asymptotic analyses to derive the modified~\eqref{eq:EKstokes}, and work with PI Quaife to design a numerical algorithm to simulate the modified system using integral formulation.
+PIs Ryham and Young will conduct the asymptotic analyses to derive the modified~\eqref{eq:EKstokes}, and work with PI Quaife to design a numerical algorithm to simulate the modified system using integral formulation.
 We will first investigate the effects of salt concentration on the assembly of Janus particles to form helices, as shown in figure~\ref{fig:helices_of_JPs}.

### 2021-11-12 NSF2021/Description/specificaim2.tex

@@
 how the non-linear Allen-Cahn equation~\eqref{eq:SL} will be iteratively
-solved using BIE formulations. Then, \S\ref{subsec:NumericalIssues}
+solved using IE formulations. Then, \S\ref{subsec:NumericalIssues}
 describes how we will combine preconditioning strategies with fast
@@
 
-\begin{wrapfigure}[28]{l}{1.8in}
+\begin{wrapfigure}[27]{l}{1.8in}
   \vspace{-4pt}
@@
 $\Gamma = \cup_i \Gamma_i$, and that it is continuous and differentiable
-across $\Lambda$.
+across $\Lambda$. This approach for using IEs to solve elliptic PDEs
+with with piecewise constant coefficients has succesfully been used in
+other application such as scattering~\cite{hyu-bar2014,
+che-cho-cai2018}.
 
@@
 
-%
-%\begin{wrapfigure}[20]{r}{2.5in}
-%\vspace*{-13pt}
-%\centerline{\includegraphics[width=2.4in]{figures/integrands}}
-%\vspace*{-13pt}
-%  \caption{{\footnotesize The Fourier modes of
-%  $K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ where
-%  $|\mathbf{x_0}| = 0.99$, $\mathbf{y} \in \partial\Omega$, and
-%  $\Omega$ is the unit disk. The trapezoid rule applied to the red
-%  integrand has large amounts of error, but the trapezoid rule is much
-%  more accurate when applied to the blue integrand. Since the difference
-%  between the red and blue curves can be accurately computed with the
-%  barycentric quadrature rule, the quadrature error applied to layer
-%  potentials for the screened Laplace equation will be uniformly bounded
-%  in $\Omega$.}}
-%\label{fig:integrands}
-%\end{wrapfigure}
-Discretizations of carefully chosen BIEs can be solved with a
-mesh-independent number of GMRES
-iterations~\cite{cam-ips-kel-mey-xue1996}. Therefore, the required CPU
-time is proportional to the cost of a matrix-vector multiplication that
-can be performed in optimal or near-optimal time with the fast multipole
-method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2, fmm3,
-fmm4, fmm6, fmm7, fmm8}. PI BQ is experienced with applying FMMs for the
-Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the screened
-Laplace equation~\cite{kro-qua2011, qua2011}.  Alternatively, fast
-direct solvers avoid iteration~\cite{fds2, fds3, fds4, fds5, fds6, fds7,
-ho2016cpam1, minden2016, minden2017siammms}, but often require a large
-amount of computational overhead, and this makes them less practical for
-problems with moving geometries. Alternatively, fast direct solver
-techniques can be used to develop efficient preconditioning strategies
-such as the inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017}.
-PI BQ used the IFMM to precondition Stokes
-equations~\cite{qua-cou-dar2018}. A suite of other preconditioners
-including sparse approximate inverses~\cite{che2000} and
+When solving for the density functions $\eta_0$, $\eta_1$, and $\sigma$,
+a carefully chosen IE formulation requires a mesh-independent number of
+GMRES iterations~\cite{cam-ips-kel-mey-xue1996}. Therefore, the required
+CPU time is proportional to the cost of a matrix-vector multiplication
+that can be performed in optimal or near-optimal time with the fast
+multipole method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2,
+fmm3, fmm4, fmm6, fmm7, fmm8}. PI BQ is experienced with applying FMMs
+for the Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the
+screened Laplace equation~\cite{kro-qua2011, qua2011}. Furthermore, to
+reduce the number of GMRES iterations, preconditioning strategies such
+as the inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017} and
+domain decomposition~\cite{che-bir2021}. PI BQ used the IFMM to
+precondition Stokes equations~\cite{qua-cou-dar2018}. A suite of other
+preconditioners including sparse approximate inverses~\cite{che2000} and
 multigrid~\cite{hem-sch1981, sch1982} will be investigated.
-%
-%Nearly touching bodies is ubiquitous in self-assembly of amphiphilic
-%particles, and this results in nearly-singular integrands. Quadrature
-%methods for these integrands have received a lot of attention in two and
-%three dimensions~\cite{alpert, kapur, sidi, duffy, bruno1, bruno2,
-%davis_1984, graglia_2008, hackbusch_sauter_1994, jarvenpaa_2003,
-%khayat_2005, schwab_1992, ying_2006, beale1, schwab_1992, ggq1, ggq2,
-%ggq3, helsing_2008a, helsing_tutorial_2012, klockner2013jcp, qbx2,
-%wala2019jcp, af2018sisc, siegel2018jcp, rachh2017jcp, ding2019arxiv,
-%bar2014}. The trapezoid rule is the workhorse for two-dimensional BIEs
-%since it achieves spectral accuracy when integrands are not
-%nearly-singular~\cite{tre-wei2014}. To address nearly-singular
-%integrands of two-dimensional BIEs, we will use a {\em barycentric
-%quadrature rule} that only requires a slight modification of the
-%trapezoid rule~\cite{ioa-pap-per1991}. In its current form, this method
-%requires the layer potential to satisfy Laplace or Stokes
-%equations~\cite{bar-wu-vee2015, chi-moo-qua2020}, but the PIs will
-%extend the method to layer potentials for the screened Laplace equation.
-%This will be done by recognizing that the fundamental solution of the
-%screened Laplace equation can be decomposed as $K(\mathbf{x},\mathbf{y})
-%= K_1(\mathbf{x},\mathbf{y}) + K_2(\mathbf{x},\mathbf{y})$, where
-%$K_1(\mathbf{x},\mathbf{y}) = -\log|\mathbf{x} - \mathbf{y}|$ and
-%$K_2(\mathbf{x},\mathbf{y}) = K(\mathbf{x},\mathbf{y}) + \log|\mathbf{x}
-%- \mathbf{y}|$. Then, layer potentials involving
-%$K_1(\mathbf{x},\mathbf{y})$ can be accurately computed with the
-%barycentric quadrature rule~\cite{ioa-pap-per1991}, and layer potentials
-%involving $K_2(\mathbf{x},\mathbf{y})$ can be accurately computed with
-%the trapezoid rule since the kernel is bounded for all $\mathbf{x}$ and
-%$\mathbf{y}$. The proposed method is demonstrated in
-%Figure~\ref{fig:integrands}, where the amplitude of the Fourier modes of
-%$K(\mathbf{x_0},\mathbf{y})$ and $K_2(\mathbf{x_0},\mathbf{y})$ are
-%plotted. The quadrature error of the trapezoid rule is the sum of the
-%unresolved Fourier modes.
 
 % ----------------------------------------------------------------------
-\subsubsection{Eliminating contact with adaptive time stepping and
-repulsion}
+\subsubsection{Eliminating contact with adaptive time stepping}
 \label{subsec:timeStepping}
@@
 particles is avoiding particle collision. The hydrophobic attraction
-potential drives the amphiphilic particles towards one another and
-this leads to physical contact in
-finite time. Such particle collisions in a dense, rigid-body suspension
-are a great challenge and can be a bottleneck in large-scale simulations.
-We propose two algorithms to remedy this computational challenge:
-high-order adaptive time stepping and repulsion forces.
-
-PI BQ developed a high-order adaptive time stepping method for
-hydrodynamic suspensions \cite{qua-bir2016}, and it has served as a
-robust method to simulate processes including mixing and adhesion in
-suspensions~\cite{qua-vee-you2019, kab-qua-bir2017}. The method uses
-a single-step, high-order time stepping method and a computationally
-cheap estimate of the error. The proposed work will use a spectral
+potential drives the amphiphilic particles towards one another and this
+leads to physical contact in finite time. Such particle collisions in a
+dense, rigid-body suspension are a great challenge and can be a
+bottleneck in large-scale simulations. We propose to remedy this
+computational challenge by developing novel high-order adaptive time
+stepping methods. PI BQ developed a high-order adaptive time stepping
+method for hydrodynamic suspensions \cite{qua-bir2016}, and it has
+served as a robust method to simulate processes including mixing and
+adhesion in suspensions~\cite{qua-vee-you2019, kab-qua-bir2017}.
+Following this previous work, the proposed work will use a spectral
 deferred correction method~\cite{dut-gre-rok2000} since it iteratively
 applies a low-order, single-step method to achieve high-order accuracy.
-To estimate the error, at each time step, we will compute the total force
-and torque of the system which is computationally cheap and physically
-zero. PI BQ's experience is that error estimates based on physical
-constraints such as force- and torque-free conditions appropriately
-determine how the time step should be adjusted so that the dynamics are
-resolved without the computational expense of techniques such as
-embedded Runge-Kutta methods, step-doubling, and Richardson
+To estimate the error, at each time step, we will compute the total
+force and torque of the system which is computationally cheap and
+physically zero. PI BQ's experience is that error estimates based on
+physical constraints such as force- and torque-free conditions
+appropriately determine how the time step should be adjusted so that the
+dynamics are resolved without the computational expense of techniques
+such as embedded Runge-Kutta methods, step-doubling, and Richardson
 extrapolation.
@@
 %%
-Our previous work avoided particle contact through Lennard-Jones body
-forces~\cite{Fu2018_SIAM}. Such steep, short-range, steric interactions 
-introduce numerical stiffness and limit the time step size. To
-remove this stiffness, we propose a geometry-based contact
-method~\cite{har-pon-sor-zor2011}. This method has been applied to
-vesicle suspensions~\cite{lu-rah-zor2017} and to rigid body suspensions in
-two dimensions~\cite{bys-sha-qua2020} and three
-dimensions~\cite{Yan2019}. These methods determine repulsion force by
-solving a non-linear complementarity problem with a geometric constraint
-that the configuration is non-overlapping. In this manner, contact is
-avoided without the excessively small time steps required by stiff
-Lennard-Jones forces.
-
+%Our previous work avoided particle contact through Lennard-Jones body
+%forces~\cite{Fu2018_SIAM}. Such steep, short-range, steric interactions 
+%introduce numerical stiffness and limit the time step size. To
+%remove this stiffness, we propose a geometry-based contact
+%method~\cite{har-pon-sor-zor2011}. This method has been applied to
+%vesicle suspensions~\cite{lu-rah-zor2017} and to rigid body suspensions in
+%two dimensions~\cite{bys-sha-qua2020} and three
+%dimensions~\cite{Yan2019}. These methods determine repulsion force by
+%solving a non-linear complementarity problem with a geometric constraint
+%that the configuration is non-overlapping. In this manner, contact is
+%avoided without the excessively small time steps required by stiff
+%Lennard-Jones forces.
+%
 %%-------------------------------------------------------------------------------

### 2021-11-12 NSF2021/Description/specificaim1.tex
Hola

@@
 \end{equation}
-The boundary condition $g$ that imposes 
-the water structure at the water-hydrocarbon interfaces.
-It is a material label that is transported with the particle motions.
+The boundary condition $g$
+is a material label that is transported with the particle motions
+(Figure \ref{fig:bcs}).
+\begin{wrapfigure}[12]{r}{0.65\textwidth}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
+\caption{
+  Boundary conditions characterize the type of water structure:
+  an amphiphilic particle (left),
+  a hydrophobic particle with anisotropic intensity (middle),
+  a water structure with plus/minus polarity (right).
+  The dashed curve is the boundary of the disk and the arrow its
+  director. 
+}
+\label{fig:bcs}
+\end{wrapfigure}
 

### 2021-11-12 NSF2021/Description/specificaim1.tex
made it to part way through SA1

--- 2021-11-11 NSF2021/Description/specificaim1.tex
@@
 facilitate optimal design of smart materials by tuning the geometry and
-properties of the amphiphilic particles.
-Specific Aim 1 achieves this through a novel mathematical model
-for particle self-organization driven by long-range interfacial forces.
+properties of the amphiphilic particles.  Specific Aim 1 achieves this
+through a novel mathematical model for particle self-organization driven
+by long-range interfacial forces.
 
 \subsubsection{Problem formulation}
-The mathematical formulation is a nonlinear system 
-for the dynamics of a collection of particles. The 
-interactions come from a system of linear partial differential equations
-(PDE) and comprise hydrodynamic interactions and hydrophobic interactions.
-The formulation prevents particle collisions through excluded volume
-potentials.
+The mathematical formulation is a nonlinear system for the dynamics of a
+collection of particles. The interactions come from a system of linear
+partial differential equations (PDE) and comprise hydrodynamic
+interactions and hydrophobic interactions.  The formulation prevents
+particle collisions through excluded volume potentials.
 
-  \begin{figure}[h!]
-\begin{center}
-  \includegraphics[width=0.8\textwidth]{figures/SpecificAim1/Domain.pdf}
-\end{center}  
-  \caption{\label{fig:flow_map} A collection of 3D
-   amphiphilic particles suspended in a solvent. The solvent velocity
-   satisfies the Stokes equations, and the hydrophobic forces depend on
-   the solvent activity that satisfies the screened Laplace equation.
-   The geometry is updated by solving the mobility problem.}     
-  \end{figure}
+%\begin{wrapfigure}[h!]
+\begin{wrapfigure}[9]{r}{0.55\textwidth}
+  \centering
+  \vspace{-20pt}
+  \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.pdf}
+  \caption{\label{fig:flow_map} A collection of amphiphilic particles
+  suspended in a solvent. The solvent velocity satisfies the Stokes
+  equations, and the hydrophobic forces depend on the solvent activity
+  that satisfies the screened Laplace equation. The geometry is updated
+  by solving the mobility problem.}
+\end{wrapfigure}
 
@@
 negligible, the particle motion is goverened by the Stokes equations
+\begin{subequations}
+  \label{eq:stokes}
   \begin{alignat}{3}
   \label{eq:stokes1}
-  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
-    && \xx \in \Omega, \\
+  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
     \label{eq:stokes2}
@@
   \end{alignat}
+\end{subequations}
+%\begin{alignat}{3}
+%\label{eq:stokes1}
+%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
+%    && \xx \in \Omega, \\
+%\label{eq:stokes2}
+%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
+%\label{eq:stokes3}
+%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
+%\end{alignat}
 %
@@
 -\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g
-\text{ on } \Omega.
+\text{ on } \bd\Omega.
 \end{equation}
-The boundary condition $g$ that imposes 
-the water structure at the water-hydrocarbon interfaces.
-It is a material label that is transported with the particle motions.
+The boundary condition $g$ is a material label that is transported with
+the particle motions (Figure~\ref{fig:bcs}).
 
-The coupling between the Stokes equations \eqref{eq:stokes1}-\eqref{eq:stokes3}
-and the semilinear elliptic equation \eqref{eq:SL}
-comes from the first variation of the energy functional.
-The particles minimize the free energy $F[u]$
-by altering the location of hydrophobic interfaces. 
-It is possible to calculate the rate of change of $F[u]$
-using variation of the domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}.
-Carrying out this variation yields a 
+\begin{wrapfigure}[10]{r}{0.65\textwidth}
+  \vspace{-22pt}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
+\caption{\label{fig:bcs} Boundary conditions characterize the type of
+  water structure: an amphiphilic particle (left), a hydrophobic
+  particle with anisotropic intensity (middle), a water structure with
+  plus/minus polarity (right). The dashed curve is the boundary of the
+  disk and the arrow its director.}
+\end{wrapfigure}
+The coupling between the Stokes equations \eqref{eq:stokes} and the
+semilinear elliptic equation \eqref{eq:SL} comes from the first
+variation of the energy functional.  The particles minimize the free
+energy $F[u]$ by altering the location of hydrophobic interfaces.  It is
+possible to calculate the rate of change of $F[u]$ using variation of
+the domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}.  Carrying out
+this variation yields a 
 %The hydrophobic forces are torques are
@@
     \end{center}
-  \caption{
-    Self assembly with a polar boundary condition leads to checkboard pattern.
-    Green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
+  \caption{ Self assembly with a polar boundary condition leads to
+  checkboard pattern.  Green is for $u < 0$, yellow is for $u > 0$, and
+  blue is for $u = 0$.
     \label{fig:self-assemblyA}}
 \end{figure}
+\todo{This figure is not referenced in the text.}
 
@@
   aqueous phase. 
-      \label{fig:self-assemblyA}}
+      \label{fig:self-assemblyB}}
 \end{figure}
+\todo{This figure is not referenced in the text.}
 Amphiphilic particles have a hydrophobic tail and a hydrophilic head
@@
       than the other (yellow).
-    \label{fig:self-assemblyA}}
+    \label{fig:self-assemblyC}}
 \end{center}
 \end{figure}
+\todo{This figure is not referenced in the text.}
 
@@
 an evolving monolayer dividing surface $\Sigma$ and director field ${\bf
-n}$ by interpolating the particle centers and orientations. Using
-\eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$ from the
-interpolated shapes.
+n}$ by interpolating the particle centers and orientations.
+Using~\eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$
+from the interpolated shapes.
 

### 2021-11-12 NSF2021/Description/specificaim1.tex
still working on SA1

@@
 \subsubsection{Problem formulation}
-The mathematical formulation is a nonlinear system for the dynamics of a
-collection of particles. The interactions come from a system of linear
-partial differential equations (PDE) and comprise hydrodynamic
-interactions and hydrophobic interactions.  The formulation prevents
-particle collisions through excluded volume potentials.
-
 %\begin{wrapfigure}[h!]
-\begin{wrapfigure}[9]{r}{0.55\textwidth}
+\begin{wrapfigure}[10]{r}{0.55\textwidth}
   \centering
-  \vspace{-20pt}
+  \vspace{-12pt}
   \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.pdf}
@@
 
+The mathematical formulation is a nonlinear system for the dynamics of a
+collection of particles. The interactions come from a system of linear
+partial differential equations (PDEs) and comprise hydrodynamic
+interactions and hydrophobic interactions.
+%The formulation prevents particle collisions through excluded volume
+%potentials. 
 The hydrodynamic interactions come from the mobility problem for rigid
-particles immersed in a viscous solvent. Assuming inertial terms are
+particles immersed in a viscous solvent, which we solve with a
+second-order Adams-Bashforth method. Assuming inertial terms are
 negligible, the particle motion is goverened by the Stokes equations
@@
 where $\uu$ is the velocity and $p$ is the pressure of the solvent,
-$\uu_\infty$ is the background flow, and $\mu$ is the constant
-solvent viscosity. The domain
-$\Omega$ is the fluid region surrounding the particles.
-Since the particles are rigid, the solvent velocity 
-satisfies a no-slip boundary condition for a rigid body motion 
+$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
+viscosity. The domain $\Omega$ is the fluid region surrounding the
+particles. Since the particles are rigid, the solvent velocity satisfies
+a no-slip boundary condition for a rigid body motion 
 %\begin{align}
@@
 %\end{align}
-on the particle boundary $\Gamma_i$
-with translational velocity $\vv_i$ and
-angular velocity $\omega_i$.
-Given imposed forces acting on each particle,
-the \emph{mobility problem} consists of finding
-translational and angular velocities so that 
-viscous fluid forces balance the imposed forces.
+on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
+and angular velocity $\omega_i$. Given imposed forces acting on each
+particle, the \emph{mobility problem} consists of finding
+translational and angular velocities so that viscous fluid forces
+balance the imposed forces.
 
-The hydrophobic interactions come from the tendency 
-of particles to minimize the free energy of the structure of
-the surrounding water molecules.  
-Experimental measurements suggest that the free energy functional
-take the form 
-\begin{equation}
+The hydrophobic interactions come from the tendency of particles to
+minimize the free energy of the structure of the surrounding water
+molecules. Experimental measurements suggest that the free energy
+functional take the form 
+\begin{align*}
 \label{eq:free_energy}
-F[u] = C \int_{\Omega}  \rho |\nabla u|^2 + \rho^{-1} f(u) \,dx
-\end{equation}
-where
-$u$ is an order parameter for the structure of water,
-$\rho$ is a decay length,
-$C$ is a constant, and $f(u)$ is a potential.
-Hydrogen-bond persistence times are on the order of picoseconds \cite{MaGa13}.
-Since waters reorient 
-on a time scale much smaller than for the particle motion, 
-then at each moment in time $u$ minimizes $F[u]$ and satisfies 
+  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
+  \,d\xx,
+\end{align*}
+where $u$ is an order parameter for the structure of water, $\rho$ is a
+decay length, $C$ is a constant, and $f(u)$ is a potential.
+Hydrogen-bond persistence times are on the order of picoseconds
+\cite{MaGa13}. Since waters reorient on a time scale much smaller than
+the particle motion, $u$ minimizes $F[u]$ at all time, and therefore
+satisfies 
 \begin{equation}
 \label{eq:SL}
--\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g
+-\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g,
 \text{ on } \bd\Omega.
@@
 \end{align}
-The imposed forces and torques from the integration of $\mathbf{T}$ along the
-particle boundary.
-The density \eqref{eq:stress}  was first introduced
-by~\cite{Fu2018_SIAM} and is the higher-dimensional analogue of
-disjoining pressure calculated by
-\cite{MaRa76, ErLjCl89, KoNa15, Nagle17, KUZMIN2005}.
-It is the mathematical ingredient responsible for forming particle
-aggregates that sequester their hydrophobic surface regions.
+The imposed forces and torques from the integration of $\mathbf{T}$
+along the particle boundary. The density~\eqref{eq:stress} was first
+introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional analogue
+of disjoining pressure calculated by \cite{MaRa76, ErLjCl89, KoNa15,
+Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
+forming particle aggregates that sequester their hydrophobic surface
+regions.
 
-By solving the above system, we obtain translational and angular
-velocities of the many-body system. 
-A second-order Adams-Bashforth scheme updates the particle positions and orientations.
+%By solving the above system, we obtain translational and angular
+%velocities of the many-body system. A second-order Adams-Bashforth
+%scheme updates the particle positions and orientations.
 
-The formulation presents a number of
-mathematical and numerical challenges. For one, the domain is constantly
-changing so that a new boundary value problem must be solved at each time step.
-The particle boundaries are nearly touching and this requires
-high-order numerical schemes to accurately calculated forces.
-The domain is unbounded and there are issues with accurately
-calculating the velocity in the far-field. 
-Finally, the numerical routine must handle
-large system sizes efficiently when their are many particles
-is large.
+The formulation presents a number of mathematical and numerical
+challenges. For one, the domain is constantly changing so that a new
+boundary value problem must be solved at each time step.  The particle
+boundaries are nearly touching and this requires high-order numerical
+schemes to accurately calculate forces and adaptively chose an
+appropriate time step size. Furthermore, there are issues with
+accurately capturing the far-field boundary conditions in the unbounded
+domain. Finally, the numerical routine must handle large system sizes
+efficiently when their are many particles is large.
 
@@
 \subsubsection{Janus-particle self-assembly} 
-In the linear response case,
-take $f(u) = u^2$ so that water structure has its lowest potential value
-at $u = 0$, representing bulk water. The solutions of \eqref{eq:SL} have
-a boundary layer structure and decay to 0 in the bulk with the decay
-length $\rho$. Nevertheless, a number of morphologies arise by altering
-boundary conditions.
+When $f(u) = u^2$, and the water structure has its lowest potential
+value at $u=0$ which represents bulk water. The solutions of
+\eqref{eq:SL} have a boundary layer structure and decay to $0$ in the
+bulk with the decay length $\rho$. Even in this linear response case, a
+number of morphologies arise by altering boundary conditions.
 
@@
     \end{center}
-  \caption{ Self assembly with a polar boundary condition leads to
-  checkboard pattern.  Green is for $u < 0$, yellow is for $u > 0$, and
-  blue is for $u = 0$.
-    \label{fig:self-assemblyA}}
+  \caption{\label{fig:self-assemblyA} Self-assembly with a polar
+  boundary condition leads to a checkerboard pattern. Green is for $u <
+  0$, yellow is for $u > 0$, and blue is for $u = 0$.}
 \end{figure}
-\todo{This figure is not referenced in the text.}
 
-Consider a polar boundary condition where
-$g_i(\mathbf{x}) = (\pi r)^{-1/2} \cos (\theta_i(\mathbf{x}))$
-where $\theta_i$ is the angle formed by $\mathbf{x}$, the particle
-center $\mathbf{a}_i$, and the particle director $\mathbf{d}_i$.
-The normalization $(\pi r)^{-1/2}$ here and others below
-provide for a uniform surface energy $\int_{\Gamma_i} g_i^2 \,ds = 1$
-when the particles are disks of radius $r$.
-The boundary condition is odd along the particle axis 
-making the particle head repel the tail.
-We simulate the dynamics of 100 particles with random initial position
-and orientation. The particles rapidly form chains with their
-directors perpendicular to the length of the chain. The equilibrium
-structure consists particles positioned on a square grid
-in a checkerboard pattern. This patterning is a consequence of energy
-minimality and allows each particle to simultaneously
-coordinate its head with that of three other particles
-and its tail with that of three other particles.
+Consider a polar boundary condition where $g_i(\xx) = (\pi r)^{-1/2}
+\cos (\theta_i(\xx))$ where $\theta_i$ is the angle formed by $\xx$, the
+particle center $\aa_i$, and the particle director $\dd_i$. The
+normalization $(\pi r)^{-1/2}$ and others below provide a uniform
+surface energy $\int_{\Gamma_i} g_i^2 \,ds = 1$ for circular particles
+of radius $r$. The boundary condition is odd along the particle axis
+making the particle head repel the tail.  We simulate the dynamics of
+100 particles with random initial position and orientation. The
+particles rapidly form chains with their directors perpendicular to the
+length of the chain. The equilibrium structure consists of particles
+positioned on a square grid in a checkerboard pattern
+(Figure~\ref{fig:self-assemblyA}. This patterning is a consequence of
+energy minimality and allows each particle to simultaneously coordinate
+its head with the head of three other particles and its tail with the
+tail of three other particles.
 
@@
     \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B2.pdf}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B3.pdf}\\
+    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B3.pdf}
 \end{center}    
-\caption{With an amphiphilic boundary condition particles self-assemble
-  into bilayers. The patterning shields the hydrophobic core (yellow) from the
-  aqueous phase. 
-      \label{fig:self-assemblyB}}
+  \caption{\label{fig:self-assemblyB} Self-assembly with with boundary
+  condition that results in hydrophobic tails and hydrophilic heads. The
+  resulting bilayer pattern shields the hydrophobic core (yellow) from
+  the aqueous phase.}
 \end{figure}
-\todo{This figure is not referenced in the text.}
-Amphiphilic particles have a hydrophobic tail and a hydrophilic head
-and are accounted for as follows.
-The hydrophilic side takes the value $u = 0$ since the
-apolar headgroup of a lipid, for example, does not alter the structure
-of adjacent waters. The hydrophobic side takes the value $u > 0$. 
-The interaction between particles is attractive. Using
-$(3\pi )^{-1/2}(1 + \cos(\theta_i(\mathbf{x})))$
-as a simple modification to the previous boundary condition 
-produces two-dimensional micelles and bilayers \cite{Fu2018_SIAM}.
-Researchers have asked us if the phenomenon is robust. To show
-that it is, we use 
+Amphiphilic particles have a hydrophobic tail and a hydrophilic head and
+are accounted for as follows. The hydrophilic side takes the value $u =
+0$ since the apolar head of a lipid, for example, does not alter
+the structure of adjacent waters. The hydrophobic side takes the value
+$u > 0$. The interaction between particles is attractive. Using $(3\pi
+)^{-1/2}(1 + \cos(\theta_i(\xx)))$ as a simple modification to
+the previous boundary condition produces two-dimensional micelles and
+bilayers \cite{Fu2018_SIAM} (Figure~\ref{fig:self-assemblyB}).
+Researchers have asked us if the phenomenon is robust. To show that it
+is, we instead use the boundary condition
 \begin{equation}
 \label{eq:vonMises}
-g_i(\mathbf{x}) =
-\sqrt{
-  \frac{\exp( \kappa_i(\theta_i(\mathbf{x}) - \theta^0_i))}
+  g_i(\xx) = \sqrt{
+  \frac{\exp( \kappa_i(\theta_i(\xx) - \theta^0_i))}
   {2\pi r_i I_0(\kappa_i)}}
 \end{equation}
-instead where the radicand is the von Mises 
-distribution with director angle $\theta^0_i$ and Bessel function
-$I_0$ of order zero. The square of this function behaves as a normal
-distribution with variance like $1/\kappa_i$. To replicate
-experimental conditions, the concentration $\kappa_i$ and radii
-$r_i$ are randomized. Using the same initial configuration, the
-particles form small groups. The small groups combine to form bilayers.
+where the radicand \todo{radicand?} is the von Mises distribution with
+director angle $\theta^0_i$ and Bessel function $I_0$ of order zero. The
+square of this function behaves as a normal distribution with variance
+like $1/\kappa_i$.To replicate experimental conditions, the
+concentration $\kappa_i$ and radii $r_i$ are randomized. Using the same
+initial configuration, the particles form small groups that
+combine to form bilayers (Figure~\ref{fig:self-assemblyC}.
 
@@
     \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C3.pdf}\\
-    \caption{This figure is for hydrophobic particles with a bias. The
-      hydrophobic intensity is greater on one side of the particle (magenta)
-      than the other (yellow).
+    \caption{Hydrophobic particles with a bias. The hydrophobic
+    intensity is greater on one side of the particle (magenta) than the
+    other (yellow).
     \label{fig:self-assemblyC}}
@@
 \end{figure}
-\todo{This figure is not referenced in the text.}
 
 Multilamelar bilayers arise with an increase by shifting the boundary condition
-further. Let $g_i(\mathbf{x}) = (9\pi )^{-1/2}(2 + \cos(\theta_i(\mathbf{x})))$.
+further. Let $g_i(\xx) = (9\pi )^{-1/2}(2 + \cos(\theta_i(\xx)))$.
 This gives a hydrophobic particle with greater intensity of hydrophobicity
@@
 \subsubsection{Hydrophobic forces as capillary wetting}
-A natural generalization of the linear response model is 
-to use a fourth-order, tilted double-well potential
-$f(u) = a(u-u_0)^2(u-u_1)^2 + bu$.
-Motivated by capillary wetting, soft matter physicist Gerhard Gompper 
-introduced a double-well model for one-dimensional hydrophobic attraction
-\cite{GoHaKo94}. The two-dimensional attraction we propose
-is more complicated and includes extra line tension effects
-not present in the one-dimensional theories.
+A natural generalization of the linear response model is to use a
+fourth-order, tilted double-well potential $f(u) = a(u-u_0)^2(u-u_1)^2 +
+bu$. Motivated by capillary wetting, soft matter physicist Gerhard
+Gompper introduced a double-well model for one-dimensional hydrophobic
+attraction \cite{GoHaKo94}. The two-dimensional attraction we propose is
+more complicated and includes extra line tension effects not present in
+the one-dimensional theories.
 
-Here, the order parameter $u$ is the mean number of nearest
-neighbors per water molecule.
-The value $u_0 = 4$ gives a local minimum for the ideal
-tetrahadral water network found at hydrophobic surfaces.  
-The value $u_1 \sim 4.4$ gives the absolute minimum
-in the bulk where there is a mixture of four and five-coordinated
-waters.
-When particles are well-separated, the energetic cost for filling
-the interstitial region with $u_0$-phase water is prohibitive
-and there is a phase shift from the $u_0$ to $u_1$ water order
----the attraction landscape is more
-or less identical to the linear response theory. Conversely, when
-particles are proximal, it becomes energetically favorable
-to coalesce $u_0$-phases. This introduces a line tension
-for the phase transition.
+Here, the order parameter $u$ is the mean number of nearest neighbors
+per water molecule. The value $u_0 = 4$ gives a local minimum for the
+ideal tetrahadral water network found at hydrophobic surfaces. The value
+$u_1 \sim 4.4$ gives the absolute minimum in the bulk where there is a
+mixture of four and five-coordinated waters. When particles are
+well-separated, the energetic cost for filling the interstitial region
+with $u_0$-phase water is prohibitive and there is a phase shift from
+the $u_0$ to $u_1$ water order---the attraction landscape is more or
+less identical to the linear response theory. Conversely, when particles
+are proximal, it becomes energetically favorable to coalesce
+$u_0$-phases. This introduces a line tension for the phase transition.
 
-The equation \eqref{eq:SL} takes the form of a steady-state
-Allen-Cahn equation. The Allen-Cahn equation is used in phase field
-formulations of immisible fluids, for example.
-PI Ryham and colaborators launched the simulation and asymptotic analysis
-of phase field functionals of membrane elastic energy,
-devising functionals for  
-for the squared mean curvature (Willmore) energy \cite{0951-7715-18-3-016}, 
-spontaneous curvature \cite{Du05} and Gaussian curvature energy \cite{DuEuler},
-as well as energetic variational approaches to coupling membrane elasticity to fluids \cite{QiangDu09}.
+Equation~\eqref{eq:SL} takes the form of a steady-state Allen-Cahn
+equation. The Allen-Cahn equation is used in phase field formulations of
+immisible fluids, for example. PI RR and colaborators launched the
+simulation and asymptotic analysis of phase field functionals of
+membrane elastic energy, devising functionals for for the squared mean
+curvature (Willmore) energy~\cite{0951-7715-18-3-016}, spontaneous
+curvature~\cite{Du05} and Gaussian curvature energy~\cite{DuEuler}, as
+well as energetic variational approaches to coupling membrane elasticity
+to fluids~\cite{QiangDu09}.
 
@@
 are well-fit by a double exponential curve in the 10 to 100 nanometer range
-of separation.  Below 10 nm, however, there is an amplification of force
+of separation. Below 10~nm, however, there is an amplification of force
 and the attraction follows a much steeper force law not accounted
-for by past phenomenoloical theories \cite{Lin2005}.
+for by past phenomenoloical theories~\cite{Lin2005}.
 
-It may be the case that the double-well formulation recreates the
-long and short-range interactions.  The advantage
-is that the two-dimensional simulations can replicate the
-experimental setup better than prior, one-dimensional theoretical work 
-Some of the model parameters directly connect 
-to long-range decay lengths and energy cost of creating hydrophobic-water
-interfaces with established ranges of values. Other parameters, like the
-well structure, are fit to the measured data. These base-line simulations
-will allow us to move on to provide more accurate colloidal suspension
-simulations.
+It may be the case that the double-well formulation recreates the long
+and short-range interactions. The advantage is that the two-dimensional
+simulations can replicate the experimental setup better than prior,
+one-dimensional theoretical work Some of the model parameters directly
+connect to long-range decay lengths and energy cost of creating
+hydrophobic-water interfaces with established ranges of values. Other
+parameters, like the well structure, are fit to the measured data. These
+base-line simulations will allow us to move on to provide more accurate
+colloidal suspension simulations.
 
-Other approaches will be required if the modified phenomenological theory 
-does not recreate the measured force curves.
-We can rule out convection in the water structure since  
-the time scale of particle motion is much larger than
-the hydrogen-bond lifetimes. One approach is to consider Gaussian fluctuation.
-Here, we expand the free energy functional around the saddle point solution.
-The fluctuation energy then involves calculation of the eigenfunctions of
-the second variation of the free energy. This accounts for the fact
-that experimental measurements are carried out at finite 
-temperatures, where thermal fluctuations should ideally also be considered.
+Other approaches will be required if the modified phenomenological
+theory does not recreate the measured force curves. We can rule out
+convection in the water structure since the time scale of particle
+motion is much larger than the hydrogen-bond lifetimes. One approach is
+to consider Gaussian fluctuation. Here, we expand the free energy
+functional around the saddle point solution. The fluctuation energy
+then involves calculation of the eigenfunctions of the second variation
+of the free energy. This accounts for the fact that experimental
+measurements are carried out at finite temperatures, where thermal
+fluctuations should ideally also be considered.
 

### 2021-11-13 NSF2021/Description/broaderimpacts.tex

@@
 This project aims to advance the mathematical modeling of collective
-dynamics of amphiphilic particles. The simulations use a new, yet intuitive,
-approach that can account for important and complex systems that are out of 
-reach in computational material science. These complex systems include 
-fusion and fission of amphiphilic bilayer membranes and optimal shape design
-in metamaterials. The development of three-dimensional 
-models describing colloidal systems could be transformative in biomedicine
-and material science. The research draws from expertise in scientific 
-computing, physics of fluids, and mathematics. The mathematical component 
-incorporates leading techniques from geometric analysis and offers  
-insight 
-into fundamentals of material science.
-The project brings socially consequential research into the classroom, and offers undergraduates the opportunity to train alongside graduate students and postdoctoral fellows.
-With its combination of mathematical modeling, analysis, and scientific computing, the project highlights the importance of mathematics and computation to all areas of science and engineering.
+dynamics of amphiphilic particles. The simulations use a new, yet
+intuitive, approach that accounts for important and complex systems
+that are out of reach in computational material science. These complex
+systems include fusion and fission of amphiphilic bilayer membranes and
+optimal shape design in metamaterials. The development of
+three-dimensional models describing colloidal systems could be
+transformative in biomedicine and material science. The research draws
+from expertise in scientific computing, physics of fluids, and
+mathematics. The mathematical component incorporates leading techniques
+from geometric analysis and offers insight into fundamentals of material
+science. The project brings socially consequential research into the
+classroom, and offers undergraduates the opportunity to train alongside
+graduate students and postdoctoral fellows. With its combination of
+mathematical modeling, analysis, and scientific computing, the project
+highlights the importance of mathematics and computation to all areas of
+science and engineering.
 %The proposed mathematical analysis, modeling, and numerical algorithms
@@
 \section{Intellectual Merit}
-The purpose of this research is to reach interesting physical phenomena with 
-less computational cost than molecular dynamics, and account for more general
-features that continuum theory misses. The main ingredient is defining a 
-nonlocal interaction through the solution of an elliptic boundary value problem
-that has the phenomenological characteristics of long-range hydrophobic
-attraction. It turns out that this minimal model gives rise to rich phenomena
-for Janus particle aggregates and correctly predicts elastic properties of bilayer. 
-The technical research tasks include quantifying collective properties of 
-amphiphilic ensembles, mathematical analysis of continuum elastic energies, 
-efficient, high-order numerical algorithms for large-scale simulations, and 
-incorporating external fields through electric charge. Lastly, the proposal 
-extends the results using three-dimensional boundary integral formulations.
+The purpose of this research is to reach interesting physical phenomena
+with less computational cost than molecular dynamics, and account for
+more general features that continuum theory misses. The main ingredient
+is defining a nonlocal interaction through the solution of an elliptic
+boundary value problem that has the phenomenological characteristics of
+long-range hydrophobic attraction. It turns out that this minimal model
+gives rise to rich phenomena for Janus particle aggregates and correctly
+predicts elastic properties of bilayer. The technical research tasks
+include quantifying collective properties of amphiphilic ensembles,
+mathematical analysis of continuum elastic energies, efficient,
+high-order numerical algorithms for large-scale simulations, and
+incorporating external fields through electric charge. Lastly, the
+proposal extends the results using three-dimensional boundary integral
+formulations.
 

### 2021-11-13 NSF2021/Description/specificaim2.tex

@@
 simulate dynamic assembly of particles under HAP potential in a viscous
-solvent. As described in~\eqref{eq:stokes1}--\eqref{eq:stokes3} and
-illustrated in Figure~\ref{fig:flow_map}, the solvent phase is modeled
-by the Stokes equations for an incompressible, viscous fluid, and these
-equations are coupled to the screened-Laplace equation~\eqref{eq:SL}
-through viscous and hydrophobic stress balance.
+solvent. As described in~\eqref{eq:stokes} and illustrated in
+Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
+equations for an incompressible, viscous fluid, and these equations are
+coupled to the screened-Laplace equation~\eqref{eq:SL} through viscous
+and hydrophobic stress balance.
 
@@
 The HAP model requires solving exterior problems for the order
-parameter~\eqref{eq:SL} and the Stokes
-equations~\eqref{eq:stokes1}--\eqref{eq:stokes3}. We will develop
-methods based on combinations of volume and layer potentials. Numerical
-methods to solve these integral equations (IEs) have several advantages
-over their PDE-based counterpart: by construction, they satisfy
-far-field and mass conservation conditions; only $\partial\Omega$ needs
-to be discretized for layer potentials; carefully chosen IEs result in a
-well-conditioned linear system that is solved with a mesh-independent
-number of GMRES iterations; and high-order or spectral accuracy is
-attainable with appropriate quadrature methods. The PIs have
-demonstrated that IEs are a powerful tool to simulate two-dimensional
-suspensions of amphiphilic particles~\cite{Fu2018_SIAM, FuQuRyYo20}.
-Moreover, elements of these formulations have been described in three
-dimensions~\cite{ying_2006, manasthesis, rac-gre2016}. This proposal
-will extend the two-dimensional methods to more general amphiphilic
-particle models that satisfy~\eqref{eq:SL}, and all the methods can
-naturally be extended to three dimensions. \S\ref{subsec:AC} describes
-how the non-linear Allen-Cahn equation~\eqref{eq:SL} will be iteratively
-solved using IE formulations. Then, \S\ref{subsec:NumericalIssues}
-describes how we will combine preconditioning strategies with fast
-summation methods to accelerate the time to solution, and
-\S\ref{subsec:timeStepping} describes adaptive time stepping methods,
+parameter~\eqref{eq:SL} and the Stokes equations~\eqref{eq:stokes}. We
+will develop methods based on combinations of volume and layer
+potentials. Numerical methods to solve these integral equations (IEs)
+have several advantages over their PDE-based counterpart: by
+construction, they satisfy far-field and mass conservation conditions;
+only $\partial\Omega$ needs to be discretized for layer potentials;
+carefully chosen IEs result in a well-conditioned linear system that is
+solved with a mesh-independent number of GMRES iterations; and
+high-order or spectral accuracy is attainable with appropriate
+quadrature methods. The PIs have demonstrated that IEs are a powerful
+tool to simulate two-dimensional suspensions of amphiphilic
+particles~\cite{Fu2018_SIAM, FuQuRyYo20}. Moreover, elements of these
+formulations have been described in three dimensions~\cite{ying_2006,
+manasthesis, rac-gre2016}. This proposal will extend the two-dimensional
+methods to more general amphiphilic particle models that
+satisfy~\eqref{eq:SL}, and all the methods can naturally be extended to
+three dimensions. \S\ref{subsec:AC} describes how the non-linear
+Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved using IE
+formulations. Then, \S\ref{subsec:NumericalIssues} describes how we will
+combine preconditioning strategies with fast summation methods to
+accelerate the time to solution, and \S\ref{subsec:timeStepping}
+describes adaptive time stepping methods,
 

### 2021-11-13 NSF2021/Description/specificaim1.tex
finished up first pass through SA1

@@
 \end{wrapfigure}
-The coupling between the Stokes equations \eqref{eq:stokes} and the
-semilinear elliptic equation \eqref{eq:SL} comes from the first
+The coupling between the Stokes equations~\eqref{eq:stokes} and the
+semilinear elliptic equation~\eqref{eq:SL} comes from the first
 variation of the energy functional. The particles minimize the free
@@
 When $f(u) = u^2$, and the water structure has its lowest potential
-value at $u=0$ which represents bulk water. The solutions of
-\eqref{eq:SL} have a boundary layer structure and decay to $0$ in the
+value at $u=0$ which represents bulk water. The solutions
+of~\eqref{eq:SL} have a boundary layer structure and decay to $0$ in the
 bulk with the decay length $\rho$. Even in this linear response case, a
@@
 of radius $r$. The boundary condition is odd along the particle axis
-making the particle head repel the tail.  We simulate the dynamics of
-100 particles with random initial position and orientation. The
-particles rapidly form chains with their directors perpendicular to the
-length of the chain. The equilibrium structure consists of particles
-positioned on a square grid in a checkerboard pattern
+making the particle head repel the tail. We simulate the dynamics of 100
+particles with random initial position and orientation. The particles
+rapidly form chains with their directors perpendicular to the length of
+the chain. The equilibrium structure consists of particles positioned on
+a square grid in a checkerboard pattern
 (Figure~\ref{fig:self-assemblyA}. This patterning is a consequence of
@@
 
-Multilamelar bilayers arise with an increase by shifting the boundary condition
-further. Let $g_i(\xx) = (9\pi )^{-1/2}(2 + \cos(\theta_i(\xx)))$.
-This gives a hydrophobic particle with greater intensity of hydrophobicity
-at $\theta_i = 0$ than at $\theta_i = \pi$.  The initial self-assembly
-is similar to that of the amphiphilic particle case, except that the bilayers
-do not stay well separated.  Rather, the bilayers stack on top of each
-other as a consequence of the interfacial tension of exposed particle heads \cite{deMeetal21}.
+Multilamelar bilayers arise with an increase by shifting the boundary
+condition further. Let $g_i(\xx) = (9\pi )^{-1/2}(2 +
+\cos(\theta_i(\xx)))$. This gives a hydrophobic particle with greater
+intensity of hydrophobicity at $\theta_i = 0$ than at $\theta_i = \pi$.
+The initial self-assembly is similar to that of the amphiphilic particle
+case, except that the bilayers do not stay well separated. Rather, the
+bilayers stack on top of each other as a consequence of the interfacial
+tension of exposed particle heads \cite{deMeetal21}.
 
@@
 rich morphologies that are valuable in the synthesizing multiphasic and
-anisotropic colloids \cite{Bradley2016,Mallory2017,Bradley2017}.
-The main experimental challenges include the ability to
-decouple particle surface properties.
-The goal is to obtain numerically aided 
-syntheses and assembly of soft matter materials.
-Applications in this area include cargo-carrying capacity, 
-catalytic activity, or stimuli-responsive shape-change to amplify colloid
-utility for a wide range of  spanning environmental remediation to drug
-delivery \cite{McBr21, HaBr20}.
+anisotropic colloids~\cite{Bradley2016,Mallory2017,Bradley2017}. The
+main experimental challenges include the ability to decouple particle
+surface properties. The goal is to obtain numerically aided syntheses
+and assembly of soft matter materials. Applications in this area include
+cargo-carrying capacity, catalytic activity, or stimuli-responsive
+shape-change to amplify colloid utility for a wide range of spanning
+environmental remediation to drug delivery~\cite{McBr21, HaBr20}.
 
@@
 The main modeling challenge is to translate the phenomenological
-parameters, e.g. boundary conditions, into measurable quantities
-such as contact angles. Collaboration with experimental groups will
-use numerical methods to predict parameter regimes 
-to control particle-particle interactions. In Specific Aim 3, we
+parameters, e.g.~boundary conditions, into measurable quantities such as
+contact angles. Collaboration with experimental groups will use
+numerical methods to predict parameter regimes to control
+particle-particle interactions. In \S~\ref{subsec:specific_aim_3}, we
 discuss how to include ions and surface charge.
@@
 bu$. Motivated by capillary wetting, soft matter physicist Gerhard
-Gompper introduced a double-well model for one-dimensional hydrophobic
-attraction \cite{GoHaKo94}. The two-dimensional attraction we propose is
-more complicated and includes extra line tension effects not present in
-the one-dimensional theories.
+Gompper introduced a double-well model for one-dimensional
+hydrophobic attraction \cite{GoHaKo94}. The two-dimensional attraction
+we propose is more complicated and includes extra line tension effects
+not present in the one-dimensional theories.
 
@@
 per water molecule. The value $u_0 = 4$ gives a local minimum for the
-ideal tetrahadral water network found at hydrophobic surfaces. The value
+ideal tetrahedral water network found at hydrophobic surfaces. The value
 $u_1 \sim 4.4$ gives the absolute minimum in the bulk where there is a
@@
 equation. The Allen-Cahn equation is used in phase field formulations of
-immisible fluids, for example. PI RR and colaborators launched the
+immiscible fluids, for example. PI RR and collaborators launched the
 simulation and asymptotic analysis of phase field functionals of
@@
 curvature (Willmore) energy~\cite{0951-7715-18-3-016}, spontaneous
-curvature~\cite{Du05} and Gaussian curvature energy~\cite{DuEuler}, as
+curvature~\cite{Du05}, and Gaussian curvature energy~\cite{DuEuler}, as
 well as energetic variational approaches to coupling membrane elasticity
@@
 One potential application of the Allen-Cahn-type formulation is to
-explaning measured hydrophobic attraction profiles.
-The experimental data on hydrophobic attraction between 
-is well-established and the literature contains data for a number of
-solvents and hydrocarbon species. The experimental measurements
-are well-fit by a double exponential curve in the 10 to 100 nanometer range
-of separation. Below 10~nm, however, there is an amplification of force
-and the attraction follows a much steeper force law not accounted
-for by past phenomenoloical theories~\cite{Lin2005}.
+explain measured hydrophobic attraction profiles. The experimental data
+on hydrophobic attraction between \todo{between what?} is
+well-established and the literature contains data for a number of
+solvents and hydrocarbon species. The experimental measurements are
+well-fit by a double exponential curve in the 10--100~nm range of
+separation. Below 10~nm, however, there is an amplification of force and
+the attraction follows a much steeper force law not accounted for by
+past phenomenological theories~\cite{Lin2005}.
 
@@
 simulations can replicate the experimental setup better than prior,
-one-dimensional theoretical work Some of the model parameters directly
+one-dimensional theoretical work. Some of the model parameters directly
 connect to long-range decay lengths and energy cost of creating
@@
 motion is much larger than the hydrogen-bond lifetimes. One approach is
-to consider Gaussian fluctuation. Here, we expand the free energy
-functional around the saddle point solution. The fluctuation energy
-then involves calculation of the eigenfunctions of the second variation
-of the free energy. This accounts for the fact that experimental
+to consider Gaussian fluctuations. Here, we expand the free energy
+functional around the saddle point solution. The fluctuation energy then
+involves calculation of the eigenfunctions of the second variation of
+the free energy. This accounts for the fact that experimental
 measurements are carried out at finite temperatures, where thermal

### 2021-11-13 NSF2021/Description/specificaim1.tex
finished up first pass through SA3

@@
 numerical methods to predict parameter regimes to control
-particle-particle interactions. In \S~\ref{subsec:specific_aim_3}, we
+particle-particle interactions. In \S\ref{subsec:specific_aim_3}, we
 discuss how to include ions and surface charge.
@@
 equation. The Allen-Cahn equation is used in phase field formulations of
-immiscible fluids, for example. PI RR and collaborators launched the
+immiscible fluids, for example. PI Ryham and collaborators launched the
 simulation and asymptotic analysis of phase field functionals of
@@
 under shape changes.  To evaluate $\KG$, we will combine the present
-particle simulations with the string method from PI RR's work on
+particle simulations with the string method from PI Ryham's work on
 membrane fusion \cite{RyKlYaCo16}. The string method is a numerical
@@
 transitions, thanks to the  Gauss-Bonnet theorem \cite{TerziDeserno17}.
-More generally, PI RR has shown that saddle splay acts as a topological
-indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}.  As a
-result, saddle splay can be quantified from the transition energies of a
-least energy path of pore formation (Figure~\ref{fig:saddle_splay}).
+More generally, PI Ryham has shown that saddle splay acts as a
+topological indicator even in the presence of nonzero tilt
+\cite{RyKlYaCo16}.  As a result, saddle splay can be quantified from the
+transition energies of a least energy path of pore formation
+(Figure~\ref{fig:saddle_splay}).
 

### 2021-11-13 NSF2021/Description/specificaim3.tex
finished up first pass through SA3

--- 2021-11-06 NSF2021/Description/specificaim3.tex
@@
 
-\subsubsection{Dynamics of a single Janus particle in ionic solutions}
-In experiments, Janus particles are often immersed in a solution of ions \cite{ChenWhitmer2011_Sci} or surfactants \cite{}.
-In electrolytic solutions the interaction between salt and Janus particle gives 
-rise to a slip velocity (on the particle surface) that depends on the ion distribution and the zeta potential \cite{BayatiJCP2016} 
-(the potential difference between the Janus particle surface and the surrounding conducting fluid).
-The short-range interactions between Janus particles depend on the salt concentration:
-At very low salt concentrations, Janus particles repel one another electrostatically, whereas at high salt concentration, van der Waals
-forces cause Janus particles to aggregate irreversibly \cite{Goodwin2019}.
-At intermediate concentrations of monovalent salt, Janus particles are found to self assemble in the form of a small number of elemental units of building blocks \cite{Chen2011_Science}.
-%
-\begin{wrapfigure}[6]{l}{0.47\textwidth}
-\centerline{\includegraphics[width=0.46\textwidth]{Figures/fig2A_Chen2011_Science}}
+\subsubsection{Dynamics of a pair of Janus particles in ionic
+solutions\label{subsubsec:JP_electrolyte}}
+\begin{wrapfigure}[7]{r}{0.45\textwidth}
   \vspace{-5pt}
-\caption{\label{fig:helices_of_JPs} \footnotesize Formation of helices of Janus particles as salt concentration increases \cite{Chen2011_Science}.}
+\centerline{\includegraphics[width=0.44\textwidth]{Figures/fig2A_Chen2011_Science}}
+  \vspace{-5pt}
+\caption{\label{fig:helices_of_JPs}Formation of helices
+  of Janus particles as salt concentration increases from 3.8 mM NaCl
+  (left) to 5 mM NaCl (right)~\cite{Chen2011_Science}.}
 \end{wrapfigure}
-%
-Figure~\ref{fig:helices_of_JPs} shows that Janus particles can self-assemble into a helix at high concentration of monovalent salt (NaCl) when the density of Janus particles is low to moderate.
-At high density, JPs are found to form wormlike structures
+In experiments, Janus particles are often immersed in a solution of
+ions~\cite{Chen2011_Science} or surfactants~\cite{Goodwin2009}. In
+electrolytic solutions, the interaction between salt and Janus particle
+gives rise to a slip velocity (on the particle surface) that depends on
+the ion distribution and the zeta potential~\cite{BayatiNajafi2016_JCP}
+(the potential difference between the Janus particle surface and the
+surrounding conducting fluid). The short-range interactions between
+Janus particles depend on the salt concentration: At very low salt
+concentrations, Janus particles repel one another electrostatically,
+whereas at high salt concentration, van der Waals forces cause Janus
+particles to aggregate irreversibly~\cite{Goodwin2009}. At intermediate
+concentrations of monovalent salt (NaCl), Janus particles are found to
+assemble in the form of a small number of elemental units of building
+blocks~\cite{Chen2011_Science}. Figure~\ref{fig:helices_of_JPs} shows
+that Janus particles can assemble into a helix at high concentration of
+monovalent salt when the volume fraction of Janus particles is low to
+moderate. At high volume fraction, helices of Janus particles form
+wormlike structures whose lifetime allow fusion of
+helices~\cite{Chen2011_Science}.
 
-The Stokes equations in~\eqref{eq:stokes} are modified to incorporate the transport of ions as
+We propose to investigate the effects of ion transport and distribution
+on the self-assembly of Janus particles within the HAP framework as
+follows. First the Stokes equations are modified to incorporate the
+transport of ions as
 \begin{equation}
-\label{eq:stokes}
+\label{eq:EKstokes}
 \begin{aligned}
@@
   &\delta^2\Delta\psi = -\frac{1}{2}\left(n_+-n_-\right),\qquad
-  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\\
-  &{\bf j}_{\pm} = -\nabla n_{\pm} \mp n_{\pm} \nabla\psi + \mbox{Pe} n_{\pm}\mathbf{u},
+  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\qquad {\bf j}_{\pm} = -\nabla n_{\pm} \mp n_{\pm} \nabla\psi + \mbox{Pe} n_{\pm}\mathbf{u},
 \end{aligned}
 \end{equation}
-where $\delta$ is the Debye length, $\mbox{Pe}$ is the Peclet number, a ratio between the convection and  thermal diffusion time scales.
-$n_{+}$ ($n_{-}$) is the concentration of cation (anion).
-The screen length $\rho$ in the HAP model is now a function of the ion concentrations: $\rho = \rho(n_+,n_-)$.
+where $\psi$ is the electric potential, $\delta$ is the ratio of Debye
+screening length (inversely proportional to the square root of ion
+concentration) to the particle size, $\mbox{Pe}$ is the Peclet number, a
+ratio between the convection and thermal diffusion time scales, and
+$n_{+}$ ($n_{-}$) is the concentration of cation (anion). In the limit
+of small $\delta$, PI Young and collaborator Y.~Mori (U Penn) used
+asymptotic analyses to show that the jump in electric potential across
+the interface (zeta potential on the Janus particle surface) may give
+rise to different physical consequences such as
+electrophoresis~\cite{Mori2018_JFM}.
+%
+An important question to address is: {\it How would such electrophoresis
+be affected by the HAP between two Janus particles?} As the first part
+of Specific Aim 3, we will address this important question. Results from
+this effort will help elucidate the effects of salt concentration on the
+assembly of Janus particles (\S\ref{subsubsec:em_effects}).
 
-Within this framework, we will first investigate the interaction between two Janus particles under HAP in an electrolytic solution described by the above
-equations.
-We will conduct analytical calculations to investigate the effects of ion transport on the hydrophobic attraction between two Janus particles using the reciprocal theorem as in \cite{BayatiNajafi2016} for two Janus particles with a small surface activity.
+We will couple the electrokinetics in~\eqref{eq:EKstokes} with the
+mobility problem of Janus particles in a viscous solvent through the
+velocity field, ion distribution, and the hydrophobic potential. First
+the screen length $\rho$ in the HAP model is now a function of ion
+concentrations: $\rho = \rho(n_+,n_-)$. 
+%
+Second the value of the HAP may depend on the distribution of ions and
+electric potential right next to the particle
+surface~\cite{Mori2018_JFM}. Within this framework, we will first
+investigate the interaction between two Janus particles under HAP in an
+electrolytic solution described by the above equations. We will conduct
+analytical calculations to investigate the effects of ion transport on
+the hydrophobic attraction between two Janus particles using the
+reciprocal theorem as in~\cite{BayatiNajafi2016_JCP} for two Janus
+particles with a small surface activity.
 
-\subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
-In recent experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending
-rigidity was determined as a function of lipid composition from 0 to 100
-mol $\%$ of charged lipids using flicker spectroscopy of the shape
-fluctuations of a giant unilamellar vesicle (GUV).
-%the bending rigidity is determined as a
-%function of lipid composition from 0 to 100 mol $\%$ of charged lipids
-%in recent experiments~\cite{FaizEtAl2019_SoftMatt}---
-Membrane bending rigidity increases with increasing lipid surface
-charge, but decreases with increasing salt concentration in the bulk
-solution due to the screening of the lipid surface charge. This
-result agrees
-with several theoretical models~\cite{Kralchevsky1996_JCIS,
-May1996_JChemPhys, LoubetEtAl2013_PRE} that also assume the quadratic
-form of the elastic energy density in the presence of surface charge and
-bulk charge~\cite{DuplantierGoldstein1990_PRL, Winterhalter1992_JPC}. As
-the electrostatic interaction is non-local in nature, we expect that the
+\subsubsection{Electromechanical effects on the dynamic assembly of Janus particles \label{subsubsec:em_effects}}
+Results from the proposed work in \S\ref{subsubsec:JP_electrolyte} will
+shed light on how the electrokinetics described in~\eqref{eq:EKstokes}
+may be simplified to a dielectric-like model where the bulk charges are
+constant, and the fluid flow and particle mobility are determined by the
+surface charge and the zeta potential as shown in~\cite{Mori2018_JFM}.
+Under such simplification, equation~\eqref{eq:EKstokes} may be
+re-formulated into integral forms. PIs Ryham and Young will conduct the
+asymptotic analyses to derive this form, and work with PI Quaife to
+design numerical algorithms to simulate the modified system. We will
+first investigate the effects of salt concentration on the assembly of
+Janus particles to form helices, as shown in
+Figure~\ref{fig:helices_of_JPs}.
+
+With these results, the PIs will be ready to make quantitative
+connections between the a Janus particle membrane and a lipid bilayer
+membrane in an electrolytic solution. In recent
+experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending rigidity was
+determined as a function of lipid composition from 0 to 100 mol $\%$ of
+charged lipids using flicker spectroscopy of the shape fluctuations of a
+giant unilamellar vesicle (GUV). Membrane bending rigidity increases
+with increasing lipid surface charge, but decreases with increasing salt
+concentration in the bulk solution due to the screening of the lipid
+surface charge. This result agrees with several theoretical
+models~\cite{Kralchevsky1996_JCIS, May1996_JChemPhys,
+LoubetEtAl2013_PRE} that also assume the quadratic form of the elastic
+energy density in the presence of surface charge and bulk
+charge~\cite{DuplantierGoldstein1990_PRL, Winterhalter1992_JPC}. As the
+electrostatic interaction is non-local in nature, we expect that the
 controversy of the HK elastic energy form (see
@@
 explicit surface charge on each particle boundary $P_i$ and compute the
-electrostatic potential as a functional of particle configuration.
-Adding the electrostatic force to the hydrophobic attraction force
+electrostatic potential as a functional of particle configuration.  By
+adding the electrostatic force to the hydrophobic attraction force
 between particles, we will assess the dependence of elastic moduli on
@@
 propose to examine how to use an external electric field to control the
-amphiphilic self-assembly in solvent. PI YNY has a track record of
+amphiphilic self-assembly in solvent. PI Young has a track record of
 working on electrohydrodynamics of an elastic, inextensible membrane
@@
 Young2015_PoF} and numerical simulations~\cite{Nganguia2015_CiCP} and
-will work with both PIs RR and BQ to extend the HAP model to study the
-electromechanical effects on the assembly of amphiphile. Results from
-this research will yield a quantitative understanding of how to utilize
-an electric field to achieve optimal control of assembly of amphiphiles
-in solvent.
+will work with both PIs Ryham and Quaife to extend the HAP model to
+study the electromechanical effects on the assembly of amphiphile.
+Results from this research will yield a quantitative understanding of
+how to utilize an electric field to achieve optimal control of assembly
+of amphiphiles in solvent.

### 2021-11-13 NSF2021/Description/specificaim3.tex
yny

@@
 
-\subsubsection{Dynamics of a pair of Janus particles in ionic
-solutions\label{subsubsec:JP_electrolyte}}
 \begin{wrapfigure}[7]{r}{0.45\textwidth}
@@
 
+\subsubsection{Dynamics of a pair of Janus particles in ionic
+solutions\label{subsubsec:JP_electrolyte}}
 We propose to investigate the effects of ion transport and distribution
@@
 velocity field, ion distribution, and the hydrophobic potential. First
-the screen length $\rho$ in the HAP model is now a function of ion
-concentrations: $\rho = \rho(n_+,n_-)$. 
+the screen length $\rho$ and the potential $f(u)$ in the HAP model are now 
+dependent on  the ion concentrations. 
 %
@@
 With these results, the PIs will be ready to make quantitative
-connections between the a Janus particle membrane and a lipid bilayer
+connections between a Janus particle membrane and a lipid bilayer
 membrane in an electrolytic solution. In recent

### 2021-11-13 NSF2021/Description/specificaim2.tex

@@
 multipole method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2,
-fmm3, fmm4, fmm6, fmm7, fmm8}. PI BQ is experienced with applying FMMs
-for the Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the
+fmm3, fmm4, fmm6, fmm7, fmm8}. PI Quaife is experienced with applying
+FMMs for the Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the
 screened Laplace equation~\cite{kro-qua2011, qua2011}. Furthermore, to
@@
 as the inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017} and
-domain decomposition~\cite{che-bir2021}. PI BQ used the IFMM to
+domain decomposition~\cite{che-bir2021}. PI Quaife used the IFMM to
 precondition Stokes equations~\cite{qua-cou-dar2018}. A suite of other
@@
 computational challenge by developing novel high-order adaptive time
-stepping methods. PI BQ developed a high-order adaptive time stepping
-method for hydrodynamic suspensions \cite{qua-bir2016}, and it has
-served as a robust method to simulate processes including mixing and
+stepping methods. PI Quaife developed a high-order adaptive time
+stepping method for hydrodynamic suspensions \cite{qua-bir2016}, and it
+has served as a robust method to simulate processes including mixing and
 adhesion in suspensions~\cite{qua-vee-you2019, kab-qua-bir2017}.
@@
 force and torque of the system which is computationally cheap and
-physically zero. PI BQ's experience is that error estimates based on
+physically zero. PI Quaife's experience is that error estimates based on
 physical constraints such as force- and torque-free conditions
@@
 extrapolation.
-
-%%
-%\begin{wrapfigure}[13]{r}{0.30\textwidth}
-%\centerline{\includegraphics[width=0.29\textwidth]{figures/BIError.pdf}}
-%  \vspace{-8pt}
-%\caption{
-%\label{fig:bierror}  
-%\footnotesize The false color map shows how numerical quadrature of
-%  layer potentials loses accuracy near the particle boundaries.  The
-%  color bar is for $\log_{10}.$}
-%\end{wrapfigure}
-%%
-%Our previous work avoided particle contact through Lennard-Jones body
-%forces~\cite{Fu2018_SIAM}. Such steep, short-range, steric interactions 
-%introduce numerical stiffness and limit the time step size. To
-%remove this stiffness, we propose a geometry-based contact
-%method~\cite{har-pon-sor-zor2011}. This method has been applied to
-%vesicle suspensions~\cite{lu-rah-zor2017} and to rigid body suspensions in
-%two dimensions~\cite{bys-sha-qua2020} and three
-%dimensions~\cite{Yan2019}. These methods determine repulsion force by
-%solving a non-linear complementarity problem with a geometric constraint
-%that the configuration is non-overlapping. In this manner, contact is
-%avoided without the excessively small time steps required by stiff
-%Lennard-Jones forces.
-%
-%%-------------------------------------------------------------------------------
-%\subsubsection{Novel reciprocal identities}
-%\label{subsec:reciprocal}
-%The force and torque formulas~\eqref{forceandtorque} use the
-%hydrophobic stress along the particle boundaries. Unfortunately,
-%layer potentials for $\nabla u$ involve hyper-singular integrals and
-%this introduces large amounts of quadrature error on the particle
-%boundaries (Figure~\ref{fig:bierror}). Therefore, it is useful to devise
-%reciprocal identities for the force and torque on body $i$ that do not
-%require integration along body $i$. One identity, that we have proved,
-%is
-%\begin{align}
-%    \label{eq:reciprocal}
-%{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
-%{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf
-%  x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} +
-%  \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, 
-%\end{align}
-%for $i=1,\ldots,N$. Here, $u_i$ is the solution of the screened Laplace
-%equation when only the contribution from particle $i$ is considered and
-%$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j \mathbf{I} +
-%\rho\left((\nabla u_i \cdot \nabla u_j) \mathbf{I} - 2 \nabla u_i
-%\otimes \nabla u_j\right)$. Equation~\eqref{eq:reciprocal} does not
-%require knowledge of $\nabla u$ on particle boundary $i$, and this is
-%enormously beneficial for calculating the hydrophobic force and torque.
-%
-%% ----------------------------------------------------------------------
-%\subsubsection{Fluctuating hydrodynamics}
-%\label{subsec:fluctuating}
-%Once algorithms that address quadrature, adaptive time stepping, and
-%contact are implemented, we will embark on incorporating fluctuating
-%hydrodynamics that are especially important at scales of amphiphilic
-%particles. Bao et al.~\cite{Bao17,Bao18} developed two-dimensional BIE
-%formulations for Brownian rigid bodies. To satisfy the covariance of the
-%rigid body velocities, they use an ill-conditioned, first-kind integral
-%equation method. The proposed work will consider a layer potential
-%formulation that has much better conditioning properties. This strategy
-%was attempted in~\cite{Bao18}, but they claim that a necessary
-%regularization of the covariance matrix leads to a drastic loss of
-%accuracy in numerical fluctuation-dissipation balance. However, only one
-%regularization strategy was considered, and as PI BQ has shown in
-%previous work, the regularization choice significantly affects the
-%resulting physics~\cite{ong-chr-qua2017}. Therefore, different
-%regularization strategies will be investigated with the goal of finding
-%well-conditioned BIE formulations that control the accuracy of the
-%fluctuation-dissipation balance.

### 2021-11-13 NSF2021/Description/specificaim3.tex

@@
 electrostatic interactions and electrokinetics. The PIs will extend the
-approaches in \S\ref{subsec:specific_aim_1} to charged lipids to
+approaches in \cite{Fu2018_SIAM} to charged lipids to
 calculate the bending moduli and compare against the experimental
 results in~\cite{FaizEtAl2019_SoftMatt}. We propose to incorporate an
-explicit surface charge on each particle boundary $P_i$ and compute the
+explicit surface charge on each particle boundary $\Gamma_i$ and compute the
 electrostatic potential as a functional of particle configuration.  By
@@
 between particles, we will assess the dependence of elastic moduli on
-electric charges using the methods described in
-\S\ref{subsec:specific_aim_1}. Results from these proposed calculations
+electric charges using the methods described in \cite{Fu2018_SIAM}. Results from these proposed calculations
 will provide further comparisons and validations of the HAP model
@@
 will work with both PIs Ryham and Quaife to extend the HAP model to
-study the electromechanical effects on the assembly of amphiphile.
+study the electromechanical effects on the assembly of colloidal amphiphiles.
 Results from this research will yield a quantitative understanding of

### 2021-11-13 NSF2021/Description/specificaim1.tex
fingers crossed

--- 2021-11-12 NSF2021/Description/specificaim1.tex
@@
 \label{subsec:specific_aim_1}
-
-The proposed research aims to provide fundamental insight into the
+Specific Aim 1 proposes a novel mathematical model for particle
+self-organization driven by long-range interfacial forces. 
+The research aims to provide fundamental insight into the
 self-assembly dynamics of amphiphilic particles. These results will
 facilitate optimal design of smart materials by tuning the geometry and
-properties of the amphiphilic particles.  Specific Aim 1 achieves this
-through a novel mathematical model for particle self-organization driven
-by long-range interfacial forces.
+properties of the amphiphilic particles.
 
@@
 %\begin{wrapfigure}[h!]
-\begin{wrapfigure}[10]{r}{0.55\textwidth}
+\begin{wrapfigure}[11]{r}{0.55\textwidth}
  \centering
-  \vspace{-12pt}
+ \vspace{-3pt}
  \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.pdf}
-  \caption{\label{fig:flow_map} A collection of amphiphilic particles
-  suspended in a solvent. The solvent velocity satisfies the Stokes
-  equations, and the hydrophobic forces depend on the solvent activity
-  that satisfies the screened Laplace equation. The geometry is updated
-  by solving the mobility problem.}
+ \caption{\label{fig:flow_map}
+   In the HAP formulation, hydronamic interactions
+   come from the Stokes equations and
+   hydrophobic interactions come from the structure order parameter $u$.}
 \end{wrapfigure}
@@
 The mathematical formulation is a nonlinear system for the dynamics of a
-collection of particles. The interactions come from a system of linear
-partial differential equations (PDEs) and comprise hydrodynamic
+collection of particles. The interactions come from a system of 
+partial differential equations (PDEs) that comprise hydrodynamic
 interactions and hydrophobic interactions.
@@
 $\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
-viscosity. The domain $\Omega$ is the fluid region surrounding the
-particles. Since the particles are rigid, the solvent velocity satisfies
+viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
+particles and changes shape as the particles move.
+Since the particles are rigid, the solvent velocity satisfies
 a no-slip boundary condition for a rigid body motion 
@@
 on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
-and angular velocity $\omega_i$. Given imposed forces acting on each
+and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
+Given imposed forces acting on each
 particle, the \emph{mobility problem} consists of finding
@@
 minimize the free energy of the structure of the surrounding water
-molecules. Experimental measurements suggest that the free energy
-functional take the form 
+molecules. The free energy functional take the form 
 \begin{align*}
@@
 Hydrogen-bond persistence times are on the order of picoseconds
-\cite{MaGa13}. Since waters reorient on a time scale much smaller than
-the particle motion, $u$ minimizes $F[u]$ at all time, and therefore
-satisfies 
+which is much smaller than characteristic time for 
+particle motion \cite{MaGa13}.
+Thus we assume $u$ minimizes $F[u]$ for all times.
+Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
+$u$ is bounded and satisfies the Euler-Lagrange equation
 \begin{equation}
 \label{eq:SL}
--\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g,
+-\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
 \text{ on } \bd\Omega.
@@
 The boundary condition $g$ is a material label that is transported with
-the particle motions (Figure~\ref{fig:bcs}).
+the particle (Figure~\ref{fig:bcs}).
 
-\begin{wrapfigure}[10]{r}{0.65\textwidth}
-  \vspace{-22pt}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
-\caption{\label{fig:bcs} Boundary conditions characterize the type of
-  water structure: an amphiphilic particle (left), a hydrophobic
-  particle with anisotropic intensity (middle), a water structure with
-  plus/minus polarity (right). The dashed curve is the boundary of the
-  disk and the arrow its director.}
-\end{wrapfigure}
-The coupling between the Stokes equations \eqref{eq:stokes} and the
-semilinear elliptic equation \eqref{eq:SL} comes from the first
-variation of the energy functional. The particles minimize the free
-energy $F[u]$ by altering the location of hydrophobic interfaces. It is
-possible to calculate the rate of change of $F[u]$ using variation of
-the domain~\cite{Bandle2015, Schiffer1954, Grinfeld2010}. Carrying out
+The particles lower the free energy $F[u]$ of the surrounding water
+by moving. We calculate the rate of change of $F[u]$ using
+\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
+Carrying out
 this variation yields a 
@@
 %\end{equation}
-surface force density 
+stress  
 \begin{align}
@@
 \end{align}
-The imposed forces and torques from the integration of $\mathbf{T}$
-along the particle boundary. The density~\eqref{eq:stress} was first
-introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional analogue
-of disjoining pressure calculated by \cite{MaRa76, ErLjCl89, KoNa15,
+The imposed forces and torques come from the integration of $\mathbf{T}$
+along the particle boundary.
+These forces and torques couple the Stokes equations \eqref{eq:stokes},
+to semilinear elliptic equation \eqref{eq:SL}.
+Solving for the translational and rotational velocities gives the
+particle evolution.
+
+The density~\eqref{eq:stress} was first
+introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
+generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
 Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
@@
 boundary value problem must be solved at each time step. The particle
-boundaries are nearly touching and this requires high-order numerical
-schemes to accurately calculate forces and adaptively chose an
-appropriate time step size. Furthermore, there are issues with
-accurately capturing the far-field boundary conditions in the unbounded
-domain. Finally, the numerical routine must handle large system sizes
-efficiently when their are many particles is large.
+boundaries are nearly touching and high-order numerical
+schemes and adaptively chosen time step sizes
+are required to calculate trajectories accurately.
+Furthermore, the domain is unbounded and care must be taken 
+in capturing the far-field boundary conditions correctly. 
+Finally, the numerical routine must handle large system sizes
+efficiently when the number of particles is large.
 
@@
 \subsubsection{Janus-particle self-assembly} 
-When $f(u) = u^2$, and the water structure has its lowest potential
-value at $u=0$ which represents bulk water. The solutions of
-\eqref{eq:SL} have a boundary layer structure and decay to $0$ in the
-bulk with the decay length $\rho$. Even in this linear response case, a
-number of morphologies arise by altering boundary conditions.
+Distinct morphologies can be obtained from 
+the HAP model by shifting the boundary condition $g$.
+Consider the linear case where $f(u) = u^2$.
+This choice makes \eqref{eq:SL} a boundary value
+problem for the screened-Laplace equation
+and the solutions have a boundary layer structure that decays to $0$ in the
+bulk with the decay length $\rho$.
+We consider three kinds of boundary conditions
+on particle $\Gamma_i$:
+\begin{equation}
+  \label{eq:bcs}
+  \begin{tabular}{c|c|c}
+     \text{(a)} & \text{(b)} & \text{(c)} \\
+    \hline
+    \rule{0pt}{4ex} 
+      $g(\mathbf{x}) = \displaystyle \frac{1+\cos (\theta_i(\xx))}{\sqrt{3\pi r}}$
+    & $g(\mathbf{x}) = \displaystyle \frac{2+\cos (\theta_i(\xx))}{\sqrt{9\pi r}}$
+    & $g(\mathbf{x}) = \displaystyle \frac{\cos (\theta_i(\xx))}{\sqrt{\pi r}}$
+\end{tabular}
+\end{equation}
+  The number $\theta_i(\xx)$ is the angle formed by the position $\xx$, the
+particle center $\aa_i$, and the particle director $\dd_i$ (Figure \ref{fig:flow_map}).
+The normalizations, e.g. $(\pi r)^{-1/2}$, provide a uniform
+surface energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles
+of radius $r$. 
+The cases (b) and (c) are obtained by applying a vertical shift
+and scaling to case (a), which amounts to changing one line of code. 
+Using this setup, we simulate the dynamics of 100 particles with random
+initial position and orientation.
+
+Case (a) models amphiphilic particles.
+Amphiphilic particles have a hydrophobic tail and a hydrophilic head
+and these are accounted for as follows.
+The hydrophilic side takes the value $u =0$.
+This mimicks the apolar head of a lipid, for example, which does
+not alter the structure of adjacent waters. The hydrophobic side
+represents hydrocarbons and takes the value 
+$u > 0$. The interaction between particles is attractive,
+and particles will collectively orient their tails toward
+one another. 
+PIs RR and YNY's previous work showed that this   
+boundary condition produces two-dimensional micelles and
+bilayers~\cite{Fu2018_SIAM}, as illustrated in 
+Figure~\ref{fig:self-assembly}(a).
+
+\begin{wrapfigure}[11]{r}{0.65\textwidth}
+  \vspace{-10pt}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
+  \caption{\label{fig:bcs} Boundary conditions characterize the water
+    structure at the particle interface: an amphiphilic particle (left),
+    a hydrophobic
+  particle with anisotropic intensity (middle), a water structure with
+  plus/minus polarity (right). The dashed curve is the boundary of the
+  disk and the arrow is its director.}
+\end{wrapfigure}
+
+Multilamelar bilayers arise when both sides of the particle
+are hydrophobic (Figure~\ref{fig:self-assembly}(b)).
+The boundary condition \eqref{eq:bcs}(b) 
+gives a particle with a hydrophobic intensity three times as great
+on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
+The initial self-assembly is similar to that in case (a).
+The difference arises in the long-time dynamics where the bilayers
+no longer remain well-separated. 
+Rather, the bilayers form layers 
+as a consequence of the interfacial tension of exposed particle
+heads~\cite{Huetal19, deMeetal21}.
 
@@
   \begin{center}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A1.pdf}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A2.pdf}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100A3.pdf}
+    \begin{tabular}{m{0.1cm}m{1.9in}m{1.9in}m{1.9in}}            
+      (a)
+    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B1.pdf}
+    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B2.pdf}
+     &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B3.pdf}    \\
+     (b)
+    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C1.pdf}
+    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C2.pdf}
+      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C3.pdf}    \\
+    (c)
+      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A1.pdf}
+      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A2.pdf}
+      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A3.pdf}    \\
+      &\multicolumn{1}{c}{$t = 0$}
+      &\multicolumn{1}{c}{intermediate time}
+      &\multicolumn{1}{c}{$t = t_{\text{final}}$}
+  \end{tabular}
     \end{center}
-  \caption{\label{fig:self-assemblyA} Self-assembly with a polar
-  boundary condition leads to a checkerboard pattern. Green is for $u <
-  0$, yellow is for $u > 0$, and blue is for $u = 0$.}
+  \caption{\label{fig:self-assembly}
+    Using the same initial configuration,
+    particles self-assemble into distinct morphologies based
+    on the boundart condition $g.$ 
+    boundary condition leads to a checkerboard pattern.
+    In row (a), self-assembly with an amphiphilic boundary
+    condition \eqref{eq:bcs}(a) results a bilayer pattern shielding
+    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
+    Row (b) shows particles with a hydrophobic intensity that is
+    greater on one side of the particle (magenta) than the other (yellow).
+    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
+    Particles orient like sides to form a checkerboard pattern.
+  }
 \end{figure}
 
-Consider a polar boundary condition where $g_i(\xx) = (\pi r)^{-1/2}
-\cos (\theta_i(\xx))$ where $\theta_i$ is the angle formed by $\xx$, the
-particle center $\aa_i$, and the particle director $\dd_i$. The
-normalization $(\pi r)^{-1/2}$ and others below provide a uniform
-surface energy $\int_{\Gamma_i} g_i^2 \,ds = 1$ for circular particles
-of radius $r$. The boundary condition is odd along the particle axis
-making the particle head repel the tail.  We simulate the dynamics of
-100 particles with random initial position and orientation. The
-particles rapidly form chains with their directors perpendicular to the
+\todo[inline]{Rationalize and citations for following} 
+Finally, boundary condition \eqref{eq:bcs}(c) models 
+a particle with oppositelly charged ends making the 
+particle heads repel the tails \cite{MaRa76, Ma77}.
+The particles initially form chains with their directors perpendicular to the
 length of the chain. The equilibrium structure consists of particles
 positioned on a square grid in a checkerboard pattern
-(Figure~\ref{fig:self-assemblyA}. This patterning is a consequence of
+Figure~\ref{fig:self-assembly}(c). This patterning is a consequence of
 energy minimality and allows each particle to simultaneously coordinate
@@
 
-\begin{figure}[h!]
-\begin{center}  
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B1.pdf}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B2.pdf}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100B3.pdf}
-\end{center}    
-  \caption{\label{fig:self-assemblyB} Self-assembly with with boundary
-  condition that results in hydrophobic tails and hydrophilic heads. The
-  resulting bilayer pattern shields the hydrophobic core (yellow) from
-  the aqueous phase.}
-\end{figure}
-Amphiphilic particles have a hydrophobic tail and a hydrophilic head and
-are accounted for as follows. The hydrophilic side takes the value $u =
-0$ since the apolar head of a lipid, for example, does not alter
-the structure of adjacent waters. The hydrophobic side takes the value
-$u > 0$. The interaction between particles is attractive. Using $(3\pi
-)^{-1/2}(1 + \cos(\theta_i(\xx)))$ as a simple modification to
-the previous boundary condition produces two-dimensional micelles and
-bilayers \cite{Fu2018_SIAM} (Figure~\ref{fig:self-assemblyB}).
-Researchers have asked us if the phenomenon is robust. To show that it
-is, we instead use the boundary condition
-\begin{equation}
-\label{eq:vonMises}
-  g_i(\xx) = \sqrt{
-  \frac{\exp( \kappa_i(\theta_i(\xx) - \theta^0_i))}
-  {2\pi r_i I_0(\kappa_i)}}
-\end{equation}
-where the radicand \todo{radicand?} is the von Mises distribution with
-director angle $\theta^0_i$ and Bessel function $I_0$ of order zero. The
-square of this function behaves as a normal distribution with variance
-like $1/\kappa_i$.To replicate experimental conditions, the
-concentration $\kappa_i$ and radii $r_i$ are randomized. Using the same
-initial configuration, the particles form small groups that
-combine to form bilayers (Figure~\ref{fig:self-assemblyC}.
-
-\begin{figure}[h!]
-  \begin{center}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C1.pdf}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C2.pdf}
-    \includegraphics[width=0.32\textwidth]{figures/SpecificAim1/N100C3.pdf}\\
-    \caption{Hydrophobic particles with a bias. The hydrophobic
-    intensity is greater on one side of the particle (magenta) than the
-    other (yellow).
-    \label{fig:self-assemblyC}}
-\end{center}
-\end{figure}
-
-Multilamelar bilayers arise with an increase by shifting the boundary condition
-further. Let $g_i(\xx) = (9\pi )^{-1/2}(2 + \cos(\theta_i(\xx)))$.
-This gives a hydrophobic particle with greater intensity of hydrophobicity
-at $\theta_i = 0$ than at $\theta_i = \pi$.  The initial self-assembly
-is similar to that of the amphiphilic particle case, except that the bilayers
-do not stay well separated.  Rather, the bilayers stack on top of each
-other as a consequence of the interfacial tension of exposed particle heads \cite{deMeetal21}.
-
-In summary, the hydrophibic interaction-mobility problem model yields
-rich morphologies that are valuable in the synthesizing multiphasic and
-anisotropic colloids \cite{Bradley2016,Mallory2017,Bradley2017}.
-The main experimental challenges include the ability to
-decouple particle surface properties.
-The goal is to obtain numerically aided 
-syntheses and assembly of soft matter materials.
+The ultimate goal is to use numerical simulations to aid
+the syntheses soft matter materials.
 Applications in this area include cargo-carrying capacity, 
@@
 delivery \cite{McBr21, HaBr20}.
+Here, mathematical models like the kind we propose are crucial
+because the model parameters control particle surface properties independently, 
+whereas these properties are often difficult to decouple in experiment
+~\cite{Bradley2016,Mallory2017,Bradley2017}.
+
+One challenge is translating phenomenological parameters
+into measurable quantities.  For example, Janus particles
+with uniform surface properties are costly or difficult to
+manufacture.  Thus, we can replace the ideal boundary
+conditions \eqref{eq:bcs} with a more realistic one like
+\begin{equation}
+\label{eq:vonMises}
+  g_i(\xx) = \sqrt{
+  \frac{\exp( \kappa_i\cos(\theta_i(\xx) - \theta^0_i))}
+  {2\pi r_i I_0(\kappa_i)}}.
+\end{equation}
+Here, the term under the square root is the von Mises distribution with
+director angle $\theta^0_i$ and Bessel function $I_0$ of order zero~\cite{Fisher_1993}.
+The square of this function behaves as a normal distribution with variance
+like $1/\kappa_i$. We can replicated surface imperfections
+by randomizing the concentration $\kappa_i$ and particle radii $r_i$,
+for example. Collaboration with experimental groups will
+use numerical methods to predict parameter regimes 
+to control particle-particle interactions.
+In Specific Aim 3, we discuss how to include ions and surface charge.
 
@@
 %\end{wrapfigure}
-The main modeling challenge is to translate the phenomenological
-parameters, e.g. boundary conditions, into measurable quantities
-such as contact angles. Collaboration with experimental groups will
-use numerical methods to predict parameter regimes 
-to control particle-particle interactions. In Specific Aim 3, we
-discuss how to include ions and surface charge.
 
 \subsubsection{Hydrophobic forces as capillary wetting}
-A natural generalization of the linear response model is to use a
-fourth-order, tilted double-well potential $f(u) = a(u-u_0)^2(u-u_1)^2 +
-bu$. Motivated by capillary wetting, soft matter physicist Gerhard
-Gompper introduced a double-well model for one-dimensional hydrophobic
-attraction \cite{GoHaKo94}. The two-dimensional attraction we propose is
-more complicated and includes extra line tension effects not present in
-the one-dimensional theories.
+A natural generalization of the linear response potential $f(u) = u^2$
+is a fourth-order, tilted double-well potential
+$f(u) = a(u-u_0)^2(u-u_1)^2 + bu$.
+Here, the order parameter $u$ is related to
+the mean number of nearest neighbors
+per water molecule \cite{GoHaKo94}.
+The value $u_0$ gives the absolute minimum in the bulk
+and $u_1$ gives a local minimum for the
+tetrahadral water network found at hydrophobic surfaces.
+Figure \ref{fig:CA}(a) illustrates a double-well potential
+and Specific Aim 2 describes the numerical implementation issues.
 
-Here, the order parameter $u$ is the mean number of nearest neighbors
-per water molecule. The value $u_0 = 4$ gives a local minimum for the
-ideal tetrahadral water network found at hydrophobic surfaces. The value
-$u_1 \sim 4.4$ gives the absolute minimum in the bulk where there is a
-mixture of four and five-coordinated waters. When particles are
-well-separated, the energetic cost for filling the interstitial region
-with $u_0$-phase water is prohibitive and there is a phase shift from
-the $u_0$ to $u_1$ water order---the attraction landscape is more or
-less identical to the linear response theory. Conversely, when particles
-are proximal, it becomes energetically favorable to coalesce
-$u_0$-phases. This introduces a line tension for the phase transition.
-
+\begin{wrapfigure}[28]{l}{1.8in}
+  \vspace{-4pt}
+  \centering
+  \input{figures/doublewell.tikz} 
+  \caption{\label{fig:CA} (a) The double well potential $u_0 =
+  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
+  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
+  and inexact Newton's methods.}
+\end{wrapfigure}
 Equation~\eqref{eq:SL} takes the form of a steady-state Allen-Cahn
 equation. The Allen-Cahn equation is used in phase field formulations of
-immisible fluids, for example. PI RR and colaborators launched the
+immisible fluids, for example.
+PI BQ has developed fast integral equation solvers for
+the Allen-Cahn equation \cite{kro-qua2011, qua2011}.
+PI RR and colaborators launched the
 simulation and asymptotic analysis of phase field functionals of
@@
 
-One potential application of the Allen-Cahn-type formulation is to
-explaning measured hydrophobic attraction profiles.
-The experimental data on hydrophobic attraction between 
-is well-established and the literature contains data for a number of
-solvents and hydrocarbon species. The experimental measurements
-are well-fit by a double exponential curve in the 10 to 100 nanometer range
-of separation. Below 10~nm, however, there is an amplification of force
-and the attraction follows a much steeper force law not accounted
-for by past phenomenoloical theories~\cite{Lin2005}.
+The key innovation is that when particles are
+well-separated, the energetic cost for filling the interstitial region
+with $u_0$-phase water is prohibitive and there is a phase shift from
+the $u_0$ to $u_1$ water order---the attraction landscape is more or
+less identical to the linear response theory. Conversely, when particles
+are proximal, it becomes energetically favorable to coalesce
+$u_0$-phases. This introduces a line tension for the phase transition
+which is an effect not present in the one-dimensional model.
 
-It may be the case that the double-well formulation recreates the long
-and short-range interactions. The advantage is that the two-dimensional
-simulations can replicate the experimental setup better than prior,
-one-dimensional theoretical work Some of the model parameters directly
-connect to long-range decay lengths and energy cost of creating
-hydrophobic-water interfaces with established ranges of values. Other
-parameters, like the well structure, are fit to the measured data. These
-base-line simulations will allow us to move on to provide more accurate
-colloidal suspension simulations.
+The double-well formulation can potentially 
+explain hydrophobic interaction over the full distance
+regime~\cite{Lum1999, Lin2005, Meyer2006, Ducker2016}.
+Motivated by capillary wetting, Gerhard
+Gompper introduced the double-well model for one-dimensional hydrophobic
+attraction \cite{GoHaKo94}.
+The results improved on previous work~\cite{ErLjCl89,MaRa76},
+but the realistic hydrophobic effect is more
+complicated and may involve higher-dimensional geometric features. 
+Some of the model parameters directly
+%connect to long-range decay lengths and energy cost of creating
+%hydrophobic-water interfaces with established ranges of
+to well-established experimental values. Other
+parameters, like the details of the well structure,
+are less well-understood and must be fit to the measured data.
+This improved model will allow us to more accurately 
+simulate colloidal suspensions.
+%The experimental data on hydrophobic attraction between 
+%is well-established and the literature contains data for a number of
+%solvents and hydrocarbon species.
+%The experimental measurements
+%are well-fit by a double exponential curve in the 10 to 100 nanometer range
+%of separation. Below 10~nm, however, there is an amplification of force
+%and the attraction follows a much steeper force law not accounted
+%for by past phenomenoloical theories~\cite{Lin2005}.
 
+%It may be the case that the double-well formulation recreates the long
+%and short-range interactions. The advantage is that the two-dimensional
+%simulations can replicate the experimental setup better than prior,
+%one-dimensional theoretical work
+
+\todo[inline]{Below needs citation and more solid explanation}
 Other approaches will be required if the modified phenomenological
-theory does not recreate the measured force curves. We can rule out
-convection in the water structure since the time scale of particle
-motion is much larger than the hydrogen-bond lifetimes. One approach is
-to consider Gaussian fluctuation. Here, we expand the free energy
+theory does not recreate the measured force curves.
+One such approach is to consider Gaussian fluctuation. Here, we expand
+the free energy
 functional around the saddle point solution. The fluctuation energy

### 2021-11-13 NSF2021/Description/specificaim2.tex
fingers crossed

@@
 
-\begin{wrapfigure}[27]{l}{1.8in}
-  \vspace{-4pt}
-  \centering
-  \input{figures/doublewell.tikz} 
-  \caption{\label{fig:CA} (a) The double well potential $u_0 =
-  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
-  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
-  and inexact Newton's methods.}
-\end{wrapfigure}
+%\begin{wrapfigure}[27]{l}{1.8in}
+%  \vspace{-4pt}
+%  \centering
+%  \input{figures/doublewell.tikz} 
+%  \caption{\label{fig:CA} (a) The double well potential $u_0 =
+%  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
+%  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
+%  and inexact Newton's methods.}
+%\end{wrapfigure}
 Having demonstrated that the inexact Newton method converges in one

### 2021-11-13 NSF2021/Description/specificaim1.tex
repaired figures: pdf -> jpg

@@
  \vspace{-3pt}
- \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.pdf}
+ \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.jpg}
  \caption{\label{fig:flow_map}
@@
    come from the Stokes equations and
-   hydrophobic interactions come from the structure order parameter $u$.}
+   hydrophobic interactions come from the structure order parameter $u$.
+   The colormap is for the intensity of $u$.}
 \end{wrapfigure}
@@
 minimize the free energy of the structure of the surrounding water
-molecules. The free energy functional take the form 
+molecules. The free energy functional takes the form 
 \begin{align*}
@@
   \vspace{-10pt}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.pdf}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.pdf}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.pdf}  
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}  
   \caption{\label{fig:bcs} Boundary conditions characterize the water
@@
       (a)
-    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B1.pdf}
-    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B2.pdf}
-     &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B3.pdf}    \\
+    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B1.jpg}
+    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B2.jpg}
+     &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B3.jpg}    \\
      (b)
-    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C1.pdf}
-    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C2.pdf}
-      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C3.pdf}    \\
+    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C1.jpg}
+    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C2.jpg}
+      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C3.jpg}    \\
     (c)
-      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A1.pdf}
-      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A2.pdf}
-      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A3.pdf}    \\
+      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A1.jpg}
+      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A2.jpg}
+      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A3.jpg}    \\
       &\multicolumn{1}{c}{$t = 0$}

### 2021-11-13 NSF2021/Description/specificaim3.tex
cleaned up gantt chart

@@
 $n_{+}$ ($n_{-}$) is the concentration of cation (anion). In the limit
-of small $\delta$, PI Young and collaborator Y.~Mori (U Penn) used
+of small $\delta$, PI YNY and collaborator Y.~Mori (U Penn) used
 asymptotic analyses to show that the jump in electric potential across
@@
 Under such simplification, equation~\eqref{eq:EKstokes} may be
-re-formulated into integral forms. PIs Ryham and Young will conduct the
-asymptotic analyses to derive this form, and work with PI Quaife to
-design numerical algorithms to simulate the modified system. We will
-first investigate the effects of salt concentration on the assembly of
-Janus particles to form helices, as shown in
-Figure~\ref{fig:helices_of_JPs}.
+re-formulated into integral forms. PIs RR and YNY will conduct the
+asymptotic analyses to derive this form, and work with PI BQ to design
+numerical algorithms to simulate the modified system. We will first
+investigate the effects of salt concentration on the assembly of Janus
+particles to form helices, as shown in Figure~\ref{fig:helices_of_JPs}.
 
@@
 propose to examine how to use an external electric field to control the
-amphiphilic self-assembly in solvent. PI Young has a track record of
+amphiphilic self-assembly in solvent. PI YNY has a track record of
 working on electrohydrodynamics of an elastic, inextensible membrane
@@
 Young2015_PoF} and numerical simulations~\cite{Nganguia2015_CiCP} and
-will work with both PIs Ryham and Quaife to extend the HAP model to
-study the electromechanical effects on the assembly of colloidal amphiphiles.
+will work with both PIs RR and BQ to extend the HAP model to study the
+electromechanical effects on the assembly of colloidal amphiphiles.
 Results from this research will yield a quantitative understanding of

### 2021-11-13 NSF2021/Description/priorsupport.tex

@@
 grant is modeling the interaction between a pure lipid bilayer membrane
-with surfactant, cholesterol and protein.
+with surfactant, cholesterol, and protein.
 %Hence, there is no overlap between these grants and the current proposal.
@@
 One PhD student (Szu-Pei Fu) was funded to work with YNY, and work has
-resulted in seven papers
-\cite{Nganguia2013_PoF,Nganguia2013_PRE,Young2014_JFM,Young2015_PoF,Nganguia2015_CiCP,Pak2015_PNAS,fu2015pre}.
-YNY has been actively involved with promotion of underrepresented
-students at NJIT. The other PhD student (Herve Nganguia) is African.
-YNY has taught a broad spectrum of courses in fluid mechanics and
-applied math modeling.
+resulted in seven papers~\cite{Nganguia2013_PoF, Nganguia2013_PRE,
+Young2014_JFM, Young2015_PoF, Nganguia2015_CiCP,
+Pak2015_PNAS,fu2015pre}. YNY has been actively involved with promotion
+of underrepresented students at NJIT. The other PhD student (Herve
+Nganguia) is African. YNY has taught a broad spectrum of courses in
+fluid mechanics and applied math modeling.
 
@@
 {\it Broader impacts:} 
-A second-year PhD student (Jake Cherry) has been assigned to this
-project. Since the funding just began, results have not yet
-been published or presented.
+A third-year PhD student (Jake Cherry) has been assigned to this
+project. One paper will be submitted before December
+2021~\cite{lin-her-qua-che2021}.
 
@@
 
-\begin{wrapfigure}[8]{r}{0.56\textwidth}
+\begin{wrapfigure}[11]{r}{0.56\textwidth}
 \vspace{-19pt}
-\definecolor{barblue}{RGB}{51,102,254}
+%\definecolor{barblue}{RGB}{51,102,254}
 %\renewcommand\sfdefault{phv}
@@
     %bar label node/.append style={left=2cm},
-    bar/.append style={draw=none, fill=barblue},
-    bar incomplete/.append style={fill=barblue},
+    bar/.append style={draw=none, fill=blue},
+    bar incomplete/.append style={fill=blue},
     bar progress label font=\mdseries\footnotesize\color{black!70},
@@
 %\ganttgroup{Tasks\hfill}{1}{12}\\
-  \ganttbar{Specific Aim 1 (2D)}{1}{4} \\
-  \ganttbar{Specific Aim 1 (3D)}{8}{12}\\
-\ganttbar{Specific Aim 2}{1}{8}\\
-\ganttbar{Specific Aim 3}{1}{12}\\
-\ganttbar{Program management}{1}{12}
+\ganttbar[bar/.append style={fill=red}]{Specific Aim 1}{1}{12} \\
+\ganttbar[bar/.append style={fill=blue}]{Specific Aim 2}{1}{12}\\
+\ganttbar[bar/.append style={fill=green}]{Specific Aim 3}{1}{12}\\
+\ganttbar[bar/.append style={fill=black}]{Program Management}{1}{12}
+\ganttbar[bar/.append style={fill=magenta}]{}{4}{4}
+\ganttbar[bar/.append style={fill=magenta}]{}{8}{8}
+\ganttbar[bar/.append style={fill=magenta}]{}{12}{12}
 \end{ganttchart}
 \vspace{-10pt}
-\caption{\footnotesize Schedule for the proposed work, measured in
-  quarters from the beginning of the project.}
+\caption{Schedule for the proposed work, measured in quarters from the
+  beginning of the project. The lead PI of each Specific Aim will be RR
+  (red), BQ (blue), and YNY (green). Project management will be
+  continuous (black), but we anticipate extra attention will be
+  necessary to align objectives in quarters 4, 8, and 12 (magenta).}
 \label{fig:schedule}
@@
 and collaborative efforts in physics, applied mathematics, algorithms,
-and computing. Ryham has been working on mathematical modeling with a
-strong analytical background. Young has been working on many areas of
+and computing. PI RR has been working on mathematical modeling with a
+strong analytical background. PI YNY has been working on many areas of
 computational fluid dynamics and applications to math biology for many
-years. Quaife has been working on integral equation methods, fast
+years. PI BQ has been working on integral equation methods, fast
 algorithms, and their applications to fluid dynamics for many years.
-Their recent collaborative work on the HAP model in two dimensions has
-provided a solid foundation for the proposed research.
+Their recent collaborative work on the HAP model in two
+dimensions~\cite{FuQuRyYo20} has provided a solid foundation for the
+proposed research.
 
-\medskip
+\smallskip
 
@@
 The management responsibility of this collaborative research will reside
-with the lead PI (Ryham) for this endeavor. The research work is
-structured to meet the tasks discussed in \S\ref{sec:proposed-work}.
-%
-The PIs, postdocs, and students will meet frequently on Zoom and
-in person when possible. During the pandemic, the three PIs will meet
-weekly on Zoom for a research meeting. Once the pandemic is under control, PI RR and PI YNY will conduct biweekly meetings in person, with PI BQ Zoom in from Florida.
-The PIs will share software packages, paper
-sources, and references on a common \textsf{Git} repository. The
-resulting software packages will be posted on the \textsf{Github}
-software repository.
+with the lead PI (RR) for this endeavor. The research work is structured
+to meet the tasks discussed in \S\ref{sec:proposed-work}. The PIs,
+postdocs, and students will meet frequently on Zoom and in person when
+possible. During the pandemic, the three PIs will meet weekly on Zoom
+for a research meeting. Once the pandemic is under control, PI RR and PI
+YNY will conduct biweekly meetings in person, with PI BQ Zoom in from
+Florida. The PIs will share software packages, paper sources, and
+references on a common \textsf{Git} repository. The resulting software
+packages will be posted on the \textsf{Github} software repository.
 
-\medskip
+\smallskip
 
 \textbf{Research Schedule:} The detailed schedule for the proposed work
-is shown in Figure~\ref{fig:schedule}. Specific Aim 1 is split over two
-periods to allow time for 3D code to be developed.
+is shown in Figure~\ref{fig:schedule}. Each PI will spearhead a
+different Specific Aim, and program management will happen
+throughout, with special coordination taken in quarters 4, 8, and
+12.

### 2021-11-13 NSF2021/Description/specificaim2.tex

@@
 multipole method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2,
-fmm3, fmm4, fmm6, fmm7, fmm8}. PI Quaife is experienced with applying
-FMMs for the Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the
+fmm3, fmm4, fmm6, fmm7, fmm8}. PI BQ is experienced with applying FMMs
+for the Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the
 screened Laplace equation~\cite{kro-qua2011, qua2011}. Furthermore, to
@@
 as the inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017} and
-domain decomposition~\cite{che-bir2021}. PI Quaife used the IFMM to
+domain decomposition~\cite{che-bir2021}. PI BQ used the IFMM to
 precondition Stokes equations~\cite{qua-cou-dar2018}. A suite of other
@@
 computational challenge by developing novel high-order adaptive time
-stepping methods. PI Quaife developed a high-order adaptive time
+stepping methods. PI BQ developed a high-order adaptive time
 stepping method for hydrodynamic suspensions \cite{qua-bir2016}, and it
@@
 force and torque of the system which is computationally cheap and
-physically zero. PI Quaife's experience is that error estimates based on
+physically zero. PI BQ's experience is that error estimates based on
 physical constraints such as force- and torque-free conditions

### 2021-11-13 NSF2021/Description/specificaim1.tex
SA1 with PDF

@@
 properties of the amphiphilic particles.
+Applications in this area include cargo-carrying capacity, 
+catalytic activity, or stimuli-responsive shape-changes
+\cite{McBr21, HaBr20}.
 
@@
   \end{center}
-  \caption{\label{fig:self-assembly}
+  \vspace{-20pt}
+  \caption{\footnotesize
+    \label{fig:self-assembly}
     Using the same initial configuration,
     particles self-assemble into distinct morphologies based
-    on the boundart condition $g.$ 
-    boundary condition leads to a checkerboard pattern.
+    on the boundary condition $g.$ 
     In row (a), self-assembly with an amphiphilic boundary
@@
     In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
-    Particles orient like sides to form a checkerboard pattern.
+    Particles orient like sides to form a checkerboard pattern.\\
   }
@@
 
+\begin{wrapfigure}[14]{l}{2in}
+  \vspace{-4pt}
+  \centering
+  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
+  \vspace{-20pt}
+  \caption{\footnotesize
+    \label{fig:OrderPDFs}
+    Probability density functions for
+    relative orientation of nearby particles
+    for the data in 
+    Figure~\ref{fig:self-assembly}, $t = t_{\text{final}}$.
+  }
+\end{wrapfigure}
 The ultimate goal is to use numerical simulations to aid
-the syntheses soft matter materials.
-Applications in this area include cargo-carrying capacity, 
-catalytic activity, or stimuli-responsive shape-change to amplify colloid
-utility for a wide range of  spanning environmental remediation to drug
-delivery \cite{McBr21, HaBr20}.
+the syntheses of soft matter materials.
 Here, mathematical models like the kind we propose are crucial
@@
 ~\cite{Bradley2016,Mallory2017,Bradley2017}.
-
-One challenge is translating phenomenological parameters
-into measurable quantities.  For example, Janus particles
+The ability to translate phenomenological parameters
+into measurable quantities is important. 
+For example, Figure~\ref{fig:OrderPDFs} plots
+the probability density functions for
+relative orientation of nearby particles.
+The single peak and broad tails for the blue curve indicates a bilayer structure.
+The bimodal red curve indicates multilamellar monolayers. Finally,
+The yellow distribution has peaks at $\pm 45^{\circ}$ 
+indicating a checkboard pattern. 
+As another example, Janus particles
 with uniform surface properties are costly or difficult to
@@
 
-\begin{wrapfigure}[28]{l}{1.8in}
+\begin{wrapfigure}[29]{l}{1.8in}
   \vspace{-4pt}
@@
 
-The key innovation is that when particles are
+The double-well formulation can potentially 
+explain hydrophobic interaction over the full distance
+regime~\cite{Lum1999, Lin2005, Meyer2006, Ducker2016}.
+Motivated by capillary wetting, Gerhard
+Gompper introduced the double-well model for one-dimensional
+hydrophobic attraction \cite{GoHaKo94}.
+The results improved on previous work~\cite{ErLjCl89,MaRa76},
+but a realistic model of hydrophobic effect 
+probably involves particle shapes in addition to distances of separation.
+The key innovation in the model we propose is that when particles are
 well-separated, the energetic cost for filling the interstitial region
@@
 
-The double-well formulation can potentially 
-explain hydrophobic interaction over the full distance
-regime~\cite{Lum1999, Lin2005, Meyer2006, Ducker2016}.
-Motivated by capillary wetting, Gerhard
-Gompper introduced the double-well model for one-dimensional hydrophobic
-attraction \cite{GoHaKo94}.
-The results improved on previous work~\cite{ErLjCl89,MaRa76},
-but the realistic hydrophobic effect is more
-complicated and may involve higher-dimensional geometric features. 
-Some of the model parameters directly
+Some of the model parameters connect directly
 %connect to long-range decay lengths and energy cost of creating
@@
 
-\todo[inline]{Below needs citation and more solid explanation}
-Other approaches will be required if the modified phenomenological
-theory does not recreate the measured force curves.
+Other approaches may be required if the modified phenomenological
+theory does not recreate measurements.
 One such approach is to consider Gaussian fluctuation. Here, we expand
@@
 fluctuations should ideally also be considered. 
+\todo[inline]{Above, needs citation and more solid explanation}
 

### 2021-11-14 NSF2021/Description/specificaim1.tex
fixed typos in whole document

@@
 The hydrodynamic interactions come from the mobility problem for rigid
-particles immersed in a viscous solvent, which we solve with a
-second-order Adams-Bashforth method. Assuming inertial terms are
+particles immersed in a viscous solvent. We then use a
+second-order Adams-Bashforth method to update the particle configuration.
+Assuming inertial terms are
 negligible, the particle motion is goverened by the Stokes equations
@@
 = C \left[ \rho^{-1} f(u) \mathbf{I}
-  + \rho \left(|\nabla u|^2 \mathbf{I} - \nabla u \nabla u^T\right)\right].
+  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
 \end{align}
@@
 
-The density~\eqref{eq:stress} was first
+The stress~\eqref{eq:stress} was first
 introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
@@
 boundaries are nearly touching and high-order numerical
-schemes and adaptively chosen time step sizes
+schemes and adaptively chosen time-step sizes
 are required to calculate trajectories accurately.
@@
 particle center $\aa_i$, and the particle director $\dd_i$ (Figure \ref{fig:flow_map}).
-The normalizations, e.g. $(\pi r)^{-1/2}$, provide a uniform
+The normalizations e.g., $(\pi r)^{-1/2}$, provide a uniform
 surface energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles
@@
 The cases (b) and (c) are obtained by applying a vertical shift
-and scaling to case (a), which amounts to changing one line of code. 
+and scaling to case (a), see Figure \ref{fig:bcs}.
 Using this setup, we simulate the dynamics of 100 particles with random
@@
 
-\begin{wrapfigure}[11]{r}{0.65\textwidth}
-  \vspace{-10pt}
+\begin{wrapfigure}[9]{r}{0.65\textwidth}
+  \vspace{-20pt}
+  \begin{center}
   \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
@@
   \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}
+  \end{center}
+  \vspace{-20pt}  
   \caption{\label{fig:bcs} Boundary conditions characterize the water
@@
   particle with anisotropic intensity (middle), a water structure with
-  plus/minus polarity (right). The dashed curve is the boundary of the
-  disk and the arrow is its director.}
+  positive/negative charge (right). The dashed curve is the boundary of the
+  disk and the arrow is its director for each particle.}
 \end{wrapfigure}
@@
 The boundary condition \eqref{eq:bcs}(b) 
-gives a particle with a hydrophobic intensity three times as great
+gives a particle with a hydrophobic intensity that is greater
 on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
@@
     \label{fig:self-assembly}
-    Using the same initial configuration,
-    particles self-assemble into distinct morphologies based
-    on the boundary condition $g.$ 
+    Rows (a)-(c) have the same initial configuration
+    but have different boundary conditions $g.$ 
     In row (a), self-assembly with an amphiphilic boundary
-    condition \eqref{eq:bcs}(a) results a bilayer pattern shielding
+    condition \eqref{eq:bcs}(a) results in a bilayer pattern shielding
     the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
@@
 \end{figure}
-
-\todo[inline]{Rationalize and citations for following} 
-Finally, boundary condition \eqref{eq:bcs}(c) models 
-a particle with oppositelly charged ends making the 
-particle heads repel the tails \cite{MaRa76, Ma77}.
-The particles initially form chains with their directors perpendicular to the
-length of the chain. The equilibrium structure consists of particles
-positioned on a square grid in a checkerboard pattern
-Figure~\ref{fig:self-assembly}(c). This patterning is a consequence of
-energy minimality and allows each particle to simultaneously coordinate
-its head with the head of three other particles and its tail with the
-tail of three other particles.
 
@@
 \end{wrapfigure}
+Finally, boundary condition \eqref{eq:bcs}(c) models 
+a \hl{particle with oppositelly charged ends} making the 
+particle heads repel the tails \cite{MaRa76, Ma77}.
+The particles initially form chains with their directors perpendicular to the
+length of the chain. The equilibrium structure consists of particles
+positioned on a square grid in a checkerboard pattern
+Figure~\ref{fig:self-assembly}(c). This patterning is a consequence of
+energy minimality and allows each particle to simultaneously coordinate
+its head with the head of three other particles and its tail with the
+tail of three other particles.
+
 The ultimate goal is to use numerical simulations to aid
@@
 Here, mathematical models like the kind we propose are crucial
-because the model parameters control particle surface properties independently, 
-whereas these properties are often difficult to decouple in experiment
+because the model parameters control surface properties independently, 
+which can be difficult to accomplish experimentaly 
 ~\cite{Bradley2016,Mallory2017,Bradley2017}.
@@
 For example, Figure~\ref{fig:OrderPDFs} plots
-the probability density functions for
-relative orientation of nearby particles.
-The single peak and broad tails for the blue curve indicates a bilayer structure.
-The bimodal red curve indicates multilamellar monolayers. Finally,
-The yellow distribution has peaks at $\pm 45^{\circ}$ 
-indicating a checkboard pattern. 
-As another example, Janus particles
-with uniform surface properties are costly or difficult to
-manufacture.  Thus, we can replace the ideal boundary
+the probability density function for 
+relative orientation of adjacent particles
+for the three boundary condition cases:
+(a) is unimodal with a peak at $\theta = 0$,
+(b) is bimodal with peaks at $\theta = 0$ and $\theta = \pi$,
+and (c) is multimodal with peaks at $\theta = 0$ and $\theta = \pm \pi/2$.
+This kind of information can be used as an indicator
+of the collective morphology. As another example,
+it is costly or difficult to manufacture
+Janus particles with uniform shape.
+Thus, we can replace the idealistic boundary
 conditions \eqref{eq:bcs} with a more realistic one like
@@
 director angle $\theta^0_i$ and Bessel function $I_0$ of order zero~\cite{Fisher_1993}.
-The square of this function behaves as a normal distribution with variance
-like $1/\kappa_i$. We can replicated surface imperfections
+The square of this function is asymptotic to a normal distribution with variance
+like $1/\kappa_i$, $\kappa_i \to \infty$. We can replicated surface imperfections
 by randomizing the concentration $\kappa_i$ and particle radii $r_i$,
-for example. Collaboration with experimental groups will
+for example. \hl{Collaboration with experimental groups will
 use numerical methods to predict parameter regimes 
-to control particle-particle interactions.
+to control particle-particle interactions.}
 In Specific Aim 3, we discuss how to include ions and surface charge.
@@
 
-\subsubsection{Hydrophobic forces as capillary wetting}
-A natural generalization of the linear response potential $f(u) = u^2$
-is a fourth-order, tilted double-well potential
-$f(u) = a(u-u_0)^2(u-u_1)^2 + bu$.
+\subsubsection{Hydrophobic forces with double-well potential}
+A natural generalization of the potential $f(u) = u^2$
+is a fourth-order, asymmetric double-well potential
+$f(u) = a(u-u_0)^2(u-u_1)^2 + c(u-u_0)^2 + bu$.
 Here, the order parameter $u$ is related to
@@
 The value $u_0$ gives the absolute minimum in the bulk
-and $u_1$ gives a local minimum for the
-tetrahadral water network found at hydrophobic surfaces.
+and $u_1$ gives a local minimum at hydrophobic surfaces.
 Figure \ref{fig:CA}(a) illustrates a double-well potential
@@
 the Allen-Cahn equation \cite{kro-qua2011, qua2011}.
-PI RR and colaborators launched the
+PI RR has experience in the 
 simulation and asymptotic analysis of phase field functionals of
@@
 well-separated, the energetic cost for filling the interstitial region
-with $u_0$-phase water is prohibitive and there is a phase shift from
+with $u_1$-phase water is prohibitive and there is a phase shift from
 the $u_0$ to $u_1$ water order---the attraction landscape is more or
@@
 are proximal, it becomes energetically favorable to coalesce
-$u_0$-phases. This introduces a line tension for the phase transition
+$u_1$-phases. This introduces a line tension for the phase transition
 which is an effect not present in the one-dimensional model.
@@
 are less well-understood and must be fit to the measured data.
-This improved model will allow us to more accurately 
-simulate colloidal suspensions.
+This improved model will afford greater physical accuracy to
+our simulations.
 %The experimental data on hydrophobic attraction between 

### 2021-11-14 NSF2021/Description/specificaim2.tex
fixed typos in whole document

@@
 Aim 2, we propose novel and efficient high-order numerical methods to
-simulate dynamic assembly of particles under HAP potential in a viscous
+simulate dynamic assembly of particles under the HAP in a viscous
 solvent. As described in~\eqref{eq:stokes} and illustrated in
@@
 will interpret the solution of~\eqref{eq:SL} as the root finding problem
+for
 \begin{align}
   \label{eq:F}
-  J[u] = -\rho^2 \Delta u + f'(u).
+  J[u] = -\rho^2 \Delta u + \tfrac{1}{2}f'(u).
 \end{align}
@@
 \end{align*}
-where $dJ^N = -\rho^2 \Delta + f''(u^N)$ is the Fr\'{e}chet derivative
+where $dJ^N = -\rho^2 \Delta + \tfrac{1}{2}f''(u^N)$ is the Fr\'{e}chet derivative
 of $F$, and $\alpha$ is the step size which will be determined using
 backtracking. As expected, the biggest computational challenge is
-solving $- \rho^2 \Delta v + f''(u^{N}) v = J[u^N]$. Solving this
+solving $- \rho^2 \Delta v + \tfrac{1}{2}f''(u^{N}) v = J[u^N]$. Solving this
 variable coefficient PDE with an integral equation is challenging since
@@
 use an inexact Newton's method where $dJ^{-1}$ is defined in terms of
-the piecewise quadratic approximation
+the continuous, piecewise quadratic approximation
 \begin{align*}
@@
     a(u - u_0)^2, &\mbox{if } u \leq (u_0 + u_1)/2, \\
-    (u - u_1)^2, &\mbox{if } u > (u_0 + u_1)/2.
+    (u - u_1)^2 + \tfrac{1}{4}(a-1)(u0-u1)^2 , &\mbox{if } u > (u_0 + u_1)/2,
   \end{cases}
@@
   \label{eq:screenedPoisson}
-  -\rho^2 \Delta v + \tilde{f}''(u^{N})v = J[u^N],
+  -\rho^2 \Delta v + \tfrac{1}{2}\tilde{f}''(u^{N})v = J[u^N],
 \end{align}
@@
 second-order finite difference method. The choice of parameters $a$,
-$b$, $U_0$, and $U_1$ result in the double well potential illustrated in
+$b$, $u_0$, and $u_1$ result in the double well potential illustrated in
 Figure~\ref{fig:CA}(a), and both the exact and inexact Newton's methods
@@
 Having demonstrated that the inexact Newton method converges in one
-dimension, it will be coupled with IE formulations to to
+dimension, it will be coupled with IE formulations to 
 solve~\eqref{eq:SL} in two and three dimensions. We first partition
@@
 u_1)/2 \}$ be their common boundary, and we let $G_0$ be the fundamental
-solution of $(-\rho^2 \Delta - 2a)$ and $G_1$ be the fundamental
-solution of $(-\rho^2 \Delta + 2)$. Then, the solution
+\hl{solution of $(-\rho^2 \Delta + a)$ and $G_1$ be the fundamental
+solution of $(-\rho^2 \Delta + 1)$. Then, the solution}
 of~\eqref{eq:screenedPoisson} can be written as $u = u^P + u^H$ where
@@
 across $\Lambda$. This approach for using IEs to solve elliptic PDEs
-with with piecewise constant coefficients has succesfully been used in
+with piecewise constant coefficients has succesfully been used in
 other application such as scattering~\cite{hyu-bar2014,

### 2021-11-14 NSF2021/Description/specificaim1.tex
fixed highlighted sentence

@@
 molecules. The free energy functional takes the form 
-\begin{align*}
+\begin{equation}
 \label{eq:free_energy}
@@
   \,d\xx,
-\end{align*}
+\end{equation}
 where $u$ is an order parameter for the structure of water, $\rho$ is a
@@
 Finally, the numerical routine must handle large system sizes
-efficiently when the number of particles is large.
+efficiently.
 
@@
 
+\begin{wrapfigure}[16]{l}{2in}
+  \vspace{-4pt}
+  \centering
+  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
+  \vspace{-20pt}
+  \caption{\footnotesize
+    \label{fig:OrderPDFs}
+    Probability density functions for
+    relative orientation of nearby particles
+    for the data in 
+    Figure~\ref{fig:self-assembly}, $t = t_{\text{final}}$.
+  }
+\end{wrapfigure}
+Finally, boundary condition \eqref{eq:bcs}(c) models 
+a particle whose head surface repels the tail surface as proposed in
+\cite{MaRa76, Ma77}.
+The particles initially form chains with their directors perpendicular to the
+length of the chain. The equilibrium structure
+resembles a checkerboard pattern
+where each particle coordinates
+its head with the head of three other particles and its tail with the
+tail of three other particles Figure~\ref{fig:self-assembly}(c).
+
 \begin{figure}[h!]
   \begin{center}
-    \begin{tabular}{m{0.1cm}m{1.9in}m{1.9in}m{1.9in}}            
+    \begin{tabular}{m{0.1cm}m{1.8in}m{1.8in}m{1.8in}}            
       (a)
-    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B1.jpg}
-    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B2.jpg}
-     &\includegraphics[width=1.9in]{figures/SpecificAim1/N100B3.jpg}    \\
+    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B1.jpg}
+    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B2.jpg}
+     &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B3.jpg}    \\
      (b)
-    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C1.jpg}
-    &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C2.jpg}
-      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100C3.jpg}    \\
+    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C1.jpg}
+    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C2.jpg}
+      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C3.jpg}    \\
     (c)
-      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A1.jpg}
-      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A2.jpg}
-      &\includegraphics[width=1.9in]{figures/SpecificAim1/N100A3.jpg}    \\
+      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A1.jpg}
+      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A2.jpg}
+      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A3.jpg}    \\
       &\multicolumn{1}{c}{$t = 0$}
@@
 \end{figure}
-
-\begin{wrapfigure}[14]{l}{2in}
-  \vspace{-4pt}
-  \centering
-  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
-  \vspace{-20pt}
-  \caption{\footnotesize
-    \label{fig:OrderPDFs}
-    Probability density functions for
-    relative orientation of nearby particles
-    for the data in 
-    Figure~\ref{fig:self-assembly}, $t = t_{\text{final}}$.
-  }
-\end{wrapfigure}
-Finally, boundary condition \eqref{eq:bcs}(c) models 
-a \hl{particle with oppositelly charged ends} making the 
-particle heads repel the tails \cite{MaRa76, Ma77}.
-The particles initially form chains with their directors perpendicular to the
-length of the chain. The equilibrium structure consists of particles
-positioned on a square grid in a checkerboard pattern
-Figure~\ref{fig:self-assembly}(c). This patterning is a consequence of
-energy minimality and allows each particle to simultaneously coordinate
-its head with the head of three other particles and its tail with the
-tail of three other particles.
 
@@
 by randomizing the concentration $\kappa_i$ and particle radii $r_i$,
-for example. \hl{Collaboration with experimental groups will
-use numerical methods to predict parameter regimes 
-to control particle-particle interactions.}
-In Specific Aim 3, we discuss how to include ions and surface charge.
+for example.
+%\hl{Collaboration with experimental groups will
+%use numerical methods to predict parameter regimes 
+%to control particle-particle interactions.}
 
@@
 and $u_1$ gives a local minimum at hydrophobic surfaces.
-Figure \ref{fig:CA}(a) illustrates a double-well potential
-and Specific Aim 2 describes the numerical implementation issues.
+Figure \ref{fig:CA}(a) illustrates a double-well potential.
 
@@
 
-Other approaches may be required if the modified phenomenological
-theory does not recreate measurements.
-One such approach is to consider Gaussian fluctuation. Here, we expand
-the free energy
-functional around the saddle point solution. The fluctuation energy
-then involves calculation of the eigenfunctions of the second variation
-of the free energy. This accounts for the fact that experimental
-measurements are carried out at finite temperatures, where thermal
-fluctuations should ideally also be considered. 
-\todo[inline]{Above, needs citation and more solid explanation}
+Specific Aim 2 describes how we plan to numerically deal with nonlinear
+equations. Once we have established implementations, 
+we can consider further generalizations of 
+\eqref{eq:free_energy} to the Oseen-Frank energy for a nematic liquid crystal
+~\cite{doi:10.1137/15M103844X, Bartels,AIHPA_1997__66_4_411_0,
+ deGennesProst,HaKiLi86,Virga}.  
+For now, Specific Aim 3 describes in detail how we plan to handle
+charges and ions in solution.
+
+%Other approaches may be required if the modified phenomenological
+%theory does not recreate measurements.
+%One such approach is to consider Gaussian fluctuation. Here, we expand
+%the free energy
+%functional around the saddle point solution. The fluctuation energy
+%then involves calculation of the eigenfunctions of the second variation
+%of the free energy. This accounts for the fact that experimental
+%measurements are carried out at finite temperatures, where thermal
+%fluctuations should ideally also be considered. 
+%\todo[inline]{Above, needs citation and more solid explanation}
 

### 2021-11-15 NSF2021/Description/priorsupport.tex
yny
fixed typos in whole document

@@
 Pak2015_PNAS,fu2015pre}. YNY has been actively involved with promotion
-of underrepresented students at NJIT. The other PhD student (Herve
-Nganguia) is African. YNY has taught a broad spectrum of courses in
-fluid mechanics and applied math modeling.
+of underrepresented students at NJIT. One PhD student, Herve Nganguia,
+is now an Assistant Professor at Towson University. YNY has taught a
+broad spectrum of courses in fluid mechanics and applied math modeling.
 
@@
 
+\begin{wrapfigure}[10]{r}{0.4\textwidth}
+  \includegraphics[width=0.4\textwidth]{figures/gantt.jpg}
+  \caption{\label{fig:schedule} Schedule for the proposed work, measured
+  in quarters from the beginning of the project. The lead PI of each
+  Specific Aim will be RR (red), BQ (blue), and YNY (green).}
+\end{wrapfigure}
+
+\begin{comment}
 \begin{wrapfigure}[11]{r}{0.56\textwidth}
@@
 \end{wrapfigure}
+\end{comment}
 \textbf{Project management}: 
@@
 postdocs, and students will meet frequently on Zoom and in person when
-possible. During the pandemic, the three PIs will meet weekly on Zoom
-for a research meeting. Once the pandemic is under control, PI RR and PI
+possible.
+%During the pandemic, the three PIs will meet weekly on Zoom
+%for a research meeting.
+Once the pandemic is under control, PI RR and PI
 YNY will conduct biweekly meetings in person, with PI BQ Zoom in from
@@
 packages will be posted on the \textsf{Github} software repository.
-
-\smallskip
-
+%
+%\smallskip
+%
 \textbf{Research Schedule:} The detailed schedule for the proposed work

### 2021-11-15 NSF2021/Description/specificaim1.tex

@@
 
-Specific Aim 2 describes how we plan to numerically deal with nonlinear
-equations. Once we have established implementations, 
-we can consider further generalizations of 
-\eqref{eq:free_energy} to the Oseen-Frank energy for a nematic liquid crystal
-~\cite{doi:10.1137/15M103844X, Bartels,AIHPA_1997__66_4_411_0,
- deGennesProst,HaKiLi86,Virga}.  
-For now, Specific Aim 3 describes in detail how we plan to handle
-charges and ions in solution.
+Specific Aim 2 describes how we propose to deal with the nonlinear
+equation~\eqref{eq:SL} numerically. Once we have established
+implementations, we will consider further generalizations
+of~\eqref{eq:free_energy}, for example to the Oseen-Frank energy for a
+nematic liquid crystal~\cite{doi:10.1137/15M103844X,
+Bartels,AIHPA_1997__66_4_411_0, deGennesProst,HaKiLi86,Virga}. For now,
+Specific Aim 3 describes in detail how we plan to handle charges and
+ions in solution.
 

### 2021-11-15 NSF2021/Description/specificaim1.tex

@@
 
+\begin{wrapfigure}[9]{r}{0.65\textwidth}
+  \vspace{-20pt}
+  \begin{center}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:bcs} Boundary conditions characterize the water
+    structure at the particle interface: an amphiphilic particle (left),
+    a hydrophobic
+  particle with anisotropic intensity (middle), a water structure with
+  positive/negative charge (right). The dashed curve is the boundary of the
+  disk and the arrow is its director for each particle.}
+\end{wrapfigure}
 Case (a) models amphiphilic particles.
@@
 
-\begin{wrapfigure}[9]{r}{0.65\textwidth}
+\begin{wrapfigure}[14]{l}{2in}
+  \vspace{-4pt}
+  \centering
+  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
   \vspace{-20pt}
-  \begin{center}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:bcs} Boundary conditions characterize the water
-    structure at the particle interface: an amphiphilic particle (left),
-    a hydrophobic
-  particle with anisotropic intensity (middle), a water structure with
-  positive/negative charge (right). The dashed curve is the boundary of the
-  disk and the arrow is its director for each particle.}
+  \caption{\footnotesize
+    \label{fig:OrderPDFs}
+    Probability density functions for
+    relative orientation of nearby particles
+    for the data in 
+    Figure~\ref{fig:self-assembly}, $t = t_{\text{final}}$.
+  }
 \end{wrapfigure}
-
 Multilamelar bilayers arise when both sides of the particle
@@
 
-\begin{wrapfigure}[16]{l}{2in}
-  \vspace{-4pt}
-  \centering
-  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
-  \vspace{-20pt}
-  \caption{\footnotesize
-    \label{fig:OrderPDFs}
-    Probability density functions for
-    relative orientation of nearby particles
-    for the data in 
-    Figure~\ref{fig:self-assembly}, $t = t_{\text{final}}$.
-  }
-\end{wrapfigure}
 Finally, boundary condition \eqref{eq:bcs}(c) models 

### 2021-11-15 NSF2021/Description/broaderimpacts.tex
BI

@@
 \label{sec:BroaderImpacts}
-
 This project aims to advance the mathematical modeling of collective
@@
 intuitive, approach that accounts for important and complex systems
-that are out of reach in computational material science. These complex
-systems include fusion and fission of amphiphilic bilayer membranes and
-optimal shape design in metamaterials. The development of
-three-dimensional models describing colloidal systems could be
+that are presently out of reach in computational material science. These complex
+systems include optimal shape design in metamaterials and
+fusion and fission of amphiphilic bilayer membranes. The further
+development to three-dimensional models describing colloidal systems could be
 transformative in biomedicine and material science. The research draws
 from expertise in scientific computing, physics of fluids, and
-mathematics. The mathematical component incorporates leading techniques
-from geometric analysis and offers insight into fundamentals of material
+mathematics. The mathematical component incorporates leading
+variational techniques and offers insight into fundamentals of material
 science. The project brings socially consequential research into the
 classroom, and offers undergraduates the opportunity to train alongside
-graduate students and postdoctoral fellows. With its combination of
+faculty and postdoctoral fellows. With its combination of
 mathematical modeling, analysis, and scientific computing, the project
@@
 \label{subsec:Educational_plans}
-The topics of this proposal have application in robotics, machine
-learning, and engineering. To foster training in mathematical sciences,
-the project will include undergraduate researchers (URs). The proposal
-supports one UR per year from the lead institution, and will include one
-or two additional URs from actively supported in-house programs
+%The topics of this proposal have application in robotics, machine
+%learning, and engineering.
+To foster training in mathematical sciences,
+the proposal supports one undergraduate researcher (UR) per year
+from the lead institution.
+PI RR has worked side-by-side and
+published with undergraduate coauthors in
+\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16}.
+He is presently mentoring a Clare Boothe Luce Scholar 
+on mathematical analysis of trends in election redistricting.
+With another Fordham supported UR,
+he is finishing a paper on a closed-form 
+energy density for translationally invariant bilayers. 
+Based on these experiences, we have outlined three projects for the present proposal.
+\begin{enumerate}[noitemsep]
+%\noitemsep
+\item Translate project code from MATLAB into a compiled language
 
-The URs will work as a team for eight weeks in the summer. They will
-collaborate directly with the senior personnel, have tutorials in topics
-such as numerical quadrature and integral equations, and train in
-mathematical writing and presentation. To maximize vertical integration,
-and to the extent possible, the PIs and personnel will travel to New
-York for one or two weeks during the summers. Fordham University
-recently constructed a seminar/collaboration space specifically for
-collaborative research, and the URs will have office space with desks
-there. As a requirement, the URs will write quality summary reports and
-give presentations at the their respective research symposia. The work
-will be considered successful if the URs also participate in a national
-conference. In the best possible outcome, the URs will co-author a
-publication.
+\item Use machine learning to post-process data from the Janus particle self-assembly
+%  This project will train UR in the MATLAB and Python programming language,
+%  how to effectively deal with large data sets, and how to represent data meaningfully
+%  using plots and graphics.
 
-There are two ways the proposal will meaningfully engage the community.
-To be more impactful, students from the Bronx High School of Science (PI
-RR) and Newark Science Park High School (PI YNY) will be encouraged to
-join the research team. PI BQ will work with undergraduate and high
+\item Mathematically investigate self-assembly in the zero-screen-length limit
+%  The UR will address the following conjecture about self-assembly:
+%  in the $\rho = 0$ limit, two convex polygons interacting through the hydrophobic attraction potential
+%  converge to a limit with maximally overlapping boundaries.
+%  This is a variational problem with ample numerical evidence. The student
+%  will learn elements of boundary layer analysis.
+
+%\item Implementing a fast-multipole method
+  %  The UR will adapt code written by undergraduates in \cite{RyKlYaCo16}.
+%  The will analyze the energies of bilayer configurations under the new, closed form
+%  energy and compare them to energies calculated in molecular dynamics studies.
+
+\end{enumerate}
+The UR support is for eight summer weeks. 
+In addition to collaborating with the PI,
+they will have tutorials and receive training in
+mathematical writing and presentation.
+The UR will have a desk and meeting room
+in a recently completed collaboration space
+built for the Mathematics Department. 
+As a condition of support, 
+they will be required to write a summary report and
+give a presentation in the university's undergraduate
+research symposium.  The PI 
+will encourage the
+UR to participate in a national conference.
+
+To meaningfully engage the community,
+the PIs will prioritize students coming
+from underrepresented groups and
+specifically target students whose socio-economic
+background prevents them from participating in out-of-state research
+experiences.  PI RR will solicit applicants from Fordham University's
+Collegiate Science and Technology Entry Program.
+Students from the Bronx High School of Science (PI
+RR) and Newark Science Park High School (PI YNY) will also be encouraged to
+join the research team. PI BQ will work with undergraduates and high
 school students through the Undergraduate Research Opportunity Program
-and Young Scholar's Program, as he has done in the past. Secondly, the
-PIs will prioritize students who would most benefit from the grant
-activity. These include students from underrepresented groups,
-and we specifically target students whose socio-economic
-background prevents them from participating in out-of-state research
-experiences.
+and Young Scholar's Program, as he has done in the past.
 
+To maximize vertical integration, the PIs and personnel
+will travel to New York for one or two weeks during the summers.
 Finally, we will create several modules to include in our courses. These
 modules will introduce topics from numerical linear algebra and
-optimization, and be based on the ideas of the proposal. Additionally,
-we and our UR collaborators will give remote, guest lectures in each
-others' courses and undergraduate seminars.
-
+optimization, and highlight concrete applications of mathematics
+based on the ideas of the proposal.
 %The proposed research will have an immediate impact on undergraduate and
@@
 include quantifying collective properties of amphiphilic ensembles,
-mathematical analysis of continuum elastic energies, efficient,
-high-order numerical algorithms for large-scale simulations, and
-incorporating external fields through electric charge. Lastly, the
-proposal extends the results using three-dimensional boundary integral
-formulations.
+improving on mathematical models, 
+efficient, high-order numerical algorithms for large-scale simulations,
+and incorporating external fields through electric charge.
+%Lastly, the
+%proposal extends the results using three-dimensional boundary integral
+%formulations.
 

### 2021-11-15 NSF2021/Description/summary.tex
summary ready for review

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\pagestyle{empty}

\begin{document}
\begin{center}
{\bf \Large Summary}\\ Collaborative Research
\begin{tabular}{ccc}\\ 
Fordham University & Florida State University& New Jersey Institute of Technology\\
Rolf Ryham &            Bryan Quaife &              Yuan-Nan Young
\end{tabular}

\end{center}

\subsection*{Overview}
This proposal aims to advance mathematical modeling and analysis of collective dynamics of amphiphilic self-assembly.  Amphiphilic particles such as lipid molecules possess both hydrophobic and hydrophilic surfaces
that self-assemble into meso/macroscopic structures such as micelles and bilayers of lipids.  Experimentalists model self-assembly
using Janus particles, which have been widely used in soft matter physics as a model amphiphilic colloids and can be designed for catalytic activity or stimuli-responsive smart materials.

Amphiphilic self-assembly comes about due to a long-range attraction called the hydrophobic force.  This force is a major source of nonspecific interactions in biology and soft matter. Despite its ubiquity, theoretical developments explaining the basic underlying principles of the hydrophobic effect have come relatively late. Motivated by its broad applicability, the PIs recently developed a novel and intuitive mathematical model, called the hydrophobic attraction potential model, based on the linear response of water to surface perturbations. This model was used to show, for the first time, self-assembly into vesicle-like structures using a partial differential equation-based particle interaction.

The PIs propose to apply their hydrophobic attraction potential model to the self-organization dynamics of Janus particles.  They aim to generalize the linear response model to more general hydrophobic interactions, which will be numerically implemented using integral equation formulations.  Finally, they will investigate and simulate the hydrophobic interaction in the presence of electric charge and ions. The unifying aspects of the project are establishing a platform for efficiently simulating the collective dynamics at large scales, and the focusing on rigorous, mathematical analysis of the underlying model equations and complicated geometries.  The project supports undergraduate and graduate student collaborators.

\subsection*{Intellectual Merit}
The purpose of this research is to reach interesting physical phenomena with less computational cost than molecular dynamics, and account for more general features that continuum theory misses. The main ingredient is defining a nonlocal interaction through the solution of an elliptic boundary value problem that has the phenomenological characteristics of long-range hydrophobic attraction. This minimal model, while intuitive, is quite a general description of amphiphiles in solvent and gives rise to rich phenomena from Janus particle aggregates to correctly predicting elastic properties of bilayer. The technical research tasks include quantifying collective properties of amphiphilic ensembles, improving on mathematical models, efficient, high-order numerical algorithms for large-scale simulations, and incorporating external fields through electric charge.

\subsection*{Broader Impacts}
This project aims to advance the mathematical modeling of collective dynamics of amphiphilic particles. The simulations use a new, yet intuitive, approach that accounts for important and complex systems that are presently out of reach in computational material science. These complex systems include optimal shape design in metamaterials and fusion and fission of amphiphilic bilayer membranes. The models describing colloidal systems could be transformative in biomedicine and material science. The research draws from expertise in scientific computing, physics of fluids, and mathematics. The mathematical component incorporates leading variational techniques and offers insight into fundamentals of material science. The project brings socially consequential research into the classroom and offers 
undergraduates the opportunity to train alongside faculty and graduate students. With its combination of mathematical modeling, analysis, and scientific computing, the project highlights the importance of mathematics and computation to all areas of science and engineering.
\end{document}

### 2021-11-23 NSF2021/Description/specificaim1.tex
last changes to NSF submission

@@
  \caption{\label{fig:flow_map}
-   In the HAP formulation, hydronamic interactions
-   come from the Stokes equations and
-   hydrophobic interactions come from the structure order parameter $u$.
-   The colormap is for the intensity of $u$.}
+   In the HAP formulation,
+   a system of exterior problems 
+   defines the hydronamic and hydrophobic interactions.
+   The colormap is for the intensity of $u$.
+   The dynamics lead to self-organized structures like a vesicle bilayer.}
 \end{wrapfigure}
@@
 
+\begin{wrapfigure}[10]{r}{0.55\textwidth}
+ \centering
+ \vspace{-3pt}
+ \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/3Particles.jpg}
+ \caption{\label{fig:3particles}
+   \footnotesize
+   Particles translate and rotate to lower the free energy $F[u]$
+   subject to \eqref{eq:SL}, $f(u) = u^2$, and reach a minimal configuration in
+   panel C. The colormap is blue for $u = 0$ and red for $u = 1$.
+   The arrows are the velocity field $\mathbf{u}$.
+ }
+\end{wrapfigure}
 The stress~\eqref{eq:stress} was first
@@
 forming particle aggregates that sequester their hydrophobic surface
-regions.
+regions (Figure \ref{fig:3particles}).
 
@@
 
-\begin{wrapfigure}[14]{l}{2in}
+\begin{wrapfigure}[13]{l}{2in}
   \vspace{-4pt}
@@
     for the data in 
-    Figure~\ref{fig:self-assembly}, $t = t_{\text{final}}$.
+    Figure~\ref{fig:self-assembly}, long time.
   }
@@
       &\multicolumn{1}{c}{intermediate time}
-      &\multicolumn{1}{c}{$t = t_{\text{final}}$}
+      &\multicolumn{1}{c}{long time}
   \end{tabular}
@@
 nematic liquid crystal~\cite{doi:10.1137/15M103844X,
-Bartels,AIHPA_1997__66_4_411_0, deGennesProst,HaKiLi86,Virga}. For now,
+  Bartels,AIHPA_1997__66_4_411_0, deGennesProst,HaKiLi86,Virga}.
+Another opportunity to build on the results of the proposed work,
+is evaluating the role of particle multilayers on the stability of
+pickering emulsions. Particle-particle interactions in the aqueous
+layer (adjacent to the water-oil interface) may provide a
+``reservoir'' of particles to stabilize the interface upon droplet deformation (see \cite{Bradley2016} and references therein).
+For now,
 Specific Aim 3 describes in detail how we plan to handle charges and

### 2021-11-23 NSF2021/Description/summary.tex
last changes to NSF submission

@@
-\documentclass{article}
+\documentclass[10pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \pagestyle{empty}
-
+\linespread{1.05}
 \begin{document}
-\begin{center}
-{\bf \Large Summary}\\ Collaborative Research
-\begin{tabular}{ccc}\\ 
-Fordham University & Florida State University& New Jersey Institute of Technology\\
-Rolf Ryham &            Bryan Quaife &              Yuan-Nan Young
-\end{tabular}
-
-\end{center}
+\section*{Summary}
 
 \subsection*{Overview}
+\vspace{-0.1in}
 This proposal aims to advance mathematical modeling and analysis of collective dynamics of amphiphilic self-assembly.
-Amphiphilic particles such as lipid molecules possess both hydrophobic and hydrophilic surfaces
-that self-assemble into meso/macroscopic structures such as micelles and bilayers of lipids.  Experimentalists model self-assembly
-using Janus particles, which have been widely used in soft matter physics as a model amphiphilic colloids and can be designed for catalytic activity or stimuli-responsive smart materials.
+Amphiphilic particles such as lipid molecules possess both hydrophobic and hydrophilic surfaces and self-assemble into meso/macroscopic structures such as micelles and bilayers of lipids.
+Experimentalists model self-assembly using Janus particles—spherical particles possessing a biphasic material label on either hemisphere.
+Janus particles have been widely used in soft matter physics as a model amphiphilic colloid and can be designed for catalytic activity or stimuli-responsive smart materials.
 
-Amphiphilic self-assembly comes about due to a long-range attraction called the hydrophobic force.
+Hydrophobic surfaces experience a nonadditive long-range attraction called the hydrophobic force.
 This force is a major source of nonspecific interactions in biology and soft matter.
-Despite its ubiquity, theoretical developments explaining the basic underlying principles of the hydrophobic effect have come relatively late.
+Despite its ubiquity, theoretical developments explaining its basic underlying principles have come relatively late.
 Motivated by its broad applicability, the PIs recently developed a novel and intuitive mathematical model, called the hydrophobic attraction potential model, based on the linear response of water to surface perturbations.
-This model was used to show, for the first time, self-assembly into vesicle-like structures using a partial differential equation-based particle interaction.
+This model was used to show, for the first time, self-assembly of Janus particles into vesicle-like structures using a partial differential equation-based particle interaction.
 
 The PIs propose to apply their hydrophobic attraction potential model to the self-organization dynamics of Janus particles.
-They aim to generalize the linear response model to more general hydrophobic interactions, which will be numerically implemented using integral equation formulations.
-Finally, they will investigate and simulate the hydrophobic interaction in the presence of electric charge and ions.
+They aim to generalize the linear-response model to more general hydrophobic interactions, and numerically implement these interactions using integral equation formulations.
+Finally, they will investigate and simulate hydrophobic interactions in the presence of electric charge and ions.
 The unifying aspects of the project are establishing a platform for efficiently simulating the collective dynamics at large scales, and the focusing on rigorous, mathematical analysis of the underlying model equations and complicated geometries.
@@
 \subsection*{Intellectual Merit}
+\vspace{-0.1in}
 The purpose of this research is to reach interesting physical phenomena with less computational cost than molecular dynamics, and account for more general features that continuum theory misses.
@@
 \subsection*{Broader Impacts}
+\vspace{-0.1in}
 This project aims to advance the mathematical modeling of collective dynamics of amphiphilic particles.
@@
 The mathematical component incorporates leading variational techniques and offers insight into fundamentals of material science.
-The project brings socially consequential research into the classroom and offers
-undergraduates the opportunity to train alongside faculty and graduate students.
+The project brings socially consequential research into the classroom and offers undergraduates the opportunity to train alongside faculty and graduate students.
 With its combination of mathematical modeling, analysis, and scientific computing, the project highlights the importance of mathematics and computation to all areas of science and engineering.

### 2021-12-29 doc/reviews/ResponseToReviewer1.tex
starting revisions to JFM paper

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Petia Vlahovska,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. Changes to the manuscript
from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
\textcolor{green}{green}, and \textcolor{magenta}{magenta},
respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei, Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

\section*{Response to Reviewer 1}
\noindent
\comment{Overall, the paper is original and interesting. The derivation
of the hydrophobic force without singular integrals is smart and well
written. The characterization of the effective properties of the
coarse-grained vesicles is also of interest and carefully conducted.
However, in many instances the manuscript looks more like a catalogue of
the different behaviors JP vesicles can exhibit in linear flows, rather
than a comprehensive study. The authors describe a few interesting
phenomena but only partially address the exciting physical questions
related to them. The paper lacks quantitative comparisons with continuum
models, parametric studies and detailed explanations to meet the
standards of JFM. In addition, the manuscript seems to have been written
in haste: a figure with no apparent connection to the content of the
paper has been inserted without being referenced or discussed in the
text (see below), some parts need some serious proofreading and
additional clarifications.}
\begin{itemize}
  \item Change 1
  \begin{quotation}
    \noindent
    Can put verbatim change in this environment.
  \end{quotation}
\end{itemize}

\noindent
\comment{There is no parametric study of the effect of the particle size
on the effective properties of the vesicles (interlayer friction,
stretching modulus, permeability,etc$\ldots$). The authors defer this
part for future work in the conclusions, but since the effect of the
particle size is important, as evidenced in Section 4.3, it should be
explored and explained more thoroughly in the manuscript, otherwise the
research would be too incremental. The effect of particle shape seems
indeed more complex and out of the scope of the current paper.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{The membrane rupture situation, briefly illustrated in Section
4.2.3, is not investigated at all. Is there a dimensionless number
related to this phenomenon with a critical value above which rupture
happens? (e.g.~quantifying the competition between shear and
attraction)}

\noindent
\comment{I understand that the results of Section 4.4 are mostly
qualitative and that the goal is to show the visual agreement between
the coarse-grained and continuum vesicle models, but it would be
insightful to provide quantitative comparisons to measure how close they
are to each other.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{The problem is not nondimensionalized with the characteristic
scales of the system but with ns, nm and $\text{pN} \cdot
\text{nm}^{-2}$. This (unusual) nondimensionalization makes it hard to
compare physical quantities and to define order parameters that would
explain/characterize some phenomena observed in the simulations
(e.g.~the membrane rupture).}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{For the sake of clarity, at the end of Section 3 the authors
should summarize the exact set of equations they use and the unknowns
they solve for.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{General comment for all the figures with colormaps: it would be
good to use colorblind friendly colormaps for colorblind people and for
black and white printing.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Figure 1: the arc length $L$ does not appear in panel (c).}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Line 50: typo: ``well-known"}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Page 3: the first two paragraphs seem to be a bit disconnected
from the rest of the introduction. Maybe the authors should rewrite that
part so that there is a transition from the physical problem into
consideration to the various numerical methods used in the literature to
simulate it.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Line 70: ``we maintain contact-free suspensions with a
relatively weak non-stiff repulsive force". What do you mean by
relatively weak repulsive force ? Weak compared to what? (see additional
question on this hereinafter).}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Equation (2.4) is not necessary as the no-slip boundary
condition is standard and it is redundant with (2.5).}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Section 2.2: for clarity, define the variable u as the
hydrophobic attraction potential in the first paragraph.}

\noindent
\comment{The equations of the continuous time evolution of the particle
positions and orientations should be written in Section 2 to close the
problem.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{I think the time-discretization Section 2.3 should go at the
end of Section 3 since this is the one devoted to the numerical
discretization of the governing equations. Also, the sentence ``particle
collisions are avoided even when using a relatively large time step" is
very vague.  What do you mean by ``relatively large time step"? Compared
to what time scale?}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Section 3: the acronym HAP is not defined in the text.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Equation 3.1: use parenthesis to show that the normal
derivative only applies to the Laplace’s Green function $K_0$ and not
the density $\sigma$.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{For clarity, use contraction products ``$\cdot$" when a second
order tensor multiplies a vector to avoid confusion (e.g.~${\bf S} \cdot
{\bf F}$ instead of ${\bf SF}$) in eqs.~(3.4), (3.5), (3.7) and so on
$\ldots$}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{In practice, how do you compute the derivatives $d\sigma /ds$,
$dv_i/ds$ and $dv_i/d\boldsymbol{\nu}$ in (3.13)?}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Line 256: you set the strength of the repulsive force $M = 4k_B
T$. In your simulations there is no thermal fluctuations, so why using
$k_B T$ as a reference energy if it is no there in the simulations?
There should be another energy scale that you could use to calibrate
$M$, right?}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Related question: how much does the interparticle distance
depend on on the strength and range of this artificial repulsive
potential? What is the impact on the vesicle shape and effective
properties?}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Figure 3a,b,d: what does the term in parenthesis ``(1)" means
on the label of the ordinate axis?}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Line 302: the authors mention that tank-threading can only be
observed for shear rate as high as $10^{6}\text{s}^{-1}$. Can such a
high value be generated in experiments?}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Eq.~4.4, typo: $v$ should be $u$.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Figure 6: the yellow particle is not visible when printing in
black and white.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Line 388, typo: ``has" should be ``have".}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Figure 7a is never referred to and its content is never
discussed in the text.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Line 393: The reference to panel ``Figure 7c" seems to be a typo. Same
for ``Figures 7c and 7d" on line 394, I think it should be ``Figures 7b
and 7c".}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Side question: Is it possible to change the vesicle stretching
modulus and hydraulic permeability independently or are these two
properties linked to each other and how?}
\begin{itemize}
  \item Change 1 
\end{itemize}

\end{document}

### 2021-12-29 doc/reviews/ResponseToReviewer2.tex
starting revisions to JFM paper

\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Petia Vlahovska,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. Changes to the manuscript
from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
\textcolor{green}{green}, and \textcolor{magenta}{magenta},
respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei, Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

\section*{Response to Reviewer 2}
\comment{
\noindent
The authors are introducing a novel numerical approach to study vesicles
under flow conditions in two dimensions. The vesicle is modelled as a
collection of amphiphilic Janus particles (JP) interacting with each
other through a hydrophobic attraction potential (HAP) and a short-range
repulsion force to avoid the overlap between particles. Both the
mobility of the particles and the HAP are recast in the form of an
integral equation of the second kind and solved numerically. The authors
presented some results on the deformation and dynamic of a single
vesicle and a pair of vesicles in different type of external flows.
\\ \\
\noindent
The originality of this work stems from coupling the HAP and Stokes
equations through a boundary integral formulation which I personally
find quite interesting. However, numerical models for vesicles and other
class of soft particles in 2D and 3D are already well established in the
literature. Disregarding the 2D nature of the model, I am not fully
convinced on how this approach outperforms the existing models either in
computational performance or in new applications. The authors should
make an extra effort to highlight this. Another weakness of this model,
if I understood correctly, is that the area of the vesicle is not
conserved beyond the small deformation limit. To the best of my
knowledge, a 2D vesicle should fulfill both constant area and perimeter
constraints. This means that the range of application of the model is
limited to the small deformation limits when used to mimic vesicles
under flow. Finally, this paper lacks a thorough validation of the
numerical results with the existing data in the literature and/or an
original application/result describing a physical phenomenon not covered
by the previous literature. This work is suitable for publication in
this journal but a major revision is needed. Below additional minor
comments to be addressed.}
\begin{itemize}
  \item Change 1
  \begin{quotation}
    \noindent
    Can put verbatim change in this environment.
  \end{quotation}
\end{itemize}

\noindent
\comment{The abbreviation HAP is not defined in the text. I guess it stands for hydrophobic attraction potential.
}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{$u$ is used for both the velocity and the solutions of the
Laplace equation. Please use another variable for the scalar function
$u$.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{$\rho$ used in the HAP is not the same as the one used in the
mobility boundary integral equation. One is a decay length of the
attraction potential, while the second is the Euclidean distance between
two JPs.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{$\nu$ is used on multiple instances, sometimes as a normal
vector (see line 97 for example), and other times as some scalar
function (see line 203).}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{What is the bending modulus here? I guess that it is not a
direct input parameter in this model but rather a quantity that can be
deduced from other input parameters. If I am right then, what are these
parameters? And could you tune them if needed to simulate the effect of
the membrane stiffness? This can be important in some applications such
as rigidity-based microfluidic sorting devices.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{To compare the results with the existing literature, I would
suggest introducing the capillary number for vesicles as defined in
\url{https://doi.org/10.1016/j.crhy.2009.10.001}.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{For both examples with the linear shear flow and the Poiseuille
flow, the area of the vesicle is not conserved and the relative error
with respect to the stress-free area increases with the increase of the
external stresses. It can reach roughly 7-8\% for the higher shear rate
in the shear flow example. This is quite significant. Do you have a way
to reduce this error to below 1\%? Note that in other numerical models
for vesicles (e.g.~\url{https://doi.org/10.1016/j.jcp.2008.11.036}),
both constant area and perimeter constraints are fulfilled even when the
vesicle is more deformed than the cases reported here.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{In some interesting applications, the fluid encapsulated by the
bilayer membrane has a viscosity which is different from the suspending
fluid. How difficult it is to add this feature to your model?}
\begin{itemize}
  \item Change 1 
\end{itemize}

\end{document}

### 2021-12-29 doc/reviews/ResponseToReviewer3.tex
starting revisions to JFM paper

\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Petia Vlahovska,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. Changes to the manuscript
from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
\textcolor{green}{green}, and \textcolor{magenta}{magenta},
respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei, Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

\section*{Response to Reviewer 3}
\comment{\noindent
The manuscript extends the authors’ previous work on modeling
amphiphilic particles in a viscous solvent to modeling amphiphilic Janus
particles suspended in a viscous background flow. The authors adopted
the GMRES iterative method to solve the screened Laplace equation for
hydrophobic attraction. They investigated the inter-monolayer friction
of vesicles formed by amphiphilic Janus particles and corresponding
membrane ruptures in viscous flows, and simulated the spatial migration
dynamics of a vesicle in a parabolic flow and also the hydrodynamics of
two vesicles in shear and extensional flows.
\\ \\
\noindent
This manuscript presents a systematic study of the hydrodynamics of
vesicles formed by amphiphilic Janus particles in viscous flows. It
provides quantitative analysis of the inter-monolayer friction, membrane
permeability and the migration dynamics of soft suspended vesicles. The
topic on hydrodynamics of complex fluids is interesting, and this
research fits the scope of Journal of Fluid Mechanics. Here, I am in a
favor of its publication at some points if the authors can address the
following concerns in the revised manuscript.
}
\begin{itemize}
  \item Change 1
  \begin{quotation}
    \noindent
    Can put verbatim change in this environment.
  \end{quotation}
\end{itemize}

\noindent
\comment{In section 2.2, the authors defined a repulsion force with an
empirical formula to prevent particle collisions. However, there is no
benchmark test to show that this artificial repulsion force can generate
correct hydrodynamic lubrication. The authors are suggested to justify
and validate the use of the Imposed Forces with comparison to well-known
lubrication forces between particles.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Fig.~3 plots the time evolution of the reduced area in (a) and
the excess length of the bilayer structure in (b). Both show obvious
oscillations with multiple frequencies, which are not as smooth as the
inset of (c) showing one dominant frequency. The authors are suggested
to explain the source of multiple frequencies generated in the time
evolution of $A$ and $\Delta$.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Fig.~6 illustrates the migration process of a JP vesicle in a
parabolic flow, where the moving velocity is 8 nm/ns and the time frame
is 0 to 12 $\mu$s. Given the length scale R = 20 nm, the migration
distance should be $1000 \times R$. However, in the figure, it shows a
migration distance about 4x R. The authors are suggested to double-check
their model parameterization.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{In Fig.~10, the significant discontinuities in streamlines
across the surface of vesicles are observed, while in most other cases
the streamlines are smooth across the interface of vesicles. The authors
are suggested to describe such discontinuity and provide the
explanation.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Minor: I read some grammatical errors in the manuscript that
should be corrected, i.e., ``replicate well-know vesicle hydrodynamics
$\ldots$" on page 2, ``$\ldots$ a baseline JP vesicles $\ldots$" on page
8, ``circular vesicles has a Laplace pressure $\ldots$" at Eq.~(4.7).
The authors are suggested to have a thorough read of the manuscript.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\end{document}

### 2021-12-29 doc/reviews/ResponseToReviewer1.tex
working on revisions

@@
 \begin{itemize}
-  \item Change 1 
+  \item This typo is corrected.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item Thank you for noticing this oversight. The definition of HAP has
+    been added at its first occurrence in Section 3.1. 
+  \item This change is in \textcolor{green} since it was also pointed
+    out by Reviewer 2.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item Parenthesis have been added to equation (3.1)
+
+  \item Equations (3.2) and (3.11) had the same notational issue, and
+    they have both been corrected.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item This notation has been adjusted throughout Section 3.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item Since the only derivatives that are required are functions
+    defined only on the boundary of the Janus particles, they are
+    computed with spectrally-accurate Fourier differentiation.
+
+  \item We have added the following sentence to the start of Section 3
+    \begin{quotation}
+      All derivatives are computed with spectrally-accurate Fourier
+      differentiation.
+    \end{quotation}
 \end{itemize}

### 2021-12-29 doc/reviews/ResponseToReviewer3.tex
working on revisions

@@
 distance should be $1000 \times R$. However, in the figure, it shows a
-migration distance about 4x R. The authors are suggested to double-check
-their model parameterization.}
+migration distance about $4 \times R$. The authors are suggested to
+double-check their model parameterization.}
 \begin{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item The typo with ``well-know" is corrected, but colored in red
+    since it was pointed out by Reviewer 1.
+
+  \item The manuscript now reads
+    \begin{quotation}
+      $\ldots$ a baseline JP vesicle $\ldots$
+    \end{quotation}
+
+  \item The typo with ``has" instead of ``have" is corrected, but
+    colored in red since it was pointed out by Reviewer 1.
+
+  \item We have read through the manuscript and made grammatical
+    changes.
+
 \end{itemize}

### 2021-12-29 doc/main_jfm.tex
working on revisions

@@
 \newcommand{\jump}[1]{[\![ #1 ]\!]}
+\newcommand{\ReviewerOne}[1]{\textcolor{red}{#1}}
+\newcommand{\ReviewerTwo}[1]{\textcolor{green}{#1}}
+\newcommand{\ReviewerThree}[1]{\textcolor{magenta}{#1}}
 
@@
 a Janus suspension under various flows. The JP vesicles in our
-simulations replicate  well-know vesicle hydrodynamics such as
-tank-treading and inter-leaflet slippage in a shear flow and migration
-in Poiseuille flow from continuum models. Furthermore we use the hybrid
-continuum model to investigate permeability and rupture of a bilayer
-membrane due to an imposed flow.  Finally, we compare a pair of
+simulations replicate  \ReviewerOne{well-known} vesicle hydrodynamics
+such as tank-treading and inter-leaflet slippage in a shear flow and
+migration in Poiseuille flow from continuum models. Furthermore we use
+the hybrid continuum model to investigate permeability and rupture of a
+bilayer membrane due to an imposed flow.  Finally, we compare a pair of
 interacting JP vesicles with a continuum model of a pair of vesicles.
@@
 $N$ points on each of the $N_b$ particles with a collocation method.
-Integrals that are smooth are computed with the spectrally-accurate
-trapezoid rule, and nearly-singular integrals, caused by close contact
-between two particles, are computed with a high-order
-interpolation-based quadrature rule (\cite{qua-bir2014}). After
-discretizing and applying quadrature, the resulting linear system is
-solved with matrix-free GMRES, and we guarantee that the number of GMRES
-iterations is mesh-independent by using second-kind BIEs.
+\ReviewerOne{All derivatives are computed with spectrally-accurate
+Fourier differentiation.} Integrals that are smooth are computed with
+the spectrally-accurate trapezoid rule, and nearly-singular integrals,
+caused by close contact between two particles, are computed with a
+high-order interpolation-based quadrature rule (\cite{qua-bir2014}).
+After discretizing and applying quadrature, the resulting linear system
+is solved with matrix-free GMRES, and we guarantee that the number of
+GMRES iterations is mesh-independent by using second-kind BIEs.
 
@@
 \subsection{HAP Boundary Integral Equation}
-Similar to our previous work (\cite{Fu20}), we represent the HAP as a
-double-layer potential
+Similar to our previous work (\cite{Fu20}), we represent the
+\ReviewerTwo{hydrophobic attraction potential (HAP)} as a double-layer
+potential
 \begin{align}
   \label{eq:HAP_DLP}
-  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
-    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
-    \quad \xx \in \Omega,
+  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
+    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \Omega,
 \end{align}
 where $K_0$ is the zeroth-order modified Bessel function of the first
-kind and the integral is taken in the sense of principle value whenever $\xx \in \partial \Omega$. 
-By requiring that the density function $\sigma$ satisfies the
-second-kind integral equation
+kind and the integral is taken in the sense of principle value whenever
+$\xx \in \partial \Omega$.  By requiring that the density function
+$\sigma$ satisfies the second-kind integral equation
 \begin{equation}
@@
   f(\xx) = \frac{1}{2}\sigma(\xx) + 
-    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
-    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
-    \quad \xx \in \bd\Omega,
+    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
+    \dif s_\yy, \quad \xx \in \bd\Omega,
 \end{equation}
@@
   \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
-    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
+    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
     \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
@@
     \frac{\rr \cdot \nnu}{|\rr|^2} \frac{\rr \otimes \rr}{|\rr|^2}
-    \eeta(\yy) \, \dif s_\yy,
+    \cdot \eeta(\yy) \, \dif s_\yy,
 \end{align}
@@
 \begin{align}
-  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
-    \frac{\rr \otimes \rr}{|\rr|^2}\right) \FF_i, \\
-  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
-\end{align}
-respectively, where $\rr = \xx - \aa_i$. The
-Stokeslet is torque-free and has force $\FF_i$ while the rotlet is
-force-free and has torque $T_i$. Therefore, the
-velocity~\eqref{eq:velocity} satisfies the total force~\eqref{eq:force}
-and torque~\eqref{eq:torque} conditions if the double-layer potential
-$\DD[\eeta]$ is force- and torque-free.  Matching the limit
-of~\eqref{eq:velocity} with the rigid body motion, and imposing that
-$\DD[\eeta]$ is force- and torque-free, the density function $\eeta$,
-translational velocity $\vv_i$, and angular velocity $\omega_i$ satisfy
+  \SS(\xx,\aa_i) \cdot \FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
+    \frac{\rr \otimes \rr}{|\rr|^2}\right) \cdot \FF_i, \\
+  \RR(\xx,\aa_i) T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
+\end{align}
+respectively, where $\rr = \xx - \aa_i$. The Stokeslet is torque-free
+and has force $\FF_i$ while the rotlet is force-free and has torque
+$T_i$. Therefore, the velocity~\eqref{eq:velocity} satisfies the total
+force~\eqref{eq:force} and torque~\eqref{eq:torque} conditions if the
+double-layer potential $\DD[\eeta]$ is force- and torque-free.  Matching
+the limit of~\eqref{eq:velocity} with the rigid body motion, and
+imposing that $\DD[\eeta]$ is force- and torque-free, the density
+function $\eeta$, translational velocity $\vv_i$, and angular velocity
+$\omega_i$ satisfy
 \begin{alignat}{3}
@@
     + \sum_{j=1}^{N_b} &
-    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
+    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),
     \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
@@
 \begin{align}
-  u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
-    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
-    \quad \xx \in \mathbb{R}^2.
+  u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \left(\pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
+    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \mathbb{R}^2.
 \end{align}
@@
   {\bf T} &=
-    \mathbf{S}(u_i,u_i)
-  +(\mathbf{S}(u_i,v_i)
-  +\mathbf{S}(v_i,u_i))
-  +\mathbf{S}(v_i,v_i) \\
+    \SS(u_i,u_i) +(\SS(u_i,v_i) +\SS(v_i,u_i)) +\SS(v_i,v_i) \\
   &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
@@
 \label{eq:Tsplit}
-\mathbf{S}(u,v)
-=  \gamma\rho^{-1} uv {\bf I} + \gamma\rho \nabla u \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla u \nabla v^T .
+\SS(u,v)
+=  \gamma\rho^{-1} uv {\bf I} + \gamma\rho \nabla u \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla u \nabla v^T.
 \end{equation}
@@
   \label{eq:prejump}
-  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \jump{{\bf T}_2  \nnu}  \, \dif s,\quad
-  T_i^{\mathrm{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \jump{{\bf T}_2 \nnu} \, \dif s.
+  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \jump{{\bf T}_2 \cdot \nnu}  \, \dif s,\quad
+  T_i^{\mathrm{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
+  \jump{{\bf T}_2 \cdot \nnu} \, \dif s.
 \end{align}
@@
 \begin{align}
-  \FF_i = \int_{\Gamma_i} {\bf T}_1\nnu + 
-    {\bf T}_2\nnu + {\bf T}_3\nnu\,\dif s.
+  \FF_i = \int_{\Gamma_i} \left({\bf T}_1 \cdot \nnu + 
+    {\bf T}_2 \cdot \nnu + {\bf T}_3 \cdot \nnu \right) \,\dif s.
 \end{align}
@@
 \begin{align}
-  \int_{\Gamma_i}  {\bf T}_1\nnu \,\dif s
+  \int_{\Gamma_i}  {\bf T}_1 \cdot \nnu \,\dif s
   = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,\dif \xx = \mathbf{0},\quad
-    \int_{\Gamma_i}  {\bf T}_3 \nnu\,\dif s
+    \int_{\Gamma_i}  {\bf T}_3 \cdot \nnu\,\dif s
   = \int_{U_i} \nabla \cdot {\bf T}_3 \,\dif \xx = \mathbf{0}.
@@
   \mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \, \dif \xx = -\int_{\Gamma_i}  
-    ({\bf T}_2 \nnu)^-\,\dif s,
+    ({\bf T}_2 \cdot \nnu)^-\,\dif s,
 \end{align}
@@
 \begin{align*}
-  \jump{{\bf T}_2\nnu}   &= \jump{\mathbf{S}(u_i,v_i)\nnu  +\mathbf{S}(v_i,u_i)\nnu} \\
-  &= \jump{( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
-- 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla u_i^T)  \nnu}\\
+  \jump{{\bf T}_2 \cdot \nnu}   &= \jump{\SS(u_i,v_i) \cdot \nnu +
+    \SS(v_i,u_i) \cdot \nnu} \\
+  &= \Big[\!\Big[ \left( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
+- 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla
+  u_i^T\right) \cdot \nnu \Big]\!\Big] \\
+%  &= \jump{\left( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
+%- 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla
+%  u_i^T\right) \cdot \nnu}\\
 &= 2\gamma\rho^{-1} \sigma v_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dv_i }{ds} \nnu
@@
 To reach consistent simulation outcomes, we first solve for a baseline
-JP vesicles that is suitably close to equilibrium. We start with an
-assumed configuration of $N=58$ JP in the form of two, circular,
-apposing monolayers of about $8$ nm in radius. The norms of the translational and
-rotational velocities vanish exponentially with an approximate decay
-rate $\sim 4.6$ $\upmu$s$^{-1}$. An equilibrium configuration is
-therefore rapidly attained. This equilibrium configuration serves as the
-initial data in the subsequent background flow simulations.
+JP \ReviewerThree{vesicle} that is suitably close to equilibrium. We
+start with an assumed configuration of $N=58$ JP in the form of two,
+circular, apposing monolayers of about $8$ nm in radius. The norms of
+the translational and rotational velocities vanish exponentially with an
+approximate decay rate $\sim 4.6$ $\upmu$s$^{-1}$. An equilibrium
+configuration is therefore rapidly attained. This equilibrium
+configuration serves as the initial data in the subsequent background
+flow simulations.
 
@@
 \end{figure}
-Finally, we show that the JP vesicle behaves as an extensible, permeable
-membrane. Figures~\ref{figure2}b shows an initial, non-equilibrium JP
+Finally, we show that the JP vesicle behaves as a permeable membrane and the inextensibility comes
+about due to a large stretching modulus.
+%an extensible, permeable membrane. 
+Figures~\ref{figure2}b shows an initial, non-equilibrium JP
 vesicle suspended in a quiescent flow $\uu_{\infty} = 0$. The color map
@@
 What could be the source of this drop in pressure? In membrane
-continuum  mechanics, changes in surface area give rise to a membrane tension
+continuum  mechanics, small changes in surface area give rise to a membrane tension
 $\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the membrane surface area
@@
 where $L$ and $L_0$ are the vesicle arc length and resting length,
-respectively. Moreover, stretched, circular vesicles has a Laplace pressure 
+respectively. Moreover, stretched, circular vesicles \ReviewerOne{have}
+a Laplace pressure 
 \begin{align}
@@
 agreement with the experimentally obtained area moduli of lipid bilayer. 
+%
+The reason the tank-treading vesicle appears inextensible ($L$ is more or less constant in Figure~\ref{figure4}c) is because the modulus $K_A$ is large.
+%
 To evaluate how changes to particle size lead to different

### 2021-12-29 doc/main_jfm.tex
working on revisions

@@
 \end{align}
-where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and rotlets
-centred at $\aa_i$ are
+where $\rr = \xx - \yy$. The Stokeslet and rotlets centred at $\aa_i$
+are
 \begin{align}
@@
   \label{eq:uidef}
-  v_i(\xx) = u(\xx) - u_i(\xx),
+  w_i(\xx) = u(\xx) - u_i(\xx),
 \end{align}
@@
 \end{align}
-That is, $v_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
-with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $v_i$, we prove
+That is, $w_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
+with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $w_i$, we prove
 \begin{theorem}
@@
   \label{eq:jumpstress1}
-  \JJ_{i} = 2\gamma\rho^{-1} \sigma v_i \nnu + 
-    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{ds} \nnu -
-    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{d\nnu} \ttau.
+  \JJ_{i} = 2\gamma\rho^{-1} \sigma w_i \nnu + 
+    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{ds} \nnu -
+    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{d\nnu} \ttau.
 \end{align}
@@
 using~\eqref{eq:hydrophobicAttraction} is that the components $\sigma$,
-$v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ of $\JJ_i$ are smooth
+$w_i$, $\frac{d\sigma}{ds}$, and $\frac{dw_i}{ds}$ of $\JJ_i$ are smooth
 functions, whereas the components of \eqref{eq:stress} are singular
@@
   {\bf T} &=
-    \SS(u_i,u_i) +(\SS(u_i,v_i) +\SS(v_i,u_i)) +\SS(v_i,v_i) \\
+    \SS(u_i,u_i) +(\SS(u_i,w_i) +\SS(w_i,u_i)) +\SS(w_i,w_i) \\
   &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
@@
 \end{equation}
-Using the fact that $u$,  $u_i$, and $v_i$ solve the screened Laplace
+Using the fact that $u$,  $u_i$, and $w_i$ solve the screened Laplace
 equation~\eqref{eq:SL}, and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1,
@@
 smooth and $\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n
-\setminus U_i$. Similarly, $v_i = u - u_i$ is smooth and $\nabla \cdot
+\setminus U_i$. Similarly, $w_i = u - u_i$ is smooth and $\nabla \cdot
 {\bf T}_3 = \mathbf{0}$ in $U_i$. By the divergence theorem,  
@@
 \end{align}
-Finally, $u_i$ and $v_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
+Finally, $u_i$ and $w_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
 \begin{align}
@@
 \jump{u_i} = \sigma, \quad
-\jump{v_i} = 0, \quad
+\jump{w_i} = 0, \quad
 \jump{\nabla u_i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
-\jump{\nabla v_i} = \mathbf{0},
+\jump{\nabla w_i} = \mathbf{0},
 \end{equation}
@@
 \begin{align*}
-  \jump{{\bf T}_2 \cdot \nnu}   &= \jump{\SS(u_i,v_i) \cdot \nnu +
-    \SS(v_i,u_i) \cdot \nnu} \\
-  &= \Big[\!\Big[ \left( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
-- 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla
+  \jump{{\bf T}_2 \cdot \nnu}   &= \jump{\SS(u_i,w_i) \cdot \nnu +
+    \SS(w_i,u_i) \cdot \nnu} \\
+  &= \Big[\!\Big[ \left( 2\gamma\rho^{-1} u_i w_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla w_i \mathbf{I} 
+- 2\gamma\rho \nabla u_i  \nabla w_i^T - 2\gamma\rho \nabla w_i \nabla
   u_i^T\right) \cdot \nnu \Big]\!\Big] \\
@@
 %  u_i^T\right) \cdot \nnu}\\
-&= 2\gamma\rho^{-1} \sigma v_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dv_i }{ds} \nnu
-- 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dv_i }{d\nu} \ttau = \JJ_i.
+&= 2\gamma\rho^{-1} \sigma w_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dw_i }{ds} \nnu
+- 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dw_i }{d\nnu} \ttau = \JJ_i.
 \end{align*}
+\todo[inline]{RR: Can you make sure the last line is correct? There was
+an unbolded $\nu$ which I changed to a bolded $\nnu$.}
 Combining this with~\eqref{eq:prejump} gives~\eqref{eq:recipforcetorque}
@@
 \begin{equation}
-U = \frac{1}{L}\int_{C_M}u_+(\mathbf{x})(1 - \delta \kappa) - v_-(\mathbf{x})(1 +  \delta \kappa) \, ds,
+  U = \frac{1}{L}\int_{C_M}\left(u_+(\mathbf{x})(1 - \delta \kappa) -
+  u_-(\mathbf{x})(1 +  \delta \kappa)\right) \, ds,
 \end{equation}

### 2022-01-11 doc/reviews/ResponseToReviewer2.tex
working on revisions

@@
 \begin{itemize}
-  \item Change 1 
+  \item Thank you for noticing this oversight. The definition of HAP has
+    been added at its first occurrence in Section 3.1. 
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item We had used $\rho$ to denote the distance between source and
+    target points in one of the layer potentials. This has been removed.
+
+  \item We now use $\rho$ to denote the HAP decay length and $\rho_0$ to
+    denote the cutoff for the repulsion force.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item We now reserve $\boldsymbol{\nu}$ for the normal vector and
+    $w_i$ denote the scalar what we previously defined to be $\nu_i$.
 \end{itemize}

### 2022-01-11 doc/main_jfm.tex
reworked intro to section 4

@@
 \begin{alignat}{3}
+\label{eq:stokes}
   -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
@@
 \right)$ is the hydrodynamic stress tensor (pressure tensor) and
-$\nnu_i$ is the particle outward normal. The process of finding the
+$\nnu$ is the particle outward normal. The process of finding the
 translational and angular velocities given the forces and torques is
@@
 are
-\begin{align}
+\begin{equation}
+\label{eq:total_forces}
   \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
@@
   i=1,\ldots,N_b.
-\end{align}
+\end{equation}
 
@@
   \label{eq:mobility1}
-  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
+  \int_{\Gamma_i} \eeta \cdot \nnu \, \dif s &= {\bf 0}, 
   &&i = 1,\ldots,N_b, \\
   \label{eq:mobility2}
-  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu_i \, \dif s &= 0,
+  \int_{\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu \, \dif s &= 0,
   &&i = 1,\ldots,N_b.
@@
 \begin{align}
-  \mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \, \dif \xx = -\int_{\Gamma_i}  
+  \mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \, \dif \xx = \int_{\Gamma_i}  
     ({\bf T}_2 \cdot \nnu)^-\,\dif s,
@@
 Combining the above gives the first equation in \eqref{eq:prejump}.
-The argument for the second equation in \eqref{eq:prejump} is identical. 
+The derivation for the second equation in \eqref{eq:prejump} is identical. 
 \end{proof}
@@
 \end{align*}
-\todo[inline]{RR: Can you make sure the last line is correct? There was
-an unbolded $\nu$ which I changed to a bolded $\nnu$.}
+%\todo[inline]{RR: Can you make sure the last line is correct? There was
+%an unbolded $\nu$ which I changed to a bolded $\nnu$.} RJR -> Correct. Thank you.
 Combining this with~\eqref{eq:prejump} gives~\eqref{eq:recipforcetorque}
@@
 \subsection{Model Parameters}
-\cite{Fu20} studied physical quantities for static JP vesicles for
-various particle shapes. In the present study, we fix the particle shape
-and vary the background flows. Specifically, the particles are circular
-disks with diameter $l_0 = 2.5$~nm. The boundary
-conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
+\cite{Fu20} studied physical quantities for static JP vesicles. 
+In the present work, we study JP vesicles in various background flows.
+We also perform parametric studies of effective properties of the JP vesicles 
+as a function of particle size and interaction strength.
+An analysis of the relationship between particle shape on effective properties is beyond 
+the scope of the current paper.
+
+The particles are circular disks with centres 
+$\aa_i$ and unit-length directors $\dd_i$ (Figure \ref{fig:figure0}(a)).
+The simulations use the reference length $l_0 = 2.5$~nm representing the
+thickness of a lipid monolayer.
+The boundary conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
 \theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
-$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle centre
-and director respectively. The particle diameter is the thickness of
-monolayers and the director points in the direction of the hydrophobic
-side of the JP.
-
-We use $\rho = 2 l_0$ for decay length, $\rho_0 = 0.2l_0$ for repulsion
-length, $M=4.0$~$k_BT$ for repulsion strength, $\gamma = \text{4.1 pN
-nm}^{-1}$ for interfacial tension, and $\mu = \text{1 cP} = \text{1 pN
-ns nm}^{-2}$ for viscosity of room-temperature water. We
-nondimensionalize the problem through the change of variables 
+$\dd_i$.
+We nondimensionalize the PDE systems 
+\eqref{eq:stokes}-\eqref{eq:total_forces}
+problem through the change of variables 
 %\begin{equation}
@@
 The numerical time step size is $\Delta t=0.2$.
+
+The base-case is a single JP vesicle consisting of $N_b = 58$ particles
+with $c = 0.5 l_0$ for particle radius, $\rho = 2 l_0$ for decay length, $\rho_0 = 0.2l_0$ for repulsion
+length, $M=4.0$~$k_BT$ for repulsion strength, $\gamma = \text{4.1 pN
+nm}^{-1}$ for interfacial tension.  The parameter $\mu = \text{1 cP} = \text{1 pN
+ns nm}^{-2}$ is viscosity of room-temperature water.
 
@@
 flow simulations.
+
+For a single JP vesicle, we consider background flows for a shear flow 
+(Section \ref{sec:ves_in_shear}), 
+a parabolic flow (Section \ref{sec:ves_in_parabolic}),
+and a quiescent flow (Section \ref{sec:ves_in_parabolic}). 
+In addition to observing the familiar tank-treading motion, the shear
+flow studies yield a friction coefficient for inter-monolayer slip 
+and a critical rupture shear rate.  Permeability coefficients and 
+stretching moduli arise from analyzing stretched JP vesicles in the 
+quiescent background flow case.
 
@@
 \subsubsection{Vesicle in a Parabolic Flow}
+\label{sec:ves_in_parabolic}
 Finally, we consider the parabolic background flow
@@
 \subsection{Stretching and Permeability}
+\label{sec:ves_in_quiescent}
 \begin{figure}

### 2022-02-08 doc/Supplementary.tex
adding movie captions

\thispagestyle{empty}

\newpage
{\Large \bf

  \noindent Supplementary Material\\

  \noindent 
  Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential}\\

\noindent 
Szu-Pei Fu$^{1,*},$ 
Bryan Quaife$^{2},$ 
Rolf J. Ryham$^{1},$ 
Y.-N. Young$^{3},$
\\

\noindent
$^{1}$Fordham University, Department of Mathematics,  Bronx, NY, USA

\noindent
$^{2}$Department of Scientific Computing, Florida State University, Tallahassee, Florida 32306, USA

\noindent
$^{3}$Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, NJ  07102 USA
\\

\noindent $^*$Corresponding author. Address: Fordham University, Department of Mathematics, 441 E. Fordham Rd, Bronx, NY 10458. email: \text{sfu17@fordham.edu}

\setcounter{page}{1}

\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}

\setcounter{equation}{0}
\renewcommand{\theequation}{S\arabic{equation}}

\setcounter{section}{0}
\renewcommand{\thesection}{S\arabic{section}}

%-----ellipse repulsion--------------------

%\Phi_{\mathrm{rep}}

\sloppy
\section{Movie Captions}\mbox{} \\

\noindent
{\bf Movie S1. Relaxation} There are 58 circular particles with radius 0.5 that form a self-enclosed bilayer structure. The simulation result shows the vesicle relaxation and the fluid pressure inside the JP vesicle decreases to 0 after a period of time.
The color field from blue to red shows the magnitude of fluid pressure and the range from 0 to 0.1. All dark blue dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
This movies includes a total 5000 time steps where the time step is $\Delta t=0.2$\\

\noindent
{\bf Movie S2. Single Vesicle Suspended in a Shear Flow} 
We adopt the relaxed configuration and place the JP vesicle in the shear flow. The simulation result shows a tank-treading motion when the shear rate is $\chi=0.005$.
The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$\\

\noindent
{\bf Movie S3. Inter-leaflet Sliding} 
Using the same setup demonstrated in Movie S2, we show the simulation result for 
inter-monolayer slip by tracking a pair of particles (blue and yellow). After $t=4000$, 
the yellow particle in the outer leaflet surpasses the blue particle in the inner leaflet by the distance about 1 particle diameter.
This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$\\

\noindent
{\bf Movie S4. Vesicle Rupture} 
The numerical results show that the JP vesicle starts to have rupture phase at the shear rate $\chi=0.0655$. The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion. This movies includes a total 3000 time steps where the time step is $\Delta t=0.2$\\

\noindent
{\bf Movie S5. Two Vesicles Suspended in a Shear Flow} 
There are two relaxed JP vesicles suspended in a shear flow. The two centroids are at coordinates $(-25,0)$ and $(25,0)$ in nm. The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion. This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$\\

\noindent
{\bf Movie S6. Single Vesicle Suspended in an Extensional Flow} 
There are two relaxed JP vesicles suspended in a shear flow.The centroid of the left JP vesicle is 0.25 nm above the $x$-axis and the right JP vesicle is 0.25 nm below the $x$-axis. The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
This movies includes a total 6000 time steps where the time step is $\Delta t=0.2$\\

%%%\end{document}

### 2022-02-09 doc/Supplementary.tex
updates

@@
 All dark blue dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-This movies includes a total 5000 time steps where the time step is $\Delta t=0.2$\\
+This movies includes a total 5000 time steps where the time step is $\Delta t=0.2$.\\
 
@@
 All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$\\
+This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\
 
@@
 the yellow particle in the outer leaflet surpasses the blue particle in the inner leaflet by the distance about 1 particle diameter.
-This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$\\
+This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\
 
@@
 All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-This movies includes a total 3000 time steps where the time step is $\Delta t=0.2$\\
+This movies includes a total 3000 time steps where the time step is $\Delta t=0.2$.\\
 
@@
 All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-This movies includes a total 6000 time steps where the time step is $\Delta t=0.2$\\
+This movies includes a total 6000 time steps where the time step is $\Delta t=0.2$.\\
 

### 2022-02-09 doc/main_jfm.tex
adding movie captions
update table 1
working on revision

@@
 \usepackage{todonotes}
+
 %
@@
 
+%original table
+%\begin{table}
+%\caption{Friction Coefficients}
+%\centering
+%\begin{tabular}{c c c c c c c c }
+% $\dot\gamma$  (ns$^{-1}$) & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
+%\hline                    
+%$b$ (pN ns nm$^{-3}$)    & 0.43 & 1.19 &   0.42  & 0.69 &   0.97  &   0.80  &  1.07 \\ 
+%\hline    
+%\end{tabular} 
+%\label{table1}
+%\end{table}
+
+%updated table
 \begin{table}
-\caption{Friction Coefficients}
+\caption{Friction Coefficients $b$ (pN ns nm$^{-3}$) \\
+}
 \centering
-\begin{tabular}{c c c c c c c c }
- $\dot\gamma$  (ns$^{-1}$) & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
-\hline                    
-%$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
-%$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
-%$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
-%$b$ (pN$\cdot$ns nm$^{-3}$)    & 0.22 & 0.87*  & 0.22 &0.21 & 1.29* & 0.31 & 0.30\\ 
-$b$ (pN ns nm$^{-3}$)    & 0.43 & 1.19 &   0.42  & 0.69 &   0.97  &   0.80  &  1.07 \\ 
-\hline    
+\begin{tabular}{c c c c c c c c c }
+& & & & $\dot\gamma$  (ns$^{-1}$) & & & &\\
+\cline{2-8}\\
+ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  & Average\\
+\cline{1-8}\\
+$N_b=53$  & 0.50  & 0.51  &  0.44 & 0.52  & 0.45 &  0.57   &  0.62 & 0.52  \\ 
+$N_b=56$ & 0.54 & 0.41 & 0.35  & 0.37 & 0.43 & 0.76  & 0.70 & 0.51\\ 
+$N_b=58$   & 0.42 & 0.63 & 0.50   & 0.40  & 0.48  & 0.53 & 0.55 & 0.50 \\   % new
+$N_b=61$  & 0.22 & 0.36 & 0.41   & 0.45  & 0.45 & 0.44   & 0.44 & 0.40\\ 
 \end{tabular} 
@@
 
-Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
-over a range of shear rates
+%Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
+\ReviewerOne{Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the default number of particles is $N_b = 58$.
+With the fixed total length of the JP vesicle, we change parameters related to the length scale, for instances, $\rho$, $\rho_0$, and the radius of particles.
+With $\{-10\%,-5\%, 5\%\}$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{53,56,58\}$, respectively. }
+%
+Over a range of shear rates
 which is in good quantitative agreement with values previously reported in the literature.
@@
 
+% table 2
+
+\begin{table}
+\caption{Stretching Moduli and Permeabilities}
+\centering
+\begin{tabular}{ c c c c c c c }
+ radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (k_BT)$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
+\hline      \hline 
+ 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
+%
+ 0.475 & 1.9  &   0.475  & 4.0 &  4.1   & 184$\pm5$  &  0.0283 \\ 
+%
+ 0.45 & 1.8  &   0.45  & 4.0   &  4.1   & 189$\pm6$  &  0.0252  \\ 
+%
+ 0.5 & 2.0  &   0.5  & 4.2   &  4.31  & 185$\pm5$  &  0.0292  \\ 
+%
+ 0.5 & 2.0  &   0.5  & 4.4   &  4.51  & 195$\pm5$  &  0.0294 \\ 
+\end{tabular} 
+\label{table2}
+\end{table}
+
 Figure~\ref{figure2}c plots the data for the pressure jump $\Delta p$
@@
 
+% Supplementary Materials
+\input{Supplementary}
+
 %\bibliographystyle{jfm}

### 2022-02-09 doc/reviews/ResponseToReviewer1.tex
working on revisions

@@
 \begin{itemize}
-  \item Change 1
+  \item Response to Summary
   \begin{quotation}
     \noindent
-    Can put verbatim change in this environment.
+	We thank the Reviewer for the assessmnet of our manuscript submission. In response
+to the comments, we have undertaken a major revision in including parametric studies and quantitative comparisons between models. We perforemed a number of simulations 
+in studies of inter-monolayer friction coefficients and an additional numerical investigation 
+of permeabilities. We have ensured that all figures are conneted with the corresponding content.
+
+%    Can put verbatim change in this environment.
   \end{quotation}
@@
 \begin{itemize}
-  \item Change 1 
+  \item This comment encouraged us to have more convergence studies in the choices of model parameters. We made a worthwhile effort to perform a large number of simulations. 
+We revised Table 1 and added Table 2 to account for effective properties of vesicles with different size of particles.
+We agree with the Reviewer that the particle/vesicle shape is complex with the setup therefore we adopted small changes in particle sizes and reported all the reults.
+
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item We agree with the Reviewer that we briefly illustrated the capability of simulating membrane rupture via the proposed model and numerical algorithm in the first submission of the manuscript.
+We further performed a series of study to find the critical shear rate for the appearance of membrane rupture and the corresopnding movie is added as a supplementary material.
+We also included the description in the section of membrane rupture.
 \end{itemize}
@@
 (e.g.~the membrane rupture).}
+
 \begin{itemize}
-  \item Change 1 
+  \item 
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item This typo is fixed.
 \end{itemize}
@@
 \noindent
-\comment{Line 393: The reference to panel ``Figure 7c" seems to be a typo. Same
-for ``Figures 7c and 7d" on line 394, I think it should be ``Figures 7b
-and 7c".}
+\comment{Line 393: The reference to panel ``Figure 7c" seems to be a
+typo. Same for ``Figures 7c and 7d" on line 394, I think it should be
+``Figures 7b and 7c".}
 \begin{itemize}

### 2022-02-09 doc/main_jfm.tex
working on revision

@@
 With the fixed total length of the JP vesicle, we change parameters related to the length scale, for instances, $\rho$, $\rho_0$, and the radius of particles.
-With $\{-10\%,-5\%, 5\%\}$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{53,56,58\}$, respectively. }
+With $-5\%$, $5\%$, and $10\%$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{61,56,53\}$, respectively. }
 %
@@
 off by the flow (Figure~\ref{figure8}d). 
+%
+\ReviewerOne{An emperical numerical study has shown that the critical shear rate for a complete membrane rupture is $\chi=0.0655$.
+Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.}
 
@@
 
-% table 2
-
-\begin{table}
-\caption{Stretching Moduli and Permeabilities}
-\centering
-\begin{tabular}{ c c c c c c c }
- radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (k_BT)$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
-\hline      \hline 
- 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
-%
- 0.475 & 1.9  &   0.475  & 4.0 &  4.1   & 184$\pm5$  &  0.0283 \\ 
-%
- 0.45 & 1.8  &   0.45  & 4.0   &  4.1   & 189$\pm6$  &  0.0252  \\ 
-%
- 0.5 & 2.0  &   0.5  & 4.2   &  4.31  & 185$\pm5$  &  0.0292  \\ 
-%
- 0.5 & 2.0  &   0.5  & 4.4   &  4.51  & 195$\pm5$  &  0.0294 \\ 
-\end{tabular} 
-\label{table2}
-\end{table}
-
 Figure~\ref{figure2}c plots the data for the pressure jump $\Delta p$
@@
 quantitative agreement with the JP data (Figure~\ref{figure2}f).
+
+% table 2
+
+\begin{table}
+\caption{Stretching Moduli and Permeabilities}
+\centering
+\begin{tabular}{ c c c c c c c }
+ radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (k_BT)$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
+\hline      \hline 
+ 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
+%
+ 0.475 & 1.9  &   0.475  & 4.0 &  4.1   & 184$\pm5$  &  0.0283 \\ 
+%
+ 0.45 & 1.8  &   0.45  & 4.0   &  4.1   & 189$\pm6$  &  0.0252  \\ 
+%
+ 0.5 & 2.0  &   0.5  & 4.2   &  4.31  & 185$\pm5$  &  0.0292  \\ 
+%
+ 0.5 & 2.0  &   0.5  & 4.4   &  4.51  & 195$\pm5$  &  0.0294 \\ 
+\end{tabular} 
+\label{table2}
+\end{table}
+%
+
+\ReviewerOne{Table~\ref{table2} provides the results of stretching moduli $K_A$ and permeabilities $P$ for various cases.
+The default setup is shown in the first row.
+The next two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$.
+One can observe that the constant $K_A$ increases
+and $P$ decreases as size of particles decreases. 
+The last two rows demonstrate the results when the force related parameters $\gamma$ and $M$ are adjusted by 5$\%$ and 10$\%$.
+The quantities examined for these two cases show that $K_A$ increases and $P$ remains constant as inter-particle interaction strength increases.
+As expected by the fact that the permeability is dependent of the particle size where the gap between each adjacent JP pair is controlled by the size of JP particles.
+However, the detailed correlation between all model parameters will be explored as
+a direction of future work.}
 

### 2022-02-09 doc/reviews/ResponseToReviewer1.tex

@@
 \begin{itemize}
-  \item 
+  \item We thank the Reviewer to point this out. There is a significant difference between 
+the proposed model in the manuscript and other continuum models in literatures. For example, refer to \emph{Rahimian, et al., J. Comput. Phys., 2011}, the 
+provided time scale is $\tau = \mu R_0^3/\kappa_B$ where $\mu$ the fluid viscosity and $\kappa_B$ the bending modulus.
+Since the bending modulus does not play any roles in the proposed model, we then scaled time unit with a realistic characteristic time ns.
+With the use of the detailed scaling laws described in section 4.1, we aim to have a comparable
+numerical results against the experiments.
 \end{itemize}

### 2022-02-10 doc/reviews/ResponseToReviewer3.tex
referee 3

@@
 \noindent
-\comment{In section 2.2, the authors defined a repulsion force with an
+\comment{{\bf 1.} In section 2.2, the authors defined a repulsion force with an
 empirical formula to prevent particle collisions. However, there is no
@@
 \begin{itemize}
-  \item Change 1 
+  \item Response: The repulsive potential we used to prevent overlap of Janus particles is the repulsive Morse potential based on the electrostatic repulsive potential between two negatively (or positively) charged particles immersed in a medium of low electrolyte concentration so that there is a well-defined zeta potential on the charged particle (Coakley {\sl et al.}, 1999, Biophys.
+J).
+This repulsive potential has been approximated by the short-range repulsive Lennard-Jones potential (Flormann {\sl et al.}, 2017, Sci.
+Reports), which has been adopted by Quaife and Young to study the interaction between two membranes in a viscous solvent in Quaife, Veerapaneni and Young, 2019, Phys.
+Rev.
+Fluids, where Quaife {\sl et al.} showed that the lubrication hydrodynamics (draining of fluid between two membrane) is well captured and the scaling of lubrication thin film is recovered.
+
+This is evidence that the lubrication hydrodynamics of the thin film between two particles under the repulsive Morse potential is well captured  if the flow velocity can be accurately calculated in the boundary integral simulations when two particles are sufficiently close to each other and the short-range repulsion is the dominant force.
+
+In this work we use similar techniques for solving the integral equations when some boundaries are quite close to each other.
+As the repulsive More potential works well to prevent overlapping of particles (provided the time step size is sufficiently small), our previous results in Quaife, Veerapaneni and Young, 2019, Phys.
+Rev.
+Fluids gives us confidence in the accuracy of the fluid flow in the thin space between the particles.
+
+\item Change: We added a short paragraph to describe our methodology to capture the lubrication flow in the space between particles in close vicinity of each other in page, between lines \$\$\$ and \$\$\$.
+
 \end{itemize}

### 2022-02-10 doc/reviews/ResponseToReviewer3.tex
reviewer 3

@@
 \noindent
-\comment{Fig.~3 plots the time evolution of the reduced area in (a) and
+\comment{{\bf 2.} Fig.~3 plots the time evolution of the reduced area in (a) and
 the excess length of the bilayer structure in (b). Both show obvious
@@
 \noindent
-\comment{Fig.~6 illustrates the migration process of a JP vesicle in a
+\comment{{\bf 3.} Fig.~6 illustrates the migration process of a JP vesicle in a
 parabolic flow, where the moving velocity is 8 nm/ns and the time frame
@@
 \noindent
-\comment{In Fig.~10, the significant discontinuities in streamlines
+\comment{{\bf 4.} In Fig.~10, the significant discontinuities in streamlines
 across the surface of vesicles are observed, while in most other cases

### 2022-02-10 doc/reviews/ResponseToReviewer1.tex
Peter working on revision

@@
 \begin{itemize}
-  \item Response to Summary
-  \begin{quotation}
-    \noindent
-	We thank the Reviewer for the assessmnet of our manuscript submission. In response
+  \item {\bf Response to Summary}: 	We thank the Reviewer for the assessmnet of our manuscript submission. In response
 to the comments, we have undertaken a major revision in including parametric studies and quantitative comparisons between models. We perforemed a number of simulations 
@@
 of permeabilities. We have ensured that all figures are conneted with the corresponding content. 
-
+  \begin{quotation}
+%    \noindent
 %    Can put verbatim change in this environment.
@@
 \begin{itemize}
-  \item Change 1 
+  \item We followed the suggestion given by the Reviewer that a summary about what to solve throughout the entire algorithm is provided at the end of Section 3.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item We thank the Review for having this meaningful comment and we agree that changing all the figure 
+to colorblind friendly colormap is insightful. We would love to make this change once the manuscript is accepted.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item We deleted the sentence ``$L$ is the arc length''.
 \end{itemize}

### 2022-02-10 doc/main_jfm.tex
Peter working on revision

@@
   eventually arrange along inner and outer leaflets. In panel (c), $C_M$
-  is the midplane curve, $A$ is the enclosed area, and $L$ is the arc
-  length. Initially stretched vesicles relax to equilibrium with fluid
+  is the midplane curve, \ReviewerOne{and} $A$ is the enclosed area\ReviewerOne{.}
+  %, and $L$ is the arc length. 
+  Initially stretched vesicles relax to equilibrium with fluid
   flow across the bilayer. The study considers a single vesicle in
@@
 
+% what we solve for?
+\ReviewerOne{To summarize, the proposed algorithm aims to obtain the JP velocities ${\bf v}_i$ and $\omega_i$. 
+After calculating the imposed forces $\FF_i$ and torques $T_i$, 
+two density functions $\sigma$ and  $\eeta$ are solved in the second-kind integral equations involving the HAP~\eqref{eq:screenedSKIE} and the mobility problem~\eqref{eq:SKIE}-\eqref{eq:mobility2} via GMRES.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
-Over a range of shear rates
-which is in good quantitative agreement with values previously reported in the literature.
+\ReviewerOne{There is no clear trend shown in Table~\ref{table1} but these values of $b$ are}
+%over a range of shear rates which is 
+in good quantitative agreement with values previously reported in the literature.
 Atomistic studies have also considered inter-monolayer slip in lipid bilayers. 

### 2022-02-11 doc/main_jfm.tex
Peter working on revision

@@
 
-\newpage
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{Figure13_Wrapper.pdf}
+  \caption{\label{figure13} Comparisons between the proposed model and a conitnuum model in 
+  two JP vesicle simulations. 
+  $d_{1,2}$ is the distance between two centroids of JP vesicles. The thick curves plot the trajectories
+  of $d_{1,2}$ generated by the continuum model and the thin curves are computed from using
+  the proposed model.}
+\end{figure}
+
+\ReviewerOne{Since the behavior of the suspended JP vesicles has similarities to the numerical 
+results generated by using the algorithm in \cite{qua-vee-you2019} (refer to all figure insets in 
+Figure~\ref{figure10} and Figure~\ref{figure12}). Figure~\ref{figure13} shows trajectory 
+comparisons between the proposed model and the continuum modeling for both shear flow and
+extensional flow cases in two vesicle simulations. The quantity $d_{1,2}$ represents the distance
+between two centroids of JP vesicles. The centroid positions are identical for both models and the
+geometry in the continuum model is created along the midplane locations of JP vesicles and the initial
+reduced area is matched. Panel (a) shows that the results of continuum model does not have a 
+periodic motion and two vesicles flow apart after 1.5 $\mu$s. Panel (b) shows that the results of
+continuum model has similar trend of dynamics with one in the proposed model.}
+
+%\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-02-11 doc/main_jfm.tex
Peter working on revision

@@
 The quantities examined for these two cases show that $K_A$ increases and $P$ remains constant as inter-particle interaction strength increases.
-As expected by the fact that the permeability is dependent of the particle size where the gap between each adjacent JP pair is controlled by the size of JP particles.
+As expected by the fact that the permeability is dependent of the particle size where the gap between each adjacent JP pair is controlled by the size of JP.
 However, the detailed correlation between all model parameters will be explored as

### 2022-02-11 doc/main_jfm.tex
Peter working on revision

@@
 pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
+%
 Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
-\begin{align}
-  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
+\ReviewerOne{the no-slip boundary condition}
+\begin{align}
+  \ReviewerOne{\uu}(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
     \xx \in \Gamma_i,
@@
 angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
-\rangle$. Therefore, the no-slip boundary condition on each particle is
-\begin{align}
-\label{eq:rigid_bc}
-  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
-    \xx \in \Gamma_i.
-\end{align}
+\rangle$.
+%Therefore, the no-slip boundary condition on each particle is
+%
+%
+%\begin{align}
+%\label{eq:rigid_bc}
+%  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
+%    \xx \in \Gamma_i.
+%\end{align}
+%
+%
 To determine the translational and angular velocities of each particle,

### 2022-02-11 doc/reviews/ResponseToReviewer1.tex
Peter working on revision

@@
 \begin{itemize}
-  \item Change 1 
+  \item We deleted the redundant equation (2.5) mentioned by the Reviewer.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item We thank the Review for the comment and we moved the original Section 2.3 {\it Time Marching} at the end of Section 3 combining the change based on the comment previously addressed about what to solve for in the proposed algorithm.
 \end{itemize}

### 2022-02-11 doc/main_jfm.tex
Peter working on revision

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Time Marching}
-By solving the mobility problem, we obtain translational and angular
-velocities of the $N_b$-body system. 
-A second-order Adams-Bashforth
-scheme updates the particle positions and orientations. By including the
-repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
-when using a relatively large time step.
+
+%%%% moved to new section 3.4
+
+%\subsection{Time Marching}
+%By solving the mobility problem, we obtain translational and angular
+%velocities of the $N_b$-body system. 
+%A second-order Adams-Bashforth
+%scheme updates the particle positions and orientations. By including the
+%repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
+%when using a relatively large time step.
 
@@
 % what we solve for?
-\ReviewerOne{To summarize, the proposed algorithm aims to obtain the JP velocities ${\bf v}_i$ and $\omega_i$. 
+\ReviewerOne{
+\subsection{Time Marching}
+To summarize, the proposed algorithm aims to obtain the JP velocities ${\bf v}_i$ and $\omega_i$. 
 After calculating the imposed forces $\FF_i$ and torques $T_i$, 
-two density functions $\sigma$ and  $\eeta$ are solved in the second-kind integral equations involving the HAP~\eqref{eq:screenedSKIE} and the mobility problem~\eqref{eq:SKIE}-\eqref{eq:mobility2} via GMRES.}
+two density functions $\sigma$ and  $\eeta$ are solved in the second-kind integral equations involving the HAP~\eqref{eq:screenedSKIE} and the mobility problem~\eqref{eq:SKIE}-\eqref{eq:mobility2} via GMRES.
+%By solving the mobility problem, we obtain translational and angular
+%velocities of the $N_b$-body system. 
+Moreover, a second-order Adams-Bashforth
+scheme updates the particle positions and orientations. By including the
+repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
+when using a relatively larger time step than $\Delta t\sim O(10^{-1})$ ns. 
+}
 
@@
 \ReviewerOne{Since the behavior of the suspended JP vesicles has similarities to the numerical 
-results generated by using the algorithm in \cite{qua-vee-you2019} (refer to all figure insets in 
-Figure~\ref{figure10} and Figure~\ref{figure12}). Figure~\ref{figure13} shows trajectory 
-comparisons between the proposed model and the continuum modeling for both shear flow and
-extensional flow cases in two vesicle simulations. The quantity $d_{1,2}$ represents the distance
-between two centroids of JP vesicles. The centroid positions are identical for both models and the
-geometry in the continuum model is created along the midplane locations of JP vesicles and the initial
-reduced area is matched. Panel (a) shows that the results of continuum model does not have a 
-periodic motion and two vesicles flow apart after 1.5 $\mu$s. Panel (b) shows that the results of
-continuum model has similar trend of dynamics with one in the proposed model.}
+results generated by using the algorithm adopted in \cite{qua-vee-you2019} (refer to all figure
+insets in Figure~\ref{figure10} and Figure~\ref{figure12}). Figure~\ref{figure13} shows 
+trajectory comparisons between the proposed model and the continuum modeling for both 
+shear flow and extensional flow cases in two vesicle simulations. The quantity $d_{1,2}$
+represents the distance between two centroids of JP vesicles. The centroid positions are 
+identical for both models and the geometry in the continuum model is created along the 
+midplane locations of JP vesicles and the initial reduced area is matched. Panel (a) shows that 
+the results of continuum model does not have a periodic motion and two vesicles flow apart 
+after 1.5 $\mu$s. Panel (b) shows that the results of continuum model has similar trend of
+dynamics with one in the proposed model.}
 

### 2022-02-11 doc/main_jfm.tex
Peter working on revision

@@
 state (Figures~\ref{figure2}c).
+\ReviewerOne{As shown in Figure~\ref{figure2}\ReviewerOne{a}, the particle translational and angular velocities vanish during the relaxation as expected.}
 
@@
 
-Figure~\ref{figure2}c plots the data for the pressure jump $\Delta p$
+%
+Figure~\ref{figure2}\ReviewerOne{b} plots the data for the pressure jump $\Delta p$
 between the particle centre and the far-field (see
-Figures~\ref{figure2}c and~\ref{figure2}d). We use $R = L/(2\pi)$ for
+Figures~\ref{figure2}\ReviewerOne{b} and~\ref{figure2}\ReviewerOne{c}). 
+We use $R = L/(2\pi)$ for
 the vesicle radius, and the horizontal axis is the relative stretch.

### 2022-02-12 doc/reviews/ResponseToReviewer1.tex

@@
 \begin{itemize}
-  \item Change 1 
+  \item The term (1) means the magnitude of the corresponding $y$-axis is of order 1.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item A shear rate of order $10^{6}\text{s}^{-1}$ is too high to be generated in experiments.
+Since the size of the JP vesicle in this work is much smaller than experimental use vesicles, 
+a very high shear rate of the flow is needed to acquire the tank-treading motion.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item Thank you for noticing this missing connection. We added a description connected to Figure 7a.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item We added a parametric study in new Table 2 and the trend provides an idea about 
+how to change vesicle stretching modulus and hydraulic permeability by adjusting the length related parameters or force related parameters.
+We think that it is possible to have better understanding about the link between all parameters and these physical quantities after more
+convergence study.
 \end{itemize}

### 2022-02-12 doc/reviews/ResponseToReviewer2.tex

@@
 \begin{itemize}
-  \item Change 1
-  \begin{quotation}
-    \noindent
-    Can put verbatim change in this environment.
-  \end{quotation}
+  \item {\bf Response to Summary}: We thank the Reviewer for this positive appraisal of 
+our manuscript. The proposed 2D JP vesicle model has a geometrical property 
+of constant perimeter with a finite number of particles.
+Study of the permeability gives a numerical evidence that the constant area constraint of this enclosed bilayer structure does not apply in this
+work. In response, we performed a number of simulations and provided more parametric study in 
+terms of small changes in parameters. 
+%  \begin{quotation}
+%    \noindent
+%    Can put verbatim change in this environment.
+%  \end{quotation}
 \end{itemize}

### 2022-02-12 doc/reviews/ResponseToReviewer3.tex

@@
 \begin{itemize}
-  \item Change 1
-  \begin{quotation}
-    \noindent
-    Can put verbatim change in this environment.
-  \end{quotation}
+  \item We would like to thank the referee for the help with the presentation, which
+has been modied as follows.
+%  \begin{quotation}
+%    \noindent
+%    Can put verbatim change in this environment.
+%  \end{quotation}
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item Fig.~6 shows snapshots for 4 time frames from 0 to 12 $\mu$s and the trajectory of the centriod is demonstrated.
+Therefore the $x$-axis of Fig.~6 represents the time horizon in unit of $\mu$s and
+the $y$-axis represents the $y$ position of the centroid of the JP vesicle.
 \end{itemize}

### 2022-02-12 doc/main_jfm.tex
RJR new Figure2_part1_Wrapper.pdf; new permeability section

--- 2022-02-11 doc/main_jfm.tex
@@
 \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:ves_in_quiescent}
+
+\begin{figure}
+\centering
+\includegraphics[width=\textwidth]{Figure2_part1_Wrapper.pdf}
+\caption{\label{figure2part1} Tension and pressure relax as
+  fluid is expelled through the particle interstices. In panel (a), inset, 
+  pressure is spatially constant inside the JP vesicle (inset). and 
+  Laplace pressure ((a), squares) and excess length ((b), squares) dissipate exponentially.  
+  The data in panels (b) and (c) show a linear relationship expressed by
+  \eqref{eq:LaplacePressure} and \eqref{eq:perm}. }
+\end{figure}
+
+In this section, we consider a circular JP vesicle suspended in a quiescent flow $\uu_{\infty} = 0$.
+We show that the JP particle bilayer behaves as an inextensible, permeable membrane with
+the inextensibility coming from a large stretching modulus.
+
+In membrane continuum  mechanics, changes in membrane surface area $A$ give rise to a tension
+$\tilde \sigma = K_A(A/A_0 - 1)$ where $A_0$ is the reference surface area \cite{NaTr00}. 
+For a two-dimensional membrane, the tension is 
+\begin{align}
+\label{eq:stretch}
+\tilde \sigma = K_A\left(L/L_0 - 1 \right),
+\end{align}
+where $L$ and $L_0$ are arc length and resting length,
+respectively. 
+Membrane tension gives rise to 
+a Laplace pressure 
+\begin{align}
+\label{eq:LaplacePressure}
+\Delta p = \tilde \sigma/R,
+\end{align}
+where $\Delta p$ is the jump in far-field pressure to internal pressure and
+$R = L/2\pi$.
+In order to relieve Laplace pressure, 
+water flows across the membrane. The rate of efflux is governed by  
+\begin{align}
+  \label{eq:perm} 
+  \frac{dA}{dt} = - P\Delta p,
+\end{align}
+where $P = k/(\mu \Delta x)$ is a constant, $k$ is hydraulic permeability, 
+$\mu$ is the solvent viscosity, and $\Delta x$ is the 
+membrane thickness, about 5 nm
+(\cite{chabanon2017, qua-gan-you2021}).
+
+Our  simulation setup consists of an initial, non-equilibrium JP
+obtained by dilating the equilibrium shape outward (Figures~\ref{figure2part1}a).
+At $t = 0$, pressure \eqref{eq:stokes} is spatially constant  inside and outside the vesicle 
+(Figures~\ref{figure2part1}a, inset)
+and Laplace pressure decreases to zero exponentially 
+(Figures~\ref{figure2part1}a,  squares).  
+At the same time, arc length decreases from its initial value $L(0)$ to its resting length $L_0$
+(Figures~\ref{figure2part1}b).
+
+To evaluate whether JP vesicles possess a stretching modulus,
+Figure~\ref{figure2part1}c plots $R \Delta p$ against the excess length $L/L_0 - 1$.  The squares
+are for the baseline simulation with vesicle diameter about 34 nm.  The diamonds 
+are for a vesicle with twice the diameter.  The linear relationships 
+are independent of vesicle size and give an area modulus $K_A = 170 \pm 9$ pN nm$^{-1}$.
+ This relatively large stretching modulus is the reason why the JP vesicle conserves length in the 
+shear-flow simulations (Figure \ref{figure2part1}c).
+The value also reasonably agrees with stretching moduli for 
+lipid bilayers, around $240$ pN nm$^{-1}$ \cite{NaTr00}.
+
+ In the initial, dilated vesicle,
+contractile motion is limited by the incompressibility of the 
+fluid bound by the vesicle.  
+Hence, the Laplace pressure 
+comes from an excess in inter-particle separation.  The vesicle-bound water,
+however, can escape through the gaps between the particles and this
+is how the JP vesicle relieves Laplace pressure over time (Figure \ref{figure2part1}a).
+
+To evaluate the rate of water outflow, 
+Figure~\ref{figure2part1}d plots the the simulation values for $dA/dt$.  
+These values are proportional to $L\Delta p$ and like for the stretching modulus, 
+the proportionality constants are 
+independent of vesicle size.
+The  linear fits give a hydraulic permeability $P = 0.0290 \pm 0.007$ nm$^3$ ns$^{-1}$ pN$^{-1}$.
+We can combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
+and~\eqref{eq:perm} to derive
+\begin{align}
+\label{eq:perm_solution}
+L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
+\end{align}
+Using the fitted values for $P$ and $K_A$, the theoretical time course for 
+\eqref{eq:perm_solution} (Figure~\ref{figure2part1}b, solid curve) is in good
+agreement with the JP data (Figure~\ref{figure2part1}b, squares).
+
+Our value for permeability disagrees 
+with permeabilities for lipid bilayers by a few orders of magnitude  (\cite{chabanon2017, qua-gan-you2021}).
+Potential reasons for this include the following. 
+Our two-dimensional simulations correspond to water flowing past a collection
+of parallel cylinders, which has a larger permeability than for a collection
+of spheres of comparable radius.   
+Second, permeability vanishes with inter-particle separation.  
+However, in our simulations, inter-particle separation is intentionally made comparable to 
+particle radius to avoid aggresive mesh refinement.
+
 \begin{figure}
@@
 \includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
-%\includegraphics[height=2in]{relax2.eps}
-%\includegraphics[height=2in]{relax.eps}\\
-%\includegraphics[height=2.in]{N58_0pres.pdf}
-%\includegraphics[height=2.in]{N58_5000pres.pdf}
-%  \todo[inline]{Put pressure of each of the two configurations below
-%  this.}
-\caption{\label{figure2} In JP vesicles, tension and pressure relax as
-  fluid is expelled through the particle interstices. In panel (a), the
-  thin curve plots the mean of the norm of the particle translational
-  velocities. The thick curve plots the mean of the absolute value of
-  the particle angular velocities. At $t = 0$ $\upmu$s, the vesicle has
-  a spatially constant internal pressure 0.05~pN nm$^{-2}$ (red color,
-  panel (b)). In panel (c), pressure has dissipated and the vesicle has
-  moved from its initial configuration (gray circles), to the
-  equilibrium configuration (black circles). The data in panels (d) and
-  (e) support the linear relationship expressed by
-  \eqref{eq:LaplacePressure} and \eqref{eq:perm}. Circles are for a
-  vesicle with 17 nm initial radius; square are for a 34 nm initial
-  radius. Asterisks are for a 18 nm initial radius but with smaller,
-  1.25 nm diameter particles. In panel (f), the theoretical time course
-  \eqref{eq:perm_solution} overlaps the data using constants $K_A$ and
-  $P$ derived from panels (d) and (e). }
+\caption{\label{figure2}  
+The ratios of the abscissa and ordinates from Figure \ref{figure2part1}c, d are well-fit by constant functions (baseline, dots).
+The open circles and diamonds are for $\gamma$ and $M$ increased by 5$\%$ and 10$\%$, respectively. 
+The x's and stars are for particle radius, $\rho$, and $\rho_0$ decreased by 5$\%$ and 10$\%$, respectively.
+The variable $x$ is used to denote the horizontal axis coordinate. 
+}
 \end{figure}
-Finally, we show that the JP vesicle behaves as a permeable membrane and the inextensibility comes
-about due to a large stretching modulus.
-%an extensible, permeable membrane. 
-Figures~\ref{figure2}b shows an initial, non-equilibrium JP
-vesicle suspended in a quiescent flow $\uu_{\infty} = 0$. The color map
-plots the pressure $p$. The red color in Figures~\ref{figure2}b shows a
-spatially constant, positive internal pressure (0.05~pN nm$^{-2}$) and the white
-shows a spatially constant zero, external pressure. There is some fluid flow and
-the pressure vanishes as the configuration tends toward the equilibrium
-state (Figures~\ref{figure2}c).
-
-What could be the source of this drop in pressure? In membrane
-continuum  mechanics, small changes in surface area give rise to a membrane tension
-$\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the membrane surface area
-and $A_0$ is the reference surface area. The area modulus $K_A$ of
-bilayers is about $240$ pN nm$^{-1}$ (\cite{NaTr00}). In the
-two-dimensional vesicles, the tension becomes
-\begin{align}
-\label{eq:stretch}
-\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
-\end{align}
-where $L$ and $L_0$ are the vesicle arc length and resting length,
-respectively. Moreover, stretched, circular vesicles \ReviewerOne{have}
-a Laplace pressure 
-\begin{align}
-\label{eq:LaplacePressure}
-\Delta p = \frac{\tilde \gamma}{R},
-\end{align}
-where $\Delta p$ is the difference in internal pressure to the pressure
-at infinity and $R^{-1}$ is the total curvature of the circular
-cylinder.
-
-Figure~\ref{figure2}c plots the data for the pressure jump $\Delta p$
-between the particle centre and the far-field (see
-Figures~\ref{figure2}c and~\ref{figure2}d). We use $R = L/(2\pi)$ for
-the vesicle radius, and the horizontal axis is the relative stretch.
-The circles are data for a vesicle with radius 17 nm. The linear fit
-(solid lines) shows that $R\Delta P$ is proportional to the relative
-stretching $L/L_0 - 1$. The squares are for a vesicle with twice the
-radius 34 nm, and the data overlap supports that the proportionality
-constant $K_A$ is a stretching modulus that is independent of vesicle
-size. The data give $K_A = 170 \pm 9$ pN nm$^{-1}$ which is in good
-agreement with the experimentally obtained area moduli of lipid bilayer. 
-%
-The reason the tank-treading vesicle appears inextensible ($L$ is more or less constant in Figure~\ref{figure4}c) is because the modulus $K_A$ is large.
-%
-To evaluate how changes to particle size lead to different
-physical properties, the asterisk symbols are for an 18 nm radius
-vesicle consisting of particles with diameter 1.25 nm, instead of the
-usual 2.5 nm. These data give a smaller stretching modulus of $K_A =
-102$~pN~nm$^{-1}$.
-
-The particles in our setup do not abut but rather have small gaps due to
-repulsive forces. The gaps allow for some fluid flux across the JP
-bilayer, and in membrane mechanics aqueous flux is quantified by the equation
-\begin{align}
-  \label{eq:perm} 
-  \frac{dA}{dt} = -P L \Delta p,
-\end{align}
-where $P$ is a hydraulic permeability constant (\cite{chabanon2017,
-qua-gan-you2021}). Figure~\ref{figure2}e shows that the data for
-$L\Delta p$ and $dA/dt$ obey the linear relationship expressed by
-\eqref{eq:perm}. The slopes of the linear fits give the hydraulic
-permeabilities $P = 0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ and $P = 0.0283$
-nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 17 nm and 34 nm radius cases,
-respectively. Like the area modulus, the data give a permeability 
-that is independent of vesicle size.
-
-\begin{figure}
+
+\begin{table}
+\caption{Stretching Moduli and Permeabilities}
+\centering
+\begin{tabular}{ c c c |c c| c |c }
+ radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (\mathrm{k_BT})$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
+\hline      \hline 
+ 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
+%
+ \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 5 \%$}  & 185$\pm5$  &  0.0292  \\ 
+%
+ \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 10 \%$}  & 195$\pm5$  &  0.0294 \\ 
+%
+ \multicolumn{3}{c|}{$- 5 \%$} & \multicolumn{2}{c|}{same}   & 184$\pm5$  &  0.0283 \\ 
+%
+ \multicolumn{3}{c|}{$- 10 \%$} & \multicolumn{2}{c|}{same}   & 189$\pm6$  &  0.0252  \\ 
+\end{tabular} 
+\label{table2}
+\end{table}
+%
+
+We performed a parametric study of the dependence of $K_A$ and $P$
+on model parameters taking into account   
+(i) changes in interfacial strength and (ii) changes in size.
+Table~\ref{table2} provides the results of stretching moduli $K_A$ and permeabilities $P$ for various cases.
+ The baseline setup is shown in the first row.
+The next two rows demonstrate the results when the tension related parameters $\gamma$ and $M$ are increased by 5$\%$ and 10$\%$. 
+The final two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$
+This data comes from Figure \ref{figure2} which  plots the \emph{ratio} of the abscissa and ordinates
+used in Figure \ref{figure2part1}c, d. The transformed data are fit by constant functions.
+
+Increases in $\gamma$ and $M$ result in
+a commensurate increase in the stretching modulus. 
+Permeability, however, is insensitive to simultaneous increases in $\gamma$ and $M$.
+To give a detailed explanation for this, the JP system has the potential energy $E = G + H$ where 
+\begin{equation}
+\label{eq:baseline_energy}
+G = \gamma \int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2 \,dx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
+       P(|\tilde{\xx}_i - \tilde{\xx}_j|).
+\end{equation}
+Here, $G$ is the hydrophobic attraction potential for the boundary value problem \eqref{eq:SL}--\eqref{eq:SLff},
+and $H$ is the repulsion potential.  
+For the circular vesicle, total energy depends only on the characteristic inter-particle distance $x$
+and has a minimum at $x_0$. 
+If $\gamma$ and $M$ are scaled by $c$, 
+we can related the scaled energy to that of the baseline case by 
+\[E_c(x) = c(G(x) + H(x)).\]
+Permeability does not change with like increases in $\gamma$ and $M$
+because the critical number for $E_c$, and hence inter-particle separations, are independent to $c$.
+The stretching modulus comes from $\frac{d^2E_c}{dx^2}$ and this 
+quantity varies proportionally with $c$.
+
+One can observe that $K_A$ increases and $P$ decreases as the length scale decreases. 
+The decrease in  $P$ is expected because 
+the size of the gap between adjacent JP particles is directly proportional to length scale.
+To give a more detailed account, pressure $p$ and water flux across the membrane $q$ scale as 
+$p_{\lambda}(\mathbf{x}) = \lambda^{-1} p(\mathbf{x}/\lambda)$ and 
+$q_{\lambda}(\mathbf{x}) = q(\mathbf{x}/\lambda)$ 
+when $l_0$ is scaled by $\lambda$. As a result, the scaled permeability constant satisfies 
+\[
+P_{\lambda} = q_{\lambda}/\Delta p_{\lambda} = q/(\lambda^{-1} \Delta p) = \lambda P.
+\]
+For the stretching modulus, the total energy transforms as 
+\[E_{\lambda}(x) = \lambda G(x/\lambda) + H(x/\lambda ).\]
+The factor $\lambda$ comes from the change of 
+variables formula for the integral in \eqref{eq:baseline_energy}.
+The stretching modulus increases because $\frac{d^2E_{\lambda}}{dx^2}$ increases with decreases in $\lambda.$
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{center}
@@
 \end{figure}
-
-The hydraulic permeability we calculate, however, is not in agreement
-with experimentally derived values and is larger by a few orders of
-magnitude. We suspect this discrepancy is due to inter-particle distance
-of the JP being large compared to the inter-lipid spacing in real
-bilayers. To test this, we calculate the permeability for the particles
-with diameter 1.25 nm. Due to their smaller size but fixed repulsion
-strength, these particles have a larger inter-particle spacing resulting
-in an increase in permeability, $P = 0.0566$~nm$^3$~ns$^{-1}$~pN$^{-1}$
-(Figure~\ref{figure2}e, asterisk symbols).
-
-Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
-combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
-and~\eqref{eq:perm}, to derive
-\begin{align}
-\label{eq:perm_solution}
-L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
-\end{align}
-All in all, the theoretical time courses for \eqref{eq:perm_solution} are in good
-quantitative agreement with the JP data (Figure~\ref{figure2}f).
-
-% table 2
-
-\begin{table}
-\caption{Stretching Moduli and Permeabilities}
-\centering
-\begin{tabular}{ c c c c c c c }
- radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (k_BT)$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
-\hline      \hline 
- 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
-%
- 0.475 & 1.9  &   0.475  & 4.0 &  4.1   & 184$\pm5$  &  0.0283 \\ 
-%
- 0.45 & 1.8  &   0.45  & 4.0   &  4.1   & 189$\pm6$  &  0.0252  \\ 
-%
- 0.5 & 2.0  &   0.5  & 4.2   &  4.31  & 185$\pm5$  &  0.0292  \\ 
-%
- 0.5 & 2.0  &   0.5  & 4.4   &  4.51  & 195$\pm5$  &  0.0294 \\ 
-\end{tabular} 
-\label{table2}
-\end{table}
-%
-
-\ReviewerOne{Table~\ref{table2} provides the results of stretching moduli $K_A$ and permeabilities $P$ for various cases.
-The default setup is shown in the first row.
-The next two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$.
-One can observe that the constant $K_A$ increases
-and $P$ decreases as size of particles decreases. 
-The last two rows demonstrate the results when the force related parameters $\gamma$ and $M$ are adjusted by 5$\%$ and 10$\%$.
-The quantities examined for these two cases show that $K_A$ increases and $P$ remains constant as inter-particle interaction strength increases.
-As expected by the fact that the permeability is dependent of the particle size where the gap between each adjacent JP pair is controlled by the size of JP.
-However, the detailed correlation between all model parameters will be explored as
-a direction of future work.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Two Vesicles in a Linear Flow}
-
 \begin{figure}

### 2022-02-13 doc/reviews/ResponseToReviewer1.tex
updated Response 1

@@
 \begin{itemize}
-  \item Change 1 
+  \item Section 2.2 introduces the imposed forces and torques in hydrophobic attraction and repulstion that are not used to obtain particle directions directly. Following the next comment by 
+the Reviewer, we agreed that Section 2.3 should be moved to the end of Section 3 and we complete the change.
 \end{itemize}
@@
   \item We thank the Review for the comment and we moved the original Section 2.3 {\it Time Marching} at the end of Section 3 combining the change based on the comment previously addressed about what to solve for in the proposed algorithm.
+As described in Section 2.2, the repulsion force with a constant strength coefficient $M$ is chosen 
+to be a large number in order to avoid particle collisions.
+If $M$ is not large enough, the hydrophobic attraction will dominate the total force and the dynamics may cause particle collisions with the use of a larger time step.
+Therefore, with an empirical study to the relationship between
+choices of M and $\gamma$, the parameter set in this work allows the time step to be as large as
+$O(10^{-1})$ with no error. Comparing the time step used in literatures, for instance, in Bystricky {\sl et al.}, Int. J. Numer. Methods Fluids), $\Delta t\sim O(10^{-2})$.
 \end{itemize}

### 2022-02-14 doc/reviews/ResponseToReviewer1.tex
Response 1 updates

@@
 provided time scale is $\tau = \mu R_0^3/\kappa_B$ where $\mu$ the fluid viscosity and $\kappa_B$ the bending modulus.
+$R_0$ is the initial radius of the reference vesicle.
 Since the bending modulus does not play any roles in the proposed model, we then scaled time unit with a realistic characteristic time ns.
-With the use of the detailed scaling laws described in section 4.1, we aim to have a comparable
-numerical results against the experiments.
+With the use of the detailed scaling laws described in section 4.1, we aim to have comparable
+numerical results against the experiments. Moreover, if we attempt to calculate the characterstic 
+time scale using characteristic length and energy scales, it will also result a vaule of order ns. 
+Since the system involves multiple length scales, diameter of the particle $l_0$ and size of the JP
+vesicle $R_0$, we decided to use ns to perform nondimensionalization for simplicity.
 \end{itemize}

### 2022-02-14 doc/reviews/ResponseToReviewer2.tex
Response 2 updates

@@
 \begin{itemize}
-  \item Change 1 
+  \item The velocity ${\bf u}({\bf x})$ introduced in the mobility problem (eqn.
+(2.1)--(2.3)) is in bold face and of a vector form.
+The scalar solution function $u$ is the solution of the screened Laplace equation boundary value problem (eqn.
+(2.7)--(2.9)).
+Therefore there is no duplication of usage in notation.
+In reponse to this point, in order to avoid confusions, we changed the scalar function to $\eta$.
 \end{itemize}

### 2022-02-14 doc/reviews/ResponseToReviewer3.tex

@@
 \begin{itemize}
-  \item Change 1 
+  \item Fig.~3(c) clearly shows that the total length of the JP vesicle has a steady periodic motion 
+which is different from the trends shown in panels (a) and (b). We showed the actual time evolution of $A^*$ and $\Delta$ and fitting curves in (a). 
+The idea is to show that we can use the fitting data to acquire the numerical expected teminal 
+reduced area $A^*_\infty$. Therefore the multiple frequencies during simulations have no correlations between
+the output in (c) and (d).
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item We corrected the original Fig.~10 by plotting all continuous streamlines. We thank the Reviewer for pointing this out and this issue occurred due to a mistake made in post-processing
+steps.
 \end{itemize}

### 2022-02-14 doc/main_jfm.tex
RJR new Figure2_part1_Wrapper.pdf; new permeability section
delete orig equations (2.5)

@@
   the mobility problem. The color map in panels (b)--(e) is the solution
-  $u$ of \eqref{eq:SL}. Red is for $u = 1$ and blue is for $u = 0$.
+  $u$ of \eqref{eq:SL}. Red is for $\ReviewerTwo{\eta} = 1$ and blue is for $\ReviewerTwo{\eta} = 0$.
   Particles self-assemble into vesicle bilayers (panel (b)) and
@@
 \begin{align}
+\label{eq:rigid_bc}
   \ReviewerOne{\uu}(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
@@
   \label{eq:SL}
--\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
+-\rho^2 \Delta \ReviewerTwo{\eta} + \ReviewerTwo{\eta} &=0,            && \xx \in \Omega,\\
 \label{eq:SLbc}
-u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
+\ReviewerTwo{\eta}(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
 \label{eq:SLff}
-u &\to 0,                          &&|\xx| \to \infty,
+\ReviewerTwo{\eta} &\to 0,                          &&|\xx| \to \infty,
 \end{alignat}
@@
 \mathbf{T}
-= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
-  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
+= \gamma\rho^{-1}\ReviewerTwo{\eta}^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
+  \ReviewerTwo{\eta}|^2 \mathbf{I} - \nabla \ReviewerTwo{\eta}  \nabla \ReviewerTwo{\eta}^T\right)
 \end{align}
@@
   \label{eq:HAP_DLP}
-  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
+  \ReviewerTwo{\eta}(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
     K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
@@
   \label{eq:uidef}
-  w_i(\xx) = u(\xx) - u_i(\xx),
+  w_i(\xx) = \ReviewerTwo{\eta}(\xx) - \ReviewerTwo{\eta}_i(\xx),
 \end{align}
@@
 \begin{align}
-  u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \left(\pderiv{}{\nnu_\yy}
+  \ReviewerTwo{\eta}_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \left(\pderiv{}{\nnu_\yy}
     K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
@@
   {\bf T} &=
-    \SS(u_i,u_i) +(\SS(u_i,w_i) +\SS(w_i,u_i)) +\SS(w_i,w_i) \\
+    \SS(\ReviewerTwo{\eta}_i,\ReviewerTwo{\eta}_i) +(\SS(\ReviewerTwo{\eta}_i,w_i) +\SS(w_i,\ReviewerTwo{\eta}_i)) +\SS(w_i,w_i) \\
   &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
@@
 \label{eq:Tsplit}
-\SS(u,v)
-=  \gamma\rho^{-1} uv {\bf I} + \gamma\rho \nabla u \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla u \nabla v^T.
+\SS(\ReviewerTwo{\eta},v)
+=  \gamma\rho^{-1} \ReviewerTwo{\eta}v {\bf I} + \gamma\rho \nabla \ReviewerTwo{\eta} \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla \ReviewerTwo{\eta} \nabla v^T.
 \end{equation}
-Using the fact that $u$,  $u_i$, and $w_i$ solve the screened Laplace
+Using the fact that $\ReviewerTwo{\eta}$,  $\ReviewerTwo{\eta}_i$, and $w_i$ solve the screened Laplace
 equation~\eqref{eq:SL}, and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1,
@@
 smooth and $\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n
-\setminus U_i$. Similarly, $w_i = u - u_i$ is smooth and $\nabla \cdot
+\setminus U_i$. Similarly, $w_i = \ReviewerTwo{\eta} - \ReviewerTwo{\eta}_i$ is smooth and $\nabla \cdot
 {\bf T}_3 = \mathbf{0}$ in $U_i$. By the divergence theorem,  
@@
 \label{eq:DLjump}
-\jump{u_i} = \sigma, \quad
+\jump{\ReviewerTwo{\eta}_i} = \sigma, \quad
 \jump{w_i} = 0, \quad
-\jump{\nabla u_i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
+\jump{\nabla \ReviewerTwo{\eta}_i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
 \jump{\nabla w_i} = \mathbf{0},
@@
 \begin{align*}
-  \jump{{\bf T}_2 \cdot \nnu}   &= \jump{\SS(u_i,w_i) \cdot \nnu +
-    \SS(w_i,u_i) \cdot \nnu} \\
-  &= \Big[\!\Big[ \left( 2\gamma\rho^{-1} u_i w_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla w_i \mathbf{I} 
-- 2\gamma\rho \nabla u_i  \nabla w_i^T - 2\gamma\rho \nabla w_i \nabla
-  u_i^T\right) \cdot \nnu \Big]\!\Big] \\
+  \jump{{\bf T}_2 \cdot \nnu}   &= \jump{\SS(\ReviewerTwo{\eta}_i,w_i) \cdot \nnu +
+    \SS(w_i,\ReviewerTwo{\eta}_i) \cdot \nnu} \\
+  &= \Big[\!\Big[ \left( 2\gamma\rho^{-1} \ReviewerTwo{\eta}_i w_i \mathbf{I} + 2\gamma\rho \nabla \ReviewerTwo{\eta}_i \cdot \nabla w_i \mathbf{I} 
+- 2\gamma\rho \nabla \ReviewerTwo{\eta}_i  \nabla w_i^T - 2\gamma\rho \nabla w_i \nabla
+  \ReviewerTwo{\eta}_i^T\right) \cdot \nnu \Big]\!\Big] \\
 %  &= \jump{\left( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
@@
 \end{figure}
-
 In this section, we consider a circular JP vesicle suspended in a quiescent flow $\uu_{\infty} = 0$.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
   \begin{center}
@@
 \begin{center}
-\includegraphics[width=0.97\textwidth]{Figure11_Wrapper.pdf}
+\includegraphics[width=0.97\textwidth]{Figure11_Wrapper_New.pdf}
 %\includegraphics[width=0.9\textwidth]{ExtTraj.eps}

### 2022-02-15 doc/reviews/ResponseToReviewer1.tex
updated by Peter

@@
 choices of M and $\gamma$, the parameter set in this work allows the time step to be as large as
-$O(10^{-1})$ with no error. Comparing the time step used in literatures, for instance, in Bystricky {\sl et al.}, Int. J. Numer. Methods Fluids), $\Delta t\sim O(10^{-2})$.
+$O(10^{-1})$ with no instability. Comparing the time step used in literatures, for instance, in Bystricky {\sl et al.}, {\bf 2020}, Int. J. Numer. Methods Fluids), $\Delta t\sim O(10^{-2})$.
 \end{itemize}
@@
     been added at its first occurrence in Section 3.1. 
-  \item This change is in \textcolor{green} since it was also pointed
+  \item This change is in \textcolor{green}{green} since it was also pointed
     out by Reviewer 2.
@@
 \begin{itemize}
-  \item Change 1 
+  \item All physical quantities in membrane mechanics such as interfacial tension, bending  modulus, and energy constant in pairwise interactions are defined in units of $k_BT$. 
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item We tested the model parameters based on matching simulation results in the previous paper  (Fu {\sl et al.}, {\bf 2020}, Multiscale Model.
+Simul.).
+The proposed work adopts a different repulsion force from the previous one and we have done studies in choosing the default parameter set to achieve similar structures.
+For the effective properties, we leave it as a future work.
 \end{itemize}

### 2022-02-15 doc/reviews/ResponseToReviewer2.tex
updated by Peter

@@
 \begin{itemize}
-  \item Change 1 
+  \item 
+Our method currently does not support a viscosity contrast in the system 
+or the setup similar to ones in (Veerapaneni {\sl et al.}, {\bf 2011}, Phys. Rev. Lett.),
+(Vlahovska and Gracia, {\bf 2007}, Phys. Rev. E), and
+(Kaoui and Harting, {\bf 2016}, Rheol Acta). 
+As described in the manuscript, the JP vesicle is permeable and the mixture of two different
+fluids has to be analyzed within the framework.
+
 \end{itemize}

### 2022-02-15 doc/reviews/ResponseToReviewer3.tex
updated by Peter

@@
 In this work we use similar techniques for solving the integral equations when some boundaries are quite close to each other.
-As the repulsive More potential works well to prevent overlapping of particles (provided the time step size is sufficiently small), our previous results in Quaife, Veerapaneni and Young, 2019, Phys.
+As the repulsive Morse potential works well to prevent overlapping of particles (provided the time step size is sufficiently small), our previous results in Quaife, Veerapaneni and Young, 2019, Phys.
 Rev.
@@
   \item Fig.~6 shows snapshots for 4 time frames from 0 to 12 $\mu$s and the trajectory of the centriod is demonstrated.
-Therefore the $x$-axis of Fig.~6 represents the time horizon in unit of $\mu$s and
-the $y$-axis represents the $y$ position of the centroid of the JP vesicle.
+Therefore the dashed horizontal line of Fig.~6 represents time in units of $\mu$s and the vertical axis represents the scaled $y$ position of the centroid of the JP vesicle.
 \end{itemize}
@@
   \item We corrected the original Fig.~10 by plotting all continuous streamlines. We thank the Reviewer for pointing this out and this issue occurred due to a mistake made in post-processing
-steps.
+steps. Moreover, we do expect some discontinuous streamlines where it occurs when a strealine flows across the JP vesicle interface.
 \end{itemize}

### 2022-02-15 doc/main_jfm.tex
updates
updated by Peter

@@
 scheme updates the particle positions and orientations. By including the
-repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
-when using a relatively larger time step than $\Delta t\sim O(10^{-1})$ ns. 
+repulsion force~\eqref{eq:REPULforce}, particle collisions can be avoided by setting time step
+size $\Delta t\sim O(10^{-1})$.
+%are avoided even when using a relatively larger time step than $\Delta t\sim O(10^{-1})$ ns. 
 }
@@
 \centering
-\begin{tabular}{c c c c c c c c c }
-& & & & $\dot\gamma$  (ns$^{-1}$) & & & &\\
-\cline{2-8}\\
- & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  & Average\\
-\cline{1-8}\\
-$N_b=53$  & 0.50  & 0.51  &  0.44 & 0.52  & 0.45 &  0.57   &  0.62 & 0.52  \\ 
-$N_b=56$ & 0.54 & 0.41 & 0.35  & 0.37 & 0.43 & 0.76  & 0.70 & 0.51\\ 
-$N_b=58$   & 0.42 & 0.63 & 0.50   & 0.40  & 0.48  & 0.53 & 0.55 & 0.50 \\   % new
-$N_b=61$  & 0.22 & 0.36 & 0.41   & 0.45  & 0.45 & 0.44   & 0.44 & 0.40\\ 
+\begin{tabular}{c c c c c c c c c c c c }
+& & & & & & & $\dot\gamma$  (ns$^{-1}$) & & & &\\
+\cline{1-11}\\
+  radius ($l_0$) &  $\rho$ ($l_0$) & $\rho_0(l_0)$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  & Average\\
+\cline{4-10}\\
+& $+ 10 \%$ &     & 0.50  & 0.51  &  0.44 & 0.52  & 0.45 &  0.57   &  0.62 & 0.52  \\ 
+& $+ 5 \%$ & & 0.54 & 0.41 & 0.35  & 0.37 & 0.43 & 0.76  & 0.70 & 0.51\\ 
+0.5 &  2.0 & 0.5    & 0.42 & 0.63 & 0.50   & 0.40  & 0.48  & 0.53 & 0.55 & 0.50 \\   % new
+& $- 5 \%$ &  & 0.22 & 0.36 & 0.41   & 0.45  & 0.45 & 0.44   & 0.44 & 0.40\\ 
 \end{tabular} 
@@
 %
-\ReviewerOne{There is no clear trend shown in Table~\ref{table1} but these values of $b$ are}
+\ReviewerOne{The overall trend shown in Table~\ref{table1} is values of $b$ decreases as $\rho$
+decreases and $b$ are}
 %over a range of shear rates which is 
@@
   drifts toward the central axis. It assumes a slipper shape and
-  undergoes tank-treading motion like in the shear flow case. The arrows
+  undergoes tank-treading motion like in the shear flow case. 
+ \ReviewerThree{The horizontal dashed line represents time in units of $\mu$s and the vertical axis represents the scaled $y$ position of the centroid of the JP vesicle.}
+  The arrows
   on the left illustrate the background flow and the arrows on the right
@@
 \label{eq:baseline_energy}
-G = \gamma \int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2 \,dx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
+G = \gamma \int_{\Omega} \rho |\nabla \ReviewerTwo{\eta}|^2 + \rho^{-1} \ReviewerTwo{\eta}^2 \,\dif\xx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
        P(|\tilde{\xx}_i - \tilde{\xx}_j|).
@@
 \includegraphics[width=0.97\textwidth]{Figure11_Wrapper_New.pdf}
-%\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
 \end{center} 
@@
   is $1.25$~nm below the $x$-axis. The streamlines appear in grey and
-  the flow rate is $\dot \gamma =0.005$~ns$^{-1}$ in all cases.}
+  the flow rate is $\dot \gamma =0.005$~ns$^{-1}$ in all cases.
+	  }
 \end{figure}
@@
   \includegraphics[width=\textwidth]{Figure12_Wrapper.pdf}
-%\includegraphics[height=2in]{N116_ext_0.pdf}
-%\includegraphics[height=2in]{N116_ext_2000.pdf}\\
-%\includegraphics[height=2in]{N116_ext_4000.pdf}
-%\includegraphics[height=2in]{N116_ext_6500.pdf}
   \caption{\label{figure12} The figure is for the simulation case (iii) of Figure~\ref{figure11},

### 2022-02-15 doc/reviews/ResponseToReviewer3.tex
yny 1st commit

@@
 
-In this work we use similar techniques for solving the integral equations when some boundaries are quite close to each other.
+In this work we used similar numerical techniques to solve the integral equations when some boundaries are quite close to each other.
 As the repulsive Morse potential works well to prevent overlapping of particles (provided the time step size is sufficiently small), our previous results in Quaife, Veerapaneni and Young, 2019, Phys.
@@
 
-\item Change: We added a short paragraph to describe our methodology to capture the lubrication flow in the space between particles in close vicinity of each other in page, between lines \$\$\$ and \$\$\$.
+\item Change: We added sentences to describe how the lubrication hydrodynamics in a narrow space between boundaries is well-captured within the boundary integral formulation in page 4, starting in line 129.
 

### 2022-02-15 doc/main_jfm.tex
yny 1st commit

@@
 $P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
-prevent particle collisions. Then, the total imposed force and torque
+prevent particle collisions. 
+\textcolor{magenta}{
+The high-order interpolation-based quadrature rule used to compute the nearly-singular integrals has
+been shown to well capture the lubrication hydrodynamics in the narrow space between boundaries 
+when the repulsive potential $P$ gives a large steric force \cite{qua-bir2014}.  
+In the simulations we adjust the spatial resolution on the particle boundary to ensure that the lubrication hydrodynamics is well resolved as in \cite{qua-vee-you2019,qua-gan-you2021}.
+}
+%
+Then, the total imposed force and torque
 are

### 2022-02-15 doc/reviews/ResponseToReviewer3.tex
yny 2nd commit

@@
 \begin{itemize}
-  \item Fig.~3(c) clearly shows that the total length of the JP vesicle has a steady periodic motion 
+  \item  Response: This part needs to be fixed with the FFT of the data that Rolf sent to Bryan.
+  {\sl What follows is from Peter:
+  Fig.~3(c) clearly shows that the total length of the JP vesicle has a steady periodic motion 
 which is different from the trends shown in panels (a) and (b). We showed the actual time evolution of $A^*$ and $\Delta$ and fitting curves in (a). 
@@
 reduced area $A^*_\infty$. Therefore the multiple frequencies during simulations have no correlations between
-the output in (c) and (d).
+the output in (c) and (d).}
+
+\item Change:
+
 \end{itemize}
@@
 \begin{itemize}
-  \item Fig.~6 shows snapshots for 4 time frames from 0 to 12 $\mu$s and the trajectory of the centriod is demonstrated.
+  \item Response: Fig.~6 shows snapshots for 4 time frames from 0 to 12 $\mu$s and the trajectory of the centriod is demonstrated.
 Therefore the dashed horizontal line of Fig.~6 represents time in units of $\mu$s and the vertical axis represents the scaled $y$ position of the centroid of the JP vesicle.
+  \item Change: In the caption of Fig.~6 (page 14) we explain that the horizontal and vertical axes.
+
 \end{itemize}
@@
 \begin{itemize}
-  \item We corrected the original Fig.~10 by plotting all continuous streamlines. We thank the Reviewer for pointing this out and this issue occurred due to a mistake made in post-processing
-steps. Moreover, we do expect some discontinuous streamlines where it occurs when a strealine flows across the JP vesicle interface.
+  \item Response: We thank the Reviewer for pointing this out and this issue occurred due to a mistake made in post-processing
+steps. Moreover, we do expect some  streamlines with large variation in gradient when they cross the JP vesicle interface.
+
+\item Change: We corrected the original Fig.~10 by plotting all continuous streamlines. 
 \end{itemize}

### 2022-02-15 doc/reviews/ResponseToReviewer1.tex

@@
 \begin{itemize}
-  \item This comment encouraged us to have more convergence studies in the choices of model parameters. We made a worthwhile effort to perform a large number of simulations. 
-We revised Table 1 and added Table 2 to account for effective properties of vesicles with different size of particles.
-We agree with the Reviewer that the particle/vesicle shape is complex with the setup therefore we adopted small changes in particle sizes and reported all the reults.
-
+  \item Response: This comment encouraged us to present more convergence studies in the choices of model parameters.
+We made a worthwhile effort to perform a large number of simulations.
+We agree with the Reviewer that the particle/vesicle shape is complex with the setup therefore we adopted small changes in particle sizes and reported all the results.
+  \item Change: We revised Table 1 (page 12) and added Table 2 (page 16) to account for effective properties of vesicles with different size of particles.
+We added a short description of the new Table 1 in lines 354-359.
 \end{itemize}
@@
 \begin{itemize}
-  \item We agree with the Reviewer that we briefly illustrated the capability of simulating membrane rupture via the proposed model and numerical algorithm in the first submission of the manuscript.
-We further performed a series of study to find the critical shear rate for the appearance of membrane rupture and the corresopnding movie is added as a supplementary material.
+  \item Response: We agree with the Reviewer that we briefly illustrated the capability of simulating membrane rupture via the proposed model and numerical algorithm in the first submission of the manuscript.
+We further performed a series of study to find the critical shear rate for the appearance of membrane rupture and the correspnding movie is added as a supplementary material.
 We also included the description in the section of membrane rupture.
+  \item Change: We added a short description of vesicle rupture (lines 374-376) in page 13. We added a movie of vesicle rupture (Movie S4) in the supplementary material (page 25).
+
 \end{itemize}
@@
 \begin{itemize}
-  \item We thank the Reviewer to point this out. There is a significant difference between 
+  \item Response: We thank the Reviewer to point this out. There is a significant difference between 
 the proposed model in the manuscript and other continuum models in literatures. For example, refer to \emph{Rahimian, et al., J. Comput. Phys., 2011}, the 
@@
 $R_0$ is the initial radius of the reference vesicle.
-Since the bending modulus does not play any roles in the proposed model, we then scaled time unit with a realistic characteristic time ns.
+Since the bending modulus results from the hydrophobic attraction between Janus particles and their dynamics in a viscous fluid in the proposed model, we thus scaled time with a realistic characteristic time ns.
 With the use of the detailed scaling laws described in section 4.1, we aim to have comparable
-numerical results against the experiments. Moreover, if we attempt to calculate the characterstic 
-time scale using characteristic length and energy scales, it will also result a vaule of order ns. 
+numerical results against the experiments. Moreover, if we attempt to calculate the characteristic 
+time scale using characteristic length and energy scales, it will also result a value of order ns. 
 Since the system involves multiple length scales, diameter of the particle $l_0$ and size of the JP
 vesicle $R_0$, we decided to use ns to perform nondimensionalization for simplicity.
+
+Finally we did manage to come up with an appropriate capillary number to characterize the rupture of a Janus vesicle under a linear shear flow at a high shear rate.
+
+\item Change: Place where the critical capillary number is given and discussed.
+
 \end{itemize}
@@
 \begin{itemize}
-  \item We followed the suggestion given by the Reviewer that a summary about what to solve throughout the entire algorithm is provided at the end of Section 3.
+  \item Response: We followed the suggestion given by the Reviewer that a summary about what to solve throughout the entire algorithm is provided at the end of Section 3.
+  \item Change: A short paragraph is added in page 8 (lines 248-253).
 \end{itemize}
@@
 \begin{itemize}
-  \item We thank the Review for having this meaningful comment and we agree that changing all the figure 
-to colorblind friendly colormap is insightful. We would love to make this change once the manuscript is accepted.
+  \item Response: We thank the Review for having this meaningful comment and we agree that changing all the figure 
+to colorblind friendly colormap is insightful. We will make this change for all figures once the manuscript is accepted. All the new figures are made with colorblind friendly colormaps.
+
+\item Change: All the modified figures (Figs.~ 9, 10, 11, 12,  13) are made with colorblind friendly colormaps. 
 \end{itemize}
@@
 \begin{itemize}
-  \item We deleted the sentence ``$L$ is the arc length''.
+  \item Change: We deleted the sentence ``$L$ is the arc length''.
 \end{itemize}
@@
 \begin{itemize}
-  \item This typo is corrected.
+  \item Change: This typo is corrected.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+ \item Response: We thank the referee for pointing this out.
+We deleted the disconnected paragraph that started with "Brandner...." and modified the end of the following paragraph in response to the next comment from the reviewer.
+  \item Change: The paragraph ``Brandner {\it et al} (2019) used the coarsae-grained...." is removed.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item Response: We modified this description for better clarity.
+  \item Change: Page 3, lines 64-65, we changed ``relatively weak repulsive force" to ``relatively soft repulsive force" and added ``(compared to the short-range repulsion that diverges in the Lennard-Jones potential)".
+
 \end{itemize}
@@
 \begin{itemize}
-  \item We deleted the redundant equation (2.5) mentioned by the Reviewer.
+  \item Change: We deleted the redundant equation (2.5) mentioned by the Reviewer.
 \end{itemize}
@@
 \begin{itemize}
-  \item Section 2.2 introduces the imposed forces and torques in hydrophobic attraction and repulstion that are not used to obtain particle directions directly. Following the next comment by 
+  \item Response: Section 2.2 introduces the imposed forces and torques in hydrophobic attraction and repulsion that are not used to obtain particle directions directly. Following the next comment by 
 the Reviewer, we agreed that Section 2.3 should be moved to the end of Section 3 and we complete the change.
+\item Change: We moved Section 2.3 to the end of Section 3.
 \end{itemize}
@@
 \begin{itemize}
-  \item We thank the Review for the comment and we moved the original Section 2.3 {\it Time Marching} at the end of Section 3 combining the change based on the comment previously addressed about what to solve for in the proposed algorithm.
+  \item Response: We thank the Review for the comment and we moved the original Section 2.3 {\it Time Marching} at the end of Section 3 combining the change based on the comment previously addressed about what to solve for in the proposed algorithm.
 As described in Section 2.2, the repulsion force with a constant strength coefficient $M$ is chosen 
@@
 $O(10^{-1})$ with no instability. Comparing the time step used in literatures, for instance, in Bystricky {\sl et al.}, {\bf 2020}, Int. J. Numer. Methods Fluids), $\Delta t\sim O(10^{-2})$.
+\item Change: We moved Section 2.3 to the end of Section 3 (Section 3.4, page 8, lines 243-248).
 \end{itemize}
@@
 \begin{itemize}
-  \item Thank you for noticing this oversight. The definition of HAP has
+  \item Response: Thank you for noticing this oversight. The definition of HAP has
     been added at its first occurrence in Section 3.1. 
-  \item This change is in \textcolor{green}{green} since it was also pointed
+  \item Change: This change is in \textcolor{green}{green} (page 5, line 144) since it was also pointed
     out by Reviewer 2.
@@
 \begin{itemize}
-  \item Parenthesis have been added to equation (3.1)
-
-  \item Equations (3.2) and (3.11) had the same notational issue, and
+  \item Change: Parenthesis have been added to equation (3.1).  Equations (3.2) and (3.11) had the same notational issue, and
     they have both been corrected.
@@
 \begin{itemize}
-  \item This notation has been adjusted throughout Section 3.
+  \item Change: This notation has been adjusted throughout Section 3.
 \end{itemize}
@@
 \begin{itemize}
-  \item Since the only derivatives that are required are functions
+  \item Response: Since the only derivatives that are required are functions
     defined only on the boundary of the Janus particles, they are
@@
 
-  \item We have added the following sentence to the start of Section 3
+  \item Change: We have added the following sentence to the start of Section 3
     \begin{quotation}
@@
 \begin{itemize}
-  \item All physical quantities in membrane mechanics such as interfacial tension, bending  modulus, and energy constant in pairwise interactions are defined in units of $k_BT$. 
+  \item Response: All physical quantities in membrane mechanics such as interfacial tension, bending  modulus, and energy constant in pairwise interactions are defined in units of $k_BT$. 
 \end{itemize}
@@
 \begin{itemize}
-  \item We tested the model parameters based on matching simulation results in the previous paper  (Fu {\sl et al.}, {\bf 2020}, Multiscale Model.
+  \item Response: We tested the model parameters based on matching simulation results in the previous paper  (Fu {\sl et al.}, {\bf 2020}, Multiscale Model.
 Simul.).
@@
 \begin{itemize}
-  \item The term (1) means the magnitude of the corresponding $y$-axis is of order 1.
+  \item Response: The term (1) means the magnitude of the corresponding $y$-axis is of order 1.
 \end{itemize}
@@
 \begin{itemize}
-  \item A shear rate of order $10^{6}\text{s}^{-1}$ is too high to be generated in experiments.
+  \item Response: A shear rate of order $10^{6}\text{s}^{-1}$ is too high to be generated in experiments.
 Since the size of the JP vesicle in this work is much smaller than experimental use vesicles, 
@@
 \begin{itemize}
-  \item This typo is fixed.
+  \item Change: This typo is fixed.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item Response: We thank the referee for this comment.
+We will re-plot all color figures with colorblind friendly colormap if the manuscript should be accepted for publication.
+We will take this into account as well.
 \end{itemize}
@@
 \begin{itemize}
-  \item Thank you for noticing this missing connection. We added a description connected to Figure 7a.
+  \item Response: Thank you for noticing this missing connection. 
+  \item Change: We added a description connected to Figure 7a.
 \end{itemize}
@@
 \begin{itemize}
-  \item We added a parametric study in new Table 2 and the trend provides an idea about 
+  \item Response: We added a parametric study in new Table 2 and the trend provides an idea about 
 how to change vesicle stretching modulus and hydraulic permeability by adjusting the length related parameters or force related parameters.
@@
 convergence study.
+\item Change: We added a new Table 2 in page 16.
 \end{itemize}

### 2022-02-15 doc/reviews/ResponseToReviewer2.tex

--- 2022-02-14 doc/reviews/ResponseToReviewer2.tex
@@
 \begin{itemize}
-  \item Thank you for noticing this oversight. The definition of HAP has
-    been added at its first occurrence in Section 3.1. 
+  \item Response: Thank you for noticing this oversight. 
+  \item Change: The definition of HAP has been added at its first occurrence in Section 3.1. 
 \end{itemize}
@@
 \begin{itemize}
-  \item The velocity ${\bf u}({\bf x})$ introduced in the mobility problem (eqn.
+  \item Response: The velocity ${\bf u}({\bf x})$ introduced in the mobility problem (eqn.
 (2.1)--(2.3)) is in bold face and of a vector form.
@@
 Therefore there is no duplication of usage in notation.
-In reponse to this point, in order to avoid confusions, we changed the scalar function to $\eta$.
+  \item Change: In response to this point, in order to avoid confusions, we changed the scalar function to $\eta$.
 \end{itemize}
@@
 \begin{itemize}
-  \item We had used $\rho$ to denote the distance between source and
+  \item Response: We had used $\rho$ to denote the distance between source and
     target points in one of the layer potentials. This has been removed.
 
-  \item We now use $\rho$ to denote the HAP decay length and $\rho_0$ to
+  \item Change: We now use $\rho$ to denote the HAP decay length and $\rho_0$ to
     denote the cutoff for the repulsion force.
@@
 \begin{itemize}
-  \item We now reserve $\boldsymbol{\nu}$ for the normal vector and
+  \item Response: We thank the referee for this oversight.
+  \item Change: We now reserve $\boldsymbol{\nu}$ for the normal vector and
     $w_i$ denote the scalar what we previously defined to be $\nu_i$.
@@
 \begin{itemize}
-  \item Change 1 
+  \item Response: We thank the referee for this comment.
+For impermeable vesicles, the referee is correct about the numerical errors reported in the literature.
+However, the Janus membrane is permeable and in our simulations we found that the Janus vesicle needs time so the Janus particles in the membrane can re-arrange themselves.
+During this process of rearrangement the Janus bilayer membrane behaves as a permeable membrane as in Quaife, Gannon and Young (PRF 2021).
+For a Janus vesicle in a linear shear flow with a shear rate of dimensionless shear $\chi = 0.002$ the enclosed area reaches a nearly constant value after $1$ $\mu$s.
+We would like to point out that this is not a numerical error, but a consequence of Janus particle hydrodynamics that gives rise to membrane permeability.
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+  \item Response: Our current numerical method does not support a viscosity contrast in the system 
+or the setup similar to the ones in (Veerapaneni {\sl et al.}, {\bf 2011}, Phys. Rev. Lett.),
+(Vlahovska and Gracia, {\bf 2007}, Phys. Rev. E), and
+(Kaoui and Harting, {\bf 2016}, Rheol Acta). 
+As described in the manuscript, the JP vesicle is permeable and the mixture of two different
+fluids has to be analyzed within the framework, which would introduce a contact line between fluid 1- JP and fluid 2 -JP boundaries on the Janus particle surface.
+It is an interesting problem and we plan to study this in the future after we establish some basic knowledge of JP vesicle dynamics in a simpler configuration here.
+
 \end{itemize}

### 2022-02-15 doc/main_jfm.tex

@@
 
-\cite{Brandner2019} used the coarse-grained force field with a lattice
-Boltzmann molecular dynamics to simulate the hydrodynamics of a
-nano-sized vesicle under a shear flow.  In MD simulations, the
-hydrodynamic interactions for the solvent phase are often approximated
-by an implicit solvent coarse-grained model.  In the present work, the
-hydrodynamic interactions come from the mobility problem for the Stokes
-equations for the incompressible, viscous solvent.
+%\cite{Brandner2019} used the coarse-grained force field with a lattice
+%Boltzmann molecular dynamics to simulate the hydrodynamics of a
+%nano-sized vesicle under a shear flow.  In MD simulations, the
+%hydrodynamic interactions for the solvent phase are often approximated
+%by an implicit solvent coarse-grained model.  In the present work, the
+%hydrodynamic interactions come from the mobility problem for the Stokes
+%equations for the incompressible, viscous solvent.
 
@@
 stiffness, but with the presence of the hydrophobic forces, we maintain
-contact-free suspensions with a relatively weak non-stiff repulsive
-force.
+contact-free suspensions with a relatively \textcolor{red}{soft} repulsive
+force \textcolor{red}{(compared to the short-range repulsion that diverges in the Lennard-Jones potential)}.
 

### 2022-02-15 doc/reviews/ResponseToReviewer3.tex
main, refs, Review1,3

@@
 \item Change: We added sentences to describe how the lubrication hydrodynamics in a narrow space between boundaries is well-captured within the boundary integral formulation in page 4, starting in line 129.
-
+  Then, in section 4.1 \textit{Model Parameters}, we show quantitatively that the lubrication and
+  artificial repulsion are comparable for our simulation parameters.
 \end{itemize}
@@
 \begin{itemize}
-  \item  Response: This part needs to be fixed with the FFT of the data that Rolf sent to Bryan.
-  {\sl What follows is from Peter:
-  Fig.~3(c) clearly shows that the total length of the JP vesicle has a steady periodic motion 
-which is different from the trends shown in panels (a) and (b). We showed the actual time evolution of $A^*$ and $\Delta$ and fitting curves in (a). 
-The idea is to show that we can use the fitting data to acquire the numerical expected teminal 
-reduced area $A^*_\infty$. Therefore the multiple frequencies during simulations have no correlations between
-the output in (c) and (d).}
+\item Response: We thank the Reviewer for pointing out this feature of
+  the curves.  We analyzed the outputs more carefully and concluded that
+  the noted frequencies correspond to the tank-treading of the slightly
+  polygonal vesicle and particles, respectively.
 
-\item Change:
+\item Change: We modified the second to last paragraph in Section 4.1.
+  Moreover, we scaled the abscissas of Figure 3 to percent, and corrected
+  a scaling factor in the time axes.
 

### 2022-02-15 doc/main_jfm.tex
main, refs, Review1,3

@@
 $\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
-$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
-prevent particle collisions. 
-\textcolor{magenta}{
-The high-order interpolation-based quadrature rule used to compute the nearly-singular integrals has
-been shown to well capture the lubrication hydrodynamics in the narrow space between boundaries 
-when the repulsive potential $P$ gives a large steric force \cite{qua-bir2014}.  
-In the simulations we adjust the spatial resolution on the particle boundary to ensure that the lubrication hydrodynamics is well resolved as in \cite{qua-vee-you2019,qua-gan-you2021}.
-}
-%
+$P(r) = M(1 - \sin(r/\rho_0))$.
 Then, the total imposed force and torque
@@
 \end{equation}
+
+\ReviewerThree{
+The high-order interpolation-based quadrature rule used to compute the nearly-singular integrals has
+been shown to well capture the lubrication hydrodynamics in the narrow space between boundaries 
+when the repulsive potential $P$ gives a large steric force \cite{qua-bir2014}.  
+In the simulations we adjust the spatial resolution on the particle boundary to ensure that the lubrication hydrodynamics is well resolved as in \cite{qua-vee-you2019,qua-gan-you2021}.
+}
+%
 
@@
 \end{equation}
-on $\Gamma_i$ (see, e.g. \cite{KlBaGrON13}). Therefore,
+on $\Gamma_i$ (see, e.g., \cite{KlBaGrON13}). Therefore,
 \begin{align*}
@@
 The base-case is a single JP vesicle consisting of $N_b = 58$ particles
-with $c = 0.5 l_0$ for particle radius, $\rho = 2 l_0$ for decay length, $\rho_0 = 0.2l_0$ for repulsion
-length, $M=4.0$~$k_BT$ for repulsion strength, $\gamma = \text{4.1 pN
-nm}^{-1}$ for interfacial tension.  The parameter $\mu = \text{1 cP} = \text{1 pN
+with $c = 0.5 l_0$ for particle radius, $\rho = 2 l_0$ for decay length,
+$\gamma = \text{4.1 pN nm}^{-1}$ for interfacial tension.
+The parameter $\mu = \text{1 cP} = \text{1 pN
 ns nm}^{-2}$ is viscosity of room-temperature water. 
+\ReviewerThree{
+  We select \ReviewerOne{$M=4.0$~$\text{pN}$} and $\rho_0 = 0.2l_0$ so that \eqref{eq:REPULforce}
+  prevents particle collisions and is comparable to hydrodynamic lubrication.
+  \cite{cawthorn_balmforth_2010} provide the asymptotic expression 
+  $F_{\text{lubr}} = -\tfrac{3}{2}\pi \mu \dot \epsilon (c/\epsilon)^{3/2}$
+  for the lubrication force between two cylinders in the distance of separation $\epsilon \to 0$.
+  For our choice of simulation parameters, $F_{\text{lubr}}$ and \eqref{eq:REPULforce} are comparable
+  because the particle gaps smaller than the particle radius
+  and the relative velocities $\dot \epsilon$ between particles are on
+  the order of nm $\text{ns}^{-1}$.
+}
 
@@
   leaflet has slid past the inner leaflet. The slopes of the curves
-  give the slip velocity. With the exception of $\chi = 0.0035$, the
-  slip velocity is generally monotonic in the shear rate.}
+  give the slip velocity. 
+  Slip velocity is generally monotonic in the shear rate.
+  The case $\chi = 0.003$ is an exception.}
 \end{figure}
@@
 value $A^*_{\infty}$. The data in panel (a) are fit to the model $A^* =
-(A^*_{\infty}-a_1-a_2) + a_1 \exp(-k_1t) + a_2 \exp(-k_2t),$ $0 < k_2 <
+A^*_{\infty} + a_1 \exp(-k_1t) + a_2 \exp(-k_2t),$ $0 < k_2 <
 k_1$. Panel (d) shows that $A^*_{\infty}$ decreases with the shear rate.
@@
 
-The oscillations in the data of Figure~\ref{figure4} are due to the
-granularity of the JP vesicle. The inset of Figure~\ref{figure4}c zooms
+\ReviewerThree{The time courses contain oscillations due to the
+granularity of the JP vesicle.
+The curve for $\chi = 0.003$ in Figure~\ref{figure4}a, for example, 
+has a low-frequency oscillation with a period around $0.7$ $\upmu$s,
+and a high-frequency oscillation with a period four times smaller.
+The JP vesicle is somwhat hexagonal (see, e.g., Figure~\ref{figure5}a)
+and the low-frequency oscillations corresponds to the tank-treading of a 
+polygon, rather than smooth, curve. The higher frequency oscillations
+comes from the trank-treading of individual particles, that is
+it corresponds to the rate of passage of particles through a fixed-angle
+axis about the vesicle centre.} 
+The inset of Figure~\ref{figure4}c zooms
 in on the arc length data for the shear rate $\chi = 0.003$. It shows
-that the oscillations are smooth and well-resolved by our second-order
+that the curves are smooth and well-resolved by our second-order
 Adams-Bashforth scheme.
@@
 %Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
-\ReviewerOne{Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the default number of particles is $N_b = 58$.
+\ReviewerOne{Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the baseline number of particles is $N_b = 58$.
 With the fixed total length of the JP vesicle, we change parameters related to the length scale, for instances, $\rho$, $\rho_0$, and the radius of particles.
@@
 %permeability constant $P$. In spite of producing these values with some discrepancy
-%using the default parameter set, we provide a new framework in measuring coarse-grained 
+%using the baseline parameter set, we provide a new framework in measuring coarse-grained 
 %membrane permeability.

### 2022-02-15 doc/main_jfm.tex
main, refs, Review1,3

@@
 and a high-frequency oscillation with a period four times smaller.
-The JP vesicle is somwhat hexagonal (see, e.g., Figure~\ref{figure5}a)
+The JP vesicle is somewhat hexagonal (see, e.g., Figure~\ref{figure5}a)
 and the low-frequency oscillations corresponds to the tank-treading of a 

### 2022-02-15 doc/main_jfm.tex
main, refs, Review1,3

@@
 polygon, rather than smooth, curve. The higher frequency oscillations
-comes from the trank-treading of individual particles, that is
-it corresponds to the rate of passage of particles through a fixed-angle
+come from the trank-treading of individual particles, that is
+they correspond to the rate of passage of particles through a fixed-angle
 axis about the vesicle centre.} 

### 2022-02-15 doc/main_jfm.tex
main, refs, Review1,3

@@
   For our choice of simulation parameters, $F_{\text{lubr}}$ and \eqref{eq:REPULforce} are comparable
-  because the particle gaps smaller than the particle radius
+  because the particle gaps are comparable to the particle radius
   and the relative velocities $\dot \epsilon$ between particles are on

### 2022-02-15 doc/main_jfm.tex
type

@@
 The high-order interpolation-based quadrature rule used to compute the nearly-singular integrals has
-been shown to well capture the lubrication hydrodynamics in the narrow space between boundaries 
-when the repulsive potential $P$ gives a large steric force \cite{qua-bir2014}.  
-In the simulations we adjust the spatial resolution on the particle boundary to ensure that the lubrication hydrodynamics is well resolved as in \cite{qua-vee-you2019,qua-gan-you2021}.
+been shown to capture well the lubrication hydrodynamics in the narrow space between boundaries 
+when the repulsive potential $P$ gives a large steric force \citep{qua-bir2014}.  
+In the simulations we adjust the spatial resolution on the particle boundary to ensure that the lubrication hydrodynamics is well resolved as in \citep{qua-vee-you2019,qua-gan-you2021}.
 }
@@
   \includegraphics[width=\textwidth]{Figure13_Wrapper.pdf}
-  \caption{\label{figure13} Comparisons between the proposed model and a conitnuum model in 
+  \caption{\label{figure13} Comparisons between the proposed HAP model and a continuum model in 
   two JP vesicle simulations. 

### 2022-02-16 doc/reviews/ResponseToReviewer1.tex
main, refs, Review1,3
yny 5th today

@@
 \begin{itemize}
-  \item {\bf Response to Summary}: 	We thank the Reviewer for the assessmnet of our manuscript submission. In response
-to the comments, we have undertaken a major revision in including parametric studies and quantitative comparisons between models. We perforemed a number of simulations 
+  \item {\bf Response to Summary}: 	We thank the Reviewer for the assessment of our manuscript submission. In response
+to the comments, we have undertaken a major revision in including parametric studies and quantitative comparisons between models. We performed a number of simulations 
 in studies of inter-monolayer friction coefficients and an additional numerical investigation 
-of permeabilities. We have ensured that all figures are conneted with the corresponding content. 
+of permeabilities. We have ensured that all figures are connected with the corresponding content. 
   \begin{quotation}
@@
   \item Response: We agree with the Reviewer that we briefly illustrated the capability of simulating membrane rupture via the proposed model and numerical algorithm in the first submission of the manuscript.
-We further performed a series of study to find the critical shear rate for the appearance of membrane rupture and the correspnding movie is added as a supplementary material.
+We further performed a series of study to find the critical shear rate for the appearance of membrane rupture and the corresponding movie is added as a supplementary material.
 We also included the description in the section of membrane rupture.
@@
 We deleted the disconnected paragraph that started with "Brandner...." and modified the end of the following paragraph in response to the next comment from the reviewer.
-  \item Change: The paragraph ``Brandner {\it et al} (2019) used the coarsae-grained...." is removed.
+  \item Change: The paragraph ``Brandner {\it et al} (2019) used the coarse-grained...." is removed.
 \end{itemize}
@@
 \begin{itemize}
-  \item Response: All physical quantities in membrane mechanics such as interfacial tension, bending  modulus, and energy constant in pairwise interactions are defined in units of $k_BT$. 
+\item We thank the reviewer for pointing this out.  This was a typo which has now been corrected. 
 \end{itemize}
@@
 \noindent
-\comment{Related question: how much does the interparticle distance
+\comment{Related question: how much does the inter-particle distance
 depend on on the strength and range of this artificial repulsive

### 2022-02-16 doc/reviews/ResponseToReviewer2.tex
yny 5th today

@@
 \begin{itemize}
-  \item {\bf Response to Summary}: We thank the Reviewer for this positive appraisal of 
-our manuscript. The proposed 2D JP vesicle model has a geometrical property 
-of constant perimeter with a finite number of particles.
-Study of the permeability gives a numerical evidence that the constant area constraint of this enclosed bilayer structure does not apply in this
-work. In response, we performed a number of simulations and provided more parametric study in 
-terms of small changes in parameters. 
+  \item {\bf Response}: We thank the Reviewer for this positive appraisal of our manuscript.  
+The goal of our work, however, is not to provide an alternative vesicle model that outperforms pre-existing continuum models for a lipid bilayer vesicle in the literature.
+Inspired by de Gennes' suggestion of a thin film from self-assembly of Janus particles, we provide a model for the dynamics of Janus particles that self-assemble into a bilayer (JP vesicle) under various flowing conditions.
+As we showed in the manuscript, there are a lot of similarities between the JP vesicle and the lipid bilayer vesicle reported in the literature.
+
+To highlight both the similarity and difference between our JP vesicle and the lipid bilayer vesicle, we study (1) the hydrodynamics of a JP vesicle in various flow conditions to compare with the corresponding results for a lipid bilayer vesicle,
+and (2) we compute the friction between the two JP leaflet, and the permeability of a JP bilayer.
+We find that the permeability of a JP vesicle allows the total water content enclosed in the JP vesicle to reach an equilibrium value in a flow.
+We find that the JP vesicle is actually closer to a permeable vesicle that we studied previously, where the 2D vesicle has a constant perimeter but the enclosed area does not stay constant.
+
+In terms of validation of our numerical results of JP vesicle of nano meter size, we have made comparison with the simulations of vesicle of the same size in the literature.
+For example we compare both the permeability and the inter-leaflet friction coefficient of a JP bilayer membrane with those of a lipid bilayer membrane.
+We also compare the critical shear rate for rupture between a JP vesicle and a lipid bilayer vesicle.
+We also compared the hydrodynamics of a JP vesicle and a lipid bilayer vesicle under various flowing conditions.
+These results are summarized in the original manuscript and re-organized in the revision with better clarity.
+
+Finally we provide a critical capillary number for rupture of a JP vesicle under a linear shear flow.
+The rupture of a lipid vesicle by a linear shear flow has been reported in experiments.
+Our prediction of a critical capillary number and how it scales with various physical parameters of the individual Janus particle is, to our knowledge, not available in the literature.
+We hope that our results can motivate experimentalist (such as Charles Schroeder who has studied extreme deformation of a vesicle due to an imposed flow) and other theoreticians to study the dynamics of bilayer structures under extreme flowing conditions.
+
 %  \begin{quotation}

### 2022-02-16 doc/main_jfm.tex

@@
   prevents particle collisions and is comparable to hydrodynamic lubrication.
-  \cite{cawthorn_balmforth_2010} provide the asymptotic expression 
+  \citep{cawthorn_balmforth_2010} provide the asymptotic expression 
   $F_{\text{lubr}} = -\tfrac{3}{2}\pi \mu \dot \epsilon (c/\epsilon)^{3/2}$

### 2022-02-16 doc/main_jfm.tex
yny 6th today

@@
 %\title{Two-Dimensional Vesicles Under External Flow via Integral Equation Method}
-\title{Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential}
+\title{Two-Dimensional Hydrodynamics of a Janus Particle Vesicle}
 %\title{Hydrodynamics of Amphiphilic Particles in Background Flows}
@@
   and at large shear rates, membrane rupture. 
-  The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
-  interactions in shear and extensional flows. The hydrodynamics of the Janus 
-  particles vesicle replicate the behaviour of an inextensible elastic vesicle membrane.
+  The simulations studies include a Janus particle vesicle in both linear and parabolic shear flows,  and 
+  interactions between two Janus particle vesicles in shear and extensional flows. The hydrodynamics of the Janus 
+  particles vesicle is similar to the behaviour of an inextensible elastic vesicle membrane with permeability.
 %    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
@@
 
-We require a numerical method to avoid unphysical contact between rigid
+To simulate the hydrodynamics of Janus particles in Stokes flow,
+we require a numerical method to avoid unphysical contact between rigid
 Janus particles. Optimization-based contact methods introduce
@@
 for low shear rates. 
+%\subsubsection{Membrane Ruptures}
+%\begin{figure}
+%\centering
+%\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
+%%\includegraphics[height=2in]{N58_rupt_0.pdf}
+%%\includegraphics[height=2in]{N58_rupt_200.pdf}
+%\\
+%%\includegraphics[height=2in]{N58_rupt_400.pdf}
+%%\includegraphics[height=2in]{N58_rupt_600.pdf}
+%  \caption{\label{figure8} Tank-treading leads to membrane rupture for
+%  large shear rates.} 
+%\end{figure}
+%A temporary fissure or a complete membrane rupture can occur at large
+%shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
+%when suspended in a shear flow. For $\chi = 0.1$, starting with a
+%circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
+%background flow and fissures appear in the bilayer structure in multiple
+%locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
+%ruptured vesicles form two planar micelles which are eventually carried
+%off by the flow (Figure~\ref{figure8}d). 
+%%
+%\ReviewerOne{An emperical numerical study has shown that the critical shear rate for a complete membrane rupture is $\chi=0.0655$.
+Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.}
+
 \subsubsection{Membrane Ruptures}
@@
 %
-\ReviewerOne{An emperical numerical study has shown that the critical shear rate for a complete membrane rupture is $\chi=0.0655$.
-Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.}
+
+\ReviewerOne{An emperical numerical study found that for the baseline parameter set,
+the dimensionless, critical shear rate is $\chi_*=0.0655$ so that the membrane ruptured whenever $\chi > \chi_*$
+  and did not rupture whenever $\chi < \chi_*.$ 
+  Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.
+  To further quantify the competition between shear and attraction,
+  we found that a 5 \% relative increase in the parameters $\gamma$ and $M$ 
+  resulted in a  4.24 \% relative increase in $\chi_*$, from $0.0655$ to $0.0688$.
+  A 5 \% decrease in the particle radius $c$ gave a -9.55 \% decrease in $\chi_*$
+  and a 10 \% increase in resting length $L_0$ gave a 20.61 \% decrease in critical shear rate $\chi_*$.
+  These relative changes suggest that there is dimensionless number $K$ given by 
+  \begin{equation}
+    \label{eq:CSR}
+  \mu \dot\gamma_* = K \frac{\gamma c^2}{\rho L^2}
+  \end{equation}
+  that relates hydrophobic attraction to the dimensional critical shear rate $\dot \gamma_* = \chi_* \text{ ns}^{-1}$.
+  Assuming a characteristic velocity $L\dot \gamma$, the number $K$ relates to the vesicle's capillary number
+  $\text{Ca} = K c^2/(\rho L)$. Here $\text{Ca}$ would be approximately $1.7$
+  so that surface forces are comparable to viscous forces.  
+  There is a related \emph{elastic} capillary number
+  $\tilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/\kappa$
+  used to characterize rheological properties of lipid bilayer membranes
+  where $R_0$ is vesicle radius $\kappa$ is bending rigidity \citep{VLAHOVSKA2009775, keller_skalak_1982}. 
+  Setting $\text{Ca}$ and $\tilde{\text{Ca}}$ equal, we can derive
+  \[
+  \kappa = \frac{\mu \dot \gamma_* R_0^3}{\text{Ca}}
+  \]
+  which yields $\kappa \approx 60$ pN $\text{nm}^{-1}$, which is a reasonable
+  value for the bending modulus of a lipid bilayer, for example \citep{NaTr00}.}
 

### 2022-02-16 doc/reviews/ResponseToReviewer3.tex
Review 3 done

--- 2022-02-15 doc/reviews/ResponseToReviewer3.tex
@@
 \noindent
-Thank you for handling the manuscript, and we would like to thank the
-reviewer for their positive and constructive comments. The attached
-manuscript addresses all the reviewer's comments and the result is what
-we believe is a stronger manuscript. An itemized list of the changes
-addressing the reviewer's comments are below. Changes to the manuscript
-from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
+We thank you for handling the manuscript and the
+Reviewers for carefully evaluating our work. 
+The revisions address all the comments and concerns
+raised by the Reviewers 
+and we believe the result is a significantly improved manuscript.
+An itemized list of the specific changes and responses follows.
+Changes to the manuscript from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
 \textcolor{green}{green}, and \textcolor{magenta}{magenta},
@@
 \begin{itemize}
-  \item We would like to thank the referee for the help with the presentation, which
-has been modied as follows.
+\item We thank the Reviewer for their positive feedback
+  and suggestions which have helped improve the content and presentation of the
+  manusript.
 %  \begin{quotation}
@@
 Rev.
-Fluids, where Quaife {\sl et al.} showed that the lubrication hydrodynamics (draining of fluid between two membrane) is well captured and the scaling of lubrication thin film is recovered.
+Fluids, where Quaife {\sl et al.} showed that the lubrication hydrodynamics (draining of fluid between two membrane) is well-captured and the scaling of lubrication thin film is recovered.
 
@@
 
-\item Change: We added sentences to describe how the lubrication hydrodynamics in a narrow space between boundaries is well-captured within the boundary integral formulation in page 4, starting in line 129.
-
+\item Change: We added added a paragraph at the end of Section 2.2 describing
+  how the lubrication hydrodynamics in a narrow space between boundaries is
+  well-captured within the boundary integral formulation.
+  Then, in section 4.1 \textit{Model Parameters}, we show quantitatively how the lubrication and
+  artificial repulsion are comparable when substituing for our simulation parameters.
 \end{itemize}
@@
 \begin{itemize}
-  \item Fig.~3(c) clearly shows that the total length of the JP vesicle has a steady periodic motion 
-which is different from the trends shown in panels (a) and (b). We showed the actual time evolution of $A^*$ and $\Delta$ and fitting curves in (a). 
-The idea is to show that we can use the fitting data to acquire the numerical expected teminal 
-reduced area $A^*_\infty$. Therefore the multiple frequencies during simulations have no correlations between
-the output in (c) and (d).
+\item Response: We thank the Reviewer for highlighting this qualitative aspect of
+  the curves.
+
+\item Change: We modified the second to last paragraph in Section 4.2.1,
+ noting that the frequencies correspond to the tank-treading of the slightly
+  polygonal vesicle and individual particles, respectively. 
+  Moreover, we scaled the abscissas of Figure 3 to percent, and corrected
+  an erroneous scale factor in the time axes. 
 \end{itemize}
@@
 \begin{itemize}
-  \item Fig.~6 shows snapshots for 4 time frames from 0 to 12 $\mu$s and the trajectory of the centriod is demonstrated.
-Therefore the dashed horizontal line of Fig.~6 represents time in units of $\mu$s and the vertical axis represents the scaled $y$ position of the centroid of the JP vesicle.
+\item Response: Fig.~6 shows 4 snapshots in the time frame from 0 to 12 $\mu$s along with the trajectory of the centriod.
+
+  \item Change: In the caption of Fig.~6,  we now clarify that the horizontal axis 
+    represents time and that the vertical axis has been scaled to make the
+    migration stand out.
+
 \end{itemize}
@@
 \begin{itemize}
-  \item We corrected the original Fig.~10 by plotting all continuous streamlines. We thank the Reviewer for pointing this out and this issue occurred due to a mistake made in post-processing
-steps. Moreover, we do expect some discontinuous streamlines where it occurs when a strealine flows across the JP vesicle interface.
+\item Response: We thank the Reviewer for pointing this out.
+  This issue occurred due to a limitation of the software used
+  to generate streamlines in post-processing.
+
+\item Change: We improved the software and the corrected streamlines now appear in Fig.~11.
+  As expected, the streamlines are continuous while their gradient is peicewise continuous
+  across the JP vesicle interface.
 \end{itemize}
@@
   \item The typo with ``well-know" is corrected, but colored in red
-    since it was pointed out by Reviewer 1.
+    since it was pointed out by Reviewer 1 as well.
 
@@
 
-  \item We have read through the manuscript and made grammatical
-    changes.
+  \item We have read through the manuscript and done our best to
+    remove further grammatical errors.
 

### 2022-02-16 doc/reviews/ResponseToReviewer2.tex
main

@@
 \noindent
-Dear Prof.~Petia Vlahovska,
+Dear Professor Petia Vlahovska,
 \\ \\
 \noindent
-Thank you for handling the manuscript, and we would like to thank the
-reviewer for their positive and constructive comments. The attached
-manuscript addresses all the reviewer's comments and the result is what
-we believe is a stronger manuscript. An itemized list of the changes
-addressing the reviewer's comments are below. Changes to the manuscript
-from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
+We thank you for handling the manuscript and the
+Reviewers for carefully evaluating our work. 
+The revisions address all the comments and concerns
+raised by the Reviewers 
+and we believe the result is a significantly improved manuscript.
+An itemized list of the specific changes and responses follows.
+Changes to the manuscript from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
 \textcolor{green}{green}, and \textcolor{magenta}{magenta},

### 2022-02-16 doc/main_jfm.tex
main

@@
 directions, respectively. We use the dimensionless shear rate $\chi =
-\dot \gamma$ (s$^{-1}$) ns.
+\dot \gamma$ ns.
 
@@
 \begin{tabular}{c c c c c c c c c c c c }
-& & & & & & & $\dot\gamma$  (ns$^{-1}$) & & & &\\
-\cline{1-11}\\
+  \hline
+& & & & & & $\dot\gamma$  (ns$^{-1}$)& & & & &
+  \\
   radius ($l_0$) &  $\rho$ ($l_0$) & $\rho_0(l_0)$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  & Average\\
 \cline{4-10}\\
-& $+ 10 \%$ &     & 0.50  & 0.51  &  0.44 & 0.52  & 0.45 &  0.57   &  0.62 & 0.52  \\ 
-& $+ 5 \%$ & & 0.54 & 0.41 & 0.35  & 0.37 & 0.43 & 0.76  & 0.70 & 0.51\\ 
+$-5 \%$ & $- 5 \%$ & $-5 \%$  & 0.22 & 0.36 & 0.41   & 0.45  & 0.45 & 0.44   & 0.44 & 0.40\\
 0.5 &  2.0 & 0.5    & 0.42 & 0.63 & 0.50   & 0.40  & 0.48  & 0.53 & 0.55 & 0.50 \\   % new
-& $- 5 \%$ &  & 0.22 & 0.36 & 0.41   & 0.45  & 0.45 & 0.44   & 0.44 & 0.40\\ 
+$+5 \%$ & $+ 5 \%$ & $+ 5 \%$  & 0.54 & 0.41 & 0.35  & 0.37 & 0.43 & 0.76  & 0.70 & 0.51\\ 
+$+ 10 \%$ & $+ 10 \%$ & $+ 10 \%$    & 0.50  & 0.51  &  0.44 & 0.52  & 0.45 &  0.57   &  0.62 & 0.52  
 \end{tabular} 
@@
 %
-\ReviewerOne{The overall trend shown in Table~\ref{table1} is values of $b$ decreases as $\rho$
-decreases and $b$ are}
-%over a range of shear rates which is 
+\ReviewerOne{The trends in Table~\ref{table1}
+  suggest that $b$ decreases with decreasing $\rho$, $\rho_0$, and particle radius.}
+Overall, the values for $b$ are 
 in good quantitative agreement with values previously reported in the literature.
@@
   There is a related \emph{elastic} capillary number
-  $\tilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/\kappa$
+  $\tilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/K_B$
   used to characterize rheological properties of lipid bilayer membranes
-  where $R_0$ is vesicle radius $\kappa$ is bending rigidity \citep{VLAHOVSKA2009775, keller_skalak_1982}. 
+  where $R_0$ is vesicle radius $K_B$ is bending rigidity \citep{VLAHOVSKA2009775, keller_skalak_1982}. 
   Setting $\text{Ca}$ and $\tilde{\text{Ca}}$ equal, we can derive
   \[
-  \kappa = \frac{\mu \dot \gamma_* R_0^3}{\text{Ca}}
+  K_B = \frac{\mu \dot \gamma_* R_0^3}{\text{Ca}}
   \]
-  which yields $\kappa \approx 60$ pN $\text{nm}^{-1}$, which is a reasonable
+  which yields $K_B \approx 60$ pN $\text{nm}^{-1}$, which is a reasonable
   value for the bending modulus of a lipid bilayer, for example \citep{NaTr00}.}
@@
   undergoes tank-treading motion like in the shear flow case. 
- \ReviewerThree{The horizontal dashed line represents time in units of $\mu$s and the vertical axis represents the scaled $y$ position of the centroid of the JP vesicle.}
+  \ReviewerThree{The horizontal dashed line represents time in units of
+    $\upmu$s and the vertical axis represents the scaled $y$ position
+    of the centroid of the JP vesicle.}
   The arrows
@@
 
+%\begin{table}
+%\caption{Stretching Moduli and Permeabilities}
+%\centering
+%\begin{tabular}{ c c c |c c| c |c }
+% radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (\mathrm{k_BT})$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$%^{-1}$pN$^{-1}$) \\
+%\hline      \hline 
+% 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
+% \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 5 \%$}  & 185$\pm5$  &  0.0292  \\ 
+% \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 10 \%$}  & 195$\pm5$  &  0.0294 \\ 
+% \multicolumn{3}{c|}{$- 5 \%$} & \multicolumn{2}{c|}{same}   & 184$\pm5$  &  0.0283 \\ 
+% \multicolumn{3}{c|}{$- 10 \%$} & \multicolumn{2}{c|}{same}   & 189$\pm6$  &  0.0252  \\ 
+%\end{tabular} 
+%\label{table2}
+%\end{table}
+%
+
 \begin{table}
@@
 \centering
-\begin{tabular}{ c c c |c c| c |c }
- radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (\mathrm{k_BT})$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
-\hline      \hline 
- 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
-%
- \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 5 \%$}  & 185$\pm5$  &  0.0292  \\ 
-%
- \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 10 \%$}  & 195$\pm5$  &  0.0294 \\ 
-%
- \multicolumn{3}{c|}{$- 5 \%$} & \multicolumn{2}{c|}{same}   & 184$\pm5$  &  0.0283 \\ 
-%
- \multicolumn{3}{c|}{$- 10 \%$} & \multicolumn{2}{c|}{same}   & 189$\pm6$  &  0.0252  \\ 
+\begin{tabular}{ c |c| c |c }
+ $k$ & $\lambda$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
+\hline    
+ 1  & 1  & 170$\pm9$   &  0.0296\\ 
+%
+ 1.05 & 1  & 185$\pm5$  &  0.0292  \\ 
+%
+ 1.10 & 1  & 195$\pm5$  &  0.0294 \\ 
+%
+ 1 & 0.95  & 184$\pm5$  &  0.0283 \\ 
+%
+ 1  & 0.9   & 189$\pm6$  &  0.0252  \\ 
 \end{tabular} 
@@
 The next two rows demonstrate the results when the tension related parameters $\gamma$ and $M$ are increased by 5$\%$ and 10$\%$. 
+The parameter $k$ is used to scale the force paramaters $\gamma, M \to k\gamma, kM$.
 The final two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$
+The parameter $\lambda$ is used to simultaneously scale length parameters;
+$\rho, \rho_0, c \to \lambda \rho, \lambda \rho_0, \lambda c$.
 This data comes from Figure \ref{figure2} which  plots the \emph{ratio} of the abscissa and ordinates
@@
 and has a minimum at $x_0$. 
-If $\gamma$ and $M$ are scaled by $c$, 
+If $\gamma$ and $M$ are scaled by a parameter $k$, 
 we can related the scaled energy to that of the baseline case by 
-\[E_c(x) = c(G(x) + H(x)).\]
+\[E_k(x) = k(G(x) + H(x)).\]
 Permeability does not change with like increases in $\gamma$ and $M$
-because the critical number for $E_c$, and hence inter-particle separations, are independent to $c$.
-The stretching modulus comes from $\frac{d^2E_c}{dx^2}$ and this 
-quantity varies proportionally with $c$.
+because the critical number for $E_k$, and hence inter-particle separations, are independent to $k$.
+The stretching modulus comes from $\frac{d^2E_k}{dx^2}$ and this 
+quantity varies proportionally with $k$.
 

### 2022-02-16 doc/reviews/ResponseToReviewer2.tex
main and reviewer 2

@@
   \item {\bf Response}: We thank the Reviewer for this positive appraisal of our manuscript.  
-The goal of our work, however, is not to provide an alternative vesicle model that outperforms pre-existing continuum models for a lipid bilayer vesicle in the literature.
-Inspired by de Gennes' suggestion of a thin film from self-assembly of Janus particles, we provide a model for the dynamics of Janus particles that self-assemble into a bilayer (JP vesicle) under various flowing conditions.
-As we showed in the manuscript, there are a lot of similarities between the JP vesicle and the lipid bilayer vesicle reported in the literature.
+    The goal of our work, however, is not to provide an alternative vesicle model that outperforms
+    pre-existing continuum models for a lipid bilayer vesicle in the literature.
+    Inspired by de Gennes' suggestion of a thin film from self-assembly of Janus particles,
+    we provide a model for the dynamics of Janus particles that self-assemble into a bilayer
+    (JP vesicle) under various flowing conditions. 
+    As we showed in the manuscript, there are a lot of similarities between the
+    JP vesicle and the lipid bilayer vesicle reported in the literature.
 
@@
 (2.7)--(2.9)).
-Therefore there is no duplication of usage in notation.
-  \item Change: In response to this point, in order to avoid confusions, we changed the scalar function to $\eta$.
+  We can see, however, how this might result in confusion. 
+\item Change: In response to this point, we changed the scalar function $u$ to $\eta$ throughout the manuscript.
+  The notation $\eta$ was used by Stjepan Marcelja to first pose the HAP formulation
+  (Croatica Chemica Acta, 1977).
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+\item Response: The Reviewer is correct that realistic bending moduli
+  and other elastic parameters can be deduced from simulation data.
+  At this point, however, we do not have an analytical connection between
+  the input and moduli and inputs, other than some scaling relationship.
+  Please see the next comment, though, regarding the bending and stretching
+  moduli.
+\item Change: In the beginning of Section 4.1,
+  we now point out that such an analysis was part of our previous work.  
 \end{itemize}
@@
 \begin{itemize}
-  \item Change 1 
+\item Response:  We thank the Reviewer for pointing out this interesting connection. 
+\item Change:  Reviewer 1 requested a parametric study of membrane rupture which
+  we now supply in Section 4.2.3. There we take up the present Reviewer's
+  suggestion and show how the critical rupture shear rate ties in with the capillary
+  number, and then use the capillary number to derive an effective bending rigidity. 
 \end{itemize}
@@
 For impermeable vesicles, the referee is correct about the numerical errors reported in the literature.
-However, the Janus membrane is permeable and in our simulations we found that the Janus vesicle needs time so the Janus particles in the membrane can re-arrange themselves.
-During this process of rearrangement the Janus bilayer membrane behaves as a permeable membrane as in Quaife, Gannon and Young (PRF 2021).
-For a Janus vesicle in a linear shear flow with a shear rate of dimensionless shear $\chi = 0.002$ the enclosed area reaches a nearly constant value after $1$ $\mu$s.
+However, the JP membrane is permeable and in our simulations we found that the Janus vesicle needs time so the Janus particles in the membrane can re-arrange themselves.
+During this process of rearrangement the JP bilayer membrane behaves as a permeable membrane as in Quaife, Gannon and Young (PRF 2021).
+For a JP vesicle in a linear shear flow with a shear rate of dimensionless shear $\chi = 0.002$ the enclosed area reaches a nearly constant value after $1$ $\mu$s.
 We would like to point out that this is not a numerical error, but a consequence of Janus particle hydrodynamics that gives rise to membrane permeability.
+
+\item Change: In response to Reviewer 1, we have rewritten Section 4.3 from scratch.
+  This section now performs a parametric study of membrane permeability.
 \end{itemize}
@@
 \begin{itemize}
-  \item Response: Our current numerical method does not support a viscosity contrast in the system 
+\item Change:
+  We now mention in the conclusion that our current numerical method does not support a viscosity contrast in the system 
 or the setup similar to the ones in (Veerapaneni {\sl et al.}, {\bf 2011}, Phys. Rev. Lett.),

### 2022-02-16 doc/main_jfm.tex
main and reviewer 2

@@
 \subsection{Model Parameters}
-\cite{Fu20} studied physical quantities for static JP vesicles. 
+\cite{Fu20} studied physical quantities for static JP vesicles
+\ReviewerTwo{and empitically deduced realistic bending moduli, stretching moduli,
+  and tilt moduli under reasonable assumptions for the input parameters.}
 In the present work, we study JP vesicles in various background flows.
@@
 as a function of particle size and interaction strength.
-An analysis of the relationship between particle shape on effective properties is beyond 
-the scope of the current paper.
 
@@
   resulted in a  4.24 \% relative increase in $\chi_*$, from $0.0655$ to $0.0688$.
-  A 5 \% decrease in the particle radius $c$ gave a -9.55 \% decrease in $\chi_*$
-  and a 10 \% increase in resting length $L_0$ gave a 20.61 \% decrease in critical shear rate $\chi_*$.
-  These relative changes suggest that there is dimensionless number $K$ given by 
+  A 5 \% decrease in the particle radius $c$, screening length $\rho$ gave a $-9.55$ \% decrease, $5.0 \%$ increase
+  respectively in $\chi_*$.
+  Finally, a 10 \% increase in resting length $L_0$ gave a 20.61 \% decrease in critical shear rate $\chi_*$.}  
+  \ReviewerOne{These relative changes suggest that there is dimensionless number $K$ given by 
   \begin{equation}
@@
   Assuming a characteristic velocity $L\dot \gamma$, the number $K$ relates to the vesicle's capillary number
-  $\text{Ca} = K c^2/(\rho L)$. Here $\text{Ca}$ would be approximately $1.7$
+  $\text{Ca} = K c^2/(\rho L)$. Based on the above data, $\text{Ca}$ would be approximately $1.7$
   so that surface forces are comparable to viscous forces.  
@@
 
-\subsection{Stretching and Permeability}
+\subsection{\ReviewerOne{Stretching and Permeability}}
 \label{sec:ves_in_quiescent}
@@
 \end{align}
-where $P = k/(\mu \Delta x)$ is a constant, $k$ is hydraulic permeability, 
+where $P = K/(\mu \Delta x)$ is a constant, $K$ is hydraulic permeability, 
 $\mu$ is the solvent viscosity, and $\Delta x$ is the 
@@
 
+Our current numerical method does not support a viscosity contrast
+like that found in
+\citep{PhysRevLett.106.158103,
+  PhysRevE.75.016313,
+  Kaoui2016}.
+The JP vesicle is permeable and the mixture of two different
+fluids requires an introduce of a contact line between
+the two phases.
+
 Our future goals include extending the current framework to a
@@
 algorithmic implementation including a fast summation method such as the
-fast multipole method. Another research direction is to include the
+fast multipole method. Oother research directions include
 fluctuating hydrodynamics for Brownian suspensions~(\cite{Bao2018}),
@@
 %This will result in Janus particles that include Brownian motion, 
-and this is critical to understand membrane diffusion. Finally, a more
+critical to understanding membrane diffusion,
+and an analysis of the relationship between particle shape on effective
+properties.
+Finally, more
 physical boundary conditions for the HAP model will allow us to draw

### 2022-02-16 doc/reviews/ResponseToReviewer1.tex
main and reviewer 1

@@
 \begin{itemize}
-  \item {\bf Response to Summary}: 	We thank the Reviewer for the assessment of our manuscript submission. In response
-to the comments, we have undertaken a major revision in including parametric studies and quantitative comparisons between models. We performed a number of simulations 
-in studies of inter-monolayer friction coefficients and an additional numerical investigation 
+\item {\bf Response to Summary}:
+  We thank the Reviewer for the positive assessment of our manuscript.
+  In hindsight, we can see how the first submission presented more a catalogue
+  of flow patterns and missed interesting opportunities.
+  In response, we have undertaken a major revision including parametric studies
+  and quantitative comparisons between models.
+  We performed a number of simulations 
+  studies of inter-monolayer friction and
+  made additional numerical investigation 
   of permeabilities. We have ensured that all figures are connected with the corresponding content. 
@@
 \begin{itemize}
-  \item Response: This comment encouraged us to present more convergence studies in the choices of model parameters.
-We made a worthwhile effort to perform a large number of simulations.
-We agree with the Reviewer that the particle/vesicle shape is complex with the setup therefore we adopted small changes in particle sizes and reported all the results.
-  \item Change: We revised Table 1 (page 12) and added Table 2 (page 16) to account for effective properties of vesicles with different size of particles.
-We added a short description of the new Table 1 in lines 354-359.
+\item Response: This comment encouraged us to present more convergence
+  studies in the choices of model parameters. We made a worthwhile
+  effort to perform a large number of simulations. We agree with the
+  Reviewer that the particle/vesicle shape is complex with the setup
+  therefore we adopted small changes in particle sizes and reported all the results.
+\item Change: We performed more than twenty new experiments to fill out Table 1
+  accounting for variations in particle size.  
+  We rewrote section 4.3 from scratch. 
+  Table 2 (page 17) now accounts for variations in particle size
+  and interfacial tension. The new text on page 17 rationalizes
+  the manner in which the effective properties vary by analyzing
+  how energy scales. 
 \end{itemize}
@@
 
+\begin{itemize}
+\item Response: We thank the Reviewer for this fruitful suggestion.
+  By tuning the shear rate, we were able to determine critical
+  shear rates for membrane rupture.  Then we studied the relative
+  change in critical shear rate as a function of model parameter
+  changes.
+\item Change:
+  The new text on Page 13 reports how critical shear rate changes
+  with model parameters, and uses these values to formulate
+  a dimensional scale factor.  Reviewer 2 suggested we make
+  a connection with the elastic capillary number, which we now do,
+  and we use this connection to derive an effective and realistic
+  bending rigidity.
+
+  Furthermore, We added a movie of vesicle rupture (Movie S4) in the supplementary material (page 25).
+\end{itemize}
+
 \noindent
@@
 \begin{itemize}
-  \item Response: We agree with the Reviewer that we briefly illustrated the capability of simulating membrane rupture via the proposed model and numerical algorithm in the first submission of the manuscript.
-We further performed a series of study to find the critical shear rate for the appearance of membrane rupture and the corresponding movie is added as a supplementary material.
-We also included the description in the section of membrane rupture.
-  \item Change: We added a short description of vesicle rupture (lines 374-376) in page 13. We added a movie of vesicle rupture (Movie S4) in the supplementary material (page 25).
 
+\item Response: The new Figure 13
+  makes a comparisons between the proposed HAP model and a continuum model for two vesicles
+  in shear flow and extensional flow.
+  The plots track the distance between the vesicle centroids 
+  and show quantitative agreement as well as qualitative differences.
+  One difference is that present model has an adhesion effect that
+  binds two vesicles in a shear flow.  
 \end{itemize}
@@
 \begin{itemize}
-  \item Response: We thank the Reviewer to point this out. There is a significant difference between 
-the proposed model in the manuscript and other continuum models in literatures. For example, refer to \emph{Rahimian, et al., J. Comput. Phys., 2011}, the 
-provided time scale is $\tau = \mu R_0^3/\kappa_B$ where $\mu$ the fluid viscosity and $\kappa_B$ the bending modulus.
+  \item Response:
+Other continuum models in literature
+like  \emph{Rahimian, et al., J. Comput. Phys., 2011}, 
+ provide a time scale $\tau = \mu R_0^3/\kappa_B$ where $\mu$ the fluid
+    viscosity and $\kappa_B$ the bending modulus, and 
     $R_0$ is the initial radius of the reference vesicle.
-Since the bending modulus results from the hydrophobic attraction between Janus particles and their dynamics in a viscous fluid in the proposed model, we thus scaled time with a realistic characteristic time ns.
-With the use of the detailed scaling laws described in section 4.1, we aim to have comparable
-numerical results against the experiments. Moreover, if we attempt to calculate the characteristic 
-time scale using characteristic length and energy scales, it will also result a value of order ns. 
-Since the system involves multiple length scales, diameter of the particle $l_0$ and size of the JP
-vesicle $R_0$, we decided to use ns to perform nondimensionalization for simplicity.
+    In our model, the bending modulus is an output and cannot be used
+    to formulate the adimensionalization a priori.
 
-Finally we did manage to come up with an appropriate capillary number to characterize the rupture of a Janus vesicle under a linear shear flow at a high shear rate.
+    We did manage to formulate an appropriate capillary number to characterize the rupture of a JP vesicles
+    under a linear shear flow at a high shear rate and derive a bending modulus that way.
 
-\item Change: Place where the critical capillary number is given and discussed.
+    One of the benefits of our nondimensionalization is that it enables
+    us to cover multiple time scales inherent to the particle-based formulation. 
+    It is possible form a time scale using the interfacial tension, as done
+    in our previous work (Fu {\sl et al.}, {\bf 2020}, Multiscale Model. Simul.),
+    This time scale is small, a few nanoseconds, and
+    corresponds to the times for particle self-assembly.
+    The time scale for the interesting vesicle deformations is longer,
+    on the order of microseconds.    
+    Finally, another benefit is that we can compare
+    results with molecular dynamics simulations
+    as well as with established continuum models.
 
@@
 \begin{itemize}
-  \item Response: We followed the suggestion given by the Reviewer that a summary about what to solve throughout the entire algorithm is provided at the end of Section 3.
-  \item Change: A short paragraph is added in page 8 (lines 248-253).
+\item Response: We followed the suggestion given by the
+  Reviewer that a summary about what to solve throughout the entire algorithm is provided at the end of Section 3.
+  \item Change: A summary paragraph was added on page 8.
 \end{itemize}
@@
 \begin{itemize}
-  \item Response: We thank the Review for having this meaningful comment and we agree that changing all the figure 
-to colorblind friendly colormap is insightful. We will make this change for all figures once the manuscript is accepted. All the new figures are made with colorblind friendly colormaps.
-
-\item Change: All the modified figures (Figs.~ 9, 10, 11, 12,  13) are made with colorblind friendly colormaps. 
+\item Response: We agree that changing all the figure 
+  to colorblind friendly colormap is helpful.  At this point,
+  we are still deciding what the best choice is for needed color
+  contrast and will make this change for all relevant figures once the
+  manuscript is accepted.
 \end{itemize}
@@
 $O(10^{-1})$ with no instability. Comparing the time step used in literatures, for instance, in Bystricky {\sl et al.}, {\bf 2020}, Int. J. Numer. Methods Fluids), $\Delta t\sim O(10^{-2})$.
-\item Change: We moved Section 2.3 to the end of Section 3 (Section 3.4, page 8, lines 243-248).
+\item Change: We moved Section 2.3 to the end of Section 3 (Section 3.4, page 8).
 \end{itemize}
@@
     been added at its first occurrence in Section 3.1. 
-  \item Change: This change is in \textcolor{green}{green} (page 5, line 144) since it was also pointed
+  \item Change: This change is in \textcolor{green}{green} (page 5) since it was also pointed
     out by Reviewer 2.

### 2022-02-16 doc/main_jfm.tex
main and reviewer 1

@@
   \includegraphics[width=\textwidth]{Figure13_Wrapper.pdf}
-  \caption{\label{figure13} Comparisons between the proposed HAP model and a continuum model in 
-  two JP vesicle simulations. 
-  $d_{1,2}$ is the distance between two centroids of JP vesicles. The thick curves plot the trajectories
+  \caption{\label{figure13} Comparisons between the proposed HAP model and a continuum model
+    for two vesicles in shear flow and in extensional flow.
+  The value $d_{1,2}$ is the distance between two centroids of JP vesicles. The thick curves plot the trajectories
   of $d_{1,2}$ generated by the continuum model and the thin curves are computed from using
-  the proposed model.}
+  the proposed HAP model.}
 \end{figure}

### 2022-02-16 doc/reviews/ResponseToReviewer1.tex
reviewer1

@@
   effort to perform a large number of simulations. We agree with the
-  Reviewer that the particle/vesicle shape is complex with the setup
-  therefore we adopted small changes in particle sizes and reported all the results.
+  Reviewer that analyzing dependence on particle shape is complex task.
+  Therefore we focus on changes in particle sizes and reported all the results.
 \item Change: We performed more than twenty new experiments to fill out Table 1
@@
   shear rates for membrane rupture.  Then we studied the relative
-  change in critical shear rate as a function of model parameter
-  changes.
+  change in critical shear rate as a function of model parameters.
+
 \item Change:
@@
   with model parameters, and uses these values to formulate
-  a dimensional scale factor.  Reviewer 2 suggested we make
+  a dimensional scale factor.  Reviewer 2 suggested that we make
   a connection with the elastic capillary number, which we now do,
@@
 
-  Furthermore, We added a movie of vesicle rupture (Movie S4) in the supplementary material (page 25).
+  Furthermore, we added a movie of vesicle rupture (Movie S4) in the supplementary material (page 25).
 \end{itemize}
@@
   and show quantitative agreement as well as qualitative differences.
-  One difference is that present model has an adhesion effect that
+  One difference is that the present model has an adhesion effect that
   binds two vesicles in a shear flow.  
@@
   \item Response:
-Other continuum models in literature
-like  \emph{Rahimian, et al., J. Comput. Phys., 2011}, 
+Other continuum models in the literature
+such as  \emph{Rahimian, et al., J. Comput. Phys., 2011}, 
  provide a time scale $\tau = \mu R_0^3/\kappa_B$ where $\mu$ the fluid
@@
     In our model, the bending modulus is an output and cannot be used
-    to formulate the adimensionalization a priori.
+    to formulate an adimensionalization.
 
@@
     us to cover multiple time scales inherent to the particle-based formulation. 
-    It is possible form a time scale using the interfacial tension, as done
-    in our previous work (Fu {\sl et al.}, {\bf 2020}, Multiscale Model. Simul.),
+    It is possible to pose a time scale using the interfacial tension, as done
+    in our previous work (Fu {\sl et al.}, {\bf 2020}, Multiscale Model. Simul.),=.
     This time scale is small, a few nanoseconds, and
@@
     on the order of microseconds.
+    Although this leads to longer simulation times, our approach can
+    handle topological changes which are presently out of reach for continuum methods. 
     Finally, another benefit is that we can compare
-    results with molecular dynamics simulations
-    as well as with established continuum models.
+    results with both molecular dynamics simulations
+    and established continuum models.
 
@@
 \item Response: We followed the suggestion given by the
-  Reviewer that a summary about what to solve throughout the entire algorithm is provided at the end of Section 3.
-  \item Change: A summary paragraph was added on page 8.
+  Reviewer that a summary about what to solve throughout the entire algorithm is helpful. 
+  \item Change: A summary paragraph was added on page 8, at the end of Section 3.
 \end{itemize}
@@
 \begin{itemize}
-\item Response: We agree that changing all the figure 
-  to colorblind friendly colormap is helpful.  At this point,
-  we are still deciding what the best choice is for needed color
+\item Response: We agree that changing all the figures 
+  to a colorblind friendly colormap is helpful.  At this point,
+  we are still deciding what the best choice is for color
   contrast and will make this change for all relevant figures once the
@@
   \item Response: We modified this description for better clarity.
-  \item Change: Page 3, lines 64-65, we changed ``relatively weak repulsive force" to ``relatively soft repulsive force" and added ``(compared to the short-range repulsion that diverges in the Lennard-Jones potential)".
+  \item Change: Page 3, we changed ``relatively weak repulsive force" to ``relatively soft repulsive force" and added ``(compared to the short-range repulsion that diverges in the Lennard-Jones potential)".
 
@@
 \begin{itemize}
-  \item Response: Section 2.2 introduces the imposed forces and torques in hydrophobic attraction and repulsion that are not used to obtain particle directions directly. Following the next comment by 
+\item Response: Section 2.2 introduces the imposed forces and torques in hydrophobic attraction.
+  Following the next comment by 
 the Reviewer, we agreed that Section 2.3 should be moved to the end of Section 3 and we complete the change.
@@
   \item Response: We thank the Review for the comment and we moved the original Section 2.3 {\it Time Marching} at the end of Section 3 combining the change based on the comment previously addressed about what to solve for in the proposed algorithm.
-As described in Section 2.2, the repulsion force with a constant strength coefficient $M$ is chosen 
+As newly described in Sections 2.2 and 4.1, the repulsion force with a constant strength coefficient $M$ is chosen 
 to be a large number in order to avoid particle collisions.
@@
 choices of M and $\gamma$, the parameter set in this work allows the time step to be as large as
-$O(10^{-1})$ with no instability. Comparing the time step used in literatures, for instance, in Bystricky {\sl et al.}, {\bf 2020}, Int. J. Numer. Methods Fluids), $\Delta t\sim O(10^{-2})$.
+$O(10^{-1})$ with no instability.
+%Comparing the time step used in literatures, for instance, in Bystricky {\sl et al.}, {\bf 2020}, Int. J. Numer. Methods Fluids), $\Delta t\sim O(10^{-2})$.
 \item Change: We moved Section 2.3 to the end of Section 3 (Section 3.4, page 8).
@@
 \begin{itemize}
-  \item Response: The term (1) means the magnitude of the corresponding $y$-axis is of order 1.
+  \item Response: We change the adimensional unit (1) to percent (\%) where appropriate. 
 \end{itemize}
@@
 \begin{itemize}
-  \item Response: A shear rate of order $10^{6}\text{s}^{-1}$ is too high to be generated in experiments.
+\item Response:
 Since the size of the JP vesicle in this work is much smaller than experimental use vesicles, 
 a very high shear rate of the flow is needed to acquire the tank-treading motion.
+A large shear rate of order $10^{6}\text{s}^{-1}$ is used in molecular dynamics
+simulations for systems of the same size as ours c.f., Brandner {\it et al} (2019).
 \end{itemize}
@@
   \item Response: Thank you for noticing this missing connection. 
-  \item Change: We added a description connected to Figure 7a.
+  \item Change: We replaced Figure 7a with one connected to the text.
 \end{itemize}

### 2022-02-16 doc/main_jfm.tex
finishing up main.tex

@@
 \ReviewerThree{
-The high-order interpolation-based quadrature rule used to compute the nearly-singular integrals has
-been shown to capture well the lubrication hydrodynamics in the narrow space between boundaries 
-when the repulsive potential $P$ gives a large steric force \citep{qua-bir2014}.  
-In the simulations we adjust the spatial resolution on the particle boundary to ensure that the lubrication hydrodynamics is well resolved as in \citep{qua-vee-you2019,qua-gan-you2021}.
+The high-order interpolation-based quadrature rule used to compute the
+nearly-singular integrals has been shown to accurately capture the
+lubrication hydrodynamics in the narrow space between boundaries when
+the repulsive potential $P$ gives a large steric
+force~\citep{qua-bir2014}. In the simulations we adjust the spatial
+resolution on the particle boundary to ensure that the lubrication
+hydrodynamics is well resolved as in~\citep{qua-vee-you2019,
+qua-gan-you2021}.
 }
@@
 \subsection{Time Marching}
-To summarize, the proposed algorithm aims to obtain the JP velocities ${\bf v}_i$ and $\omega_i$. 
-After calculating the imposed forces $\FF_i$ and torques $T_i$, 
-two density functions $\sigma$ and  $\eeta$ are solved in the second-kind integral equations involving the HAP~\eqref{eq:screenedSKIE} and the mobility problem~\eqref{eq:SKIE}-\eqref{eq:mobility2} via GMRES.
+To summarize, the proposed algorithm aims to obtain the JP velocities
+${\bf v}_i$ and $\omega_i$. After calculating the imposed forces $\FF_i$
+and torques $T_i$, two density functions $\sigma$ and  $\eeta$ are
+solved in the second-kind integral equations involving the
+HAP~\eqref{eq:screenedSKIE} and the mobility
+problem~\eqref{eq:SKIE}--\eqref{eq:mobility2} via GMRES.
 %By solving the mobility problem, we obtain translational and angular
@@
   and the relative velocities $\dot \epsilon$ between particles are on
-  the order of nm $\text{ns}^{-1}$.
+  the order of a nm $\text{ns}^{-1}$.
 }
@@
 
-\ReviewerOne{An emperical numerical study found that for the baseline parameter set,
-the dimensionless, critical shear rate is $\chi_*=0.0655$ so that the membrane ruptured whenever $\chi > \chi_*$
-  and did not rupture whenever $\chi < \chi_*.$ 
-  Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.
-  To further quantify the competition between shear and attraction,
-  we found that a 5 \% relative increase in the parameters $\gamma$ and $M$ 
-  resulted in a  4.24 \% relative increase in $\chi_*$, from $0.0655$ to $0.0688$.
-  A 5 \% decrease in the particle radius $c$, screening length $\rho$ gave a $-9.55$ \% decrease, $5.0 \%$ increase
-  respectively in $\chi_*$.
-  Finally, a 10 \% increase in resting length $L_0$ gave a 20.61 \% decrease in critical shear rate $\chi_*$.}  
+\ReviewerOne{An empirical numerical study found that for the baseline
+parameter set, the dimensionless, critical shear rate is $\chi_*=0.0655$
+so that the membrane ruptured whenever $\chi > \chi_*$ and did not
+rupture whenever $\chi < \chi_*.$ Supplementary Materials Movie 4 shows
+the membrane rupture at the critical shear rate.  To further quantify
+the competition between shear and attraction, we found that a $5 \%$
+relative increase in the parameters $\gamma$ and $M$ resulted in a $4.24
+\%$ relative increase in $\chi_*$, from $0.0655$ to $0.0688$.  A $5 \%$
+decrease in the particle radius $c$, screening length $\rho$ gave a
+$-9.55 \%$ decrease, $5.0 \%$ increase respectively in $\chi_*$.
+Finally, a $10 \%$ increase in resting length $L_0$ gave a $20.61 \%$
+decrease in critical shear rate $\chi_*$.}  
   \ReviewerOne{These relative changes suggest that there is dimensionless number $K$ given by 

### 2022-02-16 code/output/data/makeImages.m

@@ -4,14 +4,14 @@ set(0,'DefaultAxesFontSize',22)
 options.savefig = false;
 options.saveVelData = true;
 
-file = 'shear.bin';
+file = 'shearBryan.bin';
 velfile = 'shear_vel.bin';
 
 irate = 1; % controls the speed of the visualization
-ax = 5*[-1 1 -1 1];
+ax = 8*[-1 1 -1 1];
 % ax = [-1 6 -1 4];
 
-[yukawaRHS,posx,posy,xc,tau,time] = loadFile(file);
+[yukawaRHS,posx,posy,xc,tau] = loadFile(file);
 % load right hand side for Yukawa solve, positions, centers, inclination
 % angles, and times
 [velx,vely,torq] = loadVelFile(velfile);
@@ -54,7 +54,7 @@ for k = 1:irate:ntime;
   set(gca,'ytick',[])
   set(gca,'xcolor','white')
   set(gca,'ycolor','white')
-  titleStr = ['t = ' num2str(time(k),'%4.2e')];
+%  titleStr = ['t = ' num2str(time(k),'%4.2e')];
   title(titleStr)
   pause(0.01)
   if options.savefig

### 2022-02-16 doc/main_jfm.tex

@@
   There is a related \emph{elastic} capillary number
-  $\tilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/K_B$
+  $\widetilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/K_B$
   used to characterize rheological properties of lipid bilayer membranes
   where $R_0$ is vesicle radius $K_B$ is bending rigidity \citep{VLAHOVSKA2009775, keller_skalak_1982}. 
-  Setting $\text{Ca}$ and $\tilde{\text{Ca}}$ equal, we can derive
+  Setting $\text{Ca}$ and $\widetilde{\text{Ca}}$ equal, we can derive
   \[

### 2022-02-16 doc/Supplementary.tex
final updates

@@
 Bryan Quaife$^{2},$ 
-Rolf J. Ryham$^{1},$ 
+Rolf Ryham$^{1},$ 
 Y.-N. Young$^{3},$
@@
 \noindent
-{\bf Movie S6. Single Vesicle Suspended in an Extensional Flow} 
-There are two relaxed JP vesicles suspended in a shear flow.The centroid of the left JP vesicle is 0.25 nm above the $x$-axis and the right JP vesicle is 0.25 nm below the $x$-axis.
+{\bf Movie S6. Two Vesicles Suspended in an Extensional Flow} 
+There are two relaxed JP vesicles suspended in an extensional flow.
+The centroid of the left JP vesicle is 0.25 nm above the $x$-axis and the right JP vesicle is 0.25 nm below the $x$-axis.
 The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1.
 All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-This movies includes a total 6000 time steps where the time step is $\Delta t=0.2$.\\
-
+This movies includes a total 6000 time steps where the time step is $\Delta t=0.2$.
 %%%\end{document}

### 2022-03-07 code/src/capsules.m
worked on matrix-free version

@@ -33,6 +33,7 @@ NPeaks;       % change the number of peaks in cosine bc
 BK1;          
 % besselk(1,~) function evaluated for each target point with upsampled
 % source points on all other bodies
+StokesDL;
 
 end %properties
 
@@ -101,6 +102,7 @@ o.RepulStrength = prams.RepulStrength;
 % repulsion length and strength
 
 o.BK1 = [];
+o.StokesDL = [];
 
 end % capsules: constructor
 
@@ -136,13 +138,19 @@ for k = 1:nb
   [xsou,ysou] = oc.getXY(geom.X(:,Ksou));
   xsou = interpft(xsou,Nup);
   ysou = interpft(ysou,Nup);
+  [~,tangent] = oc.diffProp([xsou;ysou]);
+  [tx,ty] = oc.getXY(tangent);
   xsou = xsou(:); ysou = ysou(:);
   xsou = xsou(:,ones(N,1))';
   ysou = ysou(:,ones(N,1))';
 
-  [tx,ty] = oc.getXY(geom.xt(:,Ksou));
-  nx = interpft(-ty,Nup); nx = nx(:);
-  ny = interpft(+tx,Nup); ny = ny(:);
+  % wrong way of computing the normal vector of upsampled shapes
+%  [tx,ty] = oc.getXY(geom.xt(:,Ksou));
+%  nx = interpft(-ty,Nup); nx = nx(:);
+%  ny = interpft(+tx,Nup); ny = ny(:);
+
+  nx = -ty; nx = nx(:);
+  ny = tx; ny = ny(:);
   nx = nx(:,ones(N,1))';
   ny = ny(:,ones(N,1))';
 
@@ -152,15 +160,68 @@ for k = 1:nb
   geom.BK1(:,:,k) = -1/2/pi/geom.rho*besselk(1,dis/geom.rho).*rdotn./dis;
 end
 
-
 end % BesselDistanceMatrix
 
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function StokesDLMatrix(geom)
+% StokesDLMatrix(o,geom) computes the Stokes double-layer potential
+% between all pairs of points on different bodies. This is used to
+% accelerate the number of times exactStokesDL has to be evaulated when
[…]

### 2022-03-07 code/src/monitor.m

@@ -244,7 +244,7 @@ if o.usePlot
 end
 
 
-end % plotData
+end % plotField
 
 
 end % methods

### 2022-03-07 code/src/poten.m

@@ -31,8 +31,6 @@ o.interpMat = o.lagrangeInterp;
 
 o.N = N;
 o.rho = rho;
-%o.upRate = ceil(sqrt(N));
-%o.BK1 = [];
 
 end % poten: constructor
 
@@ -110,11 +108,11 @@ prams.shape = geomSou.shape;
 prams.petal = geomSou.petal;
 % parameters that we will need when building the upsampled geometry
 
-
 geomUp = capsules(prams,geomSou.center,geomSou.tau);
 % Build an object with the upsampled geom
 geomUp.BK1 = geomSou.BK1;
-% already computed the necessary besselk matrix
+% already computed the necessary Stokes DLP matrix
+geomUp.StokesDL = geomSou.StokesDL;
 
 interpOrder = size(o.interpMat,1);
 % lagrange interpolation order
@@ -426,8 +424,6 @@ for k=1:geom.nb  % Loop over curves
   % normal that points into each body (ie. outward normal)
   nx = nx(:,ones(Ng,1))';
   ny = ny(:,ones(Ng,1))';
-%  kernel = diffx.*(tysou(ones(Ng,1),:)) - ...
-%            diffy.*(txsou(ones(Ng,1),:));
 
   sa = geom.sa(:,k)'; % Jacobian
   cur = geom.cur(:,k)'; % curvature
@@ -457,8 +453,6 @@ for k=1:geom.nb  % Loop over curves
 
   D11 = 1/2/pi/geom.rho.*besselk(1,r12/geom.rho).*...
       rdotn./r12.*sa;
-%  omega = 1i*geom.rho;
-%  kernel = -1i/4*(omega*r12).*besselh(1,omega*r12);  
 
   D11(1:Ng+1:Ng^2) = +0.25/pi*cur.*sa(1,:);
   D(:,:,k) = D11;
@@ -491,11 +485,7 @@ for k=1:geom.nb  % Loop over curves
   yy = y(:,k);
 
   % normal vector
-  normal = [geom.xt(Ng+1:2*Ng,k) -geom.xt(1:Ng,k)]; % Normal vector(y)  
-  
-%   [tx,ty] = oc.getXY(geom.xt);
-%   tx = tx(:,k); ty = ty(:,k);
-%   % Vesicle tangent
+  normal = [geom.xt(Ng+1:2*Ng,k) -geom.xt(1:Ng,k)];
 
   % Jacobian
   sa = geom.sa(:,k)';
[…]

### 2022-03-07 code/src/rigid2D.m

@@ -9,7 +9,6 @@ tt = tstep(options,prams);
 % build initial condition of rigid body particle
 geom = capsules(prams,xc,tau);
 % plot geometry if usePlot == true
-om.plotData(geom);
 
 om.initializeFiles(geom);
 
@@ -30,11 +29,6 @@ while step <= prams.m
   % start a timer for this particular time step
   tSingleStep = tic;   
 
-%  msg = ['Yukwa reguired  ' num2str(iterYukawa) ' iterations'];
-%  om.writeMessage(msg);
-%  msg = ['Stokes reguired ' num2str(iterStokes) ' iterations'];
-%  om.writeMessage(msg);
-
   % comupute density function, translational velocity, angular velocity,
   % and the GMRES output
 
@@ -51,7 +45,8 @@ while step <= prams.m
     if step == step0
       % update geometry
       geom0 = capsules(prams,xc0,tau0);
-      [Up0, wp0,~,~,etaY0,etaS0,force,torque] = tt.timeStep(geom0,geom0.X,geom0.X);
+      [Up0, wp0,~,~,etaY0,etaS0,force,torque] = tt.timeStep(...
+          geom0,geom0.X,geom0.X);
 
       % write the velocity to a file
       om.writeVelData(time,Up0,wp0);
@@ -110,27 +105,25 @@ while step <= prams.m
       ' of time horizon ' , num2str(prams.T,'%4.2e')];
   om.writeMessage(message);
   
-
-  
   % update tracers
   if options.tracer
-  XX = load("../examples/tracers.dat");
-  UU = load("../examples/tracer_vel.dat");
-   
-  XX = XX + tt.dt*UU;
-  
-  % pacman correction for points wandering out-of-bounds
-  il = find(XX(:,1) < options.plotAxis(1)); 
-  ir = find(XX(:,1) > options.plotAxis(2)); 
-  ib = find(XX(:,2) < options.plotAxis(3)); 
-  it = find(XX(:,2) > options.plotAxis(4)); 
-  
-  XX(il,1) = options.plotAxis(2);
-  XX(ir,1) = options.plotAxis(1);
-  XX(ib,2) = options.plotAxis(4);
-  XX(it,2) = options.plotAxis(3);
-  
-  save("-ascii", "../examples/tracers.dat", "XX");
+    XX = load("../examples/tracers.dat");
+    UU = load("../examples/tracer_vel.dat");
+     
[…]

### 2022-03-07 code/src/tstep.m

@@ -93,7 +93,6 @@ end
 geom.BesselDistanceMatrix;
 
 % Solve for the density function using GMRES
-%tic
 [sigma,iflagYukawa,resYukawa,iterYukawa] = gmres(...
       @(etaY0) o.timeMatVecYukawa(etaY0,geom) ,...
       yukawaRHS, [], o.gmresTol, N*nb, ...
@@ -103,8 +102,6 @@ geom.BesselDistanceMatrix;
 %      yukawaRHS, [], o.gmresTol, N*nb); 
 iterYukawa = iterYukawa(2);
 fprintf('Yukawa required %i iterations\n',iterYukawa);
-%toc
-%pause
 
 % Unstack the density function so that it is arranged as columns for
 % each body
@@ -191,6 +188,10 @@ o.precoStokesMatrix(geom);
 % max GMRES iterations
 maxit = 2*N*nb; 
 
+
+% Build the upsampled matrix for doing stokes Layer potentials
+geom.StokesDLMatrix;
+
 % SOLVE SYSTEM USING GMRES
 %tic
 
@@ -234,7 +235,8 @@ end
 % motion to define a velocity in rigid bodies. The goal is to see
 % something cotinuous
 if o.tracer
-    op.bulkVelocity(geom,etaStokes,Up,wp,force,torque, @(X) o.farField(X));
+  op.bulkVelocity(geom,etaStokes,Up,wp,force,torque,...
+      @(X) o.farField(X));
 end
 
 end % timeStep
@@ -286,6 +288,8 @@ valFibers = valFibers + jump*eta;
 % ADD SELF CONTRIBUTION
 valFibers = valFibers + op.exactStokesDLdiag(geom,geom.DLPStokes,eta);
 
+% Matrix-free version
+if 0
 % DEFINE STOKES DLP KERNELS
 kernel = @op.exactStokesDL;
 kernelSelf = @(z) +jump*z + op.exactStokesDLdiag(geom,geom.DLPStokes,z);
@@ -293,6 +297,18 @@ kernelSelf = @(z) +jump*z + op.exactStokesDLdiag(geom,geom.DLPStokes,z);
 % ADD CONTRIBUTION FROM OTHER FIBERS
 stokesDLP = op.nearSingInt(geom,eta,kernelSelf,geom.nearStruct,...
     kernel,kernel,geom,true,false);
+end
+
[…]

### 2022-03-07 doc/JFM2022/reviews/ResponseToReviewer3.tex
fixing directory structure so that we can publish more than one paper

--- 2022-02-16 doc/reviews/ResponseToReviewer3.tex
@@
 \noindent
-Dear Prof.~Petia Vlahovska,
+Dear Professor Petia Vlahovska,
 \\ \\
 \noindent
-We thank you for handling the manuscript and the
-Reviewers for carefully evaluating our work. 
-The revisions address all the comments and concerns
-raised by the Reviewers 
-and we believe the result is a significantly improved manuscript.
-An itemized list of the specific changes and responses follows.
-Changes to the manuscript from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
+We thank you for handling the manuscript and the Reviewers for carefully
+evaluating our work. The revisions address all the comments and
+concerns raised by the Reviewers and we believe the result is a
+significantly improved manuscript. An itemized list of the specific
+changes and responses follows. Changes to the manuscript from Reviewers
+1, 2, and 3 are colored in \textcolor{red}{red},
 \textcolor{green}{green}, and \textcolor{magenta}{magenta},
@@
 \item We thank the Reviewer for their positive feedback
-  and suggestions which have helped improve the content and presentation of the
-  manusript.
-%  \begin{quotation}
-%    \noindent
-%    Can put verbatim change in this environment.
-%  \end{quotation}
+  and suggestions which have helped improve the content and presentation
+    of the manuscript.
 \end{itemize}
@@
 \begin{itemize}
-  \item Response: The repulsive potential we used to prevent overlap of Janus particles is the repulsive Morse potential based on the electrostatic repulsive potential between two negatively (or positively) charged particles immersed in a medium of low electrolyte concentration so that there is a well-defined zeta potential on the charged particle (Coakley {\sl et al.}, 1999, Biophys.
-J).
-This repulsive potential has been approximated by the short-range repulsive Lennard-Jones potential (Flormann {\sl et al.}, 2017, Sci.
-Reports), which has been adopted by Quaife and Young to study the interaction between two membranes in a viscous solvent in Quaife, Veerapaneni and Young, 2019, Phys.
-Rev.
-Fluids, where Quaife {\sl et al.} showed that the lubrication hydrodynamics (draining of fluid between two membrane) is well-captured and the scaling of lubrication thin film is recovered.
+  \item Response: The repulsive potential we used to prevent overlap of
+    Janus particles is the repulsive Morse potential based on the
+    electrostatic repulsive potential between two negatively (or
+    positively) charged particles immersed in a medium of low
+    electrolyte concentration so that there is a well-defined zeta
+    potential on the charged particle (Coakley {\sl et al.}, 1999,
+    Biophys. J). This repulsive potential has been approximated by the
+    short-range repulsive Lennard-Jones potential (Flormann {\sl et
+    al.}, 2017, Sci. Reports), which has been adopted by Quaife and
+    Young to study the interaction between two membranes in a viscous
+    solvent in Quaife, Veerapaneni and Young, 2019, Phys. Rev. Fluids,
+    where Quaife {\sl et al.} showed that the lubrication hydrodynamics
+    (draining of fluid between two membrane) is well-captured and the
+    scaling of lubrication thin film is recovered.
 
@@
 
-\item Change: We added added a paragraph at the end of Section 2.2 describing
-  how the lubrication hydrodynamics in a narrow space between boundaries is
-  well-captured within the boundary integral formulation.
-  Then, in section 4.1 \textit{Model Parameters}, we show quantitatively how the lubrication and
-  artificial repulsion are comparable when substituing for our simulation parameters.
+\item Change: We added added a paragraph at the end of Section 2.2
+  describing how the lubrication hydrodynamics in a narrow space between
+    boundaries is well-captured within the boundary integral
+    formulation. Then, in section 4.1 \textit{Model Parameters}, we
+    show quantitatively how the lubrication and artificial repulsion are
+    comparable when substituting for our simulation parameters.
 \end{itemize}
@@
 \begin{itemize}
-\item Response: Fig.~6 shows 4 snapshots in the time frame from 0 to 12 $\mu$s along with the trajectory of the centriod.
+\item Response: Fig.~6 shows 4 snapshots in the time frame from 0 to 12
+  $\mu$s along with the trajectory of the centroid.
 
-  \item Change: In the caption of Fig.~6,  we now clarify that the horizontal axis 
-    represents time and that the vertical axis has been scaled to make the
-    migration stand out.
+  \item Change: In the caption of Fig.~6, we now clarify that the
+    horizontal axis represents time and that the vertical axis has been
+    scaled to make the migration stand out.
 
@@
 \item Change: We improved the software and the corrected streamlines now appear in Fig.~11.
-  As expected, the streamlines are continuous while their gradient is peicewise continuous
+  As expected, the streamlines are continuous while their gradient is
+    piecewise continuous
   across the JP vesicle interface.
@@
 \begin{itemize}
-  \item The typo with ``well-know" is corrected, but colored in red
-    since it was pointed out by Reviewer 1 as well.
+  \item The typo with ``well-know" is corrected, but colored in
+    \textcolor{red}{red} since it was pointed out by Reviewer 1 as well.
 
@@
   \item The typo with ``has" instead of ``have" is corrected, but
-    colored in red since it was pointed out by Reviewer 1.
+    colored in \textcolor{red}{red} since it was pointed out by Reviewer
+    1.
 

### 2022-03-07 doc/JFM2022/main_jfm.tex
fixing directory structure so that we can publish more than one paper

--- 2022-02-16 doc/main_jfm.tex
@@
 \cite{Fu20} studied physical quantities for static JP vesicles
-\ReviewerTwo{and empitically deduced realistic bending moduli, stretching moduli,
+\ReviewerTwo{and empirically deduced realistic bending moduli, stretching moduli,
   and tilt moduli under reasonable assumptions for the input parameters.}
@@
   prevents particle collisions and is comparable to hydrodynamic lubrication.
-  \citep{cawthorn_balmforth_2010} provide the asymptotic expression 
+  With a slight modification, the appendix of
+  \citep{cawthorn_balmforth_2010} provides the asymptotic expression 
   $F_{\text{lubr}} = -\tfrac{3}{2}\pi \mu \dot \epsilon (c/\epsilon)^{3/2}$
@@
 approximate decay rate $\sim 4.6$ $\upmu$s$^{-1}$. An equilibrium
-configuration is therefore rapidly attained. This equilibrium
+configuration is therefore rapidly attained, as illustrated by Supplementary Movie S1. 
+This equilibrium
 configuration serves as the initial data in the subsequent background
@@
 maintains its bilayer structure throughout the simulation. 
+(See Supplementary Movie S2 for tank-treading vesicle with $\chi=0.005$.)
 %
@@
 outer leaflet onto the midplane curve, 
-is larger than that of the inner leaflet.
+is larger than that of the inner leaflet 
+(see Supplementary Movie S3).
 
@@
 
-We show snapshots of the fluid pressure in Figure~\ref{figure10}. Since the
+We show snapshots of the fluid pressure in Figure~\ref{figure10}. 
+Supplementary Movie S5 shows the overall vesicle interaction.
+Since the
 initial JP vesicles are pre-relaxed, there is initially no pressure jump
@@
 but with a greater displacement (case (iv)), the JP vesicles move much
-faster along the $\pm y$-directions.
+faster along the $\pm y$-directions (see Supplementary Movie S6).
 
@@
     for two vesicles in shear flow and in extensional flow.
-  The value $d_{1,2}$ is the distance between two centroids of JP vesicles. The thick curves plot the trajectories
-  of $d_{1,2}$ generated by the continuum model and the thin curves are computed from using
+  The value $d_{1,2}$ is the distance between two centroids of JP vesicles. The thin curves plot the trajectories
+  of $d_{1,2}$ generated by the continuum model and the thick curves are computed from using
   the proposed HAP model.}
@@
 the results of continuum model does not have a periodic motion and two vesicles flow apart 
-after 1.5 $\mu$s. Panel (b) shows that the results of continuum model has similar trend of
-dynamics with one in the proposed model.}
+after 1.5 $\mu$s. Panel (b) shows that the results of the continuum model have a similar trend as  the proposed model.}
 

### 2022-03-08 code/src/capsules.m
update bc normalization

@@ -771,7 +771,7 @@ switch geom.bcType
 
 % The boundary condition 'cosine' is normalize by a factor.
     for i = 1:geom.nb
-        rhs(:,i) = rhs(:,i)/(norm(rhs(:,i))*sqrt(2*pi*rad(i)/geom.N));
+        rhs(:,i) = rhs(:,i)/sqrt(sum(rhs(:,i).^2.*geom.sa(:,i))*2*pi/geom.N);
     end    
     
     case 'vonMises'

### 2022-03-08 code/src/REMOVED_CODE.m
cleaned up capsules.m

@@ -437,3 +437,16 @@ for p = 1:geom.nb
 end     
 
 end % evalForcesTaylor
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function [force,torque] = bodyForceTorque(o)
+
+% will direct the calculated force, torque here
+force = zeros(2*o.nb,1);  % original [1;2]
+torque = zeros(o.nb,1);   % original -10
+
+
+end % bodyForceTorque
+
+

### 2022-03-08 code/src/capsules.m

@@ -30,9 +30,11 @@ DLPStokes;    % double-layer potential matrix
 DLPYukawa;    % double-layer potential matrix for yukawa
 upRate;       % upsampling rate that is used for NSI quadrature
 NPeaks;       % change the number of peaks in cosine bc
+% besselk(1,~) kernel for each target point with upsampled source points
+% on all other bodies
 BK1;          
-% besselk(1,~) function evaluated for each target point with upsampled
-% source points on all other bodies
+% Stokes double-layer kernel for each target point with upsampled source
+% points on all other bodies
 StokesDL;
 
 end %properties
@@ -67,59 +69,48 @@ theta = (0:o.N-1)'*2*pi/o.N;
 X = zeros(o.N*2,o.nb);  
 
 switch o.shape
-    case 'circle'
-        for i = 1:o.nb
-        % shape of particle
-        refX = kron([cos(tau(i)) -sin(tau(i)); +sin(tau(i)) cos(tau(i))],...
-            eye(o.N))*[o.ar(i)*cos(theta);sin(theta)]*o.radii(i);  
-        % rotated circle
-        X(1:o.N,i) = refX(1:o.N) + xc(1,i);
-        X(o.N+1:2*o.N,i) = refX(o.N+1:end) + xc(2,i);
-        % shift to the correct center
-        end
-    case 'star'
-        for i = 1:o.nb
-        % shape of star
-        rr = o.radii(i)+o.ar(i)*cos(o.petal*theta);
-        refX = kron([cos(tau(i)) -sin(tau(i));...
-               +sin(tau(i)) cos(tau(i))],...
-            eye(o.N))*[rr.*cos(theta);rr.*sin(theta)];
-        % rotated star
-        X(1:o.N,i) = refX(1:o.N) + xc(1,i);
-        X(o.N+1:2*o.N,i) = refX(o.N+1:end) + xc(2,i);
-        % shift to the correct center
-        end
-end
+  case 'circle'
+    for i = 1:o.nb
+      % shape of particle with rotation
+      refX = kron([cos(tau(i)) -sin(tau(i)); +sin(tau(i)) cos(tau(i))],...
+          eye(o.N))*[o.ar(i)*cos(theta);sin(theta)]*o.radii(i);  
+      % shift to the correct center
+      X(1:o.N,i) = refX(1:o.N) + xc(1,i);
[…]

### 2022-03-08 code/src/tstep.m

@@ -90,7 +90,7 @@ end
 
 % build precomputed matrix with all necessary bessel functions that are
 % needed at every GMRES iteration
-geom.BesselDistanceMatrix;
+geom.YukawaKernelMatrix;
 
 % Solve for the density function using GMRES
 [sigma,iflagYukawa,resYukawa,iterYukawa] = gmres(...

### 2022-03-08 code/src/REMOVED_CODE.m
cleaned up curve.m

@@ -450,3 +450,80 @@ torque = zeros(o.nb,1);   % original -10
 end % bodyForceTorque
 
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function X = redistributeArcLength(o, X)
+% X = resdistributeArcLength(o,X) resdistributes the geometry shape
+% equispaced in arclength
+
+N = size(X,1)/2;
+modes = [(0:N/2-1) (-N/2:-1)];
+
+jac = o.diffProp(X);
+
+tol = 1e-10;
+
+if norm(jac - mean(jac),inf) > tol*mean(jac)
+  theta = o.arcLengthParameter(X(1:end/2),...
+      X(end/2+1:end));
+  zX = X(1:end/2) + 1i*X(end/2+1:end);
+  zXh = fft(zX)/N;
+  zX = zeros(N,1);
+  for j = 1:N
+    zX = zX + zXh(j)*exp(1i*modes(j)*theta);
+  end
+  X = o.setXY(real(zX),imag(zX));
+  % redistribute the geometry so that it is
+  % equispaced in arclength
+end
+
+end % redistributeArcLength
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function [theta,arcLength] = arcLengthParameter(o,x,y)
+% theta = arcLengthParamter(o,x,y) finds a discretization of parameter
+% space theta so that the resulting geometry will be equispaced in
+% arclength
+
+uprate = 1;
+N = numel(x);
+Nup = uprate*N;
+t = (0:Nup-1)'*2*pi/Nup; % this is not correct when you iterate
+x = interpft(x,Nup);
+y = interpft(y,Nup);
+[~,len] = o.geomProp([x;y]);
+% find total perimeter
+[Dx,Dy] = o.getDXY([x;y]);
+% find derivative
+arc = sqrt(Dx.^2 + Dy.^2);
+arch = fft(arc);
+modes = -1i./[(0:Nup/2-1) 0 (-Nup/2+1:-1)]';
+modes(1) = 0;
+modes(Nup/2+1) = 0;
[…]

### 2022-03-08 code/src/curve.m

@@ -92,68 +92,6 @@ area = sum( x.*Dy - y.*Dx)*pi/N;
 
 end % geomProp
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function X = redistributeArcLength(o, X)
-% X = resdistributeArcLength(o,X) resdistributes the geometry shape
-% eqiuspaced in arclength
-
-N = size(X,1)/2;
-modes = [(0:N/2-1) (-N/2:-1)];
-
-jac = o.diffProp(X);
-
-tol = 1e-10;
-
-if norm(jac - mean(jac),inf) > tol*mean(jac)
-  theta = o.arcLengthParameter(X(1:end/2),...
-      X(end/2+1:end));
-  zX = X(1:end/2) + 1i*X(end/2+1:end);
-  zXh = fft(zX)/N;
-  zX = zeros(N,1);
-  for j = 1:N
-    zX = zX + zXh(j)*exp(1i*modes(j)*theta);
-  end
-  X = o.setXY(real(zX),imag(zX));
-  % redistribute the geometry so that it is
-  % equispaced in arclength
-end
-
-end % redistributeArcLength
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function [theta,arcLength] = arcLengthParameter(o,x,y)
-% theta = arcLengthParamter(o,x,y) finds a discretization of parameter
-% space theta so that the resulting geometry will be equispaced in
-% arclength
-
-uprate = 1;
-N = numel(x);
-Nup = uprate*N;
-t = (0:Nup-1)'*2*pi/Nup; % this is not correct when you iterate
-x = interpft(x,Nup);
-y = interpft(y,Nup);
-[~,len] = o.geomProp([x;y]);
-% find total perimeter
-[Dx,Dy] = o.getDXY([x;y]);
-% find derivative
-arc = sqrt(Dx.^2 + Dy.^2);
-arch = fft(arc);
-modes = -1i./[(0:Nup/2-1) 0 (-Nup/2+1:-1)]';
-modes(1) = 0;
-modes(Nup/2+1) = 0;
-arcLength = real(ifft(modes.*arch) - sum(modes.*arch/Nup) + ...
-    arch(1)*t/Nup);
-
[…]

### 2022-03-08 code/src/REMOVED_CODE.m
cleaned up fft1.m

@@ -524,6 +524,44 @@ y = ifft(y);
 end
 
 
+function Deriv = D1(N)
+% Deriv = D1(N) constructs a N by N fourier differentiation matrix
+[FF,FFI] = fft1.fourierInt(N);
+Deriv = FFI * diag(1i*([0 -N/2+1:N/2-1])) * FF;
+Deriv = real(Deriv);
+
+end % D1
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function [FF,FFI] = fourierInt(N)
+% [FF,FFI] = fourierInt(N) returns a matrix that take in the point
+% values of a function in [0,2*pi) and returns the fourier coefficients % (FF) and a matrix that takes in the fourier coefficients and returns
+% the function values (FFI)
+
+theta = (0:N-1)'*2*pi/N;
+%modes = [0;(-N/2+1:N/2-1)'];
+modes = [-N/2;(-N/2+1:N/2-1)'];
+
+FF = zeros(N);
+for i=1:N
+  FF(:,i) = exp(-1i*theta(i)*modes);
+end
+FF = FF/N;
+% FF takes function values and returns the Fourier coefficients
+
+if (nargout > 1)
+  FFI = zeros(N);
+  for i=1:N
+    FFI(:,i) = exp(1i*modes(i)*theta);
+  end
+  % FFI takes the Fourier coefficients and returns function values.
+else
+  FFI = [];
+end
+
+
+end % fourierInt
+
 
 
 

### 2022-03-08 code/src/fft1.m

@@ -11,14 +11,6 @@ end
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 methods (Static)
 
-function Deriv = D1(N)
-% Deriv = D1(N) constructs a N by N fourier differentiation matrix
-[FF,FFI] = fft1.fourierInt(N);
-Deriv = FFI * diag(1i*([0 -N/2+1:N/2-1])) * FF;
-Deriv = real(Deriv);
-
-end % D1
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 function f = diffFT(f,IK)
 % f = diffFT(f,IK) Computes the first derivative of an array of 
@@ -52,9 +44,6 @@ IK = 1i*[(0:N/2-1) 0 (-N/2+1:-1)]';
 % diagonal term for Fourier differentiation with the -N/2 mode
 % zeroed to avoid Nyquist frequency
 
-%thresh = ceil(1/3*N/2);
-%IK(N/2+1-thresh:N/2) = 0;
-%IK(N/2+2:N/2+2+thresh-1) = 0;
 
 if nv == 2
   IK = [IK IK];
@@ -66,36 +55,6 @@ end
 
 end % modes
 
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function [FF,FFI] = fourierInt(N)
-% [FF,FFI] = fourierInt(N) returns a matrix that take in the point
-% values of a function in [0,2*pi) and returns the fourier coefficients % (FF) and a matrix that takes in the fourier coefficients and returns
-% the function values (FFI)
-
-theta = (0:N-1)'*2*pi/N;
-%modes = [0;(-N/2+1:N/2-1)'];
-modes = [-N/2;(-N/2+1:N/2-1)'];
-
-FF = zeros(N);
-for i=1:N
-  FF(:,i) = exp(-1i*theta(i)*modes);
-end
-FF = FF/N;
-% FF takes function values and returns the Fourier coefficients
-
-if (nargout > 1)
-  FFI = zeros(N);
-  for i=1:N
-    FFI(:,i) = exp(1i*modes(i)*theta);
-  end
[…]

### 2022-03-08 code/src/REMOVED_CODE.m
removing misc.m

@@ -563,5 +563,26 @@ end
 end % fourierInt
 
 
+%
+% Some miscellaneous functions 
+
+function V = trapz2(o, x1, x2, z)
+
+s = size(x1);
+m = s(1); n = s(2);
+
+I = 1:m-1;
+J = 1:n-1;
+
+%only one pair of substractions will be nonzero here. 
+
+dx1 = x1(I+1,J) - x1(I,J) + x1(I,J+1) - x1(I,J); 
+dx2 = x2(I+1,J) - x2(I,J) + x2(I,J+1) - x2(I,J);
+
+V = 0.25*( z(I,J) + z(I+1,J) + z(I,J+1) + z(I+1,J+1) ).*dx1.*dx2;
+
+V = sum(sum(V));
+
+end
 
 

### 2022-03-08 code/src/misc.m

@@ -1,31 +1,5 @@
 classdef misc
 
-%
-% Some miscellaneous functions 
-%
-%
-%
-
-methods
-
-function V = trapz2(o, x1, x2, z)
-
-s = size(x1);
-m = s(1); n = s(2);
-
-I = 1:m-1;
-J = 1:n-1;
-
-%only one pair of substractions will be nonzero here. 
-
-dx1 = x1(I+1,J) - x1(I,J) + x1(I,J+1) - x1(I,J); 
-dx2 = x2(I+1,J) - x2(I,J) + x2(I,J+1) - x2(I,J);
-
-V = 0.25*( z(I,J) + z(I+1,J) + z(I,J+1) + z(I+1,J+1) ).*dx1.*dx2;
-
-V = sum(sum(V));
-
-end
 
 end %methods
 

### 2022-03-08 code/src/misc.m
removing misc.m

@@ -1,6 +1,0 @@
-classdef misc
-
-
-end %methods
-
-end %classdef

### 2022-03-08 code/examples/shear_input.m
removing some non-used properties

@@ -38,8 +38,6 @@ options.saveData  = false;
 options.fileBase  = options.farField;
 
 options.append    = false;
-options.inear     = true;
-options.usePreco  = false;
 options.verbose   = true;
 options.timeOrder = 2;
 options.gmresTol  = 1e-10;

### 2022-03-08 code/src/curve.m

@@ -92,6 +92,8 @@ area = sum( x.*Dy - y.*Dx)*pi/N;
 
 end % geomProp
 
+end % methods
+
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 methods (Static)
@@ -191,8 +193,6 @@ function out = isLeft(o, p1, p2, q1, q2, r1, r2)
 out = (q1 - p1) .* (r2 - p2) - (r1 -  p1) .* (q2 - p2);
 
 end % isLeft
-
-
 
 end % methods (Static)
 

### 2022-03-08 code/src/monitor.m

@@ -5,7 +5,7 @@ properties
 verbose    % write data to console
 save       % save data to the dat files and log file
 dataFile   % name of data file containing fibre centres and orientations
-velFile   % name of data file containing velocities
+velFile    % name of data file containing velocities
 logFile    % name of log file
 usePlot    % flag for plotting
 plotAxis   % plotting axis
@@ -88,8 +88,8 @@ end % welcomeMessage
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 function writeStars(o)
-% writeStars writes a message of stars to the console
-% and the log file depending on verbose and saveData
+% writeStars writes a message of stars to the console and the log file
+% depending on verbose and saveData
 
 stars = '***********************************************************';
 o.writeMessage(stars)
@@ -98,19 +98,18 @@ end % writeStars
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 function writeMessage(o,message)
-% function writeMessage(message) appends message 
-% to o.fileName
+% function writeMessage(message) appends message to o.fileName
 
+% save to log file
 if o.save
   fid = fopen(o.logFile,'a');
   fprintf(fid,'%s\n',message);
   fclose(fid);
 end
-% save to log file
+% write to console if verbose==true
 if o.verbose
   disp(message)
 end
-% write to console if verbose==true
 
 
 end % writeMessage
@@ -176,9 +175,6 @@ if o.usePlot
   oc = curve;
   figure(1); clf;
   for i = 1:geom.nb
-%    xind = [geom.X(1:geom.N,i); geom.X(1,i)];
-%    yind = [geom.X(geom.N+1:2*geom.N,i); geom.X(geom.N+1,i)];
-%    plot(xind,yind,'k');
     xx = geom.center(1,i);
     yy = geom.center(2,i);
     th = geom.tau(i);

### 2022-03-08 code/src/tstep.m

@@ -7,21 +7,13 @@ properties
 
 dt              % time step size
 sstep           % starting step
-Dp              % Stokes DLP for fiber-fiber interaction
-rhs             % Right hand side of mobility problem
-rhs2            % Right hand side of screen laplace problem
-inear           % flag for using near-singular integration
 gmresTol        % GMRES tolerance
-plotAxis        % plot axes
 farField        % background flow
 janusbc         % particle boundary condition
 tracer          % flag for tracer
-precow          % block-diagonal preconditioner for walls
-potp            % class for fiber layer potentials
-potw            % class for wall layer potentials
-om              % monitor class
-precoYukawa
-precoStokes
+precoYukawa     % block-diagonal preconditioner for Yukawa
+precoStokes     % block-diagonal preconditioner for Stokes on bodies
+precoWalls      % block-diagonal preconditioner for walls
 
 end % properties
 
@@ -32,11 +24,9 @@ function o = tstep(options,prams)
 % o.tstep(options,prams): constructor.  Initialize class.  Take all
 % elements of options and prams needed by the time stepper
 
-o.inear    = options.inear;
 o.dt       = prams.T/prams.m;
 o.sstep    = prams.sstep;
 o.gmresTol = options.gmresTol;
-o.plotAxis = options.plotAxis;
 o.farField = @(X) o.bgFlow(X,options);
 o.tracer   = options.tracer;
 
@@ -47,7 +37,8 @@ end % constructor: tstep
 
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function [Up,wp,iterYukawa,iterStokes,etaYukawa,etaStokes,fforce,torque] = timeStep(o,geom,etaY0,etaS0)
+function [Up,wp,iterYukawa,iterStokes,etaYukawa,etaStokes,...
+      fforce,torque] = timeStep(o,geom,etaY0,etaS0)
 % Main time stepping routine
 oc     = curve;
 N      = geom.N;
@@ -60,24 +51,17 @@ gam    = geom.gam;
 radii  = geom.radii;
 
 % CREATE NEAR SINGULAR INTEGRATION STRUCTURES
-if o.inear
-  geom.nearStruct = geom.getZone([],1);
-end
[…]

### 2022-03-08 code/src/tstep.m
working on tstep.m

@@ -58,8 +58,7 @@ op = poten(geom.N,geom.rho);
 [R1, R2, RTq, pp] = op.Repul(geom);
 % END OF REPULSION CALCULATION
 
-
-% START OF SCREENED LAPLACE SOLVE USING GMRES
+% START OF SCREENED LAPLACE SOLVE TO FIND HYDROPHOBIC FORCE AND TORQUE
 % right hand side for the screened Laplace solver
 yukawaRHS = geom.yukawaRHS;
 
@@ -81,9 +80,6 @@ geom.YukawaKernelMatrix;
       @(etaY0) o.timeMatVecYukawa(etaY0,geom) ,...
       yukawaRHS, [], o.gmresTol, N*nb, ...
       @(etaY0) o.precoYukawaBD(etaY0)); 
-%[sigma,iflagYukawa,resYukawa,iterYukawa] = gmres(...
-%      @(etaY0) o.timeMatVecYukawa(etaY0,geom) ,...
-%      yukawaRHS, [], o.gmresTol, N*nb); 
 iterYukawa = iterYukawa(2);
 fprintf('Yukawa required %i iterations\n',iterYukawa);
 
@@ -101,10 +97,10 @@ end
 
 % tst = fopen("HAP_force_distance.dat", "r");
 % if tst == -1
-%     fid = fopen("HAP_force_distance.dat", "w");
+%   fid = fopen("HAP_force_distance.dat", "w");
 % else 
-%     fclose(tst);
-%     fid = fopen("HAP_force_distance.dat", "a");
+%   fclose(tst);
+%   fid = fopen("HAP_force_distance.dat", "a");
 % end
 % fprintf(fid,"%d %d\n", [geom.center(1,2) - geom.center(1,1) - 2,  F1(1)]');
 % fclose(fid);
@@ -132,13 +128,9 @@ pause(0.01)
 fforce  = [F1 + R1, F2 + R2].';
 force  = fforce(:);
 torque = Tq + RTq;
+% END OF SCREENED LAPLACE SOLVE TO FIND HYDROPHOBIC FORCE AND TORQUE
 
-%force = 0*[-2;1;0;0;2;-1];
-%torque = 1*[-10;0;+10];
-
[…]

### 2022-03-08 code/src/poten.m
started to clean up poten.m

@@ -25,9 +25,9 @@ methods
 function o = poten(N,rho)
 % o = poten(N): constructor; N is the number of points per curve
 
-o.interpMat = o.lagrangeInterp;
 % load in the interpolation matrix which is precomputed with 7
 % interpolation points
+o.interpMat = o.lagrangeInterp;
 
 o.N = N;
 o.rho = rho;
@@ -81,6 +81,8 @@ h = geomSou.length/Nsou; % arclength term
 
 Nup = Nsou*geomSou.upRate;
 
+% contribution on self for dealing with the interpolation point that is
+% exactly on the body
 vself = selfMat(f);
 
 % pad vself with zeros if dealing with a scalar layer potential
@@ -92,6 +94,7 @@ else
   fup = [interpft(f(1:Nsou,:),Nup); interpft(f(Nsou+1:2*Nsou,:),Nup)];
 end
 
+% parameters that we will need when building the upsampled geometry
 prams.N = Nup;
 prams.nb = geomSou.nb;
 prams.tau = geomSou.tau;
@@ -106,19 +109,18 @@ prams.bcType = geomSou.bcType;
 prams.NPeaks = geomSou.NPeaks;
 prams.shape = geomSou.shape;
 prams.petal = geomSou.petal;
-% parameters that we will need when building the upsampled geometry
 
-geomUp = capsules(prams,geomSou.center,geomSou.tau);
 % Build an object with the upsampled geom
+geomUp = capsules(prams,geomSou.center,geomSou.tau);
+% already computed the necessary Yukawa and Stokes DLP matrix
 geomUp.BK1 = geomSou.BK1;
-% already computed the necessary Stokes DLP matrix
 geomUp.StokesDL = geomSou.StokesDL;
 
-interpOrder = size(o.interpMat,1);
 % lagrange interpolation order
-p = ceil((interpOrder+1)/2);
+interpOrder = size(o.interpMat,1);
 % want half of the lagrange interpolation points to the left of the
 % closest point and the other half to the right
+p = ceil((interpOrder+1)/2);
 
 if tEqualS % sources == targets
   if nsou > 1
@@ -147,9 +149,9 @@ end
 
 nearField = zeros(2*Ntar,ntar);
 
-beta = 1.1;
[…]

### 2022-03-09 code/src/poten.m
worked on poten.m

@@ -286,7 +286,8 @@ LP = farField + nearField;
 end % nearSingInt
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% START OF ROUTINES THAT BUILD LAYER-POTENTIAL MATRICES
+% START OF ROUTINES THAT BUILD LAYER-POTENTIAL MATRICES WHEN SOURCE ==
+% TARGET
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@ -364,30 +365,29 @@ end % k
 end % stokesDLmatrix
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function N0 = stokesN0matrix(~,wall)
+function N0 = stokesN0matrix(~,geom)
 % N0 = stokesN0matrix(vesicle) generates the the integral operator with
 % kernel normal(x) \otimes normal(y) which removes the rank one
 % defficiency of the double-layer potential. Need this operator for
 % solid walls
 
 % Normal vector
-normal = [wall.xt(wall.N+1:2*wall.N,:);-wall.xt(1:wall.N,:)]; 
-normal = normal(:,ones(2*wall.N,1));
+normal = [geom.xt(geom.N+1:2*geom.N,:);-geom.xt(1:geom.N,:)]; 
+normal = normal(:,ones(2*geom.N,1));
 
-sa = [wall.sa(:,1);wall.sa(:,1)];
-sa = sa(:,ones(2*wall.N,1));
-N0 = zeros(2*wall.N,2*wall.N,wall.n);
-N0(:,:,1) = normal.*normal'.*sa'*2*pi/wall.N;
-% Use N0 if solving (-1/2 + DLP)\eta = f where f has no flux through
-% the boundary.  By solving (-1/2 + DLP + N0)\eta = f, we guarantee
-% that \eta also has no flux through the boundary.  This is not
-% required, but it means we're enforcing one addition condition on eta
[…]

### 2022-03-16 doc/PRF2022/PRF_main.tex
tex file for PRF

%% ****** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4.2 distribution.
%%   Version 4.2a of REVTeX, January, 2015
%%
%%
%%   Copyright (c) 2015 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.2
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showkeys' option to make keywords appear
\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
%\documentclass[aps,prl,preprint,superscriptaddress]{revtex4-2}
%\documentclass[aps,prl,reprint,groupedaddress]{revtex4-2}

% You should use BibTeX and apsrev.bst for references
% Choosing a journal automatically selects the correct APS
% BibTeX style file (bst file), so only uncomment the line
% below if necessary.
%\bibliographystyle{apsrev4-2}

\begin{document}

% Use the \preprint command to place your local institutional report
% number in the upper righthand corner of the title page in preprint mode.
% Multiple \preprint commands are allowed.
% Use the 'preprintnumbers' class option to override journal defaults
% to display numbers if necessary
%\preprint{}

%Title of paper
\title{Collective behavior of Suspended Janus Particles via an Integral Equation Method}

% repeat the \author .. \affiliation  etc. as needed
% \email, \thanks, \homepage, \altaffiliation all apply to the current
% author. Explanatory text should go in the []'s, actual e-mail
% address or url should go in the {}'s for \email and \homepage.
% Please use the appropriate macro foreach each type of information

% \affiliation command applies to all authors since the last
% \affiliation command. The \affiliation command should follow the
% other information
% \affiliation can be followed by \email, \homepage, \thanks as well.
\author{Szu-Pei Fu}
\email{sfu17@fordham.edu}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\author{Rolf Ryham}
\email{rryham@fordham.edu}
\affiliation{Department of Mathematics, Fordham University, Bronx, New York 10458, USA}

\author{Bryan Quaife}
\email{bquaife@fsu.edu}
 \affiliation{Department of Scientific Computing, Florida State University, Tallahassee, Florida 32306, USA}
 \author{Yuan-Nan Young}
 \email{yyoung@njit.edu}
 \affiliation{Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, New Jersey 07102, USA
 }

%Collaboration name if desired (requires use of superscriptaddress
%option in \documentclass). \noaffiliation is required (may also be
%used with the \author command).
%\collaboration can be followed by \email, \homepage, \thanks as well.
%\collaboration{}
%\noaffiliation

\date{\today}

\begin{abstract}
% insert abstract here
\end{abstract}

% insert suggested keywords - APS authors don't need to do this
%\keywords{}

%\maketitle must follow title, authors, abstract, and keywords
\maketitle

% body of paper here - Use proper section commands
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
\subsection{}
\subsubsection{}

%%%

\section{Governing Equations}

%%%

\section{Numerical Results}

%%%

\section{Conclusions}

%%%

% If in two-column mode, this environment will change to single-column
% format so that long equations can be displayed. Use
% sparingly.
%\begin{widetext}
% put long equation here
%\end{widetext}

% figures should be put into the text as floats.
% Use the graphics or graphicx packages (distributed with LaTeX2e)
% and the \includegraphics macro defined in those packages.
% See the LaTeX Graphics Companion by Michel Goosens, Sebastian Rahtz,
% and Frank Mittelbach for instance.
%
% Here is an example of the general form of a figure:
% Fill in the caption in the braces of the \caption{} command. Put the label
% that you will use with \ref{} command in the braces of the \label{} command.
% Use the figure* environment if the figure should span across the
% entire page. There is no need to do explicit centering.

% \begin{figure}
% \includegraphics{}%
% \caption{\label{}}
% \end{figure}

% Surround figure environment with turnpage environment for landscape
% figure
% \begin{turnpage}
% \begin{figure}
% \includegraphics{}%
% \caption{\label{}}
% \end{figure}
% \end{turnpage}

% tables should appear as floats within the text
%
% Here is an example of the general form of a table:
% Fill in the caption in the braces of the \caption{} command. Put the label
% that you will use with \ref{} command in the braces of the \label{} command.
% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
% \begin{tabular}{} command.
% The ruledtabular enviroment adds doubled rules to table and sets a
% reasonable default table settings.
% Use the table* environment to get a full-width table in two-column
% Add \usepackage{longtable} and the longtable (or longtable*}
% environment for nicely formatted long tables. Or use the the [H]
% placement option to break a long table (with less control than 
% in longtable).
% \begin{table}%[H] add [H] placement to break table across pages
% \caption{\label{}}
% \begin{ruledtabular}
% \begin{tabular}{}
% Lines of table here ending with \\
% \end{tabular}
% \end{ruledtabular}
% \end{table}

% Surround table environment with turnpage environment for landscape
% table
% \begin{turnpage}
% \begin{table}
% \caption{\label{}}
% \begin{ruledtabular}
% \begin{tabular}{}
% \end{tabular}
% \end{ruledtabular}
% \end{table}
% \end{turnpage}

% Specify following sections are appendices. Use \appendix* if there
% only one appendix.
%\appendix
%\section{}

% If you have acknowledgments, this puts in the proper section head.
%\begin{acknowledgments}
% put your acknowledgments here.
%\end{acknowledgments}

% Create the reference section using BibTeX:
%\bibliography{basename of .bib file}

\end{document}
%
% ****** End of file apstemplate.tex ******

### 2022-03-21 doc/JFM2022/Final/main_jfm.tex
final product

--- 2022-03-07 doc/JFM2022/main_jfm.tex
@@
 \begin{center}
-\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
+\includegraphics[width=\textwidth]{fig1.eps}
 \end{center}
@@
   the mobility problem. The color map in panels (b)--(e) is the solution
-  $u$ of \eqref{eq:SL}. Red is for $\ReviewerTwo{\eta} = 1$ and blue is for $\ReviewerTwo{\eta} = 0$.
+  $u$ of \eqref{eq:SL}. Red is for $\eta  = 1$ and blue is for $\eta  = 0$.
   Particles self-assemble into vesicle bilayers (panel (b)) and
   eventually arrange along inner and outer leaflets. In panel (c), $C_M$
-  is the midplane curve, \ReviewerOne{and} $A$ is the enclosed area\ReviewerOne{.}
+  is the midplane curve, and $A$ is the enclosed area.
   %, and $L$ is the arc length. 
@@
 a Janus suspension under various flows. The JP vesicles in our
-simulations replicate  \ReviewerOne{well-known} vesicle hydrodynamics
+simulations replicate well-known vesicle hydrodynamics
 such as tank-treading and inter-leaflet slippage in a shear flow and
@@
 stiffness, but with the presence of the hydrophobic forces, we maintain
-contact-free suspensions with a relatively \textcolor{red}{soft} repulsive
-force \textcolor{red}{(compared to the short-range repulsion that diverges in the Lennard-Jones potential)}.
+contact-free suspensions with a relatively soft repulsive
+force (compared to the short-range repulsion that diverges in the Lennard-Jones potential).
 
@@
 Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
-\ReviewerOne{the no-slip boundary condition}
+the no-slip boundary condition
 \begin{align}
 \label{eq:rigid_bc}
-  \ReviewerOne{\uu}(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
+  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
     \xx \in \Gamma_i,
@@
   \label{eq:SL}
--\rho^2 \Delta \ReviewerTwo{\eta} + \ReviewerTwo{\eta} &=0,            && \xx \in \Omega,\\
+-\rho^2 \Delta \eta  + \eta  &=0,            && \xx \in \Omega,\\
 \label{eq:SLbc}
-\ReviewerTwo{\eta}(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
+\eta (\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
 \label{eq:SLff}
-\ReviewerTwo{\eta} &\to 0,                          &&|\xx| \to \infty,
+\eta  &\to 0,                          &&|\xx| \to \infty,
 \end{alignat}
@@
 \mathbf{T}
-= \gamma\rho^{-1}\ReviewerTwo{\eta}^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
-  \ReviewerTwo{\eta}|^2 \mathbf{I} - \nabla \ReviewerTwo{\eta}  \nabla \ReviewerTwo{\eta}^T\right)
+= \gamma\rho^{-1}\eta ^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
+  \eta |^2 \mathbf{I} - \nabla \eta   \nabla \eta ^T\right)
 \end{align}
@@
 
-\ReviewerThree{
 The high-order interpolation-based quadrature rule used to compute the
@@
 qua-gan-you2021}.
-}
+
 %
@@
 $N$ points on each of the $N_b$ particles with a collocation method.
-\ReviewerOne{All derivatives are computed with spectrally-accurate
-Fourier differentiation.} Integrals that are smooth are computed with
+All derivatives are computed with spectrally-accurate
+Fourier differentiation. Integrals that are smooth are computed with
 the spectrally-accurate trapezoid rule, and nearly-singular integrals,
@@
 Similar to our previous work (\cite{Fu20}), we represent the
-\ReviewerTwo{hydrophobic attraction potential (HAP)} as a double-layer
+hydrophobic attraction potential (HAP) as a double-layer
 potential
@@
   \label{eq:HAP_DLP}
-  \ReviewerTwo{\eta}(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
+  \eta (\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
     K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
@@
   \label{eq:uidef}
-  w_i(\xx) = \ReviewerTwo{\eta}(\xx) - \ReviewerTwo{\eta}_i(\xx),
+  w_i(\xx) = \eta (\xx) - \eta _i(\xx),
 \end{align}
@@
 \begin{align}
-  \ReviewerTwo{\eta}_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \left(\pderiv{}{\nnu_\yy}
+  \eta _i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \left(\pderiv{}{\nnu_\yy}
     K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
@@
   {\bf T} &=
-    \SS(\ReviewerTwo{\eta}_i,\ReviewerTwo{\eta}_i) +(\SS(\ReviewerTwo{\eta}_i,w_i) +\SS(w_i,\ReviewerTwo{\eta}_i)) +\SS(w_i,w_i) \\
+    \SS(\eta _i,\eta _i) +(\SS(\eta _i,w_i) +\SS(w_i,\eta _i)) +\SS(w_i,w_i) \\
   &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
@@
 \label{eq:Tsplit}
-\SS(\ReviewerTwo{\eta},v)
-=  \gamma\rho^{-1} \ReviewerTwo{\eta}v {\bf I} + \gamma\rho \nabla \ReviewerTwo{\eta} \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla \ReviewerTwo{\eta} \nabla v^T.
+\SS(\eta ,v)
+=  \gamma\rho^{-1} \eta v {\bf I} + \gamma\rho \nabla \eta  \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla \eta  \nabla v^T.
 \end{equation}
-Using the fact that $\ReviewerTwo{\eta}$,  $\ReviewerTwo{\eta}_i$, and $w_i$ solve the screened Laplace
+Using the fact that $\eta $,  $\eta _i$, and $w_i$ solve the screened Laplace
 equation~\eqref{eq:SL}, and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1,
@@
 smooth and $\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n
-\setminus U_i$. Similarly, $w_i = \ReviewerTwo{\eta} - \ReviewerTwo{\eta}_i$ is smooth and $\nabla \cdot
+\setminus U_i$. Similarly, $w_i = \eta  - \eta _i$ is smooth and $\nabla \cdot
 {\bf T}_3 = \mathbf{0}$ in $U_i$. By the divergence theorem,  
@@
 \label{eq:DLjump}
-\jump{\ReviewerTwo{\eta}_i} = \sigma, \quad
+\jump{\eta _i} = \sigma, \quad
 \jump{w_i} = 0, \quad
-\jump{\nabla \ReviewerTwo{\eta}_i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
+\jump{\nabla \eta _i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
 \jump{\nabla w_i} = \mathbf{0},
@@
 \begin{align*}
-  \jump{{\bf T}_2 \cdot \nnu}   &= \jump{\SS(\ReviewerTwo{\eta}_i,w_i) \cdot \nnu +
-    \SS(w_i,\ReviewerTwo{\eta}_i) \cdot \nnu} \\
-  &= \Big[\!\Big[ \left( 2\gamma\rho^{-1} \ReviewerTwo{\eta}_i w_i \mathbf{I} + 2\gamma\rho \nabla \ReviewerTwo{\eta}_i \cdot \nabla w_i \mathbf{I} 
-- 2\gamma\rho \nabla \ReviewerTwo{\eta}_i  \nabla w_i^T - 2\gamma\rho \nabla w_i \nabla
-  \ReviewerTwo{\eta}_i^T\right) \cdot \nnu \Big]\!\Big] \\
+  \jump{{\bf T}_2 \cdot \nnu}   &= \jump{\SS(\eta _i,w_i) \cdot \nnu +
+    \SS(w_i,\eta _i) \cdot \nnu} \\
+  &= \Big[\!\Big[ \left( 2\gamma\rho^{-1} \eta _i w_i \mathbf{I} + 2\gamma\rho \nabla \eta _i \cdot \nabla w_i \mathbf{I} 
+- 2\gamma\rho \nabla \eta _i  \nabla w_i^T - 2\gamma\rho \nabla w_i \nabla
+  \eta _i^T\right) \cdot \nnu \Big]\!\Big] \\
 %  &= \jump{\left( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
@@
 % what we solve for?
-\ReviewerOne{
 \subsection{Time Marching}
@@
 %are avoided even when using a relatively larger time step than $\Delta t\sim O(10^{-1})$ ns.
-}
 
@@
 \centering
-\includegraphics[width=11.5cm]{Figure3_Wrapper.pdf}
-%\includegraphics[width=0.3\textwidth]{N58_0.pdf}
-%\includegraphics[width=0.3\textwidth]{N58_vel_0.pdf}\\
-%\includegraphics[width=0.3\textwidth]{N58_20000.pdf}
-%\includegraphics[width=0.3\textwidth]{N58_vel_20000.pdf}
+\includegraphics[width=11.5cm]{fig2.eps}
   \caption{\label{figure3} 
@@
 \cite{Fu20} studied physical quantities for static JP vesicles
-\ReviewerTwo{and empirically deduced realistic bending moduli, stretching moduli,
-  and tilt moduli under reasonable assumptions for the input parameters.}
+and empirically deduced realistic bending moduli, stretching moduli,
+  and tilt moduli under reasonable assumptions for the input parameters.
 In the present work, we study JP vesicles in various background flows.
@@
 ns nm}^{-2}$ is viscosity of room-temperature water. 
-\ReviewerThree{
-  We select \ReviewerOne{$M=4.0$~$\text{pN}$} and $\rho_0 = 0.2l_0$ so that \eqref{eq:REPULforce}
+We select $M=4.0$~$\text{pN}$ and $\rho_0 = 0.2l_0$ so that \eqref{eq:REPULforce}
   prevents particle collisions and is comparable to hydrodynamic lubrication.
@@
   the order of a nm $\text{ns}^{-1}$.
-}
 
 To reach consistent simulation outcomes, we first solve for a baseline
-JP \ReviewerThree{vesicle} that is suitably close to equilibrium. We
+JP vesicle that is suitably close to equilibrium. We
 start with an assumed configuration of $N=58$ JP in the form of two,
@@
 \begin{center}
-\includegraphics[width=13.5cm]{Figure4_Wrapper.pdf}
-%\hspace{-0.6cm}
-%\includegraphics[height=2in]{ReducedArea.pdf}
-%\hspace{0.6cm}
-%\includegraphics[height=2in]{DecayRate.eps}\\
-%\includegraphics[height=2in]{ArcLength.pdf}
-%\includegraphics[height=2in]{ExcLength.pdf}
+\includegraphics[width=13.5cm]{fig3.eps}
 \end{center} 
@@
 \begin{center}
-  \includegraphics[width=11cm]{Figure5_Wrapper.pdf}\\
-  \includegraphics[width=11cm]{Figure5B_Wrapper.pdf}
-%\includegraphics[width=0.5\textwidth]{Slip.eps}\\
-%\includegraphics[width=0.4\textwidth]{Slip2.eps}
+  \includegraphics[width=11cm]{fig4a.eps}\\
+  \includegraphics[width=11cm]{fig4b.eps}
 \end{center} 
@@
 
-\ReviewerThree{The time courses contain oscillations due to the
+The time courses contain oscillations due to the
 granularity of the JP vesicle.
@@
 they correspond to the rate of passage of particles through a fixed-angle
-axis about the vesicle centre.} 
+axis about the vesicle centre.
 The inset of Figure~\ref{figure4}c zooms
@@
 %Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
-\ReviewerOne{Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the baseline number of particles is $N_b = 58$.
+Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the baseline number of particles is $N_b = 58$.
 With the fixed total length of the JP vesicle, we change parameters related to the length scale, for instances, $\rho$, $\rho_0$, and the radius of particles.
-With $-5\%$, $5\%$, and $10\%$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{61,56,53\}$, respectively. }
-%
-\ReviewerOne{The trends in Table~\ref{table1}
-  suggest that $b$ decreases with decreasing $\rho$, $\rho_0$, and particle radius.}
+With $-5\%$, $5\%$, and $10\%$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{61,56,53\}$, respectively.
+%
+The trends in Table~\ref{table1}
+  suggest that $b$ decreases with decreasing $\rho$, $\rho_0$, and particle radius.
 Overall, the values for $b$ are 
@@
 %\centering
-%\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
-%%\includegraphics[height=2in]{N58_rupt_0.pdf}
-%%\includegraphics[height=2in]{N58_rupt_200.pdf}
+%\includegraphics[width=11.32cm]{Figure8_Wrapper.eps}
+%%\includegraphics[height=2in]{N58_rupt_0.eps}
+%%\includegraphics[height=2in]{N58_rupt_200.eps}
 %\\
-%%\includegraphics[height=2in]{N58_rupt_400.pdf}
-%%\includegraphics[height=2in]{N58_rupt_600.pdf}
+%%\includegraphics[height=2in]{N58_rupt_400.eps}
+%%\includegraphics[height=2in]{N58_rupt_600.eps}
 %  \caption{\label{figure8} Tank-treading leads to membrane rupture for
@@
 \centering
-\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
-%\includegraphics[height=2in]{N58_rupt_0.pdf}
-%\includegraphics[height=2in]{N58_rupt_200.pdf}
-\\
-%\includegraphics[height=2in]{N58_rupt_400.pdf}
-%\includegraphics[height=2in]{N58_rupt_600.pdf}
+\includegraphics[width=11.32cm]{fig5.eps}
   \caption{\label{figure8} Tank-treading leads to membrane rupture for
@@
 
-\ReviewerOne{An empirical numerical study found that for the baseline
+An empirical numerical study found that for the baseline
 parameter set, the dimensionless, critical shear rate is $\chi_*=0.0655$
@@
 Finally, a $10 \%$ increase in resting length $L_0$ gave a $20.61 \%$
-decrease in critical shear rate $\chi_*$.}  
-  \ReviewerOne{These relative changes suggest that there is dimensionless number $K$ given by 
+decrease in critical shear rate $\chi_*$.  
+These relative changes suggest that there is dimensionless number $K$ given by 
   \begin{equation}
@@
   which yields $K_B \approx 60$ pN $\text{nm}^{-1}$, which is a reasonable
-  value for the bending modulus of a lipid bilayer, for example \citep{NaTr00}.}
+  value for the bending modulus of a lipid bilayer, for example \citep{NaTr00}.
 
@@
 \centering
-\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
+\includegraphics[width=\textwidth]{fig6.eps}
 %\includegraphics[width=0.8\textwidth]{slipper.eps}
@@
   undergoes tank-treading motion like in the shear flow case. 
-  \ReviewerThree{The horizontal dashed line represents time in units of
+The horizontal dashed line represents time in units of
     $\upmu$s and the vertical axis represents the scaled $y$ position
-    of the centroid of the JP vesicle.}
+    of the centroid of the JP vesicle.
   The arrows
@@
 
-\subsection{\ReviewerOne{Stretching and Permeability}}
+\subsection{Stretching and Permeability}
 \label{sec:ves_in_quiescent}
@@
 \centering
-\includegraphics[width=\textwidth]{Figure2_part1_Wrapper.pdf}
+\includegraphics[width=\textwidth]{fig7.eps}
 \caption{\label{figure2part1} Tension and pressure relax as
@@
 \centering
-\includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
+\includegraphics[width=\textwidth]{fig8.eps}
 \caption{\label{figure2}  
@@
 \label{eq:baseline_energy}
-G = \gamma \int_{\Omega} \rho |\nabla \ReviewerTwo{\eta}|^2 + \rho^{-1} \ReviewerTwo{\eta}^2 \,\dif\xx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
+G = \gamma \int_{\Omega} \rho |\nabla \eta |^2 + \rho^{-1} \eta ^2 \,\dif\xx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
        P(|\tilde{\xx}_i - \tilde{\xx}_j|).
@@
 If $\gamma$ and $M$ are scaled by a parameter $k$, 
-we can related the scaled energy to that of the baseline case by 
+we can relate the scaled energy to that of the baseline case by 
 \[E_k(x) = k(G(x) + H(x)).\]
@@
   \begin{center}
-\includegraphics[width=\textwidth]{Figure9_Wrapper.pdf}
-%  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
+\includegraphics[width=\textwidth]{fig9.eps}
 \end{center} 
@@
   \centering
-\includegraphics[width=\textwidth]{Figure10_Wrapper.pdf}  
-%\includegraphics[height=2in]{N116_shear_0.pdf}
-%\includegraphics[height=2in]{N116_shear_2500.pdf}\\
-%\includegraphics[height=2in]{N116_shear_5000.pdf}
-%\includegraphics[height=2in]{N116_shear_7500.pdf}
+\includegraphics[width=\textwidth]{fig10.eps}  
   \caption{\label{figure10} 
@@
 \begin{center}
-\includegraphics[width=0.97\textwidth]{Figure11_Wrapper_New.pdf}
+\includegraphics[width=0.97\textwidth]{fig11.eps}
 \end{center} 
@@
   \centering
-  \includegraphics[width=\textwidth]{Figure12_Wrapper.pdf}
+  \includegraphics[width=\textwidth]{fig12.eps}
   \caption{\label{figure12} The figure is for the simulation case (iii) of Figure~\ref{figure11},
@@
   \centering
-  \includegraphics[width=\textwidth]{Figure13_Wrapper.pdf}
+  \includegraphics[width=\textwidth]{fig13.eps}
   \caption{\label{figure13} Comparisons between the proposed HAP model and a continuum model
@@
 
-\ReviewerOne{Since the behavior of the suspended JP vesicles has similarities to the numerical 
+Since the behavior of the suspended JP vesicles has similarities to the numerical 
 results generated by using the algorithm adopted in \cite{qua-vee-you2019} (refer to all figure
@@
 the results of continuum model does not have a periodic motion and two vesicles flow apart 
-after 1.5 $\mu$s. Panel (b) shows that the results of the continuum model have a similar trend as  the proposed model.}
+after 1.5 $\mu$s. Panel (b) shows that the results of the continuum model have a similar trend as  the proposed model.
 

### 2022-03-21 doc/JFM2022/OldStuff/scaling_laws.tex
final product

\documentclass[12pt,letterpaper, onecolumn]{article}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{epsfig}
\usepackage{subcaption}
\usepackage{sectsty}
\usepackage{amssymb}
\usepackage{amsmath,empheq}

\begin{document}
\title{Nondimensionalization of Lipid Dynamics Model}
\maketitle

Length scale: a half of lipid length $[L]=1.25\ \text{nm}$\\

water viscosity at $20^\circ$C$=293.15^\circ$K: $\mu=1\ \text{cP}= 10^{-12}\ \frac{\text{kg}}{\text{sec}\cdot\text{nm}}$  \\

Line tension $\gamma=\frac{45}{11}$ mJ/nm$=1\ $kT/nm $\approx 4.1$ pN nm\\

set force scale $[F]=\gamma$, we obtain\\

time scale $\displaystyle [T] = \frac{\mu [L]^2}{[F]} = \frac{11\cdot 10^{-12}\ \frac{\text{kg}}{\text{sec}\cdot\text{nm}}\cdot 1.25^2\ \text{nm}^2}
{4.5\cdot10^{-2}\ \frac{\text{kg}\cdot\text{nm}}{\text{sec}^2}} 
\approx 3.82\times10^{-10}\ $sec\\

Energy scale $[E] = [F][L] = 1\cdot1.25\ $kT $= 5.13\ $pN nm\\

dimensionless shear rate $\chi = \dot\gamma [T]$\\

(ref. Finken, Eur. Phys. J. E. {\bf 25}, 2008)

For $N=50$ vesicle simulations, the initial radius of the vesicle is \\ $R_0=6.75 [L] = 8.4375$ nm, the bending rigidity $\kappa=8.51$ kT $\approx35$ pN nm (SIAM MMS paper)\\

$\chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa} = \dot\gamma \cdot\frac{  10^{-12}\frac{\text{ kg}}{\text{sec $\cdot$ nm}} \times 8.4375^3 \text{ nm}^3}{ 35\times 10^{-3} \frac{\text{ kg}\cdot\text{nm}^2}{\text{sec}^2}} = \dot\gamma \cdot 17.16\times10^{-9}$ sec $ = \dot\gamma \cdot 44.92[T]$. \\

(ref. Brandner et al.)
In Figure 7, the shear rates are \\(a) $\dot\gamma = 3.7\times10^7\ s^{-1}$; (b) $\dot\gamma = 1.9\times10^9\ s^{-1}$; (c) $\dot\gamma = 3.7\times10^9\ s^{-1}$\\

By applying our timescale [T], we have all dimensionless shear rates: \\
(a) $\chi = 0.0141$; (b) $\chi = 0.7258$; (c) $\chi = 1.41$.\\
%Moreover, the paper mentions that the time step is 10 fs. This suggests that we can 
%use $\Delta t \approx 2.5\times10^{-5}$\\

If we adopt the scaling law from Finken's paper with $R_0=10$ nm, then we have 
$\chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa} \approx \dot\gamma \cdot 75[T]$.

\section{What kind of velocities can we expect?}
The characteristic viscous forces must be in balance with the characteristic mechanical forces. 
For the kinds of system we deal with, there are two kinds of mechanical force densities:  
\begin{equation}
\text{due to tension } \gamma H \quad  \text{ and } \quad  \text{due to bending } k_B(\Delta_{\Sigma} H + 2H(H^2-K))
\end{equation}
where $\gamma$ is interfacial tension, $k_B$ is bending, $H$ is mean curvature, and $K$ is Gaussian curvature. 
If we are talking about a 10 nm oil droplet in water, then $\gamma = 30$ pN / nm is a typical oil-water tension and $k_B = 0$ kT.  The force due to tension would be like 
\begin{equation}
\gamma H = \gamma \frac{1}{2R} = 30 \frac{ \text{pN} }{\text{nm}} \frac{1}{20 \text{ nm }} = 1.5 \frac{ \text{pN} }{\text{nm}^2}
= O \left(\frac{ \text{pN} }{\text{nm}^2}\right)
\end{equation}
That is $10^6$ Pa, about 10 atmospheres.  If we are talking about a vesicle, then $\gamma = 0$ pN / nm and 
$k_B = 10 \text{ kT } \approx 41 \text{ pN nm}$.  The force due to bending assuming 
$O(1)$ second derivative in curvature would be 
\begin{equation}
k_B \Delta_{\Sigma} H 
=  O\left( \gamma \frac{1}{2R \text{ nm}^2}             \right) 
=  O\left( \frac{ 41 \text{ pN nm}}{2R \text{ nm}^2} \right)
=  O\left( \frac{\text{ pN }}{ \text{ nm}^2} \right)
\end{equation}
Bending and tension are comparable for nm deformations.

The characteristic viscous forces are set by the gradient of the background velocity. 
Consider a shear background shear flow
\begin{equation}
\mathbf{u}_{\infty} = \dot \gamma \mathbf{x} \cdot \mathbf{e}_y \mathbf{e}_x
\end{equation}
With $\mu = 1 \text{ cP} = 1 \text{ pN ns nm}^{-2}$, the characteristic force density is 
\begin{equation}
\mu \nabla \mathbf{u}_{\infty} 
= O\left(\dot \gamma \frac{\text{ pN ns}}{\text{nm}^{2}} \right)
\end{equation}
We see that mechanical forces are comparable to viscous forces when $\dot \gamma = O( \text{ns}^{-1})$.
Thus it is not surprising that our shear rate us so large.

For a parabolic flow, 
\begin{equation}
\mathbf{u}_{\infty} = v_{\max}\left( 1 - \left( \frac{\mathbf{x} \cdot \mathbf{e}_y}{w R_0} \right)^2 \right)\mathbf{e}_x.
\end{equation}
In simulations, $|\mathbf{x}| \sim R_0$ and 
the characteristic force density is 
\begin{equation}
\mu \nabla \mathbf{u}_{\infty} 
= O\left(\frac{\text{ pN ns}}{\text{nm}^{2}}  \hat v_{\max}\frac{ \text{nm}}{ \text{ns}}\frac{2|\mathbf{x}|}{w^2R_0^2}\right)
= O\left(\frac{\hat{v}_{\max}}{5w^2}\frac{\text{ pN}}{\text{nm}^{2}} \right)
\end{equation}
For $w = 1$, say, viscous forces balance mechanical ones when $\hat{v}_{\max}$ order 10.  In the parabolic flow, the 
viscous forces balance the mechanical ones for $v_{\max}$ in the 10s of nm / ns.
\end{document}

### 2022-03-22 doc/JFM2022/OldStuff/reviews/ResponseToReviewer2.tex

--- 2022-02-16 doc/reviews/ResponseToReviewer2.tex
@@
 To highlight both the similarity and difference between our JP vesicle and the lipid bilayer vesicle, we study (1) the hydrodynamics of a JP vesicle in various flow conditions to compare with the corresponding results for a lipid bilayer vesicle,
-and (2) we compute the friction between the two JP leaflet, and the permeability of a JP bilayer.
+(2) we compute the friction between the two JP leaflet, and the permeability of a JP bilayer.
 We find that the permeability of a JP vesicle allows the total water content enclosed in the JP vesicle to reach an equilibrium value in a flow.
-We find that the JP vesicle is actually closer to a permeable vesicle that we studied previously, where the 2D vesicle has a constant perimeter but the enclosed area does not stay constant.
+We find that the JP vesicle is actually closer to a permeable vesicle, where the 2D vesicle has a constant perimeter but the enclosed area does not stay constant.
 
-In terms of validation of our numerical results of JP vesicle of nano meter size, we have made comparison with the simulations of vesicle of the same size in the literature.
+In terms of validation of our numerical results of JP vesicle of nanometer size, we have made comparison with the simulations of vesicle of the same size in the literature.
 For example we compare both the permeability and the inter-leaflet friction coefficient of a JP bilayer membrane with those of a lipid bilayer membrane.
@@
 We also compared the hydrodynamics of a JP vesicle and a lipid bilayer vesicle under various flowing conditions.
-These results are summarized in the original manuscript and re-organized in the revision with better clarity.
+These results are summarized
+and re-organized in the revision with better clarity.
 
@@
   The notation $\eta$ was used by Stjepan Marcelja to first pose the HAP formulation
-  (Croatica Chemica Acta, 1977).
+  in Croatica Chemica Acta, 1977.
 \end{itemize}
@@
   and other elastic parameters can be deduced from simulation data.
-  At this point, however, we do not have an analytical connection between
-  the input and moduli and inputs, other than some scaling relationship.
+  At this point, however, we do not have any analytical connection between
+  the input and moduli and inputs, other than some scaling relationships.
   Please see the next comment, though, regarding the bending and stretching
@@
 \item Change: In the beginning of Section 4.1,
-  we now point out that such an analysis was part of our previous work.  
+  we now point out that such an empirical analysis was part of our previous work.  
 \end{itemize}
@@
 \begin{itemize}
-\item Response:  We thank the Reviewer for pointing out this interesting connection. 
+\item Response:  We thank the Reviewer for pointing out this intriguing connection. 
 \item Change:  Reviewer 1 requested a parametric study of membrane rupture which
@@
 For impermeable vesicles, the referee is correct about the numerical errors reported in the literature.
-However, the JP membrane is permeable and in our simulations we found that the Janus vesicle needs time so the Janus particles in the membrane can re-arrange themselves.
+However, the JP membrane is permeable and in our simulations we found that the
+  JP vesicle needs time so the particles in the membrane can re-arrange themselves.
 During this process of rearrangement the JP bilayer membrane behaves as a permeable membrane as in Quaife, Gannon and Young (PRF 2021).
 For a JP vesicle in a linear shear flow with a shear rate of dimensionless shear $\chi = 0.002$ the enclosed area reaches a nearly constant value after $1$ $\mu$s.
-We would like to point out that this is not a numerical error, but a consequence of Janus particle hydrodynamics that gives rise to membrane permeability.
+We would like to point out that this is not a numerical error, but a consequence of JP hydrodynamics that gives rise to membrane permeability.
 

### 2022-03-22 doc/JFM2022/OldStuff/main_jfm_orig.tex

--- 2022-02-16 doc/main_jfm.tex
@@
 \usepackage{todonotes}
-
 %
@@
 \newcommand{\jump}[1]{[\![ #1 ]\!]}
-\newcommand{\ReviewerOne}[1]{\textcolor{red}{#1}}
-\newcommand{\ReviewerTwo}[1]{\textcolor{green}{#1}}
-\newcommand{\ReviewerThree}[1]{\textcolor{magenta}{#1}}
 
@@
 %\title{Two-Dimensional Vesicles Under External Flow via Integral Equation Method}
-\title{Two-Dimensional Hydrodynamics of a Janus Particle Vesicle}
+\title{Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential}
 %\title{Hydrodynamics of Amphiphilic Particles in Background Flows}
@@
   and at large shear rates, membrane rupture. 
-  The simulations studies include a Janus particle vesicle in both linear and parabolic shear flows,  and 
-  interactions between two Janus particle vesicles in shear and extensional flows. The hydrodynamics of the Janus 
-  particles vesicle is similar to the behaviour of an inextensible elastic vesicle membrane with permeability.
+  The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
+  interactions in shear and extensional flows. The hydrodynamics of the Janus 
+  particles vesicle replicate the behaviour of an inextensible elastic vesicle membrane.
 %    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
@@
   the mobility problem. The color map in panels (b)--(e) is the solution
-  $u$ of \eqref{eq:SL}. Red is for $\ReviewerTwo{\eta} = 1$ and blue is for $\ReviewerTwo{\eta} = 0$.
+  $u$ of \eqref{eq:SL}. Red is for $u = 1$ and blue is for $u = 0$.
   Particles self-assemble into vesicle bilayers (panel (b)) and
   eventually arrange along inner and outer leaflets. In panel (c), $C_M$
-  is the midplane curve, \ReviewerOne{and} $A$ is the enclosed area\ReviewerOne{.}
-  %, and $L$ is the arc length. 
-  Initially stretched vesicles relax to equilibrium with fluid
+  is the midplane curve, $A$ is the enclosed area, and $L$ is the arc
+  length. Initially stretched vesicles relax to equilibrium with fluid
   flow across the bilayer. The study considers a single vesicle in
@@
 a Janus suspension under various flows. The JP vesicles in our
-simulations replicate  \ReviewerOne{well-known} vesicle hydrodynamics
-such as tank-treading and inter-leaflet slippage in a shear flow and
-migration in Poiseuille flow from continuum models. Furthermore we use
-the hybrid continuum model to investigate permeability and rupture of a
-bilayer membrane due to an imposed flow.  Finally, we compare a pair of
+simulations replicate  well-know vesicle hydrodynamics such as
+tank-treading and inter-leaflet slippage in a shear flow and migration
+in Poiseuille flow from continuum models. Furthermore we use the hybrid
+continuum model to investigate permeability and rupture of a bilayer
+membrane due to an imposed flow.  Finally, we compare a pair of
 interacting JP vesicles with a continuum model of a pair of vesicles.
 
-%\cite{Brandner2019} used the coarse-grained force field with a lattice
-%Boltzmann molecular dynamics to simulate the hydrodynamics of a
-%nano-sized vesicle under a shear flow.  In MD simulations, the
-%hydrodynamic interactions for the solvent phase are often approximated
-%by an implicit solvent coarse-grained model.  In the present work, the
-%hydrodynamic interactions come from the mobility problem for the Stokes
-%equations for the incompressible, viscous solvent.
-
-To simulate the hydrodynamics of Janus particles in Stokes flow,
-we require a numerical method to avoid unphysical contact between rigid
+\cite{Brandner2019} used the coarse-grained force field with a lattice
+Boltzmann molecular dynamics to simulate the hydrodynamics of a
+nano-sized vesicle under a shear flow.  In MD simulations, the
+hydrodynamic interactions for the solvent phase are often approximated
+by an implicit solvent coarse-grained model.  In the present work, the
+hydrodynamic interactions come from the mobility problem for the Stokes
+equations for the incompressible, viscous solvent.
+
+We require a numerical method to avoid unphysical contact between rigid
 Janus particles. Optimization-based contact methods introduce
@@
 stiffness, but with the presence of the hydrophobic forces, we maintain
-contact-free suspensions with a relatively \textcolor{red}{soft} repulsive
-force \textcolor{red}{(compared to the short-range repulsion that diverges in the Lennard-Jones potential)}.
+contact-free suspensions with a relatively weak non-stiff repulsive
+force.
 
@@
 \begin{alignat}{3}
-\label{eq:stokes}
   -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
@@
 pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
-%
 Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
-\ReviewerOne{the no-slip boundary condition}
-\begin{align}
-\label{eq:rigid_bc}
-  \ReviewerOne{\uu}(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
+\begin{align}
+  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
     \xx \in \Gamma_i,
@@
 angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
-\rangle$.
-%Therefore, the no-slip boundary condition on each particle is
-%
-%
-%\begin{align}
-%\label{eq:rigid_bc}
-%  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
-%    \xx \in \Gamma_i.
-%\end{align}
-%
-%
+\rangle$. Therefore, the no-slip boundary condition on each particle is
+\begin{align}
+\label{eq:rigid_bc}
+  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
+    \xx \in \Gamma_i.
+\end{align}
 To determine the translational and angular velocities of each particle,
@@
 \right)$ is the hydrodynamic stress tensor (pressure tensor) and
-$\nnu$ is the particle outward normal. The process of finding the
+$\nnu_i$ is the particle outward normal. The process of finding the
 translational and angular velocities given the forces and torques is
@@
   \label{eq:SL}
--\rho^2 \Delta \ReviewerTwo{\eta} + \ReviewerTwo{\eta} &=0,            && \xx \in \Omega,\\
+-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
 \label{eq:SLbc}
-\ReviewerTwo{\eta}(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
+u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
 \label{eq:SLff}
-\ReviewerTwo{\eta} &\to 0,                          &&|\xx| \to \infty,
+u &\to 0,                          &&|\xx| \to \infty,
 \end{alignat}
@@
 \mathbf{T}
-= \gamma\rho^{-1}\ReviewerTwo{\eta}^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
-  \ReviewerTwo{\eta}|^2 \mathbf{I} - \nabla \ReviewerTwo{\eta}  \nabla \ReviewerTwo{\eta}^T\right)
+= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
+  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
 \end{align}
@@
 $\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
-$P(r) = M(1 - \sin(r/\rho_0))$.
-Then, the total imposed force and torque
+$P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently large to
+prevent particle collisions. Then, the total imposed force and torque
 are
-\begin{equation}
-\label{eq:total_forces}
+\begin{align}
   \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
@@
   i=1,\ldots,N_b.
-\end{equation}
-
-\ReviewerThree{
-The high-order interpolation-based quadrature rule used to compute the nearly-singular integrals has
-been shown to capture well the lubrication hydrodynamics in the narrow space between boundaries 
-when the repulsive potential $P$ gives a large steric force \citep{qua-bir2014}.  
-In the simulations we adjust the spatial resolution on the particle boundary to ensure that the lubrication hydrodynamics is well resolved as in \citep{qua-vee-you2019,qua-gan-you2021}.
-}
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%% moved to new section 3.4
-
-%\subsection{Time Marching}
-%By solving the mobility problem, we obtain translational and angular
-%velocities of the $N_b$-body system. 
-%A second-order Adams-Bashforth
-%scheme updates the particle positions and orientations. By including the
-%repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
-%when using a relatively large time step.
+\end{align}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Time Marching}
+By solving the mobility problem, we obtain translational and angular
+velocities of the $N_b$-body system. 
+A second-order Adams-Bashforth
+scheme updates the particle positions and orientations. By including the
+repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
+when using a relatively large time step.
 
@@
 $N$ points on each of the $N_b$ particles with a collocation method.
-\ReviewerOne{All derivatives are computed with spectrally-accurate
-Fourier differentiation.} Integrals that are smooth are computed with
-the spectrally-accurate trapezoid rule, and nearly-singular integrals,
-caused by close contact between two particles, are computed with a
-high-order interpolation-based quadrature rule (\cite{qua-bir2014}).
-After discretizing and applying quadrature, the resulting linear system
-is solved with matrix-free GMRES, and we guarantee that the number of
-GMRES iterations is mesh-independent by using second-kind BIEs.
+Integrals that are smooth are computed with the spectrally-accurate
+trapezoid rule, and nearly-singular integrals, caused by close contact
+between two particles, are computed with a high-order
+interpolation-based quadrature rule (\cite{qua-bir2014}). After
+discretizing and applying quadrature, the resulting linear system is
+solved with matrix-free GMRES, and we guarantee that the number of GMRES
+iterations is mesh-independent by using second-kind BIEs.
 
@@
 \subsection{HAP Boundary Integral Equation}
-Similar to our previous work (\cite{Fu20}), we represent the
-\ReviewerTwo{hydrophobic attraction potential (HAP)} as a double-layer
-potential
+Similar to our previous work (\cite{Fu20}), we represent the HAP as a
+double-layer potential
 \begin{align}
   \label{eq:HAP_DLP}
-  \ReviewerTwo{\eta}(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
-    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
-    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \Omega,
+  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
+    \quad \xx \in \Omega,
 \end{align}
 where $K_0$ is the zeroth-order modified Bessel function of the first
-kind and the integral is taken in the sense of principle value whenever
-$\xx \in \partial \Omega$.  By requiring that the density function
-$\sigma$ satisfies the second-kind integral equation
+kind and the integral is taken in the sense of principle value whenever $\xx \in \partial \Omega$. 
+By requiring that the density function $\sigma$ satisfies the
+second-kind integral equation
 \begin{equation}
@@
   f(\xx) = \frac{1}{2}\sigma(\xx) + 
-    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
-    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
-    \dif s_\yy, \quad \xx \in \bd\Omega,
+    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
+    \quad \xx \in \bd\Omega,
 \end{equation}
@@
   \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
-    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
+    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
     \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
@@
     \frac{\rr \cdot \nnu}{|\rr|^2} \frac{\rr \otimes \rr}{|\rr|^2}
-    \cdot \eeta(\yy) \, \dif s_\yy,
-\end{align}
-where $\rr = \xx - \yy$. The Stokeslet and rotlets centred at $\aa_i$
-are
-\begin{align}
-  \SS(\xx,\aa_i) \cdot \FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
-    \frac{\rr \otimes \rr}{|\rr|^2}\right) \cdot \FF_i, \\
-  \RR(\xx,\aa_i) T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
-\end{align}
-respectively, where $\rr = \xx - \aa_i$. The Stokeslet is torque-free
-and has force $\FF_i$ while the rotlet is force-free and has torque
-$T_i$. Therefore, the velocity~\eqref{eq:velocity} satisfies the total
-force~\eqref{eq:force} and torque~\eqref{eq:torque} conditions if the
-double-layer potential $\DD[\eeta]$ is force- and torque-free.  Matching
-the limit of~\eqref{eq:velocity} with the rigid body motion, and
-imposing that $\DD[\eeta]$ is force- and torque-free, the density
-function $\eeta$, translational velocity $\vv_i$, and angular velocity
-$\omega_i$ satisfy
+    \eeta(\yy) \, \dif s_\yy,
+\end{align}
+where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and rotlets
+centred at $\aa_i$ are
+\begin{align}
+  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
+    \frac{\rr \otimes \rr}{|\rr|^2}\right) \FF_i, \\
+  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
+\end{align}
+respectively, where $\rr = \xx - \aa_i$. The
+Stokeslet is torque-free and has force $\FF_i$ while the rotlet is
+force-free and has torque $T_i$. Therefore, the
+velocity~\eqref{eq:velocity} satisfies the total force~\eqref{eq:force}
+and torque~\eqref{eq:torque} conditions if the double-layer potential
+$\DD[\eeta]$ is force- and torque-free.  Matching the limit
+of~\eqref{eq:velocity} with the rigid body motion, and imposing that
+$\DD[\eeta]$ is force- and torque-free, the density function $\eeta$,
+translational velocity $\vv_i$, and angular velocity $\omega_i$ satisfy
 \begin{alignat}{3}
@@
     + \sum_{j=1}^{N_b} &
-    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),
+    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
     \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
   \label{eq:mobility1}
-  \int_{\Gamma_i} \eeta \cdot \nnu \, \dif s &= {\bf 0}, 
+  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
   &&i = 1,\ldots,N_b, \\
   \label{eq:mobility2}
-  \int_{\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu \, \dif s &= 0,
+  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu_i \, \dif s &= 0,
   &&i = 1,\ldots,N_b.
@@
   \label{eq:uidef}
-  w_i(\xx) = \ReviewerTwo{\eta}(\xx) - \ReviewerTwo{\eta}_i(\xx),
+  v_i(\xx) = u(\xx) - u_i(\xx),
 \end{align}
@@
 \begin{align}
-  \ReviewerTwo{\eta}_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \left(\pderiv{}{\nnu_\yy}
-    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
-    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \mathbb{R}^2.
-\end{align}
-That is, $w_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
-with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $w_i$, we prove
+  u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
+    \quad \xx \in \mathbb{R}^2.
+\end{align}
+That is, $v_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
+with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $v_i$, we prove
 \begin{theorem}
@@
   \label{eq:jumpstress1}
-  \JJ_{i} = 2\gamma\rho^{-1} \sigma w_i \nnu + 
-    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{ds} \nnu -
-    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{d\nnu} \ttau.
+  \JJ_{i} = 2\gamma\rho^{-1} \sigma v_i \nnu + 
+    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{ds} \nnu -
+    2\gamma\rho \frac{d\sigma}{ds} \frac{dv_i}{d\nnu} \ttau.
 \end{align}
@@
 using~\eqref{eq:hydrophobicAttraction} is that the components $\sigma$,
-$w_i$, $\frac{d\sigma}{ds}$, and $\frac{dw_i}{ds}$ of $\JJ_i$ are smooth
+$v_i$, $\frac{d\sigma}{ds}$, and $\frac{dv_i}{ds}$ of $\JJ_i$ are smooth
 functions, whereas the components of \eqref{eq:stress} are singular
@@
   {\bf T} &=
-    \SS(\ReviewerTwo{\eta}_i,\ReviewerTwo{\eta}_i) +(\SS(\ReviewerTwo{\eta}_i,w_i) +\SS(w_i,\ReviewerTwo{\eta}_i)) +\SS(w_i,w_i) \\
+    \mathbf{S}(u_i,u_i)
+  +(\mathbf{S}(u_i,v_i)
+  +\mathbf{S}(v_i,u_i))
+  +\mathbf{S}(v_i,v_i) \\
   &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
@@
 \label{eq:Tsplit}
-\SS(\ReviewerTwo{\eta},v)
-=  \gamma\rho^{-1} \ReviewerTwo{\eta}v {\bf I} + \gamma\rho \nabla \ReviewerTwo{\eta} \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla \ReviewerTwo{\eta} \nabla v^T.
+\mathbf{S}(u,v)
+=  \gamma\rho^{-1} uv {\bf I} + \gamma\rho \nabla u \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla u \nabla v^T .
 \end{equation}
-Using the fact that $\ReviewerTwo{\eta}$,  $\ReviewerTwo{\eta}_i$, and $w_i$ solve the screened Laplace
+Using the fact that $u$,  $u_i$, and $v_i$ solve the screened Laplace
 equation~\eqref{eq:SL},  and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1,
@@
   \label{eq:prejump}
-  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \jump{{\bf T}_2 \cdot \nnu}  \, \dif s,\quad
-  T_i^{\mathrm{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
-  \jump{{\bf T}_2 \cdot \nnu} \, \dif s.
+  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \jump{{\bf T}_2  \nnu}  \, \dif s,\quad
+  T_i^{\mathrm{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot \jump{{\bf T}_2 \nnu} \, \dif s.
 \end{align}
@@
 \begin{align}
-  \FF_i = \int_{\Gamma_i} \left({\bf T}_1 \cdot \nnu + 
-    {\bf T}_2 \cdot \nnu + {\bf T}_3 \cdot \nnu \right) \,\dif s.
+  \FF_i = \int_{\Gamma_i} {\bf T}_1\nnu + 
+    {\bf T}_2\nnu + {\bf T}_3\nnu\,\dif s.
 \end{align}
@@
 smooth and $\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n
-\setminus U_i$. Similarly, $w_i = \ReviewerTwo{\eta} - \ReviewerTwo{\eta}_i$ is smooth and $\nabla \cdot
+\setminus U_i$. Similarly, $v_i = u - u_i$ is smooth and $\nabla \cdot
 {\bf T}_3 = \mathbf{0}$ in $U_i$. By the divergence theorem,  
 \begin{align}
-  \int_{\Gamma_i}  {\bf T}_1 \cdot \nnu \,\dif s
+  \int_{\Gamma_i}  {\bf T}_1\nnu \,\dif s
   = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,\dif \xx = \mathbf{0},\quad
-    \int_{\Gamma_i}  {\bf T}_3 \cdot \nnu\,\dif s
+    \int_{\Gamma_i}  {\bf T}_3 \nnu\,\dif s
   = \int_{U_i} \nabla \cdot {\bf T}_3 \,\dif \xx = \mathbf{0}.
 \end{align}
-Finally, $u_i$ and $w_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
-\begin{align}
-  \mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \, \dif \xx = \int_{\Gamma_i}  
-    ({\bf T}_2 \cdot \nnu)^-\,\dif s,
+Finally, $u_i$ and $v_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
+\begin{align}
+  \mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \, \dif \xx = -\int_{\Gamma_i}  
+    ({\bf T}_2 \nnu)^-\,\dif s,
 \end{align}
@@
 Combining the above gives the first equation in \eqref{eq:prejump}.
-The derivation for the second equation in \eqref{eq:prejump} is identical. 
+The argument for the second equation in \eqref{eq:prejump} is identical. 
 \end{proof}
@@
 \label{eq:DLjump}
-\jump{\ReviewerTwo{\eta}_i} = \sigma, \quad
-\jump{w_i} = 0, \quad
-\jump{\nabla \ReviewerTwo{\eta}_i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
-\jump{\nabla w_i} = \mathbf{0},
+\jump{u_i} = \sigma, \quad
+\jump{v_i} = 0, \quad
+\jump{\nabla u_i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
+\jump{\nabla v_i} = \mathbf{0},
 \end{equation}
-on $\Gamma_i$ (see, e.g., \cite{KlBaGrON13}). Therefore,
+on $\Gamma_i$ (see, e.g. \cite{KlBaGrON13}). Therefore,
 \begin{align*}
-  \jump{{\bf T}_2 \cdot \nnu}   &= \jump{\SS(\ReviewerTwo{\eta}_i,w_i) \cdot \nnu +
-    \SS(w_i,\ReviewerTwo{\eta}_i) \cdot \nnu} \\
-  &= \Big[\!\Big[ \left( 2\gamma\rho^{-1} \ReviewerTwo{\eta}_i w_i \mathbf{I} + 2\gamma\rho \nabla \ReviewerTwo{\eta}_i \cdot \nabla w_i \mathbf{I} 
-- 2\gamma\rho \nabla \ReviewerTwo{\eta}_i  \nabla w_i^T - 2\gamma\rho \nabla w_i \nabla
-  \ReviewerTwo{\eta}_i^T\right) \cdot \nnu \Big]\!\Big] \\
-%  &= \jump{\left( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
-%- 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla
-%  u_i^T\right) \cdot \nnu}\\
-&= 2\gamma\rho^{-1} \sigma w_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dw_i }{ds} \nnu
-- 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dw_i }{d\nnu} \ttau = \JJ_i.
+  \jump{{\bf T}_2\nnu}   &= \jump{\mathbf{S}(u_i,v_i)\nnu  +\mathbf{S}(v_i,u_i)\nnu} \\
+  &= \jump{( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
+- 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla u_i^T)  \nnu}\\
+&= 2\gamma\rho^{-1} \sigma v_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dv_i }{ds} \nnu
+- 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dv_i }{d\nu} \ttau = \JJ_i.
 \end{align*}
-%\todo[inline]{RR: Can you make sure the last line is correct? There was
-%an unbolded $\nu$ which I changed to a bolded $\nnu$.} RJR -> Correct. Thank you.
 Combining this with~\eqref{eq:prejump} gives~\eqref{eq:recipforcetorque}
 as required.
-
-% what we solve for?
-\ReviewerOne{
-\subsection{Time Marching}
-To summarize, the proposed algorithm aims to obtain the JP velocities ${\bf v}_i$ and $\omega_i$. 
-After calculating the imposed forces $\FF_i$ and torques $T_i$, 
-two density functions $\sigma$ and  $\eeta$ are solved in the second-kind integral equations involving the HAP~\eqref{eq:screenedSKIE} and the mobility problem~\eqref{eq:SKIE}-\eqref{eq:mobility2} via GMRES.
-%By solving the mobility problem, we obtain translational and angular
-%velocities of the $N_b$-body system. 
-Moreover, a second-order Adams-Bashforth
-scheme updates the particle positions and orientations. By including the
-repulsion force~\eqref{eq:REPULforce}, particle collisions can be avoided by setting time step
-size $\Delta t\sim O(10^{-1})$.
-%are avoided even when using a relatively larger time step than $\Delta t\sim O(10^{-1})$ ns. 
-}
 
@@
 \subsection{Model Parameters}
-\cite{Fu20} studied physical quantities for static JP vesicles
-\ReviewerTwo{and empitically deduced realistic bending moduli, stretching moduli,
-  and tilt moduli under reasonable assumptions for the input parameters.}
-In the present work, we study JP vesicles in various background flows.
-We also perform parametric studies of effective properties of the JP vesicles 
-as a function of particle size and interaction strength.
-
-The particles are circular disks with centres 
-$\aa_i$ and unit-length directors $\dd_i$ (Figure \ref{fig:figure0}(a)).
-The simulations use the reference length $l_0 = 2.5$~nm representing the
-thickness of a lipid monolayer.
-The boundary conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
+\cite{Fu20} studied physical quantities for static JP vesicles for
+various particle shapes. In the present study, we fix the particle shape
+and vary the background flows. Specifically, the particles are circular
+disks with diameter $l_0 = 2.5$~nm. The boundary
+conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
 \theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
-$\dd_i$.
-We nondimensionalize the PDE systems 
-\eqref{eq:stokes}-\eqref{eq:total_forces}
-problem through the change of variables 
+$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle centre
+and director respectively. The particle diameter is the thickness of
+monolayers and the director points in the direction of the hydrophobic
+side of the JP.
+
+We use $\rho = 2 l_0$ for decay length, $\rho_0 = 0.2l_0$ for repulsion
+length, $M=4.0$~$k_BT$ for repulsion strength, $\gamma = \text{4.1 pN
+nm}^{-1}$ for interfacial tension, and $\mu = \text{1 cP} = \text{1 pN
+ns nm}^{-2}$ for viscosity of room-temperature water. We
+nondimensionalize the problem through the change of variables 
 %\begin{equation}
@@
 
-The base-case is a single JP vesicle consisting of $N_b = 58$ particles
-with $c = 0.5 l_0$ for particle radius, $\rho = 2 l_0$ for decay length,
-$\gamma = \text{4.1 pN nm}^{-1}$ for interfacial tension.
-The parameter $\mu = \text{1 cP} = \text{1 pN
-ns nm}^{-2}$ is viscosity of room-temperature water. 
-\ReviewerThree{
-  We select \ReviewerOne{$M=4.0$~$\text{pN}$} and $\rho_0 = 0.2l_0$ so that \eqref{eq:REPULforce}
-  prevents particle collisions and is comparable to hydrodynamic lubrication.
-  \citep{cawthorn_balmforth_2010} provide the asymptotic expression 
-  $F_{\text{lubr}} = -\tfrac{3}{2}\pi \mu \dot \epsilon (c/\epsilon)^{3/2}$
-  for the lubrication force between two cylinders in the distance of separation $\epsilon \to 0$.
-  For our choice of simulation parameters, $F_{\text{lubr}}$ and \eqref{eq:REPULforce} are comparable
-  because the particle gaps are comparable to the particle radius
-  and the relative velocities $\dot \epsilon$ between particles are on
-  the order of nm $\text{ns}^{-1}$.
-}
-
 To reach consistent simulation outcomes, we first solve for a baseline
-JP \ReviewerThree{vesicle} that is suitably close to equilibrium. We
-start with an assumed configuration of $N=58$ JP in the form of two,
-circular, apposing monolayers of about $8$ nm in radius. The norms of
-the translational and rotational velocities vanish exponentially with an
-approximate decay rate $\sim 4.6$ $\upmu$s$^{-1}$. An equilibrium
-configuration is therefore rapidly attained. This equilibrium
-configuration serves as the initial data in the subsequent background
-flow simulations.
-
-For a single JP vesicle, we consider background flows for a shear flow 
-(Section \ref{sec:ves_in_shear}), 
-a parabolic flow (Section \ref{sec:ves_in_parabolic}),
-and a quiescent flow (Section \ref{sec:ves_in_parabolic}). 
-In addition to observing the familiar tank-treading motion, the shear
-flow studies yield a friction coefficient for inter-monolayer slip 
-and a critical rupture shear rate.  Permeability coefficients and 
-stretching moduli arise from analyzing stretched JP vesicles in the 
-quiescent background flow case.
+JP vesicles that is suitably close to equilibrium. We start with an
+assumed configuration of $N=58$ JP in the form of two, circular,
+apposing monolayers of about $8$ nm in radius. The norms of the translational and
+rotational velocities vanish exponentially with an approximate decay
+rate $\sim 4.6$ $\upmu$s$^{-1}$. An equilibrium configuration is
+therefore rapidly attained. This equilibrium configuration serves as the
+initial data in the subsequent background flow simulations.
 
@@
 directions, respectively. We use the dimensionless shear rate $\chi =
-\dot \gamma$ ns.
+\dot \gamma$ (s$^{-1}$) ns.
 
@@
   leaflet has slid past the inner leaflet. The slopes of the curves
-  give the slip velocity. 
-  Slip velocity is generally monotonic in the shear rate.
-  The case $\chi = 0.003$ is an exception.}
+  give the slip velocity. With the exception of $\chi = 0.0035$, the
+  slip velocity is generally monotonic in the shear rate.}
 \end{figure}
@@
 value $A^*_{\infty}$. The data in panel (a) are fit to the model $A^* =
-A^*_{\infty} + a_1 \exp(-k_1t) + a_2 \exp(-k_2t),$ $0 < k_2 <
+(A^*_{\infty}-a_1-a_2) + a_1 \exp(-k_1t) + a_2 \exp(-k_2t),$ $0 < k_2 <
 k_1$. Panel (d) shows that $A^*_{\infty}$ decreases with the shear rate.
@@
 
-\ReviewerThree{The time courses contain oscillations due to the
-granularity of the JP vesicle.
-The curve for $\chi = 0.003$ in Figure~\ref{figure4}a, for example, 
-has a low-frequency oscillation with a period around $0.7$ $\upmu$s,
-and a high-frequency oscillation with a period four times smaller.
-The JP vesicle is somewhat hexagonal (see, e.g., Figure~\ref{figure5}a)
-and the low-frequency oscillations corresponds to the tank-treading of a 
-polygon, rather than smooth, curve. The higher frequency oscillations
-come from the trank-treading of individual particles, that is
-they correspond to the rate of passage of particles through a fixed-angle
-axis about the vesicle centre.} 
-The inset of Figure~\ref{figure4}c zooms
+The oscillations in the data of Figure~\ref{figure4} are due to the
+granularity of the JP vesicle. The inset of Figure~\ref{figure4}c zooms
 in on the arc length data for the shear rate $\chi = 0.003$. It shows
-that the curves are smooth and well-resolved by our second-order
+that the oscillations are smooth and well-resolved by our second-order
 Adams-Bashforth scheme.
@@
 
-%original table
-%\begin{table}
-%\caption{Friction Coefficients}
-%\centering
-%\begin{tabular}{c c c c c c c c }
-% $\dot\gamma$  (ns$^{-1}$) & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
-%\hline                    
-%$b$ (pN ns nm$^{-3}$)    & 0.43 & 1.19 &   0.42  & 0.69 &   0.97  &   0.80  &  1.07 \\ 
-%\hline    
-%\end{tabular} 
-%\label{table1}
-%\end{table}
-
-%updated table
 \begin{table}
-\caption{Friction Coefficients $b$ (pN ns nm$^{-3}$) \\
-}
+\caption{Friction Coefficients}
 \centering
-\begin{tabular}{c c c c c c c c c c c c }
+\begin{tabular}{c c c c c c c c }
+ $\dot\gamma$  (ns$^{-1}$) & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
 \hline                    
-& & & & & & $\dot\gamma$  (ns$^{-1}$)& & & & &
-  \\
-  radius ($l_0$) &  $\rho$ ($l_0$) & $\rho_0(l_0)$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  & Average\\
-\cline{4-10}\\
-$-5 \%$ & $- 5 \%$ & $-5 \%$  & 0.22 & 0.36 & 0.41   & 0.45  & 0.45 & 0.44   & 0.44 & 0.40\\
-0.5 &  2.0 & 0.5    & 0.42 & 0.63 & 0.50   & 0.40  & 0.48  & 0.53 & 0.55 & 0.50 \\   % new
-$+5 \%$ & $+ 5 \%$ & $+ 5 \%$  & 0.54 & 0.41 & 0.35  & 0.37 & 0.43 & 0.76  & 0.70 & 0.51\\ 
-$+ 10 \%$ & $+ 10 \%$ & $+ 10 \%$    & 0.50  & 0.51  &  0.44 & 0.52  & 0.45 &  0.57   &  0.62 & 0.52  
+%$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
+%$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
+%$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
+%$b$ (pN$\cdot$ns nm$^{-3}$)    & 0.22 & 0.87*  & 0.22 &0.21 & 1.29* & 0.31 & 0.30\\ 
+$b$ (pN ns nm$^{-3}$)    & 0.43 & 1.19 &   0.42  & 0.69 &   0.97  &   0.80  &  1.07 \\ 
+\hline    
 \end{tabular} 
@@
 \begin{equation}
-  U = \frac{1}{L}\int_{C_M}\left(u_+(\mathbf{x})(1 - \delta \kappa) -
-  u_-(\mathbf{x})(1 +  \delta \kappa)\right) \, ds,
+U = \frac{1}{L}\int_{C_M}u_+(\mathbf{x})(1 - \delta \kappa) - v_-(\mathbf{x})(1 +  \delta \kappa) \, ds,
 \end{equation}
@@
 
-%Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
-\ReviewerOne{Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the baseline number of particles is $N_b = 58$.
-With the fixed total length of the JP vesicle, we change parameters related to the length scale, for instances, $\rho$, $\rho_0$, and the radius of particles.
-With $-5\%$, $5\%$, and $10\%$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{61,56,53\}$, respectively. }
-%
-\ReviewerOne{The trends in Table~\ref{table1}
-  suggest that $b$ decreases with decreasing $\rho$, $\rho_0$, and particle radius.}
-Overall, the values for $b$ are 
-in good quantitative agreement with values previously reported in the literature.
+Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
+over a range of shear rates
+which is in good quantitative agreement with values previously reported in the literature.
 Atomistic studies have also considered inter-monolayer slip in lipid bilayers. 
@@
 for low shear rates. 
-%\subsubsection{Membrane Ruptures}
-%\begin{figure}
-%\centering
-%\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
-%%\includegraphics[height=2in]{N58_rupt_0.pdf}
-%%\includegraphics[height=2in]{N58_rupt_200.pdf}
-%\\
-%%\includegraphics[height=2in]{N58_rupt_400.pdf}
-%%\includegraphics[height=2in]{N58_rupt_600.pdf}
-%  \caption{\label{figure8} Tank-treading leads to membrane rupture for
-%  large shear rates.} 
-%\end{figure}
-%A temporary fissure or a complete membrane rupture can occur at large
-%shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
-%when suspended in a shear flow. For $\chi = 0.1$, starting with a
-%circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
-%background flow and fissures appear in the bilayer structure in multiple
-%locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
-%ruptured vesicles form two planar micelles which are eventually carried
-%off by the flow (Figure~\ref{figure8}d). 
-%%
-%\ReviewerOne{An emperical numerical study has shown that the critical shear rate for a complete membrane rupture is $\chi=0.0655$.
-Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.}
-
 \subsubsection{Membrane Ruptures}
@@
 off by the flow (Figure~\ref{figure8}d).
-%
-
-\ReviewerOne{An emperical numerical study found that for the baseline parameter set,
-the dimensionless, critical shear rate is $\chi_*=0.0655$ so that the membrane ruptured whenever $\chi > \chi_*$
-  and did not rupture whenever $\chi < \chi_*.$ 
-  Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.
-  To further quantify the competition between shear and attraction,
-  we found that a 5 \% relative increase in the parameters $\gamma$ and $M$ 
-  resulted in a  4.24 \% relative increase in $\chi_*$, from $0.0655$ to $0.0688$.
-  A 5 \% decrease in the particle radius $c$, screening length $\rho$ gave a $-9.55$ \% decrease, $5.0 \%$ increase
-  respectively in $\chi_*$.
-  Finally, a 10 \% increase in resting length $L_0$ gave a 20.61 \% decrease in critical shear rate $\chi_*$.}  
-  \ReviewerOne{These relative changes suggest that there is dimensionless number $K$ given by 
-  \begin{equation}
-    \label{eq:CSR}
-  \mu \dot\gamma_* = K \frac{\gamma c^2}{\rho L^2}
-  \end{equation}
-  that relates hydrophobic attraction to the dimensional critical shear rate $\dot \gamma_* = \chi_* \text{ ns}^{-1}$.
-  Assuming a characteristic velocity $L\dot \gamma$, the number $K$ relates to the vesicle's capillary number
-  $\text{Ca} = K c^2/(\rho L)$. Based on the above data, $\text{Ca}$ would be approximately $1.7$
-  so that surface forces are comparable to viscous forces.  
-  There is a related \emph{elastic} capillary number
-  $\tilde{\text{Ca}} = \mu \dot{\gamma} R_0^3/K_B$
-  used to characterize rheological properties of lipid bilayer membranes
-  where $R_0$ is vesicle radius $K_B$ is bending rigidity \citep{VLAHOVSKA2009775, keller_skalak_1982}. 
-  Setting $\text{Ca}$ and $\tilde{\text{Ca}}$ equal, we can derive
-  \[
-  K_B = \frac{\mu \dot \gamma_* R_0^3}{\text{Ca}}
-  \]
-  which yields $K_B \approx 60$ pN $\text{nm}^{-1}$, which is a reasonable
-  value for the bending modulus of a lipid bilayer, for example \citep{NaTr00}.}
 
@@
 \subsubsection{Vesicle in a Parabolic Flow}
-\label{sec:ves_in_parabolic}
 Finally, we consider the parabolic background flow
@@
   drifts toward the central axis. It assumes a slipper shape and
-  undergoes tank-treading motion like in the shear flow case. 
-  \ReviewerThree{The horizontal dashed line represents time in units of
-    $\upmu$s and the vertical axis represents the scaled $y$ position
-    of the centroid of the JP vesicle.}
-  The arrows
+  undergoes tank-treading motion like in the shear flow case. The arrows
   on the left illustrate the background flow and the arrows on the right
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{\ReviewerOne{Stretching and Permeability}}
-\label{sec:ves_in_quiescent}
-
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{Figure2_part1_Wrapper.pdf}
-\caption{\label{figure2part1} Tension and pressure relax as
-  fluid is expelled through the particle interstices. In panel (a), inset, 
-  pressure is spatially constant inside the JP vesicle (inset). and 
-  Laplace pressure ((a), squares) and excess length ((b), squares) dissipate exponentially.  
-  The data in panels (b) and (c) show a linear relationship expressed by
-  \eqref{eq:LaplacePressure} and \eqref{eq:perm}. }
-\end{figure}
-In this section, we consider a circular JP vesicle suspended in a quiescent flow $\uu_{\infty} = 0$.
-We show that the JP particle bilayer behaves as an inextensible, permeable membrane with
-the inextensibility coming from a large stretching modulus.
-
-In membrane continuum  mechanics, changes in membrane surface area $A$ give rise to a tension
-$\tilde \sigma = K_A(A/A_0 - 1)$ where $A_0$ is the reference surface area \cite{NaTr00}. 
-For a two-dimensional membrane, the tension is 
-\begin{align}
-\label{eq:stretch}
-\tilde \sigma = K_A\left(L/L_0 - 1 \right),
-\end{align}
-where $L$ and $L_0$ are arc length and resting length,
-respectively. 
-Membrane tension gives rise to 
-a Laplace pressure 
-\begin{align}
-\label{eq:LaplacePressure}
-\Delta p = \tilde \sigma/R,
-\end{align}
-where $\Delta p$ is the jump in far-field pressure to internal pressure and
-$R = L/2\pi$.
-In order to relieve Laplace pressure, 
-water flows across the membrane. The rate of efflux is governed by  
-\begin{align}
-  \label{eq:perm} 
-  \frac{dA}{dt} = - P\Delta p,
-\end{align}
-where $P = K/(\mu \Delta x)$ is a constant, $K$ is hydraulic permeability, 
-$\mu$ is the solvent viscosity, and $\Delta x$ is the 
-membrane thickness, about 5 nm
-(\cite{chabanon2017, qua-gan-you2021}).
-
-Our  simulation setup consists of an initial, non-equilibrium JP
-obtained by dilating the equilibrium shape outward (Figures~\ref{figure2part1}a).
-At $t = 0$, pressure \eqref{eq:stokes} is spatially constant  inside and outside the vesicle 
-(Figures~\ref{figure2part1}a, inset)
-and Laplace pressure decreases to zero exponentially 
-(Figures~\ref{figure2part1}a,  squares).  
-At the same time, arc length decreases from its initial value $L(0)$ to its resting length $L_0$
-(Figures~\ref{figure2part1}b).
-
-To evaluate whether JP vesicles possess a stretching modulus,
-Figure~\ref{figure2part1}c plots $R \Delta p$ against the excess length $L/L_0 - 1$.  The squares
-are for the baseline simulation with vesicle diameter about 34 nm.  The diamonds 
-are for a vesicle with twice the diameter.  The linear relationships 
-are independent of vesicle size and give an area modulus $K_A = 170 \pm 9$ pN nm$^{-1}$.
- This relatively large stretching modulus is the reason why the JP vesicle conserves length in the 
-shear-flow simulations (Figure \ref{figure2part1}c).
-The value also reasonably agrees with stretching moduli for 
-lipid bilayers, around $240$ pN nm$^{-1}$ \cite{NaTr00}.
-
- In the initial, dilated vesicle,
-contractile motion is limited by the incompressibility of the 
-fluid bound by the vesicle.  
-Hence, the Laplace pressure 
-comes from an excess in inter-particle separation.  The vesicle-bound water,
-however, can escape through the gaps between the particles and this
-is how the JP vesicle relieves Laplace pressure over time (Figure \ref{figure2part1}a).
-
-To evaluate the rate of water outflow, 
-Figure~\ref{figure2part1}d plots the the simulation values for $dA/dt$.  
-These values are proportional to $L\Delta p$ and like for the stretching modulus, 
-the proportionality constants are 
-independent of vesicle size.
-The  linear fits give a hydraulic permeability $P = 0.0290 \pm 0.007$ nm$^3$ ns$^{-1}$ pN$^{-1}$.
-We can combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
-and~\eqref{eq:perm} to derive
-\begin{align}
-\label{eq:perm_solution}
-L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
-\end{align}
-Using the fitted values for $P$ and $K_A$, the theoretical time course for 
-\eqref{eq:perm_solution} (Figure~\ref{figure2part1}b, solid curve) is in good
-agreement with the JP data (Figure~\ref{figure2part1}b, squares).
-
-Our value for permeability disagrees 
-with permeabilities for lipid bilayers by a few orders of magnitude  (\cite{chabanon2017, qua-gan-you2021}).
-Potential reasons for this include the following. 
-Our two-dimensional simulations correspond to water flowing past a collection
-of parallel cylinders, which has a larger permeability than for a collection
-of spheres of comparable radius.   
-Second, permeability vanishes with inter-particle separation.  
-However, in our simulations, inter-particle separation is intentionally made comparable to 
-particle radius to avoid aggresive mesh refinement.
-
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Stretching and Permeability}
 \begin{figure}
@@
 \includegraphics[width=\textwidth]{Figure2_Wrapper.pdf}
-\caption{\label{figure2}  
-The ratios of the abscissa and ordinates from Figure \ref{figure2part1}c, d are well-fit by constant functions (baseline, dots).
-The open circles and diamonds are for $\gamma$ and $M$ increased by 5$\%$ and 10$\%$, respectively. 
-The x's and stars are for particle radius, $\rho$, and $\rho_0$ decreased by 5$\%$ and 10$\%$, respectively.
-The variable $x$ is used to denote the horizontal axis coordinate. 
-}
+%\includegraphics[height=2in]{relax2.eps}
+%\includegraphics[height=2in]{relax.eps}\\
+%\includegraphics[height=2.in]{N58_0pres.pdf}
+%\includegraphics[height=2.in]{N58_5000pres.pdf}
+%  \todo[inline]{Put pressure of each of the two configurations below
+%  this.}
+\caption{\label{figure2} In JP vesicles, tension and pressure relax as
+  fluid is expelled through the particle interstices. In panel (a), the
+  thin curve plots the mean of the norm of the particle translational
+  velocities. The thick curve plots the mean of the absolute value of
+  the particle angular velocities. At $t = 0$ $\upmu$s, the vesicle has
+  a spatially constant internal pressure 0.05~pN nm$^{-2}$ (red color,
+  panel (b)). In panel (c), pressure has dissipated and the vesicle has
+  moved from its initial configuration (gray circles), to the
+  equilibrium configuration (black circles). The data in panels (d) and
+  (e) support the linear relationship expressed by
+  \eqref{eq:LaplacePressure} and \eqref{eq:perm}. Circles are for a
+  vesicle with 17 nm initial radius; square are for a 34 nm initial
+  radius. Asterisks are for a 18 nm initial radius but with smaller,
+  1.25 nm diameter particles. In panel (f), the theoretical time course
+  \eqref{eq:perm_solution} overlaps the data using constants $K_A$ and
+  $P$ derived from panels (d) and (e). }
 \end{figure}
-
-%\begin{table}
-%\caption{Stretching Moduli and Permeabilities}
-%\centering
-%\begin{tabular}{ c c c |c c| c |c }
-% radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (\mathrm{k_BT})$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$%^{-1}$pN$^{-1}$) \\
-%\hline      \hline 
-% 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
-% \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 5 \%$}  & 185$\pm5$  &  0.0292  \\ 
-% \multicolumn{3}{c|}{same} & \multicolumn{2}{c|}{$+ 10 \%$}  & 195$\pm5$  &  0.0294 \\ 
-% \multicolumn{3}{c|}{$- 5 \%$} & \multicolumn{2}{c|}{same}   & 184$\pm5$  &  0.0283 \\ 
-% \multicolumn{3}{c|}{$- 10 \%$} & \multicolumn{2}{c|}{same}   & 189$\pm6$  &  0.0252  \\ 
-%\end{tabular} 
-%\label{table2}
-%\end{table}
-%
-
-\begin{table}
-\caption{Stretching Moduli and Permeabilities}
-\centering
-\begin{tabular}{ c |c| c |c }
- $k$ & $\lambda$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
-\hline    
- 1  & 1  & 170$\pm9$   &  0.0296\\ 
-%
- 1.05 & 1  & 185$\pm5$  &  0.0292  \\ 
-%
- 1.10 & 1  & 195$\pm5$  &  0.0294 \\ 
-%
- 1 & 0.95  & 184$\pm5$  &  0.0283 \\ 
-%
- 1  & 0.9   & 189$\pm6$  &  0.0252  \\ 
-\end{tabular} 
-\label{table2}
-\end{table}
-%
-
-We performed a parametric study of the dependence of $K_A$ and $P$
-on model parameters taking into account   
-(i) changes in interfacial strength and (ii) changes in size.
-Table~\ref{table2} provides the results of stretching moduli $K_A$ and permeabilities $P$ for various cases.
-The baseline setup is shown in the first row.
-The next two rows demonstrate the results when the tension related parameters $\gamma$ and $M$ are increased by 5$\%$ and 10$\%$. 
-The parameter $k$ is used to scale the force paramaters $\gamma, M \to k\gamma, kM$.
-The final two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$
-The parameter $\lambda$ is used to simultaneously scale length parameters;
-$\rho, \rho_0, c \to \lambda \rho, \lambda \rho_0, \lambda c$.
-This data comes from Figure \ref{figure2} which  plots the \emph{ratio} of the abscissa and ordinates
-used in Figure \ref{figure2part1}c, d. The transformed data are fit by constant functions.
-
-Increases in $\gamma$ and $M$ result in
-a commensurate increase in the stretching modulus. 
-Permeability, however, is insensitive to simultaneous increases in $\gamma$ and $M$.
-To give a detailed explanation for this, the JP system has the potential energy $E = G + H$ where 
-\begin{equation}
-\label{eq:baseline_energy}
-G = \gamma \int_{\Omega} \rho |\nabla \ReviewerTwo{\eta}|^2 + \rho^{-1} \ReviewerTwo{\eta}^2 \,\dif\xx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
-       P(|\tilde{\xx}_i - \tilde{\xx}_j|).
-\end{equation}
-Here, $G$ is the hydrophobic attraction potential for the boundary value problem \eqref{eq:SL}--\eqref{eq:SLff},
-and $H$ is the repulsion potential.  
-For the circular vesicle, total energy depends only on the characteristic inter-particle distance $x$
-and has a minimum at $x_0$. 
-If $\gamma$ and $M$ are scaled by a parameter $k$, 
-we can related the scaled energy to that of the baseline case by 
-\[E_k(x) = k(G(x) + H(x)).\]
-Permeability does not change with like increases in $\gamma$ and $M$
-because the critical number for $E_k$, and hence inter-particle separations, are independent to $k$.
-The stretching modulus comes from $\frac{d^2E_k}{dx^2}$ and this 
-quantity varies proportionally with $k$.
-
-One can observe that $K_A$ increases and $P$ decreases as the length scale decreases. 
-The decrease in  $P$ is expected because 
-the size of the gap between adjacent JP particles is directly proportional to length scale.
-To give a more detailed account, pressure $p$ and water flux across the membrane $q$ scale as 
-$p_{\lambda}(\mathbf{x}) = \lambda^{-1} p(\mathbf{x}/\lambda)$ and 
-$q_{\lambda}(\mathbf{x}) = q(\mathbf{x}/\lambda)$ 
-when $l_0$ is scaled by $\lambda$. As a result, the scaled permeability constant satisfies 
-\[
-P_{\lambda} = q_{\lambda}/\Delta p_{\lambda} = q/(\lambda^{-1} \Delta p) = \lambda P.
-\]
-For the stretching modulus, the total energy transforms as 
-\[E_{\lambda}(x) = \lambda G(x/\lambda) + H(x/\lambda ).\]
-The factor $\lambda$ comes from the change of 
-variables formula for the integral in \eqref{eq:baseline_energy}.
-The stretching modulus increases because $\frac{d^2E_{\lambda}}{dx^2}$ increases with decreases in $\lambda.$
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Finally, we show that the JP vesicle behaves as a permeable membrane and the inextensibility comes
+about due to a large stretching modulus.
+%an extensible, permeable membrane. 
+Figures~\ref{figure2}b shows an initial, non-equilibrium JP
+vesicle suspended in a quiescent flow $\uu_{\infty} = 0$. The color map
+plots the pressure $p$. The red color in Figures~\ref{figure2}b shows a
+spatially constant, positive internal pressure (0.05~pN nm$^{-2}$) and the white
+shows a spatially constant zero, external pressure. There is some fluid flow and
+the pressure vanishes as the configuration tends toward the equilibrium
+state (Figures~\ref{figure2}c).
+
+What could be the source of this drop in pressure? In membrane
+continuum  mechanics, small changes in surface area give rise to a membrane tension
+$\tilde \gamma = K_A(A/A_0 - 1)$ where $A$ is the membrane surface area
+and $A_0$ is the reference surface area. The area modulus $K_A$ of
+bilayers is about $240$ pN nm$^{-1}$ (\cite{NaTr00}). In the
+two-dimensional vesicles, the tension becomes
+\begin{align}
+\label{eq:stretch}
+\tilde \gamma = K_A\left(\frac{L}{L_0} - 1 \right),
+\end{align}
+where $L$ and $L_0$ are the vesicle arc length and resting length,
+respectively. Moreover, stretched, circular vesicles has a Laplace pressure 
+\begin{align}
+\label{eq:LaplacePressure}
+\Delta p = \frac{\tilde \gamma}{R},
+\end{align}
+where $\Delta p$ is the difference in internal pressure to the pressure
+at infinity and $R^{-1}$ is the total curvature of the circular
+cylinder.
+
+Figure~\ref{figure2}c plots the data for the pressure jump $\Delta p$
+between the particle centre and the far-field (see
+Figures~\ref{figure2}c and~\ref{figure2}d). We use $R = L/(2\pi)$ for
+the vesicle radius, and the horizontal axis is the relative stretch.
+The circles are data for a vesicle with radius 17 nm. The linear fit
+(solid lines) shows that $R\Delta P$ is proportional to the relative
+stretching $L/L_0 - 1$. The squares are for a vesicle with twice the
+radius 34 nm, and the data overlap supports that the proportionality
+constant $K_A$ is a stretching modulus that is independent of vesicle
+size. The data give $K_A = 170 \pm 9$ pN nm$^{-1}$ which is in good
+agreement with the experimentally obtained area moduli of lipid bilayer. 
+%
+The reason the tank-treading vesicle appears inextensible ($L$ is more or less constant in Figure~\ref{figure4}c) is because the modulus $K_A$ is large.
+%
+To evaluate how changes to particle size lead to different
+physical properties, the asterisk symbols are for an 18 nm radius
+vesicle consisting of particles with diameter 1.25 nm, instead of the
+usual 2.5 nm. These data give a smaller stretching modulus of $K_A =
+102$~pN~nm$^{-1}$.
+
+The particles in our setup do not abut but rather have small gaps due to
+repulsive forces. The gaps allow for some fluid flux across the JP
+bilayer, and in membrane mechanics aqueous flux is quantified by the equation
+\begin{align}
+  \label{eq:perm} 
+  \frac{dA}{dt} = -P L \Delta p,
+\end{align}
+where $P$ is a hydraulic permeability constant (\cite{chabanon2017,
+qua-gan-you2021}). Figure~\ref{figure2}e shows that the data for
+$L\Delta p$ and $dA/dt$ obey the linear relationship expressed by
+\eqref{eq:perm}. The slopes of the linear fits give the hydraulic
+permeabilities $P = 0.0296$ nm$^3$ ns$^{-1}$ pN$^{-1}$ and $P = 0.0283$
+nm$^3$ ns$^{-1}$ pN$^{-1}$ for the 17 nm and 34 nm radius cases,
+respectively. Like the area modulus, the data give a permeability 
+that is independent of vesicle size.
+
 \begin{figure}
@@
 \end{figure}
+
+The hydraulic permeability we calculate, however, is not in agreement
+with experimentally derived values and is larger by a few orders of
+magnitude. We suspect this discrepancy is due to inter-particle distance
+of the JP being large compared to the inter-lipid spacing in real
+bilayers. To test this, we calculate the permeability for the particles
+with diameter 1.25 nm. Due to their smaller size but fixed repulsion
+strength, these particles have a larger inter-particle spacing resulting
+in an increase in permeability, $P = 0.0566$~nm$^3$~ns$^{-1}$~pN$^{-1}$
+(Figure~\ref{figure2}e, asterisk symbols).
+
+Since the vesicles in Figure~\ref{figure2}a are nearly circular, we can
+combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
+and~\eqref{eq:perm}, to derive
+\begin{align}
+\label{eq:perm_solution}
+L_0(L-L(0)) + L_0^2 \ln\left|\frac{L-L_0}{L(0)-L_0}\right| = -4\pi^2 P K_A t.
+\end{align}
+All in all, the theoretical time courses for \eqref{eq:perm_solution} are in good
+quantitative agreement with the JP data (Figure~\ref{figure2}f).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Two Vesicles in a Linear Flow}
+
 \begin{figure}
@@
 \begin{center}
-\includegraphics[width=0.97\textwidth]{Figure11_Wrapper_New.pdf}
+\includegraphics[width=0.97\textwidth]{Figure11_Wrapper.pdf}
+%\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
 \end{center} 
@@
   is $1.25$~nm below the $x$-axis. The streamlines appear in grey and
-  the flow rate is $\dot \gamma =0.005$~ns$^{-1}$ in all cases.
-	  }
+  the flow rate is $\dot \gamma =0.005$~ns$^{-1}$ in all cases.}
 \end{figure}
@@
   \includegraphics[width=\textwidth]{Figure12_Wrapper.pdf}
+%\includegraphics[height=2in]{N116_ext_0.pdf}
+%\includegraphics[height=2in]{N116_ext_2000.pdf}\\
+%\includegraphics[height=2in]{N116_ext_4000.pdf}
+%\includegraphics[height=2in]{N116_ext_6500.pdf}
   \caption{\label{figure12} The figure is for the simulation case (iii) of Figure~\ref{figure11},
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{Figure13_Wrapper.pdf}
-  \caption{\label{figure13} Comparisons between the proposed HAP model and a continuum model
-    for two vesicles in shear flow and in extensional flow.
-  The value $d_{1,2}$ is the distance between two centroids of JP vesicles. The thick curves plot the trajectories
-  of $d_{1,2}$ generated by the continuum model and the thin curves are computed from using
-  the proposed HAP model.}
-\end{figure}
-
-\ReviewerOne{Since the behavior of the suspended JP vesicles has similarities to the numerical 
-results generated by using the algorithm adopted in \cite{qua-vee-you2019} (refer to all figure
-insets in Figure~\ref{figure10} and Figure~\ref{figure12}). Figure~\ref{figure13} shows 
-trajectory comparisons between the proposed model and the continuum modeling for both 
-shear flow and extensional flow cases in two vesicle simulations. The quantity $d_{1,2}$
-represents the distance between two centroids of JP vesicles. The centroid positions are 
-identical for both models and the geometry in the continuum model is created along the 
-midplane locations of JP vesicles and the initial reduced area is matched. Panel (a) shows that 
-the results of continuum model does not have a periodic motion and two vesicles flow apart 
-after 1.5 $\mu$s. Panel (b) shows that the results of continuum model has similar trend of
-dynamics with one in the proposed model.}
-
-%\newpage
+\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %permeability constant $P$. In spite of producing these values with some discrepancy
-%using the baseline parameter set, we provide a new framework in measuring coarse-grained 
+%using the default parameter set, we provide a new framework in measuring coarse-grained 
 %membrane permeability.
@@
 
-Our current numerical method does not support a viscosity contrast
-like that found in
-\citep{PhysRevLett.106.158103,
-  PhysRevE.75.016313,
-  Kaoui2016}.
-The JP vesicle is permeable and the mixture of two different
-fluids requires an introduce of a contact line between
-the two phases.
-
 Our future goals include extending the current framework to a
@@
 algorithmic implementation including a fast summation method such as the
-fast multipole method. Oother research directions include
+fast multipole method. Another research direction is to include the
 fluctuating hydrodynamics for Brownian suspensions~(\cite{Bao2018}),
@@
 %This will result in Janus particles that include Brownian motion, 
-critical to understanding membrane diffusion,
-and an analysis of the relationship between particle shape on effective
-properties.
-Finally, more
+and this is critical to understand membrane diffusion. Finally, a more
 physical boundary conditions for the HAP model will allow us to draw
@@
 \bibliography{reference}% Produces the bibliography via BibTeX.
-
-% Supplementary Materials
-\input{Supplementary}
 

### 2022-03-24 doc/JFM2022/Final/Supplementary.tex
first fix by Rolf

--- 2022-02-16 doc/Supplementary.tex
@@
 {\bf Movie S1.
-Relaxation} There are 58 circular particles with radius 0.5 that form a self-enclosed bilayer structure.
+Relaxation} There are 58 circular particles with radius 1.25 nm that form a self-enclosed bilayer structure.
 The simulation result shows the vesicle relaxation and the fluid pressure inside the JP vesicle decreases to 0 after a period of time.
-The color field from blue to red shows the magnitude of fluid pressure and the range from 0 to 0.1.
-All dark blue dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-This movies includes a total 5000 time steps where the time step is $\Delta t=0.2$.\\
+The color field from blue to red shows the magnitude of fluid pressure and the range from 0 to 0.1 pN nm$^{-2}$.
+All dark blue dots in the domain are tracers that move with the calculated fluid motion.
+This movie includes a total 5000 time steps. \\
 
@@
 {\bf Movie S2. Single Vesicle Suspended in a Shear Flow} 
-We adopt the relaxed configuration and place the JP vesicle in the shear flow. The simulation result shows a tank-treading motion when the shear rate is $\chi=0.005$.
-The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1.
-All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\
+We adopt the relaxed configuration and place the JP vesicle in the shear flow. The simulation result shows a tank-treading motion for the shear rate $\chi=0.005$.
+The colored field from dark blue to dark red shows the hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain are tracers in fluid that move with the fluid motion.
+This movie includes a total 20000 time steps. \\
 
@@
 the yellow particle in the outer leaflet surpasses the blue particle in the inner leaflet by the distance about 1 particle diameter.
-This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\
+This movie includes a total 20000 time steps.\\
 
@@
 {\bf Movie S4. Vesicle Rupture} 
-The numerical results show that the JP vesicle starts to have rupture phase at the shear rate $\chi=0.0655$.
-The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1.
-All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-This movies includes a total 3000 time steps where the time step is $\Delta t=0.2$.\\
+The numerical results show that the JP vesicle ruptures at the shear rate $\chi=0.0655$.
+The colored field from dark blue to dark red shows the hydrophobic attraction activity and the range is from 0 to 1.
+All white dots in the domain are tracers in fluid that move with the fluid motion.
+This movie includes a total 3000 time steps.\\
 
@@
 The two centroids are at coordinates $(-25,0)$ and $(25,0)$ in nm.
-The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1.
-All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\
+The colored field from dark blue to dark red shows the hydrophobic attraction activity and the range is from 0 to 1.
+All white dots in the domain are tracers in fluid that move with the fluid motion.
+This movie includes a total 20000 time steps.\\
 
@@
 The centroid of the left JP vesicle is 0.25 nm above the $x$-axis and the right JP vesicle is 0.25 nm below the $x$-axis.
-The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1.
-All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-This movies includes a total 6000 time steps where the time step is $\Delta t=0.2$.
+The colored field from dark blue to dark red shows the hydrophobic attraction activity and the range is from 0 to 1.
+All white dots in the domain are tracers in fluid that move with the fluid motion.
+This movie includes a total 6000 time steps.
 %%%\end{document}

### 2022-03-25 doc/JFM2022/Final/main_jfm.tex

@@
   The results yield measurements of inter-monolayer friction, membrane permeability, 
-  and at large shear rates, membrane rupture. 
-  The simulations studies include a Janus particle vesicle in both linear and parabolic shear flows,  and 
-  interactions between two Janus particle vesicles in shear and extensional flows. The hydrodynamics of the Janus 
-  particles vesicle is similar to the behaviour of an inextensible elastic vesicle membrane with permeability.
+  and, at large shear rates, membrane rupture. 
+  The simulation studies include a Janus particle vesicle in both linear and parabolic shear flows,  and 
+  interactions between two, Janus particle vesicles in shear and extensional flows. The hydrodynamics of the Janus 
+  particle vesicle is similar to the behaviour of an inextensible, elastic vesicle membrane with permeability.
 %    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
@@
 the richness of a Janus particle suspension, as \cite{deGennes1991} suggested by the example of 
-a ``thin film of Janus grains" that can breathe due to the interstices between Janus particles.
+a ``thin film of Janus grains" that can breathe due to the interstices between particles.
 
@@
   the mobility problem. The color map in panels (b)--(e) is the solution 
-  $u$ of \eqref{eq:SL}. Red is for $\eta  = 1$ and blue is for $\eta  = 0$.
+  $\eta$ of \eqref{eq:SL}. Red is for $\eta  = 1$ and blue is for $\eta  = 0$.
   Particles self-assemble into vesicle bilayers (panel (b)) and
   eventually arrange along inner and outer leaflets. In panel (c), $C_M$
-  is the midplane curve, and $A$ is the enclosed area.
+  is the midplane curve and $A$ is the enclosed area.
   %, and $L$ is the arc length. 
@@
 In the present work, we extend the hybrid continuum model in~\cite{Fu20}
-for the Janus suspension to incorporate the collective hydrodynamics of
-a Janus suspension under various flows. The JP vesicles in our
+for suspensions to incorporate the collective hydrodynamics of
+a JP suspension under various flows. The JP vesicles in our
 simulations replicate well-known vesicle hydrodynamics
@@
 migration in Poiseuille flow from continuum models. Furthermore we use
-the hybrid continuum model to investigate permeability and rupture of a
+the hybrid continuum model to investigate permeability as well as rupture of a
 bilayer membrane due to an imposed flow.  Finally, we compare a pair of
@@
 contact-free suspensions with a relatively soft repulsive
-force (compared to the short-range repulsion that diverges in the Lennard-Jones potential).
+force compared to the short-range repulsion that diverges in the Lennard-Jones potential.
 
@@
 the zero-Reynolds number regime (Figure \ref{fig:figure0}a). In
-\S~\ref{sec:IEM} we extend the hybrid continuum model for a Janus
+\S~\ref{sec:IEM}, we extend the hybrid continuum model for a Janus
 suspension to include the effects of a far-field flow via the mobility
-problem formulation. In \S~\ref{results} we validate our model and
+problem formulation. In \S~\ref{results}, we validate our model and
 present simulation results for a single JP vesicle (Figure
@@
 where $\uu$ is the velocity, $p$ is the
-pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
+pressure, $\uu_\infty$ is the background velocity, and $\mu$ is the constant viscosity. 
 %
@@
 The second part of the imposed forces and torques comes from repulsion
-between proximal particles. Given a pair particles indexed with $i$ and
+between proximal particles. Given a pair of particles indexed with $i$ and
 $j$, we find the two points $\tilde{\xx}_i \in \Gamma_i$ and
@@
   \label{eq:REPULforce}
-  \FF_i^{\text{repul}} &= \sum_{j \neq i} 
+  \FF_i^{\text{repul}} &= \frac{M}{\rho_0} \sum_{j \neq i} 
     \frac{\tilde{\xx}_i - \tilde{\xx}_j}
     {|\tilde{\xx}_i - \tilde{\xx}_j|} 
-    P'(|\tilde{\xx}_i - \tilde{\xx}_j|), \\
+     P'\left(\frac{|\tilde{\xx}_i - \tilde{\xx}_j|}{\rho_0}\right), \\
   \label{eq:REPULtorque}
-  T_i^{\text{repul}} &= \sum_{j \neq i} 
+  T_i^{\text{repul}} &= \frac{M}{\rho_0} \sum_{j \neq i} 
     (\tilde{\xx}_i - \aa_i)^{\perp} \cdot 
@@
     {|\tilde{\xx}_i - \tilde{\xx}_j|} 
-    P'(|\tilde{\xx}_i - \tilde{\xx}_j|).
-\end{align}
-The repulsion profile $P(r)$ is set to zero for distances $r$ larger than a
+     P'\left(\frac{|\tilde{\xx}_i - \tilde{\xx}_j|}{\rho_0}\right).
+\end{align}
+The repulsion profile $P(r/\rho_0)$ is set to zero for distances $r$ larger than a
 repulsion length scale $\rho_0$. As such,~\eqref{eq:REPULforce}
@@
 $\rho_0$-tubular neighborhood of $\Gamma_i$. For $0 \leq r < \rho_0,$ we use
-$P(r) = M(1 - \sin(r/\rho_0))$.
+$P(r) = 1 - \sin(\pi r/2)$.
 Then, the total imposed force and torque
@@
 and torques requires the solution of elliptic partial differential
-equations (PDEs) in an unbounded complex domain. We recast both these
+equations (PDEs) in an unbounded complicated domain. We recast both these
 PDEs as boundary integral equations (BIEs). We discretize each BIE at
@@
 \subsection{HAP Boundary Integral Equation}
-Similar to our previous work (\cite{Fu20}), we represent the
+Similar to the previous work (\cite{Fu20}), we represent the
 hydrophobic attraction potential (HAP) as a double-layer
@@
 \end{align}
-where $\rr = \xx - \yy$. The Stokeslet and rotlets centred at $\aa_i$
+where $\rr = \xx - \yy$. The Stokeslets and rotlets centred at $\aa_i$
 are
 \begin{align}
+\label{eq:stokeslet}
   \SS(\xx,\aa_i) \cdot \FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
     \frac{\rr \otimes \rr}{|\rr|^2}\right) \cdot \FF_i, \\
+    \label{eq:rotlet}
   \RR(\xx,\aa_i) T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
 \end{align}
-respectively, where $\rr = \xx - \aa_i$. The Stokeslet is torque-free
-and has force $\FF_i$ while the rotlet is force-free and has torque
+respectively, where $\rr = \xx - \aa_i$. The Stokeslet~\eqref{eq:stokeslet}  is torque-free
+and has force $\FF_i$ while the rotlet~\eqref{eq:rotlet} is force-free and has torque
 $T_i$. Therefore, the velocity~\eqref{eq:velocity} satisfies the total
@@
 double-layer potential $\DD[\eeta]$ is force- and torque-free.  Matching
-the limit of~\eqref{eq:velocity} with the rigid body motion, and
-imposing that $\DD[\eeta]$ is force- and torque-free, the density
-function $\eeta$, translational velocity $\vv_i$, and angular velocity
+the limit of~\eqref{eq:velocity} with the rigid body motion, 
+%and imposing that $\DD[\eeta]$ is force- and torque-free, 
+%
+the density function $\eeta$, translational velocity $\vv_i$, and angular velocity
 $\omega_i$ satisfy
@@
   \label{eq:mobility1}
-  \int_{\Gamma_i} \eeta \cdot \nnu \, \dif s &= {\bf 0}, 
+  \int_{\Gamma_i} \eeta \cdot \nnu \, \dif s &= 0, 
   &&i = 1,\ldots,N_b, \\
@@
 
-We have validated our solver for~\eqref{eq:SKIE}--\eqref{eq:mobility2}
+We validated our solver for~\eqref{eq:SKIE}--\eqref{eq:mobility2}
 using a single elliptical particle suspended in a background shear flow
@@
 angle of the ellipse's major axis coming from the integral equation
-method agrees with the theoretical, Jeffery orbit time-course
+method agreed with the theoretical, Jeffery orbit time-course
 (\cite{jef1922}).
@@
   \JJ_{i} = 2\gamma\rho^{-1} \sigma w_i \nnu + 
-    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{ds} \nnu -
-    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{d\nnu} \ttau.
+    2\gamma\rho \frac{\dif \sigma}{\dif s} \frac{\dif w_i}{\dif s} \nnu -
+    2\gamma\rho \frac{\dif \sigma}{\dif s} \frac{\dif w_i}{\dif \nnu} \ttau.
 \end{align}
 \end{theorem}
-The symbols $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc
+The symbols $\ttau$ and $\frac{\dif }{\dif s}$ are the unit tangent and arc
 length derivative for $\Gamma_i$, respectively (Figure
@@
 using~\eqref{eq:hydrophobicAttraction} is that the components $\sigma$,
-$w_i$, $\frac{d\sigma}{ds}$, and $\frac{dw_i}{ds}$ of $\JJ_i$ are smooth
+$w_i$, $\frac{\dif \sigma}{\dif s}$, and $\frac{\dif w_i}{\dif s}$ of $\JJ_i$ are smooth
 functions, whereas the components of \eqref{eq:stress} are singular
@@
 \end{align}
-By~\eqref{eq:uidef} and~\eqref{eq:decompdivfree}, we have that $u_i$ is
+By~\eqref{eq:uidef} and~\eqref{eq:decompdivfree}, we have that $\eta_i$ is
 smooth and $\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n
 \setminus U_i$. Similarly, $w_i = \eta  - \eta _i$ is smooth and $\nabla \cdot
-{\bf T}_3 = \mathbf{0}$ in $U_i$. By the divergence theorem,  
+{\bf T}_3 = \mathbf{0}$ in $\overline{U}_i$. By the divergence theorem,  
 \begin{align}
@@
 \end{align}
-Finally, $u_i$ and $w_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
+Finally, $\eta_i$ and $w_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
 \begin{align}
@@
   &= \Big[\!\Big[ \left( 2\gamma\rho^{-1} \eta _i w_i \mathbf{I} + 2\gamma\rho \nabla \eta _i \cdot \nabla w_i \mathbf{I} 
-- 2\gamma\rho \nabla \eta _i  \nabla w_i^T - 2\gamma\rho \nabla w_i \nabla
-  \eta _i^T\right) \cdot \nnu \Big]\!\Big] \\
+- 2\gamma\rho \nabla \eta _i  \nabla w_i - 2\gamma\rho \nabla w_i \nabla
+  \eta _i\right) \cdot \nnu \Big]\!\Big] \\
 %  &= \jump{\left( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
@@
 %  u_i^T\right) \cdot \nnu}\\
-&= 2\gamma\rho^{-1} \sigma w_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dw_i }{ds} \nnu
-- 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dw_i }{d\nnu} \ttau = \JJ_i.
+&= 2\gamma\rho^{-1} \sigma w_i \nnu + 2\gamma\rho \frac{\dif \sigma }{\dif s}\frac{\dif w_i }{\dif s} \nnu
+- 2\gamma\rho \ \frac{\dif \sigma }{\dif s} \frac{\dif w_i }{\dif \nnu} \ttau = \JJ_i.
 \end{align*}
@@
 scheme updates the particle positions and orientations. By including the
-repulsion force~\eqref{eq:REPULforce}, particle collisions can be avoided by setting time step
-size $\Delta t\sim O(10^{-1})$.
+repulsion force~\eqref{eq:REPULforce}, particle collisions can be avoided by setting the time step
+sizes comparable to the characteristic time.
 %are avoided even when using a relatively larger time step than $\Delta t\sim O(10^{-1})$ ns.
@@
   In panel (b), the JP suspension rotates and deforms with the shear flow.
-  The color map is for the solution $u$ of \eqref{eq:SL}. 
+  The color map is for the solution $\eta$ of \eqref{eq:SL}. 
   The white curves are the streamlines of $\uu.$ 
@@
 ns nm}^{-2}$ is viscosity of room-temperature water. 
-We select $M=4.0$~$\text{pN}$ and $\rho_0 = 0.2l_0$ so that \eqref{eq:REPULforce}
+We select $M=2.0$~$\text{pN}$ and $\rho_0 = 0.2l_0$ so that \eqref{eq:REPULforce}
   prevents particle collisions and is comparable to hydrodynamic lubrication.
   With a slight modification, the appendix of
-  \citep{cawthorn_balmforth_2010} provides the asymptotic expression 
+  \cite{cawthorn_balmforth_2010} provides the asymptotic expression 
   $F_{\text{lubr}} = -\tfrac{3}{2}\pi \mu \dot \epsilon (c/\epsilon)^{3/2}$
@@
 structure (\cite{Finken08}). Here, $A$ is the enclosed area and $L$ is
-the total length of the JP vesicle (Figure \ref{fig:figure0}a).
+the total length of the JP vesicle (Figure \ref{fig:figure0}c).
 Figure~\ref{figure4} shows the evolution of the area and length for
@@
 The JP vesicle achieves a steady-state reduced area earlier when the
-shear rate is low (inset), but the decay rate $k_2$ is more or less
-constant for higher shearer rates.
+shear rate is low, but the decay rate $k_2$ is more or less
+constant for higher shearer rates (inset).
 
@@
 ones used in prior MD studies (\cite{Brandner2019}) and are a
-consequence of the fact that larger shear rates are required to produce
-the viscous stresses needed to appreciably deform smaller vesicles.
+consequence of the fact that large shear rates are required to produce
+the viscous stresses needed to appreciably deform small vesicles.
 
@@
 friction of the aqueous gaps between particles and by the constant
-unbinding and binding of particles pairs in apposing leaflets.
+unbinding and binding of particle pairs in apposing leaflets.
 
@@
 midplane $C_M$ (Figure~\ref{figure5}a), and $U$ is the slip velocity.
-The time average $\langle \cdot \rangle$ is necessary to avoid division by zero
-whenever slip velocity vanishes.
+The time average $\langle \cdot \rangle$ is taken over the intervals where $U$ lies in the 
+tenth percentile of positive slip velocities.
+
+%necessary to avoid division by zero whenever slip velocity vanishes.
 
@@
   \\
-  radius ($l_0$) &  $\rho$ ($l_0$) & $\rho_0(l_0)$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  & Average\\
+  $c$ ($l_0$) &  $\rho$ ($l_0$) & $\rho_0(l_0)$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  & Average\\
 \cline{4-10}\\
@@
   \ttau \cdot \sigma \cdot \nnu \,\dif s - \int_{\mathcal{C}_M^-} 
- \ttau \cdot \sigma \cdot \nnu \,\dif s 
+ \ttau \cdot \sigma \cdot \nnu \,\dif s,
 \end{align}
@@
   that relates hydrophobic attraction to the dimensional critical shear rate $\dot \gamma_* = \chi_* \text{ ns}^{-1}$.
-  Assuming a characteristic velocity $L\dot \gamma$, the number $K$ relates to the vesicle's capillary number
-  $\text{Ca} = K c^2/(\rho L)$. Based on the above data, $\text{Ca}$ would be approximately $1.7$
+  Assuming a characteristic velocity $L\dot \gamma_*$, the number $K$ relates to the vesicle's capillary number
+  $\text{Ca} = K c^2/(\rho L)$. Based on the above data, $\text{Ca}$ would be approximately $1.8$
   so that surface forces are comparable to viscous forces.  
@@
   \]
-  which yields $K_B \approx 60$ pN $\text{nm}^{-1}$, which is a reasonable
-  value for the bending modulus of a lipid bilayer, for example \citep{NaTr00}.
+  which yields $K_B \approx 100$ pN $\text{nm}$, which is a large
+  value for the bending modulus of a reasonable lipid bilayer given the many assumptions and approximations \citep{NaTr00}.
 
@@
 %
-where $v_{max}$ is the flow strength and $w$ determines the shape of the
-flow. The parameter $R_0$ is the radius of the JP vesicle at $t=0$ and
+where $v_{max}$ is the flow strength. 
+%and $w$ determines the shape of the flow. 
+The parameter $R_0$ is the radius of the JP vesicle at $t=0$ and
 $w$ sets the width of the profile. \cite{Kaoui09, cou-kao-pod-mis2008,
@@
 The horizontal dashed line represents time in units of
-    $\upmu$s and the vertical axis represents the scaled $y$ position
+    $\upmu$s and the vertical axis represents the scaled $y$-position
     of the centroid of the JP vesicle.
@@
   from left to right. The parameters are $v_{max} = 8$~nm ns$^{-1}$,
-  $w=10$, and $R_0=20$ nm.}
+  $w=10$, and $R_0=17$ nm.}
 \end{figure}
@@
 In membrane continuum  mechanics, changes in membrane surface area $A$ give rise to a tension
-$\tilde \sigma = K_A(A/A_0 - 1)$ where $A_0$ is the reference surface area \cite{NaTr00}. 
+$\tilde \sigma = K_A(A/A_0 - 1)$ where $A_0$ is the reference surface area \citep{NaTr00}. 
 For a two-dimensional membrane, the tension is 
@@
   \label{eq:perm} 
-  \frac{dA}{dt} = - P\Delta p,
+  \frac{\dif A}{\dif t} = - P\Delta p,
 \end{align}
@@
 
-Our  simulation setup consists of an initial, non-equilibrium JP
+Our  simulation setup consists of an initial, non-equilibrium JP vesicle
 obtained by dilating the equilibrium shape outward (Figures~\ref{figure2part1}a).
@@
 The value also reasonably agrees with stretching moduli for 
-lipid bilayers, around $240$ pN nm$^{-1}$ \cite{NaTr00}.
+lipid bilayers, around $240$ pN nm$^{-1}$ \citep{NaTr00}.
 
@@
 To evaluate the rate of water outflow, 
-Figure~\ref{figure2part1}d plots the the simulation values for $dA/dt$.  
+Figure~\ref{figure2part1}d plots the the simulation values for $\dif A/\dif t$.  
 These values are proportional to $L\Delta p$ and like for the stretching modulus, 
@@
 independent of vesicle size.
-The  linear fits give a hydraulic permeability $P = 0.0290 \pm 0.007$ nm$^3$ ns$^{-1}$ pN$^{-1}$.
+The  linear fits give a hydraulic permeability with $P = 0.0290 \pm 0.007$ nm$^3$ ns$^{-1}$ pN$^{-1}$.
 We can combine~\eqref{eq:stretch},~\eqref{eq:LaplacePressure},
@@
 \begin{tabular}{ c |c| c |c }
- $k$ & $\lambda$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
+ $k$ & $\lambda$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$ pN$^{-1}$) \\
 \hline    
@@
 The baseline setup is shown in the first row.
-The next two rows demonstrate the results when the tension related parameters $\gamma$ and $M$ are increased by 5$\%$ and 10$\%$. 
+The next two rows demonstrate the results when the force parameters $\gamma$ and $M$ are increased by 5$\%$ and 10$\%$. 
 The parameter $k$ is used to scale the force paramaters $\gamma, M \to k\gamma, kM$.
-The final two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$
+The final two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$.
 The parameter $\lambda$ is used to simultaneously scale length parameters;
 $\rho, \rho_0, c \to \lambda \rho, \lambda \rho_0, \lambda c$.
-This data comes from Figure \ref{figure2} which  plots the \emph{ratio} of the abscissa and ordinates
+The data comes from Figure \ref{figure2} which  plots the \emph{ratio} of the abscissa and ordinates
 used in Figure \ref{figure2part1}c, d. The transformed data are fit by constant functions.
@@
 \label{eq:baseline_energy}
-G = \gamma \int_{\Omega} \rho |\nabla \eta |^2 + \rho^{-1} \eta ^2 \,\dif\xx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
-       P(|\tilde{\xx}_i - \tilde{\xx}_j|).
+G = \gamma \int_{\Omega} \rho |\nabla \eta |^2 + \rho^{-1} \eta ^2 \,\dif\xx,\quad H = \frac{M}{\rho_0} \sum_{i=1}^{N_b}\sum_{j \neq i} 
+       P\left(\frac{|\tilde{\xx}_i - \tilde{\xx}_j|}{\rho_0}\right).
 \end{equation}
@@
   centroids are plotted in blue and red. The centroids are initially
-  located on the $x$-axis. The fluid velocity streamlines appear in
-  grey.  The dimensionless shear rate is $\chi=0.005$.}
+  located on the $x$-axis. The fluid velocity streamlines are for the dimensionless shear rate $\chi=0.005$.}
 \end{figure}
@@
   $1.25$~nm above the $x$-axis and the centroid of the right JP vesicle
-  is $1.25$~nm below the $x$-axis. The streamlines appear in grey and
-  the flow rate is $\dot \gamma =0.005$~ns$^{-1}$ in all cases.
+  is $1.25$~nm below the $x$-axis. The streamlines are for
+  the flow rate $\dot \gamma =0.005$~ns$^{-1}$ in all cases.
 	  }
@@
 \begin{equation}
-\uu_{\infty}(\xx) = \dot \gamma ((\mathbf{e}_x \cdot \xx)\mathbf{e}_x - (\mathbf{e}_y \cdot \xx)\mathbf{e}_y)
+\uu_{\infty}(\xx) = \dot \gamma (-(\mathbf{e}_x \cdot \xx)\mathbf{e}_x + (\mathbf{e}_y \cdot \xx)\mathbf{e}_y)
 \end{equation}
@@
 continuum vesicles under an extensional flow. In both the coarse-grained
-model and the continuum model, the vesicles initially converge towards
+model and the continuum model, the vesicles initially approach
 one other and then diverge along the $y$-axis. The behaviour of the
@@
   The value $d_{1,2}$ is the distance between two centroids of JP vesicles. The thin curves plot the trajectories
-  of $d_{1,2}$ generated by the continuum model and the thick curves are computed from using
+  of $d_{1,2}$ generated by the continuum model and the thick curves are computed using
   the proposed HAP model.}
@@
 
-Since the behavior of the suspended JP vesicles has similarities to the numerical 
+The behavior of the suspended JP vesicles has similarities to the numerical 
 results generated by using the algorithm adopted in \cite{qua-vee-you2019} (refer to all figure
@@
 shear flow and extensional flow cases in two vesicle simulations. The quantity $d_{1,2}$
-represents the distance between two centroids of JP vesicles. The centroid positions are 
+represents the distance between two centroids of JP vesicles. The initial centroid positions are 
 identical for both models and the geometry in the continuum model is created along the 
@@
 incompressible fluid at the zero-Reynolds-number limit. Numerical
-simulations of a JP suspensions revealed self-assembly of JP into
+simulations of a JP suspension revealed self-assembly of JP into
 micelles and bilayers, providing an alternative means for computing
@@
 The results showed that the reduced area $A^*$ decreases with shear rate
-but that the total length of a JP vesicle is conserved. The decay rate
-of the reduced area was independent of the shear rate values between
-$0.003$~ns$^{-1}$ and~$0.005$~ns$^{-1}$. Moreover, the proposed model
+but that the total length is conserved. The decay rate
+of the reduced area was independent of the shear rate values. Moreover, the proposed model
 describes membrane rupture in high shear rates. Therefore, our method
@@
 the JP vesicle has a larger length scale than molecular dynamics
-simulations, and in the future convergence studies we will investigate
+simulations, and future convergence studies will investigate
 how physical properties like the friction coefficient and membrane
@@
 %
-Replicating the hydrodynamics of a GUV in a Poiseuille
+Replicating the hydrodynamics of a giant unilamellar vesicle in a Poiseuille
 flow~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}), the JP
@@
 %simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). 
-An interesting result contrast with continuum results is that the JP
+An interesting contrast with continuum results is that the JP
 vesicle oscillates at a height slightly above the centre of the
@@
 expected when the two centroids are initialized on the same horizontal
-level. We also observe a rotating behaviour that is observed for models
+level. We also observe a rotating behaviour that is present in models
 involving vesicle adhesion~(\cite{qua-vee-you2019}). The hydrophobic
@@
 The JP vesicle is permeable and the mixture of two different
-fluids requires an introduce of a contact line between
+fluids requires the introduction of a contact line between
 the two phases.
@@
 algorithmic implementation including a fast summation method such as the
-fast multipole method. Oother research directions include
+fast multipole method. Other research directions include
 fluctuating hydrodynamics for Brownian suspensions~(\cite{Bao2018}),

### 2022-03-27 doc/JFM2022/Final/main_jfm.tex
figure color and text mods

@@
   the mobility problem. The color map in panels (b)--(e) is the solution 
-  $\eta$ of \eqref{eq:SL}. Red is for $\eta  = 1$ and blue is for $\eta  = 0$.
+  $\eta$ of \eqref{eq:SL}. Magenta is for $\eta  = 1$ and turquoise is for $\eta  = 0$.
   Particles self-assemble into vesicle bilayers (panel (b)) and
@@
   vesicle tank-treading motion at all shear rates. Panel (a) tracks a
-  pair of particles (blue and yellow). The shear rate is $\chi=0.005$
-  and in the right figure, the yellow particle will complete two and a
-  quarter revolutions in the same time the blue particle completes two
+  pair of particles (filled circles). The shear rate is $\chi=0.005$
+  and in the right figure, the particle in the outer monolayer will complete two and a
+  quarter revolutions in the same time the particle in the inner monolayer completes two
   revolutions. The curves in panel (b) are the distance the outer
@@
 and exposes the hydrophobic core to bulk water (Figure~\ref{figure3},
-red region). In response, hydrophobic
+magenta region). In response, hydrophobic
 attraction~\eqref{eq:hydrophobicAttraction} causes the particles to
@@
 Figure~\ref{figure5}a illustrates inter-monolayer slip by tracking the distances
-traveled by a pair of particles along the midplane curve. In the left image, the blue and yellow
-particle lie next to each other. In the right-most panel, the yellow
-particle has traveled farther than the blue particle. This suggests that
+traveled by a pair of particles along the midplane curve. In the left image,
+two particles indicated by filled circles lie next to each other. In the right-most panel, the
+particle in the outer monolayer has traveled farther than the
+particle in the inner monolayer. This suggests that
 the outer tangential velocity, obtained by projecting the velocity of the
@@
   \]
-  which yields $K_B \approx 100$ pN $\text{nm}$, which is a large
-  value for the bending modulus of a reasonable lipid bilayer given the many assumptions and approximations \citep{NaTr00}.
+  which yields $K_B \approx 100$ pN $\text{nm}$.
+  Albeit somewhat large, the resulting bending modulus is
+  reasonable considering the assumptions made.
 
@@
 where the centroid of the JP vesicle is initially placed slightly above
-the $x$-axis. We have marked a pair of particles blue and yellow in the
+the $x$-axis. We have marked a pair of particles (filled circles) in the
 inner and outer leaflets, respectively, and observe that the deformed JP
@@
 The open circles and diamonds are for $\gamma$ and $M$ increased by 5$\%$ and 10$\%$, respectively. 
-The x's and stars are for particle radius, $\rho$, and $\rho_0$ decreased by 5$\%$ and 10$\%$, respectively.
+The exes and stars are for particle radius, $\rho$, and $\rho_0$ decreased by 5$\%$ and 10$\%$, respectively.
 The variable $x$ is used to denote the horizontal axis coordinate. 

### 2022-03-27 doc/JFM2022/Final/main_jfm.tex
updates

@@
 \usepackage{todonotes}
-
+\usepackage{orcidlink}
 %
@@
 \newcommand{\ReviewerThree}[1]{\textcolor{magenta}{#1}}
+\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\textcolor[HTML]{A6CE39}{\aiOrcid}}}
 
@@
 physical boundary conditions for the HAP model will allow us to draw
-comparisons between computational and laboratory experiments.
-
-\begin{acknowledgments}
-  {\bf Acknowledgments:} B.Q.~acknowledges support from NSF (Grant
+comparisons between computational and laboratory experiments.\\
+
+%\begin{acknowledgments}
+\noindent
+  {\bf Funding.} B.Q.~acknowledges support from NSF (Grant
   No.~DMS 2012560) and from the Simons Foundation, Mathematics and
   Physical Sciences-Collaboration Grants for Mathematicians (Award
-  No.~527139). Y.-N. Y.~acknowledges support from NSF (Grant No.~DMS 1614863 and 1951600) and
-  Flatiron Institute, part of Simons Foundation.
+  No.~527139). Y.-N. Y.~acknowledges support from NSF (Grant No.~DMS 1614863 and 1951600) and Flatiron Institute, part of Simons Foundation.\\
+
+  \noindent
+  {\bf Declaration of interests.} The authors report no conflict of interest.\\
+
+  \urlstyle{rm}
+
+\noindent
+{\bf Author ORCIDs.}\\
+\orcidlink{0000-0003-0140-1909} Szu-Pei Fu  {\url{https://orcid.org/0000-0003-0140-1909}}\\
+\orcidlink{0000-0002-9186-8926} Bryan Quaife {\url{https://orcid.org/0000-0002-9186-8926}}\\  
+\orcidlink{0000-0003-1626-7052} Rolf Ryham {\url{https://orcid.org/0000-0003-1626-7052}}\\  
+\orcidlink{0000-0001-9771-5480} Yuan-Nan Young  {\url{https://orcid.org/0000-0001-9771-5480 }}
+
 %We would like to acknowledge 
-\end{acknowledgments}
+%\end{acknowledgments}
 

### 2022-03-28 doc/JFM2022/Final/Supplementary.tex
updates

@@
 All dark blue dots in the domain are tracers that move with the calculated fluid motion.
-This movie includes a total 5000 time steps. \\
+This movie includes the simulation results for 1 $\mu$s.\\ %a total 5000 time steps. \\
 
@@
 The colored field from dark blue to dark red shows the hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain are tracers in fluid that move with the fluid motion.
-This movie includes a total 20000 time steps. \\
+This movie includes the simulation results for 4 $\mu$s.\\ %a total 20000 time steps. \\
 
@@
 the yellow particle in the outer leaflet surpasses the blue particle in the inner leaflet by the distance about 1 particle diameter.
-This movie includes a total 20000 time steps.\\
+This movie includes the simulation results for 4 $\mu$s.\\ %a total 20000 time steps.\\
 
@@
 All white dots in the domain are tracers in fluid that move with the fluid motion.
-This movie includes a total 3000 time steps.\\
+This movie includes the simulation results for 0.6 $\mu$s.\\ %a total 3000 time steps.\\
 
@@
 All white dots in the domain are tracers in fluid that move with the fluid motion.
-This movie includes a total 20000 time steps.\\
+This movie includes the simulation results for 4 $\mu$s.\\ %a total 20000 time steps.\\
 
@@
 All white dots in the domain are tracers in fluid that move with the fluid motion.
-This movie includes a total 6000 time steps.
+This movie includes the simulation results for 1.2 $\mu$s.\\ %a total 6000 time steps.
 %%%\end{document}

### 2022-03-30 doc/JFM2022/Final/main_jfm.tex
4.11 corrected
updates
3.8, 3.9 updated
\cdot
updated orcid link

@@
 Rolf Ryham\aff{1}, \and
-Yuan-Nan Young\aff{3}
+Y.-N. Young\aff{3}
 }
@@
 \label{eq:stokeslet}
-  \SS(\xx,\aa_i) \cdot \FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
+  \SS(\xx,\aa_i) \cdot \FF_i &= \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + 
     \frac{\rr \otimes \rr}{|\rr|^2}\right) \cdot \FF_i, \\
@@
   \label{eq:mobility1}
-  \int_{\Gamma_i} \eeta \cdot \nnu \, \dif s &= 0, 
+  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, 
   &&i = 1,\ldots,N_b, \\
   \label{eq:mobility2}
-  \int_{\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu \, \dif s &= 0,
+  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s &= T_i,
   &&i = 1,\ldots,N_b.
@@
 \label{eq:baseline_energy}
-G = \gamma \int_{\Omega} \rho |\nabla \eta |^2 + \rho^{-1} \eta ^2 \,\dif\xx,\quad H = \frac{M}{\rho_0} \sum_{i=1}^{N_b}\sum_{j \neq i} 
+G = \gamma \int_{\Omega} \rho |\nabla \eta |^2 + \rho^{-1} \eta ^2 \,\dif\xx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
        P\left(\frac{|\tilde{\xx}_i - \tilde{\xx}_j|}{\rho_0}\right).
@@
 \orcidlink{0000-0003-1626-7052} Rolf Ryham {\url{https://orcid.org/0000-0003-1626-7052}}\\  
-\orcidlink{0000-0001-9771-5480} Yuan-Nan Young  {\url{https://orcid.org/0000-0001-9771-5480 }}
+\orcidlink{0000-0001-9771-5480} Yuan-Nan Young  {\url{https://orcid.org/0000-0001-9771-5480}}
 

### 2022-04-11 doc/PRF2022/PRF_main.tex
updates

@@
 %\bibliographystyle{apsrev4-2}
+
+\usepackage{graphicx}
+%\usepackage{epstopdf,epsfig}
+\usepackage{newtxtext}
+\usepackage{newtxmath}
+\usepackage{natbib}
+\usepackage{hyperref}
+\usepackage{mathtools}
+\usepackage{commath}
+
+\newtheorem{lemma}{Lemma}
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}
+\newcommand{\RomanNumeralCaps}[1]
+\linenumbers
+
+% Bryan's Marcros
+\renewcommand{\aa}{\mathbf{a}}
+\newcommand{\bd}{\partial}
+\newcommand{\dd}{\mathbf{d}}
+\newcommand{\DD}{\mathcal{D}}
+\newcommand{\eeta}{\boldsymbol{\eta}}
+\newcommand{\FF}{\mathbf{F}}
+\newcommand{\GG}{\mathbf{G}}
+\newcommand{\JJ}{\mathbf{J}}
+\newcommand{\nnu}{\boldsymbol{\nu}}
+\newcommand{\ttau}{\boldsymbol{\tau}}
+\newcommand{\ssigma}{\boldsymbol{\sigma}}
+\newcommand{\rr}{\mathbf{r}}
+\newcommand{\RR}{\mathbf{R}}
+\renewcommand{\SS}{\mathbf{S}}
+\newcommand{\xx}{\mathbf{x}}
+\newcommand{\XX}{\mathbf{X}}
+\newcommand{\uu}{\mathbf{u}}
+\renewcommand{\vv}{\mathbf{v}}
+\newcommand{\yy}{\mathbf{y}}
+\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
+\newcommand{\jump}[1]{[\![ #1 ]\!]}
 
@@
  \affiliation{Department of Scientific Computing, Florida State University, Tallahassee, Florida 32306, USA}
- \author{Yuan-Nan Young}
+ \author{Y.-N. Young}
  \email{yyoung@njit.edu}
@@
 %\section{\label{}}
+
 \subsection{}
+
 \subsubsection{}
@@
 
+\subsection{Screened Laplace Mobility Problem}
+
+The mathematical formulation is a nonlinear system for the dynamics of a
+collection of particles. The interactions come from a system of 
+partial differential equations (PDEs) that comprise hydrodynamic
+interactions and hydrophobic interactions.
+The hydrodynamic interactions come from the mobility problem for rigid
+particles immersed in a viscous solvent. We then use a
+second-order Adams-Bashforth method to update the particle configuration.
+Assuming inertial terms are
+negligible, the particle motion is goverened by the Stokes equations
+\begin{alignat}{3}
+\label{eq:stokes}
+  -\mu \Delta \uu + \nabla p &= \mathbf{0},     && \xx \in \Omega, \\
+  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
+  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
+\end{alignat}
+where $\uu$ is the velocity and $p$ is the pressure of the solvent,
+$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
+viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
+particles and changes shape as the particles move.
+Since the particles are rigid, the solvent velocity satisfies
+a no-slip boundary condition for a rigid body motion 
+on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
+and angular velocity $\omega_i$.
+Given imposed forces acting on each
+particle, the \emph{mobility problem} consists of finding
+translational and angular velocities so that viscous fluid forces
+balance the imposed forces.
+
+The hydrophobic interactions come from the tendency of particles to
+minimize the free energy of the structure of the surrounding water
+molecules. The free energy functional takes the form 
+\begin{equation}
+\label{eq:free_energy}
+  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
+  \,d\xx,
+\end{equation}
+where $u$ is an order parameter for the structure of water, $\rho$ is a
+decay length, $C$ is a constant, and $f(u)$ is a potential.
+Hydrogen-bond persistence times are on the order of picoseconds
+which is much smaller than characteristic time for 
+particle motion.% \cite{MaGa13}.
+Thus we assume $u$ minimizes $F[u]$ for all times.
+Assuming appropriate conditions on $f(u)$,% (\cite{evans10}, \S 8.2),
+$u$ is bounded and satisfies the Euler-Lagrange equation
+\begin{equation}
+\label{eq:SL}
+-\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
+\text{ on } \bd\Omega.
+\end{equation}
+The boundary condition $g$ is a material label that is transported with
+the particle (Figure~\ref{fig:bcs}).
+
+The particles lower the free energy $F[u]$ of the surrounding water
+by moving. We calculate the rate of change of $F[u]$ using
+\emph{variation of the domain}% ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
+Carrying out this variation yields a stress  
+\begin{align}
+  \label{eq:stress}
+\mathbf{T}
+= C \left[ \rho^{-1} f(u) \mathbf{I}
+  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
+\end{align}
+The imposed forces and torques come from the integration of $\mathbf{T}$
+along the particle boundary.
+These forces and torques couple the Stokes equations \eqref{eq:stokes},
+to semilinear elliptic equation \eqref{eq:SL}.
+Solving for the translational and rotational velocities gives the
+particle evolution.
+
+\begin{align}
+  \label{eq:velocity}
+  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
+    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
+    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
+\end{align}
+
+\begin{alignat}{3}
+  \nonumber
+  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
+    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
+  \label{eq:SKIE}
+    + \sum_{j=1}^{N_b} &
+    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),
+    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
+  \label{eq:mobility1}
+  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, 
+  &&i = 1,\ldots,N_b, \\
+  \label{eq:mobility2}
+  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s &= T_i,
+  &&i = 1,\ldots,N_b.
+\end{alignat}
+
+\subsection{Energy Calculation via Singularity Subtraction}
+
+Suppose we split the solution to the screened Laplace boundary value problem~\eqref{eq:stokes}
+into smooth portion $w_i$ and singular portion $u_i$. That is, $u = w_i + u_i$.
+Consider the case when $f(u)=u^2$ in~\eqref{eq:free_energy}, we can rewrite the free energy functional as
+
+\begin{align}
+\label{eq:free_energy2}
+  E[u(\xx)] &= C\rho \sum_{i=1}^{N_b}\int_{\Gamma_i} u \frac{\partial u}{\partial \nnu}  \,\dif s
+= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} g \left(\frac{\partial w_i}{\partial \nnu}+\frac{\partial u_i}{\partial \nnu} \right) \, \dif s, \quad \xx\in\Gamma_i.
+\end{align}
 %%%
+Follow the divergence theorem on the last term in the equation above and denote $g_i(x)$ as the boundary data on $\Gamma_i$, we obtain
+\begin{align}
+\label{eq:free_energy3}
+  E[u(\xx)] &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} g \frac{\partial w_i}{\partial \nnu} \,\dif s 
+  + \int_{U_i}\nabla g_i \nabla u_i + g_i (u_i+\frac12\sigma) \,\dif \xx\right)\\
+  &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} g_i \frac{\partial w_i}{\partial \nnu} 
+ + u_i \frac{\partial g_i}{\partial \nnu} \,\dif s - \int_{U_i}\Delta g_i u_i - g_i (u_i+\frac12\sigma) \,\dif \xx\right) \\
+ &= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} g \frac{\partial w_i}{\partial \nnu}+ (u_i+\frac12\sigma)  \frac{\partial g_i}{\partial \nnu}\,\dif s, \quad \xx\in\Gamma_i.
+\end{align}
+%
+$\sigma$ satisfies the second-kind integral equation
+\begin{equation}
+\label{eq:screenedSKIE}
+  g(\xx) = \frac{1}{2}\sigma(\xx) + 
+    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
+    \dif s_\yy, \quad \xx \in \bd\Omega,
+\end{equation}
 
@@
 
+\subsection{Self-Assembled Janus Particle with Specific Boundary Conditions}
+
+Distinct morphologies can be obtained from 
+the HAP model by shifting the boundary condition $g(\xx)$.
+Consider the linear case where $f(u) = u^2$.
+This choice makes \eqref{eq:SL} a boundary value
+problem for the screened-Laplace equation
+and the solutions have a boundary layer structure that decays to $0$ in the
+bulk with the decay length $\rho$.
+We consider three kinds of boundary conditions
+on particle $\Gamma_i$:
+\begin{equation}
+  \label{eq:bcs}
+  \begin{tabular}{c|c|c}
+     \text{(a)} & \text{(b)} & \text{(c)} \\
+    \hline
+    \rule{0pt}{4ex} 
+      $g(\mathbf{x}) = \displaystyle \frac{1+\cos (\theta_i(\xx))}{\sqrt{3\pi r}}$
+    & $g(\mathbf{x}) = \displaystyle \frac{2+\cos (\theta_i(\xx))}{\sqrt{9\pi r}}$
+    & $g(\mathbf{x}) = \displaystyle \frac{\cos (\theta_i(\xx))}{\sqrt{\pi r}}$
+\end{tabular}
+\end{equation}
+  The number $\theta_i(\xx)$ is the angle formed by the position $\xx$, the
+particle center $\aa_i$, and the particle director $\dd_i$.% (Figure \ref{fig:flow_map}).
+The normalizations e.g., $(\pi r)^{-1/2}$, provide a uniform
+surface energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles
+of radius $r$. 
+The cases (b) and (c) are obtained by applying a vertical shift
+and scaling to case (a), see Figure \ref{fig:bcs}.
+Using this setup, we simulate the dynamics of 100 particles with random
+initial position and orientation.
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.2\textwidth]{LPA.jpg}
+  \includegraphics[width=0.2\textwidth]{LPB.jpg}
+  \includegraphics[width=0.2\textwidth]{LPC.jpg}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:bcs} Boundary conditions characterize the water
+    structure at the particle interface: an amphiphilic particle (left),
+    a hydrophobic
+  particle with anisotropic intensity (middle), a water structure with
+  positive/negative charge (right). The dashed curve is the boundary of the
+  disk and the arrow is its director for each particle.}
+\end{figure}
+Case (a) models amphiphilic particles.
+Amphiphilic particles have a hydrophobic tail and a hydrophilic head
+and these are accounted for as follows.
+The hydrophilic side takes the value $u =0$.
+This mimicks the apolar head of a lipid, for example, which does
+not alter the structure of adjacent waters. The hydrophobic side
+represents hydrocarbons and takes the value 
+$u > 0$. The interaction between particles is attractive,
+and particles will collectively orient their tails toward
+one another.
+
+Multilamelar bilayers arise when both sides of the particle
+are hydrophobic.
+The boundary condition \eqref{eq:bcs}(b) 
+gives a particle with a hydrophobic intensity that is greater
+on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
+The initial self-assembly is similar to that in case (a).
+The difference arises in the long-time dynamics where the bilayers
+no longer remain well-separated. 
+Rather, the bilayers form layers 
+as a consequence of the interfacial tension of exposed particle
+heads.%~\cite{Huetal19, deMeetal21}.
+
+Finally, boundary condition \eqref{eq:bcs}(c) models 
+a particle whose head surface repels the tail surface as proposed in
+\cite{MaRa76, Ma77}.
+The particles initially form chains with their directors perpendicular to the
+length of the chain. The equilibrium structure
+resembles a checkerboard pattern
+where each particle coordinates
+its head with the head of three other particles and its tail with the
+tail of three other particles. % Figure~\ref{fig:self-assembly}(c).
+
+\subsection{Collective Janus Particles Suspended in a Shear Flow}
 %%%
@@
 % If you have acknowledgments, this puts in the proper section head.
-%\begin{acknowledgments}
+\begin{acknowledgments}
+We thank Dr.
+S\'ebastien Michelin and Dr.
+Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.
+
 % put your acknowledgments here.
-%\end{acknowledgments}
+\end{acknowledgments}
 

### 2022-04-23 doc/PRF2022/PRF_main.tex
updated derivation

@@
 
-Suppose we split the solution to the screened Laplace boundary value problem~\eqref{eq:stokes}
-into smooth portion $w_i$ and singular portion $u_i$. That is, $u = w_i + u_i$.
+Suppose we split the solution to the screened Laplace boundary value problem~\eqref{eq:SL}
+into smooth portion $w_i$ and singular portion $u_i$. That is, 
+\begin{equation}
+w_i({\bf x}) = u({\bf x}) - u_i = u({\bf x}) - \int_{\Gamma_i }\left(\pderiv{}{\nnu_\yy}
+    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma_i(\yy) \,
+    \dif s_\yy \quad \xx \in \Gamma_i.
+\end{equation}
 Consider the case when $f(u)=u^2$ in~\eqref{eq:free_energy}, we can rewrite the free energy functional as
@@
   E[u(\xx)] &= C\rho \sum_{i=1}^{N_b}\int_{\Gamma_i} u \frac{\partial u}{\partial \nnu}  \,\dif s
-= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} g \left(\frac{\partial w_i}{\partial \nnu}+\frac{\partial u_i}{\partial \nnu} \right) \, \dif s, \quad \xx\in\Gamma_i.
+= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} u \left(\frac{\partial w_i}{\partial \nnu}+\frac{\partial u_i}{\partial \nnu} \right) \, \dif s, \quad \xx\in\Gamma_i.
 \end{align}
@@
 \label{eq:free_energy3}
-  E[u(\xx)] &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} g \frac{\partial w_i}{\partial \nnu} \,\dif s 
-  + \int_{U_i}\nabla g_i \nabla u_i + g_i (u_i+\frac12\sigma) \,\dif \xx\right)\\
-  &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} g_i \frac{\partial w_i}{\partial \nnu} 
- + u_i \frac{\partial g_i}{\partial \nnu} \,\dif s - \int_{U_i}\Delta g_i u_i - g_i (u_i+\frac12\sigma) \,\dif \xx\right) \\
- &= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} g \frac{\partial w_i}{\partial \nnu}+ (u_i+\frac12\sigma)  \frac{\partial g_i}{\partial \nnu}\,\dif s, \quad \xx\in\Gamma_i.
+  E[u(\xx)] &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} \left( \nabla u \cdot\nabla u_i + u\Delta u_i\right) \,\dif \xx\right)\\
+%
+&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} u\Delta u_i\,\dif \xx
++\int_{\Gamma_i}\left(u_i+\frac12\sigma_i\right)\frac{\partial u}{\partial \nnu} \,\dif s     
+- \int_{\mathbb{R}^n\setminus \overline{U}_i} u_i\Delta u\,\dif \xx \right)\\
+&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} + 
+\left(g_i+\frac12\sigma_i\right)\frac{\partial u}{\partial \nnu}   \,\dif s \right).
 \end{align}
-%
-$\sigma$ satisfies the second-kind integral equation
-\begin{equation}
-\label{eq:screenedSKIE}
-  g(\xx) = \frac{1}{2}\sigma(\xx) + 
-    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
-    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
-    \dif s_\yy, \quad \xx \in \bd\Omega,
-\end{equation}
+
+%  &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} g_i \frac{\partial w_i}{\partial \nnu} 
+% +  \left(u_i+\frac12\sigma\right)  \frac{\partial g_i}{\partial \nnu} \,\dif s - \int_{\mathbb{R}^n\setminus \overline{U}_i}\Delta g_i  \left(u_i+\frac12\sigma\right)  - g_i \left(u_i+\frac12\sigma\right) \,\dif \xx\right) \\
+% &= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} g_i \frac{\partial w_i}{\partial \nnu}+ \left(u_i+\frac12\sigma\right)  \frac{\partial g_i}{\partial \nnu}\,\dif s, \quad \xx\in\Gamma_i.
+
+%%
+%$\sigma$ satisfies the second-kind integral equation
+%\begin{equation}
+%\label{eq:screenedSKIE}
+%  g(\xx) = \frac{1}{2}\sigma(\xx) + 
+%    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
+%    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
+%    \dif s_\yy, \quad \xx \in \bd\Omega,
+%\end{equation}
 

### 2022-04-25 doc/PRF2022/PRF_main.tex
updated derivation
updates

@@
 Given imposed forces acting on each
-particle, the \emph{mobility problem} consists of finding
+particle, the mobility problem consists of finding
 translational and angular velocities so that viscous fluid forces
@@
 which is much smaller than characteristic time for 
-particle motion.% \cite{MaGa13}.
+particle motion. % \cite{MaGa13}.
 Thus we assume $u$ minimizes $F[u]$ for all times.
@@
 by moving. We calculate the rate of change of $F[u]$ using
-\emph{variation of the domain}% ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
+variation of the domain. % ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
 Carrying out this variation yields a stress  
@@
 \end{align}
+%
+where the density function $\eeta$, translation velocity $\vv_i$ and angular velocity $\omega_i$ satisfy
 
@@
     K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma_i(\yy) \,
-    \dif s_\yy \quad \xx \in \Gamma_i.
+    \dif s_\yy, \quad \xx \in \Gamma_i.
 \end{equation}
@@
 &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} + 
-\left(g_i+\frac12\sigma_i\right)\frac{\partial u}{\partial \nnu}   \,\dif s \right).
+\left(g_i+\frac12\sigma_i\right)\frac{\partial u}{\partial \nnu}   \,\dif s \right), \quad \xx \in \Gamma_i.
 \end{align}
@@
 and scaling to case (a), see Figure \ref{fig:bcs}.
-Using this setup, we simulate the dynamics of 100 particles with random
-initial position and orientation.
+Using this setup, we simulate the dynamics of 60 particles with random
+initial position and orientation as shown in Figure~\ref{fig:relax}.
 
@@
 \end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{Fig2a.png}
+  \includegraphics[width=0.4\textwidth]{Fig2b.png}\\
+  \includegraphics[width=0.4\textwidth]{Fig2c.png}
+  \includegraphics[width=0.4\textwidth]{Fig2d.png}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:relax} (a) Initial configuration; (b)--(d) Equilibruim states for all boundary conditions~\eqref{eq:bcs}(a)--(c), respectively.
+Colors represent the boundary values that increases from minimum (blue) to maximum (red).
+}
+\end{figure}
+
 Case (a) models amphiphilic particles.
@@
 and particles will collectively orient their tails toward
-one another.
+one another. Figure~\ref{fig:relax}(b) demonstrates multiple bilayer structures such as pancake and vesicle shapes.
 
@@
 heads.%~\cite{Huetal19, deMeetal21}. 
+Figure~\ref{fig:relax}(c) shows the multilamellar structure with 8 layers when $N_b=60$. 
+The number of folds depends on a number of factors, for instances, number of particles and intial configurations.
 
@@
 tail of three other particles. % Figure~\ref{fig:self-assembly}(c).
+Figure~\ref{fig:relax}(d) gives an example that this boundary condition results a checker board/stripes equilibrium state.
 
@@
 %%%
+
+Consider placing equilibrium states of cases (b) and (c) for 60 particles in a shear flow,
+\begin{equation}
+\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
+\end{equation}
+%
+where $\dot\gamma$ is the shear rate.
+
+\subsection{Collective Janus Particles Suspended in a Taylor-Green Flow}
+
+Similar to shear flow simulations, we then place equilibrium states of all boundary conditions \eqref{eq:bcs} in a rotating Taylor-Green Flow
+\begin{equation}
+\uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx)\sin({\bf e}_y\cdot\xx)){\bf e}_x+\sin({\bf e}_x\cdot\xx)\cos({\bf e}_y\cdot\xx)\right){\bf e}_y.
+\end{equation}
+%
+The magnitude of the vortex flow is controlled by the velocity scale $V_0$.
 

### 2022-05-06 code/src/capsules.m
new energy calculation

@@ -33,6 +33,7 @@ DLPStokes;    % double-layer potential matrix for Stokes
 % rank-one correction for Stokes to remove one dimensional null space
 N0Stokes;     
 DLPYukawa;    % double-layer potential matrix for Yukawa
+SLPYukawa;    % single-layer potential matrix for Yukawa
 upRate;       % upsampling rate that is used for NSI quadrature
 NPeaks;       % change the number of peaks in cosine bc
 % besselk(1,~) kernel for each target point with upsampled source points
@@ -582,6 +583,48 @@ end % relate == 2 || relate == 3
 
 end % getZone
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function E = computeEnergyNew(geom,eta)
+
+oc = curve;
+[x,y] = oc.getXY(geom.X);
+[tx,ty] = oc.getXY(geom.xt);
+nx = ty;
+ny = -tx;
+
+op = poten(geom.N,geom.rho);
+kernel = @op.exactYukawaSL;
+kernelDirect = @op.exactYukawaSL;
+kernelSelf = @(z) op.exactYukawaSLdiag(geom,geom.SLPYukawa,z);
+
+% Compute potential at target points
+pot1 = op.nearSingInt(geom,eta.*tx,kernelSelf,...
+    geom.nearStructB2B,kernel,kernelDirect,geom,true,false);
+pot1 = pot1(1:end/2,:);
+pot1 = pot1 + op.exactYukawaSLdiag(geom,geom.SLPYukawa,eta.*tx);
+
+pot2 = op.nearSingInt(geom,eta.*ty,kernelSelf,...
+    geom.nearStructB2B,kernel,kernelDirect,geom,true,false);
+pot2 = pot2(1:end/2,:);
+pot2 = pot2 + op.exactYukawaSLdiag(geom,geom.SLPYukawa,eta.*ty);
+
+IK = oc.modes(geom.N,1);
+deta = oc.diffFT(eta,IK)./geom.sa;
+pot3 = op.nearSingInt(geom,deta,kernelSelf,...
+    geom.nearStructB2B,kernel,kernelDirect,geom,true,false);
+pot3 = pot3(1:end/2,:);
+pot3 = pot3 + op.exactYukawaSLdiag(geom,geom.SLPYukawa,deta);
+dpot3 = oc.diffFT(pot3,IK)./geom.sa;
+
[…]

### 2022-05-06 code/src/fft1.m

@@ -7,6 +7,32 @@ properties
 N; % Number of points in the incoming periodic functions
 end
 
+methods
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function A = sinterpS(o,N,y)
+% A = sinterpS(N,y) constructs the interpolation matrix A that maps
+% a function defined periodically at N equispaced points to the
+% function value at the points y
+% The points y are assumed to be the in the 0-2*pi range.
+
+A = zeros(numel(y),N);
+modes = [(0:N/2-1) 0 (-N/2+1:-1)];
+f = zeros(1,N);
+
+for j=1:N
+  f(j) = 1;
+  fhat = fft(f)/N;
+  fhat = fhat(ones(numel(y),1),:);
+  A(:,j) = A(:,j) + sum(fhat.*exp(1i*y*modes),2);
+  f(j) = 0;
+end
+% Input is real, so interpolant should be real
+A = real(A);
+
+end % sinterpS
+
+end % methods
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 methods (Static)

### 2022-05-06 code/src/poten.m

@@ -385,6 +385,63 @@ N0 = normal.*normal'.*sa'*2*pi/geom.N;
 
 end % stokesN0matrix
 
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+function S = yukawaSLmatrix(o,geom)
+% S = yukawaSLmatrix(geom) generates single-layer potential for yukawa.
+% geom is a data structure defined as in the capsules class S is (N,N,n)
+% array where Np is the number of points per curve and n is the number
+% of curves in X 
+
+oc = curve;
+% Particle positions
+[x,y] = oc.getXY(geom.X);
+
+% quadrature weights and points
+[qw,qp] = o.quadratureS(8);
+Nquad = numel(qw);
+qw = qw(:,ones(o.N,1));
+% rotation matrices
+[Rfor,Rbac] = o.rotationIndicies;
+% number of quadrature points including the extra terms that Alpert's
+% rule brings into the quadrature
+
+S = zeros(o.N,o.N,geom.nb);
+for k = 1:geom.nb % loop over all Janus particles
+  % locations
+  xx = x(:,k);
+  yy = y(:,k);
+  % jacobian
+  sa = geom.sa(:,k)';
+
+  % put target points in matrix format for quick construction of SLP
+  % matrix
+  xtar = xx(:,ones(Nquad,1))';
+  ytar = yy(:,ones(Nquad,1))';
+
+  % put source points and Jacobian in matrix format for quick
+  % construction of SLP matrix
+  xsou = xx(:,ones(geom.N,1));
+  ysou = yy(:,ones(geom.N,1));
+  sa = sa(ones(geom.N,1),:);
+
+  % rotate source points appropriately for quadrature
+  xsou = xsou(Rfor);
+  ysou = ysou(Rfor);
+
+  diffx = xtar - qp*xsou;
+  diffy = ytar - qp*ysou;
+  dist = sqrt(diffx.^2 + diffy.^2);
+
+  G = 1/2/pi*qp'*(qw.*besselk(0,dist/geom.rho));
+  G = G(Rbac);
+  S(:,:,k) = G'.*sa;
+end
+
+
+end % yukawaSLmatrix
[…]

### 2022-05-06 code/src/rigid2D.m

@@ -207,10 +207,10 @@ while step <= prams.m
   % update step counter
   step = step + 1;
 
-  figure(2);
-  plot(Energy)
-  figure(1);
-  pause(0.01) 
+%  figure(2);
+%  plot(Energy)
+%  figure(1);
+%  pause(0.01) 
 end
 
 % save final time step

### 2022-05-06 code/src/tstep.m

@@ -91,7 +91,7 @@ if o.confined
   op2 = poten(Nwall,walls.rho);
   walls.DLPYukawa = op2.yukawaDLmatrix(walls); 
   o.precoYukawaWalls.L = zeros(Nwall,Nwall,nbwall);
-  o.precoYukawaWalls.U = zeros(Nwall,Nwall,nbwall);
+  o.precoYukawaWalls.U = zeros(Nwall,Nwall,nbjwall);
   for k = 1:nbwall
     [o.precoYukawaWalls.L(:,:,k),o.precoYukawaWalls.U(:,:,k)] = ...
       lu(0.5*eye(Nwall) + walls.DLPYukawa(:,:,k));
@@ -121,7 +121,36 @@ for k = 1:nbwall
   etaYukawaWalls(:,k) = sigma(nb*N + (k-1)*Nwall+1:nb*N + k*Nwall);
 end
 
-Energy = geom.computeEnergy(etaYukawaJanus);
+if 0
+  [xtar,ytar] = meshgrid(-7:1.01:+7,-7:1.01:7);
+  [nx,ny] = size(xtar);
+  targets.N = numel(xtar);
+  targets.nb = 1;
+  targets.X = [xtar(:);ytar(:)];
+  [~,NearJanusTargets] = geom.getZone(targets,2);
+
+  kernel = @op.exactYukawaSL;
+  kernelDirect = @op.exactYukawaSL;
+  kernelSelf = @(z) op.exactYukawaSLdiag(geom,...
+        S,z);
+
+  potJanus = op.nearSingInt(geom,etaYukawaJanus,kernelSelf,...
+    NearJanusTargets,kernel,kernelDirect,targets,false,false);
+  potJanus = potJanus(1:targets.N,:);
+end
+
+% Finite difference way of computing energy
+%Energy = geom.computeEnergy(etaYukawaJanus);
+
+% generate Yukawa single-layer potential matrix for
+% self-contribution of each individual Janus particle
+geom.SLPYukawa = op.yukawaSLmatrix(geom); 
+% Layer potential way of computing energy
+Energy = geom.computeEnergyNew(etaYukawaJanus);
+
+%[Energy Energy2]
+%abs(Energy - Energy2)/Energy2
+%pause
 
 if 0
   [xtar,ytar] = meshgrid(-9:0.01:-7,-1:0.01:1);
@@ -610,7 +639,7 @@ switch options.farField
[…]

### 2022-05-08 code/src/poten.m
updates

@@ -1727,6 +1727,7 @@ end
 % restore h value   
 geom.length = h_store;
 
+RE = RE/2;
 end % Repul
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-05-08 code/src/tstep.m

@@ -140,19 +140,19 @@ if 0
 end
 
 % Finite difference way of computing energy
-%Energy = geom.computeEnergy(etaYukawaJanus);
+% Energy2 = geom.computeEnergy(etaYukawaJanus) + RE;
 
 % generate Yukawa single-layer potential matrix for
 % self-contribution of each individual Janus particle
 geom.SLPYukawa = op.yukawaSLmatrix(geom); 
 % Layer potential way of computing energy
-Energy = geom.computeEnergyNew(etaYukawaJanus);
+Energy = geom.computeEnergyNew(etaYukawaJanus) + RE;
 
-%[Energy Energy2]
-%abs(Energy - Energy2)/Energy2
-%pause
+% [Energy Energy2]
+% abs(Energy - Energy2)/Energy2
+% pause
 
-%Energy = geom.computeEnergy(etaYukawaJanus) + RE;
+
 
 if 0
   [xtar,ytar] = meshgrid(-9:0.01:-7,-1:0.01:1);

### 2022-05-08 doc/PRF2022/PRF_main.tex
updates
updated manuscript

@@
 \newcommand{\DD}{\mathcal{D}}
+\newcommand{\SSS}{\mathcal{S}}
 \newcommand{\eeta}{\boldsymbol{\eta}}
@@
 \newcommand{\xx}{\mathbf{x}}
+\newcommand{\zz}{\mathbf{z}}
 \newcommand{\XX}{\mathbf{X}}
@@
 
-\subsection{Energy Calculation via Singularity Subtraction}
+\subsection{Normal Derivative of Double Layer Potential and HAP Energy}
 
-Suppose we split the solution to the screened Laplace boundary value problem~\eqref{eq:SL}
-into smooth portion $w_i$ and singular portion $u_i$. That is, 
-\begin{equation}
-w_i({\bf x}) = u({\bf x}) - u_i = u({\bf x}) - \int_{\Gamma_i }\left(\pderiv{}{\nnu_\yy}
-    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma_i(\yy) \,
-    \dif s_\yy, \quad \xx \in \Gamma_i.
-\end{equation}
-Consider the case when $f(u)=u^2$ in~\eqref{eq:free_energy}, we can rewrite the free energy functional as
+Suppose we use the double layer potential to express the solution of \eqref{eq:SL} where the condition is $f(u)=u^2$. Then it is given by 
+\begin{align}
+u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy,
+\end{align}
+%
+where $G(\xx)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL}.
+Since the free energy functional can be written as 
+\begin{align}
+\label{eq:free_energy2}
+  E[u(\xx)] &= C\rho \int_\Gamma u \frac{\partial u}{\partial \nnu}  \,\dif s, \quad \xx\in\Gamma_i,
+\end{align}
+%
+we can then use the following identity to calculate this boundary equation without evaluating 
+the normal derivative of the double layer potential directly.
 
 \begin{align}
-\label{eq:free_energy2}
-  E[u(\xx)] &= C\rho \sum_{i=1}^{N_b}\int_{\Gamma_i} u \frac{\partial u}{\partial \nnu}  \,\dif s
-= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} u \left(\frac{\partial w_i}{\partial \nnu}+\frac{\partial u_i}{\partial \nnu} \right) \, \dif s, \quad \xx\in\Gamma_i.
+\nnu_\xx \cdot \nabla_\zz u(\zz) &=\nnu_\xx \cdot \nabla_\zz \int_\Gamma \frac{\partial G(\zz-\yy)}{\partial \nnu_\yy}\sigma(\yy) \,\dif s_\yy\\
+&=\int_\Gamma \nnu_\xx\cdot \left(\nabla_\zz\nabla_\yy^\top  G(\zz-\yy)\right)\cdot \nnu_\yy\sigma(\yy)  \,\dif s_\yy\\
+&=-\int_\Gamma \nnu_\xx\cdot \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\cdot\nnu_\yy\sigma(\yy)\ \dif s_\yy\\
+&=-\int_\Gamma {\bf t}_\xx\cdot\Delta_\yy G(\zz-\yy) {\bf t}_\yy \sigma(\yy)\ \dif s_\yy+\int_\Gamma({\bf t}_\xx\cdot\nabla_\yy)({\bf t}_\yy\cdot\nabla_\yy G(\zz-\yy))\sigma(\yy)\ \dif s_\yy\\
+&= -\int_\Gamma {\bf t}_\xx\cdot\frac1\rho^2 G(\zz-\yy) {\bf t}_\yy \sigma(\yy)\ \dif s_\yy - 
+({\bf t}_\xx\cdot\nabla_\zz)\int_\Gamma \frac{\partial G(\zz-\yy)}{\partial s_\yy}\sigma(\yy)\ \dif s_\yy\\
+&= -\frac1\rho^2 {\bf t}_\xx\cdot \int_\Gamma G(\zz-\yy){\bf t}_\yy \sigma(\yy)\ \dif s_\yy + 
+({\bf t}_\xx \cdot \nabla_\zz)\int_\Gamma G(\zz-\yy)\frac{\partial \sigma(\yy)}{\partial s}\ \dif s_\yy.
 \end{align}
-%%%
-Follow the divergence theorem on the last term in the equation above and denote $g_i(x)$ as the boundary data on $\Gamma_i$, we obtain
-\begin{align}
-\label{eq:free_energy3}
-  E[u(\xx)] &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} \left( \nabla u \cdot\nabla u_i + u\Delta u_i\right) \,\dif \xx\right)\\
 %
-&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} u\Delta u_i\,\dif \xx
-+\int_{\Gamma_i}\left(u_i+\frac12\sigma_i\right)\frac{\partial u}{\partial \nnu} \,\dif s     
-- \int_{\mathbb{R}^n\setminus \overline{U}_i} u_i\Delta u\,\dif \xx \right)\\
-&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} + 
-\left(g_i+\frac12\sigma_i\right)\frac{\partial u}{\partial \nnu}   \,\dif s \right), \quad \xx \in \Gamma_i.
-\end{align}
+Here ${\bf t}_\xx$ is the tangent vector at the point $\xx$ and $d/ds$ is the arclength derivative.
+Letting $\zz\to\xx\in\Gamma$, we obtain
+%
+\begin{equation}
+\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) = -\frac1\rho^2 {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx) + \frac{\partial}{\partial s}\SSS\left[\frac{\partial \sigma}{\partial s}\right](\xx).
+\end{equation}
+%
+
+%Suppose we split the solution to the screened Laplace boundary value problem~\eqref{eq:SL}
+%into smooth portion $w_i$ and singular portion $u_i$. That is, 
+%\begin{equation}
+%w_i({\bf x}) = u({\bf x}) - u_i = u({\bf x}) - \int_{\Gamma_i }\left(\pderiv{}{\nnu_\yy}
+%    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma_i(\yy) \,
+%    \dif s_\yy, \quad \xx \in \Gamma_i.
+%\end{equation}
+%Consider the case when $f(u)=u^2$ in~\eqref{eq:free_energy}, we can rewrite the free energy functional as 
+%
+%\begin{align}
+%\label{eq:free_energy2}
+%  E[u(\xx)] &= C\rho \sum_{i=1}^{N_b}\int_{\Gamma_i} u \frac{\partial u}{\partial \nnu}  \,\dif s
+%= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} u \left(\frac{\partial w_i}{\partial \nnu}+\frac{\partial u_i}{\partial \nnu} \right) \, \dif s, \quad \xx\in\Gamma_i.
+%\end{align}
+%%%%
+%Follow the divergence theorem on the last term in the equation above and denote $g_i(x)$ as the boundary data on $\Gamma_i$, we obtain
+%\begin{align}
+%\label{eq:free_energy3}
+%  E[u(\xx)] &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} \left( \nabla u \cdot\nabla u_i + u\Delta u_i\right) \,\dif \xx\right)\\
+%%
+%&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} u\Delta u_i\,\dif \xx
+%+\int_{\Gamma_i}\left(u+\frac12\sigma\right)\frac{\partial u_i}{\partial \nnu} \,\dif s     
+%- \int_{\mathbb{R}^n\setminus \overline{U}_i} u\Delta u_i\,\dif \xx \right)\\
+%&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} + 
+%\left(g_i+\frac12\sigma_i\right)\frac{\partial u_i}{\partial \nnu}   \,\dif s \right), \quad \xx \in \Gamma_i.
+%\end{align}
+%
+%
+%
 
@@
 \begin{equation}
-\uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx)\sin({\bf e}_y\cdot\xx)){\bf e}_x+\sin({\bf e}_x\cdot\xx)\cos({\bf e}_y\cdot\xx)\right){\bf e}_y.
+\uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx)\sin({\bf e}_y\cdot\xx){\bf e}_x+\sin({\bf e}_x\cdot\xx)\cos({\bf e}_y\cdot\xx){\bf e}_y\right).
 \end{equation}
@@
 The magnitude of the vortex flow is controlled by the velocity scale $V_0$.
+
+\subsection{Steady-State Structure Confined in Narrow Channels}
 
@@
 % Create the reference section using BibTeX:
-%\bibliography{basename of .bib file}
+\bibliography{reference}
 

### 2022-05-09 doc/PRF2022/PRF_main.tex
update

@@
 
+We measure the end-to-end distance of the multi-lamellar structure when the flow is on.
+
 \subsection{Collective Janus Particles Suspended in a Taylor-Green Flow}
 
-Similar to shear flow simulations, we then place equilibrium states of all boundary conditions \eqref{eq:bcs} in a rotating Taylor-Green Flow
+Similar to shear flow simulations, we then place equilibrium states of all boundary conditions \eqref{eq:bcs} in a rotating Taylor-Green Flow with a length scale $l$
 \begin{equation}
-\uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx)\sin({\bf e}_y\cdot\xx){\bf e}_x+\sin({\bf e}_x\cdot\xx)\cos({\bf e}_y\cdot\xx){\bf e}_y\right).
+\uu_\infty(\xx) = V_0 \left(-\cos(l{\bf e}_x\cdot\xx)\sin(l{\bf e}_y\cdot\xx){\bf e}_x+\sin(l{\bf e}_x\cdot\xx)\cos(l{\bf e}_y\cdot\xx){\bf e}_y\right).
 \end{equation}
@@
 \subsection{Steady-State Structure Confined in Narrow Channels}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{VesConf_0.png}
+  \includegraphics[width=0.4\textwidth]{VesConf_2000.png}\\
+  \includegraphics[width=0.4\textwidth]{VesConf_5000.png}
+  \includegraphics[width=0.4\textwidth]{VesConf_10000.png}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:confined_vesicle} A JP vesicle confined in a narrow channel where $N_b=25$ and $\dot\gamma=0.01$.  }
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{MultConf_100.png}
+  \includegraphics[width=0.4\textwidth]{MultConf_600.png}\\
+  \includegraphics[width=0.4\textwidth]{MultConf_1200.png}
+  \includegraphics[width=0.4\textwidth]{MultConf_2400.png}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:confined_lamellar} A JP multi-lamellar structure confined in a narrow channel where $N_b=40$ and $\dot\gamma=0.05$.  }
+\end{figure}
 

### 2022-05-10 doc/PRF2022/PRF_main.tex
update

@@
 
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{shear_0.png}
+  \includegraphics[width=0.4\textwidth]{shear_1000.png}\\
+  \includegraphics[width=0.4\textwidth]{shear_2000.png}
+    \includegraphics[width=0.4\textwidth]{shear_dist.jpg}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a shear flow when $\dot\gamma=0.05$. }
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{shear_checker_0.png}
+  \includegraphics[width=0.4\textwidth]{shear_checker_250.png}\\
+  \includegraphics[width=0.4\textwidth]{shear_checker_500.png}
+    \includegraphics[width=0.4\textwidth]{shear_checker_750.png}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:shear_2} Snapshots of simulation using boundary condition \eqref{eq:bcs}(c) in a shear flow when $\dot\gamma=0.15$. }
+\end{figure}
+
 Consider placing equilibrium states of cases (b) and (c) for 60 particles in a shear flow,
@@
 \subsection{Collective Janus Particles Suspended in a Taylor-Green Flow}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{TG_0.png}
+  \includegraphics[width=0.4\textwidth]{TG_2500.png}\\
+  \includegraphics[width=0.4\textwidth]{TG_5000.png}
+    \includegraphics[width=0.4\textwidth]{TG_dist.jpg}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
+\end{figure}
 

### 2022-05-12 doc/PRF2022/PRF_main.tex
updates

@@
 
-Suppose we use the double layer potential to express the solution of \eqref{eq:SL} where the condition is $f(u)=u^2$. Then it is given by 
+We adopt the double layer potential to express the solution of \eqref{eq:SL} where the condition is $f(u)=u^2$. Then it is given by 
 \begin{align}
+\label{eq:energy_BIE}
 u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy,
@@
 %
-where $G(\xx)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL}.
+where $G(\xx)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL} and $\nnu$ is the outward normal.
 Since the free energy functional can be written as 
@@
 %
-we can then use the following identity to calculate this boundary equation without evaluating 
-the normal derivative of the double layer potential directly.
+we can then refer to the identity (\cite{Hsiao2008}, \S 1.2) to calculate this boundary integral equation without evaluating the normal derivative of the double layer potential directly.
 
+Consider
 \begin{align}
@@
 \begin{equation}
+\label{eq:normal_deriv}
 \frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) = -\frac1\rho^2 {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx) + \frac{\partial}{\partial s}\SSS\left[\frac{\partial \sigma}{\partial s}\right](\xx).
@@
 %
+
+Substituting \eqref{eq:normal_deriv} to \eqref{eq:energy_BIE} provides the total energy calculation
+throughout this paper and this expression takes the advantage of not calculating the quadruple layer potential.
 
@@
   \begin{tabular}{c|c|c}
-     \text{(a)} & \text{(b)} & \text{(c)} \\
+     \text{(i)} & \text{(ii)} & \text{(iii)} \\
     \hline
@@
 of radius $r$. 
-The cases (b) and (c) are obtained by applying a vertical shift
-and scaling to case (a), see Figure \ref{fig:bcs}.
-Using this setup, we simulate the dynamics of 60 particles with random
-initial position and orientation as shown in Figure~\ref{fig:relax}.
+The cases (ii) and (iii) are obtained by applying a vertical shift
+and scaling to case (i), see Figure \ref{fig:bcs}.
+Using this setup, we simulate the dynamics of 60 particles with one set of random
+initial positions and orientations as shown in Figure~\ref{fig:relax}(a).
 
@@
   \vspace{-20pt}  
-  \caption{\label{fig:relax} (a) Initial configuration; (b)--(d) Equilibruim states for all boundary conditions~\eqref{eq:bcs}(a)--(c), respectively.
+  \caption{\label{fig:relax} (a) Initial configuration for $N_b=60$ structure.
+In order to expedite the self-assembly procedure, all particles are placed in a $8\times8$ box initially.
+(b)--(d) Equilibruim states for all boundary conditions~\eqref{eq:bcs}(i)--(iii), respectively.
 Colors represent the boundary values that increases from minimum (blue) to maximum (red).
-}
+Panel (b) reaches the equilibrium at $t=1200$; Panel (c) reaches the steady-state at $t=600$; Panel (d) reaches the final state at $t=180$.}
 \end{figure}
 
-Case (a) models amphiphilic particles.
+Case (i) models amphiphilic particles.
 Amphiphilic particles have a hydrophobic tail and a hydrophilic head
@@
 are hydrophobic. 
-The boundary condition \eqref{eq:bcs}(b) 
+The boundary condition \eqref{eq:bcs}(ii) 
 gives a particle with a hydrophobic intensity that is greater
 on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
-The initial self-assembly is similar to that in case (a).
+The initial self-assembly is similar to that in case (i).
 The difference arises in the long-time dynamics where the bilayers
@@
 Figure~\ref{fig:relax}(c) shows the multilamellar structure with 8 layers when $N_b=60$. 
-The number of folds depends on a number of factors, for instances, number of particles and intial configurations.
+The number of folds depends on several factors, for instances, number of particles and intial configurations.
 
-Finally, boundary condition \eqref{eq:bcs}(c) models 
+Finally, boundary condition \eqref{eq:bcs}(iii) models 
 a particle whose head surface repels the tail surface as proposed in
@@
 
+Consider placing equilibrium states of boundary condition \eqref{eq:bcs} (ii) for 60 particles in a shear flow,
+\begin{equation}
+\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
+\end{equation}
+%
+where $\dot\gamma$ is the shear rate. Figure~\ref{fig:shear_1} (a)--(c) show the snapshots of simulation results when $\dot\gamma=0.05$.
+We measure the ratio of major and minor axes $\lambda$ by adopting an ellipse fitting using the singular value decomposition and track the ratio of this multi-lamellar structure when the flow is on. 
+The result is shown in panel (d) and we observe that the multi-lamellar structure will be stretched 
+to a pancake shape while the ratio reaches above $\lambda=3.5$ level.
+
+Notice that for this simulation, the center of mass position of the initial configuration is not at the origin and it is slightly to the right of the origin.
+Therefore, the result has shown that the structure stretching occurs earlier that the case when we shift the center of mass position to the origin.
+
 \begin{figure}
@@
   \includegraphics[width=0.4\textwidth]{shear_2000.png}
-    \includegraphics[width=0.4\textwidth]{shear_dist.jpg}
+    \includegraphics[width=0.4\textwidth]{shear_dist_all.jpg}
   \end{center}
   \vspace{-20pt}  
-  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a shear flow when $\dot\gamma=0.05$. }
+  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
 \end{figure}
+
+%%%
+
+The second set of simulation is putting the equilibrium state of the boundary condition \eqref{eq:bcs} (iii), the checker board, in a shear flow.
+After a set of empirical numerical investigations, we obtain a critical shear rate $\dot\gamma=0.15$ where the checker board deforms into stripes and small groups of JP.
+Figure~\ref{fig:shear_2}(a)--(d) show configurations when $t=\{0,50,100,150\}$.
+%The deformation starts with stripe separations
 
@@
 \end{figure}
-
-Consider placing equilibrium states of cases (b) and (c) for 60 particles in a shear flow,
-\begin{equation}
-\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
-\end{equation}
-%
-where $\dot\gamma$ is the shear rate.
-
-We measure the end-to-end distance of the multi-lamellar structure when the flow is on.
 

### 2022-05-12 doc/PRF2022/PRF_main.tex
update

@@
 
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.5\textwidth]{Relax_Energy.jpg}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:relax_energy} Energy profile for all three boundary conditions.}
+\end{figure}
+
 Case (i) models amphiphilic particles.
@@
 Notice that for this simulation, the center of mass position of the initial configuration is not at the origin and it is slightly to the right of the origin.
-Therefore, the result has shown that the structure stretching occurs earlier that the case when we shift the center of mass position to the origin.
+Therefore, the result has shown that the structure stretching occurs earlier than the case when we shift the center of mass position to the origin.
 

### 2022-05-13 doc/PRF2022/PRF_main.tex
update

@@
 %
-where the density function $\eeta$, translation velocity $\vv_i$ and angular velocity $\omega_i$ satisfy
+where the number of particles $N_b$, the density function $\eeta$, translation velocity $\vv_i$ and angular velocity $\omega_i$ satisfy
 
@@
 
+Figure~\ref{fig:relax_energy} shows the energy profile of boundary conditions (i)--(iii) using 
+\eqref{eq:free_energy2} with \eqref{eq:normal_deriv} for normal derivative expression. As expected, for all simulation runs, the total energy of the systems decreases and reaches equilibrium states.
+
 \subsection{Collective Janus Particles Suspended in a Shear Flow}

### 2022-05-14 doc/PRF2022/PRF_main.tex
updates

@@
 
-Substituting \eqref{eq:normal_deriv} to \eqref{eq:energy_BIE} provides the total energy calculation
-throughout this paper and this expression takes the advantage of not calculating the quadruple layer potential.
+Substituting \eqref{eq:normal_deriv} to \eqref{eq:free_energy2} provides the total energy calculation
+throughout this paper and this expression takes the advantage of not calculating the quadruple layer potential which has well-known obstacle in numerical implementation.
 
@@
 
-Consider placing equilibrium states of boundary condition \eqref{eq:bcs} (ii) for 60 particles in a shear flow,
+Consider placing the equilibrium state of boundary condition \eqref{eq:bcs} (ii) for 60 particles in a shear flow,
 \begin{equation}
@@
 where $\dot\gamma$ is the shear rate. Figure~\ref{fig:shear_1} (a)--(c) show the snapshots of simulation results when $\dot\gamma=0.05$.
-We measure the ratio of major and minor axes $\lambda$ by adopting an ellipse fitting using the singular value decomposition and track the ratio of this multi-lamellar structure when the flow is on. 
+We measure the ratio of major and minor axes $\lambda$ by adopting an ellipse fitting using the singular value decomposition and track this aspect ratio for this multi-lamellar structure when the flow is on.
 The result is shown in panel (d) and we observe that the multi-lamellar structure will be stretched 
 to a pancake shape while the ratio reaches above $\lambda=3.5$ level.
-
+%
 Notice that for this simulation, the center of mass position of the initial configuration is not at the origin and it is slightly to the right of the origin.
 Therefore, the result has shown that the structure stretching occurs earlier than the case when we shift the center of mass position to the origin.
-
+%
 \begin{figure}
@@
 \end{figure}
+%
+
+%Consider the energy profiles for two simulations where the centor of mass is on and off the origin.
+%The 
+%
+%\begin{figure}
+%  \begin{center}
+%  \includegraphics[width=0.4\textwidth]{shear_energy1.jpg}
+%  \end{center}
+%  \vspace{-20pt}  
+%  \caption{\label{fig:shear_energy1} Energy profiles tracked during the simulations using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+%\end{figure}
 
@@
 %The deformation starts with stripe separations
-
+%
 \begin{figure}
@@
 
+Similar to shear flow simulations, we then place equilibrium states of all boundary conditions \eqref{eq:bcs} in a rotating Taylor-Green Flow with a length scale $l$,
+\begin{equation}
+\uu_\infty(\xx) = V_0 \left(-\cos(l{\bf e}_x\cdot\xx)\sin(l{\bf e}_y\cdot\xx){\bf e}_x+\sin(l{\bf e}_x\cdot\xx)\cos(l{\bf e}_y\cdot\xx){\bf e}_y\right).
+\end{equation}
+%
+The magnitude of the vortex flow is controlled by the velocity scale $V_0$.
+Similar to the setup in the shear flow cases, we shift the center of mass position to the origin then turn on the Taylor-Green flow with $V_0=0.1$ and tune the sides of zero-velocity box to $\pi$, i.e., $l=0.5$, Figure~\ref{fig:TG_1}(a)--(c) show three frames of simulation results and we
+track the aspect ratio $\lambda$ described in the previous section which is provided in panel (d). 
+The stiffness of the multi-lamellar structure is able to compete with the flow therefore the structure
+does not deform to any states other than multi-lamellar shape. 
+%We also found that the flow strength coefficient above $V_0=0.1$ will result to clear group separations during the simulations.
+
 \begin{figure}
@@
 
-Similar to shear flow simulations, we then place equilibrium states of all boundary conditions \eqref{eq:bcs} in a rotating Taylor-Green Flow with a length scale $l$
-\begin{equation}
-\uu_\infty(\xx) = V_0 \left(-\cos(l{\bf e}_x\cdot\xx)\sin(l{\bf e}_y\cdot\xx){\bf e}_x+\sin(l{\bf e}_x\cdot\xx)\cos(l{\bf e}_y\cdot\xx){\bf e}_y\right).
-\end{equation}
-%
-The magnitude of the vortex flow is controlled by the velocity scale $V_0$.
+\subsection{Steady-State Structure Confined in Narrow Channels}
 
-\subsection{Steady-State Structure Confined in Narrow Channels}
+Here are demonstrations of having JP vesical and multi-lamellar structure in a narrow channel 
+under a shear flow.
+Simulation results and snapshot are shown in Figures~\ref{fig:confined_vesicle} and Figure~\ref{fig:confined_lamellar} where the JP vesicle has $N_b=25$ particles and JP lamellar has $N_b=40$ particles.
+Both starting configurations are relaxed and the channel width in the narrow part is about 5 length units in the vesicle case and 4 length units in the lamellar case.
 

### 2022-05-14 doc/PRF2022/PRF_main.tex
updates

@@
 
-%Consider the energy profiles for two simulations where the centor of mass is on and off the origin.
-%The 
-%
-%\begin{figure}
-%  \begin{center}
-%  \includegraphics[width=0.4\textwidth]{shear_energy1.jpg}
-%  \end{center}
-%  \vspace{-20pt}  
-%  \caption{\label{fig:shear_energy1} Energy profiles tracked during the simulations using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
-%\end{figure}
+Consider the energy profiles for two simulations where the centor of mass is on and off the origin.
+Figure~\ref{fig:shear_energy1} shows numerical results for both energy profiles and magnitude of energy differences is significantly large when there is a large deformation, for instance, the case when a multi-lamellar structure deformed to a pancake shape.
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.5\textwidth]{shear_energy1.jpg}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:shear_energy1} Energy profiles tracked during the simulations using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+\end{figure}
 

### 2022-05-14 doc/PRF2022/PRF_main.tex
updates

@@
 does not deform to any states other than multi-lamellar shape. 
-%We also found that the flow strength coefficient above $V_0=0.1$ will result to clear group separations during the simulations.
+We also found that the flow strength coefficient above $V_0=0.1$ will result to clear group separations during the simulations. 
+Comparing with the case when $V_0=0.2$, we provide a frame in Figure~\ref{fig:TG_2}(a) and the energy comparison is shown in panel (b).
+Numerical results validate the phenomenon that a higher taylor green vortex flow generates large structure separations with higher total energy.
 
@@
   \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{TG0p2_2000.png}
+  \includegraphics[width=0.4\textwidth]{TG_energy1.jpg}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:TG_2} (a) Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.2$, $l=0.5$, and $t = 400$.
+(b) Energy profiles for two cases $V_0=0.1$ and $V_0=0.2$.
+}
 \end{figure}

### 2022-05-16 doc/PRF2022/PRF_main.tex
updates

@@
   \vspace{-20pt}  
-  \caption{\label{fig:relax} (a) Initial configuration for $N_b=60$ structure.
+  \caption{\label{fig:relax} (a) Initial configuration for $N_b=60$ structures.
 In order to expedite the self-assembly procedure, all particles are placed in a $8\times8$ box initially.
@@
   \vspace{-20pt}  
-  \caption{\label{fig:shear_2} Snapshots of simulation using boundary condition \eqref{eq:bcs}(c) in a shear flow when $\dot\gamma=0.15$. }
+  \caption{\label{fig:shear_2} Snapshots of simulation using boundary condition \eqref{eq:bcs}(iii) in a shear flow when $\dot\gamma=0.15$. }
 \end{figure}
@@
 
-Here are demonstrations of having JP vesical and multi-lamellar structure in a narrow channel 
+Here are demonstrations of having JP vesicle and multi-lamellar structure in a narrow channel 
 under a shear flow.
-Simulation results and snapshot are shown in Figures~\ref{fig:confined_vesicle} and Figure~\ref{fig:confined_lamellar} where the JP vesicle has $N_b=25$ particles and JP lamellar has $N_b=40$ particles.
-Both starting configurations are relaxed and the channel width in the narrow part is about 5 length units in the vesicle case and 4 length units in the lamellar case.
+Simulation results and snapshots are shown in Figures~\ref{fig:confined_vesicle} and Figure~\ref{fig:confined_lamellar} where the JP vesicle has $N_b=25$ particles and JP lamellar has $N_b=40$ particles, respectively.
+Both starting configurations are pre-relaxed and the channel width in the narrow part is about 5 length units in the vesicle case and 4 length units in the lamellar case.
 

### 2022-05-16 doc/PRF2022/PRF_main.tex
1st push yny
updates

@@
 %Title of paper
-\title{Collective behavior of Suspended Janus Particles via an Integral Equation Method}
+\title{Collective behavior of Janus Particles  Suspended in a Viscous Fluid}
 
 % repeat the \author .. \affiliation  etc. as needed
-% \email, \thanks, \homepage, \altaffiliation all apply to the current
+% \email \thanks, \homepage, \altaffiliation all apply to the current
 % author. Explanatory text should go in the []'s, actual e-mail
@@
 % insert abstract here
+
+{\bf To do list:}
+
+Unbouned Flow: 
+\begin{enumerate}
+\item $N_b=60$ self-assembly/relaxation runs with all 3 boundary conditions using $N=24$ points per particle (FIG.
+2).
+Energy profiles in a linear-log plot (FIG.
+3) ($E(t)$ or $\Delta E(t)$ v.s.
+time).
+
+\item $N_b=198$ relaxation runs with all 3 boundary conditions using $N=24$ points per particle.
+Add energy profiles to check local/absolute minimum.
+
+\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 4), check convergence using $N=16$ and $N=24$. 
+Compare the new results with the current FIG 4. (d). Revise FIG. 5 with more details.
+
+\item Use particle/checker board alignment to identify the critical shear rate for phase separation.
+
+\item $N_b=60$ structures in a Taylor-Green flow (FIG. 7-8). Add more frames for further comparison between values of flow strength $V_0$.
+\end{enumerate}
+
+Channel Flow: 
+\begin{enumerate}
+\item $Nb_25$ vesicle in a narrow channel.
+\item $Nb_40$ multi-lamellar structure in a narrow channel.
+\end{enumerate}
+
 \end{abstract}
@@
 %\section{\label{}}
-
-\subsection{}
 

### 2022-05-17 doc/PRF2022/PRF_main.tex
to do list

@@
 
-\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 4), check convergence using $N=16$ and $N=24$. 
-Compare the new results with the current FIG 4. (d). Revise FIG. 5 with more details.
+\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 4), convergence tests using $N=16$ and $N=24$ are not yet verified. 
+Compare results using $N_b=24$ with the current FIG 4. (d). Revise FIG. 5 with more details.
 
@@
 \begin{enumerate}
-\item $Nb_25$ vesicle in a narrow channel.
-\item $Nb_40$ multi-lamellar structure in a narrow channel.
+\item Convergence tests for $N_b=25$ vesicle in a narrow channel.  Add energy profile.
+
+\item Convergence tests for $N_b=40$ multi-lamellar structure in a narrow channel. Add energy profile.
+
 \end{enumerate}

### 2022-05-19 doc/PRF2022/PRF_main.tex
updates

@@
 We measure the ratio of major and minor axes $\lambda$ by adopting an ellipse fitting using the singular value decomposition and track this aspect ratio for this multi-lamellar structure when the flow is on.
-The result is shown in panel (d) and we observe that the multi-lamellar structure will be stretched 
-to a pancake shape while the ratio reaches above $\lambda=3.5$ level.
+The result is shown in panel (d) and we observe that the multi-lamellar structure will be slightly stretched and the aspect ratio $\lambda=3.5$ increases over time.
 %
 Notice that for this simulation, the center of mass position of the initial configuration is not at the origin and it is slightly to the right of the origin.
-Therefore, the result has shown that the structure stretching occurs earlier than the case when we shift the center of mass position to the origin.
+We also track the aspect ratio $\lambda$ for the case that the center of mass position is shifted to the origin.
+Panel (d) also shows that the dynamics
+of two sets of simulations are invariant of center of mass position in a shear flow.
+
 %
@@
   \includegraphics[width=0.4\textwidth]{shear_2000.png}
-    \includegraphics[width=0.4\textwidth]{shear_dist_all.jpg}
+    \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
   \end{center}
@@
 
-Consider the energy profiles for two simulations where the centor of mass is on and off the origin.
-Figure~\ref{fig:shear_energy1} shows numerical results for both energy profiles and magnitude of energy differences is significantly large when there is a large deformation, for instance, the case when a multi-lamellar structure deformed to a pancake shape.
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.5\textwidth]{shear_energy1.jpg}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:shear_energy1} Energy profiles tracked during the simulations using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
-\end{figure}
+%Consider the energy profiles for two simulations where the centor of mass is on and off the origin.
+%Figure~\ref{fig:shear_energy1} shows numerical results for both energy profiles and magnitude of energy differences is significantly large when there is a large deformation, for instance, the case when a multi-lamellar structure deformed to a pancake shape.
+%
+%\begin{figure}
+%  \begin{center}
+%  \includegraphics[width=0.5\textwidth]{shear_energy1.jpg}
+%  \end{center}
+%  \vspace{-20pt}  
+%  \caption{\label{fig:shear_energy1} Energy profiles tracked during the simulations using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+%\end{figure}
 

### 2022-05-24 doc/PRF2022/PRF_main.tex
minor changes to organization

@@
 \begin{enumerate}
-\item $N_b=60$ self-assembly/relaxation runs with all 3 boundary conditions using $N=24$ points per particle (FIG.
-2).
-Energy profiles in a linear-log plot (FIG.
-3) ($E(t)$ or $\Delta E(t)$ v.s.
-time).
+\item $N_b=60$ self-assembly/relaxation runs with all 3 boundary
+  conditions using $N=24$ points per particle (FIG. 2). Energy profiles
+    in a log-log plot (FIG. 3) ($E(t)$ or $\Delta E(t)$ v.s. time).
 
 \item $N_b=198$ relaxation runs with all 3 boundary conditions using $N=24$ points per particle.
-Add energy profiles to check local/absolute minimum.
+Add energy profiles to check local/absolute minimum. Superimpose these
+    energies on Figure 3, but scale the energies by the number of Janus
+    particles so that it is ``energy per particle"
 
-\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 4), convergence tests using $N=16$ and $N=24$ are not yet verified. 
+\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 5), convergence tests using $N=16$ and $N=24$ are not yet verified. 
 Compare results using $N_b=24$ with the current FIG 4. (d). Revise FIG. 5 with more details.
 
-\item Use particle/checker board alignment to identify the critical shear rate for phase separation.
+\item Use particle/checker board alignment and/or aspect ratio to identify the critical shear rate for phase separation.
 
@@
   \begin{center}
-  \includegraphics[width=0.4\textwidth]{shear_0.png}
-  \includegraphics[width=0.4\textwidth]{shear_1000.png}\\
-  \includegraphics[width=0.4\textwidth]{shear_2000.png}
+  \includegraphics[width=0.21\textwidth]{shear_0.png}
+  \includegraphics[width=0.21\textwidth]{shear_1000.png}
+  \includegraphics[width=0.21\textwidth]{shear_2000.png} 
+  \includegraphics[width=0.21\textwidth]{shear_2000.png} \\
+  \includegraphics[width=0.21\textwidth]{shear_checker_0.png}
+  \includegraphics[width=0.21\textwidth]{shear_checker_250.png}
+  \includegraphics[width=0.21\textwidth]{shear_checker_500.png}
+  \includegraphics[width=0.21\textwidth]{shear_checker_750.png} \\
   \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
@@
 %
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.4\textwidth]{shear_checker_0.png}
-  \includegraphics[width=0.4\textwidth]{shear_checker_250.png}\\
-  \includegraphics[width=0.4\textwidth]{shear_checker_500.png}
-    \includegraphics[width=0.4\textwidth]{shear_checker_750.png}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:shear_2} Snapshots of simulation using boundary condition \eqref{eq:bcs}(iii) in a shear flow when $\dot\gamma=0.15$. }
-\end{figure}
+%\begin{figure}
+%  \begin{center}
+%  \includegraphics[width=0.4\textwidth]{shear_checker_0.png}
+%  \includegraphics[width=0.4\textwidth]{shear_checker_250.png}\\
+%  \includegraphics[width=0.4\textwidth]{shear_checker_500.png}
+%    \includegraphics[width=0.4\textwidth]{shear_checker_750.png}
+%  \end{center}
+%  \vspace{-20pt}  
+%  \caption{\label{fig:shear_2} Snapshots of simulation using boundary condition \eqref{eq:bcs}(iii) in a shear flow when $\dot\gamma=0.15$. }
+%\end{figure}
 

### 2022-05-27 doc/PRF2022/PRF_main.tex
starting on methods section

@@
 \section{Governing Equations}
+We consider a suspension of $N_b$ Janus particles in the fluid domain
+$\Omega$. The boundary of the $\Omega$ is $\bd\Omega = \Gamma_1 \cup
+\cdots \cup \Gamma_{N_b}$, where $\Gamma_i$ is the boundary of Janus
+particle $i$. We also consider a bounded fluid domain where $\Gamma_0$
+is the fixed boundary of $\Omega$. In this case, $\bd\Omega = \Gamma_0
+\cup \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$.
 
-\subsection{Screened Laplace Mobility Problem}
-
+%%%
+\subsection{Hydrophobic Attraction Potential Mobility Problem} 
 The mathematical formulation is a nonlinear system for the dynamics of a
-collection of particles. The interactions come from a system of 
-partial differential equations (PDEs) that comprise hydrodynamic
-interactions and hydrophobic interactions.
-The hydrodynamic interactions come from the mobility problem for rigid
-particles immersed in a viscous solvent. We then use a
-second-order Adams-Bashforth method to update the particle configuration.
-Assuming inertial terms are
-negligible, the particle motion is goverened by the Stokes equations
+collection of rigid Janus particles. The interactions satisfy a system
+of partial differential equations (PDEs) that describe the hydrodynamic
+interactions and hydrophobic interactions. Assuming inertial terms are
+negligible, the solvent is goverened by the Stokes equations
 \begin{alignat}{3}
@@
 \end{alignat}
-where $\uu$ is the velocity and $p$ is the pressure of the solvent,
-$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
-viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
-particles and changes shape as the particles move.
-Since the particles are rigid, the solvent velocity satisfies
-a no-slip boundary condition for a rigid body motion 
-on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
-and angular velocity $\omega_i$.
-Given imposed forces acting on each
-particle, the mobility problem consists of finding
-translational and angular velocities so that viscous fluid forces
-balance the imposed forces.
+where $\uu$ is the velocity, $p$ is the pressure, $\uu_\infty$ is the
+background flow, and $\mu$ is the constant viscosity. The domain $\Omega
+= \Omega(t)$ is the fluid region surrounding the particles and changes
+shape as the particles move. Since the particles are rigid, the solvent
+velocity satisfies a no-slip boundary condition for a rigid body motion
+\begin{align}
+  \vv_i + \omega_i (\xx - \aa_i)^\perp = \uu(\xx), 
+    \quad \xx \in \Gamma_i
+\end{align}
+where $\vv_i$ is the translational velocity and $\omega_i$ is the
+angular velocity. Once these quantities are determined, we use
+second-order Adams-Bashforth to update the particle configuration.
 
-The hydrophobic interactions come from the tendency of particles to
-minimize the free energy of the structure of the surrounding water
-molecules. The free energy functional takes the form 
-\begin{equation}
+The translational and angular velocities guarantee that the fluid forces
+balanace the imposed forces. The imposed forces include the hydrophobic
+interactions that arise so that particles minimize the free energy of
+the structure of the surronding water molecules. The free energy
+functional is
+\begin{align}
 \label{eq:free_energy}
@@
   \,d\xx,
-\end{equation}
+\end{align}
 where $u$ is an order parameter for the structure of water, $\rho$ is a
 decay length, $C$ is a constant, and $f(u)$ is a potential.
-Hydrogen-bond persistence times are on the order of picoseconds
-which is much smaller than characteristic time for 
-particle motion. % \cite{MaGa13}.
-Thus we assume $u$ minimizes $F[u]$ for all times.
-Assuming appropriate conditions on $f(u)$,% (\cite{evans10}, \S 8.2),
- $u$ is bounded and satisfies the Euler-Lagrange equation
-\begin{equation}
+Hydrogen-bond persistence times are on the order of picoseconds which is
+much smaller than characteristic time for particle motion.
+%\cite{MaGa13}. 
+Thus we assume $u$ minimizes $F[u]$ for all times. Assuming appropriate
+conditions on $f(u)$,
+% (\cite{evans10}, \S 8.2),
+$u$ satisfies the Euler-Lagrange equation
+\begin{alignat}{3}
   \label{eq:SL}
--\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
-\text{ on } \bd\Omega.
-\end{equation}
+  -\rho^2 \Delta u + \tfrac{1}{2}f'(u) &= 0, && \xx \in \Omega, \\
+  u &= g, && \xx \in \bd\Omega, \\
+  u &\rightarrow 0, \qquad&& |\xx| \rightarrow \infty.
+\end{alignat}
 The boundary condition $g$ is a material label that is transported with

### 2022-06-04 doc/PRF2022/PRF_main.tex
added figures

@@
 
+{\bf May do list:}
 Channel Flow: 
@@
 %\section{\label{}}
+
+{\bf More results:}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{multilamellar_shear_Energy}
+    \includegraphics[width=0.4\textwidth]{multilamellar_shear_MSD}
+  \end{center}
+      \caption{A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$.
+We compute the energy and the mean square displacement $MSD(t) = \frac{1}{N_b^2}\sum_{i=1}^{N_b} ||D(t)-D(0) ||_2$ where the matrix $D$ is the pairwise distance matrix at time $t$.
+}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{multilamellar_shear0p1_Energy_LsFs}
+    \includegraphics[width=0.4\textwidth]{multilamellar_shear0p1_MSD_LsFs}
+  \end{center}
+    \caption{ A multi-lamellar structure in a shear flow when the shear rate is $\dot\gamma=0.1$.
+We tune the length scale parameters, radius, $\rho$ and $\rho_0$, by $\pm 5\%$ and the force scale parameters, $\gamma$ and $M$, by $\pm 5\%$.
+}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{multilamellar_TG_Energy}
+    \includegraphics[width=0.4\textwidth]{multilamellar_TG_MSD}
+  \end{center}
+    \caption{A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$. }
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{checker_board_shear_Energy}
+    \includegraphics[width=0.4\textwidth]{checker_board_shear_MSD}\\
+  \includegraphics[width=0.4\textwidth]{checker_board_shear0p125_OP}
+    \includegraphics[width=0.4\textwidth]{checker_board_shear0p15_OP}
+  \end{center}
+\caption{A checker board in shear flows with shear rates $\dot\gamma=\{0.125, 0.15\}$. We propose the order parameter defined by $S_2 = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{checker_board_TG_Energy}
+    \includegraphics[width=0.4\textwidth]{checker_board_TG_MSD}\\
+      \includegraphics[width=0.4\textwidth]{checker_board_TG0p2_OP}
+    \includegraphics[width=0.4\textwidth]{checker_board_TG0p3_OP}
+  \end{center}
+\caption{A checker board in Taylor-Green flows when the flow strength $V_0=\{0.2,0.3\}$. }
+\end{figure}
 

### 2022-06-06 doc/PRF2022/PRF_main.tex
working on equations

@@
 The mathematical formulation is a nonlinear system for the dynamics of a
-collection of rigid Janus particles. The interactions satisfy a system
+collection of rigid Janus particles. For the sake of completeness, we
+summarize the governing equations here, and a complete description is in
+our previous work~\cite{our_paper}. The interactions satisfy a system
 of partial differential equations (PDEs) that describe the hydrodynamic
@@
 shape as the particles move. Since the particles are rigid, the solvent
-velocity satisfies a no-slip boundary condition for a rigid body motion
+velocity satisfies the no-slip rigid body motion boundary condition
 \begin{align}
   \vv_i + \omega_i (\xx - \aa_i)^\perp = \uu(\xx), 
-    \quad \xx \in \Gamma_i
+    \quad \xx \in \Gamma_i,
 \end{align}
 where $\vv_i$ is the translational velocity and $\omega_i$ is the
-angular velocity. Once these quantities are determined, we use
+angular velocity. Once these velocities are determined, we use
 second-order Adams-Bashforth to update the particle configuration.
@@
 \end{alignat}
-The boundary condition $g$ is a material label that is transported with
-the particle (Figure~\ref{fig:bcs}).
+Equation~\eqref{eqn:eq:SL} is solved with a boundary integral equation
+method. The boundary condition $g$ is a material label that is
+transported with the particle (Figure~\ref{fig:bcs}).
 
@@
 variation of the domain. % ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
-Carrying out this variation yields a stress  
+Carrying out this variation yields the stress  
 \begin{align}

### 2022-06-06 doc/PRF2022/PRF_main.tex
worked on methods a bit

@@
 summarize the governing equations here, and a complete description is in
-our previous work~\cite{our_paper}. The interactions satisfy a system
-of partial differential equations (PDEs) that describe the hydrodynamic
-interactions and hydrophobic interactions. Assuming inertial terms are
-negligible, the solvent is goverened by the Stokes equations
+our previous work~\cite{fu-qua-ryh-you2022}. The interactions satisfy a
+system of partial differential equations (PDEs) that describe the
+hydrodynamic interactions and hydrophobic interactions. Assuming
+inertial terms are negligible, the solvent is goverened by the Stokes
+equations
 \begin{alignat}{3}
@@
 \end{alignat}
-Equation~\eqref{eqn:eq:SL} is solved with a boundary integral equation
+Equation~\eqref{eq:SL} is solved with a boundary integral equation
 method. The boundary condition $g$ is a material label that is
@@
 
+To solve the Stokes equation with the correct boundary conditions, we
+represent the velocity as the of a layer potential with Stokeslets and
+rotlets
 \begin{align}
@@
 %
-where the number of particles $N_b$, the density function $\eeta$, translation velocity $\vv_i$ and angular velocity $\omega_i$ satisfy
-
+Then, the density function $\eeta$, translation velocity $\vv_i$ and
+angular velocity $\omega_i$ satisfy
 \begin{alignat}{3}

### 2022-06-10 doc/PRF2022/PRF_main.tex
added rewrite of governing eqs to top of PRF_main.tex

@@
 
+\section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
+The governing equations are a nonlinear system
+for the position and orientation of a collection of
+rigid Janus particles.
+We first pose the Stokes equations
+for the mobility problem giving the hydrodynamic interactions
+for the particle suspension.  
+The hydrophobic forces come from solving a screened Laplace equation.
+Particle collisions are avoided through a near-field, pair
+potential.
+
+\subsection{Mobility problem}
+A suspension of $N_b$ Janus particles is immersed in a vicsous solvent.
+The domain $\Omega(t) \subset \mathbb{R}^2$ denotes the solvent phase
+where $t$ is time.
+The particles are disks of radius $c$ with center $\aa_i$ and
+orientation $\theta_i$ relative to a fixed horizontal axis.  
+The boundary of the $\Omega$ is $\bd\Omega = \Gamma_1 \cup
+\cdots \cup \Gamma_{N_b}$, where $\Gamma_i$ is the boundary of Janus
+particle $i$. Assuming inertial terms are
+negligible, we have 
+\begin{alignat}{3}
+\label{eq:stokes}
+  -\mu \Delta \uu + \nabla p &= \mathbf{0},     && \xx \in \Omega, \\
+  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
+  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
+\end{alignat}
+where $\uu$ is the velocity of the solvent,
+$p$ is the pressure, $\uu_\infty$ is the
+background flow, and $\mu$ is the constant viscosity.
+On the boundaries, the solvent
+velocity satisfies a no-slip boundary condition for a rigid body motion
+\begin{equation}
+  \label{eq:rigid-vel}
+  \vv_i + \omega_i (\xx - \aa_i)^\perp = \uu(\xx), 
+    \quad \xx \in \Gamma_i,
+\end{equation}
+where $\vv_i$ is the translational velocity, $\omega_i$ is the
+angular velocity, and
+$\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.
+
+To close the system \eqref{eq:stokes}-\eqref{eq:rigid-vel},
+we use
+\begin{equation}
+  \label{eq:force}
+  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i, \quad
+  \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
+  (\ssigma \cdot \nnu) \, \dif s = T_i,
+  \quad i=1,\ldots,N_b,
+\end{equation}
+where $\FF_i \in \mathbb{R}^2$ and $T_i \in \mathbb{R}$
+are interparticle forces and torques. 
+Here $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
+\right)$ is the hydrodynamic stress tensor (pressure tensor) and
+$\nnu$ is the particle outward normal.
+
+To get $\FF_i$ and $T_i$,
+the particles minimizes the free energy
+\begin{align}
+\label{eq:free_energy}
+F[u] = \gamma
+\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
+\,d\xx
++ \frac{M}{2}
+\sum_{j \neq i} 
+P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
+\end{align}
+Here, $u(\xx,t)$ is an order parameter for the structure of water
+in the presence of hydrophobic surfaces,
+$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
+We model water structure
+using the screened Laplace equation boundary value problem:
+\begin{gather}
+  \label{eq:SL}
+  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
+  u = g, \quad \xx \in \bd\Omega, \quad 
+  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
+\end{gather}
+The boundary condition $g$ represents the degree of hydrophobicity
+the particle (Figure~\ref{fig:bcs}).
+
+Variation of the
+the free energy \eqref{eq:free_energy}
+provides
+\begin{equation}
+  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
+  - \frac{M}{\rho_0}
+  \sum_{j \neq i}
+  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
+P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
+  ,\quad
+T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
+\end{equation}
+for $i = 1,\dots,N_b$. The term 
+$
+\mathbf{T}
+= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
+  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
+$
+is the hydrophobic stress it is derived from 
+variation of the domain as described in ~\cite{Fu2018_SIAM}.
+
+The dimensionless repulsion profile $P$
+takes the form
+$P(s) = 1 - \sin(\pi s/2)$ for $0 \leq s < 1$
+and $P(s) = 0$ for $1 \leq s < \infty$.
+As such, only those particles within
+a $\rho_0$-tubular neighborhood of $\Gamma_i$
+contribute to repulsion.  The parameter $M$ is the repuslion modulus.
+
+\subsection{Boundary integral represenation and time stepping}
+We recast \eqref{eq:stokes}-\eqref{eq:rigid-vel} and \eqref{eq:SL}
+as boundary integral equations (BIEs) and discretize each BIE at
+$N$ points on each of the $N_b$ particles with a collocation method.
+To express the solution of \eqref{eq:SL},
+we adopt the double layer potential
+\begin{align}
+\label{eq:SL_BIE}
+u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy
+, \quad \xx \in \Omega,
+\end{align}
+where $G(\xx)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL}
+and where $\sigma$ is a scalar-valued density function. 
+For the velocity, we use the representation  
+\begin{align}
+  \label{eq:velocity}
+  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
+    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
+    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
+\end{align}
+with the vector-valued density function $\eeta$,
+Stokeslet 
+$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr \otimes \rr}{|\rr|^2}\right)$,
+and Rotlet
+$\RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$.
+
+Finally, together with \eqref{eq:velocity},
+\eqref{eq:stokes}-\eqref{eq:rigid-vel} become 
+\begin{alignat}{3}
+  \label{eq:vel_BLM_rep}
+  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
+    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) 
+    + \sum_{j=1}^{N_b} 
+    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
+  \label{eq:mobility}
+  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
+  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
+\end{alignat}
+for $\xx \in \Gamma_i$ and $i = 1,\dots,N_b$.
+
+We discretize \eqref{eq:SL_BIE} and \eqref{eq:vel_BLM_rep}
+using high-order interpolation-based quadrature rules.
+Integrals that are smooth are computed with
+the spectrally-accurate trapezoid rule, and nearly-singular integrals,
+caused by close contact between two particles, are computed with a
+high-order interpolation-based quadrature rule (\cite{qua-bir2014}).
+
+After discretizing and applying quadrature,
+the result is an $NN_b \times NN_b$ and $2NN_b \times 2NN_b$
+linear system for \eqref{eq:SL_BIE} and \eqref{eq:vel_BLM_rep}, respectively.
+These are solved with matrix-free GMRES, and we guarantee that the number of
+GMRES iterations is mesh-independent by using second-kind BIEs.
+
+Once determined the translational and angular velocities $\vv_i, \omega_i$
+have been determined, a second-order Adams-Bashforth scheme updates the particle
+positions and orientations:
+\begin{equation}
+  \label{eq:adams-bashforth}
+  \begin{aligned}
+    \aa_i(t_{n+2}) &=
+\aa_i(t_{n+1})
++ \tfrac{3}{2}\Delta t \vv_i(t_{n+1})
+- \tfrac{1}{2}\Delta t \vv_i(t_{n}),\\
+    \theta_i(t_{n+2}) &=
+\theta_i(t_{n+1})
++ \tfrac{3}{2}\Delta t \omega_i(t_{n+1})
+- \tfrac{1}{2}\Delta t \omega_i(t_{n}).
+  \end{aligned}
+\end{equation}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.24\textwidth]{Fig2a.png}
+  \includegraphics[width=0.24\textwidth]{Fig2b.png}
+  \includegraphics[width=0.24\textwidth]{Fig2c.png}
+  \includegraphics[width=0.24\textwidth]{Fig2d.png}
+\end{center}
+\begin{caption}{\label{fig:relax}
+  Panel (a) shows 60 particles confined to a square with random 
+  positions and orientation.
+  In a quiescent background flow, 
+  the self-assembled particles take on distinct configurations
+  depending on the value of the shift parameter $b$.}
+\end{caption}
+\end{figure}
+
+\section{Equilibrium configurations}
+\subsection{Boundary conditions and normalization}
+The present paper considers boundary condition of the form
+\begin{equation}
+  \label{eq:bc-type}
+g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
+\end{equation}
+where $\alpha$ is the angle between $\xx - \aa_i$ and the particle director
+$\dd_i = (\cos \theta_i, \sin \theta_i)$.
+We refer to the side of the particle where $\alpha = 0$ as the head and the
+side where $\alpha = \pi$ as the tail. 
+The boundary conditions are
+normalized so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
+
+To see the effect of the shift parameter $b$, we simulate the dynamics of
+60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
+There are three cases:
+(i) $b = 1$, bilayers,
+(ii) $b = 2$, multilamellar
+and (iii) $b = 0$, striated.
+
+Case (i), $b = 1$, mimicks an amphiphilic particle.
+The boundary condition $g$ is everywhere nonnegative,
+takes the value $0$ on the
+hydrophilic tail,
+and takes the maximum value $a$ on the
+hydrophobic head. 
+The interaction is attractive, and particles collectively orient their
+hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)).
+
+In case (ii), $b = 1$ the boundary condition is positive everywhere.
+It takes the maximum value $3a$ on head where $\alpha = 0$ and the
+minimum value $a$ on the tail side where $\alpha = \pi$. This way,
+both sides of the Janus particle are hydrophobic but
+moreso on the $\alpha = 0$ side.  
+Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
+the heads are also hydrophobic and so in the long-time dynamics
+these bilayers also adhere to one another 
+forming multilamella structures. Figure~\ref{fig:relax}(c), for example, shows a
+multilamellar structure with 2 layers. The number of folds depends on several factors,
+for instances, number of particles and intial configurations.
+
+A water structure with
+positive/negative charge is possible in case (iii), $b = 0$
+\cite{MaRa76, Ma77}.
+Here, the head repels the tail of other particles
+and the particles initially form chains with their directors perpendicular
+to the length of the chain.  
+It is worth noting that in the dipolar molecules modeled by
+Laplace equation, the equilibrium configurations consist of strands,
+rather than a patch, of particles and also have
+alternating orientations \cite{}. Unlike the electrical case, though,
+the chains form striated layers
+where the particles lie on a 
+grid and the orientations alternate between layers (Figure~\ref{fig:relax}(d)).
+
+\section{DRAFT RESULTS BELOW}
 {\bf More results:}
@@
   \begin{center}
-  \includegraphics[width=0.4\textwidth]{multilamellar_shear_Energy}
-    \includegraphics[width=0.4\textwidth]{multilamellar_shear_MSD}
+  \includegraphics[height=0.2\textheight]{multilamellar_shear_Energy}
+    \includegraphics[height=0.2\textheight]{multilamellar_shear_MSD}\\
+          \includegraphics[height=0.2\textheight]{multilamellar_shear_LocPar}
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.4\textwidth]{multilamellar_shear0p1_Energy_LsFs}
-    \includegraphics[width=0.4\textwidth]{multilamellar_shear0p1_MSD_LsFs}
+  \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_Energy_LsFs}
+    \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_MSD_LsFs}
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.4\textwidth]{multilamellar_TG_Energy}
-    \includegraphics[width=0.4\textwidth]{multilamellar_TG_MSD}
+  \includegraphics[height=0.2\textheight]{multilamellar_TG_Energy}
+    \includegraphics[height=0.2\textheight]{multilamellar_TG_MSD}\\
+    \includegraphics[height=0.2\textheight]{multilamellar_TG_LocPar}
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.4\textwidth]{checker_board_shear_Energy}
-    \includegraphics[width=0.4\textwidth]{checker_board_shear_MSD}\\
-  \includegraphics[width=0.4\textwidth]{checker_board_shear0p125_OP}
-    \includegraphics[width=0.4\textwidth]{checker_board_shear0p15_OP}
+  \includegraphics[height=0.2\textheight]{checker_board_shear_Energy}
+    \includegraphics[height=0.2\textheight]{checker_board_shear_MSD}\\
+  \includegraphics[height=0.2\textheight]{checker_board_shear_LocPar}
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.4\textwidth]{checker_board_TG_Energy}
-    \includegraphics[width=0.4\textwidth]{checker_board_TG_MSD}\\
-      \includegraphics[width=0.4\textwidth]{checker_board_TG0p2_OP}
-    \includegraphics[width=0.4\textwidth]{checker_board_TG0p3_OP}
+  \includegraphics[height=0.2\textheight]{checker_board_TG_Energy}
+    \includegraphics[height=0.2\textheight]{checker_board_TG_MSD}\\
+      \includegraphics[height=0.2\textheight]{checker_board_TG_LocPar}
   \end{center}

### 2022-06-10 doc/PRF2022/PRF_main.tex
modified normal derivative calculation, added Appendix, added distance matrix/order parameter

@@
 \newcommand{\yy}{\mathbf{y}}
+\renewcommand{\tt}{\mathbf{t}}
 \newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
@@
 the particles minimizes the free energy
-\begin{align}
+\begin{equation}
 \label{eq:free_energy}
-F[u] = \gamma
+F = \gamma
 \int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
@@
 P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
-\end{align}
+\end{equation}
 Here, $u(\xx,t)$ is an order parameter for the structure of water
@@
 a $\rho_0$-tubular neighborhood of $\Gamma_i$
-contribute to repulsion.  The parameter $M$ is the repuslion modulus.
+contribute to repulsion.  The parameter $M$ is the repulsion modulus.
 
@@
 and where $\sigma$ is a scalar-valued density function.
+The subscript in $\dif s_\yy$ denotes integration with respect to $\yy \in \Gamma$. 
 For the velocity, we use the representation  
@@
 grid and the orientations alternate between layers (Figure~\ref{fig:relax}(d)).
+
+\section{Measuring deformation}
+We use the free energy $F$,
+the Euclidean distance matrix $D(t)$,
+and a scalar order parameter $S_{2}(t)$ to measure
+the deformation of particle configurations under background flows.
+
+We simplify the
+form of the free energy \eqref{eq:free_energy}
+using integration by parts and \eqref{eq:SL}
+to obtain
+\begin{equation}
+\label{eq:free_energy2}
+F[u] = -\gamma
+\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
++ \frac{M}{2}
+\sum_{j \neq i} 
+P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
+\end{equation}
+%
+This is simpler because the boundary data $g$ are known.
+Evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
+directly, however,
+involves calculating a quadruple layer potential which has a
+well-known obstacle in numerical implementation.
+To overcome this obstacle, we use
+%
+\begin{equation}
+\label{eq:normal_deriv}
+\nabla u(\xx) \cdot \nnu(\xx)=
+%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
+-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
++ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
+\end{equation}
+%
+Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
+See the Appendix section \ref{sec:appendix} for the proof and details.
+Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
+leads to single layer integral which is more straightforward to evaluate and we compute the
+arclength derivative using spectrally accurate Fourier transform.
+
+The $N_b$ by $N_b$ Euclidian distance matrix is 
+\begin{equation}
+  \label{eq:EDM}
+[D(t)]_{ij} = \|\aa_{i} - \aa_{j}\|, \quad i, j = 1, \dots, N_b.
+\end{equation}
+For weak background flow strengths, the deformation in particle
+configurations will be relatively small and the collection of
+particles behaves as a rigid body i.e., $\|D(t) - D(0)\| \ll 1$.
+
+To study the change in orientational order, we use the scalar order parameter 
+\begin{equation}
+  \label{eq:S2}
+S_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
+\end{equation}
+Here $\bar \theta$ is a circular mean defined as the
+orientation of the largest eigenvalue eigenvector of the projection 
+$\dd_1\dd_1^\top + \dots + \dd_{N_b}\dd_{N_b}^\top$.
+A value $S_2(t) = 1$ indicates a complete orientational order where all particle
+directors lie on a common axis. A value far from 1 indicated disorder.
+
+It turns out that $S_2$ is an inadequate measure of order for the bilayer and
+multilamellar configurations.  For example, the directors of a circular
+bilayer vesicle are uniformly distributed along a circle, even though
+there is a strong orientational order between neighboring particles.
+To account for these latter cases, we use
+\begin{equation}
+  \label{eq:localS2}
+\tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
+\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1).
+\end{equation}
+where $\bar \theta_i$ is the circular mean restricted to particles
+indexed by $j$ for which $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle is
+isolated and has no neighbors within a distance $4c$, then we exclude it from
+the sum \eqref{eq:localS2}.
+
+\section{Appendix}
+\label{sec:appendix}
+To prove \eqref{eq:normal_deriv}, let 
+\begin{equation}
+  \label{eq:SLP}
+  \mathcal{S}[\sigma](\xx) = \int_\Gamma G(\xx-\yy) \sigma(\yy)\, \dif s_\yy
+\end{equation}
+be the single layer potential for a density function $\sigma.$
+Fix $\xx \in \Gamma$,
+let $\nnu_{\xx} = \nnu(\xx)$ and $\nnu_{\yy}$ be the unit normal at $\xx$, respectively $\yy$, in $\Gamma$,
+and let $\zz \in \Omega$.  The subscripts in $\nabla_{\zz}$ and $\nabla_{\yy}$ denote
+differentiation with respect to $\zz$, respectively $\yy$.
+
+Recall from \eqref{eq:SL_BIE} that $u = \mathcal{D}[\sigma]$.
+Then  
+\begin{align*}
+\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
+&=\nnu_\xx \cdot \nabla_\zz \int_\Gamma \frac{\partial G(\zz-\yy)}{\partial \nnu_\yy}\sigma(\yy) \,\dif s_\yy\\
+&=\int_\Gamma \nnu_\xx^\top \left(\nabla_\zz\nabla_\yy^\top  G(\zz-\yy)\right) \nnu_\yy\sigma(\yy)  \,\dif s_\yy\\
+  &=-\int_\Gamma \nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy\sigma(\yy)\ \dif s_\yy,
+\end{align*}
+since we can interchange $\nabla_\zz$ with $-\nabla_\yy$.
+Following \cite{Hsiao2008}, \S 1.2,
+\[
+\nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy
+=
+-\tt_{\xx}^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\tt_{\yy}
++ \Delta_{\yy}G(\zz-\yy) \tt_{\xx}\cdot \tt_{\yy}
+\]
+Then, using that $\Delta_{\yy} G(\zz-\yy) = \rho^{-2} G(\zz-\yy)$,
+interchanging $\nabla_\yy$ with $-\nabla_\zz$ once more,
+and integrating by parts in arclength $s$,
+we obtain 
+\begin{align*}
+\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
+&=-\int_\Gamma  \Delta_\yy G(\zz-\yy) {\bf t}_\xx \cdot   {\bf t}_\yy \sigma(\yy)\ \dif s_\yy
++\int_\Gamma({\bf t}_\xx\cdot\nabla_\yy)({\bf t}_\yy\cdot\nabla_\yy G(\zz-\yy))\sigma(\yy)\ \dif s_\yy\\
+&= -\int_\Gamma \frac{1}{\rho^{2}} G(\zz-\yy) {\bf t}_\xx \cdot {\bf t}_\yy \sigma(\yy)\ \dif s_\yy  
+-({\bf t}_\xx\cdot\nabla_\zz)\int_\Gamma \frac{\dif}{\dif s_\yy}G(\zz-\yy) \sigma(\yy)\ \dif s_\yy\\
+&= -\frac{1}{\rho^2} {\bf t}_\xx\cdot \int_\Gamma G(\zz-\yy){\bf t}_\yy \sigma(\yy)\ \dif s_\yy + 
+({\bf t}_\xx \cdot \nabla_\zz)\int_\Gamma G(\zz-\yy)\frac{\dif }{\dif s} \sigma(\yy)  \dif s_\yy.
+\end{align*}
+%
+Letting $\zz\to\xx\in\Gamma$, and noting that both sides of the equation are continuous,
+we obtain \eqref{eq:normal_deriv}.
 

### 2022-06-13 doc/PRF2022/PRF_main.tex
updates

@@
   \begin{center}
-  \includegraphics[height=0.2\textheight]{multilamellar_shear_Energy}
-    \includegraphics[height=0.2\textheight]{multilamellar_shear_MSD}\\
-          \includegraphics[height=0.2\textheight]{multilamellar_shear_LocPar}
+  \includegraphics[width=0.3\textwidth]{MS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{MS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{MS_MSD.pdf}
   \end{center}
@@
   \begin{center}
-  \includegraphics[height=0.2\textheight]{multilamellar_TG_Energy}
-    \includegraphics[height=0.2\textheight]{multilamellar_TG_MSD}\\
-    \includegraphics[height=0.2\textheight]{multilamellar_TG_LocPar}
+  \includegraphics[width=0.3\textwidth]{MTG_E.pdf}
+   \includegraphics[width=0.3\textwidth]{MTG_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{MTG_MSD.pdf}
   \end{center}
@@
   \begin{center}
-  \includegraphics[height=0.2\textheight]{checker_board_shear_Energy}
-    \includegraphics[height=0.2\textheight]{checker_board_shear_MSD}\\
-  \includegraphics[height=0.2\textheight]{checker_board_shear_LocPar}
-  \end{center}
-\caption{A checker board in shear flows with shear rates $\dot\gamma=\{0.125, 0.15\}$. We propose the order parameter defined by $S_2 = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[height=0.2\textheight]{checker_board_TG_Energy}
-    \includegraphics[height=0.2\textheight]{checker_board_TG_MSD}\\
-      \includegraphics[height=0.2\textheight]{checker_board_TG_LocPar}
+  \includegraphics[width=0.3\textwidth]{CS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{CS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{CS_MSD.pdf}
+  \end{center}
+\caption{A checker board in shear flows with shear rates $\dot\gamma=\{0.125, 0.15\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{CTG_E.pdf}
+   \includegraphics[width=0.3\textwidth]{CTG_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{CTG_MSD.pdf}
   \end{center}
 \caption{A checker board in Taylor-Green flows when the flow strength $V_0=\{0.2,0.3\}$. }
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
+  \end{center}
+\caption{A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.1\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
+   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}
+  \end{center}
+\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1,0.2\}$. }
 \end{figure}

### 2022-06-13 doc/PRF2022/PRF_main.tex
started "results" section

@@
 \subsection{Mobility problem}
-A suspension of $N_b$ Janus particles is immersed in a vicsous solvent.
-The domain $\Omega(t) \subset \mathbb{R}^2$ denotes the solvent phase
-where $t$ is time.
-The particles are disks of radius $c$ with center $\aa_i$ and
-orientation $\theta_i$ relative to a fixed horizontal axis.  
+A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
+The domain $\Omega(t) \subset \mathbb{R}^2$ is the solvent phase
+and $t$ is time.
+The particles are disks of radius $c$, center $\aa_i$, and
+orientation $\theta_i$ relative to the horizontal axis.  
 The boundary of the $\Omega$ is $\bd\Omega = \Gamma_1 \cup
@@
 $p$ is the pressure, $\uu_\infty$ is the
-background flow, and $\mu$ is the constant viscosity.
-On the boundaries, the solvent
-velocity satisfies a no-slip boundary condition for a rigid body motion
+background flow velocity, and $\mu$ is the constant viscosity.
+The solvent velocity satisfies a no-slip boundary
+condition for a rigid body motion
 \begin{equation}
   \label{eq:rigid-vel}
-  \vv_i + \omega_i (\xx - \aa_i)^\perp = \uu(\xx), 
+  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
     \quad \xx \in \Gamma_i,
@@
 Here $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
-\right)$ is the hydrodynamic stress tensor (pressure tensor) and
+\right)$ is the hydrodynamic stress tensor (pressure tensor), and
 $\nnu$ is the particle outward normal.
@@
 To get $\FF_i$ and $T_i$,
-the particles minimizes the free energy
+the particles minimize the free energy
 \begin{equation}
@@
 \end{equation}
-Here, $u(\xx,t)$ is an order parameter for the structure of water
-in the presence of hydrophobic surfaces,
+Here, $u(\xx,t)$ is an order parameter for the structure of water,
 $\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
@@
 \end{gather}
-The boundary condition $g$ represents the degree of hydrophobicity
-the particle (Figure~\ref{fig:bcs}).
+The boundary condition $g$ gives the degree of hydrophobicity
+the particle-solvent interface (Figure~\ref{fig:bcs}).
 
@@
 $
-is the hydrophobic stress it is derived from 
-variation of the domain as described in ~\cite{Fu2018_SIAM}.
+is the hydrophobic stress identified in ~\cite{Fu2018_SIAM} 
+and derived by variation of the domain techniques.
 
@@
 As such, only those particles within
-a $\rho_0$-tubular neighborhood of $\Gamma_i$
-contribute to repulsion.  The parameter $M$ is the repulsion modulus.
-
+a distance $\rho_0$ of $\Gamma_i$
+contribute to repulsion.
+The parameter $M$ is the repulsion modulus.
+
+We use the parameters $\mu = 1$ cP, $\gamma = 4$ pN nm$^{-1}$,
+$\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.
 \subsection{Boundary integral represenation and time stepping}
@@
 \end{align}
-where $G(\xx)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL}
-and where $\sigma$ is a scalar-valued density function.
+where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL},
+$K_0$ is the zeroth-order modified Bessel function of the first kind,
+and $\sigma$ is a scalar-valued density function.
 The subscript in $\dif s_\yy$ denotes integration with respect to $\yy \in \Gamma$. 
-For the velocity, we use the representation  
+For the velocity, we use the representation [REF]
 \begin{align}
@@
 and Rotlet
-$\RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$.
+$\RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$,
+$\rr = \xx - \aa_i$ [REF].
 
@@
 \end{alignat}
-for $\xx \in \Gamma_i$ and $i = 1,\dots,N_b$.
+for $\xx \in \Gamma_i$ and $i = 1,\dots,N_b$ [REF].
 
@@
 
-Once determined the translational and angular velocities $\vv_i, \omega_i$
+Once the translational and angular velocities $\vv_i, \omega_i$
 have been determined, a second-order Adams-Bashforth scheme updates the particle
@@
 $\dd_i = (\cos \theta_i, \sin \theta_i)$.
-We refer to the side of the particle where $\alpha = 0$ as the head and the
-side where $\alpha = \pi$ as the tail. 
-The boundary conditions are
-normalized so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
+The parameter $a$ normalizes the boundary conditions 
+so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
+We refer to the side of the particle where $\alpha = 0$
+as the tail and the side where $\alpha = \pi$ as the head.
 
 To see the effect of the shift parameter $b$, we simulate the dynamics of
-60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
-There are three cases:
-(i) $b = 1$, bilayers,
-(ii) $b = 2$, multilamellar
-and (iii) $b = 0$, striated.
-
-Case (i), $b = 1$, mimicks an amphiphilic particle.
+198 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
+Three distinct configurations emerge:
+(i) bilayers for $b = 1$, 
+(ii) multilamellar for $b = 2$, and 
+(iii) striated for $b = 0$.
+
+Case (i) with $b = 1$, mimicks an amphiphilic particle.
 The boundary condition $g$ is everywhere nonnegative,
 takes the value $0$ on the
-hydrophilic tail,
+hydrophilic head,
 and takes the maximum value $a$ on the
-hydrophobic head. 
+hydrophobic tail. 
 The interaction is attractive, and particles collectively orient their
@@
 
-In case (ii), $b = 1$ the boundary condition is positive everywhere.
-It takes the maximum value $3a$ on head where $\alpha = 0$ and the
-minimum value $a$ on the tail side where $\alpha = \pi$. This way,
-both sides of the Janus particle are hydrophobic but
+In case (ii) with $b = 1$, the boundary condition is positive everywhere.
+It takes the maximum value $3a$ on tail and the
+minimum value $a$ on the head side. 
+Both sides of the Janus particle are hydrophobic but
 moreso on the $\alpha = 0$ side.  
@@
 forming multilamella structures. Figure~\ref{fig:relax}(c), for example, shows a
-multilamellar structure with 2 layers. The number of folds depends on several factors,
-for instances, number of particles and intial configurations.
+multilamellar structure with 2 layers.
+At equilibrium, the number of folds depends primarily on the number of particles.
 
@@
 to the length of the chain.  
-It is worth noting that in the dipolar molecules modeled by
-Laplace equation, the equilibrium configurations consist of strands,
-rather than a patch, of particles and also have
-alternating orientations \cite{}. Unlike the electrical case, though,
-the chains form striated layers
+The chains form stria
 where the particles lie on a 
@@
 
+The equilibrium configurations for case (ii) and (iii) are used as initial data in the
+background flow simulations found in Section \ref{sec:results}.
+In case (i), there are several connected
+components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
+To have a single, coherent vesicle (i), we reinitialize
+the case (i) particles in the form of a ring and run the relaxation procedure once more.
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.5\textwidth]{Relax_Energy.jpg}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:relax_energy}
+    The free energy \eqref{eq:free_energy} is decreasing
+    in the mobility problem formulation.  The initial energies
+    are for the configuration in Figure \ref{fig:relax}a
+    and the final energies are for the near-equilibrium
+    configurations Figure \ref{fig:relax}b--c, respectively. 
+    The red curves are the energies for the $N_b = 198$ cases normalized
+    by $60/198$, showing that the energy approximately scales with the number of
+    particles.
+  }
+\end{figure}
+
 \section{Measuring deformation}
 We use the free energy $F$,
-the Euclidean distance matrix $D(t)$,
+a Euclidean distance-based measure $d(t)$,
 and a scalar order parameter $S_{2}(t)$ to measure
@@
 
-We simplify the
+First, we must simplify the
 form of the free energy \eqref{eq:free_energy}
@@
 %
-This is simpler because the boundary data $g$ are known.
-Evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
-directly, however,
+Here, we have substituted $g$ for $u$ since the boundary values are given.
+However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
 involves calculating a quadruple layer potential which has a
@@
 arclength derivative using spectrally accurate Fourier transform.
-
-The $N_b$ by $N_b$ Euclidian distance matrix is 
+We have validated the form of \eqref{eq:normal_deriv} by extrapolating 
+the primal energy \eqref{eq:free_energy} along test curves placed slightly
+outside the particles.
+
+The Euclidian distance matrix is the $N_b \times N_b$ matrix 
+$[D(t)]_{ij} = \|\aa_{i} - \aa_{j}\|$ for $i, j = 1, \dots, N_b$
+To measure positional order, we use
 \begin{equation}
 \label{eq:EDM}
-[D(t)]_{ij} = \|\aa_{i} - \aa_{j}\|, \quad i, j = 1, \dots, N_b.
-\end{equation}
+d(t) = \frac{1}{N_b^2}\|D(t) - D(0)\|
+\end{equation}
+where $\| \cdot \|$ is the Frobeneous norm.
 For weak background flow strengths, the deformation in particle
 configurations will be relatively small and the collection of
-particles behaves as a rigid body i.e., $\|D(t) - D(0)\| \ll 1$.
-
-To study the change in orientational order, we use the scalar order parameter 
+particles behaves as a rigid body i.e., $d(t) \ll 1$.
+
+To study orientational order, we use the scalar order parameter 
 \begin{equation}
@@
 Here $\bar \theta$ is a circular mean defined as the
-orientation of the largest eigenvalue eigenvector of the projection 
+orientation of the largest eigenvalue eigenvector of 
 $\dd_1\dd_1^\top + \dots + \dd_{N_b}\dd_{N_b}^\top$.
-A value $S_2(t) = 1$ indicates a complete orientational order where all particle
-directors lie on a common axis. A value far from 1 indicated disorder.
-
-It turns out that $S_2$ is an inadequate measure of order for the bilayer and
-multilamellar configurations.  For example, the directors of a circular
+A value $S_2(t) = 1$ indicates a complete orientational
+order where all particle directors lie on a common axis e.g.,
+two parallel vectors with possibly opposite direction are ordered. 
+A value far from 1 indicates disorder.
+
+The measure $S_2$ is an inadequate for the bilayer and
+multilamellar structures.  For example, the directors of a circular
 bilayer vesicle are uniformly distributed along a circle, even though
@@
 the sum \eqref{eq:localS2}.
+
+\section{Results}
+\label{sec:results}
+\begin{figure}
+\caption{\label{fig:ves_shear} A vesicle in shear flow}
+\end{figure}
+\begin{figure}
+\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
+\end{figure}
+\subsection{Boundary condition (i):   bilayer configurations}
+The vesicle in a shear flow undergoes the familiar tank-treading deformation.
+Our previous paper \cite{Fu2022_JFM} studied the geometry,
+intermonolayer slip, and critical shear rates $\gamma^*$
+for vesicles comprised of amphiphilic Janus particles.
+
+The vesicle is subject to a shear background flow
+\begin{equation}
+\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
+\end{equation}
+%
+where $\dot\gamma$ is the shear rate. Figure~\ref{fig:shear_1} (a)--(c)
+shows snapshots of the vesicle when $\dot\gamma= ... $ is
+below the critical shear rate $\dot \gamma_* = ...$
+Here, the free energy and order parameter are more or less constant
+(Figure \ref{fig:BC1_shear}ab, solid curves).  The is a slight upward shift
+in $d(t)$ (Figure \ref{fig:BC1_shear}c, solid curve) due to relative
+displacement as the two leaflets slide past one another.
+
+In, Figure~\ref{fig:shear_2} (a)--(c), 
+$\dot\gamma= ...$ is above the critical shear rate,
+and there is a jump in energy (Figure \ref{fig:BC1_shear}a, dashed curve)
+due to the breaking of the vesicle into two components.  
+There is greater variation in the order parameter $\tilde{S}_2(t)$ as well
+with a baseline value around $0.7$
+(Figure \ref{fig:BC1_shear}b, dashed curve).The oscillations occur due to the
+orbit of the two bilayer components, and $\tilde{S}_2(t)$ increases
+to about $0.9$ when the components are nearly parallel and slide past one another.
+Positional order, however, diverges since the two component configuration
+is uncorrelated to the initial circular configuration (Figure \ref{fig:BC1_shear}c, dashed curve).
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
+  \end{center}
+  \caption{
+    \label{fig:BC1_shear}
+    A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.1\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
+   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}
+  \end{center}
+\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1,0.2\}$. }
+\end{figure}
+
+The Taylor-Green (TG) background flow is
+\begin{equation}
+  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
+  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
+\end{equation}
+where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
+%
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.24\textwidth]{shear_0.png}
+  \includegraphics[width=0.24\textwidth]{shear_1000.png}
+  \includegraphics[width=0.24\textwidth]{shear_2000.png} 
+  \includegraphics[width=0.24\textwidth]{shear_2000.png} \\
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+\end{figure}
+%
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.32\textwidth]{TG_0.png}
+  \includegraphics[width=0.32\textwidth]{TG_2500.png}
+  \includegraphics[width=0.32\textwidth]{TG_5000.png}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
+\end{figure}
+\subsection{Boundary condition (ii):  multilamellar configurations}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{MS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{MS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{MS_MSD.pdf}
+  \end{center}
+      \caption{A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$.
+We compute the energy and the mean square displacement $MSD(t) = \frac{1}{N_b^2}\sum_{i=1}^{N_b} ||D(t)-D(0) ||_2$ where the matrix $D$ is the pairwise distance matrix at time $t$.
+}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{MTG_E.pdf}
+   \includegraphics[width=0.3\textwidth]{MTG_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{MTG_MSD.pdf}
+  \end{center}
+    \caption{A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$. }
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.21\textwidth]{shear_checker_0.png}
+  \includegraphics[width=0.21\textwidth]{shear_checker_250.png}
+  \includegraphics[width=0.21\textwidth]{shear_checker_500.png}
+  \includegraphics[width=0.21\textwidth]{shear_checker_750.png} \\
+%  \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+\end{figure}
+%
+\subsection{Boundary condition (iii): striated configurations}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{CS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{CS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{CS_MSD.pdf}
+  \end{center}
+\caption{A checker board in shear flows with shear rates $\dot\gamma=\{0.125, 0.15\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{CTG_E.pdf}
+   \includegraphics[width=0.3\textwidth]{CTG_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{CTG_MSD.pdf}
+  \end{center}
+\caption{A checker board in Taylor-Green flows when the flow strength $V_0=\{0.2,0.3\}$. }
+\end{figure}
+
+\section{Discussion}
+\begin{figure}
+  \begin{center}
+  \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_Energy_LsFs}
+    \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_MSD_LsFs}
+  \end{center}
+    \caption{ A multi-lamellar structure in a shear flow when the shear rate is $\dot\gamma=0.1$.
+We tune the length scale parameters, radius, $\rho$ and $\rho_0$, by $\pm 5\%$ and the force scale parameters, $\gamma$ and $M$, by $\pm 5\%$.
+}
+\end{figure}
+
+It is worth noting that in the dipolar molecules modeled by
+Laplace equation, the equilibrium configurations consist of strands,
+rather than a patch, of particles and also have
+alternating orientations \cite{}.
 
@@
 
+\end{document}
+
 \section{DRAFT RESULTS BELOW}
 {\bf More results:}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{MS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{MS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{MS_MSD.pdf}
-  \end{center}
-      \caption{A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$.
-We compute the energy and the mean square displacement $MSD(t) = \frac{1}{N_b^2}\sum_{i=1}^{N_b} ||D(t)-D(0) ||_2$ where the matrix $D$ is the pairwise distance matrix at time $t$.
-}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_Energy_LsFs}
-    \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_MSD_LsFs}
-  \end{center}
-    \caption{ A multi-lamellar structure in a shear flow when the shear rate is $\dot\gamma=0.1$.
-We tune the length scale parameters, radius, $\rho$ and $\rho_0$, by $\pm 5\%$ and the force scale parameters, $\gamma$ and $M$, by $\pm 5\%$.
-}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{MTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{MTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{MTG_MSD.pdf}
-  \end{center}
-    \caption{A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$. }
-\end{figure}
 
@@
 \caption{A checker board in Taylor-Green flows when the flow strength $V_0=\{0.2,0.3\}$. }
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
-  \end{center}
-\caption{A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.1\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}
-  \end{center}
-\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1,0.2\}$. }
 \end{figure}

### 2022-06-15 doc/PRF2022/PRF_main.tex
updated figures

@@
 \begin{center}
-  \includegraphics[width=0.24\textwidth]{Fig2a.png}
-  \includegraphics[width=0.24\textwidth]{Fig2b.png}
-  \includegraphics[width=0.24\textwidth]{Fig2c.png}
-  \includegraphics[width=0.24\textwidth]{Fig2d.png}
+  \includegraphics[width=0.4\textwidth]{Nb198a.pdf}
+  \includegraphics[width=0.4\textwidth]{Nb198b.pdf}\\
+  \includegraphics[width=0.4\textwidth]{Nb198c.pdf}
+  \includegraphics[width=0.4\textwidth]{Nb198d.pdf}
 \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.5\textwidth]{Relax_Energy.jpg}
+  \includegraphics[width=0.5\textwidth]{Relax_Energy.jpg}\\
+  \includegraphics[width=0.3\textwidth]{Nb60b.pdf}
+  \includegraphics[width=0.3\textwidth]{Nb60c.pdf}
+  \includegraphics[width=0.3\textwidth]{Nb60d.pdf}
   \end{center}
@@
     \label{fig:BC1_shear}
-    A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.1\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
+    A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.0655, 0.075\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
 \end{figure}
@@
   \end{center}
-\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1,0.2\}$. }
+\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$. }
 \end{figure}

### 2022-06-16 doc/PRF2022/PRF_main.tex
update

@@
 % insert abstract here
-
-{\bf To do list:}
-
-Unbouned Flow: 
-\begin{enumerate}
-\item $N_b=60$ self-assembly/relaxation runs with all 3 boundary
-  conditions using $N=24$ points per particle (FIG. 2). Energy profiles
-    in a log-log plot (FIG. 3) ($E(t)$ or $\Delta E(t)$ v.s. time).
-
-\item $N_b=198$ relaxation runs with all 3 boundary conditions using $N=24$ points per particle.
-Add energy profiles to check local/absolute minimum. Superimpose these
-    energies on Figure 3, but scale the energies by the number of Janus
-    particles so that it is ``energy per particle"
-
-\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 5), convergence tests using $N=16$ and $N=24$ are not yet verified. 
-Compare results using $N_b=24$ with the current FIG 4. (d). Revise FIG. 5 with more details.
-
-\item Use particle/checker board alignment and/or aspect ratio to identify the critical shear rate for phase separation.
-
-\item $N_b=60$ structures in a Taylor-Green flow (FIG. 7-8). Add more frames for further comparison between values of flow strength $V_0$.
-\end{enumerate}
-
-{\bf May do list:}
-Channel Flow: 
-\begin{enumerate}
-\item Convergence tests for $N_b=25$ vesicle in a narrow channel.  Add energy profile.
-
-\item Convergence tests for $N_b=40$ multi-lamellar structure in a narrow channel. Add energy profile.
-
-\end{enumerate}
+%
+%{\bf To do list:}
+%
+%Unbouned Flow: 
+%\begin{enumerate}
+%\item $N_b=60$ self-assembly/relaxation runs with all 3 boundary
+%  conditions using $N=24$ points per particle (FIG. 2). Energy profiles
+%    in a log-log plot (FIG. 3) ($E(t)$ or $\Delta E(t)$ v.s. time).
+%
+%\item $N_b=198$ relaxation runs with all 3 boundary conditions using $N=24$ points per particle.
+%Add energy profiles to check local/absolute minimum. Superimpose these
+%    energies on Figure 3, but scale the energies by the number of Janus
+%    particles so that it is ``energy per particle"
+%
+%\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 5), convergence tests using $N=16$ and $N=24$ are not yet verified. 
+%Compare results using $N_b=24$ with the current FIG 4. (d). Revise FIG. 5 with more details. 
+%
+%\item Use particle/checker board alignment and/or aspect ratio to identify the critical shear rate for phase separation.
+%
+%\item $N_b=60$ structures in a Taylor-Green flow (FIG. 7-8). Add more frames for further comparison between values of flow strength $V_0$.
+%\end{enumerate}
+%
+%
+%{\bf May do list:}
+%Channel Flow: 
+%\begin{enumerate}
+%\item Convergence tests for $N_b=25$ vesicle in a narrow channel.  Add energy profile.
+%
+%\item Convergence tests for $N_b=40$ multi-lamellar structure in a narrow channel. Add energy profile.
+%
+%\end{enumerate}
 
@@
 \begin{caption}{\label{fig:relax}
-  Panel (a) shows 60 particles confined to a square with random 
+  Panel (a) shows 198 particles confined to a square with random 
   positions and orientation.
@@
   the self-assembled particles take on distinct configurations
-  depending on the value of the shift parameter $b$.}
+  depending on the value of the shift parameter $b$. (b)-(d) show the equilibrium states for $b=1, 2, 0$, respectively.}
 \end{caption}
@@
   \begin{center}
-  \includegraphics[width=0.24\textwidth]{shear_0.png}
-  \includegraphics[width=0.24\textwidth]{shear_1000.png}
-  \includegraphics[width=0.24\textwidth]{shear_2000.png} 
-  \includegraphics[width=0.24\textwidth]{shear_2000.png} \\
+  \includegraphics[width=0.32\textwidth]{shear_0.png}
+  \includegraphics[width=0.32\textwidth]{shear_1000.png}
+  \includegraphics[width=0.32\textwidth]{shear_2000.png} 
   \end{center}

### 2022-06-20 doc/PRF2022/PRF_main.tex
reordered figures, added insets

@@
 
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.4\textwidth]{Nb198a.pdf}
-  \includegraphics[width=0.4\textwidth]{Nb198b.pdf}\\
-  \includegraphics[width=0.4\textwidth]{Nb198c.pdf}
-  \includegraphics[width=0.4\textwidth]{Nb198d.pdf}
+\begin{figure}[h!]
+\begin{center}
+  \includegraphics[width=0.49\textwidth]{Nb198a.pdf}
+  \includegraphics[width=0.49\textwidth]{Nb198b_eta.pdf}\\
+  \includegraphics[width=0.49\textwidth]{Nb198c_eta.pdf}
+  \includegraphics[width=0.49\textwidth]{Nb198d_eta.pdf}
 \end{center}
 \begin{caption}{\label{fig:relax}
-  Panel (a) shows 198 particles confined to a square with random 
+  Panel (a) shows $N_b = 198$ particles confined to a square with random 
   positions and orientation.
-  In a quiescent background flow, 
-  the self-assembled particles take on distinct configurations
-  depending on the value of the shift parameter $b$. (b)-(d) show the equilibrium states for $b=1, 2, 0$, respectively.}
+  Depending on the boundary condition \eqref{eq:bc-type},
+  the particles selc-assemble into distinct configurations.
+  Panel (b) is for $b=1$ and the boundary condition mimicks that
+  of an amphiphilic particle. 
+  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
+  In panel (d), the case $b = 0$ is for a water structure with
+  positive/negative charge. 
+  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.}
 \end{caption}
@@
   \begin{center}
-  \includegraphics[width=0.5\textwidth]{Relax_Energy.jpg}\\
-  \includegraphics[width=0.3\textwidth]{Nb60b.pdf}
-  \includegraphics[width=0.3\textwidth]{Nb60c.pdf}
-  \includegraphics[width=0.3\textwidth]{Nb60d.pdf}
+  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
+%  \includegraphics[width=0.3\textwidth]{Nb60b.pdf}
+%  \includegraphics[width=0.3\textwidth]{Nb60c.pdf}
+  %  \includegraphics[width=0.3\textwidth]{Nb60d.pdf}
+  Panel (b): same but for order parameters 
   \end{center}
@@
 \label{sec:results}
-\begin{figure}
-\caption{\label{fig:ves_shear} A vesicle in shear flow}
-\end{figure}
-\begin{figure}
-\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
-\end{figure}
+
+%\begin{figure}
+%\caption{\label{fig:ves_shear} A vesicle in shear flow}
+%\end{figure}
+%\begin{figure}
+%\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
+%\end{figure}
+
+\begin{figure}
+  \begin{center}
+      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
+      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
+   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
+   \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
+   Panels (e)-(f) same but for non-vesicle initial configuration
+  \end{center}
+  \caption{
+    \label{fig:BC1_shear}
+    The figure shows a vesicle in shear flow (panels (a)-(d), $\dot \gamma = ...$) 
+    and the multiple component bilayers in shear (panels (e)-(f), $\dot \gamma = ...$).}
+\end{figure}
+
 \subsection{Boundary condition (i):   bilayer configurations}
@@
 displacement as the two leaflets slide past one another.
+
+%\begin{figure}
+%\caption{\label{fig:ves_shear} A vesicle in shear flow}
+%\end{figure}
+%\begin{figure}
+%\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
+%\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
+  \end{center}
+  \caption{
+    \label{fig:BC1_shear}
+    The quantities $E(t)$, $\tilde S_2(t)$, and $d(t)$
+    are indicators of bilayer (case (i)) deformation at various shear rates. }
+\end{figure}
 
@@
   \begin{center}
-  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
-  \end{center}
-  \caption{
-    \label{fig:BC1_shear}
-    A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.0655, 0.075\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
-\end{figure}
+  \includegraphics[width=0.32\textwidth]{vesTG_0.png}
+  \includegraphics[width=0.32\textwidth]{vesTG_2500.png}
+  \includegraphics[width=0.32\textwidth]{vesTG_5000.png} 
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+\end{figure}
+
+%
+
+The Taylor-Green (TG) background flow is
+\begin{equation}
+  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
+  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
+\end{equation}
+where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
+%
 
@@
 
-The Taylor-Green (TG) background flow is
-\begin{equation}
-  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
-  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
-\end{equation}
-where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
 %

### 2022-06-20 doc/PRF2022/PRF_main.tex
yny

--- 2022-06-16 doc/PRF2022/PRF_main.tex
@@
 %\section{\label{}}
+The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
+boundary integral numerical simulations \cite{Fu2022_JFM}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
+Immersed in a viscous solvent, the dynamics of a JP suspension results from the combination of long-range hydrodynamic interaction and non-local
+interactions between JPs through the distribution of a hydrophobic potential (HAP). In a quiescent flow, numerical simulations of a 
+JP suspension showed self-assembly into micelles and bilayers of JPs that provide an alternative means for computing the 
+mechanical moduli of a colloidal membrane.
+
+Under background flows, the hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit many familiar behaviors of a vesicle \cite{Fu2022_JFM}: 
+Elongation and alignment along the extensional direction, tank-treading, and rupture of a vesicle under shear flow.
+
+In this work we take advantage of the flexibility of the model to examine the effects of boundary condition on JP surfaces that could be controlled based on the chemicals used in the experiments, for example.
 
@@
 \begin{center}
-  \includegraphics[width=0.4\textwidth]{Nb198a.pdf}
-  \includegraphics[width=0.4\textwidth]{Nb198b.pdf}\\
-  \includegraphics[width=0.4\textwidth]{Nb198c.pdf}
-  \includegraphics[width=0.4\textwidth]{Nb198d.pdf}
+  \includegraphics[width=0.4\textwidth]{Nb198a.pdf}\\
+  \includegraphics[width=0.32\textwidth]{Nb198b_eta.pdf}
+  \includegraphics[width=0.32\textwidth]{Nb198c_eta.pdf}
+  \includegraphics[width=0.32\textwidth]{Nb198d_eta.pdf}
 \end{center}
@@
 \label{sec:results}
-\begin{figure}
-\caption{\label{fig:ves_shear} A vesicle in shear flow}
-\end{figure}
-\begin{figure}
-\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
-\end{figure}
+
+%\begin{figure}
+%\caption{\label{fig:ves_shear} A vesicle in shear flow}
+%\end{figure}
+%\begin{figure}
+%\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
+%\end{figure}
+
 \subsection{Boundary condition (i):   bilayer configurations}
@@
    \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
+    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
+      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
+      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
+   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
+    \includegraphics[width=0.22\textwidth]{VS_3.pdf}
   \end{center}
@@
 where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
+%
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.32\textwidth]{vesTG_0.png}
+  \includegraphics[width=0.32\textwidth]{vesTG_2500.png}
+  \includegraphics[width=0.32\textwidth]{vesTG_5000.png} 
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+\end{figure}
+
+%
 %

### 2022-06-26 doc/PRF2022/PRF_main.tex
updates

@@
 \begin{center}
-  \includegraphics[width=0.49\textwidth]{Nb198a.pdf}
-  \includegraphics[width=0.49\textwidth]{Nb198b_eta.pdf}\\
-  \includegraphics[width=0.49\textwidth]{Nb198c_eta.pdf}
-  \includegraphics[width=0.49\textwidth]{Nb198d_eta.pdf}
+  \includegraphics[height=0.27\textheight]{Nb198a.pdf}
+  \includegraphics[height=0.27\textheight]{Nb198b_eta.pdf}\\
+  \hspace{1.55cm}
+  \includegraphics[height=0.27\textheight]{Nb198c_eta.pdf}
+  \includegraphics[height=0.27\textheight]{Nb198d_eta_1.pdf}
 \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
-%  \includegraphics[width=0.3\textwidth]{Nb60b.pdf}
-%  \includegraphics[width=0.3\textwidth]{Nb60c.pdf}
-  %  \includegraphics[width=0.3\textwidth]{Nb60d.pdf}
-  Panel (b): same but for order parameters 
+%  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
+\includegraphics[width=0.49\textwidth]{relax_E.pdf}
+\includegraphics[width=0.49\textwidth]{relax_LOP.pdf}  \\
+  \includegraphics[height=0.15\textheight]{Nb60a.pdf}
+  \includegraphics[height=0.15\textheight]{Nb60b.pdf}
+  \includegraphics[height=0.15\textheight]{Nb60c.pdf}
+ \includegraphics[height=0.15\textheight]{Nb60d.pdf}
   \end{center}
@@
 %\end{figure}
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
+      \includegraphics[width=0.3\textwidth]{BS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{BS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{BS_MSD.pdf}
+  \end{center}
+  \caption{
+    \label{fig:BC1_shear}
+    The quantities $E(t)$, $\tilde S_2(t)$, and $d(t)$
+    are indicators of bilayer (case (i)) deformation at various shear rates. }
+\end{figure}
 
@@
    \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
-   Panels (e)-(f) same but for non-vesicle initial configuration
+         \includegraphics[width=0.22\textwidth]{BS_0.pdf}
+      \includegraphics[width=0.22\textwidth]{BS_1.pdf}
+   \includegraphics[width=0.22\textwidth]{BS_2.pdf}
+   \includegraphics[width=0.22\textwidth]{BS_3.pdf}
+%   Panels (e)-(f) same but for non-vesicle initial configuration
   \end{center}
   \caption{
-    \label{fig:BC1_shear}
+    \label{fig:BC1_shear_flow}
     The figure shows a vesicle in shear flow (panels (a)-(d), $\dot \gamma = ...$) 
@@
 %\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
-  \end{center}
-  \caption{
-    \label{fig:BC1_shear}
-    The quantities $E(t)$, $\tilde S_2(t)$, and $d(t)$
-    are indicators of bilayer (case (i)) deformation at various shear rates. }
-\end{figure}
 
@@
 
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.32\textwidth]{vesTG_0.png}
-  \includegraphics[width=0.32\textwidth]{vesTG_2500.png}
-  \includegraphics[width=0.32\textwidth]{vesTG_5000.png} 
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
-\end{figure}
-
 %
@@
    \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}
+    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}\\
+  \includegraphics[width=0.3\textwidth]{BTG_E.pdf}
+   \includegraphics[width=0.3\textwidth]{BTG_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{BTG_MSD.pdf}
   \end{center}
 \caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$. }
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.22\textwidth]{VTG_0.pdf}
+  \includegraphics[width=0.22\textwidth]{VTG_1.pdf}
+  \includegraphics[width=0.22\textwidth]{VTG_2.pdf} 
+    \includegraphics[width=0.22\textwidth]{VTG_3.pdf} \\
+      \includegraphics[width=0.22\textwidth]{BTG_0.pdf}
+  \includegraphics[width=0.22\textwidth]{BTG_1.pdf}
+  \includegraphics[width=0.22\textwidth]{BTG_2.pdf} 
+    \includegraphics[width=0.22\textwidth]{BTG_3.pdf}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:BTG_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
 \end{figure}

### 2022-06-26 doc/PRF2022/PRF_main.tex
updates

@@
 %
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.32\textwidth]{shear_0.png}
-  \includegraphics[width=0.32\textwidth]{shear_1000.png}
-  \includegraphics[width=0.32\textwidth]{shear_2000.png} 
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
-\end{figure}
-%
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.32\textwidth]{TG_0.png}
-  \includegraphics[width=0.32\textwidth]{TG_2500.png}
-  \includegraphics[width=0.32\textwidth]{TG_5000.png}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
-\end{figure}
+%\begin{figure}
+%  \begin{center}
+%  \includegraphics[width=0.32\textwidth]{shear_0.png}
+%  \includegraphics[width=0.32\textwidth]{shear_1000.png}
+%  \includegraphics[width=0.32\textwidth]{shear_2000.png} 
+%  \end{center}
+%  \vspace{-20pt}  
+%  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+%\end{figure}
+%
+%\begin{figure}
+%  \begin{center}
+%  \includegraphics[width=0.32\textwidth]{TG_0.png}
+%  \includegraphics[width=0.32\textwidth]{TG_2500.png}
+%  \includegraphics[width=0.32\textwidth]{TG_5000.png}
+%  \end{center}
+%  \vspace{-20pt}  
+%  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
+%\end{figure}
 \subsection{Boundary condition (ii):  multilamellar configurations}
@@
   \begin{center}
+  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
+  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
+  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
+    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:MS_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+\end{figure}
+
+\begin{figure}
+  \begin{center}
   \includegraphics[width=0.3\textwidth]{MTG_E.pdf}
@@
   \begin{center}
-  \includegraphics[width=0.21\textwidth]{shear_checker_0.png}
-  \includegraphics[width=0.21\textwidth]{shear_checker_250.png}
-  \includegraphics[width=0.21\textwidth]{shear_checker_500.png}
-  \includegraphics[width=0.21\textwidth]{shear_checker_750.png} \\
-%  \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
+  \includegraphics[width=0.22\textwidth]{MTG_0.pdf}
+  \includegraphics[width=0.22\textwidth]{MTG_1.pdf}
+  \includegraphics[width=0.22\textwidth]{MTG_2.pdf} 
+    \includegraphics[width=0.22\textwidth]{MTG_3.pdf} 
   \end{center}
   \vspace{-20pt}  
-  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
-\end{figure}
+  \caption{\label{fig:MTG_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+\end{figure}
+
+%\begin{figure}
+%  \begin{center}
+%  \includegraphics[width=0.21\textwidth]{shear_checker_0.png}
+%  \includegraphics[width=0.21\textwidth]{shear_checker_250.png}
+%  \includegraphics[width=0.21\textwidth]{shear_checker_500.png}
+%  \includegraphics[width=0.21\textwidth]{shear_checker_750.png} \\
+%%  \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
+%  \end{center}
+%  \vspace{-20pt}  
+%  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+%\end{figure}
 %
@@
   \begin{center}
+  \includegraphics[width=0.22\textwidth]{CS_0.pdf}
+  \includegraphics[width=0.22\textwidth]{CS_1.pdf}
+  \includegraphics[width=0.22\textwidth]{CS_2.pdf} 
+    \includegraphics[width=0.22\textwidth]{CS_3.pdf} 
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:CS_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+\end{figure}
+
+\begin{figure}
+  \begin{center}
   \includegraphics[width=0.3\textwidth]{CTG_E.pdf}
@@
 \caption{A checker board in Taylor-Green flows when the flow strength $V_0=\{0.2,0.3\}$. }
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.22\textwidth]{CTG_0.pdf}
+  \includegraphics[width=0.22\textwidth]{CTG_1.pdf}
+  \includegraphics[width=0.22\textwidth]{CTG_2.pdf} 
+    \includegraphics[width=0.22\textwidth]{CTG_3.pdf} 
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:CTG_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
 \end{figure}

### 2022-06-26 doc/PRF2022/PRF_main.tex
updates

@@
 \begin{center}
-  \includegraphics[height=0.27\textheight]{Nb198a.pdf}
-  \includegraphics[height=0.27\textheight]{Nb198b_eta.pdf}\\
+  \includegraphics[height=0.27\textheight]{Nb198a_inset.pdf}
+  \includegraphics[height=0.27\textheight]{Nb198b_eta_inset.pdf}\\
   \hspace{1.55cm}
-  \includegraphics[height=0.27\textheight]{Nb198c_eta.pdf}
-  \includegraphics[height=0.27\textheight]{Nb198d_eta_1.pdf}
+  \includegraphics[height=0.27\textheight]{Nb198c_eta_inset.pdf}
+  \includegraphics[height=0.27\textheight]{Nb198d_eta_inset.pdf}
 \end{center}
@@
 the case (i) particles in the form of a ring and run the relaxation procedure once more.
+
+%\begin{figure}
+%  \begin{center}
+%  \includegraphics[height=0.15\textheight]{Nb60a.pdf}
+%  \includegraphics[height=0.15\textheight]{Nb60b.pdf}
+%  \includegraphics[height=0.15\textheight]{Nb60c.pdf}
+% \includegraphics[height=0.15\textheight]{Nb60d.pdf}
+%  \end{center}
+%  \vspace{-20pt}  
+%  \caption{\label{fig:relax_Nb60} 
+%  }
+%\end{figure}
+
 \begin{figure}
@@
 \includegraphics[width=0.49\textwidth]{relax_E.pdf}
-\includegraphics[width=0.49\textwidth]{relax_LOP.pdf}  \\
-  \includegraphics[height=0.15\textheight]{Nb60a.pdf}
-  \includegraphics[height=0.15\textheight]{Nb60b.pdf}
-  \includegraphics[height=0.15\textheight]{Nb60c.pdf}
- \includegraphics[height=0.15\textheight]{Nb60d.pdf}
+\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
   \end{center}
@@
   \caption{\label{fig:relax_energy}
-    The free energy \eqref{eq:free_energy} is decreasing
+  A:  The free energy \eqref{eq:free_energy} is decreasing
     in the mobility problem formulation.  The initial energies
@@
     by $60/198$, showing that the energy approximately scales with the number of
-    particles.
+    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. The near-equilibrium configurations depend on the initial configuration and the results show that 
+    the striated configurations have largest value of order parameter for both $N_b=60$ and $N_b=198$ cases.
   }
@@
   \caption{\label{fig:BTG_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{VTG_Area}
+  \includegraphics[width=0.4\textwidth]{VTG_Len}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:VTG_AreaLen} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.22\textwidth]{VTG_Scale_0.pdf}
+  \includegraphics[width=0.22\textwidth]{VTG_Scale_1.pdf}
+  \includegraphics[width=0.22\textwidth]{VTG_Scale_2.pdf} 
+    \includegraphics[width=0.22\textwidth]{VTG_Scale_3.pdf}
+      \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:BTG_Scale_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
 \end{figure}

### 2022-06-26 doc/PRF2022/PRF_main.tex
Peter working on manuscript

@@
   Depending on the boundary condition \eqref{eq:bc-type},
-  the particles selc-assemble into distinct configurations.
+  the particles self-assemble into distinct configurations.
   Panel (b) is for $b=1$ and the boundary condition mimicks that
@@
   positive/negative charge. 
-  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.}
+  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
+    All figure insets are configurations using $N_b=60$ sharing with the same color map.}
 \end{caption}
@@
 
-%\begin{figure}
-%  \begin{center}
-%  \includegraphics[height=0.15\textheight]{Nb60a.pdf}
-%  \includegraphics[height=0.15\textheight]{Nb60b.pdf}
-%  \includegraphics[height=0.15\textheight]{Nb60c.pdf}
-% \includegraphics[height=0.15\textheight]{Nb60d.pdf}
-%  \end{center}
-%  \vspace{-20pt}  
-%  \caption{\label{fig:relax_Nb60} 
-%  }
-%\end{figure}
-
 \begin{figure}
@@
     \label{fig:BC1_shear}
-    The quantities $E(t)$, $\tilde S_2(t)$, and $d(t)$
-    are indicators of bilayer (case (i)) deformation at various shear rates. }
+    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$.
+Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$.
+The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures.
+For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows.
+The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
+     }
 \end{figure}

### 2022-06-26 doc/PRF2022/PRF_main.tex
Peter working on manuscript

@@
     \label{fig:BC1_shear_flow}
-    The figure shows a vesicle in shear flow (panels (a)-(d), $\dot \gamma = ...$) 
-    and the multiple component bilayers in shear (panels (e)-(f), $\dot \gamma = ...$).}
+    The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
+    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=600$).
+The streamlines are plotted in the background.
+}
 \end{figure}
@@
   \end{center}
-\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$. }
+\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$.
+The result indicates that the highest flow strength ($V_0=0.2$) makes the vesicle (top row) rupture within a short period of time and the energy rapidly increases.
+As expected, the local order parameter drops and the MSD increases.
+For bilayer structure (bottom row), for $V_0=0.15$ and $V_0 = 0.2$, the energy gradually increases over the time but the other two measures do not have  a clear trend.}
 \end{figure}
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BTG_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+  \caption{\label{fig:BTG_flow} The figure shows a vesicle in Taylor-Green flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=600$) 
+    and the multiple component bilayers in Taylor-Green flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=200$).
+The streamlines are plotted in the background.
+  }
 \end{figure}
@@
   \vspace{-20pt}  
-  \caption{\label{fig:VTG_AreaLen} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+  \caption{\label{fig:VTG_AreaLen} Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied.
+The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations.
+}
 \end{figure}
@@
 
-%
-%\begin{figure}
-%  \begin{center}
-%  \includegraphics[width=0.32\textwidth]{shear_0.png}
-%  \includegraphics[width=0.32\textwidth]{shear_1000.png}
-%  \includegraphics[width=0.32\textwidth]{shear_2000.png} 
-%  \end{center}
-%  \vspace{-20pt}  
-%  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
-%\end{figure}
-%
-%\begin{figure}
-%  \begin{center}
-%  \includegraphics[width=0.32\textwidth]{TG_0.png}
-%  \includegraphics[width=0.32\textwidth]{TG_2500.png}
-%  \includegraphics[width=0.32\textwidth]{TG_5000.png}
-%  \end{center}
-%  \vspace{-20pt}  
-%  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
-%\end{figure}
 \subsection{Boundary condition (ii):  multilamellar configurations}
@@
 
-%\begin{figure}
-%  \begin{center}
-%  \includegraphics[width=0.21\textwidth]{shear_checker_0.png}
-%  \includegraphics[width=0.21\textwidth]{shear_checker_250.png}
-%  \includegraphics[width=0.21\textwidth]{shear_checker_500.png}
-%  \includegraphics[width=0.21\textwidth]{shear_checker_750.png} \\
-%%  \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
-%  \end{center}
-%  \vspace{-20pt}  
-%  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
-%\end{figure}
-%
 \subsection{Boundary condition (iii): striated configurations}

### 2022-06-26 doc/PRF2022/PRF_main.tex
added figure captions

@@
   \end{center}
-\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$.
+\caption{\label{fig:BC1_TG} A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$.
 The result indicates that the highest flow strength ($V_0=0.2$) makes the vesicle (top row) rupture within a short period of time and the energy rapidly increases.
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BTG_flow} The figure shows a vesicle in Taylor-Green flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=600$) 
+  \caption{\label{fig:BC1_TG_flow} The figure shows a vesicle in Taylor-Green flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=600$) 
     and the multiple component bilayers in Taylor-Green flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=200$).
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BTG_Scale_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+  \caption{\label{fig:BTG_Scale_flow} With $V_0=0.1$, panels (a)-(d) show the configurations with streamlines when a vesicle is in Taylor-Green flow at $t=1000$ and $l= 1,2,3,4$, respectively.}
 \end{figure}
@@
   \end{center}
-      \caption{A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$.
-We compute the energy and the mean square displacement $MSD(t) = \frac{1}{N_b^2}\sum_{i=1}^{N_b} ||D(t)-D(0) ||_2$ where the matrix $D$ is the pairwise distance matrix at time $t$.
-}
+      \caption{\label{fig:BC2_shear} 
+      A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$.
+For this set of simulations, the local order parameter is a good indicator for tracking the rupture or structure separations.
+Moreover, all three measure show that the energy, orderparameter, and MSD increase as shear rate increases.}
 \end{figure}
@@
   \vspace{-20pt}  
-  \caption{\label{fig:MS_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+  \caption{\label{fig:BC2_shear_flow} Multi-lamellar stracture in shear flows.
+The insets of Fig~\ref{fig:relax}c is used for panels (a).
+Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=500$, respecitively.
+The streamlines are plotted in the background.}
 \end{figure}
@@
   \end{center}
-    \caption{A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$. }
+    \caption{\label{fig:BC2_TG}  A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$.
+The energy profile when $V_0=0.2$ has an increasing trend that results a large deformation after a period of time.
+Since the flow strengths for all cases are not strong enough, the convergent MSD represents that the rupture does not occur before $t=1000$.}
 \end{figure}
@@
   \vspace{-20pt}  
-  \caption{\label{fig:MTG_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+  \caption{\label{fig:BC2_TG_flow} Multi-lamellar stracture in Taylor-Green flows.
+The insets of Fig~\ref{fig:relax}c is used for panels (a).
+Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.1, 0.15, 0.2\}$ at $t=600$, respecitively.
+The streamlines are plotted in the background.
+}
 \end{figure}
@@
   \end{center}
-\caption{A checker board in shear flows with shear rates $\dot\gamma=\{0.125, 0.15\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
+\caption{\label{fig:BC3_shear} A striated configuration in shear flows with shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$.
+The energy profile, order parameter, and MSD for the case $\dot\gamma=0.15$ show that a rupture occurs during the simulation.
+For other two cases, all measures remain nearly constant.
+}
 \end{figure}
@@
   \vspace{-20pt}  
-  \caption{\label{fig:CS_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+  \caption{\label{fig:BC3_shear_flow} A striated configuration in shear flows where the streamlines are plotted in the background.
+Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$ at $t=100$, respectively.
+  }
 \end{figure}
@@
   \end{center}
-\caption{A checker board in Taylor-Green flows when the flow strength $V_0=\{0.2,0.3\}$. }
+\caption{\label{fig:BC3_TG} A striated configuration in Taylor-Green flows with flow strengths $V_0=\{0.2, 0.25, 0.3\}$.   }
 \end{figure}
@@
   \vspace{-20pt}  
-  \caption{\label{fig:CTG_flow} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
+  \caption{\label{fig:BC3_TG_flow}  A striated configuration in shear flows where the streamlines are plotted in the background.
+Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the flow strengths $V_0=\{0.2, 0.25, 0.3\}$ at $t=400$, respectively.
+.
+}
 \end{figure}
@@
 \section{Discussion}
+
 \begin{figure}
@@
   \end{center}
-    \caption{ A multi-lamellar structure in a shear flow when the shear rate is $\dot\gamma=0.1$.
+    \caption{\label{fig:BC2_tests} A multi-lamellar structure in a shear flow when the shear rate is $\dot\gamma=0.1$.
 We tune the length scale parameters, radius, $\rho$ and $\rho_0$, by $\pm 5\%$ and the force scale parameters, $\gamma$ and $M$, by $\pm 5\%$.

### 2022-06-29 doc/PRF2022/PRF_main.tex
updates
yny

@@
 %\section{\label{}}
+Janus particles are particles with two surfaces of different properties such as hydrophobicity.
+For example, it is common for a Janus particle to have a hydrophobic hemisphere and a hydrophilic hemisphere.
+In a viscous solvent Janus particles often self-assemble into structures of tunable functions for biomedical engineering applications \cite{GheisariSahfieeAbbasiEtAl2021_DMR,LiuYangHuangEtAl2016_Angew,LiWangYaoEtAl2019_Nanoscale}.
+Depending on the interactions between Janus particles and the surrounding viscous solvent, JPs self-assemble into oligomers of various geometries and sizes.
+
 The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
@@
 
-%\begin{figure}
-%\caption{\label{fig:ves_shear} A vesicle in shear flow}
-%\end{figure}
-%\begin{figure}
-%\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
-%\end{figure}
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
-      \includegraphics[width=0.3\textwidth]{BS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{BS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{BS_MSD.pdf}
-  \end{center}
-  \caption{
-    \label{fig:BC1_shear}
-    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$.
-Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$.
-The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures.
-For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows.
-The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
-     }
-\end{figure}
-
 \begin{figure}
@@
 The streamlines are plotted in the background.
+}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
+      \includegraphics[width=0.3\textwidth]{BS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{BS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{BS_MSD.pdf}
+  \end{center}
+  \caption{
+    \label{fig:BC1_shear}
+    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$.
+Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$.
+The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures.
+For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows.
+The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
      }
@@
   \begin{center}
-  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}\\
-  \includegraphics[width=0.3\textwidth]{BTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{BTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{BTG_MSD.pdf}
-  \end{center}
-\caption{\label{fig:BC1_TG} A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$.
-The result indicates that the highest flow strength ($V_0=0.2$) makes the vesicle (top row) rupture within a short period of time and the energy rapidly increases.
-As expected, the local order parameter drops and the MSD increases.
-For bilayer structure (bottom row), for $V_0=0.15$ and $V_0 = 0.2$, the energy gradually increases over the time but the other two measures do not have  a clear trend.}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
   \includegraphics[width=0.22\textwidth]{VTG_0.pdf}
@@
   \begin{center}
-  \includegraphics[width=0.4\textwidth]{VTG_Area}
-  \includegraphics[width=0.4\textwidth]{VTG_Len}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:VTG_AreaLen} Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied.
-The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations.
-}
+  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
+   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}\\
+  \includegraphics[width=0.3\textwidth]{BTG_E.pdf}
+   \includegraphics[width=0.3\textwidth]{BTG_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{BTG_MSD.pdf}
+  \end{center}
+\caption{\label{fig:BC1_TG} A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$.
+The result indicates that the highest flow strength ($V_0=0.2$) makes the vesicle (top row) rupture within a short period of time and the energy rapidly increases.
+As expected, the local order parameter drops and the MSD increases.
+For bilayer structure (bottom row), for $V_0=0.15$ and $V_0 = 0.2$, the energy gradually increases over the time but the other two measures do not have  a clear trend.}
 \end{figure}
@@
 
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{VTG_Len.pdf}
+  \includegraphics[width=0.4\textwidth]{VTG_Area.pdf}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:VTG_AreaLen} Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied.
+The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations.
+}
+\end{figure}
+
 \subsection{Boundary condition (ii):  multilamellar configurations}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
+  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
+  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
+    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:BC2_shear_flow} Multi-lamellar stracture in shear flows.
+The insets of Fig~\ref{fig:relax}c is used for panels (a).
+Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=500$, respecitively.
+The streamlines are plotted in the background.}
+\end{figure}
 
@@
 Moreover, all three measure show that the energy, orderparameter, and MSD increase as shear rate increases.}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
-  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
-  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:BC2_shear_flow} Multi-lamellar stracture in shear flows.
-The insets of Fig~\ref{fig:relax}c is used for panels (a).
-Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=500$, respecitively.
-The streamlines are plotted in the background.}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{MTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{MTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{MTG_MSD.pdf}
-  \end{center}
-    \caption{\label{fig:BC2_TG}  A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$.
-The energy profile when $V_0=0.2$ has an increasing trend that results a large deformation after a period of time.
-Since the flow strengths for all cases are not strong enough, the convergent MSD represents that the rupture does not occur before $t=1000$.}
 \end{figure}
@@
 
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{MTG_E.pdf}
+   \includegraphics[width=0.3\textwidth]{MTG_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{MTG_MSD.pdf}
+  \end{center}
+    \caption{\label{fig:BC2_TG}  A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$.
+The energy profile when $V_0=0.2$ has an increasing trend that results a large deformation after a period of time.
+Since the flow strengths for all cases are not strong enough, the convergent MSD represents that the rupture does not occur before $t=1000$.}
+\end{figure}
+
 \subsection{Boundary condition (iii): striated configurations}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.22\textwidth]{CS_0.pdf}
+  \includegraphics[width=0.22\textwidth]{CS_1.pdf}
+  \includegraphics[width=0.22\textwidth]{CS_2.pdf} 
+    \includegraphics[width=0.22\textwidth]{CS_3.pdf} 
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:BC3_shear_flow} A striated configuration in shear flows where the streamlines are plotted in the background.
+Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$ at $t=100$, respectively.
+  }
+\end{figure}
 
@@
   \begin{center}
-  \includegraphics[width=0.22\textwidth]{CS_0.pdf}
-  \includegraphics[width=0.22\textwidth]{CS_1.pdf}
-  \includegraphics[width=0.22\textwidth]{CS_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{CS_3.pdf} 
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:BC3_shear_flow} A striated configuration in shear flows where the streamlines are plotted in the background.
-Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$ at $t=100$, respectively.
-  }
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{CTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{CTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{CTG_MSD.pdf}
-  \end{center}
-\caption{\label{fig:BC3_TG} A striated configuration in Taylor-Green flows with flow strengths $V_0=\{0.2, 0.25, 0.3\}$.   }
-\end{figure}
-
-\begin{figure}
-  \begin{center}
   \includegraphics[width=0.22\textwidth]{CTG_0.pdf}
@@
 }
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{CTG_E.pdf}
+   \includegraphics[width=0.3\textwidth]{CTG_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{CTG_MSD.pdf}
+  \end{center}
+\caption{\label{fig:BC3_TG} A striated configuration in Taylor-Green flows with flow strengths $V_0=\{0.2, 0.25, 0.3\}$.   }
 \end{figure}

### 2022-06-29 doc/PRF2022/PRF_main.tex
yny

--- 2022-06-26 doc/PRF2022/PRF_main.tex
@@
 %\section{\label{}}
+Janus particles are colloids with two surfaces of different properties such as hydrophobicity. For example, it is common for the surface of a Janus particle to
+be partly hydrophilic and hydrophobic (polar and non-polar).
+In a viscous solvent Janus particles often self-assemble into structures with tunable functions for biomedical engineering applications \cite{GheisariSahfieeAbbasiEtAl2021_DMR,LiuYangHuangEtAl2016_Angew,LiWangYaoEtAl2019_Nanoscale}.
+Depending on the interactions between Janus particles and the surrounding viscous solvent, JPs self-assemble into oligomers of various geometries and sizes.
+
+{\bf The following paragraph needs to be rephrased and inserted in the introduction.
+"Dynamics offers yet another dimension of control that emerges naturally from the interactions between particles and fluid in colloidal matter.
+....Such active colloidal systems show nonequilibrium self-organization with complexity rivaling that of biological systems such as living cells, bacterial baths, and animal flocks.....long-standing challenges such as the ``inverse" problem of creating a colloidal system that will self-assemble into a prescribed structure.....the framework of geometrical frustration, which has been used to explain dis-ordered systems, could be used to design new ones instead, through specific choices for the shapes or interactions of the particles....\cite{Manoharan2015_Science}"}
+
 The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using

### 2022-06-30 doc/PRF2022/PRF_main.tex
updated figures

--- 2022-06-26 doc/PRF2022/PRF_main.tex
@@
 \begin{center}
+  \hspace{-1cm}
   \includegraphics[height=0.27\textheight]{Nb198a_inset.pdf}
+  \hspace{-0.85cm}
   \includegraphics[height=0.27\textheight]{Nb198b_eta_inset.pdf}\\
-  \hspace{1.55cm}
   \includegraphics[height=0.27\textheight]{Nb198c_eta_inset.pdf}
@@
 %  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
-\includegraphics[width=0.49\textwidth]{relax_E.pdf}
-\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
+%\includegraphics[width=0.49\textwidth]{relax_E.pdf}
+%\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
+\includegraphics[width=1.0\textwidth]{relax_E_LOP.pdf}
   \end{center}
@@
     The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
-    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=600$).
+    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=500$).
 The streamlines are plotted in the background.
+}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
+      \includegraphics[width=0.3\textwidth]{BS_E.pdf}
+   \includegraphics[width=0.3\textwidth]{BS_LOP.pdf}
+    \includegraphics[width=0.3\textwidth]{BS_MSD.pdf}
+  \end{center}
+  \caption{
+    \label{fig:BC1_shear}
+    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$.
+Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$.
+The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures.
+For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows.
+The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
      }
@@
 
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.4\textwidth]{VTG_Len.pdf}
+  \includegraphics[width=0.4\textwidth]{VTG_Area.pdf}
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:VTG_AreaLen} Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied.
+The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations.
+}
+\end{figure}
+
 \subsection{Boundary condition (ii):  multilamellar configurations}
+
+\begin{figure}
+  \begin{center}
+  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
+  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
+  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
+    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:BC2_shear_flow} Multi-lamellar stracture in shear flows.
+The insets of Fig~\ref{fig:relax}c is used for panels (a).
+Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=600$, respecitively.
+The streamlines are plotted in the background.}
+\end{figure}
 

### 2022-06-30 doc/PRF2022/PRF_main.tex

--- 2022-06-29 doc/PRF2022/PRF_main.tex
@@
     The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
-    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=600$).
+    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=500$).
 The streamlines are plotted in the background.
@@
 The insets of Fig~\ref{fig:relax}c is used for panels (a).
-Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=500$, respecitively.
+Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=600$, respecitively.
 The streamlines are plotted in the background.}

### 2022-07-04 doc/PRF2022/PRF_main.tex

@@
   \hspace{-1cm}
-  \includegraphics[height=0.27\textheight]{Nb198a_inset.pdf}
+  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
   \hspace{-0.85cm}
-  \includegraphics[height=0.27\textheight]{Nb198b_eta_inset.pdf}\\
-  \includegraphics[height=0.27\textheight]{Nb198c_eta_inset.pdf}
-  \includegraphics[height=0.27\textheight]{Nb198d_eta_inset.pdf}
+  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
+  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
+  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
 \end{center}
@@
   Panel (a) shows $N_b = 198$ particles confined to a square with random 
-  positions and orientation.
+  positions and orientation and the inset shows $N_b=60$ particles configuration.
   Depending on the boundary condition \eqref{eq:bc-type},
@@
   The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
-    All figure insets are configurations using $N_b=60$ sharing with the same color map.}
+ Panel (b)--(d) insets are configurations using $N_b=60$ sharing with the same color map.}
 \end{caption}
@@
   \caption{\label{fig:relax_energy}
-  A:  The free energy \eqref{eq:free_energy} is decreasing
+  A:  The free energy \eqref{eq:free_energy} decreases
     in the mobility problem formulation.  The initial energies
@@
     and the final energies are for the near-equilibrium
-    configurations Figure \ref{fig:relax}b--c, respectively. 
-    The red curves are the energies for the $N_b = 198$ cases normalized
+    configurations as shown in Figure \ref{fig:relax}b--d, respectively.
+    The black curves are the energies for the $N_b=60$ cases and  
+    the red curves are the energies for the $N_b = 198$ cases normalized
     by $60/198$, showing that the energy approximately scales with the number of
-    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. The near-equilibrium configurations depend on the initial configuration and the results show that 
-    the striated configurations have largest value of order parameter for both $N_b=60$ and $N_b=198$ cases.
+    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. 
+    The curve styles are identical to the ones in panel A.
+    The near-equilibrium configurations depend on the initial configuration and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trend in self-assembly in term of the local order parameter.
+The results of the striated configuration depend on the initial setup.
   }

### 2022-07-07 doc/PRF2022/PRF_main_fig_revis.tex
revised figures

--- 2022-07-04 doc/PRF2022/PRF_main.tex
@@
 \begin{center}
-  \hspace{-1cm}
   \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
-  \hspace{-0.85cm}
   \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
@@
 %\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
-\includegraphics[width=1.0\textwidth]{relax_E_LOP.pdf}
+\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
   \end{center}
@@
 
-The Euclidian distance matrix is the $N_b \times N_b$ matrix 
-$[D(t)]_{ij} = \|\aa_{i} - \aa_{j}\|$ for $i, j = 1, \dots, N_b$
-To measure positional order, we use
-\begin{equation}
-\label{eq:EDM}
-d(t) = \frac{1}{N_b^2}\|D(t) - D(0)\|
-\end{equation}
-where $\| \cdot \|$ is the Frobeneous norm.
-For weak background flow strengths, the deformation in particle
-configurations will be relatively small and the collection of
-particles behaves as a rigid body i.e., $d(t) \ll 1$.
+To measure positional order, we use a strain parameter 
+\begin{equation}
+\label{eq:SP}
+E(t) = \frac{1}{N_b} \sum_{i=1}^{N_b} \|E_i\|
+\end{equation}
+where $E_i = \tfrac{1}{2}(F_i^TF_i - I)$ is a Green-Lagrange strain tensor and $F_i$
+is an approximate deformation gradient at particle $i$; $\| \cdot \|$ is the Frobeneous norm.
+The motivation for  \eqref{eq:SP} is that 
+for relatively weak background flow strengths, the near-equilibrium particle
+collections behave as a solid and $E(t)$ is close to zero.
+More generally, the Green-Lagrange strain tensor $E_i$ 
+can be used to encode the energy of elastic deformations from the reference (equilibrium)
+to deformed configuration and $E(t)$ gives a sense of how significant these deformations
+may be.  Lacking a map from the reference state, 
+we approximate a deformation gradient $F_i$ using weighted least squares for the system 
+\[
+F_i(\aa_j(t) - \aa_i(t)) = \aa_j(0) - \aa_i(0),\quad j = 1,\dots, N_b  
+\]
+with weights $w_i = \exp(-\|\aa_j(t) - \aa_i(t)\|/4c)$ where $c$ is particle radius.
 
@@
   \begin{center}
-      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
-      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
-   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
-   \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
-         \includegraphics[width=0.22\textwidth]{BS_0.pdf}
-      \includegraphics[width=0.22\textwidth]{BS_1.pdf}
-   \includegraphics[width=0.22\textwidth]{BS_2.pdf}
-   \includegraphics[width=0.22\textwidth]{BS_3.pdf}
+   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
 %   Panels (e)-(f) same but for non-vesicle initial configuration
@@
   \begin{center}
-  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
-      \includegraphics[width=0.3\textwidth]{BS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{BS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{BS_MSD.pdf}
+    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.22\textwidth]{VTG_0.pdf}
-  \includegraphics[width=0.22\textwidth]{VTG_1.pdf}
-  \includegraphics[width=0.22\textwidth]{VTG_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{VTG_3.pdf} \\
-      \includegraphics[width=0.22\textwidth]{BTG_0.pdf}
-  \includegraphics[width=0.22\textwidth]{BTG_1.pdf}
-  \includegraphics[width=0.22\textwidth]{BTG_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{BTG_3.pdf}
+    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}\\
-  \includegraphics[width=0.3\textwidth]{BTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{BTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{BTG_MSD.pdf}
+    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.22\textwidth]{VTG_Scale_0.pdf}
-  \includegraphics[width=0.22\textwidth]{VTG_Scale_1.pdf}
-  \includegraphics[width=0.22\textwidth]{VTG_Scale_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{VTG_Scale_3.pdf}
+\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.4\textwidth]{VTG_Len.pdf}
-  \includegraphics[width=0.4\textwidth]{VTG_Area.pdf}
+\includegraphics[width=1.0\textwidth]{Figures/Figure8.pdf}
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
-  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
-  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
+\includegraphics[width=1.0\textwidth]{Figures/Figure9.pdf}    
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.3\textwidth]{MS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{MS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{MS_MSD.pdf}
+\includegraphics[width=1.0\textwidth]{Figures/Figure10.pdf}        
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.22\textwidth]{MTG_0.pdf}
-  \includegraphics[width=0.22\textwidth]{MTG_1.pdf}
-  \includegraphics[width=0.22\textwidth]{MTG_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{MTG_3.pdf} 
+\includegraphics[width=1.0\textwidth]{Figures/Figure11.pdf}            
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.3\textwidth]{MTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{MTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{MTG_MSD.pdf}
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.22\textwidth]{CS_0.pdf}
-  \includegraphics[width=0.22\textwidth]{CS_1.pdf}
-  \includegraphics[width=0.22\textwidth]{CS_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{CS_3.pdf} 
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.3\textwidth]{CS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{CS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{CS_MSD.pdf}
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.22\textwidth]{CTG_0.pdf}
-  \includegraphics[width=0.22\textwidth]{CTG_1.pdf}
-  \includegraphics[width=0.22\textwidth]{CTG_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{CTG_3.pdf} 
   \end{center}
@@
   \begin{center}
-  \includegraphics[width=0.3\textwidth]{CTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{CTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{CTG_MSD.pdf}
   \end{center}
@@
 \section{Discussion}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_Energy_LsFs}
-    \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_MSD_LsFs}
-  \end{center}
-    \caption{\label{fig:BC2_tests} A multi-lamellar structure in a shear flow when the shear rate is $\dot\gamma=0.1$.
-We tune the length scale parameters, radius, $\rho$ and $\rho_0$, by $\pm 5\%$ and the force scale parameters, $\gamma$ and $M$, by $\pm 5\%$.
-}
-\end{figure}
 

### 2022-07-08 doc/PRF2022/PRF_main.tex

@@
 % insert abstract here
-%
-%{\bf To do list:}
-%
-%Unbouned Flow: 
-%\begin{enumerate}
-%\item $N_b=60$ self-assembly/relaxation runs with all 3 boundary
-%  conditions using $N=24$ points per particle (FIG. 2). Energy profiles
-%    in a log-log plot (FIG. 3) ($E(t)$ or $\Delta E(t)$ v.s. time).
-%
-%\item $N_b=198$ relaxation runs with all 3 boundary conditions using $N=24$ points per particle.
-%Add energy profiles to check local/absolute minimum. Superimpose these
-%    energies on Figure 3, but scale the energies by the number of Janus
-%    particles so that it is ``energy per particle"
-%
-%\item $N_b=60$ structures in a shear flow: For both boundary conditions, lamellar (FIG. 4) and polar (FIG. 5), convergence tests using $N=16$ and $N=24$ are not yet verified. 
-%Compare results using $N_b=24$ with the current FIG 4. (d). Revise FIG. 5 with more details. 
-%
-%\item Use particle/checker board alignment and/or aspect ratio to identify the critical shear rate for phase separation.
-%
-%\item $N_b=60$ structures in a Taylor-Green flow (FIG. 7-8). Add more frames for further comparison between values of flow strength $V_0$.
-%\end{enumerate}
-%
-%
-%{\bf May do list:}
-%Channel Flow: 
-%\begin{enumerate}
-%\item Convergence tests for $N_b=25$ vesicle in a narrow channel.  Add energy profile.
-%
-%\item Convergence tests for $N_b=40$ multi-lamellar structure in a narrow channel. Add energy profile.
-%
-%\end{enumerate}
-
 \end{abstract}
+
+%%%
 
@@
 To see the effect of the shift parameter $b$, we simulate the dynamics of
-198 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
+198 particles and 60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
 Three distinct configurations emerge:
@@
 
+Figure~\ref{fig:relax}a shows the initial configurations with orientations of 198-particle and 60- particle cases. 
 Case (i) with $b = 1$, mimicks an amphiphilic particle.
@@
 The interaction is attractive, and particles collectively orient their
-hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)).
+hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)). The inset shows the equilibrium 
+state for 60-particle run that forms multiple bilayers with a vesicle like structure.
 
@@
 forming multilamella structures. Figure~\ref{fig:relax}(c), for example, shows a
-multilamellar structure with 2 layers.
+multilamellar structure with multiple layers.
 At equilibrium, the number of folds depends primarily on the number of particles.
+In addition, the inset provides a 3-fold structure when there are 60 particles.
 
@@
 where the particles lie on a 
-grid and the orientations alternate between layers (Figure~\ref{fig:relax}(d)).
+grid and the orientations alternate between layers (Figure~\ref{fig:relax}(d)). We observe that 
+when the number of particles is fewer, there is only single alternating pattern in particle orientations. Larger number of particles results two different patterns as shown in the figure.
 
@@
 
-\begin{figure}
-  \begin{center}
-%  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
-%\includegraphics[width=0.49\textwidth]{relax_E.pdf}
-%\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
-\includegraphics[width=1.0\textwidth]{relax_E_LOP.pdf}
+\section{Measuring deformation}
+We use the free energy $F$,
+a Euclidean distance-based measure $d(t)$,
+and a scalar order parameter $S_{2}(t)$ to measure
+the deformation of particle configurations under background flows.
+
+First, we must simplify the
+form of the free energy \eqref{eq:free_energy}
+using integration by parts and \eqref{eq:SL}
+to obtain
+\begin{equation}
+\label{eq:free_energy2}
+F[u] = -\gamma
+\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
++ \frac{M}{2}
+\sum_{j \neq i} 
+P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
+\end{equation}
+%
+Here, we have substituted $g$ for $u$ since the boundary values are given.
+However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
+involves calculating a quadruple layer potential which has a
+well-known obstacle in numerical implementation.
+To overcome this obstacle, we use
+%
+\begin{equation}
+\label{eq:normal_deriv}
+\nabla u(\xx) \cdot \nnu(\xx)=
+%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
+-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
++ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
+\end{equation}
+%
+Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
+See the Appendix section \ref{sec:appendix} for the proof and details.
+Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
+leads to single layer integral which is more straightforward to evaluate and we compute the
+arclength derivative using spectrally accurate Fourier transform.
+We have validated the form of \eqref{eq:normal_deriv} by extrapolating 
+the primal energy \eqref{eq:free_energy} along test curves placed slightly
+outside the particles.
+
+To measure positional order, we use a strain parameter 
+\begin{equation}
+\label{eq:SP}
+E(t) = \frac{1}{N_b} \sum_{i=1}^{N_b} \|E_i\|
+\end{equation}
+where $E_i = \tfrac{1}{2}(F_i^TF_i - I)$ is a Green-Lagrange strain tensor and $F_i$
+is an approximate deformation gradient at particle $i$; $\| \cdot \|$ is the Frobeneous norm.
+The motivation for  \eqref{eq:SP} is that 
+for relatively weak background flow strengths, the near-equilibrium particle
+collections behave as a solid and $E(t)$ is close to zero.
+More generally, the Green-Lagrange strain tensor $E_i$ 
+can be used to encode the energy of elastic deformations from the reference (equilibrium)
+to deformed configuration and $E(t)$ gives a sense of how significant these deformations
+may be.  Lacking a map from the reference state, 
+we approximate a deformation gradient $F_i$ using weighted least squares for the system 
+\[
+F_i(\aa_j(t) - \aa_i(t)) = \aa_j(0) - \aa_i(0),\quad j = 1,\dots, N_b  
+\]
+with weights $w_i = \exp(-\|\aa_j(t) - \aa_i(t)\|/4c)$ where $c$ is particle radius.
+
+To study orientational order, we use the scalar order parameter 
+\begin{equation}
+  \label{eq:S2}
+S_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
+\end{equation}
+Here $\bar \theta$ is a circular mean defined as the
+orientation of the largest eigenvalue eigenvector of 
+$\dd_1\dd_1^\top + \dots + \dd_{N_b}\dd_{N_b}^\top$.
+A value $S_2(t) = 1$ indicates a complete orientational
+order where all particle directors lie on a common axis e.g.,
+two parallel vectors with possibly opposite direction are ordered. 
+A value far from 1 indicates disorder.
+
+The measure $S_2$ is an inadequate for the bilayer and
+multilamellar structures.  For example, the directors of a circular
+bilayer vesicle are uniformly distributed along a circle, even though
+there is a strong orientational order between neighboring particles.
+To account for these latter cases, we use
+\begin{equation}
+  \label{eq:localS2}
+\tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
+\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1).
+\end{equation}
+where $\bar \theta_i$ is the circular mean restricted to particles
+indexed by $j$ for which $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle is
+isolated and has no neighbors within a distance $4c$, then we exclude it from
+the sum \eqref{eq:localS2}.
+
+\begin{figure}
+  \begin{center}
+\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
   \end{center}
@@
 
-\section{Measuring deformation}
-We use the free energy $F$,
-a Euclidean distance-based measure $d(t)$,
-and a scalar order parameter $S_{2}(t)$ to measure
-the deformation of particle configurations under background flows.
-
-First, we must simplify the
-form of the free energy \eqref{eq:free_energy}
-using integration by parts and \eqref{eq:SL}
-to obtain
-\begin{equation}
-\label{eq:free_energy2}
-F[u] = -\gamma
-\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
-+ \frac{M}{2}
-\sum_{j \neq i} 
-P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
-\end{equation}
-%
-Here, we have substituted $g$ for $u$ since the boundary values are given.
-However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
-involves calculating a quadruple layer potential which has a
-well-known obstacle in numerical implementation.
-To overcome this obstacle, we use
-%
-\begin{equation}
-\label{eq:normal_deriv}
-\nabla u(\xx) \cdot \nnu(\xx)=
-%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
--\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
-+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
-\end{equation}
-%
-Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
-See the Appendix section \ref{sec:appendix} for the proof and details.
-Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
-leads to single layer integral which is more straightforward to evaluate and we compute the
-arclength derivative using spectrally accurate Fourier transform.
-We have validated the form of \eqref{eq:normal_deriv} by extrapolating 
-the primal energy \eqref{eq:free_energy} along test curves placed slightly
-outside the particles.
-
-The Euclidian distance matrix is the $N_b \times N_b$ matrix 
-$[D(t)]_{ij} = \|\aa_{i} - \aa_{j}\|$ for $i, j = 1, \dots, N_b$
-To measure positional order, we use
-\begin{equation}
-\label{eq:EDM}
-d(t) = \frac{1}{N_b^2}\|D(t) - D(0)\|
-\end{equation}
-where $\| \cdot \|$ is the Frobeneous norm.
-For weak background flow strengths, the deformation in particle
-configurations will be relatively small and the collection of
-particles behaves as a rigid body i.e., $d(t) \ll 1$.
-
-To study orientational order, we use the scalar order parameter 
-\begin{equation}
-  \label{eq:S2}
-S_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
-\end{equation}
-Here $\bar \theta$ is a circular mean defined as the
-orientation of the largest eigenvalue eigenvector of 
-$\dd_1\dd_1^\top + \dots + \dd_{N_b}\dd_{N_b}^\top$.
-A value $S_2(t) = 1$ indicates a complete orientational
-order where all particle directors lie on a common axis e.g.,
-two parallel vectors with possibly opposite direction are ordered. 
-A value far from 1 indicates disorder.
-
-The measure $S_2$ is an inadequate for the bilayer and
-multilamellar structures.  For example, the directors of a circular
-bilayer vesicle are uniformly distributed along a circle, even though
-there is a strong orientational order between neighboring particles.
-To account for these latter cases, we use
-\begin{equation}
-  \label{eq:localS2}
-\tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
-\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1).
-\end{equation}
-where $\bar \theta_i$ is the circular mean restricted to particles
-indexed by $j$ for which $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle is
-isolated and has no neighbors within a distance $4c$, then we exclude it from
-the sum \eqref{eq:localS2}.
+Figure~\ref{fig:relax_energy}a tracks the free energy profiles for all relaxation runs.
+For 198-particle cases, we normalized the energies by 60/198 and the results show that all energies decrease with good agreements in all boundary conditions.
+Figure~\ref{fig:relax_energy}b
+measures the orientational order parameter $\tilde{S}_2$. Both bilayer and multilamellar 
+structures have similar trends in small and large systems. The aggregation for striated configurations may have a significant difference when the number of particles is varied.
+
+%%%%%%%
 
@@
 
-\begin{figure}
-  \begin{center}
-      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
-      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
-   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
-   \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
-         \includegraphics[width=0.22\textwidth]{BS_0.pdf}
-      \includegraphics[width=0.22\textwidth]{BS_1.pdf}
-   \includegraphics[width=0.22\textwidth]{BS_2.pdf}
-   \includegraphics[width=0.22\textwidth]{BS_3.pdf}
-%   Panels (e)-(f) same but for non-vesicle initial configuration
+%%%
+
+\subsection{Boundary condition (i):   bilayer configurations}
+
+\begin{figure}
+  \begin{center}
+   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
   \end{center}
   \caption{
-    \label{fig:BC1_shear_flow}
+    \label{fig:BC1_shear}
     The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
@@
 
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
-      \includegraphics[width=0.3\textwidth]{BS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{BS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{BS_MSD.pdf}
+The bilayer is subject to a shear background flow
+\begin{equation}
+\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
+\end{equation}
+%
+where $\dot\gamma$ is the shear rate. 
+Figure~\ref{fig:BC1_shear} (a)--(c)
+shows snapshots of the vesicle when $\dot\gamma= 0.05,0.075,0.01$.
+The free energies (Figure~\ref{fig:BC1_shear}d) are relatively constant and 
+lower shear rate results a smaller orientational parameter (Figure~\ref{fig:BC1_shear}e). The supplementary movies show that these bilayers merge and form a work-like shape in higher 
+shear flows. Figure~\ref{fig:BC1_shear}f shows that the strain parameter diverges when 
+the shear rate is large enough.
+
+%%%
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
   \end{center}
   \caption{
-    \label{fig:BC1_shear}
+    \label{fig:Ves_shear}
     Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$.
@@
 
-\subsection{Boundary condition (i):   bilayer configurations}
-The vesicle in a shear flow undergoes the familiar tank-treading deformation.
+In Figure~\ref{fig:Ves_shear} (a)--(c), the vesicle in a shear flow undergoes the familiar tank-treading deformation. 
 Our previous paper \cite{Fu2022_JFM} studied the geometry,
-intermonolayer slip, and critical shear rates $\gamma^*$
+intermonolayer slip, and critical shear rates $\gamma^*=0.066$
 for vesicles comprised of amphiphilic Janus particles. 
-
-The vesicle is subject to a shear background flow
-\begin{equation}
-\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
-\end{equation}
-%
-where $\dot\gamma$ is the shear rate. Figure~\ref{fig:shear_1} (a)--(c)
-shows snapshots of the vesicle when $\dot\gamma= ... $ is
-below the critical shear rate $\dot \gamma_* = ...$
-Here, the free energy and order parameter are more or less constant
-(Figure \ref{fig:BC1_shear}ab, solid curves).  The is a slight upward shift
-in $d(t)$ (Figure \ref{fig:BC1_shear}c, solid curve) due to relative
-displacement as the two leaflets slide past one another.
-
-%\begin{figure}
-%\caption{\label{fig:ves_shear} A vesicle in shear flow}
-%\end{figure}
-%\begin{figure}
-%\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
-%\end{figure}
-
-In, Figure~\ref{fig:shear_2} (a)--(c), 
-$\dot\gamma= ...$ is above the critical shear rate,
-and there is a jump in energy (Figure \ref{fig:BC1_shear}a, dashed curve)
-due to the breaking of the vesicle into two components.  
-There is greater variation in the order parameter $\tilde{S}_2(t)$ as well
+Here $\dot\gamma=0.05, 0.066, 0.075$ and there are jumps in energies (Figure \ref{fig:Ves_shear}d, long and short dashed curves) due to the breaking of the vesicle into two
+components. There is greater variation in the order parameter $\tilde{S}_2(t)$ as well
 with a baseline value around $0.7$
-(Figure \ref{fig:BC1_shear}b, dashed curve).The oscillations occur due to the
-orbit of the two bilayer components, and $\tilde{S}_2(t)$ increases
-to about $0.9$ when the components are nearly parallel and slide past one another.
+(Figure \ref{fig:Ves_shear}e, dashed curve).
+The oscillations occur due to the orbit of the two bilayer components, and $\tilde{S}_2(t)$ increases to about $0.9$ when the components are nearly parallel and slide past one another.
+For the lowest shear rate case, it has nearly perfect orientational parameter due to the steady tank-treading motion.
 Positional order, however, diverges since the two component configuration
-is uncorrelated to the initial circular configuration (Figure \ref{fig:BC1_shear}c, dashed curve).
-
-%
+is uncorrelated to the initial circular configuration (Figure \ref{fig:Ves_shear}f, dashed curve).
+
+%%%%%%%
 
@@
 \begin{equation}
+\label{eq:tg_flow}
   \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
@@
 \end{equation}
-where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
-%
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.22\textwidth]{VTG_0.pdf}
-  \includegraphics[width=0.22\textwidth]{VTG_1.pdf}
-  \includegraphics[width=0.22\textwidth]{VTG_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{VTG_3.pdf} \\
-      \includegraphics[width=0.22\textwidth]{BTG_0.pdf}
-  \includegraphics[width=0.22\textwidth]{BTG_1.pdf}
-  \includegraphics[width=0.22\textwidth]{BTG_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{BTG_3.pdf}
+where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. The default parameter
+$l=2$ is used through this work.
+%
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
   \end{center}
   \vspace{-20pt}  
-  \caption{\label{fig:BC1_TG_flow} The figure shows a vesicle in Taylor-Green flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=600$) 
+  \caption{\label{fig:BC1_TG} The figure shows a vesicle in Taylor-Green flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=600$) 
     and the multiple component bilayers in Taylor-Green flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=200$).
@@
 
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}\\
-  \includegraphics[width=0.3\textwidth]{BTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{BTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{BTG_MSD.pdf}
-  \end{center}
-\caption{\label{fig:BC1_TG} A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$.
+Figure~\ref{fig:BC1_TG}a--c are the snapshots when $V_0=0.1,0.15,0.2$, respectively.
+This initial configuration in TG flow encounters a number of fusion but there is no clear trend for
+all measures with respect to the flow strengths.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
+  \end{center}
+\caption{\label{fig:ves_TG} A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$.
 The result indicates that the highest flow strength ($V_0=0.2$) makes the vesicle (top row) rupture within a short period of time and the energy rapidly increases.
@@
 
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.22\textwidth]{VTG_Scale_0.pdf}
-  \includegraphics[width=0.22\textwidth]{VTG_Scale_1.pdf}
-  \includegraphics[width=0.22\textwidth]{VTG_Scale_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{VTG_Scale_3.pdf}
+For a vesicle in a Taylor-Green flow, Figure~\ref{fig:ves_TG}a--c are configurations at $t=0.2 \mu$s where $V_0=0.1,0.15,0.2$.
+Figure~\ref{fig:ves_TG}d--f indicates that the rupture occurs when the energy and strain parameter are significant larger and the orientational parameter is much lower than other cases.
+
+\begin{figure}
+  \begin{center}
+\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
   \end{center}
   \vspace{-20pt}  
-  \caption{\label{fig:BTG_Scale_flow} With $V_0=0.1$, panels (a)-(d) show the configurations with streamlines when a vesicle is in Taylor-Green flow at $t=1000$ and $l= 1,2,3,4$, respectively.}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.4\textwidth]{VTG_Len.pdf}
-  \includegraphics[width=0.4\textwidth]{VTG_Area.pdf}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:VTG_AreaLen} Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied.
+  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)-(d) show the configurations with streamlines when a vesicle is in Taylor-Green flow at $t=1000$ and $l= 1,2,3,4$, respectively.
+  Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied.
 The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations.
@@
 
+We vary the cell size by tuning the parameter $l$ in \eqref{eq:tg_flow}.
+Figure~\ref{fig:BTG_Scale}a--d show the deformation of a vesicle in a Taylor-Green flow when $V_0=0.1$ and arrows indicate rotating directions.
+Figure~\ref{fig:BTG_Scale}e presents that the area $A/A_0$ decreases during the simulations and the inset shows constant total lengths $L/L_0$ for all cases where $A_0$ and $L_0$ are initial enclose area and midplane length.
+%A/A0 plot with no monotonic trend.
+One interesting finding is that the number of cells affects the directions of structure rotation.
+
+%%%
+
 \subsection{Boundary condition (ii):  multilamellar configurations}
@@
   \begin{center}
-  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
-  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
-  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
+\includegraphics[width=1.0\textwidth]{Figures/Figure8.pdf}
   \end{center}
   \vspace{-20pt}  
-  \caption{\label{fig:BC2_shear_flow} Multi-lamellar stracture in shear flows.
+  \caption{\label{fig:BC2_shear}   Multi-lamellar stracture in shear flows.
 The insets of Fig~\ref{fig:relax}c is used for panels (a).
 Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=600$, respecitively.
-The streamlines are plotted in the background.}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{MS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{MS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{MS_MSD.pdf}
-  \end{center}
-      \caption{\label{fig:BC2_shear} 
+The streamlines are plotted in the background.
 A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$.
 For this set of simulations, the local order parameter is a good indicator for tracking the rupture or structure separations.
-Moreover, all three measure show that the energy, orderparameter, and MSD increase as shear rate increases.}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.22\textwidth]{MTG_0.pdf}
-  \includegraphics[width=0.22\textwidth]{MTG_1.pdf}
-  \includegraphics[width=0.22\textwidth]{MTG_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{MTG_3.pdf} 
+Moreover, all three measure show that the energy, orderparameter, and MSD increase as shear rate increases.
+       }
+\end{figure}
+
+We place a 60-particle multilamellar configuration (inset of Figure~\ref{fig:BC2_shear}a) in shear flows where $\dot\gamma=0.05, 0.1, 0.15$.
+Quantities such as energies, orientational parameter, and positional parameter (Figure~\ref{fig:BC2_shear}d--f) follow the same trend where they increases as shear rate increases.
+Comparing with bilayer structures, Figure~\ref{fig:BC2_shear}a--c demonstrate that the multilamellar ones are more rigid in shear flow and the rupture phenomenon can be observed 
+when the shear rate is high enough.
+
+\begin{figure}
+  \begin{center}
+\includegraphics[width=1.0\textwidth]{Figures/Figure9.pdf}    
   \end{center}
   \vspace{-20pt}  
-  \caption{\label{fig:BC2_TG_flow} Multi-lamellar stracture in Taylor-Green flows.
+  \caption{\label{fig:BC2_TG} Multi-lamellar stracture in Taylor-Green flows.
 The insets of Fig~\ref{fig:relax}c is used for panels (a).
@@
 The streamlines are plotted in the background.
+A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$.
+The energy profile when $V_0=0.2$ has an increasing trend that results a large deformation after a period of time.
+Since the flow strengths for all cases are not strong enough, the convergent MSD represents that the rupture does not occur before $t=1000$.
   }
@@
 
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{MTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{MTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{MTG_MSD.pdf}
-  \end{center}
-    \caption{\label{fig:BC2_TG}  A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$.
-The energy profile when $V_0=0.2$ has an increasing trend that results a large deformation after a period of time.
-Since the flow strengths for all cases are not strong enough, the convergent MSD represents that the rupture does not occur before $t=1000$.}
-\end{figure}
+For multilamellar structure in a Taylor-Green flow, as shown in Figure~\ref{fig:BC2_TG}a--b, lower flow strengths such as $V_0=0.1,0.15$ do not reach a critical flow rate for structural disorder. 
+When $V_0=0.2$ (Figure~\ref{fig:BC2_TG}c), the flow is strong enough to separate the structure
+into multiple groups within the cells. In all deformation measures, a similar trend in shear flow case is observed, see Figure~\ref{fig:BC2_TG}d--f.
+
+%%%
 
@@
   \begin{center}
-  \includegraphics[width=0.22\textwidth]{CS_0.pdf}
-  \includegraphics[width=0.22\textwidth]{CS_1.pdf}
-  \includegraphics[width=0.22\textwidth]{CS_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{CS_3.pdf} 
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:BC3_shear_flow} A striated configuration in shear flows where the streamlines are plotted in the background.
+\includegraphics[width=1.0\textwidth]{Figures/Figure10.pdf}        
+  \end{center}
+      \caption{\label{fig:BC3_shear}  A striated configuration in shear flows where the streamlines are plotted in the background.
 Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$ at $t=100$, respectively.
-  }
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{CS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{CS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{CS_MSD.pdf}
-  \end{center}
-\caption{\label{fig:BC3_shear} A striated configuration in shear flows with shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$.
+       A striated configuration in shear flows with shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$.
 The energy profile, order parameter, and MSD for the case $\dot\gamma=0.15$ show that a rupture occurs during the simulation.
@@
 
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.22\textwidth]{CTG_0.pdf}
-  \includegraphics[width=0.22\textwidth]{CTG_1.pdf}
-  \includegraphics[width=0.22\textwidth]{CTG_2.pdf} 
-    \includegraphics[width=0.22\textwidth]{CTG_3.pdf} 
+We place the striated configuration in a shear flow when $\dot\gamma=0.1, 0.125, 0.15$ and 
+the snapshots at $t=0.1 \mu$s are shown in Figure~\ref{fig:BC3_shear}a--c.
+Break-up deformation measures (igure~\ref{fig:BC3_shear}d--f) are similar to vesicle in shear flow case.
+Notably, for low shear rates, oscillatory behaviours are investigated in energies, orientational and positional parameters.
+
+\begin{figure}
+  \begin{center}
+\includegraphics[width=1.0\textwidth]{Figures/Figure11.pdf}            
   \end{center}
   \vspace{-20pt}  
-  \caption{\label{fig:BC3_TG_flow}  A striated configuration in shear flows where the streamlines are plotted in the background.
-Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the flow strengths $V_0=\{0.2, 0.25, 0.3\}$ at $t=400$, respectively.
-.
-}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{CTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{CTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{CTG_MSD.pdf}
-  \end{center}
-\caption{\label{fig:BC3_TG} A striated configuration in Taylor-Green flows with flow strengths $V_0=\{0.2, 0.25, 0.3\}$.   }
-\end{figure}
+  \caption{\label{fig:BC3_TG} A striated configuration in Taylor-Green flows where the streamlines are plotted in the background.
+Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the flow strengths $V_0=\{0.2, 0.25, 0.3\}$ at $t=400$, respectively.}
+\end{figure}
+
+For a striated configuration in a Taylor-Green flow, numerical experiments have shown that one needs to choose relative higher flow strengths than other boundary conditions to reach structural disorder.
+Figure~\ref{fig:BC3_TG}a--c are configurations for $V_0=0.2, 0.25, 0.3$ at $t=0.4 \mu$s.
+Figure~\ref{fig:BC3_TG}d--f show that the threshold for having clear rupture is between $V_0=0.2$ and $V_0=0.25$ and a huge jump in measures occurs soon after the flow is turned on.
 
 \section{Discussion}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_Energy_LsFs}
-    \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_MSD_LsFs}
-  \end{center}
-    \caption{\label{fig:BC2_tests} A multi-lamellar structure in a shear flow when the shear rate is $\dot\gamma=0.1$.
-We tune the length scale parameters, radius, $\rho$ and $\rho_0$, by $\pm 5\%$ and the force scale parameters, $\gamma$ and $M$, by $\pm 5\%$.
-}
-\end{figure}
 

### 2022-07-08 doc/PRF2022/PRF_main.tex
PRF_main.tex updates

@@
 % below if necessary.
-%\bibliographystyle{apsrev4-2}
+\bibliographystyle{apsrev4-2}
 
@@
 The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
-boundary integral numerical simulations \cite{Fu2022_JFM}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
+boundary integral numerical simulations \cite{fu-qua-ryh-you}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
 Immersed in a viscous solvent, the dynamics of a JP suspension results from the combination of long-range hydrodynamic interaction and non-local
@@
 
-Under background flows, the hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit many familiar behaviors of a vesicle \cite{Fu2022_JFM}: 
+Under background flows, the hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit many familiar behaviors of a vesicle \cite{fu-qua-ryh-you}: 
 Elongation and alignment along the extensional direction, tank-treading, and rupture of a vesicle under shear flow.
@@
     configurations as shown in Figure \ref{fig:relax}b--d, respectively.
-    The black curves are the energies for the $N_b=60$ cases and  
-    the red curves are the energies for the $N_b = 198$ cases normalized
+    The solid curves are the energies for the $N_b=60$ cases and  
+    the dashed curves are the energies for the $N_b = 198$ cases normalized
     by $60/198$, showing that the energy approximately scales with the number of
-    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. 
+    particles. We use different colors to distinguish from boundary conditions.
+    B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. 
     The curve styles are identical to the ones in panel A.
@@
 For 198-particle cases, we normalized the energies by 60/198 and the results show that all energies decrease with good agreements in all boundary conditions.
+This can be considered as an evidence that the proposed model with specified boudary condtions is independent of number of particles.
 Figure~\ref{fig:relax_energy}b 
 measures the orientational order parameter $\tilde{S}_2$. Both bilayer and multilamellar 
-structures have similar trends in small and large systems. The aggregation for striated configurations may have a significant difference when the number of particles is varied.
+structures have similar trends in small and large systems. The aggregation for striated configurations may have one or more different pattern formations when the number of particles is varied.
 
@@
   \caption{
-    \label{fig:BC1_shear}
-    The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
-    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=500$).
+    \label{fig:BC1_shear} Multiple component bilayers in a shear flow when $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=0.5\ \mu$s.
+The pre-relaxed initial configuration is shown in inset of panel (a).
 The streamlines are plotted in the background.
+Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
 }
@@
     \label{fig:Ves_shear}
-    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$.
-Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$.
-The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures.
-For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows.
-The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
+Single vesicle in a shear flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
+The streamlines are plotted in the background.
+Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
      }
@@
 In Figure~\ref{fig:Ves_shear} (a)--(c), the vesicle in a shear flow undergoes the familiar tank-treading deformation. 
-Our previous paper \cite{Fu2022_JFM} studied the geometry,
+Our previous paper \cite{fu-qua-ryh-you} studied the geometry,
 intermonolayer slip, and critical shear rates $\gamma^*=0.066$
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BC1_TG} The figure shows a vesicle in Taylor-Green flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=600$) 
-    and the multiple component bilayers in Taylor-Green flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $V_0 = \{0.1, 0.15, 0.2\}$ at $t=200$).
+  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
  The streamlines are plotted in the background. 
+Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
   }
@@
   \end{center}
-\caption{\label{fig:ves_TG} A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$.
-The result indicates that the highest flow strength ($V_0=0.2$) makes the vesicle (top row) rupture within a short period of time and the energy rapidly increases.
-As expected, the local order parameter drops and the MSD increases.
-For bilayer structure (bottom row), for $V_0=0.15$ and $V_0 = 0.2$, the energy gradually increases over the time but the other two measures do not have  a clear trend.}
+\caption{\label{fig:ves_TG} Single vesicle in a shear flow.
+Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
+The streamlines are plotted in the background.
+Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
+}
 \end{figure}
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)-(d) show the configurations with streamlines when a vesicle is in Taylor-Green flow at $t=1000$ and $l= 1,2,3,4$, respectively.
-  Vesicle in a Taylor-Green flow where $V_0=0.1$ and the size of rotating cell $l$ is varied.
-The enclosed area calculated from the bilayer midplane decreases over time and the total length measured from the midplane remains nearly constant with small magnitude of oscillations.
+  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)-(d) show the configurations with streamlines when a vesicle is in Taylor-Green flow at $t=1 \mu$s and $l= 1,2,3,4$, respectively.
+  For panel (e), the enclosed area $A_0/A$ calculated from the bilayer midplane decreases over time and the total length (as shown in the inset) measured from the midplane remains nearly constant with small magnitude of oscillations.
   }
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BC2_shear}   Multi-lamellar stracture in shear flows.
-The insets of Fig~\ref{fig:relax}c is used for panels (a).
-Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=600$, respecitively.
+  \caption{\label{fig:BC2_shear}
+Multilamellar structure in a shear flow.
+Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.1, 0.15\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
 The streamlines are plotted in the background.
-A multi-lamellar structure in shear flows with shear rates $\dot\gamma=\{0.05, 0.1, 0.15\}$.
-For this set of simulations, the local order parameter is a good indicator for tracking the rupture or structure separations.
-Moreover, all three measure show that the energy, orderparameter, and MSD increase as shear rate increases.
+Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
        }
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BC2_TG} Multi-lamellar stracture in Taylor-Green flows.
-The insets of Fig~\ref{fig:relax}c is used for panels (a).
-Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.1, 0.15, 0.2\}$ at $t=600$, respecitively.
+  \caption{\label{fig:BC2_TG} 
+Multilamellar structure in a Taylor-Green flow.
+Panels (a)-(c) are snapshots for $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
 The streamlines are plotted in the background.
-A multi-lamellar structure in a Taylor-Green flow when the flow strength $V_0=\{0.1,0.15,0.2\}$.
-The energy profile when $V_0=0.2$ has an increasing trend that results a large deformation after a period of time.
-Since the flow strengths for all cases are not strong enough, the convergent MSD represents that the rupture does not occur before $t=1000$.
+Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
  }
@@
   \end{center}
-      \caption{\label{fig:BC3_shear}  A striated configuration in shear flows where the streamlines are plotted in the background.
-Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$ at $t=100$, respectively.
-       A striated configuration in shear flows with shear rates $\dot\gamma=\{0.1, 0.125, 0.15\}$.
-The energy profile, order parameter, and MSD for the case $\dot\gamma=0.15$ show that a rupture occurs during the simulation.
-For other two cases, all measures remain nearly constant.
+      \caption{\label{fig:BC3_shear}  A striated configuration in a shear flow.
+Panels (a)-(c) are snapshots for $\dot \gamma = \{0.1, 0.125, 0.15\}$ at $t=0.1\mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
+The streamlines are plotted in the background.
+Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
     }
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BC3_TG} A striated configuration in Taylor-Green flows where the streamlines are plotted in the background.
-Panel (a) uses the insets of Fig~\ref{fig:relax}d and panels (b)-(d) are snapshots for the flow strengths $V_0=\{0.2, 0.25, 0.3\}$ at $t=400$, respectively.}
+  \caption{\label{fig:BC3_TG} A striated configuration in a Taylor-Green flow.
+Panels (a)-(c) are snapshots for $V_0=\{0.2, 0.25, 0.3\}$ at $t=0.4\mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
+The streamlines are plotted in the background.
+Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
+}
 \end{figure}

### 2022-07-08 doc/PRF2022/PRF_main.tex
fixed bibliography

@@
 The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
-boundary integral numerical simulations \cite{fu-qua-ryh-you}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
+boundary integral numerical simulations \cite{Fu2022_JFM}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
 Immersed in a viscous solvent, the dynamics of a JP suspension results from the combination of long-range hydrodynamic interaction and non-local
@@
 
-Under background flows, the hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit many familiar behaviors of a vesicle \cite{fu-qua-ryh-you}: 
+Under background flows, the hydrodynamics of a JP vesicle (a
+self-enclosed bilayer of JPs) exhibit many familiar behaviors of a
+vesicle \cite{Fu2022_JFM}: 
 Elongation and alignment along the extensional direction, tank-treading, and rupture of a vesicle under shear flow.
@@
 $
-is the hydrophobic stress identified in ~\cite{Fu2018_SIAM} 
+is the hydrophobic stress identified in ~\cite{Fu20} 
 and derived by variation of the domain techniques.
@@
 In Figure~\ref{fig:Ves_shear} (a)--(c), the vesicle in a shear flow undergoes the familiar tank-treading deformation. 
-Our previous paper \cite{fu-qua-ryh-you} studied the geometry,
+Our previous paper \cite{Fu2022_JFM} studied the geometry,
 intermonolayer slip, and critical shear rates $\gamma^*=0.066$
@@
 
+% If you have acknowledgments, this puts in the proper section head.
+\begin{acknowledgments}
+We thank Dr.
+S\'ebastien Michelin and Dr.
+Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.
+
+% put your acknowledgments here.
+\end{acknowledgments}
+
+% Create the reference section using BibTeX:
+\bibliography{reference}
+
 \end{document}
@@
 summarize the governing equations here, and a complete description is in
-our previous work~\cite{fu-qua-ryh-you2022}. The interactions satisfy a
+our previous work~\cite{Fu2022_JFM}. The interactions satisfy a
 system of partial differential equations (PDEs) that describe the
@@
 %\section{}
-
-% If you have acknowledgments, this puts in the proper section head.
-\begin{acknowledgments}
-We thank Dr.
-S\'ebastien Michelin and Dr.
-Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.
-
-% put your acknowledgments here.
-\end{acknowledgments}
-
-% Create the reference section using BibTeX:
-\bibliography{reference}
-
-\end{document}
-%
-% ****** End of file apstemplate.tex ******

### 2022-07-09 doc/PRF2022/PRF_main.tex
PRF_main.tex updates

@@
 
-Figure~\ref{fig:relax}a shows the initial configurations with orientations of 198-particle and 60- particle cases. 
+Figure~\ref{fig:relax}(a) shows the initial configurations with orientations of 198-particle and 60- particle cases. 
 Case (i) with $b = 1$, mimicks an amphiphilic particle.
@@
   \caption{\label{fig:relax_energy}
-  A:  The free energy \eqref{eq:free_energy} decreases
+  Panel (a) shows that the free energy \eqref{eq:free_energy} decreases
     in the mobility problem formulation.  The initial energies
-    are for the configuration in Figure \ref{fig:relax}a
+    are for the configuration in Figure \ref{fig:relax}(a)
     and the final energies are for the near-equilibrium
-    configurations as shown in Figure \ref{fig:relax}b--d, respectively.
+    configurations as shown in Figure \ref{fig:relax}(b)--(d), respectively.
     The solid curves are the energies for the $N_b=60$ cases and  
@@
     particles. We use different colors to distinguish from boundary conditions.
-    B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. 
-    The curve styles are identical to the ones in panel A.
-    The near-equilibrium configurations depend on the initial configuration and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trend in self-assembly in term of the local order parameter.
-The results of the striated configuration depend on the initial setup.
+    Panel (b) shows the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs. 
+    The curve styles are identical to the ones in panel (a).
+    The near-equilibrium configurations depend on the initial configurations and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trends in orientational parameters.
+The results of the striated configuration depend on the initial geometrical setup.
   }
@@
 
-Figure~\ref{fig:relax_energy}a tracks the free energy profiles for all relaxation runs.
+Figure~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
 For 198-particle cases, we normalized the energies by 60/198 and the results show that all energies decrease with good agreements in all boundary conditions.
 This can be considered as an evidence that the proposed model with specified boudary condtions is independent of number of particles.
-Figure~\ref{fig:relax_energy}b 
+Figure~\ref{fig:relax_energy}(b) 
 measures the orientational order parameter $\tilde{S}_2$. Both bilayer and multilamellar 
@@
 where $\dot\gamma$ is the shear rate. 
-Figure~\ref{fig:BC1_shear} (a)--(c)
+Figure~\ref{fig:BC1_shear}(a)--(c)
 shows snapshots of the vesicle when $\dot\gamma= 0.05,0.075,0.01$.
-The free energies (Figure~\ref{fig:BC1_shear}d) are relatively constant and 
-lower shear rate results a smaller orientational parameter (Figure~\ref{fig:BC1_shear}e). The supplementary movies show that these bilayers merge and form a work-like shape in higher 
-shear flows. Figure~\ref{fig:BC1_shear}f shows that the strain parameter diverges when 
+The free energies (Figure~\ref{fig:BC1_shear}(d)) are relatively constant and 
+lower shear rate results a smaller orientational parameter (Figure~\ref{fig:BC1_shear}(e)). The supplementary movies show that these bilayers merge and form a work-like shape in higher 
+shear flows. Figure~\ref{fig:BC1_shear}(f) shows that the strain parameter diverges when 
 the shear rate is large enough.
@@
 for vesicles comprised of amphiphilic Janus particles. 
-Here $\dot\gamma=0.05, 0.066, 0.075$ and there are jumps in energies (Figure \ref{fig:Ves_shear}d, long and short dashed curves) due to the breaking of the vesicle into two
+Here $\dot\gamma=0.05, 0.066, 0.075$ and there are jumps in energies (Figure \ref{fig:Ves_shear}(d), long and short dashed curves) due to the breaking of the vesicle into two
 components. There is greater variation in the order parameter $\tilde{S}_2(t)$ as well
 with a baseline value around $0.7$
-(Figure \ref{fig:Ves_shear}e, dashed curve).
+(Figure \ref{fig:Ves_shear}(e), dashed curve).
 The oscillations occur due to the orbit of the two bilayer components, and $\tilde{S}_2(t)$ increases to about $0.9$ when the components are nearly parallel and slide past one another.
@@
 Positional order, however, diverges since the two component configuration
-is uncorrelated to the initial circular configuration (Figure \ref{fig:Ves_shear}f, dashed curve).
+is uncorrelated to the initial circular configuration (Figure \ref{fig:Ves_shear}(f), dashed curve).
 
@@
 
-Figure~\ref{fig:BC1_TG}a--c are the snapshots when $V_0=0.1,0.15,0.2$, respectively.
+Figure~\ref{fig:BC1_TG}(a)--(c) are the snapshots when $V_0=0.1,0.15,0.2$, respectively.
 This initial configuration in TG flow encounters a number of fusion but there is no clear trend for
@@
 
-For a vesicle in a Taylor-Green flow, Figure~\ref{fig:ves_TG}a--c are configurations at $t=0.2 \mu$s where $V_0=0.1,0.15,0.2$.
-Figure~\ref{fig:ves_TG}d--f indicates that the rupture occurs when the energy and strain parameter are significant larger and the orientational parameter is much lower than other cases.
+For a vesicle in a Taylor-Green flow, Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\  \mu$s where $V_0=0.1,0.15,0.2$.
+Figure~\ref{fig:ves_TG}(d)--(f) indicates that the rupture occurs when the energy and strain parameter are significant larger and the orientational parameter is much lower than other cases.
 
@@
 We vary the cell size by tuning the parameter $l$ in \eqref{eq:tg_flow}.
-Figure~\ref{fig:BTG_Scale}a--d show the deformation of a vesicle in a Taylor-Green flow when $V_0=0.1$ and arrows indicate rotating directions.
-Figure~\ref{fig:BTG_Scale}e presents that the area $A/A_0$ decreases during the simulations and the inset shows constant total lengths $L/L_0$ for all cases where $A_0$ and $L_0$ are initial enclose area and midplane length.
+Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a Taylor-Green flow when $V_0=0.1$ and $t = 1\ \mu$s where arrows indicate rotating directions.
+Figure~\ref{fig:BTG_Scale}(e) presents that the area $A/A_0$ decreases during the simulations and the inset shows constant total lengths
+$L/L_0$ for all cases where $A_0$ and $L_0$ are initial enclose area and midplane length.
 %A/A0 plot with no monotonic trend.
@@
 
-We place a 60-particle multilamellar configuration (inset of Figure~\ref{fig:BC2_shear}a) in shear flows where $\dot\gamma=0.05, 0.1, 0.15$.
-Quantities such as energies, orientational parameter, and positional parameter (Figure~\ref{fig:BC2_shear}d--f) follow the same trend where they increases as shear rate increases.
-Comparing with bilayer structures, Figure~\ref{fig:BC2_shear}a--c demonstrate that the multilamellar ones are more rigid in shear flow and the rupture phenomenon can be observed 
+We place a 60-particle multilamellar configuration (inset of Figure~\ref{fig:BC2_shear}(a)) in shear flows where $\dot\gamma=0.05, 0.1, 0.15$.
+Quantities such as energies, orientational parameter, and positional parameter (Figure~\ref{fig:BC2_shear}(d)--(f)) follow the same trend where they increases as shear rate increases.
+Comparing with bilayer structures, Figure~\ref{fig:BC2_shear}(a)--(c) demonstrate that the multilamellar ones are more rigid in shear flow and the rupture phenomenon can be observed 
 when the shear rate is high enough.
@@
 
-For multilamellar structure in a Taylor-Green flow, as shown in Figure~\ref{fig:BC2_TG}a--b, lower flow strengths such as $V_0=0.1,0.15$ do not reach a critical flow rate for structural disorder. 
-When $V_0=0.2$ (Figure~\ref{fig:BC2_TG}c), the flow is strong enough to separate the structure
-into multiple groups within the cells. In all deformation measures, a similar trend in shear flow case is observed, see Figure~\ref{fig:BC2_TG}d--f.
+For multilamellar structure in a Taylor-Green flow, as shown in Figure~\ref{fig:BC2_TG}(a)--(b), lower flow strengths such as $V_0=0.1,0.15$ do not reach a critical flow rate for structural disorder. 
+When $V_0=0.2$ (Figure~\ref{fig:BC2_TG}(c)), the flow is strong enough to separate the structure
+into multiple groups within the cells. In all deformation measures, a similar trend in shear flow case is observed, see Figure~\ref{fig:BC2_TG}(d)--(f).
 
@@
 We place the striated configuration in a shear flow when $\dot\gamma=0.1, 0.125, 0.15$ and 
-the snapshots at $t=0.1 \mu$s are shown in Figure~\ref{fig:BC3_shear}a--c.
-Break-up deformation measures (igure~\ref{fig:BC3_shear}d--f) are similar to vesicle in shear flow case.
+the snapshots at $t=0.1\ \mu$s are shown in Figure~\ref{fig:BC3_shear}(a)--(c).
+Break-up deformation measures (igure~\ref{fig:BC3_shear}(d)--(f)) are similar to vesicle in shear flow case.
 Notably, for low shear rates, oscillatory behaviours are investigated in energies, orientational and positional parameters.
@@
 For a striated configuration in a Taylor-Green flow, numerical experiments have shown that one needs to choose relative higher flow strengths than other boundary conditions to reach structural disorder.
-Figure~\ref{fig:BC3_TG}a--c are configurations for $V_0=0.2, 0.25, 0.3$ at $t=0.4 \mu$s.
-Figure~\ref{fig:BC3_TG}d--f show that the threshold for having clear rupture is between $V_0=0.2$ and $V_0=0.25$ and a huge jump in measures occurs soon after the flow is turned on.
+Figure~\ref{fig:BC3_TG}(a)--(c) are configurations for $V_0=0.2, 0.25, 0.3$ at $t=0.4\  \mu$s.
+Figure~\ref{fig:BC3_TG}(d)--(f) show that the threshold for having clear rupture is between $V_0=0.2$ and $V_0=0.25$ and a huge jump in measures occurs soon after the flow is turned on.
 
@@
 alternating orientations \cite{}.
+
+We notice that the strain parameter are relatively higher (of order 10) in shear flows or not confining flows comparing with ones of order 1 in cases using Taylor-Green flows when rupture occurs.
+In order to make the structure disorder, the striated structures need the highest flow strength or shear rate in all three boundary conditions.
+Moreover, this can be interpreted by having higest free energy calculated from striated structures.
 

### 2022-07-12 doc/PRF2022/PRF_main.tex
results done

@@
 \renewcommand{\SS}{\mathbf{S}}
+\newcommand{\ff}{\mathbf{f}}
 \newcommand{\xx}{\mathbf{x}}
@@
   Panel (a) shows $N_b = 198$ particles confined to a square with random 
-  positions and orientation and the inset shows $N_b=60$ particles configuration.
-  Depending on the boundary condition \eqref{eq:bc-type},
-  the particles self-assemble into distinct configurations.
+  positions and orientations and the inset shows $N_b=60$ particles configuration.
+  The particles self-assemble into distinct configurations,
+  depending on the boundary condition \eqref{eq:bc-type}.
   Panel (b) is for $b=1$ and the boundary condition mimicks that
-  of an amphiphilic particle. 
+  of an amphiphilic particle giving bilayer structures. 
   Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
@@
   The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
- Panel (b)--(d) insets are configurations using $N_b=60$ sharing with the same color map.}
+  The insest in panel (b)--(d) are configurations using $N_b=60$ and share the same color map
+  as the main panels.}
 \end{caption}
@@
 \subsection{Boundary conditions and normalization}
-The present paper considers boundary condition of the form
+The present paper considers boundary conditions of the form
 \begin{equation}
@@
 so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
+The motivation for this normalization is that the hydrophobic attraction
+part of the free energy converges to the integral of the square of the boundary
+data in the zero-screening length limit.  
 We refer to the side of the particle where $\alpha = 0$
@@
 
-Figure~\ref{fig:relax}(a) shows the initial configurations with orientations of 198-particle and 60- particle cases. 
+Figure~\ref{fig:relax}(a)shows the initial configurations with orientations of 198-particle and 60- particle cases,
+respectively. 
 Case (i) with $b = 1$, mimicks an amphiphilic particle.
@@
 takes the value $0$ on the
-hydrophilic head,
+hydrophilic head (green),
 and takes the maximum value $a$ on the
-hydrophobic tail. 
+hydrophobic tail (red). 
 The interaction is attractive, and particles collectively orient their
 hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)). The inset shows the equilibrium 
-state for 60-particle run that forms multiple bilayers with a vesicle like structure.
-
-In case (ii) with $b = 1$, the boundary condition is positive everywhere.
-It takes the maximum value $3a$ on tail and the
-minimum value $a$ on the head side. 
+state for 60-particle run.
+Both cases form bilayers with multiple components.
+
+In case (ii) with $b = 1$, the boundary condition is everywhere positive.
+It takes the maximum value $3a$ on tail (red) and the
+minimum value $a$ on the head side (yellow). 
 Both sides of the Janus particle are hydrophobic but
@@
 the heads are also hydrophobic and so in the long-time dynamics
-these bilayers also adhere to one another 
-forming multilamella structures. Figure~\ref{fig:relax}(c), for example, shows a
-multilamellar structure with multiple layers.
-At equilibrium, the number of folds depends primarily on the number of particles.
-In addition, the inset provides a 3-fold structure when there are 60 particles.
+these bilayers form multilamella structures.
+The number of folds depends primarily on the number of particles.
+Figure~\ref{fig:relax}(c), for example, shows a
+multilamellar structure with four layers and one with two layers in the inset.
 
@@
 where the particles lie on a 
-grid and the orientations alternate between layers (Figure~\ref{fig:relax}(d)). We observe that 
-when the number of particles is fewer, there is only single alternating pattern in particle orientations. Larger number of particles results two different patterns as shown in the figure.
-
-The equilibrium configurations for case (ii) and (iii) are used as initial data in the
-background flow simulations found in Section \ref{sec:results}.
-In case (i), there are several connected
-components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
-To have a single, coherent vesicle (i), we reinitialize
-the case (i) particles in the form of a ring and run the relaxation procedure once more.
-
-\section{Measuring deformation}
-We use the free energy $F$,
-a Euclidean distance-based measure $d(t)$,
-and a scalar order parameter $S_{2}(t)$ to measure
-the deformation of particle configurations under background flows.
-
-First, we must simplify the
-form of the free energy \eqref{eq:free_energy}
-using integration by parts and \eqref{eq:SL}
-to obtain
-\begin{equation}
-\label{eq:free_energy2}
-F[u] = -\gamma
-\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
-+ \frac{M}{2}
-\sum_{j \neq i} 
-P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
-\end{equation}
-%
-Here, we have substituted $g$ for $u$ since the boundary values are given.
-However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
-involves calculating a quadruple layer potential which has a
-well-known obstacle in numerical implementation.
-To overcome this obstacle, we use
-%
-\begin{equation}
-\label{eq:normal_deriv}
-\nabla u(\xx) \cdot \nnu(\xx)=
-%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
--\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
-+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
-\end{equation}
-%
-Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
-See the Appendix section \ref{sec:appendix} for the proof and details.
-Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
-leads to single layer integral which is more straightforward to evaluate and we compute the
-arclength derivative using spectrally accurate Fourier transform.
-We have validated the form of \eqref{eq:normal_deriv} by extrapolating 
-the primal energy \eqref{eq:free_energy} along test curves placed slightly
-outside the particles.
-
-To measure positional order, we use a strain parameter 
-\begin{equation}
-\label{eq:SP}
-E(t) = \frac{1}{N_b} \sum_{i=1}^{N_b} \|E_i\|
-\end{equation}
-where $E_i = \tfrac{1}{2}(F_i^TF_i - I)$ is a Green-Lagrange strain tensor and $F_i$
-is an approximate deformation gradient at particle $i$; $\| \cdot \|$ is the Frobeneous norm.
-The motivation for  \eqref{eq:SP} is that 
-for relatively weak background flow strengths, the near-equilibrium particle
-collections behave as a solid and $E(t)$ is close to zero.
-More generally, the Green-Lagrange strain tensor $E_i$ 
-can be used to encode the energy of elastic deformations from the reference (equilibrium)
-to deformed configuration and $E(t)$ gives a sense of how significant these deformations
-may be.  Lacking a map from the reference state, 
-we approximate a deformation gradient $F_i$ using weighted least squares for the system 
-\[
-F_i(\aa_j(t) - \aa_i(t)) = \aa_j(0) - \aa_i(0),\quad j = 1,\dots, N_b  
-\]
-with weights $w_i = \exp(-\|\aa_j(t) - \aa_i(t)\|/4c)$ where $c$ is particle radius.
-
-To study orientational order, we use the scalar order parameter 
-\begin{equation}
-  \label{eq:S2}
-S_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
-\end{equation}
-Here $\bar \theta$ is a circular mean defined as the
-orientation of the largest eigenvalue eigenvector of 
-$\dd_1\dd_1^\top + \dots + \dd_{N_b}\dd_{N_b}^\top$.
-A value $S_2(t) = 1$ indicates a complete orientational
-order where all particle directors lie on a common axis e.g.,
-two parallel vectors with possibly opposite direction are ordered. 
-A value far from 1 indicates disorder.
-
-The measure $S_2$ is an inadequate for the bilayer and
-multilamellar structures.  For example, the directors of a circular
-bilayer vesicle are uniformly distributed along a circle, even though
-there is a strong orientational order between neighboring particles.
-To account for these latter cases, we use
-\begin{equation}
-  \label{eq:localS2}
-\tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
-\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1).
-\end{equation}
-where $\bar \theta_i$ is the circular mean restricted to particles
-indexed by $j$ for which $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle is
-isolated and has no neighbors within a distance $4c$, then we exclude it from
-the sum \eqref{eq:localS2}.
+square grid and the orientations alternate
+between layers (Figure~\ref{fig:relax}(d)).
 
@@
     by $60/198$, showing that the energy approximately scales with the number of
-    particles. We use different colors to distinguish from boundary conditions.
+    particles. 
     Panel (b) shows the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs. 
@@
     The near-equilibrium configurations depend on the initial configurations and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trends in orientational parameters.
-The results of the striated configuration depend on the initial geometrical setup.
+    The results of the striated configuration, however, depend on the initial geometrical setup.
   }
@@
 
+\section{Measuring deformation}
+We use the free energy $F$,
+a strain parameter $E$, 
+and two scalar order parameters $S_{2}$ and $\tilde S_2$ to measure
+the deformation of particle configurations under background flows.
+
+First, we must simplify the
+form of the free energy \eqref{eq:free_energy}
+using integration by parts and \eqref{eq:SL}
+to obtain
+\begin{equation}
+\label{eq:free_energy2}
+F = -\gamma
+\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
++ \frac{M}{2}
+\sum_{j \neq i} 
+P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
+\end{equation}
+%
+Here, we have substituted $g$ for $u$ since the boundary values are given.
+However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
+involves calculating a quadruple layer potential which has a
+well-known obstacle in numerical implementation.
+To overcome this obstacle, we use
+%
+\begin{equation}
+\label{eq:normal_deriv}
+\nabla u(\xx) \cdot \nnu(\xx)=
+%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
+-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
++ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
+\end{equation}
+%
+Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
+See the Appendix section \ref{sec:appendix} for the proof and details.
+Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
+leads to single layer integral which is more straightforward to evaluate and we compute the
+arclength derivative using spectrally accurate Fourier transform.
+We have validated the form of \eqref{eq:normal_deriv} by extrapolating 
+the primal energy \eqref{eq:free_energy} along test curves placed slightly
+outside the particles.
+
 Figure~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
-For 198-particle cases, we normalized the energies by 60/198 and the results show that all energies decrease with good agreements in all boundary conditions.
-This can be considered as an evidence that the proposed model with specified boudary condtions is independent of number of particles.
+For the 198-particle cases, we normalized the energies by 60/198 and the results
+show that all energies decrease with good agreements in all boundary conditions (dashed curves).
+This can be considered as evidence that the free energy per particle with specified
+boundary condtions is independent of number of particles.
+
+To measure positional order, we use a number,
+which we call the strain parameter, 
+\begin{equation}
+\label{eq:SP}
+E = \frac{1}{N_b} \sum_{i=1}^{N_b}
+\|\tfrac{1}{2}(\mathsf{F}_i^T \mathsf{F}_i - I)\|
+\end{equation}
+where $\mathsf{F}_i$ is an 
+approximate deformation gradient at particle $i$.
+The argument inside the Frobenius norm $\| \cdot \|$
+is the Green-Lagrange strain tensor.
+The motivation for  \eqref{eq:SP} is as follows.
+For relatively weak background flow strengths, the near-equilibrium particle
+configurations behave as an elastic solid.  There is a map $\ff(\xx,t)$
+from the reference (equilibrium) configuration with $\ff(\aa_i(0),t) = \aa_i(t)$
+for $i = 1,\dots,N_b$.  Using linear approximation,
+\[
+\aa_j(t) - \aa_i(t) = \ff(\aa_j(0),t) - \ff(\aa_i(0),t)
+\approx \nabla \ff(\aa_i(0),t)(\aa_j(0) - \aa_i(0)).
+\]
+To approximate
+the deformation gradient $\nabla \ff(\aa_i(0),t)$
+we solved the overdetermined system 
+\[
+\aa_j(t) - \aa_i(t) = \mathsf{F}_i(\aa_j(0) - \aa_i(0)),\quad j = 1,\dots, N_b  
+\]
+for $\mathsf{F}_i$ by weighted least squares. The weights  
+$w_i = \exp(-\|\aa_j(0) - \aa_i(0)\|/4c)$ with particle radius $c$
+ensure that nearby particles contribute the most to the linear approximation at $\aa_i$.
+
+Finally, we use the scalar order parameter for orientational order:
+\begin{equation}
+  \label{eq:S2}
+S_2 = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
+\end{equation}
+Here $\bar \theta$ is a circular mean defined as the
+orientation of the largest eigenvalue eigenvector of 
+$\dd_1\dd_1^\top + \dots + \dd_{N_b}\dd_{N_b}^\top$.
+A value $S_2(t) = 1$ indicates 
+that all particle directors lie on a common axis e.g.,
+two parallel vectors with possibly opposite direction are ordered. 
+A value far from 1 indicates disorder.
+
+We must modify $S_2$ to account for the bilayer and
+multilamellar structures.  In these cases, the directors 
+are more or less bilayer uniformly distributed along a circle, even though
+there is orientational order between neighboring particles.
+To account for local order, we instead use
+\begin{equation}
+  \label{eq:localS2}
+\tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
+\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1).
+\end{equation}
+where $\bar \theta_i$ is the circular mean restricted to particles
+indexed by $j$ for which $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle is
+isolated and has no neighbors within a distance $4c$, then we exclude it from
+the sum \eqref{eq:localS2}.
+
 Figure~\ref{fig:relax_energy}(b) 
-measures the orientational order parameter $\tilde{S}_2$. Both bilayer and multilamellar 
-structures have similar trends in small and large systems. The aggregation for striated configurations may have one or more different pattern formations when the number of particles is varied.
+tracks the orientational order parameter $\tilde{S}_2$.
+Both bilayer and multilamellar
+structures show similar trends in the small and large particle number systems
+(Figure \ref{fig:relax}(b) black curves, red curves respectively).
+The multilamellar structures are highly ordered in all cases (Figure~\ref{fig:relax}(c))
+whereas the bilayer structures
+are disordered because they consist of several connected
+components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
+
+The aggregation for striated configurations form more than one 
+pattern when the number of particles is varied (Figure~\ref{fig:relax}(d)).
+We observe that when the number of particles is fewer, there is only
+a single alternating pattern in particle orientations where the directors
+are more or less parallel and alternate directions between stria (Figure~\ref{fig:relax}(d), inset).
+Larger number of particles results in two different patterns: the alternating sign pattern
+as in the small particle number case (Figure~\ref{fig:relax}(d), 
+top right rectangle) and one where the directors reflect across the lines parallel
+to the stria and across the lines perpendicular to the stria (Figure~\ref{fig:relax}(d),
+top middle rectangle).
+As a result, there are different trends in orientational order
+(Figure~\ref{fig:relax_energy}(b), solid and dashed blue curves, respectively).
+
+In the Results section,
+the equilibrium configurations for cases (i), (ii), and (iii)
+(Figure~\ref{fig:relax}, insets) are
+used as initial data in the
+background flow simulations. 
+For the bilayer case (i), we include an alternate initial condition 
+consisting of a single, circular vesicle (c.f., Figure~\ref{fig:Ves_shear}).
 
 %%%%%%%
+
+\begin{figure}
+  \begin{center}
+   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
+  \end{center}
+  \caption{
+    \label{fig:BC1_shear}
+    Panels (a)-(c) are a snapshot at $t=0.5\ \mu$s of the multiple-component bilayer
+    with shear flow rate $\dot \gamma = \{0.05, 0.075, 0.1\}$.
+    The initial configuration is shown in inset of panel (a).
+    The streamlines are plotted in the background.
+    Panel (d) plots the free energies,
+    panel (e) shows the orientational parameter $\tilde{S}_2$,
+    and panel (f) shows positional parameter E.
+}
+\end{figure}
 
@@
 \label{sec:results}
-
+In this section, we subject the Janus particle structures to various background
+flows.  The purpose of this study is to understand how self-assembled particles
+respond to external fluid forcing.  We can then compare the results to guage
+the effective properties of materials comprised of Janus particles as a function
+of their amphiphilic properties.  
 %%%
-
-\subsection{Boundary condition (i):   bilayer configurations}
-
-\begin{figure}
-  \begin{center}
-   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
+%%%
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
   \end{center}
   \caption{
-    \label{fig:BC1_shear} Multiple component bilayers in a shear flow when $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=0.5\ \mu$s.
-The pre-relaxed initial configuration is shown in inset of panel (a).
+    \label{fig:Ves_shear}
+The figure shows a single vesicle in a shear flow.
+Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
 The streamlines are plotted in the background.
@@
 
-The bilayer is subject to a shear background flow
-\begin{equation}
-\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
-\end{equation}
-%
-where $\dot\gamma$ is the shear rate. 
+\subsection{Bilayer configurations in a shear flow}
+To begin, we place the bilayer structure (Figure~\ref{fig:relax}(b), inset)
+in the shear background flow
+\begin{equation}
+\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y\cdot\xx){\bf e}_x,
+\end{equation}
+%
+where $\dot\gamma$ is the dimensionless shear rate and ${\bf e}_x$ and ${\bf e}_y$
+are horizontal and vertical unit vectors, respectively.  
 Figure~\ref{fig:BC1_shear}(a)--(c)
-shows snapshots of the vesicle when $\dot\gamma= 0.05,0.075,0.01$.
-The free energies (Figure~\ref{fig:BC1_shear}(d)) are relatively constant and 
-lower shear rate results a smaller orientational parameter (Figure~\ref{fig:BC1_shear}(e)). The supplementary movies show that these bilayers merge and form a work-like shape in higher 
-shear flows. Figure~\ref{fig:BC1_shear}(f) shows that the strain parameter diverges when 
-the shear rate is large enough.
-
-%%%
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
-  \end{center}
-  \caption{
-    \label{fig:Ves_shear}
-Single vesicle in a shear flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
-The streamlines are plotted in the background.
-Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
-     }
-\end{figure}
-
-In Figure~\ref{fig:Ves_shear} (a)--(c), the vesicle in a shear flow undergoes the familiar tank-treading deformation. 
-Our previous paper \cite{Fu2022_JFM} studied the geometry,
-intermonolayer slip, and critical shear rates $\gamma^*=0.066$
-for vesicles comprised of amphiphilic Janus particles. 
-Here $\dot\gamma=0.05, 0.066, 0.075$ and there are jumps in energies (Figure \ref{fig:Ves_shear}(d), long and short dashed curves) due to the breaking of the vesicle into two
-components. There is greater variation in the order parameter $\tilde{S}_2(t)$ as well
-with a baseline value around $0.7$
-(Figure \ref{fig:Ves_shear}(e), dashed curve).
-The oscillations occur due to the orbit of the two bilayer components, and $\tilde{S}_2(t)$ increases to about $0.9$ when the components are nearly parallel and slide past one another.
-For the lowest shear rate case, it has nearly perfect orientational parameter due to the steady tank-treading motion.
-Positional order, however, diverges since the two component configuration
-is uncorrelated to the initial circular configuration (Figure \ref{fig:Ves_shear}(f), dashed curve).
-
-%%%%%%%
-
-The Taylor-Green (TG) background flow is
-\begin{equation}
-\label{eq:tg_flow}
-  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
-  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
-\end{equation}
-where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. The default parameter
-$l=2$ is used through this work.
-%
+shows snapshots of the vesicle when $\dot\gamma= 0.05,0.075,0.01$
+at $t = 0.5$ $\upmu$s.
+The general pattern consists of a rotating body.  The various bilayer components
+detach and reattach throughout so that the boyd is continuously changing morphology.
+The supplementary movies show that these bilayers merge and form a worm-like shape in higher 
+shear flows.
 
@@
 
-Figure~\ref{fig:BC1_TG}(a)--(c) are the snapshots when $V_0=0.1,0.15,0.2$, respectively.
-This initial configuration in TG flow encounters a number of fusion but there is no clear trend for
-all measures with respect to the flow strengths.
+In terms of deformations, 
+the free energies 
+are relatively constant (Figure~\ref{fig:BC1_shear}(d)),
+with the overall changes in the range of a few kT/nm.  Note that the free energy takes
+the form of a line tension because the simulations are two-dimensional.
+
+An interesting feature of the simulations is that the $\tilde S_2$ order parameter
+is on the average increasing (Figure~\ref{fig:BC1_shear}(e)).  In the initial configuration,
+the structure has three or four components.  Under the shear flow, the detachment and reattachment
+results in an overall decrease in the number of components.  This suggests that
+the shear flow perturbs the local equilibrium obtained from a random initial condition
+to an alternate local equilibrium with greater orientational order.
 
@@
   \end{center}
-\caption{\label{fig:ves_TG} Single vesicle in a shear flow.
+\caption{\label{fig:ves_TG} Single vesicle in a TG flow.
 Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
@@
 
+Finally, the strain parameter diverges in the large shear flow rate cases (Figure~\ref{fig:BC1_shear}(f))
+because the components eventually completely separate and move away from one another
+under the shear flow.
+
+We reinitialized the case (i) configuration with particles arranged in the pattern of a single, circular vesicle.
+This shape is also a local equilibrium, with somewhat less energy than the disordered state c.f.,
+Figure~\ref{fig:BC1_shear}(d) and Figure~\ref{fig:Ves_shear} (d).
+Our previous paper \cite{Fu2022_JFM} studied
+The vesicle in a shear flow undergoes the familiar tank-treading deformation (Figure~\ref{fig:Ves_shear} (a)--(c)),
+and based on previous results (\cite{Fu2022_JFM}),
+we investigate the cases $\dot\gamma=0.05, 0.066, 0.075$.
+
+Unlike the multiples component case, 
+the energies for the vesicle case show jumps from the baseline value $30$ kT/nm to 32 kT/nm
+signaling the rupture of the vesicle into multiple components
+(Figure \ref{fig:Ves_shear}(d), long and short dashed curves).
+After this initial break, the energies are more or less constant.
+
+For the lowest shear rate case, the vesicle has nearly constant orientational order $\tilde S_2 = 1$
+(Figure \ref{fig:Ves_shear}(e), solid curve).
+Following rupture ($\dot\gamma= 0.066$ and $\dot \gamma= 0.075$),
+there is greater variation in the order parameter $\tilde{S}_2$
+with a baseline value around $0.7$
+(Figure \ref{fig:Ves_shear}(e), dashed curves).
+The oscillations occur due to the orbit of the two bilayer components,
+and $\tilde{S}_2$ increases to about $0.9$ when the components slide past one another and are nearly parallel.
+
+Like with multiple component bilayer case, positional order diverges when the components of the ruptured
+vesicle separate and drift off in opposite directions (Figure \ref{fig:Ves_shear}(f), dashed curves).
+
+%%%%%%%
+\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
+Next, we subject the bilayer/vesicles configurations to a 
+Taylor-Green (TG) background flow
+\begin{equation}
+\label{eq:tg_flow}
+\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
+\left(
+-\cos\left(\frac{{\bf e}_x\cdot\xx}{\lambda}\right)
+ \sin\left(\frac{{\bf e}_y\cdot\xx}{\lambda}\right)
+         {\bf e}_x
+         +\sin\left(\frac{{\bf e}_x\cdot\xx}{\lambda}\right)
+         \cos\left(\frac{{\bf e}_y\cdot\xx}{\lambda}\right)
+             {\bf e}_y\right).
+\end{equation}
+The TG flow is a confining flow consisting of a checkboard pattern
+of cells with alternating circulation.  We control the flow by the
+the dimensionless flow strength $V_0$ and with the cell size $\lambda = l$ nm.
+The default parameter $l=2$ is used through this work.
+%
+
+There is no appreciable pattern in the deformation for the multicomponent bilayer case in TG flow. 
+Figure~\ref{fig:BC1_TG}(a)--(c) are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s.
+At all flow strengths, the bilayer components are separated and mixed by the flow in neighboring cells. 
+In the $V_0 = 0.2$ case, the flow breaks off components consisting of only a few particles,
+leading an increase in energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve).
+There is no significant change in the orientational order.  There is an initial increase in the
+strain parameter due to component mixing, but the strains remains bounded since the particles
+stay confined to within the neighbors of the central cell.
+
+Patterns in the deformation, however, do emerge in the case of a vesicle in TG flow.
 For a vesicle in a Taylor-Green flow, Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\  \mu$s where $V_0=0.1,0.15,0.2$.
-Figure~\ref{fig:ves_TG}(d)--(f) indicates that the rupture occurs when the energy and strain parameter are significant larger and the orientational parameter is much lower than other cases.
+Here, the circular vesicle takes on a steady square shape for moderate flow rates $V_0 = 0.1$ and $V_0 = 0.15$.
+In these cases, there is little change in the vesicle free energy and order (Figure~\ref{fig:ves_TG}(d)-(f))).
+The vesicle disintegrates for $V_0 = 0.2$, leading to a jump in energy, drop in order, and increase in strain,
+suggesting that the vesicle has a critical TG flow strength in the interval $[0.15, 0.2]$ separating the
+intact and ruptured end-states.
 
@@
 
-We vary the cell size by tuning the parameter $l$ in \eqref{eq:tg_flow}.
-Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a Taylor-Green flow when $V_0=0.1$ and $t = 1\ \mu$s where arrows indicate rotating directions.
-Figure~\ref{fig:BTG_Scale}(e) presents that the area $A/A_0$ decreases during the simulations and the inset shows constant total lengths
-$L/L_0$ for all cases where $A_0$ and $L_0$ are initial enclose area and midplane length.
-%A/A0 plot with no monotonic trend.
-One interesting finding is that the number of cells affects the directions of structure rotation.
+The vesicle shape is also tied to cell size $l$.  
+Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a
+TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s.  
+For the smallest cell size $l = 1$ tested, the vesicle is somewhat octogonal
+and passes through multiple cells (Figure~\ref{fig:BTG_Scale}(a)).
+For the largest cell size $l = 4$,
+the vesicle is rhomboid and surrounds a single cell.
+
+In all cases, the vesicle tank-treads like in the shear flow case.
+The direction of the tank-treading, however, varies with the cell
+size (Figure~\ref{fig:BTG_Scale}(a)--(d), directed arcs).  We attribute
+this variation to the total rotational moment of the cells that the vesicle
+passes through.
+
+We calculated the vesicle area $A$ and length $L$ (initial area $A_0$, initial length $L_0$)
+by averaging the area/length for the inner and outer leaflets.  
+As shown in Figure~\ref{fig:BTG_Scale}(e),
+the relative area $A/A_0$ decreases during the simulations, with a rate
+depending nonmonotonically on $l$.  
+The relative length $L/L_0$, is constant in $t$ for all cell sizes (Figure~\ref{fig:BTG_Scale}(e), inset).
+This implies that the vesicle behaves as an inextensible, permeable membrane.
+In previous work, \cite{Fu2022_JFM} determined the permeability constant of particle-based vesicles
+in the context of shear background flow.
 
 %%%
-
-\subsection{Boundary condition (ii):  multilamellar configurations}
-
 \begin{figure}
@@
 
-We place a 60-particle multilamellar configuration (inset of Figure~\ref{fig:BC2_shear}(a)) in shear flows where $\dot\gamma=0.05, 0.1, 0.15$.
-Quantities such as energies, orientational parameter, and positional parameter (Figure~\ref{fig:BC2_shear}(d)--(f)) follow the same trend where they increases as shear rate increases.
-Comparing with bilayer structures, Figure~\ref{fig:BC2_shear}(a)--(c) demonstrate that the multilamellar ones are more rigid in shear flow and the rupture phenomenon can be observed 
-when the shear rate is high enough.
+\subsection{Multilamellar and striated configurations in shear and TG flow}
+We have simulated particles for the multilamellar (case (ii)) and striated (case (iii))
+boundary conditions, in both shear and TG background flow.  The results are
+qualitatively similar and will be presented in tandem. 
+For the multilamellar case, we place a 60-particle configuration (inset of Figure~\ref{fig:BC2_shear}(a))
+in shear flows with $\dot\gamma=0.05, 0.1, 0.15$ and in TG flow with flow rates $V_0=0.1, 0.15, 0.2$.
+For the striated case, we also place a 60-particle configuration (inset of Figure~\ref{fig:BC3_shear}(a))
+in shear and TG background flows.  However, somewhat larger rates are required to see appreciable
+deformations for this boundary condition: $\dot\gamma=0.1, 0.125, 0.15$
+and $V_0=0.2, 0.25, 0.3$ respectively.
+
+In terms of shear flow, the free energies are steady at the lowest shear flow
+rates (Figure~\ref{fig:BC2_shear}(d), Figure~\ref{fig:BC3_shear}(d)).
+The free energy of the striated configuration oscillates by $\pm 1$ kT/nm
+due to square reference region deforming into a rhomboidal shapre under shear
+flow (Figure~\ref{fig:BC3_shear}(d), solid curve).  No such oscillation
+is present in for the multilamellar configuration since this shape is circularly
+isotropic (Figure~\ref{fig:BC2_shear}(d), solid curve).
+At the lowest shear rates, there is, however, oscillation in the strains
+of both configurations, 
+while the order parameter $\tilde S_2$ is more less constant
+(Figure~\ref{fig:BC2_shear}(e),(f), Figure~\ref{fig:BC3_shear}(e),(f), solid curves).
+In summary, both multilallar and striated configurations behave as rigid bodies
+under shear flow.
+
+In the high shear flow rate cases ($\dot\gamma=0.15$), both the
+multilamellar and striated configurations become disordered.  In case (ii),
+the lamella break apart so that individual bilayers are no longer discernable
+(Figure~\ref{fig:BC2_shear}(c)).
+In case (iii), the stria detach from the main body,
+but the stria remain instact (Figure~\ref{fig:BC3_shear}(c)).  
+Overall, the particles in case (ii) and case (iii) remain bounded
+and do not drift away in the shear background flow like for the
+case (i) boundary condition (Figure~\ref{fig:BC1_shear}(c),
+Figure~\ref{fig:Ves_shear}(c)).
 
@@
 
-For multilamellar structure in a Taylor-Green flow, as shown in Figure~\ref{fig:BC2_TG}(a)--(b), lower flow strengths such as $V_0=0.1,0.15$ do not reach a critical flow rate for structural disorder. 
-When $V_0=0.2$ (Figure~\ref{fig:BC2_TG}(c)), the flow is strong enough to separate the structure
-into multiple groups within the cells. In all deformation measures, a similar trend in shear flow case is observed, see Figure~\ref{fig:BC2_TG}(d)--(f).
+Under a TG background flow, the free energy $F$ 
+is also basically constant for the lowest flow rates $V_0$
+(Figure~\ref{fig:BC2_TG}(d), Figure~\ref{fig:BC3_TG}(d), solid curves).
+The striated configuration is unperturbed by the flow, and is engulfed by a single,
+larger, rotating flow cell
+(Figure~\ref{fig:BC3_TG}(a)). 
+The multilamellar configuration is perturbed by the flow, as seen in the increase in
+the strain parameter $E$ (Figure~\ref{fig:BC3_TG}(f), solid curve).
+The difference in response to the background flow
+suggests that the multilamellar configuration
+allows for local rearrangment of the particles while retaining the overall shape.
+
+At large flow rates $V_0$, both configurations depart significantly from their local
+equilibrium.  The lamella bilayers from case (ii) break apart, forming several,
+unlayered bilayer components (Figure~\ref{fig:BC2_TG}(c)).
+
+In case (iii), the stria also break apart, but neighboring particles form
+'X'-like arrangements (Figure~\ref{fig:BC3_TG}(d)), resembling the doubly alternating
+director equilibrium (Figure~\ref{fig:relax}(d), center, top white rectangle).
 
 %%%
-
-\subsection{Boundary condition (iii): striated configurations}
 
@@
 \end{figure}
-
-We place the striated configuration in a shear flow when $\dot\gamma=0.1, 0.125, 0.15$ and 
-the snapshots at $t=0.1\ \mu$s are shown in Figure~\ref{fig:BC3_shear}(a)--(c).
-Break-up deformation measures (igure~\ref{fig:BC3_shear}(d)--(f)) are similar to vesicle in shear flow case.
-Notably, for low shear rates, oscillatory behaviours are investigated in energies, orientational and positional parameters.
 
@@
 
+\section{Discussion}
+
+Comparing with bilayer structures, Figure~\ref{fig:BC2_shear}(a)--(c) demonstrate that the multilamellar ones are more rigid in shear flow and the rupture phenomenon can be observed 
+when the shear rate is high enough.
+
+For multilamellar structure in a Taylor-Green flow, as shown in Figure~\ref{fig:BC2_TG}(a)--(b), lower flow strengths such as $V_0=0.1,0.15$ do not reach a critical flow rate for structural disorder. 
+When $V_0=0.2$ (Figure~\ref{fig:BC2_TG}(c)), the flow is strong enough to separate the structure
+into multiple groups within the cells. In all deformation measures, a similar trend in shear flow case is observed, see Figure~\ref{fig:BC2_TG}(d)--(f).
+
 For a striated configuration in a Taylor-Green flow, numerical experiments have shown that one needs to choose relative higher flow strengths than other boundary conditions to reach structural disorder.
@@
 
-\section{Discussion}
+We place the striated configuration in a shear flow when $\dot\gamma=0.1, 0.125, 0.15$ and 
+the snapshots at $t=0.1\ \mu$s are shown in Figure~\ref{fig:BC3_shear}(a)--(c).
+Break-up deformation measures (igure~\ref{fig:BC3_shear}(d)--(f)) are similar to vesicle in shear flow case.
+Notably, for low shear rates, oscillatory behaviours are investigated in energies, orientational and positional parameters.
 

### 2022-07-14 doc/PRF2022/PRF_main.tex
picking away at paper

@@
 
+\usepackage{todonotes}
 \usepackage{graphicx}
@@
 % References should be done using the \cite, \ref, and \label commands
+
+\todo[inline]{Here are some references that Yuan sent around in the last
+few weeks}
+\cite{KolevaRehage2012_SoftMatter}
+\cite{GrandmaisonBrancherieSalasac2021_JFM}
+\cite{MusselLewisBasserHorkay2022_PRM}
+\cite{HuLongZangEHan2022_arxiv}
+\cite{BoccardoPierreLouis2022_PRL}
+
 \section{Introduction}
@@
 \section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
-The governing equations are a nonlinear system
-for the position and orientation of a collection of
-rigid Janus particles.
-We first pose the Stokes equations
-for the mobility problem giving the hydrodynamic interactions
-for the particle suspension.  
-The hydrophobic forces come from solving a screened Laplace equation.
-Particle collisions are avoided through a near-field, pair
-potential.
+The governing equations are a nonlinear system for the position and
+orientation of a collection of rigid Janus particles. We first pose the
+Stokes equations for the mobility problem giving the hydrodynamic
+interactions for the particle suspension. The hydrophobic forces come
+from solving a screened Laplace equation. Particle collisions are
+avoided through a near-field, pair potential.
 
@@
 A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
-The domain $\Omega(t) \subset \mathbb{R}^2$ is the solvent phase
-and $t$ is time.
-The particles are disks of radius $c$, center $\aa_i$, and
-orientation $\theta_i$ relative to the horizontal axis.  
-The boundary of the $\Omega$ is $\bd\Omega = \Gamma_1 \cup
-\cdots \cup \Gamma_{N_b}$, where $\Gamma_i$ is the boundary of Janus
-particle $i$. Assuming inertial terms are
-negligible, we have 
+The domain $\Omega(t) \subset \mathbb{R}^2$ is the solvent phase and $t$
+is time. The particles are disks of radius $c$, center $\aa_i$, and
+orientation $\theta_i$ relative to the horizontal axis. The boundary of
+$\Omega$ is $\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where
+$\Gamma_i$ is the boundary of Janus particle $i$. Assuming inertial
+terms are negligible, we have 
 \begin{alignat}{3}
@@
 \end{alignat}
-where $\uu$ is the velocity of the solvent,
-$p$ is the pressure, $\uu_\infty$ is the
-background flow velocity, and $\mu$ is the constant viscosity.
-The solvent velocity satisfies a no-slip boundary
-condition for a rigid body motion
+where $\uu$ is the velocity of the solvent, $p$ is the pressure,
+$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
+viscosity. The solvent velocity satisfies the no-slip boundary condition
+for a rigid body motion
 \begin{equation}
@@
 \end{equation}
-where $\vv_i$ is the translational velocity, $\omega_i$ is the
-angular velocity, and
-$\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.
-
-To close the system \eqref{eq:stokes}-\eqref{eq:rigid-vel},
-we use
+where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
+velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$. To
+close the system \eqref{eq:stokes}-\eqref{eq:rigid-vel}, we use
 \begin{equation}
@@
 
-To get $\FF_i$ and $T_i$,
-the particles minimize the free energy
+To determine $\FF_i$ and $T_i$, the particles minimize the free energy
 \begin{equation}
@@
 The cases (ii) and (iii) are obtained by applying a vertical shift
-and scaling to case (i), see Figure \ref{fig:bcs}.
+and scaling to case (i), see Figure~\ref{fig:bcs}.
 Using this setup, we simulate the dynamics of 60 particles with one set of random
-initial positions and orientations as shown in Figure~\ref{fig:relax}(a).
+initial positions and orientations as shown in Figure~\ref{fig:relax}(a)
 
@@
   \caption{\label{fig:bcs} Boundary conditions characterize the water
-    structure at the particle interface: an amphiphilic particle (left),
-    a hydrophobic
-  particle with anisotropic intensity (middle), a water structure with
-  positive/negative charge (right). The dashed curve is the boundary of the
-  disk and the arrow is its director for each particle.}
+  structure at the particle interface: an amphiphilic particle (left), a
+  hydrophobic particle with anisotropic intensity (middle), a water
+  structure with positive/negative charge (right). The dashed curve is
+  the boundary of the disk and the arrow is its director for each
+  particle.}
 \end{figure}
@@
 %
-Notice that for this simulation, the center of mass position of the initial configuration is not at the origin and it is slightly to the right of the origin.
-We also track the aspect ratio $\lambda$ for the case that the center of mass position is shifted to the origin.
-Panel (d) also shows that the dynamics
-of two sets of simulations are invariant of center of mass position in a shear flow.
+Notice that for this simulation, the center of mass position of the
+initial configuration is not at the origin and it is slightly to the
+right of the origin. We also track the aspect ratio $\lambda$ for the
+case that the center of mass position is shifted to the origin. Panel
+(d) also shows that the dynamics of two sets of simulations are
+invariant of center of mass position in a shear flow.
 

### 2022-07-15 doc/PRF2022/PRF_main.tex
small changes to paper

@@
 \end{gather}
-The boundary condition $g$ gives the degree of hydrophobicity
-the particle-solvent interface (Figure~\ref{fig:bcs}).
-
-Variation of the
-the free energy \eqref{eq:free_energy}
-provides
+The boundary condition $g$ gives the degree of hydrophobicity the
+particle-solvent interface.
+
+Variation of the the free energy \eqref{eq:free_energy} provides
 \begin{equation}
@@
 $
-is the hydrophobic stress identified in ~\cite{Fu20} 
-and derived by variation of the domain techniques.
-
-The dimensionless repulsion profile $P$
-takes the form
-$P(s) = 1 - \sin(\pi s/2)$ for $0 \leq s < 1$
-and $P(s) = 0$ for $1 \leq s < \infty$.
-As such, only those particles within
-a distance $\rho_0$ of $\Gamma_i$
-contribute to repulsion.
-The parameter $M$ is the repulsion modulus.
+is the hydrophobic stress identified in ~\cite{Fu20} and derived by
+variation of the domain techniques.
+
+The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
+\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
+\infty$.  As such, only those particles within a distance $\rho_0$ of
+$\Gamma_i$ contribute to repulsion.  The parameter $M$ is the repulsion
+modulus.
 
@@
 $\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.
+
 \subsection{Boundary integral represenation and time stepping}
-We recast \eqref{eq:stokes}-\eqref{eq:rigid-vel} and \eqref{eq:SL}
+We recast \eqref{eq:stokes}--\eqref{eq:rigid-vel} and \eqref{eq:SL}
 as boundary integral equations (BIEs) and discretize each BIE at
@@
 method. The boundary condition $g$ is a material label that is
-transported with the particle (Figure~\ref{fig:bcs}).
+transported with the particle.
 
@@
 = C \left[ \rho^{-1} f(u) \mathbf{I}
-  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
+  + \rho \left(|\nabla u|^2 \mathbf{I} - 
+  2\nabla u \nabla u^T\right)\right].
 \end{align}
 The imposed forces and torques come from the integration of $\mathbf{T}$
-along the particle boundary.
-These forces and torques couple the Stokes equations \eqref{eq:stokes},
-to semilinear elliptic equation \eqref{eq:SL}.
-Solving for the translational and rotational velocities gives the
-particle evolution.
+along the particle boundary. These forces and torques couple the Stokes
+equations \eqref{eq:stokes}, to semilinear elliptic equation
+\eqref{eq:SL}. Solving for the translational and rotational velocities
+gives the particle evolution.
 
@@
 \end{equation}
-  The number $\theta_i(\xx)$ is the angle formed by the position $\xx$, the
-particle center $\aa_i$, and the particle director $\dd_i$.% (Figure \ref{fig:flow_map}).
-The normalizations e.g., $(\pi r)^{-1/2}$, provide a uniform
-surface energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles
-of radius $r$. 
-The cases (ii) and (iii) are obtained by applying a vertical shift
-and scaling to case (i), see Figure~\ref{fig:bcs}.
-Using this setup, we simulate the dynamics of 60 particles with one set of random
-initial positions and orientations as shown in Figure~\ref{fig:relax}(a)
+The number $\theta_i(\xx)$ is the angle formed by the position $\xx$,
+the particle center $\aa_i$, and the particle director $\dd_i$.% (Figure
+\ref{fig:flow_map}).
+The normalizations e.g., $(\pi r)^{-1/2}$, provide a uniform surface
+energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles of radius
+$r$. The cases (ii) and (iii) are obtained by applying a vertical shift
+and scaling to case (i).  Using this setup, we simulate the dynamics of
+60 particles with one set of random initial positions and orientations
+as shown in Figure~\ref{fig:relax}(a)
 

### 2022-07-20 doc/PRF2022/PRF_main.tex
yny 0720 1

@@
 %  Add 'showkeys' option to make keywords appear
-\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
+%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
+\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-1}
+
 %\documentclass[aps,prl,preprint,superscriptaddress]{revtex4-2}
@@
 where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
-velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$. To
-close the system \eqref{eq:stokes}-\eqref{eq:rigid-vel}, we use
+velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$. 
+Without inertia, the system in \eqref{eq:stokes}-\eqref{eq:rigid-vel} also satisfies the force-free and torque-free conditions.
+This means that the total force $\FF_i,$ and torque $T_i$ from the hydrodynamic stress on each particle (with subscript `$i$')
+are in balance with the force and torque from the hydrophobic potential \cite{Fu2022_JFM}.
+The total force and torque from the fluid flow are computed as
 \begin{equation}
   \label{eq:force}
-  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i, \quad
-  \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
-  (\ssigma \cdot \nnu) \, \dif s = T_i,
+ \FF_i \equiv \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s, \quad
+ T_i \equiv \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
+  (\ssigma \cdot \nnu_i) \, \dif s,
   \quad i=1,\ldots,N_b,
 \end{equation}
-where $\FF_i \in \mathbb{R}^2$ and $T_i \in \mathbb{R}$
-are interparticle forces and torques. 
-Here $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
+where 
+%$\FF_i \in \mathbb{R}^2$ and $T_i \in \mathbb{R}$
+%are interparticle forces and torques. 
+$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
 \right)$ is the hydrodynamic stress tensor (pressure tensor), and
-$\nnu$ is the particle outward normal.
-
-To determine $\FF_i$ and $T_i$, the particles minimize the free energy
+$\nnu_i$ is the unit outward normal on the $i$th particle.
+
+$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
+particles and the viscous solvent. As in \citet{Fu2022_JFM} such a hydrophobic attraction potential $u(\xx,t)$ is assumed to
+the minimizer of the free energy
 \begin{equation}
@@
 \end{equation}
-Here, $u(\xx,t)$ is an order parameter for the structure of water,
+where the hydrophobic attraction potential $u(\xx,t)$ can be regarded as an order parameter for the structure of water,
 $\rho$ is a decay length, and $\gamma$ is an interfacial tension.
-We model water structure
-using the screened Laplace equation boundary value problem:
+
+The governing equation for $u(\xx,t)$ is obtained by computing the domain variation of the free energy $F$ \cite{Fu2018_SIAM}:
+We obtain
+a screened Laplace equation boundary value problem as a model for the hydrophobic interaction between water and JPs:
 \begin{gather}

### 2022-07-20 doc/PRF2022/PRF_main.tex
yny 0720 3

@@
 
-The governing equation for $u(\xx,t)$ is obtained by computing the domain variation of the free energy $F$ \cite{Fu2018_SIAM}:
+The governing equation for $u(\xx,t)$ is obtained by computing the domain variation of the free energy $F$ \cite{Fu20}:
 We obtain

### 2022-07-20 doc/PRF2022/PRF_main.tex
yny 0720 4

@@
 $\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
+$c$ is an ``effective" inter-particle distance below which the steric repulsion between a pair of JPs becomes important.
 
@@
 caused by close contact between two particles, are computed with a
-high-order interpolation-based quadrature rule (\cite{qua-bir2014}).
+high-order interpolation-based quadrature rule \cite{qua-bir2014}.
 
@@
 decay length, $C$ is a constant, and $f(u)$ is a potential.
+%$c$ is ``effective" inter-particle distance below which the steric repulsion becomes important.
 Hydrogen-bond persistence times are on the order of picoseconds which is

### 2022-07-20 doc/PRF2022/PRF_main.tex
yny 0720 5

@@
 $\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
-$c$ is an ``effective" inter-particle distance below which the steric repulsion between a pair of JPs becomes important.
+$c$ is an ``effective" distance between particle centers, below which the steric repulsion between a pair of JPs becomes important.
+In the followings we use the radius of JP for $c$.
 
@@
 \end{equation}
-where $\alpha$ is the angle between $\xx - \aa_i$ and the particle director
-$\dd_i = (\cos \theta_i, \sin \theta_i)$.
+where $\alpha$ is the angle between $\xx$ and  $\aa_i$, and 
+$\dd_i = (\cos \theta_i, \sin \theta_i)$ isthe particle director.
 The parameter $a$ normalizes the boundary conditions 
@@
 
+The boundary condition on JP can be put into three categories: min$(g) >0$, min$(g) =0$, and min$(g) <0$. Without loss of generality, 
+these three categories correspond to three characteristic values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
+%
 To see the effect of the shift parameter $b$, we simulate the dynamics of

### 2022-07-20 doc/PRF2022/PRF_main.tex
yny 0720 6

@@
 Both sides of the Janus particle are hydrophobic but
-moreso on the $\alpha = 0$ side.  
+more so on the $\alpha = 0$ side.  
 Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
@@
 
-A water structure with
-positive/negative charge is possible in case (iii), $b = 0$
-\cite{MaRa76, Ma77}.
+In case (iii) with $b=1$,
+a water structure with
+positive/negative charge is possible \cite{MaRa76, Ma77}.
 Here, the head repels the tail of other particles

### 2022-07-20 doc/PRF2022/PRF_main.tex
yny 0720 7

@@
 
-The boundary condition on JP can be put into three categories: min$(g) >0$, min$(g) =0$, and min$(g) <0$. Without loss of generality, 
+The boundary condition on JP can be classified into three categories: min$(g) >0$, min$(g) =0$, and min$(g) <0$. Without loss of generality, 
 these three categories correspond to three characteristic values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
@@
 Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
-See the Appendix section \ref{sec:appendix} for the proof and details.
+See Appendix in \S\ref{sec:appendix} for the proof and details.
 Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
@@
 This can be considered as evidence that the free energy per particle with specified
-boundary condtions is independent of number of particles.
+boundary condtions is independent of the total particle number $(N_b)$.
 

### 2022-07-20 doc/PRF2022/PRF_main.tex
yny July20 10

@@
 \end{gather}
+With 
 The boundary condition $g$ gives the degree of hydrophobicity the
@@
 
-The boundary condition on JP can be classified into three categories: min$(g) >0$, min$(g) =0$, and min$(g) <0$. Without loss of generality, 
+With max$(g)>0$ to guarantee (at least partial) hydrophobic surface on each JP,  
+the boundary condition can be classified into three categories: min$(g) >0$, min$(g) =0$, and min$(g) <0$. Without loss of generality, 
 these three categories correspond to three characteristic values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
@@
 
-Figure~\ref{fig:relax}(a)shows the initial configurations with orientations of 198-particle and 60- particle cases,
+Figure~\ref{fig:relax}(a) shows the initial configurations with orientations of 198-particle and 60- particle cases,
 respectively. 
-Case (i) with $b = 1$, mimicks an amphiphilic particle.
+Case (i) with $b = 1$ (bc(i)) mimicks an amphiphilic particle.
 The boundary condition $g$ is everywhere nonnegative,
@@
 
-In case (ii) with $b = 1$, the boundary condition is everywhere positive.
+In case (ii) with $b = 1$ (bc(ii)) the boundary condition is everywhere positive.
 It takes the maximum value $3a$ on tail (red) and the
@@
 
-In case (iii) with $b=1$,
+In case (iii) with $b=1$ (bc(iii))
 a water structure with
@@
 
-\subsection{Bilayer configurations in a shear flow}
-To begin, we place the bilayer structure (Figure~\ref{fig:relax}(b), inset)
-in the shear background flow
+\subsection{Bilayer configurations (bc(i)) in a linear shear flow}
+To begin, we place the bilayer structure (with bc(i)) from the inset of Figure~\ref{fig:relax}(b)
+in a linear shear flow
 \begin{equation}
@@
 are horizontal and vertical unit vectors, respectively.  
+The initial bilayer structure consists of a small self-enclosing bilayer (vesicle) and several pieces of bilayers.
 Figure~\ref{fig:BC1_shear}(a)--(c)
-shows snapshots of the vesicle when $\dot\gamma= 0.05,0.075,0.01$
+shows snapshots of the bilayer when $\dot\gamma= 0.05,0.075,0.01$
 at $t = 0.5$ $\upmu$s.
-The general pattern consists of a rotating body.  The various bilayer components
-detach and reattach throughout so that the boyd is continuously changing morphology.
-The supplementary movies show that these bilayers merge and form a worm-like shape in higher 
-shear flows.
-
+The dynamics of the bilayer can be found in the supplementary movies, which show that the initial pieces of bilayers merge and form a worm-like shape
+under a linear shear flow.
+At a low shear rate, the bilayer constantly goes through rotation and extensional deformation with the whole bilayer intact (figure~\ref{fig:BC1_shear}(a)).
+As the shear rate increases to a moderate value (figure~\ref{fig:BC1_shear}(b)), the bilayer is observed to shed a small piece of bilayer, similar to the asymmetric breakup of a viscous drop \cite{}.
+In figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two nearly equal bilayers, similar to the symmetric drop breakup under a linear shear flow \cite{}.
+%
 \begin{figure}
@@
 are relatively constant (Figure~\ref{fig:BC1_shear}(d)),
-with the overall changes in the range of a few kT/nm.  Note that the free energy takes
-the form of a line tension because the simulations are two-dimensional.
-
-An interesting feature of the simulations is that the $\tilde S_2$ order parameter
-is on the average increasing (Figure~\ref{fig:BC1_shear}(e)).  In the initial configuration,
-the structure has three or four components.  Under the shear flow, the detachment and reattachment
-results in an overall decrease in the number of components.  This suggests that
-the shear flow perturbs the local equilibrium obtained from a random initial condition
+with the overall changes in the range of a few kT/nm.  
+Note that the free energy $F$ in figure~\ref{fig:BC1_shear}(d) has the unit of force because our system is two dimensional.
+
+An interesting feature of the simulations is that the order parameter $\tilde S_2$ in (Figure~\ref{fig:BC1_shear}(e))
+is on average increasing.  In the initial configuration,
+the structure has three or four components.  
+%
+Under the shear flow, the shedding and merging of bilayers
+result in an overall decrease in distinct bilayer structures.  
+This suggests that
+the shear flow changes the energy landscape to move the local equilibrium obtained from a random initial condition
 to an alternate local equilibrium with greater orientational order.
@@
 \end{figure}
-
+%
 Finally, the strain parameter diverges in the large shear flow rate cases (Figure~\ref{fig:BC1_shear}(f))
@@
 
+In \citet{Fu2022_JFM} the hydrodynamics of a JP vesicle under a linear shear flow is studied. 
+Focusing on drawing analogies to hydrodynamics of a vesicle in continuum modeling (such as tank-treading, bilayer slip and permeability),
+our previous studies also show the existence of a critical shear rate above which the JP vesicle ruptures. 
+Based on the these early results, we conduct numerical simulations with $\dot\gamma=0.05, 0.066, 0.075$.
+At these shear rates, the vesicle undergoes the familiar hydrodynamics (such as elongation along the extensional axis and tank-treading motion),
+as shown in Figure~\ref{fig:Ves_shear} (a)--(c).
+%
+Here we illustrate how the three measures of structural deformation 
+correlate to the dynamics of a JP vesicle.
 We reinitialized the case (i) configuration with particles arranged in the pattern of a single, circular vesicle.
@@
 Figure~\ref{fig:BC1_shear}(d) and Figure~\ref{fig:Ves_shear} (d).
-Our previous paper \cite{Fu2022_JFM} studied
-The vesicle in a shear flow undergoes the familiar tank-treading deformation (Figure~\ref{fig:Ves_shear} (a)--(c)),
-and based on previous results (\cite{Fu2022_JFM}),
-we investigate the cases $\dot\gamma=0.05, 0.066, 0.075$.
-
-Unlike the multiples component case, 
-the energies for the vesicle case show jumps from the baseline value $30$ kT/nm to 32 kT/nm
+
+Unlike the dynamics of bilayers in figure~\ref{fig:BC1_shear}, 
+the energies of the JP vesicle in figure~\ref{fig:Ves_shear}(d) show jumps from the baseline value $30$ kT/nm to 32 kT/nm
 signaling the rupture of the vesicle into multiple components

### 2022-07-21 doc/PRF2022/PRF_main.tex
yny July20 10

@@
 %%%
-%%%
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
-  \end{center}
-  \caption{
-    \label{fig:Ves_shear}
-The figure shows a single vesicle in a shear flow.
-Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
-The streamlines are plotted in the background.
-Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
-     }
-\end{figure}
 
@@
 At a low shear rate, the bilayer constantly goes through rotation and extensional deformation with the whole bilayer intact (figure~\ref{fig:BC1_shear}(a)).
-As the shear rate increases to a moderate value (figure~\ref{fig:BC1_shear}(b)), the bilayer is observed to shed a small piece of bilayer, similar to the asymmetric breakup of a viscous drop \cite{}.
-In figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two nearly equal bilayers, similar to the symmetric drop breakup under a linear shear flow \cite{}.
-%
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
- The streamlines are plotted in the background. 
-Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
-  }
-\end{figure}
-
-In terms of deformations, 
+As the shear rate increases to a moderate value (figure~\ref{fig:BC1_shear}(b)), the bilayer is observed to shed a small piece of bilayer, 
+similar to the asymmetric breakup of a viscous drop \cite{}.
+In figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two separate, nearly equal bilayers, 
+similar to the symmetric drop breakup under a linear shear flow \cite{}.
+%%
+%\begin{figure}
+%  \begin{center}
+%    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
+%  \end{center}
+%  \vspace{-20pt}  
+%  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
+% The streamlines are plotted in the background. 
+%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
+%  }
+%\end{figure}
+
+In terms of deformation measures,  
 the free energies 
@@
 
-An interesting feature of the simulations is that the order parameter $\tilde S_2$ in (Figure~\ref{fig:BC1_shear}(e))
+An interesting feature of the simulations is that the order parameter $\tilde S_2$ in figure~\ref{fig:BC1_shear}(e)
 is on average increasing.  In the initial configuration,
@@
 to an alternate local equilibrium with greater orientational order.   
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
-  \end{center}
-\caption{\label{fig:ves_TG} Single vesicle in a TG flow.
+%
+%\begin{figure}
+%  \begin{center}
+%    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
+%  \end{center}
+%\caption{\label{fig:ves_TG} Single vesicle in a TG flow.
 Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
+The streamlines are plotted in the background.
+%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
+%}
+%\end{figure}
+%
+Finally, the strain parameter diverges in the large shear flow rate cases (Figure~\ref{fig:BC1_shear}(f))
+because the components eventually completely separate and move away from one another
+under the shear flow.
+
+%%%
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
+  \end{center}
+  \caption{
+    \label{fig:Ves_shear}
+The figure shows a single vesicle in a shear flow.
+Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
 The streamlines are plotted in the background.
@@
 %
-Finally, the strain parameter diverges in the large shear flow rate cases (Figure~\ref{fig:BC1_shear}(f))
-because the components eventually completely separate and move away from one another
-under the shear flow.
-
 In \citet{Fu2022_JFM} the hydrodynamics of a JP vesicle under a linear shear flow is studied. 
@@
 the energies of the JP vesicle in figure~\ref{fig:Ves_shear}(d) show jumps from the baseline value $30$ kT/nm to 32 kT/nm
-signaling the rupture of the vesicle into multiple components
-(Figure \ref{fig:Ves_shear}(d), long and short dashed curves).
-After this initial break, the energies are more or less constant.
+signaling the rupture of the vesicle into disconnected bilayers
+(see figure \ref{fig:Ves_shear}(d), long and short dashed curves).
+After the rupture, each piece circles around the vorticity at the center without reconnection while the energies fluctuate slightly around a constant.
 
 For the lowest shear rate case, the vesicle has nearly constant orientational order $\tilde S_2 = 1$
-(Figure \ref{fig:Ves_shear}(e), solid curve).
-Following rupture ($\dot\gamma= 0.066$ and $\dot \gamma= 0.075$),
-there is greater variation in the order parameter $\tilde{S}_2$
+(see figure \ref{fig:Ves_shear}(e), solid curve).
+After the JP vesicle
+ruptures with $\dot\gamma= 0.066$ and $\dot \gamma= 0.075$,
+we observe a greater variation in the order parameter $\tilde{S}_2$
 with a baseline value around $0.7$
-(Figure \ref{fig:Ves_shear}(e), dashed curves).
+(see figure \ref{fig:Ves_shear}(e), dashed curves).
 The oscillations occur due to the orbit of the two bilayer components,
 and $\tilde{S}_2$ increases to about $0.9$ when the components slide past one another and are nearly parallel.
-
-Like with multiple component bilayer case, positional order diverges when the components of the ruptured
-vesicle separate and drift off in opposite directions (Figure \ref{fig:Ves_shear}(f), dashed curves).
+%
+As in the previous case, peaks in the strain parameter $E$ correlate well with changes in structural topology in the bilayer dynamics, see
+the dashed curves in figure~\ref{fig:Ves_shear}(f).
 
 %%%%%%%
+%
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
+  \end{center}
+  \vspace{-20pt}  
+  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
+ The streamlines are plotted in the background. 
+Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
+  }
+\end{figure}
+%
 \subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
@@
 %
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
+  \end{center}
+\caption{\label{fig:ves_TG} Single vesicle in a TG flow.
+Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
+The streamlines are plotted in the background.
+Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
+}
+\end{figure}
 

### 2022-07-21 doc/PRF2022/PRF_main.tex
yny July20 12

@@
 \left(
--\cos\left(\frac{{\bf e}_x\cdot\xx}{\lambda}\right)
- \sin\left(\frac{{\bf e}_y\cdot\xx}{\lambda}\right)
+-\cos\left(\frac{{\bf e}_x\cdot\xx}{l}\right)
+ \sin\left(\frac{{\bf e}_y\cdot\xx}{l}\right)
          {\bf e}_x
-         +\sin\left(\frac{{\bf e}_x\cdot\xx}{\lambda}\right)
-         \cos\left(\frac{{\bf e}_y\cdot\xx}{\lambda}\right)
+         +\sin\left(\frac{{\bf e}_x\cdot\xx}{l}\right)
+         \cos\left(\frac{{\bf e}_y\cdot\xx}{l}\right)
              {\bf e}_y\right).
@@
 of cells with alternating circulation.  We control the flow by the
-the dimensionless flow strength $V_0$ and with the cell size $\lambda = l$ nm.
-The default parameter $l=2$ is used through this work.
+the dimensionless flow strength $V_0$ and with the cell size $l$ nm.
+For most of the results here the cell size $l=2$ is used in this subsection.
 %

### 2022-07-24 doc/PRF2022/PRF_main.tex
YNY july24

@@
 \begin{abstract}
+Active colloidal systems with non-equilibrium self-organization is a long-standing challenge in biology. To understand how hydrodynamic flow may be used
+to actively control self-assembly of Janus particles (JPs),  we use a model recently developed for the many-body hydrodynamics of amphiphilic JPs suspended 
+in a viscous background flow (JFM, 941, 2022). We investigate how various bilayer structures arise from tuning the hydrophobicity/hydrophilicity of the JPs. 
+Focusing on three distributions of hydrophobicity we found JPs may assemble into uni-lamella, multi-lamella, and striated structures in a viscous fluid. 
+Under a linear flow and a Taylor-Green mixing flow,  we use three measures to quantify the collective dynamics of JP particles under a background flow: 
+(a) Free energy from the hydrophobic interactions between the JPs, (b) an order parameter for the ordering of JPs in terms of alignment of their directors, 
+and (c) a strain parameter that captures the deformation in the assembly. We found the dynamics of these three measures correlate well with the hydrodynamics 
+of JPs. These numerical provide insights into dynamic control of non-equilibrium active biological systems with similar self-organization.
 % insert abstract here

### 2022-07-25 doc/PRF2022/PRF_main.tex
started section II

@@
 for a rigid body motion
-\begin{equation}
+\begin{align}
   \label{eq:rigid-vel}
@@
     \quad \xx \in \Gamma_i,
-\end{equation}
+\end{align}
 where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
 velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.
-Without inertia, the system in \eqref{eq:stokes}-\eqref{eq:rigid-vel} also satisfies the force-free and torque-free conditions.
-This means that the total force $\FF_i,$ and torque $T_i$ from the hydrodynamic stress on each particle (with subscript `$i$')
-are in balance with the force and torque from the hydrophobic potential \cite{Fu2022_JFM}.
-The total force and torque from the fluid flow are computed as
-\begin{equation}
+Without inertia, the system in~\eqref{eq:stokes}-\eqref{eq:rigid-vel}
+also satisfies the force-free and torque-free conditions.
+%This means
+%that the total force $\FF_i,$ and torque $T_i$ from the hydrodynamic
+%stress on each particle (with subscript `$i$') balance the force and
+%torque from the hydrophobic potential~\cite{Fu2022_JFM}. 
+The total force
+and torque from the fluid flow are
+\begin{align}
   \label{eq:force}
- \FF_i \equiv \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s, \quad
- T_i \equiv \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
+ \FF_i = \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s, \quad
+ T_i = \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
   (\ssigma \cdot \nnu_i) \, \dif s,
   \quad i=1,\ldots,N_b,
-\end{equation}
-where 
-%$\FF_i \in \mathbb{R}^2$ and $T_i \in \mathbb{R}$
-%are interparticle forces and torques. 
-$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
-\right)$ is the hydrodynamic stress tensor (pressure tensor), and
-$\nnu_i$ is the unit outward normal on the $i$th particle.
-
-$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
-particles and the viscous solvent. As in \citet{Fu2022_JFM} such a hydrophobic attraction potential $u(\xx,t)$ is assumed to
-the minimizer of the free energy
-\begin{equation}
+\end{align}
+respectively, where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu +
+\nabla \uu^T \right)$ is the hydrodynamic stress tensor (pressure
+tensor), and $\nnu_i$ is the unit outward normal on the $i$th particle.
+
+The total force $\FF_i,$ and torque $T_i$ from the hydrodynamic
+stress on each particle (with subscript `$i$') balance the force and
+torque from the hydrophobic potential. 
+%$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
+%particles and the viscous solvent. 
+As in~\citet{Fu2022_JFM} such a hydrophobic attraction potential
+$u(\xx,t)$ is assumed to the minimizer of the free energy
+\begin{align}
 \label{eq:free_energy}
 F = \gamma
-\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
+  \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} u^2 \right)
 \,d\xx
@@
 P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
-\end{equation}
+\end{align}
 where the hydrophobic attraction potential $u(\xx,t)$ can be regarded as an order parameter for the structure of water,
@@
 $c$ is an ``effective" distance between particle centers, below which the steric repulsion between a pair of JPs becomes important.
-In the followings we use the radius of JP for $c$.
-
-The governing equation for $u(\xx,t)$ is obtained by computing the domain variation of the free energy $F$ \cite{Fu20}:
-We obtain
-a screened Laplace equation boundary value problem as a model for the hydrophobic interaction between water and JPs:
-\begin{gather}
+In the followings we let $c$ be the radius of each JP.
+
+The governing equation for $u(\xx,t)$ is obtained by computing the
+domain variation of the free energy $F$~\cite{Fu20}. We obtain a
+screened Laplace equation boundary value problem as a model for the
+hydrophobic interaction between water and JPs:
+\begin{alignat}{3}
   \label{eq:SL}
-  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
-  u = g, \quad \xx \in \bd\Omega, \quad 
-  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
-\end{gather}
-With 
-The boundary condition $g$ gives the degree of hydrophobicity the
+  -\rho^2 \Delta u + u &= 0,\qquad &&\xx \in \Omega, \\
+  u &= g, &&\xx \in \bd\Omega, \\
+  u &\rightarrow 0, &&|\xx| \rightarrow \infty,
+\end{alignat}
+where the boundary condition $g$ gives the degree of hydrophobicity the
 particle-solvent interface.
 
-Variation of the the free energy \eqref{eq:free_energy} provides
-\begin{equation}
+The hydrophobic stress is
+\begin{align}
+\mathbf{T}
+= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
+  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
+\end{align}
+and is derived by applying variation of domain techniques to the free
+energy~\eqref{eq:free_energy}~\cite{Fu20}. Then, the hydrophobic force
+and torque are
+\begin{align}
   \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
@@
 T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
-\end{equation}
-for $i = 1,\dots,N_b$. The term 
-$
-\mathbf{T}
-= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
-  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
-$
-is the hydrophobic stress identified in ~\cite{Fu20} and derived by
-variation of the domain techniques.
-
-The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
-\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
+\end{align}
+which balance the hydrodynamic force and torque~\eqref{eq:force}, for $i
+= 1,\dots,N_b$. 
+%The term 
+%\begin{align}
+%\mathbf{T}
+%= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
+%  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
+%\end{align}
+%is the hydrophobic stress~\cite{Fu20} and derived by variation of the
+%domain techniques.
+
+Finally, the dimensionless repulsion profile $P$ takes the form $P(s) =
+1 - \sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
 \infty$.  As such, only those particles within a distance $\rho_0$ of
@@
 
-We use the parameters $\mu = 1$ cP, $\gamma = 4$ pN nm$^{-1}$,
-$\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.
-
+We use the same parameters from previous work~\cite{Fu2022_JFM}: $\mu =
+1$ cP, $\gamma = 4$ pN nm$^{-1}$, $\rho = 5$ nm, $c = 1.25$ nm, $M = 2$
+pN, and $\rho_0 = 0.5$ nm.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Boundary integral represenation and time stepping}

### 2022-07-25 doc/PRF2022/PRF_main.tex
discussion completed; abstract added

--- 2022-07-24 doc/PRF2022/PRF_main.tex
@@
 \subsection{Mobility problem}
-A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
+%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
+%RJR: In the above sentence, suspection and immersed are redundant 
+The Janus particles are suspended in a viscous solvent.
+The particles are disks of radius $c$, center $\aa_i$, and
+orientation $\theta_i$ relative to the horizontal axis, where $i = 1, \dots, N_b$
+and $N_b$ is the number of particles.
 The domain $\Omega(t) \subset \mathbb{R}^2$ is the solvent phase and $t$
-is time. The particles are disks of radius $c$, center $\aa_i$, and
-orientation $\theta_i$ relative to the horizontal axis. The boundary of
+is time.  The boundary of
 $\Omega$ is $\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where
@@
 velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.
-Without inertia, the system in \eqref{eq:stokes}-\eqref{eq:rigid-vel} also satisfies the force-free and torque-free conditions.
-This means that the total force $\FF_i,$ and torque $T_i$ from the hydrodynamic stress on each particle (with subscript `$i$')
-are in balance with the force and torque from the hydrophobic potential \cite{Fu2022_JFM}.
-The total force and torque from the fluid flow are computed as
-\begin{equation}
-  \label{eq:force}
- \FF_i \equiv \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s, \quad
- T_i \equiv \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
-  (\ssigma \cdot \nnu_i) \, \dif s,
-  \quad i=1,\ldots,N_b,
-\end{equation}
-where 
-%$\FF_i \in \mathbb{R}^2$ and $T_i \in \mathbb{R}$
-%are interparticle forces and torques. 
-$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
-\right)$ is the hydrodynamic stress tensor (pressure tensor), and
-$\nnu_i$ is the unit outward normal on the $i$th particle.
-
-$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
-particles and the viscous solvent. As in \citet{Fu2022_JFM} such a hydrophobic attraction potential $u(\xx,t)$ is assumed to
-the minimizer of the free energy
+
+Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free conditions.
+This means that the force and torque from the hydrodynamic stress on each particle 
+are in balance with the total
+force and torque coming from the hydrophobic potential and repulsion \cite{Fu2022_JFM}.
+To compute this balance, we define
+the free energy\cite{Fu2022_JFM}
 \begin{equation}
@@
 \end{equation}
-where the hydrophobic attraction potential $u(\xx,t)$ can be regarded as an order parameter for the structure of water,
+where $u(\xx,t)$ is as an order parameter for the structure of water,
 $\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
-$c$ is an ``effective" distance between particle centers, below which the steric repulsion between a pair of JPs becomes important.
-In the followings we use the radius of JP for $c$.
-
-The governing equation for $u(\xx,t)$ is obtained by computing the domain variation of the free energy $F$ \cite{Fu20}:
-We obtain
-a screened Laplace equation boundary value problem as a model for the hydrophobic interaction between water and JPs:
+The parameter $\rho_0$ is an ``effective" distance between particle centers,
+below which the steric repulsion between a pair of JPs becomes important.
+
+The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$ \cite{Fu20}.
+Its governing equations $u(\xx,t)$ 
+are a screened Laplace equation boundary value problem
+as a model for the hydrophobic interaction between water and JPs:
 \begin{gather}
@@
   -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
+  \label{eq:SLbc}
   u = g, \quad \xx \in \bd\Omega, \quad 
@@
 \end{gather}
-With 
-The boundary condition $g$ gives the degree of hydrophobicity the
+The boundary condition $g$ encodes hydrophobic properties of the
 particle-solvent interface.
 
-Variation of the the free energy \eqref{eq:free_energy} provides
+To get forces and torques from the free energy,
+we compute the variation of the domain of the free energy 
+\eqref{eq:free_energy} subject to \eqref{eq:SL}-\eqref{eq:SLbc},
+and obtain 
 \begin{equation}
-  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
+  \FF_i \equiv \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
   - \frac{M}{\rho_0}
@@
   ,\quad
-T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
+T_i \equiv \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
 \end{equation}
-for $i = 1,\dots,N_b$. The term 
+for $i = 1,\dots,N_b$ with particle outward normal $\nu$. The term 
 $
@@
 $
-is the hydrophobic stress identified in ~\cite{Fu20} and derived by
-variation of the domain techniques.
+is the hydrophobic stress.
+Repulsion is rotationally symmetric and does not contribute to the torque.
+The derivation details are found in \citet{Fu20}.
+
+Since the force and torque from the hydrodynamic stress on each particle
+are in balance with the total force and torque coming from the
+hydrophobic potential and repulsion, we have
+\begin{equation}
+  \label{eq:force}
+ \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i, \quad
+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
+  (\ssigma \cdot \nnu) \, \dif s = T_i,
+  \quad i=1,\ldots,N_b,
+\end{equation}
+where 
+%$\FF_i \in \mathbb{R}^2$ and $T_i \in \mathbb{R}$
+%are interparticle forces and torques. 
+$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
+\right)$ is the hydrodynamic stress tensor (pressure tensor).
 
@@
 
-Once the translational and angular velocities $\vv_i, \omega_i$
-have been determined, a second-order Adams-Bashforth scheme updates the particle
-positions and orientations:
-\begin{equation}
-  \label{eq:adams-bashforth}
-  \begin{aligned}
-    \aa_i(t_{n+2}) &=
-\aa_i(t_{n+1})
-+ \tfrac{3}{2}\Delta t \vv_i(t_{n+1})
-- \tfrac{1}{2}\Delta t \vv_i(t_{n}),\\
-    \theta_i(t_{n+2}) &=
-\theta_i(t_{n+1})
-+ \tfrac{3}{2}\Delta t \omega_i(t_{n+1})
-- \tfrac{1}{2}\Delta t \omega_i(t_{n}).
-  \end{aligned}
-\end{equation}
+%Once the translational and angular velocities $\vv_i, \omega_i$
+%have been determined, a second-order Adams-Bashforth scheme updates the particle
+%positions and orientations:
+%\begin{equation}
+%  \label{eq:adams-bashforth}
+%  \begin{aligned}
+%    \aa_i(t_{n+2}) &=
+%\aa_i(t_{n+1})
+%+ \tfrac{3}{2}\Delta t \vv_i(t_{n+1})
+%- \tfrac{1}{2}\Delta t \vv_i(t_{n}),\\
+%    \theta_i(t_{n+2}) &=
+%\theta_i(t_{n+1})
+%+ \tfrac{3}{2}\Delta t \omega_i(t_{n+1})
+%- \tfrac{1}{2}\Delta t \omega_i(t_{n}).
+% \end{aligned}
+%\end{equation}
 
@@
 \end{equation}
-where $\alpha$ is the angle between $\xx$ and  $\aa_i$, and 
-$\dd_i = (\cos \theta_i, \sin \theta_i)$ isthe particle director.
+where $\alpha$ is the angle between the vector $\xx - \aa_i$ and 
+the particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$.
 The parameter $a$ normalizes the boundary conditions 
-so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
+so that $\int_{\Gamma_i} g^2(\xx) \, \dif s =  2\pi c$.
 The motivation for this normalization is that the hydrophobic attraction
@@
 
-With max$(g)>0$ to guarantee (at least partial) hydrophobic surface on each JP,  
-the boundary condition can be classified into three categories: min$(g) >0$, min$(g) =0$, and min$(g) <0$. Without loss of generality, 
-these three categories correspond to three characteristic values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
+We set $\max g>0$ to guarantee at least partial hydrophobicity of the JP surface.
+Then, the boundary condition (BC) can be classified into
+three categories: $\min g >0$, $\min g =0$, and $\min g <0$.  
+These three categories correspond to three characteristic
+values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
 %
 To see the effect of the shift parameter $b$, we simulate the dynamics of
-198 particles and 60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
+198 particles and 60 particles in a quiescent flow as shown in Fig~\ref{fig:relax}.
 Three distinct configurations emerge:
-(i) bilayers for $b = 1$, 
+(i) bilayer for $b = 1$, 
 (ii) multilamellar for $b = 2$, and 
@@
 
-Figure~\ref{fig:relax}(a) shows the initial configurations with orientations of 198-particle and 60- particle cases,
+Fig~\ref{fig:relax}(a) shows the initial configurations with
+orientations of the 198-particle and 60-particle cases,
 respectively. 
-Case (i) with $b = 1$ (bc(i)) mimicks an amphiphilic particle.
-The boundary condition $g$ is everywhere nonnegative,
-takes the value $0$ on the
-hydrophilic head (green),
-and takes the maximum value $a$ on the
-hydrophobic tail (red). 
+BC (i) with $b = 1$ mimicks an amphiphilic particle.
+The boundary data $g$ is everywhere nonnegative,
+and takes
+the maximum value $a$ on the hydrophobic tail (red)
+the value $0$ on the hydrophilic head (green). 
 The interaction is attractive, and particles collectively orient their
-hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)). The inset shows the equilibrium 
-state for 60-particle run.
+hydrophobic sides to form bilayers  (Fig~\ref{fig:relax}(b)). The inset shows the equilibrium 
+state for the 60-particle run.
 Both cases form bilayers with multiple components.
 
-In case (ii) with $b = 1$ (bc(ii)) the boundary condition is everywhere positive.
-It takes the maximum value $3a$ on tail (red) and the
+In BC (ii) with $b = 1$, the boundary data is everywhere positive.
+It takes the maximum value $3a$ on the tail (red) and the
 minimum value $a$ on the head side (yellow). 
@@
 more so on the $\alpha = 0$ side.  
-Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
+Over a short time scale, these particles also self-assemble into bilayers. But unlike for  (i),
 the heads are also hydrophobic and so in the long-time dynamics
@@
 The number of folds depends primarily on the number of particles.
-Figure~\ref{fig:relax}(c), for example, shows a
+Fig~\ref{fig:relax}(c), for example, shows a
 multilamellar structure with four layers and one with two layers in the inset.
 
-In case (iii) with $b=1$ (bc(iii))
-a water structure with
-positive/negative charge is possible \cite{MaRa76, Ma77}.
+Finally, BC (iii) with $b=1$ 
+corresponds to a water structure with
+positive/negative charge \cite{MaRa76, Ma77}.
 Here, the head repels the tail of other particles
@@
 square grid and the orientations alternate
-between layers (Figure~\ref{fig:relax}(d)).
+between layers (Fig~\ref{fig:relax}(d)).
 
@@
     in the mobility problem formulation.  The initial energies
-    are for the configuration in Figure \ref{fig:relax}(a)
+    are for the configuration in Fig \ref{fig:relax}(a)
     and the final energies are for the near-equilibrium
-    configurations as shown in Figure \ref{fig:relax}(b)--(d), respectively.
+    configurations as shown in Fig \ref{fig:relax}(b)--(d), respectively.
     The solid curves are the energies for the $N_b=60$ cases and  
@@
 
-Figure~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
+Fig~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
 For the 198-particle cases, we normalized the energies by 60/198 and the results
@@
 multilamellar structures.  In these cases, the directors 
-are more or less bilayer uniformly distributed along a circle, even though
+are more or less uniformly distributed along a circle, even though
 there is orientational order between neighboring particles.
@@
 \tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
-\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1).
+\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1),
 \end{equation}
@@
 
-Figure~\ref{fig:relax_energy}(b) 
+Fig~\ref{fig:relax_energy}(b) 
 tracks the orientational order parameter $\tilde{S}_2$.
@@
 structures show similar trends in the small and large particle number systems
-(Figure \ref{fig:relax}(b) black curves, red curves respectively).
-The multilamellar structures are highly ordered in all cases (Figure~\ref{fig:relax}(c))
+(Fig \ref{fig:relax_energy}(b) black curves, red curves respectively).
+The multilamellar structures are highly ordered in all cases (Fig~\ref{fig:relax}(c))
 whereas the bilayer structures
-are disordered because they consist of several connected
-components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
-
-The aggregation for striated configurations form more than one 
-pattern when the number of particles is varied (Figure~\ref{fig:relax}(d)).
+are disordered because they consist of several 
+components forming isolated bilayers, micelles, and vesicles (Fig~\ref{fig:relax}(b)).
+
+The aggregation for striated configurations forms more than one 
+pattern when the number of particles is varied (Fig~\ref{fig:relax}(d)).
 We observe that when the number of particles is fewer, there is only
-a single alternating pattern in particle orientations where the directors
-are more or less parallel and alternate directions between stria (Figure~\ref{fig:relax}(d), inset).
+a single pattern in particle orientations where the directors
+are more or less parallel and alternate directions (Fig~\ref{fig:relax}(d), inset).
 Larger number of particles results in two different patterns: the alternating sign pattern
-as in the small particle number case (Figure~\ref{fig:relax}(d), 
+as in the small particle number case (Fig~\ref{fig:relax}(d), 
 top right rectangle) and one where the directors reflect across the lines parallel
-to the stria and across the lines perpendicular to the stria (Figure~\ref{fig:relax}(d),
+to the stria and across the lines perpendicular to the stria (Fig~\ref{fig:relax}(d),
 top middle rectangle).
 As a result, there are different trends in orientational order
-(Figure~\ref{fig:relax_energy}(b), solid and dashed blue curves, respectively).
+(Fig~\ref{fig:relax_energy}(b), solid and dashed blue curves, respectively).
 
 In the Results section,
-the equilibrium configurations for cases (i), (ii), and (iii)
-(Figure~\ref{fig:relax}, insets) are
+the equilibrium configurations for BCs (i), (ii), and (iii)
+(Fig~\ref{fig:relax}, insets) are
 used as initial data in the
 background flow simulations. 
-For the bilayer case (i), we include an alternate initial condition 
-consisting of a single, circular vesicle (c.f., Figure~\ref{fig:Ves_shear}).
+For the bilayer case BC (i), we include an alternate initial condition 
+consisting of a single, circular vesicle (c.f., Fig~\ref{fig:Ves_shear}).
 
@@
     Panels (a)-(c) are a snapshot at $t=0.5\ \mu$s of the multiple-component bilayer
-    with shear flow rate $\dot \gamma = \{0.05, 0.075, 0.1\}$.
+    with shear rate $\dot \gamma = \{0.05, 0.075, 0.1\}$.
     The initial configuration is shown in inset of panel (a).
@@
 
-\subsection{Bilayer configurations (bc(i)) in a linear shear flow}
-To begin, we place the bilayer structure (with bc(i)) from the inset of Figure~\ref{fig:relax}(b)
+\subsection{Bilayer configurations (BC (i)) in a linear shear flow}
+To begin, we place the bilayer structure (with BC (i)) from the inset of Fig~\ref{fig:relax}(b)
 in a linear shear flow
 \begin{equation}
-\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y\cdot\xx){\bf e}_x,
+\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y \cdot \mathbf{x}) {\bf e}_x,
 \end{equation}
@@
 The initial bilayer structure consists of a small self-enclosing bilayer (vesicle) and several pieces of bilayers.
-Figure~\ref{fig:BC1_shear}(a)--(c)
-shows snapshots of the bilayer when $\dot\gamma= 0.05,0.075,0.01$
-at $t = 0.5$ $\upmu$s.
-The dynamics of the bilayer can be found in the supplementary movies, which show that the initial pieces of bilayers merge and form a worm-like shape
+Fig~\ref{fig:BC1_shear}(a)--(c)
+shows a snapshot
+at $t = 0.5$ $\upmu$s
+of the bilayer for different shear rates $\dot\gamma= 0.05,0.075,0.01$.
+The dynamics of the bilayer can be found in the supplementary movies,
+which show that the initial pieces of bilayers merge and form a worm-like shape
 under a linear shear flow.
-At a low shear rate, the bilayer constantly goes through rotation and extensional deformation with the whole bilayer intact (figure~\ref{fig:BC1_shear}(a)).
-As the shear rate increases to a moderate value (figure~\ref{fig:BC1_shear}(b)), the bilayer is observed to shed a small piece of bilayer, 
+At a low shear rate, the bilayer constantly goes through rotation and
+extensional deformation with the whole bilayer remaining intact (figure~\ref{fig:BC1_shear}(a)).
+As the shear rate increases to a moderate value (figure~\ref{fig:BC1_shear}(b)),
+the bilayer is observed to shed a small piece of bilayer, 
 similar to the asymmetric breakup of a viscous drop \cite{}.
@@
 
-In terms of deformation measures,  
-the free energies 
-are relatively constant (Figure~\ref{fig:BC1_shear}(d)),
-with the overall changes in the range of a few kT/nm.  
-Note that the free energy $F$ in figure~\ref{fig:BC1_shear}(d) has the unit of force because our system is two dimensional.
-
-An interesting feature of the simulations is that the order parameter $\tilde S_2$ in figure~\ref{fig:BC1_shear}(e)
+We observe that the order parameter $\tilde S_2$ in figure~\ref{fig:BC1_shear}(e)
 is on average increasing.  In the initial configuration,
@@
 Under the shear flow, the shedding and merging of bilayers
-result in an overall decrease in distinct bilayer structures.  
+results in an overall decrease in distinct bilayer structures.  
+Similarly, the free energies 
+are slightly decreasing (Fig~\ref{fig:BC1_shear}(d)),
+with the overall changes occuring in the range of a few $\mathrm{k_BT}$/nm.  
 This suggests that
 the shear flow changes the energy landscape to move the local equilibrium obtained from a random initial condition
-to an alternate local equilibrium with greater orientational order.   
+to an alternate local equilibrium with lesser free energy and greater orientational order.   
+Note that the free energy $F$ in figure~\ref{fig:BC1_shear}(d) has the unit of force because our system is two dimensional.
 %
@@
 %
-Finally, the strain parameter diverges in the large shear flow rate cases (Figure~\ref{fig:BC1_shear}(f))
+Finally, the strain parameter diverges in the large shear rate cases (Fig~\ref{fig:BC1_shear}(f))
 because the components eventually completely separate and move away from one another
@@
 %
-In \citet{Fu2022_JFM} the hydrodynamics of a JP vesicle under a linear shear flow is studied. 
-Focusing on drawing analogies to hydrodynamics of a vesicle in continuum modeling (such as tank-treading, bilayer slip and permeability),
-our previous studies also show the existence of a critical shear rate above which the JP vesicle ruptures. 
-Based on the these early results, we conduct numerical simulations with $\dot\gamma=0.05, 0.066, 0.075$.
-At these shear rates, the vesicle undergoes the familiar hydrodynamics (such as elongation along the extensional axis and tank-treading motion),
-as shown in Figure~\ref{fig:Ves_shear} (a)--(c).
-%
-Here we illustrate how the three measures of structural deformation 
+\citet{Fu2022_JFM} studied the hydrodynamics of a JP vesicle under a linear shear flow. 
+Focusing on drawing analogies to hydrodynamics of a vesicle in continuum modeling
+(such as tank-treading, bilayer slip and permeability),
+our previous studies showed the existence of a critical shear
+rate above which the JP vesicle ruptures. 
+Based on the these early results, we
+reinitialized the BC (i) configuration
+in the form of a single, circular vesicle (rather than several bilayer components)
+and illustrate how the three measures of structural deformation 
 correlate to the dynamics of a JP vesicle.
-We reinitialized the case (i) configuration with particles arranged in the pattern of a single, circular vesicle.
-This shape is also a local equilibrium, with somewhat less energy than the disordered state c.f.,
-Figure~\ref{fig:BC1_shear}(d) and Figure~\ref{fig:Ves_shear} (d).
-
-Unlike the dynamics of bilayers in figure~\ref{fig:BC1_shear}, 
-the energies of the JP vesicle in figure~\ref{fig:Ves_shear}(d) show jumps from the baseline value $30$ kT/nm to 32 kT/nm
+
+At shear rates $\dot\gamma=0.05, 0.066, 0.075$,
+the vesicle undergoes the familiar hydrodynamics
+(such as elongation along the extensional axis and tank-treading motion),
+as shown in Fig~\ref{fig:Ves_shear} (a)--(c).
+%
+The circular shape is also a local equilibrium, with somewhat less
+energy than the disordered state c.f.,
+Fig~\ref{fig:BC1_shear}(d) and Fig~\ref{fig:Ves_shear} (d).
+But unlike the dynamics of bilayers in Fig~\ref{fig:BC1_shear}, 
+the energies of the JP vesicle in Fig~\ref{fig:Ves_shear}(d)
+jump from the baseline value 30 $\mathrm{k_BT}$/nm to about 32 $\mathrm{k_BT}$/nm,
 signaling the rupture of the vesicle into disconnected bilayers
-(see figure \ref{fig:Ves_shear}(d), long and short dashed curves).
+(see Fig~\ref{fig:Ves_shear}(d), long and short dashed curves).
 After the rupture, each piece circles around the vorticity at the center without reconnection while the energies fluctuate slightly around a constant.
@@
 For the lowest shear rate case, the vesicle has nearly constant orientational order $\tilde S_2 = 1$
-(see figure \ref{fig:Ves_shear}(e), solid curve).
+(see Fig~\ref{fig:Ves_shear}(e), solid curve).
 After the JP vesicle
@@
 with a baseline value around $0.7$
-(see figure \ref{fig:Ves_shear}(e), dashed curves).
+(see Fig~\ref{fig:Ves_shear}(e), dashed curves).
 The oscillations occur due to the orbit of the two bilayer components,
@@
 %
-As in the previous case, peaks in the strain parameter $E$ correlate well with changes in structural topology in the bilayer dynamics, see
-the dashed curves in figure~\ref{fig:Ves_shear}(f).
+As in the previous case, peaks in the strain parameter $E$
+correlate well with changes in structural topology in the bilayer dynamics, see
+the dashed curves in Fig~\ref{fig:Ves_shear}(f).
 
@@
 \subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
-Next, we subject the bilayer/vesicles configurations to a 
+Next, we subject the bilayer/vesicle configurations to a 
 Taylor-Green (TG) background flow
@@
 \left(
--\cos\left(\frac{{\bf e}_x\cdot\xx}{l}\right)
- \sin\left(\frac{{\bf e}_y\cdot\xx}{l}\right)
+-\cos\left(x/\lambda\right)
+ \sin\left(y/\lambda\right)
          {\bf e}_x
-         +\sin\left(\frac{{\bf e}_x\cdot\xx}{l}\right)
-         \cos\left(\frac{{\bf e}_y\cdot\xx}{l}\right)
-             {\bf e}_y\right).
+         +\sin\left(x/\lambda\right)
+         \cos\left(y/\lambda\right)
+             {\bf e}_y\right)
 \end{equation}
+where $x = {\bf e}_x \cdot \xx$ and $y = {\bf e}_y \cdot \xx$
+are the horizontal and vertical coordinates, respectively. 
 The TG flow is a confining flow consisting of a checkboard pattern
 of cells with alternating circulation.  We control the flow by the
-the dimensionless flow strength $V_0$ and with the cell size $l$ nm.
-For most of the results here the cell size $l=2$ is used in this subsection.
+the dimensionless flow strength $V_0$ and the dimensionless cell size $l$
+defining $\lambda = l$ nm.
+For most of the results here the parameter $l=2$ is used in this subsection.
 %
@@
 There is no appreciable pattern in the deformation for the multicomponent bilayer case in TG flow. 
-Figure~\ref{fig:BC1_TG}(a)--(c) are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s.
+Fig~\ref{fig:BC1_TG}(a)--(c) are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s.
 At all flow strengths, the bilayer components are separated and mixed by the flow in neighboring cells. 
 In the $V_0 = 0.2$ case, the flow breaks off components consisting of only a few particles,
-leading an increase in energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve).
+leading an increase in energy (Fig~\ref{fig:BC1_TG}(d), long dashed curve).
 There is no significant change in the orientational order.  There is an initial increase in the
@@
 Patterns in the deformation, however, do emerge in the case of a vesicle in TG flow.
-For a vesicle in a Taylor-Green flow, Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\  \mu$s where $V_0=0.1,0.15,0.2$.
+For a vesicle in a Taylor-Green flow, Fig~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\  \mu$s where $V_0=0.1,0.15,0.2$.
 Here, the circular vesicle takes on a steady square shape for moderate flow rates $V_0 = 0.1$ and $V_0 = 0.15$.
-In these cases, there is little change in the vesicle free energy and order (Figure~\ref{fig:ves_TG}(d)-(f))).
+In these cases, there is little change in the vesicle free energy and order (Fig~\ref{fig:ves_TG}(d)-(f))).
 The vesicle disintegrates for $V_0 = 0.2$, leading to a jump in energy, drop in order, and increase in strain,
@@
 The vesicle shape is also tied to cell size $l$.  
-Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a
+Fig~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a
 TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s.  
 For the smallest cell size $l = 1$ tested, the vesicle is somewhat octogonal
-and passes through multiple cells (Figure~\ref{fig:BTG_Scale}(a)).
+and passes through multiple cells (Fig~\ref{fig:BTG_Scale}(a)).
 For the largest cell size $l = 4$,
@@
 The direction of the tank-treading, however, varies with the cell
-size (Figure~\ref{fig:BTG_Scale}(a)--(d), directed arcs).  We attribute
-this variation to the total rotational moment of the cells that the vesicle
-passes through.
+size (Fig~\ref{fig:BTG_Scale}(a)--(d), directed arcs).  We attribute
+this change in rotational orientation to the total rotational moment
+of the cells that the vesicle passes through.
 
@@
 by averaging the area/length for the inner and outer leaflets.  
-As shown in Figure~\ref{fig:BTG_Scale}(e),
+As shown in Fig~\ref{fig:BTG_Scale}(e),
 the relative area $A/A_0$ decreases during the simulations, with a rate
 depending nonmonotonically on $l$.  
-The relative length $L/L_0$, is constant in $t$ for all cell sizes (Figure~\ref{fig:BTG_Scale}(e), inset).
+The relative length $L/L_0$, however, is constant in $t$ for all cell sizes (Fig~\ref{fig:BTG_Scale}(e), inset).
 This implies that the vesicle behaves as an inextensible, permeable membrane.
@@
 \subsection{Multilamellar and striated configurations in shear and TG flow}
-We have simulated particles for the multilamellar (case (ii)) and striated (case (iii))
+We have simulated particles for the multilamellar (BC (ii)) and striated (BC (iii))
 boundary conditions, in both shear and TG background flow.  The results are
 qualitatively similar and will be presented in tandem. 
-For the multilamellar case, we place a 60-particle configuration (inset of Figure~\ref{fig:BC2_shear}(a))
+For the multilamellar case, we place a 60-particle configuration (inset of Fig~\ref{fig:BC2_shear}(a))
 in shear flows with $\dot\gamma=0.05, 0.1, 0.15$ and in TG flow with flow rates $V_0=0.1, 0.15, 0.2$.
-For the striated case, we also place a 60-particle configuration (inset of Figure~\ref{fig:BC3_shear}(a))
-in shear and TG background flows.  However, somewhat larger rates are required to see appreciable
+For the striated case, we also place a 60-particle configuration (inset of Fig~\ref{fig:BC3_shear}(a))
+in shear and TG background flows.  Here, somewhat larger rates are required to see appreciable
 deformations for this boundary condition: $\dot\gamma=0.1, 0.125, 0.15$
@@
 
-In terms of shear flow, the free energies are steady at the lowest shear flow
-rates (Figure~\ref{fig:BC2_shear}(d), Figure~\ref{fig:BC3_shear}(d)).
-The free energy of the striated configuration oscillates by $\pm 1$ kT/nm
-due to square reference region deforming into a rhomboidal shapre under shear
-flow (Figure~\ref{fig:BC3_shear}(d), solid curve).  No such oscillation
+In terms of shear flow, the free energies are steady at the lowest shear 
+rates (Fig~\ref{fig:BC2_shear}(d), Fig~\ref{fig:BC3_shear}(d)).
+The free energy of the striated configuration oscillates by $\pm 1$ $\mathrm{k_BT}$/nm
+due to square reference region deforming into a rhomboidal shape under shear
+flow (Fig~\ref{fig:BC3_shear}(d), solid curve).  No such oscillation
 is present in for the multilamellar configuration since this shape is circularly
-isotropic (Figure~\ref{fig:BC2_shear}(d), solid curve).
+isotropic (Fig~\ref{fig:BC2_shear}(d), solid curve).
 At the lowest shear rates, there is, however, oscillation in the strains
@@
 while the order parameter $\tilde S_2$ is more less constant
-(Figure~\ref{fig:BC2_shear}(e),(f), Figure~\ref{fig:BC3_shear}(e),(f), solid curves).
-In summary, both multilallar and striated configurations behave as rigid bodies
-under shear flow.
-
-In the high shear flow rate cases ($\dot\gamma=0.15$), both the
-multilamellar and striated configurations become disordered.  In case (ii),
+(Fig~\ref{fig:BC2_shear}(e),(f), Fig~\ref{fig:BC3_shear}(e),(f), solid curves).
+In summary, both multilallar and striated configurations behave as nearly
+rigid bodies under shear flow when the shear rate $\dot \gamma$ is low.
+
+In the high shear rate cases ($\dot\gamma=0.15$), both the
+multilamellar and striated configurations become disordered.  For BC (ii),
 the lamella break apart so that individual bilayers are no longer discernable
-(Figure~\ref{fig:BC2_shear}(c)).
-In case (iii), the stria detach from the main body,
-but the stria remain instact (Figure~\ref{fig:BC3_shear}(c)).  
-Overall, the particles in case (ii) and case (iii) remain bounded
+(Fig~\ref{fig:BC2_shear}(c)).
+For BC (iii), the stria peal away from the main body,
+but remain individually intact (Fig~\ref{fig:BC3_shear}(c)).  
+Overall, the particles in BC (ii) and BC (iii) remain bounded
 and do not drift away in the shear background flow like for the
-case (i) boundary condition (Figure~\ref{fig:BC1_shear}(c),
-Figure~\ref{fig:Ves_shear}(c)).
+BC (i) boundary condition (Fig~\ref{fig:BC1_shear}(c),
+Fig~\ref{fig:Ves_shear}(c)).
 
@@
 is also basically constant for the lowest flow rates $V_0$
-(Figure~\ref{fig:BC2_TG}(d), Figure~\ref{fig:BC3_TG}(d), solid curves).
+(Fig~\ref{fig:BC2_TG}(d), Fig~\ref{fig:BC3_TG}(d), solid curves).
 The striated configuration is unperturbed by the flow, and is engulfed by a single,
 larger, rotating flow cell
-(Figure~\ref{fig:BC3_TG}(a)). 
-The multilamellar configuration is perturbed by the flow, as seen in the increase in
-the strain parameter $E$ (Figure~\ref{fig:BC3_TG}(f), solid curve).
+(Fig~\ref{fig:BC3_TG}(a)). 
+The multilamellar configuration is perturbed by the flow,
+as seen in the increase in
+the strain parameter $E$ (Fig~\ref{fig:BC3_TG}(f), solid curve).
 The difference in response to the background flow
@@
 At large flow rates $V_0$, both configurations depart significantly from their local
-equilibrium.  The lamella bilayers from case (ii) break apart, forming several,
-unlayered bilayer components (Figure~\ref{fig:BC2_TG}(c)).
-
-In case (iii), the stria also break apart, but neighboring particles form
-'X'-like arrangements (Figure~\ref{fig:BC3_TG}(d)), resembling the doubly alternating
-director equilibrium (Figure~\ref{fig:relax}(d), center, top white rectangle).
+equilibrium.  The lamella bilayers from BC (ii) break apart, forming several,
+unlayered bilayer components (Fig~\ref{fig:BC2_TG}(c)).
+In BC (iii), the stria also break apart, but neighboring particles form
+'X'-like arrangements (Fig~\ref{fig:BC3_TG}(d)), resembling the doubly alternating
+director equilibrium (Fig~\ref{fig:relax}(d), center, top white rectangle).
 
@@
 \section{Discussion}
-
-Comparing with bilayer structures, Figure~\ref{fig:BC2_shear}(a)--(c) demonstrate that the multilamellar ones are more rigid in shear flow and the rupture phenomenon can be observed 
-when the shear rate is high enough.
-
-For multilamellar structure in a Taylor-Green flow, as shown in Figure~\ref{fig:BC2_TG}(a)--(b), lower flow strengths such as $V_0=0.1,0.15$ do not reach a critical flow rate for structural disorder. 
-When $V_0=0.2$ (Figure~\ref{fig:BC2_TG}(c)), the flow is strong enough to separate the structure
-into multiple groups within the cells. In all deformation measures, a similar trend in shear flow case is observed, see Figure~\ref{fig:BC2_TG}(d)--(f).
-
-For a striated configuration in a Taylor-Green flow, numerical experiments have shown that one needs to choose relative higher flow strengths than other boundary conditions to reach structural disorder.
-Figure~\ref{fig:BC3_TG}(a)--(c) are configurations for $V_0=0.2, 0.25, 0.3$ at $t=0.4\  \mu$s.
-Figure~\ref{fig:BC3_TG}(d)--(f) show that the threshold for having clear rupture is between $V_0=0.2$ and $V_0=0.25$ and a huge jump in measures occurs soon after the flow is turned on.
-
-We place the striated configuration in a shear flow when $\dot\gamma=0.1, 0.125, 0.15$ and 
-the snapshots at $t=0.1\ \mu$s are shown in Figure~\ref{fig:BC3_shear}(a)--(c).
-Break-up deformation measures (igure~\ref{fig:BC3_shear}(d)--(f)) are similar to vesicle in shear flow case.
-Notably, for low shear rates, oscillatory behaviours are investigated in energies, orientational and positional parameters.
-
-It is worth noting that in the dipolar molecules modeled by
-Laplace equation, the equilibrium configurations consist of strands,
-rather than a patch, of particles and also have
-alternating orientations \cite{}.
-
-We notice that the strain parameter are relatively higher (of order 10) in shear flows or not confining flows comparing with ones of order 1 in cases using Taylor-Green flows when rupture occurs.
-In order to make the structure disorder, the striated structures need the highest flow strength or shear rate in all three boundary conditions.
-Moreover, this can be interpreted by having higest free energy calculated from striated structures.
+Our results were for $N_b = 60$.  This particle number was large enough for the JP to form
+measurable structures while giving managable simulation times (days) on a single computing processor.
+The simulation time for $N_b = 198$ in Fig. \ref{fig:relax} and Fig. \ref{fig:relax_energy}
+was several weeks, and so we avoided simulations of this size for our results.
+We used $N = 16$ grid points per particles for all simulations.  We performed a convergence study
+and found that using $N = 16$ or $N = 24$ grid points per particle gave quantitavely indistinguishable
+results.  The time courses consisted of $O(10^3)$ time steps with $\Delta = 0.2$ nm.
+
+The free energy $F$ defined in \eqref{eq:free_energy}
+scales with the boundary data $g$ and repulsion modulus $M$.
+To remove the degree of freedom in the boundary data,
+we scaled all boundary data so that the square integral of $g$ is independent of
+type of boundary condition; BC (i), (ii), or (iii).
+This way, for a fixed configuration, the hydrophobic interaction portion of the
+free energy (the integral in \eqref{eq:free_energy}) converges to $2\pi \gamma c N_b$
+in the limit $\rho = 0$.  This gives a free energy per particle that is independent
+of the shape/intensity of the hydrophobic interface.  In practice, $\rho > 0$ is fixed
+and the JP assume different configurations.  As a result, the equilbrium energies
+per particle in our simulations are different and depend on the boundary condition
+(Fig.~\ref{fig:relax_energy}).
+They are about 0.26 $\mathrm{k_BT}$/nm for BC (ii),
+0.55 $\mathrm{k_BT}$/nm for BC (i), and
+1.4 $\mathrm{k_BT}$/nm for BC (iii).
+
+Next, we suspended JP in viscous background flows and observed deformations
+as a function of flow strength.  There were three categories of boundary
+conditions; BC (i), BC (ii), and BC (iii); that formed bilayer, multilamellar, and striated
+configurations, respectively. For BC (i), we considered both an unstructured bilayer
+and a vesicle bilayer.  The background flows were a linear shear flow and a Taylor-Green (TG) flow.
+
+We can characterize the effective material proporties of the JP structures
+based on the changes in free energy, orientationl order, and strain as a function
+of flow strength.  Generally, $F$ increases, $\tilde S_2$ decreases, and 
+$E$ increases with increases in both $\dot \gamma$ and $V_0$, as expected.
+Structurally, the striated JP configuration for BC (iii) behaved the most
+like a rigid body over the flow strengths tested.  For this structure,
+the deformations measures were constant in time for shear rates $\dot \gamma$ up to
+$0.15$ and TG flow rate $V_0$ up to $0.25$
+(Fig.~\ref{fig:BC3_shear} and Fig.~\ref{fig:BC3_TG}).
+Conversely, a $25 - 50 \%$
+smaller value for $\dot \gamma$ or $V_0$ were required to observe
+nonrigid deformations for the BC (i) and BC (ii) cases.
+
+In terms of fluid behavior,
+the multilamellar (BC (ii)) structure behaves as shear thinning fluid
+while the striated structure (BC (iii)) has a finite yield stress and
+behaves as a Bingham plastic. 
+Qualitatively, the strains for BC (ii) increases gradually 
+with shear rate (Fig~\ref{fig:BC2_shear}(f)).
+In contrast, the strains for BC (iii) are constant over a range of flow strengths
+and then increase when the flow strengths are large enough
+to deform the body (Fig~\ref{fig:BC3_shear}(f)).
+To quantify this behavior, we form 
+\[
+\mu_{\text{sus}} = \frac{\dot \gamma}{\dot E} \mu
+\]
+as an effective dynamic viscosity of the suspension.
+The numerator $\dot \gamma \mu$ gives the force per area provided by the solvent stresses. 
+The strain rate $\dot E$ of the body is obtained by fitting the curves the strain curves e.g.,
+Fig~\ref{fig:BC2_shear}(f).
+Calculated suspension viscosities are shown
+in Table \ref{tbl:bcii_visc}.
+We observe that for the multilamellar structure, $\mu_{\text{sus}}$ is decreasing
+with increasing shear rate.  The predicted suspension viscosities 
+are on the order of hundreds of times that of water, consistent with
+measurements of noninteracting particle suspensions\cite{KONIJN201461}.
+In the case of striated structures, viscosity is effectively infinite
+for the lower two of the shear rates, and then drops to a finite value $\mu_{\text{sus}} = 60$ mPa s
+when the shear rate reaches $0.15$ ns$^{-1}$.
+\begin{table}
+  \caption{Viscosity $\mu_{\text{sus}}$ (mPa s) for the Multilamellar and Striated Suspensions    
+\label{tbl:bcii_visc}
+}
+\centering
+\begin{tabular}{c|c|c|c}
+\multicolumn{4}{c}{multilamellar BC (ii)} \\
+\hline
+  $\dot \gamma$ & 0.05 & 0.10 & 0.15\\
+  \hline
+  $\phi$ & 0.50 & 0.47 & 0.41\\
+  \hline
+  $\mu_{\text{sus}} $ & 401 & 66 & 42\\
+\hline
+\end{tabular}
+\quad \quad \quad
+\begin{tabular}{c|c|c|c}
+\multicolumn{4}{c}{striated BC (iii)} \\
+\hline
+  $\dot \gamma$ & 0.100 & 0.125 & 0.15\\
+  \hline
+  $\phi$ & 0.47 & 0.46 & 0.45\\
+  \hline
+  $\mu_{\text{sus}} $ & 2.5e3 & 1.4e3 & 60\\
+\hline
+\end{tabular}
+\end{table}
+
+We have not calculated suspension viscosities for the type (i) boundary condition,
+because the viscosities of bilayer are in-plane and require fully three-dimensional
+simulations to resolve.  Our previous work 
+did calculate, however, an intermonolayer friction coefficient $b$
+which is related but conceptually different than viscosity \cite{Fu2022_JFM}.
+
+While increased flow strengths generally injected energy into the suspension,
+the simulation results show that the unstructured bilayer 
+actually increases orientational order and has somewhat lower free energy 
+under low shear rates (Fig~\ref{fig:BC1_shear}(d,f)).
+This effect suggests that in amphiphilic suspensions,
+it might be possible decrease the excess area of the system 
+by subjecting the suspension to a moderate shear flow.
+Not all background flows produce this effect, as it was not
+observed in the TG background flow case (Fig~\ref{fig:BC1_TG}).
+
+\citet{kohl-cor-che-vee22} have simulated
+suspensions of JP in three dimensions
+using the same free energy formulation of
+hydrophobic attraction used in the
+present work. They observed spontaneous
+aggregation into micelles generically and
+formation of bilayers when the initial
+configuration was chosen sufficiently close to the final
+configuration.
+\citet{kohl-cor-che-vee22} also studied self-assembly
+of bipolar electric JP, which bare some resemblence
+to polar boundary condition we employ.
+In the case of bipolar electric JP, the particles
+form parallel chains that repel.  In contrast, the
+interaction between stria under BC (iii) is attractive.
+The existence of 'X'-shaped local arrangements as a local
+equilibrium (Fig.~\ref{fig:relax}(d), top, middle rectangle)
+further suggests there may be greater diversity in the set of
+possible equilibria in three-dimensions.
+
+\section{Conclusion}
+\label{sec:conclusion}
 
@@
 We consider a suspension of $N_b$ Janus particles in the fluid domain
-$\Omega$. The boundary of the $\Omega$ is $\bd\Omega = \Gamma_1 \cup
+$\Omega$.
+The boundary of the $\Omega$ is $\bd\Omega = \Gamma_1 \cup
 \cdots \cup \Gamma_{N_b}$, where $\Gamma_i$ is the boundary of Janus
@@
 The number $\theta_i(\xx)$ is the angle formed by the position $\xx$,
-the particle center $\aa_i$, and the particle director $\dd_i$.% (Figure
+the particle center $\aa_i$, and the particle director $\dd_i$.% (Fig
 \ref{fig:flow_map}).
@@
 60 particles with one set of random initial positions and orientations
-as shown in Figure~\ref{fig:relax}(a)
+as shown in Fig~\ref{fig:relax}(a)
 
@@
 and particles will collectively orient their tails toward
-one another. Figure~\ref{fig:relax}(b) demonstrates multiple bilayer structures such as pancake and vesicle shapes.
+one another. Fig~\ref{fig:relax}(b) demonstrates multiple bilayer structures such as pancake and vesicle shapes.
 
@@
 heads.%~\cite{Huetal19, deMeetal21}. 
-Figure~\ref{fig:relax}(c) shows the multilamellar structure with 8 layers when $N_b=60$. 
+Fig~\ref{fig:relax}(c) shows the multilamellar structure with 8 layers when $N_b=60$. 
 The number of folds depends on several factors, for instances, number of particles and intial configurations.
@@
 its head with the head of three other particles and its tail with the
-tail of three other particles. % Figure~\ref{fig:self-assembly}(c).
-Figure~\ref{fig:relax}(d) gives an example that this boundary condition results a checker board/stripes equilibrium state.
-
-Figure~\ref{fig:relax_energy} shows the energy profile of boundary conditions (i)--(iii) using 
+tail of three other particles. % Fig~\ref{fig:self-assembly}(c).
+Fig~\ref{fig:relax}(d) gives an example that this boundary condition results a checker board/stripes equilibrium state.
+
+Fig~\ref{fig:relax_energy} shows the energy profile of boundary conditions (i)--(iii) using 
 \eqref{eq:free_energy2} with \eqref{eq:normal_deriv} for normal derivative expression. As expected, for all simulation runs, the total energy of the systems decreases and reaches equilibrium states.
@@
 %
-where $\dot\gamma$ is the shear rate. Figure~\ref{fig:shear_1} (a)--(c) show the snapshots of simulation results when $\dot\gamma=0.05$.
+where $\dot\gamma$ is the shear rate. Fig~\ref{fig:shear_1} (a)--(c) show the snapshots of simulation results when $\dot\gamma=0.05$.
 We measure the ratio of major and minor axes $\lambda$ by adopting an ellipse fitting using the singular value decomposition and track this aspect ratio for this multi-lamellar structure when the flow is on.
@@
 %Consider the energy profiles for two simulations where the centor of mass is on and off the origin.
-%Figure~\ref{fig:shear_energy1} shows numerical results for both energy profiles and magnitude of energy differences is significantly large when there is a large deformation, for instance, the case when a multi-lamellar structure deformed to a pancake shape.
+%Fig~\ref{fig:shear_energy1} shows numerical results for both energy profiles and magnitude of energy differences is significantly large when there is a large deformation, for instance, the case when a multi-lamellar structure deformed to a pancake shape.
 %
@@
 After a set of empirical numerical investigations, we obtain a critical shear rate $\dot\gamma=0.15$ where the checker board deforms into stripes and small groups of JP.
-Figure~\ref{fig:shear_2}(a)--(d) show configurations when $t=\{0,50,100,150\}$.
+Fig~\ref{fig:shear_2}(a)--(d) show configurations when $t=\{0,50,100,150\}$.
 %The deformation starts with stripe separations
@@
 The magnitude of the vortex flow is controlled by the velocity scale $V_0$.
-Similar to the setup in the shear flow cases, we shift the center of mass position to the origin then turn on the Taylor-Green flow with $V_0=0.1$ and tune the sides of zero-velocity box to $\pi$, i.e., $l=0.5$, Figure~\ref{fig:TG_1}(a)--(c) show three frames of simulation results and we
+Similar to the setup in the shear flow cases, we shift the center of mass position to the origin then turn on the Taylor-Green flow with $V_0=0.1$ and tune the sides of zero-velocity box to $\pi$, i.e., $l=0.5$, Fig~\ref{fig:TG_1}(a)--(c) show three frames of simulation results and we
 track the aspect ratio $\lambda$ described in the previous section which is provided in panel (d). 
@@
 We also found that the flow strength coefficient above $V_0=0.1$ will result to clear group separations during the simulations. 
-Comparing with the case when $V_0=0.2$, we provide a frame in Figure~\ref{fig:TG_2}(a) and the energy comparison is shown in panel (b).
+Comparing with the case when $V_0=0.2$, we provide a frame in Fig~\ref{fig:TG_2}(a) and the energy comparison is shown in panel (b).
 Numerical results validate the phenomenon that a higher taylor green vortex flow generates large structure separations with higher total energy.
@@
 under a shear flow.
-Simulation results and snapshots are shown in Figures~\ref{fig:confined_vesicle} and Figure~\ref{fig:confined_lamellar} where the JP vesicle has $N_b=25$ particles and JP lamellar has $N_b=40$ particles, respectively.
+Simulation results and snapshots are shown in Figs~\ref{fig:confined_vesicle} and Fig~\ref{fig:confined_lamellar} where the JP vesicle has $N_b=25$ particles and JP lamellar has $N_b=40$ particles, respectively.
 Both starting configurations are pre-relaxed and the channel width in the narrow part is about 5 length units in the vesicle case and 4 length units in the lamellar case.

### 2022-07-25 doc/PRF2022/PRF_main.tex
continuting on Sec II

--- 2022-07-25 doc/PRF2022/PRF_main.tex
@@
 velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.
-Without inertia, the system in~\eqref{eq:stokes}-\eqref{eq:rigid-vel}
+Without inertia, the system in~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
 also satisfies the force-free and torque-free conditions.
@@
 \begin{alignat}{3}
-  \label{eq:SL}
+  \label{eq:SLpde}
   -\rho^2 \Delta u + u &= 0,\qquad &&\xx \in \Omega, \\
+  \label{eq:SLbc}
   u &= g, &&\xx \in \bd\Omega, \\
+  \label{eq:SLfarfield}
   u &\rightarrow 0, &&|\xx| \rightarrow \infty,
@@
 \subsection{Boundary integral represenation and time stepping}
-We recast \eqref{eq:stokes}--\eqref{eq:rigid-vel} and \eqref{eq:SL}
-as boundary integral equations (BIEs) and discretize each BIE at
-$N$ points on each of the $N_b$ particles with a collocation method.
-To express the solution of \eqref{eq:SL},
-we adopt the double layer potential
+We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
+and~\eqref{eq:SLpde}--\eqref{eq:SLfarfield} as boundary integral
+equations (BIEs) and discretize each BIE at $N$ points on each of the
+$N_b$ particles with a collocation method. To express the solution
+of~\eqref{eq:SLpde}--\eqref{eq:SLfarfield}, we adopt the double layer
+potential
 \begin{align}
 \label{eq:SL_BIE}
-u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy
-, \quad \xx \in \Omega,
+  u({\xx}) = \DD[\sigma](\xx) = \int_\Gamma 
+    \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, 
+    \dif s_\yy, \quad \xx \in \Omega,
 \end{align}
-where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL},
-$K_0$ is the zeroth-order modified Bessel function of the first kind,
-and $\sigma$ is a scalar-valued density function.
-The subscript in $\dif s_\yy$ denotes integration with respect to $\yy \in \Gamma$. 
-For the velocity, we use the representation [REF]
+where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
+solution to the screened Laplace equation~\eqref{eq:SLpde}, $K_0$ is the
+zeroth-order modified Bessel function of the first kind, and $\sigma$ is
+a scalar-valued density function.  The subscript in $\dif s_\yy$ denotes
+integration with respect to $\yy \in \Gamma$.  For the velocity, we use
+the representation~\cite{pow-mir1987}
 \begin{align}
@@
 \end{align}
-with the vector-valued density function $\eeta$,
-Stokeslet 
-$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr \otimes \rr}{|\rr|^2}\right)$,
-and Rotlet
-$\RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$,
-$\rr = \xx - \aa_i$ [REF].
+with the vector-valued density function $\eeta$, Stokeslet
+$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr
+\otimes \rr}{|\rr|^2}\right)$, and Rotlet $\RR(\xx,\aa_i) =
+\frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$, $\rr = \xx - \aa_i$.
 
@@
 
-First, we must simplify the
-form of the free energy \eqref{eq:free_energy}
-using integration by parts and \eqref{eq:SL}
+First, we must simplify the form of the free energy
+\eqref{eq:free_energy} using integration by parts and \eqref{eq:SLpde}
 to obtain

### 2022-07-25 doc/PRF2022/PRF_main.tex

--- 2022-07-25 doc/PRF2022/PRF_main.tex
@@
 velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.
+Without inertia, the system in~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
+also satisfies the force-free and torque-free conditions.
+%This means
+%that the total force $\FF_i,$ and torque $T_i$ from the hydrodynamic
+%stress on each particle (with subscript `$i$') balance the force and
+%torque from the hydrophobic potential~\cite{Fu2022_JFM}. 
+The total force
+and torque from the fluid flow are
+\begin{align}
+  \label{eq:force}
+ \FF_i = \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s, \quad
+ T_i = \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
+  (\ssigma \cdot \nnu_i) \, \dif s,
+  \quad i=1,\ldots,N_b,
+\end{align}
+respectively, where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu +
+\nabla \uu^T \right)$ is the hydrodynamic stress tensor (pressure
+tensor), and $\nnu_i$ is the unit outward normal on the $i$th particle.
+
+The total force $\FF_i,$ and torque $T_i$ from the hydrodynamic
+stress on each particle (with subscript `$i$') balance the force and
+torque from the hydrophobic potential. 
+%$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
+%particles and the viscous solvent. 
+As in~\citet{Fu2022_JFM} such a hydrophobic attraction potential
+$u(\xx,t)$ is assumed to the minimizer of the free energy
+\begin{align}
+=======
+velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.
 
@@
 \begin{equation}
+>>>>>>> e6ff8abf65732bc50432a8d6cd9352c76cb936ca
 \label{eq:free_energy}
@@
 $\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
+$c$ is an ``effective" distance between particle centers, below which the steric repulsion between a pair of JPs becomes important.
+In the followings we let $c$ be the radius of each JP.
+
+The governing equation for $u(\xx,t)$ is obtained by computing the
+domain variation of the free energy $F$~\cite{Fu20}. We obtain a
+screened Laplace equation boundary value problem as a model for the
+hydrophobic interaction between water and JPs:
+\begin{alignat}{3}
+  \label{eq:SLpde}
+  -\rho^2 \Delta u + u &= 0,\qquad &&\xx \in \Omega, \\
+  \label{eq:SLbc}
+  u &= g, &&\xx \in \bd\Omega, \\
+  \label{eq:SLfarfield}
+  u &\rightarrow 0, &&|\xx| \rightarrow \infty,
+\end{alignat}
+where the boundary condition $g$ gives the degree of hydrophobicity the
+=======
 The parameter $\rho_0$ is an ``effective" distance between particle centers,
@@
 The boundary condition $g$ encodes hydrophobic properties of the
+>>>>>>> e6ff8abf65732bc50432a8d6cd9352c76cb936ca
 particle-solvent interface.

### 2022-07-25 doc/PRF2022/PRF_main.tex
fixed merge issues

@@
 $u(\xx,t)$ is assumed to the minimizer of the free energy
-\begin{align}
-=======
-velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.
-
-Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free conditions.
-This means that the force and torque from the hydrodynamic stress on each particle 
-are in balance with the total
-force and torque coming from the hydrophobic potential and repulsion \cite{Fu2022_JFM}.
-To compute this balance, we define
-the free energy\cite{Fu2022_JFM}
 \begin{equation}
->>>>>>> e6ff8abf65732bc50432a8d6cd9352c76cb936ca
 \label{eq:free_energy}
@@
 where $u(\xx,t)$ is as an order parameter for the structure of water,
-$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
-$c$ is an ``effective" distance between particle centers, below which the steric repulsion between a pair of JPs becomes important.
-In the followings we let $c$ be the radius of each JP.
+$\rho$ is a decay length, and $\gamma$ is an interfacial tension.  The
+radius of the Janus particles $c$ also serves as an ``effective"
+distance between particle centers, below which the steric repulsion
+between a pair of JPs becomes important.
 
@@
 \end{alignat}
-where the boundary condition $g$ gives the degree of hydrophobicity the
-=======
-The parameter $\rho_0$ is an ``effective" distance between particle centers,
-below which the steric repulsion between a pair of JPs becomes important.
-
-The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$ \cite{Fu20}.
-Its governing equations $u(\xx,t)$ 
-are a screened Laplace equation boundary value problem
-as a model for the hydrophobic interaction between water and JPs:
-\begin{gather}
-  \label{eq:SL}
-  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
-  \label{eq:SLbc}
-  u = g, \quad \xx \in \bd\Omega, \quad 
-  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
-\end{gather}
 The boundary condition $g$ encodes hydrophobic properties of the
->>>>>>> e6ff8abf65732bc50432a8d6cd9352c76cb936ca
-particle-solvent interface.
-
-To get forces and torques from the free energy,
-we compute the variation of the domain of the free energy 
-\eqref{eq:free_energy} subject to \eqref{eq:SL}-\eqref{eq:SLbc},
-and obtain 
+particle-solvent interface. The parameter $\rho_0$ is an ``effective"
+distance between particle centers, below which the steric repulsion
+between a pair of JPs becomes important.
+\todo[inline]{We are calling both $c$ and $\rho_0$ as this ``effective"
+distance (see above). Also, $\rho_0$ is not defined. Should it be
+$\rho$?}
+
+To calculate forces and torques from the free energy, we compute the
+variation of the domain of the free energy~\eqref{eq:free_energy}
+subject to~\eqref{eq:SLpde}--\eqref{eq:SLbc}, and obtain 
 \begin{equation}
@@
 for $i = 1,\dots,N_b$ with particle outward normal $\nu$. The term 
-$
+\begin{align}
 \mathbf{T}
@@
   + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
-$
-is the hydrophobic stress.
-Repulsion is rotationally symmetric and does not contribute to the torque.
-The derivation details are found in \citet{Fu20}.
+\end{align}
+is the hydrophobic stress. Repulsion is rotationally symmetric and does
+not contribute to the torque. The derivation details are found
+in~\citet{Fu20}.
 

### 2022-07-25 doc/PRF2022/PRF_main.tex
yny

--- 2022-07-25 doc/PRF2022/PRF_main.tex
@@
 to actively control self-assembly of Janus particles (JPs),  we use a model recently developed for the many-body hydrodynamics of amphiphilic JPs suspended 
-in a viscous background flow (JFM, 941, 2022). We investigate how various bilayer structures arise from tuning the hydrophobicity/hydrophilicity of the JPs. 
+in a viscous background flow (JFM, 941, 2022) to investigate how various bilayer structures arise from tuning the hydrophobicity/hydrophilicity of the JPs. 
 Focusing on three distributions of hydrophobicity we found JPs may assemble into uni-lamella, multi-lamella, and striated structures in a viscous fluid. 
@@
 for a rigid body motion
-\begin{align}
+\begin{equation}
   \label{eq:rigid-vel}
@@
     \quad \xx \in \Gamma_i,
-\end{align}
+\end{equation}
 where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
 velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$. 
-Without inertia, the system in~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
-also satisfies the force-free and torque-free conditions.
-%This means
-%that the total force $\FF_i,$ and torque $T_i$ from the hydrodynamic
-%stress on each particle (with subscript `$i$') balance the force and
-%torque from the hydrophobic potential~\cite{Fu2022_JFM}. 
-The total force
-and torque from the fluid flow are
-\begin{align}
+Without inertia, the system in \eqref{eq:stokes}-\eqref{eq:rigid-vel} also satisfies the force-free and torque-free conditions.
+This means that the total force $\FF_i,$ and torque $T_i$ from the hydrodynamic stress on each particle (with subscript `$i$')
+are in balance with the force and torque from the hydrophobic potential \cite{Fu2022_JFM}.
+The total force and torque from the fluid flow are computed as
+\begin{equation}
   \label{eq:force}
- \FF_i = \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s, \quad
- T_i = \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
+ \FF_i \equiv \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s, \quad
+ T_i \equiv \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
   (\ssigma \cdot \nnu_i) \, \dif s,
   \quad i=1,\ldots,N_b,
-\end{align}
-respectively, where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu +
-\nabla \uu^T \right)$ is the hydrodynamic stress tensor (pressure
-tensor), and $\nnu_i$ is the unit outward normal on the $i$th particle.
-
-The total force $\FF_i,$ and torque $T_i$ from the hydrodynamic
-stress on each particle (with subscript `$i$') balance the force and
-torque from the hydrophobic potential. 
-%$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
-%particles and the viscous solvent. 
-As in~\citet{Fu2022_JFM} such a hydrophobic attraction potential
-$u(\xx,t)$ is assumed to the minimizer of the free energy
-\begin{align}
+\end{equation}
+where 
+%$\FF_i \in \mathbb{R}^2$ and $T_i \in \mathbb{R}$
+%are interparticle forces and torques. 
+$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
+\right)$ is the hydrodynamic stress tensor (pressure tensor), and
+$\nnu_i$ is the unit outward normal on the $i$th particle.
+
+$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
+particles and the viscous solvent. As in \citet{Fu2022_JFM} such a hydrophobic attraction potential $u(\xx,t)$ is assumed to
+the minimizer of the free energy
+\begin{equation}
 \label{eq:free_energy}
 F = \gamma
-  \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} u^2 \right)
+\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
 \,d\xx
@@
 P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
-\end{align}
+\end{equation}
 where the hydrophobic attraction potential $u(\xx,t)$ can be regarded as an order parameter for the structure of water,
@@
 $c$ is an ``effective" distance between particle centers, below which the steric repulsion between a pair of JPs becomes important.
-In the followings we let $c$ be the radius of each JP.
-
-The governing equation for $u(\xx,t)$ is obtained by computing the
-domain variation of the free energy $F$~\cite{Fu20}. We obtain a
-screened Laplace equation boundary value problem as a model for the
-hydrophobic interaction between water and JPs:
-\begin{alignat}{3}
-  \label{eq:SLpde}
-  -\rho^2 \Delta u + u &= 0,\qquad &&\xx \in \Omega, \\
-  \label{eq:SLbc}
-  u &= g, &&\xx \in \bd\Omega, \\
-  \label{eq:SLfarfield}
-  u &\rightarrow 0, &&|\xx| \rightarrow \infty,
-\end{alignat}
-where the boundary condition $g$ gives the degree of hydrophobicity the
+In the followings we use the radius of JP for $c$.
+
+The governing equation for $u(\xx,t)$ is obtained by computing the domain variation of the free energy $F$ \cite{Fu20}:
+We obtain
+a screened Laplace equation boundary value problem as a model for the hydrophobic interaction between water and JPs:
+\begin{gather}
+  \label{eq:SL}
+  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
+  u = g, \quad \xx \in \bd\Omega, \quad 
+  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
+\end{gather}
+With 
+The boundary condition $g$ gives the degree of hydrophobicity the
 particle-solvent interface.
 
-The hydrophobic stress is
-\begin{align}
-\mathbf{T}
-= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
-  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
-\end{align}
-and is derived by applying variation of domain techniques to the free
-energy~\eqref{eq:free_energy}~\cite{Fu20}. Then, the hydrophobic force
-and torque are
-\begin{align}
+Variation of the the free energy \eqref{eq:free_energy} provides
+\begin{equation}
   \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
@@
 T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
-\end{align}
-which balance the hydrodynamic force and torque~\eqref{eq:force}, for $i
-= 1,\dots,N_b$. 
-%The term 
-%\begin{align}
-%\mathbf{T}
-%= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
-%  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
-%\end{align}
-%is the hydrophobic stress~\cite{Fu20} and derived by variation of the
-%domain techniques.
-
-Finally, the dimensionless repulsion profile $P$ takes the form $P(s) =
-1 - \sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
+\end{equation}
+for $i = 1,\dots,N_b$. The term 
+$
+\mathbf{T}
+= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
+  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
+$
+is the hydrophobic stress identified in ~\cite{Fu20} and derived by
+variation of the domain techniques.
+
+The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
+\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
 \infty$.  As such, only those particles within a distance $\rho_0$ of
@@
 
-We use the same parameters from previous work~\cite{Fu2022_JFM}: $\mu =
-1$ cP, $\gamma = 4$ pN nm$^{-1}$, $\rho = 5$ nm, $c = 1.25$ nm, $M = 2$
-pN, and $\rho_0 = 0.5$ nm.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We use the parameters $\mu = 1$ cP, $\gamma = 4$ pN nm$^{-1}$,
+$\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.
+
 \subsection{Boundary integral represenation and time stepping}
-We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
-and~\eqref{eq:SLpde}--\eqref{eq:SLfarfield} as boundary integral
-equations (BIEs) and discretize each BIE at $N$ points on each of the
-$N_b$ particles with a collocation method. To express the solution
-of~\eqref{eq:SLpde}--\eqref{eq:SLfarfield}, we adopt the double layer
-potential
+We recast \eqref{eq:stokes}--\eqref{eq:rigid-vel} and \eqref{eq:SL}
+as boundary integral equations (BIEs) and discretize each BIE at
+$N$ points on each of the $N_b$ particles with a collocation method.
+To express the solution of \eqref{eq:SL},
+we adopt the double layer potential
 \begin{align}
 \label{eq:SL_BIE}
-  u({\xx}) = \DD[\sigma](\xx) = \int_\Gamma 
-    \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, 
-    \dif s_\yy, \quad \xx \in \Omega,
+u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy
+, \quad \xx \in \Omega,
 \end{align}
-where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
-solution to the screened Laplace equation~\eqref{eq:SLpde}, $K_0$ is the
-zeroth-order modified Bessel function of the first kind, and $\sigma$ is
-a scalar-valued density function.  The subscript in $\dif s_\yy$ denotes
-integration with respect to $\yy \in \Gamma$.  For the velocity, we use
-the representation~\cite{pow-mir1987}
+where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL},
+$K_0$ is the zeroth-order modified Bessel function of the first kind,
+and $\sigma$ is a scalar-valued density function.
+The subscript in $\dif s_\yy$ denotes integration with respect to $\yy \in \Gamma$. 
+For the velocity, we use the representation [REF]
 \begin{align}
@@
 \end{align}
-with the vector-valued density function $\eeta$, Stokeslet
-$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr
-\otimes \rr}{|\rr|^2}\right)$, and Rotlet $\RR(\xx,\aa_i) =
-\frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$, $\rr = \xx - \aa_i$.
+with the vector-valued density function $\eeta$,
+Stokeslet 
+$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr \otimes \rr}{|\rr|^2}\right)$,
+and Rotlet
+$\RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$,
+$\rr = \xx - \aa_i$ [REF].
 
@@
 
-First, we must simplify the form of the free energy
-\eqref{eq:free_energy} using integration by parts and \eqref{eq:SLpde}
+First, we must simplify the
+form of the free energy \eqref{eq:free_energy}
+using integration by parts and \eqref{eq:SL}
 to obtain

### 2022-07-26 doc/PRF2022/PRF_main.tex
updated table/tidied section 2

--- 2022-07-25 doc/PRF2022/PRF_main.tex
@@
 \usepackage{commath}
-
+\usepackage{tabularx}
+\usepackage{tabularray}
 \newtheorem{lemma}{Lemma}
@@
 velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.
-Without inertia, the system in~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
-also satisfies the force-free and torque-free conditions.
-%This means
-%that the total force $\FF_i,$ and torque $T_i$ from the hydrodynamic
-%stress on each particle (with subscript `$i$') balance the force and
-%torque from the hydrophobic potential~\cite{Fu2022_JFM}. 
-The total force
-and torque from the fluid flow are
-\begin{align}
-  \label{eq:force}
- \FF_i = \int_{\Gamma_i} \ssigma \cdot \nnu_i \, \dif s, \quad
- T_i = \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
-  (\ssigma \cdot \nnu_i) \, \dif s,
-  \quad i=1,\ldots,N_b,
-\end{align}
-respectively, where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu +
-\nabla \uu^T \right)$ is the hydrodynamic stress tensor (pressure
-tensor), and $\nnu_i$ is the unit outward normal on the $i$th particle.
-
-The total force $\FF_i,$ and torque $T_i$ from the hydrodynamic
-stress on each particle (with subscript `$i$') balance the force and
-torque from the hydrophobic potential. 
-%$\FF_i$ and $T_i$ are to be in balance with the force and torque from the hydrophobic interactions between the
-%particles and the viscous solvent. 
-As in~\citet{Fu2022_JFM} such a hydrophobic attraction potential
-$u(\xx,t)$ is assumed to the minimizer of the free energy
+
+Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free conditions.
+This means that the force and torque from the hydrodynamic stress on each particle 
+are in balance with the total
+force and torque coming from the hydrophobic potential and repulsion \cite{Fu2022_JFM}.
+To compute this balance, we define
+the free energy\cite{Fu2022_JFM}
 \begin{equation}
@@
 where $u(\xx,t)$ is as an order parameter for the structure of water,
-$\rho$ is a decay length, and $\gamma$ is an interfacial tension.  The
-radius of the Janus particles $c$ also serves as an ``effective"
-distance between particle centers, below which the steric repulsion
-between a pair of JPs becomes important.
-
-The governing equation for $u(\xx,t)$ is obtained by computing the
-domain variation of the free energy $F$~\cite{Fu20}. We obtain a
-screened Laplace equation boundary value problem as a model for the
-hydrophobic interaction between water and JPs:
-\begin{alignat}{3}
-  \label{eq:SLpde}
-  -\rho^2 \Delta u + u &= 0,\qquad &&\xx \in \Omega, \\
+$\rho$ is a decay length, and $\gamma$ is an interfacial tension.
+
+The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$ \cite{Fu20}.
+Its governing equations $u(\xx,t)$ are a screened Laplace equation boundary value problem
+\begin{gather}
+  \label{eq:SL}
+  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
   \label{eq:SLbc}
-  u &= g, &&\xx \in \bd\Omega, \\
-  \label{eq:SLfarfield}
-  u &\rightarrow 0, &&|\xx| \rightarrow \infty,
-\end{alignat}
+  u = g, \quad \xx \in \bd\Omega, \quad 
+  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
+\end{gather}
 The boundary condition $g$ encodes hydrophobic properties of the
-particle-solvent interface. The parameter $\rho_0$ is an ``effective"
-distance between particle centers, below which the steric repulsion
-between a pair of JPs becomes important.
-\todo[inline]{We are calling both $c$ and $\rho_0$ as this ``effective"
-distance (see above). Also, $\rho_0$ is not defined. Should it be
-$\rho$?}
-
-To calculate forces and torques from the free energy, we compute the
-variation of the domain of the free energy~\eqref{eq:free_energy}
-subject to~\eqref{eq:SLpde}--\eqref{eq:SLbc}, and obtain 
+particle-solvent interface.
+
+The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
+\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
+\infty$. The parameter $\rho_0$ is an ``effective" distance between particle surfaces,
+below which the steric repulsion between a pair of JPs becomes important.
+The parameter $M$ is the repulsion modulus.
+
+To get the force $\FF_i$ and torque $T_i$ on $\Gamma_i$ from the free energy,
+we compute the variation of the domain of the free energy 
+\eqref{eq:free_energy} subject to \eqref{eq:SL}-\eqref{eq:SLbc},
+and obtain 
 \begin{equation}
-  \FF_i \equiv \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
+  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
   - \frac{M}{\rho_0}
@@
   ,\quad
-T_i \equiv \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
+T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
 \end{equation}
 for $i = 1,\dots,N_b$ with particle outward normal $\nu$. The term 
-\begin{align}
+$
 \mathbf{T}
@@
   + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
-\end{align}
-is the hydrophobic stress. Repulsion is rotationally symmetric and does
-not contribute to the torque. The derivation details are found
-in~\citet{Fu20}.
+$
+is the hydrophobic stress.
+Repulsion is rotationally symmetric and does not contribute to the torque.
+The derivation details are found in \citet{Fu20}.
 
@@
 \end{equation}
-where 
-%$\FF_i \in \mathbb{R}^2$ and $T_i \in \mathbb{R}$
-%are interparticle forces and torques. 
-$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
-\right)$ is the hydrodynamic stress tensor (pressure tensor).
-
-The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
-\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
-\infty$.  As such, only those particles within a distance $\rho_0$ of
-$\Gamma_i$ contribute to repulsion.  The parameter $M$ is the repulsion
-modulus.
-
+where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
+\right)$ is the hydrodynamic stress tensor.
+
+Once \eqref{eq:stokes}-\eqref{eq:force} have been solved,
+the velocities $(\vv_i, \omega_i)$ from \eqref{eq:rigid-vel}
+update the particle positions and orientations.
 We use the parameters $\mu = 1$ cP, $\gamma = 4$ pN nm$^{-1}$,
 $\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.
+These values give a characteristic time $1$ ns and characteristic length $1$ nm.
 
 \subsection{Boundary integral represenation and time stepping}
-We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
-and~\eqref{eq:SLpde}--\eqref{eq:SLfarfield} as boundary integral
-equations (BIEs) and discretize each BIE at $N$ points on each of the
-$N_b$ particles with a collocation method. To express the solution
-of~\eqref{eq:SLpde}--\eqref{eq:SLfarfield}, we adopt the double layer
-potential
+We recast \eqref{eq:stokes}--\eqref{eq:rigid-vel} and \eqref{eq:SL}
+as boundary integral equations (BIEs) and discretize each BIE at
+$N$ points on each of the $N_b$ particles with a collocation method.
+To express the solution of \eqref{eq:SL},
+we adopt the double layer potential
 \begin{align}
 \label{eq:SL_BIE}
-  u({\xx}) = \DD[\sigma](\xx) = \int_\Gamma 
-    \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, 
-    \dif s_\yy, \quad \xx \in \Omega,
+u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy
+, \quad \xx \in \Omega,
 \end{align}
-where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
-solution to the screened Laplace equation~\eqref{eq:SLpde}, $K_0$ is the
-zeroth-order modified Bessel function of the first kind, and $\sigma$ is
-a scalar-valued density function.  The subscript in $\dif s_\yy$ denotes
-integration with respect to $\yy \in \Gamma$.  For the velocity, we use
-the representation~\cite{pow-mir1987}
+where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL},
+$K_0$ is the zeroth-order modified Bessel function of the first kind,
+and $\sigma$ is a scalar-valued density function.
+The subscript in $\dif s_\yy$ denotes integration with respect to $\yy \in \Gamma$. 
+For the velocity, we use the representation [REF]
 \begin{align}
@@
 The numerator $\dot \gamma \mu$ gives the force per area provided by the solvent stresses. 
-The strain rate $\dot E$ of the body is obtained by fitting the curves the strain curves e.g.,
-Fig~\ref{fig:BC2_shear}(f).
+The strain rate $\dot E$ of the body is the slope of a linear fit to the strain curves e.g.,
+in Fig~\ref{fig:BC2_shear}(f).
+
 Calculated suspension viscosities are shown
 in Table \ref{tbl:bcii_visc}.
-We observe that for the multilamellar structure, $\mu_{\text{sus}}$ is decreasing
+The middle row gives the solid area fraction $\phi$. 
+We observe that for the multilamellar structure,
+$\mu_{\text{sus}}$ is decreasing
 with increasing shear rate.  The predicted suspension viscosities 
@@
 \begin{table}
-  \caption{Viscosity $\mu_{\text{sus}}$ (mPa s) for the Multilamellar and Striated Suspensions    
+  \caption{Suspension viscosity $\mu_{\text{sus}}$ (mPa s) 
 \label{tbl:bcii_visc}
@@
 \centering
-\begin{tabular}{c|c|c|c}
-\multicolumn{4}{c}{multilamellar BC (ii)} \\
+\begin{tabularx}{0.7\textwidth}{c|X|X|X||X|X|X}
+&\multicolumn{3}{c||}{BC (ii)} & \multicolumn{3}{c}{BC (iii)}\\
 \hline
-  $\dot \gamma$ & 0.05 & 0.10 & 0.15\\
+  $\dot \gamma$ & 0.05 & 0.10 \quad & 0.15 & 0.100 & 0.125 & 0.15\\
   \hline
-  $\phi$ & 0.50 & 0.47 & 0.41\\
+  $\phi$ & 0.50 & 0.47 & 0.41 & 0.47 & 0.46 & 0.45 \\
   \hline
-  $\mu_{\text{sus}} $ & 401 & 66 & 42\\
+  $\mu_{\text{sus}} $ & 401 & 66 & 42 & 2.5e3 & 1.4e3 & 60\\
 \hline
-\end{tabular}
-\quad \quad \quad
-\begin{tabular}{c|c|c|c}
-\multicolumn{4}{c}{striated BC (iii)} \\
-\hline
-  $\dot \gamma$ & 0.100 & 0.125 & 0.15\\
-  \hline
-  $\phi$ & 0.47 & 0.46 & 0.45\\
-  \hline
-  $\mu_{\text{sus}} $ & 2.5e3 & 1.4e3 & 60\\
-\hline
-\end{tabular}
+\end{tabularx}
 \end{table}

### 2022-08-01 doc/PRF2022/PRF_main.tex
removed tabulararray package call
added references

--- 2022-07-26 doc/PRF2022/PRF_main.tex
@@
 \usepackage{tabularx}
-\usepackage{tabularray}
 \newtheorem{lemma}{Lemma}
@@
 \begin{abstract}
-Active colloidal systems with non-equilibrium self-organization is a long-standing challenge in biology. To understand how hydrodynamic flow may be used
-to actively control self-assembly of Janus particles (JPs),  we use a model recently developed for the many-body hydrodynamics of amphiphilic JPs suspended 
-in a viscous background flow (JFM, 941, 2022). We investigate how various bilayer structures arise from tuning the hydrophobicity/hydrophilicity of the JPs. 
-Focusing on three distributions of hydrophobicity we found JPs may assemble into uni-lamella, multi-lamella, and striated structures in a viscous fluid. 
-Under a linear flow and a Taylor-Green mixing flow,  we use three measures to quantify the collective dynamics of JP particles under a background flow: 
-(a) Free energy from the hydrophobic interactions between the JPs, (b) an order parameter for the ordering of JPs in terms of alignment of their directors, 
-and (c) a strain parameter that captures the deformation in the assembly. We found the dynamics of these three measures correlate well with the hydrodynamics 
-of JPs. These numerical provide insights into dynamic control of non-equilibrium active biological systems with similar self-organization.
+  Active colloidal systems with non-equilibrium self-organization
+  is a long-standing challenging area in biology.
+  To understand how hydrodynamic flow may be used to actively
+  control self-assembly of Janus particles (JPs), we use a model
+  recently developed for the many-body hydrodynamics of amphiphilic
+  JPs suspended in a viscous background flow (JFM, 941, 2022).
+  We investigate how various bilayer structures arise from tuning
+  the hydrophobic properties of the JP-solvent interface.
+  Focusing on a simple tuing of the hydrophobicity distribution,
+  we found
+  JPs assembled into uni-lamella, multi-lamella and striated
+  structures.  To introduce dynamics, we include a linear shear flow and a
+  Taylor-Green mixing flow, and measure the
+  collective dynamics of JP particles in terms of their 
+  (a) free energy from the hydrophobic interactions between the JPs,
+  (b) order parameter for the ordering of JPs in terms of alignment of their directors, 
+  and (c) strain parameter that captures the deformation in the assembly.
+  We characterized the effective material proporties of the JP structures
+  and found that the uni-lamellar structures increases orientation order under
+  shear flow, the multilamellar structure behaves as a shear thinning fluid,
+  and the striated structure possesses a finite yield stress.  
+  These numerical result provide insights into dynamic control of
+  non-equilibrium active biological systems with similar self-organization.
 % insert abstract here
@@
 % References should be done using the \cite, \ref, and \label commands
-
-\todo[inline]{Here are some references that Yuan sent around in the last
-few weeks}
-\cite{KolevaRehage2012_SoftMatter}
-\cite{GrandmaisonBrancherieSalasac2021_JFM}
-\cite{MusselLewisBasserHorkay2022_PRM}
-\cite{HuLongZangEHan2022_arxiv}
-\cite{BoccardoPierreLouis2022_PRL}
 
@@
 %\section{\label{}}
-Janus particles are colloids with two surfaces of different properties such as hydrophobicity. For example, it is common for the surface of a Janus particle to
+Janus particles (JPs) are colloids with two surfaces of different
+properties.
+For example, it is common for the surface of a Janus particle to
 be partly hydrophilic and hydrophobic (polar and non-polar).
-In a viscous solvent Janus particles often self-assemble into structures with tunable functions for biomedical engineering applications \cite{GheisariSahfieeAbbasiEtAl2021_DMR,LiuYangHuangEtAl2016_Angew,LiWangYaoEtAl2019_Nanoscale}.
-Depending on the interactions between Janus particles and the surrounding viscous solvent, JPs self-assemble into oligomers of various geometries and sizes.
-
-{\bf The following paragraph needs to be rephrased and inserted in the introduction.
-"Dynamics offers yet another dimension of control that emerges naturally from the interactions between particles and fluid in colloidal matter.
-....Such active colloidal systems show nonequilibrium self-organization with complexity rivaling that of biological systems such as living cells, bacterial baths, and animal flocks.....long-standing challenges such as the ``inverse" problem of creating a colloidal system that will self-assemble into a prescribed structure.....the framework of geometrical frustration, which has been used to explain dis-ordered systems, could be used to design new ones instead, through specific choices for the shapes or interactions of the particles....\cite{Manoharan2015_Science}"}
-
-The many-body hydrodynamics of amphiphilic Janus particles (JP) suspended in a viscous fluid (at zero Reynolds number) has been studied using
-boundary integral numerical simulations \cite{Fu2022_JFM}. Janus particles consist of both a hydrophobic and a hydrophilic surfaces. 
-Immersed in a viscous solvent, the dynamics of a JP suspension results from the combination of long-range hydrodynamic interaction and non-local
-interactions between JPs through the distribution of a hydrophobic potential (HAP). In a quiescent flow, numerical simulations of a 
-JP suspension showed self-assembly into micelles and bilayers of JPs that provide an alternative means for computing the 
-mechanical moduli of a colloidal membrane.
-
+In a viscous solvent, Janus particles often self-assemble into
+structures with tunable functions for biomedical engineering
+applications
+\cite{
+  GheisariSahfieeAbbasiEtAl2021_DMR,
+  LiuYangHuangEtAl2016_Angew,
+  LiWangYaoEtAl2019_Nanoscale,
+  Bradley2016}.
+Depending on the interactions between Janus particles and the surrounding viscous solvent,
+JPs self-assemble into oligomers of various geometries and sizes\cite{Bradley2017}.
+
+Dynamics offers yet another dimension of control that emerges naturally
+from the interactions between particles and fluid in colloidal matter \cite{Brandner2019,RevModPhys.93.025008}.
+Active colloidal systems show nonequilibrium self-organization with
+complexity rivaling that of biological systems such as living cells,
+bacterial baths, and animal flocks\cite{CollardGrosjeanVandewalle2020,Vutukuri2020}.
+A long-standing challenge in fluid mechanics
+and material science is to solve the ``inverse" problem of creating a model
+colloidal system that will self-assemble into a prescribed structure
+\cite{PhysRevLett.128.256102}.
+For example, the framework of geometrical frustration, which has been
+used to explain disordered systems, could be used to design new, ordered systems
+instead, through specific choices for the shapes or interactions of the particles
+\cite{Manoharan2015_Science}.
+
+The many-body hydrodynamics of amphiphilic Janus particles (JP)
+assembled as vesicles and suspended
+in a viscous fluid (at zero Reynolds number) has been studied using
+boundary integral numerical simulations \cite{Fu20,Fu2022_JFM}.
+The dynamics of the JP suspension results from the combination
+of long-range hydrodynamic interaction and non-local
+interactions between JPs through the distribution of
+a hydrophobic attraction potential (HAP).
+
+In a quiescent flow, numerical simulations of a 
+JP suspension showed self-assembly into micelles and bilayers of
+JPs that provide an alternative means for computing the 
+mechanical moduli of a colloidal membrane \cite{NaTr00,Fu20,KrFiGuKaHa13}.
 Under background flows, the hydrodynamics of a JP vesicle (a
@@
 vesicle \cite{Fu2022_JFM}: 
-Elongation and alignment along the extensional direction, tank-treading, and rupture of a vesicle under shear flow.
-
-In this work we take advantage of the flexibility of the model to examine the effects of boundary condition on JP surfaces that could be controlled based on the chemicals used in the experiments, for example.
+elongation and alignment along the extensional direction, tank-treading,
+and rupture of a vesicle under shear flow.
+
+In this work we take advantage of the flexibility of the model to examine the
+effects of boundary condition on JP surfaces that could be controlled
+based on the chemicals used in the experiments, for example.
+It turns out that a simple tuning of the hydrophobic distribution
+leads to multilamellar and striated structures. 
+Here less is understood about the flow-structure interactions
+and we investigate the
+deformation of these novel materials in background flows
+and map out their collective behavior away from equilibrium.
 
@@
 are in balance with the total
-force and torque coming from the hydrophobic potential and repulsion \cite{Fu2022_JFM}.
+force and torque coming from the hydrophobic potential and repulsion.
 To compute this balance, we define
-the free energy\cite{Fu2022_JFM}
+the free energy\cite{Ma77, GoHaKo94, Fu20, Fu2022_JFM}
 \begin{equation}
@@
 
-The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$ \cite{Fu20}.
+The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$.
 Its governing equations $u(\xx,t)$ are a screened Laplace equation boundary value problem
@@
 
-To get the force $\FF_i$ and torque $T_i$ on $\Gamma_i$ from the free energy,
+To get the force $\FF_i$ and torque $T_i$ on $\Gamma_i$ from the free energy\cite{Fu20},
 we compute the variation of the domain of the free energy 
@@
 Repulsion is rotationally symmetric and does not contribute to the torque.
-The derivation details are found in \citet{Fu20}.
 
@@
 the heads are also hydrophobic and so in the long-time dynamics
-these bilayers form multilamella structures.
+these bilayers form multilamella structures\cite{C9NR05885K}.
 The number of folds depends primarily on the number of particles.
@@
 $w_i = \exp(-\|\aa_j(0) - \aa_i(0)\|/4c)$ with particle radius $c$
-ensure that nearby particles contribute the most to the linear approximation at $\aa_i$.
+ensure that the linear approximation is valid for
+particles near $\aa_i$.
 
@@
 In this section, we subject the Janus particle structures to various background
-flows.  The purpose of this study is to understand how self-assembled particles
-respond to external fluid forcing.  We can then compare the results to guage
-the effective properties of materials comprised of Janus particles as a function
+flows.  The purpose is to understand how self-assembled particles
+respond to external forcing.
+We can then compare effective properties of
+materials comprised of Janus particles as a function
 of their amphiphilic properties.  
@@
 Focusing on drawing analogies to hydrodynamics of a vesicle in continuum modeling
-(such as tank-treading, bilayer slip and permeability),
+(such as tank-treading \cite{keller_skalak_1982,Finken08,Shaqfeh11}, bilayer slip \cite{sch-vla-mik2010,denOtter2007,Zgorski2019}, and permeability \cite{chabanon2017,qua-gan-you2021}),
 our previous studies showed the existence of a critical shear
-rate above which the JP vesicle ruptures. 
+rate above which the JP vesicle ruptures
+\cite{grandmaison_brancherie_salsac_2021,D2SM00179A}. 
 Based on the these early results, we
@@
 In previous work, \cite{Fu2022_JFM} determined the permeability constant of particle-based vesicles
-in the context of shear background flow.
+in the context of shear background flow\cite{chabanon2017,qua-gan-you2021}.
 
@@
 and found that using $N = 16$ or $N = 24$ grid points per particle gave quantitavely indistinguishable
-results.  The time courses consisted of $O(10^3)$ time steps with $\Delta = 0.2$ nm.
+results.  The time courses consisted of $O(10^3)$ time steps with $\Delta t = 0.2$ nm.
 
@@
 based on the changes in free energy, orientationl order, and strain as a function
-of flow strength.  Generally, $F$ increases, $\tilde S_2$ decreases, and 
+of flow strength.
+Generally, $F$ increases, $\tilde S_2$ decreases, and 
 $E$ increases with increases in both $\dot \gamma$ and $V_0$, as expected.
@@
 the multilamellar (BC (ii)) structure behaves as shear thinning fluid
-while the striated structure (BC (iii)) has a finite yield stress and
-behaves as a Bingham plastic. 
+while the striated structure (BC (iii)) has a finite yield stress. 
 Qualitatively, the strains for BC (ii) increases gradually 
@@
 in Table \ref{tbl:bcii_visc}.
-The middle row gives the solid area fraction $\phi$. 
+The middle row gives the solid area fraction $\phi$;
+the sum of the rigid particle areas divided by the
+total area of the solvent and particle region.
 We observe that for the multilamellar structure,
 $\mu_{\text{sus}}$ is decreasing
-with increasing shear rate.  The predicted suspension viscosities 
-are on the order of hundreds of times that of water, consistent with
-measurements of noninteracting particle suspensions\cite{KONIJN201461}.
-In the case of striated structures, viscosity is effectively infinite
-for the lower two of the shear rates, and then drops to a finite value $\mu_{\text{sus}} = 60$ mPa s
+with increasing shear rate.
+The predicted suspension viscosities 
+are on the order of hundreds of times that of water,
+consistent with measurements of noninteracting
+particle suspensions\cite{KONIJN201461}.
+In the case of striated structures, viscosity is
+effectively infinite for the lower two of the shear rates,
+and then drops to a finite value $\mu_{\text{sus}} = 60$ mPa s
 when the shear rate reaches $0.15$ ns$^{-1}$.
@@
 because the viscosities of bilayer are in-plane and require fully three-dimensional
-simulations to resolve.  Our previous work 
+simulations to resolve\cite{denOtter2007,Zgorski2019,doi:10.1073/pnas.2100156118}.  Our previous work 
 did calculate, however, an intermonolayer friction coefficient $b$
@@
 by subjecting the suspension to a moderate shear flow.
-Not all background flows produce this effect, as it was not
+Not all background flows produce this ``organizing'' effect, as it was not
 observed in the TG background flow case (Fig~\ref{fig:BC1_TG}).
+\citet{PhysRevLett.128.256102} have shown how to drive particle clusters into arbitrary target shapes by solving
+a first passage problem.
 
@@
 
+The characteristics of the self-assembly of amphiphilic JP into onion-like
+dendrimersomes have been studied
+by molecular dynamics simulations\cite{C9NR05885K}.  
+The molecular dynamics simulations
+use an anisotropic pair potential
+is used to describe the particle interactions
+where a harmonic form describes the repulsive part 
+and an anisotropic attractive part describes the hydrophobic interactions.
 \section{Conclusion}
+
 \label{sec:conclusion}

### 2022-08-01 doc/PRF2022/PRF_main.tex
updated manuscript

@@
 update the particle positions and orientations.
-We use the parameters $\mu = 1$ cP, $\gamma = 4$ pN nm$^{-1}$,
+We use the parameters $\mu = 1$ mPa s, $\gamma = 4$ pN nm$^{-1}$,
 $\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.
@@
 \[
-\mu_{\text{sus}} = \frac{\dot \gamma}{\dot E} \mu
+\mu_{\text{hyd}} = \frac{\dot \gamma}{\dot E} \mu
 \]
-as an effective dynamic viscosity of the suspension.
-The numerator $\dot \gamma \mu$ gives the force per area provided by the solvent stresses. 
+as an effective dynamic viscosity of the particle assemblies.
+The numerator $\dot \gamma \mu$ gives the force per
+area provided by the solvent stresses where
+$\mu = 1$ mPa s is
+the solvent viscosity.
 The strain rate $\dot E$ of the body is the slope of a linear fit to the strain curves e.g.,
@@
 
-Calculated suspension viscosities are shown
+Calculated viscosities of particle assemblies are shown
 in Table \ref{tbl:bcii_visc}.
@@
 We observe that for the multilamellar structure,
-$\mu_{\text{sus}}$ is decreasing
+$\mu_{\text{hyd}}$ decreases
 with increasing shear rate.
-The predicted suspension viscosities 
+The predicted viscosities of the particle assemblies
 are on the order of hundreds of times that of water,
-consistent with measurements of noninteracting
-particle suspensions\cite{KONIJN201461}.
+consistent with suspension viscosities for noninteracting
+particles \cite{KONIJN201461}.
 In the case of striated structures, viscosity is
 effectively infinite for the lower two of the shear rates,
-and then drops to a finite value $\mu_{\text{sus}} = 60$ mPa s
+and then drops to a finite value $\mu_{\text{hyd}} = 60$ mPa s
 when the shear rate reaches $0.15$ ns$^{-1}$.
 \begin{table}
-  \caption{Suspension viscosity $\mu_{\text{sus}}$ (mPa s) 
+  \caption{Dynamic viscosity of assemblies $\mu_{\text{hyd}}$ (mPa s) 
 \label{tbl:bcii_visc}
@@
 
-We have not calculated suspension viscosities for the type (i) boundary condition,
-because the viscosities of bilayer are in-plane and require fully three-dimensional
-simulations to resolve\cite{denOtter2007,Zgorski2019,doi:10.1073/pnas.2100156118}.  Our previous work 
-did calculate, however, an intermonolayer friction coefficient $b$
-which is related but conceptually different than viscosity \cite{Fu2022_JFM}.
+In the case of BC (i), our previous work\cite{Fu2022_JFM} calculated a
+friction coefficient $b$ for the intermonolayer slip between the two leaflets
+of a bilayer. \citet{denOtter2007,Zgorski2019} and
+\citet{doi:10.1073/pnas.2100156118} have
+calculated in-plane viscosities for fully three-dimensional bilayers.
+Although not part of this work,
+it is in principle possible to obtain an in-plane
+viscosity using the hydrophobic potential
+\eqref{eq:free_energy}
+by replacing the boundary condition \eqref{eq:bc-type}
+with one that is everywhere constant, in effect modeling
+lipids in a bilayer as an array of as elongated, purely hydrophobic pilars.
 

### 2022-08-01 doc/PRF2022/PRF_main.tex
worked on early secs of paper

@@
   the hydrophobic properties of the JP-solvent interface.
-  Focusing on a simple tuing of the hydrophobicity distribution,
+  Focusing on a simple tuning of the hydrophobicity distribution,
   we found
@@
   and (c) strain parameter that captures the deformation in the assembly.
-  We characterized the effective material proporties of the JP structures
+  We characterized the effective material properties of the JP structures
   and found that the uni-lamellar structures increases orientation order under
@@
 Janus particles (JPs) are colloids with two surfaces of different
-properties.
-For example, it is common for the surface of a Janus particle to
-be partly hydrophilic and hydrophobic (polar and non-polar).
+properties. For example, it is common for the surface of a Janus
+particle to be partly hydrophilic and hydrophobic (polar and non-polar).
 In a viscous solvent, Janus particles often self-assemble into
 structures with tunable functions for biomedical engineering
-applications
-\cite{
-  GheisariSahfieeAbbasiEtAl2021_DMR,
-  LiuYangHuangEtAl2016_Angew,
-  LiWangYaoEtAl2019_Nanoscale,
-  Bradley2016}.
-Depending on the interactions between Janus particles and the surrounding viscous solvent,
-JPs self-assemble into oligomers of various geometries and sizes\cite{Bradley2017}.
+applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
+LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale, Bradley2016}.
+Depending on the interactions between Janus particles and the
+surrounding viscous solvent, JPs self-assemble into oligomers of various
+geometries and sizes~\cite{Bradley2017}.
 
 Dynamics offers yet another dimension of control that emerges naturally
-from the interactions between particles and fluid in colloidal matter \cite{Brandner2019,RevModPhys.93.025008}.
-Active colloidal systems show nonequilibrium self-organization with
-complexity rivaling that of biological systems such as living cells,
-bacterial baths, and animal flocks\cite{CollardGrosjeanVandewalle2020,Vutukuri2020}.
-A long-standing challenge in fluid mechanics
-and material science is to solve the ``inverse" problem of creating a model
-colloidal system that will self-assemble into a prescribed structure
-\cite{PhysRevLett.128.256102}.
-For example, the framework of geometrical frustration, which has been
-used to explain disordered systems, could be used to design new, ordered systems
-instead, through specific choices for the shapes or interactions of the particles
-\cite{Manoharan2015_Science}.
-
-The many-body hydrodynamics of amphiphilic Janus particles (JP)
-assembled as vesicles and suspended
-in a viscous fluid (at zero Reynolds number) has been studied using
-boundary integral numerical simulations \cite{Fu20,Fu2022_JFM}.
-The dynamics of the JP suspension results from the combination
-of long-range hydrodynamic interaction and non-local
-interactions between JPs through the distribution of
-a hydrophobic attraction potential (HAP).
-
-In a quiescent flow, numerical simulations of a 
-JP suspension showed self-assembly into micelles and bilayers of
-JPs that provide an alternative means for computing the 
-mechanical moduli of a colloidal membrane \cite{NaTr00,Fu20,KrFiGuKaHa13}.
-Under background flows, the hydrodynamics of a JP vesicle (a
-self-enclosed bilayer of JPs) exhibit many familiar behaviors of a
-vesicle \cite{Fu2022_JFM}: 
-elongation and alignment along the extensional direction, tank-treading,
-and rupture of a vesicle under shear flow.
-
-In this work we take advantage of the flexibility of the model to examine the
-effects of boundary condition on JP surfaces that could be controlled
-based on the chemicals used in the experiments, for example.
-It turns out that a simple tuning of the hydrophobic distribution
-leads to multilamellar and striated structures. 
-Here less is understood about the flow-structure interactions
-and we investigate the
-deformation of these novel materials in background flows
-and map out their collective behavior away from equilibrium.
-
+from the interactions between particles and fluid in colloidal
+matter~\cite{Brandner2019,RevModPhys.93.025008}. Active colloidal
+systems show nonequilibrium self-organization with complexity rivaling
+that of biological systems such as living cells, bacterial baths, and
+animal flocks~\cite{CollardGrosjeanVandewalle2020,Vutukuri2020}. A
+long-standing challenge in fluid mechanics and material science is to
+solve the ``inverse" problem of creating a model colloidal system that
+will self-assemble into a prescribed
+structure~\cite{PhysRevLett.128.256102}. For example, the framework of
+geometrical frustration, which has been used to explain disordered
+systems, could be used to design new, ordered systems instead, through
+specific choices for the shapes or interactions of the
+particles~\cite{Manoharan2015_Science}.
+
+The many-body hydrodynamics of amphiphilic Janus particles assembled as
+vesicles and suspended in a viscous fluid (at zero Reynolds number) has
+been studied using boundary integral numerical
+simulations~\cite{Fu20,Fu2022_JFM}. The dynamics of the JP suspension
+results from the combination of long-range hydrodynamic interaction and
+non-local interactions between JPs through the distribution of a
+hydrophobic attraction potential (HAP).
+
+In a quiescent flow, numerical simulations of a JP suspension showed
+self-assembly into micelles and bilayers of JPs that provide an
+alternative means for computing the mechanical moduli of a colloidal
+membrane~\cite{NaTr00,Fu20,KrFiGuKaHa13}. Under background flows, the
+hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
+many familiar behaviors of a vesicle~\cite{Fu2022_JFM}: elongation and
+alignment along the extensional direction, tank-treading, and rupture of
+a vesicle under shear flow.
+
+In this work we take advantage of the flexibility of the model to
+examine the effects of boundary condition on JP surfaces that could be
+controlled based on the chemicals used in the experiments, for example.
+We show that a simple tuning of the hydrophobic distribution leads to
+multilamellar and striated structures. Here less is understood about the
+flow-structure interactions and we investigate the deformation of these
+novel materials in background flows and map out their collective
+behavior away from equilibrium.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Mobility problem}
@@
 %RJR: In the above sentence, suspection and immersed are redundant 
-The Janus particles are suspended in a viscous solvent.
-The particles are disks of radius $c$, center $\aa_i$, and
-orientation $\theta_i$ relative to the horizontal axis, where $i = 1, \dots, N_b$
-and $N_b$ is the number of particles.
-The domain $\Omega(t) \subset \mathbb{R}^2$ is the solvent phase and $t$
-is time.  The boundary of
-$\Omega$ is $\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where
-$\Gamma_i$ is the boundary of Janus particle $i$. Assuming inertial
-terms are negligible, we have 
+The Janus particles are suspended in a viscous solvent. The particles
+are disks of radius $c$, center $\aa_i$, and orientation $\theta_i$
+relative to the horizontal axis, where $i = 1, \dots, N_b$ and $N_b$ is
+the number of particles. The domain $\Omega(t) \subset \mathbb{R}^2$ is
+the solvent phase and $t$ is time. The boundary of $\Omega$ is
+$\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where $\Gamma_i$
+is the boundary of Janus particle $i$. Assuming inertial terms are
+negligible, we have 
 \begin{alignat}{3}
@@
     \quad \xx \in \Gamma_i,
-\end{equation}
+\end{align}
 where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
@@
 
-Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free conditions.
-This means that the force and torque from the hydrodynamic stress on each particle 
-are in balance with the total
-force and torque coming from the hydrophobic potential and repulsion.
-To compute this balance, we define
-the free energy\cite{Ma77, GoHaKo94, Fu20, Fu2022_JFM}
-\begin{equation}
+Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free
+conditions. This means that the force and torque from the hydrodynamic
+stress on each particle balance the total force and torque coming from
+the hydrophobic potential and repulsion. To compute this balance, we
+define the free energy~\cite{Ma77, GoHaKo94, Fu20, Fu2022_JFM}
+\begin{align}
 \label{eq:free_energy}
 F = \gamma
-\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
+  \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} u^2 \right)
 \,d\xx
@@
 \sum_{j \neq i} 
-P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
-\end{equation}
+P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right),
+\end{align}
 where $u(\xx,t)$ is as an order parameter for the structure of water,
@@
 
-The order parameter $u(\xx,t)$ is assumed to the minimizer of the free energy $F$.
-Its governing equations $u(\xx,t)$ are a screened Laplace equation boundary value problem
+The order parameter $u(\xx,t)$ is assumed to minimize the free energy
+$F$. Its governing equations $u(\xx,t)$ are a screened Laplace equation
+boundary value problem
 \begin{gather}
@@
 \sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
-\infty$. The parameter $\rho_0$ is an ``effective" distance between particle surfaces,
-below which the steric repulsion between a pair of JPs becomes important.
-The parameter $M$ is the repulsion modulus.
-
-To get the force $\FF_i$ and torque $T_i$ on $\Gamma_i$ from the free energy\cite{Fu20},
-we compute the variation of the domain of the free energy 
-\eqref{eq:free_energy} subject to \eqref{eq:SL}-\eqref{eq:SLbc},
-and obtain 
-\begin{equation}
+\infty$. The parameter $\rho_0$ is an ``effective" distance between
+particle surfaces, below which the steric repulsion between a pair of
+JPs becomes important. The parameter $M$ is the repulsion modulus.
+
+To calculate the force $\FF_i$ and torque $T_i$ on $\Gamma_i$ from the
+free energy~\cite{Fu20}, we compute the variation of the domain of the
+free energy~\eqref{eq:free_energy} subject
+to~\eqref{eq:SL}--\eqref{eq:SLbc}, and obtain 
+\begin{align}
   \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
@@
 T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
-\end{equation}
-for $i = 1,\dots,N_b$ with particle outward normal $\nu$. The term 
-$
-\mathbf{T}
-= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
+\end{align}
+for $i = 1,\dots,N_b$ with particle outward normal $\nnu$, where
+\begin{align}
+\mathbf{T} = \gamma \left[ \rho^{-1} u^2 \mathbf{I}
   + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
-$
-is the hydrophobic stress.
-Repulsion is rotationally symmetric and does not contribute to the torque.
+\end{align}
+is the hydrophobic stress. The repulsion is rotationally symmetric and
+does not contribute to the torque.
 
 Since the force and torque from the hydrodynamic stress on each particle
-are in balance with the total force and torque coming from the
-hydrophobic potential and repulsion, we have
+balance the total force and torque coming from the hydrophobic potential
+and repulsion, we have
 \begin{equation}
@@
 
-Once \eqref{eq:stokes}-\eqref{eq:force} have been solved,
-the velocities $(\vv_i, \omega_i)$ from \eqref{eq:rigid-vel}
-update the particle positions and orientations.
-We use the parameters $\mu = 1$ mPa s, $\gamma = 4$ pN nm$^{-1}$,
-$\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.
-These values give a characteristic time $1$ ns and characteristic length $1$ nm.
-
-\subsection{Boundary integral represenation and time stepping}
-We recast \eqref{eq:stokes}--\eqref{eq:rigid-vel} and \eqref{eq:SL}
-as boundary integral equations (BIEs) and discretize each BIE at
-$N$ points on each of the $N_b$ particles with a collocation method.
-To express the solution of \eqref{eq:SL},
-we adopt the double layer potential
+Once \eqref{eq:stokes}--\eqref{eq:force} have been solved, the
+velocities $(\vv_i, \omega_i)$ from~\eqref{eq:rigid-vel} update the
+particle positions and orientations.  We use the parameters $\mu = 1$
+mPa s, $\gamma = 4$ pN nm$^{-1}$, $\rho = 5$ nm, $c = 1.25$ nm, $M = 2$
+pN, and $\rho_0 = 0.5$ nm.  These values give a characteristic time $1$
+ns and characteristic length $1$ nm.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Boundary integral representation and time stepping}
+We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
+and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
+and discretize each BIE at $N$ points on each of the $N_b$ particles
+with a collocation method. To express the solution of
+\eqref{eq:SL}--\eqref{eq:SLbc}, we adopt the double layer potential
 \begin{align}
 \label{eq:SL_BIE}
-u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy
-, \quad \xx \in \Omega,
+u({\xx}) = \DD[\sigma](\xx) = \int_\Gamma 
+  \pderiv{G(\xx-\yy)}{\nnu_\yy}\sigma(\yy)\, \dif s_\yy, 
+  \quad \xx \in \Omega,
 \end{align}
-where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL},
-$K_0$ is the zeroth-order modified Bessel function of the first kind,
-and $\sigma$ is a scalar-valued density function.
-The subscript in $\dif s_\yy$ denotes integration with respect to $\yy \in \Gamma$. 
-For the velocity, we use the representation [REF]
+where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
+solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
+zeroth-order modified Bessel function of the first kind, and $\sigma$ is
+a scalar-valued density function. The subscript in $\dif s_\yy$ denotes
+integration with respect to $\yy \in \Gamma$. To satisfy the boundary
+condition~\eqref{eq:SLbc}, the density function must satisfy
+\begin{align}
+  \label{eq:SL_BIE2}
+  g(\xx) = \frac{1}{2} \sigma(\xx) + \DD[\sigma](\xx), \quad
+    \xx \in \Gamma.
+\end{align}
+
+For the velocity, we use the representation
 \begin{align}
@@
 \end{align}
-with the vector-valued density function $\eeta$,
-Stokeslet 
-$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr \otimes \rr}{|\rr|^2}\right)$,
-and Rotlet
-$\RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$,
-$\rr = \xx - \aa_i$ [REF].
-
-Finally, together with \eqref{eq:velocity},
-\eqref{eq:stokes}-\eqref{eq:rigid-vel} become 
+where $\eeta$ is a vector-valued density function and
+\begin{align}
+  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
+    \frac{(\xx - \yy) \cdot \nnu}{|\xx - \yy|^2}
+    \frac{(\xx - \yy) \otimes (\xx - \yy)}{|\xx - \yy|^2}
+    \cdot \eeta(\yy)\, \dif s_\yy.
+\end{align}
+The Stokeslets and Rotlets are
+\begin{align}
+  \SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} +
+    \frac{\rr \otimes \rr}{|\rr|^2}\right), \quad 
+  \RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}, 
+\end{align}
+respectively, where $\rr = \xx - \aa_i$~\cite{pow-mir1987}. Letting
+$\xx$ approach $\Gamma_i$ in~\eqref{eq:velocity}, applying the jump
+condition of the double layer potential~\cite{poz1992}, and imposing the
+no-slip boundary condition~\eqref{eq:rigid-vel}, the density function
+$\eeta$, translational velocity $\vv_i$, and rotational velocity
+$\omega_i$ satisfy
 \begin{alignat}{3}
@@
     \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
-  \label{eq:mobility}
+  \label{eq:vel_BLM_rep2}
   \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
@@
 \end{alignat}
-for $\xx \in \Gamma_i$ and $i = 1,\dots,N_b$ [REF].
-
-We discretize \eqref{eq:SL_BIE} and \eqref{eq:vel_BLM_rep}
-using high-order interpolation-based quadrature rules.
-Integrals that are smooth are computed with
-the spectrally-accurate trapezoid rule, and nearly-singular integrals,
-caused by close contact between two particles, are computed with a
-high-order interpolation-based quadrature rule \cite{qua-bir2014}.
-
-After discretizing and applying quadrature,
-the result is an $NN_b \times NN_b$ and $2NN_b \times 2NN_b$
-linear system for \eqref{eq:SL_BIE} and \eqref{eq:vel_BLM_rep}, respectively.
-These are solved with matrix-free GMRES, and we guarantee that the number of
-GMRES iterations is mesh-independent by using second-kind BIEs.
-
+for $\xx \in \Gamma_i$ and $i = 1,\dots,N_b$.
+
+We discretize~\eqref{eq:SL_BIE2}
+and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} using high-order
+interpolation-based quadrature rules.  Integrals that are smooth are
+computed with the spectrally-accurate trapezoid rule, and
+nearly-singular integrals, caused by close contact between two
+particles, are computed with a high-order interpolation-based quadrature
+rule~\cite{qua-bir2014}.
+
+After discretizing and applying quadrature, the result is an $NN_b
+\times NN_b$ and $2NN_b \times 2NN_b$ linear system
+for~\eqref{eq:SL_BIE2}
+and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
+These are solved with matrix-free GMRES, and we guarantee that the
+number of GMRES iterations is mesh-independent by using second-kind
+BIEs.
+
+\todo[inline]{BRYAN IS HERE}
 %Once the translational and angular velocities $\vv_i, \omega_i$
@@
   depending on the boundary condition \eqref{eq:bc-type}.
-  Panel (b) is for $b=1$ and the boundary condition mimicks that
+  Panel (b) is for $b=1$ and the boundary condition mimics that
   of an amphiphilic particle giving bilayer structures. 
@@
   The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
-  The insest in panel (b)--(d) are configurations using $N_b=60$ and share the same color map
+  The inset in panel (b)--(d) are configurations using $N_b=60$ and share the same color map
   as the main panels.}
@@
 respectively. 
-BC (i) with $b = 1$ mimicks an amphiphilic particle.
+BC (i) with $b = 1$ mimics an amphiphilic particle.
 The boundary data $g$ is everywhere nonnegative,
@@
 This can be considered as evidence that the free energy per particle with specified
-boundary condtions is independent of the total particle number $(N_b)$.
+boundary conditions is independent of the total particle number $(N_b)$.
 
@@
 are slightly decreasing (Fig~\ref{fig:BC1_shear}(d)),
-with the overall changes occuring in the range of a few $\mathrm{k_BT}$/nm.  
+with the overall changes occurring in the range of a few $\mathrm{k_BT}$/nm.  
 This suggests that
@@
 are the horizontal and vertical coordinates, respectively. 
-The TG flow is a confining flow consisting of a checkboard pattern
-of cells with alternating circulation.  We control the flow by the
+The TG flow is a confining flow consisting of a checkerboard pattern
+of cells with alternating circulation.  We control the flow by 
 the dimensionless flow strength $V_0$ and the dimensionless cell size $l$
@@
 TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s.  
-For the smallest cell size $l = 1$ tested, the vesicle is somewhat octogonal
+For the smallest cell size $l = 1$ tested, the vesicle is somewhat octagonal
 and passes through multiple cells (Fig~\ref{fig:BTG_Scale}(a)).
@@
 multilamellar and striated configurations become disordered.  For BC (ii),
-the lamella break apart so that individual bilayers are no longer discernable
+the lamella break apart so that individual bilayers are no longer discernible
 (Fig~\ref{fig:BC2_shear}(c)).
@@
 suggests that the multilamellar configuration
-allows for local rearrangment of the particles while retaining the overall shape.
+allows for local rearrangement of the particles while retaining the overall shape.
 
@@
 Our results were for $N_b = 60$.  This particle number was large enough for the JP to form
-measurable structures while giving managable simulation times (days) on a single computing processor.
-The simulation time for $N_b = 198$ in Fig. \ref{fig:relax} and Fig. \ref{fig:relax_energy}
+measurable structures while giving manageable simulation times (days) on a single computing processor.
+The simulation time for $N_b = 198$ in Figure~\ref{fig:relax} and Fig. \ref{fig:relax_energy}
 was several weeks, and so we avoided simulations of this size for our results.
 We used $N = 16$ grid points per particles for all simulations.  We performed a convergence study
-and found that using $N = 16$ or $N = 24$ grid points per particle gave quantitavely indistinguishable
+and found that using $N = 16$ or $N = 24$ grid points per particle gave quantitatively indistinguishable
 results.  The time courses consisted of $O(10^3)$ time steps with $\Delta t = 0.2$ nm.
@@
 of the shape/intensity of the hydrophobic interface.  In practice, $\rho > 0$ is fixed
-and the JP assume different configurations.  As a result, the equilbrium energies
+and the JP assume different configurations.  As a result, the equilibrium energies
 per particle in our simulations are different and depend on the boundary condition
@@
 
-We can characterize the effective material proporties of the JP structures
+We can characterize the effective material properties of the JP structures
 based on the changes in free energy, orientationl order, and strain as a function
@@
 with one that is everywhere constant, in effect modeling
-lipids in a bilayer as an array of as elongated, purely hydrophobic pilars.
+lipids in a bilayer as an array of as elongated, purely hydrophobic
+pillars.
 
@@
 \citet{kohl-cor-che-vee22} also studied self-assembly
-of bipolar electric JP, which bare some resemblence
+of bipolar electric JP, which bare some resemblance
 to polar boundary condition we employ.
@@
 dendrimersomes have been studied
-by molecular dynamics simulations\cite{C9NR05885K}.  
+by molecular dynamics simulations~\cite{C9NR05885K}.  
 The molecular dynamics simulations
@@
 \begin{acknowledgments}
-We thank Dr.
-S\'ebastien Michelin and Dr.
-Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.
+We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.
 
@@
 hydrodynamic interactions and hydrophobic interactions. Assuming
-inertial terms are negligible, the solvent is goverened by the Stokes
+inertial terms are negligible, the solvent is governed by the Stokes
 equations
@@
 The translational and angular velocities guarantee that the fluid forces
-balanace the imposed forces. The imposed forces include the hydrophobic
+balance the imposed forces. The imposed forces include the hydrophobic
 interactions that arise so that particles minimize the free energy of
-the structure of the surronding water molecules. The free energy
+the structure of the surrounding water molecules. The free energy
 functional is
@@
   \vspace{-20pt}  
-  \caption{\label{fig:relax} (a) Initial configuration for $N_b=60$ structures.
-In order to expedite the self-assembly procedure, all particles are placed in a $8\times8$ box initially.
-(b)--(d) Equilibruim states for all boundary conditions~\eqref{eq:bcs}(i)--(iii), respectively.
+  \caption{\label{fig:relax} (a) Initial configuration for $N_b=60$
+  structures. In order to expedite the self-assembly procedure, all
+  particles are placed in a $8\times8$ box initially. (b)--(d)
+  Equilibrium states for all boundary conditions~\eqref{eq:bcs}(i)--(iii), respectively.
 Colors represent the boundary values that increases from minimum (blue) to maximum (red).
@@
 The hydrophilic side takes the value $u =0$.
-This mimicks the apolar head of a lipid, for example, which does
+This mimics the apolar head of a lipid, for example, which does
 not alter the structure of adjacent waters. The hydrophobic side
@@
 Fig~\ref{fig:relax}(c) shows the multilamellar structure with 8 layers when $N_b=60$. 
-The number of folds depends on several factors, for instances, number of particles and intial configurations.
+The number of folds depends on several factors, for instances, number of
+particles and initial configurations.
 
@@
 Comparing with the case when $V_0=0.2$, we provide a frame in Fig~\ref{fig:TG_2}(a) and the energy comparison is shown in panel (b).
-Numerical results validate the phenomenon that a higher taylor green vortex flow generates large structure separations with higher total energy.
+Numerical results validate the phenomenon that a higher Taylor-Green vortex flow generates large structure separations with higher total energy.
 

### 2022-08-01 doc/PRF2022/PRF_main.tex
conclusion 1st draft

@@
 and an anisotropic attractive part describes the hydrophobic interactions.
+
 \section{Conclusion}
-
 \label{sec:conclusion}
+
+In this work, we employ the newly developed JP model using BIEs and tune 
+the boundary conditions with energy normalization to study the dynamics of 
+amphiphilic and dipolar like JPs. The normal derivative \eqref{eq:normal_deriv} 
+overcomes an obstacle for numerical implementations in the free energy $F$ 
+where the gradient of solution to the screened Laplace equation involves 
+hyper-singularities.
+
+Simulations include the self-assembly behaviors when the flow is absent and 
+particle aggregations when suspended in shear and TG background flows with 
+various flow rates. We track the total free energy, the orientational order 
+parameter, and the strain parameter to comprehensively summarize and classify 
+the effective properties of all three materials. Observations have shown that 
+multi-lamella and the striated structures Under a relatively weak linear shear flow 
+behave like a rigid body with minimal deformation. The effective viscosity of the 
+material gives a quantitative validation to support the statement. High shear rate 
+cases provide the range when the critical shear rate for structure to break apart 
+and major topological changes. As expected in all case studies, the free energy 
+spikes at certain levels are indicators.
+
+Under a TG flow, we examine the same measures and simulate all structures with 
+the same criteria as ones in shear flow cases. In addition, for JP vesicle under a 
+TG flow, we compare the results when the size of cell is varied and a nonmonotonic 
+trend in reduced area with respect to the cell size arises.
+
+The results reported here provide a preliminary framework for colloidal sciences. 
+The present study also helps us to understand more rheological properties of industrial 
+produced Janus particles. This study can be extended to three dimensional system 
+and it has been included in our future goals. The boundary condition can be designed 
+as one with random perturbations that are more close to lab experiments.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{DRAFT RESULTS BELOW}

### 2022-08-01 doc/PRF2022/PRF_main.tex
working on results

--- 2022-08-01 doc/PRF2022/PRF_main.tex
@@
 \newcommand{\DD}{\mathcal{D}}
+\newcommand{\DDD}{\boldsymbol{\mathcal{D}}}
 \newcommand{\SSS}{\mathcal{S}}
@@
 \renewcommand{\SS}{\mathbf{S}}
+\newcommand{\ee}{\mathbf{e}}
 \newcommand{\ff}{\mathbf{f}}
@@
 are disks of radius $c$, center $\aa_i$, and orientation $\theta_i$
-relative to the horizontal axis, where $i = 1, \dots, N_b$ and $N_b$ is
+relative to the horizontal axis, where $i = 1, \ldots, N_b$ and $N_b$ is
 the number of particles. The domain $\Omega(t) \subset \mathbb{R}^2$ is
@@
 \end{align}
-for $i = 1,\dots,N_b$ with particle outward normal $\nnu$, where
+for $i = 1,\ldots,N_b$ with particle outward normal $\nnu$, where
 \begin{align}
@@
 solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
-zeroth-order modified Bessel function of the first kind, and $\sigma$ is
-a scalar-valued density function. The subscript in $\dif s_\yy$ denotes
-integration with respect to $\yy \in \Gamma$. To satisfy the boundary
+zeroth-order modified Bessel function of the first kind, $\nnu_\yy$ is
+the unit outward normal at $\yy$, and $\sigma$ is a scalar-valued
+density function. The subscript in $\dif s_\yy$ denotes integration with
+respect to $\yy \in \Gamma$. To satisfy the boundary
 condition~\eqref{eq:SLbc}, the density function must satisfy
@@
   \label{eq:velocity}
-  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
+  \uu(\xx) = \uu_\infty(\xx) + \DDD[\eeta](\xx) + 
     \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
@@
 \begin{align}
-  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
-    \frac{(\xx - \yy) \cdot \nnu}{|\xx - \yy|^2}
+  \DDD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
+    \frac{(\xx - \yy) \cdot \nnu_\yy}{|\xx - \yy|^2}
     \frac{(\xx - \yy) \otimes (\xx - \yy)}{|\xx - \yy|^2}
@@
   \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
-    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) 
+    -\frac{1}{2} \eeta(\xx) + \DDD[\eeta](\xx) 
     + \sum_{j=1}^{N_b} 
@@
 \end{alignat}
-for $\xx \in \Gamma_i$ and $i = 1,\dots,N_b$.
+for $\xx \in \Gamma_i$ and $i = 1,\ldots,N_b$.
 
@@
 number of GMRES iterations is mesh-independent by using second-kind
-BIEs.
-
-\todo[inline]{BRYAN IS HERE}
+BIEs. Once the translational and rotational velocity are computed, the
+position and orientation of each JP is updated using the second-order
+Adams-Bashforth scheme.
+
 %Once the translational and angular velocities $\vv_i, \omega_i$
@@
   Panel (a) shows $N_b = 198$ particles confined to a square with random
-  positions and orientations and the inset shows $N_b=60$ particles configuration.
-  The particles self-assemble into distinct configurations,
-  depending on the boundary condition \eqref{eq:bc-type}.
-  Panel (b) is for $b=1$ and the boundary condition mimics that
-  of an amphiphilic particle giving bilayer structures. 
-  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
-  In panel (d), the case $b = 0$ is for a water structure with
-  positive/negative charge. 
-  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
-  The inset in panel (b)--(d) are configurations using $N_b=60$ and share the same color map
-  as the main panels.}
+  positions and orientations and the inset shows a $N_b=60$ particles
+  configuration. The particles self-assemble into distinct
+  configurations, depending on the boundary
+  condition~\eqref{eq:bc-type}. Panel (b) is for $b=1$ and the boundary
+  condition mimics that of an amphiphilic particle giving bilayer
+  structures. Panel (c) is for $b=2$ which gives rise to a
+  multilamellar configuration. In panel (d), the case $b = 0$ is for a
+  water structure with positive/negative charge. The false color maps
+  use blue for $u < 0$, green for $u = 0$, and yellow then red for $u >
+  0$. The inset in panels (b)--(d) are configurations using $N_b=60$ and
+  share the same color map as the main panels.}
 \end{caption}
@@
 \subsection{Boundary conditions and normalization}
-The present paper considers boundary conditions of the form
-\begin{equation}
+We consider boundary conditions of the form
+\begin{align}
   \label{eq:bc-type}
 g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
-\end{equation}
+\end{align}
 where $\alpha$ is the angle between the vector $\xx - \aa_i$ and 
@@
 
-We set $\max g>0$ to guarantee at least partial hydrophobicity of the JP surface.
-Then, the boundary condition (BC) can be classified into
-three categories: $\min g >0$, $\min g =0$, and $\min g <0$.  
-These three categories correspond to three characteristic
-values of $b$ in \eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
-%
-To see the effect of the shift parameter $b$, we simulate the dynamics of
-198 particles and 60 particles in a quiescent flow as shown in Fig~\ref{fig:relax}.
-Three distinct configurations emerge:
-(i) bilayer for $b = 1$, 
-(ii) multilamellar for $b = 2$, and 
-(iii) striated for $b = 0$.
-
-Fig~\ref{fig:relax}(a) shows the initial configurations with
-orientations of the 198-particle and 60-particle cases,
-respectively. 
-BC (i) with $b = 1$ mimics an amphiphilic particle.
-The boundary data $g$ is everywhere nonnegative,
-and takes
-the maximum value $a$ on the hydrophobic tail (red)
-the value $0$ on the hydrophilic head (green). 
+We set $\max g>0$ to guarantee at least partial hydrophobicity of the JP
+surface.  Then, the boundary condition (BC) can be classified into three
+categories: $\min g >0$, $\min g =0$, and $\min g <0$.  These three
+categories correspond to three characteristic values of $b$ in
+\eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
+%
+To see the effect of the shift parameter $b$, we simulate the dynamics
+of 198 particles and 60 particles in a quiescent flow as shown in
+Figure~\ref{fig:relax}. Three distinct configurations emerge: (i)
+bilayer for $b = 1$, (ii) multilamellar for $b = 2$, and (iii) striated
+for $b = 0$.
+
+Figure~\ref{fig:relax}(a) shows the initial configurations with
+orientations of the 198-particle and 60-particle cases, respectively.
+BC (i) with $b = 1$ mimics an amphiphilic particle. The boundary data
+$g$ is everywhere nonnegative, and takes the maximum value $a$ on the
+hydrophobic tail (red) the value $0$ on the hydrophilic head (green).
 The interaction is attractive, and particles collectively orient their
-hydrophobic sides to form bilayers  (Fig~\ref{fig:relax}(b)). The inset shows the equilibrium 
-state for the 60-particle run.
-Both cases form bilayers with multiple components.
-
-In BC (ii) with $b = 1$, the boundary data is everywhere positive.
-It takes the maximum value $3a$ on the tail (red) and the
-minimum value $a$ on the head side (yellow). 
-Both sides of the Janus particle are hydrophobic but
-more so on the $\alpha = 0$ side.  
-Over a short time scale, these particles also self-assemble into bilayers. But unlike for  (i),
-the heads are also hydrophobic and so in the long-time dynamics
-these bilayers form multilamella structures\cite{C9NR05885K}.
-The number of folds depends primarily on the number of particles.
-Fig~\ref{fig:relax}(c), for example, shows a
-multilamellar structure with four layers and one with two layers in the inset.
-
-Finally, BC (iii) with $b=1$ 
-corresponds to a water structure with
-positive/negative charge \cite{MaRa76, Ma77}.
-Here, the head repels the tail of other particles
-and the particles initially form chains with their directors perpendicular
-to the length of the chain.  
-The chains form stria
-where the particles lie on a 
-square grid and the orientations alternate
-between layers (Fig~\ref{fig:relax}(d)).
+hydrophobic sides to form bilayers (Figure~\ref{fig:relax}(b)). The
+inset shows the equilibrium state for the 60-particle run. Both cases
+form bilayers with multiple components.
+
+In BC (ii) with $b = 1$, the boundary data is everywhere positive. It
+takes the maximum value $3a$ on the tail (red) and the minimum value $a$
+on the head side (yellow). Both sides of the Janus particle are
+hydrophobic but more so on the $\alpha = 0$ side. Over a short time
+scale, these particles also self-assemble into bilayers. But unlike for
+BC (i), the heads are also hydrophobic and so in the long-time dynamics
+these bilayers form multilamella structures~\cite{C9NR05885K}. The
+number of folds depends primarily on the number of particles.
+Figure~\ref{fig:relax}(c), for example, shows a multilamellar structure
+with four layers and one with two layers in the inset.
+
+Finally, BC (iii) with $b=1$ corresponds to a water structure with
+positive/negative charge~\cite{MaRa76, Ma77}. Here, the head repels the
+tail of other particles and the particles initially form chains with
+their directors perpendicular to the length of the chain. The chains
+form stria where the particles lie on a square grid and the orientations
+alternate between layers (Figure~\ref{fig:relax}(d)).
 
@@
   \vspace{-20pt}
+  \todo[inline]{We should capitalize bc is that it reads BC like we have
+  in the text.}
   \caption{\label{fig:relax_energy}
-  Panel (a) shows that the free energy \eqref{eq:free_energy} decreases
-    in the mobility problem formulation.  The initial energies
-    are for the configuration in Fig \ref{fig:relax}(a)
-    and the final energies are for the near-equilibrium
-    configurations as shown in Fig \ref{fig:relax}(b)--(d), respectively.
-    The solid curves are the energies for the $N_b=60$ cases and  
-    the dashed curves are the energies for the $N_b = 198$ cases normalized
-    by $60/198$, showing that the energy approximately scales with the number of
-    particles. 
-    Panel (b) shows the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs. 
-    The curve styles are identical to the ones in panel (a).
-    The near-equilibrium configurations depend on the initial configurations and the results show that for both $N_b=60$ and $N_b=198$ cases, bilayer and multi-lamellar configurations have similar trends in orientational parameters.
-    The results of the striated configuration, however, depend on the initial geometrical setup.
-  }
+  Panel (a) shows that the free energy~\eqref{eq:free_energy} decreases
+  in the mobility problem formulation. The initial energies are for the
+  configuration in Figure~\ref{fig:relax}(a) and the final energies are
+  for the near-equilibrium configurations shown in
+  Figures~\ref{fig:relax}(b)--(d). The solid curves are the energies for
+  the $N_b=60$ cases and the dashed curves are the energies for the $N_b
+  = 198$ cases normalized by $60/198$, showing that the energy
+  approximately scales with the number of particles.  Panel (b) shows
+  the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs.
+  The curve styles are identical those in panel (a). The
+  near-equilibrium configurations depend on the initial configurations
+  and the results show that for both $N_b=60$ and $N_b=198$ cases,
+  bilayer and multi-lamellar configurations have similar trends in
+  orientational parameters. The results of the striated configuration,
+  however, depend on the initial geometrical setup.}
 \end{figure}
@@
 \section{Measuring deformation}
-We use the free energy $F$,
-a strain parameter $E$, 
-and two scalar order parameters $S_{2}$ and $\tilde S_2$ to measure
-the deformation of particle configurations under background flows.
-
-First, we must simplify the
-form of the free energy \eqref{eq:free_energy}
-using integration by parts and \eqref{eq:SL}
-to obtain
+We use the free energy $F$, a strain parameter $E$, and two scalar order
+parameters $S_{2}$ and $\tilde S_2$ to measure the deformation of
+particle configurations under background flows.
+
+First we simplify the form of the free energy~\eqref{eq:free_energy}.
+Using integration by parts and~\eqref{eq:SL}, we obtain
 \begin{equation}
@@
 %
-Here, we have substituted $g$ for $u$ since the boundary values are given.
-However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
-involves calculating a quadruple layer potential which has a
-well-known obstacle in numerical implementation.
-To overcome this obstacle, we use
+Here, we have substituted $g$ for $u$ since the boundary values are
+given. However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based
+on~\eqref{eq:SL_BIE} involves calculating a quadruple layer potential
+which has a well-known obstacle in numerical implementation.  To
+overcome this obstacle, we use
 %
@@
 %
-Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
-See Appendix in \S\ref{sec:appendix} for the proof and details.
-Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
-leads to single layer integral which is more straightforward to evaluate and we compute the
-arclength derivative using spectrally accurate Fourier transform.
-We have validated the form of \eqref{eq:normal_deriv} by extrapolating 
-the primal energy \eqref{eq:free_energy} along test curves placed slightly
-outside the particles.
-
-Fig~\ref{fig:relax_energy}(a) tracks the free energy profiles for all relaxation runs.
-For the 198-particle cases, we normalized the energies by 60/198 and the results
-show that all energies decrease with good agreements in all boundary conditions (dashed curves).
-This can be considered as evidence that the free energy per particle with specified
+Here, $\tt(\xx)$ is the tangent vector and $\dif/\dif s$ is the
+arclength derivative. See the Appendix in \S\ref{sec:appendix} for the
+proof and details. Substituting~\eqref{eq:normal_deriv}
+into~\eqref{eq:free_energy2} for the normal derivative leads to the
+single layer, $\SS$, which is more straightforward to evaluate and we
+compute the arclength derivative using spectrally accurate Fourier
+transform. We have validated the form of~\eqref{eq:normal_deriv} by
+extrapolating the primal energy~\eqref{eq:free_energy} along test curves
+placed slightly outside the particles.
+
+Figure~\ref{fig:relax_energy}(a) tracks the free energy profiles for all
+relaxation runs.  For the 198-particle cases, we normalized the energies
+by 60/198 and the results show that all energies decrease with good
+agreements in all boundary conditions (dashed curves).  This can be
+considered as evidence that the free energy per particle with specified
 boundary conditions is independent of the total particle number $(N_b)$.
 
-To measure positional order, we use a number,
-which we call the strain parameter, 
+To measure positional order, we use a number, which we call the strain
+parameter, 
 \begin{equation}
@@
 E = \frac{1}{N_b} \sum_{i=1}^{N_b}
-\|\tfrac{1}{2}(\mathsf{F}_i^T \mathsf{F}_i - I)\|
+\left\|\frac{1}{2}(\mathsf{F}_i^T \mathsf{F}_i - I)\right\|,
 \end{equation}
-where $\mathsf{F}_i$ is an 
-approximate deformation gradient at particle $i$.
-The argument inside the Frobenius norm $\| \cdot \|$
-is the Green-Lagrange strain tensor.
-The motivation for  \eqref{eq:SP} is as follows.
-For relatively weak background flow strengths, the near-equilibrium particle
-configurations behave as an elastic solid.  There is a map $\ff(\xx,t)$
-from the reference (equilibrium) configuration with $\ff(\aa_i(0),t) = \aa_i(t)$
-for $i = 1,\dots,N_b$.  Using linear approximation,
-\[
+where $\mathsf{F}_i$ is an approximate deformation gradient at particle
+$i$. The argument inside the Frobenius norm $\| \cdot \|$ is the
+Green-Lagrange strain tensor. The motivation for~\eqref{eq:SP} is as
+follows. For relatively weak background flow strengths, the
+near-equilibrium particle configurations behave as an elastic solid.
+There is a map $\ff(\xx,t)$ from the reference (equilibrium)
+configuration with $\ff(\aa_i(0),t) = \aa_i(t)$ for $i = 1,\ldots,N_b$.
+Using linear approximation,
+\begin{align}
 \aa_j(t) - \aa_i(t) = \ff(\aa_j(0),t) - \ff(\aa_i(0),t)
 \approx \nabla \ff(\aa_i(0),t)(\aa_j(0) - \aa_i(0)).
-\]
-To approximate
-the deformation gradient $\nabla \ff(\aa_i(0),t)$
-we solved the overdetermined system 
-\[
-\aa_j(t) - \aa_i(t) = \mathsf{F}_i(\aa_j(0) - \aa_i(0)),\quad j = 1,\dots, N_b  
-\]
-for $\mathsf{F}_i$ by weighted least squares. The weights  
-$w_i = \exp(-\|\aa_j(0) - \aa_i(0)\|/4c)$ with particle radius $c$
-ensure that the linear approximation is valid for
-particles near $\aa_i$.
+\end{align}
+To approximate the deformation gradient $\nabla \ff(\aa_i(0),t)$ we
+solve the overdetermined system 
+\begin{align}
+\aa_j(t) - \aa_i(t) = \mathsf{F}_i(\aa_j(0) - \aa_i(0)),\quad j =
+  1,\ldots, N_b,
+\end{align}
+for $\mathsf{F}_i$ by weighted least squares. The weights $w_i =
+\exp(-\|\aa_j(0) - \aa_i(0)\|/4c)$ with particle radius $c$ ensure that
+the linear approximation is valid for particles near $\aa_i$.
 
@@
 \end{equation}
-Here $\bar \theta$ is a circular mean defined as the
-orientation of the largest eigenvalue eigenvector of 
-$\dd_1\dd_1^\top + \dots + \dd_{N_b}\dd_{N_b}^\top$.
-A value $S_2(t) = 1$ indicates 
-that all particle directors lie on a common axis e.g.,
-two parallel vectors with possibly opposite direction are ordered. 
-A value far from 1 indicates disorder.
-
-We must modify $S_2$ to account for the bilayer and
-multilamellar structures.  In these cases, the directors 
-are more or less uniformly distributed along a circle, even though
-there is orientational order between neighboring particles.
-To account for local order, we instead use
+Here $\bar \theta$ is a circular mean defined as the orientation of the
+largest eigenvalue of $\dd_1\dd_1^\top + \cdots +
+\dd_{N_b}\dd_{N_b}^\top$. A value $S_2(t) = 1$ indicates that all
+particle directors lie on a common axis e.g., two parallel vectors with
+possibly opposite direction are ordered. A value far from 1 indicates
+disorder.
+
+We modify $S_2$ to account for the bilayer and multilamellar structures.
+In these cases, the directors are more or less uniformly distributed
+along a circle, even though there is orientational order between
+neighboring particles. To account for local order, we instead use
 \begin{equation}
@@
 where $\bar \theta_i$ is the circular mean restricted to particles
-indexed by $j$ for which $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle is
-isolated and has no neighbors within a distance $4c$, then we exclude it from
-the sum \eqref{eq:localS2}.
-
-Fig~\ref{fig:relax_energy}(b) 
-tracks the orientational order parameter $\tilde{S}_2$.
-Both bilayer and multilamellar
-structures show similar trends in the small and large particle number systems
-(Fig \ref{fig:relax_energy}(b) black curves, red curves respectively).
-The multilamellar structures are highly ordered in all cases (Fig~\ref{fig:relax}(c))
-whereas the bilayer structures
-are disordered because they consist of several 
-components forming isolated bilayers, micelles, and vesicles (Fig~\ref{fig:relax}(b)).
-
-The aggregation for striated configurations forms more than one 
-pattern when the number of particles is varied (Fig~\ref{fig:relax}(d)).
-We observe that when the number of particles is fewer, there is only
-a single pattern in particle orientations where the directors
-are more or less parallel and alternate directions (Fig~\ref{fig:relax}(d), inset).
-Larger number of particles results in two different patterns: the alternating sign pattern
-as in the small particle number case (Fig~\ref{fig:relax}(d), 
-top right rectangle) and one where the directors reflect across the lines parallel
-to the stria and across the lines perpendicular to the stria (Fig~\ref{fig:relax}(d),
-top middle rectangle).
-As a result, there are different trends in orientational order
-(Fig~\ref{fig:relax_energy}(b), solid and dashed blue curves, respectively).
-
-In the Results section,
-the equilibrium configurations for BCs (i), (ii), and (iii)
-(Fig~\ref{fig:relax}, insets) are
-used as initial data in the
-background flow simulations. 
-For the bilayer case BC (i), we include an alternate initial condition 
-consisting of a single, circular vesicle (c.f., Fig~\ref{fig:Ves_shear}).
+indexed by $j$ with $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle
+is isolated and has no neighbors within a distance $4c$, then we exclude
+it from the sum~\eqref{eq:localS2}.
+
+Figure~\ref{fig:relax_energy}(b) tracks the orientational order
+parameter $\tilde{S}_2$. Both bilayer and multilamellar structures show
+similar trends in the small and large particle number systems
+(Figure~\ref{fig:relax_energy}(b) black curves and red curves,
+respectively). The multilamellar structures are highly ordered in all
+cases (Figure~\ref{fig:relax}(c)) whereas the bilayer structures are
+disordered because they consist of several components forming isolated
+bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
+
+The aggregation for striated configurations forms more than one pattern
+when the number of particles is varied (Figure~\ref{fig:relax}(d)). We
+observe that when the number of particles is fewer, there is only a
+single pattern in particle orientations where the directors are more or
+less parallel and alternate directions (Figure~\ref{fig:relax}(d),
+inset). Larger number of particles results in two different patterns:
+the alternating sign pattern as in the small particle number case
+(Figure~\ref{fig:relax}(d), top right rectangle) and one where the
+directors reflect across the lines parallel to the stria and across the
+lines perpendicular to the stria (Figure~\ref{fig:relax}(d), top middle
+rectangle). As a result, there are different trends in orientational
+order (Figure~\ref{fig:relax_energy}(b), solid and dashed blue curves,
+respectively).
+
+In the Results section, the equilibrium configurations for BCs (i),
+(ii), and (iii) (Figure~\ref{fig:relax}, insets) are used as initial
+data in the background flow simulations. For the bilayer case BC (i),
+we include an alternate initial condition consisting of a single,
+circular vesicle (c.f., Figure~\ref{fig:Ves_shear}).
 
@@
 \label{sec:results}
-In this section, we subject the Janus particle structures to various background
-flows.  The purpose is to understand how self-assembled particles
-respond to external forcing.
-We can then compare effective properties of
-materials comprised of Janus particles as a function
-of their amphiphilic properties.  
+In this section, we subject the Janus particle structures to various
+background flows. The purpose is to understand how self-assembled
+particles respond to external forcing. We then compare effective
+properties of materials comprised of Janus particles as a function of
+their amphiphilic properties.
 %%%
@@
 \subsection{Bilayer configurations (BC (i)) in a linear shear flow}
-To begin, we place the bilayer structure (with BC (i)) from the inset of Fig~\ref{fig:relax}(b)
-in a linear shear flow
+To begin, we place the bilayer structure (with BC (i)) from the inset of
+Figure~\ref{fig:relax}(b) in a linear shear flow
 \begin{equation}
@@
 %
-where $\dot\gamma$ is the dimensionless shear rate and ${\bf e}_x$ and ${\bf e}_y$
-are horizontal and vertical unit vectors, respectively.
-The initial bilayer structure consists of a small self-enclosing bilayer (vesicle) and several pieces of bilayers.
-Fig~\ref{fig:BC1_shear}(a)--(c)
-shows a snapshot
-at $t = 0.5$ $\upmu$s
-of the bilayer for different shear rates $\dot\gamma= 0.05,0.075,0.01$.
-The dynamics of the bilayer can be found in the supplementary movies,
-which show that the initial pieces of bilayers merge and form a worm-like shape
-under a linear shear flow.
-At a low shear rate, the bilayer constantly goes through rotation and
-extensional deformation with the whole bilayer remaining intact (figure~\ref{fig:BC1_shear}(a)).
-As the shear rate increases to a moderate value (figure~\ref{fig:BC1_shear}(b)),
-the bilayer is observed to shed a small piece of bilayer, 
-similar to the asymmetric breakup of a viscous drop \cite{}.
-In figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two separate, nearly equal bilayers, 
-similar to the symmetric drop breakup under a linear shear flow \cite{}.
+where $\dot\gamma$ is the dimensionless shear rate, and ${\ee}_x$ and
+${\ee}_y$ are horizontal and vertical unit vectors, respectively. The
+initial bilayer structure consists of a small self-enclosing bilayer
+(vesicle) and several pieces of bilayers.
+Figure~\ref{fig:BC1_shear}(a)--(c) shows a snapshot at $t = 0.5$
+$\upmu$s of the bilayer for different shear rates $\dot\gamma=
+0.05,0.075,0.01$. The dynamics of the bilayer can be found in the
+supplementary movies, which show that the initial pieces of bilayers
+merge and form a worm-like shape under a linear shear flow. At a low
+shear rate, the bilayer constantly goes through rotation and extensional
+deformation with the whole bilayer remaining intact
+(Figure~\ref{fig:BC1_shear}(a)). As the shear rate increases to a
+moderate value (Figure~\ref{fig:BC1_shear}(b)), the bilayer is observed
+to shed a small piece of bilayer, similar to the asymmetric breakup of a
+viscous drop \cite{} \todo[inline]{missing citation}. In
+Figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two
+separate, nearly equal bilayers, similar to the symmetric drop breakup
+under a linear shear flow \cite{} \todo[inline]{missing citation}.
 %%
@@
 
-We observe that the order parameter $\tilde S_2$ in figure~\ref{fig:BC1_shear}(e)
-is on average increasing.  In the initial configuration,
-the structure has three or four components.  
-%
-Under the shear flow, the shedding and merging of bilayers
-results in an overall decrease in distinct bilayer structures.  
-Similarly, the free energies 
-are slightly decreasing (Fig~\ref{fig:BC1_shear}(d)),
-with the overall changes occurring in the range of a few $\mathrm{k_BT}$/nm.  
-This suggests that
-the shear flow changes the energy landscape to move the local equilibrium obtained from a random initial condition
-to an alternate local equilibrium with lesser free energy and greater orientational order.   
-Note that the free energy $F$ in figure~\ref{fig:BC1_shear}(d) has the unit of force because our system is two dimensional.
+We observe that the order parameter $\tilde S_2$ in
+Figure~\ref{fig:BC1_shear}(e) is on average increasing. In the initial
+configuration, the structure has three or four components.
+%
+Under the shear flow, the shedding and merging of bilayers results in an
+overall decrease in distinct bilayer structures. Similarly, the free
+energies are slightly decreasing (Figure~\ref{fig:BC1_shear}(d)), with
+the overall changes occurring in the range of a few $\mathrm{k_BT}$/nm.
+This suggests that the shear flow changes the energy landscape to move
+the local equilibrium obtained from a random initial condition to an
+alternate local equilibrium with less free energy and greater
+orientational order.  Note that the free energy $F$ in
+Figure~\ref{fig:BC1_shear}(d) has the unit of force because our system
+is two dimensional.
 %
@@
 %
-Finally, the strain parameter diverges in the large shear rate cases (Fig~\ref{fig:BC1_shear}(f))
+Finally, the strain parameter diverges in the large shear rate cases
+(Figure~\ref{fig:BC1_shear}(f))
 because the components eventually completely separate and move away from one another
@@
     \label{fig:Ves_shear}
-The figure shows a single vesicle in a shear flow.
-Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
-The streamlines are plotted in the background.
-Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
+A single vesicle in a shear flow. Panels (a)--(c) are snapshots for
+  $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the
+  pre-relaxed initial configuration is shown in inset of panel (a).  The
+  streamlines are plotted in the background.  Panel (d) plots the free
+  energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel
+  (f) shows positional parameter E.
      }
 \end{figure}
-%
-\citet{Fu2022_JFM} studied the hydrodynamics of a JP vesicle under a linear shear flow. 
-Focusing on drawing analogies to hydrodynamics of a vesicle in continuum modeling
-(such as tank-treading \cite{keller_skalak_1982,Finken08,Shaqfeh11}, bilayer slip \cite{sch-vla-mik2010,denOtter2007,Zgorski2019}, and permeability \cite{chabanon2017,qua-gan-you2021}),
-our previous studies showed the existence of a critical shear
-rate above which the JP vesicle ruptures
-\cite{grandmaison_brancherie_salsac_2021,D2SM00179A}. 
-Based on the these early results, we
-reinitialized the BC (i) configuration
-in the form of a single, circular vesicle (rather than several bilayer components)
-and illustrate how the three measures of structural deformation 
-correlate to the dynamics of a JP vesicle.
-
-At shear rates $\dot\gamma=0.05, 0.066, 0.075$,
-the vesicle undergoes the familiar hydrodynamics
-(such as elongation along the extensional axis and tank-treading motion),
-as shown in Fig~\ref{fig:Ves_shear} (a)--(c).
+\citet{Fu2022_JFM} studied the hydrodynamics of a JP vesicle under a
+linear shear flow. Focusing on drawing analogies to hydrodynamics of a
+vesicle in continuum modeling (such as
+tank-treading~\cite{keller_skalak_1982,Finken08,Shaqfeh11}, bilayer
+slip~\cite{sch-vla-mik2010,denOtter2007,Zgorski2019}, and
+permeability~\cite{chabanon2017, qua-gan-you2021}), our previous studies
+showed the existence of a critical shear rate above which the JP vesicle
+ruptures~\cite{grandmaison_brancherie_salsac_2021,D2SM00179A}. Based on
+the these early results, we reinitialized the BC (i) configuration in
+the form of a single, circular vesicle (rather than several bilayer
+components) and illustrate how the three measures of structural
+deformation correlate to the dynamics of a JP vesicle.
+
+At shear rates $\dot\gamma=0.05, 0.066, 0.075$, the vesicle undergoes
+familiar hydrodynamics, such as elongation along the extensional axis
+and tank-treading motion, as shown in
+Figure~\ref{fig:Ves_shear}(a)--(c).
 %
 The circular shape is also a local equilibrium, with somewhat less
-energy than the disordered state c.f.,
-Fig~\ref{fig:BC1_shear}(d) and Fig~\ref{fig:Ves_shear} (d).
-But unlike the dynamics of bilayers in Fig~\ref{fig:BC1_shear}, 
-the energies of the JP vesicle in Fig~\ref{fig:Ves_shear}(d)
-jump from the baseline value 30 $\mathrm{k_BT}$/nm to about 32 $\mathrm{k_BT}$/nm,
-signaling the rupture of the vesicle into disconnected bilayers
-(see Fig~\ref{fig:Ves_shear}(d), long and short dashed curves).
-After the rupture, each piece circles around the vorticity at the center without reconnection while the energies fluctuate slightly around a constant.
-
-For the lowest shear rate case, the vesicle has nearly constant orientational order $\tilde S_2 = 1$
-(see Fig~\ref{fig:Ves_shear}(e), solid curve).
-After the JP vesicle
-ruptures with $\dot\gamma= 0.066$ and $\dot \gamma= 0.075$,
-we observe a greater variation in the order parameter $\tilde{S}_2$
-with a baseline value around $0.7$
-(see Fig~\ref{fig:Ves_shear}(e), dashed curves).
-The oscillations occur due to the orbit of the two bilayer components,
-and $\tilde{S}_2$ increases to about $0.9$ when the components slide past one another and are nearly parallel.
-%
-As in the previous case, peaks in the strain parameter $E$
-correlate well with changes in structural topology in the bilayer dynamics, see
-the dashed curves in Fig~\ref{fig:Ves_shear}(f).
+energy than the disordered state c.f., Figure~\ref{fig:BC1_shear}(d) and
+Figure~\ref{fig:Ves_shear}(d). But unlike the dynamics of bilayers in
+Figure~\ref{fig:BC1_shear}, the energies of the JP vesicle in
+Figure~\ref{fig:Ves_shear}(d) jump from the baseline value 30
+$\mathrm{k_BT}$/nm to about 32 $\mathrm{k_BT}$/nm, signaling the rupture
+of the vesicle into disconnected bilayers (see
+Figure~\ref{fig:Ves_shear}(d), long and short dashed curves).  After the
+rupture, each piece circles around the vorticity at the center without
+reconnection while the energies fluctuate slightly around a constant.
+
+For the lowest shear rate case, the vesicle has nearly constant
+orientational order $\tilde S_2 = 1$ (see Figure~\ref{fig:Ves_shear}(e),
+solid curve). After the JP vesicle ruptures with $\dot\gamma= 0.066$ and
+$\dot \gamma= 0.075$, we observe a greater variation in the order
+parameter $\tilde{S}_2$ with a baseline value around $0.7$ (see
+Figure~\ref{fig:Ves_shear}(e), dashed curves). The oscillations occur
+due to the orbit of the two bilayer components, and $\tilde{S}_2$
+increases to about $0.9$ when the components slide past one another and
+are nearly parallel.
+%
+As in the previous case, peaks in the strain parameter $E$ correlate
+well with changes in structural topology in the bilayer dynamics (dashed
+curves in Figure~\ref{fig:Ves_shear}(f)).
 
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
- The streamlines are plotted in the background. 
-Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
-  }
+  \caption{\label{fig:BC1_TG} Multiple component bilayers in a
+  Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The
+  pre-relaxed initial configuration is shown in the inset of panel (a).
+  The streamlines are plotted in the background. Panel (d) plots the
+  free energies; panel (e) shows the orientational parameter
+  $\tilde{S}_2$; panel (f) shows the positional parameter $E$.}
 \end{figure}
@@
 \subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
-Next, we subject the bilayer/vesicle configurations to a 
-Taylor-Green (TG) background flow
+Next, we subject the JP structures to the Taylor-Green (TG) background
+flow
 \begin{equation}
@@
          \cos\left(y/\lambda\right)
-             {\bf e}_y\right)
+             {\bf e}_y\right),
 \end{equation}
@@
 The TG flow is a confining flow consisting of a checkerboard pattern
-of cells with alternating circulation.  We control the flow by 
-the dimensionless flow strength $V_0$ and the dimensionless cell size $l$
-defining $\lambda = l$ nm.
-For most of the results here the parameter $l=2$ is used in this subsection.
+of cells with alternating circulation. We control the flow by the
+dimensionless flow strength $V_0$ and the dimensionless cell size $l$
+defining $\lambda = l$ nm. For most of the results in this subsection,
+we use the parameter $l=2$.
 %
@@
 There is no appreciable pattern in the deformation for the multicomponent bilayer case in TG flow. 
-Fig~\ref{fig:BC1_TG}(a)--(c) are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s.
+Figure~\ref{fig:BC1_TG}(a)--(c) are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s.
 At all flow strengths, the bilayer components are separated and mixed by the flow in neighboring cells. 
 In the $V_0 = 0.2$ case, the flow breaks off components consisting of only a few particles,
-leading an increase in energy (Fig~\ref{fig:BC1_TG}(d), long dashed curve).
+leading an increase in energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve).
 There is no significant change in the orientational order.  There is an initial increase in the
@@
 Patterns in the deformation, however, do emerge in the case of a vesicle in TG flow.
-For a vesicle in a Taylor-Green flow, Fig~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\  \mu$s where $V_0=0.1,0.15,0.2$.
+For a vesicle in a Taylor-Green flow, Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\  \mu$s where $V_0=0.1,0.15,0.2$.
 Here, the circular vesicle takes on a steady square shape for moderate flow rates $V_0 = 0.1$ and $V_0 = 0.15$.
-In these cases, there is little change in the vesicle free energy and order (Fig~\ref{fig:ves_TG}(d)-(f))).
+In these cases, there is little change in the vesicle free energy and
+order (Figure~\ref{fig:ves_TG}(d)-(f))).
 The vesicle disintegrates for $V_0 = 0.2$, leading to a jump in energy, drop in order, and increase in strain,
@@
 The vesicle shape is also tied to cell size $l$.  
-Fig~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a
+Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a
 TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s.  
 For the smallest cell size $l = 1$ tested, the vesicle is somewhat octagonal
-and passes through multiple cells (Fig~\ref{fig:BTG_Scale}(a)).
+and passes through multiple cells (Figure~\ref{fig:BTG_Scale}(a)).
 For the largest cell size $l = 4$,
@@
 The direction of the tank-treading, however, varies with the cell
-size (Fig~\ref{fig:BTG_Scale}(a)--(d), directed arcs).  We attribute
+size (Figure~\ref{fig:BTG_Scale}(a)--(d), directed arcs).  We attribute
 this change in rotational orientation to the total rotational moment
@@
 by averaging the area/length for the inner and outer leaflets.  
-As shown in Fig~\ref{fig:BTG_Scale}(e),
+As shown in Figure~\ref{fig:BTG_Scale}(e),
 the relative area $A/A_0$ decreases during the simulations, with a rate
 depending nonmonotonically on $l$.  
-The relative length $L/L_0$, however, is constant in $t$ for all cell sizes (Fig~\ref{fig:BTG_Scale}(e), inset).
+The relative length $L/L_0$, however, is constant in $t$ for all cell
+sizes (Figure~\ref{fig:BTG_Scale}(e), inset).
 This implies that the vesicle behaves as an inextensible, permeable membrane.
@@
 qualitatively similar and will be presented in tandem. 
-For the multilamellar case, we place a 60-particle configuration (inset of Fig~\ref{fig:BC2_shear}(a))
+For the multilamellar case, we place a 60-particle configuration (inset
+of Figure~\ref{fig:BC2_shear}(a))
 in shear flows with $\dot\gamma=0.05, 0.1, 0.15$ and in TG flow with flow rates $V_0=0.1, 0.15, 0.2$.
-For the striated case, we also place a 60-particle configuration (inset of Fig~\ref{fig:BC3_shear}(a))
+For the striated case, we also place a 60-particle configuration (inset
+of Figure~\ref{fig:BC3_shear}(a))
 in shear and TG background flows.  Here, somewhat larger rates are required to see appreciable
@@
 In terms of shear flow, the free energies are steady at the lowest shear 
-rates (Fig~\ref{fig:BC2_shear}(d), Fig~\ref{fig:BC3_shear}(d)).
+rates (Figure~\ref{fig:BC2_shear}(d), Figure~\ref{fig:BC3_shear}(d)).
 The free energy of the striated configuration oscillates by $\pm 1$ $\mathrm{k_BT}$/nm
 due to square reference region deforming into a rhomboidal shape under shear
-flow (Fig~\ref{fig:BC3_shear}(d), solid curve).  No such oscillation
+flow (Figure~\ref{fig:BC3_shear}(d), solid curve).  No such oscillation
 is present in for the multilamellar configuration since this shape is circularly
-isotropic (Fig~\ref{fig:BC2_shear}(d), solid curve).
+isotropic (Figure~\ref{fig:BC2_shear}(d), solid curve).
 At the lowest shear rates, there is, however, oscillation in the strains
@@
 while the order parameter $\tilde S_2$ is more less constant
-(Fig~\ref{fig:BC2_shear}(e),(f), Fig~\ref{fig:BC3_shear}(e),(f), solid curves).
+(Figure~\ref{fig:BC2_shear}(e),(f), Figure~\ref{fig:BC3_shear}(e),(f), solid curves).
 In summary, both multilallar and striated configurations behave as nearly
@@
 the lamella break apart so that individual bilayers are no longer discernible
-(Fig~\ref{fig:BC2_shear}(c)).
+(Figure~\ref{fig:BC2_shear}(c)).
 For BC (iii), the stria peal away from the main body,
-but remain individually intact (Fig~\ref{fig:BC3_shear}(c)).  
+but remain individually intact (Figure~\ref{fig:BC3_shear}(c)).  
 Overall, the particles in BC (ii) and BC (iii) remain bounded
 and do not drift away in the shear background flow like for the
-BC (i) boundary condition (Fig~\ref{fig:BC1_shear}(c),
-Fig~\ref{fig:Ves_shear}(c)).
+BC (i) boundary condition (Figure~\ref{fig:BC1_shear}(c),
+Figure~\ref{fig:Ves_shear}(c)).
 
@@
 is also basically constant for the lowest flow rates $V_0$
-(Fig~\ref{fig:BC2_TG}(d), Fig~\ref{fig:BC3_TG}(d), solid curves).
+(Figure~\ref{fig:BC2_TG}(d), Figure~\ref{fig:BC3_TG}(d), solid curves).
 The striated configuration is unperturbed by the flow, and is engulfed by a single,
 larger, rotating flow cell
-(Fig~\ref{fig:BC3_TG}(a)). 
+(Figure~\ref{fig:BC3_TG}(a)). 
 The multilamellar configuration is perturbed by the flow,
 as seen in the increase in
-the strain parameter $E$ (Fig~\ref{fig:BC3_TG}(f), solid curve).
+the strain parameter $E$ (Figure~\ref{fig:BC3_TG}(f), solid curve).
 The difference in response to the background flow
@@
 equilibrium.  The lamella bilayers from BC (ii) break apart, forming several,
-unlayered bilayer components (Fig~\ref{fig:BC2_TG}(c)).
+unlayered bilayer components (Figure~\ref{fig:BC2_TG}(c)).
 In BC (iii), the stria also break apart, but neighboring particles form
-'X'-like arrangements (Fig~\ref{fig:BC3_TG}(d)), resembling the doubly alternating
-director equilibrium (Fig~\ref{fig:relax}(d), center, top white rectangle).
+'X'-like arrangements (Figure~\ref{fig:BC3_TG}(d)), resembling the doubly alternating
+director equilibrium (Figure~\ref{fig:relax}(d), center, top white rectangle).
 
@@
 per particle in our simulations are different and depend on the boundary condition
-(Fig.~\ref{fig:relax_energy}).
+(Figure~\ref{fig:relax_energy}).
 They are about 0.26 $\mathrm{k_BT}$/nm for BC (ii),
@@
 $0.15$ and TG flow rate $V_0$ up to $0.25$
-(Fig.~\ref{fig:BC3_shear} and Fig.~\ref{fig:BC3_TG}).
+(Figure~\ref{fig:BC3_shear} and Figure~\ref{fig:BC3_TG}).
 Conversely, a $25 - 50 \%$
@@
 Qualitatively, the strains for BC (ii) increases gradually 
-with shear rate (Fig~\ref{fig:BC2_shear}(f)).
+with shear rate (Figure~\ref{fig:BC2_shear}(f)).
 In contrast, the strains for BC (iii) are constant over a range of flow strengths
 and then increase when the flow strengths are large enough
-to deform the body (Fig~\ref{fig:BC3_shear}(f)).
+to deform the body (Figure~\ref{fig:BC3_shear}(f)).
 To quantify this behavior, we form 
@@
 The strain rate $\dot E$ of the body is the slope of a linear fit to the strain curves e.g.,
-in Fig~\ref{fig:BC2_shear}(f).
+in Figure~\ref{fig:BC2_shear}(f).
 
@@
 actually increases orientational order and has somewhat lower free energy 
-under low shear rates (Fig~\ref{fig:BC1_shear}(d,f)).
+under low shear rates (Figure~\ref{fig:BC1_shear}(d,f)).
 This effect suggests that in amphiphilic suspensions,
@@
 Not all background flows produce this ``organizing'' effect, as it was not
-observed in the TG background flow case (Fig~\ref{fig:BC1_TG}).
+observed in the TG background flow case (Figure~\ref{fig:BC1_TG}).
 \citet{PhysRevLett.128.256102} have shown how to drive particle clusters into arbitrary target shapes by solving
@@
 The existence of 'X'-shaped local arrangements as a local
-equilibrium (Fig.~\ref{fig:relax}(d), top, middle rectangle)
+equilibrium (Figure~\ref{fig:relax}(d), top, middle rectangle)
 further suggests there may be greater diversity in the set of
@@
 %
-where $G(\xx)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL} and $\nnu$ is the outward normal.
+where $G(\xx)$ is the fundamental solution to the screened Laplace
+equation \eqref{eq:SL} and $\nnu_\yy$ is the outward normal.
 Since the free energy functional can be written as 
@@
 The number $\theta_i(\xx)$ is the angle formed by the position $\xx$,
-the particle center $\aa_i$, and the particle director $\dd_i$.% (Fig
-\ref{fig:flow_map}).
-The normalizations e.g., $(\pi r)^{-1/2}$, provide a uniform surface
-energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles of radius
-$r$. The cases (ii) and (iii) are obtained by applying a vertical shift
-and scaling to case (i).  Using this setup, we simulate the dynamics of
-60 particles with one set of random initial positions and orientations
-as shown in Fig~\ref{fig:relax}(a)
+the particle center $\aa_i$, and the particle director $\dd_i$.
+(Figure~\ref{fig:flow_map}). The normalizations e.g., $(\pi r)^{-1/2}$,
+provide a uniform surface energy $\int_{\Gamma_i} g^2 \,ds = 1$ for
+circular particles of radius $r$. The cases (ii) and (iii) are obtained
+by applying a vertical shift and scaling to case (i). Using this setup,
+we simulate the dynamics of 60 particles with one set of random initial
+positions and orientations as shown in Figure~\ref{fig:relax}(a)
 
@@
 
-The second set of simulation is putting the equilibrium state of the boundary condition \eqref{eq:bcs} (iii), the checker board, in a shear flow.
-After a set of empirical numerical investigations, we obtain a critical shear rate $\dot\gamma=0.15$ where the checker board deforms into stripes and small groups of JP.
-Fig~\ref{fig:shear_2}(a)--(d) show configurations when $t=\{0,50,100,150\}$.
-%The deformation starts with stripe separations
+The second set of simulation is putting the equilibrium state of the
+boundary condition \eqref{eq:bcs} (iii), the checker board, in a shear
+flow. After a set of empirical numerical investigations, we obtain a
+critical shear rate $\dot\gamma=0.15$ where the checker board deforms
+into stripes and small groups of JP. Figure~\ref{fig:shear_2}(a)--(d) show configurations when $t=\{0,50,100,150\}$. %The deformation starts with stripe separations
 %
@@
 %
-The magnitude of the vortex flow is controlled by the velocity scale $V_0$.
-Similar to the setup in the shear flow cases, we shift the center of mass position to the origin then turn on the Taylor-Green flow with $V_0=0.1$ and tune the sides of zero-velocity box to $\pi$, i.e., $l=0.5$, Fig~\ref{fig:TG_1}(a)--(c) show three frames of simulation results and we
-track the aspect ratio $\lambda$ described in the previous section which is provided in panel (d). 
-The stiffness of the multi-lamellar structure is able to compete with the flow therefore the structure
-does not deform to any states other than multi-lamellar shape. 
-We also found that the flow strength coefficient above $V_0=0.1$ will result to clear group separations during the simulations. 
-Comparing with the case when $V_0=0.2$, we provide a frame in Fig~\ref{fig:TG_2}(a) and the energy comparison is shown in panel (b).
-Numerical results validate the phenomenon that a higher Taylor-Green vortex flow generates large structure separations with higher total energy.
+The magnitude of the vortex flow is controlled by the velocity scale
+$V_0$.  Similar to the setup in the shear flow cases, we shift the
+center of mass position to the origin then turn on the Taylor-Green flow
+with $V_0=0.1$ and tune the sides of zero-velocity box to $\pi$, i.e.,
+$l=0.5$, Figure~\ref{fig:TG_1}(a)--(c) show three frames of simulation
+results and we track the aspect ratio $\lambda$ described in the
+previous section which is provided in panel (d).  The stiffness of the
+multi-lamellar structure is able to compete with the flow therefore the
+structure does not deform to any states other than multi-lamellar shape.
+We also found that the flow strength coefficient above $V_0=0.1$ will
+result to clear group separations during the simulations.  Comparing
+with the case when $V_0=0.2$, we provide a frame in
+Figure~\ref{fig:TG_2}(a) and the energy comparison is shown in panel
+(b). Numerical results validate the phenomenon that a higher
+Taylor-Green vortex flow generates large structure separations with
+higher total energy.
 
@@
 
-Here are demonstrations of having JP vesicle and multi-lamellar structure in a narrow channel 
-under a shear flow.
-Simulation results and snapshots are shown in Figs~\ref{fig:confined_vesicle} and Fig~\ref{fig:confined_lamellar} where the JP vesicle has $N_b=25$ particles and JP lamellar has $N_b=40$ particles, respectively.
-Both starting configurations are pre-relaxed and the channel width in the narrow part is about 5 length units in the vesicle case and 4 length units in the lamellar case.
+Here are demonstrations of having JP vesicle and multi-lamellar
+structure in a narrow channel under a shear flow.  Simulation results
+and snapshots are shown in Figures~\ref{fig:confined_vesicle} and
+Figure~\ref{fig:confined_lamellar} where the JP vesicle has $N_b=25$
+particles and JP lamellar has $N_b=40$ particles, respectively. Both
+starting configurations are pre-relaxed and the channel width in the
+narrow part is about 5 length units in the vesicle case and 4 length
+units in the lamellar case.
 

### 2022-08-01 doc/PRF2022/PRF_main.tex
worked on revisions

@@
 \begin{abstract}
-  Active colloidal systems with non-equilibrium self-organization
-  is a long-standing challenging area in biology.
-  To understand how hydrodynamic flow may be used to actively
-  control self-assembly of Janus particles (JPs), we use a model
-  recently developed for the many-body hydrodynamics of amphiphilic
-  JPs suspended in a viscous background flow (JFM, 941, 2022).
-  We investigate how various bilayer structures arise from tuning
-  the hydrophobic properties of the JP-solvent interface.
-  Focusing on a simple tuning of the hydrophobicity distribution,
-  we found
-  JPs assembled into uni-lamella, multi-lamella and striated
-  structures.  To introduce dynamics, we include a linear shear flow and a
-  Taylor-Green mixing flow, and measure the
-  collective dynamics of JP particles in terms of their 
-  (a) free energy from the hydrophobic interactions between the JPs,
-  (b) order parameter for the ordering of JPs in terms of alignment of their directors, 
-  and (c) strain parameter that captures the deformation in the assembly.
-  We characterized the effective material properties of the JP structures
-  and found that the uni-lamellar structures increases orientation order under
-  shear flow, the multilamellar structure behaves as a shear thinning fluid,
-  and the striated structure possesses a finite yield stress.  
-  These numerical result provide insights into dynamic control of
-  non-equilibrium active biological systems with similar self-organization.
-% insert abstract here
+  Active colloidal systems with non-equilibrium self-organization is a
+  long-standing challenging area in biology. To understand how
+  hydrodynamic flow may be used to actively control self-assembly of
+  Janus particles (JPs), we use a model recently developed for the
+  many-body hydrodynamics of amphiphilic JPs suspended in a viscous
+  background flow (JFM, 941, 2022). We investigate how various bilayer
+  structures arise from tuning the hydrophobic properties of the
+  JP-solvent interface. Focusing on a simple tuning of the
+  hydrophobicity distribution, we found JPs assembled into uni-lamella,
+  multi-lamella and striated structures. To introduce dynamics, we
+  include a linear shear flow and a Taylor-Green mixing flow, and
+  measure the collective dynamics of JP particles in terms of their (a)
+  free energy from the hydrophobic interactions between the JPs, (b)
+  order parameter for the ordering of JPs in terms of alignment of their
+  directors, and (c) strain parameter that captures the deformation in
+  the assembly. We characterized the effective material properties of
+  the JP structures and found that the uni-lamellar structures increases
+  orientation order under shear flow, the multilamellar structure
+  behaves as a shear thinning fluid, and the striated structure
+  possesses a finite yield stress. These numerical result provide
+  insights into dynamic control of non-equilibrium active biological
+  systems with similar self-organization.
 \end{abstract}
@@
     \label{fig:BC1_shear}
-    Panels (a)-(c) are a snapshot at $t=0.5\ \mu$s of the multiple-component bilayer
-    with shear rate $\dot \gamma = \{0.05, 0.075, 0.1\}$.
-    The initial configuration is shown in inset of panel (a).
-    The streamlines are plotted in the background.
-    Panel (d) plots the free energies,
-    panel (e) shows the orientational parameter $\tilde{S}_2$,
-    and panel (f) shows positional parameter E.
-}
+    Panels (a)--(c) are a snapshot at $t=0.5\ \mu$s of the
+    multiple-component bilayer with shear rate $\dot \gamma = \{0.05,
+    0.075, 0.1\}$. The initial configuration is shown in inset of panel
+    (a). The streamlines are plotted in the background. Panel (d) shows
+    the free energies, panel (e) shows the orientational parameter
+    $\tilde{S}_2$, and panel (f) shows positional parameter E.}
 \end{figure}
@@
   pre-relaxed initial configuration is shown in inset of panel (a). The
-  streamlines are plotted in the background.  Panel (d) plots the free
+  streamlines are plotted in the background. Panel (d) shows the free
   energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel
-  (f) shows positional parameter E.
-     }
+  (f) shows positional parameter E.}
 \end{figure}
@@
   pre-relaxed initial configuration is shown in the inset of panel (a).
-  The streamlines are plotted in the background. Panel (d) plots the
+  The streamlines are plotted in the background. Panel (d) shows the
   free energies; panel (e) shows the orientational parameter
@@
   \end{center}
-\caption{\label{fig:ves_TG} Single vesicle in a TG flow.
-Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
-The streamlines are plotted in the background.
-Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
-}
-\end{figure}
-
-There is no appreciable pattern in the deformation for the multicomponent bilayer case in TG flow. 
-Figure~\ref{fig:BC1_TG}(a)--(c) are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s.
-At all flow strengths, the bilayer components are separated and mixed by the flow in neighboring cells. 
-In the $V_0 = 0.2$ case, the flow breaks off components consisting of only a few particles,
-leading an increase in energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve).
-There is no significant change in the orientational order.  There is an initial increase in the
-strain parameter due to component mixing, but the strains remains bounded since the particles
-stay confined to within the neighbors of the central cell.
-
-Patterns in the deformation, however, do emerge in the case of a vesicle in TG flow.
-For a vesicle in a Taylor-Green flow, Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\  \mu$s where $V_0=0.1,0.15,0.2$.
-Here, the circular vesicle takes on a steady square shape for moderate flow rates $V_0 = 0.1$ and $V_0 = 0.15$.
-In these cases, there is little change in the vesicle free energy and
-order (Figure~\ref{fig:ves_TG}(d)-(f))).
-The vesicle disintegrates for $V_0 = 0.2$, leading to a jump in energy, drop in order, and increase in strain,
-suggesting that the vesicle has a critical TG flow strength in the interval $[0.15, 0.2]$ separating the
-intact and ruptured end-states.
+\caption{\label{fig:ves_TG} A single vesicle in a TG flow. Panels
+  (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s
+  where the pre-relaxed initial configuration is shown in inset of panel
+  (a). The streamlines are plotted in the background. Panel (d) shows
+  the free energies; panel (e) shows orientational parameter
+  $\tilde{S}_2$; panel (f) shows positional parameter E.}
+\end{figure}
+
+There is no appreciable pattern in the deformation for the
+multicomponent bilayer case in TG flow. Figure~\ref{fig:BC1_TG}(a)--(c)
+are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s. At all
+flow strengths, the bilayer components are separated and mixed by the
+flow in neighboring cells. In the $V_0 = 0.2$ case, the flow breaks off
+components consisting of only a few particles, leading an increase in
+energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve). There is no
+significant change in the orientational order. There is an initial
+increase in the strain parameter due to component mixing, but the
+strains remains bounded since the particles stay confined to the
+neighbors of the central cell.
+
+Patterns in the deformation, however, do emerge in the case of a vesicle
+in TG flow. For a vesicle in a Taylor-Green flow,
+Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\ \mu$s
+where $V_0=0.1,0.15,0.2$. Here, the circular vesicle takes on a steady
+square shape for moderate flow rates $V_0 = 0.1$ and $V_0 = 0.15$. In
+these cases, there is little change in the vesicle free energy and order
+(Figure~\ref{fig:ves_TG}(d)--(f)). The vesicle disintegrates for $V_0 =
+0.2$, leading to a jump in energy, drop in order, and increase in
+strain, suggesting that the vesicle has a critical TG flow strength in
+the interval $[0.15, 0.2]$ separating the intact and ruptured
+end-states.
 
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)-(d) show the configurations with streamlines when a vesicle is in Taylor-Green flow at $t=1 \mu$s and $l= 1,2,3,4$, respectively.
-  For panel (e), the enclosed area $A_0/A$ calculated from the bilayer midplane decreases over time and the total length (as shown in the inset) measured from the midplane remains nearly constant with small magnitude of oscillations.
-  }
-\end{figure}
-
-The vesicle shape is also tied to cell size $l$.  
-Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in a
-TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s.  
-For the smallest cell size $l = 1$ tested, the vesicle is somewhat octagonal
-and passes through multiple cells (Figure~\ref{fig:BTG_Scale}(a)).
-For the largest cell size $l = 4$,
-the vesicle is rhomboid and surrounds a single cell.
-
-In all cases, the vesicle tank-treads like in the shear flow case.
-The direction of the tank-treading, however, varies with the cell
-size (Figure~\ref{fig:BTG_Scale}(a)--(d), directed arcs).  We attribute
-this change in rotational orientation to the total rotational moment
-of the cells that the vesicle passes through.
-
-We calculated the vesicle area $A$ and length $L$ (initial area $A_0$, initial length $L_0$)
-by averaging the area/length for the inner and outer leaflets.  
-As shown in Figure~\ref{fig:BTG_Scale}(e),
-the relative area $A/A_0$ decreases during the simulations, with a rate
-depending nonmonotonically on $l$.  
-The relative length $L/L_0$, however, is constant in $t$ for all cell
-sizes (Figure~\ref{fig:BTG_Scale}(e), inset).
-This implies that the vesicle behaves as an inextensible, permeable membrane.
-In previous work, \cite{Fu2022_JFM} determined the permeability constant of particle-based vesicles
-in the context of shear background flow\cite{chabanon2017,qua-gan-you2021}.
+  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)--(d) show
+  the configurations with streamlines of a vesicle is in a TG flow at
+  $t=1 \mu$s with $l= 1,2,3,4$, respectively. In panel (e), the enclosed
+  area $A_0/A$ calculated from the bilayer midplane decreases over time
+  and the total length (shown in the inset) measured from the midplane
+  remains nearly constant with small magnitude of oscillations.}
+\end{figure}
+
+The vesicle shape is also related to the cell size $l$.
+Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in
+a TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s. For the smallest cell
+size $l = 1$ tested, the vesicle is somewhat octagonal and passes
+through multiple cells (Figure~\ref{fig:BTG_Scale}(a)). For the largest
+cell size $l = 4$, the vesicle is rhomboid and surrounds a single cell.
+
+In all cases, the vesicle tank-treads like in the shear flow case. The
+direction of the tank-treading, however, varies with the cell size
+(Figure~\ref{fig:BTG_Scale}(a)--(d), directed arcs). We attribute this
+change in rotational orientation to the total rotational moment of the
+cells that the vesicle passes through.
+
+We calculate the vesicle area $A$ and length $L$ (initial area $A_0$,
+initial length $L_0$) by averaging the area and length of the inner and
+outer leaflets. As shown in Figure~\ref{fig:BTG_Scale}(e), the relative
+area $A/A_0$ decreases during the simulations, with the rate depending
+nonmonotonically on $l$. The relative length $L/L_0$, however, is
+constant in $t$ for all cell sizes (Figure~\ref{fig:BTG_Scale}(e),
+inset). This implies that the vesicle behaves as an inextensible,
+permeable membrane. In previous work, \citet{Fu2022_JFM} determined the
+permeability constant of particle-based vesicles in the context of shear
+background flow~\cite{chabanon2017, qua-gan-you2021}.
 
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BC2_shear}
-Multilamellar structure in a shear flow.
-Panels (a)-(c) are snapshots for $\dot \gamma = \{0.05, 0.1, 0.15\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
-The streamlines are plotted in the background.
-Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
-       }
+  \caption{\label{fig:BC2_shear} A multilamellar structure in a shear
+  flow. Panels (a)--(c) are snapshots for $\dot \gamma = \{0.05, 0.1,
+  0.15\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration
+  is shown in inset of panel (a). The streamlines are plotted in the
+  background. Panel (d) shows the free energies; panel (e) shows
+  orientational parameter $\tilde{S}_2$; panel (f) shows positional
+  parameter E.}
 \end{figure}
@@
 \subsection{Multilamellar and striated configurations in shear and TG flow}
-We have simulated particles for the multilamellar (BC (ii)) and striated (BC (iii))
-boundary conditions, in both shear and TG background flow.  The results are
-qualitatively similar and will be presented in tandem. 
+We have simulated particles for the multilamellar (BC (ii)) and striated
+(BC (iii)) boundary conditions, in both shear and TG background flow.
+The results are qualitatively similar and will be presented in tandem.
 For the multilamellar case, we place a 60-particle configuration (inset
-of Figure~\ref{fig:BC2_shear}(a))
-in shear flows with $\dot\gamma=0.05, 0.1, 0.15$ and in TG flow with flow rates $V_0=0.1, 0.15, 0.2$.
-For the striated case, we also place a 60-particle configuration (inset
-of Figure~\ref{fig:BC3_shear}(a))
-in shear and TG background flows.  Here, somewhat larger rates are required to see appreciable
-deformations for this boundary condition: $\dot\gamma=0.1, 0.125, 0.15$
-and $V_0=0.2, 0.25, 0.3$ respectively.
+of Figure~\ref{fig:BC2_shear}(a)) in shear flows with $\dot\gamma=0.05,
+0.1, 0.15$ and in TG flow with flow rates $V_0=0.1, 0.15, 0.2$. For the
+striated case, we also place a 60-particle configuration (inset of
+Figure~\ref{fig:BC3_shear}(a)) in shear and TG background flows. Here,
+somewhat larger rates are required to see appreciable deformations for
+this boundary condition: $\dot\gamma=0.1, 0.125, 0.15$ and $V_0=0.2,
+0.25, 0.3$, respectively.
 
@@
 rates (Figure~\ref{fig:BC2_shear}(d), Figure~\ref{fig:BC3_shear}(d)).
-The free energy of the striated configuration oscillates by $\pm 1$ $\mathrm{k_BT}$/nm
-due to square reference region deforming into a rhomboidal shape under shear
-flow (Figure~\ref{fig:BC3_shear}(d), solid curve).  No such oscillation
-is present in for the multilamellar configuration since this shape is circularly
-isotropic (Figure~\ref{fig:BC2_shear}(d), solid curve).
-At the lowest shear rates, there is, however, oscillation in the strains
-of both configurations, 
-while the order parameter $\tilde S_2$ is more less constant
-(Figure~\ref{fig:BC2_shear}(e),(f), Figure~\ref{fig:BC3_shear}(e),(f), solid curves).
-In summary, both multilallar and striated configurations behave as nearly
-rigid bodies under shear flow when the shear rate $\dot \gamma$ is low.
-
-In the high shear rate cases ($\dot\gamma=0.15$), both the
-multilamellar and striated configurations become disordered.  For BC (ii),
-the lamella break apart so that individual bilayers are no longer discernible
-(Figure~\ref{fig:BC2_shear}(c)).
-For BC (iii), the stria peal away from the main body,
-but remain individually intact (Figure~\ref{fig:BC3_shear}(c)).  
-Overall, the particles in BC (ii) and BC (iii) remain bounded
-and do not drift away in the shear background flow like for the
-BC (i) boundary condition (Figure~\ref{fig:BC1_shear}(c),
+The free energy of the striated configuration oscillates by $\pm 1$
+$\mathrm{k_BT}$/nm due to a square reference region deforming into a
+rhomboidal shape under shear flow (Figure~\ref{fig:BC3_shear}(d), solid
+curve). No such oscillation is present for the multilamellar
+configuration since this shape is circularly isotropic
+(Figure~\ref{fig:BC2_shear}(d), solid curve). At the lowest shear rates,
+there is, however, oscillation in the strains of both configurations,
+while the order parameter $\tilde S_2$ is nearly constant
+(Figure~\ref{fig:BC2_shear}(e),(f), Figure~\ref{fig:BC3_shear}(e),(f),
+solid curves). In summary, both multilamellar and striated
+configurations behave as nearly rigid bodies under shear flow when the
+shear rate $\dot \gamma$ is low.
+
+In the high shear rate cases ($\dot\gamma=0.15$), both the multilamellar
+and striated configurations become disordered. For BC (ii), the lamella
+break apart so that individual bilayers are no longer discernible
+(Figure~\ref{fig:BC2_shear}(c)). For BC (iii), the stria peel away from
+the main body, but remain individually intact
+(Figure~\ref{fig:BC3_shear}(c)). Overall, the particles in BC (ii) and
+BC (iii) remain bounded and do not drift away in the shear background
+flow like for the BC (i) (Figure~\ref{fig:BC1_shear}(c),
 Figure~\ref{fig:Ves_shear}(c)).
@@
   \vspace{-20pt}
-  \caption{\label{fig:BC2_TG} 
-Multilamellar structure in a Taylor-Green flow.
-Panels (a)-(c) are snapshots for $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
-The streamlines are plotted in the background.
-Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
- }
-\end{figure}
-
-Under a TG background flow, the free energy $F$ 
-is also basically constant for the lowest flow rates $V_0$
-(Figure~\ref{fig:BC2_TG}(d), Figure~\ref{fig:BC3_TG}(d), solid curves).
-The striated configuration is unperturbed by the flow, and is engulfed by a single,
-larger, rotating flow cell
-(Figure~\ref{fig:BC3_TG}(a)). 
-The multilamellar configuration is perturbed by the flow,
-as seen in the increase in
-the strain parameter $E$ (Figure~\ref{fig:BC3_TG}(f), solid curve).
-The difference in response to the background flow
-suggests that the multilamellar configuration
-allows for local rearrangement of the particles while retaining the overall shape.
-
-At large flow rates $V_0$, both configurations depart significantly from their local
-equilibrium.  The lamella bilayers from BC (ii) break apart, forming several,
-unlayered bilayer components (Figure~\ref{fig:BC2_TG}(c)).
-In BC (iii), the stria also break apart, but neighboring particles form
-'X'-like arrangements (Figure~\ref{fig:BC3_TG}(d)), resembling the doubly alternating
-director equilibrium (Figure~\ref{fig:relax}(d), center, top white rectangle).
+  \caption{\label{fig:BC2_TG} A multilamellar structure in a
+  Taylor-Green flow. Panels (a)-(c) are snapshots for $V_0 = \{0.1,
+  0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial
+  configuration is shown in inset of panel (a). The streamlines are
+  plotted in the background. Panel (d) shows the free energies; panel
+  (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows
+  positional parameter E.}
+\end{figure}
+
+Under a TG background flow, the free energy $F$ is also basically
+constant for the lowest flow rates $V_0$ (Figure~\ref{fig:BC2_TG}(d),
+Figure~\ref{fig:BC3_TG}(d), solid curves). The striated configuration is
+unperturbed by the flow, and is engulfed by a single, larger, rotating
+flow cell (Figure~\ref{fig:BC3_TG}(a)). The multilamellar configuration
+is perturbed by the flow, as seen in the increase in the strain
+parameter $E$ (Figure~\ref{fig:BC3_TG}(f), solid curve). The difference
+in response to the background flow suggests that the multilamellar
+configuration allows for local rearrangement of the particles while
+retaining the overall shape.
+
+At large flow rates $V_0$, both configurations depart significantly from
+their local equilibrium. The lamella bilayers from BC (ii) break apart,
+forming several unlayered bilayer components
+(Figure~\ref{fig:BC2_TG}(c)). In BC (iii), the stria also break apart,
+but neighboring particles form 'X'-like arrangements
+(Figure~\ref{fig:BC3_TG}(d)), resembling the doubly alternating director
+equilibrium (Figure~\ref{fig:relax}(d), center, top white rectangle).
 
@@
   \end{center}
-      \caption{\label{fig:BC3_shear}  A striated configuration in a shear flow.
-Panels (a)-(c) are snapshots for $\dot \gamma = \{0.1, 0.125, 0.15\}$ at $t=0.1\mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
-The streamlines are plotted in the background.
-Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
-    }
+  \caption{\label{fig:BC3_shear} A striated configuration in a shear
+  flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.1, 0.125,
+  0.15\}$ at $t=0.1\mu$s where the pre-relaxed initial configuration is
+  shown in inset of panel (a). The streamlines are plotted in the
+  background. Panel (d) shows the free energies; panel (e) shows
+  orientational parameter $\tilde{S}_2$; panel (f) shows positional
+  parameter E.}
 \end{figure}
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BC3_TG} A striated configuration in a Taylor-Green flow.
-Panels (a)-(c) are snapshots for $V_0=\{0.2, 0.25, 0.3\}$ at $t=0.4\mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
-The streamlines are plotted in the background.
-Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
-}
+  \caption{\label{fig:BC3_TG} A striated configuration in a Taylor-Green
+  flow. Panels (a)-(c) are snapshots for $V_0=\{0.2, 0.25, 0.3\}$ at
+  $t=0.4\mu$s where the pre-relaxed initial configuration is shown in
+  inset of panel (a). The streamlines are plotted in the background.
+  Panel (d) shows the free energies; panel (e) shows orientational
+  parameter $\tilde{S}_2$; panel (f) shows positional parameter E.}
 \end{figure}
@@
 \section{Discussion}
-Our results were for $N_b = 60$.  This particle number was large enough for the JP to form
-measurable structures while giving manageable simulation times (days) on a single computing processor.
-The simulation time for $N_b = 198$ in Figure~\ref{fig:relax} and Fig. \ref{fig:relax_energy}
-was several weeks, and so we avoided simulations of this size for our results.
-We used $N = 16$ grid points per particles for all simulations.  We performed a convergence study
-and found that using $N = 16$ or $N = 24$ grid points per particle gave quantitatively indistinguishable
-results.  The time courses consisted of $O(10^3)$ time steps with $\Delta t = 0.2$ nm.
-
-The free energy $F$ defined in \eqref{eq:free_energy}
-scales with the boundary data $g$ and repulsion modulus $M$.
-To remove the degree of freedom in the boundary data,
-we scaled all boundary data so that the square integral of $g$ is independent of
-type of boundary condition; BC (i), (ii), or (iii).
-This way, for a fixed configuration, the hydrophobic interaction portion of the
-free energy (the integral in \eqref{eq:free_energy}) converges to $2\pi \gamma c N_b$
-in the limit $\rho = 0$.  This gives a free energy per particle that is independent
-of the shape/intensity of the hydrophobic interface.  In practice, $\rho > 0$ is fixed
-and the JP assume different configurations.  As a result, the equilibrium energies
-per particle in our simulations are different and depend on the boundary condition
-(Figure~\ref{fig:relax_energy}).
-They are about 0.26 $\mathrm{k_BT}$/nm for BC (ii),
-0.55 $\mathrm{k_BT}$/nm for BC (i), and
-1.4 $\mathrm{k_BT}$/nm for BC (iii).
-
-Next, we suspended JP in viscous background flows and observed deformations
-as a function of flow strength.  There were three categories of boundary
-conditions; BC (i), BC (ii), and BC (iii); that formed bilayer, multilamellar, and striated
-configurations, respectively. For BC (i), we considered both an unstructured bilayer
-and a vesicle bilayer.  The background flows were a linear shear flow and a Taylor-Green (TG) flow.
-
-We can characterize the effective material properties of the JP structures
-based on the changes in free energy, orientationl order, and strain as a function
-of flow strength.
-Generally, $F$ increases, $\tilde S_2$ decreases, and 
-$E$ increases with increases in both $\dot \gamma$ and $V_0$, as expected.
-Structurally, the striated JP configuration for BC (iii) behaved the most
-like a rigid body over the flow strengths tested.  For this structure,
-the deformations measures were constant in time for shear rates $\dot \gamma$ up to
-$0.15$ and TG flow rate $V_0$ up to $0.25$
-(Figure~\ref{fig:BC3_shear} and Figure~\ref{fig:BC3_TG}).
-Conversely, a $25 - 50 \%$
-smaller value for $\dot \gamma$ or $V_0$ were required to observe
-nonrigid deformations for the BC (i) and BC (ii) cases.
-
-In terms of fluid behavior,
-the multilamellar (BC (ii)) structure behaves as shear thinning fluid
-while the striated structure (BC (iii)) has a finite yield stress. 
-Qualitatively, the strains for BC (ii) increases gradually 
-with shear rate (Figure~\ref{fig:BC2_shear}(f)).
-In contrast, the strains for BC (iii) are constant over a range of flow strengths
-and then increase when the flow strengths are large enough
-to deform the body (Figure~\ref{fig:BC3_shear}(f)).
-To quantify this behavior, we form 
-\[
+Our results were for $N_b = 60$ particles. This particle number was
+large enough for the JP to form measurable structures while giving
+manageable simulation times (days) on a single computing processor. The
+simulation time for $N_b = 198$ in Figure~\ref{fig:relax} and
+Figure~\ref{fig:relax_energy} was several weeks, and so we avoided
+simulations of this size for our results. We used $N = 16$ grid points
+per particle for all simulations. We performed a convergence study and
+found that using $N = 16$ or $N = 24$ grid points per particle gave
+quantitatively indistinguishable results. The time courses consisted of
+$O(10^3)$ time steps with $\Delta t = 0.2$ nm.
+
+The free energy $F$ defined in~\eqref{eq:free_energy} scales with the
+boundary data $g$ and repulsion modulus $M$. To remove the degree of
+freedom in the boundary data, we scaled all boundary data so that the
+square integral of $g$ is independent of the type of boundary condition; BC
+(i), (ii), or (iii). This way, for a fixed configuration, the
+hydrophobic interaction portion of the free energy (the integral
+in~\eqref{eq:free_energy}) converges to $2\pi \gamma c N_b$ in the limit
+$\rho = 0$. This gives a free energy per particle that is independent of
+the shape and intensity of the hydrophobic interface. In practice, $\rho
+> 0$ is fixed and the JPs assume different configurations. As a result,
+the equilibrium energies per particle in our simulations are different
+and depend on the boundary condition (Figure~\ref{fig:relax_energy}).
+They are about 0.26 $\mathrm{k_BT}$/nm for BC (ii), 0.55
+$\mathrm{k_BT}$/nm for BC (i), and 1.4 $\mathrm{k_BT}$/nm for BC (iii).
+
+Next, we suspended JPs in viscous background flows and observed
+deformations as a function of flow strength. There were three categories
+of boundary conditions---BC (i), BC (ii), and BC (iii)---that formed
+bilayer, multilamellar, and striated configurations, respectively. For
+BC (i), we considered both an unstructured bilayer and a vesicle
+bilayer. The background flows were a linear shear flow and a TG flow.
+
+We can characterize the effective material properties of the JP
+structures based on the changes in free energy, orientational order, and
+strain as a function of flow strength. Generally, $F$ increases, $\tilde
+S_2$ decreases, and $E$ increases with increases in both $\dot \gamma$
+and $V_0$, as expected. Structurally, the striated JP configuration for
+BC (iii) behaved the most like a rigid body over the flow strengths
+tested. For this structure, the deformation measures were constant in
+time for shear rates $\dot \gamma$ up to $0.15$ and TG flow rate $V_0$
+up to $0.25$ (Figure~\ref{fig:BC3_shear} and Figure~\ref{fig:BC3_TG}).
+Conversely, a $25--50 \%$ smaller value for $\dot \gamma$ or $V_0$ were
+required to observe nonrigid deformations for the BC (i) and BC (ii)
+cases.
+
+In terms of fluid behavior, the multilamellar (BC (ii)) structure
+behaves as a shear thinning fluid while the striated structure (BC (iii))
+has a finite yield stress. Qualitatively, the strains for BC (ii)
+increases gradually with shear rate (Figure~\ref{fig:BC2_shear}(f)). In
+contrast, the strains for BC (iii) are constant over a range of flow
+strengths and then increase when the flow strengths are large enough to
+deform the body (Figure~\ref{fig:BC3_shear}(f)). To quantify this
+behavior, we form 
+\begin{align}
 \mu_{\text{hyd}} = \frac{\dot \gamma}{\dot E} \mu 
-\]
-as an effective dynamic viscosity of the particle assemblies.
-The numerator $\dot \gamma \mu$ gives the force per
-area provided by the solvent stresses where
-$\mu = 1$ mPa s is
-the solvent viscosity.
-The strain rate $\dot E$ of the body is the slope of a linear fit to the strain curves e.g.,
-in Figure~\ref{fig:BC2_shear}(f).
-
-Calculated viscosities of particle assemblies are shown
-in Table \ref{tbl:bcii_visc}.
-The middle row gives the solid area fraction $\phi$;
-the sum of the rigid particle areas divided by the
-total area of the solvent and particle region.
-We observe that for the multilamellar structure,
-$\mu_{\text{hyd}}$ decreases
-with increasing shear rate.
-The predicted viscosities of the particle assemblies
-are on the order of hundreds of times that of water,
-consistent with suspension viscosities for noninteracting
-particles \cite{KONIJN201461}.
-In the case of striated structures, viscosity is
-effectively infinite for the lower two of the shear rates,
-and then drops to a finite value $\mu_{\text{hyd}} = 60$ mPa s
-when the shear rate reaches $0.15$ ns$^{-1}$.
+\end{align}
+as an effective dynamic viscosity of the particle assemblies. The
+numerator $\dot \gamma \mu$ gives the force per area provided by the
+solvent stresses where $\mu = 1$ mPa s is the solvent viscosity. The
+strain rate $\dot E$ of the body is the slope of a linear fit to the
+strain curves e.g., in Figure~\ref{fig:BC2_shear}(f).
+
+Calculated viscosities of particle assemblies are shown in
+Table~\ref{tbl:bcii_visc}. The middle row gives the solid area fraction
+$\phi$; the sum of the rigid particle areas divided by the total area of
+the solvent and particle region. We observe that for the multilamellar
+structure, $\mu_{\text{hyd}}$ decreases with increasing shear rate. The
+predicted viscosities of the particle assemblies are on the order of
+hundreds of times that of water, consistent with suspension viscosities
+for noninteracting particles~\cite{KONIJN201461}. In the case of
+striated structures, viscosity is effectively infinite for the lower two
+of the shear rates, and then drops to a finite value $\mu_{\text{hyd}} =
+60$ mPa s when the shear rate reaches $0.15$ ns$^{-1}$.
 \begin{table}
-  \caption{Dynamic viscosity of assemblies $\mu_{\text{hyd}}$ (mPa s) 
-\label{tbl:bcii_visc}
-}
+  \caption{\label{tbl:bcii_visc} The dynamic viscosity of assemblies
+  $\mu_{\text{hyd}}$ (mPa s).}
 \centering
@@
 
-In the case of BC (i), our previous work\cite{Fu2022_JFM} calculated a
-friction coefficient $b$ for the intermonolayer slip between the two leaflets
-of a bilayer. \citet{denOtter2007,Zgorski2019} and
-\citet{doi:10.1073/pnas.2100156118} have
-calculated in-plane viscosities for fully three-dimensional bilayers.
-Although not part of this work,
-it is in principle possible to obtain an in-plane
-viscosity using the hydrophobic potential
-\eqref{eq:free_energy}
-by replacing the boundary condition \eqref{eq:bc-type}
-with one that is everywhere constant, in effect modeling
-lipids in a bilayer as an array of as elongated, purely hydrophobic
-pillars.
-
-While increased flow strengths generally injected energy into the suspension,
-the simulation results show that the unstructured bilayer 
-actually increases orientational order and has somewhat lower free energy 
-under low shear rates (Figure~\ref{fig:BC1_shear}(d,f)).
-This effect suggests that in amphiphilic suspensions,
-it might be possible decrease the excess area of the system 
-by subjecting the suspension to a moderate shear flow.
-Not all background flows produce this ``organizing'' effect, as it was not
-observed in the TG background flow case (Figure~\ref{fig:BC1_TG}).
-\citet{PhysRevLett.128.256102} have shown how to drive particle clusters into arbitrary target shapes by solving
-a first passage problem.
-
-\citet{kohl-cor-che-vee22} have simulated
-suspensions of JP in three dimensions
-using the same free energy formulation of
-hydrophobic attraction used in the
-present work. They observed spontaneous
-aggregation into micelles generically and
-formation of bilayers when the initial
-configuration was chosen sufficiently close to the final
-configuration.
-\citet{kohl-cor-che-vee22} also studied self-assembly
-of bipolar electric JP, which bare some resemblance
-to polar boundary condition we employ.
-In the case of bipolar electric JP, the particles
-form parallel chains that repel.  In contrast, the
-interaction between stria under BC (iii) is attractive.
-The existence of 'X'-shaped local arrangements as a local
-equilibrium (Figure~\ref{fig:relax}(d), top, middle rectangle)
-further suggests there may be greater diversity in the set of
-possible equilibria in three-dimensions.
-
-The characteristics of the self-assembly of amphiphilic JP into onion-like
-dendrimersomes have been studied
-by molecular dynamics simulations~\cite{C9NR05885K}.  
-The molecular dynamics simulations
-use an anisotropic pair potential
-is used to describe the particle interactions
-where a harmonic form describes the repulsive part 
-and an anisotropic attractive part describes the hydrophobic interactions.
+In the case of BC (i), our previous work~\cite{Fu2022_JFM} calculated a
+friction coefficient $b$ for the intermonolayer slip between the two
+leaflets of a bilayer. \citet{denOtter2007,Zgorski2019} and
+\citet{doi:10.1073/pnas.2100156118} have calculated in-plane viscosities
+for fully three-dimensional bilayers. Although not part of this work, it
+is in principle possible to obtain an in-plane viscosity using the
+hydrophobic potential~\eqref{eq:free_energy} by replacing the boundary
+condition~\eqref{eq:bc-type} with one that is everywhere constant, in
+effect modeling lipids in a bilayer as an array of elongated, purely
+hydrophobic pillars.
+
+While increased flow strengths generally injected energy into the
+suspension, the simulation results show that the unstructured bilayer
+actually increases orientational order and has somewhat lower free
+energy under low shear rates (Figure~\ref{fig:BC1_shear}(d,f)). This
+effect suggests that in amphiphilic suspensions, it might be possible to
+decrease the excess area of the system by subjecting the suspension to a
+moderate shear flow. Not all background flows produce this
+``organizing'' effect, as it is not observed in the TG background flow
+case (Figure~\ref{fig:BC1_TG}). \citet{PhysRevLett.128.256102} have
+shown how to drive particle clusters into arbitrary target shapes by
+solving a first passage problem.
+
+\citet{kohl-cor-che-vee22} have simulated JP suspensions in three
+dimensions using the same free energy formulation of hydrophobic
+attraction used in the present work. They observed spontaneous
+aggregation into micelles generically and formation of bilayers when the
+initial configuration was chosen sufficiently close to the final
+configuration. They also studied self-assembly of bipolar electric JP,
+which bare some resemblance to polar boundary condition we employ. In
+the case of bipolar electric JP, the particles form parallel chains that
+repel. In contrast, the interaction between stria under BC (iii) is
+attractive. The existence of 'X'-shaped local arrangements as a local
+equilibrium (Figure~\ref{fig:relax}(d), top, middle rectangle) further
+suggests there may be greater diversity in the set of possible
+equilibria in three-dimensions.
+
+The characteristics of the self-assembly of amphiphilic JP into
+onion-like dendrimersomes have been studied by molecular dynamics
+simulations~\cite{C9NR05885K}. The molecular dynamics simulations use an
+anisotropic pair potential is used to describe the particle interactions
+where a harmonic form describes the repulsive part and an anisotropic
+attractive part describes the hydrophobic interactions.
 
@@
   \end{center}
-\caption{A checker board in shear flows with shear rates $\dot\gamma=\{0.125, 0.15\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
+\caption{A checkerboard in shear flow with shear rates
+  $\dot\gamma=\{0.125, 0.15\}$. We propose the order parameter defined
+  by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
 \end{figure}
@@
   \end{center}
-\caption{A checker board in Taylor-Green flows when the flow strength $V_0=\{0.2,0.3\}$. }
+\caption{A checkerboard in Taylor-Green flows when the flow strength $V_0=\{0.2,0.3\}$. }
 \end{figure}

### 2022-08-02 doc/PRF2022/PRF_main.tex
tidied up the text

@@
 \author{Szu-Pei Fu}
-\email{sfu17@fordham.edu}
+\email{peter.fu@trincoll.edu}
+\affiliation{Department of Mathematics, Trinity College, Hartford, Connecticut 06106, USA}
+
 %\homepage[]{Your web page}
@@
 \begin{abstract}
+%<<<<<<< HEAD
+%Active colloidal systems with non-equilibrium self-organization is a long-standing challenge in biology. To understand how hydrodynamic flow may be used
+%to actively control self-assembly of Janus particles (JPs),  we use a model recently developed for the many-body hydrodynamics of amphiphilic JPs suspended 
+%in a viscous background flow (JFM, 941, 2022) to investigate how various bilayer structures arise from tuning the hydrophobicity/hydrophilicity of the JPs. 
+%Focusing on three distributions of hydrophobicity we found JPs may assemble into uni-lamella, multi-lamella, and striated structures in a viscous fluid. 
+%Under a linear flow and a Taylor-Green mixing flow,  we use three measures to quantify the collective dynamics of JP particles under a background flow: 
+%(a) Free energy from the hydrophobic interactions between the JPs, (b) an order parameter for the ordering of JPs in terms of alignment of their directors, 
+%and (c) a strain parameter that captures the deformation in the assembly. We found the dynamics of these three measures correlate well with the hydrodynamics 
+%of JPs. These numerical provide insights into dynamic control of non-equilibrium active biological systems with similar self-organization.
+% insert abstract here
+%=======
   Active colloidal systems with non-equilibrium self-organization is a
-  long-standing challenging area in biology. To understand how
+  long-standing, challenging area in biology. To understand how
   hydrodynamic flow may be used to actively control self-assembly of
@@
   systems with similar self-organization.
+%>>>>>>> 4f49b2ee420baba836cbb337c263b33981e1b096
 \end{abstract}
@@
 %\section{\label{}}
-Janus particles (JPs) are colloids with two surfaces of different
-properties. For example, it is common for the surface of a Janus
-particle to be partly hydrophilic and hydrophobic (polar and non-polar).
-In a viscous solvent, Janus particles often self-assemble into
+Janus particles are colloids whose surfaces 
+%have different properties. For example, it is common for the surface of a Janus
+%particle to be 
+may be partly hydrophilic and hydrophobic (polar and non-polar).
+More generally the surface of a Janus particle may have a spatial distribution of hydrophobicity/hydrophilicity.
+In a viscous solvent, in a quiescent flow, Janus particles often self-assemble into
 structures with tunable functions for biomedical engineering
@@
 LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale, Bradley2016}.
-Depending on the interactions between Janus particles and the
+Depending on the interactions between Janus particles (JPs) and the
 surrounding viscous solvent, JPs self-assemble into oligomers of various
@@
 
-Dynamics offers yet another dimension of control that emerges naturally
+Dynamic flows offer yet another dimension of control that emerge naturally
 from the interactions between particles and fluid in colloidal
@@
 geometrical frustration, which has been used to explain disordered
-systems, could be used to design new, ordered systems instead, through
+systems, could instead be used to design new, ordered systems, through
 specific choices for the shapes or interactions of the
@@
 The many-body hydrodynamics of amphiphilic Janus particles assembled as
-vesicles and suspended in a viscous fluid (at zero Reynolds number) has
+vesicles suspended in a viscous fluid (at zero Reynolds number) has
 been studied using boundary integral numerical
@@
 hydrophobic attraction potential (HAP).
-
+%
 In a quiescent flow, numerical simulations of a JP suspension showed
@@
 hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
-many familiar behaviors of a vesicle~\cite{Fu2022_JFM}: elongation and
+many familiar behaviors of a vesicle: elongation and
 alignment along the extensional direction, tank-treading, and rupture of
-a vesicle under shear flow.
-
-In this work we take advantage of the flexibility of the model to
+a vesicle under shear flow~\cite{Fu2022_JFM}.
+
+In this work, we take advantage of the flexibility of the model to
 examine the effects of boundary condition on JP surfaces that could be
@@
 We show that a simple tuning of the hydrophobic distribution leads to
-multilamellar and striated structures. Here less is understood about the
+multilamellar and striated structures. Here, less is understood about the
 flow-structure interactions and we investigate the deformation of these
@@
 \begin{align}
+  \label{eq:FandTdef}
   \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
@@
 \end{align}
-for $i = 1,\ldots,N_b$ with particle outward normal $\nnu$, where
+for $i = 1,\ldots,N_b$ with particle outward normal $\nnu$.  The formulas
+in \eqref{eq:FandTdef} involve the second-order hydrophobic stress tensor
 \begin{align}
 \mathbf{T} = \gamma \left[ \rho^{-1} u^2 \mathbf{I}
-  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
-\end{align}
-is the hydrophobic stress. The repulsion is rotationally symmetric and
-does not contribute to the torque.
+  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
+\end{align}
+The repulsion is rotationally symmetric and
+does not contribute to the torque $T_i$.
 
@@
 respect to $\yy \in \Gamma$. To satisfy the boundary
-condition~\eqref{eq:SLbc}, the density function must satisfy
+condition~\eqref{eq:SLbc}, the density function must satisfy\cite{Hsiao2008}
 \begin{align}
@@
 The parameter $a$ normalizes the boundary conditions 
-so that $\int_{\Gamma_i} g^2(\xx) \, \dif s =  2\pi c$.
+so that $\int_{\Gamma_i} g^2(\xx) \, \dif s =  1$.
 The motivation for this normalization is that the hydrophobic attraction
@@
 surface.  Then, the boundary condition (BC) can be classified into three
-categories: $\min g >0$, $\min g =0$, and $\min g <0$.  These three
+categories: $\min g = 0$, $\min g >0$, and $\min g <0$.  These three
 categories correspond to three characteristic values of $b$ in
-\eqref{eq:bc-type}: $b=2$, $b=1$ and $b=0$, respectively. 
+\eqref{eq:bc-type}: $b=1$, $b=2$ and $b=0$, respectively. 
 %
@@
 hydrophobic sides to form bilayers (Figure~\ref{fig:relax}(b)). The
-inset shows the equilibrium state for the 60-particle run. Both cases
+inset shows the equilibrium state for the 60-particle run. Both
+$N_b = 60$ and $N_b = 198$ cases
 form bilayers with multiple components.
 
-In BC (ii) with $b = 1$, the boundary data is everywhere positive. It
+In BC (ii) with $b = 2$, the boundary data is everywhere positive. It
 takes the maximum value $3a$ on the tail (red) and the minimum value $a$
@@
 
-Finally, BC (iii) with $b=1$ corresponds to a water structure with
+Finally, BC (iii) with $b=0$ corresponds to a water structure with
 positive/negative charge~\cite{MaRa76, Ma77}. Here, the head repels the
@@
     \label{fig:BC1_shear}
-    Panels (a)--(c) are a snapshot at $t=0.5\ \mu$s of the
+    Panels (a)--(c) are a snapshot at $t=0.5\ \upmu$s of the
     multiple-component bilayer with shear rate $\dot \gamma = \{0.05,
@@
 \label{sec:results}
-In this section, we subject the Janus particle structures to various
-background flows. The purpose is to understand how self-assembled
-particles respond to external forcing. We then compare effective
-properties of materials comprised of Janus particles as a function of
+In this section, we subject the JP structures to various
+background flows. The purpose is to understand how the self-assemblies
+respond to external forcing. We then compare effective
+properties of materials comprised of JPs as a function of
 their amphiphilic properties.
@@
 orientational order.  Note that the free energy $F$ in
-Figure~\ref{fig:BC1_shear}(d) has the unit of force because our system
+Figure~\ref{fig:BC1_shear}(d) has the unit of force ($\mathrm{k_BT}$/nm $\approx$ 4.114 pN)
+because our system
 is two dimensional.
@@
 A single vesicle in a shear flow. Panels (a)--(c) are snapshots for
-  $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \mu$s where the
+  $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \upmu$s where the
   pre-relaxed initial configuration is shown in inset of panel (a). The
@@
 slip~\cite{sch-vla-mik2010,denOtter2007,Zgorski2019}, and
-permeability~\cite{chabanon2017, qua-gan-you2021}), our previous studies
-showed the existence of a critical shear rate above which the JP vesicle
+permeability~\cite{chabanon2017, qua-gan-you2021}), our previous work
+demonstrated the existence of a critical shear rate above which the JP vesicle
 ruptures~\cite{grandmaison_brancherie_salsac_2021,D2SM00179A}. Based on
@@
   \caption{\label{fig:BC1_TG} Multiple component bilayers in a
-  Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The
+  Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \upmu$s. The
   pre-relaxed initial configuration is shown in the inset of panel (a).
@@
 \caption{\label{fig:ves_TG} A single vesicle in a TG flow. Panels
-  (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s
+  (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \upmu$s
   where the pre-relaxed initial configuration is shown in inset of panel
@@
 energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve). There is no
-significant change in the orientational order. There is an initial
+apparente structure to the change in the orientational order. There is an initial
 increase in the strain parameter due to component mixing, but the
@@
 in TG flow. For a vesicle in a Taylor-Green flow,
-Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\ \mu$s
+Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\ \upmu$s
 where $V_0=0.1,0.15,0.2$. Here, the circular vesicle takes on a steady
@@
 strain, suggesting that the vesicle has a critical TG flow strength in
-the interval $[0.15, 0.2]$ separating the intact and ruptured
+the interval $0.15 < V_0 <  0.2$ separating the intact and ruptured
 end-states.
@@
   the configurations with streamlines of a vesicle is in a TG flow at
-  $t=1 \mu$s with $l= 1,2,3,4$, respectively. In panel (e), the enclosed
+  $t=1 \upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the enclosed
   area $A_0/A$ calculated from the bilayer midplane decreases over time
@@
   flow. Panels (a)--(c) are snapshots for $\dot \gamma = \{0.05, 0.1,
-  0.15\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration
+  0.15\}$ at $t=0.6\ \upmu$s where the pre-relaxed initial configuration
   is shown in inset of panel (a). The streamlines are plotted in the
@@
 hydrophobic interaction portion of the free energy (the integral
-in~\eqref{eq:free_energy}) converges to $2\pi \gamma c N_b$ in the limit
+in~\eqref{eq:free_energy}) converges to $\gamma N_b$ in the limit
 $\rho = 0$. This gives a free energy per particle that is independent of
@@
 up to $0.25$ (Figure~\ref{fig:BC3_shear} and Figure~\ref{fig:BC3_TG}).
-Conversely, a $25--50 \%$ smaller value for $\dot \gamma$ or $V_0$ were
+Conversely, a $25\%$--$50 \%$ smaller value for $\dot \gamma$ or $V_0$ was
 required to observe nonrigid deformations for the BC (i) and BC (ii)
@@
 \begin{align}
-\mu_{\text{hyd}} = \frac{\dot \gamma}{\dot E} \mu 
+\mu_{\text{asm}} = \frac{\dot \gamma}{\dot E} \mu 
 \end{align}
@@
 the solvent and particle region. We observe that for the multilamellar
-structure, $\mu_{\text{hyd}}$ decreases with increasing shear rate. The
+structure, $\mu_{\text{asm}}$ decreases with increasing shear rate. The
 predicted viscosities of the particle assemblies are on the order of
@@
 striated structures, viscosity is effectively infinite for the lower two
-of the shear rates, and then drops to a finite value $\mu_{\text{hyd}} =
+of the shear rates, and then drops to a finite value $\mu_{\text{asm}} =
 60$ mPa s when the shear rate reaches $0.15$ ns$^{-1}$.
@@
   \caption{\label{tbl:bcii_visc} The dynamic viscosity of assemblies
-  $\mu_{\text{hyd}}$ (mPa s).}
+  $\mu_{\text{asm}}$ (mPa s).}
 \centering
@@
 
+The characteristics of the self-assembly of amphiphilic JP into
+onion-like dendrimersomes like for BC (ii) were previously studied by molecular dynamics
+simulations~\cite{C9NR05885K}. The molecular dynamics simulations use an
+anisotropic pair potential to describe the particle interactions
+where a harmonic form describes the repulsive part and an anisotropic
+attractive part describes the hydrophobic interactions.
+
 \citet{kohl-cor-che-vee22} have simulated JP suspensions in three
@@
 configuration. They also studied self-assembly of bipolar electric JP,
-which bare some resemblance to polar boundary condition we employ. In
-the case of bipolar electric JP, the particles form parallel chains that
-repel. In contrast, the interaction between stria under BC (iii) is
+which use BC (ii) but electric potential, instead of a water order parameter,
+to define the interaction.  Due to the differing interaction,
+bipolar electric particles form parallel chains that
+repel. In contrast, the hydrophobic interaction between stria is
 attractive. The existence of 'X'-shaped local arrangements as a local
@@
 suggests there may be greater diversity in the set of possible
-equilibria in three-dimensions.
-
-The characteristics of the self-assembly of amphiphilic JP into
-onion-like dendrimersomes have been studied by molecular dynamics
-simulations~\cite{C9NR05885K}. The molecular dynamics simulations use an
-anisotropic pair potential is used to describe the particle interactions
-where a harmonic form describes the repulsive part and an anisotropic
-attractive part describes the hydrophobic interactions.
+equilibria in three-dimensions when employing hydrophobic attraction.
 
@@
 
-In this work, we employ the newly developed JP model using BIEs and tune 
-the boundary conditions with energy normalization to study the dynamics of 
-amphiphilic and dipolar like JPs. The normal derivative \eqref{eq:normal_deriv} 
-overcomes an obstacle for numerical implementations in the free energy $F$ 
-where the gradient of solution to the screened Laplace equation involves 
-hyper-singularities.
+In this work, we employ the newly developed JP model using BIEs ~\cite{Fu20, Fu2022_JFM} 
+and tune the boundary conditions with energy normalization to study the dynamics of 
+amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs.
+To overcome the well-known 
+obstacle for numerical implementations in the free energy $F$ where the gradient of 
+solution to the screened Laplace equation involves hyper-singularities, we derive the normal 
+derivative \eqref{eq:normal_deriv} in terms of single layer potential $\SSS$.
 
 Simulations include the self-assembly behaviors when the flow is absent and
-particle aggregations when suspended in shear and TG background flows with 
-various flow rates. We track the total free energy, the orientational order 
-parameter, and the strain parameter to comprehensively summarize and classify 
-the effective properties of all three materials. Observations have shown that 
-multi-lamella and the striated structures Under a relatively weak linear shear flow 
-behave like a rigid body with minimal deformation. The effective viscosity of the 
-material gives a quantitative validation to support the statement. High shear rate 
-cases provide the range when the critical shear rate for structure to break apart 
-and major topological changes. As expected in all case studies, the free energy 
-spikes at certain levels are indicators.
+when JP are subject to shear and TG background flows with various 
+flow strengths. The free energy profiles demonstrate that the relaxation process for 
+particles confined in a certain size of box is independent of number of particles 
+($N_b$). However, the final configurations highly depend on the initial particle 
+directors $\dd_i$. Therefore, multiple patterns or local energy minimum states may 
+appear depending on the initial setup.
+
+We track the total free energy, the orientational order parameter,
+and the strain parameter to comprehensively summarize and classify the effective properties
+of all three materials. 
+Observations have shown that multi-lamella and the striated structures under a relatively 
+weak linear shear flow behave like a rigid body with minimal deformation. The effective 
+viscosity of the material gives a quantitative validation to support the statement. High 
+shear-rate cases provide a range for critical shear rates where the structures break 
+apart and undergo major topological changes. As expected in all case studies,
+free energy, orientationl order, and strain combined 
+are good topological indicators.
 
@@
 TG flow, we compare the results when the size of cell is varied and a nonmonotonic 
-trend in reduced area with respect to the cell size arises.
-
-The results reported here provide a preliminary framework for colloidal sciences. 
-The present study also helps us to understand more rheological properties of industrial 
-produced Janus particles. This study can be extended to three dimensional system 
-and it has been included in our future goals. The boundary condition can be designed 
-as one with random perturbations that are more close to lab experiments.
+trend in reduced area with respect to the cell size arises. One finding to be noted is 
+that the TG flow with specified parameters can effectively control the structure shapes 
+such as a square vesicle or a polygonal shape.
+
+The results reported here provide an inroad computational framework for colloidal sciences. 
+The present study also helps us to understand more rheological properties of industrially 
+produced JP.
+This study can be extended to three dimensional systems 
+and it has been included in our future goals\cite{kohl-cor-che-vee22}.
+From a numerical perspective,
+it is straightforward to include
+random perturbations in the particle shape and
+boundary condition that mimick interfacial properties
+found in lab conditions\cite{Bradley2016,Bradley2017}.
 
@@
 \label{sec:appendix}
-To prove \eqref{eq:normal_deriv}, let 
+Our calculation of the free energy $F$ relied on 
+converting the body integral in \eqref{eq:free_energy}
+into the surface
+integral in \eqref{eq:free_energy2}
+involving only single layer potentials and
+tangential derivatives. 
+This section supplies a proof of identity
+\eqref{eq:normal_deriv} used in this conversion.
+Let 
 \begin{equation}

### 2022-08-02 doc/PRF2022/PRF_main.tex

@@
 More generally the surface of a Janus particle may have a spatial distribution of hydrophobicity/hydrophilicity.
-In a viscous solvent, in a quiescent flow, Janus particles often self-assemble into
-structures with tunable functions for biomedical engineering
+In the absence of any imposed flow, Janus particles often self-assemble into
+structures in a viscous solvent with tunable functions for biomedical engineering
 applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
@@
 
-Dynamic flows offer yet another dimension of control that emerge naturally
-from the interactions between particles and fluid in colloidal
-matter~\cite{Brandner2019,RevModPhys.93.025008}. Active colloidal
-systems show nonequilibrium self-organization with complexity rivaling
-that of biological systems such as living cells, bacterial baths, and
+When driven by an external flow, 
+dynamic rearrangement of JPs emerges naturally from the interactions between particles and fluid in colloidal
+matter~\cite{Brandner2019,RevModPhys.93.025008}. Such colloidal hydrodynamics belongs to a wide class of
+nonequilibrium self-organization in physics, often with complexity and features similar to that of 
+biological systems such as living cells, bacterial baths, and
 animal flocks~\cite{CollardGrosjeanVandewalle2020,Vutukuri2020}. A

### 2022-08-02 doc/PRF2022/PRF_main.tex
yny

@@
 %particle to be 
-may be partly hydrophilic and hydrophobic (polar and non-polar).
+are partly hydrophilic and hydrophobic (polar and non-polar).
 More generally the surface of a Janus particle may have a spatial distribution of hydrophobicity/hydrophilicity.
@@
 The many-body hydrodynamics of amphiphilic Janus particles assembled as
-vesicles suspended in a viscous fluid (at zero Reynolds number) has
+vesicles suspended in a viscous fluid in the inertialess regime (zero Reynolds number) has
 been studied using boundary integral numerical
@@
 
-In this work, we take advantage of the flexibility of the model to
-examine the effects of boundary condition on JP surfaces that could be
-controlled based on the chemicals used in the experiments, for example.
-We show that a simple tuning of the hydrophobic distribution leads to
-multilamellar and striated structures. Here, less is understood about the
-flow-structure interactions and we investigate the deformation of these
-novel materials in background flows and map out their collective
+In this work, we take advantage of the flexibility of the HAP model to
+examine the effects of varying hydrophobicity/hydrophilicity on JP surfaces.
+Such variation of the boundary condition on JP surfaces may be realized in the experiments by using
+chemicals to adjust the polarity of the viscous solvent, for example ({\bf references needed here}).
+We show that a simple tuning of the hydrophobic distribution leads to transitions from unilamellar to
+multilamellar or striated structures. 
+Focusing on the fluid-structure interactions that correspond to such transitions, 
+we investigate the deformation of these
+novel structures in background flows and map out their collective
 behavior away from equilibrium.

### 2022-08-02 doc/PRF2022/PRF_main.tex
fixed missing period

@@
 We show that a simple tuning of the hydrophobic distribution leads to transitions from unilamellar to
-multilamellar or striated structures. 
+multilamellar or striated bilayer assembly (structures) of JPs. 
 Focusing on the fluid-structure interactions that correspond to such transitions, 
@@
 -\tt_{\xx}^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\tt_{\yy}
-+ \Delta_{\yy}G(\zz-\yy) \tt_{\xx}\cdot \tt_{\yy}
++ \Delta_{\yy}G(\zz-\yy) \tt_{\xx}\cdot \tt_{\yy}.
 \]

### 2022-08-02 doc/PRF2022/PRF_main.tex
latest changes; added figure 2

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Boundary integral representation and time stepping}
+\subsection{Boundary integral representations}
 We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
@@
 surface.  Then, the boundary condition (BC) can be classified into three
-categories: $\min g = 0$, $\min g >0$, and $\min g <0$.  These three
+categories: $\min g(\xx) = 0$, $\min g(\xx) >0$, and $\min g(\xx) <0$
+where the extrema are taken for $\xx \in \Gamma_i$.  These three
 categories correspond to three characteristic values of $b$ in
@@
   \vspace{-20pt}
-  \todo[inline]{We should capitalize bc is that it reads BC like we have
-  in the text.}
   \caption{\label{fig:relax_energy}
@@
 Here $\bar \theta$ is a circular mean defined as the orientation of the
-largest eigenvalue of $\dd_1\dd_1^\top + \cdots +
+principal eigenvector of the matrix $\dd_1\dd_1^\top + \cdots +
 \dd_{N_b}\dd_{N_b}^\top$. A value $S_2(t) = 1$ indicates that all
@@
   the configurations with streamlines of a vesicle is in a TG flow at
-  $t=1 \upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the enclosed
-  area $A_0/A$ calculated from the bilayer midplane decreases over time
-  and the total length (shown in the inset) measured from the midplane
-  remains nearly constant with small magnitude of oscillations.}
+  $t=1$ $\upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the relative enclosed
+  area $A/A_0$ calculated from the bilayer midplane decreases over time.
+  The inset shows the relative length $l/l_0$ 
+  which remains nearly constant with small magnitude of oscillations
+  The inset and main panel have the same  horizontal axis.}
 \end{figure}

### 2022-08-03 doc/PRF2022/PRF_main.tex
worked on final points

@@
 
+%\usepackage{showkeys}
 \usepackage{todonotes}
@@
   -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
+\label{eq:stokesMass}
   \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
+\label{eq:stokesFarfield}
   \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
@@
 
-Once \eqref{eq:stokes}--\eqref{eq:force} have been solved, the
+To perform a single time step, we first solve for the HAP by
+solving~\eqref{eq:SL}--\eqref{eq:SLbc}, and then compute the force and
+torque~\eqref{eq:FandTdef}. Then the Stokes
+equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield} are solved, and
+the force-free and torque-free conditions are used to compute the rigid
+body motion~\eqref{eq:rigid-vel}.
+Once~\eqref{eq:stokes}--\eqref{eq:force} have been solved, the
 velocities $(\vv_i, \omega_i)$ from~\eqref{eq:rigid-vel} update the
@@
 for $\xx \in \Gamma_i$ and $i = 1,\ldots,N_b$.
+Equation~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} does have a
+unique solution, but we note that alternative full-rank layer potential
+representations for rigid body motions are possible~\cite{rac-gre2016,
+cor-gre-rac-vee2017}.
 
@@
   the configurations with streamlines of a vesicle is in a TG flow at
-  $t=1$ $\upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the relative enclosed
-  area $A/A_0$ calculated from the bilayer midplane decreases over time.
-  The inset shows the relative length $l/l_0$ 
-  which remains nearly constant with small magnitude of oscillations
-  The inset and main panel have the same  horizontal axis.}
+  $t=1$ $\upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the
+  relative enclosed area $A/A_0$ calculated from the bilayer midplane
+  decreases over time. The inset shows the relative length $l/l_0$ which
+  remains nearly constant with small magnitude of oscillations. The
+  inset and main panel have the same horizontal axis.}
 \end{figure}

### 2022-08-03 doc/PRF2022/PRF_main.tex
yny

@@
 to shed a small piece of bilayer, similar to the asymmetric breakup of a
-viscous drop \cite{} \todo[inline]{missing citation}. In
-Figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two
+viscous drop in confinement \cite{DuFuZhuMaLi2016_AICHEJ}.
+%\todo[inline]{missing citation}. 
+In Figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two
 separate, nearly equal bilayers, similar to the symmetric drop breakup
-under a linear shear flow \cite{} \todo[inline]{missing citation}.
+under a linear shear flow \cite{Stone1994_ARFM}. 
+%\todo[inline]{missing citation}.
 %%

### 2022-08-03 doc/PRF2022/Supplementary.tex
adding supplementary.tex

\thispagestyle{empty}

\newpage
{\Large \bf

  \noindent Supplementary Material\\

  \noindent 
  Collective behavior of Janus Particles  Suspended in a Viscous Fluid}\\

\noindent 
Szu-Pei Fu$^{1,*},$ 
Rolf Ryham$^{2},$ 
Bryan Quaife$^{3},$ 
Y.-N. Young$^{4},$
\\

\noindent
$^{1}$Department of Mathematics, Trinity College, Hartford, Connecticut 06106, USA

\noindent
$^{2}$Department of Mathematics, Fordham University,  Bronx, NY, USA

\noindent
$^{3}$Department of Scientific Computing, Florida State University, Tallahassee, Florida 32306, USA

\noindent
$^{4}$Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, NJ  07102 USA
\\

\noindent $^*$Corresponding author. Address: Department of Mathematics, Trinity College, 
300 Summit Street, Hartford, CT 06106. email: \text{peter.fu@trincoll.edu}

\setcounter{page}{1}

\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}

\setcounter{equation}{0}
\renewcommand{\theequation}{S\arabic{equation}}

\setcounter{section}{0}
\renewcommand{\thesection}{S\arabic{section}}

%-----ellipse repulsion--------------------

%\Phi_{\mathrm{rep}}

\sloppy
\section{Movie Captions}\mbox{} \\

\noindent
{\bf Movie S1. Relaxation} 
There are 60 circular particles with radius 0.5 that are initially confined in a square box.
 The simulation results show the relaxation with the use of all three boundary condition

%form a self-enclosed bilayer structure. The simulation result shows the vesicle relaxation and the fluid pressure inside the JP vesicle decreases to 0 after a period of time.
%The color field from blue to red shows the magnitude of fluid pressure and the range from 0 to 0.1. All dark blue dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
%This movies includes a total 5000 time steps where the time step is $\Delta t=0.2$.\\

\noindent
{\bf Movie S2. Structures in a Shear Flow without Ruptures} 
%We adopt the relaxed configuration and place the JP vesicle in the shear flow. The simulation result shows a tank-treading motion when the shear rate is $\chi=0.005$.
%The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
%This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\

\noindent
{\bf Movie S3. Structures in a Shear Flow with Ruptures} 
%Using the same setup demonstrated in Movie S2, we show the simulation result for 
%inter-monolayer slip by tracking a pair of particles (blue and yellow). After $t=4000$, 
%the yellow particle in the outer leaflet surpasses the blue particle in the inner leaflet by the distance about 1 particle diameter.
%This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\

\noindent
{\bf Movie S4. Structures in a Taylor-Green Flow without Ruptures} 
%The numerical results show that the JP vesicle starts to have rupture phase at the shear rate $\chi=0.0655$. The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion. This movies includes a total 3000 time steps where the time step is $\Delta t=0.2$.\\

\noindent
{\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
%There are two relaxed JP vesicles suspended in a shear flow. The two centroids are at coordinates $(-25,0)$ and $(25,0)$ in nm. The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion. This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\

### 2022-08-03 doc/PRF2022/Supplementary.tex
updated Supplementary.tex

@@
 There are 60 circular particles with radius 0.5 that are initially confined in a square box.
- The simulation results show the relaxation with the use of all three boundary condition
-
-%form a self-enclosed bilayer structure. The simulation result shows the vesicle relaxation and the fluid pressure inside the JP vesicle decreases to 0 after a period of time.
-%The color field from blue to red shows the magnitude of fluid pressure and the range from 0 to 0.1.
-All dark blue dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-%This movies includes a total 5000 time steps where the time step is $\Delta t=0.2$.\\
+The simulation results show the relaxation with the use of all three boundary conditions.
+The color on the boundary from blue to red shows the magnitude of the boundary data and 
+the range is from $\min g(\xx)$ to $\max g(\xx)$. All final configurations are adopted in 
+simulations with hydrodynamic flows. The time step of all simulations is $\Delta t=0.2$.\\
 
@@
 {\bf Movie S2. Structures in a Shear Flow without Ruptures} 
-%We adopt the relaxed configuration and place the JP vesicle in the shear flow. The simulation result shows a tank-treading motion when the shear rate is $\chi=0.005$.
-%The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1.
-All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-%This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\
+We adopt the relaxed configurations and place the JP structures in the shear flow. 
+In this movie, there is no apparent structural rupture in each case. For the choices of the shear rate, we pick: $\dot\gamma = 0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, 
+$\dot\gamma = 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated configurations.
+The time step of all simulations is $\Delta t=0.2$.\\
 
 \noindent
-{\bf Movie S3. Structures in a Shear Flow with Ruptures} 
-%Using the same setup demonstrated in Movie S2, we show the simulation result for 
-%inter-monolayer slip by tracking a pair of particles (blue and yellow). After $t=4000$, 
-%the yellow particle in the outer leaflet surpasses the blue particle in the inner leaflet by the distance about 1 particle diameter.
-%This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\
+{\bf Movie S3. Structures in a Taylor-Green Flow without Ruptures} 
+We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow. 
+In this movie, there is no apparent structural rupture in each case. For the choices of the flow strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the bilayer, 
+$V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$ for the striated configurations.
+The time step of all simulations is $\Delta t=0.2$.\\
 
 \noindent
-{\bf Movie S4. Structures in a Taylor-Green Flow without Ruptures} 
-%The numerical results show that the JP vesicle starts to have rupture phase at the shear rate $\chi=0.0655$.
-The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1.
-All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-This movies includes a total 3000 time steps where the time step is $\Delta t=0.2$.\\
+{\bf Movie S4. Structures in a Shear Flow with Ruptures} 
+We adopt the relaxed configurations and place the JP structures in the shear flow. 
+In this movie, some clear structural ruptures occur in each case. For the choices of the shear rate, we pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ for the bilayer, 
+$\dot\gamma = 0.15$ for the multi-lamellar, and $\dot\gamma = 0.15$ for the striated configurations.
+The time step of all simulations is $\Delta t=0.2$.
+In order to observe the structure behaviors at later time, we stabilize the frame by tracking the center of mass position of all JP. \\
 
@@
 {\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
-%There are two relaxed JP vesicles suspended in a shear flow.
-The two centroids are at coordinates $(-25,0)$ and $(25,0)$ in nm.
-The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1.
-All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
-This movies includes a total 20000 time steps where the time step is $\Delta t=0.2$.\\
+We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow. 
+In this movie, some clear structural ruptures occur in each case. For the choices of the flow strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the bilayer, 
+$V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the striated configurations.
+The time step of all simulations is $\Delta t=0.2$.\\

### 2022-08-03 doc/PRF2022/PRF_main.tex
adding supplementary.tex
why these parameters?; Intro to section III;

@@
 \sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
-\infty$. The parameter $\rho_0$ is an ``effective" distance between
+\infty$. The parameter $\rho_0$ is an ``effective" repulsion distance between
 particle surfaces, below which the steric repulsion between a pair of
@@
 velocities $(\vv_i, \omega_i)$ from~\eqref{eq:rigid-vel} update the
-particle positions and orientations.  We use the parameters $\mu = 1$
-mPa s, $\gamma = 4$ pN nm$^{-1}$, $\rho = 5$ nm, $c = 1.25$ nm, $M = 2$
-pN, and $\rho_0 = 0.5$ nm.  These values give a characteristic time $1$
-ns and characteristic length $1$ nm.
+particle positions and orientations.
 
@@
 
-\section{Equilibrium configurations}
-\subsection{Boundary conditions and normalization}
-We consider boundary conditions of the form
+\section{Model parameters}
+The interactions generated by the HAP-mobility problem formulation
+\eqref{eq:stokes}--\eqref{eq:force}
+lead to particle self-assembly for a broad range of parameters and
+boundary conditions.  Generally speaking, the effective distance of the
+hydrophobic interaction is set by the screening length $\rho$.
+Smaller values of the repulsion distance $\rho_0$ decrease the distance
+where attraction and repulsion are in balance and lead to more compact
+particle assemblies. 
+The rate of self assembly is proportional to the interfacial tension $\gamma$,
+and inversely proportional to solvent viscosity $\mu$; it is
+roughly inversely proportional to screening length $\rho.$
+
+To give our system physical units, we set the model parameters
+using phospholipids as a characteristic amphiphile in water \cite{Boal}.
+For solvent viscosity, we use $\mu = 1$ mPa s for the viscosity
+of water at room temperature.
+Pure lipid components give a range
+of interfacial tensions $0.7$ -- $5.3$ pN nm$^{-1}$
+~\cite{KUZMIN2005, Petelska2012,Jackson2016,GarciaSaez}.
+As in our previous works\cite{Fu20,Fu2022_JFM},
+we use $\gamma=4.1$ pN nm$^{-1}$ since this value gave
+good agreement with elastic moduli of lipid bilayers.
+The particle radius $c = 1.25$ nm
+gives a diameter representative of phospholipid length \cite{Boal},
+and the screening length $\rho = 5$ nm
+derives from experimental force-distance measurements of hydrophobic
+attraction \cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}.
+Based on empirical studies, the repulsion modulus $M = 2$ pN
+and repulsion distance $\rho_0 = 0.5$ nm give an interparticle
+distance around one particle radius.  This 
+ensures the accuracy of the boundary integral representations
+\eqref{eq:SL_BIE} and \eqref{eq:velocity}
+without having to employ overly aggresive mesh refinement. 
+Altogether, the above parameter set gives
+a characteristic time $1$
+ns and characteristic length $1$ nm.
+
+\subsection{Boundary conditions and equilibrium configurations}
+The boundary condition $g(\xx)$ in
+\eqref{eq:SLbc} defines the spatial distribution of
+hydrophobicity and hydrophilicity.  On a hydrophobic region of the
+particle surface, representing a hydrocarbon-water interface,
+for example, $g(\xx)$ takes relatively large values.
+On an apolar, hydrophilic region, $g(\xx)$ is close to zero.
+
+In the present work, we consider boundary conditions of the form
 \begin{align}
@@
 
+\input{Supplementary}
+
 \end{document}

### 2022-08-03 doc/PRF2022/PRF_main.tex
yny

@@
 % \affiliation can be followed by \email, \homepage, \thanks as well.
-\author{Szu-Pei Fu}
-\email{peter.fu@trincoll.edu}
-\affiliation{Department of Mathematics, Trinity College, Hartford, Connecticut 06106, USA}
+\author{Szu-Pei Fu$^{1}$, Rolf Ryham$^{2}$, Bryan Quaife$^{3}$ and Y.-N. Young$^{4}$}
+%\email{peter.fu@trincoll.edu}
+\affiliation{$^1$Department of Mathematics, Trinity College, Hartford, Connecticut 06106, USA\\
+$^2$Department of Mathematics, Fordham University, Bronx, New York 10458, USA \\
+$^3$Department of Scientific Computing, Florida State University, Tallahassee, Florida 32306, USA\\
+$^4$Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, New Jersey 07102, USA}
 
@@
 %\altaffiliation{}
-\author{Rolf Ryham}
-\email{rryham@fordham.edu}
-\affiliation{Department of Mathematics, Fordham University, Bronx, New York 10458, USA}
-
-\author{Bryan Quaife}
-\email{bquaife@fsu.edu}
- \affiliation{Department of Scientific Computing, Florida State University, Tallahassee, Florida 32306, USA}
- \author{Y.-N. Young}
- \email{yyoung@njit.edu}
- \affiliation{Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, New Jersey 07102, USA
- }
+%\author{Rolf Ryham}
+%\email{rryham@fordham.edu}
+%\affiliation{Department of Mathematics, Fordham University, Bronx, New York 10458, USA}
+%
+%\author{Bryan Quaife}
+%\email{bquaife@fsu.edu}
+ %\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, Florida 32306, USA}
+ %\author{Y.-N. Young}
+ %\email{yyoung@njit.edu}
+ %\affiliation{Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, New Jersey 07102, USA}
 

### 2022-08-04 doc/PRF2022/PRF_main.tex
new Fig 0, updated text, updated Supplementary.tex

@@
 
-\begin{figure}[h!]
-\begin{center}
-  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
-  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
-  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
-  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
-\end{center}
-\begin{caption}{\label{fig:relax}
-  Panel (a) shows $N_b = 198$ particles confined to a square with random
-  positions and orientations and the inset shows a $N_b=60$ particles
-  configuration. The particles self-assemble into distinct
-  configurations, depending on the boundary
-  condition~\eqref{eq:bc-type}. Panel (b) is for $b=1$ and the boundary
-  condition mimics that of an amphiphilic particle giving bilayer
-  structures. Panel (c) is for $b=2$ which gives rise to a
-  multilamellar configuration. In panel (d), the case $b = 0$ is for a
-  water structure with positive/negative charge. The false color maps
-  use blue for $u < 0$, green for $u = 0$, and yellow then red for $u >
-  0$. The inset in panels (b)--(d) are configurations using $N_b=60$ and
-  share the same color map as the main panels.}
-\end{caption}
-\end{figure}
-
-\section{Model parameters}
+\section{Model parameters and boundary conditions}
 The interactions generated by the HAP-mobility problem formulation
@@
 
+\begin{figure}[h!]
+\begin{center}
+  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
+\end{center}
+\begin{caption}{\label{fig:boundary_conditions}
+    The leftmost diagram illustrates the particle
+    $\Gamma_i$ with center $\aa_i$, radius $c$, and director $\dd$,
+    along with the angle $\alpha$ used to define $g(\xx)$ in \eqref{eq:bc-type}.
+    The three righ plots show $g(\xx)$ (black curve) for BC (i), (ii), and (iii)
+    when $\dd = (1,0)$. The surfaces are the respective solutions
+    $u(\xx)$ of \eqref{eq:SL} for a single, isolated particle.  
+  }
+\end{caption}
+\end{figure}
+
 \subsection{Boundary conditions and equilibrium configurations}
@@
 for $b = 0$.
+
+\begin{figure}[h!]
+\begin{center}
+  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
+  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
+  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
+  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
+\end{center}
+\begin{caption}{\label{fig:relax}
+  Panel (a) shows $N_b = 198$ particles confined to a square with random
+  positions and orientations and the inset shows a $N_b=60$ particles
+  configuration. The particles self-assemble into distinct
+  configurations, depending on the boundary
+  condition~\eqref{eq:bc-type}. Panel (b) is for $b=1$ and the boundary
+  condition mimics that of an amphiphilic particle giving bilayer
+  structures. Panel (c) is for $b=2$ which gives rise to a
+  multilamellar configuration. In panel (d), the case $b = 0$ is for a
+  water structure with positive/negative charge. The false color maps
+  use blue for $u < 0$, green for $u = 0$, and yellow then red for $u >
+  0$. The inset in panels (b)--(d) are configurations using $N_b=60$ and
+  share the same color map as the main panels.}
+\end{caption}
+\end{figure}
 
@@
 where $\bar \theta_i$ is the circular mean restricted to particles
-indexed by $j$ with $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle
+indexed by $j$ with $\|\aa_i - \aa_j\| < 4c$.
+This cutoff distance was chosen empirically
+so that the average includes nearest neighbors
+but excludes next nearest neighbors.
+In practice, if a particle
 is isolated and has no neighbors within a distance $4c$, then we exclude
@@
 $\upmu$s of the bilayer for different shear rates $\dot\gamma=
-0.05,0.075,0.01$. The dynamics of the bilayer can be found in the
-supplementary movies, which show that the initial pieces of bilayers
+0.05,0.075,0.01$. The dynamics of the bilayer can be found in
+Supplementary Movie S2, which shows
+that the initial pieces of bilayers
 merge and form a worm-like shape under a linear shear flow. At a low
@@
 under a linear shear flow \cite{Stone1994_ARFM}. 
+Refer to Supplementary Movie S4.
+
 %\todo[inline]{missing citation}.
@@
 alternate local equilibrium with less free energy and greater
-orientational order.  Note that the free energy $F$ in
+orientational order  (Supplementary Movie S2).  Note that the free energy $F$ in
 Figure~\ref{fig:BC1_shear}(d) has the unit of force ($\mathrm{k_BT}$/nm $\approx$ 4.114 pN)
@@
 and tank-treading motion, as shown in
-Figure~\ref{fig:Ves_shear}(a)--(c).
+Figure~\ref{fig:Ves_shear}(a)--(c)
+and Supplementary Movie S2.
 %
@@
 There is no appreciable pattern in the deformation for the
-multicomponent bilayer case in TG flow. Figure~\ref{fig:BC1_TG}(a)--(c)
+multicomponent bilayer case in TG flow
+(Supplementary Movie S3, right panel).
+Figure~\ref{fig:BC1_TG}(a)--(c)
 are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s. At all
@@
 Patterns in the deformation, however, do emerge in the case of a vesicle
-in TG flow. For a vesicle in a Taylor-Green flow,
+in TG flow (Supplementary Movie S3, left panel). For a vesicle in a Taylor-Green flow,
 Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\ \upmu$s
@@
 (Figure~\ref{fig:ves_TG}(d)--(f)). The vesicle disintegrates for $V_0 =
-0.2$, leading to a jump in energy, drop in order, and increase in
+0.2$ (Supplementary Movie S5, left panel), leading to a jump in energy, drop in order, and increase in
 strain, suggesting that the vesicle has a critical TG flow strength in
@@
 0.25, 0.3$, respectively.
+The BC (ii) and BC (iii) in shear flow cases are visualized in
+the latter half of 
+Supplementary Movie S2 (low shear rate) and 
+Supplementary Movie S4 (high shear rate), respectively.
+The low and high flow rates for TG flow are shown in
+the latter half of
+Supplementary Movie S3 and 
+Supplementary Movie S5, respectively.
 
@@
 decrease the excess area of the system by subjecting the suspension to a
-moderate shear flow. Not all background flows produce this
+moderate shear flow (Supplementary Movie S2, right panel).
+Not all background flows produce this
 ``organizing'' effect, as it is not observed in the TG background flow
-case (Figure~\ref{fig:BC1_TG}). \citet{PhysRevLett.128.256102} have
+case (Figure~\ref{fig:BC1_TG}, Supplementary Movie S3, right panel).
+\citet{PhysRevLett.128.256102} have
 shown how to drive particle clusters into arbitrary target shapes by

### 2022-08-04 doc/PRF2022/PRF_main.tex
fixed typo

@@
 solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
-zeroth-order modified Bessel function of the first kind, $\nnu_\yy$ is
+zeroth-order modified Bessel function of the second kind, $\nnu_\yy$ is
 the unit outward normal at $\yy$, and $\sigma$ is a scalar-valued

### 2022-08-04 doc/PRF2022/PRF_main.tex
yny

--- 2022-08-03 doc/PRF2022/PRF_main.tex
@@
 In this work, we employ the newly developed JP model using BIEs ~\cite{Fu20, Fu2022_JFM} 
-and tune the boundary conditions with energy normalization to study the dynamics of 
-amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs.
+and tune the boundary conditions with energy normalization to study the  collective dynamics of 
+amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under various flowing conditions (quiescent, linear shear flow, and Taylor-Green flow).
+Three quantities are computed to characterize the dynamics of the collective configurations of JPs: Free energy $F$, strain parameter $E$ and 
+scalar order parameter $S_2$.
+
 To overcome the well-known 
@@
 We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.
+B.Q. acknowledges support from the Simons Foundation, Mathematics and Physical Sciences-Collaboration Grants for Mathematicians, Award No. 527139.
+Y.-N.Y. acknowledges support from NSF (Grants No. DMS 1614863 and No. DMS 195160) and Flatiron Institute, part of Simons Foundation.
 

### 2022-08-04 doc/PRF2022/Supplementary.tex

@@
 {\bf Movie S1. Relaxation} 
-There are 60 circular particles with radius 0.5 that are initially confined in a square box.
+There are 60 circular particles with radius 1.25 nm that are initially confined in a square box.
 The simulation results show the relaxation with the use of all three boundary conditions.
-The color on the boundary from blue to red shows the magnitude of the boundary data and 
-the range is from $\min g(\xx)$ to $\max g(\xx)$. All final configurations are adopted in 
-simulations with hydrodynamic flows. The time step of all simulations is $\Delta t=0.2$.\\
+The color on the boundary from blue to red
+is for $\min g(\xx)$ to $\max g(\xx)$.
+All final configurations are adopted in 
+simulations with hydrodynamic flows.
+The time step of all simulations is $\Delta t=0.2$.\\
 
@@
 We adopt the relaxed configurations and place the JP structures in the shear flow. 
-In this movie, there is no apparent structural rupture in each case. For the choices of the shear rate, we pick: $\dot\gamma = 0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, 
+For the choices of the shear rate, we pick: $\dot\gamma = 0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, 
 $\dot\gamma = 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated configurations.
-The time step of all simulations is $\Delta t=0.2$.\\
+The vesicle case undergoes tank treading
+whereas the initially disordered BC (i) case
+increases orientational order.  The multilamellar
+assemply behaves a rigid body,
+and the striated configuration moreso.
+There are no ruptures that occur in this movie.\\
 
@@
 {\bf Movie S3. Structures in a Taylor-Green Flow without Ruptures} 
-We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow. 
-In this movie, there is no apparent structural rupture in each case. For the choices of the flow strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the bilayer, 
+We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow
+at relatively low flow rates.
+For the choices of the flow strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the
+disordered bilayer, 
 $V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$ for the striated configurations.
-The time step of all simulations is $\Delta t=0.2$.\\
+The vesicle stays inact, whereas the dissordered bilayer is pulled apart.
+Like in Supplementary Movie S2, the striated assembly is basically rigid.\\
 
@@
 {\bf Movie S4. Structures in a Shear Flow with Ruptures} 
-We adopt the relaxed configurations and place the JP structures in the shear flow. 
-In this movie, some clear structural ruptures occur in each case. For the choices of the shear rate, we pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ for the bilayer, 
+We adopt the relaxed configurations and place the JP structures in the shear flow
+at a higher shear rate. 
+For the choices of the shear rate, we pick: $\dot\gamma = 0.075$ for the
+vesicle, $\dot\gamma = 0.1$ for the bilayer, 
 $\dot\gamma = 0.15$ for the multi-lamellar, and $\dot\gamma = 0.15$ for the striated configurations.
 The time step of all simulations is $\Delta t=0.2$.
-In order to observe the structure behaviors at later time, we stabilize the frame by tracking the center of mass position of all JP. \\
+In this movie, some clear structural ruptures occur in each case.
+In order to observe the structure behaviors at later time,
+we stabilize the frame by tracking the center of mass position of all JP. \\
 
@@
 {\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
-We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow. 
-In this movie, some clear structural ruptures occur in each case. For the choices of the flow strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the bilayer, 
+We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow
+for high flow rates. 
+In this movie, some clear structural ruptures occur in each case.
+For the choices of the flow strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the bilayer, 
 $V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the striated configurations.
-The time step of all simulations is $\Delta t=0.2$.\\
+In all cases, there is significant reduction in the orientational order of the assemblies.
+While the BC (i) cases are broken into several pieces, the main body of the
+BC (ii) and BC (iii) assemblies is not pulled apart by the background flow. 
+\\

### 2022-08-04 doc/PRF2022/PRF_main.tex
yny

@@
 and tune the boundary conditions with energy normalization to study the  collective dynamics of 
-amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under various flowing conditions (quiescent, linear shear flow, and Taylor-Green flow).
+amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under various flowing conditions (quiescent flow, linear shear flow, and Taylor-Green flow).
 Three quantities are computed to characterize the dynamics of the collective configurations of JPs: Free energy $F$, strain parameter $E$ and 
-scalar order parameter $S_2$.
-
-To overcome the well-known 
-obstacle for numerical implementations in the free energy $F$ where the gradient of 
-solution to the screened Laplace equation involves hyper-singularities, we derive the normal 
-derivative \eqref{eq:normal_deriv} in terms of single layer potential $\SSS$.
-
-Simulations include the self-assembly behaviors when the flow is absent and
-when JP are subject to shear and TG background flows with various 
-flow strengths. The free energy profiles demonstrate that the relaxation process for 
+scalar order parameter $S_2$. In this numerical study we quantify how the collective hydrodynamics of JPs is affected by an external flow. 
+Under a given flow, we use the three measures of deformations to quantify the differences in the collective dynamics between the three types of JPs.
+These results, summarized below, may provide some general insight into the dynamic control of active particles in a viscous suspension.
+
+Within the framework of boundary integral equations, we derive a convenient expression for computing the free energy using the single layer potential (see 
+equation~\eqref{eq:normal_deriv}). In a quiescent flow, the free energy profiles demonstrate that the relaxation process for 
 particles confined in a certain size of box is independent of number of particles 
-($N_b$). However, the final configurations highly depend on the initial particle 
+($N_b$). However, we did find the final configurations to depend on the initial distribution of particle 
 directors $\dd_i$. Therefore, multiple patterns or local energy minimum states may 
@@
 
-We track the total free energy, the orientational order parameter,
-and the strain parameter to comprehensively summarize and classify the effective properties
-of all three materials. 
-Observations have shown that multi-lamella and the striated structures under a relatively 
-weak linear shear flow behave like a rigid body with minimal deformation. The effective 
+Under a relatively weak linear shear flow, the amphiphilic (BC (i)) JPs behave as a unilamellar vesicle that elongates and tank-treads.
+For the multi-lamella (BC (ii)) and the striated (BC (iii)) structures  the assembly of JPs behaves like a rigid body with minimal deformation. The effective 
 viscosity of the material gives a quantitative validation to support the statement. High 
@@
 apart and undergo major topological changes. As expected in all case studies,
-free energy, orientationl order, and strain combined 
+free energy, scalar order parameter, and strain combined 
 are good topological indicators.
 
-Under a TG flow, we examine the same measures and simulate all structures with 
-the same criteria as ones in shear flow cases. In addition, for JP vesicle under a 
-TG flow, we compare the results when the size of cell is varied and a nonmonotonic 
-trend in reduced area with respect to the cell size arises. One finding to be noted is 
-that the TG flow with specified parameters can effectively control the structure shapes 
-such as a square vesicle or a polygonal shape.
-
-The results reported here provide an inroad computational framework for colloidal sciences. 
-The present study also helps us to understand more rheological properties of industrially 
-produced JP.
-This study can be extended to three dimensional systems 
-and it has been included in our future goals\cite{kohl-cor-che-vee22}.
+Under a Taylor-Green flow,  we find that the amphiphilic JPs to be most interesting, exhibiting different vesicle shapes depending on the ratio of the size of the
+TG flow to the vesicle size. These results show that we can control the shape of the vesicle to be a square shape or a polygonal shape by adjusting the size of
+the cell in TG flow.
+On the other hand, the assembly of multi-lamella JPs and the striated JPs behaves more or less as a rigid body with connected subdomains, with the number of subdomains increasing with stronger strength of the TG flow.
+
+The results reported here provide an inroad modeling framework for hydrodynamics of active colloids. 
+The present study also helps us understand the rheology of JP oligomers that may be realized in the experiments.
+We are now extending this study to three dimensional systems with more realistic features such as size distributions of JPs
+and thermal fluctuations.
+%
+ %it has been included in our future goals\cite{kohl-cor-che-vee22}.
 From a numerical perspective,

### 2022-08-04 doc/PRF2022/PRF_main.tex
yny

@@
 shear-rate cases provide a range for critical shear rates where the structures break 
-apart and undergo major topological changes. As expected in all case studies,
-free energy, scalar order parameter, and strain combined 
-are good topological indicators.
+apart and undergo major topological changes. 
+We further showed that
+free energy, scalar order parameter, and strain are effective measures to quantitatively capture the dynamics of the JP oligomers under a linear shear flow.
 

### 2022-08-05 doc/PRF2022/PRF_main.tex

@@
 scalar order parameter $S_2$. In this numerical study we quantify how the collective hydrodynamics of JPs is affected by an external flow. 
-Under a given flow, we use the three measures of deformations to quantify the differences in the collective dynamics between the three types of JPs.
+Under a given flow, we use these three measures of deformations to quantify the differences in the collective dynamics between the three types of JPs.
 These results, summarized below, may provide some general insight into the dynamic control of active particles in a viscous suspension.
@@
 
-Under a relatively weak linear shear flow, the amphiphilic (BC (i)) JPs behave as a unilamellar vesicle that elongates and tank-treads.
+Under a relatively weak linear shear flow, the amphiphilic (BC (i)) JPs behave as a unilamellar vesicle that elongates and tank-treads, with the scalar order 
+parameter increasing over time.
 For the multi-lamella (BC (ii)) and the striated (BC (iii)) structures  the assembly of JPs behaves like a rigid body with minimal deformation. The effective 
@@
 On the other hand, the assembly of multi-lamella JPs and the striated JPs behaves more or less as a rigid body with connected subdomains, with the number of subdomains increasing with stronger strength of the TG flow.
+Overall, we found that the multilamellar (BC (ii)) JPs oligomers behave as a shear-thinning fluid, while the striated (BC (iii)) JPs oligomers possess a yield stress.
 

### 2022-08-05 doc/PRF2022/PRF_main.tex
added refs to intro; updated references.bib

@@
 \begin{abstract}
-%<<<<<<< HEAD
-%Active colloidal systems with non-equilibrium self-organization is a long-standing challenge in biology. To understand how hydrodynamic flow may be used
-%to actively control self-assembly of Janus particles (JPs),  we use a model recently developed for the many-body hydrodynamics of amphiphilic JPs suspended 
-%in a viscous background flow (JFM, 941, 2022) to investigate how various bilayer structures arise from tuning the hydrophobicity/hydrophilicity of the JPs. 
-%Focusing on three distributions of hydrophobicity we found JPs may assemble into uni-lamella, multi-lamella, and striated structures in a viscous fluid. 
-%Under a linear flow and a Taylor-Green mixing flow,  we use three measures to quantify the collective dynamics of JP particles under a background flow: 
-%(a) Free energy from the hydrophobic interactions between the JPs, (b) an order parameter for the ordering of JPs in terms of alignment of their directors, 
-%and (c) a strain parameter that captures the deformation in the assembly. We found the dynamics of these three measures correlate well with the hydrodynamics 
-%of JPs. These numerical provide insights into dynamic control of non-equilibrium active biological systems with similar self-organization.
-% insert abstract here
-%=======
   Active colloidal systems with non-equilibrium self-organization is a
@@
   many-body hydrodynamics of amphiphilic JPs suspended in a viscous
-  background flow (JFM, 941, 2022). We investigate how various bilayer
-  structures arise from tuning the hydrophobic properties of the
-  JP-solvent interface. Focusing on a simple tuning of the
-  hydrophobicity distribution, we found JPs assembled into uni-lamella,
+  background flow (JFM, 941, 2022). We investigate how various 
+  morphologies arise from tuning the hydrophobic distribution of the
+  JP-solvent interface.  
+  We found JPs assembled into uni-lamella,
   multi-lamella and striated structures. To introduce dynamics, we
@@
   behaves as a shear thinning fluid, and the striated structure
-  possesses a finite yield stress. These numerical result provide
+  possesses a yield stress. These numerical result provide
   insights into dynamic control of non-equilibrium active biological
   systems with similar self-organization.
-%>>>>>>> 4f49b2ee420baba836cbb337c263b33981e1b096
 \end{abstract}
@@
 %\section{\label{}}
-Janus particles are colloids whose surfaces 
-%have different properties. For example, it is common for the surface of a Janus
-%particle to be 
-are partly hydrophilic and hydrophobic (polar and non-polar).
-More generally the surface of a Janus particle may have a spatial distribution of hydrophobicity/hydrophilicity.
-In the absence of any imposed flow, Janus particles often self-assemble into
+Janus particles are colloids combining two dissimilar chemical or
+physical functionalies at their opposite sides\cite{KirillovaMarschelkeSynytska2019}.
+Self-propelling Janus particles, for example, with a permanent biphasic asymmetry,
+have emerged as a rich chemical platform for the exploration of active matter\cite{Meredithetal2022}.
+In the absence of mobility and any imposed flow, Janus particles often self-assemble into
 structures in a viscous solvent with tunable functions for biomedical engineering
 applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
-LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale, Bradley2016}.
+LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale, Bradley2016,Zarzaretal2015,KirillovaMarschelkeSynytska2019}.
 Depending on the interactions between Janus particles (JPs) and the
 surrounding viscous solvent, JPs self-assemble into oligomers of various
-geometries and sizes~\cite{Bradley2017}.
+geometries and sizes~\cite{Bradley2017,KangHonciuc2018,HongCacciutoLuijtenGranick2008}.
 
@@
 dynamic rearrangement of JPs emerges naturally from the interactions between particles and fluid in colloidal
-matter~\cite{Brandner2019,RevModPhys.93.025008}. Such colloidal hydrodynamics belongs to a wide class of
+matter~\cite{RevModPhys.93.025008}.
+Such colloidal hydrodynamics belongs to a wide class of
 nonequilibrium self-organization in physics, often with complexity and features similar to that of 
@@
 
+The surface of a Janus particle may have
+a dissimilar spatial distribution of hydrophobicity\cite{doi:10.1021/la503455h}.
 The many-body hydrodynamics of amphiphilic Janus particles assembled as
@@
 alignment along the extensional direction, tank-treading, and rupture of
-a vesicle under shear flow~\cite{Fu2022_JFM}.
+a vesicle under shear
+flow~\cite{Fu2022_JFM,grandmaison_brancherie_salsac_2021,D2SM00179A,keller_skalak_1982,Finken08,Shaqfeh11}.
+
+Molecular dynamics (MD) and Monte Carlo provide another avenue for
+simulating the interaction between JPs, solvents, and
+substrates\cite{Brandner2019,Baniketal2021,HongCacciutoLuijtenGranick2008,C9NR05885K}.
+These methods often use pair-potentials to describe the
+interaction between JPs, for example by prescribing angle
+dependent forces and torques that bring the
+hydrophobic sides of two amphiphilic JPs into opposition.
+The HAP formulation of the present work also has attractive, long-range forces and torques,
+but they are instead derived from a boundary value problem for the molecular
+structure of water\cite{Ma77, GoHaKo94,ErLjCl89,Lietal05,Israelachvili80}.
+Unlike in MD or Monte Carlo-based simulations,
+the HAP interactions are nonadditive\cite{Fu20}, so that
+the interactions between a pair of JP is affected by the presence of other particles.
 
 In this work, we take advantage of the flexibility of the HAP model to
-examine the effects of varying hydrophobicity/hydrophilicity on JP surfaces.
-Such variation of the boundary condition on JP surfaces may be realized in the experiments by using
-chemicals to adjust the polarity of the viscous solvent, for example ({\bf references needed here}).
+examine the effects of varying the distribution of hydrophobicity on JP surfaces.
+Such variation of the boundary condition on JP surfaces have been realized experimentally
+by using chemicals to adjust the polarity of the viscous solvent, for example
+\cite{Zarzaretal2015,KirillovaMarschelkeSynytska2019,doi:10.1021/la503455h}.
 We show that a simple tuning of the hydrophobic distribution leads to transitions from unilamellar to
-multilamellar or striated bilayer assembly (structures) of JPs. 
+multilamellar or striated superstructures of JPs. 
 Focusing on the fluid-structure interactions that correspond to such transitions, 
@@
 behavior away from equilibrium.
+Looking forward, including other fields like
+electric potential for JPs synthesized with
+charged polymers\cite{HongCacciutoLuijtenGranick2008,doi:10.1021/la503455h,KangHonciuc2018},
+is straightforward within the context of the boundary integral representations\cite{kohl-cor-che-vee22},
+opening further lines of investigation.
 
@@
 for $b = 0$.
+Supplementary Movie S1 shows the self-assembly process for the three cases.
 
@@
 these bilayers form multilamella structures~\cite{C9NR05885K}. The
-number of folds depends primarily on the number of particles.
+number of layers depends primarily on the number of particles.
 Figure~\ref{fig:relax}(c), for example, shows a multilamellar structure
@@
 
-Finally, we use the scalar order parameter for orientational order:
+Finally, we use the scalar order parameter for orientational order\cite{Selinger2016}:
 \begin{equation}
@@
 up to $0.25$ (Figure~\ref{fig:BC3_shear} and Figure~\ref{fig:BC3_TG}).
-Conversely, a $25\%$--$50 \%$ smaller value for $\dot \gamma$ or $V_0$ was
+In contrast, a $25\%$--$50 \%$ smaller value for $\dot \gamma$ or $V_0$ was
 required to observe nonrigid deformations for the BC (i) and BC (ii)
@@
 where a harmonic form describes the repulsive part and an anisotropic
-attractive part describes the hydrophobic interactions.
+attractive part describes the hydrophobic interactions~\cite{HongCacciutoLuijtenGranick2008}.
+We also use a pair potential $P$ in the free energy \eqref{eq:free_energy} for repulsion,
+whereas the long-range, hydrophobic attraction \eqref{eq:FandTdef}
+is nonadditive and comes from domain-dependent variation of
+the water order parameter $u(\xx)$ in the bulk.
 
@@
 
-The results reported here provide an inroad modeling framework for hydrodynamics of active colloids. 
+The results reported here provide an inroad modeling framework for hydrodynamics of active colloids
+\cite{Meredithetal2022,McGlassonBradley2021,Vutukuri2020,Mallory2017}. 
 The present study also helps us understand the rheology of JP oligomers that may be realized in the experiments.
 We are now extending this study to three dimensional systems with more realistic features such as size distributions of JPs
-and thermal fluctuations.
+and thermal fluctuations\cite{kohl-cor-che-vee22}.
 %
@@
 boundary condition that mimick interfacial properties
-found in lab conditions\cite{Bradley2016,Bradley2017}.
+found in lab conditions\cite{Bradley2016,Bradley2017,Zarzaretal2015,doi:10.1021/la503455h}.
 

### 2022-08-05 doc/PRF2022/Supplementary.tex
supplementary material

@@
 Rolf Ryham$^{2},$ 
-Bryan Quaife$^{3},$ 
-Y.-N. Young$^{4},$
+Bryan Quaife$^{3}$ and Y.-N. Young$^{4},$
 \\
@@
 {\bf Movie S1. Relaxation} 
-There are 60 circular particles with radius 1.25 nm that are initially confined in a square box.
-The simulation results show the relaxation with the use of all three boundary conditions.
-The color on the boundary from blue to red
-is for $\min g(\xx)$ to $\max g(\xx)$.
-All final configurations are adopted in 
-simulations with hydrodynamic flows.
-The time step of all simulations is $\Delta t=0.2$.\\
+There are 60 circular particles with radius 1.25~nm that are initially
+confined in a square box. The simulation results show the relaxation
+with each of the three boundary conditions. The time step of all
+simulations is $\Delta t=0.2$. The color on the boundary from blue to
+red is for $\min g(\xx)$ to $\max g(\xx)$. All final configurations are
+adopted in simulations with hydrodynamic flows. \\
 
@@
 {\bf Movie S2. Structures in a Shear Flow without Ruptures} 
-We adopt the relaxed configurations and place the JP structures in the shear flow. 
-For the choices of the shear rate, we pick: $\dot\gamma = 0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, 
-$\dot\gamma = 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated configurations.
-The vesicle case undergoes tank treading
-whereas the initially disordered BC (i) case
-increases orientational order.  The multilamellar
-assemply behaves a rigid body,
-and the striated configuration moreso.
-There are no ruptures that occur in this movie.\\
+We adopt the relaxed configurations and place the JP structures in the
+shear flow. For the choices of the shear rate, we pick: $\dot\gamma =
+0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, $\dot\gamma
+= 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated
+configurations. The vesicle case undergoes tank-treading whereas the
+initially disordered BC (i) case increases orientational order. The
+multilamellar assemply behaves as a rigid body, and the striated
+configuration moreso. No ruptures occur. \\
 
@@
 {\bf Movie S3. Structures in a Taylor-Green Flow without Ruptures} 
-We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow
-at relatively low flow rates.
-For the choices of the flow strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the
-disordered bilayer, 
-$V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$ for the striated configurations.
-The vesicle stays inact, whereas the dissordered bilayer is pulled apart.
-Like in Supplementary Movie S2, the striated assembly is basically rigid.\\
+We adopt the relaxed configurations and place the JP structures in the
+Taylor-Green flow at low flow rates. For the choices of the flow
+strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the
+disordered bilayer, $V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$
+for the striated configurations. The vesicle stays inact, whereas the
+dissordered bilayer is pulled apart. Like in Supplementary Movie S2, the
+striated assembly is basically rigid. \\
 
@@
 {\bf Movie S4. Structures in a Shear Flow with Ruptures} 
-We adopt the relaxed configurations and place the JP structures in the shear flow
-at a higher shear rate. 
-For the choices of the shear rate, we pick: $\dot\gamma = 0.075$ for the
-vesicle, $\dot\gamma = 0.1$ for the bilayer, 
-$\dot\gamma = 0.15$ for the multi-lamellar, and $\dot\gamma = 0.15$ for the striated configurations.
-The time step of all simulations is $\Delta t=0.2$.
-In this movie, some clear structural ruptures occur in each case.
-In order to observe the structure behaviors at later time,
-we stabilize the frame by tracking the center of mass position of all JP. \\
+We adopt the relaxed configurations and place the JP structures in the
+shear flow at a higher shear rate. For the choices of the shear rate, we
+pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ for the
+bilayer, $\dot\gamma = 0.15$ for the multi-lamellar, and $\dot\gamma =
+0.15$ for the striated configurations. The time step of all simulations
+is $\Delta t=0.2$. In this movie, some clear structural ruptures occur
+in each case. In order to observe the structure behaviors at later time,
+we stabilize the frame by tracking the center of mass position of all
+JP. \\
 
@@
 {\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
-We adopt the relaxed configurations and place the JP structures in the Taylor-Green flow
-for high flow rates. 
-In this movie, some clear structural ruptures occur in each case.
-For the choices of the flow strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the bilayer, 
-$V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the striated configurations.
-In all cases, there is significant reduction in the orientational order of the assemblies.
-While the BC (i) cases are broken into several pieces, the main body of the
-BC (ii) and BC (iii) assemblies is not pulled apart by the background flow. 
-\\
+We adopt the relaxed configurations and place the JP structures in the
+Taylor-Green flow at higher flow rates. For the choices of the flow
+strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the
+bilayer, $V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the
+striated configurations. Clear structural ruptures occur in each case.
+In all cases, there is significant reduction in the orientational order
+of the assemblies. While the BC (i) cases are broken into several
+pieces, the main body of the BC (ii) and BC (iii) assemblies are not
+pulled apart by the background flow.

### 2022-08-05 doc/PRF2022/PRF_main.tex

@@
   morphologies arise from tuning the hydrophobic distribution of the
-  JP-solvent interface.  
-  We found JPs assembled into uni-lamella,
+  JP-solvent interface. We find JPs assembled into uni-lamella,
   multi-lamella and striated structures. To introduce dynamics, we
@@
   directors, and (c) strain parameter that captures the deformation in
-  the assembly. We characterized the effective material properties of
-  the JP structures and found that the uni-lamellar structures increases
+  the assembly. We characterize the effective material properties of the
+  JP structures and find that the uni-lamellar structures increases
   orientation order under shear flow, the multilamellar structure
   behaves as a shear thinning fluid, and the striated structure
-  possesses a yield stress. These numerical result provide
-  insights into dynamic control of non-equilibrium active biological
-  systems with similar self-organization.
+  possesses a yield stress. These numerical results provide insights
+  into dynamic control of non-equilibrium active biological systems with
+  similar self-organization.
 \end{abstract}
@@
 Janus particles are colloids combining two dissimilar chemical or
-physical functionalies at their opposite sides\cite{KirillovaMarschelkeSynytska2019}.
-Self-propelling Janus particles, for example, with a permanent biphasic asymmetry,
-have emerged as a rich chemical platform for the exploration of active matter\cite{Meredithetal2022}.
-In the absence of mobility and any imposed flow, Janus particles often self-assemble into
-structures in a viscous solvent with tunable functions for biomedical engineering
+physical functionalities at their opposite
+sides~\cite{KirillovaMarschelkeSynytska2019}. Self-propelling Janus
+particles, for example, with a permanent biphasic asymmetry, have
+emerged as a rich chemical platform for the exploration of active
+matter~\cite{Meredithetal2022}. In the absence of mobility and any
+imposed flow, Janus particles often self-assemble into structures in a
+viscous solvent with tunable functions for biomedical engineering
 applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
-LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale, Bradley2016,Zarzaretal2015,KirillovaMarschelkeSynytska2019}.
-Depending on the interactions between Janus particles (JPs) and the
-surrounding viscous solvent, JPs self-assemble into oligomers of various
-geometries and sizes~\cite{Bradley2017,KangHonciuc2018,HongCacciutoLuijtenGranick2008}.
-
-When driven by an external flow, 
-dynamic rearrangement of JPs emerges naturally from the interactions between particles and fluid in colloidal
-matter~\cite{RevModPhys.93.025008}.
-Such colloidal hydrodynamics belongs to a wide class of
-nonequilibrium self-organization in physics, often with complexity and features similar to that of 
-biological systems such as living cells, bacterial baths, and
-animal flocks~\cite{CollardGrosjeanVandewalle2020,Vutukuri2020}. A
+LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale,
+Bradley2016,Zarzaretal2015, KirillovaMarschelkeSynytska2019}. Depending
+on the interactions between Janus particles (JPs) and the surrounding
+viscous solvent, JPs self-assemble into oligomers of various geometries
+and sizes~\cite{Bradley2017, KangHonciuc2018,
+HongCacciutoLuijtenGranick2008}.
+
+When driven by an external flow, dynamic rearrangement of JPs emerges
+naturally from the interactions between particles and fluid in colloidal
+matter~\cite{RevModPhys.93.025008}. Such colloidal hydrodynamics
+belong to a wide class of nonequilibrium self-organization in physics,
+often with complexity and features similar to that of biological systems
+such as living cells, bacterial baths, and animal
+flocks~\cite{CollardGrosjeanVandewalle2020, Vutukuri2020}. A
 long-standing challenge in fluid mechanics and material science is to
@@
 
-The surface of a Janus particle may have
-a dissimilar spatial distribution of hydrophobicity\cite{doi:10.1021/la503455h}.
-The many-body hydrodynamics of amphiphilic Janus particles assembled as
-vesicles suspended in a viscous fluid in the inertialess regime (zero Reynolds number) has
-been studied using boundary integral numerical
+The surface of a Janus particle may have a dissimilar spatial
+distribution of hydrophobicity~\cite{doi:10.1021/la503455h}. The
+many-body hydrodynamics of amphiphilic Janus particles assembled as
+vesicles suspended in a viscous fluid in the inertialess regime (zero
+Reynolds number) has been studied using boundary integral numerical
 simulations~\cite{Fu20,Fu2022_JFM}. The dynamics of the JP suspension
@@
 alternative means for computing the mechanical moduli of a colloidal
-membrane~\cite{NaTr00,Fu20,KrFiGuKaHa13}. Under background flows, the
+membrane~\cite{NaTr00, Fu20, KrFiGuKaHa13}. Under background flows, the
 hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
-many familiar behaviors of a vesicle: elongation and
-alignment along the extensional direction, tank-treading, and rupture of
-a vesicle under shear
-flow~\cite{Fu2022_JFM,grandmaison_brancherie_salsac_2021,D2SM00179A,keller_skalak_1982,Finken08,Shaqfeh11}.
+many familiar behaviors of a vesicle: elongation and alignment along the
+extensional direction, tank-treading, and rupture of a vesicle under
+shear flow~\cite{Fu2022_JFM, grandmaison_brancherie_salsac_2021,
+D2SM00179A,keller_skalak_1982, Finken08, Shaqfeh11}.
 
@@
 simulating the interaction between JPs, solvents, and
-substrates\cite{Brandner2019,Baniketal2021,HongCacciutoLuijtenGranick2008,C9NR05885K}.
-These methods often use pair-potentials to describe the
-interaction between JPs, for example by prescribing angle
-dependent forces and torques that bring the
-hydrophobic sides of two amphiphilic JPs into opposition.
-The HAP formulation of the present work also has attractive, long-range forces and torques,
-but they are instead derived from a boundary value problem for the molecular
-structure of water\cite{Ma77, GoHaKo94,ErLjCl89,Lietal05,Israelachvili80}.
-Unlike in MD or Monte Carlo-based simulations,
-the HAP interactions are nonadditive\cite{Fu20}, so that
-the interactions between a pair of JP is affected by the presence of other particles.
+substrates~\cite{Brandner2019, Baniketal2021,
+HongCacciutoLuijtenGranick2008, C9NR05885K}. These methods often use
+pair-potentials to describe the interaction between JPs, for example by
+prescribing angle dependent forces and torques that bring the
+hydrophobic sides of two amphiphilic JPs into opposition. The HAP
+formulation of the present work also has attractive, long-range forces
+and torques, but they are instead derived from a boundary value problem
+for the molecular structure of water~\cite{Ma77, GoHaKo94, ErLjCl89,
+Lietal05, Israelachvili80}. Unlike in MD or Monte Carlo simulations, the
+HAP interactions are nonadditive~\cite{Fu20}, so that the interactions
+between a pair of JPs is affected by the presence of other particles.
 
 In this work, we take advantage of the flexibility of the HAP model to
-examine the effects of varying the distribution of hydrophobicity on JP surfaces.
-Such variation of the boundary condition on JP surfaces have been realized experimentally
-by using chemicals to adjust the polarity of the viscous solvent, for example
-\cite{Zarzaretal2015,KirillovaMarschelkeSynytska2019,doi:10.1021/la503455h}.
-We show that a simple tuning of the hydrophobic distribution leads to transitions from unilamellar to
-multilamellar or striated superstructures of JPs. 
-Focusing on the fluid-structure interactions that correspond to such transitions, 
-we investigate the deformation of these
-novel structures in background flows and map out their collective
-behavior away from equilibrium.
-Looking forward, including other fields like
-electric potential for JPs synthesized with
-charged polymers\cite{HongCacciutoLuijtenGranick2008,doi:10.1021/la503455h,KangHonciuc2018},
-is straightforward within the context of the boundary integral representations\cite{kohl-cor-che-vee22},
-opening further lines of investigation.
+examine the effects of varying the distribution of hydrophobicity on JP
+surfaces. Such variation of the boundary condition on JP surfaces has
+been realized experimentally by using chemicals to adjust the polarity
+of the viscous solvent~\cite{Zarzaretal2015,
+KirillovaMarschelkeSynytska2019, doi:10.1021/la503455h}. We show that a
+simple tuning of the hydrophobic distribution leads to transitions from
+unilamellar to multilamellar or striated superstructures of JPs.
+Focusing on the fluid-structure interactions that correspond to such
+transitions, we investigate the deformation of these novel structures in
+background flows and map out their collective behavior away from
+equilibrium. Looking forward, including other fields like electric
+potential for JPs synthesized with charged
+polymers~\cite{HongCacciutoLuijtenGranick2008, doi:10.1021/la503455h,
+KangHonciuc2018}, is straightforward within the context of the boundary
+integral representations~\cite{kohl-cor-che-vee22}, opening further
+lines of investigation.
 
@@
 
-\section{Model parameters and boundary conditions}
-The interactions generated by the HAP-mobility problem formulation
-\eqref{eq:stokes}--\eqref{eq:force}
-lead to particle self-assembly for a broad range of parameters and
-boundary conditions.  Generally speaking, the effective distance of the
-hydrophobic interaction is set by the screening length $\rho$.
-Smaller values of the repulsion distance $\rho_0$ decrease the distance
-where attraction and repulsion are in balance and lead to more compact
-particle assemblies. 
-The rate of self assembly is proportional to the interfacial tension $\gamma$,
-and inversely proportional to solvent viscosity $\mu$; it is
-roughly inversely proportional to screening length $\rho.$
-
-To give our system physical units, we set the model parameters
-using phospholipids as a characteristic amphiphile in water \cite{Boal}.
-For solvent viscosity, we use $\mu = 1$ mPa s for the viscosity
-of water at room temperature.
-Pure lipid components give a range
-of interfacial tensions $0.7$ -- $5.3$ pN nm$^{-1}$
-~\cite{KUZMIN2005, Petelska2012,Jackson2016,GarciaSaez}.
-As in our previous works\cite{Fu20,Fu2022_JFM},
-we use $\gamma=4.1$ pN nm$^{-1}$ since this value gave
-good agreement with elastic moduli of lipid bilayers.
-The particle radius $c = 1.25$ nm
-gives a diameter representative of phospholipid length \cite{Boal},
-and the screening length $\rho = 5$ nm
+\section{Model parameters and boundary conditions} The interactions
+generated by the HAP-mobility problem formulation
+\eqref{eq:stokes}--\eqref{eq:force} lead to particle self-assembly for a
+broad range of parameters and boundary conditions. Generally speaking,
+the effective distance of the hydrophobic interaction is set by the
+screening length $\rho$. Smaller values of the repulsion distance
+$\rho_0$ decrease the distance where attraction and repulsion are in
+balance and lead to more compact particle assemblies. The rate of
+self-assembly is proportional to the interfacial tension $\gamma$, and
+inversely proportional to solvent viscosity $\mu$; it is roughly
+inversely proportional to screening length $\rho.$
+
+To give our system physical units, we set the model parameters using
+phospholipids as a characteristic amphiphile in water~\cite{Boal}. For
+the solvent viscosity, we use $\mu = 1$~mPa~s for the viscosity of water
+at room temperature. Pure lipid components give a range of interfacial
+tensions $0.7$--$5.3$~pN~nm$^{-1}$~\cite{KUZMIN2005, Petelska2012,
+Jackson2016, GarciaSaez}. As in our previous
+works~\cite{Fu20,Fu2022_JFM}, we use $\gamma=4.1$~pN~nm$^{-1}$ since
+this value gave good agreement with elastic moduli of lipid bilayers.
+The particle radius $c = 1.25$~nm gives a diameter representative of
+phospholipid length~\cite{Boal}, and the screening length $\rho = 5$~nm
 derives from experimental force-distance measurements of hydrophobic
-attraction \cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}.
-Based on empirical studies, the repulsion modulus $M = 2$ pN
-and repulsion distance $\rho_0 = 0.5$ nm give an interparticle
-distance around one particle radius.  This 
-ensures the accuracy of the boundary integral representations
-\eqref{eq:SL_BIE} and \eqref{eq:velocity}
-without having to employ overly aggresive mesh refinement. 
-Altogether, the above parameter set gives
-a characteristic time $1$
-ns and characteristic length $1$ nm.
-
-\begin{figure}[h!]
-\begin{center}
-  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
-\end{center}
-\begin{caption}{\label{fig:boundary_conditions}
-    The leftmost diagram illustrates the particle
-    $\Gamma_i$ with center $\aa_i$, radius $c$, and director $\dd$,
-    along with the angle $\alpha$ used to define $g(\xx)$ in \eqref{eq:bc-type}.
-    The three righ plots show $g(\xx)$ (black curve) for BC (i), (ii), and (iii)
-    when $\dd = (1,0)$. The surfaces are the respective solutions
-    $u(\xx)$ of \eqref{eq:SL} for a single, isolated particle.  
-  }
-\end{caption}
-\end{figure}
+attraction~\cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}. Based
+on empirical studies, the repulsion modulus $M = 2$~pN and repulsion
+distance $\rho_0 = 0.5$~nm give an interparticle distance around one
+particle radius. This ensures the accuracy of the boundary integral
+representations~\eqref{eq:SL_BIE} and~\eqref{eq:velocity} without having
+to employ overly aggressive mesh refinement. Altogether, the above
+parameter set gives a characteristic time $1$~ns and characteristic
+length $1$~nm.
 
@@
 \end{align}
-where $\alpha$ is the angle between the vector $\xx - \aa_i$ and 
-the particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$.
-The parameter $a$ normalizes the boundary conditions 
-so that $\int_{\Gamma_i} g^2(\xx) \, \dif s =  1$.
-The motivation for this normalization is that the hydrophobic attraction
-part of the free energy converges to the integral of the square of the boundary
-data in the zero-screening length limit.  
-We refer to the side of the particle where $\alpha = 0$
-as the tail and the side where $\alpha = \pi$ as the head.
+where $\alpha$ is the angle between the vector $\xx - \aa_i$ and the
+particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$.  The
+parameter $a$ normalizes the boundary conditions so that
+$\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.  The motivation for this
+normalization is that the hydrophobic attraction part of the free energy
+converges to the integral of the square of the boundary data in the
+zero-screening length limit. We refer to the side of the particle where
+$\alpha = 0$ as the tail and the side where $\alpha = \pi$ as the head.
+
+\begin{figure}[h!]
+\begin{center}
+  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
+\end{center}
+\begin{caption}{\label{fig:boundary_conditions} The leftmost diagram
+  illustrates the particle $\Gamma_i$ with center $\aa_i$, radius $c$,
+  and director $\dd$, along with the angle $\alpha$ used to define
+  $g(\xx)$ in~\eqref{eq:bc-type}. The three right plots show $g(\xx)$
+  (black curve) for BC (i), (ii), and (iii) when $\dd = (1,0)$. The
+  surfaces are the respective solutions $u(\xx)$ of~\eqref{eq:SL} for a
+  single, isolated particle.}
+\end{caption}
+\end{figure}
 
@@
 bilayer for $b = 1$, (ii) multilamellar for $b = 2$, and (iii) striated
-for $b = 0$.
-Supplementary Movie S1 shows the self-assembly process for the three cases.
+for $b = 0$. Supplementary Movie S1 shows the self-assembly process for
+the three cases.
 
@@
 
-In this work, we employ the newly developed JP model using BIEs ~\cite{Fu20, Fu2022_JFM} 
-and tune the boundary conditions with energy normalization to study the  collective dynamics of 
-amphiphilic (BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under various flowing conditions (quiescent flow, linear shear flow, and Taylor-Green flow).
-Three quantities are computed to characterize the dynamics of the collective configurations of JPs: Free energy $F$, strain parameter $E$ and 
-scalar order parameter $S_2$. In this numerical study we quantify how the collective hydrodynamics of JPs is affected by an external flow. 
-Under a given flow, we use these three measures of deformations to quantify the differences in the collective dynamics between the three types of JPs.
-These results, summarized below, may provide some general insight into the dynamic control of active particles in a viscous suspension.
-
-Within the framework of boundary integral equations, we derive a convenient expression for computing the free energy using the single layer potential (see 
-equation~\eqref{eq:normal_deriv}). In a quiescent flow, the free energy profiles demonstrate that the relaxation process for 
-particles confined in a certain size of box is independent of number of particles 
-($N_b$). However, we did find the final configurations to depend on the initial distribution of particle 
-directors $\dd_i$. Therefore, multiple patterns or local energy minimum states may 
-appear depending on the initial setup.
-
-Under a relatively weak linear shear flow, the amphiphilic (BC (i)) JPs behave as a unilamellar vesicle that elongates and tank-treads, with the scalar order 
-parameter increasing over time.
-For the multi-lamella (BC (ii)) and the striated (BC (iii)) structures  the assembly of JPs behaves like a rigid body with minimal deformation. The effective 
-viscosity of the material gives a quantitative validation to support the statement. High 
-shear-rate cases provide a range for critical shear rates where the structures break 
-apart and undergo major topological changes. 
-We further showed that
-free energy, scalar order parameter, and strain are effective measures to quantitatively capture the dynamics of the JP oligomers under a linear shear flow.
-
-Under a Taylor-Green flow,  we find that the amphiphilic JPs to be most interesting, exhibiting different vesicle shapes depending on the ratio of the size of the
-TG flow to the vesicle size. These results show that we can control the shape of the vesicle to be a square shape or a polygonal shape by adjusting the size of
-the cell in TG flow.
-On the other hand, the assembly of multi-lamella JPs and the striated JPs behaves more or less as a rigid body with connected subdomains, with the number of subdomains increasing with stronger strength of the TG flow.
-Overall, we found that the multilamellar (BC (ii)) JPs oligomers behave as a shear-thinning fluid, while the striated (BC (iii)) JPs oligomers possess a yield stress.
-
-The results reported here provide an inroad modeling framework for hydrodynamics of active colloids
-\cite{Meredithetal2022,McGlassonBradley2021,Vutukuri2020,Mallory2017}. 
-The present study also helps us understand the rheology of JP oligomers that may be realized in the experiments.
-We are now extending this study to three dimensional systems with more realistic features such as size distributions of JPs
-and thermal fluctuations\cite{kohl-cor-che-vee22}.
-%
- %it has been included in our future goals\cite{kohl-cor-che-vee22}.
-From a numerical perspective,
-it is straightforward to include
-random perturbations in the particle shape and
-boundary condition that mimick interfacial properties
-found in lab conditions\cite{Bradley2016,Bradley2017,Zarzaretal2015,doi:10.1021/la503455h}.
+In this work, we employ the newly developed JP model using
+BIEs~\cite{Fu20, Fu2022_JFM} and tune the boundary conditions with
+energy normalization to study the collective dynamics of amphiphilic
+(BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under
+various flowing conditions (quiescent flow, linear shear flow, and
+Taylor-Green flow). Three quantities are computed to characterize the
+dynamics of the collective configurations of JPs: free energy $F$,
+strain parameter $E$, and scalar order parameter $S_2$. 
+%We quantify how
+%the collective hydrodynamics of JPs is affected by an external flow.
+Under a given flow, we use these three measures of deformations to
+quantify the differences in the collective dynamics between the three
+types of JPs. These results, summarized below, provide general insight
+into the dynamic control of active particles in a viscous suspension.
+
+Within the framework of boundary integral equations, we derive a
+convenient expression for computing the free energy using the single
+layer potential (see equation~\eqref{eq:normal_deriv}). In a quiescent
+flow, the free energy profiles demonstrate that the relaxation process
+for particles confined in a certain size of box is independent of the
+number of particles. However, we find that the final configurations does
+depend on the initial distribution of particle directors $\dd_i$.
+Therefore, multiple patterns or local energy minimum states may appear
+depending on the initial setup.
+
+Under a relatively weak linear shear flow, the amphiphilic JPs behave as
+a unilamellar vesicle that elongates and tank-treads, with the scalar
+order parameter increasing over time. The assembly of multi-lamella and
+striated JP structures resemble a rigid body motion with minimal
+deformation. The effective viscosity of the material quantitatively
+validates this result. High shear-rate cases provide a range of critical
+shear rates where the structures break apart and undergo topological
+changes. We further show that free energy, scalar order parameter, and
+strain are effective measures to quantitatively capture the dynamics of
+the JP oligomers under a linear shear flow.
+
+Under a Taylor-Green flow, the amphiphilic JPs are the most interesting,
+exhibiting different vesicle shapes depending on the ratio of the size
+of the TG flow to the vesicle size. These results show that the shape of
+the vesicle, whether square or polygonal, can be controlled by adjusting
+the size of the cell in the TG flow. On the other hand, the assembly of
+multi-lamella JPs and the striated JPs behave more like a rigid body
+with connected subdomains, and the number of subdomains increases with
+increasing strength of the TG flow. Overall, the multilamellar (BC (ii))
+JPs oligomers behave as a shear-thinning fluid, while the striated (BC
+(iii)) JPs oligomers possess a yield stress.
+
+The results reported here provide an inroad modeling framework for
+hydrodynamics of active colloids~\cite{Meredithetal2022,
+McGlassonBradley2021, Vutukuri2020, Mallory2017}. The present study also
+helps us understand the rheology of JP oligomers that may be realized in
+the experiments. We are extending this study to three dimensional
+systems with more realistic features such as size distributions of JPs
+and thermal fluctuations~\cite{kohl-cor-che-vee22}. From a numerical
+perspective, it is straightforward to include random perturbations in
+the particle shape and boundary condition that mimic interfacial
+properties found in lab conditions~\cite{Bradley2016, Bradley2017,
+Zarzaretal2015, doi:10.1021/la503455h}.
 
@@
 \label{sec:appendix}
-Our calculation of the free energy $F$ relied on 
-converting the body integral in \eqref{eq:free_energy}
-into the surface
-integral in \eqref{eq:free_energy2}
-involving only single layer potentials and
-tangential derivatives. 
-This section supplies a proof of identity
-\eqref{eq:normal_deriv} used in this conversion.
-Let 
+Our calculation of the free energy $F$ relied on converting the body
+integral in~\eqref{eq:free_energy} into the surface integral
+in~\eqref{eq:free_energy2} involving only single layer potentials and
+tangential derivatives. This section supplies a proof of
+identity~\eqref{eq:normal_deriv} used in this conversion.  Let 
 \begin{equation}
@@
 \end{equation}
-be the single layer potential for a density function $\sigma.$
-Fix $\xx \in \Gamma$,
-let $\nnu_{\xx} = \nnu(\xx)$ and $\nnu_{\yy}$ be the unit normal at $\xx$, respectively $\yy$, in $\Gamma$,
-and let $\zz \in \Omega$.  The subscripts in $\nabla_{\zz}$ and $\nabla_{\yy}$ denote
+be the single layer potential for a density function $\sigma.$ Fix $\xx
+\in \Gamma$, let $\nnu_{\xx} = \nnu(\xx)$ and $\nnu_{\yy}$ be the unit
+normal at $\xx$, respectively $\yy$, in $\Gamma$, and let $\zz \in
+\Omega$. The subscripts in $\nabla_{\zz}$ and $\nabla_{\yy}$ denote
 differentiation with respect to $\zz$, respectively $\yy$.
 
-Recall from \eqref{eq:SL_BIE} that $u = \mathcal{D}[\sigma]$.
+Recall from~\eqref{eq:SL_BIE} that $u = \mathcal{D}[\sigma]$.
 Then  
@@
 since we can interchange $\nabla_\zz$ with $-\nabla_\yy$.
-Following \cite{Hsiao2008}, \S 1.2,
-\[
+Following~\cite{Hsiao2008}, \S 1.2,
+\begin{align}
 \nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy
@@
 + \Delta_{\yy}G(\zz-\yy) \tt_{\xx}\cdot \tt_{\yy}.
-\]
+\end{align}
 Then, using that $\Delta_{\yy} G(\zz-\yy) = \rho^{-2} G(\zz-\yy)$,
-interchanging $\nabla_\yy$ with $-\nabla_\zz$ once more,
-and integrating by parts in arclength $s$,
-we obtain 
+interchanging $\nabla_\yy$ with $-\nabla_\zz$ once more, and integrating
+by parts in arclength $s$, we obtain 
 \begin{align*}
@@
 %
-Letting $\zz\to\xx\in\Gamma$, and noting that both sides of the equation are continuous,
-we obtain \eqref{eq:normal_deriv}.
+Letting $\zz\to\xx\in\Gamma$, and noting that both sides of the equation
+are continuous, we obtain~\eqref{eq:normal_deriv}.
 
@@
 We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.
-B.Q. acknowledges support from the Simons Foundation, Mathematics and Physical Sciences-Collaboration Grants for Mathematicians, Award No. 527139.
-Y.-N.Y. acknowledges support from NSF (Grants No. DMS 1614863 and No. DMS 195160) and Flatiron Institute, part of Simons Foundation.
+B.Q.~acknowledges support from the Simons Foundation, Mathematics and Physical Sciences-Collaboration Grants for Mathematicians, Award No. 527139.
+Y.-N.Y.~acknowledges support from NSF (Grants No. DMS 1614863 and No. DMS 195160) and Flatiron Institute, part of Simons Foundation.
 

### 2022-08-05 doc/PRF2022/PRF_main.tex
yny

@@
 %Title of paper
-\title{Collective behavior of Janus Particles Suspended in a Viscous Fluid}
+\title{Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows}
 
@@
   multi-lamella and striated structures. To introduce dynamics, we
-  include a linear shear flow and a Taylor-Green mixing flow, and
+  include a linear shear flow and a steady Taylor-Green mixing flow, and
   measure the collective dynamics of JP particles in terms of their (a)
@@
 \section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
-The governing equations are a nonlinear system for the position and
+Following the formulation in \citep{Fu2022_JFM}, 
+the governing equations are expressed as a system for the position and
 orientation of a collection of rigid Janus particles. We first pose the
@@
 Once~\eqref{eq:stokes}--\eqref{eq:force} have been solved, the
-velocities $(\vv_i, \omega_i)$ from~\eqref{eq:rigid-vel} update the
+velocities $(\vv_i, \omega_i)$ from~\eqref{eq:rigid-vel} are used to update the
 particle positions and orientations.
@@
 inversely proportional to solvent viscosity $\mu$; it is roughly
-inversely proportional to screening length $\rho.$
+inversely proportional to screening length $\rho$ \cite{Fu20}.
 
@@
 Figure~\ref{fig:relax}. Three distinct configurations emerge: (i)
-bilayer for $b = 1$, (ii) multilamellar for $b = 2$, and (iii) striated
+bilayer (amphiphilic) for $b = 1$, (ii) multilamellar (biased hydrophobic) for $b = 2$, and (iii) striated (bipolar)
 for $b = 0$. Supplementary Movie S1 shows the self-assembly process for
-the three cases.
+the three cases. In the followings the terms ``multilamellar" and ``biased hydrophobic" are used  interchangeably to refer to BC (ii), while
+``striated" and ``bipolar" are used interchangeably to refer to BC (iii).
 
@@
 $N_b = 60$ and $N_b = 198$ cases
-form bilayers with multiple components.
+form bilayers with multiple domains.
 
@@
 \section{Measuring deformation}
-We use the free energy $F$, a strain parameter $E$, and two scalar order
+To quantify the collective hydrodynamics of JPs,
+we use the free energy $F$, a strain parameter $E$, and two scalar order
 parameters $S_{2}$ and $\tilde S_2$ to measure the deformation of
@@
 
-Finally, we use the scalar order parameter for orientational order\cite{Selinger2016}:
+Finally, we use the scalar order parameter $S_2$ to quantify the orientational order\cite{Selinger2016}:
 \begin{equation}
@@
 particle directors lie on a common axis e.g., two parallel vectors with
-possibly opposite direction are ordered. A value far from 1 indicates
-disorder.
+possibly opposite direction are ordered. A value below 1 indicates imperfect order, and zero indicates
+complete disorder.
 
@@
   \vspace{-20pt}  
-  \caption{\label{fig:BC1_TG} Multiple component bilayers in a
+  \caption{\label{fig:BC1_TG} Bilayers with multiple domains in a
   Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \upmu$s. The
@@
 There is no appreciable pattern in the deformation for the
-multicomponent bilayer case in TG flow
+case of bilayers with multiple domains in TG flow
 (Supplementary Movie S3, right panel).
@@
 configuration. They also studied self-assembly of bipolar electric JP,
-which use BC (ii) but electric potential, instead of a water order parameter,
+which corresponds to our BC (iii) JP (but electric potential, instead of a water order parameter),
 to define the interaction.  Due to the differing interaction,
@@
 changes. We further show that free energy, scalar order parameter, and
-strain are effective measures to quantitatively capture the dynamics of
-the JP oligomers under a linear shear flow.
+strain are effective measures to quantitatively capture the collective hydrodynamics of
+JPs under a linear shear flow.
 
@@
 increasing strength of the TG flow. Overall, the multilamellar (BC (ii))
-JPs oligomers behave as a shear-thinning fluid, while the striated (BC
-(iii)) JPs oligomers possess a yield stress.
+JP assembly behaves as a shear-thinning fluid, while the striated (BC
+(iii)) JP assembly  possesses a yield stress.
 
@@
 where $\uu$ is the velocity, $p$ is the pressure, $\uu_\infty$ is the
-background flow, and $\mu$ is the constant viscosity. The domain $\Omega
+background flow, and $\mu$ is the (constant) solvent viscosity. The domain $\Omega
 = \Omega(t)$ is the fluid region surrounding the particles and changes

### 2022-08-05 doc/PRF2022/PRF_main.tex
yny

@@
 \section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
-Following the formulation in \citep{Fu2022_JFM}, 
+Following the formulation in \citet{Fu2022_JFM}, 
 the governing equations are expressed as a system for the position and
@@
 principal eigenvector of the matrix $\dd_1\dd_1^\top + \cdots +
-\dd_{N_b}\dd_{N_b}^\top$. A value $S_2(t) = 1$ indicates that all
+\dd_{N_b}\dd_{N_b}^\top$. Defined as such, $S_2$ is always in the range $0 \le S_2 \le 1$.
+A value $S_2 = 1$ indicates that all
 particle directors lie on a common axis e.g., two parallel vectors with
-possibly opposite direction are ordered. A value below 1 indicates imperfect order, and zero indicates
+possibly opposite direction are ordered. A value below 1 indicates imperfect order, and $S_2=0$ indicates
 complete disorder.
@@
 separate, nearly equal bilayers, similar to the symmetric drop breakup
-under a linear shear flow \cite{Stone1994_ARFM}. 
-Refer to Supplementary Movie S4.
+under a linear shear flow \cite{Stone1994_ARFM}. For the dynamic evolution, see
+Supplementary Movie S4.
 
@@
 Figure~\ref{fig:BC1_shear}(e) is on average increasing. In the initial
-configuration, the structure has three or four components.
+configuration, the structure has three or four pieces of bilayer.
 %
@@
 (Figure~\ref{fig:BC1_shear}(f))
-because the components eventually completely separate and move away from one another
+because the various pieces of bilayer eventually completely separate and move away from one another
 under the shear flow.
@@
 \subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
-Next, we subject the JP structures to the Taylor-Green (TG) background
+Next, we subject the JP structures to a steady Taylor-Green (TG) background
 flow
@@
 There is no appreciable pattern in the deformation for the
-case of bilayers with multiple domains in TG flow
+case of bilayers with multiple pieces of bilayer in TG flow
 (Supplementary Movie S3, right panel).
@@
 are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s. At all
-flow strengths, the bilayer components are separated and mixed by the
+flow strengths, the bilayer pieces are separated and mixed by the
 flow in neighboring cells. In the $V_0 = 0.2$ case, the flow breaks off
-components consisting of only a few particles, leading an increase in
+bilayers consisting of only a few particles, leading an increase in
 energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve). There is no
-apparente structure to the change in the orientational order. There is an initial
-increase in the strain parameter due to component mixing, but the
+apparent structure to the change in the orientational order. There is an initial
+increase in the strain parameter due to merging and rupture of bilayers, but the
 strains remains bounded since the particles stay confined to the
@@
 
-In all cases, the vesicle tank-treads like in the shear flow case. The
+In all cases, the JP vesicle tank-treads in TG flow as it does
+in the shear flow. The
 direction of the tank-treading, however, varies with the cell size
@@
 The results are qualitatively similar and will be presented in tandem.
-For the multilamellar case, we place a 60-particle configuration (inset
-of Figure~\ref{fig:BC2_shear}(a)) in shear flows with $\dot\gamma=0.05,
-0.1, 0.15$ and in TG flow with flow rates $V_0=0.1, 0.15, 0.2$. For the
-striated case, we also place a 60-particle configuration (inset of
+For the multilamellar (BC (ii)) case, we place a 60-particle configuration (inset
+of Figure~\ref{fig:BC2_shear}(a)) in shear flow with $\dot\gamma=0.05,
+0.1, 0.15$ and in TG flow with $V_0=0.1, 0.15, 0.2$. For the
+striated  (BC (iii)) case, we also place a 60-particle configuration (inset of
 Figure~\ref{fig:BC3_shear}(a)) in shear and TG background flows. Here,
@@
 
-In the high shear rate cases ($\dot\gamma=0.15$), both the multilamellar
-and striated configurations become disordered. For BC (ii), the lamella
+In the high shear rate cases ($\dot\gamma=0.15$), both the multilamellar (BC (ii))
+and striated (BC (iii)) configurations become disordered. For BC (ii), the lamella
 break apart so that individual bilayers are no longer discernible
@@
 (Figure~\ref{fig:BC2_TG}(c)). In BC (iii), the stria also break apart,
-but neighboring particles form 'X'-like arrangements
+but neighboring particles form `X'-like arrangements
 (Figure~\ref{fig:BC3_TG}(d)), resembling the doubly alternating director
@@
 
-\section{Discussion}
-Our results were for $N_b = 60$ particles. This particle number was
+\section{Discussion\label{sec:discussion}}
+Results in \S~\ref{sec:results} are from simulations with $N_b = 60$ particles.
+%Our results were for $N_b = 60$ particles. 
+This particle number was
 large enough for the JP to form measurable structures while giving
@@
 quantitatively indistinguishable results. The time courses consisted of
-$O(10^3)$ time steps with $\Delta t = 0.2$ nm.
+$O(10^3)$ time steps with $\Delta t = 0.2$ ns.
 
 The free energy $F$ defined in~\eqref{eq:free_energy} scales with the
-boundary data $g$ and repulsion modulus $M$. To remove the degree of
-freedom in the boundary data, we scaled all boundary data so that the
+boundary data $g$ and repulsion modulus $M$. 
+%To remove the degree of freedom in the boundary data, 
+We thus scale all boundary data so that the
 square integral of $g$ is independent of the type of boundary condition; BC
@@
 
-Next, we suspended JPs in viscous background flows and observed
-deformations as a function of flow strength. There were three categories
-of boundary conditions---BC (i), BC (ii), and BC (iii)---that formed
+Next, we impose a flow on the JP suspension to study
+deformations of JP assemblies as a function of flow strength. There are three categories
+of boundary conditions---BC (i), BC (ii), and BC (iii)---that form
 bilayer, multilamellar, and striated configurations, respectively. For
-BC (i), we considered both an unstructured bilayer and a vesicle
-bilayer. The background flows were a linear shear flow and a TG flow.
-
-We can characterize the effective material properties of the JP
+BC (i), we consider both an unstructured bilayer and a vesicle
+bilayer. The background flows are a linear shear flow and a steady TG flow.
+
+We characterize the effective material properties of the JP
 structures based on the changes in free energy, orientational order, and
@@
 and $V_0$, as expected. Structurally, the striated JP configuration for
-BC (iii) behaved the most like a rigid body over the flow strengths
-tested. For this structure, the deformation measures were constant in
+BC (iii) behaves the most like a rigid body over the flow strengths
+tested. For this structure, the deformation measures are constant in
 time for shear rates $\dot \gamma$ up to $0.15$ and TG flow rate $V_0$
 up to $0.25$ (Figure~\ref{fig:BC3_shear} and Figure~\ref{fig:BC3_TG}).
-In contrast, a $25\%$--$50 \%$ smaller value for $\dot \gamma$ or $V_0$ was
+In contrast, a $25\%$--$50 \%$ smaller value for $\dot \gamma$ or $V_0$ is
 required to observe nonrigid deformations for the BC (i) and BC (ii)
@@
 \begin{align}
+\label{eq:mu_asm}
 \mu_{\text{asm}} = \frac{\dot \gamma}{\dot E} \mu 
@@
 
-Calculated viscosities of particle assemblies are shown in
+The viscosities of particle assemblies calculated from \eqref{eq:mu_asm} are shown in
 Table~\ref{tbl:bcii_visc}. The middle row gives the solid area fraction
@@
 since we can interchange $\nabla_\zz$ with $-\nabla_\yy$.
-Following~\cite{Hsiao2008}, \S 1.2,
+Following~\citet{Hsiao2008}, \S 1.2,
 \begin{align}

### 2022-08-05 doc/PRF2022/PRF_main.tex
combined intro sentence

@@
 emerged as a rich chemical platform for the exploration of active
-matter~\cite{Meredithetal2022}. In the absence of mobility and any
-imposed flow, Janus particles often self-assemble into structures in a
-viscous solvent with tunable functions for biomedical engineering
+matter~\cite{Meredithetal2022}.
+In the absence of mobility and any
+imposed flow, Janus particles (JPs) self-assemble
+into oligomers of various geometries
+and sizes
+depending on the interactions between JPs and the 
+viscous solvent~\cite{Bradley2017, KangHonciuc2018,
+HongCacciutoLuijtenGranick2008},
+with tunable functions for biomedical engineering
 applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
 LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale,
-Bradley2016,Zarzaretal2015, KirillovaMarschelkeSynytska2019}. Depending
-on the interactions between Janus particles (JPs) and the surrounding
-viscous solvent, JPs self-assemble into oligomers of various geometries
-and sizes~\cite{Bradley2017, KangHonciuc2018,
-HongCacciutoLuijtenGranick2008}.
+Bradley2016,Zarzaretal2015, KirillovaMarschelkeSynytska2019}.
 
@@
 for $b = 0$. Supplementary Movie S1 shows the self-assembly process for
-the three cases. In the followings the terms ``multilamellar" and ``biased hydrophobic" are used  interchangeably to refer to BC (ii), while
+the three cases. In the following,
+the terms ``multilamellar" and ``biased hydrophobic"
+are used  interchangeably to refer to BC (ii), while
 ``striated" and ``bipolar" are used interchangeably to refer to BC (iii).

### 2022-08-05 doc/PRF2022/PRF_main.tex
yny

--- 2022-08-05 doc/PRF2022/PRF_main.tex
@@
 \begin{acknowledgments}
-We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.
+%We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.
+We thank useful conversations with E. Corona, M. Rachh and S. Jiang.
 B.Q.~acknowledges support from the Simons Foundation, Mathematics and Physical Sciences-Collaboration Grants for Mathematicians, Award No. 527139.

### 2022-09-08 NSF2022/Description/background.tex
adding proposal for 2022

\noindent
{\bf Collaborative Research: Mathematical modeling and simulation of
self-assembling amphiphilic particles in solvent} \\
{\em Rolf Ryham (lead PI, Fordham University),
Bryan Quaife (PI, Florida State University), and
Yuan-Nan Young (PI, New Jersey Institute of Technology)}

\section{Background}
\label{sec:background}
%The goal of this collaborative proposal is to use mathematical modeling
%and numerical simulations to investigate the dynamic self-assembly of
%amphiphilic particles interacting via hydrophobic forces in solvent.
This collaborative proposal aims to advance
the mathematical modeling and numerical simulation
of dynamic self-assembly of amphiphilic particles interacting
via hydrophobic forces in solvent.
Amphiphilic particles such as lipid molecules possess both hydrophobic
and hydrophilic structures. In a viscous solvent they self-assemble into
meso-/macroscopic structures such as micelles and bilayers of lipids to
shield their hydrophobic surfaces from contact with the solvent
molecules e.g., waters. Such self-assembly of amphiphiles via hydrophobic
forces is ubiquitous in biology~\cite{Israelachvili1954},
and has been a major source of nonspecific interactions 
in soft matter~\cite{Sanchez-IglesiasEtAl2012_ACSNano,
AltantzisEtAl2013_PSC, XieYangLuEtAl2020_COCIS}. 
%The proposed research aims to provide fundamental understanding of the
%self-assembly dynamics of amphiphilic particles so to design smart
%materials of desirable properties by
%tuning the geometry and properties of the amphiphilic particles.

%The hydrophobic force arises when polar solvent molecules come in
%contact with a non-polar substance, such as hydrocarbon or vapor.
%In a polar solvent (like water), the dipole-dipole interaction between
%solvent molecules form a loosely structured hydrogen-bond network where
%each solvent molecule shares bonds with neighboring molecules at any
%given time \cite{Israelachvili1954}. In the presence of a non-polar
%solvent molecule loses the ability to form hydrogen bonds
%in one direction. 
%The decrease in the number of hydrogen bonds causes a reorientation,
%or structural change, in the surrounding water that is energetically
%very unfavorable \cite{Bjorneholm2016}.

\begin{wrapfigure}[15]{r}{0.37\textwidth}
\vspace{-8pt}
\centerline
{
\includegraphics[width=0.36\textwidth]{figures/LongRangeForce.jpg}
}
%\vspace{-20pt}
\caption{\label{fig:force_distance}
Force-distance curve for surfactant
monolayers adsorbed on mica reveals a long-range
attraction~\cite{Lin2005}.}
\end{wrapfigure}

Macroscopically, the substantial free energy of placing hydrophobic
surfaces in contact with water is roughly proportional to the surface
area of the contact region~\cite{Bjorneholm2016}.
%As a result, hydrocarbon solutes have a large interfacial tension 
%and try to minimize their surface area when in water. 
At the microscopic level, however, there is long-range interaction
between hydrophobic surfaces. Two hydrophobic surfaces, in particular,
separated by water over some distance, experience an attraction
called the
hydrophobic force~\cite{Lum1999, Meyer2006, Hammer2010, KaScScNe16}.
The force is nonadditive~\cite{SilveraBatista1242477},
and measurements show that the hydrophobic force decays exponentially with a
decay length on the order of 1--10 nm~
\cite{Israelachvili1984,Marcelja1977,Christenson2001,Lin2005,Taetal13}
(Figure \ref{fig:force_distance}).

Motivated by its broad applicability to biology, chemistry, and engineering,
PIs RR and YNY developed a mathematical model, called the
hydrophobic attraction potential (HAP) model~\cite{Fu2018_SIAM},
that is based on
the linear response of water to surface perturbations. This model was
used by all the PIs to show how amphiphilic Janus particles (JP)
self-assemble into a vesicle-like structure~\cite{FuQuRyYo20}.
Janus particles are typically spherical particles with a biphasic
material label on either hemisphere \cite{CaFaRaVe89,Gaetal13,Mallory2017,HaBr20,McBr21}.
Based on
preliminary results (\S\ref{sec:preliminary_work}), the PIs propose to
extend this HAP model as a general methodology that leads
to new mathematical ideas and efficient numerical methods.

\subsection{Hydrophobic attraction}
The hydrophobic attraction potential theory concerns the self-organization of
hydrophobic particles in a viscous solvent. It is a phenomenological
model mimicking the linear-response of water to surface perturbations
and stems from work of Stjepan Mar\v{c}elja
from the Australian National University in 1976. To explain certain
repulsion measurements between lecithin bilayers, Mar\v{c}elja and
coworkers devised a mathematical model using a Landau expansion of the
free energy density of an order parameter for the orientation of
water~\cite{LeRaPa77, MaRa76, LANDAULIFSHITZ5}. Their truncated free
energy gave a boundary value problem for water structure that was
readily solved in terms of hyperbolic trigonometric functions.

Although schematic, the model was general enough to explain a number of
physical effects. For example, the repulsion of lecithin bilayers
was explained by the free energy that decreases with distance of
separation because of the mean orientations of water being opposite at
the two interfaces. Later, a long-range attractive force between
hydrocarbon coated mica sheets was measured up to
100~nm~\cite{ClCh88,RaDe88}. The Mar\v{c}elja
theory was then applied to this problem for an order parameter
representing the excess number of hydrogen bonds per water
molecule and gave agreement with the measured force
curves~\cite{ErLjCl89}.

Analogues of Mar\v{c}elja's phenomenological theory appeared in other
areas related to biological self-assembly, such as interactions of
membrane-bound proteins~\cite{KoNa15, Nagle17, KUZMIN2005} and the
theory of polymer bead interaction in mixed solvents~\cite{deGe76}. On
the downside, it applies a continuum theory to distances of a few
molecular diameters, the association of order parameter is arbitrary, it
predicts monotonic forces, and finally the theory does not account for
the amplification in attraction at very short distances~\cite{Ni80}.

\begin{wrapfigure}[21]{l}{0.3\textwidth}
  \vspace{-5pt}
\includegraphics[width=0.3\textwidth]{figures/Fissure.jpg}
\includegraphics[width=0.3\textwidth]{figures/Landscape.jpg}
\caption{\label{fig:fissure} In fusion, fissures in the phospholipid
  monolayers expose hydrocarbon to water (top). The energy of fissures
  dominates first and third stages of fusion (bottom).
}
\end{wrapfigure}
Despite the ubiquity of
the phenomenon, theoretical developments explaining the basic underlying
principles of the hydrophobic effect have come relatively
late~\cite{Ch05}.
No single theory has been able to account, either qualitatively
or quantitatively,
for hydrophobic interaction over the full distance
regime~\cite{Lum1999, Lin2005, Meyer2006, Ducker2016}.
For example, studies of the partitioning of
hydrophobic solutes provide estimates for the energy cost of creating
hydrophobic-water contacts
that is a factor of three lower than the value derived from interfacial
tension measurements. Only recently was an explanation for this
discrepancy provided~\cite{Jackson2016}.

The continuum approach to water structure
that we present here is justified
\textit{a posteriori} by the agreement between theory and experiment.
Researchers have used Mar\v{c}elja's theory to calculate
energies of pore formation and fusion~\cite{Gletal88, Aketal17,
RyKlYaCo16}.
%When open, the attraction between apposing hydrophobic
%surfaces causes the fissure to collapse.
PI RR calculated a least energy path 
of fusion using a modified form of the Helfrich energy that
included Mar\v{c}elja's free energy for the structure of water
separating fissures~\cite{RyKlYaCo16} (Figure~\ref{fig:fissure}).
The calculated barrier heights were 
corroborated experimentally \cite{FrRoPi17}. In summary,
there is a consensus that despite its apparent simplicity, the predictions
of the hydrophobic attraction potential theory are compatible with
experimental measurements and may closely mirror the reality of
the physical process at a molecular scale~\cite{FrRoPi17, Fretal21}.

The HAP is a conceptual advance for modeling bilayer membranes.
Continuum elastic energies of membrane assume an energy density that
depends quadratically on the bilayer strain
\cite{Hamm2000,TerziDeserno17, PhysRevE.102.042406}.  The coefficients
of the continuum ansatz correspond to experimentally measured elastic
moduli \cite{Nagle17, Nagle17-2, NAGLE2000159}.  The HAP approach can
potentially explain membrane properties from first principles because it
derives elastic energies assuming parameters for the water structure and
particle shape \cite{Fu2018_SIAM, FuQuRyYo20, doi:10.1063/5.0009734,
LiAn-Chang16}.  Immersed boundary and boundary integral are highly
effective for modeling intact, giant unilamellar vesicles (GUV) because
they use relatively large time-step sizes and mesh sizes
\cite{
Shravan09,
Rahimian15,
KimLai2010_JCP,
KimLai2012_PRE,
HuLaiSeolEtAl2016_JCP,
Bartels,
Peng13,
RyKlYaCo16,
Sinha15,
Lowengrub13,
Hu,
Hu13}.
Conversely, the number of coarse-grained particles needed to track a GUV
in the HAP formalism is relatively large.  For microscopic process like
fusion, however, membrane deformations occur at a length scale
comparable to the thickness of the membrane
\cite{Kuzmin7235,Aeffner2012,KoKo2002}.  The small deformation
assumption of continuum theory no longer holds
\cite{Hamm2000,TerziDeserno17, PhysRevE.102.042406}.  The HAP theory
does encode membrane thickness through particle diameter, and it is
comparatively straightforward to account for proteins and lipid mixtures
by including several particle species.  Any ruptures or insertions occur
self-consistently in the HAP formulation.  Phase-field and level-set
methods also allow for topological changes but they require multiple
phase fields and level sets and additional (sometimes empirical) laws to
couple them to model membrane-membrane interactions
\cite{
DuLiuWang2004_JCP,
BibenKassnerMisbah2005_PRE,
DoyeuxGuyotChabannesEtAl2013_JCAM,
Du05,
QiangDu08,
doi:10.1098/rspa.2012.0505,
doi:10.1137/130941432,
Feetzl18,
doi:10.1137/16M1108406}.
In addition, these methods require the entire fluid and interfacial
domains to be discretized.  In contrast, the HAP methodology allows
evolution equations to be solved using integral equation methods that
when optimized have linear or near-linear computational complexity in
the number of particles~\cite{fmm1, fmm2, fmm3, fmm4, fmm5, fmm6, fmm7,
fmm8}.

### 2022-09-27 NSF2022/Description/broaderimpacts.tex

--- 2021-11-15 NSF2021/Description/broaderimpacts.tex
@@
 \label{sec:BroaderImpacts}
-This project aims to advance the mathematical modeling of collective
-dynamics of amphiphilic particles. The simulations use a new, yet
-intuitive, approach that accounts for important and complex systems
-that are presently out of reach in computational material science. These complex
-systems include optimal shape design in metamaterials and
-fusion and fission of amphiphilic bilayer membranes. The further
-development to three-dimensional models describing colloidal systems could be
-transformative in biomedicine and material science. The research draws
-from expertise in scientific computing, physics of fluids, and
-mathematics. The mathematical component incorporates leading
-variational techniques and offers insight into fundamentals of material
-science. The project brings socially consequential research into the
-classroom, and offers undergraduates the opportunity to train alongside
-faculty and postdoctoral fellows. With its combination of
-mathematical modeling, analysis, and scientific computing, the project
-highlights the importance of mathematics and computation to all areas of
-science and engineering.
+This project aims to advance the mathematical modeling of collective dynamics of amphiphilic particles.
+The simulations use a new, yet intuitive, approach that accounts for important and complex systems that are presently out of reach in computational material science.
+These complex systems include optimal shape design in metamaterials and fusion and fission of amphiphilic bilayer membranes.
+The models describing colloidal systems could be transformative in biomedicine and material science.
+The research draws from expertise in scientific computing, physics of fluids, and mathematics.
+The mathematical component incorporates leading variational techniques and offers insight into fundamentals of material science.
+The project brings socially consequential research into the classroom and offers
+undergraduates the opportunity to train alongside faculty and graduate students.
+With its combination of mathematical modeling, analysis, and scientific computing, the project highlights the importance of mathematics and computation to all areas of science and engineering.
+
 %The proposed mathematical analysis, modeling, and numerical algorithms
@@
 To foster training in mathematical sciences,
-the proposal supports one undergraduate researcher (UR) per year
+the proposal supports two undergraduate researchers (URs) per year
 from the lead institution.
@@
 Based on these experiences, we have outlined three projects for the present proposal.
-\begin{enumerate}[noitemsep]
+\begin{enumerate}[noitemsep,topsep=0pt]
 %\noitemsep
@@
 mathematical writing and presentation.
-The UR will have a desk and meeting room
+The URs will have desks and meeting room
 in a recently completed collaboration space
@@
 will encourage the
-UR to participate in a national conference.
+URs to participate in a national conference.
 
@@
 modules will introduce topics from numerical linear algebra and
-optimization, and highlight concrete applications of mathematics
+optimization and highlight concrete applications of mathematics
 based on the ideas of the proposal.
@@
 \section{Intellectual Merit}
-The purpose of this research is to reach interesting physical phenomena
-with less computational cost than molecular dynamics, and account for
-more general features that continuum theory misses. The main ingredient
-is defining a nonlocal interaction through the solution of an elliptic
-boundary value problem that has the phenomenological characteristics of
-long-range hydrophobic attraction. It turns out that this minimal model
-gives rise to rich phenomena for Janus particle aggregates and correctly
-predicts elastic properties of bilayer. The technical research tasks
-include quantifying collective properties of amphiphilic ensembles,
-improving on mathematical models, 
-efficient, high-order numerical algorithms for large-scale simulations,
-and incorporating external fields through electric charge.
+The purpose of this research is to reach interesting physical phenomena with less computational cost than molecular dynamics, and account for more general features that continuum theory misses.
+The main ingredient is defining a nonlocal interaction through the solution of an elliptic boundary value problem that has the phenomenological characteristics of long-range hydrophobic attraction.
+This minimal model, while intuitive, is quite a general description of amphiphiles in solvent and gives rise to rich phenomena from Janus particle aggregates to correctly predicting elastic properties of bilayer.
+The technical research tasks include quantifying collective properties of amphiphilic ensembles, improving on mathematical models, efficient, high-order numerical algorithms for large-scale simulations, and incorporating external fields through electric charge.
 %Lastly, the

### 2022-09-27 NSF2022/Description/specificaim1.tex

--- 2021-11-23 NSF2021/Description/specificaim1.tex
@@
  \vspace{-3pt}
- \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.jpg}
+ \includegraphics[width=0.55\textwidth]{figures/Domain.jpg}
  \caption{\label{fig:flow_map}
@@
  \vspace{-3pt}
- \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/3Particles.jpg}
+ \includegraphics[width=0.55\textwidth]{figures/3Particles.jpg}
  \caption{\label{fig:3particles}
@@
   \begin{center}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}
+  \includegraphics[width=0.2\textwidth]{figures/LPA.jpg}
+  \includegraphics[width=0.2\textwidth]{figures/LPB.jpg}
+  \includegraphics[width=0.2\textwidth]{figures/LPC.jpg}
   \end{center}
@@
   \centering
-  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
+  \includegraphics[width=2in]{figures/OrderPDFs.jpg} 
   \vspace{-20pt}
@@
       (a)
-    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B1.jpg}
-    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B2.jpg}
-     &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B3.jpg}    \\
+    &\includegraphics[width=1.8in]{figures/N100B1.jpg}
+    &\includegraphics[width=1.8in]{figures/N100B2.jpg}
+     &\includegraphics[width=1.8in]{figures/N100B3.jpg}    \\
      (b)
-    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C1.jpg}
-    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C2.jpg}
-      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C3.jpg}    \\
+    &\includegraphics[width=1.8in]{figures/N100C1.jpg}
+    &\includegraphics[width=1.8in]{figures/N100C2.jpg}
+      &\includegraphics[width=1.8in]{figures/N100C3.jpg}    \\
     (c)
-      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A1.jpg}
-      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A2.jpg}
-      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A3.jpg}    \\
+      &\includegraphics[width=1.8in]{figures/N100A1.jpg}
+      &\includegraphics[width=1.8in]{figures/N100A2.jpg}
+      &\includegraphics[width=1.8in]{figures/N100A3.jpg}    \\
       &\multicolumn{1}{c}{$t = 0$}
@@
 for example.
-%\hl{Collaboration with experimental groups will
-%use numerical methods to predict parameter regimes 
-%to control particle-particle interactions.}
-
-%\begin{wrapfigure}[14]{l}{0.5\textwidth}
-%\includegraphics[width=0.5\textwidth]{figures/SpecificAi%m1/multilamelar.pdf}
-%\caption{\label{fig:multilamelar}
-%  Experimentalists can transform unilamellar vesicles to% multilamellar
-%  vesicles by altering the quality of the solvent
-%    \cite{deMeetal21}.
-%  In \eqref{eq:SL}, the solvent quality enters through t%he potential
-%  $f(u)$ and boundary conditions. 
-%}
-%\end{wrapfigure}
 

### 2022-09-27 NSF2022/Description/specificaim2.tex

--- 2021-11-14 NSF2021/Description/specificaim2.tex
@@
 
-%\label{subsec:specific_aim_2}
-%\begin{wrapfigure}[14]{r}{0.61\textwidth}
-%  \centering{\includegraphics[width=0.60\textwidth]{Figures/domain.pdf}}
-%    \vspace{-15pt}
-%    \caption{\label{fig:flow_map} \footnotesize A collection of 3D
-%    amphiphilic particles suspended in a solvent. The solvent velocity
-%    satisfies the Stokes equations, and the hydrophobic forces depend on
-%    the solvent activity that satisfies the screened Laplace equation.
-%    The geometry is updated by solving the mobility problem.} 
-%\end{wrapfigure}
 The HAP model requires solving exterior problems for the order
@@
 will develop methods based on combinations of volume and layer
-potentials. Numerical methods to solve these integral equations (IEs)
-have several advantages over their PDE-based counterpart: by
-construction, they satisfy far-field and mass conservation conditions;
-only $\partial\Omega$ needs to be discretized for layer potentials;
-carefully chosen IEs result in a well-conditioned linear system that is
-solved with a mesh-independent number of GMRES iterations; and
-high-order or spectral accuracy is attainable with appropriate
-quadrature methods. The PIs have demonstrated that IEs are a powerful
-tool to simulate two-dimensional suspensions of amphiphilic
+potentials, and inexact Newton's method. Numerical methods to solve
+these integral equations (IEs) have several advantages over their
+PDE-based counterpart: by construction, they satisfy far-field and mass
+conservation conditions; only $\partial\Omega$ needs to be discretized
+for layer potentials; carefully chosen IEs result in a well-conditioned
+linear system that is solved with a mesh-independent number of GMRES
+iterations; and high-order or spectral accuracy is attainable with
+appropriate quadrature methods. The PIs have demonstrated that IEs are a
+powerful tool to simulate two-dimensional suspensions of amphiphilic
 particles~\cite{Fu2018_SIAM, FuQuRyYo20}. Moreover, elements of these
@@
 satisfy~\eqref{eq:SL}, and all the methods can naturally be extended to
-three dimensions. \S\ref{subsec:AC} describes how the non-linear
-Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved using IE
-formulations. Then, \S\ref{subsec:NumericalIssues} describes how we will
-combine preconditioning strategies with fast summation methods to
-accelerate the time to solution, and \S\ref{subsec:timeStepping}
-describes adaptive time stepping methods,
+three dimensions. These methods will be motivated by models and analysis
+developed in Specific Aims 1 and 3. \S\ref{subsec:AC} describes how the
+non-linear Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved
+using an IE formulation. Then, \S\ref{subsec:NumericalIssues} describes
+how we will combine preconditioning strategies with fast summation
+methods to accelerate the time to solution, and
+\S\ref{subsec:timeStepping} describes adaptive time stepping methods.
 
@@
     a(u - u_0)^2, &\mbox{if } u \leq (u_0 + u_1)/2, \\
-    (u - u_1)^2 + \tfrac{1}{4}(a-1)(u0-u1)^2 , &\mbox{if } u > (u_0 + u_1)/2,
+    (u - u_1)^2 + \tfrac{1}{4}(a-1)(u_0-u_1)^2 , &\mbox{if } u > (u_0 + u_1)/2,
   \end{cases}
 \end{align*}
-and the resulting inexact Newton's method requires solving the piecewise
-constant PDE
+where $a>0$, and the resulting inexact Newton's method requires solving
+the piecewise constant PDE
 \begin{align}
@@
 
-%\begin{wrapfigure}[27]{l}{1.8in}
-%  \vspace{-4pt}
-%  \centering
-%  \input{figures/doublewell.tikz} 
-%  \caption{\label{fig:CA} (a) The double well potential $u_0 =
-%  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
-%  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
-%  and inexact Newton's methods.}
-%\end{wrapfigure}
 Having demonstrated that the inexact Newton method converges in one
@@
 u_1)/2 \}$ be their common boundary, and we let $G_0$ be the fundamental
-\hl{solution of $(-\rho^2 \Delta + a)$ and $G_1$ be the fundamental
-solution of $(-\rho^2 \Delta + 1)$. Then, the solution}
+solution of $(-\rho^2 \Delta + a)$ and $G_1$ be the fundamental
+solution of $(-\rho^2 \Delta + 1)$. Then, the solution
 of~\eqref{eq:screenedPoisson} can be written as $u = u^P + u^H$ where
@@
 $\Gamma = \cup_i \Gamma_i$, and that it is continuous and differentiable
-across $\Lambda$. This approach for using IEs to solve elliptic PDEs
-with piecewise constant coefficients has succesfully been used in
-other application such as scattering~\cite{hyu-bar2014,
-che-cho-cai2018}.
+across $\Lambda$. This approach of using IEs to solve elliptic PDEs with
+piecewise constant coefficients has successfully been used in other
+application such as scattering~\cite{hyu-bar2014, che-cho-cai2018}.
 
@@
 When solving for the density functions $\eta_0$, $\eta_1$, and $\sigma$,
-a carefully chosen IE formulation requires a mesh-independent number of
-GMRES iterations~\cite{cam-ips-kel-mey-xue1996}. Therefore, the required
-CPU time is proportional to the cost of a matrix-vector multiplication
-that can be performed in optimal or near-optimal time with the fast
-multipole method (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2,
-fmm3, fmm4, fmm6, fmm7, fmm8}. PI BQ is experienced with applying FMMs
-for the Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the
-screened Laplace equation~\cite{kro-qua2011, qua2011}. Furthermore, to
-reduce the number of GMRES iterations, preconditioning strategies such
-as the inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017} and
-domain decomposition~\cite{che-bir2021}. PI BQ used the IFMM to
-precondition Stokes equations~\cite{qua-cou-dar2018}. A suite of other
-preconditioners including sparse approximate inverses~\cite{che2000} and
-multigrid~\cite{hem-sch1981, sch1982} will be investigated.
+a carefully chosen IE formulation only requires a mesh-independent
+number of GMRES iterations~\cite{cam-ips-kel-mey-xue1996}. Therefore,
+the required CPU time is proportional to the cost of a matrix-vector
+multiplication that can be performed in optimal or near-optimal time
+with the fast multipole method (FMM)~\cite{fmm5} and its
+extensions~\cite{fmm1, fmm2, fmm3, fmm4, fmm6, fmm7, fmm8}. PI BQ is
+experienced with applying FMMs for the Stokes
+equation~\cite{qua-bir2014, bys-sha-qua2020} and the screened Laplace
+equation~\cite{kro-qua2011, qua2011}. Furthermore, to reduce the number
+of GMRES iterations, the efficacy of preconditioning strategies such as
+the inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017} and
+domain decomposition~\cite{che-bir2021} will be investigated. PI BQ used
+the IFMM to precondition Stokes equations~\cite{qua-cou-dar2018}. A
+suite of other preconditioners including sparse approximate
+inverses~\cite{che2000} and multigrid~\cite{hem-sch1981, sch1982} will
+be investigated.
 
@@
 applies a low-order, single-step method to achieve high-order accuracy.
-To estimate the error, at each time step, we will compute the total
-force and torque of the system which is computationally cheap and
-physically zero. PI BQ's experience is that error estimates based on
-physical constraints such as force- and torque-free conditions
-appropriately determine how the time step should be adjusted so that the
-dynamics are resolved without the computational expense of techniques
-such as embedded Runge-Kutta methods, step-doubling, and Richardson
+At each time step, we will compute the total force and torque of the
+system which is computationally cheap and physically zero, and therefore
+provides an estimate of the local truncation error. PI BQ's experience
+is that error estimates based on physical constraints, such as force-
+and torque-free conditions, appropriately determine adaptive time step
+sizes so that the dynamics are resolved without the computational
+expense of embedded Runge-Kutta methods, step-doubling, Richardson
 extrapolation.

### 2022-09-28 NSF2022/Description/specificaim1.tex
starting proposal

--- 2021-11-15 NSF2021/Description/specificaim1.tex
@@
 \label{sec:proposed-work}
+%The proposed research develops fast,
+%high-order-accurate, parallel numerical algorithms for large-scale
+%simulations of the collective hydrodynamics of amphiphilic particles in a viscous solvent.
 %%
+We have demonstrated that our hydrophobic attraction with repulsion
+potential (HAP) approach efficiently simulates self-assembly of
+amphiphilic particles into two-dimensional micelles, bilayer membranes,
+and vesicles \cite{Fu2018_SIAM} and recreates the tank-treading
+phenomenon in external shear flows \cite{FuQuRyYo20}.
+While the results show great promise in the field of collective body
+hydrodynamics, several outstanding issues need to be addressed. These
+include a thorough analysis of elastic properties of our coarse-grained
+bilayers and efficiently simulating three-dimensional collective
+hydrodynamics of amphiphilic particles.
+We must also incorporate electric charge and account
+for how external fields control particle self-assembly. 
+%mathematically
+%characterize the variational behavior of HARP under appropriate
+%homogenized limits.
 
-\subsection{Specific Aim 1: Measuring material properties of amphiphile
-  self-assembly}
+\subsection{Specific Aim 1: Measuring material properties of amphiphile self-assembly}
 \label{subsec:specific_aim_1}
-Specific Aim 1 proposes a novel mathematical model for particle
-self-organization driven by long-range interfacial forces. 
-The research aims to provide fundamental insight into the
-self-assembly dynamics of amphiphilic particles. These results will
-facilitate optimal design of smart materials by tuning the geometry and
-properties of the amphiphilic particles.
-Applications in this area include cargo-carrying capacity, 
-catalytic activity, or stimuli-responsive shape-changes
-\cite{McBr21, HaBr20}.
 
-\subsubsection{Problem formulation}
-%\begin{wrapfigure}[h!]
-\begin{wrapfigure}[11]{r}{0.55\textwidth}
- \centering
- \vspace{-3pt}
- \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.jpg}
- \caption{\label{fig:flow_map}
-   In the HAP formulation, hydronamic interactions
-   come from the Stokes equations and
-   hydrophobic interactions come from the structure order parameter $u$.
-   The colormap is for the intensity of $u$.}
-\end{wrapfigure}
-
-The mathematical formulation is a nonlinear system for the dynamics of a
-collection of particles. The interactions come from a system of 
-partial differential equations (PDEs) that comprise hydrodynamic
-interactions and hydrophobic interactions.
-%The formulation prevents particle collisions through excluded volume
-%potentials. 
-The hydrodynamic interactions come from the mobility problem for rigid
-particles immersed in a viscous solvent. We then use a
-second-order Adams-Bashforth method to update the particle configuration.
-Assuming inertial terms are
-negligible, the particle motion is goverened by the Stokes equations
-\begin{subequations}
-  \label{eq:stokes}
-  \begin{alignat}{3}
-  \label{eq:stokes1}
-  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
-    \label{eq:stokes2}
-  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
-\label{eq:stokes3}
-  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
-  \end{alignat}
-\end{subequations}
-%\begin{alignat}{3}
-%\label{eq:stokes1}
-%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
-%    && \xx \in \Omega, \\
-%\label{eq:stokes2}
-%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
-%\label{eq:stokes3}
-%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
-%\end{alignat}
-%
-where $\uu$ is the velocity and $p$ is the pressure of the solvent,
-$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
-viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
-particles and changes shape as the particles move.
-Since the particles are rigid, the solvent velocity satisfies
-a no-slip boundary condition for a rigid body motion 
-%\begin{align}
-%\label{eq:rigid_bc}
-%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
-%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
-%\end{align}
-on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
-and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
-Given imposed forces acting on each
-particle, the \emph{mobility problem} consists of finding
-translational and angular velocities so that viscous fluid forces
-balance the imposed forces.
-
-The hydrophobic interactions come from the tendency of particles to
-minimize the free energy of the structure of the surrounding water
-molecules. The free energy functional takes the form 
-\begin{equation}
-\label{eq:free_energy}
-  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
-  \,d\xx,
-\end{equation}
-where $u$ is an order parameter for the structure of water, $\rho$ is a
-decay length, $C$ is a constant, and $f(u)$ is a potential.
-Hydrogen-bond persistence times are on the order of picoseconds
-which is much smaller than characteristic time for 
-particle motion \cite{MaGa13}.
-Thus we assume $u$ minimizes $F[u]$ for all times.
-Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
-$u$ is bounded and satisfies the Euler-Lagrange equation
-\begin{equation}
-\label{eq:SL}
--\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
-\text{ on } \bd\Omega.
-\end{equation}
-The boundary condition $g$ is a material label that is transported with
-the particle (Figure~\ref{fig:bcs}).
-
-The particles lower the free energy $F[u]$ of the surrounding water
-by moving. We calculate the rate of change of $F[u]$ using
-\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
-Carrying out
-this variation yields a 
-%The hydrophobic forces are torques are
-%\begin{equation}
-%  \label{eq:hydrophobicAttraction}
-%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
-%    \quad 
-%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
-%    ({\bf T} \cdot \nnu) \dif s.
-%\end{equation}
-stress  
-\begin{align}
-  \label{eq:stress}
-\mathbf{T}
-= C \left[ \rho^{-1} f(u) \mathbf{I}
-  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
-\end{align}
-The imposed forces and torques come from the integration of $\mathbf{T}$
-along the particle boundary.
-These forces and torques couple the Stokes equations \eqref{eq:stokes},
-to semilinear elliptic equation \eqref{eq:SL}.
-Solving for the translational and rotational velocities gives the
-particle evolution.
-
-The stress~\eqref{eq:stress} was first
-introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
-generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
-Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
-forming particle aggregates that sequester their hydrophobic surface
-regions.
-
-%By solving the above system, we obtain translational and angular
-%velocities of the many-body system. A second-order Adams-Bashforth
-%scheme updates the particle positions and orientations.
-
-The formulation presents a number of mathematical and numerical
-challenges. For one, the domain is constantly changing so that a new
-boundary value problem must be solved at each time step. The particle
-boundaries are nearly touching and high-order numerical
-schemes and adaptively chosen time-step sizes
-are required to calculate trajectories accurately.
-Furthermore, the domain is unbounded and care must be taken 
-in capturing the far-field boundary conditions correctly. 
-Finally, the numerical routine must handle large system sizes
-efficiently.
-
-%and
-%\begin{equation}
-%  \label{eq:force}
-%  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i,\quad 
-%  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \,
-%  \dif s = T_i, \qquad i=1,\ldots,N_b,
-%\end{equation}
-%where
-%$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T \right)$
-%is the hydrodynamic stress tensor (pressure tensor) and $\nnu$ is the
-%particle outward normal.
-
-\subsubsection{Janus-particle self-assembly} 
-Distinct morphologies can be obtained from 
-the HAP model by shifting the boundary condition $g$.
-Consider the linear case where $f(u) = u^2$.
-This choice makes \eqref{eq:SL} a boundary value
-problem for the screened-Laplace equation
-and the solutions have a boundary layer structure that decays to $0$ in the
-bulk with the decay length $\rho$.
-We consider three kinds of boundary conditions
-on particle $\Gamma_i$:
-\begin{equation}
-  \label{eq:bcs}
-  \begin{tabular}{c|c|c}
-     \text{(a)} & \text{(b)} & \text{(c)} \\
-    \hline
-    \rule{0pt}{4ex} 
-      $g(\mathbf{x}) = \displaystyle \frac{1+\cos (\theta_i(\xx))}{\sqrt{3\pi r}}$
-    & $g(\mathbf{x}) = \displaystyle \frac{2+\cos (\theta_i(\xx))}{\sqrt{9\pi r}}$
-    & $g(\mathbf{x}) = \displaystyle \frac{\cos (\theta_i(\xx))}{\sqrt{\pi r}}$
-\end{tabular}
-\end{equation}
-  The number $\theta_i(\xx)$ is the angle formed by the position $\xx$, the
-particle center $\aa_i$, and the particle director $\dd_i$ (Figure \ref{fig:flow_map}).
-The normalizations e.g., $(\pi r)^{-1/2}$, provide a uniform
-surface energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles
-of radius $r$. 
-The cases (b) and (c) are obtained by applying a vertical shift
-and scaling to case (a), see Figure \ref{fig:bcs}.
-Using this setup, we simulate the dynamics of 100 particles with random
-initial position and orientation.
-
-\begin{wrapfigure}[9]{r}{0.65\textwidth}
-  \vspace{-20pt}
-  \begin{center}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
-  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:bcs} Boundary conditions characterize the water
-    structure at the particle interface: an amphiphilic particle (left),
-    a hydrophobic
-  particle with anisotropic intensity (middle), a water structure with
-  positive/negative charge (right). The dashed curve is the boundary of the
-  disk and the arrow is its director for each particle.}
-\end{wrapfigure}
-Case (a) models amphiphilic particles.
-Amphiphilic particles have a hydrophobic tail and a hydrophilic head
-and these are accounted for as follows.
-The hydrophilic side takes the value $u =0$.
-This mimicks the apolar head of a lipid, for example, which does
-not alter the structure of adjacent waters. The hydrophobic side
-represents hydrocarbons and takes the value 
-$u > 0$. The interaction between particles is attractive,
-and particles will collectively orient their tails toward
-one another. 
-PIs RR and YNY's previous work showed that this   
-boundary condition produces two-dimensional micelles and
-bilayers~\cite{Fu2018_SIAM}, as illustrated in 
-Figure~\ref{fig:self-assembly}(a).
-
-\begin{wrapfigure}[14]{l}{2in}
-  \vspace{-4pt}
-  \centering
-  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
-  \vspace{-20pt}
-  \caption{\footnotesize
-    \label{fig:OrderPDFs}
-    Probability density functions for
-    relative orientation of nearby particles
-    for the data in 
-    Figure~\ref{fig:self-assembly}, $t = t_{\text{final}}$.
-  }
-\end{wrapfigure}
-Multilamelar bilayers arise when both sides of the particle
-are hydrophobic (Figure~\ref{fig:self-assembly}(b)).
-The boundary condition \eqref{eq:bcs}(b) 
-gives a particle with a hydrophobic intensity that is greater
-on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
-The initial self-assembly is similar to that in case (a).
-The difference arises in the long-time dynamics where the bilayers
-no longer remain well-separated. 
-Rather, the bilayers form layers 
-as a consequence of the interfacial tension of exposed particle
-heads~\cite{Huetal19, deMeetal21}.
-
-Finally, boundary condition \eqref{eq:bcs}(c) models 
-a particle whose head surface repels the tail surface as proposed in
-\cite{MaRa76, Ma77}.
-The particles initially form chains with their directors perpendicular to the
-length of the chain. The equilibrium structure
-resembles a checkerboard pattern
-where each particle coordinates
-its head with the head of three other particles and its tail with the
-tail of three other particles Figure~\ref{fig:self-assembly}(c).
-
-\begin{figure}[h!]
-  \begin{center}
-    \begin{tabular}{m{0.1cm}m{1.8in}m{1.8in}m{1.8in}}            
-      (a)
-    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B1.jpg}
-    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B2.jpg}
-     &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B3.jpg}    \\
-     (b)
-    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C1.jpg}
-    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C2.jpg}
-      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C3.jpg}    \\
-    (c)
-      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A1.jpg}
-      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A2.jpg}
-      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A3.jpg}    \\
-      &\multicolumn{1}{c}{$t = 0$}
-      &\multicolumn{1}{c}{intermediate time}
-      &\multicolumn{1}{c}{$t = t_{\text{final}}$}
-  \end{tabular}
-  \end{center}
-  \vspace{-20pt}
-  \caption{\footnotesize
-    \label{fig:self-assembly}
-    Rows (a)-(c) have the same initial configuration
-    but have different boundary conditions $g.$ 
-    In row (a), self-assembly with an amphiphilic boundary
-    condition \eqref{eq:bcs}(a) results in a bilayer pattern shielding
-    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
-    Row (b) shows particles with a hydrophobic intensity that is
-    greater on one side of the particle (magenta) than the other (yellow).
-    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
-    Particles orient like sides to form a checkerboard pattern.\\
-  }
-\end{figure}
-
-The ultimate goal is to use numerical simulations to aid
-the syntheses of soft matter materials.
-Here, mathematical models like the kind we propose are crucial
-because the model parameters control surface properties independently, 
-which can be difficult to accomplish experimentaly 
-~\cite{Bradley2016,Mallory2017,Bradley2017}.
-The ability to translate phenomenological parameters
-into measurable quantities is important. 
-For example, Figure~\ref{fig:OrderPDFs} plots
-the probability density function for 
-relative orientation of adjacent particles
-for the three boundary condition cases:
-(a) is unimodal with a peak at $\theta = 0$,
-(b) is bimodal with peaks at $\theta = 0$ and $\theta = \pi$,
-and (c) is multimodal with peaks at $\theta = 0$ and $\theta = \pm \pi/2$.
-This kind of information can be used as an indicator
-of the collective morphology. As another example,
-it is costly or difficult to manufacture
-Janus particles with uniform shape.
-Thus, we can replace the idealistic boundary
-conditions \eqref{eq:bcs} with a more realistic one like
-\begin{equation}
-\label{eq:vonMises}
-  g_i(\xx) = \sqrt{
-  \frac{\exp( \kappa_i\cos(\theta_i(\xx) - \theta^0_i))}
-  {2\pi r_i I_0(\kappa_i)}}.
-\end{equation}
-Here, the term under the square root is the von Mises distribution with
-director angle $\theta^0_i$ and Bessel function $I_0$ of order zero~\cite{Fisher_1993}.
-The square of this function is asymptotic to a normal distribution with variance
-like $1/\kappa_i$, $\kappa_i \to \infty$. We can replicated surface imperfections
-by randomizing the concentration $\kappa_i$ and particle radii $r_i$,
-for example.
-%\hl{Collaboration with experimental groups will
-%use numerical methods to predict parameter regimes 
-%to control particle-particle interactions.}
-
-%\begin{wrapfigure}[14]{l}{0.5\textwidth}
-%\includegraphics[width=0.5\textwidth]{figures/SpecificAi%m1/multilamelar.pdf}
-%\caption{\label{fig:multilamelar}
-%  Experimentalists can transform unilamellar vesicles to% multilamellar
-%  vesicles by altering the quality of the solvent
-%    \cite{deMeetal21}.
-%  In \eqref{eq:SL}, the solvent quality enters through t%he potential
-%  $f(u)$ and boundary conditions. 
-%}
-%\end{wrapfigure}
-
-\subsubsection{Hydrophobic forces with double-well potential}
-A natural generalization of the potential $f(u) = u^2$
-is a fourth-order, asymmetric double-well potential
-$f(u) = a(u-u_0)^2(u-u_1)^2 + c(u-u_0)^2 + bu$.
-Here, the order parameter $u$ is related to
-the mean number of nearest neighbors
-per water molecule \cite{GoHaKo94}.
-The value $u_0$ gives the absolute minimum in the bulk
-and $u_1$ gives a local minimum at hydrophobic surfaces.
-Figure \ref{fig:CA}(a) illustrates a double-well potential.
-
-\begin{wrapfigure}[29]{l}{1.8in}
-  \vspace{-4pt}
-  \centering
-  \input{figures/doublewell.tikz} 
-  \caption{\label{fig:CA} (a) The double well potential $u_0 =
-  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
-  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
-  and inexact Newton's methods.}
-\end{wrapfigure}
-Equation~\eqref{eq:SL} takes the form of a steady-state Allen-Cahn
-equation. The Allen-Cahn equation is used in phase field formulations of
-immisible fluids, for example.
-PI BQ has developed fast integral equation solvers for
-the Allen-Cahn equation \cite{kro-qua2011, qua2011}.
-PI RR has experience in the 
-simulation and asymptotic analysis of phase field functionals of
-membrane elastic energy, devising functionals for for the squared mean
-curvature (Willmore) energy~\cite{0951-7715-18-3-016}, spontaneous
-curvature~\cite{Du05} and Gaussian curvature energy~\cite{DuEuler}, as
-well as energetic variational approaches to coupling membrane elasticity
-to fluids~\cite{QiangDu09}.
-
-The double-well formulation can potentially 
-explain hydrophobic interaction over the full distance
-regime~\cite{Lum1999, Lin2005, Meyer2006, Ducker2016}.
-Motivated by capillary wetting, Gerhard
-Gompper introduced the double-well model for one-dimensional
-hydrophobic attraction \cite{GoHaKo94}.
-The results improved on previous work~\cite{ErLjCl89,MaRa76},
-but a realistic model of hydrophobic effect 
-probably involves particle shapes in addition to distances of separation.
-The key innovation in the model we propose is that when particles are
-well-separated, the energetic cost for filling the interstitial region
-with $u_1$-phase water is prohibitive and there is a phase shift from
-the $u_0$ to $u_1$ water order---the attraction landscape is more or
-less identical to the linear response theory. Conversely, when particles
-are proximal, it becomes energetically favorable to coalesce
-$u_1$-phases. This introduces a line tension for the phase transition
-which is an effect not present in the one-dimensional model.
-
-Some of the model parameters connect directly
-%connect to long-range decay lengths and energy cost of creating
-%hydrophobic-water interfaces with established ranges of
-to well-established experimental values. Other
-parameters, like the details of the well structure,
-are less well-understood and must be fit to the measured data.
-This improved model will afford greater physical accuracy to
-our simulations.
-%The experimental data on hydrophobic attraction between 
-%is well-established and the literature contains data for a number of
-%solvents and hydrocarbon species.
-%The experimental measurements
-%are well-fit by a double exponential curve in the 10 to 100 nanometer range
-%of separation. Below 10~nm, however, there is an amplification of force
-%and the attraction follows a much steeper force law not accounted
-%for by past phenomenoloical theories~\cite{Lin2005}.
-
-%It may be the case that the double-well formulation recreates the long
-%and short-range interactions. The advantage is that the two-dimensional
-%simulations can replicate the experimental setup better than prior,
-%one-dimensional theoretical work
-
-Specific Aim 2 describes how we propose to deal with the nonlinear
-equation~\eqref{eq:SL} numerically. Once we have established
-implementations, we will consider further generalizations
-of~\eqref{eq:free_energy}, for example to the Oseen-Frank energy for a
-nematic liquid crystal~\cite{doi:10.1137/15M103844X,
-Bartels,AIHPA_1997__66_4_411_0, deGennesProst,HaKiLi86,Virga}. For now,
-Specific Aim 3 describes in detail how we plan to handle charges and
-ions in solution.
-
-%Other approaches may be required if the modified phenomenological
-%theory does not recreate measurements.
-%One such approach is to consider Gaussian fluctuation. Here, we expand
-%the free energy
-%functional around the saddle point solution. The fluctuation energy
-%then involves calculation of the eigenfunctions of the second variation
-%of the free energy. This accounts for the fact that experimental
-%measurements are carried out at finite temperatures, where thermal
-%fluctuations should ideally also be considered. 
-%\todo[inline]{Above, needs citation and more solid explanation}
-
-%
-% The following commented out Nov 6, 2021.
-%
-%
-\begin{comment}
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=0.9\textwidth]{figures/SA1_fig1.pdf}
+%\end{center}
+%\caption{\footnotesize (A--C) The splay ($\Div \mathbf{d}$), 
+%saddle splay ($\det \mathsf{D}$) and twist ($\Curl \mathbf{d}$) elastic distortions of 
+%a monolayer. (D) The monolayer neutral surface $\Sigma$,  
+%director $\mathbf{d}$ and unit normal $\mathbf{n}$ in local coordinates.
+%(E--F) Lipids are able to tilt from  the surface normal, and stretch.
+%(H--J) Intermediates of membrane fusion and (K) experimental image of a stalk \cite{Aeffner2012}. }
+%\label{fig:distortions}
+%\end{figure}
 The goal of Specific Aim 1 is to characterize the material properties of
@@
 \centerline{\includegraphics[width=0.46\textwidth]{Figures/Deformations.pdf}}
+%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
   \vspace{-5pt}
@@
 these controversies due to the assumptions in the HK theory. 
+%Using the HK  model as a base,
+%PI RR and collaborators calculated, for the first time in continuum theory, a least energy path for transitions between planar bilayers, a membrane stalk,
+%hemifusion diaphragm and the fusion pore \cite{RyWaCo13,RyKlYaCo16},
+%and the energies calculated by these continuum studies (Figure \ref{fig:barriers}A),
+%are in agreement with barrier heights derived by molecular dynamics and experimental studies \cite{FrRoPi17}.
+
+%\begin{wrapfigure}[13]{l}{0.5\textwidth}
+%\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
+%\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
+%diaphragm expansion (ii) and pore formation (iii). 
+%(B) Saddle-splay energy for each change in \emph{monolayer} topology
+%calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
+%\label{fig:barriers}
+%\end{wrapfigure}
 
 \sloppy
-The HK framework assumes a three-dimensional lipid monolayer where the
-internal structure consists of straight fibers that represent elongated
-hydrocarbon chains.  The elastic energy density ${\cal W}$ is quadratic
-in the Green-Lagrange strain tensor for this striated, internal
-structure. This energy density decomposes into four, fundamental, and
-independent deformations (Figure~\ref{fig:deformations}): splay ($\Div
-{\bf n}$), twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf
-n}$), and tilt ${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where
-${\bf N}$ is the unit surface normal;
+The HK framework assumes a three-dimensional lipid monolayer where the internal structure
+consists of straight fibers that represent elongated hydrocarbon chains.
+The elastic energy density ${\cal W}$ is quadratic in the Green-Lagrange strain
+tensor for this striated, internal structure.
+%
+%
+%
+%These fibers
+%tilt and stretch with respect to the dividing surface--the surface formed lying between the hydrocarbon chains and polar heads of lipids.
+%Accordingly, the deformation takes the form 
+%\begin{equation}
+%  \label{LMdeformation}
+%{\bf x}(X_1, X_2, X_3) = {\bf x}_0(X_1, X_2) + \zeta(x_0(X_1, X_2), X_3) {\bf n}(x_0(X_1, X_2))
+%\end{equation}
+%where $(X_1,X_2,X_3)$ are points in a reference volume.
+%The map $x_0$ parametrizes the dividing surface $\Sigma$, and the unit vector field ${\bf n}$ parametrizes the
+%direction of the lipid tails in the deformed state \cite{doi:10.1021/jp075641w,KLAUDA20083074}.
+%The parameter $X_3$ and the function $\zeta$ parametrizes the distance along the hydrocarbon chain in the reference state
+%and the deformed state, respectively, and so $0 \leq X_3 \leq \delta$ where $\delta = $ 2.5 nm is a realistic monolayer thickness. 
+%
+%The elastic theory assumes an energy density that is quadratic in the Green-Lagrange strain tensor for ${\bf x}$. 
+%The chains stretch and compress to satisfy incompressibility.
+%Symmetries with respect to mirror reflection and in-plane rotation, the internal structure assumptions and incompressibility
+%lead to an elastic surface energy over the dividing surface $\Sigma$. 
+%
+This energy density decomposes into four, fundamental, and independent
+deformations (Figure~\ref{fig:deformations}): splay ($\Div {\bf n}$),
+twist ($\Curl {\bf n}$), saddle splay ($\det \nabla {\bf n}$), and tilt
+${\bf t}={\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is
+the unit surface normal;
 \begin{equation}
@@
 \end{equation}
-Here, the deformations come with elastic coefficients: the bending
-modulus $\KB$, twist modulus $\KT$, saddle-splay modulus $\KG$, and tilt
-modulus $\KTH$. The parameter $k_0$ is the spontaneous curvature and
-determines the preferred lipid splay~\cite{RoLi15,Kozlov2007}.
+Here, 
+%$(\nabla {\bf n})_{ij} = \partial_{x_j}{\bf n} \cdot {\bf e}_i$ is the surface gradient with
+%orthonormal tangent vectors $\{{\bf e}_1, {\bf e}_2\}$.
+%%\todo[inline]{YNY and BQ: What do you call a coordinate system where the metric is the identity at one point?}
+%Also, the surface divergence 
+%$\Div {\bf n}$ is the trace, and the surface curl $\Curl {\bf n}$ is the anti-trace (sum of the off-diagonal elements), of $\nabla {\bf n}$ respectively.
+%respectively (Figure \ref{fig:distortions}A--C).
+the deformations come with elastic coefficients: the bending modulus
+$\KB$, twist modulus $\KT$, saddle-splay modulus $\KG$, and tilt modulus
+$\KTH$.
+%HK define the tilt vector ${\bf t} = {\bf n}/({\bf N}\cdot {\bf n}) - {\bf N}$ where ${\bf N}$ is the unit surface normal.
+%
+The parameter $k_0$ is the spontaneous curvature and determines the
+preferred lipid splay~\cite{RoLi15,Kozlov2007}.  
+%As an illustration, the
+%lipid DSPC has $k_0 = -0.1$ nm$^{-1}$ 
+%%as a result of  %having a relatively long acyl chain. 
+%and these lipids would preferentially line the upper monolayer in Figure \ref{fig:deformations}B  
+%because the addition of a positive splay 
+%to the negative spontaneous curvature leads to lower energy \cite{Kamal22245, C3SM51829A, RoLi15,FriedSeguin15}.
+%The subtraction of $k_0^2$ makes the energy distortion free
+%\cite{Helfrich73,PhysRevLett.113.248102,Hamm2000}.
 
-Although the HK elastic theory assumes small deformations, Galimzyanov
-{\em et al.}~\cite{C9SM02079A} have shown that energies derived from
-molecular dynamics and those derived from \eqref{ansatz3} are in
-agreement, even when curvatures are large.  Under spatial scales much
-larger than the membrane thickness, membrane energy is
-well-characterized by the Canham-Helfrich energy used throughout the
-fluid-structure literature \cite{QiangDu09, Lowengrub07,KimLai2010_JCP,
-Hu, HuLaiSeolEtAl2016_JCP, qua-bir2014, qua-vee-you2019}. The
-Canham-Helfrich energy is actually a special case of \eqref{ansatz3}
-obtained by setting ${\bf n} =  \pm {\bf N}$ (the $\pm$ depending on
-orientation) and collapsing both monolayers onto the membrane midplane.
+Although the HK elastic theory assumes small deformations, 
+Galimzyanov {\em et al.}~\cite{C9SM02079A} have shown that energies derived from
+molecular dynamics and those derived from \eqref{ansatz3} are in agreement, even when curvatures are large.
+Under spatial scales much larger than the membrane thickness, membrane
+energy is well-characterized by the Canham-Helfrich energy used
+throughout the fluid-structure literature \cite{QiangDu09,
+Lowengrub07,KimLai2010_JCP, Hu, HuLaiSeolEtAl2016_JCP, qua-bir2014,
+qua-vee-you2019}. The Canham-Helfrich energy is actually a special case
+of \eqref{ansatz3} obtained by setting ${\bf n} =  \pm {\bf N}$ (the
+$\pm$ depending on orientation) and collapsing both monolayers onto the
+membrane midplane.
+%There, splay $\Div n$ equal to twice the mean curvature, saddle splay
+%$\det \nabla n$ equal to the Gauss curvature, and both twist and tilt
+%are equal to zero.
 
+%\begin{figure}
+%\begin{center}
+%\includegraphics[width=\textwidth]{figures/SA1_fig2.pdf}
+%\end{center}\vspace{-1.em}
+%\caption{\footnotesize (A) A partially clamped bilayer with mid-plane (dashed curve) under uniform load.
+%The quartic fit comes from continuum theory. 
+%(B) A circular vesicle at equilibrium. (C) The area modulus derives
+%from convexity in energy as a function of radius. 
+%\label{fig:bend}}
+%\end{figure}
+
+% Proposers should address what they want to do,
+% why they want to do it,
+% how they plan to do it,
+% how they will know if they succeed,
+% and what benefits could accrue if the project is successful.
+%\begin{center}
+%Preliminary results
+%\end{center}
+
+%\begin{wrapfigure}[13]{l}{0.5\textwidth}
+%\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1_fig3.pdf}}
+%\caption{{\footnotesize (A) Energy barriers for stalk formation (i), hemifusion
+%diaphragm expansion (ii) and pore formation (iii). 
+%(B) Saddle-splay energy for each change in \emph{monolayer} topology
+%calculated in \cite{RyKlYaCo16}. (C)--(F): Shape transition of vesicle at different values of volume to area ratio from coarse-grained simulations of lipid bilayer membranes \cite{Fu16}.}}
+%\label{fig:barriers}
+%\end{wrapfigure}
+
+%\begin{center}
+%Anticipated model simulations
+%\end{center}
 \subsubsection{Simulations of the HAP model to estimate elastic moduli
 and energy}
+%To characterize material properties of a bilayer, we compare the energies and forces generated by
+%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
+%
+%to examine conduct calculations similar to the example of figure~\ref{fig:flattening}
+%for a wide range of particle parameters and physical parameters in HARP to 
+%
+%{\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
+%as the corresponding energies in the particle system for all reasonable deformation.
+%If this is the case we will 
+%
 \begin{wrapfigure}[11]{r}{0.43\textwidth}
+%\vspace{-0.4cm}
 \centerline{\includegraphics[width=0.42\textwidth]{Figures/Flattening.pdf}}
+%  \centering{\includegraphics[width=0.80\textwidth]{Figures/Deformations.pdf}}
+%\vspace{-0.5cm}
 \caption{\label{fig:flattening} \footnotesize Example of computing
@@
 
+%To characterize material properties of a bilayer, we compare the energies and forces generated by
+%a collection of amphiphilic particles against the energies and forces of a continuum bilayer.
+%We propose to first {\bf (i)} Assess whether the continuum energies \eqref{ansatz3} are the same
+%as the corresponding energies in the particle system for all reasonable deformation.
+%If this is the case we will {\bf (ii)} determine the value of the elastic $\KB$,
+%$\KT$, $\KG$ and $\KTH$, and then {\bf (iii)} understand how the model parameters $\rho,$ $\gamma$, and particle shape map onto elastic moduli. 
+%%
+%%Motivated by our preliminary results \cite{Fu2018_SIAM}
+%%we use realistic values for particle diameter $2$ nm \cite{Boal},
+%%screening length $\rho = 2.5$ nm \cite{Eriksson1989,Lin2005,Parsegian,Israelachvili80,TerziDeserno17}
+%%and interfacial tension $\gamma=4.1$ pN nm$^{-1}$ \cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson}
+%%model parameters. The repulsion strength, repulsion length scale, particle shape (e.g. disks, ellipses), 
+%%particle diameter and the hydrophobic boundary condition \eqref{SL}
+%%are additional parameters defining the coarse-grained representation. 
+%
+%An accurate and robust way to measure material properties is to track the evolution of the bilayer.
+
 Here we start with a particle-based bilayer in a specific
@@
 respectively. 
+%bilayer by steepest gradient descent 
+%with respect to the HARP functional:
+%\begin{equation}
+%\label{SGD}   
+%\frac{\dif {\bf a}_i}{\dif t} = {\bf F}_i,    \quad  \frac{\dif {\bf R}_i}{\dif t}  = {\bf R}_i A({\bf w}_i),\quad i = 1, \dots, N.
+%\end{equation}
+%where that particle centers ${\bf a}_i$ and rotation matrices ${\bf R}_i$ determine the particle configuraton; %
+%$A({\bf w}_i)$ is the skew-symmetric matrix with axial vector ${\bf w}_i$.
+%We solve \eqref{SGD} numerically  using an Adams–Bashforth linear multistep method. 
+%The procedure involves solving \eqref{SL} based off of the current particle configuration.
+%We then use the solution $u$ to calculate the collection of forces and torques \eqref{forceandtorque}, and update the particle configuration
+%through \eqref{SGD}.
+%
 
-This yields a dissipation of the total potential \eqref{eq:total_poten},
-which stabilizes the evolving bilayer shape. Therefore, we reconstruct
-an evolving monolayer dividing surface $\Sigma$ and director field ${\bf
-n}$ by interpolating the particle centers and orientations.
-Using~\eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$
-from the interpolated shapes.
+This yields a dissipation of the total potential \eqref{eq:total_poten}, which
+stabilizes the evolving bilayer shape.
+Therefore, we reconstruct an evolving monolayer dividing surface $\Sigma$ and director field ${\bf n}$ by
+interpolating the particle centers and orientations. Using \eqref{ansatz3}, we calculate a continuum energy $\mathcal{W}$ from the interpolated shapes.
 
-We propose to conduct calculations similar to the example of
-Figure~\ref{fig:flattening} for other elastic moduli such as the
-effective twist modulus $\KT$.  Molecular dynamics investigations find a
-twist modulus about 1 \kBT~\cite{LeVeWa14}, and here, the specific
-non-equilibrium shape consists of a single layer of amphiphilic
-particles on a hydrophobic substrate as illustrated by
-Figure~\ref{fig:deformations}D. Having a nonzero twist requires nonzero
-tilt because the surface gradient of the lipid director equals the
-second fundamental form whenever tilt is zero locally. The twist
-deformation is a fully three-dimensional deformation.
-\S\ref{subsec:specific_aim_3} addresses outstanding implementation
-issues like three-dimensional boundary integral equation solvers.
+%In certain instances, the bilayer evolution involves only one or a few of the four fundamental deformations.
+%When this occurs, the elastic moduli derive from the coefficients of the linear regression between the HAP energy $\Delta \Phi = \Phi - \Phi_0$
+%and continuum energies and $\Delta E = E - E_0$, where  $\Phi_0$ and $E_0$ are respective equilibrium values.
 
-The gradient descent technique is ineffective for measuring the saddle
-splay modulus $\KG$ because the saddle splay energy is largely invariant
-under shape changes.  To evaluate $\KG$, we will combine the present
-particle simulations with the string method from PI RR's work on
-membrane fusion \cite{RyKlYaCo16}. The string method is a numerical
-scheme that finds least energy pathways separating energy basins
-\cite{doi:10.1063/1.2720838}.  In the simplified Canham-Helfrich
-formulation, saddle splay energy is an exact indicator of topological
-transitions, thanks to the  Gauss-Bonnet theorem \cite{TerziDeserno17}.
-More generally, PI RR has shown that saddle splay acts as a topological
-indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}.  As a
-result, saddle splay can be quantified from the transition energies of a
-least energy path of pore formation (Figure~\ref{fig:saddle_splay}).
+%
+%Since it is a particle-based method, the HAP model has a number of advantages over continuum-based descriptions.
+%The elastic energy \eqref{ansatz3} couples director gradients to surface geometry through
+%the tilt vector field.  Furthermore, bilayer energy is the sum of two monolayer
+%energies and the distance between these monolayers varies according to \eqref{LMdeformation}.
+%Effects like tilt and varying monolayer thickness appear at lipid domain boundaries, the edge of nanopores and at the boundary of membrane inclusions \cite{PhysRevE.102.042406}.
+%These effects are present in the proposed formulation, and the particle-based bilayers can break open and join monolayer-wise 
+%as required by fussion and fission. 
+%
+%Bending is the energetically most consequential deformations. To measure a bending modulus,  
+%we deform the midplane of a planar bilayer into the shape of a circular arc.
+%This arc stores bending energy in the form of splay $\Div {\bf n}$, while twist, saddle-splay and tilt deformations are zero.
+%The splay in the two leaflets approximately cancel when added, making the contribution of spontaneous curvature negligible.
+%In the case of a rectangular bialyer, the corresponding elastic energy 
+%$E = \int_{\Sigma} \KB \kappa^2$ where $\kappa$ is the curvature of the curved cross-section $C$.
+%Figure \ref{} shows the approximately linear relationship between $\Delta \Phi$ and $\Delta E$
+%used to values for infer $\KB$.
 
+%
+We propose to conduct calculations similar to the example of Figure~\ref{fig:flattening}
+for other elastic moduli such as the effective twist modulus $\KT$.
+Molecular dynamics investigations find a twist modulus about 1
+\kBT~\cite{LeVeWa14}, and here, the specific non-equilibrium shape consists of
+a single layer of amphiphilic particles on a hydrophobic substrate as
+illustrated by Figure~\ref{fig:deformations}D. Having a nonzero twist
+requires nonzero tilt because the surface gradient of the lipid
+director equals the second fundamental form
+%, and is therefore symmetric,
+whenever tilt is zero locally. The twist deformation is a fully
+three-dimensional deformation. \S\ref{subsec:specific_aim_3} addresses outstanding implementation issues like three-dimensional boundary integral equation solvers.
+
+%for a wide range of particle parameters and physical parameters in HARP to 
+%
+%We will also determine the effective saddle splay modulus $\KG$. 
+The gradient descent technique is ineffective for measuring the saddle splay modulus $\KG$ because
+the saddle splay energy is largely invariant under shape changes.
+To evaluate $\KG$, we will combine the present particle simulations with the string method 
+from PI RR's work on membrane fusion \cite{RyKlYaCo16}. The string method is a numerical scheme that finds
+least energy pathways separating energy basins \cite{doi:10.1063/1.2720838}. 
+In the simplified Canham-Helfrich formulation, saddle splay energy is an exact indicator of topological transitions, 
+thanks to the  Gauss-Bonnet theorem \cite{TerziDeserno17}.
+More generally, PI RR has shown that saddle splay acts as a topological indicator even in the presence of nonzero tilt \cite{RyKlYaCo16}. 
+As a result, saddle splay can be quantified from the transition energies
+of a least energy path of pore formation  (Figure 6).
+%(Figure \ref{fig:saddle_splay}).   
+%Using the string method, we will evaluate the transition energies between the intact pancake shape,
+%and one with a pore. Pore formation in a single bilayer decreases the integral of saddle splay from $4\pi$
+%to $0$. We can, in principle, detect this drop in energy because we have already accounted for the other deformations. 
+%
+%%We will also analyze $\KG$ using a helical geometry. In a helicoid with inclination $m$, the director
+%%gradient is $\nabla n = \begin{pmatrix} 0 & m(m^2+x_1^2)^{-1} \\ m(m^2+x_1^2)^{-1} & 0\end{pmatrix}$ where $x_1$ is the distance to the central
+%%axis. We observe that saddle splay, twist and tilt are zeros, and $\det \nabla n = m^2(m^2+x_1^2)^{-2}$.
+%%In the simulations, the particles forming the helicoid will be confined to two, concentric cylinders. The
+%%continuum energy $\tfrac{1}{2}\KG h(m x_1(m^2+x_1^2)^{-1} + \tan^{-1}(x_1/m)) |_{r_1}^{r_2}$ where $h$, $r_1$ and $r_2$
+%%are the cylinder heights, inner cylinder radius, and outer cylinder radius, respectively. 
+%
+%The proposed particle-based simulations of the HARP model in equations~\ref{SGD} also allow direct examination on the assumption of quadratic form of the elastic energy density.
+%As discussed earlier, recent disagreement in elastic moduli between continuum model and MD simulations originates from such assumption. 
+%The particle-based HARP model provides a unique opportunity to examine the validity of the quadratic elastic energy, and the PIs propose to examine how (if) any deviation from the quadratic elastic energy may depend on the microscopic details of the amphiphilic particles and their interactions.
+%\subsubsection{HK elastic energy form}
+
+%\noindent{\bf{HK elastic energy form:}}
 The field of membrane continuum mechanics still lacks consensus as to
 whether HK energy is the appropriate functional for bilayer energy.
-\textbf{(i)} Researchers have assumed that $\KT = 0$ to effect lateral
-fluidity in membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
-PhysRevE.102.042406}. A value $\KT = 0$, however, makes~\eqref{ansatz3}
-a noncoercive functional. \textbf{(ii)} Recently,~\cite{TerziDeserno17}
-derived a tilt curvature term that was neglected from the HK
-analysis~\cite{Hamm2000}.  Later,~\cite{C9SM02079A}
-and~\cite{PhysRevE.102.042406} independently identified an inconsistency
-in the argument used by~\cite{TerziDeserno17} arising from a transversal
-tilt invariance assumption.  In~\cite{RyKlYaCo16}, PI RR and
-collaborators showed that the tilt vector leads to unphysical cusps
-depending on how one accounts for membrane thickness.  \textbf{(iii)}
-Theoretical analysis of lipid phase transitions predict a negative
-saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
-SIEGEL20085200} that gives rise to a larger energy barrier for monolayer
-fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
+\textbf{(i)} Researchers have assumed that $\KT = 0$ to effect lateral fluidity in
+membranes~\cite{Hamm2000, TerziDeserno17, C9SM02079A,
+PhysRevE.102.042406}. 
+A value $\KT = 0$, however, makes~\eqref{ansatz3} a noncoercive functional.
+%and leads to the nonphysical conclusion that there are bilayers 
+%with $\nabla {\bf n} \to \infty$ but $\mathcal{W} \to 0.$ 
+\textbf{(ii)} Recently,~\cite{TerziDeserno17} derived a tilt curvature
+term that was neglected from the HK analysis~\cite{Hamm2000}.
+Later,~\cite{C9SM02079A} and~\cite{PhysRevE.102.042406} independently
+identified an inconsistency in the argument used
+by~\cite{TerziDeserno17} arising
+from a transversal tilt invariance assumption.
+In~\cite{RyKlYaCo16}, PI RR and collaborators showed that the tilt vector leads to unphysical cusps depending on how one accounts for membrane thickness.  
+\textbf{(iii)} Theoretical analysis of lipid phase transitions predict a
+negative saddle-splay modulus around $-8$ \kBT~\cite{SIEGEL2004366,
+SIEGEL20085200} that gives rise to a larger energy barrier for
+monolayer fusion than is found by experiments~\cite{FrRoPi17, Tran7106,
 TerziDeserno17}.
@@
 \centerline{\includegraphics[width=0.31\textwidth]{Figures/SaddleSplayDiagram.pdf}}
-  \caption{\label{fig:saddle_splay} \footnotesize Example of determining
-  the saddle splay modulus.}
+%  \vspace{-8pt}
+\caption{\label{fig:saddle_splay} \footnotesize Example of determining the
+  saddle splay modulus.}
 \end{wrapfigure}
+%
+%
+%Researchers point out, however, that this theoretical value requires a larger energy 
+%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
+%Furthermore, the stability conditions of \eqref{ansatz3} require $\KG \geq -4\min\{\KB,\KT\}$, suggesting a smaller magnitude for $\KG$.
+
+% The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
+% liquid crystal theory. However, the ``bend'' distortion from nematics  
+% is not present in monolayers since the directors have no dependence in the normal direction.
+% There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection.
 
@@
 the works~\cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000,
-C9SM02079A} utilize an approximate identity for incompressibility as a
-base, so we can considerably improve upon the analysis of monolayer
-energy.
+C9SM02079A} utilize an approximate identity for incompressibility as a base,
+so we can considerably improve upon the analysis of monolayer energy.
 
-\subsubsection{Analysis of the HAP model in terms of the HK functional}
-The HK functional~\eqref{ansatz3} has transformed how scientists understand biological membranes, yet the
-theory has received little attention in terms of
-mathematical analysis. In the calculus of variations, the
+%  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
+%  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
+%  and accounting for these couplings by Taylor expansion  
+%  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
+%
+%The form of the elastic energy density \eqref{ansatz3} is the same as
+%  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
+%  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
+%  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
+%  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
+%  Using this observation, we prove an exact identity 
+%  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
+%  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
+%  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
+%  
+%%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
+%%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
+%%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
+%%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
+%%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
+%%  This gives the continuum elastic energy equals
+%%  \begin{equation}
+%%    \label{eq:twist_energy}
+%%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
+%%  \end{equation}
+%%  which we compare to the HAP simulation data.
+%
+\subsubsection{Analysis on the HAP model in terms of the HK functional}
+The HK functional~\eqref{ansatz3} has had tremendous impact in
+understanding biological membranes, but has received little attention in
+terms of mathematical analysis. In the calculus of variations, the
 principal question is whether a minimizer of an energy functional
@@
 
+%\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of
+%HAP}
 Our goal here is to develop tools that can explain functionals
@@
 
-\end{comment}
+%The HAP energy converges to the surface energy in the limit of vanishing screening length~\cite{Shibata2004}.
+%Also, the boundary layers of the solutions to the screen Laplace equation
+%converge to area measures supported on the particle boundaries \cite{Lee2018, Lin2015, Shibata2004}.
+%These phenomena are analogous to the sharp interface limit in the phase-field functional,
+%and motivate developing the mathematical connections between the HAP energy and
+%the energy functionals used in the gradient theory of phase transitions.
+%formulation~\cite{Modica87, MODICA1987487, LuMo89}.
+%PI RR has worked on phase field approximations of membrane bending
+%energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
+%equation~\cite{1531-3492_2006_2_357, Lee2018}.
+%The screened-Laplace equations~\eqref{SL} is the linearization of the Poisson-Boltzmann equation.
+%One set of questions is to establish the HAP convergence rate as a
+%function of particle geometry~\cite{LuMo89}, which can be used as a
+%benchmark for numerical validation.
+%Ultimately, we will be able to address the so-called $\Gamma$-convergence of energy minimizing
+%particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 
+%The phase field functional approximates the perimeter of sublevel sets
+%of a so-called phase field indicator function. The approximation becomes
+%sharp in the zero interfacial thickness limit and minimizers of the
+%phase field functional converge (after normalization) to the
+%characteristic function of a set solving a perimeter minimization
+%problem
+%
+%
+
+%In the context of microstructure fabrication, the particle configurations maximally sequester hydrophobic surfaces.  
+%As an illustration, consider two fluid-bound plates $P_1$ and $P_2$ that geometrically flat and hydrophobic all sides.
+%We conjecture that in the zero-screening length limit, the plates have overlapping faces, and that 
+%\begin{equation}
+%\lim_{\rho \to 0} \min \Phi_{\text{hydro}} = \max_{\mathcal{X}} A(P_1 \Delta P_2)
+%\end{equation}
+%$A(P_1 \Delta P_2)$ is the area of the symmetric difference of the overlap.  
+%\cite{https://doi.org/10.1038/s41467-019-09787-6}
+%
+%
+%% It may come as a surprise then that the field of membrane continuum mechanics still lacks consensus as to
+%% whether \eqref{ansatz3} contains a complete list of consistent deformations.
+%%\textbf{(i)} Researcher have assumed that $\KT = 0$ \cite{Hamm2000, TerziDeserno17, C9SM02079A, PhysRevE.102.042406}.
+%%  Based on \eqref{eq:twist_energy}, a value $\KT = 0$ leads to the
+%%  unphysical conclusion that there are bilayers with $\nabla {\bf n} \to \infty$ but $E \to 0.$ 
+%%  \textbf{(ii)}
+%%  Recently, \cite{TerziDeserno17} derived a tilt curvature term that was neglected from the HK analysis \cite{Hamm2000}.
+%%  Later, \cite{C9SM02079A} 
+%%  and \cite{PhysRevE.102.042406} independently identified an inconsistency \cite{TerziDeserno17} arising
+%%  from a transversal tilt invariance assumption.
+%%  The PI Ryham showed,  that the tilt vector $T = {\bf n}/{\bf n}\cdot {\bf N} - {\bf N}$ leads to unphysical cusps when constraining membrane thickness  \cite{RyKlYaCo16}.  
+%%  \textbf{(iii)}
+%%  Theoretical analysis of lipid phase transitions predict a negative saddle-splay modulus around $-8$ \kBT\;
+%%\cite{SIEGEL2004366,SIEGEL20085200}. Researchers point out, however, that this theoretical value requires a larger energy 
+%%barrier for monolayer fusion than is found by experiment \cite{FrRoPi17,Tran7106,TerziDeserno17}.
+%%Furthermore, the stability requirements of \eqref{ansatz3} are $\KB > 0$, $K_T > 0$, $\KG \geq -4\KB$
+%%and $\KG \geq -4\KT$. Molecular dynamics investigations find a twist modulus about 1 \kBT \cite{LeVeWa14},
+%%suggesting a somewhat smaller magnitude for $\KG$.
+%
+% 
+%%The form of the elastic energy density \eqref{ansatz3} is the same as
+%%the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
+%%a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
+%%The constants $\KB$, $\KT$  and $\KG$ play the same role as the Frank constants $K_1$, $K_2$ and $K_{24}$
+%%liquid crystal theory. However, the ``bend'' distortion from nematics  
+%%is not present in monolayers since the directors have no dependence in the normal direction.
+%%There is also no ``spontaneous twist'' in monolayers due to invariance under mirror reflection. 
+%%  
+%%  We suspect the reason why, after twenty years, the field has yet to reach a consensus 
+%%  as to the form of \eqref{ansatz3} has to do with the Taylor expansions used to derive the elastic energy density. 
+%%  Past researchers expressed the strain tensor in
+%%  terms of the orthonormal frame $\{{\bf e}_1, {\bf e}_2, {\bf N}\}$ with surface tangent vectors ${\bf e}_i$ and surface normal ${\bf N}$.  
+%%  In this frame, there is a coupling between the gradients of all three terms ${\bf x}_0,$ $\zeta$ and ${\bf n}$ of the deformation \eqref{LMdeformation}.
+%%  Subtle differential geometric arguments are needed to evaluate the terms in the Taylor expansion,
+%%  and these couplings can lead to an energy density with more than ten parameters, for example \cite{PhysRevE.102.042406}.
+%%
+%%  We will revisit the HK analysis to see if any of the aforementioned inconsistencies can be resolved.
+%%  As a main analytical innovation, we have found that expanding the strain tensor in
+%%  terms of the orthonormal frame $\{{\bf e}'_1, {\bf e}'_2, n\}$ with ${\bf e}'_i$ perpendicular to ${\bf n}$
+%%  greatly simplifies the expansion because it decouples the gradient terms. As an illustration, the prominent works
+%%  \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
+%%  incompressibility condition for the lipid elongation function $\zeta$ from \eqref{LMdeformation} that is only approximately true. 
+%%  However, we prove that when expressed in the $\{{\bf e}'_1, {\bf e}'_2, n\}$ frame, the incompressility condition is \emph{exact}
+%%  and is given by a Steiner-type polynomial in terms of $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
+%%  Aside from the special case of zero tilt, \cite{Hamm2000} and coworkers seem to have been unaware of this result.
+%
+%Our investigations will leave open the possibility that the free energy of monolayers and bilayers is non-local. 
+%We have shown that hydrophic attraction is a non-additive force, meaning the force of attraction between two
+%particles is dependent on the position a third or more particles \cite{SilveraBatista1242477}.
+%Conceptually, this would arise in continuum theory if two monolayer surfaces
+%had a different elastic energy density despite having locally identical curvatures and directors.
+%The boundary integral formulation described in Specific Aim 3 easily accomodates additional linear PDE and
+%we will extend our study to include charge lipids and weak electrolytes \cite{C9SM00772E}.

### 2022-09-28 NSF2022/Description/specificaim3.tex
starting proposal

--- 2022-09-27 NSF2022/Description/specificaim2.tex
@@
-\subsection{Specific Aim 2: Efficient, high-order methods for
+\subsection{Specific Aim 3: Efficient, high-order methods for
 large-scale simulations}
+\label{subsec:specific_aim_3}
 % ----------------------------------------------------------------------
@@
 and hydrophobic stress balance.
+
+The hydrophobic interactions come from the tendency of particles to
+minimize the free energy of the structure of the surrounding water
+molecules. The HAP model uses the free energy
+\begin{align}
+\label{eq:free_energy}
+F[u] = C \int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} f(u) \,dx
+\end{align}
+where $u$ is an order parameter for the structure of water, $\rho$ is a
+decay length, $C$ is a constant, and $f(u)$ is a potential.
+Minimizing $F[u]$ requires that $u$ satisfies 
+\begin{align}
+  \label{eq:SL}
+  -\rho^2 \Delta u + f'(u) = 0  \text{ in } \Omega,\quad u = g
+  \text{ on } \Omega.
+\end{align}
+where the boundary condition $g$ is a material label that is transported
+with the particle motions.
 

### 2022-10-04 NSF2022/Description/priorsupport.tex
working on proposal

--- 2021-11-15 NSF2021/Description/priorsupport.tex
@@
 algorithms, and their applications to fluid dynamics for many years.
-Their recent collaborative work on the HAP model in two
-dimensions~\cite{FuQuRyYo20} has provided a solid foundation for the
-proposed research.
+Their recent collaborative works on the HAP model in two
+dimensions~\cite{FuQuRyYo22, fu-ryh-qua-you2022} have provided a solid
+foundation for the proposed research.
 

### 2022-10-04 NSF2022/Description/specificaim1.tex
working on proposal

@@
 and vesicles \cite{Fu2018_SIAM} and recreates the tank-treading
-phenomenon in external shear flows \cite{FuQuRyYo20}.
+phenomenon in external shear flows \cite{FuQuRyYo22}.
 While the results show great promise in the field of collective body

### 2022-10-04 NSF2022/Description/background.tex

@@
 used by all the PIs to show how amphiphilic Janus particles (JP)
-self-assemble into a vesicle-like structure~\cite{FuQuRyYo20}.
+self-assemble into a vesicle-like structure~\cite{FuQuRyYo22}.
 Janus particles are typically spherical particles with a biphasic
@@
 derives elastic energies assuming parameters for the water structure and
-particle shape \cite{Fu2018_SIAM, FuQuRyYo20, doi:10.1063/5.0009734,
+particle shape \cite{Fu2018_SIAM, FuQuRyYo22, doi:10.1063/5.0009734,
 LiAn-Chang16}.  Immersed boundary and boundary integral are highly

### 2022-10-04 NSF2022/Description/specificaim3.tex

@@
 dynamics~\cite{RYHAM20112929}, set the rate of dissipation. In Specific
-Aim 2, we propose novel and efficient high-order numerical methods to
+Aim 3, we propose novel and efficient high-order numerical methods to
 simulate dynamic assembly of particles under the HAP in a viscous
-solvent. As described in~\eqref{eq:stokes} and illustrated in
-Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
-equations for an incompressible, viscous fluid, and these equations are
-coupled to the screened-Laplace equation~\eqref{eq:SL} through viscous
-and hydrophobic stress balance.
+solvent.
 
@@
 where the boundary condition $g$ is a material label that is transported
-with the particle motions.
+with the particle motions. The motion of the solvent phase is modeled by
+the Stokes equations for an incompressible, viscous fluid, 
+\begin{align}
+  -\mu \Delta \uu + \nabla p = 0, \quad \nabla \cdot \uu = 0,
+  \label{eq:stokes}
+\end{align}
+with vanishing conditions at infinity. The hydrodynamic and
+hydrophobicity are copuled through viscous and hydrophobic stress
+balance.
 
-The HAP model requires solving exterior problems for the order
-parameter~\eqref{eq:SL} and the Stokes equations~\eqref{eq:stokes}. We
-will develop methods based on combinations of volume and layer
-potentials, and inexact Newton's method. Numerical methods to solve
-these integral equations (IEs) have several advantages over their
+We will develop methods based on combinations of integral equation-based
+volume and layer potentials, and inexact Newton's method to solve the
+elliptic PDEs~\eqref{eq:SL} and~\eqref{eq:stokes}. Numerical methods to
+solve these integral equations (IEs) have several advantages over their
 PDE-based counterpart: by construction, they satisfy far-field and mass
@@
 powerful tool to simulate two-dimensional suspensions of amphiphilic
-particles~\cite{Fu2018_SIAM, FuQuRyYo20}. Moreover, elements of these
-formulations have been described in three dimensions~\cite{ying_2006,
-manasthesis, rac-gre2016}. This proposal will extend the two-dimensional
+particles~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022}. Moreover,
+elements of these formulations have been described in three
+dimensions~\cite{ying_2006, manasthesis, rac-gre2016,
+koh-cor-che-vee2021}. This proposal will extend the two-dimensional
 methods to more general amphiphilic particle models that
@@
 three dimensions. These methods will be motivated by models and analysis
-developed in Specific Aims 1 and 3. \S\ref{subsec:AC} describes how the
+developed in Specific Aims 1 and 2.  \S\ref{subsec:AC} describes how the
 non-linear Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved

### 2022-10-11 doc/PRF2022/Reviews/ResponseToReviewer1.tex
adding reviews

\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Cecile Cottin-Bizonne,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. Changes to the manuscript
from Reviewers 1 and 2 are colored in \textcolor{red}{red} and 
\textcolor{magenta}{magenta}, respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei Fu, Rolf Ryham, Bryan Quaife, and Yuan-Nan Young

\section*{Response to Reviewer 1}
\noindent
\comment{The manuscript discusses the self-assembly of amphiphilic Janus
particles and their dynamics in various flow conditions. Different
morphologies are recovered for different boundary conditions which are
developed by varying the hydrophobicity on Janus particle surface.
These various boundary conditions give rise to unilamellar,
multilamellar and striated structures. Finally, these structures are
subjected to linear shear flow and Taylor-Green flow. The subject of
study is interesting to soft matter community.}

\begin{itemize}
  \item {\bf Response to Summary}: 	
  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
  \end{quotation}
\end{itemize}

\noindent
\comment{My main criticism is
the following: 1. Unilamellar, multilamellar and striated structured are subjected to
various flow conditions, with increasing shear rate or strength of the
flow (for TG case). For all structures in both flows, the main result
is that these structures break eventually either for increased shear
rate or increased flow rate. But this is expected. What do all these
results mean? I feel that a constructive message is missing.}

\begin{itemize}
  \item Response:

  \item Change:

\end{itemize}

\noindent
\comment{2. And the discussion section is not written well. Please write it
properly.}

\begin{itemize}
  \item Response:

  \item Change:

\end{itemize}

\noindent
\comment{Minor comments: 1. Page 18: The section ends with 
the statement “In previous work, Fu
et al. [18] determined the permeability constant of particle-based
vesicles in the context of shear background flow [53, 54]. “. I find
the statement abrupt and not related to the earlier text.}

\begin{itemize}
  \item Response:

\item Change:

\end{itemize}

\noindent
\comment{2. Fig. 8: Please describe what the arrows mean in (a), (b), (c) and
(d).}

\begin{itemize}
  \item Response:

  \item Change:

\end{itemize}

\end{document}

### 2022-10-21 NSF2022/Description/specificaim2.tex
adding specific aim 2

@@
-\subsection{Specific Aim 2: Efficient, high-order methods for
-large-scale simulations}
-% ----------------------------------------------------------------------
-Over the past decade, there has been an explosion of interest in
-small-scale processes that utilize capillary forces and van der Waals
-interactions to coordinate movement and bind microscopic components in
-solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}. Additionally,
-hydrodynamic interactions are central to fabricate complex,
-three-dimensional microstructures~\cite{Dasgupta2017, Leong2007,
-Reynolds2019, Cho2010}. Hydrodynamic effects cannot be ignored since
-they, like for the rates of biological functions like pore
-dynamics~\cite{RYHAM20112929}, set the rate of dissipation. In Specific
-Aim 2, we propose novel and efficient high-order numerical methods to
-simulate dynamic assembly of particles under the HAP in a viscous
-solvent. As described in~\eqref{eq:stokes} and illustrated in
-Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
-equations for an incompressible, viscous fluid, and these equations are
-coupled to the screened-Laplace equation~\eqref{eq:SL} through viscous
-and hydrophobic stress balance.
+\subsection{Specific Aim 2: Coarse graining and continuum models}
 
-The HAP model requires solving exterior problems for the order
-parameter~\eqref{eq:SL} and the Stokes equations~\eqref{eq:stokes}. We
-will develop methods based on combinations of volume and layer
-potentials, and inexact Newton's method. Numerical methods to solve
-these integral equations (IEs) have several advantages over their
-PDE-based counterpart: by construction, they satisfy far-field and mass
-conservation conditions; only $\partial\Omega$ needs to be discretized
-for layer potentials; carefully chosen IEs result in a well-conditioned
-linear system that is solved with a mesh-independent number of GMRES
-iterations; and high-order or spectral accuracy is attainable with
-appropriate quadrature methods. The PIs have demonstrated that IEs are a
-powerful tool to simulate two-dimensional suspensions of amphiphilic
-particles~\cite{Fu2018_SIAM, FuQuRyYo20}. Moreover, elements of these
-formulations have been described in three dimensions~\cite{ying_2006,
-manasthesis, rac-gre2016}. This proposal will extend the two-dimensional
-methods to more general amphiphilic particle models that
-satisfy~\eqref{eq:SL}, and all the methods can naturally be extended to
-three dimensions. These methods will be motivated by models and analysis
-developed in Specific Aims 1 and 3. \S\ref{subsec:AC} describes how the
-non-linear Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved
-using an IE formulation. Then, \S\ref{subsec:NumericalIssues} describes
-how we will combine preconditioning strategies with fast summation
-methods to accelerate the time to solution, and
-\S\ref{subsec:timeStepping} describes adaptive time stepping methods.
-
-\subsubsection{Iterative methods for the Allen-Cahn HAP model}
-\label{subsec:AC}
-
-The PIs have developed numerical methods to solve~\eqref{eq:SL} when
-$f(u) = u^2$---this choice results in the linear screened Laplace
-equation. For a more general $f$, such as a double well potential, we
-will interpret the solution of~\eqref{eq:SL} as the root finding problem
-for
-\begin{align}
-  \label{eq:F}
-  J[u] = -\rho^2 \Delta u + \tfrac{1}{2}f'(u).
-\end{align}
-This non-linear PDE will be solved with Newton's method
-\begin{align*}
-  u^{N+1} = u^{N} - \alpha (dJ^N)^{-1} J(u^N),
-\end{align*}
-where $dJ^N = -\rho^2 \Delta + \tfrac{1}{2}f''(u^N)$ is the Fr\'{e}chet derivative
-of $F$, and $\alpha$ is the step size which will be determined using
-backtracking. As expected, the biggest computational challenge is
-solving $- \rho^2 \Delta v + \tfrac{1}{2}f''(u^{N}) v = J[u^N]$. Solving this
-variable coefficient PDE with an integral equation is challenging since
-a fundamental solution is not readily available. We propose to instead
-use an inexact Newton's method where $dJ^{-1}$ is defined in terms of
-the continuous, piecewise quadratic approximation
-\begin{align*}
-  f(u) \approx \tilde{f}(u) = bu + \begin{cases}
-    a(u - u_0)^2, &\mbox{if } u \leq (u_0 + u_1)/2, \\
-    (u - u_1)^2 + \tfrac{1}{4}(a-1)(u_0-u_1)^2 , &\mbox{if } u > (u_0 + u_1)/2,
-  \end{cases}
-\end{align*}
-where $a>0$, and the resulting inexact Newton's method requires solving
-the piecewise constant PDE
-\begin{align}
-  \label{eq:screenedPoisson}
-  -\rho^2 \Delta v + \tfrac{1}{2}\tilde{f}''(u^{N})v = J[u^N],
-\end{align}
-which is a screened Poisson equation with piecewise a constant screening
-coefficient. We test the efficacy of exact and inexact Newton's method
-applied to~\eqref{eq:F} in $(0,1)$ by discretizing $dJ$ with a
-second-order finite difference method. The choice of parameters $a$,
-$b$, $u_0$, and $u_1$ result in the double well potential illustrated in
-Figure~\ref{fig:CA}(a), and both the exact and inexact Newton's methods
-converge to the solution in Figure~\ref{fig:CA}(b).
-Figure~\ref{fig:CA}(c) shows the max norm of the residual at each Newton
-iterate when using the exact second derivative (red curve) and the
-piecewise constant approximate (blue curve). While the inexact Newton's
-method requires roughly twice as many iterations to reach of a tolerance
-of $10^{-4}$, each iteration is significantly cheaper in higher
-dimensions.
-
-Having demonstrated that the inexact Newton method converges in one
-dimension, it will be coupled with IE formulations to 
-solve~\eqref{eq:SL} in two and three dimensions. We first partition
-$\Omega$ into $\Omega_0 = \{\xx \in \Omega \:|\: u(\xx) < (u_0 +
-u_1)/2\}$ and $\Omega_1 = \{\xx \in \Omega \:|\: u(\xx) > (u_0 +
-u_1)/2\}$, and we let $\Lambda = \{\xx \in \Omega \:|\: u(\xx) = (u_0 +
-u_1)/2 \}$ be their common boundary, and we let $G_0$ be the fundamental
-solution of $(-\rho^2 \Delta + a)$ and $G_1$ be the fundamental
-solution of $(-\rho^2 \Delta + 1)$. Then, the solution
-of~\eqref{eq:screenedPoisson} can be written as $u = u^P + u^H$ where
-$u^P$ is a volume potential and $u^H$ is a layer potential. The volume
-potential is
-\begin{align*}
-  u^{P}(\xx) = \int_{\Omega_i} G_i(\xx,\yy) J[u^N](\yy)\, d\yy, 
-    \quad i = 1,2,
-\end{align*}
-but it is discontinuous across $\Lambda$ and does not satisfy the
-prescribed hydrophobic boundary conditions on the particles $\Gamma_i$.
-Assuming the particles are entirely contained in the hydrophobic region,
-the boundary conditions will be enforced with the layer potentials
-\begin{align*}
-  u^{H}(\xx) = \begin{cases}
-    \displaystyle\int_{\Lambda} G_0(\xx,\yy) \eta_0(\yy) \, ds_\yy + 
-    \displaystyle\int_{\Gamma} \pderiv{}{\nn_\yy} G_0(\xx,\yy)
-      \sigma(\yy) \,ds_\yy, \quad & \xx \in \Omega_0, \\
-    \displaystyle\int_{\Lambda} G_1(\xx,\yy) \eta_1(\yy) \, ds_\yy,
-     & \xx \in \Omega_1.
-  \end{cases}
-\end{align*}
-The density functions $\sigma$, $\eta_0$, and $\eta_1$ are determined so
-that $u = u^P + u^H$ satisfies the hydrophobic boundary condition on
-$\Gamma = \cup_i \Gamma_i$, and that it is continuous and differentiable
-across $\Lambda$. This approach of using IEs to solve elliptic PDEs with
-piecewise constant coefficients has successfully been used in other
-application such as scattering~\cite{hyu-bar2014, che-cho-cai2018}.
-
-% ----------------------------------------------------------------------
-\subsubsection{Accelerating the iterative solvers}
-\label{subsec:NumericalIssues}
-
-When solving for the density functions $\eta_0$, $\eta_1$, and $\sigma$,
-a carefully chosen IE formulation only requires a mesh-independent
-number of GMRES iterations~\cite{cam-ips-kel-mey-xue1996}. Therefore,
-the required CPU time is proportional to the cost of a matrix-vector
-multiplication that can be performed in optimal or near-optimal time
-with the fast multipole method (FMM)~\cite{fmm5} and its
-extensions~\cite{fmm1, fmm2, fmm3, fmm4, fmm6, fmm7, fmm8}. PI BQ is
-experienced with applying FMMs for the Stokes
-equation~\cite{qua-bir2014, bys-sha-qua2020} and the screened Laplace
-equation~\cite{kro-qua2011, qua2011}. Furthermore, to reduce the number
-of GMRES iterations, the efficacy of preconditioning strategies such as
-the inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017} and
-domain decomposition~\cite{che-bir2021} will be investigated. PI BQ used
-the IFMM to precondition Stokes equations~\cite{qua-cou-dar2018}. A
-suite of other preconditioners including sparse approximate
-inverses~\cite{che2000} and multigrid~\cite{hem-sch1981, sch1982} will
-be investigated.
-
-% ----------------------------------------------------------------------
-\subsubsection{Eliminating contact with adaptive time stepping}
-\label{subsec:timeStepping}
-
-A numerical issue when simulating the self-assembly of amphiphilic
-particles is avoiding particle collision. The hydrophobic attraction
-potential drives the amphiphilic particles towards one another and this
-leads to physical contact in finite time. Such particle collisions in a
-dense, rigid-body suspension are a great challenge and can be a
-bottleneck in large-scale simulations. We propose to remedy this
-computational challenge by developing novel high-order adaptive time
-stepping methods. PI BQ developed a high-order adaptive time
-stepping method for hydrodynamic suspensions \cite{qua-bir2016}, and it
-has served as a robust method to simulate processes including mixing and
-adhesion in suspensions~\cite{qua-vee-you2019, kab-qua-bir2017}.
-Following this previous work, the proposed work will use a spectral
-deferred correction method~\cite{dut-gre-rok2000} since it iteratively
-applies a low-order, single-step method to achieve high-order accuracy.
-At each time step, we will compute the total force and torque of the
-system which is computationally cheap and physically zero, and therefore
-provides an estimate of the local truncation error. PI BQ's experience
-is that error estimates based on physical constraints, such as force-
-and torque-free conditions, appropriately determine adaptive time step
-sizes so that the dynamics are resolved without the computational
-expense of embedded Runge-Kutta methods, step-doubling, Richardson
-extrapolation.
+\label{subsec:specific_aim_2}

### 2022-10-21 doc/PRF2022/Reviews/ResponseToReviewer2.tex

\documentclass[11pt]{article}

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Cecile Cottin-Bizonne,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. Changes to the manuscript
from Reviewers 1 and 2 are colored in \textcolor{red}{red} and 
\textcolor{magenta}{magenta}, respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei Fu, Rolf Ryham, Bryan Quaife, and Yuan-Nan Young

\section*{Response to Reviewer 2}
\comment{
\noindent
I report here on the manuscript "Effects of tunable hydrophobicity on the
collective hydrodynamics of Janus particles under flows" by Szu-Pei Fu et al.
submitted for publication to Physical Review Fluids. The authors have conducted
numerical hydrodynamic simulations in 2D on the self-assembly and dynamics of
nanoscale Janus particles under simple shear flow and Taylor-Green flow using
the method of discretized boundary integrals to describe the motion of the
particles immersed in 2D Stokes flow. The Janus character of the individual
particles is realized by tuning the local hydrophobicity/hydrophilicity. The
authors have previously shown that this system forms vesicle-like structures and
investigated such structures in simple shear flow (reference [18] in the paper).
The authors now continue this work by studying different model systems by tuning
the local hydrophobicity to model (i) bilayer-forming amphiphilic particles,
(ii) formation of multilamella structures, and (iii) formation of block-chain
structures, all pre-assembled under quiescent flow conditions. These equilibrium
structures are then studied under flow of varying shear rate. The different
structures are characterized by (i) a deformation order parameter, (ii) an
orientation order parameter, and (iii) the free energy. The authors study the
dynamics of the structures under flow, when mapping to physical scales, on the
order of micro-seconds, for nanometer-sized particles and shear rates on the
order of smaller than nanoseconds$^{-1}$. The effect of shear on the conformations
is analyzed in detail, and the results are discussed with respect to related
previous literature.\\ \\
In principle I think the paper meets the criteria to be considered as an article
for Physical Review Fluids in terms of originality, quality, and presentation.
However, I am not yet convinced about the potential applicability to real
systems, as raised below:}

\begin{itemize}
  \item {\bf Response to Summary}: We thank the Reviewer for this positive appraisal of 
our manuscript. 
\end{itemize}

%  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
%  \end{quotation}

\noindent
\comment{1) The authors study the nano-hydrodynamics around the JPs very carefully by
modeling the flow as a continuous 2D Stokes flow. While I understand that
modeling the dynamics in 2D instead of 3D is fair, i.e. their results should in
principle be extensible to 3D, my major concern is the absence of thermal
fluctuations. They are expected to be very relevant on the nanometer scale,
regarding self-assembly, dynamics and stability of the JP structures.
}

\begin{itemize}
  \item Response:

  \item Change:

\end{itemize}

\noindent
\comment{2) The shear rates studied are below nanoseconds$^{-1}$. What is the relevance of
such small shear rates in real (biological) systems? Furthermore, in presence of
noise, I would expect that the JP diffusive timescale is much smaller then the
shear flow time scale, and hence effectively the associated Peclet number, i.e.
importance of flow compared to noise, is negligible in this system?}

\begin{itemize}
  \item Response:

  \item Change:

\end{itemize}

\noindent
\comment{Before I can recommend publication, the authors should clarify these points, in
particular justify why noise can be neglected, and why such small shear rates
are relevant.}

\begin{itemize}
  \item Response: 
\end{itemize}

\end{document}

### 2022-11-01 NSF2022/Description/background.tex
pushed organizational changes

@@
+\section{Comments on structure of proposal}
+
+\begin{itemize}
+\item Background: should be much broader, example applications
+\begin{itemize}
+\item Vesicles for drug delivery
+\item Extracellular vesicles (EVs) are newly recognized as important vectors for carrying and spreading antibiotic resistance genes (ARGs)
+\item Building with nanoparticles, from the bottom up
+\item Motivation:
+MD and continuum simulations are clumsy; work over limited time/length scales; we need a
+a robust method to complement established methods and processes.
+The present proposal is our first attempt at creating such a model.
+\end{itemize}
+
+\item Model formulation: put the applied math formulas up front; change name ``particle'' to something else
+\item Numerics: discuss advantages and challenges if BIE
+
+\item Summary of respective resumes/contributions to this area
+
+\item Specific Aim 1: Measuring material properties of amphiphile self-assembly
+\item Specific Aim 2: Efficient, high-order methods for large-scale simulations
+\item Specific Aim 3: Coarse graining and continuum models
+
+\item Broader Impacts
+\item Intellectual Merit
+\item Prior NSF support
+
+\item Other notes: do not waste the CV and prior work section:
+play up significance of works.
+``In our JFM/Nature/Biophys J paper'', ``In our much noticed,'' ``In our highly cited/referenced'', ``Detailed modeling and simulation which is the crown jewel of
+applied mathematics''.
+Use suggested reviewers to our advantage.
+
+%Here is an interesting problem.
+%Here is how it’s addressed.
+%Here is what we are going to do.
+
+\end{itemize}
+
 \noindent
@@
 \label{sec:background}
-%The goal of this collaborative proposal is to use mathematical modeling
-%and numerical simulations to investigate the dynamic self-assembly of
-%amphiphilic particles interacting via hydrophobic forces in solvent.
-This collaborative proposal aims to advance
-the mathematical modeling and numerical simulation
-of dynamic self-assembly of amphiphilic particles interacting
-via hydrophobic forces in solvent.
-Amphiphilic particles such as lipid molecules possess both hydrophobic
-and hydrophilic structures. In a viscous solvent they self-assemble into
-meso-/macroscopic structures such as micelles and bilayers of lipids to
-shield their hydrophobic surfaces from contact with the solvent
-molecules e.g., waters. Such self-assembly of amphiphiles via hydrophobic
-forces is ubiquitous in biology~\cite{Israelachvili1954},
-and has been a major source of nonspecific interactions 
-in soft matter~\cite{Sanchez-IglesiasEtAl2012_ACSNano,
-AltantzisEtAl2013_PSC, XieYangLuEtAl2020_COCIS}. 
-%The proposed research aims to provide fundamental understanding of the
-%self-assembly dynamics of amphiphilic particles so to design smart
-%materials of desirable properties by
-%tuning the geometry and properties of the amphiphilic particles.
 
-%The hydrophobic force arises when polar solvent molecules come in
-%contact with a non-polar substance, such as hydrocarbon or vapor.
-%In a polar solvent (like water), the dipole-dipole interaction between
-%solvent molecules form a loosely structured hydrogen-bond network where
-%each solvent molecule shares bonds with neighboring molecules at any
-%given time \cite{Israelachvili1954}. In the presence of a non-polar
-%solvent molecule loses the ability to form hydrogen bonds
-%in one direction. 
-%The decrease in the number of hydrogen bonds causes a reorientation,
-%or structural change, in the surrounding water that is energetically
-%very unfavorable \cite{Bjorneholm2016}.
+\textbf{Very broad introduction}
 
-\begin{wrapfigure}[15]{r}{0.37\textwidth}
-\vspace{-8pt}
-\centerline
-{
-\includegraphics[width=0.36\textwidth]{figures/LongRangeForce.jpg}
-}
-%\vspace{-20pt}
-\caption{\label{fig:force_distance}
-Force-distance curve for surfactant
-monolayers adsorbed on mica reveals a long-range
-attraction~\cite{Lin2005}.}
+\subsubsection{Problem formulation}
+%\begin{wrapfigure}[h!]
+\begin{wrapfigure}[11]{r}{0.55\textwidth}
+ \centering
+ \vspace{-3pt}
+ \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.jpg}
+ \caption{\label{fig:flow_map}
+   In the HAP formulation,
+   a system of exterior problems 
+   defines the hydronamic and hydrophobic interactions.
+   The colormap is for the intensity of $u$.
+   The dynamics lead to self-organized structures like a vesicle bilayer.}
 \end{wrapfigure}
 
-Macroscopically, the substantial free energy of placing hydrophobic
-surfaces in contact with water is roughly proportional to the surface
-area of the contact region~\cite{Bjorneholm2016}.
-%As a result, hydrocarbon solutes have a large interfacial tension 
-%and try to minimize their surface area when in water. 
-At the microscopic level, however, there is long-range interaction
-between hydrophobic surfaces. Two hydrophobic surfaces, in particular,
-separated by water over some distance, experience an attraction
-called the
-hydrophobic force~\cite{Lum1999, Meyer2006, Hammer2010, KaScScNe16}.
-The force is nonadditive~\cite{SilveraBatista1242477},
-and measurements show that the hydrophobic force decays exponentially with a
-decay length on the order of 1--10 nm~
-\cite{Israelachvili1984,Marcelja1977,Christenson2001,Lin2005,Taetal13}
-(Figure \ref{fig:force_distance}).
+The mathematical formulation is a nonlinear system for the dynamics of a
+collection of particles. The interactions come from a system of 
+partial differential equations (PDEs) that comprise hydrodynamic
+interactions and hydrophobic interactions.
+%The formulation prevents particle collisions through excluded volume
+%potentials. 
+The hydrodynamic interactions come from the mobility problem for rigid
+particles immersed in a viscous solvent. We then use a
+second-order Adams-Bashforth method to update the particle configuration.
+Assuming inertial terms are
+negligible, the particle motion is goverened by the Stokes equations
+\begin{subequations}
+  \label{eq:stokes}
+  \begin{alignat}{3}
+  \label{eq:stokes1}
+  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
+    \label{eq:stokes2}
+  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
+\label{eq:stokes3}
+  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
+  \end{alignat}
+\end{subequations}
+%\begin{alignat}{3}
+%\label{eq:stokes1}
+%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
+%    && \xx \in \Omega, \\
+%\label{eq:stokes2}
+%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
+%\label{eq:stokes3}
+%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
+%\end{alignat}
+%
+where $\uu$ is the velocity and $p$ is the pressure of the solvent,
+$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
+viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
+particles and changes shape as the particles move.
+Since the particles are rigid, the solvent velocity satisfies
+a no-slip boundary condition for a rigid body motion 
+%\begin{align}
+%\label{eq:rigid_bc}
+%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
+%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
+%\end{align}
+on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
+and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
+Given imposed forces acting on each
+particle, the \emph{mobility problem} consists of finding
+translational and angular velocities so that viscous fluid forces
+balance the imposed forces.
 
-Motivated by its broad applicability to biology, chemistry, and engineering,
-PIs RR and YNY developed a mathematical model, called the
-hydrophobic attraction potential (HAP) model~\cite{Fu2018_SIAM},
-that is based on
-the linear response of water to surface perturbations. This model was
-used by all the PIs to show how amphiphilic Janus particles (JP)
-self-assemble into a vesicle-like structure~\cite{FuQuRyYo22}.
-Janus particles are typically spherical particles with a biphasic
-material label on either hemisphere \cite{CaFaRaVe89,Gaetal13,Mallory2017,HaBr20,McBr21}.
-Based on
-preliminary results (\S\ref{sec:preliminary_work}), the PIs propose to
-extend this HAP model as a general methodology that leads
-to new mathematical ideas and efficient numerical methods.
+The hydrophobic interactions come from the tendency of particles to
+minimize the free energy of the structure of the surrounding water
+molecules. The free energy functional takes the form 
+\begin{equation}
+\label{eq:free_energy}
+  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
+  \,d\xx,
+\end{equation}
+where $u$ is an order parameter for the structure of water, $\rho$ is a
+decay length, $C$ is a constant, and $f(u)$ is a potential.
+Hydrogen-bond persistence times are on the order of picoseconds
+which is much smaller than characteristic time for 
+particle motion \cite{MaGa13}.
+Thus we assume $u$ minimizes $F[u]$ for all times.
+Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
+$u$ is bounded and satisfies the Euler-Lagrange equation
+\begin{equation}
+\label{eq:SL}
+-\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
+\text{ on } \bd\Omega.
+\end{equation}
+The boundary condition $g$ is a material label that is transported with
+the particle (Figure~\ref{fig:bcs}).
 
-\subsection{Hydrophobic attraction}
-The hydrophobic attraction potential theory concerns the self-organization of
-hydrophobic particles in a viscous solvent. It is a phenomenological
-model mimicking the linear-response of water to surface perturbations
-and stems from work of Stjepan Mar\v{c}elja
-from the Australian National University in 1976. To explain certain
-repulsion measurements between lecithin bilayers, Mar\v{c}elja and
-coworkers devised a mathematical model using a Landau expansion of the
-free energy density of an order parameter for the orientation of
-water~\cite{LeRaPa77, MaRa76, LANDAULIFSHITZ5}. Their truncated free
-energy gave a boundary value problem for water structure that was
-readily solved in terms of hyperbolic trigonometric functions.
+The particles lower the free energy $F[u]$ of the surrounding water
+by moving. We calculate the rate of change of $F[u]$ using
+\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
+Carrying out
+this variation yields a 
+%The hydrophobic forces are torques are
+%\begin{equation}
+%  \label{eq:hydrophobicAttraction}
+%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
+%    \quad 
+%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
+%    ({\bf T} \cdot \nnu) \dif s.
+%\end{equation}
+stress  
+\begin{align}
+  \label{eq:stress}
+\mathbf{T}
+= C \left[ \rho^{-1} f(u) \mathbf{I}
+  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
+\end{align}
+The imposed forces and torques come from the integration of $\mathbf{T}$
+along the particle boundary.
+These forces and torques couple the Stokes equations \eqref{eq:stokes},
+to semilinear elliptic equation \eqref{eq:SL}.
+Solving for the translational and rotational velocities gives the
+particle evolution.
 
-Although schematic, the model was general enough to explain a number of
-physical effects. For example, the repulsion of lecithin bilayers
-was explained by the free energy that decreases with distance of
-separation because of the mean orientations of water being opposite at
-the two interfaces. Later, a long-range attractive force between
-hydrocarbon coated mica sheets was measured up to
-100~nm~\cite{ClCh88,RaDe88}. The Mar\v{c}elja
-theory was then applied to this problem for an order parameter
-representing the excess number of hydrogen bonds per water
-molecule and gave agreement with the measured force
-curves~\cite{ErLjCl89}.
-
-Analogues of Mar\v{c}elja's phenomenological theory appeared in other
-areas related to biological self-assembly, such as interactions of
-membrane-bound proteins~\cite{KoNa15, Nagle17, KUZMIN2005} and the
-theory of polymer bead interaction in mixed solvents~\cite{deGe76}. On
-the downside, it applies a continuum theory to distances of a few
-molecular diameters, the association of order parameter is arbitrary, it
-predicts monotonic forces, and finally the theory does not account for
-the amplification in attraction at very short distances~\cite{Ni80}.
-
-\begin{wrapfigure}[21]{l}{0.3\textwidth}
-  \vspace{-5pt}
-\includegraphics[width=0.3\textwidth]{figures/Fissure.jpg}
-\includegraphics[width=0.3\textwidth]{figures/Landscape.jpg}
-\caption{\label{fig:fissure} In fusion, fissures in the phospholipid
-  monolayers expose hydrocarbon to water (top). The energy of fissures
-  dominates first and third stages of fusion (bottom).
+\begin{wrapfigure}[10]{r}{0.55\textwidth}
+ \centering
+ \vspace{-3pt}
+ \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/3Particles.jpg}
+ \caption{\label{fig:3particles}
+   \footnotesize
+   Particles translate and rotate to lower the free energy $F[u]$
+   subject to \eqref{eq:SL}, $f(u) = u^2$, and reach a minimal configuration in
+   panel C. The colormap is blue for $u = 0$ and red for $u = 1$.
+   The arrows are the velocity field $\mathbf{u}$.
  }
 \end{wrapfigure}
-Despite the ubiquity of
-the phenomenon, theoretical developments explaining the basic underlying
-principles of the hydrophobic effect have come relatively
-late~\cite{Ch05}.
-No single theory has been able to account, either qualitatively
-or quantitatively,
-for hydrophobic interaction over the full distance
-regime~\cite{Lum1999, Lin2005, Meyer2006, Ducker2016}.
-For example, studies of the partitioning of
-hydrophobic solutes provide estimates for the energy cost of creating
-hydrophobic-water contacts
-that is a factor of three lower than the value derived from interfacial
-tension measurements. Only recently was an explanation for this
-discrepancy provided~\cite{Jackson2016}.
+The stress~\eqref{eq:stress} was first
+introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
+generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
+Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
+forming particle aggregates that sequester their hydrophobic surface
+regions (Figure \ref{fig:3particles}).
 
-The continuum approach to water structure
-that we present here is justified
-\textit{a posteriori} by the agreement between theory and experiment.
-Researchers have used Mar\v{c}elja's theory to calculate
-energies of pore formation and fusion~\cite{Gletal88, Aketal17,
-RyKlYaCo16}.
-%When open, the attraction between apposing hydrophobic
-%surfaces causes the fissure to collapse.
-PI RR calculated a least energy path 
-of fusion using a modified form of the Helfrich energy that
-included Mar\v{c}elja's free energy for the structure of water
-separating fissures~\cite{RyKlYaCo16} (Figure~\ref{fig:fissure}).
-The calculated barrier heights were 
-corroborated experimentally \cite{FrRoPi17}. In summary,
-there is a consensus that despite its apparent simplicity, the predictions
-of the hydrophobic attraction potential theory are compatible with
-experimental measurements and may closely mirror the reality of
-the physical process at a molecular scale~\cite{FrRoPi17, Fretal21}.
+%By solving the above system, we obtain translational and angular
+%velocities of the many-body system. A second-order Adams-Bashforth
+%scheme updates the particle positions and orientations.
 
-The HAP is a conceptual advance for modeling bilayer membranes.
-Continuum elastic energies of membrane assume an energy density that
-depends quadratically on the bilayer strain
-\cite{Hamm2000,TerziDeserno17, PhysRevE.102.042406}.  The coefficients
-of the continuum ansatz correspond to experimentally measured elastic
-moduli \cite{Nagle17, Nagle17-2, NAGLE2000159}.  The HAP approach can
-potentially explain membrane properties from first principles because it
-derives elastic energies assuming parameters for the water structure and
-particle shape \cite{Fu2018_SIAM, FuQuRyYo22, doi:10.1063/5.0009734,
-LiAn-Chang16}.  Immersed boundary and boundary integral are highly
-effective for modeling intact, giant unilamellar vesicles (GUV) because
-they use relatively large time-step sizes and mesh sizes
-\cite{
-Shravan09,
-Rahimian15,
-KimLai2010_JCP,
-KimLai2012_PRE,
-HuLaiSeolEtAl2016_JCP,
-Bartels,
-Peng13,
-RyKlYaCo16,
-Sinha15,
-Lowengrub13,
-Hu,
-Hu13}.
-Conversely, the number of coarse-grained particles needed to track a GUV
-in the HAP formalism is relatively large.  For microscopic process like
-fusion, however, membrane deformations occur at a length scale
-comparable to the thickness of the membrane
-\cite{Kuzmin7235,Aeffner2012,KoKo2002}.  The small deformation
-assumption of continuum theory no longer holds
-\cite{Hamm2000,TerziDeserno17, PhysRevE.102.042406}.  The HAP theory
-does encode membrane thickness through particle diameter, and it is
-comparatively straightforward to account for proteins and lipid mixtures
-by including several particle species.  Any ruptures or insertions occur
-self-consistently in the HAP formulation.  Phase-field and level-set
-methods also allow for topological changes but they require multiple
-phase fields and level sets and additional (sometimes empirical) laws to
-couple them to model membrane-membrane interactions
-\cite{
-DuLiuWang2004_JCP,
-BibenKassnerMisbah2005_PRE,
-DoyeuxGuyotChabannesEtAl2013_JCAM,
-Du05,
-QiangDu08,
-doi:10.1098/rspa.2012.0505,
-doi:10.1137/130941432,
-Feetzl18,
-doi:10.1137/16M1108406}.
-In addition, these methods require the entire fluid and interfacial
-domains to be discretized.  In contrast, the HAP methodology allows
-evolution equations to be solved using integral equation methods that
-when optimized have linear or near-linear computational complexity in
-the number of particles~\cite{fmm1, fmm2, fmm3, fmm4, fmm5, fmm6, fmm7,
-fmm8}.
+The formulation presents a number of mathematical and numerical
+challenges. For one, the domain is constantly changing so that a new
+boundary value problem must be solved at each time step. The particle
+boundaries are nearly touching and high-order numerical
+schemes and adaptively chosen time-step sizes
+are required to calculate trajectories accurately.
+Furthermore, the domain is unbounded and care must be taken 
+in capturing the far-field boundary conditions correctly. 
+Finally, the numerical routine must handle large system sizes
+efficiently.
+
+%and
+%\begin{equation}
+%  \label{eq:force}
+%  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i,\quad 
+%  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \,
+%  \dif s = T_i, \qquad i=1,\ldots,N_b,
+%\end{equation}
+%where
+%$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T \right)$
+%is the hydrodynamic stress tensor (pressure tensor) and $\nnu$ is the
+%particle outward normal.
+
+\subsection{Boundary Integral formulation}
+\textbf{Take from prior years proposal}
+
+\subsection{Outline of the proposal}

### 2022-11-01 NSF2022/Description/specificaim1.tex
pushed organizational changes

--- 2022-09-27 NSF2022/Description/specificaim1.tex
@@
 \label{subsec:specific_aim_1}
+%The goal of this collaborative proposal is to use mathematical modeling
+%and numerical simulations to investigate the dynamic self-assembly of
+%amphiphilic particles interacting via hydrophobic forces in solvent.
+This collaborative proposal aims to advance
+the mathematical modeling and numerical simulation
+of dynamic self-assembly of amphiphilic particles interacting
+via hydrophobic forces in solvent.
+Amphiphilic particles such as lipid molecules possess both hydrophobic
+and hydrophilic structures. In a viscous solvent they self-assemble into
+meso-/macroscopic structures such as micelles and bilayers of lipids to
+shield their hydrophobic surfaces from contact with the solvent
+molecules e.g., waters. Such self-assembly of amphiphiles via hydrophobic
+forces is ubiquitous in biology~\cite{Israelachvili1954},
+and has been a major source of nonspecific interactions 
+in soft matter~\cite{Sanchez-IglesiasEtAl2012_ACSNano,
+AltantzisEtAl2013_PSC, XieYangLuEtAl2020_COCIS}. 
+%The proposed research aims to provide fundamental understanding of the
+%self-assembly dynamics of amphiphilic particles so to design smart
+%materials of desirable properties by
+%tuning the geometry and properties of the amphiphilic particles.
+
+%The hydrophobic force arises when polar solvent molecules come in
+%contact with a non-polar substance, such as hydrocarbon or vapor.
+%In a polar solvent (like water), the dipole-dipole interaction between
+%solvent molecules form a loosely structured hydrogen-bond network where
+%each solvent molecule shares bonds with neighboring molecules at any
+%given time \cite{Israelachvili1954}. In the presence of a non-polar
+%solvent molecule loses the ability to form hydrogen bonds
+%in one direction. 
+%The decrease in the number of hydrogen bonds causes a reorientation,
+%or structural change, in the surrounding water that is energetically
+%very unfavorable \cite{Bjorneholm2016}.
+
+\begin{wrapfigure}[15]{r}{0.37\textwidth}
+\vspace{-8pt}
+\centerline
+{
+\includegraphics[width=0.36\textwidth]{figures/Background/LongRangeForce.jpg}
+}
+%\vspace{-20pt}
+\caption{\label{fig:force_distance}
+Force-distance curve for surfactant
+monolayers adsorbed on mica reveals a long-range
+attraction~\cite{Lin2005}.}
+\end{wrapfigure}
+
+Macroscopically, the substantial free energy of placing hydrophobic
+surfaces in contact with water is roughly proportional to the surface
+area of the contact region~\cite{Bjorneholm2016}.
+%As a result, hydrocarbon solutes have a large interfacial tension 
+%and try to minimize their surface area when in water. 
+At the microscopic level, however, there is long-range interaction
+between hydrophobic surfaces. Two hydrophobic surfaces, in particular,
+separated by water over some distance, experience an attraction
+called the
+hydrophobic force~\cite{Lum1999, Meyer2006, Hammer2010, KaScScNe16}.
+The force is nonadditive~\cite{SilveraBatista1242477},
+and measurements show that the hydrophobic force decays exponentially with a
+decay length on the order of 1--10 nm~
+\cite{Israelachvili1984,Marcelja1977,Christenson2001,Lin2005,Taetal13}
+(Figure \ref{fig:force_distance}).
+
+Motivated by its broad applicability to biology, chemistry, and engineering,
+PIs RR and YNY developed a mathematical model, called the
+hydrophobic attraction potential (HAP) model~\cite{Fu2018_SIAM},
+that is based on
+the linear response of water to surface perturbations. This model was
+used by all the PIs to show how amphiphilic Janus particles (JP)
+self-assemble into a vesicle-like structure~\cite{FuQuRyYo20}.
+Janus particles are typically spherical particles with a biphasic
+material label on either hemisphere \cite{CaFaRaVe89,Gaetal13,Mallory2017,HaBr20,McBr21}.
+Based on
+preliminary results (\S\ref{sec:preliminary_work}), the PIs propose to
+extend this HAP model as a general methodology that leads
+to new mathematical ideas and efficient numerical methods.
+
+\subsection{Hydrophobic attraction}
+The hydrophobic attraction potential theory concerns the self-organization of
+hydrophobic particles in a viscous solvent. It is a phenomenological
+model mimicking the linear-response of water to surface perturbations
+and stems from work of Stjepan Mar\v{c}elja
+from the Australian National University in 1976. To explain certain
+repulsion measurements between lecithin bilayers, Mar\v{c}elja and
+coworkers devised a mathematical model using a Landau expansion of the
+free energy density of an order parameter for the orientation of
+water~\cite{LeRaPa77, MaRa76, LANDAULIFSHITZ5}. Their truncated free
+energy gave a boundary value problem for water structure that was
+readily solved in terms of hyperbolic trigonometric functions.
+
+Although schematic, the model was general enough to explain a number of
+physical effects. For example, the repulsion of lecithin bilayers
+was explained by the free energy that decreases with distance of
+separation because of the mean orientations of water being opposite at
+the two interfaces. Later, a long-range attractive force between
+hydrocarbon coated mica sheets was measured up to
+100~nm~\cite{ClCh88,RaDe88}. The Mar\v{c}elja
+theory was then applied to this problem for an order parameter
+representing the excess number of hydrogen bonds per water
+molecule and gave agreement with the measured force
+curves~\cite{ErLjCl89}.
+
+%\begin{wrapfigure}[7]{r}{0.32\textwidth}
+%  \vspace{-0pt}
+%  \centering
+%  \includegraphics[width=0.32\textwidth]{figures/Background/ChandlerWeeks.pdf}
+%%  \vspace{-20pt}
+%  \caption{\label{fig:chandler_weeks}
+%  }
+%\end{wrapfigure}
+%\todo{This figure is not referenced in the text.}
+Analogues of Mar\v{c}elja's phenomenological theory appeared in other
+areas related to biological self-assembly, such as interactions of
+membrane-bound proteins~\cite{KoNa15, Nagle17, KUZMIN2005} and the 
+theory of polymer bead interaction in mixed
+solvents~\cite{deGe76}.
+%In the latter, the free energy corresponds to
+%the Ornstein-Zernike form of the order parameter correlation function.
+On the downside, it applies a continuum theory to distances of a few
+molecular diameters, the association of order parameter is arbitrary, it
+predicts monotonic forces, and finally the theory does not account
+for the amplification in attraction at very short distances~\cite{Ni80}.
+
+\begin{wrapfigure}[21]{l}{0.3\textwidth}
+  \vspace{-5pt}
+\includegraphics[width=0.3\textwidth]{figures/Background/Fissure.jpg}
+\includegraphics[width=0.3\textwidth]{figures/Background/Landscape.jpg}
+\caption{\label{fig:fissure} In fusion, fissures in the phospholipid
+  monolayers expose hydrocarbon to water (top). The energy of fissures
+  dominates first and third stages of fusion (bottom).
+}
+\end{wrapfigure}
+Despite the ubiquity of
+the phenomenon, theoretical developments explaining the basic underlying
+principles of the hydrophobic effect have come relatively
+late~\cite{Ch05}.
+No single theory has been able to account, either qualitatively
+or quantitatively,
+for hydrophobic interaction over the full distance
+regime~\cite{Lum1999, Lin2005, Meyer2006, Ducker2016}.
+For example, studies of the partitioning of
+hydrophobic solutes provide estimates for the energy cost of creating
+hydrophobic-water contacts
+that is a factor of three lower than the value derived from interfacial
+tension measurements. Only recently was an explanation for this
+discrepancy provided~\cite{Jackson2016}.
+
+The continuum approach to water structure
+that we present here is justified
+\textit{a posteriori} by the agreement between theory and experiment.
+Researchers have used Mar\v{c}elja's theory to calculate
+energies of pore formation and fusion~\cite{Gletal88, Aketal17,
+RyKlYaCo16}.
+%When open, the attraction between apposing hydrophobic
+%surfaces causes the fissure to collapse.
+PI RR calculated a least energy path 
+of fusion using a modified form of the Helfrich energy that
+included Mar\v{c}elja's free energy for the structure of water
+separating fissures~\cite{RyKlYaCo16} (Figure~\ref{fig:fissure}).
+The calculated barrier heights were 
+corroborated experimentally \cite{FrRoPi17}. In summary,
+there is a consensus that despite its apparent simplicity, the predictions
+of the hydrophobic attraction potential theory are compatible with
+experimental measurements and may closely mirror the reality of
+the physical process at a molecular scale~\cite{FrRoPi17, Fretal21}.
+
+The HAP is a conceptual advance for modeling bilayer membranes.
+Continuum elastic energies of membrane assume an energy density that
+depends quadratically on the bilayer strain
+\cite{Hamm2000,TerziDeserno17, PhysRevE.102.042406}.  The coefficients
+of the continuum ansatz correspond to experimentally measured elastic
+moduli \cite{Nagle17, Nagle17-2, NAGLE2000159}.  The HAP approach can
+potentially explain membrane properties from first principles because it
+derives elastic energies assuming parameters for the water structure and
+particle shape \cite{Fu2018_SIAM, FuQuRyYo20, doi:10.1063/5.0009734,
+LiAn-Chang16}.  Immersed boundary and boundary integral are highly
+effective for modeling intact, giant unilamellar vesicles (GUV) because
+they use relatively large time-step sizes and mesh sizes
+\cite{
+Shravan09,
+Rahimian15,
+KimLai2010_JCP,
+KimLai2012_PRE,
+HuLaiSeolEtAl2016_JCP,
+Bartels,
+Peng13,
+RyKlYaCo16,
+Sinha15,
+Lowengrub13,
+Hu,
+Hu13}.
+Conversely, the number of coarse-grained particles needed to track a GUV
+in the HAP formalism is relatively large.  For microscopic process like
+fusion, however, membrane deformations occur at a length scale
+comparable to the thickness of the membrane
+\cite{Kuzmin7235,Aeffner2012,KoKo2002}.  The small deformation
+assumption of continuum theory no longer holds
+\cite{Hamm2000,TerziDeserno17, PhysRevE.102.042406}.  The HAP theory
+does encode membrane thickness through particle diameter, and it is
+comparatively straightforward to account for proteins and lipid mixtures
+by including several particle species.  Any ruptures or insertions occur
+self-consistently in the HAP formulation.  Phase-field and level-set
+methods also allow for topological changes but they require multiple
+phase fields and level sets and additional (sometimes empirical) laws to
+couple them to model membrane-membrane interactions
+\cite{
+DuLiuWang2004_JCP,
+BibenKassnerMisbah2005_PRE,
+DoyeuxGuyotChabannesEtAl2013_JCAM,
+Du05,
+QiangDu08,
+doi:10.1098/rspa.2012.0505,
+doi:10.1137/130941432,
+Feetzl18,
+doi:10.1137/16M1108406}.
+In addition, these methods require the entire fluid and interfacial
+domains to be discretized.  In contrast, the HAP methodology allows
+evolution equations to be solved using integral equation methods that
+when optimized have linear or near-linear computational complexity in
+the number of particles~\cite{fmm1, fmm2, fmm3, fmm4, fmm5, fmm6, fmm7,
+fmm8}.
+
 Specific Aim 1 proposes a novel mathematical model for particle
@@
 \cite{McBr21, HaBr20}.
-
-\subsubsection{Problem formulation}
-%\begin{wrapfigure}[h!]
-\begin{wrapfigure}[11]{r}{0.55\textwidth}
- \centering
- \vspace{-3pt}
- \includegraphics[width=0.55\textwidth]{figures/Domain.jpg}
- \caption{\label{fig:flow_map}
-   In the HAP formulation,
-   a system of exterior problems 
-   defines the hydronamic and hydrophobic interactions.
-   The colormap is for the intensity of $u$.
-   The dynamics lead to self-organized structures like a vesicle bilayer.}
-\end{wrapfigure}
-
-The mathematical formulation is a nonlinear system for the dynamics of a
-collection of particles. The interactions come from a system of 
-partial differential equations (PDEs) that comprise hydrodynamic
-interactions and hydrophobic interactions.
-%The formulation prevents particle collisions through excluded volume
-%potentials. 
-The hydrodynamic interactions come from the mobility problem for rigid
-particles immersed in a viscous solvent. We then use a
-second-order Adams-Bashforth method to update the particle configuration.
-Assuming inertial terms are
-negligible, the particle motion is goverened by the Stokes equations
-\begin{subequations}
-  \label{eq:stokes}
-  \begin{alignat}{3}
-  \label{eq:stokes1}
-  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
-    \label{eq:stokes2}
-  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
-\label{eq:stokes3}
-  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
-  \end{alignat}
-\end{subequations}
-%\begin{alignat}{3}
-%\label{eq:stokes1}
-%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
-%    && \xx \in \Omega, \\
-%\label{eq:stokes2}
-%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
-%\label{eq:stokes3}
-%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
-%\end{alignat}
-%
-where $\uu$ is the velocity and $p$ is the pressure of the solvent,
-$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
-viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
-particles and changes shape as the particles move.
-Since the particles are rigid, the solvent velocity satisfies
-a no-slip boundary condition for a rigid body motion 
-%\begin{align}
-%\label{eq:rigid_bc}
-%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
-%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
-%\end{align}
-on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
-and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
-Given imposed forces acting on each
-particle, the \emph{mobility problem} consists of finding
-translational and angular velocities so that viscous fluid forces
-balance the imposed forces.
-
-The hydrophobic interactions come from the tendency of particles to
-minimize the free energy of the structure of the surrounding water
-molecules. The free energy functional takes the form 
-\begin{equation}
-\label{eq:free_energy}
-  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
-  \,d\xx,
-\end{equation}
-where $u$ is an order parameter for the structure of water, $\rho$ is a
-decay length, $C$ is a constant, and $f(u)$ is a potential.
-Hydrogen-bond persistence times are on the order of picoseconds
-which is much smaller than characteristic time for 
-particle motion \cite{MaGa13}.
-Thus we assume $u$ minimizes $F[u]$ for all times.
-Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
-$u$ is bounded and satisfies the Euler-Lagrange equation
-\begin{equation}
-\label{eq:SL}
--\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
-\text{ on } \bd\Omega.
-\end{equation}
-The boundary condition $g$ is a material label that is transported with
-the particle (Figure~\ref{fig:bcs}).
-
-The particles lower the free energy $F[u]$ of the surrounding water
-by moving. We calculate the rate of change of $F[u]$ using
-\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
-Carrying out
-this variation yields a 
-%The hydrophobic forces are torques are
-%\begin{equation}
-%  \label{eq:hydrophobicAttraction}
-%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
-%    \quad 
-%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
-%    ({\bf T} \cdot \nnu) \dif s.
-%\end{equation}
-stress  
-\begin{align}
-  \label{eq:stress}
-\mathbf{T}
-= C \left[ \rho^{-1} f(u) \mathbf{I}
-  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
-\end{align}
-The imposed forces and torques come from the integration of $\mathbf{T}$
-along the particle boundary.
-These forces and torques couple the Stokes equations \eqref{eq:stokes},
-to semilinear elliptic equation \eqref{eq:SL}.
-Solving for the translational and rotational velocities gives the
-particle evolution.
-
-\begin{wrapfigure}[10]{r}{0.55\textwidth}
- \centering
- \vspace{-3pt}
- \includegraphics[width=0.55\textwidth]{figures/3Particles.jpg}
- \caption{\label{fig:3particles}
-   \footnotesize
-   Particles translate and rotate to lower the free energy $F[u]$
-   subject to \eqref{eq:SL}, $f(u) = u^2$, and reach a minimal configuration in
-   panel C. The colormap is blue for $u = 0$ and red for $u = 1$.
-   The arrows are the velocity field $\mathbf{u}$.
- }
-\end{wrapfigure}
-The stress~\eqref{eq:stress} was first
-introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
-generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
-Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
-forming particle aggregates that sequester their hydrophobic surface
-regions (Figure \ref{fig:3particles}).
-
-%By solving the above system, we obtain translational and angular
-%velocities of the many-body system. A second-order Adams-Bashforth
-%scheme updates the particle positions and orientations.
-
-The formulation presents a number of mathematical and numerical
-challenges. For one, the domain is constantly changing so that a new
-boundary value problem must be solved at each time step. The particle
-boundaries are nearly touching and high-order numerical
-schemes and adaptively chosen time-step sizes
-are required to calculate trajectories accurately.
-Furthermore, the domain is unbounded and care must be taken 
-in capturing the far-field boundary conditions correctly. 
-Finally, the numerical routine must handle large system sizes
-efficiently.
-
-%and
-%\begin{equation}
-%  \label{eq:force}
-%  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i,\quad 
-%  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \,
-%  \dif s = T_i, \qquad i=1,\ldots,N_b,
-%\end{equation}
-%where
-%$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T \right)$
-%is the hydrodynamic stress tensor (pressure tensor) and $\nnu$ is the
-%particle outward normal.
 
@@
   \begin{center}
-  \includegraphics[width=0.2\textwidth]{figures/LPA.jpg}
-  \includegraphics[width=0.2\textwidth]{figures/LPB.jpg}
-  \includegraphics[width=0.2\textwidth]{figures/LPC.jpg}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPA.jpg}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPB.jpg}
+  \includegraphics[width=0.2\textwidth]{figures/SpecificAim1/LPC.jpg}
   \end{center}
@@
   \centering
-  \includegraphics[width=2in]{figures/OrderPDFs.jpg} 
+  \includegraphics[width=2in]{figures/SpecificAim1/OrderPDFs.jpg} 
   \vspace{-20pt}
@@
       (a)
-    &\includegraphics[width=1.8in]{figures/N100B1.jpg}
-    &\includegraphics[width=1.8in]{figures/N100B2.jpg}
-     &\includegraphics[width=1.8in]{figures/N100B3.jpg}    \\
+    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B1.jpg}
+    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B2.jpg}
+     &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B3.jpg}    \\
      (b)
-    &\includegraphics[width=1.8in]{figures/N100C1.jpg}
-    &\includegraphics[width=1.8in]{figures/N100C2.jpg}
-      &\includegraphics[width=1.8in]{figures/N100C3.jpg}    \\
+    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C1.jpg}
+    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C2.jpg}
+      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C3.jpg}    \\
     (c)
-      &\includegraphics[width=1.8in]{figures/N100A1.jpg}
-      &\includegraphics[width=1.8in]{figures/N100A2.jpg}
-      &\includegraphics[width=1.8in]{figures/N100A3.jpg}    \\
+      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A1.jpg}
+      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A2.jpg}
+      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A3.jpg}    \\
       &\multicolumn{1}{c}{$t = 0$}
@@
 for example.
+%\hl{Collaboration with experimental groups will
+%use numerical methods to predict parameter regimes 
+%to control particle-particle interactions.}
+
+%\begin{wrapfigure}[14]{l}{0.5\textwidth}
+%\includegraphics[width=0.5\textwidth]{figures/SpecificAi%m1/multilamelar.pdf}
+%\caption{\label{fig:multilamelar}
+%  Experimentalists can transform unilamellar vesicles to% multilamellar
+%  vesicles by altering the quality of the solvent
+%    \cite{deMeetal21}.
+%  In \eqref{eq:SL}, the solvent quality enters through t%he potential
+%  $f(u)$ and boundary conditions. 
+%}
+%\end{wrapfigure}
 

### 2022-11-01 NSF2022/Description/specificaim3.tex
pushed organizational changes

--- 2022-09-27 NSF2022/Description/specificaim2.tex
@@
-\subsection{Specific Aim 2: Efficient, high-order methods for
-large-scale simulations}
-% ----------------------------------------------------------------------
-Over the past decade, there has been an explosion of interest in
-small-scale processes that utilize capillary forces and van der Waals
-interactions to coordinate movement and bind microscopic components in
-solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}. Additionally,
-hydrodynamic interactions are central to fabricate complex,
-three-dimensional microstructures~\cite{Dasgupta2017, Leong2007,
-Reynolds2019, Cho2010}. Hydrodynamic effects cannot be ignored since
-they, like for the rates of biological functions like pore
-dynamics~\cite{RYHAM20112929}, set the rate of dissipation. In Specific
-Aim 2, we propose novel and efficient high-order numerical methods to
-simulate dynamic assembly of particles under the HAP in a viscous
-solvent. As described in~\eqref{eq:stokes} and illustrated in
-Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
-equations for an incompressible, viscous fluid, and these equations are
-coupled to the screened-Laplace equation~\eqref{eq:SL} through viscous
-and hydrophobic stress balance.
+\subsection{Specific Aim 3: Self-assembly of Janus particles in ionic solutions}
+\label{subsec:specific_aim_3}
 
-The HAP model requires solving exterior problems for the order
-parameter~\eqref{eq:SL} and the Stokes equations~\eqref{eq:stokes}. We
-will develop methods based on combinations of volume and layer
-potentials, and inexact Newton's method. Numerical methods to solve
-these integral equations (IEs) have several advantages over their
-PDE-based counterpart: by construction, they satisfy far-field and mass
-conservation conditions; only $\partial\Omega$ needs to be discretized
-for layer potentials; carefully chosen IEs result in a well-conditioned
-linear system that is solved with a mesh-independent number of GMRES
-iterations; and high-order or spectral accuracy is attainable with
-appropriate quadrature methods. The PIs have demonstrated that IEs are a
-powerful tool to simulate two-dimensional suspensions of amphiphilic
-particles~\cite{Fu2018_SIAM, FuQuRyYo20}. Moreover, elements of these
-formulations have been described in three dimensions~\cite{ying_2006,
-manasthesis, rac-gre2016}. This proposal will extend the two-dimensional
-methods to more general amphiphilic particle models that
-satisfy~\eqref{eq:SL}, and all the methods can naturally be extended to
-three dimensions. These methods will be motivated by models and analysis
-developed in Specific Aims 1 and 3. \S\ref{subsec:AC} describes how the
-non-linear Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved
-using an IE formulation. Then, \S\ref{subsec:NumericalIssues} describes
-how we will combine preconditioning strategies with fast summation
-methods to accelerate the time to solution, and
-\S\ref{subsec:timeStepping} describes adaptive time stepping methods.
+\begin{wrapfigure}[7]{r}{0.45\textwidth}
+  \vspace{-5pt}
+\centerline{\includegraphics[width=0.44\textwidth]{Figures/fig2A_Chen2011_Science}}
+  \vspace{-5pt}
+\caption{\label{fig:helices_of_JPs}Formation of helices
+  of Janus particles as salt concentration increases from 3.8 mM NaCl
+  (left) to 5 mM NaCl (right)~\cite{Chen2011_Science}.}
+\end{wrapfigure}
+In experiments, Janus particles are often immersed in a solution of
+ions~\cite{Chen2011_Science} or surfactants~\cite{Goodwin2009}. In
+electrolytic solutions, the interaction between salt and Janus particle
+gives rise to a slip velocity (on the particle surface) that depends on
+the ion distribution and the zeta potential~\cite{BayatiNajafi2016_JCP}
+(the potential difference between the Janus particle surface and the
+surrounding conducting fluid). The short-range interactions between
+Janus particles depend on the salt concentration: At very low salt
+concentrations, Janus particles repel one another electrostatically,
+whereas at high salt concentration, van der Waals forces cause Janus
+particles to aggregate irreversibly~\cite{Goodwin2009}. At intermediate
+concentrations of monovalent salt (NaCl), Janus particles are found to
+assemble in the form of a small number of elemental units of building
+blocks~\cite{Chen2011_Science}. Figure~\ref{fig:helices_of_JPs} shows
+that Janus particles can assemble into a helix at high concentration of
+monovalent salt when the volume fraction of Janus particles is low to
+moderate. At high volume fraction, helices of Janus particles form
+wormlike structures whose lifetimes allow fusion of
+helices~\cite{Chen2011_Science}.
 
-\subsubsection{Iterative methods for the Allen-Cahn HAP model}
-\label{subsec:AC}
+\subsubsection{Dynamics of a pair of Janus particles in ionic
+solutions\label{subsubsec:JP_electrolyte}}
+We propose to investigate the effects of ion transport and distribution
+on the self-assembly of Janus particles within the HAP framework as
+follows. First the Stokes equations are modified to incorporate the
+transport of ions as
+\begin{equation}
+\label{eq:EKstokes}
+\begin{aligned}
+  &-\Delta \mathbf{u} + \nabla p = \Delta\psi\cdot\nabla\psi, \qquad
+  \nabla \cdot \mathbf{u} = 0,  \quad \mathbf{x} \in \Omega,\\
+  &\delta^2\Delta\psi = -\frac{1}{2}\left(n_+-n_-\right),\qquad
+  \frac{\partial n_{\pm}}{\partial t} + \nabla\cdot{\bf j}_{\pm} = 0,\qquad {\bf j}_{\pm} = -\nabla n_{\pm} \mp n_{\pm} \nabla\psi + \mbox{Pe} n_{\pm}\mathbf{u},
+\end{aligned}
+\end{equation}
+where $\psi$ is the electric potential, $\delta$ is the ratio of Debye
+screening length (inversely proportional to the square root of ion
+concentration) to the particle size, $\mbox{Pe}$ is the Peclet number, a
+ratio between the convection and thermal diffusion time scales, and
+$n_{+}$ and $n_{-}$ are the concentration of cation and anion respectively.
+In the limit
+of small $\delta$, PI YNY and collaborator Y.~Mori (U Penn) used
+asymptotic analyses to show that the jump in electric potential across
+the interface (zeta potential on the Janus particle surface) may give
+rise to different physical consequences such as
+electrophoresis~\cite{Mori2018_JFM}.
+%
+An important question to address is: {\it How would such electrophoresis
+be affected by the HAP between two Janus particles?} As the first part
+of Specific Aim 3, we will address this important question. Results from
+this effort will help elucidate the effects of salt concentration on the
+assembly of Janus particles (\S\ref{subsubsec:em_effects}).
 
-The PIs have developed numerical methods to solve~\eqref{eq:SL} when
-$f(u) = u^2$---this choice results in the linear screened Laplace
-equation. For a more general $f$, such as a double well potential, we
-will interpret the solution of~\eqref{eq:SL} as the root finding problem
-for
-\begin{align}
-  \label{eq:F}
-  J[u] = -\rho^2 \Delta u + \tfrac{1}{2}f'(u).
-\end{align}
-This non-linear PDE will be solved with Newton's method
-\begin{align*}
-  u^{N+1} = u^{N} - \alpha (dJ^N)^{-1} J(u^N),
-\end{align*}
-where $dJ^N = -\rho^2 \Delta + \tfrac{1}{2}f''(u^N)$ is the Fr\'{e}chet derivative
-of $F$, and $\alpha$ is the step size which will be determined using
-backtracking. As expected, the biggest computational challenge is
-solving $- \rho^2 \Delta v + \tfrac{1}{2}f''(u^{N}) v = J[u^N]$. Solving this
-variable coefficient PDE with an integral equation is challenging since
-a fundamental solution is not readily available. We propose to instead
-use an inexact Newton's method where $dJ^{-1}$ is defined in terms of
-the continuous, piecewise quadratic approximation
-\begin{align*}
-  f(u) \approx \tilde{f}(u) = bu + \begin{cases}
-    a(u - u_0)^2, &\mbox{if } u \leq (u_0 + u_1)/2, \\
-    (u - u_1)^2 + \tfrac{1}{4}(a-1)(u_0-u_1)^2 , &\mbox{if } u > (u_0 + u_1)/2,
-  \end{cases}
-\end{align*}
-where $a>0$, and the resulting inexact Newton's method requires solving
-the piecewise constant PDE
-\begin{align}
-  \label{eq:screenedPoisson}
-  -\rho^2 \Delta v + \tfrac{1}{2}\tilde{f}''(u^{N})v = J[u^N],
-\end{align}
-which is a screened Poisson equation with piecewise a constant screening
-coefficient. We test the efficacy of exact and inexact Newton's method
-applied to~\eqref{eq:F} in $(0,1)$ by discretizing $dJ$ with a
-second-order finite difference method. The choice of parameters $a$,
-$b$, $u_0$, and $u_1$ result in the double well potential illustrated in
-Figure~\ref{fig:CA}(a), and both the exact and inexact Newton's methods
-converge to the solution in Figure~\ref{fig:CA}(b).
-Figure~\ref{fig:CA}(c) shows the max norm of the residual at each Newton
-iterate when using the exact second derivative (red curve) and the
-piecewise constant approximate (blue curve). While the inexact Newton's
-method requires roughly twice as many iterations to reach of a tolerance
-of $10^{-4}$, each iteration is significantly cheaper in higher
-dimensions.
+We will couple the electrokinetics in~\eqref{eq:EKstokes} with the
+mobility problem of Janus particles in a viscous solvent through the
+velocity field, ion distribution, and the hydrophobic potential. First
+the screen length $\rho$ and the potential $f(u)$ in the HAP model are now 
+dependent on  the ion concentrations. 
+%
+Second the value of the HAP may depend on the distribution of ions and
+electric potential right next to the particle
+surface~\cite{Mori2018_JFM}. Within this framework, we will first
+investigate the interaction between two Janus particles under HAP in an
+electrolytic solution described by the above equations. We will conduct
+analytical calculations to investigate the effects of ion transport on
+the hydrophobic attraction between two Janus particles using the
+reciprocal theorem as in~\cite{BayatiNajafi2016_JCP} for two Janus
+particles with a small surface activity.
 
-Having demonstrated that the inexact Newton method converges in one
-dimension, it will be coupled with IE formulations to 
-solve~\eqref{eq:SL} in two and three dimensions. We first partition
-$\Omega$ into $\Omega_0 = \{\xx \in \Omega \:|\: u(\xx) < (u_0 +
-u_1)/2\}$ and $\Omega_1 = \{\xx \in \Omega \:|\: u(\xx) > (u_0 +
-u_1)/2\}$, and we let $\Lambda = \{\xx \in \Omega \:|\: u(\xx) = (u_0 +
-u_1)/2 \}$ be their common boundary, and we let $G_0$ be the fundamental
-solution of $(-\rho^2 \Delta + a)$ and $G_1$ be the fundamental
-solution of $(-\rho^2 \Delta + 1)$. Then, the solution
-of~\eqref{eq:screenedPoisson} can be written as $u = u^P + u^H$ where
-$u^P$ is a volume potential and $u^H$ is a layer potential. The volume
-potential is
-\begin{align*}
-  u^{P}(\xx) = \int_{\Omega_i} G_i(\xx,\yy) J[u^N](\yy)\, d\yy, 
-    \quad i = 1,2,
-\end{align*}
-but it is discontinuous across $\Lambda$ and does not satisfy the
-prescribed hydrophobic boundary conditions on the particles $\Gamma_i$.
-Assuming the particles are entirely contained in the hydrophobic region,
-the boundary conditions will be enforced with the layer potentials
-\begin{align*}
-  u^{H}(\xx) = \begin{cases}
-    \displaystyle\int_{\Lambda} G_0(\xx,\yy) \eta_0(\yy) \, ds_\yy + 
-    \displaystyle\int_{\Gamma} \pderiv{}{\nn_\yy} G_0(\xx,\yy)
-      \sigma(\yy) \,ds_\yy, \quad & \xx \in \Omega_0, \\
-    \displaystyle\int_{\Lambda} G_1(\xx,\yy) \eta_1(\yy) \, ds_\yy,
-     & \xx \in \Omega_1.
-  \end{cases}
-\end{align*}
-The density functions $\sigma$, $\eta_0$, and $\eta_1$ are determined so
-that $u = u^P + u^H$ satisfies the hydrophobic boundary condition on
-$\Gamma = \cup_i \Gamma_i$, and that it is continuous and differentiable
-across $\Lambda$. This approach of using IEs to solve elliptic PDEs with
-piecewise constant coefficients has successfully been used in other
-application such as scattering~\cite{hyu-bar2014, che-cho-cai2018}.
+\subsubsection{Electromechanical effects on the dynamic assembly of Janus particles \label{subsubsec:em_effects}}
+Results from the proposed work in \S\ref{subsubsec:JP_electrolyte} will
+shed light on how the electrokinetics described in~\eqref{eq:EKstokes}
+may be simplified to a dielectric-like model where the bulk charges are
+constant, and the fluid flow and particle mobility are determined by the
+surface charge and the zeta potential as shown in~\cite{Mori2018_JFM}.
+Under such simplification, equation~\eqref{eq:EKstokes} may be
+re-formulated into integral forms. PIs RR and YNY will conduct the
+asymptotic analyses to derive this form, and work with PI BQ to design
+numerical algorithms to simulate the modified system. We will first
+investigate the effects of salt concentration on the assembly of Janus
+particles to form helices, as shown in Figure~\ref{fig:helices_of_JPs}.
 
-% ----------------------------------------------------------------------
-\subsubsection{Accelerating the iterative solvers}
-\label{subsec:NumericalIssues}
+With these results, the PIs will be ready to make quantitative
+connections between a Janus particle membrane and a lipid bilayer
+membrane in an electrolytic solution. In recent
+experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending rigidity was
+determined as a function of lipid composition from 0 to 100 mol $\%$ of
+charged lipids using flicker spectroscopy of the shape fluctuations of a
+giant unilamellar vesicle (GUV). Membrane bending rigidity increases
+with increasing lipid surface charge, but decreases with increasing salt
+concentration in the bulk solution due to the screening of the lipid
+surface charge. This result agrees with several theoretical
+models~\cite{Kralchevsky1996_JCIS, May1996_JChemPhys,
+LoubetEtAl2013_PRE} that also assume the quadratic form of the elastic
+energy density in the presence of surface charge and bulk
+charge~\cite{DuplantierGoldstein1990_PRL, Winterhalter1992_JPC}.
+%As the
+%electrostatic interaction is non-local in nature, we expect that the
+%controversy of the HK elastic energy form (see
+%\S\ref{subsec:specific_aim_1}) would worsen in the presence of
+%electrostatic interactions and electrokinetics.
+The PIs will extend the
+approaches in \cite{Fu2018_SIAM} to charged lipids to
+calculate the bending moduli and compare against the experimental
+results in~\cite{FaizEtAl2019_SoftMatt}. We propose to incorporate an
+explicit surface charge on each particle boundary $\Gamma_i$ and compute the
+electrostatic potential as a functional of particle configuration.  By
+adding the electrostatic force to the hydrophobic attraction force
+between particles, we will assess the dependence of elastic moduli on
+electric charges using the methods described in \cite{Fu2018_SIAM}. Results from these proposed calculations
+will provide further comparisons and validations of the HAP model
+against the continuum mechanics.
 
-When solving for the density functions $\eta_0$, $\eta_1$, and $\sigma$,
-a carefully chosen IE formulation only requires a mesh-independent
-number of GMRES iterations~\cite{cam-ips-kel-mey-xue1996}. Therefore,
-the required CPU time is proportional to the cost of a matrix-vector
-multiplication that can be performed in optimal or near-optimal time
-with the fast multipole method (FMM)~\cite{fmm5} and its
-extensions~\cite{fmm1, fmm2, fmm3, fmm4, fmm6, fmm7, fmm8}. PI BQ is
-experienced with applying FMMs for the Stokes
-equation~\cite{qua-bir2014, bys-sha-qua2020} and the screened Laplace
-equation~\cite{kro-qua2011, qua2011}. Furthermore, to reduce the number
-of GMRES iterations, the efficacy of preconditioning strategies such as
-the inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017} and
-domain decomposition~\cite{che-bir2021} will be investigated. PI BQ used
-the IFMM to precondition Stokes equations~\cite{qua-cou-dar2018}. A
-suite of other preconditioners including sparse approximate
-inverses~\cite{che2000} and multigrid~\cite{hem-sch1981, sch1982} will
-be investigated.
-
-% ----------------------------------------------------------------------
-\subsubsection{Eliminating contact with adaptive time stepping}
-\label{subsec:timeStepping}
-
-A numerical issue when simulating the self-assembly of amphiphilic
-particles is avoiding particle collision. The hydrophobic attraction
-potential drives the amphiphilic particles towards one another and this
-leads to physical contact in finite time. Such particle collisions in a
-dense, rigid-body suspension are a great challenge and can be a
-bottleneck in large-scale simulations. We propose to remedy this
-computational challenge by developing novel high-order adaptive time
-stepping methods. PI BQ developed a high-order adaptive time
-stepping method for hydrodynamic suspensions \cite{qua-bir2016}, and it
-has served as a robust method to simulate processes including mixing and
-adhesion in suspensions~\cite{qua-vee-you2019, kab-qua-bir2017}.
-Following this previous work, the proposed work will use a spectral
-deferred correction method~\cite{dut-gre-rok2000} since it iteratively
-applies a low-order, single-step method to achieve high-order accuracy.
-At each time step, we will compute the total force and torque of the
-system which is computationally cheap and physically zero, and therefore
-provides an estimate of the local truncation error. PI BQ's experience
-is that error estimates based on physical constraints, such as force-
-and torque-free conditions, appropriately determine adaptive time step
-sizes so that the dynamics are resolved without the computational
-expense of embedded Runge-Kutta methods, step-doubling, Richardson
-extrapolation.
+Once the effects of lipid charges on the moduli are verified, the PIs
+propose to examine how to use an external electric field to control the
+amphiphilic self-assembly in solvent. PI YNY has a track record of
+working on electrohydrodynamics of an elastic, inextensible membrane
+using both asymptotic analysis~\cite{Nganguia2013_PRE, Young2014_JFM,
+Young2015_PoF} and numerical simulations~\cite{Nganguia2015_CiCP} and
+will work with both PIs RR and BQ to extend the HAP model to study the
+electromechanical effects on the assembly of colloidal amphiphiles.
+Results from this research will yield a quantitative understanding of
+how to utilize an electric field to achieve optimal control of assembly
+of amphiphiles in solvent.

### 2022-11-02 NSF2022/Description/backgroundv2.tex
new background

\noindent
{\bf Collaborative Research: Mathematical modeling and simulation of
self-assembling amphiphilic particles in solvent {\bf MAKE MORE MATHEMATICAL}} \\
{\em Rolf Ryham (lead PI, Fordham University),
Bryan Quaife (PI, Florida State University), and
Yuan-Nan Young (PI, New Jersey Institute of Technology)}

\section{Background}
\label{sec:background}

Mathematical models of self-organization encompasses a
broad range of interesting and challenging phenomena.
For example, understanding the organization of lipids and proteins in vesicles
is crucial to design effective drug and vaccine carriers.
The COVID-19 pandemic has lead to an unprecedented and concerted worldwide
effort in biophysical modeling of the mechanisms of RNA condensation
by structural proteins, protein oligomerization, and cellular
membrane–protein interactions that control ultimate virus structure,
in an effort to curtail pathogens like the Severe Acute Respiratory Syndrome Coronavirus 2.
Using powerful capillary and van der Waals forces that exist at the nanoscale, engineers
have developed superior techniques to print 
high-resolution, nanoscale features on devices like sensors, lasers, and LEDs.
Finally, researchers have introduced data-driven methods 
to study complex patterns that emerge in particle and agent-based systems like swarms
and flocking.

A number of mathematical techniques have beed developed to handle
self-organizing systems.  Each technique has its advantages and disadvantages.
Prominent in chemistry and biology, molecular
dynamics (MD) simulations offers unparalleled resolution of protein-lipid interactions,
say, but because of the large number of non-linear interactions involved,
is limited to short time and small spatial scales.
In terms of inverse problems,
agent based systems also involve relatively large numbers of particles
and here researchers extensively consider the problem  
of learning interaction kernels in these dynamical systems
constrained to evolve on Riemannian manifolds from given trajectory data.
Once the interaction kernels are known, one can in principle derive
partial differential equations (PDE) for the macroscopic behavior.

The phase field method and self-consistent field theory are popular  
approaches to self-organization in applied mathematics.
Motivated by Ginzburg-Landau theory, these methods introduce a scalar-valued
phase field function for the volume fraction of
lipids and water in modeling vesicles membranes, for example. 
Sometimes called diffuse interface methods, here one devises energy functionals
involving the gradient and well-potentials of the phase field, and possibly
long range interaction kernels, that yield approximate mathematical surfaces
of almost arbitrary topology.
Because the fluid interfaces are given by the level-set
of a smooth function, the evolution equations
can be studied by well-established tools like variational methods
and regularity theory, and are amenable to numerical approximation.
On the downside, granular details like the shape changes of a protein, for
example, are clumsy to incorporate in the model.  Moreover, numerical
simulations of phase field models typically discretize the entire fluid
domain under consideration, and apply cutoff boundary conditions
when periodic domains are not under consideration.

(Surface-director models.)

\begin{figure}
  \begin{center}
    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
% \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.jpg}    
 \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map}
   Left: In the HAP formulation,
   a system of exterior problems 
   defines the hydronamic and hydrophobic interactions.
  Right:
     Particles translate and rotate to lower the free energy $F[u]$
   subject to \eqref{eq:SL}, $f(u) = u^2$, and reach a minimal configuration in
   panel C. The colormap is blue for $u = 0$ and red for $u = 1$.
   The arrows are the velocity field $\mathbf{u}$.}
\end{figure}

Recently, we have developed a new mathematical model of self-organization.
The model takes ideas from the phase field method 
and leverages boundary integral equations to speed up computations.
To formulate the problem, consider a collection of $N_b$-many rigid bodies
$U_i$ immersed in an incompressible, zero-Reynolds number fluid
$\Omega_t \mathbb{R}^n \setminus \cup_{i=1}^{N_b} U_i$.
The subscript $t$ reinforces that $\Omega_t$ is time-varying. 
We use the grain shape and boundary conditions to capture the local 
properties of the suspended media.
Unlike particles, the bodies, which we will call grains (``using `grains' as an easy find-replace for
when we settle on vocabulary), have finite size.

The first key idea is
to define the grain interactions using a boundary value problem
\begin{align}
  -\mu\Delta \uu + \nabla p &= \mathbf{0},\\
  \nabla \cdot \uu &= 0,\\
-\rho^2 \Delta \eta + f'(\eta) &= 0, \quad \text{ in } \Omega_t,
\end{align}
with boundary conditions
\begin{align}
  \frac{d\xx}{dt} &= \uu,\\
  \uu &= \vv_i + \omega_i \times (\xx - \aa_i)\\
  \eta &= h_i(\xx,t),\quad \text{ for } \xx \in \Gamma_i
\end{align}
and
\begin{equation}
\int_{\Gamma_i} \mu(\nabla \uu + \nabla \uu^T + pI)\nu \,\dif s = 
\int_{\Gamma_i}
\underbrace{(-\rho^{-1} f'(\eta)
  + \rho(\tfrac{1}{2}|\nabla \eta|^2 - \nabla \eta \nabla \eta^T)}_{T_i} \nu \, \dif s
\end{equation}
This is a semi-linear system for evolution of the grains.  At the top,
the Stokes equations describe the velocity $\uu$ and pressure $p$ of the
aqueous phase. In third equation describes the phase transitions of the
scalar order parameter $\eta$ with a decay length $\rho.$
Mathematically, this order parameter is responsible for the attraction
and adhesion between grains that want to align boundaries of like phase.  
Physically, water molecules are polar and $\eta$ describes the orientational
order of water e.g. $\eta = 1$ when water molecules share alignment
and $\eta = 0$ when the water orientations are disordered.
The well-potential $f$ accounts for possibly distinct equilibrium phases,
as occurs with 3-bond and 4-bond hydrogen bonding.

The next three equations are the moving domain boundary conditions.
The first two specify a non-slip boundary condition for a rigid body
with translation velocity $\vv_i$ and angular velocity $\omega_i$.
In the third boundary condition, the function $h_i$ is a material label
speficying the water phase at the water-grain interface.  This material
label is transported by the fluid and therefore satisfies $h_i(\xx,t)
= h^0_i(\xx(\XX,t),t)$ where $h_i^0$ and $\XX$ are reference labels, coordinates
given by the initial conditions, and $\xx(\XX,t)$ is the flow map for the
rigid bodies.  Finally, the last boundary condition closes the system
and says that the hydrodynamic stress is balanced by the water-order stress.

Intriguingly, the formulation ()-() captures exactly the right behavior
expected from amphiphilic self-assembly.  Three bodies with amphiphilic
label spontaneously translate and change orientations to sequester the
disordered fluid phase.  In our simulations (see section ()), we include
a finite length repulsion to avoid particle collisions.
Moreover, a simple change of boundary conditions from amphiphilic,
to biased hydrophobic, to polar results in distinct equilibrium morphologies.

\begin{figure}[h]
  \begin{center}
    \begin{tabular}{m{0.1cm}m{1.8in}m{1.8in}m{1.8in}}            
      (a)
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B3.jpg}    \\
     (b)
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C3.jpg}    \\
    (c)
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A3.jpg}    \\
      &\multicolumn{1}{c}{$t = 0$}
      &\multicolumn{1}{c}{intermediate time}
      &\multicolumn{1}{c}{long time}
  \end{tabular}
  \end{center}
  \vspace{-20pt}
  \caption{\footnotesize
    \label{fig:self-assembly}
    Rows (a)-(c) have the same initial configuration
    but have different boundary conditions $g.$ 
    In row (a), self-assembly with an amphiphilic boundary
    condition \eqref{eq:bcs}(a) results in a bilayer pattern shielding
    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
    Row (b) shows particles with a hydrophobic intensity that is
    greater on one side of the particle (magenta) than the other (yellow).
    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
    Particles orient like sides to form a checkerboard pattern.\\
  }
\end{figure}

The system ()-() has an elegant mathematical structure.
In terms of locally in time well-posedness, given disjoint grains with
sufficiently smooth boundaries
and data, the system ()-() always has a solution and that these solutions
have a locally Lipschitz dependence on the particle centers and orientations. 
Solutions of ()-() obey the energy law
\begin{equation}
  \frac{d}{dt}F
  = - \int_{\Omega_t} \tfrac{1}{2}\mu|\nabla \uu + \nabla \uu^T|^2 \,dx,
  \quad
  F = \int_{\Omega_t}
  \rho |\nabla \eta|^2 + \rho^{-1} f(\eta) \,dx.
\end{equation}
Mathematically, this energy law states that the free energy $F$ of the water order
phase transitions, which depends on the grain configurations, is lost due to
hydrodynamic dissipation.  It is evident that minimizers of the functional $F$
are unique and satisfy the Euler-Lagrange equation ().
There is a subtlety in the energy law, though.  Namely, the
time derivative of the free energy $F$ also involves the moving
boundary, accounted for by the Rayleigh Transport Theorem, and the
fact that the boundary data for $\eta$ are transported by the rigid body motion.
In fact, the water order surface stress $T_i$ is the variational derivative that
shows up in this calculation.

The model has a broad range of applicability to self-organization phenomena
in chemistry and biological physics. Since the formulation is
scale independent, it can represent a suspension of amphiphiles,
where the grains represent
the mean properties of a small collection of lipids, at the nanoscopic scale.
For larger scales, the representation is literal and the grains Janus spheres.  
The proposal deals with the physical origins in section ().

To summarize, the formulation ()-() shares a lot of the features in phase field modeling,
with the big exception that the free energy depends on the grain configurations,
rather than phase field
function.
To make an explicit connection though, we can consider a phase field model 
where one ``fluid'' phase instantaneously reaches minimality while the other ``solid''
phase moves to further decrease free energy. 
The model is also closely related to
a recent and strongly developing direction studying 
colloids immersed in nematic liquid crystals.
As is the case for nematics, it is natural to understand what is the effect of the flow in
such a context, but a first step is to obtain some solid well-posedness results.
The proposal discusses some mathematical generalizations in section ().

The boundary integral equation (BIE) method is
the idea numerical method for the present study
in terms of computational cost and accuracy.
Boundary integral equations
require linear PDE and so we take $f(\eta) = \tfrac{1}{2}\eta^2$,
yielding in () the so called screened Laplace equation
$-\rho^2 \Delta \eta + \eta$.  This is a Helmholtz equation with purely imaginary
wave number, enabling us to represent the solution
in terms of layer potentials:
\begin{equation}
  \eta(\xx) = \int_{\partial \Omega} \frac{\partial G}{\partial \nu}
  \left(\frac{\xx-\yy}{\rho}\right) \sigma(\yy) \,ds_{\yy}
\end{equation}
where $\frac{\partial G}{\partial \nu}$ is the normal derivative of the
fundamental solution of the screened Laplace equation
(a Bessel function in two space dimensions and
an exponential times the standard fundamental solution of the Laplace equation
in three space dimensions).
This representation allows us to transfer the boundary value problem ()-()
to an equation only involving in terms of domain boundary.

The numerical advantages of doing so are as follows.  If $h = N^{-1}$
is the characeristic grid spacing of the grain boundaries, then a
finite element or finite difference discretization of ()-()
requires on the order of $N_b N^n$ grid points
for dense suspensions.  In contrast BIE require onely 
With finite elements, mesh regeneration
would be needed at each time step since the domain is moving.  
In the boundary integral approach, collocation points can be selected
for the initial grain configuration and then used throughout the
time-course.
As a downside, integral equations require specialized quadrature
routines to resolve self interactions and nearly touching
grain boundaries.  
Finally, the far field boundary conditions which are important for
imposed flow problems automatically hold, whereas with 
finite element and finite difference methods
artificial boundary conditions must be imposed.
\begin{figure}
A figure comparing FE versus BIE meshes
\end{figure}

\subsubsection{Problem formulation}
%\begin{wrapfigure}[h!]

The mathematical formulation is a nonlinear system for the dynamics of a
collection of particles. The interactions come from a system of 
partial differential equations (PDEs) that comprise hydrodynamic
interactions and hydrophobic interactions.
%The formulation prevents particle collisions through excluded volume
%potentials. 
The hydrodynamic interactions come from the mobility problem for rigid
particles immersed in a viscous solvent. We then use a
second-order Adams-Bashforth method to update the particle configuration.
Assuming inertial terms are
negligible, the particle motion is goverened by the Stokes equations
\begin{subequations}
  \label{eq:stokes}
  \begin{alignat}{3}
  \label{eq:stokes1}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
    \label{eq:stokes2}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokes3}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
  \end{alignat}
\end{subequations}
%\begin{alignat}{3}
%\label{eq:stokes1}
%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
%    && \xx \in \Omega, \\
%\label{eq:stokes2}
%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
%\label{eq:stokes3}
%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
%\end{alignat}
%
where $\uu$ is the velocity and $p$ is the pressure of the solvent,
$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
particles and changes shape as the particles move.
Since the particles are rigid, the solvent velocity satisfies
a no-slip boundary condition for a rigid body motion 
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
%\end{align}
on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
Given imposed forces acting on each
particle, the \emph{mobility problem} consists of finding
translational and angular velocities so that viscous fluid forces
balance the imposed forces.

The hydrophobic interactions come from the tendency of particles to
minimize the free energy of the structure of the surrounding water
molecules. The free energy functional takes the form 
\begin{equation}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{equation}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds
which is much smaller than characteristic time for 
particle motion \cite{MaGa13}.
Thus we assume $u$ minimizes $F[u]$ for all times.
Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
$u$ is bounded and satisfies the Euler-Lagrange equation
\begin{equation}
\label{eq:SL}
-\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
\text{ on } \bd\Omega.
\end{equation}
The boundary condition $g$ is a material label that is transported with
the particle (Figure~\ref{fig:bcs}).

The particles lower the free energy $F[u]$ of the surrounding water
by moving. We calculate the rate of change of $F[u]$ using
\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
Carrying out
this variation yields a 
%The hydrophobic forces are torques are
%\begin{equation}
%  \label{eq:hydrophobicAttraction}
%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
%    \quad 
%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
%    ({\bf T} \cdot \nnu) \dif s.
%\end{equation}
stress  
\begin{align}
  \label{eq:stress}
\mathbf{T}
= C \left[ \rho^{-1} f(u) \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
\end{align}
The imposed forces and torques come from the integration of $\mathbf{T}$
along the particle boundary.
These forces and torques couple the Stokes equations \eqref{eq:stokes},
to semilinear elliptic equation \eqref{eq:SL}.
Solving for the translational and rotational velocities gives the
particle evolution.

The stress~\eqref{eq:stress} was first
introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
forming particle aggregates that sequester their hydrophobic surface
regions (Figure \ref{fig:3particles}).

%By solving the above system, we obtain translational and angular
%velocities of the many-body system. A second-order Adams-Bashforth
%scheme updates the particle positions and orientations.

The formulation presents a number of mathematical and numerical
challenges. For one, the domain is constantly changing so that a new
boundary value problem must be solved at each time step. The particle
boundaries are nearly touching and high-order numerical
schemes and adaptively chosen time-step sizes
are required to calculate trajectories accurately.
Furthermore, the domain is unbounded and care must be taken 
in capturing the far-field boundary conditions correctly. 
Finally, the numerical routine must handle large system sizes
efficiently.

%and
%\begin{equation}
%  \label{eq:force}
%  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i,\quad 
%  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \,
%  \dif s = T_i, \qquad i=1,\ldots,N_b,
%\end{equation}
%where
%$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T \right)$
%is the hydrodynamic stress tensor (pressure tensor) and $\nnu$ is the
%particle outward normal.

\subsection{Boundary Integral formulation}
\textbf{Take from prior years proposal}

\subsection{Outline of the proposal}

### 2022-11-04 NSF2022/Description/backgroundv2.tex
started to work on BIE section

@@
 self-assembling amphiphilic particles in solvent {\bf MAKE MORE MATHEMATICAL}} \\
-{\em Rolf Ryham (lead PI, Fordham University),
-Bryan Quaife (PI, Florida State University), and
+{\em Rolf Ryham (PI, Fordham University),
+Bryan Quaife (lead PI, Florida State University), and
 Yuan-Nan Young (PI, New Jersey Institute of Technology)}
@@
 
+\subsection{Problem formulation}
 Recently, we have developed a new mathematical model of self-organization.
@@
 
-The first key idea is
-to define the grain interactions using a boundary value problem
-\begin{align}
-  -\mu\Delta \uu + \nabla p &= \mathbf{0},\\
-  \nabla \cdot \uu &= 0,\\
--\rho^2 \Delta \eta + f'(\eta) &= 0, \quad \text{ in } \Omega_t,
-\end{align}
+The first key idea is to define the grain interactions using a boundary
+value problem
+\begin{alignat}{3}
+  -\mu\Delta \uu + \nabla p &= \mathbf{0}, \:
+  \nabla \cdot \uu = 0, \quad &&\xx \in \Omega, \label {eqn:stokes} \\
+  -\rho^2 \Delta \eta + f'(\eta) &= 0, &&\xx \in \Omega,
+  \label{eqn:phase}
+\end{alignat}
 with boundary conditions
-\begin{align}
-  \frac{d\xx}{dt} &= \uu,\\
-  \uu &= \vv_i + \omega_i \times (\xx - \aa_i)\\
-  \eta &= h_i(\xx,t),\quad \text{ for } \xx \in \Gamma_i
-\end{align}
+\begin{alignat}{3}
+  \frac{d\xx}{dt} &= \uu, &&\xx \in \bd\Omega \\
+  \uu &= \vv_i + \omega_i \times (\xx - \aa_i), \quad &&\xx \in
+  \Gamma_i,\, i=1,\ldots,N_b, \\
+  \eta &= h_i(\xx,t),  &&\xx \in \Gamma_i,\, i=1,\ldots,N_b,
+\end{alignat}
 and
@@
 
-The boundary integral equation (BIE) method is
-the idea numerical method for the present study
-in terms of computational cost and accuracy.
-Boundary integral equations
-require linear PDE and so we take $f(\eta) = \tfrac{1}{2}\eta^2$,
-yielding in () the so called screened Laplace equation
-$-\rho^2 \Delta \eta + \eta$.  This is a Helmholtz equation with purely imaginary
-wave number, enabling us to represent the solution
-in terms of layer potentials:
-\begin{equation}
-  \eta(\xx) = \int_{\partial \Omega} \frac{\partial G}{\partial \nu}
-  \left(\frac{\xx-\yy}{\rho}\right) \sigma(\yy) \,ds_{\yy}
-\end{equation}
-where $\frac{\partial G}{\partial \nu}$ is the normal derivative of the
-fundamental solution of the screened Laplace equation
-(a Bessel function in two space dimensions and
-an exponential times the standard fundamental solution of the Laplace equation
-in three space dimensions).
-This representation allows us to transfer the boundary value problem ()-()
-to an equation only involving in terms of domain boundary.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Boundary Integral formulation}
+Boundary integral equations (BIEs) are a reformulation of elliptic PDEs.
+For example, solutions of the Stokes equations~\eqref{eqn:stokes} can be
+written as the convolution 
+\begin{align*}
+  \uu(\xx) = \int_{\partial\Omega} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
+\end{align*}
+where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
+fundamental solution and $\ssigma: \partial \Omega \rightarrow \RR^2$ is
+an unknown density function. The BIE reformulation has several immediate
+advantages including a dimension reduction since the unknown density
+function is defined only on $\partial \Omega$, and the far field
+boundary condition of the PDE is automatically satisfied. The density
+function $\ssigma$ is chosen to satisfy the boundary condition, and this
+results in a BIE 
+\begin{align*}
+  \gg(\xx) = \lambda \ssigma(\xx) + 
+    \int_{\partial\Omega} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
+    \quad \xx \in \bd\Omega,
+\end{align*}
+where $\gg$ is the Dirichlet boundary condition, and $\lambda$ is a
+constant that depends on the choice of $G$. Note that if the
+well-potential is $f(u) = \tfrac{1}{2}u^2$, then
+equation~\eqref{eqn:phase} becomes the so-called linear screened Laplace
+equation and can be written as a BIE with an unknown scalar-valued
+density function.
 
-The numerical advantages of doing so are as follows.  If $h = N^{-1}$
-is the characeristic grid spacing of the grain boundaries, then a
-finite element or finite difference discretization of ()-()
-requires on the order of $N_b N^n$ grid points
-for dense suspensions.  In contrast BIE require onely 
-With finite elements, mesh regeneration
-would be needed at each time step since the domain is moving.  
-In the boundary integral approach, collocation points can be selected
-for the initial grain configuration and then used throughout the
-time-course.
-As a downside, integral equations require specialized quadrature
-routines to resolve self interactions and nearly touching
-grain boundaries.  
-Finally, the far field boundary conditions which are important for
-imposed flow problems automatically hold, whereas with 
-finite element and finite difference methods
-artificial boundary conditions must be imposed.
-\begin{figure}
-A figure comparing FE versus BIE meshes
-\end{figure}
+In addition to the dimension reduction and far field conditions being
+automatically solved, additional advantages of a BIE formulation are
+that they are high-order, or even spectrally, accurate; their
+discretization results in a well-conditioned linear system that can be
+solved iteratively with a mesh-independent number of iterations of a
+Krylov method such as the generalized minimal residual method (GMRES);
+and complex geometries are easier to address than mesh based methods
+such as the finite element method Figure~\ref{fig:fem_vs_bie}. However,
+BIEs do have several challenges: nearly touching grains requires a
+quadrature rule for nearly-singular integrals; their discretization
+results in dense matrices; and they are not immediately suitable to
+non-linear PDEs. The BIE community, including PI Quaife, has developed a
+variety of tools to address these numerical challenges, and we discuss
+our planned approach in Section~\ref{sec:specificaim2}.
+
+%The boundary integral equation (BIE) method is the ideal numerical
+%method for the present study in terms of computational cost and
+%accuracy. Boundary integral equations require linear PDE and so we take
+%$f(\eta) = \tfrac{1}{2}\eta^2$, yielding in () the so called screened
+%Laplace equation $-\rho^2 \Delta \eta + \eta$.  This is a Helmholtz
+%equation with purely imaginary wave number, enabling us to represent the
+%solution in terms of layer potentials:
+%\begin{equation}
+%  \eta(\xx) = \int_{\partial \Omega} \frac{\partial G}{\partial \nu}
+%  \left(\frac{\xx-\yy}{\rho}\right) \sigma(\yy) \,ds_{\yy}
+%\end{equation}
+%where $\frac{\partial G}{\partial \nu}$ is the normal derivative of the
+%fundamental solution of the screened Laplace equation
+%(a Bessel function in two space dimensions and
+%an exponential times the standard fundamental solution of the Laplace equation
+%in three space dimensions).
+%This representation allows us to transfer the boundary value problem ()-()
+%to an equation only involving in terms of domain boundary.  
+%
+%The numerical advantages of doing so are as follows.  If $h = N^{-1}$ is
+%the characeristic grid spacing of the grain boundaries, then a finite
+%element or finite difference discretization of ()-() requires on the
+%order of $N_b N^n$ grid points for dense suspensions.  In contrast BIE
+%require onely With finite elements, mesh regeneration would be needed at
+%each time step since the domain is moving.  In the boundary integral
+%approach, collocation points can be selected for the initial grain
+%configuration and then used throughout the time-course.  As a downside,
+%integral equations require specialized quadrature routines to resolve
+%self interactions and nearly touching grain boundaries.  Finally, the
+%far field boundary conditions which are important for imposed flow
+%problems automatically hold, whereas with finite element and finite
+%difference methods artificial boundary conditions must be imposed.
+\begin{wrapfigure}[10]{r}{2in}
+  \todo[inline]{A figure comparing FEM versus BIE meshes}
+  \caption{\label{fig:fem_vs_bie} A finite element method requires
+  meshing the entire domain (typically into triangles), while a BIE
+  only requires meshing the boundary of the domain.}
+\end{wrapfigure}
 
@@
 
-\subsection{Boundary Integral formulation}
-\textbf{Take from prior years proposal}
-
 \subsection{Outline of the proposal}

### 2022-11-05 NSF2022/Description/backgroundv2.tex
working on background

@@
   \end{center}
-  \caption{\label{fig:flow_map}
-   Left: In the HAP formulation,
-   a system of exterior problems 
-   defines the hydronamic and hydrophobic interactions.
-  Right:
-     Particles translate and rotate to lower the free energy $F[u]$
-   subject to \eqref{eq:SL}, $f(u) = u^2$, and reach a minimal configuration in
-   panel C. The colormap is blue for $u = 0$ and red for $u = 1$.
-   The arrows are the velocity field $\mathbf{u}$.}
+  \caption{\label{fig:flow_map} \footnotesize {\em Left:} In the HAP
+  formulation, a system of exterior problems defines the hydrodynamic
+  and hydrophobic interactions. {\em Right:} Particles translate and
+  rotate to lower the free energy $F[u]$ subject to \eqref{eq:SL}, $f(u)
+  = u^2$, and reach a minimal configuration in panel C. The colormap is
+  blue for $u = 0$ and red for $u = 1$. The arrows are the velocity
+  field $\mathbf{u}$.}
 \end{figure}
@@
 \subsection{Problem formulation}
-Recently, we have developed a new mathematical model of self-organization.
-The model takes ideas from the phase field method 
-and leverages boundary integral equations to speed up computations.
-To formulate the problem, consider a collection of $N_b$-many rigid bodies
-$U_i$ immersed in an incompressible, zero-Reynolds number fluid
-$\Omega_t \mathbb{R}^n \setminus \cup_{i=1}^{N_b} U_i$.
-The subscript $t$ reinforces that $\Omega_t$ is time-varying. 
-We use the grain shape and boundary conditions to capture the local 
-properties of the suspended media.
-Unlike particles, the bodies, which we will call grains (``using `grains' as an easy find-replace for
-when we settle on vocabulary), have finite size.
+Recently, we have developed a new mathematical model of
+self-organization~\cite{FuQuRyYo22,ru-ryh-qua-you2022,Fu2018_SIAM}. The
+model takes ideas from the phase field method and leverages boundary
+integral equations to speed up computations. To formulate the problem,
+consider a collection of $N_b$-many rigid bodies $U_i$, with boundary
+$\Gamma_i$, immersed in an incompressible, zero-Reynolds number fluid
+$\Omega_t = \RR^n \setminus \cup_{i=1}^{N_b} U_i$. The subscript $t$
+reinforces that $\Omega_t$ is time-varying. We use the grain shape and
+boundary conditions to capture the local properties of the suspended
+media. Unlike particles, the bodies, which we will call grains, have
+finite size.  \todo[inline]{using `grains' as an easy find-replace for
+when we settle on vocabulary}
 
@@
   -\mu\Delta \uu + \nabla p &= \mathbf{0}, \:
-  \nabla \cdot \uu = 0, \quad &&\xx \in \Omega, \label {eqn:stokes} \\
-  -\rho^2 \Delta \eta + f'(\eta) &= 0, &&\xx \in \Omega,
+  \nabla \cdot \uu = 0, \quad &&\xx \in \Omega_t, \label {eqn:stokes} \\
+  -\rho^2 \Delta \eta + f'(\eta) &= 0, &&\xx \in \Omega_t,
   \label{eqn:phase}
@@
 \begin{alignat}{3}
-  \frac{d\xx}{dt} &= \uu, &&\xx \in \bd\Omega \\
+  \frac{d\xx}{dt} &= \uu, &&\xx \in \bd\Omega_t \label{eqn:noslip} \\
   \uu &= \vv_i + \omega_i \times (\xx - \aa_i), \quad &&\xx \in
-  \Gamma_i,\, i=1,\ldots,N_b, \\
+  \Gamma_i,\, i=1,\ldots,N_b, \label{eqn:rbm} \\
   \eta &= h_i(\xx,t),  &&\xx \in \Gamma_i,\, i=1,\ldots,N_b,
+  \label{eqn:material}
 \end{alignat}
 and
-\begin{equation}
+\begin{align}
 \int_{\Gamma_i} \mu(\nabla \uu + \nabla \uu^T + pI)\nu \,\dif s = 
 \int_{\Gamma_i}
-\underbrace{(-\rho^{-1} f'(\eta)
-  + \rho(\tfrac{1}{2}|\nabla \eta|^2 - \nabla \eta \nabla \eta^T)}_{T_i} \nu \, \dif s
-\end{equation}
-This is a semi-linear system for evolution of the grains.  At the top,
-the Stokes equations describe the velocity $\uu$ and pressure $p$ of the
-aqueous phase. In third equation describes the phase transitions of the
-scalar order parameter $\eta$ with a decay length $\rho.$
-Mathematically, this order parameter is responsible for the attraction
-and adhesion between grains that want to align boundaries of like phase.  
-Physically, water molecules are polar and $\eta$ describes the orientational
-order of water e.g. $\eta = 1$ when water molecules share alignment
-and $\eta = 0$ when the water orientations are disordered.
-The well-potential $f$ accounts for possibly distinct equilibrium phases,
-as occurs with 3-bond and 4-bond hydrogen bonding.
+\underbrace{\left(-\rho^{-1} f'(\eta)
+  + \rho\left(\tfrac{1}{2}|\nabla \eta|^2 - \nabla \eta \nabla
+  \eta^T\right)\right)}_{T_i}
+  \nnu \, \dif s.
+  \label{eqn:stressbalance}
+\end{align}
+This is a semi-linear system for evolution of the grains.
+Equation~\eqref{eqn:stokes} is the Stokes equations that describes the
+velocity $\uu$ and pressure $p$ of the viscous aqueous phase.
+Equation~\eqref{eqn:phase} describes the phase transitions of the scalar
+order parameter $\eta$ with a decay length $\rho$. Mathematically, this
+order parameter is responsible for the attraction and adhesion between
+grains that want to align boundaries of like phase. Physically, water
+molecules are polar and $\eta$ describes the orientational order of
+water e.g.~$\eta = 1$ when water molecules share alignment and $\eta =
+0$ when the water orientations are disordered. The well-potential $f$
+accounts for possibly distinct equilibrium phases, as occurs with 3-bond
+and 4-bond hydrogen bonding.
 
 The next three equations are the moving domain boundary conditions.
-The first two specify a non-slip boundary condition for a rigid body
-with translation velocity $\vv_i$ and angular velocity $\omega_i$.
-In the third boundary condition, the function $h_i$ is a material label
-speficying the water phase at the water-grain interface.  This material
-label is transported by the fluid and therefore satisfies $h_i(\xx,t)
-= h^0_i(\xx(\XX,t),t)$ where $h_i^0$ and $\XX$ are reference labels, coordinates
-given by the initial conditions, and $\xx(\XX,t)$ is the flow map for the
-rigid bodies.  Finally, the last boundary condition closes the system
-and says that the hydrodynamic stress is balanced by the water-order stress.
+Equations~\eqref{eqn:noslip} and~\eqref{eqn:rbm} specify a non-slip
+boundary condition for a rigid body with translation velocity $\vv_i$
+and angular velocity $\omega_i$ about the point $\aa_i \in \Omega_i$. In
+equation~\eqref{eqn:material}, the function $h_i$ is a material label
+specifying the water phase at the water-grain interface. This material
+label is transported by the fluid and therefore satisfies $h_i(\xx,t) =
+h^0_i(\xx(\XX,t),t)$ where $h_i^0$ and $\XX$ are reference labels,
+coordinates given by the initial conditions, and $\xx(\XX,t)$ is the
+flow map for the rigid bodies. Finally,
+equation~\eqref{eqn:stressbalance} closes the system by requiring that
+the hydrodynamic stress is balanced by the water-order stress.
 
-Intriguingly, the formulation ()-() captures exactly the right behavior
-expected from amphiphilic self-assembly.  Three bodies with amphiphilic
-label spontaneously translate and change orientations to sequester the
-disordered fluid phase.  In our simulations (see section ()), we include
-a finite length repulsion to avoid particle collisions.
-Moreover, a simple change of boundary conditions from amphiphilic,
-to biased hydrophobic, to polar results in distinct equilibrium morphologies.
+Intriguingly, the
+formulation~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} captures
+exactly the right behavior expected from amphiphilic self-assembly.
+Three bodies with amphiphilic label spontaneously translate and change
+orientations to sequester the disordered fluid phase. In our simulations
+(see section ()), we include a finite length repulsion to avoid particle
+collisions. Moreover, a simple change of boundary conditions from
+amphiphilic, to biased hydrophobic, to polar results in distinct
+equilibrium morphologies (Figure~\ref{fig:self-assembly}).
 
@@
   \vspace{-20pt}
-  \caption{\footnotesize
-    \label{fig:self-assembly}
-    Rows (a)-(c) have the same initial configuration
-    but have different boundary conditions $g.$ 
-    In row (a), self-assembly with an amphiphilic boundary
-    condition \eqref{eq:bcs}(a) results in a bilayer pattern shielding
-    the hydrophobic core (yellow, $u > 0$) from the aqueous phase (blue, $u = 0$).
-    Row (b) shows particles with a hydrophobic intensity that is
-    greater on one side of the particle (magenta) than the other (yellow).
-    In row (c), green is for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$.
-    Particles orient like sides to form a checkerboard pattern.\\
-  }
+  \caption{\footnotesize \label{fig:self-assembly} Rows (a)-(c) have the
+  same initial configuration but different boundary conditions $g$. In
+  row (a), self-assembly with an amphiphilic boundary condition results
+  in a bilayer pattern shielding the hydrophobic core (yellow, $u > 0$)
+  from the aqueous phase (blue, $u = 0$). Row (b) shows particles with a
+  hydrophobic intensity that is greater on one side of the particle
+  (magenta) than the other (yellow). In row (c), green is for $u < 0$,
+  yellow is for $u > 0$, and blue is for $u = 0$. Particles orient like
+  sides to form a checkerboard pattern.}
 \end{figure}
 
-The system ()-() has an elegant mathematical structure.
-In terms of locally in time well-posedness, given disjoint grains with
-sufficiently smooth boundaries
-and data, the system ()-() always has a solution and that these solutions
-have a locally Lipschitz dependence on the particle centers and orientations. 
-Solutions of ()-() obey the energy law
+The system~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} has an elegant
+mathematical structure. In terms of locally in time well-posedness,
+given disjoint grains with sufficiently smooth boundaries and data, the
+system always has a solution and these solutions have a locally
+Lipschitz dependence on the particle centers and orientations.
+Solutions of~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} obey the
+energy law
 \begin{equation}
   \frac{d}{dt}F
-  = - \int_{\Omega_t} \tfrac{1}{2}\mu|\nabla \uu + \nabla \uu^T|^2 \,dx,
+  = - \int_{\Omega_t} \tfrac{1}{2}\mu|\nabla \uu + \nabla \uu^T|^2 \,d\xx,
   \quad
   F = \int_{\Omega_t}
-  \rho |\nabla \eta|^2 + \rho^{-1} f(\eta) \,dx.
+  \rho |\nabla \eta|^2 + \rho^{-1} f(\eta) \,d\xx.
 \end{equation}
-Mathematically, this energy law states that the free energy $F$ of the water order
-phase transitions, which depends on the grain configurations, is lost due to
-hydrodynamic dissipation.  It is evident that minimizers of the functional $F$
-are unique and satisfy the Euler-Lagrange equation ().
-There is a subtlety in the energy law, though.  Namely, the
-time derivative of the free energy $F$ also involves the moving
-boundary, accounted for by the Rayleigh Transport Theorem, and the
-fact that the boundary data for $\eta$ are transported by the rigid body motion.
-In fact, the water order surface stress $T_i$ is the variational derivative that
-shows up in this calculation.
+Mathematically, this energy law states that the free energy $F$ of the
+water order phase transitions, which depends on the grain
+configurations, is lost due to hydrodynamic dissipation. It is evident
+that minimizers of the functional $F$ are unique and satisfy the
+Euler-Lagrange equation (). There is a subtlety in the energy law,
+though. Namely, the time derivative of the free energy $F$ also involves
+the moving boundary, accounted for by the Rayleigh Transport Theorem,
+and the fact that the boundary data for $\eta$ are transported by the
+rigid body motion. In fact, the water order surface stress $T_i$ is the
+variational derivative that shows up in this calculation.
 
-The model has a broad range of applicability to self-organization phenomena
-in chemistry and biological physics. Since the formulation is
-scale independent, it can represent a suspension of amphiphiles,
-where the grains represent
-the mean properties of a small collection of lipids, at the nanoscopic scale.
-For larger scales, the representation is literal and the grains Janus spheres.  
-The proposal deals with the physical origins in section ().
+The model has a broad range of applicability to self-organization
+phenomena in chemistry and biological physics. Since the formulation is
+scale independent, it can represent a suspension of amphiphiles, where
+the grains represent the mean properties of a small collection of
+lipids, at the nanoscopic scale.  For larger scales, the representation
+is literal and the grains Janus spheres.  The proposal deals with the
+physical origins in section ().
 
-To summarize, the formulation ()-() shares a lot of the features in phase field modeling,
-with the big exception that the free energy depends on the grain configurations,
-rather than phase field
-function.
-To make an explicit connection though, we can consider a phase field model 
-where one ``fluid'' phase instantaneously reaches minimality while the other ``solid''
-phase moves to further decrease free energy. 
-The model is also closely related to
-a recent and strongly developing direction studying 
-colloids immersed in nematic liquid crystals.
-As is the case for nematics, it is natural to understand what is the effect of the flow in
-such a context, but a first step is to obtain some solid well-posedness results.
-The proposal discusses some mathematical generalizations in section ().
+To summarize, the
+formulation~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} shares a lot
+of the features in phase field modeling, with the big exception that the
+free energy depends on the grain configurations, rather than phase field
+function. To make an explicit connection though, we can consider a phase
+field model where one ``fluid'' phase instantaneously reaches minimality
+while the other ``solid'' phase moves to further decrease free energy.
+The model is also closely related to a recent and strongly developing
+direction studying colloids immersed in nematic liquid crystals. As is
+the case for nematics, it is natural to understand what is the effect of
+the flow in such a context, but a first step is to obtain some solid
+well-posedness results. The proposal discusses some mathematical
+generalizations in section ().
 
@@
 \begin{align*}
-  \uu(\xx) = \int_{\partial\Omega} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
+  \uu(\xx) = \int_{\partial\Omega_t} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
 \end{align*}
 where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
-fundamental solution and $\ssigma: \partial \Omega \rightarrow \RR^2$ is
-an unknown density function. The BIE reformulation has several immediate
-advantages including a dimension reduction since the unknown density
-function is defined only on $\partial \Omega$, and the far field
-boundary condition of the PDE is automatically satisfied. The density
-function $\ssigma$ is chosen to satisfy the boundary condition, and this
-results in a BIE 
+fundamental solution and $\ssigma: \partial \Omega_t \rightarrow \RR^2$
+is an unknown density function. The BIE reformulation has several
+immediate advantages including a dimension reduction since the unknown
+density function is defined only on $\partial \Omega_t$, and the far
+field boundary condition of the PDE is automatically satisfied. The
+density function $\ssigma$ is chosen to satisfy the boundary condition,
+and this results in a BIE 
 \begin{align*}
   \gg(\xx) = \lambda \ssigma(\xx) + 
-    \int_{\partial\Omega} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
-    \quad \xx \in \bd\Omega,
+    \int_{\partial\Omega_t} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
+    \quad \xx \in \partial\Omega_t,
 \end{align*}
@@
   \todo[inline]{A figure comparing FEM versus BIE meshes}
-  \caption{\label{fig:fem_vs_bie} A finite element method requires
-  meshing the entire domain (typically into triangles), while a BIE
-  only requires meshing the boundary of the domain.}
+  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
+  requires meshing the entire domain (typically into triangles), while a
+  BIE only requires meshing the boundary of the domain.}
 \end{wrapfigure}

### 2022-11-05 NSF2022/Description/specificaim2.tex
pushed organizational changes
started to work on BIE section
working on background

--- 2022-09-27 NSF2022/Description/specificaim2.tex
@@
 large-scale simulations}
+\label{sec:specificaim2}
+\begin{itemize}
+  \item Make clear that we know how to address NSI and fast summation
+  \item Talk about collision as per talk with Bryce
+  \item Wen's paper can be used to give numbers on how large or a
+    problem could hypothetically be considered
+  \item Emphasize that we've learned a lot from just $\mathcal(O)(100)$
+    particles, but now it's time to do more
+  \item Confinement and rheology
+\end{itemize}
+
 % ----------------------------------------------------------------------
@@
 
+%\label{subsec:specific_aim_2}
+%\begin{wrapfigure}[14]{r}{0.61\textwidth}
+%  \centering{\includegraphics[width=0.60\textwidth]{Figures/domain.pdf}}
+%    \vspace{-15pt}
+%    \caption{\label{fig:flow_map} \footnotesize A collection of 3D
+%    amphiphilic particles suspended in a solvent. The solvent velocity
+%    satisfies the Stokes equations, and the hydrophobic forces depend on
+%    the solvent activity that satisfies the screened Laplace equation.
+%    The geometry is updated by solving the mobility problem.} 
+%\end{wrapfigure}
 The HAP model requires solving exterior problems for the order
@@
 
+%\begin{wrapfigure}[27]{l}{1.8in}
+%  \vspace{-4pt}
+%  \centering
+%  \input{figures/doublewell.tikz} 
+%  \caption{\label{fig:CA} (a) The double well potential $u_0 =
+%  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
+%  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
+%  and inexact Newton's methods.}
+%\end{wrapfigure}
 Having demonstrated that the inexact Newton method converges in one

### 2022-11-07 NSF2022/Description/backgroundv2.tex

@@
   \begin{center}
-    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
-% \includegraphics[width=0.55\textwidth]{figures/SpecificAim1/Domain.jpg}    
- \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
+%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
+%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
+    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
+    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
   \end{center}
@@
 \begin{align}
-\int_{\Gamma_i} \mu(\nabla \uu + \nabla \uu^T + pI)\nu \,\dif s = 
+\int_{\Gamma_i} \mu(\nabla \uu + \nabla \uu^T + pI)\nnu \,\dif s = 
 \int_{\Gamma_i}
@@
   \eta^T\right)\right)}_{T_i}
-  \nnu \, \dif s.
+  \nnu \, \dif s,
   \label{eqn:stressbalance}
 \end{align}
-This is a semi-linear system for evolution of the grains.
-Equation~\eqref{eqn:stokes} is the Stokes equations that describes the
-velocity $\uu$ and pressure $p$ of the viscous aqueous phase.
-Equation~\eqref{eqn:phase} describes the phase transitions of the scalar
-order parameter $\eta$ with a decay length $\rho$. Mathematically, this
-order parameter is responsible for the attraction and adhesion between
-grains that want to align boundaries of like phase. Physically, water
-molecules are polar and $\eta$ describes the orientational order of
-water e.g.~$\eta = 1$ when water molecules share alignment and $\eta =
-0$ when the water orientations are disordered. The well-potential $f$
-accounts for possibly distinct equilibrium phases, as occurs with 3-bond
-and 4-bond hydrogen bonding.
+where $\nnu$ is the unit outward normal vector. This is a semi-linear
+system for evolution of the grains.  Equation~\eqref{eqn:stokes} is the
+Stokes equations that describes the velocity $\uu$ and pressure $p$ of
+the viscous aqueous phase.  Equation~\eqref{eqn:phase} describes the
+phase transitions of the scalar order parameter $\eta$ with a decay
+length $\rho$. Mathematically, this order parameter is responsible for
+the attraction and adhesion between grains that want to align boundaries
+of like phase. Physically, water molecules are polar and $\eta$
+describes the orientational order of water e.g.~$\eta = 1$ when water
+molecules share alignment and $\eta = 0$ when the water orientations are
+disordered. The well-potential $f$ accounts for possibly distinct
+equilibrium phases, as occurs with 3-bond and 4-bond hydrogen bonding.
 
 The next three equations are the moving domain boundary conditions.
-Equations~\eqref{eqn:noslip} and~\eqref{eqn:rbm} specify a non-slip
+Equations~\eqref{eqn:noslip} and~\eqref{eqn:rbm} specify a no-slip
 boundary condition for a rigid body with translation velocity $\vv_i$
@@
 amphiphilic, to biased hydrophobic, to polar results in distinct
-equilibrium morphologies (Figure~\ref{fig:self-assembly}).
+equilibrium morphologies (Figure~\ref{fig:self-assembly2}).
 
@@
   \vspace{-20pt}
-  \caption{\footnotesize \label{fig:self-assembly} Rows (a)-(c) have the
-  same initial configuration but different boundary conditions $g$. In
-  row (a), self-assembly with an amphiphilic boundary condition results
-  in a bilayer pattern shielding the hydrophobic core (yellow, $u > 0$)
-  from the aqueous phase (blue, $u = 0$). Row (b) shows particles with a
-  hydrophobic intensity that is greater on one side of the particle
-  (magenta) than the other (yellow). In row (c), green is for $u < 0$,
-  yellow is for $u > 0$, and blue is for $u = 0$. Particles orient like
-  sides to form a checkerboard pattern.}
+  \caption{\footnotesize \label{fig:self-assembly2} Rows (a)-(c) have
+  the same initial configuration but different boundary conditions $g$.
+  In row (a), self-assembly with an amphiphilic boundary condition
+  results in a bilayer pattern shielding the hydrophobic core (yellow,
+  $u > 0$) from the aqueous phase (blue, $u = 0$). Row (b) shows
+  particles with a hydrophobic intensity that is greater on one side of
+  the particle (magenta) than the other (yellow). In row (c), green is
+  for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$. Particles
+  orient like sides to form a checkerboard pattern.}
 \end{figure}
@@
 energy law
-\begin{equation}
+\begin{align}
+  F = \int_{\Omega_t}
+  \left(\rho |\nabla \eta|^2 + \rho^{-1} f(\eta)\right) \,d\xx,
+  \quad
   \frac{d}{dt}F
-  = - \int_{\Omega_t} \tfrac{1}{2}\mu|\nabla \uu + \nabla \uu^T|^2 \,d\xx,
-  \quad
-  F = \int_{\Omega_t}
-  \rho |\nabla \eta|^2 + \rho^{-1} f(\eta) \,d\xx.
-\end{equation}
+  = - \int_{\Omega_t} \left(\tfrac{1}{2}\mu|\nabla \uu + \nabla
+  \uu^T|^2\right) \,d\xx.
+\end{align}
 Mathematically, this energy law states that the free energy $F$ of the
@@
 that minimizers of the functional $F$ are unique and satisfy the
-Euler-Lagrange equation (). There is a subtlety in the energy law,
-though. Namely, the time derivative of the free energy $F$ also involves
-the moving boundary, accounted for by the Rayleigh Transport Theorem,
-and the fact that the boundary data for $\eta$ are transported by the
-rigid body motion. In fact, the water order surface stress $T_i$ is the
-variational derivative that shows up in this calculation.
+Euler-Lagrange equation~\eqref{eqn:phase}. There is a subtlety in the
+energy law, though. Namely, the time derivative of the free energy $F$
+also involves the moving boundary, accounted for by the Rayleigh
+Transport Theorem, and the fact that the boundary data for $\eta$ are
+transported by the rigid body motion. In fact, the water order surface
+stress $T_i$ is the variational derivative that shows up in this
+calculation.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Boundary Integral formulation}
-Boundary integral equations (BIEs) are a reformulation of elliptic PDEs.
-For example, solutions of the Stokes equations~\eqref{eqn:stokes} can be
-written as the convolution 
+\subsection{Boundary integral formulation}
+
+\begin{wrapfigure}[10]{r}{2in}
+  \todo[inline]{A figure comparing FEM versus BIE meshes}
+  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
+  requires meshing the entire domain (typically into triangles), while a
+  BIE only requires meshing the boundary of the domain.}
+\end{wrapfigure}
+Boundary integral equations (BIEs) are a reformulation of elliptic PDEs
+including the Stokes equation~\eqref{eqn:stokes} and the phase
+equation~\eqref{eqn:phase} in the special case of $f(u) =
+\tfrac{1}{2}u^2$. Using the Stokes equation as an example, its solution
+can be written as a convolution 
 \begin{align*}
@@
 is an unknown density function. The BIE reformulation has several
-immediate advantages including a dimension reduction since the unknown
-density function is defined only on $\partial \Omega_t$, and the far
-field boundary condition of the PDE is automatically satisfied. The
-density function $\ssigma$ is chosen to satisfy the boundary condition,
-and this results in a BIE 
+immediate advantages including a dimension reduction since $\ssigma$ is
+defined only on $\partial \Omega_t$, and the far field boundary
+condition of the PDE is automatically satisfied. The density
+function $\ssigma$ is chosen to satisfy the boundary condition, and this
+results in a BIE 
 \begin{align*}
@@
 where $\gg$ is the Dirichlet boundary condition, and $\lambda$ is a
-constant that depends on the choice of $G$. Note that if the
-well-potential is $f(u) = \tfrac{1}{2}u^2$, then
-equation~\eqref{eqn:phase} becomes the so-called linear screened Laplace
-equation and can be written as a BIE with an unknown scalar-valued
-density function.
+constant that depends on the choice of $G$. For numerical stability,
+choices of $G$ that result in second-kind Fredholm integral equations,
+meaning $\lambda \neq 0$, are preferred.
 
-In addition to the dimension reduction and far field conditions being
-automatically solved, additional advantages of a BIE formulation are
-that they are high-order, or even spectrally, accurate; their
-discretization results in a well-conditioned linear system that can be
-solved iteratively with a mesh-independent number of iterations of a
-Krylov method such as the generalized minimal residual method (GMRES);
-and complex geometries are easier to address than mesh based methods
-such as the finite element method Figure~\ref{fig:fem_vs_bie}. However,
-BIEs do have several challenges: nearly touching grains requires a
-quadrature rule for nearly-singular integrals; their discretization
-results in dense matrices; and they are not immediately suitable to
-non-linear PDEs. The BIE community, including PI Quaife, has developed a
-variety of tools to address these numerical challenges, and we discuss
-our planned approach in Section~\ref{sec:specificaim2}.
+A consequence of the dimension reduction in a BIE formulation is that
+complex geometries are much easier to resolve than a mesh-based method
+since only $\partial \Omega_t$ needs to be discretized
+(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a BIE
+formulation includes a discretization that is high-order, or even
+spectrally, accurate; results in a well-conditioned linear system that
+can be solved iteratively with a mesh-independent number of iterations
+of a Krylov method such as the generalized minimal residual method
+(GMRES). However, BIEs do have several challenges: nearly touching
+grains requires a quadrature rule for nearly-singular integrals; their
+discretization results in dense matrices; and they cannot immediately be
+applied to non-linear PDEs. The BIE community, including PI Quaife, has
+developed a variety of tools to address these numerical challenges, and
+we discuss our planned approach in Section~\ref{sec:specificaim2}.
 
@@
 %difference methods artificial boundary conditions must be imposed.
-\begin{wrapfigure}[10]{r}{2in}
-  \todo[inline]{A figure comparing FEM versus BIE meshes}
-  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
-  requires meshing the entire domain (typically into triangles), while a
-  BIE only requires meshing the boundary of the domain.}
-\end{wrapfigure}
 

### 2022-11-08 NSF2022/Description/backgroundv2.tex
background, SA1

@@
 \noindent
-{\bf Collaborative Research: Mathematical modeling and simulation of
-self-assembling amphiphilic particles in solvent {\bf MAKE MORE MATHEMATICAL}} \\
+{\bf Collaborative Research:
+Collaborative research: self-orgzanization by moving domain elliptic PDE}\\
 {\em Rolf Ryham (PI, Fordham University),
@@
 integral equations to speed up computations. To formulate the problem,
-consider a collection of $N_b$-many rigid bodies $U_i$, with boundary
-$\Gamma_i$, immersed in an incompressible, zero-Reynolds number fluid
-$\Omega_t = \RR^n \setminus \cup_{i=1}^{N_b} U_i$. The subscript $t$
-reinforces that $\Omega_t$ is time-varying. We use the grain shape and
-boundary conditions to capture the local properties of the suspended
-media. Unlike particles, the bodies, which we will call grains, have
-finite size.  \todo[inline]{using `grains' as an easy find-replace for
-when we settle on vocabulary}
+consider a collection of $N_b$-many rigid bodies $U_i(t) \subset \mathbb{R}^n$
+with boundary $\Gamma_i(t)$.
+We call these bodies ``granules''.
+The granules are immersed 
+in an incompressible, zero-Reynolds number fluid
+$\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b} U_i(t)$
+(Figure \ref{fig:flow_map}).
 
-The first key idea is to define the grain interactions using a boundary
-value problem
-\begin{alignat}{3}
-  -\mu\Delta \uu + \nabla p &= \mathbf{0}, \:
-  \nabla \cdot \uu = 0, \quad &&\xx \in \Omega_t, \label {eqn:stokes} \\
-  -\rho^2 \Delta \eta + f'(\eta) &= 0, &&\xx \in \Omega_t,
+We look for $N_b$-many rigid body transformations
+\begin{equation}
+\label{eq:RBT}
+F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
+\end{equation}
+where $i = 1,\ldots,N_b,$
+$R_i(t)$ is a rotation (proper orthogonal) $n \times n$ matrix,
+$\aa_i(t)$ are the granule centers, and $\XX$ is a reference coordinate.
+The transformations \eqref{eq:RBT} tell us how the granules move through space
+and we use the shape and
+boundary conditions for $U_i$ to capture the local
+properties of the suspended media e.g., lipids, peptides, Janus spheres.
+Throughout, $\nu$ refers to unit normal pointing into $\Omega(t)$ (Figure \ref{fig:flow_map}).
+
+The key idea is to define the dynamics using the following
+boundary value problem system:
+\begin{alignat}{4}
+  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
+  && \nabla \cdot \uu = 0, && \quad \xx \in \Omega(t), \label {eqn:stokes} \\
   \label{eqn:phase}
+  -\rho^2 \Delta \eta + f'(\eta) &= 0, && &&\quad \xx \in \Omega(t),\\
+\label{eqn:noslip}        
+\uu(\xx) &= \frac{dF_i}{dt}(\XX,t)
+&&=\vv_i + \omega_i \times (\xx - \aa_i), 
+&&\quad \xx \in \Gamma_i(t),\\
+\label{eqn:material}
+\eta(\xx) &= h_i(\XX), &&  &&\quad \xx \in \Gamma_i(t),
 \end{alignat}
-with boundary conditions
-\begin{alignat}{3}
-  \frac{d\xx}{dt} &= \uu, &&\xx \in \bd\Omega_t \label{eqn:noslip} \\
-  \uu &= \vv_i + \omega_i \times (\xx - \aa_i), \quad &&\xx \in
-  \Gamma_i,\, i=1,\ldots,N_b, \label{eqn:rbm} \\
-  \eta &= h_i(\xx,t),  &&\xx \in \Gamma_i,\, i=1,\ldots,N_b,
-  \label{eqn:material}
-\end{alignat}
-and
-\begin{align}
-\int_{\Gamma_i} \mu(\nabla \uu + \nabla \uu^T + pI)\nnu \,\dif s = 
-\int_{\Gamma_i}
-\underbrace{\left(-\rho^{-1} f'(\eta)
-  + \rho\left(\tfrac{1}{2}|\nabla \eta|^2 - \nabla \eta \nabla
-  \eta^T\right)\right)}_{T_i}
-  \nnu \, \dif s,
+for $i=1,\ldots,N_b$
+and where $\xx = F_i(\XX,t)$.
+Finally,
+\begin{equation}
 \label{eqn:stressbalance}
-\end{align}
-where $\nnu$ is the unit outward normal vector. This is a semi-linear
-system for evolution of the grains.  Equation~\eqref{eqn:stokes} is the
+\int_{\Gamma_i} \left[\mu(\nabla \uu + \nabla \uu^T + pI) + T_i\right]\nnu \,\dif s = \mathbf{0},\quad
+\end{equation}
+where
+\begin{equation}
+\label{eqn:hydro_stress}
+T_i = -\rho^{-1} f'(\eta)I
+  + \rho\left(\tfrac{1}{2}|\nabla \eta|^2I - \nabla \eta \nabla
+  \eta^T\right)
+\end{equation}
+for the identity matrix $I$.
+
+The above form a semi-linear elliptic 
+system for evolution of the granules.  Equation~\eqref{eqn:stokes} is the
 Stokes equations that describes the velocity $\uu$ and pressure $p$ of
@@
 length $\rho$. Mathematically, this order parameter is responsible for
-the attraction and adhesion between grains that want to align boundaries
-of like phase. Physically, water molecules are polar and $\eta$
-describes the orientational order of water e.g.~$\eta = 1$ when water
-molecules share alignment and $\eta = 0$ when the water orientations are
-disordered. The well-potential $f$ accounts for possibly distinct
-equilibrium phases, as occurs with 3-bond and 4-bond hydrogen bonding.
+the attraction and adhesion between granules that want to align boundaries
+of like phase.
 
 The next three equations are the moving domain boundary conditions.
-Equations~\eqref{eqn:noslip} and~\eqref{eqn:rbm} specify a no-slip
-boundary condition for a rigid body with translation velocity $\vv_i$
-and angular velocity $\omega_i$ about the point $\aa_i \in \Omega_i$. In
+Equations~\eqref{eqn:noslip} specify a no-slip
+boundary condition for a rigid body with translation velocity $\aa'_i(t) = \vv_i$
+and angular velocity $\omega_i$
+about the point $\aa_i(t) \in U_i(t)$.
+($\omega_i$ is the axial vector of the
+skew symmetric matrix $R'_i(t)$.)
+In
 equation~\eqref{eqn:material}, the function $h_i$ is a material label
-specifying the water phase at the water-grain interface. This material
-label is transported by the fluid and therefore satisfies $h_i(\xx,t) =
-h^0_i(\xx(\XX,t),t)$ where $h_i^0$ and $\XX$ are reference labels,
-coordinates given by the initial conditions, and $\xx(\XX,t)$ is the
-flow map for the rigid bodies. Finally,
+specifying the phases at water-granule interface.
+In other words, the boundary condition for $\eta$ is transported by the flow.
+Finally,
 equation~\eqref{eqn:stressbalance} closes the system by requiring that
-the hydrodynamic stress is balanced by the water-order stress.
+the hydrodynamic stress is balanced by the phase stress $T_i$ in
+\eqref{eqn:hydro_stress}.
+
+We call the rigid bodies $U_i(t)$ granules since they are small, compact
+parcels of a suspended medium, e.g. lipids, Janus spheres.
+We have departed from the terminology ``particles'' here
+to emphasize the role played by their finite size. 
+In our simulations
+(see section \ref{sec:specific_aim1}),
+we include a finite length repulsion to avoid particle
+collisions.
 
@@
 exactly the right behavior expected from amphiphilic self-assembly.
-Three bodies with amphiphilic label spontaneously translate and change
-orientations to sequester the disordered fluid phase. In our simulations
-(see section ()), we include a finite length repulsion to avoid particle
-collisions. Moreover, a simple change of boundary conditions from
+For example, three bodies with amphiphilic label
+(see section \ref{sec:specific_aim1}) spontaneously
+self-organize to sequester the hydrophobic fluid phase
+(the red phase in Figure \ref{fig:flow_map}).
+Moreover, a simple change of boundary conditions from
 amphiphilic, to biased hydrophobic, to polar results in distinct
@@
 
-\begin{figure}[h]
+\begin{figure}[t!]
   \begin{center}
@@
 mathematical structure. In terms of locally in time well-posedness,
-given disjoint grains with sufficiently smooth boundaries and data, the
+given disjoint granules with sufficiently smooth boundaries and data, the
 system always has a solution and these solutions have a locally
@@
 Mathematically, this energy law states that the free energy $F$ of the
-water order phase transitions, which depends on the grain
+water order phase transitions, which depends on the granule
 configurations, is lost due to hydrodynamic dissipation. It is evident
@@
 
+\begin{figure}[t!]
+\begin{center}
+\includegraphics[width=\textwidth]{figures/Background/coarsening.pdf}
+\end{center}
+\caption{\label{fig:coarsening}}
+\end{figure}
 The model has a broad range of applicability to self-organization
@@
 scale independent, it can represent a suspension of amphiphiles, where
-the grains represent the mean properties of a small collection of
+the granules represent the mean properties of a small collection of
 lipids, at the nanoscopic scale. For larger scales, the representation
-is literal and the grains Janus spheres. The proposal deals with the
+is literal and the granules Janus spheres. The proposal deals with the
 physical origins in section ().
@@
 of the features in phase field modeling, with the big exception that the
-free energy depends on the grain configurations, rather than phase field
+free energy depends on the granule configurations, rather than phase field
 function. To make an explicit connection though, we can consider a phase
@@
 (GMRES). However, BIEs do have several challenges: nearly touching
-grains requires a quadrature rule for nearly-singular integrals; their
+granules requires a quadrature rule for nearly-singular integrals; their
 discretization results in dense matrices; and they cannot immediately be
@@
 
-%The boundary integral equation (BIE) method is the ideal numerical
-%method for the present study in terms of computational cost and
-%accuracy. Boundary integral equations require linear PDE and so we take
-%$f(\eta) = \tfrac{1}{2}\eta^2$, yielding in () the so called screened
-%Laplace equation $-\rho^2 \Delta \eta + \eta$. This is a Helmholtz
-%equation with purely imaginary wave number, enabling us to represent the
-%solution in terms of layer potentials:
-%\begin{equation}
-%  \eta(\xx) = \int_{\partial \Omega} \frac{\partial G}{\partial \nu}
-%  \left(\frac{\xx-\yy}{\rho}\right) \sigma(\yy) \,ds_{\yy}
-%\end{equation}
-%where $\frac{\partial G}{\partial \nu}$ is the normal derivative of the
-%fundamental solution of the screened Laplace equation
-%(a Bessel function in two space dimensions and
-%an exponential times the standard fundamental solution of the Laplace equation
-%in three space dimensions).
-%This representation allows us to transfer the boundary value problem ()-()
-%to an equation only involving in terms of domain boundary.  
-%
-%The numerical advantages of doing so are as follows.  If $h = N^{-1}$ is
-%the characeristic grid spacing of the grain boundaries, then a finite
-%element or finite difference discretization of ()-() requires on the
-%order of $N_b N^n$ grid points for dense suspensions.  In contrast BIE
-%require onely With finite elements, mesh regeneration would be needed at
-%each time step since the domain is moving.  In the boundary integral
-%approach, collocation points can be selected for the initial grain
-%configuration and then used throughout the time-course.  As a downside,
-%integral equations require specialized quadrature routines to resolve
-%self interactions and nearly touching grain boundaries.  Finally, the
-%far field boundary conditions which are important for imposed flow
-%problems automatically hold, whereas with finite element and finite
-%difference methods artificial boundary conditions must be imposed.
-
-\subsubsection{Problem formulation}
-%\begin{wrapfigure}[h!]
-
-The mathematical formulation is a nonlinear system for the dynamics of a
-collection of particles. The interactions come from a system of 
-partial differential equations (PDEs) that comprise hydrodynamic
-interactions and hydrophobic interactions.
-%The formulation prevents particle collisions through excluded volume
-%potentials. 
-The hydrodynamic interactions come from the mobility problem for rigid
-particles immersed in a viscous solvent. We then use a
-second-order Adams-Bashforth method to update the particle configuration.
-Assuming inertial terms are
-negligible, the particle motion is goverened by the Stokes equations
-\begin{subequations}
-  \label{eq:stokes}
-  \begin{alignat}{3}
-  \label{eq:stokes1}
-  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
-    \label{eq:stokes2}
-  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
-\label{eq:stokes3}
-  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
-  \end{alignat}
-\end{subequations}
-%\begin{alignat}{3}
-%\label{eq:stokes1}
-%  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
-%    && \xx \in \Omega, \\
-%\label{eq:stokes2}
-%  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
-%\label{eq:stokes3}
-%  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
-%\end{alignat}
-%
-where $\uu$ is the velocity and $p$ is the pressure of the solvent,
-$\uu_\infty$ is the background flow, and $\mu$ is the constant solvent
-viscosity. The domain $\Omega = \Omega(t)$ is the fluid region surrounding the
-particles and changes shape as the particles move.
-Since the particles are rigid, the solvent velocity satisfies
-a no-slip boundary condition for a rigid body motion 
-%\begin{align}
-%\label{eq:rigid_bc}
-%  \uu(\xx) = \vv_i + \omega_i  (\xx - \aa_i)^\perp, \quad
-%    \xx \in \Gamma_i,\qquad  i=1,\ldots,N_p,
-%\end{align}
-on the particle boundary $\Gamma_i$ with translational velocity $\vv_i$
-and angular velocity $\omega_i$ (Figure \ref{fig:flow_map}).
-Given imposed forces acting on each
-particle, the \emph{mobility problem} consists of finding
-translational and angular velocities so that viscous fluid forces
-balance the imposed forces.
-
-The hydrophobic interactions come from the tendency of particles to
-minimize the free energy of the structure of the surrounding water
-molecules. The free energy functional takes the form 
-\begin{equation}
-\label{eq:free_energy}
-  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
-  \,d\xx,
-\end{equation}
-where $u$ is an order parameter for the structure of water, $\rho$ is a
-decay length, $C$ is a constant, and $f(u)$ is a potential.
-Hydrogen-bond persistence times are on the order of picoseconds
-which is much smaller than characteristic time for 
-particle motion \cite{MaGa13}.
-Thus we assume $u$ minimizes $F[u]$ for all times.
-Assuming appropriate conditions on $f(u)$ (\cite{evans10}, \S 8.2),
-$u$ is bounded and satisfies the Euler-Lagrange equation
-\begin{equation}
-\label{eq:SL}
--\rho^2 \Delta u + \tfrac{1}{2}f'(u) = 0  \text{ in } \Omega,\quad u = g,
-\text{ on } \bd\Omega.
-\end{equation}
-The boundary condition $g$ is a material label that is transported with
-the particle (Figure~\ref{fig:bcs}).
-
-The particles lower the free energy $F[u]$ of the surrounding water
-by moving. We calculate the rate of change of $F[u]$ using
-\emph{variation of the domain} ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
-Carrying out
-this variation yields a 
-%The hydrophobic forces are torques are
-%\begin{equation}
-%  \label{eq:hydrophobicAttraction}
-%  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
-%    \quad 
-%    T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
-%    ({\bf T} \cdot \nnu) \dif s.
-%\end{equation}
-stress  
-\begin{align}
-  \label{eq:stress}
-\mathbf{T}
-= C \left[ \rho^{-1} f(u) \mathbf{I}
-  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
-\end{align}
-The imposed forces and torques come from the integration of $\mathbf{T}$
-along the particle boundary.
-These forces and torques couple the Stokes equations \eqref{eq:stokes},
-to semilinear elliptic equation \eqref{eq:SL}.
-Solving for the translational and rotational velocities gives the
-particle evolution.
-
-The stress~\eqref{eq:stress} was first
-introduced by~\cite{Fu2018_SIAM} and is the higher-dimensional
-generalization of disjoining pressure \cite{MaRa76, ErLjCl89, KoNa15,
-Nagle17, KUZMIN2005}. It is the mathematical ingredient responsible for
-forming particle aggregates that sequester their hydrophobic surface
-regions (Figure \ref{fig:3particles}).
-
-%By solving the above system, we obtain translational and angular
-%velocities of the many-body system. A second-order Adams-Bashforth
-%scheme updates the particle positions and orientations.
-
-The formulation presents a number of mathematical and numerical
-challenges. For one, the domain is constantly changing so that a new
-boundary value problem must be solved at each time step. The particle
-boundaries are nearly touching and high-order numerical
-schemes and adaptively chosen time-step sizes
-are required to calculate trajectories accurately.
-Furthermore, the domain is unbounded and care must be taken 
-in capturing the far-field boundary conditions correctly. 
-Finally, the numerical routine must handle large system sizes
-efficiently.
-
-%and
-%\begin{equation}
-%  \label{eq:force}
-%  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i,\quad 
-%  \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot (\ssigma \cdot \nnu) \,
-%  \dif s = T_i, \qquad i=1,\ldots,N_b,
-%\end{equation}
-%where
-%$\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T \right)$
-%is the hydrodynamic stress tensor (pressure tensor) and $\nnu$ is the
-%particle outward normal.
-
 \subsection{Outline of the proposal}

### 2022-11-08 NSF2022/Description/specificaim2.tex
working on SA2

@@
 \begin{itemize}
-  \item Make clear that we know how to address NSI and fast summation
+%  \item Make clear that we know how to address NSI and fast summation
   \item Talk about collision as per talk with Bryce
-  \item Wen's paper can be used to give numbers on how large or a
-    problem could hypothetically be considered
-  \item Emphasize that we've learned a lot from just $\mathcal(O)(100)$
-    particles, but now it's time to do more
+%  \item Wen's paper can be used to give numbers on how large or a
+%    problem could hypothetically be considered
+%  \item Emphasize that we've learned a lot from just $\mathcal(O)(100)$
+%    particles, but now it's time to do more
   \item Confinement and rheology
@@
 simulate dynamic assembly of particles under the HAP in a viscous
-solvent. As described in~\eqref{eq:stokes} and illustrated in
+solvent. As described in~\eqref{eqn:stokes} and illustrated in
 Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
 equations for an incompressible, viscous fluid, and these equations are
-coupled to the screened-Laplace equation~\eqref{eq:SL} through viscous
-and hydrophobic stress balance.
+coupled to the non-linear screened-Laplace equation~\eqref{eqn:phase}
+through viscous and hydrophobic stress balance.
 
@@
 The HAP model requires solving exterior problems for the order
-parameter~\eqref{eq:SL} and the Stokes equations~\eqref{eq:stokes}. We
-will develop methods based on combinations of volume and layer
-potentials, and inexact Newton's method. Numerical methods to solve
-these integral equations (IEs) have several advantages over their
-PDE-based counterpart: by construction, they satisfy far-field and mass
-conservation conditions; only $\partial\Omega$ needs to be discretized
-for layer potentials; carefully chosen IEs result in a well-conditioned
-linear system that is solved with a mesh-independent number of GMRES
-iterations; and high-order or spectral accuracy is attainable with
-appropriate quadrature methods. The PIs have demonstrated that IEs are a
-powerful tool to simulate two-dimensional suspensions of amphiphilic
-particles~\cite{Fu2018_SIAM, FuQuRyYo20}. Moreover, elements of these
-formulations have been described in three dimensions~\cite{ying_2006,
-manasthesis, rac-gre2016}. This proposal will extend the two-dimensional
-methods to more general amphiphilic particle models that
-satisfy~\eqref{eq:SL}, and all the methods can naturally be extended to
-three dimensions. These methods will be motivated by models and analysis
-developed in Specific Aims 1 and 3. \S\ref{subsec:AC} describes how the
-non-linear Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved
-using an IE formulation. Then, \S\ref{subsec:NumericalIssues} describes
-how we will combine preconditioning strategies with fast summation
-methods to accelerate the time to solution, and
-\S\ref{subsec:timeStepping} describes adaptive time stepping methods.
+parameter~\eqref{eqn:phase} and the Stokes equations~\eqref{eqn:stokes}.
+We will develop methods based on combinations of volume and layer
+potentials, and inexact Newton's method. As mentioned in
+Section~\ref{sec:bie}, numerical methods to solve these integral
+equations (IEs) have several advantages over their PDE-based
+counterpart. The PIs have demonstrated that IEs are a powerful tool to
+simulate two-dimensional suspensions of amphiphilic
+particles~\cite{Fu2018_SIAM, FuQuRyYo20, fu-ryh-qua-you2022}. Moreover,
+elements of these formulations have been described in three
+dimensions~\cite{ying_2006, manasthesis, rac-gre2016}. This proposal
+will extend the two-dimensional methods to more general amphiphilic
+particle models and also to three dimensions. In addition, the methods
+will allow us to use results we have shown for $\mathcal{O}(100)$
+grains, and extend them to suspensions with 100X--1000X more grains.
+These methods will be motivated by models and analysis developed in
+Specific Aims 1 and 3. \S\ref{subsec:AC} describes how the non-linear
+Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved using an IE
+formulation. Then, \S\ref{subsec:NumericalIssues} describes how we will
+combine accurate quadrature and fast summation methods to accelerate the
+time to accurate solutions. A natural extension to create simulations
+that are realizable by experimentalists is to include confinement, and
+this is discussed in \S\ref{subsec:Confinement}. This extension will
+also allow us to study new rheological properties of the suspensions.
+Finally, \S\ref{subsec:timeStepping} proposes collision-aware adaptive
+time stepping methods.
 
+% ----------------------------------------------------------------------
 \subsubsection{Iterative methods for the Allen-Cahn HAP model}
@@
 
-The PIs have developed numerical methods to solve~\eqref{eq:SL} when
+The PIs have developed numerical methods to solve~\eqref{eqn:phase} when
 $f(u) = u^2$---this choice results in the linear screened Laplace
 equation. For a more general $f$, such as a double well potential, we
-will interpret the solution of~\eqref{eq:SL} as the root finding problem
-for
+will interpret the solution of~\eqref{eqn:phase} as the root finding
+problem for
 \begin{align}
@@
 \end{align*}
-where $dJ^N = -\rho^2 \Delta + \tfrac{1}{2}f''(u^N)$ is the Fr\'{e}chet derivative
-of $F$, and $\alpha$ is the step size which will be determined using
-backtracking. As expected, the biggest computational challenge is
-solving $- \rho^2 \Delta v + \tfrac{1}{2}f''(u^{N}) v = J[u^N]$. Solving this
-variable coefficient PDE with an integral equation is challenging since
-a fundamental solution is not readily available. We propose to instead
-use an inexact Newton's method where $dJ^{-1}$ is defined in terms of
-the continuous, piecewise quadratic approximation
+where $dJ^N = -\rho^2 \Delta + \tfrac{1}{2}f''(u^N)$ is the Fr\'{e}chet
+derivative of $F$, and $\alpha$ is the step size which will be
+determined using backtracking. As expected, the biggest computational
+challenge is solving $- \rho^2 \Delta v + \tfrac{1}{2}f''(u^{N}) v =
+J[u^N]$. Solving this variable coefficient PDE with an integral equation
+is challenging since a fundamental solution is not readily available.
+However, since $f''(u_0) = f''(u_1) = 2a(u_1 - u)0)^2 + 2c$, f' We
+propose to instead use an inexact Newton's method where $dJ^{-1}$ is
+defined in terms of the continuous, piecewise quadratic approximation
 \begin{align*}
@@
 % ----------------------------------------------------------------------
-\subsubsection{Accelerating the iterative solvers}
+\subsubsection{Increased accuracy and reduced CPU time}
 \label{subsec:NumericalIssues}
+While IE formulations of PDEs have several advantages, several
+challenges must be overcome before the code can be used to simulate
+systems with large numbers of grains. For example, when grains are close
+to one another, which is inevitable in dense suspensions, the resulting
+integrals are nearly-singular. This issue is well-known in the IE
+community and several algorithms have been developed in the last 30
+years. An incomplete list of methods that address near-singular
+integration include panel-based methods~\cite{helsing_2008a,
+helsing_tutorial_2012}, Quadrature by Expansions
+(QBX)~\cite{din-hua-mar-tan2021, klo-bar-gre-one2013, ste-bar2022,
+af2018sisc}, and interpolation-based methods~\cite{ying_2006,
+qua-bir2014, rah-vee-zor-bir2015}. The proposed research, which is
+described next,  will combine several methods including singularity
+subtraction, analytic function theory, and spherical basis
+representations.
 
-When solving for the density functions $\eta_0$, $\eta_1$, and $\sigma$,
-a carefully chosen IE formulation only requires a mesh-independent
-number of GMRES iterations~\cite{cam-ips-kel-mey-xue1996}. Therefore,
-the required CPU time is proportional to the cost of a matrix-vector
-multiplication that can be performed in optimal or near-optimal time
-with the fast multipole method (FMM)~\cite{fmm5} and its
-extensions~\cite{fmm1, fmm2, fmm3, fmm4, fmm6, fmm7, fmm8}. PI BQ is
-experienced with applying FMMs for the Stokes
-equation~\cite{qua-bir2014, bys-sha-qua2020} and the screened Laplace
-equation~\cite{kro-qua2011, qua2011}. Furthermore, to reduce the number
-of GMRES iterations, the efficacy of preconditioning strategies such as
-the inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017} and
-domain decomposition~\cite{che-bir2021} will be investigated. PI BQ used
-the IFMM to precondition Stokes equations~\cite{qua-cou-dar2018}. A
-suite of other preconditioners including sparse approximate
-inverses~\cite{che2000} and multigrid~\cite{hem-sch1981, sch1982} will
-be investigated.
+In two-dimensions, analytic function theory can be used to derive a
+quadrature method whose error is uniformly bounded~\cite{bar2014,
+bar-wu-vee2015, ioa-pap-per1991}, but these works only show how to apply
+the method to the two-dimensional Laplace and Stokes equations. PI BQ
+recently showed that these quadrature methods can be extended to other
+PDEs with singularity subtraction~\cite{che-lin-her-qua2021}. For
+example, the fundamental solution of the screened Laplace
+equation~\eqref{eqn:phase} involves the modified Bessel function of the
+second kind, $K_0(\|\xx - \yy\|)$. The behavior of this function as $\yy
+\rightarrow \xx$ is $K_0(\alpha \|\xx - \yy\|) = \log\|\xx - \yy\| +
+S(\xx - \yy)$, where $S(\xx - \yy)$ is continuously differentiable. This
+suggests a quadrature scheme for where the aforementioned quadrature
+method is applied to the $\log\|\xx - \yy\|$ kernel, and high-order
+methods~\cite{tre-wei2014} are applied to integrals involving the smooth
+kernel $S(\xx - \yy)$.Similar techniques, which they call subtraction
+techniques, have been considered by Camille Carvalho and her
+colleagues~\cite{car2021, car2020, car-kha-kim2018}.  These methods are
+particularly powerful when computing gradients of layer potentials which
+is required, for example, when computing the water-order
+stress~\eqref{eqn:stressbalance}.
+
+In three dimensions, the quadrature methods are much more challenging.
+Singularity subtraction methods can be applied, but analytic function
+theory is no longer applicable. Singularity subtraction methods have
+been applied using, for example, smoothed variations of
+the~\cite{beale1, cor2001, tlu-bea2019}. Alternatively, efficient
+quadrature methods can be applied directly to accurately compute
+singular and near-singular integrals~\cite{khayat_2005,
+gimbutas2013sisc}. However, since we are interested in round (2D) and
+spherical (3D) grains, we will exploit the fact that integrals can be
+computed exactly after transforming the integrals to to a Fourier (2D)
+or spherical harmonic (3D) basis. This technique can be used to evaluate
+layer potentials for both Stokes~\cite{cor-vee2018} and the screened
+Laplace equation~\cite{koh-cor-che-vee2021}.
+
+Another facet to consider when choosing the quadrature rule is its
+ability to be applied efficiently. Since carefully chosen IE
+formulations require a mesh-independent number of GMRES
+iterations~\cite{cam-ips-kel-mey-xue1996}, the required CPU time is
+proportional to the cost of a matrix-vector multiplication that can be
+performed in optimal or near-optimal time with the fast multipole method
+(FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2, fmm3, fmm4, fmm6,
+fmm7, ros-ols2016}. PI BQ is experienced with applying FMMs for the
+Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the screened
+Laplace equation~\cite{kro-qua2011, qua2011}. Many of these methods rely
+on analytic expansions of the PDE's fundamental solution, but recent
+work has demonstrated that a kernel-independent method applied to
+suspensions of 80,000 spheres can be simulated with only $\sim$10
+seconds per time step on 1792 compute cores~\cite{Yan2019}.
+
+%
+%Furthermore, to reduce the
+%number of GMRES iterations, the efficacy of preconditioning strategies
+%such as the inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017}
+%and domain decomposition~\cite{che-bir2021} will be investigated. PI BQ
+%used the IFMM to precondition Stokes equations~\cite{qua-cou-dar2018}. A
+%suite of other preconditioners including sparse approximate
+%inverses~\cite{che2000} and multigrid~\cite{hem-sch1981, sch1982} will
+%be investigated.
 
 % ----------------------------------------------------------------------
-\subsubsection{Eliminating contact with adaptive time stepping}
+\subsubsection{Incorporating confinement}
+\label{subsec:Confinement}
+In experiments, it is known that interactions between bounding walls and
+grains cannot be ignored~\cite{qua-gan-you2021,
+KaouiHartingMisbah2011_PRE, her-sto-gra2005}. Therefore, the necessary
+modifications to the code will be performed so that confinement can be
+considered. PI BQ has considered suspensions with confinement for
+several projects including dynamic suspensions~\cite{qua-bir2014,
+bys-sha-qua2020} and porous media~\cite{chi-moo-qua2020,
+dea-qua-bir-jua2018, moo-che-chi-qua2022, qua-gan-you2021}.
+
+% ----------------------------------------------------------------------
+\subsubsection{Collision-aware suspensions with adaptive time stepping}
 \label{subsec:timeStepping}

### 2022-11-08 NSF2022/Description/specificaim1v2.tex

%\documentclass[11pt]{article}
%
%%\usepackage[margin=1.01in]{geometry}
%%\usepackage{mathpazo}
%\usepackage[utf8]{inputenc}
%\usepackage{NSFProposal}
%
%%\addtolength{\oddsidemargin}{-0.6in}
%%\addtolength{\evensidemargin}{-0.75in}
%%\addtolength{\textwidth}{1.2in}
%%\addtolength{\topmargin}{-0.75in}
%%\addtolength{\textheight}{1.4in}
%%
%%\usepackage[margin=1.02in]{geometry}
%%\def\baselinestretch{1}
%%\special{papersize=8.5in,11in}
%
%%\usepackage[left=1.1in, right=1.1in]{geometry}
%
%%
%\usepackage{url}
%\usepackage{amsfonts,amsmath,amssymb,amsbsy}
%\usepackage{latexsym}
%
%\usepackage{bm}
%\usepackage{comment}
%%\usepackage{upgreek}
%\usepackage{graphics,graphicx}
%\usepackage{psfrag}
%\usepackage{epsfig}
%\usepackage{wrapfig}
%\usepackage{mathrsfs}
%
%\usepackage{pgfgantt}
%\usepackage{subfigure}
%
%\usepackage[square,numbers,comma,sort&compress]{natbib}
%%\usepackage{hyperref}
%
%\usepackage{commath}
%\usepackage{array}
%%\newcommand{\todo}[1]{%
%%  {\bfseries\color{red} XXX TODO: #1}
%%}
%\usepackage[font=small,labelfont=bf,labelsep=period]{caption}
%%\usepackage[margin=30pt,font=small,labelfont=bf,
%%  labelsep=period,skip=10pt]{caption}
%
%\usepackage{todonotes}
%\usepackage{pgfplots,tikz,color,soul,array,enumitem}
%
%
%\newcounter{midequation}
%
%\newtheorem{definition}{Definition}
%\newtheorem{lemma}{Lemma}
%\newtheorem{example}{Example}
%\newtheorem{theorem}{Theorem}
%\newtheorem{proposition}{Proposition}
%\newtheorem{remark}{Remark}
%
%
%
%\newcommand{\diff}{\mathrm{d}}
%\newcommand{\intd}{\,\mathrm{d}}
%\newcommand{\kBT}{$\mathrm{k}_{\mathrm{B}}\mathrm{T}$}
%\newcommand{\KB}{k_{\mathrm{B}}}
%\newcommand{\KG}{k_{\mathrm{G}}}
%\newcommand{\KT}{k_{\mathrm{T}}}
%\newcommand{\KTH}{k_{\theta}}
%\newcommand{\KA}{k_{\mathrm{A}}}
%\newcommand{\eg}{{\it e.g.~}}
%\newcommand{\ie}{{\it i.e.~}}
%\DeclareMathOperator{\Div}{div}
%\DeclareMathOperator{\Curl}{curl}
%
%% Bryan's Marcros
%\renewcommand{\aa}{\mathbf{a}}
%\newcommand{\bd}{\partial}
%\newcommand{\dd}{\mathbf{d}}
%\newcommand{\DD}{\mathcal{D}}
%\newcommand{\eeta}{\boldsymbol{\eta}}
%\newcommand{\FF}{\mathbf{F}}
%\renewcommand{\gg}{\mathbf{g}}
%\newcommand{\GG}{\mathbf{G}}
%\newcommand{\JJ}{\mathbf{J}}
%\newcommand{\nn}{\mathbf{n}}
%\newcommand{\NN}{\mathbf{N}}
%\newcommand{\nnu}{\boldsymbol{\nu}}
%\newcommand{\ttau}{\boldsymbol{\tau}}
%\newcommand{\ssigma}{\boldsymbol{\sigma}}
%\newcommand{\rr}{\mathbf{r}}
%\newcommand{\RR}{\mathbb{R}}
%\renewcommand{\SS}{\mathbf{S}}
%\newcommand{\TT}{\mathbf{T}}
%\newcommand{\xx}{\mathbf{x}}
%\newcommand{\XX}{\mathbf{X}}
%\newcommand{\uu}{\mathbf{u}}
%\newcommand{\vv}{\mathbf{v}}
%\newcommand{\yy}{\mathbf{y}}
%\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
%\newcommand{\jump}[1]{[\![ #1 ]\!]}
%
%\begin{document}
%
%
%\newpage
%\pagenumbering{arabic}
%%\input{summary}
%\pagestyle{empty}

\section{Specific Aim 2: Membrane vesicles as self-organized granules}
\subsection{Prior work related to the proposal.}

\subsubsection{Vesicles}
\begin{wrapfigure}[12]{r}{0.3\textwidth}
  \vspace{-5pt}
\centerline{\includegraphics[width=0.3\textwidth]{figures/SA1Figures/LiposomePore.pdf}}
  \vspace{-5pt}
\caption{\label{fig:LiposomePore}Pore formation in a
stressed liposome~\cite{Kaetal03, BrdGSa00}.}
\end{wrapfigure}
PI Ryham has made fundamental contributions to interface modeling in
membrane biology.  His first works include
phase field formulations for the elastic bending energy \cite{0951-7715-18-3-016,Du05}
and 
topological indicators \cite{DuEuler} of vesicle membranes
and fluid-vesicle interactions \cite{QiangDu09}.
A decade ago, Ryham focused on the
problem of \emph{lipidic pore dynamics}.  
This problem came from 
experiments in the late 1990's 
showing that liposomes swollen by osmotic stress can form a single pore that
widens to allow the release of fluid (see Figure \ref{fig:LiposomePore}). 
Once pressure is released,
the widened pore closes according to a linear
followed by a square root law \cite{BrdGSa00}.  Researchers have
used the rates of pore closure to infer properties of the lipid membrane \cite{PoDi10}.

In \cite{BrdGSa00}, 
physicists Olivier Sandre and Fran\c{c}oise Brochard-Wyart
and Nobel laureate Pierre-Gilles de Gennes
(PGG) formulated
rate equations for lipid pore dynamics.  These equations couple
the liposome stretching tension, pore edge tension, and membrane
dissipation.  A coefficient $C$ accounting for dissipation due to water
movement, however, was left unspecified because the Stokes flow
problem for the fluid surrounding a spherical cap with a moving hole
was unknown at the time \cite{Ra73}.  PI Ryham approached this problem using
a two-phase field method model \cite{RyCoEi12} and in a much-cited work
(coauthored with an undergraduate math major) by
fitting a dissipation coefficient $C \approx 8$ to data.
data \cite{RYHAM20112929}.  Finally, in the sole-author 
JFM paper \cite{Ryham2017OnTV},
Ryham solved the Stokes flow problem for
a moving pore completely yielding a value 
$C = \frac{4}{\pi}\csc \alpha\cot^2\frac{\alpha}{2}(\alpha - \sin \alpha + \alpha^2 \tan \frac{\alpha}{2})
~\sim 2\pi + 5(\alpha - \pi)$ in the pore angle $\alpha$.
Olivier Sandre wrote about the publication of the PI’s JFM paper:

\begin{quotation}“Maybe you can tell them this story: In my thesis
paper with Brochard \& PGG we got a factor of 8 wrong in determining
the viscosity of lipid membranes until a math teacher from the
Bronx corrected the model prefactor!”  Sandre, Olivier @Olive\_Free.
Twitter, January 3, 2018, https://twitter.com/Olive\_Free/status/948640705362169857
\end{quotation}

\begin{wrapfigure}[14]{l}{0.4\textwidth}
  \vspace{-5pt}
\centerline{\includegraphics[width=0.4\textwidth]{figures/SA1Figures/FusionMicroscopy.pdf}}
  \vspace{-5pt}
\caption{\label{fig:FusionMicroscopy}
Fusion of an influenza virus-like particle with a liposome resolved
by electron tomography
~\cite{Chetal16}.}
\end{wrapfigure}

\noindent\textbf{Membrane Fusion.} Ryham has contributed
physically relevant, state-of-the-art methods in the
area of \emph{membrane fusion} (see Figure \ref{fig:FusionMicroscopy}).
Membranes fuse as a part of many biological
processes such as synaptic transmission, intracellular trafficking,
fertilization, and viral infection, and  a major challenge
to determine the forces needed to merge two lipid bilayers
~\cite{chernomordik2008mechanics, kozlov1982possible, Kuzmin19062001, markin2002membrane, qian2012novel}.  
Studying fusion is such a difficult problem because bilayers
consist of two monolayer surfaces coupled by a pair of surface vector fields
that model the elongated lipids.

In his much noticed Biophysical Journal
and Nature papers~\cite{RyKlYaCo16,Chetal16}, Ryham and collaborators 
calculated, for the first time, a least energy path for membrane fusion.  
One mathematical innovation of this paper was to combine
the underlying surface-director model  with the simplified string method 
introduced by Weinan E, Weiqing Ren, and Eric Vanden-Eijnden
~\cite{doi:10.1063/1.2720838}
to calculate the saddle point separating two energy basins. 
The results~\cite{RyKlYaCo16} yielded energy barriers for stages of fusion
consistent with predictions from prominent MD and experimental groups
\cite{SmRiMu19,2017PNAS..114.1238F}.
The PI's papers ~\cite{RyWaCo13} and ~\cite{RyKlYaCo16} 
were also coauthored with undergraduate
mathematics majors.

\begin{wrapfigure}[10]{r}{0.4\textwidth}
  \vspace{-5pt}
\centerline{\includegraphics[width=0.4\textwidth]{figures/SA1Figures/Hemifusion.pdf}}
  \vspace{-5pt}
\caption{\label{fig:Hemifusion}
Axisymmetric hemifusion stage of two planar bilayers~\cite{RyKlYaCo16}.
Bilayer energy depends not only on surface curvature, but lipid orientations as well.}
\end{wrapfigure}
Phase field methods have been used to
study fusion in two dimensions~\cite{C9SM01983A} (MORE REFS), 
but these models do not resolve lipid orientations that play a crucial
role in processes like fusion.

\subsection{Vesicles as self-organized granules}
Interface problems coming from biology are a challenging
area of applied mathematics.  Broadly speaking, these problems
involve a fluid structure interaction where the modeler must
solve for the velocity in the aqueous phase, track the interface,
and couple the velocity boundary condition to the interface through
stress balance boundary conditions.  The aqueous phase can
be a low Reynolds number fluid, a porous medium, or viscoelastic fluid,
and the interfacial forces can come from surface tension, elasticity,
or electrostatics.
One typically enforces constant volume constraints through a no-slip
boundary condition for the velocity; if the interface is area incompressible
then one can additionally require that the velocity surface divergence
be zero.  Incorporating all these details can lead to models with substantial
complexity.

\subsubsection{Mathematical innovations.}
We developed the model \eqref{eqn:stokes}-\eqref{eqn:hydro_stress} 
as a robust and flexible approach
that cuts across many of the aforementioned challenging aspects to vesicle modeling.
\begin{enumerate}
\item The granules are not fixed to a stencil which
affords greater flexibility in terms of vesicle morphology 
and topological changes--sufficiently large forces will pull the granules apart 
as physically required,
\item An elliptic PDE \eqref{eqn:phase} provides the attraction that binds granules together,
opening the possibility for mathematical analysis, 
\item The model includes important details like lipid orientations and inter-monolayer
slip not present in diffusive interface models, and
\item With the help of boundary integral equations
and fast summation methods, the dynamics can be solved in 
near-linear complexity in $N_b$, which is equal to or better than 
that of related sharp interface methods. 
\end{enumerate}
The main insight that leads a collection of granules to form bilayers
is to define a so-called ``amphiphilic'' boundary condition for \eqref{}
It takes the form:
\begin{equation}
\label{eq:amphiphilic_BC}
h_i(\mathbf{x}) = \tfrac{1}{2}\left(\dd_i \cdot (\xx - \aa_i)/c_i + 1\right)
\end{equation}
where $\dd_i$ is the director, $\aa_i$ is the center, and $c_i$ the
``radius'' of the $i$th granule.  Inspired
by the amphiphilic structure of lipids, 
\eqref{eq:amphiphilic_BC} 
takes values close to $1$ on in the direction $\dd_i$,
representing a hydrophobic tail, and values close to $0$ 
in the direction $\dd_i$ representing the hydrophilic head.
%\begin{figure}
%Wrapped figure: a picture of a lipid and the granule geometry.
%\end{figure}

\begin{wrapfigure}[13]{r}{0.5\textwidth}
  \vspace{-5pt}
\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-5pt}
\caption{\label{fig:amphiphilic_assembly}
Self-organization under amphiphilic boundary condition \eqref{eq:amphiphilic_BC}.
Granules first match hydrophobic tails (red) (a), then align length-wise (b). 
The behavior is the same in three dimensions 
as simulated by Kohl, Corona, and Veerapaneni
\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
The basic self-organization proceeds in two steps.
(a) Supensions of granules first minimize energy by matching hydrophobic
hydrophobic tails with one or more apposing granules
(Figure \ref{fig:amphiphilic_assembly}a, red regions.)
Once matched, there is still some residual energy in the
exposed sides.  In the minimimal configuration, pairs of
granules line up side by side, forming a bilayer,
and sequestering the hydrophobic
phase to the smallest possible region
(Figure \ref{fig:amphiphilic_assembly}b).
For numerical stability and physical realism,
we include a repulsion to prevent the granules from colliding.

\subsubsection{Do granule-based vesicle behave like continuum vesicles?}
A vesicle is a ring-shaped (or sphere-shaped in $\mathbb{R}^3$) 
and we analyze its energy as follows:
\begin{enumerate}
\item[Bending]
  The vesicle has bending energy because the directors are not
  parallel.  In the outer layer, the directors have negative
  splay $\nabla \cdot \dd < 0$ and in the inner layer
  the directors have positive splay $\nabla \cdot \dd > 0$.
  Due to minimality, the energy depends locally quadratically
  on the splay and has a bending modulus $k_B$.
  When $\dd$ is everywhere parallel to the unit normal $\NN,$ then
  \[
  \nabla \dd = -2H
  \]
  where $H$ is the mean curvature. 
\item[Stretch]
  If the vesicle is stretched, then the distance between
  neighboring granules is increased from rest.  The energy
  for this increase is Hookean and for small deformations
  equals
  \begin{equation}
    \label{eq:stretch}
    \tfrac{1}{2}k_A(L - L_0)^2/L_0
  \end{equation}
  where $k_A$ is a stretching modulus, $L$ and $L_0$ are stretched
  vesicle length and length at rest, respectively
  ($\tfrac{1}{2}k_A(A - A_0)^2/A_0$ in three dimensions).
  If the stretching is too great, the vesicle ruptures
  and the free eneds either rejoin, repairing the vesicle,
  of move apart forming a flat bilayer.
\item[Tilt]
  The directors in Figure \ref{} are normal to the vesicle surface.
  However, there are situations where the directors are not normal
  to the surface and this introduces the tilt angle $\theta$
  given by $\cos \theta = \dd \cdot \NN$.
  The energy for tilt is also Hooken and behaves like
  $k_{\theta}|\dd \times \NN|^2$ for the tilt modulus $k_{\theta}$.
\end{enumerate}

With regard to vesicle membranes and bilayers, two prominent 
classes of models researchers consider are the
Canham-Helfrich model and the more general Helfrich model.
In the Canham-Helfrich model, the membrane is assumed to have
negligible thickness and the lipids that form the membrane bilayer
are normal to the interface $\Sigma$.  The elastic energy takes the form
\begin{equation}
\label{eq:Canham-Helfrich}
  \int_{\Sigma} k_B(H - k_0)^2 + k_{\theta} \sigma\, dS 
\end{equation}
where $H$ is the mean curvature, $k_0$ is a spontaneous curvature,
$G$ is the Gaussian curvature, and $k_B$, $k_G$, $\sigma$, and $\gamma$ are
moduli for bending, saddle splay, surface tension, and line tension, respectively. 
If $\Sigma$ is a closed surface, then the integral
of Gaussian curvature is constant due to the Gauss-Bonnet Theorem.

This is our first step to showing the energy of the granule-based
vesicles have the same elastic energy as bilayers in the limit $N_b \to \infty$.
Once we have simulations for large systems sizes, we can provide
evidence that the two formulations are the same.
So and so has made simulations with thousands of granules in three-D
and this is now a technical/not theoretical limitation.

\subsubsection{Do granule-based vesicles share hydrodynamic behavior of continuum vesicles?}

\begin{figure}R
  eview bend/stretch/tilt experiments
\end{figure}
\subsection{Vesicles in background flows}
\begin{itemize}
\item pull from JFM paper
\item we will consider background flows ...
\item results, rupture, critical shear rate
\item extensional flows
\item Taylor green flows; reorganization; do not know critical flow rate yet
\end{itemize}

\begin{remark}
  Mathematical problems: well-posedness of the system;
  Extensions to problems with transport;
  Calc-variational problem; place granules on fixed curve; study PDE system in
  SL -> 0; radius -> 0; Nb -> infty limit
\end{remark}
\begin{remark}
  In biophysics, tilt is defined by the tilt vector
  $\TT = \dd/\dd\cdot \NN - \NN$ so that the tilt energy density
  behaves like $\tan^2 \theta$ rather than $\sin^2 \theta$.
  These two energies densities are, however, asymptotically equal
  for small deformations.
Hamm and Kozlov [] and later Terzi and Deserno [], Pinigen et al. []
showed that the full Helfrich elastic energy of a \emph{monolayer} takes the form
\begin{equation}
\label{eq:Helfrich}
  \begin{aligned}
 &\int_{\Sigma}
  %\label{eq:Pinigan}
\tfrac{1}{2}k_{b}[(\nabla \cdot \mathbf{d} + k_{0})^{2} -  k^{2}_{0}]  
+ \tfrac{1}{2}k_{\theta}\mathbf{T}^{2} + \tfrac{1}{2}k_a[(\alpha - \alpha_0)^2 - \alpha_0^2] \\
&+ k_{c}\textbf{T} \cdot \nabla \nabla \cdot \mathbf{d}  + \tfrac{1}{2}k_{g}(\nabla \nabla \cdot \mathbf{d})^{2}
 + A\alpha \nabla \cdot \mathbf{d}
+ B \mathbf{T} \cdot \nabla \alpha \\
&- \tfrac{1}{2}k_c |\nabla \alpha|^2 + C \nabla \alpha \cdot \nabla \nabla \cdot \mathbf{d}\,dS
\end{aligned}
\end{equation}
where $\nabla$ and $\nabla \cdot$ are the surface gradient and surface divergence,
respectively, and $k_B$, $k_{\theta}$, $k_a$, $k_c$, $k_g$, $A$, $B$, $C$ are
appropriate elastic moduli.  An important and consequential distinction between
\eqref{eq:Canham-Helfrich} is the presence of the terms $\mathbf{T}$ and $\alpha$.
These are, respectively, the \emph{tilt} vector $\mathbf{T}$ measuring
the difference between the lipid director $\mathbf{d}$ and the surface normal
$\mathbf{N}$; the \emph{area per lipid} $\alpha$ area density at rest $\alpha_0$.
The two models \eqref{eq:Canham-Helfrich} and \eqref{eq:Helfrich} agree
when $\mathbf{T} = 0$ and $\alpha = \alpha_0$ everywhere.
\end{remark}

(Researchers Take from former background grant)

In biological processes like fusion and fission, however, the length scales of the
deformation (tens of nanometers) are comparable to membrane thickness (about 5 nm)
and so the detailed structure of bilayer cannot be ignored.
These models assign a surface $\Sigma$ to each of the two monolayers
of a bilayer, and a director field $\mathbf{n}:\Sigma \to \mathbb{R}^3$
for lipid orientation. Under very general continuum mechanical assumptions,

(Surface-director models).

The holy grail of biologically inspired fluid-interface models is
to have a formulation sufficient detailed and robust to make predictions
about biological processes.  Here, the Helfrich and Canham-Helfrich models
used throughout the field unfortunately fall short. For one,
realistic membranes are composed of a mixture of lipid species proteins.
Secondly, the membranes of living cells are constantly changing topology,
whether through fusion and fission with other membranes, or through
insertion or penetration by proteins and peptides.  Topological
changes are clumsy to incorporate into 
sharp interface formulations of the Helfrich and Canham-Helfrich energies
since computations rely on a parametrized surface of fixed topology.
Topological changes are permitted in phase field and level set formulations
of \eqref{eq:Canham-Helfrich}, but these methods smear out the 
details of lipid orientations, for example, that are important to the
process.  Recent work by [] and [] have incorporated lipid mixtures in \eqref{eq:Canham-Helfrich}
(although not \eqref{eq:Helfrich}), but these models have formidable complexity
due to the additional constraints and transport equations involved.

Nematic liquid crystals on surfaces is a related are of study.  These models,
which are closely related to \eqref{eq:Canham-Helfrich}, consider the energy
of a nematic liquid crystal (or Q-tensor ?) on a surface to study how the
surface geometry effects the director field and vice versa. Researchers
have formulated finite element methods for [][] and studied the existence
of minimizers []-[].  Liquid crystals are an extremely well-studied
are in mathematics [], where there are still a lot of open problems.

\begin{figure}
True bilayer; vesicle zero thickness; phase field; surface director
\end{figure}

We introduces \eqref{}-\eqref{} to overcome the challenges faced by
traditional Helfrich-type models of elastic membranes.

\noindent\textbf{Modeling vesicles} To make granular surfaces, we
form a collection of amphiphilic granules.  The granules have a
director $\mathbf{d} \in \mathbb{R}^n$ and the boundary condition
$g$ takes the form
\begin{equation}
g(\mathbf{x}) = \frac{1}{2}(\mathbf{d}\cdot(\mathbf{x}-\mathbf{a})/c + 1)
\end{equation}
where $c$ is granule radius.
This $g$ is smooth (real analytic even)
and takes values close to $1$ on the pole in the direction $\mathbf{d}$,
representing a hydrophobic face, and values close to $0$ on the pole
in the direction $-\mathbf{d}$ representing the hydrophilic face.
Then we define the well potential $f(\eta) = \tfrac{1}{2}\eta^2.$
This way, the hydrophilic side has the same phase as the bulk
($\eta = 0$, the minimum of $f$) and the hydrophobic side has
a higher potential energy phase.

Using \eqref{}-\eqref{}, suspensions of these granules self-organize
so that (i) apposing hydrophobic sides abut and (ii) granules align
side by side into sheets.  Vesicles are a stable configuration
of this process and the self-organization automatically expels or
absorbs the number of granules needed to minimize frustration between
the two leaflets.  But even for random initial configurations,
the granules form a collection of small vesicles and bilayer segments.
These disordered collections typically represent a local energy minimum 
because under a slight perturbation, the small vesicles and segments
further combine to form larger, stable vesicles.

%\setcounter{page}{1}
%\addcontentsline{toc}{section}{Bibliography}
%\bibliographystyle{abbrvnat}
%%
%\bibliography{refs}
%
%
%
%\end{document}

### 2022-11-08 NSF2022/Description/backgroundv2.tex
working on SA2
fixing title

@@
 {\bf Collaborative Research:
-Collaborative research: self-orgzanization by moving domain elliptic PDE}\\
+Collaborative research: Self-organization modeled by moving domain
+elliptic PDEs} \\
 {\em Rolf Ryham (PI, Fordham University),
@@
 \subsection{Boundary integral formulation}
+\label{sec:bie}
 

### 2022-11-08 NSF2022/Description/priorsupport.tex
removed extra commas in bibtex

--- 2021-11-15 NSF2021/Description/priorsupport.tex
@@
 project. One paper will be submitted before December
-2021~\cite{lin-her-qua-che2021}.
+2021~\cite{che-lin-her-qua2022}.
 
@@
 Their recent collaborative work on the HAP model in two
-dimensions~\cite{FuQuRyYo20} has provided a solid foundation for the
+dimensions~\cite{FuQuRyYo22} has provided a solid foundation for the
 proposed research.

### 2022-11-08 NSF2022/Description/specificaim2.tex
removed extra commas in bibtex

@@
 simulate two-dimensional suspensions of amphiphilic
-particles~\cite{Fu2018_SIAM, FuQuRyYo20, fu-ryh-qua-you2022}. Moreover,
+particles~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022}. Moreover,
 elements of these formulations have been described in three
@@
 recently showed that these quadrature methods can be extended to other
-PDEs with singularity subtraction~\cite{che-lin-her-qua2021}. For
+PDEs with singularity subtraction~\cite{che-lin-her-qua2022}. For
 example, the fundamental solution of the screened Laplace

### 2022-11-09 NSF2022/Description/backgroundv2.tex

@@
 Recently, we have developed a new mathematical model of
-self-organization~\cite{FuQuRyYo22,ru-ryh-qua-you2022,Fu2018_SIAM}. The
+self-organization~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}. The
 model takes ideas from the phase field method and leverages boundary

### 2022-11-09 NSF2022/Description/backgroundv2.tex
background mods

@@
 $\aa_i(t)$ are the granule centers, and $\XX$ is a reference coordinate.
-The transformations \eqref{eq:RBT} tell us how the granules move through space
-and we use the shape and
-boundary conditions for $U_i$ to capture the local
-properties of the suspended media e.g., lipids, peptides, Janus spheres.
+The transformations \eqref{eq:RBT} tell us how the granules move through space.
 Throughout, $\nu$ refers to unit normal pointing into $\Omega(t)$ (Figure \ref{fig:flow_map}).
@@
   \label{eqn:phase}
-  -\rho^2 \Delta \eta + f'(\eta) &= 0, && &&\quad \xx \in \Omega(t),\\
+  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, && &&\quad \xx \in \Omega(t),\\
 \label{eqn:noslip}        
@@
 \label{eqn:material}
-\eta(\xx) &= h_i(\XX), &&  &&\quad \xx \in \Gamma_i(t),
+\phi(\xx) &= h_i(\XX), &&  &&\quad \xx \in \Gamma_i(t),
 \end{alignat}
@@
 \label{eqn:stressbalance}
-\int_{\Gamma_i} \left[\mu(\nabla \uu + \nabla \uu^T + pI) + T_i\right]\nnu \,\dif s = \mathbf{0},\quad
+\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
+\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
 \end{equation}
@@
 \label{eqn:hydro_stress}
-T_i = -\rho^{-1} f'(\eta)I
-  + \rho\left(\tfrac{1}{2}|\nabla \eta|^2I - \nabla \eta \nabla
-  \eta^T\right)
+\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
+T_i = -\epsilon^{-1} W'(\phi)I
+  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
+  \phi^T\right)
 \end{equation}
-for the identity matrix $I$.
+are the hydrodynamic and phase stresses, respectively; 
+$I$ is the $n\times n$ identity matrix.
+For vectors $\aa, \bb \in \mathbb{R}^2$,
+we follow the usual convention of defining
+the ``cross product'' as
+$\aa \times \bb = (\aa^{\perp} \cdot \bb) \kk$
+where $\kk = (0,0,1) \in \mathbb{R}^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$.
 
 The above form a semi-linear elliptic 
-system for evolution of the granules.  Equation~\eqref{eqn:stokes} is the
+system for evolution of the granules.  Equations~\eqref{eqn:stokes} are the
 Stokes equations that describes the velocity $\uu$ and pressure $p$ of
 the viscous aqueous phase.  Equation~\eqref{eqn:phase} describes the
-phase transitions of the scalar order parameter $\eta$ with a decay
-length $\rho$. Mathematically, this order parameter is responsible for
+phase transitions of the scalar order parameter $\phi$ with a decay
+length $\epsilon$.
+The scalar function $W(\phi)$ is a well potential where the local 
+minimima representing low energy states of the water phase.
+Mathematically, this order parameter is responsible for
 the attraction and adhesion between granules that want to align boundaries
@@
 specifying the phases at water-granule interface.
-In other words, the boundary condition for $\eta$ is transported by the flow.
+The boundary condition for $\phi$ is transported by the flow
+and satisfies $\phi_t + \uu \cdot \nabla \phi = 0$ on $\Gamma_i$.
 Finally,
-equation~\eqref{eqn:stressbalance} closes the system by requiring that
-the hydrodynamic stress is balanced by the phase stress $T_i$ in
+equation~\eqref{eqn:stressbalance} closes the system by
+requiring that the force and torque generated by 
+hydrodynamic stress balances that generated by phase stress $T_i$ in
 \eqref{eqn:hydro_stress}.
@@
 We call the rigid bodies $U_i(t)$ granules since they are small, compact
-parcels of a suspended medium, e.g. lipids, Janus spheres.
+parcels of a suspended media, e.g. lipids, Janus spheres.
+We use the shape and boundary conditions for $U_i$ to capture the local
+properties of the suspended media. 
 We have departed from the terminology ``particles'' here
 to emphasize the role played by their finite size. 
-In our simulations
-(see section \ref{sec:specific_aim1}),
+In our simulations (see section \ref{sec:specific_aim1}),
 we include a finite length repulsion to avoid particle
@@
 
-Intriguingly, the
-formulation~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} captures
+The system~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
+has the energy law
+\begin{equation}
+\label{eq:energy_law}
+  \frac{d}{dt}E
+  = - \int_{\Omega_t}\tfrac{1}{2}\mu|\nabla \uu + \nabla
+  \uu^T|^2 \,d\xx,\quad
+    E = \int_{\Omega(t)}
+  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
+\end{equation}
+Here $E$ is the energy stored in the phase transitions.
+Because $E$ depends both on $\phi$ and $\Omega(t)$,
+the derivation of \eqref{eq:energy_law}
+is somewhat subtle and has been worked out in detail in \cite{Fu2018_SIAM}.
+It goes as follows.
+Using the Rayleigh Transport Theorem, 
+the time derivative out $E$ yields an energy
+density flux involving the phase stress $T_i$
+at the boundary, plus a bulk term involving 
+the Euler-Lagrange derivative of $E.$
+The Euler-Lagrange derivative vanishes due to~\eqref{eqn:phase}
+and the boundary flux transforms into viscous dissipation due to 
+\eqref{eqn:hydro_stress} and the Stokes equations.
+
+Mathematically, a change in granule configuration
+instantaneously changes the phase energy $E$
+the dynamics are such that energy is lost due to hydrodynamic dissipation.
+Further details and generalizations are provided in
+the Specific Aim 1 section \ref{sec:specific_aim1}.
+
+The model has a broad range of applicability to self-organization
+phenomena in chemistry and biological physics. For one,
+the formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures
 exactly the right behavior expected from amphiphilic self-assembly.
@@
 equilibrium morphologies (Figure~\ref{fig:self-assembly2}).
+Since the formulation is
+scale independent, it can represent a suspension of amphiphiles, where
+the granules represent the mean properties of a small collection of
+lipids, at the nanoscopic scale. For larger scales, the representation
+is literal and the granules Janus spheres. The proposal deals with the
+physical origins in section ().
+\todo[inline]{
+List applications; don't forget Bertozzi.}
 
@@
 
-The system~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} has an elegant
-mathematical structure. In terms of locally in time well-posedness,
-given disjoint granules with sufficiently smooth boundaries and data, the
-system always has a solution and these solutions have a locally
-Lipschitz dependence on the particle centers and orientations.
-Solutions of~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} obey the
-energy law
-\begin{align}
-  F = \int_{\Omega_t}
-  \left(\rho |\nabla \eta|^2 + \rho^{-1} f(\eta)\right) \,d\xx,
-  \quad
-  \frac{d}{dt}F
-  = - \int_{\Omega_t} \left(\tfrac{1}{2}\mu|\nabla \uu + \nabla
-  \uu^T|^2\right) \,d\xx.
-\end{align}
-Mathematically, this energy law states that the free energy $F$ of the
-water order phase transitions, which depends on the granule
-configurations, is lost due to hydrodynamic dissipation. It is evident
-that minimizers of the functional $F$ are unique and satisfy the
-Euler-Lagrange equation~\eqref{eqn:phase}. There is a subtlety in the
-energy law, though. Namely, the time derivative of the free energy $F$
-also involves the moving boundary, accounted for by the Rayleigh
-Transport Theorem, and the fact that the boundary data for $\eta$ are
-transported by the rigid body motion. In fact, the water order surface
-stress $T_i$ is the variational derivative that shows up in this
-calculation.
-
 \begin{figure}[t!]
@@
 \end{figure}
-The model has a broad range of applicability to self-organization
-phenomena in chemistry and biological physics. Since the formulation is
-scale independent, it can represent a suspension of amphiphiles, where
-the granules represent the mean properties of a small collection of
-lipids, at the nanoscopic scale. For larger scales, the representation
-is literal and the granules Janus spheres. The proposal deals with the
-physical origins in section ().
-
-To summarize, the
-formulation~\eqref{eqn:stokes}--\eqref{eqn:stressbalance} shares a lot
-of the features in phase field modeling, with the big exception that the
-free energy depends on the granule configurations, rather than phase field
-function. To make an explicit connection though, we can consider a phase
-field model where one ``fluid'' phase instantaneously reaches minimality
-while the other ``solid'' phase moves to further decrease free energy.
-The model is also closely related to a recent and strongly developing
-direction studying colloids immersed in nematic liquid crystals. As is
-the case for nematics, it is natural to understand what is the effect of
-the flow in such a context, but a first step is to obtain some solid
-well-posedness results. The proposal discusses some mathematical
-generalizations in section ().
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-11-09 NSF2022/Description/specificaim2.tex

@@
 will allow us to use results we have shown for $\mathcal{O}(100)$
-grains, and extend them to suspensions with 100X--1000X more grains.
+granules, and extend them to suspensions with 100X--1000X more granules.
 These methods will be motivated by models and analysis developed in
 Specific Aims 1 and 3. \S\ref{subsec:AC} describes how the non-linear
-Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved using an IE
-formulation. Then, \S\ref{subsec:NumericalIssues} describes how we will
-combine accurate quadrature and fast summation methods to accelerate the
-time to accurate solutions. A natural extension to create simulations
-that are realizable by experimentalists is to include confinement, and
-this is discussed in \S\ref{subsec:Confinement}. This extension will
-also allow us to study new rheological properties of the suspensions.
-Finally, \S\ref{subsec:timeStepping} proposes collision-aware adaptive
-time stepping methods.
+equation for the order parameter~\eqref{eqn:phase} will be iteratively
+solved using an IE formulation. Then, \S\ref{subsec:NumericalIssues}
+describes how we will combine accurate quadrature and fast summation
+methods to accelerate the time to accurate solutions. A natural
+extension to create simulations that are realizable by experimentalists
+is to include confinement, and this is discussed in
+\S\ref{subsec:Confinement}. This extension will also allow us to study
+new rheological properties of the suspensions.  Finally,
+\S\ref{subsec:timeStepping} proposes collision-aware adaptive time
+stepping methods.
 
@@
 $f(u) = u^2$---this choice results in the linear screened Laplace
-equation. For a more general $f$, such as a double well potential, we
-will interpret the solution of~\eqref{eqn:phase} as the root finding
-problem for
+equation. For a more general double well potential $f$, with local
+minimums at $u_0$ and $u_1$, we will interpret the solution
+of~\eqref{eqn:phase} as the root finding problem for
 \begin{align}
-  \label{eq:F}
+  \label{eqn:phaseRoot}
   J[u] = -\rho^2 \Delta u + \tfrac{1}{2}f'(u).
 \end{align}
-This non-linear PDE will be solved with Newton's method
-\begin{align*}
-  u^{N+1} = u^{N} - \alpha (dJ^N)^{-1} J(u^N),
-\end{align*}
-where $dJ^N = -\rho^2 \Delta + \tfrac{1}{2}f''(u^N)$ is the Fr\'{e}chet
-derivative of $F$, and $\alpha$ is the step size which will be
-determined using backtracking. As expected, the biggest computational
-challenge is solving $- \rho^2 \Delta v + \tfrac{1}{2}f''(u^{N}) v =
-J[u^N]$. Solving this variable coefficient PDE with an integral equation
-is challenging since a fundamental solution is not readily available.
-However, since $f''(u_0) = f''(u_1) = 2a(u_1 - u)0)^2 + 2c$, f' We
-propose to instead use an inexact Newton's method where $dJ^{-1}$ is
-defined in terms of the continuous, piecewise quadratic approximation
-\begin{align*}
-  f(u) \approx \tilde{f}(u) = bu + \begin{cases}
-    a(u - u_0)^2, &\mbox{if } u \leq (u_0 + u_1)/2, \\
-    (u - u_1)^2 + \tfrac{1}{4}(a-1)(u_0-u_1)^2 , &\mbox{if } u > (u_0 + u_1)/2,
-  \end{cases}
-\end{align*}
-where $a>0$, and the resulting inexact Newton's method requires solving
-the piecewise constant PDE
-\begin{align}
-  \label{eq:screenedPoisson}
-  -\rho^2 \Delta v + \tfrac{1}{2}\tilde{f}''(u^{N})v = J[u^N],
-\end{align}
-which is a screened Poisson equation with piecewise a constant screening
-coefficient. We test the efficacy of exact and inexact Newton's method
-applied to~\eqref{eq:F} in $(0,1)$ by discretizing $dJ$ with a
-second-order finite difference method. The choice of parameters $a$,
-$b$, $u_0$, and $u_1$ result in the double well potential illustrated in
-Figure~\ref{fig:CA}(a), and both the exact and inexact Newton's methods
-converge to the solution in Figure~\ref{fig:CA}(b).
+This non-linear PDE will be solved with Newton's method, $u^{N+1} =
+u^{N} - \alpha (dJ^N)^{-1} J(u^N)$, where $dJ^N = -\rho^2 \Delta +
+\tfrac{1}{2}f''(u^N)$ is the Fr\'{e}chet derivative of $F$, and $\alpha$
+is the step size which will be determined using backtracking. As
+expected, the biggest computational challenge is solving $-\rho^2 \Delta
+v + \tfrac{1}{2}f''(u^{N}) v = J[u^N]$. Solving this variable
+coefficient PDE with an integral equation is challenging since a
+fundamental solution is not readily available. However, by choosing a
+double well potential with $f''(u_0) = f''(u_1) = \beta$, we propose to
+instead use an inexact Newton's method where $dJ^{-1}$ is approximated
+by solving $-\rho^2 \Delta v + \tfrac{beta}{2} v = J[u^N]$. We test the
+efficacy of exact and inexact Newton's method applied
+to~\eqref{eqn:phaseRoot} in $(0,1)$ by discretizing $dJ$ with a
+second-order finite difference method. The double well potential is
+illustrated in Figure~\ref{fig:CA}(a), and both the exact and inexact
+Newton's methods converge to the solution in Figure~\ref{fig:CA}(b).
 Figure~\ref{fig:CA}(c) shows the max norm of the residual at each Newton
 iterate when using the exact second derivative (red curve) and the
-piecewise constant approximate (blue curve). While the inexact Newton's
+approximate second derivative (blue curve). While the inexact Newton's
 method requires roughly twice as many iterations to reach of a tolerance
-of $10^{-4}$, each iteration is significantly cheaper in higher
-dimensions.
+of $10^{-4}$, each iteration is significantly cheaper to apply.
+\todo[inline]{put pics here}
 
@@
 challenges must be overcome before the code can be used to simulate
-systems with large numbers of grains. For example, when grains are close
-to one another, which is inevitable in dense suspensions, the resulting
-integrals are nearly-singular. This issue is well-known in the IE
-community and several algorithms have been developed in the last 30
+systems with large numbers of granules. For example, when granules are
+close to one another, which is inevitable in dense suspensions, the
+resulting integrals are nearly-singular. This issue is well-known in the
+IE community and several algorithms have been developed in the last 30
 years. An incomplete list of methods that address near-singular
@@
 gimbutas2013sisc}. However, since we are interested in round (2D) and
-spherical (3D) grains, we will exploit the fact that integrals can be
+spherical (3D) granules, we will exploit the fact that integrals can be
 computed exactly after transforming the integrals to to a Fourier (2D)
@@
 In experiments, it is known that interactions between bounding walls and
-grains cannot be ignored~\cite{qua-gan-you2021,
+granules cannot be ignored~\cite{qua-gan-you2021,
 KaouiHartingMisbah2011_PRE, her-sto-gra2005}. Therefore, the necessary

### 2022-11-09 NSF2022/Description/backgroundv2.tex

@@
   -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
-  && \nabla \cdot \uu = 0, && \quad \xx \in \Omega(t), \label {eqn:stokes} \\
+  &&\quad \nabla \cdot \uu = 0, && \quad \xx \in \Omega(t), \label {eqn:stokes} \\
   \label{eqn:phase}
@@
 \label{eqn:noslip}        
-\uu(\xx) &= \frac{dF_i}{dt}(\XX,t)
+\frac{dF_i}{dt}(\XX,t) & = \uu(\xx) 
 &&=\vv_i + \omega_i \times (\xx - \aa_i), 
@@
 \sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
-T_i = -\epsilon^{-1} W'(\phi)I
+T_i = \gamma\left[\epsilon^{-1} W'(\phi)I
   + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
-  \phi^T\right)
+  \phi^T\right)\right]
 \end{equation}
@@
 Stokes equations that describes the velocity $\uu$ and pressure $p$ of
-the viscous aqueous phase.  Equation~\eqref{eqn:phase} describes the
+the aqueous region with viscosity $\mu$.  Equation~\eqref{eqn:phase} describes the
 phase transitions of the scalar order parameter $\phi$ with a decay
@@
 \eqref{eqn:hydro_stress}.
+The parameter $\gamma > 0$ is surface tension.
 
@@
   \uu^T|^2 \,d\xx,\quad
-    E = \int_{\Omega(t)}
+    E = \gamma \int_{\Omega(t)}
   \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
@@
 Here $E$ is the energy stored in the phase transitions.
+Mathematically, the energy law states that changes
+in granule configuration instantaneously change the phase energy $E$.
+The dynamics are such that the change energy
+is lost due to hydrodynamic dissipation.
+Further details and generalizations are provided in
+the Specific Aim 1 section \ref{sec:specific_aim1}.
+
 Because $E$ depends both on $\phi$ and $\Omega(t)$,
@@
 
-Mathematically, a change in granule configuration
-instantaneously changes the phase energy $E$
-the dynamics are such that energy is lost due to hydrodynamic dissipation.
-Further details and generalizations are provided in
-the Specific Aim 1 section \ref{sec:specific_aim1}.
+In terms of physical justification, the
+derivation of the one-dimensional version of our model
+was carried out by \cite{MaRa76} and \cite{ErLjCl89}
+using a Landau expansion of the
+free energy density for a single-well potential.
+The double-well potential case was derived by
+Gompper in \cite{GoHaKo94} to describe metastable coordination of water.
+In the field of surface chemistry \cite{Israelachvili1954},
+there is a large empirical literature on properties of
+long-range hydrophobic interaction~\cite{LeRaPa77,KoNa15,
+Nagle17,Lum1999, Lin2005, Meyer2006, Ducker2016,Jackson2016,Gletal88,Aketal17,Ch05}.
+The stress~\eqref{eqn:stressbalance} was first
+identified by PIs Ryham and Young in~\cite{Fu2018_SIAM}
+and generalizes one-dimensional hydrophobic interaction to
+the $n$-dimensional setting.
+
+Finally, we mention that in the single-well case
+$W(\phi) = \tfrac{1}{2}u^2,$ \eqref{eqn:phase} takes the form
+of a screened Laplace (SL) equation $-\epsilon^2 \Delta \phi + \phi =0$.
+If the material label $h_i = 1$ everywhere, then $\phi$
+has a boundary layer going from $1$ at the boundary to $0$ in the bulk
+and one can prove that 
+\begin{equation}
+\label{eqn:math_motivation}
+\lim_{\epsilon \to 0} E = \frac{\gamma}{2} \int_{\partial \Omega} 1 \,dS
+\end{equation}
+under the assumption that $\Omega$ has a class $\mathbf{C}^2$ boundary \cite{}.
+In other words, the phase energy can be viewed as an
+approximation of surface energy that ``extends'' into the bulk.
+In the general case, $h_i^2$ replaces $1$ in \eqref{eqn:math_motivation}.
+We are confident that \eqref{eq:RBT}--\eqref{eqn:stressbalance}
+is a correct description of long-range surface interactions.
 

### 2022-11-09 NSF2022/Description/backgroundv2.tex
SA1 getting there

@@
   and hydrophobic interactions. {\em Right:} Particles translate and
-  rotate to lower the free energy $F[u]$ subject to \eqref{eq:SL}, $f(u)
-  = u^2$, and reach a minimal configuration in panel C. The colormap is
+  rotate to lower the free energy $F[u]$ subject to \eqref{eq:SL}, $W(\phi)
+  = \phi^2$, and reach a minimal configuration in panel C. The colormap is
   blue for $u = 0$ and red for $u = 1$. The arrows are the velocity
@@
 Finally, we mention that in the single-well case
-$W(\phi) = \tfrac{1}{2}u^2,$ \eqref{eqn:phase} takes the form
+$W(\phi) = \tfrac{1}{2}\phi^2,$ \eqref{eqn:phase} takes the form
 of a screened Laplace (SL) equation $-\epsilon^2 \Delta \phi + \phi =0$.

### 2022-11-09 NSF2022/Description/specificaim2.tex
new refs

@@
 simulate two-dimensional suspensions of amphiphilic
-particles~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022}. Moreover,
-elements of these formulations have been described in three
+particles~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022}, and
+elements of these formulations have been developed in three
 dimensions~\cite{ying_2006, manasthesis, rac-gre2016}. This proposal
@@
 is to include confinement, and this is discussed in
-\S\ref{subsec:Confinement}. This extension will also allow us to study
+\S\ref{subsec:Confinement}. This extension will also allow us to develop
 new rheological properties of the suspensions.  Finally,
@@
 
+\begin{wrapfigure}[28]{l}{1.8in}
+  \vspace{-8pt}
+  \centering
+  \input{figures/doublewell.tikz} 
+  \caption{\label{fig:CA} \footnotesize (a) A double well potential. (b)
+  The solution of the one-dimensional phase
+  transition~\eqref{eqn:phase}. (c) The convergence of exact and inexact
+  Newton's methods.}
+\end{wrapfigure}
 The PIs have developed numerical methods to solve~\eqref{eqn:phase} when
-$f(u) = u^2$---this choice results in the linear screened Laplace
-equation. For a more general double well potential $f$, with local
-minimums at $u_0$ and $u_1$, we will interpret the solution
+$W(\phi) = \phi^2$---this choice results in the linear screened Laplace
+equation. For a general double well potential $W$, with local minima at
+$\phi_0$ and $\phi_1$, we will interpret the solution
 of~\eqref{eqn:phase} as the root finding problem for
@@
   \label{eqn:phaseRoot}
-  J[u] = -\rho^2 \Delta u + \tfrac{1}{2}f'(u).
+  J[\phi] = -\epsilon^2 \Delta \phi + \tfrac{1}{2}W'(\phi).
 \end{align}
-This non-linear PDE will be solved with Newton's method, $u^{N+1} =
-u^{N} - \alpha (dJ^N)^{-1} J(u^N)$, where $dJ^N = -\rho^2 \Delta +
-\tfrac{1}{2}f''(u^N)$ is the Fr\'{e}chet derivative of $F$, and $\alpha$
-is the step size which will be determined using backtracking. As
-expected, the biggest computational challenge is solving $-\rho^2 \Delta
-v + \tfrac{1}{2}f''(u^{N}) v = J[u^N]$. Solving this variable
-coefficient PDE with an integral equation is challenging since a
-fundamental solution is not readily available. However, by choosing a
-double well potential with $f''(u_0) = f''(u_1) = \beta$, we propose to
-instead use an inexact Newton's method where $dJ^{-1}$ is approximated
-by solving $-\rho^2 \Delta v + \tfrac{beta}{2} v = J[u^N]$. We test the
+Equation~\eqref{eqn:phaseRoot} will be solved with Newton's method,
+$\phi^{N+1} = \phi^{N} - \alpha (dJ^N)^{-1} J(\phi^N)$, where $dJ^N =
+-\epsilon^2 \Delta + \tfrac{1}{2}W''(\phi^N)$ is the Fr\'{e}chet
+derivative of $F$, and $\alpha$ is the step size that will be determined
+using backtracking. As expected, the biggest computational challenge is
+solving $-\epsilon^2 \Delta v + \tfrac{1}{2}W''(\phi^{N}) v =
+J[\phi^N]$. Solving this variable coefficient PDE with an integral
+equation is challenging since a fundamental solution is not readily
+available. However, by choosing a double well potential with
+$W''(\phi_0) = W''(\phi_1) = \beta$, we propose to instead use an
+inexact Newton's method where $dJ^{-1}$ is approximated by solving
+$-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$. We test the
 efficacy of exact and inexact Newton's method applied
@@
 of $10^{-4}$, each iteration is significantly cheaper to apply.
-\todo[inline]{put pics here}
 
-%\begin{wrapfigure}[27]{l}{1.8in}
-%  \vspace{-4pt}
-%  \centering
-%  \input{figures/doublewell.tikz} 
-%  \caption{\label{fig:CA} (a) The double well potential $u_0 =
-%  0.5$, $u_1 = 2$, $a = 1$, $b = 0.4$. (b) The solution of the
-%  Allen-Cahn equation~\eqref{eq:SL}. (c) The convergence of the exact
-%  and inexact Newton's methods.}
-%\end{wrapfigure}
 Having demonstrated that the inexact Newton method converges in one
 dimension, it will be coupled with IE formulations to
-solve~\eqref{eq:SL} in two and three dimensions. We first partition
-$\Omega$ into $\Omega_0 = \{\xx \in \Omega \:|\: u(\xx) < (u_0 +
-u_1)/2\}$ and $\Omega_1 = \{\xx \in \Omega \:|\: u(\xx) > (u_0 +
-u_1)/2\}$, and we let $\Lambda = \{\xx \in \Omega \:|\: u(\xx) = (u_0 +
-u_1)/2 \}$ be their common boundary, and we let $G_0$ be the fundamental
-solution of $(-\rho^2 \Delta + a)$ and $G_1$ be the fundamental
-solution of $(-\rho^2 \Delta + 1)$. Then, the solution
-of~\eqref{eq:screenedPoisson} can be written as $u = u^P + u^H$ where
-$u^P$ is a volume potential and $u^H$ is a layer potential. The volume
-potential is
+solve~\eqref{eqn:phase} in two and three dimensions. The solution of
+$-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$ can be written
+as $v = \phi^P + \phi^H$ where $\phi^P$ is a volume potential and
+$\phi^H$ is a layer potential. The volume potential is
 \begin{align*}
-  u^{P}(\xx) = \int_{\Omega_i} G_i(\xx,\yy) J[u^N](\yy)\, d\yy, 
-    \quad i = 1,2,
+  \phi^{P}(\xx) = \int_{\Omega(t)} G(\xx,\yy) J[\phi^N](\yy)\, d\yy, 
+    \quad \xx \in \Omega(t),
 \end{align*}
-but it is discontinuous across $\Lambda$ and does not satisfy the
-prescribed hydrophobic boundary conditions on the particles $\Gamma_i$.
-Assuming the particles are entirely contained in the hydrophobic region,
-the boundary conditions will be enforced with the layer potentials
-\begin{align*}
-  u^{H}(\xx) = \begin{cases}
-    \displaystyle\int_{\Lambda} G_0(\xx,\yy) \eta_0(\yy) \, ds_\yy + 
-    \displaystyle\int_{\Gamma} \pderiv{}{\nn_\yy} G_0(\xx,\yy)
-      \sigma(\yy) \,ds_\yy, \quad & \xx \in \Omega_0, \\
-    \displaystyle\int_{\Lambda} G_1(\xx,\yy) \eta_1(\yy) \, ds_\yy,
-     & \xx \in \Omega_1.
-  \end{cases}
-\end{align*}
-The density functions $\sigma$, $\eta_0$, and $\eta_1$ are determined so
-that $u = u^P + u^H$ satisfies the hydrophobic boundary condition on
-$\Gamma = \cup_i \Gamma_i$, and that it is continuous and differentiable
-across $\Lambda$. This approach of using IEs to solve elliptic PDEs with
-piecewise constant coefficients has successfully been used in other
-application such as scattering~\cite{hyu-bar2014, che-cho-cai2018}.
+where $G$ is the fundamental solution of $-\epsilon^2 \Delta +
+\tfrac{\beta}{2}$. Volume potentials are more challenging to compute
+numerically than layer potentials. However, very recently, a suite of
+new methods have been developed to accurately and efficiently compute
+volume potentials~\cite{fry-leh-tor2018, and-zhu-vee2022}. The boundary
+condition will be enforced using $\phi^H(\xx)$ which will be represented
+as a double-layer potential. This approach of combining volume and layer
+potentials has successfully been used by PI BQ~\cite{kro-qua2010} and
+others~\cite{fry-kro-tor2019, kli-ask-kro2020, che-hua-lei2005}.
 

### 2022-11-09 NSF2022/Description/specificaim2.tex
first draft of Newton solver sec

@@
 % ----------------------------------------------------------------------
-\subsubsection{Iterative methods for the Allen-Cahn HAP model}
+\subsubsection{An inexact Newton solver for the phase transition PDE}
 \label{subsec:AC}
@@
 $W(\phi) = \phi^2$---this choice results in the linear screened Laplace
-equation. For a general double well potential $W$, with local minima at
-$\phi_0$ and $\phi_1$, we will interpret the solution
-of~\eqref{eqn:phase} as the root finding problem for
+equation. For a general double well potential $W$ with local minima at
+$\phi_0$ and $\phi_1$, we propose to interpret the solution as the root
+finding problem for
 \begin{align}
@@
 derivative of $F$, and $\alpha$ is the step size that will be determined
-using backtracking. As expected, the biggest computational challenge is
-solving $-\epsilon^2 \Delta v + \tfrac{1}{2}W''(\phi^{N}) v =
-J[\phi^N]$. Solving this variable coefficient PDE with an integral
-equation is challenging since a fundamental solution is not readily
-available. However, by choosing a double well potential with
-$W''(\phi_0) = W''(\phi_1) = \beta$, we propose to instead use an
+using backtracking. This requires Solving the variable coefficient PDE
+$-\epsilon^2 \Delta v + \tfrac{1}{2}W''(\phi^{N}) v = J[\phi^N]$ with an
+integral equation, but this is challenging since a fundamental solution
+is not readily available. However, by choosing a double well potential
+with $W''(\phi_0) = W''(\phi_1) = \beta$, we propose to instead use an
 inexact Newton's method where $dJ^{-1}$ is approximated by solving
 $-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$. We test the
-efficacy of exact and inexact Newton's method applied
-to~\eqref{eqn:phaseRoot} in $(0,1)$ by discretizing $dJ$ with a
-second-order finite difference method. The double well potential is
-illustrated in Figure~\ref{fig:CA}(a), and both the exact and inexact
+efficacy of the exact and inexact Newton's method applied
+to~\eqref{eqn:phaseRoot} in $(0,1) \subset \RR$ by discretizing $dJ$
+with a second-order finite difference stencil. The double well potential
+is illustrated in Figure~\ref{fig:CA}(a), and both the exact and inexact
 Newton's methods converge to the solution in Figure~\ref{fig:CA}(b).
-Figure~\ref{fig:CA}(c) shows the max norm of the residual at each Newton
+Figure~\ref{fig:CA}(c) shows the norm of the residual at each Newton
 iterate when using the exact second derivative (red curve) and the
@@
 $-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$ can be written
-as $v = \phi^P + \phi^H$ where $\phi^P$ is a volume potential and
-$\phi^H$ is a layer potential. The volume potential is
+as $v = v^P + v^H$ where $v^P$ is a volume potential and
+$v^H$ is the double layer potential. The volume potential is
 \begin{align*}
-  \phi^{P}(\xx) = \int_{\Omega(t)} G(\xx,\yy) J[\phi^N](\yy)\, d\yy, 
+  v^{P}(\xx) = \int_{\Omega(t)} G(\xx,\yy) J[\phi^N](\yy)\, d\yy, 
     \quad \xx \in \Omega(t),
@@
 where $G$ is the fundamental solution of $-\epsilon^2 \Delta +
-\tfrac{\beta}{2}$. Volume potentials are more challenging to compute
-numerically than layer potentials. However, very recently, a suite of
-new methods have been developed to accurately and efficiently compute
-volume potentials~\cite{fry-leh-tor2018, and-zhu-vee2022}. The boundary
+\tfrac{\beta}{2}$. Volume potentials are more challenging to numerically
+compute than layer potentials, but methods have recently been developed
+to accurately and efficiently compute volume
+potentials~\cite{fry-leh-tor2018, and-zhu-vee2022}. The boundary
 condition will be enforced using $\phi^H(\xx)$ which will be represented

### 2022-11-09 NSF2022/Description/specificaim2.tex
worked on SA2

@@
 derivative of $F$, and $\alpha$ is the step size that will be determined
-using backtracking. This requires Solving the variable coefficient PDE
-$-\epsilon^2 \Delta v + \tfrac{1}{2}W''(\phi^{N}) v = J[\phi^N]$ with an
-integral equation, but this is challenging since a fundamental solution
-is not readily available. However, by choosing a double well potential
-with $W''(\phi_0) = W''(\phi_1) = \beta$, we propose to instead use an
-inexact Newton's method where $dJ^{-1}$ is approximated by solving
-$-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$. We test the
-efficacy of the exact and inexact Newton's method applied
+using backtracking. This requires solving the variable coefficient PDE
+$-\epsilon^2 \Delta v + \tfrac{1}{2}W''(\phi^{N}) v = J[\phi^N]$, which
+is challenging with an integral equation since a fundamental solution is
+not readily available. However, by choosing a double well potential with
+$W''(\phi_0) = W''(\phi_1) = \beta$, we propose to instead use an
+inexact Newton's method where $dJ^{-1}$ is approximated with the
+solution of $-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$. We
+test the efficacy of the exact and inexact Newton's method applied
 to~\eqref{eqn:phaseRoot} in $(0,1) \subset \RR$ by discretizing $dJ$
@@
 $-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$ can be written
-as $v = v^P + v^H$ where $v^P$ is a volume potential and
-$v^H$ is the double layer potential. The volume potential is
+as $v = v^P + v^H$ where $v^P$ is a volume potential and $v^H$ is a
+homogeneous solution of the PDE, which is represented as a layer
+potential, and is used to satisfy the boundary condition. The volume
+potential is
 \begin{align*}
@@
 where $G$ is the fundamental solution of $-\epsilon^2 \Delta +
-\tfrac{\beta}{2}$. Volume potentials are more challenging to numerically
-compute than layer potentials, but methods have recently been developed
-to accurately and efficiently compute volume
-potentials~\cite{fry-leh-tor2018, and-zhu-vee2022}. The boundary
-condition will be enforced using $\phi^H(\xx)$ which will be represented
-as a double-layer potential. This approach of combining volume and layer
-potentials has successfully been used by PI BQ~\cite{kro-qua2010} and
-others~\cite{fry-kro-tor2019, kli-ask-kro2020, che-hua-lei2005}.
+\tfrac{\beta}{2}$. Traditionally, volume potentials are more challenging
+to compute than layer potentials, but new methods have recently been
+developed that allows them to be computed accurately and
+efficiently~\cite{fry-leh-tor2018, and-zhu-vee2022}. This approach of
+combining volume and layer potentials has successfully been used by PI
+BQ~\cite{kro-qua2010} and others~\cite{fry-kro-tor2019, kli-ask-kro2020,
+che-hua-lei2005}.
 

### 2022-11-10 NSF2022/Description/specificaim1v2.tex
more BG mods

@@
 
-\section{Specific Aim 2: Membrane vesicles as self-organized granules}
+\section{Specific Aim 1: Membrane vesicles as self-organized granules}
+\label{sec:specific_aim1}
 \subsection{Prior work related to the proposal.}
@@
 
+A natural questions concerns the well-posedness
+\eqref{eq:RBT}--\eqref{eqn:stressbalance}
+and its generalizations. A recent and strongly developing direction in
+the area of nematics liquid crystals concerns the interaction of
+Landau de Gennes functionals like \eqref{eq:energy_law} with colloids
+\cite{doi:10.1098/rsta.2020.0432}.
+In this spirit, a first step to understand the effect of the flow
+in our model is to obtain some solid well-posedness results.
+
+\begin{quotation}
+  \textbf{Problem 1.} Consider a collection the closed,
+  disjoint granules $U_i$ with smooth boundary,
+with no-slip, rigid body motion boundary conditions.
+Assume a either a single or double well potential
+and a smooth phase field boundary condition.  
+Study the well-posedness of the coupled system
+\eqref{eq:RBT}--\eqref{eqn:stressbalance}
+for short times.  For global in time solutions, determine
+whether lubrication forces ensure positive distance
+between granules.  Describe the behaviour in the limit
+zero screening length limit.  
+\end{quotation}
+
+This problem is attractive because combines the diffusive interface
+effects involving a free boundary in aqueous part of the region \cite{}
+with interfacial effects coming from the long range inter-granual
+attraction. Generalizations of Problem 1 include modifying the 
+system to account for various time scales.
+We may consider, for example, modifying \eqref{eqn:phase}
+to include transport of the phase field by the background fluid;
+\begin{equation*}
+\phi_t + \uu \cdot \nabla = -\lambda \frac{\delta E}{\delta \phi} = \lambda(\epsilon^2 \Delta \phi - W'(\phi))
+\end{equation*}
+The modified systems enjoys the same energy law as \eqref{eq:energy_law} 
+except that there will be an addtional dissipation term coming from the
+Euler-Lagrange derivative $\frac{\delta E}{\delta \phi}$.
+
+The second problem we consider concerns the approximation
+of equilibrium elastic energy of curves and surfaces.
+We have compared two-dimensional configurations of amphiphilic granules
+to membrane configurations found in continuum mechanics.
+The simulations results in~\cite{Fu2018_SIAM,FuQuRyYo22}
+showed that the granular bilayers 
+basically replicated the elastic energies for bending, tilt, and
+stretching
+but we do not yet have any analytical evidence to support this conclusion.
+To understand the approximation mathematically, we take the following:
+\begin{quotation}
+  \textbf{Problem 2.} Place a collection of
+  amphiphilic granules
+with equally spaced centers along a curve $\mathcal{C}$.
+For simplicity, assume that the directors are normal to the curve
+and that the granules are all disks with radius proportional to $\epsilon$. 
+Study the sharp interface limit of the energy $E$ 
+relative to that of an array of granules placed along a flat curve. 
+In this limit, the number of granules $N_b$ goes to infinity
+to ensure equal spacing.
+Study how the bending the bending $k_B$ and stretching $k_A$ coefficients
+depend on the granual size relative to their spacing.
+Generalize the problem to account for aspect ratio of elliptical granules
+and nonzero tilt. 
+\end{quotation}
+Given the relatively complicated geometry consising
+of a plane with a number of disjoint disks removed, 
+we can start by approaching the problem in a simplified
+setting such as when the reference curve is a circle.
+There is a large body work in this direction for nematics
+studying either the case of a single coloidal particle and
+the qualitative structure of defects around it
+\cite{Alama2015MinimizersOT, Alama2021SaturnRD, PhysRevE.96.042702}
+many particles and the homogenization effects
+\cite{Canevari2019DesignOE,doi:10.1137/18M1163919,doi:10.1137/18M1163919,BERLYAND200597,doi:10.1137/130910348}.
+A closely related area that consider similar analysis
+dimension reduction for
+Landau-de Gennes models on curved nematic confined to thin films
+\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,doi:10.1142/S0218202516500470, FoFrLe07}.
+
 %\setcounter{page}{1}

### 2022-11-10 NSF2022/Description/backgroundv2.tex
cleaning up BG

@@
 \noindent
-{\bf Collaborative Research:
-Collaborative research: Self-organization modeled by moving domain
+{\bf Collaborative research: Self-organization modeled by moving domain
 elliptic PDEs} \\
@@
 length $\epsilon$.
-The scalar function $W(\phi)$ is a well potential where the local 
-minimima representing low energy states of the water phase.
+The scalar function $W(\phi)$ is a nonnegative
+well potential where the local 
+minimima represent metastable states $\phi_0,$ $\phi_1$ etc. of the water phase.
+To have finite bulk energy, the minimum potential phase
+$\phi_0$ has $W(\phi_0) = 0.$
 Mathematically, this order parameter is responsible for
@@
 
-The system~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
+In the absence of external flow,
+the system~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
 has the energy law
@@
 
+In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$
+and for the background flow, we require that
+$\lim_{\xx \to \infty} \uu(\xx) - \uu_{\infty}(\xx) = \mathbf{0}.$ 
+In the case of shear background flow, for example,
+\begin{equation}
+\label{eqn:shear_BG_flow}
+\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
+\end{equation}
+where $\dot \gamma$ is the shear rate and
+$\mathbf{e}_x$, $\mathbf{e}_y$ are horizontal and vertical
+basis vectors, respectively.  Other background flows include
+extensional, parabolic Poiseuille, and Taylor-Green flow.
+For numerical stability and physical realism,
+we introduce pairwise repulsive forces and torques in \eqref{eqn:stressbalance}
+to prevent the collosion between neighboring granules.
+We include the repulsive potential in the energy law \eqref{eq:energy_law} 
+and refer to \cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM} for details.
+A background flow adds elastic energy to the granule configurations
+and is quantified by simulation.
+
 In terms of physical justification, the
@@
 free energy density for a single-well potential.
-The double-well potential case was derived by
+The double-well potential case was dealt with by
 Gompper in \cite{GoHaKo94} to describe metastable coordination of water.
@@
 
-Finally, we mention that in the single-well case
+Finally, in terms of mathematical justifications, we mention
+that in the single-well case
 $W(\phi) = \tfrac{1}{2}\phi^2,$ \eqref{eqn:phase} takes the form
@@
 We are confident that \eqref{eq:RBT}--\eqref{eqn:stressbalance}
-is a correct description of long-range surface interactions.
+is a correct description of long-range interactions between granule
+surfaces.
 
-The model has a broad range of applicability to self-organization
-phenomena in chemistry and biological physics. For one,
+\begin{wrapfigure}[23]{r}{3.2in}
+  \vspace{-15pt}
+  \begin{center}
+    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
+    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
+    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
+     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
+    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
+    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
+      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
+      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
+      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
+      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
+  \end{tabular}
+  \end{center}
+  \vspace{-5pt}
+  \caption{\footnotesize \label{fig:self-assembly2} Rows (a)-(c) have
+  the same initial configuration but different boundary conditions $g$.
+  In row (a), self-assembly with an amphiphilic boundary condition
+  results in a bilayer pattern shielding the hydrophobic core (yellow,
+  $u > 0$) from the aqueous phase (blue, $u = 0$). Row (b) shows
+  particles with a hydrophobic intensity that is greater on one side of
+  the particle (magenta) than the other (yellow). In row (c), green is
+  for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$. Particles
+  orient like sides to form a checkerboard pattern.}
+\end{wrapfigure}
+\subsection{Applications}
+Since the formulation is scale independent,
+it can be applied broad range of
+nonspecific self-organization
+phenomena in surface chemistry, biology and engineering.
+For one,
 the formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures
@@
 equilibrium morphologies (Figure~\ref{fig:self-assembly2}).
+(i)
+Chemistry: Janus spheres
 Since the formulation is
@@
 lipids, at the nanoscopic scale. For larger scales, the representation
-is literal and the granules Janus spheres. The proposal deals with the
-physical origins in section ().
-\todo[inline]{
-List applications; don't forget Bertozzi.}
+is literal and the granules Janus spheres.
+(ii) Pickering emulsion 
+(iii) Bertozzi's problem
+(iv) Tension driven microprinting
+(v) Vesicle hydrodynamics.
+
+\subsection{Vesicles as self-organized granules}
+\label{sec:vesicles_as_granules}
+Interface problems coming from biology are a challenging
+area of applied mathematics.  Broadly speaking, these problems
+involve a fluid structure interaction where the modeler must
+solve for the velocity in the aqueous phase, track the interface,
+and couple the velocity boundary condition to the interface through
+stress balance boundary conditions.  The aqueous phase can
+be a low Reynolds-number fluid, a porous medium, or viscoelastic fluid,
+and the interfacial forces can come from surface tension, elasticity,
+or electrostatics.
+Incorporating all these details can lead to models with substantial
+complexity and there is a need for robust, general models that
+cut across these issues.
+
+This section shows the principles of PDE-driven
+self-organization apply to the concrete
+problem of \emph{vesicle hydrodynamics}.
+A vesicle is a small, fluid filled membrane sack.
+Microscopically, the membrane of a vesicle is comprised
+elongated amphiphilic lipids that form inner and outer monolayers.  
+The goal in vesicle hydrodynamics is to study the flow patterns e.g.,
+tank-treading, tumbling, that arrise due to the interaction
+between membrane elasticity and surrounding fluid.
+Traditional models represent a vesicle as a
+continuous surface or curve $\Sigma$.
+The elastic energy takes the form
+\begin{equation}
+\label{eq:Canham-Helfrich}
+  \int_{\Sigma} k_B(H - k_0)^2\, dS 
+\end{equation}
+where $H$ is the mean curvature, $k_0$ is a spontaneous curvature,
+and $k_B$ is a bending modulus. 
+The variation of \eqref{eq:Canham-Helfrich} gives rise to a surface force
+that pointwise balances the jump in hydrodynamic stress across the interace.
+A vesicle is closed surface, and so while energy does involve
+the Gaussian curvature, it does not enter \eqref{eq:Canham-Helfrich}
+since Gauss-Bonnet Theorem guarantees that
+the integral of Gaussian curvature is independent of the shape of $\Sigma$.
+
+Depending on the situation,
+one can further enforce constant volume constraints or permeability relationships.
+If the interface is area incompressible, then the surface divergence
+of velocity is zero.  On the other hand, if the surface is area compressible,
+then \eqref{eq:Canham-Helfrich} contains an additional stretching term of the
+form $k_A(\alpha - \alpha_0)^2/\alpha_0$ where $\alpha$ and $\alpha_0$ are the
+deformed and equilibrium area densitities respectively.
+
+\begin{wrapfigure}[12]{r}{0.5\textwidth}
+  \vspace{-5pt}
+\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
+  \vspace{-5pt}
+\caption{\label{fig:amphiphilic_assembly}
+Self-organization under amphiphilic boundary condition.
+(a) Granules first match hydrophobic tails (red),
+(b) then align length-wise.
+The principle of self-organization holds in three dimensions 
+as simulated by Kohl, Corona, and Veerapaneni
+\cite{koh-cor-che-vee2021}.}
+\end{wrapfigure}
+There are downsides to traditional models in terms of generality and physical realism.
+(i) Motivated by drug delivery applications, experimenters use electric
+fields, for example, to controllably open and close pores in membranes
+\cite{}.
+These kinds of topological changes are clumsy to incorporate into 
+sharp interface formulations that assume a continuous surface \cite{}.
+(ii) Sharp-interface models assume a membrane of neglible thickness. 
+However, in biological processes
+like fusion, fission, or insertion and penetration by proteins and peptides, 
+the length scales of the
+deformation (tens of nanometers) are comparable to membrane thickness (about 5 nm).
+Moreover, these processes crucially rely on variable lipid
+orientation relative to the surface normal (the so-called \emph{tilt}
+deformation),
+whereas \eqref{eq:Canham-Helfrich} implicitly assumes that the lipids
+are everywhere normal to the surface.  
+(iii) Finally, realistic membranes are comprised of a mixtures of lipids and proteins.
+Recent work \cite{} has incorporated lipid mixtures in \eqref{eq:Canham-Helfrich},
+but these models are formidably complicated 
+due to the additional constraints and transport equations involved.
+
+Diffusive interface models and surface-director models partially make up for some of
+these shortcomings. 
+Topological changes are permitted in phase field and level set formulations,
+but these methods smear out the details of lipid orientations.
+The question lipid orientations is closely related to the vast and well-studied
+field of nematic liquid crystals.  Here there has been recent development
+in the simulation and theory of nematic liquid crystals on surfaces.
+These models consider the interplay between defects and surface geometry \cite{},
+finite element formulations \cite{}, and existence of minimizers \cite{}.
+
+\subsubsection{Main modeling innovations}
+We developed the model \eqref{eq:RBT}-\eqref{eqn:hydro_stress} 
+as a robust and flexible approach
+that cuts across many of the aforementioned challenging aspects to vesicle modeling.
+(i) The granules are not fixed to a stencil, 
+affording flexibility in terms of vesicle morphology and topology--sufficiently
+large forces will pull the granules apart as physically required.
+(ii) The model formulation is built around important details like lipid orientations,
+and exhibits and inter-monolayer slip not present in diffusive interface models.
+(iii) It is straightforward to consider mixtures of granules with different
+types of shapes and boundary conditions of the granules.
+With the help of boundary integral equations
+and fast summation methods, the dynamics can be solved in 
+near-linear complexity in $N_b$, which is equal to or better than 
+the computational complexity of related sharp interface methods.
+
+Inspired
+by the amphiphilic structure of lipids,
+we formulated a so-called ``amphiphilic'' boundary condition
+that leads a collection of granules to form bilayers.
+Referring to Figure \ref{fig:amphiphilic_assembly}, 
+\begin{equation}
+\label{eq:amphiphilic_BC}
+\phi(\mathbf{x}) = h_i(\mathbf{x}) = \tfrac{1}{2}\left(\dd_i \cdot (\xx - \aa_i)/c_i + 1\right), \quad
+\mathbf{x} \in \Gamma_i,
+\end{equation}
+where $\dd_i$ is the director, $\aa_i$ is the center, and $c_i$ the
+``radius'' of the $i$th granule.  
+The phase $\phi$ takes values close to $1$ on in the direction $\dd_i$,
+representing a hydrophobic tail, and values close to $0$ 
+in the direction $\dd_i$ representing the hydrophilic head.
 
@@
 \begin{center}
-    \begin{tabular}{m{0.1cm}m{1.8in}m{1.8in}m{1.8in}}            
-      (a)
-    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B1.jpg}
-    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B2.jpg}
-     &\includegraphics[width=1.8in]{figures/SpecificAim1/N100B3.jpg}    \\
-     (b)
-    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C1.jpg}
-    &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C2.jpg}
-      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100C3.jpg}    \\
-    (c)
-      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A1.jpg}
-      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A2.jpg}
-      &\includegraphics[width=1.8in]{figures/SpecificAim1/N100A3.jpg}    \\
-      &\multicolumn{1}{c}{$t = 0$}
-      &\multicolumn{1}{c}{intermediate time}
-      &\multicolumn{1}{c}{long time}
-  \end{tabular}
+\includegraphics[width=0.9\textwidth]{figures/Background/coarsening.pdf}
 \end{center}
 \vspace{-20pt}
-  \caption{\footnotesize \label{fig:self-assembly2} Rows (a)-(c) have
-  the same initial configuration but different boundary conditions $g$.
-  In row (a), self-assembly with an amphiphilic boundary condition
-  results in a bilayer pattern shielding the hydrophobic core (yellow,
-  $u > 0$) from the aqueous phase (blue, $u = 0$). Row (b) shows
-  particles with a hydrophobic intensity that is greater on one side of
-  the particle (magenta) than the other (yellow). In row (c), green is
-  for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$. Particles
-  orient like sides to form a checkerboard pattern.}
+\caption{\label{fig:coarsening}
+Modeling procedure.
+We initilize a suspension of granules.
+Under the moving domain problem
+\eqref{eq:RBT}-\eqref{eqn:hydro_stress}
+with amphiphilic boundary condition, the granules
+self-organize into vesicle bilayers.
+We then introduce external hydrodynamic effects to study elastic properties.
+}
+\vspace{5pt}
 \end{figure}
+\subsubsection{How do granule-based vesicles have an elastic energy?}
+A natural question to ask is how 
+elastic energy enters a formulation
+coming from surface interactions like \eqref{eqn:math_motivation}.
+Conceptually, random suspensions of amphiphilic
+granules undergo a rapid coarsening to form bilayers.
+For small granule numbers, the bilayers form a single stable, ring-shaped vesicle
+with energy $E_{\text{stable}}$ (Figure \ref{fig:coarsening}, (c)).
+This vesicle configuration, however, is only a local minimizer,
+whereas the planar configuration (Figure \ref{fig:coarsening}, (e))
+is the global minimizer.  The difference between
+$E(t)$ and $E_{\min}$ is the elastic energy stored by granules.
+Indeed, if a background flow overcomes the energy barrier to force granules apart,
+then bilayer unfolds from its circular shape into a flat shape.
 
-\begin{figure}[t!]
-\begin{center}
-\includegraphics[width=\textwidth]{figures/Background/coarsening.pdf}
-\end{center}
-\caption{\label{fig:coarsening}}
-\end{figure}
+When many granules are involved, the granules reach an intermediate
+state consisting of several bilayer segments (see Figure \ref{fig:self-assembly2}, top right).
+Placing this metastable state into a mild background flow
+causes the segments to join up into isolated vesicles \cite{fu-ryh-qua-you2022}.
+
+and we analyze its energy as follows:
+\begin{enumerate}
+\item[Bending]
+  The vesicle has bending energy because the directors are not
+  parallel.  In the outer layer, the directors have negative
+  splay $\nabla \cdot \dd < 0$ and in the inner layer
+  the directors have positive splay $\nabla \cdot \dd > 0$.
+  Due to minimality, the energy depends locally quadratically
+  on the splay and has a bending modulus $k_B$.
+  When $\dd$ is everywhere parallel to the unit normal $\NN,$ then
+  \[
+  \nabla \dd = -2H
+  \]
+  where $H$ is the mean curvature. 
+\item[Stretch]
+  If the vesicle is stretched, then the distance between
+  neighboring granules is increased from rest.  The energy
+  for this increase is Hookean and for small deformations
+  equals
+  \begin{equation}
+    \label{eq:stretch}
+    \tfrac{1}{2}k_A(L - L_0)^2/L_0
+  \end{equation}
+  where $k_A$ is a stretching modulus, $L$ and $L_0$ are stretched
+  vesicle length and length at rest, respectively
+  ($\tfrac{1}{2}k_A(A - A_0)^2/A_0$ in three dimensions).
+  If the stretching is too great, the vesicle ruptures
+  and the free eneds either rejoin, repairing the vesicle,
+  of move apart forming a flat bilayer.
+\item[Tilt]
+  The directors in Figure \ref{} are normal to the vesicle surface.
+  However, there are situations where the directors are not normal
+  to the surface and this introduces the tilt angle $\theta$
+  given by $\cos \theta = \dd \cdot \NN$.
+  The energy for tilt is also Hooken and behaves like
+  $k_{\theta}|\dd \times \NN|^2$ for the tilt modulus $k_{\theta}$.
+\end{enumerate}
+
+\begin{wrapfigure}[11]{r}{0.5\textwidth}
+\includegraphics[width=0.5\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
+\caption{\label{fig:JPv_linearshear}The JP vesicles undergo tank-treading in background shear flow.}
+\end{wrapfigure}
+
+\begin{wrapfigure}[14]{l}{0.475\textwidth}
+%\vspace{-10pt}
+\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
+\caption{\label{fig:JPv_rupture}The JP vesicles rupture under large shear rates.}
+\end{wrapfigure}
+
+This is our first step to showing the energy of the granule-based
+vesicles have the same elastic energy as bilayers in the limit $N_b \to \infty$.
+Once we have simulations for large systems sizes, we can provide
+evidence that the two formulations are the same.
+So and so has made simulations with thousands of granules in three-D
+and this is now a technical/not theoretical limitation.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Outline of the proposal}
+The outline of the proposal goes as follows.
+Section \ref{sec:resume} describes the
+PIs's expertise and prior works
+in (1) membrane-fluid mechanics (2) boundary integral equations
+and (3) complex fluid dynamics
+that are critical to the success of this proposal. 
+Section \ref{sec:proposed-work}
+goes over the three specific aims of the proposal.

### 2022-11-10 NSF2022/Description/specificaim1v2.tex
cleaning up BG

@@
-%\documentclass[11pt]{article}
-%
-%%\usepackage[margin=1.01in]{geometry}
-%%\usepackage{mathpazo}
-%\usepackage[utf8]{inputenc}
-%\usepackage{NSFProposal}
-%
-%%\addtolength{\oddsidemargin}{-0.6in}
-%%\addtolength{\evensidemargin}{-0.75in}
-%%\addtolength{\textwidth}{1.2in}
-%%\addtolength{\topmargin}{-0.75in}
-%%\addtolength{\textheight}{1.4in}
-%%
-%%\usepackage[margin=1.02in]{geometry}
-%%\def\baselinestretch{1}
-%%\special{papersize=8.5in,11in}
-%
-%%\usepackage[left=1.1in, right=1.1in]{geometry}
-%
-%%
-%\usepackage{url}
-%\usepackage{amsfonts,amsmath,amssymb,amsbsy}
-%\usepackage{latexsym}
-%
-%\usepackage{bm}
-%\usepackage{comment}
-%%\usepackage{upgreek}
-%\usepackage{graphics,graphicx}
-%\usepackage{psfrag}
-%\usepackage{epsfig}
-%\usepackage{wrapfig}
-%\usepackage{mathrsfs}
-%
-%\usepackage{pgfgantt}
-%\usepackage{subfigure}
-%
-%\usepackage[square,numbers,comma,sort&compress]{natbib}
-%%\usepackage{hyperref}
-%
-%\usepackage{commath}
-%\usepackage{array}
-%%\newcommand{\todo}[1]{%
-%%  {\bfseries\color{red} XXX TODO: #1}
-%%}
-%\usepackage[font=small,labelfont=bf,labelsep=period]{caption}
-%%\usepackage[margin=30pt,font=small,labelfont=bf,
-%%  labelsep=period,skip=10pt]{caption}
-%
-%\usepackage{todonotes}
-%\usepackage{pgfplots,tikz,color,soul,array,enumitem}
-%
-%
-%\newcounter{midequation}
-%
-%\newtheorem{definition}{Definition}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{example}{Example}
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{proposition}{Proposition}
-%\newtheorem{remark}{Remark}
-%
-%
-%
-%\newcommand{\diff}{\mathrm{d}}
-%\newcommand{\intd}{\,\mathrm{d}}
-%\newcommand{\kBT}{$\mathrm{k}_{\mathrm{B}}\mathrm{T}$}
-%\newcommand{\KB}{k_{\mathrm{B}}}
-%\newcommand{\KG}{k_{\mathrm{G}}}
-%\newcommand{\KT}{k_{\mathrm{T}}}
-%\newcommand{\KTH}{k_{\theta}}
-%\newcommand{\KA}{k_{\mathrm{A}}}
-%\newcommand{\eg}{{\it e.g.~}}
-%\newcommand{\ie}{{\it i.e.~}}
-%\DeclareMathOperator{\Div}{div}
-%\DeclareMathOperator{\Curl}{curl}
-%
-%% Bryan's Marcros
-%\renewcommand{\aa}{\mathbf{a}}
-%\newcommand{\bd}{\partial}
-%\newcommand{\dd}{\mathbf{d}}
-%\newcommand{\DD}{\mathcal{D}}
-%\newcommand{\eeta}{\boldsymbol{\eta}}
-%\newcommand{\FF}{\mathbf{F}}
-%\renewcommand{\gg}{\mathbf{g}}
-%\newcommand{\GG}{\mathbf{G}}
-%\newcommand{\JJ}{\mathbf{J}}
-%\newcommand{\nn}{\mathbf{n}}
-%\newcommand{\NN}{\mathbf{N}}
-%\newcommand{\nnu}{\boldsymbol{\nu}}
-%\newcommand{\ttau}{\boldsymbol{\tau}}
-%\newcommand{\ssigma}{\boldsymbol{\sigma}}
-%\newcommand{\rr}{\mathbf{r}}
-%\newcommand{\RR}{\mathbb{R}}
-%\renewcommand{\SS}{\mathbf{S}}
-%\newcommand{\TT}{\mathbf{T}}
-%\newcommand{\xx}{\mathbf{x}}
-%\newcommand{\XX}{\mathbf{X}}
-%\newcommand{\uu}{\mathbf{u}}
-%\newcommand{\vv}{\mathbf{v}}
-%\newcommand{\yy}{\mathbf{y}}
-%\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
-%\newcommand{\jump}[1]{[\![ #1 ]\!]}
-%
-%\begin{document}
-%
-%
-%\newpage
-%\pagenumbering{arabic}
-%%\input{summary}
-%\pagestyle{empty}
+\section{Proposed Research}
+\label{sec:proposed-work}
 
-\section{Specific Aim 1: Membrane vesicles as self-organized granules}
+\subsection{Specific Aim 1: Membrane vesicles as self-organized granules}
 \label{sec:specific_aim1}
-\subsection{Prior work related to the proposal.}
 
-\subsubsection{Vesicles}
-\begin{wrapfigure}[12]{r}{0.3\textwidth}
-  \vspace{-5pt}
-\centerline{\includegraphics[width=0.3\textwidth]{figures/SA1Figures/LiposomePore.pdf}}
-  \vspace{-5pt}
-\caption{\label{fig:LiposomePore}Pore formation in a
-stressed liposome~\cite{Kaetal03, BrdGSa00}.}
-\end{wrapfigure}
-PI Ryham has made fundamental contributions to interface modeling in
-membrane biology.  His first works include
-phase field formulations for the elastic bending energy \cite{0951-7715-18-3-016,Du05}
-and 
-topological indicators \cite{DuEuler} of vesicle membranes
-and fluid-vesicle interactions \cite{QiangDu09}.
-A decade ago, Ryham focused on the
-problem of \emph{lipidic pore dynamics}.  
-This problem came from 
-experiments in the late 1990's 
-showing that liposomes swollen by osmotic stress can form a single pore that
-widens to allow the release of fluid (see Figure \ref{fig:LiposomePore}). 
-Once pressure is released,
-the widened pore closes according to a linear
-followed by a square root law \cite{BrdGSa00}.  Researchers have
-used the rates of pore closure to infer properties of the lipid membrane \cite{PoDi10}.
-
-In \cite{BrdGSa00}, 
-physicists Olivier Sandre and Fran\c{c}oise Brochard-Wyart
-and Nobel laureate Pierre-Gilles de Gennes
-(PGG) formulated
-rate equations for lipid pore dynamics.  These equations couple
-the liposome stretching tension, pore edge tension, and membrane
-dissipation.  A coefficient $C$ accounting for dissipation due to water
-movement, however, was left unspecified because the Stokes flow
-problem for the fluid surrounding a spherical cap with a moving hole
-was unknown at the time \cite{Ra73}.  PI Ryham approached this problem using
-a two-phase field method model \cite{RyCoEi12} and in a much-cited work
-(coauthored with an undergraduate math major) by
-fitting a dissipation coefficient $C \approx 8$ to data.
-data \cite{RYHAM20112929}.  Finally, in the sole-author 
-JFM paper \cite{Ryham2017OnTV},
-Ryham solved the Stokes flow problem for
-a moving pore completely yielding a value 
-$C = \frac{4}{\pi}\csc \alpha\cot^2\frac{\alpha}{2}(\alpha - \sin \alpha + \alpha^2 \tan \frac{\alpha}{2})
-~\sim 2\pi + 5(\alpha - \pi)$ in the pore angle $\alpha$.
-Olivier Sandre wrote about the publication of the PI’s JFM paper:
-
-\begin{quotation}“Maybe you can tell them this story: In my thesis
-paper with Brochard \& PGG we got a factor of 8 wrong in determining
-the viscosity of lipid membranes until a math teacher from the
-Bronx corrected the model prefactor!”  Sandre, Olivier @Olive\_Free.
-Twitter, January 3, 2018, https://twitter.com/Olive\_Free/status/948640705362169857
-\end{quotation}
-
-\begin{wrapfigure}[14]{l}{0.4\textwidth}
-  \vspace{-5pt}
-\centerline{\includegraphics[width=0.4\textwidth]{figures/SA1Figures/FusionMicroscopy.pdf}}
-  \vspace{-5pt}
-\caption{\label{fig:FusionMicroscopy}
-Fusion of an influenza virus-like particle with a liposome resolved
-by electron tomography
-~\cite{Chetal16}.}
-\end{wrapfigure}
-
-\noindent\textbf{Membrane Fusion.} Ryham has contributed
-physically relevant, state-of-the-art methods in the
-area of \emph{membrane fusion} (see Figure \ref{fig:FusionMicroscopy}).
-Membranes fuse as a part of many biological
-processes such as synaptic transmission, intracellular trafficking,
-fertilization, and viral infection, and  a major challenge
-to determine the forces needed to merge two lipid bilayers
-~\cite{chernomordik2008mechanics, kozlov1982possible, Kuzmin19062001, markin2002membrane, qian2012novel}.  
-Studying fusion is such a difficult problem because bilayers
-consist of two monolayer surfaces coupled by a pair of surface vector fields
-that model the elongated lipids.
-
-In his much noticed Biophysical Journal
-and Nature papers~\cite{RyKlYaCo16,Chetal16}, Ryham and collaborators 
-calculated, for the first time, a least energy path for membrane fusion.  
-One mathematical innovation of this paper was to combine
-the underlying surface-director model  with the simplified string method 
-introduced by Weinan E, Weiqing Ren, and Eric Vanden-Eijnden
-~\cite{doi:10.1063/1.2720838}
-to calculate the saddle point separating two energy basins. 
-The results~\cite{RyKlYaCo16} yielded energy barriers for stages of fusion
-consistent with predictions from prominent MD and experimental groups
-\cite{SmRiMu19,2017PNAS..114.1238F}.
-The PI's papers ~\cite{RyWaCo13} and ~\cite{RyKlYaCo16} 
-were also coauthored with undergraduate
-mathematics majors.
-
-\begin{wrapfigure}[10]{r}{0.4\textwidth}
-  \vspace{-5pt}
-\centerline{\includegraphics[width=0.4\textwidth]{figures/SA1Figures/Hemifusion.pdf}}
-  \vspace{-5pt}
-\caption{\label{fig:Hemifusion}
-Axisymmetric hemifusion stage of two planar bilayers~\cite{RyKlYaCo16}.
-Bilayer energy depends not only on surface curvature, but lipid orientations as well.}
-\end{wrapfigure}
-Phase field methods have been used to
-study fusion in two dimensions~\cite{C9SM01983A} (MORE REFS), 
-but these models do not resolve lipid orientations that play a crucial
-role in processes like fusion.
-
-\subsection{Vesicles as self-organized granules}
-Interface problems coming from biology are a challenging
-area of applied mathematics.  Broadly speaking, these problems
-involve a fluid structure interaction where the modeler must
-solve for the velocity in the aqueous phase, track the interface,
-and couple the velocity boundary condition to the interface through
-stress balance boundary conditions.  The aqueous phase can
-be a low Reynolds number fluid, a porous medium, or viscoelastic fluid,
-and the interfacial forces can come from surface tension, elasticity,
-or electrostatics.
-One typically enforces constant volume constraints through a no-slip
-boundary condition for the velocity; if the interface is area incompressible
-then one can additionally require that the velocity surface divergence
-be zero.  Incorporating all these details can lead to models with substantial
-complexity.
-
-\subsubsection{Mathematical innovations.}
-We developed the model \eqref{eqn:stokes}-\eqref{eqn:hydro_stress} 
-as a robust and flexible approach
-that cuts across many of the aforementioned challenging aspects to vesicle modeling.
-\begin{enumerate}
-\item The granules are not fixed to a stencil which
-affords greater flexibility in terms of vesicle morphology 
-and topological changes--sufficiently large forces will pull the granules apart 
-as physically required,
-\item An elliptic PDE \eqref{eqn:phase} provides the attraction that binds granules together,
-opening the possibility for mathematical analysis, 
-\item The model includes important details like lipid orientations and inter-monolayer
-slip not present in diffusive interface models, and
-\item With the help of boundary integral equations
-and fast summation methods, the dynamics can be solved in 
-near-linear complexity in $N_b$, which is equal to or better than 
-that of related sharp interface methods. 
-\end{enumerate}
-The main insight that leads a collection of granules to form bilayers
-is to define a so-called ``amphiphilic'' boundary condition for \eqref{}
-It takes the form:
-\begin{equation}
-\label{eq:amphiphilic_BC}
-h_i(\mathbf{x}) = \tfrac{1}{2}\left(\dd_i \cdot (\xx - \aa_i)/c_i + 1\right)
-\end{equation}
-where $\dd_i$ is the director, $\aa_i$ is the center, and $c_i$ the
-``radius'' of the $i$th granule.  Inspired
-by the amphiphilic structure of lipids, 
-\eqref{eq:amphiphilic_BC} 
-takes values close to $1$ on in the direction $\dd_i$,
-representing a hydrophobic tail, and values close to $0$ 
-in the direction $\dd_i$ representing the hydrophilic head.
-%\begin{figure}
-%Wrapped figure: a picture of a lipid and the granule geometry.
-%\end{figure}
-
-\begin{wrapfigure}[13]{r}{0.5\textwidth}
-  \vspace{-5pt}
-\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
-  \vspace{-5pt}
-\caption{\label{fig:amphiphilic_assembly}
-Self-organization under amphiphilic boundary condition \eqref{eq:amphiphilic_BC}.
-Granules first match hydrophobic tails (red) (a), then align length-wise (b). 
-The behavior is the same in three dimensions 
-as simulated by Kohl, Corona, and Veerapaneni
-\cite{koh-cor-che-vee2021}.}
-\end{wrapfigure}
-The basic self-organization proceeds in two steps.
-(a) Supensions of granules first minimize energy by matching hydrophobic
-hydrophobic tails with one or more apposing granules
-(Figure \ref{fig:amphiphilic_assembly}a, red regions.)
-Once matched, there is still some residual energy in the
-exposed sides.  In the minimimal configuration, pairs of
-granules line up side by side, forming a bilayer,
-and sequestering the hydrophobic
-phase to the smallest possible region
-(Figure \ref{fig:amphiphilic_assembly}b).
-For numerical stability and physical realism,
-we include a repulsion to prevent the granules from colliding.
-
-\subsubsection{Do granule-based vesicle behave like continuum vesicles?}
-A vesicle is a ring-shaped (or sphere-shaped in $\mathbb{R}^3$) 
-and we analyze its energy as follows:
-\begin{enumerate}
-\item[Bending]
-  The vesicle has bending energy because the directors are not
-  parallel.  In the outer layer, the directors have negative
-  splay $\nabla \cdot \dd < 0$ and in the inner layer
-  the directors have positive splay $\nabla \cdot \dd > 0$.
-  Due to minimality, the energy depends locally quadratically
-  on the splay and has a bending modulus $k_B$.
-  When $\dd$ is everywhere parallel to the unit normal $\NN,$ then
-  \[
-  \nabla \dd = -2H
-  \]
-  where $H$ is the mean curvature. 
-\item[Stretch]
-  If the vesicle is stretched, then the distance between
-  neighboring granules is increased from rest.  The energy
-  for this increase is Hookean and for small deformations
-  equals
-  \begin{equation}
-    \label{eq:stretch}
-    \tfrac{1}{2}k_A(L - L_0)^2/L_0
-  \end{equation}
-  where $k_A$ is a stretching modulus, $L$ and $L_0$ are stretched
-  vesicle length and length at rest, respectively
-  ($\tfrac{1}{2}k_A(A - A_0)^2/A_0$ in three dimensions).
-  If the stretching is too great, the vesicle ruptures
-  and the free eneds either rejoin, repairing the vesicle,
-  of move apart forming a flat bilayer.
-\item[Tilt]
-  The directors in Figure \ref{} are normal to the vesicle surface.
-  However, there are situations where the directors are not normal
-  to the surface and this introduces the tilt angle $\theta$
-  given by $\cos \theta = \dd \cdot \NN$.
-  The energy for tilt is also Hooken and behaves like
-  $k_{\theta}|\dd \times \NN|^2$ for the tilt modulus $k_{\theta}$.
-\end{enumerate}
-
-With regard to vesicle membranes and bilayers, two prominent 
-classes of models researchers consider are the
-Canham-Helfrich model and the more general Helfrich model.
-In the Canham-Helfrich model, the membrane is assumed to have
-negligible thickness and the lipids that form the membrane bilayer
-are normal to the interface $\Sigma$.  The elastic energy takes the form
-\begin{equation}
-\label{eq:Canham-Helfrich}
-  \int_{\Sigma} k_B(H - k_0)^2 + k_{\theta} \sigma\, dS 
-\end{equation}
-where $H$ is the mean curvature, $k_0$ is a spontaneous curvature,
-$G$ is the Gaussian curvature, and $k_B$, $k_G$, $\sigma$, and $\gamma$ are
-moduli for bending, saddle splay, surface tension, and line tension, respectively. 
-If $\Sigma$ is a closed surface, then the integral
-of Gaussian curvature is constant due to the Gauss-Bonnet Theorem.
-
-This is our first step to showing the energy of the granule-based
-vesicles have the same elastic energy as bilayers in the limit $N_b \to \infty$.
-Once we have simulations for large systems sizes, we can provide
-evidence that the two formulations are the same.
-So and so has made simulations with thousands of granules in three-D
-and this is now a technical/not theoretical limitation.
-
-\subsubsection{Do granule-based vesicles share hydrodynamic behavior of continuum vesicles?}
-
-\begin{figure}R
-  eview bend/stretch/tilt experiments
-\end{figure}
-\subsection{Vesicles in background flows}
-\begin{itemize}
-\item pull from JFM paper
-\item we will consider background flows ...
-\item results, rupture, critical shear rate
-\item extensional flows
-\item Taylor green flows; reorganization; do not know critical flow rate yet
-\end{itemize}
-
-\begin{remark}
-  Mathematical problems: well-posedness of the system;
-  Extensions to problems with transport;
-  Calc-variational problem; place granules on fixed curve; study PDE system in
-  SL -> 0; radius -> 0; Nb -> infty limit
-\end{remark}
-\begin{remark}
-  In biophysics, tilt is defined by the tilt vector
-  $\TT = \dd/\dd\cdot \NN - \NN$ so that the tilt energy density
-  behaves like $\tan^2 \theta$ rather than $\sin^2 \theta$.
-  These two energies densities are, however, asymptotically equal
-  for small deformations.
-Hamm and Kozlov [] and later Terzi and Deserno [], Pinigen et al. []
-showed that the full Helfrich elastic energy of a \emph{monolayer} takes the form
-\begin{equation}
-\label{eq:Helfrich}
-  \begin{aligned}
- &\int_{\Sigma}
-  %\label{eq:Pinigan}
-\tfrac{1}{2}k_{b}[(\nabla \cdot \mathbf{d} + k_{0})^{2} -  k^{2}_{0}]  
-+ \tfrac{1}{2}k_{\theta}\mathbf{T}^{2} + \tfrac{1}{2}k_a[(\alpha - \alpha_0)^2 - \alpha_0^2] \\
-&+ k_{c}\textbf{T} \cdot \nabla \nabla \cdot \mathbf{d}  + \tfrac{1}{2}k_{g}(\nabla \nabla \cdot \mathbf{d})^{2}
- + A\alpha \nabla \cdot \mathbf{d}
-+ B \mathbf{T} \cdot \nabla \alpha \\
-&- \tfrac{1}{2}k_c |\nabla \alpha|^2 + C \nabla \alpha \cdot \nabla \nabla \cdot \mathbf{d}\,dS
-\end{aligned}
-\end{equation}
-where $\nabla$ and $\nabla \cdot$ are the surface gradient and surface divergence,
-respectively, and $k_B$, $k_{\theta}$, $k_a$, $k_c$, $k_g$, $A$, $B$, $C$ are
-appropriate elastic moduli.  An important and consequential distinction between
-\eqref{eq:Canham-Helfrich} is the presence of the terms $\mathbf{T}$ and $\alpha$.
-These are, respectively, the \emph{tilt} vector $\mathbf{T}$ measuring
-the difference between the lipid director $\mathbf{d}$ and the surface normal
-$\mathbf{N}$; the \emph{area per lipid} $\alpha$ area density at rest $\alpha_0$.
-The two models \eqref{eq:Canham-Helfrich} and \eqref{eq:Helfrich} agree
-when $\mathbf{T} = 0$ and $\alpha = \alpha_0$ everywhere.
-\end{remark}
-
-(Researchers Take from former background grant)
-
-In biological processes like fusion and fission, however, the length scales of the
-deformation (tens of nanometers) are comparable to membrane thickness (about 5 nm)
-and so the detailed structure of bilayer cannot be ignored.
-These models assign a surface $\Sigma$ to each of the two monolayers
-of a bilayer, and a director field $\mathbf{n}:\Sigma \to \mathbb{R}^3$
-for lipid orientation. Under very general continuum mechanical assumptions,
-
-(Surface-director models).
-
-The holy grail of biologically inspired fluid-interface models is
-to have a formulation sufficient detailed and robust to make predictions
-about biological processes.  Here, the Helfrich and Canham-Helfrich models
-used throughout the field unfortunately fall short. For one,
-realistic membranes are composed of a mixture of lipid species proteins.
-Secondly, the membranes of living cells are constantly changing topology,
-whether through fusion and fission with other membranes, or through
-insertion or penetration by proteins and peptides.  Topological
-changes are clumsy to incorporate into 
-sharp interface formulations of the Helfrich and Canham-Helfrich energies
-since computations rely on a parametrized surface of fixed topology.
-Topological changes are permitted in phase field and level set formulations
-of \eqref{eq:Canham-Helfrich}, but these methods smear out the 
-details of lipid orientations, for example, that are important to the
-process.  Recent work by [] and [] have incorporated lipid mixtures in \eqref{eq:Canham-Helfrich}
-(although not \eqref{eq:Helfrich}), but these models have formidable complexity
-due to the additional constraints and transport equations involved.
-
-Nematic liquid crystals on surfaces is a related are of study.  These models,
-which are closely related to \eqref{eq:Canham-Helfrich}, consider the energy
-of a nematic liquid crystal (or Q-tensor ?) on a surface to study how the
-surface geometry effects the director field and vice versa. Researchers
-have formulated finite element methods for [][] and studied the existence
-of minimizers []-[].  Liquid crystals are an extremely well-studied
-are in mathematics [], where there are still a lot of open problems.
-
-\begin{figure}
-True bilayer; vesicle zero thickness; phase field; surface director
-\end{figure}
-
-We introduces \eqref{}-\eqref{} to overcome the challenges faced by
+We introduced \eqref{eq:RBT}--\eqref{eqn:stressbalance} to overcome the challenges faced by
 traditional Helfrich-type models of elastic membranes.
-
-\noindent\textbf{Modeling vesicles} To make granular surfaces, we
-form a collection of amphiphilic granules.  The granules have a
-director $\mathbf{d} \in \mathbb{R}^n$ and the boundary condition
-$g$ takes the form
-\begin{equation}
-g(\mathbf{x}) = \frac{1}{2}(\mathbf{d}\cdot(\mathbf{x}-\mathbf{a})/c + 1)
-\end{equation}
-where $c$ is granule radius.
-This $g$ is smooth (real analytic even)
-and takes values close to $1$ on the pole in the direction $\mathbf{d}$,
-representing a hydrophobic face, and values close to $0$ on the pole
-in the direction $-\mathbf{d}$ representing the hydrophilic face.
-Then we define the well potential $f(\eta) = \tfrac{1}{2}\eta^2.$
-This way, the hydrophilic side has the same phase as the bulk
-($\eta = 0$, the minimum of $f$) and the hydrophobic side has
-a higher potential energy phase.
-
-Using \eqref{}-\eqref{}, suspensions of these granules self-organize
-so that (i) apposing hydrophobic sides abut and (ii) granules align
-side by side into sheets.  Vesicles are a stable configuration
-of this process and the self-organization automatically expels or
-absorbs the number of granules needed to minimize frustration between
-the two leaflets.  But even for random initial configurations,
-the granules form a collection of small vesicles and bilayer segments.
-These disordered collections typically represent a local energy minimum 
-because under a slight perturbation, the small vesicles and segments
-further combine to form larger, stable vesicles.
+We have compared two-dimensional configurations of amphiphilic granules
+to membrane configurations found in continuum mechanics.
+The simulations results in~\cite{Fu2018_SIAM,FuQuRyYo22}
+showed that the granular bilayers 
+basically replicated the elastic energies for bending, tilt, and
+stretching.
+The hydrodynamics of the Janus particle vesicle is similar to the behaviour of an inextensible,
+elastic vesicle membrane with permeability.
+The model has reached sufficient maturity to warrant 
+rigorous studies in analysis.
 
@@
 This problem is attractive because combines the diffusive interface
-effects involving a free boundary in aqueous part of the region \cite{}
-with interfacial effects coming from the long range inter-granual
-attraction. Generalizations of Problem 1 include modifying the 
+effects involving a free boundary in aqueous part of the region \cite{}.
+The well-posedness of Allen-Cahn-type equations is well-established in the
+literature.  What makes this challening, though, is that
+the moving domain means the function space for the solution,
+a Sobolov space, is also changing with time.
+On ther other hand, the problem \eqref{eq:RBT}--\eqref{eqn:stressbalance}
+is an autonmous ordinary differential equation for rigid body transformations.
+The right-hand side of this equation is defined by a system of elliptic
+PDE.  On the other hand, several methods have been developed for
+analysing the smooth domain dependence of solutions to elliptic PDE,
+especially in the study of eigenvalue problems, for example.
+It is conceivable that moving domain estimates can be applied to the
+present problem to exhibit locally Lipschitz dependence on
+the rigid deformations.
+
+Generalizations of Problem 1 include modifying the 
 system to account for various time scales.
@@
 Euler-Lagrange derivative $\frac{\delta E}{\delta \phi}$.
+(DEFINE $\lambda$)
 
@@
 of equilibrium elastic energy of curves and surfaces.
-We have compared two-dimensional configurations of amphiphilic granules
-to membrane configurations found in continuum mechanics.
-The simulations results in~\cite{Fu2018_SIAM,FuQuRyYo22}
-showed that the granular bilayers 
-basically replicated the elastic energies for bending, tilt, and
-stretching
-but we do not yet have any analytical evidence to support this conclusion.
 To understand the approximation mathematically, we take the following:
@@
 
+We conclude this section by highlighting another well-developed
+area connected to our approach.  Surface-director models 
+considers the energy of a nematic liquid crystal on a surface to study how the
+surface geometry effects the director field and vice versa. Researchers
+have formulated finite element methods for [][] and studied the existence
+of minimizers []-[].
+Liquid crystals are an extremely well-studied are in mathematics [].
+
+On the other hand, in biophysics, tilt is defined by the tilt vector
+  $\TT = \dd/\dd\cdot \NN - \NN$ so that the tilt energy density
+  behaves like $\tan^2 \theta$ rather than $\sin^2 \theta$.
+  These two energies densities are, however, asymptotically equal
+  for small deformations.
+Hamm and Kozlov [] and later Terzi and Deserno [], Pinigen et al. []
+showed that the full Helfrich elastic energy of a \emph{monolayer} takes the form
+\begin{equation}
+\label{eq:Helfrich}
+  \begin{aligned}
+ &\int_{\Sigma}
+  %\label{eq:Pinigan}
+\tfrac{1}{2}k_{b}[(\nabla \cdot \mathbf{d} + k_{0})^{2} -  k^{2}_{0}]  
++ \tfrac{1}{2}k_{\theta}\mathbf{T}^{2} + \tfrac{1}{2}k_a[(\alpha - \alpha_0)^2 - \alpha_0^2] \\
+&+ k_{c}\textbf{T} \cdot \nabla \nabla \cdot \mathbf{d}  + \tfrac{1}{2}k_{g}(\nabla \nabla \cdot \mathbf{d})^{2}
+ + A\alpha \nabla \cdot \mathbf{d}
++ B \mathbf{T} \cdot \nabla \alpha \\
+&- \tfrac{1}{2}k_c |\nabla \alpha|^2 + C \nabla \alpha \cdot \nabla \nabla \cdot \mathbf{d}\,dS
+\end{aligned}
+\end{equation}
+where $\nabla$ and $\nabla \cdot$ are the surface gradient and surface divergence,
+respectively, and $k_B$, $k_{\theta}$, $k_a$, $k_c$, $k_g$, $A$, $B$, $C$ are
+appropriate elastic moduli.  An important and consequential distinction between
+\eqref{eq:Canham-Helfrich} is the presence of the terms $\mathbf{T}$ and $\alpha$.
+These are, respectively, the \emph{tilt} vector $\mathbf{T}$ measuring
+the difference between the lipid director $\mathbf{d}$ and the surface normal
+$\mathbf{N}$; the \emph{area per lipid} $\alpha$ area density at rest $\alpha_0$.
+The two models \eqref{eq:Canham-Helfrich} and \eqref{eq:Helfrich} agree
+when $\mathbf{T} = 0$ and $\alpha = \alpha_0$ everywhere.
+
+(MAKE CONNECTION WITH SPECIFIC AIM 2)
+(PLAN B)
+(SHORTER PROBLEM STATEMENT; ADDRESS IN PARAGRAPH)
+
 %\setcounter{page}{1}

### 2022-11-10 NSF2022/Description/backgroundv2.tex
BG almost done

@@
 when periodic domains are not under consideration.
-
-(Surface-director models.)
 
@@
 Traditional models represent a vesicle as a
-continuous surface or curve $\Sigma$.
+continuous surface (or curve in $\mathbb{R}^2$) $\Sigma$.
 The elastic energy takes the form
@@
 and $k_B$ is a bending modulus. 
-The variation of \eqref{eq:Canham-Helfrich} gives rise to a surface force
+The variation of \eqref{eq:Canham-Helfrich} with respect to position
+gives rise to a surface force
 that pointwise balances the jump in hydrodynamic stress across the interace.
-A vesicle is closed surface, and so while energy does involve
-the Gaussian curvature, it does not enter \eqref{eq:Canham-Helfrich}
+While energy density does depend on Gaussian curvature,
+it does not appear in \eqref{eq:Canham-Helfrich}
 since Gauss-Bonnet Theorem guarantees that
-the integral of Gaussian curvature is independent of the shape of $\Sigma$.
+the integral of Gaussian curvature over a closed surface is independent of the shape of $\Sigma$.
 
@@
 then \eqref{eq:Canham-Helfrich} contains an additional stretching term of the
-form $k_A(\alpha - \alpha_0)^2/\alpha_0$ where $\alpha$ and $\alpha_0$ are the
+form $k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are the
 deformed and equilibrium area densitities respectively.
@@
 \cite{}.
-These kinds of topological changes are clumsy to incorporate into 
+These kinds of topological changes are clumsy to incorporate in
 sharp interface formulations that assume a continuous surface \cite{}.
@@
 
-Diffusive interface models and surface-director models partially make up for some of
+Diffusive interface models and surface-director models partially address 
 these shortcomings. 
@@
 but these methods smear out the details of lipid orientations.
-The question lipid orientations is closely related to the vast and well-studied
-field of nematic liquid crystals.  Here there has been recent development
-in the simulation and theory of nematic liquid crystals on surfaces.
+The detailed energies of lipid orientation that include tilt are
+closely related to the celebraated and well-studied
+field of nematic liquid crystals.  Here, there have been recent development
+in simulation and theory of nematic liquid crystals on surfaces.
 These models consider the interplay between defects and surface geometry \cite{},
@@
 as a robust and flexible approach
-that cuts across many of the aforementioned challenging aspects to vesicle modeling.
+that cuts across many of the aforementioned challenges.
 (i) The granules are not fixed to a stencil, 
 affording flexibility in terms of vesicle morphology and topology--sufficiently
-large forces will pull the granules apart as physically required.
+large forces will even pull the granules apart as physically required.
 (ii) The model formulation is built around important details like lipid orientations,
-and exhibits and inter-monolayer slip not present in diffusive interface models.
+and exhibits inter-monolayer slip that must be added into diffusive interface models
+post hoc. 
 (iii) It is straightforward to consider mixtures of granules with different
@@
 granules undergo a rapid coarsening to form bilayers.
-For small granule numbers, the bilayers form a single stable, ring-shaped vesicle
+For tens of granule, the bilayers form a single stable, ring-shaped vesicle
 with energy $E_{\text{stable}}$ (Figure \ref{fig:coarsening}, (c)).
@@
 is the global minimizer.  The difference between
-$E(t)$ and $E_{\min}$ is the elastic energy stored by granules.
+$E(t)$ and $E_{\min}$ is the vesicle elastic energy.
 Indeed, if a background flow overcomes the energy barrier to force granules apart,
-then bilayer unfolds from its circular shape into a flat shape.
+then the bilayer unfolds from its circular shape into a flat shape.
 
-When many granules are involved, the granules reach an intermediate
+When hundreds granules are involved,
+the two-dimensional granules reach an intermediate
 state consisting of several bilayer segments (see Figure \ref{fig:self-assembly2}, top right).
@@
 
-and we analyze its energy as follows:
-\begin{enumerate}
-\item[Bending]
-  The vesicle has bending energy because the directors are not
-  parallel.  In the outer layer, the directors have negative
-  splay $\nabla \cdot \dd < 0$ and in the inner layer
-  the directors have positive splay $\nabla \cdot \dd > 0$.
-  Due to minimality, the energy depends locally quadratically
-  on the splay and has a bending modulus $k_B$.
-  When $\dd$ is everywhere parallel to the unit normal $\NN,$ then
-  \[
-  \nabla \dd = -2H
-  \]
-  where $H$ is the mean curvature. 
-\item[Stretch]
-  If the vesicle is stretched, then the distance between
-  neighboring granules is increased from rest.  The energy
-  for this increase is Hookean and for small deformations
-  equals
-  \begin{equation}
-    \label{eq:stretch}
-    \tfrac{1}{2}k_A(L - L_0)^2/L_0
-  \end{equation}
-  where $k_A$ is a stretching modulus, $L$ and $L_0$ are stretched
-  vesicle length and length at rest, respectively
-  ($\tfrac{1}{2}k_A(A - A_0)^2/A_0$ in three dimensions).
-  If the stretching is too great, the vesicle ruptures
-  and the free eneds either rejoin, repairing the vesicle,
-  of move apart forming a flat bilayer.
-\item[Tilt]
-  The directors in Figure \ref{} are normal to the vesicle surface.
-  However, there are situations where the directors are not normal
-  to the surface and this introduces the tilt angle $\theta$
-  given by $\cos \theta = \dd \cdot \NN$.
-  The energy for tilt is also Hooken and behaves like
-  $k_{\theta}|\dd \times \NN|^2$ for the tilt modulus $k_{\theta}$.
-\end{enumerate}
+Having a non-specific model that replicates detailed
+physics and biology is the crown jewel of applied mathematics
+and we believe that ours is such a model.
 
@@
 \end{wrapfigure}
+\textit{Summary of results from the paper \cite{Fu2018_SIAM}.}
+A striking aspect of the
+model is its fidelity to physics.
+The model contains a few
+parameters; granule radius $c$,
+screening length $\epsilon$,
+surface tension $\gamma$.
+When set to realistic values,
+\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
+we recover many of the well-known
+elastic moduli for single-component lipid bilayers
+\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}.
+\emph{Bending:}
+The bending deformation enters through the splay of the
+granule directors.  In Figure \ref{fig:JPv_linearshear},
+for example, the directors have negative, respectively positive,
+splay $\nabla_{\Sigma} \cdot \dd$
+in the outer, respectively inner monolayers.
+Here $\nabla_{\Sigma}\cdot{} = \nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$
+is the surface divergence for the unit normal $\NN$
+and the splay energy density
+for the granule configuration is Hookean with bending modulus $k_B$.
+It is a fact from differential geometry that
+when $\dd$ is everywhere parallel to $\NN,$
+then $\nabla\cdot \dd = \pm 2H$ and this is how the
+curvature term arises for \eqref{eq:Canham-Helfrich}
+($2H = \kappa$ in the two-dimensional setting).
+In the case of mixtures of granules of different sizes,
+spontaneous curvature $k_0$ arises
+from asymmetry in the monolayer leaflets.
+\emph{Stretching.}
+When stretched, the distance between
+neighboring granules is increased from rest
+and the energy for stretching behaves as 
+$\tfrac{1}{2}k_A(L - L_0)^2/L_0$
+for a stretching modulus $k_A$,
+length $L$, and
+length at rest $L_0$ of the two-dimensional vesicle. 
+\emph{Tilt.}
+Finally, the granules possess a 
+tilt decay length scale $\lambda = \sqrt{k_B/k_{\theta}}$
+well-known from the biophysical literature
+for the case when the directors $\mathbf{d}$ are no longer normal
+to the surface
+\cite{KUZMIN2005}.
+
+\textit{Summary of results from the paper \cite{FuQuRyYo22}.}
 
@@
 \end{wrapfigure}
-
-This is our first step to showing the energy of the granule-based
-vesicles have the same elastic energy as bilayers in the limit $N_b \to \infty$.
-Once we have simulations for large systems sizes, we can provide
-evidence that the two formulations are the same.
-So and so has made simulations with thousands of granules in three-D
-and this is now a technical/not theoretical limitation.
 

### 2022-11-10 NSF2022/Description/specificaim2.tex
working on SA2

@@
 \label{sec:specificaim2}
-\begin{itemize}
-%  \item Make clear that we know how to address NSI and fast summation
-  \item Talk about collision as per talk with Bryce
-%  \item Wen's paper can be used to give numbers on how large or a
-%    problem could hypothetically be considered
-%  \item Emphasize that we've learned a lot from just $\mathcal(O)(100)$
-%    particles, but now it's time to do more
-  \item Confinement and rheology
-\end{itemize}
-
 % ----------------------------------------------------------------------
@@
 they, like for the rates of biological functions like pore
-dynamics~\cite{RYHAM20112929}, set the rate of dissipation. In Specific
-Aim 2, we propose novel and efficient high-order numerical methods to
-simulate dynamic assembly of particles under the HAP in a viscous
-solvent. As described in~\eqref{eqn:stokes} and illustrated in
-Figure~\ref{fig:flow_map}, the solvent phase is modeled by the Stokes
-equations for an incompressible, viscous fluid, and these equations are
-coupled to the non-linear screened-Laplace equation~\eqref{eqn:phase}
-through viscous and hydrophobic stress balance.
-
-%\label{subsec:specific_aim_2}
-%\begin{wrapfigure}[14]{r}{0.61\textwidth}
-%  \centering{\includegraphics[width=0.60\textwidth]{Figures/domain.pdf}}
-%    \vspace{-15pt}
-%    \caption{\label{fig:flow_map} \footnotesize A collection of 3D
-%    amphiphilic particles suspended in a solvent. The solvent velocity
-%    satisfies the Stokes equations, and the hydrophobic forces depend on
-%    the solvent activity that satisfies the screened Laplace equation.
-%    The geometry is updated by solving the mobility problem.} 
-%\end{wrapfigure}
-The HAP model requires solving exterior problems for the order
-parameter~\eqref{eqn:phase} and the Stokes equations~\eqref{eqn:stokes}.
-We will develop methods based on combinations of volume and layer
-potentials, and inexact Newton's method. As mentioned in
-Section~\ref{sec:bie}, numerical methods to solve these integral
-equations (IEs) have several advantages over their PDE-based
+dynamics~\cite{RYHAM20112929}, set the rate of dissipation. The success
+of Specific Aims 1 and 3 depends on the ability to accurately and
+efficiently simulate dense suspensions of granules governed by
+equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance}. Because of their
+ability to resolve complex unbounded domains and achieve high-order
+accuracy, integral equation methods will be a central theme of the
+computational tools. As discussed in Section~\ref{sec:bie}, numerical
+methods to solve IEs have several advantages over their PDE-based
 counterpart. The PIs have demonstrated that IEs are a powerful tool to
@@
 elements of these formulations have been developed in three
-dimensions~\cite{ying_2006, manasthesis, rac-gre2016}. This proposal
-will extend the two-dimensional methods to more general amphiphilic
-particle models and also to three dimensions. In addition, the methods
-will allow us to use results we have shown for $\mathcal{O}(100)$
-granules, and extend them to suspensions with 100X--1000X more granules.
-These methods will be motivated by models and analysis developed in
-Specific Aims 1 and 3. \S\ref{subsec:AC} describes how the non-linear
-equation for the order parameter~\eqref{eqn:phase} will be iteratively
-solved using an IE formulation. Then, \S\ref{subsec:NumericalIssues}
-describes how we will combine accurate quadrature and fast summation
-methods to accelerate the time to accurate solutions. A natural
-extension to create simulations that are realizable by experimentalists
-is to include confinement, and this is discussed in
-\S\ref{subsec:Confinement}. This extension will also allow us to develop
-new rheological properties of the suspensions.  Finally,
-\S\ref{subsec:timeStepping} proposes collision-aware adaptive time
-stepping methods.
+dimensions~\cite{ying_2006, manasthesis, rac-gre2016}. In our current
+implementation, we can simulate $\mathcal{O}(100)$ two-dimensional
+granules, and the proposed research will allow for the suspensions with
+100X--1000X more two-dimensional granules and $\mathcal{O}(1000)$
+three-dimensional granules.
 
-% ----------------------------------------------------------------------
-\subsubsection{An inexact Newton solver for the phase transition PDE}
-\label{subsec:AC}
-
-\begin{wrapfigure}[28]{l}{1.8in}
+\begin{wrapfigure}[27]{l}{1.8in}
   \vspace{-8pt}
@@
 \end{wrapfigure}
+
+The order parameter is governed by the PDE~\eqref{eqn:phase} in the
+solvent phase $\Omega(t)$. For the single-well $W(\phi) = \phi^2$,
+equation~\eqref{eqn:phase} is linear, and the PIs have demonstrated that
+IEs are a powerful tool to solve for the order
+parameter~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022}. However,
+for a general double-well potential $W(\phi)$, the resulting PDE is
+nonlinear, motivating the following problem:
+
+% ----------------------------------------------------------------------
+\begin{quotation}
+  \noindent
+  \textbf{Problem 3.} How can IEs be coupled with a Newton solver to
+  solve the non-linear PDE~\eqref{eqn:phase}?
+\end{quotation}
+
 The PIs have developed numerical methods to solve~\eqref{eqn:phase} when
@@
   \label{eqn:phaseRoot}
-  J[\phi] = -\epsilon^2 \Delta \phi + \tfrac{1}{2}W'(\phi).
+  F[\phi] = -\epsilon^2 \Delta \phi + \tfrac{1}{2}W'(\phi).
 \end{align}
 Equation~\eqref{eqn:phaseRoot} will be solved with Newton's method,
-$\phi^{N+1} = \phi^{N} - \alpha (dJ^N)^{-1} J(\phi^N)$, where $dJ^N =
+$\phi^{N+1} = \phi^{N} - \alpha (dF^N)^{-1} F(\phi^N)$, where $dF^N =
 -\epsilon^2 \Delta + \tfrac{1}{2}W''(\phi^N)$ is the Fr\'{e}chet
@@
 using backtracking. This requires solving the variable coefficient PDE
-$-\epsilon^2 \Delta v + \tfrac{1}{2}W''(\phi^{N}) v = J[\phi^N]$, which
+$-\epsilon^2 \Delta v + \tfrac{1}{2}W''(\phi^{N}) v = F[\phi^N]$, which
 is challenging with an integral equation since a fundamental solution is
@@
 $W''(\phi_0) = W''(\phi_1) = \beta$, we propose to instead use an
-inexact Newton's method where $dJ^{-1}$ is approximated with the
-solution of $-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$. We
+inexact Newton's method where $dF^{-1}$ is approximated with the
+solution of $-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = F[\phi^N]$. We
 test the efficacy of the exact and inexact Newton's method applied
-to~\eqref{eqn:phaseRoot} in $(0,1) \subset \RR$ by discretizing $dJ$
+to~\eqref{eqn:phaseRoot} in $(0,1) \subset \RR$ by discretizing $dF$
 with a second-order finite difference stencil. The double well potential
@@
 solve~\eqref{eqn:phase} in two and three dimensions. The solution of
-$-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = J[\phi^N]$ can be written
+$-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = F[\phi^N]$ can be written
 as $v = v^P + v^H$ where $v^P$ is a volume potential and $v^H$ is a
@@
 \begin{align*}
-  v^{P}(\xx) = \int_{\Omega(t)} G(\xx,\yy) J[\phi^N](\yy)\, d\yy, 
+  v^{P}(\xx) = \int_{\Omega(t)} G(\xx,\yy) F[\phi^N](\yy)\, d\yy, 
     \quad \xx \in \Omega(t),
@@
 che-hua-lei2005}.
+% ----------------------------------------------------------------------
+\begin{quotation}
+  \noindent
+  \textbf{Problem 4.} How can novel quadrature, time adaptivity, fast
+  summation, and collision-detection be combined to accurately and
+  efficiently solve the governing
+  equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} in bounded and
+  unbounded domains in two and three dimensions?
+\end{quotation}
 
-% ----------------------------------------------------------------------
-\subsubsection{Increased accuracy and reduced CPU time}
-\label{subsec:NumericalIssues}
-While IE formulations of PDEs have several advantages, several
-challenges must be overcome before the code can be used to simulate
-systems with large numbers of granules. For example, when granules are
-close to one another, which is inevitable in dense suspensions, the
-resulting integrals are nearly-singular. This issue is well-known in the
-IE community and several algorithms have been developed in the last 30
-years. An incomplete list of methods that address near-singular
-integration include panel-based methods~\cite{helsing_2008a,
-helsing_tutorial_2012}, Quadrature by Expansions
-(QBX)~\cite{din-hua-mar-tan2021, klo-bar-gre-one2013, ste-bar2022,
-af2018sisc}, and interpolation-based methods~\cite{ying_2006,
-qua-bir2014, rah-vee-zor-bir2015}. The proposed research, which is
-described next,  will combine several methods including singularity
-subtraction, analytic function theory, and spherical basis
-representations.
+\begin{wrapfigure}[]{r}{2.1in}
+  \centering
+  \input{figures/near_sing.tikz}
+  \caption{\label{fig:interpquad} An interpolation-based quadrature
+  method that works in two and three dimensions. The spectrally-accurate
+  trapezoid rule is used in points in $\mathtt{Far}(\Gamma_i)$, while
+  one dimensional interpolant is used for points in
+  $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength spacing.}
+\end{wrapfigure}
+
+In experiments, it is known that interactions between bounding walls and
+granules cannot be ignored~\cite{qua-gan-you2021,
+KaouiHartingMisbah2011_PRE, her-sto-gra2005}. Therefore, the necessary
+modification to the code will be performed so that confinement can be
+considered. This modification requires introducing an additional layer
+potential on the bounding walls, and elements of this modification have
+already been incorporated (Figure~\ref{fig:stenosis}). However, to
+consider rheological properties of the suspensions, a periodic domain,
+such as a Couette device, will be considered. This multiply-connected
+domain requires additional modifications. PI Quaife has considered
+suspensions with confinement for several projects including dynamic
+suspensions~\cite{qua-bir2014, bys-sha-qua2020} and porous
+media~\cite{chi-moo-qua2020, dea-qua-bir-jua2018, moo-che-chi-qua2022,
+qua-gan-you2021}.
+
+When granules are close to one another, which is inevitable in dense and
+confined suspensions, the resulting integrals are nearly-singular. This
+issue is well-known in the IE community and several algorithms have been
+developed in the last 30 years, including panel-based
+methods~\cite{helsing_2008a, helsing_tutorial_2012}, Quadrature by
+Expansions (QBX)~\cite{din-hua-mar-tan2021, klo-bar-gre-one2013,
+ste-bar2022, af2018sisc}, Barycentric-type formulae for Cauchy
+integrals~\cite{bar2014, bar-wu-vee2015, ioa-pap-per1991}, and
+interpolation-based methods~\cite{ying_2006, qua-bir2014,
+rah-vee-zor-bir2015} (Figure~\ref{fig:interpquad}). The proposed
+research, which is described next, will combine several methods
+including singularity subtraction, analytic function theory, and
+spherical basis representations.
 
@@
 \label{subsec:Confinement}
-In experiments, it is known that interactions between bounding walls and
-granules cannot be ignored~\cite{qua-gan-you2021,
-KaouiHartingMisbah2011_PRE, her-sto-gra2005}. Therefore, the necessary
-modifications to the code will be performed so that confinement can be
-considered. PI BQ has considered suspensions with confinement for
-several projects including dynamic suspensions~\cite{qua-bir2014,
-bys-sha-qua2020} and porous media~\cite{chi-moo-qua2020,
-dea-qua-bir-jua2018, moo-che-chi-qua2022, qua-gan-you2021}.
 

### 2022-11-10 NSF2022/Description/backgroundv2.tex

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Boundary integral formulation}
+\label{sec:bie}
+
+\begin{wrapfigure}[10]{r}{2in}
+  \todo[inline]{A figure comparing FEM versus BIE meshes}
+  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
+  requires meshing the entire domain (typically into triangles), while a
+  BIE only requires meshing the boundary of the domain.}
+\end{wrapfigure}
+Boundary integral equations (BIEs) are a reformulation of elliptic PDEs
+including the Stokes equation~\eqref{eqn:stokes} and the phase
+equation~\eqref{eqn:phase} in the special case of $f(u) =
+\tfrac{1}{2}u^2$. Using the Stokes equation as an example, its solution
+can be written as a convolution 
+\begin{align*}
+  \uu(\xx) = \int_{\partial\Omega_t} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
+\end{align*}
+where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
+fundamental solution and $\ssigma: \partial \Omega_t \rightarrow \RR^2$
+is an unknown density function. The BIE reformulation has several
+immediate advantages including a dimension reduction since $\ssigma$ is
+defined only on $\partial \Omega_t$, and the far field boundary
+condition of the PDE is automatically satisfied. The density
+function $\ssigma$ is chosen to satisfy the boundary condition, and this
+results in a BIE 
+\begin{align*}
+  \gg(\xx) = \lambda \ssigma(\xx) + 
+    \int_{\partial\Omega_t} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
+    \quad \xx \in \partial\Omega_t,
+\end{align*}
+where $\gg$ is the Dirichlet boundary condition, and $\lambda$ is a
+constant that depends on the choice of $G$. For numerical stability,
+choices of $G$ that result in second-kind Fredholm integral equations,
+meaning $\lambda \neq 0$, are preferred.
+
+A consequence of the dimension reduction in a BIE formulation is that
+complex geometries are much easier to resolve than a mesh-based method
+since only $\partial \Omega_t$ needs to be discretized
+(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a BIE
+formulation includes a discretization that is high-order, or even
+spectrally, accurate; results in a well-conditioned linear system that
+can be solved iteratively with a mesh-independent number of iterations
+of a Krylov method such as the generalized minimal residual method
+(GMRES). However, BIEs do have several challenges: nearly touching
+granules requires a quadrature rule for nearly-singular integrals; their
+discretization results in dense matrices; and they cannot immediately be
+applied to non-linear PDEs. The BIE community, including PI Quaife, has
+developed a variety of tools to address these numerical challenges, and
+we discuss our planned approach in Section~\ref{sec:specificaim2}.
+
 \subsection{Vesicles as self-organized granules}
@@
 
-\begin{wrapfigure}[12]{r}{0.5\textwidth}
-  \vspace{-5pt}
-\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
-  \vspace{-5pt}
-\caption{\label{fig:amphiphilic_assembly}
-Self-organization under amphiphilic boundary condition.
-(a) Granules first match hydrophobic tails (red),
-(b) then align length-wise.
-The principle of self-organization holds in three dimensions 
-as simulated by Kohl, Corona, and Veerapaneni
-\cite{koh-cor-che-vee2021}.}
-\end{wrapfigure}
 There are downsides to traditional models in terms of generality and physical realism.
@@
 
+\begin{wrapfigure}[12]{r}{0.5\textwidth}
+  \vspace{-5pt}
+\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
+  \vspace{-5pt}
+\caption{\label{fig:amphiphilic_assembly}
+Self-organization under amphiphilic boundary condition.
+(a) Granules first match hydrophobic tails (red),
+(b) then align length-wise.
+The principle of self-organization holds in three dimensions 
+as simulated by Kohl, Corona, and Veerapaneni
+\cite{koh-cor-che-vee2021}.}
+\end{wrapfigure}
 Diffusive interface models and surface-director models partially address 
@@
 \includegraphics[width=0.5\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
-\caption{\label{fig:JPv_linearshear}The JP vesicles undergo tank-treading in background shear flow.}
+\caption{\label{fig:JPv_linearshear}Granular vesicles undergo
+tank-treading in background shear flow.}
 \end{wrapfigure}
@@
 
-\textit{Summary of results from the paper \cite{FuQuRyYo22}.}
-
 \begin{wrapfigure}[14]{l}{0.475\textwidth}
@@
 \includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
-\caption{\label{fig:JPv_rupture}The JP vesicles rupture under large shear rates.}
+\caption{\label{fig:JPv_rupture}Rupture of a granular vesicle under large shear rates.}
 \end{wrapfigure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Boundary integral formulation}
-\label{sec:bie}
-
-\begin{wrapfigure}[10]{r}{2in}
-  \todo[inline]{A figure comparing FEM versus BIE meshes}
-  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
-  requires meshing the entire domain (typically into triangles), while a
-  BIE only requires meshing the boundary of the domain.}
-\end{wrapfigure}
-Boundary integral equations (BIEs) are a reformulation of elliptic PDEs
-including the Stokes equation~\eqref{eqn:stokes} and the phase
-equation~\eqref{eqn:phase} in the special case of $f(u) =
-\tfrac{1}{2}u^2$. Using the Stokes equation as an example, its solution
-can be written as a convolution 
-\begin{align*}
-  \uu(\xx) = \int_{\partial\Omega_t} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
-\end{align*}
-where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
-fundamental solution and $\ssigma: \partial \Omega_t \rightarrow \RR^2$
-is an unknown density function. The BIE reformulation has several
-immediate advantages including a dimension reduction since $\ssigma$ is
-defined only on $\partial \Omega_t$, and the far field boundary
-condition of the PDE is automatically satisfied. The density
-function $\ssigma$ is chosen to satisfy the boundary condition, and this
-results in a BIE 
-\begin{align*}
-  \gg(\xx) = \lambda \ssigma(\xx) + 
-    \int_{\partial\Omega_t} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
-    \quad \xx \in \partial\Omega_t,
-\end{align*}
-where $\gg$ is the Dirichlet boundary condition, and $\lambda$ is a
-constant that depends on the choice of $G$. For numerical stability,
-choices of $G$ that result in second-kind Fredholm integral equations,
-meaning $\lambda \neq 0$, are preferred.
-
-A consequence of the dimension reduction in a BIE formulation is that
-complex geometries are much easier to resolve than a mesh-based method
-since only $\partial \Omega_t$ needs to be discretized
-(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a BIE
-formulation includes a discretization that is high-order, or even
-spectrally, accurate; results in a well-conditioned linear system that
-can be solved iteratively with a mesh-independent number of iterations
-of a Krylov method such as the generalized minimal residual method
-(GMRES). However, BIEs do have several challenges: nearly touching
-granules requires a quadrature rule for nearly-singular integrals; their
-discretization results in dense matrices; and they cannot immediately be
-applied to non-linear PDEs. The BIE community, including PI Quaife, has
-developed a variety of tools to address these numerical challenges, and
-we discuss our planned approach in Section~\ref{sec:specificaim2}.
+\textit{Summary of results from the paper \cite{FuQuRyYo22}.}
+In terms of hydrodynamics, the granule vesicles in linear
+background flows \eqref{eqn:shear_BG_flow} also replicates
+the behaviour of an continous, inextensible,
+elastic vesicle with permeability.
+The simulations showed, for the first time,
+a granule-vesicle suspension behaving
+as a tank-treading vesicle \cite{Finken2008, Shaqfeh11}
+(see Figure \ref{fig:JPv_linearshear}).
+Movies of Figure \ref{fig:JPv_linearshear} reveal
+intermonolayer slip and derived values for intermonolayer
+friction were in good quantitative agreement 
+those derived by atomistic and Martini force field
+simulation studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}.
+In Figure \ref{fig:JPv_rupture},
+membrane rupture occurs at large shear rates $\dot \gamma$
+and we derived a dimensional scaling to 
+predict critical shear rate for rupture
+\cite{VLAHOVSKA2009775,keller_skalak_1982}.
+Finally, a side-by-side comparison
+of granule-based vesicles and the continuous model using
+\eqref{eq:Canham-Helfrich} yielded shapes and trajectories that
+basically overlapped.
 

### 2022-11-10 NSF2022/Description/specificaim1v2.tex

@@
 
-%\setcounter{page}{1}
-%\addcontentsline{toc}{section}{Bibliography}
-%\bibliographystyle{abbrvnat}
-%%
-%\bibliography{refs}
-%
-%
-%
-%\end{document}
+Our future goals include extending the current framework to a three-dimensional JP vesicle system.
+This will require additional algorithmic implementation including a fast summation method such as the fast multipole method.
+Other research directions include fluctuating hydrodynamics for Brownian suspensions (Bao et al.
+2018), critical to understanding membrane diffusion, and an analysis of the relationship between particle shape on effective properties.
+Finally, physically more accurate boundary conditions for the HAP model will allow us to draw comparisons between computational and laboratory experiments.

### 2022-11-10 NSF2022/Description/backgroundv2.tex
BG

@@
 in an incompressible, zero-Reynolds number fluid
-$\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b} U_i(t)$
+$\Omega_t = \RR^n \setminus \cup_{i=1}^{N_b} U_i(t)$
 (Figure \ref{fig:flow_map}).
@@
   -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
-  &&\quad \nabla \cdot \uu = 0, && \quad \xx \in \Omega(t), \label {eqn:stokes} \\
+  &&\quad \nabla \cdot \uu = 0, && \quad \xx \in \Omega_t, \label {eqn:stokes} \\
   \label{eqn:phase}
-  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, && &&\quad \xx \in \Omega(t),\\
+  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, && &&\quad \xx \in \Omega_t,\\
 \label{eqn:noslip}        
@@
   \uu^T|^2 \,d\xx,\quad
-    E = \gamma \int_{\Omega(t)}
+    E = \gamma \int_{\Omega_t}
   \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
@@
 
-Because $E$ depends both on $\phi$ and $\Omega(t)$,
+Because $E$ depends both on $\phi$ and $\Omega_t$,
 the derivation of \eqref{eq:energy_law}
@@
 of a screened Laplace (SL) equation $-\epsilon^2 \Delta \phi + \phi =0$.
-If the material label $h_i = 1$ everywhere, then $\phi$
+For a fixed domain $\Omega$ with class $\mathbf{C}^2$ boundary \cite{},
+if the material label $h_i = 1$ everywhere, then $\phi$
 has a boundary layer going from $1$ at the boundary to $0$ in the bulk
@@
 \label{eqn:math_motivation}
-\lim_{\epsilon \to 0} E = \frac{\gamma}{2} \int_{\partial \Omega} 1 \,dS
+\lim_{\epsilon \to 0} E = \frac{\gamma}{2} \int_{\partial \Omega} 1 \,dS.
 \end{equation}
-under the assumption that $\Omega$ has a class $\mathbf{C}^2$ boundary \cite{}.
 In other words, the phase energy can be viewed as an
@@
 \label{sec:bie}
-
 \begin{wrapfigure}[10]{r}{2in}
@@
 \end{wrapfigure}
+The solution of PDEs in a domain surrounding a mobile, dense suspension
+of bodies is highly nontrivial and requires accurate,
+dimension-reducting discretization
+that do not require continual remeshing.  
 Boundary integral equations (BIEs) are a reformulation of elliptic PDEs

### 2022-11-10 NSF2022/Description/backgroundv2.tex
changes to  background

@@
 
-Mathematical models of self-organization encompasses a
-broad range of interesting and challenging phenomena.
-For example, understanding the organization of lipids and proteins in vesicles
-is crucial to design effective drug and vaccine carriers.
-The COVID-19 pandemic has lead to an unprecedented and concerted worldwide
-effort in biophysical modeling of the mechanisms of RNA condensation
-by structural proteins, protein oligomerization, and cellular
-membrane–protein interactions that control ultimate virus structure,
-in an effort to curtail pathogens like the Severe Acute Respiratory Syndrome Coronavirus 2.
-Using powerful capillary and van der Waals forces that exist at the nanoscale, engineers
-have developed superior techniques to print 
-high-resolution, nanoscale features on devices like sensors, lasers, and LEDs.
-Finally, researchers have introduced data-driven methods 
-to study complex patterns that emerge in particle and agent-based systems like swarms
-and flocking.
+Mathematical models of self-organization encompasses a broad range of
+interesting and challenging phenomena. For example, understanding the
+organization of lipids and proteins in vesicles is crucial to design
+effective drug and vaccine carriers. The COVID-19 pandemic has led to an
+unprecedented and concerted worldwide effort in biophysical modeling of
+the mechanisms of RNA condensation by structural proteins, protein
+oligomerization, and cellular membrane–protein interactions that
+ultimately control virus structure, in an effort to curtail pathogens
+like the Severe Acute Respiratory Syndrome Coronavirus 2. Using powerful
+capillary and van der Waals forces that exist at the nanoscale,
+engineers have developed superior techniques to print high-resolution,
+nanoscale features on devices like sensors, lasers, and LEDs. Finally,
+researchers have introduced data-driven methods to study complex
+patterns that emerge in particle and agent-based systems like swarms and
+flocking.
 
-A number of mathematical techniques have beed developed to handle
-self-organizing systems.  Each technique has its advantages and disadvantages.
-Prominent in chemistry and biology, molecular
-dynamics (MD) simulations offers unparalleled resolution of protein-lipid interactions,
-say, but because of the large number of non-linear interactions involved,
-is limited to short time and small spatial scales.
-In terms of inverse problems,
-agent based systems also involve relatively large numbers of particles
-and here researchers extensively consider the problem  
-of learning interaction kernels in these dynamical systems
-constrained to evolve on Riemannian manifolds from given trajectory data.
-Once the interaction kernels are known, one can in principle derive
-partial differential equations (PDE) for the macroscopic behavior.
+A number of mathematical techniques have been developed to handle
+self-organizing systems. Each technique has its advantages and
+disadvantages. Prominent in chemistry and biology, molecular dynamics
+(MD) simulations offers unparalleled resolution of protein-lipid
+interactions, say, but because of the large number of non-linear
+interactions involved, is limited to short time and small spatial
+scales. In terms of inverse problems, agent based systems also involve
+relatively large numbers of particles and researchers extensively
+consider the problem of using trajectory data to learn interaction
+kernels of the dynamics when constrained to evolve on Riemannian
+manifolds. Once the interaction kernels are known, one can in principle
+derive partial differential equations (PDE) for the macroscopic
+behavior.
 
 The phase field method and self-consistent field theory are popular
-approaches to self-organization in applied mathematics.
-Motivated by Ginzburg-Landau theory, these methods introduce a scalar-valued
-phase field function for the volume fraction of
-lipids and water in modeling vesicles membranes, for example. 
-Sometimes called diffuse interface methods, here one devises energy functionals
-involving the gradient and well-potentials of the phase field, and possibly
-long range interaction kernels, that yield approximate mathematical surfaces
-of almost arbitrary topology.
-Because the fluid interfaces are given by the level-set
-of a smooth function, the evolution equations
-can be studied by well-established tools like variational methods
-and regularity theory, and are amenable to numerical approximation.
-On the downside, granular details like the shape changes of a protein, for
-example, are clumsy to incorporate in the model.  Moreover, numerical
-simulations of phase field models typically discretize the entire fluid
-domain under consideration, and apply cutoff boundary conditions
-when periodic domains are not under consideration.
+approaches to self-organization in Applied Mathematics. Motivated by
+Ginzburg-Landau theory, these methods introduce a scalar-valued phase
+field function for the volume fraction of lipids and water in modeling
+vesicles membranes, for example. Sometimes called diffuse interface
+methods, one devises energy functionals involving the gradient and
+well-potentials of the phase field, and possibly long range interaction
+kernels, that yield approximate mathematical surfaces of almost
+arbitrary topology. Because the fluid interfaces are given by the
+level-set of a smooth function, the evolution equations can be studied
+by well-established tools like variational methods and regularity
+theory, and are amenable to numerical approximation. On the downside,
+granular details like the shape changes of a protein, for example, are
+clumsy to incorporate in the model. Moreover, numerical simulations of
+phase field models typically discretize the entire fluid domain under
+consideration, and apply cutoff boundary conditions when periodic
+domains are not under consideration.
 
@@
   \caption{\label{fig:flow_map} \footnotesize {\em Left:} In the HAP
-  formulation, a system of exterior problems defines the hydrodynamic
-  and hydrophobic interactions. {\em Right:} Particles translate and
-  rotate to lower the free energy $F[u]$ subject to \eqref{eq:SL}, $W(\phi)
-  = \phi^2$, and reach a minimal configuration in panel C. The colormap is
-  blue for $u = 0$ and red for $u = 1$. The arrows are the velocity
-  field $\mathbf{u}$.}
+  formulation~\cite{Fu2018_SIAM}, a system of exterior problems defines
+  the hydrodynamic and hydrophobic interactions. {\em Right:} Particles
+  translate and rotate to lower the free energy $E[u]$ subject
+  to~\eqref{eqn:phase}, $W(\phi) = \phi^2$, and reach a minimal
+  configuration in panel C. The colormap is blue for $\eta = 0$ and red
+  for $eta = 1$. The arrows are the velocity field $\uu$.}
 \end{figure}
@@
 model takes ideas from the phase field method and leverages boundary
-integral equations to speed up computations. To formulate the problem,
-consider a collection of $N_b$-many rigid bodies $U_i(t) \subset \mathbb{R}^n$
-with boundary $\Gamma_i(t)$.
-We call these bodies ``granules''.
-The granules are immersed 
-in an incompressible, zero-Reynolds number fluid
-$\Omega_t = \RR^n \setminus \cup_{i=1}^{N_b} U_i(t)$
-(Figure \ref{fig:flow_map}).
+integral equations to resolve complex domains and speed up computations.
+To formulate the problem, consider a collection of $N_b$-many rigid
+bodies $U_i(t) \subset RR^n$ with boundary $\Gamma_i(t)$. We call these
+bodies ``granules''. The granules are immersed in an incompressible,
+zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
+U_i(t)$ (Figure~\ref{fig:flow_map}).
 
 We look for $N_b$-many rigid body transformations
-\begin{equation}
+\begin{align}
 \label{eq:RBT}
 F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
-\end{equation}
-where $i = 1,\ldots,N_b,$
-$R_i(t)$ is a rotation (proper orthogonal) $n \times n$ matrix,
-$\aa_i(t)$ are the granule centers, and $\XX$ is a reference coordinate.
-The transformations \eqref{eq:RBT} tell us how the granules move through space.
-Throughout, $\nu$ refers to unit normal pointing into $\Omega(t)$ (Figure \ref{fig:flow_map}).
+\end{align}
+where $i = 1,\ldots,N_b,$ $R_i(t)$ is a rotation (proper orthogonal) $n
+\times n$ matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
+reference coordinate. The transformations~\eqref{eq:RBT} determine how
+the granules move through space. Throughout, $\nnu$ refers to unit
+normal pointing into $\Omega(t)$ (Figure~\ref{fig:flow_map}).
 
-The key idea is to define the dynamics using the following
-boundary value problem system:
+The key idea is to define the dynamics using the following boundary
+value problem system:
 \begin{alignat}{4}
+  \label{eqn:stokes} 
   -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
-  &&\quad \nabla \cdot \uu = 0, && \quad \xx \in \Omega_t, \label {eqn:stokes} \\
+  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
   \label{eqn:phase}
-  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, && &&\quad \xx \in \Omega_t,\\
+  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, && \xx \in \Omega(t),\\
   \label{eqn:noslip}        
-\frac{dF_i}{dt}(\XX,t) & = \uu(\xx) 
-&&=\vv_i + \omega_i \times (\xx - \aa_i), 
+  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
+    \vv_i + \omega_i \times (\xx - \aa_i), 
   &&\quad \xx \in \Gamma_i(t),\\
@@
 \end{alignat}
-for $i=1,\ldots,N_b$
-and where $\xx = F_i(\XX,t)$.
-Finally,
-\begin{equation}
+for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
+\begin{align}
 \label{eqn:stressbalance}
@@
 \int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
-\end{equation}
+\end{align}
 where
-\begin{equation}
+\begin{align}
 \label{eqn:hydro_stress}
@@
   \phi^T\right)\right]
-\end{equation}
-are the hydrodynamic and phase stresses, respectively; 
-$I$ is the $n\times n$ identity matrix.
-For vectors $\aa, \bb \in \mathbb{R}^2$,
-we follow the usual convention of defining
-the ``cross product'' as
-$\aa \times \bb = (\aa^{\perp} \cdot \bb) \kk$
-where $\kk = (0,0,1) \in \mathbb{R}^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$.
+\end{align}
+are the hydrodynamic and phase stresses, respectively; $I$ is the
+$n\times n$ identity matrix. For vectors $\aa, \bb \in \mathbb{R}^2$,
+we follow the usual convention of defining the ``cross product'' as $\aa
+\times \bb = (\aa^{\perp} \cdot \bb) \kk$ where $\kk = (0,0,1) \in
+\RR^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$.
 
-The above form a semi-linear elliptic 
-system for evolution of the granules.  Equations~\eqref{eqn:stokes} are the
-Stokes equations that describes the velocity $\uu$ and pressure $p$ of
-the aqueous region with viscosity $\mu$.  Equation~\eqref{eqn:phase} describes the
-phase transitions of the scalar order parameter $\phi$ with a decay
-length $\epsilon$.
-The scalar function $W(\phi)$ is a nonnegative
-well potential where the local 
-minimima represent metastable states $\phi_0,$ $\phi_1$ etc. of the water phase.
-To have finite bulk energy, the minimum potential phase
-$\phi_0$ has $W(\phi_0) = 0.$
-Mathematically, this order parameter is responsible for
-the attraction and adhesion between granules that want to align boundaries
-of like phase.
+The above form a semi-linear elliptic system for evolution of the
+granules. Equation~\eqref{eqn:stokes} is the Stokes equations that
+describes the velocity $\uu$ and pressure $p$ of the aqueous region with
+viscosity $\mu$. Equation~\eqref{eqn:phase} describes the phase
+transitions of the scalar order parameter $\phi$ with a decay length
+$\epsilon$. The scalar function $W(\phi)$ is a nonnegative well
+potential where the local minima represent metastable states $\phi_0,
+\phi_1,\ldots$ of the water phase. To have finite bulk energy, the
+minimum potential phase $\phi_0$ has $W(\phi_0) = 0$. Mathematically,
+this order parameter is responsible for the attraction and adhesion
+between granules that want to align boundaries of like phase.
 
 The next three equations are the moving domain boundary conditions.
-Equations~\eqref{eqn:noslip} specify a no-slip
-boundary condition for a rigid body with translation velocity $\aa'_i(t) = \vv_i$
-and angular velocity $\omega_i$
-about the point $\aa_i(t) \in U_i(t)$.
-($\omega_i$ is the axial vector of the
-skew symmetric matrix $R'_i(t)$.)
-In
+Equations~\eqref{eqn:noslip} specify a no-slip boundary condition for a
+rigid body with translation velocity $\aa'_i(t) = \vv_i$ and angular
+velocity $\omega_i$ about the point $\aa_i(t) \in U_i(t)$. ($\omega_i$
+is the axial vector of the skew symmetric matrix $R'_i(t)$.) In
 equation~\eqref{eqn:material}, the function $h_i$ is a material label
-specifying the phases at water-granule interface.
-The boundary condition for $\phi$ is transported by the flow
-and satisfies $\phi_t + \uu \cdot \nabla \phi = 0$ on $\Gamma_i$.
-Finally,
-equation~\eqref{eqn:stressbalance} closes the system by
-requiring that the force and torque generated by 
-hydrodynamic stress balances that generated by phase stress $T_i$ in
-\eqref{eqn:hydro_stress}.
-The parameter $\gamma > 0$ is surface tension.
+specifying the phases at water-granule interface. The boundary condition
+for $\phi$ is transported by the flow and satisfies $\phi_t + \uu \cdot
+\nabla \phi = 0$ on $\Gamma_i$. Finally,
+equation~\eqref{eqn:stressbalance} closes the system by requiring that
+the force and torque generated by hydrodynamic stress balances that
+generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
+parameter $\gamma > 0$ is surface tension.
 
 We call the rigid bodies $U_i(t)$ granules since they are small, compact
-parcels of a suspended media, e.g. lipids, Janus spheres.
-We use the shape and boundary conditions for $U_i$ to capture the local
-properties of the suspended media. 
-We have departed from the terminology ``particles'' here
-to emphasize the role played by their finite size. 
-In our simulations (see section \ref{sec:specific_aim1}),
-we include a finite length repulsion to avoid particle
-collisions.
+parcels of a suspended media, e.g.~lipids, Janus spheres. We use the
+shape and boundary conditions for $U_i$ to capture the local properties
+of the suspended media. We have departed from the terminology
+``particles'' to emphasize the role played by their finite size. In our
+simulations (see \S\ref{sec:specific_aim1}), we include a finite length
+repulsion to avoid particle collisions.
 
-In the absence of external flow,
-the system~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
-has the energy law
-\begin{equation}
+In the absence of external flow, the
+system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
+\begin{align}
 \label{eq:energy_law}
   \frac{d}{dt}E
-  = - \int_{\Omega_t}\tfrac{1}{2}\mu|\nabla \uu + \nabla
+  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
   \uu^T|^2 \,d\xx,\quad
-    E = \gamma \int_{\Omega_t}
+    E = \gamma \int_{\Omega(t)}
   \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
-\end{equation}
-Here $E$ is the energy stored in the phase transitions.
-Mathematically, the energy law states that changes
-in granule configuration instantaneously change the phase energy $E$.
-The dynamics are such that the change energy
-is lost due to hydrodynamic dissipation.
-Further details and generalizations are provided in
-the Specific Aim 1 section \ref{sec:specific_aim1}.
+\end{align}
+Here $E$ is the energy stored in the phase transitions. Mathematically,
+the energy law states that changes in granule configuration
+instantaneously change the phase energy $E$. The dynamics are such that
+the change energy is lost due to hydrodynamic dissipation. Further
+details and generalizations are provided in \S\ref{sec:specific_aim1}
+and \S\ref{sec:specific_aim_3}. Because $E$ depends both on $\phi$ and
+$\Omega(t)$, the derivation of~\eqref{eq:energy_law} is somewhat subtle
+and has been worked out in detail in~\cite{Fu2018_SIAM}. The
+calculation uses the Rayleigh Transport Theorem to write the time
+derivative of $E$ as an energy density flux involving the phase stress
+$T_i$ on the boundary, and a bulk term involving the Euler-Lagrange
+derivative of $E$. The Euler-Lagrange derivative vanishes due
+to~\eqref{eqn:phase} and the boundary flux transforms into viscous
+dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
 
-Because $E$ depends both on $\phi$ and $\Omega_t$,
-the derivation of \eqref{eq:energy_law}
-is somewhat subtle and has been worked out in detail in \cite{Fu2018_SIAM}.
-It goes as follows.
-Using the Rayleigh Transport Theorem, 
-the time derivative out $E$ yields an energy
-density flux involving the phase stress $T_i$
-at the boundary, plus a bulk term involving 
-the Euler-Lagrange derivative of $E.$
-The Euler-Lagrange derivative vanishes due to~\eqref{eqn:phase}
-and the boundary flux transforms into viscous dissipation due to 
-\eqref{eqn:hydro_stress} and the Stokes equations.
+%It goes as follows. Using the Rayleigh Transport Theorem, the time
+%derivative out $E$ yields an energy density flux involving the phase
+%stress $T_i$ at the boundary, plus a bulk term involving the
+%Euler-Lagrange derivative of $E$.
 
-In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$
-and for the background flow, we require that
-$\lim_{\xx \to \infty} \uu(\xx) - \uu_{\infty}(\xx) = \mathbf{0}.$ 
-In the case of shear background flow, for example,
-\begin{equation}
+In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
+background flow, we require that $\lim_{\xx \to \infty} \uu(\xx) -
+\uu_{\infty}(\xx) = \mathbf{0}$. In the case of shear background flow,
+for example,
+\begin{align}
 \label{eqn:shear_BG_flow}
 \uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
-\end{equation}
-where $\dot \gamma$ is the shear rate and
-$\mathbf{e}_x$, $\mathbf{e}_y$ are horizontal and vertical
-basis vectors, respectively.  Other background flows include
-extensional, parabolic Poiseuille, and Taylor-Green flow.
-For numerical stability and physical realism,
-we introduce pairwise repulsive forces and torques in \eqref{eqn:stressbalance}
-to prevent the collosion between neighboring granules.
-We include the repulsive potential in the energy law \eqref{eq:energy_law} 
-and refer to \cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM} for details.
-A background flow adds elastic energy to the granule configurations
-and is quantified by simulation.
+\end{align}
+where $\dot \gamma$ is the shear rate and $\mathbf{e}_x$, $\mathbf{e}_y$
+are horizontal and vertical basis vectors, respectively. Other
+background flows include extensional, parabolic Poiseuille, and
+Taylor-Green flow. For numerical stability and physical realism, we
+introduce pairwise repulsive forces and torques
+in~\eqref{eqn:stressbalance} to prevent the collision between
+neighboring granules. We include the repulsive potential in the energy
+law~\eqref{eq:energy_law}. A background flow adds elastic energy to the
+granule configurations and is quantified by simulation. We refer to the
+PIs work~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM} for details.
 
-In terms of physical justification, the
-derivation of the one-dimensional version of our model
-was carried out by \cite{MaRa76} and \cite{ErLjCl89}
-using a Landau expansion of the
-free energy density for a single-well potential.
-The double-well potential case was dealt with by
-Gompper in \cite{GoHaKo94} to describe metastable coordination of water.
-In the field of surface chemistry \cite{Israelachvili1954},
-there is a large empirical literature on properties of
-long-range hydrophobic interaction~\cite{LeRaPa77,KoNa15,
-Nagle17,Lum1999, Lin2005, Meyer2006, Ducker2016,Jackson2016,Gletal88,Aketal17,Ch05}.
-The stress~\eqref{eqn:stressbalance} was first
-identified by PIs Ryham and Young in~\cite{Fu2018_SIAM}
-and generalizes one-dimensional hydrophobic interaction to
-the $n$-dimensional setting.
+In terms of physical justification, the derivation of the
+one-dimensional version of our model was carried out using a Landau
+expansion of the free energy density for a single-well
+potential~\cite{MaRa76, ErLjCl89}. The double-well potential case was
+considered by Gompper~\cite{GoHaKo94} to describe metastable
+coordination of water. In the field of surface
+chemistry~\cite{Israelachvili1954}, there is a large empirical
+literature on properties of long-range hydrophobic
+interaction~\cite{LeRaPa77, KoNa15, Nagle17, Lum1999, Lin2005,
+Meyer2006, Ducker2016, Jackson2016, Gletal88, Aketal17, Ch05}. The
+stress~\eqref{eqn:stressbalance} was first identified by PIs Ryham and
+Young in~\cite{Fu2018_SIAM} and generalizes one-dimensional hydrophobic
+interaction to the $n$-dimensional setting.
 
-Finally, in terms of mathematical justifications, we mention
-that in the single-well case
-$W(\phi) = \tfrac{1}{2}\phi^2,$ \eqref{eqn:phase} takes the form
-of a screened Laplace (SL) equation $-\epsilon^2 \Delta \phi + \phi =0$.
-For a fixed domain $\Omega$ with class $\mathbf{C}^2$ boundary \cite{},
-if the material label $h_i = 1$ everywhere, then $\phi$
-has a boundary layer going from $1$ at the boundary to $0$ in the bulk
-and one can prove that 
-\begin{equation}
+Finally, in terms of mathematical justifications, we mention that in the
+single-well case $W(\phi) = \tfrac{1}{2}\phi^2$, equation
+\eqref{eqn:phase} takes the form of a screened Laplace equation
+$-\epsilon^2 \Delta \phi + \phi =0$. For a fixed domain $\Omega$ with
+class $\mathbf{C}^2$ boundary~\cite{}, if the material label $h_i = 1$
+everywhere, then $\phi$ has a boundary layer going from $1$ at the
+boundary to $0$ in the bulk and one can prove that 
+\begin{align}
 \label{eqn:math_motivation}
 \lim_{\epsilon \to 0} E = \frac{\gamma}{2} \int_{\partial \Omega} 1 \,dS.
-\end{equation}
-In other words, the phase energy can be viewed as an
-approximation of surface energy that ``extends'' into the bulk.
-In the general case, $h_i^2$ replaces $1$ in \eqref{eqn:math_motivation}.
-We are confident that \eqref{eq:RBT}--\eqref{eqn:stressbalance}
-is a correct description of long-range interactions between granule
-surfaces.
+\end{align}
+In other words, the phase energy can be viewed as an approximation of
+surface energy that ``extends'' into the bulk. In the general case,
+$h_i^2$ replaces $1$ in~\eqref{eqn:math_motivation}. We are confident
+that~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is a correct description
+of long-range interactions between granule surfaces.
 
@@
   \vspace{-5pt}
-  \caption{\footnotesize \label{fig:self-assembly2} Rows (a)-(c) have
+  \caption{\footnotesize \label{fig:self-assembly2} Rows (a)--(c) have
   the same initial configuration but different boundary conditions $g$.
-  In row (a), self-assembly with an amphiphilic boundary condition
+  {Top Row:} Granules with an amphiphilic boundary condition
   results in a bilayer pattern shielding the hydrophobic core (yellow,
-  $u > 0$) from the aqueous phase (blue, $u = 0$). Row (b) shows
-  particles with a hydrophobic intensity that is greater on one side of
-  the particle (magenta) than the other (yellow). In row (c), green is
-  for $u < 0$, yellow is for $u > 0$, and blue is for $u = 0$. Particles
-  orient like sides to form a checkerboard pattern.}
+  $\eta > 0$) from the aqueous phase (blue, $\eta = 0$). {\em Middle
+  Row:} Biased granules with a hydrophobic intensity that is greater on
+  one side of the particle (magenta) than the other (yellow). {\em
+  Bottom Row:} Bipolar granules where green is for $\eta < 0$, yellow is
+  for $\eta > 0$, and blue is for $\eta = 0$. Particles orient like
+  sides to form a checkerboard pattern.}
 \end{wrapfigure}
+
 \subsection{Applications}
-Since the formulation is scale independent,
-it can be applied broad range of
-nonspecific self-organization
-phenomena in surface chemistry, biology and engineering.
-For one,
-the formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures
-exactly the right behavior expected from amphiphilic self-assembly.
-For example, three bodies with amphiphilic label
-(see section \ref{sec:specific_aim1}) spontaneously
-self-organize to sequester the hydrophobic fluid phase
-(the red phase in Figure \ref{fig:flow_map}).
-Moreover, a simple change of boundary conditions from
-amphiphilic, to biased hydrophobic, to polar results in distinct
-equilibrium morphologies (Figure~\ref{fig:self-assembly2}).
-(i)
-Chemistry: Janus spheres
-Since the formulation is
-scale independent, it can represent a suspension of amphiphiles, where
-the granules represent the mean properties of a small collection of
-lipids, at the nanoscopic scale. For larger scales, the representation
-is literal and the granules Janus spheres.
-(ii) Pickering emulsion 
-(iii) Bertozzi's problem
-(iv) Tension driven microprinting
-(v) Vesicle hydrodynamics.
+Since the formulation is scale independent, it can be applied broad
+range of nonspecific self-organization phenomena in surface chemistry,
+biology and engineering. For one, the
+formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
+the right behavior expected from amphiphilic self-assembly. For example,
+three bodies with amphiphilic label (\S\ref{sec:specific_aim1})
+spontaneously self-organize to sequester the hydrophobic fluid phase
+(the red phase in Figure~\ref{fig:flow_map}).  Moreover, a simple change
+of boundary conditions from amphiphilic, to biased hydrophobic, to polar
+results in distinct equilibrium morphologies
+(Figure~\ref{fig:self-assembly2}). (i) Chemistry: Janus spheres Since
+the formulation is scale independent, it can represent a suspension of
+amphiphiles, where the granules represent the mean properties of a small
+collection of lipids, at the nanoscopic scale. For larger scales, the
+representation is literal and the granules Janus spheres. (ii) Pickering
+emulsion (iii) \todo[inline]{Bertozzi's problem} (iv) Tension driven
+microprinting (v) Vesicle hydrodynamics.
 
@@
 \subsection{Boundary integral formulation}
+\todo[inline]{Bryan left off here}
 \label{sec:bie}

### 2022-11-10 NSF2022/Description/specificaim2.tex
changes to  background

@@
 
-\begin{wrapfigure}[]{r}{2.1in}
+\begin{wrapfigure}[]{l}{2.1in}
   \centering
-  \input{figures/near_sing.tikz}
-  \caption{\label{fig:interpquad} An interpolation-based quadrature
-  method that works in two and three dimensions. The spectrally-accurate
-  trapezoid rule is used in points in $\mathtt{Far}(\Gamma_i)$, while
-  one dimensional interpolant is used for points in
-  $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength spacing.}
+  \includegraphics[width=2in]{figures/SA2Figures/confinement.pdf}
+  \caption{\label{fig:stenosis} A granule-based vesicle passing through
+  a constricted geometry.}
 \end{wrapfigure}
@@
 media~\cite{chi-moo-qua2020, dea-qua-bir-jua2018, moo-che-chi-qua2022,
-qua-gan-you2021}.
-
-When granules are close to one another, which is inevitable in dense and
-confined suspensions, the resulting integrals are nearly-singular. This
-issue is well-known in the IE community and several algorithms have been
-developed in the last 30 years, including panel-based
-methods~\cite{helsing_2008a, helsing_tutorial_2012}, Quadrature by
-Expansions (QBX)~\cite{din-hua-mar-tan2021, klo-bar-gre-one2013,
-ste-bar2022, af2018sisc}, Barycentric-type formulae for Cauchy
-integrals~\cite{bar2014, bar-wu-vee2015, ioa-pap-per1991}, and
-interpolation-based methods~\cite{ying_2006, qua-bir2014,
+qua-gan-you2021}. The strong confinement introduces an aditional
+computational challenge---acuartely computing integrals between
+nearly-touching bodies. This issue is well-known in the IE community and
+several algorithms have been developed in the last 30 years, including
+panel-based methods~\cite{helsing_2008a, helsing_tutorial_2012},
+Quadrature by Expansions (QBX)~\cite{din-hua-mar-tan2021,
+klo-bar-gre-one2013, ste-bar2022, af2018sisc}, Barycentric-type formulae
+for Cauchy integrals~\cite{bar2014, bar-wu-vee2015, ioa-pap-per1991},
+and interpolation-based methods~\cite{ying_2006, qua-bir2014,
 rah-vee-zor-bir2015} (Figure~\ref{fig:interpquad}). The proposed
@@
 
-In two-dimensions, analytic function theory can be used to derive a
-quadrature method whose error is uniformly bounded~\cite{bar2014,
-bar-wu-vee2015, ioa-pap-per1991}, but these works only show how to apply
-the method to the two-dimensional Laplace and Stokes equations. PI BQ
-recently showed that these quadrature methods can be extended to other
-PDEs with singularity subtraction~\cite{che-lin-her-qua2022}. For
-example, the fundamental solution of the screened Laplace
-equation~\eqref{eqn:phase} involves the modified Bessel function of the
-second kind, $K_0(\|\xx - \yy\|)$. The behavior of this function as $\yy
-\rightarrow \xx$ is $K_0(\alpha \|\xx - \yy\|) = \log\|\xx - \yy\| +
-S(\xx - \yy)$, where $S(\xx - \yy)$ is continuously differentiable. This
-suggests a quadrature scheme for where the aforementioned quadrature
-method is applied to the $\log\|\xx - \yy\|$ kernel, and high-order
-methods~\cite{tre-wei2014} are applied to integrals involving the smooth
-kernel $S(\xx - \yy)$.Similar techniques, which they call subtraction
-techniques, have been considered by Camille Carvalho and her
-colleagues~\cite{car2021, car2020, car-kha-kim2018}. These methods are
-particularly powerful when computing gradients of layer potentials which
-is required, for example, when computing the water-order
-stress~\eqref{eqn:stressbalance}.
+\begin{wrapfigure}[]{r}{2.1in}
+  \centering
+  \input{figures/near_sing.tikz}
+  \caption{\label{fig:interpquad} An interpolation-based quadrature
+  method that works in two and three dimensions. The spectrally-accurate
+  trapezoid rule is used in points in $\mathtt{Far}(\Gamma_i)$, while
+  one dimensional interpolant is used for points in
+  $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength spacing.}
+\end{wrapfigure}
 
-In three dimensions, the quadrature methods are much more challenging.
-Singularity subtraction methods can be applied, but analytic function
-theory is no longer applicable. Singularity subtraction methods have
-been applied using, for example, smoothed variations of
-the~\cite{beale1, cor2001, tlu-bea2019}. Alternatively, efficient
-quadrature methods can be applied directly to accurately compute
-singular and near-singular integrals~\cite{khayat_2005,
-gimbutas2013sisc}. However, since we are interested in round (2D) and
-spherical (3D) granules, we will exploit the fact that integrals can be
-computed exactly after transforming the integrals to to a Fourier (2D)
-or spherical harmonic (3D) basis. This technique can be used to evaluate
-layer potentials for both Stokes~\cite{cor-vee2018} and the screened
-Laplace equation~\cite{koh-cor-che-vee2021}.
+Since we are interested in round (2D) and spherical (3D) granules, we
+will exploit the fact that integrals can be computed with spectral
+accuracy by transforming the integrals to to a Fourier (2D) or spherical
+harmonic (3D) basis. This technique can be used to evaluate layer
+potentials for both Stokes~\cite{cor-vee2018} and the screened Laplace
+equation~\cite{koh-cor-che-vee2021}. However, for other elliptical and
+other shapes, an alternative approach is necessary. The Barycentric-type
+formulae for Cauchy integrals results in a uniformly bounded quadrature
+error, but the method is described only for the two-dimensional Laplace
+and Stokes equations. PI Quaife recently showed that these quadrature
+methods can be extended to other two-dimensional
+PDEs~\cite{che-lin-her-qua2022}. The method uses singularity subtraction
+write the fundamental solution of the PDE as a sum of two terms: a
+logarithmic function and a continuously differentiable function. Then
+the Barycentric-type formulae can be applied to the logarithmic
+function, and the standard trapezoid rule~\cite{tre-wei2014} can be
+applied to the other function. These singularity subtraction methods can
+also accurately compute derivatives of layer potentials~\cite{car2021,
+car2020, car-kha-kim2018} which is required, for example, when computing
+the water-order stress~\eqref{eqn:stressbalance}. Quadrature is much
+more challenging in three dimensions. Singularity subtraction methods
+can be applied, but not combined with Barycentric-type formulae.
+Alternatively, smoothed variations of the fundamental solution can be
+used to address nearly-singular integrals~\cite{beale1, cor2001,
+tlu-bea2019}.  Alternatively, efficient quadrature methods can be
+applied directly to accurately compute singular and near-singular
+integrals~\cite{khayat_2005, gimbutas2013sisc}.
 
@@
 (FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2, fmm3, fmm4, fmm6,
-fmm7, ros-ols2016}. PI BQ is experienced with applying FMMs for the
+fmm7, ros-ols2016}. PI Quaife is experienced with applying FMMs for the
 Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the screened
@@
 
-%
-%Furthermore, to reduce the
-%number of GMRES iterations, the efficacy of preconditioning strategies
-%such as the inverse Fast Multipole Method (IFMM)~\cite{cou-pou-dar2017}
-%and domain decomposition~\cite{che-bir2021} will be investigated. PI BQ
-%used the IFMM to precondition Stokes equations~\cite{qua-cou-dar2018}. A
-%suite of other preconditioners including sparse approximate
-%inverses~\cite{che2000} and multigrid~\cite{hem-sch1981, sch1982} will
-%be investigated.
-
-% ----------------------------------------------------------------------
-\subsubsection{Incorporating confinement}
-\label{subsec:Confinement}
-
-% ----------------------------------------------------------------------
-\subsubsection{Collision-aware suspensions with adaptive time stepping}
-\label{subsec:timeStepping}
-
-A numerical issue when simulating the self-assembly of amphiphilic
-particles is avoiding particle collision. The hydrophobic attraction
-potential drives the amphiphilic particles towards one another and this
-leads to physical contact in finite time. Such particle collisions in a
-dense, rigid-body suspension are a great challenge and can be a
-bottleneck in large-scale simulations. We propose to remedy this
-computational challenge by developing novel high-order adaptive time
-stepping methods. PI BQ developed a high-order adaptive time
-stepping method for hydrodynamic suspensions \cite{qua-bir2016}, and it
-has served as a robust method to simulate processes including mixing and
-adhesion in suspensions~\cite{qua-vee-you2019, kab-qua-bir2017}.
-Following this previous work, the proposed work will use a spectral
-deferred correction method~\cite{dut-gre-rok2000} since it iteratively
-applies a low-order, single-step method to achieve high-order accuracy.
-At each time step, we will compute the total force and torque of the
-system which is computationally cheap and physically zero, and therefore
-provides an estimate of the local truncation error. PI BQ's experience
-is that error estimates based on physical constraints, such as force-
-and torque-free conditions, appropriately determine adaptive time step
-sizes so that the dynamics are resolved without the computational
-expense of embedded Runge-Kutta methods, step-doubling, Richardson
-extrapolation.
+While the inclusion of high-order quadrature and fast methods is
+necessary to simulate dense suspensions, an additional reqired
+computational tool is a collision-aware adaptive time stepping method.
+The order parameter results in the granules attracting one another and
+this leads to physical contact in finite time. Our current
+implementation uses a repulsive Lennard-Jones force, but this introduces
+stiffness, thereby requiring small time steps, and this can be a
+bottleneck when simulating dense suspensions. Therefore, we will develop
+a high-order collision-avoiding adaptive time stepping method. This
+method will avoid collisions with by using the minimal separation
+distance to impose a non-overlapping constraint. This results in a
+linear complementarity problem that can be solve efficiently with a
+projected gradient descent method~\cite{Yan2019}. High-order time
+adaptivity will be based on PI Quaife's previous work on
+suspensions~\cite{qua-bir2016}, and this method has proven to be a
+robust method to simulate dense suspensions~\cite{qua-vee-you2019,
+kab-qua-bir2017, qua-gan-you2022}. Following this previous work, the
+proposed work will use a spectral deferred correction method since it
+iteratively applies a low-order, single-step method to achieve
+high-order accuracy. At each time step, we will compute the total force
+and torque of the system which is computationally cheap and physically
+zero, and therefore provides an estimate of the local truncation error.
+PI Quaife's experience is that error estimates based on physical
+constraints, such as force- and torque-free conditions, appropriately
+determine adaptive time step sizes so that the dynamics are resolved
+without the computational expense of techniques such as embedded
+Runge-Kutta, step-doubling, and Richardson extrapolation.

### 2022-11-11 NSF2022/Description/backgroundv2.tex

@@
 \label{sec:bie}
-\begin{wrapfigure}[10]{r}{2in}
-  \todo[inline]{A figure comparing FEM versus BIE meshes}
-  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
-  requires meshing the entire domain (typically into triangles), while a
-  BIE only requires meshing the boundary of the domain.}
-\end{wrapfigure}
 The solution of PDEs in a domain surrounding a mobile, dense suspension
@@
 \begin{align*}
-  \uu(\xx) = \int_{\partial\Omega_t} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
+  \uu(\xx) = \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
 \end{align*}
 where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
-fundamental solution and $\ssigma: \partial \Omega_t \rightarrow \RR^2$
+fundamental solution and $\ssigma: \partial \Omega(t) \rightarrow \RR^2$
 is an unknown density function. The BIE reformulation has several
 immediate advantages including a dimension reduction since $\ssigma$ is
-defined only on $\partial \Omega_t$, and the far field boundary
+defined only on $\partial \Omega(t)$, and the far field boundary
 condition of the PDE is automatically satisfied. The density
@@
   \gg(\xx) = \lambda \ssigma(\xx) + 
-    \int_{\partial\Omega_t} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
-    \quad \xx \in \partial\Omega_t,
+    \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
+    \quad \xx \in \partial\Omega(t),
 \end{align*}
@@
 
+\begin{wrapfigure}[]{l}{2.1in}
+  \centering
+  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
+  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
+  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
+  ({\em left}) requires meshing the entire domain (typically into
+  triangles), while a BIE ({\em right}) requires meshing only the
+  boundary of the domain.}
+\end{wrapfigure}
+
 A consequence of the dimension reduction in a BIE formulation is that
 complex geometries are much easier to resolve than a mesh-based method
-since only $\partial \Omega_t$ needs to be discretized
+since only $\partial \Omega(t)$ needs to be discretized
 (Figure~\ref{fig:fem_vs_bie}). Additional advantages of a BIE

### 2022-11-11 NSF2022/Description/specificaim2.tex
working on SA2

@@
 ability to resolve complex unbounded domains and achieve high-order
-accuracy, integral equation methods will be a central theme of the
-computational tools. As discussed in Section~\ref{sec:bie}, numerical
-methods to solve IEs have several advantages over their PDE-based
-counterpart. The PIs have demonstrated that IEs are a powerful tool to
-simulate two-dimensional suspensions of amphiphilic
-particles~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022}, and
-elements of these formulations have been developed in three
-dimensions~\cite{ying_2006, manasthesis, rac-gre2016}. In our current
-implementation, we can simulate $\mathcal{O}(100)$ two-dimensional
-granules, and the proposed research will allow for the suspensions with
-100X--1000X more two-dimensional granules and $\mathcal{O}(1000)$
-three-dimensional granules.
+accuracy, integral equations (IEs) will be a central theme of the
+computational tools.
 
@@
 solvent phase $\Omega(t)$. For the single-well $W(\phi) = \phi^2$,
-equation~\eqref{eqn:phase} is linear, and the PIs have demonstrated that
-IEs are a powerful tool to solve for the order
-parameter~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022}. However,
-for a general double-well potential $W(\phi)$, the resulting PDE is
-nonlinear, motivating the following problem:
+equation~\eqref{eqn:phase} is linear, and the PIs have used IEs to solve
+for the order parameter~\cite{Fu2018_SIAM, FuQuRyYo22,
+fu-ryh-qua-you2022}. However, for a double-well potential $W(\phi)$, the
+resulting PDE is nonlinear, motivating the following problem:
 
@@
   \noindent
-  \textbf{Problem 3.} How can IEs be coupled with a Newton solver to
+  \textbf{Problem 4.} How can IEs be coupled with a Newton solver to
   solve the non-linear PDE~\eqref{eqn:phase}?
@@
 
-The PIs have developed numerical methods to solve~\eqref{eqn:phase} when
-$W(\phi) = \phi^2$---this choice results in the linear screened Laplace
-equation. For a general double well potential $W$ with local minima at
-$\phi_0$ and $\phi_1$, we propose to interpret the solution as the root
-finding problem for
+For a general double-well potential $W(\phi)$ with local minima at
+$\phi_0$ and $\phi_1$, we propose to interpret the solution
+of~\eqref{eqn:phase} as a root finding problem for
 \begin{align}
@@
 is challenging with an integral equation since a fundamental solution is
-not readily available. However, by choosing a double well potential with
+not readily available. However, by choosing a double-well potential with
 $W''(\phi_0) = W''(\phi_1) = \beta$, we propose to instead use an
@@
 dimension, it will be coupled with IE formulations to
-solve~\eqref{eqn:phase} in two and three dimensions. The solution of
+solve~\eqref{eqn:phaseRoot} in two and three dimensions. The solution of
 $-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = F[\phi^N]$ can be written
@@
 to compute than layer potentials, but new methods have recently been
-developed that allows them to be computed accurately and
+developed that allow them to be computed accurately and
 efficiently~\cite{fry-leh-tor2018, and-zhu-vee2022}. This approach of
 combining volume and layer potentials has successfully been used by PI
-BQ~\cite{kro-qua2010} and others~\cite{fry-kro-tor2019, kli-ask-kro2020,
-che-hua-lei2005}.
+Quaife~\cite{kro-qua2010} and others~\cite{fry-kro-tor2019,
+kli-ask-kro2020, che-hua-lei2005} in other contexts, such as time
+stepping.
+
+As discussed in Section~\ref{sec:bie},
+numerical methods to solve IEs have several advantages over their
+PDE-based counterpart. The PIs have demonstrated that IEs are a powerful
+tool to simulate two-dimensional suspensions of amphiphilic
+particles~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022}, and
+elements of these formulations have been developed in three
+dimensions~\cite{ying_2006, manasthesis, rac-gre2016}. In our current
+implementation, we simulate $\mathcal{O}(100)$ two-dimensional granules,
+and the proposed research will allow for the suspensions with
+100X--1000X more two-dimensional granules and $\mathcal{O}(1000)$
+three-dimensional granules.
+
 % ----------------------------------------------------------------------
@@
   \noindent
-  \textbf{Problem 4.} How can novel quadrature, time adaptivity, fast
+  \textbf{Problem 5.} How can novel quadrature, time adaptivity, fast
   summation, and collision-detection be combined to accurately and
@@
   \includegraphics[width=2in]{figures/SA2Figures/confinement.pdf}
-  \caption{\label{fig:stenosis} A granule-based vesicle passing through
-  a constricted geometry.}
+  \caption{\label{fig:stenosis} \footnotesize A granule vesicle passing
+  through a constricted geometry.}
 \end{wrapfigure}
@@
 media~\cite{chi-moo-qua2020, dea-qua-bir-jua2018, moo-che-chi-qua2022,
-qua-gan-you2021}. The strong confinement introduces an aditional
-computational challenge---acuartely computing integrals between
-nearly-touching bodies. This issue is well-known in the IE community and
-several algorithms have been developed in the last 30 years, including
+qua-gan-you2021}.
+
+The confinement introduces an additional computational
+challenge---accurately computing integrals between nearly-touching
+bodies. This issue is well-known in the IE community and several
+algorithms have been developed in the last 30 years, including
 panel-based methods~\cite{helsing_2008a, helsing_tutorial_2012},
@@
   \input{figures/near_sing.tikz}
-  \caption{\label{fig:interpquad} An interpolation-based quadrature
-  method that works in two and three dimensions. The spectrally-accurate
-  trapezoid rule is used in points in $\mathtt{Far}(\Gamma_i)$, while
-  one dimensional interpolant is used for points in
-  $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength spacing.}
+  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
+  quadrature method that works in two and three dimensions. The
+  spectrally-accurate trapezoid rule is used in points in
+  $\mathtt{Far}(\Gamma_i)$, while one dimensional interpolant is used
+  for points in $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength
+  spacing.}
 \end{wrapfigure}
@@
 robust method to simulate dense suspensions~\cite{qua-vee-you2019,
-kab-qua-bir2017, qua-gan-you2022}. Following this previous work, the
+kab-qua-bir2017, qua-gan-you2021}. Following this previous work, the
 proposed work will use a spectral deferred correction method since it

### 2022-11-11 NSF2022/Description/specificaim2.tex
cleaned up BIE section a bit

@@
 computational tools.
+
+To briefly describe IE formulations of PDEs, we consider the Stokes
+equation~\eqref{eqn:stokes} as an example. Its solution can be written
+as a convolution 
+\begin{align*}
+  \uu(\xx) = \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
+\end{align*}
+where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
+fundamental solution and $\ssigma: \partial \Omega(t) \rightarrow \RR^2$
+is an unknown density function. The IE reformulation has several
+immediate advantages including a dimension reduction since $\ssigma$ is
+defined only on $\partial \Omega(t)$, and the far field boundary
+condition of the PDE is automatically satisfied. The density
+function $\ssigma$ is chosen to satisfy the boundary condition, and this
+results in a IE 
+\begin{align*}
+  \gg(\xx) = \lambda \ssigma(\xx) + 
+    \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
+    \quad \xx \in \partial\Omega(t),
+\end{align*}
+where $\gg$ is the Dirichlet boundary condition, and $\lambda$ is a
+constant that depends on the choice of $G$. For numerical stability,
+choices of $G$ that result in second-kind Fredholm integral equations,
+meaning $\lambda \neq 0$, are preferred.
 

### 2022-11-11 NSF2022/Description/backgroundv2.tex

@@
 To formulate the problem, consider a collection of $N_b$-many rigid
-bodies $U_i(t) \subset RR^n$ with boundary $\Gamma_i(t)$. We call these
+bodies $U_i(t) \subset \RR^n$ with boundary $\Gamma_i(t)$. We call these
 bodies ``granules''. The granules are immersed in an incompressible,
@@
 repulsion to avoid particle collisions.
+
+The solution of the PDEs~\eqref{eqn:stokes} and~\eqref{eqn:phse} is
+challenging because of the complex and unbounded domain. Even more
+troubling is when dense suspensions are considered. Integral equation
+methods offer an alternative formulation of the PDEs that only require
+meshing the boundary of the granules rather than all of $\Omega(t)$
+(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a IE formulation
+includes a discretization that is high-order, or even spectrally,
+accurate; results in a well-conditioned linear system that can be solved
+iteratively with a mesh-independent number of iterations of a Krylov
+method such as the generalized minimal residual method (GMRES). However,
+IEs do have several challenges: nearly touching granules requires a
+quadrature rule for nearly-singular integrals; their discretization
+results in dense matrices; and they cannot immediately be applied to
+non-linear PDEs. The IE community, including PI Quaife, has developed a
+variety of tools to address these numerical challenges, and we discuss
+our planned approach in Section~\ref{sec:specificaim2}.
+
+\begin{wrapfigure}[]{l}{2.1in}
+  \centering
+  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
+  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
+  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
+  ({\em left}) requires meshing the entire domain (typically into
+  triangles), while a BIE ({\em right}) requires meshing only the
+  boundary of the domain.}
+\end{wrapfigure}
 
@@
 microprinting (v) Vesicle hydrodynamics.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Boundary integral formulation}
-\todo[inline]{Bryan left off here}
-\label{sec:bie}
-The solution of PDEs in a domain surrounding a mobile, dense suspension
-of bodies is highly nontrivial and requires accurate,
-dimension-reducting discretization
-that do not require continual remeshing.  
-Boundary integral equations (BIEs) are a reformulation of elliptic PDEs
-including the Stokes equation~\eqref{eqn:stokes} and the phase
-equation~\eqref{eqn:phase} in the special case of $f(u) =
-\tfrac{1}{2}u^2$. Using the Stokes equation as an example, its solution
-can be written as a convolution 
-\begin{align*}
-  \uu(\xx) = \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
-\end{align*}
-where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
-fundamental solution and $\ssigma: \partial \Omega(t) \rightarrow \RR^2$
-is an unknown density function. The BIE reformulation has several
-immediate advantages including a dimension reduction since $\ssigma$ is
-defined only on $\partial \Omega(t)$, and the far field boundary
-condition of the PDE is automatically satisfied. The density
-function $\ssigma$ is chosen to satisfy the boundary condition, and this
-results in a BIE 
-\begin{align*}
-  \gg(\xx) = \lambda \ssigma(\xx) + 
-    \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
-    \quad \xx \in \partial\Omega(t),
-\end{align*}
-where $\gg$ is the Dirichlet boundary condition, and $\lambda$ is a
-constant that depends on the choice of $G$. For numerical stability,
-choices of $G$ that result in second-kind Fredholm integral equations,
-meaning $\lambda \neq 0$, are preferred.
-
-\begin{wrapfigure}[]{l}{2.1in}
-  \centering
-  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
-  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
-  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
-  ({\em left}) requires meshing the entire domain (typically into
-  triangles), while a BIE ({\em right}) requires meshing only the
-  boundary of the domain.}
-\end{wrapfigure}
-
-A consequence of the dimension reduction in a BIE formulation is that
-complex geometries are much easier to resolve than a mesh-based method
-since only $\partial \Omega(t)$ needs to be discretized
-(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a BIE
-formulation includes a discretization that is high-order, or even
-spectrally, accurate; results in a well-conditioned linear system that
-can be solved iteratively with a mesh-independent number of iterations
-of a Krylov method such as the generalized minimal residual method
-(GMRES). However, BIEs do have several challenges: nearly touching
-granules requires a quadrature rule for nearly-singular integrals; their
-discretization results in dense matrices; and they cannot immediately be
-applied to non-linear PDEs. The BIE community, including PI Quaife, has
-developed a variety of tools to address these numerical challenges, and
-we discuss our planned approach in Section~\ref{sec:specificaim2}.
 

### 2022-11-11 NSF2022/Description/specificaim1v2.tex
SA1 body done; new refs

--- 2022-11-10 NSF2022/Description/specificaim1v2.tex
@@
 \label{sec:specific_aim1}
+We introduced \eqref{eq:RBT}--\eqref{eqn:stressbalance} to complement
+existing methods for studing vesicles and bilayers. 
+The simulations results in \S \ref{sec:vesicles_as_granules}
+show that two-dimensional, granule-based vesicles replicate the 
+equilibria and hydrodynamics for continuous curves.
+Having shown that the model is effective in terms of simulation,
+our next goal is to study the model using rigorous analysis
+and consider three-dimensionsional effects.
 
-We introduced \eqref{eq:RBT}--\eqref{eqn:stressbalance} to overcome the challenges faced by
-traditional Helfrich-type models of elastic membranes.
-We have compared two-dimensional configurations of amphiphilic granules
-to membrane configurations found in continuum mechanics.
-The simulations results in~\cite{Fu2018_SIAM,FuQuRyYo22}
-showed that the granular bilayers 
-basically replicated the elastic energies for bending, tilt, and
-stretching.
-The hydrodynamics of the Janus particle vesicle is similar to the behaviour of an inextensible,
-elastic vesicle membrane with permeability.
-The model has reached sufficient maturity to warrant 
-rigorous studies in analysis.
+The first step is to obtain some solid well-posedness results
+for \eqref{eq:RBT}--\eqref{eqn:stressbalance}.
+This system is an autonomous ordinary differential equation for
+rigid body transformations $F_i$.  The right-hand side of this
+equation is defined by a system of PDE.  In the single-well case,
+\eqref{eqn:phase} is a linear equation
+and for fixed $t$ there is a unique solution
+($\phi, \uu$) for the interactions under appropriate
+assumptions for the boundaries and boundary data
+\cite{manasthesis,rac-gre2016,LAX}.
+This leads to 
+\begin{quotation}
+  \textbf{Problem 1.} 
+  Consider a collection the closed, disjoint granules
+  $U_i$ with smooth boundary, with no-slip, rigid body
+  motion boundary conditions, and a linear background flow.
+  Assume a single-well potential and a smooth phase field
+  boundary condition.  Study the well-posedness in
+  time of the coupled system \eqref{eq:RBT}--\eqref{eqn:stressbalance}.
+\end{quotation}
+Problem 1 involves mathematically interesting techniques.
+First, we must establish that the system has a local-in-time solution.
+This involves domain perturbations and estimates for the
+solutions of second order elliptic equations
+\cite{Savar2002DomainPA, DANERS20081, Lamboley2015EstimatesOF},
+which also find extensive application in extremal domain problems
+\cite{Schiffer1954VariationOD, Henrot2006ExtremumPF,
+  bogosel:hal-03607776,Bogosel2022OnTP}, for example.
+For global-in-time solutions,
+we can ensure positivity in time for the distance between granules
+using the fluid mechanical principle of
+lubrication forces \cite{cawthorn_balmforth_2010, leal_2007}.
+Finally, we can describe the granule-flow
+behavior in the limit zero screening length limit.
 
-A natural questions concerns the well-posedness
-\eqref{eq:RBT}--\eqref{eqn:stressbalance}
-and its generalizations. A recent and strongly developing direction in
+In the double-well potential case, \eqref{eqn:phase}
+is a nonlinear Allen-Cahn
+equation.
+This situation models granules immersed in a two-phase fluid
+(e.g. granules in an emulsion) 
+where there is an interesting interplay
+(1) the long-range alignment of granules with (2) 
+the diffusive interface energy of the free boundary
+between fluid phases.
+On unbounded domains like $\Omega(t)$,
+Allen-Cahn equations can have multiple of solutions
+\cite{Alama1997StationaryLS,Alikakos2008OnAE,Bronsard1993OnTB,
+  Byeon2014SolutionsOH, Byeon2013OnAP, Alessio2005ENTIRESI,
+  Trumper2007ExistenceOA} and so we must reformulate
+\eqref{eqn:phase} so that $\phi$ is well-defined.
+A natural modification changes
+\eqref{eqn:phase} to an initial value problem with
+transport by the background fluid;
+\begin{equation}
+  \label{eqn:phase_transport}
+  \phi_t + \uu \cdot \nabla
+  = -\lambda \frac{\delta E}{\delta \phi}
+  =  \lambda(\epsilon^2 \Delta \phi - W'(\phi)),
+  \quad \phi(\xx,0) = \phi_0(\xx),
+\end{equation}
+for initial data $\phi_0$.
+The modified systems enjoys energy law similar to \eqref{eq:energy_law} 
+with an addtional dissipation term involving the square 
+the Euler-Lagrange derivative $\frac{\delta E}{\delta \phi}$ and dampening factor $\lambda > 0$.
+There are several works dealing with the
+geometric characterization of the geometric evolution
+of interfaces under the Allen-Cahn and Cahn-Hilliard equations
+\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF, Dai2019WeakSF,
+  Promislow2017ExistenceBA, Dai2015CompetitiveGE, Promislow2012CriticalPO,
+  Dai2022GeometricEO, Dai2020MinimizersFT,Dai2013GeometricEO,Promislow2022UndulatedBI} and
+well-posedness when coupled to flow in static domains
+\cite{Jiang2017TwophaseIF, Liu2012StrongSF, Giorgini2019WellPosednessOA,
+Wu2022WellposednessOA, Gal2010AsymptoticBO,
+Giorgini2020DiffuseIM,Giorgini2019UniquenessAR}.
+The proposed research extends these results to
+problems with moving domains.
+
+A closely related and strongly developing direction in
 the area of nematics liquid crystals concerns the interaction of
-Landau de Gennes functionals like \eqref{eq:energy_law} with colloids
-\cite{doi:10.1098/rsta.2020.0432}.
-In this spirit, a first step to understand the effect of the flow
-in our model is to obtain some solid well-posedness results.
+Landau de Gennes functionals with colloids, and studies
+the qualitative structure of defects around single or multiple
+coloidal particles
+\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT, Alama2021SaturnRD, PhysRevE.96.042702}.
 
+The second problem considers the approximation
+of equilibrium elastic energy of curves and surfaces,
+and seeks to make rigorous the simulation results of
+\S \ref{sec:vesicles_as_granules}.
 \begin{quotation}
-  \textbf{Problem 1.} Consider a collection the closed,
-  disjoint granules $U_i$ with smooth boundary,
-with no-slip, rigid body motion boundary conditions.
-Assume a either a single or double well potential
-and a smooth phase field boundary condition.  
-Study the well-posedness of the coupled system
-\eqref{eq:RBT}--\eqref{eqn:stressbalance}
-for short times.  For global in time solutions, determine
-whether lubrication forces ensure positive distance
-between granules.  Describe the behaviour in the limit
-zero screening length limit.  
+\textbf{Problem 2.} Place a collection of
+two-dimensional amphiphilic granules along a curve $\mathcal{C}$.
+Study the sharp interface limit of the energy $E$ 
+as the number of granules goes to infinity and their size to zero.
+\end{quotation}
+Problems like these have been addressed for bulk nematic liquid
+crystal potentials in the area of colloidal homogenization
+\cite{Canevari2019DesignOE,doi:10.1137/18M1163919,doi:10.1137/18M1163919,
+  BERLYAND200597,doi:10.1137/130910348},
+and is closely related to 
+dimension reduction for curved nematics confined to thin films
+\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,
+doi:10.1142/S0218202516500470, FoFrLe07}.
+Given the relatively complicated geometry consising
+of a plane with a number of disjoint disks removed, 
+we start by assuming that the directors are normal to the curve
+and that the granules are all disks with radius proportional to $\epsilon$. 
+The bending $k_B$ and stretching $k_A$ coefficients
+depend on the granual size relative to their spacing.
+We can then generalize the problem to account for aspect ratio of
+elliptical granules and nonzero tilt.
+
+Finally, to consider three-dimensionsional effects, we
+will generalize Problem 2 to \emph{numerically}
+study the energies of amphiphilic granules confined to surfaces.
+Recent work on nematics on a surface has studied
+the interplay between 
+surface geometry and a director field
+\cite{Nestler2020PropertiesOS, Nitschke2018NematicLC,
+  Nestler2018OrientationalOO, Nitschke2019HydrodynamicII,
+  Nitschke2020LiquidCO}.
+Researchers have formulated finite element methods for
+\cite{Bartels2012FiniteEM, Nochetto2015NumericsFL,
+  Nestler2019AFE}
+  and studied minimizers
+\cite{Segatti2014EquilibriumCO,Segatti2014AnalysisOA}.
+On the other hand, in biophysics,
+\cite{Hamm2000ElasticEO,Terzi2019CurvatureTiltTO,Terzi2019ACQ,Terzi2017NovelTC}
+and most recently \cite{Pinigin2020NewCT}
+derived an elastic energy for lipid bilayers,
+the generalized Helfrich energy.
+This energy involves the lipid director $\dd$,
+tilt vector $\mathbf{T}$, and area per lipid $\alpha$,
+and coupling terms and contains
+the Helfrich elastic energy \eqref{eq:Canham-Helfrich}
+as a special case.
+\begin{quotation}
+\textbf{Problem 3.}
+Simulate surfaces made up of three-dimensional, amphilic granules.
+Do you recover the generalized Helfrich elastic energy
+or related Landau deGennes energies for large $N_b$ simulations?
 \end{quotation}
 
-This problem is attractive because combines the diffusive interface
-effects involving a free boundary in aqueous part of the region \cite{}.
-The well-posedness of Allen-Cahn-type equations is well-established in the
-literature.  What makes this challening, though, is that
-the moving domain means the function space for the solution,
-a Sobolov space, is also changing with time.
-On ther other hand, the problem \eqref{eq:RBT}--\eqref{eqn:stressbalance}
-is an autonmous ordinary differential equation for rigid body transformations.
-The right-hand side of this equation is defined by a system of elliptic
-PDE.  On the other hand, several methods have been developed for
-analysing the smooth domain dependence of solutions to elliptic PDE,
-especially in the study of eigenvalue problems, for example.
-It is conceivable that moving domain estimates can be applied to the
-present problem to exhibit locally Lipschitz dependence on
-the rigid deformations.
+The completion of Problems 1, 2, and especially 3 
+requires additional algorithmic implementation including a
+fast summation method such as the fast multipole method.
+The implementation details, especially how we deal with large
+granule numbers and three-dimensional systems, are
+described in \S \ref{sec:specificaim2} Specific Aim 2.
 
-Generalizations of Problem 1 include modifying the 
-system to account for various time scales.
-We may consider, for example, modifying \eqref{eqn:phase}
-to include transport of the phase field by the background fluid;
-\begin{equation*}
-\phi_t + \uu \cdot \nabla = -\lambda \frac{\delta E}{\delta \phi} = \lambda(\epsilon^2 \Delta \phi - W'(\phi))
-\end{equation*}
-The modified systems enjoys the same energy law as \eqref{eq:energy_law} 
-except that there will be an addtional dissipation term coming from the
-Euler-Lagrange derivative $\frac{\delta E}{\delta \phi}$.
-(DEFINE $\lambda$)
+PI Ryham has made fundamental contributions to interface modeling in
+membrane biology.  His first works include
+phase field formulations for the elastic bending energy \cite{0951-7715-18-3-016,Du05} and topological indicators \cite{DuEuler} of vesicle membranes
+and fluid-vesicle interactions \cite{QiangDu09}.
+In his much noticed Biophysical Journal
+and Nature papers~\cite{RyKlYaCo16,Chetal16}, Ryham and collaborators 
+calculated, for the first time, a least energy path for membrane fusion.
 
-The second problem we consider concerns the approximation
-of equilibrium elastic energy of curves and surfaces.
-To understand the approximation mathematically, we take the following:
-\begin{quotation}
-  \textbf{Problem 2.} Place a collection of
-  amphiphilic granules
-with equally spaced centers along a curve $\mathcal{C}$.
-For simplicity, assume that the directors are normal to the curve
-and that the granules are all disks with radius proportional to $\epsilon$. 
-Study the sharp interface limit of the energy $E$ 
-relative to that of an array of granules placed along a flat curve. 
-In this limit, the number of granules $N_b$ goes to infinity
-to ensure equal spacing.
-Study how the bending the bending $k_B$ and stretching $k_A$ coefficients
-depend on the granual size relative to their spacing.
-Generalize the problem to account for aspect ratio of elliptical granules
-and nonzero tilt. 
-\end{quotation}
-Given the relatively complicated geometry consising
-of a plane with a number of disjoint disks removed, 
-we can start by approaching the problem in a simplified
-setting such as when the reference curve is a circle.
-There is a large body work in this direction for nematics
-studying either the case of a single coloidal particle and
-the qualitative structure of defects around it
-\cite{Alama2015MinimizersOT, Alama2021SaturnRD, PhysRevE.96.042702}
-many particles and the homogenization effects
-\cite{Canevari2019DesignOE,doi:10.1137/18M1163919,doi:10.1137/18M1163919,BERLYAND200597,doi:10.1137/130910348}.
-A closely related area that consider similar analysis
-dimension reduction for
-Landau-de Gennes models on curved nematic confined to thin films
-\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,doi:10.1142/S0218202516500470, FoFrLe07}.
-
-We conclude this section by highlighting another well-developed
-area connected to our approach.  Surface-director models 
-considers the energy of a nematic liquid crystal on a surface to study how the
-surface geometry effects the director field and vice versa. Researchers
-have formulated finite element methods for [][] and studied the existence
-of minimizers []-[].
-Liquid crystals are an extremely well-studied are in mathematics [].
-
-On the other hand, in biophysics, tilt is defined by the tilt vector
-  $\TT = \dd/\dd\cdot \NN - \NN$ so that the tilt energy density
-  behaves like $\tan^2 \theta$ rather than $\sin^2 \theta$.
-  These two energies densities are, however, asymptotically equal
-  for small deformations.
-Hamm and Kozlov [] and later Terzi and Deserno [], Pinigen et al. []
-showed that the full Helfrich elastic energy of a \emph{monolayer} takes the form
-\begin{equation}
-\label{eq:Helfrich}
-  \begin{aligned}
- &\int_{\Sigma}
-  %\label{eq:Pinigan}
-\tfrac{1}{2}k_{b}[(\nabla \cdot \mathbf{d} + k_{0})^{2} -  k^{2}_{0}]  
-+ \tfrac{1}{2}k_{\theta}\mathbf{T}^{2} + \tfrac{1}{2}k_a[(\alpha - \alpha_0)^2 - \alpha_0^2] \\
-&+ k_{c}\textbf{T} \cdot \nabla \nabla \cdot \mathbf{d}  + \tfrac{1}{2}k_{g}(\nabla \nabla \cdot \mathbf{d})^{2}
- + A\alpha \nabla \cdot \mathbf{d}
-+ B \mathbf{T} \cdot \nabla \alpha \\
-&- \tfrac{1}{2}k_c |\nabla \alpha|^2 + C \nabla \alpha \cdot \nabla \nabla \cdot \mathbf{d}\,dS
-\end{aligned}
-\end{equation}
-where $\nabla$ and $\nabla \cdot$ are the surface gradient and surface divergence,
-respectively, and $k_B$, $k_{\theta}$, $k_a$, $k_c$, $k_g$, $A$, $B$, $C$ are
-appropriate elastic moduli.  An important and consequential distinction between
-\eqref{eq:Canham-Helfrich} is the presence of the terms $\mathbf{T}$ and $\alpha$.
-These are, respectively, the \emph{tilt} vector $\mathbf{T}$ measuring
-the difference between the lipid director $\mathbf{d}$ and the surface normal
-$\mathbf{N}$; the \emph{area per lipid} $\alpha$ area density at rest $\alpha_0$.
-The two models \eqref{eq:Canham-Helfrich} and \eqref{eq:Helfrich} agree
-when $\mathbf{T} = 0$ and $\alpha = \alpha_0$ everywhere.
-
-(MAKE CONNECTION WITH SPECIFIC AIM 2)
-(PLAN B)
-(SHORTER PROBLEM STATEMENT; ADDRESS IN PARAGRAPH)
-
-%\setcounter{page}{1}
-%\addcontentsline{toc}{section}{Bibliography}
-%\bibliographystyle{abbrvnat}
-%%
-%\bibliography{refs}
-%
-%
-%
-%\end{document}
+%\begin{equation}
+%\label{eq:Helfrich}
+%  \begin{aligned}
+% &\int_{\Sigma}
+%  %\label{eq:Pinigan}
+%\tfrac{1}{2}k_{b}[(\nabla_{\Sigma} \cdot \mathbf{d} + k_{0})^{2} -  k^{2}_{0}]  
+%+ \tfrac{1}{2}k_{\theta}\mathbf{T}^{2} + \tfrac{1}{2}k_a[(\alpha - \alpha_0)^2 - \alpha_0^2] \\
+%&+ k_{c}\textbf{T} \cdot \nabla_{\Sigma} \nabla_{\Sigma} \cdot \mathbf{d}  + \tfrac{1}{2}k_{g}(\nabla_{\Sigma} \nabla_{\Sigma} \cdot \mathbf{d})^{2}
+% + A\alpha \nabla_{\Sigma} \cdot \mathbf{d}
+%+ B \mathbf{T} \cdot \nabla_{\Sigma} \alpha \\
+%&- \tfrac{1}{2}k_c |\nabla_{\Sigma} \alpha|^2 + C \nabla_{\Sigma} \alpha \cdot \nabla_{\Sigma} \nabla_{\Sigma} \cdot \mathbf{d}\,dS
+%\end{aligned}
+%\end{equation}
+%in the lipid director $\dd$,
+%tilt vector $\mathbf{T}$
+%the difference between the lipid director $\mathbf{d}$ and the surface normal
+%$\mathbf{N}$; area per lipid $\alpha$,
+%and where $\nabla$ and $\nabla \cdot$ are the surface gradient and surface divergence, respectively. 
+%The two models \eqref{eq:Canham-Helfrich} and \eqref{eq:Helfrich} agree
+%when $\mathbf{T} = 0$ and $\alpha = \alpha_0$ everywhere.
+%The remaining term $k_B$, $k_{\theta}$, $k_a$, $k_c$, $k_g$, $A$, $B$, $C$ are
+%appropriate elastic moduli.

### 2022-11-11 NSF2022/Description/backgroundv2.tex
wrapped up first draft of SA2

@@
   \label{eqn:phase}
-  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, && \xx \in \Omega(t),\\
+  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
   \label{eqn:noslip}        
@@
     \vv_i + \omega_i \times (\xx - \aa_i), 
-  &&\quad \xx \in \Gamma_i(t),\\
+  \quad &&\xx \in \Gamma_i(t),\\
   \label{eqn:material}
-  \phi(\xx) &= h_i(\XX), &&  &&\quad \xx \in \Gamma_i(t),
+  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
 \end{alignat}
@@
 
-The solution of the PDEs~\eqref{eqn:stokes} and~\eqref{eqn:phse} is
-challenging because of the complex and unbounded domain. Even more
-troubling is when dense suspensions are considered. Integral equation
-methods offer an alternative formulation of the PDEs that only require
-meshing the boundary of the granules rather than all of $\Omega(t)$
-(Figure~\ref{fig:fem_vs_bie}). Additional advantages of a IE formulation
-includes a discretization that is high-order, or even spectrally,
-accurate; results in a well-conditioned linear system that can be solved
-iteratively with a mesh-independent number of iterations of a Krylov
-method such as the generalized minimal residual method (GMRES). However,
-IEs do have several challenges: nearly touching granules requires a
-quadrature rule for nearly-singular integrals; their discretization
-results in dense matrices; and they cannot immediately be applied to
-non-linear PDEs. The IE community, including PI Quaife, has developed a
-variety of tools to address these numerical challenges, and we discuss
-our planned approach in Section~\ref{sec:specificaim2}.
-
 \begin{wrapfigure}[]{l}{2.1in}
@@
 \end{wrapfigure}
+
+Computational methods to solve the PDEs~\eqref{eqn:stokes}
+and~\eqref{eqn:phase} are challenging to develop because of the complex
+and unbounded domain. This challenge is compounded when dense
+suspensions are considered. Integral equations (IEs) offer an
+alternative formulation of the PDEs that only require meshing the
+boundary of the granules rather than all of $\Omega(t)$
+(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
+conditions. Additional advantages of an discretizations of IE
+formulations include high-order, or even spectral, accuracy and
+well-conditioned linear system that can be solved iteratively with a
+mesh-independent number of Krylov iterations such as the generalized
+minimal residual method (GMRES). However, IEs have challenges: nearly
+touching granules requires a quadrature rule for nearly-singular
+integrals; their discretization results in dense matrices; and they
+cannot immediately be applied to non-linear PDEs. The IE community,
+including PI Quaife, has developed a variety of tools to address these
+numerical challenges, and we discuss our planned approach in
+Section~\ref{sec:specificaim2}.
 
@@
 details and generalizations are provided in \S\ref{sec:specific_aim1}
-and \S\ref{sec:specific_aim_3}. Because $E$ depends both on $\phi$ and
-$\Omega(t)$, the derivation of~\eqref{eq:energy_law} is somewhat subtle
-and has been worked out in detail in~\cite{Fu2018_SIAM}. The
+and \S\ref{subsec:specific_aim_3}. Because $E$ depends both on $\phi$
+and $\Omega(t)$, the derivation of~\eqref{eq:energy_law} is somewhat
+subtle and has been worked out in detail in~\cite{Fu2018_SIAM}. The
 calculation uses the Rayleigh Transport Theorem to write the time

### 2022-11-12 NSF2022/Description/specificaim2.tex

@@
 accuracy, integral equations (IEs) will be a central theme of the
-computational tools.
+computational framework.
 
@@
 function $\ssigma$ is chosen to satisfy the boundary condition, and this
-results in a IE 
+results in an IE 
 \begin{align*}
@@
 \end{align*}
-where $\gg$ is the Dirichlet boundary condition, and $\lambda$ is a
-constant that depends on the choice of $G$. For numerical stability,
-choices of $G$ that result in second-kind Fredholm integral equations,
-meaning $\lambda \neq 0$, are preferred.
+where $\gg$ is the boundary condition, and $\lambda$ is a constant that
+depends on the choice of $G$. For numerical stability, choices of $G$
+that result in second-kind Fredholm integral equations, meaning $\lambda
+\neq 0$, are preferred.
+
+The PIs have demonstrated that IEs are a powerful tool to simulate
+two-dimensional suspensions of amphiphilic particles~\cite{Fu2018_SIAM,
+FuQuRyYo22, fu-ryh-qua-you2022}, and elements of these formulations have
+been developed in three dimensions~\cite{ying_2006, manasthesis,
+rac-gre2016}. In our current implementation, we simulate
+$\mathcal{O}(100)$ two-dimensional granules, and the proposed research
+will allow for the suspensions with 100X--1000X more two-dimensional
+granules and $\mathcal{O}(1000)$ three-dimensional granules.
+
+% ----------------------------------------------------------------------
+\begin{quotation}
+  \noindent
+  \textbf{Problem 4.} How can novel quadrature, time adaptivity, fast
+  summation, and collision-detection be combined to accurately and
+  efficiently solve the governing
+  equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} with dense
+  suspensions of two- and three-dimensional granules in bounded and
+  unbounded domains?
+\end{quotation}
+
+\begin{wrapfigure}[]{l}{2.1in}
+  \centering
+  \includegraphics[width=2in]{figures/SA2Figures/confinement.pdf}
+  \caption{\label{fig:stenosis} \footnotesize A granule vesicle passing
+  through a constricted geometry.}
+\end{wrapfigure}
+
+In experiments, it is known that interactions between bounding walls and
+granules cannot be ignored~\cite{qua-gan-you2021,
+KaouiHartingMisbah2011_PRE, her-sto-gra2005}. Therefore, the necessary
+modification to the code will be implemented so that confinement can be
+considered. This modification requires introducing an additional layer
+potential on the bounding walls, and elements of this modification have
+already been incorporated (Figure~\ref{fig:stenosis}). However, to
+consider rheological properties of the suspensions, a periodic domain,
+such as a Couette device, will be considered. Such multiply-connected
+domains require additional modifications to the IE formulation. PI
+Quaife has considered suspensions with confinement for several projects
+including dynamic suspensions~\cite{qua-bir2014, bys-sha-qua2020} and
+porous media~\cite{chi-moo-qua2020, dea-qua-bir-jua2018,
+moo-che-chi-qua2022, qua-gan-you2021}.
+
+The confinement introduces an additional computational
+challenge---accurately computing integrals between nearly-touching
+bodies. This issue is well-known in the IE community and several
+algorithms have been developed in the last 30 years, including
+panel-based methods~\cite{helsing_2008a, helsing_tutorial_2012},
+Quadrature by Expansions (QBX)~\cite{din-hua-mar-tan2021,
+klo-bar-gre-one2013, ste-bar2022, af2018sisc}, Barycentric-type formulae
+for Cauchy integrals~\cite{bar2014, bar-wu-vee2015, ioa-pap-per1991},
+and interpolation-based methods~\cite{ying_2006, qua-bir2014,
+rah-vee-zor-bir2015} (Figure~\ref{fig:interpquad}). The proposed
+research, which is described next, will combine several methods
+including singularity subtraction, analytic function theory, and
+analytic methods.
+
+\begin{wrapfigure}[]{r}{2.1in}
+  \centering
+  \input{figures/near_sing.tikz}
+  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
+  quadrature method that works in two and three dimensions. The
+  spectrally-accurate trapezoid rule is used in points in
+  $\mathtt{Far}(\Gamma_i)$, while one dimensional interpolant is used
+  for points in $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength
+  spacing.}
+\end{wrapfigure}
+
+Since we are interested in round (2D) and spherical (3D) granules, we
+will exploit the fact that integrals can be computed with spectral
+accuracy by transforming the integrals to to a Fourier (2D) or spherical
+harmonic (3D) basis. This technique can be used to evaluate layer
+potentials for both Stokes~\cite{cor-vee2018} and the screened Laplace
+equation~\cite{koh-cor-che-vee2021}. However, this quadrature is not
+appropriate or other shapes, and an alternative approach is necessary.
+The Barycentric-type formulae for Cauchy integrals results in a
+uniformly bounded quadrature error, but the method is described only for
+the two-dimensional Laplace and Stokes equations. PI Quaife recently
+showed that these quadrature methods can be extended to other
+two-dimensional PDEs~\cite{che-lin-her-qua2022}. The method uses
+singularity subtraction write the fundamental solution of the PDE as a
+sum of two terms: a logarithmic function and a continuously
+differentiable function. Then the Barycentric-type formulae can be
+applied to the logarithmic function, and the standard trapezoid
+rule~\cite{tre-wei2014} can be applied to the other function. These
+singularity subtraction methods can also accurately compute derivatives
+of layer potentials~\cite{car2021, car2020, car-kha-kim2018} which is
+required, for example, when computing the water-order
+stress~\eqref{eqn:stressbalance}. Singularity subtraction methods can
+also be applied in three dimensions, but not combined with
+Barycentric-type formulae. Alternatively, smoothed variations of the
+fundamental solution can be used to address nearly-singular
+integrals~\cite{beale1, cor2001, tlu-bea2019}. Alternatively, efficient
+quadrature methods can be applied directly to accurately compute
+singular and near-singular integrals~\cite{khayat_2005,
+gimbutas2013sisc}.
+
+Another facet to consider when choosing the quadrature rule is its
+ability to be applied efficiently. Since carefully chosen IE
+formulations require a mesh-independent number of GMRES
+iterations~\cite{cam-ips-kel-mey-xue1996}, the required CPU time is
+proportional to the cost of a matrix-vector multiplication that can be
+performed in optimal or near-optimal time with the fast multipole method
+(FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2, fmm3, fmm4, fmm6,
+fmm7, ros-ols2016}. PI Quaife is experienced with applying FMMs for the
+Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the screened
+Laplace equation~\cite{kro-qua2011, qua2011}. Many of these methods rely
+on analytic expansions of the PDE's fundamental solution, but recent
+work has demonstrated that a kernel-independent method applied to
+suspensions of 80,000 spheres can be simulated with only $\sim$10
+seconds per time step on 1792 compute cores~\cite{Yan2019}.
+
+While the inclusion of high-order quadrature and fast methods is
+necessary to simulate dense suspensions, an additional required
+computational tool is a collision-aware adaptive time stepping method.
+The order parameter results in the granules attracting one another and
+this leads to physical contact in finite time. Our current
+implementation uses a repulsive Lennard-Jones force, but this introduces
+stiffness, thereby requiring small time steps, and this can be a
+bottleneck when simulating dense suspensions. Therefore, we will develop
+a high-order collision-avoiding adaptive time stepping method. This
+method will avoid collisions with by using the minimal separation
+distance to impose a non-overlapping constraint. This results in a
+linear complementarity problem that can be solve efficiently with a
+projected gradient descent method~\cite{Yan2019}. High-order time
+adaptivity will be based on PI Quaife's previous work on
+suspensions~\cite{qua-bir2016}, and this method has proven to be a
+robust method to simulate dense suspensions~\cite{qua-vee-you2019,
+kab-qua-bir2017, qua-gan-you2021}. Following this previous work, the
+proposed work will use a spectral deferred correction method since it
+iteratively applies a low-order, single-step method to achieve
+high-order accuracy. At each time step, we will compute the total force
+and torque of the system which is computationally cheap and physically
+zero, and therefore provides an estimate of the local truncation error.
+PI Quaife's experience is that error estimates based on physical
+constraints, such as force- and torque-free conditions, appropriately
+determine adaptive time step sizes so that the dynamics are resolved
+without the computational expense of techniques such as embedded
+Runge-Kutta, step-doubling, and Richardson extrapolation.
 
@@
   \input{figures/doublewell.tikz} 
-  \caption{\label{fig:CA} \footnotesize (a) A double well potential. (b)
+  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
   The solution of the one-dimensional phase
@@
 The order parameter is governed by the PDE~\eqref{eqn:phase} in the
-solvent phase $\Omega(t)$. For the single-well $W(\phi) = \phi^2$,
+solvent phase $\Omega(t)$. If $W(\phi) = \phi^2$,
 equation~\eqref{eqn:phase} is linear, and the PIs have used IEs to solve
 for the order parameter~\cite{Fu2018_SIAM, FuQuRyYo22,
-fu-ryh-qua-you2022}. However, for a double-well potential $W(\phi)$, the
+fu-ryh-qua-you2022}, but for a double-well potential $W(\phi)$, the
 resulting PDE is nonlinear, motivating the following problem:
@@
   \noindent
-  \textbf{Problem 4.} How can IEs be coupled with a Newton solver to
+  \textbf{Problem 5.} How can IEs be coupled with a Newton solver to
   solve the non-linear PDE~\eqref{eqn:phase}?
@@
 Equation~\eqref{eqn:phaseRoot} will be solved with Newton's method,
-$\phi^{N+1} = \phi^{N} - \alpha (dF^N)^{-1} F(\phi^N)$, where $dF^N =
--\epsilon^2 \Delta + \tfrac{1}{2}W''(\phi^N)$ is the Fr\'{e}chet
-derivative of $F$, and $\alpha$ is the step size that will be determined
-using backtracking. This requires solving the variable coefficient PDE
-$-\epsilon^2 \Delta v + \tfrac{1}{2}W''(\phi^{N}) v = F[\phi^N]$, which
-is challenging with an integral equation since a fundamental solution is
-not readily available. However, by choosing a double-well potential with
-$W''(\phi_0) = W''(\phi_1) = \beta$, we propose to instead use an
-inexact Newton's method where $dF^{-1}$ is approximated with the
-solution of $-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = F[\phi^N]$. We
-test the efficacy of the exact and inexact Newton's method applied
-to~\eqref{eqn:phaseRoot} in $(0,1) \subset \RR$ by discretizing $dF$
-with a second-order finite difference stencil. The double well potential
-is illustrated in Figure~\ref{fig:CA}(a), and both the exact and inexact
-Newton's methods converge to the solution in Figure~\ref{fig:CA}(b).
+$\phi^{N+1} = \phi^{N} - \alpha (F'(\phi^N))^{-1} F(\phi^N)$, where
+$F'(\phi^N) = -\epsilon^2 \Delta + \tfrac{1}{2}W''(\phi^N)$ is the
+Fr\'{e}chet derivative of $F$, and $\alpha$ is the step size that will
+be determined using backtracking. This requires solving the variable
+coefficient PDE $-\epsilon^2 \Delta v + \tfrac{1}{2}W''(\phi^{N}) v =
+F[\phi^N]$, which is challenging with an integral equation since a
+fundamental solution is not readily available. However, by choosing a
+double-well potential with $W''(\phi_0) = W''(\phi_1) = \beta$, we
+propose to instead use an inexact Newton's method where $F^{-1}$ is
+approximated with the solution of $-\epsilon^2 \Delta v +
+\tfrac{\beta}{2} v = F[\phi^N]$. We test the efficacy of the exact and
+inexact Newton's method applied to~\eqref{eqn:phaseRoot} in $(0,1)
+\subset \RR$ by discretizing $F'$ with a second-order finite difference
+stencil. The double-well potential is illustrated in
+Figure~\ref{fig:CA}(a), and both the exact and inexact Newton's methods
+converge to the solution in Figure~\ref{fig:CA}(b).
 Figure~\ref{fig:CA}(c) shows the norm of the residual at each Newton
@@
 stepping.
-
-As discussed in Section~\ref{sec:bie},
-numerical methods to solve IEs have several advantages over their
-PDE-based counterpart. The PIs have demonstrated that IEs are a powerful
-tool to simulate two-dimensional suspensions of amphiphilic
-particles~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022}, and
-elements of these formulations have been developed in three
-dimensions~\cite{ying_2006, manasthesis, rac-gre2016}. In our current
-implementation, we simulate $\mathcal{O}(100)$ two-dimensional granules,
-and the proposed research will allow for the suspensions with
-100X--1000X more two-dimensional granules and $\mathcal{O}(1000)$
-three-dimensional granules.
-
-% ----------------------------------------------------------------------
-\begin{quotation}
-  \noindent
-  \textbf{Problem 5.} How can novel quadrature, time adaptivity, fast
-  summation, and collision-detection be combined to accurately and
-  efficiently solve the governing
-  equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} in bounded and
-  unbounded domains in two and three dimensions?
-\end{quotation}
-
-\begin{wrapfigure}[]{l}{2.1in}
-  \centering
-  \includegraphics[width=2in]{figures/SA2Figures/confinement.pdf}
-  \caption{\label{fig:stenosis} \footnotesize A granule vesicle passing
-  through a constricted geometry.}
-\end{wrapfigure}
-
-In experiments, it is known that interactions between bounding walls and
-granules cannot be ignored~\cite{qua-gan-you2021,
-KaouiHartingMisbah2011_PRE, her-sto-gra2005}. Therefore, the necessary
-modification to the code will be performed so that confinement can be
-considered. This modification requires introducing an additional layer
-potential on the bounding walls, and elements of this modification have
-already been incorporated (Figure~\ref{fig:stenosis}). However, to
-consider rheological properties of the suspensions, a periodic domain,
-such as a Couette device, will be considered. This multiply-connected
-domain requires additional modifications. PI Quaife has considered
-suspensions with confinement for several projects including dynamic
-suspensions~\cite{qua-bir2014, bys-sha-qua2020} and porous
-media~\cite{chi-moo-qua2020, dea-qua-bir-jua2018, moo-che-chi-qua2022,
-qua-gan-you2021}.
-
-The confinement introduces an additional computational
-challenge---accurately computing integrals between nearly-touching
-bodies. This issue is well-known in the IE community and several
-algorithms have been developed in the last 30 years, including
-panel-based methods~\cite{helsing_2008a, helsing_tutorial_2012},
-Quadrature by Expansions (QBX)~\cite{din-hua-mar-tan2021,
-klo-bar-gre-one2013, ste-bar2022, af2018sisc}, Barycentric-type formulae
-for Cauchy integrals~\cite{bar2014, bar-wu-vee2015, ioa-pap-per1991},
-and interpolation-based methods~\cite{ying_2006, qua-bir2014,
-rah-vee-zor-bir2015} (Figure~\ref{fig:interpquad}). The proposed
-research, which is described next, will combine several methods
-including singularity subtraction, analytic function theory, and
-spherical basis representations.
-
-\begin{wrapfigure}[]{r}{2.1in}
-  \centering
-  \input{figures/near_sing.tikz}
-  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
-  quadrature method that works in two and three dimensions. The
-  spectrally-accurate trapezoid rule is used in points in
-  $\mathtt{Far}(\Gamma_i)$, while one dimensional interpolant is used
-  for points in $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength
-  spacing.}
-\end{wrapfigure}
-
-Since we are interested in round (2D) and spherical (3D) granules, we
-will exploit the fact that integrals can be computed with spectral
-accuracy by transforming the integrals to to a Fourier (2D) or spherical
-harmonic (3D) basis. This technique can be used to evaluate layer
-potentials for both Stokes~\cite{cor-vee2018} and the screened Laplace
-equation~\cite{koh-cor-che-vee2021}. However, for other elliptical and
-other shapes, an alternative approach is necessary. The Barycentric-type
-formulae for Cauchy integrals results in a uniformly bounded quadrature
-error, but the method is described only for the two-dimensional Laplace
-and Stokes equations. PI Quaife recently showed that these quadrature
-methods can be extended to other two-dimensional
-PDEs~\cite{che-lin-her-qua2022}. The method uses singularity subtraction
-write the fundamental solution of the PDE as a sum of two terms: a
-logarithmic function and a continuously differentiable function. Then
-the Barycentric-type formulae can be applied to the logarithmic
-function, and the standard trapezoid rule~\cite{tre-wei2014} can be
-applied to the other function. These singularity subtraction methods can
-also accurately compute derivatives of layer potentials~\cite{car2021,
-car2020, car-kha-kim2018} which is required, for example, when computing
-the water-order stress~\eqref{eqn:stressbalance}. Quadrature is much
-more challenging in three dimensions. Singularity subtraction methods
-can be applied, but not combined with Barycentric-type formulae.
-Alternatively, smoothed variations of the fundamental solution can be
-used to address nearly-singular integrals~\cite{beale1, cor2001,
-tlu-bea2019}.  Alternatively, efficient quadrature methods can be
-applied directly to accurately compute singular and near-singular
-integrals~\cite{khayat_2005, gimbutas2013sisc}.
-
-Another facet to consider when choosing the quadrature rule is its
-ability to be applied efficiently. Since carefully chosen IE
-formulations require a mesh-independent number of GMRES
-iterations~\cite{cam-ips-kel-mey-xue1996}, the required CPU time is
-proportional to the cost of a matrix-vector multiplication that can be
-performed in optimal or near-optimal time with the fast multipole method
-(FMM)~\cite{fmm5} and its extensions~\cite{fmm1, fmm2, fmm3, fmm4, fmm6,
-fmm7, ros-ols2016}. PI Quaife is experienced with applying FMMs for the
-Stokes equation~\cite{qua-bir2014, bys-sha-qua2020} and the screened
-Laplace equation~\cite{kro-qua2011, qua2011}. Many of these methods rely
-on analytic expansions of the PDE's fundamental solution, but recent
-work has demonstrated that a kernel-independent method applied to
-suspensions of 80,000 spheres can be simulated with only $\sim$10
-seconds per time step on 1792 compute cores~\cite{Yan2019}.
-
-While the inclusion of high-order quadrature and fast methods is
-necessary to simulate dense suspensions, an additional reqired
-computational tool is a collision-aware adaptive time stepping method.
-The order parameter results in the granules attracting one another and
-this leads to physical contact in finite time. Our current
-implementation uses a repulsive Lennard-Jones force, but this introduces
-stiffness, thereby requiring small time steps, and this can be a
-bottleneck when simulating dense suspensions. Therefore, we will develop
-a high-order collision-avoiding adaptive time stepping method. This
-method will avoid collisions with by using the minimal separation
-distance to impose a non-overlapping constraint. This results in a
-linear complementarity problem that can be solve efficiently with a
-projected gradient descent method~\cite{Yan2019}. High-order time
-adaptivity will be based on PI Quaife's previous work on
-suspensions~\cite{qua-bir2016}, and this method has proven to be a
-robust method to simulate dense suspensions~\cite{qua-vee-you2019,
-kab-qua-bir2017, qua-gan-you2021}. Following this previous work, the
-proposed work will use a spectral deferred correction method since it
-iteratively applies a low-order, single-step method to achieve
-high-order accuracy. At each time step, we will compute the total force
-and torque of the system which is computationally cheap and physically
-zero, and therefore provides an estimate of the local truncation error.
-PI Quaife's experience is that error estimates based on physical
-constraints, such as force- and torque-free conditions, appropriately
-determine adaptive time step sizes so that the dynamics are resolved
-without the computational expense of techniques such as embedded
-Runge-Kutta, step-doubling, and Richardson extrapolation.

### 2022-11-12 NSF2022/Description/backgroundv2.tex
BG mods

@@
 
-Mathematical models of self-organization encompasses a broad range of
-interesting and challenging phenomena. For example, understanding the
+Self-organization encompasses a broad range of
+interesting and challenging phenomena in engineering and science.
+For example, understanding the
 organization of lipids and proteins in vesicles is crucial to design
-effective drug and vaccine carriers. The COVID-19 pandemic has led to an
-unprecedented and concerted worldwide effort in biophysical modeling of
-the mechanisms of RNA condensation by structural proteins, protein
-oligomerization, and cellular membrane–protein interactions that
-ultimately control virus structure, in an effort to curtail pathogens
-like the Severe Acute Respiratory Syndrome Coronavirus 2. Using powerful
-capillary and van der Waals forces that exist at the nanoscale,
-engineers have developed superior techniques to print high-resolution,
-nanoscale features on devices like sensors, lasers, and LEDs. Finally,
-researchers have introduced data-driven methods to study complex
-patterns that emerge in particle and agent-based systems like swarms and
-flocking.
+effective drug carriers
+and functional mimics of cell membranes
+\cite{Marui2022IncreasedEO,https://doi.org/10.1002/adma.202206288}.
+The COVID-19 pandemic has led to a
+concerted, worldwide efforts to understand
+the mechanisms of RNA condensation by structural proteins protein
+oligomerization that control virus structure
+\cite{Kim2021SelfassembledMV}.
+Engineers have developed superior techniques
+that rely on nanoscale  
+capillary and van der Waals forces
+to print high-resolution
+features on devices \cite{Zeng20223DprintedMT}.
+Finally, researchers design efficient algorithms for
+constructing for the interaction kernels to study complex
+patterns in agent-based systems like swarms and flocking
+\cite{Lu2019NonparametricIO,Tadmor2021OnTM}.
 
-A number of mathematical techniques have been developed to handle
-self-organizing systems. Each technique has its advantages and
-disadvantages. Prominent in chemistry and biology, molecular dynamics
-(MD) simulations offers unparalleled resolution of protein-lipid
-interactions, say, but because of the large number of non-linear
-interactions involved, is limited to short time and small spatial
-scales. In terms of inverse problems, agent based systems also involve
-relatively large numbers of particles and researchers extensively
-consider the problem of using trajectory data to learn interaction
-kernels of the dynamics when constrained to evolve on Riemannian
-manifolds. Once the interaction kernels are known, one can in principle
-derive partial differential equations (PDE) for the macroscopic
-behavior.
+%A number of mathematical techniques have been developed to handle
+%self-organizing systems. Each technique has its advantages and
+%disadvantages. Prominent in chemistry and biology, molecular dynamics
+%(MD) simulations offers unparalleled resolution of protein-lipid
+%interactions, say, but because of the large number of non-linear
+%interactions involved, is limited to short time and small spatial
+%scales. In terms of inverse problems, agent based systems also involve
+%relatively large numbers of particles and researchers extensively
+%consider the problem of using trajectory data to learn interaction
+%kernels of the dynamics when constrained to evolve on Riemannian
+%manifolds. Once the interaction kernels are known, one can in principle
+%derive partial differential equations (PDE) for the macroscopic
+%behavior.
 
-The phase field method and self-consistent field theory are popular
-approaches to self-organization in Applied Mathematics. Motivated by
-Ginzburg-Landau theory, these methods introduce a scalar-valued phase
-field function for the volume fraction of lipids and water in modeling
-vesicles membranes, for example. Sometimes called diffuse interface
+When fluids are involved,
+tracking self-organization
+becomes difficult due to the deformability of
+suspended media.  A dominant approach in this area,
+the phase field method
+introduce a scalar-valued phase
+field function for the volume fraction of
+amphiphilic lipids or polymers in solvent, for example.
+Sometimes called diffuse interface
 methods, one devises energy functionals involving the gradient and
 well-potentials of the phase field, and possibly long range interaction
-kernels, that yield approximate mathematical surfaces of almost
-arbitrary topology. Because the fluid interfaces are given by the
-level-set of a smooth function, the evolution equations can be studied
-by well-established tools like variational methods and regularity
-theory, and are amenable to numerical approximation. On the downside,
-granular details like the shape changes of a protein, for example, are
+kernels, 
+\cite{Promislow2022UndulatedBI,C9SM01983A,doi:10.1063/5.0009734,
+LiAn-Chang16,Choksi2003OnTD}.
+Because the fluid interfaces are given by the
+level-set of a smooth function,
+they can have almost arbitrary topology
+e.g., free ends, junctions
+\cite{Promislow2017ExistenceBA,Promislow2022UndulatedBI},
+the evolution equations can be studied
+by well-established tools variational and analytical means,
+\cite{Gavish2011CurvatureDF,Dai2019WeakSF,Dai2015CompetitiveGE,
+Dai2022GeometricEO,Dai2020MinimizersFT,Dai2013GeometricEO},
+and the governing equations are amenable to numerical approximation
+\cite{Christlieb2020BenchmarkCO,Christlieb2019CompetitionAC}.
+One of the downsides, though, 
+is that granular details like molecular orientations and
+shape changes induced by proteins that may be crucial to the physics, are
 clumsy to incorporate in the model. Moreover, numerical simulations of
@@
 \subsection{Problem formulation}
-Recently, we have developed a new mathematical model of
-self-organization~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}. The
-model takes ideas from the phase field method and leverages boundary
+We recently developed a new mathematical model of
+self-organization~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}.
+It takes ideas from the phase field method and leverages boundary
 integral equations to resolve complex domains and speed up computations.
@@
 U_i(t)$ (Figure~\ref{fig:flow_map}).
+Throughout, $\nnu$ refers to unit
+normal pointing into $\Omega(t)$ (Figure~\ref{fig:flow_map}).
 
-We look for $N_b$-many rigid body transformations
+To determine how the granules move through space,
+we look for rigid body transformations
 \begin{align}
@@
 \times n$ matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
-reference coordinate. The transformations~\eqref{eq:RBT} determine how
-the granules move through space. Throughout, $\nnu$ refers to unit
-normal pointing into $\Omega(t)$ (Figure~\ref{fig:flow_map}).
-
-The key idea is to define the dynamics using the following boundary
-value problem system:
+reference coordinate.
+The dynamics come from the following system of semi-linear, elliptic boundary value problems:
 \begin{alignat}{4}
@@
 \end{align}
-are the hydrodynamic and phase stresses, respectively; $I$ is the
-$n\times n$ identity matrix. For vectors $\aa, \bb \in \mathbb{R}^2$,
-we follow the usual convention of defining the ``cross product'' as $\aa
-\times \bb = (\aa^{\perp} \cdot \bb) \kk$ where $\kk = (0,0,1) \in
-\RR^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$.
+are the hydrodynamic and phase field stresses, respectively.
+Equation~\eqref{eqn:stokes} is the Stokes equations 
+describing the velocity $\uu$ and pressure $p$ of the aqueous region with
+viscosity $\mu$.
+Equation~\eqref{eqn:phase} describes the
+transitions of the scalar order parameter $\phi$ with a decay length
+$\epsilon$.
+The scalar function $W(\phi) : \mathbb{R} \to \mathbb{R}$ is a nonnegative
+well-potential with local minima $\phi_0, \phi_1$  etc.
+representing metastable states of the solvent.
+For the single well case, $W(\phi) = \frac{1}{2}\phi^2$
+has the minimum $\phi_0 = 0$ and the phase field equation
+\eqref{eqn:phase} becomes the \emph{linear} screened Laplace equation.
+For the double well case e.g, $W(\phi) = \frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$,
+the phase field equation \eqref{eqn:phase} takes the form of an
+Allen-Cahn equation with local minima $\phi_0 < 0 < \phi_1$.
+Section \ref{sec:specific_aim1} discusses certain
+modifications needed for \eqref{eqn:phase} in the nonlinear case.
 
-The above form a semi-linear elliptic system for evolution of the
-granules. Equation~\eqref{eqn:stokes} is the Stokes equations that
-describes the velocity $\uu$ and pressure $p$ of the aqueous region with
-viscosity $\mu$. Equation~\eqref{eqn:phase} describes the phase
-transitions of the scalar order parameter $\phi$ with a decay length
-$\epsilon$. The scalar function $W(\phi)$ is a nonnegative well
-potential where the local minima represent metastable states $\phi_0,
-\phi_1,\ldots$ of the water phase. To have finite bulk energy, the
-minimum potential phase $\phi_0$ has $W(\phi_0) = 0$. Mathematically,
-this order parameter is responsible for the attraction and adhesion
-between granules that want to align boundaries of like phase.
-
-The next three equations are the moving domain boundary conditions.
-Equations~\eqref{eqn:noslip} specify a no-slip boundary condition for a
+For the moving domain boundary conditions,
+equations~\eqref{eqn:noslip} specify a no-slip boundary condition for a
 rigid body with translation velocity $\aa'_i(t) = \vv_i$ and angular
-velocity $\omega_i$ about the point $\aa_i(t) \in U_i(t)$. ($\omega_i$
-is the axial vector of the skew symmetric matrix $R'_i(t)$.) In
+velocity $\omega_i$ (the axial vector for $R'_i(t)R_i(t)^T$)
+about the point $\aa_i(t) \in U_i(t)$. In
 equation~\eqref{eqn:material}, the function $h_i$ is a material label
-specifying the phases at water-granule interface. The boundary condition
-for $\phi$ is transported by the flow and satisfies $\phi_t + \uu \cdot
-\nabla \phi = 0$ on $\Gamma_i$. Finally,
-equation~\eqref{eqn:stressbalance} closes the system by requiring that
+specifying the phase at water-granule interface.
+Finally, equation~\eqref{eqn:stressbalance} closes the system by requiring that
 the force and torque generated by hydrodynamic stress balances that
 generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
-parameter $\gamma > 0$ is surface tension.
+parameter $\gamma > 0$ is surface tension,
+$I$ is the $n\times n$ identity matrix,
+and we define the ``cross product'' as
+$\aa \times \bb = (\aa^{\perp} \cdot \bb) \kk$ where $\kk = (0,0,1) \in
+\RR^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$ when $\aa, \bb \in \mathbb{R}^2$.
 
@@
 Computational methods to solve the PDEs~\eqref{eqn:stokes}
-and~\eqref{eqn:phase} are challenging to develop because of the complex
-and unbounded domain. This challenge is compounded when dense
+and~\eqref{eqn:phase} are challenging to develop because of
+the complicated and unbounded domain.
+This challenge is compounded when dense
 suspensions are considered. Integral equations (IEs) offer an
@@
 \end{align}
-Here $E$ is the energy stored in the phase transitions. Mathematically,
-the energy law states that changes in granule configuration
-instantaneously change the phase energy $E$. The dynamics are such that
-the change energy is lost due to hydrodynamic dissipation. Further
-details and generalizations are provided in \S\ref{sec:specific_aim1}
-and \S\ref{subsec:specific_aim_3}. Because $E$ depends both on $\phi$
-and $\Omega(t)$, the derivation of~\eqref{eq:energy_law} is somewhat
-subtle and has been worked out in detail in~\cite{Fu2018_SIAM}. The
-calculation uses the Rayleigh Transport Theorem to write the time
-derivative of $E$ as an energy density flux involving the phase stress
-$T_i$ on the boundary, and a bulk term involving the Euler-Lagrange
-derivative of $E$. The Euler-Lagrange derivative vanishes due
+Here $E$ is the energy stored in the phase transitions
+and the energy law states that
+the granules move to decrease energy,
+which is lost due to viscous dissipation.
+The derivation of \eqref{eq:energy_law} is interesting
+because $E$ depends both on $\phi$
+and $\Omega(t)$. It uses the Rayleigh Transport Theorem to write the time
+derivative of $E$ as an energy density flux through the boundary
+involving the phase stress $T_i$, and a bulk term involving the Euler-Lagrange
+derivative of $E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
 to~\eqref{eqn:phase} and the boundary flux transforms into viscous
@@
 
-%It goes as follows. Using the Rayleigh Transport Theorem, the time
-%derivative out $E$ yields an energy density flux involving the phase
-%stress $T_i$ at the boundary, plus a bulk term involving the
-%Euler-Lagrange derivative of $E$.
-
 In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
 background flow, we require that $\lim_{\xx \to \infty} \uu(\xx) -
-\uu_{\infty}(\xx) = \mathbf{0}$. In the case of shear background flow,
-for example,
-\begin{align}
-\label{eqn:shear_BG_flow}
-\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
-\end{align}
-where $\dot \gamma$ is the shear rate and $\mathbf{e}_x$, $\mathbf{e}_y$
-are horizontal and vertical basis vectors, respectively. Other
-background flows include extensional, parabolic Poiseuille, and
-Taylor-Green flow. For numerical stability and physical realism, we
-introduce pairwise repulsive forces and torques
+\uu_{\infty}(\xx) = \mathbf{0}$, where
+the background flow takes the form
+%In the case of shear background flow,
+%for example,
+%\begin{align}
+%\label{eqn:shear_BG_flow}
+%\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
+%\end{align}
+%where $\dot \gamma$ is the shear rate and $\mathbf{e}_x$, $\mathbf{e}_y$
+%are horizontal and vertical basis vectors, respectively.
+%Other
+%background flows include
+shear, extensional, parabolic Poiseuille, and
+Taylor-Green flow, for example.
+For numerical stability and physical realism, we
+include pairwise repulsive forces and torques
 in~\eqref{eqn:stressbalance} to prevent the collision between
-neighboring granules. We include the repulsive potential in the energy
-law~\eqref{eq:energy_law}. A background flow adds elastic energy to the
-granule configurations and is quantified by simulation. We refer to the
-PIs work~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM} for details.
+neighboring granules which introduces a repulsive potential in the energy
+law~\eqref{eq:energy_law}. Background flow adds elastic energy to the
+granule configurations.
+%and is quantified by simulation. We refer to the
+%PIs work~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM} for details.
 
@@
 
-Finally, in terms of mathematical justifications, we mention that in the
-single-well case $W(\phi) = \tfrac{1}{2}\phi^2$, equation
-\eqref{eqn:phase} takes the form of a screened Laplace equation
-$-\epsilon^2 \Delta \phi + \phi =0$. For a fixed domain $\Omega$ with
-class $\mathbf{C}^2$ boundary~\cite{}, if the material label $h_i = 1$
+In terms of mathematical justifications, we mention that when
+equation \eqref{eqn:phase} takes the form of a screened Laplace equation
+$-\epsilon^2 \Delta \phi + \phi =0$, for a fixed domain $\Omega$ with
+smooth boundary, if the material label $h_i = 1$
 everywhere, then $\phi$ has a boundary layer going from $1$ at the
 boundary to $0$ in the bulk and one can prove that 
-\begin{align}
-\label{eqn:math_motivation}
-\lim_{\epsilon \to 0} E = \frac{\gamma}{2} \int_{\partial \Omega} 1 \,dS.
-\end{align}
-In other words, the phase energy can be viewed as an approximation of
-surface energy that ``extends'' into the bulk. In the general case,
-$h_i^2$ replaces $1$ in~\eqref{eqn:math_motivation}. We are confident
+$\lim_{\epsilon \to 0} E = \frac{1}{2}\gamma |\partial \Omega|$.
+In other words, because of the introduction of granule boundaries,
+interfacial energy enters the problem even in the linear case.
+We are confident
 that~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is a correct description
@@
 formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
-the right behavior expected from amphiphilic self-assembly. For example,
+the right behavior expected from amphiphilic self-assembly.
+For example,
 three bodies with amphiphilic label (\S\ref{sec:specific_aim1})
 spontaneously self-organize to sequester the hydrophobic fluid phase
-(the red phase in Figure~\ref{fig:flow_map}).  Moreover, a simple change
-of boundary conditions from amphiphilic, to biased hydrophobic, to polar
+(the red phase in Figure~\ref{fig:flow_map}).
+Moreover, a simple change
+of boundary conditions from amphiphilic,
+to biased hydrophobic, to polar
 results in distinct equilibrium morphologies
-(Figure~\ref{fig:self-assembly2}). (i) Chemistry: Janus spheres Since
+(Figure~\ref{fig:self-assembly2}).
+Some further applications are
+(i) Chemistry: Janus spheres Since
 the formulation is scale independent, it can represent a suspension of
@@
 collection of lipids, at the nanoscopic scale. For larger scales, the
-representation is literal and the granules Janus spheres. (ii) Pickering
-emulsion (iii) \todo[inline]{Bertozzi's problem} (iv) Tension driven
-microprinting (v) Vesicle hydrodynamics.
+representation is literal and the granules Janus spheres.
+(ii) Pickering emulsion
+(iii) \todo[inline]{Bertozzi's problem}
+(iv) Tension driven microprinting
+(v) Vesicle hydrodynamics.
 

### 2022-11-12 NSF2022/Description/specificaim1v2.tex
BG mods

@@
   Byeon2014SolutionsOH, Byeon2013OnAP, Alessio2005ENTIRESI,
-  Trumper2007ExistenceOA} and so we must reformulate
-\eqref{eqn:phase} so that $\phi$ is well-defined.
+  Trumper2007ExistenceOA,Benci2019MultipleSF}
+and so we must reformulate
+\eqref{eqn:phase}.
 A natural modification changes

### 2022-11-12 NSF2022/Description/backgroundv2.tex
BGv2 done

@@
 (Figure~\ref{fig:self-assembly2}).
-Some further applications are
-(i) Chemistry: Janus spheres Since
-the formulation is scale independent, it can represent a suspension of
-amphiphiles, where the granules represent the mean properties of a small
-collection of lipids, at the nanoscopic scale. For larger scales, the
-representation is literal and the granules Janus spheres.
-(ii) Pickering emulsion
-(iii) \todo[inline]{Bertozzi's problem}
-(iv) Tension driven microprinting
-(v) Vesicle hydrodynamics.
+Further applications include
+(i) amphiphilic Janus spheres that form diverse suprastructures
+\cite{HaBr20,McBr21,Bradley2017},
+(ii) pickering emulsions involving
+two-phase fluids and dense suspensions \cite{Bradley2016},
+(iii) creation and manipulation of small droplets
+using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
+and (iv) tension drivent fabrication of microstructures
+~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
 

### 2022-11-12 NSF2022/Description/backgroundv3.tex
BG reworked

--- 2022-11-12 NSF2022/Description/backgroundv2.tex
@@
 
+We recently developed a new mathematical model of
+self-organization in fluid systems~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}.
+The framework uses small, rigid bodies called ``granules''
+to represent parcels of a suspended media.
+The granule shapes and boundary conditions
+capture the local properties of the suspension,
+and instead of volume fraction, a phase field function represents
+the properties of the solvent.
+Our approach falls into the category of work that considers
+particles as a discretization of a continuous problem;
+in this case one is dealing with a particle
+method, as an alternative to other discretization methods
+such as finite-difference, finite-element, and spectral methods
+\cite{Wilson2021ComparisonOT}.
+We have departed from the terminology
+``particles'', though, to emphasize the role played the granules' finite size.
+
+The framework is robust, flexible, and
+cuts across many of the aforementioned challenges.
+(i) The granules are not fixed to a stencil, 
+affording flexibility in terms of morphology and topology---sufficiently
+large forces will even pull granules apart as physically required.
+(ii) The model formulation is built around important details like molecular orientations,
+and exhibits inter-molecular slip that must be added into diffusive interface models
+post hoc. 
+(iii) It is straightforward to consider mixtures of granules with different
+types of shapes and boundary conditions.
+Leveraging boundary and fast summation methods, the dynamics can be solved in 
+near-linear complexity in the number of granules,
+which is equal to or better than 
+the computational complexity of related sharp interface methods.
+
 \begin{figure}
@@
 \subsection{Problem formulation}
-We recently developed a new mathematical model of
-self-organization~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}.
-It takes ideas from the phase field method and leverages boundary
-integral equations to resolve complex domains and speed up computations.
 To formulate the problem, consider a collection of $N_b$-many rigid
@@
 \end{align}
-where $i = 1,\ldots,N_b,$ $R_i(t)$ is a rotation (proper orthogonal) $n
-\times n$ matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
+where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
+\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
 reference coordinate.
@@
 are the hydrodynamic and phase field stresses, respectively.
-Equation~\eqref{eqn:stokes} is the Stokes equations 
-describing the velocity $\uu$ and pressure $p$ of the aqueous region with
-viscosity $\mu$.
+Equations~\eqref{eqn:stokes} are the Stokes equations 
+describing the velocity $\uu$ and pressure $p$ of
+the incompressible fluid region with viscosity $\mu$.
 Equation~\eqref{eqn:phase} describes the
@@
 parameter $\gamma > 0$ is surface tension,
-$I$ is the $n\times n$ identity matrix,
-and we define the ``cross product'' as
+$I$ is the identity matrix,
+and we define the ``cross product'' 
 $\aa \times \bb = (\aa^{\perp} \cdot \bb) \kk$ where $\kk = (0,0,1) \in
-\RR^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$ when $\aa, \bb \in \mathbb{R}^2$.
+\RR^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$ whenever $\aa, \bb \in \mathbb{R}^2$.
 
-We call the rigid bodies $U_i(t)$ granules since they are small, compact
-parcels of a suspended media, e.g.~lipids, Janus spheres. We use the
-shape and boundary conditions for $U_i$ to capture the local properties
-of the suspended media. We have departed from the terminology
-``particles'' to emphasize the role played by their finite size. In our
-simulations (see \S\ref{sec:specific_aim1}), we include a finite length
-repulsion to avoid particle collisions.
+\begin{wrapfigure}[22]{r}{3.2in}
+  \vspace{-15pt}
+  \begin{center}
+    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
+    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
+    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
+     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
+    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
+    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
+      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
+      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
+      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
+      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
+  \end{tabular}
+  \end{center}
+  \vspace{-15pt}
+  \caption{\footnotesize \label{fig:self-assembly2}
+  Changes in the boundary condition \eqref{eqn:material}
+  yield distinct morphologies.
+  Each row has the same initial configuration, $W(\phi) = \tfrac{1}{2}\phi^2$.
+  (\emph{Top}) Granules with an amphiphilic boundary condition
+  results in a bilayer pattern (yellow,
+  $\phi = 1$, blue, $\phi = 0$).
+  (\emph{Middle}) Granules with $\phi = 2$ (magenta) on one side and $\phi = 1$
+  on the other   form multilamellar bilayers.
+  (\emph{Bottom}) Bipolar granules with $\phi = \pm 1$ (yellow, green, resp.)
+  on poler ends   form a checkerboard pattern.}
+\end{wrapfigure}
+\subsection{Applications}
+Since the framework is scale independent, it can be applied broad
+range of nonspecific self-organization phenomena in surface chemistry,
+biology and engineering. For one, the
+formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
+the right behavior expected from amphiphilic self-assembly.
+For example, three bodies with amphiphilic label (\S\ref{sec:specific_aim1})
+spontaneously self-organize to sequester the hydrophobic fluid phase
+(Figure~\ref{fig:flow_map}).
+Changes in the boundary conditions result in
+distint morphologies
+(Figure~\ref{fig:self-assembly2})
+whose rheology can be further investigate (\S\ref{subsec:specific_aim_3}).
 
-\begin{wrapfigure}[]{l}{2.1in}
-  \centering
-  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
-  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
-  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
-  ({\em left}) requires meshing the entire domain (typically into
-  triangles), while a BIE ({\em right}) requires meshing only the
-  boundary of the domain.}
+A concrete application we have considered in our
+SIAM Multiscale Modeling and Simulation and Journal of Fluid Mechanics works
+\cite{Fu2018_SIAM, FuQuRyYo22}
+is the problem of \emph{vesicle hydrodynamics}.
+A vesicle is a small, fluid filled membrane sack.
+The goal in vesicle hydrodynamics is to study the flow patterns 
+that arrise due to the interaction
+between membrane elasticity and the fluid.
+
+A striking aspect of our hydrodynamic
+simulation is its fidelity to physics.
+The model contains a few
+parameters; granule radius $c$,
+screening length $\epsilon$,
+surface tension $\gamma$.
+When set to realistic values,
+\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
+we recover many of the well-known
+elastic moduli for single-component lipid bilayers
+\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}.
+
+In terms of hydrodynamics, the granule vesicles in
+background flows replicate
+the behaviour of an continous, inextensible,
+elastic vesicle with permeability.
+The simulations showed, for the first time,
+a granule-vesicle suspension behaving
+as a tank-treading vesicle \cite{Finken2008, Shaqfeh11}
+(see Figure \ref{fig:JPv_linearshear}).
+Movies of Figure \ref{fig:JPv_linearshear} reveal
+intermonolayer slip and derived values for intermonolayer
+friction were in good quantitative agreement 
+those derived by atomistic and Martini force field
+simulation studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}.
+In Figure \ref{fig:JPv_rupture},
+membrane rupture occurs at large shear rates 
+and yields a dimensional scaling for 
+critical rupture shear rate 
+\cite{VLAHOVSKA2009775,keller_skalak_1982}.
+A side-by-side comparison
+of granule-based vesicles and the sharp interface
+representation yielded shapes and trajectories that
+overlapped.
+
+\begin{wrapfigure}[10]{l}{0.46\textwidth}
+\includegraphics[width=0.46\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
+\caption{\label{fig:JPv_linearshear}Granular vesicles undergo
+tank-treading in background shear flow.}
 \end{wrapfigure}
+Having a non-specific model that replicates physical details
+is the crown jewel of applied mathematics.
+\emph{Further applications} include
+(i) amphiphilic Janus spheres that form diverse suprastructures
+\cite{HaBr20,McBr21,Bradley2017},
+(ii) pickering emulsions involving
+two-phase fluids and dense suspensions \cite{Bradley2016},
+(iii) creation and manipulation of small droplets
+using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
+and (iv) tension drivent fabrication of microstructures
+~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
+\newline
 
+\subsection{Computational method and mathematical properties}
+\begin{wrapfigure}[14]{r}{0.475\textwidth}
+%\vspace{-10pt}
+\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
+\caption{\label{fig:JPv_rupture}Rupture of a granular vesicle under large shear rates.}
+\end{wrapfigure}
 Computational methods to solve the PDEs~\eqref{eqn:stokes}
@@
 including PI Quaife, has developed a variety of tools to address these
-numerical challenges, and we discuss our planned approach in
-Section~\ref{sec:specificaim2}.
+numerical challenges, and we discuss in \S~\ref{sec:specificaim2}.
 
@@
 
+\begin{wrapfigure}[10]{l}{2.1in}
+  \centering
+  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
+  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
+  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
+  ({\em left}) requires meshing the entire domain (typically into
+  triangles), while a BIE ({\em right}) requires meshing only the
+  boundary of the domain.}
+\end{wrapfigure}
 In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
@@
 
-In terms of mathematical justifications, we mention that when
-equation \eqref{eqn:phase} takes the form of a screened Laplace equation
+Regarding mathematical motivation for~\eqref{eq:RBT}--\eqref{eqn:stressbalance},
+when equation \eqref{eqn:phase} takes the form of a screened Laplace equation
 $-\epsilon^2 \Delta \phi + \phi =0$, for a fixed domain $\Omega$ with
@@
 $\lim_{\epsilon \to 0} E = \frac{1}{2}\gamma |\partial \Omega|$.
-In other words, because of the introduction of granule boundaries,
-interfacial energy enters the problem even in the linear case.
+In other words, 
+interfacial energy enters the problem even in the linear case,
+\emph{because of the introduction of granule boundaries.}
 We are confident
@@
 
-\begin{wrapfigure}[23]{r}{3.2in}
-  \vspace{-15pt}
-  \begin{center}
-    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
-    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
-    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
-     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
-    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
-    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
-      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
-      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
-      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
-      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
-  \end{tabular}
-  \end{center}
-  \vspace{-5pt}
-  \caption{\footnotesize \label{fig:self-assembly2} Rows (a)--(c) have
-  the same initial configuration but different boundary conditions $g$.
-  {Top Row:} Granules with an amphiphilic boundary condition
-  results in a bilayer pattern shielding the hydrophobic core (yellow,
-  $\eta > 0$) from the aqueous phase (blue, $\eta = 0$). {\em Middle
-  Row:} Biased granules with a hydrophobic intensity that is greater on
-  one side of the particle (magenta) than the other (yellow). {\em
-  Bottom Row:} Bipolar granules where green is for $\eta < 0$, yellow is
-  for $\eta > 0$, and blue is for $\eta = 0$. Particles orient like
-  sides to form a checkerboard pattern.}
-\end{wrapfigure}
-
-\subsection{Applications}
-Since the formulation is scale independent, it can be applied broad
-range of nonspecific self-organization phenomena in surface chemistry,
-biology and engineering. For one, the
-formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
-the right behavior expected from amphiphilic self-assembly.
-For example,
-three bodies with amphiphilic label (\S\ref{sec:specific_aim1})
-spontaneously self-organize to sequester the hydrophobic fluid phase
-(the red phase in Figure~\ref{fig:flow_map}).
-Moreover, a simple change
-of boundary conditions from amphiphilic,
-to biased hydrophobic, to polar
-results in distinct equilibrium morphologies
-(Figure~\ref{fig:self-assembly2}).
-Further applications include
-(i) amphiphilic Janus spheres that form diverse suprastructures
-\cite{HaBr20,McBr21,Bradley2017},
-(ii) pickering emulsions involving
-two-phase fluids and dense suspensions \cite{Bradley2016},
-(iii) creation and manipulation of small droplets
-using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
-and (iv) tension drivent fabrication of microstructures
-~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
-
-\subsection{Vesicles as self-organized granules}
-\label{sec:vesicles_as_granules}
-Interface problems coming from biology are a challenging
-area of applied mathematics.  Broadly speaking, these problems
-involve a fluid structure interaction where the modeler must
-solve for the velocity in the aqueous phase, track the interface,
-and couple the velocity boundary condition to the interface through
-stress balance boundary conditions.  The aqueous phase can
-be a low Reynolds-number fluid, a porous medium, or viscoelastic fluid,
-and the interfacial forces can come from surface tension, elasticity,
-or electrostatics.
-Incorporating all these details can lead to models with substantial
-complexity and there is a need for robust, general models that
-cut across these issues.
-
-This section shows the principles of PDE-driven
-self-organization apply to the concrete
-problem of \emph{vesicle hydrodynamics}.
-A vesicle is a small, fluid filled membrane sack.
-Microscopically, the membrane of a vesicle is comprised
-elongated amphiphilic lipids that form inner and outer monolayers.  
-The goal in vesicle hydrodynamics is to study the flow patterns e.g.,
-tank-treading, tumbling, that arrise due to the interaction
-between membrane elasticity and surrounding fluid.
-Traditional models represent a vesicle as a
-continuous surface (or curve in $\mathbb{R}^2$) $\Sigma$.
-The elastic energy takes the form
-\begin{equation}
-\label{eq:Canham-Helfrich}
-  \int_{\Sigma} k_B(H - k_0)^2\, dS 
-\end{equation}
-where $H$ is the mean curvature, $k_0$ is a spontaneous curvature,
-and $k_B$ is a bending modulus. 
-The variation of \eqref{eq:Canham-Helfrich} with respect to position
-gives rise to a surface force
-that pointwise balances the jump in hydrodynamic stress across the interace.
-While energy density does depend on Gaussian curvature,
-it does not appear in \eqref{eq:Canham-Helfrich}
-since Gauss-Bonnet Theorem guarantees that
-the integral of Gaussian curvature over a closed surface is independent of the shape of $\Sigma$.
-
-Depending on the situation,
-one can further enforce constant volume constraints or permeability relationships.
-If the interface is area incompressible, then the surface divergence
-of velocity is zero.  On the other hand, if the surface is area compressible,
-then \eqref{eq:Canham-Helfrich} contains an additional stretching term of the
-form $k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are the
-deformed and equilibrium area densitities respectively.
-
-There are downsides to traditional models in terms of generality and physical realism.
-(i) Motivated by drug delivery applications, experimenters use electric
-fields, for example, to controllably open and close pores in membranes
-\cite{}.
-These kinds of topological changes are clumsy to incorporate in
-sharp interface formulations that assume a continuous surface \cite{}.
-(ii) Sharp-interface models assume a membrane of neglible thickness. 
-However, in biological processes
-like fusion, fission, or insertion and penetration by proteins and peptides, 
-the length scales of the
-deformation (tens of nanometers) are comparable to membrane thickness (about 5 nm).
-Moreover, these processes crucially rely on variable lipid
-orientation relative to the surface normal (the so-called \emph{tilt}
-deformation),
-whereas \eqref{eq:Canham-Helfrich} implicitly assumes that the lipids
-are everywhere normal to the surface.  
-(iii) Finally, realistic membranes are comprised of a mixtures of lipids and proteins.
-Recent work \cite{} has incorporated lipid mixtures in \eqref{eq:Canham-Helfrich},
-but these models are formidably complicated 
-due to the additional constraints and transport equations involved.
-
-\begin{wrapfigure}[12]{r}{0.5\textwidth}
-  \vspace{-5pt}
-\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
-  \vspace{-5pt}
-\caption{\label{fig:amphiphilic_assembly}
-Self-organization under amphiphilic boundary condition.
-(a) Granules first match hydrophobic tails (red),
-(b) then align length-wise.
-The principle of self-organization holds in three dimensions 
-as simulated by Kohl, Corona, and Veerapaneni
-\cite{koh-cor-che-vee2021}.}
-\end{wrapfigure}
-Diffusive interface models and surface-director models partially address 
-these shortcomings. 
-Topological changes are permitted in phase field and level set formulations,
-but these methods smear out the details of lipid orientations.
-The detailed energies of lipid orientation that include tilt are
-closely related to the celebraated and well-studied
-field of nematic liquid crystals.  Here, there have been recent development
-in simulation and theory of nematic liquid crystals on surfaces.
-These models consider the interplay between defects and surface geometry \cite{},
-finite element formulations \cite{}, and existence of minimizers \cite{}.
-
-\subsubsection{Main modeling innovations}
-We developed the model \eqref{eq:RBT}-\eqref{eqn:hydro_stress} 
-as a robust and flexible approach
-that cuts across many of the aforementioned challenges.
-(i) The granules are not fixed to a stencil, 
-affording flexibility in terms of vesicle morphology and topology--sufficiently
-large forces will even pull the granules apart as physically required.
-(ii) The model formulation is built around important details like lipid orientations,
-and exhibits inter-monolayer slip that must be added into diffusive interface models
-post hoc. 
-(iii) It is straightforward to consider mixtures of granules with different
-types of shapes and boundary conditions of the granules.
-With the help of boundary integral equations
-and fast summation methods, the dynamics can be solved in 
-near-linear complexity in $N_b$, which is equal to or better than 
-the computational complexity of related sharp interface methods.
-
-Inspired
-by the amphiphilic structure of lipids,
-we formulated a so-called ``amphiphilic'' boundary condition
-that leads a collection of granules to form bilayers.
-Referring to Figure \ref{fig:amphiphilic_assembly}, 
-\begin{equation}
-\label{eq:amphiphilic_BC}
-\phi(\mathbf{x}) = h_i(\mathbf{x}) = \tfrac{1}{2}\left(\dd_i \cdot (\xx - \aa_i)/c_i + 1\right), \quad
-\mathbf{x} \in \Gamma_i,
-\end{equation}
-where $\dd_i$ is the director, $\aa_i$ is the center, and $c_i$ the
-``radius'' of the $i$th granule.  
-The phase $\phi$ takes values close to $1$ on in the direction $\dd_i$,
-representing a hydrophobic tail, and values close to $0$ 
-in the direction $\dd_i$ representing the hydrophilic head.
-
-\begin{figure}[t!]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{figures/Background/coarsening.pdf}
-\end{center}
-\vspace{-20pt}
-\caption{\label{fig:coarsening}
-Modeling procedure.
-We initilize a suspension of granules.
-Under the moving domain problem
-\eqref{eq:RBT}-\eqref{eqn:hydro_stress}
-with amphiphilic boundary condition, the granules
-self-organize into vesicle bilayers.
-We then introduce external hydrodynamic effects to study elastic properties.
-}
-\vspace{5pt}
-\end{figure}
-\subsubsection{How do granule-based vesicles have an elastic energy?}
-A natural question to ask is how 
-elastic energy enters a formulation
-coming from surface interactions like \eqref{eqn:math_motivation}.
-Conceptually, random suspensions of amphiphilic
-granules undergo a rapid coarsening to form bilayers.
-For tens of granule, the bilayers form a single stable, ring-shaped vesicle
-with energy $E_{\text{stable}}$ (Figure \ref{fig:coarsening}, (c)).
-This vesicle configuration, however, is only a local minimizer,
-whereas the planar configuration (Figure \ref{fig:coarsening}, (e))
-is the global minimizer.  The difference between
-$E(t)$ and $E_{\min}$ is the vesicle elastic energy.
-Indeed, if a background flow overcomes the energy barrier to force granules apart,
-then the bilayer unfolds from its circular shape into a flat shape.
-
-When hundreds granules are involved,
-the two-dimensional granules reach an intermediate
-state consisting of several bilayer segments (see Figure \ref{fig:self-assembly2}, top right).
-Placing this metastable state into a mild background flow
-causes the segments to join up into isolated vesicles \cite{fu-ryh-qua-you2022}.
-
-Having a non-specific model that replicates detailed
-physics and biology is the crown jewel of applied mathematics
-and we believe that ours is such a model.
-
-\begin{wrapfigure}[11]{r}{0.5\textwidth}
-\includegraphics[width=0.5\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
-\caption{\label{fig:JPv_linearshear}Granular vesicles undergo
-tank-treading in background shear flow.}
-\end{wrapfigure}
-\textit{Summary of results from the paper \cite{Fu2018_SIAM}.}
-A striking aspect of the
-model is its fidelity to physics.
-The model contains a few
-parameters; granule radius $c$,
-screening length $\epsilon$,
-surface tension $\gamma$.
-When set to realistic values,
-\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
-we recover many of the well-known
-elastic moduli for single-component lipid bilayers
-\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}.
-\emph{Bending:}
-The bending deformation enters through the splay of the
-granule directors.  In Figure \ref{fig:JPv_linearshear},
-for example, the directors have negative, respectively positive,
-splay $\nabla_{\Sigma} \cdot \dd$
-in the outer, respectively inner monolayers.
-Here $\nabla_{\Sigma}\cdot{} = \nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$
-is the surface divergence for the unit normal $\NN$
-and the splay energy density
-for the granule configuration is Hookean with bending modulus $k_B$.
-It is a fact from differential geometry that
-when $\dd$ is everywhere parallel to $\NN,$
-then $\nabla\cdot \dd = \pm 2H$ and this is how the
-curvature term arises for \eqref{eq:Canham-Helfrich}
-($2H = \kappa$ in the two-dimensional setting).
-In the case of mixtures of granules of different sizes,
-spontaneous curvature $k_0$ arises
-from asymmetry in the monolayer leaflets.
-\emph{Stretching.}
-When stretched, the distance between
-neighboring granules is increased from rest
-and the energy for stretching behaves as 
-$\tfrac{1}{2}k_A(L - L_0)^2/L_0$
-for a stretching modulus $k_A$,
-length $L$, and
-length at rest $L_0$ of the two-dimensional vesicle. 
-\emph{Tilt.}
-Finally, the granules possess a 
-tilt decay length scale $\lambda = \sqrt{k_B/k_{\theta}}$
-well-known from the biophysical literature
-for the case when the directors $\mathbf{d}$ are no longer normal
-to the surface
-\cite{KUZMIN2005}.
-
-\begin{wrapfigure}[14]{l}{0.475\textwidth}
-%\vspace{-10pt}
-\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
-\caption{\label{fig:JPv_rupture}Rupture of a granular vesicle under large shear rates.}
-\end{wrapfigure}
-\textit{Summary of results from the paper \cite{FuQuRyYo22}.}
-In terms of hydrodynamics, the granule vesicles in linear
-background flows \eqref{eqn:shear_BG_flow} also replicates
-the behaviour of an continous, inextensible,
-elastic vesicle with permeability.
-The simulations showed, for the first time,
-a granule-vesicle suspension behaving
-as a tank-treading vesicle \cite{Finken2008, Shaqfeh11}
-(see Figure \ref{fig:JPv_linearshear}).
-Movies of Figure \ref{fig:JPv_linearshear} reveal
-intermonolayer slip and derived values for intermonolayer
-friction were in good quantitative agreement 
-those derived by atomistic and Martini force field
-simulation studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}.
-In Figure \ref{fig:JPv_rupture},
-membrane rupture occurs at large shear rates $\dot \gamma$
-and we derived a dimensional scaling to 
-predict critical shear rate for rupture
-\cite{VLAHOVSKA2009775,keller_skalak_1982}.
-Finally, a side-by-side comparison
-of granule-based vesicles and the continuous model using
-\eqref{eq:Canham-Helfrich} yielded shapes and trajectories that
-basically overlapped.
-
 \subsection{Outline of the proposal}
-The outline of the proposal goes as follows.
-Section \ref{sec:resume} describes the
-PIs's expertise and prior works
-in (1) membrane-fluid mechanics (2) boundary integral equations
-and (3) complex fluid dynamics
-that are critical to the success of this proposal. 
-Section \ref{sec:proposed-work}
-goes over the three specific aims of the proposal.
+The aim of this proposal is to advance the simulation
+and theory for soft-matter systems
+and foster training in mathematical sciences.
+Section \ref{sec:BroaderImpacts} summarizes the broader
+impacts and intellectual merit of our research activity.
+Section \ref{sec:proposed-work} contains our
+three specific aims.  They are
+mathematical analysis of the system
+(\S \ref{sec:specificaim1}: PI Ryham),
+numerical implementation
+(\S \ref{sec:specificaim2}: PI Quaife),
+and  kinetic theory
+(\S \ref{sec:specificaim3}: PI Young).

### 2022-11-12 NSF2022/Description/backgroundv2.tex
SA1

@@
 between membrane elasticity and surrounding fluid.
-Traditional models represent a vesicle as a
-continuous surface (or curve in $\mathbb{R}^2$) $\Sigma$.
-The elastic energy takes the form
-\begin{equation}
-\label{eq:Canham-Helfrich}
-  \int_{\Sigma} k_B(H - k_0)^2\, dS 
-\end{equation}
-where $H$ is the mean curvature, $k_0$ is a spontaneous curvature,
-and $k_B$ is a bending modulus. 
-The variation of \eqref{eq:Canham-Helfrich} with respect to position
-gives rise to a surface force
-that pointwise balances the jump in hydrodynamic stress across the interace.
-While energy density does depend on Gaussian curvature,
-it does not appear in \eqref{eq:Canham-Helfrich}
-since Gauss-Bonnet Theorem guarantees that
-the integral of Gaussian curvature over a closed surface is independent of the shape of $\Sigma$.
-
-Depending on the situation,
-one can further enforce constant volume constraints or permeability relationships.
-If the interface is area incompressible, then the surface divergence
-of velocity is zero.  On the other hand, if the surface is area compressible,
-then \eqref{eq:Canham-Helfrich} contains an additional stretching term of the
-form $k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are the
-deformed and equilibrium area densitities respectively.
 

### 2022-11-12 NSF2022/Description/specificaim1v2.tex
BG reworked
SA1

@@
 \subsection{Specific Aim 1: Membrane vesicles as self-organized granules}
-\label{sec:specific_aim1}
+\label{sec:specificaim1}
 We introduced \eqref{eq:RBT}--\eqref{eqn:stressbalance} to complement
 existing methods for studing vesicles and bilayers. 
-The simulations results in \S \ref{sec:vesicles_as_granules}
-show that two-dimensional, granule-based vesicles replicate the 
-equilibria and hydrodynamics for continuous curves.
-Having shown that the model is effective in terms of simulation,
-our next goal is to study the model using rigorous analysis
+The simulation results in 
+(Figures \ref{fig:JPv_linearshear} and \ref{fig:JPv_rupture})
+showed that two-dimensional, granule-based vesicles replicate the 
+equilibria and hydrodynamics for continuous curves
+\cite{FuQuRyYo22, Fu2018_SIAM}.
+Our next goal is to study the model using rigorous analysis
 and consider three-dimensionsional effects.
@@
 This system is an autonomous ordinary differential equation for
-rigid body transformations $F_i$.  The right-hand side of this
-equation is defined by a system of PDE.  In the single-well case,
+the body transformations $F_i$
+with the rate of change is defined by a system of PDEs.
+Regarding this system, in the single-well case,
 \eqref{eqn:phase} is a linear equation
 and for fixed $t$ there is a unique solution
-($\phi, \uu$) for the interactions under appropriate
+($\phi, \uu$) under appropriate
 assumptions for the boundaries and boundary data
@@
 behavior in the limit zero screening length limit.
+In this limit, we should recover the hydrodynamics of
+a (noninteracting) rigid body suspension.
 
@@
   \phi_t + \uu \cdot \nabla
-  = -\lambda \frac{\delta E}{\delta \phi}
-  =  \lambda(\epsilon^2 \Delta \phi - W'(\phi)),
+  = -\beta \frac{\delta E}{\delta \phi}
+  =  \beta(\epsilon^2 \Delta \phi - W'(\phi)),
   \quad \phi(\xx,0) = \phi_0(\xx),
@@
 with an addtional dissipation term involving the square 
-the Euler-Lagrange derivative $\frac{\delta E}{\delta \phi}$ and dampening factor $\lambda > 0$.
+the Euler-Lagrange derivative $\frac{\delta E}{\delta \phi}$ and dampening factor $\beta > 0$.
 There are several works dealing with the
-geometric characterization of the geometric evolution
+characterization of the geometric evolution
 of interfaces under the Allen-Cahn and Cahn-Hilliard equations
@@
 problems with moving domains.
-
 A closely related and strongly developing direction in
@@
 The second problem considers the approximation
-of equilibrium elastic energy of curves and surfaces,
+of elastic energy of curves and surfaces,
 and seeks to make rigorous the simulation results of
-\S \ref{sec:vesicles_as_granules}.
+\cite{FuQuRyYo22, Fu2018_SIAM}.
 \begin{quotation}
-\textbf{Problem 2.} Place a collection of
-two-dimensional amphiphilic granules along a curve $\mathcal{C}$.
+  \textbf{Problem 2.}
+  Consider a collection of two-dimensional
+  granules along a closed curve. 
   Study the sharp interface limit of the energy $E$ 
@@
 \end{quotation}
+Sharp interface models
+traditionally represent a vesicle as an
+inextensible continuous surface $\Sigma$ with elastic energy
+\begin{equation}
+\label{eq:Canham-Helfrich}
+  \int_{\Sigma} k_B(H - k_0)^2\, dS,
+\end{equation}
+where $H$ is the mean curvature, $k_0$ is a spontaneous curvature,
+and $k_B$ is a bending modulus.
+Real membranes, however, are somewhat extensible and
+have a large stretching modulus $k_A$.
+When the surface is area compressible,
+\eqref{eq:Canham-Helfrich} contains an additional stretching term of the
+form $k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are the
+deformed and equilibrium area densitities respectively.
+
+The bending deformation enters through the splay of the
+granule directors.  In Figure \ref{fig:JPv_linearshear},
+for example, the directors have negative, respectively positive,
+splay $\nabla_{\Sigma} \cdot \dd$
+in the outer, respectively inner monolayers.
+Here $\nabla_{\Sigma}\cdot{} = \nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$
+is the surface divergence for the unit normal $\NN$
+and the splay energy density
+for the granule configuration is Hookean with bending modulus $k_B$.
+It is a fact from differential geometry that
+when $\dd$ is everywhere parallel to $\NN,$
+then $\nabla\cdot \dd = \pm 2H$ and this is how the
+curvature term arises for \eqref{eq:Canham-Helfrich}
+($2H = \kappa$ in the two-dimensional setting).
+In the case of mixtures of granules of different sizes,
+spontaneous curvature $k_0$ arises
+from asymmetry in the monolayer leaflets.
+\emph{Stretching.}
+When stretched, the distance between
+neighboring granules is increased from rest
+and the energy for stretching behaves as 
+$\tfrac{1}{2}k_A(L - L_0)^2/L_0$
+for a stretching modulus $k_A$,
+length $L$, and
+length at rest $L_0$ of the two-dimensional vesicle. 
+\emph{Tilt.}
+Finally, the granules possess a 
+tilt decay length scale $\lambda = \sqrt{k_B/k_{\theta}}$
+well-known from the biophysical literature
+for the case when the directors $\mathbf{d}$ are no longer normal
+to the surface
+\cite{KUZMIN2005}.
+
 Problems like these have been addressed for bulk nematic liquid

### 2022-11-13 NSF2022/Description/backgroundv2.tex
SA1 done

@@
 Allen-Cahn equation with local minima $\phi_0 < 0 < \phi_1$.
-Section \ref{sec:specific_aim1} discusses certain
+Section \ref{sec:specificaim1} discusses certain
 modifications needed for \eqref{eqn:phase} in the nonlinear case.
@@
 by the amphiphilic structure of lipids,
-we formulated a so-called ``amphiphilic'' boundary condition
+we formulated a so-called
+``amphiphilic'' boundary condition
 that leads a collection of granules to form bilayers.
@@
 \emph{Bending:}
-The bending deformation enters through the splay of the
-granule directors.  In Figure \ref{fig:JPv_linearshear},
-for example, the directors have negative, respectively positive,
-splay $\nabla_{\Sigma} \cdot \dd$
-in the outer, respectively inner monolayers.
-Here $\nabla_{\Sigma}\cdot{} = \nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$
-is the surface divergence for the unit normal $\NN$
-and the splay energy density
-for the granule configuration is Hookean with bending modulus $k_B$.
-It is a fact from differential geometry that
-when $\dd$ is everywhere parallel to $\NN,$
-then $\nabla\cdot \dd = \pm 2H$ and this is how the
-curvature term arises for \eqref{eq:Canham-Helfrich}
-($2H = \kappa$ in the two-dimensional setting).
-In the case of mixtures of granules of different sizes,
-spontaneous curvature $k_0$ arises
-from asymmetry in the monolayer leaflets.
-\emph{Stretching.}
-When stretched, the distance between
-neighboring granules is increased from rest
-and the energy for stretching behaves as 
-$\tfrac{1}{2}k_A(L - L_0)^2/L_0$
-for a stretching modulus $k_A$,
-length $L$, and
-length at rest $L_0$ of the two-dimensional vesicle. 
-\emph{Tilt.}
-Finally, the granules possess a 
-tilt decay length scale $\lambda = \sqrt{k_B/k_{\theta}}$
-well-known from the biophysical literature
-for the case when the directors $\mathbf{d}$ are no longer normal
-to the surface
-\cite{KUZMIN2005}.
 

### 2022-11-13 NSF2022/Description/specificaim1v2.tex

@@
 the body transformations $F_i$
-with the rate of change is defined by a system of PDEs.
-Regarding this system, in the single-well case,
-\eqref{eqn:phase} is a linear equation
-and for fixed $t$ there is a unique solution
-($\phi, \uu$) under appropriate
-assumptions for the boundaries and boundary data
+with the rate of change defined by a system of PDEs.
+Regarding this system, in the single-well case and
+for fixed $t$, the linear system has a unique solution
+($\phi, \uu$) 
+under appropriate assumptions for the boundaries and boundary data
 \cite{manasthesis,rac-gre2016,LAX}.
+These define the instantaneous rigid body translational velocity and rotation.
 This leads to 
@@
 we can ensure positivity in time for the distance between granules
-using the fluid mechanical principle of
-lubrication forces \cite{cawthorn_balmforth_2010, leal_2007}.
+using lubrication forces \cite{cawthorn_balmforth_2010, leal_2007}.
 Finally, we can describe the granule-flow
-behavior in the limit zero screening length limit.
+behavior in the zero-screening length limit.
 In this limit, we should recover the hydrodynamics of
@@
 \cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT, Alama2021SaturnRD, PhysRevE.96.042702}.
+PI Ryham has several works on membrane vesicles
+dealing both with Allen-Cahn formulations
+and fluid-vesicle interactions 
+\cite{QiangDu09, RYHAM20112929, RyCoEi12,Ryham2017OnTV}.
 
@@
 \cite{FuQuRyYo22, Fu2018_SIAM}.
+We employ the so-called ``amphiphilic'' boundary condition
+that leads a collection of granules to form bilayers.
+Referring to Figure \ref{fig:amphiphilic_assembly}, 
+\begin{equation}
+\label{eq:amphiphilic_BC}
+\phi(\mathbf{x}) = h_i(\mathbf{x}) = \tfrac{1}{2}\left(\dd_i \cdot (\xx - \aa_i)/c_i + 1\right), \quad
+\mathbf{x} \in \Gamma_i,
+\end{equation}
+where $\dd_i$ is the director, $\aa_i$ is the center, and $c_i$ the
+``radius'' of the $i$th granule.  
+The phase $\phi$ takes values close to $1$ on in the direction $\dd_i$,
+representing a hydrophobic tail, and values close to $0$ 
+in the direction $\dd_i$ representing the hydrophilic head.
+
 \begin{quotation}
@@
   Consider a collection of two-dimensional
-  granules along a closed curve. 
+  amphiphilic granules along a closed curve $\mathbf{C}$. 
   Study the sharp interface limit of the energy $E$ 
@@
 \end{quotation}
-Sharp interface models
-traditionally represent a vesicle as an
+The sharp interface model
+represent a membrane vesicle as an
 inextensible continuous surface $\Sigma$ with elastic energy
@@
 and $k_B$ is a bending modulus.
-Real membranes, however, are somewhat extensible and
-have a large stretching modulus $k_A$.
-When the surface is area compressible,
-\eqref{eq:Canham-Helfrich} contains an additional stretching term of the
-form $k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are the
-deformed and equilibrium area densitities respectively.
+One can also account for extensibility
+by including in 
+\eqref{eq:Canham-Helfrich} an additional stretching term
+$k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are the deformed and equilibrium area densitities respectively.
 
-The bending deformation enters through the splay of the
-granule directors.  In Figure \ref{fig:JPv_linearshear},
+\begin{wrapfigure}[12]{r}{0.5\textwidth}
+  \vspace{-5pt}
+\centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
+  \vspace{-5pt}
+\caption{\label{fig:amphiphilic_assembly}
+Self-organization under amphiphilic boundary condition.
+(a) Granules first match hydrophobic tails (red),
+(b) then align length-wise.
+The principle of self-organization holds in three dimensions 
+as simulated by Kohl, Corona, and Veerapaneni
+\cite{koh-cor-che-vee2021}.}
+\end{wrapfigure}
+Bending enters through the splay of the
+granule directors.
+In Figure \ref{fig:JPv_linearshear},
 for example, the directors have negative, respectively positive,
@@
 Here $\nabla_{\Sigma}\cdot{} = \nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$
-is the surface divergence for the unit normal $\NN$
-and the splay energy density
-for the granule configuration is Hookean with bending modulus $k_B$.
-It is a fact from differential geometry that
-when $\dd$ is everywhere parallel to $\NN,$
-then $\nabla\cdot \dd = \pm 2H$ and this is how the
-curvature term arises for \eqref{eq:Canham-Helfrich}
-($2H = \kappa$ in the two-dimensional setting).
-In the case of mixtures of granules of different sizes,
-spontaneous curvature $k_0$ arises
-from asymmetry in the monolayer leaflets.
-\emph{Stretching.}
-When stretched, the distance between
-neighboring granules is increased from rest
-and the energy for stretching behaves as 
-$\tfrac{1}{2}k_A(L - L_0)^2/L_0$
-for a stretching modulus $k_A$,
-length $L$, and
-length at rest $L_0$ of the two-dimensional vesicle. 
-\emph{Tilt.}
-Finally, the granules possess a 
-tilt decay length scale $\lambda = \sqrt{k_B/k_{\theta}}$
-well-known from the biophysical literature
-for the case when the directors $\mathbf{d}$ are no longer normal
-to the surface
-\cite{KUZMIN2005}.
+is the surface divergence for the outward unit surface normal $\NN$.
+From differential geometry, we have that 
+$\nabla\cdot \dd = \pm 2H$ whenever
+$\dd$ is everywhere parallel to $\NN,$
+and this is how the
+curvature term arises for \eqref{eq:Canham-Helfrich}.
+(For two-dimensional vesicles, the curvature $\kappa$ of the curve $\mathbf{C}$).
+Granules are at rest when attraction balances repulsion, 
+and will have stretching when the distance between
+neighboring granules is increased from rest.
 
-Problems like these have been addressed for bulk nematic liquid
+PI Ryham has experience in the sharp interface analysis
+for phase field formulations of elastic
+bending energy \cite{0951-7715-18-3-016,Du05}, and
+topological indicators \cite{DuEuler},
+as well as for Poisson-Boltzman equations \cite{Lee2018,1531-3492_2006_2_357}.  Tools for addressing Problem 2 have
+been developed for bulk nematic liquid
 crystal potentials in the area of colloidal homogenization
-\cite{Canevari2019DesignOE,doi:10.1137/18M1163919,doi:10.1137/18M1163919,
-  BERLYAND200597,doi:10.1137/130910348},
-and is closely related to 
+\cite{Canevari2019DesignOE,doi:10.1137/18M1163919,doi:10.1137/18M1163919, BERLYAND200597,doi:10.1137/130910348},
+and is related to 
 dimension reduction for curved nematics confined to thin films
@@
 doi:10.1142/S0218202516500470, FoFrLe07}.
-Given the relatively complicated geometry consising
-of a plane with a number of disjoint disks removed, 
-we start by assuming that the directors are normal to the curve
-and that the granules are all disks with radius proportional to $\epsilon$. 
-The bending $k_B$ and stretching $k_A$ coefficients
-depend on the granual size relative to their spacing.
-We can then generalize the problem to account for aspect ratio of
+We start by assume circular granules aligned normally to the curve,
+and then generalize the problem to account for aspect ratio of
 elliptical granules and nonzero tilt.
@@
 On the other hand, in biophysics,
-\cite{Hamm2000ElasticEO,Terzi2019CurvatureTiltTO,Terzi2019ACQ,Terzi2017NovelTC}
-and most recently \cite{Pinigin2020NewCT}
-derived an elastic energy for lipid bilayers,
-the generalized Helfrich energy.
-This energy involves the lipid director $\dd$,
-tilt vector $\mathbf{T}$, and area per lipid $\alpha$,
-and coupling terms and contains
-the Helfrich elastic energy \eqref{eq:Canham-Helfrich}
+\cite{Hamm2000ElasticEO,Terzi2019CurvatureTiltTO,Terzi2019ACQ,Terzi2017NovelTC,Pinigin2020NewCT} have
+derived the general Helfrich energy for lipid bilayers
+that involves effects coupling lipid tilt to 
+director splay.  This energy contains \eqref{eq:Canham-Helfrich}
 as a special case.
@@
 Simulate surfaces made up of three-dimensional, amphilic granules.
-Do you recover the generalized Helfrich elastic energy
-or related Landau deGennes energies for large $N_b$ simulations?
+Numerically investigate the limiting energy for large $N_b$ simulations.
 \end{quotation}
+In his much noticed Biophysical Journal
+and Nature papers~\cite{RyKlYaCo16,Chetal16}, PI Ryham
+calculated the least energy path for \emph{membrane fusion}
+using a surface-director model based on the general Helfrich energy. 
+The energy barriers calculated in~\cite{RyKlYaCo16} 
+proved consistent with later molecular dynamics
+and experimental results \cite{SmRiMu19,2017PNAS..114.1238F}.
 
@@
 fast summation method such as the fast multipole method.
-The implementation details, especially how we deal with large
-granule numbers and three-dimensional systems, are
+The implementation details, in particular how we deal with large
+granule numbers and three-dimensional systems are
 described in \S \ref{sec:specificaim2} Specific Aim 2.
-
-PI Ryham has made fundamental contributions to interface modeling in
-membrane biology.  His first works include
-phase field formulations for the elastic bending energy \cite{0951-7715-18-3-016,Du05} and topological indicators \cite{DuEuler} of vesicle membranes
-and fluid-vesicle interactions \cite{QiangDu09}.
-In his much noticed Biophysical Journal
-and Nature papers~\cite{RyKlYaCo16,Chetal16}, Ryham and collaborators 
-calculated, for the first time, a least energy path for membrane fusion.
-
 %\begin{equation}

### 2022-11-13 NSF2022/Description/specificaim2.tex
BGv2 done
fig to BG

@@
 solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}. Additionally,
-hydrodynamic interactions are central to fabricate complex,
+hydrodynamic interactions are central to
+fabricate complex,
 three-dimensional microstructures~\cite{Dasgupta2017, Leong2007,
-Reynolds2019, Cho2010}. Hydrodynamic effects cannot be ignored since
+  Reynolds2019, Cho2010}.
+Hydrodynamic effects cannot be ignored since
 they, like for the rates of biological functions like pore
@@
 
+\begin{wrapfigure}[27]{l}{1.8in}
+  \vspace{-8pt}
+  \centering
+  \input{figures/doublewell.tikz} 
+  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
+  The solution of the one-dimensional phase
+  transition~\eqref{eqn:phase}. (c) The convergence of exact and inexact
+  Newton's methods.}
+\end{wrapfigure}
 While the inclusion of high-order quadrature and fast methods is
@@
 Runge-Kutta, step-doubling, and Richardson extrapolation.
-
-\begin{wrapfigure}[27]{l}{1.8in}
-  \vspace{-8pt}
-  \centering
-  \input{figures/doublewell.tikz} 
-  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
-  The solution of the one-dimensional phase
-  transition~\eqref{eqn:phase}. (c) The convergence of exact and inexact
-  Newton's methods.}
-\end{wrapfigure}
 

### 2022-11-13 NSF2022/Description/backgroundv3.tex

@@
 
-\begin{wrapfigure}[10]{l}{2.1in}
-  \centering
-  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
-  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
-  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
-  ({\em left}) requires meshing the entire domain (typically into
-  triangles), while a BIE ({\em right}) requires meshing only the
-  boundary of the domain.}
+\begin{wrapfigure}[16]{l}{4in} 
+\includegraphics[width=4in]{figures/Background/coarsening.pdf}
+\vspace{-20pt}
+\caption{\label{fig:coarsening}
+Modeling procedure.
+We initilize a suspension of granules.
+Under the moving domain problem
+\eqref{eq:RBT}-\eqref{eqn:hydro_stress}
+with amphiphilic boundary condition, the granules
+self-organize into vesicle bilayers.
+We then introduce external hydrodynamic effects to study elastic properties.
+}
+\vspace{5pt}
 \end{wrapfigure}
@@
 
+\begin{wrapfigure}[10]{r}{2.1in}
+  \centering
+  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
+  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
+  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
+  ({\em left}) requires meshing the entire domain (typically into
+  triangles), while a BIE ({\em right}) requires meshing only the
+  boundary of the domain.}
+\end{wrapfigure}
 Regarding mathematical motivation for~\eqref{eq:RBT}--\eqref{eqn:stressbalance},

### 2022-11-13 NSF2022/Description/backgroundv3.tex
SA1, SA2, and bibliography

@@
 the right behavior expected from amphiphilic self-assembly.
-For example, three bodies with amphiphilic label (\S\ref{sec:specific_aim1})
+For example, three bodies with amphiphilic label (\S\ref{sec:specificaim1})
 spontaneously self-organize to sequester the hydrophobic fluid phase
@@
 (Figure~\ref{fig:self-assembly2})
-whose rheology can be further investigate (\S\ref{subsec:specific_aim_3}).
+whose rheology can be further investigate (\S\ref{sec:specificaim3}).
 

### 2022-11-13 NSF2022/Description/specificaim2.tex
SA1, SA2, and bibliography

@@
 fundamental solution and $\ssigma: \partial \Omega(t) \rightarrow \RR^2$
-is an unknown density function. The IE reformulation has several
-immediate advantages including a dimension reduction since $\ssigma$ is
-defined only on $\partial \Omega(t)$, and the far field boundary
-condition of the PDE is automatically satisfied. The density
-function $\ssigma$ is chosen to satisfy the boundary condition, and this
-results in an IE 
+is an unknown density function. This is analogous to the problem of
+finding the global electrostatic potential $u$ with surface charge
+density $\sigma$
 \begin{align*}
+  u(x) = -\frac{1}{4\pi}\int_{\partial \Omega(t)} 
+    \frac{1}{|\xx - \yy|}\sigma(y) \, ds_\yy.
+\end{align*}
+
+The IE reformulation has several immediate advantages including a
+dimension reduction since $\ssigma$ is defined only on $\partial
+\Omega(t)$, and the far field boundary condition of the PDE is
+automatically satisfied. The density function $\ssigma$ is chosen to
+satisfy the boundary condition, and this results in an IE 
+\begin{align}
   \gg(\xx) = \lambda \ssigma(\xx) + 
@@
     \quad \xx \in \partial\Omega(t),
-\end{align*}
-where $\gg$ is the boundary condition, and $\lambda$ is a constant that
-depends on the choice of $G$. For numerical stability, choices of $G$
-that result in second-kind Fredholm integral equations, meaning $\lambda
-\neq 0$, are preferred.
+  \label{eqn:bie}
+\end{align} where $\gg$ is the boundary condition, and $\lambda$ is a
+constant that depends on the choice of $G$. For numerical stability,
+choices of $G$ that result in second-kind Fredholm integral equations,
+meaning $\lambda \neq 0$, are preferred. Returning to electrostatics,
+equation~\eqref{eqn:bie} is analogous to Gauss's Law that relates the
+electrostatic potential on $\bd \Omega(t)$ to the surface charge
+density.
 

### 2022-11-13 NSF2022/Description/backgroundv3.tex
small fixes

@@
 elliptic PDEs} \\
-{\em Rolf Ryham (PI, Fordham University),
-Bryan Quaife (lead PI, Florida State University), and
-Yuan-Nan Young (PI, New Jersey Institute of Technology)}
+{Bryan Quaife (lead PI, Florida State University), \em Rolf Ryham (PI,
+Fordham University), and Yuan-Nan Young (PI, New Jersey Institute of
+Technology)}
 

### 2022-11-13 NSF2022/Description/broaderimpacts.tex
small fixes

@@
 
-%The proposed mathematical analysis, modeling, and numerical algorithms
-%will transform our understanding of the collective dynamics of
-%amphiphilic particles such as (1) their self-assembly into micelles and
-%bilayers, (2) the material properties of such self-assembly, and (3) the
-%interaction between these building blocks. In addition to biophysical
-%applications, amphiphilic Janus particles have recent popularity in the
-%fabrication of smart materials. The proposed work will have a
-%transformative impact on precision design for specific mechanical
-%properties of materials made of amphiphilic nanoparticles. An important
-%component of this proposal is the interdisciplinary education and
-%training of both undergraduate students, graduate students, and
-%postdoctoral fellows. The combination of mathematical modeling,
-%analysis, and scientific computing in this project provides a compelling
-%example of the importance of mathematics and computation in biophysics
-%and engineering applications. The concepts and methods described here go
-%beyond the context of amphiphilic particles and lipid molecules. They
-%extend to other problems featuring microscopic phase separation that
-%leads to formation of mesoscopic domains. This situation arises, for
-%example, in biological development in systems biology. The methods
-%developed here have the potential to impact those and other related
-%areas in biomedicine and biotechnology.
-
 \subsection{Educational Impacts}
 \label{subsec:Educational_plans}
-%The topics of this proposal have application in robotics, machine
-%learning, and engineering.
 To foster training in mathematical sciences,
@@
 from the lead institution.
-PI RR has worked side-by-side and
+PI Ryham has worked side-by-side and
 published with undergraduate coauthors in
@@
 \item Use machine learning to post-process data from the Janus particle self-assembly
-%  This project will train UR in the MATLAB and Python programming language,
-%  how to effectively deal with large data sets, and how to represent data meaningfully
-%  using plots and graphics.
 
 \item Mathematically investigate self-assembly in the zero-screen-length limit
-%  The UR will address the following conjecture about self-assembly:
-%  in the $\rho = 0$ limit, two convex polygons interacting through the hydrophobic attraction potential
-%  converge to a limit with maximally overlapping boundaries.
-%  This is a variational problem with ample numerical evidence. The student
-%  will learn elements of boundary layer analysis.
-
-%\item Implementing a fast-multipole method
-  %  The UR will adapt code written by undergraduates in \cite{RyKlYaCo16}.
-%  The will analyze the energies of bilayer configurations under the new, closed form
-%  energy and compare them to energies calculated in molecular dynamics studies.
 
@@
 
-To meaningfully engage the community,
-the PIs will prioritize students coming
-from underrepresented groups and
-specifically target students whose socio-economic
-background prevents them from participating in out-of-state research
-experiences.  PI RR will solicit applicants from Fordham University's
-Collegiate Science and Technology Entry Program.
-Students from the Bronx High School of Science (PI
-RR) and Newark Science Park High School (PI YNY) will also be encouraged to
-join the research team. PI BQ will work with undergraduates and high
+To meaningfully engage the community, the PIs will prioritize students
+coming from underrepresented groups and specifically target students
+whose socio-economic background prevents them from participating in
+out-of-state research experiences.  PI Ryham will solicit applicants
+from Fordham University's Collegiate Science and Technology Entry
+Program.  Students from the Bronx High School of Science (PI Ryham) and
+Newark Science Park High School (PI Young) will also be encouraged to
+join the research team. PI Quaife will work with undergraduates and high
 school students through the Undergraduate Research Opportunity Program
@@
 based on the ideas of the proposal.
-%The proposed research will have an immediate impact on undergraduate and
-%graduate education. At the undergraduate level, the project will include
-%and support undergraduate researchers from Fordham University. The
-%supported summer researchers will gain valuable first-hand
-%interdisciplinary experience in mathematical modeling and computation.
-%We will incorporate research into teaching, especially in differential
-%equation and programming courses. PI YNY will work on simple modeling of
-%self-assembly problems with both undergraduate and high school students
-%from Newark Science Park High School. PI YNY has a track record of
-%working with local high school students for their research projects
-%before they apply for colleges. PI BQ will work with undergraduate and
-%high school students through the Undergraduate Research Opportunity
-%Program and Young Scholar's Program as he has done in the past.
-
-%Over the past eight years, PI RR has included many undergraduates in the
-%execution of research initiatives and coauthoring publications. He has a
-%track record for supporting underrepresented groups, being called on by
-%the Collegiate Science and Technology Entry Program (CSTEP) to make
-%opportunities for promising students, for example. He has mentored two
-%Clare Boothe Luce Scholars, one a U.S.~Marine Corp veteran, and a high
-%school student in the NYU GSTEM program.
-
-%The PIs will capitalize on the synergy between both FSU's doctoral
-%program in Scientific Computing, NJIT's doctoral program in Mathematical
-%Sciences, and Fordham's undergraduate focus in the Department of
-%Mathematics. Promising, young undergraduate scientists from the Bronx
-%community will find a natural pipeline into graduate studies by working
-%directly or indirectly on this project. At the graduate-level, PI YNY
-%expects to train and support a PhD student for two more years. PI BQ
-%will advise a postdoctoral fellow for two years. The PIs will foster
-%vertical integration between the senior personnel, their collaborators,
-%postdocs, doctoral, and Bachelor students, enhancing the learning
-%environment.
-
-%The PIs expect
-%to involve undergraduate students in this project through
-%their continuing and active involvement in undergraduate advising and research mentoring:
-%YNY has mentored undergraduate students as a co-Investigator in CSUMS: Research and Education
-%in Computational Mathematics for undergraduates in the Mathematical 
-%Sciences at NJIT (funded by NSF) and the lecturer for Capstone Applied
-%Mathematics Lab at NJIT (also funded by NSF).
-%YNY has track records in involving undergraduate students in research
-%that emphasizes both numerical computations and desktop experiments.
-%
-%such as MATH 340: Advanced Numerical Methods.
-%Simple MATLAB codes have been used as teaching tools to show students how to use MATLAB
-%to simulate the slender-body equations for an elastic filament in Stokes flow.
-%
-%In the past year YNY has been mentoring Ufuomaefe Ogbe, a high school student
-%from Newark. Ufuomaefe is an African American who 
-%worked with PI on a simplified model for vesicles in flow. Based
-%on what he learned about modeling and programming, 
-%he has applied to the Applied Mathematics/Computer Science programs at both NJIT
-%and Rutgers/Newark.
 
@@
 The technical research tasks include quantifying collective properties of amphiphilic ensembles, improving on mathematical models, efficient, high-order numerical algorithms for large-scale simulations, and incorporating external fields through electric charge.
-%Lastly, the
-%proposal extends the results using three-dimensional boundary integral
-%formulations.
-
-%A central theme of the project is the mathematical development and
-%analysis of the physical model for interaction between many amphiphilic
-%particles. The model formulates the interaction potential through a
-%screened Laplace equation boundary value problem possessing the physical
-%properties like non-additivity and decay of realistic hydrophobic
-%attraction. Colloidal systems collectively self-assemble into bilayer
-%morphologies, and we analyze the elastic properties of these amphiphilic
-%particle ensembles. This allows us to interpret the Helfrich free energy
-%in terms of hydrophobic interactions and specific molecular
-%characteristics. We extend the capabilities of the boundary integral
-%equation and time stepping methods to stably perform large particle
-%number simulations in three dimensions. Results from these computations
-%will be used to compare collective amphiphilic against experiments and
-%to study the optimal design of three-dimensional functional materials.

### 2022-11-13 NSF2022/Description/priorsupport.tex

@@
 with surfactant, cholesterol, and protein.
-%Hence, there is no overlap between these grants and the current proposal.
-
-%YNY and collaborators have studied (1) asymmetry of lipid bilayer due to its interaction
-%with proteins and surfactants, (2) the electrohydrodynamics of a LBM under an
-%electric field, and (3) the coupling between LBM dynamics and a transmembrane protein,
-%such as a mechanosensitive channel.
 
@@
 {\it Broader impacts:} 
-One PhD student (Szu-Pei Fu) was funded to work with YNY, and work has
-resulted in seven papers~\cite{Nganguia2013_PoF, Nganguia2013_PRE,
-Young2014_JFM, Young2015_PoF, Nganguia2015_CiCP,
-Pak2015_PNAS,fu2015pre}. YNY has been actively involved with promotion
-of underrepresented students at NJIT. One PhD student, Herve Nganguia,
-is now an Assistant Professor at Towson University. YNY has taught a
+One PhD student (Szu-Pei Fu) was funded to work with PI Young, and work
+has resulted in seven papers~\cite{Nganguia2013_PoF, Nganguia2013_PRE,
+Young2014_JFM, Young2015_PoF, Nganguia2015_CiCP, Pak2015_PNAS,
+fu2015pre}. PI Young has been actively involved with promotion of
+underrepresented students at NJIT. One PhD student, Herve Nganguia, is
+now an Assistant Professor at Towson University. PI Young has taught a
 broad spectrum of courses in fluid mechanics and applied math modeling.
@@
 A third-year PhD student (Jake Cherry) has been assigned to this
-project. One paper will be submitted before December
-2021~\cite{che-lin-her-qua2022}.
+project. One paper has been accepted~\cite{che-lin-her-qua2022} and
+another is under review~\cite{moo-che-chi-qua2022}.
 
@@
   in quarters from the beginning of the project. The lead PI of each
-  Specific Aim will be RR (red), BQ (blue), and YNY (green).}
+  Specific Aim will be Ryham (red), Quaife (blue), and Young (green).}
 \end{wrapfigure}
@@
 \caption{Schedule for the proposed work, measured in quarters from the
-  beginning of the project. The lead PI of each Specific Aim will be RR
-  (red), BQ (blue), and YNY (green). Project management will be
-  continuous (black), but we anticipate extra attention will be
+  beginning of the project. The lead PI of each Specific Aim will be
+  Ryham (red), Quaife (blue), and Young (green). Project management will
+  be continuous (black), but we anticipate extra attention will be
   necessary to align objectives in quarters 4, 8, and 12 (magenta).}
@@
 and collaborative efforts in physics, applied mathematics, algorithms,
-and computing. PI RR has been working on mathematical modeling with a
-strong analytical background. PI YNY has been working on many areas of
+and computing. PI Ryham has been working on mathematical modeling with a
+strong analytical background. PI Young has been working on many areas of
 computational fluid dynamics and applications to math biology for many
-years. PI BQ has been working on integral equation methods, fast
+years. PI Quaife has been working on integral equation methods, fast
 algorithms, and their applications to fluid dynamics for many years.
-Their recent collaborative work on the HAP model in two
-dimensions~\cite{FuQuRyYo22} has provided a solid foundation for the
-proposed research.
+Their recent collaborative works on the granule-based vesicles in two
+dimensions~\cite{FuQuRyYo22, fu-ryh-qua-you2022} has provided a solid
+foundation for the proposed research.
 
@@
 The management responsibility of this collaborative research will reside
-with the lead PI (RR) for this endeavor. The research work is structured
-to meet the tasks discussed in \S\ref{sec:proposed-work}. The PIs,
-postdocs, and students will meet frequently on Zoom and in person when
-possible.
-%During the pandemic, the three PIs will meet weekly on Zoom
-%for a research meeting.
-Once the pandemic is under control, PI RR and PI
-YNY will conduct biweekly meetings in person, with PI BQ Zoom in from
-Florida. The PIs will share software packages, paper sources, and
-references on a common \textsf{Git} repository. The resulting software
-packages will be posted on the \textsf{Github} software repository.
+with the lead PI (Quaife) for this endeavor. The research work is
+structured to meet the tasks discussed in \S\ref{sec:proposed-work}. The
+PIs and students will meet frequently on Zoom and in person when
+possible. PI Ryham and PI Young will conduct biweekly meetings in
+person, with PI Quaife Zoom in from Florida. The PIs will share software
+packages, paper sources, and references on a common \textsf{Git}
+repository. The resulting software packages will be posted on the
+\textsf{Github} software repository.
 %

### 2022-11-13 NSF2022/Description/specificaim1v2.tex

@@
 We introduced \eqref{eq:RBT}--\eqref{eqn:stressbalance} to complement
-existing methods for studing vesicles and bilayers. 
-The simulation results in 
-(Figures \ref{fig:JPv_linearshear} and \ref{fig:JPv_rupture})
-showed that two-dimensional, granule-based vesicles replicate the 
-equilibria and hydrodynamics for continuous curves
-\cite{FuQuRyYo22, Fu2018_SIAM}.
-Our next goal is to study the model using rigorous analysis
-and consider three-dimensionsional effects.
+existing methods for studing vesicles and bilayers. The simulation
+results in (Figures~\ref{fig:JPv_linearshear} and~\ref{fig:JPv_rupture})
+show that two-dimensional, granule-based vesicles replicate the
+equilibria and hydrodynamics for continuous curves~\cite{FuQuRyYo22,
+Fu2018_SIAM}. Our next goal is to study the model using rigorous
+analysis and consider three-dimensionsional effects.
 
-The first step is to obtain some solid well-posedness results
-for \eqref{eq:RBT}--\eqref{eqn:stressbalance}.
-This system is an autonomous ordinary differential equation for
-the body transformations $F_i$
-with the rate of change defined by a system of PDEs.
-Regarding this system, in the single-well case and
-for fixed $t$, the linear system has a unique solution
-($\phi, \uu$) 
-under appropriate assumptions for the boundaries and boundary data
-\cite{manasthesis,rac-gre2016,LAX}.
-These define the instantaneous rigid body translational velocity and rotation.
+The first step is to obtain some solid well-posedness results for
+\eqref{eq:RBT}--\eqref{eqn:stressbalance}. This system is an autonomous
+ordinary differential equation for the body transformations $F_i$ with
+the rate of change defined by a system of PDEs. Regarding this system,
+in the single-well case and for fixed $t$, the linear system has a
+unique solution ($\phi, \uu$) under appropriate assumptions for the
+boundaries and boundary data~\cite{manasthesis, rac-gre2016, LAX}. These
+define the instantaneous rigid body translational velocity and rotation.
 This leads to 
 \begin{quotation}
+  \noindent
   \textbf{Problem 1.} 
-  Consider a collection the closed, disjoint granules
-  $U_i$ with smooth boundary, with no-slip, rigid body
-  motion boundary conditions, and a linear background flow.
-  Assume a single-well potential and a smooth phase field
-  boundary condition.  Study the well-posedness in
-  time of the coupled system \eqref{eq:RBT}--\eqref{eqn:stressbalance}.
+  Consider a collection the closed, disjoint granules $U_i$ with smooth
+  boundary, with no-slip, rigid body motion boundary conditions, and a
+  linear background flow. Assume a single-well potential and a smooth
+  phase field boundary condition. What is the well-posedness in time of
+  the coupled system \eqref{eq:RBT}--\eqref{eqn:stressbalance}?
 \end{quotation}
-Problem 1 involves mathematically interesting techniques.
-First, we must establish that the system has a local-in-time solution.
-This involves domain perturbations and estimates for the
-solutions of second order elliptic equations
-\cite{Savar2002DomainPA, DANERS20081, Lamboley2015EstimatesOF},
-which also find extensive application in extremal domain problems
-\cite{Schiffer1954VariationOD, Henrot2006ExtremumPF,
-  bogosel:hal-03607776,Bogosel2022OnTP}, for example.
-For global-in-time solutions,
-we can ensure positivity in time for the distance between granules
-using lubrication forces \cite{cawthorn_balmforth_2010, leal_2007}.
-Finally, we can describe the granule-flow
-behavior in the zero-screening length limit.
-In this limit, we should recover the hydrodynamics of
-a (noninteracting) rigid body suspension.
+Problem 1 involves mathematically interesting techniques. First, we
+must establish that the system has a local-in-time solution. This
+involves domain perturbations and estimates for the solutions of second
+order elliptic equations~\cite{Savar2002DomainPA, DANERS20081,
+Lamboley2015EstimatesOF}, which also find extensive application in
+extremal domain problems~\cite{Schiffer1954VariationOD,
+Henrot2006ExtremumPF, bogosel:hal-03607776,Bogosel2022OnTP}, for
+example. For global-in-time solutions, we can ensure positivity in time
+for the distance between granules using lubrication
+forces~\cite{cawthorn_balmforth_2010, leal_2007}. Finally, we can
+describe the granule-flow behavior in the zero-screening length limit.
+In this limit, we should recover the hydrodynamics of a (noninteracting)
+rigid body suspension.
 
-In the double-well potential case, \eqref{eqn:phase}
-is a nonlinear Allen-Cahn
-equation.
-This situation models granules immersed in a two-phase fluid
-(e.g. granules in an emulsion) 
-where there is an interesting interplay
-(1) the long-range alignment of granules with (2) 
-the diffusive interface energy of the free boundary
-between fluid phases.
-On unbounded domains like $\Omega(t)$,
-Allen-Cahn equations can have multiple of solutions
-\cite{Alama1997StationaryLS,Alikakos2008OnAE,Bronsard1993OnTB,
-  Byeon2014SolutionsOH, Byeon2013OnAP, Alessio2005ENTIRESI,
-  Trumper2007ExistenceOA,Benci2019MultipleSF}
-and so we must reformulate
-\eqref{eqn:phase}.
-A natural modification changes
-\eqref{eqn:phase} to an initial value problem with
-transport by the background fluid;
-\begin{equation}
+In the double-well potential case,equation~\eqref{eqn:phase} is a
+nonlinear Allen-Cahn equation. This situation models granules immersed
+in a two-phase fluid (e.g.~granules in an emulsion) where there is an
+interesting interplay between the long-range alignment of granules and
+the diffusive interface energy of the free boundary between fluid
+phases. On unbounded domains like $\Omega(t)$, Allen-Cahn equations can
+have multiple solutions~\cite{Alama1997StationaryLS,
+Alikakos2008OnAE, Bronsard1993OnTB, Byeon2014SolutionsOH, Byeon2013OnAP,
+Alessio2005ENTIRESI, Trumper2007ExistenceOA, Benci2019MultipleSF} and so
+we must reformulate~\eqref{eqn:phase}. A natural modification changes
+\eqref{eqn:phase} to an initial value problem with transport by the
+background fluid;
+\begin{align}
   \label{eqn:phase_transport}
@@
   \quad \phi(\xx,0) = \phi_0(\xx),
-\end{equation}
-for initial data $\phi_0$.
-The modified systems enjoys energy law similar to \eqref{eq:energy_law} 
-with an addtional dissipation term involving the square 
-the Euler-Lagrange derivative $\frac{\delta E}{\delta \phi}$ and dampening factor $\beta > 0$.
-There are several works dealing with the
-characterization of the geometric evolution
-of interfaces under the Allen-Cahn and Cahn-Hilliard equations
-\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF, Dai2019WeakSF,
-  Promislow2017ExistenceBA, Dai2015CompetitiveGE, Promislow2012CriticalPO,
-  Dai2022GeometricEO, Dai2020MinimizersFT,Dai2013GeometricEO,Promislow2022UndulatedBI} and
-well-posedness when coupled to flow in static domains
-\cite{Jiang2017TwophaseIF, Liu2012StrongSF, Giorgini2019WellPosednessOA,
-Wu2022WellposednessOA, Gal2010AsymptoticBO,
-Giorgini2020DiffuseIM,Giorgini2019UniquenessAR}.
-The proposed research extends these results to
-problems with moving domains.
-A closely related and strongly developing direction in
-the area of nematics liquid crystals concerns the interaction of
-Landau de Gennes functionals with colloids, and studies
-the qualitative structure of defects around single or multiple
-coloidal particles
-\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT, Alama2021SaturnRD, PhysRevE.96.042702}.
-PI Ryham has several works on membrane vesicles
-dealing both with Allen-Cahn formulations
-and fluid-vesicle interactions 
-\cite{QiangDu09, RYHAM20112929, RyCoEi12,Ryham2017OnTV}.
+\end{align}
+for initial data $\phi_0$. The modified system enjoys an energy law
+similar to~\eqref{eq:energy_law} with an addtional dissipation term
+involving the square the Euler-Lagrange derivative $\frac{\delta
+E}{\delta \phi}$ and dampening factor $\beta > 0$. There are several
+works dealing with the characterization of the geometric evolution of
+interfaces under the Allen-Cahn and Cahn-Hilliard
+equations~\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF,
+Dai2019WeakSF, Promislow2017ExistenceBA, Dai2015CompetitiveGE,
+Promislow2012CriticalPO, Dai2022GeometricEO, Dai2020MinimizersFT,
+Dai2013GeometricEO, Promislow2022UndulatedBI} and well-posedness when
+coupled to flow in static domains~\cite{Jiang2017TwophaseIF,
+Liu2012StrongSF, Giorgini2019WellPosednessOA, Wu2022WellposednessOA,
+Gal2010AsymptoticBO, Giorgini2020DiffuseIM, Giorgini2019UniquenessAR}.
+The proposed research extends these results to problems with moving
+domains. A closely related and strongly developing direction in the area
+of nematics liquid crystals concerns the interaction of Landau de Gennes
+functionals with colloids, and studies the qualitative structure of
+defects around single or multiple coloidal
+particles~\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT,
+Alama2021SaturnRD, PhysRevE.96.042702}. PI Ryham has several works on
+membrane vesicles dealing both with Allen-Cahn formulations and
+fluid-vesicle interactions~\cite{QiangDu09, RYHAM20112929, RyCoEi12,
+Ryham2017OnTV}.
 
-The second problem considers the approximation
-of elastic energy of curves and surfaces,
-and seeks to make rigorous the simulation results of
-\cite{FuQuRyYo22, Fu2018_SIAM}.
-We employ the so-called ``amphiphilic'' boundary condition
-that leads a collection of granules to form bilayers.
-Referring to Figure \ref{fig:amphiphilic_assembly}, 
-\begin{equation}
+The second problem considers the approximation of elastic energy of
+curves and surfaces, and seeks to make rigorous the simulation results
+of~\cite{FuQuRyYo22, Fu2018_SIAM}. We employ the so-called
+``amphiphilic'' boundary condition that leads to a collection of
+granules that form bilayers. Referring to
+Figure~\ref{fig:amphiphilic_assembly}, 
+\begin{align}
 \label{eq:amphiphilic_BC}
-\phi(\mathbf{x}) = h_i(\mathbf{x}) = \tfrac{1}{2}\left(\dd_i \cdot (\xx - \aa_i)/c_i + 1\right), \quad
-\mathbf{x} \in \Gamma_i,
-\end{equation}
+  \phi(\xx) = h_i(\xx) = \tfrac{1}{2}\left(\dd_i \cdot 
+    (\xx - \aa_i)/c_i + 1\right), \quad \xx \in \Gamma_i,
+\end{align}
 where $\dd_i$ is the director, $\aa_i$ is the center, and $c_i$ the
-``radius'' of the $i$th granule.  
-The phase $\phi$ takes values close to $1$ on in the direction $\dd_i$,
-representing a hydrophobic tail, and values close to $0$ 
-in the direction $\dd_i$ representing the hydrophilic head.
+``radius'' of the $i$th granule. The phase $\phi$ takes values close to
+$1$ on in the direction $\dd_i$, representing a hydrophobic tail, and
+values close to $0$ in the direction $\dd_i$ representing the
+hydrophilic head.
 
 \begin{quotation}
+  \noindent
   \textbf{Problem 2.}
-  Consider a collection of two-dimensional
-  amphiphilic granules along a closed curve $\mathbf{C}$. 
-  Study the sharp interface limit of the energy $E$ 
-  as the number of granules goes to infinity and their size to zero.
+  Consider a collection of two-dimensional amphiphilic granules along a
+  closed curve $\mathbf{C}$. What is the sharp interface limit of the
+  energy $E$ as the number of granules goes to infinity and their size
+  to zero?
 \end{quotation}
-The sharp interface model
-represent a membrane vesicle as an
+The sharp interface model represents a membrane vesicle as an
 inextensible continuous surface $\Sigma$ with elastic energy
-\begin{equation}
+\begin{align}
   \label{eq:Canham-Helfrich}
   \int_{\Sigma} k_B(H - k_0)^2\, dS,
-\end{equation}
-where $H$ is the mean curvature, $k_0$ is a spontaneous curvature,
-and $k_B$ is a bending modulus.
-One can also account for extensibility
-by including in 
-\eqref{eq:Canham-Helfrich} an additional stretching term
-$k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are the deformed and equilibrium area densitities respectively.
+\end{align}
+where $H$ is the mean curvature, $k_0$ is a spontaneous curvature, and
+$k_B$ is a bending modulus. One can also account for extensibility by
+including in~\eqref{eq:Canham-Helfrich} an additional stretching term
+$k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are
+the deformed and equilibrium area densitities respectively.
 
@@
   \vspace{-5pt}
-\caption{\label{fig:amphiphilic_assembly}
-Self-organization under amphiphilic boundary condition.
-(a) Granules first match hydrophobic tails (red),
-(b) then align length-wise.
-The principle of self-organization holds in three dimensions 
-as simulated by Kohl, Corona, and Veerapaneni
-\cite{koh-cor-che-vee2021}.}
+  \caption{\label{fig:amphiphilic_assembly} Self-organization under
+  amphiphilic boundary condition. (a) Granules first match hydrophobic
+  tails (red), (b) then align length-wise. (c) The principle of
+  self-organization holds in three dimensions as simulated by Kohl,
+  Corona, and Veerapaneni~\cite{koh-cor-che-vee2021}.}
 \end{wrapfigure}
-Bending enters through the splay of the
-granule directors.
-In Figure \ref{fig:JPv_linearshear},
-for example, the directors have negative, respectively positive,
-splay $\nabla_{\Sigma} \cdot \dd$
-in the outer, respectively inner monolayers.
-Here $\nabla_{\Sigma}\cdot{} = \nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$
-is the surface divergence for the outward unit surface normal $\NN$.
-From differential geometry, we have that 
-$\nabla\cdot \dd = \pm 2H$ whenever
-$\dd$ is everywhere parallel to $\NN,$
-and this is how the
-curvature term arises for \eqref{eq:Canham-Helfrich}.
-(For two-dimensional vesicles, the curvature $\kappa$ of the curve $\mathbf{C}$).
-Granules are at rest when attraction balances repulsion, 
-and will have stretching when the distance between
-neighboring granules is increased from rest.
+Bending enters through the splay of the granule directors. In
+Figure~\ref{fig:JPv_linearshear}, for example, the directors have
+negative, respectively positive, splay $\nabla_{\Sigma} \cdot \dd$ in
+the outer, respectively inner monolayers. Here $\nabla_{\Sigma}\cdot{} =
+\nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$ is the surface
+divergence for the outward unit surface normal $\NN$. From differential
+geometry, we have that $\nabla\cdot \dd = \pm 2H$ whenever $\dd$ is
+everywhere parallel to $\NN$, and this is how the curvature term arises
+in equation~\eqref{eq:Canham-Helfrich}. For two-dimensional vesicles,
+$H$ is replaced with the curvature $\kappa$ of the curve $\mathbf{C}$.
+Granules are at rest when attraction balances repulsion, and will have
+stretching when the distance between neighboring granules is increased
+from rest.
 
-PI Ryham has experience in the sharp interface analysis
-for phase field formulations of elastic
-bending energy \cite{0951-7715-18-3-016,Du05}, and
-topological indicators \cite{DuEuler},
-as well as for Poisson-Boltzman equations \cite{Lee2018,1531-3492_2006_2_357}.  Tools for addressing Problem 2 have
-been developed for bulk nematic liquid
-crystal potentials in the area of colloidal homogenization
-\cite{Canevari2019DesignOE,doi:10.1137/18M1163919,doi:10.1137/18M1163919, BERLYAND200597,doi:10.1137/130910348},
-and is related to 
-dimension reduction for curved nematics confined to thin films
-\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,
-doi:10.1142/S0218202516500470, FoFrLe07}.
-We start by assume circular granules aligned normally to the curve,
-and then generalize the problem to account for aspect ratio of
-elliptical granules and nonzero tilt.
+PI Ryham has experience in the sharp interface analysis for phase field
+formulations of elastic bending energy~\cite{0951-7715-18-3-016, Du05},
+and topological indicators~\cite{DuEuler}, as well as for
+Poisson-Boltzman equations~\cite{Lee2018, 1531-3492_2006_2_357}. Tools
+for addressing Problem 2 have been developed for bulk nematic liquid
+crystal potentials in the area of colloidal
+homogenization~\cite{Canevari2019DesignOE, doi:10.1137/18M1163919,
+doi:10.1137/18M1163919, BERLYAND200597, doi:10.1137/130910348}, and is
+related to dimension reduction for curved nematics confined to thin
+films~\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,
+doi:10.1142/S0218202516500470, FoFrLe07}. We start by assuming circular
+granules aligned normally to the curve, and then generalize the problem
+to account for aspect ratio of elliptical granules and nonzero tilt.
 
-Finally, to consider three-dimensionsional effects, we
-will generalize Problem 2 to \emph{numerically}
-study the energies of amphiphilic granules confined to surfaces.
-Recent work on nematics on a surface has studied
-the interplay between 
-surface geometry and a director field
-\cite{Nestler2020PropertiesOS, Nitschke2018NematicLC,
+Finally, to consider three-dimensionsional effects, we will generalize
+Problem 2 to \emph{numerically} study the energies of amphiphilic
+granules confined to surfaces. Recent work on nematics on a surface has
+studied the interplay between surface geometry and a director
+field~\cite{Nestler2020PropertiesOS, Nitschke2018NematicLC,
 Nestler2018OrientationalOO, Nitschke2019HydrodynamicII,
-  Nitschke2020LiquidCO}.
-Researchers have formulated finite element methods for
-\cite{Bartels2012FiniteEM, Nochetto2015NumericsFL,
-  Nestler2019AFE}
-  and studied minimizers
-\cite{Segatti2014EquilibriumCO,Segatti2014AnalysisOA}.
-On the other hand, in biophysics,
-\cite{Hamm2000ElasticEO,Terzi2019CurvatureTiltTO,Terzi2019ACQ,Terzi2017NovelTC,Pinigin2020NewCT} have
-derived the general Helfrich energy for lipid bilayers
-that involves effects coupling lipid tilt to 
-director splay.  This energy contains \eqref{eq:Canham-Helfrich}
-as a special case.
+Nitschke2020LiquidCO}. Researchers have formulated finite element
+methods for~\cite{Bartels2012FiniteEM, Nochetto2015NumericsFL,
+Nestler2019AFE} and studied minimizers~\cite{Segatti2014EquilibriumCO,
+Segatti2014AnalysisOA}. On the other hand, in biophysics, researchers
+have derived the general Helfrich energy for lipid bilayers that
+involves effects coupling lipid tilt to director
+splay~\cite{Hamm2000ElasticEO, Terzi2019CurvatureTiltTO, Terzi2019ACQ,
+Terzi2017NovelTC, Pinigin2020NewCT}. This energy
+contains~\eqref{eq:Canham-Helfrich} as a special case.
 \begin{quotation}
-\textbf{Problem 3.}
-Simulate surfaces made up of three-dimensional, amphilic granules.
-Numerically investigate the limiting energy for large $N_b$ simulations.
+  \noindent
+  \textbf{Problem 3.} Simulate surfaces made up of three-dimensional,
+  amphilic granules. Numerically investigate the limiting energy for
+  large $N_b$ suspensions.
 \end{quotation}
-In his much noticed Biophysical Journal
-and Nature papers~\cite{RyKlYaCo16,Chetal16}, PI Ryham
-calculated the least energy path for \emph{membrane fusion}
-using a surface-director model based on the general Helfrich energy. 
-The energy barriers calculated in~\cite{RyKlYaCo16} 
-proved consistent with later molecular dynamics
-and experimental results \cite{SmRiMu19,2017PNAS..114.1238F}.
+In his much noticed Biophysical Journal and Nature
+papers~\cite{RyKlYaCo16, Chetal16}, PI Ryham calculated the least energy
+path for \emph{membrane fusion} using a surface-director model based on
+the general Helfrich energy. The energy barriers calculated
+in~\cite{RyKlYaCo16} proved consistent with later molecular dynamics and
+experimental results~\cite{SmRiMu19, 2017PNAS..114.1238F}.
 
-The completion of Problems 1, 2, and especially 3 
-requires additional algorithmic implementation including a
-fast summation method such as the fast multipole method.
-The implementation details, in particular how we deal with large
-granule numbers and three-dimensional systems are
-described in \S \ref{sec:specificaim2} Specific Aim 2.
+The completion of Problems 1, 2, and especially 3 requires additional
+algorithmic implementation including a fast summation method such as the
+fast multipole method. The implementation details, in particular how we
+deal with large granule numbers and three-dimensional systems are
+described in Specific Aim 2 (\S\ref{sec:specificaim2}).
 %\begin{equation}

### 2022-11-13 NSF2022/Description/backgroundv2.tex

@@
 \end{wrapfigure}
-
 Computational methods to solve the PDEs~\eqref{eqn:stokes}

### 2022-11-13 NSF2022/Description/backgroundv3.tex
yny 1113a

@@
 becomes difficult due to the deformability of
-suspended media.  A dominant approach in this area,
+suspended media in the presence of non-local hydrodynamic interactions.  
+A dominant approach in this area,
 the phase field method
@@
 surface tension $\gamma$.
-When set to realistic values,
+When set to realistic values in the literature
 \cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
@@
 to~\eqref{eqn:phase} and the boundary flux transforms into viscous
-dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
+dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations. Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the self-assembly process to
+the collective dynamics of the assembly under external forcing.
 
-\begin{wrapfigure}[16]{l}{4in} 
+\begin{wrapfigure}[17]{l}{4in} 
 \includegraphics[width=4in]{figures/Background/coarsening.pdf}
@@
 \caption{\label{fig:coarsening}
-Modeling procedure.
-We initilize a suspension of granules.
+Energy $E$ in equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules versus time $t$.
 Under the moving domain problem
@@
 self-organize into vesicle bilayers.
-We then introduce external hydrodynamic effects to study elastic properties.
+External hydrodynamic effects are introduced to study elastic properties the the granules assembly \cite{Fu2018_SIAM,FuQuRyYo22}.
 }
@@
 Section \ref{sec:BroaderImpacts} summarizes the broader
-impacts and intellectual merit of our research activity.
+impacts and section \ref{sec:IntellectualMerit} summarizes the intellectual merit of our research activity.
 Section \ref{sec:proposed-work} contains our

### 2022-11-13 NSF2022/Description/broaderimpacts.tex
yny 1113a

@@
 \section{Intellectual Merit}
+\label{sec:IntellectualMerit}
 The purpose of this research is to reach interesting physical phenomena with less computational cost than molecular dynamics, and account for more general features that continuum theory misses.

### 2022-11-13 NSF2022/Description/backgroundv3.tex
fixed up graphics

@@
 zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
-U_i(t)$ (Figure~\ref{fig:flow_map}).
-Throughout, $\nnu$ refers to unit
-normal pointing into $\Omega(t)$ (Figure~\ref{fig:flow_map}).
+U_i(t)$ (Figure~\ref{fig:flow_map}). Throughout, $\nnu$ refers to unit
+normal pointing into $\Omega(t)$.
 
@@
 
-For the moving domain boundary conditions,
-equations~\eqref{eqn:noslip} specify a no-slip boundary condition for a
-rigid body with translation velocity $\aa'_i(t) = \vv_i$ and angular
-velocity $\omega_i$ (the axial vector for $R'_i(t)R_i(t)^T$)
-about the point $\aa_i(t) \in U_i(t)$. In
-equation~\eqref{eqn:material}, the function $h_i$ is a material label
-specifying the phase at water-granule interface.
-Finally, equation~\eqref{eqn:stressbalance} closes the system by requiring that
-the force and torque generated by hydrodynamic stress balances that
-generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
-parameter $\gamma > 0$ is surface tension,
-$I$ is the identity matrix,
-and we define the ``cross product'' 
-$\aa \times \bb = (\aa^{\perp} \cdot \bb) \kk$ where $\kk = (0,0,1) \in
-\RR^3$ and $(a_1,a_2)^{\perp} = (-a_2,a_1)$ whenever $\aa, \bb \in \mathbb{R}^2$.
-
-\begin{wrapfigure}[22]{r}{3.2in}
-  \vspace{-15pt}
+\begin{wrapfigure}[21]{r}{3.2in}
+  \vspace{-10pt}
   \begin{center}
@@
   \end{center}
-  \vspace{-15pt}
-  \caption{\footnotesize \label{fig:self-assembly2}
-  Changes in the boundary condition \eqref{eqn:material}
-  yield distinct morphologies.
-  Each row has the same initial configuration, $W(\phi) = \tfrac{1}{2}\phi^2$.
-  (\emph{Top}) Granules with an amphiphilic boundary condition
-  results in a bilayer pattern (yellow,
-  $\phi = 1$, blue, $\phi = 0$).
-  (\emph{Middle}) Granules with $\phi = 2$ (magenta) on one side and $\phi = 1$
-  on the other   form multilamellar bilayers.
-  (\emph{Bottom}) Bipolar granules with $\phi = \pm 1$ (yellow, green, resp.)
-  on poler ends   form a checkerboard pattern.}
+  \vspace{-20pt}
+  \caption{\footnotesize \label{fig:self-assembly2} Changes in the
+  boundary condition \eqref{eqn:material} yield distinct morphologies.
+  Each row has the same initial configuration, $W(\phi) =
+  \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
+  boundary condition results in a bilayer pattern (yellow, $\phi = 1$,
+  blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
+  on one side and $\phi = 1$ on the other form multilamellar bilayers.
+  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
+  and $\phi=-1$ (green) on the other side form a checkerboard pattern.}
 \end{wrapfigure}
+
+For the moving domain boundary conditions, equations~\eqref{eqn:noslip}
+specify a no-slip boundary condition for a rigid body with translation
+velocity $\aa'_i(t) = \vv_i$ and angular velocity $\omega_i$ (the axial
+vector for $R'_i(t)R_i(t)^T$) about the point $\aa_i(t) \in U_i(t)$. In
+equation~\eqref{eqn:material}, the function $h_i$ is a material label
+specifying the phase at water-granule interface. Finally,
+equation~\eqref{eqn:stressbalance} closes the system by requiring that
+the force and torque generated by hydrodynamic stress balances that
+generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
+parameter $\gamma > 0$ is surface tension, $I$ is the identity matrix,
+and we define the ``cross product'' $\aa \times \bb = (\aa^{\perp} \cdot
+\bb) \kk$ where $\kk = (0,0,1) \in \RR^3$ and $(a_1,a_2)^{\perp} =
+(-a_2,a_1)$ whenever $\aa, \bb \in \mathbb{R}^2$.
+
 \subsection{Applications}
-Since the framework is scale independent, it can be applied broad
-range of nonspecific self-organization phenomena in surface chemistry,
-biology and engineering. For one, the
+Since the framework is scale independent, it can be applied broad range
+of nonspecific self-organization phenomena in surface chemistry, biology
+and engineering. For one, the
 formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
-the right behavior expected from amphiphilic self-assembly.
-For example, three bodies with amphiphilic label (\S\ref{sec:specificaim1})
+the right behavior expected from amphiphilic self-assembly. For example,
+three bodies with amphiphilic label (\S\ref{sec:specificaim1})
 spontaneously self-organize to sequester the hydrophobic fluid phase
-(Figure~\ref{fig:flow_map}).
-Changes in the boundary conditions result in
-distint morphologies
-(Figure~\ref{fig:self-assembly2})
-whose rheology can be further investigate (\S\ref{sec:specificaim3}).
+(Figure~\ref{fig:flow_map}). Changes in the boundary conditions result
+in distint morphologies (Figure~\ref{fig:self-assembly2}) whose rheology
+can be further investigate (\S\ref{sec:specificaim3}).
 
@@
 
-In terms of hydrodynamics, the granule vesicles in
-background flows replicate
-the behaviour of an continous, inextensible,
-elastic vesicle with permeability.
-The simulations showed, for the first time,
-a granule-vesicle suspension behaving
-as a tank-treading vesicle \cite{Finken2008, Shaqfeh11}
-(see Figure \ref{fig:JPv_linearshear}).
-Movies of Figure \ref{fig:JPv_linearshear} reveal
-intermonolayer slip and derived values for intermonolayer
-friction were in good quantitative agreement 
-those derived by atomistic and Martini force field
-simulation studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}.
-In Figure \ref{fig:JPv_rupture},
-membrane rupture occurs at large shear rates 
-and yields a dimensional scaling for 
-critical rupture shear rate 
-\cite{VLAHOVSKA2009775,keller_skalak_1982}.
-A side-by-side comparison
-of granule-based vesicles and the sharp interface
-representation yielded shapes and trajectories that
-overlapped.
-
 \begin{wrapfigure}[10]{l}{0.46\textwidth}
 \includegraphics[width=0.46\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
-\caption{\label{fig:JPv_linearshear}Granular vesicles undergo
-tank-treading in background shear flow.}
+\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
+  undergo tank-treading in background shear flow.}
 \end{wrapfigure}
+
+In terms of hydrodynamics, the granule vesicles in background flows
+replicate the behaviour of an continous, inextensible, elastic vesicle
+with permeability. The simulations showed, for the first time, a
+granule-vesicle suspension behaving as a tank-treading vesicle
+\cite{Finken2008, Shaqfeh11} (see Figure \ref{fig:JPv_linearshear}).
+Movies of Figure \ref{fig:JPv_linearshear} reveal intermonolayer slip
+and derived values for intermonolayer friction were in good quantitative
+agreement those derived by atomistic and Martini force field simulation
+studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
+Figure \ref{fig:JPv_rupture}, membrane rupture occurs at large shear
+rates and yields a dimensional scaling for critical rupture shear rate
+\cite{VLAHOVSKA2009775,keller_skalak_1982}. A side-by-side comparison of
+granule-based vesicles and the sharp interface representation yielded
+shapes and trajectories that overlapped.
+
+\begin{wrapfigure}[14]{r}{0.475\textwidth}
+%\vspace{-10pt}
+\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
+\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
+  vesicle under large shear rates.}
+\end{wrapfigure}
+
 Having a non-specific model that replicates physical details
@@
 ~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
-\newline
+\begin{wrapfigure}[8]{l}{2.1in}
+  \vspace{-5pt}
+  \centering
+  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
+  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
+  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
+  ({\em left}) requires meshing the entire domain (typically into
+  triangles), while a BIE ({\em right}) requires meshing only the
+  boundary of the domain.}
+\end{wrapfigure}
 
 \subsection{Computational method and mathematical properties}
-\begin{wrapfigure}[14]{r}{0.475\textwidth}
-%\vspace{-10pt}
-\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
-\caption{\label{fig:JPv_rupture}Rupture of a granular vesicle under large shear rates.}
-\end{wrapfigure}
 Computational methods to solve the PDEs~\eqref{eqn:stokes}
@@
 \label{eq:energy_law}
+  \begin{split}
   \frac{d}{dt}E
   = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
-  \uu^T|^2 \,d\xx,\quad
+  \uu^T|^2 \,d\xx, \\
     E = \gamma \int_{\Omega(t)}
   \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
+  \end{split}
 \end{align}
+%\begin{align}
+%\label{eq:energy_law}
+%  \frac{d}{dt}E
+%  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
+%  \uu^T|^2 \,d\xx,\quad
+%    E = \gamma \int_{\Omega(t)}
+%  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
+%\end{align}
 Here $E$ is the energy stored in the phase transitions
@@
 the collective dynamics of the assembly under external forcing.
-
-\begin{wrapfigure}[17]{l}{4in} 
+\begin{wrapfigure}[16]{r}{4in} 
   \includegraphics[width=4in]{figures/Background/coarsening.pdf}
   \vspace{-20pt}
-\caption{\label{fig:coarsening}
-Energy $E$ in equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules versus time $t$.
-Under the moving domain problem
-\eqref{eq:RBT}-\eqref{eqn:hydro_stress}
-with amphiphilic boundary condition, the granules
-self-organize into vesicle bilayers.
-External hydrodynamic effects are introduced to study elastic properties the the granules assembly \cite{Fu2018_SIAM,FuQuRyYo22}.
-}
+  \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
+  equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules
+  versus time $t$. Under the moving domain problem
+  \eqref{eq:RBT}--\eqref{eqn:hydro_stress} with amphiphilic boundary
+  condition, the granules self-organize into vesicle bilayers. External
+  hydrodynamic effects are introduced to study elastic properties the
+  the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}
   \vspace{5pt}
 \end{wrapfigure}
+
 In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
@@
 
-\begin{wrapfigure}[10]{r}{2.1in}
-  \centering
-  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
-  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
-  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
-  ({\em left}) requires meshing the entire domain (typically into
-  triangles), while a BIE ({\em right}) requires meshing only the
-  boundary of the domain.}
-\end{wrapfigure}
 Regarding mathematical motivation for~\eqref{eq:RBT}--\eqref{eqn:stressbalance},

### 2022-11-13 NSF2022/Description/specificaim2.tex
fixed up graphics

@@
 moo-che-chi-qua2022, qua-gan-you2021}.
+\begin{wrapfigure}[16]{r}{2.1in}
+  \vspace{-8pt}
+  \centering
+  \input{figures/near_sing.tikz}
+  \vspace{-15pt}
+  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
+  quadrature method that works in two and three dimensions. The
+  spectrally-accurate trapezoid rule is used in points in
+  $\mathtt{Far}(\Gamma_i)$, while one dimensional interpolant is used
+  for points in $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength
+  spacing.}
+\end{wrapfigure}
 
@@
 analytic methods.
-
-\begin{wrapfigure}[]{r}{2.1in}
-  \centering
-  \input{figures/near_sing.tikz}
-  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
-  quadrature method that works in two and three dimensions. The
-  spectrally-accurate trapezoid rule is used in points in
-  $\mathtt{Far}(\Gamma_i)$, while one dimensional interpolant is used
-  for points in $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength
-  spacing.}
-\end{wrapfigure}
 
@@
 gimbutas2013sisc}.
+\begin{wrapfigure}[27]{l}{1.8in}
+  \vspace{-8pt}
+  \centering
+  \input{figures/doublewell.tikz} 
+  \vspace{-10pt}
+  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
+  The solution of the one-dimensional phase
+  transition~\eqref{eqn:phase}. (c) The convergence of exact and inexact
+  Newton's methods.}
+\end{wrapfigure}
 
@@
 
-\begin{wrapfigure}[27]{l}{1.8in}
-  \vspace{-8pt}
-  \centering
-  \input{figures/doublewell.tikz} 
-  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
-  The solution of the one-dimensional phase
-  transition~\eqref{eqn:phase}. (c) The convergence of exact and inexact
-  Newton's methods.}
-\end{wrapfigure}
 While the inclusion of high-order quadrature and fast methods is

### 2022-11-13 NSF2022/Description/backgroundv3.tex
fix typo
yny 1113b

@@
 
-We recently developed a new mathematical model of
+The PIs recently developed a new mathematical model of
 self-organization in fluid systems~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}.
 The framework uses small, rigid bodies called ``granules''
-to represent parcels of a suspended media.
+to represent parcels of suspended media.
 The granule shapes and boundary conditions
@@
 types of shapes and boundary conditions.
-Leveraging boundary and fast summation methods, the dynamics can be solved in 
+Leveraging boundary integral and fast summation methods, the dynamics can be solved in 
 near-linear complexity in the number of granules,
@@
 can be further investigate (\S\ref{sec:specificaim3}).
-
-A concrete application we have considered in our
+%
+A concrete application the PIs have considered in our
 SIAM Multiscale Modeling and Simulation and Journal of Fluid Mechanics works
@@
 \cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
-we recover many of the well-known
+we quantitatively recover many of the well-known
 elastic moduli for single-component lipid bilayers
 \cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}. 
+Such agreement is a validation that equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} 
+correctly capture the long-range interactions between amphiphilic granules (such as lipid macromolecules) surfaces.
 
-\begin{wrapfigure}[10]{l}{0.46\textwidth}
+\begin{wrapfigure}[9]{l}{0.46\textwidth}
+\vspace{-10pt}
 \includegraphics[width=0.46\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
+\vspace{-20pt}
 \caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
@@
 \end{wrapfigure}
-
+%
 In terms of hydrodynamics, the granule vesicles in background flows
@@
 ~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
-\begin{wrapfigure}[8]{l}{2.1in}
+\begin{wrapfigure}[9]{l}{2.1in}
   \vspace{-5pt}
@@
   \frac{d}{dt}E
-  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
+    &= - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
   \uu^T|^2 \,d\xx, \\
-    E = \gamma \int_{\Omega(t)}
+    E &= \gamma \int_{\Omega(t)}
   \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
@@
   condition, the granules self-organize into vesicle bilayers. External
-  hydrodynamic effects are introduced to study elastic properties the
+  hydrodynamic effects are introduced to study elastic properties of
   the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}

### 2022-11-13 NSF2022/Description/backgroundv3.tex
yny 1113c

@@
 \subsection{Applications}
-Since the framework is scale independent, it can be applied broad range
+Since the framework is scale independent, it can be applied to a broad range
 of nonspecific self-organization phenomena in surface chemistry, biology
@@
 %
-A concrete application the PIs have considered in our
+A concrete application the PIs have considered in their
 SIAM Multiscale Modeling and Simulation and Journal of Fluid Mechanics works

### 2022-11-13 NSF2022/Description/backgroundv3.tex
yny 1113d

@@
 
-Having a non-specific model that replicates physical details
-is the crown jewel of applied mathematics.
-\emph{Further applications} include
+%Having a non-specific model that replicates physical details
+%is the crown jewel of applied mathematics.
+The mathematical framework in equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
+are highly desirable from the applied math point of view as there are many
+\emph{Further Applications}, such as
 (i) amphiphilic Janus spheres that form diverse suprastructures
@@
 
-Regarding mathematical motivation for~\eqref{eq:RBT}--\eqref{eqn:stressbalance},
+Regarding the mathematical motivation for~\eqref{eq:RBT}--\eqref{eqn:stressbalance},
 when equation \eqref{eqn:phase} takes the form of a screened Laplace equation

### 2022-11-13 NSF2022/Description/backgroundv3.tex
new domain figure

@@
   \begin{center}
+    \includegraphics[width=\textwidth]{figures/Background/Domain.pdf}
 %    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
 %    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
-    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
-    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
+%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
+%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
   \end{center}
-  \caption{\label{fig:flow_map} \footnotesize {\em Left:} In the HAP
-  formulation~\cite{Fu2018_SIAM}, a system of exterior problems defines
-  the hydrodynamic and hydrophobic interactions. {\em Right:} Particles
-  translate and rotate to lower the free energy $E[u]$ subject
-  to~\eqref{eqn:phase}, $W(\phi) = \phi^2$, and reach a minimal
-  configuration in panel C. The colormap is blue for $\eta = 0$ and red
-  for $eta = 1$. The arrows are the velocity field $\uu$.}
+  \caption{\label{fig:flow_map} \footnotesize
+  (a) Granules make a superstructure e.g., a vesicle. The panel shows
+  the moving domain $\Omega(t)$, granules with centers $\aa_i$ and directors $\dd_i$,
+  and the unit inward normal $\nu.$ Panels b, c, d show the
+  interplay between the phase field $\phi$ (colormap) and granule configuration.
+  Red is for $\phi = 1$ and blue for $\phi = 0$; $W(\phi) = \tfrac{1}{2}\phi^2$.
+  The white arrows are the fluid velocity field.  
+  }
 \end{figure}
@@
 \begin{wrapfigure}[21]{r}{3.2in}
-  \vspace{-10pt}
+  \vspace{-15pt}
   \begin{center}
@@
 A vesicle is a small, fluid filled membrane sack.
-The goal in vesicle hydrodynamics is to study the flow patterns 
-that arrise due to the interaction
+The goal in vesicle hydrodynamics is to study flow patterns 
+arrising from the interaction
 between membrane elasticity and the fluid.
 
-A striking aspect of our hydrodynamic
-simulation is its fidelity to physics.
+\begin{wrapfigure}[11]{l}{0.48\textwidth}
+\vspace{-5pt}
+\includegraphics[width=0.48\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
+\vspace{-20pt}
+\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
+  undergo tank-treading in background shear flow.}
+\end{wrapfigure}
+%
+A striking feature of our hydrodynamic
+simulations is their fidelity to physics.
 The model contains a few
@@
 surface tension $\gamma$.
-When set to realistic values in the literature
+When set to their realistic values 
 \cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
@@
 correctly capture the long-range interactions between amphiphilic granules (such as lipid macromolecules) surfaces.
+\newpage
 
-\begin{wrapfigure}[9]{l}{0.46\textwidth}
+\begin{wrapfigure}[13]{l}{0.475\textwidth}
 \vspace{-10pt}
-\includegraphics[width=0.46\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
-\vspace{-20pt}
-\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
-  undergo tank-treading in background shear flow.}
+\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
+\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
+  vesicle under large shear rates.}
 \end{wrapfigure}
-%
 In terms of hydrodynamics, the granule vesicles in background flows
@@
 
-\begin{wrapfigure}[14]{r}{0.475\textwidth}
-%\vspace{-10pt}
-\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
-\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
-  vesicle under large shear rates.}
-\end{wrapfigure}
-
 %Having a non-specific model that replicates physical details
@@
 The mathematical framework in equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
-are highly desirable from the applied math point of view as there are many
+is highly desirable from the applied math point of view as there are many
 \emph{Further Applications}, such as
@@
 ~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
-\begin{wrapfigure}[9]{l}{2.1in}
-  \vspace{-5pt}
+
+\subsection{Computational method and mathematical properties}
+\begin{wrapfigure}[15]{r}{2.1in}
+  \vspace{-0pt}
   \centering
   \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
-  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
+  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}\\
+  \includegraphics[width=2in]{figures/Background/NSF.pdf}\\
 \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
-  ({\em left}) requires meshing the entire domain (typically into
-  triangles), while a BIE ({\em right}) requires meshing only the
-  boundary of the domain.}
+  ({\em top left}) requires meshing the entire domain (typically into
+  triangles), while a BIE ({\em top right}) requires meshing only the
+  boundary of the domain.
+  ({\em bottom}) BIE can handle intricately shaped domains as well.}
 \end{wrapfigure}
-
-\subsection{Computational method and mathematical properties}
 Computational methods to solve the PDEs~\eqref{eqn:stokes}
@@
 integrals; their discretization results in dense matrices; and they
-cannot immediately be applied to non-linear PDEs. The IE community,
-including PI Quaife, has developed a variety of tools to address these
-numerical challenges, and we discuss in \S~\ref{sec:specificaim2}.
+cannot immediately be applied to non-linear PDEs.
+\S~\ref{sec:specificaim2} discusses
+a variety of tools the IE community,
+including PI Quaife, has developed
+to address these numerical challenges.
 
@@
 system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
+%\begin{align}
+%\label{eq:energy_law}
+%  \begin{split}
+%  \frac{d}{dt}E
+%    &= - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
+%  \uu^T|^2 \,d\xx, \\
+%    E &= \gamma \int_{\Omega(t)}
+%  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
+%  \end{split}
+%\end{align}
 \begin{align}
 \label{eq:energy_law}
-  \begin{split}
   \frac{d}{dt}E
-    &= - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
-  \uu^T|^2 \,d\xx, \\
-    E &= \gamma \int_{\Omega(t)}
+  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
+  \uu^T|^2 \,d\xx,\quad
+    E = \gamma \int_{\Omega(t)}
   \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
-  \end{split}
 \end{align}
-%\begin{align}
-%\label{eq:energy_law}
-%  \frac{d}{dt}E
-%  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
-%  \uu^T|^2 \,d\xx,\quad
-%    E = \gamma \int_{\Omega(t)}
-%  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
-%\end{align}
 Here $E$ is the energy stored in the phase transitions

### 2022-11-13 NSF2022/Description/broaderimpacts.tex
suggested reviewers

@@
 \label{sec:BroaderImpacts}
-This project aims to advance the mathematical modeling of collective dynamics of amphiphilic particles.
-The simulations use a new, yet intuitive, approach that accounts for important and complex systems that are presently out of reach in computational material science.
-These complex systems include optimal shape design in metamaterials and fusion and fission of amphiphilic bilayer membranes.
-The models describing colloidal systems could be transformative in biomedicine and material science.
-The research draws from expertise in scientific computing, physics of fluids, and mathematics.
-The mathematical component incorporates leading variational techniques and offers insight into fundamentals of material science.
-The project brings socially consequential research into the classroom and offers
+This project aims to advance the mathematical modeling of collective
+dynamics of amphiphilic granules. The framework uses a new PDE-based
+formulation and fast and accurate computational techniques that account
+for important and complex systems in
+soft matter.  These complex systems include
+optimal shape design in metamaterials and fusion and fission of amphiphilic
+bilayer membranes. The models describing colloidal systems could be
+transformative in biomedicine and material science.
+The research draws from
+expertise in scientific computing, physics of fluids, and mathematics. The
+mathematical component incorporates leading variational techniques and offers
+insight into fundamentals of material science. The project brings socially
+consequential research into the classroom and offers 
 undergraduates the opportunity to train alongside faculty and graduate students.
-With its combination of mathematical modeling, analysis, and scientific computing, the project highlights the importance of mathematics and computation to all areas of science and engineering.
+With its combination of mathematical modeling, analysis, and scientific computing,
+the project highlights the importance of mathematics and computation to all areas
+of science and engineering.
 

### 2022-11-14 NSF2022/SupplementaryDocs/datamanagement.tex
adding list of reviewer files

--- 2020-11-14 NSF2020/Description/DataManagement.tex
@@
 \usepackage{todonotes}
-
+\pagestyle{empty}
 \begin{document}
@@
 \begin{center}
-\Large \bf Data Management Plan
+{\Large \bf Data Management Plan}\\
+Collaborative Research
+\begin{tabular}{ccc}\\ 
+  Florida State University & Fordham University & New Jersey Institute
+  of Technology\\
+  Bryan Quaife & Rolf Ryham & Yuan-Nan Young
+\end{tabular}
 \end{center}
@@
 simulations, and theoretical modeling. These data pertain to the
-proposed research subjects on self-assembling amphiphilic particles in
+proposed research subjects on self-assembling amphiphilic granules in
 solvent. These data will lead to quantitative understanding of the
-formation of biophysical structures and smart materials.
+formation of structures in soft matter.
 
@@
 allowed only under the consent from the PIs under the policies of
-Fordham University, Florida State University (FSU), and New Jersey
+Florida State University (FSU), Fordham University, and New Jersey
 Institute of Technology (NJIT). No sharing and access of data will be
@@
 The data can be re-used and/or re-distributed only upon the consent from
-the PIs under the policies of Fordham University, FSU, and NJIT. Any
+the PIs under the policies of FSU, Fordham University, and NJIT. Any
 derivatives from the data generated from the proposed research follow
@@
 products}
-The data will be archived following the policies of Fordham University,
-FSU, and NJIT. All samples and research products will be protected by
-Fordham University, FSU, and NJIT under the agreement with the National
-Science Foundation.
+The data will be archived following the policies of FSU, Fordham
+University, and NJIT. All samples and research products will be
+protected by FSU, Fordham University, and NJIT under the agreement with
+the National Science Foundation.
 
@@
 students with access to data will receive instruction in the Responsible
-Conduct of Research (Fordham University, FSU, and NJIT). The PIs are
+Conduct of Research (FSU, Fordham University, and NJIT). The PIs are
 responsible for enforcing the Data Management Plan outlined in this
@@
 research data and materials created or gathered in the course of the
-proposed project. The data acquired and preserved in the context of
-this proposal will be further governed by Fordham University, FSU, and
-NJIT's policies pertaining to intellectual property, record retention,
-and data
+proposed project. The data acquired and preserved in the context of this
+proposal will be further governed by FSU, Fordham University, and NJIT's
+policies pertaining to intellectual property, record retention, and data
 management.
@@
 project}
-{\bf PI Ryham}: The following summarizes the type of analytical data to
-be produced: \todo[inline]{Rolf to fill in}
-
-\noindent
 {\bf PI Quaife}: The following summarizes the type of numerical data to
@@
 
+\noindent
+{\bf PI Ryham}: The following summarizes the type of numerical data to
+be produced: (i) Matlab codes for running simulations and processing
+figures, (ii) Gnuplot code for creating manuscript figures, (iii) C++
+code for large-scale simulations, and (iv) and ASCII files of simulation
+outputs. The estimated size of these data will be under 1 TB for the
+duration of the project.
+
 \noindent {\bf PI Young}: The following summarizes the type of
@@
 osmophoresis. The estimated size of all the data is approximately 200 GB
-per year. \todo[inline]{Yuan to update. This is what was in the CBET
-proposal}
+per year.
 
@@
 following commonly accepted practices in the field. Data will be shared
-by using cloud-type storage like Dropbox if files are small or USB
-key/DVD if files are large.
+by using cloud-type storage such as Dropbox.
 

### 2022-11-14 NSF2022/SupplementaryDocs/excludedreviewers.tex
adding list of reviewer files

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{enumitem}
\pagestyle{empty}
\begin{document}
\topmargin0.25in
%\thispagestyle{empty}
\sloppy

\noindent
\today \\ \\
Dear Program Officer:
\\ \\
Professor Alex Donev (donev@courant.nyu.edu) is a competitor that is
working on similar problems to those described in the proposal entitled
``Collaborative Proposal: Self-organization modeled by moving domain
elliptic PDEs". We request that they are not chosen to review the
proposal.
\\ \\
Sincerely, \\ \\
Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

\end{document}

### 2022-11-14 NSF2022/SupplementaryDocs/suggestedreviewers.tex
adding list of reviewer files

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{enumitem}
\pagestyle{empty}
\begin{document}
\topmargin0.25in
%\thispagestyle{empty}
\sloppy

\noindent
\today \\ \\
Dear Program Officer:
\\ \\
\noindent
The following individuals have the expertise to fairly evaluate the 
proposal entitled ``Collaborative Proposal: Self-organization modeled by
moving domain elliptic PDEs". They are organized according to specific
themes of the proposed research.
\\ \\
Sincerely, \\ \\
Bryan Quaife, Rolf Ryham, and Yuan-Nan Young \\

\subsubsection*{Fluid structure interactions}
\begin{tabular}{ll}
  Suncica Canic & canics@berkeley.edu \\
  Shibin Dai & sdai4@ua.edu \\
  Giovanna Guidoboni \qquad & guidobonig@missouri.edu \\
  Keith Promislow & kpromisl@math.msu.edu
\end{tabular}

\subsubsection*{Integral Equation Methods}
\begin{tabular}{ll}
  Alex Barnett & abarnett@flatironinstitute.org \\
  Andrew Christlieb \qquad &christli@msu.edu \\
  Tony Gao & gaotong@egr.msu.edu \\
  Shuwang Li & sli@math.iit.edu \\
  John Lowengrub & jlowengr@uci.edu
\end{tabular}

\subsubsection*{Fluid Mechanics and Soft Matter}
\begin{tabular}{ll}
Silas Alben & alben@umich.edu \\
Robert Krasny & krasny@umich.edu \\
Saverio Spagnolie \qquad & spagnolie@math.wisc.edu \\
Petial Vlahovska & petia.vlahovska@northwestern.edu \\
Noel Walkington & noelw@andrew.cmu.edu 
\end{tabular}

\subsubsection*{Amphiphiles}
\begin{tabular}{ll}
Andrea Bertozzi & bertozzi@math.ucla.edu \\
Bob Guy & guy@math.ucdavis.edu \\
Alice McGillman \qquad &  \\
Mike Shelley & mshelley@flatironinstitute.org 
\end{tabular}

\end{document}

### 2022-11-14 NSF2022/Description/backgroundv3.tex
proof reading

@@
 
-Self-organization encompasses a broad range of
+The field of self-organization encompasses a broad range of
 interesting and challenging phenomena in engineering and science.
 For example, understanding the
-organization of lipids and proteins in vesicles is crucial to design
-effective drug carriers
-and functional mimics of cell membranes
+organization of lipids and proteins in vesicles is crucial to
+designing effective drug carriers
+and functional mimics of cells
 \cite{Marui2022IncreasedEO,https://doi.org/10.1002/adma.202206288}.
 The COVID-19 pandemic has led to a
-concerted, worldwide efforts to understand
-the mechanisms of RNA condensation by structural proteins protein
-oligomerization that control virus structure
+concerted effort to understand
+the mechanisms of RNA condensation by structural proteins
+that control virus structure
 \cite{Kim2021SelfassembledMV}.
@@
 Finally, researchers design efficient algorithms for
-constructing for the interaction kernels to study complex
-patterns in agent-based systems like swarms and flocking
+constructing interaction kernels in the to study 
+of agent-based systems like swarms and flocking
 \cite{Lu2019NonparametricIO,Tadmor2021OnTM}.
@@
 suspended media in the presence of non-local hydrodynamic interactions.  
-A dominant approach in this area,
-the phase field method
+The phase field method,
+a prominent approach in this area,
 introduce a scalar-valued phase
@@
 amphiphilic lipids or polymers in solvent, for example.
-Sometimes called diffuse interface
-methods, one devises energy functionals involving the gradient and
-well-potentials of the phase field, and possibly long range interaction
-kernels, 
+Sometimes called the diffuse interface
+method, one devises energy functionals involving the gradient and
+well-potentials of the phase field, and possibly convolution
+kernels, to characterize the self- and solvent-interaction of the
+suspended media 
 \cite{Promislow2022UndulatedBI,C9SM01983A,doi:10.1063/5.0009734,
 LiAn-Chang16,Choksi2003OnTD}.
-Because the fluid interfaces are given by the
-level-set of a smooth function,
+Because the fluid interfaces are given by 
+level-sets of a smooth function,
 they can have almost arbitrary topology
@@
 the evolution equations can be studied
-by well-established tools variational and analytical means,
+by well-established variational and analytical tools,
 \cite{Gavish2011CurvatureDF,Dai2019WeakSF,Dai2015CompetitiveGE,
@@
 One of the downsides, though, 
-is that granular details like molecular orientations and
-shape changes induced by proteins that may be crucial to the physics, are
-clumsy to incorporate in the model. Moreover, numerical simulations of
-phase field models typically discretize the entire fluid domain under
-consideration, and apply cutoff boundary conditions when periodic
+is that granular details like molecular heterogeneity
+and orientations that may be crucial to the physics at mesoscopic scales, are
+clumsy to incorporate in the model. Moreover,
+numerical simulations of
+phase field models typically discretize the entire fluid domain, a
+nd apply cutoff boundary conditions when periodic
 domains are not under consideration.
@@
 affording flexibility in terms of morphology and topology---sufficiently
-large forces will even pull granules apart as physically required.
+large forces will even pull groups of granules apart as physically required.
 (ii) The model formulation is built around important details like molecular orientations,
@@
 (iii) It is straightforward to consider mixtures of granules with different
-types of shapes and boundary conditions.
+shapes and boundary conditions.
 Leveraging boundary integral and fast summation methods, the dynamics can be solved in 
@@
   The white arrows are the fluid velocity field.
+  The panels reach an equilibrium state in panel d.
   }
@@
 zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
-U_i(t)$ (Figure~\ref{fig:flow_map}). Throughout, $\nnu$ refers to unit
-normal pointing into $\Omega(t)$.
+U_i(t)$ (Figure~\ref{fig:flow_map}). Throughout, $\nnu$ refers to
+the unit normal pointing into $\Omega(t)$.
 
@@
 \sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
-T_i = \gamma\left[\epsilon^{-1} W'(\phi)I
+T_i = \gamma\left[\epsilon^{-1} W(\phi)I
   + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
@@
 The scalar function $W(\phi) : \mathbb{R} \to \mathbb{R}$ is a nonnegative
-well-potential with local minima $\phi_0, \phi_1$  etc.
+well-potential with local minima $\phi_0, \phi_1$,  etc.,
 representing metastable states of the solvent.
-For the single well case, $W(\phi) = \frac{1}{2}\phi^2$
+In the single-well case, $W(\phi) = \frac{1}{2}\phi^2$
 has the minimum $\phi_0 = 0$ and the phase field equation
 \eqref{eqn:phase} becomes the \emph{linear} screened Laplace equation.
-For the double well case e.g, $W(\phi) = \frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$,
+In the double-well case e.g, $W(\phi) = \frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$,
 the phase field equation \eqref{eqn:phase} takes the form of an
@@
   boundary condition \eqref{eqn:material} yield distinct morphologies.
-  Each row has the same initial configuration, $W(\phi) =
+  Each row has the same initial configuration; $W(\phi) =
   \tfrac{1}{2}\phi^2$. (\emph{Top}) Granules with an amphiphilic
-  boundary condition results in a bilayer pattern (yellow, $\phi = 1$,
+  boundary condition form bilayer configurations (yellow, $\phi = 1$,
   blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
@@
 
-For the moving domain boundary conditions, equations~\eqref{eqn:noslip}
+For the moving domain, equations~\eqref{eqn:noslip}
 specify a no-slip boundary condition for a rigid body with translation
@@
 equation~\eqref{eqn:material}, the function $h_i$ is a material label
-specifying the phase at water-granule interface. Finally,
+specifying the phase at the solvent-granule interface. Finally,
 equation~\eqref{eqn:stressbalance} closes the system by requiring that
-the force and torque generated by hydrodynamic stress balances that
+the force and torque generated by hydrodynamic stress balances
+the force and torque 
 generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
 parameter $\gamma > 0$ is surface tension, $I$ is the identity matrix,
-and we define the ``cross product'' $\aa \times \bb = (\aa^{\perp} \cdot
+and we interpret the ``cross product'' as $\aa \times \bb = (\aa^{\perp} \cdot
 \bb) \kk$ where $\kk = (0,0,1) \in \RR^3$ and $(a_1,a_2)^{\perp} =
@@
 the right behavior expected from amphiphilic self-assembly. For example,
-three bodies with amphiphilic label (\S\ref{sec:specificaim1})
+three bodies with amphiphilic label
+(\S\ref{sec:specificaim1}, equation \eqref{eq:amphiphilic_BC})
 spontaneously self-organize to sequester the hydrophobic fluid phase
@@
 
-\begin{wrapfigure}[11]{l}{0.48\textwidth}
+\begin{wrapfigure}[10]{l}{0.48\textwidth}
 \vspace{-5pt}
@@
 surface tension $\gamma$.
-When set to their realistic values 
+When these are set to realistic values 
 \cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
@@
 Such agreement is a validation that equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} 
-correctly capture the long-range interactions between amphiphilic granules (such as lipid macromolecules) surfaces.
-\newpage
+correctly capture the
 
@@
 \end{wrapfigure}
+\noindent long-range interactions between amphiphilic
+granules (such as lipid macromolecules) surfaces.
+
 In terms of hydrodynamics, the granule vesicles in background flows
-replicate the behaviour of an continous, inextensible, elastic vesicle
-with permeability. The simulations showed, for the first time, a
+replicate the behaviour of a continous, permeable, inextensible,
+elastic vesicle.
+The simulations showed, for the first time, a
 granule-vesicle suspension behaving as a tank-treading vesicle
@@
 Movies of Figure \ref{fig:JPv_linearshear} reveal intermonolayer slip
-and derived values for intermonolayer friction were in good quantitative
+and derived values for intermonolayer friction are in good quantitative
 agreement those derived by atomistic and Martini force field simulation
@@
 granule-based vesicles and the sharp interface representation yielded
-shapes and trajectories that overlapped.
+shapes and trajectories that basically overlapped.
 
@@
 using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
-and (iv) tension drivent fabrication of microstructures
+and (iv) tension driven fabrication of microstructures
 ~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
@@
 \subsection{Computational method and mathematical properties}
-\begin{wrapfigure}[15]{r}{2.1in}
+\begin{wrapfigure}[18]{r}{3.1in}
   \vspace{-0pt}
   \centering
-  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
-  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}\\
-  \includegraphics[width=2in]{figures/Background/NSF.pdf}\\
+  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutFEM.pdf}
+  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutIE.pdf}\\
+  \includegraphics[width=3in]{figures/Background/NSF.pdf}\\
 \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
@@
 \end{wrapfigure}
-Computational methods to solve the PDEs~\eqref{eqn:stokes}
+Computational methods to solve the partial differential equations
+(PDEs)~\eqref{eqn:stokes}
 and~\eqref{eqn:phase} are challenging to develop because of
@@
 boundary of the granules rather than all of $\Omega(t)$
-(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far field
-conditions. Additional advantages of an discretizations of IE
+(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far-field
+conditions. Additional advantages of discretizations of IE
 formulations include high-order, or even spectral, accuracy and
@@
 \end{align}
-Here $E$ is the energy stored in the phase transitions
-and the energy law states that
+Here $E$ is the energy stored by the phase transitions
+between the granule boundaries and the solvent and the energy law states that
 the granules move to decrease energy,
@@
 to~\eqref{eqn:phase} and the boundary flux transforms into viscous
-dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations. Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the self-assembly process to
+dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
+In terms of self-consistency, the sum of the forces given by the
+integral of the phase stress vectors $T_i\nu$ over the granule boundaries
+is zero. 
+Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the
+self-assembly process to
 the collective dynamics of the assembly under external forcing.
+
 \begin{wrapfigure}[16]{r}{4in} 
   \includegraphics[width=4in]{figures/Background/coarsening.pdf}
-  \vspace{-20pt}
+  \vspace{-30pt}
   \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
@@
   the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}
-  \vspace{5pt}
 \end{wrapfigure}
 
-In the far field, $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ and for the
-background flow, we require that $\lim_{\xx \to \infty} \uu(\xx) -
+We have $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ in the far field
+and when
+background flows are involved, we require that $\lim_{\xx \to \infty} \uu(\xx) -
 \uu_{\infty}(\xx) = \mathbf{0}$, where
-the background flow takes the form
+$\uu_{\infty}$ can take the form
 %In the case of shear background flow,
@@
 %background flows include
-shear, extensional, parabolic Poiseuille, and
+of a shear, extensional, parabolic Poiseuille, or
 Taylor-Green flow, for example.
-For numerical stability and physical realism, we
+For numerical stability, we
 include pairwise repulsive forces and torques
-in~\eqref{eqn:stressbalance} to prevent the collision between
-neighboring granules which introduces a repulsive potential in the energy
-law~\eqref{eq:energy_law}. Background flow adds elastic energy to the
-granule configurations.
+in~\eqref{eqn:stressbalance} to prevent the near-collision between
+neighboring granules.  This introduces a repulsive potential in the energy
+law~\eqref{eq:energy_law}.
+Background flow adds elastic energy to the granule configurations,
+as illustrated in Figure \ref{fig:coarsening}.
 %and is quantified by simulation. We refer to the
@@
 one-dimensional version of our model was carried out using a Landau
-expansion of the free energy density for a single-well
-potential~\cite{MaRa76, ErLjCl89}. The double-well potential case was
+expansion for a single-well potential~\cite{MaRa76, ErLjCl89}.
+The double-well potential case was
 considered by Gompper~\cite{GoHaKo94} to describe metastable
@@
 everywhere, then $\phi$ has a boundary layer going from $1$ at the
-boundary to $0$ in the bulk and one can prove that 
+boundary to $0$ so that 
 $\lim_{\epsilon \to 0} E = \frac{1}{2}\gamma |\partial \Omega|$.
@@
 Section \ref{sec:proposed-work} contains our
-three specific aims.  They are
-mathematical analysis of the system
-(\S \ref{sec:specificaim1}: PI Ryham),
-numerical implementation
-(\S \ref{sec:specificaim2}: PI Quaife),
-and  kinetic theory
-(\S \ref{sec:specificaim3}: PI Young).
+specific aims.

### 2022-11-14 NSF2022/Description/specificaim1v2.tex
proof reading

@@
 \label{sec:proposed-work}
-
+The three specific aims of this proposal are
+mathematical analysis of the system
+and three-dimensional energies
+(\S \ref{sec:specificaim1}: PI Ryham),
+numerical implementation for large granule-number
+and three dimensional suspensions
+(\S \ref{sec:specificaim2}: PI Quaife),
+and kinetic theory
+(\S \ref{sec:specificaim3}: PI Young).
 \subsection{Specific Aim 1: Membrane vesicles as self-organized granules}
@@
 
-\begin{wrapfigure}[12]{r}{0.5\textwidth}
-  \vspace{-5pt}
+\begin{wrapfigure}[11]{r}{0.5\textwidth}
+  \vspace{-8pt}
   \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
-  \vspace{-5pt}
-  \caption{\label{fig:amphiphilic_assembly} Self-organization under
-  amphiphilic boundary condition. (a) Granules first match hydrophobic
-  tails (red), (b) then align length-wise. (c) The principle of
-  self-organization holds in three dimensions as simulated by Kohl,
-  Corona, and Veerapaneni~\cite{koh-cor-che-vee2021}.}
+  \vspace{-8pt}
+  \caption{\label{fig:amphiphilic_assembly} \footnotesize
+  Self-organization under amphiphilic boundary condition. (a) Granules
+  first match hydrophobic tails (red), (b) then align length-wise. (c)
+  The principle of self-organization holds in three dimensions as
+  simulated by Kohl, Corona, and
+  Veerapaneni~\cite{koh-cor-che-vee2021}.}
 \end{wrapfigure}
@@
 
-PI Ryham has experience in the sharp interface analysis for phase field
+PI Ryham has carried out sharp interface-limit analyses for phase field
 formulations of elastic bending energy~\cite{0951-7715-18-3-016, Du05},

### 2022-11-14 NSF2022/Description/backgroundv3.tex
proofed SA1

@@
 parameters; granule radius $c$,
-screening length $\epsilon$,
+decay length $\epsilon$,
 surface tension $\gamma$.
@@
 dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
-In terms of self-consistency, the sum of the forces given by the
-integral of the phase stress vectors $T_i\nu$ over the granule boundaries
-is zero. 
+Furthermore, the integral of the 
+phase stress vectors $T_i\nu$ over $\partial \Omega$ is zero.
 Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the

### 2022-11-14 NSF2022/Description/specificaim1v2.tex
proofed SA1

--- 2022-11-13 NSF2022/Description/specificaim1v2.tex
@@
 \label{sec:proposed-work}
-
+The specific aims of this proposal are
+mathematical analysis and three-dimensional energies
+(\S \ref{sec:specificaim1}: PI Ryham),
+numerical implementation for large granule-number
+and three-dimensional suspensions
+(\S \ref{sec:specificaim2}: PI Quaife),
+and kinetic theory
+(\S \ref{sec:specificaim3}: PI Young).
 \subsection{Specific Aim 1: Membrane vesicles as self-organized granules}
@@
 ordinary differential equation for the body transformations $F_i$ with
-the rate of change defined by a system of PDEs. Regarding this system,
-in the single-well case and for fixed $t$, the linear system has a
+the rate of change defined by a system of PDEs. Regarding the PDE system,
+in the linear case and for fixed $t$, there is a
 unique solution ($\phi, \uu$) under appropriate assumptions for the
 boundaries and boundary data~\cite{manasthesis, rac-gre2016, LAX}. These
-define the instantaneous rigid body translational velocity and rotation.
-This leads to 
+define instantaneous rigid body velocities and rotations,
+leading to 
 \begin{quotation}
@@
 Henrot2006ExtremumPF, bogosel:hal-03607776,Bogosel2022OnTP}, for
-example. For global-in-time solutions, we can ensure positivity in time
-for the distance between granules using lubrication
-forces~\cite{cawthorn_balmforth_2010, leal_2007}. Finally, we can
-describe the granule-flow behavior in the zero-screening length limit.
-In this limit, we should recover the hydrodynamics of a (noninteracting)
-rigid body suspension.
+example. For global-in-time solutions, we can 
+use lubrication forces~\cite{cawthorn_balmforth_2010, leal_2007}.
+Here, the lubrication force required to bring granules into contact
+blows up with distance, whereas the attraction \eqref{eqn:stressbalance}
+is finite, guaranteeing positivity in the distance between granules.
+Finally, we can study the granule-flow behavior in the zero-decay length
+limit. This limit should recover the hydrodynamics of a (noninteracting)
+rigid-body suspension.
 
-In the double-well potential case,equation~\eqref{eqn:phase} is a
+In the double-well potential case, equation~\eqref{eqn:phase} is a
 nonlinear Allen-Cahn equation. This situation models granules immersed
@@
 Alessio2005ENTIRESI, Trumper2007ExistenceOA, Benci2019MultipleSF} and so
-we must reformulate~\eqref{eqn:phase}. A natural modification changes
-\eqref{eqn:phase} to an initial value problem with transport by the
-background fluid;
+we must reformulate~\eqref{eqn:phase}. An appropriate reformulation
+is the following initial value problem with transport:
 \begin{align}
@@
 Promislow2012CriticalPO, Dai2022GeometricEO, Dai2020MinimizersFT,
-Dai2013GeometricEO, Promislow2022UndulatedBI} and well-posedness when
-coupled to flow in static domains~\cite{Jiang2017TwophaseIF,
+Dai2013GeometricEO, Promislow2022UndulatedBI} and well-posedness
+results when coupled to flow in static domains~\cite{Jiang2017TwophaseIF,
 Liu2012StrongSF, Giorgini2019WellPosednessOA, Wu2022WellposednessOA,
@@
 of~\cite{FuQuRyYo22, Fu2018_SIAM}. We employ the so-called
-``amphiphilic'' boundary condition that leads to a collection of
-granules that form bilayers. Referring to
+``amphiphilic'' boundary condition that leads a collection of
+granules to form bilayers. Referring to
 Figure~\ref{fig:amphiphilic_assembly}, 
@@
 ``radius'' of the $i$th granule. The phase $\phi$ takes values close to
-$1$ on in the direction $\dd_i$, representing a hydrophobic tail, and
+$1$ in the direction $\dd_i$, representing a hydrophobic tail, and
 values close to $0$ in the direction $\dd_i$ representing the
@@
   Consider a collection of two-dimensional amphiphilic granules along a
-  closed curve $\mathbf{C}$. What is the sharp interface limit of the
+  closed curve $\mathcal{C}$. What is the sharp interface limit of the
   energy $E$ as the number of granules goes to infinity and their size
@@
 \end{quotation}
-The sharp interface model represents a membrane vesicle as an
-inextensible continuous surface $\Sigma$ with elastic energy
+
+\begin{wrapfigure}[11]{r}{0.5\textwidth}
+  \vspace{-8pt}
+  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
+  \vspace{-8pt}
+  \caption{\label{fig:amphiphilic_assembly} \footnotesize
+  Self-organization under amphiphilic boundary condition. (a) Granules
+  first match hydrophobic tails (red), (b) then align length-wise. (c)
+  The same pattern of self-organization holds in three dimensions, as
+  simulated by Kohl, Corona, and
+  Veerapaneni~\cite{koh-cor-che-vee2021}.}
+\end{wrapfigure}
+
+Sharp interface models represent a membrane vesicle as an
+inextensible, continuous, closed surface $\Sigma$ with elastic energy
 \begin{align}
@@
 
-\begin{wrapfigure}[12]{r}{0.5\textwidth}
-  \vspace{-5pt}
-  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
-  \vspace{-5pt}
-  \caption{\label{fig:amphiphilic_assembly} Self-organization under
-  amphiphilic boundary condition. (a) Granules first match hydrophobic
-  tails (red), (b) then align length-wise. (c) The principle of
-  self-organization holds in three dimensions as simulated by Kohl,
-  Corona, and Veerapaneni~\cite{koh-cor-che-vee2021}.}
-\end{wrapfigure}
-Bending enters through the splay of the granule directors. In
+In the case of granules, bending enters through the
+splay of the granule directors. In
 Figure~\ref{fig:JPv_linearshear}, for example, the directors have
@@
 geometry, we have that $\nabla\cdot \dd = \pm 2H$ whenever $\dd$ is
-everywhere parallel to $\NN$, and this is how the curvature term arises
-in equation~\eqref{eq:Canham-Helfrich}. For two-dimensional vesicles,
-$H$ is replaced with the curvature $\kappa$ of the curve $\mathbf{C}$.
+everywhere parallel to $\NN$, and this is how curvature enters
+the granule-based description.  For two-dimensional vesicles,
+$H$ is replaced with the curvature $\kappa$ of the curve $\mathcal{C}$.
 Granules are at rest when attraction balances repulsion, and will have
-stretching when the distance between neighboring granules is increased
+stretching energy when the distance between neighboring granules is increased
 from rest.
 
-PI Ryham has experience in the sharp interface analysis for phase field
-formulations of elastic bending energy~\cite{0951-7715-18-3-016, Du05},
-and topological indicators~\cite{DuEuler}, as well as for
-Poisson-Boltzman equations~\cite{Lee2018, 1531-3492_2006_2_357}. Tools
-for addressing Problem 2 have been developed for bulk nematic liquid
+Tools for addressing Problem 2 have been developed for bulk nematic liquid
 crystal potentials in the area of colloidal
 homogenization~\cite{Canevari2019DesignOE, doi:10.1137/18M1163919,
-doi:10.1137/18M1163919, BERLYAND200597, doi:10.1137/130910348}, and is
-related to dimension reduction for curved nematics confined to thin
-films~\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,
-doi:10.1142/S0218202516500470, FoFrLe07}. We start by assuming circular
-granules aligned normally to the curve, and then generalize the problem
-to account for aspect ratio of elliptical granules and nonzero tilt.
+  doi:10.1137/18M1163919, BERLYAND200597, doi:10.1137/130910348}, and
+the problem is closely related to dimension reduction for curved nematics
+confined to thin films~\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,
+  doi:10.1142/S0218202516500470, FoFrLe07}.
+PI Ryham has carried out sharp interface-limit analyses for phase field
+formulations of elastic bending energy~\cite{0951-7715-18-3-016, Du05},
+approximations of Gaussian curvature and the Euler characteristic in
+phase field~\cite{DuEuler}, and vanishing Debye-length in 
+Poisson-Boltzman equations~\cite{Lee2018, 1531-3492_2006_2_357}.
 
@@
 Problem 2 to \emph{numerically} study the energies of amphiphilic
-granules confined to surfaces. Recent work on nematics on a surface has
+granules confined to surfaces. Recent works on nematics on a surface have
 studied the interplay between surface geometry and a director
@@
 Nitschke2020LiquidCO}. Researchers have formulated finite element
-methods for~\cite{Bartels2012FiniteEM, Nochetto2015NumericsFL,
+methods~\cite{Bartels2012FiniteEM, Nochetto2015NumericsFL,
 Nestler2019AFE} and studied minimizers~\cite{Segatti2014EquilibriumCO,
-Segatti2014AnalysisOA}. On the other hand, in biophysics, researchers
-have derived the general Helfrich energy for lipid bilayers that
-involves effects coupling lipid tilt to director
+Segatti2014AnalysisOA}. In biophysics, researchers
+have derived the generalized Helfrich energy for lipid bilayers that
+involves coupling effects between lipid tilt to director
 splay~\cite{Hamm2000ElasticEO, Terzi2019CurvatureTiltTO, Terzi2019ACQ,
-Terzi2017NovelTC, Pinigin2020NewCT}. This energy
-contains~\eqref{eq:Canham-Helfrich} as a special case.
+  Terzi2017NovelTC, Pinigin2020NewCT}. It contains~\eqref{eq:Canham-Helfrich}
+as a special case.
 \begin{quotation}
@@
   amphilic granules. Numerically investigate the limiting energy for
-  large $N_b$ suspensions.
+  large-$N_b$ suspensions.
 \end{quotation}
-In his much noticed Biophysical Journal and Nature
-papers~\cite{RyKlYaCo16, Chetal16}, PI Ryham calculated the least energy
-path for \emph{membrane fusion} using a surface-director model based on
+We will study Problem 3 by simulating large granule-number membranes.
+If, after thoroughly sampling shapes and boundary conditions,
+it turns out that the granule energies are not described by
+a nematic or  Helfrich-type energy, then we will change
+hypotheses and look for alternative sharp interface elastic energies.
+PI Ryham is well-qualified to perform this investigation.
+In the much noticed Biophysical Journal and Nature
+papers~\cite{RyKlYaCo16, Chetal16}, he calculated least energy
+paths for \emph{membrane fusion} using a surface-director model based on
 the general Helfrich energy. The energy barriers calculated
@@
 described in Specific Aim 2 (\S\ref{sec:specificaim2}).
+
 %\begin{equation}

### 2022-11-14 NSF2022/Description/specificaim1v2.tex
...

@@
 \label{sec:proposed-work}
-The specific aims of this proposal are
-mathematical analysis and three-dimensional energies
+This proposal is an outgrowth of the 
+PIs' ongoing successful collaboration.
+Building off complementary expertises,
+the specific aims of this proposal are:
+mathematical analysis and three-dimensional
+membrane energies
 (\S \ref{sec:specificaim1}: PI Ryham),
-numerical implementation for large granule-number
+BIE implementation for large granule-number
 and three-dimensional suspensions
@@
 paths for \emph{membrane fusion} using a surface-director model based on
-the general Helfrich energy. The energy barriers calculated
-in~\cite{RyKlYaCo16} proved consistent with later molecular dynamics and
-experimental results~\cite{SmRiMu19, 2017PNAS..114.1238F}.
+the general Helfrich energy. The energy barriers 
+proved consistent with later results from molecular dynamic
+simulation and experiment~\cite{SmRiMu19, 2017PNAS..114.1238F}.
 

### 2022-11-14 NSF2022/Description/specificaim2.tex
...
SA2 proofed

@@
   Reynolds2019, Cho2010}.
-Hydrodynamic effects cannot be ignored since
-they, like for the rates of biological functions like pore
-dynamics~\cite{RYHAM20112929}, set the rate of dissipation. The success
+%Hydrodynamic effects cannot be ignored since
+%they, like for the rates of biological functions like pore
+%dynamics~\cite{RYHAM20112929}, set the rate of dissipation.
+The success
 of Specific Aims 1 and 3 depends on the ability to accurately and
@@
 as a convolution 
-\begin{align*}
+\begin{align}
   \uu(\xx) = \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
-\end{align*}
+  \label{eqn:conv}
+\end{align}
 where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
 fundamental solution and $\ssigma: \partial \Omega(t) \rightarrow \RR^2$
-is an unknown density function. This is analogous to the problem of
-finding the global electrostatic potential $u$ with surface charge
-density $\sigma$
-\begin{align*}
-  u(x) = -\frac{1}{4\pi}\int_{\partial \Omega(t)} 
-    \frac{1}{|\xx - \yy|}\sigma(y) \, ds_\yy.
-\end{align*}
-
+is an unknown density function.
+%This is analogous to the problem of
+%finding the global electrostatic potential $u$ with surface charge
+%density $\sigma$
+%\begin{align*}
+%  u(x) = -\frac{1}{4\pi}\int_{\partial \Omega(t)} 
+%    \frac{1}{|\xx - \yy|}\sigma(y) \, ds_\yy.
+%\end{align*}
 The IE reformulation has several immediate advantages including a
@@
 choices of $G$ that result in second-kind Fredholm integral equations,
-meaning $\lambda \neq 0$, are preferred. Returning to electrostatics,
-equation~\eqref{eqn:bie} is analogous to Gauss's Law that relates the
-electrostatic potential on $\bd \Omega(t)$ to the surface charge
-density.
+meaning $\lambda \neq 0$, are preferred.
+
+As an illustration, the problem of finding the global
+electrostatic potential $u$ with surface
+charge density $\sigma$ is a special case of \eqref{eqn:conv}, where
+$G(\xx - \yy) = (4\pi \epsilon_0)^{-1}|\xx - \yy|^{-1}$
+in three dimensions
+($-(2\pi \epsilon_0)^{-1}\log|\xx - \yy|$ in two dimensions)
+with $\epsilon_0$ the permittivity of vacuum.  In this context, 
+~\eqref{eqn:bie} is analogous to Gauss's Law.
 
@@
 
-\begin{wrapfigure}[]{l}{2.1in}
+\begin{wrapfigure}[]{l}{2.6in}
   \centering
-  \includegraphics[width=2in]{figures/SA2Figures/confinement.pdf}
+  \includegraphics[width=2.5in]{figures/SA2Figures/confinement.pdf}
   \caption{\label{fig:stenosis} \footnotesize A granule vesicle passing
@@
 two-dimensional PDEs~\cite{che-lin-her-qua2022}. The method uses
-singularity subtraction write the fundamental solution of the PDE as a
+singularity subtraction to write the fundamental solution of the PDE as a
 sum of two terms: a logarithmic function and a continuously
@@
 of layer potentials~\cite{car2021, car2020, car-kha-kim2018} which is
-required, for example, when computing the water-order
+required, for example, when computing the phase
 stress~\eqref{eqn:stressbalance}. Singularity subtraction methods can
@@
 gimbutas2013sisc}.
-\begin{wrapfigure}[27]{l}{1.8in}
-  \vspace{-8pt}
-  \centering
-  \input{figures/doublewell.tikz} 
-  \vspace{-10pt}
-  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
-  The solution of the one-dimensional phase
-  transition~\eqref{eqn:phase}. (c) The convergence of exact and inexact
-  Newton's methods.}
-\end{wrapfigure}
 
@@
 computational tool is a collision-aware adaptive time stepping method.
-The order parameter results in the granules attracting one another and
-this leads to physical contact in finite time. Our current
+The phase field results in the granules attracting one another and
+this leads to nearly contacting boundaries. Our current
 implementation uses a repulsive Lennard-Jones force, but this introduces
 stiffness, thereby requiring small time steps, and this can be a
-bottleneck when simulating dense suspensions. Therefore, we will develop
+bottleneck when 
+\begin{wrapfigure}[26]{l}{1.8in}
+  \vspace{-0pt}
+  \centering
+  \input{figures/doublewell.tikz} 
+  \vspace{-10pt}
+  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
+  The solution of the one-dimensional phase
+  transition~\eqref{eqn:phase}. (c) The convergence of exact and inexact
+  Newton's methods.}
+\end{wrapfigure}
+simulating dense suspensions. Therefore, we will develop
 a high-order collision-avoiding adaptive time stepping method. This
-method will avoid collisions with by using the minimal separation
+method will avoid collisions by using the minimal separation
 distance to impose a non-overlapping constraint. This results in a
@@
 
-The order parameter is governed by the PDE~\eqref{eqn:phase} in the
-solvent phase $\Omega(t)$. If $W(\phi) = \phi^2$,
+The phase field is governed by the PDE~\eqref{eqn:phase} in the
+solvent region $\Omega(t)$. If $W(\phi) = \tfrac{1}{2}\phi^2$,
 equation~\eqref{eqn:phase} is linear, and the PIs have used IEs to solve
-for the order parameter~\cite{Fu2018_SIAM, FuQuRyYo22,
+address this problem~\cite{Fu2018_SIAM, FuQuRyYo22,
 fu-ryh-qua-you2022}, but for a double-well potential $W(\phi)$, the
@@
   \label{eqn:phaseRoot}
-  F[\phi] = -\epsilon^2 \Delta \phi + \tfrac{1}{2}W'(\phi).
+  F[\phi] = -\epsilon^2 \Delta \phi + W'(\phi).
 \end{align}
@@
 $\phi^{N+1} = \phi^{N} - \alpha (F'(\phi^N))^{-1} F(\phi^N)$, where
-$F'(\phi^N) = -\epsilon^2 \Delta + \tfrac{1}{2}W''(\phi^N)$ is the
+$F'(\phi^N) = -\epsilon^2 \Delta + W''(\phi^N)$ is the
 Fr\'{e}chet derivative of $F$, and $\alpha$ is the step size that will
 be determined using backtracking. This requires solving the variable
-coefficient PDE $-\epsilon^2 \Delta v + \tfrac{1}{2}W''(\phi^{N}) v =
+coefficient PDE $-\epsilon^2 \Delta v + W''(\phi^{N}) v =
 F[\phi^N]$, which is challenging with an integral equation since a
@@
 approximated with the solution of $-\epsilon^2 \Delta v +
-\tfrac{\beta}{2} v = F[\phi^N]$. We test the efficacy of the exact and
+\beta v = F[\phi^N]$. We test the efficacy of the exact and
 inexact Newton's method applied to~\eqref{eqn:phaseRoot} in $(0,1)
@@
 solve~\eqref{eqn:phaseRoot} in two and three dimensions. The solution of
-$-\epsilon^2 \Delta v + \tfrac{\beta}{2} v = F[\phi^N]$ can be written
+$-\epsilon^2 \Delta v + \beta v = F[\phi^N]$ can be written
 as $v = v^P + v^H$ where $v^P$ is a volume potential and $v^H$ is a
@@
 where $G$ is the fundamental solution of $-\epsilon^2 \Delta +
-\tfrac{\beta}{2}$. Traditionally, volume potentials are more challenging
+\beta$. Traditionally, volume potentials are more challenging
 to compute than layer potentials, but new methods have recently been
@@
 efficiently~\cite{fry-leh-tor2018, and-zhu-vee2022}. This approach of
-combining volume and layer potentials has successfully been used by PI
+combining volume and layer potentials has been successfully used by PI
 Quaife~\cite{kro-qua2010} and others~\cite{fry-kro-tor2019,

### 2022-11-14 NSF2022/Description/backgroundv3.tex

@@
 
-The field of self-organization encompasses a broad range of
-interesting and challenging phenomena in engineering and science.
-For example, understanding the
-organization of lipids and proteins in vesicles is crucial to
-designing effective drug carriers
-and functional mimics of cells
-\cite{Marui2022IncreasedEO,https://doi.org/10.1002/adma.202206288}.
-The COVID-19 pandemic has led to a
-concerted effort to understand
-the mechanisms of RNA condensation by structural proteins
-that control virus structure
-\cite{Kim2021SelfassembledMV}.
-Engineers have developed superior techniques
-that rely on nanoscale  
-capillary and van der Waals forces
-to print high-resolution
-features on devices \cite{Zeng20223DprintedMT}.
-Finally, researchers design efficient algorithms for
-constructing interaction kernels in the to study 
-of agent-based systems like swarms and flocking
-\cite{Lu2019NonparametricIO,Tadmor2021OnTM}.
+The field of self-organization encompasses a broad range of interesting
+and challenging phenomena in engineering and science. For example,
+understanding the organization of lipids and proteins in vesicles is
+crucial to designing effective drug carriers and functional mimics of
+cells~\cite{Marui2022IncreasedEO,
+https://doi.org/10.1002/adma.202206288}. The COVID-19 pandemic has led
+to a concerted effort to understand the mechanisms of RNA condensation
+by structural proteins that control virus
+structure~\cite{Kim2021SelfassembledMV}. Engineers have developed
+superior techniques that rely on nanoscale capillary and van der Waals
+forces to print high-resolution features on
+devices~\cite{Zeng20223DprintedMT}. Finally, researchers design
+efficient algorithms for constructing interaction kernels in the to
+study of agent-based systems like swarms and
+flocking~\cite{Lu2019NonparametricIO, Tadmor2021OnTM}.
 
@@
 
-When fluids are involved,
-tracking self-organization
-becomes difficult due to the deformability of
-suspended media in the presence of non-local hydrodynamic interactions.  
-The phase field method,
-a prominent approach in this area,
-introduce a scalar-valued phase
-field function for the volume fraction of
-amphiphilic lipids or polymers in solvent, for example.
-Sometimes called the diffuse interface
-method, one devises energy functionals involving the gradient and
-well-potentials of the phase field, and possibly convolution
-kernels, to characterize the self- and solvent-interaction of the
-suspended media 
-\cite{Promislow2022UndulatedBI,C9SM01983A,doi:10.1063/5.0009734,
-LiAn-Chang16,Choksi2003OnTD}.
-Because the fluid interfaces are given by 
-level-sets of a smooth function,
-they can have almost arbitrary topology
-e.g., free ends, junctions
-\cite{Promislow2017ExistenceBA,Promislow2022UndulatedBI},
-the evolution equations can be studied
-by well-established variational and analytical tools,
-\cite{Gavish2011CurvatureDF,Dai2019WeakSF,Dai2015CompetitiveGE,
-Dai2022GeometricEO,Dai2020MinimizersFT,Dai2013GeometricEO},
-and the governing equations are amenable to numerical approximation
-\cite{Christlieb2020BenchmarkCO,Christlieb2019CompetitionAC}.
-One of the downsides, though, 
-is that granular details like molecular heterogeneity
-and orientations that may be crucial to the physics at mesoscopic scales, are
-clumsy to incorporate in the model. Moreover,
-numerical simulations of
-phase field models typically discretize the entire fluid domain, a
-nd apply cutoff boundary conditions when periodic
-domains are not under consideration.
+When fluids are involved, tracking self-organization becomes difficult
+due to the deformability of suspended media in the presence of non-local
+hydrodynamic interactions. The phase field method, a prominent approach
+in this area, introduces a scalar-valued phase field function for the
+volume fraction of amphiphilic lipids or polymers in solvent, for
+example. Sometimes called the diffuse interface method, one devises
+energy functionals involving the gradient and well-potentials of the
+phase field, and possibly convolution kernels, to characterize the self-
+and solvent-interaction of the suspended
+media~\cite{Promislow2022UndulatedBI, C9SM01983A,doi:10.1063/5.0009734,
+LiAn-Chang16, Choksi2003OnTD}. Because the fluid interfaces are given by
+level-sets of a smooth function, they can have almost arbitrary topology
+e.g., free ends, junctions~\cite{Promislow2017ExistenceBA,
+Promislow2022UndulatedBI}, the evolution equations can be studied by
+well-established variational and analytical
+tools~\cite{Gavish2011CurvatureDF, Dai2019WeakSF, Dai2015CompetitiveGE,
+Dai2022GeometricEO, Dai2020MinimizersFT, Dai2013GeometricEO}, and the
+governing equations are amenable to numerical
+approximation~\cite{Christlieb2020BenchmarkCO,
+Christlieb2019CompetitionAC}. One of the downsides, though, is that
+granular details like molecular heterogeneity and orientations that may
+be crucial to the physics at mesoscopic scales, are clumsy to
+incorporate in the model. Moreover, numerical simulations of phase field
+models typically discretize the entire fluid domain, and apply cutoff
+boundary conditions when periodic domains are not under consideration.
 
-The PIs recently developed a new mathematical model of
-self-organization in fluid systems~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}.
-The framework uses small, rigid bodies called ``granules''
-to represent parcels of suspended media.
-The granule shapes and boundary conditions
-capture the local properties of the suspension,
-and instead of volume fraction, a phase field function represents
-the properties of the solvent.
-Our approach falls into the category of work that considers
-particles as a discretization of a continuous problem;
-in this case one is dealing with a particle
-method, as an alternative to other discretization methods
-such as finite-difference, finite-element, and spectral methods
-\cite{Wilson2021ComparisonOT}.
-We have departed from the terminology
-``particles'', though, to emphasize the role played the granules' finite size.
+The PIs recently developed a new mathematical model of self-organization
+in fluid systems~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM}. The
+framework uses small, rigid bodies called ``granules'' to represent
+parcels of suspended media. The granule shapes and boundary conditions
+capture the local properties of the suspension, and instead of volume
+fraction, a phase field function represents the properties of the
+solvent. Our approach falls into the category of work that considers
+particles as a discretization of a continuous problem; in this case one
+is dealing with a particle method, as an alternative to other
+discretization methods such as finite-difference, finite-element, and
+spectral methods~\cite{Wilson2021ComparisonOT}. We have departed from
+the terminology ``particles'', though, to emphasize the role played the
+granules' finite size.
 
-The framework is robust, flexible, and
-cuts across many of the aforementioned challenges.
-(i) The granules are not fixed to a stencil, 
+The framework is robust, flexible, and cuts across many of the
+aforementioned challenges. (i) The granules are not fixed to a stencil,
 affording flexibility in terms of morphology and topology---sufficiently
-large forces will even pull groups of granules apart as physically required.
-(ii) The model formulation is built around important details like molecular orientations,
-and exhibits inter-molecular slip that must be added into diffusive interface models
-post hoc. 
-(iii) It is straightforward to consider mixtures of granules with different
-shapes and boundary conditions.
-Leveraging boundary integral and fast summation methods, the dynamics can be solved in 
-near-linear complexity in the number of granules,
-which is equal to or better than 
-the computational complexity of related sharp interface methods.
+large forces will even pull groups of granules apart as physically
+required. (ii) The model formulation is built around important details
+like molecular orientations, and exhibits inter-molecular slip that must
+be added into diffusive interface models post hoc. (iii) It is
+straightforward to consider mixtures of granules with different shapes
+and boundary conditions. Leveraging boundary integral and fast summation
+methods, the dynamics can be solved in near-linear complexity in the
+number of granules, which is equal to or better than the computational
+complexity of related sharp interface methods.
 
@@
   \end{center}
-  \caption{\label{fig:flow_map} \footnotesize
-  (a) Granules make a superstructure e.g., a vesicle. The panel shows
-  the moving domain $\Omega(t)$, granules with centers $\aa_i$ and directors $\dd_i$,
-  and the unit inward normal $\nu.$ Panels b, c, d show the
-  interplay between the phase field $\phi$ (colormap) and granule configuration.
-  Red is for $\phi = 1$ and blue for $\phi = 0$; $W(\phi) = \tfrac{1}{2}\phi^2$.
-  The white arrows are the fluid velocity field.
-  The panels reach an equilibrium state in panel d.
-  }
+  \caption{\label{fig:flow_map} \footnotesize (a) Granules make a
+  superstructure e.g., a vesicle. The panel shows the moving domain
+  $\Omega(t)$, granules with centers $\aa_i$ and directors $\dd_i$, and
+  the unit inward normal $\nnu$. Panels (b), (c), (d) show the interplay
+  between the phase field $\phi$ (colormap) and granule configuration.
+  Red is for $\phi = 1$ and blue for $\phi = 0$; $W(\phi) =
+  \tfrac{1}{2}\phi^2$. The white arrows are the fluid velocity field.
+  The panels reach an equilibrium state in panel (d).}
 \end{figure}
@@
 
-To determine how the granules move through space,
-we look for rigid body transformations
+To determine how the granules move through space, we look for rigid body
+transformations
 \begin{align}
 \label{eq:RBT}
-  F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
+  \FF_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
 \end{align}
@@
   \label{eqn:noslip}        
-  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
-    \vv_i + \omega_i \times (\xx - \aa_i), 
+  \frac{d\FF_i}{dt}(\XX,t) & = \uu(\xx) = 
+    \vv_i + \oomega_i \times (\xx - \aa_i), 
   \quad &&\xx \in \Gamma_i(t),\\
@@
 \end{alignat}
-for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
+for $i=1,\ldots,N_b$ and where $\xx = \FF_i(\XX,t)$. Finally,
 \begin{align}
@@
 \int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
-\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
+\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu
+  \,\dif s = \mathbf{0},
 \end{align}
@@
 are the hydrodynamic and phase field stresses, respectively.
-Equations~\eqref{eqn:stokes} are the Stokes equations 
-describing the velocity $\uu$ and pressure $p$ of
-the incompressible fluid region with viscosity $\mu$.
-Equation~\eqref{eqn:phase} describes the
-transitions of the scalar order parameter $\phi$ with a decay length
-$\epsilon$.
-The scalar function $W(\phi) : \mathbb{R} \to \mathbb{R}$ is a nonnegative
-well-potential with local minima $\phi_0, \phi_1$,  etc.,
-representing metastable states of the solvent.
-In the single-well case, $W(\phi) = \frac{1}{2}\phi^2$
-has the minimum $\phi_0 = 0$ and the phase field equation
-\eqref{eqn:phase} becomes the \emph{linear} screened Laplace equation.
-In the double-well case e.g, $W(\phi) = \frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$,
-the phase field equation \eqref{eqn:phase} takes the form of an
-Allen-Cahn equation with local minima $\phi_0 < 0 < \phi_1$.
-Section \ref{sec:specificaim1} discusses certain
-modifications needed for \eqref{eqn:phase} in the nonlinear case.
+Equations~\eqref{eqn:stokes} are the Stokes equations describing the
+velocity $\uu$ and pressure $p$ of the incompressible fluid region with
+viscosity $\mu$. Equation~\eqref{eqn:phase} describes the transitions
+of the scalar order parameter $\phi$ with a decay length $\epsilon$.
+The scalar function $W(\phi) : \RR \to \RR$ is a nonnegative
+well-potential with local minima $\phi_0, \phi_1$, etc., representing
+metastable states of the solvent. In the single-well case, $W(\phi) =
+\frac{1}{2}\phi^2$ has the minimum $\phi_0 = 0$ and the phase field
+equation~\eqref{eqn:phase} becomes the \emph{linear} screened Laplace
+equation. In the double-well case e.g, $W(\phi) =
+\frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$, the phase field
+equation~\eqref{eqn:phase} takes the form of an Allen-Cahn equation with
+local minima $\phi_0 < 0 < \phi_1$. Section \ref{sec:specificaim1}
+discusses certain modifications needed for~\eqref{eqn:phase} in the
+nonlinear case.
 
@@
 specify a no-slip boundary condition for a rigid body with translation
-velocity $\aa'_i(t) = \vv_i$ and angular velocity $\omega_i$ (the axial
+velocity $\aa'_i(t) = \vv_i$ and angular velocity $\oomega_i$ (the axial
 vector for $R'_i(t)R_i(t)^T$) about the point $\aa_i(t) \in U_i(t)$. In
@@
 equation~\eqref{eqn:stressbalance} closes the system by requiring that
-the force and torque generated by hydrodynamic stress balances
+the force and torque generated by hydrodynamic stress balance
 the force and torque 
@@
 \subsection{Applications}
-Since the framework is scale independent, it can be applied to a broad range
-of nonspecific self-organization phenomena in surface chemistry, biology
-and engineering. For one, the
+Since the framework is scale independent, it can be applied to a broad
+range of nonspecific self-organization phenomena in surface chemistry,
+biology, and engineering. For one, the
 formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
 the right behavior expected from amphiphilic self-assembly. For example,
-three bodies with amphiphilic label
-(\S\ref{sec:specificaim1}, equation \eqref{eq:amphiphilic_BC})
-spontaneously self-organize to sequester the hydrophobic fluid phase
-(Figure~\ref{fig:flow_map}). Changes in the boundary conditions result
-in distint morphologies (Figure~\ref{fig:self-assembly2}) whose rheology
-can be further investigate (\S\ref{sec:specificaim3}).
+three bodies with amphiphilic label (\S\ref{sec:specificaim1}, equation
+\eqref{eq:amphiphilic_BC}) spontaneously self-organize to sequester the
+hydrophobic fluid phase (Figure~\ref{fig:flow_map}). Changes in the
+boundary conditions result in distinct morphologies
+(Figure~\ref{fig:self-assembly2}) whose rheology can be further
+investigated (\S\ref{sec:specificaim3}).
 %
-A concrete application the PIs have considered in their
-SIAM Multiscale Modeling and Simulation and Journal of Fluid Mechanics works
-\cite{Fu2018_SIAM, FuQuRyYo22}
-is the problem of \emph{vesicle hydrodynamics}.
-A vesicle is a small, fluid filled membrane sack.
-The goal in vesicle hydrodynamics is to study flow patterns 
-arrising from the interaction
-between membrane elasticity and the fluid.
+A concrete application the PIs have considered in their SIAM Multiscale
+Modeling and Simulation and Journal of Fluid Mechanics
+works~\cite{Fu2018_SIAM, FuQuRyYo22} is the problem of \emph{vesicle
+hydrodynamics}. A vesicle is a small, fluid filled membrane sack. The
+goal in vesicle hydrodynamics is to study flow patterns arising from the
+interaction between membrane elasticity and the fluid.
 
@@
 %
-A striking feature of our hydrodynamic
-simulations is their fidelity to physics.
-The model contains a few
-parameters; granule radius $c$,
-decay length $\epsilon$,
-surface tension $\gamma$.
-When these are set to realistic values 
-\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
-we quantitatively recover many of the well-known
-elastic moduli for single-component lipid bilayers
-\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}. 
-Such agreement is a validation that equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} 
-correctly capture the
-
+A striking feature of our hydrodynamic simulations is their fidelity to
+physics. The model contains a few parameters; granule radius $c$, decay
+length $\epsilon$, surface tension $\gamma$. When these are set to
+realistic values \cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian,
+Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016}, we
+quantitatively recover many of the well-known elastic moduli for
+single-component lipid bilayers \cite{Nagle17, Nagle17-2,
+LeVeWa14,NAGLE2000159}. Such agreement is a validation that
+equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} correctly capture
+the long-range interactions between amphiphilic granules (such as lipid
+macromolecules) surfaces.
 \begin{wrapfigure}[13]{l}{0.475\textwidth}
@@
 \end{wrapfigure}
-\noindent long-range interactions between amphiphilic
-granules (such as lipid macromolecules) surfaces.
 
 In terms of hydrodynamics, the granule vesicles in background flows
-replicate the behaviour of a continous, permeable, inextensible,
-elastic vesicle.
-The simulations showed, for the first time, a
-granule-vesicle suspension behaving as a tank-treading vesicle
-\cite{Finken2008, Shaqfeh11} (see Figure \ref{fig:JPv_linearshear}).
-Movies of Figure \ref{fig:JPv_linearshear} reveal intermonolayer slip
-and derived values for intermonolayer friction are in good quantitative
-agreement those derived by atomistic and Martini force field simulation
-studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
-Figure \ref{fig:JPv_rupture}, membrane rupture occurs at large shear
-rates and yields a dimensional scaling for critical rupture shear rate
-\cite{VLAHOVSKA2009775,keller_skalak_1982}. A side-by-side comparison of
-granule-based vesicles and the sharp interface representation yielded
-shapes and trajectories that basically overlapped.
+replicate the behaviour of a continuous, permeable, inextensible,
+elastic vesicle. The simulations showed, for the first time, a
+granule-vesicle suspension behaving as a tank-treading
+vesicle~\cite{Finken2008, Shaqfeh11} (see
+Figure~\ref{fig:JPv_linearshear}). Movies of
+Figure~\ref{fig:JPv_linearshear} reveal intermonolayer slip and derived
+values for intermonolayer friction are in good quantitative agreement
+those derived by atomistic and Martini force field simulation
+studies~\cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
+Figure~\ref{fig:JPv_rupture}, membrane rupture occurs at large shear
+rates and yields a dimensional scaling for critical rupture shear
+rate~\cite{VLAHOVSKA2009775, keller_skalak_1982}. A side-by-side
+comparison of granule-based vesicles and the sharp interface
+representation yields shapes and trajectories that basically overlapped.
 
@@
 %is the crown jewel of applied mathematics.
-The mathematical framework in equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
-is highly desirable from the applied math point of view as there are many
-\emph{Further Applications}, such as
-(i) amphiphilic Janus spheres that form diverse suprastructures
-\cite{HaBr20,McBr21,Bradley2017},
-(ii) pickering emulsions involving
-two-phase fluids and dense suspensions \cite{Bradley2016},
-(iii) creation and manipulation of small droplets
-using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
-and (iv) tension driven fabrication of microstructures
-~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
+The mathematical framework in
+equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is highly desirable
+from the Applied Math point of view as there are many \emph{Further
+Applications}, such as (i) amphiphilic Janus spheres that form diverse
+suprastructures~\cite{HaBr20, McBr21, Bradley2017}, (ii) pickering
+emulsions involving two-phase fluids and dense suspensions
+\cite{Bradley2016}, (iii) creation and manipulation of small droplets
+using amphiphilic microparticles~\cite{Ha2022SurfaceEM,
+Ha2020MinimalSC}, and (iv) tension driven fabrication of
+microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,
+Zeng20223DprintedMT, Russell2016EnergyLF}.
 
 \subsection{Computational method and mathematical properties}
-\begin{wrapfigure}[18]{r}{3.1in}
-  \vspace{-0pt}
+\begin{wrapfigure}[17]{r}{3.1in}
+  \vspace{-8pt}
   \centering
@@
 Computational methods to solve the partial differential equations
-(PDEs)~\eqref{eqn:stokes}
-and~\eqref{eqn:phase} are challenging to develop because of
-the complicated and unbounded domain.
-This challenge is compounded when dense
-suspensions are considered. Integral equations (IEs) offer an
-alternative formulation of the PDEs that only require meshing the
-boundary of the granules rather than all of $\Omega(t)$
-(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far-field
-conditions. Additional advantages of discretizations of IE
-formulations include high-order, or even spectral, accuracy and
-well-conditioned linear system that can be solved iteratively with a
-mesh-independent number of Krylov iterations such as the generalized
-minimal residual method (GMRES). However, IEs have challenges: nearly
-touching granules requires a quadrature rule for nearly-singular
-integrals; their discretization results in dense matrices; and they
-cannot immediately be applied to non-linear PDEs.
-\S~\ref{sec:specificaim2} discusses
-a variety of tools the IE community,
-including PI Quaife, has developed
-to address these numerical challenges.
+(PDEs)~\eqref{eqn:stokes} and~\eqref{eqn:phase} are challenging to
+develop because of the complicated and unbounded domain. This challenge
+is compounded when dense suspensions are considered. Integral equations
+(IEs) offer an alternative formulation of the PDEs that only require
+meshing the boundary of the granules rather than all of $\Omega(t)$
+(Figure~\ref{fig:fem_vs_bie}), and they automatically satisfy far-field
+conditions. Additional advantages of discretizations of IE formulations
+include high-order, or even spectral, accuracy and well-conditioned
+linear system that can be solved iteratively with a mesh-independent
+number of Krylov iterations such as the generalized minimal residual
+method (GMRES). However, IEs have challenges: nearly touching granules
+requires a quadrature rule for nearly-singular integrals; their
+discretization results in dense matrices; and they cannot immediately be
+applied to non-linear PDEs. \S\ref{sec:specificaim2} discusses a variety
+of tools the IE community, including PI Quaife, has developed to address
+these numerical challenges.
 
@@
 system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
-%\begin{align}
-%\label{eq:energy_law}
-%  \begin{split}
-%  \frac{d}{dt}E
-%    &= - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
-%  \uu^T|^2 \,d\xx, \\
-%    E &= \gamma \int_{\Omega(t)}
-%  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
-%  \end{split}
-%\end{align}
 \begin{align}
@@
 \end{align}
-Here $E$ is the energy stored by the phase transitions
-between the granule boundaries and the solvent and the energy law states that
-the granules move to decrease energy,
-which is lost due to viscous dissipation.
-The derivation of \eqref{eq:energy_law} is interesting
-because $E$ depends both on $\phi$
-and $\Omega(t)$. It uses the Rayleigh Transport Theorem to write the time
-derivative of $E$ as an energy density flux through the boundary
-involving the phase stress $T_i$, and a bulk term involving the Euler-Lagrange
-derivative of $E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
+Here $E$ is the energy stored by the phase transitions between the
+granule boundaries and the solvent and the energy law states that the
+granules move to decrease energy, which is lost due to viscous
+dissipation. The derivation of~\eqref{eq:energy_law} is interesting
+because $E$ depends both on $\phi$ and $\Omega(t)$. It uses the Rayleigh
+Transport Theorem to write the time derivative of $E$ as an energy
+density flux through the boundary involving the phase stress $T_i$, and
+a bulk term involving the Euler-Lagrange derivative of
+$E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
 to~\eqref{eqn:phase} and the boundary flux transforms into viscous
 dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
-Furthermore, the integral of the 
-phase stress vectors $T_i\nu$ over $\partial \Omega$ is zero.
-Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the
-self-assembly process to
-the collective dynamics of the assembly under external forcing.
+Furthermore, the integral of the phase stress vectors $T_i\nnu$ over
+$\partial \Omega$ is zero. Figure~\ref{fig:coarsening} summarizes the
+general evolution of $E$ from the self-assembly process to the
+collective dynamics of the assembly under external forcing.
 
@@
   \includegraphics[width=4in]{figures/Background/coarsening.pdf}
-  \vspace{-30pt}
+  \vspace{-25pt}
   \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
@@
 
-We have $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ in the far field
-and when
-background flows are involved, we require that $\lim_{\xx \to \infty} \uu(\xx) -
-\uu_{\infty}(\xx) = \mathbf{0}$, where
-$\uu_{\infty}$ can take the form
+We have $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ in the far field and
+when background flows are involved, we require that $\lim_{\xx \to
+\infty} \uu(\xx) - \uu_{\infty}(\xx) = \mathbf{0}$, where $\uu_{\infty}$
+can take the form
 %In the case of shear background flow,
@@
 %background flows include
-of a shear, extensional, parabolic Poiseuille, or
-Taylor-Green flow, for example.
-For numerical stability, we
-include pairwise repulsive forces and torques
-in~\eqref{eqn:stressbalance} to prevent the near-collision between
-neighboring granules.  This introduces a repulsive potential in the energy
-law~\eqref{eq:energy_law}.
-Background flow adds elastic energy to the granule configurations,
-as illustrated in Figure \ref{fig:coarsening}.
+of a shear, extensional, parabolic Poiseuille, or Taylor-Green flow, for
+example. For numerical stability, we include pairwise repulsive forces
+and torques in~\eqref{eqn:stressbalance} to prevent the near-collision
+between neighboring granules. This introduces a repulsive potential in
+the energy law~\eqref{eq:energy_law}. Background flow adds elastic
+energy to the granule configurations, as illustrated in
+Figure~\ref{fig:coarsening}.
 %and is quantified by simulation. We refer to the
@@
 \subsection{Outline of the proposal}
-The aim of this proposal is to advance the simulation
-and theory for soft-matter systems
-and foster training in mathematical sciences.
-Section \ref{sec:BroaderImpacts} summarizes the broader
-impacts and section \ref{sec:IntellectualMerit} summarizes the intellectual merit of our research activity.
-Section \ref{sec:proposed-work} contains our
+The aim of this proposal is to advance the simulation and theory for
+soft-matter systems and foster training in Mathematical Sciences.
+Section~\ref{sec:BroaderImpacts} summarizes the broader impacts and
+section~\ref{sec:IntellectualMerit} summarizes the intellectual merit of
+our research activity. Section~\ref{sec:proposed-work} contains our
 specific aims.

### 2022-11-14 NSF2022/Description/backgroundv3.tex
...

@@
 \end{align}
-Here $E$ is the energy stored by the phase transitions between the
-granule boundaries and the solvent and the energy law states that the
-granules move to decrease energy, which is lost due to viscous
+Here $E$ is the energy stored by solvent phase transitions to the
+boundary. It states that energy is always lost as viscous
 dissipation. The derivation of~\eqref{eq:energy_law} is interesting

### 2022-11-14 NSF2022/Description/specificaim1v2.tex

@@
   \textbf{Problem 1.} 
-  Consider a collection the closed, disjoint granules $U_i$ with smooth
+  Consider a collection of closed, disjoint granules $U_i$ with smooth
   boundary, with no-slip, rigid body motion boundary conditions, and a
   linear background flow. Assume a single-well potential and a smooth
-  phase field boundary condition. What is the well-posedness in time of
+  phase field boundary conditions. What is the well-posedness in time of
   the coupled system \eqref{eq:RBT}--\eqref{eqn:stressbalance}?
@@
 Here, the lubrication force required to bring granules into contact
-blows up with distance, whereas the attraction \eqref{eqn:stressbalance}
-is finite, guaranteeing positivity in the distance between granules.
+blows up with distance, 
+and we must analyze whether the attraction \eqref{eqn:stressbalance}
+stays finite in order to  
+guarantee positivity in the distance between granules.
 Finally, we can study the granule-flow behavior in the zero-decay length
@@
 hypotheses and look for alternative sharp interface elastic energies.
-PI Ryham is well-qualified to perform this investigation.
-In the much noticed Biophysical Journal and Nature
+PI Ryham is well-qualified to lead this investigation.
+In his much noticed Biophysical Journal and Nature
 papers~\cite{RyKlYaCo16, Chetal16}, he calculated least energy

### 2022-11-14 NSF2022/Description/broaderimpacts.tex
starting braoder impacts

@@
 dynamics of amphiphilic granules. The framework uses a new PDE-based
-formulation and fast and accurate computational techniques that account
-for important and complex systems in
-soft matter.  These complex systems include
-optimal shape design in metamaterials and fusion and fission of amphiphilic
-bilayer membranes. The models describing colloidal systems could be
-transformative in biomedicine and material science.
-The research draws from
-expertise in scientific computing, physics of fluids, and mathematics. The
-mathematical component incorporates leading variational techniques and offers
-insight into fundamentals of material science. The project brings socially
-consequential research into the classroom and offers 
-undergraduates the opportunity to train alongside faculty and graduate students.
-With its combination of mathematical modeling, analysis, and scientific computing,
-the project highlights the importance of mathematics and computation to all areas
-of science and engineering.
+formulation that accounts for important and complex systems in soft
+matter. These complex systems include optimal shape design in
+metamaterials and fusion and fission of amphiphilic bilayer membranes.
+The simulations will be performed with computational tools designed to
+solve the governing PDEs both efficiently and with high-order accuracy.
+The models describing granular systems could be transformative in
+biomedicine and material science. The research draws from expertise in
+scientific computing, physics of fluids, and mathematics. The
+mathematical component incorporates leading variational techniques and
+offers insight into fundamentals of self-organization and collective
+dynamics. The project brings socially consequential research into the
+classroom and offers undergraduates the opportunity to train alongside
+faculty and graduate students. With its combination of mathematical
+modeling, analysis, and scientific computing, the project highlights the
+importance of mathematics and computation to all areas of science and
+engineering.
 
@@
 \label{subsec:Educational_plans}
-To foster training in mathematical sciences,
-the proposal supports two undergraduate researchers (URs) per year
-from the lead institution.
-PI Ryham has worked side-by-side and
-published with undergraduate coauthors in
-\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16}.
-He is presently mentoring a Clare Boothe Luce Scholar 
-on mathematical analysis of trends in election redistricting.
-With another Fordham supported UR,
-he is finishing a paper on a closed-form 
-energy density for translationally invariant bilayers. 
-Based on these experiences, we have outlined three projects for the present proposal.
+To foster training in mathematical sciences, the proposal supports two
+undergraduate researchers (URs) per year at Fordham University. PI Ryham
+has worked side-by-side and published with undergraduate
+coauthors~\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16}. He is presently
+mentoring a Clare Boothe Luce Scholar on mathematical analysis of trends
+in election redistricting. With another Fordham supported UR, he is
+finishing a paper on a closed-form energy density for translationally
+invariant bilayers. Based on these experiences, we have outlined three
+projects for the present proposal.
+\todo[inline]{Rolf: Can you update this?}
 \begin{enumerate}[noitemsep,topsep=0pt]
-%\noitemsep
 \item Translate project code from MATLAB into a compiled language
@@
 \item Mathematically investigate self-assembly in the zero-screen-length limit
-
 \end{enumerate}
-The UR support is for eight summer weeks. 
-In addition to collaborating with the PI,
-they will have tutorials and receive training in
-mathematical writing and presentation.
-The URs will have desks and meeting room
-in a recently completed collaboration space
-built for the Mathematics Department. 
-As a condition of support, 
-they will be required to write a summary report and
-give a presentation in the university's undergraduate
-research symposium.  The PI 
-will encourage the
-URs to participate in a national conference.
+The UR support is for eight summer weeks. In addition to collaborating
+with the PI, they will have tutorials and receive training in
+mathematical writing and presentation. The URs will have desks and
+meeting room in a recently completed collaboration space built for the
+Mathematics Department. As a condition of support, they will be required
+to write a summary report and give a presentation in the university's
+undergraduate research symposium. The PI will encourage the URs to
+participate in a national conference.
 
@@
 whose socio-economic background prevents them from participating in
-out-of-state research experiences.  PI Ryham will solicit applicants
-from Fordham University's Collegiate Science and Technology Entry
-Program.  Students from the Bronx High School of Science (PI Ryham) and
-Newark Science Park High School (PI Young) will also be encouraged to
-join the research team. PI Quaife will work with undergraduates and high
-school students through the Undergraduate Research Opportunity Program
-and Young Scholar's Program, as he has done in the past.
+out-of-state research experiences. PI Ryham will solicit applicants from
+Fordham University's Collegiate Science and Technology Entry Program.
+Students from the Bronx High School of Science (PI Ryham) and Newark
+Science Park High School (PI Young) will also be encouraged to join the
+research team. PI Quaife will work with undergraduates and high school
+students through the Undergraduate Research Opportunity Program and
+Young Scholar's Program, as he has done in the past.
 
-To maximize vertical integration, the PIs and personnel
-will travel to New York for one or two weeks during the summers.
-Finally, we will create several modules to include in our courses. These
-modules will introduce topics from numerical linear algebra and
-optimization and highlight concrete applications of mathematics
-based on the ideas of the proposal.
+To maximize vertical integration, the PIs and personnel will travel to
+New York for one or two weeks during the summers. Finally, we will
+create several modules to include in our courses. These modules will
+introduce topics from numerical linear algebra and optimization and
+highlight concrete applications of mathematics based on the ideas of the
+proposal.
 
@@
 \label{sec:IntellectualMerit}
-The purpose of this research is to reach interesting physical phenomena with less computational cost than molecular dynamics, and account for more general features that continuum theory misses.
-The main ingredient is defining a nonlocal interaction through the solution of an elliptic boundary value problem that has the phenomenological characteristics of long-range hydrophobic attraction.
-This minimal model, while intuitive, is quite a general description of amphiphiles in solvent and gives rise to rich phenomena from Janus particle aggregates to correctly predicting elastic properties of bilayer.
-The technical research tasks include quantifying collective properties of amphiphilic ensembles, improving on mathematical models, efficient, high-order numerical algorithms for large-scale simulations, and incorporating external fields through electric charge.
+The purpose of this research is to reach interesting physical phenomena
+with less computational cost than molecular dynamics, and account for
+more general features that continuum theory misses. The main ingredient
+is defining a nonlocal interaction through the solution of an elliptic
+boundary value problem that has the phenomenological characteristics of
+long-range hydrophobic attraction. This minimal model, while intuitive,
+is quite a general description of amphiphiles in solvent and gives rise
+to rich phenomena from Janus particle aggregates to correctly predicting
+elastic properties of bilayer. The technical research tasks include
+quantifying collective properties of amphiphilic ensembles, improving on
+mathematical models, efficient, high-order numerical algorithms for
+large-scale simulations, and incorporating external fields through
+electric charge.

### 2022-11-14 NSF2022/Description/broaderimpacts.tex
yny 1114b

@@
 classroom and offers undergraduates the opportunity to train alongside
-faculty and graduate students. With its combination of mathematical
+faculty and graduate students. With its unique combination of mathematical
 modeling, analysis, and scientific computing, the project highlights the
-importance of mathematics and computation to all areas of science and
-engineering.
+potential advancement of STEM from applied mathematics.
 

### 2022-11-14 NSF2022/Description/summary.tex
edited SA1

--- 2021-11-23 NSF2021/Description/summary.tex
@@
 \vspace{-0.1in}
-This proposal aims to advance mathematical modeling and analysis of collective dynamics of amphiphilic self-assembly.
-Amphiphilic particles such as lipid molecules possess both hydrophobic and hydrophilic surfaces and self-assemble into meso/macroscopic structures such as micelles and bilayers of lipids.
-Experimentalists model self-assembly using Janus particles—spherical particles possessing a biphasic material label on either hemisphere.
-Janus particles have been widely used in soft matter physics as a model amphiphilic colloid and can be designed for catalytic activity or stimuli-responsive smart materials.
+This proposal aims to advance mathematical modeling and analysis of
+collective dynamics of amphiphilic self-assembly. Amphiphilic particles
+such as lipid molecules possess both hydrophobic and hydrophilic
+surfaces and self-assemble into meso/macroscopic structures such as
+micelles and bilayers of lipids. Experimentalists model self-assembly
+using Janus particles—spherical particles possessing a biphasic material
+label on either hemisphere. Janus particles have been widely used in
+soft matter physics as a model amphiphilic colloid and can be designed
+for catalytic activity or stimuli-responsive smart materials.
 
-Hydrophobic surfaces experience a nonadditive long-range attraction called the hydrophobic force.
-This force is a major source of nonspecific interactions in biology and soft matter.
-Despite its ubiquity, theoretical developments explaining its basic underlying principles have come relatively late.
-Motivated by its broad applicability, the PIs recently developed a novel and intuitive mathematical model, called the hydrophobic attraction potential model, based on the linear response of water to surface perturbations.
-This model was used to show, for the first time, self-assembly of Janus particles into vesicle-like structures using a partial differential equation-based particle interaction.
+Hydrophobic surfaces experience a nonadditive long-range attraction
+called the hydrophobic force. This force is a major source of
+nonspecific interactions in biology and soft matter. Despite its
+ubiquity, theoretical developments explaining its basic underlying
+principles have come relatively late. Motivated by its broad
+applicability, the PIs recently developed a novel and intuitive
+mathematical model, called the hydrophobic attraction potential model,
+based on the linear response of water to surface perturbations. This
+model was used to show, for the first time, self-assembly of Janus
+particles into vesicle-like structures using a partial differential
+equation-based particle interaction.
 
-The PIs propose to apply their hydrophobic attraction potential model to the self-organization dynamics of Janus particles.
-They aim to generalize the linear-response model to more general hydrophobic interactions, and numerically implement these interactions using integral equation formulations.
-Finally, they will investigate and simulate hydrophobic interactions in the presence of electric charge and ions.
-The unifying aspects of the project are establishing a platform for efficiently simulating the collective dynamics at large scales, and the focusing on rigorous, mathematical analysis of the underlying model equations and complicated geometries.
-The project supports undergraduate and graduate student collaborators.
+The PIs propose to apply their hydrophobic attraction potential model to
+the self-organization dynamics of Janus particles. They aim to
+generalize the linear-response model to more general hydrophobic
+interactions, and numerically implement these interactions using
+integral equation formulations. Finally, they will investigate and
+simulate hydrophobic interactions in the presence of electric charge and
+ions. The unifying aspects of the project are establishing a platform
+for efficiently simulating the collective dynamics at large scales, and
+the focusing on rigorous, mathematical analysis of the underlying model
+equations and complicated geometries. The project supports undergraduate
+and graduate student collaborators.
 
@@
 \vspace{-0.1in}
-The purpose of this research is to reach interesting physical phenomena with less computational cost than molecular dynamics, and account for more general features that continuum theory misses.
-The main ingredient is defining a nonlocal interaction through the solution of an elliptic boundary value problem that has the phenomenological characteristics of long-range hydrophobic attraction.
-This minimal model, while intuitive, is quite a general description of amphiphiles in solvent and gives rise to rich phenomena from Janus particle aggregates to correctly predicting elastic properties of bilayer.
-The technical research tasks include quantifying collective properties of amphiphilic ensembles, improving on mathematical models, efficient, high-order numerical algorithms for large-scale simulations, and incorporating external fields through electric charge.
+The purpose of this research is to reach interesting physical phenomena
+with less computational cost than molecular dynamics, and account for
+more general features that continuum theory misses. The main ingredient
+is defining a nonlocal interaction through the solution of an elliptic
+boundary value problem that has the phenomenological characteristics of
+long-range hydrophobic attraction. This minimal model, while intuitive,
+is quite a general description of amphiphiles in solvent and gives rise
+to rich phenomena from Janus particle aggregates to correctly predicting
+elastic properties of bilayer. The technical research tasks include
+quantifying collective properties of amphiphilic ensembles, improving on
+mathematical models, efficient, high-order numerical algorithms for
+large-scale simulations, and incorporating external fields through
+electric charge.
 
@@
 \vspace{-0.1in}
-This project aims to advance the mathematical modeling of collective dynamics of amphiphilic particles.
-The simulations use a new, yet intuitive, approach that accounts for important and complex systems that are presently out of reach in computational material science.
-These complex systems include optimal shape design in metamaterials and fusion and fission of amphiphilic bilayer membranes.
-The models describing colloidal systems could be transformative in biomedicine and material science.
-The research draws from expertise in scientific computing, physics of fluids, and mathematics.
-The mathematical component incorporates leading variational techniques and offers insight into fundamentals of material science.
-The project brings socially consequential research into the classroom and offers undergraduates the opportunity to train alongside faculty and graduate students.
-With its combination of mathematical modeling, analysis, and scientific computing, the project highlights the importance of mathematics and computation to all areas of science and engineering.
+This project aims to advance the mathematical modeling of collective
+dynamics of amphiphilic granules. The framework uses a new PDE-based
+formulation that accounts for important and complex systems in soft
+matter. These complex systems include optimal shape design in
+metamaterials and fusion and fission of amphiphilic bilayer membranes.
+The simulations will be performed with computational tools designed to
+solve the governing PDEs both efficiently and with high-order accuracy.
+The models describing granular systems could be transformative in
+biomedicine and material science. The research draws from expertise in
+scientific computing, physics of fluids, and mathematics. The
+mathematical component incorporates leading variational techniques and
+offers insight into fundamentals of self-organization and collective
+dynamics. The project brings socially consequential research into the
+classroom and offers undergraduates the opportunity to train alongside
+faculty and graduate students. With its unique combination of
+mathematical modeling, analysis, and scientific computing, the project
+highlights the potential advancement of STEM from applied mathematics.
+
 \end{document}

### 2022-11-14 NSF2022/Description/specificaim1v2.tex
fixed overhanging figure

@@
 \label{sec:proposed-work}
-This proposal is an outgrowth of the 
-PIs' ongoing successful collaboration.
-Building off complementary expertises,
-the specific aims of this proposal are:
-mathematical analysis and three-dimensional
-membrane energies
-(\S \ref{sec:specificaim1}: PI Ryham),
-BIE implementation for large granule-number
-and three-dimensional suspensions
-(\S \ref{sec:specificaim2}: PI Quaife),
-and kinetic theory
-(\S \ref{sec:specificaim3}: PI Young).
+This proposal is an outgrowth of the PIs' ongoing successful
+collaboration. Building off complementary expertises, the specific aims
+of this proposal are: mathematical analysis and three-dimensional
+membrane energies (\S\ref{sec:specificaim1}: PI Ryham), BIE
+implementation for large granule-number and three-dimensional
+suspensions (\S\ref{sec:specificaim2}: PI Quaife), and kinetic theory
+(\S\ref{sec:specificaim3}: PI Young).
+
 \subsection{Specific Aim 1: Membrane vesicles as self-organized granules}
 \label{sec:specificaim1}
-We introduced \eqref{eq:RBT}--\eqref{eqn:stressbalance} to complement
+We introduced~\eqref{eq:RBT}--\eqref{eqn:stressbalance} to complement
 existing methods for studing vesicles and bilayers. The simulation
-results in (Figures~\ref{fig:JPv_linearshear} and~\ref{fig:JPv_rupture})
+results in Figures~\ref{fig:JPv_linearshear} and~\ref{fig:JPv_rupture}
 show that two-dimensional, granule-based vesicles replicate the
@@
 
-The first step is to obtain some solid well-posedness results for
-\eqref{eq:RBT}--\eqref{eqn:stressbalance}. This system is an autonomous
-ordinary differential equation for the body transformations $F_i$ with
-the rate of change defined by a system of PDEs. Regarding the PDE system,
-in the linear case and for fixed $t$, there is a
-unique solution ($\phi, \uu$) under appropriate assumptions for the
-boundaries and boundary data~\cite{manasthesis, rac-gre2016, LAX}. These
-define instantaneous rigid body velocities and rotations,
-leading to 
+The first step is to obtain some solid well-posedness results
+for~\eqref{eq:RBT}--\eqref{eqn:stressbalance}. This system is an
+autonomous ordinary differential equation for the body transformations
+$\FF_i$ with the rate of change defined by a system of PDEs. Regarding
+the PDE system, in the linear case and for fixed $t$, there is a unique
+solution ($\phi, \uu$) under appropriate assumptions for the boundaries
+and boundary data~\cite{manasthesis, rac-gre2016, LAX}. These define
+instantaneous rigid body velocities and rotations, leading to the
+following problem.
 \begin{quotation}
@@
 \end{quotation}
-Problem 1 involves mathematically interesting techniques. First, we
-must establish that the system has a local-in-time solution. This
-involves domain perturbations and estimates for the solutions of second
-order elliptic equations~\cite{Savar2002DomainPA, DANERS20081,
+Problem 1 involves mathematically interesting techniques. First, we must
+establish that the system has a local-in-time solution. This involves
+domain perturbations and estimates for the solutions of second order
+elliptic equations~\cite{Savar2002DomainPA, DANERS20081,
 Lamboley2015EstimatesOF}, which also find extensive application in
@@
 Henrot2006ExtremumPF, bogosel:hal-03607776,Bogosel2022OnTP}, for
-example. For global-in-time solutions, we can 
-use lubrication forces~\cite{cawthorn_balmforth_2010, leal_2007}.
-Here, the lubrication force required to bring granules into contact
-blows up with distance, 
-and we must analyze whether the attraction \eqref{eqn:stressbalance}
-stays finite in order to  
-guarantee positivity in the distance between granules.
-Finally, we can study the granule-flow behavior in the zero-decay length
-limit. This limit should recover the hydrodynamics of a (noninteracting)
-rigid-body suspension.
+example. For global-in-time solutions, we can use lubrication
+forces~\cite{cawthorn_balmforth_2010, leal_2007}. Here, the lubrication
+force required to bring granules into contact blows up with distance,
+and we must analyze whether the attraction~\eqref{eqn:stressbalance}
+stays finite in order to guarantee positivity in the distance between
+granules. Finally, we can study the granule-flow behavior in the
+zero-decay length limit. This limit should recover the hydrodynamics of
+a (noninteracting) rigid-body suspension.
 
+\begin{wrapfigure}[11]{r}{0.5\textwidth}
+  \vspace{-8pt}
+  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
+  \vspace{-8pt}
+  \caption{\label{fig:amphiphilic_assembly} \footnotesize
+  Self-organization under amphiphilic boundary condition. (a) Granules
+  first match hydrophobic tails (red), (b) then align length-wise. (c)
+  The same pattern of self-organization holds in three dimensions, as
+  simulated by Kohl, Corona, and
+  Veerapaneni~\cite{koh-cor-che-vee2021}.}
+\end{wrapfigure}
 In the double-well potential case, equation~\eqref{eqn:phase} is a
 nonlinear Allen-Cahn equation. This situation models granules immersed
-in a two-phase fluid (e.g.~granules in an emulsion) where there is an
+in a two-phase fluid (e.g., granules in an emulsion) where there is an
 interesting interplay between the long-range alignment of granules and
@@
 
-\begin{wrapfigure}[11]{r}{0.5\textwidth}
-  \vspace{-8pt}
-  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
-  \vspace{-8pt}
-  \caption{\label{fig:amphiphilic_assembly} \footnotesize
-  Self-organization under amphiphilic boundary condition. (a) Granules
-  first match hydrophobic tails (red), (b) then align length-wise. (c)
-  The same pattern of self-organization holds in three dimensions, as
-  simulated by Kohl, Corona, and
-  Veerapaneni~\cite{koh-cor-che-vee2021}.}
-\end{wrapfigure}
-
 Sharp interface models represent a membrane vesicle as an
@@
 
-Tools for addressing Problem 2 have been developed for bulk nematic liquid
-crystal potentials in the area of colloidal
+Tools for addressing Problem 2 have been developed for bulk nematic
+liquid crystal potentials in the area of colloidal
 homogenization~\cite{Canevari2019DesignOE, doi:10.1137/18M1163919,
-  doi:10.1137/18M1163919, BERLYAND200597, doi:10.1137/130910348}, and
-the problem is closely related to dimension reduction for curved nematics
-confined to thin films~\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,
-  doi:10.1142/S0218202516500470, FoFrLe07}.
-PI Ryham has carried out sharp interface-limit analyses for phase field
-formulations of elastic bending energy~\cite{0951-7715-18-3-016, Du05},
-approximations of Gaussian curvature and the Euler characteristic in
-phase field~\cite{DuEuler}, and vanishing Debye-length in 
-Poisson-Boltzman equations~\cite{Lee2018, 1531-3492_2006_2_357}.
+BERLYAND200597, doi:10.1137/130910348}, and the problem is closely
+related to dimension reduction for curved nematics confined to thin
+films~\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,
+doi:10.1142/S0218202516500470, FoFrLe07}.  PI Ryham has carried out
+sharp interface-limit analyses for phase field formulations of elastic
+bending energy~\cite{0951-7715-18-3-016, Du05}, approximations of
+Gaussian curvature and the Euler characteristic in phase
+field~\cite{DuEuler}, and vanishing Debye-length in Poisson-Boltzman
+equations~\cite{Lee2018, 1531-3492_2006_2_357}.
 

### 2022-11-14 NSF2022/Description/priorsupport.tex
went through rest of proposal

@@
 
-\begin{wrapfigure}[10]{r}{0.4\textwidth}
+\begin{wrapfigure}[9]{r}{0.4\textwidth}
+  \vspace{-5pt}
   \includegraphics[width=0.4\textwidth]{figures/gantt.jpg}
-  \caption{\label{fig:schedule} Schedule for the proposed work, measured
-  in quarters from the beginning of the project. The lead PI of each
-  Specific Aim will be Ryham (red), Quaife (blue), and Young (green).}
+  \vspace{-20pt}
+  \caption{\label{fig:schedule} \footnotesize Schedule for the proposed
+  work, measured in quarters from the beginning of the project. The lead
+  PI of each Specific Aim will be Ryham (red), Quaife (blue), and Young
+  (green).}
 \end{wrapfigure}
@@
 The success of the proposed research requires complementary expertise
-and collaborative efforts in physics, applied mathematics, algorithms,
-and computing. PI Ryham has been working on mathematical modeling with a
-strong analytical background. PI Young has been working on many areas of
-computational fluid dynamics and applications to math biology for many
-years. PI Quaife has been working on integral equation methods, fast
-algorithms, and their applications to fluid dynamics for many years.
-Their recent collaborative works on the granule-based vesicles in two
-dimensions~\cite{FuQuRyYo22, fu-ryh-qua-you2022} has provided a solid
-foundation for the proposed research.
+and collaborative efforts in physics, applied mathematics, and
+scientific computing. PI Ryham has been working on mathematical modeling
+with a strong analytical background. PI Young has been working on many
+areas of computational fluid dynamics and applications to math biology
+for many years. PI Quaife has been working on integral equation methods,
+fast algorithms, and their applications to fluid dynamics for many
+years.  Their recent collaborative works on the granule-based vesicles
+in two dimensions~\cite{FuQuRyYo22, fu-ryh-qua-you2022} has provided a
+solid foundation for the proposed research.
 
@@
 The management responsibility of this collaborative research will reside
-with the lead PI (Quaife) for this endeavor. The research work is
-structured to meet the tasks discussed in \S\ref{sec:proposed-work}. The
-PIs and students will meet frequently on Zoom and in person when
-possible. PI Ryham and PI Young will conduct biweekly meetings in
-person, with PI Quaife Zoom in from Florida. The PIs will share software
-packages, paper sources, and references on a common \textsf{Git}
-repository. The resulting software packages will be posted on the
-\textsf{Github} software repository.
+with PI Quaife. The research work is structured to meet the tasks
+discussed in \S\ref{sec:proposed-work}. The PIs and students will meet
+frequently on Zoom and in person when possible. PI Ryham and PI Young
+will conduct biweekly meetings in person, with PI Quaife joining over
+Zoom from Florida. The PIs will share software packages, paper sources,
+and references on a common \textsf{Git} repository. The resulting
+software packages will be posted on the \textsf{Github} software
+repository.
 %

### 2022-11-14 NSF2022/Description/specificaim2.tex

@@
 solvent~\cite{Pandey2011, Zhang2017, Siontorou2017}. Additionally,
-hydrodynamic interactions are central to
-fabricate complex,
+hydrodynamic interactions are central to fabricate complex,
 three-dimensional microstructures~\cite{Dasgupta2017, Leong2007,
@@
 %dynamics~\cite{RYHAM20112929}, set the rate of dissipation.
-The success
-of Specific Aims 1 and 3 depends on the ability to accurately and
-efficiently simulate dense suspensions of granules governed by
-equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance}. Because of their
-ability to resolve complex unbounded domains and achieve high-order
-accuracy, integral equations (IEs) will be a central theme of the
-computational framework.
+The success of Specific Aims 1 and 3 depends on the ability to
+accurately and efficiently simulate dense suspensions of granules
+governed by equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance}. Because
+of their ability to resolve complex unbounded domains and achieve
+high-order accuracy, integral equations (IEs) will be a central theme of
+the computational framework.
 
@@
 fundamental solution and $\ssigma: \partial \Omega(t) \rightarrow \RR^2$
-is an unknown density function.
+is an unknown density function. The integral
+representation~\eqref{eqn:conv} is known as a layer potential.
 %This is analogous to the problem of
@@
 
-As an illustration, the problem of finding the global
-electrostatic potential $u$ with surface
-charge density $\sigma$ is a special case of \eqref{eqn:conv}, where
-$G(\xx - \yy) = (4\pi \epsilon_0)^{-1}|\xx - \yy|^{-1}$
-in three dimensions
-($-(2\pi \epsilon_0)^{-1}\log|\xx - \yy|$ in two dimensions)
-with $\epsilon_0$ the permittivity of vacuum.  In this context, 
-~\eqref{eqn:bie} is analogous to Gauss's Law.
+As an illustration, the problem of finding the global electrostatic
+potential $u$ with surface charge density $\sigma$ is a special case of
+\eqref{eqn:conv}, where $G(\xx - \yy) = (4\pi \epsilon_0)^{-1}|\xx -
+\yy|^{-1}$ in three dimensions ($-(2\pi \epsilon_0)^{-1}\log|\xx - \yy|$
+in two dimensions) with $\epsilon_0$ the permittivity of vacuum.  In
+this context, equation~\eqref{eqn:bie} is analogous to Gauss's Law.
 
@@
 
-\begin{wrapfigure}[]{l}{2.6in}
+\begin{wrapfigure}[6]{l}{2.6in}
   \centering
+%  \vspace{-10pt}
   \includegraphics[width=2.5in]{figures/SA2Figures/confinement.pdf}
+  \vspace{-10pt}
   \caption{\label{fig:stenosis} \footnotesize A granule vesicle passing
@@
 domains require additional modifications to the IE formulation. PI
-Quaife has considered suspensions with confinement for several projects
-including dynamic suspensions~\cite{qua-bir2014, bys-sha-qua2020} and
-porous media~\cite{chi-moo-qua2020, dea-qua-bir-jua2018,
-moo-che-chi-qua2022, qua-gan-you2021}.
+Quaife is qualified to perform this task since he has simulated
+suspensions with confinement for several projects including dynamic
+suspensions~\cite{qua-bir2014, bys-sha-qua2020} and porous
+media~\cite{chi-moo-qua2020, dea-qua-bir-jua2018, moo-che-chi-qua2022,
+qua-gan-you2021}.
 \begin{wrapfigure}[16]{r}{2.1in}
-  \vspace{-8pt}
+  \vspace{-4pt}
   \centering
@@
 fundamental solution can be used to address nearly-singular
-integrals~\cite{beale1, cor2001, tlu-bea2019}. Alternatively, efficient
+integrals~\cite{beale1, cor2001, tlu-bea2019}. Finally, efficient
 quadrature methods can be applied directly to accurately compute
@@
 double-well potential with $W''(\phi_0) = W''(\phi_1) = \beta$, we
-propose to instead use an inexact Newton's method where $F^{-1}$ is
+propose to instead use an inexact Newton's method where $(F')^{-1}$ is
 approximated with the solution of $-\epsilon^2 \Delta v +

### 2022-11-14 NSF2022/Description/summary.tex
working on overview

@@
 This proposal aims to advance mathematical modeling and analysis of
-collective dynamics of amphiphilic self-assembly. Amphiphilic particles
-such as lipid molecules possess both hydrophobic and hydrophilic
-surfaces and self-assemble into meso/macroscopic structures such as
-micelles and bilayers of lipids. Experimentalists model self-assembly
-using Janus particles—spherical particles possessing a biphasic material
-label on either hemisphere. Janus particles have been widely used in
-soft matter physics as a model amphiphilic colloid and can be designed
-for catalytic activity or stimuli-responsive smart materials.
+collective dynamics and self-assembly arising from attractive
+interactions between dipolar/nematic particles in a suspension. For
+example, the organization of lipids and proteins in vesicles is crucial
+to design effective drug carriers. Physicists model such a self-assembly
+using particles possessing a biphasic material label on either half,
+with one more hydrophobic than the other. Hydrophobic surfaces
+experience a nonadditive long-range attraction called the hydrophobic
+force. This force is a major source of nonspecific interactions in
+biology and soft matter. Despite its ubiquity, theoretical developments
+explaining its basic underlying principles have come relatively late.
+Motivated by its broad applicability, the PIs recently developed a novel
+and intuitive mathematical model, called the hydrophobic attraction
+potential model, based on the linear response of water to surface
+perturbations. This model was used to show, for the first time,
+self-assembly of such bipolar particles into vesicle-like structures
+using moving domain elliptic partial differential equations.
 
-Hydrophobic surfaces experience a nonadditive long-range attraction
-called the hydrophobic force. This force is a major source of
-nonspecific interactions in biology and soft matter. Despite its
-ubiquity, theoretical developments explaining its basic underlying
-principles have come relatively late. Motivated by its broad
-applicability, the PIs recently developed a novel and intuitive
-mathematical model, called the hydrophobic attraction potential model,
-based on the linear response of water to surface perturbations. This
-model was used to show, for the first time, self-assembly of Janus
-particles into vesicle-like structures using a partial differential
-equation-based particle interaction.
+%This proposal aims to advance mathematical modeling and analysis of
+%collective dynamics of amphiphilic self-assembly. Amphiphilic particles
+%such as lipid molecules possess both hydrophobic and hydrophilic
+%surfaces and self-assemble into meso/macroscopic structures such as
+%micelles and bilayers of lipids. Experimentalists model self-assembly
+%using Janus particles—spherical particles possessing a biphasic material
+%label on either hemisphere. Janus particles have been widely used in
+%soft matter physics as a model amphiphilic colloid and can be designed
+%for catalytic activity or stimuli-responsive smart materials.
+
+%Hydrophobic surfaces experience a nonadditive long-range attraction
+%called the hydrophobic force. This force is a major source of
+%nonspecific interactions in biology and soft matter. Despite its
+%ubiquity, theoretical developments explaining its basic underlying
+%principles have come relatively late. Motivated by its broad
+%applicability, the PIs recently developed a novel and intuitive
+%mathematical model, called the hydrophobic attraction potential model,
+%based on the linear response of water to surface perturbations. This
+%model was used to show, for the first time, self-assembly of Janus
+%particles into vesicle-like structures using a partial differential
+%equation-based particle interaction.
 
 The PIs propose to apply their hydrophobic attraction potential model to
-the self-organization dynamics of Janus particles. They aim to
-generalize the linear-response model to more general hydrophobic
-interactions, and numerically implement these interactions using
-integral equation formulations. Finally, they will investigate and
-simulate hydrophobic interactions in the presence of electric charge and
-ions. The unifying aspects of the project are establishing a platform
-for efficiently simulating the collective dynamics at large scales, and
-the focusing on rigorous, mathematical analysis of the underlying model
-equations and complicated geometries. The project supports undergraduate
-and graduate student collaborators.
+more general self-organization dynamics. They aim to generalize the
+linear-response model to more general hydrophobic interactions, and
+numerically implement these interactions using integral equation
+formulations. Finally, they will investigate and simulate hydrophobic
+interactions in the presence of electric charge and ions. The unifying
+aspects of the project are establishing a platform for efficiently
+simulating the collective dynamics at large scales, and the focusing on
+rigorous, mathematical analysis of the underlying model equations and
+complicated geometries. The project supports undergraduate and graduate
+student collaborators.
 

### 2022-11-14 NSF2022/SupplementaryDocs/excludedreviewers.tex
working on overview

@@
 \\ \\
-Professor Alex Donev (donev@courant.nyu.edu) is a competitor that is
-working on similar problems to those described in the proposal entitled
-``Collaborative Proposal: Self-organization modeled by moving domain
-elliptic PDEs". We request that they are not chosen to review the
-proposal.
+Professors Alex Donev (donev@courant.nyu.edu) and Yoichiro Mori
+(y1mori@sas.upenn.edu) are competitors that are working on similar
+problems to those described in the proposal entitled ``Collaborative
+Proposal: Self-organization modeled by moving domain elliptic PDEs". We
+request that they are not chosen to review the proposal.
 \\ \\

### 2022-11-14 NSF2022/Description/summary.tex
yny 1114c

@@
 \vspace{-0.1in}
-This proposal aims to advance mathematical modeling and analysis of
+This proposal aims to advance mathematical modeling, analysis and numerical simulations of
 collective dynamics and self-assembly arising from attractive
-interactions between dipolar/nematic particles in a suspension. For
-example, the organization of lipids and proteins in vesicles is crucial
-to design effective drug carriers. Physicists model such a self-assembly
+interactions between dipolar/nematic particles in a suspension. 
+%
+%One example is the organization of lipids and proteins in vesicles, which is crucial
+%to design effective drug carriers. 
+%
+Physicists model such a self-assembly
 using particles possessing a biphasic material label on either half,
@@
 numerically implement these interactions using integral equation
-formulations. Finally, they will investigate and simulate hydrophobic
-interactions in the presence of electric charge and ions. The unifying
+formulations. Finally, they will develop a coarse-grained model based on 
+the kinetic theory to investigate the rheological properties of the assembly of 
+particles with tunable hydrophobicity. The unifying
 aspects of the project are establishing a platform for efficiently

### 2022-11-14 NSF2022/Description/summary.tex
yny 1114c

@@
 with one more hydrophobic than the other. Hydrophobic surfaces
-experience a nonadditive long-range attraction called the hydrophobic
+experience a non-additive long-range attraction called the hydrophobic
 force. This force is a major source of nonspecific interactions in
@@
 
-The PIs propose to apply their hydrophobic attraction potential model to
+The PIs propose to analyze the near-linear elliptic PDEs, develop fast and accurate numerical schemes, 
+and apply their hydrophobic attraction potential model to
 more general self-organization dynamics. They aim to generalize the
-linear-response model to more general hydrophobic interactions, and
+linear-response model to  a wider class of hydrophobic interactions, and
 numerically implement these interactions using integral equation

### 2022-11-14 NSF2022/Description/backgroundv3.tex
refs added

@@
 is dealing with a particle method, as an alternative to other
-discretization methods such as finite-difference, finite-element, and
-spectral methods~\cite{Wilson2021ComparisonOT}. We have departed from
-the terminology ``particles'', though, to emphasize the role played the
-granules' finite size.
+stencil-based discretization methods~\cite{Wilson2021ComparisonOT,Gross2020MeshfreeMO,
+Sigurdsson2016HydrodynamicCO}.
+We have departed from the terminology ``particles'', though,
+to emphasize the role played elliptic equations and the granules'
+finite size.
 
@@
 like molecular orientations, and exhibits inter-molecular slip that must
-be added into diffusive interface models post hoc. (iii) It is
+be added into continuum models post hoc. (iii) It is
 straightforward to consider mixtures of granules with different shapes
@@
 works~\cite{Fu2018_SIAM, FuQuRyYo22} is the problem of \emph{vesicle
-hydrodynamics}. A vesicle is a small, fluid filled membrane sack. The
+hydrodynamics}.
+%A vesicle is a small, fluid filled membrane sack.
+The
 goal in vesicle hydrodynamics is to study flow patterns arising from the
-interaction between membrane elasticity and the fluid.
+interaction between membrane elasticity/viscoelasticity and the fluid
+\cite{Gera2022SwingingAT,Cox2015TheEO,wangthesis,C6SM02452A,Strychalski2012ViscoelasticIB}.
 
-\begin{wrapfigure}[10]{l}{0.48\textwidth}
+\begin{wrapfigure}[10]{l}{0.5\textwidth}
 \vspace{-5pt}
-\includegraphics[width=0.48\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
+\includegraphics[width=0.5\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
 \vspace{-20pt}
@@
 Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016}, we
-quantitatively recover many of the well-known elastic moduli for
+quantitatively recover well-known elastic moduli for
 single-component lipid bilayers \cite{Nagle17, Nagle17-2,
@@
 \begin{wrapfigure}[13]{l}{0.475\textwidth}
-\vspace{-10pt}
+\vspace{-0pt}
 \includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
@@
 develop because of the complicated and unbounded domain. This challenge
-is compounded when dense suspensions are considered. Integral equations
+is compounded when dense suspensions are considered.
+Integral equations
 (IEs) offer an alternative formulation of the PDEs that only require

### 2022-11-14 NSF2022/Description/specificaim1v2.tex
refs added

@@
 The first step is to obtain some solid well-posedness results
-for~\eqref{eq:RBT}--\eqref{eqn:stressbalance}. This system is an
-autonomous ordinary differential equation for the body transformations
-$\FF_i$ with the rate of change defined by a system of PDEs. Regarding
-the PDE system, in the linear case and for fixed $t$, there is a unique
+for~\eqref{eq:RBT}--\eqref{eqn:stressbalance}.
+This system is an
+autonomous ordinary differential equations (ODEs) for the body transformations
+$\FF_i$ with the rate of change defined by a system of PDEs.
+Strategies have been proposed for the solution of
+coupled PDE/ODE systems 
+\cite{Carichino2018EnergybasedOS,Quarteroni2016GeometricMM}.
+Regarding \eqref{eq:RBT}--\eqref{eqn:stressbalance},
+in the linear case and for fixed $t$, there is a unique
 solution ($\phi, \uu$) under appropriate assumptions for the boundaries
@@
 Henrot2006ExtremumPF, bogosel:hal-03607776,Bogosel2022OnTP}, for
-example. For global-in-time solutions, we can use lubrication
+example.
+For global-in-time solutions, we can use lubrication
 forces~\cite{cawthorn_balmforth_2010, leal_2007}. Here, the lubrication
@@
 stays finite in order to guarantee positivity in the distance between
-granules. Finally, we can study the granule-flow behavior in the
+granules.
+Finally, we can study the granule-flow behavior in the
 zero-decay length limit. This limit should recover the hydrodynamics of
@@
 Promislow2012CriticalPO, Dai2022GeometricEO, Dai2020MinimizersFT,
-Dai2013GeometricEO, Promislow2022UndulatedBI} and well-posedness
+Dai2013GeometricEO, Promislow2022UndulatedBI, Gera2017CahnHilliardOS}
+and well-posedness
 results when coupled to flow in static domains~\cite{Jiang2017TwophaseIF,
@@
 particles~\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT,
-Alama2021SaturnRD, PhysRevE.96.042702}. PI Ryham has several works on
+  Alama2021SaturnRD, PhysRevE.96.042702}.
+
+PI Ryham has several works on
 membrane vesicles dealing both with Allen-Cahn formulations and
@@
 where $H$ is the mean curvature, $k_0$ is a spontaneous curvature, and
-$k_B$ is a bending modulus. One can also account for extensibility by
+$k_B$ is a bending modulus. One can also account
+for spatially dependent spontaneous curvature
+\cite{PhysRevE.79.031926,Lowengrub13,mahapatra_saintillan_rangamani_2020}
+and for extensibility by
 including in~\eqref{eq:Canham-Helfrich} an additional stretching term
 $k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are
-the deformed and equilibrium area densitities respectively.
+the deformed and equilibrium area densitities respectively
+\cite{chabanon2017}.
 
@@
 splay~\cite{Hamm2000ElasticEO, Terzi2019CurvatureTiltTO, Terzi2019ACQ,
-  Terzi2017NovelTC, Pinigin2020NewCT}. It contains~\eqref{eq:Canham-Helfrich}
+  Terzi2017NovelTC, Pinigin2020NewCT,Rangamani20140463}. It contains~\eqref{eq:Canham-Helfrich}
 as a special case.

### 2022-11-14 NSF2022/Description/specificaim2.tex
refs added

@@
 
-\begin{wrapfigure}[6]{l}{2.6in}
-  \centering
-%  \vspace{-10pt}
-  \includegraphics[width=2.5in]{figures/SA2Figures/confinement.pdf}
-  \vspace{-10pt}
-  \caption{\label{fig:stenosis} \footnotesize A granule vesicle passing
-  through a constricted geometry.}
-\end{wrapfigure}
-
 In experiments, it is known that interactions between bounding walls and
@@
 qua-gan-you2021}.
-\begin{wrapfigure}[16]{r}{2.1in}
-  \vspace{-4pt}
+
+\begin{wrapfigure}[6]{l}{2.6in}
   \centering
-  \input{figures/near_sing.tikz}
-  \vspace{-15pt}
-  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
-  quadrature method that works in two and three dimensions. The
-  spectrally-accurate trapezoid rule is used in points in
-  $\mathtt{Far}(\Gamma_i)$, while one dimensional interpolant is used
-  for points in $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength
-  spacing.}
+%  \vspace{-10pt}
+  \includegraphics[width=2.5in]{figures/SA2Figures/confinement.pdf}
+  \vspace{-10pt}
+  \caption{\label{fig:stenosis} \footnotesize A granule vesicle passing
+  through a constricted geometry.}
 \end{wrapfigure}
-
 The confinement introduces an additional computational
@@
 
+\begin{wrapfigure}[16]{r}{2.1in}
+  \vspace{-4pt}
+  \centering
+  \input{figures/near_sing.tikz}
+  \vspace{-15pt}
+  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
+  quadrature method that works in two and three dimensions. The
+  spectrally-accurate trapezoid rule is used in points in
+  $\mathtt{Far}(\Gamma_i)$, while one dimensional interpolant is used
+  for points in $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength
+  spacing.}
+\end{wrapfigure}
 Since we are interested in round (2D) and spherical (3D) granules, we

### 2022-11-14 NSF2022/SupplementaryDocs/suggestedreviewers.tex

@@
 Silas Alben & alben@umich.edu \\
+  Paul Atzberger & atzberg@math.ucsb.edu \\
 Robert Krasny & krasny@umich.edu \\
 Saverio Spagnolie \qquad & spagnolie@math.wisc.edu \\
-Petial Vlahovska & petia.vlahovska@northwestern.edu \\
+Petia Vlahovska & petia.vlahovska@northwestern.edu \\
 Noel Walkington & noelw@andrew.cmu.edu 
@@
 Bob Guy & guy@math.ucdavis.edu \\
-Alice McGillman \qquad &  \\
 Mike Shelley & mshelley@flatironinstitute.org 

### 2022-11-14 NSF2022/Description/summary.tex
summary updated

@@
 \vspace{-0.1in}
-This proposal aims to advance mathematical modeling, analysis and numerical simulations of
-collective dynamics and self-assembly arising from attractive
-interactions between dipolar/nematic particles in a suspension. 
-%
-%One example is the organization of lipids and proteins in vesicles, which is crucial
-%to design effective drug carriers. 
-%
-Physicists model such a self-assembly
-using particles possessing a biphasic material label on either half,
-with one more hydrophobic than the other. Hydrophobic surfaces
-experience a non-additive long-range attraction called the hydrophobic
-force. This force is a major source of nonspecific interactions in
-biology and soft matter. Despite its ubiquity, theoretical developments
-explaining its basic underlying principles have come relatively late.
-Motivated by its broad applicability, the PIs recently developed a novel
-and intuitive mathematical model, called the hydrophobic attraction
-potential model, based on the linear response of water to surface
-perturbations. This model was used to show, for the first time,
-self-assembly of such bipolar particles into vesicle-like structures
-using moving domain elliptic partial differential equations.
+This proposal aims to advance mathematical modeling, analysis, and
+numerical simulations of collective dynamics and self-assembly arising
+from attractive interactions between dipolar/nematic particles in a
+suspension. Physicists model such a self-assembly using particles
+possessing a biphasic material label on either half, with one more
+hydrophobic than the other. Hydrophobic surfaces experience a
+non-additive long-range attraction called the hydrophobic force. This
+force is a major source of nonspecific interactions in biology and soft
+matter. Despite its ubiquity, theoretical developments explaining its
+basic underlying principles have come relatively late.  Motivated by its
+broad applicability, the PIs recently developed a novel and intuitive
+mathematical model, called the hydrophobic attraction potential model,
+based on the linear response of water to surface perturbations. This
+model was used to show, for the first time, self-assembly of such
+bipolar particles into vesicle-like structures using moving domain
+elliptic partial differential equations (PDEs).
 
@@
 
-The PIs propose to analyze the near-linear elliptic PDEs, develop fast and accurate numerical schemes, 
-and apply their hydrophobic attraction potential model to
-more general self-organization dynamics. They aim to generalize the
-linear-response model to  a wider class of hydrophobic interactions, and
-numerically implement these interactions using integral equation
+The PIs propose to analyze the elliptic PDEs, develop fast and accurate
+numerical algorithms, and apply their hydrophobic attraction potential
+model to more general self-organization dynamics. They aim to generalize
+the linear-response model to a wider class of hydrophobic interactions,
+and numerically implement these interactions using integral equation
 formulations. Finally, they will develop a coarse-grained model based on
-the kinetic theory to investigate the rheological properties of the assembly of 
-particles with tunable hydrophobicity. The unifying
-aspects of the project are establishing a platform for efficiently
-simulating the collective dynamics at large scales, and the focusing on
-rigorous, mathematical analysis of the underlying model equations and
-complicated geometries. The project supports undergraduate and graduate
+the kinetic theory to investigate the rheological properties of the
+assembly of particles with tunable hydrophobicity. The unifying aspects
+of the project will establish a platform for efficiently simulating
+the collective dynamics of large numbers of particles, and focus on
+rigorous, mathematical analysis of the underlying model equations in
+complex geometries. The project supports undergraduate and graduate
 student collaborators.

### 2022-11-14 NSF2022/Description/summary.tex

@@
 \vspace{-0.1in}
-The purpose of this research is to reach interesting physical phenomena
-with less computational cost than molecular dynamics, and account for
-more general features that continuum theory misses. The main ingredient
-is defining a nonlocal interaction through the solution of an elliptic
-boundary value problem that has the phenomenological characteristics of
-long-range hydrophobic attraction. This minimal model, while intuitive,
-is quite a general description of amphiphiles in solvent and gives rise
-to rich phenomena from Janus particle aggregates to correctly predicting
-elastic properties of bilayer. The technical research tasks include
-quantifying collective properties of amphiphilic ensembles, improving on
-mathematical models, efficient, high-order numerical algorithms for
-large-scale simulations, and incorporating external fields through
-electric charge.
+This collaborative project focuses on modeling, simulation, and analysis
+of self-assembly and collective dynamics of granules. The main
+ingredient is a nonlocal interaction through the solution of an moving
+domain elliptic PDE that encompasses long-range amphiphilic and
+short-range steric interactions. The PIs have validated this
+coarse-grained model against well-known vesicle hydrodynamics. The
+technical research tasks include quantifying collective properties of
+amphiphilic ensembles, improving on mathematical models, efficient,
+high-order numerical algorithms for large-scale two- and
+three-dimensional simulations with confinement, and developing a kinetic
+theory for the collective dynamics.
+
+%The purpose of this research is to reach interesting physical phenomena
+%with less computational cost than molecular dynamics, and account for
+%more general features that continuum theory misses. The main ingredient
+%is defining a nonlocal interaction through the solution of an elliptic
+%boundary value problem that has the phenomenological characteristics of
+%long-range hydrophobic attraction. This minimal model, while intuitive,
+%is quite a general description of amphiphiles in solvent and gives rise
+%to rich phenomena from Janus particle aggregates to correctly predicting
+%elastic properties of bilayer. The technical research tasks include
+%quantifying collective properties of amphiphilic ensembles, improving on
+%mathematical models, efficient, high-order numerical algorithms for
+%large-scale simulations, and incorporating external fields through
+%electric charge.
 

### 2022-11-14 NSF2022/Description/backgroundv3.tex
clumsy-> blurred

@@
 granular details like molecular heterogeneity and orientations that may
-be crucial to the physics at mesoscopic scales, are clumsy to
-incorporate in the model. Moreover, numerical simulations of phase field
+be crucial to the physics at mesoscopic scales \cite{Midya2022}, are blurred
+by the model. Moreover, numerical simulations of phase field
 models typically discretize the entire fluid domain, and apply cutoff

### 2022-11-14 NSF2022/Description/specificaim1v2.tex
...

@@
 negative, respectively positive, splay $\nabla_{\Sigma} \cdot \dd$ in
-the outer, respectively inner monolayers. Here $\nabla_{\Sigma}\cdot{} =
-\nabla \cdot {} - \mathbf{N}\mathbf{N}^T \nabla$ is the surface
-divergence for the outward unit surface normal $\NN$. From differential
+the outer, respectively inner monolayers. Here $\nabla_{\Sigma}\cdot{}$
+the surface divergence. From differential
 geometry, we have that $\nabla\cdot \dd = \pm 2H$ whenever $\dd$ is
-everywhere parallel to $\NN$, and this is how curvature enters
+everywhere normal to $\Sigma$, and this is how curvature enters
 the granule-based description.  For two-dimensional vesicles,

### 2022-11-15 NSF2022/Description/summary.tex

@@
 This collaborative project focuses on modeling, simulation, and analysis
-of self-assembly and collective dynamics of granules. The main
+of self-assembly and collective dynamics of granules with non-uniform hydrophobicity on their boundaries. The main
 ingredient is a nonlocal interaction through the solution of an moving
@@
 short-range steric interactions. The PIs have validated this
-coarse-grained model against well-known vesicle hydrodynamics. The
+coarse-grained model against well-studied vesicle hydrodynamics. The
 technical research tasks include quantifying collective properties of
-amphiphilic ensembles, improving on mathematical models, efficient,
+ensembles of granules with tunable hydrophobicity, analyzing the mathematical in distinguished limits to make connection with continuum model,
+designing efficient,
 high-order numerical algorithms for large-scale two- and
 three-dimensional simulations with confinement, and developing a kinetic
-theory for the collective dynamics.
+theory to quantify the ratio of polar to nematic components in the collective dynamics.
 

### 2022-11-15 NSF2022/Description/specificaim1v2.tex
SA1 minor changes

@@
 Alikakos2008OnAE, Bronsard1993OnTB, Byeon2014SolutionsOH, Byeon2013OnAP,
-Alessio2005ENTIRESI, Trumper2007ExistenceOA, Benci2019MultipleSF} and so
-we must reformulate~\eqref{eqn:phase}. An appropriate reformulation
-is the following initial value problem with transport:
+Alessio2005ENTIRESI, Trumper2007ExistenceOA, Benci2019MultipleSF}.
+To have one solution $\phi$ for each $t$, 
+we must reformulate~\eqref{eqn:phase} as
+the following initial value problem with transport:
 \begin{align}
@@
 domains. A closely related and strongly developing direction in the area
-of nematics liquid crystals concerns the interaction of Landau de Gennes
+of nematics liquid crystals concerns the interaction of Landau-de Gennes
 functionals with colloids, and studies the qualitative structure of
@@
 \label{eq:amphiphilic_BC}
-  \phi(\xx) = h_i(\xx) = \tfrac{1}{2}\left(\dd_i \cdot 
+  \phi(\xx) = \tfrac{1}{2}\left(\dd_i \cdot 
     (\xx - \aa_i)/c_i + 1\right), \quad \xx \in \Gamma_i,
 \end{align}
-where $\dd_i$ is the director, $\aa_i$ is the center, and $c_i$ the
+where $\dd_i$ is the director, $\|\dd_i\| = 1$,
+$\aa_i$ is the center, and $c_i$ the
 ``radius'' of the $i$th granule. The phase $\phi$ takes values close to

### 2022-11-15 NSF2022/Description/backgroundv3.tex

@@
 by structural proteins that control virus
-structure~\cite{Kim2021SelfassembledMV}. Engineers have developed
-superior techniques that rely on nanoscale capillary and van der Waals
-forces to print high-resolution features on
-devices~\cite{Zeng20223DprintedMT}. Finally, researchers design
-efficient algorithms for constructing interaction kernels in the to
-study of agent-based systems like swarms and
-flocking~\cite{Lu2019NonparametricIO, Tadmor2021OnTM}.
+structure~\cite{Kim2021SelfassembledMV}. Engineers develop superior
+techniques that rely on nanoscale capillary and van der Waals forces to
+print high-resolution features on devices~\cite{Zeng20223DprintedMT}.
+Finally, researchers design efficient algorithms for constructing
+interaction kernels in the to study of agent-based systems like swarms
+and flocking~\cite{Lu2019NonparametricIO, Tadmor2021OnTM}.
 
@@
 level-sets of a smooth function, they can have almost arbitrary topology
-e.g., free ends, junctions~\cite{Promislow2017ExistenceBA,
+such as free ends and junctions~\cite{Promislow2017ExistenceBA,
 Promislow2022UndulatedBI}, the evolution equations can be studied by
@@
   superstructure e.g., a vesicle. The panel shows the moving domain
-  $\Omega(t)$, granules with centers $\aa_i$ and directors $\dd_i$, and
-  the unit inward normal $\nnu$. Panels (b), (c), (d) show the interplay
-  between the phase field $\phi$ (colormap) and granule configuration.
-  Red is for $\phi = 1$ and blue for $\phi = 0$; $W(\phi) =
-  \tfrac{1}{2}\phi^2$. The white arrows are the fluid velocity field.
-  The panels reach an equilibrium state in panel (d).}
+  $\Omega(t)$, granules with centers $\aa_i$ and directors $\dd_i$ with
+  $|\dd_i| = 1$, and the unit inward normal $\nnu$. Panels (b), (c), (d)
+  show the interplay between the phase field $\phi$ (colormap) and
+  granule configuration. Red is for $\phi = 1$ and blue for $\phi = 0$;
+  $W(\phi) = \tfrac{1}{2}\phi^2$. The white arrows are the fluid
+  velocity field. The panels reach an equilibrium state in panel (d).}
 \end{figure}
@@
 \sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
-T_i = \gamma\left[\epsilon^{-1} W(\phi)I
-  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
-  \phi^T\right)\right]
+T_i = \gamma\left(\frac{1}{\epsilon}W(\phi)I + \frac{\epsilon}{2}|\nabla \phi|^2 - \epsilon \nabla \phi \nabla \phi^T\right)
+%T_i = \gamma\left[\epsilon^{-1} W(\phi)I
+%  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
+%  \phi^T\right)\right]
 \end{align}
@@
 \includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
+\vspace{-25pt}
 \caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
@@
 \begin{wrapfigure}[16]{r}{4in} 
+  \vspace{-10pt}
   \includegraphics[width=4in]{figures/Background/coarsening.pdf}

### 2022-11-15 NSF2022/Description/specificaim2.tex
...

@@
 potential $u$ with surface charge density $\sigma$ is a special case of
-\eqref{eqn:conv}, where $G(\xx - \yy) = (4\pi \epsilon_0)^{-1}|\xx -
-\yy|^{-1}$ in three dimensions ($-(2\pi \epsilon_0)^{-1}\log|\xx - \yy|$
-in two dimensions) with $\epsilon_0$ the permittivity of vacuum.  In
+\eqref{eqn:conv}, where $G(\xx - \yy)$  takes the form
+$-(2\pi \epsilon_0)^{-1}\log|\xx - \yy|$
+in two dimensions and 
+$(4\pi \epsilon_0)^{-1}|\xx -\yy|^{-1}$ in three dimensions
+with $\epsilon_0$ the permittivity of vacuum.  In
 this context, equation~\eqref{eqn:bie} is analogous to Gauss's Law.
@@
 potential is
-\begin{align*}
+\begin{align}
   v^{P}(\xx) = \int_{\Omega(t)} G(\xx,\yy) F[\phi^N](\yy)\, d\yy, 
     \quad \xx \in \Omega(t),
-\end{align*}
+\end{align}
 where $G$ is the fundamental solution of $-\epsilon^2 \Delta +

### 2022-11-15 NSF2022/Description/summary.tex
yny 1114f

--- 2022-11-14 NSF2022/Description/summary.tex
@@
 This collaborative project focuses on modeling, simulation, and analysis
-of self-assembly and collective dynamics of granules. The main
-ingredient is a nonlocal interaction through the solution of an moving
-domain elliptic PDE that encompasses long-range amphiphilic and
+of self-assembly and collective dynamics of a suspension of granules with 
+non-uniform hydrophobicity on their boundaries. The main
+ingredient is a nonlocal interaction through the solution of moving
+domain elliptic PDEs that encompasses long-range (non-additive) amphiphilic and
 short-range steric interactions. The PIs have validated this
-coarse-grained model against well-known vesicle hydrodynamics. The
+coarse-grained model against well-studied vesicle hydrodynamics. The
 technical research tasks include quantifying collective properties of
-amphiphilic ensembles, improving on mathematical models, efficient,
+ensembles of granules with tunable hydrophobicity, analyzing the mathematical model in 
+distinguished limits to make connection with continuum models,
+designing efficient and
 high-order numerical algorithms for large-scale two- and
 three-dimensional simulations with confinement, and developing a kinetic
-theory for the collective dynamics.
+theory to quantify the both the polar and nematic characteristics in the collective dynamics.
 

### 2022-11-15 NSF2022/Description/broaderimpacts.tex
yny 1114h

@@
 classroom and offers undergraduates the opportunity to train alongside
-faculty and graduate students. With its unique combination of mathematical
-modeling, analysis, and scientific computing, the project highlights the
-potential advancement of STEM from applied mathematics.
+faculty and graduate students. With its unique combination of
+mathematical modeling, analysis, and scientific computing, the project
+highlights the potential advancement of STEM from applied mathematics.
 
@@
 
-\item Use machine learning to post-process data from the Janus particle self-assembly
+\item Use machine learning to post-process data from the granules self-assembly
 
@@
 The UR support is for eight summer weeks. In addition to collaborating
-with the PI, they will have tutorials and receive training in
+with PI Ryham, they will have tutorials and receive training in
 mathematical writing and presentation. The URs will have desks and
@@
 to write a summary report and give a presentation in the university's
-undergraduate research symposium. The PI will encourage the URs to
+undergraduate research symposium. PI Ryham will encourage the URs to
 participate in a national conference.
@@
 Science Park High School (PI Young) will also be encouraged to join the
-research team. PI Quaife will work with undergraduates and high school
+research team.
+
+PI Young has been actively involved with promotion of
+underrepresented students at NJIT. One PhD student, Herve Nganguia, is
+now an Assistant Professor at Towson University. PI Young has taught a
+broad spectrum of courses in fluid mechanics and applied math modeling.
+PI Quaife will work with undergraduates and high school
 students through the Undergraduate Research Opportunity Program and
@@
 
-To maximize vertical integration, the PIs and personnel will travel to
-New York for one or two weeks during the summers. Finally, we will
+%To maximize vertical integration, the PIs and personnel will travel to
+%New York for one or two weeks during the summers. 
+Finally, we will
 create several modules to include in our courses. These modules will
@@
 \label{sec:IntellectualMerit}
-The purpose of this research is to reach interesting physical phenomena
-with less computational cost than molecular dynamics, and account for
-more general features that continuum theory misses. The main ingredient
-is defining a nonlocal interaction through the solution of an elliptic
-boundary value problem that has the phenomenological characteristics of
-long-range hydrophobic attraction. This minimal model, while intuitive,
-is quite a general description of amphiphiles in solvent and gives rise
-to rich phenomena from Janus particle aggregates to correctly predicting
-elastic properties of bilayer. The technical research tasks include
-quantifying collective properties of amphiphilic ensembles, improving on
-mathematical models, efficient, high-order numerical algorithms for
-large-scale simulations, and incorporating external fields through
-electric charge.
+This collaborative project focuses on modeling, simulation, and analysis
+of self-assembly and collective dynamics of a suspension of granules with 
+non-uniform hydrophobicity on their boundaries. The main
+ingredient is a nonlocal interaction through the solution of moving
+domain elliptic PDEs that encompasses long-range (non-additive) amphiphilic and
+short-range steric interactions. The PIs have validated this
+coarse-grained model against well-studied vesicle hydrodynamics. The
+technical research tasks include quantifying collective properties of
+ensembles of granules with tunable hydrophobicity, analyzing the mathematical model in 
+distinguished limits to make connection with continuum models,
+designing efficient and
+high-order numerical algorithms for large-scale two- and
+three-dimensional simulations with confinement, and developing a kinetic
+theory to quantify the both the polar and nematic characteristics in the collective dynamics.
+%
+%The purpose of this research is to reach interesting physical phenomena
+%with less computational cost than molecular dynamics, and account for
+%more general features that continuum theory misses. The main ingredient
+%is defining a nonlocal interaction through the solution of an elliptic
+%boundary value problem that has the phenomenological characteristics of
+%long-range hydrophobic attraction. This minimal model, while intuitive,
+%is quite a general description of amphiphiles in solvent and gives rise
+%to rich phenomena from Janus particle aggregates to correctly predicting
+%elastic properties of bilayer. The technical research tasks include
+%quantifying collective properties of amphiphilic ensembles, improving on
+%mathematical models, efficient, high-order numerical algorithms for
+%large-scale simulations, and incorporating external fields through
+%electric charge.

### 2022-11-15 NSF2022/Description/priorsupport.tex
yny 1114h

@@
 Young2014_JFM, Young2015_PoF, Nganguia2015_CiCP, Pak2015_PNAS,
-fu2015pre}. PI Young has been actively involved with promotion of
-underrepresented students at NJIT. One PhD student, Herve Nganguia, is
-now an Assistant Professor at Towson University. PI Young has taught a
-broad spectrum of courses in fluid mechanics and applied math modeling.
+fu2015pre}. 
+%PI Young has been actively involved with promotion of
+%underrepresented students at NJIT. One PhD student, Herve Nganguia, is
+%now an Assistant Professor at Towson University. PI Young has taught a
+%broad spectrum of courses in fluid mechanics and applied math modeling.
 
@@
 with a strong analytical background. PI Young has been working on many
-areas of computational fluid dynamics and applications to math biology
-for many years. PI Quaife has been working on integral equation methods,
-fast algorithms, and their applications to fluid dynamics for many
-years.  Their recent collaborative works on the granule-based vesicles
+areas of fluid dynamics with applications to soft matters. 
+PI Quaife has been working on integral equation methods,
+fast algorithms, and their applications to fluid dynamics.  
+Their recent collaborative works on the granule-based vesicles
 in two dimensions~\cite{FuQuRyYo22, fu-ryh-qua-you2022} has provided a
@@
 %
-The management responsibility of this collaborative research will reside
-with PI Quaife. The research work is structured to meet the tasks
-discussed in \S\ref{sec:proposed-work}. The PIs and students will meet
-frequently on Zoom and in person when possible. PI Ryham and PI Young
+PI Quaife is responsible for the overall management of the project.
+The research work is structured to meet the tasks
+in \S\ref{sec:proposed-work}. The PIs and students will meet
+on Zoom and in person when possible. PI Ryham and PI Young
 will conduct biweekly meetings in person, with PI Quaife joining over
@@
 is shown in Figure~\ref{fig:schedule}. Each PI will spearhead a
-different Specific Aim, and program management will happen
+Specific Aim, and program management will happen
 throughout, with special coordination taken in quarters 4, 8, and

### 2022-11-15 NSF2022/Description/backgroundv3.tex
SA3
finished up background

@@
   \end{center}
-  \caption{\label{fig:flow_map} \footnotesize (a) Granules make a
-  superstructure e.g., a vesicle. The panel shows the moving domain
-  $\Omega(t)$, granules with centers $\aa_i$ and directors $\dd_i$ with
+  \caption{\label{fig:flow_map} \footnotesize (a) The moving domain,
+  $\Omega(t)$, of granules with centers $\aa_i$, directors $\dd_i$ with
   $|\dd_i| = 1$, and the unit inward normal $\nnu$. Panels (b), (c), (d)
@@
 \sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
-T_i = \gamma\left(\frac{1}{\epsilon}W(\phi)I + \frac{\epsilon}{2}|\nabla \phi|^2 - \epsilon \nabla \phi \nabla \phi^T\right)
+T_i = \gamma\left(\frac{1}{\epsilon}W(\phi)I + \frac{\epsilon}{2}|\nabla
+  \phi|^2 - \epsilon \nabla \phi \nabla \phi^T\right),
 %T_i = \gamma\left[\epsilon^{-1} W(\phi)I
@@
   blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
-  on one side and $\phi = 1$ on the other form multilamellar bilayers.
-  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
-  and $\phi=-1$ (green) on the other side form a checkerboard pattern.}
+  on one side and $\phi = 1$ (yellow) on the other form multilamellar
+  bilayers.  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow)
+  on one side and $\phi=-1$ (green) on the other side form a
+  checkerboard pattern.}
 \end{wrapfigure}
@@
 granule-vesicle suspension behaving as a tank-treading
-vesicle~\cite{Finken2008, Shaqfeh11} (see
-Figure~\ref{fig:JPv_linearshear}). Movies of
-Figure~\ref{fig:JPv_linearshear} reveal intermonolayer slip and derived
-values for intermonolayer friction are in good quantitative agreement
-those derived by atomistic and Martini force field simulation
+vesicle~\cite{Finken2008, Shaqfeh11} (Figure~\ref{fig:JPv_linearshear}).
+Movies of Figure~\ref{fig:JPv_linearshear} reveal intermonolayer slip
+and derived values for intermonolayer friction are in good quantitative
+agreement those derived by atomistic and Martini force field simulation
 studies~\cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
@@
 comparison of granule-based vesicles and the sharp interface
-representation yields shapes and trajectories that basically overlapped.
+representation yields shapes and trajectories that basically overlap.
 
@@
 equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is highly desirable
-from the Applied Math point of view as there are many \emph{Further
-Applications}, such as (i) amphiphilic Janus spheres that form diverse
-suprastructures~\cite{HaBr20, McBr21, Bradley2017}, (ii) pickering
-emulsions involving two-phase fluids and dense suspensions
+from the Applied Mathematics point of view as there are many
+\emph{Further Applications}, such as (i) amphiphilic Janus spheres that
+form diverse suprastructures~\cite{HaBr20, McBr21, Bradley2017}, (ii)
+pickering emulsions involving two-phase fluids and dense suspensions
 \cite{Bradley2016}, (iii) creation and manipulation of small droplets
@@
 include high-order, or even spectral, accuracy and well-conditioned
-linear system that can be solved iteratively with a mesh-independent
+linear systems that can be solved iteratively with a mesh-independent
 number of Krylov iterations such as the generalized minimal residual
 method (GMRES). However, IEs have challenges: nearly touching granules
-requires a quadrature rule for nearly-singular integrals; their
-discretization results in dense matrices; and they cannot immediately be
+requires a quadrature rule for nearly-singular integrals, their
+discretization results in dense matrices, and they cannot immediately be
 applied to non-linear PDEs. \S\ref{sec:specificaim2} discusses a variety
@@
 \subsection{Outline of the proposal}
-The aim of this proposal is to advance the simulation and theory for
-soft-matter systems and foster training in Mathematical Sciences.
-Section~\ref{sec:BroaderImpacts} summarizes the broader impacts and
-section~\ref{sec:IntellectualMerit} summarizes the intellectual merit of
-our research activity. Section~\ref{sec:proposed-work} contains our
-specific aims.
+The aim of this proposal is to advance the theory, simulation and
+modeling for soft-matter systems and foster training in Mathematical
+Sciences.  Section~\ref{sec:BroaderImpacts} summarizes the broader
+impacts and section~\ref{sec:IntellectualMerit} summarizes the
+intellectual merit of our research activity.
+Section~\ref{sec:proposed-work} contains our specific aims.

### 2022-11-15 NSF2022/Description/specificaim1v2.tex
SA1 minor changes
small change
SA3
spell checked SA1

@@
 We introduced~\eqref{eq:RBT}--\eqref{eqn:stressbalance} to complement
-existing methods for studing vesicles and bilayers. The simulation
+existing methods for studying vesicles and bilayers. The simulation
 results in Figures~\ref{fig:JPv_linearshear} and~\ref{fig:JPv_rupture}
@@
 Fu2018_SIAM}. Our next goal is to study the model using rigorous
-analysis and consider three-dimensionsional effects.
+analysis and consider three-dimensional effects.
 
@@
 for initial data $\phi_0$. The modified system enjoys an energy law
-similar to~\eqref{eq:energy_law} with an addtional dissipation term
+similar to~\eqref{eq:energy_law} with an additional dissipation term
 involving the square the Euler-Lagrange derivative $\frac{\delta
@@
 functionals with colloids, and studies the qualitative structure of
-defects around single or multiple coloidal
+defects around single or multiple colloidal
 particles~\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT,
@@
 \end{align}
-where $\dd_i$ is the director, $\|\dd_i\| = 1$,
-$\aa_i$ is the center, and $c_i$ the
-``radius'' of the $i$th granule. The phase $\phi$ takes values close to
-$1$ in the direction $\dd_i$, representing a hydrophobic tail, and
-values close to $0$ in the direction $\dd_i$ representing the
+where $\dd_i$ is the unit length director, $\aa_i$ is the center, and
+$c_i$ the ``radius'' of the $i$th granule. The phase $\phi$ takes values
+close to $1$ in the direction $\dd_i$, representing a hydrophobic tail,
+and values close to $0$ in the direction $\dd_i$ representing the
 hydrophilic head.
@@
 $k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are
-the deformed and equilibrium area densitities respectively
+the deformed and equilibrium area densities respectively
 \cite{chabanon2017}.
@@
 
-Finally, to consider three-dimensionsional effects, we will generalize
+Finally, to consider three-dimensional effects, we will generalize
 Problem 2 to \emph{numerically} study the energies of amphiphilic
@@
   \textbf{Problem 3.} Simulate surfaces made up of three-dimensional,
-  amphilic granules. Numerically investigate the limiting energy for
+  amphiphilic granules. Numerically investigate the limiting energy for
   large-$N_b$ suspensions.

### 2022-11-15 NSF2022/Description/specificaim1v2.tex
worked on SA1

@@
 The first step is to obtain some solid well-posedness results
-for~\eqref{eq:RBT}--\eqref{eqn:stressbalance}.
-This system is an
-autonomous ordinary differential equations (ODEs) for the body transformations
-$\FF_i$ with the rate of change defined by a system of PDEs.
-Strategies have been proposed for the solution of
-coupled PDE/ODE systems 
-\cite{Carichino2018EnergybasedOS,Quarteroni2016GeometricMM}.
-Regarding \eqref{eq:RBT}--\eqref{eqn:stressbalance},
-in the linear case and for fixed $t$, there is a unique
-solution ($\phi, \uu$) under appropriate assumptions for the boundaries
-and boundary data~\cite{manasthesis, rac-gre2016, LAX}. These define
-instantaneous rigid body velocities and rotations, leading to the
-following problem.
+for~\eqref{eq:RBT}--\eqref{eqn:stressbalance}. This system is an
+autonomous system of ordinary differential equations (ODEs) for the body
+transformations $\FF_i$ with the rate of change defined by a system of
+PDEs. Strategies have been proposed for the solution of coupled PDE/ODE
+systems \cite{Carichino2018EnergybasedOS,Quarteroni2016GeometricMM}.
+Regarding \eqref{eq:RBT}--\eqref{eqn:stressbalance}, in the linear case
+and for fixed $t$, there is a unique solution ($\phi, \uu$) under
+appropriate assumptions for the boundaries and boundary
+data~\cite{manasthesis, rac-gre2016, LAX}. These define instantaneous
+rigid body velocities and rotations, leading to the following problem.
 \begin{quotation}
@@
   boundary, with no-slip, rigid body motion boundary conditions, and a
-  linear background flow. Assume a single-well potential and a smooth
+  linear background flow. Assume a single-well potential and smooth
   phase field boundary conditions. What is the well-posedness in time of
@@
 establish that the system has a local-in-time solution. This involves
-domain perturbations and estimates for the solutions of second order
+domain perturbations and estimates for the solutions of second-order
 elliptic equations~\cite{Savar2002DomainPA, DANERS20081,
@@
   \caption{\label{fig:amphiphilic_assembly} \footnotesize
-  Self-organization under amphiphilic boundary condition. (a) Granules
-  first match hydrophobic tails (red), (b) then align length-wise. (c)
-  The same pattern of self-organization holds in three dimensions, as
-  simulated by Kohl, Corona, and
+  Self-organization under an amphiphilic boundary condition. (a)
+  Granules first match hydrophobic tails (red), (b) then align
+  length-wise. (c) The same pattern of self-organization holds in three
+  dimensions, as simulated by Kohl, Corona, and
   Veerapaneni~\cite{koh-cor-che-vee2021}.}
@@
 Alama2021SaturnRD, PhysRevE.96.042702}.
-
 PI Ryham has several works on
@@
 
-In the case of granules, bending enters through the
-splay of the granule directors. In
-Figure~\ref{fig:JPv_linearshear}, for example, the directors have
-negative, respectively positive, splay $\nabla_{\Sigma} \cdot \dd$ in
-the outer, respectively inner monolayers. Here $\nabla_{\Sigma}\cdot{}$
-the surface divergence. From differential
+In the case of granules, bending enters through the splay of the granule
+directors. In Figure~\ref{fig:JPv_linearshear}, for example, the
+directors have negative, respectively positive, splay $\nabla_{\Sigma}
+\cdot \dd$ in the outer, respectively inner monolayers. Here
+$\nabla_{\Sigma}\cdot{}$ is the surface divergence. From differential
 geometry, we have that $\nabla\cdot \dd = \pm 2H$ whenever $\dd$ is
-everywhere normal to $\Sigma$, and this is how curvature enters
-the granule-based description.  For two-dimensional vesicles,
-$H$ is replaced with the curvature $\kappa$ of the curve $\mathcal{C}$.
-Granules are at rest when attraction balances repulsion, and will have
-stretching energy when the distance between neighboring granules is increased
-from rest.
+everywhere normal to $\Sigma$, and this is how curvature enters the
+granule-based description. For two-dimensional vesicles, $H$ is replaced
+with the curvature $\kappa$ of the curve $\mathcal{C}$. Granules are at
+rest when attraction balances repulsion, and will have stretching energy
+when the distance between neighboring granules is increased from rest.
 
@@
 films~\cite{Golovaty2017DimensionRF, Golovaty2015DimensionRF,
-doi:10.1142/S0218202516500470, FoFrLe07}.  PI Ryham has carried out
-sharp interface-limit analyses for phase field formulations of elastic
-bending energy~\cite{0951-7715-18-3-016, Du05}, approximations of
-Gaussian curvature and the Euler characteristic in phase
-field~\cite{DuEuler}, and vanishing Debye-length in Poisson-Boltzman
-equations~\cite{Lee2018, 1531-3492_2006_2_357}.
+doi:10.1142/S0218202516500470, FoFrLe07}. PI Ryham has carried out sharp
+interface-limit analyses for phase field formulations of elastic bending
+energy~\cite{0951-7715-18-3-016, Du05}, approximations of Gaussian
+curvature and the Euler characteristic in phase field~\cite{DuEuler},
+and vanishing Debye-length in Poisson-Boltzman equations~\cite{Lee2018,
+1531-3492_2006_2_357}.
 

### 2022-11-15 NSF2022/Description/backgroundv3.tex
SA3 done

@@
 \label{eqn:hydro_stress}
-\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
-T_i = \gamma\left(\frac{1}{\epsilon}W(\phi)I + \frac{\epsilon}{2}|\nabla
-  \phi|^2 - \epsilon \nabla \phi \nabla \phi^T\right),
+\sigma = -pI + \mu(\nabla \uu + \nabla \uu^T),\quad 
+T_i = \gamma\left(\frac{1}{\epsilon}W(\phi)I + \frac{\epsilon}{2}|\nabla \phi|^2I - \epsilon \nabla \phi \nabla \phi^T\right)
 %T_i = \gamma\left[\epsilon^{-1} W(\phi)I
@@
   blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
-  on one side and $\phi = 1$ (yellow) on the other form multilamellar
-  bilayers.  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow)
-  on one side and $\phi=-1$ (green) on the other side form a
-  checkerboard pattern.}
+  on one side and $\phi = 2$ on the other form multilamellar bilayers.
+  (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
+  and $\phi=-1$ (green) on the other side form a checkerboard pattern.}
 \end{wrapfigure}
@@
 modeling for soft-matter systems and foster training in Mathematical
-Sciences.  Section~\ref{sec:BroaderImpacts} summarizes the broader
+Sciences.
+The success of the proposed research requires complementary expertise
+and collaborative efforts in physics, applied mathematics, and
+scientific computing. The PIs' recent collaborative
+works~\cite{FuQuRyYo22, fu-ryh-qua-you2022,FuQuRyYo22}
+are a solid foundation for the proposed research.
+
+Section~\ref{sec:BroaderImpacts} summarizes the broader
 impacts and section~\ref{sec:IntellectualMerit} summarizes the

### 2022-11-15 NSF2022/Description/priorsupport.tex

@@
 \end{comment}
-\textbf{Project management}: 
-%
-The success of the proposed research requires complementary expertise
-and collaborative efforts in physics, applied mathematics, and
-scientific computing. PI Ryham has been working on mathematical modeling
-with a strong analytical background. PI Young has been working on many
-areas of fluid dynamics with applications to soft matters. 
-PI Quaife has been working on integral equation methods,
-fast algorithms, and their applications to fluid dynamics.  
-Their recent collaborative works on the granule-based vesicles
-in two dimensions~\cite{FuQuRyYo22, fu-ryh-qua-you2022} has provided a
-solid foundation for the proposed research.
-
-\smallskip
-
-\textbf{Collaboration plan}: 
-%
 PI Quaife is responsible for the overall management of the project.
@@
 in \S\ref{sec:proposed-work}. The PIs and students will meet
-on Zoom and in person when possible. PI Ryham and PI Young
+by video conference and in person when possible. PI Ryham and PI Young
 will conduct biweekly meetings in person, with PI Quaife joining over
-Zoom from Florida. The PIs will share software packages, paper sources,
+video conference from Florida. The PIs will share software packages, paper sources,
 and references on a common \textsf{Git} repository. The resulting
@@
 %
-\textbf{Research Schedule:} The detailed schedule for the proposed work
+The detailed schedule for the proposed work
 is shown in Figure~\ref{fig:schedule}. Each PI will spearhead a

### 2022-11-15 NSF2022/Description/broaderimpacts.tex
ed imp done

@@
 \label{subsec:Educational_plans}
-To foster training in mathematical sciences, the proposal supports two
-undergraduate researchers (URs) per year at Fordham University. PI Ryham
-has worked side-by-side and published with undergraduate
-coauthors~\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16}. He is presently
-mentoring a Clare Boothe Luce Scholar on mathematical analysis of trends
-in election redistricting. With another Fordham supported UR, he is
-finishing a paper on a closed-form energy density for translationally
-invariant bilayers. Based on these experiences, we have outlined three
-projects for the present proposal.
-\todo[inline]{Rolf: Can you update this?}
+To foster training in mathematical sciences,
+the proposal supports two undergraduate researchers
+(URs) per year at Fordham University---for eight summer weeks.
+The UR will collaborate directly with PI Ryham,
+receive tutorials e.g., numerical methods,
+and be guided on mathematical writing and presentation.
+Fordham Mathematics recently completed a collaboration studio 
+purpose-built for UR support.
+Work products include a summary manuscript,
+a presentation in the Fordham Undergraduate Research Symposium
+and departmental seminars, and participation in a national conference.
+We have outlined three projects for the present proposal.
 \begin{enumerate}[noitemsep,topsep=0pt]
 \item Translate project code from MATLAB into a compiled language 
+\item Use machine learning to post-process data of granule dynamics
+\item Investigate geometrical self-assembly and generate visualizations
+\end{enumerate}
+PI Ryham has worked side-by-side with dozens of
+undergraduates and high-schoolers in
+supported summer research, Girls in Science Technology and Mathematics,
+and the Clare Boothe Luce Scholarship program
+and the activity benefited their careers in
+machine learning, water resources engineering, threat detection,
+and the NYC Department of Education.
+Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on election redistricting.
+The PI is finishing works on the energy density lipid  bilayers
+with a recently graduated UR, now working at Raytheon Technologies.
+His published works~\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16} include
+four undegraduate coauthors.
 
-\item Use machine learning to post-process data from the granules self-assembly
-
-\item Mathematically investigate self-assembly in the zero-screen-length limit
-\end{enumerate}
-The UR support is for eight summer weeks. In addition to collaborating
-with PI Ryham, they will have tutorials and receive training in
-mathematical writing and presentation. The URs will have desks and
-meeting room in a recently completed collaboration space built for the
-Mathematics Department. As a condition of support, they will be required
-to write a summary report and give a presentation in the university's
-undergraduate research symposium. PI Ryham will encourage the URs to
-participate in a national conference.
-
-To meaningfully engage the community, the PIs will prioritize students
-coming from underrepresented groups and specifically target students
+To increase the participation of women,
+persons with disabilities and underrepresented minorities in STEM,
+the PIs will specifically target students
 whose socio-economic background prevents them from participating in
-out-of-state research experiences. PI Ryham will solicit applicants from
+out-of-state research experiences.
+The inclusion objective will be aided by the fact that  
+Fordham's class of 2026 weighs in with 63 \% women
+and more than 46 \% domestic students of color. 
+PI Ryham will solicit applicants from
 Fordham University's Collegiate Science and Technology Entry Program.

### 2022-11-15 NSF2022/Description/specificaim2.tex

@@
 \begin{align}
-  \uu(\xx) = \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
+  \uu(\xx) = \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, dS_\yy,
   \label{eqn:conv}
@@
 automatically satisfied. The density function $\ssigma$ is chosen to
-satisfy the boundary condition, and this results in an IE 
+satisfy the boundary condition, and this results is an IE 
 \begin{align}
   \gg(\xx) = \lambda \ssigma(\xx) + 
-    \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
+    \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, dS_\yy,
     \quad \xx \in \partial\Omega(t),
@@
 As an illustration, the problem of finding the global electrostatic
-potential $u$ with surface charge density $\sigma$ is a special case of
-\eqref{eqn:conv}, where $G(\xx - \yy)$  takes the form
-$-(2\pi \epsilon_0)^{-1}\log|\xx - \yy|$
-in two dimensions and 
-$(4\pi \epsilon_0)^{-1}|\xx -\yy|^{-1}$ in three dimensions
-with $\epsilon_0$ the permittivity of vacuum.  In
-this context, equation~\eqref{eqn:bie} is analogous to Gauss's Law.
+potential $u$ with surface charge density $\sigma$ is a special case
+of~\eqref{eqn:conv}, where $G(\xx - \yy)$ takes the form $-(2\pi
+\epsilon_0)^{-1}\log|\xx - \yy|$ in two dimensions and $(4\pi
+\epsilon_0)^{-1}|\xx -\yy|^{-1}$ in three dimensions with $\epsilon_0$
+the permittivity in a vacuum. In this context, equation~\eqref{eqn:bie}
+is analogous to Gauss's Law.
 
@@
 
-\begin{wrapfigure}[16]{r}{2.1in}
+\begin{wrapfigure}[17]{r}{1.9in}
   \vspace{-4pt}
@@
   \caption{\label{fig:interpquad} \footnotesize An interpolation-based
-  quadrature method that works in two and three dimensions. The
-  spectrally-accurate trapezoid rule is used in points in
-  $\mathtt{Far}(\Gamma_i)$, while one dimensional interpolant is used
-  for points in $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength
-  spacing.}
+  quadrature method that works in two and three dimensions. The accurate
+  trapezoid rule is used in points in $\mathtt{Far}(\Gamma_i)$, while
+  one dimensional interpolant is used for points in
+  $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength spacing.}
 \end{wrapfigure}
@@
 will exploit the fact that integrals can be computed with spectral
-accuracy by transforming the integrals to to a Fourier (2D) or spherical
+accuracy by transforming the integrals to a Fourier (2D) or spherical
 harmonic (3D) basis. This technique can be used to evaluate layer
@@
 two-dimensional PDEs~\cite{che-lin-her-qua2022}. The method uses
-singularity subtraction to write the fundamental solution of the PDE as a
-sum of two terms: a logarithmic function and a continuously
-differentiable function. Then the Barycentric-type formulae can be
+singularity subtraction to write the fundamental solution of the PDE as
+a sum of two terms: a logarithmic function and a continuously
+differentiable remainder. Then the Barycentric-type formulae can be
 applied to the logarithmic function, and the standard trapezoid
-rule~\cite{tre-wei2014} can be applied to the other function. These
+rule~\cite{tre-wei2014} can be applied to the remainder. These
 singularity subtraction methods can also accurately compute derivatives
@@
 computational tool is a collision-aware adaptive time stepping method.
-The phase field results in the granules attracting one another and
-this leads to nearly contacting boundaries. Our current
+The phase field results in the granules attracting one another and this
+leads to nearly contacting boundaries that, even with high-order spatial
+accuracy, can collide due to time stepping error. Our current
 implementation uses a repulsive Lennard-Jones force, but this introduces
 stiffness, thereby requiring small time steps, and this can be a
-bottleneck when 
+bottleneck when simulating
 \begin{wrapfigure}[26]{l}{1.8in}
@@
 \end{wrapfigure}
-simulating dense suspensions. Therefore, we will develop
-a high-order collision-avoiding adaptive time stepping method. This
-method will avoid collisions by using the minimal separation
-distance to impose a non-overlapping constraint. This results in a
-linear complementarity problem that can be solve efficiently with a
-projected gradient descent method~\cite{Yan2019}. High-order time
-adaptivity will be based on PI Quaife's previous work on
-suspensions~\cite{qua-bir2016}, and this method has proven to be a
-robust method to simulate dense suspensions~\cite{qua-vee-you2019,
-kab-qua-bir2017, qua-gan-you2021}. Following this previous work, the
-proposed work will use a spectral deferred correction method since it
-iteratively applies a low-order, single-step method to achieve
-high-order accuracy. At each time step, we will compute the total force
-and torque of the system which is computationally cheap and physically
-zero, and therefore provides an estimate of the local truncation error.
-PI Quaife's experience is that error estimates based on physical
-constraints, such as force- and torque-free conditions, appropriately
-determine adaptive time step sizes so that the dynamics are resolved
-without the computational expense of techniques such as embedded
-Runge-Kutta, step-doubling, and Richardson extrapolation.
+dense suspensions. Therefore, we will develop a high-order
+collision-avoiding adaptive time stepping method. This method will avoid
+collisions by using the minimal separation distance to impose a
+non-overlapping constraint. This results in a linear complementarity
+problem that can be solve efficiently with a projected gradient descent
+method~\cite{Yan2019}. High-order time adaptivity will be based on PI
+Quaife's previous work on suspensions~\cite{qua-bir2016}, and this
+method has proven to be a robust method to simulate dense
+suspensions~\cite{qua-vee-you2019, kab-qua-bir2017, qua-gan-you2021}.
+Following this previous work, the proposed work will use a spectral
+deferred correction method that iteratively applies a low-order,
+single-step method to achieve high-order accuracy. At each time step, we
+will compute the total force and torque of the system which is
+computationally cheap and physically zero, and therefore provides an
+estimate of the time stepping error. PI Quaife's experience is that
+error estimates based on physical constraints, such as force- and
+torque-free conditions, appropriately determine adaptive time step sizes
+so that the dynamics are resolved without the computational expense of
+techniques such as embedded Runge-Kutta, step-doubling, and Richardson
+extrapolation.
 
-The phase field is governed by the PDE~\eqref{eqn:phase} in the
-solvent region $\Omega(t)$. If $W(\phi) = \tfrac{1}{2}\phi^2$,
+The phase field is governed by the PDE~\eqref{eqn:phase} in the solvent
+region $\Omega(t)$. If $W(\phi) = \tfrac{1}{2}\phi^2$,
 equation~\eqref{eqn:phase} is linear, and the PIs have used IEs to solve
-address this problem~\cite{Fu2018_SIAM, FuQuRyYo22,
-fu-ryh-qua-you2022}, but for a double-well potential $W(\phi)$, the
-resulting PDE is nonlinear, motivating the following problem:
+address this problem~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022},
+but for a double-well potential $W(\phi)$, the resulting PDE is
+nonlinear, motivating the following problem:
 
@@
   \noindent
-  \textbf{Problem 5.} How can IEs be coupled with a Newton solver to
+  \textbf{Problem 5.} How can IEs be coupled with a Newton method to
   solve the non-linear PDE~\eqref{eqn:phase}?
@@
 approximate second derivative (blue curve). While the inexact Newton's
-method requires roughly twice as many iterations to reach of a tolerance
+method requires roughly twice as many iterations to reach a tolerance
 of $10^{-4}$, each iteration is significantly cheaper to apply.

### 2022-11-15 NSF2022/Description/broaderimpacts.tex
touch up

@@
 (URs) per year at Fordham University---for eight summer weeks.
-The UR will collaborate directly with PI Ryham,
+The URs will collaborate directly with the PIs,
 receive tutorials e.g., numerical methods,
@@
 and the NYC Department of Education.
-Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on election redistricting.
-The PI is finishing works on the energy density lipid  bilayers
+Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on
+polling accessibility in New York City.
+The PI is finishing works on energy densities for lipid  bilayers
 with a recently graduated UR, now working at Raytheon Technologies.
-His published works~\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16} include
-four undegraduate coauthors.
+His publications include works
+with seven undegraduate coauthors
+~\cite{Figueroa2012CuttingCI, RYHAM20112929, RyWaCo13, RyKlYaCo16}.
 
@@
 out-of-state research experiences.
-The inclusion objective will be aided by the fact that  
+The inclusion objectives will be aided by the fact that  
 Fordham's class of 2026 weighs in with 63 \% women

### 2022-11-15 NSF2022/Description/broaderimpacts.tex
yny 1115a

@@
 PI Young has been actively involved with promotion of
-underrepresented students at NJIT. One PhD student, Herve Nganguia, is
-now an Assistant Professor at Towson University. PI Young has taught a
-broad spectrum of courses in fluid mechanics and applied math modeling.
-PI Quaife will work with undergraduates and high school
+underrepresented students at NJIT.  A former PhD student, Herve Nganguia, is African American and 
+now an Assistant Professor at Towson University. 
+%PI Young has taught a
+%broad spectrum of courses in fluid mechanics and applied math modeling.
+PI Quaife will continue to work with undergraduates and high school
 students through the Undergraduate Research Opportunity Program and
-Young Scholar's Program, as he has done in the past.
+Young Scholar's Program.
+%, as he has done in the past.
 

### 2022-11-15 NSF2022/Description/specificaim1v2.tex
yny 1115b

@@
 implementation for large granule-number and three-dimensional
-suspensions (\S\ref{sec:specificaim2}: PI Quaife), and kinetic theory
+suspensions (\S\ref{sec:specificaim2}: PI Quaife), and kinetic theory modeling
 (\S\ref{sec:specificaim3}: PI Young).
@@
 \end{align}
-where $\dd_i$ is the unit length director, $\aa_i$ is the center, and
+where $\dd_i$ is the director, $|\dd_i| = 1$, $\aa_i$ is the center, and
 $c_i$ the ``radius'' of the $i$th granule. The phase $\phi$ takes values

### 2022-11-15 NSF2022/Description/backgroundv3.tex
touch up
...

@@
 using amphiphilic microparticles~\cite{Ha2022SurfaceEM,
-Ha2020MinimalSC}, and (iv) tension driven fabrication of
-microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,
+Ha2020MinimalSC}, and (iv) tension driven microfabrication
+~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,
 Zeng20223DprintedMT, Russell2016EnergyLF}.
@@
 scientific computing. The PIs' recent collaborative
-works~\cite{FuQuRyYo22, fu-ryh-qua-you2022,FuQuRyYo22}
+works~\cite{FuQuRyYo22, fu-ryh-qua-you2022}
 are a solid foundation for the proposed research.
-
 Section~\ref{sec:BroaderImpacts} summarizes the broader

### 2022-11-15 NSF2022/Description/broaderimpacts.tex
...
did broader impacts, intellectual merit, and overview

@@
 mathematical modeling, analysis, and scientific computing, the project
-highlights the potential advancement of STEM from applied mathematics.
+highlights the potential advancement of STEM from Applied Mathematics.
 
@@
 \item Translate project code from MATLAB into a compiled language 
-\item Use machine learning to post-process data of granule dynamics
-\item Investigate geometrical self-assembly and generate visualizations
+\item Use machine learning and visualizations to post-process data of granule dynamics
+\item Mathematical modeling of group affiliation in social science  
 \end{enumerate}
@@
 This collaborative project focuses on modeling, simulation, and analysis
-of self-assembly and collective dynamics of a suspension of granules with 
-non-uniform hydrophobicity on their boundaries. The main
-ingredient is a nonlocal interaction through the solution of moving
-domain elliptic PDEs that encompasses long-range (non-additive) amphiphilic and
+of self-assembly and collective dynamics of a suspension of granules
+with non-uniform hydrophobicity on their boundaries. The main ingredient
+is a nonlocal interaction through the solution of moving domain elliptic
+PDEs that encompasses long-range (non-additive) amphiphilic and
 short-range steric interactions. The PIs have validated this
@@
 technical research tasks include quantifying collective properties of
-ensembles of granules with tunable hydrophobicity, analyzing the mathematical model in 
-distinguished limits to make connection with continuum models,
-designing efficient and
-high-order numerical algorithms for large-scale two- and
-three-dimensional simulations with confinement, and developing a kinetic
-theory to quantify the both the polar and nematic characteristics in the collective dynamics.
-%
-%The purpose of this research is to reach interesting physical phenomena
-%with less computational cost than molecular dynamics, and account for
-%more general features that continuum theory misses. The main ingredient
-%is defining a nonlocal interaction through the solution of an elliptic
-%boundary value problem that has the phenomenological characteristics of
-%long-range hydrophobic attraction. This minimal model, while intuitive,
-%is quite a general description of amphiphiles in solvent and gives rise
-%to rich phenomena from Janus particle aggregates to correctly predicting
-%elastic properties of bilayer. The technical research tasks include
-%quantifying collective properties of amphiphilic ensembles, improving on
-%mathematical models, efficient, high-order numerical algorithms for
-%large-scale simulations, and incorporating external fields through
-%electric charge.
+ensembles of granules with tunable hydrophobicity, analyzing the
+mathematical model in distinguished limits to make connections with
+continuum models, designing efficient and high-order numerical
+algorithms for large-scale two- and three-dimensional simulations with
+confinement, and developing a kinetic theory to quantify both the polar
+and nematic characteristics in the collective dynamics.

### 2022-11-15 NSF2022/Description/summary.tex
did broader impacts, intellectual merit, and overview

@@
 
-%This proposal aims to advance mathematical modeling and analysis of
-%collective dynamics of amphiphilic self-assembly. Amphiphilic particles
-%such as lipid molecules possess both hydrophobic and hydrophilic
-%surfaces and self-assemble into meso/macroscopic structures such as
-%micelles and bilayers of lipids. Experimentalists model self-assembly
-%using Janus particles—spherical particles possessing a biphasic material
-%label on either hemisphere. Janus particles have been widely used in
-%soft matter physics as a model amphiphilic colloid and can be designed
-%for catalytic activity or stimuli-responsive smart materials.
-
-%Hydrophobic surfaces experience a nonadditive long-range attraction
-%called the hydrophobic force. This force is a major source of
-%nonspecific interactions in biology and soft matter. Despite its
-%ubiquity, theoretical developments explaining its basic underlying
-%principles have come relatively late. Motivated by its broad
-%applicability, the PIs recently developed a novel and intuitive
-%mathematical model, called the hydrophobic attraction potential model,
-%based on the linear response of water to surface perturbations. This
-%model was used to show, for the first time, self-assembly of Janus
-%particles into vesicle-like structures using a partial differential
-%equation-based particle interaction.
-
 The PIs propose to analyze the elliptic PDEs, develop fast and accurate
@@
 assembly of particles with tunable hydrophobicity. The unifying aspects
-of the project will establish a platform for efficiently simulating
-the collective dynamics of large numbers of particles, and focus on
+of the project will establish a platform for efficiently simulating the
+collective dynamics of large numbers of particles, and focus on
 rigorous, mathematical analysis of the underlying model equations in
@@
 technical research tasks include quantifying collective properties of
-ensembles of granules with tunable hydrophobicity, analyzing the mathematical model in 
-distinguished limits to make connection with continuum models,
-designing efficient and
-high-order numerical algorithms for large-scale two- and
-three-dimensional simulations with confinement, and developing a kinetic
-theory to quantify the both the polar and nematic characteristics in the collective dynamics.
+ensembles of granules with tunable hydrophobicity, analyzing the
+mathematical model in distinguished limits to make connections with
+continuum models, designing efficient and high-order numerical
+algorithms for large-scale two- and three-dimensional simulations with
+confinement, and developing a kinetic theory to quantify both the polar
+and nematic characteristics in the collective dynamics.
 

### 2022-11-15 NSF2022/Description/broaderimpacts.tex
changes throughout

@@
 \label{subsec:Educational_plans}
-To foster training in mathematical sciences,
-the proposal supports two undergraduate researchers
-(URs) per year at Fordham University---for eight summer weeks.
-The URs will collaborate directly with the PIs,
-receive tutorials e.g., numerical methods,
-and be guided on mathematical writing and presentation.
-Fordham Mathematics recently completed a collaboration studio 
-purpose-built for UR support.
-Work products include a summary manuscript,
-a presentation in the Fordham Undergraduate Research Symposium
-and departmental seminars, and participation in a national conference.
-We have outlined three projects for the present proposal.
+To foster training in mathematical sciences, the proposal supports two
+undergraduate researchers (URs) per year at Fordham University---for
+eight summer weeks. The URs will collaborate directly with the PIs,
+receive tutorials (e.g., numerical methods), and be guided on
+mathematical writing and presentation. Fordham Mathematics recently
+completed a collaboration studio purpose-built for UR support. Work
+products include a summary manuscript, a presentation in the Fordham
+Undergraduate Research Symposium and departmental seminars, and
+participation in a national conference. We have outlined three projects
+for the present proposal:
 \begin{enumerate}[noitemsep,topsep=0pt]
-\item Translate project code from MATLAB into a compiled language 
-\item Use machine learning and visualizations to post-process data of granule dynamics
-\item Mathematical modeling of group affiliation in social science  
+  \item Translate project code from MATLAB into a compiled language;
+  \item Use machine learning and visualizations to post-process data of
+    granule dynamics;
+  \item Mathematical modeling of group affiliation in social science.
 \end{enumerate}
-PI Ryham has worked side-by-side with dozens of
-undergraduates and high-schoolers in
-supported summer research, Girls in Science Technology and Mathematics,
-and the Clare Boothe Luce Scholarship program
-and the activity benefited their careers in
-machine learning, water resources engineering, threat detection,
-and the NYC Department of Education.
-Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on
-polling accessibility in New York City.
-The PI is finishing works on energy densities for lipid  bilayers
-with a recently graduated UR, now working at Raytheon Technologies.
-His publications include works
-with seven undegraduate coauthors
-~\cite{Figueroa2012CuttingCI, RYHAM20112929, RyWaCo13, RyKlYaCo16}.
+PI Ryham has worked side-by-side with dozens of undergraduates and
+high-schoolers in supported summer research, Girls in Science Technology
+and Mathematics, and the Clare Boothe Luce Scholarship program and the
+activity benefited their careers in machine learning, water resources
+engineering, threat detection, and the NYC Department of Education.
+Presently PI Ryham is mentoring a Clare Boothe Luce Scholar on polling
+accessibility in New York City. The PI is finishing works on energy
+densities for lipid bilayers with a recently graduated UR, now working
+at Raytheon Technologies. His publications include works with seven
+undergraduate coauthors~\cite{Figueroa2012CuttingCI, RYHAM20112929,
+RyWaCo13, RyKlYaCo16}.
 
-To increase the participation of women,
-persons with disabilities and underrepresented minorities in STEM,
-the PIs will specifically target students
-whose socio-economic background prevents them from participating in
-out-of-state research experiences.
-The inclusion objectives will be aided by the fact that  
-Fordham's class of 2026 weighs in with 63 \% women
-and more than 46 \% domestic students of color. 
-PI Ryham will solicit applicants from
-Fordham University's Collegiate Science and Technology Entry Program.
-Students from the Bronx High School of Science (PI Ryham) and Newark
-Science Park High School (PI Young) will also be encouraged to join the
-research team.
+To increase the participation of women, persons with disabilities and
+underrepresented minorities in STEM, the PIs will specifically target
+students whose socio-economic background prevents them from
+participating in out-of-state research experiences. The inclusion
+objectives will be aided by the fact that Fordham's class of 2026 weighs
+in with 63\% women and more than 46\% domestic students of color. PI
+Ryham will solicit applicants from Fordham University's Collegiate
+Science and Technology Entry Program. Students from the Bronx High
+School of Science (PI Ryham) and Newark Science Park High School (PI
+Young) will also be encouraged to join the research team.
 
-PI Young has been actively involved with promotion of
-underrepresented students at NJIT.  A former PhD student, Herve Nganguia, is African American and 
-now an Assistant Professor at Towson University. 
-%PI Young has taught a
-%broad spectrum of courses in fluid mechanics and applied math modeling.
-PI Quaife will continue to work with undergraduates and high school
-students through the Undergraduate Research Opportunity Program and
-Young Scholar's Program.
-%, as he has done in the past.
+PI Young has been actively involved with promotion of underrepresented
+students at NJIT. A former PhD student, Herve Nganguia, is African
+American and now an Assistant Professor at Towson University. PI Quaife
+is currently advising three female PhD students, and one is African
+American and the recipient of the McKnight Doctoral Fellowship which
+addresses the underrepresentation of African American and Hispanic
+faculty at colleges and universities in the state of Florida. PI Quaife
+will also continue to work with undergraduates and high school students
+through the Undergraduate Research Opportunity Program and Young
+Scholar's Program.
 
-%To maximize vertical integration, the PIs and personnel will travel to
-%New York for one or two weeks during the summers. 
-Finally, we will
-create several modules to include in our courses. These modules will
-introduce topics from numerical linear algebra and optimization and
-highlight concrete applications of mathematics based on the ideas of the
-proposal.
+Finally, we will create several modules to include in our courses. These
+modules will introduce topics from numerical linear algebra and
+optimization and highlight concrete applications of mathematics based on
+the ideas of the proposal.
 

### 2022-11-15 NSF2022/Description/specificaim2.tex
changes throughout

@@
 bottleneck when simulating
-\begin{wrapfigure}[26]{l}{1.8in}
-  \vspace{-0pt}
-  \centering
-  \input{figures/doublewell.tikz} 
-  \vspace{-10pt}
-  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
-  The solution of the one-dimensional phase
-  transition~\eqref{eqn:phase}. (c) The convergence of exact and inexact
-  Newton's methods.}
-\end{wrapfigure}
 dense suspensions. Therefore, we will develop a high-order
@@
 equation~\eqref{eqn:phase} is linear, and the PIs have used IEs to solve
-address this problem~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022},
-but for a double-well potential $W(\phi)$, the resulting PDE is
-nonlinear, motivating the following problem:
+this problem~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022}, but for
+a double-well potential $W(\phi)$, the resulting PDE is nonlinear,
+motivating the following problem:
 
@@
 $\phi^{N+1} = \phi^{N} - \alpha (F'(\phi^N))^{-1} F(\phi^N)$, where
-$F'(\phi^N) = -\epsilon^2 \Delta + W''(\phi^N)$ is the
-Fr\'{e}chet derivative of $F$, and $\alpha$ is the step size that will
-be determined using backtracking. This requires solving the variable
-coefficient PDE $-\epsilon^2 \Delta v + W''(\phi^{N}) v =
-F[\phi^N]$, which is challenging with an integral equation since a
-fundamental solution is not readily available. However, by choosing a
-double-well potential with $W''(\phi_0) = W''(\phi_1) = \beta$, we
-propose to instead use an inexact Newton's method where $(F')^{-1}$ is
-approximated with the solution of $-\epsilon^2 \Delta v +
-\beta v = F[\phi^N]$. We test the efficacy of the exact and
-inexact Newton's method applied to~\eqref{eqn:phaseRoot} in $(0,1)
-\subset \RR$ by discretizing $F'$ with a second-order finite difference
-stencil. The double-well potential is illustrated in
-Figure~\ref{fig:CA}(a), and both the exact and inexact Newton's methods
-converge to the solution in Figure~\ref{fig:CA}(b).
-Figure~\ref{fig:CA}(c) shows the norm of the residual at each Newton
+$F'(\phi^N) = -\epsilon^2 \Delta + W''(\phi^N)$ is the Fr\'{e}chet
+derivative of $F$, and $\alpha$ is the step size that will be determined
+using backtracking. This requires solving the variable coefficient PDE
+$-\epsilon^2 \Delta v + W''(\phi^{N}) v = F[\phi^N]$, which is
+challenging with an integral equation since a fundamental solution is
+not readily available. However, by choosing a double-well potential with
+$W''(\phi_0) = W''(\phi_1) = \beta$, we propose to instead use an
+inexact Newton's method where $(F')^{-1}$ is approximated with the
+solution of $-\epsilon^2 \Delta v + \beta v = F[\phi^N]$. We test the
+efficacy of the exact and inexact Newton's method applied
+to~\eqref{eqn:phaseRoot} in $(0,1) \subset \RR$ by discretizing $F'$
+with a second-order finite difference stencil. The double-well potential
+is illustrated in Figure~\ref{fig:CA}(a), and both the exact and inexact
+Newton's methods converge to the same solution. Figure~\ref{fig:CA}(b)
+shows the norm of the residual at each Newton
+\begin{wrapfigure}[18]{l}{1.8in}
+  \vspace{-7pt}
+  \centering
+  \input{figures/doublewell.tikz} 
+  \vspace{-10pt}
+  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
+  The convergence of exact and inexact Newton's methods applied
+  to~\eqref{eqn:phaseRoot}.}
+\end{wrapfigure}
 iterate when using the exact second derivative (red curve) and the

### 2022-11-15 NSF2022/Description/priorsupport.tex
yny 1115a

@@
 \noindent
-{\it Broader impacts:} 
+{\em Broader impacts:} 
 One PhD student (Szu-Pei Fu) was funded to work with PI Young, and work
@@
 \noindent
-{\it Broader impacts:} 
+{\em Broader impacts:} 
 A third-year PhD student (Jake Cherry) has been assigned to this
@@
 will conduct biweekly meetings in person, with PI Quaife joining over
-video conference from Florida. The PIs will share software packages, paper sources,
-and references on a common \textsf{Git} repository. The resulting
-software packages will be posted on the \textsf{Github} software
-repository.
+video conference from Florida. 
+%The PIs will share software packages, paper sources,
+%and references on a common \textsf{Git} repository. 
+Documents and 
+software will be managed and shared on \textsf{Github}.
 %
@@
 %
-The detailed schedule for the proposed work
-is shown in Figure~\ref{fig:schedule}. Each PI will spearhead a
-Specific Aim, and program management will happen
-throughout, with special coordination taken in quarters 4, 8, and
-12.
+The detailed schedule for the proposed work is shown in
+Figure~\ref{fig:schedule}. Each PI will spearhead a Specific Aim, and
+program management will happen throughout, with special coordination
+taken in quarters 4, 8, and 12.

### 2022-11-15 NSF2022/Description/specificaim1v2.tex
...

@@
 $\nabla_{\Sigma}\cdot{}$ is the surface divergence. From differential
-geometry, we have that $\nabla\cdot \dd = \pm 2H$ whenever $\dd$ is
+geometry, we have that $\nabla_{\Sigma} \cdot \dd = \pm 2H$ whenever $\dd$ is
 everywhere normal to $\Sigma$, and this is how curvature enters the

### 2022-11-15 NSF2022/Description/summary.tex
last few changes

@@
-\documentclass[10pt]{article}
+\documentclass[11pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \pagestyle{empty}
-\linespread{1.05}
+%\linespread{1.05}
 \begin{document}
-\section*{Summary}
+%\section*{Summary}
 
@@
 numerical simulations of collective dynamics and self-assembly arising
-from attractive interactions between dipolar/nematic particles in a
-suspension. Physicists model such a self-assembly using particles
-possessing a biphasic material label on either half, with one more
-hydrophobic than the other. Hydrophobic surfaces experience a
-non-additive long-range attraction called the hydrophobic force. This
-force is a major source of nonspecific interactions in biology and soft
-matter. Despite its ubiquity, theoretical developments explaining its
-basic underlying principles have come relatively late. Motivated by its
-broad applicability, the PIs recently developed a novel and intuitive
-mathematical model, called the hydrophobic attraction potential model,
-based on the linear response of water to surface perturbations. This
-model was used to show, for the first time, self-assembly of such
-bipolar particles into vesicle-like structures using moving domain
-elliptic partial differential equations (PDEs).
+from amphiphilic attractive interactions between finite-sized bipolar
+particles in a suspension. Experimentalists study amphiphilic
+self-assembly using particles with a biphasic
+material label.
+These amphiphilic particles experience a non-additive, long-range
+attraction that is a ubiquitous source of nonspecific interactions in
+biology and soft matter. Motivated by its broad applicability, the PIs
+recently developed a mathematical model for phase-field-mediated
+interactions between particles. This model was used to show, for the
+first time, self-assembly of bipolar particles into vesicle-like
+structures using moving domain elliptic partial differential equations
+(PDEs).
 
@@
 model to more general self-organization dynamics. They aim to generalize
-the linear-response model to a wider class of hydrophobic interactions,
-and numerically implement these interactions using integral equation
+the linear model to a wider class of hydrophobic interactions, and
+numerically implement these interactions using integral equation
 formulations. Finally, they will develop a coarse-grained model based on
-the kinetic theory to investigate the rheological properties of the
-assembly of particles with tunable hydrophobicity. The unifying aspects
-of the project will establish a platform for efficiently simulating the
+kinetic theory to investigate the rheological properties of the assembly
+of particles with tunable hydrophobicity. The unifying aspects of the
+project will establish a platform for efficiently simulating the
 collective dynamics of large numbers of particles, and focus on
@@
 
+\vspace{-0.1in}
 \subsection*{Intellectual Merit}
@@
 
+\vspace{-0.1in}
 \subsection*{Broader Impacts}
@@
 scientific computing, physics of fluids, and mathematics. The
-mathematical component incorporates leading variational techniques and
-offers insight into fundamentals of self-organization and collective
-dynamics. The project brings socially consequential research into the
-classroom and offers undergraduates the opportunity to train alongside
-faculty and graduate students. With its unique combination of
-mathematical modeling, analysis, and scientific computing, the project
-highlights the potential advancement of STEM from Applied Mathematics.
+mathematical component incorporates variational techniques and offers
+insight into fundamentals of self-organization and collective dynamics.
+The project brings socially consequential research into the classroom
+and offers undergraduates the opportunity to train alongside faculty and
+graduate students. With its unique combination of mathematical modeling,
+analysis, and scientific computing, the project highlights the potential
+advancement of STEM from Applied Mathematics.
 

### 2022-11-15 NSF2022/Description/broaderimpacts.tex

@@
     granule dynamics;
-  \item Mathematical modeling of group affiliation in social science.
+  \item Mathematical modeling of collective behavior in social sciences.
 \end{enumerate}

### 2022-11-15 NSF2022/Description/backgroundv3.tex
...
yuans and bryans changes done

@@
 bodies ``granules''. The granules are immersed in an incompressible,
-zero-Reynolds number fluid $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
+zero-Reynolds number fluid occupying the region $\Omega(t) = \RR^n \setminus \cup_{i=1}^{N_b}
 U_i(t)$ (Figure~\ref{fig:flow_map}). Throughout, $\nnu$ refers to
@@
 
-To determine how the granules move through space, we look for rigid body
+To determine how the granules move through space, we seek rigid body
 transformations
@@
 reference coordinate.
-The dynamics come from the following system of semi-linear, elliptic boundary value problems:
+The dynamics comes from the following system of semi-linear, elliptic boundary value problems:
 \begin{alignat}{4}
@@
 \label{eqn:stressbalance}
-\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
+\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif S = \mathbf{0},\quad
 \int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu
-  \,\dif s = \mathbf{0},
+  \,\dif S = \mathbf{0},
 \end{align}
@@
 equation~\eqref{eqn:phase} becomes the \emph{linear} screened Laplace
-equation. In the double-well case e.g, $W(\phi) =
-\frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$, the phase field
-equation~\eqref{eqn:phase} takes the form of an Allen-Cahn equation with
-local minima $\phi_0 < 0 < \phi_1$. Section \ref{sec:specificaim1}
-discusses certain modifications needed for~\eqref{eqn:phase} in the
-nonlinear case.
+equation. In the double-well case such as $W(\phi) =
+\frac{1}{4}(\phi^2-1)^2+b_1 x + b_2$, the phase field
+equation~\eqref{eqn:phase} takes the form of an Allen-Cahn equation,
+where $b_1$ and $b_2$ are chosen so that the local minima satisfy
+$\phi_0 < 0 < \phi_1$ and $W(\phi_0) = 0$. Section
+\ref{sec:specificaim1} discusses certain modifications needed
+for~\eqref{eqn:phase} in the nonlinear case.
 
@@
   blue, $\phi = 0$). (\emph{Middle}) Granules with $\phi = 2$ (magenta)
-  on one side and $\phi = 2$ on the other form multilamellar bilayers.
+  on one side and $\phi = 1$ on the other form multilamellar bilayers.
   (\emph{Bottom}) Bipolar granules with $\phi = 1$ (yellow) on one side
@@
 physics. The model contains a few parameters; granule radius $c$, decay
-length $\epsilon$, surface tension $\gamma$. When these are set to
+length $\epsilon$, and surface tension $\gamma$. When these are set to
 realistic values \cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian,
@@
 the long-range interactions between amphiphilic granules (such as lipid
-macromolecules) surfaces.
+macromolecules) on surfaces.
 \begin{wrapfigure}[13]{l}{0.475\textwidth}
@@
   ({\em top left}) requires meshing the entire domain (typically into
-  triangles), while a BIE ({\em top right}) requires meshing only the
-  boundary of the domain.
-  ({\em bottom}) BIE can handle intricately shaped domains as well.}
+  triangles), while an IE method ({\em top right}) requires meshing only
+  the boundary of the domain.  ({\em bottom}) An IE method can handle
+  intricately shaped domains as well.}
 \end{wrapfigure}
@@
 (PDEs)~\eqref{eqn:stokes} and~\eqref{eqn:phase} are challenging to
-develop because of the complicated and unbounded domain. This challenge
+develop because of the complex and unbounded domain. This challenge
 is compounded when dense suspensions are considered.
@@
 to~\eqref{eqn:phase} and the boundary flux transforms into viscous
-dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
-Furthermore, the integral of the phase stress vectors $T_i\nnu$ over
-$\partial \Omega$ is zero. Figure~\ref{fig:coarsening} summarizes the
+dissipation due to~\eqref{eqn:hydro_stress} and the Stokes
+equations~\eqref{eqn:stokes}.
+Furthermore, while the integral of the phase stress vector
+field $T_i\nnu$ over $\Gamma_i$ yields the force on
+each granule, the sum of these forces is zero. 
+Figure~\ref{fig:coarsening} summarizes the
 general evolution of $E$ from the self-assembly process to the
@@
   versus time $t$. Under the moving domain problem
-  \eqref{eq:RBT}--\eqref{eqn:hydro_stress} with amphiphilic boundary
+  \eqref{eq:RBT}--\eqref{eqn:stressbalance} with amphiphilic boundary
   condition, the granules self-organize into vesicle bilayers. External
@@
 \subsection{Outline of the proposal}
-The aim of this proposal is to advance the theory, simulation and
+The aim of this proposal is to advance the theory, simulation, and
 modeling for soft-matter systems and foster training in Mathematical
@@
 Section~\ref{sec:proposed-work} contains our specific aims.
+Sections~\ref{sec:prior} and~\ref{sec:manage} summarize prior support
+and project management.

### 2022-11-15 NSF2022/Description/broaderimpacts.tex
yuans and bryans changes done

@@
 To foster training in mathematical sciences, the proposal supports two
-undergraduate researchers (URs) per year at Fordham University---for
-eight summer weeks. The URs will collaborate directly with the PIs,
+summer undergraduate researchers (URs) per year at Fordham University for
+eight weeks. The URs will collaborate directly with the PIs,
 receive tutorials (e.g., numerical methods), and be guided on
@@
 PI Young has been actively involved with promotion of underrepresented
-students at NJIT. A former PhD student, Herve Nganguia, is African
-American and now an Assistant Professor at Towson University. PI Quaife
-is currently advising three female PhD students, and one is African
-American and the recipient of the McKnight Doctoral Fellowship which
-addresses the underrepresentation of African American and Hispanic
-faculty at colleges and universities in the state of Florida. PI Quaife
-will also continue to work with undergraduates and high school students
-through the Undergraduate Research Opportunity Program and Young
-Scholar's Program.
+students at New Jersey Institute of Technology. A former PhD student,
+Herve Nganguia, is African American and now an Assistant Professor at
+Towson University. PI Quaife is currently advising three female PhD
+students, and one is African American and the recipient of the McKnight
+Doctoral Fellowship which addresses the underrepresentation of African
+American and Hispanic faculty at colleges and universities in Florida.
+PI Quaife will also continue to work with undergraduates and high school
+students through the Undergraduate Research Opportunity Program and
+Young Scholar's Program at Florida State University.
 

### 2022-11-15 NSF2022/Description/specificaim1v2.tex

@@
   Granules first match hydrophobic tails (red), (b) then align
-  length-wise. (c) The same pattern of self-organization holds in three
+  lengthwise. (c) The same pattern of self-organization holds in three
   dimensions, as simulated by Kohl, Corona, and
@@
 domains. A closely related and strongly developing direction in the area
-of nematics liquid crystals concerns the interaction of Landau-de Gennes
+of nematic liquid crystals concerns the interaction of Landau-de Gennes
 functionals with colloids, and studies the qualitative structure of
@@
 \end{quotation}
-
 Sharp interface models represent a membrane vesicle as an
@@
 the deformed and equilibrium area densities respectively
-\cite{chabanon2017}.
+\cite{chabanon2017}, and $k_A$ is a stretching modulus.
 

### 2022-11-15 NSF2022/Description/specificaim2.tex

@@
 dimension reduction since $\ssigma$ is defined only on $\partial
-\Omega(t)$, and the far field boundary condition of the PDE is
+\Omega(t)$, and the far-field boundary condition of the PDE is
 automatically satisfied. The density function $\ssigma$ is chosen to
@@
 \end{quotation}
-
 In experiments, it is known that interactions between bounding walls and
@@
 \end{quotation}
-
 For a general double-well potential $W(\phi)$ with local minima at
@@
 not readily available. However, by choosing a double-well potential with
-$W''(\phi_0) = W''(\phi_1) = \beta$, we propose to instead use an
+$W''(\phi_0) = W''(\phi_1) = \beta > 0$, we propose to instead use an
 inexact Newton's method where $(F')^{-1}$ is approximated with the

### 2022-11-15 NSF2022/Description/backgroundv3.tex
...

@@
 Finally, researchers design efficient algorithms for constructing
-interaction kernels in the to study of agent-based systems like swarms
+interaction kernels to study agent-based systems like swarms
 and flocking~\cite{Lu2019NonparametricIO, Tadmor2021OnTM}.
@@
 hydrodynamic interactions. The phase field method, a prominent approach
-in this area, introduces a scalar-valued phase field function for the
+in this area, introduces a scalar-valued phase-field function for the
 volume fraction of amphiphilic lipids or polymers in solvent, for
@@
 We have departed from the terminology ``particles'', though,
-to emphasize the role played elliptic equations and the granules'
+to emphasize the role played by elliptic equations and the granules'
 finite size.
@@
 affording flexibility in terms of morphology and topology---sufficiently
-large forces will even pull groups of granules apart as physically
-required. (ii) The model formulation is built around important details
+large forces will even pull groups of granules apart as physically required.
+(ii) The model formulation is built around important details
 like molecular orientations, and exhibits inter-molecular slip that must
@@
   $W(\phi) = \tfrac{1}{2}\phi^2$. The white arrows are the fluid
-  velocity field. The panels reach an equilibrium state in panel (d).}
+  velocity field. The granules reach an equilibrium state in panel (d).}
 \end{figure}
@@
 and derived values for intermonolayer friction are in good quantitative
-agreement those derived by atomistic and Martini force field simulation
+agreement with those derived by atomistic and Martini force field simulation
 studies~\cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In

### 2022-11-15 NSF2022/Description/broaderimpacts.tex
...

@@
 and offers undergraduates the opportunity to train alongside faculty and
-graduate students. With its unique combination of mathematical modeling,
+graduate students. With its combination of mathematical modeling,
 analysis, and scientific computing, the project highlights the potential
@@
 eight weeks. The URs will collaborate directly with the PIs,
-receive tutorials (e.g., numerical methods), and be guided on
+receive tutorials (e.g., on numerical methods), and be guided on
 mathematical writing and presentation. Fordham Mathematics recently

### 2022-11-15 NSF2022/Description/specificaim1v2.tex
...

@@
 stays finite in order to guarantee positivity in the distance between
-granules.
+granules with respect to time.
 Finally, we can study the granule-flow behavior in the
@@
   \label{eqn:phase_transport}
-  \phi_t + \uu \cdot \nabla
-  = -\beta \frac{\delta E}{\delta \phi}
-  = \beta(\epsilon^2 \Delta \phi - W'(\phi)),
+  \phi_t + \uu \cdot \nabla \phi
+  = -\zeta \frac{\delta E}{\delta \phi}
+  = \zeta(\epsilon^2 \Delta \phi - W'(\phi)),
   \quad \phi(\xx,0) = \phi_0(\xx),
@@
 involving the square the Euler-Lagrange derivative $\frac{\delta
-E}{\delta \phi}$ and dampening factor $\beta > 0$. There are several
+E}{\delta \phi}$ and dampening factor $\zeta > 0$. There are several
 works dealing with the characterization of the geometric evolution of
@@
 $k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are
-the deformed and equilibrium area densities respectively
+the deformed and equilibrium area densities, respectively
 \cite{chabanon2017}, and $k_A$ is a stretching modulus.

### 2022-11-15 NSF2022/Description/specificaim2.tex
...

@@
 As an illustration, the problem of finding the global electrostatic
-potential $u$ with surface charge density $\sigma$ is a special case
+potential with surface charge density $\sigma$ is a special case
 of~\eqref{eqn:conv}, where $G(\xx - \yy)$ takes the form $-(2\pi
@@
 $\mathcal{O}(100)$ two-dimensional granules, and the proposed research
-will allow for the suspensions with 100X--1000X more two-dimensional
+will allow for the suspensions with 100--1000 times more two-dimensional
 granules and $\mathcal{O}(1000)$ three-dimensional granules.
@@
 equation~\cite{koh-cor-che-vee2021}. However, this quadrature is not
-appropriate or other shapes, and an alternative approach is necessary.
+appropriate for other shapes, and an alternative approach is necessary.
 The Barycentric-type formulae for Cauchy integrals results in a
@@
 required, for example, when computing the phase
-stress~\eqref{eqn:stressbalance}. Singularity subtraction methods can
+stress $T_i$ in equation~\eqref{eqn:hydro_stress}. Singularity subtraction methods can
 also be applied in three dimensions, but not combined with

### 2022-11-15 NSF2022/Description/specificaim2.tex
put back to 15 pages

@@
 \end{quotation}
+\begin{wrapfigure}[18]{l}{2.3in}
+  \vspace{-7pt}
+  \centering
+  \input{figures/doublewell.tikz} 
+  \vspace{-10pt}
+  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
+  The convergence of exact and inexact Newton's methods applied
+  to~\eqref{eqn:phaseRoot}.}
+\end{wrapfigure}
 For a general double-well potential $W(\phi)$ with local minima at
@@
 shows the norm of the residual at each Newton
-\begin{wrapfigure}[18]{l}{1.8in}
-  \vspace{-7pt}
-  \centering
-  \input{figures/doublewell.tikz} 
-  \vspace{-10pt}
-  \caption{\label{fig:CA} \footnotesize (a) A double-well potential. (b)
-  The convergence of exact and inexact Newton's methods applied
-  to~\eqref{eqn:phaseRoot}.}
-\end{wrapfigure}
 iterate when using the exact second derivative (red curve) and the

### 2022-11-15 NSF2022/Description/specificaim2.tex
all set: AMDG

@@
 Equation~\eqref{eqn:phaseRoot} will be solved with Newton's method,
-$\phi^{N+1} = \phi^{N} - \alpha (F'(\phi^N))^{-1} F(\phi^N)$, where
+$\phi^{N+1} = \phi^{N} - \xi (F'(\phi^N))^{-1} F(\phi^N)$, where
 $F'(\phi^N) = -\epsilon^2 \Delta + W''(\phi^N)$ is the Fr\'{e}chet
-derivative of $F$, and $\alpha$ is the step size that will be determined
+derivative of $F$, and $\xi$ is the step size that will be determined
 using backtracking. This requires solving the variable coefficient PDE

### 2023-02-12 doc/PRF2022/writeup_peter.tex
peter added parameter study

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass[11pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information

\usepackage{graphicx} % support the \includegraphics command and options

% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
\usepackage{sectsty}
\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

%%% END Article customizations

%%% The "real" document content comes below...

\title{Brief Article}
\author{The Author}
%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is printed

\begin{document}
%\maketitle

\begin{figure}[h!]
\begin{center}
  \includegraphics[height=0.3\textheight]{ChangeLengthForce.pdf}
\end{center}
\begin{caption}{\label{fig:PramChange}
  Panel (a) shows a linear relationship between change of force parameters and the critical shear rate $\dot\gamma^*$. 
  %
  Panel (b) provides numerical results of critical shear rates $\dot\gamma^*$ when the length parameters are adjusted.}
\end{caption}
\end{figure}

The rheology study has shown that the striated structure under shear and Taylor-Green flows exhibit a shear-thinning behavior.
To further quantify the contest between shear and head-tail attraction, we found that a 5\% and 10\% relative increases in the parameters $\gamma$ and
$M$ resulted in 4.29\% and 8.57\% relative increases in critial shear rate $\dot\gamma$, from 0.14 to 0.0.146 and 0.14 to 0.152, respectively. 
A proportional relationship is observed as the parameters decrease and it is shown in Figure~\ref{fig:PramChange}(a).
Moreover, Figure~\ref{fig:PramChange}(b) shows that 5\% and 10\% decreases in the particle radius c, screening length $\rho$ and repulsion distance $\rho_0$ gave 5.71\%  and 7.14\% increase in $\dot\gamma$ from 0.14 to 0.148 and 0.14 to 0.15.
In addition, 5\% and 10\% increases in length parameters gave 11.43\% and 18.57\% decrease in critical shear rate $\dot\gamma$.
The overall result provides another evidence that a different hydrophobicity suggests an unalike rheology and dynamics viscosity from the suspended vesicle experiments.

\end{document}

### 2023-02-16 doc/PRF2022/PRF_main.tex
peter added some results in discussion

@@
 
+%%%
+
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[height=0.3\textheight]{ChangeLengthForce.pdf}
+\end{center}
+\begin{caption}{\label{fig:PramChange}
+  Panel (a) shows a linear relationship between change of force parameters and the critical shear rate $\dot\gamma^*$. 
+  %
+  Panel (b) provides numerical results of critical shear rates $\dot\gamma^*$ when the length parameters are adjusted.}
+\end{caption}
+\end{figure}
+
+%The rheology study has shown that the striated structure under shear and Taylor-Green flows exhibit a shear-thinning behavior.
+To further examine the contest between shear and head-tail attraction, we found that a 5\% and 10\% relative increases in the parameters $\gamma$ and
+$M$ resulted in 4.29\% and 8.57\% relative increases in critial shear rate $\dot\gamma$, from 0.14 to 0.146 and 0.14 to 0.152, respectively. 
+A proportional relationship is observed as the parameters decrease and it is shown in Figure~\ref{fig:PramChange}(a).
+Moreover, Figure~\ref{fig:PramChange}(b) shows that 5\% and 10\% decreases in the particle radius c, screening length $\rho$ and repulsion distance $\rho_0$ gave 5.71\%  and 7.14\% increase in $\dot\gamma$ from 0.14 to 0.148 and 0.14 to 0.15.
+In addition, 5\% and 10\% increases in length parameters gave 11.43\% and 18.57\% decrease in critical shear rate $\dot\gamma$.
+The overall result provides another evidence that a different hydrophobicity suggests a dissimilar rheology and dynamics viscosity from the suspended vesicle experiments.
+
+%%%
+
 The viscosities of particle assemblies calculated from \eqref{eq:mu_asm} are shown in

### 2023-02-23 doc/PRF2022/PRF_main.tex
peter revised a figure and its caption

--- 2022-08-05 doc/PRF2022/PRF_main.tex
@@
 
+%%%
+
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[height=0.3\textheight]{ChangeLengthForce.pdf}
+\end{center}
+\begin{caption}{\label{fig:PramChange}
+When the force parameters are tuned in the same percentage change, a linear proportional relationship between changes (square symbol) and the critical shear rates $\dot\gamma^*$ is shown in numerical results.
+The same adjustment in length parameters give a nearly linear trend with an inverse proportional relationship between changes (triangle symbol) and the critical shear rates.}
+\end{caption}
+\end{figure}
+
+To further examine the contest between shear and head-tail attraction, we found that a 5\% and 10\% relative increases in the parameters $\gamma$ and
+$M$ resulted in 4.29\% and 8.57\% relative increases in critial shear rate $\dot\gamma$, from 0.14 to 0.146 and 0.14 to 0.152, respectively. 
+A proportional relationship is observed as the parameters decrease and it is shown in Figure~\ref{fig:PramChange}.
+Moreover, Figure~\ref{fig:PramChange} also shows that 5\% and 10\% decreases in the particle radius c, screening length $\rho$ and repulsion distance $\rho_0$ gave 5.71\%  and 7.14\% increase in $\dot\gamma$ from 0.14 to 0.148 and 0.14 to 0.15.
+In addition, 5\% and 10\% increases in length parameters gave 11.43\% and 18.57\% decrease in critical shear rate $\dot\gamma$.
+The overall result provides another evidence that a different hydrophobicity suggests a dissimilar rheology and dynamics viscosity from the suspended vesicle experiments.
+
+%%%
+
 The viscosities of particle assemblies calculated from \eqref{eq:mu_asm} are shown in

### 2023-02-24 doc/PRF2022/PRF_main.tex
changes

@@
 \section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
-Following the formulation in \citet{Fu2022_JFM}, 
-the governing equations are expressed as a system for the position and
-orientation of a collection of rigid Janus particles. We first pose the
+The governing equations are a system for the position and
+orientation of a collection of rigid JPs~\cite{Fu2022_JFM}.
+We first pose the
 Stokes equations for the mobility problem giving the hydrodynamic
@@
 %RJR: In the above sentence, suspection and immersed are redundant 
-The Janus particles are suspended in a viscous solvent. The particles
-are disks of radius $c$, center $\aa_i$, and orientation $\theta_i$
+The JPs are disks of radius $c$ suspended in a viscous solvent
+with center $\aa_i$, and orientation $\theta_i$
 relative to the horizontal axis, where $i = 1, \ldots, N_b$ and $N_b$ is
-the number of particles. The domain $\Omega(t) \subset \mathbb{R}^2$ is
+the number of particles. The domain $\Omega \subset \mathbb{R}^2$ is
 the solvent phase and $t$ is time. The boundary of $\Omega$ is
 $\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where $\Gamma_i$
-is the boundary of Janus particle $i$. Assuming inertial terms are
-negligible, we have 
+is the boundary of Janus particle $i$.
+The sets $\Omega$, $\Gamma_1$, \dots, and $\Gamma_{N_b}$ depend on $t$.
+Assuming inertial terms are negligible, we have the Stokes equations
 \begin{alignat}{3}
@@
 $\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
-viscosity. The solvent velocity satisfies the no-slip boundary condition
-for a rigid body motion
+solvent viscosity. The solvent velocity satisfies the no-slip boundary
+condition for a rigid body motion
 \begin{align}
@@
 
-Without inertia, $(\uu, p)$ also satisfy the force-free and torque-free
-conditions. This means that the force and torque from the hydrodynamic
-stress on each particle balance the total force and torque coming from
-the hydrophobic potential and repulsion. To compute this balance, we
-define the free energy~\cite{Ma77, GoHaKo94, Fu20, Fu2022_JFM}
+To obtain forces, define the free
+energy~\cite{Fu20, Fu2022_JFM}
 \begin{align}
@@
 \end{align}
-where $u(\xx,t)$ is as an order parameter for the structure of water,
+where $u(\xx,t)$ is as the order parameter for water\cite{Ma77, GoHaKo94},
 $\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
-
 The order parameter $u(\xx,t)$ is assumed to minimize the free energy
-$F$. Its governing equations $u(\xx,t)$ are a screened Laplace equation
+$F$ and therefore satisfies the screened Laplace equation
 boundary value problem
@@
 particle-solvent interface.
-
 The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
 \sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
-\infty$. The parameter $\rho_0$ is an ``effective" repulsion distance between
-particle surfaces, below which the steric repulsion between a pair of
-JPs becomes important. The parameter $M$ is the repulsion modulus.
-
-To calculate the force $\FF_i$ and torque $T_i$ on $\Gamma_i$ from the
-free energy~\cite{Fu20}, we compute the variation of the domain of the
-free energy~\eqref{eq:free_energy} subject
-to~\eqref{eq:SL}--\eqref{eq:SLbc}, and obtain 
+\infty$. The parameter $\rho_0$ is the distance 
+below which steric repulsion becomes important and 
+$M$ is the repulsion modulus.
+
+Letting $\nnu$ be the particle outward normal,
+the force $\FF_i$ and torque $T_i$ coming from the free energy
+acting on $\Gamma_i$ are~\cite{Fu20}
+%from the
+%free energy~\cite{Fu20}, we compute the variation of the domain of the
+%free energy~\eqref{eq:free_energy} subject
+%to~\eqref{eq:SL}--\eqref{eq:SLbc},
+%and obtain 
 \begin{align}
@@
 \end{align}
-for $i = 1,\ldots,N_b$ with particle outward normal $\nnu$.  The formulas
-in \eqref{eq:FandTdef} involve the second-order hydrophobic stress tensor
+Here,
 \begin{align}
@@
 \end{align}
-The repulsion is rotationally symmetric and
-does not contribute to the torque $T_i$.
-
-Since the force and torque from the hydrodynamic stress on each particle
-balance the total force and torque coming from the hydrophobic potential
-and repulsion, we have
+is the second-order hydrophobic stress tensor.
+Repulsion is rotationally symmetric and
+does not enter $T_i$.
+
+Without inertia, $(\uu, p)$ satisfy the force-free and torque-free
+conditions, meaning that the force and torque from the hydrodynamic
+stress on each particle balance the total force and torque coming from
+the hydrophobic potential and repulsion. We have
 \begin{equation}
@@
 
-To perform a single time step, we first solve for the HAP by
-solving~\eqref{eq:SL}--\eqref{eq:SLbc}, and then compute the force and
-torque~\eqref{eq:FandTdef}. Then the Stokes
-equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield} are solved, and
-the force-free and torque-free conditions are used to compute the rigid
-body motion~\eqref{eq:rigid-vel}.
-Once~\eqref{eq:stokes}--\eqref{eq:force} have been solved, the
-velocities $(\vv_i, \omega_i)$ from~\eqref{eq:rigid-vel} are used to update the
-particle positions and orientations.
+To perform a single time step, we
+(i) solve~\eqref{eq:SL}--\eqref{eq:SLbc} for $u$,
+(ii) compute the force and torque~\eqref{eq:FandTdef},
+and finally (iii) solve the Stokes equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield}
+subject to~\eqref{eq:rigid-vel} and \eqref{eq:force}. 
+The velocities $(\vv_i, \omega_i)$ obtained
+from~\eqref{eq:rigid-vel} are used to update the
+particle positions and orientations
+using the second-order Adams-Bashforth scheme.
+
+The interactions
+generated by the HAP-mobility problem formulation
+\eqref{eq:stokes}--\eqref{eq:force} lead to particle self-assembly.
+In terms of scaling, $\rho$ sets the effective distance of the hydrophobic
+interactions; $\rho_0$ determines the distance where attraction and repulsion are in
+balance i.e. smaller values of $\rho_0$ lead to more compact particle assemblies.
+The rate of self-assembly are proportional to tension $\gamma$,
+inversely proportional to viscosity $\mu$, and
+approximately inversely proportional to $\rho$~\cite{Fu20}.
 
@@
 \subsection{Boundary integral representations}
+It is challenging to solve the Stokes and screened Laplace equations
+and far-field boundary conditions accurately. 
 We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
@@
 \label{eq:SL_BIE}
-u({\xx}) = \DD[\sigma](\xx) = \int_\Gamma 
+u({\xx}) = \DD[\sigma](\xx) = \int_{\partial \Omega} 
   \pderiv{G(\xx-\yy)}{\nnu_\yy}\sigma(\yy)\, \dif s_\yy, 
@@
 density function. The subscript in $\dif s_\yy$ denotes integration with
-respect to $\yy \in \Gamma$. To satisfy the boundary
+respect to $\yy \in \partial \Omega$. To satisfy the boundary
 condition~\eqref{eq:SLbc}, the density function must satisfy\cite{Hsiao2008}
@@
 for $\xx \in \Gamma_i$ and $i = 1,\ldots,N_b$.
-Equation~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} does have a
-unique solution, but we note that alternative full-rank layer potential
+%Equation~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} does have a
+%unique solution, but we note that
+Alternative full-rank layer potential
 representations for rigid body motions are possible~\cite{rac-gre2016,
@@
 number of GMRES iterations is mesh-independent by using second-kind
-BIEs. Once the translational and rotational velocity are computed, the
-position and orientation of each JP is updated using the second-order
-Adams-Bashforth scheme.
+BIEs.
 
@@
 
-\section{Model parameters and boundary conditions} The interactions
-generated by the HAP-mobility problem formulation
-\eqref{eq:stokes}--\eqref{eq:force} lead to particle self-assembly for a
-broad range of parameters and boundary conditions. Generally speaking,
-the effective distance of the hydrophobic interaction is set by the
-screening length $\rho$. Smaller values of the repulsion distance
-$\rho_0$ decrease the distance where attraction and repulsion are in
-balance and lead to more compact particle assemblies. The rate of
-self-assembly is proportional to the interfacial tension $\gamma$, and
-inversely proportional to solvent viscosity $\mu$; it is roughly
-inversely proportional to screening length $\rho$ \cite{Fu20}.
-
-To give our system physical units, we set the model parameters using
-phospholipids as a characteristic amphiphile in water~\cite{Boal}. For
-the solvent viscosity, we use $\mu = 1$~mPa~s for the viscosity of water
+\section{Tunable hydrophobicity}
+The parameters are modeled after those for
+phospholipid in water~\cite{Boal}.
+We use $\mu = 1$~mPa~s for the viscosity of water
 at room temperature. Pure lipid components give a range of interfacial
 tensions $0.7$--$5.3$~pN~nm$^{-1}$~\cite{KUZMIN2005, Petelska2012,
-Jackson2016, GarciaSaez}. As in our previous
-works~\cite{Fu20,Fu2022_JFM}, we use $\gamma=4.1$~pN~nm$^{-1}$ since
-this value gave good agreement with elastic moduli of lipid bilayers.
-The particle radius $c = 1.25$~nm gives a diameter representative of
-phospholipid length~\cite{Boal}, and the screening length $\rho = 5$~nm
+  Jackson2016, GarciaSaez}.
+we use $\gamma=4.1$~pN~nm$^{-1}$ since
+this value gave good agreement with elastic moduli of lipid bilayers~\cite{Fu20,Fu2022_JFM}.
+The particle radius $c = 1.25$~nm represents one half 
+of phospholipid length~\cite{Boal}, and the screening length $\rho = 5$~nm
 derives from experimental force-distance measurements of hydrophobic
-attraction~\cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}. Based
-on empirical studies, the repulsion modulus $M = 2$~pN and repulsion
-distance $\rho_0 = 0.5$~nm give an interparticle distance around one
-particle radius. This ensures the accuracy of the boundary integral
-representations~\eqref{eq:SL_BIE} and~\eqref{eq:velocity} without having
-to employ overly aggressive mesh refinement. Altogether, the above
-parameter set gives a characteristic time $1$~ns and characteristic
-length $1$~nm.
-
+attraction~\cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}. 
+A repulsion modulus $M = 2$~pN and 
+distance $\rho_0 = 0.5$~nm gives an interparticle distance around one
+particle radius, ensuring the accuracy of the boundary integral
+representations~\eqref{eq:SL_BIE} and~\eqref{eq:velocity} without 
+overly aggressive mesh refinement. The characteristic time
+and length are $1$~ns and  $1$~nm respectively.
+
+\begin{figure}[t!]
+\begin{center}
+  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
+\end{center}
+\begin{caption}{\label{fig:boundary_conditions} The leftmost diagram
+  illustrates the particle $\Gamma_i$ with center $\aa_i$, radius $c$,
+  and director $\dd$, along with the angle $\alpha$.
+  The three rightmost panels plots show $g(\xx)$ and
+  the respective solutions $u(\xx)$ of~\eqref{eq:SL} 
+  for an isolated particle.}
+\end{caption}
+\end{figure}
 \subsection{Boundary conditions and equilibrium configurations}
@@
 \eqref{eq:SLbc} defines the spatial distribution of
-hydrophobicity and hydrophilicity.  On a hydrophobic region of the
-particle surface, representing a hydrocarbon-water interface,
-for example, $g(\xx)$ takes relatively large values.
-On an apolar, hydrophilic region, $g(\xx)$ is close to zero.
-
-In the present work, we consider boundary conditions of the form
+hydrophobicity and hydrophilicity.
+Referring to Figure \ref{fig:boundary_conditions},
 \begin{align}
@@
 where $\alpha$ is the angle between the vector $\xx - \aa_i$ and the
-particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$.  The
-parameter $a$ normalizes the boundary conditions so that
-$\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.  The motivation for this
-normalization is that the hydrophobic attraction part of the free energy
-converges to the integral of the square of the boundary data in the
-zero-screening length limit. We refer to the side of the particle where
-$\alpha = 0$ as the tail and the side where $\alpha = \pi$ as the head.
-
-\begin{figure}[h!]
-\begin{center}
-  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
-\end{center}
-\begin{caption}{\label{fig:boundary_conditions} The leftmost diagram
-  illustrates the particle $\Gamma_i$ with center $\aa_i$, radius $c$,
-  and director $\dd$, along with the angle $\alpha$ used to define
-  $g(\xx)$ in~\eqref{eq:bc-type}. The three right plots show $g(\xx)$
-  (black curve) for BC (i), (ii), and (iii) when $\dd = (1,0)$. The
-  surfaces are the respective solutions $u(\xx)$ of~\eqref{eq:SL} for a
-  single, isolated particle.}
+particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$
+The scalar $a$ normalizes $g$ so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
+The side of the particle where
+$\alpha = 0$ is called the tail and the side where $\alpha = \pi$ is the head.
+
+Based on the choice of $b$,
+the boundary condition (BC) \eqref{eq:bc-type}
+can be classified into one of three categories:
+(Type I, amphiphile, $b = 1$) $g$ is positive on 
+one side representing a hydrocarbon-water interface, and
+is zero on the other representing an apolar, hydrophilic region;
+(Type II, asymmetric hydrophobe, $b = 2$) $g$ is positive
+on both sides but greater on one side;
+(Type III, poler, $b = -1/2$) $g$ is positive on one
+side and negative on the other, representing a
+water structure with positive/negative charge~\cite{MaRa76, Ma77}.
+
+Figure~\ref{fig:relax} shows the steady state in a quiescent flow.
+Three distinct phases emerge. For Type I, amphiphiles,
+the tail interactions are attractive, and particles collectively
+form multiple domains of bilayers (Figure~\ref{fig:relax}(b)).
+We refer to this as the ``bilayer'' phase.
+
+\begin{figure}[t!]
+\begin{center}
+  \includegraphics[width=\textwidth]{Figures/Figure1and2.pdf}
+%  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
+%  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
+%  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
+%  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
+\end{center}
+\begin{caption}{\label{fig:relax}
+  Panel (a) shows the initial $N_b = 198$ particle configuration with random
+  position and orientation.
+  Panels (b), (d), (e) show bilayer, multilamellar, and striated phases
+  composed of amphiphilic (Type I), asymmetric hydrophobic (Type II),
+  and poler (Type 3) JP, respectively. 
+  Panels (c) and (f) plot the free energies~\eqref{eq:free_energy}
+  and alignment order parameter~\eqref{eq:S2} with respect
+  to $t$. The solid markers in panel (c) are 
+  normalized by $60/198$, showing that the energy
+  approximately scales with the number of particles.
+  Alignment in the striated phase is particle-number dependent; 
+  triangle markers, panel (f).}  
 \end{caption}
@@
 
-We set $\max g>0$ to guarantee at least partial hydrophobicity of the JP
-surface. Then, the boundary condition (BC) can be classified into three
-categories: $\min g(\xx) = 0$, $\min g(\xx) >0$, and $\min g(\xx) <0$
-where the extrema are taken for $\xx \in \Gamma_i$. These three
-categories correspond to three characteristic values of $b$ in
-\eqref{eq:bc-type}: $b=1$, $b=2$ and $b=0$, respectively. 
-%
-To see the effect of the shift parameter $b$, we simulate the dynamics
-of 198 particles and 60 particles in a quiescent flow as shown in
-Figure~\ref{fig:relax}. Three distinct configurations emerge: (i)
-bilayer (amphiphilic) for $b = 1$, (ii) multilamellar (biased hydrophobic) for $b = 2$, and (iii) striated (bipolar)
-for $b = 0$. Supplementary Movie S1 shows the self-assembly process for
-the three cases. In the following,
-the terms ``multilamellar" and ``biased hydrophobic"
-are used  interchangeably to refer to BC (ii), while
-``striated" and ``bipolar" are used interchangeably to refer to BC (iii).
-
-\begin{figure}[h!]
-\begin{center}
-  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
-  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
-  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
-  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
-\end{center}
-\begin{caption}{\label{fig:relax}
-  Panel (a) shows $N_b = 198$ particles confined to a square with random
-  positions and orientations and the inset shows a $N_b=60$ particles
-  configuration. The particles self-assemble into distinct
-  configurations, depending on the boundary
-  condition~\eqref{eq:bc-type}. Panel (b) is for $b=1$ and the boundary
-  condition mimics that of an amphiphilic particle giving bilayer
-  structures. Panel (c) is for $b=2$ which gives rise to a
-  multilamellar configuration. In panel (d), the case $b = 0$ is for a
-  water structure with positive/negative charge. The false color maps
-  use blue for $u < 0$, green for $u = 0$, and yellow then red for $u >
-  0$. The inset in panels (b)--(d) are configurations using $N_b=60$ and
-  share the same color map as the main panels.}
-\end{caption}
-\end{figure}
-
-Figure~\ref{fig:relax}(a) shows the initial configurations with
-orientations of the 198-particle and 60-particle cases, respectively.
-BC (i) with $b = 1$ mimics an amphiphilic particle. The boundary data
-$g$ is everywhere nonnegative, and takes the maximum value $a$ on the
-hydrophobic tail (red) the value $0$ on the hydrophilic head (green).
-The interaction is attractive, and particles collectively orient their
-hydrophobic sides to form bilayers (Figure~\ref{fig:relax}(b)). The
-inset shows the equilibrium state for the 60-particle run. Both
-$N_b = 60$ and $N_b = 198$ cases
-form bilayers with multiple domains.
-
-In BC (ii) with $b = 2$, the boundary data is everywhere positive. It
-takes the maximum value $3a$ on the tail (red) and the minimum value $a$
-on the head side (yellow). Both sides of the Janus particle are
-hydrophobic but more so on the $\alpha = 0$ side. Over a short time
-scale, these particles also self-assemble into bilayers. But unlike for
-BC (i), the heads are also hydrophobic and so in the long-time dynamics
-these bilayers form multilamella structures~\cite{C9NR05885K}. The
-number of layers depends primarily on the number of particles.
+For Type II, asymmetric hydrophobes,
+both sides of the JP are hydrophobic but more so on the tail.
+Over short times, these particles self-assemble into bilayers. But unlike for
+Type I JP, the heads are also hydrophobic and so over long times, 
+the bilayers sort into a ``multilamellar'' phase.
+The number of layers depends primarily on the number of particles.
 Figure~\ref{fig:relax}(c), for example, shows a multilamellar structure
 with four layers and one with two layers in the inset.
-
-Finally, BC (iii) with $b=0$ corresponds to a water structure with
-positive/negative charge~\cite{MaRa76, Ma77}. Here, the head repels the
-tail of other particles and the particles initially form chains with
+Onion-like dendrimersomes have previously been studied by molecular dynamics
+simulations using an 
+anisotropic pair potential~\cite{C9NR05885K,HongCacciutoLuijtenGranick2008}.
+
+Finally, Type III, bipolar JPs possess a
+head that repels the tail of neighboring particles.
+These JP initially form chains with
 their directors perpendicular to the length of the chain. The chains
@@
 alternate between layers (Figure~\ref{fig:relax}(d)).
-
-\begin{figure}
-  \begin{center}
-\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
-  \end{center}
-  \vspace{-20pt}
-  \caption{\label{fig:relax_energy}
-  Panel (a) shows that the free energy~\eqref{eq:free_energy} decreases
-  in the mobility problem formulation. The initial energies are for the
-  configuration in Figure~\ref{fig:relax}(a) and the final energies are
-  for the near-equilibrium configurations shown in
-  Figures~\ref{fig:relax}(b)--(d). The solid curves are the energies for
-  the $N_b=60$ cases and the dashed curves are the energies for the $N_b
-  = 198$ cases normalized by $60/198$, showing that the energy
-  approximately scales with the number of particles.  Panel (b) shows
-  the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs.
-  The curve styles are identical those in panel (a). The
-  near-equilibrium configurations depend on the initial configurations
-  and the results show that for both $N_b=60$ and $N_b=198$ cases,
-  bilayer and multi-lamellar configurations have similar trends in
-  orientational parameters. The results of the striated configuration,
-  however, depend on the initial geometrical setup.}
-\end{figure}
+We refer to this as the ``striated'' phase.
+
+%\begin{figure}
+%  \begin{center}
+%\includegraphics[width=1.0\textwidth]{Figures/Figure2.pdf}
+%  \end{center}
+%  \vspace{-20pt}
+%  \caption{\label{fig:relax_energy}
+%  Panel (a) shows that the free energy~\eqref{eq:free_energy} decreases
+%  in the mobility problem formulation. The initial energies are for the
+%  configuration in Figure~\ref{fig:relax}(a) and the final energies are
+%  for the near-equilibrium configurations shown in
+%  Figures~\ref{fig:relax}(b)--(d). The solid curves are the energies for
+%  the $N_b=60$ cases and the dashed curves are the energies for the $N_b
+%  = 198$ cases normalized by $60/198$, showing that the energy
+%  approximately scales with the number of particles.  Panel (b) shows
+%  the orientational parameters $\tilde{S}_2$ for all 6 relaxation runs.
+%  The curve styles are identical those in panel (a). The
+%  near-equilibrium configurations depend on the initial configurations
+%  and the results show that for both $N_b=60$ and $N_b=198$ cases,
+%  bilayer and multi-lamellar configurations have similar trends in
+%  orientational parameters. The results of the striated configuration,
+%  however, depend on the initial geometrical setup.}
+%\end{figure}
 
 \section{Measuring deformation}
-To quantify the collective hydrodynamics of JPs,
-we use the free energy $F$, a strain parameter $E$, and two scalar order
-parameters $S_{2}$ and $\tilde S_2$ to measure the deformation of
-particle configurations under background flows.
-
+To quantify the hydrodynamics of JP phases,
+we use the free energy $F$, a strain parameter $E$, and
+a scalar order parameters $S_{2}$ for alignment.
 First we simplify the form of the free energy~\eqref{eq:free_energy}.
@@
 F = -\gamma
-\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
+\int_{\partial \Omega} \rho g \nabla u \cdot \nnu \,\dif s
 + \frac{M}{2}
@@
 Here, we have substituted $g$ for $u$ since the boundary values are
-given. However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based
+given. However, evaluating $\nabla u \cdot \nnu$ on $\partial \Omega$ based
 on~\eqref{eq:SL_BIE} involves calculating a quadruple layer potential
-which has a well-known obstacle in numerical implementation.  To
-overcome this obstacle, we use
-%
-\begin{equation}
-\label{eq:normal_deriv}
-\nabla u(\xx) \cdot \nnu(\xx)=
-%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
--\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
-+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
-\end{equation}
-%
-Here, $\tt(\xx)$ is the tangent vector and $\dif/\dif s$ is the
-arclength derivative. See the Appendix in \S\ref{sec:appendix} for the
-proof and details. Substituting~\eqref{eq:normal_deriv}
-into~\eqref{eq:free_energy2} for the normal derivative leads to the
-single layer, $\SS$, which is more straightforward to evaluate and we
-compute the arclength derivative using spectrally accurate Fourier
-transform. We have validated the form of~\eqref{eq:normal_deriv} by
-extrapolating the primal energy~\eqref{eq:free_energy} along test curves
-placed slightly outside the particles.
-
-Figure~\ref{fig:relax_energy}(a) tracks the free energy profiles for all
-relaxation runs.  For the 198-particle cases, we normalized the energies
-by 60/198 and the results show that all energies decrease with good
-agreements in all boundary conditions (dashed curves).  This can be
-considered as evidence that the free energy per particle with specified
-boundary conditions is independent of the total particle number $(N_b)$.
-
-To measure positional order, we use a number, which we call the strain
+which has a well-known obstacle in numerical implementation.
+Appendix \S\ref{sec:appendix} describes
+how we overcome this obstacle.
+
+Figure~\ref{fig:relax}(c) tracks the free energy profiles for all
+relaxation runs.  In quiescent background flow, the energies are
+decreasing with respect to $t$ showing time stepping correctly
+accounts for viscous dissipation.  Furthermore, the normalized energy
+plots provide evidence that the free energy per particle with specified
+boundary condition is independent of the total particle number $(N_b)$.
+
+To measure positional order, we introduce the strain
 parameter, 
@@
 E = \frac{1}{N_b} \sum_{i=1}^{N_b}
-\left\|\frac{1}{2}(\mathsf{F}_i^T \mathsf{F}_i - I)\right\|,
+\left\|\tfrac{1}{2}(\mathsf{F}_i^T \mathsf{F}_i - I)\right\|,
 \end{equation}
-where $\mathsf{F}_i$ is an approximate deformation gradient at particle
-$i$. The argument inside the Frobenius norm $\| \cdot \|$ is the
-Green-Lagrange strain tensor. The motivation for~\eqref{eq:SP} is as
-follows. For relatively weak background flow strengths, the
-near-equilibrium particle configurations behave as an elastic solid.
-There is a map $\ff(\xx,t)$ from the reference (equilibrium)
-configuration with $\ff(\aa_i(0),t) = \aa_i(t)$ for $i = 1,\ldots,N_b$.
-Using linear approximation,
-\begin{align}
-\aa_j(t) - \aa_i(t) = \ff(\aa_j(0),t) - \ff(\aa_i(0),t)
-\approx \nabla \ff(\aa_i(0),t)(\aa_j(0) - \aa_i(0)).
-\end{align}
-To approximate the deformation gradient $\nabla \ff(\aa_i(0),t)$ we
+where $\mathsf{F}_i$ is an approximate deformation gradient
+and $\| \cdot \|$ is the Frobenius norm. 
+The Green-Lagrange strain tensor
+$\tfrac{1}{2}(\mathsf{F}_i^T \mathsf{F}_i - I)$
+measures departure of fluid deformations from a rigid
+body motion.  To define $\mathsf{F}_i$,
+we
 solve the overdetermined system 
@@
 \end{align}
-for $\mathsf{F}_i$ by weighted least squares. The weights $w_i =
+for $\mathsf{F}_i$ by weighted least squares.
+That way, if the particle positions are given by
+a map $\ff(\aa_i(0),t) = \aa_i(t)$, then
+$\mathsf{F}_i \approx \nabla \ff(\aa_i(0),t)$.
+The weights $w_i =
 \exp(-\|\aa_j(0) - \aa_i(0)\|/4c)$ with particle radius $c$ ensure that
-the linear approximation is valid for particles near $\aa_i$.
-
-Finally, we use the scalar order parameter $S_2$ to quantify the orientational order\cite{Selinger2016}:
+the linear approximation holds for particles near $\aa_i$.
+
+Finally, we use the scalar order parameter $S_2$
+to quantify the orientational order\cite{Selinger2016}:
 \begin{equation}
@@
 \end{equation}
-Here $\bar \theta$ is a circular mean defined as the orientation of the
-principal eigenvector of the matrix $\dd_1\dd_1^\top + \cdots +
-\dd_{N_b}\dd_{N_b}^\top$. Defined as such, $S_2$ is always in the range $0 \le S_2 \le 1$.
-A value $S_2 = 1$ indicates that all
-particle directors lie on a common axis e.g., two parallel vectors with
-possibly opposite direction are ordered. A value below 1 indicates imperfect order, and $S_2=0$ indicates
-complete disorder.
-
-We modify $S_2$ to account for the bilayer and multilamellar structures.
-In these cases, the directors are more or less uniformly distributed
-along a circle, even though there is orientational order between
-neighboring particles. To account for local order, we instead use
-\begin{equation}
-  \label{eq:localS2}
-\tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
-\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1),
-\end{equation}
-where $\bar \theta_i$ is the circular mean restricted to particles
-indexed by $j$ with $\|\aa_i - \aa_j\| < 4c$.
+Here $\bar \theta_i$ is a circular mean defined as the orientation of the
+principal eigenvector of the matrix
+$\sum_{j} \dd_j\dd_j^\top$ where $j$ runs over the particles
+whose centers lie with $4c$ of that of particle $i$. 
+Defined as such, $S_2$ lies in the range $-1/2 \le S_2 \le 1$.
+with a value $S_2 = 1$ indicates perfect alignment between particles
+while $S_2=-1/2$ indicates isotropic alignment locally.
 This cutoff distance was chosen empirically
@@
 but excludes next nearest neighbors.
-In practice, if a particle
-is isolated and has no neighbors within a distance $4c$, then we exclude
-it from the sum~\eqref{eq:localS2}.
-
-Figure~\ref{fig:relax_energy}(b) tracks the orientational order
-parameter $\tilde{S}_2$. Both bilayer and multilamellar structures show
-similar trends in the small and large particle number systems
-(Figure~\ref{fig:relax_energy}(b) black curves and red curves,
-respectively). The multilamellar structures are highly ordered in all
-cases (Figure~\ref{fig:relax}(c)) whereas the bilayer structures are
-disordered because they consist of several components forming isolated
+
+In Figure~\ref{fig:relax}(f), the multilamellar phase is highly ordered 
+whereas the bilayer phase is somewhat
+disordered because it consists of several components forming isolated
 bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
 
-The aggregation for striated configurations forms more than one pattern
-when the number of particles is varied (Figure~\ref{fig:relax}(d)). We
-observe that when the number of particles is fewer, there is only a
+The striated phase order admits more than one pattern
+depending on the number of particles (Figure~\ref{fig:relax}(f), bottom and top curves).
+When the number of particles is fewer, there is only a
 single pattern in particle orientations where the directors are more or
-less parallel and alternate directions (Figure~\ref{fig:relax}(d),
-inset). Larger number of particles results in two different patterns:
+less parallel and alternate directions (Figure~\ref{fig:relax}(e),
+inset). Larger number of particles results in multiple alignment patterns:
 the alternating sign pattern as in the small particle number case
-(Figure~\ref{fig:relax}(d), top right rectangle) and one where the
-directors reflect across the lines parallel to the stria and across the
-lines perpendicular to the stria (Figure~\ref{fig:relax}(d), top middle
-rectangle). As a result, there are different trends in orientational
-order (Figure~\ref{fig:relax_energy}(b), solid and dashed blue curves,
-respectively).
-
-In the Results section, the equilibrium configurations for BCs (i),
-(ii), and (iii) (Figure~\ref{fig:relax}, insets) are used as initial
-data in the background flow simulations. For the bilayer case BC (i),
-we include an alternate initial condition consisting of a single,
-circular vesicle (c.f., Figure~\ref{fig:Ves_shear}).
+(Figure~\ref{fig:relax}(e), top right rectangle) and an 'X'-shaped
+alignment (Figure~\ref{fig:relax}(e), top left rectangle).
 
@@
 \label{sec:appendix}
-Our calculation of the free energy $F$ relied on converting the body
-integral in~\eqref{eq:free_energy} into the surface integral
-in~\eqref{eq:free_energy2} involving only single layer potentials and
-tangential derivatives. This section supplies a proof of
-identity~\eqref{eq:normal_deriv} used in this conversion.  Let 
+The boundary integral calculation
+of \ref{eq:free_energy2} relies
+on the following identiy 
+%
+\begin{equation}
+\label{eq:normal_deriv}
+\nabla u(\xx) \cdot \nnu(\xx)=
+%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
+-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
++ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \partial \Omega.
+\end{equation}
+%
+Here, $\tt(\xx)$ is the tangent vector and $\dif/\dif s$ is the
+arclength derivative.
+Substituting~\eqref{eq:normal_deriv}
+into~\eqref{eq:free_energy2} for the normal derivative leads to the
+single layer, $\SS$, which is more straightforward to evaluate.
+The arclength derivative is computed using
+the spectrally accurate Fourier transform.
+
+To prove ~\eqref{eq:normal_deriv}, let
 \begin{equation}

### 2023-02-24 doc/PRF2022/PRF_main.tex
edits

@@
 particle positions and orientations
-using the second-order Adams-Bashforth scheme.
+using the second-order Adams-Bashforth scheme
+with time step size $\Delta t.$
 
@@
 the tail interactions are attractive, and particles collectively
-form multiple domains of bilayers (Figure~\ref{fig:relax}(b)).
+form disjoint bilayer components (Figure~\ref{fig:relax}(b)).
 We refer to this as the ``bilayer'' phase.

### 2023-03-10 doc/PRF2022/PRF_main.tex
new figs
Results and SM updated

@@
-%% ****** Start of file apstemplate.tex ****** %
+%% ***A*** Start of file apstemplate.tex ****** %
 %%
@@
 \usepackage{tabularx}
+\usepackage{color,soul}
 \newtheorem{lemma}{Lemma}
@@
 \newcommand{\JJ}{\mathbf{J}}
+\newcommand{\kk}{\mathbf{k}}
 \newcommand{\nnu}{\boldsymbol{\nu}}
@@
 \newcommand{\jump}[1]{[\![ #1 ]\!]}
+\newcommand{\kbt}{\mathrm{k}_{\text{B}}\mathrm{T}}
+\newcommand{\KBT}{k$_{\text{B}}$T}
+\newcommand{\kb}{\kappa_{\text{B}}}
+\newcommand{\ka}{\kappa_{\text{A}}}
 
@@
 between a pair of JPs is affected by the presence of other particles.
+
+\hl{Qi Wang has a preprint "A hybrid phase field method for fluid-structure interactions in viscous fluids"}.
 
@@
 \section{Tunable hydrophobicity}
+\label{sec:tunable_hydrophobicity}
 The parameters are modeled after those for
@@
 
-\begin{figure}
+\section{Results and Discussion}
+\label{sec:results}
+\begin{figure}[t]
 \begin{center}
-   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
+\includegraphics[width=\textwidth]{S2ESummary.pdf}
 \end{center}
-  \caption{
-    \label{fig:BC1_shear}
-    Panels (a)--(c) are a snapshot at $t=0.5\ \upmu$s of the
-    multiple-component bilayer with shear rate $\dot \gamma = \{0.05,
-    0.075, 0.1\}$. The initial configuration is shown in inset of panel
-    (a). The streamlines are plotted in the background. Panel (d) shows
-    the free energies, panel (e) shows the orientational parameter
-    $\tilde{S}_2$, and panel (f) shows positional parameter E.}
+\caption{\label{fig:s2esummary}asdf}
 \end{figure}
-
-\section{Results}
-\label{sec:results}
-In this section, we subject the JP structures to various
-background flows. The purpose is to understand how the self-assemblies
-respond to external forcing. We then compare effective
-properties of materials comprised of JPs as a function of
-their amphiphilic properties.
-%%%
-
-\subsection{Bilayer configurations (BC (i)) in a linear shear flow}
-To begin, we place the bilayer structure (with BC (i)) from the inset of
-Figure~\ref{fig:relax}(b) in a linear shear flow
+We subjected the Type I, II, and III JP phases to background flows and measured 
+their material response.  The background flows were a shear flow
 \begin{equation}
-\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y \cdot \mathbf{x}) {\bf e}_x,
+\label{eq:sh_flow}
+\uu_\infty^{\text{sh}}(\xx) = 
+\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
 \end{equation}
-%
-where $\dot\gamma$ is the dimensionless shear rate, and ${\ee}_x$ and
-${\ee}_y$ are horizontal and vertical unit vectors, respectively. The
-initial bilayer structure consists of a small self-enclosing bilayer
-(vesicle) and several pieces of bilayers.
-Figure~\ref{fig:BC1_shear}(a)--(c) shows a snapshot at $t = 0.5$
-$\upmu$s of the bilayer for different shear rates $\dot\gamma=
-0.05,0.075,0.01$. The dynamics of the bilayer can be found in
-Supplementary Movie S2, which shows
-that the initial pieces of bilayers
-merge and form a worm-like shape under a linear shear flow. At a low
-shear rate, the bilayer constantly goes through rotation and extensional
-deformation with the whole bilayer remaining intact
-(Figure~\ref{fig:BC1_shear}(a)). As the shear rate increases to a
-moderate value (Figure~\ref{fig:BC1_shear}(b)), the bilayer is observed
-to shed a small piece of bilayer, similar to the asymmetric breakup of a
-viscous drop in confinement \cite{DuFuZhuMaLi2016_AICHEJ}.
-%\todo[inline]{missing citation}. 
-In Figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two
-separate, nearly equal bilayers, similar to the symmetric drop breakup
-under a linear shear flow \cite{Stone1994_ARFM}. For the dynamic evolution, see
-Supplementary Movie S4.
-
-%\todo[inline]{missing citation}.
-%%
-%\begin{figure}
-%  \begin{center}
-%    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
-%  \end{center}
-%  \vspace{-20pt}  
-%  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
-% The streamlines are plotted in the background. 
-%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
-%  }
-%\end{figure}
-
-We observe that the order parameter $\tilde S_2$ in
-Figure~\ref{fig:BC1_shear}(e) is on average increasing. In the initial
-configuration, the structure has three or four pieces of bilayer.
-%
-Under the shear flow, the shedding and merging of bilayers results in an
-overall decrease in distinct bilayer structures. Similarly, the free
-energies are slightly decreasing (Figure~\ref{fig:BC1_shear}(d)), with
-the overall changes occurring in the range of a few $\mathrm{k_BT}$/nm.
-This suggests that the shear flow changes the energy landscape to move
-the local equilibrium obtained from a random initial condition to an
-alternate local equilibrium with less free energy and greater
-orientational order  (Supplementary Movie S2).  Note that the free energy $F$ in
-Figure~\ref{fig:BC1_shear}(d) has the unit of force ($\mathrm{k_BT}$/nm $\approx$ 4.114 pN)
-because our system
-is two dimensional.
-%
-%\begin{figure}
-%  \begin{center}
-%    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
-%  \end{center}
-%\caption{\label{fig:ves_TG} Single vesicle in a TG flow.
-Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a).
-The streamlines are plotted in the background.
-%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
-%}
-%\end{figure}
-%
-Finally, the strain parameter diverges in the large shear rate cases
-(Figure~\ref{fig:BC1_shear}(f))
-because the various pieces of bilayer eventually completely separate and move away from one another
-under the shear flow.
-
-%%%
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
-  \end{center}
-  \caption{
-    \label{fig:Ves_shear}
-A single vesicle in a shear flow. Panels (a)--(c) are snapshots for
-  $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \upmu$s where the
-  pre-relaxed initial configuration is shown in inset of panel (a). The
-  streamlines are plotted in the background. Panel (d) shows the free
-  energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel
-  (f) shows positional parameter E.}
-\end{figure}
-\citet{Fu2022_JFM} studied the hydrodynamics of a JP vesicle under a
-linear shear flow. Focusing on drawing analogies to hydrodynamics of a
-vesicle in continuum modeling (such as
-tank-treading~\cite{keller_skalak_1982,Finken08,Shaqfeh11}, bilayer
-slip~\cite{sch-vla-mik2010,denOtter2007,Zgorski2019}, and
-permeability~\cite{chabanon2017, qua-gan-you2021}), our previous work
-demonstrated the existence of a critical shear rate above which the JP vesicle
-ruptures~\cite{grandmaison_brancherie_salsac_2021,D2SM00179A}. Based on
-the these early results, we reinitialized the BC (i) configuration in
-the form of a single, circular vesicle (rather than several bilayer
-components) and illustrate how the three measures of structural
-deformation correlate to the dynamics of a JP vesicle.
-
-At shear rates $\dot\gamma=0.05, 0.066, 0.075$, the vesicle undergoes
-familiar hydrodynamics, such as elongation along the extensional axis
-and tank-treading motion, as shown in
-Figure~\ref{fig:Ves_shear}(a)--(c)
-and Supplementary Movie S2.
-%
-The circular shape is also a local equilibrium, with somewhat less
-energy than the disordered state c.f., Figure~\ref{fig:BC1_shear}(d) and
-Figure~\ref{fig:Ves_shear}(d). But unlike the dynamics of bilayers in
-Figure~\ref{fig:BC1_shear}, the energies of the JP vesicle in
-Figure~\ref{fig:Ves_shear}(d) jump from the baseline value 30
-$\mathrm{k_BT}$/nm to about 32 $\mathrm{k_BT}$/nm, signaling the rupture
-of the vesicle into disconnected bilayers (see
-Figure~\ref{fig:Ves_shear}(d), long and short dashed curves).  After the
-rupture, each piece circles around the vorticity at the center without
-reconnection while the energies fluctuate slightly around a constant.
-
-For the lowest shear rate case, the vesicle has nearly constant
-orientational order $\tilde S_2 = 1$ (see Figure~\ref{fig:Ves_shear}(e),
-solid curve). After the JP vesicle ruptures with $\dot\gamma= 0.066$ and
-$\dot \gamma= 0.075$, we observe a greater variation in the order
-parameter $\tilde{S}_2$ with a baseline value around $0.7$ (see
-Figure~\ref{fig:Ves_shear}(e), dashed curves). The oscillations occur
-due to the orbit of the two bilayer components, and $\tilde{S}_2$
-increases to about $0.9$ when the components slide past one another and
-are nearly parallel.
-%
-As in the previous case, peaks in the strain parameter $E$ correlate
-well with changes in structural topology in the bilayer dynamics (dashed
-curves in Figure~\ref{fig:Ves_shear}(f)).
-
-%%%%%%%
-%
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:BC1_TG} Bilayers with multiple domains in a
-  Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \upmu$s. The
-  pre-relaxed initial configuration is shown in the inset of panel (a).
-  The streamlines are plotted in the background. Panel (d) shows the
-  free energies; panel (e) shows the orientational parameter
-  $\tilde{S}_2$; panel (f) shows the positional parameter $E$.}
-\end{figure}
-%
-\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
-Next, we subject the JP structures to a steady Taylor-Green (TG) background
-flow
+and a Taylor-Green (TG) flow
 \begin{equation}
 \label{eq:tg_flow}
-\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
-\left(
--\cos\left(x/\lambda\right)
- \sin\left(y/\lambda\right)
-         {\bf e}_x
-         +\sin\left(x/\lambda\right)
-         \cos\left(y/\lambda\right)
-             {\bf e}_y\right),
+\uu_\infty^{\text{TG}}(\xx) = 
+\lambda \dot \gamma \left(
+-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
++\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
 \end{equation}
-where $x = {\bf e}_x \cdot \xx$ and $y = {\bf e}_y \cdot \xx$
-are the horizontal and vertical coordinates, respectively. 
-The TG flow is a confining flow consisting of a checkerboard pattern
-of cells with alternating circulation. We control the flow by the
-dimensionless flow strength $V_0$ and the dimensionless cell size $l$
-defining $\lambda = l$ nm. For most of the results in this subsection,
-we use the parameter $l=2$.
-%
-
-\begin{figure}
+where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal
+and vertical directions, respectively. 
+In both cases, $\dot \gamma$ is the shear rate.
+To obtain a range for $\dot \gamma$, 
+consider the capillary number 
+\begin{equation}
+\label{eq:capillary}
+C_a = \frac{\mu \dot \gamma R^3}{\kappa}
+\end{equation}
+where $R = 10$ nm and $\kappa = 20\;\kbt$ are 
+the characteristic phase sample radius 
+and bending rigidity, respectively. 
+That is, $\kappa$ gives the elastic stress 
+for restoring the phase-sample shape.
+Shear stress overcomes elastic stress   
+when $C_a > 1$ and this yields 
+$\dot \gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$ s.
+Thus our values for $\dot \gamma$ range between 
+$0$ ns$^{-1}$ corresponding to quiescent flow
+up to $0.2$ ns$^{-1}$ capable of rupturing the sample. 
+Such shear rates are compatible with molecular dynamics 
+simulation \cite{Bradner}, those for large unilamellar vesicles (LUV),
+\cite{Bernard2005ShearinducedPA} and shearing in blood capillary vessels 
+ where shear rates range over 100--1000 s$^{-1}$ \cite{NEEDED}.
+
+The shear flow replicates the motion of a fluid between two parallel, moving plates
+excluding wall effects.  In TG flow, the flow pattern
+consists of an array of counter rotating cells each with size 
+$2\pi \lambda \times 2\pi \lambda$.  Throughout, we use $\lambda = 2$ nm
+so that the JP phases occupy about nine cells.  To compare shear
+on equal terms, the flow rate $\lambda \dot \gamma$  
+was chosen for \eqref{eq:tg_flow} so that it has has the same
+rate viscous dissipation per area as for \eqref{eq:sh_flow}.
+In other words, 
+$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ 
+is the same for 
+$\uu = \uu_{\infty}^{\text{sh}}$ as for 
+$\uu = \uu_{\infty}^{\text{TG}}$
+when integrated over a common cell $A$.
+
+For initial data, the steady-state Type I amphiphiles phase
+consisted of a number of disjoint bilayer components
+(Figure \ref{fig:relax}(b)). To also have a single-component Type I phase, 
+we reinitialized the data to have a ring-shaped vesicle bilayer.
+This phase is distinguished from "bilayer" by "vesicle BL" in the figures.
+For the same number of JP, the vesicle bilayer
+has lower free  steady-state energy ($F = 24.6 \;\kbt$ nm$^{-1}$) than the 
+disordered bilayer phase ($F = 24.6 \;\kbt$ nm$^{-1}$). 
+Since the simulations are for two dimensions,
+multiplying $F$ by a length gives the energy 
+of a transversely invariant, three-dimensional 
+phase.
+
+Figure \ref{fig:s2esummary} (e)--(l) show the typical streamlines
+for JP phases in background flow.  Although the plots only show
+the region near the JP phases, the fluid velocity $\uu$ and 
+order parameter $u$ are solved for in all of $\mathbb{R}^2$.
+Moreover, $\uu$ satisfies the rigid boundary condition at 
+every JP-fluid interface i.e., the particles interact with local
+flow field and are not merely carried by background flow.
+
+The simulation setup consisted of placing each of the three JP phases
+in either a shear or TG background flow and then solving for the 
+particle trajectories in time.  A total of $500$ steps were solved
+for with $\Delta t = 2$ ns, yielding time courses for various 
+$\dot \gamma$ up to $T = 1$ $\upmu$s.  We then post-processed the trajectories
+to infer free energy $F$, alignment order $S_2$, and strain $E$.
+
+\subsection{Strain and alignment}
+The plots reveal highly distinct material responses from each phase.
+Figure \ref{fig:s2esummary} (a) and (b) show the time-averaged
+strain $\frac{1}{T}\int_0^T E \,\dif t$ over a broad
+range of shear rates.  Strain $E$
+measures the non-rigid-body deformation relative to the initial state
+and expectedly increases with shear rate.
+The greatest increase occurs with the Type I amphiphiles, 
+suggesting that this phase has the lowest elastic modulus. In comparison, 
+the  striated phase consisting of  Type III polar JP is
+basically rigid.
+
+Figure \ref{fig:s2esummary} (c) and (d) plot the time-averaged
+alignment order $S_2$. The vesicle and striated phases possess
+the greatest alignment order and, 
+for the most part, $S_2$ decreases with increases in shear rate.
+But there is an exception.  The Type I bilayer phase alignment
+order actually increases under both shear and TG flows (solid squares).  
+This suggests that 
+the mixing action of background flow has the effect of moving the
+disordered bilayer phase out of a local equilibrium and into a state
+with greater order.
+This surprising increase, 
+brought about by combining previously broken bilayer 
+end caps, is accompanied
+by a slight decrease in free energy (Figure \ref{fig:fsummary}a, solid squares).
+
+The sudden jumps in  Figure \ref{fig:s2esummary} (a) and (b)
+and commensurate drops in panels (c) and (d) indicate
+the existence of a critical shear rate $\gamma_*$.  This means that 
+for $\gamma < \gamma_*$, the JP phase remains intact while
+for $\gamma > \gamma_*$, the phase ruptures. 
+For example, the vesicles phase has 
+$\gamma_* = 0.05$ ns$^{-1}$ 
+under shear flow and TG flow. However, the critical shear rate
+is flow-pattern dependent because 
+the striated phase has $\gamma_* = 0.14$ ns$^{-1}$ under shear flow
+while $\gamma_* = 0.05$ ns$^{-1}$ under  TG flow.
+Due to variable stress distribution, 
+the critical shear rate in TG likely 
+depends on the cell size parameter $\lambda$.
+The disordered bilayer phase does not really possess a critical
+shear rate because it already consists of several, disjoint components.
+The jump in Figure \ref{fig:s2esummary} (a) (solid squares)
+simply corresponds to disjoint components drifting apart in the shear
+flow.  The Type II multilamellar phase did
+not rupture for any of the shear rates considered.
+
+\begin{figure}[t]
 \begin{center}
-    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
+\includegraphics[width=\textwidth]{FSummary.pdf}
 \end{center}
-\caption{\label{fig:ves_TG} A single vesicle in a TG flow. Panels
-  (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \upmu$s
-  where the pre-relaxed initial configuration is shown in inset of panel
-  (a). The streamlines are plotted in the background. Panel (d) shows
-  the free energies; panel (e) shows orientational parameter
-  $\tilde{S}_2$; panel (f) shows positional parameter E.}
+\caption{\label{fig:fsummary}}
 \end{figure}
 
-There is no appreciable pattern in the deformation for the
-case of bilayers with multiple pieces of bilayer in TG flow
-(Supplementary Movie S3, right panel).
-Figure~\ref{fig:BC1_TG}(a)--(c)
-are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s. At all
-flow strengths, the bilayer pieces are separated and mixed by the
-flow in neighboring cells. In the $V_0 = 0.2$ case, the flow breaks off
-bilayers consisting of only a few particles, leading an increase in
-energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve). There is no
-apparent structure to the change in the orientational order. There is an initial
-increase in the strain parameter due to merging and rupture of bilayers, but the
-strains remains bounded since the particles stay confined to the
-neighbors of the central cell.
-
-Patterns in the deformation, however, do emerge in the case of a vesicle
-in TG flow (Supplementary Movie S3, left panel). For a vesicle in a Taylor-Green flow,
-Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\ \upmu$s
-where $V_0=0.1,0.15,0.2$. Here, the circular vesicle takes on a steady
-square shape for moderate flow rates $V_0 = 0.1$ and $V_0 = 0.15$. In
-these cases, there is little change in the vesicle free energy and order
-(Figure~\ref{fig:ves_TG}(d)--(f)). The vesicle disintegrates for $V_0 =
-0.2$ (Supplementary Movie S5, left panel), leading to a jump in energy, drop in order, and increase in
-strain, suggesting that the vesicle has a critical TG flow strength in
-the interval $0.15 < V_0 <  0.2$ separating the intact and ruptured
-end-states.
-
-\begin{figure}
+\subsection{Free energy}
+Figure \ref{fig:fsummary} plots the time-averaged
+relative free energy $\frac{1}{T}\int_0^T F - F_0 \,\dif t$ where $F_0$ is 
+\eqref{eq:free_energy2} at $t = 0$.  The 
+greatest increase occurs with the Type II 
+multilamellar phase, with the other phases 
+showing a moderate change in a few \KBT\;per 
+nm.
+
+Figure \ref{fig:fsummary} (c) plots free energy 
+against $x = c E$ representing the mean  
+inter-particle displacement;    
+zero displacement corresponds
+to an inter-particle distance where 
+repulsion and attraction are in balance;
+$c = 1.25$ nm is particle radius.
+The energies in Figure \ref{fig:fsummary} (c) are essentially  
+quadratic in $x$ suggesting that the interactions 
+are harmonic locally around equilibrium.
+The harmonic bond strength is strongest between 
+polar JP, and greater by a factor of two and five than
+that for asymmetric hydrophobes and amphiphiles,
+respectively.  This makes sense when considering 
+that the free energy of the steady-state striated
+phase is also greatest (Figure \ref{fig:relax} (c), around 85 \KBT\;nm$^{-1}$).
+However, the bond strength in the multilamellar 
+phase comes in second, despite having least steady-state free energy
+(around 15 \KBT\;nm$^{-1}$).
+The data point to the fact that the binding properties 
+do not merely scale with free energy, 
+but also involve the details of the interface's
+hydrophobicity 
+which are tuned by \ref{eq:bc-type} in our model.
+
+\begin{figure}[t]
 \begin{center}
-\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
+\includegraphics[width=\textwidth]{RheologySummary.pdf}
 \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)--(d) show
-  the configurations with streamlines of a vesicle is in a TG flow at
+\caption{\label{fig:rheologysummary}}
+\end{figure}
+\subsection{Rheology}
+So far, we have considered static material properties, namely
+constant strains maintained by an external force provided by   
+background flow. Now we consider dynamic material properties.
+Specifically, we look at the strain rate 
+\begin{equation}
+\label{eq:strainrate}
+\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
+\end{equation}
+The reason for defining $\dot E$ in this was is that 
+the shear flow $\uu_{\infty}^{\text{sh}}$
+simulations correspond to a complex fluid within a drag plate
+rheometer where the shear stress is set by $\mu \dot\gamma$  
+and the observed, sample shear rate is $\dot E$. 
+The definitions carry over to the TG flow case directly. 
+Also, as a practical consideration,
+the rotation of non-isotropic JP phases in the background 
+flow leads to oscillation in the strain time courses 
+making systematic fitting challenging (see 
+Supplementary Material Figures \ref{fig:veshraw}--\ref{fig:sttgraw}). 
+The integral in \eqref{eq:strainrate} averages out these oscillations
+and gives physically meaningful values.
+
+The shear stress--strain rate data are 
+excellently fit by power laws.  
+Figures \ref{fig:rheologysummary} (a), (b), and (c)
+show the data for Type I, Type II and Type III JPs, respectively,
+under both shear flow (squares) and TG flow (triangles).
+The bilayer phases consisting of Type I JPs are basically Newtonian
+with viscosity $0.014$ MPa\;ns $= 14$ mPa\;s,
+about 14 times the the viscosity of water at room temperature
+(Figures \ref{fig:rheologysummary}(a), dashed curve). 
+The vesicle bilayer phase is slightly shear thickening
+(Figures \ref{fig:rheologysummary}(a), solid curve).
+The multilamellar phase consisting of Type II JPs
+is somewhat shear thinning,  but its viscosity 
+is larger than for Type I.  Finally, the striated
+phase is strongly shear-thinning.  This 
+further explains the rigid-like behavior of the 
+striated phase found in the strain, shear-rate relationships from 
+Figure \ref{fig:s2esummary}(a), (b) (triangles).
+
+\begin{figure}[t]
+\begin{center}
+  \includegraphics[width=\textwidth]{critical_shear_and_cell_size.pdf}
+\end{center}
+\caption{\label{fig:PramChange}
+In panel (a), relative change in $\dot \gamma_*$ is linear 
+in the relative change of tension with slope $1$.
+Conversely, relative change in $\dot \gamma_*$ 
+has slope $-2$ with respect to relative change in tension.
+Panels (b)--(e) show the tank-treading configuration 
+of a vesicle bilayer the configurations with streamlines of a vesicle is in a TG flow at
 $t=1$ $\upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the
   relative enclosed area $A/A_0$ calculated from the bilayer midplane
-  decreases over time. The inset shows the relative length $l/l_0$ which
+  decreases over time. The inset shows the relative length $L/L_0$ which
   remains nearly constant with small magnitude of oscillations. The
@@
 
-The vesicle shape is also related to the cell size $l$.
-Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in
-a TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s. For the smallest cell
-size $l = 1$ tested, the vesicle is somewhat octagonal and passes
-through multiple cells (Figure~\ref{fig:BTG_Scale}(a)). For the largest
-cell size $l = 4$, the vesicle is rhomboid and surrounds a single cell.
-
-In all cases, the JP vesicle tank-treads in TG flow as it does
-in the shear flow. The
-direction of the tank-treading, however, varies with the cell size
-(Figure~\ref{fig:BTG_Scale}(a)--(d), directed arcs). We attribute this
-change in rotational orientation to the total rotational moment of the
-cells that the vesicle passes through.
-
-We calculate the vesicle area $A$ and length $L$ (initial area $A_0$,
-initial length $L_0$) by averaging the area and length of the inner and
-outer leaflets. As shown in Figure~\ref{fig:BTG_Scale}(e), the relative
-area $A/A_0$ decreases during the simulations, with the rate depending
-nonmonotonically on $l$. The relative length $L/L_0$, however, is
-constant in $t$ for all cell sizes (Figure~\ref{fig:BTG_Scale}(e),
-inset). This implies that the vesicle behaves as an inextensible,
-permeable membrane. In previous work, \citet{Fu2022_JFM} determined the
-permeability constant of particle-based vesicles in the context of shear
-background flow~\cite{chabanon2017, qua-gan-you2021}.
-
-%%%
-\begin{figure}
-  \begin{center}
-\includegraphics[width=1.0\textwidth]{Figures/Figure8.pdf}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:BC2_shear} A multilamellar structure in a shear
-  flow. Panels (a)--(c) are snapshots for $\dot \gamma = \{0.05, 0.1,
-  0.15\}$ at $t=0.6\ \upmu$s where the pre-relaxed initial configuration
-  is shown in inset of panel (a). The streamlines are plotted in the
-  background. Panel (d) shows the free energies; panel (e) shows
-  orientational parameter $\tilde{S}_2$; panel (f) shows positional
-  parameter E.}
-\end{figure}
-
-\subsection{Multilamellar and striated configurations in shear and TG flow}
-We have simulated particles for the multilamellar (BC (ii)) and striated
-(BC (iii)) boundary conditions, in both shear and TG background flow.
-The results are qualitatively similar and will be presented in tandem.
-For the multilamellar (BC (ii)) case, we place a 60-particle configuration (inset
-of Figure~\ref{fig:BC2_shear}(a)) in shear flow with $\dot\gamma=0.05,
-0.1, 0.15$ and in TG flow with $V_0=0.1, 0.15, 0.2$. For the
-striated  (BC (iii)) case, we also place a 60-particle configuration (inset of
-Figure~\ref{fig:BC3_shear}(a)) in shear and TG background flows. Here,
-somewhat larger rates are required to see appreciable deformations for
-this boundary condition: $\dot\gamma=0.1, 0.125, 0.15$ and $V_0=0.2,
-0.25, 0.3$, respectively.
-The BC (ii) and BC (iii) in shear flow cases are visualized in
-the latter half of 
-Supplementary Movie S2 (low shear rate) and 
-Supplementary Movie S4 (high shear rate), respectively.
-The low and high flow rates for TG flow are shown in
-the latter half of
-Supplementary Movie S3 and 
-Supplementary Movie S5, respectively.
-
-In terms of shear flow, the free energies are steady at the lowest shear
-rates (Figure~\ref{fig:BC2_shear}(d), Figure~\ref{fig:BC3_shear}(d)).
-The free energy of the striated configuration oscillates by $\pm 1$
-$\mathrm{k_BT}$/nm due to a square reference region deforming into a
-rhomboidal shape under shear flow (Figure~\ref{fig:BC3_shear}(d), solid
-curve). No such oscillation is present for the multilamellar
-configuration since this shape is circularly isotropic
-(Figure~\ref{fig:BC2_shear}(d), solid curve). At the lowest shear rates,
-there is, however, oscillation in the strains of both configurations,
-while the order parameter $\tilde S_2$ is nearly constant
-(Figure~\ref{fig:BC2_shear}(e),(f), Figure~\ref{fig:BC3_shear}(e),(f),
-solid curves). In summary, both multilamellar and striated
-configurations behave as nearly rigid bodies under shear flow when the
-shear rate $\dot \gamma$ is low.
-
-In the high shear rate cases ($\dot\gamma=0.15$), both the multilamellar (BC (ii))
-and striated (BC (iii)) configurations become disordered. For BC (ii), the lamella
-break apart so that individual bilayers are no longer discernible
-(Figure~\ref{fig:BC2_shear}(c)). For BC (iii), the stria peel away from
-the main body, but remain individually intact
-(Figure~\ref{fig:BC3_shear}(c)). Overall, the particles in BC (ii) and
-BC (iii) remain bounded and do not drift away in the shear background
-flow like for the BC (i) (Figure~\ref{fig:BC1_shear}(c),
-Figure~\ref{fig:Ves_shear}(c)).
-
-\begin{figure}
-  \begin{center}
-\includegraphics[width=1.0\textwidth]{Figures/Figure9.pdf} 
-  \end{center}
-  \vspace{-20pt}
-  \caption{\label{fig:BC2_TG} A multilamellar structure in a
-  Taylor-Green flow. Panels (a)-(c) are snapshots for $V_0 = \{0.1,
-  0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial
-  configuration is shown in inset of panel (a). The streamlines are
-  plotted in the background. Panel (d) shows the free energies; panel
-  (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows
-  positional parameter E.}
-\end{figure}
-
-Under a TG background flow, the free energy $F$ is also basically
-constant for the lowest flow rates $V_0$ (Figure~\ref{fig:BC2_TG}(d),
-Figure~\ref{fig:BC3_TG}(d), solid curves). The striated configuration is
-unperturbed by the flow, and is engulfed by a single, larger, rotating
-flow cell (Figure~\ref{fig:BC3_TG}(a)). The multilamellar configuration
-is perturbed by the flow, as seen in the increase in the strain
-parameter $E$ (Figure~\ref{fig:BC3_TG}(f), solid curve). The difference
-in response to the background flow suggests that the multilamellar
-configuration allows for local rearrangement of the particles while
-retaining the overall shape.
-
-At large flow rates $V_0$, both configurations depart significantly from
-their local equilibrium. The lamella bilayers from BC (ii) break apart,
-forming several unlayered bilayer components
-(Figure~\ref{fig:BC2_TG}(c)). In BC (iii), the stria also break apart,
-but neighboring particles form `X'-like arrangements
-(Figure~\ref{fig:BC3_TG}(d)), resembling the doubly alternating director
-equilibrium (Figure~\ref{fig:relax}(d), center, top white rectangle).
-
-%%%
-
-\begin{figure}
-  \begin{center}
-\includegraphics[width=1.0\textwidth]{Figures/Figure10.pdf}        
-  \end{center}
-  \caption{\label{fig:BC3_shear} A striated configuration in a shear
-  flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.1, 0.125,
-  0.15\}$ at $t=0.1\mu$s where the pre-relaxed initial configuration is
-  shown in inset of panel (a). The streamlines are plotted in the
-  background. Panel (d) shows the free energies; panel (e) shows
-  orientational parameter $\tilde{S}_2$; panel (f) shows positional
-  parameter E.}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-\includegraphics[width=1.0\textwidth]{Figures/Figure11.pdf}            
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:BC3_TG} A striated configuration in a Taylor-Green
-  flow. Panels (a)-(c) are snapshots for $V_0=\{0.2, 0.25, 0.3\}$ at
-  $t=0.4\mu$s where the pre-relaxed initial configuration is shown in
-  inset of panel (a). The streamlines are plotted in the background.
-  Panel (d) shows the free energies; panel (e) shows orientational
-  parameter $\tilde{S}_2$; panel (f) shows positional parameter E.}
-\end{figure}
-
-\section{Discussion\label{sec:discussion}}
-Results in \S~\ref{sec:results} are from simulations with $N_b = 60$ particles.
-%Our results were for $N_b = 60$ particles. 
-This particle number was
-large enough for the JP to form measurable structures while giving
-manageable simulation times (days) on a single computing processor. The
-simulation time for $N_b = 198$ in Figure~\ref{fig:relax} and
-Figure~\ref{fig:relax_energy} was several weeks, and so we avoided
-simulations of this size for our results. We used $N = 16$ grid points
-per particle for all simulations. We performed a convergence study and
-found that using $N = 16$ or $N = 24$ grid points per particle gave
-quantitatively indistinguishable results. The time courses consisted of
-$O(10^3)$ time steps with $\Delta t = 0.2$ ns.
-
-The free energy $F$ defined in~\eqref{eq:free_energy} scales with the
-boundary data $g$ and repulsion modulus $M$. 
-%To remove the degree of freedom in the boundary data, 
-We thus scale all boundary data so that the
-square integral of $g$ is independent of the type of boundary condition; BC
-(i), (ii), or (iii). This way, for a fixed configuration, the
-hydrophobic interaction portion of the free energy (the integral
-in~\eqref{eq:free_energy}) converges to $\gamma N_b$ in the limit
-$\rho = 0$. This gives a free energy per particle that is independent of
-the shape and intensity of the hydrophobic interface. In practice, $\rho
-> 0$ is fixed and the JPs assume different configurations. As a result,
-the equilibrium energies per particle in our simulations are different
-and depend on the boundary condition (Figure~\ref{fig:relax_energy}).
-They are about 0.26 $\mathrm{k_BT}$/nm for BC (ii), 0.55
-$\mathrm{k_BT}$/nm for BC (i), and 1.4 $\mathrm{k_BT}$/nm for BC (iii).
-
-Next, we impose a flow on the JP suspension to study
-deformations of JP assemblies as a function of flow strength. There are three categories
-of boundary conditions---BC (i), BC (ii), and BC (iii)---that form
-bilayer, multilamellar, and striated configurations, respectively. For
-BC (i), we consider both an unstructured bilayer and a vesicle
-bilayer. The background flows are a linear shear flow and a steady TG flow.
-
-We characterize the effective material properties of the JP
-structures based on the changes in free energy, orientational order, and
-strain as a function of flow strength. Generally, $F$ increases, $\tilde
-S_2$ decreases, and $E$ increases with increases in both $\dot \gamma$
-and $V_0$, as expected. Structurally, the striated JP configuration for
-BC (iii) behaves the most like a rigid body over the flow strengths
-tested. For this structure, the deformation measures are constant in
-time for shear rates $\dot \gamma$ up to $0.15$ and TG flow rate $V_0$
-up to $0.25$ (Figure~\ref{fig:BC3_shear} and Figure~\ref{fig:BC3_TG}).
-In contrast, a $25\%$--$50 \%$ smaller value for $\dot \gamma$ or $V_0$ is
-required to observe nonrigid deformations for the BC (i) and BC (ii)
-cases.
-
-In terms of fluid behavior, the multilamellar (BC (ii)) structure
-behaves as a shear thinning fluid while the striated structure (BC (iii))
-has a finite yield stress. Qualitatively, the strains for BC (ii)
-increases gradually with shear rate (Figure~\ref{fig:BC2_shear}(f)). In
-contrast, the strains for BC (iii) are constant over a range of flow
-strengths and then increase when the flow strengths are large enough to
-deform the body (Figure~\ref{fig:BC3_shear}(f)). To quantify this
-behavior, we form 
-\begin{align}
-\label{eq:mu_asm}
-\mu_{\text{asm}} = \frac{\dot \gamma}{\dot E} \mu 
-\end{align}
-as an effective dynamic viscosity of the particle assemblies. The
-numerator $\dot \gamma \mu$ gives the force per area provided by the
-solvent stresses where $\mu = 1$ mPa s is the solvent viscosity. The
-strain rate $\dot E$ of the body is the slope of a linear fit to the
-strain curves e.g., in Figure~\ref{fig:BC2_shear}(f).
-
-%%%
-
-\begin{figure}[t]
-\begin{center}
-  \includegraphics[height=0.3\textheight]{ChangeLengthForce.pdf}
-\end{center}
-\begin{caption}{\label{fig:PramChange}
-When the force parameters are tuned in the same percentage change, a linear proportional relationship between changes (square symbol) and the critical shear rates $\dot\gamma^*$ is shown in numerical results.
-The same adjustment in length parameters give a nearly linear trend with an inverse proportional relationship between changes (triangle symbol) and the critical shear rates.}
-\end{caption}
-\end{figure}
-
-To further examine the contest between shear and head-tail attraction, we found that a 5\% and 10\% relative increases in the parameters $\gamma$ and
-$M$ resulted in 4.29\% and 8.57\% relative increases in critial shear rate $\dot\gamma$, from 0.14 to 0.146 and 0.14 to 0.152, respectively. 
-A proportional relationship is observed as the parameters decrease and it is shown in Figure~\ref{fig:PramChange}.
-Moreover, Figure~\ref{fig:PramChange} also shows that 5\% and 10\% decreases in the particle radius c, screening length $\rho$ and repulsion distance $\rho_0$ gave 5.71\%  and 7.14\% increase in $\dot\gamma$ from 0.14 to 0.148 and 0.14 to 0.15.
-In addition, 5\% and 10\% increases in length parameters gave 11.43\% and 18.57\% decrease in critical shear rate $\dot\gamma$.
-The overall result provides another evidence that a different hydrophobicity suggests a dissimilar rheology and dynamics viscosity from the suspended vesicle experiments.
-
-%%%
-
-The viscosities of particle assemblies calculated from \eqref{eq:mu_asm} are shown in
-Table~\ref{tbl:bcii_visc}. The middle row gives the solid area fraction
-$\phi$; the sum of the rigid particle areas divided by the total area of
-the solvent and particle region. We observe that for the multilamellar
-structure, $\mu_{\text{asm}}$ decreases with increasing shear rate. The
-predicted viscosities of the particle assemblies are on the order of
-hundreds of times that of water, consistent with suspension viscosities
-for noninteracting particles~\cite{KONIJN201461}. In the case of
-striated structures, viscosity is effectively infinite for the lower two
-of the shear rates, and then drops to a finite value $\mu_{\text{asm}} =
-60$ mPa s when the shear rate reaches $0.15$ ns$^{-1}$.
-\begin{table}
-  \caption{\label{tbl:bcii_visc} The dynamic viscosity of assemblies
-  $\mu_{\text{asm}}$ (mPa s).}
-\centering
-\begin{tabularx}{0.7\textwidth}{c|X|X|X||X|X|X}
-&\multicolumn{3}{c||}{BC (ii)} & \multicolumn{3}{c}{BC (iii)}\\
-\hline
-  $\dot \gamma$ & 0.05 & 0.10 \quad & 0.15 & 0.100 & 0.125 & 0.15\\
-  \hline
-  $\phi$ & 0.50 & 0.47 & 0.41 & 0.47 & 0.46 & 0.45 \\
-  \hline
-  $\mu_{\text{sus}} $ & 401 & 66 & 42 & 2.5e3 & 1.4e3 & 60\\
-\hline
-\end{tabularx}
-\end{table}
-
-In the case of BC (i), our previous work~\cite{Fu2022_JFM} calculated a
-friction coefficient $b$ for the intermonolayer slip between the two
-leaflets of a bilayer. \citet{denOtter2007,Zgorski2019} and
-\citet{doi:10.1073/pnas.2100156118} have calculated in-plane viscosities
-for fully three-dimensional bilayers. Although not part of this work, it
-is in principle possible to obtain an in-plane viscosity using the
-hydrophobic potential~\eqref{eq:free_energy} by replacing the boundary
-condition~\eqref{eq:bc-type} with one that is everywhere constant, in
-effect modeling lipids in a bilayer as an array of elongated, purely
-hydrophobic pillars.
-
-While increased flow strengths generally injected energy into the
-suspension, the simulation results show that the unstructured bilayer
-actually increases orientational order and has somewhat lower free
-energy under low shear rates (Figure~\ref{fig:BC1_shear}(d,f)). This
-effect suggests that in amphiphilic suspensions, it might be possible to
-decrease the excess area of the system by subjecting the suspension to a
-moderate shear flow (Supplementary Movie S2, right panel).
-Not all background flows produce this
-``organizing'' effect, as it is not observed in the TG background flow
-case (Figure~\ref{fig:BC1_TG}, Supplementary Movie S3, right panel).
-\citet{PhysRevLett.128.256102} have
-shown how to drive particle clusters into arbitrary target shapes by
-solving a first passage problem.
-
-The characteristics of the self-assembly of amphiphilic JP into
-onion-like dendrimersomes like for BC (ii) were previously studied by molecular dynamics
-simulations~\cite{C9NR05885K}. The molecular dynamics simulations use an
-anisotropic pair potential to describe the particle interactions
-where a harmonic form describes the repulsive part and an anisotropic
-attractive part describes the hydrophobic interactions~\cite{HongCacciutoLuijtenGranick2008}.
-We also use a pair potential $P$ in the free energy \eqref{eq:free_energy} for repulsion,
-whereas the long-range, hydrophobic attraction \eqref{eq:FandTdef}
-is nonadditive and comes from domain-dependent variation of
-the water order parameter $u(\xx)$ in the bulk.
-
-\citet{kohl-cor-che-vee22} have simulated JP suspensions in three
-dimensions using the same free energy formulation of hydrophobic
-attraction used in the present work. They observed spontaneous
-aggregation into micelles generically and formation of bilayers when the
-initial configuration was chosen sufficiently close to the final
-configuration. They also studied self-assembly of bipolar electric JP,
-which corresponds to our BC (iii) JP (but electric potential, instead of a water order parameter),
-to define the interaction.  Due to the differing interaction,
-bipolar electric particles form parallel chains that
-repel. In contrast, the hydrophobic interaction between stria is
-attractive. The existence of 'X'-shaped local arrangements as a local
-equilibrium (Figure~\ref{fig:relax}(d), top, middle rectangle) further
-suggests there may be greater diversity in the set of possible
-equilibria in three-dimensions when employing hydrophobic attraction.
+\subsection{Discussion}
+We chose the range of shear rates $\dot \gamma \in [0, 0.02]$ ns$^{-1}$
+by analyzing the capillary number of the JP phases.  Within this range, 
+there was a critical shear rate $\dot \gamma_*$ for the vesicle bilayer
+and striated phases where shear stresses exceeded elastic stresses,
+leading to rupture.  (The multilamellar phase did not rupture.)
+By varying model parameters, we can perform a dimensional analysis 
+on $\dot \gamma_*$.  Focusing on Type III JP in shear flow, 
+$\dot \gamma_* = 0.14$ ns$^{-1}$ for the basic model parameters
+(see Section \ref{sec:tunable_hydrophobicity}).  Increasing 
+the tension parameters $\gamma$ and $M$ by 5\% (collectively denoted
+$\Delta \gamma/\gamma$) led to a 4.29\% increase in critical shear
+rate (denoted $\Delta \dot \gamma_*/\dot \gamma_*$).  This suggests
+that critical shear rate scales linearly with the tension parameters.
+Conversely, increasing the length parameters $c$, $\rho$, and $\rho_0$
+by 5 \% (collectively denoted $\Delta c/c$) led to a -11.43 \% 
+decrease in critical shear rate.  This points to an inverse-quadratic
+scaling in length. Figure \ref{fig:PramChange}(a) summarizes the 
+findings and suggest the scaling
+\begin{equation}
+\label{eq:CSR}
+\mu \dot\gamma_* = K_{\text{III}} \frac{\gamma L}{c^2}.
+\end{equation}
+The scalar $K_{\text{III}}$ is specific to the striated phase under shear flow.
+Here $L$ is the diameter of the phase sample, which scales proportionally 
+with $\gamma^*$ since the striated phase tends to cleave during
+rupture (see Supplementary Movie S4).
+The scaling for vesicle bilayers in shear flow is different
+and takes the form $\mu \dot\gamma_* = K_{\text{I}} \gamma c^2/(\rho L^2)$
+and is proportional to particle size \cite{Fu2022_JFM}, versus inverse quadratic
+like for Type III JPs.
+
+The Results section showed that 
+variations in free energy and strain 
+generally depend the distribution
+of fluid stresses i.e. shear versus TG flow.   
+To further illustrate how fluid stresses interact with the geometry of the JP
+phases, we considered the initially circular vesicle bilayer
+for various TG-flow cell sizes (Figure \ref{fig:PramChange}(b)--(e)). 
+In all cases, the vesicle and TG flow reach a steady-state tank-treading motion,
+but the geometry and motion varies nonmonotonically. 
+For $\lambda$ ranging from $1$ nm to $4$ nm,
+the steady-state vesicle shape goes from an octagon, to a dimpled square,
+to a rounded diamond. \hl{Surprisingly, the direction of rotation switches,
+so that for $\lambda = 1$ nm, the rotation is counterclockwise while
+for $\lambda = 3$ nm, the rotation is clockwise, for example.  }
+Finally, we calculated the vesicle area $A$ and length $L$ (initial area $A_0$,
+initial length $L_0$). 
+As shown in Figure~\ref{fig:PramChange}(f), the relative
+area $A/A_0$ achieves a steady-state that is greatest for $\lambda = 4$ nm
+yet least for $\lambda = 2$ nm. 
+(The relative length $L/L_0$, however, is
+constant in $t$ for all cell sizes (Figure~\ref{fig:PramChange}(e),
+inset)).
+
+We have excluded thermal fluctuations because they are unresolved in the JP phases we consider. 
+For a tensionless, planar membrane, the spectrum of the Fourier coefficients for the 
+profile height 
+$h(\xx) = \sum_{\kk} h(\kk)e^{i \kk \cdot \xx}$ satisfy\cite{Merath2006FluctuationSO}  
+\begin{equation}
+\label{eq:fourier_spectrum}
+\langle |h(\kk)|^2 \rangle = \frac{\kbt}{L_xL_y}\frac{1}{\kappa k^4}
+\end{equation}
+where $\xx$ is a point in an $L_x$ by $L_y$ rectangular membrane patch,
+$\kk = \left(2\pi m/L_x, 2\pi n/L_y\right)$ with
+$m, n = 0, \pm 1, \pm 2, \dots$ not both zero, and $\kappa$ is the membrane bending modulus.
+
+To estimate $h(\kk)$, 
+the $N_b = 60$ JP
+vesicle in Figure \ref{fig:ES2_summary}(e) 
+has arc length $L_x \approx 50$ nm. 
+Our prior work\cite{Fu20,Fu2022_JFM} gave $\kappa  \approx 20$ $\kbt$.
+Since our simulations are two-dimensional, we restrict our attention
+to transversely invariant fluctuations where $n = 0$.
+Substituting these values gives 
+\begin{equation}
+\label{eq:fourier_spectrum_upper}
+\langle |h(\kk)|^2 \rangle \approx \frac{4 \text{ nm}^3}{L_y}\frac{1}{m^4}, \quad m = \pm 1, \pm 2, \dots
+\end{equation}
+For any moderate width, say $L_y > 4$ nm, the leading Fourier coefficient
+has an expected magnitude less than $1$ nm with the remaining coefficients
+dropping off to zero precipitously.  The expected amplitudes coming from thermal
+fluctuation are therefore negligible compared to particle size.
+The elastic
+moduli for the Type (II) and Type (III) phases are by greater by a factor of two
+and five, respectively, than for Type (I) (Figure \ref{fig:F_summary}(c)), making thermal fluctuation
+even more negligible in these cases.
+
+The fact that the fluctuation amplitudes are small 
+is not a consequence of stiffness. Quite the opposite, the value $\kappa = 20$ $\kbt$
+is in  agreement with the experimental literature where 
+micron sized vesicles observably fluctuate. 
+Rather, larger energies are required to fluctuate membranes 
+over smaller wavelengths and these energies exceed available 
+thermal energy when the wavelengths approach tens of nanometers
+as demonstrated above.
+
+The calculated viscosities---14 mPa s for Type I 
+and 21 mPa s for Type II JP phases---are physically reasonable.
+In two-dimensions, the Einstein viscosity correction 
+takes the form $1 + 2.0 \phi + 4.0\phi^2 + O(\phi^3)$
+in the volume fraction $\phi$
+\cite{PhysRevFluids.1.043301,Haines2011APO,Khair2006TheC,Brady1983TheEV}.
+For the JPs in Figure \ref{fig:s2esummary}(e)--(h), this volume fractions
+is about $0.5$ and would give a small viscosity $3$ mPa s.
+On the other hand, the Einstein correction is only valid for dilute
+suspensions, and for large volume fractions like $\phi = 0.5$, 
+one expects viscosities ten or more times that of water  
+\cite{Konijn2014ExperimentalSO}.
+
+Nevertheless, further simulations results are required to 
+differentiate between purely suspension effects
+and particles' preferred alignments
+in analyzing viscosities from Figure \ref{fig:rheologysummary}. 
+For example, the difference between the values 14 mPa s for Type I and 
+21 mPa s for Type II JPs can be explained by the fact that 
+the multilamellar phase is more tightly packed than the bilayer phase
+(Figure \ref{fig:s2esummary}(e)--(h)).
+Furthermore, it seems that the viscosity, and the tendency toward
+shear thinning in the case of Type III JPs where viscosity is 
+effectively infinite for low strain rates 
+(Figure \ref{fig:rheologysummary}(c)), is related 
+to particle coordination.  
+To leading order, a single particle coordinates with: 
+one neighbor in the apposing bilayer for Type I, two neighbors
+at the tail and head interfaces for Type II, and four
+neighbors (front, back, left, and right) for Type III.
 
@@
 %We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.
-We thank useful conversations with E. Corona, M. Rachh and S. Jiang.
+We thank useful conversations with E. Corona, M. Rachh, S. Jiang, and Thomas Beck.
 B.Q.~acknowledges support from the Simons Foundation, Mathematics and Physical Sciences-Collaboration Grants for Mathematicians, Award No. 527139.

### 2023-03-10 doc/PRF2022/Results_old.tex
Results and SM updated

In this section, we subject the JP structures to various
background flows. The purpose is to understand how the self-assemblies
respond to external forcing. We then compare effective
properties of materials comprised of JPs as a function of
their amphiphilic properties.
%%%

\subsection{Bilayer configurations (BC (i)) in a linear shear flow}
To begin, we place the bilayer structure (with BC (i)) from the inset of
Figure~\ref{fig:relax}(b) in a linear shear flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y \cdot \mathbf{x}) {\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate, and ${\ee}_x$ and
${\ee}_y$ are horizontal and vertical unit vectors, respectively. The
initial bilayer structure consists of a small self-enclosing bilayer
(vesicle) and several pieces of bilayers.
Figure~\ref{fig:BC1_shear}(a)--(c) shows a snapshot at $t = 0.5$
$\upmu$s of the bilayer for different shear rates $\dot\gamma=
0.05,0.075,0.01$. The dynamics of the bilayer can be found in
Supplementary Movie S2, which shows
that the initial pieces of bilayers
merge and form a worm-like shape under a linear shear flow. At a low
shear rate, the bilayer constantly goes through rotation and extensional
deformation with the whole bilayer remaining intact
(Figure~\ref{fig:BC1_shear}(a)). As the shear rate increases to a
moderate value (Figure~\ref{fig:BC1_shear}(b)), the bilayer is observed
to shed a small piece of bilayer, similar to the asymmetric breakup of a
viscous drop in confinement \cite{DuFuZhuMaLi2016_AICHEJ}.
%\todo[inline]{missing citation}. 
In Figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two
separate, nearly equal bilayers, similar to the symmetric drop breakup
under a linear shear flow \cite{Stone1994_ARFM}. For the dynamic evolution, see
Supplementary Movie S4.

%\todo[inline]{missing citation}.
%%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
% The streamlines are plotted in the background. 
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%  }
%\end{figure}

We observe that the order parameter $\tilde S_2$ in
Figure~\ref{fig:BC1_shear}(e) is on average increasing. In the initial
configuration, the structure has three or four pieces of bilayer.
%
Under the shear flow, the shedding and merging of bilayers results in an
overall decrease in distinct bilayer structures. Similarly, the free
energies are slightly decreasing (Figure~\ref{fig:BC1_shear}(d)), with
the overall changes occurring in the range of a few $\mathrm{k_BT}$/nm.
This suggests that the shear flow changes the energy landscape to move
the local equilibrium obtained from a random initial condition to an
alternate local equilibrium with less free energy and greater
orientational order  (Supplementary Movie S2).  Note that the free energy $F$ in
Figure~\ref{fig:BC1_shear}(d) has the unit of force ($\mathrm{k_BT}$/nm $\approx$ 4.114 pN)
because our system
is two dimensional.
%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
%  \end{center}
%\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%}
%\end{figure}
%
Finally, the strain parameter diverges in the large shear rate cases
(Figure~\ref{fig:BC1_shear}(f))
because the various pieces of bilayer eventually completely separate and move away from one another
under the shear flow.

%%%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
  \end{center}
  \caption{
    \label{fig:Ves_shear}
A single vesicle in a shear flow. Panels (a)--(c) are snapshots for
  $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \upmu$s where the
  pre-relaxed initial configuration is shown in inset of panel (a). The
  streamlines are plotted in the background. Panel (d) shows the free
  energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel
  (f) shows positional parameter E.}
\end{figure}
\citet{Fu2022_JFM} studied the hydrodynamics of a JP vesicle under a
linear shear flow. Focusing on drawing analogies to hydrodynamics of a
vesicle in continuum modeling (such as
tank-treading~\cite{keller_skalak_1982,Finken08,Shaqfeh11}, bilayer
slip~\cite{sch-vla-mik2010,denOtter2007,Zgorski2019}, and
permeability~\cite{chabanon2017, qua-gan-you2021}), our previous work
demonstrated the existence of a critical shear rate above which the JP vesicle
ruptures~\cite{grandmaison_brancherie_salsac_2021,D2SM00179A}. Based on
the these early results, we reinitialized the BC (i) configuration in
the form of a single, circular vesicle (rather than several bilayer
components) and illustrate how the three measures of structural
deformation correlate to the dynamics of a JP vesicle.

At shear rates $\dot\gamma=0.05, 0.066, 0.075$, the vesicle undergoes
familiar hydrodynamics, such as elongation along the extensional axis
and tank-treading motion, as shown in
Figure~\ref{fig:Ves_shear}(a)--(c)
and Supplementary Movie S2.
%
The circular shape is also a local equilibrium, with somewhat less
energy than the disordered state c.f., Figure~\ref{fig:BC1_shear}(d) and
Figure~\ref{fig:Ves_shear}(d). But unlike the dynamics of bilayers in
Figure~\ref{fig:BC1_shear}, the energies of the JP vesicle in
Figure~\ref{fig:Ves_shear}(d) jump from the baseline value 30
$\mathrm{k_BT}$/nm to about 32 $\mathrm{k_BT}$/nm, signaling the rupture
of the vesicle into disconnected bilayers (see
Figure~\ref{fig:Ves_shear}(d), long and short dashed curves).  After the
rupture, each piece circles around the vorticity at the center without
reconnection while the energies fluctuate slightly around a constant.

For the lowest shear rate case, the vesicle has nearly constant
orientational order $\tilde S_2 = 1$ (see Figure~\ref{fig:Ves_shear}(e),
solid curve). After the JP vesicle ruptures with $\dot\gamma= 0.066$ and
$\dot \gamma= 0.075$, we observe a greater variation in the order
parameter $\tilde{S}_2$ with a baseline value around $0.7$ (see
Figure~\ref{fig:Ves_shear}(e), dashed curves). The oscillations occur
due to the orbit of the two bilayer components, and $\tilde{S}_2$
increases to about $0.9$ when the components slide past one another and
are nearly parallel.
%
As in the previous case, peaks in the strain parameter $E$ correlate
well with changes in structural topology in the bilayer dynamics (dashed
curves in Figure~\ref{fig:Ves_shear}(f)).

%%%%%%%
%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} Bilayers with multiple domains in a
  Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \upmu$s. The
  pre-relaxed initial configuration is shown in the inset of panel (a).
  The streamlines are plotted in the background. Panel (d) shows the
  free energies; panel (e) shows the orientational parameter
  $\tilde{S}_2$; panel (f) shows the positional parameter $E$.}
\end{figure}
%
\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
Next, we subject the JP structures to a steady Taylor-Green (TG) background
flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
\left(
-\cos\left(x/\lambda\right)
 \sin\left(y/\lambda\right)
         {\bf e}_x
         +\sin\left(x/\lambda\right)
         \cos\left(y/\lambda\right)
             {\bf e}_y\right),
\end{equation}
where $x = {\bf e}_x \cdot \xx$ and $y = {\bf e}_y \cdot \xx$
are the horizontal and vertical coordinates, respectively. 
The TG flow is a confining flow consisting of a checkerboard pattern
of cells with alternating circulation. We control the flow by the
dimensionless flow strength $V_0$ and the dimensionless cell size $l$
defining $\lambda = l$ nm. For most of the results in this subsection,
we use the parameter $l=2$.
%

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
  \end{center}
\caption{\label{fig:ves_TG} A single vesicle in a TG flow. Panels
  (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \upmu$s
  where the pre-relaxed initial configuration is shown in inset of panel
  (a). The streamlines are plotted in the background. Panel (d) shows
  the free energies; panel (e) shows orientational parameter
  $\tilde{S}_2$; panel (f) shows positional parameter E.}
\end{figure}

There is no appreciable pattern in the deformation for the
case of bilayers with multiple pieces of bilayer in TG flow
(Supplementary Movie S3, right panel).
Figure~\ref{fig:BC1_TG}(a)--(c)
are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s. At all
flow strengths, the bilayer pieces are separated and mixed by the
flow in neighboring cells. In the $V_0 = 0.2$ case, the flow breaks off
bilayers consisting of only a few particles, leading an increase in
energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve). There is no
apparent structure to the change in the orientational order. There is an initial
increase in the strain parameter due to merging and rupture of bilayers, but the
strains remains bounded since the particles stay confined to the
neighbors of the central cell.

Patterns in the deformation, however, do emerge in the case of a vesicle
in TG flow (Supplementary Movie S3, left panel). For a vesicle in a Taylor-Green flow,
Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\ \upmu$s
where $V_0=0.1,0.15,0.2$. Here, the circular vesicle takes on a steady
square shape for moderate flow rates $V_0 = 0.1$ and $V_0 = 0.15$. In
these cases, there is little change in the vesicle free energy and order
(Figure~\ref{fig:ves_TG}(d)--(f)). The vesicle disintegrates for $V_0 =
0.2$ (Supplementary Movie S5, left panel), leading to a jump in energy, drop in order, and increase in
strain, suggesting that the vesicle has a critical TG flow strength in
the interval $0.15 < V_0 <  0.2$ separating the intact and ruptured
end-states.

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)--(d) show
  the configurations with streamlines of a vesicle is in a TG flow at
  $t=1$ $\upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the
  relative enclosed area $A/A_0$ calculated from the bilayer midplane
  decreases over time. The inset shows the relative length $l/l_0$ which
  remains nearly constant with small magnitude of oscillations. The
  inset and main panel have the same horizontal axis.}
\end{figure}

The vesicle shape is also related to the cell size $l$.
Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in
a TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s. For the smallest cell
size $l = 1$ tested, the vesicle is somewhat octagonal and passes
through multiple cells (Figure~\ref{fig:BTG_Scale}(a)). For the largest
cell size $l = 4$, the vesicle is rhomboid and surrounds a single cell.

In all cases, the JP vesicle tank-treads in TG flow as it does
in the shear flow. The
direction of the tank-treading, however, varies with the cell size
(Figure~\ref{fig:BTG_Scale}(a)--(d), directed arcs). We attribute this
change in rotational orientation to the total rotational moment of the
cells that the vesicle passes through.

We calculate the vesicle area $A$ and length $L$ (initial area $A_0$,
initial length $L_0$) by averaging the area and length of the inner and
outer leaflets. As shown in Figure~\ref{fig:BTG_Scale}(e), the relative
area $A/A_0$ decreases during the simulations, with the rate depending
nonmonotonically on $l$. The relative length $L/L_0$, however, is
constant in $t$ for all cell sizes (Figure~\ref{fig:BTG_Scale}(e),
inset). This implies that the vesicle behaves as an inextensible,
permeable membrane. In previous work, \citet{Fu2022_JFM} determined the
permeability constant of particle-based vesicles in the context of shear
background flow~\cite{chabanon2017, qua-gan-you2021}.

%%%
\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure8.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_shear} A multilamellar structure in a shear
  flow. Panels (a)--(c) are snapshots for $\dot \gamma = \{0.05, 0.1,
  0.15\}$ at $t=0.6\ \upmu$s where the pre-relaxed initial configuration
  is shown in inset of panel (a). The streamlines are plotted in the
  background. Panel (d) shows the free energies; panel (e) shows
  orientational parameter $\tilde{S}_2$; panel (f) shows positional
  parameter E.}
\end{figure}

\subsection{Multilamellar and striated configurations in shear and TG flow}
We have simulated particles for the multilamellar (BC (ii)) and striated
(BC (iii)) boundary conditions, in both shear and TG background flow.
The results are qualitatively similar and will be presented in tandem.
For the multilamellar (BC (ii)) case, we place a 60-particle configuration (inset
of Figure~\ref{fig:BC2_shear}(a)) in shear flow with $\dot\gamma=0.05,
0.1, 0.15$ and in TG flow with $V_0=0.1, 0.15, 0.2$. For the
striated  (BC (iii)) case, we also place a 60-particle configuration (inset of
Figure~\ref{fig:BC3_shear}(a)) in shear and TG background flows. Here,
somewhat larger rates are required to see appreciable deformations for
this boundary condition: $\dot\gamma=0.1, 0.125, 0.15$ and $V_0=0.2,
0.25, 0.3$, respectively.
The BC (ii) and BC (iii) in shear flow cases are visualized in
the latter half of 
Supplementary Movie S2 (low shear rate) and 
Supplementary Movie S4 (high shear rate), respectively.
The low and high flow rates for TG flow are shown in
the latter half of
Supplementary Movie S3 and 
Supplementary Movie S5, respectively.

In terms of shear flow, the free energies are steady at the lowest shear
rates (Figure~\ref{fig:BC2_shear}(d), Figure~\ref{fig:BC3_shear}(d)).
The free energy of the striated configuration oscillates by $\pm 1$
$\mathrm{k_BT}$/nm due to a square reference region deforming into a
rhomboidal shape under shear flow (Figure~\ref{fig:BC3_shear}(d), solid
curve). No such oscillation is present for the multilamellar
configuration since this shape is circularly isotropic
(Figure~\ref{fig:BC2_shear}(d), solid curve). At the lowest shear rates,
there is, however, oscillation in the strains of both configurations,
while the order parameter $\tilde S_2$ is nearly constant
(Figure~\ref{fig:BC2_shear}(e),(f), Figure~\ref{fig:BC3_shear}(e),(f),
solid curves). In summary, both multilamellar and striated
configurations behave as nearly rigid bodies under shear flow when the
shear rate $\dot \gamma$ is low.

In the high shear rate cases ($\dot\gamma=0.15$), both the multilamellar (BC (ii))
and striated (BC (iii)) configurations become disordered. For BC (ii), the lamella
break apart so that individual bilayers are no longer discernible
(Figure~\ref{fig:BC2_shear}(c)). For BC (iii), the stria peel away from
the main body, but remain individually intact
(Figure~\ref{fig:BC3_shear}(c)). Overall, the particles in BC (ii) and
BC (iii) remain bounded and do not drift away in the shear background
flow like for the BC (i) (Figure~\ref{fig:BC1_shear}(c),
Figure~\ref{fig:Ves_shear}(c)).

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure9.pdf} 
  \end{center}
  \vspace{-20pt}
  \caption{\label{fig:BC2_TG} A multilamellar structure in a
  Taylor-Green flow. Panels (a)-(c) are snapshots for $V_0 = \{0.1,
  0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial
  configuration is shown in inset of panel (a). The streamlines are
  plotted in the background. Panel (d) shows the free energies; panel
  (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows
  positional parameter E.}
\end{figure}

Under a TG background flow, the free energy $F$ is also basically
constant for the lowest flow rates $V_0$ (Figure~\ref{fig:BC2_TG}(d),
Figure~\ref{fig:BC3_TG}(d), solid curves). The striated configuration is
unperturbed by the flow, and is engulfed by a single, larger, rotating
flow cell (Figure~\ref{fig:BC3_TG}(a)). The multilamellar configuration
is perturbed by the flow, as seen in the increase in the strain
parameter $E$ (Figure~\ref{fig:BC3_TG}(f), solid curve). The difference
in response to the background flow suggests that the multilamellar
configuration allows for local rearrangement of the particles while
retaining the overall shape.

At large flow rates $V_0$, both configurations depart significantly from
their local equilibrium. The lamella bilayers from BC (ii) break apart,
forming several unlayered bilayer components
(Figure~\ref{fig:BC2_TG}(c)). In BC (iii), the stria also break apart,
but neighboring particles form `X'-like arrangements
(Figure~\ref{fig:BC3_TG}(d)), resembling the doubly alternating director
equilibrium (Figure~\ref{fig:relax}(d), center, top white rectangle).

%%%

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure10.pdf}        
  \end{center}
  \caption{\label{fig:BC3_shear} A striated configuration in a shear
  flow. Panels (a)-(c) are snapshots for $\dot \gamma = \{0.1, 0.125,
  0.15\}$ at $t=0.1\mu$s where the pre-relaxed initial configuration is
  shown in inset of panel (a). The streamlines are plotted in the
  background. Panel (d) shows the free energies; panel (e) shows
  orientational parameter $\tilde{S}_2$; panel (f) shows positional
  parameter E.}
\end{figure}

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure11.pdf}            
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC3_TG} A striated configuration in a Taylor-Green
  flow. Panels (a)-(c) are snapshots for $V_0=\{0.2, 0.25, 0.3\}$ at
  $t=0.4\mu$s where the pre-relaxed initial configuration is shown in
  inset of panel (a). The streamlines are plotted in the background.
  Panel (d) shows the free energies; panel (e) shows orientational
  parameter $\tilde{S}_2$; panel (f) shows positional parameter E.}
\end{figure}

\section{Discussion\label{sec:discussion}}
Results in \S~\ref{sec:results} are from simulations with $N_b = 60$ particles.
%Our results were for $N_b = 60$ particles. 
This particle number was
large enough for the JP to form measurable structures while giving
manageable simulation times (days) on a single computing processor. The
simulation time for $N_b = 198$ in Figure~\ref{fig:relax} and
Figure~\ref{fig:relax_energy} was several weeks, and so we avoided
simulations of this size for our results. We used $N = 16$ grid points
per particle for all simulations. We performed a convergence study and
found that using $N = 16$ or $N = 24$ grid points per particle gave
quantitatively indistinguishable results. The time courses consisted of
$O(10^3)$ time steps with $\Delta t = 0.2$ ns.

The free energy $F$ defined in~\eqref{eq:free_energy} scales with the
boundary data $g$ and repulsion modulus $M$. 
%To remove the degree of freedom in the boundary data, 
We thus scale all boundary data so that the
square integral of $g$ is independent of the type of boundary condition; BC
(i), (ii), or (iii). This way, for a fixed configuration, the
hydrophobic interaction portion of the free energy (the integral
in~\eqref{eq:free_energy}) converges to $\gamma N_b$ in the limit
$\rho = 0$. This gives a free energy per particle that is independent of
the shape and intensity of the hydrophobic interface. In practice, $\rho
> 0$ is fixed and the JPs assume different configurations. As a result,
the equilibrium energies per particle in our simulations are different
and depend on the boundary condition (Figure~\ref{fig:relax_energy}).
They are about 0.26 $\mathrm{k_BT}$/nm for BC (ii), 0.55
$\mathrm{k_BT}$/nm for BC (i), and 1.4 $\mathrm{k_BT}$/nm for BC (iii).

Next, we impose a flow on the JP suspension to study
deformations of JP assemblies as a function of flow strength. There are three categories
of boundary conditions---BC (i), BC (ii), and BC (iii)---that form
bilayer, multilamellar, and striated configurations, respectively. For
BC (i), we consider both an unstructured bilayer and a vesicle
bilayer. The background flows are a linear shear flow and a steady TG flow.

We characterize the effective material properties of the JP
structures based on the changes in free energy, orientational order, and
strain as a function of flow strength. Generally, $F$ increases, $\tilde
S_2$ decreases, and $E$ increases with increases in both $\dot \gamma$
and $V_0$, as expected. Structurally, the striated JP configuration for
BC (iii) behaves the most like a rigid body over the flow strengths
tested. For this structure, the deformation measures are constant in
time for shear rates $\dot \gamma$ up to $0.15$ and TG flow rate $V_0$
up to $0.25$ (Figure~\ref{fig:BC3_shear} and Figure~\ref{fig:BC3_TG}).
In contrast, a $25\%$--$50 \%$ smaller value for $\dot \gamma$ or $V_0$ is
required to observe nonrigid deformations for the BC (i) and BC (ii)
cases.

In terms of fluid behavior, the multilamellar (BC (ii)) structure
behaves as a shear thinning fluid while the striated structure (BC (iii))
has a finite yield stress. Qualitatively, the strains for BC (ii)
increases gradually with shear rate (Figure~\ref{fig:BC2_shear}(f)). In
contrast, the strains for BC (iii) are constant over a range of flow
strengths and then increase when the flow strengths are large enough to
deform the body (Figure~\ref{fig:BC3_shear}(f)). To quantify this
behavior, we form 
\begin{align}
\label{eq:mu_asm}
\mu_{\text{asm}} = \frac{\dot \gamma}{\dot E} \mu 
\end{align}
as an effective dynamic viscosity of the particle assemblies. The
numerator $\dot \gamma \mu$ gives the force per area provided by the
solvent stresses where $\mu = 1$ mPa s is the solvent viscosity. The
strain rate $\dot E$ of the body is the slope of a linear fit to the
strain curves e.g., in Figure~\ref{fig:BC2_shear}(f).

%%%

\begin{figure}[t]
\begin{center}
  \includegraphics[height=0.3\textheight]{ChangeLengthForce.pdf}
\end{center}
\begin{caption}{\label{fig:PramChange}
When the force parameters are tuned in the same percentage change, a linear proportional relationship between changes (square symbol) and the critical shear rates $\dot\gamma^*$ is shown in numerical results. The same adjustment in length parameters give a nearly linear trend with an inverse proportional relationship between changes (triangle symbol) and the critical shear rates.}
\end{caption}
\end{figure}

To further examine the contest between shear and head-tail attraction, we found that a 5\% and 10\% relative increases in the parameters $\gamma$ and
$M$ resulted in 4.29\% and 8.57\% relative increases in critial shear rate $\dot\gamma$, from 0.14 to 0.146 and 0.14 to 0.152, respectively. 
A proportional relationship is observed as the parameters decrease and it is shown in Figure~\ref{fig:PramChange}.
Moreover, Figure~\ref{fig:PramChange} also shows that 5\% and 10\% decreases in the particle radius c, screening length $\rho$ and repulsion distance $\rho_0$ gave 5.71\%  and 7.14\% increase in $\dot\gamma$ from 0.14 to 0.148 and 0.14 to 0.15.
In addition, 5\% and 10\% increases in length parameters gave 11.43\% and 18.57\% decrease in critical shear rate $\dot\gamma$.
The overall result provides another evidence that a different hydrophobicity suggests a dissimilar rheology and dynamics viscosity from the suspended vesicle experiments.

%%%

The viscosities of particle assemblies calculated from \eqref{eq:mu_asm} are shown in
Table~\ref{tbl:bcii_visc}. The middle row gives the solid area fraction
$\phi$; the sum of the rigid particle areas divided by the total area of
the solvent and particle region. We observe that for the multilamellar
structure, $\mu_{\text{asm}}$ decreases with increasing shear rate. The
predicted viscosities of the particle assemblies are on the order of
hundreds of times that of water, consistent with suspension viscosities
for noninteracting particles~\cite{KONIJN201461}. In the case of
striated structures, viscosity is effectively infinite for the lower two
of the shear rates, and then drops to a finite value $\mu_{\text{asm}} =
60$ mPa s when the shear rate reaches $0.15$ ns$^{-1}$.
\begin{table}
  \caption{\label{tbl:bcii_visc} The dynamic viscosity of assemblies
  $\mu_{\text{asm}}$ (mPa s).}
\centering
\begin{tabularx}{0.7\textwidth}{c|X|X|X||X|X|X}
&\multicolumn{3}{c||}{BC (ii)} & \multicolumn{3}{c}{BC (iii)}\\
\hline
  $\dot \gamma$ & 0.05 & 0.10 \quad & 0.15 & 0.100 & 0.125 & 0.15\\
  \hline
  $\phi$ & 0.50 & 0.47 & 0.41 & 0.47 & 0.46 & 0.45 \\
  \hline
  $\mu_{\text{sus}} $ & 401 & 66 & 42 & 2.5e3 & 1.4e3 & 60\\
\hline
\end{tabularx}
\end{table}

In the case of BC (i), our previous work~\cite{Fu2022_JFM} calculated a
friction coefficient $b$ for the intermonolayer slip between the two
leaflets of a bilayer. \citet{denOtter2007,Zgorski2019} and
\citet{doi:10.1073/pnas.2100156118} have calculated in-plane viscosities
for fully three-dimensional bilayers. Although not part of this work, it
is in principle possible to obtain an in-plane viscosity using the
hydrophobic potential~\eqref{eq:free_energy} by replacing the boundary
condition~\eqref{eq:bc-type} with one that is everywhere constant, in
effect modeling lipids in a bilayer as an array of elongated, purely
hydrophobic pillars.

While increased flow strengths generally injected energy into the
suspension, the simulation results show that the unstructured bilayer
actually increases orientational order and has somewhat lower free
energy under low shear rates (Figure~\ref{fig:BC1_shear}(d,f)). This
effect suggests that in amphiphilic suspensions, it might be possible to
decrease the excess area of the system by subjecting the suspension to a
moderate shear flow (Supplementary Movie S2, right panel).
Not all background flows produce this
``organizing'' effect, as it is not observed in the TG background flow
case (Figure~\ref{fig:BC1_TG}, Supplementary Movie S3, right panel).
\citet{PhysRevLett.128.256102} have
shown how to drive particle clusters into arbitrary target shapes by
solving a first passage problem.

The characteristics of the self-assembly of amphiphilic JP into
onion-like dendrimersomes like for BC (ii) were previously studied by molecular dynamics
simulations~\cite{C9NR05885K}. The molecular dynamics simulations use an
anisotropic pair potential to describe the particle interactions
where a harmonic form describes the repulsive part and an anisotropic
attractive part describes the hydrophobic interactions~\cite{HongCacciutoLuijtenGranick2008}.
We also use a pair potential $P$ in the free energy \eqref{eq:free_energy} for repulsion,
whereas the long-range, hydrophobic attraction \eqref{eq:FandTdef}
is nonadditive and comes from domain-dependent variation of
the water order parameter $u(\xx)$ in the bulk.

\citet{kohl-cor-che-vee22} have simulated JP suspensions in three
dimensions using the same free energy formulation of hydrophobic
attraction used in the present work. They observed spontaneous
aggregation into micelles generically and formation of bilayers when the
initial configuration was chosen sufficiently close to the final
configuration. They also studied self-assembly of bipolar electric JP,
which corresponds to our BC (iii) JP (but electric potential, instead of a water order parameter),
to define the interaction.  Due to the differing interaction,
bipolar electric particles form parallel chains that
repel. In contrast, the hydrophobic interaction between stria is
attractive. The existence of 'X'-shaped local arrangements as a local
equilibrium (Figure~\ref{fig:relax}(d), top, middle rectangle) further
suggests there may be greater diversity in the set of possible
equilibria in three-dimensions when employing hydrophobic attraction.

### 2023-03-12 doc/PRF2022/PRF_main.tex
peter working on tasks

@@
 %\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
-\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-1}
+\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-2}
 
@@
 % below if necessary.
-\bibliographystyle{apsrev4-2}
+%\bibliographystyle{apsrev4-2}
 
@@
 Such shear rates are compatible with molecular dynamics 
-simulation \cite{Bradner}, those for large unilamellar vesicles (LUV),
+simulation \cite{Brandner2019}, those for large unilamellar vesicles (LUV),
 \cite{Bernard2005ShearinducedPA} and shearing in blood capillary vessels 
- where shear rates range over 100--1000 s$^{-1}$ \cite{NEEDED}.
+ where shear rates range over 100--2000 s$^{-1}$ \cite{Cho2011}.
 
@@
 the $N_b = 60$ JP
-vesicle in Figure \ref{fig:ES2_summary}(e) 
+vesicle in Figure \ref{fig:s2esummary}(e) 
 has arc length $L_x \approx 50$ nm. 
@@
 moduli for the Type (II) and Type (III) phases are by greater by a factor of two
-and five, respectively, than for Type (I) (Figure \ref{fig:F_summary}(c)), making thermal fluctuation
-even more negligible in these cases.
+and five, respectively, than for Type (I) (Figure \ref{fig:fsummary}(c)), making thermal fluctuation even more negligible in these cases.
 

### 2023-03-12 doc/PRF2022/PRF_main.tex
peter added captions

@@
 %\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
-\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-2}
+\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-1}
 
@@
 \end{center}
-\caption{\label{fig:s2esummary}asdf}
+\caption{\label{fig:s2esummary}
+Panel (a)-(b) show the average strain increase in percentage of vesicle, bilayer, multilamellar, and striated JP structures under a shear flow and a TG flow, respectively.
+Panel (c)-(d) show the average alignment of four JP structures under a shear flow and a TG flow, respectively. 
+Each snapshot of panels (e)-(l) contains the configurations of the JP structure using a specific type of boundary bondition without ruptures and the backgroud curves indicate the streamlines.}
 \end{figure}
+%
 We subjected the Type I, II, and III JP phases to background flows and measured 
@@
 \end{center}
-\caption{\label{fig:fsummary}}
+\caption{\label{fig:fsummary}
+The change of average free energy versus shear rates for shear flow and TG flow simulation results are plotted in panels (a)-(b).
+Panel (c) shows the relationships between the changes of the free energy as mean displacements of JP increases and the types of boundary conditions.
+All data points are fitted by quadratic functions and represented in dashed curves.}
 \end{figure}
@@
 \end{center}
-\caption{\label{fig:rheologysummary}}
+\caption{\label{fig:rheologysummary}
+Rheology in Type I, II, and III.
+Panel (a) shows that unilamellar JP bilayer and vesicle both behave close to a Newtonian fluid.
+Panel (b) provides that the multilamellar phase shows a near shear thinning behaviour.
+A pseudoplastic behaviour of deformation in striated JP structure is shown in panel (c).
+}
 \end{figure}

### 2023-03-12 doc/PRF2022/Supplementary.tex
Results and SM updated
peter working on tasks
peter added captions

@@
   \noindent 
-  Collective behavior of Janus Particles Suspended in a Viscous Fluid}\\
+ Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows}\\
 
@@
 %\Phi_{\mathrm{rep}}
+
+\section{Raw Data}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=\textwidth]{SMFigures/VeShRaw.pdf}
+\end{center}
+\caption{A Vesicle under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.075$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:veshraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=\textwidth]{SMFigures/ULShRaw.pdf}
+\end{center}
+\caption{A unilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.013\sim0.075$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:ulshraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=\textwidth]{SMFigures/MLShRaw.pdf}
+\end{center}
+\caption{A multilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.025\sim0.075$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:mlshraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=\textwidth]{SMFigures/StShRaw.pdf}
+\end{center}
+\caption{A striated JP structure under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.07$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:stshraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=\textwidth]{SMFigures/VeTGRaw.pdf}
+\end{center}
+\caption{A vesicle JP structure under a TG flow with choices of shear rates $\dot\gamma=0.005\sim0.044$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:vetgraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=\textwidth]{SMFigures/ULTGRaw.pdf}
+\end{center}
+\caption{A unilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.013\sim0.05$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:ultgraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=\textwidth]{SMFigures/MLTGRaw.pdf}
+\end{center}
+\caption{A multilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.025\sim0.069$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:mltgraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=\textwidth]{SMFigures/StTGRaw.pdf}
+\end{center}
+\caption{A striated JP structure under a TG flow with choices of shear rates $\dot\gamma=0.01\sim0.069$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:mltgraw}
+\label{fig:sttgraw}
+\end{figure}
 

### 2023-03-12 doc/PRF2022/PRF_main.tex
minor checks

@@
 the steady-state vesicle shape goes from an octagon, to a dimpled square,
-to a rounded diamond. \hl{Surprisingly, the direction of rotation switches,
-so that for $\lambda = 1$ nm, the rotation is counterclockwise while
-for $\lambda = 3$ nm, the rotation is clockwise, for example.  }
+to a rounded diamond. Surprisingly, the direction of rotation switches,
+so that for $\lambda = 2$ nm, the rotation is clockwise while
+for $\lambda = 4$ nm, the rotation is counterclockwise, for example. 
 Finally, we calculated the vesicle area $A$ and length $L$ (initial area $A_0$,

### 2023-03-16 doc/PRF2022/PRF_main.tex
edits

@@
-%% ***A*** Start of file apstemplate.tex ****** %
+%% ***** Start of file apstemplate.tex ****** %
 %%
@@
 The sets $\Omega$, $\Gamma_1$, \dots, and $\Gamma_{N_b}$ depend on $t$.
-Assuming inertial terms are negligible, we have the Stokes equations
+Assuming inertial terms are negligible, the solvent satisfies the Stokes equations
 \begin{alignat}{3}
@@
 \end{alignat}
-where $\uu$ is the velocity of the solvent, $p$ is the pressure,
+where $\uu$ is the velocity, $p$ is the pressure,
 $\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
@@
 The order parameter $u(\xx,t)$ is assumed to minimize the free energy
-$F$ and therefore satisfies the screened Laplace equation
-boundary value problem
+$F$ and therefore satisfies the screened Laplace boundary value problem
 \begin{gather}
@@
 The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
-\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for $1 \leq s <
-\infty$. The parameter $\rho_0$ is the distance 
+\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for
+$s \geq 1$. The parameter $\rho_0$ is the distance 
 below which steric repulsion becomes important and 
@@
   ,\quad
-T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
+T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s.
 \end{align}
@@
 (ii) compute the force and torque~\eqref{eq:FandTdef},
-and finally (iii) solve the Stokes equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield}
+and (iii) solve the Stokes equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield}
 subject to~\eqref{eq:rigid-vel} and \eqref{eq:force}. 
@@
 \subsection{Boundary integral representations}
-It is challenging to solve the Stokes and screened Laplace equations
-and far-field boundary conditions accurately. 
+We require a method to accurately solve the Stokes and
+screened Laplace equations in intricate, unbounded geometries.
 We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
@@
 with a collocation method. To express the solution of
-\eqref{eq:SL}--\eqref{eq:SLbc}, we adopt the double layer potential
+\eqref{eq:SL}--\eqref{eq:SLbc},
+we adopt the double layer potential
 \begin{align}
@@
 u({\xx}) = \DD[\sigma](\xx) = \int_{\partial \Omega} 
-  \pderiv{G(\xx-\yy)}{\nnu_\yy}\sigma(\yy)\, \dif s_\yy, 
+  \pderiv{G(\xx-\yy)}{\nnu_\yy}\eta(\yy)\, \dif s_\yy, 
   \quad \xx \in \Omega,
@@
 zeroth-order modified Bessel function of the second kind, $\nnu_\yy$ is
-the unit outward normal at $\yy$, and $\sigma$ is a scalar-valued
+the unit outward normal at $\yy$, and $\eta$ is a scalar-valued
 density function. The subscript in $\dif s_\yy$ denotes integration with
@@
   \label{eq:SL_BIE2}
-  g(\xx) = \frac{1}{2} \sigma(\xx) + \DD[\sigma](\xx), \quad
-    \xx \in \Gamma.
+  g(\xx) = \frac{1}{2} \eta(\xx) + \DD[\eta](\xx), \quad
+    \xx \in \partial \Omega.
 \end{align}
 
-For the velocity, we use the representation
+For the velocity, we use the completed double-layer potential
+representation~\cite{pow-mir1987}
 \begin{align}
@@
 \end{align}
-respectively, where $\rr = \xx - \aa_i$~\cite{pow-mir1987}. Letting
+respectively, where $\rr = \xx - \aa_i$. Letting
 $\xx$ approach $\Gamma_i$ in~\eqref{eq:velocity}, applying the jump
@@
 and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
-These are solved with matrix-free GMRES, and we guarantee that the
-number of GMRES iterations is mesh-independent by using second-kind
-BIEs.
+These are solved with matrix-free GMRES
+and the second-kind BIEs
+guarantee that the number of GMRES iterations is
+mesh-independent.
 
@@
 at room temperature. Pure lipid components give a range of interfacial
-tensions $0.7$--$5.3$~pN~nm$^{-1}$~\cite{KUZMIN2005, Petelska2012,
-  Jackson2016, GarciaSaez}.
-we use $\gamma=4.1$~pN~nm$^{-1}$ since
-this value gave good agreement with elastic moduli of lipid bilayers~\cite{Fu20,Fu2022_JFM}.
+tensions~\cite{KUZMIN2005, Petelska2012,Jackson2016, GarciaSaez}; $0.7$--$5.3$~pN~nm$^{-1}$.
+We use $\gamma=4.1$~pN~nm$^{-1}$ which gives a physically reasonable 
+elastic modulus $\kappa$ of lipid bilayers~\cite{Fu20,Fu2022_JFM}.
 The particle radius $c = 1.25$~nm represents one half 
@@
 overly aggressive mesh refinement. The characteristic time
-and length are $1$~ns and  $1$~nm respectively.
+and length are $1$~ns and  $1$~nm, respectively.
 
@@
 particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$
-The scalar $a$ normalizes $g$ so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
+The scalar $b$ shifts the periodic date up and down and the scalar
+$a$ normalizes $g$ so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
 The side of the particle where
@@
 can be classified into one of three categories:
-(Type I, amphiphile, $b = 1$) $g$ is positive on 
+Type I, amphiphile, $b = 1$, $g$ is positive on 
 one side representing a hydrocarbon-water interface, and
 is zero on the other representing an apolar, hydrophilic region;
-(Type II, asymmetric hydrophobe, $b = 2$) $g$ is positive
-on both sides but greater on one side;
-(Type III, poler, $b = -1/2$) $g$ is positive on one
+Type II, asymmetric hydrophobe, $b = 2$, $g$ is positive
+on both sides but more so on one side;
+Type III, polar, $b = 0$, $g$ is positive on one
 side and negative on the other, representing a
@@
 \begin{caption}{\label{fig:relax}
-  Panel (a) shows the initial $N_b = 198$ particle configuration with random
-  position and orientation.
+    Panel (a) shows the $t = 0$, $N_b = 198$ particle configuration
+    with random orientation and initially confined to a box. 
   Panels (b), (d), (e) show bilayer, multilamellar, and striated phases
-  composed of amphiphilic (Type I), asymmetric hydrophobic (Type II),
-  and poler (Type 3) JP, respectively. 
+  composed of amphiphilic (Type I), asymmetric hydrophobe (Type II),
+  and polar (Type III) JP, respectively. 
   Panels (c) and (f) plot the free energies~\eqref{eq:free_energy}
   and alignment order parameter~\eqref{eq:S2} with respect
-  to $t$. The solid markers in panel (c) are 
+  to $t$. The open markers in panel (c)
+  are for $N_b = 60$ and the
+  solid markers are for $N_b = 198$ but 
   normalized by $60/198$, showing that the energy
@@
 Over short times, these particles self-assemble into bilayers. But unlike for
-Type I JP, the heads are also hydrophobic and so over long times, 
+Type I JPs, the heads are also hydrophobic and so over long times, 
 the bilayers sort into a ``multilamellar'' phase.
-The number of layers depends primarily on the number of particles.
+The number of layers depends on the number of particles.
 Figure~\ref{fig:relax}(c), for example, shows a multilamellar structure
@@
 whose centers lie with $4c$ of that of particle $i$. 
-Defined as such, $S_2$ lies in the range $-1/2 \le S_2 \le 1$.
-with a value $S_2 = 1$ indicates perfect alignment between particles
-while $S_2=-1/2$ indicates isotropic alignment locally.
-This cutoff distance was chosen empirically
+Defined as such, $S_2$ lies in the range $-1/2 \le S_2 \le 1$
+with a value $S_2 = 1$ indicating perfect alignment between particles
+while $S_2=-1/2$ indicating isotropic alignment locally.
+The cutoff distance $4c$ was chosen empirically
 so that the average includes nearest neighbors
@@
 The striated phase order admits more than one pattern
-depending on the number of particles (Figure~\ref{fig:relax}(f), bottom and top curves).
+depending on the number of particles (Figure~\ref{fig:relax}(f), triangles).
 When the number of particles is fewer, there is only a
-single pattern in particle orientations where the directors are more or
+single pattern where the directors are more or
 less parallel and alternate directions (Figure~\ref{fig:relax}(e),
@@
 \caption{\label{fig:s2esummary}
-Panel (a)-(b) show the average strain increase in percentage of vesicle, bilayer, multilamellar, and striated JP structures under a shear flow and a TG flow, respectively.
+  Panel (a)-(b) show the average strain increase for bilayer, vesicle BL,
+  multilamellar, and striated JP structures under a shear flow and a TG flow, respectively.
 Panel (c)-(d) show the average alignment of four JP structures under a shear flow and a TG flow, respectively. 
-Each snapshot of panels (e)-(l) contains the configurations of the JP structure using a specific type of boundary bondition without ruptures and the backgroud curves indicate the streamlines.}
+Each snapshot of panels (e)-(l) contains the configurations of the JP structure using a specific type of boundary bondition without ruptures and the backgroud curves indicate the velocity streamlines.}
 \end{figure}
@@
 In both cases, $\dot \gamma$ is the shear rate.
+In \eqref{eq:tg_flow}, $\lambda$ is the cell-size parameter.
+
 To obtain a range for $\dot \gamma$, 
@@
 \cite{Bernard2005ShearinducedPA} and shearing in blood capillary vessels
- where shear rates range over 100--2000 s$^{-1}$ \cite{Cho2011}.
+\cite{Cho2011} where shear rates range over 100--2000 s$^{-1}$.
 
@@
 on equal terms, the flow rate $\lambda \dot \gamma$  
-was chosen for \eqref{eq:tg_flow} so that it has has the same
-rate viscous dissipation per area as for \eqref{eq:sh_flow}.
+was chosen for \eqref{eq:tg_flow} so that it has the same
+rate of viscous dissipation per area as for \eqref{eq:sh_flow}.
 In other words, 
@@
 $\uu = \uu_{\infty}^{\text{TG}}$
-when integrated over a common cell $A$.
+when integrated over a $TG$ cell $A$.
 
@@
 we reinitialized the data to have a ring-shaped vesicle bilayer.
-This phase is distinguished from "bilayer" by "vesicle BL" in the figures.
+This phase is distinguished from ``bilayer'' by ``vesicle BL'' in the figures.
 For the same number of JP, the vesicle bilayer
-has lower free  steady-state energy ($F = 24.6 \;\kbt$ nm$^{-1}$) than the 
-disordered bilayer phase ($F = 24.6 \;\kbt$ nm$^{-1}$). 
+has lower free  steady-state energy
+($F = 24.6 \;\kbt$ nm$^{-1}$) than the 
+disordered bilayer phase ($F = 27.2 \;\kbt$ nm$^{-1}$). 
 Since the simulations are for two dimensions,
@@
 Moreover, $\uu$ satisfies the rigid boundary condition at 
-every JP-fluid interface i.e., the particles interact with local
+every JP-fluid interface i.e., the particles interact with the local
 flow field and are not merely carried by background flow.
@@
 The greatest increase occurs with the Type I amphiphiles, 
-suggesting that this phase has the lowest elastic modulus. In comparison, 
+suggesting that this phase has the lowest elastic modulus
+(squares). In comparison, 
 the  striated phase consisting of  Type III polar JP is
-basically rigid.
+basically rigid (triangles).
 
@@
 for $\gamma > \gamma_*$, the phase ruptures. 
-For example, the vesicles phase has 
-$\gamma_* = 0.05$ ns$^{-1}$ 
+For example, the vesicle BL phase has 
+$\gamma_*$ approximately $0.05$ ns$^{-1}$ 
 under shear flow and TG flow. However, the critical shear rate
@@
 Due to variable stress distribution, 
-the critical shear rate in TG likely 
+the critical shear rate in TG flow likely 
 depends on the cell size parameter $\lambda$.
@@
 \caption{\label{fig:fsummary}
-The change of average free energy versus shear rates for shear flow and TG flow simulation results are plotted in panels (a)-(b).
-Panel (c) shows the relationships between the changes of the free energy as mean displacements of JP increases and the types of boundary conditions.
-All data points are fitted by quadratic functions and represented in dashed curves.}
+  The change of average free energy versus shear rates for shear flow and TG flow simulation results are plotted in panels (a)-(b). Panel (c) contains quadratic fits
+  to the change in free energy as a function of displacement in interparticle distance
+  from equilbrium.}
 \end{figure}
@@
 multilamellar phase, with the other phases 
-showing a moderate change in a few \KBT\;per 
-nm.
+showing a moderate change in a few \KBT\,nm$^{-1}$.
 
 Figure \ref{fig:fsummary} (c) plots free energy 
-against $x = c E$ representing the mean  
-inter-particle displacement;    
-zero displacement corresponds
-to an inter-particle distance where 
-repulsion and attraction are in balance;
+against the displacement $x = c E$ representing the
+change in mean  interparticle displacement from equilibrium;
 $c = 1.25$ nm is particle radius.
@@
 hydrophobicity 
-which are tuned by \ref{eq:bc-type} in our model.
+which are tuned by \eqref{eq:bc-type} in our model.
 
@@
 \caption{\label{fig:rheologysummary}
-Rheology in Type I, II, and III.
-Panel (a) shows that unilamellar JP bilayer and vesicle both behave close to a Newtonian fluid.
+  Rheology of Type I, II, and III phases.
+  Panel (a) shows that bilayer phases  behave as a Newtonian fluid.
   Panel (b) provides that the multilamellar phase shows a near shear thinning behaviour.
-A pseudoplastic behaviour of deformation in striated JP structure is shown in panel (c).
-}
+  A pseudoplastic behaviour of deformation in striated phases is shown in panel (c). }
 \end{figure}
@@
 \end{equation}
-The reason for defining $\dot E$ in this was is that 
+The reason for defining $\dot E$ in this way is that 
 the shear flow $\uu_{\infty}^{\text{sh}}$
@@
 The bilayer phases consisting of Type I JPs are basically Newtonian
-with viscosity $0.014$ MPa\;ns $= 14$ mPa\;s,
+with viscosity $0.014$ MPa\;$\upmu$s $= 14$ mPa\;s,
 about 14 times the the viscosity of water at room temperature
@@
 Figure \ref{fig:s2esummary}(a), (b) (triangles).
+\todo[inline]{RBC flow refereces}
 
@@
 \subsection{Discussion}
-We chose the range of shear rates $\dot \gamma \in [0, 0.02]$ ns$^{-1}$
-by analyzing the capillary number of the JP phases.  Within this range, 
-there was a critical shear rate $\dot \gamma_*$ for the vesicle bilayer
+We choose the range of shear rates $\dot \gamma \in [0, 0.02]$ ns$^{-1}$
+by analyzing the capillary number of the JP phases.  With this range, 
+there was a critical shear rate $\dot \gamma_*$ for the vesicle BL
 and striated phases where shear stresses exceeded elastic stresses,
-leading to rupture.  (The multilamellar phase did not rupture.)
+leading to rupture.  The multilamellar phase did not rupture.
 By varying model parameters, we can perform a dimensional analysis 
-on $\dot \gamma_*$.  Focusing on Type III JP in shear flow, 
+on $\dot \gamma_*$.  Focusing on Type III JPs in shear flow, 
 $\dot \gamma_* = 0.14$ ns$^{-1}$ for the basic model parameters
 (see Section \ref{sec:tunable_hydrophobicity}).  Increasing
-the tension parameters $\gamma$ and $M$ by 5\% (collectively denoted
-$\Delta \gamma/\gamma$) led to a 4.29\% increase in critical shear
+and decreasing the 
+the tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
+$\Delta \gamma/\gamma$) led to basically the same relative
+increase/decrease in critical shear
 rate (denoted $\Delta \dot \gamma_*/\dot \gamma_*$).  This suggests
-that critical shear rate scales linearly with the tension parameters.
-Conversely, increasing the length parameters $c$, $\rho$, and $\rho_0$
-by 5 \% (collectively denoted $\Delta c/c$) led to a -11.43 \% 
-decrease in critical shear rate.  This points to an inverse-quadratic
+that the critical shear rate scales linearly with the tension parameters.
+Conversely, increasing (resp. decreasing) the length parameters $c$, $\rho$, and $\rho_0$
+by up to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
+relative \emph{decrease} (resp. increasing) in the critical shear rate.  This points to an inverse-quadratic
 scaling in length. Figure \ref{fig:PramChange}(a) summarizes the 
@@
 The scalar $K_{\text{III}}$ is specific to the striated phase under shear flow.
-Here $L$ is the diameter of the phase sample, which scales proportionally 
-with $\gamma^*$ since the striated phase tends to cleave during
+Here $L$ is the diameter of the phase sample, which is proportional
+to $\gamma^*$ since the striated phase tends to cleave during
 rupture (see Supplementary Movie S4).
-The scaling for vesicle bilayers in shear flow is different
-and takes the form $\mu \dot\gamma_* = K_{\text{I}} \gamma c^2/(\rho L^2)$
-and is proportional to particle size \cite{Fu2022_JFM}, versus inverse quadratic
-like for Type III JPs.
+Our previous work\cite{Fu2022_JFM}
+found the scaling $\mu \dot\gamma_* = K_{\text{I}} \gamma c^2/(\rho L^2)$
+for vesicle BL in shear flow.
 
@@
 generally depend the distribution
-of fluid stresses i.e. shear versus TG flow.   
+of fluid stresses i.e., shear versus TG flow.   
 To further illustrate how fluid stresses interact with the geometry of the JP
@@
   \label{eq:SLP}
-  \mathcal{S}[\sigma](\xx) = \int_\Gamma G(\xx-\yy) \sigma(\yy)\, \dif s_\yy
+  \mathcal{S}[\sigma](\xx) = \int_{\partial \Omega} G(\xx-\yy) \sigma(\yy)\, \dif s_\yy
 \end{equation}
 be the single layer potential for a density function $\sigma.$ Fix $\xx
-\in \Gamma$, let $\nnu_{\xx} = \nnu(\xx)$ and $\nnu_{\yy}$ be the unit
-normal at $\xx$, respectively $\yy$, in $\Gamma$, and let $\zz \in
+\in {\partial \Omega}$, let $\nnu_{\xx} = \nnu(\xx)$ and $\nnu_{\yy}$ be the unit
+normal at $\xx$, respectively $\yy$, in ${\partial \Omega}$, and let $\zz \in
 \Omega$. The subscripts in $\nabla_{\zz}$ and $\nabla_{\yy}$ denote
@@
 \nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
-&=\nnu_\xx \cdot \nabla_\zz \int_\Gamma \frac{\partial G(\zz-\yy)}{\partial \nnu_\yy}\sigma(\yy) \,\dif s_\yy\\
-&=\int_\Gamma \nnu_\xx^\top \left(\nabla_\zz\nabla_\yy^\top  G(\zz-\yy)\right) \nnu_\yy\sigma(\yy)  \,\dif s_\yy\\
-  &=-\int_\Gamma \nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy\sigma(\yy)\ \dif s_\yy,
+&=\nnu_\xx \cdot \nabla_\zz \int_{\partial \Omega} \frac{\partial G(\zz-\yy)}{\partial \nnu_\yy}\sigma(\yy) \,\dif s_\yy\\
+&=\int_{\partial \Omega} \nnu_\xx^\top \left(\nabla_\zz\nabla_\yy^\top  G(\zz-\yy)\right) \nnu_\yy\sigma(\yy)  \,\dif s_\yy\\
+  &=-\int_{\partial \Omega} \nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy\sigma(\yy)\ \dif s_\yy,
 \end{align*}
@@
 \nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
-&=-\int_\Gamma  \Delta_\yy G(\zz-\yy) {\bf t}_\xx \cdot   {\bf t}_\yy \sigma(\yy)\ \dif s_\yy
-+\int_\Gamma({\bf t}_\xx\cdot\nabla_\yy)({\bf t}_\yy\cdot\nabla_\yy G(\zz-\yy))\sigma(\yy)\ \dif s_\yy\\
-&= -\int_\Gamma \frac{1}{\rho^{2}} G(\zz-\yy) {\bf t}_\xx \cdot {\bf t}_\yy \sigma(\yy)\ \dif s_\yy  
--({\bf t}_\xx\cdot\nabla_\zz)\int_\Gamma \frac{\dif}{\dif s_\yy}G(\zz-\yy) \sigma(\yy)\ \dif s_\yy\\
-&= -\frac{1}{\rho^2} {\bf t}_\xx\cdot \int_\Gamma G(\zz-\yy){\bf t}_\yy \sigma(\yy)\ \dif s_\yy + 
-({\bf t}_\xx \cdot \nabla_\zz)\int_\Gamma G(\zz-\yy)\frac{\dif }{\dif s} \sigma(\yy)  \dif s_\yy.
+&=-\int_{\partial \Omega}  \Delta_\yy G(\zz-\yy) {\bf t}_\xx \cdot   {\bf t}_\yy \sigma(\yy)\ \dif s_\yy
++\int_{\partial \Omega}({\bf t}_\xx\cdot\nabla_\yy)({\bf t}_\yy\cdot\nabla_\yy G(\zz-\yy))\sigma(\yy)\ \dif s_\yy\\
+&= -\int_{\partial \Omega} \frac{1}{\rho^{2}} G(\zz-\yy) {\bf t}_\xx \cdot {\bf t}_\yy \sigma(\yy)\ \dif s_\yy  
+-({\bf t}_\xx\cdot\nabla_\zz)\int_{\partial \Omega} \frac{\dif}{\dif s_\yy}G(\zz-\yy) \sigma(\yy)\ \dif s_\yy\\
+&= -\frac{1}{\rho^2} {\bf t}_\xx\cdot \int_{\partial \Omega} G(\zz-\yy){\bf t}_\yy \sigma(\yy)\ \dif s_\yy + 
+({\bf t}_\xx \cdot \nabla_\zz)\int_{\partial \Omega} G(\zz-\yy)\frac{\dif }{\dif s} \sigma(\yy)  \dif s_\yy.
 \end{align*}
 %
-Letting $\zz\to\xx\in\Gamma$, and noting that both sides of the equation
+Letting $\zz\to\xx\in{\partial \Omega}$, and noting that both sides of the equation
 are continuous, we obtain~\eqref{eq:normal_deriv}.
@@
 
-We adopt the double layer potential to express the solution of \eqref{eq:SL} where the condition is $f(u)=u^2$. Then it is given by 
+We adopt the double layer potential to express the solution of \eqref{eq:SL} where the
+condition is $f(u)=u^2$. Then it is given by 
 \begin{align}

### 2023-03-16 doc/PRF2022/PRF_main.tex

@@
 to infer free energy $F$, alignment order $S_2$, and strain $E$.     
+\todo[inline]{Reference the supplementary material here.}
 
@@
 \caption{\label{fig:PramChange}
-In panel (a), relative change in $\dot \gamma_*$ is linear 
-in the relative change of tension with slope $1$.
-Conversely, relative change in $\dot \gamma_*$ 
-has slope $-2$ with respect to relative change in tension.
-Panels (b)--(e) show the tank-treading configuration 
-of a vesicle bilayer the configurations with streamlines of a vesicle is in a TG flow at
-$t=1$ $\upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the
-  relative enclosed area $A/A_0$ calculated from the bilayer midplane
-  decreases over time. The inset shows the relative length $L/L_0$ which
-  remains nearly constant with small magnitude of oscillations. The
-  inset and main panel have the same horizontal axis.}
+In panel (a), the relative change in $\dot \gamma_*$ is linear in the
+  relative change of the tension parameters $\gamma$ and $M$ with slope
+  $1$.  Additionally, the relative change in $\dot \gamma_*$ has slope
+  $-2$ with respect to the relative change in the length parameters $c$,
+  $\rho$, and $\rho_0$.  Panels (b)--(e) show the tank-treading
+  configuration of a vesicle bilayer the configurations with streamlines
+  of a vesicle is in a TG flow at $t=1$ $\upmu$s with $l= 1,2,3,4$,
+  respectively. In panel (f), the relative enclosed area $A/A_0$
+  calculated from the bilayer midplane decreases over time. The inset
+  shows the relative length $L/L_0$ which remains nearly constant with a
+  small oscillation. The inset and main panel have the same horizontal
+  axis.} 
+  \todo[inline]{We propose to relate panel (f) to the pressure drops
+  across the JP vesicles. Also, panel (a) should be its own figure, and
+  (b)--(e) can be their own figure, but with darker stream lines. Also,
+  should not be talking about tank treading, but rather about sliding
+  between layers, and how they are affected by the correlation between
+  the bilayer location and the TG cell boundary.  This correlation also
+  somehow determines the shape.  Can count the number of partial TG
+  cells inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has
+  2 + 4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$,
+  and (e) has 1 cell.}
 \end{figure}
@@
 (see Section \ref{sec:tunable_hydrophobicity}).  Increasing
-and decreasing the 
-the tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
+and decreasing the tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
 $\Delta \gamma/\gamma$) led to basically the same relative
@@
 that the critical shear rate scales linearly with the tension parameters.
-Conversely, increasing (resp. decreasing) the length parameters $c$, $\rho$, and $\rho_0$
+Conversely, increasing (resp.~decreasing) the length parameters $c$, $\rho$, and $\rho_0$
 by up to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
-relative \emph{decrease} (resp. increasing) in the critical shear rate.  This points to an inverse-quadratic
+relative \emph{decrease} (resp.~increasing) in the critical shear rate.  This points to an inverse-quadratic
 scaling in length. Figure \ref{fig:PramChange}(a) summarizes the 
@@
 \end{equation}
-The scalar $K_{\text{III}}$ is specific to the striated phase under shear flow.
-Here $L$ is the diameter of the phase sample, which is proportional
-to $\gamma^*$ since the striated phase tends to cleave during
-rupture (see Supplementary Movie S4).
-Our previous work\cite{Fu2022_JFM}
-found the scaling $\mu \dot\gamma_* = K_{\text{I}} \gamma c^2/(\rho L^2)$
-for vesicle BL in shear flow.
-
-The Results section showed that 
-variations in free energy and strain 
-generally depend the distribution
-of fluid stresses i.e., shear versus TG flow.   
-To further illustrate how fluid stresses interact with the geometry of the JP
-phases, we considered the initially circular vesicle bilayer
-for various TG-flow cell sizes (Figure \ref{fig:PramChange}(b)--(e)). 
-In all cases, the vesicle and TG flow reach a steady-state tank-treading motion,
-but the geometry and motion varies nonmonotonically. 
-For $\lambda$ ranging from $1$ nm to $4$ nm,
-the steady-state vesicle shape goes from an octagon, to a dimpled square,
-to a rounded diamond. Surprisingly, the direction of rotation switches,
-so that for $\lambda = 2$ nm, the rotation is clockwise while
-for $\lambda = 4$ nm, the rotation is counterclockwise, for example. 
-Finally, we calculated the vesicle area $A$ and length $L$ (initial area $A_0$,
-initial length $L_0$). 
-As shown in Figure~\ref{fig:PramChange}(f), the relative
-area $A/A_0$ achieves a steady-state that is greatest for $\lambda = 4$ nm
-yet least for $\lambda = 2$ nm. 
-(The relative length $L/L_0$, however, is
-constant in $t$ for all cell sizes (Figure~\ref{fig:PramChange}(e),
-inset)).
-
-We have excluded thermal fluctuations because they are unresolved in the JP phases we consider. 
-For a tensionless, planar membrane, the spectrum of the Fourier coefficients for the 
-profile height 
+The scalar $K_{\text{III}}$ is specific to the striated phase under
+shear flow.  Here $L$ is the diameter of the phase sample, which is
+proportional to $\gamma^*$ since the striated phase tends to cleave
+during rupture (see Supplementary Movie S4).  Our previous
+work\cite{Fu2022_JFM} found the scaling $\mu \dot\gamma_* = K_{\text{I}}
+\gamma c^2/(\rho L^2)$ for vesicle BL in shear flow.
+
+The Results section showed that variations in free energy and strain
+generally depend on the distribution of fluid stresses i.e., shear
+versus TG flow. To further illustrate how fluid stresses interact with
+the geometry of the JP phases, we initialize a circular vesicle bilayer
+in various TG-flow cell sizes (Figure \ref{fig:PramChange}(b)--(e)). In
+all cases, the vesicle and TG flow reach a steady-state tank-treading
+motion, but the geometry and motion varies non-monotonically. For
+$\lambda$ ranging from $1$ nm to $4$ nm, the steady-state vesicle shape
+goes from an octagon, to a dimpled square, to a rounded diamond, to a
+rounded square. Surprisingly, the direction of rotation switches: for
+$\lambda = 2$ nm the rotation is clockwise, while for $\lambda = 4$ nm
+the rotation is counterclockwise. Finally, we calculate the vesicle area
+$A$ and length $L$. As shown in Figure~\ref{fig:PramChange}(f), the
+relative area $A/A_0$ achieves a steady-state that is greatest for
+$\lambda = 4$ nm yet least for $\lambda = 2$ nm. The relative length
+$L/L_0$, however, is constant in $t$ for all cell sizes
+(Figure~\ref{fig:PramChange}(e), inset). In other words, the flow
+pattern is non-monotonic in the cell size $\lambda$.
+
+We have excluded thermal fluctuations because they are unresolved in the
+JP phases we consider.  For a tensionless, planar membrane, the spectrum
+of the Fourier coefficients for the profile height 
 $h(\xx) = \sum_{\kk} h(\kk)e^{i \kk \cdot \xx}$ satisfy\cite{Merath2006FluctuationSO}  
@@
 \label{eq:fourier_spectrum}
-\langle |h(\kk)|^2 \rangle = \frac{\kbt}{L_xL_y}\frac{1}{\kappa k^4}
+\langle |h(\kk)|^2 \rangle = \frac{\kbt}{L_xL_y}\frac{1}{\kappa k^4},
 \end{equation}
-where $\xx$ is a point in an $L_x$ by $L_y$ rectangular membrane patch,
-$\kk = \left(2\pi m/L_x, 2\pi n/L_y\right)$ with
-$m, n = 0, \pm 1, \pm 2, \dots$ not both zero, and $\kappa$ is the membrane bending modulus.
+where $\xx$ is a point in an $L_x \times L_y$ rectangular membrane
+patch, $\kk = \left(2\pi m/L_x, 2\pi n/L_y\right)$ with $m,n \in
+\mathbb{Z}$, not both zero, and $\kappa$ is the membrane bending
+modulus.
 
@@
 vesicle in Figure \ref{fig:s2esummary}(e) 
-has arc length $L_x \approx 50$ nm. 
+has arclength $L_x \approx 50$ nm. 
 Our prior work\cite{Fu20,Fu2022_JFM} gave $\kappa  \approx 20$ $\kbt$.
@@
 \end{equation}
-For any moderate width, say $L_y > 4$ nm, the leading Fourier coefficient
-has an expected magnitude less than $1$ nm with the remaining coefficients
-dropping off to zero precipitously.  The expected amplitudes coming from thermal
-fluctuation are therefore negligible compared to particle size.
-The elastic
-moduli for the Type (II) and Type (III) phases are by greater by a factor of two
-and five, respectively, than for Type (I) (Figure \ref{fig:fsummary}(c)), making thermal fluctuation even more negligible in these cases.
-
-The fact that the fluctuation amplitudes are small 
-is not a consequence of stiffness. Quite the opposite, the value $\kappa = 20$ $\kbt$
-is in  agreement with the experimental literature where 
-micron sized vesicles observably fluctuate. 
-Rather, larger energies are required to fluctuate membranes 
-over smaller wavelengths and these energies exceed available 
-thermal energy when the wavelengths approach tens of nanometers
-as demonstrated above.
-
-The calculated viscosities---14 mPa s for Type I 
-and 21 mPa s for Type II JP phases---are physically reasonable.
-In two-dimensions, the Einstein viscosity correction 
-takes the form $1 + 2.0 \phi + 4.0\phi^2 + O(\phi^3)$
-in the volume fraction $\phi$
-\cite{PhysRevFluids.1.043301,Haines2011APO,Khair2006TheC,Brady1983TheEV}.
-For the JPs in Figure \ref{fig:s2esummary}(e)--(h), this volume fractions
-is about $0.5$ and would give a small viscosity $3$ mPa s.
-On the other hand, the Einstein correction is only valid for dilute
-suspensions, and for large volume fractions like $\phi = 0.5$, 
-one expects viscosities ten or more times that of water  
+For any moderate transverse depth, say $L_y > 4$ nm, the leading Fourier
+coefficient has a magnitude less than $1$ nm with the remaining
+coefficients dropping off to zero precipitously.  The expected
+amplitudes coming from thermal fluctuations are therefore negligible
+compared to particle size.  The elastic moduli for the Type II and
+Type III phases are greater by a factor of two and five, respectively,
+than for Type I (Figure~\ref{fig:fsummary}(c)), making thermal
+fluctuation even more negligible in these cases.
+
+The fact that the fluctuation amplitudes are small is not a consequence
+of stiffness. Quite the opposite, the value $\kappa = 20$ $\kbt$ agrees
+with the experimental literature where micron sized vesicles observably
+fluctuate.  Rather, larger energies are required to fluctuate membranes
+over smaller wavelengths and these energies exceed available thermal
+energy when the wavelengths approach tens of nanometers as demonstrated
+above.
+
+The calculated viscosities---14 mPa s for Type I and 21 mPa s for Type
+II JP phases---are physically reasonable.  In two-dimensional dilute
+suspensions, the Einstein viscosity correction is $1 + 2 \phi + 4\phi^2 +
+O(\phi^3)$, where $\phi \ll 1$ is the volume
+fraction~\cite{PhysRevFluids.1.043301, Haines2011APO, Khair2006TheC,
+Brady1983TheEV}. In Figures \ref{fig:s2esummary}(e)--(h), the volume
+fraction is $\phi \approx 0.5$, which would correspond to a effective
+shear viscosity of $4$ mPa s according to Einstein's viscosity
+correction. Note, however, that since $\phi = 0.5$ is outside of the
+dilute limit, one expects viscosities ten or more times that of water
 \cite{Konijn2014ExperimentalSO}.
 
-Nevertheless, further simulations results are required to 
-differentiate between purely suspension effects
-and particles' preferred alignments
-in analyzing viscosities from Figure \ref{fig:rheologysummary}. 
-For example, the difference between the values 14 mPa s for Type I and 
-21 mPa s for Type II JPs can be explained by the fact that 
-the multilamellar phase is more tightly packed than the bilayer phase
-(Figure \ref{fig:s2esummary}(e)--(h)).
-Furthermore, it seems that the viscosity, and the tendency toward
-shear thinning in the case of Type III JPs where viscosity is 
-effectively infinite for low strain rates 
-(Figure \ref{fig:rheologysummary}(c)), is related 
-to particle coordination.  
-To leading order, a single particle coordinates with: 
-one neighbor in the apposing bilayer for Type I, two neighbors
-at the tail and head interfaces for Type II, and four
-neighbors (front, back, left, and right) for Type III.
+Nevertheless, further simulations are required to differentiate between
+purely suspension effects and particles' preferred alignments. For
+example, the difference between the values 14 mPa s for Type I and 21
+mPa s for Type II JPs can be explained by the fact that the
+multilamellar phase is more tightly packed than the bilayer phase
+(Figure \ref{fig:s2esummary}(e)--(h)).  Furthermore, it seems that the
+viscosity, and the tendency toward shear thinning in the case of Type
+III JPs where viscosity is effectively infinite for low strain rates
+(Figure \ref{fig:rheologysummary}(c)), is related to particle
+coordination.  To leading order, a single particle coordinates with: one
+neighbor in the apposing bilayer for Type I, two neighbors at the tail
+and head interfaces for Type II, and four neighbors (front, back, left,
+and right) for Type III.
 
@@
 The boundary integral calculation
-of \ref{eq:free_energy2} relies
-on the following identiy 
+of \eqref{eq:free_energy2} relies
+on the following identity 
 %
@@
 \label{eq:normal_deriv}
-\nabla u(\xx) \cdot \nnu(\xx)=
+\nabla u(\xx) \cdot \nnu_\xx=
 %\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
@@
 %
-Here, $\tt(\xx)$ is the tangent vector and $\dif/\dif s$ is the
+Here, $\tt_\xx$ is the tangent vector and $\dif/\dif s$ is the
 arclength derivative.
@@
 into~\eqref{eq:free_energy2} for the normal derivative leads to the
-single layer, $\SS$, which is more straightforward to evaluate.
+single layer, $\SSS$, which is more straightforward to evaluate.
 The arclength derivative is computed using
-the spectrally accurate Fourier transform.
+the spectrally accurate Fourier differentiation.
 
@@
 be the single layer potential for a density function $\sigma.$ Fix $\xx
-\in {\partial \Omega}$, let $\nnu_{\xx} = \nnu(\xx)$ and $\nnu_{\yy}$ be the unit
+\in {\partial \Omega}$, let $\nnu_{\xx}$ and $\nnu_{\yy}$ be the unit
 normal at $\xx$, respectively $\yy$, in ${\partial \Omega}$, and let $\zz \in
@@
 since we can interchange $\nabla_\zz$ with $-\nabla_\yy$.
-Following~\citet{Hsiao2008}, \S 1.2,
+Following~\citet{Hsiao2008} (see \S 1.2),
 \begin{align}
@@
 %We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.
-We thank useful conversations with E. Corona, M. Rachh, S. Jiang, and Thomas Beck.
-B.Q.~acknowledges support from the Simons Foundation, Mathematics and Physical Sciences-Collaboration Grants for Mathematicians, Award No. 527139.
-Y.-N.Y.~acknowledges support from NSF (Grants No. DMS 1614863 and No. DMS 195160) and Flatiron Institute, part of Simons Foundation.
+We thank useful conversations with E.~Corona, M.~Rachh, S.~Jiang, and
+  T.~Beck.  B.Q.~acknowledges support from the Simons Foundation,
+  Mathematics and Physical Sciences-Collaboration Grants for
+  Mathematicians, Award No.~527139.  Y.-N.Y.~acknowledges support from
+  NSF (Grants No.~DMS 1614863 and No.~DMS 195160) and Flatiron
+  Institute, part of Simons Foundation.
 

### 2023-03-16 doc/PRF2022/PRF_main.tex
yuans edits to intro

@@
   Active colloidal systems with non-equilibrium self-organization is a
-  long-standing, challenging area in biology. To understand how
+  long-standing, challenging area in material sciences and biology. To understand how
   hydrodynamic flow may be used to actively control self-assembly of
-  Janus particles (JPs), we use a model recently developed for the
+  Janus particles (JPs), we developed  a model for the
   many-body hydrodynamics of amphiphilic JPs suspended in a viscous
-  background flow (JFM, 941, 2022). We investigate how various
-  morphologies arise from tuning the hydrophobic distribution of the
-  JP-solvent interface. We find JPs assembled into uni-lamella,
-  multi-lamella and striated structures. To introduce dynamics, we
-  include a linear shear flow and a steady Taylor-Green mixing flow, and
+  fluid with imposed far-field background flows (Journal of Fluid Mech., 941, 2022). 
+  In this work we alter the hydrophobic distribution on the JP-solvent
+  interface to investigate the hydrodynamics that underlies the various
+  morphologies and rheological properties of the JP assembly in the
+  suspension.
+  We find JPs assemble into uni-lamella,
+  multi-lamella, and striated structures. To introduce dynamics, we
+  include a planar linear shear flow and a steady Taylor-Green mixing flow, and
   measure the collective dynamics of JP particles in terms of their (a)
@@
 %\section{\label{}}
-Janus particles are colloids combining two dissimilar chemical or
-physical functionalities at their opposite
-sides~\cite{KirillovaMarschelkeSynytska2019}. Self-propelling Janus
+Janus particles are colloids with dissimilar chemical or
+physical functionalities between the two sides of their surfaces
+~\cite{deGennes1992,KirillovaMarschelkeSynytska2019}. Self-propelling Janus
 particles, for example, with a permanent biphasic asymmetry, have
 emerged as a rich chemical platform for the exploration of active
-matter~\cite{Meredithetal2022}.
+matter~\cite{Meredithetal2022} and mobility induced phase separation.
 In the absence of mobility and any
@@
 solve the ``inverse" problem of creating a model colloidal system that
-will self-assemble into a prescribed
-structure~\cite{PhysRevLett.128.256102}. For example, the framework of
+will self-assemble into prescribed
+structures~\cite{PhysRevLett.128.256102}. For example, the framework of
 geometrical frustration, which has been used to explain disordered
@@
 
-The surface of a Janus particle may have a dissimilar spatial
-distribution of hydrophobicity~\cite{doi:10.1021/la503455h}. The
-many-body hydrodynamics of amphiphilic Janus particles assembled as
-vesicles suspended in a viscous fluid in the inertialess regime (zero
+In this work we focus on collective hydrodynamics of immobile
+amphiphilic JPs in a
+viscous fluid under an imposed far-field flow. The amphiphilic JP has a
+hydrophobic surface on one side and a hydrophilic surface on the other
+side \cite{doi:10.1021/la503455h}.
+The many-body hydrodynamics of amphiphilic Janus particles assembled as
+vesicles (self-enclosed bilayers of JPs) suspended in a viscous fluid in the inertialess regime (zero
 Reynolds number) has been studied using boundary integral numerical
@@
 %
-In a quiescent flow, numerical simulations of a JP suspension showed
-self-assembly into micelles and bilayers of JPs that provide an
+In a quiescent flow, a JP suspension 
+self-assemble into micelles and bilayers of JPs that provide an
 alternative means for computing the mechanical moduli of a colloidal
-membrane~\cite{NaTr00, Fu20, KrFiGuKaHa13}. Under background flows, the
+membrane in numerical simulations~\cite{NaTr00, Fu20, KrFiGuKaHa13}. Under background flows, the
 hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
@@
 
-Molecular dynamics (MD) and Monte Carlo provide another avenue for
+Molecular dynamics (MD) and Monte Carlo simulations provide another avenue for
 simulating the interaction between JPs, solvents, and
 substrates~\cite{Brandner2019, Baniketal2021,
-HongCacciutoLuijtenGranick2008, C9NR05885K}. These methods often use
-pair-potentials to describe the interaction between JPs, for example by
+HongCacciutoLuijtenGranick2008, C9NR05885K}. In these methods 
+pair-potentials are used to describe the interaction between JPs, for example by
 prescribing angle dependent forces and torques that bring the
-hydrophobic sides of two amphiphilic JPs into opposition. The HAP
-formulation of the present work also has attractive, long-range forces
-and torques, but they are instead derived from a boundary value problem
+hydrophobic sides of two amphiphilic JPs into opposition. On the other
+hand, the HAP
+formulation of the present work has attractive, long-range forces
+and torques, and they are instead derived from a boundary value problem
 for the molecular structure of water~\cite{Ma77, GoHaKo94, ErLjCl89,
@@
 between a pair of JPs is affected by the presence of other particles. 
-
-\hl{Qi Wang has a preprint "A hybrid phase field method for fluid-structure interactions in viscous fluids"}.
-
-In this work, we take advantage of the flexibility of the HAP model to
-examine the effects of varying the distribution of hydrophobicity on JP
+As such, the HAP is a phase-field function that represents the
+properties of the solvent in the presence of JPs. Such approach falls
+into the category of work that considers particles as a discretization
+of a continuum problem~\cite{HongWang2021_arXiv}.
+
+%\hl{Qi Wang has a preprint "A hybrid phase field method for fluid-structure interactions in viscous fluids"}.
+
+Here we take advantage of the flexibility of the HAP model to
+examine the effects of tuning the distribution of hydrophobicity on JP
 surfaces. Such variation of the boundary condition on JP surfaces has
@@
 lines of investigation.
+
+This paper is organized as follows. \S~II summarizes the general
+mathematical formulation. \S~III describes the three types of
+hydrophobicity distribution that we use in the numerical simulations.
+\S~IV outlines the quantitative measures used to describe the collective
+hydrodynamics of JPs summarized and discussed in \S~V. \S~VI provides a
+conclusion and discussion for future directions.
 

### 2023-03-17 doc/PRF2022/PRF_main.tex
updated fig0, supplementary reference

@@
 and vertical directions, respectively.
+The shear flow replicates the motion of a fluid between two parallel,
+moving plates excluding wall effects.
+In TG flow, $\lambda$ controls the size of the
+$2\pi \lambda \times 2\pi \lambda$ TG cells.
+Throughout, we use $\lambda = 2$ nm
+so that the JP phases occupy about nine cells.
+
 In both cases, $\dot \gamma$ is the shear rate.
-In \eqref{eq:tg_flow}, $\lambda$ is the cell-size parameter.
+The flow rate $\lambda \dot \gamma$  
+was chosen so that \eqref{eq:tg_flow} has the same
+rate of viscous dissipation per area as for \eqref{eq:sh_flow}.
+In other words, 
+$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ 
+is the same for 
+$\uu = \uu_{\infty}^{\text{sh}}$ as for 
+$\uu = \uu_{\infty}^{\text{TG}}$
+when integrated over a $TG$ cell $A$.
 
@@
 
-The shear flow replicates the motion of a fluid between two parallel, moving plates
-excluding wall effects.  In TG flow, the flow pattern
-consists of an array of counter rotating cells each with size 
-$2\pi \lambda \times 2\pi \lambda$.  Throughout, we use $\lambda = 2$ nm
-so that the JP phases occupy about nine cells.  To compare shear
-on equal terms, the flow rate $\lambda \dot \gamma$  
-was chosen for \eqref{eq:tg_flow} so that it has the same
-rate of viscous dissipation per area as for \eqref{eq:sh_flow}.
-In other words, 
-$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ 
-is the same for 
-$\uu = \uu_{\infty}^{\text{sh}}$ as for 
-$\uu = \uu_{\infty}^{\text{TG}}$
-when integrated over a $TG$ cell $A$.
-
 For initial data, the steady-state Type I amphiphiles phase
@@
 the region near the JP phases, the fluid velocity $\uu$ and 
-order parameter $u$ are solved for in all of $\mathbb{R}^2$.
+order parameter $u$ are accounted for in all of $\mathbb{R}^2$.
 Moreover, $\uu$ satisfies the rigid boundary condition at 
@@
 
-The simulation setup consisted of placing each of the three JP phases
-in either a shear or TG background flow and then solving for the 
-particle trajectories in time.  A total of $500$ steps were solved
-for with $\Delta t = 2$ ns, yielding time courses for various 
-$\dot \gamma$ up to $T = 1$ $\upmu$s.  We then post-processed the trajectories
-to infer free energy $F$, alignment order $S_2$, and strain $E$.     
-\todo[inline]{Reference the supplementary material here.}
+The simulation setup consisted of placing each of the 
+phases in either a shear or TG background flow and then solving for the 
+particle trajectories in time. In each setup, we solved for $500$ time steps 
+with $\Delta t = 2$ ns, yielding time courses for $t \in [0, T]$, $T = 1$ $\upmu$s.
+We then post-processed the trajectories.
+
+Supplementary Figures~\ref{fig:veshraw}--\ref{fig:sttgraw}
+contain the fully-resolved time courses for free energy $F$,
+alignment order $S_2$, and strain $E$. The eight setups
+correspond to the four JP phases---bilayer, vesicle BL, multilamellar,
+and striated---and two background flows---shear and TG,
+and the data are plotted with the same ordinate to facilitate
+comparisons between simulation setups.  Each setup considers
+a range of shear rates $\dot \gamma$ in the interval $[0, 0.2]$ ns$^{-1}$.
+
+The fully-resolved time courses
+in Supplementary Figures~\ref{fig:veshraw}--\ref{fig:sttgraw}
+contain significant oscillations due to the particle-based formulation
+and tumbling inherent to the background flows.  To extract meaningful
+data, we further postprocessed the $F$, $S_2$, $E$ curves by taking
+their time averate over the interval $t \in [0, T]$.
 
 \subsection{Strain and alignment}
+\label{sec:strain-alignment}
 The plots reveal highly distinct material responses from each phase.
@@
 \subsection{Free energy}
+\label{sec:free-energy}
 Figure \ref{fig:fsummary} plots the time-averaged
@@
 \end{figure}
+
 \subsection{Rheology}
+\label{sec:rheology}
 So far, we have considered static material properties, namely

### 2023-03-17 doc/PRF2022/Supplementary.tex
updated fig0, supplementary reference

--- 2022-08-05 doc/PRF2022/Supplementary.tex
@@
 
-\sloppy
 \section{Movie Captions}\mbox{} \\
@@
 pulled apart by the background flow.
+
+\section{Raw Data}
+The following figures plot the fully resolved simulation time-courses
+organized in terms of the bilayer, vesicle BL, multilamellar, and striated JP phases
+under shear flow (Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:stshraw})
+and under TG flow (Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
+Throughout, panels (a) are for relative free energy $F - F_0$,
+panels (b) for alignment $S_2$, and panels (c) for strain $E$ (as a percentage). 
+A common ordinate is used for each of the respective panels to facilitate
+comparison between data sets. 
+\newpage
+
+\begin{figure}[h!]
+\begin{center}
+\textbf{\textsc{Shear Flow cases}}\par\medskip
+\textbf{Type I, bilayer phase under shear flow}\par\medskip
+\includegraphics[width=\textwidth]{SMFigures/ULShRaw.pdf}
+\end{center}
+\caption{
+Relative free energy $F - F_0$,
+alignment $S_2$, and strain $E$ for
+Type I, bilayer phase under shear flow with choices of shear rates $\dot\gamma=0.013$ -- $0.075$ ns$^{-1}$.
+%The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:ulshraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\textbf{Type I, vesicle BL phase under shear flow}\par\medskip
+\includegraphics[width=\textwidth]{SMFigures/VeShRaw.pdf}
+\end{center}
+\caption{
+Relative free energy $F - F_0$,
+alignment $S_2$, and strain $E$ for
+Type I, bilayer phase under shear flow with choices of shear rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.
+The JP type is the same as for Supplementary Figure \ref{fig:ulshraw} but with a
+ring-shaped, rather than disordered, bilayer for initial configuration.  
+%A Vesicle under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.075$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:veshraw}
+\end{figure}
+
+\begin{figure}[h!]
+\textbf{Type II, multilamellar phase under shear flow}\par\medskip
+\begin{center}
+\includegraphics[width=\textwidth]{SMFigures/MLShRaw.pdf}
+\end{center}
+\caption{
+Relative free energy $F - F_0$,
+alignment $S_2$, and strain $E$ for
+Type II, multilamellar phase under shear flow with choices of shear rates $\dot\gamma=0.025$ -- $0.075$ ns$^{-1}$.
+%A multilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.025\sim0.075$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:mlshraw}
+\end{figure}
+
+\begin{figure}[h!]
+\textbf{Type III, striated phase under shear flow}\par\medskip
+\begin{center}
+\includegraphics[width=\textwidth]{SMFigures/StShRaw.pdf}
+\end{center}
+\caption{
+Relative free energy $F - F_0$,
+alignment $S_2$, and strain $E$ for
+Type III, striated phase under shear flow with choices of shear rates $\dot\gamma=0.01$ -- $0.07$ ns$^{-1}$.
+%A striated JP structure under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.07$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:stshraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\textbf{\textsc{TG Flow Cases}}\par\medskip
+\textbf{Type I, bilayer  phase under TG flow}\par\medskip
+\includegraphics[width=\textwidth]{SMFigures/ULTGRaw.pdf}
+\end{center}
+\caption{
+Relative free energy $F - F_0$,
+alignment $S_2$, and strain $E$ for
+Type I, bilayer phase under TG flow with choices of shear rates $\dot\gamma=0.013$ -- $0.05$ ns$^{-1}$.
+%A unilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.013\sim0.05$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:ultgraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\textbf{Type I, vesicle BL phase under TG flow}\par\medskip
+\includegraphics[width=\textwidth]{SMFigures/VeTGRaw.pdf}
+\end{center}
+\caption{
+Relative free energy $F - F_0$,
+alignment $S_2$, and strain $E$ for
+Type I, vesicle bilayer phase under TG flow with choices of shear rates $\dot\gamma=0.005$ -- $0.044$ ns$^{-1}$.
+The JP type is the same as for Supplementary Figure \ref{fig:ultgraw} but with a
+ring-shaped, rather than disordered, bilayer for initial configuration.  
+%A vesicle JP structure under a TG flow with choices of shear rates $\dot\gamma=0.005\sim0.044$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:vetgraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\textbf{Type II, multilamellar phase under TG flow}\par\medskip
+\includegraphics[width=\textwidth]{SMFigures/MLTGRaw.pdf}
+\end{center}
+\caption{
+Relative free energy $F - F_0$,
+alignment $S_2$, and strain $E$ for
+Type II, multilamellar phase under TG flow with choices of shear rates $\dot\gamma=0.025$ -- $0.069$ ns$^{-1}$.
+%A multilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.025\sim0.069$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:mltgraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\textbf{Type III, striated phase under TG flow}\par\medskip
+\includegraphics[width=\textwidth]{SMFigures/StTGRaw.pdf}
+\end{center}
+\caption{
+Relative free energy $F - F_0$,
+alignment $S_2$, and strain $E$ for
+Type III, striated phase under TG flow with choices of shear rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.
+%A striated JP structure under a TG flow with choices of shear rates $\dot\gamma=0.01\sim0.069$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:sttgraw}
+\end{figure}

### 2023-03-17 doc/PRF2022/PRF_main.tex

@@
 %RJR: In the above sentence, suspection and immersed are redundant 
-The JPs are disks of radius $c$ suspended in a viscous solvent
-with center $\aa_i$, and orientation $\theta_i$
-relative to the horizontal axis, where $i = 1, \ldots, N_b$ and $N_b$ is
-the number of particles. The domain $\Omega \subset \mathbb{R}^2$ is
-the solvent phase and $t$ is time. The boundary of $\Omega$ is
-$\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where $\Gamma_i$
-is the boundary of Janus particle $i$.
+The JPs are disks of radius $c$ suspended in a viscous solvent with
+center $\aa_i$, and orientation $\theta_i$ relative to the horizontal
+axis, where $i = 1, \ldots, N_b$, and $N_b$ is the number of particles.
+The domain $\Omega \subset \mathbb{R}^2$ is the solvent phase and $t$ is
+time. The boundary of $\Omega$ is $\bd\Omega = \Gamma_1 \cup \cdots \cup
+\Gamma_{N_b}$, where $\Gamma_i$ is the boundary of Janus particle $i$.
 The sets $\Omega$, $\Gamma_1$, \dots, and $\Gamma_{N_b}$ depend on $t$.
-Assuming inertial terms are negligible, the solvent satisfies the Stokes equations
+Assuming inertial terms are negligible, the solvent satisfies the Stokes
+equations
 \begin{alignat}{3}
@@
 \mathbf{T} = \gamma \left[ \rho^{-1} u^2 \mathbf{I}
-  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
+  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
 \end{align}
-is the second-order hydrophobic stress tensor.
-Repulsion is rotationally symmetric and
-does not enter $T_i$.
+is the second-order hydrophobic stress tensor. Repulsion is
+rotationally symmetric and does not enter $T_i$.
 
@@
 
-To perform a single time step, we
-(i) solve~\eqref{eq:SL}--\eqref{eq:SLbc} for $u$,
-(ii) compute the force and torque~\eqref{eq:FandTdef},
-and (iii) solve the Stokes equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield}
-subject to~\eqref{eq:rigid-vel} and \eqref{eq:force}. 
-The velocities $(\vv_i, \omega_i)$ obtained
-from~\eqref{eq:rigid-vel} are used to update the
-particle positions and orientations
-using the second-order Adams-Bashforth scheme
-with time step size $\Delta t.$
-
-The interactions
-generated by the HAP-mobility problem formulation
-\eqref{eq:stokes}--\eqref{eq:force} lead to particle self-assembly.
-In terms of scaling, $\rho$ sets the effective distance of the hydrophobic
-interactions; $\rho_0$ determines the distance where attraction and repulsion are in
-balance i.e. smaller values of $\rho_0$ lead to more compact particle assemblies.
-The rate of self-assembly are proportional to tension $\gamma$,
-inversely proportional to viscosity $\mu$, and
+To perform a single time step, we (i)
+solve~\eqref{eq:SL}--\eqref{eq:SLbc} for $u$, (ii) compute the force and
+torque~\eqref{eq:FandTdef}, and (iii) solve the Stokes
+equations~\eqref{eq:stokes}--\eqref{eq:stokesFarfield} subject
+to~\eqref{eq:rigid-vel} and \eqref{eq:force}. The velocities $(\vv_i,
+\omega_i)$ obtained from~\eqref{eq:rigid-vel} are used to update the
+particle positions and orientations using the second-order
+Adams-Bashforth scheme with time step size $\Delta t.$
+
+The interactions generated by the HAP-mobility problem formulation
+\eqref{eq:stokes}--\eqref{eq:force} lead to particle self-assembly. In
+terms of scaling, $\rho$ sets the effective distance of the hydrophobic
+interactions; $\rho_0$ determines the distance where attraction and
+repulsion are in balance i.e. smaller values of $\rho_0$ lead to more
+compact particle assemblies. The rate of self-assembly is proportional
+to tension $\gamma$, inversely proportional to viscosity $\mu$, and
 approximately inversely proportional to $\rho$~\cite{Fu20}.
@@
 \subsection{Boundary integral representations}
-We require a method to accurately solve the Stokes and
-screened Laplace equations in intricate, unbounded geometries.
-We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
+We require a method to accurately solve the Stokes and screened Laplace
+equations in intricate, unbounded geometries.  This is done by
+recasting~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
 and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
-and discretize each BIE at $N$ points on each of the $N_b$ particles
+and discretizing each BIE at $N$ points on each of the $N_b$ particles
 with a collocation method. To express the solution of
-\eqref{eq:SL}--\eqref{eq:SLbc},
-we adopt the double layer potential
+\eqref{eq:SL}--\eqref{eq:SLbc}, we adopt the double-layer potential
 \begin{align}

### 2023-03-18 doc/PRF2022/PRF_main.tex
fixed up BIE section

@@
 where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
-solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
+solution of the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
 zeroth-order modified Bessel function of the second kind, $\nnu_\yy$ is
-the unit outward normal at $\yy$, and $\eta$ is a scalar-valued
-density function. The subscript in $\dif s_\yy$ denotes integration with
-respect to $\yy \in \partial \Omega$. To satisfy the boundary
-condition~\eqref{eq:SLbc}, the density function must satisfy\cite{Hsiao2008}
+the unit outward normal at $\yy$, and $\eta$ is a scalar-valued density
+function. The subscript in $\dif s_\yy$ denotes integration with respect
+to $\yy \in \partial \Omega$. To satisfy the boundary
+condition~\eqref{eq:SLbc}, the density function must
+satisfy~\cite{Hsiao2008}
 \begin{align}
@@
 After discretizing and applying quadrature, the result is an $NN_b
-\times NN_b$ and $2NN_b \times 2NN_b$ linear system
+\times NN_b$ and $(2N+3)N_b \times (2N+3)N_b$ linear system
 for~\eqref{eq:SL_BIE2}
 and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
-These are solved with matrix-free GMRES
-and the second-kind BIEs
-guarantee that the number of GMRES iterations is
-mesh-independent.
+These are solved with matrix-free GMRES and the second-kind BIEs
+guarantee that the number of GMRES iterations is mesh-independent.
 

### 2023-03-21 doc/PRF2022/PRF_main.tex
peter updated s.m.

@@
 $\uu = \uu_{\infty}^{\text{TG}}$
-when integrated over a $TG$ cell $A$.
+when integrated over a TG cell $A$.
 
@@
 
-Supplementary Figures~\ref{fig:veshraw}--\ref{fig:sttgraw}
+Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}
 contain the fully-resolved time courses for free energy $F$,
@@
 The fully-resolved time courses
-in Supplementary Figures~\ref{fig:veshraw}--\ref{fig:sttgraw}
+in Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}
 contain significant oscillations due to the particle-based formulation
@@
 data, we further postprocessed the $F$, $S_2$, $E$ curves by taking
-their time averate over the interval $t \in [0, T]$.
+their time average over the interval $t \in [0, T]$.
 
@@
 making systematic fitting challenging (see 
-Supplementary Material Figures \ref{fig:veshraw}--\ref{fig:sttgraw}). 
+Supplementary Material Figures \ref{fig:ulshraw}--\ref{fig:sttgraw}). 
 The integral in \eqref{eq:strainrate} averages out these oscillations

### 2023-03-21 doc/PRF2022/Supplementary.tex
peter updated s.m.

@@
 shear flow. For the choices of the shear rate, we pick: $\dot\gamma =
-0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, $\dot\gamma
-= 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated
+0.05$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.05$ ns$^{-1}$ for the bilayer, $\dot\gamma
+= 0.05$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.1$ ns$^{-1}$ for the striated
 configurations. The vesicle case undergoes tank-treading whereas the
@@
 Taylor-Green flow at low flow rates. For the choices of the flow
-strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the
-disordered bilayer, $V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$
+strength, we pick: $\dot\gamma = 0.05$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.05$ ns$^{-1}$ for the
+disordered bilayer, $\dot\gamma = 0.05$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.1$ ns$^{-1}$
 for the striated configurations. The vesicle stays inact, whereas the
@@
 shear flow at a higher shear rate. For the choices of the shear rate, we
-pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ for the
-bilayer, $\dot\gamma = 0.15$ for the multi-lamellar, and $\dot\gamma =
-0.15$ for the striated configurations. The time step of all simulations
-is $\Delta t=0.2$. In this movie, some clear structural ruptures occur
+pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ ns$^{-1}$ for the
+bilayer, $\dot\gamma = 0.15$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma =
+0.15$ ns$^{-1}$ for the striated configurations. The time step of all simulations
+is $\Delta t=0.2$ ns$^{-1}$. In this movie, some clear structural ruptures occur
 in each case. In order to observe the structure behaviors at later time,
@@
 Taylor-Green flow at higher flow rates. For the choices of the flow
-strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the
-bilayer, $V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the
+strength, we pick: $\dot\gamma = 0.1$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.1$ ns$^{-1}$ for the
+bilayer, $\dot\gamma = 0.1$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.15$ ns$^{-1}$ for the
 striated configurations. Clear structural ruptures occur in each case.
@@
 pieces, the main body of the BC (ii) and BC (iii) assemblies are not
-pulled apart by the background flow.
+pulled apart by the background flow.\\
+
+\noindent
+{\bf Movie S6. Single Vesicle in a Taylor-Green Flow with Various $\lambda$ Values} 
+The parameter $\lambda$ controls the cell size in Taylor-Green flow. 
+$\lambda$ values are varied from 1.0 to 4.0 while the flow rate $\lambda\dot\gamma=0.1$ is fixed.
+There is a rotation transition from counterclockwise ($\lambda=1$ nm and  2 nm) to clockwise ($\lambda=3$ nm and 4 nm).
+\\
 
@@
 comparison between data sets. 
-\newpage
+%\newpage
 

### 2023-03-21 doc/PRF2022/PRF_main.tex
read up to start of Sec V

@@
   Active colloidal systems with non-equilibrium self-organization is a
-  long-standing, challenging area in material sciences and biology. To understand how
-  hydrodynamic flow may be used to actively control self-assembly of
-  Janus particles (JPs), we developed  a model for the
+  long-standing, challenging area in material sciences and biology. To
+  understand how hydrodynamic flow may be used to actively control
+  self-assembly of Janus particles (JPs), we developed a model for the
   many-body hydrodynamics of amphiphilic JPs suspended in a viscous
-  fluid with imposed far-field background flows (Journal of Fluid Mech., 941, 2022). 
-  In this work we alter the hydrophobic distribution on the JP-solvent
-  interface to investigate the hydrodynamics that underlies the various
-  morphologies and rheological properties of the JP assembly in the
-  suspension.
-  We find JPs assemble into uni-lamella,
-  multi-lamella, and striated structures. To introduce dynamics, we
-  include a planar linear shear flow and a steady Taylor-Green mixing flow, and
-  measure the collective dynamics of JP particles in terms of their (a)
-  free energy from the hydrophobic interactions between the JPs, (b)
-  order parameter for the ordering of JPs in terms of alignment of their
-  directors, and (c) strain parameter that captures the deformation in
-  the assembly. We characterize the effective material properties of the
-  JP structures and find that the uni-lamellar structures increases
-  orientation order under shear flow, the multilamellar structure
-  behaves as a shear thinning fluid, and the striated structure
-  possesses a yield stress. These numerical results provide insights
-  into dynamic control of non-equilibrium active biological systems with
-  similar self-organization.
+  fluid with imposed far-field background flows (Journal of Fluid
+  Mechanics, 941, 2022). In this work we alter the hydrophobic
+  distribution on the JP-solvent interface to investigate the
+  hydrodynamics that underlies the various morphologies and rheological
+  properties of the JP assembly in the suspension. We find JPs assemble
+  into uni-lamella, multi-lamella, and striated structures. To introduce
+  dynamics, we include a planar linear shear flow and a steady
+  Taylor-Green mixing flow, and measure the collective dynamics of JP
+  particles in terms of their (a) free energy from the hydrophobic
+  interactions between the JPs, (b) order parameter for the ordering of
+  JPs in terms of alignment of their directors, and (c) strain parameter
+  that captures the deformation in the assembly. We characterize the
+  effective material properties of the JP structures and find that the
+  uni-lamellar structures increases orientation order under shear flow,
+  the multilamellar structure behaves as a shear thinning fluid, and the
+  striated structure possesses a yield stress. These numerical results
+  provide insights into dynamic control of non-equilibrium active
+  biological systems with similar self-organization.
 \end{abstract}
@@
 %\section{\label{}}
-Janus particles are colloids with dissimilar chemical or
-physical functionalities between the two sides of their surfaces
-~\cite{deGennes1992,KirillovaMarschelkeSynytska2019}. Self-propelling Janus
-particles, for example, with a permanent biphasic asymmetry, have
-emerged as a rich chemical platform for the exploration of active
+Janus particles (JPs) are colloids with dissimilar chemical or physical
+functionalities between the two sides of their surfaces
+~\cite{deGennes1992,KirillovaMarschelkeSynytska2019}. Self-propelling
+JPs, for example, with a permanent biphasic asymmetry, have emerged as a
+rich chemical platform for the exploration of active
 matter~\cite{Meredithetal2022} and mobility induced phase separation.
-In the absence of mobility and any
-imposed flow, Janus particles (JPs) self-assemble
-into oligomers of various geometries
-and sizes
-depending on the interactions between JPs and the 
-viscous solvent~\cite{Bradley2017, KangHonciuc2018,
-HongCacciutoLuijtenGranick2008},
-with tunable functions for biomedical engineering
-applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
+In the absence of mobility and any imposed flow, JPs self-assemble into
+oligomers of various geometries and sizes depending on the interactions
+between JPs and the viscous solvent~\cite{Bradley2017, KangHonciuc2018,
+HongCacciutoLuijtenGranick2008}, with tunable functions for biomedical
+engineering applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
 LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale,
@@
 long-standing challenge in fluid mechanics and material science is to
-solve the ``inverse" problem of creating a model colloidal system that
+solve the ``inverse'' problem of creating a model colloidal system that
 will self-assemble into prescribed
@@
 %
-In a quiescent flow, a JP suspension 
-self-assemble into micelles and bilayers of JPs that provide an
-alternative means for computing the mechanical moduli of a colloidal
-membrane in numerical simulations~\cite{NaTr00, Fu20, KrFiGuKaHa13}. Under background flows, the
-hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
-many familiar behaviors of a vesicle: elongation and alignment along the
-extensional direction, tank-treading, and rupture of a vesicle under
-shear flow~\cite{Fu2022_JFM, grandmaison_brancherie_salsac_2021,
+In a quiescent flow, a JP suspension self-assembles into micelles and
+bilayers of JPs that provide an alternative means for computing the
+mechanical moduli of a colloidal membrane in numerical
+simulations~\cite{NaTr00, Fu20, KrFiGuKaHa13}. Under background flows,
+the hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs)
+exhibit many familiar behaviors of a vesicle: elongation and alignment
+along the extensional direction, tank-treading, and rupture of a vesicle
+under shear flow~\cite{Fu2022_JFM, grandmaison_brancherie_salsac_2021,
 D2SM00179A,keller_skalak_1982, Finken08, Shaqfeh11}.
 
-Molecular dynamics (MD) and Monte Carlo simulations provide another avenue for
-simulating the interaction between JPs, solvents, and
+Molecular dynamics (MD) and Monte Carlo simulations provide another
+avenue for simulating the interaction between JPs, solvents, and
 substrates~\cite{Brandner2019, Baniketal2021,
 HongCacciutoLuijtenGranick2008, C9NR05885K}. In these methods
-pair-potentials are used to describe the interaction between JPs, for example by
-prescribing angle dependent forces and torques that bring the
+pair-potentials are used to describe the interaction between JPs, for
+example by prescribing angle dependent forces and torques that bring the
 hydrophobic sides of two amphiphilic JPs into opposition. On the other
-hand, the HAP
-formulation of the present work has attractive, long-range forces
-and torques, and they are instead derived from a boundary value problem
-for the molecular structure of water~\cite{Ma77, GoHaKo94, ErLjCl89,
-Lietal05, Israelachvili80}. Unlike in MD or Monte Carlo simulations, the
-HAP interactions are nonadditive~\cite{Fu20}, so that the interactions
-between a pair of JPs is affected by the presence of other particles. 
-As such, the HAP is a phase-field function that represents the
-properties of the solvent in the presence of JPs. Such approach falls
-into the category of work that considers particles as a discretization
-of a continuum problem~\cite{HongWang2021_arXiv}.
+hand, the HAP formulation of the present work has attractive, long-range
+forces and torques, and they are instead derived from a boundary value
+problem for the molecular structure of water~\cite{Ma77, GoHaKo94,
+ErLjCl89, Lietal05, Israelachvili80}. Unlike in MD or Monte Carlo
+simulations, the HAP interactions are nonadditive~\cite{Fu20}, so that
+the interactions between a pair of JPs is affected by the presence of
+other particles.  As such, the HAP is a phase-field function that
+represents the properties of the solvent in the presence of JPs. Such
+approach falls into the category of work that considers particles as a
+discretization of a continuum problem~\cite{HongWang2021_arXiv}.
 
@@
 
-Here we take advantage of the flexibility of the HAP model to
-examine the effects of tuning the distribution of hydrophobicity on JP
-surfaces. Such variation of the boundary condition on JP surfaces has
-been realized experimentally by using chemicals to adjust the polarity
-of the viscous solvent~\cite{Zarzaretal2015,
-KirillovaMarschelkeSynytska2019, doi:10.1021/la503455h}. We show that a
-simple tuning of the hydrophobic distribution leads to transitions from
-unilamellar to multilamellar or striated superstructures of JPs.
-Focusing on the fluid-structure interactions that correspond to such
-transitions, we investigate the deformation of these novel structures in
-background flows and map out their collective behavior away from
-equilibrium. Looking forward, including other fields like electric
-potential for JPs synthesized with charged
-polymers~\cite{HongCacciutoLuijtenGranick2008, doi:10.1021/la503455h,
-KangHonciuc2018}, is straightforward within the context of the boundary
-integral representations~\cite{kohl-cor-che-vee22}, opening further
-lines of investigation.
-
-This paper is organized as follows. \S~II summarizes the general
-mathematical formulation. \S~III describes the three types of
+Here we take advantage of the flexibility of the HAP model to examine
+the effects of tuning the distribution of hydrophobicity on JP surfaces.
+Such variation of the boundary condition on JP surfaces has been
+realized experimentally by using chemicals to adjust the polarity of the
+viscous solvent~\cite{Zarzaretal2015, KirillovaMarschelkeSynytska2019,
+doi:10.1021/la503455h}. We show that a simple tuning of the hydrophobic
+distribution leads to transitions from unilamellar to multilamellar or
+striated superstructures of JPs. Focusing on the fluid-structure
+interactions that correspond to such transitions, we investigate the
+deformation of these novel structures in background flows and map out
+their collective behavior away from equilibrium. Looking forward,
+including other fields like electric potential for JPs synthesized with
+charged polymers~\cite{HongCacciutoLuijtenGranick2008,
+doi:10.1021/la503455h, KangHonciuc2018}, is straightforward within the
+context of the boundary integral
+representations~\cite{kohl-cor-che-vee22}, opening further lines of
+investigation.
+
+This paper is organized as follows. \S~\ref{sec:governing_equations}
+summarizes the general mathematical formulation.
+\S~\ref{sec:tunable_hydrophobicity} describes the three types of
 hydrophobicity distribution that we use in the numerical simulations.
-\S~IV outlines the quantitative measures used to describe the collective
-hydrodynamics of JPs summarized and discussed in \S~V. \S~VI provides a
-conclusion and discussion for future directions.
+\S~\ref{sec:measuring_deformation} outlines the quantitative measures
+used to describe the collective hydrodynamics of JPs summarized and
+discussed in \S~\ref{sec:results}. Finally, \S~\ref{sec:conclusion}
+provides a conclusion and discussion for future directions.
 
@@
 \section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
-The governing equations are a system for the position and
-orientation of a collection of rigid JPs~\cite{Fu2022_JFM}.
-We first pose the
-Stokes equations for the mobility problem giving the hydrodynamic
-interactions for the particle suspension. The hydrophobic forces come
-from solving a screened Laplace equation. Particle collisions are
-avoided through a near-field, pair potential.
+\label{sec:governing_equations}
+The governing equations are a system for the position and orientation of
+a collection of rigid JPs~\cite{Fu2022_JFM}. We first pose the Stokes
+equations for the mobility problem giving the hydrodynamic interactions
+for the particle suspension. The hydrophobic forces come from solving a
+screened Laplace equation. Particle collisions are avoided through a
+near-field, pair potential.
 
@@
 \end{align}
-where $u(\xx,t)$ is as the order parameter for water\cite{Ma77, GoHaKo94},
-$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
-The order parameter $u(\xx,t)$ is assumed to minimize the free energy
-$F$ and therefore satisfies the screened Laplace boundary value problem
+where $u(\xx,t)$ is as the order parameter for water~\cite{Ma77,
+GoHaKo94}, $\rho$ is a decay length, and $\gamma$ is an interfacial
+tension. The order parameter $u(\xx,t)$ is assumed to minimize the free
+energy $F$ and therefore satisfies the screened Laplace boundary value
+problem
 \begin{gather}
@@
 The boundary condition $g$ encodes hydrophobic properties of the
-particle-solvent interface.
-The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
-\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for
-$s \geq 1$. The parameter $\rho_0$ is the distance 
-below which steric repulsion becomes important and 
-$M$ is the repulsion modulus.
-
-Letting $\nnu$ be the particle outward normal,
-the force $\FF_i$ and torque $T_i$ coming from the free energy
-acting on $\Gamma_i$ are~\cite{Fu20}
+particle-solvent interface.  The dimensionless repulsion profile takes
+the form $P(s) = 1 - \sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$
+for $s \geq 1$. The parameter $\rho_0$ is the distance below which
+steric repulsion becomes important and $M$ is the repulsion modulus.
+
+Letting $\nnu$ be the particle outward normal, the force $\FF_i$ and
+torque $T_i$ coming from the free energy acting on $\Gamma_i$
+are~\cite{Fu20}
 %from the
@@
 \end{alignat}
-for $\xx \in \Gamma_i$ and $i = 1,\ldots,N_b$.
-%Equation~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} does have a
-%unique solution, but we note that
-Alternative full-rank layer potential
-representations for rigid body motions are possible~\cite{rac-gre2016,
-cor-gre-rac-vee2017}.
+for $\xx \in \Gamma_i$ and $i = 1,\ldots,N_b$. Alternative full-rank
+layer potential representations for rigid body motions are
+possible~\cite{rac-gre2016, cor-gre-rac-vee2017}.
 
@@
 and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
-These are solved with matrix-free GMRES and the second-kind BIEs
-guarantee that the number of GMRES iterations is mesh-independent.
+These are solved with matrix-free GMRES and the second-kind nature of
+the BIEs guarantees that the number of GMRES iterations is
+mesh-independent.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Tunable hydrophobicity}
 \label{sec:tunable_hydrophobicity}
-The parameters are modeled after those for
-phospholipid in water~\cite{Boal}.
-We use $\mu = 1$~mPa~s for the viscosity of water
-at room temperature. Pure lipid components give a range of interfacial
-tensions~\cite{KUZMIN2005, Petelska2012,Jackson2016, GarciaSaez}; $0.7$--$5.3$~pN~nm$^{-1}$.
-We use $\gamma=4.1$~pN~nm$^{-1}$ which gives a physically reasonable 
-elastic modulus $\kappa$ of lipid bilayers~\cite{Fu20,Fu2022_JFM}.
-The particle radius $c = 1.25$~nm represents one half 
-of phospholipid length~\cite{Boal}, and the screening length $\rho = 5$~nm
-derives from experimental force-distance measurements of hydrophobic
-attraction~\cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}. 
-A repulsion modulus $M = 2$~pN and 
+The parameters are modeled after those for phospholipid in
+water~\cite{Boal}. We use $\mu = 1$~mPa~s for the viscosity of water at
+room temperature. Pure lipid components give a range of interfacial
+tensions~\cite{KUZMIN2005, Petelska2012,Jackson2016, GarciaSaez};
+$0.7$--$5.3$~pN~nm$^{-1}$. We use $\gamma=4.1$~pN~nm$^{-1}$ which gives
+a physically reasonable elastic modulus $\kappa$ of lipid
+bilayers~\cite{Fu20, Fu2022_JFM}. The particle radius $c = 1.25$~nm
+represents one half of phospholipid length~\cite{Boal}, and the
+screening length $\rho = 5$~nm derives from experimental force-distance
+measurements of hydrophobic attraction~\cite{ErLjCl89, Lietal05,
+Israelachvili80, Jackson2016}. A repulsion modulus $M = 2$~pN and
 distance $\rho_0 = 0.5$~nm gives an interparticle distance around one
 particle radius, ensuring the accuracy of the boundary integral
-representations~\eqref{eq:SL_BIE} and~\eqref{eq:velocity} without 
-overly aggressive mesh refinement. The characteristic time
-and length are $1$~ns and  $1$~nm, respectively.
+representations~\eqref{eq:SL_BIE} and~\eqref{eq:velocity} without overly
+aggressive mesh refinement. The characteristic time and length are
+$1$~ns and $1$~nm, respectively.
 
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Boundary conditions and equilibrium configurations}
-The boundary condition $g(\xx)$ in
-\eqref{eq:SLbc} defines the spatial distribution of
-hydrophobicity and hydrophilicity.
-Referring to Figure \ref{fig:boundary_conditions},
+The boundary condition $g(\xx)$ in \eqref{eq:SLbc} defines the spatial
+distribution of hydrophobicity and hydrophilicity.  Referring to Figure
+\ref{fig:boundary_conditions}, we let
 \begin{align}
@@
 where $\alpha$ is the angle between the vector $\xx - \aa_i$ and the
-particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$
-The scalar $b$ shifts the periodic date up and down and the scalar
-$a$ normalizes $g$ so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
-The side of the particle where
-$\alpha = 0$ is called the tail and the side where $\alpha = \pi$ is the head.
-
-Based on the choice of $b$,
-the boundary condition (BC) \eqref{eq:bc-type}
-can be classified into one of three categories:
-Type I, amphiphile, $b = 1$, $g$ is positive on 
-one side representing a hydrocarbon-water interface, and
-is zero on the other representing an apolar, hydrophilic region;
-Type II, asymmetric hydrophobe, $b = 2$, $g$ is positive
-on both sides but more so on one side;
-Type III, polar, $b = 0$, $g$ is positive on one
-side and negative on the other, representing a
-water structure with positive/negative charge~\cite{MaRa76, Ma77}.
+particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$.  The scalar
+$b$ shifts the periodic date up and down and the scalar $a$ normalizes
+$g$ so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$. The side of the
+particle where $\alpha = 0$ is called the tail and the side where
+$\alpha = \pi$ is the head.
+
+Based on the choice of $b$, the boundary condition (BC)
+\eqref{eq:bc-type} can be classified into one of three categories: Type
+I, amphiphile, $b = 1$, $g$ is positive on one side representing a
+hydrocarbon-water interface, and is zero on the other representing an
+apolar, hydrophilic region; Type II, asymmetric hydrophobe, $b = 2$, $g$
+is positive on both sides but more so on one side; Type III, polar, $b =
+0$, $g$ is positive on one side and negative on the other, representing
+a water structure with positive/negative charge~\cite{MaRa76, Ma77}.
 
 Figure~\ref{fig:relax} shows the steady state in a quiescent flow.
-Three distinct phases emerge. For Type I, amphiphiles,
-the tail interactions are attractive, and particles collectively
-form disjoint bilayer components (Figure~\ref{fig:relax}(b)).
-We refer to this as the ``bilayer'' phase.
+Three distinct phases emerge. For Type I, amphiphiles, the tail
+interactions are attractive, and particles collectively form disjoint
+bilayer components (Figure~\ref{fig:relax}(b)). We refer to this as the
+``bilayer'' phase.
 
@@
 \begin{caption}{\label{fig:relax}
-    Panel (a) shows the $t = 0$, $N_b = 198$ particle configuration
-    with random orientation and initially confined to a box. 
-  Panels (b), (d), (e) show bilayer, multilamellar, and striated phases
-  composed of amphiphilic (Type I), asymmetric hydrophobe (Type II),
-  and polar (Type III) JP, respectively. 
-  Panels (c) and (f) plot the free energies~\eqref{eq:free_energy}
-  and alignment order parameter~\eqref{eq:S2} with respect
-  to $t$. The open markers in panel (c)
-  are for $N_b = 60$ and the
-  solid markers are for $N_b = 198$ but 
-  normalized by $60/198$, showing that the energy
-  approximately scales with the number of particles.
-  Alignment in the striated phase is particle-number dependent; 
-  triangle markers, panel (f).}  
+  Panel (a) shows the $t = 0$, $N_b = 198$ particle configuration with
+  random orientation and initially confined to a box. Panels (b), (d),
+  (e) show bilayer, multilamellar, and striated phases composed of
+  amphiphilic (Type I), asymmetric hydrophobe (Type II), and polar (Type
+  III) JP, respectively. Panels (c) and (f) plot the free
+  energies~\eqref{eq:free_energy} and alignment order
+  parameter~\eqref{eq:S2} with respect to $t$. The open markers in panel
+  (c) are for $N_b = 60$ and the solid markers are for $N_b = 198$ but
+  normalized by $60/198$, showing that the energy approximately scales
+  with the number of particles. Alignment in the striated phase is
+  particle-number dependent; triangle markers, panel (f).}
 \end{caption}
@@
 
-For Type II, asymmetric hydrophobes,
-both sides of the JP are hydrophobic but more so on the tail.
-Over short times, these particles self-assemble into bilayers. But unlike for
-Type I JPs, the heads are also hydrophobic and so over long times, 
-the bilayers sort into a ``multilamellar'' phase.
-The number of layers depends on the number of particles.
-Figure~\ref{fig:relax}(c), for example, shows a multilamellar structure
-with four layers and one with two layers in the inset.
-Onion-like dendrimersomes have previously been studied by molecular dynamics
-simulations using an 
-anisotropic pair potential~\cite{C9NR05885K,HongCacciutoLuijtenGranick2008}.
-
-Finally, Type III, bipolar JPs possess a
-head that repels the tail of neighboring particles.
-These JP initially form chains with
-their directors perpendicular to the length of the chain. The chains
-form stria where the particles lie on a square grid and the orientations
-alternate between layers (Figure~\ref{fig:relax}(d)).
-We refer to this as the ``striated'' phase.
+For Type II, asymmetric hydrophobes, both sides of the JP are
+hydrophobic but more so on the tail. Over short times, these particles
+self-assemble into bilayers. But unlike for Type I JPs, the heads are
+also hydrophobic and so over long times, the bilayers sort into a
+``multilamellar'' phase. The number of layers depends on the number of
+particles. Figure~\ref{fig:relax}(d), for example, shows a multilamellar
+structure with four layers and one with two layers in the inset.
+Onion-like dendrimersomes have previously been studied by molecular
+dynamics simulations using an anisotropic pair
+potential~\cite{C9NR05885K,HongCacciutoLuijtenGranick2008}.
+
+Finally, Type III, bipolar JPs possess a head that repels the tail of
+neighboring particles. These JP initially form chains with their
+directors perpendicular to the length of the chain. The chains form
+stria where the particles lie on a square grid and the orientations
+alternate between layers (Figure~\ref{fig:relax}(e)). We refer to this
+as the ``striated'' phase.
 
@@
 \section{Measuring deformation}
-To quantify the hydrodynamics of JP phases,
-we use the free energy $F$, a strain parameter $E$, and
-a scalar order parameters $S_{2}$ for alignment.
-First we simplify the form of the free energy~\eqref{eq:free_energy}.
-Using integration by parts and~\eqref{eq:SL}, we obtain
+\label{sec:measuring_deformation}
+To quantify the hydrodynamics of JP phases, we use the free energy $F$,
+a strain parameter $E$, and a scalar order parameters $S_{2}$ for
+alignment. First we simplify the form of the free
+energy~\eqref{eq:free_energy}. Using integration by parts
+and~\eqref{eq:SL}, we obtain
 \begin{equation}
@@
 Here, we have substituted $g$ for $u$ since the boundary values are
-given. However, evaluating $\nabla u \cdot \nnu$ on $\partial \Omega$ based
-on~\eqref{eq:SL_BIE} involves calculating a quadruple layer potential
-which has a well-known obstacle in numerical implementation.
-Appendix \S\ref{sec:appendix} describes
-how we overcome this obstacle.
+given. However, evaluating $\nabla u \cdot \nnu$ on $\partial \Omega$
+based on~\eqref{eq:SL_BIE} involves calculating a gradient of a
+double-layer potential which has a well-known obstacle in numerical
+implementation. Appendix~\ref{sec:appendix} describes how we overcome
+this obstacle.
 
@@
 relaxation runs. In quiescent background flow, the energies are
-decreasing with respect to $t$ showing time stepping correctly
-accounts for viscous dissipation.  Furthermore, the normalized energy
-plots provide evidence that the free energy per particle with specified
+decreasing with respect to $t$ showing time stepping correctly accounts
+for viscous dissipation. Furthermore, the normalized energy plots
+provide evidence that the free energy per particle with specified
 boundary condition is independent of the total particle number $(N_b)$.
 
-To measure positional order, we introduce the strain
-parameter, 
+To measure positional order, we introduce the strain parameter, 
 \begin{equation}
@@
 \end{equation}
-where $\mathsf{F}_i$ is an approximate deformation gradient
-and $\| \cdot \|$ is the Frobenius norm. 
-The Green-Lagrange strain tensor
-$\tfrac{1}{2}(\mathsf{F}_i^T \mathsf{F}_i - I)$
-measures departure of fluid deformations from a rigid
-body motion.  To define $\mathsf{F}_i$,
-we
-solve the overdetermined system 
+where $\mathsf{F}_i$ is an approximate deformation gradient and $\|
+\cdot \|$ is the Frobenius norm. The Green-Lagrange strain tensor
+$\tfrac{1}{2}(\mathsf{F}_i^T \mathsf{F}_i - I)$ measures departure of
+fluid deformations from a rigid body motion. To define $\mathsf{F}_i$,
+we solve the overdetermined system 
 \begin{align}
@@
 \end{align}
-for $\mathsf{F}_i$ by weighted least squares.
-That way, if the particle positions are given by
-a map $\ff(\aa_i(0),t) = \aa_i(t)$, then
-$\mathsf{F}_i \approx \nabla \ff(\aa_i(0),t)$.
-The weights $w_i =
+for $\mathsf{F}_i$ by weighted least squares. That way, if the particle
+positions are given by a map $\ff(\aa_i(0),t) = \aa_i(t)$, then
+$\mathsf{F}_i \approx \nabla \ff(\aa_i(0),t)$. The weights $w_i =
 \exp(-\|\aa_j(0) - \aa_i(0)\|/4c)$ with particle radius $c$ ensure that
@@
 
-Finally, we use the scalar order parameter $S_2$
-to quantify the orientational order\cite{Selinger2016}:
+Finally, we use the scalar order parameter $S_2$ to quantify the
+orientational order~\cite{Selinger2016}:
 \begin{equation}
@@
 \end{equation}
-Here $\bar \theta_i$ is a circular mean defined as the orientation of the
-principal eigenvector of the matrix
-$\sum_{j} \dd_j\dd_j^\top$ where $j$ runs over the particles
-whose centers lie with $4c$ of that of particle $i$. 
-Defined as such, $S_2$ lies in the range $-1/2 \le S_2 \le 1$
-with a value $S_2 = 1$ indicating perfect alignment between particles
-while $S_2=-1/2$ indicating isotropic alignment locally.
-The cutoff distance $4c$ was chosen empirically
-so that the average includes nearest neighbors
-but excludes next nearest neighbors.
+Here $\bar \theta_i$ is a circular mean defined as the orientation of
+the principal eigenvector of the matrix $\sum_{j} \dd_j\dd_j^\top$ where
+$j$ runs over the particles whose centers lie with $4c$ of that of
+particle $i$.  Defined as such, $S_2$ lies in the range $-1/2 \le S_2
+\le 1$ with a value $S_2 = 1$ indicating perfect alignment between
+particles while $S_2=-1/2$ indicating isotropic alignment locally.  The
+cutoff distance $4c$ was chosen empirically so that the average includes
+nearest neighbors but excludes next nearest neighbors.
 
 In Figure~\ref{fig:relax}(f), the multilamellar phase is highly ordered
-whereas the bilayer phase is somewhat
-disordered because it consists of several components forming isolated
-bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
-
-The striated phase order admits more than one pattern
-depending on the number of particles (Figure~\ref{fig:relax}(f), triangles).
-When the number of particles is fewer, there is only a
-single pattern where the directors are more or
-less parallel and alternate directions (Figure~\ref{fig:relax}(e),
-inset). Larger number of particles results in multiple alignment patterns:
-the alternating sign pattern as in the small particle number case
-(Figure~\ref{fig:relax}(e), top right rectangle) and an 'X'-shaped
-alignment (Figure~\ref{fig:relax}(e), top left rectangle).
+whereas the bilayer phase is somewhat disordered because it consists of
+several components forming isolated bilayers, micelles, and vesicles
+(Figure~\ref{fig:relax}(b)).
+
+The striated phase order admits more than one pattern depending on the
+number of particles (Figure~\ref{fig:relax}(f), triangles).  When the
+number of particles is fewer, there is only a single pattern where the
+directors are more or less parallel and alternate directions
+(Figure~\ref{fig:relax}(e), inset). Larger number of particles results
+in multiple alignment patterns: the alternating sign pattern as in the
+small particle number case (Figure~\ref{fig:relax}(e), top right
+rectangle) and an `X'-shaped alignment (Figure~\ref{fig:relax}(e), top
+left rectangle).
 

### 2023-03-21 doc/PRF2022/PRF_main.tex
almost done results

@@
 $j$ runs over the particles whose centers lie with $4c$ of that of
-particle $i$.  Defined as such, $S_2$ lies in the range $-1/2 \le S_2
-\le 1$ with a value $S_2 = 1$ indicating perfect alignment between
-particles while $S_2=-1/2$ indicating isotropic alignment locally.  The
-cutoff distance $4c$ was chosen empirically so that the average includes
+particle $i$. Defined as such, $S_2$ lies in the range $-1/2 \le S_2 \le
+1$ with a value $S_2 = 1$ indicating perfect alignment between particles
+while $S_2=-1/2$ indicating isotropic alignment locally. The cutoff
+distance $4c$ was chosen empirically so that the average includes
 nearest neighbors but excludes next nearest neighbors.
@@
 \caption{\label{fig:s2esummary}
-  Panel (a)-(b) show the average strain increase for bilayer, vesicle BL,
-  multilamellar, and striated JP structures under a shear flow and a TG flow, respectively.
-Panel (c)-(d) show the average alignment of four JP structures under a shear flow and a TG flow, respectively. 
-Each snapshot of panels (e)-(l) contains the configurations of the JP structure using a specific type of boundary bondition without ruptures and the backgroud curves indicate the velocity streamlines.}
+  Panel (a)--(b) show the average strain increase for bilayer, vesicle
+  BL, multilamellar, and striated JP structures under a shear flow and a
+  TG flow, respectively. Panel (c)--(d) show the average alignment of
+  four JP structures under a shear flow and a TG flow, respectively.
+  Each snapshot of panels (e)--(l) contains the configurations of the JP
+  structure without ruptures using a specific type of boundary condition
+  and the background curves indicate the velocity streamlines.}
 \end{figure}
 %
-We subjected the Type I, II, and III JP phases to background flows and measured 
-their material response.  The background flows were a shear flow
+We subject the Type I, II, and III JP phases to background flows and
+measure their material response. The background flows are a shear flow
 \begin{equation}
@@
 \end{equation}
-where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal
-and vertical directions, respectively.
-The shear flow replicates the motion of a fluid between two parallel,
-moving plates excluding wall effects.
-In TG flow, $\lambda$ controls the size of the
-$2\pi \lambda \times 2\pi \lambda$ TG cells.
-Throughout, we use $\lambda = 2$ nm
-so that the JP phases occupy about nine cells.
-
-In both cases, $\dot \gamma$ is the shear rate.
-The flow rate $\lambda \dot \gamma$  
-was chosen so that \eqref{eq:tg_flow} has the same
-rate of viscous dissipation per area as for \eqref{eq:sh_flow}.
-In other words, 
-$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ 
-is the same for 
-$\uu = \uu_{\infty}^{\text{sh}}$ as for 
-$\uu = \uu_{\infty}^{\text{TG}}$
-when integrated over a TG cell $A$.
-
-To obtain a range for $\dot \gamma$, 
-consider the capillary number 
+where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal and
+vertical directions, respectively. The shear flow replicates the motion
+of a fluid between two parallel, moving plates excluding wall effects.
+In TG flow, $\lambda$ controls the size of the $2\pi \lambda \times 2\pi
+\lambda$ TG cells. Throughout, we use $\lambda = 2$ nm so that the JP
+phases occupy about nine cells.
+
+In both cases, $\dot \gamma$ is the shear rate. The flow rate $\lambda
+\dot \gamma$ is chosen so that~\eqref{eq:tg_flow} has the same rate of
+viscous dissipation per area as for~\eqref{eq:sh_flow}. In other words,
+$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ is the
+same for $\uu = \uu_{\infty}^{\text{sh}}$ as for $\uu =
+\uu_{\infty}^{\text{TG}}$ when integrated over a TG cell $A$.
+
+To obtain a range for $\dot \gamma$, consider the capillary number 
 \begin{equation}
@@
 \end{equation}
-where $R = 10$ nm and $\kappa = 20\;\kbt$ are 
-the characteristic phase sample radius 
-and bending rigidity, respectively. 
-That is, $\kappa$ gives the elastic stress 
-for restoring the phase-sample shape.
-Shear stress overcomes elastic stress   
-when $C_a > 1$ and this yields 
-$\dot \gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$ s.
-Thus our values for $\dot \gamma$ range between 
-$0$ ns$^{-1}$ corresponding to quiescent flow
-up to $0.2$ ns$^{-1}$ capable of rupturing the sample. 
-Such shear rates are compatible with molecular dynamics 
-simulation \cite{Brandner2019}, those for large unilamellar vesicles (LUV),
-\cite{Bernard2005ShearinducedPA} and shearing in blood capillary vessels
-\cite{Cho2011} where shear rates range over 100--2000 s$^{-1}$.
-
-For initial data, the steady-state Type I amphiphiles phase
-consisted of a number of disjoint bilayer components
-(Figure \ref{fig:relax}(b)). To also have a single-component Type I phase, 
-we reinitialized the data to have a ring-shaped vesicle bilayer.
-This phase is distinguished from ``bilayer'' by ``vesicle BL'' in the figures.
-For the same number of JP, the vesicle bilayer
-has lower free  steady-state energy
-($F = 24.6 \;\kbt$ nm$^{-1}$) than the 
-disordered bilayer phase ($F = 27.2 \;\kbt$ nm$^{-1}$). 
-Since the simulations are for two dimensions,
-multiplying $F$ by a length gives the energy 
-of a transversely invariant, three-dimensional 
-phase.
-
-Figure \ref{fig:s2esummary} (e)--(l) show the typical streamlines
-for JP phases in background flow.  Although the plots only show
-the region near the JP phases, the fluid velocity $\uu$ and 
-order parameter $u$ are accounted for in all of $\mathbb{R}^2$.
-Moreover, $\uu$ satisfies the rigid boundary condition at 
-every JP-fluid interface i.e., the particles interact with the local
-flow field and are not merely carried by background flow.
-
-The simulation setup consisted of placing each of the 
-phases in either a shear or TG background flow and then solving for the 
-particle trajectories in time. In each setup, we solved for $500$ time steps 
-with $\Delta t = 2$ ns, yielding time courses for $t \in [0, T]$, $T = 1$ $\upmu$s.
-We then post-processed the trajectories.
-
-Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}
-contain the fully-resolved time courses for free energy $F$,
-alignment order $S_2$, and strain $E$. The eight setups
-correspond to the four JP phases---bilayer, vesicle BL, multilamellar,
-and striated---and two background flows---shear and TG,
-and the data are plotted with the same ordinate to facilitate
-comparisons between simulation setups.  Each setup considers
-a range of shear rates $\dot \gamma$ in the interval $[0, 0.2]$ ns$^{-1}$.
-
-The fully-resolved time courses
-in Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}
-contain significant oscillations due to the particle-based formulation
-and tumbling inherent to the background flows.  To extract meaningful
-data, we further postprocessed the $F$, $S_2$, $E$ curves by taking
-their time average over the interval $t \in [0, T]$.
+where $R = 10$~nm and $\kappa = 20\;\kbt$ are the characteristic phase
+sample radius and bending rigidity, respectively. That is, $\kappa$
+gives the elastic stress for restoring the phase-sample shape. Shear
+stress overcomes elastic stress when $C_a > 1$ and this yields $\dot
+\gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$~s. Thus our values
+for $\dot \gamma$ range between $0$ ns$^{-1}$ corresponding to quiescent
+flow up to $0.2$~ns$^{-1}$ capable of rupturing the sample. Such shear
+rates are compatible with molecular dynamics simulation
+\cite{Brandner2019}, those for large unilamellar vesicles (LUV),
+\cite{Bernard2005ShearinducedPA}, and shearing in blood capillary
+vessels \cite{Cho2011} where shear rates range over 100--2000 s$^{-1}$.
+
+For initial data, note that the steady-state Type I amphiphiles phase
+consists of a number of disjoint bilayer components
+(Figure~\ref{fig:relax}(b)). To also have a single-component Type I
+phase, we reinitialize the data to have a ring-shaped vesicle bilayer.
+This phase is distinguished from ``bilayer'' by ``vesicle BL'' in the
+figures. For the same number of JP, the vesicle bilayer has lower free
+steady-state energy ($F = 24.6 \;\kbt$ nm$^{-1}$) than the disordered
+bilayer phase ($F = 27.2 \;\kbt$ nm$^{-1}$). Since the simulations are
+for two dimensions, multiplying $F$ by a length gives the energy of a
+transversely invariant, three-dimensional phase.
+
+The simulation setup consists of placing each of the phases in either a
+shear or TG background flow and then solving for the particle
+trajectories in time. In each setup, we solved for $500$ time steps with
+$\Delta t = 2$~ns, yielding time courses for $t \in [0, T]$, $T =
+1$~$\upmu$s. We then post-process the trajectories.
+
+Figure~\ref{fig:s2esummary}(e)--(l) show the typical streamlines for JP
+phases in background flow. Although the plots only show the region near
+the JP phases, the fluid velocity $\uu$ and order parameter $u$ are
+accounted for in all of $\mathbb{R}^2$. Moreover, $\uu$ satisfies the
+rigid boundary condition at every JP-fluid interface i.e., the particles
+interact with the local flow field and are not merely carried by
+background flow.
+
+Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} contain the
+fully-resolved time courses for the free energy $F$, alignment order
+$S_2$, and strain $E$. The eight setups correspond to the four JP
+phases---bilayer, vesicle BL, multilamellar, and striated---and two
+background flows---shear and TG, and the data are plotted with the same
+ordinate to facilitate comparisons between simulation setups. Each setup
+considers a range of shear rates $\dot \gamma$ in the interval $[0,
+0.2]$ ns$^{-1}$.
+
+The fully-resolved time courses in Supplementary
+Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} contain significant
+oscillations due to the particle-based formulation and tumbling inherent
+to the background flows. To extract meaningful data, we further
+post-process the $F$, $S_2$, $E$ curves by taking their time average
+over the interval $t \in [0, T]$.
 
@@
 The plots reveal highly distinct material responses from each phase.
-Figure \ref{fig:s2esummary} (a) and (b) show the time-averaged
-strain $\frac{1}{T}\int_0^T E \,\dif t$ over a broad
-range of shear rates.  Strain $E$
-measures the non-rigid-body deformation relative to the initial state
-and expectedly increases with shear rate.
-The greatest increase occurs with the Type I amphiphiles, 
-suggesting that this phase has the lowest elastic modulus
-(squares). In comparison, 
-the  striated phase consisting of  Type III polar JP is
-basically rigid (triangles).
-
-Figure \ref{fig:s2esummary} (c) and (d) plot the time-averaged
-alignment order $S_2$. The vesicle and striated phases possess
-the greatest alignment order and, 
-for the most part, $S_2$ decreases with increases in shear rate.
-But there is an exception.  The Type I bilayer phase alignment
-order actually increases under both shear and TG flows (solid squares).  
-This suggests that 
-the mixing action of background flow has the effect of moving the
-disordered bilayer phase out of a local equilibrium and into a state
-with greater order.
-This surprising increase, 
-brought about by combining previously broken bilayer 
-end caps, is accompanied
-by a slight decrease in free energy (Figure \ref{fig:fsummary}a, solid squares).
-
-The sudden jumps in  Figure \ref{fig:s2esummary} (a) and (b)
-and commensurate drops in panels (c) and (d) indicate
-the existence of a critical shear rate $\gamma_*$.  This means that 
-for $\gamma < \gamma_*$, the JP phase remains intact while
-for $\gamma > \gamma_*$, the phase ruptures. 
-For example, the vesicle BL phase has 
-$\gamma_*$ approximately $0.05$ ns$^{-1}$ 
-under shear flow and TG flow. However, the critical shear rate
-is flow-pattern dependent because 
-the striated phase has $\gamma_* = 0.14$ ns$^{-1}$ under shear flow
-while $\gamma_* = 0.05$ ns$^{-1}$ under  TG flow.
-Due to variable stress distribution, 
-the critical shear rate in TG flow likely 
-depends on the cell size parameter $\lambda$.
-The disordered bilayer phase does not really possess a critical
-shear rate because it already consists of several, disjoint components.
-The jump in Figure \ref{fig:s2esummary} (a) (solid squares)
+Figures~\ref{fig:s2esummary}(a) and (b) show the time-averaged strain
+$\frac{1}{T}\int_0^T E \,\dif t$ over a broad range of shear rates.
+Strain $E$ measures the non-rigid-body deformation relative to the
+initial state and expectedly increases with shear rate. The greatest
+increase occurs with the Type I amphiphiles, suggesting that this phase
+has the lowest elastic modulus (squares). In comparison, the striated
+phase consisting of Type III polar JP is basically rigid (triangles).
+
+Figures~\ref{fig:s2esummary}(c) and (d) plot the time-averaged alignment
+order $S_2$. The vesicle and striated phases possess the greatest
+alignment order and, for the most part, $S_2$ decreases with increases
+in shear rate. But there is an exception. The Type I bilayer phase
+alignment order actually increases under both shear and TG flows (solid
+squares). This suggests that the mixing action of background flow has
+the effect of moving the disordered bilayer phase out of a local
+equilibrium and into a state with greater order. This surprising
+increase, brought about by combining previously broken bilayer end caps,
+is accompanied by a slight decrease in free energy
+(Figure~\ref{fig:fsummary}(a), solid squares).
+
+The sudden jumps in Figures~\ref{fig:s2esummary}(a) and (b) and
+commensurate drops in panels (c) and (d) indicate the existence of a
+critical shear rate $\gamma_*$. This means that for $\gamma < \gamma_*$,
+the JP phase remains intact while for $\gamma > \gamma_*$, the phase
+ruptures. For example, the vesicle BL phase has $\gamma_*$ approximately
+$0.05$ ns$^{-1}$ under shear flow and TG flow. However, the critical
+shear rate is flow-pattern dependent because the striated phase has
+$\gamma_* = 0.14$ ns$^{-1}$ under shear flow while $\gamma_* = 0.05$
+ns$^{-1}$ under TG flow. Due to variable stress distribution, the
+critical shear rate in TG flow likely depends on the cell size parameter
+$\lambda$. The disordered bilayer phase does not really possess a
+critical shear rate because it already consists of several, disjoint
+components. The jump in Figure~\ref{fig:s2esummary}(a) (solid squares)
 simply corresponds to disjoint components drifting apart in the shear
-flow.  The Type II multilamellar phase did
-not rupture for any of the shear rates considered.
+flow. The Type II multilamellar phase did not rupture for any of the
+shear rates considered.
 
@@
 \caption{\label{fig:fsummary}
-  The change of average free energy versus shear rates for shear flow and TG flow simulation results are plotted in panels (a)-(b). Panel (c) contains quadratic fits
-  to the change in free energy as a function of displacement in interparticle distance
-  from equilbrium.}
+  The change of average free energy versus shear rates for shear flow
+  and TG flow simulation results are plotted in panels (a)-(b). Panel
+  (c) contains quadratic fits to the change in free energy as a function
+  of displacement in interparticle distance from equilibrium.}
 \end{figure}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Free energy}
 \label{sec:free-energy}
-Figure \ref{fig:fsummary} plots the time-averaged
-relative free energy $\frac{1}{T}\int_0^T F - F_0 \,\dif t$ where $F_0$ is 
-\eqref{eq:free_energy2} at $t = 0$.  The 
-greatest increase occurs with the Type II 
-multilamellar phase, with the other phases 
-showing a moderate change in a few \KBT\,nm$^{-1}$.
-
-Figure \ref{fig:fsummary} (c) plots free energy 
-against the displacement $x = c E$ representing the
-change in mean  interparticle displacement from equilibrium;
-$c = 1.25$ nm is particle radius.
-The energies in Figure \ref{fig:fsummary} (c) are essentially  
-quadratic in $x$ suggesting that the interactions 
-are harmonic locally around equilibrium.
-The harmonic bond strength is strongest between 
-polar JP, and greater by a factor of two and five than
-that for asymmetric hydrophobes and amphiphiles,
-respectively.  This makes sense when considering 
-that the free energy of the steady-state striated
-phase is also greatest (Figure \ref{fig:relax} (c), around 85 \KBT\;nm$^{-1}$).
-However, the bond strength in the multilamellar 
-phase comes in second, despite having least steady-state free energy
-(around 15 \KBT\;nm$^{-1}$).
-The data point to the fact that the binding properties 
-do not merely scale with free energy, 
-but also involve the details of the interface's
-hydrophobicity 
-which are tuned by \eqref{eq:bc-type} in our model.
+Figure~\ref{fig:fsummary} plots the time-averaged relative free energy
+$\frac{1}{T}\int_0^T F - F_0 \,\dif t$ where $F_0$
+is~\eqref{eq:free_energy2} at $t = 0$. The greatest increase occurs with
+the Type II multilamellar phase, with the other phases showing a
+moderate change in a few \KBT\,nm$^{-1}$.
+
+Figure~\ref{fig:fsummary}(c) plots the free energy against the
+displacement $x = c E$ representing the change in mean interparticle
+displacement from equilibrium; $c = 1.25$~nm is the particle radius.
+The energies in Figure~\ref{fig:fsummary}(c) are essentially quadratic
+in $x$ suggesting that the interactions are harmonic locally around
+equilibrium. The harmonic bond strength is strongest between polar JP,
+and greater by a factor of two and five than that for asymmetric
+hydrophobes and amphiphiles, respectively. This makes sense when
+considering that the free energy of the steady-state striated phase is
+also greatest (Figure~\ref{fig:relax}(c), around 85 \KBT\;nm$^{-1}$).
+However, the bond strength in the multilamellar phase comes in second,
+despite having least steady-state free energy (around
+15~\KBT\;nm$^{-1}$). The data point to the fact that the binding
+properties do not merely scale with free energy, but also involve the
+details of the interface's hydrophobicity which are tuned
+by~\eqref{eq:bc-type} in our model.
 
@@
 \end{center}
-\caption{\label{fig:rheologysummary}
-  Rheology of Type I, II, and III phases.
-  Panel (a) shows that bilayer phases  behave as a Newtonian fluid.
-  Panel (b) provides that the multilamellar phase shows a near shear thinning behaviour.
-  A pseudoplastic behaviour of deformation in striated phases is shown in panel (c). }
+\caption{\label{fig:rheologysummary} Rheology of Type I, II, and III
+  phases. Panel (a) shows that bilayer phases behave as a Newtonian
+  fluid. Panel (b) provides that the multilamellar phase shows a near
+  shear thinning behaviour. A pseudoplastic behaviour of deformation in
+  striated phases is shown in panel (c).}
 \end{figure}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Rheology}
 \label{sec:rheology}
-So far, we have considered static material properties, namely
-constant strains maintained by an external force provided by   
-background flow. Now we consider dynamic material properties.
-Specifically, we look at the strain rate 
+So far, we have considered static material properties, namely constant
+strains maintained by an external force provided by background flow.
+Now we consider dynamic material properties. Specifically, we look at
+the strain rate 
 \begin{equation}
@@
 \end{equation}
-The reason for defining $\dot E$ in this way is that 
-the shear flow $\uu_{\infty}^{\text{sh}}$
-simulations correspond to a complex fluid within a drag plate
-rheometer where the shear stress is set by $\mu \dot\gamma$  
-and the observed, sample shear rate is $\dot E$. 
-The definitions carry over to the TG flow case directly. 
-Also, as a practical consideration,
-the rotation of non-isotropic JP phases in the background 
-flow leads to oscillation in the strain time courses 
-making systematic fitting challenging (see 
-Supplementary Material Figures \ref{fig:ulshraw}--\ref{fig:sttgraw}). 
-The integral in \eqref{eq:strainrate} averages out these oscillations
-and gives physically meaningful values.
-
-The shear stress--strain rate data are 
-excellently fit by power laws.  
-Figures \ref{fig:rheologysummary} (a), (b), and (c)
-show the data for Type I, Type II and Type III JPs, respectively,
-under both shear flow (squares) and TG flow (triangles).
-The bilayer phases consisting of Type I JPs are basically Newtonian
-with viscosity $0.014$ MPa\;$\upmu$s $= 14$ mPa\;s,
-about 14 times the the viscosity of water at room temperature
-(Figures \ref{fig:rheologysummary}(a), dashed curve). 
-The vesicle bilayer phase is slightly shear thickening
-(Figures \ref{fig:rheologysummary}(a), solid curve).
-The multilamellar phase consisting of Type II JPs
-is somewhat shear thinning,  but its viscosity 
-is larger than for Type I.  Finally, the striated
-phase is strongly shear-thinning.  This 
-further explains the rigid-like behavior of the 
-striated phase found in the strain, shear-rate relationships from 
-Figure \ref{fig:s2esummary}(a), (b) (triangles).
+The reason for defining $\dot E$ in this way is that the shear flow
+$\uu_{\infty}^{\text{sh}}$ simulations correspond to a complex fluid
+within a drag plate rheometer where the shear stress is set by $\mu
+\dot\gamma$ and the observed, sample shear rate is $\dot E$. The
+definitions carry over to the TG flow case directly. Also, as a
+practical consideration, the rotation of non-isotropic JP phases in the
+background flow leads to oscillation in the strain time courses making
+systematic fitting challenging (see Supplementary Material
+Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}). The integral
+in~\eqref{eq:strainrate} averages out these oscillations and gives
+physically meaningful values.
+
+The shear stress-strain rate data are excellently fit by power laws.
+Figures~\ref{fig:rheologysummary}(a)--(c) show the data for Type I, Type
+II and Type III JPs, respectively, under both shear flow (squares) and
+TG flow (triangles). The bilayer phases consisting of Type I JPs are
+basically Newtonian with viscosity $0.014$ MPa\;$\upmu$s $= 14$ mPa\;s,
+about 14 times the viscosity of water at room temperature
+(Figures~\ref{fig:rheologysummary}(a), dashed curve). The vesicle
+bilayer phase is slightly shear thickening
+(Figure~\ref{fig:rheologysummary}(a), solid curve). The multilamellar
+phase consisting of Type II JPs is somewhat shear thinning, but its
+viscosity is larger than for Type I. Finally, the striated phase is
+strongly shear-thinning. This further explains the rigid-like behavior
+of the striated phase found in the strain, shear-rate relationships from
+Figures~\ref{fig:s2esummary}(a) and (b) (triangles).
 \todo[inline]{RBC flow refereces}
@@
   the bilayer location and the TG cell boundary. This correlation also
-  somehow determines the shape.  Can count the number of partial TG
-  cells inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has
-  2 + 4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$,
-  and (e) has 1 cell.}
+  somehow determines the shape. Can count the number of partial TG cells
+  inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has 2 +
+  4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$, and
+  (e) has 1 cell.}
 \end{figure}
@@
 \subsection{Discussion}
-We choose the range of shear rates $\dot \gamma \in [0, 0.02]$ ns$^{-1}$
+We choose the range of shear rates $\dot \gamma \in [0, 0.02]$~ns$^{-1}$
 by analyzing the capillary number of the JP phases. With this range,
-there was a critical shear rate $\dot \gamma_*$ for the vesicle BL
-and striated phases where shear stresses exceeded elastic stresses,
-leading to rupture.  The multilamellar phase did not rupture.
-By varying model parameters, we can perform a dimensional analysis 
-on $\dot \gamma_*$. Focusing on Type III JPs in shear flow, 
-$\dot \gamma_* = 0.14$ ns$^{-1}$ for the basic model parameters
-(see Section \ref{sec:tunable_hydrophobicity}).  Increasing
-and decreasing the tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
+there is a critical shear rate $\dot \gamma_*$ for the vesicle BL and
+striated phases where shear stresses exceeded elastic stresses, leading
+to rupture. The multilamellar phase did not rupture. By varying model
+parameters, we perform a dimensional analysis on $\dot \gamma_*$.
+Focusing on Type III JPs in shear flow, $\dot \gamma_* = 0.14$ ns$^{-1}$
+for the basic model parameters (see
+Section~\ref{sec:tunable_hydrophobicity}). Increasing and decreasing the
+tension parameters $\gamma$ and $M$ by up to 10\% (collectively denoted
 $\Delta \gamma/\gamma$) led to basically the same relative
-increase/decrease in critical shear
-rate (denoted $\Delta \dot \gamma_*/\dot \gamma_*$).  This suggests
-that the critical shear rate scales linearly with the tension parameters.
-Conversely, increasing (resp.~decreasing) the length parameters $c$, $\rho$, and $\rho_0$
-by up to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
-relative \emph{decrease} (resp.~increasing) in the critical shear rate.  This points to an inverse-quadratic
-scaling in length. Figure \ref{fig:PramChange}(a) summarizes the 
-findings and suggest the scaling
+increase/decrease in critical shear rate (denoted $\Delta \dot
+\gamma_*/\dot \gamma_*$). This suggests that the critical shear rate
+scales linearly with the tension parameters. Conversely, increasing
+(resp.~decreasing) the length parameters $c$, $\rho$, and $\rho_0$ by up
+to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
+relative \emph{decrease} (resp.~increase) in the critical shear rate.
+This points to an inverse-quadratic scaling in length.
+Figure~\ref{fig:PramChange}(a) summarizes the findings and suggest the
+scaling
 \begin{equation}
@@
 during rupture (see Supplementary Movie S4). Our previous
-work\cite{Fu2022_JFM} found the scaling $\mu \dot\gamma_* = K_{\text{I}}
-\gamma c^2/(\rho L^2)$ for vesicle BL in shear flow.
+work~\cite{Fu2022_JFM} found the scaling $\mu \dot\gamma_* =
+K_{\text{I}} \gamma c^2/(\rho L^2)$ for a vesicle BL in shear flow.
 
@@
 all cases, the vesicle and TG flow reach a steady-state tank-treading
-motion, but the geometry and motion varies non-monotonically. For
-$\lambda$ ranging from $1$ nm to $4$ nm, the steady-state vesicle shape
-goes from an octagon, to a dimpled square, to a rounded diamond, to a
-rounded square. Surprisingly, the direction of rotation switches: for
-$\lambda = 2$ nm the rotation is clockwise, while for $\lambda = 4$ nm
-the rotation is counterclockwise. Finally, we calculate the vesicle area
-$A$ and length $L$. As shown in Figure~\ref{fig:PramChange}(f), the
-relative area $A/A_0$ achieves a steady-state that is greatest for
-$\lambda = 4$ nm yet least for $\lambda = 2$ nm. The relative length
-$L/L_0$, however, is constant in $t$ for all cell sizes
-(Figure~\ref{fig:PramChange}(e), inset). In other words, the flow
-pattern is non-monotonic in the cell size $\lambda$.
+motion \todo[inline]{no longer true}, but the geometry and motion varies
+non-monotonically. For $\lambda$ ranging from $1$ nm to $4$ nm, the
+steady-state vesicle shape goes from an octagon, to a dimpled square, to
+a rounded diamond, to a rounded square. Surprisingly, the direction of
+rotation switches: for $\lambda = 2$ nm the rotation is clockwise, while
+for $\lambda = 4$ nm the rotation is counterclockwise. Finally, we
+calculate the vesicle area $A$ and length $L$. As shown in
+Figure~\ref{fig:PramChange}(f), the relative area $A/A_0$ achieves a
+steady-state that is greatest for $\lambda = 4$ nm yet least for
+$\lambda = 2$ nm. The relative length $L/L_0$, however, is constant in
+$t$ for all cell sizes (Figure~\ref{fig:PramChange}(e), inset). In other
+words, the flow pattern is non-monotonic in the cell size $\lambda$.
 
 We have excluded thermal fluctuations because they are unresolved in the
-JP phases we consider.  For a tensionless, planar membrane, the spectrum
-of the Fourier coefficients for the profile height 
-$h(\xx) = \sum_{\kk} h(\kk)e^{i \kk \cdot \xx}$ satisfy\cite{Merath2006FluctuationSO}  
+JP phases we consider. For a tensionless, planar membrane, the Fourier
+coefficients for the profile height $h(\xx) = \sum_{\kk} h(\kk)e^{i \kk
+\cdot \xx}$ satisfy~\cite{Merath2006FluctuationSO}  
 \begin{equation}

### 2023-03-21 doc/PRF2022/PRF_main.tex
finishing up discussion

@@
 
-To estimate $h(\kk)$, 
-the $N_b = 60$ JP
-vesicle in Figure \ref{fig:s2esummary}(e) 
-has arclength $L_x \approx 50$ nm. 
-Our prior work\cite{Fu20,Fu2022_JFM} gave $\kappa  \approx 20$ $\kbt$.
-Since our simulations are two-dimensional, we restrict our attention
-to transversely invariant fluctuations where $n = 0$.
-Substituting these values gives 
+To estimate $h(\kk)$, the $N_b = 60$ JP vesicle in
+Figure~\ref{fig:s2esummary}(e) has arclength $L_x \approx 50$~nm. Our
+prior work~\cite{Fu20,Fu2022_JFM} gave $\kappa \approx 20$ $\kbt$. Since
+our simulations are two-dimensional, we restrict our attention to
+transversely invariant fluctuations where $n = 0$. Substituting these
+values gives 
 \begin{equation}
@@
 \end{equation}
-For any moderate transverse depth, say $L_y > 4$ nm, the leading Fourier
-coefficient has a magnitude less than $1$ nm with the remaining
-coefficients dropping off to zero precipitously.  The expected
-amplitudes coming from thermal fluctuations are therefore negligible
-compared to particle size.  The elastic moduli for the Type II and
-Type III phases are greater by a factor of two and five, respectively,
-than for Type I (Figure~\ref{fig:fsummary}(c)), making thermal
-fluctuation even more negligible in these cases.
+For any moderate transverse depth, say $L_y > 4$~nm, the leading Fourier
+coefficient has a magnitude less than $1$~nm with the remaining
+coefficients dropping off to zero precipitously. The expected amplitudes
+coming from thermal fluctuations are therefore negligible compared to
+particle size. The elastic moduli for the Type II and Type III phases
+are greater by a factor of two and five, respectively, than for Type I
+(Figure~\ref{fig:fsummary}(c)), making thermal fluctuation even more
+negligible in these cases.
 
 The fact that the fluctuation amplitudes are small is not a consequence
-of stiffness. Quite the opposite, the value $\kappa = 20$ $\kbt$ agrees
+of stiffness. Quite the opposite, the value $\kappa = 20$~$\kbt$ agrees
 with the experimental literature where micron sized vesicles observably
@@
 
-The calculated viscosities---14 mPa s for Type I and 21 mPa s for Type
+The calculated viscosities---14~mPa~s for Type I and 21~mPa~s for Type
 II JP phases---are physically reasonable. In two-dimensional dilute
-suspensions, the Einstein viscosity correction is $1 + 2 \phi + 4\phi^2 +
-O(\phi^3)$, where $\phi \ll 1$ is the volume
+suspensions, the Einstein viscosity correction is $1 + 2 \phi + 4\phi^2
++ O(\phi^3)$, where $\phi \ll 1$ is the volume
 fraction~\cite{PhysRevFluids.1.043301, Haines2011APO, Khair2006TheC,
-Brady1983TheEV}. In Figures \ref{fig:s2esummary}(e)--(h), the volume
+Brady1983TheEV}. In Figures~\ref{fig:s2esummary}(e)--(h), the volume
 fraction is $\phi \approx 0.5$, which would correspond to a effective
-shear viscosity of $4$ mPa s according to Einstein's viscosity
+shear viscosity of $4$~mPa~s according to Einstein's viscosity
 correction. Note, however, that since $\phi = 0.5$ is outside of the
-dilute limit, one expects viscosities ten or more times that of water
-\cite{Konijn2014ExperimentalSO}.
+dilute limit, one expects viscosities ten or more times greater than the
+viscosity of water~\cite{Konijn2014ExperimentalSO}.
 
@@
 purely suspension effects and particles' preferred alignments. For
-example, the difference between the values 14 mPa s for Type I and 21
-mPa s for Type II JPs can be explained by the fact that the
+example, the difference between the values 14~mPa~s for Type I and
+21~mPa~s for Type II JPs can be explained by the fact that the
 multilamellar phase is more tightly packed than the bilayer phase
-(Figure \ref{fig:s2esummary}(e)--(h)).  Furthermore, it seems that the
+(Figures \ref{fig:s2esummary}(e)--(h)). Furthermore, it seems that the
 viscosity, and the tendency toward shear thinning in the case of Type
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusion}
@@
 BIEs~\cite{Fu20, Fu2022_JFM} and tune the boundary conditions with
-energy normalization to study the collective dynamics of amphiphilic
-(BC(i)), biased hydrophobic (BC (ii)), and bipolar (BC(iii)) JPs under
-various flowing conditions (quiescent flow, linear shear flow, and
-Taylor-Green flow). Three quantities are computed to characterize the
-dynamics of the collective configurations of JPs: free energy $F$,
-strain parameter $E$, and scalar order parameter $S_2$. 
+energy normalization to study the collective dynamics of amphiphilic (BC
+I), biased hydrophobic (BC II), and bipolar (BC III) JPs under various
+flowing conditions (quiescent flow, linear shear flow, and Taylor-Green
+flow). Three quantities are computed to characterize the dynamics of the
+collective configurations of JPs: free energy $F$, strain parameter $E$,
+and scalar order parameter $S_2$. 
 %We quantify how

### 2023-03-21 doc/PRF2022/PRF_main.tex
finished up small changes. Now need to fix Fig 6 and area

@@
   properties of the JP assembly in the suspension. We find JPs assemble
-  into uni-lamella, multi-lamella, and striated structures. To introduce
+  into unilamellar, multilamellar, and striated structures. To introduce
   dynamics, we include a planar linear shear flow and a steady
@@
   effective material properties of the JP structures and find that the
-  uni-lamellar structures increases orientation order under shear flow,
+  unilamellar structures increases orientation order under shear flow,
   the multilamellar structure behaves as a shear thinning fluid, and the
@@
 naturally from the interactions between particles and fluid in colloidal
-matter~\cite{RevModPhys.93.025008}. Such colloidal hydrodynamics
-belong to a wide class of nonequilibrium self-organization in physics,
-often with complexity and features similar to that of biological systems
-such as living cells, bacterial baths, and animal
+matter~\cite{RevModPhys.93.025008}. Such colloidal hydrodynamics belong
+to a wide class of nonequilibrium self-organization in physics, often
+with complexity and features similar to that of biological systems such
+as living cells, bacterial baths, and animal
 flocks~\cite{CollardGrosjeanVandewalle2020, Vutukuri2020}. A
@@
 In this work we focus on collective hydrodynamics of immobile
-amphiphilic JPs in a
-viscous fluid under an imposed far-field flow. The amphiphilic JP has a
-hydrophobic surface on one side and a hydrophilic surface on the other
-side \cite{doi:10.1021/la503455h}.
-The many-body hydrodynamics of amphiphilic Janus particles assembled as
-vesicles (self-enclosed bilayers of JPs) suspended in a viscous fluid in the inertialess regime (zero
-Reynolds number) has been studied using boundary integral numerical
-simulations~\cite{Fu20,Fu2022_JFM}. The dynamics of the JP suspension
-results from the combination of long-range hydrodynamic interaction and
-non-local interactions between JPs through the distribution of a
-hydrophobic attraction potential (HAP).
+amphiphilic JPs in a viscous fluid under an imposed far-field flow. The
+amphiphilic JP has a hydrophobic surface on one side and a hydrophilic
+surface on the other side \cite{doi:10.1021/la503455h}. The many-body
+hydrodynamics of amphiphilic Janus particles assembled as vesicles
+(self-enclosed bilayers of JPs) suspended in a viscous fluid in the
+inertialess regime (zero Reynolds number) has been studied using
+boundary integral numerical simulations~\cite{Fu20,Fu2022_JFM}. The
+dynamics of the JP suspension results from the combination of long-range
+hydrodynamic interaction and non-local interactions between JPs through
+the distribution of a hydrophobic attraction potential (HAP).
 %
@@
 Figures~\ref{fig:s2esummary}(a) and (b) (triangles).
-\todo[inline]{RBC flow refereces}
+\todo[inline]{RBC flow references}
 
@@
 BIEs~\cite{Fu20, Fu2022_JFM} and tune the boundary conditions with
-energy normalization to study the collective dynamics of amphiphilic (BC
-I), biased hydrophobic (BC II), and bipolar (BC III) JPs under various
-flowing conditions (quiescent flow, linear shear flow, and Taylor-Green
-flow). Three quantities are computed to characterize the dynamics of the
-collective configurations of JPs: free energy $F$, strain parameter $E$,
-and scalar order parameter $S_2$. 
+energy normalization to study the collective dynamics of amphiphilic
+(Type I), biased hydrophobic (Type II), and bipolar (Type III) JPs under
+various flowing conditions (quiescent flow, linear shear flow, and
+Taylor-Green flow). Three quantities are computed to characterize the
+dynamics of the collective configurations of JPs: free energy $F$,
+strain parameter $E$, and scalar order parameter $S_2$. 
 %We quantify how
@@
 
-Within the framework of boundary integral equations, we derive a
-convenient expression for computing the free energy using the single
-layer potential (see equation~\eqref{eq:normal_deriv}). In a quiescent
-flow, the free energy profiles demonstrate that the relaxation process
-for particles confined in a certain size of box is independent of the
-number of particles. However, we find that the final configurations does
-depend on the initial distribution of particle directors $\dd_i$.
-Therefore, multiple patterns or local energy minimum states may appear
-depending on the initial setup.
+%Within the framework of boundary integral equations, we derive a
+%convenient expression for computing the free energy using the
+%single-layer potential (see equation~\eqref{eq:normal_deriv}).
+In a quiescent flow, the free energy profiles demonstrate that the
+relaxation process for particles confined in a certain size of box is
+independent of the number of particles. However, we find that the final
+configurations does depend on the initial distribution of particle
+directors $\dd_i$. Therefore, multiple patterns or local energy minimum
+states may appear depending on the initial setup.
 
@@
 a unilamellar vesicle that elongates and tank-treads, with the scalar
-order parameter increasing over time. The assembly of multi-lamella and
+order parameter increasing over time. The assembly of multilamellar and
 striated JP structures resemble a rigid body motion with minimal
@@
 changes. We further show that free energy, scalar order parameter, and
-strain are effective measures to quantitatively capture the collective hydrodynamics of
-JPs under a linear shear flow.
+strain are effective measures to quantitatively capture the collective
+hydrodynamics of JPs under a linear shear flow.
 
@@
 the size of the cell in the TG flow. On the other hand, the assembly of
-multi-lamella JPs and the striated JPs behave more like a rigid body
+multilamellar JPs and the striated JPs behave more like a rigid body
 with connected subdomains, and the number of subdomains increases with
-increasing strength of the TG flow. Overall, the multilamellar (BC (ii))
-JP assembly behaves as a shear-thinning fluid, while the striated (BC
-(iii)) JP assembly  possesses a yield stress.
+increasing strength of the TG flow. Overall, the multilamellar (Type II)
+JP assembly behaves as a shear-thinning fluid, while the striated (Type
+III) JP assembly possesses a yield stress.
 
@@
 McGlassonBradley2021, Vutukuri2020, Mallory2017}. The present study also
-helps us understand the rheology of JP oligomers that may be realized in
-the experiments. We are extending this study to three dimensional
-systems with more realistic features such as size distributions of JPs
-and thermal fluctuations~\cite{kohl-cor-che-vee22}. From a numerical
+helps to understand the rheology of JP oligomers that may be realized in
+experiments. We are extending this study to three dimensional systems
+with more realistic features such as size distributions of JPs and
+thermal fluctuations~\cite{kohl-cor-che-vee22}. From a numerical
 perspective, it is straightforward to include random perturbations in
@@
 \label{sec:appendix}
-The boundary integral calculation
-of \eqref{eq:free_energy2} relies
-on the following identity 
+The boundary integral calculation of~\eqref{eq:free_energy2} relies on
+the following identity 
 %
@@
 %
-Here, $\tt_\xx$ is the tangent vector and $\dif/\dif s$ is the
-arclength derivative.
-Substituting~\eqref{eq:normal_deriv}
+Here, $\tt_\xx$ is the tangent vector and $\dif/\dif s$ is the arclength
+derivative. Substituting~\eqref{eq:normal_deriv}
 into~\eqref{eq:free_energy2} for the normal derivative leads to the
-single layer, $\SSS$, which is more straightforward to evaluate.
-The arclength derivative is computed using
-the spectrally accurate Fourier differentiation.
+single layer, $\SSS$, which is more straightforward to evaluate. The
+arclength derivative is computed using the spectrally accurate Fourier
+differentiation.
 
@@
 \in {\partial \Omega}$, let $\nnu_{\xx}$ and $\nnu_{\yy}$ be the unit
-normal at $\xx$, respectively $\yy$, in ${\partial \Omega}$, and let $\zz \in
-\Omega$. The subscripts in $\nabla_{\zz}$ and $\nabla_{\yy}$ denote
-differentiation with respect to $\zz$, respectively $\yy$.
-
-Recall from~\eqref{eq:SL_BIE} that $u = \mathcal{D}[\sigma]$.
-Then  
+normal at $\xx$, respectively $\yy$, in ${\partial \Omega}$, and let
+$\zz \in \Omega$. The subscripts in $\nabla_{\zz}$ and $\nabla_{\yy}$
+denote differentiation with respect to $\zz$, respectively $\yy$.
+
+Recall from~\eqref{eq:SL_BIE} that $u = \mathcal{D}[\sigma]$. Then
 \begin{align*}
@@
 %
-Letting $\zz\to\xx\in{\partial \Omega}$, and noting that both sides of the equation
-are continuous, we obtain~\eqref{eq:normal_deriv}.
+Letting $\zz\to\xx\in{\partial \Omega}$, and noting that both sides of
+the equation are continuous, we obtain~\eqref{eq:normal_deriv}.
 
@@
 \begin{acknowledgments}
-%We thank Dr.~S\'ebastien Michelin and Dr.~Cecile Cottin-Bizzonne from LadHyX - Ecole Polytechnique Institut Polytechnique de Paris for organizing the focus-session ``interfacial active matter'' in the conference APS-DFD 2021 and the invitation of submitting a special collection paper.
 We thank useful conversations with E.~Corona, M.~Rachh, S.~Jiang, and
@@
 heads.%~\cite{Huetal19, deMeetal21}. 
-Fig~\ref{fig:relax}(c) shows the multilamellar structure with 8 layers when $N_b=60$. 
-The number of folds depends on several factors, for instances, number of
-particles and initial configurations.
-
-Finally, boundary condition \eqref{eq:bcs}(iii) models 
-a particle whose head surface repels the tail surface as proposed in
-\cite{MaRa76, Ma77}.
-The particles initially form chains with their directors perpendicular to the
-length of the chain. The equilibrium structure
-resembles a checkerboard pattern
-where each particle coordinates
-its head with the head of three other particles and its tail with the
-tail of three other particles. % Fig~\ref{fig:self-assembly}(c).
-Fig~\ref{fig:relax}(d) gives an example that this boundary condition results a checker board/stripes equilibrium state.
+Figure~\ref{fig:relax}(c) shows the multilamellar structure with 8
+layers when $N_b=60$.  The number of folds depends on several factors,
+for instances, number of particles and initial configurations.
+
+Finally, boundary condition \eqref{eq:bcs}(iii) models a particle whose
+head surface repels the tail surface as proposed in \cite{MaRa76, Ma77}.
+The particles initially form chains with their directors perpendicular
+to the length of the chain. The equilibrium structure resembles a
+checkerboard pattern where each particle coordinates its head with the
+head of three other particles and its tail with the tail of three other
+particles. Figure~\ref{fig:relax}(d) gives an example that this boundary
+condition results a checker board/stripes equilibrium state.
 
@@
 where $\dot\gamma$ is the shear rate. Fig~\ref{fig:shear_1} (a)--(c) show the snapshots of simulation results when $\dot\gamma=0.05$.
-We measure the ratio of major and minor axes $\lambda$ by adopting an ellipse fitting using the singular value decomposition and track this aspect ratio for this multi-lamellar structure when the flow is on.
-The result is shown in panel (d) and we observe that the multi-lamellar structure will be slightly stretched and the aspect ratio $\lambda=3.5$ increases over time.
+We measure the ratio of major and minor axes $\lambda$ by adopting an ellipse fitting using the singular value decomposition and track this aspect ratio for this multilamellar structure when the flow is on.
+The result is shown in panel (d) and we observe that the multilamellar structure will be slightly stretched and the aspect ratio $\lambda=3.5$ increases over time.
 %
@@
 previous section which is provided in panel (d).  The stiffness of the
-multi-lamellar structure is able to compete with the flow therefore the
-structure does not deform to any states other than multi-lamellar shape.
+multilamellar structure is able to compete with the flow therefore the
+structure does not deform to any states other than multilamellar shape.
 We also found that the flow strength coefficient above $V_0=0.1$ will
@@
 
-Here are demonstrations of having JP vesicle and multi-lamellar
+Here are demonstrations of having JP vesicle and multilamellar
 structure in a narrow channel under a shear flow. Simulation results
@@
   \vspace{-20pt}  
-  \caption{\label{fig:confined_lamellar} A JP multi-lamellar structure confined in a narrow channel where $N_b=40$ and $\dot\gamma=0.05$.  }
+  \caption{\label{fig:confined_lamellar} A JP multilamellar structure
+  confined in a narrow channel where $N_b=40$ and $\dot\gamma=0.05$.}
 \end{figure}

### 2023-03-21 doc/PRF2022/PRF_main.tex
yny

@@
   axis.} 
-  \todo[inline]{We propose to relate panel (f) to the pressure drops
-  across the JP vesicles. Also, panel (a) should be its own figure, and
-  (b)--(e) can be their own figure, but with darker stream lines. Also,
-  should not be talking about tank treading, but rather about sliding
-  between layers, and how they are affected by the correlation between
-  the bilayer location and the TG cell boundary. This correlation also
-  somehow determines the shape. Can count the number of partial TG cells
-  inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has 2 +
-  4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$, and
-  (e) has 1 cell.}
+%  \todo[inline]{We propose to relate panel (f) to the pressure drops
+%  across the JP vesicles. Also, panel (a) should be its own figure, and
+%  (b)--(e) can be their own figure, but with darker stream lines. Also,
+%  should not be talking about tank treading, but rather about sliding
+%  between layers, and how they are affected by the correlation between
+%  the bilayer location and the TG cell boundary. This correlation also
+%  somehow determines the shape. Can count the number of partial TG cells
+%  inside each of the JP bilayer vesicles. (b) has 9 cells, (c) has 2 +
+%  4*0.5 cells, (d) has 1 + 4$\epsilon$ cells where $\epsilon < 1/4$, and
+%  (e) has 1 cell.}
 \end{figure}
@@
 the geometry of the JP phases, we initialize a circular vesicle bilayer
-in various TG-flow cell sizes (Figure \ref{fig:PramChange}(b)--(e)). In
-all cases, the vesicle and TG flow reach a steady-state tank-treading
-motion \todo[inline]{no longer true}, but the geometry and motion varies
-non-monotonically. For $\lambda$ ranging from $1$ nm to $4$ nm, the
-steady-state vesicle shape goes from an octagon, to a dimpled square, to
-a rounded diamond, to a rounded square. Surprisingly, the direction of
-rotation switches: for $\lambda = 2$ nm the rotation is clockwise, while
-for $\lambda = 4$ nm the rotation is counterclockwise. Finally, we
-calculate the vesicle area $A$ and length $L$. As shown in
+in various TG-flow cell sizes $\lambda$ ranging from $\lambda=1$ nm in 
+figure~\ref{fig:PramChange}(b) to $\lambda=4$ nm in figure~\ref{fig:PramChange}(e).
+As shown in the supplementary material, these JP vesicles fluctuate/deform around a
+steady shape of an octagon ($\lambda=1$ nm), a dimpled square ($\lambda=2$ nm),
+a rounded diamond ($\lambda=3$ nm), and a rounded rectangle ($\lambda=4$ nm).
+
+For $\lambda=1$ nm and $\lambda=2$ nm, multiple TG cells are inside the JP vesicle
+as the inner leaflet of JPs move clockwise along the boundary faster than the outer leaflet.
+For $\lambda=3$ nm and $\lambda=4$ nm, there is only one TG cell inside the JP vesicle
+and the JPs in the bilayer tank-treading in the counter-clockwise direction
+(Figure \ref{fig:PramChange}(b)--(e)). 
+%
+Finally, we calculate the vesicle area $A$ and length $L$. As shown in
 Figure~\ref{fig:PramChange}(f), the relative area $A/A_0$ achieves a

### 2023-03-21 doc/PRF2022/PRF_main.tex
yny

@@
   of a vesicle is in a TG flow at $t=1$ $\upmu$s with $l= 1,2,3,4$,
-  respectively. In panel (f), the relative enclosed area $A/A_0$
-  calculated from the bilayer midplane decreases over time. The inset
-  shows the relative length $L/L_0$ which remains nearly constant with a
-  small oscillation. The inset and main panel have the same horizontal
+  respectively. In panel (f), the relative enclosed area $A/A_0$ decreases over time. The inset
+  shows the relative length $L/L_0$ which remains nearly constant with
+  small fluctuations. The inset and main panel have the same horizontal
   axis.} 
@@
 This points to an inverse-quadratic scaling in length.
-Figure~\ref{fig:PramChange}(a) summarizes the findings and suggest the
+Figure~\ref{fig:PramChange}(a) summarizes the findings and suggests the
 scaling

### 2023-03-22 doc/PRF2022/PRF_main.tex

@@
 bilayer phase is slightly shear thickening
-(Figure~\ref{fig:rheologysummary}(a), solid curve). The multilamellar
-phase consisting of Type II JPs is somewhat shear thinning, but its
-viscosity is larger than for Type I. Finally, the striated phase is
-strongly shear-thinning. This further explains the rigid-like behavior
-of the striated phase found in the strain, shear-rate relationships from
+(Figure~\ref{fig:rheologysummary}(a), solid curve). Similar shear
+thickening behaviors are found in continuum vesicle
+models~\cite{rah-vee-bir2010}. The multilamellar phase consisting of
+Type II JPs is somewhat shear thinning, but its viscosity is larger than
+for Type I. Finally, the striated phase is strongly shear-thinning. This
+further explains the rigid-like behavior of the striated phase found in
+the strain, shear-rate relationships from
 Figures~\ref{fig:s2esummary}(a) and (b) (triangles).
-\todo[inline]{RBC flow references}
 
@@
   of a vesicle is in a TG flow at $t=1$ $\upmu$s with $l= 1,2,3,4$,
-  respectively. In panel (f), the relative enclosed area $A/A_0$ decreases over time. The inset
-  shows the relative length $L/L_0$ which remains nearly constant with
-  small fluctuations. The inset and main panel have the same horizontal
-  axis.} 
+  respectively. In panel (f), the relative enclosed area $A/A_0$
+  decreases over time. The inset shows the relative length $L/L_0$ which
+  remains nearly constant with small fluctuations. The inset and main
+  panel have the same horizontal axis.} 
 %  \todo[inline]{We propose to relate panel (f) to the pressure drops
@@
 to 10\% (collectively denoted $\Delta c/c$) leads to roughly twice the
-relative \emph{decrease} (resp.~increase) in the critical shear rate.
-This points to an inverse-quadratic scaling in length.
+relative decrease (resp.~increase) in the critical shear rate. This
+points to an inverse-quadratic scaling in length.
 Figure~\ref{fig:PramChange}(a) summarizes the findings and suggests the
@@
 in various TG-flow cell sizes $\lambda$ ranging from $\lambda=1$ nm in
-figure~\ref{fig:PramChange}(b) to $\lambda=4$ nm in figure~\ref{fig:PramChange}(e).
-As shown in the supplementary material, these JP vesicles fluctuate/deform around a
-steady shape of an octagon ($\lambda=1$ nm), a dimpled square ($\lambda=2$ nm),
-a rounded diamond ($\lambda=3$ nm), and a rounded rectangle ($\lambda=4$ nm).
-
-For $\lambda=1$ nm and $\lambda=2$ nm, multiple TG cells are inside the JP vesicle
-as the inner leaflet of JPs move clockwise along the boundary faster than the outer leaflet.
-For $\lambda=3$ nm and $\lambda=4$ nm, there is only one TG cell inside the JP vesicle
-and the JPs in the bilayer tank-treading in the counter-clockwise direction
-(Figure \ref{fig:PramChange}(b)--(e)). 
+Figure~\ref{fig:PramChange}(b) to $\lambda=4$ nm in
+Figure~\ref{fig:PramChange}(e). As shown in the Supplementary Material,
+these JP vesicles fluctuate and deform around a steady shape of an
+octagon ($\lambda=1$~nm), a dimpled square ($\lambda=2$~nm), a rounded
+diamond ($\lambda=3$~nm), and a rounded rectangle ($\lambda=4$~nm).
+
+For $\lambda=1$~nm and $\lambda=2$~nm, multiple TG cells are inside the
+JP vesicle as the inner leaflet of JPs move clockwise along the boundary
+faster than the outer leaflet. For $\lambda=3$~nm and $\lambda=4$~nm,
+there is only one TG cell inside the JP vesicle and the JPs in the
+bilayer tank-tread in the counter-clockwise direction (Figure
+\ref{fig:PramChange}(b)--(e)). 
 %
@@
 Figure~\ref{fig:PramChange}(f), the relative area $A/A_0$ achieves a
-steady-state that is greatest for $\lambda = 4$ nm yet least for
-$\lambda = 2$ nm. The relative length $L/L_0$, however, is constant in
+steady-state that is greatest for $\lambda = 4$~nm yet least for
+$\lambda = 2$~nm. The relative length $L/L_0$, however, is constant in
 $t$ for all cell sizes (Figure~\ref{fig:PramChange}(e), inset). In other

### 2023-03-22 doc/PRF2022/PRF_main.tex
minor fix by peter

@@
 Figure~\ref{fig:PramChange}(b) to $\lambda=4$ nm in
-Figure~\ref{fig:PramChange}(e). As shown in the Supplementary Material,
+Figure~\ref{fig:PramChange}(e). As shown in the Supplementary Material Movie S6,
 these JP vesicles fluctuate and deform around a steady shape of an

### 2023-03-22 doc/PRF2022/Supplementary.tex
minor fix by peter

@@
 \noindent
-{\bf Movie S6. Single Vesicle in a Taylor-Green Flow with Various $\lambda$ Values} 
-The parameter $\lambda$ controls the cell size in Taylor-Green flow. 
-$\lambda$ values are varied from 1.0 to 4.0 while the flow rate $\lambda\dot\gamma=0.1$ is fixed.
-There is a rotation transition from counterclockwise ($\lambda=1$ nm and  2 nm) to clockwise ($\lambda=3$ nm and 4 nm).
-\\
+{\label{MovieS6}\bf Movie S6. Single Vesicle in a Taylor-Green Flow with Various $\lambda$ Values} 
+A circular vesicle bilayer is placed in the Taylor-Green flow. 
+The parameter $\lambda$ controls the cell size and the values are varied from 1.0 nm to 4.0 nm while the flow rate $\lambda\dot\gamma=0.1$ is fixed.
+There is a rotation transition from clockwise ($\lambda=1$ nm and  2 nm) to counterclockwise ($\lambda=3$ nm and 4 nm).
+Moreover, the resulting steady shapes of all cases are different polygons.
+We plot the streamlines in the background.\\
 

### 2023-03-22 doc/PRF2022/Supplementary.tex

--- 2023-03-17 doc/PRF2022/Supplementary.tex
@@
 
-\section{Movie Captions}\mbox{} \\
+\section{Movie Descriptions}
+We consider suspensions of JPs of radius 1.25~nm. The time step size for
+all simulations is $\Delta t = 0.2$~ns. The colors of the JPs are as
+follows: for Type I and Vesicles, red is hydrophobic ($\max g > 0$) and
+blue is hydrophilic ($\min g = 0$); for Type II, red is more hydrophobic
+($\max g >0$) than blue ($\min g > 0$); for Type III, red is positively
+charged ($\max g > 0$) and blue is negatively charged ($\min g < 0$).
+%\mbox{} \\
 
 \noindent
-{\bf Movie S1. Relaxation} 
-There are 60 circular particles with radius 1.25~nm that are initially
-confined in a square box. The simulation results show the relaxation
-with each of the three boundary conditions. The time step of all
-simulations is $\Delta t=0.2$. The color on the boundary from blue to
-red is for $\min g(\xx)$ to $\max g(\xx)$. All final configurations are
-adopted in simulations with hydrodynamic flows. \\
+{\bf Relaxation}: The relaxation of 60 circular JPs that are initialized
+with random locations and orientations. The JPs self-assemble into
+unilamellar (Type I), multilamellar (Type II), and striated (Type III)
+configurations. The final configurations are used as initial conditions
+for the simulations that include a background flow.
+
+%There are 60 circular particles with radius 1.25~nm that are initially
+%confined in a square box. The simulation results show the relaxation
+%with each of the three boundary conditions. The time step of all
+%simulations is $\Delta t=0.2$. The color on the boundary from blue to
+%red is for $\min g(\xx)$ to $\max g(\xx)$. All final configurations are
+%adopted in simulations with hydrodynamic flows. \\
 
 \noindent
-{\bf Movie S2. Structures in a Shear Flow without Ruptures} 
-We adopt the relaxed configurations and place the JP structures in the
-shear flow. For the choices of the shear rate, we pick: $\dot\gamma =
-0.05$ for the vesicle, $\dot\gamma = 0.05$ for the bilayer, $\dot\gamma
-= 0.05$ for the multi-lamellar, and $\dot\gamma = 0.1$ for the striated
-configurations. The vesicle case undergoes tank-treading whereas the
-initially disordered BC (i) case increases orientational order. The
-multilamellar assemply behaves as a rigid body, and the striated
-configuration moreso. No ruptures occur. \\
+{\bf Structures in a Weak Shear Flow}:
+The relaxed configurations of the 60 JPs are subjected to a weak shear
+flow. The shear rate is $\dot{\gamma} = 0.05$~ns$^{-1}$ for the Vesicle,
+Type I, and Type II configurations, and $\dot{\gamma} = 0.1$~ns$^{-1}$
+for the Type III configuration. The vesicle undergoes tank-treading and
+the bilayer increases its orientational order. The multilamellar
+configuration resembles a rigid body motion, and the striated
+configuration has an even stronger resemblance to a rigid body motion.
+No ruptures occur in these examples.
+
+%We adopt the relaxed configurations and place the JP structures in the
+%shear flow. For the choices of the shear rate, we pick: $\dot\gamma =
+%0.05$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.05$ ns$^{-1}$ for the
+%bilayer, $\dot\gamma = 0.05$ ns$^{-1}$ for the multi-lamellar, and
+%$\dot\gamma = 0.1$ ns$^{-1}$ for the striated configurations. The
+%vesicle case undergoes tank-treading whereas the initially disordered
+%BC (i) case increases orientational order. The multilamellar assemply
+%behaves as a rigid body, and the striated configuration moreso. No
+%ruptures occur. \\
 
 \noindent
-{\bf Movie S3. Structures in a Taylor-Green Flow without Ruptures} 
-We adopt the relaxed configurations and place the JP structures in the
-Taylor-Green flow at low flow rates. For the choices of the flow
-strength, we pick: $V_0 = 0.1$ for the vesicle, $V_0 = 0.1$ for the
-disordered bilayer, $V_0 = 0.1$ for the multi-lamellar, and $V_0 = 0.2$
-for the striated configurations. The vesicle stays inact, whereas the
-dissordered bilayer is pulled apart. Like in Supplementary Movie S2, the
-striated assembly is basically rigid. \\
+{\bf Structures in a Weak Taylor-Green Flow}:
+The relaxed configurations of the 60 JPs are subjected to a weak
+Taylor-Green flow. The flow rate is $\dot{\gamma} = 0.05$~ns$^{-1}$ for
+the Vesicle, Type I, and Type II configurations, and $\dot{\gamma} =
+0.1$~ns$^{-1}$ for the Type III configuration. The vesicle stays intact,
+whereas the bilayer is pulled apart into different TG cells. Like in the
+weak shear flow example, the multilamellar and striated configurations
+behave as rigid bodies.
+
+%For the choices of the flow strength, we pick: $\dot\gamma = 0.05$
+%ns$^{-1}$ for the vesicle, $\dot\gamma = 0.05$ ns$^{-1}$ for the
+%disordered bilayer, $\dot\gamma = 0.05$ ns$^{-1}$ for the
+%multi-lamellar, and $\dot\gamma = 0.1$ ns$^{-1}$ for the striated
+%configurations. The vesicle stays inact, whereas the dissordered
+%bilayer is pulled apart. Like in Supplementary Movie S2, the striated
+%assembly is basically rigid. \\
+
+%We adopt the relaxed configurations and place the JP structures in the
+%Taylor-Green flow at low flow rates. For the choices of the flow
+%strength, we pick: $\dot\gamma = 0.05$ ns$^{-1}$ for the vesicle,
+%$\dot\gamma = 0.05$ ns$^{-1}$ for the disordered bilayer, $\dot\gamma =
+%0.05$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.1$
+%ns$^{-1}$ for the striated configurations. The vesicle stays inact,
+%whereas the dissordered bilayer is pulled apart. Like in Supplementary
+%Movie S2, the striated assembly is basically rigid. \\
 
 \noindent
-{\bf Movie S4. Structures in a Shear Flow with Ruptures} 
-We adopt the relaxed configurations and place the JP structures in the
-shear flow at a higher shear rate. For the choices of the shear rate, we
-pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ for the
-bilayer, $\dot\gamma = 0.15$ for the multi-lamellar, and $\dot\gamma =
-0.15$ for the striated configurations. The time step of all simulations
-is $\Delta t=0.2$. In this movie, some clear structural ruptures occur
-in each case. In order to observe the structure behaviors at later time,
-we stabilize the frame by tracking the center of mass position of all
-JP. \\
+{\bf Structures in a Strong Shear Flow}:
+The relaxed configurations of the 60 JPs are subjected to a strong shear
+flow. The shear rate is $\dot{\gamma} = 0.075$~ns$^{-1}$ for the Vesicle
+configuration, $\dot{\gamma} = 0.1$~ns$^{-1}$ for the Type I
+configuration, and $\dot{\gamma} = 0.15$~ns$^{-1}$ for the Type II and
+Type III configurations. In all cases, the structure is ruptured by the
+flow. The frames are stabilized by moving with the center of mass of all
+the JPs.
+
+%We adopt the relaxed configurations and place the JP structures in the
+%shear flow at a higher shear rate. For the choices of the shear rate, we
+%pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ ns$^{-1}$
+%for the bilayer, $\dot\gamma = 0.15$ ns$^{-1}$ for the multi-lamellar,
+%and $\dot\gamma = 0.15$ ns$^{-1}$ for the striated configurations. The
+%time step of all simulations is $\Delta t=0.2$ ns$^{-1}$. In this movie,
+%some clear structural ruptures occur in each case. In order to observe
+%the structure behaviors at later time, we stabilize the frame by
+%tracking the center of mass position of all JP. \\
 
 \noindent
-{\bf Movie S5. Structures in a Taylor-Green Flow with Ruptures} 
-We adopt the relaxed configurations and place the JP structures in the
-Taylor-Green flow at higher flow rates. For the choices of the flow
-strength, we pick: $V_0 = 0.2$ for the vesicle, $V_0 = 0.2$ for the
-bilayer, $V_0 = 0.2$ for the multi-lamellar, and $V_0 = 0.3$ for the
-striated configurations. Clear structural ruptures occur in each case.
-In all cases, there is significant reduction in the orientational order
-of the assemblies. While the BC (i) cases are broken into several
-pieces, the main body of the BC (ii) and BC (iii) assemblies are not
-pulled apart by the background flow.
+{\bf Structures in a Strong Taylor-Green Flow}:
+The relaxed configurations of the 60 JPs are subjected to a strong
+Taylor-Green flow. The flow rate is $\dot{\gamma} = 0.1$~ns$^{-1}$ for
+the Vesicle, Type I, and Type II configurations, and $\dot{\gamma} =
+0.15$~ns$^{-1}$ for the Type III configuration. In all cases, the
+structure is ruptured by the flow and there is a significant reduction
+in the orientation order. While the Vesicle Type I configurations are
+broken into several pieces, the main body of the Type II and Type III
+configurations are not pulled apart by the background flow.
+
+%We adopt the relaxed configurations and place the JP structures in the
+%Taylor-Green flow at higher flow rates. For the choices of the flow
+%strength, we pick: $\dot\gamma = 0.1$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.1$ ns$^{-1}$ for the
+%bilayer, $\dot\gamma = 0.1$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.15$ ns$^{-1}$ for the
+%striated configurations. Clear structural ruptures occur in each case.
+%In all cases, there is significant reduction in the orientational order
+%of the assemblies. While the BC (i) cases are broken into several
+%pieces, the main body of the BC (ii) and BC (iii) assemblies are not
+%pulled apart by the background flow.\\
+
+\noindent
+%{\label{MovieS6}\bf JP Vesicle in a Taylor-Green Flow with Various
+%$\lambda$ Values}: 
+{\label{MovieS6}\bf JP Vesicle in Various Taylor-Green Flows}: A
+circular vesicle bilayer is placed in a Taylor-Green flow. The parameter
+$\lambda$ controls the TG cell size and the values are varied from 1~nm
+to 4~nm while the flow rate is chosen so that
+$\lambda\dot\gamma=0.1$~nm/ns. The parameter $\lambda$ determines the
+steady-state polygonal tank-treading shape. The rotation direction is
+clockwise for $\lambda=1$~nm and $\lambda=2$~nm, and counterclockwise
+for $\lambda=3$~nm and $\lambda=4$~nm. Streamlines of the flow are
+included.
+
+%A circular vesicle bilayer is placed in the Taylor-Green flow.  The
+%parameter $\lambda$ controls the cell size and the values are varied
+%from 1.0 nm to 4.0 nm while the flow rate $\lambda\dot\gamma=0.1$ is
+%fixed. There is a rotation transition from clockwise ($\lambda=1$ nm and
+%2 nm) to counterclockwise ($\lambda=3$ nm and 4 nm). Moreover, the
+%resulting steady shapes of all cases are different polygons. We plot the
+%streamlines in the background.\\
 

### 2023-03-22 doc/PRF2022/Supplementary.tex
wworking on supp

@@
 \section{Movie Descriptions}
+\label{sec:movie_description}
 We consider suspensions of JPs of radius 1.25~nm. The time step size for
@@
 The following figures plot the fully resolved simulation time-courses
-organized in terms of the bilayer, vesicle BL, multilamellar, and striated JP phases
-under shear flow (Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:stshraw})
-and under TG flow (Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
-Throughout, panels (a) are for relative free energy $F - F_0$,
-panels (b) for alignment $S_2$, and panels (c) for strain $E$ (as a percentage). 
-A common ordinate is used for each of the respective panels to facilitate
-comparison between data sets. 
+organized in terms of the bilayer, vesicle BL, multilamellar, and
+striated JP configurations under shear flow (Supplementary
+Figures~\ref{fig:ulshraw}--\ref{fig:stshraw}) and under TG flow
+(Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
+Throughout, panels (a) are for relative free energy $F - F_0$, panels
+(b) for alignment $S_2$, and panels (c) are for strain $E$ (as a
+percentage).  A common ordinate is used for each of the respective
+panels to facilitate comparison between data sets. 
 %\newpage
@@
 \end{center}
-\caption{
-Relative free energy $F - F_0$,
-alignment $S_2$, and strain $E$ for
-Type I, bilayer phase under shear flow with choices of shear rates $\dot\gamma=0.013$ -- $0.075$ ns$^{-1}$.
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type I, bilayer phase under shear flow with shear
+  rates $\dot\gamma=0.013$ -- $0.075$ ns$^{-1}$.
 %The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
@@
 \end{center}
-\caption{
-Relative free energy $F - F_0$,
-alignment $S_2$, and strain $E$ for
-Type I, bilayer phase under shear flow with choices of shear rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.
-The JP type is the same as for Supplementary Figure \ref{fig:ulshraw} but with a
-ring-shaped, rather than disordered, bilayer for initial configuration.  
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type I, bilayer phase under shear flow with shear
+  rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.  The JP type is the same
+  as Figure \ref{fig:ulshraw} except with a vesicle-shaped initial
+  configuration rather than a
+  disordered bilayer.  
 %A Vesicle under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.075$.
@@
 \end{center}
-\caption{
-Relative free energy $F - F_0$,
-alignment $S_2$, and strain $E$ for
-Type II, multilamellar phase under shear flow with choices of shear rates $\dot\gamma=0.025$ -- $0.075$ ns$^{-1}$.
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type II, multilamellar phase under shear flow with
+  shear rates $\dot\gamma=0.025$ -- $0.075$ ns$^{-1}$.
 %A multilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.025\sim0.075$.
@@
 \end{center}
-\caption{
-Relative free energy $F - F_0$,
-alignment $S_2$, and strain $E$ for
-Type III, striated phase under shear flow with choices of shear rates $\dot\gamma=0.01$ -- $0.07$ ns$^{-1}$.
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type III, striated phase under shear flow with
+  shear rates $\dot\gamma=0.01$ -- $0.07$ ns$^{-1}$.
 %A striated JP structure under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.07$.
@@
 alignment $S_2$, and strain $E$ for
-Type I, bilayer phase under TG flow with choices of shear rates $\dot\gamma=0.013$ -- $0.05$ ns$^{-1}$.
+Type I, bilayer phase under TG flow with shear rates $\dot\gamma=0.013$ -- $0.05$ ns$^{-1}$.
 %A unilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.013\sim0.05$.
@@
 alignment $S_2$, and strain $E$ for
-Type I, vesicle bilayer phase under TG flow with choices of shear rates $\dot\gamma=0.005$ -- $0.044$ ns$^{-1}$.
+Type I, vesicle bilayer phase under TG flow with shear rates $\dot\gamma=0.005$ -- $0.044$ ns$^{-1}$.
 The JP type is the same as for Supplementary Figure \ref{fig:ultgraw} but with a
@@
 alignment $S_2$, and strain $E$ for
-Type II, multilamellar phase under TG flow with choices of shear rates $\dot\gamma=0.025$ -- $0.069$ ns$^{-1}$.
+Type II, multilamellar phase under TG flow with shear rates $\dot\gamma=0.025$ -- $0.069$ ns$^{-1}$.
 %A multilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.025\sim0.069$.
@@
 alignment $S_2$, and strain $E$ for
-Type III, striated phase under TG flow with choices of shear rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.
+Type III, striated phase under TG flow with shear rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.
 %A striated JP structure under a TG flow with choices of shear rates $\dot\gamma=0.01\sim0.069$.

### 2023-03-22 doc/PRF2022/Supplementary.tex
finishing up supp material

@@
   (c) strain $E$ for Type I, bilayer phase under shear flow with shear
-  rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.  The JP type is the same
+  rates $\dot\gamma=0.01$--$0.075$ ns$^{-1}$.  The JP type is the same
   as Figure \ref{fig:ulshraw} except with a vesicle-shaped initial
@@
   (c) strain $E$ for Type II, multilamellar phase under shear flow with
-  shear rates $\dot\gamma=0.025$ -- $0.075$ ns$^{-1}$.
+  shear rates $\dot\gamma=0.025$--$0.075$ ns$^{-1}$.
 %A multilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.025\sim0.075$.
@@
   (c) strain $E$ for Type III, striated phase under shear flow with
-  shear rates $\dot\gamma=0.01$ -- $0.07$ ns$^{-1}$.
+  shear rates $\dot\gamma=0.01$--$0.07$ ns$^{-1}$.
 %A striated JP structure under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.07$.
@@
 \end{center}
-\caption{
-Relative free energy $F - F_0$,
-alignment $S_2$, and strain $E$ for
-Type I, bilayer phase under TG flow with shear rates $\dot\gamma=0.013$ -- $0.05$ ns$^{-1}$.
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type I, bilayer phase under TG flow with flow 
+  rates $\dot\gamma=0.013$--$0.05$ ns$^{-1}$.
 %A unilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.013\sim0.05$.
@@
 \end{center}
-\caption{
-Relative free energy $F - F_0$,
-alignment $S_2$, and strain $E$ for
-Type I, vesicle bilayer phase under TG flow with shear rates $\dot\gamma=0.005$ -- $0.044$ ns$^{-1}$.
-The JP type is the same as for Supplementary Figure \ref{fig:ultgraw} but with a
-ring-shaped, rather than disordered, bilayer for initial configuration.  
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type I, vesicle bilayer phase under TG flow with
+  flow rates $\dot\gamma=0.005$--$0.044$ ns$^{-1}$. The JP type is the
+  same as Figure~\ref{fig:ultgraw} except with a vesicle-shaped initial
+  configuration rather than a disordered bilayer.
 %A vesicle JP structure under a TG flow with choices of shear rates $\dot\gamma=0.005\sim0.044$.
@@
 \end{center}
-\caption{
-Relative free energy $F - F_0$,
-alignment $S_2$, and strain $E$ for
-Type II, multilamellar phase under TG flow with shear rates $\dot\gamma=0.025$ -- $0.069$ ns$^{-1}$.
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type II, multilamellar phase under TG flow with
+  flow rates $\dot\gamma=0.025$--$0.069$~ns$^{-1}$.
 %A multilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.025\sim0.069$.
@@
 \end{center}
-\caption{
-Relative free energy $F - F_0$,
-alignment $S_2$, and strain $E$ for
-Type III, striated phase under TG flow with shear rates $\dot\gamma=0.01$ -- $0.075$ ns$^{-1}$.
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type III, striated phase under TG flow with flow
+  rates $\dot\gamma=0.01$--$0.075$~ns$^{-1}$.
 %A striated JP structure under a TG flow with choices of shear rates $\dot\gamma=0.01\sim0.069$.

### 2023-03-22 doc/PRF2022/PRF_main.tex

--- 2023-03-22 doc/PRF2022/PRF_main.tex
@@
 
+See Section~\ref{sec:movie_description} in the [Supplementary Material]
+for movies showing the transition of 60 JPs that are initialized
+randomly (inset of Figure~\ref{fig:relax}(a)) to the steady state
+configurations (inset of Figures~\ref{fig:relax}(b), (d), and (e)).
+
 %\begin{figure}
@@
 phases in background flow. Although the plots only show the region near
-the JP phases, the fluid velocity $\uu$ and order parameter $u$ are
-accounted for in all of $\mathbb{R}^2$. Moreover, $\uu$ satisfies the
-rigid boundary condition at every JP-fluid interface i.e., the particles
+the JPs, the fluid velocity $\uu$ and order parameter $u$ are accounted
+for in all of $\mathbb{R}^2$. Moreover, $\uu$ satisfies the rigid
+boundary condition at every JP-fluid interface i.e., the particles
 interact with the local flow field and are not merely carried by
-background flow.
+background flow. See Section~\ref{sec:movie_description} in the
+[Supplementary Material] for movies showing the dynamics of the JP
+suspensions in Figure~\ref{fig:s2esummary}.
 
@@
 proportional to $\gamma^*$ since the striated phase tends to cleave
-during rupture (see Supplementary Movie S4). Our previous
+during rupture (see Supplementary movie). Our previous
 work~\cite{Fu2022_JFM} found the scaling $\mu \dot\gamma_* =
@@
 Figure~\ref{fig:PramChange}(b) to $\lambda=4$ nm in
-Figure~\ref{fig:PramChange}(e). As shown in the Supplementary Material,
-these JP vesicles fluctuate and deform around a steady shape of an
+Figure~\ref{fig:PramChange}(e).
+%As shown in the Supplementary Material Movie S6,
+These JP vesicles fluctuate and deform around a steady shape of an
 octagon ($\lambda=1$~nm), a dimpled square ($\lambda=2$~nm), a rounded
-diamond ($\lambda=3$~nm), and a rounded rectangle ($\lambda=4$~nm).
+diamond ($\lambda=3$~nm), and a rounded rectangle ($\lambda=4$~nm). See
+Section~\ref{sec:movie_description} in the [Supplementary Material] for
+a movie showing the dynamics of the JP vesicle for the four different
+values of $\lambda$ in Figure~\ref{fig:PramChange}(b)--(e).
 

### 2023-03-22 doc/PRF2022/PRF_main.tex
\dot\gamma checks

@@
 commensurate drops in panels (c) and (d) indicate the existence of a
-critical shear rate $\gamma_*$. This means that for $\gamma < \gamma_*$,
-the JP phase remains intact while for $\gamma > \gamma_*$, the phase
-ruptures. For example, the vesicle BL phase has $\gamma_*$ approximately
+critical shear rate $\dot\gamma_*$. This means that for $\dot\gamma < \dot\gamma_*$,
+the JP phase remains intact while for $\dot\gamma > \dot\gamma_*$, the phase
+ruptures. For example, the vesicle BL phase has $\dot\gamma_*$ approximately
 $0.05$ ns$^{-1}$ under shear flow and TG flow. However, the critical
 shear rate is flow-pattern dependent because the striated phase has
-$\gamma_* = 0.14$ ns$^{-1}$ under shear flow while $\gamma_* = 0.05$
+$\dot\gamma_* = 0.14$ ns$^{-1}$ under shear flow while $\dot\gamma_* = 0.05$
 ns$^{-1}$ under TG flow. Due to variable stress distribution, the

### 2023-03-23 doc/PRF2022/Supplementary.tex
removed word 'ordinate'
finished up my changesg

@@
 %$\lambda$ Values}: 
-{\label{MovieS6}\bf JP Vesicle in Various Taylor-Green Flows}: A
-circular vesicle bilayer is placed in a Taylor-Green flow. The parameter
-$\lambda$ controls the TG cell size and the values are varied from 1~nm
-to 4~nm while the flow rate is chosen so that
-$\lambda\dot\gamma=0.1$~nm/ns. The parameter $\lambda$ determines the
-steady-state polygonal tank-treading shape. The rotation direction is
-clockwise for $\lambda=1$~nm and $\lambda=2$~nm, and counterclockwise
-for $\lambda=3$~nm and $\lambda=4$~nm. Streamlines of the flow are
-included.
+{\bf JP Vesicle in Various Taylor-Green Flows}: A circular vesicle
+bilayer is placed in a Taylor-Green flow. The parameter $\lambda$
+controls the TG cell size and the values are varied from 1~nm to 4~nm
+while the flow rate is chosen so that $\lambda\dot\gamma=0.1$~nm/ns. The
+parameter $\lambda$ determines the steady-state polygonal tank-treading
+shape. The rotation direction is clockwise for $\lambda=1$~nm and
+$\lambda=2$~nm, and counterclockwise for $\lambda=3$~nm and
+$\lambda=4$~nm. Streamlines of the flow are included.
 
@@
 Throughout, panels (a) are for relative free energy $F - F_0$, panels
-(b) for alignment $S_2$, and panels (c) are for strain $E$ (as a
-percentage).  A common ordinate is used for each of the respective
-panels to facilitate comparison between data sets. 
+(b) are for alignment $S_2$, and panels (c) are for strain $E$ (as a
+percentage). The same vertical and horizontal axes are used for each of
+the respective panels to facilitate comparison between data sets. 
 %\newpage
@@
   (c) strain $E$ for Type I, bilayer phase under shear flow with shear
-  rates $\dot\gamma=0.01$--$0.075$ ns$^{-1}$.  The JP type is the same
-  as Figure \ref{fig:ulshraw} except with a vesicle-shaped initial
-  configuration rather than a
-  disordered bilayer.  
+  rates $\dot\gamma=0.01$--$0.075$ ns$^{-1}$. The JP type is the same as
+  Figure \ref{fig:ulshraw} except with a vesicle-shaped initial
+  configuration rather than a disordered bilayer.
 %A Vesicle under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.075$.

### 2023-03-24 doc/PRF2022/PRF_main.tex

@@
 
-Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} contain the
-fully-resolved time courses for the free energy $F$, alignment order
-$S_2$, and strain $E$. The eight setups correspond to the four JP
-phases---bilayer, vesicle BL, multilamellar, and striated---and two
-background flows---shear and TG, and the data are plotted with the same
-ordinate to facilitate comparisons between simulation setups. Each setup
-considers a range of shear rates $\dot \gamma$ in the interval $[0,
-0.2]$ ns$^{-1}$.
-
-The fully-resolved time courses in Supplementary
-Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} contain significant
-oscillations due to the particle-based formulation and tumbling inherent
-to the background flows. To extract meaningful data, we further
-post-process the $F$, $S_2$, $E$ curves by taking their time average
-over the interval $t \in [0, T]$.
+Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} in the [Supplementary
+Material] contain the fully-resolved time courses for the free energy
+$F$, alignment order $S_2$, and strain $E$. The eight setups correspond
+to the four JP phases---bilayer, vesicle BL, multilamellar, and
+striated---and two background flows---shear and TG, and the data are
+plotted with the same vertical and horizontal axes to facilitate
+comparisons between simulation setups. Each setup considers a range of
+shear rates $\dot \gamma$ in the interval $[0, 0.2]$ ns$^{-1}$.
+
+The fully-resolved time courses in
+Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} in the [Supplementary
+Material] contain significant oscillations due to the particle-based
+formulation and tumbling inherent to the background flows. To extract
+meaningful data, we further post-process the $F$, $S_2$, $E$ curves by
+taking their time average over the interval $t \in [0, T]$.
 
@@
 Figure~\ref{fig:fsummary} plots the time-averaged relative free energy
-$\frac{1}{T}\int_0^T F - F_0 \,\dif t$ where $F_0$
+$\frac{1}{T}\int_0^T (F - F_0) \,\dif t$ where $F_0$
 is~\eqref{eq:free_energy2} at $t = 0$. The greatest increase occurs with
@@
 background flow leads to oscillation in the strain time courses making
-systematic fitting challenging (see Supplementary Material
+systematic fitting challenging (see [Supplementary Material]
 Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}). The integral

### 2023-03-24 doc/PRF2022/PRF_main.tex
rheology refs added

@@
 thickening behaviors are found in continuum vesicle
-models~\cite{rah-vee-bir2010}. The multilamellar phase consisting of
+models~\cite{rah-vee-bir2010,NaitOuhra2019RheologyOA}.
+The multilamellar phase consisting of
 Type II JPs is somewhat shear thinning, but its viscosity is larger than
@@
 dilute limit, one expects viscosities ten or more times greater than the
-viscosity of water~\cite{Konijn2014ExperimentalSO}.
-
-Nevertheless, further simulations are required to differentiate between
-purely suspension effects and particles' preferred alignments. For
-example, the difference between the values 14~mPa~s for Type I and
+viscosity of water~\cite{Konijn2014ExperimentalSO}
+and number of analytical and numerical
+approaches have been successfully applied to these dense suspensions
+\citep{Guazzelli2018RheologyOD}.
+
+Further parametric studies are required to differentiate
+between passive effects and JPs' preferred alignments. 
+For example, the difference between the values 14~mPa~s for Type I and
 21~mPa~s for Type II JPs can be explained by the fact that the
@@
 III JPs where viscosity is effectively infinite for low strain rates
-(Figure \ref{fig:rheologysummary}(c)), is related to particle
-coordination. To leading order, a single particle coordinates with: one
+(Figure~\ref{fig:rheologysummary}(c)), is related to particle
+coordination. That is, a single JP coordinates with: one
 neighbor in the apposing bilayer for Type I, two neighbors at the tail
@@
 and right) for Type III.
+
+Scaling laws for the ``virial viscosity'', the nonhydrodynamic part of the
+relative viscosity in steady shear, have 
+been determined experimentally~\citep{PhysRevFluids.5.053302}. 
+Other simulation studies have investigated the rheology of strain-hardening
+capsules as a function of membrane inexstensibility
+using the three-dimensional immersed boundary method~\cite{aouane_scagliarini_harting_2021},
+dilute suspensions of compound particles~\cite{singeetham_chaithanya_thampi_2021},
+and shown how shear
+thickening in systems with widely different particle properties stems 
+arise when adhesion forces bring particles into frictional contact
+~\cite{PhysRevFluids.7.054302}. Within this context, membrane inexinsibility
+in the case of Type I amphiphiles and adhesion in general 
+can be inferred from the functional relationships between free energy
+and displacement in Figure~\ref{fig:fsummary}(c), for example.
+
+For active particles, researchers have 
+obtained analytical expressions for the effective viscosity
+resulting from the activity of dilute swimmers
+in extensional flows
+~\cite{Saintillan2010ExtensionalRO} and compared
+numerical predictions under shear flow derived from
+Stokesian dynamics and lubrication theory~\cite{ishikawa_brumley_pedley_2021}.
+Suspensions of pushers can yield an apparent reduction
+in viscous dissipation arising from particle activity
+In contrast, the JP suspensions of the present study
+do not inject, but rather store energy coming from the
+background flow.
 

### 2023-03-24 doc/PRF2022/PRF_main.tex
figs and refs

@@
   of a vesicle is in a TG flow at $t=1$ $\upmu$s with $l= 1,2,3,4$,
-  respectively. In panel (f), the relative enclosed area $A/A_0$
-  decreases over time. The inset shows the relative length $L/L_0$ which
-  remains nearly constant with small fluctuations. The inset and main
-  panel have the same horizontal axis.} 
+  respectively. In panel (f),
+  inset, the relative enclosed area $A/A_0$
+  for the four cases in panels (b)--(e) decays to a steady state.
+  The steady-state $A_{\infty}/A_0$ relative area is non-monotonic
+  in $\lambda$.} 
 %  \todo[inline]{We propose to relate panel (f) to the pressure drops
@@
 %
-Finally, we calculate the vesicle area $A$ and length $L$. As shown in
-Figure~\ref{fig:PramChange}(f), the relative area $A/A_0$ achieves a
-steady-state that is greatest for $\lambda = 4$~nm yet least for
+Finally, we calculated the vesicle area $A$ and length $L$. As shown in
+Figure~\ref{fig:PramChange}(f), the relative area achieves a
+steady state $A_{\infty}/A_0$ that is greatest for $\lambda = 4$~nm yet least for
 $\lambda = 2$~nm. The relative length $L/L_0$, however, is constant in
-$t$ for all cell sizes (Figure~\ref{fig:PramChange}(e), inset). In other
+$t$ for all cell sizes (data not shown). In other
 words, the flow pattern is non-monotonic in the cell size $\lambda$.
@@
 using the three-dimensional immersed boundary method~\cite{aouane_scagliarini_harting_2021},
-dilute suspensions of compound particles~\cite{singeetham_chaithanya_thampi_2021},
+studied dilute suspensions of compound particles~\cite{singeetham_chaithanya_thampi_2021},
 and shown how shear

### 2023-03-25 doc/PRF2022/PRF_main.tex
yny
yny2

@@
 $\lambda = 2$~nm. The relative length $L/L_0$, however, is constant in
-$t$ for all cell sizes (data not shown). In other
-words, the flow pattern is non-monotonic in the cell size $\lambda$.
+$t$ for all cell sizes (data not shown). 
+In other words, the fluid-structure interactions of JPs give rise to 
+non-monotonic dependence of membrane permeability on the TG cell size $\lambda$.
+This result is similar to the non-monotonic pressure-flow rate relation in the clogging of
+spherical particles in a rectangular microfluidic channel \cite{MooreEtAl2023_PRL}.
 

### 2023-03-25 doc/PRF2022/PRF_main.tex
yny3

@@
 non-monotonic dependence of membrane permeability on the TG cell size $\lambda$.
-This result is similar to the non-monotonic pressure-flow rate relation in the clogging of
+Such dynamic pressure-flow rate relation is also found in the clogging of
 spherical particles in a rectangular microfluidic channel \cite{MooreEtAl2023_PRL}.

### 2023-03-25 doc/PRF2022/PRF_main.tex
yny5

@@
 non-monotonic dependence of membrane permeability on the TG cell size $\lambda$.
-Such dynamic pressure-flow rate relation is also found in the clogging of
+Such dynamic permeability due to fluid-structure interactions is also found in the clogging of
 spherical particles in a rectangular microfluidic channel \cite{MooreEtAl2023_PRL}.

### 2023-03-28 doc/PRF2022/PRF_main.tex
yny

@@
 
-In this work we focus on collective hydrodynamics of immobile
+In this work we focus on collective hydrodynamics of immobile (non self-propelling)
 amphiphilic JPs in a viscous fluid under an imposed far-field flow. The
@@
 boundary integral numerical simulations~\cite{Fu20,Fu2022_JFM}. The
-dynamics of the JP suspension results from the combination of long-range
+dynamics of the JP suspension arises spontaneously from the combination of long-range
 hydrodynamic interaction and non-local interactions between JPs through
@@
 Molecular dynamics (MD) and Monte Carlo simulations provide another
-avenue for simulating the interaction between JPs, solvents, and
+means for simulating the interaction between JPs, solvents, and
 substrates~\cite{Brandner2019, Baniketal2021,

### 2023-03-29 doc/PRF2022/PRF_main.tex
yny

@@
 In this work we focus on collective hydrodynamics of immobile (non self-propelling)
-amphiphilic JPs in a viscous fluid under an imposed far-field flow. The
+JPs in a viscous fluid under an imposed far-field flow. The
 amphiphilic JP has a hydrophobic surface on one side and a hydrophilic
@@
 %
-In a quiescent flow, a JP suspension self-assembles into micelles and
+In a quiescent flow, an amphiphilic JP suspension self-assembles into micelles and
 bilayers of JPs that provide an alternative means for computing the
@@
 Molecular dynamics (MD) and Monte Carlo simulations provide another
-means for simulating the interaction between JPs, solvents, and
+means for simulating the interaction between amphiphilic JPs, solvents, and
 substrates~\cite{Brandner2019, Baniketal2021,
 HongCacciutoLuijtenGranick2008, C9NR05885K}. In these methods
-pair-potentials are used to describe the interaction between JPs, for
-example by prescribing angle dependent forces and torques that bring the
+pair-potentials are used to describe the interaction between amphiphilic JPs
+by prescribing angle dependent forces and torques that bring the
 hydrophobic sides of two amphiphilic JPs into opposition. On the other

### 2023-03-29 doc/PRF2022/PRF_main.tex
yny

@@
 \label{sec:governing_equations}
-The governing equations are a system for the position and orientation of
+The governing equations are a system of partial differential equations for the position and orientation of
 a collection of rigid JPs~\cite{Fu2022_JFM}. We first pose the Stokes
@@
 the vesicle, whether square or polygonal, can be controlled by adjusting
-the size of the cell in the TG flow. On the other hand, the assembly of
+the size of the cell in the TG flow. In addition the permeability of the JP bilayer
+varies non-monotonically with the TG cell size.
+%
+On the other hand, the assembly of
 multilamellar JPs and the striated JPs behave more like a rigid body

### 2023-03-29 doc/PRF2022/PRF_main.tex
yny

@@
 screened Laplace equation. Particle collisions are avoided through a
-near-field, pair potential.
+near-field, pair potential for their steric interactions.
 
@@
 and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} using high-order
-interpolation-based quadrature rules. Integrals that are smooth are
+interpolation-based quadrature rules. Smooth integrals are
 computed with the spectrally-accurate trapezoid rule, and

### 2023-03-30 doc/PRF2022/PRF_main.tex
yny

@@
 In TG flow, $\lambda$ controls the size of the $2\pi \lambda \times 2\pi
-\lambda$ TG cells. Throughout, we use $\lambda = 2$ nm so that the JP
+\lambda$ TG cells. Throughout this section, we use $\lambda = 2$ nm so that the JP
 phases occupy about nine cells.
@@
   configuration of a vesicle bilayer the configurations with streamlines
-  of a vesicle is in a TG flow at $t=1$ $\upmu$s with $l= 1,2,3,4$,
+  of a vesicle is in a TG flow at $t=1$ $\upmu$s with $\lambda= 1,2,3,4$,
   respectively. In panel (f),

### 2023-04-01 doc/PRF2022/Reviews/ResponseToReviewer1.tex
Review2

@@
 we believe is a stronger manuscript. An itemized list of the changes
-addressing the reviewer's comments are below. Changes to the manuscript
-from Reviewers 1 and 2 are colored in \textcolor{red}{red} and 
-\textcolor{magenta}{magenta}, respectively. \\ \\
+addressing the reviewer's comments are below. 
+%Changes to the manuscript from Reviewers 1 and 2 are colored in
+%\textcolor{red}{red} and \textcolor{magenta}{magenta}, respectively. 
+\\ \\
 \noindent
@@
 \begin{itemize}
-  \item {\bf Response to Summary}: 	
-  \begin{quotation}
+  \item {\bf Response to Summary}: We thank the Reviewer for the
+    positive assessment of our manuscript. We have addressed each of the
+    reviewer's comments which are summarized below.
+%  \begin{quotation}
 %    \noindent
 %    Can put verbatim change in this environment.
-  \end{quotation}
+%  \end{quotation}
 \end{itemize}
@@
 \noindent
-\comment{My main criticism is
-the following: 1. Unilamellar, multilamellar and striated structured are subjected to
-various flow conditions, with increasing shear rate or strength of the
-flow (for TG case). For all structures in both flows, the main result
-is that these structures break eventually either for increased shear
-rate or increased flow rate. But this is expected. What do all these
-results mean? I feel that a constructive message is missing.}
+\comment{My main criticism is the following: 1. Unilamellar,
+multilamellar and striated structured are subjected to various flow
+conditions, with increasing shear rate or strength of the flow (for TG
+case). For all structures in both flows, the main result is that these
+structures break eventually either for increased shear rate or increased
+flow rate. But this is expected. What do all these results mean? I feel
+that a constructive message is missing.}
 
 \begin{itemize}
-  \item Response:
-
-  \item Change:
-
+  \item {\bf Response:}
+  Reviewer 1 pointed out that most of the simulation runs
+  corresponded to breakage in JP phases. The new Figure 3
+  now includes simulation runs for shear rates ranging
+  from $0$ ns$^{-1}$ to $0.1$ ns$^{-1}$ in shear flow
+  and from $0$ ns$^{-1}$ to $0.05$ ns$^{-1}$ in TG flow.
+  These additional data allowed us to plot pre-rupture
+  shear stress against shear rate in the new Figure 5
+  revealing the rheological properties of the distinct
+  JP phases.    
 \end{itemize}

### 2023-04-01 doc/PRF2022/Reviews/ResponseToReviewer2.tex
Review2

@@
 
-\noindent
-Dear Prof.~Cecile Cottin-Bizonne,
-\\ \\
-\noindent
-Thank you for handling the manuscript, and we would like to thank the
-reviewer for their positive and constructive comments. The attached
-manuscript addresses all the reviewer's comments and the result is what
-we believe is a stronger manuscript. An itemized list of the changes
-addressing the reviewer's comments are below. Changes to the manuscript
-from Reviewers 1 and 2 are colored in \textcolor{red}{red} and 
-\textcolor{magenta}{magenta}, respectively. \\ \\
+\noindent Dear Prof. Cecile Cottin-Bizonne,\\
+
+\noindent Thank you for handling the manuscript.
+We thank the Reviewer for their constructive feedback.
+A point-by-point list of changes to the manuscript 
+addressing the Reviewer's comments appears below.\\
+
+\noindent As a summary, we have undertaken a major revision of the manuscript
+that includes further detailed simulation data and analyses,
+reorganized figures, and a new ``Results and Discussion'' section
+written from scratch.  These changes address all the reviewers'
+comments and we believe the result is a stronger manuscript.\\
+
 \noindent
@@
 \section*{Response to Reviewer 2}
+
+\noindent Changes appear in \textcolor{magenta}{magenta}.
+(Other changes specific to Reviewers 1 appear in \textcolor{red}{red}.)\\ \\
+
 \comment{
@@
 \begin{itemize}
-  \item {\bf Response to Summary}: We thank the Reviewer for this positive appraisal of 
+  \item {\bf Response}: We thank the Reviewer for this positive appraisal of 
 our manuscript. 
@@
 \begin{itemize}
-  \item Response:
+\item {\bf Response:}
+  To motivate excluding thermal fluctuations in our system,
+  the new Section V.D. 
+  analyzes that fluctuation Fourier spectrum 
+  of a planar membrane corresponding to the Type I JP bilayer phase
+  (starting on page 18).
+  As the Reviewer points out, our 2D system applies
+  to a transversely invariant phase with depth denoted by $L_y$.
+  Equation (29) shows that the expected fluctutation is small
+  relative to particle size, meaning that thermal fluctuations can
+  be safely ignored when 2D system corresponds to a material that 
+  is more than a few particles deep.  The elastic modulus $\kappa$ for
+  Type II and Type III phases is still greater than for Type I.
 
-  \item Change:
-
+  We point out though, that because the wave vector $\mathbf{k}$ is inversely
+  proportional to the characteristic phase-sample size,
+  fluctuation will be large provided the $L_x$ or $L_y$ is sufficiently large,
+  as in the case of micron-sized vesicles.
 \end{itemize}
@@
 shear flow time scale, and hence effectively the associated Peclet number, i.e.
-importance of flow compared to noise, is negligible in this system?}
+importance of flow compared to noise, is negligible in this system?
 
-\begin{itemize}
-  \item Response:
-
-  \item Change:
-
-\end{itemize}
-
-\noindent
-\comment{Before I can recommend publication, the authors should clarify these points, in
+Before I can recommend publication, the authors should clarify these points, in
 particular justify why noise can be neglected, and why such small shear rates
@@
 \begin{itemize}
-  \item Response: 
+\item {\bf Response:}
+  In the beginning  of the new ``Results and Discussion'' Section V. (page 12),
+  we now derive the range of shear rates 
+  based on the capillary number $C_a$.  The derivation shows that shear forces dominate
+  interfacial forces when $\dot \gamma$ exceeds
+  10$^{-2}$ ns $^{-1} = 10^6$ s$^{-1}$.  Following the derivation,
+  we include references to molecular dynamics simulations that also
+  consider nm system sizes like ours, along with references to
+  larger experimental systems were shear rates are more moderate,
+  on the order of $10^3$ s$^{-1}$.  We end by calculating the
+  P\'eclet number $\mathrm{Pe} = 60$, showing that
+  noise is negligible compared to advection in our system.
+
+  Although the range of simulation shear rates is unchanged in our
+  revision, we thank the Reviewer as their comment has clarified
+  two important points: why we chose the range of shear
+  rates that we did and how neglecting noise and
+  thermal fluctuation can be justified in our system.
+
+  Reviewer 1 pointed out that most of the simulation runs
+  corresponded to breakage in JP phases. The new Figure 3
+  now includes simulation runs for shear rates ranging
+  from $0$ ns$^{-1}$ to $0.1$ ns$^{-1}$ in shear flow
+  and from $0$ ns$^{-1}$ to $0.05$ ns$^{-1}$ in TG flow.
+  These additional data allowed us to plot pre-rupture
+  shear stress against shear rate in the new Figure 5
+  revealing the rheological properties of the distinct
+  JP phases. 
 \end{itemize}

### 2023-04-01 doc/PRF2022/PRF_main.tex
Review2

@@
 of a fluid between two parallel, moving plates excluding wall effects.
-In TG flow, $\lambda$ controls the size of the $2\pi \lambda \times 2\pi
+In TG flow, $\lambda$ controls the size of the $\pi \lambda \times \pi
 \lambda$ TG cells. Throughout this section, we use $\lambda = 2$ nm so that the JP
@@
 
+{\color{magenta}
 To obtain a range for $\dot \gamma$, consider the capillary number 
@@
 stress overcomes elastic stress when $C_a > 1$ and this yields $\dot
-\gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$~s. Thus our values
+\gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$~s$^{-1}$. Thus our values
 for $\dot \gamma$ range between $0$ ns$^{-1}$ corresponding to quiescent
@@
 vessels \cite{Cho2011} where shear rates range over 100--2000 s$^{-1}$.
+From the particle diffusion time $D/L^2$  
+and advection time $L/u = (\dot\gamma)^{-1}$,
+$D = 0.17\cdot 10^{-9}$~m$^2$~s$^{-1}$ and $L \sim 10$~nm, we 
+obtain a P\'eclet number $\mathrm{Pe} = (D/L^2)/(L/u) \sim 60$,
+suggesting that advection dominates the particle transport.
+% L u = L^2 gammadot = 10 nm^2/ns 
+% D = kBT/(6 pi mu c) = kBT/(6 pi mPa s c) 
+%   = kBT/(6 pi 1e-3 N/m^2 1.25 nm) 
+%   = 4 1e-12 N nm/(6 pi 1.25e-3 m^{-2} s N nm) 
+%   = 0.17e-9 m^2/s
+%  
+% Pe = L u/D = 10 nm^2/ns/(0.17e-9 m^2/s)
+%    = 59e9 1e-18 1e9 = 59
+}
 
@@
 
+{\color{magenta}
   We have excluded thermal fluctuations because they are unresolved in the
@@
 \label{eq:fourier_spectrum}
-\langle |h(\kk)|^2 \rangle = \frac{\kbt}{L_xL_y}\frac{1}{\kappa k^4},
+\langle |h(\kk)|^2 \rangle = \frac{\kbt}{L_xL_y}\frac{1}{\kappa |\kk|^4},
 \end{equation}
@@
 with the experimental literature where micron sized vesicles observably
-fluctuate. Rather, larger energies are required to fluctuate membranes
+fluctuate \cite{D0SM00943A}.
+Rather, because the wave vector $\mathbf{k}$ is inversely proportional
+to the characteristic
+size of $L_x$ and $L_y$, larger energies are required to fluctuate membranes
 over smaller wavelengths and these energies exceed available thermal
@@
 above.
+}
 
@@
 \begin{acknowledgments}
-We thank useful conversations with E.~Corona, M.~Rachh, S.~Jiang, and
-  T.~Beck. B.Q.~acknowledges support from the Simons Foundation,
+  We thank the anonymous referees for pointing out
+  the P\'eclet number, capillary number, and fluctuation analysis.
+  E.~Corona, M.~Rachh, S.~Jiang, and T.~Beck
+  provided useful insights.
+  B.Q.~acknowledges support from the Simons Foundation,
   Mathematics and Physical Sciences-Collaboration Grants for

### 2023-04-01 code/tests/stressTest.m

@@ -8,6 +8,12 @@ prams.gam = 1;
 prams.ar = [2 1.5];
 prams.RepulLength = 1;
 prams.RepulStrength = 1;
+prams.bcShift = 0;
+prams.bcType = 0;
+prams.bcType        = 'cosine';
+prams.NPeaks        = 1;
+prams.shape         = 'star'; % options: 'circle'; 'star'
+prams.petal         = 5;
 
 xc = [[+1;0] [-1;3]];
 tau = [-1 +1];

### 2023-04-01 code/tests/yukawa_force.m

@@ -2,14 +2,14 @@
 
 % Here we translate Bryan's geometry class into extant variables 
 
-N = N;                 % number of points per componenet
-Nb = nb;               % number of rigid bodies
-x1 = X(1:N,:);         % grid points on curves 
-x2 = X(N+1:2*N,:);            
-pc = center;           % center of each rigid body
-orn = tau;             % orientation of each rigid body
-a = radii;             % radius of each rigid body
-rho = rho;             % screen length of particles
+N = prams.N;                 % number of points per componenet
+Nb = prams.nb;               % number of rigid bodies
+x1 = geom.X(1:N,:);         % grid points on curves 
+x2 = geom.X(N+1:2*N,:);            
+pc = geom.center;           % center of each rigid body
+orn = geom.tau;             % orientation of each rigid body
+a = geom.radii;             % radius of each rigid body
+rho = geom.rho;             % screen length of particles
 xt = geom.xt;          % tangent unit vector
 tau1 = xt(1:N,:);      
 tau2 = xt(N+1:2*N,:);

### 2023-04-01 doc/PRF2022/Reviews/ResponseToReviewer1.tex
Responses and Letter done:

--- 2022-10-11 doc/PRF2022/Reviews/ResponseToReviewer1.tex
@@
 \noindent
-Dear Prof.~Cecile Cottin-Bizonne,
+Dear Prof.~C\'ecile Cottin-Bizonne,
 \\ \\
 \noindent 
-Thank you for handling the manuscript, and we would like to thank the
-reviewer for their positive and constructive comments. The attached
-manuscript addresses all the reviewer's comments and the result is what
-we believe is a stronger manuscript. An itemized list of the changes
-addressing the reviewer's comments are below. Changes to the manuscript
-from Reviewers 1 and 2 are colored in \textcolor{red}{red} and 
-\textcolor{magenta}{magenta}, respectively. \\ \\
+We thank the Reviewer for their constructive feedback.
+A point-by-point list of changes to the manuscript 
+addressing the Reviewer's comments appears below.\\
+
+\noindent As a summary, we have undertaken a major revision of the manuscript
+that includes further detailed simulation data and analyses,
+reorganized figures, and a new ``Results and Discussion'' section
+written from scratch.  These changes address all the Reviewer's
+comments and we believe the result is a significantly stronger manuscript.
+\\ \\
 \noindent
@@
 \section*{Response to Reviewer 1}
+
+\noindent Changes appear in \textcolor{red}{red}.
+(Other changes specific to Reviewer 2 appear in \textcolor{magenta}{magenta}.)\\ \\
+
 \noindent
@@
 \begin{itemize}
-  \item {\bf Response to Summary}: 	
-  \begin{quotation}
+  \item {\bf Response to Summary}: We thank the Reviewer for their
+    positive assessment of our manuscript.  
+%  \begin{quotation}
 %    \noindent
 %    Can put verbatim change in this environment.
-  \end{quotation}
+%  \end{quotation}
 \end{itemize}
@@
 \noindent
-\comment{My main criticism is
-the following: 1. Unilamellar, multilamellar and striated structured are subjected to
-various flow conditions, with increasing shear rate or strength of the
-flow (for TG case). For all structures in both flows, the main result
-is that these structures break eventually either for increased shear
-rate or increased flow rate. But this is expected. What do all these
-results mean? I feel that a constructive message is missing.}
+\comment{My main criticism is the following: 1. Unilamellar,
+multilamellar and striated structured are subjected to various flow
+conditions, with increasing shear rate or strength of the flow (for TG
+case). For all structures in both flows, the main result is that these
+structures break eventually either for increased shear rate or increased
+flow rate. But this is expected. What do all these results mean? I feel
+that a constructive message is missing.}
 
 \begin{itemize}
-  \item Response:
+  \item[] {\bf Response:}
+      The Results Section V of our first submission
+    analyzed simulation data on a case-by-case basis. 
+    This made it unnecessarily difficult for the reader to
+    make meaningful connections and we agree with the Reviewer:
+    a constructive message was missing.  Moreover,
+    the large-shear-rate 
+    simulation runs for the most part corresponded to breakage in
+    JP phases.
 
-  \item Change:
+    To address these deficiencies,
+    we performed further simulations 
+    for moderate shear rates ranging
+    from $0$ ns$^{-1}$ to $0.1$ ns$^{-1}$ in shear flow
+    and from $0$ ns$^{-1}$ to $0.05$ ns$^{-1}$ in TG flow.
+    These additional data allowed us to examine 
+    material properties in greater detail: the new
+    \begin{itemize}
+      \item[$\bullet$] Figure 3 summarizes the strain and alignment data
+        under \emph{all} flow and JP-type conditions.
+      \item[$\bullet$] Figure 4 characterizes the change in free and binding energies.
+      \item[$\bullet$] Figure 5 plots pre-rupture
+        shear stress against shear rate revealing the rheological properties of
+        the three distinct JP phases.    
+    \end{itemize}
+    A constructive message---identification a critical shear rate,
+    relative binding strengths as a function of JP type,
+    and effective viscosities and presence of shear thinning---is
+    now formulated thanks to exploring the full range of
+    shear rates.
 
+    Finally, we normalized the TG flow rate (previously $V_0$)
+    so that we can compare the shear and TG flow in terms of the same
+    shear rate $\dot \gamma$.  See page 11, equation (24) and page 12,
+    top paragraph.
 \end{itemize}
@@
 properly.}
+    \begin{itemize}
+    \item[] {\bf Response:}
+      The address this,
+      we rewrote the Results section from scratch
+    to what is now Section V ``Results and Discussion''.
+    We highlighted the section heading on page 11 to indicate
+    that the entire section is rewritten.
 
-\begin{itemize}
-  \item Response:
+    Starting on page 11, this section introduces the background flows,
+    characterizes the system's capillary and P\'eclet numbers.
+    As described in the previous response, Section V examines the data
+    as a whole and is divided into subsections A. Strain and alignment,
+    B. Free energy, and C. Rheology.
 
-  \item Change:
+    The raw data, which was previously shown in the
+    main text, has now been placed in Supplementary Material
+    and appropriately captioned.  We also combined
+    Figures 2 and 3 into a simpler, more readable Figure 2.
 
+    Finally, we rewrote the previous Discussion Section VI from scratch
+    into Section V, subsection D. Here,
+    we perform a dimensional analysis of the critical shear rate $\dot \gamma_*$
+    for rupture, show how fluid-structure interactions
+    give rise to non-monotonic dependence, justify why
+    fluctuation can been omitted from the simulations, and
+    discuss the rheological data in the context of 
+    rheologies for classical and active suspensions.
+
+    We feel that these changes have significantly improved the readability
+    of the manuscript.  As an added advantage, the main text of the
+    revised manuscript is 21 pages, whereas the first submission's was
+    25 pages.  
     \end{itemize}
@@
 \begin{itemize}
-  \item Response:
-
-\item Change:
-
+  \item[] {\bf Response:}
+    We have omitted this sentence and rewritten the discussion
+    for vesicles in TG flow.  See second middle of page 18.   
 \end{itemize}
@@
 \begin{itemize}
-  \item Response:
-
-  \item Change:
-
+\item[] {\bf Response:}
+  In our first submission, these arrows showed the clockwise or counterclockwise
+  vesicle motion in TG flow.  These arrows have been omitted in the new Figure 6,
+  and the motion is instead described in the middle of page 18. 
 \end{itemize}

### 2023-04-01 doc/PRF2022/Reviews/ResponseToReviewer2.tex
Responses and Letter done:

@@
 
-\noindent Dear Prof. Cecile Cottin-Bizonne,\\
+\noindent Dear Prof. C\'ecile Cottin-Bizonne,\\
 
-\noindent Thank you for handling the manuscript.
+\noindent 
 We thank the Reviewer for their constructive feedback.
@@
 reorganized figures, and a new ``Results and Discussion'' section
-written from scratch.  These changes address all the reviewers'
-comments and we believe the result is a stronger manuscript.\\
+written from scratch.  These changes address all the Reviewer's
+comments and we believe the result is a
+significantly stronger manuscript.\\
 
@@
 \noindent Changes appear in \textcolor{magenta}{magenta}.
-(Other changes specific to Reviewers 1 appear in \textcolor{red}{red}.)\\ \\
+(Other changes specific to Reviewer 1 appear in \textcolor{red}{red}.)\\ \\
 
@@
 \item {\bf Response:}
-  To motivate excluding thermal fluctuations in our system,
-  the new Section V.D. 
-  analyzes that fluctuation Fourier spectrum 
+  To justify excluding thermal fluctuations in our system,
+  the new Section V D 
+  analyzes the fluctuation Fourier spectrum 
   of a planar membrane corresponding to the Type I JP bilayer phase
@@
   As the Reviewer points out, our 2D system applies
-  to a transversely invariant phase with depth denoted by $L_y$.
+  to a transversely invariant bilayer with depth denoted by $L_y$.
   Equation (29) shows that the expected fluctutation is small
   relative to particle size, meaning that thermal fluctuations can
-  be safely ignored when 2D system corresponds to a material that 
+  be safely ignored when the 2D system corresponds to a material that 
   is more than a few particles deep.  The elastic modulus $\kappa$ for
@@
   proportional to the characteristic phase-sample size,
-  fluctuation will be large provided the $L_x$ or $L_y$ is sufficiently large,
+  fluctuation will be large provided $L_x$ or $L_y$ is sufficiently large,
   as in the case of micron-sized vesicles.
@@
 \item {\bf Response:}
-  In the beginning  of the new ``Results and Discussion'' Section V. (page 12),
+  In the beginning  of the new Section V ``Results and Discussion'' (page 12),
   we now derive the range of shear rates 
-  based on the capillary number $C_a$.  The derivation shows that shear forces dominate
+  based on the capillary number $\mathrm{Ca}$.  The derivation shows that shear forces dominate
   interfacial forces when $\dot \gamma$ exceeds
@@
   we include references to molecular dynamics simulations that also
-  consider nm system sizes like ours, along with references to
+  consider nm system-sizes like ours, along with references to
   larger experimental systems were shear rates are more moderate,
@@
   Although the range of simulation shear rates is unchanged in our
-  revision, we thank the Reviewer as their comment has clarified
+  revision, we thank the Reviewer for pointing these details out
+  as their comment has clarified
   two important points: why we chose the range of shear

### 2023-04-01 doc/PRF2022/PRF_main.tex
Responses and Letter done:

@@
 %%%%%%%
-
-\section{Results and Discussion}
+{\color{red}
+\section{Results and Discussion}}
 \label{sec:results}
@@
 and a Taylor-Green (TG) flow
+{\color{red}
   \begin{equation}
@@
   \end{equation}
+  }
 where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal and
@@
 
+{\color{red}
   In both cases, $\dot \gamma$ is the shear rate. The flow rate $\lambda
@@
 \uu_{\infty}^{\text{TG}}$ when integrated over a TG cell $A$. 
+}
 
@@
 \label{eq:capillary}
-C_a = \frac{\mu \dot \gamma R^3}{\kappa}
+\mathrm{Ca} = \frac{\mu \dot \gamma R^3}{\kappa}
 \end{equation}
@@
 gives the elastic stress for restoring the phase-sample shape. Shear
-stress overcomes elastic stress when $C_a > 1$ and this yields $\dot
+stress overcomes elastic stress when $\mathrm{Ca} > 1$ and this yields $\dot
 \gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$~s$^{-1}$. Thus our values
@@
 
-For $\lambda=1$~nm and $\lambda=2$~nm, multiple TG cells are inside the
+{\color{red} For $\lambda=1$~nm and $\lambda=2$~nm, multiple TG cells are inside the
 JP vesicle as the inner leaflet of JPs move clockwise along the boundary
@@
 bilayer tank-tread in the counter-clockwise direction (Figure
-\ref{fig:PramChange}(b)--(e)). 
+\ref{fig:PramChange}(b)--(e)). }
 %
@@
 non-monotonic dependence of membrane permeability on the TG cell size $\lambda$.
-Such dynamic permeability due to fluid-structure interactions is also found in the clogging of
-spherical particles in a rectangular microfluidic channel \cite{MooreEtAl2023_PRL}.
+{\color{red}Such dynamic permeability due to fluid-structure interactions is also found in the clogging of
+spherical particles in a rectangular microfluidic channel \cite{MooreEtAl2023_PRL}.}
 

### 2023-04-02 doc/PRF2022/Reviews/ResponseToReviewer2.tex
final touches

@@
   we include references to molecular dynamics simulations that also
-  consider nm system-sizes like ours, along with references to
+  consider nm system-sizes like ours and use the same shear rates,
+  along with references to
   larger experimental systems were shear rates are more moderate,
@@
   as their comment has clarified
-  two important points: why we chose the range of shear
+  two important points: how we chose the range of shear
   rates that we did and how neglecting noise and

### 2023-04-03 doc/PRF2022/Reviews/ResponseToReviewer1.tex
yny
final touches
minor changes

@@
   \item[] {\bf Response:}
-      The Results Section V of our first submission
-    analyzed simulation data on a case-by-case basis. 
-    This made it unnecessarily difficult for the reader to
-    make meaningful connections and we agree with the Reviewer:
-    a constructive message was missing.  Moreover,
-    the large-shear-rate 
-    simulation runs for the most part corresponded to breakage in
-    JP phases.
+    The Results Section V of our first submission analyzed simulation
+    data on a case-by-case basis. This made it unnecessarily difficult
+    for the reader to make meaningful connections and we agree with the
+    Reviewer: a constructive message was missing. Moreover, the
+    large-shear-rate simulation runs for the most part corresponded to
+    breakage in JP phases.
 
-    To address these deficiencies,
-    we performed further simulations 
-    for moderate shear rates ranging
-    from $0$ ns$^{-1}$ to $0.1$ ns$^{-1}$ in shear flow
-    and from $0$ ns$^{-1}$ to $0.05$ ns$^{-1}$ in TG flow.
-    These additional data allowed us to examine 
-    material properties in greater detail: the new
+    To address these deficiencies, we performed additional simulations
+    for moderate shear rates ranging from $0$ ns$^{-1}$ to $0.1$
+    ns$^{-1}$ in shear flow and from $0$ ns$^{-1}$ to $0.05$ ns$^{-1}$
+    in TG flow. These additional data allowed us to examine material
+    properties in greater detail: the new
     \begin{itemize}
@@
     \item[] {\bf Response:}
-      The address this,
+      To address this,
       we rewrote the Results section from scratch
@@
     We have omitted this sentence and rewritten the discussion
-    for vesicles in TG flow.  See second middle of page 18.   
+    for vesicles in TG flow.  See middle of page 18.   
 \end{itemize}

### 2023-04-25 doc/PRF2022/PRF_main.tex
Peter updated files

@@
 %\usepackage{showkeys}
-\usepackage{todonotes}
+%\usepackage{todonotes}
 \usepackage{graphicx}
@@
 \begin{center}
-  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
+  \includegraphics[width=\textwidth]{Figure1.pdf}
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=\textwidth]{Figures/Figure1and2.pdf}
-%  \includegraphics[height=0.3\textheight]{Nb198a_inset.pdf}
-%  \includegraphics[height=0.3\textheight]{Nb198b_eta_inset.pdf}\\
-%  \includegraphics[height=0.3\textheight]{Nb198c_eta_inset.pdf}
-%  \includegraphics[height=0.3\textheight]{Nb198d_eta_inset.pdf}
+  \includegraphics[width=\textwidth]{Figure2.pdf}
 \end{center}
@@
 
-See Section~\ref{sec:movie_description} in the [Supplementary Material]
+See Section~\ref{sec:movie_description} in the Supplementary Material
 for movies showing the transition of 60 JPs that are initialized
 randomly (inset of Figure~\ref{fig:relax}(a)) to the steady state
-configurations (inset of Figures~\ref{fig:relax}(b), (d), and (e)).
+configurations (inset of Figures~\ref{fig:relax}(b), (d), and (e))~\cite{supp}.
 
@@
 \begin{center}
-\includegraphics[width=\textwidth]{S2ESummary.pdf}
+\includegraphics[width=\textwidth]{Figure3.pdf}
 \end{center}
@@
 background flow. See Section~\ref{sec:movie_description} in the
-[Supplementary Material] for movies showing the dynamics of the JP
-suspensions in Figure~\ref{fig:s2esummary}.
-
-Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} in the [Supplementary
-Material] contain the fully-resolved time courses for the free energy
-$F$, alignment order $S_2$, and strain $E$. The eight setups correspond
+Supplementary Material for movies showing the dynamics of the JP
+suspensions in Figure~\ref{fig:s2esummary}~\cite{supp}.
+
+Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} in the Supplementary
+Material contain the fully-resolved time courses for the free energy
+$F$, alignment order $S_2$, and strain $E$~\cite{supp}. The eight setups correspond
 to the four JP phases---bilayer, vesicle BL, multilamellar, and
@@
 The fully-resolved time courses in
-Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} in the [Supplementary
-Material] contain significant oscillations due to the particle-based
-formulation and tumbling inherent to the background flows. To extract
+Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} in the Supplementary
+Material contain significant oscillations due to the particle-based
+formulation and tumbling inherent to the background flows~\cite{supp}. To extract
 meaningful data, we further post-process the $F$, $S_2$, $E$ curves by
@@
 \begin{center}
-\includegraphics[width=\textwidth]{FSummary.pdf}
+\includegraphics[width=\textwidth]{Figure4.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{RheologySummary.pdf}
+\includegraphics[width=\textwidth]{Figure5.pdf}
 \end{center}
@@
 background flow leads to oscillation in the strain time courses making
-systematic fitting challenging (see [Supplementary Material]
-Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}). The integral
+systematic fitting challenging (see Supplementary Material
+Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}~\cite{supp}). The integral
 in~\eqref{eq:strainrate} averages out these oscillations and gives
@@
 \begin{center}
-  \includegraphics[width=\textwidth]{critical_shear_and_cell_size.pdf}
+  \includegraphics[width=\textwidth]{Figure6.pdf}
 \end{center}
@@
 proportional to $\gamma^*$ since the striated phase tends to cleave
-during rupture (see Supplementary movie). Our previous
+during rupture (see Supplementary movie~\cite{supp}). Our previous
 work~\cite{Fu2022_JFM} found the scaling $\mu \dot\gamma_* =
@@
 diamond ($\lambda=3$~nm), and a rounded rectangle ($\lambda=4$~nm). See
-Section~\ref{sec:movie_description} in the [Supplementary Material] for
+Section~\ref{sec:movie_description} in the Supplementary Material for
 a movie showing the dynamics of the JP vesicle for the four different
-values of $\lambda$ in Figure~\ref{fig:PramChange}(b)--(e).
+values of $\lambda$ in Figure~\ref{fig:PramChange}(b)--(e)~\cite{supp}.
 
@@
 
-\input{Supplementary}
+%\input{Supplementary}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\thispagestyle{empty}
+
+\newpage
+{\Large \bf
+
+  \noindent Supplementary Material\\
+
+  \noindent 
+ Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows}\\
+
+\noindent 
+Szu-Pei Fu$^{1,*},$ 
+Rolf Ryham$^{2},$ 
+Bryan Quaife$^{3}$ and Y.-N. Young$^{4},$
+\\
+
+\noindent
+$^{1}$Department of Mathematics, Trinity College, Hartford, Connecticut 06106, USA
+
+\noindent
+$^{2}$Department of Mathematics, Fordham University, Bronx, NY, USA
+
+\noindent
+$^{3}$Department of Scientific Computing, Florida State University, Tallahassee, Florida 32306, USA
+
+\noindent
+$^{4}$Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, NJ 07102 USA
+\\
+
+\noindent $^*$Corresponding author. Address: Department of Mathematics, Trinity College, 
+300 Summit Street, Hartford, CT 06106. email: \text{peter.fu@trincoll.edu}
+
+\setcounter{page}{1}
+
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{S\arabic{figure}}
+
+\setcounter{equation}{0}
+\renewcommand{\theequation}{S\arabic{equation}}
+
+\setcounter{section}{0}
+\renewcommand{\thesection}{S\arabic{section}}
+
+%-----ellipse repulsion--------------------
+
+%\Phi_{\mathrm{rep}}
+
+\section{Movie Descriptions}
+\label{sec:movie_description}
+We consider suspensions of JPs of radius 1.25~nm. The time step size for
+all simulations is $\Delta t = 0.2$~ns. The colors of the JPs are as
+follows: for Type I and Vesicles, red is hydrophobic ($\max g > 0$) and
+blue is hydrophilic ($\min g = 0$); for Type II, red is more hydrophobic
+($\max g >0$) than blue ($\min g > 0$); for Type III, red is positively
+charged ($\max g > 0$) and blue is negatively charged ($\min g < 0$).
+%\mbox{} \\
+
+\noindent
+{\bf Relaxation}: The relaxation of 60 circular JPs that are initialized
+with random locations and orientations. The JPs self-assemble into
+unilamellar (Type I), multilamellar (Type II), and striated (Type III)
+configurations. The final configurations are used as initial conditions
+for the simulations that include a background flow.
+
+%There are 60 circular particles with radius 1.25~nm that are initially
+%confined in a square box. The simulation results show the relaxation
+%with each of the three boundary conditions. The time step of all
+%simulations is $\Delta t=0.2$. The color on the boundary from blue to
+%red is for $\min g(\xx)$ to $\max g(\xx)$. All final configurations are
+%adopted in simulations with hydrodynamic flows. \\
+
+\noindent
+{\bf Structures in a Weak Shear Flow}:
+The relaxed configurations of the 60 JPs are subjected to a weak shear
+flow. The shear rate is $\dot{\gamma} = 0.05$~ns$^{-1}$ for the Vesicle,
+Type I, and Type II configurations, and $\dot{\gamma} = 0.1$~ns$^{-1}$
+for the Type III configuration. The vesicle undergoes tank-treading and
+the bilayer increases its orientational order. The multilamellar
+configuration resembles a rigid body motion, and the striated
+configuration has an even stronger resemblance to a rigid body motion.
+No ruptures occur in these examples. The frame rate for the movie of 
+Type I configuration is twice as much ones used in movies of other configurations.
+
+%We adopt the relaxed configurations and place the JP structures in the
+%shear flow. For the choices of the shear rate, we pick: $\dot\gamma =
+%0.05$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.05$ ns$^{-1}$ for the
+%bilayer, $\dot\gamma = 0.05$ ns$^{-1}$ for the multi-lamellar, and
+%$\dot\gamma = 0.1$ ns$^{-1}$ for the striated configurations. The
+%vesicle case undergoes tank-treading whereas the initially disordered
+%BC (i) case increases orientational order. The multilamellar assemply
+%behaves as a rigid body, and the striated configuration moreso. No
+%ruptures occur. \\
+
+\noindent
+{\bf Structures in a Weak Taylor-Green Flow}:
+The relaxed configurations of the 60 JPs are subjected to a weak
+Taylor-Green flow. The flow rate is $\dot{\gamma} = 0.05$~ns$^{-1}$ for
+the Vesicle, Type I, and Type II configurations, and $\dot{\gamma} =
+0.1$~ns$^{-1}$ for the Type III configuration. The vesicle stays intact,
+whereas the bilayer is pulled apart into different TG cells. Like in the
+weak shear flow example, the multilamellar and striated configurations
+behave as rigid bodies.
+
+%For the choices of the flow strength, we pick: $\dot\gamma = 0.05$
+%ns$^{-1}$ for the vesicle, $\dot\gamma = 0.05$ ns$^{-1}$ for the
+%disordered bilayer, $\dot\gamma = 0.05$ ns$^{-1}$ for the
+%multi-lamellar, and $\dot\gamma = 0.1$ ns$^{-1}$ for the striated
+%configurations. The vesicle stays inact, whereas the dissordered
+%bilayer is pulled apart. Like in Supplementary Movie S2, the striated
+%assembly is basically rigid. \\
+
+%We adopt the relaxed configurations and place the JP structures in the
+%Taylor-Green flow at low flow rates. For the choices of the flow
+%strength, we pick: $\dot\gamma = 0.05$ ns$^{-1}$ for the vesicle,
+%$\dot\gamma = 0.05$ ns$^{-1}$ for the disordered bilayer, $\dot\gamma =
+%0.05$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.1$
+%ns$^{-1}$ for the striated configurations. The vesicle stays inact,
+%whereas the dissordered bilayer is pulled apart. Like in Supplementary
+%Movie S2, the striated assembly is basically rigid. \\
+
+\noindent
+{\bf Structures in a Strong Shear Flow}:
+The relaxed configurations of the 60 JPs are subjected to a strong shear
+flow. The shear rate is $\dot{\gamma} = 0.075$~ns$^{-1}$ for the Vesicle
+configuration, $\dot{\gamma} = 0.1$~ns$^{-1}$ for the Type I
+configuration, and $\dot{\gamma} = 0.15$~ns$^{-1}$ for the Type II and
+Type III configurations. In all cases, the structure is ruptured by the
+flow. The frames are stabilized by moving with the center of mass of all
+the JPs.
+
+%We adopt the relaxed configurations and place the JP structures in the
+%shear flow at a higher shear rate. For the choices of the shear rate, we
+%pick: $\dot\gamma = 0.075$ for the vesicle, $\dot\gamma = 0.1$ ns$^{-1}$
+%for the bilayer, $\dot\gamma = 0.15$ ns$^{-1}$ for the multi-lamellar,
+%and $\dot\gamma = 0.15$ ns$^{-1}$ for the striated configurations. The
+%time step of all simulations is $\Delta t=0.2$ ns$^{-1}$. In this movie,
+%some clear structural ruptures occur in each case. In order to observe
+%the structure behaviors at later time, we stabilize the frame by
+%tracking the center of mass position of all JP. \\
+
+\noindent
+{\bf Structures in a Strong Taylor-Green Flow}:
+The relaxed configurations of the 60 JPs are subjected to a strong
+Taylor-Green flow. The flow rate is $\dot{\gamma} = 0.1$~ns$^{-1}$ for
+the Vesicle, Type I, and Type II configurations, and $\dot{\gamma} =
+0.15$~ns$^{-1}$ for the Type III configuration. In all cases, the
+structure is ruptured by the flow and there is a significant reduction
+in the orientation order. While the Vesicle Type I configurations are
+broken into several pieces, the main body of the Type II and Type III
+configurations are not pulled apart by the background flow.
+
+%We adopt the relaxed configurations and place the JP structures in the
+%Taylor-Green flow at higher flow rates. For the choices of the flow
+%strength, we pick: $\dot\gamma = 0.1$ ns$^{-1}$ for the vesicle, $\dot\gamma = 0.1$ ns$^{-1}$ for the
+%bilayer, $\dot\gamma = 0.1$ ns$^{-1}$ for the multi-lamellar, and $\dot\gamma = 0.15$ ns$^{-1}$ for the
+%striated configurations. Clear structural ruptures occur in each case.
+%In all cases, there is significant reduction in the orientational order
+%of the assemblies. While the BC (i) cases are broken into several
+%pieces, the main body of the BC (ii) and BC (iii) assemblies are not
+%pulled apart by the background flow.\\
+
+\noindent
+%{\label{MovieS6}\bf JP Vesicle in a Taylor-Green Flow with Various
+%$\lambda$ Values}: 
+{\bf JP Vesicle in Various Taylor-Green Flows}: A circular vesicle
+bilayer is placed in a Taylor-Green flow. The parameter $\lambda$
+controls the TG cell size and the values are varied from 1~nm to 4~nm
+while the flow rate is chosen so that $\lambda\dot\gamma=0.1$~nm/ns. The
+parameter $\lambda$ determines the steady-state polygonal tank-treading
+shape. The rotation direction is clockwise for $\lambda=1$~nm and
+$\lambda=2$~nm, and counterclockwise for $\lambda=3$~nm and
+$\lambda=4$~nm. Streamlines of the flow are included.
+
+%A circular vesicle bilayer is placed in the Taylor-Green flow.  The
+%parameter $\lambda$ controls the cell size and the values are varied
+%from 1.0 nm to 4.0 nm while the flow rate $\lambda\dot\gamma=0.1$ is
+%fixed. There is a rotation transition from clockwise ($\lambda=1$ nm and
+%2 nm) to counterclockwise ($\lambda=3$ nm and 4 nm). Moreover, the
+%resulting steady shapes of all cases are different polygons. We plot the
+%streamlines in the background.\\
+
+\section{Raw Data}
+The following figures plot the fully resolved simulation time-courses
+organized in terms of the bilayer, vesicle BL, multilamellar, and
+striated JP configurations under shear flow (Supplementary
+Figures~\ref{fig:ulshraw}--\ref{fig:stshraw}) and under TG flow
+(Supplementary Figures~\ref{fig:ultgraw}--\ref{fig:sttgraw}).
+Throughout, panels (a) are for relative free energy $F - F_0$, panels
+(b) are for alignment $S_2$, and panels (c) are for strain $E$ (as a
+percentage). The same vertical and horizontal axes are used for each of
+the respective panels to facilitate comparison between data sets. 
+%\newpage
+
+\begin{figure}[h!]
+\begin{center}
+\textbf{\textsc{Shear Flow cases}}\par\medskip
+\textbf{Type I, bilayer phase under shear flow}\par\medskip
+\includegraphics[width=\textwidth]{FigureS1.pdf}
+\end{center}
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type I, bilayer phase under shear flow with shear
+  rates $\dot\gamma=0.013$ -- $0.075$ ns$^{-1}$.
+%The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:ulshraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\textbf{Type I, vesicle BL phase under shear flow}\par\medskip
+\includegraphics[width=\textwidth]{FigureS2.pdf}
+\end{center}
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type I, bilayer phase under shear flow with shear
+  rates $\dot\gamma=0.01$--$0.075$ ns$^{-1}$. The JP type is the same as
+  Figure \ref{fig:ulshraw} except with a vesicle-shaped initial
+  configuration rather than a disordered bilayer.
+%A Vesicle under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.075$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:veshraw}
+\end{figure}
+
+\begin{figure}[h!]
+\textbf{Type II, multilamellar phase under shear flow}\par\medskip
+\begin{center}
+\includegraphics[width=\textwidth]{FigureS3.pdf}
+\end{center}
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type II, multilamellar phase under shear flow with
+  shear rates $\dot\gamma=0.025$--$0.075$ ns$^{-1}$.
+%A multilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.025\sim0.075$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:mlshraw}
+\end{figure}
+
+\begin{figure}[h!]
+\textbf{Type III, striated phase under shear flow}\par\medskip
+\begin{center}
+\includegraphics[width=\textwidth]{FigureS4.pdf}
+\end{center}
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type III, striated phase under shear flow with
+  shear rates $\dot\gamma=0.01$--$0.07$ ns$^{-1}$.
+%A striated JP structure under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.07$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:stshraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\textbf{\textsc{TG Flow Cases}}\par\medskip
+\textbf{Type I, bilayer phase under TG flow}\par\medskip
+\includegraphics[width=\textwidth]{FigureS5.pdf}
+\end{center}
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type I, bilayer phase under TG flow with flow 
+  rates $\dot\gamma=0.013$--$0.05$ ns$^{-1}$.
+%A unilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.013\sim0.05$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:ultgraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\textbf{Type I, vesicle BL phase under TG flow}\par\medskip
+\includegraphics[width=\textwidth]{FigureS6.pdf}
+\end{center}
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type I, vesicle bilayer phase under TG flow with
+  flow rates $\dot\gamma=0.005$--$0.044$ ns$^{-1}$. The JP type is the
+  same as Figure~\ref{fig:ultgraw} except with a vesicle-shaped initial
+  configuration rather than a disordered bilayer.
+%A vesicle JP structure under a TG flow with choices of shear rates $\dot\gamma=0.005\sim0.044$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:vetgraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\textbf{Type II, multilamellar phase under TG flow}\par\medskip
+\includegraphics[width=\textwidth]{FigureS7.pdf}
+\end{center}
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type II, multilamellar phase under TG flow with
+  flow rates $\dot\gamma=0.025$--$0.069$~ns$^{-1}$.
+%A multilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.025\sim0.069$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:mltgraw}
+\end{figure}
+
+\begin{figure}[h!]
+\begin{center}
+\textbf{Type III, striated phase under TG flow}\par\medskip
+\includegraphics[width=\textwidth]{FigureS8.pdf}
+\end{center}
+\caption{(a) Relative free energy $F - F_0$, (b) alignment $S_2$, and
+  (c) strain $E$ for Type III, striated phase under TG flow with flow
+  rates $\dot\gamma=0.01$--$0.075$~ns$^{-1}$.
+%A striated JP structure under a TG flow with choices of shear rates $\dot\gamma=0.01\sim0.069$.
+The change in free energy $F$ is plotted in panel (a).
+Panel (b) shows the scalar order parameter $S_2$ over time $t$.
+Panel (c) plots the change of strain parameter $E$ in percentage over time $t$.
+}
+\label{fig:sttgraw}
+\end{figure}
 
 \end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{DRAFT RESULTS BELOW}
-{\bf More results:}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{CS_E.pdf}
-   \includegraphics[width=0.3\textwidth]{CS_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{CS_MSD.pdf}
-  \end{center}
-\caption{A checkerboard in shear flow with shear rates
-  $\dot\gamma=\{0.125, 0.15\}$. We propose the order parameter defined
-  by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.3\textwidth]{CTG_E.pdf}
-   \includegraphics[width=0.3\textwidth]{CTG_LOP.pdf}
-    \includegraphics[width=0.3\textwidth]{CTG_MSD.pdf}
-  \end{center}
-\caption{A checkerboard in Taylor-Green flows when the flow strength $V_0=\{0.2,0.3\}$. }
-\end{figure}
-
-\subsubsection{}
-
-%%%
-
-\section{Governing Equations}
-We consider a suspension of $N_b$ Janus particles in the fluid domain
-$\Omega$.
-The boundary of the $\Omega$ is $\bd\Omega = \Gamma_1 \cup
-\cdots \cup \Gamma_{N_b}$, where $\Gamma_i$ is the boundary of Janus
-particle $i$. We also consider a bounded fluid domain where $\Gamma_0$
-is the fixed boundary of $\Omega$. In this case, $\bd\Omega = \Gamma_0
-\cup \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$.
-
-%%%
-\subsection{Hydrophobic Attraction Potential Mobility Problem} 
-The mathematical formulation is a nonlinear system for the dynamics of a
-collection of rigid Janus particles. For the sake of completeness, we
-summarize the governing equations here, and a complete description is in
-our previous work~\cite{Fu2022_JFM}. The interactions satisfy a
-system of partial differential equations (PDEs) that describe the
-hydrodynamic interactions and hydrophobic interactions. Assuming
-inertial terms are negligible, the solvent is governed by the Stokes
-equations
-\begin{alignat}{3}
-\label{eq:stokes}
-  -\mu \Delta \uu + \nabla p &= \mathbf{0},     && \xx \in \Omega, \\
-  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
-  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
-\end{alignat}
-where $\uu$ is the velocity, $p$ is the pressure, $\uu_\infty$ is the
-background flow, and $\mu$ is the (constant) solvent viscosity. The domain $\Omega
-= \Omega(t)$ is the fluid region surrounding the particles and changes
-shape as the particles move. Since the particles are rigid, the solvent
-velocity satisfies the no-slip rigid body motion boundary condition
-\begin{align}
-  \vv_i + \omega_i (\xx - \aa_i)^\perp = \uu(\xx), 
-    \quad \xx \in \Gamma_i,
-\end{align}
-where $\vv_i$ is the translational velocity and $\omega_i$ is the
-angular velocity. Once these velocities are determined, we use
-second-order Adams-Bashforth to update the particle configuration.
-
-The translational and angular velocities guarantee that the fluid forces
-balance the imposed forces. The imposed forces include the hydrophobic
-interactions that arise so that particles minimize the free energy of
-the structure of the surrounding water molecules. The free energy
-functional is
-\begin{align}
-\label{eq:free_energy}
-  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
-  \,d\xx,
-\end{align}
-where $u$ is an order parameter for the structure of water, $\rho$ is a
-decay length, $C$ is a constant, and $f(u)$ is a potential.
-%$c$ is ``effective" inter-particle distance below which the steric repulsion becomes important.
-Hydrogen-bond persistence times are on the order of picoseconds which is
-much smaller than characteristic time for particle motion.
-%\cite{MaGa13}. 
-Thus we assume $u$ minimizes $F[u]$ for all times. Assuming appropriate
-conditions on $f(u)$,
-% (\cite{evans10}, \S 8.2),
-$u$ satisfies the Euler-Lagrange equation
-\begin{alignat}{3}
-  \label{eq:SL}
-  -\rho^2 \Delta u + \tfrac{1}{2}f'(u) &= 0, && \xx \in \Omega, \\
-  u &= g, && \xx \in \bd\Omega, \\
-  u &\rightarrow 0, \qquad&& |\xx| \rightarrow \infty.
-\end{alignat}
-Equation~\eqref{eq:SL} is solved with a boundary integral equation
-method. The boundary condition $g$ is a material label that is
-transported with the particle.
-
-The particles lower the free energy $F[u]$ of the surrounding water
-by moving. We calculate the rate of change of $F[u]$ using
-variation of the domain. % ~\cite{Fu2018_SIAM,Bandle2015, Schiffer1954, Grinfeld2010}.
-Carrying out this variation yields the stress  
-\begin{align}
-  \label{eq:stress}
-\mathbf{T}
-= C \left[ \rho^{-1} f(u) \mathbf{I}
-  + \rho \left(|\nabla u|^2 \mathbf{I} - 
-  2\nabla u \nabla u^T\right)\right].
-\end{align}
-The imposed forces and torques come from the integration of $\mathbf{T}$
-along the particle boundary. These forces and torques couple the Stokes
-equations \eqref{eq:stokes}, to semilinear elliptic equation
-\eqref{eq:SL}. Solving for the translational and rotational velocities
-gives the particle evolution.
-
-To solve the Stokes equation with the correct boundary conditions, we
-represent the velocity as the of a layer potential with Stokeslets and
-rotlets
-\begin{align}
-  \label{eq:velocity}
-  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
-    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
-    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
-\end{align}
-%
-Then, the density function $\eeta$, translation velocity $\vv_i$ and
-angular velocity $\omega_i$ satisfy
-\begin{alignat}{3}
-  \nonumber
-  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
-    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
-  \label{eq:SKIE}
-    + \sum_{j=1}^{N_b} &
-    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),
-    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
-  \label{eq:mobility1}
-  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, 
-  &&i = 1,\ldots,N_b, \\
-  \label{eq:mobility2}
-  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s &= T_i,
-  &&i = 1,\ldots,N_b.
-\end{alignat}
-
-\subsection{Normal Derivative of Double Layer Potential and HAP Energy}
-
-We adopt the double layer potential to express the solution of \eqref{eq:SL} where the
-condition is $f(u)=u^2$. Then it is given by 
-\begin{align}
-\label{eq:energy_BIE}
-u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy,
-\end{align}
-%
-where $G(\xx)$ is the fundamental solution to the screened Laplace
-equation \eqref{eq:SL} and $\nnu_\yy$ is the outward normal.
-Since the free energy functional can be written as 
-\begin{align}
-\label{eq:free_energy2}
-  E[u(\xx)] &= C\rho \int_\Gamma u \frac{\partial u}{\partial \nnu}  \,\dif s, \quad \xx\in\Gamma_i,
-\end{align}
-%
-we can then refer to the identity (\cite{Hsiao2008}, \S 1.2) to calculate this boundary integral equation without evaluating the normal derivative of the double layer potential directly.
-
-Consider
-\begin{align}
-\nnu_\xx \cdot \nabla_\zz u(\zz) &=\nnu_\xx \cdot \nabla_\zz \int_\Gamma \frac{\partial G(\zz-\yy)}{\partial \nnu_\yy}\sigma(\yy) \,\dif s_\yy\\
-&=\int_\Gamma \nnu_\xx\cdot \left(\nabla_\zz\nabla_\yy^\top  G(\zz-\yy)\right)\cdot \nnu_\yy\sigma(\yy)  \,\dif s_\yy\\
-&=-\int_\Gamma \nnu_\xx\cdot \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\cdot\nnu_\yy\sigma(\yy)\ \dif s_\yy\\
-&=-\int_\Gamma {\bf t}_\xx\cdot\Delta_\yy G(\zz-\yy) {\bf t}_\yy \sigma(\yy)\ \dif s_\yy+\int_\Gamma({\bf t}_\xx\cdot\nabla_\yy)({\bf t}_\yy\cdot\nabla_\yy G(\zz-\yy))\sigma(\yy)\ \dif s_\yy\\
-&= -\int_\Gamma {\bf t}_\xx\cdot\frac1\rho^2 G(\zz-\yy) {\bf t}_\yy \sigma(\yy)\ \dif s_\yy - 
-({\bf t}_\xx\cdot\nabla_\zz)\int_\Gamma \frac{\partial G(\zz-\yy)}{\partial s_\yy}\sigma(\yy)\ \dif s_\yy\\
-&= -\frac1\rho^2 {\bf t}_\xx\cdot \int_\Gamma G(\zz-\yy){\bf t}_\yy \sigma(\yy)\ \dif s_\yy + 
-({\bf t}_\xx \cdot \nabla_\zz)\int_\Gamma G(\zz-\yy)\frac{\partial \sigma(\yy)}{\partial s}\ \dif s_\yy.
-\end{align}
-%
-Here ${\bf t}_\xx$ is the tangent vector at the point $\xx$ and $d/ds$ is the arclength derivative.
-Letting $\zz\to\xx\in\Gamma$, we obtain
-%
-\begin{equation}
-\label{eq:normal_deriv}
-\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) = -\frac1\rho^2 {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx) + \frac{\partial}{\partial s}\SSS\left[\frac{\partial \sigma}{\partial s}\right](\xx).
-\end{equation}
-%
-
-Substituting \eqref{eq:normal_deriv} to \eqref{eq:free_energy2} provides the total energy calculation
-throughout this paper and this expression takes the advantage of not calculating the quadruple layer potential which has well-known obstacle in numerical implementation.
-
-%Suppose we split the solution to the screened Laplace boundary value problem~\eqref{eq:SL}
-%into smooth portion $w_i$ and singular portion $u_i$. That is, 
-%\begin{equation}
-%w_i({\bf x}) = u({\bf x}) - u_i = u({\bf x}) - \int_{\Gamma_i }\left(\pderiv{}{\nnu_\yy}
-%    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma_i(\yy) \,
-%    \dif s_\yy, \quad \xx \in \Gamma_i.
-%\end{equation}
-%Consider the case when $f(u)=u^2$ in~\eqref{eq:free_energy}, we can rewrite the free energy functional as 
-%
-%\begin{align}
-%\label{eq:free_energy2}
-%  E[u(\xx)] &= C\rho \sum_{i=1}^{N_b}\int_{\Gamma_i} u \frac{\partial u}{\partial \nnu}  \,\dif s
-%= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} u \left(\frac{\partial w_i}{\partial \nnu}+\frac{\partial u_i}{\partial \nnu} \right) \, \dif s, \quad \xx\in\Gamma_i.
-%\end{align}
-%%%%
-%Follow the divergence theorem on the last term in the equation above and denote $g_i(x)$ as the boundary data on $\Gamma_i$, we obtain
-%\begin{align}
-%\label{eq:free_energy3}
-%  E[u(\xx)] &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} \left( \nabla u \cdot\nabla u_i + u\Delta u_i\right) \,\dif \xx\right)\\
-%%
-%&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} \,\dif s  + \int_{\mathbb{R}^n\setminus \overline{U}_i} u\Delta u_i\,\dif \xx
-%+\int_{\Gamma_i}\left(u+\frac12\sigma\right)\frac{\partial u_i}{\partial \nnu} \,\dif s     
-%- \int_{\mathbb{R}^n\setminus \overline{U}_i} u\Delta u_i\,\dif \xx \right)\\
-%&= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} u \frac{\partial w_i}{\partial \nnu} + 
-%\left(g_i+\frac12\sigma_i\right)\frac{\partial u_i}{\partial \nnu}   \,\dif s \right), \quad \xx \in \Gamma_i.
-%\end{align}
-%
-%
-%
-
-%  &= C\rho\sum_{i=1}^{N_b}\left(\int_{\Gamma_i} g_i \frac{\partial w_i}{\partial \nnu} 
-% +  \left(u_i+\frac12\sigma\right)  \frac{\partial g_i}{\partial \nnu} \,\dif s - \int_{\mathbb{R}^n\setminus \overline{U}_i}\Delta g_i  \left(u_i+\frac12\sigma\right)  - g_i \left(u_i+\frac12\sigma\right) \,\dif \xx\right) \\
-% &= C\rho\sum_{i=1}^{N_b}\int_{\Gamma_i} g_i \frac{\partial w_i}{\partial \nnu}+ \left(u_i+\frac12\sigma\right)  \frac{\partial g_i}{\partial \nnu}\,\dif s, \quad \xx\in\Gamma_i.
-
-%%
-%$\sigma$ satisfies the second-kind integral equation
-%\begin{equation}
-%\label{eq:screenedSKIE}
-%  g(\xx) = \frac{1}{2}\sigma(\xx) + 
-%    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
-%    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
-%    \dif s_\yy, \quad \xx \in \bd\Omega,
-%\end{equation}
-
-\section{Numerical Results}
-
-\subsection{Self-Assembled Janus Particle with Specific Boundary Conditions}
-
-Distinct morphologies can be obtained from 
-the HAP model by shifting the boundary condition $g(\xx)$.
-Consider the linear case where $f(u) = u^2$.
-This choice makes \eqref{eq:SL} a boundary value
-problem for the screened-Laplace equation
-and the solutions have a boundary layer structure that decays to $0$ in the
-bulk with the decay length $\rho$.
-We consider three kinds of boundary conditions
-on particle $\Gamma_i$:
-\begin{equation}
-  \label{eq:bcs}
-  \begin{tabular}{c|c|c}
-     \text{(i)} & \text{(ii)} & \text{(iii)} \\
-    \hline
-    \rule{0pt}{4ex} 
-      $g(\mathbf{x}) = \displaystyle \frac{1+\cos (\theta_i(\xx))}{\sqrt{3\pi r}}$
-    & $g(\mathbf{x}) = \displaystyle \frac{2+\cos (\theta_i(\xx))}{\sqrt{9\pi r}}$
-    & $g(\mathbf{x}) = \displaystyle \frac{\cos (\theta_i(\xx))}{\sqrt{\pi r}}$
-\end{tabular}
-\end{equation}
-The number $\theta_i(\xx)$ is the angle formed by the position $\xx$,
-the particle center $\aa_i$, and the particle director $\dd_i$.
-(Figure~\ref{fig:flow_map}). The normalizations e.g., $(\pi r)^{-1/2}$,
-provide a uniform surface energy $\int_{\Gamma_i} g^2 \,ds = 1$ for
-circular particles of radius $r$. The cases (ii) and (iii) are obtained
-by applying a vertical shift and scaling to case (i). Using this setup,
-we simulate the dynamics of 60 particles with one set of random initial
-positions and orientations as shown in Figure~\ref{fig:relax}(a)
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.2\textwidth]{LPA.jpg}
-  \includegraphics[width=0.2\textwidth]{LPB.jpg}
-  \includegraphics[width=0.2\textwidth]{LPC.jpg}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:bcs} Boundary conditions characterize the water
-  structure at the particle interface: an amphiphilic particle (left), a
-  hydrophobic particle with anisotropic intensity (middle), a water
-  structure with positive/negative charge (right). The dashed curve is
-  the boundary of the disk and the arrow is its director for each
-  particle.}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.4\textwidth]{Fig2a.png}
-  \includegraphics[width=0.4\textwidth]{Fig2b.png}\\
-  \includegraphics[width=0.4\textwidth]{Fig2c.png}
-  \includegraphics[width=0.4\textwidth]{Fig2d.png}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:relax} (a) Initial configuration for $N_b=60$
-  structures. In order to expedite the self-assembly procedure, all
-  particles are placed in a $8\times8$ box initially. (b)--(d)
-  Equilibrium states for all boundary conditions~\eqref{eq:bcs}(i)--(iii), respectively.
-Colors represent the boundary values that increases from minimum (blue) to maximum (red).
-Panel (b) reaches the equilibrium at $t=1200$; Panel (c) reaches the steady-state at $t=600$; Panel (d) reaches the final state at $t=180$.}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.5\textwidth]{Relax_Energy.jpg}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:relax_energy} Energy profile for all three boundary conditions.}
-\end{figure}
-
-Case (i) models amphiphilic particles.
-Amphiphilic particles have a hydrophobic tail and a hydrophilic head
-and these are accounted for as follows.
-The hydrophilic side takes the value $u =0$.
-This mimics the apolar head of a lipid, for example, which does
-not alter the structure of adjacent waters. The hydrophobic side
-represents hydrocarbons and takes the value 
-$u > 0$. The interaction between particles is attractive,
-and particles will collectively orient their tails toward
-one another. Fig~\ref{fig:relax}(b) demonstrates multiple bilayer structures such as pancake and vesicle shapes.
-
-Multilamelar bilayers arise when both sides of the particle 
-are hydrophobic. 
-The boundary condition \eqref{eq:bcs}(ii) 
-gives a particle with a hydrophobic intensity that is greater
-on the $\theta_i = 0$ side than on the $\theta_i = \pi$ side.
-The initial self-assembly is similar to that in case (i).
-The difference arises in the long-time dynamics where the bilayers
-no longer remain well-separated. 
-Rather, the bilayers form layers 
-as a consequence of the interfacial tension of exposed particle
-heads.%~\cite{Huetal19, deMeetal21}. 
-Figure~\ref{fig:relax}(c) shows the multilamellar structure with 8
-layers when $N_b=60$.  The number of folds depends on several factors,
-for instances, number of particles and initial configurations.
-
-Finally, boundary condition \eqref{eq:bcs}(iii) models a particle whose
-head surface repels the tail surface as proposed in \cite{MaRa76, Ma77}.
-The particles initially form chains with their directors perpendicular
-to the length of the chain. The equilibrium structure resembles a
-checkerboard pattern where each particle coordinates its head with the
-head of three other particles and its tail with the tail of three other
-particles. Figure~\ref{fig:relax}(d) gives an example that this boundary
-condition results a checker board/stripes equilibrium state.
-
-Fig~\ref{fig:relax_energy} shows the energy profile of boundary conditions (i)--(iii) using 
-\eqref{eq:free_energy2} with \eqref{eq:normal_deriv} for normal derivative expression. As expected, for all simulation runs, the total energy of the systems decreases and reaches equilibrium states.
-
-\subsection{Collective Janus Particles Suspended in a Shear Flow}
-%%%
-
-Consider placing the equilibrium state of boundary condition \eqref{eq:bcs} (ii) for 60 particles in a shear flow,
-\begin{equation}
-\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
-\end{equation}
-%
-where $\dot\gamma$ is the shear rate. Fig~\ref{fig:shear_1} (a)--(c) show the snapshots of simulation results when $\dot\gamma=0.05$.
-We measure the ratio of major and minor axes $\lambda$ by adopting an ellipse fitting using the singular value decomposition and track this aspect ratio for this multilamellar structure when the flow is on.
-The result is shown in panel (d) and we observe that the multilamellar structure will be slightly stretched and the aspect ratio $\lambda=3.5$ increases over time.
-%
-Notice that for this simulation, the center of mass position of the
-initial configuration is not at the origin and it is slightly to the
-right of the origin. We also track the aspect ratio $\lambda$ for the
-case that the center of mass position is shifted to the origin. Panel
-(d) also shows that the dynamics of two sets of simulations are
-invariant of center of mass position in a shear flow.
-
-%
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.21\textwidth]{shear_0.png}
-  \includegraphics[width=0.21\textwidth]{shear_1000.png}
-  \includegraphics[width=0.21\textwidth]{shear_2000.png} 
-  \includegraphics[width=0.21\textwidth]{shear_2000.png} \\
-  \includegraphics[width=0.21\textwidth]{shear_checker_0.png}
-  \includegraphics[width=0.21\textwidth]{shear_checker_250.png}
-  \includegraphics[width=0.21\textwidth]{shear_checker_500.png}
-  \includegraphics[width=0.21\textwidth]{shear_checker_750.png} \\
-  \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
-\end{figure}
-%
-
-%Consider the energy profiles for two simulations where the centor of mass is on and off the origin.
-%Fig~\ref{fig:shear_energy1} shows numerical results for both energy profiles and magnitude of energy differences is significantly large when there is a large deformation, for instance, the case when a multi-lamellar structure deformed to a pancake shape.
-%
-%\begin{figure}
-%  \begin{center}
-%  \includegraphics[width=0.5\textwidth]{shear_energy1.jpg}
-%  \end{center}
-%  \vspace{-20pt}  
-%  \caption{\label{fig:shear_energy1} Energy profiles tracked during the simulations using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
-%\end{figure}
-
-%%%
-
-The second set of simulation is putting the equilibrium state of the
-boundary condition \eqref{eq:bcs} (iii), the checker board, in a shear
-flow. After a set of empirical numerical investigations, we obtain a
-critical shear rate $\dot\gamma=0.15$ where the checker board deforms
-into stripes and small groups of JP. Figure~\ref{fig:shear_2}(a)--(d) show configurations when $t=\{0,50,100,150\}$. %The deformation starts with stripe separations
-%
-%\begin{figure}
-%  \begin{center}
-%  \includegraphics[width=0.4\textwidth]{shear_checker_0.png}
-%  \includegraphics[width=0.4\textwidth]{shear_checker_250.png}\\
-%  \includegraphics[width=0.4\textwidth]{shear_checker_500.png}
-%    \includegraphics[width=0.4\textwidth]{shear_checker_750.png}
-%  \end{center}
-%  \vspace{-20pt}  
-%  \caption{\label{fig:shear_2} Snapshots of simulation using boundary condition \eqref{eq:bcs}(iii) in a shear flow when $\dot\gamma=0.15$. }
-%\end{figure}
-
-\subsection{Collective Janus Particles Suspended in a Taylor-Green Flow}
-
-Similar to shear flow simulations, we then place equilibrium states of all boundary conditions \eqref{eq:bcs} in a rotating Taylor-Green Flow with a length scale $l$,
-\begin{equation}
-\uu_\infty(\xx) = V_0 \left(-\cos(l{\bf e}_x\cdot\xx)\sin(l{\bf e}_y\cdot\xx){\bf e}_x+\sin(l{\bf e}_x\cdot\xx)\cos(l{\bf e}_y\cdot\xx){\bf e}_y\right).
-\end{equation}
-%
-The magnitude of the vortex flow is controlled by the velocity scale
-$V_0$.  Similar to the setup in the shear flow cases, we shift the
-center of mass position to the origin then turn on the Taylor-Green flow
-with $V_0=0.1$ and tune the sides of zero-velocity box to $\pi$, i.e.,
-$l=0.5$, Figure~\ref{fig:TG_1}(a)--(c) show three frames of simulation
-results and we track the aspect ratio $\lambda$ described in the
-previous section which is provided in panel (d).  The stiffness of the
-multilamellar structure is able to compete with the flow therefore the
-structure does not deform to any states other than multilamellar shape.
-We also found that the flow strength coefficient above $V_0=0.1$ will
-result to clear group separations during the simulations.  Comparing
-with the case when $V_0=0.2$, we provide a frame in
-Figure~\ref{fig:TG_2}(a) and the energy comparison is shown in panel
-(b). Numerical results validate the phenomenon that a higher
-Taylor-Green vortex flow generates large structure separations with
-higher total energy.
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.4\textwidth]{TG_0.png}
-  \includegraphics[width=0.4\textwidth]{TG_2500.png}\\
-  \includegraphics[width=0.4\textwidth]{TG_5000.png}
-    \includegraphics[width=0.4\textwidth]{TG_dist.jpg}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.4\textwidth]{TG0p2_2000.png}
-  \includegraphics[width=0.4\textwidth]{TG_energy1.jpg}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:TG_2} (a) Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.2$, $l=0.5$, and $t = 400$.
-(b) Energy profiles for two cases $V_0=0.1$ and $V_0=0.2$.
-}
-\end{figure}
-
-\subsection{Steady-State Structure Confined in Narrow Channels}
-
-Here are demonstrations of having JP vesicle and multilamellar
-structure in a narrow channel under a shear flow. Simulation results
-and snapshots are shown in Figures~\ref{fig:confined_vesicle} and
-Figure~\ref{fig:confined_lamellar} where the JP vesicle has $N_b=25$
-particles and JP lamellar has $N_b=40$ particles, respectively. Both
-starting configurations are pre-relaxed and the channel width in the
-narrow part is about 5 length units in the vesicle case and 4 length
-units in the lamellar case.
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.4\textwidth]{VesConf_0.png}
-  \includegraphics[width=0.4\textwidth]{VesConf_2000.png}\\
-  \includegraphics[width=0.4\textwidth]{VesConf_5000.png}
-  \includegraphics[width=0.4\textwidth]{VesConf_10000.png}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:confined_vesicle} A JP vesicle confined in a narrow channel where $N_b=25$ and $\dot\gamma=0.01$.  }
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-  \includegraphics[width=0.4\textwidth]{MultConf_100.png}
-  \includegraphics[width=0.4\textwidth]{MultConf_600.png}\\
-  \includegraphics[width=0.4\textwidth]{MultConf_1200.png}
-  \includegraphics[width=0.4\textwidth]{MultConf_2400.png}
-  \end{center}
-  \vspace{-20pt}  
-  \caption{\label{fig:confined_lamellar} A JP multilamellar structure
-  confined in a narrow channel where $N_b=40$ and $\dot\gamma=0.05$.}
-\end{figure}
-
-\section{Conclusions}
-
-%%%
-
-% If in two-column mode, this environment will change to single-column
-% format so that long equations can be displayed. Use
-% sparingly.
-%\begin{widetext}
-% put long equation here
-%\end{widetext}
-
-% figures should be put into the text as floats.
-% Use the graphics or graphicx packages (distributed with LaTeX2e)
-% and the \includegraphics macro defined in those packages.
-% See the LaTeX Graphics Companion by Michel Goosens, Sebastian Rahtz,
-% and Frank Mittelbach for instance.
-%
-% Here is an example of the general form of a figure:
-% Fill in the caption in the braces of the \caption{} command. Put the label
-% that you will use with \ref{} command in the braces of the \label{} command.
-% Use the figure* environment if the figure should span across the
-% entire page. There is no need to do explicit centering.
-
-% \begin{figure}
-% \includegraphics{}%
-% \caption{\label{}}
-% \end{figure}
-
-% Surround figure environment with turnpage environment for landscape
-% figure
-% \begin{turnpage}
-% \begin{figure}
-% \includegraphics{}%
-% \caption{\label{}}
-% \end{figure}
-% \end{turnpage}
-
-% tables should appear as floats within the text
-%
-% Here is an example of the general form of a table:
-% Fill in the caption in the braces of the \caption{} command. Put the label
-% that you will use with \ref{} command in the braces of the \label{} command.
-% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
-% \begin{tabular}{} command.
-% The ruledtabular enviroment adds doubled rules to table and sets a
-% reasonable default table settings.
-% Use the table* environment to get a full-width table in two-column
-% Add \usepackage{longtable} and the longtable (or longtable*}
-% environment for nicely formatted long tables. Or use the the [H]
-% placement option to break a long table (with less control than 
-% in longtable).
-% \begin{table}%[H] add [H] placement to break table across pages
-% \caption{\label{}}
-% \begin{ruledtabular}
-% \begin{tabular}{}
-% Lines of table here ending with \\
-% \end{tabular}
-% \end{ruledtabular}
-% \end{table}
-
-% Surround table environment with turnpage environment for landscape
-% table
-% \begin{turnpage}
-% \begin{table}
-% \caption{\label{}}
-% \begin{ruledtabular}
-% \begin{tabular}{}
-% \end{tabular}
-% \end{ruledtabular}
-% \end{table}
-% \end{turnpage}
-
-% Specify following sections are appendices. Use \appendix* if there
-% only one appendix.
-%\appendix
-%\section{}
